### 2022-02-16 manuscript/artworks/figures.tex
Initial commit, branched from AdaptaPop

\documentclass[8pt]{beamer}

\usepackage{amssymb,amsfonts,amsmath,amsthm,mathtools}
\usepackage{lmodern}
\usepackage{xfrac, nicefrac}
\usepackage{pgfplots, pgf,tikz}
\usepackage{enumitem}
\usepgfplotslibrary{fillbetween}
\usebackgroundtemplate{\tikz\node[opacity=0]{};}
\setbeamertemplate{footline}[frame number]{}
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{footline}{}
\usefonttheme{serif}
\pgfplotsset{compat=1.16}

\definecolor{RED}{HTML}{EB6231}
\definecolor{YELLOW}{HTML}{E29D26}
\definecolor{BLUE}{HTML}{5D80B4}
\definecolor{LIGHTGREEN}{HTML}{6ABD9B}
\definecolor{GREEN}{HTML}{8FB03E}
\definecolor{PURPLE}{HTML}{BE1E2D}
\definecolor{BROWN}{HTML}{A97C50}
\definecolor{PINK}{HTML}{DA1C5C}

\pgfplotsset{every axis/.append style={line width=1pt}}
\pgfplotscreateplotcyclelist{colors}{LIGHTGREEN\\YELLOW\\RED\\GREEN\\BLUE\\}

\newcommand{\der}{\mathrm{d}}
\newcommand{\e}{\text{e}}
\newcommand{\Ne}{N_{\text{e}}}
\newcommand{\pnps}{\pn / \ps}
\newcommand{\proba}{\mathbb{P}}
\newcommand{\pfix}{\proba_{\text{fix}}}

\newcommand{\ci}{{\color{BLUE}{\textbf{ATT}}}}
\newcommand{\cj}{{\color{YELLOW}\textbf{ATG}}}
\newcommand{\nuci}{{\color{BLUE}\textbf{T}}}
\newcommand{\nucj}{{\color{YELLOW}\textbf{G}}}
\newcommand{\aai}{{\color{BLUE}\textbf{Ile}}}
\newcommand{\aaj}{{\color{YELLOW}\textbf{Met}}}
\newcommand{\Fi}{{F_{\aai}}}
\newcommand{\Fj}{{F_{\aaj}}}
\newcommand{\aaitoj}{{\aai \rightarrow \aaj}}
\newcommand{\nucitoj}{\nuci \rightarrow \nucj}
\newcommand{\citoj}{\ci \rightarrow \cj}
\newcommand{\AtoB}{A \rightarrow B}
\newcommand{\itoj}{ i \rightarrow j }

\begin{document}
	\begin{frame}
		\begin{itemize}[label=$\bullet$]
			\item $s_{\AtoB}$ is the selection coefficient of allele $B$ in a population of $A$.
			\item $w_A$ is the Wrightian fitness (survival $\times$ fecundity) of allele $A$.
			\item $f_A = \ln (w_A) $ is the Malthusian fitness of allele $A$.
		\end{itemize}
		\begin{align*}
			s_{\AtoB} &  = \frac{w_B - w_A}{w_A} \\
							     &  = \frac{w_B}{w_A} - 1 \\
								 &  \simeq \ln \left( \frac{w_B}{w_A} \right) \\
								 &  = \ln (w_B) - \ln (w_A) \\
								 &  = f_B - f_A. \\
		\end{align*}
		$s_{\AtoB}$ = 0.01 means that B is favored with a increased chance of survival or fecundity by 1\%.
	\end{frame}
	\begin{frame}
		For a diploid population of size $\Ne$ the initial frequency of a mutation with selection coefficient $s$ is $p = 1/2\Ne$. Its probability of fixation
denoted $\pfix(s)$ is given by:
		\begin{align*}
		\pfix(s) &  = \frac{1 - \e^{ -2s}}{1 - \e^{ -4 \Ne s}}  \\
		 	     & \simeq \frac{2s}{1 - \e^{ -4 \Ne s}}.
		\end{align*}
		The special case of a neutral allele can be obtained by taking the limit $s \rightarrow 0$:
		\begin{align*}
			\pfix(0) &  = \lim_{s \rightarrow 0} \pfix(s), \\
					 &  = \lim_{s \rightarrow 0} \frac{2s}{1 - \e^{ -4 \Ne s}} \\
					 &  = \lim_{s \rightarrow 0} \frac{2s}{1 - (1 - 4 \Ne s)} \\
					 &  = \lim_{s \rightarrow 0} \frac{2s}{4 \Ne s} \\
					 & = \frac{1}{2 \Ne}.
		\end{align*}
	\end{frame}
	\begin{frame}
		\begin{itemize}[label=$\bullet$]
			\item $\Ne$ is the number of diploid individuals. 
			\item $q$ is the substitution rate of new alleles.
			\item $\mu$ is the mutation rate of new alleles.
			\item $\pfix(s)$ is the probability of fixation of new allele, with selection coefficient $s$.
		\end{itemize}
		\begin{align*}
			q &  = 2 \Ne \times \mu \times \pfix(s), \\
			&  = 2 \Ne \times \mu \times \frac{2s}{1 - \e^{ -4 \Ne s}}, \\
			&  =   \mu \times \frac{S}{1 - \e^{ - S}} \text{ with } S=4 \Ne s.
		\end{align*}
	\end{frame}
	\begin{frame}
		\centering
		\begin{tikzpicture}
			\begin{axis}[
				width=\textwidth,
				height=0.5\textwidth,
				ylabel={Relative fixation probability},
				xlabel={Scaled selection coefficient ($S=4 \Ne s$)},
				cycle list name=colors,
				domain=-5:5,
				ymin=0.0, ymax=5.0,
				samples=200,
				legend entries={$\frac{S}{1 - \e^{-S}}$},
				legend cell align=left,
				minor tick num=2,
				axis x line=bottom,
				axis y line=left,
				legend style={at={(0.02,0.9)},anchor=north west}
				]
				\addplot[line width=2.0pt, BLUE]{ x / (1 - exp(- x))};
				\addplot[name path=B, dashed, YELLOW, line width=0.5pt] coordinates {(-1, 0) (-1, 5)};
				\addplot[name path=A, line width=0pt] coordinates {(-5, 0) (-5, 5)};
				\addplot[black, dashed, line width=1.0pt]{1.0};
				\addplot[black, dashed, line width=1.0pt] coordinates {(0, 0) (0, 5)};
				\addplot[name path=C, dashed, YELLOW, line width=0.5pt] coordinates {(1, 0) (1, 5)};
				\addplot[name path=D, line width=0pt] coordinates {(5, 0) (5, 5)};
				\addplot[fill=RED, opacity=0.2] fill between[ of = A and B];
				\addplot[fill=YELLOW, opacity=0.2] fill between[ of = B and C];
				\addplot[fill=GREEN, opacity=0.2] fill between[ of = C and D];
			\end{axis}
		\end{tikzpicture}
	\end{frame}
	\begin{frame}
		\begin{itemize}[label=$\bullet$]
			\item $q_{\citoj}$ is the substitution rate from codon $\ci$ to $\cj$.
			\item $\mu_{\nucitoj}$ is the mutation rate from nucleotide $\nuci$ to $\nucj$.
			\item $S_{\aaitoj}=4\Ne s_{\aaitoj}$ is the scaled selection coefficient from $\aai$ to $\aaj$.
			\item $\Fi=4\Ne f_{\aai} $ is the scaled fitness of Isoleucine.
			\item $\Fj=4\Ne f_{\aaj} $ is the scaled fitness of Methionine.
		\end{itemize}
		\begin{align*}
				q_{\citoj}  &  = \mu_{\nucitoj}   \dfrac{S_{\aaitoj}}{1 - \e^{-S_{\aaitoj}} } \\
				&  = \mu_{\nucitoj}   \dfrac{\Fj - \Fi}{1 - \e^{\Fi - \Fj} } \\
		\end{align*}
	\end{frame}
	\begin{frame}
	\begin{itemize}[label=$\bullet$]
		\item $q_{\itoj}$ is the substitution rate from codon $i$ to $j$.
		\item $\mu_{\itoj}$ is the mutation rate from codon $i$ to $j$.
		\item $ F_i $ is the scaled fitness of codon $i$ ($F_j$ for codon $j$).
	\end{itemize}
	\begin{equation*}
		\begin{dcases}
			q_{\itoj} = \mu_{\itoj} & \text{for synonymous substitutions} \\
			q_{\itoj} = \mu_{\itoj} \frac{F_j - F_i}{1 - \e^{ F_i - F_j}} & \text{for non-synonymous substitutions}\\
		\end{dcases}
	\end{equation*}
	\end{frame}
	\begin{frame}
		Before fixation or extinction, the probability of an allele to be at a certain frequency can be related to its selection coefficient ($s$) and to the effective population size ($\Ne$).
		\begin{itemize}[label=$\bullet$]
			\item $g(x) \der x $ is the expected time for which the population frequency of derived allele is in the range $(x, x+\der x)$ before eventual absorption
		\end{itemize}
		\begin{align*}
			g(x, S) & = \dfrac{\left( 1 - \e^{- 2 s }\right) \left( 1 - \e^{-4 \Ne s(1-x)}\right)}{ s (1 - \e^{-4 \Ne s})x(1-x)} \\
			        & \approx \dfrac{2 \left( 1 - \e^{-S(1-x)}\right)}{(1 - \e^{-S})x(1-x)}
		\end{align*}
	\end{frame}
	\begin{frame}
		\centering
		\begin{tikzpicture}[
		declare function={
			f(\x,\k)= 2 * (1 - exp(-\k * (1-\x))) / ((1 - exp(- \k))*\x*(1-\x));
		},]
		\begin{axis}[
		width=\textwidth,
		height=0.6\textwidth,
		ylabel={$g(x, S)$},
		xlabel={frequency of the derived allele ($x$)},
		domain=0.05:0.95,
		cycle list name=colors,
		samples=200,
		legend entries={$S=12$, $ S=4$, $S=0$, $S=-4$, $S=-12$},
		legend cell align=left,
		minor tick num=2,
		axis x line=bottom,
		axis y line=left,
		legend style={at={(0.3,0.7)},anchor=north west}
		]
		\addplot{f(\x, 12)};
		\addplot{f(\x, 4)};
		\addplot{2 / x};
		\addplot{f(\x, -4)};
		\addplot{f(\x, -12)};
		\end{axis}
		\end{tikzpicture}
	\end{frame}
	\begin{frame}
		\begin{itemize}[label=$\bullet$]
			\item $n$ is the number of sampled chromosomes (twice the number of individuals).
			\item $1 \leq i \leq n - 1 $ is number of chromosomes with the derived allele.
			\item $\beta_i$ is the number of SNPs with derived allele carried by $i$ chromosomes.
			\item $\beta_i' = \beta_i \times i $ is the scaled $\beta_i$.
		\end{itemize}
	\end{frame}
\begin{frame}
	\begin{align*}
		H & = \frac{2}{n(n-1)} \left( \sum_{i=1}^{n-1} \beta_i \times (n-i) \times i   - \sum_{i=1}^{n-1} \beta_i \times i^2 \right)
	\end{align*}
	\begin{itemize}[label=$\bullet$]
		\item $H = 0$:  no evidence of deviation from neutrality. 
		\item $H > 0$: deficit of SNPs at high frequency (negative selection).
		\item $H < 0$: excess of SNPs at high frequency (positive selection).
	\end{itemize}
\end{frame}
\end{document}

### 2022-02-16 manuscript/include-figures.tex
Initial commit, branched from AdaptaPop

\section{Tajima's D - Fay \& Hu's H}

\subsection{Site-specific mutation-selection codon models.} 
\begin{center}
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.D_tajima.heatmap.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.D_tajima.scatter.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.H_fay_wu.heatmap.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.H_fay_wu.scatter.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.fay_wu.heatmap.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.fay_wu.scatter.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.tajima.heatmap.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.tajima.scatter.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.watterson.heatmap.pdf} \\
\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.watterson.scatter.pdf} \\
\end{center}
\section{Bos taurus}

\subsection{UGBT}

\subsubsection*{SFS for site-specific Mutation-Selection codon models.} 
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.UGBT.MutSel.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth}
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.UGBT.MutSel.normalize.pdf} 
\end{minipage}
\\ 
\section{Chlorocebus sabaeus}

\subsection{Zambia}

\subsubsection*{SFS for site-specific Mutation-Selection codon models.} 
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Zambia.MutSel.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth}
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Zambia.MutSel.normalize.pdf} 
\end{minipage}
\\ 
\section{Homo sapiens}

\subsection{AMR}

\subsubsection*{SFS for site-specific Mutation-Selection codon models.} 
\begin{minipage}{0.49\linewidth} 
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.AMR.MutSel.pdf} 
\end{minipage}
\begin{minipage}{0.49\linewidth}
\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.AMR.MutSel.normalize.pdf} 
\end{minipage}
\\

### 2022-02-16 manuscript/main.tex
Initial commit, branched from AdaptaPop

%! BibTeX Compiler = biber
%TC:ignore
\documentclass{article}

\usepackage{xcolor, colortbl}
\definecolor{BLUELINK}{HTML}{0645AD}
\definecolor{DARKBLUELINK}{HTML}{0B0080}
\definecolor{LIGHTBLUELINK}{HTML}{3366BB}
\definecolor{PURPLELINK}{HTML}{663366}
\definecolor{RED}{HTML}{EB6231}
\definecolor{GREEN}{HTML}{8FB03E}
\definecolor{LIGHTGREY}{gray}{0.9}
\PassOptionsToPackage{hyphens}{url}
\usepackage[colorlinks=false]{hyperref}
% for linking between references, figures, TOC, etc in the pdf document
\hypersetup{colorlinks,
    linkcolor=DARKBLUELINK,
    anchorcolor=DARKBLUELINK,
    citecolor=DARKBLUELINK,
    filecolor=DARKBLUELINK,
    menucolor=DARKBLUELINK,
    urlcolor=BLUELINK
} % Color citation links in purple
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{naturalnames}{hyperref}

\usepackage{biorxiv}
\usepackage[backend=biber,style=nature]{biblatex}
\addbibresource{codon_models.bib}

\usepackage{url}
\usepackage{amssymb,amsfonts,amsmath,amsthm,mathtools}
\usepackage{textcomp}
\usepackage{gensymb}
\usepackage{cancel}
\usepackage{lmodern}
\usepackage{xfrac, nicefrac}
\usepackage{blkarray}
\usepackage{pgf,tikz}
\usetikzlibrary{positioning,arrows,automata,calc}
\usepackage{bm}
\usepackage{listings, enumerate, enumitem}
\usepackage[export]{adjustbox}
\usepackage{graphicx}
\usepackage{tabu}
\usepackage{hhline}
\usepackage{multicol,multirow,array}
\usepackage{etoolbox}
\usepackage{booktabs}

\usepackage[flushleft] {threeparttable}
\usepackage{bbold}
\usepackage{pdfpages}
\usetikzlibrary{positioning}
\usetikzlibrary{arrows,automata}
\pdfinclusioncopyfonts=1
\usepackage{nicefrac} % compact symbols for 1/2, etc.
\usepackage{microtype} % microtypography
\usepackage{lineno}

\newcommand{\specialcell}[2][c]{%
    \begin{tabular}[#1]{@{}c@{}}
        #2
    \end{tabular}}

\newcommand{\UniDimArray}[1]{\bm{#1}}
\newcommand{\BiDimArray}[1]{\bm{#1}}

\DeclareMathOperator{\E}{\mathbb{E}}
\DeclareMathOperator{\Var}{\mathrm{Var}}
\newcommand{\der}{\mathrm{d}}
\newcommand{\angstrom}{\mathrm{\normalfont\AA}}
\newcommand{\e}{\mathrm{e}}
\newcommand{\avg}[1]{\left< #1 \right>} % for average
\newcommand{\Ne}{N_{\mathrm{e}}}
\newcommand{\Ner}{N_{\mathrm{r}}}
\newcommand{\dn}{d_N}
\newcommand{\ds}{d_S}
\newcommand{\dnds}{\dn / \ds}
\newcommand{\pn}{\pi_N}
\newcommand{\ps}{\pi_S}
\newcommand{\pnps}{\pn / \ps}
\newcommand{\proba}{\mathbb{P}}
\newcommand{\pfix}{\proba_{\mathrm{fix}}}
\newcommand{\Pfix}{2 \Ne \proba_{\mathrm{fix}}}
\newcommand{\indice}{a}
\newcommand{\indiceexp}{^{(\indice)}}

\renewcommand{\baselinestretch}{1.5}
\renewcommand{\arraystretch}{0.6}
\linenumbers

\title{Selection coefficients at the phylogenetic and population-genetic scale}

\author{
    \large
    T. {Latrille}$^{1}$, N. {Salamin}$^{1}$\\
    $^{1}$Université de Lausanne, Lausanne, Switzerland
}

\begin{document}
    \maketitle

    \begin{abstract}
        At the phylogenetic scale, recent mutation-selection models provide a direct estimate of the selection coefficient for any mutation in a coding sequence, depending on the amino-acids involved in the mutation.
        At the population-genetic scale, the frequency at which a polymorphism segregates in a population is also a function of its selection coefficient.
        Taking advantage of this relationship between phylogenetic and population genetics, we can assess whether selection coefficients estimated at the phylogenetic scale can predict the frequency of polymorphism.
        In this study, we integrated divergence and polymorphism data across the entire exome for 29 populations across 7 genera, and showed that selection coefficients are correlated at the phylogenetic and population-genetic scales.
        Altogether, our work is paving the way for studies and methods augmenting molecular polymorphism data within species with information about divergence data between species, and by assessing empirically the relationship between phylogenetic and population genetics.
    \end{abstract}

    \keywords{Selection \and phylogenetic \and population genetics \and codon models}

    \tableofcontents

    \section{Introduction}\label{sec:introduction}
%TC:endignore

    In phylogeny-based methods, mutation-selection models provide a nearly-neutral model of evolution by estimating the fitness landscape over amino-acid sequences, for each site of the sequence\cite{yang_mutationselection_2008, halpern_evolutionary_1998, rodrigue_mechanistic_2010}.
    At the mutation-selection balance, the probability for a specific codon to be fixed in the population is proportional to its fitness, and a mutation from a high fitness amino-acid towards a low fitness amino-acid will have a small probability of fixation, genuinely accounting for purifying selection.
    Conversely, only nearly-neutral mutations between high fitness amino acids will tend to be permitted by the model, allowing for the explicit calculation of the scaled selection coefficient of non-synonymous mutations at mutation-selection balance\cite{spielman_relationship_2015, rodrigue_detecting_2017}.
    In this study, we thus first applied mutation-selection codon models to whole exome data from placental mammals, such as to quantify the amino-acid fitness profile for each site of each protein.

    The goal of this study is to assess whether the signal of selection at the phylogenetic and population-genetic scale are correlated.
    The population- and phylogeny-based methods work over very different time scales, for that reason, they might be capturing different signals.
    Nonetheless, we expect sites and proteins under long-term evolution to maintain their signal of selection in several independent lineages for which we computed the unfolded site frequency spectrum (SFS).
    To test this hypothesis, we leverage a pipeline integrating divergence and polymorphism data across the entire exome for 29 populations across 7 genera, namely \textit{Equus}, \textit{Canis}, \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus} and \textit{Homo}.

%TC:ignore

    \section{Methods}\label{sec:methods}

    \subsection*{Phylogenetic dataset}
    protein-coding DNA sequences alignments in placental mammals are extracted from the \href{https://www.orthomam.univ-montp2.fr}{OrthoMaM} database\cite{ranwez_orthomam_2007, douzery_orthomam_2014, scornavacca_orthomam_2019}.
    Genes located on the X, Y and mitochondrial chromosome are discarded from the analysis, since the number of polymorphism, necessary in population-based method, is expected to be different on these sequences.
    Additionally, sequences from the species for which polymorphism are available, as well as their sister species have been discarded from the analysis to ensure independence between the data used in the phylogenetic and population-genetic method.

    \subsection{Selection coefficient in phylogeny-based method}
    Mutation-selection models assume that the protein-coding sequence is at mutation-selection balance under a fixed fitness landscape, which is itself characterized by a fitness vector over the $20$ amino-acid at each site\cite{yang_mutationselection_2008, halpern_evolutionary_1998, rodrigue_mechanistic_2010}.
    Mathematically, the rate of non-synonymous substitution from codon $a$ to codon $b$ ($q_{a \mapsto b}^{(i)}$) at site $i$ of the sequence is equal to the rate of mutation from the underlying DNA change ($\mu_{a \mapsto b}$) multiplied by the scaled probability of fixation of the mutation ($\proba_{a \mapsto b}^{(i)}$).
    Crucially, the probability of fixation depends on the difference of scaled fitness between the amino-acid encoded by the mutated codon ($F_b^{(i)}$) and the fitness of the amino-acid encoded by the original codon ($F_a^{(i)}$) of site $i$\cite{wright_evolution_1931, fisher_genetical_1930}.
    Altogether, the rate of substitution from codon $a$ to $b$ at a given site $i$ is:
    \begin{equation}
        q_{a \mapsto b}^{(i)} = \mu_{a \mapsto b} \proba_{a \mapsto b}^{(i)} = \mu_{a \mapsto b} \dfrac{F_b^{(i)} - F_a^{(i)}}{1 - \e^{F_a^{(i)} - F_b^{(i)}}}.
    \end{equation}

    Fitting the mutation-selection model on a sequence alignment leads to an estimation of the mutation rate matrix ($\UniDimArray{\mu}$) as well as the 20 amino-acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$.

    We ran the Bayesian software \href{https://github.com/bayesiancook/bayescode}{BayesCode} on each protein-coding DNA alignment\cite{lartillot_phylobayes_2013, rodrigue_detecting_2017}.
    Each Monte-Carlo Markov-Chain (MCMC) is run during $2000$ points, with a burn-in of $1000$ points, allowing to compute the mean amino-acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$ across the MCMC.

    \subsection{Polymorphism dataset}

    In order to compare polymorphism and divergence, each SNP (chromosome, position, strand) in the focal species must be matched to its relative position in the protein-coding DNA alignment.
    First, genomic positions are converted to relative position in the coding sequence (CDS) using gene annotation files (GTF format) downloaded from Ensembl (\url{ensembl.org}), we verified the SNP match the reference in the CDS (FASTA format) also downloaded from Ensembl.
    Secondly, relative position in the CDS is converted to position in the multiple sequence alignment (containing gaps) from OrthoMaM database\cite{ranwez_orthomam_2007, douzery_orthomam_2014, scornavacca_orthomam_2019} by doing a global pairwise alignment (Biopython pairwise2) between the CDS fasta and the sequence found in the alignment.
    This conversion from genomic position to position in the alignment is only possible if the assembly used for SNP calling is the same as the one used in the alignment, the GTF annotations and the FASTA sequences.
    We retrieved polymorphism from different projects.
    \textit{Equus caballus} variants called on the EquCab2 assembly in the EVA study PRJEB9799, we considered \textit{Ceratotherium simum simum} as its sister species.
    \textit{Canis familiars} variants called on the CanFam3.1 assembly in the EVA study PRJEB24066, we considered \textit{Ursus maritimus} as its sister species.
    \textit{Bos taurus} variants called on the UMD3.1 assembly in the next-gen project, we considered \textit{Bison bison bison} as its sister species.
    \textit{Ovis aries} variants called on the Oar\_v3.1 assembly in the next-gen project, we considered \textit{Pantholops hodgsonii} as its sister species.
    \textit{Capra Hircus} variants called on the CHIR1 assembly in the next-gen project, we performed a liftover to the ARS1 assembly and considered \textit{Pantholops hodgsonii} as its sister species.
    \textit{Chlorocebus sabaeus} variants are called on the ChlSab1.1 assembly in the EVA study PRJEB22989\cite{svardal_ancient_2017}, we considered \textit{Macaca mulatta} as its sister species.
    \textit{Homo sapiens} variants are called on the GRCh38 assembly in the 1000-genome project\cite{consortium_integrated_2012, the1000genomesprojectconsortium_global_2015}, we considered \textit{Pan troglodytes} as its sister species.
    Variants not inside genes are discarded at the beginning of the analysis.
    Insertions and deletions are not analyzed, and only Single Nucleotide Polymorphisms (SNPs) with only one mutant allele are considered.
    Stop codon mutants are also discarded.
    For populations containing more than $8$ sampled individuals, the site-frequency spectrum (SFS) is subsampled down to $16$ chromosomes ($8$ diploid individuals) without replacement (hyper-geometric distribution) to alleviate the effect of different sampling depth in the $29$ populations.
    Moreover, subsampling mitigate the impact of moderately deleterious mutations segregating at low frequency on $\pnps$, since they are more likely to be discarded than polymorphism segregating at higher frequency.
    SNPs are polarized using the $3$ closest outgroups found in the OrthoMam alignment with est-usfs\cite{keightley_inferring_2018}.
    The Snakemake pipeline for integrating polymorphism and divergence data uses custom scripts written in python 3.8.

    \subsection{Site frequency spectrum}
    The probability of fixation of an allele can be empirically observable, and in the context of a Wright-Fisher processes it is related to selection and drift.
    However, this absorbing fate is not the sole characteristic of the process that relates empirical observable quantities to parameters of the process.
    Along the whole trajectory of an allele, before fixation or extinction, the probability of this allele to be at a certain frequency can be related to its selection coefficient and to the effective population size.
    More precisely, $g(x) \der x $ is the expected time for which the population frequency of derived allele is in the range $(x, x+\der x)$ before eventual absorption, which is derived using the Kolmogorov forward equation as a function of $x$ and $S$:
    \begin{align}
        g(x, s, \Ne) & = \dfrac{\left( 1 - \e^{- 2 s }\right) \left( 1 - \e^{-4 \Ne s(1-x)}\right)}{ s (1 - \e^{-4 \Ne s})x(1-x)} \\
        \Rightarrow g(x, S) & \approx \dfrac{2 \left( 1 - \e^{-S(1-x)}\right)}{(1 - \e^{-S})x(1-x)} \label{eq:expected_time}
    \end{align}

    \begin{center}
        \includegraphics[width=0.4\textwidth, page=4] {artworks/figures.pdf}
        \flushleft
        Expected time at a derived frequency $g(x, S)$ in the vertical axis as a function of the frequency $x$, shown for different scaled selection coefficient.
        Allele with a positive selection coefficient can be observed at high frequency, while alleles with negative selection coefficients are unlikely to be observed at high frequency.
    \end{center}

    This equation is solely valid for a gene with two alleles, a configuration which is rarely observed in empirical data since more than two variants of a gene are usually present in the population.
    However, it is frequent to observe sites inside a gene sequence for which only two alleles are segregating.
    This observation led to the development of a site-specific Wright-Fisher process, assuming that each site follows an independent process.
    Strictly speaking, this model considers a collection of independently evolving loci, meaning without linkage.
    It provides a good approximation if there is free recombination between sites.
    Moreover, the collection is considered infinite whereas the total mutation rate across this infinite collection is considered finite.
    The assumption of an infinite number of sites is necessary to ensure that each mutation arises at a new site, with a Poisson distribution of total rate $u$ per generation for the whole sequence.

    From an empirical perspective, for a sample of $n$ sequences taken in the population, the expected number of sites with $i$ copies of the derived allele (with $i$ ranging from $1$ to $n - 1$) is denoted $G(i, n)$.
    The collection of all $G(i, n)$ generates what is called a site frequency spectrum ({SFS}), which can intuitively be interpreted as the discrete version of the expected time at a derived frequency, readily available from a sample of sequences from a population.
    Given the scaled selection coefficient ($S=4 \Ne s$), and the scaled mutation rate per generation for the whole sequence ($\theta = 4 \Ne u $), each entry of the {SFS} is:
    \begin{align}
        G(i, n) & = \int_{0}^{1}  2 \Ne u g(x, S) \binom{n}{i} x^{i} (1-x)^{n-i} \der x \\
        & = \theta \int_{0}^{1} \dfrac{1 - \e^{-S(1-x)}}{(1 - \e^{-S})x(1-x)} \binom{n}{i} x^{i} (1-x)^{n-i} \der x \\
        & =  \dfrac{\theta }{1 - \e^{-S}} \binom{n}{i} \int_{0}^{1} \left( 1 - \e^{-S(1-x)} \right) x^{i-1} (1-x)^{n-i-1} \der x
    \end{align}

    This site frequency spectrum can be confronted to empirical polymorphic data in order to estimate the scaled selection coefficient of new mutations.
    However, a single selection coefficient for all sites and all mutations is biologically not realistic.
    Accordingly, a distribution of selection coefficients across sites is assumed, which is usually modelled as a continuous distribution, known as the distribution of fitness effects of mutations (DFE).
    Mixing over this distribution, the SFS can then be computed as a function of the underlying DFE, and can thus be estimated based on empirical data\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009}.

    \printbibliography

    \include{include-figures}
\end{document}

### 2022-02-16 install.sh

@@ -1,0 +1,6 @@
+#!/usr/bin/env bash
+git clone https://github.com/ThibaultLatrille/AdaptaPop
+cd AdaptaPop
+sudo apt install -qq -y python3-dev python3-pip
+pip3 install --user scipy numpy matplotlib pandas
+sudo apt install -qq -y snakemake

### 2022-02-16 scripts/gather_sfs_theta.py

@@ -1,0 +1,78 @@
+import argparse
+import os
+import numpy as np
+import pandas as pd
+import statsmodels.api as sm
+
+from libraries_plot import plt, my_dpi, format_pop, sp_sorted, CategorySNP, annotate_heatmap, heatmap, cm, \
+    shiftedColorMap
+
+
+def open_tsv(filepath):
+    ddf = pd.read_csv(filepath, sep="\t")
+    ddf["species"], pop, ddf["method"] = os.path.basename(filepath).replace(".tsv", "").split(".")
+    ddf["pop"] = format_pop(pop.replace("_", " "))
+    return ddf
+
+
+theta_dict = {"watterson": "$\\theta_W$ (Watterson)", "tajima": "$\\theta_{\\pi}$ (Tajima)",
+              "fay_wu": "$\\theta_{H}$ (Fay and Wu)"}
+d_dict = {"D_tajima": "Tajima's $D$", "H_fay_wu": "Fay and Wu's $H$"}
+d_dict.update(theta_dict)
+
+if __name__ == '__main__':
+    parser = argparse.ArgumentParser(formatter_class=argparse.ArgumentDefaultsHelpFormatter)
+    parser.add_argument('-s', '--sfs', required=False, type=str, nargs="+", dest="tsv", help="Input pdf file")
+    parser.add_argument('-o', '--output', required=False, type=str, dest="output", help="Output tex file")
+    parser.add_argument('-l', '--sample_list', required=False, type=str, dest="sample_list", help="Sample list file")
+
+    args = parser.parse_args()
+    df_merge = pd.concat([open_tsv(filepath.replace(".pdf", ".tsv")) for filepath in args.tsv])
+    df_merge["D_tajima"] = df_merge["tajima"] - df_merge["watterson"]
+    df_merge["H_fay_wu"] = df_merge["tajima"] - df_merge["fay_wu"]
+    df_merge.to_csv(args.output, sep="\t", index=False)
+    pop2sp = {pop: sp for (pop, sp), d in df_merge.groupby(["pop", "species"])}
+
+    theta = "tajima"
+    for method, df in df_merge.groupby(["method"]):
+        cat_snps = CategorySNP(method)
+        for d, d_label in d_dict.items():
+            _, ax = plt.subplots(figsize=(1920 / my_dpi, 880 / my_dpi), dpi=my_dpi)
+            for cat in cat_snps.non_syn():
+                x = df[df["category"] == "syn"][theta].values
[…]

### 2022-02-16 scripts/libraries.py

@@ -1,0 +1,47 @@
+#!/usr/bin/env python3
+from collections import namedtuple
+import numpy as np
+from math import floor
+
+confidence_interval = namedtuple('confidence_interval', ['low', 'mean', 'up'])
+sfs_weight = {"watterson": lambda i, n: 1.0 / i, "tajima": lambda i, n: n - i, "fay_wu": lambda i, n: i}
+
+
+def theta(sfs_epsilon, daf_n, weight_method):
+    sfs_theta = sfs_epsilon * np.array(range(1, daf_n))
+    weights = np.array([sfs_weight[weight_method](i, daf_n) for i in range(1, daf_n)])
+    return sum(sfs_theta * weights) / sum(weights)
+
+
+def write_dofe(sfs_syn, sfs_non_syn, l_non_syn, d_non_syn, l_syn, d_syn, k, filepath, sp_focal, sp_sister, is_unfolded,
+               L):
+    sfs_list = [k]
+    for sfs, nbr_site in [(sfs_non_syn, l_non_syn), (sfs_syn, l_syn)]:
+        if is_unfolded:
+            sfs_list += [nbr_site] + [sfs[i] for i in range(1, k)]
+        else:
+            range_sfs = range(1, int(floor(k // 2)) + 1)
+            assert len(range_sfs) * 2 == k
+            sfs_list += [nbr_site] + [(sfs[i] + sfs[k - i]) if k - i != i else sfs[i] for i in range_sfs]
+    sfs_list += [l_non_syn, d_non_syn, l_syn, d_syn]
+
+    dofe_file = open(filepath + ".dofe", 'w')
+    dofe_file.write(f"{sp_focal}+{sp_sister} ({int(L)} sites)\n")
+    if is_unfolded:
+        dofe_file.write("#unfolded\n")
+    dofe_file.write("Summed\t" + "\t".join(map(lambda i: str(int(i)), sfs_list)) + "\n")
+    dofe_file.close()
+
+
+def write_sfs(sfs_syn, sfs_non_syn, l_non_syn, d_non_syn, l_syn, d_syn, k, filepath, sp_focal, sp_sister, div=True):
+    sfs_syn_str = " ".join([str(int(sfs_syn[i])) for i in range(1, k)]) + f"\t{int(l_syn)}"
[…]

### 2022-02-16 scripts/libraries_plot.py

@@ -1,0 +1,282 @@
+from collections import namedtuple
+import numpy as np
+import pandas as pd
+import matplotlib
+
+matplotlib.rcParams["font.family"] = ["Latin Modern Sans"]
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+from matplotlib import cm
+from matplotlib.collections import LineCollection
+from matplotlib.colors import to_rgb, Normalize
+
+fontsize = 16
+fontsize_legend = 14
+my_dpi = 256
+GREEN = "#8FB03E"
+RED = "#EB6231"
+YELLOW = "#E29D26"
+BLUE = "#5D80B4"
+LIGHTGREEN = "#6ABD9B"
+RED_RGB = to_rgb(RED)
+BLUE_RGB = to_rgb(BLUE)
+GREEN_RGB = to_rgb(GREEN)
+GREY_RGB = to_rgb("grey")
+BLACK_RGB = to_rgb("black")
+
+
+def shiftedColorMap(cmap, start=0, midpoint=0.5, stop=1.0, name='shiftedcmap'):
+    '''
+    Function to offset the "center" of a colormap. Useful for
+    data with a negative min and positive max and you want the
+    middle of the colormap's dynamic range to be at zero.
+
+    Input
+    -----
+      cmap : The matplotlib colormap to be altered
+      start : Offset from lowest point in the colormap's range.
+          Defaults to 0.0 (no lower offset). Should be between
+          0.0 and `midpoint`.
+      midpoint : The new center of the colormap. Defaults to
+          0.5 (no shift). Should be between 0.0 and 1.0. In
+          general, this should be  1 - vmax / (vmax + abs(vmin))
+          For example if your data range from -15.0 to +5.0 and
+          you want the center of the colormap at 0.0, `midpoint`
+          should be set to  1 - 5/(5 + 15)) or 0.75
+      stop : Offset from highest point in the colormap's range.
+          Defaults to 1.0 (no upper offset). Should be between
+          `midpoint` and 1.0.
+    '''
+    cdict = {
+        'red': [],
+        'green': [],
+        'blue': [],
+        'alpha': []
+    }
+
+    # regular index to compute the colors
+    reg_index = np.linspace(start, stop, 257)
+
+    # shifted index to match the data
+    shift_index = np.hstack([
[…]

### 2022-02-16 scripts/parse_results.py

@@ -1,0 +1,143 @@
+import argparse
+from glob import glob
+import pandas as pd
+import numpy as np
+from Bio.Phylo.PAML import yn00
+from collections import defaultdict
+from libraries import theta
+
+
+def exp_curve(x, a, b, c):
+    return a - b * np.exp(-c * x)
+
+
+def read_polyDFE(path):
+    dico_out = {}
+    with open(path, 'r') as file:
+        for line in file.readlines():
+            if line.count("=") != 1: continue
+            k, v = line.strip().split("=")
+            for ch in ["E[", "]", "-", " "]:
+                k = k.replace(ch, "")
+            dico_out[k] = float(v)
+    return dico_out
+
+
+def read_yn(path):
+    return yn00.read(path)
+
+
+def parse_line(line):
+    return float(line.split(",")[0].split("=")[-1])
+
+
+if __name__ == '__main__':
+    parser = argparse.ArgumentParser(formatter_class=argparse.ArgumentDefaultsHelpFormatter)
+    parser.add_argument('-f', '--folder', required=False, type=str, dest="folder", help="Folder path")
+    parser.add_argument('-m', '--model', required=False, type=str, dest="model", help="Model name")
+    parser.add_argument('-o', '--output', required=False, type=str, dest="output", help="Output path")
+    args = parser.parse_args()
+    omega_dict = defaultdict(list)
+    phylo_dict = defaultdict(list)
+    for filepath in glob(args.folder + "/*.txt"):
+        f = open(filepath, 'r')
+        while True:
+            omega_line = f.readline()
+            if omega_line.strip() == "":
+                break
+            omega_0_line = f.readline()
+            omega_A_line = f.readline()
+            if "all adaptive" in omega_line:
+                adaptive = True
+            elif ("resampled nearly" in omega_line) or ('all genome' in omega_line):
+                adaptive = False
+            else:
+                continue
+            phylo_dict["OMEGA"].append(parse_line(omega_line))
+            phylo_dict["OMEGA_0"].append(parse_line(omega_0_line))
+            phylo_dict["OMEGA_A"].append(parse_line(omega_A_line))
+            phylo_dict["ADAPTIVE"].append(adaptive)
+
[…]

### 2022-02-16 scripts/plot_sfs.py

@@ -1,0 +1,211 @@
+import argparse
+import gzip
+import numpy as np
+import pandas as pd
+import scipy.stats as sps
+from libraries_plot import plt, CategorySNP, my_dpi, multiline
+from libraries import sfs_weight, theta, write_sfs, write_dofe
+from collections import defaultdict
+
+weak = ["A", "T"]
+strong = ["G", "C"]
+
+
+def daf_to_sfs(daf_list, min_n):
+    array_daf = np.array(daf_list, dtype=np.int64).T
+    return np.array([np.bincount(d, minlength=min_n) for d in array_daf])
+
+
+if __name__ == '__main__':
+    parser = argparse.ArgumentParser(formatter_class=argparse.ArgumentDefaultsHelpFormatter)
+    parser.add_argument('--vcf', required=False, type=str, dest="vcf", help="Input vcf file")
+    parser.add_argument('--method', required=False, type=str, dest="method", help="Sel coeff parameter")
+    parser.add_argument('--output', required=False, type=str, dest="output", help="Output pdf file")
+    parser.add_argument('--genome_results', required=False, type=str, dest="genome",
+                        help="Input genome results tsv file")
+    parser.add_argument('--pop', required=False, type=str, dest="pop", help="Focal population")
+    parser.add_argument('--subsample', required=False, type=int, default=16, dest="subsample")
+    parser.add_argument('--nbr_replicates', required=False, type=int, default=1, dest="nbr_replicates")
+    args = parser.parse_args()
+
+    assert args.method in ["MutSel", "Omega", "Omega_0", "WS", "SW", "SIFT"]
+
+    genome_results = pd.read_csv(args.genome, sep='\t')
+    row = genome_results[genome_results["pop"] == args.pop.replace("_", " ")]
+    assert len(row) > 0
+    Ldn, dn, Lds, ds = row["Ldn"].values[0], row["dn"].values[0], row["Lds"].values[0], row["ds"].values[0]
+    print(f'ratio Ldn/(Lds + Ldn)={Ldn / (Lds + Ldn)}')
+    vcf_file = gzip.open(args.vcf, 'rt')
+    list_non_syn = []
+    max_daf_set = set()
+    snp_dico = defaultdict(list)
+    header = {}
+    for vcf_line in vcf_file:
+        if vcf_line[0] == '#':
[…]

### 2022-02-16 scripts/tex_sfs.py

@@ -1,0 +1,69 @@
+import argparse
+from glob import glob
+from collections import defaultdict
+import os
+from libraries_plot import format_pop
+
+dict_method = {"MutSel": "site-specific Mutation-Selection codon models.",
+               "Omega": "site-specific codon models.",
+               "Omega 0": "site-specific Mutation-Selection codon models (average over all amino acids).",
+               "SIFT": "SIFT score",
+               "WS": "weak to strong mutations (AT$\\rightarrow$GC)",
+               "SW": "strong to weak mutations (GC$\\rightarrow$AT)"}
+
+if __name__ == '__main__':
+    parser = argparse.ArgumentParser(formatter_class=argparse.ArgumentDefaultsHelpFormatter)
+    parser.add_argument('--sfs', required=False, type=str, nargs="+", dest="sfs", help="Input sfs file (pdf)")
+    parser.add_argument('--tex_doc', required=False, type=str, dest="tex_doc", help="Main document tex file")
+    parser.add_argument('--results', required=False, type=str, dest="results", help="Results tsv file")
+    parser.add_argument('--tex_include', required=False, type=str, dest="tex_include", help="Include tex file")
+    args = parser.parse_args()
+
+    heatmap_dict = defaultdict(list)
+    for result in sorted(glob(f"{os.path.dirname(args.results)}/*.pdf")):
+        method, theta, plot = os.path.basename(result).replace(".pdf", "").replace("_", " ").split(".")
+        heatmap_dict[method].append(result)
+
+    o = open(args.tex_include, 'w')
+    o.write("\\section{Tajima's D - Fay \\& Hu's H} \n \n")
+    for method, list_heatmap in heatmap_dict.items():
+        o.write("\\subsection{" + dict_method[method].capitalize() + '} \n')
+        o.write("\\begin{center}\n")
+        for plot in list_heatmap:
+            o.write("\\includegraphics[width=0.75\\linewidth, page=1]{" + plot + "} \\\\\n")
+        o.write("\\end{center}\n")
+
+    nested_dict = defaultdict(lambda: defaultdict(dict))
+    for sfs in sorted(args.sfs):
+        sp, pop, method = os.path.basename(sfs).replace(".pdf", "").replace("_", " ").split(".")
+        nested_dict[sp][pop][method] = sfs
+
+    for sp, nested_dict_1 in nested_dict.items():
+        o.write("\\section{" + sp + "} \n \n")
[…]

### 2022-02-22 manuscript/include-figures.tex
Refactored call to main(). DFE with SIFT scores

@@
 \begin{center}
-\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.D_tajima.heatmap.pdf} \\
-\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.D_tajima.scatter.pdf} \\
-\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.H_fay_wu.heatmap.pdf} \\
-\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.H_fay_wu.scatter.pdf} \\
-\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.fay_wu.heatmap.pdf} \\
-\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.fay_wu.scatter.pdf} \\
-\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.tajima.heatmap.pdf} \\
-\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.tajima.scatter.pdf} \\
-\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.watterson.heatmap.pdf} \\
-\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.watterson.scatter.pdf} \\
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/DFE.MutSel.P(S<0).heatmap.pdf} \\
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/DFE.MutSel.P(S=0).heatmap.pdf} \\
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/DFE.MutSel.P(S>0).heatmap.pdf} \\
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.MutSel.D_tajima.heatmap.pdf} \\
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.MutSel.H_fay_wu.heatmap.pdf} \\
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.MutSel.fay_wu.heatmap.pdf} \\
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.MutSel.tajima.heatmap.pdf} \\
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.MutSel.watterson.heatmap.pdf} \\
+\end{center}
+\subsection{Site-specific codon models.} 
+\begin{center}
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/DFE.Omega.P(S<0).heatmap.pdf} \\
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/DFE.Omega.P(S=0).heatmap.pdf} \\
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/DFE.Omega.P(S>0).heatmap.pdf} \\
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.Omega.D_tajima.heatmap.pdf} \\
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.Omega.H_fay_wu.heatmap.pdf} \\
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.Omega.fay_wu.heatmap.pdf} \\
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.Omega.tajima.heatmap.pdf} \\
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.Omega.watterson.heatmap.pdf} \\
+\end{center}
+\subsection{Sift score} 
+\begin{center}
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/DFE.SIFT.P(S<0).heatmap.pdf} \\
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/DFE.SIFT.P(S=0).heatmap.pdf} \\
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/DFE.SIFT.P(S>0).heatmap.pdf} \\
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.SIFT.D_tajima.heatmap.pdf} \\
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.SIFT.H_fay_wu.heatmap.pdf} \\
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.SIFT.fay_wu.heatmap.pdf} \\
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.SIFT.tajima.heatmap.pdf} \\
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.SIFT.watterson.heatmap.pdf} \\
 \end{center}
@@
 
+\subsection{IRBT}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.IRBT.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.IRBT.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.IRBT.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.IRBT.MutSel.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{Site-specific codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.IRBT.Omega.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.IRBT.Omega.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.IRBT.Omega.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.IRBT.Omega.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{SIFT score} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.IRBT.SIFT.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.IRBT.SIFT.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.IRBT.SIFT.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.IRBT.SIFT_vs_MutSel.pdf} 
+\end{minipage}
+\\ 
 \subsection{UGBT}
 
-\subsubsection*{SFS for site-specific Mutation-Selection codon models.} 
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
 \begin{minipage}{0.49\linewidth} 
@@
 \end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.UGBT.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.UGBT.MutSel.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{Site-specific codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.UGBT.Omega.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.UGBT.Omega.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.UGBT.Omega.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.UGBT.Omega.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{SIFT score} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.UGBT.SIFT.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.UGBT.SIFT.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.UGBT.SIFT.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.UGBT.SIFT_vs_MutSel.pdf} 
+\end{minipage}
+\\ 
+\section{Canis familiaris}
+
+\subsection{Canis}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Canis_familiaris.dogs.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Canis_familiaris.dogs.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Canis_familiaris.dogs.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Canis_familiaris.dogs.MutSel.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{Site-specific codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Canis_familiaris.dogs.Omega.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Canis_familiaris.dogs.Omega.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Canis_familiaris.dogs.Omega.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Canis_familiaris.dogs.Omega.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{SIFT score} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Canis_familiaris.dogs.SIFT.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Canis_familiaris.dogs.SIFT.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Canis_familiaris.dogs.SIFT.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Canis_familiaris.dogs.SIFT_vs_MutSel.pdf} 
+\end{minipage}
+\\ 
+\section{Capra hircus}
+
+\subsection{AUCH}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.AUCH.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.AUCH.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.AUCH.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.AUCH.MutSel.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{Site-specific codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.AUCH.Omega.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.AUCH.Omega.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.AUCH.Omega.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.AUCH.Omega.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{SIFT score} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.AUCH.SIFT.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.AUCH.SIFT.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.AUCH.SIFT.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.AUCH.SIFT_vs_MutSel.pdf} 
+\end{minipage}
+\\ 
+\subsection{FRCH}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.FRCH.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.FRCH.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.FRCH.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.FRCH.MutSel.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{Site-specific codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.FRCH.Omega.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.FRCH.Omega.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.FRCH.Omega.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.FRCH.Omega.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{SIFT score} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.FRCH.SIFT.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.FRCH.SIFT.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.FRCH.SIFT.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.FRCH.SIFT_vs_MutSel.pdf} 
+\end{minipage}
+\\ 
+\subsection{IRCA}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCA.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCA.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCA.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCA.MutSel.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{Site-specific codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCA.Omega.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCA.Omega.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCA.Omega.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCA.Omega.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{SIFT score} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCA.SIFT.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCA.SIFT.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCA.SIFT.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCA.SIFT_vs_MutSel.pdf} 
+\end{minipage}
+\\ 
+\subsection{IRCH}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCH.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCH.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCH.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCH.MutSel.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{Site-specific codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCH.Omega.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCH.Omega.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCH.Omega.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCH.Omega.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{SIFT score} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCH.SIFT.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCH.SIFT.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCH.SIFT.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCH.SIFT_vs_MutSel.pdf} 
+\end{minipage}
+\\ 
+\subsection{ITCH}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.ITCH.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.ITCH.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.ITCH.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.ITCH.MutSel.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{Site-specific codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.ITCH.Omega.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.ITCH.Omega.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.ITCH.Omega.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.ITCH.Omega.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{SIFT score} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.ITCH.SIFT.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.ITCH.SIFT.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.ITCH.SIFT.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.ITCH.SIFT_vs_MutSel.pdf} 
+\end{minipage}
+\\ 
+\subsection{MOCH}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.MOCH.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.MOCH.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.MOCH.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.MOCH.MutSel.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{Site-specific codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.MOCH.Omega.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.MOCH.Omega.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.MOCH.Omega.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.MOCH.Omega.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{SIFT score} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.MOCH.SIFT.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.MOCH.SIFT.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.MOCH.SIFT.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.MOCH.SIFT_vs_MutSel.pdf} 
+\end{minipage}
 \\ 
@@
 
+\subsection{Barbados}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Barbados.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Barbados.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Barbados.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Barbados.MutSel.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{Site-specific codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Barbados.Omega.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Barbados.Omega.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Barbados.Omega.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Barbados.Omega.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsection{Central African Republic (CAR)}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{Site-specific codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Central_African_Republic.Omega.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Central_African_Republic.Omega.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Central_African_Republic.Omega.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Central_African_Republic.Omega.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsection{Ethiopia}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{Site-specific codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Ethiopia.Omega.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Ethiopia.Omega.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Ethiopia.Omega.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Ethiopia.Omega.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsection{Gambia}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Gambia.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Gambia.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Gambia.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Gambia.MutSel.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{Site-specific codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Gambia.Omega.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Gambia.Omega.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Gambia.Omega.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Gambia.Omega.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsection{Kenya}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Kenya.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Kenya.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Kenya.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Kenya.MutSel.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{Site-specific codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Kenya.Omega.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Kenya.Omega.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Kenya.Omega.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Kenya.Omega.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsection{Nevis}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Nevis.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Nevis.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Nevis.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Nevis.MutSel.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{Site-specific codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Nevis.Omega.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Nevis.Omega.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Nevis.Omega.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Nevis.Omega.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsection{Saint Kitts (SK)}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Saint_Kitts.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Saint_Kitts.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Saint_Kitts.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Saint_Kitts.MutSel.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{Site-specific codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Saint_Kitts.Omega.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Saint_Kitts.Omega.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Saint_Kitts.Omega.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Saint_Kitts.Omega.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsection{South Africa (SA)}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.South_Africa.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.South_Africa.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.South_Africa.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.South_Africa.MutSel.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{Site-specific codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.South_Africa.Omega.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.South_Africa.Omega.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.South_Africa.Omega.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.South_Africa.Omega.histogram.pdf} 
+\end{minipage}
+\\ 
 \subsection{Zambia}
 
-\subsubsection*{SFS for site-specific Mutation-Selection codon models.} 
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
 \begin{minipage}{0.49\linewidth} 
@@
 \end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Zambia.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Zambia.MutSel.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{Site-specific codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Zambia.Omega.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Zambia.Omega.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Zambia.Omega.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Zambia.Omega.histogram.pdf} 
+\end{minipage}
+\\ 
+\section{Equus caballus}
+
+\subsection{Equus}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Equus_caballus.up.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Equus_caballus.up.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Equus_caballus.up.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Equus_caballus.up.MutSel.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{Site-specific codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Equus_caballus.up.Omega.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Equus_caballus.up.Omega.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Equus_caballus.up.Omega.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Equus_caballus.up.Omega.histogram.pdf} 
+\end{minipage}
 \\ 
@@
 
+\subsection{AFR}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.AFR.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.AFR.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.AFR.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.AFR.MutSel.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{Site-specific codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.AFR.Omega.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.AFR.Omega.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.AFR.Omega.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.AFR.Omega.histogram.pdf} 
+\end{minipage}
+\\ 
 \subsection{AMR}
 
-\subsubsection*{SFS for site-specific Mutation-Selection codon models.} 
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
 \begin{minipage}{0.49\linewidth} 
@@
 \end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.AMR.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.AMR.MutSel.histogram.pdf} 
+\end{minipage}
 \\ 
+\subsubsection*{Site-specific codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.AMR.Omega.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.AMR.Omega.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.AMR.Omega.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.AMR.Omega.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsection{EAS}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.EAS.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.EAS.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.EAS.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.EAS.MutSel.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{Site-specific codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.EAS.Omega.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.EAS.Omega.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.EAS.Omega.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.EAS.Omega.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsection{EUR}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.EUR.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.EUR.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.EUR.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.EUR.MutSel.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{Site-specific codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.EUR.Omega.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.EUR.Omega.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.EUR.Omega.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.EUR.Omega.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsection{SAS}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.SAS.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.SAS.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.SAS.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.SAS.MutSel.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{Site-specific codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.SAS.Omega.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.SAS.Omega.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.SAS.Omega.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.SAS.Omega.histogram.pdf} 
+\end{minipage}
+\\ 
+\section{Ovis aries}
+
+\subsection{IROA}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROA.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROA.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROA.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROA.MutSel.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{Site-specific codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROA.Omega.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROA.Omega.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROA.Omega.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROA.Omega.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{SIFT score} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROA.SIFT.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROA.SIFT.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROA.SIFT.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROA.SIFT_vs_MutSel.pdf} 
+\end{minipage}
+\\ 
+\subsection{IROO}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROO.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROO.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROO.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROO.MutSel.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{Site-specific codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROO.Omega.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROO.Omega.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROO.Omega.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROO.Omega.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{SIFT score} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROO.SIFT.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROO.SIFT.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROO.SIFT.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROO.SIFT_vs_MutSel.pdf} 
+\end{minipage}
+\\ 
+\subsection{IROV}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROV.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROV.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROV.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROV.MutSel.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{Site-specific codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROV.Omega.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROV.Omega.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROV.Omega.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROV.Omega.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{SIFT score} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROV.SIFT.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROV.SIFT.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROV.SIFT.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROV.SIFT_vs_MutSel.pdf} 
+\end{minipage}
+\\ 
+\subsection{ISGC}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.ISGC.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.ISGC.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.ISGC.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.ISGC.MutSel.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{Site-specific codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.ISGC.Omega.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.ISGC.Omega.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.ISGC.Omega.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.ISGC.Omega.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{SIFT score} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.ISGC.SIFT.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.ISGC.SIFT.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.ISGC.SIFT.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.ISGC.SIFT_vs_MutSel.pdf} 
+\end{minipage}
+\\ 
+\subsection{MOOA}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.MOOA.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.MOOA.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.MOOA.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.MOOA.MutSel.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{Site-specific codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.MOOA.Omega.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.MOOA.Omega.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.MOOA.Omega.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.MOOA.Omega.histogram.pdf} 
+\end{minipage}
+\\ 
+\subsubsection*{SIFT score} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.MOOA.SIFT.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.MOOA.SIFT.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.MOOA.SIFT.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.MOOA.SIFT_vs_MutSel.pdf} 
+\end{minipage}
+\\

### 2022-02-22 scripts/libraries.py

@@ -2,6 +2,27 @@
 from collections import namedtuple
 import numpy as np
 from math import floor
+import matplotlib
+
+matplotlib.rcParams["font.family"] = ["Latin Modern Sans"]
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+from matplotlib.collections import LineCollection
+from matplotlib.colors import to_rgb
+
+fontsize = 16
+fontsize_legend = 14
+my_dpi = 256
+GREEN = "#8FB03E"
+RED = "#EB6231"
+YELLOW = "#E29D26"
+BLUE = "#5D80B4"
+LIGHTGREEN = "#6ABD9B"
+RED_RGB = to_rgb(RED)
+BLUE_RGB = to_rgb(BLUE)
+GREEN_RGB = to_rgb(GREEN)
+GREY_RGB = to_rgb("grey")
+BLACK_RGB = to_rgb("black")
 
 confidence_interval = namedtuple('confidence_interval', ['low', 'mean', 'up'])
 sfs_weight = {"watterson": lambda i, n: 1.0 / i, "tajima": lambda i, n: n - i, "fay_wu": lambda i, n: i}
@@ -45,3 +66,192 @@ def write_sfs(sfs_syn, sfs_non_syn, l_non_syn, d_non_syn, l_syn, d_syn, k, filep
     sfs_file.write(sfs_syn_str + "\n")
     sfs_file.write(sfs_non_syn_str + "\n")
     sfs_file.close()
+
+
+def shiftedColorMap(cmap, start=0, midpoint=0.5, stop=1.0, name='shiftedcmap'):
+    '''
+    Function to offset the "center" of a colormap. Useful for
+    data with a negative min and positive max and you want the
+    middle of the colormap's dynamic range to be at zero.
+
+    Input
+    -----
+      cmap : The matplotlib colormap to be altered
+      start : Offset from lowest point in the colormap's range.
+          Defaults to 0.0 (no lower offset). Should be between
+          0.0 and `midpoint`.
+      midpoint : The new center of the colormap. Defaults to
+          0.5 (no shift). Should be between 0.0 and 1.0. In
+          general, this should be  1 - vmax / (vmax + abs(vmin))
+          For example if your data range from -15.0 to +5.0 and
+          you want the center of the colormap at 0.0, `midpoint`
+          should be set to  1 - 5/(5 + 15)) or 0.75
+      stop : Offset from highest point in the colormap's range.
[…]

### 2022-02-22 scripts/libraries_plot.py

@@ -1,282 +1,0 @@
-from collections import namedtuple
-import numpy as np
-import pandas as pd
-import matplotlib
-
-matplotlib.rcParams["font.family"] = ["Latin Modern Sans"]
-matplotlib.use('Agg')
-import matplotlib.pyplot as plt
-from matplotlib import cm
-from matplotlib.collections import LineCollection
-from matplotlib.colors import to_rgb, Normalize
-
-fontsize = 16
-fontsize_legend = 14
-my_dpi = 256
-GREEN = "#8FB03E"
-RED = "#EB6231"
-YELLOW = "#E29D26"
-BLUE = "#5D80B4"
-LIGHTGREEN = "#6ABD9B"
-RED_RGB = to_rgb(RED)
-BLUE_RGB = to_rgb(BLUE)
-GREEN_RGB = to_rgb(GREEN)
-GREY_RGB = to_rgb("grey")
-BLACK_RGB = to_rgb("black")
-
-
-def shiftedColorMap(cmap, start=0, midpoint=0.5, stop=1.0, name='shiftedcmap'):
-    '''
-    Function to offset the "center" of a colormap. Useful for
-    data with a negative min and positive max and you want the
-    middle of the colormap's dynamic range to be at zero.
-
-    Input
-    -----
-      cmap : The matplotlib colormap to be altered
-      start : Offset from lowest point in the colormap's range.
-          Defaults to 0.0 (no lower offset). Should be between
-          0.0 and `midpoint`.
-      midpoint : The new center of the colormap. Defaults to
-          0.5 (no shift). Should be between 0.0 and 1.0. In
-          general, this should be  1 - vmax / (vmax + abs(vmin))
-          For example if your data range from -15.0 to +5.0 and
-          you want the center of the colormap at 0.0, `midpoint`
-          should be set to  1 - 5/(5 + 15)) or 0.75
-      stop : Offset from highest point in the colormap's range.
-          Defaults to 1.0 (no upper offset). Should be between
-          `midpoint` and 1.0.
-    '''
-    cdict = {
-        'red': [],
-        'green': [],
-        'blue': [],
-        'alpha': []
-    }
-
-    # regular index to compute the colors
-    reg_index = np.linspace(start, stop, 257)
-
-    # shifted index to match the data
-    shift_index = np.hstack([
[…]

### 2022-02-22 scripts/parse_results.py

@@ -1,143 +1,0 @@
-import argparse
-from glob import glob
-import pandas as pd
-import numpy as np
-from Bio.Phylo.PAML import yn00
-from collections import defaultdict
-from libraries import theta
-
-
-def exp_curve(x, a, b, c):
-    return a - b * np.exp(-c * x)
-
-
-def read_polyDFE(path):
-    dico_out = {}
-    with open(path, 'r') as file:
-        for line in file.readlines():
-            if line.count("=") != 1: continue
-            k, v = line.strip().split("=")
-            for ch in ["E[", "]", "-", " "]:
-                k = k.replace(ch, "")
-            dico_out[k] = float(v)
-    return dico_out
-
-
-def read_yn(path):
-    return yn00.read(path)
-
-
-def parse_line(line):
-    return float(line.split(",")[0].split("=")[-1])
-
-
-if __name__ == '__main__':
-    parser = argparse.ArgumentParser(formatter_class=argparse.ArgumentDefaultsHelpFormatter)
-    parser.add_argument('-f', '--folder', required=False, type=str, dest="folder", help="Folder path")
-    parser.add_argument('-m', '--model', required=False, type=str, dest="model", help="Model name")
-    parser.add_argument('-o', '--output', required=False, type=str, dest="output", help="Output path")
-    args = parser.parse_args()
-    omega_dict = defaultdict(list)
-    phylo_dict = defaultdict(list)
-    for filepath in glob(args.folder + "/*.txt"):
-        f = open(filepath, 'r')
-        while True:
-            omega_line = f.readline()
-            if omega_line.strip() == "":
-                break
-            omega_0_line = f.readline()
-            omega_A_line = f.readline()
-            if "all adaptive" in omega_line:
-                adaptive = True
-            elif ("resampled nearly" in omega_line) or ('all genome' in omega_line):
-                adaptive = False
-            else:
-                continue
-            phylo_dict["OMEGA"].append(parse_line(omega_line))
-            phylo_dict["OMEGA_0"].append(parse_line(omega_0_line))
-            phylo_dict["OMEGA_A"].append(parse_line(omega_A_line))
-            phylo_dict["ADAPTIVE"].append(adaptive)
-
[…]

### 2022-02-22 scripts/parse_results_DFE.py

@@ -4,11 +4,11 @@ import argparse
 import numpy as np
 import pandas as pd
 from scipy.stats import expon, gamma
-from libraries_plot import plt, CategorySNP, BLUE, my_dpi
+from libraries import plt, CategorySNP, my_dpi
 
 
 def read_polyDFE(path):
-    out = {}
+    out_polyDFE = {}
     with open(path, 'r') as f:
         for line in f:
             if "Model: C" in line or "Model: D" in line:
@@ -18,16 +18,16 @@ def read_polyDFE(path):
                 values = re.sub(' +', ' ', f.readline().replace("--", "").strip()).split(" ")
                 if "Model: C" in line:
                     for h_i, h in enumerate(header):
-                        out[h] = float(values[h_i])
-                    out["S_d"] = -out["S_d"]
+                        out_polyDFE[h] = float(values[h_i])
+                    out_polyDFE["S_d"] = -out_polyDFE["S_d"]
                 elif "Model: D" in line:
                     for v_i, v in enumerate(values):
-                        out[f"s_{v_i + 1}"] = float(header[v_i * 2 + 1])
-                        out[f"p(S={header[v_i * 2 + 1]})"] = float(v)
+                        out_polyDFE[f"S_{v_i + 1}"] = float(header[v_i * 2 + 1])
+                        out_polyDFE[f"p(S={header[v_i * 2 + 1]})"] = float(v)
             if "alpha_dfe" in line:
                 k, v = line.strip().split("=")
-                out["$\\alpha$"] = float(v)
-    return out
+                out_polyDFE["$\\alpha$"] = float(v)
+    return out_polyDFE
 
 
 def read_grapes(path):
@@ -38,31 +38,36 @@ def read_grapes(path):
             "$\\alpha$": float(ge_df["alpha"])}
 
 
-if __name__ == '__main__':
-    parser = argparse.ArgumentParser(formatter_class=argparse.ArgumentDefaultsHelpFormatter)
-    parser.add_argument('-i', '--input', required=False, type=str, nargs="+", dest="input", help="Input polyDFE file")
-    parser.add_argument('-o', '--output', required=False, type=str, dest="output", help="Output tex file")
-    parser.add_argument('-l', '--sample_list', required=False, type=str, dest="sample_list", help="Sample list file")
[…]

### 2022-02-22 scripts/plot_heatmap.py

@@ -1,0 +1,87 @@
+import os
+import argparse
+import numpy as np
+import pandas as pd
+import statsmodels.api as sm
+from matplotlib import cm
+from libraries import plt, my_dpi, format_pop, sp_sorted, CategorySNP, annotate_heatmap, heatmap, shiftedColorMap
+
+theta_dict = {"watterson": "Watterson $\\theta_W$", "tajima": "Tajima $\\theta_{\\pi}$ ",
+              "fay_wu": "Fay and Wu $\\theta_{H}$"}
+
+
+def open_tsv(filepath):
+    ddf = pd.read_csv(filepath, sep="\t")
+    ddf["species"], pop, ddf["method"] = os.path.basename(filepath).replace(".tsv", "").split(".")[:3]
+    ddf["pop"] = format_pop(pop.replace("_", " "))
+    return ddf
+
+
+def scatter_plot(cat_snps, df, d, d_dict, file):
+    theta = "tajima"
+    _, _ = plt.subplots(figsize=(1920 / my_dpi, 880 / my_dpi), dpi=my_dpi)
+    for cat in cat_snps.non_syn():
+        x = df[df["category"] == "syn"][theta].values
+        y = df[df["category"] == cat][d].values
+        plt.scatter(x, y, color=cat_snps.color(cat))
+        model = sm.OLS(y, sm.add_constant(x))
+        r = model.fit()
+        b, a = r.params[0:2]
+        idf = np.linspace(min(x), max(x), 100)
+        sign = '+' if float(b) > 0 else '-'
+        label = f"{cat_snps.label(cat)}: $y={a:.2g}x {sign} {abs(b):.2g}$ ($r^2={r.rsquared:.2g})$"
+        plt.plot(idf, a * idf + b, '-', color=cat_snps.color(cat), label=label)
+    plt.xlabel(theta_dict[theta])
+    plt.ylabel(f"{d_dict[d]}")
+    plt.legend()
+    plt.tight_layout()
+    plt.savefig(file, format="pdf")
+    plt.clf()
+    plt.close("all")
+
+
+def main(args):
+    df_merge = pd.concat([open_tsv(filepath) for filepath in args.tsv])
+    if ("tajima" in df_merge) and ("watterson" in df_merge) and ("fay_wu" in df_merge):
+        df_merge["D_tajima"] = df_merge["tajima"] - df_merge["watterson"]
+        df_merge["H_fay_wu"] = df_merge["tajima"] - df_merge["fay_wu"]
[…]

### 2022-02-22 scripts/plot_sfs.py

@@ -3,9 +3,8 @@ import gzip
 import numpy as np
 import pandas as pd
 import scipy.stats as sps
-from libraries_plot import plt, CategorySNP, my_dpi, multiline
-from libraries import sfs_weight, theta, write_sfs, write_dofe
 from collections import defaultdict
+from libraries import plt, CategorySNP, my_dpi, multiline, sfs_weight, theta, write_sfs, write_dofe
 
 weak = ["A", "T"]
 strong = ["G", "C"]
@@ -16,35 +15,16 @@ def daf_to_sfs(daf_list, min_n):
     return np.array([np.bincount(d, minlength=min_n) for d in array_daf])
 
 
-if __name__ == '__main__':
-    parser = argparse.ArgumentParser(formatter_class=argparse.ArgumentDefaultsHelpFormatter)
-    parser.add_argument('--vcf', required=False, type=str, dest="vcf", help="Input vcf file")
-    parser.add_argument('--method', required=False, type=str, dest="method", help="Sel coeff parameter")
-    parser.add_argument('--output', required=False, type=str, dest="output", help="Output pdf file")
-    parser.add_argument('--genome_results', required=False, type=str, dest="genome",
-                        help="Input genome results tsv file")
-    parser.add_argument('--pop', required=False, type=str, dest="pop", help="Focal population")
-    parser.add_argument('--subsample', required=False, type=int, default=16, dest="subsample")
-    parser.add_argument('--nbr_replicates', required=False, type=int, default=1, dest="nbr_replicates")
-    args = parser.parse_args()
-
-    assert args.method in ["MutSel", "Omega", "Omega_0", "WS", "SW", "SIFT"]
-
-    genome_results = pd.read_csv(args.genome, sep='\t')
-    row = genome_results[genome_results["pop"] == args.pop.replace("_", " ")]
-    assert len(row) > 0
-    Ldn, dn, Lds, ds = row["Ldn"].values[0], row["dn"].values[0], row["Lds"].values[0], row["ds"].values[0]
-    print(f'ratio Ldn/(Lds + Ldn)={Ldn / (Lds + Ldn)}')
-    vcf_file = gzip.open(args.vcf, 'rt')
-    list_non_syn = []
+def read_vcf(vcf, method, subsample, nbr_replicates):
+    vcf_file = gzip.open(vcf, 'rt')
[…]

### 2022-02-22 scripts/tex_sfs.py

@@ -2,26 +2,27 @@ import argparse
 from glob import glob
 from collections import defaultdict
 import os
-from libraries_plot import format_pop
+from libraries import format_pop
 
-dict_method = {"MutSel": "site-specific Mutation-Selection codon models.",
-               "Omega": "site-specific codon models.",
-               "Omega 0": "site-specific Mutation-Selection codon models (average over all amino acids).",
+dict_method = {"MutSel": "Site-specific Mutation-Selection codon models.",
+               "Omega": "Site-specific codon models.",
+               "Omega 0": "Site-specific Mutation-Selection codon models (average over all amino acids).",
                "SIFT": "SIFT score",
                "WS": "weak to strong mutations (AT$\\rightarrow$GC)",
                "SW": "strong to weak mutations (GC$\\rightarrow$AT)"}
 
-if __name__ == '__main__':
-    parser = argparse.ArgumentParser(formatter_class=argparse.ArgumentDefaultsHelpFormatter)
-    parser.add_argument('--sfs', required=False, type=str, nargs="+", dest="sfs", help="Input sfs file (pdf)")
-    parser.add_argument('--tex_doc', required=False, type=str, dest="tex_doc", help="Main document tex file")
-    parser.add_argument('--results', required=False, type=str, dest="results", help="Results tsv file")
-    parser.add_argument('--tex_include', required=False, type=str, dest="tex_include", help="Include tex file")
-    args = parser.parse_args()
 
+def minipage(size, file):
+    out = "\\begin{minipage}{" + str(size) + "\\linewidth} \n"
+    out += "\\includegraphics[width=\\linewidth, page=1]{" + file + "} \n"
+    out += "\\end{minipage}\n"
+    return out
+
+
+def main(args):
     heatmap_dict = defaultdict(list)
     for result in sorted(glob(f"{os.path.dirname(args.results)}/*.pdf")):
-        method, theta, plot = os.path.basename(result).replace(".pdf", "").replace("_", " ").split(".")
+        _, method, theta, plot = os.path.basename(result).replace(".pdf", "").replace("_", " ").split(".")
         heatmap_dict[method].append(result)
 
     o = open(args.tex_include, 'w')
@@ -47,23 +48,29 @@ if __name__ == '__main__':
                 o.write("\\subsection{" + format_pop(pop) + "} \n \n")
 
             for method, sfs in nested_dict_2.items():
[…]

### 2022-03-01 manuscript/include-figures.tex
Compute mutational opportunities for each category to normalize SFSs

--- 2022-02-16 manuscript/include-figures.tex
@@
 \begin{center}
-\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.D_tajima.heatmap.pdf} \\
-\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.D_tajima.scatter.pdf} \\
-\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.H_fay_wu.heatmap.pdf} \\
-\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.H_fay_wu.scatter.pdf} \\
-\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.fay_wu.heatmap.pdf} \\
-\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.fay_wu.scatter.pdf} \\
-\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.tajima.heatmap.pdf} \\
-\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.tajima.scatter.pdf} \\
-\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.watterson.heatmap.pdf} \\
-\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/MutSel.watterson.scatter.pdf} \\
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/DFE.MutSel.P(S<0).heatmap.pdf} \\
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/DFE.MutSel.P(S=0).heatmap.pdf} \\
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/DFE.MutSel.P(S>0).heatmap.pdf} \\
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.MutSel.D_tajima.heatmap.pdf} \\
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.MutSel.H_fay_wu.heatmap.pdf} \\
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.MutSel.fay_wu.heatmap.pdf} \\
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.MutSel.tajima.heatmap.pdf} \\
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.MutSel.watterson.heatmap.pdf} \\
 \end{center}
@@
 
+\subsection{IRBT}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.IRBT.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.IRBT.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.IRBT.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.IRBT.MutSel.S_histogram.pdf} 
+\end{minipage}
+\\ 
 \subsection{UGBT}
 
-\subsubsection*{SFS for site-specific Mutation-Selection codon models.} 
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
 \begin{minipage}{0.49\linewidth} 
@@
 \end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.UGBT.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.UGBT.MutSel.S_histogram.pdf} 
+\end{minipage}
+\\ 
+\section{Canis familiaris}
+
+\subsection{Canis}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Canis_familiaris.dogs.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Canis_familiaris.dogs.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Canis_familiaris.dogs.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Canis_familiaris.dogs.MutSel.S_histogram.pdf} 
+\end{minipage}
+\\ 
+\section{Capra hircus}
+
+\subsection{AUCH}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.AUCH.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.AUCH.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.AUCH.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.AUCH.MutSel.S_histogram.pdf} 
+\end{minipage}
+\\ 
+\subsection{FRCH}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.FRCH.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.FRCH.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.FRCH.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.FRCH.MutSel.S_histogram.pdf} 
+\end{minipage}
+\\ 
+\subsection{IRCA}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCA.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCA.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCA.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCA.MutSel.S_histogram.pdf} 
+\end{minipage}
+\\ 
+\subsection{IRCH}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCH.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCH.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCH.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCH.MutSel.S_histogram.pdf} 
+\end{minipage}
+\\ 
+\subsection{ITCH}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.ITCH.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.ITCH.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.ITCH.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.ITCH.MutSel.S_histogram.pdf} 
+\end{minipage}
+\\ 
+\subsection{MOCH}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.MOCH.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.MOCH.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.MOCH.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.MOCH.MutSel.S_histogram.pdf} 
+\end{minipage}
 \\ 
@@
 
+\subsection{Barbados}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Barbados.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Barbados.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Barbados.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Barbados.MutSel.S_histogram.pdf} 
+\end{minipage}
+\\ 
+\subsection{Central African Republic (CAR)}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel.S_histogram.pdf} 
+\end{minipage}
+\\ 
+\subsection{Ethiopia}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel.S_histogram.pdf} 
+\end{minipage}
+\\ 
+\subsection{Gambia}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Gambia.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Gambia.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Gambia.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Gambia.MutSel.S_histogram.pdf} 
+\end{minipage}
+\\ 
+\subsection{Kenya}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Kenya.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Kenya.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Kenya.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Kenya.MutSel.S_histogram.pdf} 
+\end{minipage}
+\\ 
+\subsection{Nevis}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Nevis.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Nevis.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Nevis.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Nevis.MutSel.S_histogram.pdf} 
+\end{minipage}
+\\ 
+\subsection{Saint Kitts (SK)}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Saint_Kitts.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Saint_Kitts.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Saint_Kitts.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Saint_Kitts.MutSel.S_histogram.pdf} 
+\end{minipage}
+\\ 
+\subsection{South Africa (SA)}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.South_Africa.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.South_Africa.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.South_Africa.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.South_Africa.MutSel.S_histogram.pdf} 
+\end{minipage}
+\\ 
 \subsection{Zambia}
 
-\subsubsection*{SFS for site-specific Mutation-Selection codon models.} 
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
 \begin{minipage}{0.49\linewidth} 
@@
 \end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Zambia.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Zambia.MutSel.S_histogram.pdf} 
+\end{minipage}
+\\ 
+\section{Equus caballus}
+
+\subsection{Equus}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Equus_caballus.up.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Equus_caballus.up.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Equus_caballus.up.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Equus_caballus.up.MutSel.S_histogram.pdf} 
+\end{minipage}
 \\ 
@@
 
+\subsection{AFR}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.AFR.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.AFR.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.AFR.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.AFR.MutSel.S_histogram.pdf} 
+\end{minipage}
+\\ 
 \subsection{AMR}
 
-\subsubsection*{SFS for site-specific Mutation-Selection codon models.} 
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
 \begin{minipage}{0.49\linewidth} 
@@
 \end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.AMR.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.AMR.MutSel.S_histogram.pdf} 
+\end{minipage}
 \\ 
+\subsection{EAS}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.EAS.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.EAS.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.EAS.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.EAS.MutSel.S_histogram.pdf} 
+\end{minipage}
+\\ 
+\subsection{EUR}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.EUR.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.EUR.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.EUR.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.EUR.MutSel.S_histogram.pdf} 
+\end{minipage}
+\\ 
+\subsection{SAS}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.SAS.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.SAS.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.SAS.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.SAS.MutSel.S_histogram.pdf} 
+\end{minipage}
+\\ 
+\section{Ovis aries}
+
+\subsection{IROA}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROA.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROA.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROA.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROA.MutSel.S_histogram.pdf} 
+\end{minipage}
+\\ 
+\subsection{IROO}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROO.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROO.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROO.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROO.MutSel.S_histogram.pdf} 
+\end{minipage}
+\\ 
+\subsection{IROV}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROV.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROV.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROV.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROV.MutSel.S_histogram.pdf} 
+\end{minipage}
+\\ 
+\subsection{ISGC}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.ISGC.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.ISGC.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.ISGC.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.ISGC.MutSel.S_histogram.pdf} 
+\end{minipage}
+\\ 
+\subsection{MOOA}
+
+\subsubsection*{Site-specific Mutation-Selection codon models.} 
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.MOOA.MutSel.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.MOOA.MutSel.normalize.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.MOOA.MutSel.polyDFE_D.pdf} 
+\end{minipage}
+\begin{minipage}{0.49\linewidth} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.MOOA.MutSel.S_histogram.pdf} 
+\end{minipage}
+\\

### 2022-03-01 scripts/genome_opportunities.py

@@ -1,0 +1,93 @@
+import os
+import argparse
+import numpy as np
+import pandas as pd
+from collections import defaultdict
+from libraries import nucleotides, codontable, CategorySNP
+
+transitions = {('A', 'G'), ('G', 'A'), ('C', 'T'), ('T', 'C')}
+
+
+class CdsSelCoeff(dict):
+    def __init__(self, method, exp_folder):
+        self.method = method
+        assert self.method in ["Omega", "MutSel"], 'Method must be either "Omega" or "MutSel"'
+        self.exp_folder = exp_folder
+        super().__init__()
+
+    def add_engs(self, ensg):
+        f_path = f"{self.exp_folder}/{ensg}"
+        if self.method == "MutSel":
+            path = f"{f_path}/sitemutsel_1.run.siteprofiles"
+            self[ensg] = pd.read_csv(path, sep="\t", skiprows=1, header=None,
+                                     names="site,A,C,D,E,F,G,H,I,K,L,M,N,P,Q,R,S,T,V,W,Y".split(","))
+        elif self.method == "Omega":
+            path = f"{f_path}/siteomega_1.run.ci0.025.tsv"
+            self[ensg] = pd.read_csv(path, sep="\t")["gene_omega"].values[1:]
+
+    def sel_coeff(self, ensg, ref_aa, alt_aa, c_site):
+        if ensg not in self:
+            self.add_engs(ensg)
+        if self.method == "MutSel":
+            return np.log(self[ensg][alt_aa][c_site] / self[ensg][ref_aa][c_site])
+        elif self.method == "Omega":
+            return self[ensg][c_site]
+
+
+def ali_seq(fasta_folder, fasta_file, species):
+    path = f"{fasta_folder}/{fasta_file}.fasta"
+    ali_file = open(path, 'r')
+    for sp in ali_file:
+        seq = ali_file.readline()
+        if sp.replace(">", "").strip() == species:
+            return seq.strip()
+    return None
+
+
+def main(args):
+    if args.method == "Omega":
+        cat_snps = CategorySNP(args.method, transform_bound=lambda s: s / (1 - np.exp(-s)) if s != 0 else 1.0)
+    else:
+        cat_snps = CategorySNP(args.method)
+
+    dico_profiles = CdsSelCoeff(args.method, args.exp_folder)
+    output_dict = defaultdict(list)
+    for species in args.species:
+        dico_opp_sp = defaultdict(int)
[…]

### 2022-03-01 scripts/libraries.py

@@ -1,5 +1,5 @@
 #!/usr/bin/env python3
-from collections import namedtuple
+from collections import namedtuple, defaultdict
 import numpy as np
 from math import floor
 import matplotlib
@@ -9,6 +9,7 @@ matplotlib.use('Agg')
 import matplotlib.pyplot as plt
 from matplotlib.collections import LineCollection
 from matplotlib.colors import to_rgb
+from matplotlib.cm import get_cmap
 
 fontsize = 16
 fontsize_legend = 14
@@ -24,6 +25,26 @@ GREEN_RGB = to_rgb(GREEN)
 GREY_RGB = to_rgb("grey")
 BLACK_RGB = to_rgb("black")
 
+complement = {'A': 'T', 'C': 'G', 'G': 'C', 'T': 'A'}
+nucleotides = list(sorted(complement.keys()))
+codontable = defaultdict(lambda: "-")
+codontable.update({
+    'ATA': 'I', 'ATC': 'I', 'ATT': 'I', 'ATG': 'M',
+    'ACA': 'T', 'ACC': 'T', 'ACG': 'T', 'ACT': 'T',
+    'AAC': 'N', 'AAT': 'N', 'AAA': 'K', 'AAG': 'K',
+    'AGC': 'S', 'AGT': 'S', 'AGA': 'R', 'AGG': 'R',
+    'CTA': 'L', 'CTC': 'L', 'CTG': 'L', 'CTT': 'L',
+    'CCA': 'P', 'CCC': 'P', 'CCG': 'P', 'CCT': 'P',
+    'CAC': 'H', 'CAT': 'H', 'CAA': 'Q', 'CAG': 'Q',
+    'CGA': 'R', 'CGC': 'R', 'CGG': 'R', 'CGT': 'R',
+    'GTA': 'V', 'GTC': 'V', 'GTG': 'V', 'GTT': 'V',
+    'GCA': 'A', 'GCC': 'A', 'GCG': 'A', 'GCT': 'A',
+    'GAC': 'D', 'GAT': 'D', 'GAA': 'E', 'GAG': 'E',
+    'GGA': 'G', 'GGC': 'G', 'GGG': 'G', 'GGT': 'G',
+    'TCA': 'S', 'TCC': 'S', 'TCG': 'S', 'TCT': 'S',
+    'TTC': 'F', 'TTT': 'F', 'TTA': 'L', 'TTG': 'L',
[…]

### 2022-03-01 scripts/parse_results_DFE.py

@@ -7,8 +7,8 @@ from scipy.stats import expon, gamma
 from libraries import plt, CategorySNP, my_dpi
 
 
-def read_polyDFE(path):
-    out_polyDFE = {}
+def read_poly_dfe(path):
+    out_poly_dfe = {}
     with open(path, 'r') as f:
         for line in f:
             if "Model: C" in line or "Model: D" in line:
@@ -18,16 +18,16 @@ def read_polyDFE(path):
                 values = re.sub(' +', ' ', f.readline().replace("--", "").strip()).split(" ")
                 if "Model: C" in line:
                     for h_i, h in enumerate(header):
-                        out_polyDFE[h] = float(values[h_i])
-                    out_polyDFE["S_d"] = -out_polyDFE["S_d"]
+                        out_poly_dfe[h] = float(values[h_i])
+                    out_poly_dfe["S_d"] = -out_poly_dfe["S_d"]
                 elif "Model: D" in line:
                     for v_i, v in enumerate(values):
-                        out_polyDFE[f"S_{v_i + 1}"] = float(header[v_i * 2 + 1])
-                        out_polyDFE[f"p(S={header[v_i * 2 + 1]})"] = float(v)
+                        out_poly_dfe[f"S_{v_i + 1}"] = float(header[v_i * 2 + 1])
+                        out_poly_dfe[f"p(S={header[v_i * 2 + 1]})"] = float(v)
             if "alpha_dfe" in line:
                 k, v = line.strip().split("=")
-                out_polyDFE["$\\alpha$"] = float(v)
-    return out_polyDFE
+                out_poly_dfe["$\\alpha$"] = float(v)
+    return out_poly_dfe
 
 
 def read_grapes(path):
@@ -39,12 +39,12 @@ def read_grapes(path):
 
 
 def main(args):
-    cat_snps = CategorySNP(args.method)
-    list_cat = cat_snps.non_syn() + ["all"]
+    cat_snps = CategorySNP(args.method, args.bins)
+    list_cat = cat_snps.all()
     s_dico = dict()
     for file in args.input:
         cat = os.path.basename(file).replace(".out", "").split(".")[-2]
-        out = read_polyDFE(file) if "polyDFE" in file else read_grapes(file)
+        out = read_poly_dfe(file) if "polyDFE" in file else read_grapes(file)
         if "polyDFE_D" in file:
             p_list = np.array([v for k, v in out.items() if "p(S=" in k])
[…]

### 2022-03-01 scripts/plot_heatmap.py

@@ -53,7 +53,7 @@ def main(args):
     pop2sp = {pop: sp for (pop, sp), d in df_merge.groupby(["pop", "species"])}
 
     for method, df in df_merge.groupby(["method"]):
-        cat_snps = CategorySNP(method)
+        cat_snps = CategorySNP(method, args.bins)
         for d, d_label in d_dict.items():
             # scatter_plot(cat_snps, df, d, d_dict, f"{args.output.replace('.tsv', '')}/{method}.{d}.scatter.pdf")
 
@@ -66,12 +66,12 @@ def main(args):
             _, ax = plt.subplots(figsize=(1920 / my_dpi, 880 / my_dpi), dpi=my_dpi)
             cat_labels = [cat_snps.label(cat) for cat in cat_snps.non_syn()]
             start, end = np.nanmin(matrix), np.nanmax(matrix)
-            RdBu = cm.get_cmap('RdBu_r')
+            rd_bu = cm.get_cmap('RdBu_r')
             if np.sign(start) != np.sign(end):
                 midpoint = - start / (np.nanmax(matrix) - start)
-                RdBu = shiftedColorMap(RdBu, midpoint=midpoint, name='shifted')
+                rd_bu = shiftedColorMap(rd_bu, midpoint=midpoint, name='shifted')
 
-            im, _ = heatmap(matrix.T, cat_labels, matrix.index, ax=ax, cmap=RdBu, cbarlabel=d_label)
+            im, _ = heatmap(matrix.T, cat_labels, matrix.index, ax=ax, cmap=rd_bu, cbarlabel=d_label)
             annotate_heatmap(im, valfmt=lambda p: "{0:.2f}".format(p), div=True, fontsize=5)
             plt.tight_layout()
             plt.savefig(args.output.replace('results.tsv', f'{method}.{d}.heatmap.pdf'), format="pdf")
@@ -84,4 +84,5 @@ if __name__ == '__main__':
     parser.add_argument('--tsv', required=False, type=str, nargs="+", dest="tsv", help="Input tsv file")
     parser.add_argument('--output', required=False, type=str, dest="output", help="Output tsv file")
     parser.add_argument('--sample_list', required=False, type=str, dest="sample_list", help="Sample list file")
+    parser.add_argument('--bins', required=False, default=0, type=int, dest="bins", help="Number of bins")
     main(parser.parse_args())

### 2022-03-01 scripts/plot_sfs.py

@@ -3,11 +3,13 @@ import gzip
 import numpy as np
 import pandas as pd
 import scipy.stats as sps
-from collections import defaultdict
+from collections import defaultdict, namedtuple
+from matplotlib.patches import Rectangle
 from libraries import plt, CategorySNP, my_dpi, multiline, sfs_weight, theta, write_sfs, write_dofe
 
 weak = ["A", "T"]
 strong = ["G", "C"]
+SNP = namedtuple('SNP', ['id', 's_sift', 's_mutsel', 's_omega', 's_omega_0', 'derived_count', 'frequency'])
 
 
 def daf_to_sfs(daf_list, min_n):
@@ -31,7 +33,8 @@ def read_vcf(vcf, method, subsample, nbr_replicates):
             continue
 
         split_line = vcf_line.strip().split("\t")
-        info = split_line[header["INFO"]]
+        snp_id = str(split_line[header["ID"]])
+        info = str(split_line[header["INFO"]])
         dico_info = {k: v for k, v in [s.split('=') for s in info.split(';') if '=' in s]}
 
         if method == "WS" and not ((dico_info["NUC_ANC"] in weak) and (dico_info["NUC_DER"] in strong)):
@@ -41,11 +44,13 @@ def read_vcf(vcf, method, subsample, nbr_replicates):
             continue
 
         polarized = dico_info["POLARIZED"] == "True"
-        if not polarized and method == "SIFT" and dico_info["SNP_TYPE"] == "NonSyn":
+        if not polarized and method == "SIFT":
             continue
 
         sample_size = int(dico_info["SAMPLE_SIZE"])
         k = int(dico_info["COUNT_POLARIZED"])
+        if k == 0:
+            continue
         max_daf = min(sample_size, subsample)
         max_daf_set.add(max_daf)
         if sample_size > subsample:
@@ -54,30 +59,20 @@ def read_vcf(vcf, method, subsample, nbr_replicates):
         else:
             count = [k]
 
-        if np.all([i == 0 for i in count]):
-            continue
-
         if dico_info["SNP_TYPE"] == "Syn":
             list_syn.append(count)
         elif dico_info["SNP_TYPE"] == "NonSyn":
[…]

### 2022-03-03 manuscript/include-figures.tex
Use polyDFE model C, nearly-neutral mutations as |S|<1

--- 2022-02-22 manuscript/include-figures.tex
@@
 \begin{center}
-\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/DFE.MutSel.P(S<0).heatmap.pdf} \\
-\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/DFE.MutSel.P(S=0).heatmap.pdf} \\
-\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/DFE.MutSel.P(S>0).heatmap.pdf} \\
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/DFE.MutSel.P-Seq0.heatmap.pdf} \\
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/DFE.MutSel.P-Sinf0.heatmap.pdf} \\
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/DFE.MutSel.P-Ssup0.heatmap.pdf} \\
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/DFE.MutSel.S.heatmap.pdf} \\
 \includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.MutSel.D_tajima.heatmap.pdf} \\
@@
 \begin{center}
-\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/DFE.Omega.P(S<0).heatmap.pdf} \\
-\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/DFE.Omega.P(S=0).heatmap.pdf} \\
-\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/DFE.Omega.P(S>0).heatmap.pdf} \\
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/DFE.Omega.P-Seq0.heatmap.pdf} \\
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/DFE.Omega.P-Sinf0.heatmap.pdf} \\
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/DFE.Omega.P-Ssup0.heatmap.pdf} \\
+\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/DFE.Omega.S.heatmap.pdf} \\
 \includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.Omega.D_tajima.heatmap.pdf} \\
@@
 \end{center}
-\subsection{Sift score} 
-\begin{center}
-\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/DFE.SIFT.P(S<0).heatmap.pdf} \\
-\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/DFE.SIFT.P(S=0).heatmap.pdf} \\
-\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/DFE.SIFT.P(S>0).heatmap.pdf} \\
-\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.SIFT.D_tajima.heatmap.pdf} \\
-\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.SIFT.H_fay_wu.heatmap.pdf} \\
-\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.SIFT.fay_wu.heatmap.pdf} \\
-\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.SIFT.tajima.heatmap.pdf} \\
-\includegraphics[width=0.75\linewidth, page=1]{/home/thibault/Documents/SelCoeff/results/Theta.SIFT.watterson.heatmap.pdf} \\
-\end{center}
 \section{Bos taurus}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.IRBT.MutSel.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.IRBT.MutSel.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.IRBT.Omega.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.IRBT.Omega.polyDFE_C.pdf} 
 \end{minipage}
@@
 \\ 
-\subsubsection*{SIFT score} 
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.IRBT.SIFT.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.IRBT.SIFT.normalize.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.IRBT.SIFT.polyDFE_D.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.IRBT.SIFT_vs_MutSel.pdf} 
-\end{minipage}
-\\ 
 \subsection{UGBT}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.UGBT.MutSel.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.UGBT.MutSel.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.UGBT.Omega.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.UGBT.Omega.polyDFE_C.pdf} 
 \end{minipage}
@@
 \\ 
-\subsubsection*{SIFT score} 
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.UGBT.SIFT.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.UGBT.SIFT.normalize.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.UGBT.SIFT.polyDFE_D.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Bos_taurus.UGBT.SIFT_vs_MutSel.pdf} 
-\end{minipage}
-\\ 
 \section{Canis familiaris}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Canis_familiaris.dogs.MutSel.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Canis_familiaris.dogs.MutSel.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Canis_familiaris.dogs.Omega.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Canis_familiaris.dogs.Omega.polyDFE_C.pdf} 
 \end{minipage}
@@
 \\ 
-\subsubsection*{SIFT score} 
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Canis_familiaris.dogs.SIFT.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Canis_familiaris.dogs.SIFT.normalize.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Canis_familiaris.dogs.SIFT.polyDFE_D.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Canis_familiaris.dogs.SIFT_vs_MutSel.pdf} 
-\end{minipage}
-\\ 
 \section{Capra hircus}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.AUCH.MutSel.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.AUCH.MutSel.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.AUCH.Omega.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.AUCH.Omega.polyDFE_C.pdf} 
 \end{minipage}
@@
 \\ 
-\subsubsection*{SIFT score} 
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.AUCH.SIFT.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.AUCH.SIFT.normalize.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.AUCH.SIFT.polyDFE_D.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.AUCH.SIFT_vs_MutSel.pdf} 
-\end{minipage}
-\\ 
 \subsection{FRCH}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.FRCH.MutSel.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.FRCH.MutSel.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.FRCH.Omega.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.FRCH.Omega.polyDFE_C.pdf} 
 \end{minipage}
@@
 \\ 
-\subsubsection*{SIFT score} 
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.FRCH.SIFT.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.FRCH.SIFT.normalize.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.FRCH.SIFT.polyDFE_D.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.FRCH.SIFT_vs_MutSel.pdf} 
-\end{minipage}
-\\ 
 \subsection{IRCA}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCA.MutSel.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCA.MutSel.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCA.Omega.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCA.Omega.polyDFE_C.pdf} 
 \end{minipage}
@@
 \\ 
-\subsubsection*{SIFT score} 
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCA.SIFT.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCA.SIFT.normalize.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCA.SIFT.polyDFE_D.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCA.SIFT_vs_MutSel.pdf} 
-\end{minipage}
-\\ 
 \subsection{IRCH}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCH.MutSel.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCH.MutSel.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCH.Omega.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCH.Omega.polyDFE_C.pdf} 
 \end{minipage}
@@
 \\ 
-\subsubsection*{SIFT score} 
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCH.SIFT.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCH.SIFT.normalize.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCH.SIFT.polyDFE_D.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.IRCH.SIFT_vs_MutSel.pdf} 
-\end{minipage}
-\\ 
 \subsection{ITCH}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.ITCH.MutSel.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.ITCH.MutSel.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.ITCH.Omega.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.ITCH.Omega.polyDFE_C.pdf} 
 \end{minipage}
@@
 \\ 
-\subsubsection*{SIFT score} 
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.ITCH.SIFT.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.ITCH.SIFT.normalize.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.ITCH.SIFT.polyDFE_D.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.ITCH.SIFT_vs_MutSel.pdf} 
-\end{minipage}
-\\ 
 \subsection{MOCH}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.MOCH.MutSel.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.MOCH.MutSel.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.MOCH.Omega.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.MOCH.Omega.polyDFE_C.pdf} 
 \end{minipage}
@@
 \\ 
-\subsubsection*{SIFT score} 
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.MOCH.SIFT.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.MOCH.SIFT.normalize.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.MOCH.SIFT.polyDFE_D.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Capra_hircus.MOCH.SIFT_vs_MutSel.pdf} 
-\end{minipage}
-\\ 
 \section{Chlorocebus sabaeus}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Barbados.MutSel.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Barbados.MutSel.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Barbados.Omega.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Barbados.Omega.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Central_African_Republic.Omega.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Central_African_Republic.Omega.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Ethiopia.Omega.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Ethiopia.Omega.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Gambia.MutSel.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Gambia.MutSel.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Gambia.Omega.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Gambia.Omega.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Kenya.MutSel.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Kenya.MutSel.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Kenya.Omega.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Kenya.Omega.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Nevis.MutSel.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Nevis.MutSel.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Nevis.Omega.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Nevis.Omega.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Saint_Kitts.MutSel.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Saint_Kitts.MutSel.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Saint_Kitts.Omega.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Saint_Kitts.Omega.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.South_Africa.MutSel.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.South_Africa.MutSel.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.South_Africa.Omega.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.South_Africa.Omega.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Zambia.MutSel.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Zambia.MutSel.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Zambia.Omega.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Chlorocebus_sabaeus.Zambia.Omega.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Equus_caballus.up.MutSel.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Equus_caballus.up.MutSel.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Equus_caballus.up.Omega.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Equus_caballus.up.Omega.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.AFR.MutSel.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.AFR.MutSel.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.AFR.Omega.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.AFR.Omega.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.AMR.MutSel.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.AMR.MutSel.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.AMR.Omega.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.AMR.Omega.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.EAS.MutSel.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.EAS.MutSel.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.EAS.Omega.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.EAS.Omega.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.EUR.MutSel.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.EUR.MutSel.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.EUR.Omega.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.EUR.Omega.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.SAS.MutSel.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.SAS.MutSel.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.SAS.Omega.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Homo_sapiens.SAS.Omega.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROA.MutSel.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROA.MutSel.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROA.Omega.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROA.Omega.polyDFE_C.pdf} 
 \end{minipage}
@@
 \\ 
-\subsubsection*{SIFT score} 
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROA.SIFT.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROA.SIFT.normalize.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROA.SIFT.polyDFE_D.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROA.SIFT_vs_MutSel.pdf} 
-\end{minipage}
-\\ 
 \subsection{IROO}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROO.MutSel.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROO.MutSel.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROO.Omega.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROO.Omega.polyDFE_C.pdf} 
 \end{minipage}
@@
 \\ 
-\subsubsection*{SIFT score} 
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROO.SIFT.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROO.SIFT.normalize.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROO.SIFT.polyDFE_D.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROO.SIFT_vs_MutSel.pdf} 
-\end{minipage}
-\\ 
 \subsection{IROV}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROV.MutSel.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROV.MutSel.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROV.Omega.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROV.Omega.polyDFE_C.pdf} 
 \end{minipage}
@@
 \\ 
-\subsubsection*{SIFT score} 
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROV.SIFT.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROV.SIFT.normalize.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROV.SIFT.polyDFE_D.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.IROV.SIFT_vs_MutSel.pdf} 
-\end{minipage}
-\\ 
 \subsection{ISGC}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.ISGC.MutSel.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.ISGC.MutSel.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.ISGC.Omega.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.ISGC.Omega.polyDFE_C.pdf} 
 \end{minipage}
@@
 \\ 
-\subsubsection*{SIFT score} 
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.ISGC.SIFT.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.ISGC.SIFT.normalize.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.ISGC.SIFT.polyDFE_D.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.ISGC.SIFT_vs_MutSel.pdf} 
-\end{minipage}
-\\ 
 \subsection{MOOA}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.MOOA.MutSel.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.MOOA.MutSel.polyDFE_C.pdf} 
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.MOOA.Omega.polyDFE_D.pdf} 
+\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.MOOA.Omega.polyDFE_C.pdf} 
 \end{minipage}
@@
 \\
-\subsubsection*{SIFT score} 
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.MOOA.SIFT.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.MOOA.SIFT.normalize.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.MOOA.SIFT.polyDFE_D.pdf} 
-\end{minipage}
-\begin{minipage}{0.49\linewidth} 
-\includegraphics[width=\linewidth, page=1]{/home/thibault/Documents/SelCoeff/analysis/Ovis_aries.MOOA.SIFT_vs_MutSel.pdf} 
-\end{minipage}
-\\

### 2022-03-03 scripts/genome_opportunities.py

@@ -54,7 +54,8 @@ def main(args):
     output_dict = defaultdict(list)
     for species in args.species:
         dico_opp_sp = defaultdict(int)
-        for ensg in sorted(os.listdir(args.exp_folder))[:500]:
+        files = sorted(os.listdir(args.exp_folder))
+        for ensg in np.random.choice(files, size=min(1000, len(files)), replace=False):
             seq = ali_seq(args.fasta_folder, ensg, species)
             if not seq:
                 continue

### 2022-03-03 scripts/libraries.py

@@ -47,6 +47,8 @@ codontable.update({
     'TGC': 'C', 'TGT': 'C', 'TGA': 'X', 'TGG': 'W', '---': '-'})
 confidence_interval = namedtuple('confidence_interval', ['low', 'mean', 'up'])
 sfs_weight = {"watterson": lambda i, n: 1.0 / i, "tajima": lambda i, n: n - i, "fay_wu": lambda i, n: i}
+polydfe_cat_dico = {"S": "$S^{pop}$", "P-Sinf0": "$p_{-}$", "P-Seq0": "$p_{neutral}$", "P-Ssup0": "$p_{+}$"}
+polydfe_cat_list = list(polydfe_cat_dico.keys())
 
 
 def theta(sfs_epsilon, daf_n, weight_method):

### 2022-03-03 scripts/plot_heatmap.py

@@ -1,10 +1,9 @@
 import os
 import argparse
-import numpy as np
 import pandas as pd
 import statsmodels.api as sm
 from matplotlib import cm
-from libraries import plt, my_dpi, format_pop, sp_sorted, CategorySNP, annotate_heatmap, heatmap, shiftedColorMap
+from libraries import *
 
 theta_dict = {"watterson": "Watterson $\\theta_W$", "tajima": "Tajima $\\theta_{\\pi}$ ",
               "fay_wu": "Fay and Wu $\\theta_{H}$"}
@@ -18,10 +17,10 @@ def open_tsv(filepath):
 
 
 def scatter_plot(cat_snps, df, d, d_dict, file):
-    theta = "tajima"
+    theta_param = "tajima"
     _, _ = plt.subplots(figsize=(1920 / my_dpi, 880 / my_dpi), dpi=my_dpi)
     for cat in cat_snps.non_syn():
-        x = df[df["category"] == "syn"][theta].values
+        x = df[df["category"] == "syn"][theta_param].values
         y = df[df["category"] == cat][d].values
         plt.scatter(x, y, color=cat_snps.color(cat))
         model = sm.OLS(y, sm.add_constant(x))
@@ -31,7 +30,7 @@ def scatter_plot(cat_snps, df, d, d_dict, file):
         sign = '+' if float(b) > 0 else '-'
         label = f"{cat_snps.label(cat)}: $y={a:.2g}x {sign} {abs(b):.2g}$ ($r^2={r.rsquared:.2g})$"
         plt.plot(idf, a * idf + b, '-', color=cat_snps.color(cat), label=label)
-    plt.xlabel(theta_dict[theta])
+    plt.xlabel(theta_dict[theta_param])
     plt.ylabel(f"{d_dict[d]}")
     plt.legend()
     plt.tight_layout()
@@ -48,7 +47,7 @@ def main(args):
         d_dict = {"D_tajima": "Tajima's $D$", "H_fay_wu": "Fay and Wu's $H$"}
         d_dict.update(theta_dict)
     else:
-        d_dict = {"P(S<0)": "P(S<0)", "P(S=0)": "P(S=0)", "P(S>0)": "P(S>0)"}
+        d_dict = polydfe_cat_dico
     df_merge.to_csv(args.output, sep="\t", index=False)
     pop2sp = {pop: sp for (pop, sp), d in df_merge.groupby(["pop", "species"])}
 
@@ -56,7 +55,6 @@ def main(args):
[…]

### 2022-03-03 manuscript/supp-mat.tex
Each experiment has its own folder

--- 2022-02-16 manuscript/main.tex
@@
-%! BibTeX Compiler = biber
 %TC:ignore
@@
 \definecolor{DARKBLUELINK}{HTML}{0B0080}
-\definecolor{LIGHTBLUELINK}{HTML}{3366BB}
-\definecolor{PURPLELINK}{HTML}{663366}
-\definecolor{RED}{HTML}{EB6231}
-\definecolor{GREEN}{HTML}{8FB03E}
-\definecolor{LIGHTGREY}{gray}{0.9}
 \PassOptionsToPackage{hyphens}{url}
@@
 
-\usepackage{biorxiv}
-\usepackage[backend=biber,style=nature]{biblatex}
-\addbibresource{codon_models.bib}
-
-\usepackage{url}
+\usepackage[margin=60pt]{geometry}
 \usepackage{amssymb,amsfonts,amsmath,amsthm,mathtools}
-\usepackage{textcomp}
-\usepackage{gensymb}
-\usepackage{cancel}
 \usepackage{lmodern}
-\usepackage{xfrac, nicefrac}
-\usepackage{blkarray}
-\usepackage{pgf,tikz}
-\usetikzlibrary{positioning,arrows,automata,calc}
-\usepackage{bm}
+\usepackage{bm,bbold}
+\usepackage{verbatim}
+\usepackage{float}
 \usepackage{listings, enumerate, enumitem}
 \usepackage[export]{adjustbox}
-\usepackage{graphicx}
 \usepackage{tabu}
+\usepackage{longtable}
+\tabulinesep=0.6mm
+\newcommand\cellwidth{\TX@col@width}
 \usepackage{hhline}
+\setlength{\arrayrulewidth}{1.2pt}
 \usepackage{multicol,multirow,array}
 \usepackage{etoolbox}
+\AtBeginEnvironment{tabu}{\footnotesize}
 \usepackage{booktabs}
-
-\usepackage[flushleft] {threeparttable}
-\usepackage{bbold}
-\usepackage{pdfpages}
-\usetikzlibrary{positioning}
-\usetikzlibrary{arrows,automata}
+\usepackage{graphicx}
 \pdfinclusioncopyfonts=1
-\usepackage{nicefrac} % compact symbols for 1/2, etc.
-\usepackage{microtype} % microtypography
-\usepackage{lineno}
-
-\newcommand{\specialcell}[2][c]{%
-    \begin{tabular}[#1]{@{}c@{}}
-        #2
-    \end{tabular}}
-
-\newcommand{\UniDimArray}[1]{\bm{#1}}
-\newcommand{\BiDimArray}[1]{\bm{#1}}
-
-\DeclareMathOperator{\E}{\mathbb{E}}
-\DeclareMathOperator{\Var}{\mathrm{Var}}
-\newcommand{\der}{\mathrm{d}}
-\newcommand{\angstrom}{\mathrm{\normalfont\AA}}
-\newcommand{\e}{\mathrm{e}}
-\newcommand{\avg}[1]{\left< #1 \right>} % for average
-\newcommand{\Ne}{N_{\mathrm{e}}}
-\newcommand{\Ner}{N_{\mathrm{r}}}
-\newcommand{\dn}{d_N}
-\newcommand{\ds}{d_S}
-\newcommand{\dnds}{\dn / \ds}
-\newcommand{\pn}{\pi_N}
-\newcommand{\ps}{\pi_S}
-\newcommand{\pnps}{\pn / \ps}
-\newcommand{\proba}{\mathbb{P}}
-\newcommand{\pfix}{\proba_{\mathrm{fix}}}
-\newcommand{\Pfix}{2 \Ne \proba_{\mathrm{fix}}}
-\newcommand{\indice}{a}
-\newcommand{\indiceexp}{^{(\indice)}}
-
-\renewcommand{\baselinestretch}{1.5}
-\renewcommand{\arraystretch}{0.6}
-\linenumbers
 
@@
     \large
-    T. {Latrille}$^{1}$, N. {Salamin}$^{1}$\\
+    T. {Latrille}$^{1}$, J. {Joseph}$^{2}$, N. {Salamin}$^{1}$\\
     $^{1}$Université de Lausanne, Lausanne, Switzerland
+    $^{1}$Université de Lyon, Lyon, France
 }
@@
     \maketitle
-
-    \begin{abstract}
-        At the phylogenetic scale, recent mutation-selection models provide a direct estimate of the selection coefficient for any mutation in a coding sequence, depending on the amino-acids involved in the mutation.
-        At the population-genetic scale, the frequency at which a polymorphism segregates in a population is also a function of its selection coefficient.
-        Taking advantage of this relationship between phylogenetic and population genetics, we can assess whether selection coefficients estimated at the phylogenetic scale can predict the frequency of polymorphism.
-        In this study, we integrated divergence and polymorphism data across the entire exome for 29 populations across 7 genera, and showed that selection coefficients are correlated at the phylogenetic and population-genetic scales.
-        Altogether, our work is paving the way for studies and methods augmenting molecular polymorphism data within species with information about divergence data between species, and by assessing empirically the relationship between phylogenetic and population genetics.
-    \end{abstract}
-
-    \keywords{Selection \and phylogenetic \and population genetics \and codon models}
-
     \tableofcontents
-
-    \section{Introduction}\label{sec:introduction}
-%TC:endignore
-
-    In phylogeny-based methods, mutation-selection models provide a nearly-neutral model of evolution by estimating the fitness landscape over amino-acid sequences, for each site of the sequence\cite{yang_mutationselection_2008, halpern_evolutionary_1998, rodrigue_mechanistic_2010}.
-    At the mutation-selection balance, the probability for a specific codon to be fixed in the population is proportional to its fitness, and a mutation from a high fitness amino-acid towards a low fitness amino-acid will have a small probability of fixation, genuinely accounting for purifying selection.
-    Conversely, only nearly-neutral mutations between high fitness amino acids will tend to be permitted by the model, allowing for the explicit calculation of the scaled selection coefficient of non-synonymous mutations at mutation-selection balance\cite{spielman_relationship_2015, rodrigue_detecting_2017}.
-    In this study, we thus first applied mutation-selection codon models to whole exome data from placental mammals, such as to quantify the amino-acid fitness profile for each site of each protein.
-
-    The goal of this study is to assess whether the signal of selection at the phylogenetic and population-genetic scale are correlated.
-    The population- and phylogeny-based methods work over very different time scales, for that reason, they might be capturing different signals.
-    Nonetheless, we expect sites and proteins under long-term evolution to maintain their signal of selection in several independent lineages for which we computed the unfolded site frequency spectrum (SFS).
-    To test this hypothesis, we leverage a pipeline integrating divergence and polymorphism data across the entire exome for 29 populations across 7 genera, namely \textit{Equus}, \textit{Canis}, \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus} and \textit{Homo}.
-
-%TC:ignore
-
-    \section{Methods}\label{sec:methods}
-
-    \subsection*{Phylogenetic dataset}
-    protein-coding DNA sequences alignments in placental mammals are extracted from the \href{https://www.orthomam.univ-montp2.fr}{OrthoMaM} database\cite{ranwez_orthomam_2007, douzery_orthomam_2014, scornavacca_orthomam_2019}.
-    Genes located on the X, Y and mitochondrial chromosome are discarded from the analysis, since the number of polymorphism, necessary in population-based method, is expected to be different on these sequences.
-    Additionally, sequences from the species for which polymorphism are available, as well as their sister species have been discarded from the analysis to ensure independence between the data used in the phylogenetic and population-genetic method.
-
-    \subsection{Selection coefficient in phylogeny-based method}
-    Mutation-selection models assume that the protein-coding sequence is at mutation-selection balance under a fixed fitness landscape, which is itself characterized by a fitness vector over the $20$ amino-acid at each site\cite{yang_mutationselection_2008, halpern_evolutionary_1998, rodrigue_mechanistic_2010}.
-    Mathematically, the rate of non-synonymous substitution from codon $a$ to codon $b$ ($q_{a \mapsto b}^{(i)}$) at site $i$ of the sequence is equal to the rate of mutation from the underlying DNA change ($\mu_{a \mapsto b}$) multiplied by the scaled probability of fixation of the mutation ($\proba_{a \mapsto b}^{(i)}$).
-    Crucially, the probability of fixation depends on the difference of scaled fitness between the amino-acid encoded by the mutated codon ($F_b^{(i)}$) and the fitness of the amino-acid encoded by the original codon ($F_a^{(i)}$) of site $i$\cite{wright_evolution_1931, fisher_genetical_1930}.
-    Altogether, the rate of substitution from codon $a$ to $b$ at a given site $i$ is:
-    \begin{equation}
-        q_{a \mapsto b}^{(i)} = \mu_{a \mapsto b} \proba_{a \mapsto b}^{(i)} = \mu_{a \mapsto b} \dfrac{F_b^{(i)} - F_a^{(i)}}{1 - \e^{F_a^{(i)} - F_b^{(i)}}}.
-    \end{equation}
-
-    Fitting the mutation-selection model on a sequence alignment leads to an estimation of the mutation rate matrix ($\UniDimArray{\mu}$) as well as the 20 amino-acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$.
-
-    We ran the Bayesian software \href{https://github.com/bayesiancook/bayescode}{BayesCode} on each protein-coding DNA alignment\cite{lartillot_phylobayes_2013, rodrigue_detecting_2017}.
-    Each Monte-Carlo Markov-Chain (MCMC) is run during $2000$ points, with a burn-in of $1000$ points, allowing to compute the mean amino-acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$ across the MCMC.
-
-    \subsection{Polymorphism dataset}
-
-    In order to compare polymorphism and divergence, each SNP (chromosome, position, strand) in the focal species must be matched to its relative position in the protein-coding DNA alignment.
-    First, genomic positions are converted to relative position in the coding sequence (CDS) using gene annotation files (GTF format) downloaded from Ensembl (\url{ensembl.org}), we verified the SNP match the reference in the CDS (FASTA format) also downloaded from Ensembl.
-    Secondly, relative position in the CDS is converted to position in the multiple sequence alignment (containing gaps) from OrthoMaM database\cite{ranwez_orthomam_2007, douzery_orthomam_2014, scornavacca_orthomam_2019} by doing a global pairwise alignment (Biopython pairwise2) between the CDS fasta and the sequence found in the alignment.
-    This conversion from genomic position to position in the alignment is only possible if the assembly used for SNP calling is the same as the one used in the alignment, the GTF annotations and the FASTA sequences.
-    We retrieved polymorphism from different projects.
-    \textit{Equus caballus} variants called on the EquCab2 assembly in the EVA study PRJEB9799, we considered \textit{Ceratotherium simum simum} as its sister species.
-    \textit{Canis familiars} variants called on the CanFam3.1 assembly in the EVA study PRJEB24066, we considered \textit{Ursus maritimus} as its sister species.
-    \textit{Bos taurus} variants called on the UMD3.1 assembly in the next-gen project, we considered \textit{Bison bison bison} as its sister species.
-    \textit{Ovis aries} variants called on the Oar\_v3.1 assembly in the next-gen project, we considered \textit{Pantholops hodgsonii} as its sister species.
-    \textit{Capra Hircus} variants called on the CHIR1 assembly in the next-gen project, we performed a liftover to the ARS1 assembly and considered \textit{Pantholops hodgsonii} as its sister species.
-    \textit{Chlorocebus sabaeus} variants are called on the ChlSab1.1 assembly in the EVA study PRJEB22989\cite{svardal_ancient_2017}, we considered \textit{Macaca mulatta} as its sister species.
-    \textit{Homo sapiens} variants are called on the GRCh38 assembly in the 1000-genome project\cite{consortium_integrated_2012, the1000genomesprojectconsortium_global_2015}, we considered \textit{Pan troglodytes} as its sister species.
-    Variants not inside genes are discarded at the beginning of the analysis.
-    Insertions and deletions are not analyzed, and only Single Nucleotide Polymorphisms (SNPs) with only one mutant allele are considered.
-    Stop codon mutants are also discarded.
-    For populations containing more than $8$ sampled individuals, the site-frequency spectrum (SFS) is subsampled down to $16$ chromosomes ($8$ diploid individuals) without replacement (hyper-geometric distribution) to alleviate the effect of different sampling depth in the $29$ populations.
-    Moreover, subsampling mitigate the impact of moderately deleterious mutations segregating at low frequency on $\pnps$, since they are more likely to be discarded than polymorphism segregating at higher frequency.
-    SNPs are polarized using the $3$ closest outgroups found in the OrthoMam alignment with est-usfs\cite{keightley_inferring_2018}.
-    The Snakemake pipeline for integrating polymorphism and divergence data uses custom scripts written in python 3.8.
-
-    \subsection{Site frequency spectrum}
-    The probability of fixation of an allele can be empirically observable, and in the context of a Wright-Fisher processes it is related to selection and drift.
-    However, this absorbing fate is not the sole characteristic of the process that relates empirical observable quantities to parameters of the process.
-    Along the whole trajectory of an allele, before fixation or extinction, the probability of this allele to be at a certain frequency can be related to its selection coefficient and to the effective population size.
-    More precisely, $g(x) \der x $ is the expected time for which the population frequency of derived allele is in the range $(x, x+\der x)$ before eventual absorption, which is derived using the Kolmogorov forward equation as a function of $x$ and $S$:
-    \begin{align}
-        g(x, s, \Ne) & = \dfrac{\left( 1 - \e^{- 2 s }\right) \left( 1 - \e^{-4 \Ne s(1-x)}\right)}{ s (1 - \e^{-4 \Ne s})x(1-x)} \\
-        \Rightarrow g(x, S) & \approx \dfrac{2 \left( 1 - \e^{-S(1-x)}\right)}{(1 - \e^{-S})x(1-x)} \label{eq:expected_time}
-    \end{align}
-
-    \begin{center}
-        \includegraphics[width=0.4\textwidth, page=4] {artworks/figures.pdf}
-        \flushleft
-        Expected time at a derived frequency $g(x, S)$ in the vertical axis as a function of the frequency $x$, shown for different scaled selection coefficient.
-        Allele with a positive selection coefficient can be observed at high frequency, while alleles with negative selection coefficients are unlikely to be observed at high frequency.
-    \end{center}
-
-    This equation is solely valid for a gene with two alleles, a configuration which is rarely observed in empirical data since more than two variants of a gene are usually present in the population.
-    However, it is frequent to observe sites inside a gene sequence for which only two alleles are segregating.
-    This observation led to the development of a site-specific Wright-Fisher process, assuming that each site follows an independent process.
-    Strictly speaking, this model considers a collection of independently evolving loci, meaning without linkage.
-    It provides a good approximation if there is free recombination between sites.
-    Moreover, the collection is considered infinite whereas the total mutation rate across this infinite collection is considered finite.
-    The assumption of an infinite number of sites is necessary to ensure that each mutation arises at a new site, with a Poisson distribution of total rate $u$ per generation for the whole sequence.
-
-    From an empirical perspective, for a sample of $n$ sequences taken in the population, the expected number of sites with $i$ copies of the derived allele (with $i$ ranging from $1$ to $n - 1$) is denoted $G(i, n)$.
-    The collection of all $G(i, n)$ generates what is called a site frequency spectrum ({SFS}), which can intuitively be interpreted as the discrete version of the expected time at a derived frequency, readily available from a sample of sequences from a population.
-    Given the scaled selection coefficient ($S=4 \Ne s$), and the scaled mutation rate per generation for the whole sequence ($\theta = 4 \Ne u $), each entry of the {SFS} is:
-    \begin{align}
-        G(i, n) & = \int_{0}^{1}  2 \Ne u g(x, S) \binom{n}{i} x^{i} (1-x)^{n-i} \der x \\
-        & = \theta \int_{0}^{1} \dfrac{1 - \e^{-S(1-x)}}{(1 - \e^{-S})x(1-x)} \binom{n}{i} x^{i} (1-x)^{n-i} \der x \\
-        & =  \dfrac{\theta }{1 - \e^{-S}} \binom{n}{i} \int_{0}^{1} \left( 1 - \e^{-S(1-x)} \right) x^{i-1} (1-x)^{n-i-1} \der x
-    \end{align}
-
-    This site frequency spectrum can be confronted to empirical polymorphic data in order to estimate the scaled selection coefficient of new mutations.
-    However, a single selection coefficient for all sites and all mutations is biologically not realistic.
-    Accordingly, a distribution of selection coefficients across sites is assumed, which is usually modelled as a continuous distribution, known as the distribution of fitness effects of mutations (DFE).
-    Mixing over this distribution, the SFS can then be computed as a function of the underlying DFE, and can thus be estimated based on empirical data\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009}.
-
-    \printbibliography
-
     \include{include-figures}

### 2022-04-07 manuscript/main.tex
Each experiment has its own folder
Manuscript updated.

@@
 \usepackage{amssymb,amsfonts,amsmath,amsthm,mathtools}
-\usepackage{textcomp}
-\usepackage{gensymb}
-\usepackage{cancel}
 \usepackage{lmodern}
 \usepackage{xfrac, nicefrac}
-\usepackage{blkarray}
-\usepackage{pgf,tikz}
-\usetikzlibrary{positioning,arrows,automata,calc}
 \usepackage{bm}
@@
 \usepackage{graphicx}
-\usepackage{tabu}
-\usepackage{hhline}
-\usepackage{multicol,multirow,array}
-\usepackage{etoolbox}
-\usepackage{booktabs}
-
-\usepackage[flushleft] {threeparttable}
 \usepackage{bbold}
 \usepackage{pdfpages}
-\usetikzlibrary{positioning}
-\usetikzlibrary{arrows,automata}
 \pdfinclusioncopyfonts=1
-\usepackage{nicefrac} % compact symbols for 1/2, etc.
-\usepackage{microtype} % microtypography
 \usepackage{lineno}
-
-\newcommand{\specialcell}[2][c]{%
-    \begin{tabular}[#1]{@{}c@{}}
-        #2
-    \end{tabular}}
 
@@
 \newcommand{\BiDimArray}[1]{\bm{#1}}
-
 \DeclareMathOperator{\E}{\mathbb{E}}
@@
 \newcommand{\der}{\mathrm{d}}
-\newcommand{\angstrom}{\mathrm{\normalfont\AA}}
 \newcommand{\e}{\mathrm{e}}
@@
 \newcommand{\Ne}{N_{\mathrm{e}}}
-\newcommand{\Ner}{N_{\mathrm{r}}}
-\newcommand{\dn}{d_N}
-\newcommand{\ds}{d_S}
-\newcommand{\dnds}{\dn / \ds}
-\newcommand{\pn}{\pi_N}
-\newcommand{\ps}{\pi_S}
-\newcommand{\pnps}{\pn / \ps}
 \newcommand{\proba}{\mathbb{P}}
 \newcommand{\pfix}{\proba_{\mathrm{fix}}}
-\newcommand{\Pfix}{2 \Ne \proba_{\mathrm{fix}}}
-\newcommand{\indice}{a}
-\newcommand{\indiceexp}{^{(\indice)}}
+\newcommand{\Spop}{\beta}
+\newcommand{\SpopMean}{\overline{\Spop}}
+\newcommand{\Sphy}{S}
+\newcommand{\SphyMean}{\overline{\Sphy}}
 
 \renewcommand{\baselinestretch}{1.5}
-\renewcommand{\arraystretch}{0.6}
 \linenumbers
 
-\title{Selection coefficients at the phylogenetic and population-genetic scale}
+\title{Empirical evidence for positive selection that is not adaptive evolution}
 
@@
     \large
-    T. {Latrille}$^{1}$, N. {Salamin}$^{1}$\\
-    $^{1}$Université de Lausanne, Lausanne, Switzerland
+    \textbf{T. {Latrille}$^{1}$, J. {Joseph}$^{2}$, N. {Salamin}$^{1}$}\\
+    \normalsize
+    $^{1}$Université de Lausanne, Lausanne, Switzerland\\
+    $^{1}$Université de Lyon, Lyon, France \\
+    \texttt{\href{mailto:thibault.latrille@ens-lyon.org}{thibault.latrille@ens-lyon.org}} \\
 }
@@
     \begin{abstract}
-        At the phylogenetic scale, recent mutation-selection models provide a direct estimate of the selection coefficient for any mutation in a coding sequence, depending on the amino-acids involved in the mutation.
-        At the population-genetic scale, the frequency at which a polymorphism segregates in a population is also a function of its selection coefficient.
-        Taking advantage of this relationship between phylogenetic and population genetics, we can assess whether selection coefficients estimated at the phylogenetic scale can predict the frequency of polymorphism.
-        In this study, we integrated divergence and polymorphism data across the entire exome for 29 populations across 7 genera, and showed that selection coefficients are correlated at the phylogenetic and population-genetic scales.
-        Altogether, our work is paving the way for studies and methods augmenting molecular polymorphism data within species with information about divergence data between species, and by assessing empirically the relationship between phylogenetic and population genetics.
+        Evidence for positive selection occurring in protein-coding DNA sequence is widespread across different taxa.
+        Positive selection can be a result of adaptive evolution, meaning that individuals have had to adapt to a change in environment or selective pressure.
+        However, current positive selection can also be the result of mutations compensating for deleterious substitutions that have accumulated along lineages, in which case positive selection is non-adaptive and predictable.
+        To evaluate the extent of non-adaptive positive selection, we have combined population-genetics and phylogenetics datasets.
+        We first leveraged phylogenetic codon models which are based on a population-genetics formalism, assuming a non-adaptive fitness landscape.
+        These models estimate the fitness of each of the 20 amino acids for each protein site, given mammalian protein-coding DNA alignments and gene tree topologies.
+        Second, we integrated mammalian divergence data with polymorphic variants found in 29 populations across 7 mammalian genera.
+        For each non-synonymous variant observed at the population level, we predicted its change in fitness from amino-acid fitnesses estimated at the mammalian scale.
+        We found that a large proportion of observed non-synonymous changes are predicted to be positively selected, meaning that the ancestral allele is sub-optimal.
+        These supposedly advantageous variants are indeed showing signs of recent positive selection in all populations.
+        Our work confirms that deleterious substitutions have accumulated across the phylogeny and are currently being compensated for, resulting in widespread positive selection that is not adaptive evolution.
+        This study also shows the leverage obtained by integrating phylogenetic and population genetics on a common formalism.
     \end{abstract}
@@
 
-    \tableofcontents
+    Adaptive evolution in proteins can be quantified by comparing sequence variation inside a population to the sequence divergence with a sister species\cite{mcdonald_adaptative_1991}.
+    This method has been largely improved\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009, galtier_adaptive_2016, tataru_inference_2017}, and it's application across many taxa has uncovered that a large proportion of substitutions are positively selected\cite{moutinho_variation_2019}.
+    In practice, the estimated proportion of fixed substitutions that are positively selected varies from 30\% to 70\%.
+    Inside a protein, structural properties such as solvent exposure are positively correlated with the proportion of positively selected substitutions\cite{moutinho_impact_2019}.
+    The root causes for this widespread rate of positive selection are however scarcely investigated, often assumed to be the end result of change in the environment or in selection pressure driving individuals to adapt.
+    In this view, positive selection is adaptive and the two terms are confounded, such that the underlying fitness landscape is changing with time, theoretically known as seascape~\cite{mustonen_fitness_2009}.
+    However, even under the assumption that the fitness landscape is immutable, the nearly-neutral theory\cite{ohta_nearly_1992} predicts that positive selection can occur to compensate for deleterious substitutions that have accumulated along lineages.
+    Theoretically, at the nearly-neutral equilibrium, the net flow of deleterious and advantageous mutations reaching fixation are equal~\cite{sella_application_2005}.
+    In other words, mutations are more likely to be deleterious but are less likely to reach fixation, and the total number of fixation are compensated.
+    In this view of positive selection, advantageous mutations are predictable and evolution is non-adaptive since individuals are not climbing toward higher fitness in the fitness landscape~\cite{lassig_predicting_2017}.
+    Altogether, the goad is this study is to evaluate the extent of non-adaptive positive selection, by combining population-genetics and phylogenetics datasets, and ask a broad range of questions.
+    Are proteins optimal?
+    Is the fitness landscape stable across the mammalian evolution?
+    Can we use phylogenetics to predict the selection coefficient of a mutation?
+    Are deleterious mutations reliably purged only when selection overpowers drift?
 
-    \section{Introduction}\label{sec:introduction}
-%TC:endignore
+    A necessary step is being able to estimate fitness landscape on long-term evolution at the phylogenetic scale.
+    So called mutation-selection codon models provide a nearly-neutral model of evolution by estimating the fitness landscape over amino-acid sequences, for each site of the sequence\cite{ halpern_evolutionary_1998, rodrigue_mechanistic_2010, tamuri_estimating_2012}.
+    Only nearly-neutral mutations between high fitness amino acids will tend to be permitted by the model, allowing for the explicit calculation of the scaled selection coefficient of non-synonymous mutations between codons.
+    These models have be used as a null-model to predict the overall rate of evolution of proteins\cite{spielman_relationship_2015, dosreis_how_2015}, from which a departure in the observed overall rate that proteins are evolving under a changing fitness landscape\cite{rodrigue_detecting_2017, tamuri_mutationselection_2021} and is a signal of adaptive evolution\cite{rodrigue_bayesian_2021}.
+    Available multiple sequence alignment between mammalian species\cite{ranwez_orthomam_2007, howe_ensembl_2021} are used to estimate fitness landscape on long-term evolution.
 
-    In phylogeny-based methods, mutation-selection models provide a nearly-neutral model of evolution by estimating the fitness landscape over amino-acid sequences, for each site of the sequence\cite{yang_mutationselection_2008, halpern_evolutionary_1998, rodrigue_mechanistic_2010}.
-    At the mutation-selection balance, the probability for a specific codon to be fixed in the population is proportional to its fitness, and a mutation from a high fitness amino-acid towards a low fitness amino-acid will have a small probability of fixation, genuinely accounting for purifying selection.
-    Conversely, only nearly-neutral mutations between high fitness amino acids will tend to be permitted by the model, allowing for the explicit calculation of the scaled selection coefficient of non-synonymous mutations at mutation-selection balance\cite{spielman_relationship_2015, rodrigue_detecting_2017}.
-    In this study, we thus first applied mutation-selection codon models to whole exome data from placental mammals, such as to quantify the amino-acid fitness profile for each site of each protein.
+    \begin{figure*}[!ht]
+        \centering
+        \includegraphics[width=\textwidth, page=1] {artworks/figure1}
+        \caption{
+            Integrating divergence and polymorphism for the detection of adaptation.
+            At the phylogenetic level (panel A), amino-acid Wrightian fitness for each site are estimated from protein-coding DNA alignments using mutation-selection codon models.
+            At the population-genetic level (panel B), for each observed single nucleotide polymorphism (SNP), selection coefficient are computed as the difference in amino-acid fitness between the ancestral and derived variant.
+        }
+        \label{fig:method}
+    \end{figure*}
 
-    The goal of this study is to assess whether the signal of selection at the phylogenetic and population-genetic scale are correlated.
-    The population- and phylogeny-based methods work over very different time scales, for that reason, they might be capturing different signals.
-    Nonetheless, we expect sites and proteins under long-term evolution to maintain their signal of selection in several independent lineages for which we computed the unfolded site frequency spectrum (SFS).
-    To test this hypothesis, we leverage a pipeline integrating divergence and polymorphism data across the entire exome for 29 populations across 7 genera, namely \textit{Equus}, \textit{Canis}, \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus} and \textit{Homo}.
+    % How to articulate phylogenetic and population genetic
+    This information can be contrasted with the observed variation inside population, such that we can predict the scaled selection coefficient (the change in fitness) for each non-synonymous single nucleotide polymorphism (SNP) observed in a population (fig.~\ref{fig:method}).
+    We developed and leveraged a pipeline integrating divergence and polymorphism data across the entire exome for 29 populations across 7 genera, namely \textit{Equus}, \textit{Canis}, \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus} and \textit{Homo}.
+    For each non-synonymous SNP observed at the population level, we predicted its scaled selection coefficient ($\Sphy$) in fitness from amino-acid fitness estimated at the mammalian scale (fig.~\ref{fig:homo-afr-results}A).
+    Then we ask whether the variants that are supposedly advantageous are showing signature of short term evolution.
+    In other words, if a variant is found in many mammals but not in ancestral humans, and a mutation in human is toward the mammal version, is this mutation advantageous for the individual carry it?
+    All observed SNPs are divided in 5 classes of selection: severely deleterious with $\Sphy<-3$, deleterious with $-3<\Sphy<-1$, weakly deleterious with $-1<\Sphy<0$, weakly advantageous with $0<\Sphy<1<$ and advantageous with $1<\Sphy$.
+    For each class of selection, we first derived its site-frequency spectrum (SFS), which represent the proportion of mutations with a given number of derived allele in the population (fig.~\ref{fig:homo-afr-results}B).
+    Compared to synonymous mutations (supposedly neutral), mutations predicted to be advantageous are over-represented at higher frequency, while severally deleterious are under-represented at high frequency, a signature that our prediction are qualitatively in the right direction.
+    Aside from the frequency of the derived allele, another information is the total number of observed alleles compared to its expectation, given by the total mutation rate.
+    The total mutation rate for each class is computed from the ancestral genome reconstruction (fig.~\ref{fig:homo-afr-results}C).
+    For example, for the category of selection with $1<\Sphy$, the expected total mutation rate is obtained by adding together mutation rates for all possible non-synonymous mutations for which the derived allele ($d$) is toward a fitter amino-acid than the ancestral allele ($a$) with $S > 1$.
+    The total mutation rate and the SFS are combined to estimate the distribution of the selection coefficient given by population-based model~\cite{tataru_inference_2017, tataru_polydfe_2020}.
+    These population based models cannot give a specific estimate of $\Spop$ for each SNP, but by gathering information across many SNPs, they can estimate the proportion of advantageous mutations $p_+=\proba \left( 1 < \Spop \right)$, of nearly-neutral mutations $p_0=\proba \left( -1 < \Spop < 1 \right)$ and of deleterious mutations $p_-=\proba \left( \Spop < -1 \right)$ (fig.~\ref{fig:homo-afr-results}D).
 
-%TC:ignore
+    \begin{figure*}[!ht]
+        \centering
+        \includegraphics[width=\textwidth, page=1] {artworks/figure2}
+        \caption{
+            Panel A: Histogram of predicted selection coefficient (S) for each observed mutation in a sample of 512 individuals (1024 alleles) with African descent.
+            Mutations are divided in 5 classes of selection: severely deleterious (blue), deleterious (green), weakly deleterious (light green), weakly advantageous (yellow) and advantageous (red).
+            Panel B: Site-frequency spectrum (SFS) represent the proportion of mutations (y-axis) with a given number of derived allele in the population (x-axis).
+            SFS are drawn for a random sample of 16 alleles (mean in solid line and standard deviation in filled color) for each class of selection and for synonymous mutations supposedly neutral (black).
+            Supposedly advantageous are over-represented at higher frequency, while severally deleterious are under-represented at high frequency, a signature of selection.
+            Panel C. Histogram of predicted selection coefficient (S) for each possible mutation away from the ancestral human genome, weighted by the mutation rate.
+            For each class of selection, the sum of histogram in this class thus gives the expected total mutation rate toward this class.
+            If they are less mutations observed than expected, this class is thus undergoing purifying selection.
+            Panel D.
+For each class of selection (and for the set of all non-synonymous mutations), information from the SFS and the expected total mutation rate are combined at the population-genetic scale to estimate the proportion of advantageous mutations $p_+=\proba \left( 1 < \Spop \right)$, of nearly-neutral mutations $p_0=\proba \left( -1 < \Spop < 1 \right)$ and of deleterious mutations $p_-=\proba \left( \Spop < -1 \right)$.
+        }
+        \label{fig:homo-afr-results}
+    \end{figure*}
 
-    \section{Methods}\label{sec:methods}
+    \begin{figure*}[!ht]
+        \centering
+        \includegraphics[width=\textwidth, page=1] {artworks/figure3}
+        \caption{
+            Reproducibility of results shown in figure~\ref{fig:homo-afr-results} in 29 populations across 7 genera.
+            From a site-frequency spectrum and total mutation rates are combined at the population-genetic scale to estimate the proportion of advantageous mutations $p_+=\proba \left( 1 < \Spop \right)$ in top panel, of nearly-neutral mutations $p_0=\proba \left( -1 < \Spop < 1 \right)$ in middle panel and of deleterious mutations $p_-=\proba \left( \Spop < -1 \right)$ in bottom panel.
+        }
+        \label{fig:all-pop-results}
+    \end{figure*}
 
-    \subsection*{Phylogenetic dataset}
-    protein-coding DNA sequences alignments in placental mammals are extracted from the \href{https://www.orthomam.univ-montp2.fr}{OrthoMaM} database\cite{ranwez_orthomam_2007, douzery_orthomam_2014, scornavacca_orthomam_2019}.
+    Because of this observed overlap between phylogenetic and population-genetic methods, both estimating a scaled selection coefficient, we could study the estimation of the mean $\SpopMean$ as a function of the mean $\SphyMean$.
+    However, the mean selection coefficient estimated at the phylogenetic scale is usually drastically negative because of the heavy tail of the negative part of the estimated DFE.
+    Hence we focused on the relationship between $\SpopMean$ and $\SphyMean$ for a subset of SNPs, for which $\Sphy$ is close to $0$.
+    Sliding window of groups of $5.000$ SNPs are taken with a mean $\SphyMean$ between $-0.5$ and $0.5$ (fig.~\ref{fig:selcoeff-pop-phylo}A). 
+    $\SpopMean$ is estimated for each group, with some groups that might have part of same SNPs that overlap.
+    The relationship between $\Spop$ and $\SphyMean$ is best described as a second order polynomial, and the slope of this polynomial at $\SphyMean=0$ gives the ratio $\Spop/\Sphy$ for each population.
+    We observ that $\Spop/\Sphy$, representing the efficiency of selection at the short versus long term is positively correlated with synonymous diversity, a proxy of effective population siz.
+    Altogether, population with large effective population size are under more efficient selection.
+
+    \begin{figure*}[!ht]
+        \centering
+        \includegraphics[width=\textwidth, page=1] {artworks/figure4}
+        \caption{
+            Panel A. Mean selection coefficient at the population scale $\SpopMean$ as a function of phylogenetic $\SphyMean$.
+            Observed SNPs are sorted and groups of $5.000$ SNPs are taken as a sliding windows with increasing mean $\SphyMean$.
+            For each group, $\SpopMean$ (y-axis) is estimated based on SFS and the total mutation rate (between both extreme of $\SphyMean$ in the group) and compared to the mean $\Sphy$ (y-axis).
+            A second order polynomial is fitted for each population, and the slope of this polynomial at $\SphyMean=0$ gives the ratio $\SpopMean/\SphyMean$ given in legend.
+            Panel B. Ratio $\SpopMean/\SphyMean$ as a function of the synonymous diversity for each population.
+            Populations with higher diversity are showing higher ratio of ratio $\SpopMean/\Sphy$.
+        }
+        \label{fig:selcoeff-pop-phylo}
+    \end{figure*}d
+
+    % Our study is a bridge between phylogenetic and population genetics
+    From a theoretical evolution perspective, we found that we could use phylogenetics to predict the selection coefficient of a mutation.
+    Appart from phylogenetic mutation-selection codon models, SIFT scores based on amino-acid alignments across species have already be found to be informative of the selection pressure exerted at the population scale\cite{chen_hunting_2021}.
+    However, they do not integrate the underlying phylogeny nor the underlying mutational process.
+    Additionally, they are not based on population-genetics formalism, hence the relationship between selection coefficient and SIFT score is not straightforward.
+    We found here that mutation-selection formalism greatly outperforms SIFT score to predict the selection coefficient of mutations (Supplementary Materials).
+    Most importantly, we showed that mutation-selection codon models formalize a bridge between phylogenetics and population genetics.
+    Our study is a bridge between phylogenetic and population genetics, but both ends has its limitation.
+
+    % Problem with the current mutation-selection model, and the way forward
+    For phylogenetic models, current mutation-selection codon model are sensitive to mis-alignment.
+    They are also assuming no changes in effective population size\cite{latrille_inferring_2021}.
+    Epistasis is not modelled while it can have drastic consequence on the change in fitness landscape\cite{latrille_quantifying_2021}.
+    However, both relaxation are computationally intensive, and would require new mutation-selection models and optimization techniques to be able to manipulate genome-wide datasets.
+    For population-genetic model, the distribution of fitness effects have so far been assumed to be constrained by
+    The DFE is assumed to be a gamma-distribution for deleterious mutations and an exponential for advantageous mutations, thus implicitly assuming a peak around 0.
+    The DFE predicted from fitness landscapes are very different, with peak is shifted toward negatively selected mutations.
+    Moreover, these methods estimate selection coefficient that are very negative on average, which is not biologically sensible.
+    Altogether, we should seek to reproduce our experiment with other clades, such as drosophila, birds and with for more shallow but wider phylogeny to determine the extend of reproducibilty of our results.
+
+    % We should take that into account.
+    From a structural biology perspective, we found that proteins are not optimal, with a large proportion of mutations still toward more optimal amino acids.
+    Seen from another angle, it means that we could theoretically derive the fittest proteins using only the amino acid with the highest fitness.
+    We could then test whether fittest proteins are also thermodynamically more stable, leveraging recent developments able to compute efficiently and accurately the folding of proteins.
+    From an evolutionary biology perspective, we found that the fitness landscape is relatively stable across the mammalian evolution.
+    Mutations with $\Sphy<-1$ are more strongly purged, mutations with $1<\Sphy$ are more often segregating.
+    However, how to reliably quantify the overlap between phylogenetic and population-genetic methods?
+    The DFE has indeed be found to be reliably constant between species\cite{castellano_comparison_2019}.
+    Are deleterious mutations reliably purged only when selection overpowers drift?
+    Yes, mutations with predicted $-1<\Sphy<1$ are equivalent to neutral mutations.
+
+    \section*{Acknowledgment}
+    \label{sec:acknowledgment}
+    We gratefully acknowledge the help of Nicolas Lartillot for his advice and review concerning this manuscript.
+    This work was performed using the computing facilities of the CC LBBE/PRABI\@.
+    \textbf{Funding:}
+    Université de Lausanne;
+    French National Research Agency, Grant ANR-19-CE12-0019 / HotRec.
+    \textbf{Author contributions:}
+    Original idea: T.L.\ and J.J.;
+    Model conception: T.L., J.J.\ and N.S.;
+    Code: T.L.;
+    Data analyses: T.L.\ and J.J.;
+    Interpretation: T.L., J.J.\ and N.S.;
+    First draft, editing and revisions: T.L., J.J.\ and N.S.;
+    Project management and funding: N.S\@.
+    \textbf{Competing interests:}
+    The authors declare no conflicts of interest.
+    \textbf{Data and materials availability:}
+    Snakemake pipeline, analysis scripts and documentations are available at \href{https://github.com/ThibaultLatrille/SelCoeff}{github.com/ThibaultLatrille/SelCoeff}.
+
+    \section{Material \& Methods}
+    \label{sec:methods}
+
+    \subsection{Phylogenetic dataset}
+
+    Protein-coding DNA sequences alignments in placental mammals are extracted from the \href{https://www.orthomam.univ-montp2.fr}{OrthoMaM} database\cite{ranwez_orthomam_2007, douzery_orthomam_2014, scornavacca_orthomam_2019}.
     Genes located on the X, Y and mitochondrial chromosome are discarded from the analysis, since the number of polymorphism, necessary in population-based method, is expected to be different on these sequences.
@@
 
-    \subsection{Selection coefficient in phylogeny-based method}
+    \subsection{Selection coefficient (S) in phylogeny-based method}
+    \label{subsec:s-phylogeny-method}
+
     Mutation-selection models assume that the protein-coding sequence is at mutation-selection balance under a fixed fitness landscape, which is itself characterized by a fitness vector over the $20$ amino-acid at each site\cite{yang_mutationselection_2008, halpern_evolutionary_1998, rodrigue_mechanistic_2010}.
@@
     \begin{equation}
-        q_{a \mapsto b}^{(i)} = \mu_{a \mapsto b} \proba_{a \mapsto b}^{(i)} = \mu_{a \mapsto b} \dfrac{F_b^{(i)} - F_a^{(i)}}{1 - \e^{F_a^{(i)} - F_b^{(i)}}}.
+        q_{a \mapsto b}^{(i)} = \mu_{a \mapsto b} \proba_{a \mapsto b}^{(i)} = \mu_{a \mapsto b} \dfrac{F_b^{(i)} - F_a^{(i)}}{1 - \e^{F_a^{(i)} - F_b^{(i)}}}.\label{eq:equation}
     \end{equation}
-
     Fitting the mutation-selection model on a sequence alignment leads to an estimation of the mutation rate matrix ($\UniDimArray{\mu}$) as well as the 20 amino-acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$.
-
     We ran the Bayesian software \href{https://github.com/bayesiancook/bayescode}{BayesCode} on each protein-coding DNA alignment\cite{lartillot_phylobayes_2013, rodrigue_detecting_2017}.
-    Each Monte-Carlo Markov-Chain (MCMC) is run during $2000$ points, with a burn-in of $1000$ points, allowing to compute the mean amino-acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$ across the MCMC.
+    Each Monte-Carlo Markov-Chain (MCMC) is run during $2000$ points, with a burn-in of $1000$ points, allowing to compute the mean amino-acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$ across the MCMC\@.
 
     \subsection{Polymorphism dataset}
+    \label{subsec:polymorphism-dataset}
 
@@
     We retrieved polymorphism from different projects.
-    \textit{Equus caballus} variants called on the EquCab2 assembly in the EVA study PRJEB9799, we considered \textit{Ceratotherium simum simum} as its sister species.
-    \textit{Canis familiars} variants called on the CanFam3.1 assembly in the EVA study PRJEB24066, we considered \textit{Ursus maritimus} as its sister species.
-    \textit{Bos taurus} variants called on the UMD3.1 assembly in the next-gen project, we considered \textit{Bison bison bison} as its sister species.
-    \textit{Ovis aries} variants called on the Oar\_v3.1 assembly in the next-gen project, we considered \textit{Pantholops hodgsonii} as its sister species.
-    \textit{Capra Hircus} variants called on the CHIR1 assembly in the next-gen project, we performed a liftover to the ARS1 assembly and considered \textit{Pantholops hodgsonii} as its sister species.
-    \textit{Chlorocebus sabaeus} variants are called on the ChlSab1.1 assembly in the EVA study PRJEB22989\cite{svardal_ancient_2017}, we considered \textit{Macaca mulatta} as its sister species.
-    \textit{Homo sapiens} variants are called on the GRCh38 assembly in the 1000-genome project\cite{consortium_integrated_2012, the1000genomesprojectconsortium_global_2015}, we considered \textit{Pan troglodytes} as its sister species.
+    \textit{Equus caballus} variants called on the EquCab2 assembly in the EVA study PRJEB9799.
+    \textit{Canis familiars} variants called on the CanFam3.1 assembly in the EVA study PRJEB24066.
+    \textit{Bos taurus} variants called on the UMD3.1 assembly in the next-gen project.
+    \textit{Ovis aries} variants called on the Oar\_v3.1 assembly in the next-gen project.
+    \textit{Capra Hircus} variants called on the CHIR1 assembly in the next-gen project, we performed a liftover to the ARS1 assembly.
+    \textit{Chlorocebus sabaeus} variants are called on the ChlSab1.1 assembly in the EVA study PRJEB22989\cite{svardal_ancient_2017}.
+    \textit{Homo sapiens} variants are called on the GRCh38 assembly in the 1000-genome project\cite{consortium_integrated_2012, the1000genomesprojectconsortium_global_2015}.
     Variants not inside genes are discarded at the beginning of the analysis.
@@
     Stop codon mutants are also discarded.
-    For populations containing more than $8$ sampled individuals, the site-frequency spectrum (SFS) is subsampled down to $16$ chromosomes ($8$ diploid individuals) without replacement (hyper-geometric distribution) to alleviate the effect of different sampling depth in the $29$ populations.
-    Moreover, subsampling mitigate the impact of moderately deleterious mutations segregating at low frequency on $\pnps$, since they are more likely to be discarded than polymorphism segregating at higher frequency.
-    SNPs are polarized using the $3$ closest outgroups found in the OrthoMam alignment with est-usfs\cite{keightley_inferring_2018}.
+    For populations containing more than $8$ sampled individuals, the site-frequency spectrum (SFS) is sub-sampled down to $16$ chromosomes ($8$ diploid individuals) without replacement (hyper-geometric distribution) to alleviate the effect of different sampling depth in the $29$ populations.
+    SNPs are polarized using the $3$ closest out-groups found in the OrthoMam alignment with est-usfs\cite{keightley_inferring_2018}.
     The Snakemake pipeline for integrating polymorphism and divergence data uses custom scripts written in python 3.8.
 
-    \subsection{Site frequency spectrum}
-    The probability of fixation of an allele can be empirically observable, and in the context of a Wright-Fisher processes it is related to selection and drift.
-    However, this absorbing fate is not the sole characteristic of the process that relates empirical observable quantities to parameters of the process.
-    Along the whole trajectory of an allele, before fixation or extinction, the probability of this allele to be at a certain frequency can be related to its selection coefficient and to the effective population size.
-    More precisely, $g(x) \der x $ is the expected time for which the population frequency of derived allele is in the range $(x, x+\der x)$ before eventual absorption, which is derived using the Kolmogorov forward equation as a function of $x$ and $S$:
-    \begin{align}
-        g(x, s, \Ne) & = \dfrac{\left( 1 - \e^{- 2 s }\right) \left( 1 - \e^{-4 \Ne s(1-x)}\right)}{ s (1 - \e^{-4 \Ne s})x(1-x)} \\
-        \Rightarrow g(x, S) & \approx \dfrac{2 \left( 1 - \e^{-S(1-x)}\right)}{(1 - \e^{-S})x(1-x)} \label{eq:expected_time}
-    \end{align}
-
-    \begin{center}
-        \includegraphics[width=0.4\textwidth, page=4] {artworks/figures.pdf}
-        \flushleft
-        Expected time at a derived frequency $g(x, S)$ in the vertical axis as a function of the frequency $x$, shown for different scaled selection coefficient.
-        Allele with a positive selection coefficient can be observed at high frequency, while alleles with negative selection coefficients are unlikely to be observed at high frequency.
-    \end{center}
-
-    This equation is solely valid for a gene with two alleles, a configuration which is rarely observed in empirical data since more than two variants of a gene are usually present in the population.
-    However, it is frequent to observe sites inside a gene sequence for which only two alleles are segregating.
-    This observation led to the development of a site-specific Wright-Fisher process, assuming that each site follows an independent process.
-    Strictly speaking, this model considers a collection of independently evolving loci, meaning without linkage.
-    It provides a good approximation if there is free recombination between sites.
-    Moreover, the collection is considered infinite whereas the total mutation rate across this infinite collection is considered finite.
-    The assumption of an infinite number of sites is necessary to ensure that each mutation arises at a new site, with a Poisson distribution of total rate $u$ per generation for the whole sequence.
-
-    From an empirical perspective, for a sample of $n$ sequences taken in the population, the expected number of sites with $i$ copies of the derived allele (with $i$ ranging from $1$ to $n - 1$) is denoted $G(i, n)$.
-    The collection of all $G(i, n)$ generates what is called a site frequency spectrum ({SFS}), which can intuitively be interpreted as the discrete version of the expected time at a derived frequency, readily available from a sample of sequences from a population.
-    Given the scaled selection coefficient ($S=4 \Ne s$), and the scaled mutation rate per generation for the whole sequence ($\theta = 4 \Ne u $), each entry of the {SFS} is:
-    \begin{align}
-        G(i, n) & = \int_{0}^{1}  2 \Ne u g(x, S) \binom{n}{i} x^{i} (1-x)^{n-i} \der x \\
-        & = \theta \int_{0}^{1} \dfrac{1 - \e^{-S(1-x)}}{(1 - \e^{-S})x(1-x)} \binom{n}{i} x^{i} (1-x)^{n-i} \der x \\
-        & =  \dfrac{\theta }{1 - \e^{-S}} \binom{n}{i} \int_{0}^{1} \left( 1 - \e^{-S(1-x)} \right) x^{i-1} (1-x)^{n-i-1} \der x
-    \end{align}
-
-    This site frequency spectrum can be confronted to empirical polymorphic data in order to estimate the scaled selection coefficient of new mutations.
-    However, a single selection coefficient for all sites and all mutations is biologically not realistic.
-    Accordingly, a distribution of selection coefficients across sites is assumed, which is usually modelled as a continuous distribution, known as the distribution of fitness effects of mutations (DFE).
-    Mixing over this distribution, the SFS can then be computed as a function of the underlying DFE, and can thus be estimated based on empirical data\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009}.
+    \subsection{Selection coefficient ($\Spop$) in population-based method}
+    \label{subsec:s-polymorphism-method}
+    The probability to sample allele at a given frequency (before fixation or extinction) is informative of its scaled selection coefficient at the population-scale ($\Spop$).
+    Pooled across many sites, the SFS is thus informative on the underlying $\Spop$ of mutations, given we have a neutral expectation.
+    In this configuration, a single $\Spop$ for all sampled mutations is biologically not realistic.
+    Accordingly, a distribution of fitness effects of mutations (DFE) is assumed, usually modelled as a continuous distribution~\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009}.
+    In this study, we used the software polyDFE\cite{tataru_inference_2017, tataru_polydfe_2020}, for which the DFE ($\phi$) is given by a mixture of a $\Gamma$ and Exponential distributions, parameterized by $\Spop_d$ , $b$, $p_b$
+    and $\Spop_b$ as:
+    \begin{equation*}
+        \phi \left( \Spop; \Spop_d , b, p_b, \Spop_b \right) =
+        \begin{dcases}
+            \left( 1 - p_b \right) f_{\Gamma}(-\Spop; -\Spop_d, b) & \text{ if $\Spop \leq 0$,} \\
+            p_b f_{e}(\Spop; \Spop_b) & \text{ if $\Spop \leq 0$,} \\
+        \end{dcases}
+    \end{equation*}
+    where $\Spop_d$ is the mean of the DFE for $\Spop \leq 0$
+    $b$ is the shape of the $\Gamma$ distribution,
+    $p_b$ is the probability that $\Spop > 0$,
+    $\Spop_b$ is the mean of the DFE for $\Spop > 0$,
+    and $f_{\Gamma}(x; m, b)$ is the density of the $\Gamma$ distribution with mean m and shape b, while $f_{e}(x; m)$ is the density of the Exponential distribution with mean $m$.
+    Once the DFE is fitted to the data, the proportion of advantageous ($p_+$), nearly-neutral ($p_0$) and deleterious mutations ($p_-$) are given as:
+    \begin{align*}
+        p_+ &= \proba_{\phi} \left( 1 < \Spop \right) = p_b \int_{1}^{+\infty} f_{e}(\Spop; \Spop_b)  \\
+        p_0 &= \proba_{\phi} \left( -1 < \Spop < 1 \right) = p_b \int_{0}^{1} f_{e}(\Spop; \Spop_b) + \left( 1 - p_b \right) \int_{0}^{1} f_{\Gamma}(\Spop; \Spop_d, b) \\
+        p_- &= \proba_{\phi} \left( \Spop < -1 \right) = \left( 1 - p_b \right) \int_{1}^{+\infty} f_{\Gamma}(\Spop; \Spop_d, b)
+    \end{align*}
+    And finally, the mean of the DFE $\overline{\Spop}$ is given by:
+    \begin{align*}
+        \SpopMean & = \int_{-\infty}^{+\infty} \Spop \phi \left( \Spop; \Spop_d , b, p_b, \Spop_b \right) \\
+                         & =  p_b \Spop_b - \left( 1 - p_b \right) \Spop_d
+    \end{align*}
+    PolyDFE requires one SFS for non-synonymous mutations and one for synonymous mutations (neutral expectation), as well as the total mutation rate (mutation rate per site multiplied by number of sites) on which each SFS has been sampled.
+    The total mutation rate for each SFS is thus obtained using the following three-steps procedure.
+    First, for each gene, the reference DNA sequence is adjusted with ancestral and fixed polymorphism for each population.
+    Second, from this reconstructed sequence, all possible mutations are computed, weighted by the mutation rate between nucleotide estimated at the phylogenetic scale $\UniDimArray{\mu}$.
+    Third, these possible mutation are then classified whether they are synonymous or non-synonymous (stop mutations are excluded), non-synonymous mutations are then also classified depending on their selection coefficient ($\Sphy$).
+    From the SFS and the total mutation rate for the both synonymous and for the class of non-syonymous, polyDFE estimates the DFE $\phi$ using maximum likelihood.\@.
 
     \printbibliography
-
-    \include{include-figures}
 \end{document}

### 2022-04-12 scripts/gather_bounds.py
Plot stacked bar for increasing diversity. Exploratort regression.

@@ -1,0 +1,25 @@
+import os
+import argparse
+import pandas as pd
+from libraries import format_pop
+
+
+def open_tsv(filepath):
+    ddf = pd.read_csv(filepath, sep="\t")
+    ddf["species"], pop = os.path.basename(filepath).replace(".tsv", "").split(".")[-2:]
+    ddf["pop"] = format_pop(pop.replace("_", " "))
+    return ddf
+
+
+def main(args):
+    os.makedirs(os.path.dirname(args.output), exist_ok=True)
+    df_merge = pd.concat([open_tsv(filepath) for filepath in sorted(args.tsv)])
+    df_merge.to_csv(args.output, sep="\t", index=False)
+
+
+if __name__ == '__main__':
+    parser = argparse.ArgumentParser(formatter_class=argparse.ArgumentDefaultsHelpFormatter)
+    parser.add_argument('--tsv', required=False, type=str, nargs="+", dest="tsv", help="Input tsv file")
+    parser.add_argument('--output', required=False, type=str, dest="output", help="Output tsv file")
+    parser.add_argument('--sample_list', required=False, type=str, dest="sample_list", help="Sample list file")
+    main(parser.parse_args())

### 2022-04-12 scripts/libraries.py

@@ -50,7 +50,11 @@ codontable.update({
     'TGC': 'C', 'TGT': 'C', 'TGA': 'X', 'TGG': 'W'})
 confidence_interval = namedtuple('confidence_interval', ['low', 'mean', 'up'])
 sfs_weight = {"watterson": lambda i, n: 1.0 / i, "tajima": lambda i, n: n - i, "fay_wu": lambda i, n: i}
-polydfe_cat_dico = {"P-Ssup0": "$p(1<S^{pop})$", "P-Seq0": "$p(-1<S^{pop}<1)$", "P-Sinf0": "$p(S^{pop}<-1)$"}
+polydfe_cat_dico = {
+    "P-Ssup0": "$\\mathbb{P} [ 1<\\beta ]$",
+    "P-Seq0": "$\\mathbb{P} [ -1<\\beta<1 ]$",
+    "P-Sinf0": "$\\mathbb{P} [ \\beta<-1 ]$",
+}
 polydfe_cat_list = list(polydfe_cat_dico.keys())
 xlim_dico = {"Omega": (0.0, 2.0), "MutSel": (-10, 10), "SIFT": (0.0, 1.0)}
 rate_dico = {"MutSel": "Scaled selection coefficient (S)",
@@ -285,6 +289,46 @@ def sp_sorted(pop, sp):
         return "T" + out
     else:
         return out
+
+
+def extend_pop(p, sample):
+    fp = format_pop(p)
+    if sample[p] == fp:
+        return p
+    else:
+        return f"{sample[p]} ({fp})"
+
+
+def sort_df(df, sample_list_path):
+    df = df.iloc[df.apply(lambda r: sp_sorted(format_pop(r["pop"]), r["species"]), axis=1).argsort()]
+    df["species"] = df.apply(lambda r: r["species"].replace("_", " "), axis=1)
+    df["species"] = df.apply(lambda r: "Ovis orientalis" if r["pop"] == "IROO" else r["species"], axis=1)
+    df["species"] = df.apply(lambda r: "Ovis vignei" if r["pop"] == "IROV" else r["species"], axis=1)
+    df["species"] = df.apply(lambda r: "Capra aegagrus" if r["pop"] == "IRCA" else r["species"], axis=1)
+
+    sample_iterrows = list(pd.read_csv(sample_list_path, sep='\t').iterrows())
+    dico_sample = {format_pop(r["SampleName"].replace("_", " ")): r["Location"] for _, r in sample_iterrows}
+
[…]

### 2022-04-12 scripts/parse_results_DFE.py

@@ -1,9 +1,6 @@
 import argparse
 from scipy.stats import expon, gamma
-import statsmodels.api as sm
-import seaborn as sns
 from libraries import *
-from matplotlib import cm
 
 
 def read_poly_dfe(path):
@@ -29,28 +26,6 @@ def read_poly_dfe(path):
     return out_poly_dfe
 
 
-def plot_color_stack_param(list_cat, cat_snps, cat_poly_snps, s_dico, output):
-    fig, ax = plt.subplots(figsize=(1920 / my_dpi, 960 / my_dpi), dpi=my_dpi)
-    x_pos = range(len(list_cat))
-    hatches_list = ['', '', '//', '//', '']
-    colors = [cat_snps.color(cat) for cat in list_cat]
-    bottom = np.array([0.0] * len(list_cat))
-    for p_i, param in enumerate(cat_poly_snps.non_syn_list[::-1]):
-        y = np.array([s_dico[cat][param] for cat in list_cat])
-        ax.bar(x_pos, y, bottom=bottom, edgecolor="black", color=cat_poly_snps.color(param), hatch=hatches_list[p_i])
-        bottom += y
-    ax.set_xlabel("Category of S at the phylogenetic scale")
-    ax.set_ylabel("Proportion estimated at the population scale")
-    ax.set_xticks(x_pos)
-    ax.set_ylim((0, 1))
-    ax.set_xticklabels([cat_snps.label(cat) for cat in list_cat])
-    for ticklabel, tickcolor in zip(plt.gca().get_xticklabels(), colors):
-        ticklabel.set_color(tickcolor)
-    plt.tight_layout()
-    plt.savefig(output)
-    plt.close("all")
-
-
 def plot_stack_param(list_cat, cat_snps, s_dico, output):
     fig, ax = plt.subplots(figsize=(1920 / my_dpi, 960 / my_dpi), dpi=my_dpi)
     x_pos = range(len(list_cat))
@@ -72,26 +47,6 @@ def plot_stack_param(list_cat, cat_snps, s_dico, output):
         ticklabel.set_color(tickcolor)
     plt.tight_layout()
     plt.savefig(output)
-    plt.close("all")
-
-
-def plot_heatmap(cat_snps, cat_poly_snps, s_dico, output):
-    cat_labels_cols = [cat_snps.label(cat) for cat in cat_snps.non_syn_list]
[…]

### 2022-04-12 scripts/plot_heatmap.py

@@ -3,12 +3,6 @@ from matplotlib import cm
 import seaborn as sns
 from libraries import *
 
-theta_dict = {"watterson": "Watterson $\\theta_W$"}
-
-
-# theta_dict = {"watterson": "Watterson $\\theta_W$", "tajima": "Tajima $\\theta_{\\pi}$ ",
-#               "fay_wu": "Fay and Wu $\\theta_{H}$", "D_tajima": "Tajima's $D$", "H_fay_wu": "Fay and Wu's $H$"}
-
 
 def open_tsv(filepath):
     ddf = pd.read_csv(filepath, sep="\t")
@@ -17,29 +11,61 @@ def open_tsv(filepath):
     return ddf
 
 
+def plot_stack_param(list_pops, df_all, title, output):
+    fig, ax = plt.subplots(figsize=(1920 / my_dpi, 640 / my_dpi), dpi=my_dpi)
+    x_pos = range(len(list_pops))
+    hatches_list = ['', '', '//']
+    colors_list = ["black", "silver", "white"]
+    edgecolors_list = ["black", "black", "black"]
+    bottom = np.array([0.0] * len(list_pops))
+    for p_i, param in enumerate(polydfe_cat_dico):
+        y = df_all[param].values
+        ax.bar(x_pos, y, bottom=bottom, edgecolor=edgecolors_list[p_i], color=colors_list[p_i], hatch=hatches_list[p_i])
+        bottom += y
+    ax.set_title(title)
+    ax.set_xlabel("Population")
+    ax.set_ylabel("Proportion estimated")
+    ax.set_xticks(x_pos)
+    ax.set_ylim((0, 1))
+    ax.set_xticklabels(list_pops)
+    plt.setp(ax.get_xticklabels(), rotation=45, ha="right", rotation_mode="anchor")
+    plt.tight_layout()
+    plt.savefig(output)
+    plt.close("all")
+
+
 def main(args):
     os.makedirs(os.path.dirname(args.output), exist_ok=True)
-    df_merge = pd.concat([open_tsv(filepath) for filepath in sorted(args.tsv)])
-    if ("tajima" in df_merge) and ("watterson" in df_merge) and ("fay_wu" in df_merge):
-        df_merge["D_tajima"] = df_merge["tajima"] - df_merge["watterson"]
-        df_merge["H_fay_wu"] = df_merge["tajima"] - df_merge["fay_wu"]
-        d_dict = theta_dict
-    else:
[…]

### 2022-04-12 scripts/plot_multiple_regression.py

@@ -3,7 +3,6 @@ import argparse
 import numpy as np
 import pandas as pd
 from collections import defaultdict
-import statsmodels.api as sm
 from matplotlib.cm import get_cmap
 from matplotlib.lines import Line2D
 from libraries import my_dpi, format_pop, plt, sp_sorted
@@ -26,7 +25,7 @@ def main(args):
     cm = get_cmap('tab10')
     colors = {sp: cm((i + 1) / len(sp2pop)) for i, sp in enumerate(sp2pop)}
     for method, df_filter in df_merge.groupby(["method"]):
-        plt.figure(figsize=(1920 / my_dpi, 1080 / my_dpi), dpi=my_dpi)
+        plt.figure(figsize=(1920 / my_dpi, 960 / my_dpi), dpi=my_dpi)
         plt.xlim((-0.5, 0.5))
         idf = np.linspace(min(df_filter["S_phy"]), max(df_filter["S_phy"]), 30)
         dico_out = defaultdict(list)
@@ -49,7 +48,7 @@ def main(args):
             plt.scatter(x, y, s=8.0, color=c, edgecolors="dimgrey", alpha=0.5, linewidths=0.05, zorder=zorder + 100)
             dico_out["pop"].append(pop)
             dico_out["species"].append(sp)
-            dico_out["a"].append(ffit.deriv()(0))
+            dico_out["betaS_ratio"].append(ffit.deriv()(0))
 
         df_out = pd.DataFrame(dico_out)
         df_out = df_out.iloc[df_out.apply(lambda r: sp_sorted(format_pop(r["pop"]), r["species"]), axis=1).argsort()]
@@ -62,8 +61,8 @@ def main(args):
         legend_elements = [Line2D([0], [0], color=colors[sp],
                                   label=f'{sp.replace("_", " ")}: f\'(0)={sp_slopes[sp]}') for sp in sp2pop]
         plt.legend(handles=legend_elements)
-        plt.xlabel("$S$ at the phylogenetic scale (Mutation-selection)")
-        plt.ylabel("$S^{pop}$ at the population scale (polyDFE)")
+        plt.xlabel("$\\overline{S}$ at the phylogenetic scale (Mutation-selection)")
+        plt.ylabel("$\\overline{\\beta}$ at the population scale (polyDFE)")
         plt.tight_layout()
         plt.savefig(args.output.replace('results.tsv', f'{method}.SelCoeff.scatter.pdf'), format="pdf")
         plt.clf()

### 2022-04-12 scripts/plot_regression.py

@@ -7,13 +7,28 @@ from collections import defaultdict
 import statsmodels.api as sm
 from matplotlib.cm import get_cmap
 from matplotlib.lines import Line2D
-from libraries import my_dpi, format_pop, plt, sp_sorted
+from libraries import my_dpi, plt, polydfe_cat_dico, tex_f, sort_df, sp_sorted, format_pop, CategorySNP
+
+cat_snps = CategorySNP("MutSel")
+markers = ["o", "d", "s", '.']
 
 
 def open_tsv(filepath):
     ddf = pd.read_csv(filepath, sep="\t")
     if os.path.basename(filepath) == "Theta.results.tsv":
-        ddf = ddf[ddf["category"] == "syn"]
+        df_theta = ddf[(ddf["method"] == "MutSel") & (ddf["category"] == "syn")]
+        df_theta = df_theta.dropna(axis='columns')
+        df_theta = df_theta.drop(["method", "species", "category"], axis=1)
+        df_dfe = ddf[(ddf["method"] == "MutSel") & (ddf["category"] != "syn")]
+        m_list = []
+        for cat_poly in list(polydfe_cat_dico) + [f"P-{cat}" for cat in cat_snps.non_syn_list]:
+            matrix = df_dfe.pivot(index="pop", columns="category", values=cat_poly).add_suffix(f'_{cat_poly}')
+            m_list.append(matrix)
+        df_pivot = pd.concat(m_list, axis=1)
+        ddf = pd.merge(df_pivot, df_theta, on=["pop"])
+    elif "bounds" in os.path.basename(filepath):
+        ddf = ddf[ddf["method"] == "MutSel"]
+        ddf = ddf.pivot(index="pop", columns="cat", values="sampled_fraction").add_suffix('_snps')
     return ddf
 
 
@@ -21,10 +36,61 @@ def discard_col(col, df):
     return (col not in df) or (df.dtypes[col] == np.object) or (not np.all(np.isfinite(df[col])))
 
 
-param_dict = {"watterson": "Watterson $\\theta_W$", "tajima": "Tajima $\\theta_{\\pi}$ ",
+def generate_xy_plot():
+    xy_dico = defaultdict(list)
+    dico_label = {'pop': "Population", "species": "Species", "watterson": "Watterson $\\theta_W$",
+                  "proba": "$\\mathbb{P}$"}
+
+    y_dico = {"tajima": "Tajima $\\theta_{\\pi}$ ",
[…]

### 2022-04-12 scripts/plot_sfs.py

@@ -19,7 +19,7 @@ def normalize_sfs(sfs):
     return (sfs.T / np.sum(sfs, axis=1)).T
 
 
-def plot_sfs(cat_snps, snp_sfs, normed_sfs_syn_mean, max_daf, daf_axis, cat_dico_count, output, scaled):
+def plot_sfs(cat_snps, snp_sfs, normed_sfs_syn_mean, max_daf, daf_axis, output, scaled):
     fig, ax = plt.subplots(figsize=(1920 / my_dpi, 960 / my_dpi), dpi=my_dpi)
     for cat in snp_sfs:
         sfs = snp_sfs[cat][:, 1:].copy()
@@ -35,9 +35,8 @@ def plot_sfs(cat_snps, snp_sfs, normed_sfs_syn_mean, max_daf, daf_axis, cat_dico
 
         mean_sfs = np.mean(sfs, axis=0)
         std_sfs = np.std(sfs, axis=0)
-        label = cat_snps.label(cat) + f" $({int(cat_dico_count[cat])}~mutations)$"
         plt.scatter(daf_axis, mean_sfs, color=cat_snps.color(cat))
-        plt.plot(daf_axis, mean_sfs, label=label, color=cat_snps.color(cat), linewidth=1.0)
+        plt.plot(daf_axis, mean_sfs, label=cat_snps.label(cat), color=cat_snps.color(cat), linewidth=1.0)
         plt.fill_between(daf_axis, mean_sfs - std_sfs, mean_sfs + std_sfs, linewidth=1.0,
                          color=cat_snps.color(cat), alpha=0.2)
     if max_daf < 32:
@@ -90,7 +89,6 @@ def main(args):
                 count = [k]
             snps_daf[cat].append(count)
 
-    cat_dico_count = {cat: len(daf) for cat, daf in snps_daf.items()}
     snp_sfs = {cat: daf_to_sfs(daf, max_daf) for cat, daf in snps_daf.items()}
     snp_sfs_mean = {cat: np.mean(sfs, axis=0) for cat, sfs in snp_sfs.items()}
 
@@ -119,7 +117,7 @@ def main(args):
     normed_sfs_syn_mean = snp_sfs_mean["syn"][1:] / np.sum(snp_sfs_mean["syn"][1:])
     for scaled in ["", "neutral", "normalize", "synonymous"]:
[…]

### 2022-04-13 manuscript/include-MutSel-non-adaptive.tex
Supp. Mat.

\subsection{All populations}
\begin{center}
    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/results/Theta.MutSel.all.stacked.pdf} \\
    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/results/Theta.MutSel.neg-strong.stacked.pdf} \\
    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/results/Theta.MutSel.neg.stacked.pdf} \\
    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/results/Theta.MutSel.neg-weak.stacked.pdf} \\
    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/results/Theta.MutSel.pos-weak.stacked.pdf} \\
    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/results/Theta.MutSel.pos.stacked.pdf}

\end{center}

\subsection{Bos taurus}

\subsubsection{Iran (IRBT)}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Bos_taurus.IRBT.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Bos_taurus.IRBT.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Bos_taurus.IRBT.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Bos_taurus.IRBT.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Uganda (UGBT)}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Bos_taurus.UGBT.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Bos_taurus.UGBT.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Bos_taurus.UGBT.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Bos_taurus.UGBT.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsection{Canis familiaris}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Canis_familiaris.dogs.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Canis_familiaris.dogs.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Canis_familiaris.dogs.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Canis_familiaris.dogs.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsection{Capra}

\subsubsection{Australia (AUCH) - Capra hircus}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Capra_hircus.AUCH.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.AUCH.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Capra_hircus.AUCH.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.AUCH.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{France (FRCH) - Capra hircus}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Capra_hircus.FRCH.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.FRCH.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Capra_hircus.FRCH.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.FRCH.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Iran (IRCA) - Capra aegagrus}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Capra_hircus.IRCA.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.IRCA.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Capra_hircus.IRCA.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.IRCA.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Iran (IRCH) - Capra hircus}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Capra_hircus.IRCH.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.IRCH.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Capra_hircus.IRCH.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.IRCH.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Italy (ITCH) - Capra hircus}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Capra_hircus.ITCH.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.ITCH.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Capra_hircus.ITCH.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.ITCH.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Morocco (MOCH) - Capra hircus}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Capra_hircus.MOCH.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.MOCH.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Capra_hircus.MOCH.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.MOCH.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsection{Chlorocebus sabaeus}

\subsubsection{Barbados}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Chlorocebus_sabaeus.Barbados.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Barbados.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Chlorocebus_sabaeus.Barbados.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Barbados.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Central African Republic (CAR)}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Chlorocebus_sabaeus.Central_African_Republic.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Chlorocebus_sabaeus.Central_African_Republic.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Ethiopia}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Chlorocebus_sabaeus.Ethiopia.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Chlorocebus_sabaeus.Ethiopia.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Gambia}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Chlorocebus_sabaeus.Gambia.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Gambia.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Chlorocebus_sabaeus.Gambia.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Gambia.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Kenya}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Chlorocebus_sabaeus.Kenya.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Kenya.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Chlorocebus_sabaeus.Kenya.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Kenya.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Nevis}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Chlorocebus_sabaeus.Nevis.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Nevis.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Chlorocebus_sabaeus.Nevis.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Nevis.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Saint Kitts (SK)}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Chlorocebus_sabaeus.Saint_Kitts.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Saint_Kitts.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Chlorocebus_sabaeus.Saint_Kitts.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Saint_Kitts.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{South Africa (SA)}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Chlorocebus_sabaeus.South_Africa.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.South_Africa.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Chlorocebus_sabaeus.South_Africa.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.South_Africa.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Zambia}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Chlorocebus_sabaeus.Zambia.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Zambia.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Chlorocebus_sabaeus.Zambia.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Zambia.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsection{Equus caballus}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Equus_caballus.up.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Equus_caballus.up.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Equus_caballus.up.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Equus_caballus.up.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsection{Homo sapiens}

\subsubsection{African (AFR)}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Homo_sapiens.AFR.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.AFR.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Homo_sapiens.AFR.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.AFR.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Ad Mixed American (AMR)}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Homo_sapiens.AMR.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.AMR.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Homo_sapiens.AMR.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.AMR.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{East Asian (EAS)}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Homo_sapiens.EAS.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.EAS.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Homo_sapiens.EAS.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.EAS.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{European (EUR)}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Homo_sapiens.EUR.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.EUR.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Homo_sapiens.EUR.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.EUR.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{South Asian (SAS)}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Homo_sapiens.SAS.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.SAS.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Homo_sapiens.SAS.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.SAS.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsection{Ovis}

\subsubsection{Iran (IROA) - Ovis aries}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Ovis_aries.IROA.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROA.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Ovis_aries.IROA.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROA.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Iran (IROO) - Ovis orientalis}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Ovis_aries.IROO.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROO.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Ovis_aries.IROO.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROO.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Iran (IROV) - Ovis vignei}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Ovis_aries.IROV.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROV.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Ovis_aries.IROV.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROV.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Various (ISGC) - Ovis aries}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Ovis_aries.ISGC.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.ISGC.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Ovis_aries.ISGC.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.ISGC.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Morocco (MOOA) - Ovis aries}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Ovis_aries.MOOA.MutSel.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.MOOA.MutSel-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Ovis_aries.MOOA.MutSel.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.MOOA.MutSel.polyDFE_C.pdf}
\end{minipage}
\\

### 2022-04-13 manuscript/include-Omega-adaptive.tex
Supp. Mat.

\subsection{All populations}
\begin{center}
    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC/results/Theta.Omega.P-Sinf0.heatmap.pdf} \\
    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC/results/Theta.Omega.P-Seq0.heatmap.pdf} \\
    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC/results/Theta.Omega.P-Ssup0.heatmap.pdf} \\
    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC/results/Theta.Omega.all.stacked.pdf} \\
    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC/results/Theta.Omega.neg-strong.stacked.pdf} \\
    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC/results/Theta.Omega.neg.stacked.pdf} \\
    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC/results/Theta.Omega.neg-weak.stacked.pdf} \\
    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC/results/Theta.Omega.pos-weak.stacked.pdf} \\
    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC/results/Theta.Omega.pos.stacked.pdf}
\end{center}

\subsection{Bos taurus}

\subsubsection{Iran (IRBT)}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Bos_taurus.IRBT.Omega.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Bos_taurus.IRBT.Omega-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Bos_taurus.IRBT.Omega.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Bos_taurus.IRBT.Omega.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Uganda (UGBT)}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Bos_taurus.UGBT.Omega.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Bos_taurus.UGBT.Omega-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Bos_taurus.UGBT.Omega.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Bos_taurus.UGBT.Omega.polyDFE_C.pdf}
\end{minipage}
\\

\subsection{Canis familiaris}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Canis_familiaris.dogs.Omega.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Canis_familiaris.dogs.Omega-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Canis_familiaris.dogs.Omega.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Canis_familiaris.dogs.Omega.polyDFE_C.pdf}
\end{minipage}
\\

\subsection{Capra}

\subsubsection{Australia (AUCH) - Capra hircus}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Capra_hircus.AUCH.Omega.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Capra_hircus.AUCH.Omega-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Capra_hircus.AUCH.Omega.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Capra_hircus.AUCH.Omega.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{France (FRCH) - Capra hircus}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Capra_hircus.FRCH.Omega.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Capra_hircus.FRCH.Omega-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Capra_hircus.FRCH.Omega.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Capra_hircus.FRCH.Omega.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Iran (IRCA) - Capra aegagrus}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Capra_hircus.IRCA.Omega.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Capra_hircus.IRCA.Omega-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Capra_hircus.IRCA.Omega.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Capra_hircus.IRCA.Omega.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Iran (IRCH) - Capra hircus}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Capra_hircus.IRCH.Omega.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Capra_hircus.IRCH.Omega-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Capra_hircus.IRCH.Omega.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Capra_hircus.IRCH.Omega.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Italy (ITCH) - Capra hircus}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Capra_hircus.ITCH.Omega.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Capra_hircus.ITCH.Omega-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Capra_hircus.ITCH.Omega.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Capra_hircus.ITCH.Omega.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Morocco (MOCH) - Capra hircus}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Capra_hircus.MOCH.Omega.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Capra_hircus.MOCH.Omega-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Capra_hircus.MOCH.Omega.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Capra_hircus.MOCH.Omega.polyDFE_C.pdf}
\end{minipage}
\\

\subsection{Chlorocebus sabaeus}

\subsubsection{Barbados}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Chlorocebus_sabaeus.Barbados.Omega.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Chlorocebus_sabaeus.Barbados.Omega-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Chlorocebus_sabaeus.Barbados.Omega.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Chlorocebus_sabaeus.Barbados.Omega.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Central African Republic (CAR)}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Chlorocebus_sabaeus.Central_African_Republic.Omega.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Chlorocebus_sabaeus.Central_African_Republic.Omega-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Chlorocebus_sabaeus.Central_African_Republic.Omega.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Chlorocebus_sabaeus.Central_African_Republic.Omega.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Ethiopia}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Chlorocebus_sabaeus.Ethiopia.Omega.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Chlorocebus_sabaeus.Ethiopia.Omega-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Chlorocebus_sabaeus.Ethiopia.Omega.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Chlorocebus_sabaeus.Ethiopia.Omega.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Gambia}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Chlorocebus_sabaeus.Gambia.Omega.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Chlorocebus_sabaeus.Gambia.Omega-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Chlorocebus_sabaeus.Gambia.Omega.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Chlorocebus_sabaeus.Gambia.Omega.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Kenya}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Chlorocebus_sabaeus.Kenya.Omega.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Chlorocebus_sabaeus.Kenya.Omega-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Chlorocebus_sabaeus.Kenya.Omega.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Chlorocebus_sabaeus.Kenya.Omega.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Nevis}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Chlorocebus_sabaeus.Nevis.Omega.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Chlorocebus_sabaeus.Nevis.Omega-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Chlorocebus_sabaeus.Nevis.Omega.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Chlorocebus_sabaeus.Nevis.Omega.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Saint Kitts (SK)}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Chlorocebus_sabaeus.Saint_Kitts.Omega.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Chlorocebus_sabaeus.Saint_Kitts.Omega-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Chlorocebus_sabaeus.Saint_Kitts.Omega.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Chlorocebus_sabaeus.Saint_Kitts.Omega.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{South Africa (SA)}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Chlorocebus_sabaeus.South_Africa.Omega.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Chlorocebus_sabaeus.South_Africa.Omega-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Chlorocebus_sabaeus.South_Africa.Omega.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Chlorocebus_sabaeus.South_Africa.Omega.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Zambia}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Chlorocebus_sabaeus.Zambia.Omega.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Chlorocebus_sabaeus.Zambia.Omega-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Chlorocebus_sabaeus.Zambia.Omega.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Chlorocebus_sabaeus.Zambia.Omega.polyDFE_C.pdf}
\end{minipage}
\\

\subsection{Equus caballus}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Equus_caballus.up.Omega.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Equus_caballus.up.Omega-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Equus_caballus.up.Omega.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Equus_caballus.up.Omega.polyDFE_C.pdf}
\end{minipage}
\\

\subsection{Homo sapiens}

\subsubsection{African (AFR)}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Homo_sapiens.AFR.Omega.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Homo_sapiens.AFR.Omega-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Homo_sapiens.AFR.Omega.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Homo_sapiens.AFR.Omega.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Ad Mixed American (AMR)}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Homo_sapiens.AMR.Omega.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Homo_sapiens.AMR.Omega-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Homo_sapiens.AMR.Omega.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Homo_sapiens.AMR.Omega.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{East Asian (EAS)}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Homo_sapiens.EAS.Omega.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Homo_sapiens.EAS.Omega-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Homo_sapiens.EAS.Omega.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Homo_sapiens.EAS.Omega.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{European (EUR)}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Homo_sapiens.EUR.Omega.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Homo_sapiens.EUR.Omega-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Homo_sapiens.EUR.Omega.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Homo_sapiens.EUR.Omega.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{South Asian (SAS)}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Homo_sapiens.SAS.Omega.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Homo_sapiens.SAS.Omega-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Homo_sapiens.SAS.Omega.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Homo_sapiens.SAS.Omega.polyDFE_C.pdf}
\end{minipage}
\\

\subsection{Ovis}

\subsubsection{Iran (IROA) - Ovis aries}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Ovis_aries.IROA.Omega.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Ovis_aries.IROA.Omega-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Ovis_aries.IROA.Omega.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Ovis_aries.IROA.Omega.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Iran (IROO) - Ovis orientalis}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Ovis_aries.IROO.Omega.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Ovis_aries.IROO.Omega-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Ovis_aries.IROO.Omega.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Ovis_aries.IROO.Omega.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Iran (IROV) - Ovis vignei}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Ovis_aries.IROV.Omega.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Ovis_aries.IROV.Omega-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Ovis_aries.IROV.Omega.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Ovis_aries.IROV.Omega.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Various (ISGC) - Ovis aries}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Ovis_aries.ISGC.Omega.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Ovis_aries.ISGC.Omega-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Ovis_aries.ISGC.Omega.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Ovis_aries.ISGC.Omega.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Morocco (MOOA) - Ovis aries}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Ovis_aries.MOOA.Omega.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Ovis_aries.MOOA.Omega-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Ovis_aries.MOOA.Omega.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Ovis_aries.MOOA.Omega.polyDFE_C.pdf}
\end{minipage}
\\

### 2022-04-13 manuscript/include-SIFT-non-adaptive.tex
Supp. Mat.

\subsection{All populations}
\begin{center}
    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/results/Theta.SIFT.P-Sinf0.heatmap.pdf} \\
    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/results/Theta.SIFT.P-Seq0.heatmap.pdf} \\
    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/results/Theta.SIFT.P-Ssup0.heatmap.pdf} \\
    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/results/Theta.SIFT.all.stacked.pdf} \\
    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/results/Theta.SIFT.neg-strong.stacked.pdf} \\
    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/results/Theta.SIFT.neg.stacked.pdf} \\
    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/results/Theta.SIFT.neg-weak.stacked.pdf} \\
    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/results/Theta.SIFT.pos-weak.stacked.pdf} \\
    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/results/Theta.SIFT.pos.stacked.pdf}
\end{center}

\subsection{Bos taurus}

\subsubsection{Iran (IRBT)}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Bos_taurus.IRBT.SIFT.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Bos_taurus.IRBT.SIFT-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Bos_taurus.IRBT.SIFT.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Bos_taurus.IRBT.SIFT.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Uganda (UGBT)}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Bos_taurus.UGBT.SIFT.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Bos_taurus.UGBT.SIFT-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Bos_taurus.UGBT.SIFT.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Bos_taurus.UGBT.SIFT.polyDFE_C.pdf}
\end{minipage}
\\

\subsection{Canis familiaris}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Canis_familiaris.dogs.SIFT.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Canis_familiaris.dogs.SIFT-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Canis_familiaris.dogs.SIFT.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Canis_familiaris.dogs.SIFT.polyDFE_C.pdf}
\end{minipage}
\\

\subsection{Capra}

\subsubsection{Australia (AUCH) - Capra hircus}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Capra_hircus.AUCH.SIFT.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.AUCH.SIFT-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Capra_hircus.AUCH.SIFT.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.AUCH.SIFT.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{France (FRCH) - Capra hircus}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Capra_hircus.FRCH.SIFT.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.FRCH.SIFT-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Capra_hircus.FRCH.SIFT.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.FRCH.SIFT.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Iran (IRCA) - Capra aegagrus}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Capra_hircus.IRCA.SIFT.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.IRCA.SIFT-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Capra_hircus.IRCA.SIFT.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.IRCA.SIFT.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Iran (IRCH) - Capra hircus}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Capra_hircus.IRCH.SIFT.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.IRCH.SIFT-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Capra_hircus.IRCH.SIFT.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.IRCH.SIFT.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Italy (ITCH) - Capra hircus}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Capra_hircus.ITCH.SIFT.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.ITCH.SIFT-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Capra_hircus.ITCH.SIFT.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.ITCH.SIFT.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Morocco (MOCH) - Capra hircus}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Capra_hircus.MOCH.SIFT.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.MOCH.SIFT-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Capra_hircus.MOCH.SIFT.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.MOCH.SIFT.polyDFE_C.pdf}
\end{minipage}
\\

\subsection{Chlorocebus sabaeus}

\subsubsection{Barbados}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Chlorocebus_sabaeus.Barbados.SIFT.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Barbados.SIFT-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Chlorocebus_sabaeus.Barbados.SIFT.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Barbados.SIFT.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Central African Republic (CAR)}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Chlorocebus_sabaeus.Central_African_Republic.SIFT.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Central_African_Republic.SIFT-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Chlorocebus_sabaeus.Central_African_Republic.SIFT.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Central_African_Republic.SIFT.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Ethiopia}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Chlorocebus_sabaeus.Ethiopia.SIFT.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Ethiopia.SIFT-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Chlorocebus_sabaeus.Ethiopia.SIFT.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Ethiopia.SIFT.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Gambia}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Chlorocebus_sabaeus.Gambia.SIFT.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Gambia.SIFT-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Chlorocebus_sabaeus.Gambia.SIFT.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Gambia.SIFT.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Kenya}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Chlorocebus_sabaeus.Kenya.SIFT.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Kenya.SIFT-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Chlorocebus_sabaeus.Kenya.SIFT.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Kenya.SIFT.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Nevis}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Chlorocebus_sabaeus.Nevis.SIFT.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Nevis.SIFT-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Chlorocebus_sabaeus.Nevis.SIFT.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Nevis.SIFT.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Saint Kitts (SK)}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Chlorocebus_sabaeus.Saint_Kitts.SIFT.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Saint_Kitts.SIFT-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Chlorocebus_sabaeus.Saint_Kitts.SIFT.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Saint_Kitts.SIFT.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{South Africa (SA)}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Chlorocebus_sabaeus.South_Africa.SIFT.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.South_Africa.SIFT-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Chlorocebus_sabaeus.South_Africa.SIFT.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.South_Africa.SIFT.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Zambia}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Chlorocebus_sabaeus.Zambia.SIFT.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Zambia.SIFT-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Chlorocebus_sabaeus.Zambia.SIFT.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Zambia.SIFT.polyDFE_C.pdf}
\end{minipage}
\\

\subsection{Equus caballus}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Equus_caballus.up.SIFT.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Equus_caballus.up.SIFT-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Equus_caballus.up.SIFT.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Equus_caballus.up.SIFT.polyDFE_C.pdf}
\end{minipage}
\\

\subsection{Homo sapiens}

\subsubsection{African (AFR)}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Homo_sapiens.AFR.SIFT.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.AFR.SIFT-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Homo_sapiens.AFR.SIFT.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.AFR.SIFT.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Ad Mixed American (AMR)}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Homo_sapiens.AMR.SIFT.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.AMR.SIFT-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Homo_sapiens.AMR.SIFT.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.AMR.SIFT.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{East Asian (EAS)}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Homo_sapiens.EAS.SIFT.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.EAS.SIFT-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Homo_sapiens.EAS.SIFT.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.EAS.SIFT.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{European (EUR)}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Homo_sapiens.EUR.SIFT.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.EUR.SIFT-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Homo_sapiens.EUR.SIFT.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.EUR.SIFT.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{South Asian (SAS)}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Homo_sapiens.SAS.SIFT.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.SAS.SIFT-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Homo_sapiens.SAS.SIFT.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.SAS.SIFT.polyDFE_C.pdf}
\end{minipage}
\\

\subsection{Ovis}

\subsubsection{Iran (IROA) - Ovis aries}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Ovis_aries.IROA.SIFT.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROA.SIFT-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Ovis_aries.IROA.SIFT.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROA.SIFT.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Iran (IROO) - Ovis orientalis}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Ovis_aries.IROO.SIFT.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROO.SIFT-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Ovis_aries.IROO.SIFT.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROO.SIFT.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Iran (IROV) - Ovis vignei}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Ovis_aries.IROV.SIFT.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROV.SIFT-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Ovis_aries.IROV.SIFT.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROV.SIFT.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Various (ISGC) - Ovis aries}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Ovis_aries.ISGC.SIFT.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.ISGC.SIFT-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Ovis_aries.ISGC.SIFT.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.ISGC.SIFT.polyDFE_C.pdf}
\end{minipage}
\\

\subsubsection{Morocco (MOOA) - Ovis aries}

\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Ovis_aries.MOOA.SIFT.histogram.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.MOOA.SIFT-sfs.normalize.pdf}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Ovis_aries.MOOA.SIFT.pdf}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.MOOA.SIFT.polyDFE_C.pdf}
\end{minipage}
\\

### 2022-04-13 manuscript/main.tex
Supp. Mat.

@@
 \newcommand{\SphyMean}{\overline{\Sphy}}
+\newcommand{\polyDel}{\proba \left[ {\Spop < -1} \right]}
+\newcommand{\polyNeutral}{\proba \left[ -1 < \Spop < 1 \right]}
+\newcommand{\polyAdv}{\proba \left[ 1 < \Spop  \right]}
 
@@
     Adaptive evolution in proteins can be quantified by comparing sequence variation inside a population to the sequence divergence with a sister species\cite{mcdonald_adaptative_1991}.
-    This method has been largely improved\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009, galtier_adaptive_2016, tataru_inference_2017}, and it's application across many taxa has uncovered that a large proportion of substitutions are positively selected\cite{moutinho_variation_2019}.
-    In practice, the estimated proportion of fixed substitutions that are positively selected varies from 30\% to 70\%.
+    Indeed, strongly adaptive mutations are expected to be observed in substitutions but not in polymorphism because they reach fixation quickly.
+    This method has been largely improved to account for possible bias-inducing factors such as the presence of weak positive selection, background selection and demography fluctuations\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009, galtier_adaptive_2016, tataru_inference_2017}.
+    It's application across many taxa has uncovered that a large proportion of substitutions are positively selected\cite{moutinho_variation_2019}.
+    In practice, the estimated proportion of fixed substitutions that are positively selected varies from 30\% to 70\% (reference).
     Inside a protein, structural properties such as solvent exposure are positively correlated with the proportion of positively selected substitutions\cite{moutinho_impact_2019}.
-    The root causes for this widespread rate of positive selection are however scarcely investigated, often assumed to be the end result of change in the environment or in selection pressure driving individuals to adapt.
-    In this view, positive selection is adaptive and the two terms are confounded, such that the underlying fitness landscape is changing with time, theoretically known as seascape~\cite{mustonen_fitness_2009}.
-    However, even under the assumption that the fitness landscape is immutable, the nearly-neutral theory\cite{ohta_nearly_1992} predicts that positive selection can occur to compensate for deleterious substitutions that have accumulated along lineages.
-    Theoretically, at the nearly-neutral equilibrium, the net flow of deleterious and advantageous mutations reaching fixation are equal~\cite{sella_application_2005}.
+    The root causes for this widespread rate of positive selection are however scarcely investigated, often assumed to be the end result of change in the environment or in selection pressure driving individuals to adapt (reference).
+    In this view, positive selection is adaptive, such that the underlying fitness landscape is changing with time in response to external constraints, theoretically known as seascape\cite{mustonen_fitness_2009}.
+    However, even under the assumption that the fitness landscape is stable, the nearly-neutral theory\cite{ohta_nearly_1992} predicts that positive selection can occur to compensate for deleterious substitutions that have accumulated along lineages.
+    Theoretically, at the nearly-neutral equilibrium, the net flow of deleterious and advantageous mutations reaching fixation are equal\cite{sella_application_2005}.
     In other words, mutations are more likely to be deleterious but are less likely to reach fixation, and the total number of fixation are compensated.
-    In this view of positive selection, advantageous mutations are predictable and evolution is non-adaptive since individuals are not climbing toward higher fitness in the fitness landscape~\cite{lassig_predicting_2017}.
-    Altogether, the goad is this study is to evaluate the extent of non-adaptive positive selection, by combining population-genetics and phylogenetics datasets, and ask a broad range of questions.
+    Under this kind of positive selection, advantageous mutations are predictable and evolution is non-adaptive since there is no genetic innovation in response to external constraint, just an advantage to restore a good functioning of proteins\cite{lassig_predicting_2017}.
+
+    Altogether, the goal of this study is to evaluate the extent of non-adaptive positive selection, by combining population-genetics and phylogenetics datasets, and ask a broad range of questions.
     Are proteins optimal?
@@
     The total mutation rate for each class is computed from the ancestral genome reconstruction (fig.~\ref{fig:homo-afr-results}C).
-    For example, for the category of selection with $1<\Sphy$, the expected total mutation rate is obtained by adding together mutation rates for all possible non-synonymous mutations for which the derived allele ($d$) is toward a fitter amino-acid than the ancestral allele ($a$) with $S > 1$.
-    The total mutation rate and the SFS are combined to estimate the distribution of the selection coefficient given by population-based model~\cite{tataru_inference_2017, tataru_polydfe_2020}.
-    These population based models cannot give a specific estimate of $\Spop$ for each SNP, but by gathering information across many SNPs, they can estimate the proportion of advantageous mutations $p_+=\proba \left( 1 < \Spop \right)$, of nearly-neutral mutations $p_0=\proba \left( -1 < \Spop < 1 \right)$ and of deleterious mutations $p_-=\proba \left( \Spop < -1 \right)$ (fig.~\ref{fig:homo-afr-results}D).
+    For example, for the category of selection with $1<\Sphy$, the expected total mutation rate is obtained by adding together mutation rates for all possible non-synonymous mutations for which the derived allele is toward a fitter amino-acid than the ancestral allele with $\Sphy > 1$.
+    The total mutation rate and the SFS are combined to estimate the distribution of the selection coefficient $\Spop$ given by population-based model\cite{tataru_inference_2017, tataru_polydfe_2020}.
+    These population based models cannot give a specific estimate of $\Spop$ for each SNP, but by gathering information across many SNPs, these models can estimate the proportion of advantageous mutations ($\polyAdv$), of nearly-neutral mutations ($\polyNeutral$) and of deleterious mutations ($\polyDel$) (fig.~\ref{fig:homo-afr-results}D).
 
@@
             Panel D.
-For each class of selection (and for the set of all non-synonymous mutations), information from the SFS and the expected total mutation rate are combined at the population-genetic scale to estimate the proportion of advantageous mutations $p_+=\proba \left( 1 < \Spop \right)$, of nearly-neutral mutations $p_0=\proba \left( -1 < \Spop < 1 \right)$ and of deleterious mutations $p_-=\proba \left( \Spop < -1 \right)$.
+For each class of selection (and for the set of all non-synonymous mutations), information from the SFS and the expected total mutation rate are combined at the population-genetic scale to estimate the proportion of advantageous mutations $\polyAdv$, of nearly-neutral mutations $\polyNeutral$ and of deleterious mutations $\polyDel$.
         }
@@
             Reproducibility of results shown in figure~\ref{fig:homo-afr-results} in 29 populations across 7 genera.
-            From a site-frequency spectrum and total mutation rates are combined at the population-genetic scale to estimate the proportion of advantageous mutations $p_+=\proba \left( 1 < \Spop \right)$ in top panel, of nearly-neutral mutations $p_0=\proba \left( -1 < \Spop < 1 \right)$ in middle panel and of deleterious mutations $p_-=\proba \left( \Spop < -1 \right)$ in bottom panel.
+            From a site-frequency spectrum and total mutation rates are combined at the population-genetic scale to estimate the proportion of advantageous mutations $\polyAdv$ in top panel, of nearly-neutral mutations $\polyNeutral$ in middle panel and of deleterious mutations $\polyDel$ in bottom panel.
         }
@@
     However, the mean selection coefficient estimated at the phylogenetic scale is usually drastically negative because of the heavy tail of the negative part of the estimated DFE.
-    Hence we focused on the relationship between $\SpopMean$ and $\SphyMean$ for a subset of SNPs, for which $\Sphy$ is close to $0$.
+    Hence we focused on the relationship between $\SpopMean$ and $\SphyMean$ for a subset of SNPs, for which $\SphyMean$ is close to $0$.
     Sliding window of groups of $5.000$ SNPs are taken with a mean $\SphyMean$ between $-0.5$ and $0.5$ (fig.~\ref{fig:selcoeff-pop-phylo}A).
     $\SpopMean$ is estimated for each group, with some groups that might have part of same SNPs that overlap.
-    The relationship between $\Spop$ and $\SphyMean$ is best described as a second order polynomial, and the slope of this polynomial at $\SphyMean=0$ gives the ratio $\Spop/\Sphy$ for each population.
-    We observ that $\Spop/\Sphy$, representing the efficiency of selection at the short versus long term is positively correlated with synonymous diversity, a proxy of effective population siz.
+    The relationship between $\SpopMean$ and $\SphyMean$ is best described as a second order polynomial, and the slope of this polynomial at $\SphyMean=0$ gives the ratio $\SpopMean/\SphyMean$ for each population.
+    We observ that $\SpopMean/\SphyMean$, representing the efficiency of selection at the short versus long term is positively correlated with synonymous diversity, a proxy of effective population siz.
     Altogether, population with large effective population size are under more efficient selection.
@@
         \caption{
-            Panel A. Mean selection coefficient at the population scale $\SpopMean$ as a function of phylogenetic $\SphyMean$.
-            Observed SNPs are sorted and groups of $5.000$ SNPs are taken as a sliding windows with increasing mean $\SphyMean$.
-            For each group, $\SpopMean$ (y-axis) is estimated based on SFS and the total mutation rate (between both extreme of $\SphyMean$ in the group) and compared to the mean $\Sphy$ (y-axis).
+            Panel A. For each population, proportion of advantageous ($\polyAdv$), nearly-neutral ($\polyNeutral$) and of deleterious ($\polyDel$) mutations estimated at the population-genetic scale.
+            Estimation is performed with SNPs predicted to be weakly-advantageous at the phylogenetic scale $0<\Sphy<1<$.
+            Panel B. Mean selection coefficient at the population scale $\SpopMean$ as a function of phylogenetic $\SphyMean$.
+            Observed SNPs are sorted and groups of $5.000$ SNPs are taken as a sliding windows with increasing mean $-0.5 \leq \SphyMean \leq 0.5$.
+            For each group along the sliding window, $\SpopMean$ (y-axis) is estimated based on SFS and the total mutation rate, and compared to the mean $\SphyMean$ (x-axis).
             A second order polynomial is fitted for each population, and the slope of this polynomial at $\SphyMean=0$ gives the ratio $\SpopMean/\SphyMean$ given in legend.
-            Panel B. Ratio $\SpopMean/\SphyMean$ as a function of the synonymous diversity for each population.
-            Populations with higher diversity are showing higher ratio of ratio $\SpopMean/\Sphy$.
+            Panel C. Ratio $\SpopMean/\SphyMean$ as a function of the synonymous diversity for each population.
+            Populations with higher diversity are showing higher ratio of ratio $\SpopMean/\SphyMean$.
         }
         \label{fig:selcoeff-pop-phylo}
-    \end{figure*}d
+    \end{figure*}
 
@@
     In this configuration, a single $\Spop$ for all sampled mutations is biologically not realistic.
-    Accordingly, a distribution of fitness effects of mutations (DFE) is assumed, usually modelled as a continuous distribution~\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009}.
+    Accordingly, a distribution of fitness effects of mutations (DFE) is assumed, usually modelled as a continuous distribution\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009}.
     In this study, we used the software polyDFE\cite{tataru_inference_2017, tataru_polydfe_2020}, for which the DFE ($\phi$) is given by a mixture of a $\Gamma$ and Exponential distributions, parameterized by $\Spop_d$ , $b$, $p_b$
@@
             \left( 1 - p_b \right) f_{\Gamma}(-\Spop; -\Spop_d, b) & \text{ if $\Spop \leq 0$,} \\
-            p_b f_{e}(\Spop; \Spop_b) & \text{ if $\Spop \leq 0$,} \\
+            p_b f_{e}(\Spop; \Spop_b) & \text{ if $\Spop > 0$,} \\
         \end{dcases}
     \end{equation*}
-    where $\Spop_d$ is the mean of the DFE for $\Spop \leq 0$
-    $b$ is the shape of the $\Gamma$ distribution,
-    $p_b$ is the probability that $\Spop > 0$,
-    $\Spop_b$ is the mean of the DFE for $\Spop > 0$,
+    where $\Spop_d < 0 $ is the mean of the DFE for $\Spop \leq 0$,
+    $b > 0$ is the shape of the $\Gamma$ distribution,
+    $0 \leq p_b \leq 1$ is the probability that $\Spop > 0$,
+    $\Spop_b > 0$ is the mean of the DFE for $\Spop > 0$,
     and $f_{\Gamma}(x; m, b)$ is the density of the $\Gamma$ distribution with mean m and shape b, while $f_{e}(x; m)$ is the density of the Exponential distribution with mean $m$.
-    Once the DFE is fitted to the data, the proportion of advantageous ($p_+$), nearly-neutral ($p_0$) and deleterious mutations ($p_-$) are given as:
+    Once the DFE is fitted to the data, the proportion of advantageous ($\polyAdv$), nearly-neutral ($\polyNeutral$) and deleterious mutations ($\polyDel$) are given as:
     \begin{align*}
-        p_+ &= \proba_{\phi} \left( 1 < \Spop \right) = p_b \int_{1}^{+\infty} f_{e}(\Spop; \Spop_b)  \\
-        p_0 &= \proba_{\phi} \left( -1 < \Spop < 1 \right) = p_b \int_{0}^{1} f_{e}(\Spop; \Spop_b) + \left( 1 - p_b \right) \int_{0}^{1} f_{\Gamma}(\Spop; \Spop_d, b) \\
-        p_- &= \proba_{\phi} \left( \Spop < -1 \right) = \left( 1 - p_b \right) \int_{1}^{+\infty} f_{\Gamma}(\Spop; \Spop_d, b)
+        \polyAdv &= p_b \int_{1}^{+\infty} f_{e}(\Spop; \Spop_b) \der \Spop  \\
+        \polyNeutral &= p_b \int_{0}^{1} f_{e}(\Spop; \Spop_b) \der \Spop + \left( 1 - p_b \right) \int_{0}^{1} f_{\Gamma}(\Spop; -\Spop_d, b) \der \Spop \\
+        \polyDel &= \left( 1 - p_b \right) \int_{1}^{+\infty} f_{\Gamma}(\Spop; -\Spop_d, b) \der \Spop
     \end{align*}
@@
     \begin{align*}
-        \SpopMean & = \int_{-\infty}^{+\infty} \Spop \phi \left( \Spop; \Spop_d , b, p_b, \Spop_b \right) \\
-                         & =  p_b \Spop_b - \left( 1 - p_b \right) \Spop_d
+        \SpopMean & = \int_{-\infty}^{+\infty} \Spop \phi \left( \Spop; \Spop_d , b, p_b, \Spop_b \right) \der \Spop \\
+        & =  p_b \Spop_b + \left( 1 - p_b \right) \Spop_d
     \end{align*}

### 2022-04-13 manuscript/supp-mat.tex
Supp. Mat.

@@
     \tableofcontents
-    \include{include-figures}
+    \clearpage
+
+    \section{Site-specific mutation-selection codon models}
+
+    \subsection{Summary table}
+    \begin{center}
+        \begin{longtable}{|l|l|r|r|r|r|}
+            \toprule
+            Population                     & Species             & Tajima $\theta_{\pi}$ & $\mathbb{P}_{obs}[1<S]$ & $\mathbb{P} [ 1<\beta ]$ & $\mathbb{P} [ 1<\beta  | 1<S]$ \\
+            \midrule
+            \endhead
+            \midrule
+            \multicolumn{6}{r}{{Continued on next page}} \\
+            \midrule
+            \endfoot
+
+            \bottomrule
+            \endlastfoot
+            Diverse (Equus)                & Equus caballus      & $ 0.003$              & $ 0.161$                & $ 0.073$                 & $ 0.779$                     \\
+            Diverse (Canis)                & Canis familiaris    & $ 0.004$              & $ 0.069$                & $ 0.041$                 & $ 0.262$                     \\
+            Iran (IRBT)                    & Bos taurus          & $ 0.009$              & $ 0.123$                & $ 0.054$                 & $ 0.300$                     \\
+            Uganda (UGBT)                  & Bos taurus          & $ 0.010$              & $ 0.139$                & $ 0.060$                 & $ 0.779$                     \\
+            Australia (AUCH)               & Capra hircus        & $ 0.004$              & $ 0.105$                & $ 0.061$                 & $ 0.119$                     \\
+            France (FRCH)                  & Capra hircus        & $ 0.004$              & $ 0.105$                & $ 0.060$                 & $ 0.059$                     \\
+            Iran (IRCA)                    & Capra aegagrus      & $ 0.004$              & $ 0.105$                & $ 0.062$                 & $ 0.053$                     \\
+            Iran (IRCH)                    & Capra hircus        & $ 0.005$              & $ 0.093$                & $ 0.058$                 & $ 0.094$                     \\
+            Italy (ITCH)                   & Capra hircus        & $ 0.004$              & $ 0.103$                & $ 0.059$                 & $ 0.053$                     \\
+            Morocco (MOCH)                 & Capra hircus        & $ 0.005$              & $ 0.077$                & $ 0.057$                 & $ 0.045$                     \\
+            Iran (IROA)                    & Ovis aries          & $ 0.009$              & $ 0.107$                & $ 0.048$                 & $ 0.144$                     \\
+            Iran (IROO)                    & Ovis orientalis     & $ 0.010$              & $ 0.110$                & $ 0.050$                 & $ 0.177$                     \\
+            Iran (IROV)                    & Ovis vignei         & $ 0.009$              & $ 0.127$                & $ 0.049$                 & $ 0.252$                     \\
+            Various (ISGC)                 & Ovis aries          & $ 0.009$              & $ 0.108$                & $ 0.049$                 & $ 0.194$                     \\
+            Morocco (MOOA)                 & Ovis aries          & $ 0.009$              & $ 0.086$                & $ 0.045$                 & $ 0.144$                     \\
+            Barbados                       & Chlorocebus sabaeus & $ 0.004$              & $ 0.104$                & $ 0.072$                 & $ 0.484$                     \\
+            Central African Republic (CAR) & Chlorocebus sabaeus & $ 0.007$              & $ 0.105$                & $ 0.066$                 & $ 0.312$                     \\
+            Ethiopia                       & Chlorocebus sabaeus & $ 0.006$              & $ 0.097$                & $ 0.068$                 & $ 0.245$                     \\
+            Gambia                         & Chlorocebus sabaeus & $ 0.006$              & $ 0.101$                & $ 0.064$                 & $ 0.411$                     \\
+            Kenya                          & Chlorocebus sabaeus & $ 0.006$              & $ 0.104$                & $ 0.066$                 & $ 0.323$                     \\
+            Nevis                          & Chlorocebus sabaeus & $ 0.004$              & $ 0.105$                & $ 0.068$                 & $ 0.445$                     \\
+            South Africa (SA)              & Chlorocebus sabaeus & $ 0.007$              & $ 0.095$                & $ 0.065$                 & $ 0.233$                     \\
+            Saint Kitts (SK)               & Chlorocebus sabaeus & $ 0.005$              & $ 0.101$                & $ 0.071$                 & $ 0.442$                     \\
+            Zambia                         & Chlorocebus sabaeus & $ 0.007$              & $ 0.101$                & $ 0.070$                 & $ 0.290$                     \\
+            African (AFR)                  & Homo sapiens        & $ 0.003$              & $ 0.052$                & $ 0.092$                 & $ 0.779$                     \\
+            Ad Mixed American (AMR)        & Homo sapiens        & $ 0.002$              & $ 0.055$                & $ 0.087$                 & $ 0.779$                     \\
+            East Asian (EAS)               & Homo sapiens        & $ 0.002$              & $ 0.051$                & $ 0.084$                 & $ 0.779$                     \\
+            European (EUR)                 & Homo sapiens        & $ 0.002$              & $ 0.053$                & $ 0.087$                 & $ 0.779$                     \\
+            South Asian (SAS)              & Homo sapiens        & $ 0.002$              & $ 0.051$                & $ 0.084$                 & $ 0.779$                     \\
+        \end{longtable}
+    \end{center}
+
+    \subsection{Correlation with diversity}
+
+    \subsubsection{Proportion of positive selection}
+    \begin{minipage}{0.32\linewidth}
+        \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/regression/results.watterson.all_P-Ssup0.scatter.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/regression/results.watterson.pos_P-Ssup0.scatter.pdf}
+    \end{minipage}
+
+    \subsubsection{Proportion of negative selection}
+    \begin{minipage}{0.32\linewidth}
+        \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/regression/results.watterson.all_P-Sinf0.scatter.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/regression/results.watterson.neg_P-Sinf0.scatter.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/regression/results.watterson.neg-strong_P-Sinf0.scatter.pdf}
+    \end{minipage}
+
+    \subsubsection{Proportion of weak selection}
+    \begin{minipage}{0.32\linewidth}
+        \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/regression/results.watterson.all_P-Seq0.scatter.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/regression/results.watterson.neg-weak_P-Seq0.scatter.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/regression/results.watterson.pos-weak_P-Seq0.scatter.pdf}
+    \end{minipage}
+
+    \input{include-MutSel-non-adaptive}
+
+    \section{SIFT scores}
+    \input{include-SIFT-non-adaptive}
+
+    \section{Site-specific codon models.}
+    \input{include-Omega-adaptive}
 \end{document}

### 2022-04-13 scripts/libraries.py

@@ -299,16 +299,32 @@ def extend_pop(p, sample):
         return f"{sample[p]} ({fp})"
 
 
-def sort_df(df, sample_list_path):
-    df = df.iloc[df.apply(lambda r: sp_sorted(format_pop(r["pop"]), r["species"]), axis=1).argsort()]
+def set_species(df):
     df["species"] = df.apply(lambda r: r["species"].replace("_", " "), axis=1)
     df["species"] = df.apply(lambda r: "Ovis orientalis" if r["pop"] == "IROO" else r["species"], axis=1)
     df["species"] = df.apply(lambda r: "Ovis vignei" if r["pop"] == "IROV" else r["species"], axis=1)
     df["species"] = df.apply(lambda r: "Capra aegagrus" if r["pop"] == "IRCA" else r["species"], axis=1)
+    return df
 
-    sample_iterrows = list(pd.read_csv(sample_list_path, sep='\t').iterrows())
+
+def sample_list_dico(sample_list_path):
+    df = pd.read_csv(sample_list_path, sep='\t')
+    df["pop"] = df.apply(lambda r: format_pop(r["SampleName"].replace("_", " ")), axis=1)
+    df["species"] = df.apply(lambda r: r["Species"].replace("_", " "), axis=1)
+    df = set_species(df)
+    dico_sample = {r["pop"]: r["Location"] for _, r in df.iterrows()}
+    df["ext_pop"] = df.apply(lambda r: extend_pop(r["pop"], dico_sample), axis=1)
+    dico_sample = {
+        r["pop"]: r["ext_pop"] + (f' - {r["species"]}' if r["species"].split(" ")[0] in ["Capra", "Ovis"] else "") for
+        _, r in df.iterrows()}
+    return dico_sample
+
+
+def sort_df(df, sample_list_path):
+    df = df.iloc[df.apply(lambda r: sp_sorted(format_pop(r["pop"]), r["species"]), axis=1).argsort()]
+    df = set_species(df)
+    sample_iterrows = pd.read_csv(sample_list_path, sep='\t').iterrows()
     dico_sample = {format_pop(r["SampleName"].replace("_", " ")): r["Location"] for _, r in sample_iterrows}
-
     df["pop"] = df.apply(lambda r: extend_pop(r["pop"], dico_sample), axis=1)
     return df
 

### 2022-04-13 scripts/plot_regression.py

@@ -22,8 +22,9 @@ def open_tsv(filepath):
         df_dfe = ddf[(ddf["method"] == "MutSel") & (ddf["category"] != "syn")]
         m_list = []
         for cat_poly in list(polydfe_cat_dico) + [f"P-{cat}" for cat in cat_snps.non_syn_list]:
-            matrix = df_dfe.pivot(index="pop", columns="category", values=cat_poly).add_suffix(f'_{cat_poly}')
-            m_list.append(matrix)
+            if cat_poly in df_dfe:
+                matrix = df_dfe.pivot(index="pop", columns="category", values=cat_poly).add_suffix(f'_{cat_poly}')
+                m_list.append(matrix)
         df_pivot = pd.concat(m_list, axis=1)
         ddf = pd.merge(df_pivot, df_theta, on=["pop"])
     elif "bounds" in os.path.basename(filepath):
@@ -49,16 +50,26 @@ def generate_xy_plot():
     y_dico.update({f'all_{cat_poly}': v for cat_poly, v in polydfe_cat_dico.items()})
 
     for cat in cat_snps.non_syn_list + ['weak', 'all']:
-        label = cat_snps.label(cat).replace("$", "") if cat != "weak" else "-1 < S < 1"
-        y_dico.update({f'{cat}_{cat_poly}': v.replace(']', f'| {label}]') for cat_poly, v in polydfe_cat_dico.items()})
-        y_dico.update(
-            {f'{cat}_P-{cat_poly}': cat_snps.label(cat_poly).replace('S', '\\beta').replace(']', f'| {label}]') for
-             cat_poly in cat_snps.all() if cat_poly != "syn"})
+        s = ""
+        if cat == "weak":
+            s = " -1 < S < 1"
+        elif cat != "all":
+            s = cat_snps.label(cat).replace("$", "")
 
-    y_dico.update({f'pos-weak_P-pos-weak': "$\\mathbb{P} [ 0<\\beta<1 | 0<S<1]$"})
-    y_dico.update({'pos_snps': "$\\mathbb{P}_{obs} [ 1 < S ]$"})
-    y_dico.update({'pos': "$\\mathbb{P}_{exp} [ 1 < S ]$"})
-    dico_label |= y_dico
+        dico_label[cat] = "$\\mathbb{P}" + f"[{s}]$"
+        dico_label[f"{cat}_snps"] = "$\\mathbb{P}_{obs}" + f"[{s}]$"
[…]

### 2022-04-13 scripts/tex_sfs.py

@@ -2,7 +2,7 @@ import argparse
 from glob import glob
 from collections import defaultdict
 import os
-from libraries import format_pop
+from libraries import format_pop, sample_list_dico
 
 dict_method = {"MutSel": "Site-specific Mutation-Selection codon models.",
                "Omega": "Site-specific codon models.",
@@ -18,37 +18,35 @@ def minipage(size, file):
 
 def main(args):
     os.makedirs(os.path.dirname(args.results), exist_ok=True)
+    sample_dico = sample_list_dico(args.sample_list)
     heatmap_dict = defaultdict(list)
     for result in sorted(glob(f"{os.path.dirname(args.results)}/*.pdf")):
         _, method_lr, theta, plot, ext = os.path.basename(result).replace("_", " ").split(".")
         method = method_lr.split("-")[0]
         heatmap_dict[method].append(result)
 
+    nested_dict = defaultdict(lambda: defaultdict(dict))
+    for sfs in sorted(args.sfs):
+        sp, pop, method_lr, ext = os.path.basename(sfs).replace("_", " ").split(".")
+        method = method_lr.split("-")[0]
+        nested_dict[method][sp][pop] = sfs
+
     o = open(args.tex_include, 'w')
-    o.write("\\section{Summary statistics across all populations} \n \n")
-    for method, list_heatmap in heatmap_dict.items():
-        o.write("\\subsection{" + dict_method[method].capitalize() + '} \n')
+    for method, nested_dict_1 in nested_dict.items():
+        o.write("\\section{" + dict_method[method].capitalize() + '} \n')
+
+        list_heatmap = heatmap_dict[method]
+        o.write("\\subsection{All populations} \n")
         o.write("\\begin{center}\n")
         for plot in list_heatmap:
             o.write("\\includegraphics[width=0.95\\linewidth, page=1]{" + plot + "} \\\\\n")
         o.write("\\end{center}\n")
 
-    nested_dict = defaultdict(lambda: defaultdict(dict))
-    for sfs in sorted(args.sfs):
-        sp, pop, method_lr, ext = os.path.basename(sfs).replace("_", " ").split(".")
-        method = method_lr.split("-")[0]
-        nested_dict[sp][pop][method] = sfs
-
-    for sp, nested_dict_1 in nested_dict.items():
-        o.write("\\section{" + sp + "} \n \n")
-        for pop, nested_dict_2 in nested_dict_1.items():
-            if " " in pop:
[…]

### 2022-04-20 manuscript/include-MutSel-non-adaptive.tex
Updated manuscript with JJ intro and TL experiment description.

@@
 \begin{center}
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/results/Theta.MutSel.all.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/results/Theta.MutSel.neg-strong.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/results/Theta.MutSel.neg.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/results/Theta.MutSel.neg-weak.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/results/Theta.MutSel.pos-weak.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/results/Theta.MutSel.pos.stacked.pdf}
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/results/Theta.MutSel.all.stacked.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/results/Theta.MutSel.neg-strong.stacked.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/results/Theta.MutSel.neg.stacked.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/results/Theta.MutSel.neg-weak.stacked.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/results/Theta.MutSel.pos-weak.stacked.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/results/Theta.MutSel.pos.stacked.pdf}
 
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Bos_taurus.IRBT.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Bos_taurus.IRBT.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Bos_taurus.IRBT.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Bos_taurus.IRBT.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Bos_taurus.UGBT.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Bos_taurus.UGBT.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Bos_taurus.UGBT.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Bos_taurus.UGBT.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Canis_familiaris.dogs.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Canis_familiaris.dogs.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Canis_familiaris.dogs.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Canis_familiaris.dogs.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.AUCH.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.AUCH.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.AUCH.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.AUCH.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.FRCH.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.FRCH.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.FRCH.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.FRCH.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.IRCA.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.IRCA.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.IRCA.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.IRCA.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.IRCH.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.IRCH.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.IRCH.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.IRCH.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.ITCH.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.ITCH.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.ITCH.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.ITCH.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.MOCH.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.MOCH.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.MOCH.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.MOCH.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Barbados.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Barbados.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Barbados.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Barbados.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Gambia.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Gambia.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Gambia.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Gambia.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Kenya.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Kenya.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Kenya.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Kenya.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Nevis.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Nevis.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Nevis.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Nevis.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Saint_Kitts.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Saint_Kitts.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Saint_Kitts.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Saint_Kitts.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.South_Africa.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.South_Africa.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.South_Africa.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.South_Africa.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Zambia.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Zambia.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Zambia.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Zambia.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Equus_caballus.up.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Equus_caballus.up.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Equus_caballus.up.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Equus_caballus.up.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.AFR.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.AFR.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.AFR.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.AFR.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.AMR.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.AMR.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.AMR.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.AMR.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.EAS.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.EAS.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.EAS.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.EAS.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.EUR.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.EUR.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.EUR.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.EUR.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.SAS.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.SAS.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.SAS.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.SAS.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROA.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROA.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROA.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROA.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROO.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROO.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROO.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROO.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROV.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROV.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROV.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROV.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.ISGC.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.ISGC.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.ISGC.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.ISGC.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.MOOA.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.MOOA.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.MOOA.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.MOOA.MutSel.polyDFE_C.pdf}
 \end{minipage}

### 2022-04-20 manuscript/include-Omega-adaptive.tex
Updated manuscript with JJ intro and TL experiment description.

@@
 \begin{center}
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC/results/Theta.Omega.P-Sinf0.heatmap.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC/results/Theta.Omega.P-Seq0.heatmap.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC/results/Theta.Omega.P-Ssup0.heatmap.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC/results/Theta.Omega.all.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC/results/Theta.Omega.neg-strong.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC/results/Theta.Omega.neg.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC/results/Theta.Omega.neg-weak.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC/results/Theta.Omega.pos-weak.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC/results/Theta.Omega.pos.stacked.pdf}
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC/results/Theta.Omega.P-Sinf0.heatmap.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC/results/Theta.Omega.P-Seq0.heatmap.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC/results/Theta.Omega.P-Ssup0.heatmap.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC/results/Theta.Omega.all.stacked.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC/results/Theta.Omega.neg-strong.stacked.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC/results/Theta.Omega.neg.stacked.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC/results/Theta.Omega.neg-weak.stacked.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC/results/Theta.Omega.pos-weak.stacked.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC/results/Theta.Omega.pos.stacked.pdf}
 \end{center}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Bos_taurus.IRBT.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Bos_taurus.IRBT.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Bos_taurus.IRBT.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Bos_taurus.IRBT.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Bos_taurus.UGBT.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Bos_taurus.UGBT.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Bos_taurus.UGBT.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Bos_taurus.UGBT.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Canis_familiaris.dogs.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Canis_familiaris.dogs.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Canis_familiaris.dogs.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Canis_familiaris.dogs.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Capra_hircus.AUCH.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Capra_hircus.AUCH.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Capra_hircus.AUCH.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Capra_hircus.AUCH.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Capra_hircus.FRCH.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Capra_hircus.FRCH.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Capra_hircus.FRCH.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Capra_hircus.FRCH.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Capra_hircus.IRCA.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Capra_hircus.IRCA.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Capra_hircus.IRCA.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Capra_hircus.IRCA.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Capra_hircus.IRCH.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Capra_hircus.IRCH.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Capra_hircus.IRCH.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Capra_hircus.IRCH.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Capra_hircus.ITCH.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Capra_hircus.ITCH.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Capra_hircus.ITCH.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Capra_hircus.ITCH.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Capra_hircus.MOCH.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Capra_hircus.MOCH.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Capra_hircus.MOCH.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Capra_hircus.MOCH.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Chlorocebus_sabaeus.Barbados.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Chlorocebus_sabaeus.Barbados.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Chlorocebus_sabaeus.Barbados.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Chlorocebus_sabaeus.Barbados.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Chlorocebus_sabaeus.Central_African_Republic.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Chlorocebus_sabaeus.Central_African_Republic.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Chlorocebus_sabaeus.Central_African_Republic.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Chlorocebus_sabaeus.Central_African_Republic.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Chlorocebus_sabaeus.Ethiopia.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Chlorocebus_sabaeus.Ethiopia.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Chlorocebus_sabaeus.Ethiopia.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Chlorocebus_sabaeus.Ethiopia.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Chlorocebus_sabaeus.Gambia.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Chlorocebus_sabaeus.Gambia.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Chlorocebus_sabaeus.Gambia.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Chlorocebus_sabaeus.Gambia.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Chlorocebus_sabaeus.Kenya.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Chlorocebus_sabaeus.Kenya.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Chlorocebus_sabaeus.Kenya.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Chlorocebus_sabaeus.Kenya.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Chlorocebus_sabaeus.Nevis.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Chlorocebus_sabaeus.Nevis.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Chlorocebus_sabaeus.Nevis.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Chlorocebus_sabaeus.Nevis.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Chlorocebus_sabaeus.Saint_Kitts.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Chlorocebus_sabaeus.Saint_Kitts.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Chlorocebus_sabaeus.Saint_Kitts.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Chlorocebus_sabaeus.Saint_Kitts.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Chlorocebus_sabaeus.South_Africa.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Chlorocebus_sabaeus.South_Africa.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Chlorocebus_sabaeus.South_Africa.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Chlorocebus_sabaeus.South_Africa.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Chlorocebus_sabaeus.Zambia.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Chlorocebus_sabaeus.Zambia.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Chlorocebus_sabaeus.Zambia.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Chlorocebus_sabaeus.Zambia.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Equus_caballus.up.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Equus_caballus.up.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Equus_caballus.up.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Equus_caballus.up.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Homo_sapiens.AFR.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Homo_sapiens.AFR.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Homo_sapiens.AFR.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Homo_sapiens.AFR.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Homo_sapiens.AMR.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Homo_sapiens.AMR.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Homo_sapiens.AMR.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Homo_sapiens.AMR.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Homo_sapiens.EAS.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Homo_sapiens.EAS.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Homo_sapiens.EAS.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Homo_sapiens.EAS.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Homo_sapiens.EUR.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Homo_sapiens.EUR.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Homo_sapiens.EUR.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Homo_sapiens.EUR.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Homo_sapiens.SAS.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Homo_sapiens.SAS.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Homo_sapiens.SAS.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Homo_sapiens.SAS.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Ovis_aries.IROA.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Ovis_aries.IROA.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Ovis_aries.IROA.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Ovis_aries.IROA.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Ovis_aries.IROO.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Ovis_aries.IROO.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Ovis_aries.IROO.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Ovis_aries.IROO.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Ovis_aries.IROV.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Ovis_aries.IROV.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Ovis_aries.IROV.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Ovis_aries.IROV.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Ovis_aries.ISGC.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Ovis_aries.ISGC.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Ovis_aries.ISGC.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Ovis_aries.ISGC.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Ovis_aries.MOOA.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Ovis_aries.MOOA.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC/analysis/Ovis_aries.MOOA.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Ovis_aries.MOOA.Omega.polyDFE_C.pdf}
 \end{minipage}

### 2022-04-20 manuscript/include-SIFT-non-adaptive.tex
Updated manuscript with JJ intro and TL experiment description.

@@
 \begin{center}
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/results/Theta.SIFT.P-Sinf0.heatmap.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/results/Theta.SIFT.P-Seq0.heatmap.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/results/Theta.SIFT.P-Ssup0.heatmap.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/results/Theta.SIFT.all.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/results/Theta.SIFT.neg-strong.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/results/Theta.SIFT.neg.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/results/Theta.SIFT.neg-weak.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/results/Theta.SIFT.pos-weak.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/results/Theta.SIFT.pos.stacked.pdf}
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/results/Theta.SIFT.P-Sinf0.heatmap.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/results/Theta.SIFT.P-Seq0.heatmap.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/results/Theta.SIFT.P-Ssup0.heatmap.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/results/Theta.SIFT.all.stacked.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/results/Theta.SIFT.neg-strong.stacked.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/results/Theta.SIFT.neg.stacked.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/results/Theta.SIFT.neg-weak.stacked.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/results/Theta.SIFT.pos-weak.stacked.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/results/Theta.SIFT.pos.stacked.pdf}
 \end{center}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Bos_taurus.IRBT.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Bos_taurus.IRBT.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Bos_taurus.IRBT.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Bos_taurus.IRBT.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Bos_taurus.UGBT.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Bos_taurus.UGBT.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Bos_taurus.UGBT.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Bos_taurus.UGBT.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Canis_familiaris.dogs.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Canis_familiaris.dogs.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Canis_familiaris.dogs.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Canis_familiaris.dogs.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.AUCH.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.AUCH.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.AUCH.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.AUCH.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.FRCH.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.FRCH.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.FRCH.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.FRCH.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.IRCA.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.IRCA.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.IRCA.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.IRCA.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.IRCH.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.IRCH.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.IRCH.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.IRCH.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.ITCH.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.ITCH.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.ITCH.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.ITCH.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.MOCH.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.MOCH.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Capra_hircus.MOCH.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.MOCH.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Barbados.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Barbados.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Barbados.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Barbados.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Central_African_Republic.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Central_African_Republic.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Central_African_Republic.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Central_African_Republic.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Ethiopia.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Ethiopia.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Ethiopia.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Ethiopia.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Gambia.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Gambia.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Gambia.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Gambia.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Kenya.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Kenya.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Kenya.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Kenya.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Nevis.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Nevis.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Nevis.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Nevis.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Saint_Kitts.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Saint_Kitts.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Saint_Kitts.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Saint_Kitts.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.South_Africa.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.South_Africa.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.South_Africa.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.South_Africa.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Zambia.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Zambia.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Zambia.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Zambia.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Equus_caballus.up.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Equus_caballus.up.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Equus_caballus.up.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Equus_caballus.up.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.AFR.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.AFR.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.AFR.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.AFR.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.AMR.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.AMR.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.AMR.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.AMR.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.EAS.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.EAS.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.EAS.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.EAS.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.EUR.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.EUR.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.EUR.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.EUR.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.SAS.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.SAS.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.SAS.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.SAS.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROA.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROA.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROA.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROA.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROO.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROO.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROO.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROO.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROV.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROV.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROV.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROV.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.ISGC.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.ISGC.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.ISGC.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.ISGC.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.MOOA.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.MOOA.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/analysis/Ovis_aries.MOOA.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.MOOA.SIFT.polyDFE_C.pdf}
 \end{minipage}

### 2022-04-20 manuscript/main.tex
Updated manuscript with JJ intro and TL experiment description.

@@
 
+    We usually say that a mutation is undergoing positive selection when it brings a fitness advantage to its bearer, and thus facilitate its own transmission to the next generation.
+    However, the causes of this advantage can be diverse.
+    We can distinguish two main advantages.
+    The first correspond to what we usually call adaptive evolution.
+    he advantage in fitness of a new mutation allows its bearer to become better adapted to a changing environment.
+    The second we call maintenance positive selection.
+    The mutation restores the ancestral state which corresponded to an optimal functioning of the individual in a constant environment, but has been lost due to the fixation of a deleterious mutation by drift.
+    These two different kinds of selection result in a positive transmission bias of the advantageous allele, but their consequences are conceptually different.
+    While adaptive evolution promotes phenotype diversification, maintenance positive selection promotes phenotype stability and preserves well established biological systems.
+    It is thus of importance to be able to distinguish those two kinds of positive selection in order to understand the diversification of species.
+
     Adaptive evolution in proteins can be quantified by comparing sequence variation inside a population to the sequence divergence with a sister species\cite{mcdonald_adaptative_1991}.
@@
     It's application across many taxa has uncovered that a large proportion of substitutions are positively selected\cite{moutinho_variation_2019}.
-    In practice, the estimated proportion of fixed substitutions that are positively selected varies from 30\% to 70\% (reference).
-    Inside a protein, structural properties such as solvent exposure are positively correlated with the proportion of positively selected substitutions\cite{moutinho_impact_2019}.
-    The root causes for this widespread rate of positive selection are however scarcely investigated, often assumed to be the end result of change in the environment or in selection pressure driving individuals to adapt (reference).
-    In this view, positive selection is adaptive, such that the underlying fitness landscape is changing with time in response to external constraints, theoretically known as seascape\cite{mustonen_fitness_2009}.
-    However, even under the assumption that the fitness landscape is stable, the nearly-neutral theory\cite{ohta_nearly_1992} predicts that positive selection can occur to compensate for deleterious substitutions that have accumulated along lineages.
-    Theoretically, at the nearly-neutral equilibrium, the net flow of deleterious and advantageous mutations reaching fixation are equal\cite{sella_application_2005}.
-    In other words, mutations are more likely to be deleterious but are less likely to reach fixation, and the total number of fixation are compensated.
-    Under this kind of positive selection, advantageous mutations are predictable and evolution is non-adaptive since there is no genetic innovation in response to external constraint, just an advantage to restore a good functioning of proteins\cite{lassig_predicting_2017}.
+    The root causes for this widespread rate of positive selection are however scarcely investigated, often assumed to be the end result of adaptive evolution.
+    However, as mentioned above, not all these mutations contribute to genetic innovation and diversification.
+    Adaptive evolution can only be well estimated if maintenance positive selection is taken into account.
+    While adaptive evolution is unpredictable because it brings an advantage concerning an unpredictable change in the environment of organisms, the second is predictable because optimal states should be more or less the same for closely related organisms which share most of their environment and physiology.
+    A way to measure maintenance positive selection is to compute selection coefficients assuming a constant and stable fitness landscape estimated from the alignment of protein-coding genes.
+    For each site of the proteic alignment, the fitness of each amino-acid can be estimated from their frequency in the alignment.
+    One of the most used method to make these predictions is SIFT (Sort Intolerant From Tolerant) which reliably detects deleterious mutations in many taxa.
+    However, this method has two major shortcomings.
+    First, this method uses amino-acid frequency as a proxy for amino-acid fitness, even if we know that a lot of mechanisms can influence amino-acid frequency other than fitness (mutation biases, GC-biased gene conversion, mutational paths).
+    Second, each mutations is attributed a score to describe if it should be under purifying selection on one hand or be neutral or advantageous on the other hand.
+    But this score makes little sense to actual measure of fitness, and is not interpretable in terms of population genetics.
+    So called mutation-selection codon models provide a nearly-neutral framework of evolution by estimating the fitness landscape over amino-acid sequences for each site of the sequence while taking into account non adaptive-processes impacting codon frequency\cite{ halpern_evolutionary_1998, rodrigue_mechanistic_2010, tamuri_estimating_2012}.
+    Only nearly-neutral mutations between high fitness amino acids will tend to be permitted by the model, allowing for the explicit calculation of the scaled selection coefficient of non-synonymous mutations between codons.
+    These models have been used as a null-model to predict the overall rate of evolution of proteins\cite{spielman_relationship_2015, dosreis_how_2015}.
+    A departure from this model indicates that proteins are evolving under a changing fitness landscape\cite{rodrigue_detecting_2017, tamuri_mutationselection_2021} and is a signal of adaptive evolution\cite{rodrigue_bayesian_2021}.
+    In this study we want to address three main questions: which proportions of the polymorphism we observe in mammals is undergoing maintenance positive selection ?
+    Are these mutations actually under positive selection at the scale of populations ?
+    How does effective population size modulate positive, negative and weak selection ?
 
-    Altogether, the goal of this study is to evaluate the extent of non-adaptive positive selection, by combining population-genetics and phylogenetics datasets, and ask a broad range of questions.
-    Are proteins optimal?
-    Is the fitness landscape stable across the mammalian evolution?
-    Can we use phylogenetics to predict the selection coefficient of a mutation?
-    Are deleterious mutations reliably purged only when selection overpowers drift?
-
-    A necessary step is being able to estimate fitness landscape on long-term evolution at the phylogenetic scale.
-    So called mutation-selection codon models provide a nearly-neutral model of evolution by estimating the fitness landscape over amino-acid sequences, for each site of the sequence\cite{ halpern_evolutionary_1998, rodrigue_mechanistic_2010, tamuri_estimating_2012}.
-    Only nearly-neutral mutations between high fitness amino acids will tend to be permitted by the model, allowing for the explicit calculation of the scaled selection coefficient of non-synonymous mutations between codons.
-    These models have be used as a null-model to predict the overall rate of evolution of proteins\cite{spielman_relationship_2015, dosreis_how_2015}, from which a departure in the observed overall rate that proteins are evolving under a changing fitness landscape\cite{rodrigue_detecting_2017, tamuri_mutationselection_2021} and is a signal of adaptive evolution\cite{rodrigue_bayesian_2021}.
-    Available multiple sequence alignment between mammalian species\cite{ranwez_orthomam_2007, howe_ensembl_2021} are used to estimate fitness landscape on long-term evolution.
+    For this we used available multiple sequence alignment between mammalian species\cite{ranwez_orthomam_2007, howe_ensembl_2021} to estimate fitness landscape on long-term evolution.
 
@@
     % How to articulate phylogenetic and population genetic
-    This information can be contrasted with the observed variation inside population, such that we can predict the scaled selection coefficient (the change in fitness) for each non-synonymous single nucleotide polymorphism (SNP) observed in a population (fig.~\ref{fig:method}).
-    We developed and leveraged a pipeline integrating divergence and polymorphism data across the entire exome for 29 populations across 7 genera, namely \textit{Equus}, \textit{Canis}, \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus} and \textit{Homo}.
+    We developed and leveraged a pipeline integrating divergence and polymorphism data across the entire exome for 29 populations across 7 genera, namely \textit{Equus}, \textit{Canis}, \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus} and \textit{Homo} (fig.~\ref{fig:method}).
     For each non-synonymous SNP observed at the population level, we predicted its scaled selection coefficient ($\Sphy$) in fitness from amino-acid fitness estimated at the mammalian scale (fig.~\ref{fig:homo-afr-results}A).
-    Then we ask whether the variants that are supposedly advantageous are showing signature of short term evolution.
-    In other words, if a variant is found in many mammals but not in ancestral humans, and a mutation in human is toward the mammal version, is this mutation advantageous for the individual carry it?
-    All observed SNPs are divided in 5 classes of selection: severely deleterious with $\Sphy<-3$, deleterious with $-3<\Sphy<-1$, weakly deleterious with $-1<\Sphy<0$, weakly advantageous with $0<\Sphy<1<$ and advantageous with $1<\Sphy$.
+    Then we ask whether the variants that are supposedly advantageous are showing signature of short term positive selection.
+    In other words, if a variant is found in many mammals but not in ancestral humans, and a mutation in human is toward the mammal version, is this mutation advantageous for the individual carrying it?
+    We divided all observed SNPs in 5 classes of selection: severely deleterious with $\Sphy<-3$, deleterious with $-3<\Sphy<-1$, weakly deleterious with $-1<\Sphy<0$, weakly advantageous with $0<\Sphy<1<$ and advantageous with $1<\Sphy$.
     For each class of selection, we first derived its site-frequency spectrum (SFS), which represent the proportion of mutations with a given number of derived allele in the population (fig.~\ref{fig:homo-afr-results}B).
@@
     These population based models cannot give a specific estimate of $\Spop$ for each SNP, but by gathering information across many SNPs, these models can estimate the proportion of advantageous mutations ($\polyAdv$), of nearly-neutral mutations ($\polyNeutral$) and of deleterious mutations ($\polyDel$) (fig.~\ref{fig:homo-afr-results}D).
+    We found that SNPs predicted to be advantageous given their selection coefficient $\Sphy$ are indeed under positive selection at the population-genetic scale, confirming that there is a local ongoing selection toward amino acids that are advantageous across mammals.
+    From another angle, mutations toward amino acids deemed deleterious across mammals are effectively purged at the population-genetic scale.
+    In between, mutations predicted to be weakly selected are effectively composed of neutral, positively and negatively selected mutations.
+
+    We replicated such experiment across 29 populations (fig.~\ref{fig:all-pop-results}), and found that mutations predicted to be deleterious are indeed purged at the population-genetic scale (fig.~\ref{fig:all-pop-results}A), while mutations predicted to be advantageous are indeed positively selected (fig.~\ref{fig:all-pop-results}C) .
+    However, mutation predicted to be weakly advantageous ($0<\Sphy<1<$) are composed of a mix of neutral and selected mutations with varying proportions across the different populations (fig.~\ref{fig:all-pop-results}B).
+    When populations are ordered by increased diversity (fig.~\ref{fig:selcoeff-pop-phylo}A), the proportion of neutral mutations is decreasing, suggesting that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) are more likely to discriminate whether mutations are advantageous or deleterious.
+    Alternatively stated, mutations in populations with low diversity (e.g.~\textit{Homo}) are effectively nearly-neutral and behave as would a neutral mutation.
+    This result is in accordance with the nearly-neutral theory of evolution that mutations are less efficiently selected for small populations.
+    Moreover, we found this effect to be in the same direction but less pronounced when we focused on all SNPs (fig.~S1) than on the SNPs predicted to be weakly selected (fig.~S2-3).
+    For populations with high diversity, because mutations are less likely to be neutral they are mechanically more likely to be selected and thus deleterious (fig.~S4), especially for mutations predicted to be deleterious at the phylogenetic scale (fig.~S5-6).
+    However, and surprisingly, a decrease in the proportion of neutral mutation did not translate into an increase proportion of advantageous mutations.
+    Instead, populations with higher diversity have both a lower proportion of neutral and advantageous mutations (fig.~S7), this effect is also more pronounced for mutations predicted to be advantageous at the phylogenetic scale (fig.~S8).
+    This discrepancy can be explained by the fact that population with larger diversity have already depleted the putatively advantageous mutations, and that only deleterious are remaining possible.
+    In other words, being on the top of a fixed fitness landscape leaves you with only paths going downhill.
+    Altogether, populations with increased diversity are showing signature of increased selection efficiency and are also less likely to generate positively selected mutations.
+    To look further into the relation between diversity and selection efficacy, we studied the estimation of the mean $\SpopMean$ as a function of the mean $\SphyMean$ for a subset of SNPs, for which $\SphyMean$ is close to $0$.
+    Sliding window of groups of $5.000$ SNPs are taken with a mean $\SphyMean$ between $-0.5$ and $0.5$ (fig.~\ref{fig:selcoeff-pop-phylo}B).
+    $\SpopMean$ is estimated for each group, with some groups that might have part of same SNPs that overlap.
+    The relationship between $\SpopMean$ and $\SphyMean$ is described as a second order polynomial, and the slope of this polynomial at $\SphyMean=0$ gives the ratio $\SpopMean/\SphyMean$ for each population.
+    We observe that $\SpopMean/\SphyMean$, representing the efficiency of selection at the short versus long term is positively correlated with synonymous diversity (fig.~\ref{fig:selcoeff-pop-phylo}C), a proxy of effective population size.
+    Altogether, population with large effective population size are under more efficient selection, confirming the prediction of the nearly-neutral theory of evolution.
 
@@
         \caption{
-            Panel A: Histogram of predicted selection coefficient (S) for each observed mutation in a sample of 512 individuals (1024 alleles) with African descent.
+            Panel A: Histogram of predicted selection coefficient (S) for each observed mutation in a sample of 8 individuals (out of 512 in the original dataset) with African descent.
             Mutations are divided in 5 classes of selection: severely deleterious (blue), deleterious (green), weakly deleterious (light green), weakly advantageous (yellow) and advantageous (red).
@@
             Reproducibility of results shown in figure~\ref{fig:homo-afr-results} in 29 populations across 7 genera.
-            From a site-frequency spectrum and total mutation rates are combined at the population-genetic scale to estimate the proportion of advantageous mutations $\polyAdv$ in top panel, of nearly-neutral mutations $\polyNeutral$ in middle panel and of deleterious mutations $\polyDel$ in bottom panel.
+            Site-frequency spectra and total mutation rates are combined at the population-genetic scale to estimate the proportion of advantageous mutations ($\polyAdv$) in top panel, of nearly-neutral mutations ($\polyNeutral$) in middle panel and of deleterious mutations ($\polyDel$) in bottom panel.
         }
@@
     \end{figure*}
-
-    Because of this observed overlap between phylogenetic and population-genetic methods, both estimating a scaled selection coefficient, we could study the estimation of the mean $\SpopMean$ as a function of the mean $\SphyMean$.
-    However, the mean selection coefficient estimated at the phylogenetic scale is usually drastically negative because of the heavy tail of the negative part of the estimated DFE.
-    Hence we focused on the relationship between $\SpopMean$ and $\SphyMean$ for a subset of SNPs, for which $\SphyMean$ is close to $0$.
-    Sliding window of groups of $5.000$ SNPs are taken with a mean $\SphyMean$ between $-0.5$ and $0.5$ (fig.~\ref{fig:selcoeff-pop-phylo}A).
-    $\SpopMean$ is estimated for each group, with some groups that might have part of same SNPs that overlap.
-    The relationship between $\SpopMean$ and $\SphyMean$ is best described as a second order polynomial, and the slope of this polynomial at $\SphyMean=0$ gives the ratio $\SpopMean/\SphyMean$ for each population.
-    We observ that $\SpopMean/\SphyMean$, representing the efficiency of selection at the short versus long term is positively correlated with synonymous diversity, a proxy of effective population siz.
-    Altogether, population with large effective population size are under more efficient selection.
 
@@
             Panel A. For each population, proportion of advantageous ($\polyAdv$), nearly-neutral ($\polyNeutral$) and of deleterious ($\polyDel$) mutations estimated at the population-genetic scale.
-            Estimation is performed with SNPs predicted to be weakly-advantageous at the phylogenetic scale $0<\Sphy<1<$.
+            Estimation is performed with SNPs predicted to be weakly-advantageous at the phylogenetic scale ($0<\Sphy<1$).
             Panel B. Mean selection coefficient at the population scale $\SpopMean$ as a function of phylogenetic $\SphyMean$.
@@
     % Our study is a bridge between phylogenetic and population genetics
-    From a theoretical evolution perspective, we found that we could use phylogenetics to predict the selection coefficient of a mutation.
+    From a theoretical evolution perspective, we found that we could use phylogenetic to predict the selection coefficient of a mutation.
     Appart from phylogenetic mutation-selection codon models, SIFT scores based on amino-acid alignments across species have already be found to be informative of the selection pressure exerted at the population scale\cite{chen_hunting_2021}.
@@
     They are also assuming no changes in effective population size\cite{latrille_inferring_2021}.
-    Epistasis is not modelled while it can have drastic consequence on the change in fitness landscape\cite{latrille_quantifying_2021}.
+    Epistasis is not modelled while it can have drastic consequences on the change in fitness landscape\cite{latrille_quantifying_2021}.
     However, both relaxation are computationally intensive, and would require new mutation-selection models and optimization techniques to be able to manipulate genome-wide datasets.
@@
     Moreover, these methods estimate selection coefficient that are very negative on average, which is not biologically sensible.
-    Altogether, we should seek to reproduce our experiment with other clades, such as drosophila, birds and with for more shallow but wider phylogeny to determine the extend of reproducibilty of our results.
+    Altogether, we should seek to reproduce our experiment with other clades, such as drosophila, birds and with for more shallow but wider phylogeny to determine the extent of reproducibilty of our results.
 
@@
     Third, these possible mutation are then classified whether they are synonymous or non-synonymous (stop mutations are excluded), non-synonymous mutations are then also classified depending on their selection coefficient ($\Sphy$).
-    From the SFS and the total mutation rate for the both synonymous and for the class of non-syonymous, polyDFE estimates the DFE $\phi$ using maximum likelihood.\@.
+    From the SFS and the total mutation rate for the both synonymous and for the class of non-synonymous, polyDFE estimates the DFE $\phi$ using maximum likelihood.
 

### 2022-04-20 manuscript/supp-mat.tex
Updated manuscript with JJ intro and TL experiment description.

@@
 \pdfinclusioncopyfonts=1
+
+\newcommand{\proba}{\mathbb{P}}
+\newcommand{\pfix}{\proba_{\mathrm{fix}}}
+\newcommand{\Spop}{\beta}
+\newcommand{\SpopMean}{\overline{\Spop}}
+\newcommand{\Sphy}{S}
+\newcommand{\SphyMean}{\overline{\Sphy}}
+\newcommand{\polyDel}{\proba \left[ {\Spop < -1} \right]}
+\newcommand{\polyNeutral}{\proba \left[ -1 < \Spop < 1 \right]}
+\newcommand{\polyAdv}{\proba \left[ 1 < \Spop  \right]}
 
@@
 
-    \subsubsection{Proportion of positive selection}
+    \subsubsection{Proportion of nearly-neutral mutations ($\polyNeutral$)}
     \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/regression/results.watterson.all_P-Ssup0.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/regression/results.watterson.all_P-Seq0.scatter.pdf}
     \end{minipage}
     \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/regression/results.watterson.pos_P-Ssup0.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/regression/results.watterson.neg-weak_P-Seq0.scatter.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/regression/results.watterson.pos-weak_P-Seq0.scatter.pdf}
     \end{minipage}
 
-    \subsubsection{Proportion of negative selection}
+    \subsubsection{Proportion of deleterious mutations ($\polyDel$)}
     \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/regression/results.watterson.all_P-Sinf0.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/regression/results.watterson.all_P-Sinf0.scatter.pdf}
     \end{minipage}
     \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/regression/results.watterson.neg_P-Sinf0.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/regression/results.watterson.neg_P-Sinf0.scatter.pdf}
     \end{minipage}
     \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/regression/results.watterson.neg-strong_P-Sinf0.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/regression/results.watterson.neg-strong_P-Sinf0.scatter.pdf}
     \end{minipage}
 
-    \subsubsection{Proportion of weak selection}
+    \subsubsection{Proportion of advantageous mutations ($\polyAdv$)}
     \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/regression/results.watterson.all_P-Seq0.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/regression/results.watterson.all_P-Ssup0.scatter.pdf}
     \end{minipage}
     \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/regression/results.watterson.neg-weak_P-Seq0.scatter.pdf}
-    \end{minipage}
-    \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/5cat-polyDFE-mC-non-adaptive/regression/results.watterson.pos-weak_P-Seq0.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/regression/results.watterson.pos_P-Ssup0.scatter.pdf}
     \end{minipage}

### 2022-04-20 copy_artworks.sh

@@ -1,11 +1,11 @@
 #!/usr/bin/env bash
 \cp -rf ./experiments/50windows-polyDFE-mC-non-adaptive/regression/results.watterson.a.scatter.pdf ./manuscript/artworks/scatter.watterson.slopeSpopSphy.pdf
 \cp -rf ./experiments/50windows-polyDFE-mC-non-adaptive/results/regression.MutSel.SelCoeff.scatter.pdf ./manuscript/artworks/scatter.Sphy.Spop.pdf
-\cp -rf ./experiments/5cat-polyDFE-mC-non-adaptive/results/Theta.MutSel.P-Seq0.heatmap.pdf ./manuscript/artworks/heatmap.neutral.pdf
-\cp -rf ./experiments/5cat-polyDFE-mC-non-adaptive/results/Theta.MutSel.P-Sinf0.heatmap.pdf ./manuscript/artworks/heatmap.neg.pdf
-\cp -rf ./experiments/5cat-polyDFE-mC-non-adaptive/results/Theta.MutSel.P-Ssup0.heatmap.pdf ./manuscript/artworks/heatmap.pos.pdf
-\cp -rf ./experiments/5cat-polyDFE-mC-non-adaptive/results/Theta.MutSel.pos-weak.stacked.pdf ./manuscript/artworks/pos-weak.stacked.pdf
-\cp -rf ./experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.AFR.MutSel-sfs.normalize.pdf ./manuscript/artworks/AFR.SFS.pdf
-\cp -rf ./experiments/5cat-polyDFE-mC-non-adaptive/analysis/Homo_sapiens.AFR.MutSel.polyDFE_C.pdf ./manuscript/artworks/AFR.polyDFE.pdf
+\cp -rf ./experiments/polyDFE-mC-non-adaptive/results/Theta.MutSel.P-Seq0.heatmap.pdf ./manuscript/artworks/heatmap.neutral.pdf
+\cp -rf ./experiments/polyDFE-mC-non-adaptive/results/Theta.MutSel.P-Sinf0.heatmap.pdf ./manuscript/artworks/heatmap.neg.pdf
+\cp -rf ./experiments/polyDFE-mC-non-adaptive/results/Theta.MutSel.P-Ssup0.heatmap.pdf ./manuscript/artworks/heatmap.pos.pdf
[…]

### 2022-04-20 scripts/plot_multiple_regression.py

@@ -55,14 +55,12 @@ def main(args):
         df_out["method"] = method
         merge_out.append(df_out)
 
-        sp_slopes = {
-            sp: (f"[{min(df['a']):.2f}, {max(df['a']):.2f}]" if len(df) > 1 else f"{df['a'].values[0]:.2f}") for
-            sp, df in df_out.groupby(["species"])}
+        sp_slopes = {sp: (f"[{min(df['betaS_ratio']):.2f}, {max(df['betaS_ratio']):.2f}]" if len(df) > 1 else f"{df['betaS_ratio'].values[0]:.2f}") for sp, df in df_out.groupby(["species"])}
         legend_elements = [Line2D([0], [0], color=colors[sp],
                                   label=f'{sp.replace("_", " ")}: f\'(0)={sp_slopes[sp]}') for sp in sp2pop]
         plt.legend(handles=legend_elements)
-        plt.xlabel("$\\overline{S}$ at the phylogenetic scale (Mutation-selection)")
-        plt.ylabel("$\\overline{\\beta}$ at the population scale (polyDFE)")
+        plt.xlabel("Mean $\\overline{S}$ (phylogenetic)")
+        plt.ylabel("Mean $\\overline{\\beta}$ (population-genetics)")
         plt.tight_layout()
         plt.savefig(args.output.replace('results.tsv', f'{method}.SelCoeff.scatter.pdf'), format="pdf")
         plt.clf()

### 2022-04-20 scripts/plot_regression.py

@@ -9,11 +9,10 @@ from matplotlib.cm import get_cmap
 from matplotlib.lines import Line2D
 from libraries import my_dpi, plt, polydfe_cat_dico, tex_f, sort_df, sp_sorted, format_pop, CategorySNP
 
-cat_snps = CategorySNP("MutSel")
 markers = ["o", "d", "s", '.']
 
 
-def open_tsv(filepath):
+def open_tsv(filepath, cat_snps):
     ddf = pd.read_csv(filepath, sep="\t")
     if os.path.basename(filepath) == "Theta.results.tsv":
         df_theta = ddf[(ddf["method"] == "MutSel") & (ddf["category"] == "syn")]
@@ -37,7 +36,7 @@ def discard_col(col, df):
     return (col not in df) or (df.dtypes[col] == np.object) or (not np.all(np.isfinite(df[col])))
 
 
-def generate_xy_plot():
+def generate_xy_plot(cat_snps):
     xy_dico = defaultdict(list)
     dico_label = {'pop': "Population", "species": "Species", "watterson": "Watterson $\\theta_W$",
                   "proba": "$\\mathbb{P}$"}
@@ -59,7 +58,7 @@ def generate_xy_plot():
         dico_label[cat] = "$\\mathbb{P}" + f"[{s}]$"
         dico_label[f"{cat}_snps"] = "$\\mathbb{P}_{obs}" + f"[{s}]$"
         for cat_poly, beta_tex in polydfe_cat_dico.items():
-            beta = beta_tex[beta_tex.find("[")+1:beta_tex.rfind("]")]
+            beta = beta_tex[beta_tex.find("[") + 1:beta_tex.rfind("]")]
             s_given_beta_key = f'{cat_poly}_P-{cat}'
             dico_label[s_given_beta_key] = "$\\mathbb{P}" + f"[ {s} | {beta}]$"
 
@@ -95,9 +94,14 @@ def column_format(size):
     return "|" + "|".join(["l"] * 2 + ["r"] * (size - 2)) + "|"
 
 
+def logit(x):
+    return np.log(x / (1 - x))
+
+
 def main(args):
     os.makedirs(os.path.dirname(args.output), exist_ok=True)
-    df_list = [open_tsv(filepath) for filepath in sorted(args.tsv)]
+    cat_snps = CategorySNP("MutSel", bins=args.bins, windows=args.windows)
+    df_list = [open_tsv(filepath, cat_snps) for filepath in sorted(args.tsv)]
[…]

### 2022-04-22 manuscript/main.tex
Manuscript by JJ and TL.

@@
 \newcommand{\pfix}{\proba_{\mathrm{fix}}}
+
+\newcommand{\Sphy}{S}
+\newcommand{\SphyMean}{\overline{\Sphy}}
+\newcommand{\divStrongDel}{\Sphy < -3}
+\newcommand{\divDel}{-3 < \Sphy < -1}
+\newcommand{\divWeakDel}{-1 < \Sphy < 0}
+\newcommand{\divWeakAdv}{0 < \Sphy < 1}
+\newcommand{\divAdv}{ \Sphy > 1}
+\newcommand{\PdivStrongDel}{\proba \left[ \divStrongDel \right]}
+\newcommand{\PdivDel}{\proba \left[ \divDel \right]}
+\newcommand{\PdivWeakDel}{\proba \left[ \divWeakDel \right]}
+\newcommand{\PdivWeakAdv}{\proba \left[ \divWeakAdv \right]}
+\newcommand{\PdivAdv}{\proba \left[ \divAdv \right]}
+
 \newcommand{\Spop}{\beta}
 \newcommand{\SpopMean}{\overline{\Spop}}
-\newcommand{\Sphy}{S}
-\newcommand{\SphyMean}{\overline{\Sphy}}
-\newcommand{\polyDel}{\proba \left[ {\Spop < -1} \right]}
-\newcommand{\polyNeutral}{\proba \left[ -1 < \Spop < 1 \right]}
-\newcommand{\polyAdv}{\proba \left[ 1 < \Spop  \right]}
+\newcommand{\polyDel}{\Spop < -1}
+\newcommand{\polyNeutral}{-1 < \Spop < 1}
+\newcommand{\polyAdv}{ \Spop > 1}
+\newcommand{\PpolyDel}{\proba \left[ \polyDel \right]}
+\newcommand{\PpolyNeutral}{\proba \left[ \polyNeutral \right]}
+\newcommand{\PpolyAdv}{\proba \left[ \polyAdv \right]}
 
@@
         However, current positive selection can also be the result of mutations compensating for deleterious substitutions that have accumulated along lineages, in which case positive selection is non-adaptive and predictable.
-        To evaluate the extent of non-adaptive positive selection, we have combined population-genetics and phylogenetics datasets.
+        To evaluate the extent of non-adaptive positive selection, we have combined population genetics and phylogenetic datasets.
         We first leveraged phylogenetic codon models which are based on a population-genetics formalism, assuming a non-adaptive fitness landscape.
@@
         Second, we integrated mammalian divergence data with polymorphic variants found in 29 populations across 7 mammalian genera.
-        For each non-synonymous variant observed at the population level, we predicted its change in fitness from amino-acid fitnesses estimated at the mammalian scale.
-        We found that a large proportion of observed non-synonymous changes are predicted to be positively selected, meaning that the ancestral allele is sub-optimal.
+        For each non-synonymous variant observed at the population level, we predicted its change in fitness from amino-acid fitness estimated at the mammalian scale.
+        We found that a large proportion of observed non-synonymous changes are predicted to be positively selected, meaning that the ancestral allele is suboptimal.
         These supposedly advantageous variants are indeed showing signs of recent positive selection in all populations.
@@
     We can distinguish two main advantages.
-    The first correspond to what we usually call adaptive evolution.
-    he advantage in fitness of a new mutation allows its bearer to become better adapted to a changing environment.
-    The second we call maintenance positive selection.
-    The mutation restores the ancestral state which corresponded to an optimal functioning of the individual in a constant environment, but has been lost due to the fixation of a deleterious mutation by drift.
+    The first advantage allows its bearer to become better adapted to a new or a changing environment, what we typically call adaptive evolution.
+    The population as a whole is thus climbing the fitness landscape along an adaptive walk\cite{tenaillon_utility_2014}.
+    The second is non-adaptive, in the sense that the increase in fitness of a new mutation is not a response to a new or a changing environment.
+    Instead, the mutation restores the ancestral state which corresponded to an optimal functioning of the individual in a constant environment, but has been lost due to the fixation of a deleterious mutation by drift.
+    The population as a whole is thus merely staying in the same position in fitness landscape at this equilibrium, and positive selection compensates for deleterious mutations that reach fixation due to drift\cite{sella_application_2005, mustonen_fitness_2009}.
     These two different kinds of selection result in a positive transmission bias of the advantageous allele, but their consequences are conceptually different.
-    While adaptive evolution promotes phenotype diversification, maintenance positive selection promotes phenotype stability and preserves well established biological systems.
+    While adaptive evolution promotes phenotype diversification, non-adaptive positive selection promotes phenotype stability and preserves well established biological systems.
     It is thus of importance to be able to distinguish those two kinds of positive selection in order to understand the diversification of species.
 
-    Adaptive evolution in proteins can be quantified by comparing sequence variation inside a population to the sequence divergence with a sister species\cite{mcdonald_adaptative_1991}.
-    Indeed, strongly adaptive mutations are expected to be observed in substitutions but not in polymorphism because they reach fixation quickly.
+    Inside proteins, positive selection can be quantified by comparing sequence variation inside a population with the sequence divergence with a sister species\cite{mcdonald_adaptative_1991}.
+    Indeed, strongly advantageous mutations are expected to be observed in substitutions but not in polymorphism because they reach fixation quickly.
     This method has been largely improved to account for possible bias-inducing factors such as the presence of weak positive selection, background selection and demography fluctuations\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009, galtier_adaptive_2016, tataru_inference_2017}.
     It's application across many taxa has uncovered that a large proportion of substitutions are positively selected\cite{moutinho_variation_2019}.
-    The root causes for this widespread rate of positive selection are however scarcely investigated, often assumed to be the end result of adaptive evolution.
+    The root cause for this widespread rate of positive selection is, however, scarcely investigated, often assumed to be the end result of adaptive evolution.
     However, as mentioned above, not all these mutations contribute to genetic innovation and diversification.
-    Adaptive evolution can only be well estimated if maintenance positive selection is taken into account.
+    Adaptive evolution can only be well estimated if non-adaptive positive selection is taken into account.
     While adaptive evolution is unpredictable because it brings an advantage concerning an unpredictable change in the environment of organisms, the second is predictable because optimal states should be more or less the same for closely related organisms which share most of their environment and physiology.
-    A way to measure maintenance positive selection is to compute selection coefficients assuming a constant and stable fitness landscape estimated from the alignment of protein-coding genes.
-    For each site of the proteic alignment, the fitness of each amino-acid can be estimated from their frequency in the alignment.
-    One of the most used method to make these predictions is SIFT (Sort Intolerant From Tolerant) which reliably detects deleterious mutations in many taxa.
+    A way to thus measure non-adaptive positive selection is to compute selection coefficients assuming a constant and stable fitness landscape estimated from the alignment of protein-coding genes.
+    For each site of the protein alignment, amino-acid frequencies in the alignment is a proxy for its fitness, since for example a deleterious amino acid will be absent in the alignment.
+    One of the most used methods to make these predictions is SIFT (Sort Intolerant From Tolerant) which reliably detects deleterious mutations in many taxa\cite{ng_sift_2003, vaser_sift_2016}.
     However, this method has two major shortcomings.
-    First, this method uses amino-acid frequency as a proxy for amino-acid fitness, even if we know that a lot of mechanisms can influence amino-acid frequency other than fitness (mutation biases, GC-biased gene conversion, mutational paths).
-    Second, each mutations is attributed a score to describe if it should be under purifying selection on one hand or be neutral or advantageous on the other hand.
+    First, this method uses amino-acid frequency as a proxy for amino-acid fitness, even if we know that a lot of mechanisms can influence amino-acid frequency other than fitness (phylogeny, mutation biases, GC-biased gene conversion, mutational paths).
+    Second, each mutation is attributed a score to describe if it should be under purifying selection on one hand or be neutral or advantageous, on the other hand.
     But this score makes little sense to actual measure of fitness, and is not interpretable in terms of population genetics.
-    So called mutation-selection codon models provide a nearly-neutral framework of evolution by estimating the fitness landscape over amino-acid sequences for each site of the sequence while taking into account non adaptive-processes impacting codon frequency\cite{ halpern_evolutionary_1998, rodrigue_mechanistic_2010, tamuri_estimating_2012}.
+    In the other hand, at the DNA level, so-called mutation-selection codon models are rooted with population genetics formalism\cite{halpern_evolutionary_1998, mccandlish_modeling_2014}.
+    Such models provide a nearly-neutral framework of evolution by estimating the fitness landscape over amino-acid sequences for each site of the sequence while taking into account non-adaptive processes impacting codon frequency\cite{halpern_evolutionary_1998, rodrigue_mechanistic_2010, tamuri_estimating_2012}.
     Only nearly-neutral mutations between high fitness amino acids will tend to be permitted by the model, allowing for the explicit calculation of the scaled selection coefficient of non-synonymous mutations between codons.
-    These models have been used as a null-model to predict the overall rate of evolution of proteins\cite{spielman_relationship_2015, dosreis_how_2015}.
+    These models have been used as a null model to predict the overall rate of evolution of proteins\cite{spielman_relationship_2015, dosreis_how_2015}.
     A departure from this model indicates that proteins are evolving under a changing fitness landscape\cite{rodrigue_detecting_2017, tamuri_mutationselection_2021} and is a signal of adaptive evolution\cite{rodrigue_bayesian_2021}.
-    In this study we want to address three main questions: which proportions of the polymorphism we observe in mammals is undergoing maintenance positive selection ?
+    In this study we want to address three main questions: which proportions of the polymorphism we observe in mammals is undergoing non-adaptive positive selection ?
     Are these mutations actually under positive selection at the scale of populations ?
-    How does effective population size modulate positive, negative and weak selection ?
-
-    For this we used available multiple sequence alignment between mammalian species\cite{ranwez_orthomam_2007, howe_ensembl_2021} to estimate fitness landscape on long-term evolution.
+    How does effective population size modulates positive, negative and weak selection ?
 
     \begin{figure*}[!ht]
+        \
         \centering
@@
 
-    % How to articulate phylogenetic and population genetic
+    For this we used available multiple sequence alignment between mammalian species\cite{ranwez_orthomam_2007, howe_ensembl_2021} to estimate fitness landscape on long-term evolution.
     We developed and leveraged a pipeline integrating divergence and polymorphism data across the entire exome for 29 populations across 7 genera, namely \textit{Equus}, \textit{Canis}, \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus} and \textit{Homo} (fig.~\ref{fig:method}).
@@
     Then we ask whether the variants that are supposedly advantageous are showing signature of short term positive selection.
-    In other words, if a variant is found in many mammals but not in ancestral humans, and a mutation in human is toward the mammal version, is this mutation advantageous for the individual carrying it?
-    We divided all observed SNPs in 5 classes of selection: severely deleterious with $\Sphy<-3$, deleterious with $-3<\Sphy<-1$, weakly deleterious with $-1<\Sphy<0$, weakly advantageous with $0<\Sphy<1<$ and advantageous with $1<\Sphy$.
-    For each class of selection, we first derived its site-frequency spectrum (SFS), which represent the proportion of mutations with a given number of derived allele in the population (fig.~\ref{fig:homo-afr-results}B).
-    Compared to synonymous mutations (supposedly neutral), mutations predicted to be advantageous are over-represented at higher frequency, while severally deleterious are under-represented at high frequency, a signature that our prediction are qualitatively in the right direction.
-    Aside from the frequency of the derived allele, another information is the total number of observed alleles compared to its expectation, given by the total mutation rate.
-    The total mutation rate for each class is computed from the ancestral genome reconstruction (fig.~\ref{fig:homo-afr-results}C).
-    For example, for the category of selection with $1<\Sphy$, the expected total mutation rate is obtained by adding together mutation rates for all possible non-synonymous mutations for which the derived allele is toward a fitter amino-acid than the ancestral allele with $\Sphy > 1$.
-    The total mutation rate and the SFS are combined to estimate the distribution of the selection coefficient $\Spop$ given by population-based model\cite{tataru_inference_2017, tataru_polydfe_2020}.
-    These population based models cannot give a specific estimate of $\Spop$ for each SNP, but by gathering information across many SNPs, these models can estimate the proportion of advantageous mutations ($\polyAdv$), of nearly-neutral mutations ($\polyNeutral$) and of deleterious mutations ($\polyDel$) (fig.~\ref{fig:homo-afr-results}D).
-    We found that SNPs predicted to be advantageous given their selection coefficient $\Sphy$ are indeed under positive selection at the population-genetic scale, confirming that there is a local ongoing selection toward amino acids that are advantageous across mammals.
-    From another angle, mutations toward amino acids deemed deleterious across mammals are effectively purged at the population-genetic scale.
-    In between, mutations predicted to be weakly selected are effectively composed of neutral, positively and negatively selected mutations.
+    In other words, if a variant is found in many mammals but not in ancestral humans, and a mutation in humans is toward the mammalian version, is this mutation advantageous for the individual carrying it?
+    At the population level (e.g.
+in humans with Asian descent in fig.~\ref{fig:homo-afr-results}), we divided all observed SNPs in 5 classes of predicted selection coefficient: severely deleterious with $\divStrongDel$, deleterious with $\divDel$, weakly deleterious with $\divWeakDel$, weakly advantageous with $\divWeakAdv$ and advantageous with $\divAdv$.
+    For each class of selection, SNPs are then grouped by the number of derived alleles in the population (fig.~\ref{fig:homo-afr-results}B), generating so called site-frequency spectrum (SFS).
+    Compared to synonymous mutations supposedly neutral (black line in fig.~\ref{fig:homo-afr-results}B), mutations predicted to be deleterious (blue and green lines in fig.~\ref{fig:homo-afr-results}B) are underrepresented at high frequency in the population, a signature of ongoing purifying selection.
+    Remarkably, SNPs predicted to be advantageous (red line in fig.~\ref{fig:homo-afr-results}B) are over-represented at higher frequency in the population, meaning they are more likely to reach fixation as a consequence of ongoing positive selection.
+    However, these observations remain qualitative.
+    Thus, we quantified the distribution of selection coefficient for each category of SNPs with the model polyDFE\cite{tataru_inference_2017, tataru_polydfe_2020}.
+    The model uses the count of derived allele for each frequency class of the SFS to infer the distribution of fitness effects (DFE) of the region under study.
+    For each category of SNPs, it is important to compute the expected number of mutations giving birth to a SNP of that category given a mutational matrix (fig.~\ref{fig:homo-afr-results}C).
+    The model uses both the mutational expectation for each category, and the counts of synonymous derived allele as a neutral model, which allow to control for demographic effects, and polarization errors when inferring the ancestral state.
+    These populations based models cannot give a specific estimate of $\Spop$ for each SNP, but by gathering information across many SNPs, these models can estimate the proportion of advantageous mutations ($\PpolyAdv$), of nearly-neutral mutations ($\PpolyNeutral$) and of deleterious mutations ($\PpolyDel$) (fig.~\ref{fig:homo-afr-results}D).
+    We found that SNPs predicted to be deleterious given their selection coefficient $\Sphy$ across mammals are effectively purged at the population-genetic scale, demonstrating that purifying selection is largely predictable and amino acids with low fitness across mammals are effectively purged away in each population.
+    Notably, SNPs predicted to be advantageous given their selection coefficient $\Sphy$ are indeed under positive selection at the population-genetic scale, confirming that there is a local ongoing selection toward amino acids that are restoring the optimally functioning protein.
+    In between these two extremes, mutations predicted to be weakly selected (cyan and orange in fig.~\ref{fig:homo-afr-results}) are effectively composed of neutral, positively and negatively selected mutations.
 
-    We replicated such experiment across 29 populations (fig.~\ref{fig:all-pop-results}), and found that mutations predicted to be deleterious are indeed purged at the population-genetic scale (fig.~\ref{fig:all-pop-results}A), while mutations predicted to be advantageous are indeed positively selected (fig.~\ref{fig:all-pop-results}C) .
-    However, mutation predicted to be weakly advantageous ($0<\Sphy<1<$) are composed of a mix of neutral and selected mutations with varying proportions across the different populations (fig.~\ref{fig:all-pop-results}B).
-    When populations are ordered by increased diversity (fig.~\ref{fig:selcoeff-pop-phylo}A), the proportion of neutral mutations is decreasing, suggesting that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) are more likely to discriminate whether mutations are advantageous or deleterious.
+    We replicated such experiment across 29 populations (fig.~\ref{fig:all-pop-results}), and found that mutations predicted to be deleterious are indeed purged at the population-genetic scale (blue and green rows in fig.~\ref{fig:all-pop-results}A).
+    However, mutation predicted to be weakly advantageous ($\divWeakAdv$) are composed of a mix of neutral and selected mutations with varying proportions across the different populations (orange row in fig.~\ref{fig:all-pop-results}B).
+    Similarly, mutations predicted to be advantageous are found to be positively selected with varying proportions (red row in fig.~\ref{fig:all-pop-results}C).
+    A variable which could explain those variations between populations is the effective number of individuals in the population ($\Ne$), a major driver of selection efficacy.
+    $\Ne$ is not directly accessible, and a reasonable proxy usually used is the synonymous diversity ($\theta=4\Ne\mu$ with $\mu$ the mutation rate).
+    We thus ordered populations by increased synonymous diversity (fig.~\ref{fig:selcoeff-pop-phylo}A), exhibiting a decreased proportion of neutral mutations.
+    This result suggest that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) are more likely to discriminate whether mutations are advantageous or deleterious.
     Alternatively stated, mutations in populations with low diversity (e.g.~\textit{Homo}) are effectively nearly-neutral and behave as would a neutral mutation.
-    This result is in accordance with the nearly-neutral theory of evolution that mutations are less efficiently selected for small populations.
-    Moreover, we found this effect to be in the same direction but less pronounced when we focused on all SNPs (fig.~S1) than on the SNPs predicted to be weakly selected (fig.~S2-3).
-    For populations with high diversity, because mutations are less likely to be neutral they are mechanically more likely to be selected and thus deleterious (fig.~S4), especially for mutations predicted to be deleterious at the phylogenetic scale (fig.~S5-6).
-    However, and surprisingly, a decrease in the proportion of neutral mutation did not translate into an increase proportion of advantageous mutations.
-    Instead, populations with higher diversity have both a lower proportion of neutral and advantageous mutations (fig.~S7), this effect is also more pronounced for mutations predicted to be advantageous at the phylogenetic scale (fig.~S8).
-    This discrepancy can be explained by the fact that population with larger diversity have already depleted the putatively advantageous mutations, and that only deleterious are remaining possible.
+    This result is qualitatively in accordance with the nearly-neutral theory of evolution that mutations are less efficiently selected for small populations.
+    Moreover, we found this effect to be in the same direction but less pronounced when we focused on all SNPs (fig.~S1) rather than only the SNPs predicted to be weakly selected (fig.~S2-3).
+    To look further into the relation between diversity and selection efficacy, we thus studied the estimation of the mean $\SpopMean$ as a function of the mean $\SphyMean$ for a subset of SNPs, for which $\SphyMean$ is close to $0$.
+    Indeed, polyDFE is a nearly neutral model and is not able to reliably compute selection coefficients for only strongly deleterious or only strongly advantageous SNPs.
+    Sliding window of groups of $5.000$ SNPs are taken with a mean $\SphyMean$ between $-0.5$ and $0.5$ (fig.~\ref{fig:selcoeff-pop-phylo}B).
+    $\SpopMean$ is estimated for each group, with some groups that might have part of same SNPs that overlap.
+    The relationship between $\SpopMean$ and $\SphyMean$ is described as a second-order polynomial, and the slope of this polynomial at $\SphyMean=0$ gives the ratio $\SpopMean/\SphyMean$ for each population.
+    We observe that $\SpopMean/\SphyMean$, representing the efficacy of selection at the short versus long-term is positively correlated with synonymous diversity (fig.~\ref{fig:selcoeff-pop-phylo}C), a proxy of effective population size.
+    Altogether, populations with large effective population size are under more efficient selection, confirming the prediction of the nearly-neutral theory of evolution.
+
+    As a consequence of increased selection efficacy, mutations in populations with high diversity are mechanically more likely to be deleterious (fig.~S4), especially for mutations predicted already to be deleterious at the phylogenetic scale (fig.~S5-6).
+    However, and surprisingly, a decrease in the proportion of neutral mutation did not translate into a mechanical increase in the proportion of advantageous mutations.
+    Instead, populations with higher diversity have a lower proportion of advantageous mutations (fig.~S7), this effect is also more pronounced for mutations predicted to be advantageous at the phylogenetic scale (red row in fig.~\ref{fig:all-pop-results}C and fig.~S8).
+    This discrepancy can be explained by the fact that populations with larger diversity have already depleted the putatively advantageous mutations, and that only deleterious are remaining possible.
     In other words, being on the top of a fixed fitness landscape leaves you with only paths going downhill.
     Altogether, populations with increased diversity are showing signature of increased selection efficiency and are also less likely to generate positively selected mutations.
-    To look further into the relation between diversity and selection efficacy, we studied the estimation of the mean $\SpopMean$ as a function of the mean $\SphyMean$ for a subset of SNPs, for which $\SphyMean$ is close to $0$.
-    Sliding window of groups of $5.000$ SNPs are taken with a mean $\SphyMean$ between $-0.5$ and $0.5$ (fig.~\ref{fig:selcoeff-pop-phylo}B).
-    $\SpopMean$ is estimated for each group, with some groups that might have part of same SNPs that overlap.
-    The relationship between $\SpopMean$ and $\SphyMean$ is described as a second order polynomial, and the slope of this polynomial at $\SphyMean=0$ gives the ratio $\SpopMean/\SphyMean$ for each population.
-    We observe that $\SpopMean/\SphyMean$, representing the efficiency of selection at the short versus long term is positively correlated with synonymous diversity (fig.~\ref{fig:selcoeff-pop-phylo}C), a proxy of effective population size.
-    Altogether, population with large effective population size are under more efficient selection, confirming the prediction of the nearly-neutral theory of evolution.
 
@@
         \caption{
-            Panel A: Histogram of predicted selection coefficient (S) for each observed mutation in a sample of 8 individuals (out of 512 in the original dataset) with African descent.
+            Panel A: Histogram of predicted selection coefficient ($\Sphy$) for each observed mutation in a sample of 8 individuals (out of 512 in the original dataset) with African descent.
             Mutations are divided in 5 classes of selection: severely deleterious (blue), deleterious (green), weakly deleterious (light green), weakly advantageous (yellow) and advantageous (red).
-            Panel B: Site-frequency spectrum (SFS) represent the proportion of mutations (y-axis) with a given number of derived allele in the population (x-axis).
+            Panel B: Site-frequency spectrum (SFS) represents the proportion of mutations (y-axis) with a given number of derived alleles in the population (x-axis).
             SFS are drawn for a random sample of 16 alleles (mean in solid line and standard deviation in filled color) for each class of selection and for synonymous mutations supposedly neutral (black).
-            Supposedly advantageous are over-represented at higher frequency, while severally deleterious are under-represented at high frequency, a signature of selection.
-            Panel C. Histogram of predicted selection coefficient (S) for each possible mutation away from the ancestral human genome, weighted by the mutation rate.
+            Supposedly advantageous are over-represented at higher frequency, while severally deleterious are underrepresented at high frequency, a signature of selection.
+            Panel C. Histogram of predicted selection coefficient ($\Sphy$) for each possible mutation away from the ancestral human genome, weighted by the mutation rate.
             For each class of selection, the sum of histogram in this class thus gives the expected total mutation rate toward this class.
@@
             Panel D.
-For each class of selection (and for the set of all non-synonymous mutations), information from the SFS and the expected total mutation rate are combined at the population-genetic scale to estimate the proportion of advantageous mutations $\polyAdv$, of nearly-neutral mutations $\polyNeutral$ and of deleterious mutations $\polyDel$.
+For each class of selection (and for the set of all non-synonymous mutations), information from the SFS and the expected total mutation rate are combined at the population-genetic scale to estimate the proportion of advantageous mutations $\PpolyAdv$, of nearly-neutral mutations $\PpolyNeutral$ and of deleterious mutations $\PpolyDel$.
         }
@@
             Reproducibility of results shown in figure~\ref{fig:homo-afr-results} in 29 populations across 7 genera.
-            Site-frequency spectra and total mutation rates are combined at the population-genetic scale to estimate the proportion of advantageous mutations ($\polyAdv$) in top panel, of nearly-neutral mutations ($\polyNeutral$) in middle panel and of deleterious mutations ($\polyDel$) in bottom panel.
+            Site-frequency spectra and total mutation rates are combined at the population-genetic scale to estimate the proportion of advantageous mutations ($\PpolyAdv$) in top panel, of nearly-neutral mutations ($\PpolyNeutral$) in middle panel and of deleterious mutations ($\PpolyDel$) in bottom panel.
         }
@@
         \caption{
-            Panel A. For each population, proportion of advantageous ($\polyAdv$), nearly-neutral ($\polyNeutral$) and of deleterious ($\polyDel$) mutations estimated at the population-genetic scale.
-            Estimation is performed with SNPs predicted to be weakly-advantageous at the phylogenetic scale ($0<\Sphy<1$).
+            Panel A.
+For each population, proportion of advantageous ($\PpolyAdv$), nearly-neutral ($\PpolyNeutral$) and of deleterious ($\PpolyDel$) mutations estimated at the population-genetic scale.
+            Estimation is performed with SNPs predicted to be weakly advantageous at the phylogenetic scale ($\divWeakAdv$).
             Panel B. Mean selection coefficient at the population scale $\SpopMean$ as a function of phylogenetic $\SphyMean$.
-            Observed SNPs are sorted and groups of $5.000$ SNPs are taken as a sliding windows with increasing mean $-0.5 \leq \SphyMean \leq 0.5$.
+            Observed SNPs are sorted and groups of $5.000$ SNPs are taken as a sliding window with increasing mean $-0.5 \leq \SphyMean \leq 0.5$.
             For each group along the sliding window, $\SpopMean$ (y-axis) is estimated based on SFS and the total mutation rate, and compared to the mean $\SphyMean$ (x-axis).
@@
 
+    From a structural biology perspective, we found that proteins are not optimal, with a large proportion of mutations still toward more optimal amino acids.
+    Seen from another angle, it means that we could theoretically derive the fittest proteins using only the amino acid with the highest fitness.
+    Another way to confirm our predictions on amino acid fitness would be to test whether fittest proteins are also thermodynamically more stable, leveraging recent developments able to compute efficiently and accurately the folding of proteins.
+
     % Our study is a bridge between phylogenetic and population genetics
-    From a theoretical evolution perspective, we found that we could use phylogenetic to predict the selection coefficient of a mutation.
-    Appart from phylogenetic mutation-selection codon models, SIFT scores based on amino-acid alignments across species have already be found to be informative of the selection pressure exerted at the population scale\cite{chen_hunting_2021}.
-    However, they do not integrate the underlying phylogeny nor the underlying mutational process.
-    Additionally, they are not based on population-genetics formalism, hence the relationship between selection coefficient and SIFT score is not straightforward.
-    We found here that mutation-selection formalism greatly outperforms SIFT score to predict the selection coefficient of mutations (Supplementary Materials).
-    Most importantly, we showed that mutation-selection codon models formalize a bridge between phylogenetics and population genetics.
-    Our study is a bridge between phylogenetic and population genetics, but both ends has its limitation.
+    From a theoretical evolution perspective, we found that we could use phylogenetic signal to predict the selection coefficient of a mutation.
+    Apart from phylogenetic mutation-selection codon models, SIFT scores based on amino-acid alignments across species have already been found to be informative of the selection pressure exerted at the population scale\cite{chen_hunting_2021}.
+    Our study concur in that direction, that sites with higher SIFT score at the phylogenetic scale are more positively selected in the different populations (supp.\ mat\  section 2).
+    In practice, SIFT score are more coarse grained, with for example a bulk a mutations with a score of 1.0 (the highest), and does not provide a boundary between advantageous and deleterious mutations.
+    Moreover, they are not based on population-genetics formalism, hence the relationship between selection coefficient and SIFT score is not straightforward.
+    Alternatively at the DNA level, $\omega$-based codon model use the ratio of non-synonymous over synonymous substitution as signature of selection\cite{goldman_codonbased_1994, yang_codonsubstitution_2002}, taking into account the mutational bias and the underlying phylogeny.
+    We also show that sites with higher $\omega$ are more positively selected in the different populations (supp.\ mat\  section 3).
+    However, even sites which are supposedly under pervasive positive selection at the phylogenetic scale ($\omega>1$) are not necessarily positively selected in the populations.
+    Most importantly, such models do not leverage the information of the source and target amino acid involve in the mutation, and thus cannot be used to estimate the non-adaptive part of positive selection.
+    Altogether, we showed that mutation-selection codon models formalize a bridge between phylogenetics and population genetics models, but both ends has its limitation and could be improved.
 
     % Problem with the current mutation-selection model, and the way forward
-    For phylogenetic models, current mutation-selection codon model are sensitive to mis-alignment.
-    They are also assuming no changes in effective population size\cite{latrille_inferring_2021}.
-    Epistasis is not modelled while it can have drastic consequences on the change in fitness landscape\cite{latrille_quantifying_2021}.
-    However, both relaxation are computationally intensive, and would require new mutation-selection models and optimization techniques to be able to manipulate genome-wide datasets.
-    For population-genetic model, the distribution of fitness effects have so far been assumed to be constrained by
-    The DFE is assumed to be a gamma-distribution for deleterious mutations and an exponential for advantageous mutations, thus implicitly assuming a peak around 0.
-    The DFE predicted from fitness landscapes are very different, with peak is shifted toward negatively selected mutations.
-    Moreover, these methods estimate selection coefficient that are very negative on average, which is not biologically sensible.
-    Altogether, we should seek to reproduce our experiment with other clades, such as drosophila, birds and with for more shallow but wider phylogeny to determine the extent of reproducibilty of our results.
+    Phylogenetic codon models make two assumptions which have a negative impact on the prediction of the selection coefficient.
+    First, they are assuming no changes in effective population size while it has been established that population size has a major effect on selection dynamics\cite{lanfear_population_2014, platt_protein_2018}.
+    Estimating effective population size along with fitness landscape is possible\cite{latrille_inferring_2021}, but is for the moment too computational intensive to be performed genome-wide\cite{latrille_inferring_2021}.
+    Hybrid mutation-selection and $\omega$-based codon model could provide a way forward\cite{brevet_reconstructing_2021}.
+    Second, epistasis is not modeled while it can have drastic consequences on the change in fitness landscape\cite{latrille_quantifying_2021}.
+    Some models using Direct Coupling Analysis (DCA) can infer coevolution between sites, and thus provide a score of fitness of an amino-acid which depends on other sites of the sequence\cite{bisardi_modeling_2022}.
+    However, as SIFT scores, the scores given by DCA are not formalized in terms of selection coefficient and thus are hard to interpret in terms of population genetics, while also neglecting the underlying phylogeny and mutational biases.
+    Relaxing both assumptions are computationally intensive\cite{rodrigue_site_2005, kleinman_statistical_2010,latrille_inferring_2021}, and would require new mutation-selection models and optimization techniques to be able to manipulate genome-wide datasets.
+    In the other hand, in population-genetic codon models, there is no consensus on the expected shape of the DFE\cite{welch_divergence_2008, bataillon_effects_2014}, but it has indeed be found to be reliably constant between species\cite{castellano_comparison_2019}.
+    The model we used allows the inference of a full DFE (both positive and negative), but it has chosen to model the negative part of the DFE as a gamma distribution, and as an exponential one for the positive part.
+    However, when we aggregate SNPs that are expected to be strongly deleterious or strongly advantageous, the model struggles to fit their DFE to a gamma or an exponential distribution.
+    As a result, while the proportions of negative/weak/positive mutations stays reliable, the mean values for selection coefficients ($\Spop$) estimated by polyDFE become biologically absurd ($\Spop \ll -10^3$).
+    Such effect is not found for neutral SNPs and to method to accurately estimate the mean value of selection coefficients from SFS without assuming any shape for the DFE remains yet to be available.
 
-    % We should take that into account.
-    From a structural biology perspective, we found that proteins are not optimal, with a large proportion of mutations still toward more optimal amino acids.
-    Seen from another angle, it means that we could theoretically derive the fittest proteins using only the amino acid with the highest fitness.
-    We could then test whether fittest proteins are also thermodynamically more stable, leveraging recent developments able to compute efficiently and accurately the folding of proteins.
-    From an evolutionary biology perspective, we found that the fitness landscape is relatively stable across the mammalian evolution.
-    Mutations with $\Sphy<-1$ are more strongly purged, mutations with $1<\Sphy$ are more often segregating.
-    However, how to reliably quantify the overlap between phylogenetic and population-genetic methods?
-    The DFE has indeed be found to be reliably constant between species\cite{castellano_comparison_2019}.
-    Are deleterious mutations reliably purged only when selection overpowers drift?
-    Yes, mutations with predicted $-1<\Sphy<1$ are equivalent to neutral mutations.
+    Aside from methodological limitations, the mammalian case study might also not be representative of other clades.
+    Indeed, our dataset is quite convenient because of relatively small population sizes since a large amount of deleterious mutations are fixed, and thus, there is a lot of opportunities for non-adaptive positive selection to arise.
+    It would thus be of great interest to reproduce our experiment with other clades, such as \textit{drosophila} or birds which have higher effective population size.
+    It would also be interesting to have access to more shallow but wider phylogenies to increase the resolution of our predictions.
+    % Moreover, mammalian are less affected by codon usage
 
@@
     \textbf{Data and materials availability:}
-    Snakemake pipeline, analysis scripts and documentations are available at \href{https://github.com/ThibaultLatrille/SelCoeff}{github.com/ThibaultLatrille/SelCoeff}.
+    Snakemake pipeline, analysis scripts and documentation are available at \href{https://github.com/ThibaultLatrille/SelCoeff}{github.com/ThibaultLatrille/SelCoeff}.
 
@@
 
-    \subsection{Selection coefficient (S) in phylogeny-based method}
+    \subsection{Selection coefficient ($\Sphy$) in phylogeny-based method}
     \label{subsec:s-phylogeny-method}
@@
     \begin{equation}
-        q_{a \mapsto b}^{(i)} = \mu_{a \mapsto b} \proba_{a \mapsto b}^{(i)} = \mu_{a \mapsto b} \dfrac{F_b^{(i)} - F_a^{(i)}}{1 - \e^{F_a^{(i)} - F_b^{(i)}}}.\label{eq:equation}
+        \begin{dcases}
+            q_{a \mapsto b}^{(i)} & = 0 \text{ if codons $a$ and $b$ are more than one mutation away,} \\
+            q_{a \mapsto b}^{(i)} & = \mu_{a \mapsto b} \text{ if codons $a$ and $b$ are synonymous,} \\
+            q_{a \mapsto b}^{(i)} & = \mu_{a \mapsto b}  \mu_{a \mapsto b} \dfrac{F_b^{(i)} - F_a^{(i)}}{1 - \e^{F_a^{(i)} - F_b^{(i)}}} \text{ if codons $a$ and $b$ are non-synonymous}.
+        \end{dcases}
     \end{equation}
     Fitting the mutation-selection model on a sequence alignment leads to an estimation of the mutation rate matrix ($\UniDimArray{\mu}$) as well as the 20 amino-acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$.
-    We ran the Bayesian software \href{https://github.com/bayesiancook/bayescode}{BayesCode} on each protein-coding DNA alignment\cite{lartillot_phylobayes_2013, rodrigue_detecting_2017}.
+    The selection coefficient for a mutation from codon $a$ to codon $b$ at site $i$ is defined :
+    \begin{equation}
+        S_{a \mapsto b}^{(i)} = \Delta F^{(i)} = F^{(i)}_{b} - F^{(i)}_{a}.
+    \end{equation}
+    In the manuscript and the following material, the source ($a$) and target ($b$) codons as well as the site ($i$) are implicit and thus never explicitly written.
+    We ran the Bayesian software \href{https://github.com/bayesiancook/bayescode}{BayesCode} on each protein-coding DNA alignment\cite{lartillot_phylobayes_2013, rodrigue_detecting_2017, rodrigue_bayesian_2021}.
     Each Monte-Carlo Markov-Chain (MCMC) is run during $2000$ points, with a burn-in of $1000$ points, allowing to compute the mean amino-acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$ across the MCMC\@.
@@
     Stop codon mutants are also discarded.
-    For populations containing more than $8$ sampled individuals, the site-frequency spectrum (SFS) is sub-sampled down to $16$ chromosomes ($8$ diploid individuals) without replacement (hyper-geometric distribution) to alleviate the effect of different sampling depth in the $29$ populations.
+    For populations containing more than $8$ sampled individuals, the site-frequency spectrum (SFS) is subsampled down to $16$ chromosomes ($8$ diploid individuals) without replacement (hyper-geometric distribution) to alleviate the effect of different sampling depth in the $29$ populations.
     SNPs are polarized using the $3$ closest out-groups found in the OrthoMam alignment with est-usfs\cite{keightley_inferring_2018}.
-    The Snakemake pipeline for integrating polymorphism and divergence data uses custom scripts written in python 3.8.
+    The Snakemake pipeline for integrating polymorphism and divergence data uses custom scripts written in python 3.9.
 
@@
     \label{subsec:s-polymorphism-method}
-    The probability to sample allele at a given frequency (before fixation or extinction) is informative of its scaled selection coefficient at the population-scale ($\Spop$).
+    The probability to sample allele at a given frequency (before fixation or extinction) is informative of its scaled selection coefficient at the population scale ($\Spop$).
     Pooled across many sites, the SFS is thus informative on the underlying $\Spop$ of mutations, given we have a neutral expectation.
     In this configuration, a single $\Spop$ for all sampled mutations is biologically not realistic.
-    Accordingly, a distribution of fitness effects of mutations (DFE) is assumed, usually modelled as a continuous distribution\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009}.
+    Accordingly, a distribution of fitness effects of mutations (DFE) is assumed, usually modeled as a continuous distribution\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009}.
     In this study, we used the software polyDFE\cite{tataru_inference_2017, tataru_polydfe_2020}, for which the DFE ($\phi$) is given by a mixture of a $\Gamma$ and Exponential distributions, parameterized by $\Spop_d$ , $b$, $p_b$
@@
     and $f_{\Gamma}(x; m, b)$ is the density of the $\Gamma$ distribution with mean m and shape b, while $f_{e}(x; m)$ is the density of the Exponential distribution with mean $m$.
-    Once the DFE is fitted to the data, the proportion of advantageous ($\polyAdv$), nearly-neutral ($\polyNeutral$) and deleterious mutations ($\polyDel$) are given as:
+    Once the DFE is fitted to the data, the proportion of advantageous ($\PpolyAdv$), nearly-neutral ($\PpolyNeutral$) and deleterious mutations ($\PpolyDel$) are given as:
     \begin{align*}
-        \polyAdv &= p_b \int_{1}^{+\infty} f_{e}(\Spop; \Spop_b) \der \Spop  \\
-        \polyNeutral &= p_b \int_{0}^{1} f_{e}(\Spop; \Spop_b) \der \Spop + \left( 1 - p_b \right) \int_{0}^{1} f_{\Gamma}(\Spop; -\Spop_d, b) \der \Spop \\
-        \polyDel &= \left( 1 - p_b \right) \int_{1}^{+\infty} f_{\Gamma}(\Spop; -\Spop_d, b) \der \Spop
+        \PpolyAdv &= p_b \int_{1}^{+\infty} f_{e}(\Spop; \Spop_b) \der \Spop  \\
+        \PpolyNeutral &= p_b \int_{0}^{1} f_{e}(\Spop; \Spop_b) \der \Spop + \left( 1 - p_b \right) \int_{0}^{1} f_{\Gamma}(\Spop; -\Spop_d, b) \der \Spop \\
+        \PpolyDel &= \left( 1 - p_b \right) \int_{1}^{+\infty} f_{\Gamma}(\Spop; -\Spop_d, b) \der \Spop
     \end{align*}
@@
     \end{align*}
-    PolyDFE requires one SFS for non-synonymous mutations and one for synonymous mutations (neutral expectation), as well as the total mutation rate (mutation rate per site multiplied by number of sites) on which each SFS has been sampled.
-    The total mutation rate for each SFS is thus obtained using the following three-steps procedure.
+    PolyDFE requires one SFS for non-synonymous mutations and one for synonymous mutations (neutral expectation), as well as the total mutation rate (mutation rate per site multiplied by the number of sites) on which each SFS has been sampled.
+    The number of sites for each SFS is thus obtained using the following four-step procedure.
     First, for each gene, the reference DNA sequence is adjusted with ancestral and fixed polymorphism for each population.
     Second, from this reconstructed sequence, all possible mutations are computed, weighted by the mutation rate between nucleotide estimated at the phylogenetic scale $\UniDimArray{\mu}$.
-    Third, these possible mutation are then classified whether they are synonymous or non-synonymous (stop mutations are excluded), non-synonymous mutations are then also classified depending on their selection coefficient ($\Sphy$).
-    From the SFS and the total mutation rate for the both synonymous and for the class of non-synonymous, polyDFE estimates the DFE $\phi$ using maximum likelihood.
+    Third, these possible mutations are then classified whether they are synonymous or non-synonymous (stop mutations are excluded), non-synonymous mutations are then also classified depending on their selection coefficient ($\Sphy$).
+    Fourth, the number of sites for each class of selection coefficient is then computed as the total number of sites across the genome weighted by the ratio of the aggregated mutations rates falling in the class over the total mutation rate for all possible mutations.
+    From the SFS and the number of sites for the both synonymous and for the class of non-synonymous, polyDFE estimates parameters of the DFE $\phi \left( \Spop; \Spop_d , b, p_b, \Spop_b \right)$ using maximum likelihood.
 

### 2022-04-22 manuscript/supp-mat.tex
Manuscript by JJ and TL.

@@
 
+\newcommand{\UniDimArray}[1]{\bm{#1}}
+\newcommand{\BiDimArray}[1]{\bm{#1}}
+\DeclareMathOperator{\E}{\mathbb{E}}
+\DeclareMathOperator{\Var}{\mathrm{Var}}
+\newcommand{\der}{\mathrm{d}}
+\newcommand{\e}{\mathrm{e}}
+\newcommand{\avg}[1]{\left< #1 \right>} % for average
+\newcommand{\Ne}{N_{\mathrm{e}}}
 \newcommand{\proba}{\mathbb{P}}
 \newcommand{\pfix}{\proba_{\mathrm{fix}}}
+
+\newcommand{\Sphy}{S}
+\newcommand{\SphyMean}{\overline{\Sphy}}
+\newcommand{\divStrongDel}{\Sphy < -3}
+\newcommand{\divDel}{-3 < \Sphy < -1}
+\newcommand{\divWeakDel}{-1 < \Sphy < 0}
+\newcommand{\divWeakAdv}{0 < \Sphy < 1}
+\newcommand{\divAdv}{ \Sphy > 1}
+\newcommand{\PdivStrongDel}{\proba \left[ \divStrongDel \right]}
+\newcommand{\PdivDel}{\proba \left[ \divDel \right]}
+\newcommand{\PdivWeakDel}{\proba \left[ \divWeakDel \right]}
+\newcommand{\PdivWeakAdv}{\proba \left[ \divWeakAdv \right]}
+\newcommand{\PdivAdv}{\proba \left[ \divAdv \right]}
+
 \newcommand{\Spop}{\beta}
 \newcommand{\SpopMean}{\overline{\Spop}}
-\newcommand{\Sphy}{S}
-\newcommand{\SphyMean}{\overline{\Sphy}}
-\newcommand{\polyDel}{\proba \left[ {\Spop < -1} \right]}
-\newcommand{\polyNeutral}{\proba \left[ -1 < \Spop < 1 \right]}
-\newcommand{\polyAdv}{\proba \left[ 1 < \Spop  \right]}
+\newcommand{\polyDel}{\Spop < -1}
+\newcommand{\polyNeutral}{-1 < \Spop < 1}
+\newcommand{\polyAdv}{ \Spop > 1}
+\newcommand{\PpolyDel}{\proba \left[ \polyDel \right]}
+\newcommand{\PpolyNeutral}{\proba \left[ \polyNeutral \right]}
+\newcommand{\PpolyAdv}{\proba \left[ \polyAdv \right]}
 
@@
 
+    In BayesCode (\url{https://github.com/ThibaultLatrille/bayescode}), mutation-selection codon models are obtained by running \textit{mutselomega} for 2000 points of MCMC with the options:
+    \begin{scriptsize}
+        \begin{verbatim}
+        mutselomega ---omegashift 0.0 --ncat 30 -a my_alignment.phy -t my_tree.newick -u 2000 my_genename
+        \end{verbatim}
+    \end{scriptsize}
+    The collection of site-specific fitness profiles ($\UniDimArray{F^{(i)}}, \forall i$) are then obtained by running \textit{readmutselomega}, reading 1000 points of MCMC (first 1000 are considered as burn-in) with the options:
+    \begin{scriptsize}
+        \begin{verbatim}
+        readmutselomega --every 1 --until 2000 --burnin 1000 --ss my_genename
+        \end{verbatim}
+    \end{scriptsize}
+    The gene-specific mutation matrix ($\UniDimArray{\mu}$) is also obtained by running \textit{readmutselomega}, reading 1000 points of MCMC (first 1000 are considered as burn-in) with the options:
+    \begin{scriptsize}
+        \begin{verbatim}
+        readmutselomega --every 1 --until 2000 --burnin 1000 --nuc my_genename
+        \end{verbatim}
+    \end{scriptsize}
+
     \subsection{Summary table}
+
     \begin{center}
@@
             \toprule
-            Population                     & Species             & Tajima $\theta_{\pi}$ & $\mathbb{P}_{obs}[1<S]$ & $\mathbb{P} [ 1<\beta ]$ & $\mathbb{P} [ 1<\beta  | 1<S]$ \\
+            Population                     & Species             & Tajima $\theta$ & $\proba_{obs}[\divAdv]$ & $\PpolyAdv$ & $\proba [ \polyAdv | \divAdv]$ \\
             \midrule
@@
     \end{center}
+    \begin{itemize}
+        \item Tajima $\theta$ is the synonymous diversity.
+        \item $\proba_{obs}[\divAdv]$ is the proportion of SNPs observed with a selection coefficient at the phylogenetic scale ($\Sphy$) larger than 1.
+        \item $\PpolyAdv $ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) larger than 1, estimated for the whole genome.
+        \item $\proba [ \polyAdv | \divAdv]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) larger than 1, estimated of SNPs observed with a selection coefficient at the phylogenetic scale ($\Sphy$) larger than 1.
+    \end{itemize}
 
@@
     \subsubsection{Proportion of nearly-neutral mutations ($\polyNeutral$)}
+
     \begin{minipage}{0.32\linewidth}
@@
 
+    \begin{itemize}
+        \item $\ \proba [ \polyNeutral ]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) between -1 and 1, estimated for the whole genome.
+        \item $\ \proba [ \polyNeutral | \divWeakDel]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) between -1 and 1, estimated of SNPs observed with a selection coefficient at the phylogenetic scale ($\Sphy$) between -1 and 0.
+        \item $\ \proba [ \polyNeutral | \divWeakAdv ]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) between -1 and 1, estimated of SNPs observed with a selection coefficient at the phylogenetic scale ($\Sphy$) between 0 and 1.
+    \end{itemize}
+
     \subsubsection{Proportion of deleterious mutations ($\polyDel$)}
+
     \begin{minipage}{0.32\linewidth}
@@
 
+    \begin{itemize}
+        \item $\ \proba [ \polyDel ]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) lower than -1, estimated for the whole genome.
+        \item $\ \proba [ \polyDel | \divDel]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) lower than -1, estimated of SNPs observed with a selection coefficient at the phylogenetic scale ($\Sphy$) between -3 and -3.
+        \item $\ \proba [ \polyDel | \divStrongDel ]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) lower than -1, estimated of SNPs observed with a selection coefficient at the phylogenetic scale ($\Sphy$) lower than -3.
+    \end{itemize}
+
     \subsubsection{Proportion of advantageous mutations ($\polyAdv$)}
+
     \begin{minipage}{0.32\linewidth}
@@
 
+    \begin{itemize}
+        \item $\ \proba [ \polyAdv  ]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) greater than 1, estimated for the whole genome.
+        \item $\ \proba [ \polyAdv | \divAdv] $ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) greater than 1, estimated of SNPs observed with a selection coefficient at the phylogenetic scale ($\Sphy$) greater than 1.
+    \end{itemize}
+
     \input{include-MutSel-non-adaptive}
@@
 
-    \section{Site-specific codon models.}
+    \section{Site-specific $\omega$-based codon models.}
+    The $61$-by-$61$ codon substitution matrix ($\UniDimArray{q^{(i)}}$) at site $i$ is defined entirely by the mutation matrix ($\UniDimArray{\mu}$), $\omega^{(i)}$ and the genetic code:
+    \begin{equation}
+        \begin{dcases}
+            q_{a \mapsto b}^{(i)} & = 0 \text{ if codons $a$ and $b$ are more than one mutation away,} \\
+            q_{a \mapsto b}^{(i)} & = \mu_{a \mapsto b} \text{ if codons $a$ and $b$ are synonymous,} \\
+            q_{a \mapsto b}^{(i)} & = \omega^{(i)} \mu_{a \mapsto b} \text{ if codons $a$ and $b$ are non-synonymous}.
+        \end{dcases}
+    \end{equation}
+    By definition of the instantaneous rate matrix, the sum of the entries in each row of the codon substitution rate matrix $\UniDimArray{q}$ is equal to $0$, giving the diagonal entries:
+    \begin{equation}
+        q_{a \mapsto b}^{(i)}= - \sum\limits_{b \neq a, b = 1}^{61} q_{a \mapsto b}^{(i)}.
+    \end{equation}
+
+    In BayesCode (\url{https://github.com/ThibaultLatrille/bayescode}), $\omega$-based site-specific codon models are obtained by running \textit{mutselomega} with the options:
+    \begin{scriptsize}
+        \begin{verbatim}
+        mutselomega --omegashift 0.0 --freeomega --omegancat 30 --flatfitness -a my_alignment.phy -t my_tree.newick -u 2000 my_genename
+        \end{verbatim}
+    \end{scriptsize}
+    The mean value of $\omega$ per site is then obtained by running \textit{readmutselomega} with the options:
+    \begin{scriptsize}
+        \begin{verbatim}
+        readmutselomega --every 1 --until 2000 --burnin 1000 -c 0.025 my_genename
+        \end{verbatim}
+    \end{scriptsize}
+
     \input{include-Omega-adaptive}

### 2022-04-22 scripts/libraries.py

@@ -51,7 +51,7 @@ codontable.update({
 confidence_interval = namedtuple('confidence_interval', ['low', 'mean', 'up'])
 sfs_weight = {"watterson": lambda i, n: 1.0 / i, "tajima": lambda i, n: n - i, "fay_wu": lambda i, n: i}
 polydfe_cat_dico = {
-    "P-Ssup0": "$\\mathbb{P} [ 1<\\beta ]$",
+    "P-Ssup0": "$\\mathbb{P} [ \\beta > 1 ]$",
     "P-Seq0": "$\\mathbb{P} [ -1<\\beta<1 ]$",
     "P-Sinf0": "$\\mathbb{P} [ \\beta<-1 ]$",
 }
@@ -299,33 +299,18 @@ def extend_pop(p, sample):
         return f"{sample[p]} ({fp})"
 
 
-def set_species(df):
-    df["species"] = df.apply(lambda r: r["species"].replace("_", " "), axis=1)
-    df["species"] = df.apply(lambda r: "Ovis orientalis" if r["pop"] == "IROO" else r["species"], axis=1)
-    df["species"] = df.apply(lambda r: "Ovis vignei" if r["pop"] == "IROV" else r["species"], axis=1)
-    df["species"] = df.apply(lambda r: "Capra aegagrus" if r["pop"] == "IRCA" else r["species"], axis=1)
-    return df
-
-
 def sample_list_dico(sample_list_path):
     df = pd.read_csv(sample_list_path, sep='\t')
     df["pop"] = df.apply(lambda r: format_pop(r["SampleName"].replace("_", " ")), axis=1)
-    df["species"] = df.apply(lambda r: r["Species"].replace("_", " "), axis=1)
-    df = set_species(df)
-    dico_sample = {r["pop"]: r["Location"] for _, r in df.iterrows()}
-    df["ext_pop"] = df.apply(lambda r: extend_pop(r["pop"], dico_sample), axis=1)
-    dico_sample = {
-        r["pop"]: r["ext_pop"] + (f' - {r["species"]}' if r["species"].split(" ")[0] in ["Capra", "Ovis"] else "") for
-        _, r in df.iterrows()}
+    dico_sample = {r["pop"]: r["DisplayName"] for _, r in df.iterrows()}
     return dico_sample
 
 
 def sort_df(df, sample_list_path):
     df = df.iloc[df.apply(lambda r: sp_sorted(format_pop(r["pop"]), r["species"]), axis=1).argsort()]
-    df = set_species(df)
[…]

### 2022-04-22 scripts/plot_heatmap.py

@@ -11,8 +11,8 @@ def open_tsv(filepath):
     return ddf
 
 
-def plot_stack_param(list_pops, df_all, title, output):
-    fig, ax = plt.subplots(figsize=(1920 / my_dpi, 640 / my_dpi), dpi=my_dpi)
+def plot_stack_param(list_pops, df_all, pop_colors, title, output):
+    fig, ax = plt.subplots(figsize=(1920 / my_dpi, 780 / my_dpi), dpi=my_dpi)
     x_pos = range(len(list_pops))
     hatches_list = ['', '', '//']
     colors_list = ["black", "silver", "white"]
@@ -22,13 +22,21 @@ def plot_stack_param(list_pops, df_all, title, output):
         y = df_all[param].values
         ax.bar(x_pos, y, bottom=bottom, edgecolor=edgecolors_list[p_i], color=colors_list[p_i], hatch=hatches_list[p_i])
         bottom += y
-    ax.set_title(title)
-    ax.set_xlabel("Population")
+
+    if title == 'All':
+        ax.set_title("Estimation for all SNPs:", loc='left')
+    else:
+        ax.set_title("Estimation for SNPs with " + title + ":", loc='left')
+
+    ax.set_xlabel("Populations")
     ax.set_ylabel("Proportion estimated")
     ax.set_xticks(x_pos)
     ax.set_ylim((0, 1))
     ax.set_xticklabels(list_pops)
-    plt.setp(ax.get_xticklabels(), rotation=45, ha="right", rotation_mode="anchor")
+    ax.tick_params(top=True, bottom=False, labeltop=True, labelbottom=False)
+    plt.setp(ax.get_xticklabels(), rotation=-45, ha="right", rotation_mode="anchor")
+    for ticklabel, tickcolor in zip(plt.gca().get_xticklabels(), pop_colors):
+        ticklabel.set_color(tickcolor)
     plt.tight_layout()
     plt.savefig(output)
     plt.close("all")
@@ -43,18 +51,26 @@ def main(args):
     df_merge["H_fay_wu"] = df_merge["tajima"] - df_merge["fay_wu"]
     d_dict = {"watterson": "Watterson $\\theta_W$"}
     d_dict.update(polydfe_cat_dico)
+
+    df_merge = df_merge.iloc[df_merge.apply(lambda r: sp_sorted(format_pop(r["pop"]), r["species"]), axis=1).argsort()]
     df_merge.to_csv(args.output, sep="\t", index=False)
[…]

### 2022-05-16 manuscript/include-MutSel-non-adaptive.tex
Ancestral reconstruction with codon models

@@
 \begin{center}
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/results/Theta.MutSel.all.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/results/Theta.MutSel.neg-strong.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/results/Theta.MutSel.neg.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/results/Theta.MutSel.neg-weak.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/results/Theta.MutSel.pos-weak.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/results/Theta.MutSel.pos.stacked.pdf}
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.MutSel.all.stacked.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.MutSel.neg-strong.stacked.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.MutSel.neg.stacked.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.MutSel.neg-weak.stacked.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.MutSel.pos-weak.stacked.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.MutSel.pos.stacked.pdf}
 
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Bos_taurus.IRBT.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Bos_taurus.IRBT.MutSel.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Bos_taurus.IRBT.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Bos_taurus.IRBT.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Bos_taurus.IRBT.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Bos_taurus.IRBT.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Bos_taurus.IRBT.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Bos_taurus.IRBT.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Bos_taurus.UGBT.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Bos_taurus.UGBT.MutSel.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Bos_taurus.UGBT.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Bos_taurus.UGBT.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Bos_taurus.UGBT.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Bos_taurus.UGBT.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Bos_taurus.UGBT.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Bos_taurus.UGBT.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Canis_familiaris.dogs.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Canis_familiaris.dogs.MutSel.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Canis_familiaris.dogs.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Canis_familiaris.dogs.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Canis_familiaris.dogs.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Canis_familiaris.dogs.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Canis_familiaris.dogs.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Canis_familiaris.dogs.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Capra_hircus.AUCH.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.AUCH.MutSel.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.AUCH.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.AUCH.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Capra_hircus.AUCH.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.AUCH.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.AUCH.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.AUCH.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Capra_hircus.FRCH.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.FRCH.MutSel.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.FRCH.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.FRCH.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Capra_hircus.FRCH.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.FRCH.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.FRCH.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.FRCH.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Capra_hircus.IRCA.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.IRCA.MutSel.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.IRCA.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.IRCA.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Capra_hircus.IRCA.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.IRCA.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.IRCA.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.IRCA.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Capra_hircus.IRCH.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.IRCH.MutSel.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.IRCH.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.IRCH.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Capra_hircus.IRCH.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.IRCH.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.IRCH.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.IRCH.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Capra_hircus.ITCH.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.ITCH.MutSel.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.ITCH.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.ITCH.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Capra_hircus.ITCH.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.ITCH.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.ITCH.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.ITCH.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Capra_hircus.MOCH.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.MOCH.MutSel.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.MOCH.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.MOCH.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Capra_hircus.MOCH.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.MOCH.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.MOCH.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.MOCH.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Chlorocebus_sabaeus.Barbados.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Barbados.MutSel.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Barbados.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Barbados.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Chlorocebus_sabaeus.Barbados.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Barbados.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Barbados.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Barbados.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Chlorocebus_sabaeus.Central_African_Republic.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Central_African_Republic.MutSel.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Chlorocebus_sabaeus.Central_African_Republic.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Central_African_Republic.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Chlorocebus_sabaeus.Ethiopia.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Ethiopia.MutSel.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Chlorocebus_sabaeus.Ethiopia.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Ethiopia.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Chlorocebus_sabaeus.Gambia.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Gambia.MutSel.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Gambia.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Gambia.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Chlorocebus_sabaeus.Gambia.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Gambia.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Gambia.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Gambia.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Chlorocebus_sabaeus.Kenya.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Kenya.MutSel.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Kenya.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Kenya.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Chlorocebus_sabaeus.Kenya.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Kenya.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Kenya.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Kenya.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Chlorocebus_sabaeus.Nevis.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Nevis.MutSel.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Nevis.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Nevis.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Chlorocebus_sabaeus.Nevis.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Nevis.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Nevis.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Nevis.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Chlorocebus_sabaeus.Saint_Kitts.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Saint_Kitts.MutSel.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Saint_Kitts.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Saint_Kitts.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Chlorocebus_sabaeus.Saint_Kitts.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Saint_Kitts.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Saint_Kitts.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Saint_Kitts.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Chlorocebus_sabaeus.South_Africa.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.South_Africa.MutSel.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.South_Africa.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.South_Africa.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Chlorocebus_sabaeus.South_Africa.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.South_Africa.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.South_Africa.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.South_Africa.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Chlorocebus_sabaeus.Zambia.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Zambia.MutSel.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Zambia.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Zambia.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Chlorocebus_sabaeus.Zambia.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Zambia.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Zambia.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Zambia.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Equus_caballus.up.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Equus_caballus.up.MutSel.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Equus_caballus.up.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Equus_caballus.up.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Equus_caballus.up.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Equus_caballus.up.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Equus_caballus.up.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Equus_caballus.up.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Homo_sapiens.AFR.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Homo_sapiens.AFR.MutSel.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.AFR.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.AFR.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Homo_sapiens.AFR.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.AFR.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.AFR.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.AFR.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Homo_sapiens.AMR.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Homo_sapiens.AMR.MutSel.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.AMR.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.AMR.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Homo_sapiens.AMR.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.AMR.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.AMR.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.AMR.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Homo_sapiens.EAS.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Homo_sapiens.EAS.MutSel.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.EAS.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.EAS.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Homo_sapiens.EAS.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.EAS.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.EAS.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.EAS.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Homo_sapiens.EUR.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Homo_sapiens.EUR.MutSel.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.EUR.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.EUR.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Homo_sapiens.EUR.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.EUR.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.EUR.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.EUR.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Homo_sapiens.SAS.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Homo_sapiens.SAS.MutSel.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.SAS.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.SAS.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Homo_sapiens.SAS.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.SAS.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.SAS.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.SAS.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Ovis_aries.IROA.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Ovis_aries.IROA.MutSel.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROA.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROA.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Ovis_aries.IROA.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.IROA.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROA.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROA.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Ovis_aries.IROO.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Ovis_aries.IROO.MutSel.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROO.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROO.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Ovis_aries.IROO.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.IROO.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROO.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROO.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Ovis_aries.IROV.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Ovis_aries.IROV.MutSel.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROV.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROV.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Ovis_aries.IROV.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.IROV.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROV.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROV.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Ovis_aries.ISGC.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Ovis_aries.ISGC.MutSel.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.ISGC.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.ISGC.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Ovis_aries.ISGC.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.ISGC.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.ISGC.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.ISGC.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Ovis_aries.MOOA.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Ovis_aries.MOOA.MutSel.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.MOOA.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.MOOA.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Ovis_aries.MOOA.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.MOOA.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.MOOA.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.MOOA.MutSel.polyDFE_C.pdf}
 \end{minipage}

### 2022-05-16 manuscript/include-Omega-adaptive.tex
Ancestral reconstruction with codon models

@@
 \begin{center}
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC/results/Theta.Omega.P-Sinf0.heatmap.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC/results/Theta.Omega.P-Seq0.heatmap.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC/results/Theta.Omega.P-Ssup0.heatmap.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC/results/Theta.Omega.all.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC/results/Theta.Omega.neg-strong.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC/results/Theta.Omega.neg.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC/results/Theta.Omega.neg-weak.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC/results/Theta.Omega.pos-weak.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC/results/Theta.Omega.pos.stacked.pdf}
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.Omega.P-Sinf0.heatmap.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.Omega.P-Seq0.heatmap.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.Omega.P-Ssup0.heatmap.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.Omega.all.stacked.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.Omega.neg-strong.stacked.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.Omega.neg.stacked.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.Omega.neg-weak.stacked.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.Omega.pos-weak.stacked.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.Omega.pos.stacked.pdf}
 \end{center}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Bos_taurus.IRBT.Omega.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Bos_taurus.IRBT.Omega.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Bos_taurus.IRBT.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Bos_taurus.IRBT.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Bos_taurus.IRBT.Omega.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Bos_taurus.IRBT.Omega.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Bos_taurus.IRBT.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Bos_taurus.IRBT.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Bos_taurus.UGBT.Omega.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Bos_taurus.UGBT.Omega.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Bos_taurus.UGBT.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Bos_taurus.UGBT.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Bos_taurus.UGBT.Omega.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Bos_taurus.UGBT.Omega.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Bos_taurus.UGBT.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Bos_taurus.UGBT.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Canis_familiaris.dogs.Omega.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Canis_familiaris.dogs.Omega.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Canis_familiaris.dogs.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Canis_familiaris.dogs.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Canis_familiaris.dogs.Omega.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Canis_familiaris.dogs.Omega.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Canis_familiaris.dogs.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Canis_familiaris.dogs.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Capra_hircus.AUCH.Omega.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.AUCH.Omega.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Capra_hircus.AUCH.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.AUCH.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Capra_hircus.AUCH.Omega.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.AUCH.Omega.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Capra_hircus.AUCH.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.AUCH.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Capra_hircus.FRCH.Omega.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.FRCH.Omega.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Capra_hircus.FRCH.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.FRCH.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Capra_hircus.FRCH.Omega.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.FRCH.Omega.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Capra_hircus.FRCH.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.FRCH.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Capra_hircus.IRCA.Omega.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.IRCA.Omega.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Capra_hircus.IRCA.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.IRCA.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Capra_hircus.IRCA.Omega.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.IRCA.Omega.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Capra_hircus.IRCA.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.IRCA.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Capra_hircus.IRCH.Omega.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.IRCH.Omega.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Capra_hircus.IRCH.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.IRCH.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Capra_hircus.IRCH.Omega.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.IRCH.Omega.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Capra_hircus.IRCH.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.IRCH.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Capra_hircus.ITCH.Omega.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.ITCH.Omega.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Capra_hircus.ITCH.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.ITCH.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Capra_hircus.ITCH.Omega.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.ITCH.Omega.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Capra_hircus.ITCH.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.ITCH.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Capra_hircus.MOCH.Omega.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.MOCH.Omega.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Capra_hircus.MOCH.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.MOCH.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Capra_hircus.MOCH.Omega.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.MOCH.Omega.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Capra_hircus.MOCH.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.MOCH.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Chlorocebus_sabaeus.Barbados.Omega.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Barbados.Omega.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Chlorocebus_sabaeus.Barbados.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Barbados.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Chlorocebus_sabaeus.Barbados.Omega.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Barbados.Omega.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Chlorocebus_sabaeus.Barbados.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Barbados.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Chlorocebus_sabaeus.Central_African_Republic.Omega.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Central_African_Republic.Omega.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Chlorocebus_sabaeus.Central_African_Republic.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Central_African_Republic.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Chlorocebus_sabaeus.Central_African_Republic.Omega.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Central_African_Republic.Omega.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Chlorocebus_sabaeus.Central_African_Republic.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Central_African_Republic.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Chlorocebus_sabaeus.Ethiopia.Omega.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Ethiopia.Omega.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Chlorocebus_sabaeus.Ethiopia.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Ethiopia.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Chlorocebus_sabaeus.Ethiopia.Omega.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Ethiopia.Omega.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Chlorocebus_sabaeus.Ethiopia.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Ethiopia.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Chlorocebus_sabaeus.Gambia.Omega.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Gambia.Omega.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Chlorocebus_sabaeus.Gambia.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Gambia.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Chlorocebus_sabaeus.Gambia.Omega.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Gambia.Omega.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Chlorocebus_sabaeus.Gambia.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Gambia.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Chlorocebus_sabaeus.Kenya.Omega.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Kenya.Omega.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Chlorocebus_sabaeus.Kenya.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Kenya.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Chlorocebus_sabaeus.Kenya.Omega.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Kenya.Omega.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Chlorocebus_sabaeus.Kenya.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Kenya.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Chlorocebus_sabaeus.Nevis.Omega.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Nevis.Omega.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Chlorocebus_sabaeus.Nevis.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Nevis.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Chlorocebus_sabaeus.Nevis.Omega.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Nevis.Omega.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Chlorocebus_sabaeus.Nevis.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Nevis.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Chlorocebus_sabaeus.Saint_Kitts.Omega.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Saint_Kitts.Omega.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Chlorocebus_sabaeus.Saint_Kitts.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Saint_Kitts.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Chlorocebus_sabaeus.Saint_Kitts.Omega.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Saint_Kitts.Omega.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Chlorocebus_sabaeus.Saint_Kitts.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Saint_Kitts.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Chlorocebus_sabaeus.South_Africa.Omega.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.South_Africa.Omega.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Chlorocebus_sabaeus.South_Africa.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.South_Africa.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Chlorocebus_sabaeus.South_Africa.Omega.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.South_Africa.Omega.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Chlorocebus_sabaeus.South_Africa.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.South_Africa.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Chlorocebus_sabaeus.Zambia.Omega.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Zambia.Omega.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Chlorocebus_sabaeus.Zambia.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Zambia.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Chlorocebus_sabaeus.Zambia.Omega.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Zambia.Omega.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Chlorocebus_sabaeus.Zambia.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Zambia.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Equus_caballus.up.Omega.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Equus_caballus.up.Omega.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Equus_caballus.up.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Equus_caballus.up.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Equus_caballus.up.Omega.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Equus_caballus.up.Omega.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Equus_caballus.up.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Equus_caballus.up.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Homo_sapiens.AFR.Omega.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Homo_sapiens.AFR.Omega.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Homo_sapiens.AFR.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.AFR.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Homo_sapiens.AFR.Omega.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.AFR.Omega.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Homo_sapiens.AFR.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.AFR.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Homo_sapiens.AMR.Omega.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Homo_sapiens.AMR.Omega.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Homo_sapiens.AMR.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.AMR.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Homo_sapiens.AMR.Omega.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.AMR.Omega.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Homo_sapiens.AMR.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.AMR.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Homo_sapiens.EAS.Omega.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Homo_sapiens.EAS.Omega.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Homo_sapiens.EAS.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.EAS.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Homo_sapiens.EAS.Omega.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.EAS.Omega.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Homo_sapiens.EAS.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.EAS.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Homo_sapiens.EUR.Omega.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Homo_sapiens.EUR.Omega.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Homo_sapiens.EUR.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.EUR.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Homo_sapiens.EUR.Omega.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.EUR.Omega.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Homo_sapiens.EUR.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.EUR.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Homo_sapiens.SAS.Omega.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Homo_sapiens.SAS.Omega.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Homo_sapiens.SAS.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.SAS.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Homo_sapiens.SAS.Omega.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.SAS.Omega.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Homo_sapiens.SAS.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.SAS.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Ovis_aries.IROA.Omega.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Ovis_aries.IROA.Omega.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Ovis_aries.IROA.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROA.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Ovis_aries.IROA.Omega.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.IROA.Omega.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Ovis_aries.IROA.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROA.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Ovis_aries.IROO.Omega.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Ovis_aries.IROO.Omega.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Ovis_aries.IROO.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROO.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Ovis_aries.IROO.Omega.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.IROO.Omega.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Ovis_aries.IROO.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROO.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Ovis_aries.IROV.Omega.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Ovis_aries.IROV.Omega.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Ovis_aries.IROV.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROV.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Ovis_aries.IROV.Omega.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.IROV.Omega.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Ovis_aries.IROV.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROV.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Ovis_aries.ISGC.Omega.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Ovis_aries.ISGC.Omega.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Ovis_aries.ISGC.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.ISGC.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Ovis_aries.ISGC.Omega.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.ISGC.Omega.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Ovis_aries.ISGC.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.ISGC.Omega.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0/snps.Ovis_aries.MOOA.Omega.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Ovis_aries.MOOA.Omega.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Ovis_aries.MOOA.Omega-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.MOOA.Omega-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0/DFE.Ovis_aries.MOOA.Omega.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.MOOA.Omega.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC/analysis/Ovis_aries.MOOA.Omega.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.MOOA.Omega.polyDFE_C.pdf}
 \end{minipage}

### 2022-05-16 manuscript/include-SIFT-non-adaptive.tex
Ancestral reconstruction with codon models

@@
 \begin{center}
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/results/Theta.SIFT.P-Sinf0.heatmap.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/results/Theta.SIFT.P-Seq0.heatmap.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/results/Theta.SIFT.P-Ssup0.heatmap.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/results/Theta.SIFT.all.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/results/Theta.SIFT.neg-strong.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/results/Theta.SIFT.neg.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/results/Theta.SIFT.neg-weak.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/results/Theta.SIFT.pos-weak.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/results/Theta.SIFT.pos.stacked.pdf}
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.SIFT.P-Sinf0.heatmap.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.SIFT.P-Seq0.heatmap.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.SIFT.P-Ssup0.heatmap.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.SIFT.all.stacked.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.SIFT.neg-strong.stacked.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.SIFT.neg.stacked.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.SIFT.neg-weak.stacked.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.SIFT.pos-weak.stacked.pdf} \\
+    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.SIFT.pos.stacked.pdf}
 \end{center}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Bos_taurus.IRBT.SIFT.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Bos_taurus.IRBT.SIFT.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Bos_taurus.IRBT.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Bos_taurus.IRBT.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Bos_taurus.IRBT.SIFT.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Bos_taurus.IRBT.SIFT.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Bos_taurus.IRBT.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Bos_taurus.IRBT.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Bos_taurus.UGBT.SIFT.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Bos_taurus.UGBT.SIFT.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Bos_taurus.UGBT.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Bos_taurus.UGBT.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Bos_taurus.UGBT.SIFT.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Bos_taurus.UGBT.SIFT.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Bos_taurus.UGBT.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Bos_taurus.UGBT.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Canis_familiaris.dogs.SIFT.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Canis_familiaris.dogs.SIFT.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Canis_familiaris.dogs.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Canis_familiaris.dogs.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Canis_familiaris.dogs.SIFT.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Canis_familiaris.dogs.SIFT.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Canis_familiaris.dogs.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Canis_familiaris.dogs.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Capra_hircus.AUCH.SIFT.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.AUCH.SIFT.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.AUCH.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.AUCH.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Capra_hircus.AUCH.SIFT.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.AUCH.SIFT.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.AUCH.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.AUCH.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Capra_hircus.FRCH.SIFT.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.FRCH.SIFT.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.FRCH.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.FRCH.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Capra_hircus.FRCH.SIFT.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.FRCH.SIFT.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.FRCH.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.FRCH.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Capra_hircus.IRCA.SIFT.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.IRCA.SIFT.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.IRCA.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.IRCA.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Capra_hircus.IRCA.SIFT.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.IRCA.SIFT.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.IRCA.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.IRCA.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Capra_hircus.IRCH.SIFT.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.IRCH.SIFT.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.IRCH.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.IRCH.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Capra_hircus.IRCH.SIFT.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.IRCH.SIFT.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.IRCH.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.IRCH.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Capra_hircus.ITCH.SIFT.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.ITCH.SIFT.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.ITCH.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.ITCH.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Capra_hircus.ITCH.SIFT.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.ITCH.SIFT.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.ITCH.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.ITCH.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Capra_hircus.MOCH.SIFT.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.MOCH.SIFT.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.MOCH.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.MOCH.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Capra_hircus.MOCH.SIFT.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.MOCH.SIFT.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Capra_hircus.MOCH.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.MOCH.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Chlorocebus_sabaeus.Barbados.SIFT.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Barbados.SIFT.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Barbados.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Barbados.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Chlorocebus_sabaeus.Barbados.SIFT.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Barbados.SIFT.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Barbados.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Barbados.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Chlorocebus_sabaeus.Central_African_Republic.SIFT.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Central_African_Republic.SIFT.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Central_African_Republic.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Central_African_Republic.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Chlorocebus_sabaeus.Central_African_Republic.SIFT.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Central_African_Republic.SIFT.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Central_African_Republic.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Central_African_Republic.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Chlorocebus_sabaeus.Ethiopia.SIFT.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Ethiopia.SIFT.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Ethiopia.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Ethiopia.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Chlorocebus_sabaeus.Ethiopia.SIFT.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Ethiopia.SIFT.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Ethiopia.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Ethiopia.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Chlorocebus_sabaeus.Gambia.SIFT.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Gambia.SIFT.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Gambia.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Gambia.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Chlorocebus_sabaeus.Gambia.SIFT.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Gambia.SIFT.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Gambia.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Gambia.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Chlorocebus_sabaeus.Kenya.SIFT.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Kenya.SIFT.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Kenya.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Kenya.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Chlorocebus_sabaeus.Kenya.SIFT.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Kenya.SIFT.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Kenya.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Kenya.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Chlorocebus_sabaeus.Nevis.SIFT.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Nevis.SIFT.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Nevis.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Nevis.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Chlorocebus_sabaeus.Nevis.SIFT.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Nevis.SIFT.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Nevis.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Nevis.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Chlorocebus_sabaeus.Saint_Kitts.SIFT.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Saint_Kitts.SIFT.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Saint_Kitts.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Saint_Kitts.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Chlorocebus_sabaeus.Saint_Kitts.SIFT.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Saint_Kitts.SIFT.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Saint_Kitts.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Saint_Kitts.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Chlorocebus_sabaeus.South_Africa.SIFT.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.South_Africa.SIFT.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.South_Africa.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.South_Africa.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Chlorocebus_sabaeus.South_Africa.SIFT.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.South_Africa.SIFT.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.South_Africa.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.South_Africa.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Chlorocebus_sabaeus.Zambia.SIFT.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Zambia.SIFT.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Zambia.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Zambia.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Chlorocebus_sabaeus.Zambia.SIFT.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Zambia.SIFT.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Chlorocebus_sabaeus.Zambia.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Zambia.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Equus_caballus.up.SIFT.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Equus_caballus.up.SIFT.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Equus_caballus.up.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Equus_caballus.up.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Equus_caballus.up.SIFT.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Equus_caballus.up.SIFT.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Equus_caballus.up.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Equus_caballus.up.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Homo_sapiens.AFR.SIFT.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Homo_sapiens.AFR.SIFT.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.AFR.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.AFR.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Homo_sapiens.AFR.SIFT.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.AFR.SIFT.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.AFR.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.AFR.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Homo_sapiens.AMR.SIFT.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Homo_sapiens.AMR.SIFT.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.AMR.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.AMR.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Homo_sapiens.AMR.SIFT.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.AMR.SIFT.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.AMR.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.AMR.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Homo_sapiens.EAS.SIFT.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Homo_sapiens.EAS.SIFT.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.EAS.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.EAS.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Homo_sapiens.EAS.SIFT.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.EAS.SIFT.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.EAS.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.EAS.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Homo_sapiens.EUR.SIFT.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Homo_sapiens.EUR.SIFT.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.EUR.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.EUR.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Homo_sapiens.EUR.SIFT.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.EUR.SIFT.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.EUR.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.EUR.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Homo_sapiens.SAS.SIFT.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Homo_sapiens.SAS.SIFT.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.SAS.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.SAS.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Homo_sapiens.SAS.SIFT.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.SAS.SIFT.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.SAS.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.SAS.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Ovis_aries.IROA.SIFT.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Ovis_aries.IROA.SIFT.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROA.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROA.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Ovis_aries.IROA.SIFT.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.IROA.SIFT.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROA.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROA.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Ovis_aries.IROO.SIFT.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Ovis_aries.IROO.SIFT.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROO.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROO.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Ovis_aries.IROO.SIFT.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.IROO.SIFT.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROO.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROO.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Ovis_aries.IROV.SIFT.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Ovis_aries.IROV.SIFT.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROV.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROV.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Ovis_aries.IROV.SIFT.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.IROV.SIFT.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.IROV.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROV.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Ovis_aries.ISGC.SIFT.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Ovis_aries.ISGC.SIFT.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.ISGC.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.ISGC.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Ovis_aries.ISGC.SIFT.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.ISGC.SIFT.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.ISGC.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.ISGC.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins0NonAdaptive/snps.Ovis_aries.MOOA.SIFT.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Ovis_aries.MOOA.SIFT.histogram.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.MOOA.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.MOOA.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins0NonAdaptive/DFE.Ovis_aries.MOOA.SIFT.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.MOOA.SIFT.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/analysis/Ovis_aries.MOOA.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.MOOA.SIFT.polyDFE_C.pdf}
 \end{minipage}

### 2022-05-16 manuscript/main.tex
Ancestral reconstruction with codon models

@@
         Positive selection can be a result of adaptive evolution, meaning that individuals have had to adapt to a change in environment or selective pressure.
-        However, current positive selection can also be the result of mutations compensating for deleterious substitutions that have accumulated along lineages, in which case positive selection is non-adaptive and predictable.
+        However, recent positive selection can also be the result of mutations compensating for deleterious substitutions that have accumulated along lineages, in which case positive selection is non-adaptive.
         To evaluate the extent of non-adaptive positive selection, we have combined population genetics and phylogenetic datasets.
@@
         Second, we integrated mammalian divergence data with polymorphic variants found in 29 populations across 7 mammalian genera.
-        For each non-synonymous variant observed at the population level, we predicted its change in fitness from amino-acid fitness estimated at the mammalian scale.
+        For each non-synonymous variant observed at the population level, we predicted its change in fitness from amino-acid fitnesses estimated at the mammalian scale.
         We found that a large proportion of observed non-synonymous changes are predicted to be positively selected, meaning that the ancestral allele is suboptimal.
@@
     However, the causes of this advantage can be diverse.
-    We can distinguish two main advantages.
-    The first advantage allows its bearer to become better adapted to a new or a changing environment, what we typically call adaptive evolution.
-    The population as a whole is thus climbing the fitness landscape along an adaptive walk\cite{tenaillon_utility_2014}.
-    The second is non-adaptive, in the sense that the increase in fitness of a new mutation is not a response to a new or a changing environment.
+    We can distinguish two main scenarios in which a mutation is advantageous.
+    The first scenario concerns environmental change.
+    The bearer of the mutation that is advantageous in a new environment will be better adapted. Hence, its chances of survival and reproduction will be higher.
+    This process is typically referred to as adaptive evolution.
+    The second scenario involves the fixation of a deleterious mutation by drift, in which case the mutation restores the ancestral state which corresponded to an optimal state of the individual.
+    This process is non-adaptive, in the sense that the increase in fitness of the new mutation is not in response to a new or a changing environment.
     Instead, the mutation restores the ancestral state which corresponded to an optimal functioning of the individual in a constant environment, but has been lost due to the fixation of a deleterious mutation by drift.
-    The population as a whole is thus merely staying in the same position in fitness landscape at this equilibrium, and positive selection compensates for deleterious mutations that reach fixation due to drift\cite{sella_application_2005, mustonen_fitness_2009}.
+    Regarding the difference between these two scenarios at the population scale, while in the case of environmental change, the population as a whole is climbing the fitness landscape along an adaptive walk\cite{tenaillon_utility_2014}, in the case of
+    non-adaptive positive selection, the population as a whole is thus merely staying in the same position in fitness landscape at this equilibrium, and positive selection compensates for deleterious mutations that reach fixation due to drift\cite{sella_application_2005, mustonen_fitness_2009}.
     These two different kinds of selection result in a positive transmission bias of the advantageous allele, but their consequences are conceptually different.
@@
 
-    Inside proteins, positive selection can be quantified by comparing sequence variation inside a population with the sequence divergence with a sister species\cite{mcdonald_adaptative_1991}.
+    Positive selection can be quantified by comparing sequence variation inside a population with the sequence divergence with a sister species\cite{mcdonald_adaptative_1991}.
     Indeed, strongly advantageous mutations are expected to be observed in substitutions but not in polymorphism because they reach fixation quickly.
     This method has been largely improved to account for possible bias-inducing factors such as the presence of weak positive selection, background selection and demography fluctuations\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009, galtier_adaptive_2016, tataru_inference_2017}.
-    It's application across many taxa has uncovered that a large proportion of substitutions are positively selected\cite{moutinho_variation_2019}.
+    It's application across many taxa has uncovered widespread positive selection\cite{moutinho_variation_2019}.
     The root cause for this widespread rate of positive selection is, however, scarcely investigated, often assumed to be the end result of adaptive evolution.
@@
     For each site of the protein alignment, amino-acid frequencies in the alignment is a proxy for its fitness, since for example a deleterious amino acid will be absent in the alignment.
-    One of the most used methods to make these predictions is SIFT (Sort Intolerant From Tolerant) which reliably detects deleterious mutations in many taxa\cite{ng_sift_2003, vaser_sift_2016}.
+    One of the most used methods to make these predictions is SIFT (Sort Intolerant From Tolerant), which reliably detects deleterious mutations in many taxa\cite{ng_sift_2003, vaser_sift_2016}.
     However, this method has two major shortcomings.
@@
     But this score makes little sense to actual measure of fitness, and is not interpretable in terms of population genetics.
-    In the other hand, at the DNA level, so-called mutation-selection codon models are rooted with population genetics formalism\cite{halpern_evolutionary_1998, mccandlish_modeling_2014}.
+    At a finer scale, modelling at the codon level can disentangle processes of mutation at the DNA level and selection at the amino-acid level.
+    For example, so-called mutation-selection codon models are rooted with population genetics formalism\cite{halpern_evolutionary_1998, mccandlish_modeling_2014}.
     Such models provide a nearly-neutral framework of evolution by estimating the fitness landscape over amino-acid sequences for each site of the sequence while taking into account non-adaptive processes impacting codon frequency\cite{halpern_evolutionary_1998, rodrigue_mechanistic_2010, tamuri_estimating_2012}.
     Only nearly-neutral mutations between high fitness amino acids will tend to be permitted by the model, allowing for the explicit calculation of the scaled selection coefficient of non-synonymous mutations between codons.
-    These models have been used as a null model to predict the overall rate of evolution of proteins\cite{spielman_relationship_2015, dosreis_how_2015}.
-    A departure from this model indicates that proteins are evolving under a changing fitness landscape\cite{rodrigue_detecting_2017, tamuri_mutationselection_2021} and is a signal of adaptive evolution\cite{rodrigue_bayesian_2021}.
-    In this study we want to address three main questions: which proportions of the polymorphism we observe in mammals is undergoing non-adaptive positive selection ?
-    Are these mutations actually under positive selection at the scale of populations ?
-    How does effective population size modulates positive, negative and weak selection ?
+    As a consequence, by integrating datasets at the species and population level, we can estimate the selection coefficient for each mutation currently segregating in a population.
+    Such dataset can allow us to address different questions regarding positive selection affecting protein-coding DNA sequences.
+    Which proportion of the segregating polymorphism are predicted to be positively selected, from a suboptimal to a more optimal amino acid?
+    Are these polymorphism actually under ongoing positive selection at the scale of populations?
+    How does effective population size modulates positive, negative and weak selection?
+    Finally, how much of the recent substitutions are due to non-adaptive positive selection?
 
-    \begin{figure*}[!ht]
-        \
+    \begin{figure*}[!ht]\
     \centering
@@
     \caption{
-            Integrating divergence and polymorphism for the detection of adaptation.
+        Integrating divergence and polymorphism.
         At the phylogenetic level (panel A), amino-acid Wrightian fitness for each site are estimated from protein-coding DNA alignments using mutation-selection codon models.
-            At the population-genetic level (panel B), for each observed single nucleotide polymorphism (SNP), selection coefficient are computed as the difference in amino-acid fitness between the ancestral and derived variant.
+        At the population-genetic level (panel B), for each observed single nucleotide polymorphism (SNP) segregating in the population, selection coefficient are computed as the difference in amino-acid fitness between the ancestral and derived variant.
     }
@@
     Altogether, populations with large effective population size are under more efficient selection, confirming the prediction of the nearly-neutral theory of evolution.
+    As a consequence of increased selection efficacy, mutations in populations with high diversity are mechanically more likely to be deleterious (fig.~S4), especially for mutations predicted already to be deleterious at the phylogenetic scale (fig.~S5-6).
 
-    As a consequence of increased selection efficacy, mutations in populations with high diversity are mechanically more likely to be deleterious (fig.~S4), especially for mutations predicted already to be deleterious at the phylogenetic scale (fig.~S5-6).
-    However, and surprisingly, a decrease in the proportion of neutral mutation did not translate into a mechanical increase in the proportion of advantageous mutations.
-    Instead, populations with higher diversity have a lower proportion of advantageous mutations (fig.~S7), this effect is also more pronounced for mutations predicted to be advantageous at the phylogenetic scale (red row in fig.~\ref{fig:all-pop-results}C and fig.~S8).
-    This discrepancy can be explained by the fact that populations with larger diversity have already depleted the putatively advantageous mutations, and that only deleterious are remaining possible.
-    In other words, being on the top of a fixed fitness landscape leaves you with only paths going downhill.
-    Altogether, populations with increased diversity are showing signature of increased selection efficiency and are also less likely to generate positively selected mutations.
+    Finally, we computed the proportion of substitutions in the terminal branches that were predicted to be under positive selection ($\Sphy > 0$).
+    To this aim, for each population with polymorphism data available, we reconstructed the ancestral sequences before the last genus split in the tree.
+    In these populations, we show that out of all polarized substitutions in the branches, between 22 and 42\% of all substitutions are under $\Sphy > 0$ (table S1).
+    This proportion must be compared to the estimated probability of a mutation to be positively selected ($\Spop > 0$), which is between 4.8 and 11.3\%(table S1).
+    As a result, these observed substitutions are likely to have been positive selected because they restored the state which corresponded to an optimal state of the population.
+    Statistically, genomes are thus involved in a tug-of-war between a large volume deleterious mutations that eventually reach fixation due to drift, and scarce advantageous mutations that are repairing ancestral deleterious substitutions.
+    Taking into account that observed substitutions are likely to be due to positive selection that is not adaptive is thus crucial if one seek to estimate the proportion of adaptation while relying on substitutions between close species\cite{mcdonald_adaptative_1991}.
+    % However, and surprisingly, a decrease in the proportion of neutral mutation did not translate into a mechanical increase in the proportion of advantageous mutations.
+    % Instead, populations with higher diversity have a lower proportion of advantageous mutations (fig.~S7), this effect is also more pronounced for mutations predicted to be advantageous at the phylogenetic scale (red row in fig.~\ref{fig:all-pop-results}C and fig.~S8).
+    % This discrepancy can be explained by the fact that populations with larger diversity have already depleted the putatively advantageous mutations, and that only deleterious are remaining possible.
+    % In other words, being on the top of a fixed fitness landscape leaves you with only paths going downhill.
+    % Altogether, populations with increased diversity are showing signature of increased selection efficiency and are also less likely to generate positively selected mutations.
 
@@
 
-    From a structural biology perspective, we found that proteins are not optimal, with a large proportion of mutations still toward more optimal amino acids.
-    Seen from another angle, it means that we could theoretically derive the fittest proteins using only the amino acid with the highest fitness.
-    Another way to confirm our predictions on amino acid fitness would be to test whether fittest proteins are also thermodynamically more stable, leveraging recent developments able to compute efficiently and accurately the folding of proteins.
-
     % Our study is a bridge between phylogenetic and population genetics
@@
     Aside from methodological limitations, the mammalian case study might also not be representative of other clades.
-    Indeed, our dataset is quite convenient because of relatively small population sizes since a large amount of deleterious mutations are fixed, and thus, there is a lot of opportunities for non-adaptive positive selection to arise.
+    Indeed, our dataset is quite convenient because mammals have relatively small population sizes, which allow large amount of deleterious mutations to be fixed, and thus, there is a lot of opportunities for non-adaptive positive selection to arise.
     It would thus be of great interest to reproduce our experiment with other clades, such as \textit{drosophila} or birds which have higher effective population size.
@@
     % Moreover, mammalian are less affected by codon usage
+
+    From a structural biology perspective, we found that proteins are not optimal for their fitness, which has been proved for their kinetics and thermodynamics.
+    We argue that mutation-selection models are thus a mandatory tool in evolutionary biology to detect and quantify adaptation since they genuinely take into account the tug-of-war between scarce advantageous mutations likely to reach fixation and a bulk of deleterious mutations eventually reaching fixations due to their sheer mass.
+    Indeed, these models can be used as a null model to predict the overall rate of evolution of proteins\cite{spielman_relationship_2015, dosreis_how_2015}.
+    A departure from this model indicates that proteins are evolving under a changing fitness landscape\cite{rodrigue_detecting_2017, tamuri_mutationselection_2021} and is a signal of adaptive evolution\cite{rodrigue_bayesian_2021}.
 

### 2022-05-16 manuscript/supp-mat.tex
Ancestral reconstruction with codon models

@@
     \begin{center}
-        \begin{longtable}{|l|l|r|r|r|r|}
+        \begin{longtable}{|l|l|r|r|r|r|r|}
             \toprule
-            Population                     & Species             & Tajima $\theta$ & $\proba_{obs}[\divAdv]$ & $\PpolyAdv$ & $\proba [ \polyAdv | \divAdv]$ \\
+            Population           & Species             & Tajima $\theta_{\pi}$ & $\mathbb{P}_{div}(S > 0)$ & $\mathbb{P}_{obs}[S>0]$ & $\mathbb{P} [ \beta > 0 ]$ & $\mathbb{P} [ \beta > 0  | S>0]$ \\
             \midrule
@@
             \midrule
-            \multicolumn{6}{r}{{Continued on next page}} \\
+            \multicolumn{7}{r}{{Continued on next page}} \\
             \midrule
@@
             \endlastfoot
-            Diverse (Equus)                & Equus caballus      & $ 0.003$        & $ 0.161$                & $ 0.073$    & $ 0.779$                       \\
-            Diverse (Canis)                & Canis familiaris    & $ 0.004$        & $ 0.069$                & $ 0.041$    & $ 0.262$                       \\
-            Iran (IRBT)                    & Bos taurus          & $ 0.009$        & $ 0.123$                & $ 0.054$    & $ 0.300$                       \\
-            Uganda (UGBT)                  & Bos taurus          & $ 0.010$        & $ 0.139$                & $ 0.060$    & $ 0.779$                       \\
-            Australia (AUCH)               & Capra hircus        & $ 0.004$        & $ 0.105$                & $ 0.061$    & $ 0.119$                       \\
-            France (FRCH)                  & Capra hircus        & $ 0.004$        & $ 0.105$                & $ 0.060$    & $ 0.059$                       \\
-            Iran (IRCA)                    & Capra aegagrus      & $ 0.004$        & $ 0.105$                & $ 0.062$    & $ 0.053$                       \\
-            Iran (IRCH)                    & Capra hircus        & $ 0.005$        & $ 0.093$                & $ 0.058$    & $ 0.094$                       \\
-            Italy (ITCH)                   & Capra hircus        & $ 0.004$        & $ 0.103$                & $ 0.059$    & $ 0.053$                       \\
-            Morocco (MOCH)                 & Capra hircus        & $ 0.005$        & $ 0.077$                & $ 0.057$    & $ 0.045$                       \\
-            Iran (IROA)                    & Ovis aries          & $ 0.009$        & $ 0.107$                & $ 0.048$    & $ 0.144$                       \\
-            Iran (IROO)                    & Ovis orientalis     & $ 0.010$        & $ 0.110$                & $ 0.050$    & $ 0.177$                       \\
-            Iran (IROV)                    & Ovis vignei         & $ 0.009$        & $ 0.127$                & $ 0.049$    & $ 0.252$                       \\
-            Various (ISGC)                 & Ovis aries          & $ 0.009$        & $ 0.108$                & $ 0.049$    & $ 0.194$                       \\
-            Morocco (MOOA)                 & Ovis aries          & $ 0.009$        & $ 0.086$                & $ 0.045$    & $ 0.144$                       \\
-            Barbados                       & Chlorocebus sabaeus & $ 0.004$        & $ 0.104$                & $ 0.072$    & $ 0.484$                       \\
-            Central African Republic (CAR) & Chlorocebus sabaeus & $ 0.007$        & $ 0.105$                & $ 0.066$    & $ 0.312$                       \\
-            Ethiopia                       & Chlorocebus sabaeus & $ 0.006$        & $ 0.097$                & $ 0.068$    & $ 0.245$                       \\
-            Gambia                         & Chlorocebus sabaeus & $ 0.006$        & $ 0.101$                & $ 0.064$    & $ 0.411$                       \\
-            Kenya                          & Chlorocebus sabaeus & $ 0.006$        & $ 0.104$                & $ 0.066$    & $ 0.323$                       \\
-            Nevis                          & Chlorocebus sabaeus & $ 0.004$        & $ 0.105$                & $ 0.068$    & $ 0.445$                       \\
-            South Africa (SA)              & Chlorocebus sabaeus & $ 0.007$        & $ 0.095$                & $ 0.065$    & $ 0.233$                       \\
-            Saint Kitts (SK)               & Chlorocebus sabaeus & $ 0.005$        & $ 0.101$                & $ 0.071$    & $ 0.442$                       \\
-            Zambia                         & Chlorocebus sabaeus & $ 0.007$        & $ 0.101$                & $ 0.070$    & $ 0.290$                       \\
-            African (AFR)                  & Homo sapiens        & $ 0.003$        & $ 0.052$                & $ 0.092$    & $ 0.779$                       \\
-            Ad Mixed American (AMR)        & Homo sapiens        & $ 0.002$        & $ 0.055$                & $ 0.087$    & $ 0.779$                       \\
-            East Asian (EAS)               & Homo sapiens        & $ 0.002$        & $ 0.051$                & $ 0.084$    & $ 0.779$                       \\
-            European (EUR)                 & Homo sapiens        & $ 0.002$        & $ 0.053$                & $ 0.087$    & $ 0.779$                       \\
-            South Asian (SAS)              & Homo sapiens        & $ 0.002$        & $ 0.051$                & $ 0.084$    & $ 0.779$                       \\
+            Equus c.             & Equus caballus      & $ 0.002$              & $ 0.301$                  & $ 0.243$                & $ 0.113$                   & $ 0.793$                       \\
+            Canis f.             & Canis familiaris    & $ 0.003$              & $ 0.421$                  & $ 0.181$                & $ 0.048$                   & $ 0.761$                       \\
+            Iran                 & Bos taurus          & $ 0.005$              & $ 0.249$                  & $ 0.264$                & $ 0.098$                   & $ 0.605$                       \\
+            Uganda               & Bos taurus          & $ 0.006$              & $ 0.254$                  & $ 0.249$                & $ 0.095$                   & $ 0.630$                       \\
+            Australia            & Capra hircus        & $ 0.003$              & $ 0.286$                  & $ 0.265$                & $ 0.096$                   & $ 0.512$                       \\
+            France               & Capra hircus        & $ 0.004$              & $ 0.285$                  & $ 0.274$                & $ 0.092$                   & $ 0.529$                       \\
+            Iran (C. aegagrus)   & Capra hircus        & $ 0.004$              & $ 0.284$                  & $ 0.270$                & $ 0.095$                   & $ 0.455$                       \\
+            Iran                 & Capra hircus        & $ 0.004$              & $ 0.297$                  & $ 0.239$                & $ 0.080$                   & $ 0.500$                       \\
+            Italy                & Capra hircus        & $ 0.004$              & $ 0.285$                  & $ 0.265$                & $ 0.087$                   & $ 0.500$                       \\
+            Morocco              & Capra hircus        & $ 0.004$              & $ 0.296$                  & $ 0.200$                & $ 0.080$                   & $ 0.509$                       \\
+            Iran                 & Ovis aries          & $ 0.008$              & $ 0.229$                  & $ 0.259$                & $ 0.060$                   & $ 0.366$                       \\
+            Iran (O. orientalis) & Ovis aries          & $ 0.009$              & $ 0.226$                  & $ 0.272$                & $ 0.067$                   & $ 0.344$                       \\
+            Iran (O. vignei)     & Ovis aries          & $ 0.008$              & $ 0.235$                  & $ 0.307$                & $ 0.075$                   & $ 0.464$                       \\
+            Various              & Ovis aries          & $ 0.009$              & $ 0.226$                  & $ 0.279$                & $ 0.065$                   & $ 0.378$                       \\
+            Morocco              & Ovis aries          & $ 0.008$              & $ 0.225$                  & $ 0.212$                & $ 0.054$                   & $ 0.377$                       \\
+            Barbados             & Chlorocebus sabaeus & $ 0.004$              & $ 0.314$                  & $ 0.258$                & $ 0.109$                   & $ 0.670$                       \\
+            Central Afr. Rep.    & Chlorocebus sabaeus & $ 0.006$              & $ 0.315$                  & $ 0.264$                & $ 0.094$                   & $ 0.619$                       \\
+            Ethiopia             & Chlorocebus sabaeus & $ 0.005$              & $ 0.307$                  & $ 0.252$                & $ 0.107$                   & $ 0.660$                       \\
+            Gambia               & Chlorocebus sabaeus & $ 0.005$              & $ 0.303$                  & $ 0.249$                & $ 0.085$                   & $ 0.666$                       \\
+            Kenya                & Chlorocebus sabaeus & $ 0.006$              & $ 0.311$                  & $ 0.272$                & $ 0.095$                   & $ 0.602$                       \\
+            Nevis                & Chlorocebus sabaeus & $ 0.004$              & $ 0.302$                  & $ 0.252$                & $ 0.102$                   & $ 0.642$                       \\
+            South Africa         & Chlorocebus sabaeus & $ 0.007$              & $ 0.312$                  & $ 0.246$                & $ 0.094$                   & $ 0.638$                       \\
+            Saint Kitts          & Chlorocebus sabaeus & $ 0.004$              & $ 0.306$                  & $ 0.250$                & $ 0.106$                   & $ 0.664$                       \\
+            Zambia               & Chlorocebus sabaeus & $ 0.006$              & $ 0.308$                  & $ 0.261$                & $ 0.103$                   & $ 0.630$                       \\
+            African              & Homo sapiens        & $ 0.003$              & $ 0.256$                  & $ 0.141$                & $ 0.103$                   & $ 1.000$                       \\
+            Admixed American     & Homo sapiens        & $ 0.002$              & $ 0.247$                  & $ 0.145$                & $ 0.103$                   & $ 0.945$                       \\
+            East Asian           & Homo sapiens        & $ 0.002$              & $ 0.241$                  & $ 0.129$                & $ 0.098$                   & $ 0.918$                       \\
+            European             & Homo sapiens        & $ 0.002$              & $ 0.254$                  & $ 0.130$                & $ 0.098$                   & $ 0.919$                       \\
+            South Asian          & Homo sapiens        & $ 0.002$              & $ 0.246$                  & $ 0.131$                & $ 0.096$                   & $ 0.912$                       \\
         \end{longtable}
@@
         \item Tajima $\theta$ is the synonymous diversity.
-        \item $\proba_{obs}[\divAdv]$ is the proportion of SNPs observed with a selection coefficient at the phylogenetic scale ($\Sphy$) larger than 1.
-        \item $\PpolyAdv $ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) larger than 1, estimated for the whole genome.
-        \item $\proba [ \polyAdv | \divAdv]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) larger than 1, estimated of SNPs observed with a selection coefficient at the phylogenetic scale ($\Sphy$) larger than 1.
+        \item $\mathbb{P}_{div}(S > 0)$ is the proportion of substitution in the terminal branch observed with a selection coefficient at the phylogenetic scale ($\Sphy$) larger than 0.
+        \item $\mathbb{P}_{obs}[S>0]$ is the proportion of SNPs observed with a predicted selection coefficient at the phylogenetic scale ($\Sphy$) larger than 0.
+        \item $\mathbb{P} [ \beta > 0 ]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) larger than 1, estimated for the whole genome.
+        \item $\proba [ \polyAdv | \divAdv]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) larger than 1, estimated on the subset of SNPs observed with a predicted selection coefficient at the phylogenetic scale ($\Sphy$) larger than 0.
     \end{itemize}
@@
     \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/regression/results.watterson.all_P-Seq0.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression/results.watterson.all_P-Seq0.scatter.pdf}
     \end{minipage}
     \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/regression/results.watterson.neg-weak_P-Seq0.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression/results.watterson.neg-weak_P-Seq0.scatter.pdf}
     \end{minipage}
     \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/regression/results.watterson.pos-weak_P-Seq0.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression/results.watterson.pos-weak_P-Seq0.scatter.pdf}
     \end{minipage}
@@
     \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/regression/results.watterson.all_P-Sinf0.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression/results.watterson.all_P-Sinf0.scatter.pdf}
     \end{minipage}
     \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/regression/results.watterson.neg_P-Sinf0.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression/results.watterson.neg_P-Sinf0.scatter.pdf}
     \end{minipage}
     \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/regression/results.watterson.neg-strong_P-Sinf0.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression/results.watterson.neg-strong_P-Sinf0.scatter.pdf}
     \end{minipage}
@@
     \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/regression/results.watterson.all_P-Ssup0.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression/results.watterson.all_P-Ssup0.scatter.pdf}
     \end{minipage}
     \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/polyDFE-mC-non-adaptive/regression/results.watterson.pos_P-Ssup0.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression/results.watterson.pos_P-Ssup0.scatter.pdf}
     \end{minipage}

### 2022-05-16 copy_artworks.sh

@@ -1,11 +1,11 @@
 #!/usr/bin/env bash
 \cp -rf ./experiments/50windows-polyDFE-mC-non-adaptive/regression/results.watterson.a.scatter.pdf ./manuscript/artworks/scatter.watterson.slopeSpopSphy.pdf
 \cp -rf ./experiments/50windows-polyDFE-mC-non-adaptive/results/regression.MutSel.SelCoeff.scatter.pdf ./manuscript/artworks/scatter.Sphy.Spop.pdf
-\cp -rf ./experiments/polyDFE-mC-non-adaptive/results/Theta.MutSel.P-Seq0.heatmap.pdf ./manuscript/artworks/heatmap.neutral.pdf
-\cp -rf ./experiments/polyDFE-mC-non-adaptive/results/Theta.MutSel.P-Sinf0.heatmap.pdf ./manuscript/artworks/heatmap.neg.pdf
-\cp -rf ./experiments/polyDFE-mC-non-adaptive/results/Theta.MutSel.P-Ssup0.heatmap.pdf ./manuscript/artworks/heatmap.pos.pdf
-\cp -rf ./experiments/polyDFE-mC-non-adaptive/results/Theta.MutSel.pos-weak.stacked.pdf ./manuscript/artworks/pos-weak.stacked.pdf
-\cp -rf ./experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.AFR.MutSel-sfs.normalize.pdf ./manuscript/artworks/AFR.SFS.pdf
-\cp -rf ./experiments/polyDFE-mC-non-adaptive/analysis/Homo_sapiens.AFR.MutSel.polyDFE_C.pdf ./manuscript/artworks/AFR.polyDFE.pdf
-\cp -rf ./data_processed/opportunities_bins0NonAdaptive/DFE.Homo_sapiens.AFR.MutSel.pdf ./manuscript/artworks/AFR.histogramDFE.pdf
-\cp -rf ./data_processed/vcf_annotate_bins0NonAdaptive/snps.Homo_sapiens.AFR.MutSel.histogram.pdf ./manuscript/artworks/AFR.histogramSNP.pdf
+\cp -rf ./experiments/5bins-polyDFE-mC/results/Theta.MutSel.P-Seq0.heatmap.pdf ./manuscript/artworks/heatmap.neutral.pdf
[…]

### 2022-05-16 scripts/ancestral_reconstruction.py

@@ -3,11 +3,20 @@ import argparse
 from ete3 import Tree
 import subprocess
 import numpy as np
-from libraries import open_fasta, write_fasta, nucleotides
+from libraries import open_fasta, write_fasta, codontable
 
 
 def most_common(lst):
     return max(set(lst), key=lst.count)
+
+
+def clean_sequence(seq):
+    codon_list = []
+    for pos in range(len(seq) // 3):
+        codon = seq[pos * 3: pos * 3 + 3]
+        codon = codon if (codontable[codon] != "-" and codontable[codon] != "X") else "---"
+        codon_list.append(codon)
+    return "".join(codon_list)
 
 
 def SubsetMostCommon(alignment, specie, tree_path, fasta_pop):
@@ -18,7 +27,7 @@ def SubsetMostCommon(alignment, specie, tree_path, fasta_pop):
     assert len(leaves) == 1
     node = leaves[0]
 
-    subali = {specie: fasta_pop.replace("!", "-")}
+    subali = {specie: clean_sequence(fasta_pop)}
     while len(subali) < 4:
         if node is None:
             break
@@ -33,9 +42,10 @@ def SubsetMostCommon(alignment, specie, tree_path, fasta_pop):
 
                 seqs = [alignment[sp] for sp in diff_genus_names]
                 ref_seq = []
-                for pos in range(len(seqs[0])):
-                    states = [s[pos] for s in seqs if s[pos] in nucleotides]
-                    ref_seq.append("-" if len(states) == 0 else most_common(states))
+                for pos in range(len(seqs[0]) // 3):
+                    codons = [s[pos * 3: pos * 3 + 3] for s in seqs]
+                    codons = [c for c in codons if codontable[c] != "-" and codontable[c] != "X"]
+                    ref_seq.append("---" if len(codons) == 0 else most_common(codons))
 
                 subali[sister_names[0]] = "".join(ref_seq)
 
@@ -44,23 +54,6 @@ def SubsetMostCommon(alignment, specie, tree_path, fasta_pop):
     tree.prune(subali.keys())
     print(subali.keys())
     return subali, tree
-
-
-def Subset(alignment, specie, tree_path, fasta_pop):
-    if not os.path.exists(tree_path):
-        tree_path = tree_path.replace("_null_", "__")
-
-    t = Tree(tree_path)
-    leaves = t.get_leaves_by_name(specie)
[…]

### 2022-05-16 scripts/parse_results_DFE.py

@@ -108,14 +108,27 @@ def omega_div(df_div, cat):
     return (div_non_syn / div_syn) * (l_syn / l_non_syn)
 
 
-def omega_na_model_C(p_pos, d_neg, d_pos):
-    neg_res = integrate.quad(lambda s: (1 - p_pos) * d_neg.pdf(-s) * pfix(s), -100, 0)
-    pos_res = integrate.quad(lambda s: p_pos * d_pos.pdf(s) * pfix(s), 0, 0)
-    return neg_res[0] + pos_res[0]
+def omega_model_C(p_pos, d_neg, d_pos, min_s, max_s):
+    out = 0.0
+    if min_s < 0:
+        out += integrate.quad(lambda s: (1 - p_pos) * d_neg.pdf(-s) * pfix(s), min_s, 0)[0]
+    if max_s > 0:
+        out += integrate.quad(lambda s: p_pos * d_pos.pdf(s) * pfix(s), 0, max_s)[0]
+    return out
 
 
-def omega_na_model_D(p_list, s_list):
-    return sum([p * pfix(s) for p, s in zip(p_list, s_list) if s <= 0])
+def omega_model_D(p_list, s_list, min_s, max_s):
+    return sum([p * pfix(s) for p, s in zip(p_list, s_list) if min_s <= s < max_s])
+
+
+def omega_dico(df_div, cat, omega_dfe, omega_na_dfe, omega_a_dfe):
+    out = {f'omega_dfe': omega_dfe, f'omega_NAdfe': omega_na_dfe, f'omega_Adfe': omega_a_dfe}
+    if df_div is not None:
+        omega = omega_div(df_div, cat)
+        div = float(df_div[f"div_{cat}"].values[0])
+        out |= {f"div": div, f'omega_div': omega, f'omega_Adiv': omega - omega_na_dfe,
+                f'alpha_div': (omega - omega_na_dfe) / omega}
+    return out
 
 
 def alpha_model_D(p_list, s_list, lim_left=0.0):
@@ -148,14 +161,10 @@ def main(args):
             for lim_left in alpha_sup_limits:
                 out[f'alpha{lim_left}'] = alpha_model_D(p_list, s_list, lim_left=lim_left)
 
-            if df_div is not None:
-                omega = omega_div(df_div, cat)
-                omega_na = omega_na_model_D(p_list, s_list)
-                out[f'omega'] = omega
-                out[f'omega_na'] = omega_na
-                out[f'omega_a'] = omega - omega_na
[…]

### 2022-05-16 scripts/plot_regression.py

@@ -12,8 +12,8 @@ from libraries import my_dpi, plt, polydfe_cat_dico, tex_f, sort_df, sp_sorted, 
     alpha_sup_limits
 
 markers = ["o", "d", "s", '.']
-alpha_suffix = alpha_sup_limits + ["_div", "_MKF", "_MKW", "_MKT"]
-omega_suffix = ["", "_na", "_a"]
+alpha_suffix = alpha_sup_limits + ["_div", "_mkt", "_mkw", "_mkf"]
+omega_suffix = ["_div", "_dfe", "_NAdfe", "_Adiv", "_Adfe", "_Amkt", "_Amkw", "_Amkf"]
 
 
 def open_tsv(filepath, cat_snps):
@@ -24,7 +24,7 @@ def open_tsv(filepath, cat_snps):
         df_theta = df_theta.drop(["method", "species", "category"], axis=1)
         df_dfe = ddf[(ddf["method"] == "MutSel") & (ddf["category"] != "syn")]
         cols = list(polydfe_cat_dico) + [f"P-{cat}" for cat in cat_snps.non_syn_list]
-        cols += ['p_b', 'S_b', 'S_d', 'b', 'logL', 'S', 'S+', 'S-', 'fay_wu', 'tajima', 'watterson']
+        cols += ['p_b', 'S_b', 'S_d', 'b', 'logL', 'S', 'S+', 'S-', 'fay_wu', 'tajima', 'watterson', 'div']
         cols += [f"omega{sup}" for sup in omega_suffix]
         cols += [f"alpha{sup}" for sup in alpha_suffix]
         m_list = []
@@ -77,7 +77,7 @@ def generate_xy_plot(cat_snps):
             dico_label[f'{cat}_omega{sup}'] = f"$\\omega^{{{str(sup).replace('_', '')}}} {s}$"
         for p, param in [('S_b', "\\beta_b"), ('S_d', "\\beta_d"), ('b', "b"), ('p_b', "p_b"), ('logL', "LnL"),
                          ('S', "S"), ('S+', "S^+"), ('S-', "S^-"), ('pnpsT', "\\pi_T"),
-                         ('pnpsF', "\\pi_F"), ('pnpsW', "\\pi_W")]:
+                         ('pnpsF', "\\pi_F"), ('pnpsW', "\\pi_W"), ('div', "d")]:
[…]

### 2022-05-16 scripts/substitutions_mapping.py

@@ -58,6 +58,8 @@ def main(args):
             for cat in cats:
                 dico_div[f"div_{cat}"] += 1.0
 
+        cds_rates.rm_ensg(ensg)
+
     df_opp = pd.read_csv(args.opp, sep="\t")
     for cat in cat_snps.non_syn_list:
         dico_div[f"L_{cat}"] = df_opp[cat].values[0] * df_opp["Ldn"].values[0]

### 2022-06-17 copy_artworks.sh
Plot histogram of S for substitutions

@@ -9,3 +9,5 @@
 \cp -rf ./experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.AFR.MutSel.polyDFE_C.pdf ./manuscript/artworks/AFR.polyDFE.pdf
 \cp -rf ./data_processed/opportunities_bins5/DFE.Homo_sapiens.AFR.MutSel.pdf ./manuscript/artworks/AFR.histogramDFE.pdf
 \cp -rf ./data_processed/vcf_annotate_bins5/snps.Homo_sapiens.AFR.MutSel.histogram.pdf ./manuscript/artworks/AFR.histogramSNP.pdf
+\cp -rf ./data_processed/vcf_annotate_bins5/snps.Homo_sapiens.AFR.MutSel.histogram.full.pdf ./manuscript/artworks/AFR.histogramSNP.full.pdf
+\cp -rf ./data_processed/ancestral_bins5/Homo_sapiens.AFR.pdf ./manuscript/artworks/AFR.histogramDiv.pdf

### 2022-06-17 scripts/plot_regression.py

@@ -61,8 +61,10 @@ def generate_xy_plot(cat_snps):
         if cat != "all":
             s = cat_snps.label(cat).replace("$", "")
 
-        dico_label[cat] = "$\\mathbb{P}" + f"[{s}]$"
-        dico_label[f"{cat}_snps"] = "$\\mathbb{P}_{obs}" + f"[{s}]$"
+        dico_label[cat] = "$\\mathbb{P}_{mut}" + f"[{s}]$"
+        dico_label[f"{cat}_snps"] = "$\\mathbb{P}_{poly}" + f"[{s}]$"
+        dico_label[f"proba_{cat}_div"] = "$\\mathbb{P}_{div}" + f"[{s}]$"
+
         for cat_poly, beta_tex in polydfe_cat_dico.items():
             beta = beta_tex[beta_tex.find("[") + 1:beta_tex.rfind("]")]
             s_given_beta_key = f'{cat_poly}_P-{cat}'
@@ -227,20 +229,20 @@ def main(args):
                 df[f"{cat}_alpha_mkw"] = df[f"{cat}_omega_Amkw"] / df[f"{cat}_omega_div"]
                 df[f"{cat}_alpha_mkf"] = df[f"{cat}_omega_Amkf"] / df[f"{cat}_omega_div"]
 
+        if f"{cat}_div" in df and "all_div" in df:
+            df[f"proba_{cat}_div"] = df[f"{cat}_div"] / df["all_div"]
+
     if "neg_P-Ssup0" in df:
         df["neg_R_Ssup0"] = 100 * (1 - df["neg_P-Ssup0"] / df["all_P-Ssup0"])
         dico_label['neg_R_Ssup0'] = f"1 - {dico_label['neg_P-Ssup0']} / {dico_label['all_P-Ssup0']} (\\%)"
 
-    if "pos_div" in df and "neg_div" in df:
-        df["proba_pos_div"] = df["pos_div"] / (df["neg_div"] + df["pos_div"])
-        dico_label['proba_pos_div'] = "$\\mathbb{P}_{div}(S > 0)$"
-
     cols_suffix = [['S_b'], ['p_b'], ['logL'], ['S_d'], ['b'], ['S-'], ['S'], ['P-Ssup0'], ['R_Ssup0'], ['P-Seq0'],
                    ['P-Sinf0'], ['omega_div'], ['omega_dfe'], ['omega_NAdfe'], ['pnpsW'], ['omega_Adfe'],
[…]

### 2022-06-17 scripts/substitutions_mapping.py

@@ -1,11 +1,39 @@
-import os
 import argparse
-import numpy as np
-import pandas as pd
 from glob import glob
-from collections import defaultdict
 from ete3 import Tree
-from libraries import CdsRates, CategorySNP, open_fasta, codontable
+from matplotlib.patches import Rectangle
+from libraries import *
+
+
+def plot_histogram(score_list, cat_snps, method, file):
+    fig, ax = plt.subplots(figsize=(1920 / my_dpi, 960 / my_dpi), dpi=my_dpi)
+    xmin, xmax = xlim_dico[method][0], xlim_dico[method][1]
+    n, bins, patches = plt.hist([s for s in score_list if np.isfinite(s)], bins=np.linspace(xmin, xmax, 61),
+                                range=(xmin, xmax), edgecolor="black", linewidth=1.0)
+    total_n = sum(n)
+    if cat_snps.bins <= 10:
+        n_cat = defaultdict(float)
+        for i, b in enumerate(bins[1:]):
+            cats = cat_snps.rate2cats(b)
+            assert len(cats) >= 1
+            cat = cats[0]
+            patches[i].set_facecolor(cat_snps.color(cat))
+            n_cat[cat] += n[i] / total_n
+        handles = [Rectangle((0, 0), 1, 1, color=c) for c in [cat_snps.color(cat) for cat in cat_snps.non_syn_list]]
+        labels = [cat_snps.label(cat) + f" ({n_cat[cat] * 100:.2f}% of total)" for cat in cat_snps.non_syn_list]
+        plt.legend(handles, labels)
+    plt.xlabel(rate_dico[method])
+    plt.ylabel("Density")
+    for x in cat_snps.inner_bound:
+        plt.axvline(x, color="grey", lw=1, ls='--')
+    if xmin < -1.0 and xmax > 1.0:
+        ax.xaxis.set_major_locator(plt.MultipleLocator(1))
+    plt.axvline(0, color="black", lw=2)
+    plt.xlim((xmin, xmax))
+    plt.tight_layout()
+    plt.savefig(file, format="pdf")
+    plt.clf()
+    plt.close("all")
 
 
 def main(args):
@@ -13,6 +41,7 @@ def main(args):
     dico_div = defaultdict(float)
     cat_snps = CategorySNP("MutSel", args.bounds, bins=args.bins, windows=args.windows)
     cds_rates = CdsRates("MutSel", args.exp_folder)
+    score_list = []
 
[…]

### 2022-06-17 manuscript/main.tex
Table with proba of S > 1 for mutatations, SNPs and div in supp. mat.

@@
     \label{sec:acknowledgment}
-    We gratefully acknowledge the help of Nicolas Lartillot for his advice and review concerning this manuscript.
     This work was performed using the computing facilities of the CC LBBE/PRABI\@.
@@
     Université de Lausanne;
-    French National Research Agency, Grant ANR-19-CE12-0019 / HotRec.
     \textbf{Author contributions:}

### 2022-06-17 manuscript/supp-mat.tex
Table with proba of S > 1 for mutatations, SNPs and div in supp. mat.

@@
 
-\title{Selection coefficients at the phylogenetic and population-genetic scale}
+\title{Empirical evidence for positive selection that is not adaptive evolution}
 
@@
     \large
-    T. {Latrille}$^{1}$, J. {Joseph}$^{2}$, N. {Salamin}$^{1}$\\
-    $^{1}$Université de Lausanne, Lausanne, Switzerland
-    $^{1}$Université de Lyon, Lyon, France
+    T. {Latrille}, J. {Joseph}, N. {Salamin}\\
 }
@@
     \maketitle
+    \part*{Supplementary materials}
     \tableofcontents
@@
     \begin{center}
-        \begin{longtable}{|l|l|r|r|r|r|r|}
+        \begin{longtable}{|l|l|r|r|r|r|}
             \toprule
-            Population           & Species             & Tajima $\theta_{\pi}$ & $\mathbb{P}_{div}(S > 0)$ & $\mathbb{P}_{obs}[S>0]$ & $\mathbb{P} [ \beta > 0 ]$ & $\mathbb{P} [ \beta > 0  | S>0]$ \\
+            Population           & Species             & Tajima $\theta_{\pi}$ & $\mathbb{P}_{mut}[S>0]$ & $\mathbb{P}_{poly}[S>0]$ & $\mathbb{P}_{div}[S>0]$ \\
             \midrule
@@
             \midrule
-            \multicolumn{7}{r}{{Continued on next page}} \\
+            \multicolumn{6}{r}{{Continued on next page}} \\
             \midrule
@@
             \endlastfoot
-            Equus c.             & Equus caballus      & $ 0.002$              & $ 0.301$                  & $ 0.243$                & $ 0.113$                   & $ 0.793$                       \\
-            Canis f.             & Canis familiaris    & $ 0.003$              & $ 0.421$                  & $ 0.181$                & $ 0.048$                   & $ 0.761$                       \\
-            Iran                 & Bos taurus          & $ 0.005$              & $ 0.249$                  & $ 0.264$                & $ 0.098$                   & $ 0.605$                       \\
-            Uganda               & Bos taurus          & $ 0.006$              & $ 0.254$                  & $ 0.249$                & $ 0.095$                   & $ 0.630$                       \\
-            Australia            & Capra hircus        & $ 0.003$              & $ 0.286$                  & $ 0.265$                & $ 0.096$                   & $ 0.512$                       \\
-            France               & Capra hircus        & $ 0.004$              & $ 0.285$                  & $ 0.274$                & $ 0.092$                   & $ 0.529$                       \\
-            Iran (C. aegagrus)   & Capra hircus        & $ 0.004$              & $ 0.284$                  & $ 0.270$                & $ 0.095$                   & $ 0.455$                       \\
-            Iran                 & Capra hircus        & $ 0.004$              & $ 0.297$                  & $ 0.239$                & $ 0.080$                   & $ 0.500$                       \\
-            Italy                & Capra hircus        & $ 0.004$              & $ 0.285$                  & $ 0.265$                & $ 0.087$                   & $ 0.500$                       \\
-            Morocco              & Capra hircus        & $ 0.004$              & $ 0.296$                  & $ 0.200$                & $ 0.080$                   & $ 0.509$                       \\
-            Iran                 & Ovis aries          & $ 0.008$              & $ 0.229$                  & $ 0.259$                & $ 0.060$                   & $ 0.366$                       \\
-            Iran (O. orientalis) & Ovis aries          & $ 0.009$              & $ 0.226$                  & $ 0.272$                & $ 0.067$                   & $ 0.344$                       \\
-            Iran (O. vignei)     & Ovis aries          & $ 0.008$              & $ 0.235$                  & $ 0.307$                & $ 0.075$                   & $ 0.464$                       \\
-            Various              & Ovis aries          & $ 0.009$              & $ 0.226$                  & $ 0.279$                & $ 0.065$                   & $ 0.378$                       \\
-            Morocco              & Ovis aries          & $ 0.008$              & $ 0.225$                  & $ 0.212$                & $ 0.054$                   & $ 0.377$                       \\
-            Barbados             & Chlorocebus sabaeus & $ 0.004$              & $ 0.314$                  & $ 0.258$                & $ 0.109$                   & $ 0.670$                       \\
-            Central Afr. Rep.    & Chlorocebus sabaeus & $ 0.006$              & $ 0.315$                  & $ 0.264$                & $ 0.094$                   & $ 0.619$                       \\
-            Ethiopia             & Chlorocebus sabaeus & $ 0.005$              & $ 0.307$                  & $ 0.252$                & $ 0.107$                   & $ 0.660$                       \\
-            Gambia               & Chlorocebus sabaeus & $ 0.005$              & $ 0.303$                  & $ 0.249$                & $ 0.085$                   & $ 0.666$                       \\
-            Kenya                & Chlorocebus sabaeus & $ 0.006$              & $ 0.311$                  & $ 0.272$                & $ 0.095$                   & $ 0.602$                       \\
-            Nevis                & Chlorocebus sabaeus & $ 0.004$              & $ 0.302$                  & $ 0.252$                & $ 0.102$                   & $ 0.642$                       \\
-            South Africa         & Chlorocebus sabaeus & $ 0.007$              & $ 0.312$                  & $ 0.246$                & $ 0.094$                   & $ 0.638$                       \\
-            Saint Kitts          & Chlorocebus sabaeus & $ 0.004$              & $ 0.306$                  & $ 0.250$                & $ 0.106$                   & $ 0.664$                       \\
-            Zambia               & Chlorocebus sabaeus & $ 0.006$              & $ 0.308$                  & $ 0.261$                & $ 0.103$                   & $ 0.630$                       \\
-            African              & Homo sapiens        & $ 0.003$              & $ 0.256$                  & $ 0.141$                & $ 0.103$                   & $ 1.000$                       \\
-            Admixed American     & Homo sapiens        & $ 0.002$              & $ 0.247$                  & $ 0.145$                & $ 0.103$                   & $ 0.945$                       \\
-            East Asian           & Homo sapiens        & $ 0.002$              & $ 0.241$                  & $ 0.129$                & $ 0.098$                   & $ 0.918$                       \\
-            European             & Homo sapiens        & $ 0.002$              & $ 0.254$                  & $ 0.130$                & $ 0.098$                   & $ 0.919$                       \\
-            South Asian          & Homo sapiens        & $ 0.002$              & $ 0.246$                  & $ 0.131$                & $ 0.096$                   & $ 0.912$                       \\
+            Equus c.             & Equus caballus      & $ 0.002$              & $ 0.054$                & $ 0.243$                 & $ 0.301$                \\
+            Canis f.             & Canis familiaris    & $ 0.003$              & $ 0.049$                & $ 0.181$                 & $ 0.423$                \\
+            Iran                 & Bos taurus          & $ 0.005$              & $ 0.053$                & $ 0.264$                 & $ 0.266$                \\
+            Uganda               & Bos taurus          & $ 0.006$              & $ 0.053$                & $ 0.249$                 & $ 0.267$                \\
+            Australia            & Capra hircus        & $ 0.003$              & $ 0.054$                & $ 0.265$                 & $ 0.301$                \\
+            France               & Capra hircus        & $ 0.004$              & $ 0.054$                & $ 0.274$                 & $ 0.301$                \\
+            Iran (C. aegagrus)   & Capra hircus        & $ 0.004$              & $ 0.054$                & $ 0.270$                 & $ 0.301$                \\
+            Iran                 & Capra hircus        & $ 0.004$              & $ 0.054$                & $ 0.239$                 & $ 0.303$                \\
+            Italy                & Capra hircus        & $ 0.004$              & $ 0.054$                & $ 0.265$                 & $ 0.301$                \\
+            Morocco              & Capra hircus        & $ 0.004$              & $ 0.054$                & $ 0.200$                 & $ 0.303$                \\
+            Iran                 & Ovis aries          & $ 0.008$              & $ 0.054$                & $ 0.259$                 & $ 0.229$                \\
+            Iran (O. orientalis) & Ovis aries          & $ 0.009$              & $ 0.054$                & $ 0.272$                 & $ 0.226$                \\
+            Iran (O. vignei)     & Ovis aries          & $ 0.008$              & $ 0.054$                & $ 0.307$                 & $ 0.235$                \\
+            Various              & Ovis aries          & $ 0.009$              & $ 0.054$                & $ 0.279$                 & $ 0.226$                \\
+            Morocco              & Ovis aries          & $ 0.008$              & $ 0.054$                & $ 0.212$                 & $ 0.225$                \\
+            Barbados             & Chlorocebus sabaeus & $ 0.004$              & $ 0.050$                & $ 0.258$                 & $ 0.305$                \\
+            Central Afr. Rep.    & Chlorocebus sabaeus & $ 0.006$              & $ 0.050$                & $ 0.264$                 & $ 0.307$                \\
+            Ethiopia             & Chlorocebus sabaeus & $ 0.005$              & $ 0.050$                & $ 0.252$                 & $ 0.305$                \\
+            Gambia               & Chlorocebus sabaeus & $ 0.005$              & $ 0.050$                & $ 0.249$                 & $ 0.307$                \\
+            Kenya                & Chlorocebus sabaeus & $ 0.006$              & $ 0.050$                & $ 0.272$                 & $ 0.309$                \\
+            Nevis                & Chlorocebus sabaeus & $ 0.004$              & $ 0.050$                & $ 0.252$                 & $ 0.305$                \\
+            South Africa         & Chlorocebus sabaeus & $ 0.007$              & $ 0.050$                & $ 0.246$                 & $ 0.309$                \\
+            Saint Kitts          & Chlorocebus sabaeus & $ 0.004$              & $ 0.050$                & $ 0.250$                 & $ 0.309$                \\
+            Zambia               & Chlorocebus sabaeus & $ 0.006$              & $ 0.050$                & $ 0.261$                 & $ 0.307$                \\
+            African              & Homo sapiens        & $ 0.003$              & $ 0.051$                & $ 0.141$                 & $ 0.259$                \\
+            Admixed American     & Homo sapiens        & $ 0.002$              & $ 0.051$                & $ 0.145$                 & $ 0.258$                \\
+            East Asian           & Homo sapiens        & $ 0.002$              & $ 0.051$                & $ 0.129$                 & $ 0.259$                \\
+            European             & Homo sapiens        & $ 0.002$              & $ 0.051$                & $ 0.130$                 & $ 0.258$                \\
+            South Asian          & Homo sapiens        & $ 0.002$              & $ 0.051$                & $ 0.131$                 & $ 0.259$                \\
         \end{longtable}
@@
         \item Tajima $\theta$ is the synonymous diversity.
-        \item $\mathbb{P}_{div}(S > 0)$ is the proportion of substitution in the terminal branch observed with a selection coefficient at the phylogenetic scale ($\Sphy$) larger than 0.
-        \item $\mathbb{P}_{obs}[S>0]$ is the proportion of SNPs observed with a predicted selection coefficient at the phylogenetic scale ($\Sphy$) larger than 0.
-        \item $\mathbb{P} [ \beta > 0 ]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) larger than 1, estimated for the whole genome.
-        \item $\proba [ \polyAdv | \divAdv]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) larger than 1, estimated on the subset of SNPs observed with a predicted selection coefficient at the phylogenetic scale ($\Sphy$) larger than 0.
+        \item $\mathbb{P}_{mut}[S>0]$ is the proportion of mutational opportunities with a predicted selection coefficient at the phylogenetic scale ($\Sphy$) larger than 0.
+        \item $\mathbb{P}_{poly}[S>0]$ is the proportion of SNPs observed with a predicted selection coefficient at the phylogenetic scale ($\Sphy$) larger than 0.
+        \item $\mathbb{P}_{div}[S>0]$ is the proportion of substitution in the terminal branch observed with a selection coefficient at the phylogenetic scale ($\Sphy$) larger than 0.
+    \end{itemize}
+
+    \begin{center}
+        \begin{longtable}{|l|l|r|r|r|r|}
+            \toprule
+            Population           & Species             & Tajima $\theta_{\pi}$ & $\mathbb{P}_{mut}[S>1]$ & $\mathbb{P}_{poly}[S>1]$ & $\mathbb{P}_{div}[S>1]$ \\
+            \midrule
+            \endhead
+            \midrule
+            \multicolumn{6}{r}{{Continued on next page}} \\
+            \midrule
+            \endfoot
+
+            \bottomrule
+            \endlastfoot
+            Equus c.             & Equus caballus      & $ 0.002$              & $ 0.018$                & $ 0.098$                 & $ 0.113$                \\
+            Canis f.             & Canis familiaris    & $ 0.003$              & $ 0.014$                & $ 0.070$                 & $ 0.167$                \\
+            Iran                 & Bos taurus          & $ 0.005$              & $ 0.017$                & $ 0.111$                 & $ 0.105$                \\
+            Uganda               & Bos taurus          & $ 0.006$              & $ 0.017$                & $ 0.104$                 & $ 0.107$                \\
+            Australia            & Capra hircus        & $ 0.003$              & $ 0.017$                & $ 0.103$                 & $ 0.122$                \\
+            France               & Capra hircus        & $ 0.004$              & $ 0.017$                & $ 0.106$                 & $ 0.122$                \\
+            Iran (C. aegagrus)   & Capra hircus        & $ 0.004$              & $ 0.017$                & $ 0.103$                 & $ 0.123$                \\
+            Iran                 & Capra hircus        & $ 0.004$              & $ 0.017$                & $ 0.092$                 & $ 0.124$                \\
+            Italy                & Capra hircus        & $ 0.004$              & $ 0.017$                & $ 0.103$                 & $ 0.122$                \\
+            Morocco              & Capra hircus        & $ 0.004$              & $ 0.017$                & $ 0.079$                 & $ 0.124$                \\
+            Iran                 & Ovis aries          & $ 0.008$              & $ 0.018$                & $ 0.102$                 & $ 0.102$                \\
+            Iran (O. orientalis) & Ovis aries          & $ 0.009$              & $ 0.018$                & $ 0.107$                 & $ 0.099$                \\
+            Iran (O. vignei)     & Ovis aries          & $ 0.008$              & $ 0.018$                & $ 0.121$                 & $ 0.103$                \\
+            Various              & Ovis aries          & $ 0.009$              & $ 0.018$                & $ 0.114$                 & $ 0.100$                \\
+            Morocco              & Ovis aries          & $ 0.008$              & $ 0.018$                & $ 0.084$                 & $ 0.099$                \\
+            Barbados             & Chlorocebus sabaeus & $ 0.004$              & $ 0.015$                & $ 0.102$                 & $ 0.126$                \\
+            Central Afr. Rep.    & Chlorocebus sabaeus & $ 0.006$              & $ 0.015$                & $ 0.106$                 & $ 0.124$                \\
+            Ethiopia             & Chlorocebus sabaeus & $ 0.005$              & $ 0.015$                & $ 0.097$                 & $ 0.123$                \\
+            Gambia               & Chlorocebus sabaeus & $ 0.005$              & $ 0.015$                & $ 0.101$                 & $ 0.127$                \\
+            Kenya                & Chlorocebus sabaeus & $ 0.006$              & $ 0.015$                & $ 0.105$                 & $ 0.128$                \\
+            Nevis                & Chlorocebus sabaeus & $ 0.004$              & $ 0.015$                & $ 0.102$                 & $ 0.125$                \\
+            South Africa         & Chlorocebus sabaeus & $ 0.007$              & $ 0.015$                & $ 0.098$                 & $ 0.125$                \\
+            Saint Kitts          & Chlorocebus sabaeus & $ 0.004$              & $ 0.015$                & $ 0.099$                 & $ 0.126$                \\
+            Zambia               & Chlorocebus sabaeus & $ 0.006$              & $ 0.015$                & $ 0.104$                 & $ 0.123$                \\
+            African              & Homo sapiens        & $ 0.003$              & $ 0.015$                & $ 0.057$                 & $ 0.104$                \\
+            Admixed American     & Homo sapiens        & $ 0.002$              & $ 0.015$                & $ 0.058$                 & $ 0.103$                \\
+            East Asian           & Homo sapiens        & $ 0.002$              & $ 0.015$                & $ 0.052$                 & $ 0.104$                \\
+            European             & Homo sapiens        & $ 0.002$              & $ 0.015$                & $ 0.052$                 & $ 0.103$                \\
+            South Asian          & Homo sapiens        & $ 0.002$              & $ 0.015$                & $ 0.051$                 & $ 0.104$                \\
+        \end{longtable}
+    \end{center}
+    \begin{itemize}
+        \item Tajima $\theta$ is the synonymous diversity.
+        \item $\mathbb{P}_{mut}[S>1]$ is the proportion of mutational opportunities with a predicted selection coefficient at the phylogenetic scale ($\Sphy$) larger than 1.
+        \item $\mathbb{P}_{poly}[S>1]$ is the proportion of SNPs observed with a predicted selection coefficient at the phylogenetic scale ($\Sphy$) larger than 1.
+        \item $\mathbb{P}_{div}[S>1]$ is the proportion of substitution in the terminal branch observed with a selection coefficient at the phylogenetic scale ($\Sphy$) larger than 1.
     \end{itemize}

### 2022-06-23 manuscript/artworks/figures.tex
Mat & Met sister species

@@
 				height=0.5\textwidth,
-				ylabel={Relative fixation probability},
+				ylabel={$\frac{Q}{\mu} = \frac{S}{1 - \e^{-S}}$},
 				xlabel={Scaled selection coefficient ($S=4 \Ne s$)},
 				cycle list name=colors,
-				domain=-5:5,
+				domain=-10:10,
 				ymin=0.0, ymax=5.0,
@@
 				\addplot[line width=2.0pt, BLUE]{ x / (1 - exp(- x))};
-				\addplot[name path=B, dashed, YELLOW, line width=0.5pt] coordinates {(-1, 0) (-1, 5)};
-				\addplot[name path=A, line width=0pt] coordinates {(-5, 0) (-5, 5)};
+				\addplot[name path=B, dashed, YELLOW, line width=0.5pt] coordinates {(-1, 0) (-1, 10)};
+				\addplot[name path=A, line width=0pt] coordinates {(-10, 0) (-10, 10)};
 				\addplot[black, dashed, line width=1.0pt]{1.0};
-				\addplot[black, dashed, line width=1.0pt] coordinates {(0, 0) (0, 5)};
-				\addplot[name path=C, dashed, YELLOW, line width=0.5pt] coordinates {(1, 0) (1, 5)};
-				\addplot[name path=D, line width=0pt] coordinates {(5, 0) (5, 5)};
+				\addplot[black, dashed, line width=1.0pt] coordinates {(0, 0) (0, 10)};
+				\addplot[name path=C, dashed, YELLOW, line width=0.5pt] coordinates {(1, 0) (1, 10)};
+				\addplot[name path=D, line width=0pt] coordinates {(10, 0) (10, 10)};
 				\addplot[fill=RED, opacity=0.2] fill between[ of = A and B];
@@
 		\begin{dcases}
-			q_{\itoj} = \mu_{\itoj} & \text{for synonymous substitutions} \\
-			q_{\itoj} = \mu_{\itoj} \frac{F_j - F_i}{1 - \e^{ F_i - F_j}} & \text{for non-synonymous substitutions}\\
+			q_{\itoj} = \mu_{\itoj} & \text{if synonymous,} \\
+			q_{\itoj} = \mu_{\itoj} \frac{F_j - F_i}{1 - \e^{ F_i - F_j}} & \text{if non-synonymous.}\\
 		\end{dcases}

### 2022-06-23 manuscript/main.tex
Mat & Met sister species

@@
 
-    Protein-coding DNA sequences alignments in placental mammals are extracted from the \href{https://www.orthomam.univ-montp2.fr}{OrthoMaM} database\cite{ranwez_orthomam_2007, douzery_orthomam_2014, scornavacca_orthomam_2019}.
+    Protein-coding DNA sequences alignments in placental mammals and gene trees are extracted from the \href{https://www.orthomam.univ-montp2.fr}{OrthoMaM} database, containing $116$ mammalian reference sequences in v10c\cite{ranwez_orthomam_2007, douzery_orthomam_2014, scornavacca_orthomam_2019}.
     Genes located on the X, Y and mitochondrial chromosome are discarded from the analysis, since the number of polymorphism, necessary in population-based method, is expected to be different on these sequences.
     Additionally, sequences from the species for which polymorphism are available, as well as their sister species have been discarded from the analysis to ensure independence between the data used in the phylogenetic and population-genetic method.
+    Altogether, $14,509$ protein-coding DNA sequences alignment have been analyzed containing at most $87$ reference sequences of placental mammals per alignment.
 
@@
     We retrieved polymorphism from different projects.
-    \textit{Equus caballus} variants called on the EquCab2 assembly in the EVA study PRJEB9799.
-    \textit{Canis familiars} variants called on the CanFam3.1 assembly in the EVA study PRJEB24066.
-    \textit{Bos taurus} variants called on the UMD3.1 assembly in the next-gen project.
-    \textit{Ovis aries} variants called on the Oar\_v3.1 assembly in the next-gen project.
-    \textit{Capra Hircus} variants called on the CHIR1 assembly in the next-gen project, we performed a liftover to the ARS1 assembly.
-    \textit{Chlorocebus sabaeus} variants are called on the ChlSab1.1 assembly in the EVA study PRJEB22989\cite{svardal_ancient_2017}.
-    \textit{Homo sapiens} variants are called on the GRCh38 assembly in the 1000-genome project\cite{consortium_integrated_2012, the1000genomesprojectconsortium_global_2015}.
+    \textit{Equus caballus} variants called on the EquCab2 assembly in the EVA study PRJEB9799, we considered \textit{Ceratotherium simum simum} as its sister species.
+    \textit{Canis familiars} variants called on the CanFam3.1 assembly in the EVA study PRJEB24066, we considered \textit{Ursus maritimus} as its sister species.
+    \textit{Bos taurus} variants called on the UMD3.1 assembly in the next-gen project, we considered \textit{Bison bison bison} as its sister species.
+    \textit{Ovis aries} variants called on the Oar\_v3.1 assembly in the next-gen project, we considered \textit{Pantholops hodgsonii} as its sister species.
+    \textit{Capra Hircus} variants called on the CHIR1 assembly in the next-gen project, we performed a liftover to the ARS1 assembly and considered \textit{Pantholops hodgsonii} as its sister species.
+    \textit{Chlorocebus sabaeus} variants are called on the ChlSab1.1 assembly in the EVA study PRJEB22989\cite{svardal_ancient_2017}, we considered \textit{Macaca mulatta} as its sister species.
+    \textit{Homo sapiens} variants are called on the GRCh38 assembly in the 1000-genome project\cite{consortium_integrated_2012, the1000genomesprojectconsortium_global_2015}, we considered \textit{Pan troglodytes} as its sister species.
     Variants not inside genes are discarded at the beginning of the analysis.
@@
     For populations containing more than $8$ sampled individuals, the site-frequency spectrum (SFS) is subsampled down to $16$ chromosomes ($8$ diploid individuals) without replacement (hyper-geometric distribution) to alleviate the effect of different sampling depth in the $29$ populations.
-    SNPs are polarized using the $3$ closest out-groups found in the OrthoMam alignment with est-usfs\cite{keightley_inferring_2018}.
+    SNPs are polarized using the $3$ closest out-groups found in the OrthoMam alignment with est-usfs v2.04\cite{keightley_inferring_2018}.
     The Snakemake pipeline for integrating polymorphism and divergence data uses custom scripts written in python 3.9.

### 2022-07-08 manuscript/include-MutSel-non-adaptive.tex
D. Hartasanchez corrections. Epistasis discussion. Removed Canis Lupus (too much div to sister species).

@@
     \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.MutSel.pos.stacked.pdf}
-
 \end{center}
@@
 
-\subsubsection{Iran (IRBT)}
+\subsubsection{Iran}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Bos_taurus.IRBT.MutSel.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Bos_taurus.IRBT.MutSel-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Bos_taurus.IRBT.MutSel.pdf}
 \end{minipage}
@@
 
-\subsubsection{Uganda (UGBT)}
+\subsubsection{Uganda}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Bos_taurus.UGBT.MutSel.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Bos_taurus.UGBT.MutSel-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Bos_taurus.UGBT.MutSel.pdf}
 \end{minipage}
@@
 
-\subsection{Canis familiaris}
+\subsection{Capra}
+
+\subsubsection{Australia}
 
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Canis_familiaris.dogs.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.AUCH.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Canis_familiaris.dogs.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.AUCH.MutSel.histogram.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Canis_familiaris.dogs.MutSel.pdf}
-\end{minipage}
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Canis_familiaris.dogs.MutSel.polyDFE_C.pdf}
-\end{minipage}
-\\
-
-\subsection{Capra}
-
-\subsubsection{Australia (AUCH) - Capra hircus}
-
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.AUCH.MutSel.histogram.pdf}
-\end{minipage}
-\begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.AUCH.MutSel-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.AUCH.MutSel.pdf}
 \end{minipage}
@@
 
-\subsubsection{France (FRCH) - Capra hircus}
+\subsubsection{France}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.FRCH.MutSel.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.FRCH.MutSel-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.FRCH.MutSel.pdf}
 \end{minipage}
@@
 
-\subsubsection{Iran (IRCA) - Capra aegagrus}
+\subsubsection{Iran (C. aegagrus)}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.IRCA.MutSel.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.IRCA.MutSel-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.IRCA.MutSel.pdf}
 \end{minipage}
@@
 
-\subsubsection{Iran (IRCH) - Capra hircus}
+\subsubsection{Iran}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.IRCH.MutSel.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.IRCH.MutSel-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.IRCH.MutSel.pdf}
 \end{minipage}
@@
 
-\subsubsection{Italy (ITCH) - Capra hircus}
+\subsubsection{Italy}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.ITCH.MutSel.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.ITCH.MutSel-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.ITCH.MutSel.pdf}
 \end{minipage}
@@
 
-\subsubsection{Morocco (MOCH) - Capra hircus}
+\subsubsection{Morocco}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.MOCH.MutSel.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.MOCH.MutSel-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.MOCH.MutSel.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Barbados.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Barbados.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Barbados.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Barbados.MutSel.histogram.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Barbados.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Barbados.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 
-\subsubsection{Central African Republic (CAR)}
+\subsubsection{Central Afr. Rep.}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Central_African_Republic.MutSel.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Central_African_Republic.MutSel.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Ethiopia.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Ethiopia.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Ethiopia.MutSel.histogram.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Ethiopia.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Gambia.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Gambia.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Gambia.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Gambia.MutSel.histogram.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Gambia.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Gambia.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Kenya.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Kenya.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Kenya.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Kenya.MutSel.histogram.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Kenya.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Kenya.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Nevis.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Nevis.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Nevis.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Nevis.MutSel.histogram.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Nevis.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Nevis.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 
-\subsubsection{Saint Kitts (SK)}
+\subsubsection{Saint Kitts}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Saint_Kitts.MutSel.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Saint_Kitts.MutSel-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Saint_Kitts.MutSel.pdf}
 \end{minipage}
@@
 
-\subsubsection{South Africa (SA)}
+\subsubsection{South Africa}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.South_Africa.MutSel.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.South_Africa.MutSel-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.South_Africa.MutSel.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Zambia.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Zambia.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Zambia.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Zambia.MutSel.histogram.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Zambia.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Zambia.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Equus_caballus.up.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Equus_caballus.up.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Equus_caballus.up.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Equus_caballus.up.MutSel.histogram.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Equus_caballus.up.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Equus_caballus.up.MutSel-sfs.normalize.pdf}
 \end{minipage}
@@
 
-\subsubsection{African (AFR)}
+\subsubsection{African}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.AFR.MutSel.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.AFR.MutSel-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.AFR.MutSel.pdf}
 \end{minipage}
@@
 
-\subsubsection{Ad Mixed American (AMR)}
+\subsubsection{Admixed American}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.AMR.MutSel.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.AMR.MutSel-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.AMR.MutSel.pdf}
 \end{minipage}
@@
 
-\subsubsection{East Asian (EAS)}
+\subsubsection{East Asian}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.EAS.MutSel.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.EAS.MutSel-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.EAS.MutSel.pdf}
 \end{minipage}
@@
 
-\subsubsection{European (EUR)}
+\subsubsection{European}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.EUR.MutSel.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.EUR.MutSel-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.EUR.MutSel.pdf}
 \end{minipage}
@@
 
-\subsubsection{South Asian (SAS)}
+\subsubsection{South Asian}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.SAS.MutSel.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.SAS.MutSel-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.SAS.MutSel.pdf}
 \end{minipage}
@@
 
-\subsubsection{Iran (IROA) - Ovis aries}
+\subsubsection{Iran}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.IROA.MutSel.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROA.MutSel-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.IROA.MutSel.pdf}
 \end{minipage}
@@
 
-\subsubsection{Iran (IROO) - Ovis orientalis}
+\subsubsection{Iran (O. orientalis)}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.IROO.MutSel.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROO.MutSel-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.IROO.MutSel.pdf}
 \end{minipage}
@@
 
-\subsubsection{Iran (IROV) - Ovis vignei}
+\subsubsection{Iran (O. vignei)}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.IROV.MutSel.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROV.MutSel-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.IROV.MutSel.pdf}
 \end{minipage}
@@
 
-\subsubsection{Various (ISGC) - Ovis aries}
+\subsubsection{Various}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.ISGC.MutSel.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.ISGC.MutSel-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.ISGC.MutSel.pdf}
 \end{minipage}
@@
 
-\subsubsection{Morocco (MOOA) - Ovis aries}
+\subsubsection{Morocco}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.MOOA.MutSel.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.MOOA.MutSel-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.MOOA.MutSel.pdf}
 \end{minipage}

### 2022-07-08 manuscript/main.tex
D. Hartasanchez corrections. Epistasis discussion. Removed Canis Lupus (too much div to sister species).

--- 2022-06-17 manuscript/main.tex
@@
 \newcommand{\pfix}{\proba_{\mathrm{fix}}}
-
+\newcommand{\dn}{d_N}
+\newcommand{\ds}{d_S}
+\newcommand{\dnds}{\dn / \ds}
 \newcommand{\Sphy}{S}
@@
 
-\title{Empirical evidence for positive selection that is not adaptive evolution}
+\title{In mammals, 20 to 40\% of advantageous mutations are restoring damaged genomes instead of creating adaptive innovations}
 
@@
     $^{1}$Université de Lausanne, Lausanne, Switzerland\\
-    $^{1}$Université de Lyon, Lyon, France \\
+    $^{2}$Université de Lyon, Lyon, France \\
     \texttt{\href{mailto:thibault.latrille@ens-lyon.org}{thibault.latrille@ens-lyon.org}} \\
@@
     \begin{abstract}
-        Evidence for positive selection occurring in protein-coding DNA sequence is widespread across different taxa.
-        Positive selection can be a result of adaptive evolution, meaning that individuals have had to adapt to a change in environment or selective pressure.
-        However, recent positive selection can also be the result of mutations compensating for deleterious substitutions that have accumulated along lineages, in which case positive selection is non-adaptive.
-        To evaluate the extent of non-adaptive positive selection, we have combined population genetics and phylogenetic datasets.
-        We first leveraged phylogenetic codon models which are based on a population-genetics formalism, assuming a non-adaptive fitness landscape.
-        These models estimate the fitness of each of the 20 amino acids for each protein site, given mammalian protein-coding DNA alignments and gene tree topologies.
-        Second, we integrated mammalian divergence data with polymorphic variants found in 29 populations across 7 mammalian genera.
-        For each non-synonymous variant observed at the population level, we predicted its change in fitness from amino-acid fitnesses estimated at the mammalian scale.
-        We found that a large proportion of observed non-synonymous changes are predicted to be positively selected, meaning that the ancestral allele is suboptimal.
-        These supposedly advantageous variants are indeed showing signs of recent positive selection in all populations.
-        Our work confirms that deleterious substitutions have accumulated across the phylogeny and are currently being compensated for, resulting in widespread positive selection that is not adaptive evolution.
-        This study also shows the leverage obtained by integrating phylogenetic and population genetics on a common formalism.
+        Positive selection can be the result of adaptive evolution, driven by a change in environment or selective pressure.
+        However, positive selection can also be the result of compensatory positive selection where advantageous mutations are compensating for deleterious substitutions without any change of the environment.
+        The evolutionary outcomes of these two positive selections are drastically different.
+        While adaptive evolution acts as a diversifying force, compensatory positive selection stabilizes phenotypes and reduces diversity across species.
+        By leveraging polymorphism data in 28 populations and divergence data between 94 mammalian species, we estimate that 20 to 40\% of all new advantageous mutations are under compensatory positive selection.
+        Our work confirms that deleterious substitutions have accumulated in mammals and are currently being compensated for, resulting in widespread positive selection that is not adaptive evolution.
     \end{abstract}
 
-    \keywords{Selection \and phylogenetic \and population genetics \and codon models}
+    \keywords{Selection \and phylogenetic \and population genetics \and codon models \and adaptation }
 
@@
     The first scenario concerns environmental change.
-    The bearer of the mutation that is advantageous in a new environment will be better adapted. Hence, its chances of survival and reproduction will be higher.
+    The bearer of the mutation that is advantageous in a new environment will be better adapted, and its chances of survival and reproduction will be higher.
     This process is typically referred to as adaptive evolution.
-    The second scenario involves the fixation of a deleterious mutation by drift, in which case the mutation restores the ancestral state which corresponded to an optimal state of the individual.
-    This process is non-adaptive, in the sense that the increase in fitness of the new mutation is not in response to a new or a changing environment.
-    Instead, the mutation restores the ancestral state which corresponded to an optimal functioning of the individual in a constant environment, but has been lost due to the fixation of a deleterious mutation by drift.
-    Regarding the difference between these two scenarios at the population scale, while in the case of environmental change, the population as a whole is climbing the fitness landscape along an adaptive walk\cite{tenaillon_utility_2014}, in the case of
-    non-adaptive positive selection, the population as a whole is thus merely staying in the same position in fitness landscape at this equilibrium, and positive selection compensates for deleterious mutations that reach fixation due to drift\cite{sella_application_2005, mustonen_fitness_2009}.
+    The second scenario involves a mutation restoring the ancestral allele which corresponded to an optimal state of the individual in a constant environment, but has been lost due to the fixation of a deleterious mutation by drift.
+    Regarding the difference between these two scenarios at the population scale, while in the case of environmental change, the population as a whole is climbing the fitness landscape along an adaptive walk\cite{tenaillon_utility_2014}, in the case of non-adaptive positive selection, the population as a whole is thus merely staying in the same position in the fitness landscape at the mutation-selection equilibrium, and positive selection compensates for deleterious mutations that reach fixation due to drift\cite{sella_application_2005, mustonen_fitness_2009}.
     These two different kinds of selection result in a positive transmission bias of the advantageous allele, but their consequences are conceptually different.
-    While adaptive evolution promotes phenotype diversification, non-adaptive positive selection promotes phenotype stability and preserves well established biological systems.
+    While adaptive evolution promotes phenotype diversification, non-adaptive positive selection promotes phenotype stability and preserves well established biological systems (fig.~\ref{fig:fitness-landscape}).
     It is thus of importance to be able to distinguish those two kinds of positive selection in order to understand the diversification of species.
@@
     Second, each mutation is attributed a score to describe if it should be under purifying selection on one hand or be neutral or advantageous, on the other hand.
-    But this score makes little sense to actual measure of fitness, and is not interpretable in terms of population genetics.
+    However, this score makes little sense as an actual measure of fitness, and is not interpretable in terms of population genetics.
     At a finer scale, modelling at the codon level can disentangle processes of mutation at the DNA level and selection at the amino-acid level.
-    For example, so-called mutation-selection codon models are rooted with population genetics formalism\cite{halpern_evolutionary_1998, mccandlish_modeling_2014}.
+    For example, the so-called mutation-selection codon models are rooted within a population genetics formalism\cite{halpern_evolutionary_1998, mccandlish_modeling_2014}.
     Such models provide a nearly-neutral framework of evolution by estimating the fitness landscape over amino-acid sequences for each site of the sequence while taking into account non-adaptive processes impacting codon frequency\cite{halpern_evolutionary_1998, rodrigue_mechanistic_2010, tamuri_estimating_2012}.
@@
     As a consequence, by integrating datasets at the species and population level, we can estimate the selection coefficient for each mutation currently segregating in a population.
-    Such dataset can allow us to address different questions regarding positive selection affecting protein-coding DNA sequences.
-    Which proportion of the segregating polymorphism are predicted to be positively selected, from a suboptimal to a more optimal amino acid?
-    Are these polymorphism actually under ongoing positive selection at the scale of populations?
-    How does effective population size modulates positive, negative and weak selection?
+    Such a dataset can allow us to address different questions regarding positive selection affecting protein-coding DNA sequences.
+    Which proportion of the segregating polymorphisms are predicted to be positively selected, from a suboptimal to a more optimal amino acid?
+    Are these polymorphisms actually under ongoing positive selection at the scale of populations?
     Finally, how much of the recent substitutions are due to non-adaptive positive selection?
 
-    \begin{figure*}[!ht]\
+    \begin{figure*}[!ht]
+        \
         \centering
-    \includegraphics[width=\textwidth, page=1] {artworks/figure1}
+        \includegraphics[width=\textwidth, page=1] {artworks/figure.fitness-landscape}
+        \caption{
+            Panel A and B: at a given site inside a protein-coding DNA sequence, the different amino acids (x-axis) have different fitnesses (y-axis).
+            Under a fluctuating fitness landscape (panel A), these fitnesses are changing with time.
+            The protein sequence is always lagging behind the moving target defined by the amino acid fitnesses, and since substitutions are accepted preferentially if they are in the direction of this target, substitutions are on average adaptive.
+            At the phylogenetic scale (panel C), this phenomena promotes phenotype diversification across species.
+            Under a static fitness landscape (panel B), the protein sequence only fluctuates at the mutation-selection balance.
+            All the mutations reaching fixation are either slightly deleterious and reaching fixation due to drift or are advantageous and restoring a more optimal amino acid.
+            At the phylogenetic scale (panel D), this phenomena promotes promotes phenotype stability and preserves well established biological systems.
+        }
+        \label{fig:fitness-landscape}
+    \end{figure*}
+
+    \begin{figure*}[!ht]
+        \
+        \centering
+        \includegraphics[width=\textwidth, page=1] {artworks/figure.method}
         \caption{
             Integrating divergence and polymorphism.
-        At the phylogenetic level (panel A), amino-acid Wrightian fitness for each site are estimated from protein-coding DNA alignments using mutation-selection codon models.
-        At the population-genetic level (panel B), for each observed single nucleotide polymorphism (SNP) segregating in the population, selection coefficient are computed as the difference in amino-acid fitness between the ancestral and derived variant.
+            At the phylogenetic level (panel A), the amino-acid Wrightian fitness for each site is estimated from protein-coding DNA alignments using mutation-selection codon models.
+            At the population-genetic level (panel B), for each observed single nucleotide polymorphism (SNP) segregating in the population, selection coefficient are computed as the difference in amino-acid fitness between the ancestral and derived variants.
         }
@@
 
-    For this we used available multiple sequence alignment between mammalian species\cite{ranwez_orthomam_2007, howe_ensembl_2021} to estimate fitness landscape on long-term evolution.
-    We developed and leveraged a pipeline integrating divergence and polymorphism data across the entire exome for 29 populations across 7 genera, namely \textit{Equus}, \textit{Canis}, \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus} and \textit{Homo} (fig.~\ref{fig:method}).
-    For each non-synonymous SNP observed at the population level, we predicted its scaled selection coefficient ($\Sphy$) in fitness from amino-acid fitness estimated at the mammalian scale (fig.~\ref{fig:homo-afr-results}A).
-    Then we ask whether the variants that are supposedly advantageous are showing signature of short term positive selection.
-    In other words, if a variant is found in many mammals but not in ancestral humans, and a mutation in humans is toward the mammalian version, is this mutation advantageous for the individual carrying it?
+    To answer these questions, we have estimated a fitness landscape for long-term evolution using available multiple sequence alignments between mammalian species\cite{ranwez_orthomam_2007, howe_ensembl_2021}.
+    We then developed and leveraged a pipeline integrating divergence and polymorphism data across the entire exome for 28 populations across 6 genera, namely \textit{Equus},  \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus} and \textit{Homo} (fig.~\ref{fig:method}).
+    For each non-synonymous SNP observed at the population level, we predicted its scaled selection coefficient ($\Sphy$) from amino-acid fitnesses estimated at the mammalian scale (fig.~\ref{fig:homo-afr-results}A).
+    Then we ask whether the variants that are supposedly advantageous are showing signatures of short term positive selection.
+    For example, if a variant is found to be fixed in many mammals but not in ancestral humans, and a mutation in humans is toward the mammalian version, is this mutation advantageous for the individual carrying it?
     At the population level (e.g.
-in humans with Asian descent in fig.~\ref{fig:homo-afr-results}), we divided all observed SNPs in 5 classes of predicted selection coefficient: severely deleterious with $\divStrongDel$, deleterious with $\divDel$, weakly deleterious with $\divWeakDel$, weakly advantageous with $\divWeakAdv$ and advantageous with $\divAdv$.
-    For each class of selection, SNPs are then grouped by the number of derived alleles in the population (fig.~\ref{fig:homo-afr-results}B), generating so called site-frequency spectrum (SFS).
-    Compared to synonymous mutations supposedly neutral (black line in fig.~\ref{fig:homo-afr-results}B), mutations predicted to be deleterious (blue and green lines in fig.~\ref{fig:homo-afr-results}B) are underrepresented at high frequency in the population, a signature of ongoing purifying selection.
-    Remarkably, SNPs predicted to be advantageous (red line in fig.~\ref{fig:homo-afr-results}B) are over-represented at higher frequency in the population, meaning they are more likely to reach fixation as a consequence of ongoing positive selection.
+in humans of Asian descent in fig.~\ref{fig:homo-afr-results}), we divided all observed SNPs in 5 classes of predicted selection coefficient: severely deleterious with $\divStrongDel$, deleterious with $\divDel$, weakly deleterious with $\divWeakDel$, weakly advantageous with $\divWeakAdv$ and advantageous with $\divAdv$.
+    In each of theses classes, SNPs are then grouped by the number of derived alleles in the population (fig.~\ref{fig:homo-afr-results}B), generating a so called site-frequency spectrum (SFS).
+    Compared to synonymous mutations which are supposedly neutral (black line in fig.~\ref{fig:homo-afr-results}B), mutations predicted to be deleterious (blue and green lines in fig.~\ref{fig:homo-afr-results}B) are underrepresented at high frequencies in the population, a signature of ongoing purifying selection.
+    Remarkably, SNPs predicted to be advantageous (red line in fig.~\ref{fig:homo-afr-results}B) are overrepresented at higher frequencies in the population, meaning they are more likely to reach fixation as a consequence of ongoing positive selection.
     However, these observations remain qualitative.
-    Thus, we quantified the distribution of selection coefficient for each category of SNPs with the model polyDFE\cite{tataru_inference_2017, tataru_polydfe_2020}.
-    The model uses the count of derived allele for each frequency class of the SFS to infer the distribution of fitness effects (DFE) of the region under study.
-    For each category of SNPs, it is important to compute the expected number of mutations giving birth to a SNP of that category given a mutational matrix (fig.~\ref{fig:homo-afr-results}C).
-    The model uses both the mutational expectation for each category, and the counts of synonymous derived allele as a neutral model, which allow to control for demographic effects, and polarization errors when inferring the ancestral state.
-    These populations based models cannot give a specific estimate of $\Spop$ for each SNP, but by gathering information across many SNPs, these models can estimate the proportion of advantageous mutations ($\PpolyAdv$), of nearly-neutral mutations ($\PpolyNeutral$) and of deleterious mutations ($\PpolyDel$) (fig.~\ref{fig:homo-afr-results}D).
+
+    To obtain a quantitative estimate of the distribution of selection coefficient for each category of SNPs, we used the model polyDFE\cite{tataru_inference_2017, tataru_polydfe_2020}.
+    This model uses the count of derived alleles for each frequency class of the SFS to infer the distribution of fitness effects (DFE) of the region under study.
+    The model uses both the mutational expectation for each category (fig.~\ref{fig:homo-afr-results}C) (see Material and Methods), and the counts of synonymous derived allele as a neutral model, which allow to control for demographic effects, and polarization errors when inferring the ancestral state.
+    These population-based models cannot give a specific estimate of the selection coefficient at the population-genetic scale ($\Spop$) for each SNP, but by gathering information across many SNPs, these models can estimate the proportion of advantageous mutations ($\PpolyAdv$), of nearly-neutral mutations ($\PpolyNeutral$) and of deleterious mutations ($\PpolyDel$) (fig.~\ref{fig:homo-afr-results}D).
     We found that SNPs predicted to be deleterious given their selection coefficient $\Sphy$ across mammals are effectively purged at the population-genetic scale, demonstrating that purifying selection is largely predictable and amino acids with low fitness across mammals are effectively purged away in each population.
@@
 
-    We replicated such experiment across 29 populations (fig.~\ref{fig:all-pop-results}), and found that mutations predicted to be deleterious are indeed purged at the population-genetic scale (blue and green rows in fig.~\ref{fig:all-pop-results}A).
-    However, mutation predicted to be weakly advantageous ($\divWeakAdv$) are composed of a mix of neutral and selected mutations with varying proportions across the different populations (orange row in fig.~\ref{fig:all-pop-results}B).
-    Similarly, mutations predicted to be advantageous are found to be positively selected with varying proportions (red row in fig.~\ref{fig:all-pop-results}C).
-    A variable which could explain those variations between populations is the effective number of individuals in the population ($\Ne$), a major driver of selection efficacy.
-    $\Ne$ is not directly accessible, and a reasonable proxy usually used is the synonymous diversity ($\theta=4\Ne\mu$ with $\mu$ the mutation rate).
-    We thus ordered populations by increased synonymous diversity (fig.~\ref{fig:selcoeff-pop-phylo}A), exhibiting a decreased proportion of neutral mutations.
-    This result suggest that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) are more likely to discriminate whether mutations are advantageous or deleterious.
+    We replicated such experiment across 28 populations (fig.~\ref{fig:heatmap}), and found that mutations predicted to be deleterious are indeed purged at the population-genetic scale (blue and green rows in fig.~\ref{fig:heatmap}A).
+    However, mutations predicted to be weakly advantageous ($\divWeakAdv$) are composed of a mix of neutral and selected mutations with varying proportions across the different populations (orange row in fig.~\ref{fig:heatmap}B).
+    Similarly, mutations predicted to be advantageous are found to be positively selected with varying proportions across populations (red row in fig.~\ref{fig:heatmap}C).
+    These variable proportions between populations can be explained by the effective number of individuals in the population ($\Ne$), a major driver of selection efficacy.
+    Since $\Ne$ is not directly measurable, a reasonable proxy usually used is the synonymous diversity (see material and methods).
+    We thus ordered populations by their levels of synonymous diversity (fig.~\ref{fig:diversity}A) and confirmed that higher synonymous diversity is usually accompanied by a smaller proportion of neutral mutations.
+    This result suggests that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) are more likely to discriminate whether mutations are advantageous or deleterious.
     Alternatively stated, mutations in populations with low diversity (e.g.~\textit{Homo}) are effectively nearly-neutral and behave as would a neutral mutation.
-    This result is qualitatively in accordance with the nearly-neutral theory of evolution that mutations are less efficiently selected for small populations.
-    Moreover, we found this effect to be in the same direction but less pronounced when we focused on all SNPs (fig.~S1) rather than only the SNPs predicted to be weakly selected (fig.~S2-3).
-    To look further into the relation between diversity and selection efficacy, we thus studied the estimation of the mean $\SpopMean$ as a function of the mean $\SphyMean$ for a subset of SNPs, for which $\SphyMean$ is close to $0$.
-    Indeed, polyDFE is a nearly neutral model and is not able to reliably compute selection coefficients for only strongly deleterious or only strongly advantageous SNPs.
-    Sliding window of groups of $5.000$ SNPs are taken with a mean $\SphyMean$ between $-0.5$ and $0.5$ (fig.~\ref{fig:selcoeff-pop-phylo}B).
-    $\SpopMean$ is estimated for each group, with some groups that might have part of same SNPs that overlap.
-    The relationship between $\SpopMean$ and $\SphyMean$ is described as a second-order polynomial, and the slope of this polynomial at $\SphyMean=0$ gives the ratio $\SpopMean/\SphyMean$ for each population.
-    We observe that $\SpopMean/\SphyMean$, representing the efficacy of selection at the short versus long-term is positively correlated with synonymous diversity (fig.~\ref{fig:selcoeff-pop-phylo}C), a proxy of effective population size.
-    Altogether, populations with large effective population size are under more efficient selection, confirming the prediction of the nearly-neutral theory of evolution.
-    As a consequence of increased selection efficacy, mutations in populations with high diversity are mechanically more likely to be deleterious (fig.~S4), especially for mutations predicted already to be deleterious at the phylogenetic scale (fig.~S5-6).
+    This result is qualitatively in accordance with the nearly-neutral theory of evolution which argues that mutations are less efficiently selected for in small populations.
 
-    Finally, we computed the proportion of substitutions in the terminal branches that were predicted to be under positive selection ($\Sphy > 0$).
-    To this aim, for each population with polymorphism data available, we reconstructed the ancestral sequences before the last genus split in the tree.
-    In these populations, we show that out of all polarized substitutions in the branches, between 22 and 42\% of all substitutions are under $\Sphy > 0$ (table S1).
-    This proportion must be compared to the estimated probability of a mutation to be positively selected ($\Spop > 0$), which is between 4.8 and 11.3\%(table S1).
-    As a result, these observed substitutions are likely to have been positive selected because they restored the state which corresponded to an optimal state of the population.
-    Statistically, genomes are thus involved in a tug-of-war between a large volume deleterious mutations that eventually reach fixation due to drift, and scarce advantageous mutations that are repairing ancestral deleterious substitutions.
-    Taking into account that observed substitutions are likely to be due to positive selection that is not adaptive is thus crucial if one seek to estimate the proportion of adaptation while relying on substitutions between close species\cite{mcdonald_adaptative_1991}.
+    Finally, we reconstructed the substitutions in the terminal branches of the phylogenetic tree in order to determine the distribution of their selection coefficients.
+    To this aim, for each population with polymorphism data available, we first reconstructed the ancestral sequence (which is different than the reference sequence), then we mapped the substitutions from the last genus split to this reconstructed ancestral sequence.
+    In these populations, we show that out of all polarized substitutions in the branches, between 10 and 17\% of all substitutions have an $\Sphy > 1$ (table S1) and between 22 and 42\% of all substitutions have an $\Sphy > 0$ (table S2).
+    Most importantly, there is clear signal that the substitutions with an $\Sphy > 1$ have been positively selected since their ratio of non-synonymous over synonymous divergence, a ratio called $\dnds$, is between 1.05 and 1.81 in the different populations (table S1), meaning that mutations with $\Sphy > 1$ reach fixation more frequently that synonymous mutations (supposedly neutral).
+    %This also means that the ratio $\dnds$ usually used to detect adaptation while relying on substitutions between close species\cite{mcdonald_adaptative_1991, galtier_adaptive_2016} or at the phylogenetic scale\cite{goldman_codonbased_1994, yang_codonsubstitution_2002} is overestimated.
+    These observed substitutions are likely to have been positive selected because they restored a more optimal state, not because they are driving innovations to a new environment or a function.
+    %Altogether, we estimated that between 18 and 39\% of $\dnds$ is over-estimated (table S1), corresponding to non-adaptive positive selection.
+    In a nearly neutral framework, genomes could be viewed as the arena of a tug-of-war between a large volume of deleterious mutations that eventually reach fixation due to drift, and scarce advantageous mutations that are restoring a more optimal ancestral state.
     % However, and surprisingly, a decrease in the proportion of neutral mutation did not translate into a mechanical increase in the proportion of advantageous mutations.
-    % Instead, populations with higher diversity have a lower proportion of advantageous mutations (fig.~S7), this effect is also more pronounced for mutations predicted to be advantageous at the phylogenetic scale (red row in fig.~\ref{fig:all-pop-results}C and fig.~S8).
+    % Instead, populations with higher diversity have a lower proportion of advantageous mutations (fig.~S7), this effect is also more pronounced for mutations predicted to be advantageous at the phylogenetic scale (red row in fig.~\ref{fig:heatmap}C and fig.~S8).
     % This discrepancy can be explained by the fact that populations with larger diversity have already depleted the putatively advantageous mutations, and that only deleterious are remaining possible.
@@
         \centering
-        \includegraphics[width=\textwidth, page=1] {artworks/figure2}
+        \includegraphics[width=\textwidth, page=1] {artworks/figure.homo-afr-results}
         \caption{
-            Panel A: Histogram of predicted selection coefficient ($\Sphy$) for each observed mutation in a sample of 8 individuals (out of 512 in the original dataset) with African descent.
-            Mutations are divided in 5 classes of selection: severely deleterious (blue), deleterious (green), weakly deleterious (light green), weakly advantageous (yellow) and advantageous (red).
-            Panel B: Site-frequency spectrum (SFS) represents the proportion of mutations (y-axis) with a given number of derived alleles in the population (x-axis).
-            SFS are drawn for a random sample of 16 alleles (mean in solid line and standard deviation in filled color) for each class of selection and for synonymous mutations supposedly neutral (black).
-            Supposedly advantageous are over-represented at higher frequency, while severally deleterious are underrepresented at high frequency, a signature of selection.
-            Panel C. Histogram of predicted selection coefficient ($\Sphy$) for each possible mutation away from the ancestral human genome, weighted by the mutation rate.
-            For each class of selection, the sum of histogram in this class thus gives the expected total mutation rate toward this class.
+            Panel A: Histogram of predicted selection coefficients ($\Sphy$) for all possible mutations away from the ancestral human genome, weighted by the mutation rate.
+            Mutations are divided into 5 classes: severely deleterious (blue), deleterious (green), weakly deleterious (light green), weakly advantageous (yellow) and advantageous (red).
+            Panel B. Histogram of predicted selection coefficients ($\Sphy$) for all observed mutations in a sample of 8 individuals (out of 512 in the original dataset) of African descent.
             If they are less mutations observed than expected, this class is thus undergoing purifying selection.
+            Panel B: The site-frequency spectrum (SFS) represents the proportion of mutations (y-axis) with a given number of derived alleles in the population (x-axis).
+            SFS are drawn for a random sample of 16 alleles (mean in solid line and standard deviation in filled color) for each class of selection coefficient and for synonymous mutations which are supposedly neutral (black).
+            At high frequencies, supposedly severally deleterious mutations are underrepresented.
             Panel D.
@@
         \centering
-        \includegraphics[width=\textwidth, page=1] {artworks/figure3}
+        \includegraphics[width=\textwidth, page=1] {artworks/figure.heatmap}
         \caption{
-            Reproducibility of results shown in figure~\ref{fig:homo-afr-results} in 29 populations across 7 genera.
-            Site-frequency spectra and total mutation rates are combined at the population-genetic scale to estimate the proportion of advantageous mutations ($\PpolyAdv$) in top panel, of nearly-neutral mutations ($\PpolyNeutral$) in middle panel and of deleterious mutations ($\PpolyDel$) in bottom panel.
+            Reproducibility of results shown in figure~\ref{fig:homo-afr-results} in 28 populations across 6 genera.
+            Site-frequency spectra and total mutation rates are combined at the population-genetic scale to estimate the proportion of advantageous mutations ($\PpolyAdv$) in the top panel, of nearly-neutral mutations ($\PpolyNeutral$) in the middle panel and of deleterious mutations ($\PpolyDel$) in the bottom panel.
         }
-        \label{fig:all-pop-results}
+        \label{fig:heatmap}
     \end{figure*}
@@
         \centering
-        \includegraphics[width=\textwidth, page=1] {artworks/figure4}
+        \includegraphics[width=\textwidth, page=1] {artworks/figure.diversity}
         \caption{
             Panel A.
-For each population, proportion of advantageous ($\PpolyAdv$), nearly-neutral ($\PpolyNeutral$) and of deleterious ($\PpolyDel$) mutations estimated at the population-genetic scale.
+For each population, the proportion of advantageous ($\PpolyAdv$), nearly-neutral ($\PpolyNeutral$) and of deleterious ($\PpolyDel$) mutations estimated at the population-genetic scale is shown.
             Estimation is performed with SNPs predicted to be weakly advantageous at the phylogenetic scale ($\divWeakAdv$).
             Panel B. Mean selection coefficient at the population scale $\SpopMean$ as a function of phylogenetic $\SphyMean$.
-            Observed SNPs are sorted and groups of $5.000$ SNPs are taken as a sliding window with increasing mean $-0.5 \leq \SphyMean \leq 0.5$.
+            Observed SNPs are sorted and groups of $5,000$ SNPs are taken as a sliding window with increasing mean $-0.5 \leq \SphyMean \leq 0.5$.
             For each group along the sliding window, $\SpopMean$ (y-axis) is estimated based on SFS and the total mutation rate, and compared to the mean $\SphyMean$ (x-axis).
-            A second order polynomial is fitted for each population, and the slope of this polynomial at $\SphyMean=0$ gives the ratio $\SpopMean/\SphyMean$ given in legend.
-            Panel C. Ratio $\SpopMean/\SphyMean$ as a function of the synonymous diversity for each population.
-            Populations with higher diversity are showing higher ratio of ratio $\SpopMean/\SphyMean$.
+            A second order polynomial is fitted for each population, and the slope of this polynomial at $\SphyMean=0$ gives the ratio $\SpopMean/\SphyMean$, specified in the legend as $f'(0)$ estimates.
+            Panel C. $\SpopMean/\SphyMean$ ratio as a function of the synonymous diversity for each population.
+            Populations with higher diversity show a higher $\SpopMean/\SphyMean$ ratio.
         }
-        \label{fig:selcoeff-pop-phylo}
+        \label{fig:diversity}
     \end{figure*}
 
+    Biologically, another repairing mechanism is compensatory mutations, which are repairing damage caused by deleterious mutations at another site in the genome and generating a widespread signal of non-adaptive positive selection\cite{hartl_compensatory_1996, pollock_strong_2014, starr_epistasis_2016}.
+    In our study we focused on mutations restoring the more optimal ancestral state at a given site, not accounting for compensatory mutations since we assumed a model of fitness landscape without epistasis, providing a reasonable estimate of average fitness profiles\cite{youssef_consequences_2020}.
+    But most importantly, we argue that our estimation of the amount of non-adaptive positive selection is an underestimation, and that accounting for compensatory mutations by means of epistasis would mechanically increase that amount.
+    Indeed, a fluctuating fitness landscape due to an external forces (e.i.
+changes in environment) results in an acceleration of the rate of evolution\cite{ rodrigue_detecting_2017, rodrigue_bayesian_2021} which generates epistatic mutations that are immediately beneficial\cite{gong_epistatically_2014}.
+    On the contrary, pervasive epistasis generates the opposite, an entrenchment\cite{goldstein_evolutionary_2004, goldstein_nonadaptive_2015} resulting in a slowing down of the rate evolution\cite{rodrigue_detecting_2017, patel_epistasis_2022} or a standstill\cite{youssef_evolution_2022}.
+    In other words, under pervasive epistasis, finding empirical evidence for restoring mutations is harder since restoring mutations becomes less and less likely to occur over time\cite{goldstein_nonadaptive_2015, goldstein_sequence_2017, park_epistatic_2022}.
+    Our study thus shows that restoring mutations should instead not be overlooked, and we argue that both restoring and compensatory mutations play an important role to avoid our genome to collapse under a mutation load.
+
     % Our study is a bridge between phylogenetic and population genetics
-    From a theoretical evolution perspective, we found that we could use phylogenetic signal to predict the selection coefficient of a mutation.
-    Apart from phylogenetic mutation-selection codon models, SIFT scores based on amino-acid alignments across species have already been found to be informative of the selection pressure exerted at the population scale\cite{chen_hunting_2021}.
-    Our study concur in that direction, that sites with higher SIFT score at the phylogenetic scale are more positively selected in the different populations (supp.\ mat\  section 2).
-    In practice, SIFT score are more coarse grained, with for example a bulk a mutations with a score of 1.0 (the highest), and does not provide a boundary between advantageous and deleterious mutations.
-    Moreover, they are not based on population-genetics formalism, hence the relationship between selection coefficient and SIFT score is not straightforward.
-    Alternatively at the DNA level, $\omega$-based codon model use the ratio of non-synonymous over synonymous substitution as signature of selection\cite{goldman_codonbased_1994, yang_codonsubstitution_2002}, taking into account the mutational bias and the underlying phylogeny.
-    We also show that sites with higher $\omega$ are more positively selected in the different populations (supp.\ mat\  section 3).
-    However, even sites which are supposedly under pervasive positive selection at the phylogenetic scale ($\omega>1$) are not necessarily positively selected in the populations.
-    Most importantly, such models do not leverage the information of the source and target amino acid involve in the mutation, and thus cannot be used to estimate the non-adaptive part of positive selection.
-    Altogether, we showed that mutation-selection codon models formalize a bridge between phylogenetics and population genetics models, but both ends has its limitation and could be improved.
+    From a theoretical evolution perspective, we have found that we can use phylogenetic signals and mutation-selection codon models to predict the selection coefficient of a mutation.
+    However, we so far assumed no changes in effective population size while it has been established that population size changes have a major effect on selection dynamics\cite{lanfear_population_2014, jones_shifting_2017, platt_protein_2018}.
+    Estimating effective population sizes along with fitness landscapes is possible\cite{latrille_inferring_2021}, but is, for the moment, too computational intensive to be performed genome-wide\cite{latrille_inferring_2021}.
+    Hybrid mutation-selection and $\omega$-based codon models could provide a way forward\cite{brevet_reconstructing_2021}.
+    Moreover, SIFT scores based on amino-acid alignments across species have also been found to be informative of the selection pressure exerted at the population scale\cite{chen_hunting_2021}.
+    Accordingly, our study shows that sites with a higher SIFT score at the phylogenetic scale are more positively selected in the different populations (supp.\ mat\  section 2).
+    In practice, SIFT scores are more coarse grained, with for example a bulk of mutations with a score of 1.0 (the highest), and does not provide a boundary between advantageous and deleterious mutations, nor are they based on a population-genetics formalism.
 
-    % Problem with the current mutation-selection model, and the way forward
-    Phylogenetic codon models make two assumptions which have a negative impact on the prediction of the selection coefficient.
-    First, they are assuming no changes in effective population size while it has been established that population size has a major effect on selection dynamics\cite{lanfear_population_2014, platt_protein_2018}.
-    Estimating effective population size along with fitness landscape is possible\cite{latrille_inferring_2021}, but is for the moment too computational intensive to be performed genome-wide\cite{latrille_inferring_2021}.
-    Hybrid mutation-selection and $\omega$-based codon model could provide a way forward\cite{brevet_reconstructing_2021}.
-    Second, epistasis is not modeled while it can have drastic consequences on the change in fitness landscape\cite{latrille_quantifying_2021}.
-    Some models using Direct Coupling Analysis (DCA) can infer coevolution between sites, and thus provide a score of fitness of an amino-acid which depends on other sites of the sequence\cite{bisardi_modeling_2022}.
-    However, as SIFT scores, the scores given by DCA are not formalized in terms of selection coefficient and thus are hard to interpret in terms of population genetics, while also neglecting the underlying phylogeny and mutational biases.
-    Relaxing both assumptions are computationally intensive\cite{rodrigue_site_2005, kleinman_statistical_2010,latrille_inferring_2021}, and would require new mutation-selection models and optimization techniques to be able to manipulate genome-wide datasets.
-    In the other hand, in population-genetic codon models, there is no consensus on the expected shape of the DFE\cite{welch_divergence_2008, bataillon_effects_2014}, but it has indeed be found to be reliably constant between species\cite{castellano_comparison_2019}.
-    The model we used allows the inference of a full DFE (both positive and negative), but it has chosen to model the negative part of the DFE as a gamma distribution, and as an exponential one for the positive part.
-    However, when we aggregate SNPs that are expected to be strongly deleterious or strongly advantageous, the model struggles to fit their DFE to a gamma or an exponential distribution.
+    %Second, epistasis is not modelled while it can have drastic consequences on the change in fitness landscape\cite{latrille_quantifying_2021}.
+    %Some models using Direct Coupling Analysis (DCA) can infer coevolution between sites, and thus provide a fitness score for amino acids which depends on other sites of the sequence\cite{bisardi_modeling_2022}.
+    %However, as SIFT scores, the scores given by DCA are not formalized in terms of selection coefficients and thus are hard to interpret in terms of population genetics, while also neglecting the underlying phylogeny and mutational biases.
+    %Relaxing both assumptions are computationally intensive\cite{rodrigue_site_2005, kleinman_statistical_2010}, and would require new mutation-selection models and optimization techniques to be able to manipulate genome-wide datasets..
+
+    % Alternatively at the DNA level, $\omega$-based codon model use the ratio of non-synonymous over synonymous substitution as signature of selection\cite{goldman_codonbased_1994, yang_codonsubstitution_2002}, taking into account the mutational bias and the underlying phylogeny.
+    % We also show that sites with higher $\omega$ are more positively selected in the different populations (supp.\ mat\  section 3).
+    % However, even sites which are supposedly under pervasive positive selection at the phylogenetic scale ($\omega>1$) are not necessarily positively selected in the populations.
+    %Most importantly, such models do not leverage the information of the source and target amino acid involve in the mutation, and thus cannot be used to estimate the non-adaptive part of positive selection.
+    %Altogether, we here show that mutation-selection codon models formalize a bridge between phylogenetics and population genetics models, but both ends have its limitation and could be improved.
+
+    In population genetics, models also have shortcomings, such that there is no consensus on the expected shape of the DFE\cite{welch_divergence_2008, bataillon_effects_2014}, but it has indeed been found to be reliably constant between species\cite{castellano_comparison_2019}.
+    The model we used allows the inference of a full DFE, modelling the negative part of the DFE as a gamma distribution, and the positive part as an exponential distribution.
+    However, when we aggregate SNPs that are expected to be strongly deleterious or strongly advantageous, the model struggles to fit their DFE to a gamma or an exponential distribution.\cite{brevet_reconstructing_2021}
     As a result, while the proportions of negative/weak/positive mutations stays reliable, the mean values for selection coefficients ($\Spop$) estimated by polyDFE become biologically absurd ($\Spop \ll -10^3$).
-    Such effect is not found for neutral SNPs and to method to accurately estimate the mean value of selection coefficients from SFS without assuming any shape for the DFE remains yet to be available.
-
+    Such effect is not found for neutral SNPs and a method to accurately estimate the mean value of selection coefficients from SFS without assuming any shape for the DFE remains yet to be available.
     Aside from methodological limitations, the mammalian case study might also not be representative of other clades.
-    Indeed, our dataset is quite convenient because mammals have relatively small population sizes, which allow large amount of deleterious mutations to be fixed, and thus, there is a lot of opportunities for non-adaptive positive selection to arise.
-    It would thus be of great interest to reproduce our experiment with other clades, such as \textit{drosophila} or birds which have higher effective population size.
+    Indeed, our dataset is quite convenient because mammals have relatively small population sizes, which allow large amount of deleterious mutations to be fixed, and thus, there are a lot of opportunities for non-adaptive positive selection to arise.
+    It would thus be of great interest to reproduce our experiment with other clades, such as \textit{Drosophila} or birds which tend to have higher effective population size.
     It would also be interesting to have access to more shallow but wider phylogenies to increase the resolution of our predictions.
@@
 
-    From a structural biology perspective, we found that proteins are not optimal for their fitness, which has been proved for their kinetics and thermodynamics.
-    We argue that mutation-selection models are thus a mandatory tool in evolutionary biology to detect and quantify adaptation since they genuinely take into account the tug-of-war between scarce advantageous mutations likely to reach fixation and a bulk of deleterious mutations eventually reaching fixations due to their sheer mass.
+    From a structural biology perspective, we have found that proteins are not optimal for their fitness, which has been proved for their kinetics and thermodynamics\cite{taverna_why_2002, goldstein_evolution_2011}.
+    We argue that mutation-selection models are thus a mandatory tool in evolutionary biology to detect and quantify adaptation since they genuinely take into account the tug-of-war between scarce advantageous mutations likely to reach fixation and a bulk of deleterious mutations eventually reaching fixation due to their sheer mass.
     Indeed, these models can be used as a null model to predict the overall rate of evolution of proteins\cite{spielman_relationship_2015, dosreis_how_2015}.
@@
 
-    \section*{Acknowledgment}
+    \section*{Acknowledgments}
     \label{sec:acknowledgment}
@@
     \textit{Equus caballus} variants called on the EquCab2 assembly in the EVA study PRJEB9799.
-    \textit{Canis familiars} variants called on the CanFam3.1 assembly in the EVA study PRJEB24066.
     \textit{Bos taurus} variants called on the UMD3.1 assembly in the next-gen project.
@@
     Stop codon mutants are also discarded.
-    For populations containing more than $8$ sampled individuals, the site-frequency spectrum (SFS) is subsampled down to $16$ chromosomes ($8$ diploid individuals) without replacement (hyper-geometric distribution) to alleviate the effect of different sampling depth in the $29$ populations.
-    SNPs are polarized using the $3$ closest out-groups found in the OrthoMam alignment with est-usfs\cite{keightley_inferring_2018}.
+    SNPs are polarized using the $3$ closest outgroups found in the OrthoMam alignment with est-usfs v2.04\cite{keightley_inferring_2018}.
+    For populations containing more than $8$ sampled individuals, the site-frequency spectrum (SFS) is subsampled down to $16$ chromosomes ($8$ diploid individuals) without replacement (hyper-geometric distribution) to alleviate the effect of different sampling depth in the 28 populations.
     The Snakemake pipeline for integrating polymorphism and divergence data uses custom scripts written in python 3.9.
+
+    \subsection*{Substitution mapping in the terminal branch}
+
+    For each population with polymorphism data available, the polarized SNPs (ancestral and derived alleles) are used to correct the DNA reference sequence such as to contain only substitutions and no segregating polymorphisms.
+    If a SNP is still segregating in the population, the ancestral version of the SNP is used.
+    However, if the derived allele is shared by all individuals in the population, the allele is considered fixed and the derived allele of the SNP is used instead.
+    Then, using this corrected DNA reference and the $3$ closest outgroups found in the OrthoMam alignment, we reconstructed the ancestral protein-coding DNA sequences for each node of the 4-leaves tree with FastML.v3.11\cite{ashkenazy_fastml_2012}.
+    All polarized codon substitutions are then obtained by comparing the ancestral protein-coding DNA sequences before the split to the sister species (closest outgroup) to the corrected DNA reference for the population of interest.
+    We considered \textit{Ceratotherium simum simum} as \textit{Equus caballus} sister species; \textit{Bison bison bison} as \textit{Bos taurus} sister species; \textit{Pantholops hodgsonii} as \textit{Ovis aries} sister species; \textit{Pantholops hodgsonii} as \textit{Capra Hircus} sister species; \textit{Macaca mulatta} as \textit{Chlorocebus sabaeus} sister species and finally we considered \textit{Pan troglodytes} as \textit{Homo sapiens} sister species.
+    The selection coefficient ($\Sphy$) of each substitution is then obtained by comparing the difference in amino-acid fitnesses for each polarized non-synonymous codon substitution, by referring to the site-specific fitness profile obtained in the phylogeny-based method (see~\ref{subsec:s-phylogeny-method}).
 
@@
     \end{equation*}
-    where $\Spop_d < 0 $ is the mean of the DFE for $\Spop \leq 0$,
-    $b > 0$ is the shape of the $\Gamma$ distribution,
-    $0 \leq p_b \leq 1$ is the probability that $\Spop > 0$,
-    $\Spop_b > 0$ is the mean of the DFE for $\Spop > 0$,
+    where $\Spop_d \leq -1 $ is the estimated mean of the DFE for $\Spop \leq 0$,
+    $b \geq 0.4$ is the estimated shape of the $\Gamma$ distribution,
+    $0 \leq p_b \leq 1$ is the estimated probability that $\Spop > 0$,
+    $\Spop_b \geq 1$ is the estimated mean of the DFE for $\Spop > 0$,
     and $f_{\Gamma}(x; m, b)$ is the density of the $\Gamma$ distribution with mean m and shape b, while $f_{e}(x; m)$ is the density of the Exponential distribution with mean $m$.
@@
     \end{align*}
-    And finally, the mean of the DFE $\overline{\Spop}$ is given by:
-    \begin{align*}
-        \SpopMean & = \int_{-\infty}^{+\infty} \Spop \phi \left( \Spop; \Spop_d , b, p_b, \Spop_b \right) \der \Spop \\
-        & =  p_b \Spop_b + \left( 1 - p_b \right) \Spop_d
-    \end{align*}
+
     PolyDFE requires one SFS for non-synonymous mutations and one for synonymous mutations (neutral expectation), as well as the total mutation rate (mutation rate per site multiplied by the number of sites) on which each SFS has been sampled.
@@
 
+    %
+    %We first leveraged phylogenetic codon models which are based on a population-genetics formalism, assuming a non-adaptive fitness landscape.
+    %These models estimate the fitness of each of the 20 amino acids for each protein site, given mammalian protein-coding DNA alignments and gene tree topologies.
+    %Second, we integrated mammalian divergence data with polymorphic variants found in 28 populations across 6 mammalian genera.
+    %For each non-synonymous variant observed at the population level, we predicted its change in fitness from amino-acid fitnesses estimated at the mammalian scale.
+
     \printbibliography

### 2022-07-08 manuscript/supp-mat.tex
D. Hartasanchez corrections. Epistasis discussion. Removed Canis Lupus (too much div to sister species).

--- 2022-05-16 manuscript/supp-mat.tex
@@
 
-\title{Selection coefficients at the phylogenetic and population-genetic scale}
+\title{In mammals, 20 to 40\% of advantageous mutations are restoring damaged genomes instead of creating adaptive innovations}
 
@@
     \large
-    T. {Latrille}$^{1}$, J. {Joseph}$^{2}$, N. {Salamin}$^{1}$\\
-    $^{1}$Université de Lausanne, Lausanne, Switzerland
-    $^{1}$Université de Lyon, Lyon, France
+    \textbf{T. {Latrille}$^{1}$, J. {Joseph}$^{2}$, N. {Salamin}$^{1}$}\\
+    \normalsize $^{1}$Université de Lausanne, Lausanne, Switzerland\\
+    \normalsize $^{2}$Université de Lyon, Lyon, France \\
+    \normalsize \texttt{\href{mailto:thibault.latrille@ens-lyon.org}{thibault.latrille@ens-lyon.org}} \\
 }
@@
     \begin{center}
-        \begin{longtable}{|l|l|r|r|r|r|r|}
+        \footnotesize
+        \begin{longtable}{|l|l|r|r|r|r|r|r|}
             \toprule
-            Population           & Species             & Tajima $\theta_{\pi}$ & $\mathbb{P}_{div}(S > 0)$ & $\mathbb{P}_{obs}[S>0]$ & $\mathbb{P} [ \beta > 0 ]$ & $\mathbb{P} [ \beta > 0  | S>0]$ \\
+            Population           & Species             & Tajima $\theta$ & $\mathbb{P} [ \Spop > 1 ]$ & $\mathbb{P}_{mut}[\Sphy > 1]$ & $\mathbb{P} [ \Spop > 1  | \Sphy > 1]$ & $\mathbb{P}_{div}[\Sphy > 1]$ & $\dnds[\Sphy > 1]$ \\
             \midrule
@@
             \midrule
-            \multicolumn{7}{r}{{Continued on next page}} \\
+            \multicolumn{8}{r}{{Continued on next page}} \\
             \midrule
@@
             \endlastfoot
-            Equus c.             & Equus caballus      & $ 0.002$              & $ 0.301$                  & $ 0.243$                & $ 0.113$                   & $ 0.793$                       \\
-            Canis f.             & Canis familiaris    & $ 0.003$              & $ 0.421$                  & $ 0.181$                & $ 0.048$                   & $ 0.761$                       \\
-            Iran                 & Bos taurus          & $ 0.005$              & $ 0.249$                  & $ 0.264$                & $ 0.098$                   & $ 0.605$                       \\
-            Uganda               & Bos taurus          & $ 0.006$              & $ 0.254$                  & $ 0.249$                & $ 0.095$                   & $ 0.630$                       \\
-            Australia            & Capra hircus        & $ 0.003$              & $ 0.286$                  & $ 0.265$                & $ 0.096$                   & $ 0.512$                       \\
-            France               & Capra hircus        & $ 0.004$              & $ 0.285$                  & $ 0.274$                & $ 0.092$                   & $ 0.529$                       \\
-            Iran (C. aegagrus)   & Capra hircus        & $ 0.004$              & $ 0.284$                  & $ 0.270$                & $ 0.095$                   & $ 0.455$                       \\
-            Iran                 & Capra hircus        & $ 0.004$              & $ 0.297$                  & $ 0.239$                & $ 0.080$                   & $ 0.500$                       \\
-            Italy                & Capra hircus        & $ 0.004$              & $ 0.285$                  & $ 0.265$                & $ 0.087$                   & $ 0.500$                       \\
-            Morocco              & Capra hircus        & $ 0.004$              & $ 0.296$                  & $ 0.200$                & $ 0.080$                   & $ 0.509$                       \\
-            Iran                 & Ovis aries          & $ 0.008$              & $ 0.229$                  & $ 0.259$                & $ 0.060$                   & $ 0.366$                       \\
-            Iran (O. orientalis) & Ovis aries          & $ 0.009$              & $ 0.226$                  & $ 0.272$                & $ 0.067$                   & $ 0.344$                       \\
-            Iran (O. vignei)     & Ovis aries          & $ 0.008$              & $ 0.235$                  & $ 0.307$                & $ 0.075$                   & $ 0.464$                       \\
-            Various              & Ovis aries          & $ 0.009$              & $ 0.226$                  & $ 0.279$                & $ 0.065$                   & $ 0.378$                       \\
-            Morocco              & Ovis aries          & $ 0.008$              & $ 0.225$                  & $ 0.212$                & $ 0.054$                   & $ 0.377$                       \\
-            Barbados             & Chlorocebus sabaeus & $ 0.004$              & $ 0.314$                  & $ 0.258$                & $ 0.109$                   & $ 0.670$                       \\
-            Central Afr. Rep.    & Chlorocebus sabaeus & $ 0.006$              & $ 0.315$                  & $ 0.264$                & $ 0.094$                   & $ 0.619$                       \\
-            Ethiopia             & Chlorocebus sabaeus & $ 0.005$              & $ 0.307$                  & $ 0.252$                & $ 0.107$                   & $ 0.660$                       \\
-            Gambia               & Chlorocebus sabaeus & $ 0.005$              & $ 0.303$                  & $ 0.249$                & $ 0.085$                   & $ 0.666$                       \\
-            Kenya                & Chlorocebus sabaeus & $ 0.006$              & $ 0.311$                  & $ 0.272$                & $ 0.095$                   & $ 0.602$                       \\
-            Nevis                & Chlorocebus sabaeus & $ 0.004$              & $ 0.302$                  & $ 0.252$                & $ 0.102$                   & $ 0.642$                       \\
-            South Africa         & Chlorocebus sabaeus & $ 0.007$              & $ 0.312$                  & $ 0.246$                & $ 0.094$                   & $ 0.638$                       \\
-            Saint Kitts          & Chlorocebus sabaeus & $ 0.004$              & $ 0.306$                  & $ 0.250$                & $ 0.106$                   & $ 0.664$                       \\
-            Zambia               & Chlorocebus sabaeus & $ 0.006$              & $ 0.308$                  & $ 0.261$                & $ 0.103$                   & $ 0.630$                       \\
-            African              & Homo sapiens        & $ 0.003$              & $ 0.256$                  & $ 0.141$                & $ 0.103$                   & $ 1.000$                       \\
-            Admixed American     & Homo sapiens        & $ 0.002$              & $ 0.247$                  & $ 0.145$                & $ 0.103$                   & $ 0.945$                       \\
-            East Asian           & Homo sapiens        & $ 0.002$              & $ 0.241$                  & $ 0.129$                & $ 0.098$                   & $ 0.918$                       \\
-            European             & Homo sapiens        & $ 0.002$              & $ 0.254$                  & $ 0.130$                & $ 0.098$                   & $ 0.919$                       \\
-            South Asian          & Homo sapiens        & $ 0.002$              & $ 0.246$                  & $ 0.131$                & $ 0.096$                   & $ 0.912$                       \\
+            Equus c.
+& Equus caballus      & $ 0.002$        & $ 0.042$                   & $ 0.018$                      & $ 0.404$                             & $ 0.113$                      & $ 1.123$           \\
+            Iran                 & Bos taurus          & $ 0.005$        & $ 0.036$                   & $ 0.017$                      & $ 0.368$                             & $ 0.105$                      & $ 1.233$           \\
+            Uganda               & Bos taurus          & $ 0.006$        & $ 0.035$                   & $ 0.017$                      & $ 0.369$                             & $ 0.107$                      & $ 1.260$           \\
+            Australia            & Capra hircus        & $ 0.003$        & $ 0.036$                   & $ 0.017$                      & $ 0.144$                             & $ 0.122$                      & $ 1.035$           \\
+            France               & Capra hircus        & $ 0.004$        & $ 0.034$                   & $ 0.017$                      & $ 0.168$                             & $ 0.122$                      & $ 1.043$           \\
+            Iran (C.
+aegagrus)   & Capra hircus        & $ 0.004$        & $ 0.035$                   & $ 0.017$                      & $ 0.093$                             & $ 0.123$                      & $ 1.042$           \\
+            Iran                 & Capra hircus        & $ 0.004$        & $ 0.030$                   & $ 0.017$                      & $ 0.140$                             & $ 0.124$                      & $ 1.052$           \\
+            Italy                & Capra hircus        & $ 0.004$        & $ 0.032$                   & $ 0.017$                      & $ 0.150$                             & $ 0.122$                      & $ 1.037$           \\
+            Morocco              & Capra hircus        & $ 0.004$        & $ 0.029$                   & $ 0.017$                      & $ 0.137$                             & $ 0.124$                      & $ 1.057$           \\
+            Iran                 & Ovis aries          & $ 0.008$        & $ 0.022$                   & $ 0.018$                      & $ 0.046$                             & $ 0.102$                      & $ 1.148$           \\
+            Iran (O.
+orientalis) & Ovis aries          & $ 0.009$        & $ 0.025$                   & $ 0.018$                      & $ 0.071$                             & $ 0.099$                      & $ 1.120$           \\
+            Iran (O.
+vignei)     & Ovis aries          & $ 0.008$        & $ 0.028$                   & $ 0.018$                      & $ 0.220$                             & $ 0.103$                      & $ 1.149$           \\
+            Various              & Ovis aries          & $ 0.009$        & $ 0.024$                   & $ 0.018$                      & $ 0.108$                             & $ 0.100$                      & $ 1.126$           \\
+            Morocco              & Ovis aries          & $ 0.008$        & $ 0.020$                   & $ 0.018$                      & $ 0.070$                             & $ 0.099$                      & $ 1.109$           \\
+            Barbados             & Chlorocebus sabaeus & $ 0.004$        & $ 0.040$                   & $ 0.015$                      & $ 0.374$                             & $ 0.126$                      & $ 1.417$           \\
+            Central Afr. Rep.    & Chlorocebus sabaeus & $ 0.006$        & $ 0.034$                   & $ 0.015$                      & $ 0.368$                             & $ 0.124$ & $ 1.445$ \\
+            Ethiopia             & Chlorocebus sabaeus & $ 0.005$        & $ 0.040$                   & $ 0.015$                      & $ 0.368$                             & $ 0.123$                      & $ 1.422$           \\
+            Gambia               & Chlorocebus sabaeus & $ 0.005$        & $ 0.031$                   & $ 0.015$                      & $ 0.377$                             & $ 0.127$                      & $ 1.446$           \\
+            Kenya                & Chlorocebus sabaeus & $ 0.006$        & $ 0.035$                   & $ 0.015$                      & $ 0.308$                             & $ 0.128$                      & $ 1.453$           \\
+            Nevis                & Chlorocebus sabaeus & $ 0.004$        & $ 0.037$                   & $ 0.015$                      & $ 0.368$                             & $ 0.125$                      & $ 1.416$           \\
+            South Africa         & Chlorocebus sabaeus & $ 0.007$        & $ 0.034$                   & $ 0.015$                      & $ 0.368$                             & $ 0.125$                      & $ 1.453$           \\
+            Saint Kitts          & Chlorocebus sabaeus & $ 0.004$        & $ 0.039$                   & $ 0.015$                      & $ 0.368$                             & $ 0.126$                      & $ 1.420$           \\
+            Zambia               & Chlorocebus sabaeus & $ 0.006$        & $ 0.038$                   & $ 0.015$                      & $ 0.368$                             & $ 0.123$                      & $ 1.424$           \\
+            African              & Homo sapiens        & $ 0.003$        & $ 0.038$                   & $ 0.015$                      & $ 0.604$                             & $ 0.104$                      & $ 1.475$           \\
+            Admixed American     & Homo sapiens        & $ 0.002$        & $ 0.037$                   & $ 0.015$                      & $ 0.574$                             & $ 0.103$                      & $ 1.466$           \\
+            East Asian           & Homo sapiens        & $ 0.002$        & $ 0.036$                   & $ 0.015$                      & $ 0.484$                             & $ 0.104$                      & $ 1.478$           \\
+            European             & Homo sapiens        & $ 0.002$        & $ 0.037$                   & $ 0.015$                      & $ 0.517$                             & $ 0.103$                      & $ 1.461$           \\
+            South Asian          & Homo sapiens        & $ 0.002$        & $ 0.036$                   & $ 0.015$                      & $ 0.532$                             & $ 0.104$                      & $ 1.473$           \\
         \end{longtable}
@@
         \item Tajima $\theta$ is the synonymous diversity.
-        \item $\mathbb{P}_{div}(S > 0)$ is the proportion of substitution in the terminal branch observed with a selection coefficient at the phylogenetic scale ($\Sphy$) larger than 0.
-        \item $\mathbb{P}_{obs}[S>0]$ is the proportion of SNPs observed with a predicted selection coefficient at the phylogenetic scale ($\Sphy$) larger than 0.
-        \item $\mathbb{P} [ \beta > 0 ]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) larger than 1, estimated for the whole genome.
-        \item $\proba [ \polyAdv | \divAdv]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) larger than 1, estimated on the subset of SNPs observed with a predicted selection coefficient at the phylogenetic scale ($\Sphy$) larger than 0.
+        \item $\mathbb{P} [ \Spop > 1 ]$ is the probability of $\Spop > 1$ estimated by polyDFE from all SNPs.
+        \item $\mathbb{P}_{mut}[\Sphy > 0]$ is the proportion of mutational opportunities with a predicted selection coefficient larger than 1 ($\Sphy > 1$).
+        \item $\mathbb{P} [ \Spop > 1  | \Sphy > 1]$ is the probability of $\Spop > 1$ estimated by polyDFE for SNPs with a predicted selection coefficient larger than 1 ($\Sphy > 1$).
+        \item $\mathbb{P}_{div}[\Sphy > 1]$ is the proportion of substitutions in the terminal branch observed with a selection coefficient at the phylogenetic scale larger than 1 ($\Sphy > 1$).
+        \item $\dnds[\Sphy > 1]$ is the ratio of non-synonymous over synonymous divergence (also called $\dnds$) estimated for the non-synonymous substitutions in the terminal branch with a selection coefficient larger than 1 ($\Sphy > 1$).
+    \end{itemize}
+
+    \begin{center}
+        \footnotesize
+        \begin{longtable}{|l|l|r|r|r|r|r|r|r|r|}
+            \toprule
+            Population           & Species             & Tajima $\theta_{\pi}$ & $\mathbb{P}_{div}[\Sphy > 0]$ & $\dnds $ & $\dnds  | S<0$ & R($\dnds $) & $p_b $ & $p_b  | S<0$ & R($p_b $) \\
+            \midrule
+            \endhead
+            \midrule
+            \multicolumn{9}{r}{{Continued on next page}} \\
+            \midrule
+            \endfoot
+
+            \bottomrule
+            \endlastfoot
+            Equus c. &       Equus caballus &               $ 0.002$ &                $ 0.301$ &        $ 0.183$ &              $ 0.135$ &           $  26.2$ & $ 0.113$ &     $ 0.081$ &  $  28.5$ \\
+            Iran &           Bos taurus &               $ 0.005$ &                $ 0.266$ &        $ 0.199$ &              $ 0.154$ &           $  22.6$ & $ 0.098$ &     $ 0.067$ &  $  31.2$ \\
+            Uganda &           Bos taurus &               $ 0.006$ &                $ 0.267$ &        $ 0.201$ &              $ 0.156$ &           $  22.6$ & $ 0.094$ &     $ 0.062$ &  $  33.8$ \\
+            Australia &         Capra hircus &               $ 0.003$ &                $ 0.301$ &        $ 0.148$ &              $ 0.109$ &           $  26.1$ & $ 0.096$ &     $ 0.071$ &  $  26.2$ \\
+            France &         Capra hircus &               $ 0.004$ &                $ 0.301$ &        $ 0.149$ &              $ 0.110$ &           $  26.1$ & $ 0.092$ &     $ 0.067$ &  $  26.7$ \\
+            Iran (C.
+aegagrus) &         Capra hircus &               $ 0.004$ &                $ 0.301$ &        $ 0.148$ &              $ 0.109$ &           $  26.1$ & $ 0.096$ &     $ 0.072$ &  $  25.0$ \\
+            Iran &         Capra hircus &               $ 0.004$ &                $ 0.303$ &        $ 0.148$ &              $ 0.109$ &           $  26.4$ & $ 0.080$ &     $ 0.055$ &  $  31.9$ \\
+            Italy &         Capra hircus &               $ 0.004$ &                $ 0.301$ &        $ 0.149$ &              $ 0.110$ &           $  26.1$ & $ 0.087$ &     $ 0.060$ &  $  30.5$ \\
+            Morocco &         Capra hircus &               $ 0.004$ &                $ 0.303$ &        $ 0.148$ &              $ 0.109$ &           $  26.4$ & $ 0.079$ &     $ 0.054$ &  $  31.5$ \\
+            Iran &           Ovis aries &               $ 0.008$ &                $ 0.229$ &        $ 0.198$ &              $ 0.161$ &           $  18.6$ & $ 0.060$ &     $ 0.038$ &  $  36.5$ \\
+            Iran (O.
+orientalis) &           Ovis aries &               $ 0.009$ &                $ 0.226$ &        $ 0.200$ &              $ 0.164$ &           $  18.2$ & $ 0.067$ &     $ 0.044$ &  $  33.4$ \\
+            Iran (O.
+vignei) &           Ovis aries &               $ 0.008$ &                $ 0.235$ &        $ 0.197$ &              $ 0.159$ &           $  19.2$ & $ 0.075$ &     $ 0.052$ &  $  30.5$ \\
+            Various &           Ovis aries &               $ 0.009$ &                $ 0.226$ &        $ 0.199$ &              $ 0.163$ &           $  18.2$ & $ 0.064$ &     $ 0.041$ &  $  36.7$ \\
+            Morocco &           Ovis aries &               $ 0.008$ &                $ 0.225$ &        $ 0.199$ &              $ 0.163$ &           $  18.1$ & $ 0.055$ &     $ 0.034$ &  $  38.0$ \\
+            Barbados &  Chlorocebus sabaeus &               $ 0.004$ &                $ 0.305$ &        $ 0.169$ &              $ 0.123$ &           $  26.9$ & $ 0.109$ &     $ 0.081$ &  $  25.3$ \\
+            Central Afr.
+Rep.
+&  Chlorocebus sabaeus &               $ 0.006$ &                $ 0.307$ &        $ 0.174$ &              $ 0.127$ &           $  27.0$ & $ 0.094$ &     $ 0.063$ &  $  33.1$ \\
+            Ethiopia &  Chlorocebus sabaeus &               $ 0.005$ &                $ 0.305$ &        $ 0.172$ &              $ 0.126$ &           $  26.9$ & $ 0.108$ &     $ 0.081$ &  $  25.0$ \\
+            Gambia &  Chlorocebus sabaeus &               $ 0.005$ &                $ 0.307$ &        $ 0.171$ &              $ 0.124$ &           $  27.1$ & $ 0.084$ &     $ 0.057$ &  $  31.8$ \\
+            Kenya &  Chlorocebus sabaeus &               $ 0.006$ &                $ 0.309$ &        $ 0.170$ &              $ 0.124$ &           $  27.2$ & $ 0.095$ &     $ 0.071$ &  $  25.0$ \\
+            Nevis &  Chlorocebus sabaeus &               $ 0.004$ &                $ 0.305$ &        $ 0.169$ &              $ 0.124$ &           $  26.8$ & $ 0.101$ &     $ 0.077$ &  $  23.6$ \\
+            South Africa &  Chlorocebus sabaeus &               $ 0.007$ &                $ 0.309$ &        $ 0.173$ &              $ 0.126$ &           $  27.2$ & $ 0.094$ &     $ 0.068$ &  $  27.7$ \\
+            Saint Kitts &  Chlorocebus sabaeus &               $ 0.004$ &                $ 0.309$ &        $ 0.168$ &              $ 0.122$ &           $  27.2$ & $ 0.106$ &     $ 0.079$ &  $  26.1$ \\
+            Zambia &  Chlorocebus sabaeus &               $ 0.006$ &                $ 0.307$ &        $ 0.173$ &              $ 0.126$ &           $  27.0$ & $ 0.104$ &     $ 0.077$ &  $  25.6$ \\
+            African &         Homo sapiens &               $ 0.003$ &                $ 0.259$ &        $ 0.216$ &              $ 0.169$ &           $  21.9$ & $ 0.103$ &     $ 0.069$ &  $  32.4$ \\
+            Admixed American &         Homo sapiens &               $ 0.002$ &                $ 0.258$ &        $ 0.216$ &              $ 0.169$ &           $  21.8$ & $ 0.104$ &     $ 0.071$ &  $  31.3$ \\
+            East Asian &         Homo sapiens &               $ 0.002$ &                $ 0.259$ &        $ 0.217$ &              $ 0.169$ &           $  22.0$ & $ 0.098$ &     $ 0.068$ &  $  30.3$ \\
+            European &         Homo sapiens &               $ 0.002$ &                $ 0.258$ &        $ 0.216$ &              $ 0.169$ &           $  21.8$ & $ 0.097$ &     $ 0.067$ &  $  31.0$ \\
+            South Asian &         Homo sapiens &               $ 0.002$ &                $ 0.259$ &        $ 0.216$ &              $ 0.169$ &           $  21.9$ & $ 0.096$ &     $ 0.066$ &  $  31.7$ \\
+        \end{longtable}
+
+    \end{center}
+    \begin{itemize}
+        \item Tajima $\theta$ is the synonymous diversity.
+        \item $\mathbb{P}_{div}[\Sphy > 0]$ is the proportion of substitutions in the terminal branch observed with a selection coefficient at the phylogenetic scale larger than 0 ($\Sphy > 0$).
+        \item $\dnds$ is the ratio of non-synonymous over synonymous divergence estimated for all the non-synonymous substitutions in the terminal branch.
+        \item $\dnds[\Sphy < 0]$ is the ratio of non-synonymous over synonymous divergence estimated for the non-synonymous substitutions in the terminal branch with a selection coefficient lower than 0 ($\Sphy < 0$).
+        This is the estimated divergence when we removed the restoring substitutions.
+        \item $R(\dnds)=\dfrac{\dnds - \dnds[\Sphy < 0]}{\dnds}$ is the fraction of the divergence ($\dnds$) that is over-estimated, $\dnds$ is compared to the estimated divergence when we removed the restoring substitutions $\dnds[\Sphy < 0]$.
+        \item $p_b$ is the probability for a new mutation to be advantageous, estimated (with polyDFE) using all available polymorphism.
+        \item $p_b[\Sphy < 0]$ is the probability for a new mutation to be advantageous, estimated (with polyDFE) using polymorphism with a selection coefficient lower than 0 ($\Sphy < 0$).
+        This is the estimated probability for a new mutation to be advantageous when we removed the restoring polymorphism from the dataset.
+        \item $R(p_b)=\dfrac{p_b - p_b[\Sphy < 0]}{p_b}$ is the fraction of the probability for a new mutation to be advantageous ($p_b$) that is over-estimated, $p_b$ is compared to its estimation when we had removed all the restoring mutations $p_b[\Sphy < 0]$.
     \end{itemize}
@@
 
+    \subsection{Selection efficacy correlation with diversity}
+
+    The mean of the DFE $\SpopMean$ estimated by polyDFE is given by:
+    \begin{align*}
+        \SpopMean & = \int_{-\infty}^{+\infty} \Spop \phi \left( \Spop; \Spop_d , b, p_b, \Spop_b \right) \der \Spop \\
+        & =  p_b \Spop_b + \left( 1 - p_b \right) \Spop_d
+    \end{align*}
+
+    To look further into the relation between diversity and selection efficacy, we studied the estimation of the mean $\SpopMean$ as a function of the mean $\SphyMean$ for a subset of SNPs, for which $\SphyMean$ is close to $0$.
+    Indeed, polyDFE is a nearly-neutral model and is not able to reliably compute selection coefficients for only strongly deleterious or only strongly advantageous SNPs.
+    Sliding windows of $5,000$ SNPs are taken with a mean $\SphyMean$ between $-0.5$ and $0.5$.
+    $\SpopMean$ is estimated for each group, with some groups that might have part of same SNPs that overlap.
+    The relationship between $\SpopMean$ and $\SphyMean$ can be described by a second-order polynomial, and the slope of this polynomial at $\SphyMean=0$ gives the ratio $\SpopMean/\SphyMean$ for each population.
+    We observe that $\SpopMean/\SphyMean$, representing the efficacy of selection at the short versus long-term is positively correlated with synonymous diversity, a proxy of effective population size.
+    Altogether, populations with a large effective population size are under more efficient selection, confirming the prediction of the nearly-neutral theory of evolution.
+    As a consequence of an increased selection efficiency, mutations in populations with high diversity are mechanistically more likely to be deleterious (fig.~S4), especially for mutations predicted already to be deleterious at the phylogenetic scale (fig.~S5-6).
+
+    \begin{center}
+        \includegraphics[width=\linewidth, page=1]{artworks/figure.slope-beta-S}
+    \end{center}
+
     \input{include-MutSel-non-adaptive}
 
-    \section{SIFT scores}
-    \input{include-SIFT-non-adaptive}
+    %\section{SIFT scores}
+    %\input{include-SIFT-non-adaptive}
 
-    \section{Site-specific $\omega$-based codon models.}
-    The $61$-by-$61$ codon substitution matrix ($\UniDimArray{q^{(i)}}$) at site $i$ is defined entirely by the mutation matrix ($\UniDimArray{\mu}$), $\omega^{(i)}$ and the genetic code:
-    \begin{equation}
-        \begin{dcases}
-            q_{a \mapsto b}^{(i)} & = 0 \text{ if codons $a$ and $b$ are more than one mutation away,} \\
-            q_{a \mapsto b}^{(i)} & = \mu_{a \mapsto b} \text{ if codons $a$ and $b$ are synonymous,} \\
-            q_{a \mapsto b}^{(i)} & = \omega^{(i)} \mu_{a \mapsto b} \text{ if codons $a$ and $b$ are non-synonymous}.
-        \end{dcases}
-    \end{equation}
-    By definition of the instantaneous rate matrix, the sum of the entries in each row of the codon substitution rate matrix $\UniDimArray{q}$ is equal to $0$, giving the diagonal entries:
-    \begin{equation}
-        q_{a \mapsto b}^{(i)}= - \sum\limits_{b \neq a, b = 1}^{61} q_{a \mapsto b}^{(i)}.
-    \end{equation}
-
-    In BayesCode (\url{https://github.com/ThibaultLatrille/bayescode}), $\omega$-based site-specific codon models are obtained by running \textit{mutselomega} with the options:
-    \begin{scriptsize}
-        \begin{verbatim}
-        mutselomega --omegashift 0.0 --freeomega --omegancat 30 --flatfitness -a my_alignment.phy -t my_tree.newick -u 2000 my_genename
-        \end{verbatim}
-    \end{scriptsize}
-    The mean value of $\omega$ per site is then obtained by running \textit{readmutselomega} with the options:
-    \begin{scriptsize}
-        \begin{verbatim}
-        readmutselomega --every 1 --until 2000 --burnin 1000 -c 0.025 my_genename
-        \end{verbatim}
-    \end{scriptsize}
-
-    \input{include-Omega-adaptive}
 \end{document}

### 2022-07-08 copy_artworks.sh

@@ -1,13 +1,19 @@
 #!/usr/bin/env bash
 \cp -rf ./experiments/50windows-polyDFE-mC-non-adaptive/regression/results.watterson.a.scatter.pdf ./manuscript/artworks/scatter.watterson.slopeSpopSphy.pdf
 \cp -rf ./experiments/50windows-polyDFE-mC-non-adaptive/results/regression.MutSel.SelCoeff.scatter.pdf ./manuscript/artworks/scatter.Sphy.Spop.pdf
+\cp -rf ./experiments/3bins-polyDFE-mC/results/Theta.MutSel.weak.stacked.pdf ./manuscript/artworks/stacked.weakSNPs.pdf
+\cp -rf ./experiments/5bins-polyDFE-mC/results/Theta.MutSel.all.stacked.pdf ./manuscript/artworks/stacked.allSNPs.pdf
+\cp -rf ./experiments/5bins-polyDFE-mC/results/Theta.MutSel.pos-weak.stacked.pdf ./manuscript/artworks/stacked.weak-pos-SNPs.pdf
+\cp -rf ./experiments/5bins-polyDFE-mC/results/Theta.MutSel.neg-weak.stacked.pdf ./manuscript/artworks/stacked.weak-neg-SNPs.pdf
 \cp -rf ./experiments/5bins-polyDFE-mC/results/Theta.MutSel.P-Seq0.heatmap.pdf ./manuscript/artworks/heatmap.neutral.pdf
 \cp -rf ./experiments/5bins-polyDFE-mC/results/Theta.MutSel.P-Sinf0.heatmap.pdf ./manuscript/artworks/heatmap.neg.pdf
 \cp -rf ./experiments/5bins-polyDFE-mC/results/Theta.MutSel.P-Ssup0.heatmap.pdf ./manuscript/artworks/heatmap.pos.pdf
-\cp -rf ./experiments/5bins-polyDFE-mC/results/Theta.MutSel.pos-weak.stacked.pdf ./manuscript/artworks/pos-weak.stacked.pdf
 \cp -rf ./experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.AFR.MutSel-sfs.normalize.pdf ./manuscript/artworks/AFR.SFS.pdf
 \cp -rf ./experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.AFR.MutSel.polyDFE_C.pdf ./manuscript/artworks/AFR.polyDFE.pdf
[…]

### 2022-07-08 scripts/tex_sfs.py

@@ -49,12 +49,13 @@ def main(args):
                     o.write("\\subsubsection{" + sample_dico[format_pop(pop)] + "} \n \n")
                 hist_suffix = f"{sp}.{pop}.{method}.histogram.pdf".replace(' ', '_')
                 hist_path = f"{args.hist_prefix}{hist_suffix}"
-                o.write(minipage(0.49, hist_path))
-                o.write(minipage(0.49, sfs.replace(".pdf", ".normalize.pdf")))
-                o.write("\\\\ \n")
                 dfe_suffix = f"{sp}.{pop}.{method}.pdf".replace(' ', '_')
                 dfe_path = f"{args.dfe_prefix}{dfe_suffix}"
+
                 o.write(minipage(0.49, dfe_path))
+                o.write(minipage(0.49, hist_path))
+                o.write("\\\\ \n")
+                o.write(minipage(0.49, sfs.replace(".pdf", ".normalize.pdf")))
                 for model in ["C", "D"]:
                     polyDFE = sfs.replace("-sfs.pdf", f".polyDFE_{model}.pdf")
                     if os.path.exists(polyDFE):

### 2022-07-10 manuscript/include-SIFT-non-adaptive.tex
R as function of diversity in figure 5

@@
 \begin{center}
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.SIFT.P-Sinf0.heatmap.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.SIFT.P-Seq0.heatmap.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.SIFT.P-Ssup0.heatmap.pdf} \\
     \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.SIFT.all.stacked.pdf} \\
@@
 
-\subsubsection{Iran (IRBT)}
+\subsubsection{Iran}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Bos_taurus.IRBT.SIFT.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Bos_taurus.IRBT.SIFT-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Bos_taurus.IRBT.SIFT.pdf}
 \end{minipage}
@@
 
-\subsubsection{Uganda (UGBT)}
+\subsubsection{Uganda}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Bos_taurus.UGBT.SIFT.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Bos_taurus.UGBT.SIFT-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Bos_taurus.UGBT.SIFT.pdf}
 \end{minipage}
@@
 
-\subsection{Canis familiaris}
+\subsection{Capra}
+
+\subsubsection{Australia}
 
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Canis_familiaris.dogs.SIFT.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.AUCH.SIFT.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Canis_familiaris.dogs.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.AUCH.SIFT.histogram.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Canis_familiaris.dogs.SIFT.pdf}
-\end{minipage}
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Canis_familiaris.dogs.SIFT.polyDFE_C.pdf}
-\end{minipage}
-\\
-
-\subsection{Capra}
-
-\subsubsection{Australia (AUCH) - Capra hircus}
-
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.AUCH.SIFT.histogram.pdf}
-\end{minipage}
-\begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.AUCH.SIFT-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.AUCH.SIFT.pdf}
 \end{minipage}
@@
 
-\subsubsection{France (FRCH) - Capra hircus}
+\subsubsection{France}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.FRCH.SIFT.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.FRCH.SIFT-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.FRCH.SIFT.pdf}
 \end{minipage}
@@
 
-\subsubsection{Iran (IRCA) - Capra aegagrus}
+\subsubsection{Iran (C. aegagrus)}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.IRCA.SIFT.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.IRCA.SIFT-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.IRCA.SIFT.pdf}
 \end{minipage}
@@
 
-\subsubsection{Iran (IRCH) - Capra hircus}
+\subsubsection{Iran}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.IRCH.SIFT.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.IRCH.SIFT-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.IRCH.SIFT.pdf}
 \end{minipage}
@@
 
-\subsubsection{Italy (ITCH) - Capra hircus}
+\subsubsection{Italy}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.ITCH.SIFT.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.ITCH.SIFT-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.ITCH.SIFT.pdf}
 \end{minipage}
@@
 
-\subsubsection{Morocco (MOCH) - Capra hircus}
+\subsubsection{Morocco}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.MOCH.SIFT.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.MOCH.SIFT-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.MOCH.SIFT.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Barbados.SIFT.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Barbados.SIFT.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Barbados.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Barbados.SIFT.histogram.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Barbados.SIFT.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Barbados.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 
-\subsubsection{Central African Republic (CAR)}
+\subsubsection{Central Afr. Rep.}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Central_African_Republic.SIFT.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Central_African_Republic.SIFT-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Central_African_Republic.SIFT.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Ethiopia.SIFT.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Ethiopia.SIFT.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Ethiopia.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Ethiopia.SIFT.histogram.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Ethiopia.SIFT.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Ethiopia.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Gambia.SIFT.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Gambia.SIFT.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Gambia.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Gambia.SIFT.histogram.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Gambia.SIFT.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Gambia.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Kenya.SIFT.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Kenya.SIFT.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Kenya.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Kenya.SIFT.histogram.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Kenya.SIFT.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Kenya.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Nevis.SIFT.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Nevis.SIFT.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Nevis.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Nevis.SIFT.histogram.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Nevis.SIFT.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Nevis.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 
-\subsubsection{Saint Kitts (SK)}
+\subsubsection{Saint Kitts}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Saint_Kitts.SIFT.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Saint_Kitts.SIFT-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Saint_Kitts.SIFT.pdf}
 \end{minipage}
@@
 
-\subsubsection{South Africa (SA)}
+\subsubsection{South Africa}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.South_Africa.SIFT.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.South_Africa.SIFT-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.South_Africa.SIFT.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Zambia.SIFT.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Zambia.SIFT.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Zambia.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Zambia.SIFT.histogram.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Zambia.SIFT.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Zambia.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Equus_caballus.up.SIFT.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Equus_caballus.up.SIFT.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Equus_caballus.up.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Equus_caballus.up.SIFT.histogram.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Equus_caballus.up.SIFT.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Equus_caballus.up.SIFT-sfs.normalize.pdf}
 \end{minipage}
@@
 
-\subsubsection{African (AFR)}
+\subsubsection{African}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.AFR.SIFT.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.AFR.SIFT-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.AFR.SIFT.pdf}
 \end{minipage}
@@
 
-\subsubsection{Ad Mixed American (AMR)}
+\subsubsection{Admixed American}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.AMR.SIFT.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.AMR.SIFT-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.AMR.SIFT.pdf}
 \end{minipage}
@@
 
-\subsubsection{East Asian (EAS)}
+\subsubsection{East Asian}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.EAS.SIFT.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.EAS.SIFT-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.EAS.SIFT.pdf}
 \end{minipage}
@@
 
-\subsubsection{European (EUR)}
+\subsubsection{European}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.EUR.SIFT.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.EUR.SIFT-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.EUR.SIFT.pdf}
 \end{minipage}
@@
 
-\subsubsection{South Asian (SAS)}
+\subsubsection{South Asian}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.SAS.SIFT.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.SAS.SIFT-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.SAS.SIFT.pdf}
 \end{minipage}
@@
 
-\subsubsection{Iran (IROA) - Ovis aries}
+\subsubsection{Iran}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.IROA.SIFT.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROA.SIFT-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.IROA.SIFT.pdf}
 \end{minipage}
@@
 
-\subsubsection{Iran (IROO) - Ovis orientalis}
+\subsubsection{Iran (O. orientalis)}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.IROO.SIFT.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROO.SIFT-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.IROO.SIFT.pdf}
 \end{minipage}
@@
 
-\subsubsection{Iran (IROV) - Ovis vignei}
+\subsubsection{Iran (O. vignei)}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.IROV.SIFT.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROV.SIFT-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.IROV.SIFT.pdf}
 \end{minipage}
@@
 
-\subsubsection{Various (ISGC) - Ovis aries}
+\subsubsection{Various}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.ISGC.SIFT.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.ISGC.SIFT-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.ISGC.SIFT.pdf}
 \end{minipage}
@@
 
-\subsubsection{Morocco (MOOA) - Ovis aries}
+\subsubsection{Morocco}
 
+\begin{minipage}{0.49\linewidth}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.MOOA.SIFT.pdf}
+\end{minipage}
 \begin{minipage}{0.49\linewidth}
@@
 \end{minipage}
+\\
 \begin{minipage}{0.49\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.MOOA.SIFT-sfs.normalize.pdf}
-\end{minipage}
-\\
-\begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.MOOA.SIFT.pdf}
 \end{minipage}

### 2022-07-10 manuscript/main.tex
R as function of diversity in figure 5

@@
 \newcommand{\Sphy}{S}
+\newcommand{\Sphyclass}{\mathcal{C}}
 \newcommand{\SphyMean}{\overline{\Sphy}}
@@
     $^{1}$Université de Lausanne, Lausanne, Switzerland\\
-    $^{2}$Université de Lyon, Lyon, France \\
+    $^{2}$Université de Lyon, CNRS, LBBE UMR 5558, Villeurbanne, France \\
     \texttt{\href{mailto:thibault.latrille@ens-lyon.org}{thibault.latrille@ens-lyon.org}} \\
@@
         Positive selection can be the result of adaptive evolution, driven by a change in environment or selective pressure.
-        However, positive selection can also be the result of compensatory positive selection where advantageous mutations are compensating for deleterious substitutions without any change of the environment.
+        However, positive selection can also be the result of what we call maintenance positive selection where advantageous mutations are compensating for deleterious substitutions without any change of the environment.
         The evolutionary outcomes of these two positive selections are drastically different.
-        While adaptive evolution acts as a diversifying force, compensatory positive selection stabilizes phenotypes and reduces diversity across species.
-        By leveraging polymorphism data in 28 populations and divergence data between 94 mammalian species, we estimate that 20 to 40\% of all new advantageous mutations are under compensatory positive selection.
+        While adaptive evolution acts as a diversifying force, maintenance positive selection stabilizes phenotypes and reduces diversity across species.
+        By leveraging polymorphism data in 28 populations and divergence data between 94 mammalian species, we estimate that 20 to 40\% of all new advantageous mutations are under maintenance positive selection.
         Our work confirms that deleterious substitutions have accumulated in mammals and are currently being compensated for, resulting in widespread positive selection that is not adaptive evolution.
@@
     The second scenario involves a mutation restoring the ancestral allele which corresponded to an optimal state of the individual in a constant environment, but has been lost due to the fixation of a deleterious mutation by drift.
-    Regarding the difference between these two scenarios at the population scale, while in the case of environmental change, the population as a whole is climbing the fitness landscape along an adaptive walk\cite{tenaillon_utility_2014}, in the case of non-adaptive positive selection, the population as a whole is thus merely staying in the same position in the fitness landscape at the mutation-selection equilibrium, and positive selection compensates for deleterious mutations that reach fixation due to drift\cite{sella_application_2005, mustonen_fitness_2009}.
+    In this manuscript, this process will be referred to as maintenance positive selection.
+    Regarding the difference between these two scenarios at the population scale, while in the case of environmental change, the population as a whole is climbing the fitness landscape along an adaptive walk\cite{tenaillon_utility_2014}, in the case of maintenance positive selection, the population as a whole is thus merely staying in the same position in the fitness landscape at the mutation-selection equilibrium, and positive selection compensates for deleterious mutations that reach fixation due to drift\cite{sella_application_2005, mustonen_fitness_2009}.
     These two different kinds of selection result in a positive transmission bias of the advantageous allele, but their consequences are conceptually different.
-    While adaptive evolution promotes phenotype diversification, non-adaptive positive selection promotes phenotype stability and preserves well established biological systems (fig.~\ref{fig:fitness-landscape}).
+    While adaptive evolution promotes phenotype diversification, maintenance positive selection promotes phenotype stability and preserves well established biological systems (fig.~\ref{fig:fitness-landscape}).
     It is thus of importance to be able to distinguish those two kinds of positive selection in order to understand the diversification of species.
@@
     However, as mentioned above, not all these mutations contribute to genetic innovation and diversification.
-    Adaptive evolution can only be well estimated if non-adaptive positive selection is taken into account.
+    Adaptive evolution can only be well estimated if maintenance positive selection is taken into account.
     While adaptive evolution is unpredictable because it brings an advantage concerning an unpredictable change in the environment of organisms, the second is predictable because optimal states should be more or less the same for closely related organisms which share most of their environment and physiology.
-    A way to thus measure non-adaptive positive selection is to compute selection coefficients assuming a constant and stable fitness landscape estimated from the alignment of protein-coding genes.
+    A way to thus measure maintenance positive selection is to compute selection coefficients assuming a constant and stable fitness landscape estimated from the alignment of protein-coding genes.
     For each site of the protein alignment, amino-acid frequencies in the alignment is a proxy for its fitness, since for example a deleterious amino acid will be absent in the alignment.
@@
     Are these polymorphisms actually under ongoing positive selection at the scale of populations?
-    Finally, how much of the recent substitutions are due to non-adaptive positive selection?
+    Finally, how much of the recent substitutions are due to maintenance positive selection?
 
@@
     We then developed and leveraged a pipeline integrating divergence and polymorphism data across the entire exome for 28 populations across 6 genera, namely \textit{Equus},  \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus} and \textit{Homo} (fig.~\ref{fig:method}).
+
+    \subsection*{SNPs which are predicted to be advantageous are positively selected at the population scale}
+
     For each non-synonymous SNP observed at the population level, we predicted its scaled selection coefficient ($\Sphy$) from amino-acid fitnesses estimated at the mammalian scale (fig.~\ref{fig:homo-afr-results}A).
@@
 
+    We then tried to estimate the proportion of restoring mutations among advantageous ones.
+    Since adaptation does not fit the fitness predictions, the proportion of adaptive mutation is expected to be the same among SNPs which are predicted to be advantageous, and among SNPs which are predicted to be deleterious.
+    Thus the proportion of advantageous mutations among SNPs which are predicted to be deleterious directly correspond to the proportion of all mutations which are adaptive.
+    So if we divide the proportion of mutations which are predicted to be advantageous among supposedly deleterious SNPs by the proportion of mutations which are predicted to be advantageous among all SNPs.
+    We directly get the proportion of mutations which are adaptive among advantageous ones. It results that 60 to 80\% of advantageous mutations are adaptive.
+
     Finally, we reconstructed the substitutions in the terminal branches of the phylogenetic tree in order to determine the distribution of their selection coefficients.
@@
     These observed substitutions are likely to have been positive selected because they restored a more optimal state, not because they are driving innovations to a new environment or a function.
-    %Altogether, we estimated that between 18 and 39\% of $\dnds$ is over-estimated (table S1), corresponding to non-adaptive positive selection.
+    %Altogether, we estimated that between 18 and 39\% of $\dnds$ is over-estimated (table S1), corresponding to maintenance positive selection.
     In a nearly neutral framework, genomes could be viewed as the arena of a tug-of-war between a large volume of deleterious mutations that eventually reach fixation due to drift, and scarce advantageous mutations that are restoring a more optimal ancestral state.
@@
             Panel A.
-For each population, the proportion of advantageous ($\PpolyAdv$), nearly-neutral ($\PpolyNeutral$) and of deleterious ($\PpolyDel$) mutations estimated at the population-genetic scale is shown.
+For each population, the proportion of advantageous ($p_+=\PpolyAdv$), nearly-neutral ($\PpolyNeutral$) and of deleterious ($\PpolyDel$) mutations estimated at the population-genetic scale is shown.
             Estimation is performed with SNPs predicted to be weakly advantageous at the phylogenetic scale ($\divWeakAdv$).
-            Panel B. Mean selection coefficient at the population scale $\SpopMean$ as a function of phylogenetic $\SphyMean$.
-            Observed SNPs are sorted and groups of $5,000$ SNPs are taken as a sliding window with increasing mean $-0.5 \leq \SphyMean \leq 0.5$.
-            For each group along the sliding window, $\SpopMean$ (y-axis) is estimated based on SFS and the total mutation rate, and compared to the mean $\SphyMean$ (x-axis).
-            A second order polynomial is fitted for each population, and the slope of this polynomial at $\SphyMean=0$ gives the ratio $\SpopMean/\SphyMean$, specified in the legend as $f'(0)$ estimates.
-            Panel C. $\SpopMean/\SphyMean$ ratio as a function of the synonymous diversity for each population.
-            Populations with higher diversity show a higher $\SpopMean/\SphyMean$ ratio.
+            Panel B.
+$R(p_+)=\dfrac{p_+ - p_+[\Sphy < 0]}{p_+}$ is the fraction of the probability for a new mutation to be advantageous ($p_+=\PpolyAdv$) that is over-estimated, $p_+$ is compared to its estimation when we had removed all the restoring mutations $p_+[\Sphy < 0]$.
+            $R(p_+)$ (y-axis) is shown as a function of the synonymous diversity (Watterson $\theta_w$ in x-axis).
+            Panel C.
+$R(\dnds)=\dfrac{\dnds - \dnds[\Sphy < 0]}{\dnds}$ is the fraction of the divergence ($\dnds$) that is over-estimated, where $\dnds$ is compared to the estimated divergence when we removed the restoring substitutions $\dnds[\Sphy < 0]$.
+            $R(\dnds)$ (y-axis) is shown as a function of the synonymous diversity (Watterson $\theta_w$ in x-axis).
         }
@@
     In our study we focused on mutations restoring the more optimal ancestral state at a given site, not accounting for compensatory mutations since we assumed a model of fitness landscape without epistasis, providing a reasonable estimate of average fitness profiles\cite{youssef_consequences_2020}.
-    But most importantly, we argue that our estimation of the amount of non-adaptive positive selection is an underestimation, and that accounting for compensatory mutations by means of epistasis would mechanically increase that amount.
+    But most importantly, we argue that our estimation of the amount of maintenance positive selection is an underestimation, and that accounting for compensatory mutations by means of epistasis would mechanically increase that amount.
     Indeed, a fluctuating fitness landscape due to an external forces (e.i.
@@
     Aside from methodological limitations, the mammalian case study might also not be representative of other clades.
-    Indeed, our dataset is quite convenient because mammals have relatively small population sizes, which allow large amount of deleterious mutations to be fixed, and thus, there are a lot of opportunities for non-adaptive positive selection to arise.
+    Indeed, our dataset is quite convenient because mammals have relatively small population sizes, which allow large amount of deleterious mutations to be fixed, and thus, there are a lot of opportunities for maintenance positive selection to arise.
     It would thus be of great interest to reproduce our experiment with other clades, such as \textit{Drosophila} or birds which tend to have higher effective population size.
@@
     \label{sec:acknowledgment}
+    We gratefully also acknowledge the help of Diego A. Hartasánchez Frenk for his advice and review concerning this manuscript.
     This work was performed using the computing facilities of the CC LBBE/PRABI\@.
@@
 
-    \subsection*{Substitution mapping in the terminal branch}
-
-    For each population with polymorphism data available, the polarized SNPs (ancestral and derived alleles) are used to correct the DNA reference sequence such as to contain only substitutions and no segregating polymorphisms.
-    If a SNP is still segregating in the population, the ancestral version of the SNP is used.
-    However, if the derived allele is shared by all individuals in the population, the allele is considered fixed and the derived allele of the SNP is used instead.
-    Then, using this corrected DNA reference and the $3$ closest outgroups found in the OrthoMam alignment, we reconstructed the ancestral protein-coding DNA sequences for each node of the 4-leaves tree with FastML.v3.11\cite{ashkenazy_fastml_2012}.
-    All polarized codon substitutions are then obtained by comparing the ancestral protein-coding DNA sequences before the split to the sister species (closest outgroup) to the corrected DNA reference for the population of interest.
-    We considered \textit{Ceratotherium simum simum} as \textit{Equus caballus} sister species; \textit{Bison bison bison} as \textit{Bos taurus} sister species; \textit{Pantholops hodgsonii} as \textit{Ovis aries} sister species; \textit{Pantholops hodgsonii} as \textit{Capra Hircus} sister species; \textit{Macaca mulatta} as \textit{Chlorocebus sabaeus} sister species and finally we considered \textit{Pan troglodytes} as \textit{Homo sapiens} sister species.
-    The selection coefficient ($\Sphy$) of each substitution is then obtained by comparing the difference in amino-acid fitnesses for each polarized non-synonymous codon substitution, by referring to the site-specific fitness profile obtained in the phylogeny-based method (see~\ref{subsec:s-phylogeny-method}).
-
     \subsection{Selection coefficient ($\Spop$) in population-based method}
@@
     Second, from this reconstructed sequence, all possible mutations are computed, weighted by the mutation rate between nucleotide estimated at the phylogenetic scale $\UniDimArray{\mu}$.
-    Third, these possible mutations are then classified whether they are synonymous or non-synonymous (stop mutations are excluded), non-synonymous mutations are then also classified depending on their selection coefficient ($\Sphy$).
-    Fourth, the number of sites for each class of selection coefficient is then computed as the total number of sites across the genome weighted by the ratio of the aggregated mutations rates falling in the class over the total mutation rate for all possible mutations.
-    From the SFS and the number of sites for the both synonymous and for the class of non-synonymous, polyDFE estimates parameters of the DFE $\phi \left( \Spop; \Spop_d , b, p_b, \Spop_b \right)$ using maximum likelihood.
+    Third, the total mutation rate for synonymous mutations, called $\mu_{\mathrm{syn}}$, is the sum across the genome.
+    Similarly, the total mutation rate for each class of selection, called  $\mu_{\Sphyclass}$, is the sum across all non-synonymous mutations if their selection coefficient at the phylogenetic scale ($\Sphy$) is in the class $\Sphyclass$, where $\Sphyclass \in \{\divStrongDel, \divDel, \divWeakDel, \divWeakAdv, \divAdv \}$.
+    Fourth, the number of sites ($L$) for each class of selection coefficient ($\Sphyclass$) is then computed as the total number of sites across the genome ($L_{tot}$) weighted by the ratio of the aggregated mutations rates falling in the class ($\mu_{\Sphyclass}$) over the total mutation rate for all possible mutations:
+    \begin{align*}
+        L_{\mathrm{non-syn}} | \Sphyclass &= L_{tot} \frac{\mu_{\Sphyclass}}{\mu_{tot}},
+        L_{\mathrm{syn}} &= L_{tot} \frac{\mu_{\mathrm{syn}}}{\mu_{tot}},
+    \end{align*}
+    From the SFS and the number of sites $L$ for the both synonymous and for the class of non-synonymous, polyDFE estimates parameters of the DFE $\phi \left( \Spop; \Spop_d , b, p_b, \Spop_b \right)$ using maximum likelihood.
 
-    %
-    %We first leveraged phylogenetic codon models which are based on a population-genetics formalism, assuming a non-adaptive fitness landscape.
-    %These models estimate the fitness of each of the 20 amino acids for each protein site, given mammalian protein-coding DNA alignments and gene tree topologies.
-    %Second, we integrated mammalian divergence data with polymorphic variants found in 28 populations across 6 mammalian genera.
-    %For each non-synonymous variant observed at the population level, we predicted its change in fitness from amino-acid fitnesses estimated at the mammalian scale.
+    \subsection*{Substitution mapping in the terminal branch}
+    \label{subsec:substitution-mapping-in-the-terminal-branch}
+    For each population with polymorphism data available, the polarized SNPs (ancestral and derived alleles) are used to correct the DNA reference sequence such as to contain only substitutions and no segregating polymorphisms.
+    If a SNP is still segregating in the population, the ancestral version of the SNP is used.
+    However, if the derived allele is shared by all individuals in the population, the allele is considered fixed and the derived allele of the SNP is used instead.
+    Then, using this ancestral DNA reference and the $3$ closest outgroups found in the OrthoMam alignment, we reconstructed the ancestral protein-coding DNA sequences for each node of the 4-leaves tree with the yang M5 codon model (gamma site rate variation) in FastML.v3.11\cite{ashkenazy_fastml_2012}.
+    All polarized codon substitutions are then obtained by comparing the ancestral protein-coding DNA sequences before the split to the sister species (closest outgroup) to the corrected DNA reference for the population of interest.
+    We considered \textit{Ceratotherium simum simum} as \textit{Equus caballus} sister species; \textit{Bison bison bison} as \textit{Bos taurus} sister species; \textit{Pantholops hodgsonii} as \textit{Ovis aries} sister species; \textit{Pantholops hodgsonii} as \textit{Capra Hircus} sister species; \textit{Macaca mulatta} as \textit{Chlorocebus sabaeus} sister species and finally we considered \textit{Pan troglodytes} as \textit{Homo sapiens} sister species.
+    The selection coefficient ($\Sphy$) of each substitution is then obtained by comparing the difference in amino-acid fitnesses for each polarized non-synonymous codon substitution, by referring to the site-specific fitness profile obtained in the phylogeny-based method (see~\ref{subsec:s-phylogeny-method}).
+    Finally, the rate of non-synonymous over synonymous substitution for a given class of selection coefficient ($\Sphyclass$) is computed as:
+    \begin{equation*}
+        \dnds | \Sphyclass = \frac{\sfrac{D_{\mathrm{non-syn} | \Sphyclass}}{L_{\mathrm{non-syn}} | \Sphyclass}}{\sfrac{D_{\mathrm{syn}}}{L_{\mathrm{syn}}}},
+    \end{equation*}
+    where $D_{\mathrm{non-syn}} | \Sphyclass $ is the number of non-synonymous substitutions in the class $\Sphyclass$, $D_{\mathrm{syn}}$ is the number of synonymous substitutions across the genome, while $L_{\mathrm{non-syn}} | \Sphyclass$ and $L_{\mathrm{syn}}$ are the number of non-synonymous and synonymous sites as defined in the previous section.
 

### 2022-07-10 manuscript/supp-mat.tex
R as function of diversity in figure 5

@@
 
-\usepackage[margin=60pt]{geometry}
+\usepackage[margin=50pt]{geometry}
 \usepackage{amssymb,amsfonts,amsmath,amsthm,mathtools}
@@
 
-    \section{Site-specific mutation-selection codon models}
-
+    \section{Site-specific mutation-selection codon models}\label{sec:site-specific-mutation-selection-codon-models}
     In BayesCode (\url{https://github.com/ThibaultLatrille/bayescode}), mutation-selection codon models are obtained by running \textit{mutselomega} for 2000 points of MCMC with the options:
@@
 
-    \subsection{Summary table}
-
+    \subsection{Summary table}\label{subsec:summary-table-mutsel}
     \begin{center}
-        \footnotesize
+        \scriptsize
         \begin{longtable}{|l|l|r|r|r|r|r|r|}
@@
             Equus c.
-& Equus caballus      & $ 0.002$        & $ 0.042$                   & $ 0.018$                      & $ 0.404$                             & $ 0.113$                      & $ 1.123$           \\
-            Iran                 & Bos taurus          & $ 0.005$        & $ 0.036$                   & $ 0.017$                      & $ 0.368$                             & $ 0.105$                      & $ 1.233$           \\
-            Uganda               & Bos taurus          & $ 0.006$        & $ 0.035$                   & $ 0.017$                      & $ 0.369$                             & $ 0.107$                      & $ 1.260$           \\
+& Equus caballus      & $ 0.002$        & $ 0.042$                   & $ 0.018$                      & $ 0.404$                             & $ 0.115$                      & $ 1.197$           \\
+            Iran                 & Bos taurus          & $ 0.005$        & $ 0.036$                   & $ 0.017$                      & $ 0.368$                             & $ 0.125$                      & $ 1.322$           \\
+            Uganda               & Bos taurus          & $ 0.006$        & $ 0.035$                   & $ 0.017$                      & $ 0.369$                             & $ 0.126$                      & $ 1.363$           \\
             Australia            & Capra hircus        & $ 0.003$        & $ 0.036$                   & $ 0.017$                      & $ 0.144$                             & $ 0.122$                      & $ 1.035$           \\
@@
             Morocco              & Capra hircus        & $ 0.004$        & $ 0.029$                   & $ 0.017$                      & $ 0.137$                             & $ 0.124$                      & $ 1.057$           \\
-            Iran                 & Ovis aries          & $ 0.008$        & $ 0.022$                   & $ 0.018$                      & $ 0.046$                             & $ 0.102$                      & $ 1.148$           \\
+            Iran                 & Ovis aries          & $ 0.008$        & $ 0.022$                   & $ 0.018$                      & $ 0.046$                             & $ 0.104$                      & $ 1.180$           \\
             Iran (O.
-orientalis) & Ovis aries          & $ 0.009$        & $ 0.025$                   & $ 0.018$                      & $ 0.071$                             & $ 0.099$                      & $ 1.120$           \\
+orientalis) & Ovis aries          & $ 0.009$        & $ 0.025$                   & $ 0.018$                      & $ 0.071$                             & $ 0.103$                      & $ 1.187$           \\
             Iran (O.
-vignei)     & Ovis aries          & $ 0.008$        & $ 0.028$                   & $ 0.018$                      & $ 0.220$                             & $ 0.103$                      & $ 1.149$           \\
-            Various              & Ovis aries          & $ 0.009$        & $ 0.024$                   & $ 0.018$                      & $ 0.108$                             & $ 0.100$                      & $ 1.126$           \\
-            Morocco              & Ovis aries          & $ 0.008$        & $ 0.020$                   & $ 0.018$                      & $ 0.070$                             & $ 0.099$                      & $ 1.109$           \\
-            Barbados             & Chlorocebus sabaeus & $ 0.004$        & $ 0.040$                   & $ 0.015$                      & $ 0.374$                             & $ 0.126$                      & $ 1.417$           \\
-            Central Afr. Rep.    & Chlorocebus sabaeus & $ 0.006$        & $ 0.034$                   & $ 0.015$                      & $ 0.368$                             & $ 0.124$ & $ 1.445$ \\
-            Ethiopia             & Chlorocebus sabaeus & $ 0.005$        & $ 0.040$                   & $ 0.015$                      & $ 0.368$                             & $ 0.123$                      & $ 1.422$           \\
-            Gambia               & Chlorocebus sabaeus & $ 0.005$        & $ 0.031$                   & $ 0.015$                      & $ 0.377$                             & $ 0.127$                      & $ 1.446$           \\
-            Kenya                & Chlorocebus sabaeus & $ 0.006$        & $ 0.035$                   & $ 0.015$                      & $ 0.308$                             & $ 0.128$                      & $ 1.453$           \\
-            Nevis                & Chlorocebus sabaeus & $ 0.004$        & $ 0.037$                   & $ 0.015$                      & $ 0.368$                             & $ 0.125$                      & $ 1.416$           \\
-            South Africa         & Chlorocebus sabaeus & $ 0.007$        & $ 0.034$                   & $ 0.015$                      & $ 0.368$                             & $ 0.125$                      & $ 1.453$           \\
-            Saint Kitts          & Chlorocebus sabaeus & $ 0.004$        & $ 0.039$                   & $ 0.015$                      & $ 0.368$                             & $ 0.126$                      & $ 1.420$           \\
-            Zambia               & Chlorocebus sabaeus & $ 0.006$        & $ 0.038$                   & $ 0.015$                      & $ 0.368$                             & $ 0.123$                      & $ 1.424$           \\
+vignei)     & Ovis aries          & $ 0.008$        & $ 0.028$                   & $ 0.018$                      & $ 0.220$                             & $ 0.104$                      & $ 1.172$           \\
+            Various              & Ovis aries          & $ 0.009$        & $ 0.024$                   & $ 0.018$                      & $ 0.108$                             & $ 0.103$                      & $ 1.182$           \\
+            Morocco              & Ovis aries          & $ 0.008$        & $ 0.020$                   & $ 0.018$                      & $ 0.070$                             & $ 0.104$                      & $ 1.189$           \\
+            Barbados             & Chlorocebus sabaeus & $ 0.004$        & $ 0.040$                   & $ 0.015$                      & $ 0.374$                             & $ 0.123$                      & $ 1.341$           \\
+            Central Afr. Rep.    & Chlorocebus sabaeus & $ 0.006$        & $ 0.034$                   & $ 0.015$                      & $ 0.368$                             & $ 0.124$ & $ 1.370$ \\
+            Ethiopia             & Chlorocebus sabaeus & $ 0.005$        & $ 0.040$                   & $ 0.015$                      & $ 0.368$                             & $ 0.124$                      & $ 1.361$           \\
+            Gambia               & Chlorocebus sabaeus & $ 0.005$        & $ 0.031$                   & $ 0.015$                      & $ 0.377$                             & $ 0.124$                      & $ 1.359$           \\
+            Kenya                & Chlorocebus sabaeus & $ 0.006$        & $ 0.035$                   & $ 0.015$                      & $ 0.308$                             & $ 0.125$                      & $ 1.371$           \\
+            Nevis                & Chlorocebus sabaeus & $ 0.004$        & $ 0.037$                   & $ 0.015$                      & $ 0.368$                             & $ 0.124$                      & $ 1.349$           \\
+            South Africa         & Chlorocebus sabaeus & $ 0.007$        & $ 0.034$                   & $ 0.015$                      & $ 0.368$                             & $ 0.126$                      & $ 1.391$           \\
+            Saint Kitts          & Chlorocebus sabaeus & $ 0.004$        & $ 0.039$                   & $ 0.015$                      & $ 0.368$                             & $ 0.125$                      & $ 1.362$           \\
+            Zambia               & Chlorocebus sabaeus & $ 0.006$        & $ 0.038$                   & $ 0.015$                      & $ 0.368$                             & $ 0.124$                      & $ 1.362$           \\
             African              & Homo sapiens        & $ 0.003$        & $ 0.038$                   & $ 0.015$                      & $ 0.604$                             & $ 0.104$                      & $ 1.475$           \\
@@
     \begin{center}
-        \footnotesize
+        \scriptsize
         \begin{longtable}{|l|l|r|r|r|r|r|r|r|r|}
             \toprule
-            Population           & Species             & Tajima $\theta_{\pi}$ & $\mathbb{P}_{div}[\Sphy > 0]$ & $\dnds $ & $\dnds  | S<0$ & R($\dnds $) & $p_b $ & $p_b  | S<0$ & R($p_b $) \\
+            Population           & Species             & Tajima $\theta_{\pi}$ & $\mathbb{P}_{div}[\Sphy > 0]$ & $\dnds $ & $\dnds  | S<0$ & R($\dnds $) & $p_+ $ & $p_+  | S<0$ & R($p_+ $) \\
             \midrule
@@
             \endlastfoot
-            Equus c. &       Equus caballus &               $ 0.002$ &                $ 0.301$ &        $ 0.183$ &              $ 0.135$ &           $  26.2$ & $ 0.113$ &     $ 0.081$ &  $  28.5$ \\
-            Iran &           Bos taurus &               $ 0.005$ &                $ 0.266$ &        $ 0.199$ &              $ 0.154$ &           $  22.6$ & $ 0.098$ &     $ 0.067$ &  $  31.2$ \\
-            Uganda &           Bos taurus &               $ 0.006$ &                $ 0.267$ &        $ 0.201$ &              $ 0.156$ &           $  22.6$ & $ 0.094$ &     $ 0.062$ &  $  33.8$ \\
-            Australia &         Capra hircus &               $ 0.003$ &                $ 0.301$ &        $ 0.148$ &              $ 0.109$ &           $  26.1$ & $ 0.096$ &     $ 0.071$ &  $  26.2$ \\
-            France &         Capra hircus &               $ 0.004$ &                $ 0.301$ &        $ 0.149$ &              $ 0.110$ &           $  26.1$ & $ 0.092$ &     $ 0.067$ &  $  26.7$ \\
-            Iran (C.
-aegagrus) &         Capra hircus &               $ 0.004$ &                $ 0.301$ &        $ 0.148$ &              $ 0.109$ &           $  26.1$ & $ 0.096$ &     $ 0.072$ &  $  25.0$ \\
-            Iran &         Capra hircus &               $ 0.004$ &                $ 0.303$ &        $ 0.148$ &              $ 0.109$ &           $  26.4$ & $ 0.080$ &     $ 0.055$ &  $  31.9$ \\
-            Italy &         Capra hircus &               $ 0.004$ &                $ 0.301$ &        $ 0.149$ &              $ 0.110$ &           $  26.1$ & $ 0.087$ &     $ 0.060$ &  $  30.5$ \\
-            Morocco &         Capra hircus &               $ 0.004$ &                $ 0.303$ &        $ 0.148$ &              $ 0.109$ &           $  26.4$ & $ 0.079$ &     $ 0.054$ &  $  31.5$ \\
-            Iran &           Ovis aries &               $ 0.008$ &                $ 0.229$ &        $ 0.198$ &              $ 0.161$ &           $  18.6$ & $ 0.060$ &     $ 0.038$ &  $  36.5$ \\
-            Iran (O.
-orientalis) &           Ovis aries &               $ 0.009$ &                $ 0.226$ &        $ 0.200$ &              $ 0.164$ &           $  18.2$ & $ 0.067$ &     $ 0.044$ &  $  33.4$ \\
-            Iran (O.
-vignei) &           Ovis aries &               $ 0.008$ &                $ 0.235$ &        $ 0.197$ &              $ 0.159$ &           $  19.2$ & $ 0.075$ &     $ 0.052$ &  $  30.5$ \\
-            Various &           Ovis aries &               $ 0.009$ &                $ 0.226$ &        $ 0.199$ &              $ 0.163$ &           $  18.2$ & $ 0.064$ &     $ 0.041$ &  $  36.7$ \\
-            Morocco &           Ovis aries &               $ 0.008$ &                $ 0.225$ &        $ 0.199$ &              $ 0.163$ &           $  18.1$ & $ 0.055$ &     $ 0.034$ &  $  38.0$ \\
-            Barbados &  Chlorocebus sabaeus &               $ 0.004$ &                $ 0.305$ &        $ 0.169$ &              $ 0.123$ &           $  26.9$ & $ 0.109$ &     $ 0.081$ &  $  25.3$ \\
-            Central Afr.
-Rep.
-&  Chlorocebus sabaeus &               $ 0.006$ &                $ 0.307$ &        $ 0.174$ &              $ 0.127$ &           $  27.0$ & $ 0.094$ &     $ 0.063$ &  $  33.1$ \\
-            Ethiopia &  Chlorocebus sabaeus &               $ 0.005$ &                $ 0.305$ &        $ 0.172$ &              $ 0.126$ &           $  26.9$ & $ 0.108$ &     $ 0.081$ &  $  25.0$ \\
-            Gambia &  Chlorocebus sabaeus &               $ 0.005$ &                $ 0.307$ &        $ 0.171$ &              $ 0.124$ &           $  27.1$ & $ 0.084$ &     $ 0.057$ &  $  31.8$ \\
-            Kenya &  Chlorocebus sabaeus &               $ 0.006$ &                $ 0.309$ &        $ 0.170$ &              $ 0.124$ &           $  27.2$ & $ 0.095$ &     $ 0.071$ &  $  25.0$ \\
-            Nevis &  Chlorocebus sabaeus &               $ 0.004$ &                $ 0.305$ &        $ 0.169$ &              $ 0.124$ &           $  26.8$ & $ 0.101$ &     $ 0.077$ &  $  23.6$ \\
-            South Africa &  Chlorocebus sabaeus &               $ 0.007$ &                $ 0.309$ &        $ 0.173$ &              $ 0.126$ &           $  27.2$ & $ 0.094$ &     $ 0.068$ &  $  27.7$ \\
-            Saint Kitts &  Chlorocebus sabaeus &               $ 0.004$ &                $ 0.309$ &        $ 0.168$ &              $ 0.122$ &           $  27.2$ & $ 0.106$ &     $ 0.079$ &  $  26.1$ \\
-            Zambia &  Chlorocebus sabaeus &               $ 0.006$ &                $ 0.307$ &        $ 0.173$ &              $ 0.126$ &           $  27.0$ & $ 0.104$ &     $ 0.077$ &  $  25.6$ \\
-            African &         Homo sapiens &               $ 0.003$ &                $ 0.259$ &        $ 0.216$ &              $ 0.169$ &           $  21.9$ & $ 0.103$ &     $ 0.069$ &  $  32.4$ \\
-            Admixed American &         Homo sapiens &               $ 0.002$ &                $ 0.258$ &        $ 0.216$ &              $ 0.169$ &           $  21.8$ & $ 0.104$ &     $ 0.071$ &  $  31.3$ \\
-            East Asian &         Homo sapiens &               $ 0.002$ &                $ 0.259$ &        $ 0.217$ &              $ 0.169$ &           $  22.0$ & $ 0.098$ &     $ 0.068$ &  $  30.3$ \\
-            European &         Homo sapiens &               $ 0.002$ &                $ 0.258$ &        $ 0.216$ &              $ 0.169$ &           $  21.8$ & $ 0.097$ &     $ 0.067$ &  $  31.0$ \\
-            South Asian &         Homo sapiens &               $ 0.002$ &                $ 0.259$ &        $ 0.216$ &              $ 0.169$ &           $  21.9$ & $ 0.096$ &     $ 0.066$ &  $  31.7$ \\
+            Equus c.             & Equus caballus      & $ 0.002$              & $ 0.275$                      & $ 0.148$ & $ 0.113$     & $  23.4$      & $ 0.042$ & $ 0.030$ & $  28.5$ \\
+            Iran                 & Bos taurus          & $ 0.005$              & $ 0.274$                      & $ 0.130$ & $ 0.100$     & $  23.3$      & $ 0.036$ & $ 0.025$   & $  30.9$    \\
+            Uganda               & Bos taurus          & $ 0.006$              & $ 0.277$                      & $ 0.133$ & $ 0.101$     & $  23.6$      & $ 0.035$ & $ 0.023$   & $  33.7$    \\
+            Australia            & Capra hircus        & $ 0.003$              & $ 0.286$                      & $ 0.126$ & $ 0.095$     & $  24.6$      & $ 0.036$ & $ 0.026$ & $  26.8$ \\
+            France               & Capra hircus        & $ 0.004$              & $ 0.286$                      & $ 0.127$ & $ 0.096$     & $  24.6$      & $ 0.034$ & $ 0.025$ & $  26.7$ \\
+            Iran (C. aegagrus)   & Capra hircus        & $ 0.004$              & $ 0.285$                      & $ 0.126$ & $ 0.095$     & $  24.5$      & $ 0.035$ & $ 0.026$ & $  25.0$ \\
+            Iran                 & Capra hircus        & $ 0.004$              & $ 0.288$                      & $ 0.126$ & $ 0.095$     & $  24.8$      & $ 0.030$ & $ 0.020$   & $  31.8$    \\
+            Italy                & Capra hircus        & $ 0.004$              & $ 0.287$                      & $ 0.127$ & $ 0.096$     & $  24.6$      & $ 0.032$ & $ 0.022$   & $  30.6$    \\
+            Morocco              & Capra hircus        & $ 0.004$              & $ 0.288$                      & $ 0.126$ & $ 0.095$     & $  24.7$      & $ 0.029$ & $ 0.020$ & $  31.5$ \\
+            Iran                 & Ovis aries          & $ 0.008$              & $ 0.243$                      & $ 0.149$ & $ 0.120$     & $  20.0$      & $ 0.022$ & $ 0.014$   & $  36.5$    \\
+            Iran (O. orientalis) & Ovis aries          & $ 0.009$              & $ 0.241$                      & $ 0.151$ & $ 0.121$     & $  19.8$      & $ 0.025$ & $ 0.016$ & $  33.4$ \\
+            Iran (O. vignei)     & Ovis aries          & $ 0.008$              & $ 0.243$                      & $ 0.149$ & $ 0.119$     & $  20.0$      & $ 0.028$ & $ 0.019$ & $  30.5$ \\
+            Various              & Ovis aries          & $ 0.009$              & $ 0.240$                      & $ 0.151$ & $ 0.121$     & $  19.7$      & $ 0.024$ & $ 0.015$   & $  36.7$    \\
+            Morocco              & Ovis aries          & $ 0.008$              & $ 0.241$                      & $ 0.151$ & $ 0.121$     & $  19.7$      & $ 0.020$ & $ 0.013$   & $  38.0$    \\
+            Barbados             & Chlorocebus sabaeus & $ 0.004$              & $ 0.289$                      & $ 0.141$ & $ 0.106$     & $  25.1$      & $ 0.040$ & $ 0.030$ & $  25.3$ \\
+            Central Afr. Rep.    & Chlorocebus sabaeus & $ 0.006$              & $ 0.287$                      & $ 0.141$ & $ 0.106$     & $  24.9$ & $ 0.034$ & $ 0.026$ & $  24.7$ \\
+            Ethiopia             & Chlorocebus sabaeus & $ 0.005$              & $ 0.290$                      & $ 0.141$ & $ 0.105$     & $  25.2$      & $ 0.040$ & $ 0.030$ & $  25.0$ \\
+            Gambia               & Chlorocebus sabaeus & $ 0.005$              & $ 0.287$                      & $ 0.141$ & $ 0.106$     & $  25.0$      & $ 0.031$ & $ 0.021$ & $  31.8$ \\
+            Kenya                & Chlorocebus sabaeus & $ 0.006$              & $ 0.290$                      & $ 0.142$ & $ 0.106$     & $  25.2$      & $ 0.035$ & $ 0.026$ & $  24.9$ \\
+            Nevis                & Chlorocebus sabaeus & $ 0.004$              & $ 0.289$                      & $ 0.141$ & $ 0.106$     & $  25.1$      & $ 0.037$ & $ 0.028$ & $  23.6$ \\
+            South Africa         & Chlorocebus sabaeus & $ 0.007$              & $ 0.291$                      & $ 0.141$ & $ 0.105$     & $  25.4$      & $ 0.035$ & $ 0.025$ & $  27.7$ \\
+            Saint Kitts          & Chlorocebus sabaeus & $ 0.004$              & $ 0.290$                      & $ 0.141$ & $ 0.105$     & $  25.3$      & $ 0.039$ & $ 0.029$ & $  26.1$ \\
+            Zambia               & Chlorocebus sabaeus & $ 0.006$              & $ 0.288$                      & $ 0.141$ & $ 0.106$     & $  25.0$      & $ 0.038$ & $ 0.029$ & $  25.3$ \\
+            African              & Homo sapiens        & $ 0.003$              & $ 0.243$                      & $ 0.195$ & $ 0.156$     & $  20.2$      & $ 0.038$ & $ 0.026$ & $  32.4$ \\
+            Admixed American     & Homo sapiens        & $ 0.002$              & $ 0.242$                      & $ 0.195$ & $ 0.156$     & $  20.2$      & $ 0.038$ & $ 0.026$ & $  31.3$ \\
+            East Asian           & Homo sapiens        & $ 0.002$              & $ 0.244$                      & $ 0.195$ & $ 0.155$     & $  20.4$      & $ 0.036$ & $ 0.025$ & $  30.2$ \\
+            European             & Homo sapiens        & $ 0.002$              & $ 0.242$                      & $ 0.195$ & $ 0.156$     & $  20.1$      & $ 0.036$ & $ 0.025$ & $  30.9$ \\
+            South Asian          & Homo sapiens        & $ 0.002$              & $ 0.244$                      & $ 0.195$ & $ 0.156$     & $  20.3$      & $ 0.035$ & $ 0.024$ & $  31.7$ \\
         \end{longtable}
@@
         \item $R(\dnds)=\dfrac{\dnds - \dnds[\Sphy < 0]}{\dnds}$ is the fraction of the divergence ($\dnds$) that is over-estimated, $\dnds$ is compared to the estimated divergence when we removed the restoring substitutions $\dnds[\Sphy < 0]$.
-        \item $p_b$ is the probability for a new mutation to be advantageous, estimated (with polyDFE) using all available polymorphism.
-        \item $p_b[\Sphy < 0]$ is the probability for a new mutation to be advantageous, estimated (with polyDFE) using polymorphism with a selection coefficient lower than 0 ($\Sphy < 0$).
+        \item $p_+=\PpolyAdv$ is the probability for a new mutation to be advantageous, estimated (with polyDFE) using all available polymorphism.
+        \item $p_+[\Sphy < 0]$ is the probability for a new mutation to be advantageous, estimated (with polyDFE) using polymorphism with a selection coefficient lower than 0 ($\Sphy < 0$).
         This is the estimated probability for a new mutation to be advantageous when we removed the restoring polymorphism from the dataset.
-        \item $R(p_b)=\dfrac{p_b - p_b[\Sphy < 0]}{p_b}$ is the fraction of the probability for a new mutation to be advantageous ($p_b$) that is over-estimated, $p_b$ is compared to its estimation when we had removed all the restoring mutations $p_b[\Sphy < 0]$.
+        \item $R(p_+)=\dfrac{p_+ - p_+[\Sphy < 0]}{p_+}$ is the fraction of the probability for a new mutation to be advantageous ($p_+$) that is over-estimated, $p_+$ is compared to its estimation when we had removed all the restoring mutations $p_+[\Sphy < 0]$.
     \end{itemize}
@@
 
-    \subsubsection{Proportion of nearly-neutral mutations ($\polyNeutral$)}
+    \subsubsection{Proportion of nearly-neutral mutations ($\polyNeutral$)}\label{subsec:proportion-nearly-neutral-mutations}
 
     \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression/results.watterson.all_P-Seq0.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression-MutSel/results.watterson.all_P-Seq0.scatter.pdf}
     \end{minipage}
     \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression/results.watterson.neg-weak_P-Seq0.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression-MutSel/results.watterson.neg-weak_P-Seq0.scatter.pdf}
     \end{minipage}
     \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression/results.watterson.pos-weak_P-Seq0.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression-MutSel/results.watterson.pos-weak_P-Seq0.scatter.pdf}
     \end{minipage}
@@
 
-    \subsubsection{Proportion of deleterious mutations ($\polyDel$)}
+    \subsubsection{Proportion of deleterious mutations ($\polyDel$)}\label{subsec:proportion-deleterious-mutations}
 
     \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression/results.watterson.all_P-Sinf0.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression-MutSel/results.watterson.all_P-Sinf0.scatter.pdf}
     \end{minipage}
     \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression/results.watterson.neg_P-Sinf0.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression-MutSel/results.watterson.neg_P-Sinf0.scatter.pdf}
     \end{minipage}
     \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression/results.watterson.neg-strong_P-Sinf0.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression-MutSel/results.watterson.neg-strong_P-Sinf0.scatter.pdf}
     \end{minipage}
@@
 
-    \subsubsection{Proportion of advantageous mutations ($\polyAdv$)}
+    \subsubsection{Proportion of advantageous mutations ($\polyAdv$)}\label{subsec:proportion-advantageous-mutations}
 
     \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression/results.watterson.all_P-Ssup0.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression-MutSel/results.watterson.all_P-Ssup0.scatter.pdf}
     \end{minipage}
     \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression/results.watterson.pos_P-Ssup0.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression-MutSel/results.watterson.pos_P-Ssup0.scatter.pdf}
     \end{minipage}
@@
 
-    \subsection{Selection efficacy correlation with diversity}
+    \subsection{Selection efficacy correlation with diversity}\label{subsec:selection-efficacy-correlation-with-diversity}
 
@@
     The relationship between $\SpopMean$ and $\SphyMean$ can be described by a second-order polynomial, and the slope of this polynomial at $\SphyMean=0$ gives the ratio $\SpopMean/\SphyMean$ for each population.
-    We observe that $\SpopMean/\SphyMean$, representing the efficacy of selection at the short versus long-term is positively correlated with synonymous diversity, a proxy of effective population size.
-    Altogether, populations with a large effective population size are under more efficient selection, confirming the prediction of the nearly-neutral theory of evolution.
-    As a consequence of an increased selection efficiency, mutations in populations with high diversity are mechanistically more likely to be deleterious (fig.~S4), especially for mutations predicted already to be deleterious at the phylogenetic scale (fig.~S5-6).
 
@@
 
+    We observe that $\SpopMean/\SphyMean$, representing the efficacy of selection at the short versus long-term is positively correlated with synonymous diversity, a proxy of effective population size.
+    Altogether, populations with a large effective population size are under more efficient selection, confirming the prediction of the nearly-neutral theory of evolution that mutations are less likely to be considered neutral in populations with high diversity (see~\ref{subsec:proportion-nearly-neutral-mutations}, left scatter-plot), especially for mutations predicted already to be nearly-neutral at the phylogenetic scale (see~\ref{subsec:proportion-nearly-neutral-mutations}, middle and right scatter-plot).
+    As a consequence of an increased selection efficiency, mutations in populations with high diversity are mechanistically more likely to be deleterious (see~\ref{subsec:proportion-deleterious-mutations}, left scatter-plot), especially for mutations predicted already to be deleterious at the phylogenetic scale (see~\ref{subsec:proportion-deleterious-mutations}, middle and right scatter-plot).
+
     \input{include-MutSel-non-adaptive}
 
-    %\section{SIFT scores}
-    %\input{include-SIFT-non-adaptive}
+    \section{SIFT scores}\label{sec:sift-scores}
+
+    \subsection{Summary table}\label{subsec:summary-table-sift-scores}
+
+    \begin{center}
+        \footnotesize
+        \begin{longtable}{|l|l|r|r|r|r|}
+            \toprule
+            Population           & Species             & Tajima $\theta_{\pi}$ & $p_+$    & $p_+ [ SIFT < 0.8]$ & R($p_+$) \\
+            \midrule
+            \endhead
+            \midrule
+            \multicolumn{6}{r}{{Continued on next page}} \\
+            \midrule
+            \endfoot
+
+            \bottomrule
+            \endlastfoot
+            Equus c.             & Equus caballus      & $ 0.002$              & $ 0.042$ & $ 0.037$            & $  12.2$   \\
+            Iran                 & Bos taurus          & $ 0.005$              & $ 0.036$ & $ 0.031$            & $  14.7$   \\
+            Uganda               & Bos taurus          & $ 0.006$              & $ 0.035$ & $ 0.029$            & $  16.2$   \\
+            Australia            & Capra hircus        & $ 0.003$              & $ 0.036$ & $ 0.032$            & $ 9.214$ \\
+            France               & Capra hircus        & $ 0.004$              & $ 0.034$ & $ 0.034$            & $-1.445$ \\
+            Iran (C. aegagrus)   & Capra hircus        & $ 0.004$              & $ 0.035$ & $ 0.032$            & $ 9.881$ \\
+            Iran                 & Capra hircus        & $ 0.004$              & $ 0.030$ & $ 0.026$            & $  12.3$   \\
+            Italy                & Capra hircus        & $ 0.004$              & $ 0.032$ & $ 0.029$            & $ 8.754$ \\
+            Morocco              & Capra hircus        & $ 0.004$              & $ 0.029$ & $ 0.025$            & $  12.7$   \\
+            Iran                 & Ovis aries          & $ 0.008$              & $ 0.022$ & $ 0.019$            & $  12.9$   \\
+            Iran (O. orientalis) & Ovis aries          & $ 0.009$              & $ 0.025$ & $ 0.021$            & $  13.6$   \\
+            Iran (O. vignei)     & Ovis aries          & $ 0.008$              & $ 0.028$ & $ 0.024$            & $  14.2$   \\
+            Various              & Ovis aries          & $ 0.009$              & $ 0.024$ & $ 0.019$            & $  19.0$   \\
+            Morocco              & Ovis aries          & $ 0.008$              & $ 0.020$ & $ 0.017$            & $  14.4$   \\
+            Barbados             & Chlorocebus sabaeus & $ 0.004$              & $ 0.040$ & $ 0.037$            & $ 7.660$ \\
+            Central Afr. Rep.    & Chlorocebus sabaeus & $ 0.006$              & $ 0.034$ & $ 0.032$            & $ 7.610$ \\
+            Ethiopia             & Chlorocebus sabaeus & $ 0.005$              & $ 0.040$ & $ 0.037$            & $ 7.464$ \\
+            Gambia               & Chlorocebus sabaeus & $ 0.005$              & $ 0.031$ & $ 0.028$            & $ 9.891$ \\
+            Kenya                & Chlorocebus sabaeus & $ 0.006$              & $ 0.035$ & $ 0.033$            & $ 6.180$ \\
+            Nevis                & Chlorocebus sabaeus & $ 0.004$              & $ 0.037$ & $ 0.035$            & $ 6.532$ \\
+            South Africa         & Chlorocebus sabaeus & $ 0.007$              & $ 0.034$ & $ 0.031$            & $ 8.924$ \\
+            Saint Kitts          & Chlorocebus sabaeus & $ 0.004$              & $ 0.039$ & $ 0.036$            & $ 7.642$ \\
+            Zambia               & Chlorocebus sabaeus & $ 0.006$              & $ 0.039$ & $ 0.035$            & $ 8.197$ \\
+            African              & Homo sapiens        & $ 0.003$              & $ 0.038$ & $ 0.032$            & $  17.1$   \\
+            Admixed American     & Homo sapiens        & $ 0.002$              & $ 0.039$ & $ 0.033$            & $  14.9$   \\
+            East Asian           & Homo sapiens        & $ 0.002$              & $ 0.036$ & $ 0.033$            & $ 9.250$ \\
+            European             & Homo sapiens        & $ 0.002$              & $ 0.036$ & $ 0.033$            & $ 8.704$ \\
+            South Asian          & Homo sapiens        & $ 0.002$              & $ 0.036$ & $ 0.032$            & $ 9.853$ \\
+        \end{longtable}
+
+    \end{center}
+    \begin{itemize}
+        \item Tajima $\theta$ is the synonymous diversity.
+        \item $p_+=\PpolyAdv$ is the probability for a new mutation to be advantageous, estimated (with polyDFE) using all available polymorphism.
+        \item $p_+ [ SIFT < 0.8]$ is the probability for a new mutation to be advantageous, estimated (with polyDFE) using polymorphism with a SIFT lower than 0.8 ($SIFT < 0.8$).
+        This is the estimated probability for a new mutation to be advantageous when we removed the restoring polymorphism from the dataset.
+        \item $R(p_+)=\dfrac{p_+ - p_+ [ SIFT < 0.8]}{p_+}$ is the fraction of the probability for a new mutation to be advantageous ($p_+$) that is over-estimated, $p_+$ is compared to its estimation when we had removed all the restoring mutations $p_+ [ SIFT < 0.8]$.
+    \end{itemize}
+    \input{include-SIFT-non-adaptive}
 

### 2022-07-10 scripts/plot_regression.py

@@ -16,13 +16,13 @@ alpha_suffix = alpha_sup_limits + ["_div", "_mkt", "_mkw", "_mkf"]
 omega_suffix = ["_div", "_dfe", "_NAdfe", "_Adiv", "_Adfe", "_Amkt", "_Amkw", "_Amkf"]
 
 
-def open_tsv(filepath, cat_snps):
+def open_tsv(filepath, cat_snps, method):
     ddf = pd.read_csv(filepath, sep="\t")
     if os.path.basename(filepath) == "Theta.results.tsv":
-        df_theta = ddf[(ddf["method"] == "MutSel") & (ddf["category"] == "syn")]
+        df_theta = ddf[(ddf["method"] == method) & (ddf["category"] == "syn")]
         df_theta = df_theta.dropna(axis='columns')
         df_theta = df_theta.drop(["method", "species", "category"], axis=1)
-        df_dfe = ddf[(ddf["method"] == "MutSel") & (ddf["category"] != "syn")]
+        df_dfe = ddf[(ddf["method"] == method) & (ddf["category"] != "syn")]
         cols = list(polydfe_cat_dico) + [f"P-{cat}" for cat in cat_snps.non_syn_list]
         cols += ['p_b', 'S_b', 'S_d', 'b', 'logL', 'S', 'S+', 'S-', 'fay_wu', 'tajima', 'watterson', 'div']
         cols += [f"omega{sup}" for sup in omega_suffix]
@@ -35,7 +35,7 @@ def open_tsv(filepath, cat_snps):
         df_pivot = pd.concat(m_list, axis=1)
         ddf = pd.merge(df_pivot, df_theta, on=["pop"])
     elif "bounds" in os.path.basename(filepath):
-        ddf = ddf[ddf["method"] == "MutSel"]
+        ddf = ddf[ddf["method"] == method]
         ddf = ddf.pivot(index="pop", columns="cat", values="sampled_fraction").add_suffix('_snps')
     return ddf
 
@@ -93,7 +93,7 @@ def generate_xy_plot(cat_snps):
         xy_dico["y"].append(y)
 
     xy_list = [("pos_snps", "all_P-Ssup0"), ("pos_snps", "pos_P-Ssup0"), ("pos_snps", "pos")]
-    xy_list += [("watterson", "all_p_b"), ("watterson", "ratio_neg_p_b"), ("watterson", "ratio_neg_omega_div")]
[…]

### 2022-07-10 scripts/substitutions_mapping.py

@@ -36,6 +36,19 @@ def plot_histogram(score_list, cat_snps, method, file):
     plt.close("all")
 
 
+def open_prob(path):
+    prob_list = []
+    with open(path) as f:
+        for line in f:
+            if "joint probs" in line:
+                f.readline()
+                break
+        for line in f:
+            prob = line.strip().split(",")[1]
+            prob_list.append(float(prob))
+    return prob_list
+
+
 def main(args):
     os.makedirs(os.path.dirname(args.output), exist_ok=True)
     dico_div = defaultdict(float)
@@ -54,10 +67,16 @@ def main(args):
         ancestor = t.get_leaves_by_name(args.species)[0].up.name
         anc_seq = seqs[ancestor]
         der_seq = seqs[args.species]
-
         assert len(anc_seq) == len(der_seq)
 
+        proba_path = anc_file.replace(".joint.fasta", ".join.prob")
+        prob_list = open_prob(proba_path)
+        assert len(prob_list) == (len(anc_seq) // 3)
+
         for c_site in range(len(anc_seq) // 3):
+            if prob_list[c_site] < args.threshold:
+                continue
+
             anc_codon = anc_seq[c_site * 3:c_site * 3 + 3]
             der_codon = der_seq[c_site * 3:c_site * 3 + 3]
             if anc_codon == der_codon:
@@ -111,4 +130,6 @@ if __name__ == '__main__':
     parser.add_argument('--bins', required=False, default=0, type=int, dest="bins", help="Number of bins")
     parser.add_argument('--windows', required=False, default=0, type=int, dest="windows", help="Number of windows")
     parser.add_argument('--species', required=True, type=str, dest="species", help="The focal species")
+    parser.add_argument('--threshold', required=False, default=0.0, type=float, dest="threshold",
+                        help="The threshold for the probability")
     main(parser.parse_args())

### 2022-07-11 manuscript/main.tex
Round of corrections

@@
 \DeclareMathOperator{\E}{\mathbb{E}}
-\DeclareMathOperator{\Var}{\mathrm{Var}}
-\newcommand{\der}{\mathrm{d}}
-\newcommand{\e}{\mathrm{e}}
+\DeclareMathOperator{\Var}{\textrm{Var}}
+\newcommand{\der}{\textrm{d}}
+\newcommand{\e}{\textrm{e}}
 \newcommand{\avg}[1]{\left< #1 \right>} % for average
-\newcommand{\Ne}{N_{\mathrm{e}}}
+\newcommand{\Ne}{N_{\textrm{e}}}
 \newcommand{\proba}{\mathbb{P}}
-\newcommand{\pfix}{\proba_{\mathrm{fix}}}
+\newcommand{\pfix}{\proba_{\textrm{fix}}}
 \newcommand{\dn}{d_N}
@@
 
-    We usually say that a mutation is undergoing positive selection when it brings a fitness advantage to its bearer, and thus facilitate its own transmission to the next generation.
+    We usually say that a mutation is undergoing positive selection when it brings a fitness advantage to its bearer, and thus facilitates its own transmission to the next generation.
     However, the causes of this advantage can be diverse.
@@
     The first scenario concerns environmental change.
-    The bearer of the mutation that is advantageous in a new environment will be better adapted, and its chances of survival and reproduction will be higher.
+    The bearer of the mutation that is advantageous in a new environment will be better adapted, and its chances of survival and reproduction will be higher (fig.~\ref{fig:fitness-landscape}A).
     This process is typically referred to as adaptive evolution.
-    The second scenario involves a mutation restoring the ancestral allele which corresponded to an optimal state of the individual in a constant environment, but has been lost due to the fixation of a deleterious mutation by drift.
+    The second scenario involves a mutation restoring the ancestral allele which corresponded to an optimal state of the individual in a constant environment, but has been lost due to the fixation of a deleterious mutation by drift (fig.~\ref{fig:fitness-landscape}B).
     In this manuscript, this process will be referred to as maintenance positive selection.
     Regarding the difference between these two scenarios at the population scale, while in the case of environmental change, the population as a whole is climbing the fitness landscape along an adaptive walk\cite{tenaillon_utility_2014}, in the case of maintenance positive selection, the population as a whole is thus merely staying in the same position in the fitness landscape at the mutation-selection equilibrium, and positive selection compensates for deleterious mutations that reach fixation due to drift\cite{sella_application_2005, mustonen_fitness_2009}.
-    These two different kinds of selection result in a positive transmission bias of the advantageous allele, but their consequences are conceptually different.
-    While adaptive evolution promotes phenotype diversification, maintenance positive selection promotes phenotype stability and preserves well established biological systems (fig.~\ref{fig:fitness-landscape}).
-    It is thus of importance to be able to distinguish those two kinds of positive selection in order to understand the diversification of species.
+    These two different kinds of selection result in a positive transmission bias of the advantageous allele, but their consequences at a macro-evolutionary scale are fundamentally different.
+    While adaptive evolution promotes phenotype diversification (fig.~\ref{fig:fitness-landscape}C), maintenance positive selection promotes phenotype stability and preserves well established biological systems (fig.~\ref{fig:fitness-landscape}D).
+    It is thus of importance to be able to distinguish those two kinds of positive selection in order to understand how selection impacts the diversification of species.
 
@@
     A way to thus measure maintenance positive selection is to compute selection coefficients assuming a constant and stable fitness landscape estimated from the alignment of protein-coding genes.
-    For each site of the protein alignment, amino-acid frequencies in the alignment is a proxy for its fitness, since for example a deleterious amino acid will be absent in the alignment.
+    For each site of the protein alignment, amino-acid frequency is a proxy for its fitness, since for example a deleterious amino acid will be more likely to be absent in the alignment.
     One of the most used methods to make these predictions is SIFT (Sort Intolerant From Tolerant), which reliably detects deleterious mutations in many taxa\cite{ng_sift_2003, vaser_sift_2016}.
@@
     First, this method uses amino-acid frequency as a proxy for amino-acid fitness, even if we know that a lot of mechanisms can influence amino-acid frequency other than fitness (phylogeny, mutation biases, GC-biased gene conversion, mutational paths).
-    Second, each mutation is attributed a score to describe if it should be under purifying selection on one hand or be neutral or advantageous, on the other hand.
-    However, this score makes little sense as an actual measure of fitness, and is not interpretable in terms of population genetics.
-    At a finer scale, modelling at the codon level can disentangle processes of mutation at the DNA level and selection at the amino-acid level.
-    For example, the so-called mutation-selection codon models are rooted within a population genetics formalism\cite{halpern_evolutionary_1998, mccandlish_modeling_2014}.
-    Such models provide a nearly-neutral framework of evolution by estimating the fitness landscape over amino-acid sequences for each site of the sequence while taking into account non-adaptive processes impacting codon frequency\cite{halpern_evolutionary_1998, rodrigue_mechanistic_2010, tamuri_estimating_2012}.
+    Second, SIFT scores makes little sense as an actual measure of fitness, and is not interpretable in terms of population genetics.
+    Contrarily, so-called mutation-selection codon models are rooted within a population genetics formalism\cite{halpern_evolutionary_1998, mccandlish_modeling_2014}.
+    These phylogenetic codon models can disentangle processes of mutation at the DNA level and selection at the amino-acid level.
+    Such codon models provide a nearly-neutral framework of evolution by estimating the fitness landscape over amino-acid sequences for each site of the sequence (fig~\ref{fig:method}A) while taking into account non-adaptive processes impacting codon frequency\cite{halpern_evolutionary_1998, rodrigue_mechanistic_2010, tamuri_estimating_2012}.
     Only nearly-neutral mutations between high fitness amino acids will tend to be permitted by the model, allowing for the explicit calculation of the scaled selection coefficient of non-synonymous mutations between codons.
@@
     \begin{figure*}[!ht]
-        \
         \centering
@@
     To answer these questions, we have estimated a fitness landscape for long-term evolution using available multiple sequence alignments between mammalian species\cite{ranwez_orthomam_2007, howe_ensembl_2021}.
-    We then developed and leveraged a pipeline integrating divergence and polymorphism data across the entire exome for 28 populations across 6 genera, namely \textit{Equus},  \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus} and \textit{Homo} (fig.~\ref{fig:method}).
+    We then developed and leveraged a pipeline integrating divergence and polymorphism data across the entire exome for 28 populations across 6 genera, namely \textit{Equus},  \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus} and \textit{Homo} (fig.~\ref{fig:method}A\&B).
 
@@
 
-    For each non-synonymous SNP observed at the population level, we predicted its scaled selection coefficient ($\Sphy$) from amino-acid fitnesses estimated at the mammalian scale (fig.~\ref{fig:homo-afr-results}A).
+    For each non-synonymous SNP observed at the population level, we predicted its scaled selection coefficient ($\Sphy$) from amino-acid fitnesses estimated at the mammalian scale (fig.~\ref{fig:method}B).
     Then we ask whether the variants that are supposedly advantageous are showing signatures of short term positive selection.
@@
     At the population level (e.g.
-in humans of Asian descent in fig.~\ref{fig:homo-afr-results}), we divided all observed SNPs in 5 classes of predicted selection coefficient: severely deleterious with $\divStrongDel$, deleterious with $\divDel$, weakly deleterious with $\divWeakDel$, weakly advantageous with $\divWeakAdv$ and advantageous with $\divAdv$.
-    In each of theses classes, SNPs are then grouped by the number of derived alleles in the population (fig.~\ref{fig:homo-afr-results}B), generating a so called site-frequency spectrum (SFS).
-    Compared to synonymous mutations which are supposedly neutral (black line in fig.~\ref{fig:homo-afr-results}B), mutations predicted to be deleterious (blue and green lines in fig.~\ref{fig:homo-afr-results}B) are underrepresented at high frequencies in the population, a signature of ongoing purifying selection.
-    Remarkably, SNPs predicted to be advantageous (red line in fig.~\ref{fig:homo-afr-results}B) are overrepresented at higher frequencies in the population, meaning they are more likely to reach fixation as a consequence of ongoing positive selection.
+in humans of Asian descent in fig.~\ref{fig:homo-afr-results}), we divided all observed SNPs in 5 classes of predicted selection coefficient: severely deleterious with $\divStrongDel$, deleterious with $\divDel$, weakly deleterious with $\divWeakDel$, weakly advantageous with $\divWeakAdv$ and advantageous with $\divAdv$ (fig.~\ref{fig:homo-afr-results}B).
+    In each of theses classes, SNPs are then grouped by the number of derived alleles in the population (fig.~\ref{fig:homo-afr-results}C), generating a so called site-frequency spectrum (SFS).
+    Compared to synonymous mutations which are supposedly neutral (black line in fig.~\ref{fig:homo-afr-results}C), mutations predicted to be deleterious (blue and green lines in fig.~\ref{fig:homo-afr-results}C) are underrepresented at high frequencies in the population, a signature of ongoing purifying selection.
     However, these observations remain qualitative.
@@
     This model uses the count of derived alleles for each frequency class of the SFS to infer the distribution of fitness effects (DFE) of the region under study.
-    The model uses both the mutational expectation for each category (fig.~\ref{fig:homo-afr-results}C) (see Material and Methods), and the counts of synonymous derived allele as a neutral model, which allow to control for demographic effects, and polarization errors when inferring the ancestral state.
+    The model uses both the number of sites ($L$) for each category (fig.~\ref{fig:homo-afr-results}A, see Material and Methods), and the counts of synonymous derived allele as a neutral model, which allow to control for demographic effects, and polarization errors when inferring the ancestral state.
     These population-based models cannot give a specific estimate of the selection coefficient at the population-genetic scale ($\Spop$) for each SNP, but by gathering information across many SNPs, these models can estimate the proportion of advantageous mutations ($\PpolyAdv$), of nearly-neutral mutations ($\PpolyNeutral$) and of deleterious mutations ($\PpolyDel$) (fig.~\ref{fig:homo-afr-results}D).
     We found that SNPs predicted to be deleterious given their selection coefficient $\Sphy$ across mammals are effectively purged at the population-genetic scale, demonstrating that purifying selection is largely predictable and amino acids with low fitness across mammals are effectively purged away in each population.
-    Notably, SNPs predicted to be advantageous given their selection coefficient $\Sphy$ are indeed under positive selection at the population-genetic scale, confirming that there is a local ongoing selection toward amino acids that are restoring the optimally functioning protein.
+    Notably, SNPs predicted to be advantageous given their selection coefficient $\Sphy$ are indeed under positive selection at the population-genetic scale, confirming that there is a local ongoing selection towards amino acids that are restoring the optimally functioning protein.
     In between these two extremes, mutations predicted to be weakly selected (cyan and orange in fig.~\ref{fig:homo-afr-results}) are effectively composed of neutral, positively and negatively selected mutations.
@@
     Since $\Ne$ is not directly measurable, a reasonable proxy usually used is the synonymous diversity (see material and methods).
-    We thus ordered populations by their levels of synonymous diversity (fig.~\ref{fig:diversity}A) and confirmed that higher synonymous diversity is usually accompanied by a smaller proportion of neutral mutations.
-    This result suggests that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) are more likely to discriminate whether mutations are advantageous or deleterious.
+    We thus ordered populations by their levels of synonymous diversity (fig.~\ref{fig:diversity}A) and confirmed that higher synonymous diversity is typically accompanied by a smaller proportion of neutral mutations.
+    This result suggests that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) are more likely to discriminate whether mutations are advantageous or deleterious (fig~S1-S5).
     Alternatively stated, mutations in populations with low diversity (e.g.~\textit{Homo}) are effectively nearly-neutral and behave as would a neutral mutation.
+    %, especially for mutations already predicted to be nearly-neutral at the phylogenetic scale (fig~S8-S9).
     This result is qualitatively in accordance with the nearly-neutral theory of evolution which argues that mutations are less efficiently selected for in small populations.
-
-    We then tried to estimate the proportion of restoring mutations among advantageous ones.
-    Since adaptation does not fit the fitness predictions, the proportion of adaptive mutation is expected to be the same among SNPs which are predicted to be advantageous, and among SNPs which are predicted to be deleterious.
-    Thus the proportion of advantageous mutations among SNPs which are predicted to be deleterious directly correspond to the proportion of all mutations which are adaptive.
-    So if we divide the proportion of mutations which are predicted to be advantageous among supposedly deleterious SNPs by the proportion of mutations which are predicted to be advantageous among all SNPs.
-    We directly get the proportion of mutations which are adaptive among advantageous ones. It results that 60 to 80\% of advantageous mutations are adaptive.
 
@@
     %This also means that the ratio $\dnds$ usually used to detect adaptation while relying on substitutions between close species\cite{mcdonald_adaptative_1991, galtier_adaptive_2016} or at the phylogenetic scale\cite{goldman_codonbased_1994, yang_codonsubstitution_2002} is overestimated.
-    These observed substitutions are likely to have been positive selected because they restored a more optimal state, not because they are driving innovations to a new environment or a function.
+    These observed substitutions are likely to have been positive selected because they restored a more optimal state, not because they are driving innovations to a new environment or a new function.
+
+    \subsection*{A large proportion of advantageous mutations are non-adaptive}
+
+    We then tried to estimate the proportion of restoring mutations among advantageous ones.
+    Since adaptation does not fit the fitness predictions, the proportion of adaptive mutation is expected to be the same among SNPs which are predicted to be advantageous, and among SNPs which are predicted to be deleterious.
+    Thus the proportion of advantageous mutations among SNPs which are predicted to be deleterious directly correspond to the proportion of all mutations which are adaptive.
+    So if we divide the proportion of mutations which are predicted to be advantageous among supposedly deleterious SNPs by the proportion of mutations which are predicted to be advantageous among all SNPs, we directly get the proportion of mutations which are adaptive among advantageous ones.
+    It results that 20 to 40\% of advantageous mutations are due to maintenance positive selection (fig~\ref{fig:diversity}B \& table S2).
+
+    In a similar way, we can consider that the total $\dnds$ encompasses the rate of evolution of deleterious, restoring and adaptive substitutions.
+    Then, the $\dnds$ computed exclusively on non-synonymous sites with a $\Sphy < 0$ only represent the rate of evolution of solely deleterious and adaptive substitutions, discarding the restoring substitutions by construction.
+    Thus, if we divide the $\dnds$ estimated on all substitutions, by the one estimated only on substitutions predicted to be deleterious, we directly get the proportion of the rate of evolution which is due to maintenance positive selection.
+    This way, we estimated that between 20 and 25\% of the evolutionary rate is due to maintenance positive selection (fig~\ref{fig:diversity}C \& table S2).
+
+    Interestingly, the proportion of restoring mutations among advantageous ones and the proportion of the rate of evolution explained by maintenance positive selection do not show a clear relationship with the synonymous diversity (a proxy for the effective population size) (fig.~\ref{fig:diversity}B and C).
+    Indeed, the relationship between $\Ne$ and the proportion of restoring mutations is not trivial and should highly depend on time scales.
+    A population which experienced a high long term $\Ne$ in the past is supposed to be closer to the optimal state (under a stable fitness landscape), and should not leave much space for restoring mutations.
+    On the other hand a high short term $\Ne$ will induce more extreme fitness effects and a larger proportion of otherwise effectively neutral restoring mutations will be positively selected, thus increasing the proportion of restoring mutations.
+    Overall, the proportion of restoring mutations is expected to be more dependent on effective population size contraction or expansion rather than on the short term effective population size captured by the synonymous diversity.
+
     %Altogether, we estimated that between 18 and 39\% of $\dnds$ is over-estimated (table S1), corresponding to maintenance positive selection.
-    In a nearly neutral framework, genomes could be viewed as the arena of a tug-of-war between a large volume of deleterious mutations that eventually reach fixation due to drift, and scarce advantageous mutations that are restoring a more optimal ancestral state.
+    %In a nearly neutral framework, genomes could be viewed as the arena of a tug-of-war between a large volume of deleterious mutations that eventually reach fixation due to drift, and scarce advantageous mutations that are restoring a more optimal ancestral state.
     % However, and surprisingly, a decrease in the proportion of neutral mutation did not translate into a mechanical increase in the proportion of advantageous mutations.
@@
         \caption{
-            Panel A: Histogram of predicted selection coefficients ($\Sphy$) for all possible mutations away from the ancestral human genome, weighted by the mutation rate.
+            Panel A: Histogram of predicted selection coefficients ($\Sphy$) for all possible mutations away from the ancestral human genome, giving the number of sites ($L$, in y-axis) across the genome with a given $\Sphy$.
             Mutations are divided into 5 classes: severely deleterious (blue), deleterious (green), weakly deleterious (light green), weakly advantageous (yellow) and advantageous (red).
@@
             Panel B.
-$R(p_+)=\dfrac{p_+ - p_+[\Sphy < 0]}{p_+}$ is the fraction of the probability for a new mutation to be advantageous ($p_+=\PpolyAdv$) that is over-estimated, $p_+$ is compared to its estimation when we had removed all the restoring mutations $p_+[\Sphy < 0]$.
+$R(p_+)=\dfrac{p_+ - p_+(\Sphy < 0)}{p_+}$ is the fraction of non-adaptive advantageous mutations, $p_+$ is compared to its estimation when we had removed all the restoring mutations $p_+(\Sphy < 0)$.
             $R(p_+)$ (y-axis) is shown as a function of the synonymous diversity (Watterson $\theta_w$ in x-axis).
             Panel C.
-$R(\dnds)=\dfrac{\dnds - \dnds[\Sphy < 0]}{\dnds}$ is the fraction of the divergence ($\dnds$) that is over-estimated, where $\dnds$ is compared to the estimated divergence when we removed the restoring substitutions $\dnds[\Sphy < 0]$.
-            $R(\dnds)$ (y-axis) is shown as a function of the synonymous diversity (Watterson $\theta_w$ in x-axis).
+$R(\dnds)=\dfrac{\dnds - \dn(\Sphy < 0) / \ds}{\dnds}$ is the fraction of divergence ($\dnds$) that is due to maintenance positive selection, where $\dnds$ is compared to the estimated divergence when we removed the restoring substitutions $\dn(\Sphy < 0)/\ds$.
+            $R(\dn)$ (y-axis) is shown as a function of the synonymous diversity (Watterson $\theta_w$ in x-axis).
         }
@@
     \end{figure*}
-
-    Biologically, another repairing mechanism is compensatory mutations, which are repairing damage caused by deleterious mutations at another site in the genome and generating a widespread signal of non-adaptive positive selection\cite{hartl_compensatory_1996, pollock_strong_2014, starr_epistasis_2016}.
-    In our study we focused on mutations restoring the more optimal ancestral state at a given site, not accounting for compensatory mutations since we assumed a model of fitness landscape without epistasis, providing a reasonable estimate of average fitness profiles\cite{youssef_consequences_2020}.
-    But most importantly, we argue that our estimation of the amount of maintenance positive selection is an underestimation, and that accounting for compensatory mutations by means of epistasis would mechanically increase that amount.
-    Indeed, a fluctuating fitness landscape due to an external forces (e.i.
-changes in environment) results in an acceleration of the rate of evolution\cite{ rodrigue_detecting_2017, rodrigue_bayesian_2021} which generates epistatic mutations that are immediately beneficial\cite{gong_epistatically_2014}.
-    On the contrary, pervasive epistasis generates the opposite, an entrenchment\cite{goldstein_evolutionary_2004, goldstein_nonadaptive_2015} resulting in a slowing down of the rate evolution\cite{rodrigue_detecting_2017, patel_epistasis_2022} or a standstill\cite{youssef_evolution_2022}.
-    In other words, under pervasive epistasis, finding empirical evidence for restoring mutations is harder since restoring mutations becomes less and less likely to occur over time\cite{goldstein_nonadaptive_2015, goldstein_sequence_2017, park_epistatic_2022}.
-    Our study thus shows that restoring mutations should instead not be overlooked, and we argue that both restoring and compensatory mutations play an important role to avoid our genome to collapse under a mutation load.
 
@@
     In practice, SIFT scores are more coarse grained, with for example a bulk of mutations with a score of 1.0 (the highest), and does not provide a boundary between advantageous and deleterious mutations, nor are they based on a population-genetics formalism.
+
+    Biologically, another mechanism which generate maintenance positive selection is compensatory mutations, which are repairing damage caused by deleterious mutations at another site in the genome and generating a widespread signal of non-adaptive positive selection\cite{hartl_compensatory_1996, pollock_strong_2014, starr_epistasis_2016}.
+    In our study we focused on mutations restoring the more optimal ancestral state at a given site, not accounting for compensatory mutations since we assumed a model of fitness landscape without epistasis, providing a reasonable estimate of average fitness profiles\cite{youssef_consequences_2020}.
+    But most importantly, we argue that our estimation of the amount of maintenance positive selection is an underestimation, and that accounting for compensatory mutations by means of epistasis would mechanically increase that amount.
+    Indeed, a fluctuating fitness landscape due to an external forces (e.i.
+changes in environment) results in an acceleration of the rate of evolution\cite{ rodrigue_detecting_2017, rodrigue_bayesian_2021} which generates epistatic mutations that are immediately beneficial\cite{gong_epistatically_2014}.
+    On the contrary, pervasive epistasis generates the opposite, an entrenchment\cite{goldstein_evolutionary_2004, goldstein_nonadaptive_2015} resulting in a slowing down of the rate evolution\cite{rodrigue_detecting_2017, patel_epistasis_2022} or a standstill\cite{youssef_evolution_2022}.
+    In other words, under pervasive epistasis, finding empirical evidence for restoring mutations is harder since restoring mutations become less and less likely to occur over time\cite{goldstein_nonadaptive_2015, goldstein_sequence_2017, park_epistatic_2022}.
+    Our study thus shows that restoring mutations should not be overlooked, and we argue that both restoring and compensatory mutations play an important role in preventing our genome from collapsing under a mutation load.
 
@@
 
-    In population genetics, models also have shortcomings, such that there is no consensus on the expected shape of the DFE\cite{welch_divergence_2008, bataillon_effects_2014}, but it has indeed been found to be reliably constant between species\cite{castellano_comparison_2019}.
+    At the population-genetic level, our study relied on models with some shortcomings, such that there is no consensus on the expected shape of the DFE\cite{welch_divergence_2008, bataillon_effects_2014}, although it has been found to be reliably constant between species\cite{castellano_comparison_2019}.
     The model we used allows the inference of a full DFE, modelling the negative part of the DFE as a gamma distribution, and the positive part as an exponential distribution.
@@
     As a result, while the proportions of negative/weak/positive mutations stays reliable, the mean values for selection coefficients ($\Spop$) estimated by polyDFE become biologically absurd ($\Spop \ll -10^3$).
-    Such effect is not found for neutral SNPs and a method to accurately estimate the mean value of selection coefficients from SFS without assuming any shape for the DFE remains yet to be available.
+    Such effect is not found for neutral SNPs and a method to accurately estimate the mean value of selection coefficients from SFS without assuming any shape for the DFE remains yet to be developed.
     Aside from methodological limitations, the mammalian case study might also not be representative of other clades.
-    Indeed, our dataset is quite convenient because mammals have relatively small population sizes, which allow large amount of deleterious mutations to be fixed, and thus, there are a lot of opportunities for maintenance positive selection to arise.
+    Indeed, mammals have relatively small long term population sizes, which allow large amounts of deleterious mutations to be fixed, and thus, there are a lot of opportunities for maintenance positive selection to arise.
     It would thus be of great interest to reproduce our experiment with other clades, such as \textit{Drosophila} or birds which tend to have higher effective population size.
@@
     We argue that mutation-selection models are thus a mandatory tool in evolutionary biology to detect and quantify adaptation since they genuinely take into account the tug-of-war between scarce advantageous mutations likely to reach fixation and a bulk of deleterious mutations eventually reaching fixation due to their sheer mass.
-    Indeed, these models can be used as a null model to predict the overall rate of evolution of proteins\cite{spielman_relationship_2015, dosreis_how_2015}.
-    A departure from this model indicates that proteins are evolving under a changing fitness landscape\cite{rodrigue_detecting_2017, tamuri_mutationselection_2021} and is a signal of adaptive evolution\cite{rodrigue_bayesian_2021}.
+    Indeed, these models can be used as a null model to predict the expected rate of evolution of proteins\cite{spielman_relationship_2015, dosreis_how_2015} under a stable fitness landscape.
+    A departure from this model indicates that proteins are evolving under a changing fitness landscape\cite{rodrigue_detecting_2017, tamuri_mutationselection_2021} and is a signal of pervasive adaptive evolution\cite{rodrigue_bayesian_2021} or of pervasive epistasis\cite{rodrigue_detecting_2017}.
 
@@
     \label{sec:acknowledgment}
-    We gratefully also acknowledge the help of Diego A. Hartasánchez Frenk for his advice and review concerning this manuscript.
+    We gratefully acknowledge the help of Diego A. Hartasánchez Frenk for his advice and review concerning this manuscript.
     This work was performed using the computing facilities of the CC LBBE/PRABI\@.
@@
             q_{a \mapsto b}^{(i)} & = \mu_{a \mapsto b} \text{ if codons $a$ and $b$ are synonymous,} \\
-            q_{a \mapsto b}^{(i)} & = \mu_{a \mapsto b}  \mu_{a \mapsto b} \dfrac{F_b^{(i)} - F_a^{(i)}}{1 - \e^{F_a^{(i)} - F_b^{(i)}}} \text{ if codons $a$ and $b$ are non-synonymous}.
+            q_{a \mapsto b}^{(i)} & = \mu_{a \mapsto b} \dfrac{F_b^{(i)} - F_a^{(i)}}{1 - \e^{F_a^{(i)} - F_b^{(i)}}} \text{ if codons $a$ and $b$ are non-synonymous}.
         \end{dcases}
@@
     and $\Spop_b$ as:
-    \begin{equation*}
+    \begin{equation}
         \phi \left( \Spop; \Spop_d , b, p_b, \Spop_b \right) =
@@
         \end{dcases}
-    \end{equation*}
+    \end{equation}
     where $\Spop_d \leq -1 $ is the estimated mean of the DFE for $\Spop \leq 0$,
@@
     Once the DFE is fitted to the data, the proportion of advantageous ($\PpolyAdv$), nearly-neutral ($\PpolyNeutral$) and deleterious mutations ($\PpolyDel$) are given as:
-    \begin{align*}
-        \PpolyAdv &= p_b \int_{1}^{+\infty} f_{e}(\Spop; \Spop_b) \der \Spop  \\
-        \PpolyNeutral &= p_b \int_{0}^{1} f_{e}(\Spop; \Spop_b) \der \Spop + \left( 1 - p_b \right) \int_{0}^{1} f_{\Gamma}(\Spop; -\Spop_d, b) \der \Spop \\
-        \PpolyDel &= \left( 1 - p_b \right) \int_{1}^{+\infty} f_{\Gamma}(\Spop; -\Spop_d, b) \der \Spop
-    \end{align*}
+    \begin{align}
+        p_+ = \PpolyAdv &= p_b \int_{1}^{+\infty} f_{e}(\Spop; \Spop_b) \der \Spop,  \\
+        \PpolyNeutral &= p_b \int_{0}^{1} f_{e}(\Spop; \Spop_b) \der \Spop + \left( 1 - p_b \right) \int_{0}^{1} f_{\Gamma}(\Spop; -\Spop_d, b) \der \Spop, \\
+        \PpolyDel &= \left( 1 - p_b \right) \int_{1}^{+\infty} f_{\Gamma}(\Spop; -\Spop_d, b) \der \Spop.
+    \end{align}
 
@@
     First, for each gene, the reference DNA sequence is adjusted with ancestral and fixed polymorphism for each population.
-    Second, from this reconstructed sequence, all possible mutations are computed, weighted by the mutation rate between nucleotide estimated at the phylogenetic scale $\UniDimArray{\mu}$.
-    Third, the total mutation rate for synonymous mutations, called $\mu_{\mathrm{syn}}$, is the sum across the genome.
-    Similarly, the total mutation rate for each class of selection, called  $\mu_{\Sphyclass}$, is the sum across all non-synonymous mutations if their selection coefficient at the phylogenetic scale ($\Sphy$) is in the class $\Sphyclass$, where $\Sphyclass \in \{\divStrongDel, \divDel, \divWeakDel, \divWeakAdv, \divAdv \}$.
-    Fourth, the number of sites ($L$) for each class of selection coefficient ($\Sphyclass$) is then computed as the total number of sites across the genome ($L_{tot}$) weighted by the ratio of the aggregated mutations rates falling in the class ($\mu_{\Sphyclass}$) over the total mutation rate for all possible mutations:
-    \begin{align*}
-        L_{\mathrm{non-syn}} | \Sphyclass &= L_{tot} \frac{\mu_{\Sphyclass}}{\mu_{tot}},
-        L_{\mathrm{syn}} &= L_{tot} \frac{\mu_{\mathrm{syn}}}{\mu_{tot}},
-    \end{align*}
+    Second, from this reconstructed sequence, all possible mutations are computed, weighted by the mutation rate between nucleotide ($\mu$) estimated at the phylogenetic scale.
+    Third, the total mutation rate for synonymous mutations, called $\mu_{\textrm{syn}}$, is the sum across the genome.
+    Similarly, the total mutation rate for each class of selection, called  $\mu\left( \Sphyclass \right)$, is the sum across all non-synonymous mutations if their selection coefficient at the phylogenetic scale ($\Sphy$) is in the class $\Sphyclass$ (e.g.
+$\Sphyclass = \divAdv$).
+    Fourth, the number of sites ($L$) for each class of selection coefficient ($\Sphyclass$) is then computed as the total number of sites across the genome ($L_{tot}$) weighted by the ratio of the aggregated mutations rates falling in the class ($\mu\left( \Sphyclass \right)$) over the total mutation rate for all possible mutations:
+    \begin{align}
+        L_{\textrm{non-syn}} \left( \Sphyclass \right) &= L_{tot} \frac{\mu\left( \Sphyclass \right)}{\mu_{tot}}, \\
+        L_{\textrm{syn}} &= L_{tot} \frac{\mu_{\textrm{syn}}}{\mu_{tot}}.
+    \end{align}
     From the SFS and the number of sites $L$ for the both synonymous and for the class of non-synonymous, polyDFE estimates parameters of the DFE $\phi \left( \Spop; \Spop_d , b, p_b, \Spop_b \right)$ using maximum likelihood.
+
+    The fraction of non-adaptive advantageous mutations $R(p_+)$ is computed the fraction of advantageous mutations ($p_+$) that is due to maintenance positive selection, where $p_+$ is compared to the estimated divergence when we removed the restoring substitutions $p_+(\Sphy < 0)$.
+    \begin{equation}
+        R(p_+)=\dfrac{p_+ - p_+(\Sphy < 0)}{p_+}
+    \end{equation}
 
@@
     Finally, the rate of non-synonymous over synonymous substitution for a given class of selection coefficient ($\Sphyclass$) is computed as:
-    \begin{equation*}
-        \dnds | \Sphyclass = \frac{\sfrac{D_{\mathrm{non-syn} | \Sphyclass}}{L_{\mathrm{non-syn}} | \Sphyclass}}{\sfrac{D_{\mathrm{syn}}}{L_{\mathrm{syn}}}},
-    \end{equation*}
-    where $D_{\mathrm{non-syn}} | \Sphyclass $ is the number of non-synonymous substitutions in the class $\Sphyclass$, $D_{\mathrm{syn}}$ is the number of synonymous substitutions across the genome, while $L_{\mathrm{non-syn}} | \Sphyclass$ and $L_{\mathrm{syn}}$ are the number of non-synonymous and synonymous sites as defined in the previous section.
+    \begin{align}
+        \dn \left( \Sphyclass \right) &= \dfrac{D_{\textrm{non-syn}}\left( \Sphyclass \right)}{L_{\textrm{non-syn}} \left( \Sphyclass \right)}, \\
+        \ds &= \dfrac{D_{\textrm{syn}}}{L_{\textrm{syn}}},
+    \end{align}
+    where $D_{\textrm{non-syn}} \left( \Sphyclass \right) $ is the number of non-synonymous substitutions in the class $\Sphyclass$, $D_{\textrm{syn}}$ is the number of synonymous substitutions across the genome, while $L_{\textrm{non-syn}} \left( \Sphyclass \right)$ and $L_{\textrm{syn}}$ are the number of non-synonymous and synonymous sites as defined in the previous section.
+    Of note, the quantities $R(\dn)$ and $R(\dnds)$ are equivalent due to simplification of the factor $\ds$:
+    \begin{align}
+        R(\dnds) &= \dfrac{\dnds - \dn(\Sphy < 0) / \ds}{\dnds} = \dfrac{\dn - \dn(\Sphy < 0)}{\dn} = R(\dn) \\
+        &= 1 - \dfrac{ L_{\textrm{non-syn}} \cdot D_{\textrm{non-syn}}\left( \Sphyclass \right) }{ D_{\textrm{non-syn}} \cdot L_{\textrm{non-syn}} \left( \Sphyclass \right)}
+    \end{align}
 

### 2022-07-11 manuscript/supp-mat.tex
Round of corrections

@@
 \documentclass{article}
-
+\usepackage{caption}
 \usepackage{xcolor, colortbl}
@@
     \begin{center}
+        \captionof{table}{}
         \scriptsize
-        \begin{longtable}{|l|l|r|r|r|r|r|r|}
+        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
             \toprule
-            Population           & Species             & Tajima $\theta$ & $\mathbb{P} [ \Spop > 1 ]$ & $\mathbb{P}_{mut}[\Sphy > 1]$ & $\mathbb{P} [ \Spop > 1  | \Sphy > 1]$ & $\mathbb{P}_{div}[\Sphy > 1]$ & $\dnds[\Sphy > 1]$ \\
+            Population           & Species             & Tajima $\theta$ & $\mathbb{P} [ \Spop > 1 ]$ & $\mathbb{P}_{mut}[\Sphy > 1]$ & $\mathbb{P} [ \Spop > 1  | \Sphy > 1]$ & $\mathbb{P}_{div}[\Sphy > 1]$ & $\dn(\Sphy > 1) / \ds$ \\
             \midrule
@@
             South Asian          & Homo sapiens        & $ 0.002$        & $ 0.036$                   & $ 0.015$                      & $ 0.532$                             & $ 0.104$                      & $ 1.473$           \\
-        \end{longtable}
+        \end{longtable*}
     \end{center}
@@
         \item $\mathbb{P}_{div}[\Sphy > 1]$ is the proportion of substitutions in the terminal branch observed with a selection coefficient at the phylogenetic scale larger than 1 ($\Sphy > 1$).
-        \item $\dnds[\Sphy > 1]$ is the ratio of non-synonymous over synonymous divergence (also called $\dnds$) estimated for the non-synonymous substitutions in the terminal branch with a selection coefficient larger than 1 ($\Sphy > 1$).
+        \item $\dn(\Sphy > 1) / \ds$ is the ratio of non-synonymous over synonymous divergence (also called $\dnds$) estimated for the non-synonymous substitutions in the terminal branch with a selection coefficient larger than 1 ($\Sphy > 1$).
     \end{itemize}
 
+    \newpage
     \begin{center}
+        \captionof{table}{}
         \scriptsize
-        \begin{longtable}{|l|l|r|r|r|r|r|r|r|r|}
+        \begin{longtable*}{|l|l|r|r|r|r|r|r|r|r|}
             \toprule
-            Population           & Species             & Tajima $\theta_{\pi}$ & $\mathbb{P}_{div}[\Sphy > 0]$ & $\dnds $ & $\dnds  | S<0$ & R($\dnds $) & $p_+ $ & $p_+  | S<0$ & R($p_+ $) \\
+            Population           & Species             & Tajima $\theta_{\pi}$ & $\mathbb{P}_{div}[\Sphy > 0]$ & $\dnds $ & $\dn(\Sphy < 0) / \ds$ & R($\dnds $) & $p_+ $ & $p_+(\Sphy < 0)$ & R($p_+ $) \\
             \midrule
@@
             South Asian          & Homo sapiens        & $ 0.002$              & $ 0.244$                      & $ 0.195$ & $ 0.156$     & $  20.3$      & $ 0.035$ & $ 0.024$ & $  31.7$ \\
-        \end{longtable}
-
+        \end{longtable*}
     \end{center}
@@
         \item $\dnds$ is the ratio of non-synonymous over synonymous divergence estimated for all the non-synonymous substitutions in the terminal branch.
-        \item $\dnds[\Sphy < 0]$ is the ratio of non-synonymous over synonymous divergence estimated for the non-synonymous substitutions in the terminal branch with a selection coefficient lower than 0 ($\Sphy < 0$).
+        \item $\dn(\Sphy < 0) / \ds$ is the ratio of non-synonymous over synonymous divergence estimated for the non-synonymous substitutions in the terminal branch with a selection coefficient lower than 0 ($\Sphy < 0$).
         This is the estimated divergence when we removed the restoring substitutions.
-        \item $R(\dnds)=\dfrac{\dnds - \dnds[\Sphy < 0]}{\dnds}$ is the fraction of the divergence ($\dnds$) that is over-estimated, $\dnds$ is compared to the estimated divergence when we removed the restoring substitutions $\dnds[\Sphy < 0]$.
+        \item $R(\dnds)=\dfrac{\dnds - \dn(\Sphy < 0) / \ds}{\dnds}$ is the fraction of the divergence ($\dnds$) that is over-estimated, $\dnds$ is compared to the estimated divergence when we removed the restoring substitutions $\dn(\Sphy < 0) / \ds$.
         \item $p_+=\PpolyAdv$ is the probability for a new mutation to be advantageous, estimated (with polyDFE) using all available polymorphism.
-        \item $p_+[\Sphy < 0]$ is the probability for a new mutation to be advantageous, estimated (with polyDFE) using polymorphism with a selection coefficient lower than 0 ($\Sphy < 0$).
+        \item $p_+(\Sphy < 0)$ is the probability for a new mutation to be advantageous, estimated (with polyDFE) using polymorphism with a selection coefficient lower than 0 ($\Sphy < 0$).
         This is the estimated probability for a new mutation to be advantageous when we removed the restoring polymorphism from the dataset.
-        \item $R(p_+)=\dfrac{p_+ - p_+[\Sphy < 0]}{p_+}$ is the fraction of the probability for a new mutation to be advantageous ($p_+$) that is over-estimated, $p_+$ is compared to its estimation when we had removed all the restoring mutations $p_+[\Sphy < 0]$.
+        \item $R(p_+)=\dfrac{p_+ - p_+(\Sphy < 0)}{p_+}$ is the fraction of the probability for a new mutation to be advantageous ($p_+$) that is over-estimated, $p_+$ is compared to its estimation when we had removed all the restoring mutations $p_+(\Sphy < 0)$.
     \end{itemize}
 
+    \newpage
     \subsection{Correlation with diversity}
-
     \subsubsection{Proportion of nearly-neutral mutations ($\polyNeutral$)}\label{subsec:proportion-nearly-neutral-mutations}
-
+    \captionof{figure}{}
     \begin{minipage}{0.32\linewidth}
@@
     \end{minipage}
-
     \begin{itemize}
@@
     \subsubsection{Proportion of deleterious mutations ($\polyDel$)}\label{subsec:proportion-deleterious-mutations}
-
+    \captionof{figure}{}
     \begin{minipage}{0.32\linewidth}
@@
     \subsubsection{Proportion of advantageous mutations ($\polyAdv$)}\label{subsec:proportion-advantageous-mutations}
-
+    \captionof{figure}{}
     \begin{minipage}{0.32\linewidth}
@@
     \end{minipage}
-
     \begin{itemize}
-        \item $\ \proba [ \polyAdv  ]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) greater than 1, estimated for the whole genome.
-        \item $\ \proba [ \polyAdv | \divAdv] $ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) greater than 1, estimated of SNPs observed with a selection coefficient at the phylogenetic scale ($\Sphy$) greater than 1.
+        \item $\ p_+ = \proba [ \polyAdv  ]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) greater than 1, estimated for the whole genome.
+        \item $\ p_+( \divAdv) = \proba [ \polyAdv | \divAdv] $ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) greater than 1, estimated of SNPs observed with a selection coefficient at the phylogenetic scale ($\Sphy$) greater than 1.
     \end{itemize}
@@
     \subsection{Selection efficacy correlation with diversity}\label{subsec:selection-efficacy-correlation-with-diversity}
-
     The mean of the DFE $\SpopMean$ estimated by polyDFE is given by:
@@
     The relationship between $\SpopMean$ and $\SphyMean$ can be described by a second-order polynomial, and the slope of this polynomial at $\SphyMean=0$ gives the ratio $\SpopMean/\SphyMean$ for each population.
-
+    \captionof{figure}{}
     \begin{center}
@@
 
+    \newpage
     \section{SIFT scores}\label{sec:sift-scores}
@@
     \begin{center}
+        \captionof{table}{}
         \footnotesize
@@
             \toprule
-            Population           & Species             & Tajima $\theta_{\pi}$ & $p_+$    & $p_+ [ SIFT < 0.8]$ & R($p_+$) \\
+            Population           & Species             & Tajima $\theta_{\pi}$ & $p_+$    & $p_+ (\textrm{SIFT} < 0.8)$ & R($p_+$) \\
             \midrule
@@
         \item $p_+=\PpolyAdv$ is the probability for a new mutation to be advantageous, estimated (with polyDFE) using all available polymorphism.
-        \item $p_+ [ SIFT < 0.8]$ is the probability for a new mutation to be advantageous, estimated (with polyDFE) using polymorphism with a SIFT lower than 0.8 ($SIFT < 0.8$).
+        \item $p_+ (\textrm{SIFT} < 0.8)$ is the probability for a new mutation to be advantageous, estimated (with polyDFE) using polymorphism with a SIFT lower than 0.8 ($SIFT < 0.8$).
         This is the estimated probability for a new mutation to be advantageous when we removed the restoring polymorphism from the dataset.
-        \item $R(p_+)=\dfrac{p_+ - p_+ [ SIFT < 0.8]}{p_+}$ is the fraction of the probability for a new mutation to be advantageous ($p_+$) that is over-estimated, $p_+$ is compared to its estimation when we had removed all the restoring mutations $p_+ [ SIFT < 0.8]$.
+        \item $R(p_+)=\dfrac{p_+ - p_+ (\textrm{SIFT} < 0.8)}{p_+}$ is the fraction of the probability for a new mutation to be advantageous ($p_+$) that is over-estimated, $p_+$ is compared to its estimation when we had removed all the restoring mutations $p_+ (\textrm{SIFT} < 0.8)$.
     \end{itemize}
+    \newpage
     \input{include-SIFT-non-adaptive}

### 2022-07-12 manuscript/include-MutSel-non-adaptive.tex
Round of corrections
Refactored Supp. Mat. and included explanations

@@
-\subsection{All populations}
-\begin{center}
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.MutSel.all.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.MutSel.neg-strong.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.MutSel.neg.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.MutSel.neg-weak.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.MutSel.pos-weak.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.MutSel.pos.stacked.pdf}
-\end{center}
-
 \subsection{Bos taurus}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Bos_taurus.IRBT.MutSel.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Bos_taurus.UGBT.MutSel.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.AUCH.MutSel.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.FRCH.MutSel.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.IRCA.MutSel.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.IRCH.MutSel.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.ITCH.MutSel.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.MOCH.MutSel.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Barbados.MutSel.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Gambia.MutSel.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Kenya.MutSel.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Nevis.MutSel.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Saint_Kitts.MutSel.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.South_Africa.MutSel.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Zambia.MutSel.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Equus_caballus.up.MutSel.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.AFR.MutSel.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.AMR.MutSel.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.EAS.MutSel.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.EUR.MutSel.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.SAS.MutSel.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROA.MutSel.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROO.MutSel.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROV.MutSel.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.ISGC.MutSel.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}

### 2022-07-12 manuscript/include-SIFT-non-adaptive.tex
Round of corrections
Refactored Supp. Mat. and included explanations

@@
-\subsection{All populations}
-\begin{center}
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.SIFT.all.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.SIFT.neg-strong.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.SIFT.neg.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.SIFT.neg-weak.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.SIFT.pos-weak.stacked.pdf} \\
-    \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.SIFT.pos.stacked.pdf}
-\end{center}
-
 \subsection{Bos taurus}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Bos_taurus.IRBT.SIFT.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Bos_taurus.UGBT.SIFT.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.AUCH.SIFT.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.FRCH.SIFT.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.IRCA.SIFT.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.IRCH.SIFT.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.ITCH.SIFT.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.MOCH.SIFT.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Barbados.SIFT.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Central_African_Republic.SIFT.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Ethiopia.SIFT.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Gambia.SIFT.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Kenya.SIFT.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Nevis.SIFT.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Saint_Kitts.SIFT.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.South_Africa.SIFT.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Zambia.SIFT.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Equus_caballus.up.SIFT.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.AFR.SIFT.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.AMR.SIFT.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.EAS.SIFT.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.EUR.SIFT.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.SAS.SIFT.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROA.SIFT.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROO.SIFT.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROV.SIFT.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}{0.49\linewidth}
+\begin{minipage}{0.4\linewidth}
     \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.ISGC.SIFT.polyDFE_C.pdf}
+\end{minipage}
+\begin{minipage}{0.09\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat.top}
 \end{minipage}

### 2022-07-12 manuscript/main.tex
Refactored Supp. Mat. and included explanations

@@
     This result suggests that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) are more likely to discriminate whether mutations are advantageous or deleterious (fig~S1-S5).
-    Alternatively stated, mutations in populations with low diversity (e.g.~\textit{Homo}) are effectively nearly-neutral and behave as would a neutral mutation.
-    %, especially for mutations already predicted to be nearly-neutral at the phylogenetic scale (fig~S8-S9).
+    Alternatively stated, mutations in populations with low diversity (e.g.~\textit{Homo}) are effectively nearly-neutral and behave as would a neutral mutation, especially for mutations already predicted to be nearly-neutral at the phylogenetic scale (fig~S8-S9).
     This result is qualitatively in accordance with the nearly-neutral theory of evolution which argues that mutations are less efficiently selected for in small populations.
@@
 
-    %Altogether, we estimated that between 18 and 39\% of $\dnds$ is over-estimated (table S1), corresponding to maintenance positive selection.
-    %In a nearly neutral framework, genomes could be viewed as the arena of a tug-of-war between a large volume of deleterious mutations that eventually reach fixation due to drift, and scarce advantageous mutations that are restoring a more optimal ancestral state.
-    % However, and surprisingly, a decrease in the proportion of neutral mutation did not translate into a mechanical increase in the proportion of advantageous mutations.
-    % Instead, populations with higher diversity have a lower proportion of advantageous mutations (fig.~S7), this effect is also more pronounced for mutations predicted to be advantageous at the phylogenetic scale (red row in fig.~\ref{fig:heatmap}C and fig.~S8).
-    % This discrepancy can be explained by the fact that populations with larger diversity have already depleted the putatively advantageous mutations, and that only deleterious are remaining possible.
-    % In other words, being on the top of a fixed fitness landscape leaves you with only paths going downhill.
-    % Altogether, populations with increased diversity are showing signature of increased selection efficiency and are also less likely to generate positively selected mutations.
-
     \begin{figure*}[!ht]
@@
             Reproducibility of results shown in figure~\ref{fig:homo-afr-results} in 28 populations across 6 genera.
-            Site-frequency spectra and total mutation rates are combined at the population-genetic scale to estimate the proportion of advantageous mutations ($\PpolyAdv$) in the top panel, of nearly-neutral mutations ($\PpolyNeutral$) in the middle panel and of deleterious mutations ($\PpolyDel$) in the bottom panel.
-        }
+            For each class of selection at the phylogenetic scale ($\Sphyclass \in \{ \divStrongDel, \divDel,  \divWeakDel,  \divWeakAdv, \divAdv \}$, in rows), site-frequency spectra and total number of sites are combined at the population-genetic scale to estimate the proportion of advantageous mutations ($\PpolyAdv$) in the top panel, of nearly-neutral mutations ($\PpolyNeutral$) in the middle panel and of deleterious mutations ($\PpolyDel$) in the bottom panel.
+        }.
         \label{fig:heatmap}
@@
             Panel A.
-For each population, the proportion of advantageous ($p_+=\PpolyAdv$), nearly-neutral ($\PpolyNeutral$) and of deleterious ($\PpolyDel$) mutations estimated at the population-genetic scale is shown.
-            Estimation is performed with SNPs predicted to be weakly advantageous at the phylogenetic scale ($\divWeakAdv$).
+For each population, the proportion of advantageous ($p_+=\PpolyAdv$), nearly-neutral ($\PpolyNeutral$) and of deleterious ($\PpolyDel$) mutations estimated at the population-genetic scale using all SNPs available.
+            Population are sorted for increased synonymous diversity.
             Panel B.
@@
     Moreover, SIFT scores based on amino-acid alignments across species have also been found to be informative of the selection pressure exerted at the population scale\cite{chen_hunting_2021}.
-    Accordingly, our study shows that sites with a higher SIFT score at the phylogenetic scale are more positively selected in the different populations (supp.\ mat\  section 2).
+    Accordingly, our study shows that sites with a higher SIFT score at the phylogenetic scale are more positively selected in the different populations (supp.\ mat\  section SIFT scores).
     In practice, SIFT scores are more coarse grained, with for example a bulk of mutations with a score of 1.0 (the highest), and does not provide a boundary between advantageous and deleterious mutations, nor are they based on a population-genetics formalism.
@@
     It would also be interesting to have access to more shallow but wider phylogenies to increase the resolution of our predictions.
-    % Moreover, mammalian are less affected by codon usage
 

### 2022-07-12 manuscript/supp-mat.tex
Refactored Supp. Mat. and included explanations

@@
 
-    \section{Site-specific mutation-selection codon models}\label{sec:site-specific-mutation-selection-codon-models}
+    \section{Mutation-selection codon models}\label{sec:site-specific-mutation-selection-codon-models}
     In BayesCode (\url{https://github.com/ThibaultLatrille/bayescode}), mutation-selection codon models are obtained by running \textit{mutselomega} for 2000 points of MCMC with the options:
@@
 
-    \subsection{Summary table}\label{subsec:summary-table-mutsel}
+    \subsection{Summary tables}\label{subsec:summary-table-mutsel}
     \begin{center}
-        \captionof{table}{}
+        \captionof{table}{~}
         \scriptsize
@@
     \begin{center}
-        \captionof{table}{}
+        \captionof{table}{~}
         \scriptsize
@@
 
+    We estimated that between 20 and 25\% of $\dnds$ is over-estimated ($R(\dnds)$), corresponding to maintenance positive selection exerted on substitutions.
+    Moreover, we estimated that between 24 and 38\% of $p_+$ is over-estimated ($R(p_+)$), corresponding to maintenance positive selection exerted on segregating mutations.
+    Altogether, in a nearly neutral framework, genomes could be viewed as the arena of a tug-of-war between a large volume of deleterious mutations that eventually reach fixation due to drift, and scarce advantageous mutations that are restoring a more optimal ancestral state.
+
     \newpage
+
     \subsection{Correlation with diversity}
+
     \subsubsection{Proportion of nearly-neutral mutations ($\polyNeutral$)}\label{subsec:proportion-nearly-neutral-mutations}
-    \captionof{figure}{}
+    \captionof{figure}{~}
     \begin{minipage}{0.32\linewidth}
@@
     \subsubsection{Proportion of deleterious mutations ($\polyDel$)}\label{subsec:proportion-deleterious-mutations}
-    \captionof{figure}{}
+    \captionof{figure}{~}
     \begin{minipage}{0.32\linewidth}
@@
     \subsubsection{Proportion of advantageous mutations ($\polyAdv$)}\label{subsec:proportion-advantageous-mutations}
-    \captionof{figure}{}
+    \captionof{figure}{~}
     \begin{minipage}{0.32\linewidth}
@@
     The relationship between $\SpopMean$ and $\SphyMean$ can be described by a second-order polynomial, and the slope of this polynomial at $\SphyMean=0$ gives the ratio $\SpopMean/\SphyMean$ for each population.
-    \captionof{figure}{}
+    \captionof{figure}{~}
     \begin{center}
@@
     As a consequence of an increased selection efficiency, mutations in populations with high diversity are mechanistically more likely to be deleterious (see~\ref{subsec:proportion-deleterious-mutations}, left scatter-plot), especially for mutations predicted already to be deleterious at the phylogenetic scale (see~\ref{subsec:proportion-deleterious-mutations}, middle and right scatter-plot).
+    % A decrease in the proportion of neutral mutation did not translate into a mechanical increase in the proportion of advantageous mutations.
+    % Instead, populations with higher diversity have a lower proportion of advantageous mutations, this effect is also more pronounced for mutations predicted to be advantageous at the phylogenetic scale.
+    % This discrepancy can be explained by the fact that populations with larger diversity have already depleted the putatively advantageous mutations, and that only deleterious are remaining possible.
+    % In other words, being on the top of a fixed fitness landscape leaves you with only paths going downhill.
+    % Altogether, populations with increased diversity are showing signature of increased selection efficiency and are also less likely to generate positively selected mutations.
+
+    \newpage
+
+    \subsection{Proportion of selected mutations}
+
+    For each population, the proportion of advantageous ($p_+=\PpolyAdv$), nearly-neutral ($\PpolyNeutral$) and of deleterious ($\PpolyDel$) mutations estimated at the population-genetic scale is shown.
+    Estimation is performed with SNPs with different class of selection at the phylogenetic scale: $\Sphyclass \in \{ \divStrongDel, \divDel,  \divWeakDel,  \divWeakAdv, \divAdv \}$
+    Population are sorted for increased synonymous diversity.
+
+    \begin{center}
+        \captionof{figure}{~}
+        \begin{minipage}{0.9\linewidth}
+            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.MutSel.all.stacked.pdf}
+        \end{minipage}
+        \begin{minipage}{0.09\linewidth}
+            \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
+        \end{minipage}
+        \captionof{figure}{~}
+        \begin{minipage}{0.9\linewidth}
+            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.MutSel.neg-strong.stacked.pdf} \\
+        \end{minipage}
+        \begin{minipage}{0.09\linewidth}
+            \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
+        \end{minipage}\captionof{figure}{~}
+        \begin{minipage}{0.9\linewidth}
+            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.MutSel.neg.stacked.pdf} \\
+        \end{minipage}
+        \begin{minipage}{0.09\linewidth}
+            \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
+        \end{minipage}\captionof{figure}{~}
+        \begin{minipage}{0.9\linewidth}
+            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.MutSel.neg-weak.stacked.pdf} \\
+        \end{minipage}
+        \begin{minipage}{0.09\linewidth}
+            \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
+        \end{minipage}\captionof{figure}{~}
+        \begin{minipage}{0.9\linewidth}
+            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.MutSel.pos-weak.stacked.pdf} \\
+        \end{minipage}
+        \begin{minipage}{0.09\linewidth}
+            \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
+        \end{minipage}\captionof{figure}{~}
+        \begin{minipage}{0.9\linewidth}
+            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.MutSel.pos.stacked.pdf}
+        \end{minipage}
+        \begin{minipage}{0.09\linewidth}
+            \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
+        \end{minipage}
+    \end{center}
+    We confirmed that higher synonymous diversity is typically accompanied by a smaller proportion of neutral mutations.
+    This result is specially visible when we restricted the analysis to class of mutations that are supposedly nearly-neutral at the phylogenetic scale ($\divWeakDel$  and $\divWeakAdv$).
+    This result suggests that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) are more likely to discriminate whether mutations are advantageous or deleterious.
+    Alternatively stated, mutations in populations with low diversity (e.g.~\textit{Homo}) are effectively nearly-neutral and behave as would a neutral mutation.
+    This result is qualitatively in accordance with the nearly-neutral theory of evolution which argues that mutations are less efficiently selected for in small populations.
+
+    \section{Mutation-selection models: histograms and SFS for each population}\label{sec:mutation-selection-models:-histograms-and-sfs-for-each-population}
+    For each population, the same figure is shown.
+    \begin{itemize}
+        \item Top-left panel: Histogram of predicted selection coefficients ($\Sphy$) for all possible mutations away from the ancestral genome, giving the number of sites ($L$, in y-axis) across the genome with a given $\Sphy$.
+        Mutations are divided into 5 classes: severely deleterious (blue), deleterious (green), weakly deleterious (light green), weakly advantageous (yellow) and advantageous (red).
+        \item Top-right panel: Histogram of predicted selection coefficients ($\Sphy$) for all observed mutations in a sample of 8 individuals (out of 512 in the original dataset) of African descent.
+        If they are less mutations observed than expected, this class is thus undergoing purifying selection.
+        \item Bottom-left panel: The site-frequency spectrum (SFS) represents the proportion of mutations (y-axis) with a given number of derived alleles in the population (x-axis).
+        SFS are drawn for a random sample of 16 alleles (mean in solid line and standard deviation in filled color) for each class of selection coefficient and for synonymous mutations which are supposedly neutral (black).
+        At high frequencies, supposedly severally deleterious mutations are underrepresented.
+        \item Bottom-right panel:For each class of selection (and for the set of all non-synonymous mutations), information from the SFS and the expected total mutation rate are combined at the population-genetic scale to estimate the proportion of advantageous mutations $\PpolyAdv$, of nearly-neutral mutations $\PpolyNeutral$ and of deleterious mutations $\PpolyDel$.
+    \end{itemize}
 
@@
 
-    \subsection{Summary table}\label{subsec:summary-table-sift-scores}
+    \subsection{Proportion of selected mutations}\label{subsec:proportion-of-selected-mutations}
+    For each population, the proportion of advantageous ($p_+=\PpolyAdv$), nearly-neutral ($\PpolyNeutral$) and of deleterious ($\PpolyDel$) mutations estimated at the population-genetic scale is shown.
+    Estimation is performed with SNPs with different class of SIFT scores at the phylogenetic scale.
+    Population are sorted for increased synonymous diversity.
 
     \begin{center}
-        \captionof{table}{}
+        \captionof{figure}{~}
+        \begin{minipage}{0.9\linewidth}
+            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.SIFT.all.stacked.pdf}
+        \end{minipage}
+        \begin{minipage}{0.09\linewidth}
+            \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
+        \end{minipage}
+        \captionof{figure}{~}
+        \begin{minipage}{0.9\linewidth}
+            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.SIFT.neg-strong.stacked.pdf} \\
+        \end{minipage}
+        \begin{minipage}{0.09\linewidth}
+            \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
+        \end{minipage}\captionof{figure}{~}
+        \begin{minipage}{0.9\linewidth}
+            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.SIFT.neg.stacked.pdf} \\
+        \end{minipage}
+        \begin{minipage}{0.09\linewidth}
+            \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
+        \end{minipage}\captionof{figure}{~}
+        \begin{minipage}{0.9\linewidth}
+            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.SIFT.neg-weak.stacked.pdf} \\
+        \end{minipage}
+        \begin{minipage}{0.09\linewidth}
+            \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
+        \end{minipage}\captionof{figure}{~}
+        \begin{minipage}{0.9\linewidth}
+            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.SIFT.pos-weak.stacked.pdf} \\
+        \end{minipage}
+        \begin{minipage}{0.09\linewidth}
+            \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
+        \end{minipage}\captionof{figure}{~}
+        \begin{minipage}{0.9\linewidth}
+            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.SIFT.pos.stacked.pdf}
+        \end{minipage}
+        \begin{minipage}{0.09\linewidth}
+            \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
+        \end{minipage}
+    \end{center}
+    Sites with a higher SIFT score at the phylogenetic scale are more positively selected in the different populations.
+
+    \subsection{Summary table}\label{subsec:summary-table-sift-scores}
+    \begin{center}
+        \captionof{table}{~}
         \footnotesize
@@
     \end{itemize}
+
+    The previous section showed that mutations with a higher SIFT score at the phylogenetic scale are more positively selected in the different populations.
+    However, whenever we removed the category of SNPs with the highest SIFT score ($\textrm{SIFT} \geq 0.8$), we expected the estimation of $p_+ (\textrm{SIFT} < 0.8)$ to be lower than $p_+$ (estimated on the all dataset), as we have shown that $p_+ (\Sphy < 0) < p_+$ with mutation-selection codon models.
+    Thus SIFT scores are not providing reliable information on the current selective strength exerted on mutations, at least for high SIFT scores.
+    Moreover, there is no defined threshold (here we arbitrarily used 0.8) to cut-off between advantageous and deleterious changes.
+
     \newpage
+    \section{SIFT scores: histograms and SFS for each population}\label{sec:sift-scores:-histograms-and-sfs-for-each-population}
+    For each population, the same figure is shown.
+    \begin{itemize}
+        \item Top-left panel: Histogram of SIFT score for all possible mutations away from the ancestral genome, giving the number of sites ($L$, in y-axis) across the genome with a given SIFT score.
+        Mutations are divided into 5 classes: severely deleterious (blue), deleterious (green), weakly deleterious (light green), weakly advantageous (yellow) and advantageous (red).
+        \item Top-right panel: Histogram of SIFT score for all observed mutations in a sample of 8 individuals (out of 512 in the original dataset) of African descent.
+        If they are less mutations observed than expected, this class is thus undergoing purifying selection.
+        \item Bottom-left panel: The site-frequency spectrum (SFS) represents the proportion of mutations (y-axis) with a given number of derived alleles in the population (x-axis).
+        SFS are drawn for a random sample of 16 alleles (mean in solid line and standard deviation in filled color) for each class of selection coefficient and for synonymous mutations which are supposedly neutral (black).
+        At high frequencies, supposedly severally deleterious mutations are underrepresented.
+        \item Bottom-right panel:For each class of selection (and for the set of all non-synonymous mutations), information from the SFS and the expected total mutation rate are combined at the population-genetic scale to estimate the proportion of advantageous mutations $\PpolyAdv$, of nearly-neutral mutations $\PpolyNeutral$ and of deleterious mutations $\PpolyDel$.
+    \end{itemize}
     \input{include-SIFT-non-adaptive}

### 2022-08-10 manuscript/main.tex
N. Salamin corrections

@@
 \usepackage{biorxiv}
-\usepackage[backend=biber,style=nature]{biblatex}
+\usepackage[backend=biber,,isbn=false,url=false,intitle=true,style=nature]{biblatex}
 \addbibresource{codon_models.bib}
@@
 \usepackage{lineno}
+
+\newcommand{\NS}[1]{\textcolor{red}{\textbf{\emph{[NS: #1]}}}}
 
@@
 
-    We usually say that a mutation is undergoing positive selection when it brings a fitness advantage to its bearer, and thus facilitates its own transmission to the next generation.
-    However, the causes of this advantage can be diverse.
-    We can distinguish two main scenarios in which a mutation is advantageous.
-    The first scenario concerns environmental change.
-    The bearer of the mutation that is advantageous in a new environment will be better adapted, and its chances of survival and reproduction will be higher (fig.~\ref{fig:fitness-landscape}A).
-    This process is typically referred to as adaptive evolution.
-    The second scenario involves a mutation restoring the ancestral allele which corresponded to an optimal state of the individual in a constant environment, but has been lost due to the fixation of a deleterious mutation by drift (fig.~\ref{fig:fitness-landscape}B).
-    In this manuscript, this process will be referred to as maintenance positive selection.
-    Regarding the difference between these two scenarios at the population scale, while in the case of environmental change, the population as a whole is climbing the fitness landscape along an adaptive walk\cite{tenaillon_utility_2014}, in the case of maintenance positive selection, the population as a whole is thus merely staying in the same position in the fitness landscape at the mutation-selection equilibrium, and positive selection compensates for deleterious mutations that reach fixation due to drift\cite{sella_application_2005, mustonen_fitness_2009}.
-    These two different kinds of selection result in a positive transmission bias of the advantageous allele, but their consequences at a macro-evolutionary scale are fundamentally different.
+    \NS{on devrait plus placer le départ de l'intro dans un contexte historique, pour dire que de connaître si une mutation est avantageuse est la base de la génétique moléculaire (en citant des papiers clés)}
+
+    We usually say that a mutation is undergoing positive selection when it brings a fitness advantage to its bearer with the consequence of facilitating its own transmission to the next generation.
+    We can distinguish two main scenarios that can lead to such positive selection.
+    In the first scenario, a change of environment will modify the fitness of the individuals and the bearer of the mutation that is advantageous in the new environment will be better adapted.
+    Its chances of survival and reproduction will be higher and this process is typically referred to as adaptive evolution (fig.~\ref{fig:fitness-landscape}A).
+    The second scenario involves a mutation restoring the ancestral allele which corresponded to an optimal fitness for an individual in a constant environment, but has been lost due to the fixation of a deleterious mutation by drift (fig.~\ref{fig:fitness-landscape}B).
+    In this study, this process will be referred to as maintenance positive selection.
+    At the scale of a population, these two scenarios display different dynamics.
+    While in the case of environmental change, the population as a whole is climbing the fitness landscape along an adaptive walk\cite{tenaillon_utility_2014}, in the case of maintenance positive selection, the population as a whole is at mutation-selection equilibrium and therefore merely stays at the same location in the fitness landscape \cite{sella_application_2005, mustonen_fitness_2009}.
+
+    At the population scale, these two different kinds of selection are indistinguishable and both result in a positive transmission bias of the advantageous allele, but their consequences at a macro-evolutionary scale are fundamentally different.
     While adaptive evolution promotes phenotype diversification (fig.~\ref{fig:fitness-landscape}C), maintenance positive selection promotes phenotype stability and preserves well established biological systems (fig.~\ref{fig:fitness-landscape}D).
-    It is thus of importance to be able to distinguish those two kinds of positive selection in order to understand how selection impacts the diversification of species.
+    It is thus essential to distinguish these two types of positive selection to understand the long term effects of selection on the diversification of species.
 
-    Positive selection can be quantified by comparing sequence variation inside a population with the sequence divergence with a sister species\cite{mcdonald_adaptative_1991}.
-    Indeed, strongly advantageous mutations are expected to be observed in substitutions but not in polymorphism because they reach fixation quickly.
-    This method has been largely improved to account for possible bias-inducing factors such as the presence of weak positive selection, background selection and demography fluctuations\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009, galtier_adaptive_2016, tataru_inference_2017}.
-    It's application across many taxa has uncovered widespread positive selection\cite{moutinho_variation_2019}.
-    The root cause for this widespread rate of positive selection is, however, scarcely investigated, often assumed to be the end result of adaptive evolution.
-    However, as mentioned above, not all these mutations contribute to genetic innovation and diversification.
-    Adaptive evolution can only be well estimated if maintenance positive selection is taken into account.
-    While adaptive evolution is unpredictable because it brings an advantage concerning an unpredictable change in the environment of organisms, the second is predictable because optimal states should be more or less the same for closely related organisms which share most of their environment and physiology.
-    A way to thus measure maintenance positive selection is to compute selection coefficients assuming a constant and stable fitness landscape estimated from the alignment of protein-coding genes.
-    For each site of the protein alignment, amino-acid frequency is a proxy for its fitness, since for example a deleterious amino acid will be more likely to be absent in the alignment.
+    Positive selection can be quantified by comparing sequence variation inside a population with the sequence divergence from a sister species\cite{mcdonald_adaptative_1991}.
+    The basic idea is that advantageous mutations are expected to be observed in substitutions between species but not in polymorphism within a population because they reach fixation too quickly.
+    This method has been largely improved to account for possible bias-inducing factors such as the presence of weak positive selection, background selection and demographic fluctuations\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009, galtier_adaptive_2016, tataru_inference_2017}.
+    It has been applied across many organisms and enabled the discovery of widespread positive selection\cite{moutinho_variation_2019}.
+    However, the exact causes for this widespread occurrence of positive selection have been scarcely investigated\NS{is it the case in the conclusion of the previous paper??
+would be nice to back it up with references}.
+    As mentioned above, not all advantageous mutations contribute to genetic innovation and diversification and truly adaptive evolution can only be well estimated if maintenance positive selection is taken into account.
+    While adaptive evolution is unpredictable because it caused by an unpredictable change in the environment of organisms, the second is predictable because optimal states should be more or less the same for closely related organisms which share most of their environment and physiology.
+    A way to thus measure maintenance positive selection is to predict selection coefficients assuming a constant and stable fitness landscape estimated from the alignment of protein-coding genes.
+    For each site of the protein alignment, a first approximation would be to consider that the frequency of an amino-acid is a proxy for its fitness, since for example a deleterious amino acid will be more likely to be absent in the alignment.
     One of the most used methods to make these predictions is SIFT (Sort Intolerant From Tolerant), which reliably detects deleterious mutations in many taxa\cite{ng_sift_2003, vaser_sift_2016}.
     However, this method has two major shortcomings.
-    First, this method uses amino-acid frequency as a proxy for amino-acid fitness, even if we know that a lot of mechanisms can influence amino-acid frequency other than fitness (phylogeny, mutation biases, GC-biased gene conversion, mutational paths).
+    First, we know that a lot of mechanisms can influence amino-acid frequency other than fitness (phylogeny, mutation biases, GC-biased gene conversion, mutational paths) which are not accounted for in SIFT.
     Second, SIFT scores makes little sense as an actual measure of fitness, and is not interpretable in terms of population genetics.
@@
     Such codon models provide a nearly-neutral framework of evolution by estimating the fitness landscape over amino-acid sequences for each site of the sequence (fig~\ref{fig:method}A) while taking into account non-adaptive processes impacting codon frequency\cite{halpern_evolutionary_1998, rodrigue_mechanistic_2010, tamuri_estimating_2012}.
-    Only nearly-neutral mutations between high fitness amino acids will tend to be permitted by the model, allowing for the explicit calculation of the scaled selection coefficient of non-synonymous mutations between codons.
+    %Only nearly-neutral mutations between high fitness amino acids will tend to be permitted by the model, allowing for the explicit calculation of the scaled selection coefficient of non-synonymous mutations between codons.
     As a consequence, by integrating datasets at the species and population level, we can estimate the selection coefficient for each mutation currently segregating in a population.
@@
 
-    To answer these questions, we have estimated a fitness landscape for long-term evolution using available multiple sequence alignments between mammalian species\cite{ranwez_orthomam_2007, howe_ensembl_2021}.
-    We then developed and leveraged a pipeline integrating divergence and polymorphism data across the entire exome for 28 populations across 6 genera, namely \textit{Equus},  \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus} and \textit{Homo} (fig.~\ref{fig:method}A\&B).
+    To answer these questions, we estimated the fitness landscape of amino-acid for long-term evolution using available multiple sequence alignments between mammalian species\cite{ranwez_orthomam_2007, howe_ensembl_2021}.
+    We developed a pipeline to integrate data at the phylogenetic and population scale to estimate divergence and polymorphism, respectively, across the entire exome for 28 populations from 6 genera (\textit{Equus},  \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus} and \textit{Homo}; fig.~\ref{fig:method}A\&B).
 
@@
     We thus ordered populations by their levels of synonymous diversity (fig.~\ref{fig:diversity}A) and confirmed that higher synonymous diversity is typically accompanied by a smaller proportion of neutral mutations.
-    This result suggests that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) are more likely to discriminate whether mutations are advantageous or deleterious (fig~S1-S5).
-    Alternatively stated, mutations in populations with low diversity (e.g.~\textit{Homo}) are effectively nearly-neutral and behave as would a neutral mutation, especially for mutations already predicted to be nearly-neutral at the phylogenetic scale (fig~S8-S9).
+    This result suggests that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) are more likely to discriminate between advantageous and deleterious mutations (fig~S1-S5).
+    Alternatively stated, mutations in populations with low diversity (e.g.~\textit{Homo}) are effectively nearly-neutral and behave as would a neutral mutation.
+    %, especially for mutations already predicted to be nearly-neutral at the phylogenetic scale (fig~S8-S9).
     This result is qualitatively in accordance with the nearly-neutral theory of evolution which argues that mutations are less efficiently selected for in small populations.
 
-    Finally, we reconstructed the substitutions in the terminal branches of the phylogenetic tree in order to determine the distribution of their selection coefficients.
-    To this aim, for each population with polymorphism data available, we first reconstructed the ancestral sequence (which is different than the reference sequence), then we mapped the substitutions from the last genus split to this reconstructed ancestral sequence.
+    Finally, we reconstructed the substitutions in the terminal branches of the phylogenetic tree to determine the distribution of their selection coefficients.
+    For each population with available polymorphism data, we first reconstructed the ancestral sequence (which is different than the reference sequence), then we mapped the substitutions from the last genus split to this reconstructed ancestral sequence.
     In these populations, we show that out of all polarized substitutions in the branches, between 10 and 17\% of all substitutions have an $\Sphy > 1$ (table S1) and between 22 and 42\% of all substitutions have an $\Sphy > 0$ (table S2).
@@
     %This also means that the ratio $\dnds$ usually used to detect adaptation while relying on substitutions between close species\cite{mcdonald_adaptative_1991, galtier_adaptive_2016} or at the phylogenetic scale\cite{goldman_codonbased_1994, yang_codonsubstitution_2002} is overestimated.
-    These observed substitutions are likely to have been positive selected because they restored a more optimal state, not because they are driving innovations to a new environment or a new function.
+    These observed substitutions are likely to have been positively selected because they restored a more optimal state, not because they are driving innovations to a new environment or a new function.
 
@@
     This work was performed using the computing facilities of the CC LBBE/PRABI\@.
+    This study makes use of data generated by the NextGen Consortium.
+    The European Union’s Seventh Framework Programme (FP7/2010-2014) provided funding for the project under grant agreement no 244356 - “NextGen”.
     \textbf{Funding:}
-    Université de Lausanne;
+    Université de Lausanne; French National Research Agency, Grant ANR-15-CE12-0010-01 / DASIRE.
     \textbf{Author contributions:}
@@
 
-    Protein-coding DNA sequences alignments in placental mammals and gene trees are extracted from the \href{https://www.orthomam.univ-montp2.fr}{OrthoMaM} database, containing $116$ mammalian reference sequences in v10c\cite{ranwez_orthomam_2007, douzery_orthomam_2014, scornavacca_orthomam_2019}.
-    Genes located on the X, Y and mitochondrial chromosome are discarded from the analysis, since the number of polymorphism, necessary in population-based method, is expected to be different on these sequences.
-    Additionally, sequences from the species for which polymorphism are available, as well as their sister species have been discarded from the analysis to ensure independence between the data used in the phylogenetic and population-genetic method.
-    Altogether, $14,509$ protein-coding DNA sequences alignment have been analyzed containing at most $87$ reference sequences of placental mammals per alignment.
+    Protein-coding DNA sequences alignments in placental mammals and their corresponding gene trees were extracted from the \href{https://www.orthomam.univ-montp2.fr}{OrthoMaM} database.
+It contained a total of $116$ mammalian reference sequences in v10c\cite{ranwez_orthomam_2007, douzery_orthomam_2014, scornavacca_orthomam_2019}.
+    Genes located on the X, Y chromosomes and the mitochondrial genome were discarded from the analysis, because the level of polymorphism, which is necessary in the population-based analyses, is expected to be different in these three genomic regions.
+    Sequences of species for which we used poppulation-level polymorphism (see below), as well as their sister species, were removed from the analysis to ensure independence between the data used in the phylogenetic and population genetic scale.
+    Altogether, we analyzed $14,509$ protein-coding DNA sequences for at most $87$ sequences of placental mammals.
 
@@
 
-    Mutation-selection models assume that the protein-coding sequence is at mutation-selection balance under a fixed fitness landscape, which is itself characterized by a fitness vector over the $20$ amino-acid at each site\cite{yang_mutationselection_2008, halpern_evolutionary_1998, rodrigue_mechanistic_2010}.
-    Mathematically, the rate of non-synonymous substitution from codon $a$ to codon $b$ ($q_{a \mapsto b}^{(i)}$) at site $i$ of the sequence is equal to the rate of mutation from the underlying DNA change ($\mu_{a \mapsto b}$) multiplied by the scaled probability of fixation of the mutation ($\proba_{a \mapsto b}^{(i)}$).
-    Crucially, the probability of fixation depends on the difference of scaled fitness between the amino-acid encoded by the mutated codon ($F_b^{(i)}$) and the fitness of the amino-acid encoded by the original codon ($F_a^{(i)}$) of site $i$\cite{wright_evolution_1931, fisher_genetical_1930}.
-    Altogether, the rate of substitution from codon $a$ to $b$ at a given site $i$ is:
+    We analyzed the phylogenetic level data using mutation-selection models.
+These models assume that the protein-coding sequence are at mutation-selection balance under a fixed fitness landscape characterized by a fitness vector over the $20$ amino-acid at each site\cite{yang_mutationselection_2008, halpern_evolutionary_1998, rodrigue_mechanistic_2010}.
+    Mathematically, the rate of non-synonymous substitution from codon $a$ to codon $b$ ($q_{a \mapsto b}^{(i)}$) at site $i$ of the sequence is equal to the rate of mutation of the underlying nucleotide change ($\mu_{a \mapsto b}$) multiplied by the scaled probability of fixation of the mutation ($\proba_{a \mapsto b}^{(i)}$).
+    The probability of fixation depends on the difference of scaled fitness of the amino-acid encoded by the mutated codon ($F_b^{(i)}$) and the amino-acid encoded by the original codon ($F_a^{(i)}$) at site $i$\cite{wright_evolution_1931, fisher_genetical_1930}.
+    The rate of substitution from codon $a$ to $b$ at a site $i$ is thus:
     \begin{equation}
@@
     We ran the Bayesian software \href{https://github.com/bayesiancook/bayescode}{BayesCode} on each protein-coding DNA alignment\cite{lartillot_phylobayes_2013, rodrigue_detecting_2017, rodrigue_bayesian_2021}.
-    Each Monte-Carlo Markov-Chain (MCMC) is run during $2000$ points, with a burn-in of $1000$ points, allowing to compute the mean amino-acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$ across the MCMC\@.
+    We ran a Markov chain Monte-Carlo (MCMC) analysis during $2000$ generations, with a burn-in period of $1000$ generations, to obtain posterior mean estimates of the amino-acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$\@.
 
@@
 
-    In order to compare polymorphism and divergence, each SNP (chromosome, position, strand) in the focal species must be matched to its relative position in the protein-coding DNA alignment.
-    First, genomic positions are converted to relative position in the coding sequence (CDS) using gene annotation files (GTF format) downloaded from Ensembl (\url{ensembl.org}), we verified the SNP match the reference in the CDS (FASTA format) also downloaded from Ensembl.
-    Secondly, relative position in the CDS is converted to position in the multiple sequence alignment (containing gaps) from OrthoMaM database\cite{ranwez_orthomam_2007, douzery_orthomam_2014, scornavacca_orthomam_2019} by doing a global pairwise alignment (Biopython pairwise2) between the CDS fasta and the sequence found in the alignment.
+    We retrieved the genetic variants representing the population level polymorphism from the following species and respective available datasets: \textit{Equus caballus} (EquCab2 assembly in the EVA study PRJEB9799\cite{alabri_whole_2020}), \textit{Bos taurus} (UMD3.1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}), \textit{Ovis aries} (Oar\_v3.1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}), \textit{Capra Hircus} (CHIR1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}, liftover to the ARS1 assembly), \textit{Chlorocebus sabaeus} (ChlSab1.1 assembly in the EVA project PRJEB22989\cite{svardal_ancient_2017}), \textit{Homo sapiens} (GRCh38 assembly from the 1000-genome project\cite{consortium_integrated_2012, the1000genomesprojectconsortium_global_2015}).
+    In total, we analyzed 28 populations across the 6 different species with polymorphism data.
+    Genetic variants that were not found within a gene were not used in further analyses.
+    We also did not analyzed insertions and deletions and focused only on Single Nucleotide Polymorphisms (SNPs) with a single mutant allele.
+    Finally, stop codon mutants were also discarded.
+
+    Each SNP (chromosome, position, strand) in the focal species was matched to its relative position (chromosome, position, strand) in the protein-coding DNA alignment by first converting the genomic positions to relative position in the coding sequence (CDS) using gene annotation files (GTF format) downloaded from Ensembl (\url{ensembl.org}).
+    We then verified that the SNP downloaded from Ensembl were matching the reference in the CDS (FASTA format).
+    Second, the relative position in the CDS was converted to position in the multiple sequence alignment (containing gaps) from OrthoMaM database\cite{ranwez_orthomam_2007, douzery_orthomam_2014, scornavacca_orthomam_2019} by doing a global pairwise alignment, using the Biopython function pairwise2, between the CDS fasta and the sequence found in the alignment.
     This conversion from genomic position to position in the alignment is only possible if the assembly used for SNP calling is the same as the one used in the alignment, the GTF annotations and the FASTA sequences.
-    We retrieved polymorphism from different projects.
-    \textit{Equus caballus} variants called on the EquCab2 assembly in the EVA study PRJEB9799.
-    \textit{Bos taurus} variants called on the UMD3.1 assembly in the next-gen project.
-    \textit{Ovis aries} variants called on the Oar\_v3.1 assembly in the next-gen project.
-    \textit{Capra Hircus} variants called on the CHIR1 assembly in the next-gen project, we performed a liftover to the ARS1 assembly.
-    \textit{Chlorocebus sabaeus} variants are called on the ChlSab1.1 assembly in the EVA study PRJEB22989\cite{svardal_ancient_2017}.
-    \textit{Homo sapiens} variants are called on the GRCh38 assembly in the 1000-genome project\cite{consortium_integrated_2012, the1000genomesprojectconsortium_global_2015}.
-    Variants not inside genes are discarded at the beginning of the analysis.
-    Insertions and deletions are not analyzed, and only Single Nucleotide Polymorphisms (SNPs) with only one mutant allele are considered.
-    Stop codon mutants are also discarded.
-    SNPs are polarized using the $3$ closest outgroups found in the OrthoMam alignment with est-usfs v2.04\cite{keightley_inferring_2018}.
-    For populations containing more than $8$ sampled individuals, the site-frequency spectrum (SFS) is subsampled down to $16$ chromosomes ($8$ diploid individuals) without replacement (hyper-geometric distribution) to alleviate the effect of different sampling depth in the 28 populations.
-    The Snakemake pipeline for integrating polymorphism and divergence data uses custom scripts written in python 3.9.
+
+    SNPs were polarized using the $3$ closest outgroups found in the OrthoMam alignment with est-usfs v2.04\cite{keightley_inferring_2018}.
+    For populations containing more than $8$ individuals, the site-frequency spectrum (SFS) was subsampled down to $16$ chromosomes ($8$ diploid individuals) without replacement (hyper-geometric distribution) to alleviate the effect of different sampling depth in the 28 populations.
+
+    We developped a Snakemake pipeline to integrate polymorphism and divergence data with custom scripts written in python 3.9.
 
@@
     \label{subsec:s-polymorphism-method}
-    The probability to sample allele at a given frequency (before fixation or extinction) is informative of its scaled selection coefficient at the population scale ($\Spop$).
-    Pooled across many sites, the SFS is thus informative on the underlying $\Spop$ of mutations, given we have a neutral expectation.
-    In this configuration, a single $\Spop$ for all sampled mutations is biologically not realistic.
-    Accordingly, a distribution of fitness effects of mutations (DFE) is assumed, usually modeled as a continuous distribution\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009}.
-    In this study, we used the software polyDFE\cite{tataru_inference_2017, tataru_polydfe_2020}, for which the DFE ($\phi$) is given by a mixture of a $\Gamma$ and Exponential distributions, parameterized by $\Spop_d$ , $b$, $p_b$
-    and $\Spop_b$ as:
+    The probability to sample an allele at a given frequency (before fixation or extinction) is informative of its scaled selection coefficient at the population scale ($\Spop$).
+    Pooled across many sites, the SFS provides therefore information on the underlying $\Spop$ of mutations.
+    However, estimating a single $\Spop$ for all sampled mutations is biologically unrealistic and a distribution of fitness effects of mutations (DFE) is usually assumed~\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009}.
+    In this study, we used the software polyDFE\cite{tataru_inference_2017, tataru_polydfe_2020}, which used a mixture of a $\Gamma$ and Exponential distributions to model the DFE of non-synonymous mutations, while synonymous mutations are considered neutral.
+    The model estimates the parameters $\Spop_d$ , $b$, $p_b$ and $\Spop_b$ for non-synonymous mutations as:
     \begin{equation}
@@
     and $f_{\Gamma}(x; m, b)$ is the density of the $\Gamma$ distribution with mean m and shape b, while $f_{e}(x; m)$ is the density of the Exponential distribution with mean $m$.
-    Once the DFE is fitted to the data, the proportion of advantageous ($\PpolyAdv$), nearly-neutral ($\PpolyNeutral$) and deleterious mutations ($\PpolyDel$) are given as:
+    Once the DFE was fitted to the data, the proportion of advantageous ($\PpolyAdv$), nearly-neutral ($\PpolyNeutral$) and deleterious mutations ($\PpolyDel$) were given as:
     \begin{align}
@@
 
-    PolyDFE requires one SFS for non-synonymous mutations and one for synonymous mutations (neutral expectation), as well as the total mutation rate (mutation rate per site multiplied by the number of sites) on which each SFS has been sampled.
-    The number of sites for each SFS is thus obtained using the following four-step procedure.
-    First, for each gene, the reference DNA sequence is adjusted with ancestral and fixed polymorphism for each population.
-    Second, from this reconstructed sequence, all possible mutations are computed, weighted by the mutation rate between nucleotide ($\mu$) estimated at the phylogenetic scale.
-    Third, the total mutation rate for synonymous mutations, called $\mu_{\textrm{syn}}$, is the sum across the genome.
-    Similarly, the total mutation rate for each class of selection, called  $\mu\left( \Sphyclass \right)$, is the sum across all non-synonymous mutations if their selection coefficient at the phylogenetic scale ($\Sphy$) is in the class $\Sphyclass$ (e.g.
+    PolyDFE required one SFS for non-synonymous mutations and one for synonymous mutations (neutral expectation), as well as the total mutation rate (i.e.~mutation rate per site multiplied by the number of sites) on which each SFS has been sampled.
+    We performed the following four-step procedure to obtain the number of sites for each SFS.
+    First, for each population with polymorphism data available, the polarized SNPs (ancestral and derived alleles) were used to reconstruct the ancestral DNA sequence, containing only substitutions and no segregating polymorphisms.
+    If a SNP is still segregating in the population, the ancestral version of the SNP is used.
+    However, if the derived allele is shared by all individuals in the population, the allele is considered fixed and the derived allele of the SNP is used instead.
+    Second, from this reconstructed ancestral sequence, all possible mutations were computed, weighted by the mutation rate between nucleotide ($\mu$), which was estimated at the phylogenetic scale.
+    Third, the total mutation rate for synonymous mutations, called $\mu_{\textrm{syn}}$, was estimated as the sum across the whole genome.
+    Similarly, the total mutation rate for each class of selection, called  $\mu\left( \Sphyclass \right)$, was estimated as the sum across all non-synonymous mutations if their selection coefficient at the phylogenetic scale ($\Sphy$) was in the class $\Sphyclass$ (e.g.
 $\Sphyclass = \divAdv$).
-    Fourth, the number of sites ($L$) for each class of selection coefficient ($\Sphyclass$) is then computed as the total number of sites across the genome ($L_{tot}$) weighted by the ratio of the aggregated mutations rates falling in the class ($\mu\left( \Sphyclass \right)$) over the total mutation rate for all possible mutations:
+    Fourth, the number of sites ($L$) for each class of selection coefficient ($\Sphyclass$) was finally computed as the total number of sites across the genome ($L_{tot}$) weighted by the ratio of the aggregated mutations rates falling in the class ($\mu\left( \Sphyclass \right)$) over the total mutation rate for all possible mutations:
     \begin{align}
@@
     \end{align}
-    From the SFS and the number of sites $L$ for the both synonymous and for the class of non-synonymous, polyDFE estimates parameters of the DFE $\phi \left( \Spop; \Spop_d , b, p_b, \Spop_b \right)$ using maximum likelihood.
+    From the SFS and the number of sites $L$ for both the synonymous and non-synonymous classes, polyDFE estimated the parameters of the DFE $\phi \left( \Spop; \Spop_d , b, p_b, \Spop_b \right)$ using maximum likelihood.
 
-    The fraction of non-adaptive advantageous mutations $R(p_+)$ is computed the fraction of advantageous mutations ($p_+$) that is due to maintenance positive selection, where $p_+$ is compared to the estimated divergence when we removed the restoring substitutions $p_+(\Sphy < 0)$.
+    The fraction of non-adaptive advantageous mutations $R(p_+)$ was computed as the ratio between the difference in the numbers of advantageous mutations ($p_+$), which were due to maintenance positive selection, and the estimated divergence when we removed the restoring substitutions $p_+(\Sphy < 0)$, over $p_+$.
     \begin{equation}
@@
     \label{subsec:substitution-mapping-in-the-terminal-branch}
-    For each population with polymorphism data available, the polarized SNPs (ancestral and derived alleles) are used to correct the DNA reference sequence such as to contain only substitutions and no segregating polymorphisms.
-    If a SNP is still segregating in the population, the ancestral version of the SNP is used.
-    However, if the derived allele is shared by all individuals in the population, the allele is considered fixed and the derived allele of the SNP is used instead.
+    For each gene and for each population with polymorphism data available, the ancestral DNA sequence was reconstructed from ancestral and fixed polymorphism (see previous section).
     Then, using this ancestral DNA reference and the $3$ closest outgroups found in the OrthoMam alignment, we reconstructed the ancestral protein-coding DNA sequences for each node of the 4-leaves tree with the yang M5 codon model (gamma site rate variation) in FastML.v3.11\cite{ashkenazy_fastml_2012}.
-    All polarized codon substitutions are then obtained by comparing the ancestral protein-coding DNA sequences before the split to the sister species (closest outgroup) to the corrected DNA reference for the population of interest.
+    All polarized codon substitutions are then obtained by comparing the ancestral protein-coding DNA sequences before the split to the sister species (closest outgroup) to the ancestral DNA reference for the population of interest (without segregating polymorphism).
     We considered \textit{Ceratotherium simum simum} as \textit{Equus caballus} sister species; \textit{Bison bison bison} as \textit{Bos taurus} sister species; \textit{Pantholops hodgsonii} as \textit{Ovis aries} sister species; \textit{Pantholops hodgsonii} as \textit{Capra Hircus} sister species; \textit{Macaca mulatta} as \textit{Chlorocebus sabaeus} sister species and finally we considered \textit{Pan troglodytes} as \textit{Homo sapiens} sister species.

### 2022-08-10 manuscript/main.tex
J. Joseph corrections

@@
 
-    \NS{on devrait plus placer le départ de l'intro dans un contexte historique, pour dire que de connaître si une mutation est avantageuse est la base de la génétique moléculaire (en citant des papiers clés)}
-
+    %\NS{on devrait plus placer le départ de l'intro dans un contexte historique, pour dire que de connaître si une mutation est avantageuse est la base de la génétique moléculaire (en citant des papiers clés)}
     We usually say that a mutation is undergoing positive selection when it brings a fitness advantage to its bearer with the consequence of facilitating its own transmission to the next generation.
     We can distinguish two main scenarios that can lead to such positive selection.
-    In the first scenario, a change of environment will modify the fitness of the individuals and the bearer of the mutation that is advantageous in the new environment will be better adapted.
-    Its chances of survival and reproduction will be higher and this process is typically referred to as adaptive evolution (fig.~\ref{fig:fitness-landscape}A).
+    In the first scenario, a mutation towards a state which was deleterious is now advantageous because of a change of environment.
+    A change of environment could be a change of temperature, viral exposition but it could also be a change in another part of the species' genome.
+    In the new environment, the mutation allows its bearer to survive and reproduce more than the others and thus will be positively selected.
+    This process is typically referred to as adaptive evolution (fig.~\ref{fig:fitness-landscape}A).
+
     The second scenario involves a mutation restoring the ancestral allele which corresponded to an optimal fitness for an individual in a constant environment, but has been lost due to the fixation of a deleterious mutation by drift (fig.~\ref{fig:fitness-landscape}B).
@@
     At the scale of a population, these two scenarios display different dynamics.
-    While in the case of environmental change, the population as a whole is climbing the fitness landscape along an adaptive walk\cite{tenaillon_utility_2014}, in the case of maintenance positive selection, the population as a whole is at mutation-selection equilibrium and therefore merely stays at the same location in the fitness landscape \cite{sella_application_2005, mustonen_fitness_2009}.
+    While in the case of environmental change, the population as a whole is climbing the fitness landscape along an adaptive walk\cite{tenaillon_utility_2014}, in the case of maintenance positive selection, the population as a whole is at mutation-selection equilibrium and therefore merely stays at the same location in the fitness landscape\cite{sella_application_2005, mustonen_fitness_2009}.
 
@@
     It has been applied across many organisms and enabled the discovery of widespread positive selection\cite{moutinho_variation_2019}.
-    However, the exact causes for this widespread occurrence of positive selection have been scarcely investigated\NS{is it the case in the conclusion of the previous paper??
+    However, the exact causes for this widespread occurrence of positive selection have been scarcely investigated\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009, galtier_adaptive_2016} %\NS{is it the case in the conclusion of the previous paper??
 would be nice to back it up with references}.
@@
     \textbf{Funding:}
-    Université de Lausanne; French National Research Agency, Grant ANR-15-CE12-0010-01 / DASIRE.
+    Université de Lausanne; Agence Nationale de la Recherche, Grant ANR-19-CE12-0019 / HotRec.
     \textbf{Author contributions:}

### 2022-08-10 manuscript/main.tex
Amino-acid -> amino acid

@@
     A way to thus measure maintenance positive selection is to predict selection coefficients assuming a constant and stable fitness landscape estimated from the alignment of protein-coding genes.
-    For each site of the protein alignment, a first approximation would be to consider that the frequency of an amino-acid is a proxy for its fitness, since for example a deleterious amino acid will be more likely to be absent in the alignment.
+    For each site of the protein alignment, a first approximation would be to consider that the frequency of an amino acid is a proxy for its fitness, since for example a deleterious amino acid will be more likely to be absent in the alignment.
     One of the most used methods to make these predictions is SIFT (Sort Intolerant From Tolerant), which reliably detects deleterious mutations in many taxa\cite{ng_sift_2003, vaser_sift_2016}.
     However, this method has two major shortcomings.
-    First, we know that a lot of mechanisms can influence amino-acid frequency other than fitness (phylogeny, mutation biases, GC-biased gene conversion, mutational paths) which are not accounted for in SIFT.
+    First, we know that a lot of mechanisms can influence amino acid frequency other than fitness (phylogeny, mutation biases, GC-biased gene conversion, mutational paths) which are not accounted for in SIFT.
     Second, SIFT scores makes little sense as an actual measure of fitness, and is not interpretable in terms of population genetics.
     Contrarily, so-called mutation-selection codon models are rooted within a population genetics formalism\cite{halpern_evolutionary_1998, mccandlish_modeling_2014}.
-    These phylogenetic codon models can disentangle processes of mutation at the DNA level and selection at the amino-acid level.
-    Such codon models provide a nearly-neutral framework of evolution by estimating the fitness landscape over amino-acid sequences for each site of the sequence (fig~\ref{fig:method}A) while taking into account non-adaptive processes impacting codon frequency\cite{halpern_evolutionary_1998, rodrigue_mechanistic_2010, tamuri_estimating_2012}.
+    These phylogenetic codon models can disentangle processes of mutation at the DNA level and selection at the amino acid level.
+    Such codon models provide a nearly-neutral framework of evolution by estimating the fitness landscape over amino acid sequences for each site of the sequence (fig~\ref{fig:method}A) while taking into account non-adaptive processes impacting codon frequency\cite{halpern_evolutionary_1998, rodrigue_mechanistic_2010, tamuri_estimating_2012}.
     %Only nearly-neutral mutations between high fitness amino acids will tend to be permitted by the model, allowing for the explicit calculation of the scaled selection coefficient of non-synonymous mutations between codons.
@@
             Integrating divergence and polymorphism.
-            At the phylogenetic level (panel A), the amino-acid Wrightian fitness for each site is estimated from protein-coding DNA alignments using mutation-selection codon models.
-            At the population-genetic level (panel B), for each observed single nucleotide polymorphism (SNP) segregating in the population, selection coefficient are computed as the difference in amino-acid fitness between the ancestral and derived variants.
+            At the phylogenetic level (panel A), the amino acid Wrightian fitness for each site is estimated from protein-coding DNA alignments using mutation-selection codon models.
+            At the population-genetic level (panel B), for each observed single nucleotide polymorphism (SNP) segregating in the population, selection coefficient are computed as the difference in amino acid fitness between the ancestral and derived variants.
         }
@@
 
-    To answer these questions, we estimated the fitness landscape of amino-acid for long-term evolution using available multiple sequence alignments between mammalian species\cite{ranwez_orthomam_2007, howe_ensembl_2021}.
+    To answer these questions, we estimated the fitness landscape of amino acid for long-term evolution using available multiple sequence alignments between mammalian species\cite{ranwez_orthomam_2007, howe_ensembl_2021}.
     We developed a pipeline to integrate data at the phylogenetic and population scale to estimate divergence and polymorphism, respectively, across the entire exome for 28 populations from 6 genera (\textit{Equus},  \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus} and \textit{Homo}; fig.~\ref{fig:method}A\&B).
@@
 
-    For each non-synonymous SNP observed at the population level, we predicted its scaled selection coefficient ($\Sphy$) from amino-acid fitnesses estimated at the mammalian scale (fig.~\ref{fig:method}B).
+    For each non-synonymous SNP observed at the population level, we predicted its scaled selection coefficient ($\Sphy$) from amino acid fitnesses estimated at the mammalian scale (fig.~\ref{fig:method}B).
     Then we ask whether the variants that are supposedly advantageous are showing signatures of short term positive selection.
@@
     Hybrid mutation-selection and $\omega$-based codon models could provide a way forward\cite{brevet_reconstructing_2021}.
-    Moreover, SIFT scores based on amino-acid alignments across species have also been found to be informative of the selection pressure exerted at the population scale\cite{chen_hunting_2021}.
+    Moreover, SIFT scores based on amino acid alignments across species have also been found to be informative of the selection pressure exerted at the population scale\cite{chen_hunting_2021}.
     Accordingly, our study shows that sites with a higher SIFT score at the phylogenetic scale are more positively selected in the different populations (supp.\ mat\  section SIFT scores).
@@
     We analyzed the phylogenetic level data using mutation-selection models.
-These models assume that the protein-coding sequence are at mutation-selection balance under a fixed fitness landscape characterized by a fitness vector over the $20$ amino-acid at each site\cite{yang_mutationselection_2008, halpern_evolutionary_1998, rodrigue_mechanistic_2010}.
+These models assume that the protein-coding sequence are at mutation-selection balance under a fixed fitness landscape characterized by a fitness vector over the $20$ amino acid at each site\cite{yang_mutationselection_2008, halpern_evolutionary_1998, rodrigue_mechanistic_2010}.
     Mathematically, the rate of non-synonymous substitution from codon $a$ to codon $b$ ($q_{a \mapsto b}^{(i)}$) at site $i$ of the sequence is equal to the rate of mutation of the underlying nucleotide change ($\mu_{a \mapsto b}$) multiplied by the scaled probability of fixation of the mutation ($\proba_{a \mapsto b}^{(i)}$).
-    The probability of fixation depends on the difference of scaled fitness of the amino-acid encoded by the mutated codon ($F_b^{(i)}$) and the amino-acid encoded by the original codon ($F_a^{(i)}$) at site $i$\cite{wright_evolution_1931, fisher_genetical_1930}.
+    The probability of fixation depends on the difference of scaled fitness of the amino acid encoded by the mutated codon ($F_b^{(i)}$) and the amino acid encoded by the original codon ($F_a^{(i)}$) at site $i$\cite{wright_evolution_1931, fisher_genetical_1930}.
     The rate of substitution from codon $a$ to $b$ at a site $i$ is thus:
@@
     \end{equation}
-    Fitting the mutation-selection model on a sequence alignment leads to an estimation of the mutation rate matrix ($\UniDimArray{\mu}$) as well as the 20 amino-acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$.
+    Fitting the mutation-selection model on a sequence alignment leads to an estimation of the mutation rate matrix ($\UniDimArray{\mu}$) as well as the 20 amino acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$.
     The selection coefficient for a mutation from codon $a$ to codon $b$ at site $i$ is defined :
@@
     We ran the Bayesian software \href{https://github.com/bayesiancook/bayescode}{BayesCode} on each protein-coding DNA alignment\cite{lartillot_phylobayes_2013, rodrigue_detecting_2017, rodrigue_bayesian_2021}.
-    We ran a Markov chain Monte-Carlo (MCMC) analysis during $2000$ generations, with a burn-in period of $1000$ generations, to obtain posterior mean estimates of the amino-acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$\@.
+    We ran a Markov chain Monte-Carlo (MCMC) analysis during $2000$ generations, with a burn-in period of $1000$ generations, to obtain posterior mean estimates of the amino acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$\@.
 
@@
     We considered \textit{Ceratotherium simum simum} as \textit{Equus caballus} sister species; \textit{Bison bison bison} as \textit{Bos taurus} sister species; \textit{Pantholops hodgsonii} as \textit{Ovis aries} sister species; \textit{Pantholops hodgsonii} as \textit{Capra Hircus} sister species; \textit{Macaca mulatta} as \textit{Chlorocebus sabaeus} sister species and finally we considered \textit{Pan troglodytes} as \textit{Homo sapiens} sister species.
-    The selection coefficient ($\Sphy$) of each substitution is then obtained by comparing the difference in amino-acid fitnesses for each polarized non-synonymous codon substitution, by referring to the site-specific fitness profile obtained in the phylogeny-based method (see~\ref{subsec:s-phylogeny-method}).
+    The selection coefficient ($\Sphy$) of each substitution is then obtained by comparing the difference in amino acid fitnesses for each polarized non-synonymous codon substitution, by referring to the site-specific fitness profile obtained in the phylogeny-based method (see~\ref{subsec:s-phylogeny-method}).
     Finally, the rate of non-synonymous over synonymous substitution for a given class of selection coefficient ($\Sphyclass$) is computed as:

### 2022-09-15 manuscript/main.tex
Added conditional probabilities

@@
 \newcommand{\PdivAdv}{\proba \left[ \divAdv \right]}
-
+\newcommand{\given}{\mid}
 \newcommand{\Spop}{\beta}
@@
 
-\title{In mammals, 20 to 40\% of advantageous mutations are restoring damaged genomes instead of creating adaptive innovations}
+\title{In mammals, an important proportion of advantageous mutations are repairing damaged genomes instead of creating adaptive innovations}
 
@@
         While adaptive evolution acts as a diversifying force, maintenance positive selection stabilizes phenotypes and reduces diversity across species.
-        By leveraging polymorphism data in 28 populations and divergence data between 94 mammalian species, we estimate that 20 to 40\% of all new advantageous mutations are under maintenance positive selection.
+        By leveraging polymorphism data in 28 populations and divergence data between 94 mammalian species, we estimate that around 25\% of observed substitutions are owed to maintenance positive selection.
         Our work confirms that deleterious substitutions have accumulated in mammals and are currently being compensated for, resulting in widespread positive selection that is not adaptive evolution.
@@
     However, this method has two major shortcomings.
-    First, we know that a lot of mechanisms can influence amino acid frequency other than fitness (phylogeny, mutation biases, GC-biased gene conversion, mutational paths) which are not accounted for in SIFT.
-    Second, SIFT scores makes little sense as an actual measure of fitness, and is not interpretable in terms of population genetics.
+    First, we know that a lot of mechanisms can influence amino acid frequency other than fitness (phylogeny, mutation biases, GC-biased gene conversion, mutational paths) which are not accounted for in SIFT\@.
+    Second, SIFT scores is not interpretable as a selection coefficient.
     Contrarily, so-called mutation-selection codon models are rooted within a population genetics formalism\cite{halpern_evolutionary_1998, mccandlish_modeling_2014}.
@@
     Such codon models provide a nearly-neutral framework of evolution by estimating the fitness landscape over amino acid sequences for each site of the sequence (fig~\ref{fig:method}A) while taking into account non-adaptive processes impacting codon frequency\cite{halpern_evolutionary_1998, rodrigue_mechanistic_2010, tamuri_estimating_2012}.
-    %Only nearly-neutral mutations between high fitness amino acids will tend to be permitted by the model, allowing for the explicit calculation of the scaled selection coefficient of non-synonymous mutations between codons.
-    As a consequence, by integrating datasets at the species and population level, we can estimate the selection coefficient for each mutation currently segregating in a population.
+    From the fitness landscape obtained by fitting the model to the data, one can thus compute the scaled selection coefficient ($\Sphy$) of any non-synonymous mutations.
+    Importantly, mutation-selection assume that the underlying fitness landscape is stable along the phylogeny (as in fig.~\ref{fig:fitness-landscape}B), thus a mutation with a positive $\Sphy$ would be driving the current site toward a fitter amino-acid, and such mutation is effectively considered under maintenance positive selection.
+
+    By integrating datasets at the species and population level, we can predict $\Sphy$ for each mutation currently segregating in a population (fig~\ref{fig:method}B).
     Such a dataset can allow us to address different questions regarding positive selection affecting protein-coding DNA sequences.
-    Which proportion of the segregating polymorphisms are predicted to be positively selected, from a suboptimal to a more optimal amino acid?
-    Are these polymorphisms actually under ongoing positive selection at the scale of populations?
-    Finally, how much of the recent substitutions are due to maintenance positive selection?
+    Which proportion of the segregating polymorphisms in population are predicted toward a more optimal amino acid (positive $\Sphy$), thus supposedly under maintenance positive selection?
+    Are these polymorphisms effectively under positive selection at the scale of populations?
+    Finally, how much of positive selection observed in populations is due to maintenance positive selection?
+    To answer these questions, we estimated the fitness landscape of amino acid for long-term evolution using available multiple sequence alignments between mammalian species\cite{ranwez_orthomam_2007, howe_ensembl_2021}.
+    We then integrated data at the phylogenetic and population scale to estimate divergence and polymorphism, respectively, across the entire exome for 28 populations from 6 genera (\textit{Equus},  \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus} and \textit{Homo}; fig.~\ref{fig:method}A\&B).
 
@@
             At the phylogenetic scale (panel C), this phenomena promotes phenotype diversification across species.
-            Under a static fitness landscape (panel B), the protein sequence only fluctuates at the mutation-selection balance.
+            Under a stable fitness landscape (panel B), the protein sequence only fluctuates at the mutation-selection balance.
             All the mutations reaching fixation are either slightly deleterious and reaching fixation due to drift or are advantageous and restoring a more optimal amino acid.
@@
             At the phylogenetic level (panel A), the amino acid Wrightian fitness for each site is estimated from protein-coding DNA alignments using mutation-selection codon models.
-            At the population-genetic level (panel B), for each observed single nucleotide polymorphism (SNP) segregating in the population, selection coefficient are computed as the difference in amino acid fitness between the ancestral and derived variants.
+            At the population-genetic level (panel B), for each observed single nucleotide polymorphism (SNP) segregating in the population, selection coefficient ($\Sphy$) are computed as the difference in amino acid fitness between the ancestral and derived variants.
+            Mutation-selection codon models that the underlying fitness landscape is stable along the phylogeny, taking into account only non-adaptive evolution, thus a mutation with a positive $\Sphy$ would be driving the current site toward are fitter amino-acid, and such mutation are effectively considered under maintenance positive selection.
         }
@@
 
-    To answer these questions, we estimated the fitness landscape of amino acid for long-term evolution using available multiple sequence alignments between mammalian species\cite{ranwez_orthomam_2007, howe_ensembl_2021}.
-    We developed a pipeline to integrate data at the phylogenetic and population scale to estimate divergence and polymorphism, respectively, across the entire exome for 28 populations from 6 genera (\textit{Equus},  \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus} and \textit{Homo}; fig.~\ref{fig:method}A\&B).
-
     \subsection*{SNPs which are predicted to be advantageous are positively selected at the population scale}
@@
     For each non-synonymous SNP observed at the population level, we predicted its scaled selection coefficient ($\Sphy$) from amino acid fitnesses estimated at the mammalian scale (fig.~\ref{fig:method}B).
-    Then we ask whether the variants that are supposedly advantageous are showing signatures of short term positive selection.
+    Then we ask whether the variants that are predicted to be advantageous, thus supposedly under maintenance selection, are showing signatures of short term positive selection.
     For example, if a variant is found to be fixed in many mammals but not in ancestral humans, and a mutation in humans is toward the mammalian version, is this mutation advantageous for the individual carrying it?
-    At the population level (e.g.
-in humans of Asian descent in fig.~\ref{fig:homo-afr-results}), we divided all observed SNPs in 5 classes of predicted selection coefficient: severely deleterious with $\divStrongDel$, deleterious with $\divDel$, weakly deleterious with $\divWeakDel$, weakly advantageous with $\divWeakAdv$ and advantageous with $\divAdv$ (fig.~\ref{fig:homo-afr-results}B).
+    At the population level (e.g.~in humans of Asian descent in fig.~\ref{fig:homo-afr-results}), we divided all observed SNPs in 5 classes of predicted selection coefficient: severely deleterious with $\divStrongDel$, deleterious with $\divDel$, weakly deleterious with $\divWeakDel$, weakly advantageous with $\divWeakAdv$ and advantageous with $\divAdv$ (fig.~\ref{fig:homo-afr-results}B).
     In each of theses classes, SNPs are then grouped by the number of derived alleles in the population (fig.~\ref{fig:homo-afr-results}C), generating a so called site-frequency spectrum (SFS).
@@
     We found that SNPs predicted to be deleterious given their selection coefficient $\Sphy$ across mammals are effectively purged at the population-genetic scale, demonstrating that purifying selection is largely predictable and amino acids with low fitness across mammals are effectively purged away in each population.
-    Notably, SNPs predicted to be advantageous given their selection coefficient $\Sphy$ are indeed under positive selection at the population-genetic scale, confirming that there is a local ongoing selection towards amino acids that are restoring the optimally functioning protein.
+    Notably, SNPs predicted to be advantageous given their selection coefficient $\Sphy$, thus supposedly under maintenance selection, are indeed under positive selection at the population-genetic scale, confirming that there is a local ongoing selection towards amino acids that are restoring the optimally functioning protein.
     In between these two extremes, mutations predicted to be weakly selected (cyan and orange in fig.~\ref{fig:homo-afr-results}) are effectively composed of neutral, positively and negatively selected mutations.
@@
     However, mutations predicted to be weakly advantageous ($\divWeakAdv$) are composed of a mix of neutral and selected mutations with varying proportions across the different populations (orange row in fig.~\ref{fig:heatmap}B).
-    Similarly, mutations predicted to be advantageous are found to be positively selected with varying proportions across populations (red row in fig.~\ref{fig:heatmap}C).
+    Similarly, mutations predicted to be advantageous ($\divAdv$, under maintenance selection) are found to be positively selected with varying proportions across populations (red row in fig.~\ref{fig:heatmap}C).
+    In other words, mutations predicted to be deleterious by the mutation-selection model are effectively purified away in any population, while mutations predicted to be advantageous can be either neutral or advantageous depending on the population.
     These variable proportions between populations can be explained by the effective number of individuals in the population ($\Ne$), a major driver of selection efficacy.
-    Since $\Ne$ is not directly measurable, a reasonable proxy usually used is the synonymous diversity (see material and methods).
+    Since $\Ne$ is not directly measurable, a reasonable proxy usually used is the within a population (Watterson $\theta_w$).
     We thus ordered populations by their levels of synonymous diversity (fig.~\ref{fig:diversity}A) and confirmed that higher synonymous diversity is typically accompanied by a smaller proportion of neutral mutations.
@@
     Alternatively stated, mutations in populations with low diversity (e.g.~\textit{Homo}) are effectively nearly-neutral and behave as would a neutral mutation.
+    This result is qualitatively in accordance with the nearly-neutral theory of evolution which argues that mutations are less efficiently selected for in small populations.
     %, especially for mutations already predicted to be nearly-neutral at the phylogenetic scale (fig~S8-S9).
-    This result is qualitatively in accordance with the nearly-neutral theory of evolution which argues that mutations are less efficiently selected for in small populations.
 
@@
     In these populations, we show that out of all polarized substitutions in the branches, between 10 and 17\% of all substitutions have an $\Sphy > 1$ (table S1) and between 22 and 42\% of all substitutions have an $\Sphy > 0$ (table S2).
-    Most importantly, there is clear signal that the substitutions with an $\Sphy > 1$ have been positively selected since their ratio of non-synonymous over synonymous divergence, a ratio called $\dnds$, is between 1.05 and 1.81 in the different populations (table S1), meaning that mutations with $\Sphy > 1$ reach fixation more frequently that synonymous mutations (supposedly neutral).
+    Most importantly, there is clear signal that the substitutions with an $\Sphy > 1$ have been positively selected since their ratio of non-synonymous over synonymous divergence, a ratio called $\dnds$, is between 1.05 and 1.81 in the different populations (table S1), meaning that mutations under maintenance selection with $\Sphy > 1$ reach fixation more frequently that synonymous mutations (supposedly neutral).
+    These observed substitutions are likely to have been positively selected because they restored a more optimal state, not because they are driving innovations to a new environment or a new function.
     %This also means that the ratio $\dnds$ usually used to detect adaptation while relying on substitutions between close species\cite{mcdonald_adaptative_1991, galtier_adaptive_2016} or at the phylogenetic scale\cite{goldman_codonbased_1994, yang_codonsubstitution_2002} is overestimated.
-    These observed substitutions are likely to have been positively selected because they restored a more optimal state, not because they are driving innovations to a new environment or a new function.
 
-    \subsection*{A large proportion of advantageous mutations are non-adaptive}
+    \subsection*{A large proportion of advantageous mutations are under maintenance selection}
 
-    We then tried to estimate the proportion of restoring mutations among advantageous ones.
-    Since adaptation does not fit the fitness predictions, the proportion of adaptive mutation is expected to be the same among SNPs which are predicted to be advantageous, and among SNPs which are predicted to be deleterious.
-    Thus the proportion of advantageous mutations among SNPs which are predicted to be deleterious directly correspond to the proportion of all mutations which are adaptive.
-    So if we divide the proportion of mutations which are predicted to be advantageous among supposedly deleterious SNPs by the proportion of mutations which are predicted to be advantageous among all SNPs, we directly get the proportion of mutations which are adaptive among advantageous ones.
-    It results that 20 to 40\% of advantageous mutations are due to maintenance positive selection (fig~\ref{fig:diversity}B \& table S2).
+    We then sought to estimate the proportion of positive selection that is due to maintenance selection.
+    Mathematically, this corresponds to $\mathbb{P} [ \Sphy > 1  \given  \Spop > 1]$, namely the probability for a mutation to be due to maintenance selection, given it is positively selected.
+    This probability is given by Bayes formula (see methods), given we have access to $\mathbb{P} [ \Sphy > 1 ]$, $\mathbb{P} [ \Spop > 1 ]$, $\mathbb{P} [ \Spop > 1  \given  \Sphy > 1]$.
+    First, $\mathbb{P} [ \Sphy > 1 ]$ the probability for a mutation away from the ancestral sequence to have $\Sphy > 1$ (red fill of histogram in fig~\ref{fig:homo-afr-results}A and table S2).
+    Second, $\mathbb{P} [ \Spop > 1 ]$ is is the part of the DFE estimated at the population-scale greater than 1 when we used all the SNPs available in the population (black fill in fig~\ref{fig:diversity}A and table S2).
+    Finally, $\mathbb{P} [ \Spop > 1  \given  \Sphy > 1]$ is the part of the DFE estimated at the population-scale greater than 1, when we restricted our analysis on SNPs that are already predicted by mutation-selection models to have a selection coefficient greater than 1 (black fill for the category $\Sphy > 1$ in fig~\ref{fig:homo-afr-results}D and table S2).
+    Altogether, the probability for a mutation to be restoring the genome given that it is positively selected is obtained for each population, and varies between 4 and 24\% (table S2).
+    % Since adaptation does not fit the fitness predictions, the proportion of adaptive mutation is expected to be the same among SNPs which are predicted to be advantageous, and among SNPs which are predicted to be deleterious.
+    % Thus the proportion of advantageous mutations among SNPs which are predicted to be deleterious directly correspond to the proportion of all mutations which are adaptive.
+    % So if we divide the proportion of mutations which are predicted to be advantageous among supposedly deleterious SNPs by the proportion of mutations which are predicted to be advantageous among all SNPs, we directly get the proportion of mutations which are adaptive among advantageous ones.
+    % It results that 20 to 40\% of advantageous mutations are due to maintenance positive selection (fig~\ref{fig:diversity}B \& table S2).
 
-    In a similar way, we can consider that the total $\dnds$ encompasses the rate of evolution of deleterious, restoring and adaptive substitutions.
-    Then, the $\dnds$ computed exclusively on non-synonymous sites with a $\Sphy < 0$ only represent the rate of evolution of solely deleterious and adaptive substitutions, discarding the restoring substitutions by construction.
-    Thus, if we divide the $\dnds$ estimated on all substitutions, by the one estimated only on substitutions predicted to be deleterious, we directly get the proportion of the rate of evolution which is due to maintenance positive selection.
-    This way, we estimated that between 20 and 25\% of the evolutionary rate is due to maintenance positive selection (fig~\ref{fig:diversity}C \& table S2).
+    Focusing on substitutions in the terminal lineages, we can consider that the total $\dnds$ encompasses the rate of evolution for deleterious and advantageous (both adaptive and non-adaptive) substitutions.
+    Then, the $\dnds$ computed exclusively on non-synonymous sites with a $\Sphy < 0$ only represent the rate of evolution of solely deleterious and adaptive substitutions, discarding maintenance selection by construction.
+    Thus, if we divide the $\dnds$ estimated on all substitutions, by the one estimated only on substitutions predicted to be deleterious, we directly get the proportion of the rate of evolution which is contributed by maintenance selection (see methods).
+    This way, we estimated that between 20 and 25\% of the evolutionary rate is due to maintenance positive selection (fig~\ref{fig:diversity}C \& table S3).
 
-    Interestingly, the proportion of restoring mutations among advantageous ones and the proportion of the rate of evolution explained by maintenance positive selection do not show a clear relationship with the synonymous diversity (a proxy for the effective population size) (fig.~\ref{fig:diversity}B and C).
-    Indeed, the relationship between $\Ne$ and the proportion of restoring mutations is not trivial and should highly depend on time scales.
-    A population which experienced a high long term $\Ne$ in the past is supposed to be closer to the optimal state (under a stable fitness landscape), and should not leave much space for restoring mutations.
-    On the other hand a high short term $\Ne$ will induce more extreme fitness effects and a larger proportion of otherwise effectively neutral restoring mutations will be positively selected, thus increasing the proportion of restoring mutations.
-    Overall, the proportion of restoring mutations is expected to be more dependent on effective population size contraction or expansion rather than on the short term effective population size captured by the synonymous diversity.
+    Interestingly, the proportion of maintenance selection among advantageous ones and the proportion of the rate of evolution explained by maintenance positive selection do not show a clear relationship with the synonymous diversity within a population (Watterson $\theta_w$), a proxy for the effective population size (fig.~\ref{fig:diversity}B and C).
+    Indeed, the relationship between $\Ne$ and the proportion of maintenance selection is not trivial and should highly depend on time scales.
+    A population which experienced a high long term $\Ne$ in the past is supposed to be closer to the optimal state (under a stable fitness landscape), and should not leave much space for maintenance selection.
+    On the other hand a high short term $\Ne$ will induce more extreme fitness effects and a larger proportion of mutations will be positively selected (otherwise effectively neutral), thus increasing the proportion of maintenance selection.
+    Overall, the proportion of maintenance selection is expected to be more dependent on effective population size contraction or expansion rather than on the short term effective population size captured by the synonymous diversity.
 
@@
             Panel A: Histogram of predicted selection coefficients ($\Sphy$) for all possible mutations away from the ancestral human genome, giving the number of sites ($L$, in y-axis) across the genome with a given $\Sphy$.
-            Mutations are divided into 5 classes: severely deleterious (blue), deleterious (green), weakly deleterious (light green), weakly advantageous (yellow) and advantageous (red).
+            Mutations are divided into 5 classes: severely deleterious (blue), deleterious (green), weakly deleterious (light green), weakly advantageous (yellow) and advantageous (red, supposedly under maintenance selection).
             Panel B. Histogram of predicted selection coefficients ($\Sphy$) for all observed mutations in a sample of 8 individuals (out of 512 in the original dataset) of African descent.
@@
             Panel A.
-For each population, the proportion of advantageous ($p_+=\PpolyAdv$), nearly-neutral ($\PpolyNeutral$) and of deleterious ($\PpolyDel$) mutations estimated at the population-genetic scale using all SNPs available.
+For each population, the proportion of advantageous ($\PpolyAdv$), nearly-neutral ($\PpolyNeutral$) and of deleterious ($\PpolyDel$) mutations estimated at the population-genetic scale using all SNPs available.
             Population are sorted for increased synonymous diversity.
             Panel B.
-$R(p_+)=\dfrac{p_+ - p_+(\Sphy < 0)}{p_+}$ is the fraction of non-adaptive advantageous mutations, $p_+$ is compared to its estimation when we had removed all the restoring mutations $p_+(\Sphy < 0)$.
-            $R(p_+)$ (y-axis) is shown as a function of the synonymous diversity (Watterson $\theta_w$ in x-axis).
+Probability for a mutation to be due to maintenance positive selection, given it is positively selected ($\mathbb{P} [ \Sphy > 1  \given  \Spop > 1]$ in y-axis), shown as a function of the synonymous diversity (Watterson $\theta_w$ in x-axis).
             Panel C.
-$R(\dnds)=\dfrac{\dnds - \dn(\Sphy < 0) / \ds}{\dnds}$ is the fraction of divergence ($\dnds$) that is due to maintenance positive selection, where $\dnds$ is compared to the estimated divergence when we removed the restoring substitutions $\dn(\Sphy < 0)/\ds$.
+$R(\dnds)=\dfrac{\dnds - \dn(\Sphy < 0) / \ds}{\dnds}$ is the fraction of divergence ($\dnds$) that is due to maintenance positive selection, where $\dnds$ is compared to the estimated divergence when we removed maintenance selection $\dn(\Sphy < 0)/\ds$.
             $R(\dn)$ (y-axis) is shown as a function of the synonymous diversity (Watterson $\theta_w$ in x-axis).
@@
     However, we so far assumed no changes in effective population size while it has been established that population size changes have a major effect on selection dynamics\cite{lanfear_population_2014, jones_shifting_2017, platt_protein_2018}.
-    Estimating effective population sizes along with fitness landscapes is possible\cite{latrille_inferring_2021}, but is, for the moment, too computational intensive to be performed genome-wide\cite{latrille_inferring_2021}.
+    Mutation-selection models with changes in effective population sizes along the phylogeny have been developed\cite{latrille_inferring_2021}, but are, for the moment, too computational intensive to be performed genome-wide.
     Hybrid mutation-selection and $\omega$-based codon models could provide a way forward\cite{brevet_reconstructing_2021}.
@@
     Biologically, another mechanism which generate maintenance positive selection is compensatory mutations, which are repairing damage caused by deleterious mutations at another site in the genome and generating a widespread signal of non-adaptive positive selection\cite{hartl_compensatory_1996, pollock_strong_2014, starr_epistasis_2016}.
-    In our study we focused on mutations restoring the more optimal ancestral state at a given site, not accounting for compensatory mutations since we assumed a model of fitness landscape without epistasis, providing a reasonable estimate of average fitness profiles\cite{youssef_consequences_2020}.
+    In our study we focused on mutations toward a more optimal amino-acid at a given site, not accounting for compensatory mutations since we assumed a model of fitness landscape without epistasis.
+    These models without epistasis provide a reasonable estimate of average fitness profiles\cite{youssef_consequences_2020}.
     But most importantly, we argue that our estimation of the amount of maintenance positive selection is an underestimation, and that accounting for compensatory mutations by means of epistasis would mechanically increase that amount.
@@
     On the contrary, pervasive epistasis generates the opposite, an entrenchment\cite{goldstein_evolutionary_2004, goldstein_nonadaptive_2015} resulting in a slowing down of the rate evolution\cite{rodrigue_detecting_2017, patel_epistasis_2022} or a standstill\cite{youssef_evolution_2022}.
-    In other words, under pervasive epistasis, finding empirical evidence for restoring mutations is harder since restoring mutations become less and less likely to occur over time\cite{goldstein_nonadaptive_2015, goldstein_sequence_2017, park_epistatic_2022}.
-    Our study thus shows that restoring mutations should not be overlooked, and we argue that both restoring and compensatory mutations play an important role in preventing our genome from collapsing under a mutation load.
+    In other words, under pervasive epistasis, finding empirical evidence for maintenance selection is harder since restoring mutations become less and less likely to occur over time\cite{goldstein_nonadaptive_2015, goldstein_sequence_2017, park_epistatic_2022}.
+    Our study thus shows that maintenance selection should not be overlooked, and we argue that both maintenance selection and compensatory mutations play an important role in preventing our genome from collapsing under a mutation load.
 
@@
     From a structural biology perspective, we have found that proteins are not optimal for their fitness, which has been proved for their kinetics and thermodynamics\cite{taverna_why_2002, goldstein_evolution_2011}.
-    We argue that mutation-selection models are thus a mandatory tool in evolutionary biology to detect and quantify adaptation since they genuinely take into account the tug-of-war between scarce advantageous mutations likely to reach fixation and a bulk of deleterious mutations eventually reaching fixation due to their sheer mass.
-    Indeed, these models can be used as a null model to predict the expected rate of evolution of proteins\cite{spielman_relationship_2015, dosreis_how_2015} under a stable fitness landscape.
+    Philosophically, our distinction between maintenance selection and adaptation can appear to be rather far-fetched and not biologically motivated, and one can argue that maintenance selection is adaptation to its own deteriorating genome.
+    However, we argue that this distinction is important when we seek to detect adaptation, and is actually not an encumbrance but rather a strength.
+    Indeed, mutation-selection models are genuinely take into account the tug-of-war between scarce advantageous mutations likely to reach fixation and a bulk of deleterious mutations eventually reaching fixation due to their sheer mass.
+    These models can thus be used as a null model to predict the expected rate of evolution of proteins\cite{spielman_relationship_2015, dosreis_how_2015} under a stable fitness landscape.
     A departure from this model indicates that proteins are evolving under a changing fitness landscape\cite{rodrigue_detecting_2017, tamuri_mutationselection_2021} and is a signal of pervasive adaptive evolution\cite{rodrigue_bayesian_2021} or of pervasive epistasis\cite{rodrigue_detecting_2017}.
+    As such, a stable fitness landscape as a null model is thus statistically more powerful than assuming that the null model is neutral.
+    Altogether, mutation-selection models is a mandatory tool in evolutionary biology to detect and quantify adaptation, as it lowers the bar to detect adaptation.
 
@@
     Genes located on the X, Y chromosomes and the mitochondrial genome were discarded from the analysis, because the level of polymorphism, which is necessary in the population-based analyses, is expected to be different in these three genomic regions.
-    Sequences of species for which we used poppulation-level polymorphism (see below), as well as their sister species, were removed from the analysis to ensure independence between the data used in the phylogenetic and population genetic scale.
+    Sequences of species for which we used population-level polymorphism (see below), as well as their sister species, were removed from the analysis to ensure independence between the data used in the phylogenetic and population genetic scale.
     Altogether, we analyzed $14,509$ protein-coding DNA sequences for at most $87$ sequences of placental mammals.
@@
     In the manuscript and the following material, the source ($a$) and target ($b$) codons as well as the site ($i$) are implicit and thus never explicitly written.
-    We ran the Bayesian software \href{https://github.com/bayesiancook/bayescode}{BayesCode} on each protein-coding DNA alignment\cite{lartillot_phylobayes_2013, rodrigue_detecting_2017, rodrigue_bayesian_2021}.
+    We ran the Bayesian software \textit{BayesCode} (\url{https://github.com/ThibaultLatrille/bayescode}) on each protein-coding DNA alignment\cite{rodrigue_bayesian_2021}.
     We ran a Markov chain Monte-Carlo (MCMC) analysis during $2000$ generations, with a burn-in period of $1000$ generations, to obtain posterior mean estimates of the amino acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$\@.
@@
     \begin{align}
-        p_+ = \PpolyAdv &= p_b \int_{1}^{+\infty} f_{e}(\Spop; \Spop_b) \der \Spop,  \\
+        \PpolyAdv &= p_b \int_{1}^{+\infty} f_{e}(\Spop; \Spop_b) \der \Spop,  \label{eq:polyProbaAdv} \\
         \PpolyNeutral &= p_b \int_{0}^{1} f_{e}(\Spop; \Spop_b) \der \Spop + \left( 1 - p_b \right) \int_{0}^{1} f_{\Gamma}(\Spop; -\Spop_d, b) \der \Spop, \\
-        \PpolyDel &= \left( 1 - p_b \right) \int_{1}^{+\infty} f_{\Gamma}(\Spop; -\Spop_d, b) \der \Spop.
+        \PpolyDel &= \left( 1 - p_b \right) \int_{1}^{+\infty} f_{\Gamma}(\Spop; -\Spop_d, b) \der \Spop. \label{eq:polyProbaDel}
     \end{align}
 
-    PolyDFE required one SFS for non-synonymous mutations and one for synonymous mutations (neutral expectation), as well as the total mutation rate (i.e.~mutation rate per site multiplied by the number of sites) on which each SFS has been sampled.
+    PolyDFE required one SFS for non-synonymous mutations and one for synonymous mutations (neutral expectation), as well as the number of sites on which each SFS has been sampled.
     We performed the following four-step procedure to obtain the number of sites for each SFS.
@@
     If a SNP is still segregating in the population, the ancestral version of the SNP is used.
-    However, if the derived allele is shared by all individuals in the population, the allele is considered fixed and the derived allele of the SNP is used instead.
+    However, if the derived allele is shared by all individuals in the population, the allele is considered fixed and the derived allele of the SNP is used as the ancestral.
     Second, from this reconstructed ancestral sequence, all possible mutations were computed, weighted by the mutation rate between nucleotide ($\mu$), which was estimated at the phylogenetic scale.
@@
 $\Sphyclass = \divAdv$).
-    Fourth, the number of sites ($L$) for each class of selection coefficient ($\Sphyclass$) was finally computed as the total number of sites across the genome ($L_{tot}$) weighted by the ratio of the aggregated mutations rates falling in the class ($\mu\left( \Sphyclass \right)$) over the total mutation rate for all possible mutations:
+    Fourth, the number of sites ($L \left( \Sphyclass \right)$) for each class of selection coefficient ($\Sphyclass$) was finally computed as the total number of sites across the genome ($L_{tot}$) weighted by the ratio of the aggregated mutations rates falling in the class ($\mu\left( \Sphyclass \right)$) over the total mutation rate for all possible mutations ($\mu_{tot}$) as:
     \begin{align}
-        L_{\textrm{non-syn}} \left( \Sphyclass \right) &= L_{tot} \frac{\mu\left( \Sphyclass \right)}{\mu_{tot}}, \\
+        L \left( \Sphyclass \right) &= L_{tot} \frac{\mu\left( \Sphyclass \right)}{\mu_{tot}}, \\
         L_{\textrm{syn}} &= L_{tot} \frac{\mu_{\textrm{syn}}}{\mu_{tot}}.
     \end{align}
-    From the SFS and the number of sites $L$ for both the synonymous and non-synonymous classes, polyDFE estimated the parameters of the DFE $\phi \left( \Spop; \Spop_d , b, p_b, \Spop_b \right)$ using maximum likelihood.
 
-    The fraction of non-adaptive advantageous mutations $R(p_+)$ was computed as the ratio between the difference in the numbers of advantageous mutations ($p_+$), which were due to maintenance positive selection, and the estimated divergence when we removed the restoring substitutions $p_+(\Sphy < 0)$, over $p_+$.
+    Altogether, for each class of selection ($\Sphyclass$) of non-synonymous SNPs (or for all SNPs), we thus estimated the parameters of the DFE $\left( \Spop; \Spop_d , b, p_b, \Spop_b \right)$ using maximum likelihood with polyDFE from the number of sites and the SFS obtained by aggregating all the SNPs in the selection class.
+    Once fitted to the data, the parameters of the DFE $\left( \Spop; \Spop_d , b, p_b, \Spop_b \right)$ are used to compute $\PpolyAdv$, $\PpolyNeutral$, $\PpolyDel$ using eq.~\ref{eq:polyProbaAdv}-\ref{eq:polyProbaDel}.
+
+    From Bayes theorem, it is now possible to obtain the amount of positive selection due to maintenance selection.
+    In other words, we seek to get the probability that a mutation is repairing the genome ($\divAdv$) given that it is advantageous ($\polyAdv$), as:
     \begin{equation}
-        R(p_+)=\dfrac{p_+ - p_+(\Sphy < 0)}{p_+}
+        \proba \left[\divAdv \given \polyAdv\right] = \frac{\proba \left[\polyAdv \given \divAdv\right] \times \proba\left[\divAdv\right]}{\PpolyAdv},
+        \label{eq:bayes}
+    \end{equation}
+    where $\PpolyAdv$ is computed from all SNPS, $\proba \left[\polyAdv \given \divAdv\right]$ is obtained from the set of SNPs in the class $\Sphyclass = \divAdv$, and $\proba\left[\divAdv\right]$ is the probability for a new mutation to be inside the class $\divAdv$, thus computed as:
+    \begin{equation}
+        \proba\left[\divAdv\right] = \frac{\mu\left( \Sphyclass = \divAdv \right)}{\mu_{tot}},
+        \label{eq:proba-dfe-mutsel}
     \end{equation}
@@
     \begin{align}
-        \dn \left( \Sphyclass \right) &= \dfrac{D_{\textrm{non-syn}}\left( \Sphyclass \right)}{L_{\textrm{non-syn}} \left( \Sphyclass \right)}, \\
+        \dn \left( \Sphyclass \right) &= \dfrac{D\left( \Sphyclass \right)}{L \left( \Sphyclass \right)}, \\
         \ds &= \dfrac{D_{\textrm{syn}}}{L_{\textrm{syn}}},
     \end{align}
-    where $D_{\textrm{non-syn}} \left( \Sphyclass \right) $ is the number of non-synonymous substitutions in the class $\Sphyclass$, $D_{\textrm{syn}}$ is the number of synonymous substitutions across the genome, while $L_{\textrm{non-syn}} \left( \Sphyclass \right)$ and $L_{\textrm{syn}}$ are the number of non-synonymous and synonymous sites as defined in the previous section.
+    where $D \left( \Sphyclass \right) $ is the number of non-synonymous substitutions in the class $\Sphyclass$, $D_{\textrm{syn}}$ is the number of synonymous substitutions across the genome, while $L \left( \Sphyclass \right)$ and $L_{\textrm{syn}}$ are the number of non-synonymous and synonymous sites as defined in the previous section.
+    The fraction of non-adaptive advantageous substitutions $R(\dnds)$ was computed as the ratio between the difference in the numbers of advantageous substitutions ($\dnds$), which were due to maintenance positive selection, and the estimated divergence when we removed maintenance selection $\dn (\Sphy < 0) / \ds$, over $\dnds$.
     Of note, the quantities $R(\dn)$ and $R(\dnds)$ are equivalent due to simplification of the factor $\ds$:
-    \begin{align}
-        R(\dnds) &= \dfrac{\dnds - \dn(\Sphy < 0) / \ds}{\dnds} = \dfrac{\dn - \dn(\Sphy < 0)}{\dn} = R(\dn) \\
-        &= 1 - \dfrac{ L_{\textrm{non-syn}} \cdot D_{\textrm{non-syn}}\left( \Sphyclass \right) }{ D_{\textrm{non-syn}} \cdot L_{\textrm{non-syn}} \left( \Sphyclass \right)}
-    \end{align}
+    \begin{equation}
+        R(\dnds) = \dfrac{\dnds - \dn(\Sphy < 0) / \ds}{\dnds} = \dfrac{\dn - \dn(\Sphy < 0)}{\dn} = R(\dn)
+    \end{equation}
 

### 2022-09-15 manuscript/supp-mat.tex
Figure labels in Supp. Mat.
N. Salamin corrections
Added conditional probabilities

@@
 
+\renewcommand{\thetable}{S\arabic{table}}
+\renewcommand{\thefigure}{S\arabic{figure}}
+
 \newcommand{\UniDimArray}[1]{\bm{#1}}
@@
     \normalsize $^{1}$Université de Lausanne, Lausanne, Switzerland\\
-    \normalsize $^{2}$Université de Lyon, Lyon, France \\
+    \normalsize $^{2}$Université de Lyon, CNRS, LBBE UMR 5558, Villeurbanne, France \\
     \normalsize \texttt{\href{mailto:thibault.latrille@ens-lyon.org}{thibault.latrille@ens-lyon.org}} \\
 }
+
+\date{}
 
@@
     \subsection{Summary tables}\label{subsec:summary-table-mutsel}
+
+    \begin{center}
+        \captionof{table}{~}
+        \scriptsize
+        \begin{longtable*}{|l|l|r|r|r|}
+            \toprule
+            Population & Species & Tajima $\theta_{\pi}$ & $\mathbb{P}_{div}[\Sphy > 1]$ & $\dn(\Sphy > 1) / \ds$ \\
+            \midrule
+            \endhead
+            \midrule
+            \multicolumn{5}{r}{{Continued on next page}} \\
+            \midrule
+            \endfoot
+
+            \bottomrule
+            \endlastfoot
+            Equus c. & Equus caballus & $ 0.002$ & $ 0.115$ & $ 1.187$ \\
+            Iran & Bos taurus & $ 0.005$ & $ 0.125$ & $ 1.322$ \\
+            Uganda & Bos taurus & $ 0.006$ & $ 0.126$ & $ 1.363$ \\
+            Australia & Capra hircus & $ 0.003$ & $ 0.122$ & $ 1.035$ \\
+            France & Capra hircus & $ 0.004$ & $ 0.122$ & $ 1.043$ \\
+            Iran (C. aegagrus) & Capra hircus & $ 0.004$ & $ 0.123$ & $ 1.042$ \\
+            Iran & Capra hircus & $ 0.004$ & $ 0.124$ & $ 1.052$ \\
+            Italy & Capra hircus & $ 0.004$ & $ 0.122$ & $ 1.037$ \\
+            Morocco & Capra hircus & $ 0.004$ & $ 0.124$ & $ 1.057$ \\
+            Iran & Ovis aries & $ 0.008$ & $ 0.104$ & $ 1.180$ \\
+            Iran (O. orientalis) & Ovis aries & $ 0.009$ & $ 0.103$ & $ 1.187$ \\
+            Iran (O. vignei) & Ovis aries & $ 0.008$ & $ 0.104$ & $ 1.172$ \\
+            Various & Ovis aries & $ 0.009$ & $ 0.103$ & $ 1.182$ \\
+            Morocco & Ovis aries & $ 0.008$ & $ 0.104$ & $ 1.189$ \\
+            Barbados & Chlorocebus sabaeus & $ 0.004$ & $ 0.123$ & $ 1.341$ \\
+            Central Afr. Rep. & Chlorocebus sabaeus & $ 0.006$ & $ 0.124$ & $ 1.370$ \\
+            Ethiopia & Chlorocebus sabaeus & $ 0.005$ & $ 0.124$ & $ 1.361$ \\
+            Gambia & Chlorocebus sabaeus & $ 0.005$ & $ 0.124$ & $ 1.359$ \\
+            Kenya & Chlorocebus sabaeus & $ 0.006$ & $ 0.125$ & $ 1.371$ \\
+            Nevis & Chlorocebus sabaeus & $ 0.004$ & $ 0.124$ & $ 1.349$ \\
+            South Africa & Chlorocebus sabaeus & $ 0.007$ & $ 0.126$ & $ 1.391$ \\
+            Saint Kitts & Chlorocebus sabaeus & $ 0.004$ & $ 0.125$ & $ 1.362$ \\
+            Zambia & Chlorocebus sabaeus & $ 0.006$ & $ 0.124$ & $ 1.362$ \\
+            African & Homo sapiens & $ 0.003$ & $ 0.104$ & $ 1.475$ \\
+            Admixed American & Homo sapiens & $ 0.002$ & $ 0.103$ & $ 1.466$ \\
+            East Asian & Homo sapiens & $ 0.002$ & $ 0.104$ & $ 1.478$ \\
+            European & Homo sapiens & $ 0.002$ & $ 0.103$ & $ 1.461$ \\
+            South Asian & Homo sapiens & $ 0.002$ & $ 0.104$ & $ 1.473$ \\
+        \end{longtable*}
+    \end{center}
+    \begin{itemize}
+        \item Tajima $\theta$ is the synonymous diversity.
+        \item $\mathbb{P}_{div}[\Sphy > 1]$ is the proportion of substitutions in the terminal branch observed with a selection coefficient at the phylogenetic scale larger than 1 ($\Sphy > 1$).
+        \item $\dn(\Sphy > 1) / \ds$ is the ratio of non-synonymous over synonymous divergence (also called $\dnds$) estimated for the non-synonymous substitutions in the terminal branch with a selection coefficient larger than 1 ($\Sphy > 1$).
+    \end{itemize}
+
+    \newpage
     \begin{center}
@@
             \toprule
-            Population           & Species             & Tajima $\theta$ & $\mathbb{P} [ \Spop > 1 ]$ & $\mathbb{P}_{mut}[\Sphy > 1]$ & $\mathbb{P} [ \Spop > 1  | \Sphy > 1]$ & $\mathbb{P}_{div}[\Sphy > 1]$ & $\dn(\Sphy > 1) / \ds$ \\
+            Population & Species & Tajima $\theta_{\pi}$ & $\mathbb{P}[\Sphy > 1]$ & $\mathbb{P} [ \Spop > 1 ]$ & $\frac{\mathbb{P}[\Sphy > 1]}{\mathbb{P}[ \Spop > 1 ]}$ & $\mathbb{P} [ \Spop > 1 \given \Sphy > 1]$ & $\mathbb{P}[\Sphy > 1\given \Spop > 1 ]$ \\
             \midrule
@@
             \endlastfoot
-            Equus c.
-& Equus caballus      & $ 0.002$        & $ 0.042$                   & $ 0.018$                      & $ 0.404$                             & $ 0.115$                      & $ 1.197$           \\
-            Iran                 & Bos taurus          & $ 0.005$        & $ 0.036$                   & $ 0.017$                      & $ 0.368$                             & $ 0.125$                      & $ 1.322$           \\
-            Uganda               & Bos taurus          & $ 0.006$        & $ 0.035$                   & $ 0.017$                      & $ 0.369$                             & $ 0.126$                      & $ 1.363$           \\
-            Australia            & Capra hircus        & $ 0.003$        & $ 0.036$                   & $ 0.017$                      & $ 0.144$                             & $ 0.122$                      & $ 1.035$           \\
-            France               & Capra hircus        & $ 0.004$        & $ 0.034$                   & $ 0.017$                      & $ 0.168$                             & $ 0.122$                      & $ 1.043$           \\
-            Iran (C.
-aegagrus)   & Capra hircus        & $ 0.004$        & $ 0.035$                   & $ 0.017$                      & $ 0.093$                             & $ 0.123$                      & $ 1.042$           \\
-            Iran                 & Capra hircus        & $ 0.004$        & $ 0.030$                   & $ 0.017$                      & $ 0.140$                             & $ 0.124$                      & $ 1.052$           \\
-            Italy                & Capra hircus        & $ 0.004$        & $ 0.032$                   & $ 0.017$                      & $ 0.150$                             & $ 0.122$                      & $ 1.037$           \\
-            Morocco              & Capra hircus        & $ 0.004$        & $ 0.029$                   & $ 0.017$                      & $ 0.137$                             & $ 0.124$                      & $ 1.057$           \\
-            Iran                 & Ovis aries          & $ 0.008$        & $ 0.022$                   & $ 0.018$                      & $ 0.046$                             & $ 0.104$                      & $ 1.180$           \\
-            Iran (O.
-orientalis) & Ovis aries          & $ 0.009$        & $ 0.025$                   & $ 0.018$                      & $ 0.071$                             & $ 0.103$                      & $ 1.187$           \\
-            Iran (O.
-vignei)     & Ovis aries          & $ 0.008$        & $ 0.028$                   & $ 0.018$                      & $ 0.220$                             & $ 0.104$                      & $ 1.172$           \\
-            Various              & Ovis aries          & $ 0.009$        & $ 0.024$                   & $ 0.018$                      & $ 0.108$                             & $ 0.103$                      & $ 1.182$           \\
-            Morocco              & Ovis aries          & $ 0.008$        & $ 0.020$                   & $ 0.018$                      & $ 0.070$                             & $ 0.104$                      & $ 1.189$           \\
-            Barbados             & Chlorocebus sabaeus & $ 0.004$        & $ 0.040$                   & $ 0.015$                      & $ 0.374$                             & $ 0.123$                      & $ 1.341$           \\
-            Central Afr. Rep.    & Chlorocebus sabaeus & $ 0.006$        & $ 0.034$                   & $ 0.015$                      & $ 0.368$                             & $ 0.124$ & $ 1.370$ \\
-            Ethiopia             & Chlorocebus sabaeus & $ 0.005$        & $ 0.040$                   & $ 0.015$                      & $ 0.368$                             & $ 0.124$                      & $ 1.361$           \\
-            Gambia               & Chlorocebus sabaeus & $ 0.005$        & $ 0.031$                   & $ 0.015$                      & $ 0.377$                             & $ 0.124$                      & $ 1.359$           \\
-            Kenya                & Chlorocebus sabaeus & $ 0.006$        & $ 0.035$                   & $ 0.015$                      & $ 0.308$                             & $ 0.125$                      & $ 1.371$           \\
-            Nevis                & Chlorocebus sabaeus & $ 0.004$        & $ 0.037$                   & $ 0.015$                      & $ 0.368$                             & $ 0.124$                      & $ 1.349$           \\
-            South Africa         & Chlorocebus sabaeus & $ 0.007$        & $ 0.034$                   & $ 0.015$                      & $ 0.368$                             & $ 0.126$                      & $ 1.391$           \\
-            Saint Kitts          & Chlorocebus sabaeus & $ 0.004$        & $ 0.039$                   & $ 0.015$                      & $ 0.368$                             & $ 0.125$                      & $ 1.362$           \\
-            Zambia               & Chlorocebus sabaeus & $ 0.006$        & $ 0.038$                   & $ 0.015$                      & $ 0.368$                             & $ 0.124$                      & $ 1.362$           \\
-            African              & Homo sapiens        & $ 0.003$        & $ 0.038$                   & $ 0.015$                      & $ 0.604$                             & $ 0.104$                      & $ 1.475$           \\
-            Admixed American     & Homo sapiens        & $ 0.002$        & $ 0.037$                   & $ 0.015$                      & $ 0.574$                             & $ 0.103$                      & $ 1.466$           \\
-            East Asian           & Homo sapiens        & $ 0.002$        & $ 0.036$                   & $ 0.015$                      & $ 0.484$                             & $ 0.104$                      & $ 1.478$           \\
-            European             & Homo sapiens        & $ 0.002$        & $ 0.037$                   & $ 0.015$                      & $ 0.517$                             & $ 0.103$                      & $ 1.461$           \\
-            South Asian          & Homo sapiens        & $ 0.002$        & $ 0.036$                   & $ 0.015$                      & $ 0.532$                             & $ 0.104$                      & $ 1.473$           \\
+            Equus c. & Equus caballus & $ 0.002$ & $ 0.018$ & $ 0.042$ & $ 0.443$ & $ 0.404$ & $ 0.179$ \\
+            Iran & Bos taurus & $ 0.005$ & $ 0.017$ & $ 0.036$ & $ 0.471$ & $ 0.368$ & $ 0.173$ \\
+            Uganda & Bos taurus & $ 0.006$ & $ 0.017$ & $ 0.035$ & $ 0.490$ & $ 0.369$ & $ 0.181$ \\
+            Australia & Capra hircus & $ 0.003$ & $ 0.017$ & $ 0.036$ & $ 0.488$ & $ 0.144$ & $ 0.070$ \\
+            France & Capra hircus & $ 0.004$ & $ 0.017$ & $ 0.034$ & $ 0.515$ & $ 0.168$ & $ 0.086$ \\
+            Iran (C. aegagrus) & Capra hircus & $ 0.004$ & $ 0.017$ & $ 0.035$ & $ 0.493$ & $ 0.093$ & $ 0.046$ \\
+            Iran & Capra hircus & $ 0.004$ & $ 0.017$ & $ 0.030$ & $ 0.589$ & $ 0.140$ & $ 0.083$ \\
+            Italy & Capra hircus & $ 0.004$ & $ 0.017$ & $ 0.032$ & $ 0.545$ & $ 0.150$ & $ 0.081$ \\
+            Morocco & Capra hircus & $ 0.004$ & $ 0.017$ & $ 0.029$ & $ 0.598$ & $ 0.137$ & $ 0.082$ \\
+            Iran & Ovis aries & $ 0.008$ & $ 0.018$ & $ 0.022$ & $ 0.802$ & $ 0.046$ & $ 0.037$ \\
+            Iran (O. orientalis) & Ovis aries & $ 0.009$ & $ 0.018$ & $ 0.025$ & $ 0.718$ & $ 0.071$ & $ 0.051$ \\
+            Iran (O. vignei) & Ovis aries & $ 0.008$ & $ 0.018$ & $ 0.028$ & $ 0.642$ & $ 0.220$ & $ 0.141$ \\
+            Various & Ovis aries & $ 0.009$ & $ 0.018$ & $ 0.024$ & $ 0.748$ & $ 0.108$ & $ 0.081$ \\
+            Morocco & Ovis aries & $ 0.008$ & $ 0.018$ & $ 0.020$ & $ 0.883$ & $ 0.070$ & $ 0.062$ \\
+            Barbados & Chlorocebus sabaeus & $ 0.004$ & $ 0.015$ & $ 0.040$ & $ 0.375$ & $ 0.374$ & $ 0.140$ \\
+            Central Afr. Rep. & Chlorocebus sabaeus & $ 0.006$ & $ 0.015$ & $ 0.034$ & $ 0.435$ & $ 0.368$ & $ 0.160$ \\
+            Ethiopia & Chlorocebus sabaeus & $ 0.005$ & $ 0.015$ & $ 0.040$ & $ 0.377$ & $ 0.368$ & $ 0.139$ \\
+            Gambia & Chlorocebus sabaeus & $ 0.005$ & $ 0.015$ & $ 0.031$ & $ 0.482$ & $ 0.377$ & $ 0.182$ \\
+            Kenya & Chlorocebus sabaeus & $ 0.006$ & $ 0.015$ & $ 0.035$ & $ 0.428$ & $ 0.308$ & $ 0.132$ \\
+            Nevis & Chlorocebus sabaeus & $ 0.004$ & $ 0.015$ & $ 0.037$ & $ 0.404$ & $ 0.368$ & $ 0.149$ \\
+            South Africa & Chlorocebus sabaeus & $ 0.007$ & $ 0.015$ & $ 0.034$ & $ 0.435$ & $ 0.368$ & $ 0.160$ \\
+            Saint Kitts & Chlorocebus sabaeus & $ 0.004$ & $ 0.015$ & $ 0.039$ & $ 0.388$ & $ 0.368$ & $ 0.143$ \\
+            Zambia & Chlorocebus sabaeus & $ 0.006$ & $ 0.015$ & $ 0.038$ & $ 0.392$ & $ 0.368$ & $ 0.144$ \\
+            African & Homo sapiens & $ 0.003$ & $ 0.015$ & $ 0.038$ & $ 0.403$ & $ 0.604$ & $ 0.243$ \\
+            Admixed American & Homo sapiens & $ 0.002$ & $ 0.015$ & $ 0.037$ & $ 0.409$ & $ 0.574$ & $ 0.235$ \\
+            East Asian & Homo sapiens & $ 0.002$ & $ 0.015$ & $ 0.036$ & $ 0.426$ & $ 0.484$ & $ 0.206$ \\
+            European & Homo sapiens & $ 0.002$ & $ 0.015$ & $ 0.037$ & $ 0.414$ & $ 0.517$ & $ 0.214$ \\
+            South Asian & Homo sapiens & $ 0.002$ & $ 0.015$ & $ 0.036$ & $ 0.428$ & $ 0.532$ & $ 0.227$ \\
         \end{longtable*}
@@
         \item Tajima $\theta$ is the synonymous diversity.
-        \item $\mathbb{P} [ \Spop > 1 ]$ is the probability of $\Spop > 1$ estimated by polyDFE from all SNPs.
-        \item $\mathbb{P}_{mut}[\Sphy > 0]$ is the proportion of mutational opportunities with a predicted selection coefficient larger than 1 ($\Sphy > 1$).
-        \item $\mathbb{P} [ \Spop > 1  | \Sphy > 1]$ is the probability of $\Spop > 1$ estimated by polyDFE for SNPs with a predicted selection coefficient larger than 1 ($\Sphy > 1$).
-        \item $\mathbb{P}_{div}[\Sphy > 1]$ is the proportion of substitutions in the terminal branch observed with a selection coefficient at the phylogenetic scale larger than 1 ($\Sphy > 1$).
-        \item $\dn(\Sphy > 1) / \ds$ is the ratio of non-synonymous over synonymous divergence (also called $\dnds$) estimated for the non-synonymous substitutions in the terminal branch with a selection coefficient larger than 1 ($\Sphy > 1$).
+        \item $\mathbb{P} [ \Sphy > 1 ]$ is the probability for a new mutation to be under maintenance selection.
+        These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1 ($\Sphy > 1$), thus toward a more fit amino-acid.
+        In other words, this probability is the part of the DFE estimated by mutation-selection models greater than 1.
+        \item $\mathbb{P} [ \Spop > 1 ]$ is the probability for a mutation to be positively selected.
+        These mutations have a selection coefficient at the population-scale larger than 1 ($\Spop > 1$), estimated from all SNPs in the population.
+        In other words, this probability is the part of the DFE estimated by polyDFE greater than 1.
+        \item $\mathbb{P} [ \Spop > 1 \given \Sphy > 1]$ is the probability for a mutation to be positively selected, given it is under maintenance selection.
+        These mutations have a selection coefficient at the population-scale larger than 1 ($\Spop > 1$), estimated by polyDFE on the SNPs with a predicted selection coefficient larger than 1 ($\Sphy > 1$).
+        In other words, this probability is the part of the DFE estimated by polyDFE greater than 1, when we restricted our analysis on SNPs that are already predicted by mutation-selection models to have a selection coefficient greater than 1.
+        \item $\mathbb{P} [ \Sphy > 1 \given \Spop > 1]$ is the probability for a mutation to be under maintenance selection, given it is positively selected.
+        This probability is obtained using Bayes' formula.
     \end{itemize}
@@
     \newpage
+%    \begin{center}
+%        \captionof{table}{~}
+%        \scriptsize
+%        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
+%            \toprule
+%            Population & Species & Tajima $\theta_{\pi}$ & $\mathbb{P}[\Sphy > 0]$ & $\mathbb{P} [\Spop > 0 ]$ & $\frac{\mathbb{P}[\Sphy > 0]}{\mathbb{P}[\Spop > 0]}$ & $\mathbb{P} [\Spop > 0 \given \Sphy > 0]$ & $\mathbb{P}[\Sphy > 0|\Spop > 0]$ \\
+%            \midrule
+%            \endhead
+%            \midrule
+%            \multicolumn{8}{r}{{Continued on next page}} \\
+%            \midrule
+%            \endfoot
+%%
+%            \bottomrule
+%            \endlastfoot
+%            Equus c. & Equus caballus & $ 0.002$ & $ 0.054$ & $ 0.113$ & $ 0.473$ & $ 0.489$ & $ 0.231$ \\
+%            Iran & Bos taurus & $ 0.005$ & $ 0.053$ & $ 0.098$ & $ 0.540$ & $ 0.368$ & $ 0.198$ \\
+%            Uganda & Bos taurus & $ 0.006$ & $ 0.053$ & $ 0.094$ & $ 0.558$ & $ 0.419$ & $ 0.234$ \\
+%            Australia & Capra hircus & $ 0.003$ & $ 0.054$ & $ 0.096$ & $ 0.557$ & $ 0.126$ & $ 0.070$ \\
+%            France & Capra hircus & $ 0.004$ & $ 0.054$ & $ 0.092$ & $ 0.583$ & $ 0.297$ & $ 0.173$ \\
+%            Iran (C. aegagrus) & Capra hircus & $ 0.004$ & $ 0.054$ & $ 0.096$ & $ 0.561$ & $ 0.080$ & $ 0.045$ \\
+%            Iran & Capra hircus & $ 0.004$ & $ 0.054$ & $ 0.080$ & $ 0.667$ & $ 0.281$ & $ 0.188$ \\
+%            Italy & Capra hircus & $ 0.004$ & $ 0.054$ & $ 0.087$ & $ 0.617$ & $ 0.304$ & $ 0.187$ \\
+%            Morocco & Capra hircus & $ 0.004$ & $ 0.054$ & $ 0.079$ & $ 0.679$ & $ 0.131$ & $ 0.089$ \\
+%            Iran & Ovis aries & $ 0.008$ & $ 0.054$ & $ 0.060$ & $ 0.897$ & $ 0.304$ & $ 0.273$ \\
+%            Iran (O. orientalis) & Ovis aries & $ 0.009$ & $ 0.054$ & $ 0.067$ & $ 0.806$ & $ 0.345$ & $ 0.278$ \\
+%            Iran (O. vignei) & Ovis aries & $ 0.008$ & $ 0.054$ & $ 0.075$ & $ 0.720$ & $ 0.464$ & $ 0.334$ \\
+%            Various & Ovis aries & $ 0.009$ & $ 0.054$ & $ 0.064$ & $ 0.840$ & $ 0.359$ & $ 0.302$ \\
+%            Morocco & Ovis aries & $ 0.008$ & $ 0.054$ & $ 0.055$ & $ 0.971$ & $ 0.247$ & $ 0.240$ \\
+%            Barbados & Chlorocebus sabaeus & $ 0.004$ & $ 0.050$ & $ 0.109$ & $ 0.463$ & $ 0.350$ & $ 0.162$ \\
+%            Central Afr. Rep. & Chlorocebus sabaeus & $ 0.006$ & $ 0.050$ & $ 0.094$ & $ 0.537$ & $ 0.225$ & $ 0.121$ \\
+%            Ethiopia & Chlorocebus sabaeus & $ 0.005$ & $ 0.050$ & $ 0.108$ & $ 0.466$ & $ 0.312$ & $ 0.145$ \\
+%            Gambia & Chlorocebus sabaeus & $ 0.005$ & $ 0.050$ & $ 0.084$ & $ 0.602$ & $ 0.286$ & $ 0.172$ \\
+%            Kenya & Chlorocebus sabaeus & $ 0.006$ & $ 0.050$ & $ 0.095$ & $ 0.529$ & $ 0.196$ & $ 0.104$ \\
+%            Nevis & Chlorocebus sabaeus & $ 0.004$ & $ 0.050$ & $ 0.101$ & $ 0.500$ & $ 0.296$ & $ 0.148$ \\
+%            South Africa & Chlorocebus sabaeus & $ 0.007$ & $ 0.050$ & $ 0.094$ & $ 0.534$ & $ 0.243$ & $ 0.130$ \\
+%            Saint Kitts & Chlorocebus sabaeus & $ 0.004$ & $ 0.050$ & $ 0.106$ & $ 0.473$ & $ 0.309$ & $ 0.146$ \\
+%            Zambia & Chlorocebus sabaeus & $ 0.006$ & $ 0.050$ & $ 0.104$ & $ 0.485$ & $ 0.245$ & $ 0.119$ \\
+%            African & Homo sapiens & $ 0.003$ & $ 0.051$ & $ 0.103$ & $ 0.497$ & $ 0.785$ & $ 0.390$ \\
+%            Admixed American & Homo sapiens & $ 0.002$ & $ 0.051$ & $ 0.104$ & $ 0.492$ & $ 0.737$ & $ 0.363$ \\
+%            East Asian & Homo sapiens & $ 0.002$ & $ 0.051$ & $ 0.098$ & $ 0.521$ & $ 0.684$ & $ 0.356$ \\
+%            European & Homo sapiens & $ 0.002$ & $ 0.051$ & $ 0.097$ & $ 0.526$ & $ 0.687$ & $ 0.361$ \\
+%            South Asian & Homo sapiens & $ 0.002$ & $ 0.051$ & $ 0.096$ & $ 0.530$ & $ 0.691$ & $ 0.366$ \\
+%        \end{longtable*}
+%    \end{center}
+%    \begin{itemize}
+%        \item Tajima $\theta$ is the synonymous diversity.
+%        \item $\mathbb{P} [ \Sphy > 0 ]$ is the probability for a new mutation to be under maintenance selection.
+%        These mutations have a positive selection coefficient predicted at the phylogenetic-scale larger ($\Sphy > 0$), thus toward a more fit amino-acid.
+%        In other words, this probability is the positive part of the DFE estimated by mutation-selection models.
+%        \item $\mathbb{P} [ \Spop > 0 ]$ is the probability for a mutation to be positively selected.
+%        These mutations have a positive selection coefficient at the population-scale larger ($\Spop > 0$), estimated from all SNPs in the population.
+%        In other words, this probability is the positive part of the DFE estimated by polyDFE.
+%        \item $\mathbb{P} [ \Spop > 0 \given \Sphy > 0]$ is the probability for a mutation to be positively selected, given it is under maintenance selection.
+%        These mutations have a positive selection coefficient at the population-scale larger ($\Spop > 0$), estimated by polyDFE on the SNPs with a positive predicted selection coefficient ($\Sphy > 0$).
+%        In other words, this probability is the positive part of the DFE estimated by polyDFE, when we restricted our analysis on SNPs that are already predicted by mutation-selection models to have a positive selection coefficient.
+%        \item $\mathbb{P} [ \Sphy > 0 \given \Spop > 0]$ is the probability for a mutation to be under maintenance selection, given it is positively selected.
+%        This probability is obtained using Bayes' formula.
+%    \end{itemize}
     \begin{center}
@@
         \scriptsize
-        \begin{longtable*}{|l|l|r|r|r|r|r|r|r|r|}
+        \begin{longtable*}{|l|l|r|r|r|r|r|}
             \toprule
-            Population           & Species             & Tajima $\theta_{\pi}$ & $\mathbb{P}_{div}[\Sphy > 0]$ & $\dnds $ & $\dn(\Sphy < 0) / \ds$ & R($\dnds $) & $p_+ $ & $p_+(\Sphy < 0)$ & R($p_+ $) \\
+            Population & Species & Tajima $\theta_{\pi}$ & $\mathbb{P}_{div}[\Sphy > 0]$ & $\dnds $ & $\dn(\Sphy < 0) / \ds$ & R($\dnds $) \\
             \midrule
@@
             \midrule
-            \multicolumn{9}{r}{{Continued on next page}} \\
+            \multicolumn{7}{r}{{Continued on next page}} \\
             \midrule
@@
             \endlastfoot
-            Equus c.             & Equus caballus      & $ 0.002$              & $ 0.275$                      & $ 0.148$ & $ 0.113$     & $  23.4$      & $ 0.042$ & $ 0.030$ & $  28.5$ \\
-            Iran                 & Bos taurus          & $ 0.005$              & $ 0.274$                      & $ 0.130$ & $ 0.100$     & $  23.3$      & $ 0.036$ & $ 0.025$   & $  30.9$    \\
-            Uganda               & Bos taurus          & $ 0.006$              & $ 0.277$                      & $ 0.133$ & $ 0.101$     & $  23.6$      & $ 0.035$ & $ 0.023$   & $  33.7$    \\
-            Australia            & Capra hircus        & $ 0.003$              & $ 0.286$                      & $ 0.126$ & $ 0.095$     & $  24.6$      & $ 0.036$ & $ 0.026$ & $  26.8$ \\
-            France               & Capra hircus        & $ 0.004$              & $ 0.286$                      & $ 0.127$ & $ 0.096$     & $  24.6$      & $ 0.034$ & $ 0.025$ & $  26.7$ \\
-            Iran (C. aegagrus)   & Capra hircus        & $ 0.004$              & $ 0.285$                      & $ 0.126$ & $ 0.095$     & $  24.5$      & $ 0.035$ & $ 0.026$ & $  25.0$ \\
-            Iran                 & Capra hircus        & $ 0.004$              & $ 0.288$                      & $ 0.126$ & $ 0.095$     & $  24.8$      & $ 0.030$ & $ 0.020$   & $  31.8$    \\
-            Italy                & Capra hircus        & $ 0.004$              & $ 0.287$                      & $ 0.127$ & $ 0.096$     & $  24.6$      & $ 0.032$ & $ 0.022$   & $  30.6$    \\
-            Morocco              & Capra hircus        & $ 0.004$              & $ 0.288$                      & $ 0.126$ & $ 0.095$     & $  24.7$      & $ 0.029$ & $ 0.020$ & $  31.5$ \\
-            Iran                 & Ovis aries          & $ 0.008$              & $ 0.243$                      & $ 0.149$ & $ 0.120$     & $  20.0$      & $ 0.022$ & $ 0.014$   & $  36.5$    \\
-            Iran (O. orientalis) & Ovis aries          & $ 0.009$              & $ 0.241$                      & $ 0.151$ & $ 0.121$     & $  19.8$      & $ 0.025$ & $ 0.016$ & $  33.4$ \\
-            Iran (O. vignei)     & Ovis aries          & $ 0.008$              & $ 0.243$                      & $ 0.149$ & $ 0.119$     & $  20.0$      & $ 0.028$ & $ 0.019$ & $  30.5$ \\
-            Various              & Ovis aries          & $ 0.009$              & $ 0.240$                      & $ 0.151$ & $ 0.121$     & $  19.7$      & $ 0.024$ & $ 0.015$   & $  36.7$    \\
-            Morocco              & Ovis aries          & $ 0.008$              & $ 0.241$                      & $ 0.151$ & $ 0.121$     & $  19.7$      & $ 0.020$ & $ 0.013$   & $  38.0$    \\
-            Barbados             & Chlorocebus sabaeus & $ 0.004$              & $ 0.289$                      & $ 0.141$ & $ 0.106$     & $  25.1$      & $ 0.040$ & $ 0.030$ & $  25.3$ \\
-            Central Afr. Rep.    & Chlorocebus sabaeus & $ 0.006$              & $ 0.287$                      & $ 0.141$ & $ 0.106$     & $  24.9$ & $ 0.034$ & $ 0.026$ & $  24.7$ \\
-            Ethiopia             & Chlorocebus sabaeus & $ 0.005$              & $ 0.290$                      & $ 0.141$ & $ 0.105$     & $  25.2$      & $ 0.040$ & $ 0.030$ & $  25.0$ \\
-            Gambia               & Chlorocebus sabaeus & $ 0.005$              & $ 0.287$                      & $ 0.141$ & $ 0.106$     & $  25.0$      & $ 0.031$ & $ 0.021$ & $  31.8$ \\
-            Kenya                & Chlorocebus sabaeus & $ 0.006$              & $ 0.290$                      & $ 0.142$ & $ 0.106$     & $  25.2$      & $ 0.035$ & $ 0.026$ & $  24.9$ \\
-            Nevis                & Chlorocebus sabaeus & $ 0.004$              & $ 0.289$                      & $ 0.141$ & $ 0.106$     & $  25.1$      & $ 0.037$ & $ 0.028$ & $  23.6$ \\
-            South Africa         & Chlorocebus sabaeus & $ 0.007$              & $ 0.291$                      & $ 0.141$ & $ 0.105$     & $  25.4$      & $ 0.035$ & $ 0.025$ & $  27.7$ \\
-            Saint Kitts          & Chlorocebus sabaeus & $ 0.004$              & $ 0.290$                      & $ 0.141$ & $ 0.105$     & $  25.3$      & $ 0.039$ & $ 0.029$ & $  26.1$ \\
-            Zambia               & Chlorocebus sabaeus & $ 0.006$              & $ 0.288$                      & $ 0.141$ & $ 0.106$     & $  25.0$      & $ 0.038$ & $ 0.029$ & $  25.3$ \\
-            African              & Homo sapiens        & $ 0.003$              & $ 0.243$                      & $ 0.195$ & $ 0.156$     & $  20.2$      & $ 0.038$ & $ 0.026$ & $  32.4$ \\
-            Admixed American     & Homo sapiens        & $ 0.002$              & $ 0.242$                      & $ 0.195$ & $ 0.156$     & $  20.2$      & $ 0.038$ & $ 0.026$ & $  31.3$ \\
-            East Asian           & Homo sapiens        & $ 0.002$              & $ 0.244$                      & $ 0.195$ & $ 0.155$     & $  20.4$      & $ 0.036$ & $ 0.025$ & $  30.2$ \\
-            European             & Homo sapiens        & $ 0.002$              & $ 0.242$                      & $ 0.195$ & $ 0.156$     & $  20.1$      & $ 0.036$ & $ 0.025$ & $  30.9$ \\
-            South Asian          & Homo sapiens        & $ 0.002$              & $ 0.244$                      & $ 0.195$ & $ 0.156$     & $  20.3$      & $ 0.035$ & $ 0.024$ & $  31.7$ \\
+            Equus c. & Equus caballus & $ 0.002$ & $ 0.304$ & $ 0.190$ & $ 0.140$ & $ 26.4$ \\
+            Iran & Bos taurus & $ 0.005$ & $ 0.280$ & $ 0.181$ & $ 0.137$ & $ 24.0$ \\
+            Uganda & Bos taurus & $ 0.006$ & $ 0.284$ & $ 0.184$ & $ 0.139$ & $ 24.4$ \\
+            Australia & Capra hircus & $ 0.003$ & $ 0.301$ & $ 0.148$ & $ 0.109$ & $ 26.1$ \\
+            France & Capra hircus & $ 0.004$ & $ 0.301$ & $ 0.149$ & $ 0.110$ & $ 26.1$ \\
+            Iran (C. aegagrus) & Capra hircus & $ 0.004$ & $ 0.301$ & $ 0.148$ & $ 0.109$ & $ 26.1$ \\
+            Iran & Capra hircus & $ 0.004$ & $ 0.303$ & $ 0.148$ & $ 0.109$ & $ 26.4$ \\
+            Italy & Capra hircus & $ 0.004$ & $ 0.301$ & $ 0.149$ & $ 0.110$ & $ 26.1$ \\
+            Morocco & Capra hircus & $ 0.004$ & $ 0.303$ & $ 0.148$ & $ 0.109$ & $ 26.4$ \\
+            Iran & Ovis aries & $ 0.008$ & $ 0.241$ & $ 0.200$ & $ 0.160$ & $ 19.8$ \\
+            Iran (O. orientalis) & Ovis aries & $ 0.009$ & $ 0.239$ & $ 0.203$ & $ 0.163$ & $ 19.6$ \\
+            Iran (O. vignei) & Ovis aries & $ 0.008$ & $ 0.243$ & $ 0.199$ & $ 0.159$ & $ 20.0$ \\
+            Various & Ovis aries & $ 0.009$ & $ 0.239$ & $ 0.203$ & $ 0.163$ & $ 19.6$ \\
+            Morocco & Ovis aries & $ 0.008$ & $ 0.240$ & $ 0.202$ & $ 0.163$ & $ 19.7$ \\
+            Barbados & Chlorocebus sabaeus & $ 0.004$ & $ 0.302$ & $ 0.163$ & $ 0.120$ & $ 26.5$ \\
+            Central Afr. Rep. & Chlorocebus sabaeus & $ 0.006$ & $ 0.304$ & $ 0.165$ & $ 0.121$ & $ 26.7$ \\
+            Ethiopia & Chlorocebus sabaeus & $ 0.005$ & $ 0.304$ & $ 0.164$ & $ 0.120$ & $ 26.7$ \\
+            Gambia & Chlorocebus sabaeus & $ 0.005$ & $ 0.303$ & $ 0.164$ & $ 0.120$ & $ 26.6$ \\
+            Kenya & Chlorocebus sabaeus & $ 0.006$ & $ 0.304$ & $ 0.164$ & $ 0.120$ & $ 26.7$ \\
+            Nevis & Chlorocebus sabaeus & $ 0.004$ & $ 0.303$ & $ 0.163$ & $ 0.120$ & $ 26.6$ \\
+            South Africa & Chlorocebus sabaeus & $ 0.007$ & $ 0.306$ & $ 0.164$ & $ 0.120$ & $ 26.9$ \\
+            Saint Kitts & Chlorocebus sabaeus & $ 0.004$ & $ 0.305$ & $ 0.163$ & $ 0.120$ & $ 26.8$ \\
+            Zambia & Chlorocebus sabaeus & $ 0.006$ & $ 0.303$ & $ 0.164$ & $ 0.120$ & $ 26.7$ \\
+            African & Homo sapiens & $ 0.003$ & $ 0.259$ & $ 0.216$ & $ 0.169$ & $ 21.9$ \\
+            Admixed American & Homo sapiens & $ 0.002$ & $ 0.258$ & $ 0.216$ & $ 0.169$ & $ 21.8$ \\
+            East Asian & Homo sapiens & $ 0.002$ & $ 0.259$ & $ 0.217$ & $ 0.169$ & $ 22.0$ \\
+            European & Homo sapiens & $ 0.002$ & $ 0.258$ & $ 0.216$ & $ 0.169$ & $ 21.8$ \\
+            South Asian & Homo sapiens & $ 0.002$ & $ 0.259$ & $ 0.216$ & $ 0.169$ & $ 21.9$ \\
         \end{longtable*}
@@
         \item $\dn(\Sphy < 0) / \ds$ is the ratio of non-synonymous over synonymous divergence estimated for the non-synonymous substitutions in the terminal branch with a selection coefficient lower than 0 ($\Sphy < 0$).
-        This is the estimated divergence when we removed the restoring substitutions.
-        \item $R(\dnds)=\dfrac{\dnds - \dn(\Sphy < 0) / \ds}{\dnds}$ is the fraction of the divergence ($\dnds$) that is over-estimated, $\dnds$ is compared to the estimated divergence when we removed the restoring substitutions $\dn(\Sphy < 0) / \ds$.
-        \item $p_+=\PpolyAdv$ is the probability for a new mutation to be advantageous, estimated (with polyDFE) using all available polymorphism.
-        \item $p_+(\Sphy < 0)$ is the probability for a new mutation to be advantageous, estimated (with polyDFE) using polymorphism with a selection coefficient lower than 0 ($\Sphy < 0$).
-        This is the estimated probability for a new mutation to be advantageous when we removed the restoring polymorphism from the dataset.
-        \item $R(p_+)=\dfrac{p_+ - p_+(\Sphy < 0)}{p_+}$ is the fraction of the probability for a new mutation to be advantageous ($p_+$) that is over-estimated, $p_+$ is compared to its estimation when we had removed all the restoring mutations $p_+(\Sphy < 0)$.
+        This is the estimated divergence when we removed maintenance selection.
+        \item $R(\dnds)=\dfrac{\dnds - \dn(\Sphy < 0) / \ds}{\dnds}$ is the fraction of the divergence ($\dnds$) that is over-estimated, $\dnds$ is compared to the estimated divergence when we removed maintenance selection $\dn(\Sphy < 0) / \ds$.
     \end{itemize}
@@
     We estimated that between 20 and 25\% of $\dnds$ is over-estimated ($R(\dnds)$), corresponding to maintenance positive selection exerted on substitutions.
-    Moreover, we estimated that between 24 and 38\% of $p_+$ is over-estimated ($R(p_+)$), corresponding to maintenance positive selection exerted on segregating mutations.
     Altogether, in a nearly neutral framework, genomes could be viewed as the arena of a tug-of-war between a large volume of deleterious mutations that eventually reach fixation due to drift, and scarce advantageous mutations that are restoring a more optimal ancestral state.
@@
         \item $\ \proba [ \polyNeutral ]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) between -1 and 1, estimated for the whole genome.
-        \item $\ \proba [ \polyNeutral | \divWeakDel]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) between -1 and 1, estimated of SNPs observed with a selection coefficient at the phylogenetic scale ($\Sphy$) between -1 and 0.
-        \item $\ \proba [ \polyNeutral | \divWeakAdv ]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) between -1 and 1, estimated of SNPs observed with a selection coefficient at the phylogenetic scale ($\Sphy$) between 0 and 1.
+        \item $\ \proba [ \polyNeutral \given \divWeakDel]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) between -1 and 1, estimated of SNPs observed with a selection coefficient at the phylogenetic scale ($\Sphy$) between -1 and 0.
+        \item $\ \proba [ \polyNeutral \given \divWeakAdv ]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) between -1 and 1, estimated of SNPs observed with a selection coefficient at the phylogenetic scale ($\Sphy$) between 0 and 1.
     \end{itemize}
@@
         \item $\ \proba [ \polyDel ]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) lower than -1, estimated for the whole genome.
-        \item $\ \proba [ \polyDel | \divDel]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) lower than -1, estimated of SNPs observed with a selection coefficient at the phylogenetic scale ($\Sphy$) between -3 and -3.
-        \item $\ \proba [ \polyDel | \divStrongDel ]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) lower than -1, estimated of SNPs observed with a selection coefficient at the phylogenetic scale ($\Sphy$) lower than -3.
+        \item $\ \proba [ \polyDel \given \divDel]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) lower than -1, estimated of SNPs observed with a selection coefficient at the phylogenetic scale ($\Sphy$) between -3 and -3.
+        \item $\ \proba [ \polyDel \given \divStrongDel ]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) lower than -1, estimated of SNPs observed with a selection coefficient at the phylogenetic scale ($\Sphy$) lower than -3.
     \end{itemize}
@@
     \begin{itemize}
-        \item $\ p_+ = \proba [ \polyAdv  ]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) greater than 1, estimated for the whole genome.
-        \item $\ p_+( \divAdv) = \proba [ \polyAdv | \divAdv] $ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) greater than 1, estimated of SNPs observed with a selection coefficient at the phylogenetic scale ($\Sphy$) greater than 1.
+        \item $ \proba [ \polyAdv ]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) greater than 1, estimated for the whole genome.
+        \item $\proba [ \polyAdv \given \divAdv] $ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) greater than 1, estimated of SNPs observed with a selection coefficient at the phylogenetic scale ($\Sphy$) greater than 1.
     \end{itemize}
@@
     \newpage
+
     \section{SIFT scores}\label{sec:sift-scores}
@@
     \subsection{Proportion of selected mutations}\label{subsec:proportion-of-selected-mutations}
-    For each population, the proportion of advantageous ($p_+=\PpolyAdv$), nearly-neutral ($\PpolyNeutral$) and of deleterious ($\PpolyDel$) mutations estimated at the population-genetic scale is shown.
+    For each population, the proportion of advantageous ($\PpolyAdv$), nearly-neutral ($\PpolyNeutral$) and of deleterious ($\PpolyDel$) mutations estimated at the population-genetic scale is shown.
     Estimation is performed with SNPs with different class of SIFT scores at the phylogenetic scale.
@@
 
-    \subsection{Summary table}\label{subsec:summary-table-sift-scores}
-    \begin{center}
-        \captionof{table}{~}
-        \footnotesize
-        \begin{longtable}{|l|l|r|r|r|r|}
-            \toprule
-            Population           & Species             & Tajima $\theta_{\pi}$ & $p_+$    & $p_+ (\textrm{SIFT} < 0.8)$ & R($p_+$) \\
-            \midrule
-            \endhead
-            \midrule
-            \multicolumn{6}{r}{{Continued on next page}} \\
-            \midrule
-            \endfoot
+    % The previous section showed that mutations with a higher SIFT score at the phylogenetic scale are more positively selected in the different populations.
+    % However, whenever we removed the category of SNPs with the highest SIFT score ($\textrm{SIFT} \geq 0.8$), we expected the estimation of $p_+ (\textrm{SIFT} < 0.8)$ to be lower than $p_+$ (estimated on the all dataset), as we have shown that $p_+ (\Sphy < 0) < p_+$ with mutation-selection codon models.
+    % Thus SIFT scores are not providing reliable information on the current selective strength exerted on mutations, at least for high SIFT scores.
+    % Moreover, there is no defined threshold (here we arbitrarily used 0.8) to cut-off between advantageous and deleterious changes.
 
-            \bottomrule
-            \endlastfoot
-            Equus c.             & Equus caballus      & $ 0.002$              & $ 0.042$ & $ 0.037$                    & $  12.2$   \\
-            Iran                 & Bos taurus          & $ 0.005$              & $ 0.036$ & $ 0.031$                    & $  14.7$   \\
-            Uganda               & Bos taurus          & $ 0.006$              & $ 0.035$ & $ 0.029$                    & $  16.2$   \\
-            Australia            & Capra hircus        & $ 0.003$              & $ 0.036$ & $ 0.032$                    & $ 9.214$ \\
-            France               & Capra hircus        & $ 0.004$              & $ 0.034$ & $ 0.034$                    & $-1.445$ \\
-            Iran (C. aegagrus)   & Capra hircus        & $ 0.004$              & $ 0.035$ & $ 0.032$                    & $ 9.881$ \\
-            Iran                 & Capra hircus        & $ 0.004$              & $ 0.030$ & $ 0.026$                    & $  12.3$   \\
-            Italy                & Capra hircus        & $ 0.004$              & $ 0.032$ & $ 0.029$                    & $ 8.754$ \\
-            Morocco              & Capra hircus        & $ 0.004$              & $ 0.029$ & $ 0.025$                    & $  12.7$   \\
-            Iran                 & Ovis aries          & $ 0.008$              & $ 0.022$ & $ 0.019$                    & $  12.9$   \\
-            Iran (O. orientalis) & Ovis aries          & $ 0.009$              & $ 0.025$ & $ 0.021$                    & $  13.6$   \\
-            Iran (O. vignei)     & Ovis aries          & $ 0.008$              & $ 0.028$ & $ 0.024$                    & $  14.2$   \\
-            Various              & Ovis aries          & $ 0.009$              & $ 0.024$ & $ 0.019$                    & $  19.0$   \\
-            Morocco              & Ovis aries          & $ 0.008$              & $ 0.020$ & $ 0.017$                    & $  14.4$   \\
-            Barbados             & Chlorocebus sabaeus & $ 0.004$              & $ 0.040$ & $ 0.037$                    & $ 7.660$ \\
-            Central Afr. Rep.    & Chlorocebus sabaeus & $ 0.006$              & $ 0.034$ & $ 0.032$                    & $ 7.610$ \\
-            Ethiopia             & Chlorocebus sabaeus & $ 0.005$              & $ 0.040$ & $ 0.037$                    & $ 7.464$ \\
-            Gambia               & Chlorocebus sabaeus & $ 0.005$              & $ 0.031$ & $ 0.028$                    & $ 9.891$ \\
-            Kenya                & Chlorocebus sabaeus & $ 0.006$              & $ 0.035$ & $ 0.033$                    & $ 6.180$ \\
-            Nevis                & Chlorocebus sabaeus & $ 0.004$              & $ 0.037$ & $ 0.035$                    & $ 6.532$ \\
-            South Africa         & Chlorocebus sabaeus & $ 0.007$              & $ 0.034$ & $ 0.031$                    & $ 8.924$ \\
-            Saint Kitts          & Chlorocebus sabaeus & $ 0.004$              & $ 0.039$ & $ 0.036$                    & $ 7.642$ \\
-            Zambia               & Chlorocebus sabaeus & $ 0.006$              & $ 0.039$ & $ 0.035$                    & $ 8.197$ \\
-            African              & Homo sapiens        & $ 0.003$              & $ 0.038$ & $ 0.032$                    & $  17.1$   \\
-            Admixed American     & Homo sapiens        & $ 0.002$              & $ 0.039$ & $ 0.033$                    & $  14.9$   \\
-            East Asian           & Homo sapiens        & $ 0.002$              & $ 0.036$ & $ 0.033$                    & $ 9.250$ \\
-            European             & Homo sapiens        & $ 0.002$              & $ 0.036$ & $ 0.033$                    & $ 8.704$ \\
-            South Asian          & Homo sapiens        & $ 0.002$              & $ 0.036$ & $ 0.032$                    & $ 9.853$ \\
-        \end{longtable}
-
-    \end{center}
-    \begin{itemize}
-        \item Tajima $\theta$ is the synonymous diversity.
-        \item $p_+=\PpolyAdv$ is the probability for a new mutation to be advantageous, estimated (with polyDFE) using all available polymorphism.
-        \item $p_+ (\textrm{SIFT} < 0.8)$ is the probability for a new mutation to be advantageous, estimated (with polyDFE) using polymorphism with a SIFT lower than 0.8 ($SIFT < 0.8$).
-        This is the estimated probability for a new mutation to be advantageous when we removed the restoring polymorphism from the dataset.
-        \item $R(p_+)=\dfrac{p_+ - p_+ (\textrm{SIFT} < 0.8)}{p_+}$ is the fraction of the probability for a new mutation to be advantageous ($p_+$) that is over-estimated, $p_+$ is compared to its estimation when we had removed all the restoring mutations $p_+ (\textrm{SIFT} < 0.8)$.
-    \end{itemize}
-
-    The previous section showed that mutations with a higher SIFT score at the phylogenetic scale are more positively selected in the different populations.
-    However, whenever we removed the category of SNPs with the highest SIFT score ($\textrm{SIFT} \geq 0.8$), we expected the estimation of $p_+ (\textrm{SIFT} < 0.8)$ to be lower than $p_+$ (estimated on the all dataset), as we have shown that $p_+ (\Sphy < 0) < p_+$ with mutation-selection codon models.
-    Thus SIFT scores are not providing reliable information on the current selective strength exerted on mutations, at least for high SIFT scores.
-    Moreover, there is no defined threshold (here we arbitrarily used 0.8) to cut-off between advantageous and deleterious changes.
-
-    \newpage
     \section{SIFT scores: histograms and SFS for each population}\label{sec:sift-scores:-histograms-and-sfs-for-each-population}

### 2022-09-15 copy_artworks.sh

@@ -17,5 +17,6 @@
 \cp -rf ./experiments/5bins-polyDFE-mC/regression-MutSel/results.watterson.all_P-Ssup0.scatter.pdf  ./manuscript/artworks/scatter.watterson.allSNPs.P-Ssup0.pdf
 \cp -rf ./experiments/5bins-polyDFE-mC/regression-MutSel/results.watterson.all_P-Sinf0.scatter.pdf  ./manuscript/artworks/scatter.watterson.allSNPs.P-Sinf0.pdf
 \cp -rf ./experiments/5bins-polyDFE-mC/regression-MutSel/results.watterson.all_P-Seq0.scatter.pdf  ./manuscript/artworks/scatter.watterson.allSNPs.P-Seq0.pdf
+\cp -rf ./experiments/5bins-polyDFE-mC/regression-MutSel/results.watterson.bayes_P-Ssup0_P-pos.scatter.pdf ./manuscript/artworks/scatter.watterson.Bayes.pdf
 \cp -rf ./experiments/2bins-polyDFE-mC/regression-MutSel/results.watterson.ratio_neg_P-Ssup0.scatter.pdf ./manuscript/artworks/scatter.watterson.R_p+.pdf
 \cp -rf ./experiments/2bins-polyDFE-mC/regression-MutSel/results.watterson.ratio_neg_omega_div.scatter.pdf ./manuscript/artworks/scatter.watterson.R_div.pdf

### 2022-10-11 manuscript/main.tex
Updated manuscript

@@
         Positive selection can be the result of adaptive evolution, driven by a change in environment or selective pressure.
-        However, positive selection can also be the result of what we call maintenance positive selection where advantageous mutations are compensating for deleterious substitutions without any change of the environment.
+        However, positive selection can also be the result of what we call maintenance positive selection where advantageous mutations are reverting deleterious substitutions without any change of the environment.
         The evolutionary outcomes of these two positive selections are drastically different.
@@
         By leveraging polymorphism data in 28 populations and divergence data between 94 mammalian species, we estimate that around 25\% of observed substitutions are owed to maintenance positive selection.
-        Our work confirms that deleterious substitutions have accumulated in mammals and are currently being compensated for, resulting in widespread positive selection that is not adaptive evolution.
+        Our work confirms that deleterious substitutions have accumulated in mammals and are currently being eliminated, resulting in widespread positive selection that is not adaptive evolution.
     \end{abstract}
@@
     %\NS{on devrait plus placer le départ de l'intro dans un contexte historique, pour dire que de connaître si une mutation est avantageuse est la base de la génétique moléculaire (en citant des papiers clés)}
-    We usually say that a mutation is undergoing positive selection when it brings a fitness advantage to its bearer with the consequence of facilitating its own transmission to the next generation.
-    We can distinguish two main scenarios that can lead to such positive selection.
-    In the first scenario, a mutation towards a state which was deleterious is now advantageous because of a change of environment.
-    A change of environment could be a change of temperature, viral exposition but it could also be a change in another part of the species' genome.
-    In the new environment, the mutation allows its bearer to survive and reproduce more than the others and thus will be positively selected.
-    This process is typically referred to as adaptive evolution (fig.~\ref{fig:fitness-landscape}A).
-
-    The second scenario involves a mutation restoring the ancestral allele which corresponded to an optimal fitness for an individual in a constant environment, but has been lost due to the fixation of a deleterious mutation by drift (fig.~\ref{fig:fitness-landscape}B).
+    Adaptation is considered as the main process driving the diversity of forms and functions in the tree of life\cite{darwin_origin_1859}.
+    It allows species to live in new ecological niches, and to evolve in response to a change in environment\cite{darwin_origin_1859, merrell_adaptive_1994}.
+    The notion of adaptation, in its eco-evolutionary sense, is tightly linked to the notion of change, both of the environment (biotic and abiotic), and of the species responding to the latter\cite{merrell_adaptive_1994}.
+    With the discovery of DNA, the main support of heritable information, evolutionary geneticists looked for signatures of adaptation in genomes, such as to quantify it\cite{mcdonald_adaptative_1991, eyre-walker_distribution_2006}.
+    In that context arose the term of rate of adaptive evolution\cite{mcdonald_adaptative_1991, eyre-walker_distribution_2006, galtier_adaptive_2016}.
+    However, in contrast to adaptation in its eco-evolutionary sense, adaptive evolution is merely used as a synonymous of evolution under positive selection\cite{eyre-walker_distribution_2006}.
+    This leads to a misunderstanding on what is adaptation with the loss of the notion of change, and a misinterpretation of the so-called rate of adaptive evolution.
+    Indeed, adaptive evolution is not the only process which can lead to positive selection at the population scale\cite{sella_application_2005, mustonen_fitness_2009}.
+    At mutation-selection-drift equilibrium, a mutation restoring the ancestral allele which corresponded to an optimal fitness in a constant environment, but lost due to the fixation of a deleterious mutation by drift, will also be positively selected (fig.~\ref{fig:fitness-landscape}B).
     In this study, this process will be referred to as maintenance positive selection.
-    At the scale of a population, these two scenarios display different dynamics.
-    While in the case of environmental change, the population as a whole is climbing the fitness landscape along an adaptive walk\cite{tenaillon_utility_2014}, in the case of maintenance positive selection, the population as a whole is at mutation-selection equilibrium and therefore merely stays at the same location in the fitness landscape\cite{sella_application_2005, mustonen_fitness_2009}.
-
-    At the population scale, these two different kinds of selection are indistinguishable and both result in a positive transmission bias of the advantageous allele, but their consequences at a macro-evolutionary scale are fundamentally different.
+    %At the scale of a population, adaptive evolution and maintenance positive selection display different dynamics.
+    %While in the case of environmental change, the population as a whole is climbing the fitness landscape along an adaptive walk\cite{tenaillon_utility_2014}, in the case of maintenance positive selection, the population as a whole is at mutation-selection equilibrium and therefore merely stays at the same location in the fitness landscape\cite{sella_application_2005, mustonen_fitness_2009}.
+    %We can distinguish two main scenarios that can lead to such positive selection.
+    %In the first scenario, a mutation towards a state which was deleterious is now advantageous because of a change of environment.
+    %A change of environment could be a change of temperature, viral exposition but it could also be a change in another part of the species' genome.
+    %In the new environment, the mutation allows its bearer to survive and reproduce more than the others and thus will be positively selected.
+    %This process is typically referred to as adaptive evolution (fig.~\ref{fig:fitness-landscape}A), and meets the eco-evolutionary definition of adaptation.
+    At the population scale, maintenance positive selection and adaptive evolution are indistinguishable and both result in a positive transmission bias of the advantageous allele, but their consequences at a macro-evolutionary scale are fundamentally different.
     While adaptive evolution promotes phenotype diversification (fig.~\ref{fig:fitness-landscape}C), maintenance positive selection promotes phenotype stability and preserves well established biological systems (fig.~\ref{fig:fitness-landscape}D).
@@
 
-    Positive selection can be quantified by comparing sequence variation inside a population with the sequence divergence from a sister species\cite{mcdonald_adaptative_1991}.
+    At the gene level, positive selection can be quantified by comparing sequence variation inside a population with the sequence divergence from a sister species\cite{mcdonald_adaptative_1991}.
     The basic idea is that advantageous mutations are expected to be observed in substitutions between species but not in polymorphism within a population because they reach fixation too quickly.
@@
 would be nice to back it up with references}.
-    As mentioned above, not all advantageous mutations contribute to genetic innovation and diversification and truly adaptive evolution can only be well estimated if maintenance positive selection is taken into account.
+    As mentioned above, not all advantageous mutations contribute to genetic innovation and diversification, and truly adaptive evolution can only be well estimated if maintenance positive selection is taken into account.
     While adaptive evolution is unpredictable because it caused by an unpredictable change in the environment of organisms, the second is predictable because optimal states should be more or less the same for closely related organisms which share most of their environment and physiology.
@@
     These phylogenetic codon models can disentangle processes of mutation at the DNA level and selection at the amino acid level.
-    Such codon models provide a nearly-neutral framework of evolution by estimating the fitness landscape over amino acid sequences for each site of the sequence (fig~\ref{fig:method}A) while taking into account non-adaptive processes impacting codon frequency\cite{halpern_evolutionary_1998, rodrigue_mechanistic_2010, tamuri_estimating_2012}.
+    Such codon models provide a nearly-neutral framework of evolution by estimating the fitness landscape over amino acid sequences for each site of the sequence (fig~\ref{fig:method}A) while taking into account non-adaptive processes impacting codon frequency\cite{halpern_evolutionary_1998, rodrigue_mechanistic_2010, tamuri_estimating_2012, latrille_improved_2022}.
     From the fitness landscape obtained by fitting the model to the data, one can thus compute the scaled selection coefficient ($\Sphy$) of any non-synonymous mutations.
-    Importantly, mutation-selection assume that the underlying fitness landscape is stable along the phylogeny (as in fig.~\ref{fig:fitness-landscape}B), thus a mutation with a positive $\Sphy$ would be driving the current site toward a fitter amino-acid, and such mutation is effectively considered under maintenance positive selection.
+    Importantly, mutation-selection codon models assume that the underlying fitness landscape is stable along the phylogeny (as in fig.~\ref{fig:fitness-landscape}B), thus a mutation with a positive $\Sphy$ would be driving the current site toward a fitter amino-acid, and such mutation is effectively considered under maintenance positive selection.
 
@@
     Finally, how much of positive selection observed in populations is due to maintenance positive selection?
-    To answer these questions, we estimated the fitness landscape of amino acid for long-term evolution using available multiple sequence alignments between mammalian species\cite{ranwez_orthomam_2007, howe_ensembl_2021}.
+    To answer these questions, we estimated the fitness landscape of amino-acids for long-term evolution using available multiple sequence alignments between mammalian species\cite{ranwez_orthomam_2007, howe_ensembl_2021}.
     We then integrated data at the phylogenetic and population scale to estimate divergence and polymorphism, respectively, across the entire exome for 28 populations from 6 genera (\textit{Equus},  \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus} and \textit{Homo}; fig.~\ref{fig:method}A\&B).
@@
     For each population with available polymorphism data, we first reconstructed the ancestral sequence (which is different than the reference sequence), then we mapped the substitutions from the last genus split to this reconstructed ancestral sequence.
-    In these populations, we show that out of all polarized substitutions in the branches, between 10 and 17\% of all substitutions have an $\Sphy > 1$ (table S1) and between 22 and 42\% of all substitutions have an $\Sphy > 0$ (table S2).
-    Most importantly, there is clear signal that the substitutions with an $\Sphy > 1$ have been positively selected since their ratio of non-synonymous over synonymous divergence, a ratio called $\dnds$, is between 1.05 and 1.81 in the different populations (table S1), meaning that mutations under maintenance selection with $\Sphy > 1$ reach fixation more frequently that synonymous mutations (supposedly neutral).
+    In these populations, we show that out of all polarized substitutions in the branches, between 10 and 13\% of all substitutions have an $\Sphy > 1$ (table S1) and between 25 and 30\% of all substitutions have an $\Sphy > 0$ (table S3).
+    Most importantly, there is clear signal that the substitutions with an $\Sphy > 1$ have been positively selected since their ratio of non-synonymous over synonymous divergence, a ratio called $\dnds$, is between 1.15 and 1.68 in the different populations (table S1), meaning that mutations under maintenance selection with $\Sphy > 1$ reach fixation more frequently that synonymous mutations (supposedly neutral).
     These observed substitutions are likely to have been positively selected because they restored a more optimal state, not because they are driving innovations to a new environment or a new function.
@@
     Finally, $\mathbb{P} [ \Spop > 1  \given  \Sphy > 1]$ is the part of the DFE estimated at the population-scale greater than 1, when we restricted our analysis on SNPs that are already predicted by mutation-selection models to have a selection coefficient greater than 1 (black fill for the category $\Sphy > 1$ in fig~\ref{fig:homo-afr-results}D and table S2).
-    Altogether, the probability for a mutation to be restoring the genome given that it is positively selected is obtained for each population, and varies between 4 and 24\% (table S2).
+    Altogether, the probability for a mutation to be restoring the genome given that it is positively selected is obtained for each population, and varies between 10 and 26\% (table S2).
     % Since adaptation does not fit the fitness predictions, the proportion of adaptive mutation is expected to be the same among SNPs which are predicted to be advantageous, and among SNPs which are predicted to be deleterious.
@@
     Thus, if we divide the $\dnds$ estimated on all substitutions, by the one estimated only on substitutions predicted to be deleterious, we directly get the proportion of the rate of evolution which is contributed by maintenance selection (see methods).
-    This way, we estimated that between 20 and 25\% of the evolutionary rate is due to maintenance positive selection (fig~\ref{fig:diversity}C \& table S3).
+    This way, we estimated that between 22 and 27\% of the evolutionary rate is due to maintenance positive selection (fig~\ref{fig:diversity}C \& table S3).
 
@@
     From a structural biology perspective, we have found that proteins are not optimal for their fitness, which has been proved for their kinetics and thermodynamics\cite{taverna_why_2002, goldstein_evolution_2011}.
-    Philosophically, our distinction between maintenance selection and adaptation can appear to be rather far-fetched and not biologically motivated, and one can argue that maintenance selection is adaptation to its own deteriorating genome.
-    However, we argue that this distinction is important when we seek to detect adaptation, and is actually not an encumbrance but rather a strength.
-    Indeed, mutation-selection models are genuinely take into account the tug-of-war between scarce advantageous mutations likely to reach fixation and a bulk of deleterious mutations eventually reaching fixation due to their sheer mass.
+    Philosophically, our distinction between maintenance selection and adaptation can appear to be far-fetched, and one can argue that maintenance selection is adaptation to its own deteriorating genome.
+    However, there is a difference between adapting to a mutation, for instance by the mean of a compensatory mutation elsewhere, and cancelling the mutation, by the mean of a substitution on the misfit amino-acid.
+    The first still implies changes in the genetic sequence and thus genetic diversification, while the second reduces the diversity.
+    We also argue that this distinction is important when we seek to detect adaptation, and is actually not an encumbrance but rather a strength.
+    Indeed, mutation-selection models are genuinely taking into account the tug-of-war between scarce advantageous mutations likely to reach fixation and a bulk of deleterious mutations eventually reaching fixation due to their sheer mass.
     These models can thus be used as a null model to predict the expected rate of evolution of proteins\cite{spielman_relationship_2015, dosreis_how_2015} under a stable fitness landscape.
     A departure from this model indicates that proteins are evolving under a changing fitness landscape\cite{rodrigue_detecting_2017, tamuri_mutationselection_2021} and is a signal of pervasive adaptive evolution\cite{rodrigue_bayesian_2021} or of pervasive epistasis\cite{rodrigue_detecting_2017}.
-    As such, a stable fitness landscape as a null model is thus statistically more powerful than assuming that the null model is neutral.
-    Altogether, mutation-selection models is a mandatory tool in evolutionary biology to detect and quantify adaptation, as it lowers the bar to detect adaptation.
+    As such, a stable fitness landscape as a null model is thus statistically more powerful to detect adaptation than assuming that the null model is neutral evolution.
+    Altogether, mutation-selection models are a mandatory tool in evolutionary biology to detect and quantify adaptation at the phylogenetic scale.
 
@@
     Interpretation: T.L., J.J.\ and N.S.;
-    First draft, editing and revisions: T.L., J.J.\ and N.S.;
+    First draft: T.L.\ and J.J.;
+    Editing and revisions: T.L., J.J.\ and N.S.
     Project management and funding: N.S\@.

### 2022-10-11 manuscript/supp-mat.tex
Updated manuscript

@@
             \endlastfoot
-            Equus c. & Equus caballus & $ 0.002$ & $ 0.115$ & $ 1.187$ \\
-            Iran & Bos taurus & $ 0.005$ & $ 0.125$ & $ 1.322$ \\
-            Uganda & Bos taurus & $ 0.006$ & $ 0.126$ & $ 1.363$ \\
-            Australia & Capra hircus & $ 0.003$ & $ 0.122$ & $ 1.035$ \\
-            France & Capra hircus & $ 0.004$ & $ 0.122$ & $ 1.043$ \\
-            Iran (C. aegagrus) & Capra hircus & $ 0.004$ & $ 0.123$ & $ 1.042$ \\
-            Iran & Capra hircus & $ 0.004$ & $ 0.124$ & $ 1.052$ \\
-            Italy & Capra hircus & $ 0.004$ & $ 0.122$ & $ 1.037$ \\
-            Morocco & Capra hircus & $ 0.004$ & $ 0.124$ & $ 1.057$ \\
-            Iran & Ovis aries & $ 0.008$ & $ 0.104$ & $ 1.180$ \\
-            Iran (O. orientalis) & Ovis aries & $ 0.009$ & $ 0.103$ & $ 1.187$ \\
-            Iran (O. vignei) & Ovis aries & $ 0.008$ & $ 0.104$ & $ 1.172$ \\
-            Various & Ovis aries & $ 0.009$ & $ 0.103$ & $ 1.182$ \\
-            Morocco & Ovis aries & $ 0.008$ & $ 0.104$ & $ 1.189$ \\
-            Barbados & Chlorocebus sabaeus & $ 0.004$ & $ 0.123$ & $ 1.341$ \\
-            Central Afr. Rep. & Chlorocebus sabaeus & $ 0.006$ & $ 0.124$ & $ 1.370$ \\
-            Ethiopia & Chlorocebus sabaeus & $ 0.005$ & $ 0.124$ & $ 1.361$ \\
-            Gambia & Chlorocebus sabaeus & $ 0.005$ & $ 0.124$ & $ 1.359$ \\
-            Kenya & Chlorocebus sabaeus & $ 0.006$ & $ 0.125$ & $ 1.371$ \\
-            Nevis & Chlorocebus sabaeus & $ 0.004$ & $ 0.124$ & $ 1.349$ \\
-            South Africa & Chlorocebus sabaeus & $ 0.007$ & $ 0.126$ & $ 1.391$ \\
-            Saint Kitts & Chlorocebus sabaeus & $ 0.004$ & $ 0.125$ & $ 1.362$ \\
-            Zambia & Chlorocebus sabaeus & $ 0.006$ & $ 0.124$ & $ 1.362$ \\
-            African & Homo sapiens & $ 0.003$ & $ 0.104$ & $ 1.475$ \\
-            Admixed American & Homo sapiens & $ 0.002$ & $ 0.103$ & $ 1.466$ \\
-            East Asian & Homo sapiens & $ 0.002$ & $ 0.104$ & $ 1.478$ \\
-            European & Homo sapiens & $ 0.002$ & $ 0.103$ & $ 1.461$ \\
-            South Asian & Homo sapiens & $ 0.002$ & $ 0.104$ & $ 1.473$ \\
+            Equus c. &      Equus caballus &               $ 0.002$ &                $ 0.116$ &              $ 1.214$ \\
+            Iran &          Bos taurus &               $ 0.005$ &                $ 0.128$ &              $ 1.309$ \\
+            Uganda &          Bos taurus &               $ 0.005$ &                $ 0.130$ &              $ 1.352$ \\
+            Australia &        Capra hircus &               $ 0.003$ &                $ 0.121$ &              $ 1.147$ \\
+            France &        Capra hircus &               $ 0.003$ &                $ 0.121$ &              $ 1.154$ \\
+            Iran (C. aegagrus) &        Capra hircus &               $ 0.003$ &                $ 0.121$ &              $ 1.154$ \\
+            Iran &        Capra hircus &               $ 0.004$ &                $ 0.122$ &              $ 1.164$ \\
+            Italy &        Capra hircus &               $ 0.003$ &                $ 0.120$ &              $ 1.148$ \\
+            Morocco &        Capra hircus &               $ 0.004$ &                $ 0.123$ &              $ 1.170$ \\
+            Iran &          Ovis aries &               $ 0.007$ &                $ 0.113$ &              $ 1.210$ \\
+            Iran (O. orientalis) &          Ovis aries &               $ 0.009$ &                $ 0.112$ &              $ 1.214$ \\
+            Iran (O. vignei) &          Ovis aries &               $ 0.007$ &                $ 0.113$ &              $ 1.200$ \\
+            Various &          Ovis aries &               $ 0.009$ &                $ 0.112$ &              $ 1.207$ \\
+            Morocco &          Ovis aries &               $ 0.007$ &                $ 0.113$ &              $ 1.215$ \\
+            Barbados & Chlorocebus sabaeus &               $ 0.004$ &                $ 0.122$ &              $ 1.477$ \\
+            Central Afr. Rep. & Chlorocebus sabaeus &               $ 0.006$ &                $ 0.123$ &              $ 1.501$ \\
+            Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &                $ 0.123$ &              $ 1.494$ \\
+            Gambia & Chlorocebus sabaeus &               $ 0.005$ &                $ 0.123$ &              $ 1.491$ \\
+            Kenya & Chlorocebus sabaeus &               $ 0.005$ &                $ 0.123$ &              $ 1.503$ \\
+            Nevis & Chlorocebus sabaeus &               $ 0.003$ &                $ 0.123$ &              $ 1.484$ \\
+            South Africa & Chlorocebus sabaeus &               $ 0.006$ &                $ 0.125$ &              $ 1.528$ \\
+            Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &                $ 0.123$ &              $ 1.495$ \\
+            Zambia & Chlorocebus sabaeus &               $ 0.006$ &                $ 0.123$ &              $ 1.493$ \\
+            African &        Homo sapiens &               $ 0.003$ &                $ 0.102$ &              $ 1.676$ \\
+            Admixed American &        Homo sapiens &               $ 0.002$ &                $ 0.102$ &              $ 1.669$ \\
+            East Asian &        Homo sapiens &               $ 0.002$ &                $ 0.102$ &              $ 1.682$ \\
+            European &        Homo sapiens &               $ 0.002$ &                $ 0.101$ &              $ 1.659$ \\
+            South Asian &        Homo sapiens &               $ 0.002$ &                $ 0.102$ &              $ 1.676$ \\
         \end{longtable*}
@@
             \endlastfoot
-            Equus c. & Equus caballus & $ 0.002$ & $ 0.018$ & $ 0.042$ & $ 0.443$ & $ 0.404$ & $ 0.179$ \\
-            Iran & Bos taurus & $ 0.005$ & $ 0.017$ & $ 0.036$ & $ 0.471$ & $ 0.368$ & $ 0.173$ \\
-            Uganda & Bos taurus & $ 0.006$ & $ 0.017$ & $ 0.035$ & $ 0.490$ & $ 0.369$ & $ 0.181$ \\
-            Australia & Capra hircus & $ 0.003$ & $ 0.017$ & $ 0.036$ & $ 0.488$ & $ 0.144$ & $ 0.070$ \\
-            France & Capra hircus & $ 0.004$ & $ 0.017$ & $ 0.034$ & $ 0.515$ & $ 0.168$ & $ 0.086$ \\
-            Iran (C. aegagrus) & Capra hircus & $ 0.004$ & $ 0.017$ & $ 0.035$ & $ 0.493$ & $ 0.093$ & $ 0.046$ \\
-            Iran & Capra hircus & $ 0.004$ & $ 0.017$ & $ 0.030$ & $ 0.589$ & $ 0.140$ & $ 0.083$ \\
-            Italy & Capra hircus & $ 0.004$ & $ 0.017$ & $ 0.032$ & $ 0.545$ & $ 0.150$ & $ 0.081$ \\
-            Morocco & Capra hircus & $ 0.004$ & $ 0.017$ & $ 0.029$ & $ 0.598$ & $ 0.137$ & $ 0.082$ \\
-            Iran & Ovis aries & $ 0.008$ & $ 0.018$ & $ 0.022$ & $ 0.802$ & $ 0.046$ & $ 0.037$ \\
-            Iran (O. orientalis) & Ovis aries & $ 0.009$ & $ 0.018$ & $ 0.025$ & $ 0.718$ & $ 0.071$ & $ 0.051$ \\
-            Iran (O. vignei) & Ovis aries & $ 0.008$ & $ 0.018$ & $ 0.028$ & $ 0.642$ & $ 0.220$ & $ 0.141$ \\
-            Various & Ovis aries & $ 0.009$ & $ 0.018$ & $ 0.024$ & $ 0.748$ & $ 0.108$ & $ 0.081$ \\
-            Morocco & Ovis aries & $ 0.008$ & $ 0.018$ & $ 0.020$ & $ 0.883$ & $ 0.070$ & $ 0.062$ \\
-            Barbados & Chlorocebus sabaeus & $ 0.004$ & $ 0.015$ & $ 0.040$ & $ 0.375$ & $ 0.374$ & $ 0.140$ \\
-            Central Afr. Rep. & Chlorocebus sabaeus & $ 0.006$ & $ 0.015$ & $ 0.034$ & $ 0.435$ & $ 0.368$ & $ 0.160$ \\
-            Ethiopia & Chlorocebus sabaeus & $ 0.005$ & $ 0.015$ & $ 0.040$ & $ 0.377$ & $ 0.368$ & $ 0.139$ \\
-            Gambia & Chlorocebus sabaeus & $ 0.005$ & $ 0.015$ & $ 0.031$ & $ 0.482$ & $ 0.377$ & $ 0.182$ \\
-            Kenya & Chlorocebus sabaeus & $ 0.006$ & $ 0.015$ & $ 0.035$ & $ 0.428$ & $ 0.308$ & $ 0.132$ \\
-            Nevis & Chlorocebus sabaeus & $ 0.004$ & $ 0.015$ & $ 0.037$ & $ 0.404$ & $ 0.368$ & $ 0.149$ \\
-            South Africa & Chlorocebus sabaeus & $ 0.007$ & $ 0.015$ & $ 0.034$ & $ 0.435$ & $ 0.368$ & $ 0.160$ \\
-            Saint Kitts & Chlorocebus sabaeus & $ 0.004$ & $ 0.015$ & $ 0.039$ & $ 0.388$ & $ 0.368$ & $ 0.143$ \\
-            Zambia & Chlorocebus sabaeus & $ 0.006$ & $ 0.015$ & $ 0.038$ & $ 0.392$ & $ 0.368$ & $ 0.144$ \\
-            African & Homo sapiens & $ 0.003$ & $ 0.015$ & $ 0.038$ & $ 0.403$ & $ 0.604$ & $ 0.243$ \\
-            Admixed American & Homo sapiens & $ 0.002$ & $ 0.015$ & $ 0.037$ & $ 0.409$ & $ 0.574$ & $ 0.235$ \\
-            East Asian & Homo sapiens & $ 0.002$ & $ 0.015$ & $ 0.036$ & $ 0.426$ & $ 0.484$ & $ 0.206$ \\
-            European & Homo sapiens & $ 0.002$ & $ 0.015$ & $ 0.037$ & $ 0.414$ & $ 0.517$ & $ 0.214$ \\
-            South Asian & Homo sapiens & $ 0.002$ & $ 0.015$ & $ 0.036$ & $ 0.428$ & $ 0.532$ & $ 0.227$ \\
+            Equus c.
+&      Equus caballus &               $ 0.002$ &          $ 0.017$ &                   $ 0.046$ &                                          $ 0.378$ &                         $ 0.678$ &                      $ 0.256$ \\
+            Iran &          Bos taurus &               $ 0.005$ &          $ 0.016$ &                   $ 0.040$ &                                          $ 0.402$ &                         $ 0.525$ &                      $ 0.211$ \\
+            Uganda &          Bos taurus &               $ 0.005$ &          $ 0.016$ &                   $ 0.038$ &                                          $ 0.420$ &                         $ 0.610$ &                      $ 0.256$ \\
+            Australia &        Capra hircus &               $ 0.003$ &          $ 0.017$ &                   $ 0.039$ &                                          $ 0.419$ &                         $ 0.368$ &                      $ 0.154$ \\
+            France &        Capra hircus &               $ 0.003$ &          $ 0.017$ &                   $ 0.038$ &                                          $ 0.440$ &                         $ 0.368$ &                      $ 0.162$ \\
+            Iran (C.
+aegagrus) &        Capra hircus &               $ 0.003$ &          $ 0.017$ &                   $ 0.040$ &                                          $ 0.418$ &                         $ 0.235$ &                      $ 0.098$ \\
+            Iran &        Capra hircus &               $ 0.004$ &          $ 0.017$ &                   $ 0.033$ &                                          $ 0.500$ &                         $ 0.368$ &                      $ 0.184$ \\
+            Italy &        Capra hircus &               $ 0.003$ &          $ 0.017$ &                   $ 0.035$ &                                          $ 0.466$ &                         $ 0.309$ &                      $ 0.144$ \\
+            Morocco &        Capra hircus &               $ 0.004$ &          $ 0.017$ &                   $ 0.032$ &                                          $ 0.514$ &                         $ 0.368$ &                      $ 0.189$ \\
+            Iran &          Ovis aries &               $ 0.007$ &          $ 0.017$ &                   $ 0.024$ &                                          $ 0.686$ &                         $ 0.174$ &                      $ 0.119$ \\
+            Iran (O.
+orientalis) &          Ovis aries &               $ 0.009$ &          $ 0.017$ &                   $ 0.027$ &                                          $ 0.612$ &                         $ 0.165$ &                      $ 0.101$ \\
+            Iran (O.
+vignei) &          Ovis aries &               $ 0.007$ &          $ 0.017$ &                   $ 0.031$ &                                          $ 0.542$ &                         $ 0.228$ &                      $ 0.124$ \\
+            Various &          Ovis aries &               $ 0.009$ &          $ 0.017$ &                   $ 0.026$ &                                          $ 0.641$ &                         $ 0.238$ &                      $ 0.153$ \\
+            Morocco &          Ovis aries &               $ 0.007$ &          $ 0.017$ &                   $ 0.023$ &                                          $ 0.742$ &                         $ 0.192$ &                      $ 0.142$ \\
+            Barbados & Chlorocebus sabaeus &               $ 0.004$ &          $ 0.014$ &                   $ 0.045$ &                                          $ 0.319$ &                         $ 0.595$ &                      $ 0.190$ \\
+            Central Afr.
+Rep.
+& Chlorocebus sabaeus &               $ 0.006$ &          $ 0.014$ &                   $ 0.039$ &                                          $ 0.368$ &                         $ 0.497$ &                      $ 0.183$ \\
+            Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &          $ 0.014$ &                   $ 0.044$ &                                          $ 0.322$ &                         $ 0.502$ &                      $ 0.162$ \\
+            Gambia & Chlorocebus sabaeus &               $ 0.005$ &          $ 0.014$ &                   $ 0.034$ &                                          $ 0.415$ &                         $ 0.541$ &                      $ 0.224$ \\
+            Kenya & Chlorocebus sabaeus &               $ 0.005$ &          $ 0.014$ &                   $ 0.039$ &                                          $ 0.363$ &                         $ 0.492$ &                      $ 0.179$ \\
+            Nevis & Chlorocebus sabaeus &               $ 0.003$ &          $ 0.014$ &                   $ 0.041$ &                                          $ 0.345$ &                         $ 0.549$ &                      $ 0.190$ \\
+            South Africa & Chlorocebus sabaeus &               $ 0.006$ &          $ 0.014$ &                   $ 0.039$ &                                          $ 0.367$ &                         $ 0.504$ &                      $ 0.185$ \\
+            Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &          $ 0.014$ &                   $ 0.043$ &                                          $ 0.326$ &                         $ 0.538$ &                      $ 0.175$ \\
+            Zambia & Chlorocebus sabaeus &               $ 0.006$ &          $ 0.014$ &                   $ 0.043$ &                                          $ 0.332$ &                         $ 0.529$ &                      $ 0.175$ \\
+            African &        Homo sapiens &               $ 0.003$ &          $ 0.014$ &                   $ 0.042$ &                                          $ 0.343$ &                         $ 0.724$ &                      $ 0.249$ \\
+            Admixed American &        Homo sapiens &               $ 0.002$ &          $ 0.014$ &                   $ 0.040$ &                                          $ 0.358$ &                         $ 0.695$ &                      $ 0.249$ \\
+            East Asian &        Homo sapiens &               $ 0.002$ &          $ 0.014$ &                   $ 0.039$ &                                          $ 0.366$ &                         $ 0.652$ &                      $ 0.239$ \\
+            European &        Homo sapiens &               $ 0.002$ &          $ 0.014$ &                   $ 0.039$ &                                          $ 0.373$ &                         $ 0.666$ &                      $ 0.249$ \\
+            South Asian &        Homo sapiens &               $ 0.002$ &          $ 0.014$ &                   $ 0.038$ &                                          $ 0.378$ &                         $ 0.677$ &                      $ 0.256$ \\
         \end{longtable*}
@@
     \newpage
-%    \begin{center}
-%        \captionof{table}{~}
-%        \scriptsize
-%        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
-%            \toprule
-%            Population & Species & Tajima $\theta_{\pi}$ & $\mathbb{P}[\Sphy > 0]$ & $\mathbb{P} [\Spop > 0 ]$ & $\frac{\mathbb{P}[\Sphy > 0]}{\mathbb{P}[\Spop > 0]}$ & $\mathbb{P} [\Spop > 0 \given \Sphy > 0]$ & $\mathbb{P}[\Sphy > 0|\Spop > 0]$ \\
-%            \midrule
-%            \endhead
-%            \midrule
-%            \multicolumn{8}{r}{{Continued on next page}} \\
-%            \midrule
-%            \endfoot
-%%
-%            \bottomrule
-%            \endlastfoot
-%            Equus c. & Equus caballus & $ 0.002$ & $ 0.054$ & $ 0.113$ & $ 0.473$ & $ 0.489$ & $ 0.231$ \\
-%            Iran & Bos taurus & $ 0.005$ & $ 0.053$ & $ 0.098$ & $ 0.540$ & $ 0.368$ & $ 0.198$ \\
-%            Uganda & Bos taurus & $ 0.006$ & $ 0.053$ & $ 0.094$ & $ 0.558$ & $ 0.419$ & $ 0.234$ \\
-%            Australia & Capra hircus & $ 0.003$ & $ 0.054$ & $ 0.096$ & $ 0.557$ & $ 0.126$ & $ 0.070$ \\
-%            France & Capra hircus & $ 0.004$ & $ 0.054$ & $ 0.092$ & $ 0.583$ & $ 0.297$ & $ 0.173$ \\
-%            Iran (C. aegagrus) & Capra hircus & $ 0.004$ & $ 0.054$ & $ 0.096$ & $ 0.561$ & $ 0.080$ & $ 0.045$ \\
-%            Iran & Capra hircus & $ 0.004$ & $ 0.054$ & $ 0.080$ & $ 0.667$ & $ 0.281$ & $ 0.188$ \\
-%            Italy & Capra hircus & $ 0.004$ & $ 0.054$ & $ 0.087$ & $ 0.617$ & $ 0.304$ & $ 0.187$ \\
-%            Morocco & Capra hircus & $ 0.004$ & $ 0.054$ & $ 0.079$ & $ 0.679$ & $ 0.131$ & $ 0.089$ \\
-%            Iran & Ovis aries & $ 0.008$ & $ 0.054$ & $ 0.060$ & $ 0.897$ & $ 0.304$ & $ 0.273$ \\
-%            Iran (O. orientalis) & Ovis aries & $ 0.009$ & $ 0.054$ & $ 0.067$ & $ 0.806$ & $ 0.345$ & $ 0.278$ \\
-%            Iran (O. vignei) & Ovis aries & $ 0.008$ & $ 0.054$ & $ 0.075$ & $ 0.720$ & $ 0.464$ & $ 0.334$ \\
-%            Various & Ovis aries & $ 0.009$ & $ 0.054$ & $ 0.064$ & $ 0.840$ & $ 0.359$ & $ 0.302$ \\
-%            Morocco & Ovis aries & $ 0.008$ & $ 0.054$ & $ 0.055$ & $ 0.971$ & $ 0.247$ & $ 0.240$ \\
-%            Barbados & Chlorocebus sabaeus & $ 0.004$ & $ 0.050$ & $ 0.109$ & $ 0.463$ & $ 0.350$ & $ 0.162$ \\
-%            Central Afr. Rep. & Chlorocebus sabaeus & $ 0.006$ & $ 0.050$ & $ 0.094$ & $ 0.537$ & $ 0.225$ & $ 0.121$ \\
-%            Ethiopia & Chlorocebus sabaeus & $ 0.005$ & $ 0.050$ & $ 0.108$ & $ 0.466$ & $ 0.312$ & $ 0.145$ \\
-%            Gambia & Chlorocebus sabaeus & $ 0.005$ & $ 0.050$ & $ 0.084$ & $ 0.602$ & $ 0.286$ & $ 0.172$ \\
-%            Kenya & Chlorocebus sabaeus & $ 0.006$ & $ 0.050$ & $ 0.095$ & $ 0.529$ & $ 0.196$ & $ 0.104$ \\
-%            Nevis & Chlorocebus sabaeus & $ 0.004$ & $ 0.050$ & $ 0.101$ & $ 0.500$ & $ 0.296$ & $ 0.148$ \\
-%            South Africa & Chlorocebus sabaeus & $ 0.007$ & $ 0.050$ & $ 0.094$ & $ 0.534$ & $ 0.243$ & $ 0.130$ \\
-%            Saint Kitts & Chlorocebus sabaeus & $ 0.004$ & $ 0.050$ & $ 0.106$ & $ 0.473$ & $ 0.309$ & $ 0.146$ \\
-%            Zambia & Chlorocebus sabaeus & $ 0.006$ & $ 0.050$ & $ 0.104$ & $ 0.485$ & $ 0.245$ & $ 0.119$ \\
-%            African & Homo sapiens & $ 0.003$ & $ 0.051$ & $ 0.103$ & $ 0.497$ & $ 0.785$ & $ 0.390$ \\
-%            Admixed American & Homo sapiens & $ 0.002$ & $ 0.051$ & $ 0.104$ & $ 0.492$ & $ 0.737$ & $ 0.363$ \\
-%            East Asian & Homo sapiens & $ 0.002$ & $ 0.051$ & $ 0.098$ & $ 0.521$ & $ 0.684$ & $ 0.356$ \\
-%            European & Homo sapiens & $ 0.002$ & $ 0.051$ & $ 0.097$ & $ 0.526$ & $ 0.687$ & $ 0.361$ \\
-%            South Asian & Homo sapiens & $ 0.002$ & $ 0.051$ & $ 0.096$ & $ 0.530$ & $ 0.691$ & $ 0.366$ \\
-%        \end{longtable*}
-%    \end{center}
-%    \begin{itemize}
-%        \item Tajima $\theta$ is the synonymous diversity.
-%        \item $\mathbb{P} [ \Sphy > 0 ]$ is the probability for a new mutation to be under maintenance selection.
-%        These mutations have a positive selection coefficient predicted at the phylogenetic-scale larger ($\Sphy > 0$), thus toward a more fit amino-acid.
-%        In other words, this probability is the positive part of the DFE estimated by mutation-selection models.
-%        \item $\mathbb{P} [ \Spop > 0 ]$ is the probability for a mutation to be positively selected.
-%        These mutations have a positive selection coefficient at the population-scale larger ($\Spop > 0$), estimated from all SNPs in the population.
-%        In other words, this probability is the positive part of the DFE estimated by polyDFE.
-%        \item $\mathbb{P} [ \Spop > 0 \given \Sphy > 0]$ is the probability for a mutation to be positively selected, given it is under maintenance selection.
-%        These mutations have a positive selection coefficient at the population-scale larger ($\Spop > 0$), estimated by polyDFE on the SNPs with a positive predicted selection coefficient ($\Sphy > 0$).
-%        In other words, this probability is the positive part of the DFE estimated by polyDFE, when we restricted our analysis on SNPs that are already predicted by mutation-selection models to have a positive selection coefficient.
-%        \item $\mathbb{P} [ \Sphy > 0 \given \Spop > 0]$ is the probability for a mutation to be under maintenance selection, given it is positively selected.
-%        This probability is obtained using Bayes' formula.
-%    \end{itemize}
     \begin{center}
@@
             \endlastfoot
-            Equus c. & Equus caballus & $ 0.002$ & $ 0.304$ & $ 0.190$ & $ 0.140$ & $ 26.4$ \\
-            Iran & Bos taurus & $ 0.005$ & $ 0.280$ & $ 0.181$ & $ 0.137$ & $ 24.0$ \\
-            Uganda & Bos taurus & $ 0.006$ & $ 0.284$ & $ 0.184$ & $ 0.139$ & $ 24.4$ \\
-            Australia & Capra hircus & $ 0.003$ & $ 0.301$ & $ 0.148$ & $ 0.109$ & $ 26.1$ \\
-            France & Capra hircus & $ 0.004$ & $ 0.301$ & $ 0.149$ & $ 0.110$ & $ 26.1$ \\
-            Iran (C. aegagrus) & Capra hircus & $ 0.004$ & $ 0.301$ & $ 0.148$ & $ 0.109$ & $ 26.1$ \\
-            Iran & Capra hircus & $ 0.004$ & $ 0.303$ & $ 0.148$ & $ 0.109$ & $ 26.4$ \\
-            Italy & Capra hircus & $ 0.004$ & $ 0.301$ & $ 0.149$ & $ 0.110$ & $ 26.1$ \\
-            Morocco & Capra hircus & $ 0.004$ & $ 0.303$ & $ 0.148$ & $ 0.109$ & $ 26.4$ \\
-            Iran & Ovis aries & $ 0.008$ & $ 0.241$ & $ 0.200$ & $ 0.160$ & $ 19.8$ \\
-            Iran (O. orientalis) & Ovis aries & $ 0.009$ & $ 0.239$ & $ 0.203$ & $ 0.163$ & $ 19.6$ \\
-            Iran (O. vignei) & Ovis aries & $ 0.008$ & $ 0.243$ & $ 0.199$ & $ 0.159$ & $ 20.0$ \\
-            Various & Ovis aries & $ 0.009$ & $ 0.239$ & $ 0.203$ & $ 0.163$ & $ 19.6$ \\
-            Morocco & Ovis aries & $ 0.008$ & $ 0.240$ & $ 0.202$ & $ 0.163$ & $ 19.7$ \\
-            Barbados & Chlorocebus sabaeus & $ 0.004$ & $ 0.302$ & $ 0.163$ & $ 0.120$ & $ 26.5$ \\
-            Central Afr. Rep. & Chlorocebus sabaeus & $ 0.006$ & $ 0.304$ & $ 0.165$ & $ 0.121$ & $ 26.7$ \\
-            Ethiopia & Chlorocebus sabaeus & $ 0.005$ & $ 0.304$ & $ 0.164$ & $ 0.120$ & $ 26.7$ \\
-            Gambia & Chlorocebus sabaeus & $ 0.005$ & $ 0.303$ & $ 0.164$ & $ 0.120$ & $ 26.6$ \\
-            Kenya & Chlorocebus sabaeus & $ 0.006$ & $ 0.304$ & $ 0.164$ & $ 0.120$ & $ 26.7$ \\
-            Nevis & Chlorocebus sabaeus & $ 0.004$ & $ 0.303$ & $ 0.163$ & $ 0.120$ & $ 26.6$ \\
-            South Africa & Chlorocebus sabaeus & $ 0.007$ & $ 0.306$ & $ 0.164$ & $ 0.120$ & $ 26.9$ \\
-            Saint Kitts & Chlorocebus sabaeus & $ 0.004$ & $ 0.305$ & $ 0.163$ & $ 0.120$ & $ 26.8$ \\
-            Zambia & Chlorocebus sabaeus & $ 0.006$ & $ 0.303$ & $ 0.164$ & $ 0.120$ & $ 26.7$ \\
-            African & Homo sapiens & $ 0.003$ & $ 0.259$ & $ 0.216$ & $ 0.169$ & $ 21.9$ \\
-            Admixed American & Homo sapiens & $ 0.002$ & $ 0.258$ & $ 0.216$ & $ 0.169$ & $ 21.8$ \\
-            East Asian & Homo sapiens & $ 0.002$ & $ 0.259$ & $ 0.217$ & $ 0.169$ & $ 22.0$ \\
-            European & Homo sapiens & $ 0.002$ & $ 0.258$ & $ 0.216$ & $ 0.169$ & $ 21.8$ \\
-            South Asian & Homo sapiens & $ 0.002$ & $ 0.259$ & $ 0.216$ & $ 0.169$ & $ 21.9$ \\
+            Equus c. &      Equus caballus &               $ 0.002$ &                $ 0.307$ &        $ 0.182$ &              $ 0.133$ &           $  27.0$ \\
+            Iran &          Bos taurus &               $ 0.005$ &                $ 0.298$ &        $ 0.164$ &              $ 0.122$ &           $  26.1$ \\
+            Uganda &          Bos taurus &               $ 0.005$ &                $ 0.303$ &        $ 0.167$ &              $ 0.123$ &           $  26.6$ \\
+            Australia &        Capra hircus &               $ 0.003$ &                $ 0.301$ &        $ 0.157$ &              $ 0.116$ &           $  26.4$ \\
+            France &        Capra hircus &               $ 0.003$ &                $ 0.300$ &        $ 0.158$ &              $ 0.116$ &           $  26.3$ \\
+            Iran (C. aegagrus) &        Capra hircus &               $ 0.003$ &                $ 0.300$ &        $ 0.158$ &              $ 0.116$ &           $  26.3$ \\
+            Iran &        Capra hircus &               $ 0.004$ &                $ 0.303$ &        $ 0.157$ &              $ 0.115$ &           $  26.6$ \\
+            Italy &        Capra hircus &               $ 0.003$ &                $ 0.300$ &        $ 0.158$ &              $ 0.116$ &           $  26.3$ \\
+            Morocco &        Capra hircus &               $ 0.004$ &                $ 0.303$ &        $ 0.157$ &              $ 0.115$ &           $  26.6$ \\
+            Iran &          Ovis aries &               $ 0.007$ &                $ 0.266$ &        $ 0.179$ &              $ 0.138$ &           $  22.7$ \\
+            Iran (O. orientalis) &          Ovis aries &               $ 0.009$ &                $ 0.265$ &        $ 0.180$ &              $ 0.140$ &           $  22.6$ \\
+            Iran (O. vignei) &          Ovis aries &               $ 0.007$ &                $ 0.268$ &        $ 0.178$ &              $ 0.137$ &           $  22.8$ \\
+            Various &          Ovis aries &               $ 0.009$ &                $ 0.264$ &        $ 0.180$ &              $ 0.140$ &           $  22.5$ \\
+            Morocco &          Ovis aries &               $ 0.007$ &                $ 0.265$ &        $ 0.180$ &              $ 0.140$ &           $  22.6$ \\
+            Barbados & Chlorocebus sabaeus &               $ 0.004$ &                $ 0.303$ &        $ 0.172$ &              $ 0.126$ &           $  26.8$ \\
+            Central Afr. Rep. & Chlorocebus sabaeus &               $ 0.006$ &                $ 0.304$ &        $ 0.173$ &              $ 0.126$ &           $  27.0$ \\
+            Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &                $ 0.305$ &        $ 0.172$ &              $ 0.126$ &           $  27.1$ \\
+            Gambia & Chlorocebus sabaeus &               $ 0.005$ &                $ 0.304$ &        $ 0.172$ &              $ 0.126$ &           $  26.9$ \\
+            Kenya & Chlorocebus sabaeus &               $ 0.005$ &                $ 0.304$ &        $ 0.173$ &              $ 0.126$ &           $  27.0$ \\
+            Nevis & Chlorocebus sabaeus &               $ 0.003$ &                $ 0.304$ &        $ 0.172$ &              $ 0.126$ &           $  26.9$ \\
+            South Africa & Chlorocebus sabaeus &               $ 0.006$ &                $ 0.307$ &        $ 0.172$ &              $ 0.125$ &           $  27.3$ \\
+            Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &                $ 0.306$ &        $ 0.172$ &              $ 0.125$ &           $  27.1$ \\
+            Zambia & Chlorocebus sabaeus &               $ 0.006$ &                $ 0.304$ &        $ 0.172$ &              $ 0.126$ &           $  27.0$ \\
+            African &        Homo sapiens &               $ 0.003$ &                $ 0.257$ &        $ 0.237$ &              $ 0.185$ &           $  22.0$ \\
+            Admixed American &        Homo sapiens &               $ 0.002$ &                $ 0.256$ &        $ 0.237$ &              $ 0.185$ &           $  21.9$ \\
+            East Asian &        Homo sapiens &               $ 0.002$ &                $ 0.258$ &        $ 0.238$ &              $ 0.185$ &           $  22.0$ \\
+            European &        Homo sapiens &               $ 0.002$ &                $ 0.256$ &        $ 0.237$ &              $ 0.185$ &           $  21.8$ \\
+            South Asian &        Homo sapiens &               $ 0.002$ &                $ 0.257$ &        $ 0.237$ &              $ 0.185$ &           $  22.0$ \\
         \end{longtable*}

### 2022-10-11 copy_artworks.sh

@@ -1,7 +1,6 @@
 #!/usr/bin/env bash
 \cp -rf ./experiments/50windows-polyDFE-mC-non-adaptive/regression/results.watterson.a.scatter.pdf ./manuscript/artworks/scatter.watterson.slopeSpopSphy.pdf
 \cp -rf ./experiments/50windows-polyDFE-mC-non-adaptive/results/regression.MutSel.SelCoeff.scatter.pdf ./manuscript/artworks/scatter.Sphy.Spop.pdf
-\cp -rf ./experiments/3bins-polyDFE-mC/results/Theta.MutSel.weak.stacked.pdf ./manuscript/artworks/stacked.weakSNPs.pdf
 \cp -rf ./experiments/5bins-polyDFE-mC/results/Theta.MutSel.all.stacked.pdf ./manuscript/artworks/stacked.allSNPs.pdf
 \cp -rf ./experiments/5bins-polyDFE-mC/results/Theta.MutSel.pos-weak.stacked.pdf ./manuscript/artworks/stacked.weak-pos-SNPs.pdf
 \cp -rf ./experiments/5bins-polyDFE-mC/results/Theta.MutSel.neg-weak.stacked.pdf ./manuscript/artworks/stacked.weak-neg-SNPs.pdf

### 2022-10-26 manuscript/main_rev.tex
Revision by L. Duret & J. Joseph

--- 2022-10-11 manuscript/main.tex
@@
 \usepackage{biorxiv}
-\usepackage[backend=biber,,isbn=false,url=false,intitle=true,style=nature]{biblatex}
+\usepackage[backend=biber,eprint=false,isbn=false,url=false,intitle=true,style=nature,date=year]{biblatex}
 \addbibresource{codon_models.bib}
@@
         Positive selection can be the result of adaptive evolution, driven by a change in environment or selective pressure.
-        However, positive selection can also be the result of what we call maintenance positive selection where advantageous mutations are reverting deleterious substitutions without any change of the environment.
+        However, positive selection can also be the result of what we call maintenance positive selection where advantageous back-mutations are reverting deleterious substitutions without any change of the environment.
         The evolutionary outcomes of these two positive selections are drastically different.
@@
 
-    %\NS{on devrait plus placer le départ de l'intro dans un contexte historique, pour dire que de connaître si une mutation est avantageuse est la base de la génétique moléculaire (en citant des papiers clés)}
-    Adaptation is considered as the main process driving the diversity of forms and functions in the tree of life\cite{darwin_origin_1859}.
-    It allows species to live in new ecological niches, and to evolve in response to a change in environment\cite{darwin_origin_1859, merrell_adaptive_1994}.
+    Adaptation is considered as the main process driving the diversity of forms and functions across the tree of life\cite{darwin_origin_1859}, and it enables species to live in new ecological niches, and to evolve in response to a change in environment\cite{darwin_origin_1859, merrell_adaptive_1994}.
     The notion of adaptation, in its eco-evolutionary sense, is tightly linked to the notion of change, both of the environment (biotic and abiotic), and of the species responding to the latter\cite{merrell_adaptive_1994}.
-    With the discovery of DNA, the main support of heritable information, evolutionary geneticists looked for signatures of adaptation in genomes, such as to quantify it\cite{mcdonald_adaptative_1991, eyre-walker_distribution_2006}.
+    With the discovery of DNA, the main support of heritable information, evolutionary geneticists looked for signatures of adaptation in genomes, and tried to quantify it\cite{mcdonald_adaptative_1991, eyre-walker_distribution_2006}.
     In that context arose the term of rate of adaptive evolution\cite{mcdonald_adaptative_1991, eyre-walker_distribution_2006, galtier_adaptive_2016}.
@@
     In this study, this process will be referred to as maintenance positive selection.
-    %At the scale of a population, adaptive evolution and maintenance positive selection display different dynamics.
-    %While in the case of environmental change, the population as a whole is climbing the fitness landscape along an adaptive walk\cite{tenaillon_utility_2014}, in the case of maintenance positive selection, the population as a whole is at mutation-selection equilibrium and therefore merely stays at the same location in the fitness landscape\cite{sella_application_2005, mustonen_fitness_2009}.
-    %We can distinguish two main scenarios that can lead to such positive selection.
-    %In the first scenario, a mutation towards a state which was deleterious is now advantageous because of a change of environment.
-    %A change of environment could be a change of temperature, viral exposition but it could also be a change in another part of the species' genome.
-    %In the new environment, the mutation allows its bearer to survive and reproduce more than the others and thus will be positively selected.
-    %This process is typically referred to as adaptive evolution (fig.~\ref{fig:fitness-landscape}A), and meets the eco-evolutionary definition of adaptation.
     At the population scale, maintenance positive selection and adaptive evolution are indistinguishable and both result in a positive transmission bias of the advantageous allele, but their consequences at a macro-evolutionary scale are fundamentally different.
@@
     While adaptive evolution is unpredictable because it caused by an unpredictable change in the environment of organisms, the second is predictable because optimal states should be more or less the same for closely related organisms which share most of their environment and physiology.
-    A way to thus measure maintenance positive selection is to predict selection coefficients assuming a constant and stable fitness landscape estimated from the alignment of protein-coding genes.
+    A way to measure maintenance positive selection is to predict selection coefficients assuming a constant and stable fitness landscape estimated from the alignment of protein-coding genes.
     For each site of the protein alignment, a first approximation would be to consider that the frequency of an amino acid is a proxy for its fitness, since for example a deleterious amino acid will be more likely to be absent in the alignment.
@@
     However, this method has two major shortcomings.
-    First, we know that a lot of mechanisms can influence amino acid frequency other than fitness (phylogeny, mutation biases, GC-biased gene conversion, mutational paths) which are not accounted for in SIFT\@.
+    First, we know that a lot of mechanisms can influence amino acid frequency other than fitness (phylogenetic inertia, mutation biases, GC-biased gene conversion, mutational paths) which are not accounted for in SIFT\@.
     Second, SIFT scores is not interpretable as a selection coefficient.
@@
     From the fitness landscape obtained by fitting the model to the data, one can thus compute the scaled selection coefficient ($\Sphy$) of any non-synonymous mutations.
-    Importantly, mutation-selection codon models assume that the underlying fitness landscape is stable along the phylogeny (as in fig.~\ref{fig:fitness-landscape}B), thus a mutation with a positive $\Sphy$ would be driving the current site toward a fitter amino-acid, and such mutation is effectively considered under maintenance positive selection.
+    Importantly, mutation-selection codon models assume that the underlying fitness landscape is stable along the phylogeny (as in fig.~\ref{fig:fitness-landscape}B), thus a mutation with a positive $\Sphy$ would be driving the current site toward a fitter amino-acid, and such mutation is effectively considered under maintenance positive selection, and is non-adaptive.
 
-    By integrating datasets at the species and population level, we can predict $\Sphy$ for each mutation currently segregating in a population (fig~\ref{fig:method}B).
+    By integrating datasets at the species and population level, we can predict $\Sphy$ for any mutation currently segregating in a population (fig~\ref{fig:method}B) under a stable fitness landscape.
     Such a dataset can allow us to address different questions regarding positive selection affecting protein-coding DNA sequences.
     Which proportion of the segregating polymorphisms in population are predicted toward a more optimal amino acid (positive $\Sphy$), thus supposedly under maintenance positive selection?
-    Are these polymorphisms effectively under positive selection at the scale of populations?
+    Are these polymorphisms effectively under positive selection along the terminal branches ? At the scale of populations ?
     Finally, how much of positive selection observed in populations is due to maintenance positive selection?
@@
             At the phylogenetic level (panel A), the amino acid Wrightian fitness for each site is estimated from protein-coding DNA alignments using mutation-selection codon models.
-            At the population-genetic level (panel B), for each observed single nucleotide polymorphism (SNP) segregating in the population, selection coefficient ($\Sphy$) are computed as the difference in amino acid fitness between the ancestral and derived variants.
-            Mutation-selection codon models that the underlying fitness landscape is stable along the phylogeny, taking into account only non-adaptive evolution, thus a mutation with a positive $\Sphy$ would be driving the current site toward are fitter amino-acid, and such mutation are effectively considered under maintenance positive selection.
+            At the population-genetic level (panel B), for each observed single nucleotide polymorphism (SNP) segregating in the population, selection coefficient ($\Sphy$) are estimated as the difference in amino acid fitness between the ancestral and derived variants.
+            Mutation-selection codon models assume that the underlying fitness landscape is stable along the phylogeny, taking into account only non-adaptive evolution, thus a mutation with a positive $\Sphy$ would be driving the current site toward are fitter amino-acid, and such mutation are effectively considered under maintenance positive selection.
         }
@@
 
-    For each non-synonymous SNP observed at the population level, we predicted its scaled selection coefficient ($\Sphy$) from amino acid fitnesses estimated at the mammalian scale (fig.~\ref{fig:method}B).
+    For each non-synonymous SNP observed at the population level, we predicted its scaled selection coefficient ($\Sphy$) from a stable fitness landscape estimated at the mammalian scale (fig.~\ref{fig:method}B).
     Then we ask whether the variants that are predicted to be advantageous, thus supposedly under maintenance selection, are showing signatures of short term positive selection.
-    For example, if a variant is found to be fixed in many mammals but not in ancestral humans, and a mutation in humans is toward the mammalian version, is this mutation advantageous for the individual carrying it?
+    For example, if a variant predicted to be non-optimal is found to be fixed in the last common ancestor of extant humans.
+If a mutation occurs in extant humans towards the allele predicted to be optimal, is this mutation positively selected at the population-scale?
     At the population level (e.g.~in humans of Asian descent in fig.~\ref{fig:homo-afr-results}), we divided all observed SNPs in 5 classes of predicted selection coefficient: severely deleterious with $\divStrongDel$, deleterious with $\divDel$, weakly deleterious with $\divWeakDel$, weakly advantageous with $\divWeakAdv$ and advantageous with $\divAdv$ (fig.~\ref{fig:homo-afr-results}B).
-    In each of theses classes, SNPs are then grouped by the number of derived alleles in the population (fig.~\ref{fig:homo-afr-results}C), generating a so called site-frequency spectrum (SFS).
+    In each of theses classes, SNPs are then grouped by the frequency of derived alleles in the population (fig.~\ref{fig:homo-afr-results}C), generating a so called site-frequency spectrum (SFS).
     Compared to synonymous mutations which are supposedly neutral (black line in fig.~\ref{fig:homo-afr-results}C), mutations predicted to be deleterious (blue and green lines in fig.~\ref{fig:homo-afr-results}C) are underrepresented at high frequencies in the population, a signature of ongoing purifying selection.
@@
 
-    We replicated such experiment across 28 populations (fig.~\ref{fig:heatmap}), and found that mutations predicted to be deleterious are indeed purged at the population-genetic scale (blue and green rows in fig.~\ref{fig:heatmap}A).
+    We replicated such experiment across 28 populations from 6 species(fig.~\ref{fig:heatmap}), and found that mutations predicted to be deleterious are indeed purged at the population-scale (blue and green rows in fig.~\ref{fig:heatmap}A).
     However, mutations predicted to be weakly advantageous ($\divWeakAdv$) are composed of a mix of neutral and selected mutations with varying proportions across the different populations (orange row in fig.~\ref{fig:heatmap}B).
@@
     These variable proportions between populations can be explained by the effective number of individuals in the population ($\Ne$), a major driver of selection efficacy.
-    Since $\Ne$ is not directly measurable, a reasonable proxy usually used is the within a population (Watterson $\theta_w$).
-    We thus ordered populations by their levels of synonymous diversity (fig.~\ref{fig:diversity}A) and confirmed that higher synonymous diversity is typically accompanied by a smaller proportion of neutral mutations.
+    Since $\Ne$ is not directly measurable, a reasonable proxy usually used is the neutral diversity (Watterson $\theta_w$).
+    Assuming that synonymous positions are effectively neutral in mammals, we thus ordered populations by their levels of synonymous diversity (fig.~\ref{fig:diversity}A) and confirmed that higher synonymous diversity is typically accompanied by a smaller proportion of neutral mutations.
     This result suggests that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) are more likely to discriminate between advantageous and deleterious mutations (fig~S1-S5).
@@
     Finally, we reconstructed the substitutions in the terminal branches of the phylogenetic tree to determine the distribution of their selection coefficients.
-    For each population with available polymorphism data, we first reconstructed the ancestral sequence (which is different than the reference sequence), then we mapped the substitutions from the last genus split to this reconstructed ancestral sequence.
-    In these populations, we show that out of all polarized substitutions in the branches, between 10 and 13\% of all substitutions have an $\Sphy > 1$ (table S1) and between 25 and 30\% of all substitutions have an $\Sphy > 0$ (table S3).
+    For each population with available polymorphism data, we first reconstructed the ancestral sequence by replacing all variable site of the reference genome with the ancestral allele predicted by est-usfs, then we mapped the substitutions from the last genus split to this reconstructed ancestral sequence.
+    In these populations, we show that out of all polarized substitutions in the branches, between 10\% and 13\% of all substitutions have an $\Sphy > 1$ (table S1) and between 25\% and 30\% of all substitutions have an $\Sphy > 0$ (table S3).
     Most importantly, there is clear signal that the substitutions with an $\Sphy > 1$ have been positively selected since their ratio of non-synonymous over synonymous divergence, a ratio called $\dnds$, is between 1.15 and 1.68 in the different populations (table S1), meaning that mutations under maintenance selection with $\Sphy > 1$ reach fixation more frequently that synonymous mutations (supposedly neutral).
@@
     Finally, $\mathbb{P} [ \Spop > 1  \given  \Sphy > 1]$ is the part of the DFE estimated at the population-scale greater than 1, when we restricted our analysis on SNPs that are already predicted by mutation-selection models to have a selection coefficient greater than 1 (black fill for the category $\Sphy > 1$ in fig~\ref{fig:homo-afr-results}D and table S2).
-    Altogether, the probability for a mutation to be restoring the genome given that it is positively selected is obtained for each population, and varies between 10 and 26\% (table S2).
+    Altogether, the probability for a mutation to be restoring the genome given that it is positively selected is obtained for each population, and varies between 10\% and 26\% depending of the population (table S2).
     % Since adaptation does not fit the fitness predictions, the proportion of adaptive mutation is expected to be the same among SNPs which are predicted to be advantageous, and among SNPs which are predicted to be deleterious.
@@
     Thus, if we divide the $\dnds$ estimated on all substitutions, by the one estimated only on substitutions predicted to be deleterious, we directly get the proportion of the rate of evolution which is contributed by maintenance selection (see methods).
-    This way, we estimated that between 22 and 27\% of the evolutionary rate is due to maintenance positive selection (fig~\ref{fig:diversity}C \& table S3).
+    This way, we estimated that between 22\% and 27\% of the evolutionary rate is due to maintenance positive selection (fig~\ref{fig:diversity}C \& table S3).
 

### 2022-11-04 manuscript/include-MutSel-non-adaptive.tex
Reorganized the manuscript, substitutions then SNPs

@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Bos_taurus.IRBT.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Bos_taurus.IRBT.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Bos_taurus.IRBT.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Bos_taurus.IRBT.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Bos_taurus.UGBT.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Bos_taurus.UGBT.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Bos_taurus.UGBT.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Bos_taurus.UGBT.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.AUCH.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Capra_hircus.AUCH.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.AUCH.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Capra_hircus.AUCH.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.FRCH.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Capra_hircus.FRCH.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.FRCH.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Capra_hircus.FRCH.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.IRCA.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Capra_hircus.IRCA.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.IRCA.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Capra_hircus.IRCA.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.IRCH.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Capra_hircus.IRCH.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.IRCH.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Capra_hircus.IRCH.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.ITCH.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Capra_hircus.ITCH.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.ITCH.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Capra_hircus.ITCH.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.MOCH.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Capra_hircus.MOCH.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.MOCH.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Capra_hircus.MOCH.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Barbados.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Barbados.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Barbados.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Barbados.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Gambia.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Gambia.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Gambia.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Gambia.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Kenya.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Kenya.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Kenya.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Kenya.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Nevis.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Nevis.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Nevis.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Nevis.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Saint_Kitts.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Saint_Kitts.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Saint_Kitts.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Saint_Kitts.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.South_Africa.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.South_Africa.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.South_Africa.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.South_Africa.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Zambia.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Zambia.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Zambia.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Zambia.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Equus_caballus.up.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Equus_caballus.up.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Equus_caballus.up.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Equus_caballus.up.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.AFR.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Homo_sapiens.AFR.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.AFR.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Homo_sapiens.AFR.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.AMR.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Homo_sapiens.AMR.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.AMR.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Homo_sapiens.AMR.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.EAS.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Homo_sapiens.EAS.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.EAS.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Homo_sapiens.EAS.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.EUR.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Homo_sapiens.EUR.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.EUR.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Homo_sapiens.EUR.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.SAS.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Homo_sapiens.SAS.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.SAS.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Homo_sapiens.SAS.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROA.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Ovis_aries.IROA.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROA.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Ovis_aries.IROA.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROO.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Ovis_aries.IROO.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROO.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Ovis_aries.IROO.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROV.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Ovis_aries.IROV.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROV.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Ovis_aries.IROV.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.ISGC.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Ovis_aries.ISGC.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.ISGC.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Ovis_aries.ISGC.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.MOOA.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Ovis_aries.MOOA.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.MOOA.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Ovis_aries.MOOA.MutSel.polyDFE_C.pdf}
 \end{minipage}

### 2022-11-04 manuscript/include-SIFT-non-adaptive.tex
Reorganized the manuscript, substitutions then SNPs

@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Bos_taurus.IRBT.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Bos_taurus.IRBT.SIFT-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Bos_taurus.IRBT.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Bos_taurus.IRBT.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Bos_taurus.UGBT.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Bos_taurus.UGBT.SIFT-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Bos_taurus.UGBT.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Bos_taurus.UGBT.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.AUCH.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Capra_hircus.AUCH.SIFT-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.AUCH.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Capra_hircus.AUCH.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.FRCH.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Capra_hircus.FRCH.SIFT-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.FRCH.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Capra_hircus.FRCH.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.IRCA.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Capra_hircus.IRCA.SIFT-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.IRCA.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Capra_hircus.IRCA.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.IRCH.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Capra_hircus.IRCH.SIFT-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.IRCH.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Capra_hircus.IRCH.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.ITCH.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Capra_hircus.ITCH.SIFT-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.ITCH.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Capra_hircus.ITCH.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.MOCH.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Capra_hircus.MOCH.SIFT-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Capra_hircus.MOCH.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Capra_hircus.MOCH.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Barbados.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Barbados.SIFT-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Barbados.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Barbados.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Central_African_Republic.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Central_African_Republic.SIFT-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Central_African_Republic.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Central_African_Republic.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Ethiopia.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Ethiopia.SIFT-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Ethiopia.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Ethiopia.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Gambia.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Gambia.SIFT-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Gambia.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Gambia.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Kenya.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Kenya.SIFT-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Kenya.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Kenya.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Nevis.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Nevis.SIFT-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Nevis.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Nevis.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Saint_Kitts.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Saint_Kitts.SIFT-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Saint_Kitts.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Saint_Kitts.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.South_Africa.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.South_Africa.SIFT-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.South_Africa.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.South_Africa.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Zambia.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Zambia.SIFT-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Chlorocebus_sabaeus.Zambia.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Zambia.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Equus_caballus.up.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Equus_caballus.up.SIFT-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Equus_caballus.up.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Equus_caballus.up.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.AFR.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Homo_sapiens.AFR.SIFT-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.AFR.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Homo_sapiens.AFR.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.AMR.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Homo_sapiens.AMR.SIFT-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.AMR.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Homo_sapiens.AMR.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.EAS.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Homo_sapiens.EAS.SIFT-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.EAS.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Homo_sapiens.EAS.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.EUR.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Homo_sapiens.EUR.SIFT-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.EUR.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Homo_sapiens.EUR.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.SAS.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Homo_sapiens.SAS.SIFT-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.SAS.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Homo_sapiens.SAS.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROA.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Ovis_aries.IROA.SIFT-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROA.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Ovis_aries.IROA.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROO.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Ovis_aries.IROO.SIFT-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROO.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Ovis_aries.IROO.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROV.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Ovis_aries.IROV.SIFT-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.IROV.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Ovis_aries.IROV.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.ISGC.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Ovis_aries.ISGC.SIFT-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.ISGC.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Ovis_aries.ISGC.SIFT.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.MOOA.SIFT-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Ovis_aries.MOOA.SIFT-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/analysis/Ovis_aries.MOOA.SIFT.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Ovis_aries.MOOA.SIFT.polyDFE_C.pdf}
 \end{minipage}

### 2022-11-04 manuscript/main.tex
Reorganized the manuscript, substitutions then SNPs

@@
 \newcommand{\dnds}{\dn / \ds}
-\newcommand{\Sphy}{S}
+\newcommand{\Sphy}{S_{0}}
 \newcommand{\Sphyclass}{\mathcal{C}}
@@
 \newcommand{\given}{\mid}
-\newcommand{\Spop}{\beta}
+\newcommand{\Spop}{S}
 \newcommand{\SpopMean}{\overline{\Spop}}
@@
 
-\title{In mammals, an important proportion of advantageous mutations are repairing damaged genomes instead of creating adaptive innovations}
+\title{Up to 25\% of beneficial mutations in protein sequences are not adaptive innovations in mammals}
 
@@
     \begin{abstract}
-        Positive selection can be the result of adaptive evolution, driven by a change in environment or selective pressure.
-        However, positive selection can also be the result of what we call maintenance positive selection where advantageous mutations are reverting deleterious substitutions without any change of the environment.
-        The evolutionary outcomes of these two positive selections are drastically different.
-        While adaptive evolution acts as a diversifying force, maintenance positive selection stabilizes phenotypes and reduces diversity across species.
-        By leveraging polymorphism data in 28 populations and divergence data between 94 mammalian species, we estimate that around 25\% of observed substitutions are owed to maintenance positive selection.
-        Our work confirms that deleterious substitutions have accumulated in mammals and are currently being eliminated, resulting in widespread positive selection that is not adaptive evolution.
+        Mutations can be beneficial by bringing a new innovation to their bearer, allowing them to adapt to change in environments or in selection.
+        However, mutations can also be beneficial because they are repairing previous deleterious changes, simply restoring existing functions
+        In this study, we first estimated selective effects of mutations inside protein coding sequence, under a model assuming no adaptation at the phylogenetic scale.
+        We then estimated the proportion of beneficial mutations that are not adaptive innovations, and subsequently estimated their proportion among all beneficial mutations at the population scale.
+        Our work confirms that deleterious substitutions have accumulated in mammals and are currently being eliminated, resulting in up to 25\% of beneficial mutations that are not adaptive innovations, but instead are repairing previous deleterious changes.
+
     \end{abstract}
 
-    \keywords{Selection \and phylogenetic \and population genetics \and codon models \and adaptation }
+    \keywords{Adaptation \and beneficial mutations \and phylogenetic \and population-genetics \and codon models }
 
-    %\NS{on devrait plus placer le départ de l'intro dans un contexte historique, pour dire que de connaître si une mutation est avantageuse est la base de la génétique moléculaire (en citant des papiers clés)}
-    Adaptation is considered as the main process driving the diversity of forms and functions in the tree of life\cite{darwin_origin_1859}.
-    It allows species to live in new ecological niches, and to evolve in response to a change in environment\cite{darwin_origin_1859, merrell_adaptive_1994}.
-    The notion of adaptation, in its eco-evolutionary sense, is tightly linked to the notion of change, both of the environment (biotic and abiotic), and of the species responding to the latter\cite{merrell_adaptive_1994}.
-    With the discovery of DNA, the main support of heritable information, evolutionary geneticists looked for signatures of adaptation in genomes, such as to quantify it\cite{mcdonald_adaptative_1991, eyre-walker_distribution_2006}.
-    In that context arose the term of rate of adaptive evolution\cite{mcdonald_adaptative_1991, eyre-walker_distribution_2006, galtier_adaptive_2016}.
-    However, in contrast to adaptation in its eco-evolutionary sense, adaptive evolution is merely used as a synonymous of evolution under positive selection\cite{eyre-walker_distribution_2006}.
-    This leads to a misunderstanding on what is adaptation with the loss of the notion of change, and a misinterpretation of the so-called rate of adaptive evolution.
-    Indeed, adaptive evolution is not the only process which can lead to positive selection at the population scale\cite{sella_application_2005, mustonen_fitness_2009}.
-    At mutation-selection-drift equilibrium, a mutation restoring the ancestral allele which corresponded to an optimal fitness in a constant environment, but lost due to the fixation of a deleterious mutation by drift, will also be positively selected (fig.~\ref{fig:fitness-landscape}B).
-    In this study, this process will be referred to as maintenance positive selection.
-    %At the scale of a population, adaptive evolution and maintenance positive selection display different dynamics.
-    %While in the case of environmental change, the population as a whole is climbing the fitness landscape along an adaptive walk\cite{tenaillon_utility_2014}, in the case of maintenance positive selection, the population as a whole is at mutation-selection equilibrium and therefore merely stays at the same location in the fitness landscape\cite{sella_application_2005, mustonen_fitness_2009}.
-    %We can distinguish two main scenarios that can lead to such positive selection.
-    %In the first scenario, a mutation towards a state which was deleterious is now advantageous because of a change of environment.
-    %A change of environment could be a change of temperature, viral exposition but it could also be a change in another part of the species' genome.
-    %In the new environment, the mutation allows its bearer to survive and reproduce more than the others and thus will be positively selected.
-    %This process is typically referred to as adaptive evolution (fig.~\ref{fig:fitness-landscape}A), and meets the eco-evolutionary definition of adaptation.
-    At the population scale, maintenance positive selection and adaptive evolution are indistinguishable and both result in a positive transmission bias of the advantageous allele, but their consequences at a macro-evolutionary scale are fundamentally different.
-    While adaptive evolution promotes phenotype diversification (fig.~\ref{fig:fitness-landscape}C), maintenance positive selection promotes phenotype stability and preserves well established biological systems (fig.~\ref{fig:fitness-landscape}D).
-    It is thus essential to distinguish these two types of positive selection to understand the long term effects of selection on the diversification of species.
+    Adaptation is considered as the main process driving the diversity of forms and functions across the tree of life, as it enables species to access new ecological niches and also respond to changes in their environment\cite{darwin_origin_1859}.
+    In this context of adaptative evolution, a change in environment is echoed as a change of species' forms and functions, ultimately leaving signatures of accelerated changes in the species' genome\cite{merrell_adaptive_1994}.
+    This signature of an accelerated rate of changes, generating an excess of beneficial mutations is used to quantify adaptation (fig.~\ref{fig:fitness-landscape}A), for specific genes along a specific lineage\cite{mcdonald_adaptative_1991, smith_adaptive_2002a, welch_estimating_2006}.
+    The current availability of large scale genomic data and the development of theoretical models allowed to detect and quantify adaption across genes and lineages, which is now a common practice in evolutionary biology\cite{yang_statistical_2000, eyre-walker_genomic_2006, moutinho_variation_2019}.
+    Although these approaches led to a better understanding of the processes shaping molecular evolution, it had the effect to merely associate beneficial mutations with adaptive evolution, which should be dissociated since adaptive evolution is not the only process which can lead to beneficial mutations\cite{charlesworth_other_2007, mustonen_fitness_2009}.
+    Indeed, even in a constant environment for which the population is already adapted, a deleterious mutation in an individual can reach fixation in the population by genetic drift\cite{Ohta1992}.
+    Subsequently, a mutation restoring the ancestral state will thus be beneficial (fig.~\ref{fig:fitness-landscape}B), even though no change in the environment occurred\cite{hartl_compensatory_1996, sella_application_2005, mustonen_fitness_2009, cvijovic_fate_2015}.
+    More precisely, this restoration of the ancestral state can happen at another loci, in which case it is referred as compensating mutations\cite{hartl_compensatory_1996, mustonen_fitness_2009}.
+    Conversely, the restoration of the ancestral state can happen at the same locus, in which case it is referred as a beneficial back-mutation\cite{piganeau_estimating_2003, charlesworth_other_2007}, which are the focus of this study.
+    Taken together, not all beneficial mutations contribute to genetic innovation, and truly adaptive evolution can only be well estimated under the background of beneficial back-mutations\cite{keightley_what_2010, rice_evolutionarily_2015}.
+    It is thus essential to distinguish the underlying reason for the advantage brought by a beneficial mutation, a back-mutation repairing damaged genomes or creating an adaptive innovations.
 
-    At the gene level, positive selection can be quantified by comparing sequence variation inside a population with the sequence divergence from a sister species\cite{mcdonald_adaptative_1991}.
-    The basic idea is that advantageous mutations are expected to be observed in substitutions between species but not in polymorphism within a population because they reach fixation too quickly.
-    This method has been largely improved to account for possible bias-inducing factors such as the presence of weak positive selection, background selection and demographic fluctuations\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009, galtier_adaptive_2016, tataru_inference_2017}.
-    It has been applied across many organisms and enabled the discovery of widespread positive selection\cite{moutinho_variation_2019}.
-    However, the exact causes for this widespread occurrence of positive selection have been scarcely investigated\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009, galtier_adaptive_2016} %\NS{is it the case in the conclusion of the previous paper??
-would be nice to back it up with references}.
-    As mentioned above, not all advantageous mutations contribute to genetic innovation and diversification, and truly adaptive evolution can only be well estimated if maintenance positive selection is taken into account.
-    While adaptive evolution is unpredictable because it caused by an unpredictable change in the environment of organisms, the second is predictable because optimal states should be more or less the same for closely related organisms which share most of their environment and physiology.
-    A way to thus measure maintenance positive selection is to predict selection coefficients assuming a constant and stable fitness landscape estimated from the alignment of protein-coding genes.
-    For each site of the protein alignment, a first approximation would be to consider that the frequency of an amino acid is a proxy for its fitness, since for example a deleterious amino acid will be more likely to be absent in the alignment.
+    For an individual carrying a beneficial mutation, whether this mutation is new innovation as response to a change in environment or a beneficial back-mutation is indistinguishable.
+    Likewise, at the level of the population, both will result in a positive transmission bias of the beneficial allele.
+    However, their consequences at the macro-evolutionary scale are fundamentally different.
+    While adaptive evolution promotes phenotype diversification (fig.~\ref{fig:fitness-landscape}C), beneficial back-mutations promotes phenotype stability and preserves well established biological systems (fig.~\ref{fig:fitness-landscape}D).
+    Fundamentally, adaptive evolution is unpredictable because it caused by an unpredictable change in the environment and the underlying fitness landscape\cite{bazykin_changing_2015}.
+    On the other hand, beneficial back-mutations are predictable if the underlying stable fitness landscape is known.
+    As a result, a way to quantify the amount of back-mutation is to estimate the underlying fitness landscape, assuming it is constant and stable across time.
+
+    In this study, fitness landscapes of protein-coding genes are estimated from multi-species sequence alignments.
+    Multi-species sequence alignments can be used as a proxy for fitness, since for example a deleterious amino acid will be more likely to be absent in the alignment.
     One of the most used methods to make these predictions is SIFT (Sort Intolerant From Tolerant), which reliably detects deleterious mutations in many taxa\cite{ng_sift_2003, vaser_sift_2016}.
-    However, this method has two major shortcomings.
-    First, we know that a lot of mechanisms can influence amino acid frequency other than fitness (phylogeny, mutation biases, GC-biased gene conversion, mutational paths) which are not accounted for in SIFT\@.
-    Second, SIFT scores is not interpretable as a selection coefficient.
-    Contrarily, so-called mutation-selection codon models are rooted within a population genetics formalism\cite{halpern_evolutionary_1998, mccandlish_modeling_2014}.
+    However, SIFT scores is not interpretable as a selection coefficient.
+    Second, we know that a lot of mechanisms can influence amino acid frequency other than fitness (phylogenetic inertia, mutation biases, GC-biased gene conversion, mutational paths) which are not accounted for in SIFT\@.
+    Contrarily, so-called mutation-selection codon models are rooted within a population-genetic formalism\cite{halpern_evolutionary_1998, mccandlish_modeling_2014}.
     These phylogenetic codon models can disentangle processes of mutation at the DNA level and selection at the amino acid level.
-    Such codon models provide a nearly-neutral framework of evolution by estimating the fitness landscape over amino acid sequences for each site of the sequence (fig~\ref{fig:method}A) while taking into account non-adaptive processes impacting codon frequency\cite{halpern_evolutionary_1998, rodrigue_mechanistic_2010, tamuri_estimating_2012, latrille_improved_2022}.
-    From the fitness landscape obtained by fitting the model to the data, one can thus compute the scaled selection coefficient ($\Sphy$) of any non-synonymous mutations.
-    Importantly, mutation-selection codon models assume that the underlying fitness landscape is stable along the phylogeny (as in fig.~\ref{fig:fitness-landscape}B), thus a mutation with a positive $\Sphy$ would be driving the current site toward a fitter amino-acid, and such mutation is effectively considered under maintenance positive selection.
+    Such codon models provide a nearly-neutral framework of evolution by estimating the fitness landscape over amino acid sequences for each site of the sequence (fig~\ref{fig:method}A) while taking into account non-adaptive processes impacting codon frequency\cite{halpern_evolutionary_1998, rodrigue_mechanistic_2010, tamuri_estimating_2012, latrille_improved_2022a}.
+    From the fitness landscape obtained by fitting the model to the data, one can thus compute the scaled selection coefficient, denoted $\Sphy$, of any non-synonymous mutations.
+    Importantly, mutation-selection codon models assume that the underlying fitness landscape is stable along the phylogeny (as in fig.~\ref{fig:fitness-landscape}B), hence the null subscript $0$ for $\Sphy$.
+    As a result, a mutation with a positive $\Sphy$ would be driving the current site toward a fitter amino-acid, and thus considered a beneficial back-mutation repairing existing functions.
+    Altogether, our expectation if that beneficial back-mutations are detectable and scattered across the genomes, while at the same time some slightly deleterious mutations are reaching fixations at other loci, generating a balance at which genomes are constantly both damaged and repaired at different loci.
+    Even though each of these back-mutations is expected to have a small beneficial effect on their bearer, and that our assumptions may not always be valid, we expect that the genome-wide signature of beneficial back-mutations can be detected and quantified.
 
-    By integrating datasets at the species and population level, we can predict $\Sphy$ for each mutation currently segregating in a population (fig~\ref{fig:method}B).
-    Such a dataset can allow us to address different questions regarding positive selection affecting protein-coding DNA sequences.
-    Which proportion of the segregating polymorphisms in population are predicted toward a more optimal amino acid (positive $\Sphy$), thus supposedly under maintenance positive selection?
-    Are these polymorphisms effectively under positive selection at the scale of populations?
-    Finally, how much of positive selection observed in populations is due to maintenance positive selection?
+    By integrating datasets at different scales (phylogeny and population), we can predict whether substitutions in terminal lineages or any mutation currently segregating in a population are beneficial back-mutations, i.e with a positive $\Sphy$ (fig~\ref{fig:method}B).
+    Such a dataset can allow us to address different questions regarding the selection affecting protein-coding DNA sequences.
+    Are we empirically observing beneficial back-mutations that reached fixation recently, and one that are currently segregating in populations?
+    Are they effectively beneficial for the individual carrying it?
+    Conversely, what is the probability for a beneficial mutation to be a back-mutation?
+    In other words, can we find empirical evidence and can we quantify the amount of beneficial mutations that are restoring damaged genomes instead of creating adaptive innovations.
     To answer these questions, we estimated the fitness landscape of amino-acids for long-term evolution using available multiple sequence alignments between mammalian species\cite{ranwez_orthomam_2007, howe_ensembl_2021}.
-    We then integrated data at the phylogenetic and population scale to estimate divergence and polymorphism, respectively, across the entire exome for 28 populations from 6 genera (\textit{Equus},  \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus} and \textit{Homo}; fig.~\ref{fig:method}A\&B).
+    We then integrated data at the phylogenetic and population scale to estimate the amount of beneficial mutations across the entire exome for 28 populations from 6 genera (\textit{Equus},  \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus} and \textit{Homo}; fig.~\ref{fig:method}A\&B).
 
@@
             At the phylogenetic scale (panel C), this phenomena promotes phenotype diversification across species.
-            Under a stable fitness landscape (panel B), the protein sequence only fluctuates at the mutation-selection balance.
-            All the mutations reaching fixation are either slightly deleterious and reaching fixation due to drift or are advantageous and restoring a more optimal amino acid.
+            Under a stable fitness landscape (panel B), all the mutations reaching fixation are either slightly deleterious and reaching fixation due to drift, or are beneficial back-mutations restoring a more optimal amino acid.
+            Scarce beneficial back-mutations are likely to reach fixation and a bulk of deleterious mutations are eventually reaching fixation due to their sheer mass.
+            Across the genome, this process generate a balance at which genomes are constantly both damaged and repaired at different loci.
             At the phylogenetic scale (panel D), this phenomena promotes promotes phenotype stability and preserves well established biological systems.
@@
         \centering
-        \includegraphics[width=\textwidth, page=1] {artworks/figure.method}
+        \includegraphics[width=\textwidth, page=1] {artworks/figure.method.proba}
         \caption{
-            Integrating divergence and polymorphism.
+            Integrating datasets at different scales.
             At the phylogenetic level (panel A), the amino acid Wrightian fitness for each site is estimated from protein-coding DNA alignments using mutation-selection codon models.
-            At the population-genetic level (panel B), for each observed single nucleotide polymorphism (SNP) segregating in the population, selection coefficient ($\Sphy$) are computed as the difference in amino acid fitness between the ancestral and derived variants.
-            Mutation-selection codon models that the underlying fitness landscape is stable along the phylogeny, taking into account only non-adaptive evolution, thus a mutation with a positive $\Sphy$ would be driving the current site toward are fitter amino-acid, and such mutation are effectively considered under maintenance positive selection.
+            Mutation-selection models assume a stable fitness landscape, taking into account only non-adaptive evolution.
+            A mutation with a $\Sphy > 1$ would be driving the current site toward are fitter amino-acid, and such mutation are considered a beneficial back-mutation repairing existing functions (panel B).
+            At the population scale (panel C), each single nucleotide polymorphism (SNP) segregating in the population can be classified as a beneficial back-mutation (in red) or not.
+            The number of derived allele allow to estimate the probability of beneficial mutations at the population scale, for all SNPs or among back-mutations (panel D).
+            The probability of back-mutation is obtained as their fraction among all possible mutations from the ancestral genome sequence (panel E).
+            Altogether, we can estimate the probability of back-mutations among all beneficial ones, using Bayes' theorem (panel F).
         }
@@
 
-    \subsection*{SNPs which are predicted to be advantageous are positively selected at the population scale}
+    \subsection*{Back-mutations in the terminal lineages}
+    We first probed for empirical evidence of beneficial back-mutation in the terminal lineages, which should be effectively beneficial.
+    We thus reconstructed the substitutions occurring along the terminal branches of the phylogenetic tree.
+    For each substitution, we estimated its scaled selection coefficient ($\Sphy$) based on the stable fitness landscape of amino-acids estimated at the scale of the mammals' phylogeny (fig.~\ref{fig:method}A).
+    We showed that among all the substitutions in the terminal lineages, between 10 and 13\% had $\Sphy > 1$ (table SX) and between 25 and 30\% had $\Sphy > 0$ (table SX).
+    Substitutions with $\Sphy > 1$ have been beneficial since the ratio of non-synonymous over synonymous divergence, called $\dnds$, was estimated to be between 1.15 and 1.68 in the different lineages (table SX).
+    This meant that beneficial back-mutations with $\Sphy > 1$ reach fixation more frequently than synonymous mutations, which are supposed to be neutral, thus are effectively beneficial.
+    This also means that the ratio $\dnds$ usually used to detect adaptation while relying on substitutions between close species\cite{mcdonald_adaptative_1991, galtier_adaptive_2016} or at the phylogenetic scale\cite{goldman_codonbased_1994, yang_codonsubstitution_2002} is overinflated due to beneficial back-mutations.
+    Then, $\dnds$ computed exclusively on non-synonymous sites with a $\Sphy < 0$ only represent the rate of evolution discarding beneficial back-mutations by construction.
+    Thus, if we divide the $\dnds$ estimated on all substitutions by the one estimated only on substitutions predicted to be deleterious, we directly get the proportion of the rate of evolution which is contributed by beneficial back-mutations (see methods).
+    This way, we estimated that between 22\% and 27\% of $\dnds$ is inflated because of beneficial back-mutations (table SX).
 
-    For each non-synonymous SNP observed at the population level, we predicted its scaled selection coefficient ($\Sphy$) from amino acid fitnesses estimated at the mammalian scale (fig.~\ref{fig:method}B).
-    Then we ask whether the variants that are predicted to be advantageous, thus supposedly under maintenance selection, are showing signatures of short term positive selection.
-    For example, if a variant is found to be fixed in many mammals but not in ancestral humans, and a mutation in humans is toward the mammalian version, is this mutation advantageous for the individual carrying it?
-    At the population level (e.g.~in humans of Asian descent in fig.~\ref{fig:homo-afr-results}), we divided all observed SNPs in 5 classes of predicted selection coefficient: severely deleterious with $\divStrongDel$, deleterious with $\divDel$, weakly deleterious with $\divWeakDel$, weakly advantageous with $\divWeakAdv$ and advantageous with $\divAdv$ (fig.~\ref{fig:homo-afr-results}B).
-    In each of theses classes, SNPs are then grouped by the number of derived alleles in the population (fig.~\ref{fig:homo-afr-results}C), generating a so called site-frequency spectrum (SFS).
-    Compared to synonymous mutations which are supposedly neutral (black line in fig.~\ref{fig:homo-afr-results}C), mutations predicted to be deleterious (blue and green lines in fig.~\ref{fig:homo-afr-results}C) are underrepresented at high frequencies in the population, a signature of ongoing purifying selection.
+    \subsection*{Back-mutations in the populations}
+    Given that beneficial back-mutations are effectively selected for, we then ask which proportion of new mutations are beneficial back-mutations.
+    For each population with available polymorphism data, we first reconstructed the ancestral sequence (instead of the reference sequence) at the base of the population genealogy.
+    From this reference sequence, we computed the scaled selection coefficient ($\Sphy$) for each possible non-synonymous mutations.
+    We thus obtained the distribution of fitness effects (DFE) of new mutations from the ancestral sequence in \textit{Homo sapiens} (fig.~\ref{fig:homo-afr-results}A), under the assumption of the stable fitness landscape.
+    Because $\Sphy$ is based on estimation of fitnesses at the mammalian scale, mutations with $\Sphy>1$ are considered beneficial back-mutations.
+    Beneficial back-mutations only represents ~1.5\% of all possible new mutations (red in fig.~\ref{fig:homo-afr-results}A, table~SX).
+    However, when focusing on the mutations that are observed in populations, namely single nucleotide polymorphism (SNP), beneficial back-mutations represents ~8.5\% of all observed mutations (red in fig.~\ref{fig:homo-afr-results}B, table~SX).
+
+    Additionally, in populations, the frequencies at which SNPs are segregating is informative of their selective effect, e.g.
+deleterious SNPs are segregating at lower frequencies because they are purified.
+    As such, methods have been developed to estimate the distribution of fitness effect (DFE) at the population scale by gathering information across many SNPs\cite{eyre-walker_distribution_2006a, eyre-walker_estimating_2009a, galtier_adaptive_2016, tataru_inference_2017}.
+    These methods offer a unique opportunity to compare the DFE at the population scale ($\Spop$) and at the phylogenetic scale ($\Sphy$).
+    In order to estimate the DFE at the population level and gather robust statistical estimates, we grouped SNPs observed at the population level (e.g.~in humans of African descent in fig.~\ref{fig:homo-afr-results}) in 5 classes of predicted selection coefficient: severely deleterious with $\divStrongDel$, deleterious with $\divDel$, weakly deleterious with $\divWeakDel$, weakly beneficial with $\divWeakAdv$ and beneficial with $\divAdv$ (fig.~\ref{fig:homo-afr-results}B).
+    In each of theses classes, the number of derived alleles in the population for each SNPs is used to generate a site-frequency spectrum (SFS) (fig.~\ref{fig:homo-afr-results}C).
+    Compared to synonymous mutations which are supposedly neutral (black line in fig.~\ref{fig:homo-afr-results}C), mutations predicted to be deleterious (blue and green lines in fig.~\ref{fig:homo-afr-results}C) were, as expected, underrepresented at high frequencies in the population, a signature of ongoing purifying selection.
     However, these observations remain qualitative.
@@
     This model uses the count of derived alleles for each frequency class of the SFS to infer the distribution of fitness effects (DFE) of the region under study.
-    The model uses both the number of sites ($L$) for each category (fig.~\ref{fig:homo-afr-results}A, see Material and Methods), and the counts of synonymous derived allele as a neutral model, which allow to control for demographic effects, and polarization errors when inferring the ancestral state.
-    These population-based models cannot give a specific estimate of the selection coefficient at the population-genetic scale ($\Spop$) for each SNP, but by gathering information across many SNPs, these models can estimate the proportion of advantageous mutations ($\PpolyAdv$), of nearly-neutral mutations ($\PpolyNeutral$) and of deleterious mutations ($\PpolyDel$) (fig.~\ref{fig:homo-afr-results}D).
-    We found that SNPs predicted to be deleterious given their selection coefficient $\Sphy$ across mammals are effectively purged at the population-genetic scale, demonstrating that purifying selection is largely predictable and amino acids with low fitness across mammals are effectively purged away in each population.
-    Notably, SNPs predicted to be advantageous given their selection coefficient $\Sphy$, thus supposedly under maintenance selection, are indeed under positive selection at the population-genetic scale, confirming that there is a local ongoing selection towards amino acids that are restoring the optimally functioning protein.
-    In between these two extremes, mutations predicted to be weakly selected (cyan and orange in fig.~\ref{fig:homo-afr-results}) are effectively composed of neutral, positively and negatively selected mutations.
+    The model uses the number of sites ($L$) for each category (fig.~\ref{fig:homo-afr-results}A, see Material and Methods), the counts of synonymous derived allele as a neutral model, which allow to control for demographic effects, and polarization errors when inferring the ancestral state.
+    We could estimate the proportion of beneficial mutations ($\PpolyAdv$), nearly-neutral mutations ($\PpolyNeutral$) and deleterious mutations ($\PpolyDel$) for each class of selection previously defined (fig.~\ref{fig:homo-afr-results}D).
+    We found that SNPs predicted to be deleterious based on the selection coefficient $\Sphy$ estimated across the phylogeny of mammals were effectively purged at the population scale.
+    Purifying selection is therefore largely predictable and amino acids with low fitness across mammals are effectively purged away in each population.
+    Then, SNPs predicted to be beneficial based on the selection coefficient $\Sphy$ estimated at the scale of the phylogeny of mammals are indeed beneficial for individuals currently bearing them.
+    These results confirmed that selection towards amino acids that are restoring existing function is ongoing in these populations.
+    Between these two extreme cases, SNPs predicted to be weakly selected (cyan and orange in fig.~\ref{fig:homo-afr-results}) were effectively composed of neutral, beneficial and deleterious mutations.
 
-    We replicated such experiment across 28 populations (fig.~\ref{fig:heatmap}), and found that mutations predicted to be deleterious are indeed purged at the population-genetic scale (blue and green rows in fig.~\ref{fig:heatmap}A).
-    However, mutations predicted to be weakly advantageous ($\divWeakAdv$) are composed of a mix of neutral and selected mutations with varying proportions across the different populations (orange row in fig.~\ref{fig:heatmap}B).
-    Similarly, mutations predicted to be advantageous ($\divAdv$, under maintenance selection) are found to be positively selected with varying proportions across populations (red row in fig.~\ref{fig:heatmap}C).
-    In other words, mutations predicted to be deleterious by the mutation-selection model are effectively purified away in any population, while mutations predicted to be advantageous can be either neutral or advantageous depending on the population.
-    These variable proportions between populations can be explained by the effective number of individuals in the population ($\Ne$), a major driver of selection efficacy.
-    Since $\Ne$ is not directly measurable, a reasonable proxy usually used is the within a population (Watterson $\theta_w$).
-    We thus ordered populations by their levels of synonymous diversity (fig.~\ref{fig:diversity}A) and confirmed that higher synonymous diversity is typically accompanied by a smaller proportion of neutral mutations.
-    This result suggests that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) are more likely to discriminate between advantageous and deleterious mutations (fig~S1-S5).
-    Alternatively stated, mutations in populations with low diversity (e.g.~\textit{Homo}) are effectively nearly-neutral and behave as would a neutral mutation.
-    This result is qualitatively in accordance with the nearly-neutral theory of evolution which argues that mutations are less efficiently selected for in small populations.
-    %, especially for mutations already predicted to be nearly-neutral at the phylogenetic scale (fig~S8-S9).
+    We replicated our experiment across 28 populations of different mammal species (fig.~\ref{fig:heatmap}) and found that SNPs predicted to be deleterious were indeed purged at the population scale (blue and green rows in fig.~\ref{fig:heatmap}A).
+    However, SNPs predicted to be weakly beneficial ($\divWeakAdv$) were composed of a mix of neutral and selected mutations with varying proportions across the different populations (orange row in fig.~\ref{fig:heatmap}B).
+    Finally, SNPs predicted to be beneficial back-mutations ($\divAdv$) were found to be beneficial with varying proportions across populations (red row in fig.~\ref{fig:heatmap}C).
+    The variable proportions found between populations can be explained by the effective number of individuals in the population ($\Ne$), which is well-known to be a major driver of selection efficacy.
+    Since $\Ne$ is not directly measurable, we used the Watterson $\theta_w$ as a proxy to order populations by their levels of synonymous diversity.
+    Higher synonymous diversity is associated with a smaller proportion of neutral mutations (fig.~\ref{fig:diversity}A).
+    This result confirms the nearly-neutral theory and suggests that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) are more likely to discriminate between beneficial and deleterious mutations (fig~SX-SX), while mutations in populations with low diversity (e.g.~\textit{Homo}) are effectively nearly-neutral.
 
-    Finally, we reconstructed the substitutions in the terminal branches of the phylogenetic tree to determine the distribution of their selection coefficients.
-    For each population with available polymorphism data, we first reconstructed the ancestral sequence (which is different than the reference sequence), then we mapped the substitutions from the last genus split to this reconstructed ancestral sequence.
-    In these populations, we show that out of all polarized substitutions in the branches, between 10 and 13\% of all substitutions have an $\Sphy > 1$ (table S1) and between 25 and 30\% of all substitutions have an $\Sphy > 0$ (table S3).
-    Most importantly, there is clear signal that the substitutions with an $\Sphy > 1$ have been positively selected since their ratio of non-synonymous over synonymous divergence, a ratio called $\dnds$, is between 1.15 and 1.68 in the different populations (table S1), meaning that mutations under maintenance selection with $\Sphy > 1$ reach fixation more frequently that synonymous mutations (supposedly neutral).
-    These observed substitutions are likely to have been positively selected because they restored a more optimal state, not because they are driving innovations to a new environment or a new function.
-    %This also means that the ratio $\dnds$ usually used to detect adaptation while relying on substitutions between close species\cite{mcdonald_adaptative_1991, galtier_adaptive_2016} or at the phylogenetic scale\cite{goldman_codonbased_1994, yang_codonsubstitution_2002} is overestimated.
+    \subsection*{Proportion of back-mutations among all beneficial mutations}
 
-    \subsection*{A large proportion of advantageous mutations are under maintenance selection}
+    Finally, we propose a new measure to estimate the probability for a beneficial mutation to be a back-mutation, i.e. $\mathbb{P} [ \Sphy > 1  \given  \Spop > 1]$.
+    We obtained from the analyses above the following probabilities $\mathbb{P} [ \Sphy > 1 ]$, $\mathbb{P} [ \Spop > 1 ]$, $\mathbb{P} [ \Spop > 1  \given  \Sphy > 1]$.
+    First, $\mathbb{P} [ \Sphy > 1 ]$ is the probability for a beneficial back-mutation ($\Sphy > 1$) from the ancestral sequence (red fill of histogram in fig~\ref{fig:homo-afr-results}A and table S2).
+    Second, $\mathbb{P} [ \Spop > 1 ]$ is the probability of mutation to be beneficial at the level of the population ($\Spop > 1$), estimated from all available SNPs (black fill in fig~\ref{fig:diversity}A and table S2).
+    Finally, $\mathbb{P} [ \Spop > 1  \given  \Sphy > 1]$ is the probability for a back-mutation ($\Sphy > 1$) to be effectively beneficial at the level of the population ($\Spop > 1$), when we restricted our analysis on SNPs that are already predicted to be beneficial back-mutations (black fill for the category $\Sphy > 1$ in fig~\ref{fig:homo-afr-results}D and table S2).
+    Combining these probabilities using Bayes theorem, we now obtain the probability for a beneficial mutation to be a back-mutation $\mathbb{P} [ \Sphy > 1  \given  \Spop > 1]$ (see Material and Methods).
+    We estimated $\mathbb{P} [ \Sphy > 1  \given  \Spop > 1]$ across all populations sampled and obtained a proportion that varies between 10 and 26\% (table S2).
 
-    We then sought to estimate the proportion of positive selection that is due to maintenance selection.
-    Mathematically, this corresponds to $\mathbb{P} [ \Sphy > 1  \given  \Spop > 1]$, namely the probability for a mutation to be due to maintenance selection, given it is positively selected.
-    This probability is given by Bayes formula (see methods), given we have access to $\mathbb{P} [ \Sphy > 1 ]$, $\mathbb{P} [ \Spop > 1 ]$, $\mathbb{P} [ \Spop > 1  \given  \Sphy > 1]$.
-    First, $\mathbb{P} [ \Sphy > 1 ]$ the probability for a mutation away from the ancestral sequence to have $\Sphy > 1$ (red fill of histogram in fig~\ref{fig:homo-afr-results}A and table S2).
-    Second, $\mathbb{P} [ \Spop > 1 ]$ is is the part of the DFE estimated at the population-scale greater than 1 when we used all the SNPs available in the population (black fill in fig~\ref{fig:diversity}A and table S2).
-    Finally, $\mathbb{P} [ \Spop > 1  \given  \Sphy > 1]$ is the part of the DFE estimated at the population-scale greater than 1, when we restricted our analysis on SNPs that are already predicted by mutation-selection models to have a selection coefficient greater than 1 (black fill for the category $\Sphy > 1$ in fig~\ref{fig:homo-afr-results}D and table S2).
-    Altogether, the probability for a mutation to be restoring the genome given that it is positively selected is obtained for each population, and varies between 10 and 26\% (table S2).
-    % Since adaptation does not fit the fitness predictions, the proportion of adaptive mutation is expected to be the same among SNPs which are predicted to be advantageous, and among SNPs which are predicted to be deleterious.
-    % Thus the proportion of advantageous mutations among SNPs which are predicted to be deleterious directly correspond to the proportion of all mutations which are adaptive.
-    % So if we divide the proportion of mutations which are predicted to be advantageous among supposedly deleterious SNPs by the proportion of mutations which are predicted to be advantageous among all SNPs, we directly get the proportion of mutations which are adaptive among advantageous ones.
-    % It results that 20 to 40\% of advantageous mutations are due to maintenance positive selection (fig~\ref{fig:diversity}B \& table S2).
-
-    Focusing on substitutions in the terminal lineages, we can consider that the total $\dnds$ encompasses the rate of evolution for deleterious and advantageous (both adaptive and non-adaptive) substitutions.
-    Then, the $\dnds$ computed exclusively on non-synonymous sites with a $\Sphy < 0$ only represent the rate of evolution of solely deleterious and adaptive substitutions, discarding maintenance selection by construction.
-    Thus, if we divide the $\dnds$ estimated on all substitutions, by the one estimated only on substitutions predicted to be deleterious, we directly get the proportion of the rate of evolution which is contributed by maintenance selection (see methods).
-    This way, we estimated that between 22 and 27\% of the evolutionary rate is due to maintenance positive selection (fig~\ref{fig:diversity}C \& table S3).
-
-    Interestingly, the proportion of maintenance selection among advantageous ones and the proportion of the rate of evolution explained by maintenance positive selection do not show a clear relationship with the synonymous diversity within a population (Watterson $\theta_w$), a proxy for the effective population size (fig.~\ref{fig:diversity}B and C).
-    Indeed, the relationship between $\Ne$ and the proportion of maintenance selection is not trivial and should highly depend on time scales.
-    A population which experienced a high long term $\Ne$ in the past is supposed to be closer to the optimal state (under a stable fitness landscape), and should not leave much space for maintenance selection.
-    On the other hand a high short term $\Ne$ will induce more extreme fitness effects and a larger proportion of mutations will be positively selected (otherwise effectively neutral), thus increasing the proportion of maintenance selection.
-    Overall, the proportion of maintenance selection is expected to be more dependent on effective population size contraction or expansion rather than on the short term effective population size captured by the synonymous diversity.
+    The proportion of back-mutations among all beneficial one did not show a clear relationship with the synonymous diversity within a population (Watterson $\theta_w$) (fig.~\ref{fig:diversity}B).
+    Indeed, the relationship between $\Ne$ and the proportion of beneficial back-mutations is not trivial and should highly depend on time scales\cite{charlesworth_other_2007}.
+    A population that experienced a high $\Ne$ along its evolutionary time should be closer to the optimal state under a stable fitness landscape because of the higher efficacy of selection.
+    This should decrease the probability of beneficial back-mutations.
+    On the other hand, a high $\Ne$ over a short evolutionary time will induce more extreme fitness effects and a larger proportion of mutations will be beneficial (otherwise effectively neutral), thus increasing the proportion of beneficial back-mutations.
+    Overall, the proportion of beneficial back-mutations is expected to be more dependent on effective population size contraction or expansion rather than on the short term effective population size captured by the synonymous diversity\cite{charlesworth_other_2007}.
 
@@
         \caption{
-            Panel A: Histogram of predicted selection coefficients ($\Sphy$) for all possible mutations away from the ancestral human genome, giving the number of sites ($L$, in y-axis) across the genome with a given $\Sphy$.
-            Mutations are divided into 5 classes: severely deleterious (blue), deleterious (green), weakly deleterious (light green), weakly advantageous (yellow) and advantageous (red, supposedly under maintenance selection).
-            Panel B. Histogram of predicted selection coefficients ($\Sphy$) for all observed mutations in a sample of 8 individuals (out of 512 in the original dataset) of African descent.
+            Panel A: Distribution of fitness effects ($\Sphy$), predicted for all possible mutations away from the ancestral human genome.
+            Mutations are divided into 5 classes of selection: severely deleterious (blue), deleterious (green), weakly deleterious (light green), weakly beneficial (yellow) and beneficial (red, supposedly beneficial back-mutations).
+            Panel B. Distribution of fitness effects ($\Sphy$) for all observed SNPs in a sample of 8 individuals (out of 512 in the original dataset) of African descent.
             If they are less mutations observed than expected, this class is thus undergoing purifying selection.
             Panel B: The site-frequency spectrum (SFS) represents the proportion of mutations (y-axis) with a given number of derived alleles in the population (x-axis).
-            SFS are drawn for a random sample of 16 alleles (mean in solid line and standard deviation in filled color) for each class of selection coefficient and for synonymous mutations which are supposedly neutral (black).
+            SFS are drawn for a random sample of 16 alleles (mean in solid line and standard deviation in filled color) for each class of selection and for synonymous mutations which are supposedly neutral (black).
             At high frequencies, supposedly severally deleterious mutations are underrepresented.
             Panel D.
-For each class of selection (and for the set of all non-synonymous mutations), information from the SFS and the expected total mutation rate are combined at the population-genetic scale to estimate the proportion of advantageous mutations $\PpolyAdv$, of nearly-neutral mutations $\PpolyNeutral$ and of deleterious mutations $\PpolyDel$.
+For each class of selection (and for the set of all non-synonymous mutations), information from the SFS and the distribution of fitness effects are combined at the population scale to estimate the proportion of beneficial mutations $\PpolyAdv$, of nearly-neutral mutations $\PpolyNeutral$ and of deleterious mutations $\PpolyDel$.
         }
@@
             Reproducibility of results shown in figure~\ref{fig:homo-afr-results} in 28 populations across 6 genera.
-            For each class of selection at the phylogenetic scale ($\Sphyclass \in \{ \divStrongDel, \divDel,  \divWeakDel,  \divWeakAdv, \divAdv \}$, in rows), site-frequency spectra and total number of sites are combined at the population-genetic scale to estimate the proportion of advantageous mutations ($\PpolyAdv$) in the top panel, of nearly-neutral mutations ($\PpolyNeutral$) in the middle panel and of deleterious mutations ($\PpolyDel$) in the bottom panel.
+            For each class of selection at the phylogenetic scale ($\Sphyclass \in \{ \divStrongDel, \divDel,  \divWeakDel,  \divWeakAdv, \divAdv \}$, in rows), site-frequency spectra and total number of sites are combined at the population scale to estimate the proportion of beneficial mutations ($\PpolyAdv$) in the top panel, of nearly-neutral mutations ($\PpolyNeutral$) in the middle panel and of deleterious mutations ($\PpolyDel$) in the bottom panel.
         }.
@@
             Panel A.
-For each population, the proportion of advantageous ($\PpolyAdv$), nearly-neutral ($\PpolyNeutral$) and of deleterious ($\PpolyDel$) mutations estimated at the population-genetic scale using all SNPs available.
+For each population, the proportion of beneficial ($\PpolyAdv$), nearly-neutral ($\PpolyNeutral$) and of deleterious ($\PpolyDel$) mutations estimated at the population scale using all SNPs available.
             Population are sorted for increased synonymous diversity.
             Panel B.
-Probability for a mutation to be due to maintenance positive selection, given it is positively selected ($\mathbb{P} [ \Sphy > 1  \given  \Spop > 1]$ in y-axis), shown as a function of the synonymous diversity (Watterson $\theta_w$ in x-axis).
-            Panel C.
-$R(\dnds)=\dfrac{\dnds - \dn(\Sphy < 0) / \ds}{\dnds}$ is the fraction of divergence ($\dnds$) that is due to maintenance positive selection, where $\dnds$ is compared to the estimated divergence when we removed maintenance selection $\dn(\Sphy < 0)/\ds$.
-            $R(\dn)$ (y-axis) is shown as a function of the synonymous diversity (Watterson $\theta_w$ in x-axis).
+Proportion of beneficial back-mutations among all beneficial mutations ($\mathbb{P} [ \Sphy > 1  \given  \Spop > 1]$ in y-axis), shown as a function of the synonymous diversity (Watterson $\theta_w$ in x-axis).
         }
@@
 
-    % Our study is a bridge between phylogenetic and population genetics
-    From a theoretical evolution perspective, we have found that we can use phylogenetic signals and mutation-selection codon models to predict the selection coefficient of a mutation.
-    However, we so far assumed no changes in effective population size while it has been established that population size changes have a major effect on selection dynamics\cite{lanfear_population_2014, jones_shifting_2017, platt_protein_2018}.
-    Mutation-selection models with changes in effective population sizes along the phylogeny have been developed\cite{latrille_inferring_2021}, but are, for the moment, too computational intensive to be performed genome-wide.
-    Hybrid mutation-selection and $\omega$-based codon models could provide a way forward\cite{brevet_reconstructing_2021}.
-    Moreover, SIFT scores based on amino acid alignments across species have also been found to be informative of the selection pressure exerted at the population scale\cite{chen_hunting_2021}.
-    Accordingly, our study shows that sites with a higher SIFT score at the phylogenetic scale are more positively selected in the different populations (supp.\ mat\  section SIFT scores).
-    In practice, SIFT scores are more coarse grained, with for example a bulk of mutations with a score of 1.0 (the highest), and does not provide a boundary between advantageous and deleterious mutations, nor are they based on a population-genetics formalism.
+    \subsection*{a bridge between phylogenetic and population-genetics}
+    In this study, we first estimated selective effects of mutations inside protein coding sequence, under a model assuming no adaptation at the phylogenetic scale.
+    We then estimated the proportion of beneficial mutations that are not adaptive innovations, and subsequently estimated their proportion among all beneficial mutations at the population scale.
+    Our work confirms that deleterious substitutions have accumulated in mammals and are currently being eliminated, resulting in up to 25\% of beneficial mutations that are not adaptive innovations, but instead are repairing previous deleterious changes.
 
-    Biologically, another mechanism which generate maintenance positive selection is compensatory mutations, which are repairing damage caused by deleterious mutations at another site in the genome and generating a widespread signal of non-adaptive positive selection\cite{hartl_compensatory_1996, pollock_strong_2014, starr_epistasis_2016}.
+    From a theoretical evolution perspective, we have found that we can use phylogenetic signals and mutation-selection codon models to predict the selection coefficient of a mutation ($\Sphy$).
+    However, we so far assumed no changes in effective population size along the phylogeny while it has been established that population size changes have a major effect on selection dynamics\cite{lanfear_population_2014, jones_shifting_2017, platt_protein_2018}.
+    Mutation-selection models with changes in effective population sizes along the phylogeny have been developed\cite{latrille_inferring_2021a}, but are, for the moment, too computational intensive to be performed genome-wide.
+    Hybrid mutation-selection and $\omega$-based codon models could provide a way forward to in integrate site-specific selection and branch-specific drift\cite{brevet_reconstructing_2021a}.
+    As for the estimate of selection, SIFT scores based on amino acid alignments across species have also been found to be informative of the selection pressure exerted at the population scale\cite{chen_hunting_2021}.
+    Our study indeed showed that sites with a higher SIFT score at the phylogenetic scale are more beneficial in the different populations (supp.\ mat\  section SIFT scores).
+    In practice, SIFT scores are more coarse grained, with for example a bulk of mutations with a score of 1.0 (the highest), and does not provide a boundary between beneficial and deleterious mutations, nor are they based on population-genetic formalism.
+
+    Biologically, another mechanism which generate non-adaptive beneficial mutations is compensatory mutations, which are repairing damage caused by deleterious mutations at another loci in the genome and generating a widespread signal of non-adaptative evolution\cite{hartl_compensatory_1996, pollock_strong_2014, starr_epistasis_2016}.
     In our study we focused on mutations toward a more optimal amino-acid at a given site, not accounting for compensatory mutations since we assumed a model of fitness landscape without epistasis.
-    These models without epistasis provide a reasonable estimate of average fitness profiles\cite{youssef_consequences_2020}.
-    But most importantly, we argue that our estimation of the amount of maintenance positive selection is an underestimation, and that accounting for compensatory mutations by means of epistasis would mechanically increase that amount.
-    Indeed, a fluctuating fitness landscape due to an external forces (e.i.
-changes in environment) results in an acceleration of the rate of evolution\cite{ rodrigue_detecting_2017, rodrigue_bayesian_2021} which generates epistatic mutations that are immediately beneficial\cite{gong_epistatically_2014}.
-    On the contrary, pervasive epistasis generates the opposite, an entrenchment\cite{goldstein_evolutionary_2004, goldstein_nonadaptive_2015} resulting in a slowing down of the rate evolution\cite{rodrigue_detecting_2017, patel_epistasis_2022} or a standstill\cite{youssef_evolution_2022}.
-    In other words, under pervasive epistasis, finding empirical evidence for maintenance selection is harder since restoring mutations become less and less likely to occur over time\cite{goldstein_nonadaptive_2015, goldstein_sequence_2017, park_epistatic_2022}.
-    Our study thus shows that maintenance selection should not be overlooked, and we argue that both maintenance selection and compensatory mutations play an important role in preventing our genome from collapsing under a mutation load.
+    As shown in other studies, these models without epistasis provide a reasonable estimate of average fitness profiles\cite{youssef_consequences_2020}.
+    But most importantly, we argue that our estimation of the amount of beneficial back-mutations is an underestimation, and that accounting for compensatory mutations by means of epistasis would mechanically increase our estimate.
+    Indeed, a fluctuating fitness landscape due to an external forces (i.e.
+changes in environment) results in an acceleration of the rate of evolution\cite{ rodrigue_detecting_2017, rodrigue_bayesian_2021}, which generates epistatic mutations that are immediately beneficial\cite{gong_epistatically_2014}.
+    In contrast, pervasive epistasis generates the opposite pattern, an entrenchment\cite{goldstein_evolutionary_2004, goldstein_nonadaptive_2015} resulting in a slowing down of the rate evolution\cite{rodrigue_detecting_2017, patel_epistasis_2022} or a standstill\cite{youssef_evolution_2022}.
+    In other words, under pervasive epistasis, finding empirical evidence for beneficial back-mutations is harder since restoring mutations become less and less likely to occur over time\cite{goldstein_nonadaptive_2015, goldstein_sequence_2017, park_epistatic_2022}.
+    Our study thus shows that beneficial back-mutations should not be overlooked, and we argue that both beneficial back-mutations and compensatory mutations play an important role in preventing our genome from collapsing under a mutation load.
 
-    %Second, epistasis is not modelled while it can have drastic consequences on the change in fitness landscape\cite{latrille_quantifying_2021}.
-    %Some models using Direct Coupling Analysis (DCA) can infer coevolution between sites, and thus provide a fitness score for amino acids which depends on other sites of the sequence\cite{bisardi_modeling_2022}.
-    %However, as SIFT scores, the scores given by DCA are not formalized in terms of selection coefficients and thus are hard to interpret in terms of population genetics, while also neglecting the underlying phylogeny and mutational biases.
-    %Relaxing both assumptions are computationally intensive\cite{rodrigue_site_2005, kleinman_statistical_2010}, and would require new mutation-selection models and optimization techniques to be able to manipulate genome-wide datasets..
-
-    % Alternatively at the DNA level, $\omega$-based codon model use the ratio of non-synonymous over synonymous substitution as signature of selection\cite{goldman_codonbased_1994, yang_codonsubstitution_2002}, taking into account the mutational bias and the underlying phylogeny.
-    % We also show that sites with higher $\omega$ are more positively selected in the different populations (supp.\ mat\  section 3).
-    % However, even sites which are supposedly under pervasive positive selection at the phylogenetic scale ($\omega>1$) are not necessarily positively selected in the populations.
-    %Most importantly, such models do not leverage the information of the source and target amino acid involve in the mutation, and thus cannot be used to estimate the non-adaptive part of positive selection.
-    %Altogether, we here show that mutation-selection codon models formalize a bridge between phylogenetics and population genetics models, but both ends have its limitation and could be improved.
-
-    At the population-genetic level, our study relied on models with some shortcomings, such that there is no consensus on the expected shape of the DFE\cite{welch_divergence_2008, bataillon_effects_2014}, although it has been found to be reliably constant between species\cite{castellano_comparison_2019}.
-    The model we used allows the inference of a full DFE, modelling the negative part of the DFE as a gamma distribution, and the positive part as an exponential distribution.
-    However, when we aggregate SNPs that are expected to be strongly deleterious or strongly advantageous, the model struggles to fit their DFE to a gamma or an exponential distribution.\cite{brevet_reconstructing_2021}
-    As a result, while the proportions of negative/weak/positive mutations stays reliable, the mean values for selection coefficients ($\Spop$) estimated by polyDFE become biologically absurd ($\Spop \ll -10^3$).
+    For the estimates of selection at the population scale ($\Spop$), there is no consensus on the expected shape of the DFE\cite{welch_divergence_2008, bataillon_effects_2014}, although it has been found to be reliably constant between species\cite{castellano_comparison_2019}.
+    We used a model that allowed the inference of a full DFE by modelling the negative side of the DFE as a gamma distribution, and the positive side as an exponential distribution.
+    However, when we aggregate SNPs that are expected to be strongly deleterious or strongly beneficial, the model struggles to fit their DFE to a gamma or an exponential distribution.
+    As a result, while the proportions of deleterious/weakly-selected/beneficial mutations stays reliable, the mean values for selection coefficients ($\Spop$) estimated by polyDFE become biologically absurd ($\Spop \ll -10^3$).
     Such effect is not found for neutral SNPs and a method to accurately estimate the mean value of selection coefficients from SFS without assuming any shape for the DFE remains yet to be developed.
     Aside from methodological limitations, the mammalian case study might also not be representative of other clades.
-    Indeed, mammals have relatively small long term population sizes, which allow large amounts of deleterious mutations to be fixed, and thus, there are a lot of opportunities for maintenance positive selection to arise.
+    Indeed, mammals have relatively small long term population sizes, which allow large amounts of deleterious mutations to be fixed, and thus, there are a lot of opportunities for beneficial back-mutations to arise.
     It would thus be of great interest to reproduce our experiment with other clades, such as \textit{Drosophila} or birds which tend to have higher effective population size.
@@
 
-    From a structural biology perspective, we have found that proteins are not optimal for their fitness, which has been proved for their kinetics and thermodynamics\cite{taverna_why_2002, goldstein_evolution_2011}.
-    Philosophically, our distinction between maintenance selection and adaptation can appear to be far-fetched, and one can argue that maintenance selection is adaptation to its own deteriorating genome.
+    From a structural biology perspective, we have found that proteins are not optimal for their fitness, which has been proved for their kinetics and thermodynamics\cite{hartl_compensatory_1996, taverna_why_2002, goldstein_evolution_2011}.
+    Philosophically, our distinction between beneficial back-mutations and adaptation can appear to be far-fetched, and one can argue that beneficial back-mutations is adaptation to its own deteriorating genome.
     However, there is a difference between adapting to a mutation, for instance by the mean of a compensatory mutation elsewhere, and cancelling the mutation, by the mean of a substitution on the misfit amino-acid.
@@
     We also argue that this distinction is important when we seek to detect adaptation, and is actually not an encumbrance but rather a strength.
-    Indeed, mutation-selection models are genuinely taking into account the tug-of-war between scarce advantageous mutations likely to reach fixation and a bulk of deleterious mutations eventually reaching fixation due to their sheer mass.
+    Precisely, mutation-selection models are genuinely taking into account the tug-of-war between scarce beneficial mutations likely to reach fixation and a bulk of deleterious mutations eventually reaching fixation due to their sheer mass.
     These models can thus be used as a null model to predict the expected rate of evolution of proteins\cite{spielman_relationship_2015, dosreis_how_2015} under a stable fitness landscape.
-    A departure from this model indicates that proteins are evolving under a changing fitness landscape\cite{rodrigue_detecting_2017, tamuri_mutationselection_2021} and is a signal of pervasive adaptive evolution\cite{rodrigue_bayesian_2021} or of pervasive epistasis\cite{rodrigue_detecting_2017}.
+    A departure from this model indicates that proteins are evolving under a changing fitness landscape\cite{cvijovic_fate_2015, rodrigue_detecting_2017, tamuri_mutationselection_2021} and is a signal of pervasive adaptive evolution\cite{rodrigue_bayesian_2021} or of pervasive epistasis\cite{rodrigue_detecting_2017}.
     As such, a stable fitness landscape as a null model is thus statistically more powerful to detect adaptation than assuming that the null model is neutral evolution.
-    Altogether, mutation-selection models are a mandatory tool in evolutionary biology to detect and quantify adaptation at the phylogenetic scale.
+    Taken together, mutation-selection models are a mandatory tool in evolutionary biology to detect and quantify adaptation at the phylogenetic scale, while acknowledging beneficial back-mutations.
+
+    In conclusion, we showed that by integrating genome-wide datasets at the phylogeny and the population scale, it is possible to estimate the proportion of beneficial mutations repairing existing functions instead of generating adaptive innovations.
+    We argue that our approach is general and our methodology can be readily applied to different estimations of fitness landscape at the phylogenetic scale, and different models and methods estimating distribution of fitness effects at the population scale.
+    This study at the interface between phylogenetic and population-genetics thus provide a step toward an integration of different scales necessary to decipher the combined effects of mutation, selection and drift on genome evolution.
 
@@
     \label{sec:acknowledgment}
-    We gratefully acknowledge the help of Diego A. Hartasánchez Frenk for his advice and review concerning this manuscript.
+    We gratefully acknowledge the help of Mélodie Bastian, Nicolas Lartillot, Laurent Duret and Diego A. Hartasánchez Frenk for their advices and reviews concerning this manuscript.
     This work was performed using the computing facilities of the CC LBBE/PRABI\@.
@@
     Genes located on the X, Y chromosomes and the mitochondrial genome were discarded from the analysis, because the level of polymorphism, which is necessary in the population-based analyses, is expected to be different in these three genomic regions.
-    Sequences of species for which we used population-level polymorphism (see below), as well as their sister species, were removed from the analysis to ensure independence between the data used in the phylogenetic and population genetic scale.
+    Sequences of species for which we used population-level polymorphism (see below), as well as their sister species, were removed from the analysis to ensure independence between the data used in the phylogenetic and population scale.
     Altogether, we analyzed $14,509$ protein-coding DNA sequences for at most $87$ sequences of placental mammals.
@@
     Mathematically, the rate of non-synonymous substitution from codon $a$ to codon $b$ ($q_{a \mapsto b}^{(i)}$) at site $i$ of the sequence is equal to the rate of mutation of the underlying nucleotide change ($\mu_{a \mapsto b}$) multiplied by the scaled probability of fixation of the mutation ($\proba_{a \mapsto b}^{(i)}$).
-    The probability of fixation depends on the difference of scaled fitness of the amino acid encoded by the mutated codon ($F_b^{(i)}$) and the amino acid encoded by the original codon ($F_a^{(i)}$) at site $i$\cite{wright_evolution_1931, fisher_genetical_1930}.
+    The probability of fixation depends on the difference of scaled fitness of the amino acid encoded by the mutated codon ($F_b^{(i)}$) and the amino acid encoded by the original codon ($F_a^{(i)}$) at site $i$\cite{wright_evolution_1931a, fisher_genetical_1930a}.
     The rate of substitution from codon $a$ to $b$ at a site $i$ is thus:
@@
     \begin{equation}
-        S_{a \mapsto b}^{(i)} = \Delta F^{(i)} = F^{(i)}_{b} - F^{(i)}_{a}.
+        \Sphy^{(i)} (a \mapsto b) = \Delta F^{(i)} = F^{(i)}_{b} - F^{(i)}_{a}.
     \end{equation}
@@
 
-    We retrieved the genetic variants representing the population level polymorphism from the following species and respective available datasets: \textit{Equus caballus} (EquCab2 assembly in the EVA study PRJEB9799\cite{alabri_whole_2020}), \textit{Bos taurus} (UMD3.1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}), \textit{Ovis aries} (Oar\_v3.1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}), \textit{Capra Hircus} (CHIR1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}, liftover to the ARS1 assembly), \textit{Chlorocebus sabaeus} (ChlSab1.1 assembly in the EVA project PRJEB22989\cite{svardal_ancient_2017}), \textit{Homo sapiens} (GRCh38 assembly from the 1000-genome project\cite{consortium_integrated_2012, the1000genomesprojectconsortium_global_2015}).
+    We retrieved the genetic variants representing the population level polymorphism from the following species and respective available datasets: \textit{Equus caballus} (EquCab2 assembly in the EVA study PRJEB9799\cite{alabri_whole_2020}), \textit{Bos taurus} (UMD3.1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}), \textit{Ovis aries} (Oar\_v3.1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}), \textit{Capra Hircus} (CHIR1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}, liftover to the ARS1 assembly), \textit{Chlorocebus sabaeus} (ChlSab1.1 assembly in the EVA project PRJEB22989\cite{svardal_ancient_2017}), \textit{Homo sapiens} (GRCh38 assembly from the 1000-genome project\cite{consortium_integrated_2012a, the1000genomesprojectconsortium_global_2015}).
     In total, we analyzed 28 populations across the 6 different species with polymorphism data.
@@
     This conversion from genomic position to position in the alignment is only possible if the assembly used for SNP calling is the same as the one used in the alignment, the GTF annotations and the FASTA sequences.
-
     SNPs were polarized using the $3$ closest outgroups found in the OrthoMam alignment with est-usfs v2.04\cite{keightley_inferring_2018}.
     For populations containing more than $8$ individuals, the site-frequency spectrum (SFS) was subsampled down to $16$ chromosomes ($8$ diploid individuals) without replacement (hyper-geometric distribution) to alleviate the effect of different sampling depth in the 28 populations.
-
     We developped a Snakemake pipeline to integrate polymorphism and divergence data with custom scripts written in python 3.9.
@@
     Pooled across many sites, the SFS provides therefore information on the underlying $\Spop$ of mutations.
-    However, estimating a single $\Spop$ for all sampled mutations is biologically unrealistic and a distribution of fitness effects of mutations (DFE) is usually assumed~\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009}.
+    However, estimating a single $\Spop$ for all sampled mutations is biologically unrealistic and a distribution of fitness effects of mutations (DFE) is usually assumed\cite{eyre-walker_distribution_2006a, eyre-walker_estimating_2009a}.
     In this study, we used the software polyDFE\cite{tataru_inference_2017, tataru_polydfe_2020}, which used a mixture of a $\Gamma$ and Exponential distributions to model the DFE of non-synonymous mutations, while synonymous mutations are considered neutral.
@@
     and $f_{\Gamma}(x; m, b)$ is the density of the $\Gamma$ distribution with mean m and shape b, while $f_{e}(x; m)$ is the density of the Exponential distribution with mean $m$.
-    Once the DFE was fitted to the data, the proportion of advantageous ($\PpolyAdv$), nearly-neutral ($\PpolyNeutral$) and deleterious mutations ($\PpolyDel$) were given as:
+    Once the DFE was fitted to the data, the proportion of beneficial ($\PpolyAdv$), nearly-neutral ($\PpolyNeutral$) and deleterious mutations ($\PpolyDel$) were given as:
     \begin{align}
@@
 
-    PolyDFE required one SFS for non-synonymous mutations and one for synonymous mutations (neutral expectation), as well as the number of sites on which each SFS has been sampled.
+    PolyDFE required one SFS for non-synonymous mutatipons and one for synonymous mutations (neutral expectation), as well as the number of sites on which each SFS has been sampled.
     We performed the following four-step procedure to obtain the number of sites for each SFS.
@@
 
-    From Bayes theorem, it is now possible to obtain the amount of positive selection due to maintenance selection.
-    In other words, we seek to get the probability that a mutation is repairing the genome ($\divAdv$) given that it is advantageous ($\polyAdv$), as:
+    From Bayes theorem, it is now possible to obtain the probability for a beneficial mutation to be a back-mutation .
+    In other words, we seek to get the probability that a mutation is repairing the genome ($\divAdv$) given that it is beneficial ($\polyAdv$), as:
     \begin{equation}
@@
     where $D \left( \Sphyclass \right) $ is the number of non-synonymous substitutions in the class $\Sphyclass$, $D_{\textrm{syn}}$ is the number of synonymous substitutions across the genome, while $L \left( \Sphyclass \right)$ and $L_{\textrm{syn}}$ are the number of non-synonymous and synonymous sites as defined in the previous section.
-    The fraction of non-adaptive advantageous substitutions $R(\dnds)$ was computed as the ratio between the difference in the numbers of advantageous substitutions ($\dnds$), which were due to maintenance positive selection, and the estimated divergence when we removed maintenance selection $\dn (\Sphy < 0) / \ds$, over $\dnds$.
+    The fraction of non-adaptive beneficial substitutions $R(\dnds)$ was computed as the ratio between the difference in the numbers of beneficial substitutions ($\dnds$), which were due to beneficial back-mutations, and the estimated divergence when we removed beneficial back-mutations $\dn (\Sphy < 0) / \ds$, over $\dnds$.
     Of note, the quantities $R(\dn)$ and $R(\dnds)$ are equivalent due to simplification of the factor $\ds$:

### 2022-11-04 manuscript/main_rev.tex
Reorganized the manuscript, substitutions then SNPs

@@
 
-    Adaptation is considered as the main process driving the diversity of forms and functions across the tree of life\cite{darwin_origin_1859}, and it enables species to live in new ecological niches, and to evolve in response to a change in environment\cite{darwin_origin_1859, merrell_adaptive_1994}.
-    The notion of adaptation, in its eco-evolutionary sense, is tightly linked to the notion of change, both of the environment (biotic and abiotic), and of the species responding to the latter\cite{merrell_adaptive_1994}.
-    With the discovery of DNA, the main support of heritable information, evolutionary geneticists looked for signatures of adaptation in genomes, and tried to quantify it\cite{mcdonald_adaptative_1991, eyre-walker_distribution_2006}.
-    In that context arose the term of rate of adaptive evolution\cite{mcdonald_adaptative_1991, eyre-walker_distribution_2006, galtier_adaptive_2016}.
-    However, in contrast to adaptation in its eco-evolutionary sense, adaptive evolution is merely used as a synonymous of evolution under positive selection\cite{eyre-walker_distribution_2006}.
-    This leads to a misunderstanding on what is adaptation with the loss of the notion of change, and a misinterpretation of the so-called rate of adaptive evolution.
-    Indeed, adaptive evolution is not the only process which can lead to positive selection at the population scale\cite{sella_application_2005, mustonen_fitness_2009}.
-    At mutation-selection-drift equilibrium, a mutation restoring the ancestral allele which corresponded to an optimal fitness in a constant environment, but lost due to the fixation of a deleterious mutation by drift, will also be positively selected (fig.~\ref{fig:fitness-landscape}B).
-    In this study, this process will be referred to as maintenance positive selection.
-    At the population scale, maintenance positive selection and adaptive evolution are indistinguishable and both result in a positive transmission bias of the advantageous allele, but their consequences at a macro-evolutionary scale are fundamentally different.
+    Adaptation is one of the main processes driving the diversity of forms and functions across the tree of life\cite{darwin_origin_1859}, but it plays a key role as it enables species to access new ecological niches or evolve in response to a change in their environment\cite{darwin_origin_1859, merrell_adaptive_1994}.
+    Adaptation is tightly linked to changes both at the level of the environment, through biotic or abiotic factors, and of the species responding to the latter\cite{merrell_adaptive_1994}.\NS{cette phrase me semble redondante avec la précédente}
+    Detecting adaptation has become a common practice in evolutionary biology since the development of theoretical models taken advantage of the availability of large scale genomic data\cite{mcdonald_adaptative_1991, eyre-walker_distribution_2006}.
+    This allowed researchers to quantify adaptation by comparing lineages and genomic regions to infer their specific rate of adaptive evolution\cite{mcdonald_adaptative_1991, eyre-walker_distribution_2006, galtier_adaptive_2016}.
+    Although these approaches led to a better understanding of the processes shaping molecular evolution\NS{refs serait top}, it had the effect to merely associate adaptive evolution with evolution under positive selection\cite{eyre-walker_distribution_2006}.
+    This misunderstanding of what is adaptation and the disconnection with the notion of change is troublesome and can foster a misinterpretation of the so-called rate of adaptive evolution.
+    Indeed, adaptive evolution is not the only process that can lead to positive selection at the scale of populations\cite{sella_application_2005, mustonen_fitness_2009}.
+    At mutation-selection-drift equilibrium, an ancestral allele, which had optimal fitness in a constant environment, can be lost due to the fixation of a deleterious mutation by drift.
+    A new mutation restoring this ancestral allele will also be positively selected (fig.~\ref{fig:fitness-landscape}B), even though no change in the adaptive landscape occurred.
+    This process will be referred to as maintenance positive selection because it does not involve adaptation as defined above.
+
+    At the population scale, maintenance positive selection and adaptive evolution are indistinguishable.
+    Both result in a positive transmission bias of the advantageous allele, but their consequences at a macro-evolutionary scale are fundamentally different.
+
     While adaptive evolution promotes phenotype diversification (fig.~\ref{fig:fitness-landscape}C), maintenance positive selection promotes phenotype stability and preserves well established biological systems (fig.~\ref{fig:fitness-landscape}D).
     It is thus essential to distinguish these two types of positive selection to understand the long term effects of selection on the diversification of species.
+    In this study, we analysed genomic data across mammals and estimate the rate of adaptive evolution for each protein coding gene across the mammalian genomes.
+    We decompose these estimates into a proportion of changes that are effectively due to adaptation versus those that are due to maintenance positive selection.
+\NS{à compléter un peu pour rendre plus fort et mieux lier avec le paragraphe suivant}
 
-    At the gene level, positive selection can be quantified by comparing sequence variation inside a population with the sequence divergence from a sister species\cite{mcdonald_adaptative_1991}.
+    At the level of a gene, positive selection can be quantified by comparing sequence variation inside a population with the sequence divergence from a sister species\cite{mcdonald_adaptative_1991}.
     The basic idea is that advantageous mutations are expected to be observed in substitutions between species but not in polymorphism within a population because they reach fixation too quickly.
-    This method has been largely improved to account for possible bias-inducing factors such as the presence of weak positive selection, background selection and demographic fluctuations\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009, galtier_adaptive_2016, tataru_inference_2017}.
+    This method can be biased due to the presence of weak positive selection, background selection and demographic fluctuations, but several improvements have been proposed to account for these biases\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009, galtier_adaptive_2016, tataru_inference_2017}.
     It has been applied across many organisms and enabled the discovery of widespread positive selection\cite{moutinho_variation_2019}.
-    However, the exact causes for this widespread occurrence of positive selection have been scarcely investigated\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009, galtier_adaptive_2016} %\NS{is it the case in the conclusion of the previous paper??
+
+    However, the exact causes for this widespread occurrence of positive selection have not been clearly investigated\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009, galtier_adaptive_2016} %\NS{is it the case in the conclusion of the previous paper??
 would be nice to back it up with references}.
-    As mentioned above, not all advantageous mutations contribute to genetic innovation and diversification, and truly adaptive evolution can only be well estimated if maintenance positive selection is taken into account.
-    While adaptive evolution is unpredictable because it caused by an unpredictable change in the environment of organisms, the second is predictable because optimal states should be more or less the same for closely related organisms which share most of their environment and physiology.
-    A way to measure maintenance positive selection is to predict selection coefficients assuming a constant and stable fitness landscape estimated from the alignment of protein-coding genes.
-    For each site of the protein alignment, a first approximation would be to consider that the frequency of an amino acid is a proxy for its fitness, since for example a deleterious amino acid will be more likely to be absent in the alignment.
+    %Not all advantageous mutations contribute to genetic innovation and diversification, and truly adaptive evolution can only be well estimated if we can identify the cases of maintenance positive selection.
+    Adaptive evolution is unpredictable because it is caused by a change in the environment during the evolution of an organism.
+    We can, however, identify maintenance positive selection because optimal genetic variants should be similar for closely related organisms that share most of their environment and life history traits.
+    We propose in this study a novel approach to measure the latter by assuming a constant and stable fitness landscape that can be estimated from the alignment of protein-coding genes.
+    For each site of a protein alignment, a first approximation would be to consider the frequency of an amino acid as a proxy for its fitness.
+    For example, an amino acid that is deleterious is unlikely to be present in many organisms and should therefore appear at low frequency if present at all.
     One of the most used methods to make these predictions is SIFT (Sort Intolerant From Tolerant), which reliably detects deleterious mutations in many taxa\cite{ng_sift_2003, vaser_sift_2016}.
     However, this method has two major shortcomings.
-    First, we know that a lot of mechanisms can influence amino acid frequency other than fitness (phylogenetic inertia, mutation biases, GC-biased gene conversion, mutational paths) which are not accounted for in SIFT\@.
-    Second, SIFT scores is not interpretable as a selection coefficient.
-    Contrarily, so-called mutation-selection codon models are rooted within a population genetics formalism\cite{halpern_evolutionary_1998, mccandlish_modeling_2014}.
+    First, we know that many mechanisms other than fitness can influence amino acid frequency (e.g.
+phylogeny, mutation biases, GC-biased gene conversion, mutational paths) and these are not accounted for in SIFT\@.
+    Second, SIFT scores are not interpretable as a selection coefficient.
+    In contrast, mutation-selection codon models are rooted within a population genetics formalism\cite{halpern_evolutionary_1998, mccandlish_modeling_2014}.
     These phylogenetic codon models can disentangle processes of mutation at the DNA level and selection at the amino acid level.
-    Such codon models provide a nearly-neutral framework of evolution by estimating the fitness landscape over amino acid sequences for each site of the sequence (fig~\ref{fig:method}A) while taking into account non-adaptive processes impacting codon frequency\cite{halpern_evolutionary_1998, rodrigue_mechanistic_2010, tamuri_estimating_2012, latrille_improved_2022}.
-    From the fitness landscape obtained by fitting the model to the data, one can thus compute the scaled selection coefficient ($\Sphy$) of any non-synonymous mutations.
-    Importantly, mutation-selection codon models assume that the underlying fitness landscape is stable along the phylogeny (as in fig.~\ref{fig:fitness-landscape}B), thus a mutation with a positive $\Sphy$ would be driving the current site toward a fitter amino-acid, and such mutation is effectively considered under maintenance positive selection, and is non-adaptive.
+    Such codon models provide a nearly-neutral framework of evolution by estimating the fitness landscape for each site of amino acid sequences (fig~\ref{fig:method}A), while accounting for non-adaptive processes affecting codon frequency\cite{halpern_evolutionary_1998, rodrigue_mechanistic_2010, tamuri_estimating_2012, latrille_improved_2022}.
+    From the fitness landscape obtained from this model, we can thus compute the scaled selection coefficient ($\Sphy$) of any non-synonymous mutations.
+    Mutation-selection codon models further assume that the underlying fitness landscape is stable along the phylogeny (as in fig.~\ref{fig:fitness-landscape}B).
+    A mutation with a positive $\Sphy$ would thus be driving the site toward a fitter amino-acid, which is exactly what is considered under maintenance positive selection.
 
-    By integrating datasets at the species and population level, we can predict $\Sphy$ for any mutation currently segregating in a population (fig~\ref{fig:method}B) under a stable fitness landscape.
-    Such a dataset can allow us to address different questions regarding positive selection affecting protein-coding DNA sequences.
-    Which proportion of the segregating polymorphisms in population are predicted toward a more optimal amino acid (positive $\Sphy$), thus supposedly under maintenance positive selection?
-    Are these polymorphisms effectively under positive selection along the terminal branches ? At the scale of populations ?
-    Finally, how much of positive selection observed in populations is due to maintenance positive selection?
-    To answer these questions, we estimated the fitness landscape of amino-acids for long-term evolution using available multiple sequence alignments between mammalian species\cite{ranwez_orthomam_2007, howe_ensembl_2021}.
+    By integrating genomic data at both the species and population level, we can predict $\Sphy$ for each mutation (or Single Nucleotide Polymorphism; SNP) currently segregating in a population (fig~\ref{fig:method}B) and tease apart the effects of adaptation from maintenance positive selection.
+    We used large scale genomic data on mammals to estimate the fitness landscape of amino-acids for long-term evolution using available multiple sequence alignments between mammalian species\cite{ranwez_orthomam_2007, howe_ensembl_2021}.
+
     We then integrated data at the phylogenetic and population scale to estimate divergence and polymorphism, respectively, across the entire exome for 28 populations from 6 genera (\textit{Equus},  \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus} and \textit{Homo}; fig.~\ref{fig:method}A\&B).
+    Our new approach enabled us to estimate the proportion of the segregating polymorphisms in a population that are predicted to be under maintenance positive selection (positive $\Sphy$) and test if these polymorphisms are effectively under positive selection at the scale of populations.
+    We show that ... and our results change ...
 
@@
 
-    For each non-synonymous SNP observed at the population level, we predicted its scaled selection coefficient ($\Sphy$) from a stable fitness landscape estimated at the mammalian scale (fig.~\ref{fig:method}B).
-    Then we ask whether the variants that are predicted to be advantageous, thus supposedly under maintenance selection, are showing signatures of short term positive selection.
-    For example, if a variant predicted to be non-optimal is found to be fixed in the last common ancestor of extant humans.
-If a mutation occurs in extant humans towards the allele predicted to be optimal, is this mutation positively selected at the population-scale?
-    At the population level (e.g.~in humans of Asian descent in fig.~\ref{fig:homo-afr-results}), we divided all observed SNPs in 5 classes of predicted selection coefficient: severely deleterious with $\divStrongDel$, deleterious with $\divDel$, weakly deleterious with $\divWeakDel$, weakly advantageous with $\divWeakAdv$ and advantageous with $\divAdv$ (fig.~\ref{fig:homo-afr-results}B).
-    In each of theses classes, SNPs are then grouped by the frequency of derived alleles in the population (fig.~\ref{fig:homo-afr-results}C), generating a so called site-frequency spectrum (SFS).
-    Compared to synonymous mutations which are supposedly neutral (black line in fig.~\ref{fig:homo-afr-results}C), mutations predicted to be deleterious (blue and green lines in fig.~\ref{fig:homo-afr-results}C) are underrepresented at high frequencies in the population, a signature of ongoing purifying selection.
+    For each non-synonymous SNP observed at the population level, we predicted its scaled selection coefficient ($\Sphy$) from the fitness of amino acids estimated at the scale of the mammals phylogeny (fig.~\ref{fig:method}B).
+    We then asked whether the variants that were predicted to be advantageous (i.e.
+with $\Sphy > 1$) and potentially under maintenance selection, were showing signatures of short term positive selection.
+    %For example, if a variant is found to be fixed in many mammals but not in ancestral humans, and a mutation in humans is toward the mammalian version, is this mutation advantageous for the individual carrying it?
+    To estimate the short term selection, we divided all SNPs observed at the population level (e.g.~in humans of Asian descent in fig.~\ref{fig:homo-afr-results}) in 5 classes of predicted selection coefficient\NS{pas clair comment on obtient ces classes}: severely deleterious with $\divStrongDel$, deleterious with $\divDel$, weakly deleterious with $\divWeakDel$, weakly advantageous with $\divWeakAdv$ and advantageous with $\divAdv$ (fig.~\ref{fig:homo-afr-results}B).
+    In each of theses classes, SNPs were then grouped by the number of derived alleles in the population (fig.~\ref{fig:homo-afr-results}C) to generate a site-frequency spectrum (SFS)\NS{pourquoi est-ce qu'on le fait?}.
+    Compared to synonymous mutations which are supposedly neutral (black line in fig.~\ref{fig:homo-afr-results}C), mutations predicted to be deleterious (blue and green lines in fig.~\ref{fig:homo-afr-results}C) were, as expected, underrepresented at high frequencies in the population, a signature of ongoing purifying selection.
     However, these observations remain qualitative.
@@
     To obtain a quantitative estimate of the distribution of selection coefficient for each category of SNPs, we used the model polyDFE\cite{tataru_inference_2017, tataru_polydfe_2020}.
-    This model uses the count of derived alleles for each frequency class of the SFS to infer the distribution of fitness effects (DFE) of the region under study.
-    The model uses both the number of sites ($L$) for each category (fig.~\ref{fig:homo-afr-results}A, see Material and Methods), and the counts of synonymous derived allele as a neutral model, which allow to control for demographic effects, and polarization errors when inferring the ancestral state.
-    These population-based models cannot give a specific estimate of the selection coefficient at the population-genetic scale ($\Spop$) for each SNP, but by gathering information across many SNPs, these models can estimate the proportion of advantageous mutations ($\PpolyAdv$), of nearly-neutral mutations ($\PpolyNeutral$) and of deleterious mutations ($\PpolyDel$) (fig.~\ref{fig:homo-afr-results}D).
-    We found that SNPs predicted to be deleterious given their selection coefficient $\Sphy$ across mammals are effectively purged at the population-genetic scale, demonstrating that purifying selection is largely predictable and amino acids with low fitness across mammals are effectively purged away in each population.
-    Notably, SNPs predicted to be advantageous given their selection coefficient $\Sphy$, thus supposedly under maintenance selection, are indeed under positive selection at the population-genetic scale, confirming that there is a local ongoing selection towards amino acids that are restoring the optimally functioning protein.
-    In between these two extremes, mutations predicted to be weakly selected (cyan and orange in fig.~\ref{fig:homo-afr-results}) are effectively composed of neutral, positively and negatively selected mutations.
+    This model uses the count of derived alleles for each frequency class of the SFS to infer the distribution of fitness effects (DFE) of the region under study.\NS{faudrait indiquer qu'on illustre avec ce jeu de données, sinon on ne comprend pas bien à mon avis.}
+    The model uses the number of sites ($L$) for each category (fig.~\ref{fig:homo-afr-results}A, see Material and Methods), the counts of synonymous derived allele as a neutral model, which allow to control for demographic effects, and polarization errors when inferring the ancestral state.
+    These population-based models cannot give a specific estimate of the selection coefficient for each SNP at the population scale ($\Spop$).
+    However, we could estimate the proportion of advantageous mutations ($\PpolyAdv$), nearly-neutral mutations ($\PpolyNeutral$) and deleterious mutations ($\PpolyDel$) by gathering information across many SNPs (fig.~\ref{fig:homo-afr-results}D).
+    We found that SNPs predicted to be deleterious based on the selection coefficient $\Sphy$ estimated across the phylogeny of mammals were effectively purged at the population scale.
+    Purifying selection is therefore largely predictable and amino acids with low fitness across mammals are effectively purged away in each population.
+    Then, SNPs predicted to be advantageous based on the selection coefficient $\Sphy$ estimated at the scale of the phylogeny of mammals are indeed under positive selection at the population scale.
+    These results confirmed that selection towards amino acids that are restoring the optimally functioning protein is ongoing in these populations.
+    Between these two extreme cases, SNPs predicted to be weakly selected (cyan and orange in fig.~\ref{fig:homo-afr-results}) were effectively composed of neutral, positively and negatively selected mutations.
 
-    We replicated such experiment across 28 populations from 6 species(fig.~\ref{fig:heatmap}), and found that mutations predicted to be deleterious are indeed purged at the population-scale (blue and green rows in fig.~\ref{fig:heatmap}A).
-    However, mutations predicted to be weakly advantageous ($\divWeakAdv$) are composed of a mix of neutral and selected mutations with varying proportions across the different populations (orange row in fig.~\ref{fig:heatmap}B).
-    Similarly, mutations predicted to be advantageous ($\divAdv$, under maintenance selection) are found to be positively selected with varying proportions across populations (red row in fig.~\ref{fig:heatmap}C).
-    In other words, mutations predicted to be deleterious by the mutation-selection model are effectively purified away in any population, while mutations predicted to be advantageous can be either neutral or advantageous depending on the population.
-    These variable proportions between populations can be explained by the effective number of individuals in the population ($\Ne$), a major driver of selection efficacy.
-    Since $\Ne$ is not directly measurable, a reasonable proxy usually used is the neutral diversity (Watterson $\theta_w$).
-    Assuming that synonymous positions are effectively neutral in mammals, we thus ordered populations by their levels of synonymous diversity (fig.~\ref{fig:diversity}A) and confirmed that higher synonymous diversity is typically accompanied by a smaller proportion of neutral mutations.
-    This result suggests that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) are more likely to discriminate between advantageous and deleterious mutations (fig~S1-S5).
-    Alternatively stated, mutations in populations with low diversity (e.g.~\textit{Homo}) are effectively nearly-neutral and behave as would a neutral mutation.
-    This result is qualitatively in accordance with the nearly-neutral theory of evolution which argues that mutations are less efficiently selected for in small populations.
+    We replicated our experiment across 28 populations of different mammal species (fig.~\ref{fig:heatmap}) and found that SNPs predicted to be deleterious were indeed purged at the population scale (blue and green rows in fig.~\ref{fig:heatmap}A).
+    However, SNPs predicted to be weakly advantageous ($\divWeakAdv$) were composed of a mix of neutral and selected mutations with varying proportions across the different populations (orange row in fig.~\ref{fig:heatmap}B).
+    Finally, SNPs predicted to be advantageous ($\divAdv$, under maintenance selection) were found to be positively selected with varying proportions across populations (red row in fig.~\ref{fig:heatmap}C).
+    %In other words, mutations predicted to be deleterious by the mutation-selection model are effectively purified away in any population, while mutations predicted to be advantageous can be either neutral or advantageous depending on the population.
+    The variable proportions found between populations can be explained by the effective number of individuals in the population ($\Ne$), which is well-known to be a major driver of selection efficacy.
+    Since $\Ne$ is not directly measurable, we used the Watterson $\theta_w$ as a proxy to order populations by their levels of synonymous diversity (fig.~\ref{fig:diversity}A).
+    We showed that higher synonymous diversity is associated with a smaller proportion of neutral mutations.
+    This result confirms the nearly-neutral theory and suggests that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) are more likely to discriminate between advantageous and deleterious mutations (fig~S1-S5), while mutations in populations with low diversity (e.g.~\textit{Homo}) are effectively nearly-neutral.
+    %This result is in accordance with the nearly-neutral theory of evolution which argues that mutations are less efficiently selected for in small populations.
     %, especially for mutations already predicted to be nearly-neutral at the phylogenetic scale (fig~S8-S9).
-
-    Finally, we reconstructed the substitutions in the terminal branches of the phylogenetic tree to determine the distribution of their selection coefficients.
-    For each population with available polymorphism data, we first reconstructed the ancestral sequence by replacing all variable site of the reference genome with the ancestral allele predicted by est-usfs, then we mapped the substitutions from the last genus split to this reconstructed ancestral sequence.
-    In these populations, we show that out of all polarized substitutions in the branches, between 10\% and 13\% of all substitutions have an $\Sphy > 1$ (table S1) and between 25\% and 30\% of all substitutions have an $\Sphy > 0$ (table S3).
-    Most importantly, there is clear signal that the substitutions with an $\Sphy > 1$ have been positively selected since their ratio of non-synonymous over synonymous divergence, a ratio called $\dnds$, is between 1.15 and 1.68 in the different populations (table S1), meaning that mutations under maintenance selection with $\Sphy > 1$ reach fixation more frequently that synonymous mutations (supposedly neutral).
-    These observed substitutions are likely to have been positively selected because they restored a more optimal state, not because they are driving innovations to a new environment or a new function.
-    %This also means that the ratio $\dnds$ usually used to detect adaptation while relying on substitutions between close species\cite{mcdonald_adaptative_1991, galtier_adaptive_2016} or at the phylogenetic scale\cite{goldman_codonbased_1994, yang_codonsubstitution_2002} is overestimated.
 
@@
 
-    We then sought to estimate the proportion of positive selection that is due to maintenance selection.
-    Mathematically, this corresponds to $\mathbb{P} [ \Sphy > 1  \given  \Spop > 1]$, namely the probability for a mutation to be due to maintenance selection, given it is positively selected.
-    This probability is given by Bayes formula (see methods), given we have access to $\mathbb{P} [ \Sphy > 1 ]$, $\mathbb{P} [ \Spop > 1 ]$, $\mathbb{P} [ \Spop > 1  \given  \Sphy > 1]$.
-    First, $\mathbb{P} [ \Sphy > 1 ]$ the probability for a mutation away from the ancestral sequence to have $\Sphy > 1$ (red fill of histogram in fig~\ref{fig:homo-afr-results}A and table S2).
-    Second, $\mathbb{P} [ \Spop > 1 ]$ is is the part of the DFE estimated at the population-scale greater than 1 when we used all the SNPs available in the population (black fill in fig~\ref{fig:diversity}A and table S2).
-    Finally, $\mathbb{P} [ \Spop > 1  \given  \Sphy > 1]$ is the part of the DFE estimated at the population-scale greater than 1, when we restricted our analysis on SNPs that are already predicted by mutation-selection models to have a selection coefficient greater than 1 (black fill for the category $\Sphy > 1$ in fig~\ref{fig:homo-afr-results}D and table S2).
-    Altogether, the probability for a mutation to be restoring the genome given that it is positively selected is obtained for each population, and varies between 10\% and 26\% depending of the population (table S2).
-    % Since adaptation does not fit the fitness predictions, the proportion of adaptive mutation is expected to be the same among SNPs which are predicted to be advantageous, and among SNPs which are predicted to be deleterious.
-    % Thus the proportion of advantageous mutations among SNPs which are predicted to be deleterious directly correspond to the proportion of all mutations which are adaptive.
-    % So if we divide the proportion of mutations which are predicted to be advantageous among supposedly deleterious SNPs by the proportion of mutations which are predicted to be advantageous among all SNPs, we directly get the proportion of mutations which are adaptive among advantageous ones.
-    % It results that 20 to 40\% of advantageous mutations are due to maintenance positive selection (fig~\ref{fig:diversity}B \& table S2).
+    We then estimated the proportion of positive selection that is due to maintenance selection.
+    We propose a new measure to estimate the probability that a mutation is due to maintenance selection given that it is positively selection i.e. $\mathbb{P} [ \Sphy > 1  \given  \Spop > 1]$.
+    We obtained from the analyses above the following probabilities $\mathbb{P} [ \Sphy > 1 ]$, $\mathbb{P} [ \Spop > 1 ]$, $\mathbb{P} [ \Spop > 1  \given  \Sphy > 1]$.
+    First, $\mathbb{P} [ \Sphy > 1 ]$ is the probability for a mutation different from the ancestral sequence to have $\Sphy > 1$ (red fill of histogram in fig~\ref{fig:homo-afr-results}A and table S2).
+    Second, $\mathbb{P} [ \Spop > 1 ]$ is the proportion of the DFE estimated on all available SNPs greater than 1 (black fill in fig~\ref{fig:diversity}A and table S2).
+    Finally, $\mathbb{P} [ \Spop > 1  \given  \Sphy > 1]$ is the part of the DFE greater than 1 when we restricted our analysis on SNPs that are already predicted by mutation-selection models to have a selection coefficient greater than 1 (black fill for the category $\Sphy > 1$ in fig~\ref{fig:homo-afr-results}D and table S2).
+    We estimated these probabilities for a mutation to be restoring the genome integrity given that it is positively selected across all populations sampled and obtained a proportion that varies between 10 and 26\% (table S2).
 
-    Focusing on substitutions in the terminal lineages, we can consider that the total $\dnds$ encompasses the rate of evolution for deleterious and advantageous (both adaptive and non-adaptive) substitutions.
+    \NS{pourquoi est-ce qu'on regarde cela?
+En quoi est-ce différent avec l'estimation précédente?
+Ce n'est pas forcément clair et surtout le lien avec la partie qui précède}Focusing on substitutions in the terminal lineages, we can consider that the total $\dnds$ encompasses the rate of evolution for deleterious and advantageous (both adaptive and non-adaptive) substitutions.
     Then, the $\dnds$ computed exclusively on non-synonymous sites with a $\Sphy < 0$ only represent the rate of evolution of solely deleterious and adaptive substitutions, discarding maintenance selection by construction.
@@
 
-    Interestingly, the proportion of maintenance selection among advantageous ones and the proportion of the rate of evolution explained by maintenance positive selection do not show a clear relationship with the synonymous diversity within a population (Watterson $\theta_w$), a proxy for the effective population size (fig.~\ref{fig:diversity}B and C).
+    The proportion of maintenance selection among advantageous ones and the proportion of the rate of evolution explained by maintenance positive selection did not show a clear relationship with the synonymous diversity within a population (Watterson $\theta_w$) (fig.~\ref{fig:diversity}B and C).
     Indeed, the relationship between $\Ne$ and the proportion of maintenance selection is not trivial and should highly depend on time scales.
-    A population which experienced a high long term $\Ne$ in the past is supposed to be closer to the optimal state (under a stable fitness landscape), and should not leave much space for maintenance selection.
-    On the other hand a high short term $\Ne$ will induce more extreme fitness effects and a larger proportion of mutations will be positively selected (otherwise effectively neutral), thus increasing the proportion of maintenance selection.
+    A population that experienced a high $\Ne$ along its evolutionary time should be closer to the optimal state under a stable fitness landscape because of the higher efficacy of selection.
+    This should decrease the probability of maintenance selection.
+    On the other hand, a high $\Ne$ over a short evolutionary time will induce more extreme fitness effects and a larger proportion of mutations will be positively selected (otherwise effectively neutral), thus increasing the proportion of maintenance selection.
     Overall, the proportion of maintenance selection is expected to be more dependent on effective population size contraction or expansion rather than on the short term effective population size captured by the synonymous diversity.
@@
     % Our study is a bridge between phylogenetic and population genetics
-    From a theoretical evolution perspective, we have found that we can use phylogenetic signals and mutation-selection codon models to predict the selection coefficient of a mutation.
-    However, we so far assumed no changes in effective population size while it has been established that population size changes have a major effect on selection dynamics\cite{lanfear_population_2014, jones_shifting_2017, platt_protein_2018}.
-    Mutation-selection models with changes in effective population sizes along the phylogeny have been developed\cite{latrille_inferring_2021}, but are, for the moment, too computational intensive to be performed genome-wide.
+    We found that the selection coefficient of a mutation can be predicted from mutation-selection codon models estimated over phylogenetic trees.
+    However, these models assume that there are no changes in effective population size across the evolutionary time scales.
+    It has however been established that changes in population size would have a major effect on selection dynamics\cite{lanfear_population_2014, jones_shifting_2017, platt_protein_2018}.
+    Mutation-selection models with changes in effective population sizes along the phylogeny have been developed\cite{latrille_inferring_2021}, but are, for the moment, too computational intensive to be performed across genomic data.
     Hybrid mutation-selection and $\omega$-based codon models could provide a way forward\cite{brevet_reconstructing_2021}.
     Moreover, SIFT scores based on amino acid alignments across species have also been found to be informative of the selection pressure exerted at the population scale\cite{chen_hunting_2021}.
-    Accordingly, our study shows that sites with a higher SIFT score at the phylogenetic scale are more positively selected in the different populations (supp.\ mat\  section SIFT scores).
+    Our study indeed showed that sites with a higher SIFT score at the phylogenetic scale are more positively selected in the different populations (supp.\ mat\  section SIFT scores).
     In practice, SIFT scores are more coarse grained, with for example a bulk of mutations with a score of 1.0 (the highest), and does not provide a boundary between advantageous and deleterious mutations, nor are they based on a population-genetics formalism.
@@
     These models without epistasis provide a reasonable estimate of average fitness profiles\cite{youssef_consequences_2020}.
-    But most importantly, we argue that our estimation of the amount of maintenance positive selection is an underestimation, and that accounting for compensatory mutations by means of epistasis would mechanically increase that amount.
-    Indeed, a fluctuating fitness landscape due to an external forces (e.i.
-changes in environment) results in an acceleration of the rate of evolution\cite{ rodrigue_detecting_2017, rodrigue_bayesian_2021} which generates epistatic mutations that are immediately beneficial\cite{gong_epistatically_2014}.
-    On the contrary, pervasive epistasis generates the opposite, an entrenchment\cite{goldstein_evolutionary_2004, goldstein_nonadaptive_2015} resulting in a slowing down of the rate evolution\cite{rodrigue_detecting_2017, patel_epistasis_2022} or a standstill\cite{youssef_evolution_2022}.
+    But most importantly, we argue that our estimation of the amount of maintenance positive selection is an underestimation, and that accounting for compensatory mutations by means of epistasis would mechanically increase our estimate.
+    Indeed, a fluctuating fitness landscape due to an external forces (i.e.
+changes in environment) results in an acceleration of the rate of evolution\cite{ rodrigue_detecting_2017, rodrigue_bayesian_2021}, which generates epistatic mutations that are immediately beneficial\cite{gong_epistatically_2014}.
+    In contrast, pervasive epistasis generates the opposite pattern, an entrenchment\cite{goldstein_evolutionary_2004, goldstein_nonadaptive_2015} resulting in a slowing down of the rate evolution\cite{rodrigue_detecting_2017, patel_epistasis_2022} or a standstill\cite{youssef_evolution_2022}.
     In other words, under pervasive epistasis, finding empirical evidence for maintenance selection is harder since restoring mutations become less and less likely to occur over time\cite{goldstein_nonadaptive_2015, goldstein_sequence_2017, park_epistatic_2022}.
@@
 
-    %Second, epistasis is not modelled while it can have drastic consequences on the change in fitness landscape\cite{latrille_quantifying_2021}.
-    %Some models using Direct Coupling Analysis (DCA) can infer coevolution between sites, and thus provide a fitness score for amino acids which depends on other sites of the sequence\cite{bisardi_modeling_2022}.
-    %However, as SIFT scores, the scores given by DCA are not formalized in terms of selection coefficients and thus are hard to interpret in terms of population genetics, while also neglecting the underlying phylogeny and mutational biases.
-    %Relaxing both assumptions are computationally intensive\cite{rodrigue_site_2005, kleinman_statistical_2010}, and would require new mutation-selection models and optimization techniques to be able to manipulate genome-wide datasets..
-
-    % Alternatively at the DNA level, $\omega$-based codon model use the ratio of non-synonymous over synonymous substitution as signature of selection\cite{goldman_codonbased_1994, yang_codonsubstitution_2002}, taking into account the mutational bias and the underlying phylogeny.
-    % We also show that sites with higher $\omega$ are more positively selected in the different populations (supp.\ mat\  section 3).
-    % However, even sites which are supposedly under pervasive positive selection at the phylogenetic scale ($\omega>1$) are not necessarily positively selected in the populations.
-    %Most importantly, such models do not leverage the information of the source and target amino acid involve in the mutation, and thus cannot be used to estimate the non-adaptive part of positive selection.
-    %Altogether, we here show that mutation-selection codon models formalize a bridge between phylogenetics and population genetics models, but both ends have its limitation and could be improved.
-
-    At the population-genetic level, our study relied on models with some shortcomings, such that there is no consensus on the expected shape of the DFE\cite{welch_divergence_2008, bataillon_effects_2014}, although it has been found to be reliably constant between species\cite{castellano_comparison_2019}.
-    The model we used allows the inference of a full DFE, modelling the negative part of the DFE as a gamma distribution, and the positive part as an exponential distribution.
+    For the estimates of selection at the population scale, there is no consensus on the expected shape of the DFE\cite{welch_divergence_2008, bataillon_effects_2014}, although it has been found to be reliably constant between species\cite{castellano_comparison_2019}.
+    We used a model that allowed the inference of a full DFE by modelling the negative side of the DFE as a gamma distribution, and the positive side as an exponential distribution.
     However, when we aggregate SNPs that are expected to be strongly deleterious or strongly advantageous, the model struggles to fit their DFE to a gamma or an exponential distribution.\cite{brevet_reconstructing_2021}
@@
     Altogether, mutation-selection models are a mandatory tool in evolutionary biology to detect and quantify adaptation at the phylogenetic scale.
+
+    \NS{on finit sur des aspects de limitations et des points plus techniques.
+Il faudrait réouvrir la discussion en mettant en avant ce que l'étude amène.
+Il me semble qu'on doit vraiment pousser pour le fait que l'interprétation des modèles dn/ds doit être revue et qu'un dn/ds > 1 ne veut pas dire adaptation.
+On pourrait conclure qu'avec l'avènement de la génomique pour plein d'espèces, notre approche peut être utilisée globalement pour découvrir quelles substitutions avec dn/ds > 1 est adaptative ou non, ce qui peut avoir un gros impact sur notre connaissance des processus lié à la diversification et les key innovations.}
 

### 2022-11-04 manuscript/supp-mat.tex
Revision by L. Duret & J. Joseph
Reorganized the manuscript, substitutions then SNPs

@@
 \PassOptionsToPackage{naturalnames}{hyperref}
+
+\usepackage[backend=biber,eprint=false,isbn=false,url=false,intitle=true,style=nature,date=year]{biblatex}
+\addbibresource{codon_models.bib}
 
@@
     \textbf{T. {Latrille}$^{1}$, J. {Joseph}$^{2}$, N. {Salamin}$^{1}$}\\
-    \normalsize $^{1}$Université de Lausanne, Lausanne, Switzerland\\
-    \normalsize $^{2}$Université de Lyon, CNRS, LBBE UMR 5558, Villeurbanne, France \\
-    \normalsize \texttt{\href{mailto:thibault.latrille@ens-lyon.org}{thibault.latrille@ens-lyon.org}} \\
+    \normalsize
+    $^{1}$Université de Lausanne, Lausanne, Switzerland\\
+    $^{2}$Université de Lyon, CNRS, LBBE UMR 5558, Villeurbanne, France \\
+    \texttt{\href{mailto:thibault.latrille@ens-lyon.org}{thibault.latrille@ens-lyon.org}} \\
 }
@@
         \scriptsize
+        \begin{longtable*}{|l|l|r|r|r|r|r|}
+            \toprule
+            Population & Species & Tajima $\theta_{\pi}$ & $\mathbb{P}_{div}[\Sphy > 0]$ & $\dnds $ & $\dn(\Sphy < 0) / \ds$ & R($\dnds $) \\
+            \midrule
+            \endhead
+            \midrule
+            \multicolumn{7}{r}{{Continued on next page}} \\
+            \midrule
+            \endfoot
+
+            \bottomrule
+            \endlastfoot
+            Equus c. &      Equus caballus &               $ 0.002$ &                $ 0.307$ &        $ 0.182$ &              $ 0.133$ &           $  27.0$ \\
+            Iran &          Bos taurus &               $ 0.005$ &                $ 0.298$ &        $ 0.164$ &              $ 0.122$ &           $  26.1$ \\
+            Uganda &          Bos taurus &               $ 0.005$ &                $ 0.303$ &        $ 0.167$ &              $ 0.123$ &           $  26.6$ \\
+            Australia &        Capra hircus &               $ 0.003$ &                $ 0.301$ &        $ 0.157$ &              $ 0.116$ &           $  26.4$ \\
+            France &        Capra hircus &               $ 0.003$ &                $ 0.300$ &        $ 0.158$ &              $ 0.116$ &           $  26.3$ \\
+            Iran (C. aegagrus) &        Capra hircus &               $ 0.003$ &                $ 0.300$ &        $ 0.158$ &              $ 0.116$ &           $  26.3$ \\
+            Iran &        Capra hircus &               $ 0.004$ &                $ 0.303$ &        $ 0.157$ &              $ 0.115$ &           $  26.6$ \\
+            Italy &        Capra hircus &               $ 0.003$ &                $ 0.300$ &        $ 0.158$ &              $ 0.116$ &           $  26.3$ \\
+            Morocco &        Capra hircus &               $ 0.004$ &                $ 0.303$ &        $ 0.157$ &              $ 0.115$ &           $  26.6$ \\
+            Iran &          Ovis aries &               $ 0.007$ &                $ 0.266$ &        $ 0.179$ &              $ 0.138$ &           $  22.7$ \\
+            Iran (O. orientalis) &          Ovis aries &               $ 0.009$ &                $ 0.265$ &        $ 0.180$ &              $ 0.140$ &           $  22.6$ \\
+            Iran (O. vignei) &          Ovis aries &               $ 0.007$ &                $ 0.268$ &        $ 0.178$ &              $ 0.137$ &           $  22.8$ \\
+            Various &          Ovis aries &               $ 0.009$ &                $ 0.264$ &        $ 0.180$ &              $ 0.140$ &           $  22.5$ \\
+            Morocco &          Ovis aries &               $ 0.007$ &                $ 0.265$ &        $ 0.180$ &              $ 0.140$ &           $  22.6$ \\
+            Barbados & Chlorocebus sabaeus &               $ 0.004$ &                $ 0.303$ &        $ 0.172$ &              $ 0.126$ &           $  26.8$ \\
+            Central Afr. Rep. & Chlorocebus sabaeus &               $ 0.006$ &                $ 0.304$ &        $ 0.173$ &              $ 0.126$ &           $  27.0$ \\
+            Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &                $ 0.305$ &        $ 0.172$ &              $ 0.126$ &           $  27.1$ \\
+            Gambia & Chlorocebus sabaeus &               $ 0.005$ &                $ 0.304$ &        $ 0.172$ &              $ 0.126$ &           $  26.9$ \\
+            Kenya & Chlorocebus sabaeus &               $ 0.005$ &                $ 0.304$ &        $ 0.173$ &              $ 0.126$ &           $  27.0$ \\
+            Nevis & Chlorocebus sabaeus &               $ 0.003$ &                $ 0.304$ &        $ 0.172$ &              $ 0.126$ &           $  26.9$ \\
+            South Africa & Chlorocebus sabaeus &               $ 0.006$ &                $ 0.307$ &        $ 0.172$ &              $ 0.125$ &           $  27.3$ \\
+            Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &                $ 0.306$ &        $ 0.172$ &              $ 0.125$ &           $  27.1$ \\
+            Zambia & Chlorocebus sabaeus &               $ 0.006$ &                $ 0.304$ &        $ 0.172$ &              $ 0.126$ &           $  27.0$ \\
+            African &        Homo sapiens &               $ 0.003$ &                $ 0.257$ &        $ 0.237$ &              $ 0.185$ &           $  22.0$ \\
+            Admixed American &        Homo sapiens &               $ 0.002$ &                $ 0.256$ &        $ 0.237$ &              $ 0.185$ &           $  21.9$ \\
+            East Asian &        Homo sapiens &               $ 0.002$ &                $ 0.258$ &        $ 0.238$ &              $ 0.185$ &           $  22.0$ \\
+            European &        Homo sapiens &               $ 0.002$ &                $ 0.256$ &        $ 0.237$ &              $ 0.185$ &           $  21.8$ \\
+            South Asian &        Homo sapiens &               $ 0.002$ &                $ 0.257$ &        $ 0.237$ &              $ 0.185$ &           $  22.0$ \\
+        \end{longtable*}
+    \end{center}
+    \begin{itemize}
+        \item Tajima $\theta$ is the synonymous diversity.
+        \item $\mathbb{P}_{div}[\Sphy > 0]$ is the proportion of substitutions in the terminal branch observed with a selection coefficient at the phylogenetic scale larger than 0 ($\Sphy > 0$).
+        \item $\dnds$ is the ratio of non-synonymous over synonymous divergence estimated for all the non-synonymous substitutions in the terminal branch.
+        \item $\dn(\Sphy < 0) / \ds$ is the ratio of non-synonymous over synonymous divergence estimated for the non-synonymous substitutions in the terminal branch with a selection coefficient lower than 0 ($\Sphy < 0$).
+        This is the estimated divergence when we removed beneficial back-mutations.
+        \item $R(\dnds)=\dfrac{\dnds - \dn(\Sphy < 0) / \ds}{\dnds}$ is the fraction of the divergence ($\dnds$) that is over-estimated, $\dnds$ is compared to the estimated divergence when we removed beneficial back-mutations $\dn(\Sphy < 0) / \ds$.
+    \end{itemize}
+    We estimated that between 20 and 25\% of $\dnds$ is over-estimated ($R(\dnds)$), corresponding to beneficial back-mutation inflating the $\dnds$ statistic.
+
+    \newpage
+    \begin{center}
+        \captionof{table}{~}
+        \scriptsize
         \begin{longtable*}{|l|l|r|r|r|r|r|r|}
@@
         \item Tajima $\theta$ is the synonymous diversity.
-        \item $\mathbb{P} [ \Sphy > 1 ]$ is the probability for a new mutation to be under maintenance selection.
+        \item $\mathbb{P} [ \Sphy > 1 ]$ is the probability for a new mutation a beneficial back-mutation.
         These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1 ($\Sphy > 1$), thus toward a more fit amino-acid.
         In other words, this probability is the part of the DFE estimated by mutation-selection models greater than 1.
-        \item $\mathbb{P} [ \Spop > 1 ]$ is the probability for a mutation to be positively selected.
+        \item $\mathbb{P} [ \Spop > 1 ]$ is the probability for a mutation to be beneficial.
         These mutations have a selection coefficient at the population-scale larger than 1 ($\Spop > 1$), estimated from all SNPs in the population.
         In other words, this probability is the part of the DFE estimated by polyDFE greater than 1.
-        \item $\mathbb{P} [ \Spop > 1 \given \Sphy > 1]$ is the probability for a mutation to be positively selected, given it is under maintenance selection.
-        These mutations have a selection coefficient at the population-scale larger than 1 ($\Spop > 1$), estimated by polyDFE on the SNPs with a predicted selection coefficient larger than 1 ($\Sphy > 1$).
-        In other words, this probability is the part of the DFE estimated by polyDFE greater than 1, when we restricted our analysis on SNPs that are already predicted by mutation-selection models to have a selection coefficient greater than 1.
-        \item $\mathbb{P} [ \Sphy > 1 \given \Spop > 1]$ is the probability for a mutation to be under maintenance selection, given it is positively selected.
+        \item $\mathbb{P} [ \Spop > 1 \given \Sphy > 1]$ is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale.
+        These mutations have a selection coefficient at the population scale larger than 1 ($\Spop > 1$), estimated by polyDFE on the SNPs with a predicted selection coefficient at the phylogenetic scale larger than 1 ($\Sphy > 1$).
+        In other words, this probability is the part of the DFE estimated by polyDFE greater than 1, when we restricted our analysis on SNPs that are already predicted by mutation-selection models to have a selection coefficient ($\Sphy$) greater than 1.
+        \item $\mathbb{P} [ \Sphy > 1 \given \Spop > 1]$ is the probability for a mutation to a beneficial back-mutations, given it is beneficial.
         This probability is obtained using Bayes' formula.
     \end{itemize}
-
-    \newpage
-    \begin{center}
-        \captionof{table}{~}
-        \scriptsize
-        \begin{longtable*}{|l|l|r|r|r|r|r|}
-            \toprule
-            Population & Species & Tajima $\theta_{\pi}$ & $\mathbb{P}_{div}[\Sphy > 0]$ & $\dnds $ & $\dn(\Sphy < 0) / \ds$ & R($\dnds $) \\
-            \midrule
-            \endhead
-            \midrule
-            \multicolumn{7}{r}{{Continued on next page}} \\
-            \midrule
-            \endfoot
-
-            \bottomrule
-            \endlastfoot
-            Equus c. &      Equus caballus &               $ 0.002$ &                $ 0.307$ &        $ 0.182$ &              $ 0.133$ &           $  27.0$ \\
-            Iran &          Bos taurus &               $ 0.005$ &                $ 0.298$ &        $ 0.164$ &              $ 0.122$ &           $  26.1$ \\
-            Uganda &          Bos taurus &               $ 0.005$ &                $ 0.303$ &        $ 0.167$ &              $ 0.123$ &           $  26.6$ \\
-            Australia &        Capra hircus &               $ 0.003$ &                $ 0.301$ &        $ 0.157$ &              $ 0.116$ &           $  26.4$ \\
-            France &        Capra hircus &               $ 0.003$ &                $ 0.300$ &        $ 0.158$ &              $ 0.116$ &           $  26.3$ \\
-            Iran (C. aegagrus) &        Capra hircus &               $ 0.003$ &                $ 0.300$ &        $ 0.158$ &              $ 0.116$ &           $  26.3$ \\
-            Iran &        Capra hircus &               $ 0.004$ &                $ 0.303$ &        $ 0.157$ &              $ 0.115$ &           $  26.6$ \\
-            Italy &        Capra hircus &               $ 0.003$ &                $ 0.300$ &        $ 0.158$ &              $ 0.116$ &           $  26.3$ \\
-            Morocco &        Capra hircus &               $ 0.004$ &                $ 0.303$ &        $ 0.157$ &              $ 0.115$ &           $  26.6$ \\
-            Iran &          Ovis aries &               $ 0.007$ &                $ 0.266$ &        $ 0.179$ &              $ 0.138$ &           $  22.7$ \\
-            Iran (O. orientalis) &          Ovis aries &               $ 0.009$ &                $ 0.265$ &        $ 0.180$ &              $ 0.140$ &           $  22.6$ \\
-            Iran (O. vignei) &          Ovis aries &               $ 0.007$ &                $ 0.268$ &        $ 0.178$ &              $ 0.137$ &           $  22.8$ \\
-            Various &          Ovis aries &               $ 0.009$ &                $ 0.264$ &        $ 0.180$ &              $ 0.140$ &           $  22.5$ \\
-            Morocco &          Ovis aries &               $ 0.007$ &                $ 0.265$ &        $ 0.180$ &              $ 0.140$ &           $  22.6$ \\
-            Barbados & Chlorocebus sabaeus &               $ 0.004$ &                $ 0.303$ &        $ 0.172$ &              $ 0.126$ &           $  26.8$ \\
-            Central Afr. Rep. & Chlorocebus sabaeus &               $ 0.006$ &                $ 0.304$ &        $ 0.173$ &              $ 0.126$ &           $  27.0$ \\
-            Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &                $ 0.305$ &        $ 0.172$ &              $ 0.126$ &           $  27.1$ \\
-            Gambia & Chlorocebus sabaeus &               $ 0.005$ &                $ 0.304$ &        $ 0.172$ &              $ 0.126$ &           $  26.9$ \\
-            Kenya & Chlorocebus sabaeus &               $ 0.005$ &                $ 0.304$ &        $ 0.173$ &              $ 0.126$ &           $  27.0$ \\
-            Nevis & Chlorocebus sabaeus &               $ 0.003$ &                $ 0.304$ &        $ 0.172$ &              $ 0.126$ &           $  26.9$ \\
-            South Africa & Chlorocebus sabaeus &               $ 0.006$ &                $ 0.307$ &        $ 0.172$ &              $ 0.125$ &           $  27.3$ \\
-            Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &                $ 0.306$ &        $ 0.172$ &              $ 0.125$ &           $  27.1$ \\
-            Zambia & Chlorocebus sabaeus &               $ 0.006$ &                $ 0.304$ &        $ 0.172$ &              $ 0.126$ &           $  27.0$ \\
-            African &        Homo sapiens &               $ 0.003$ &                $ 0.257$ &        $ 0.237$ &              $ 0.185$ &           $  22.0$ \\
-            Admixed American &        Homo sapiens &               $ 0.002$ &                $ 0.256$ &        $ 0.237$ &              $ 0.185$ &           $  21.9$ \\
-            East Asian &        Homo sapiens &               $ 0.002$ &                $ 0.258$ &        $ 0.238$ &              $ 0.185$ &           $  22.0$ \\
-            European &        Homo sapiens &               $ 0.002$ &                $ 0.256$ &        $ 0.237$ &              $ 0.185$ &           $  21.8$ \\
-            South Asian &        Homo sapiens &               $ 0.002$ &                $ 0.257$ &        $ 0.237$ &              $ 0.185$ &           $  22.0$ \\
-        \end{longtable*}
-    \end{center}
-    \begin{itemize}
-        \item Tajima $\theta$ is the synonymous diversity.
-        \item $\mathbb{P}_{div}[\Sphy > 0]$ is the proportion of substitutions in the terminal branch observed with a selection coefficient at the phylogenetic scale larger than 0 ($\Sphy > 0$).
-        \item $\dnds$ is the ratio of non-synonymous over synonymous divergence estimated for all the non-synonymous substitutions in the terminal branch.
-        \item $\dn(\Sphy < 0) / \ds$ is the ratio of non-synonymous over synonymous divergence estimated for the non-synonymous substitutions in the terminal branch with a selection coefficient lower than 0 ($\Sphy < 0$).
-        This is the estimated divergence when we removed maintenance selection.
-        \item $R(\dnds)=\dfrac{\dnds - \dn(\Sphy < 0) / \ds}{\dnds}$ is the fraction of the divergence ($\dnds$) that is over-estimated, $\dnds$ is compared to the estimated divergence when we removed maintenance selection $\dn(\Sphy < 0) / \ds$.
-    \end{itemize}
-
-    We estimated that between 20 and 25\% of $\dnds$ is over-estimated ($R(\dnds)$), corresponding to maintenance positive selection exerted on substitutions.
-    Altogether, in a nearly neutral framework, genomes could be viewed as the arena of a tug-of-war between a large volume of deleterious mutations that eventually reach fixation due to drift, and scarce advantageous mutations that are restoring a more optimal ancestral state.
 
@@
     \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression-MutSel/results.watterson.all_P-Seq0.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/regression-MutSel/results.watterson.all_P-Seq0.scatter.pdf}
     \end{minipage}
     \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression-MutSel/results.watterson.neg-weak_P-Seq0.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/regression-MutSel/results.watterson.neg-weak_P-Seq0.scatter.pdf}
     \end{minipage}
     \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression-MutSel/results.watterson.pos-weak_P-Seq0.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/regression-MutSel/results.watterson.pos-weak_P-Seq0.scatter.pdf}
     \end{minipage}
@@
     \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression-MutSel/results.watterson.all_P-Sinf0.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/regression-MutSel/results.watterson.all_P-Sinf0.scatter.pdf}
     \end{minipage}
     \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression-MutSel/results.watterson.neg_P-Sinf0.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/regression-MutSel/results.watterson.neg_P-Sinf0.scatter.pdf}
     \end{minipage}
     \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression-MutSel/results.watterson.neg-strong_P-Sinf0.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/regression-MutSel/results.watterson.neg-strong_P-Sinf0.scatter.pdf}
     \end{minipage}
@@
 
-    \subsubsection{Proportion of advantageous mutations ($\polyAdv$)}\label{subsec:proportion-advantageous-mutations}
+    \subsubsection{Proportion of beneficial mutations ($\polyAdv$)}\label{subsec:proportion-beneficial-mutations}
     \captionof{figure}{~}
     \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression-MutSel/results.watterson.all_P-Ssup0.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/regression-MutSel/results.watterson.all_P-Ssup0.scatter.pdf}
     \end{minipage}
     \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-polyDFE-mC/regression-MutSel/results.watterson.pos_P-Ssup0.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/regression-MutSel/results.watterson.pos_P-Ssup0.scatter.pdf}
     \end{minipage}
@@
 
-    \subsection{Selection efficacy correlation with diversity}\label{subsec:selection-efficacy-correlation-with-diversity}
-    The mean of the DFE $\SpopMean$ estimated by polyDFE is given by:
-    \begin{align*}
-        \SpopMean & = \int_{-\infty}^{+\infty} \Spop \phi \left( \Spop; \Spop_d , b, p_b, \Spop_b \right) \der \Spop \\
-        & = p_b \Spop_b + \left( 1 - p_b \right) \Spop_d
-    \end{align*}
+    \newpage
 
-    To look further into the relation between diversity and selection efficacy, we studied the estimation of the mean $\SpopMean$ as a function of the mean $\SphyMean$ for a subset of SNPs, for which $\SphyMean$ is close to $0$.
-    Indeed, polyDFE is a nearly-neutral model and is not able to reliably compute selection coefficients for only strongly deleterious or only strongly advantageous SNPs.
-    Sliding windows of $5,000$ SNPs are taken with a mean $\SphyMean$ between $-0.5$ and $0.5$.
-    $\SpopMean$ is estimated for each group, with some groups that might have part of same SNPs that overlap.
-    The relationship between $\SpopMean$ and $\SphyMean$ can be described by a second-order polynomial, and the slope of this polynomial at $\SphyMean=0$ gives the ratio $\SpopMean/\SphyMean$ for each population.
-    \captionof{figure}{~}
-    \begin{center}
-        \includegraphics[width=\linewidth, page=1]{artworks/figure.slope-beta-S}
-    \end{center}
-
-    We observe that $\SpopMean/\SphyMean$, representing the efficacy of selection at the short versus long-term is positively correlated with synonymous diversity, a proxy of effective population size.
-    Altogether, populations with a large effective population size are under more efficient selection, confirming the prediction of the nearly-neutral theory of evolution that mutations are less likely to be considered neutral in populations with high diversity (see~\ref{subsec:proportion-nearly-neutral-mutations}, left scatter-plot), especially for mutations predicted already to be nearly-neutral at the phylogenetic scale (see~\ref{subsec:proportion-nearly-neutral-mutations}, middle and right scatter-plot).
-    As a consequence of an increased selection efficiency, mutations in populations with high diversity are mechanistically more likely to be deleterious (see~\ref{subsec:proportion-deleterious-mutations}, left scatter-plot), especially for mutations predicted already to be deleterious at the phylogenetic scale (see~\ref{subsec:proportion-deleterious-mutations}, middle and right scatter-plot).
-    % A decrease in the proportion of neutral mutation did not translate into a mechanical increase in the proportion of advantageous mutations.
-    % Instead, populations with higher diversity have a lower proportion of advantageous mutations, this effect is also more pronounced for mutations predicted to be advantageous at the phylogenetic scale.
-    % This discrepancy can be explained by the fact that populations with larger diversity have already depleted the putatively advantageous mutations, and that only deleterious are remaining possible.
+%    \subsection{Selection efficacy correlation with diversity}\label{subsec:selection-efficacy-correlation-with-diversity}
+%    The mean of the DFE $\SpopMean$ estimated by polyDFE is given by:
+%    \begin{align*}
+%        \SpopMean & = \int_{-\infty}^{+\infty} \Spop \phi \left( \Spop; \Spop_d , b, p_b, \Spop_b \right) \der \Spop \\
+%        & = p_b \Spop_b + \left( 1 - p_b \right) \Spop_d
+%    \end{align*}
+%
+%    To look further into the relation between diversity and selection efficacy, we studied the estimation of the mean $\SpopMean$ as a function of the mean $\SphyMean$ for a subset of SNPs, for which $\SphyMean$ is close to $0$.
+%    Indeed, polyDFE is a nearly-neutral model and is not able to reliably compute selection coefficients for only strongly deleterious or only strongly beneficial SNPs.
+%    Sliding windows of $5,000$ SNPs are taken with a mean $\SphyMean$ between $-0.5$ and $0.5$.
+%    $\SpopMean$ is estimated for each group, with some groups that might have part of same SNPs that overlap.
+%    The relationship between $\SpopMean$ and $\SphyMean$ can be described by a second-order polynomial, and the slope of this polynomial at $\SphyMean=0$ gives the ratio $\SpopMean/\SphyMean$ for each population.
+%    \captionof{figure}{~}
+%    \begin{center}
+%        \includegraphics[width=\linewidth, page=1]{artworks/figure.slope-beta-S}
+%    \end{center}
+%
+%    We observe that $\SpopMean/\SphyMean$, representing the efficacy of selection at the short versus long-term is positively correlated with synonymous diversity, a proxy of effective population size.
+%    Altogether, populations with a large effective population size are under more efficient selection, confirming the prediction of the nearly-neutral theory of evolution that mutations are less likely to be considered neutral in populations with high diversity (see~\ref{subsec:proportion-nearly-neutral-mutations}, left scatter-plot), especially for mutations predicted already to be nearly-neutral at the phylogenetic scale (see~\ref{subsec:proportion-nearly-neutral-mutations}, middle and right scatter-plot).
+%    As a consequence of an increased selection efficiency, mutations in populations with high diversity are mechanistically more likely to be deleterious (see~\ref{subsec:proportion-deleterious-mutations}, left scatter-plot), especially for mutations predicted already to be deleterious at the phylogenetic scale (see~\ref{subsec:proportion-deleterious-mutations}, middle and right scatter-plot).
+%    A decrease in the proportion of neutral mutation did not translate into a mechanical increase in the proportion of beneficial mutations.
+%    Instead, populations with higher diversity have a lower proportion of beneficial mutations, this effect is also more pronounced for mutations predicted to be beneficial at the phylogenetic scale.
+%    This discrepancy can be explained by the fact that populations with larger diversity have already depleted the putatively beneficial mutations, and that only deleterious are remaining possible.
 %    In other words, being on the top of a fixed fitness landscape leaves you with only paths going downhill.
 %    Altogether, populations with increased diversity are showing signature of increased selection efficiency and are also less likely to generate positively selected mutations.
-
-    \newpage
+%   \newpage
 
@@
 
-    For each population, the proportion of advantageous ($p_+=\PpolyAdv$), nearly-neutral ($\PpolyNeutral$) and of deleterious ($\PpolyDel$) mutations estimated at the population-genetic scale is shown.
+    For each population, the proportion of beneficial ($p_+=\PpolyAdv$), nearly-neutral ($\PpolyNeutral$) and of deleterious ($\PpolyDel$) mutations estimated at the population-genetic scale is shown.
     Estimation is performed with SNPs with different class of selection at the phylogenetic scale: $\Sphyclass \in \{ \divStrongDel, \divDel, \divWeakDel, \divWeakAdv, \divAdv \}$
@@
         \begin{minipage}{0.9\linewidth}
-            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.MutSel.all.stacked.pdf}
+            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-all/results/Theta.MutSel.all.stacked.pdf}
         \end{minipage}
@@
         \begin{minipage}{0.9\linewidth}
-            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.MutSel.neg-strong.stacked.pdf} \\
+            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-all/results/Theta.MutSel.neg-strong.stacked.pdf} \\
         \end{minipage}
@@
         \begin{minipage}{0.9\linewidth}
-            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.MutSel.neg.stacked.pdf} \\
+            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-all/results/Theta.MutSel.neg.stacked.pdf} \\
         \end{minipage}
@@
         \begin{minipage}{0.9\linewidth}
-            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.MutSel.neg-weak.stacked.pdf} \\
+            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-all/results/Theta.MutSel.neg-weak.stacked.pdf} \\
         \end{minipage}
@@
         \begin{minipage}{0.9\linewidth}
-            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.MutSel.pos-weak.stacked.pdf} \\
+            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-all/results/Theta.MutSel.pos-weak.stacked.pdf} \\
         \end{minipage}
@@
         \begin{minipage}{0.9\linewidth}
-            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.MutSel.pos.stacked.pdf}
+            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-all/results/Theta.MutSel.pos.stacked.pdf}
         \end{minipage}
@@
     This result is specially visible when we restricted the analysis to class of mutations that are supposedly nearly-neutral at the phylogenetic scale ($\divWeakDel$ and $\divWeakAdv$).
-    This result suggests that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) are more likely to discriminate whether mutations are advantageous or deleterious.
+    This result suggests that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) are more likely to discriminate whether mutations are beneficial or deleterious.
     Alternatively stated, mutations in populations with low diversity (e.g.~\textit{Homo}) are effectively nearly-neutral and behave as would a neutral mutation.
@@
         \item Top-left panel: Histogram of predicted selection coefficients ($\Sphy$) for all possible mutations away from the ancestral genome, giving the number of sites ($L$, in y-axis) across the genome with a given $\Sphy$.
-        Mutations are divided into 5 classes: severely deleterious (blue), deleterious (green), weakly deleterious (light green), weakly advantageous (yellow) and advantageous (red).
+        Mutations are divided into 5 classes: severely deleterious (blue), deleterious (green), weakly deleterious (light green), weakly beneficial (yellow) and beneficial (red).
         \item Top-right panel: Histogram of predicted selection coefficients ($\Sphy$) for all observed mutations in a sample of 8 individuals (out of 512 in the original dataset) of African descent.
@@
         At high frequencies, supposedly severally deleterious mutations are underrepresented.
-        \item Bottom-right panel:For each class of selection (and for the set of all non-synonymous mutations), information from the SFS and the expected total mutation rate are combined at the population-genetic scale to estimate the proportion of advantageous mutations $\PpolyAdv$, of nearly-neutral mutations $\PpolyNeutral$ and of deleterious mutations $\PpolyDel$.
+        \item Bottom-right panel:For each class of selection (and for the set of all non-synonymous mutations), information from the SFS and the expected total mutation rate are combined at the population-genetic scale to estimate the proportion of beneficial mutations $\PpolyAdv$, of nearly-neutral mutations $\PpolyNeutral$ and of deleterious mutations $\PpolyDel$.
     \end{itemize}
@@
     \subsection{Proportion of selected mutations}\label{subsec:proportion-of-selected-mutations}
-    For each population, the proportion of advantageous ($\PpolyAdv$), nearly-neutral ($\PpolyNeutral$) and of deleterious ($\PpolyDel$) mutations estimated at the population-genetic scale is shown.
+    For each population, the proportion of beneficial ($\PpolyAdv$), nearly-neutral ($\PpolyNeutral$) and of deleterious ($\PpolyDel$) mutations estimated at the population-genetic scale is shown.
     Estimation is performed with SNPs with different class of SIFT scores at the phylogenetic scale.
@@
         \begin{minipage}{0.9\linewidth}
-            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.SIFT.all.stacked.pdf}
+            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-all/results/Theta.SIFT.all.stacked.pdf}
         \end{minipage}
@@
         \begin{minipage}{0.9\linewidth}
-            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.SIFT.neg-strong.stacked.pdf} \\
+            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-all/results/Theta.SIFT.neg-strong.stacked.pdf} \\
         \end{minipage}
@@
         \begin{minipage}{0.9\linewidth}
-            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.SIFT.neg.stacked.pdf} \\
+            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-all/results/Theta.SIFT.neg.stacked.pdf} \\
         \end{minipage}
@@
         \begin{minipage}{0.9\linewidth}
-            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.SIFT.neg-weak.stacked.pdf} \\
+            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-all/results/Theta.SIFT.neg-weak.stacked.pdf} \\
         \end{minipage}
@@
         \begin{minipage}{0.9\linewidth}
-            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.SIFT.pos-weak.stacked.pdf} \\
+            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-all/results/Theta.SIFT.pos-weak.stacked.pdf} \\
         \end{minipage}
@@
         \begin{minipage}{0.9\linewidth}
-            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-polyDFE-mC/results/Theta.SIFT.pos.stacked.pdf}
+            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-all/results/Theta.SIFT.pos.stacked.pdf}
         \end{minipage}
@@
     % Thus SIFT scores are not providing reliable information on the current selective strength exerted on mutations, at least for high SIFT scores.
-    % Moreover, there is no defined threshold (here we arbitrarily used 0.8) to cut-off between advantageous and deleterious changes.
+    % Moreover, there is no defined threshold (here we arbitrarily used 0.8) to cut-off between beneficial and deleterious changes.
 
-    \section{SIFT scores: histograms and SFS for each population}\label{sec:sift-scores:-histograms-and-sfs-for-each-population}
-    For each population, the same figure is shown.
-    \begin{itemize}
-        \item Top-left panel: Histogram of SIFT score for all possible mutations away from the ancestral genome, giving the number of sites ($L$, in y-axis) across the genome with a given SIFT score.
-        Mutations are divided into 5 classes: severely deleterious (blue), deleterious (green), weakly deleterious (light green), weakly advantageous (yellow) and advantageous (red).
-        \item Top-right panel: Histogram of SIFT score for all observed mutations in a sample of 8 individuals (out of 512 in the original dataset) of African descent.
-        If they are less mutations observed than expected, this class is thus undergoing purifying selection.
-        \item Bottom-left panel: The site-frequency spectrum (SFS) represents the proportion of mutations (y-axis) with a given number of derived alleles in the population (x-axis).
-        SFS are drawn for a random sample of 16 alleles (mean in solid line and standard deviation in filled color) for each class of selection coefficient and for synonymous mutations which are supposedly neutral (black).
-        At high frequencies, supposedly severally deleterious mutations are underrepresented.
-        \item Bottom-right panel:For each class of selection (and for the set of all non-synonymous mutations), information from the SFS and the expected total mutation rate are combined at the population-genetic scale to estimate the proportion of advantageous mutations $\PpolyAdv$, of nearly-neutral mutations $\PpolyNeutral$ and of deleterious mutations $\PpolyDel$.
-    \end{itemize}
-    \input{include-SIFT-non-adaptive}
+%    \section{SIFT scores: histograms and SFS for each population}\label{sec:sift-scores:-histograms-and-sfs-for-each-population}
+%    For each population, the same figure is shown.
+%    \begin{itemize}
+%        \item Top-left panel: Histogram of SIFT score for all possible mutations away from the ancestral genome, giving the number of sites ($L$, in y-axis) across the genome with a given SIFT score.
+%        Mutations are divided into 5 classes: severely deleterious (blue), deleterious (green), weakly deleterious (light green), weakly beneficial (yellow) and beneficial (red).
+%        \item Top-right panel: Histogram of SIFT score for all observed mutations in a sample of 8 individuals (out of 512 in the original dataset) of African descent.
+%        If they are less mutations observed than expected, this class is thus undergoing purifying selection.
+%        \item Bottom-left panel: The site-frequency spectrum (SFS) represents the proportion of mutations (y-axis) with a given number of derived alleles in the population (x-axis).
+%        SFS are drawn for a random sample of 16 alleles (mean in solid line and standard deviation in filled color) for each class of selection coefficient and for synonymous mutations which are supposedly neutral (black).
+%        At high frequencies, supposedly severally deleterious mutations are underrepresented.
+%        \item Bottom-right panel:For each class of selection (and for the set of all non-synonymous mutations), information from the SFS and the expected total mutation rate are combined at the population-genetic scale to estimate the proportion of beneficial mutations $\PpolyAdv$, of nearly-neutral mutations $\PpolyNeutral$ and of deleterious mutations $\PpolyDel$.
+%    \end{itemize}
+%    \input{include-SIFT-non-adaptive}
+
+    \section*{References}
+    \printbibliography
 

### 2022-11-04 scripts/libraries.py

@@ -52,14 +52,14 @@ codontable.update({
 confidence_interval = namedtuple('confidence_interval', ['low', 'mean', 'up'])
 sfs_weight = {"watterson": lambda i, n: 1.0 / i, "tajima": lambda i, n: n - i, "fay_wu": lambda i, n: i}
 polydfe_cat_dico = {
-    "P-Ssup0": "$\\mathbb{P} [ \\beta > 1 ]$",
-    "P-Seq0": "$\\mathbb{P} [ -1<\\beta<1 ]$",
-    "P-Sinf0": "$\\mathbb{P} [ \\beta<-1 ]$",
+    "P-Ssup0": "$\\mathbb{P} [ S > 1 ]$",
+    "P-Seq0": "$\\mathbb{P} [ -1< S <1 ]$",
+    "P-Sinf0": "$\\mathbb{P} [ S <-1 ]$",
 }
 alpha_sup_limits = [0, 1, 3, 5]
 polydfe_cat_list = list(polydfe_cat_dico.keys())
 xlim_dico = {"Omega": (0.0, 2.0), "MutSel": (-10, 10), "SIFT": (0.0, 1.0)}
-rate_dico = {"MutSel": "Scaled selection coefficient (S)",
+rate_dico = {"MutSel": "Scaled selection coefficient ($S_0$)",
              "Omega": "Rate of evolution ($\\omega$)",
              "SIFT": "SIFT score"}
 
@@ -470,27 +470,27 @@ class CategorySNP(list):
             if self.bins == 2:
                 self.inner_bound = [0]
                 self.dico = {
-                    "neg": P("$S<0$", BLUE, -np.float("infinity"), 0),
+                    "neg": P("$S_0 < 0$", BLUE, -np.float("infinity"), 0),
                     "syn": P("$Synonymous$", 'black', None, None),
-                    "pos": P("$S>0$", RED, 0, np.float("infinity"))
+                    "pos": P("$S_0 >0$", RED, 0, np.float("infinity"))
                 }
             elif self.bins == 3:
                 self.inner_bound = [-1, 1]
                 self.dico = {
-                    "neg": P("$S<-1$", BLUE, -np.float("infinity"), -1),
-                    "weak": P("$-1<S<1$", LIGHTGREEN, -1, 1),
-                    "pos": P("$S>1$", RED, 1, np.float("infinity")),
[…]

### 2022-11-04 scripts/parse_results_DFE.py

@@ -44,7 +44,7 @@ def plot_stack_param(list_cat, cat_snps, s_dico, output):
         y = np.array([s_dico[cat][param] for cat in list_cat])
         ax.bar(x_pos, y, bottom=bottom, edgecolor=edgecolors_list[p_i], color=colors_list[p_i], hatch=hatches_list[p_i])
         bottom += y
-    ax.set_xlabel("Category of S at the phylogenetic scale")
+    ax.set_xlabel("Category of $S_0$")
     ax.set_ylabel("Proportion estimated at the population scale")
     ax.set_xticks(x_pos)
     ax.set_ylim((0, 1))

### 2022-11-04 scripts/plot_regression.py

@@ -52,8 +52,8 @@ def generate_xy_plot(cat_snps):
 
     y_dico = {"tajima": "Tajima $\\theta_{\\pi}$ ",
               "flowPos": "$\\Psi_{+}$", "flowNeg": "$\\Psi_{-}$", "flowRatio": "$\\Psi_{+} / \\Psi_{-}$",
-              "logFitness": "Mean log-fitness", "SMean": "$\\overline{S}$",
-              "betaS_ratio": "Slope of $\\overline{\\beta}(\\overline{S})$ at $\\overline{S}=0$",
+              "logFitness": "Mean log-fitness", "SMean": "$\\overline{S_0}$",
+              "betaS_ratio": "Slope of $\\overline{S}(\\overline{S_0})$ at $\\overline{S_0}=0$",
               "fay_wu": "Fay and Wu $\\theta_{H}$", "D_tajima": "Tajima's $D$", "H_fay_wu": "Fay and Wu's $H$"}
     y_dico.update({f'all_{cat_poly}': v for cat_poly, v in polydfe_cat_dico.items()})
 
@@ -71,8 +71,8 @@ def generate_xy_plot(cat_snps):
             dico_label[f'bayes_{cat_poly}_P-{cat}'] = f"${pr}[{s}|{beta}]$"
             dico_label[f'mut_sum_{cat_poly}'] = f"${pr}_{{mut}}[{beta}]$"
             dico_label[f'frac_{cat}_{cat_poly}'] = f"$\\frac{{{pr}[{s}]}}{{{pr}[{beta}]}}$"
-        dico_label[f'bayes_p_b_P-{cat}'] = f"${pr}[{s}|\\beta>0]$"
-        dico_label[f'frac_{cat}_p_b'] = f"$\\frac{{{pr}[{s}]}}{{{pr}[\\beta>0]}}$"
+        dico_label[f'bayes_p_b_P-{cat}'] = f"${pr}[{s}|S>0]$"
+        dico_label[f'frac_{cat}_p_b'] = f"$\\frac{{{pr}[{s}]}}{{{pr}[S>0]}}$"
         if cat != "all":
             s = f" | {s}"
 
@@ -81,14 +81,14 @@ def generate_xy_plot(cat_snps):
         for sup in omega_suffix:
             dico_label[f'{cat}_omega{sup}'] = f"$\\omega^{{{str(sup).replace('_', '')}}} {s}$"
[…]

### 2022-11-04 manuscript/main.tex
References to figures and tables

@@
 
-    Adaptation is considered as the main process driving the diversity of forms and functions across the tree of life, as it enables species to access new ecological niches and also respond to changes in their environment\cite{darwin_origin_1859}.
-    In this context of adaptative evolution, a change in environment is echoed as a change of species' forms and functions, ultimately leaving signatures of accelerated changes in the species' genome\cite{merrell_adaptive_1994}.
-    This signature of an accelerated rate of changes, generating an excess of beneficial mutations is used to quantify adaptation (fig.~\ref{fig:fitness-landscape}A), for specific genes along a specific lineage\cite{mcdonald_adaptative_1991, smith_adaptive_2002a, welch_estimating_2006}.
-    The current availability of large scale genomic data and the development of theoretical models allowed to detect and quantify adaption across genes and lineages, which is now a common practice in evolutionary biology\cite{yang_statistical_2000, eyre-walker_genomic_2006, moutinho_variation_2019}.
-    Although these approaches led to a better understanding of the processes shaping molecular evolution, it had the effect to merely associate beneficial mutations with adaptive evolution, which should be dissociated since adaptive evolution is not the only process which can lead to beneficial mutations\cite{charlesworth_other_2007, mustonen_fitness_2009}.
-    Indeed, even in a constant environment for which the population is already adapted, a deleterious mutation in an individual can reach fixation in the population by genetic drift\cite{Ohta1992}.
-    Subsequently, a mutation restoring the ancestral state will thus be beneficial (fig.~\ref{fig:fitness-landscape}B), even though no change in the environment occurred\cite{hartl_compensatory_1996, sella_application_2005, mustonen_fitness_2009, cvijovic_fate_2015}.
-    More precisely, this restoration of the ancestral state can happen at another loci, in which case it is referred as compensating mutations\cite{hartl_compensatory_1996, mustonen_fitness_2009}.
-    Conversely, the restoration of the ancestral state can happen at the same locus, in which case it is referred as a beneficial back-mutation\cite{piganeau_estimating_2003, charlesworth_other_2007}, which are the focus of this study.
-    Taken together, not all beneficial mutations contribute to genetic innovation, and truly adaptive evolution can only be well estimated under the background of beneficial back-mutations\cite{keightley_what_2010, rice_evolutionarily_2015}.
+    Adaptation is considered as the main process driving the diversity of forms and functions across the tree of life, as it enables species to access new ecological niches and also respond to changes in their environment~\cite{darwin_origin_1859}.
+    In this context of adaptative evolution, a change in environment is echoed as a change of species' forms and functions, ultimately leaving signatures of accelerated changes in the species' genome~\cite{merrell_adaptive_1994}.
+    This signature of an accelerated rate of changes, generating an excess of beneficial mutations is used to quantify adaptation (fig.~\ref{fig:fitness-landscape}A), for specific genes along a specific lineage~\cite{mcdonald_adaptative_1991, smith_adaptive_2002a, welch_estimating_2006}.
+    The current availability of large scale genomic data and the development of theoretical models allowed to detect and quantify adaption across genes and lineages, which is now a common practice in evolutionary biology~\cite{yang_statistical_2000, eyre-walker_genomic_2006, moutinho_variation_2019}.
+    Although these approaches led to a better understanding of the processes shaping molecular evolution, it had the effect to merely associate beneficial mutations with adaptive evolution, which should be dissociated since adaptive evolution is not the only process which can lead to beneficial mutations~\cite{charlesworth_other_2007, mustonen_fitness_2009}.
+    Indeed, even in a constant environment for which the population is already adapted, a deleterious mutation in an individual can reach fixation in the population by genetic drift~\cite{Ohta1992}.
+    Subsequently, a mutation restoring the ancestral state will thus be beneficial (fig.~\ref{fig:fitness-landscape}B), even though no change in the environment occurred~\cite{hartl_compensatory_1996, sella_application_2005, mustonen_fitness_2009, cvijovic_fate_2015}.
+    More precisely, this restoration of the ancestral state can happen at another loci, in which case it is referred as compensating mutations~\cite{hartl_compensatory_1996, mustonen_fitness_2009}.
+    Conversely, the restoration of the ancestral state can happen at the same locus, in which case it is referred as a beneficial back-mutation~\cite{piganeau_estimating_2003, charlesworth_other_2007}, which are the focus of this study.
+    Taken together, not all beneficial mutations contribute to genetic innovation, and truly adaptive evolution can only be well estimated under the background of beneficial back-mutations~\cite{keightley_what_2010, rice_evolutionarily_2015}.
     It is thus essential to distinguish the underlying reason for the advantage brought by a beneficial mutation, a back-mutation repairing damaged genomes or creating an adaptive innovations.
@@
     While adaptive evolution promotes phenotype diversification (fig.~\ref{fig:fitness-landscape}C), beneficial back-mutations promotes phenotype stability and preserves well established biological systems (fig.~\ref{fig:fitness-landscape}D).
-    Fundamentally, adaptive evolution is unpredictable because it caused by an unpredictable change in the environment and the underlying fitness landscape\cite{bazykin_changing_2015}.
+    Fundamentally, adaptive evolution is unpredictable because it caused by an unpredictable change in the environment and the underlying fitness landscape~\cite{bazykin_changing_2015}.
     On the other hand, beneficial back-mutations are predictable if the underlying stable fitness landscape is known.
@@
     Multi-species sequence alignments can be used as a proxy for fitness, since for example a deleterious amino acid will be more likely to be absent in the alignment.
-    One of the most used methods to make these predictions is SIFT (Sort Intolerant From Tolerant), which reliably detects deleterious mutations in many taxa\cite{ng_sift_2003, vaser_sift_2016}.
+    One of the most used methods to make these predictions is SIFT (Sort Intolerant From Tolerant), which reliably detects deleterious mutations in many taxa~\cite{ng_sift_2003, vaser_sift_2016}.
     However, SIFT scores is not interpretable as a selection coefficient.
     Second, we know that a lot of mechanisms can influence amino acid frequency other than fitness (phylogenetic inertia, mutation biases, GC-biased gene conversion, mutational paths) which are not accounted for in SIFT\@.
-    Contrarily, so-called mutation-selection codon models are rooted within a population-genetic formalism\cite{halpern_evolutionary_1998, mccandlish_modeling_2014}.
+    Contrarily, so-called mutation-selection codon models are rooted within a population-genetic formalism~\cite{halpern_evolutionary_1998, mccandlish_modeling_2014}.
     These phylogenetic codon models can disentangle processes of mutation at the DNA level and selection at the amino acid level.
-    Such codon models provide a nearly-neutral framework of evolution by estimating the fitness landscape over amino acid sequences for each site of the sequence (fig~\ref{fig:method}A) while taking into account non-adaptive processes impacting codon frequency\cite{halpern_evolutionary_1998, rodrigue_mechanistic_2010, tamuri_estimating_2012, latrille_improved_2022a}.
+    Such codon models provide a nearly-neutral framework of evolution by estimating the fitness landscape over amino acid sequences for each site of the sequence (fig~\ref{fig:method}A) while taking into account non-adaptive processes impacting codon frequency~\cite{halpern_evolutionary_1998, rodrigue_mechanistic_2010, tamuri_estimating_2012, latrille_improved_2022a}.
     From the fitness landscape obtained by fitting the model to the data, one can thus compute the scaled selection coefficient, denoted $\Sphy$, of any non-synonymous mutations.
@@
 
-    By integrating datasets at different scales (phylogeny and population), we can predict whether substitutions in terminal lineages or any mutation currently segregating in a population are beneficial back-mutations, i.e with a positive $\Sphy$ (fig~\ref{fig:method}B).
+    By integrating datasets at different scales (phylogeny and population), we can predict whether substitutions in terminal lineages or any mutation currently segregating in a population are beneficial back-mutations, i.e with a positive $\Sphy$ (fig~\ref{fig:method}A\&B).
     Such a dataset can allow us to address different questions regarding the selection affecting protein-coding DNA sequences.
@@
     In other words, can we find empirical evidence and can we quantify the amount of beneficial mutations that are restoring damaged genomes instead of creating adaptive innovations.
-    To answer these questions, we estimated the fitness landscape of amino-acids for long-term evolution using available multiple sequence alignments between mammalian species\cite{ranwez_orthomam_2007, howe_ensembl_2021}.
-    We then integrated data at the phylogenetic and population scale to estimate the amount of beneficial mutations across the entire exome for 28 populations from 6 genera (\textit{Equus},  \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus} and \textit{Homo}; fig.~\ref{fig:method}A\&B).
+    To answer these questions, we estimated the fitness landscape of amino-acids for long-term evolution using available multiple sequence alignments between mammalian species~\cite{ranwez_orthomam_2007, howe_ensembl_2021}.
+    We then integrated data at the phylogenetic and population scale to estimate the amount of beneficial mutations across the entire exome (fig.~\ref{fig:method}A-F), for 28 populations from 6 genera (\textit{Equus},  \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus} and \textit{Homo}).
 
@@
     For each substitution, we estimated its scaled selection coefficient ($\Sphy$) based on the stable fitness landscape of amino-acids estimated at the scale of the mammals' phylogeny (fig.~\ref{fig:method}A).
-    We showed that among all the substitutions in the terminal lineages, between 10 and 13\% had $\Sphy > 1$ (table SX) and between 25 and 30\% had $\Sphy > 0$ (table SX).
-    Substitutions with $\Sphy > 1$ have been beneficial since the ratio of non-synonymous over synonymous divergence, called $\dnds$, was estimated to be between 1.15 and 1.68 in the different lineages (table SX).
+    We showed that among all the substitutions in the terminal lineages, between 10 and 13\% had $\Sphy > 1$ (table~S1) and between 25 and 30\% had $\Sphy > 0$ (table~S2).
+    Substitutions with $\Sphy > 1$ have been beneficial since the ratio of non-synonymous over synonymous divergence, called $\dnds$, was estimated to be between 1.15 and 1.68 in the different lineages (table~S1).
     This meant that beneficial back-mutations with $\Sphy > 1$ reach fixation more frequently than synonymous mutations, which are supposed to be neutral, thus are effectively beneficial.
-    This also means that the ratio $\dnds$ usually used to detect adaptation while relying on substitutions between close species\cite{mcdonald_adaptative_1991, galtier_adaptive_2016} or at the phylogenetic scale\cite{goldman_codonbased_1994, yang_codonsubstitution_2002} is overinflated due to beneficial back-mutations.
+    This also means that the ratio $\dnds$ usually used to detect adaptation while relying on substitutions between close species~\cite{mcdonald_adaptative_1991, galtier_adaptive_2016} or at the phylogenetic scale~\cite{goldman_codonbased_1994, yang_codonsubstitution_2002} is overinflated due to beneficial back-mutations.
     Then, $\dnds$ computed exclusively on non-synonymous sites with a $\Sphy < 0$ only represent the rate of evolution discarding beneficial back-mutations by construction.
     Thus, if we divide the $\dnds$ estimated on all substitutions by the one estimated only on substitutions predicted to be deleterious, we directly get the proportion of the rate of evolution which is contributed by beneficial back-mutations (see methods).
-    This way, we estimated that between 22\% and 27\% of $\dnds$ is inflated because of beneficial back-mutations (table SX).
+    This way, we estimated that between 22\% and 27\% of $\dnds$ is inflated because of beneficial back-mutations (table~S2).
 
     \subsection*{Back-mutations in the populations}
-    Given that beneficial back-mutations are effectively selected for, we then ask which proportion of new mutations are beneficial back-mutations.
+    Given that beneficial back-mutations are effectively selected for, we then ask which proportion of new mutations are beneficial back-mutations and are also beneficial at the population scale (fig.~\ref{fig:method}C-E).
     For each population with available polymorphism data, we first reconstructed the ancestral sequence (instead of the reference sequence) at the base of the population genealogy.
@@
     Because $\Sphy$ is based on estimation of fitnesses at the mammalian scale, mutations with $\Sphy>1$ are considered beneficial back-mutations.
-    Beneficial back-mutations only represents ~1.5\% of all possible new mutations (red in fig.~\ref{fig:homo-afr-results}A, table~SX).
-    However, when focusing on the mutations that are observed in populations, namely single nucleotide polymorphism (SNP), beneficial back-mutations represents ~8.5\% of all observed mutations (red in fig.~\ref{fig:homo-afr-results}B, table~SX).
+    Beneficial back-mutations only represents ~1.5\% of all possible new mutations (red in fig.~\ref{fig:homo-afr-results}A, table~S3).
+    However, when focusing on the mutations that are observed in populations, namely single nucleotide polymorphism (SNP), beneficial back-mutations represents ~8.5\% of all observed mutations (red in fig.~\ref{fig:homo-afr-results}B, table~S3).
 
@@
 deleterious SNPs are segregating at lower frequencies because they are purified.
-    As such, methods have been developed to estimate the distribution of fitness effect (DFE) at the population scale by gathering information across many SNPs\cite{eyre-walker_distribution_2006a, eyre-walker_estimating_2009a, galtier_adaptive_2016, tataru_inference_2017}.
+    As such, methods have been developed to estimate the distribution of fitness effect (DFE) at the population scale by gathering information across many SNPs~\cite{eyre-walker_distribution_2006a, eyre-walker_estimating_2009a, galtier_adaptive_2016, tataru_inference_2017}.
     These methods offer a unique opportunity to compare the DFE at the population scale ($\Spop$) and at the phylogenetic scale ($\Sphy$).
@@
 
-    To obtain a quantitative estimate of the distribution of selection coefficient for each category of SNPs, we used the model polyDFE\cite{tataru_inference_2017, tataru_polydfe_2020}.
+    To obtain a quantitative estimate of the distribution of selection coefficient for each category of SNPs, we used the model polyDFE~\cite{tataru_inference_2017, tataru_polydfe_2020}.
     This model uses the count of derived alleles for each frequency class of the SFS to infer the distribution of fitness effects (DFE) of the region under study.
@@
     Since $\Ne$ is not directly measurable, we used the Watterson $\theta_w$ as a proxy to order populations by their levels of synonymous diversity.
-    Higher synonymous diversity is associated with a smaller proportion of neutral mutations (fig.~\ref{fig:diversity}A).
-    This result confirms the nearly-neutral theory and suggests that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) are more likely to discriminate between beneficial and deleterious mutations (fig~SX-SX), while mutations in populations with low diversity (e.g.~\textit{Homo}) are effectively nearly-neutral.
+    Higher synonymous diversity is associated with a smaller proportion of nearly-neutral mutations (fig.~\ref{fig:diversity}A\&B).
+    This result confirms the nearly-neutral theory and suggests that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) are more likely to discriminate between beneficial and deleterious mutations (fig~S1-S9), while mutations in populations with low diversity (e.g.~\textit{Homo}) are effectively nearly-neutral.
 
@@
 
-    Finally, we propose a new measure to estimate the probability for a beneficial mutation to be a back-mutation, i.e. $\mathbb{P} [ \Sphy > 1  \given  \Spop > 1]$.
+    Finally, we propose an estimator for the probability of a beneficial mutation to be a beneficial back-mutation, i.e. $\mathbb{P} [ \Sphy > 1  \given  \Spop > 1]$ (fig.~\ref{fig:method}C-F).
     We obtained from the analyses above the following probabilities $\mathbb{P} [ \Sphy > 1 ]$, $\mathbb{P} [ \Spop > 1 ]$, $\mathbb{P} [ \Spop > 1  \given  \Sphy > 1]$.
-    First, $\mathbb{P} [ \Sphy > 1 ]$ is the probability for a beneficial back-mutation ($\Sphy > 1$) from the ancestral sequence (red fill of histogram in fig~\ref{fig:homo-afr-results}A and table S2).
-    Second, $\mathbb{P} [ \Spop > 1 ]$ is the probability of mutation to be beneficial at the level of the population ($\Spop > 1$), estimated from all available SNPs (black fill in fig~\ref{fig:diversity}A and table S2).
-    Finally, $\mathbb{P} [ \Spop > 1  \given  \Sphy > 1]$ is the probability for a back-mutation ($\Sphy > 1$) to be effectively beneficial at the level of the population ($\Spop > 1$), when we restricted our analysis on SNPs that are already predicted to be beneficial back-mutations (black fill for the category $\Sphy > 1$ in fig~\ref{fig:homo-afr-results}D and table S2).
+    First, $\mathbb{P} [ \Sphy > 1 ]$ is the probability for a beneficial back-mutation ($\Sphy > 1$) from the ancestral sequence (red fill of histogram in fig~\ref{fig:homo-afr-results}A and table~S3).
+    Second, $\mathbb{P} [ \Spop > 1 ]$ is the probability of mutation to be beneficial at the level of the population ($\Spop > 1$), estimated from all available SNPs (black fill in fig~\ref{fig:diversity}A and table~S3).
+    Finally, $\mathbb{P} [ \Spop > 1  \given  \Sphy > 1]$ is the probability for a back-mutation ($\Sphy > 1$) to be effectively beneficial at the level of the population ($\Spop > 1$), when we restricted our analysis on SNPs that are already predicted to be beneficial back-mutations (black fill for the category $\Sphy > 1$ in fig~\ref{fig:homo-afr-results}D and table~S3).
     Combining these probabilities using Bayes theorem, we now obtain the probability for a beneficial mutation to be a back-mutation $\mathbb{P} [ \Sphy > 1  \given  \Spop > 1]$ (see Material and Methods).
-    We estimated $\mathbb{P} [ \Sphy > 1  \given  \Spop > 1]$ across all populations sampled and obtained a proportion that varies between 10 and 26\% (table S2).
+    We estimated $\mathbb{P} [ \Sphy > 1  \given  \Spop > 1]$ across all populations sampled and obtained a proportion that varies between 10 and 26\% (table~S3).
 
-    The proportion of back-mutations among all beneficial one did not show a clear relationship with the synonymous diversity within a population (Watterson $\theta_w$) (fig.~\ref{fig:diversity}B).
-    Indeed, the relationship between $\Ne$ and the proportion of beneficial back-mutations is not trivial and should highly depend on time scales\cite{charlesworth_other_2007}.
+    The proportion of back-mutations among all beneficial one did not show a clear relationship with the synonymous diversity within a population (Watterson $\theta_w$) (fig.~\ref{fig:diversity}C).
+    Indeed, the relationship between $\Ne$ and the proportion of beneficial back-mutations is not trivial and should highly depend on time scales~\cite{charlesworth_other_2007}.
     A population that experienced a high $\Ne$ along its evolutionary time should be closer to the optimal state under a stable fitness landscape because of the higher efficacy of selection.
@@
     On the other hand, a high $\Ne$ over a short evolutionary time will induce more extreme fitness effects and a larger proportion of mutations will be beneficial (otherwise effectively neutral), thus increasing the proportion of beneficial back-mutations.
-    Overall, the proportion of beneficial back-mutations is expected to be more dependent on effective population size contraction or expansion rather than on the short term effective population size captured by the synonymous diversity\cite{charlesworth_other_2007}.
+    Overall, the proportion of beneficial back-mutations is expected to be more dependent on effective population size contraction or expansion rather than on the short term effective population size captured by the synonymous diversity~\cite{charlesworth_other_2007}.
 
@@
             Population are sorted for increased synonymous diversity.
-            Panel B.
+            Panel B. Proportion of nearly-neutral mutations ($\mathbb{P} [ -1 < \Spop < 1]$ in y-axis), shown as a function of the synonymous diversity (Watterson $\theta_w$ in x-axis).
+            Panel C.
 Proportion of beneficial back-mutations among all beneficial mutations ($\mathbb{P} [ \Sphy > 1  \given  \Spop > 1]$ in y-axis), shown as a function of the synonymous diversity (Watterson $\theta_w$ in x-axis).
@@
     From a theoretical evolution perspective, we have found that we can use phylogenetic signals and mutation-selection codon models to predict the selection coefficient of a mutation ($\Sphy$).
-    However, we so far assumed no changes in effective population size along the phylogeny while it has been established that population size changes have a major effect on selection dynamics\cite{lanfear_population_2014, jones_shifting_2017, platt_protein_2018}.
-    Mutation-selection models with changes in effective population sizes along the phylogeny have been developed\cite{latrille_inferring_2021a}, but are, for the moment, too computational intensive to be performed genome-wide.
-    Hybrid mutation-selection and $\omega$-based codon models could provide a way forward to in integrate site-specific selection and branch-specific drift\cite{brevet_reconstructing_2021a}.
-    As for the estimate of selection, SIFT scores based on amino acid alignments across species have also been found to be informative of the selection pressure exerted at the population scale\cite{chen_hunting_2021}.
+    However, we so far assumed no changes in effective population size along the phylogeny while it has been established that population size changes have a major effect on selection dynamics~\cite{lanfear_population_2014, jones_shifting_2017, platt_protein_2018}.
+    Mutation-selection models with changes in effective population sizes along the phylogeny have been developed~\cite{latrille_inferring_2021a}, but are, for the moment, too computational intensive to be performed genome-wide.
+    Hybrid mutation-selection and $\omega$-based codon models could provide a way forward to in integrate site-specific selection and branch-specific drift~\cite{brevet_reconstructing_2021a}.
+    As for the estimate of selection, SIFT scores based on amino acid alignments across species have also been found to be informative of the selection pressure exerted at the population scale~\cite{chen_hunting_2021}.
     Our study indeed showed that sites with a higher SIFT score at the phylogenetic scale are more beneficial in the different populations (supp.\ mat\  section SIFT scores).
@@
 
-    Biologically, another mechanism which generate non-adaptive beneficial mutations is compensatory mutations, which are repairing damage caused by deleterious mutations at another loci in the genome and generating a widespread signal of non-adaptative evolution\cite{hartl_compensatory_1996, pollock_strong_2014, starr_epistasis_2016}.
+    Biologically, another mechanism which generate non-adaptive beneficial mutations is compensatory mutations, which are repairing damage caused by deleterious mutations at another loci in the genome and generating a widespread signal of non-adaptative evolution~\cite{hartl_compensatory_1996, pollock_strong_2014, starr_epistasis_2016}.
     In our study we focused on mutations toward a more optimal amino-acid at a given site, not accounting for compensatory mutations since we assumed a model of fitness landscape without epistasis.
-    As shown in other studies, these models without epistasis provide a reasonable estimate of average fitness profiles\cite{youssef_consequences_2020}.
+    As shown in other studies, these models without epistasis provide a reasonable estimate of average fitness profiles~\cite{youssef_consequences_2020}.
     But most importantly, we argue that our estimation of the amount of beneficial back-mutations is an underestimation, and that accounting for compensatory mutations by means of epistasis would mechanically increase our estimate.
     Indeed, a fluctuating fitness landscape due to an external forces (i.e.
-changes in environment) results in an acceleration of the rate of evolution\cite{ rodrigue_detecting_2017, rodrigue_bayesian_2021}, which generates epistatic mutations that are immediately beneficial\cite{gong_epistatically_2014}.
-    In contrast, pervasive epistasis generates the opposite pattern, an entrenchment\cite{goldstein_evolutionary_2004, goldstein_nonadaptive_2015} resulting in a slowing down of the rate evolution\cite{rodrigue_detecting_2017, patel_epistasis_2022} or a standstill\cite{youssef_evolution_2022}.
-    In other words, under pervasive epistasis, finding empirical evidence for beneficial back-mutations is harder since restoring mutations become less and less likely to occur over time\cite{goldstein_nonadaptive_2015, goldstein_sequence_2017, park_epistatic_2022}.
+changes in environment) results in an acceleration of the rate of evolution~\cite{ rodrigue_detecting_2017, rodrigue_bayesian_2021}, which generates epistatic mutations that are immediately beneficial~\cite{gong_epistatically_2014}.
+    In contrast, pervasive epistasis generates the opposite pattern, an entrenchment~\cite{goldstein_evolutionary_2004, goldstein_nonadaptive_2015} resulting in a slowing down of the rate evolution~\cite{rodrigue_detecting_2017, patel_epistasis_2022} or a standstill~\cite{youssef_evolution_2022}.
+    In other words, under pervasive epistasis, finding empirical evidence for beneficial back-mutations is harder since restoring mutations become less and less likely to occur over time~\cite{goldstein_nonadaptive_2015, goldstein_sequence_2017, park_epistatic_2022}.
     Our study thus shows that beneficial back-mutations should not be overlooked, and we argue that both beneficial back-mutations and compensatory mutations play an important role in preventing our genome from collapsing under a mutation load.
 
-    For the estimates of selection at the population scale ($\Spop$), there is no consensus on the expected shape of the DFE\cite{welch_divergence_2008, bataillon_effects_2014}, although it has been found to be reliably constant between species\cite{castellano_comparison_2019}.
+    For the estimates of selection at the population scale ($\Spop$), there is no consensus on the expected shape of the DFE~\cite{welch_divergence_2008, bataillon_effects_2014}, although it has been found to be reliably constant between species~\cite{castellano_comparison_2019}.
     We used a model that allowed the inference of a full DFE by modelling the negative side of the DFE as a gamma distribution, and the positive side as an exponential distribution.
@@
 
-    From a structural biology perspective, we have found that proteins are not optimal for their fitness, which has been proved for their kinetics and thermodynamics\cite{hartl_compensatory_1996, taverna_why_2002, goldstein_evolution_2011}.
+    From a structural biology perspective, we have found that proteins are not optimal for their fitness, which has been proved for their kinetics and thermodynamics~\cite{hartl_compensatory_1996, taverna_why_2002, goldstein_evolution_2011}.
     Philosophically, our distinction between beneficial back-mutations and adaptation can appear to be far-fetched, and one can argue that beneficial back-mutations is adaptation to its own deteriorating genome.
@@
     Precisely, mutation-selection models are genuinely taking into account the tug-of-war between scarce beneficial mutations likely to reach fixation and a bulk of deleterious mutations eventually reaching fixation due to their sheer mass.
-    These models can thus be used as a null model to predict the expected rate of evolution of proteins\cite{spielman_relationship_2015, dosreis_how_2015} under a stable fitness landscape.
-    A departure from this model indicates that proteins are evolving under a changing fitness landscape\cite{cvijovic_fate_2015, rodrigue_detecting_2017, tamuri_mutationselection_2021} and is a signal of pervasive adaptive evolution\cite{rodrigue_bayesian_2021} or of pervasive epistasis\cite{rodrigue_detecting_2017}.
+    These models can thus be used as a null model to predict the expected rate of evolution of proteins~\cite{spielman_relationship_2015, dosreis_how_2015} under a stable fitness landscape.
+    A departure from this model indicates that proteins are evolving under a changing fitness landscape~\cite{cvijovic_fate_2015, rodrigue_detecting_2017, tamuri_mutationselection_2021} and is a signal of pervasive adaptive evolution~\cite{rodrigue_bayesian_2021} or of pervasive epistasis~\cite{rodrigue_detecting_2017}.
     As such, a stable fitness landscape as a null model is thus statistically more powerful to detect adaptation than assuming that the null model is neutral evolution.
@@
     Protein-coding DNA sequences alignments in placental mammals and their corresponding gene trees were extracted from the \href{https://www.orthomam.univ-montp2.fr}{OrthoMaM} database.
-    It contained a total of $116$ mammalian reference sequences in v10c\cite{ranwez_orthomam_2007, douzery_orthomam_2014, scornavacca_orthomam_2019}.
+    It contained a total of $116$ mammalian reference sequences in v10c~\cite{ranwez_orthomam_2007, douzery_orthomam_2014, scornavacca_orthomam_2019}.
     Genes located on the X, Y chromosomes and the mitochondrial genome were discarded from the analysis, because the level of polymorphism, which is necessary in the population-based analyses, is expected to be different in these three genomic regions.
@@
     We analyzed the phylogenetic level data using mutation-selection models.
-    These models assume that the protein-coding sequence are at mutation-selection balance under a fixed fitness landscape characterized by a fitness vector over the $20$ amino acid at each site\cite{yang_mutationselection_2008, halpern_evolutionary_1998, rodrigue_mechanistic_2010}.
+    These models assume that the protein-coding sequence are at mutation-selection balance under a fixed fitness landscape characterized by a fitness vector over the $20$ amino acid at each site~\cite{yang_mutationselection_2008, halpern_evolutionary_1998, rodrigue_mechanistic_2010}.
     Mathematically, the rate of non-synonymous substitution from codon $a$ to codon $b$ ($q_{a \mapsto b}^{(i)}$) at site $i$ of the sequence is equal to the rate of mutation of the underlying nucleotide change ($\mu_{a \mapsto b}$) multiplied by the scaled probability of fixation of the mutation ($\proba_{a \mapsto b}^{(i)}$).
-    The probability of fixation depends on the difference of scaled fitness of the amino acid encoded by the mutated codon ($F_b^{(i)}$) and the amino acid encoded by the original codon ($F_a^{(i)}$) at site $i$\cite{wright_evolution_1931a, fisher_genetical_1930a}.
+    The probability of fixation depends on the difference of scaled fitness of the amino acid encoded by the mutated codon ($F_b^{(i)}$) and the amino acid encoded by the original codon ($F_a^{(i)}$) at site $i$~\cite{wright_evolution_1931a, fisher_genetical_1930a}.
     The rate of substitution from codon $a$ to $b$ at a site $i$ is thus:
@@
     In the manuscript and the following material, the source ($a$) and target ($b$) codons as well as the site ($i$) are implicit and thus never explicitly written.
-    We ran the Bayesian software \textit{BayesCode} (\url{https://github.com/ThibaultLatrille/bayescode}) on each protein-coding DNA alignment\cite{rodrigue_bayesian_2021}.
+    We ran the Bayesian software \textit{BayesCode} (\url{https://github.com/ThibaultLatrille/bayescode}) on each protein-coding DNA alignment~\cite{rodrigue_bayesian_2021}.
     We ran a Markov chain Monte-Carlo (MCMC) analysis during $2000$ generations, with a burn-in period of $1000$ generations, to obtain posterior mean estimates of the amino acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$\@.
@@
 
-    We retrieved the genetic variants representing the population level polymorphism from the following species and respective available datasets: \textit{Equus caballus} (EquCab2 assembly in the EVA study PRJEB9799\cite{alabri_whole_2020}), \textit{Bos taurus} (UMD3.1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}), \textit{Ovis aries} (Oar\_v3.1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}), \textit{Capra Hircus} (CHIR1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}, liftover to the ARS1 assembly), \textit{Chlorocebus sabaeus} (ChlSab1.1 assembly in the EVA project PRJEB22989\cite{svardal_ancient_2017}), \textit{Homo sapiens} (GRCh38 assembly from the 1000-genome project\cite{consortium_integrated_2012a, the1000genomesprojectconsortium_global_2015}).
+    We retrieved the genetic variants representing the population level polymorphism from the following species and respective available datasets: \textit{Equus caballus} (EquCab2 assembly in the EVA study PRJEB9799~\cite{alabri_whole_2020}), \textit{Bos taurus} (UMD3.1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}), \textit{Ovis aries} (Oar\_v3.1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}), \textit{Capra Hircus} (CHIR1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}, liftover to the ARS1 assembly), \textit{Chlorocebus sabaeus} (ChlSab1.1 assembly in the EVA project PRJEB22989~\cite{svardal_ancient_2017}), \textit{Homo sapiens} (GRCh38 assembly from the 1000-genome project~\cite{consortium_integrated_2012a, the1000genomesprojectconsortium_global_2015}).
     In total, we analyzed 28 populations across the 6 different species with polymorphism data.
@@
     We then verified that the SNP downloaded from Ensembl were matching the reference in the CDS (FASTA format).
-    Second, the relative position in the CDS was converted to position in the multiple sequence alignment (containing gaps) from OrthoMaM database\cite{ranwez_orthomam_2007, douzery_orthomam_2014, scornavacca_orthomam_2019} by doing a global pairwise alignment, using the Biopython function pairwise2, between the CDS fasta and the sequence found in the alignment.
+    Second, the relative position in the CDS was converted to position in the multiple sequence alignment (containing gaps) from OrthoMaM database~\cite{ranwez_orthomam_2007, douzery_orthomam_2014, scornavacca_orthomam_2019} by doing a global pairwise alignment, using the Biopython function pairwise2, between the CDS fasta and the sequence found in the alignment.
     This conversion from genomic position to position in the alignment is only possible if the assembly used for SNP calling is the same as the one used in the alignment, the GTF annotations and the FASTA sequences.
-    SNPs were polarized using the $3$ closest outgroups found in the OrthoMam alignment with est-usfs v2.04\cite{keightley_inferring_2018}.
+    SNPs were polarized using the $3$ closest outgroups found in the OrthoMam alignment with est-usfs v2.04~\cite{keightley_inferring_2018}.
     For populations containing more than $8$ individuals, the site-frequency spectrum (SFS) was subsampled down to $16$ chromosomes ($8$ diploid individuals) without replacement (hyper-geometric distribution) to alleviate the effect of different sampling depth in the 28 populations.
@@
     Pooled across many sites, the SFS provides therefore information on the underlying $\Spop$ of mutations.
-    However, estimating a single $\Spop$ for all sampled mutations is biologically unrealistic and a distribution of fitness effects of mutations (DFE) is usually assumed\cite{eyre-walker_distribution_2006a, eyre-walker_estimating_2009a}.
-    In this study, we used the software polyDFE\cite{tataru_inference_2017, tataru_polydfe_2020}, which used a mixture of a $\Gamma$ and Exponential distributions to model the DFE of non-synonymous mutations, while synonymous mutations are considered neutral.
+    However, estimating a single $\Spop$ for all sampled mutations is biologically unrealistic and a distribution of fitness effects of mutations (DFE) is usually assumed~\cite{eyre-walker_distribution_2006a, eyre-walker_estimating_2009a}.
+    In this study, we used the software polyDFE~\cite{tataru_inference_2017, tataru_polydfe_2020}, which used a mixture of a $\Gamma$ and Exponential distributions to model the DFE of non-synonymous mutations, while synonymous mutations are considered neutral.
     The model estimates the parameters $\Spop_d$ , $b$, $p_b$ and $\Spop_b$ for non-synonymous mutations as:
@@
     For each gene and for each population with polymorphism data available, the ancestral DNA sequence was reconstructed from ancestral and fixed polymorphism (see previous section).
-    Then, using this ancestral DNA reference and the $3$ closest outgroups found in the OrthoMam alignment, we reconstructed the ancestral protein-coding DNA sequences for each node of the 4-leaves tree with the yang M5 codon model (gamma site rate variation) in FastML.v3.11\cite{ashkenazy_fastml_2012}.
+    Then, using this ancestral DNA reference and the $3$ closest outgroups found in the OrthoMam alignment, we reconstructed the ancestral protein-coding DNA sequences for each node of the 4-leaves tree with the yang M5 codon model (gamma site rate variation) in FastML.v3.11~\cite{ashkenazy_fastml_2012}.
     All polarized codon substitutions are then obtained by comparing the ancestral protein-coding DNA sequences before the split to the sister species (closest outgroup) to the ancestral DNA reference for the population of interest (without segregating polymorphism).

### 2022-11-04 copy_artworks.sh

@@ -1,21 +1,21 @@
 #!/usr/bin/env bash
 \cp -rf ./experiments/50windows-polyDFE-mC-non-adaptive/regression/results.watterson.a.scatter.pdf ./manuscript/artworks/scatter.watterson.slopeSpopSphy.pdf
 \cp -rf ./experiments/50windows-polyDFE-mC-non-adaptive/results/regression.MutSel.SelCoeff.scatter.pdf ./manuscript/artworks/scatter.Sphy.Spop.pdf
-\cp -rf ./experiments/5bins-polyDFE-mC/results/Theta.MutSel.all.stacked.pdf ./manuscript/artworks/stacked.allSNPs.pdf
-\cp -rf ./experiments/5bins-polyDFE-mC/results/Theta.MutSel.pos-weak.stacked.pdf ./manuscript/artworks/stacked.weak-pos-SNPs.pdf
-\cp -rf ./experiments/5bins-polyDFE-mC/results/Theta.MutSel.neg-weak.stacked.pdf ./manuscript/artworks/stacked.weak-neg-SNPs.pdf
-\cp -rf ./experiments/5bins-polyDFE-mC/results/Theta.MutSel.P-Seq0.heatmap.pdf ./manuscript/artworks/heatmap.neutral.pdf
-\cp -rf ./experiments/5bins-polyDFE-mC/results/Theta.MutSel.P-Sinf0.heatmap.pdf ./manuscript/artworks/heatmap.neg.pdf
-\cp -rf ./experiments/5bins-polyDFE-mC/results/Theta.MutSel.P-Ssup0.heatmap.pdf ./manuscript/artworks/heatmap.pos.pdf
-\cp -rf ./experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.AFR.MutSel-sfs.normalize.pdf ./manuscript/artworks/AFR.SFS.pdf
-\cp -rf ./experiments/5bins-polyDFE-mC/analysis/Homo_sapiens.AFR.MutSel.polyDFE_C.pdf ./manuscript/artworks/AFR.polyDFE.pdf
+\cp -rf ./experiments/5bins-all/results/Theta.MutSel.all.stacked.pdf ./manuscript/artworks/stacked.allSNPs.pdf
+\cp -rf ./experiments/5bins-all/results/Theta.MutSel.pos-weak.stacked.pdf ./manuscript/artworks/stacked.weak-pos-SNPs.pdf
[…]

### 2022-11-29 manuscript/main.tex
Refactored manuscript

@@
 \newcommand{\PpolyAdv}{\proba \left[ \polyAdv \right]}
-
+\newcommand{\AdvMean}{\beta_b}
+\newcommand{\DelMean}{\beta_d}
 \renewcommand{\baselinestretch}{1.5}
@@
 
+% The submission checklist is available at:
+% https://docs.google.com/document/d/1aHCF1on0mHTK2DoroPCLP_xto4xwHnGJCGwaL1Vm2UE/edit?usp=sharing
+
 \begin{document}
@@
 
+%TC:endignore
     \begin{abstract}
-        Mutations can be beneficial by bringing a new innovation to their bearer, allowing them to adapt to change in environments or in selection.
-        However, mutations can also be beneficial because they are repairing previous deleterious changes, simply restoring existing functions
-        In this study, we first estimated selective effects of mutations inside protein coding sequence, under a model assuming no adaptation at the phylogenetic scale.
-        We then estimated the proportion of beneficial mutations that are not adaptive innovations, and subsequently estimated their proportion among all beneficial mutations at the population scale.
-        Our work confirms that deleterious substitutions have accumulated in mammals and are currently being eliminated, resulting in up to 25\% of beneficial mutations that are not adaptive innovations, but instead are repairing previous deleterious changes.
-
+        Mutations can be beneficial by bringing an innovation to their bearer, allowing them to adapt to changes in environments or in selective pressure.
+        However, mutations can also be beneficial because they are repairing previous deleterious changes, simply restoring existing functions.
+        In this study, we first estimated selective effects of mutations inside mammalian protein coding sequences, under a model assuming no adaptation at the phylogenetic scale.
+        We then estimated the proportion of beneficial mutations that are not adaptive innovations among all beneficial mutations at the population scale.
+        Our work confirms that deleterious substitutions have accumulated in mammals and are currently being eliminated.
+        In modern humans, it results in around 25\% of beneficial mutations that are not adaptive innovations, but instead are repairing previous deleterious changes.
     \end{abstract}
 
-    \keywords{Adaptation \and beneficial mutations \and phylogenetic \and population-genetics \and codon models }
+    \keywords{Adaptation \and Back-mutation \and Phylogenetic \and Population-genetics \and Codon models }
 
-    Adaptation is considered as the main process driving the diversity of forms and functions across the tree of life, as it enables species to access new ecological niches and also respond to changes in their environment~\cite{darwin_origin_1859}.
-    In this context of adaptative evolution, a change in environment is echoed as a change of species' forms and functions, ultimately leaving signatures of accelerated changes in the species' genome~\cite{merrell_adaptive_1994}.
-    This signature of an accelerated rate of changes, generating an excess of beneficial mutations is used to quantify adaptation (fig.~\ref{fig:fitness-landscape}A), for specific genes along a specific lineage~\cite{mcdonald_adaptative_1991, smith_adaptive_2002a, welch_estimating_2006}.
+    Adaptation is considered as the main process shaping the diversity of forms and functions across the tree of life~\cite{darwin_origin_1859}.
+    It enables species to access new ecological niches and also respond to changes in their environment~\cite{darwin_origin_1859}.
+    The notion of adaptation, in its evolutionary sense, is tightly linked to the notion of change, both of the environment, and of the species responding to the latter~\cite{merrell_adaptive_1994}.
+    In genomes, adaptation leaves marks of accelerated evolution since beneficial mutations fix faster than neutral ones (fig.~\ref{fig:fitness-landscape}A).
+    The signature of an accelerated rate of substitutions can thus be interpreted as a sign of adaptation~\cite{mcdonald_adaptative_1991, smith_adaptive_2002a, welch_estimating_2006}.
     The current availability of large scale genomic data and the development of theoretical models allowed to detect and quantify adaption across genes and lineages, which is now a common practice in evolutionary biology~\cite{yang_statistical_2000, eyre-walker_genomic_2006, moutinho_variation_2019}.
-    Although these approaches led to a better understanding of the processes shaping molecular evolution, it had the effect to merely associate beneficial mutations with adaptive evolution, which should be dissociated since adaptive evolution is not the only process which can lead to beneficial mutations~\cite{charlesworth_other_2007, mustonen_fitness_2009}.
+    Although these approaches led to a better understanding of the processes shaping the rates of molecular evolution, it had the effect to associate beneficial mutations with adaptive evolution, with a loss of the notion of change.
+    However, we argue that they should be dissociated since adaptive evolution is not the only process which can lead to beneficial mutations~\cite{charlesworth_other_2007, mustonen_fitness_2009}.
     Indeed, even in a constant environment for which the population is already adapted, a deleterious mutation in an individual can reach fixation in the population by genetic drift~\cite{Ohta1992}.
-    Subsequently, a mutation restoring the ancestral state will thus be beneficial (fig.~\ref{fig:fitness-landscape}B), even though no change in the environment occurred~\cite{hartl_compensatory_1996, sella_application_2005, mustonen_fitness_2009, cvijovic_fate_2015}.
-    More precisely, this restoration of the ancestral state can happen at another loci, in which case it is referred as compensating mutations~\cite{hartl_compensatory_1996, mustonen_fitness_2009}.
-    Conversely, the restoration of the ancestral state can happen at the same locus, in which case it is referred as a beneficial back-mutation~\cite{piganeau_estimating_2003, charlesworth_other_2007}, which are the focus of this study.
+    Subsequently, a mutation restoring the ancestral fitness will thus be beneficial (fig.~\ref{fig:fitness-landscape}B), even though no change in the environment occurred~\cite{hartl_compensatory_1996, sella_application_2005, mustonen_fitness_2009, cvijovic_fate_2015}.
+    More precisely, this restoration of the ancestral fitness can happen at another loci, in which case it is referred as compensating mutations~\cite{hartl_compensatory_1996, mustonen_fitness_2009}.
+    Conversely, the restoration of the ancestral fitness can happen at the same locus, in which case it is referred as a beneficial back-mutation~\cite{piganeau_estimating_2003, charlesworth_other_2007}, which are the focus of this study.
+    If compensatory mutations still induce changes in the genetic sequence and thus genetic diversification, beneficial-back mutations reduce the diversity and do not contribute to genetic innovation, they cancel the deleterious changes.
     Taken together, not all beneficial mutations contribute to genetic innovation, and truly adaptive evolution can only be well estimated under the background of beneficial back-mutations~\cite{keightley_what_2010, rice_evolutionarily_2015}.
-    It is thus essential to distinguish the underlying reason for the advantage brought by a beneficial mutation, a back-mutation repairing damaged genomes or creating an adaptive innovations.
+    % Philosophically, our distinction between beneficial back-mutations and adaptation can appear to be far-fetched, and one can argue that beneficial back-mutations is adaptation to its own deteriorating genome.
+    % However, there is a difference between adapting to a mutation, for instance by the mean of a compensatory mutation elsewhere, and cancelling the mutation, by the mean of a substitution on the misfit amino-acid.
 
-    For an individual carrying a beneficial mutation, whether this mutation is new innovation as response to a change in environment or a beneficial back-mutation is indistinguishable.
+    For an individual carrying a beneficial mutation, whether this mutation is a new innovation responding to a change in environment or a beneficial back-mutation is indistinguishable~\cite{charlesworth_other_2007}.
     Likewise, at the level of the population, both will result in a positive transmission bias of the beneficial allele.
     However, their consequences at the macro-evolutionary scale are fundamentally different.
-    While adaptive evolution promotes phenotype diversification (fig.~\ref{fig:fitness-landscape}C), beneficial back-mutations promotes phenotype stability and preserves well established biological systems (fig.~\ref{fig:fitness-landscape}D).
-    Fundamentally, adaptive evolution is unpredictable because it caused by an unpredictable change in the environment and the underlying fitness landscape~\cite{bazykin_changing_2015}.
+    While adaptive evolution promotes phenotype diversification (fig.~\ref{fig:fitness-landscape}C), beneficial back-mutations promote phenotype stability and preserves well established biological systems (fig.~\ref{fig:fitness-landscape}D).
+    Fundamentally, the direction of adaptive evolution is unpredictable because it is caused by an unpredictable change in the environment and the underlying fitness landscape~\cite{bazykin_changing_2015}.
     On the other hand, beneficial back-mutations are predictable if the underlying stable fitness landscape is known.
@@
     In this study, fitness landscapes of protein-coding genes are estimated from multi-species sequence alignments.
-    Multi-species sequence alignments can be used as a proxy for fitness, since for example a deleterious amino acid will be more likely to be absent in the alignment.
+    Multi-species sequence alignments can be used to estimate amino acid fitness, since for example a deleterious amino acid will be more likely to be absent in the alignment.
     One of the most used methods to make these predictions is SIFT (Sort Intolerant From Tolerant), which reliably detects deleterious mutations in many taxa~\cite{ng_sift_2003, vaser_sift_2016}.
     However, SIFT scores is not interpretable as a selection coefficient.
-    Second, we know that a lot of mechanisms can influence amino acid frequency other than fitness (phylogenetic inertia, mutation biases, GC-biased gene conversion, mutational paths) which are not accounted for in SIFT\@.
+    Moreover, SIFT scores do not acknowledge some key processes that can influence the abundance of an amino-acid in an alignment.
+For instance, it does not take into account phylogenetic inertia, mutation biases, GC-biased gene conversion, or mutational paths.
     Contrarily, so-called mutation-selection codon models are rooted within a population-genetic formalism~\cite{halpern_evolutionary_1998, mccandlish_modeling_2014}.
     These phylogenetic codon models can disentangle processes of mutation at the DNA level and selection at the amino acid level.
-    Such codon models provide a nearly-neutral framework of evolution by estimating the fitness landscape over amino acid sequences for each site of the sequence (fig~\ref{fig:method}A) while taking into account non-adaptive processes impacting codon frequency~\cite{halpern_evolutionary_1998, rodrigue_mechanistic_2010, tamuri_estimating_2012, latrille_improved_2022a}.
-    From the fitness landscape obtained by fitting the model to the data, one can thus compute the scaled selection coefficient, denoted $\Sphy$, of any non-synonymous mutations.
-    Importantly, mutation-selection codon models assume that the underlying fitness landscape is stable along the phylogeny (as in fig.~\ref{fig:fitness-landscape}B), hence the null subscript $0$ for $\Sphy$.
-    As a result, a mutation with a positive $\Sphy$ would be driving the current site toward a fitter amino-acid, and thus considered a beneficial back-mutation repairing existing functions.
-    Altogether, our expectation if that beneficial back-mutations are detectable and scattered across the genomes, while at the same time some slightly deleterious mutations are reaching fixations at other loci, generating a balance at which genomes are constantly both damaged and repaired at different loci.
-    Even though each of these back-mutations is expected to have a small beneficial effect on their bearer, and that our assumptions may not always be valid, we expect that the genome-wide signature of beneficial back-mutations can be detected and quantified.
+    Such codon models provide a nearly-neutral framework of evolution by estimating the fitness landscape over amino acid sequences for each site of the sequence while taking into account non-adaptive processes impacting codon frequency~\cite{halpern_evolutionary_1998, rodrigue_mechanistic_2010, tamuri_estimating_2012, latrille_improved_2022a}.
+    Importantly, mutation-selection codon models assume that the underlying fitness landscape is stable along the phylogeny, hence is a null model of evolution without adaptation.
+    From the fitness landscape obtained by fitting the model to the multi-species sequence alignments (fig~\ref{fig:method}A), one can compute the scaled selection coefficient under this null model of evolution, denoted $\Sphy$, of any non-synonymous mutations.
+    In this context, a mutation with a positive $\Sphy$ would be driving the current site toward a fitter amino-acid, and thus considered a beneficial back-mutation (fig~\ref{fig:method}B).
+    At the genome-wide level, our expectation is that slightly deleterious mutations that are reaching fixations due to drift are scattered across the genome, such that beneficial back-mutations concurrently segregating are also expected to be spread across genes, generating a balance at which genomes are constantly both damaged and repaired simultaneously at different loci.
+    Even though each of these back-mutations is expected to have individually a small beneficial effect on their bearer, we expect that the genome-wide signature of beneficial back-mutations can be detected and quantified.
 
-    By integrating datasets at different scales (phylogeny and population), we can predict whether substitutions in terminal lineages or any mutation currently segregating in a population are beneficial back-mutations, i.e with a positive $\Sphy$ (fig~\ref{fig:method}A\&B).
+    In this study, by integrating datasets at different scales (phylogeny and population), we seek to predict whether substitutions in terminal lineages or any mutation currently segregating in a population are beneficial back-mutations, i.e with a positive $\Sphy$.
     Such a dataset can allow us to address different questions regarding the selection affecting protein-coding DNA sequences.
-    Are we empirically observing beneficial back-mutations that reached fixation recently, and one that are currently segregating in populations?
+    Can we observe beneficial back-mutations that reached fixation recently, and one that are currently segregating in populations?
     Are they effectively beneficial for the individual carrying it?
@@
             Under a stable fitness landscape (panel B), all the mutations reaching fixation are either slightly deleterious and reaching fixation due to drift, or are beneficial back-mutations restoring a more optimal amino acid.
-            Scarce beneficial back-mutations are likely to reach fixation and a bulk of deleterious mutations are eventually reaching fixation due to their sheer mass.
-            Across the genome, this process generate a balance at which genomes are constantly both damaged and repaired at different loci.
             At the phylogenetic scale (panel D), this phenomena promotes promotes phenotype stability and preserves well established biological systems.
+            At the genome level, slightly deleterious mutations that have reached fixation are supposedly scattered at different loci, such that beneficial back-mutations should also be spread across the genome.
+            We thus expect that the genome-wide signature of beneficial back-mutations can be detected and quantified, even though each mutation has individually a small beneficial effect on their bearer.
         }
@@
     \subsection*{Back-mutations in the terminal lineages}
-    We first probed for empirical evidence of beneficial back-mutation in the terminal lineages, which should be effectively beneficial.
+    We first investigated whether we could find empirical evidence of beneficial back-mutation in the terminal branches of mammals.
     We thus reconstructed the substitutions occurring along the terminal branches of the phylogenetic tree.
     For each substitution, we estimated its scaled selection coefficient ($\Sphy$) based on the stable fitness landscape of amino-acids estimated at the scale of the mammals' phylogeny (fig.~\ref{fig:method}A).
-    We showed that among all the substitutions in the terminal lineages, between 10 and 13\% had $\Sphy > 1$ (table~S1) and between 25 and 30\% had $\Sphy > 0$ (table~S2).
-    Substitutions with $\Sphy > 1$ have been beneficial since the ratio of non-synonymous over synonymous divergence, called $\dnds$, was estimated to be between 1.15 and 1.68 in the different lineages (table~S1).
+    We showed that among all the substitutions in the terminal branches, between 10 and 13\% had $\Sphy > 1$ (table~S1) and between 25 and 30\% had $\Sphy > 0$ (table~S2).
+    For substitutions with $\Sphy > 1$, the ratio of non-synonymous over synonymous divergence, called $\dnds$, was estimated to be between 1.15 and 1.68 in the different lineages (table~S1).
     This meant that beneficial back-mutations with $\Sphy > 1$ reach fixation more frequently than synonymous mutations, which are supposed to be neutral, thus are effectively beneficial.
     This also means that the ratio $\dnds$ usually used to detect adaptation while relying on substitutions between close species~\cite{mcdonald_adaptative_1991, galtier_adaptive_2016} or at the phylogenetic scale~\cite{goldman_codonbased_1994, yang_codonsubstitution_2002} is overinflated due to beneficial back-mutations.
-    Then, $\dnds$ computed exclusively on non-synonymous sites with a $\Sphy < 0$ only represent the rate of evolution discarding beneficial back-mutations by construction.
-    Thus, if we divide the $\dnds$ estimated on all substitutions by the one estimated only on substitutions predicted to be deleterious, we directly get the proportion of the rate of evolution which is contributed by beneficial back-mutations (see methods).
-    This way, we estimated that between 22\% and 27\% of $\dnds$ is inflated because of beneficial back-mutations (table~S2).
+    To alleviate this bias, $\dnds$ is computed exclusively on non-synonymous sites with a $\Sphy < 0$, representing the rate of evolution discarding beneficial back-mutations by construction.
+    By dividing $\dnds$ estimated on all substitutions by the one estimated only on substitutions predicted to be deleterious, we directly get the proportion of the rate of evolution which is contributed by beneficial back-mutations (see Material \& Methods).
+    This way, we estimated that between 22\% and 27\% of $\dnds$ is inflated because of beneficial back-mutations while they only represent between 1\% and 2\% of mutational opportunities (table~S2).
 
@@
     Given that beneficial back-mutations are effectively selected for, we then ask which proportion of new mutations are beneficial back-mutations and are also beneficial at the population scale (fig.~\ref{fig:method}C-E).
-    For each population with available polymorphism data, we first reconstructed the ancestral sequence (instead of the reference sequence) at the base of the population genealogy.
-    From this reference sequence, we computed the scaled selection coefficient ($\Sphy$) for each possible non-synonymous mutations.
+    For each population with available polymorphism data, we first reconstructed the ancestral genome (instead of the reference genome) at the base of the population genealogy.
+    From this reference sequence, we computed the scaled selection coefficient ($\Sphy$) for each possible non-synonymous mutations, weighted by their mutational opportunity (see Material \& Methods).
     We thus obtained the distribution of fitness effects (DFE) of new mutations from the ancestral sequence in \textit{Homo sapiens} (fig.~\ref{fig:homo-afr-results}A), under the assumption of the stable fitness landscape.
     Because $\Sphy$ is based on estimation of fitnesses at the mammalian scale, mutations with $\Sphy>1$ are considered beneficial back-mutations.
-    Beneficial back-mutations only represents ~1.5\% of all possible new mutations (red in fig.~\ref{fig:homo-afr-results}A, table~S3).
-    However, when focusing on the mutations that are observed in populations, namely single nucleotide polymorphism (SNP), beneficial back-mutations represents ~8.5\% of all observed mutations (red in fig.~\ref{fig:homo-afr-results}B, table~S3).
+    Beneficial back-mutations only represents \~1.5\% of all possible new mutations (red in fig.~\ref{fig:homo-afr-results}A, table~S3).
+    However, when focusing on the mutations that are observed in populations, namely single nucleotide polymorphism (SNP), beneficial back-mutations represents \~8.5\% of all observed mutations (red in fig.~\ref{fig:homo-afr-results}B, table~S3).
 
@@
     As such, methods have been developed to estimate the distribution of fitness effect (DFE) at the population scale by gathering information across many SNPs~\cite{eyre-walker_distribution_2006a, eyre-walker_estimating_2009a, galtier_adaptive_2016, tataru_inference_2017}.
-    These methods offer a unique opportunity to compare the DFE at the population scale ($\Spop$) and at the phylogenetic scale ($\Sphy$).
+    These methods offer a unique opportunity to compare selection coefficients estimated at the population scale ($\Spop$) and at the phylogenetic scale ($\Sphy$).
     In order to estimate the DFE at the population level and gather robust statistical estimates, we grouped SNPs observed at the population level (e.g.~in humans of African descent in fig.~\ref{fig:homo-afr-results}) in 5 classes of predicted selection coefficient: severely deleterious with $\divStrongDel$, deleterious with $\divDel$, weakly deleterious with $\divWeakDel$, weakly beneficial with $\divWeakAdv$ and beneficial with $\divAdv$ (fig.~\ref{fig:homo-afr-results}B).
-    In each of theses classes, the number of derived alleles in the population for each SNPs is used to generate a site-frequency spectrum (SFS) (fig.~\ref{fig:homo-afr-results}C).
-    Compared to synonymous mutations which are supposedly neutral (black line in fig.~\ref{fig:homo-afr-results}C), mutations predicted to be deleterious (blue and green lines in fig.~\ref{fig:homo-afr-results}C) were, as expected, underrepresented at high frequencies in the population, a signature of ongoing purifying selection.
-    However, these observations remain qualitative.
 
     To obtain a quantitative estimate of the distribution of selection coefficient for each category of SNPs, we used the model polyDFE~\cite{tataru_inference_2017, tataru_polydfe_2020}.
-    This model uses the count of derived alleles for each frequency class of the SFS to infer the distribution of fitness effects (DFE) of the region under study.
-    The model uses the number of sites ($L$) for each category (fig.~\ref{fig:homo-afr-results}A, see Material and Methods), the counts of synonymous derived allele as a neutral model, which allow to control for demographic effects, and polarization errors when inferring the ancestral state.
+    This model uses the count of derived alleles for each frequency class (fig.~\ref{fig:homo-afr-results}C) to infer the distribution of fitness effects (DFE).
+    Moreover, the model relies on the mutational opportunities ($L$) for each category of $\Sphy$ (fig.~\ref{fig:homo-afr-results}A, see Material \& Methods) as well as the count of synonymous derived alleles used as a neutral model, which allow to control for demographic effects, and polarization errors when inferring the ancestral states.
     We could estimate the proportion of beneficial mutations ($\PpolyAdv$), nearly-neutral mutations ($\PpolyNeutral$) and deleterious mutations ($\PpolyDel$) for each class of selection previously defined (fig.~\ref{fig:homo-afr-results}D).
-    We found that SNPs predicted to be deleterious based on the selection coefficient $\Sphy$ estimated across the phylogeny of mammals were effectively purged at the population scale.
+    We found that SNPs predicted to be deleterious based on the selection coefficient $\Sphy$ estimated across the phylogeny of mammals were effectively purged at the population scale (blue and green columns in fig.~\ref{fig:homo-afr-results}D)
     Purifying selection is therefore largely predictable and amino acids with low fitness across mammals are effectively purged away in each population.
-    Then, SNPs predicted to be beneficial based on the selection coefficient $\Sphy$ estimated at the scale of the phylogeny of mammals are indeed beneficial for individuals currently bearing them.
+    Then, SNPs predicted to be beneficial based on the selection coefficient $\Sphy$ estimated at the scale of the phylogeny of mammals are indeed beneficial for individuals currently bearing them (red column in fig.~\ref{fig:homo-afr-results}D).
     These results confirmed that selection towards amino acids that are restoring existing function is ongoing in these populations.
-    Between these two extreme cases, SNPs predicted to be weakly selected (cyan and orange in fig.~\ref{fig:homo-afr-results}) were effectively composed of neutral, beneficial and deleterious mutations.
+    Between these two extreme cases, SNPs predicted to be weakly selected (cyan and orange columns in fig.~\ref{fig:homo-afr-results}D) were effectively composed of neutral, beneficial and deleterious mutations.
 
     We replicated our experiment across 28 populations of different mammal species (fig.~\ref{fig:heatmap}) and found that SNPs predicted to be deleterious were indeed purged at the population scale (blue and green rows in fig.~\ref{fig:heatmap}A).
-    However, SNPs predicted to be weakly beneficial ($\divWeakAdv$) were composed of a mix of neutral and selected mutations with varying proportions across the different populations (orange row in fig.~\ref{fig:heatmap}B).
+    However, SNPs predicted to be weakly beneficial ($\divWeakAdv$) were composed of a mix of neutral and selected mutations with varying proportions across the different populations (cyan and orange row in fig.~\ref{fig:heatmap}B).
     Finally, SNPs predicted to be beneficial back-mutations ($\divAdv$) were found to be beneficial with varying proportions across populations (red row in fig.~\ref{fig:heatmap}C).
@@
 
-    Finally, we propose an estimator for the probability of a beneficial mutation to be a beneficial back-mutation, i.e. $\mathbb{P} [ \Sphy > 1  \given  \Spop > 1]$ (fig.~\ref{fig:method}C-F).
+    Finally, we propose an estimator for the probability of a beneficial mutation to be a beneficial back-mutation, computed as $\mathbb{P} [ \Sphy > 1  \given  \Spop > 1]$ (fig.~\ref{fig:method}C-F).
     We obtained from the analyses above the following probabilities $\mathbb{P} [ \Sphy > 1 ]$, $\mathbb{P} [ \Spop > 1 ]$, $\mathbb{P} [ \Spop > 1  \given  \Sphy > 1]$.
@@
     Finally, $\mathbb{P} [ \Spop > 1  \given  \Sphy > 1]$ is the probability for a back-mutation ($\Sphy > 1$) to be effectively beneficial at the level of the population ($\Spop > 1$), when we restricted our analysis on SNPs that are already predicted to be beneficial back-mutations (black fill for the category $\Sphy > 1$ in fig~\ref{fig:homo-afr-results}D and table~S3).
-    Combining these probabilities using Bayes theorem, we now obtain the probability for a beneficial mutation to be a back-mutation $\mathbb{P} [ \Sphy > 1  \given  \Spop > 1]$ (see Material and Methods).
+    Combining these probabilities using Bayes theorem, we now obtain the probability for a beneficial mutation to be a back-mutation $\mathbb{P} [ \Sphy > 1  \given  \Spop > 1]$ (see Material \& Methods).
     We estimated $\mathbb{P} [ \Sphy > 1  \given  \Spop > 1]$ across all populations sampled and obtained a proportion that varies between 10 and 26\% (table~S3).
@@
     A population that experienced a high $\Ne$ along its evolutionary time should be closer to the optimal state under a stable fitness landscape because of the higher efficacy of selection.
-    This should decrease the probability of beneficial back-mutations.
+    This should decrease the probability of beneficial back-mutations~\cite{huber_determining_2017}.
     On the other hand, a high $\Ne$ over a short evolutionary time will induce more extreme fitness effects and a larger proportion of mutations will be beneficial (otherwise effectively neutral), thus increasing the proportion of beneficial back-mutations.
-    Overall, the proportion of beneficial back-mutations is expected to be more dependent on effective population size contraction or expansion rather than on the short term effective population size captured by the synonymous diversity~\cite{charlesworth_other_2007}.
+    Overall, the proportion of beneficial back-mutations is expected to be more dependent on long-term effective population size as well as contraction or expansion rather than on the short term effective population size captured by the synonymous diversity~\cite{charlesworth_other_2007,huber_determining_2017}.
 
@@
 
-    \subsection*{a bridge between phylogenetic and population-genetics}
+    \subsection*{A bridge between phylogenetic and population-genetics}
     In this study, we first estimated selective effects of mutations inside protein coding sequence, under a model assuming no adaptation at the phylogenetic scale.
-    We then estimated the proportion of beneficial mutations that are not adaptive innovations, and subsequently estimated their proportion among all beneficial mutations at the population scale.
+    We then estimated the proportion of beneficial back-mutations, that are not adaptive innovations, and subsequently estimated their proportion among all beneficial mutations at the population scale.
     Our work confirms that deleterious substitutions have accumulated in mammals and are currently being eliminated, resulting in up to 25\% of beneficial mutations that are not adaptive innovations, but instead are repairing previous deleterious changes.
 
-    From a theoretical evolution perspective, we have found that we can use phylogenetic signals and mutation-selection codon models to predict the selection coefficient of a mutation ($\Sphy$).
+    At the phylogenetic scale, we have found that we can use mutation-selection codon models to predict the selection coefficient of a mutation ($\Sphy$).
     However, we so far assumed no changes in effective population size along the phylogeny while it has been established that population size changes have a major effect on selection dynamics~\cite{lanfear_population_2014, jones_shifting_2017, platt_protein_2018}.
     Mutation-selection models with changes in effective population sizes along the phylogeny have been developed~\cite{latrille_inferring_2021a}, but are, for the moment, too computational intensive to be performed genome-wide.
-    Hybrid mutation-selection and $\omega$-based codon models could provide a way forward to in integrate site-specific selection and branch-specific drift~\cite{brevet_reconstructing_2021a}.
+    Hybrid mutation-selection and phenomenological codon models could provide a way forward to integrate site-specific selection and branch-specific drift~\cite{brevet_reconstructing_2021a}.
     As for the estimate of selection, SIFT scores based on amino acid alignments across species have also been found to be informative of the selection pressure exerted at the population scale~\cite{chen_hunting_2021}.
-    Our study indeed showed that sites with a higher SIFT score at the phylogenetic scale are more beneficial in the different populations (supp.\ mat\  section SIFT scores).
-    In practice, SIFT scores are more coarse grained, with for example a bulk of mutations with a score of 1.0 (the highest), and does not provide a boundary between beneficial and deleterious mutations, nor are they based on population-genetic formalism.
+    We also concur that mutations with a low SIFT score are more deleterious in the different populations, and conversely mutations with a high SIFT scores are more beneficial (supp.\ mat.\  section SIFT scores).
+    In practice, SIFT scores are more coarse grained, with for example a bulk of mutations with a score of 1.0 (the highest), and it does not provide a boundary between beneficial and deleterious mutations.
+    On the contrary, mutation-selection codon models are genuinely taking into account the tug-of-war between scarce beneficial mutations likely to reach fixation and a bulk of deleterious mutations eventually reaching fixation due to their sheer mass.
+    As such, these models can be used as a null model to predict the expected rate of evolution of proteins~\cite{spielman_relationship_2015, dosreis_how_2015} under a stable fitness landscape.
+    A departure from this null model of evolution would indicate that proteins are evolving under a changing fitness landscape~\cite{cvijovic_fate_2015, rodrigue_detecting_2017, tamuri_mutationselection_2021} and is a signal of pervasive adaptive evolution~\cite{rodrigue_bayesian_2021} or of pervasive epistasis~\cite{rodrigue_detecting_2017}.
+    As such, a stable fitness landscape as a null model is thus statistically more powerful to detect adaptation than assuming that the null model is neutral evolution.
+    Taken together, mutation-selection models are a mandatory tool in evolutionary biology to detect and quantify adaptation at the phylogenetic scale, while acknowledging the contribution of beneficial back-mutations.
 
-    Biologically, another mechanism which generate non-adaptive beneficial mutations is compensatory mutations, which are repairing damage caused by deleterious mutations at another loci in the genome and generating a widespread signal of non-adaptative evolution~\cite{hartl_compensatory_1996, pollock_strong_2014, starr_epistasis_2016}.
-    In our study we focused on mutations toward a more optimal amino-acid at a given site, not accounting for compensatory mutations since we assumed a model of fitness landscape without epistasis.
-    As shown in other studies, these models without epistasis provide a reasonable estimate of average fitness profiles~\cite{youssef_consequences_2020}.
-    But most importantly, we argue that our estimation of the amount of beneficial back-mutations is an underestimation, and that accounting for compensatory mutations by means of epistasis would mechanically increase our estimate.
-    Indeed, a fluctuating fitness landscape due to an external forces (i.e.
-changes in environment) results in an acceleration of the rate of evolution~\cite{ rodrigue_detecting_2017, rodrigue_bayesian_2021}, which generates epistatic mutations that are immediately beneficial~\cite{gong_epistatically_2014}.
-    In contrast, pervasive epistasis generates the opposite pattern, an entrenchment~\cite{goldstein_evolutionary_2004, goldstein_nonadaptive_2015} resulting in a slowing down of the rate evolution~\cite{rodrigue_detecting_2017, patel_epistasis_2022} or a standstill~\cite{youssef_evolution_2022}.
-    In other words, under pervasive epistasis, finding empirical evidence for beneficial back-mutations is harder since restoring mutations become less and less likely to occur over time~\cite{goldstein_nonadaptive_2015, goldstein_sequence_2017, park_epistatic_2022}.
-    Our study thus shows that beneficial back-mutations should not be overlooked, and we argue that both beneficial back-mutations and compensatory mutations play an important role in preventing our genome from collapsing under a mutation load.
+    At the population scale ($\Spop$), our results also rely on some hypothesis and thresholds.
+    We first defined the threshold to consider a mutation beneficial ($\Spop$ or $\Sphy$ greater than one), such that nearly-neutral mutations that are only slightly-beneficial are discarded.
+    To also consider slightly-beneficial mutations, we performed the same analysis with a threshold of zero.
+    With this methodology, the proportion of back-mutations among all beneficial mutations increases and ranges from 12 to 45\% across populations(table~S4).
+    Second, there is no consensus on the expected shape of the distribution of fitness effects (DFE)~\cite{welch_divergence_2008, bataillon_effects_2014}, although it has been found to be reliably constant between closely related species~\cite{castellano_comparison_2019}.
+    We used a model that allowed the inference of a continuous DFE by modelling the negative side of the DFE as a gamma distribution, and the positive side as an exponential distribution with a mean greater than one.
+    To control for the uncertainty of the underlying DFE, we also performed our analysis assuming a discretized DFE with 5 categories of selection coefficients, and the proportion of back-mutations among all beneficial mutations with this DFE ranges from 3 to 20\% across populations (table~S5).
+    Consequently, even though our general framework contrasting the phylogenetic and population scale is theoretically consistent, we acknowledge that estimating the proportion of back-mutations among all beneficial ones is dependent on the assumption for the underlying DFE at the population scale and the threshold used to define a beneficial mutation.
+    As a result, further work are required to investigate the shape of the DFE at the population scale.
+    Notably, DFE estimated at the mammalian scale (fig.~\ref{fig:homo-afr-results}A) have a negative mode (around $\Sphy=-5$), consistent with experimental DFEs obtained by mutation accumulation (fig.~S10).
+    Contrarily, continuous DFEs estimated at the population scale have by definition a mode at 0.
+    We argue that methods estimating DFE at the population scale should as a result assume a mode shifted toward negative values of $\Spop$.
 
-    For the estimates of selection at the population scale ($\Spop$), there is no consensus on the expected shape of the DFE~\cite{welch_divergence_2008, bataillon_effects_2014}, although it has been found to be reliably constant between species~\cite{castellano_comparison_2019}.
-    We used a model that allowed the inference of a full DFE by modelling the negative side of the DFE as a gamma distribution, and the positive side as an exponential distribution.
-    However, when we aggregate SNPs that are expected to be strongly deleterious or strongly beneficial, the model struggles to fit their DFE to a gamma or an exponential distribution.
-    As a result, while the proportions of deleterious/weakly-selected/beneficial mutations stays reliable, the mean values for selection coefficients ($\Spop$) estimated by polyDFE become biologically absurd ($\Spop \ll -10^3$).
-    Such effect is not found for neutral SNPs and a method to accurately estimate the mean value of selection coefficients from SFS without assuming any shape for the DFE remains yet to be developed.
     Aside from methodological limitations, the mammalian case study might also not be representative of other clades.
@@
     It would thus be of great interest to reproduce our experiment with other clades, such as \textit{Drosophila} or birds which tend to have higher effective population size.
-    It would also be interesting to have access to more shallow but wider phylogenies to increase the resolution of our predictions.
+    It would also be interesting to have access to more shallow but wider phylogenies to estimate fitness landscapes at short time-scales.
 
     From a structural biology perspective, we have found that proteins are not optimal for their fitness, which has been proved for their kinetics and thermodynamics~\cite{hartl_compensatory_1996, taverna_why_2002, goldstein_evolution_2011}.
-    Philosophically, our distinction between beneficial back-mutations and adaptation can appear to be far-fetched, and one can argue that beneficial back-mutations is adaptation to its own deteriorating genome.
-    However, there is a difference between adapting to a mutation, for instance by the mean of a compensatory mutation elsewhere, and cancelling the mutation, by the mean of a substitution on the misfit amino-acid.
-    The first still implies changes in the genetic sequence and thus genetic diversification, while the second reduces the diversity.
-    We also argue that this distinction is important when we seek to detect adaptation, and is actually not an encumbrance but rather a strength.
-    Precisely, mutation-selection models are genuinely taking into account the tug-of-war between scarce beneficial mutations likely to reach fixation and a bulk of deleterious mutations eventually reaching fixation due to their sheer mass.
-    These models can thus be used as a null model to predict the expected rate of evolution of proteins~\cite{spielman_relationship_2015, dosreis_how_2015} under a stable fitness landscape.
-    A departure from this model indicates that proteins are evolving under a changing fitness landscape~\cite{cvijovic_fate_2015, rodrigue_detecting_2017, tamuri_mutationselection_2021} and is a signal of pervasive adaptive evolution~\cite{rodrigue_bayesian_2021} or of pervasive epistasis~\cite{rodrigue_detecting_2017}.
-    As such, a stable fitness landscape as a null model is thus statistically more powerful to detect adaptation than assuming that the null model is neutral evolution.
-    Taken together, mutation-selection models are a mandatory tool in evolutionary biology to detect and quantify adaptation at the phylogenetic scale, while acknowledging beneficial back-mutations.
+    In this context of suboptimal fitness, compensatory mutations can repair damage caused by deleterious mutations at another loci and generate a widespread signal of positive selection~\cite{hartl_compensatory_1996, pollock_strong_2014, starr_epistasis_2016}.
+    In our study we focused on mutations toward a more optimal amino-acid at a given site, not accounting for compensatory mutations since we assumed a model of fitness landscape without epistasis, where site-specific amino-acid profiles are independent of one another.
+    As shown in other studies, these models without epistasis provide a reasonable estimate of average fitness profiles~\cite{youssef_consequences_2020}.
+    But most importantly, we argue that our estimation of the amount of beneficial back-mutations is an underestimation, and that accounting for compensatory mutations by means of epistasis would mechanically increase our estimate.
+    Indeed, a fluctuating fitness landscape due to an external forces (i.e.~changes in environment) results in an acceleration of the rate of evolution~\cite{rodrigue_detecting_2017, rodrigue_bayesian_2021}, which generates epistatic mutations that are immediately beneficial~\cite{gong_epistatically_2014}.
+    In contrast, pervasive epistasis generates the opposite pattern, an entrenchment~\cite{goldstein_evolutionary_2004, goldstein_nonadaptive_2015} resulting in a slowing down of the rate evolution~\cite{rodrigue_detecting_2017, patel_epistasis_2022} or a standstill~\cite{youssef_evolution_2022}.
+    In other words, under pervasive epistasis, finding empirical evidence for beneficial back-mutations is harder since restoring mutations become less and less likely to occur over time~\cite{goldstein_nonadaptive_2015, goldstein_sequence_2017, park_epistatic_2022}.
+    As our study shows that beneficial back-mutations should not be overlooked, we argue that both beneficial back-mutations and compensatory mutations play an important role in preventing our genome from collapsing under a mutation load.
 
     In conclusion, we showed that by integrating genome-wide datasets at the phylogeny and the population scale, it is possible to estimate the proportion of beneficial mutations repairing existing functions instead of generating adaptive innovations.
+    This study at the interface between phylogenetic and population-genetics thus provide a step toward an integration of different scales necessary to decipher the combined effects of mutation, selection and drift on genome evolution.
     We argue that our approach is general and our methodology can be readily applied to different estimations of fitness landscape at the phylogenetic scale, and different models and methods estimating distribution of fitness effects at the population scale.
-    This study at the interface between phylogenetic and population-genetics thus provide a step toward an integration of different scales necessary to decipher the combined effects of mutation, selection and drift on genome evolution.
 
+%TC:ignore
     \section*{Acknowledgments}
@@
 
-    Protein-coding DNA sequences alignments in placental mammals and their corresponding gene trees were extracted from the \href{https://www.orthomam.univ-montp2.fr}{OrthoMaM} database.
-    It contained a total of $116$ mammalian reference sequences in v10c~\cite{ranwez_orthomam_2007, douzery_orthomam_2014, scornavacca_orthomam_2019}.
+    Protein-coding DNA sequences alignments in placental mammals and their corresponding gene trees are from the \href{https://www.orthomam.univ-montp2.fr}{OrthoMaM} database, and processed as in \textcite{latrille_genes_2022}.
+    OrthoMaM contains a total of $116$ mammalian reference sequences in v10c~\cite{ranwez_orthomam_2007, douzery_orthomam_2014, scornavacca_orthomam_2019}.
     Genes located on the X, Y chromosomes and the mitochondrial genome were discarded from the analysis, because the level of polymorphism, which is necessary in the population-based analyses, is expected to be different in these three genomic regions.
     Sequences of species for which we used population-level polymorphism (see below), as well as their sister species, were removed from the analysis to ensure independence between the data used in the phylogenetic and population scale.
-    Altogether, we analyzed $14,509$ protein-coding DNA sequences for at most $87$ sequences of placental mammals.
+    Altogether, our genome-wide dataset contains $14,509$ protein-coding DNA sequences for at most $87$ sequences of placental mammals.
 
@@
     \label{subsec:s-phylogeny-method}
-
     We analyzed the phylogenetic level data using mutation-selection models.
@@
     In the manuscript and the following material, the source ($a$) and target ($b$) codons as well as the site ($i$) are implicit and thus never explicitly written.
-    We ran the Bayesian software \textit{BayesCode} (\url{https://github.com/ThibaultLatrille/bayescode}) on each protein-coding DNA alignment~\cite{rodrigue_bayesian_2021}.
-    We ran a Markov chain Monte-Carlo (MCMC) analysis during $2000$ generations, with a burn-in period of $1000$ generations, to obtain posterior mean estimates of the amino acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$\@.
+    The Bayesian software \textit{BayesCode} (\url{https://github.com/ThibaultLatrille/bayescode}) was run on each protein-coding DNA alignment for $2000$ generations of Markov Chain Monte-Carlo (MCMC), as in \textcite{latrille_genes_2022}.
+    For each gene, after discarding the burn-in period of $1000$ generations of MCMC, we obtain posterior mean estimates (over the $1000$ generations left of MCMC) of the mutation rate matrix ($\UniDimArray{\mu}$) as well as the 20 amino acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$.
 
@@
 
-    We retrieved the genetic variants representing the population level polymorphism from the following species and respective available datasets: \textit{Equus caballus} (EquCab2 assembly in the EVA study PRJEB9799~\cite{alabri_whole_2020}), \textit{Bos taurus} (UMD3.1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}), \textit{Ovis aries} (Oar\_v3.1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}), \textit{Capra Hircus} (CHIR1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}, liftover to the ARS1 assembly), \textit{Chlorocebus sabaeus} (ChlSab1.1 assembly in the EVA project PRJEB22989~\cite{svardal_ancient_2017}), \textit{Homo sapiens} (GRCh38 assembly from the 1000-genome project~\cite{consortium_integrated_2012a, the1000genomesprojectconsortium_global_2015}).
-    In total, we analyzed 28 populations across the 6 different species with polymorphism data.
+    The genetic variants representing the population level polymorphism are from the following species and respective available datasets: \textit{Equus caballus} (EquCab2 assembly in the EVA study PRJEB9799~\cite{alabri_whole_2020}), \textit{Bos taurus} (UMD3.1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}), \textit{Ovis aries} (Oar\_v3.1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}), \textit{Capra Hircus} (CHIR1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}, converted to ARS1 assembly with dbSNP identifiers\cite{sherry_dbsnp_2001}), \textit{Chlorocebus sabaeus} (ChlSab1.1 assembly in the EVA project PRJEB22989~\cite{svardal_ancient_2017}), \textit{Homo sapiens} (GRCh38 assembly from the 1000-genome project~\cite{consortium_integrated_2012a, the1000genomesprojectconsortium_global_2015}).
+    In total, we analyzed 28 populations across the 6 different species with polymorphism data, also processed as in \textcite{latrille_genes_2022}.
+
     Genetic variants that were not found within a gene were not used in further analyses.
@@
     Finally, stop codon mutants were also discarded.
-
     Each SNP (chromosome, position, strand) in the focal species was matched to its relative position (chromosome, position, strand) in the protein-coding DNA alignment by first converting the genomic positions to relative position in the coding sequence (CDS) using gene annotation files (GTF format) downloaded from Ensembl (\url{ensembl.org}).
     We then verified that the SNP downloaded from Ensembl were matching the reference in the CDS (FASTA format).
-    Second, the relative position in the CDS was converted to position in the multiple sequence alignment (containing gaps) from OrthoMaM database~\cite{ranwez_orthomam_2007, douzery_orthomam_2014, scornavacca_orthomam_2019} by doing a global pairwise alignment, using the Biopython function pairwise2, between the CDS fasta and the sequence found in the alignment.
-    This conversion from genomic position to position in the alignment is only possible if the assembly used for SNP calling is the same as the one used in the alignment, the GTF annotations and the FASTA sequences.
+    Second, the relative position in the CDS was converted to position in the multiple sequence alignment (containing gaps) from OrthoMaM database (see section \ref{subsec:s-phylogeny-method}) by doing a global pairwise alignment, using the Biopython function pairwise2, between the CDS fasta and the sequence found in the alignment.
+    This conversion from genomic position to alignment position is only possible if the assembly used for SNP calling is the same as the one used in the alignment, the GTF annotations and the FASTA sequences.
     SNPs were polarized using the $3$ closest outgroups found in the OrthoMam alignment with est-usfs v2.04~\cite{keightley_inferring_2018}.
-    For populations containing more than $8$ individuals, the site-frequency spectrum (SFS) was subsampled down to $16$ chromosomes ($8$ diploid individuals) without replacement (hyper-geometric distribution) to alleviate the effect of different sampling depth in the 28 populations.
-    We developped a Snakemake pipeline to integrate polymorphism and divergence data with custom scripts written in python 3.9.
 
-    \subsection{Selection coefficient ($\Spop$) in population-based method}
-    \label{subsec:s-polymorphism-method}
-    The probability to sample an allele at a given frequency (before fixation or extinction) is informative of its scaled selection coefficient at the population scale ($\Spop$).
-    Pooled across many sites, the SFS provides therefore information on the underlying $\Spop$ of mutations.
-    However, estimating a single $\Spop$ for all sampled mutations is biologically unrealistic and a distribution of fitness effects of mutations (DFE) is usually assumed~\cite{eyre-walker_distribution_2006a, eyre-walker_estimating_2009a}.
-    In this study, we used the software polyDFE~\cite{tataru_inference_2017, tataru_polydfe_2020}, which used a mixture of a $\Gamma$ and Exponential distributions to model the DFE of non-synonymous mutations, while synonymous mutations are considered neutral.
-    The model estimates the parameters $\Spop_d$ , $b$, $p_b$ and $\Spop_b$ for non-synonymous mutations as:
-    \begin{equation}
-        \phi \left( \Spop; \Spop_d , b, p_b, \Spop_b \right) =
-        \begin{dcases}
-            \left( 1 - p_b \right) f_{\Gamma}(-\Spop; -\Spop_d, b) & \text{ if $\Spop \leq 0$,} \\
-            p_b f_{e}(\Spop; \Spop_b) & \text{ if $\Spop > 0$,} \\
-        \end{dcases}
-    \end{equation}
-    where $\Spop_d \leq -1 $ is the estimated mean of the DFE for $\Spop \leq 0$,
-    $b \geq 0.4$ is the estimated shape of the $\Gamma$ distribution,
-    $0 \leq p_b \leq 1$ is the estimated probability that $\Spop > 0$,
-    $\Spop_b \geq 1$ is the estimated mean of the DFE for $\Spop > 0$,
-    and $f_{\Gamma}(x; m, b)$ is the density of the $\Gamma$ distribution with mean m and shape b, while $f_{e}(x; m)$ is the density of the Exponential distribution with mean $m$.
-    Once the DFE was fitted to the data, the proportion of beneficial ($\PpolyAdv$), nearly-neutral ($\PpolyNeutral$) and deleterious mutations ($\PpolyDel$) were given as:
-    \begin{align}
-        \PpolyAdv &= p_b \int_{1}^{+\infty} f_{e}(\Spop; \Spop_b) \der \Spop,  \label{eq:polyProbaAdv} \\
-        \PpolyNeutral &= p_b \int_{0}^{1} f_{e}(\Spop; \Spop_b) \der \Spop + \left( 1 - p_b \right) \int_{0}^{1} f_{\Gamma}(\Spop; -\Spop_d, b) \der \Spop, \\
-        \PpolyDel &= \left( 1 - p_b \right) \int_{1}^{+\infty} f_{\Gamma}(\Spop; -\Spop_d, b) \der \Spop. \label{eq:polyProbaDel}
-    \end{align}
-
-    PolyDFE required one SFS for non-synonymous mutatipons and one for synonymous mutations (neutral expectation), as well as the number of sites on which each SFS has been sampled.
-    We performed the following four-step procedure to obtain the number of sites for each SFS.
-    First, for each population with polymorphism data available, the polarized SNPs (ancestral and derived alleles) were used to reconstruct the ancestral DNA sequence, containing only substitutions and no segregating polymorphisms.
+    \subsection{Mutational opportunities}
+    \label{subsec:nunber-of-sites}.
+    For each population with polymorphism data available, the polarized SNPs (ancestral and derived alleles) were used to reconstruct the ancestral DNA sequence, containing only substitutions and no segregating polymorphisms.
     If a SNP is still segregating in the population, the ancestral version of the SNP is used.
     However, if the derived allele is shared by all individuals in the population, the allele is considered fixed and the derived allele of the SNP is used as the ancestral.
-    Second, from this reconstructed ancestral sequence, all possible mutations were computed, weighted by the mutation rate between nucleotide ($\mu$), which was estimated at the phylogenetic scale.
-    Third, the total mutation rate for synonymous mutations, called $\mu_{\textrm{syn}}$, was estimated as the sum across the whole genome.
-    Similarly, the total mutation rate for each class of selection, called  $\mu\left( \Sphyclass \right)$, was estimated as the sum across all non-synonymous mutations if their selection coefficient at the phylogenetic scale ($\Sphy$) was in the class $\Sphyclass$ (e.g.
+    From this reconstructed ancestral genome (instead of the reference genome) at the base of the population genealogy, all possible mutations were computed, weighted by the mutation rate between nucleotide ($\mu$), which was estimated at the phylogenetic scale.
+    The total mutation rate for synonymous mutations, called $\mu_{\textrm{syn}}$, was estimated as the sum across the whole genome.
+    Similarly, the total mutation rate for each class of selection $\Sphyclass$, called $\mu\left( \Sphyclass \right)$, was estimated as the sum across all non-synonymous mutations if their selection coefficient at the phylogenetic scale ($\Sphy$) was in the class $\Sphy \in \Sphyclass$ (e.g.
 $\Sphyclass = \divAdv$).
-    Fourth, the number of sites ($L \left( \Sphyclass \right)$) for each class of selection coefficient ($\Sphyclass$) was finally computed as the total number of sites across the genome ($L_{tot}$) weighted by the ratio of the aggregated mutations rates falling in the class ($\mu\left( \Sphyclass \right)$) over the total mutation rate for all possible mutations ($\mu_{tot}$) as:
+    Finally, the mutational opportunities ($L \left( \Sphyclass \right)$) for each class of selection coefficient ($\Sphyclass$) was finally computed as the total number of sites across the genome ($L_{tot}$) weighted by the ratio of the aggregated mutations rates falling in the class ($\mu\left( \Sphyclass \right)$) over the total mutation rate for all possible mutations ($\mu_{tot}$) as:
     \begin{align}
@@
 
-    Altogether, for each class of selection ($\Sphyclass$) of non-synonymous SNPs (or for all SNPs), we thus estimated the parameters of the DFE $\left( \Spop; \Spop_d , b, p_b, \Spop_b \right)$ using maximum likelihood with polyDFE from the number of sites and the SFS obtained by aggregating all the SNPs in the selection class.
-    Once fitted to the data, the parameters of the DFE $\left( \Spop; \Spop_d , b, p_b, \Spop_b \right)$ are used to compute $\PpolyAdv$, $\PpolyNeutral$, $\PpolyDel$ using eq.~\ref{eq:polyProbaAdv}-\ref{eq:polyProbaDel}.
-
-    From Bayes theorem, it is now possible to obtain the probability for a beneficial mutation to be a back-mutation .
-    In other words, we seek to get the probability that a mutation is repairing the genome ($\divAdv$) given that it is beneficial ($\polyAdv$), as:
-    \begin{equation}
-        \proba \left[\divAdv \given \polyAdv\right] = \frac{\proba \left[\polyAdv \given \divAdv\right] \times \proba\left[\divAdv\right]}{\PpolyAdv},
-        \label{eq:bayes}
-    \end{equation}
-    where $\PpolyAdv$ is computed from all SNPS, $\proba \left[\polyAdv \given \divAdv\right]$ is obtained from the set of SNPs in the class $\Sphyclass = \divAdv$, and $\proba\left[\divAdv\right]$ is the probability for a new mutation to be inside the class $\divAdv$, thus computed as:
-    \begin{equation}
-        \proba\left[\divAdv\right] = \frac{\mu\left( \Sphyclass = \divAdv \right)}{\mu_{tot}},
-        \label{eq:proba-dfe-mutsel}
-    \end{equation}
-
-    \subsection*{Substitution mapping in the terminal branch}
+    \subsection{Substitution mapping in the terminal branch}
     \label{subsec:substitution-mapping-in-the-terminal-branch}
-    For each gene and for each population with polymorphism data available, the ancestral DNA sequence was reconstructed from ancestral and fixed polymorphism (see previous section).
-    Then, using this ancestral DNA reference and the $3$ closest outgroups found in the OrthoMam alignment, we reconstructed the ancestral protein-coding DNA sequences for each node of the 4-leaves tree with the yang M5 codon model (gamma site rate variation) in FastML.v3.11~\cite{ashkenazy_fastml_2012}.
-    All polarized codon substitutions are then obtained by comparing the ancestral protein-coding DNA sequences before the split to the sister species (closest outgroup) to the ancestral DNA reference for the population of interest (without segregating polymorphism).
+    For each gene and for each population with polymorphism data available, the genome at the base of the population genealogy was reconstructed (see section \ref{subsec:nunber-of-sites}).
+    Then, using this genome at the base of the population genealogy and the $3$ closest outgroups found in the OrthoMam alignment, we reconstructed the ancestral protein-coding DNA sequences for each node of the 4-leaves tree with the yang M5 codon model (gamma site rate variation) in FastML.v3.11~\cite{ashkenazy_fastml_2012}.
+    All polarized codon substitutions are then obtained by comparing the ancestral protein-coding DNA sequences before the split to the sister species (closest outgroup) to the genome at the base of the population genealogy.
     We considered \textit{Ceratotherium simum simum} as \textit{Equus caballus} sister species; \textit{Bison bison bison} as \textit{Bos taurus} sister species; \textit{Pantholops hodgsonii} as \textit{Ovis aries} sister species; \textit{Pantholops hodgsonii} as \textit{Capra Hircus} sister species; \textit{Macaca mulatta} as \textit{Chlorocebus sabaeus} sister species and finally we considered \textit{Pan troglodytes} as \textit{Homo sapiens} sister species.
@@
     \end{align}
-    where $D \left( \Sphyclass \right) $ is the number of non-synonymous substitutions in the class $\Sphyclass$, $D_{\textrm{syn}}$ is the number of synonymous substitutions across the genome, while $L \left( \Sphyclass \right)$ and $L_{\textrm{syn}}$ are the number of non-synonymous and synonymous sites as defined in the previous section.
+    where $D \left( \Sphyclass \right) $ is the number of non-synonymous substitutions in the class $\Sphyclass$, $D_{\textrm{syn}}$ is the number of synonymous substitutions across the genome, while $L \left( \Sphyclass \right)$ and $L_{\textrm{syn}}$ are the number of non-synonymous and synonymous mutational opportunities as defined in section \ref{subsec:nunber-of-sites}.
     The fraction of non-adaptive beneficial substitutions $R(\dnds)$ was computed as the ratio between the difference in the numbers of beneficial substitutions ($\dnds$), which were due to beneficial back-mutations, and the estimated divergence when we removed beneficial back-mutations $\dn (\Sphy < 0) / \ds$, over $\dnds$.
@@
 
+    \subsection{Selection coefficient ($\Spop$) in population-based method}
+    \label{subsec:s-polymorphism-method}
+    The probability to sample an allele at a given frequency (before fixation or extinction) is informative of its scaled selection coefficient at the population scale ($\Spop$).
+    Pooled across many sites, the site-frequency spectrum (SFS) provides therefore information on the underlying $\Spop$ of mutations.
+    However, estimating a single $\Spop$ for all sampled mutations is biologically unrealistic and a distribution of fitness effects of mutations (DFE) is usually assumed~\cite{eyre-walker_distribution_2006a, eyre-walker_estimating_2009a}.
+    In this study, we used the software polyDFE~\cite{tataru_inference_2017, tataru_polydfe_2020}, which used a mixture of a $\Gamma$ and Exponential distributions to model the DFE of non-synonymous mutations, while synonymous mutations are considered neutral.
+    The model estimates the parameters $\DelMean$ , $b$, $p_b$ and $\AdvMean$ for non-synonymous mutations as:
+    \begin{equation}
+        \phi \left( \Spop; \DelMean , b, p_b, \AdvMean \right) =
+        \begin{dcases}
+            \left( 1 - p_b \right) f_{\Gamma}(-\Spop; -\DelMean, b) & \text{ if $\Spop \leq 0$,} \\
+            p_b f_{e}(\Spop; \AdvMean) & \text{ if $\Spop > 0$,} \\
+        \end{dcases}
+    \end{equation}
+    where $\DelMean \leq -1 $ is the estimated mean of the DFE for $\Spop \leq 0$,
+    $b \geq 0.4$ is the estimated shape of the $\Gamma$ distribution,
+    $0 \leq p_b \leq 1$ is the estimated probability that $\Spop > 0$,
+    $\AdvMean \geq 1$ is the estimated mean of the DFE for $\Spop > 0$,
+    and $f_{\Gamma}(x; m, b)$ is the density of the $\Gamma$ distribution with mean m and shape b, while $f_{e}(x; m)$ is the density of the Exponential distribution with mean $m$.
+    Once the DFE was fitted to the data, the proportion of beneficial ($\PpolyAdv$), nearly-neutral ($\PpolyNeutral$) and deleterious mutations ($\PpolyDel$) were given as:
+    \begin{align}
+        \PpolyAdv &= p_b \int_{1}^{+\infty} f_{e}(\Spop; \AdvMean) \der \Spop,  \label{eq:polyProbaAdv} \\
+        \PpolyNeutral &= p_b \int_{0}^{1} f_{e}(\Spop; \AdvMean) \der \Spop + \left( 1 - p_b \right) \int_{0}^{1} f_{\Gamma}(\Spop; -\DelMean, b) \der \Spop, \\
+        \PpolyDel &= \left( 1 - p_b \right) \int_{1}^{+\infty} f_{\Gamma}(\Spop; -\DelMean, b) \der \Spop. \label{eq:polyProbaDel}
+    \end{align}
+
+    PolyDFE required one SFS for non-synonymous mutations and one for synonymous mutations (neutral expectation), as well as the number of sites on which each SFS has been sampled.
+    For populations containing more than $8$ individuals, the site-frequency spectrum (SFS) was subsampled down to $16$ chromosomes ($8$ diploid individuals) without replacement (hyper-geometric distribution) to alleviate the effect of different sampling depth in the 28 populations.
+    Altogether, for each class of selection ($\Sphyclass$) of non-synonymous SNPs (or for all SNPs), we thus estimated the parameters of the DFE $\left( \Spop; \DelMean , b, p_b, \AdvMean \right)$ using maximum likelihood with polyDFE from the number of sites and the SFS obtained by aggregating all the SNPs in the selection class.
+    Once fitted to the data, the parameters of the DFE $\left( \Spop; \DelMean , b, p_b, \AdvMean \right)$ are used to compute $\PpolyAdv$, $\PpolyNeutral$, $\PpolyDel$ using eq.~\ref{eq:polyProbaAdv}-\ref{eq:polyProbaDel}.
+
+    From Bayes theorem, it is now possible to obtain the probability for a beneficial mutation to be a back-mutation.
+    In other words, we seek to get the probability that a mutation is a back-mutation ($\divAdv$) given that it is beneficial ($\polyAdv$), as:
+    \begin{equation}
+        \proba \left[\divAdv \given \polyAdv\right] = \frac{\proba \left[\polyAdv \given \divAdv\right] \times \proba\left[\divAdv\right]}{\PpolyAdv},
+        \label{eq:bayes}
+    \end{equation}
+    where $\PpolyAdv$ is computed from all SNPS, $\proba \left[\polyAdv \given \divAdv\right]$ is obtained from the set of SNPs in the class $\Sphyclass = \divAdv$, and $\proba\left[\divAdv\right]$ is the probability for a new mutation to be inside the class $\divAdv$, thus computed as:
+    \begin{equation}
+        \proba\left[\divAdv\right] = \frac{L\left( \Sphyclass = \divAdv \right)}{L_{tot}},
+        \label{eq:proba-dfe-mutsel}
+    \end{equation}
+
     \printbibliography
 \end{document}
+%TC:endignore

### 2022-11-29 manuscript/supp-mat.tex
Refactored manuscript

@@
 
+    \subsubsection{$\dnds$ and beneficial back-mutations}
     \begin{center}
-        \captionof{table}{~}
+        \captionof{table}{$\dnds$ of beneficial back-mutations.}
         \scriptsize
@@
     \begin{center}
-        \captionof{table}{~}
+        \captionof{table}{$\dnds$ over-estimation due to beneficial back-mutations.}
         \scriptsize
@@
     \newpage
+
+    \subsubsection{Probabilities of beneficial back-mutations}
     \begin{center}
-        \captionof{table}{~}
+        \captionof{table}{Probability of beneficial back-mutations among all beneficial ones with PolyDFE model C.}
         \scriptsize
@@
     \end{itemize}
+    With polyDFE model C, the DFE of non-synonymous mutations is given as a mixture of a $\Gamma$ (negative side) and Exponential (positive side) distributions, see Materials and Methods.
 
+    \newpage
+    \begin{center}
+        \captionof{table}{Probability of beneficial back-mutations among all beneficial ones (including slightly-beneficial mutations) with PolyDFE model C.}
+        \scriptsize
+        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
+            \toprule
+            Population & Species & Tajima $\theta_{\pi}$ & $\mathbb{P}[\Sphy > 0]$ & $\mathbb{P} [ \Spop > 0 ]$ & $\frac{\mathbb{P}[\Sphy > 0]}{\mathbb{P}[ \Spop > 0 ]}$ & $\mathbb{P} [ \Spop > 0 \given \Sphy > 0]$ & $\mathbb{P}[\Sphy > 0\given \Spop > 0 ]$ \\
+            \midrule
+            \endhead
+            \midrule
+            \multicolumn{8}{r}{{Continued on next page}} \\
+            \midrule
+            \endfoot
+
+            \bottomrule
+            \endlastfoot
+            Equus c.
+&      Equus caballus &               $ 0.002$ &             $ 0.050$ &              $ 0.125$ &                                     $ 0.403$ &                       $ 1.000$ &                 $ 0.403$ \\
+            Iran &          Bos taurus &               $ 0.005$ &             $ 0.050$ &              $ 0.108$ &                                     $ 0.457$ &                       $ 0.640$ &                 $ 0.293$ \\
+            Uganda &          Bos taurus &               $ 0.005$ &             $ 0.050$ &              $ 0.104$ &                                     $ 0.477$ &                       $ 0.708$ &                 $ 0.338$ \\
+            Australia &        Capra hircus &               $ 0.003$ &             $ 0.051$ &              $ 0.107$ &                                     $ 0.471$ &                       $ 0.416$ &                 $ 0.196$ \\
+            France &        Capra hircus &               $ 0.003$ &             $ 0.051$ &              $ 0.102$ &                                     $ 0.495$ &                       $ 0.464$ &                 $ 0.230$ \\
+            Iran (C.
+aegagrus) &        Capra hircus &               $ 0.003$ &             $ 0.051$ &              $ 0.107$ &                                     $ 0.473$ &                       $ 0.327$ &                 $ 0.155$ \\
+            Iran &        Capra hircus &               $ 0.004$ &             $ 0.051$ &              $ 0.089$ &                                     $ 0.569$ &                       $ 0.384$ &                 $ 0.219$ \\
+            Italy &        Capra hircus &               $ 0.003$ &             $ 0.051$ &              $ 0.096$ &                                     $ 0.525$ &                       $ 0.402$ &                 $ 0.211$ \\
+            Morocco &        Capra hircus &               $ 0.004$ &             $ 0.051$ &              $ 0.088$ &                                     $ 0.571$ &                       $ 0.408$ &                 $ 0.233$ \\
+            Iran &          Ovis aries &               $ 0.007$ &             $ 0.051$ &              $ 0.066$ &                                     $ 0.769$ &                       $ 0.159$ &                 $ 0.122$ \\
+            Iran (O.
+orientalis) &          Ovis aries &               $ 0.009$ &             $ 0.051$ &              $ 0.074$ &                                     $ 0.686$ &                       $ 0.259$ &                 $ 0.177$ \\
+            Iran (O.
+vignei) &          Ovis aries &               $ 0.007$ &             $ 0.051$ &              $ 0.084$ &                                     $ 0.605$ &                       $ 0.499$ &                 $ 0.302$ \\
+            Various &          Ovis aries &               $ 0.009$ &             $ 0.051$ &              $ 0.071$ &                                     $ 0.712$ &                       $ 0.253$ &                 $ 0.180$ \\
+            Morocco &          Ovis aries &               $ 0.007$ &             $ 0.051$ &              $ 0.060$ &                                     $ 0.839$ &                       $ 0.155$ &                 $ 0.130$ \\
+            Barbados & Chlorocebus sabaeus &               $ 0.004$ &             $ 0.048$ &              $ 0.121$ &                                     $ 0.392$ &                       $ 0.771$ &                 $ 0.303$ \\
+            Central Afr.
+Rep.
+& Chlorocebus sabaeus &               $ 0.006$ &             $ 0.047$ &              $ 0.105$ &                                     $ 0.454$ &                       $ 0.637$ &                 $ 0.289$ \\
+            Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &             $ 0.047$ &              $ 0.120$ &                                     $ 0.395$ &                       $ 0.708$ &                 $ 0.280$ \\
+            Gambia & Chlorocebus sabaeus &               $ 0.005$ &             $ 0.047$ &              $ 0.090$ &                                     $ 0.528$ &                       $ 0.725$ &                 $ 0.383$ \\
+            Kenya & Chlorocebus sabaeus &               $ 0.005$ &             $ 0.047$ &              $ 0.106$ &                                     $ 0.447$ &                       $ 0.627$ &                 $ 0.280$ \\
+            Nevis & Chlorocebus sabaeus &               $ 0.003$ &             $ 0.048$ &              $ 0.111$ &                                     $ 0.429$ &                       $ 0.676$ &                 $ 0.290$ \\
+            South Africa & Chlorocebus sabaeus &               $ 0.006$ &             $ 0.047$ &              $ 0.104$ &                                     $ 0.456$ &                       $ 0.659$ &                 $ 0.301$ \\
+            Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &             $ 0.047$ &              $ 0.117$ &                                     $ 0.405$ &                       $ 0.723$ &                 $ 0.293$ \\
+            Zambia & Chlorocebus sabaeus &               $ 0.006$ &             $ 0.047$ &              $ 0.116$ &                                     $ 0.409$ &                       $ 0.671$ &                 $ 0.275$ \\
+            African &        Homo sapiens &               $ 0.003$ &             $ 0.048$ &              $ 0.114$ &                                     $ 0.424$ &                       $ 1.000$ &                 $ 0.424$ \\
+            Admixed American &        Homo sapiens &               $ 0.002$ &             $ 0.048$ &              $ 0.110$ &                                     $ 0.437$ &                       $ 1.000$ &                 $ 0.437$ \\
+            East Asian &        Homo sapiens &               $ 0.002$ &             $ 0.048$ &              $ 0.106$ &                                     $ 0.453$ &                       $ 1.000$ &                 $ 0.453$ \\
+            European &        Homo sapiens &               $ 0.002$ &             $ 0.048$ &              $ 0.107$ &                                     $ 0.452$ &                       $ 1.000$ &                 $ 0.452$ \\
+            South Asian &        Homo sapiens &               $ 0.002$ &             $ 0.048$ &              $ 0.106$ &                                     $ 0.454$ &                       $ 1.000$ &                 $ 0.454$ \\
+        \end{longtable*}
+    \end{center}
+    \begin{itemize}
+        \item Tajima $\theta$ is the synonymous diversity.
+        \item $\mathbb{P} [ \Sphy > 0 ]$ is the probability for a new mutation a beneficial back-mutation.
+        These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 0 ($\Sphy > 0$), thus toward a more fit amino-acid.
+        In other words, this probability is the part of the DFE estimated by mutation-selection models greater than 0.
+        \item $\mathbb{P} [ \Spop > 0 ]$ is the probability for a mutation to be beneficial.
+        These mutations have a selection coefficient at the population-scale larger than 0 ($\Spop > 0$), estimated from all SNPs in the population.
+        In other words, this probability is the part of the DFE estimated by polyDFE greater than 0.
+        \item $\mathbb{P} [ \Spop > 0 \given \Sphy > 0]$ is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale.
+        These mutations have a selection coefficient at the population scale larger than 0 ($\Spop > 0$), estimated by polyDFE on the SNPs with a predicted selection coefficient at the phylogenetic scale larger than 0 ($\Sphy > 0$).
+        In other words, this probability is the part of the DFE estimated by polyDFE greater than 0, when we restricted our analysis on SNPs that are already predicted by mutation-selection models to have a selection coefficient ($\Sphy$) greater than 0.
+        \item $\mathbb{P} [ \Sphy > 0 \given \Spop > 0]$ is the probability for a mutation to a beneficial back-mutations, given it is beneficial.
+        This probability is obtained using Bayes' formula.
+    \end{itemize}
+    With polyDFE model C, the DFE of non-synonymous mutations is given as a mixture of a $\Gamma$ (negative side) and Exponential (positive side) distributions, see Materials and Methods.
+
+    \newpage
+    \begin{center}
+        \captionof{table}{Probability of beneficial back-mutations among all beneficial ones (including slightly-beneficial mutations) with PolyDFE model D.}
+        \scriptsize
+        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
+            \toprule
+            Population & Species & Tajima $\theta_{\pi}$ & $\mathbb{P}[\Sphy \geq 0]$ & $\mathbb{P} [ \Spop \geq 0 ]$ & $\frac{\mathbb{P}[\Sphy \geq 0]}{\mathbb{P}[ \Spop \geq 0 ]}$ & $\mathbb{P} [ \Spop \geq 0 \given \Sphy \geq 0]$ & $\mathbb{P}[\Sphy \geq 0\given \Spop \geq 0 ]$ \\
+            \midrule
+            \endhead
+            \midrule
+            \multicolumn{8}{r}{{Continued on next page}} \\
+            \midrule
+            \endfoot
+
+            \bottomrule
+            \endlastfoot
+            Equus c.
+&      Equus caballus &               $ 0.002$ &             $ 0.050$ &              $ 0.219$ &                                     $ 0.230$ &                       $ 0.461$ &                 $ 0.106$ \\
+            Iran &          Bos taurus &               $ 0.005$ &             $ 0.050$ &              $ 0.181$ &                                     $ 0.274$ &                       $ 0.407$ &                 $ 0.112$ \\
+            Uganda &          Bos taurus &               $ 0.005$ &             $ 0.050$ &              $ 0.175$ &                                     $ 0.283$ &                       $ 0.470$ &                 $ 0.133$ \\
+            Australia &        Capra hircus &               $ 0.003$ &             $ 0.051$ &              $ 0.182$ &                                     $ 0.277$ &                       $ 0.472$ &                 $ 0.131$ \\
+            France &        Capra hircus &               $ 0.003$ &             $ 0.051$ &              $ 0.177$ &                                     $ 0.286$ &                       $ 0.492$ &                 $ 0.141$ \\
+            Iran (C.
+aegagrus) &        Capra hircus &               $ 0.003$ &             $ 0.051$ &              $ 0.171$ &                                     $ 0.295$ &                       $ 0.463$ &                 $ 0.137$ \\
+            Iran &        Capra hircus &               $ 0.004$ &             $ 0.051$ &              $ 0.161$ &                                     $ 0.313$ &                       $ 0.450$ &                 $ 0.141$ \\
+            Italy &        Capra hircus &               $ 0.003$ &             $ 0.051$ &              $ 0.174$ &                                     $ 0.291$ &                       $ 0.509$ &                 $ 0.148$ \\
+            Morocco &        Capra hircus &               $ 0.004$ &             $ 0.051$ &              $ 0.170$ &                                     $ 0.298$ &                       $ 0.442$ &                 $ 0.132$ \\
+            Iran &          Ovis aries &               $ 0.007$ &             $ 0.051$ &              $ 0.141$ &                                     $ 0.359$ &                       $ 0.506$ &                 $ 0.182$ \\
+            Iran (O.
+orientalis) &          Ovis aries &               $ 0.009$ &             $ 0.051$ &              $ 0.139$ &                                     $ 0.365$ &                       $ 0.484$ &                 $ 0.177$ \\
+            Iran (O.
+vignei) &          Ovis aries &               $ 0.007$ &             $ 0.051$ &              $ 0.134$ &                                     $ 0.379$ &                       $ 0.517$ &                 $ 0.196$ \\
+            Various &          Ovis aries &               $ 0.009$ &             $ 0.051$ &              $ 0.136$ &                                     $ 0.372$ &                       $ 0.513$ &                 $ 0.191$ \\
+            Morocco &          Ovis aries &               $ 0.007$ &             $ 0.051$ &              $ 0.139$ &                                     $ 0.364$ &                       $ 0.477$ &                 $ 0.174$ \\
+            Barbados & Chlorocebus sabaeus &               $ 0.004$ &             $ 0.048$ &              $ 0.205$ &                                     $ 0.232$ &                       $ 0.543$ &                 $ 0.126$ \\
+            Central Afr.
+Rep.
+& Chlorocebus sabaeus &               $ 0.006$ &             $ 0.047$ &              $ 0.179$ &                                     $ 0.265$ &                       $ 0.345$ &                 $ 0.091$ \\
+            Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &             $ 0.047$ &              $ 0.203$ &                                     $ 0.234$ &                       $ 0.464$ &                 $ 0.108$ \\
+            Gambia & Chlorocebus sabaeus &               $ 0.005$ &             $ 0.047$ &              $ 0.183$ &                                     $ 0.260$ &                       $ 0.442$ &                 $ 0.115$ \\
+            Kenya & Chlorocebus sabaeus &               $ 0.005$ &             $ 0.047$ &              $ 0.179$ &                                     $ 0.265$ &                       $ 0.478$ &                 $ 0.127$ \\
+            Nevis & Chlorocebus sabaeus &               $ 0.003$ &             $ 0.048$ &              $ 0.203$ &                                     $ 0.234$ &                       $ 0.552$ &                 $ 0.129$ \\
+            South Africa & Chlorocebus sabaeus &               $ 0.006$ &             $ 0.047$ &              $ 0.184$ &                                     $ 0.258$ &                       $ 0.477$ &                 $ 0.123$ \\
+            Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &             $ 0.047$ &              $ 0.204$ &                                     $ 0.233$ &                       $ 0.527$ &                 $ 0.123$ \\
+            Zambia & Chlorocebus sabaeus &               $ 0.006$ &             $ 0.047$ &              $ 0.187$ &                                     $ 0.253$ &                       $ 0.477$ &                 $ 0.121$ \\
+            African &        Homo sapiens &               $ 0.003$ &             $ 0.048$ &              $ 0.239$ &                                     $ 0.202$ &                       $ 0.158$ &                 $ 0.032$ \\
+            Admixed American &        Homo sapiens &               $ 0.002$ &             $ 0.048$ &              $ 0.252$ &                                     $ 0.192$ &                       $ 0.452$ &                 $ 0.087$ \\
+            East Asian &        Homo sapiens &               $ 0.002$ &             $ 0.048$ &              $ 0.260$ &                                     $ 0.185$ &                       $ 0.440$ &                 $ 0.082$ \\
+            European &        Homo sapiens &               $ 0.002$ &             $ 0.048$ &              $ 0.255$ &                                     $ 0.189$ &                       $ 0.453$ &                 $ 0.086$ \\
+            South Asian &        Homo sapiens &               $ 0.002$ &             $ 0.048$ &              $ 0.248$ &                                     $ 0.194$ &                       $ 0.439$ &                 $ 0.085$ \\
+        \end{longtable*}
+    \end{center}
+    \begin{itemize}
+        \item Tajima $\theta$ is the synonymous diversity.
+        \item $\mathbb{P} [ \Sphy \geq 0 ]$ is the probability for a new mutation a beneficial back-mutation.
+        These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 0 ($\Sphy \geq 0$), thus toward a more fit amino-acid.
+        In other words, this probability is the part of the DFE estimated by mutation-selection models greater than 0.
+        \item $\mathbb{P} [ \Spop \geq 0 ]$ is the probability for a mutation to be beneficial.
+        These mutations have a selection coefficient at the population-scale larger than 0 ($\Spop \geq 0$), estimated from all SNPs in the population.
+        In other words, this probability is the part of the DFE estimated by polyDFE greater than 0.
+        \item $\mathbb{P} [ \Spop \geq 0 \given \Sphy \geq 0]$ is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale.
+        These mutations have a selection coefficient at the population scale larger than 0 ($\Spop \geq 0$), estimated by polyDFE on the SNPs with a predicted selection coefficient at the phylogenetic scale larger than 0 ($\Sphy \geq 0$).
+        In other words, this probability is the part of the DFE estimated by polyDFE greater than 0, when we restricted our analysis on SNPs that are already predicted by mutation-selection models to have a selection coefficient ($\Sphy$) greater than 0.
+        \item $\mathbb{P} [ \Sphy \geq 0 \given \Spop \geq 0]$ is the probability for a mutation to a beneficial back-mutations, given it is beneficial.
+        This probability is obtained using Bayes' formula.
+    \end{itemize}
+    With polyDFE model D, the DFE of non-synonymous mutations is given as a discrete DFE of $K$ categories, where the selection coefficients of each category $i$ ($1 \leq i \leq K$) are fixed parameters $\Spop_i$, and each value $\Spop_i$ has a probability $p_i$ (estimated), with $\sum_{i=1}^{K} p_i =1$.
+    We used $K=5$ with $\Spop_1 = -400$, $\Spop_2 = -10$, $\Spop_3 = 0$, $\Spop_4 = 1$, $\Spop_5 = 4$.\\
+
+    Altogether, comparing tables S3-S5, we acknowledge that estimating the proportion of beneficial back-mutations among all beneficial ones is dependent on the assumption for the underlying distribution of fitness effects at the population scale and the threshold used to define a beneficial mutation.
     \newpage
@@
 
-    \section{Mutation-selection models: histograms and SFS for each population}\label{sec:mutation-selection-models:-histograms-and-sfs-for-each-population}
+    \section{Distribution of fitness effects}
+
+    \captionof{figure}{~}
+    \begin{minipage}{0.49\linewidth}
+        \includegraphics[width=\linewidth, page=1]{artworks/2bins.Yeast.experimentalDFE.pdf}
+    \end{minipage}
+    \begin{minipage}{0.49\linewidth}
+        \includegraphics[width=\linewidth, page=1]{artworks/2bins.AFR.histogramDFE.pdf}
+    \end{minipage}
+    \begin{itemize}
+        \item Left panel: Distribution of fitness effects experimentally determined in Yeast, data obtained in \textcite{shen_synonymous_2022}.
+        \item Middle panel: Distribution of fitness effects ($\Sphy$) as predicted with mutation-selection codon models, from reconstructed ancestral genome in \textit{Homo sapiens}).
+    \end{itemize}
+    The DFE predicted with mutation-selection codon models has a negative mode, consistently with experimental DFEs, meaning that most mutations are effectively deleterious.
+
+    \newpage
+
+    \section{Mutation-selection models: DFE and SFS for each population}\label{sec:mutation-selection-models:-histograms-and-sfs-for-each-population}
     For each population, the same figure is shown.
     \begin{itemize}
-        \item Top-left panel: Histogram of predicted selection coefficients ($\Sphy$) for all possible mutations away from the ancestral genome, giving the number of sites ($L$, in y-axis) across the genome with a given $\Sphy$.
-        Mutations are divided into 5 classes: severely deleterious (blue), deleterious (green), weakly deleterious (light green), weakly beneficial (yellow) and beneficial (red).
+        \item Top-left panel: Distribution of fitness effects ($\Sphy$), predicted for all possible mutations away from the ancestral human genome.
+        Mutations are divided into 5 classes of selection: severely deleterious (blue), deleterious (green), weakly deleterious (light green), weakly beneficial (yellow) and beneficial (red, supposedly beneficial back-mutations).
         \item Top-right panel: Histogram of predicted selection coefficients ($\Sphy$) for all observed mutations in a sample of 8 individuals (out of 512 in the original dataset) of African descent.

### 2023-01-16 manuscript/main.tex
Updated manuscript, changed colors.

@@
 
-\title{Up to 25\% of beneficial mutations in protein sequences are not adaptive innovations in mammals}
+\title{Up to 25\% of beneficial mutations in human protein sequences are not adaptive innovations in mammals}
 
@@
     \large
-    \textbf{T. {Latrille}$^{1}$, J. {Joseph}$^{2}$, N. {Salamin}$^{1}$}\\
+    \textbf{T. {Latrille}$^{1}$, J. {Joseph}$^{2}$, D.~A. {Hartasánchez}$^{1}$, N. {Salamin}$^{1}$}\\
     \normalsize
@@
 
-    \keywords{Adaptation \and Back-mutation \and Phylogenetic \and Population-genetics \and Codon models }
+    \keywords{Adaptation \and Back-mutation \and Phylogenetics \and Population-genetics \and Codon models }
 
-    Adaptation is considered as the main process shaping the diversity of forms and functions across the tree of life~\cite{darwin_origin_1859}.
-    It enables species to access new ecological niches and also respond to changes in their environment~\cite{darwin_origin_1859}.
-    The notion of adaptation, in its evolutionary sense, is tightly linked to the notion of change, both of the environment, and of the species responding to the latter~\cite{merrell_adaptive_1994}.
-    In genomes, adaptation leaves marks of accelerated evolution since beneficial mutations fix faster than neutral ones (fig.~\ref{fig:fitness-landscape}A).
-    The signature of an accelerated rate of substitutions can thus be interpreted as a sign of adaptation~\cite{mcdonald_adaptative_1991, smith_adaptive_2002a, welch_estimating_2006}.
-    The current availability of large scale genomic data and the development of theoretical models allowed to detect and quantify adaption across genes and lineages, which is now a common practice in evolutionary biology~\cite{yang_statistical_2000, eyre-walker_genomic_2006, moutinho_variation_2019}.
-    Although these approaches led to a better understanding of the processes shaping the rates of molecular evolution, it had the effect to associate beneficial mutations with adaptive evolution, with a loss of the notion of change.
-    However, we argue that they should be dissociated since adaptive evolution is not the only process which can lead to beneficial mutations~\cite{charlesworth_other_2007, mustonen_fitness_2009}.
-    Indeed, even in a constant environment for which the population is already adapted, a deleterious mutation in an individual can reach fixation in the population by genetic drift~\cite{Ohta1992}.
-    Subsequently, a mutation restoring the ancestral fitness will thus be beneficial (fig.~\ref{fig:fitness-landscape}B), even though no change in the environment occurred~\cite{hartl_compensatory_1996, sella_application_2005, mustonen_fitness_2009, cvijovic_fate_2015}.
-    More precisely, this restoration of the ancestral fitness can happen at another loci, in which case it is referred as compensating mutations~\cite{hartl_compensatory_1996, mustonen_fitness_2009}.
-    Conversely, the restoration of the ancestral fitness can happen at the same locus, in which case it is referred as a beneficial back-mutation~\cite{piganeau_estimating_2003, charlesworth_other_2007}, which are the focus of this study.
-    If compensatory mutations still induce changes in the genetic sequence and thus genetic diversification, beneficial-back mutations reduce the diversity and do not contribute to genetic innovation, they cancel the deleterious changes.
-    Taken together, not all beneficial mutations contribute to genetic innovation, and truly adaptive evolution can only be well estimated under the background of beneficial back-mutations~\cite{keightley_what_2010, rice_evolutionarily_2015}.
+    Adaptation is considered one of the main processes shaping the diversity of forms and functions across the tree of life~\cite{darwin_origin_1859}.
+    It enables species to access new ecological niches and also respond to changes in their environment~\cite{darwin_origin_1859} [NS: maybe cite Losos or some key papers on ecological speciation rather than Darwin twice].
+    In evolution, adaptation is tightly linked to the notion of change at the level of the environment and to species responding to this change~\cite{merrell_adaptive_1994}.
+    The process of adaptation leaves marks of accelerated evolution in genomes since mutations that are beneficial under new conditions fix faster than neutral mutations (fig.~\ref{fig:fitness-landscape}A).
+    The signature of an accelerated rate of substitutions, defined as the rate of mutation times the probability of fixation, can thus be interpreted as a sign of adaptation~\cite{mcdonald_adaptative_1991, smith_adaptive_2002, welch_estimating_2006}.
+    The current availability of large-scale genomic data and the development of theoretical models have allowed to detect and quantify adaptation across genes and lineages, and these analyses have become common practice in evolutionary biology~\cite{yang_statistical_2000, eyre-walker_genomic_2006, moutinho_variation_2019} [NS: cite the paper by Anna Marcionetti here].
+    Although these approaches have led to a better understanding of the processes determining the rates of molecular evolution, they have had the effect of associating beneficial mutations with adaptive evolution, while disconnecting them from the notion of change defining adaptation.
+    We argue that we should limit the use of adaptive mutations to those that are associated with adaptation as such and dissociate beneficial mutations from adaptive mutations since adaptive evolution is not the only process that can lead to beneficial mutations~\cite{charlesworth_other_2007, mustonen_fitness_2009}.
+    We propose here a new approach to identify the mechanisms underlying the origin of beneficial mutations.
+    In particular, we suggest that many beneficial mutations are not adaptive, but are rather restoring ancestral states of higher fitness.
+    We used large-scale genomic data to integrate analyses at both the phylogenetic and population scales to differentiate between truly adaptive mutations from mutations restoring the ancestral fitness.
+    Our results show that up to a quarter of beneficial mutations across mammal species are not driven by adaptive innovations, but rather compensate the effect of ancestral mutations to recover the optimal state of the species.
+
+    In a constant environment, if a population is already adapted to these conditions, a deleterious mutation in an individual can reach fixation in the population by genetic drift~\cite{Ohta1992}.
+    Subsequently, a new mutation that is restoring the ancestral fitness will thus be beneficial (fig.~\ref{fig:fitness-landscape}B), even though no change in the environment occurred~\cite{hartl_compensatory_1996, sella_application_2005, mustonen_fitness_2009, cvijovic_fate_2015}.
+    The restoration of the ancestral fitness can happen at a different locus than the initial mutation, in which case it is referred to as a compensating [NS: ou compensatory ?] mutation~\cite{hartl_compensatory_1996, mustonen_fitness_2009}.
+    However, if the restoration of the ancestral fitness happens at the same locus than the initial mutation, in which case it is referred to as a beneficial back-mutation~\cite{piganeau_estimating_2003, charlesworth_other_2007}.
+    In this study, we focus on the latter case.
+    While compensatory mutations induce genetic changes at the sequence level, and thus genetic diversification, beneficial back-mutations reduce the genetic diversity and do not contribute to genetic innovation.
+    They merely cancel the effect of the previous deleterious changes.
+    As a consequence, not all beneficial mutations contribute to genetic innovation and truly adaptive evolution can only be correctly estimated if we can account for the number of beneficial back-mutations~\cite{keightley_what_2010, rice_evolutionarily_2015}.
     % Philosophically, our distinction between beneficial back-mutations and adaptation can appear to be far-fetched, and one can argue that beneficial back-mutations is adaptation to its own deteriorating genome.
-    % However, there is a difference between adapting to a mutation, for instance by the mean of a compensatory mutation elsewhere, and cancelling the mutation, by the mean of a substitution on the misfit amino-acid.
+    % However, there is a difference between adapting to a mutation, for instance by means of a compensatory mutation elsewhere, and cancelling the mutation, by means of a substitution on the misfit amino-acid.
 
-    For an individual carrying a beneficial mutation, whether this mutation is a new innovation responding to a change in environment or a beneficial back-mutation is indistinguishable~\cite{charlesworth_other_2007}.
-    Likewise, at the level of the population, both will result in a positive transmission bias of the beneficial allele.
-    However, their consequences at the macro-evolutionary scale are fundamentally different.
-    While adaptive evolution promotes phenotype diversification (fig.~\ref{fig:fitness-landscape}C), beneficial back-mutations promote phenotype stability and preserves well established biological systems (fig.~\ref{fig:fitness-landscape}D).
-    Fundamentally, the direction of adaptive evolution is unpredictable because it is caused by an unpredictable change in the environment and the underlying fitness landscape~\cite{bazykin_changing_2015}.
-    On the other hand, beneficial back-mutations are predictable if the underlying stable fitness landscape is known.
-    As a result, a way to quantify the amount of back-mutation is to estimate the underlying fitness landscape, assuming it is constant and stable across time.
+    %For an individual carrying a beneficial mutation, whether this mutation is a new innovation responding to a change in environment or a beneficial back-mutation is indistinguishable~\cite{charlesworth_other_2007}.
+    Given a beneficial mutation, distinguishing whether it is a new innovation responding to a change in environment or a beneficial back-mutation is impossible with only one individual at hand~\cite{charlesworth_other_2007}.
+    This limitation persists at the level of the population, since both types of mutation will result in a positive transmission bias of the beneficial allele.
+    However, at the macro-evolutionary scale the consequences of these two types of mutations are fundamentally different.
+    While adaptive evolution promotes phenotype diversification (fig.~\ref{fig:fitness-landscape}C), beneficial back-mutations promote phenotype stability and preserve well established biological systems (fig.~\ref{fig:fitness-landscape}D).
+    Additionally, the direction of adaptive evolution is unpredictable because it is caused by an unpredictable change in the environment and, hence, in the underlying fitness landscape~\cite{bazykin_changing_2015}.
+    On the other hand, beneficial back-mutations are predictable if the underlying stable fitness landscape is known because we will expect to see changes from non-optimal amino acids to optimal ones.
+    If we wish to quantify the amount of beneficial back-mutations that have happened along a phylogeny we need to identify the selection coefficients of mutations and to achieve this we require the fitness landscape to be stable and be known.
 
-    In this study, fitness landscapes of protein-coding genes are estimated from multi-species sequence alignments.
-    Multi-species sequence alignments can be used to estimate amino acid fitness, since for example a deleterious amino acid will be more likely to be absent in the alignment.
-    One of the most used methods to make these predictions is SIFT (Sort Intolerant From Tolerant), which reliably detects deleterious mutations in many taxa~\cite{ng_sift_2003, vaser_sift_2016}.
-    However, SIFT scores is not interpretable as a selection coefficient.
-    Moreover, SIFT scores do not acknowledge some key processes that can influence the abundance of an amino-acid in an alignment.
-For instance, it does not take into account phylogenetic inertia, mutation biases, GC-biased gene conversion, or mutational paths.
-    Contrarily, so-called mutation-selection codon models are rooted within a population-genetic formalism~\cite{halpern_evolutionary_1998, mccandlish_modeling_2014}.
-    These phylogenetic codon models can disentangle processes of mutation at the DNA level and selection at the amino acid level.
-    Such codon models provide a nearly-neutral framework of evolution by estimating the fitness landscape over amino acid sequences for each site of the sequence while taking into account non-adaptive processes impacting codon frequency~\cite{halpern_evolutionary_1998, rodrigue_mechanistic_2010, tamuri_estimating_2012, latrille_improved_2022a}.
-    Importantly, mutation-selection codon models assume that the underlying fitness landscape is stable along the phylogeny, hence is a null model of evolution without adaptation.
-    From the fitness landscape obtained by fitting the model to the multi-species sequence alignments (fig~\ref{fig:method}A), one can compute the scaled selection coefficient under this null model of evolution, denoted $\Sphy$, of any non-synonymous mutations.
-    In this context, a mutation with a positive $\Sphy$ would be driving the current site toward a fitter amino-acid, and thus considered a beneficial back-mutation (fig~\ref{fig:method}B).
-    At the genome-wide level, our expectation is that slightly deleterious mutations that are reaching fixations due to drift are scattered across the genome, such that beneficial back-mutations concurrently segregating are also expected to be spread across genes, generating a balance at which genomes are constantly both damaged and repaired simultaneously at different loci.
-    Even though each of these back-mutations is expected to have individually a small beneficial effect on their bearer, we expect that the genome-wide signature of beneficial back-mutations can be detected and quantified.
+    The placental mammals represent an excellent study system to perform this analysis.
+    Having originated ~100 Mya\cite{kumar_timetree_2017}, they diversified quickly.
+    Additionally, we have polymorphism data available for many species\cite{howe_ensembl_2021} and high quality protein-coding DNA alignments across the genome\cite{ranwez_orthomam_2007, scornavacca_orthomam_2019}.
+    By restricting our analysis to protein-coding orthologous genes to all the phylogeny, and further excluding any genes for which there have been claims of pervasive directional selection, we can not only assume a constant fitness landscape for each of them throughout placental mammal evolution, but actually reconstruct the fitness landscape from variable positions within the sequence along the phylogeny.
+    For each gene, we used a codon model of mutation-selection~\cite{halpern_evolutionary_1998, mccandlish_modeling_2014} to obtain relative fitnesses for all amino-acids for each site of the sequence by fitting the model to the multi-species sequence alignment (fig~\ref{fig:method}A) and assuming that the underlying fitness landscape is stable along the phylogenetic tree.
+    %Mutation-selection codon models provide a nearly neutral framework of evolution taking into account non-adaptive processes impacting codon frequency~\cite{halpern_evolutionary_1998, rodrigue_mechanistic_2010, tamuri_estimating_2012, latrille_improved_2022}.
+    From the fitness landscape, we can calculate the scaled selection coefficient $\Sphy$ for any possible amino-acid change at each position.
+    Under this model, a mutation with a positive $\Sphy$ would be driving the current site toward a known fitter amino-acid and would thus be considered as a beneficial back-mutation (fig~\ref{fig:method}B), given the assumed stability of the fitness landscape.
 
-    In this study, by integrating datasets at different scales (phylogeny and population), we seek to predict whether substitutions in terminal lineages or any mutation currently segregating in a population are beneficial back-mutations, i.e with a positive $\Sphy$.
-    Such a dataset can allow us to address different questions regarding the selection affecting protein-coding DNA sequences.
-    Can we observe beneficial back-mutations that reached fixation recently, and one that are currently segregating in populations?
-    Are they effectively beneficial for the individual carrying it?
-    Conversely, what is the probability for a beneficial mutation to be a back-mutation?
-    In other words, can we find empirical evidence and can we quantify the amount of beneficial mutations that are restoring damaged genomes instead of creating adaptive innovations.
-    To answer these questions, we estimated the fitness landscape of amino-acids for long-term evolution using available multiple sequence alignments between mammalian species~\cite{ranwez_orthomam_2007, howe_ensembl_2021}.
-    We then integrated data at the phylogenetic and population scale to estimate the amount of beneficial mutations across the entire exome (fig.~\ref{fig:method}A-F), for 28 populations from 6 genera (\textit{Equus},  \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus} and \textit{Homo}).
+    Having identified which potential amino-acid changes could represent beneficial back-mutations at the phylogenetic scale, we retrieved polymorphism data from 28 populations belonging to 6 genera (\textit{Equus}, \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus} and \textit{Homo}) to assess the presence of beneficial back-mutations at the population scale.
+    We focused on currently segregating mutations within populations and also on substitutions in the terminal lineages, and checked if any of these observed changes where predicted beneficial back-mutations.
+    Essentially, by integrating large scale genomic datasets at both phylogenetic and population scales we have been able to estimate the amount of beneficial back-mutations across the entire exome for 6 different mammalian genera (fig~\ref{fig:method}A-F).
+
+    Our analyses allow us to test long-standing questions in molecular evolution:
+    How common are beneficial back-mutations?
+    Can we identify beneficial back-mutations that have reached fixation recently, and ones that are currently segregating in populations?
+    Are hypothetical beneficial back-mutations effectively beneficial for the individuals carrying them?
+    Furthermore, what is the probability for any beneficial mutation observed in current populations to be a back-mutation?
+    In other words, can we quantify the amount of beneficial mutations that are restoring damaged genomes instead of creating adaptive innovations.
+    By addressing these questions we provide
+    novel insight on how selection is affecting protein-coding DNA sequences.
 
@@
         \caption{
-            Panel A and B: at a given site inside a protein-coding DNA sequence, the different amino acids (x-axis) have different fitnesses (y-axis).
+            Panel A and B: at a given site of a protein-coding DNA sequence, the different amino acids (x-axis) have different fitnesses (y-axis).
             Under a fluctuating fitness landscape (panel A), these fitnesses are changing with time.
@@
             A mutation with a $\Sphy > 1$ would be driving the current site toward are fitter amino-acid, and such mutation are considered a beneficial back-mutation repairing existing functions (panel B).
-            At the population scale (panel C), each single nucleotide polymorphism (SNP) segregating in the population can be classified as a beneficial back-mutation (in red) or not.
-            The number of derived allele allow to estimate the probability of beneficial mutations at the population scale, for all SNPs or among back-mutations (panel D).
+            At the population scale (panel C), each single nucleotide polymorphism (SNP) segregating in the population can be classified as a beneficial back-mutation (in blue) or not.
+            The number of derived alleles allows us to estimate the probability of beneficial mutations at the population scale, for all SNPs or among back-mutations (panel D).
             The probability of back-mutation is obtained as their fraction among all possible mutations from the ancestral genome sequence (panel E).
@@
     \subsection*{Back-mutations in the terminal lineages}
-    We first investigated whether we could find empirical evidence of beneficial back-mutation in the terminal branches of mammals.
-    We thus reconstructed the substitutions occurring along the terminal branches of the phylogenetic tree.
-    For each substitution, we estimated its scaled selection coefficient ($\Sphy$) based on the stable fitness landscape of amino-acids estimated at the scale of the mammals' phylogeny (fig.~\ref{fig:method}A).
-    We showed that among all the substitutions in the terminal branches, between 10 and 13\% had $\Sphy > 1$ (table~S1) and between 25 and 30\% had $\Sphy > 0$ (table~S2).
-    For substitutions with $\Sphy > 1$, the ratio of non-synonymous over synonymous divergence, called $\dnds$, was estimated to be between 1.15 and 1.68 in the different lineages (table~S1).
-    This meant that beneficial back-mutations with $\Sphy > 1$ reach fixation more frequently than synonymous mutations, which are supposed to be neutral, thus are effectively beneficial.
-    This also means that the ratio $\dnds$ usually used to detect adaptation while relying on substitutions between close species~\cite{mcdonald_adaptative_1991, galtier_adaptive_2016} or at the phylogenetic scale~\cite{goldman_codonbased_1994, yang_codonsubstitution_2002} is overinflated due to beneficial back-mutations.
-    To alleviate this bias, $\dnds$ is computed exclusively on non-synonymous sites with a $\Sphy < 0$, representing the rate of evolution discarding beneficial back-mutations by construction.
-    By dividing $\dnds$ estimated on all substitutions by the one estimated only on substitutions predicted to be deleterious, we directly get the proportion of the rate of evolution which is contributed by beneficial back-mutations (see Material \& Methods).
-    This way, we estimated that between 22\% and 27\% of $\dnds$ is inflated because of beneficial back-mutations while they only represent between 1\% and 2\% of mutational opportunities (table~S2).
+    We first estimated the number of beneficial back-mutation in the terminal branches of mammals by reconstructing the substitutions occurring along the terminal branches of the phylogenetic tree.
+    For each substitution, we estimated its scaled selection coefficient ($\Sphy$) based on the stable fitness landscape of amino-acids estimated at the scale of the phylogenetic tree of mammals (fig.~\ref{fig:method}A).
+    Among all the substitutions that were found in the terminal branches, between 10 and 13\% had $\Sphy > 1$ (table~S1), while between 25 and 30\% had $\Sphy > 0$ (table~S2).
+    For substitutions with $\Sphy > 1$, the $\dnds$ ratio of non-synonymous over synonymous divergence was estimated to be between 1.15 and 1.68 in the different lineages (table~S1).
+    Beneficial back-mutations with $\Sphy > 1$ therefore reached fixation more frequently than synonymous mutations that are supposed to be neutral, which means that these back-mutations are effectively beneficial.
+    This result further indicated that $\dnds$ used to detect adaptation while relying on substitutions between closely related species~\cite{mcdonald_adaptative_1991, galtier_adaptive_2016} or at the phylogenetic scale~\cite{goldman_codonbased_1994, yang_codonsubstitution_2002} is biased due to the presence of beneficial back-mutations that are not adaptive.
+    We can alleviate this bias by computing $\dnds$ exclusively on non-synonymous sites with a $\Sphy < 0$, which represents the rate of evolution when beneficial back-mutations are discarded.
+    By comparing these two ways of estimating $\dnds$ (see Material \& Methods), we estimated that between 22\% and 27\% of $\dnds$ is inflated because of beneficial back-mutations while they only represent between 1\% and 2\% of mutational opportunities (table~S2).
 
     \subsection*{Back-mutations in the populations}
-    Given that beneficial back-mutations are effectively selected for, we then ask which proportion of new mutations are beneficial back-mutations and are also beneficial at the population scale (fig.~\ref{fig:method}C-E).
-    For each population with available polymorphism data, we first reconstructed the ancestral genome (instead of the reference genome) at the base of the population genealogy.
-    From this reference sequence, we computed the scaled selection coefficient ($\Sphy$) for each possible non-synonymous mutations, weighted by their mutational opportunity (see Material \& Methods).
-    We thus obtained the distribution of fitness effects (DFE) of new mutations from the ancestral sequence in \textit{Homo sapiens} (fig.~\ref{fig:homo-afr-results}A), under the assumption of the stable fitness landscape.
-    Because $\Sphy$ is based on estimation of fitnesses at the mammalian scale, mutations with $\Sphy>1$ are considered beneficial back-mutations.
-    Beneficial back-mutations only represents \~1.5\% of all possible new mutations (red in fig.~\ref{fig:homo-afr-results}A, table~S3).
-    However, when focusing on the mutations that are observed in populations, namely single nucleotide polymorphism (SNP), beneficial back-mutations represents \~8.5\% of all observed mutations (red in fig.~\ref{fig:homo-afr-results}B, table~S3).
+    We then estimated the proportion of new mutations that were beneficial back-mutations while being under selection at the population scale (fig.~\ref{fig:method}C-E).
+    We first reconstructed the ancestral genome (instead of the reference genome) of each mammal species with available polymorphism data.
+    We computed the scaled selection coefficient ($\Sphy$) along this ancestral genome for each possible non-synonymous mutations, weighted by their mutational opportunity (see Material \& Methods).
+    It allowed us to obtain the distribution of fitness effects (DFE) of new mutations from the ancestral sequence under the assumption of the stable fitness landscape as shown for \textit{Homo sapiens} in Fig.~\ref{fig:homo-afr-results}A.
+    Because $\Sphy$ was based on estimation of fitnesses at the mammalian scale, mutations with $\Sphy>1$ were considered, as shown above, beneficial back-mutations and only represented ca.~1.5\% of all possible new mutations (blue in fig.~\ref{fig:homo-afr-results}A, table~S3).
+    However, when focusing on the mutations that are observed in populations, namely single nucleotide polymorphism (SNP), beneficial back-mutations represents ca.~8.5\% of all observed mutations (blue in fig.~\ref{fig:homo-afr-results}B, table~S3).
 
-    Additionally, in populations, the frequencies at which SNPs are segregating is informative of their selective effect, e.g.
-deleterious SNPs are segregating at lower frequencies because they are purified.
-    As such, methods have been developed to estimate the distribution of fitness effect (DFE) at the population scale by gathering information across many SNPs~\cite{eyre-walker_distribution_2006a, eyre-walker_estimating_2009a, galtier_adaptive_2016, tataru_inference_2017}.
-    These methods offer a unique opportunity to compare selection coefficients estimated at the population scale ($\Spop$) and at the phylogenetic scale ($\Sphy$).
-    In order to estimate the DFE at the population level and gather robust statistical estimates, we grouped SNPs observed at the population level (e.g.~in humans of African descent in fig.~\ref{fig:homo-afr-results}) in 5 classes of predicted selection coefficient: severely deleterious with $\divStrongDel$, deleterious with $\divDel$, weakly deleterious with $\divWeakDel$, weakly beneficial with $\divWeakAdv$ and beneficial with $\divAdv$ (fig.~\ref{fig:homo-afr-results}B).
-
-    To obtain a quantitative estimate of the distribution of selection coefficient for each category of SNPs, we used the model polyDFE~\cite{tataru_inference_2017, tataru_polydfe_2020}.
-    This model uses the count of derived alleles for each frequency class (fig.~\ref{fig:homo-afr-results}C) to infer the distribution of fitness effects (DFE).
-    Moreover, the model relies on the mutational opportunities ($L$) for each category of $\Sphy$ (fig.~\ref{fig:homo-afr-results}A, see Material \& Methods) as well as the count of synonymous derived alleles used as a neutral model, which allow to control for demographic effects, and polarization errors when inferring the ancestral states.
-    We could estimate the proportion of beneficial mutations ($\PpolyAdv$), nearly-neutral mutations ($\PpolyNeutral$) and deleterious mutations ($\PpolyDel$) for each class of selection previously defined (fig.~\ref{fig:homo-afr-results}D).
-    We found that SNPs predicted to be deleterious based on the selection coefficient $\Sphy$ estimated across the phylogeny of mammals were effectively purged at the population scale (blue and green columns in fig.~\ref{fig:homo-afr-results}D)
-    Purifying selection is therefore largely predictable and amino acids with low fitness across mammals are effectively purged away in each population.
-    Then, SNPs predicted to be beneficial based on the selection coefficient $\Sphy$ estimated at the scale of the phylogeny of mammals are indeed beneficial for individuals currently bearing them (red column in fig.~\ref{fig:homo-afr-results}D).
+    Within populations, the frequencies at which SNPs are segregating is also providing information on their selective effect.
+    For instance, deleterious SNPs are segregating at lower frequencies because of the effect of purifying selection, which removes them from the population.
+    It is possible to estimate the DFE at the population scale by gathering information across many SNPs~\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009, galtier_adaptive_2016, tataru_inference_2017} and these approaches offer a unique opportunity to compare selection coefficients estimated at the population scale ($\Spop$) and at the phylogenetic scale ($\Sphy$).
+    We estimated the DFE at the population level and gathered robust statistical estimates by grouping SNPs observed in 5 classes of predicted selection coefficient (e.g.~in humans of African descent in fig.~\ref{fig:homo-afr-results}): severely deleterious with $\divStrongDel$, deleterious with $\divDel$, weakly deleterious with $\divWeakDel$, weakly beneficial with $\divWeakAdv$ and beneficial with $\divAdv$ (fig.~\ref{fig:homo-afr-results}B).
+	%in mat/met
+	%To obtain a quantitative estimate of the distribution of selection coefficient for each category of SNPs, we used the model polyDFE~\cite{tataru_inference_2017, tataru_polydfe_2020}.
+    %This model uses the count of derived alleles for each frequency class (fig.~\ref{fig:homo-afr-results}C) to infer the distribution of fitness effects (DFE).
+    %Moreover, the model relies on the mutational opportunities ($L$) for each category of $\Sphy$ (fig.~\ref{fig:homo-afr-results}A, see Material \& Methods) as well as the count of synonymous derived alleles used as a neutral model, which allow to control for demographic effects, and polarization errors when inferring the ancestral states.
+    From the DFE, we further estimated the proportion of beneficial mutations ($\PpolyAdv$), nearly-neutral mutations ($\PpolyNeutral$) and deleterious mutations ($\PpolyDel$) for each class of selection previously defined (fig.~\ref{fig:homo-afr-results}D).
+    We found that SNPs predicted to be deleterious based on the selection coefficient $\Sphy$ estimated across the phylogenetic tree of mammals were effectively purged at the population scale (red and yellow columns in fig.~\ref{fig:homo-afr-results}D)
+    Purifying selection was therefore largely predictable and amino acids with low fitness across mammals were effectively purged away in each population.
+    Then, SNPs predicted to be beneficial based on the selection coefficient $\Sphy$ estimated at the phylogenetic scale were indeed beneficial for individuals currently bearing them (blue column in fig.~\ref{fig:homo-afr-results}D).
     These results confirmed that selection towards amino acids that are restoring existing function is ongoing in these populations.
@@
 
-    We replicated our experiment across 28 populations of different mammal species (fig.~\ref{fig:heatmap}) and found that SNPs predicted to be deleterious were indeed purged at the population scale (blue and green rows in fig.~\ref{fig:heatmap}A).
+    We replicated our experiment across 28 populations of different mammal species (fig.~\ref{fig:heatmap}) and found that SNPs predicted to be deleterious were indeed purged at the population scale (red and yellow rows in fig.~\ref{fig:heatmap}A).
     However, SNPs predicted to be weakly beneficial ($\divWeakAdv$) were composed of a mix of neutral and selected mutations with varying proportions across the different populations (cyan and orange row in fig.~\ref{fig:heatmap}B).
-    Finally, SNPs predicted to be beneficial back-mutations ($\divAdv$) were found to be beneficial with varying proportions across populations (red row in fig.~\ref{fig:heatmap}C).
-    The variable proportions found between populations can be explained by the effective number of individuals in the population ($\Ne$), which is well-known to be a major driver of selection efficacy.
+    Finally, SNPs predicted to be beneficial back-mutations ($\divAdv$) were found to be beneficial with varying proportions across populations (blue row in fig.~\ref{fig:heatmap}C).
+    The variable proportions found between populations can be explained by the effective number of individuals in the population ($\Ne$), which is known to be a major driver of selection efficacy.
     Since $\Ne$ is not directly measurable, we used the Watterson $\theta_w$ as a proxy to order populations by their levels of synonymous diversity.
-    Higher synonymous diversity is associated with a smaller proportion of nearly-neutral mutations (fig.~\ref{fig:diversity}A\&B).
-    This result confirms the nearly-neutral theory and suggests that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) are more likely to discriminate between beneficial and deleterious mutations (fig~S1-S9), while mutations in populations with low diversity (e.g.~\textit{Homo}) are effectively nearly-neutral.
+    Higher synonymous diversity was associated with a smaller proportion of nearly-neutral mutations (fig.~\ref{fig:diversity}A\&B).
+    This result confirmed the nearly-neutral theory and suggested that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) were more likely to discriminate between beneficial and deleterious mutations (fig~S1-S9), while mutations in populations with low diversity (e.g.~\textit{Homo}) were effectively nearly-neutral.
 
@@
 
-    Finally, we propose an estimator for the probability of a beneficial mutation to be a beneficial back-mutation, computed as $\mathbb{P} [ \Sphy > 1  \given  \Spop > 1]$ (fig.~\ref{fig:method}C-F).
-    We obtained from the analyses above the following probabilities $\mathbb{P} [ \Sphy > 1 ]$, $\mathbb{P} [ \Spop > 1 ]$, $\mathbb{P} [ \Spop > 1  \given  \Sphy > 1]$.
-    First, $\mathbb{P} [ \Sphy > 1 ]$ is the probability for a beneficial back-mutation ($\Sphy > 1$) from the ancestral sequence (red fill of histogram in fig~\ref{fig:homo-afr-results}A and table~S3).
+    Finally, we proposed an estimator for the probability of a beneficial mutation to be a beneficial back-mutation, computed as $\mathbb{P} [ \Sphy > 1  \given  \Spop > 1]$ (fig.~\ref{fig:method}C-F).
+    We obtained from the analyses above the probabilities $\mathbb{P} [ \Sphy > 1 ]$, $\mathbb{P} [ \Spop > 1 ]$, $\mathbb{P} [ \Spop > 1  \given  \Sphy > 1]$.
+    First, $\mathbb{P} [ \Sphy > 1 ]$ is the probability for a beneficial back-mutation ($\Sphy > 1$) from the ancestral sequence (blue fill of histogram in fig~\ref{fig:homo-afr-results}A and table~S3).
     Second, $\mathbb{P} [ \Spop > 1 ]$ is the probability of mutation to be beneficial at the level of the population ($\Spop > 1$), estimated from all available SNPs (black fill in fig~\ref{fig:diversity}A and table~S3).
-    Finally, $\mathbb{P} [ \Spop > 1  \given  \Sphy > 1]$ is the probability for a back-mutation ($\Sphy > 1$) to be effectively beneficial at the level of the population ($\Spop > 1$), when we restricted our analysis on SNPs that are already predicted to be beneficial back-mutations (black fill for the category $\Sphy > 1$ in fig~\ref{fig:homo-afr-results}D and table~S3).
-    Combining these probabilities using Bayes theorem, we now obtain the probability for a beneficial mutation to be a back-mutation $\mathbb{P} [ \Sphy > 1  \given  \Spop > 1]$ (see Material \& Methods).
-    We estimated $\mathbb{P} [ \Sphy > 1  \given  \Spop > 1]$ across all populations sampled and obtained a proportion that varies between 10 and 26\% (table~S3).
+    Finally, $\mathbb{P} [ \Spop > 1  \given  \Sphy > 1]$ is the probability for a back-mutation ($\Sphy > 1$) to be effectively beneficial at the level of the population ($\Spop > 1$), when we restricted our analysis on SNPs that were already predicted to be beneficial back-mutations (black fill for the category $\Sphy > 1$ in fig~\ref{fig:homo-afr-results}D and table~S3).
+    Combining these probabilities using Bayes theorem allowed us to obtain the probability for a beneficial mutation to be a back-mutation $\mathbb{P} [ \Sphy > 1  \given  \Spop > 1]$ (see Material \& Methods).
+    We estimated $\mathbb{P} [ \Sphy > 1  \given  \Spop > 1]$ across all populations sampled and obtained a proportion that varied between 10 and 26\% (table~S3).
 
-    The proportion of back-mutations among all beneficial one did not show a clear relationship with the synonymous diversity within a population (Watterson $\theta_w$) (fig.~\ref{fig:diversity}C).
+    The proportion of back-mutations among all beneficial ones did not show a clear relationship with the synonymous diversity within a population (Watterson $\theta_w$) (fig.~\ref{fig:diversity}C).
     Indeed, the relationship between $\Ne$ and the proportion of beneficial back-mutations is not trivial and should highly depend on time scales~\cite{charlesworth_other_2007}.
@@
             Panel A: Distribution of fitness effects ($\Sphy$), predicted for all possible mutations away from the ancestral human genome.
-            Mutations are divided into 5 classes of selection: severely deleterious (blue), deleterious (green), weakly deleterious (light green), weakly beneficial (yellow) and beneficial (red, supposedly beneficial back-mutations).
+            Mutations are divided into 5 classes of selection: severely deleterious (red), deleterious (yellow), weakly deleterious (light green), weakly beneficial (green) and beneficial (blue, supposedly beneficial back-mutations).
             Panel B. Distribution of fitness effects ($\Sphy$) for all observed SNPs in a sample of 8 individuals (out of 512 in the original dataset) of African descent.
@@
     However, we so far assumed no changes in effective population size along the phylogeny while it has been established that population size changes have a major effect on selection dynamics~\cite{lanfear_population_2014, jones_shifting_2017, platt_protein_2018}.
-    Mutation-selection models with changes in effective population sizes along the phylogeny have been developed~\cite{latrille_inferring_2021a}, but are, for the moment, too computational intensive to be performed genome-wide.
+    Mutation-selection models with changes in effective population sizes along the phylogeny have been developed~\cite{latrille_inferring_2021}, but are, for the moment, too computational intensive to be performed genome-wide.
     Hybrid mutation-selection and phenomenological codon models could provide a way forward to integrate site-specific selection and branch-specific drift~\cite{brevet_reconstructing_2021a}.
@@
 %TC:ignore
-    \section*{Acknowledgments}
+    \section*{Acknowledgements}
     \label{sec:acknowledgment}
-    We gratefully acknowledge the help of Mélodie Bastian, Nicolas Lartillot, Laurent Duret and Diego A. Hartasánchez Frenk for their advices and reviews concerning this manuscript.
+    We gratefully acknowledge the help of Mélodie Bastian, Nicolas Lartillot and Laurent Duret for their advice and reviews concerning this manuscript.
     This work was performed using the computing facilities of the CC LBBE/PRABI\@.
@@
     Data analyses: T.L.\ and J.J.;
-    Interpretation: T.L., J.J.\ and N.S.;
+    Interpretation: T.L., J.J., D.A.H.\ and N.S.;
     First draft: T.L.\ and J.J.;
-    Editing and revisions: T.L., J.J.\ and N.S.
+    Editing and revisions: T.L., J.J., D.A.H.\ and N.S.
     Project management and funding: N.S\@.
@@
 
-    \section{Material \& Methods}
+    \section{Materials \& Methods}
     \label{sec:methods}
@@
     Genes located on the X, Y chromosomes and the mitochondrial genome were discarded from the analysis, because the level of polymorphism, which is necessary in the population-based analyses, is expected to be different in these three genomic regions.
-    Sequences of species for which we used population-level polymorphism (see below), as well as their sister species, were removed from the analysis to ensure independence between the data used in the phylogenetic and population scale.
+    Sequences of species for which we used population-level polymorphism (see below), as well as their sister species, were removed from the analysis to ensure independence between the data used in the phylogenetic and population scales.
     Altogether, our genome-wide dataset contains $14,509$ protein-coding DNA sequences for at most $87$ sequences of placental mammals.
@@
     \label{subsec:s-phylogeny-method}
-    We analyzed the phylogenetic level data using mutation-selection models.
+    One of the most used methods to predict selective effects is SIFT (Sort Intolerant From Tolerant), which reliably detects deleterious mutations in many taxa~\cite{ng_sift_2003, vaser_sift_2016}.
+    However, SIFT scores are not interpretable as a selection coefficient.
+    Moreover, SIFT scores do not account for some key processes that can influence the abundance of an amino-acid in an alignment.
+    For instance, it does not take into account phylogenetic inertia, mutation biases, GC-biased gene conversion, or mutational paths.
+    Here, we analyzed the phylogenetic level data using mutation-selection models.
     These models assume that the protein-coding sequence are at mutation-selection balance under a fixed fitness landscape characterized by a fitness vector over the $20$ amino acid at each site~\cite{yang_mutationselection_2008, halpern_evolutionary_1998, rodrigue_mechanistic_2010}.
     Mathematically, the rate of non-synonymous substitution from codon $a$ to codon $b$ ($q_{a \mapsto b}^{(i)}$) at site $i$ of the sequence is equal to the rate of mutation of the underlying nucleotide change ($\mu_{a \mapsto b}$) multiplied by the scaled probability of fixation of the mutation ($\proba_{a \mapsto b}^{(i)}$).
-    The probability of fixation depends on the difference of scaled fitness of the amino acid encoded by the mutated codon ($F_b^{(i)}$) and the amino acid encoded by the original codon ($F_a^{(i)}$) at site $i$~\cite{wright_evolution_1931a, fisher_genetical_1930a}.
+    The probability of fixation depends on the difference of scaled fitness of the amino acid encoded by the mutated codon ($F_b^{(i)}$) and the amino acid encoded by the original codon ($F_a^{(i)}$) at site $i$~\cite{wright_evolution_1931, fisher_genetical_1930}.
     The rate of substitution from codon $a$ to $b$ at a site $i$ is thus:
@@
     \end{equation}
-    Fitting the mutation-selection model on a sequence alignment leads to an estimation of the mutation rate matrix ($\UniDimArray{\mu}$) as well as the 20 amino acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$.
+    Fitting the mutation-selection model on a multi-species sequence alignment leads to an estimation of the mutation rate matrix ($\UniDimArray{\mu}$) as well as the 20 amino acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$.
     The selection coefficient for a mutation from codon $a$ to codon $b$ at site $i$ is defined :
@@
     \end{equation}
-    In the manuscript and the following material, the source ($a$) and target ($b$) codons as well as the site ($i$) are implicit and thus never explicitly written.
-    The Bayesian software \textit{BayesCode} (\url{https://github.com/ThibaultLatrille/bayescode}) was run on each protein-coding DNA alignment for $2000$ generations of Markov Chain Monte-Carlo (MCMC), as in \textcite{latrille_genes_2022}.
-    For each gene, after discarding the burn-in period of $1000$ generations of MCMC, we obtain posterior mean estimates (over the $1000$ generations left of MCMC) of the mutation rate matrix ($\UniDimArray{\mu}$) as well as the 20 amino acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$.
+    %In the manuscript and the following material, the source ($a$) and target ($b$) codons as well as the site ($i$) are implicit and thus never explicitly written.
+    We used the Bayesian software \textit{BayesCode} (\url{https://github.com/ThibaultLatrille/bayescode}) to estimate the selection coefficients for each protein-coding genes in the mammal dataset.
+    We ran the Markov chain Monte-Carlo (MCMC) algorithm implemented in BayesCode for $2,000$ generations as described in \textcite{latrille_genes_2022}.
+    For each gene, after discarding a burn-in period of $1,000$ generations of MCMC, we obtained posterior mean estimates (over the $1,000$ generations left of MCMC) of the mutation rate matrix ($\UniDimArray{\mu}$) as well as the 20 amino acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$.
 
@@
 
-    The genetic variants representing the population level polymorphism are from the following species and respective available datasets: \textit{Equus caballus} (EquCab2 assembly in the EVA study PRJEB9799~\cite{alabri_whole_2020}), \textit{Bos taurus} (UMD3.1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}), \textit{Ovis aries} (Oar\_v3.1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}), \textit{Capra Hircus} (CHIR1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}, converted to ARS1 assembly with dbSNP identifiers\cite{sherry_dbsnp_2001}), \textit{Chlorocebus sabaeus} (ChlSab1.1 assembly in the EVA project PRJEB22989~\cite{svardal_ancient_2017}), \textit{Homo sapiens} (GRCh38 assembly from the 1000-genome project~\cite{consortium_integrated_2012a, the1000genomesprojectconsortium_global_2015}).
-    In total, we analyzed 28 populations across the 6 different species with polymorphism data, also processed as in \textcite{latrille_genes_2022}.
+    The genetic variants representing the population level polymorphism were obtained from the following species and respective available datasets: \textit{Equus caballus} (EquCab2 assembly in the EVA study PRJEB9799~\cite{alabri_whole_2020}), \textit{Bos taurus} (UMD3.1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}), \textit{Ovis aries} (Oar\_v3.1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}), \textit{Capra Hircus} (CHIR1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}, converted to ARS1 assembly with dbSNP identifiers\cite{sherry_dbsnp_2001}), \textit{Chlorocebus sabaeus} (ChlSab1.1 assembly in the EVA project PRJEB22989~\cite{svardal_ancient_2017}), \textit{Homo sapiens} (GRCh38 assembly from the 1000-genome project~\cite{consortium_integrated_2012, the1000genomesprojectconsortium_global_2015}).
+    In total, we analyzed 28 populations across the 6 different species with polymorphism data.
+    The data was processed as described in \textcite{latrille_genes_2022}.
 
     Genetic variants that were not found within a gene were not used in further analyses.
-    We also did not analyzed insertions and deletions and focused only on Single Nucleotide Polymorphisms (SNPs) with a single mutant allele.
-    Finally, stop codon mutants were also discarded.
-    Each SNP (chromosome, position, strand) in the focal species was matched to its relative position (chromosome, position, strand) in the protein-coding DNA alignment by first converting the genomic positions to relative position in the coding sequence (CDS) using gene annotation files (GTF format) downloaded from Ensembl (\url{ensembl.org}).
-    We then verified that the SNP downloaded from Ensembl were matching the reference in the CDS (FASTA format).
-    Second, the relative position in the CDS was converted to position in the multiple sequence alignment (containing gaps) from OrthoMaM database (see section \ref{subsec:s-phylogeny-method}) by doing a global pairwise alignment, using the Biopython function pairwise2, between the CDS fasta and the sequence found in the alignment.
-    This conversion from genomic position to alignment position is only possible if the assembly used for SNP calling is the same as the one used in the alignment, the GTF annotations and the FASTA sequences.
+    We also did not analyzed insertions and deletions and focused only on Single Nucleotide Polymorphisms (SNPs) with a single mutant allele, while stop codon variants were also discarded.
+    First, each SNP (chromosome, position, strand) in the focal species was matched to its relative position (chromosome, position, strand) in the protein-coding DNA alignment by first converting the genomic positions to relative position in the coding sequence (CDS) using gene annotation files (GTF format) downloaded from Ensembl (\url{ensembl.org}).
+    We then verified that the SNP downloaded from Ensembl were matching the reference in the CDS in FASTA format.
+    Second, the relative position in the CDS was converted to position in the multi-species sequence alignment (containing gaps) from OrthoMaM database (see section \ref{subsec:s-phylogeny-method}) by doing a global pairwise alignment, using the Biopython function pairwise2, between the CDS fasta and the sequence found in the alignment.
+    This conversion from genomic position to alignment position was only possible when the assembly used for SNP calling was the same as the one used in the alignment, the GTF annotations and the FASTA sequences.
     SNPs were polarized using the $3$ closest outgroups found in the OrthoMam alignment with est-usfs v2.04~\cite{keightley_inferring_2018}.
@@
     For each population with polymorphism data available, the polarized SNPs (ancestral and derived alleles) were used to reconstruct the ancestral DNA sequence, containing only substitutions and no segregating polymorphisms.
-    If a SNP is still segregating in the population, the ancestral version of the SNP is used.
-    However, if the derived allele is shared by all individuals in the population, the allele is considered fixed and the derived allele of the SNP is used as the ancestral.
-    From this reconstructed ancestral genome (instead of the reference genome) at the base of the population genealogy, all possible mutations were computed, weighted by the mutation rate between nucleotide ($\mu$), which was estimated at the phylogenetic scale.
+    If a SNP was still segregating in the population, the ancestral version of the SNP was used.
+    However, if the derived allele was shared by all individuals in the population, the allele was considered fixed and the derived allele of the SNP was used as the ancestral.
+    This ancestral genome is different from the reference genome as it accounts for the variability present in the population analysed.
+    From this reconstructed ancestral genome at the base of the population genealogy, all possible mutations were computed, weighted by the mutation rate between nucleotide ($\mu$), which was estimated at the phylogenetic scale.
     The total mutation rate for synonymous mutations, called $\mu_{\textrm{syn}}$, was estimated as the sum across the whole genome.
@@
     For each gene and for each population with polymorphism data available, the genome at the base of the population genealogy was reconstructed (see section \ref{subsec:nunber-of-sites}).
-    Then, using this genome at the base of the population genealogy and the $3$ closest outgroups found in the OrthoMam alignment, we reconstructed the ancestral protein-coding DNA sequences for each node of the 4-leaves tree with the yang M5 codon model (gamma site rate variation) in FastML.v3.11~\cite{ashkenazy_fastml_2012}.
-    All polarized codon substitutions are then obtained by comparing the ancestral protein-coding DNA sequences before the split to the sister species (closest outgroup) to the genome at the base of the population genealogy.
+    We used the ancestral genome reconstructed at the base of the population genealogy and the $3$ closest outgroups found in the OrthoMam alignment to infer the ancestral protein-coding DNA sequences for each node of the 4-taxa tree by applying the M5 codon model (gamma site rate variation) as implemented in FastML.v3.11~\cite{ashkenazy_fastml_2012}.
+    All polarized codon substitutions were then obtained by comparing the ancestral protein-coding DNA sequences before the split to the sister species (closest outgroup) to the genome at the base of the population genealogy.
     We considered \textit{Ceratotherium simum simum} as \textit{Equus caballus} sister species; \textit{Bison bison bison} as \textit{Bos taurus} sister species; \textit{Pantholops hodgsonii} as \textit{Ovis aries} sister species; \textit{Pantholops hodgsonii} as \textit{Capra Hircus} sister species; \textit{Macaca mulatta} as \textit{Chlorocebus sabaeus} sister species and finally we considered \textit{Pan troglodytes} as \textit{Homo sapiens} sister species.
-    The selection coefficient ($\Sphy$) of each substitution is then obtained by comparing the difference in amino acid fitnesses for each polarized non-synonymous codon substitution, by referring to the site-specific fitness profile obtained in the phylogeny-based method (see~\ref{subsec:s-phylogeny-method}).
-    Finally, the rate of non-synonymous over synonymous substitution for a given class of selection coefficient ($\Sphyclass$) is computed as:
+    The selection coefficient ($\Sphy$) of each substitution was then obtained by comparing the difference in amino acid fitnesses for each polarized non-synonymous codon substitution, by referring to the site-specific fitness profile obtained in the phylogeny-based method (see~\ref{subsec:s-phylogeny-method}).
+    Finally, the rate of non-synonymous over synonymous substitution for a given class of selection coefficient ($\Sphyclass$) was computed as:
     \begin{align}
@@
     \end{align}
-    where $D \left( \Sphyclass \right) $ is the number of non-synonymous substitutions in the class $\Sphyclass$, $D_{\textrm{syn}}$ is the number of synonymous substitutions across the genome, while $L \left( \Sphyclass \right)$ and $L_{\textrm{syn}}$ are the number of non-synonymous and synonymous mutational opportunities as defined in section \ref{subsec:nunber-of-sites}.
+    where $D \left( \Sphyclass \right) $ was the number of non-synonymous substitutions in the class $\Sphyclass$, $D_{\textrm{syn}}$ was the number of synonymous substitutions across the genome, while $L \left( \Sphyclass \right)$ and $L_{\textrm{syn}}$ were the number of non-synonymous and synonymous mutational opportunities as defined in section \ref{subsec:nunber-of-sites}.
     The fraction of non-adaptive beneficial substitutions $R(\dnds)$ was computed as the ratio between the difference in the numbers of beneficial substitutions ($\dnds$), which were due to beneficial back-mutations, and the estimated divergence when we removed beneficial back-mutations $\dn (\Sphy < 0) / \ds$, over $\dnds$.
@@
     Pooled across many sites, the site-frequency spectrum (SFS) provides therefore information on the underlying $\Spop$ of mutations.
-    However, estimating a single $\Spop$ for all sampled mutations is biologically unrealistic and a distribution of fitness effects of mutations (DFE) is usually assumed~\cite{eyre-walker_distribution_2006a, eyre-walker_estimating_2009a}.
-    In this study, we used the software polyDFE~\cite{tataru_inference_2017, tataru_polydfe_2020}, which used a mixture of a $\Gamma$ and Exponential distributions to model the DFE of non-synonymous mutations, while synonymous mutations are considered neutral.
+    However, estimating a single $\Spop$ for all sampled mutations is biologically unrealistic and a distribution of fitness effects (DFE) of mutations is usually assumed~\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009}.
+    We used the software polyDFE~\cite{tataru_inference_2017, tataru_polydfe_2020} that implemented a mixture of a $\Gamma$ and Exponential distributions to model the DFE of non-synonymous mutations, while synonymous mutations are considered neutral.
     The model estimates the parameters $\DelMean$ , $b$, $p_b$ and $\AdvMean$ for non-synonymous mutations as:
@@
     \end{equation}
-    where $\DelMean \leq -1 $ is the estimated mean of the DFE for $\Spop \leq 0$,
-    $b \geq 0.4$ is the estimated shape of the $\Gamma$ distribution,
-    $0 \leq p_b \leq 1$ is the estimated probability that $\Spop > 0$,
-    $\AdvMean \geq 1$ is the estimated mean of the DFE for $\Spop > 0$,
-    and $f_{\Gamma}(x; m, b)$ is the density of the $\Gamma$ distribution with mean m and shape b, while $f_{e}(x; m)$ is the density of the Exponential distribution with mean $m$.
+    where $\DelMean \leq -1 $ was the estimated mean of the DFE for $\Spop \leq 0$,
+    $b \geq 0.4$ was the estimated shape of the $\Gamma$ distribution,
+    $0 \leq p_b \leq 1$ was the estimated probability that $\Spop > 0$,
+    $\AdvMean \geq 1$ wass the estimated mean of the DFE for $\Spop > 0$,
+    and $f_{\Gamma}(x; m, b)$ was the density of the $\Gamma$ distribution with mean m and shape b, while $f_{e}(x; m)$ is the density of the Exponential distribution with mean $m$.
     Once the DFE was fitted to the data, the proportion of beneficial ($\PpolyAdv$), nearly-neutral ($\PpolyNeutral$) and deleterious mutations ($\PpolyDel$) were given as:
@@
 
-    PolyDFE required one SFS for non-synonymous mutations and one for synonymous mutations (neutral expectation), as well as the number of sites on which each SFS has been sampled.
+    PolyDFE required one SFS for non-synonymous mutations and one for synonymous mutations (neutral expectation), as well as the number of sites on which each SFS was sampled.
     For populations containing more than $8$ individuals, the site-frequency spectrum (SFS) was subsampled down to $16$ chromosomes ($8$ diploid individuals) without replacement (hyper-geometric distribution) to alleviate the effect of different sampling depth in the 28 populations.
     Altogether, for each class of selection ($\Sphyclass$) of non-synonymous SNPs (or for all SNPs), we thus estimated the parameters of the DFE $\left( \Spop; \DelMean , b, p_b, \AdvMean \right)$ using maximum likelihood with polyDFE from the number of sites and the SFS obtained by aggregating all the SNPs in the selection class.
-    Once fitted to the data, the parameters of the DFE $\left( \Spop; \DelMean , b, p_b, \AdvMean \right)$ are used to compute $\PpolyAdv$, $\PpolyNeutral$, $\PpolyDel$ using eq.~\ref{eq:polyProbaAdv}-\ref{eq:polyProbaDel}.
+    Once fitted to the data, the parameters of the DFE $\left( \Spop; \DelMean , b, p_b, \AdvMean \right)$ were used to compute $\PpolyAdv$, $\PpolyNeutral$, $\PpolyDel$ using eq.~\ref{eq:polyProbaAdv}-\ref{eq:polyProbaDel}.
 
-    From Bayes theorem, it is now possible to obtain the probability for a beneficial mutation to be a back-mutation.
-    In other words, we seek to get the probability that a mutation is a back-mutation ($\divAdv$) given that it is beneficial ($\polyAdv$), as:
+    Using Bayes theorem, we obtained the probability for a beneficial mutation to be a back-mutation by estimating the probability that a mutation was a back-mutation ($\divAdv$) given that it was beneficial ($\polyAdv$), as:
     \begin{equation}
@@
     \end{equation}
-    where $\PpolyAdv$ is computed from all SNPS, $\proba \left[\polyAdv \given \divAdv\right]$ is obtained from the set of SNPs in the class $\Sphyclass = \divAdv$, and $\proba\left[\divAdv\right]$ is the probability for a new mutation to be inside the class $\divAdv$, thus computed as:
+    where $\PpolyAdv$ was computed from all SNPS, $\proba \left[\polyAdv \given \divAdv\right]$ was obtained from the set of SNPs in the class $\Sphyclass = \divAdv$, and $\proba\left[\divAdv\right]$ was the probability for a new mutation to be inside the class $\divAdv$, thus computed as:
     \begin{equation}

### 2023-01-16 scripts/libraries.py

@@ -418,26 +418,26 @@ class CategorySNP(list):
             if self.bins == 2:
                 self.inner_bound = [0.8]
                 self.dico = {
-                    "neg": P("$SIFT < 0.8$", BLUE, 0, 0.8),
-                    "pos": P("$SIFT > 0.8$", RED, 0.8, 1.0),
+                    "neg": P("$SIFT < 0.8$", RED, 0, 0.8),
+                    "pos": P("$SIFT > 0.8$", BLUE, 0.8, 1.0),
                     "syn": P("$Synonymous$", 'black', None, None)
                 }
             elif self.bins == 3:
                 self.inner_bound = [0.05, 0.8]
                 self.dico = {
-                    "neg-strong": P("$SIFT<0.05$", BLUE, 0, 0.05),
+                    "neg-strong": P("$SIFT<0.05$", RED, 0, 0.05),
                     "weak": P("$0.05<SIFT<0.8$", LIGHTGREEN, 0.05, 0.8),
-                    "pos": P("$SIFT > 0.8$", RED, 0.8, 1.0),
+                    "pos": P("$SIFT > 0.8$", BLUE, 0.8, 1.0),
                     "syn": P("$Synonymous$", 'black', None, None)
                 }
             else:
                 self.inner_bound = [0.05, 0.1, 0.3, 0.8]
                 self.dico = {
-                    "neg-strong": P("$SIFT<0.05$", BLUE, 0, 0.05),
-                    "neg": P("$0.05<SIFT<0.1$", GREEN, 0.05, 0.1),
+                    "neg-strong": P("$SIFT<0.05$", RED, 0, 0.05),
+                    "neg": P("$0.05<SIFT<0.1$", YELLOW, 0.05, 0.1),
                     "neg-weak": P("$0.1<SIFT<0.3$", LIGHTGREEN, 0.1, 0.3),
-                    "pos-weak": P("$0.3<SIFT<0.8$", YELLOW, 0.3, 0.8),
-                    "pos": P("$SIFT > 0.8$", RED, 0.8, 1.0),
+                    "pos-weak": P("$0.3<SIFT<0.8$", GREEN, 0.3, 0.8),
+                    "pos": P("$SIFT > 0.8$", BLUE, 0.8, 1.0),
                     "syn": P("$Synonymous$", 'black', None, None)
                 }
             self.update()
@@ -445,26 +445,26 @@ class CategorySNP(list):
             if self.bins == 2:
                 self.inner_bound = [1.0]
                 self.dico = {
[…]

### 2023-01-16 scripts/population_DFE.py

@@ -21,18 +21,18 @@ def main(output):
     print(x[-1])
     y = [(1 - p_pos) * d_neg.pdf(-s) for s in x]
     print(y[-1])
-    plt.plot(x, y, color=BLUE)
-    plt.fill_between(x, y, color=BLUE, alpha=0.5)
+    plt.plot(x, y, color=RED)
+    plt.fill_between(x, y, color=RED, alpha=0.5)
     d_pos = expon(scale=scale_pos)
     x = np.linspace(0, 10, 1000)
     y = [p_pos * d_pos.pdf(s) for s in x]
-    plt.plot(x, y, color=RED)
+    plt.plot(x, y, color=BLUE)
     plt.ylim((0, 0.2))
-    plt.fill_between(x, y, color=RED, alpha=0.5)
+    plt.fill_between(x, y, color=BLUE, alpha=0.5)
     plt.axvline(-1, color="grey", lw=1, ls='--')
     plt.axvline(1, color="grey", lw=1, ls='--')
     plt.axvline(0, color="black", lw=2, ls='--')
-    handles = [Rectangle((0, 0), 1, 1, color=c) for c in [BLUE, RED]]
+    handles = [Rectangle((0, 0), 1, 1, color=c) for c in [RED, BLUE]]
     labels = [f"$S < 0$ ({(1 - p_b) * 100:.2f}% of total)", f"$S > 0$ ({p_b * 100:.2f}% of total)"]
 
     plt.legend(handles, labels)

### 2023-02-01 manuscript/back-mutations-intro.tex
Introduction with focus on back-mutations as a separate file

--- 2023-01-16 manuscript/main.tex
@@
-%! BibTeX Compiler = biber
-%TC:ignore
-\documentclass{article}
-
-\usepackage{xcolor, colortbl}
-\definecolor{BLUELINK}{HTML}{0645AD}
-\definecolor{DARKBLUELINK}{HTML}{0B0080}
-\PassOptionsToPackage{hyphens}{url}
-\usepackage[colorlinks=false]{hyperref}
-% for linking between references, figures, TOC, etc in the pdf document
-\hypersetup{colorlinks,
-    linkcolor=DARKBLUELINK,
-    anchorcolor=DARKBLUELINK,
-    citecolor=DARKBLUELINK,
-    filecolor=DARKBLUELINK,
-    menucolor=DARKBLUELINK,
-    urlcolor=BLUELINK
-} % Color citation links in purple
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{naturalnames}{hyperref}
-
-\usepackage{biorxiv}
-\usepackage[backend=biber,eprint=false,isbn=false,url=false,intitle=true,style=nature,date=year]{biblatex}
-\addbibresource{codon_models.bib}
-
-\usepackage{url}
-\usepackage{amssymb,amsfonts,amsmath,amsthm,mathtools}
-\usepackage{lmodern}
-\usepackage{xfrac, nicefrac}
-\usepackage{bm}
-\usepackage{listings, enumerate, enumitem}
-\usepackage[export]{adjustbox}
-\usepackage{graphicx}
-\usepackage{bbold}
-\usepackage{pdfpages}
-\pdfinclusioncopyfonts=1
-\usepackage{lineno}
-
-\newcommand{\NS}[1]{\textcolor{red}{\textbf{\emph{[NS: #1]}}}}
-
-\newcommand{\UniDimArray}[1]{\bm{#1}}
-\newcommand{\BiDimArray}[1]{\bm{#1}}
-\DeclareMathOperator{\E}{\mathbb{E}}
-\DeclareMathOperator{\Var}{\textrm{Var}}
-\newcommand{\der}{\textrm{d}}
-\newcommand{\e}{\textrm{e}}
-\newcommand{\avg}[1]{\left< #1 \right>} % for average
-\newcommand{\Ne}{N_{\textrm{e}}}
-\newcommand{\proba}{\mathbb{P}}
-\newcommand{\pfix}{\proba_{\textrm{fix}}}
-\newcommand{\dn}{d_N}
-\newcommand{\ds}{d_S}
-\newcommand{\dnds}{\dn / \ds}
-\newcommand{\Sphy}{S_{0}}
-\newcommand{\Sphyclass}{\mathcal{C}}
-\newcommand{\SphyMean}{\overline{\Sphy}}
-\newcommand{\divStrongDel}{\Sphy < -3}
-\newcommand{\divDel}{-3 < \Sphy < -1}
-\newcommand{\divWeakDel}{-1 < \Sphy < 0}
-\newcommand{\divWeakAdv}{0 < \Sphy < 1}
-\newcommand{\divAdv}{ \Sphy > 1}
-\newcommand{\PdivStrongDel}{\proba \left[ \divStrongDel \right]}
-\newcommand{\PdivDel}{\proba \left[ \divDel \right]}
-\newcommand{\PdivWeakDel}{\proba \left[ \divWeakDel \right]}
-\newcommand{\PdivWeakAdv}{\proba \left[ \divWeakAdv \right]}
-\newcommand{\PdivAdv}{\proba \left[ \divAdv \right]}
-\newcommand{\given}{\mid}
-\newcommand{\Spop}{S}
-\newcommand{\SpopMean}{\overline{\Spop}}
-\newcommand{\polyDel}{\Spop < -1}
-\newcommand{\polyNeutral}{-1 < \Spop < 1}
-\newcommand{\polyAdv}{ \Spop > 1}
-\newcommand{\PpolyDel}{\proba \left[ \polyDel \right]}
-\newcommand{\PpolyNeutral}{\proba \left[ \polyNeutral \right]}
-\newcommand{\PpolyAdv}{\proba \left[ \polyAdv \right]}
-\newcommand{\AdvMean}{\beta_b}
-\newcommand{\DelMean}{\beta_d}
-\renewcommand{\baselinestretch}{1.5}
-\linenumbers
-
-\title{Up to 25\% of beneficial mutations in human protein sequences are not adaptive innovations in mammals}
-
-\author{
-    \large
-    \textbf{T. {Latrille}$^{1}$, J. {Joseph}$^{2}$, D.~A. {Hartasánchez}$^{1}$, N. {Salamin}$^{1}$}\\
-    \normalsize
-    $^{1}$Université de Lausanne, Lausanne, Switzerland\\
-    $^{2}$Université de Lyon, CNRS, LBBE UMR 5558, Villeurbanne, France \\
-    \texttt{\href{mailto:thibault.latrille@ens-lyon.org}{thibault.latrille@ens-lyon.org}} \\
-}
-
-% The submission checklist is available at:
-% https://docs.google.com/document/d/1aHCF1on0mHTK2DoroPCLP_xto4xwHnGJCGwaL1Vm2UE/edit?usp=sharing
-
-\begin{document}
-    \maketitle
-
-%TC:endignore
 \begin{abstract}
@@
 
-    Adaptation is considered one of the main processes shaping the diversity of forms and functions across the tree of life~\cite{darwin_origin_1859}.
-    It enables species to access new ecological niches and also respond to changes in their environment~\cite{darwin_origin_1859} [NS: maybe cite Losos or some key papers on ecological speciation rather than Darwin twice].
-    In evolution, adaptation is tightly linked to the notion of change at the level of the environment and to species responding to this change~\cite{merrell_adaptive_1994}.
+Adaptation is considered one of the main processes shaping the diversity of forms and functions across the tree of life\cite{darwin_origin_1859}.
+It enables species to access new ecological niches and also respond to changes in their environment\cite{gavrilets_adaptive_2009}.
+In evolution, adaptation is tightly linked to the notion of change at the level of the environment and to species responding to this change\cite{merrell_adaptive_1994}.
 The process of adaptation leaves marks of accelerated evolution in genomes since mutations that are beneficial under new conditions fix faster than neutral mutations (fig.~\ref{fig:fitness-landscape}A).
-    The signature of an accelerated rate of substitutions, defined as the rate of mutation times the probability of fixation, can thus be interpreted as a sign of adaptation~\cite{mcdonald_adaptative_1991, smith_adaptive_2002, welch_estimating_2006}.
-    The current availability of large-scale genomic data and the development of theoretical models have allowed to detect and quantify adaptation across genes and lineages, and these analyses have become common practice in evolutionary biology~\cite{yang_statistical_2000, eyre-walker_genomic_2006, moutinho_variation_2019} [NS: cite the paper by Anna Marcionetti here].
-    Although these approaches have led to a better understanding of the processes determining the rates of molecular evolution, they have had the effect of associating beneficial mutations with adaptive evolution, while disconnecting them from the notion of change defining adaptation.
-    We argue that we should limit the use of adaptive mutations to those that are associated with adaptation as such and dissociate beneficial mutations from adaptive mutations since adaptive evolution is not the only process that can lead to beneficial mutations~\cite{charlesworth_other_2007, mustonen_fitness_2009}.
-    We propose here a new approach to identify the mechanisms underlying the origin of beneficial mutations.
-    In particular, we suggest that many beneficial mutations are not adaptive, but are rather restoring ancestral states of higher fitness.
+The signature of an accelerated rate of substitutions can thus be interpreted as a sign of adaptation\cite{mcdonald_adaptative_1991, smith_adaptive_2002, welch_estimating_2006}.
+The current availability of large-scale genomic data and the development of theoretical models have allowed to detect and quantify acceleration of substitution rates across genes and lineages, and these analyses have become common practice in evolutionary biology\cite{yang_statistical_2000, eyre-walker_genomic_2006, moutinho_variation_2019}.
+Although these approaches have led to a better understanding of the processes determining the rates of molecular evolution, they have had the collateral effect of associating beneficial mutations with adaptive evolution.
+We argue that we should dissociate beneficial mutations from adaptive mutations since adaptive evolution is not the only process that can lead to beneficial mutations\cite{charlesworth_other_2007, mustonen_fitness_2009}, and in turn, limit the use of adaptive mutations to those that are associated with adaptation to environmental change as such.
+We here suggest that many beneficial mutations are not adaptive, but are rather restoring ancestral states of higher fitness.
 We used large-scale genomic data to integrate analyses at both the phylogenetic and population scales to differentiate between truly adaptive mutations from mutations restoring the ancestral fitness.
-    Our results show that up to a quarter of beneficial mutations across mammal species are not driven by adaptive innovations, but rather compensate the effect of ancestral mutations to recover the optimal state of the species.
+Our results show that between 10 and 25\% of beneficial mutations in mammalian populations are not driven by adaptive innovations, but rather compensate the effect of ancestral deleterious mutations.
 
-    In a constant environment, if a population is already adapted to these conditions, a deleterious mutation in an individual can reach fixation in the population by genetic drift~\cite{Ohta1992}.
-    Subsequently, a new mutation that is restoring the ancestral fitness will thus be beneficial (fig.~\ref{fig:fitness-landscape}B), even though no change in the environment occurred~\cite{hartl_compensatory_1996, sella_application_2005, mustonen_fitness_2009, cvijovic_fate_2015}.
-    The restoration of the ancestral fitness can happen at a different locus than the initial mutation, in which case it is referred to as a compensating [NS: ou compensatory ?] mutation~\cite{hartl_compensatory_1996, mustonen_fitness_2009}.
-    However, if the restoration of the ancestral fitness happens at the same locus than the initial mutation, in which case it is referred to as a beneficial back-mutation~\cite{piganeau_estimating_2003, charlesworth_other_2007}.
-    In this study, we focus on the latter case.
+In a constant environment, a deleterious mutation can reach fixation in the population by genetic drift\cite{Ohta1992}.
+Subsequently, a new mutation that is restoring the ancestral fitness will thus be beneficial (fig.~\ref{fig:fitness-landscape}B), even though no change in the environment has occurred\cite{hartl_compensatory_1996, sella_application_2005, mustonen_fitness_2009, cvijovic_fate_2015}.
+The restoration of the ancestral fitness can happen either at a different locus than the initial mutation, in which case it is referred to as a compensatory mutation\cite{hartl_compensatory_1996, mustonen_fitness_2009}, or at the same locus than the initial mutation, referred to as a beneficial back-mutation\cite{piganeau_estimating_2003, charlesworth_other_2007}.
 While compensatory mutations induce genetic changes at the sequence level, and thus genetic diversification, beneficial back-mutations reduce the genetic diversity and do not contribute to genetic innovation.
-    They merely cancel the effect of the previous deleterious changes.
-    As a consequence, not all beneficial mutations contribute to genetic innovation and truly adaptive evolution can only be correctly estimated if we can account for the number of beneficial back-mutations~\cite{keightley_what_2010, rice_evolutionarily_2015}.
-    % Philosophically, our distinction between beneficial back-mutations and adaptation can appear to be far-fetched, and one can argue that beneficial back-mutations is adaptation to its own deteriorating genome.
-    % However, there is a difference between adapting to a mutation, for instance by means of a compensatory mutation elsewhere, and cancelling the mutation, by means of a substitution on the misfit amino-acid.
+In this study, we focus on beneficial back-mutations, which merely cancel the effect of the previous deleterious changes.
+Altogether, we argue that not all beneficial mutations contribute to genetic innovation, and thus that the extent of adaptive evolution can only be correctly estimated if we can account for the number of beneficial back-mutations\cite{keightley_what_2010, rice_evolutionarily_2015}.
 
-    %For an individual carrying a beneficial mutation, whether this mutation is a new innovation responding to a change in environment or a beneficial back-mutation is indistinguishable~\cite{charlesworth_other_2007}.
-    Given a beneficial mutation, distinguishing whether it is a new innovation responding to a change in environment or a beneficial back-mutation is impossible with only one individual at hand~\cite{charlesworth_other_2007}.
-    This limitation persists at the level of the population, since both types of mutation will result in a positive transmission bias of the beneficial allele.
+Given a beneficial mutation, whether it is a new innovation responding to a change in environment or a beneficial back-mutation has the same consequences on its bearer\cite{charlesworth_other_2007}.
+Similarly, at the level of the population, both types of mutation will result in a positive transmission bias of the beneficial allele.
 However, at the macro-evolutionary scale the consequences of these two types of mutations are fundamentally different.
-    While adaptive evolution promotes phenotype diversification (fig.~\ref{fig:fitness-landscape}C), beneficial back-mutations promote phenotype stability and preserve well established biological systems (fig.~\ref{fig:fitness-landscape}D).
-    Additionally, the direction of adaptive evolution is unpredictable because it is caused by an unpredictable change in the environment and, hence, in the underlying fitness landscape~\cite{bazykin_changing_2015}.
+While adaptive evolution promotes phenotype diversification (fig.~\ref{fig:fitness-landscape}C), beneficial back-mutations promote phenotype stability and may help preserve well established biological systems (fig.~\ref{fig:fitness-landscape}D).
+Additionally, the direction of adaptive evolution is unpredictable because it is caused by an unpredictable change in the environment and, hence, in the underlying fitness landscape\cite{bazykin_changing_2015}.
 On the other hand, beneficial back-mutations are predictable if the underlying stable fitness landscape is known because we will expect to see changes from non-optimal amino acids to optimal ones.
@@
 The placental mammals represent an excellent study system to perform this analysis.
-    Having originated ~100 Mya\cite{kumar_timetree_2017}, they diversified quickly.
+Having originated $\sim$100 Mya\cite{kumar_timetree_2017}, they diversified quickly.
 Additionally, we have polymorphism data available for many species\cite{howe_ensembl_2021} and high quality protein-coding DNA alignments across the genome\cite{ranwez_orthomam_2007, scornavacca_orthomam_2019}.
 By restricting our analysis to protein-coding orthologous genes to all the phylogeny, and further excluding any genes for which there have been claims of pervasive directional selection, we can not only assume a constant fitness landscape for each of them throughout placental mammal evolution, but actually reconstruct the fitness landscape from variable positions within the sequence along the phylogeny.
-    For each gene, we used a codon model of mutation-selection~\cite{halpern_evolutionary_1998, mccandlish_modeling_2014} to obtain relative fitnesses for all amino-acids for each site of the sequence by fitting the model to the multi-species sequence alignment (fig~\ref{fig:method}A) and assuming that the underlying fitness landscape is stable along the phylogenetic tree.
-    %Mutation-selection codon models provide a nearly neutral framework of evolution taking into account non-adaptive processes impacting codon frequency~\cite{halpern_evolutionary_1998, rodrigue_mechanistic_2010, tamuri_estimating_2012, latrille_improved_2022}.
+For each gene, we used a codon model of mutation-selection\cite{halpern_evolutionary_1998, mccandlish_modeling_2014} to obtain relative fitnesses for all amino-acids for each site of the sequence by fitting the model to the multi-species sequence alignment (fig~\ref{fig:method}A) and assuming that the underlying fitness landscape is stable along the phylogenetic tree.
+%Mutation-selection codon models provide a nearly neutral framework of evolution taking into account non-adaptive processes impacting codon frequency\cite{halpern_evolutionary_1998, rodrigue_mechanistic_2010, tamuri_estimating_2012, latrille_improved_2022}.
 From the fitness landscape, we can calculate the scaled selection coefficient $\Sphy$ for any possible amino-acid change at each position.
@@
     \caption{
-            Panel A and B: at a given site of a protein-coding DNA sequence, the different amino acids (x-axis) have different fitnesses (y-axis).
+        Panel A and B: at a given site of a protein-coding DNA sequence, the different amino-acids (x-axis) have different fitnesses (y-axis).
         Under a fluctuating fitness landscape (panel A), these fitnesses are changing with time.
-            The protein sequence is always lagging behind the moving target defined by the amino acid fitnesses, and since substitutions are accepted preferentially if they are in the direction of this target, substitutions are on average adaptive.
+        The protein sequence is always lagging behind the moving target defined by the amino-acid fitnesses, and since substitutions are accepted preferentially if they are in the direction of this target, substitutions are on average adaptive.
         At the phylogenetic scale (panel C), this phenomena promotes phenotype diversification across species.
-            Under a stable fitness landscape (panel B), all the mutations reaching fixation are either slightly deleterious and reaching fixation due to drift, or are beneficial back-mutations restoring a more optimal amino acid.
+        Under a stable fitness landscape (panel B), all the mutations reaching fixation are either slightly deleterious and reaching fixation due to drift, or are beneficial back-mutations restoring a more optimal amino-acid.
         At the phylogenetic scale (panel D), this phenomena promotes promotes phenotype stability and preserves well established biological systems.
@@
 \end{figure*}
-
-    \begin{figure*}[!ht]
-        \centering
-        \includegraphics[width=\textwidth, page=1] {artworks/figure.method.proba}
-        \caption{
-            Integrating datasets at different scales.
-            At the phylogenetic level (panel A), the amino acid Wrightian fitness for each site is estimated from protein-coding DNA alignments using mutation-selection codon models.
-            Mutation-selection models assume a stable fitness landscape, taking into account only non-adaptive evolution.
-            A mutation with a $\Sphy > 1$ would be driving the current site toward are fitter amino-acid, and such mutation are considered a beneficial back-mutation repairing existing functions (panel B).
-            At the population scale (panel C), each single nucleotide polymorphism (SNP) segregating in the population can be classified as a beneficial back-mutation (in blue) or not.
-            The number of derived alleles allows us to estimate the probability of beneficial mutations at the population scale, for all SNPs or among back-mutations (panel D).
-            The probability of back-mutation is obtained as their fraction among all possible mutations from the ancestral genome sequence (panel E).
-            Altogether, we can estimate the probability of back-mutations among all beneficial ones, using Bayes' theorem (panel F).
-        }
-        \label{fig:method}
-    \end{figure*}
-
-    \subsection*{Back-mutations in the terminal lineages}
-    We first estimated the number of beneficial back-mutation in the terminal branches of mammals by reconstructing the substitutions occurring along the terminal branches of the phylogenetic tree.
-    For each substitution, we estimated its scaled selection coefficient ($\Sphy$) based on the stable fitness landscape of amino-acids estimated at the scale of the phylogenetic tree of mammals (fig.~\ref{fig:method}A).
-    Among all the substitutions that were found in the terminal branches, between 10 and 13\% had $\Sphy > 1$ (table~S1), while between 25 and 30\% had $\Sphy > 0$ (table~S2).
-    For substitutions with $\Sphy > 1$, the $\dnds$ ratio of non-synonymous over synonymous divergence was estimated to be between 1.15 and 1.68 in the different lineages (table~S1).
-    Beneficial back-mutations with $\Sphy > 1$ therefore reached fixation more frequently than synonymous mutations that are supposed to be neutral, which means that these back-mutations are effectively beneficial.
-    This result further indicated that $\dnds$ used to detect adaptation while relying on substitutions between closely related species~\cite{mcdonald_adaptative_1991, galtier_adaptive_2016} or at the phylogenetic scale~\cite{goldman_codonbased_1994, yang_codonsubstitution_2002} is biased due to the presence of beneficial back-mutations that are not adaptive.
-    We can alleviate this bias by computing $\dnds$ exclusively on non-synonymous sites with a $\Sphy < 0$, which represents the rate of evolution when beneficial back-mutations are discarded.
-    By comparing these two ways of estimating $\dnds$ (see Material \& Methods), we estimated that between 22\% and 27\% of $\dnds$ is inflated because of beneficial back-mutations while they only represent between 1\% and 2\% of mutational opportunities (table~S2).
-
-    \subsection*{Back-mutations in the populations}
-    We then estimated the proportion of new mutations that were beneficial back-mutations while being under selection at the population scale (fig.~\ref{fig:method}C-E).
-    We first reconstructed the ancestral genome (instead of the reference genome) of each mammal species with available polymorphism data.
-    We computed the scaled selection coefficient ($\Sphy$) along this ancestral genome for each possible non-synonymous mutations, weighted by their mutational opportunity (see Material \& Methods).
-    It allowed us to obtain the distribution of fitness effects (DFE) of new mutations from the ancestral sequence under the assumption of the stable fitness landscape as shown for \textit{Homo sapiens} in Fig.~\ref{fig:homo-afr-results}A.
-    Because $\Sphy$ was based on estimation of fitnesses at the mammalian scale, mutations with $\Sphy>1$ were considered, as shown above, beneficial back-mutations and only represented ca.~1.5\% of all possible new mutations (blue in fig.~\ref{fig:homo-afr-results}A, table~S3).
-    However, when focusing on the mutations that are observed in populations, namely single nucleotide polymorphism (SNP), beneficial back-mutations represents ca.~8.5\% of all observed mutations (blue in fig.~\ref{fig:homo-afr-results}B, table~S3).
-
-    Within populations, the frequencies at which SNPs are segregating is also providing information on their selective effect.
-    For instance, deleterious SNPs are segregating at lower frequencies because of the effect of purifying selection, which removes them from the population.
-    It is possible to estimate the DFE at the population scale by gathering information across many SNPs~\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009, galtier_adaptive_2016, tataru_inference_2017} and these approaches offer a unique opportunity to compare selection coefficients estimated at the population scale ($\Spop$) and at the phylogenetic scale ($\Sphy$).
-    We estimated the DFE at the population level and gathered robust statistical estimates by grouping SNPs observed in 5 classes of predicted selection coefficient (e.g.~in humans of African descent in fig.~\ref{fig:homo-afr-results}): severely deleterious with $\divStrongDel$, deleterious with $\divDel$, weakly deleterious with $\divWeakDel$, weakly beneficial with $\divWeakAdv$ and beneficial with $\divAdv$ (fig.~\ref{fig:homo-afr-results}B).
-	%in mat/met
-	%To obtain a quantitative estimate of the distribution of selection coefficient for each category of SNPs, we used the model polyDFE~\cite{tataru_inference_2017, tataru_polydfe_2020}.
-    %This model uses the count of derived alleles for each frequency class (fig.~\ref{fig:homo-afr-results}C) to infer the distribution of fitness effects (DFE).
-    %Moreover, the model relies on the mutational opportunities ($L$) for each category of $\Sphy$ (fig.~\ref{fig:homo-afr-results}A, see Material \& Methods) as well as the count of synonymous derived alleles used as a neutral model, which allow to control for demographic effects, and polarization errors when inferring the ancestral states.
-    From the DFE, we further estimated the proportion of beneficial mutations ($\PpolyAdv$), nearly-neutral mutations ($\PpolyNeutral$) and deleterious mutations ($\PpolyDel$) for each class of selection previously defined (fig.~\ref{fig:homo-afr-results}D).
-    We found that SNPs predicted to be deleterious based on the selection coefficient $\Sphy$ estimated across the phylogenetic tree of mammals were effectively purged at the population scale (red and yellow columns in fig.~\ref{fig:homo-afr-results}D)
-    Purifying selection was therefore largely predictable and amino acids with low fitness across mammals were effectively purged away in each population.
-    Then, SNPs predicted to be beneficial based on the selection coefficient $\Sphy$ estimated at the phylogenetic scale were indeed beneficial for individuals currently bearing them (blue column in fig.~\ref{fig:homo-afr-results}D).
-    These results confirmed that selection towards amino acids that are restoring existing function is ongoing in these populations.
-    Between these two extreme cases, SNPs predicted to be weakly selected (cyan and orange columns in fig.~\ref{fig:homo-afr-results}D) were effectively composed of neutral, beneficial and deleterious mutations.
-
-    We replicated our experiment across 28 populations of different mammal species (fig.~\ref{fig:heatmap}) and found that SNPs predicted to be deleterious were indeed purged at the population scale (red and yellow rows in fig.~\ref{fig:heatmap}A).
-    However, SNPs predicted to be weakly beneficial ($\divWeakAdv$) were composed of a mix of neutral and selected mutations with varying proportions across the different populations (cyan and orange row in fig.~\ref{fig:heatmap}B).
-    Finally, SNPs predicted to be beneficial back-mutations ($\divAdv$) were found to be beneficial with varying proportions across populations (blue row in fig.~\ref{fig:heatmap}C).
-    The variable proportions found between populations can be explained by the effective number of individuals in the population ($\Ne$), which is known to be a major driver of selection efficacy.
-    Since $\Ne$ is not directly measurable, we used the Watterson $\theta_w$ as a proxy to order populations by their levels of synonymous diversity.
-    Higher synonymous diversity was associated with a smaller proportion of nearly-neutral mutations (fig.~\ref{fig:diversity}A\&B).
-    This result confirmed the nearly-neutral theory and suggested that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) were more likely to discriminate between beneficial and deleterious mutations (fig~S1-S9), while mutations in populations with low diversity (e.g.~\textit{Homo}) were effectively nearly-neutral.
-
-    \subsection*{Proportion of back-mutations among all beneficial mutations}
-
-    Finally, we proposed an estimator for the probability of a beneficial mutation to be a beneficial back-mutation, computed as $\mathbb{P} [ \Sphy > 1  \given  \Spop > 1]$ (fig.~\ref{fig:method}C-F).
-    We obtained from the analyses above the probabilities $\mathbb{P} [ \Sphy > 1 ]$, $\mathbb{P} [ \Spop > 1 ]$, $\mathbb{P} [ \Spop > 1  \given  \Sphy > 1]$.
-    First, $\mathbb{P} [ \Sphy > 1 ]$ is the probability for a beneficial back-mutation ($\Sphy > 1$) from the ancestral sequence (blue fill of histogram in fig~\ref{fig:homo-afr-results}A and table~S3).
-    Second, $\mathbb{P} [ \Spop > 1 ]$ is the probability of mutation to be beneficial at the level of the population ($\Spop > 1$), estimated from all available SNPs (black fill in fig~\ref{fig:diversity}A and table~S3).
-    Finally, $\mathbb{P} [ \Spop > 1  \given  \Sphy > 1]$ is the probability for a back-mutation ($\Sphy > 1$) to be effectively beneficial at the level of the population ($\Spop > 1$), when we restricted our analysis on SNPs that were already predicted to be beneficial back-mutations (black fill for the category $\Sphy > 1$ in fig~\ref{fig:homo-afr-results}D and table~S3).
-    Combining these probabilities using Bayes theorem allowed us to obtain the probability for a beneficial mutation to be a back-mutation $\mathbb{P} [ \Sphy > 1  \given  \Spop > 1]$ (see Material \& Methods).
-    We estimated $\mathbb{P} [ \Sphy > 1  \given  \Spop > 1]$ across all populations sampled and obtained a proportion that varied between 10 and 26\% (table~S3).
-
-    The proportion of back-mutations among all beneficial ones did not show a clear relationship with the synonymous diversity within a population (Watterson $\theta_w$) (fig.~\ref{fig:diversity}C).
-    Indeed, the relationship between $\Ne$ and the proportion of beneficial back-mutations is not trivial and should highly depend on time scales~\cite{charlesworth_other_2007}.
-    A population that experienced a high $\Ne$ along its evolutionary time should be closer to the optimal state under a stable fitness landscape because of the higher efficacy of selection.
-    This should decrease the probability of beneficial back-mutations~\cite{huber_determining_2017}.
-    On the other hand, a high $\Ne$ over a short evolutionary time will induce more extreme fitness effects and a larger proportion of mutations will be beneficial (otherwise effectively neutral), thus increasing the proportion of beneficial back-mutations.
-    Overall, the proportion of beneficial back-mutations is expected to be more dependent on long-term effective population size as well as contraction or expansion rather than on the short term effective population size captured by the synonymous diversity~\cite{charlesworth_other_2007,huber_determining_2017}.
-
-    \begin{figure*}[!ht]
-        \centering
-        \includegraphics[width=\textwidth, page=1] {artworks/figure.homo-afr-results}
-        \caption{
-            Panel A: Distribution of fitness effects ($\Sphy$), predicted for all possible mutations away from the ancestral human genome.
-            Mutations are divided into 5 classes of selection: severely deleterious (red), deleterious (yellow), weakly deleterious (light green), weakly beneficial (green) and beneficial (blue, supposedly beneficial back-mutations).
-            Panel B. Distribution of fitness effects ($\Sphy$) for all observed SNPs in a sample of 8 individuals (out of 512 in the original dataset) of African descent.
-            If they are less mutations observed than expected, this class is thus undergoing purifying selection.
-            Panel B: The site-frequency spectrum (SFS) represents the proportion of mutations (y-axis) with a given number of derived alleles in the population (x-axis).
-            SFS are drawn for a random sample of 16 alleles (mean in solid line and standard deviation in filled color) for each class of selection and for synonymous mutations which are supposedly neutral (black).
-            At high frequencies, supposedly severally deleterious mutations are underrepresented.
-            Panel D.
-For each class of selection (and for the set of all non-synonymous mutations), information from the SFS and the distribution of fitness effects are combined at the population scale to estimate the proportion of beneficial mutations $\PpolyAdv$, of nearly-neutral mutations $\PpolyNeutral$ and of deleterious mutations $\PpolyDel$.
-        }
-        \label{fig:homo-afr-results}
-    \end{figure*}
-
-    \begin{figure*}[!ht]
-        \centering
-        \includegraphics[width=\textwidth, page=1] {artworks/figure.heatmap}
-        \caption{
-            Reproducibility of results shown in figure~\ref{fig:homo-afr-results} in 28 populations across 6 genera.
-            For each class of selection at the phylogenetic scale ($\Sphyclass \in \{ \divStrongDel, \divDel,  \divWeakDel,  \divWeakAdv, \divAdv \}$, in rows), site-frequency spectra and total number of sites are combined at the population scale to estimate the proportion of beneficial mutations ($\PpolyAdv$) in the top panel, of nearly-neutral mutations ($\PpolyNeutral$) in the middle panel and of deleterious mutations ($\PpolyDel$) in the bottom panel.
-        }.
-        \label{fig:heatmap}
-    \end{figure*}
-
-    \begin{figure*}[!ht]
-        \centering
-        \includegraphics[width=\textwidth, page=1] {artworks/figure.diversity}
-        \caption{
-            Panel A.
-For each population, the proportion of beneficial ($\PpolyAdv$), nearly-neutral ($\PpolyNeutral$) and of deleterious ($\PpolyDel$) mutations estimated at the population scale using all SNPs available.
-            Population are sorted for increased synonymous diversity.
-            Panel B. Proportion of nearly-neutral mutations ($\mathbb{P} [ -1 < \Spop < 1]$ in y-axis), shown as a function of the synonymous diversity (Watterson $\theta_w$ in x-axis).
-            Panel C.
-Proportion of beneficial back-mutations among all beneficial mutations ($\mathbb{P} [ \Sphy > 1  \given  \Spop > 1]$ in y-axis), shown as a function of the synonymous diversity (Watterson $\theta_w$ in x-axis).
-        }
-        \label{fig:diversity}
-    \end{figure*}
-
-    \subsection*{A bridge between phylogenetic and population-genetics}
-    In this study, we first estimated selective effects of mutations inside protein coding sequence, under a model assuming no adaptation at the phylogenetic scale.
-    We then estimated the proportion of beneficial back-mutations, that are not adaptive innovations, and subsequently estimated their proportion among all beneficial mutations at the population scale.
-    Our work confirms that deleterious substitutions have accumulated in mammals and are currently being eliminated, resulting in up to 25\% of beneficial mutations that are not adaptive innovations, but instead are repairing previous deleterious changes.
-
-    At the phylogenetic scale, we have found that we can use mutation-selection codon models to predict the selection coefficient of a mutation ($\Sphy$).
-    However, we so far assumed no changes in effective population size along the phylogeny while it has been established that population size changes have a major effect on selection dynamics~\cite{lanfear_population_2014, jones_shifting_2017, platt_protein_2018}.
-    Mutation-selection models with changes in effective population sizes along the phylogeny have been developed~\cite{latrille_inferring_2021}, but are, for the moment, too computational intensive to be performed genome-wide.
-    Hybrid mutation-selection and phenomenological codon models could provide a way forward to integrate site-specific selection and branch-specific drift~\cite{brevet_reconstructing_2021a}.
-    As for the estimate of selection, SIFT scores based on amino acid alignments across species have also been found to be informative of the selection pressure exerted at the population scale~\cite{chen_hunting_2021}.
-    We also concur that mutations with a low SIFT score are more deleterious in the different populations, and conversely mutations with a high SIFT scores are more beneficial (supp.\ mat.\  section SIFT scores).
-    In practice, SIFT scores are more coarse grained, with for example a bulk of mutations with a score of 1.0 (the highest), and it does not provide a boundary between beneficial and deleterious mutations.
-    On the contrary, mutation-selection codon models are genuinely taking into account the tug-of-war between scarce beneficial mutations likely to reach fixation and a bulk of deleterious mutations eventually reaching fixation due to their sheer mass.
-    As such, these models can be used as a null model to predict the expected rate of evolution of proteins~\cite{spielman_relationship_2015, dosreis_how_2015} under a stable fitness landscape.
-    A departure from this null model of evolution would indicate that proteins are evolving under a changing fitness landscape~\cite{cvijovic_fate_2015, rodrigue_detecting_2017, tamuri_mutationselection_2021} and is a signal of pervasive adaptive evolution~\cite{rodrigue_bayesian_2021} or of pervasive epistasis~\cite{rodrigue_detecting_2017}.
-    As such, a stable fitness landscape as a null model is thus statistically more powerful to detect adaptation than assuming that the null model is neutral evolution.
-    Taken together, mutation-selection models are a mandatory tool in evolutionary biology to detect and quantify adaptation at the phylogenetic scale, while acknowledging the contribution of beneficial back-mutations.
-
-    At the population scale ($\Spop$), our results also rely on some hypothesis and thresholds.
-    We first defined the threshold to consider a mutation beneficial ($\Spop$ or $\Sphy$ greater than one), such that nearly-neutral mutations that are only slightly-beneficial are discarded.
-    To also consider slightly-beneficial mutations, we performed the same analysis with a threshold of zero.
-    With this methodology, the proportion of back-mutations among all beneficial mutations increases and ranges from 12 to 45\% across populations(table~S4).
-    Second, there is no consensus on the expected shape of the distribution of fitness effects (DFE)~\cite{welch_divergence_2008, bataillon_effects_2014}, although it has been found to be reliably constant between closely related species~\cite{castellano_comparison_2019}.
-    We used a model that allowed the inference of a continuous DFE by modelling the negative side of the DFE as a gamma distribution, and the positive side as an exponential distribution with a mean greater than one.
-    To control for the uncertainty of the underlying DFE, we also performed our analysis assuming a discretized DFE with 5 categories of selection coefficients, and the proportion of back-mutations among all beneficial mutations with this DFE ranges from 3 to 20\% across populations (table~S5).
-    Consequently, even though our general framework contrasting the phylogenetic and population scale is theoretically consistent, we acknowledge that estimating the proportion of back-mutations among all beneficial ones is dependent on the assumption for the underlying DFE at the population scale and the threshold used to define a beneficial mutation.
-    As a result, further work are required to investigate the shape of the DFE at the population scale.
-    Notably, DFE estimated at the mammalian scale (fig.~\ref{fig:homo-afr-results}A) have a negative mode (around $\Sphy=-5$), consistent with experimental DFEs obtained by mutation accumulation (fig.~S10).
-    Contrarily, continuous DFEs estimated at the population scale have by definition a mode at 0.
-    We argue that methods estimating DFE at the population scale should as a result assume a mode shifted toward negative values of $\Spop$.
-
-    Aside from methodological limitations, the mammalian case study might also not be representative of other clades.
-    Indeed, mammals have relatively small long term population sizes, which allow large amounts of deleterious mutations to be fixed, and thus, there are a lot of opportunities for beneficial back-mutations to arise.
-    It would thus be of great interest to reproduce our experiment with other clades, such as \textit{Drosophila} or birds which tend to have higher effective population size.
-    It would also be interesting to have access to more shallow but wider phylogenies to estimate fitness landscapes at short time-scales.
-
-    From a structural biology perspective, we have found that proteins are not optimal for their fitness, which has been proved for their kinetics and thermodynamics~\cite{hartl_compensatory_1996, taverna_why_2002, goldstein_evolution_2011}.
-    In this context of suboptimal fitness, compensatory mutations can repair damage caused by deleterious mutations at another loci and generate a widespread signal of positive selection~\cite{hartl_compensatory_1996, pollock_strong_2014, starr_epistasis_2016}.
-    In our study we focused on mutations toward a more optimal amino-acid at a given site, not accounting for compensatory mutations since we assumed a model of fitness landscape without epistasis, where site-specific amino-acid profiles are independent of one another.
-    As shown in other studies, these models without epistasis provide a reasonable estimate of average fitness profiles~\cite{youssef_consequences_2020}.
-    But most importantly, we argue that our estimation of the amount of beneficial back-mutations is an underestimation, and that accounting for compensatory mutations by means of epistasis would mechanically increase our estimate.
-    Indeed, a fluctuating fitness landscape due to an external forces (i.e.~changes in environment) results in an acceleration of the rate of evolution~\cite{rodrigue_detecting_2017, rodrigue_bayesian_2021}, which generates epistatic mutations that are immediately beneficial~\cite{gong_epistatically_2014}.
-    In contrast, pervasive epistasis generates the opposite pattern, an entrenchment~\cite{goldstein_evolutionary_2004, goldstein_nonadaptive_2015} resulting in a slowing down of the rate evolution~\cite{rodrigue_detecting_2017, patel_epistasis_2022} or a standstill~\cite{youssef_evolution_2022}.
-    In other words, under pervasive epistasis, finding empirical evidence for beneficial back-mutations is harder since restoring mutations become less and less likely to occur over time~\cite{goldstein_nonadaptive_2015, goldstein_sequence_2017, park_epistatic_2022}.
-    As our study shows that beneficial back-mutations should not be overlooked, we argue that both beneficial back-mutations and compensatory mutations play an important role in preventing our genome from collapsing under a mutation load.
-
-    In conclusion, we showed that by integrating genome-wide datasets at the phylogeny and the population scale, it is possible to estimate the proportion of beneficial mutations repairing existing functions instead of generating adaptive innovations.
-    This study at the interface between phylogenetic and population-genetics thus provide a step toward an integration of different scales necessary to decipher the combined effects of mutation, selection and drift on genome evolution.
-    We argue that our approach is general and our methodology can be readily applied to different estimations of fitness landscape at the phylogenetic scale, and different models and methods estimating distribution of fitness effects at the population scale.
-
-%TC:ignore
-    \section*{Acknowledgements}
-    \label{sec:acknowledgment}
-    We gratefully acknowledge the help of Mélodie Bastian, Nicolas Lartillot and Laurent Duret for their advice and reviews concerning this manuscript.
-    This work was performed using the computing facilities of the CC LBBE/PRABI\@.
-    This study makes use of data generated by the NextGen Consortium.
-    The European Union’s Seventh Framework Programme (FP7/2010-2014) provided funding for the project under grant agreement no 244356 - “NextGen”.
-    \textbf{Funding:}
-    Université de Lausanne; Agence Nationale de la Recherche, Grant ANR-19-CE12-0019 / HotRec.
-    \textbf{Author contributions:}
-    Original idea: T.L.\ and J.J.;
-    Model conception: T.L., J.J.\ and N.S.;
-    Code: T.L.;
-    Data analyses: T.L.\ and J.J.;
-    Interpretation: T.L., J.J., D.A.H.\ and N.S.;
-    First draft: T.L.\ and J.J.;
-    Editing and revisions: T.L., J.J., D.A.H.\ and N.S.
-    Project management and funding: N.S\@.
-    \textbf{Competing interests:}
-    The authors declare no conflicts of interest.
-    \textbf{Data and materials availability:}
-    Snakemake pipeline, analysis scripts and documentation are available at \href{https://github.com/ThibaultLatrille/SelCoeff}{github.com/ThibaultLatrille/SelCoeff}.
-
-    \section{Materials \& Methods}
-    \label{sec:methods}
-
-    \subsection{Phylogenetic dataset}
-
-    Protein-coding DNA sequences alignments in placental mammals and their corresponding gene trees are from the \href{https://www.orthomam.univ-montp2.fr}{OrthoMaM} database, and processed as in \textcite{latrille_genes_2022}.
-    OrthoMaM contains a total of $116$ mammalian reference sequences in v10c~\cite{ranwez_orthomam_2007, douzery_orthomam_2014, scornavacca_orthomam_2019}.
-    Genes located on the X, Y chromosomes and the mitochondrial genome were discarded from the analysis, because the level of polymorphism, which is necessary in the population-based analyses, is expected to be different in these three genomic regions.
-    Sequences of species for which we used population-level polymorphism (see below), as well as their sister species, were removed from the analysis to ensure independence between the data used in the phylogenetic and population scales.
-    Altogether, our genome-wide dataset contains $14,509$ protein-coding DNA sequences for at most $87$ sequences of placental mammals.
-
-    \subsection{Selection coefficient ($\Sphy$) in phylogeny-based method}
-    \label{subsec:s-phylogeny-method}
-    One of the most used methods to predict selective effects is SIFT (Sort Intolerant From Tolerant), which reliably detects deleterious mutations in many taxa~\cite{ng_sift_2003, vaser_sift_2016}.
-    However, SIFT scores are not interpretable as a selection coefficient.
-    Moreover, SIFT scores do not account for some key processes that can influence the abundance of an amino-acid in an alignment.
-    For instance, it does not take into account phylogenetic inertia, mutation biases, GC-biased gene conversion, or mutational paths.
-    Here, we analyzed the phylogenetic level data using mutation-selection models.
-    These models assume that the protein-coding sequence are at mutation-selection balance under a fixed fitness landscape characterized by a fitness vector over the $20$ amino acid at each site~\cite{yang_mutationselection_2008, halpern_evolutionary_1998, rodrigue_mechanistic_2010}.
-    Mathematically, the rate of non-synonymous substitution from codon $a$ to codon $b$ ($q_{a \mapsto b}^{(i)}$) at site $i$ of the sequence is equal to the rate of mutation of the underlying nucleotide change ($\mu_{a \mapsto b}$) multiplied by the scaled probability of fixation of the mutation ($\proba_{a \mapsto b}^{(i)}$).
-    The probability of fixation depends on the difference of scaled fitness of the amino acid encoded by the mutated codon ($F_b^{(i)}$) and the amino acid encoded by the original codon ($F_a^{(i)}$) at site $i$~\cite{wright_evolution_1931, fisher_genetical_1930}.
-    The rate of substitution from codon $a$ to $b$ at a site $i$ is thus:
-    \begin{equation}
-        \begin{dcases}
-            q_{a \mapsto b}^{(i)} & = 0 \text{ if codons $a$ and $b$ are more than one mutation away,} \\
-            q_{a \mapsto b}^{(i)} & = \mu_{a \mapsto b} \text{ if codons $a$ and $b$ are synonymous,} \\
-            q_{a \mapsto b}^{(i)} & = \mu_{a \mapsto b} \dfrac{F_b^{(i)} - F_a^{(i)}}{1 - \e^{F_a^{(i)} - F_b^{(i)}}} \text{ if codons $a$ and $b$ are non-synonymous}.
-        \end{dcases}
-    \end{equation}
-    Fitting the mutation-selection model on a multi-species sequence alignment leads to an estimation of the mutation rate matrix ($\UniDimArray{\mu}$) as well as the 20 amino acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$.
-    The selection coefficient for a mutation from codon $a$ to codon $b$ at site $i$ is defined :
-    \begin{equation}
-        \Sphy^{(i)} (a \mapsto b) = \Delta F^{(i)} = F^{(i)}_{b} - F^{(i)}_{a}.
-    \end{equation}
-    %In the manuscript and the following material, the source ($a$) and target ($b$) codons as well as the site ($i$) are implicit and thus never explicitly written.
-    We used the Bayesian software \textit{BayesCode} (\url{https://github.com/ThibaultLatrille/bayescode}) to estimate the selection coefficients for each protein-coding genes in the mammal dataset.
-    We ran the Markov chain Monte-Carlo (MCMC) algorithm implemented in BayesCode for $2,000$ generations as described in \textcite{latrille_genes_2022}.
-    For each gene, after discarding a burn-in period of $1,000$ generations of MCMC, we obtained posterior mean estimates (over the $1,000$ generations left of MCMC) of the mutation rate matrix ($\UniDimArray{\mu}$) as well as the 20 amino acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$.
-
-    \subsection{Polymorphism dataset}
-    \label{subsec:polymorphism-dataset}
-
-    The genetic variants representing the population level polymorphism were obtained from the following species and respective available datasets: \textit{Equus caballus} (EquCab2 assembly in the EVA study PRJEB9799~\cite{alabri_whole_2020}), \textit{Bos taurus} (UMD3.1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}), \textit{Ovis aries} (Oar\_v3.1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}), \textit{Capra Hircus} (CHIR1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}, converted to ARS1 assembly with dbSNP identifiers\cite{sherry_dbsnp_2001}), \textit{Chlorocebus sabaeus} (ChlSab1.1 assembly in the EVA project PRJEB22989~\cite{svardal_ancient_2017}), \textit{Homo sapiens} (GRCh38 assembly from the 1000-genome project~\cite{consortium_integrated_2012, the1000genomesprojectconsortium_global_2015}).
-    In total, we analyzed 28 populations across the 6 different species with polymorphism data.
-    The data was processed as described in \textcite{latrille_genes_2022}.
-
-    Genetic variants that were not found within a gene were not used in further analyses.
-    We also did not analyzed insertions and deletions and focused only on Single Nucleotide Polymorphisms (SNPs) with a single mutant allele, while stop codon variants were also discarded.
-    First, each SNP (chromosome, position, strand) in the focal species was matched to its relative position (chromosome, position, strand) in the protein-coding DNA alignment by first converting the genomic positions to relative position in the coding sequence (CDS) using gene annotation files (GTF format) downloaded from Ensembl (\url{ensembl.org}).
-    We then verified that the SNP downloaded from Ensembl were matching the reference in the CDS in FASTA format.
-    Second, the relative position in the CDS was converted to position in the multi-species sequence alignment (containing gaps) from OrthoMaM database (see section \ref{subsec:s-phylogeny-method}) by doing a global pairwise alignment, using the Biopython function pairwise2, between the CDS fasta and the sequence found in the alignment.
-    This conversion from genomic position to alignment position was only possible when the assembly used for SNP calling was the same as the one used in the alignment, the GTF annotations and the FASTA sequences.
-    SNPs were polarized using the $3$ closest outgroups found in the OrthoMam alignment with est-usfs v2.04~\cite{keightley_inferring_2018}.
-
-    \subsection{Mutational opportunities}
-    \label{subsec:nunber-of-sites}.
-    For each population with polymorphism data available, the polarized SNPs (ancestral and derived alleles) were used to reconstruct the ancestral DNA sequence, containing only substitutions and no segregating polymorphisms.
-    If a SNP was still segregating in the population, the ancestral version of the SNP was used.
-    However, if the derived allele was shared by all individuals in the population, the allele was considered fixed and the derived allele of the SNP was used as the ancestral.
-    This ancestral genome is different from the reference genome as it accounts for the variability present in the population analysed.
-    From this reconstructed ancestral genome at the base of the population genealogy, all possible mutations were computed, weighted by the mutation rate between nucleotide ($\mu$), which was estimated at the phylogenetic scale.
-    The total mutation rate for synonymous mutations, called $\mu_{\textrm{syn}}$, was estimated as the sum across the whole genome.
-    Similarly, the total mutation rate for each class of selection $\Sphyclass$, called $\mu\left( \Sphyclass \right)$, was estimated as the sum across all non-synonymous mutations if their selection coefficient at the phylogenetic scale ($\Sphy$) was in the class $\Sphy \in \Sphyclass$ (e.g.
-$\Sphyclass = \divAdv$).
-    Finally, the mutational opportunities ($L \left( \Sphyclass \right)$) for each class of selection coefficient ($\Sphyclass$) was finally computed as the total number of sites across the genome ($L_{tot}$) weighted by the ratio of the aggregated mutations rates falling in the class ($\mu\left( \Sphyclass \right)$) over the total mutation rate for all possible mutations ($\mu_{tot}$) as:
-    \begin{align}
-        L \left( \Sphyclass \right) &= L_{tot} \frac{\mu\left( \Sphyclass \right)}{\mu_{tot}}, \\
-        L_{\textrm{syn}} &= L_{tot} \frac{\mu_{\textrm{syn}}}{\mu_{tot}}.
-    \end{align}
-
-    \subsection{Substitution mapping in the terminal branch}
-    \label{subsec:substitution-mapping-in-the-terminal-branch}
-    For each gene and for each population with polymorphism data available, the genome at the base of the population genealogy was reconstructed (see section \ref{subsec:nunber-of-sites}).
-    We used the ancestral genome reconstructed at the base of the population genealogy and the $3$ closest outgroups found in the OrthoMam alignment to infer the ancestral protein-coding DNA sequences for each node of the 4-taxa tree by applying the M5 codon model (gamma site rate variation) as implemented in FastML.v3.11~\cite{ashkenazy_fastml_2012}.
-    All polarized codon substitutions were then obtained by comparing the ancestral protein-coding DNA sequences before the split to the sister species (closest outgroup) to the genome at the base of the population genealogy.
-    We considered \textit{Ceratotherium simum simum} as \textit{Equus caballus} sister species; \textit{Bison bison bison} as \textit{Bos taurus} sister species; \textit{Pantholops hodgsonii} as \textit{Ovis aries} sister species; \textit{Pantholops hodgsonii} as \textit{Capra Hircus} sister species; \textit{Macaca mulatta} as \textit{Chlorocebus sabaeus} sister species and finally we considered \textit{Pan troglodytes} as \textit{Homo sapiens} sister species.
-    The selection coefficient ($\Sphy$) of each substitution was then obtained by comparing the difference in amino acid fitnesses for each polarized non-synonymous codon substitution, by referring to the site-specific fitness profile obtained in the phylogeny-based method (see~\ref{subsec:s-phylogeny-method}).
-    Finally, the rate of non-synonymous over synonymous substitution for a given class of selection coefficient ($\Sphyclass$) was computed as:
-    \begin{align}
-        \dn \left( \Sphyclass \right) &= \dfrac{D\left( \Sphyclass \right)}{L \left( \Sphyclass \right)}, \\
-        \ds &= \dfrac{D_{\textrm{syn}}}{L_{\textrm{syn}}},
-    \end{align}
-    where $D \left( \Sphyclass \right) $ was the number of non-synonymous substitutions in the class $\Sphyclass$, $D_{\textrm{syn}}$ was the number of synonymous substitutions across the genome, while $L \left( \Sphyclass \right)$ and $L_{\textrm{syn}}$ were the number of non-synonymous and synonymous mutational opportunities as defined in section \ref{subsec:nunber-of-sites}.
-    The fraction of non-adaptive beneficial substitutions $R(\dnds)$ was computed as the ratio between the difference in the numbers of beneficial substitutions ($\dnds$), which were due to beneficial back-mutations, and the estimated divergence when we removed beneficial back-mutations $\dn (\Sphy < 0) / \ds$, over $\dnds$.
-    Of note, the quantities $R(\dn)$ and $R(\dnds)$ are equivalent due to simplification of the factor $\ds$:
-    \begin{equation}
-        R(\dnds) = \dfrac{\dnds - \dn(\Sphy < 0) / \ds}{\dnds} = \dfrac{\dn - \dn(\Sphy < 0)}{\dn} = R(\dn)
-    \end{equation}
-
-    \subsection{Selection coefficient ($\Spop$) in population-based method}
-    \label{subsec:s-polymorphism-method}
-    The probability to sample an allele at a given frequency (before fixation or extinction) is informative of its scaled selection coefficient at the population scale ($\Spop$).
-    Pooled across many sites, the site-frequency spectrum (SFS) provides therefore information on the underlying $\Spop$ of mutations.
-    However, estimating a single $\Spop$ for all sampled mutations is biologically unrealistic and a distribution of fitness effects (DFE) of mutations is usually assumed~\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009}.
-    We used the software polyDFE~\cite{tataru_inference_2017, tataru_polydfe_2020} that implemented a mixture of a $\Gamma$ and Exponential distributions to model the DFE of non-synonymous mutations, while synonymous mutations are considered neutral.
-    The model estimates the parameters $\DelMean$ , $b$, $p_b$ and $\AdvMean$ for non-synonymous mutations as:
-    \begin{equation}
-        \phi \left( \Spop; \DelMean , b, p_b, \AdvMean \right) =
-        \begin{dcases}
-            \left( 1 - p_b \right) f_{\Gamma}(-\Spop; -\DelMean, b) & \text{ if $\Spop \leq 0$,} \\
-            p_b f_{e}(\Spop; \AdvMean) & \text{ if $\Spop > 0$,} \\
-        \end{dcases}
-    \end{equation}
-    where $\DelMean \leq -1 $ was the estimated mean of the DFE for $\Spop \leq 0$,
-    $b \geq 0.4$ was the estimated shape of the $\Gamma$ distribution,
-    $0 \leq p_b \leq 1$ was the estimated probability that $\Spop > 0$,
-    $\AdvMean \geq 1$ wass the estimated mean of the DFE for $\Spop > 0$,
-    and $f_{\Gamma}(x; m, b)$ was the density of the $\Gamma$ distribution with mean m and shape b, while $f_{e}(x; m)$ is the density of the Exponential distribution with mean $m$.
-    Once the DFE was fitted to the data, the proportion of beneficial ($\PpolyAdv$), nearly-neutral ($\PpolyNeutral$) and deleterious mutations ($\PpolyDel$) were given as:
-    \begin{align}
-        \PpolyAdv &= p_b \int_{1}^{+\infty} f_{e}(\Spop; \AdvMean) \der \Spop,  \label{eq:polyProbaAdv} \\
-        \PpolyNeutral &= p_b \int_{0}^{1} f_{e}(\Spop; \AdvMean) \der \Spop + \left( 1 - p_b \right) \int_{0}^{1} f_{\Gamma}(\Spop; -\DelMean, b) \der \Spop, \\
-        \PpolyDel &= \left( 1 - p_b \right) \int_{1}^{+\infty} f_{\Gamma}(\Spop; -\DelMean, b) \der \Spop. \label{eq:polyProbaDel}
-    \end{align}
-
-    PolyDFE required one SFS for non-synonymous mutations and one for synonymous mutations (neutral expectation), as well as the number of sites on which each SFS was sampled.
-    For populations containing more than $8$ individuals, the site-frequency spectrum (SFS) was subsampled down to $16$ chromosomes ($8$ diploid individuals) without replacement (hyper-geometric distribution) to alleviate the effect of different sampling depth in the 28 populations.
-    Altogether, for each class of selection ($\Sphyclass$) of non-synonymous SNPs (or for all SNPs), we thus estimated the parameters of the DFE $\left( \Spop; \DelMean , b, p_b, \AdvMean \right)$ using maximum likelihood with polyDFE from the number of sites and the SFS obtained by aggregating all the SNPs in the selection class.
-    Once fitted to the data, the parameters of the DFE $\left( \Spop; \DelMean , b, p_b, \AdvMean \right)$ were used to compute $\PpolyAdv$, $\PpolyNeutral$, $\PpolyDel$ using eq.~\ref{eq:polyProbaAdv}-\ref{eq:polyProbaDel}.
-
-    Using Bayes theorem, we obtained the probability for a beneficial mutation to be a back-mutation by estimating the probability that a mutation was a back-mutation ($\divAdv$) given that it was beneficial ($\polyAdv$), as:
-    \begin{equation}
-        \proba \left[\divAdv \given \polyAdv\right] = \frac{\proba \left[\polyAdv \given \divAdv\right] \times \proba\left[\divAdv\right]}{\PpolyAdv},
-        \label{eq:bayes}
-    \end{equation}
-    where $\PpolyAdv$ was computed from all SNPS, $\proba \left[\polyAdv \given \divAdv\right]$ was obtained from the set of SNPs in the class $\Sphyclass = \divAdv$, and $\proba\left[\divAdv\right]$ was the probability for a new mutation to be inside the class $\divAdv$, thus computed as:
-    \begin{equation}
-        \proba\left[\divAdv\right] = \frac{L\left( \Sphyclass = \divAdv \right)}{L_{tot}},
-        \label{eq:proba-dfe-mutsel}
-    \end{equation}
-
-    \printbibliography
-\end{document}
-%TC:endignore

### 2023-03-13 manuscript/main.tex
Version for corrections.

@@
 \definecolor{DARKBLUELINK}{HTML}{0B0080}
+\definecolor{LIGHTGREY}{gray}{0.9}
 \PassOptionsToPackage{hyphens}{url}
@@
 \usepackage{lineno}
+\usepackage{tabu}
+\usepackage{hhline}
+\usepackage{multicol,multirow,array}
+\usepackage{etoolbox}
+\usepackage{booktabs}
+\usepackage{makecell}
 
@@
 \newcommand{\UniDimArray}[1]{\bm{#1}}
-\newcommand{\BiDimArray}[1]{\bm{#1}}
-\DeclareMathOperator{\E}{\mathbb{E}}
-\DeclareMathOperator{\Var}{\textrm{Var}}
-\newcommand{\der}{\textrm{d}}
-\newcommand{\e}{\textrm{e}}
-\newcommand{\avg}[1]{\left< #1 \right>} % for average
-\newcommand{\Ne}{N_{\textrm{e}}}
+\newcommand{\der}{\text{d}}
+\newcommand{\e}{\text{e}}
+\newcommand{\Ne}{N_{\text{e}}}
 \newcommand{\proba}{\mathbb{P}}
-\newcommand{\pfix}{\proba_{\textrm{fix}}}
+\newcommand{\pfix}{\proba_{\text{fix}}}
 \newcommand{\dn}{d_N}
@@
 \newcommand{\Sphyclass}{\mathcal{C}}
-\newcommand{\SphyMean}{\overline{\Sphy}}
-\newcommand{\divStrongDel}{\Sphy < -3}
-\newcommand{\divDel}{-3 < \Sphy < -1}
-\newcommand{\divWeakDel}{-1 < \Sphy < 0}
-\newcommand{\divWeakAdv}{0 < \Sphy < 1}
-\newcommand{\divAdv}{ \Sphy > 1}
-\newcommand{\PdivStrongDel}{\proba \left[ \divStrongDel \right]}
-\newcommand{\PdivDel}{\proba \left[ \divDel \right]}
-\newcommand{\PdivWeakDel}{\proba \left[ \divWeakDel \right]}
-\newcommand{\PdivWeakAdv}{\proba \left[ \divWeakAdv \right]}
-\newcommand{\PdivAdv}{\proba \left[ \divAdv \right]}
 \newcommand{\given}{\mid}
 \newcommand{\Spop}{S}
-\newcommand{\SpopMean}{\overline{\Spop}}
-\newcommand{\polyDel}{\Spop < -1}
-\newcommand{\polyNeutral}{-1 < \Spop < 1}
-\newcommand{\polyAdv}{ \Spop > 1}
-\newcommand{\PpolyDel}{\proba \left[ \polyDel \right]}
-\newcommand{\PpolyNeutral}{\proba \left[ \polyNeutral \right]}
-\newcommand{\PpolyAdv}{\proba \left[ \polyAdv \right]}
+\newcommand{\PpolyDel}{\proba [ \Spop^{\text{d}}]}
+\newcommand{\PpolyNeutral}{\proba [ \Spop^{\text{n}} ]}
+\newcommand{\PpolyAdv}{\proba [ \Spop^{\text{b}} ]}
 \newcommand{\AdvMean}{\beta_b}
@@
 \renewcommand{\baselinestretch}{1.5}
+\renewcommand{\arraystretch}{0.6}
 \linenumbers
+\frenchspacing
 
-\title{Up to 25\% of beneficial mutations in human protein sequences are not adaptive innovations in mammals}
+\title{Mammalian protein-coding genes exhibit widespread beneficial mutations that are not adaptive}
+% Empirical evidence for widespread beneficial mutations that are not adaptive in mammalian genes
 
@@
     \normalsize
-    $^{1}$Université de Lausanne, Lausanne, Switzerland\\
-    $^{2}$Université de Lyon, CNRS, LBBE UMR 5558, Villeurbanne, France \\
+    $^{1}$Department of Computational Biology, Université de Lausanne, Lausanne, Switzerland\\
+    $^{2}$Université de Lyon, Université Lyon 1, CNRS, VetAgro Sup, Laboratoire de Biométrie et Biologie Evolutive, UMR5558, Villeurbanne, France \\
     \texttt{\href{mailto:thibault.latrille@ens-lyon.org}{thibault.latrille@ens-lyon.org}} \\
@@
     \begin{abstract}
-        Mutations can be beneficial by bringing an innovation to their bearer, allowing them to adapt to changes in environments or in selective pressure.
-However, mutations can also be beneficial because they are repairing previous deleterious changes, simply restoring existing functions.
-In this study, we first estimated selective effects of mutations inside mammalian protein coding sequences, under a model assuming no adaptation at the phylogenetic scale.
-We then estimated the proportion of beneficial mutations that are not adaptive innovations among all beneficial mutations at the population scale.
-Our work confirms that deleterious substitutions have accumulated in mammals and are currently being eliminated.
-In modern humans, it results in around 25\% of beneficial mutations that are not adaptive innovations, but instead are repairing previous deleterious changes.
+        Mutations can be beneficial by bringing an innovation to their bearer, allowing them to adapt to changes in their environments.
+However, mutations can also be beneficial because they are reverting previous deleterious changes, simply restoring pre-existing functions.
+By integrating phylogenomic and population data in mammals we estimated the contribution of beneficial back-mutations to molecular evolution, which has remained widely overlooked to this day.
+Applying a mutation-selection model to mammalian conserved protein-coding genes, we estimated amino-acid fitness landscapes.
+Assuming no changes in these fitness landscapes, any beneficial mutation is necessarily a back-mutation.
+We confirm that these beneficial back-mutations are positively selected in extant populations and demonstrate that a substantial part of ongoing positive selection is not driven by adaptation to environmental change in mammals.
     \end{abstract}
 
-    \keywords{Adaptation \and Back-mutation \and Phylogenetics \and Population-genetics \and Codon models }
+    \keywords{Adaptation \and Back-mutations \and Phylogenetics \and Population-genetics \and Codon models }
 
-    Adaptation is considered one of the main processes shaping the diversity of forms and functions across the tree of life~\cite{darwin_origin_1859}.
-    It enables species to access new ecological niches and also respond to changes in their environment~\cite{darwin_origin_1859} [NS: maybe cite Losos or some key papers on ecological speciation rather than Darwin twice].
-    In evolution, adaptation is tightly linked to the notion of change at the level of the environment and to species responding to this change~\cite{merrell_adaptive_1994}.
-    The process of adaptation leaves marks of accelerated evolution in genomes since mutations that are beneficial under new conditions fix faster than neutral mutations (fig.~\ref{fig:fitness-landscape}A).
-    The signature of an accelerated rate of substitutions, defined as the rate of mutation times the probability of fixation, can thus be interpreted as a sign of adaptation~\cite{mcdonald_adaptative_1991, smith_adaptive_2002, welch_estimating_2006}.
-    The current availability of large-scale genomic data and the development of theoretical models have allowed to detect and quantify adaptation across genes and lineages, and these analyses have become common practice in evolutionary biology~\cite{yang_statistical_2000, eyre-walker_genomic_2006, moutinho_variation_2019} [NS: cite the paper by Anna Marcionetti here].
-    Although these approaches have led to a better understanding of the processes determining the rates of molecular evolution, they have had the effect of associating beneficial mutations with adaptive evolution, while disconnecting them from the notion of change defining adaptation.
-    We argue that we should limit the use of adaptive mutations to those that are associated with adaptation as such and dissociate beneficial mutations from adaptive mutations since adaptive evolution is not the only process that can lead to beneficial mutations~\cite{charlesworth_other_2007, mustonen_fitness_2009}.
-    We propose here a new approach to identify the mechanisms underlying the origin of beneficial mutations.
-    In particular, we suggest that many beneficial mutations are not adaptive, but are rather restoring ancestral states of higher fitness.
-    We used large-scale genomic data to integrate analyses at both the phylogenetic and population scales to differentiate between truly adaptive mutations from mutations restoring the ancestral fitness.
-    Our results show that up to a quarter of beneficial mutations across mammal species are not driven by adaptive innovations, but rather compensate the effect of ancestral mutations to recover the optimal state of the species.
+    Adaptation is considered one of the main processes shaping the diversity of forms and functions across the tree of life\cite{darwin_origin_1859}.
+    In evolution, adaptation is tightly linked to the notion of environmental change and to species responding to this change\cite{merrell_adaptive_1994, gavrilets_adaptive_2009}.
+    For adaptation to take place, there needs to be variation within populations, which at the molecular level mostly appears via mutations in the DNA sequence.
+    While neutral mutations will have no impact on the fitness of an individual, deleterious mutations have a negative effect and beneficial mutations lead their bearer toward a higher fitness.
+    Compared to a neutral mutation, a beneficial mutation is thus more likely to reach fixation in the population, resulting in a substitution at the species level.
+    Upon environmental change, adaptive beneficial mutations toward new fitness optima are more likely to rise in frequency, resulting in an increased substitution rate (fig.~\ref{fig:fitness-landscape}A).
+    Altogether, an accelerated substitution rate is thus commonly interpreted as a sign of adaptation\cite{mcdonald_adaptative_1991, smith_adaptive_2002, welch_estimating_2006}.
+    The current availability of large-scale genomic data and the development of theoretical models have enabled us to detect and quantify acceleration of substitution rates across genes and lineages, and these analyses have become common practice in evolutionary biology\cite{yang_statistical_2000, eyre-walker_genomic_2006, moutinho_variation_2019}.
+    These approaches have led to a better understanding of the processes determining the rates of molecular evolution.
+    However, they have had the collateral effect of associating beneficial mutations with adaptive evolution when, in fact, adaptive evolution is not the only process that can lead to beneficial mutations\cite{charlesworth_other_2007, mustonen_fitness_2009}.
 
-    In a constant environment, if a population is already adapted to these conditions, a deleterious mutation in an individual can reach fixation in the population by genetic drift~\cite{Ohta1992}.
-    Subsequently, a new mutation that is restoring the ancestral fitness will thus be beneficial (fig.~\ref{fig:fitness-landscape}B), even though no change in the environment occurred~\cite{hartl_compensatory_1996, sella_application_2005, mustonen_fitness_2009, cvijovic_fate_2015}.
-    The restoration of the ancestral fitness can happen at a different locus than the initial mutation, in which case it is referred to as a compensating [NS: ou compensatory ?] mutation~\cite{hartl_compensatory_1996, mustonen_fitness_2009}.
-    However, if the restoration of the ancestral fitness happens at the same locus than the initial mutation, in which case it is referred to as a beneficial back-mutation~\cite{piganeau_estimating_2003, charlesworth_other_2007}.
-    In this study, we focus on the latter case.
-    While compensatory mutations induce genetic changes at the sequence level, and thus genetic diversification, beneficial back-mutations reduce the genetic diversity and do not contribute to genetic innovation.
-    They merely cancel the effect of the previous deleterious changes.
-    As a consequence, not all beneficial mutations contribute to genetic innovation and truly adaptive evolution can only be correctly estimated if we can account for the number of beneficial back-mutations~\cite{keightley_what_2010, rice_evolutionarily_2015}.
-    % Philosophically, our distinction between beneficial back-mutations and adaptation can appear to be far-fetched, and one can argue that beneficial back-mutations is adaptation to its own deteriorating genome.
-    % However, there is a difference between adapting to a mutation, for instance by means of a compensatory mutation elsewhere, and cancelling the mutation, by means of a substitution on the misfit amino-acid.
+    In a constant environment, a deleterious mutation can reach fixation in the population by genetic drift\cite{Ohta1992}.
+    Subsequently, a new mutation restoring the ancestral fitness will thus be beneficial (fig.~\ref{fig:fitness-landscape}B), even though no change in the environment has occurred\cite{hartl_compensatory_1996, sella_application_2005, mustonen_fitness_2009, cvijovic_fate_2015}.
+    The restoration of the ancestral fitness can happen with a mutation occurring either at a different locus from that of the initial mutation, in which case it is referred to as a compensatory mutation\cite{hartl_compensatory_1996, mustonen_fitness_2009}, or at the same locus of the initial mutation, referred to as a beneficial back-mutation\cite{piganeau_estimating_2003, charlesworth_other_2007}.
+    Now, while compensatory mutations induce genetic changes at the sequence level, and thus genetic diversification, beneficial back-mutations reduce the inter-specific genetic diversity and do not contribute to genetic innovation.
+    Although beneficial back-mutations were considered negligible in the enunciation of the nearly-neutral theory by Tomoko Ohta\cite{Ohta1992}, their importance during a population size expansion has been acknowledged more recently\cite{charlesworth_other_2007}.
+    However, differentiating between an adaptive mutation and a beneficial back-mutation has remained challenging\cite{chi_detecting_2020}.
+    In this study, we seek to find empirical evidence for beneficial back-mutations and to test long-standing questions in molecular evolution such as how common are beneficial back-mutations, and
+    what is the probability for any beneficial mutation observed in current populations to be a back-mutation.
+    By addressing these questions we provide novel insight on the process of adaptation and, more broadly, on how natural selection has affected protein-coding DNA sequences throughout evolution.
 
-    %For an individual carrying a beneficial mutation, whether this mutation is a new innovation responding to a change in environment or a beneficial back-mutation is indistinguishable~\cite{charlesworth_other_2007}.
-    Given a beneficial mutation, distinguishing whether it is a new innovation responding to a change in environment or a beneficial back-mutation is impossible with only one individual at hand~\cite{charlesworth_other_2007}.
-    This limitation persists at the level of the population, since both types of mutation will result in a positive transmission bias of the beneficial allele.
+    \subsection*{Fitness landscape reconstruction}
+
+    An adaptive mutation responding to a change in the environment or a beneficial back-mutation have equivalent consequences for their bearer\cite{charlesworth_other_2007}.
+    Similarly, at the level of the population, both types of mutations will result in a positive transmission bias of the beneficial allele.
     However, at the macro-evolutionary scale the consequences of these two types of mutations are fundamentally different.
-    While adaptive evolution promotes phenotype diversification (fig.~\ref{fig:fitness-landscape}C), beneficial back-mutations promote phenotype stability and preserve well established biological systems (fig.~\ref{fig:fitness-landscape}D).
-    Additionally, the direction of adaptive evolution is unpredictable because it is caused by an unpredictable change in the environment and, hence, in the underlying fitness landscape~\cite{bazykin_changing_2015}.
-    On the other hand, beneficial back-mutations are predictable if the underlying stable fitness landscape is known because we will expect to see changes from non-optimal amino acids to optimal ones.
-    If we wish to quantify the amount of beneficial back-mutations that have happened along a phylogeny we need to identify the selection coefficients of mutations and to achieve this we require the fitness landscape to be stable and be known.
+    While adaptive mutations promote phenotype diversification (fig.~\ref{fig:fitness-landscape}C), beneficial back-mutations promote phenotype stability and may help preserve well established biological systems (fig.~\ref{fig:fitness-landscape}D).
+    Additionally, the direction of adaptive evolution is unpredictable because it is caused by an unpredictable change in the environment and, hence, in the underlying fitness landscape\cite{bazykin_changing_2015}.
+    On the other hand, beneficial back-mutations are predictable if the underlying stable fitness landscape is known because changes from non-optimal amino acids to optimal ones will be expected.
+    In this context, the mutation-selection framework permits to relate the patterns of substitution along a phylogeny to the underlying fitness landscape\cite{halpern_evolutionary_1998, mccandlish_modeling_2014}.
+    Such mutation-selection models applied to protein coding DNA sequences allow us to estimate relative fitnesses for all amino-acids for each site of the sequence, explicitly assuming that the underlying fitness landscape is stable along the phylogenetic tree\cite{rodrigue_mechanistic_2010, tamuri_estimating_2012, rodrigue_detecting_2017}.
+    Importantly, because mutation-selection models at the phylogenetic scale are based on population-genetics equations, their estimates of fitness effects are directly interpretable as fitness effects for an individual within a population.
+    %These methods account for phylogenetic relationships, the structure of the genetic code and accommodate for underlying mutational biases\cite{rodrigue_mechanistic_2010, tamuri_estimating_2012, latrille_improved_2022}.
 
-    The placental mammals represent an excellent study system to perform this analysis.
-    Having originated ~100 Mya\cite{kumar_timetree_2017}, they diversified quickly.
-    Additionally, we have polymorphism data available for many species\cite{howe_ensembl_2021} and high quality protein-coding DNA alignments across the genome\cite{ranwez_orthomam_2007, scornavacca_orthomam_2019}.
-    By restricting our analysis to protein-coding orthologous genes to all the phylogeny, and further excluding any genes for which there have been claims of pervasive directional selection, we can not only assume a constant fitness landscape for each of them throughout placental mammal evolution, but actually reconstruct the fitness landscape from variable positions within the sequence along the phylogeny.
-    For each gene, we used a codon model of mutation-selection~\cite{halpern_evolutionary_1998, mccandlish_modeling_2014} to obtain relative fitnesses for all amino-acids for each site of the sequence by fitting the model to the multi-species sequence alignment (fig~\ref{fig:method}A) and assuming that the underlying fitness landscape is stable along the phylogenetic tree.
-    %Mutation-selection codon models provide a nearly neutral framework of evolution taking into account non-adaptive processes impacting codon frequency~\cite{halpern_evolutionary_1998, rodrigue_mechanistic_2010, tamuri_estimating_2012, latrille_improved_2022}.
+    Theoretically, we can thus use large-scale genomic data to assess whether the fitnesses estimated at the phylogenetic scale are predictive of the fitness effect at the population scale, for both deleterious and beneficial back-mutations.
+    The placental mammals represent an excellent study system to perform such analysis.
+    Having originated $\sim$100 Mya\cite{kumar_timetree_2017}, they diversified quickly.
+    Additionally, polymorphism data are available for many species\cite{howe_ensembl_2021} as high quality protein-coding DNA alignments across the genome\cite{ranwez_orthomam_2007, scornavacca_orthomam_2019}.
+    By restricting our analysis to protein-coding orthologous genes across all the phylogeny, we restrict our analysis to genes mostly under functional constrains across mammals.
+    For each gene, fitting the mutation-selection model to the multi-species sequence alignment assuming that the underlying fitness landscape is stable along the phylogenetic tree allows obtain relative fitnesses for all amino-acids for each site of the alignment (fig~\ref{fig:method}A).
     From the fitness landscape, we can calculate the scaled selection coefficient $\Sphy$ for any possible amino-acid change at each position.
-    Under this model, a mutation with a positive $\Sphy$ would be driving the current site toward a known fitter amino-acid and would thus be considered as a beneficial back-mutation (fig~\ref{fig:method}B), given the assumed stability of the fitness landscape.
-
-    Having identified which potential amino-acid changes could represent beneficial back-mutations at the phylogenetic scale, we retrieved polymorphism data from 28 populations belonging to 6 genera (\textit{Equus}, \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus} and \textit{Homo}) to assess the presence of beneficial back-mutations at the population scale.
-    We focused on currently segregating mutations within populations and also on substitutions in the terminal lineages, and checked if any of these observed changes where predicted beneficial back-mutations.
-    Essentially, by integrating large scale genomic datasets at both phylogenetic and population scales we have been able to estimate the amount of beneficial back-mutations across the entire exome for 6 different mammalian genera (fig~\ref{fig:method}A-F).
-
-    Our analyses allow us to test long-standing questions in molecular evolution:
-    How common are beneficial back-mutations?
-    Can we identify beneficial back-mutations that have reached fixation recently, and ones that are currently segregating in populations?
-    Are hypothetical beneficial back-mutations effectively beneficial for the individuals carrying them?
-    Furthermore, what is the probability for any beneficial mutation observed in current populations to be a back-mutation?
-    In other words, can we quantify the amount of beneficial mutations that are restoring damaged genomes instead of creating adaptive innovations.
-    By addressing these questions we provide
-    novel insight on how selection is affecting protein-coding DNA sequences.
+    From the selection coefficient, we can classify any mutation as either a deleterious mutation toward a less fit amino-acid ($\Sphy^{\text{d}}$), a nearly-neutral mutation ($\Sphy^{\text{n}}$) or a beneficial back-mutation toward a known fitter amino-acid ($\Sphy^{\text{b}}$).
+    Having identified which potential DNA changes represent beneficial back-mutations (fig~\ref{fig:method}B), we retrieved polymorphism data from 28 populations belonging to 6 genera (\textit{Equus}, \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus} and \textit{Homo}) to assess the presence of beneficial back-mutations at the population scale.
+    We focused on currently segregating mutations within populations and also on substitutions in the terminal branches, and checked if any of these observed changes where beneficial back-mutations (fig~\ref{fig:method}C-E).
+    Essentially, by integrating large scale genomic datasets at both phylogenetic and population scales we have been able to estimate the amount of beneficial back-mutations across the entire exome for 6 different mammalian genera (fig~\ref{fig:method}F-H).
 
@@
         \caption{
-            Panel A and B: at a given site of a protein-coding DNA sequence, the different amino acids (x-axis) have different fitnesses (y-axis).
-            Under a fluctuating fitness landscape (panel A), these fitnesses are changing with time.
-            The protein sequence is always lagging behind the moving target defined by the amino acid fitnesses, and since substitutions are accepted preferentially if they are in the direction of this target, substitutions are on average adaptive.
-            At the phylogenetic scale (panel C), this phenomena promotes phenotype diversification across species.
-            Under a stable fitness landscape (panel B), all the mutations reaching fixation are either slightly deleterious and reaching fixation due to drift, or are beneficial back-mutations restoring a more optimal amino acid.
-            At the phylogenetic scale (panel D), this phenomena promotes promotes phenotype stability and preserves well established biological systems.
-            At the genome level, slightly deleterious mutations that have reached fixation are supposedly scattered at different loci, such that beneficial back-mutations should also be spread across the genome.
-            We thus expect that the genome-wide signature of beneficial back-mutations can be detected and quantified, even though each mutation has individually a small beneficial effect on their bearer.
-        }
+            (A \& B) At a given site of a protein-coding DNA sequence, the different amino-acids (x-axis) have different fitness values (y-axis).
+            Under a fluctuating fitness landscape (A), these fitnesses change with time.
+            The protein sequence follows the moving target defined by the amino-acid fitnesses, and since substitutions are accepted preferentially if they are in the direction of this target, substitutions are on average adaptive.
+            At the phylogenetic scale (C) beneficial substitutions are common (positive signs), promoting phenotype diversification across species.
+            Under a stable fitness landscape (B), most mutations reaching fixation are either slightly deleterious reaching fixation due to drift, or are beneficial back-mutations restoring a more optimal amino-acid.
+            At the phylogenetic scale (D) deleterious substitutions (negative signs) are often reverted via beneficial back-mutations (positive signs), promoting phenotype stability and preserving well established biological systems.
+            Even though individually any back-mutation might have a small beneficial effect on its bearer, we expect beneficial back-mutations to be scattered across the genome and the genome-wide signature of beneficial back-mutations to be detectable and quantifiable.}
         \label{fig:fitness-landscape}
@@
         \caption{
-            Integrating datasets at different scales.
-            At the phylogenetic level (panel A), the amino acid Wrightian fitness for each site is estimated from protein-coding DNA alignments using mutation-selection codon models.
-            Mutation-selection models assume a stable fitness landscape, taking into account only non-adaptive evolution.
-            A mutation with a $\Sphy > 1$ would be driving the current site toward are fitter amino-acid, and such mutation are considered a beneficial back-mutation repairing existing functions (panel B).
-            At the population scale (panel C), each single nucleotide polymorphism (SNP) segregating in the population can be classified as a beneficial back-mutation (in blue) or not.
-            The number of derived alleles allows us to estimate the probability of beneficial mutations at the population scale, for all SNPs or among back-mutations (panel D).
-            The probability of back-mutation is obtained as their fraction among all possible mutations from the ancestral genome sequence (panel E).
-            Altogether, we can estimate the probability of back-mutations among all beneficial ones, using Bayes' theorem (panel F).
+            Selection coefficients at the phylogenetic and population scales.
+            At the phylogenetic scale (A), the amino-acid Wrightian fitness for each site is estimated from protein-coding DNA alignments using mutation-selection codon models.
+            For every possible mutation, the difference in amino-acid fitness before and after the mutation allows us to compute the selection coefficient at the phylogenetic scale ($\Sphy$).
+            Mutations with $\Sphy < -1$ are considered deleterious ($\Sphy^{\text{d}}$ in red), and mutations with $-1 < \Sphy < 1$ are considered nearly-neutral ($\Sphy^{\text{n}}$ in green).
+            Mutations with $\Sphy > 1$ are toward a fitter amino-acids, and thus are considered beneficial back-mutations ($\Sphy^{\text{b}}$ in green blue), repairing existing functions (B).
+            At the population scale (C), each observed single nucleotide polymorphism (SNP) segregating in the population is classified according to its $\Sphy$ value.
+            Similarly, substitutions along the terminal branch are classified depending on their $\Sphy$ value.
+            Together, substitutions and polymorphisms are contrasted to synonymous changes used as a neutral expectation such as estimate selection coefficients at the population scale ($\Spop$).
+            For each class of selection ($\Sphy^{\text{b}}$, $\Sphy^{\text{n}}$, $\Sphy^{\text{d}}$), we can thus assess whether $\Sphy$ predicts $\Spop$ (E), and compute \textit{precision} (F-G) and \textit{recall} (F-H) for each class.
+            The \textit{recall} value for the class $\Sphy^{\text{b}}$ is the probability of back-mutations among all beneficial ones (H).
         }
@@
 
-    \subsection*{Back-mutations in the terminal lineages}
-    We first estimated the number of beneficial back-mutation in the terminal branches of mammals by reconstructing the substitutions occurring along the terminal branches of the phylogenetic tree.
-    For each substitution, we estimated its scaled selection coefficient ($\Sphy$) based on the stable fitness landscape of amino-acids estimated at the scale of the phylogenetic tree of mammals (fig.~\ref{fig:method}A).
-    Among all the substitutions that were found in the terminal branches, between 10 and 13\% had $\Sphy > 1$ (table~S1), while between 25 and 30\% had $\Sphy > 0$ (table~S2).
-    For substitutions with $\Sphy > 1$, the $\dnds$ ratio of non-synonymous over synonymous divergence was estimated to be between 1.15 and 1.68 in the different lineages (table~S1).
-    Beneficial back-mutations with $\Sphy > 1$ therefore reached fixation more frequently than synonymous mutations that are supposed to be neutral, which means that these back-mutations are effectively beneficial.
-    This result further indicated that $\dnds$ used to detect adaptation while relying on substitutions between closely related species~\cite{mcdonald_adaptative_1991, galtier_adaptive_2016} or at the phylogenetic scale~\cite{goldman_codonbased_1994, yang_codonsubstitution_2002} is biased due to the presence of beneficial back-mutations that are not adaptive.
-    We can alleviate this bias by computing $\dnds$ exclusively on non-synonymous sites with a $\Sphy < 0$, which represents the rate of evolution when beneficial back-mutations are discarded.
-    By comparing these two ways of estimating $\dnds$ (see Material \& Methods), we estimated that between 22\% and 27\% of $\dnds$ is inflated because of beneficial back-mutations while they only represent between 1\% and 2\% of mutational opportunities (table~S2).
+    \subsection*{Selection along the terminal branches}
+    First, we assessed whether fitness effects derived from the mutation-selection model at the phylogenetic scale are predictive of selection occurring in terminal branches.
+    To achieve this, we recovered the mutations that reached fixation in the terminal branches of 6 different mammalian genera.
+    Only mutations fixed in a population were considered as substitutions in the corresponding branch, while segregating mutations were discarded from this analysis.
+    For each substitution identified in the terminal branches, we obtained its scaled selection coefficient ($\Sphy$) as the change in amino-acid fitness at the corresponding codon site in the mammalian alignment (fig.~\ref{fig:method}A-C).
+    Importantly, the mammalian alignment used to estimate amino-acid fitness landscape does not include the genera for which we reconstructed the substitutions, to avoid fallacy and circularity in the reasoning.
+    Because $\Sphy$ was based on estimation of fitness effects at the mammalian scale, mutations with $\Sphy>1$ were considered beneficial back-mutations ($\Sphy^{\text{b}}$), toward a fitter amino acid.
+    Among all the substitutions that were found in each terminal branch, between 10 and 13\% were $\Sphy^{\text{b}}$ (table~S1).
+    In principle, beneficial back-mutations are bound to reach fixation more often than neutral substitutions.
+    Hence, we calculated the $\dnds$ ratio of non-synonymous over synonymous divergence for all terminal lineages, restricting the non-synonymous changes to our set of $\Sphy^{\text{b}}$.
+    We obtained values between 1.15 and 1.68 in the different lineages (table~S1), implying that $\Sphy^{\text{b}}$ reached fixation more frequently than synonymous mutations that are supposed to be neutral, which means that these back-mutations are effectively beneficial.
 
-    \subsection*{Back-mutations in the populations}
-    We then estimated the proportion of new mutations that were beneficial back-mutations while being under selection at the population scale (fig.~\ref{fig:method}C-E).
-    We first reconstructed the ancestral genome (instead of the reference genome) of each mammal species with available polymorphism data.
-    We computed the scaled selection coefficient ($\Sphy$) along this ancestral genome for each possible non-synonymous mutations, weighted by their mutational opportunity (see Material \& Methods).
-    It allowed us to obtain the distribution of fitness effects (DFE) of new mutations from the ancestral sequence under the assumption of the stable fitness landscape as shown for \textit{Homo sapiens} in Fig.~\ref{fig:homo-afr-results}A.
-    Because $\Sphy$ was based on estimation of fitnesses at the mammalian scale, mutations with $\Sphy>1$ were considered, as shown above, beneficial back-mutations and only represented ca.~1.5\% of all possible new mutations (blue in fig.~\ref{fig:homo-afr-results}A, table~S3).
-    However, when focusing on the mutations that are observed in populations, namely single nucleotide polymorphism (SNP), beneficial back-mutations represents ca.~8.5\% of all observed mutations (blue in fig.~\ref{fig:homo-afr-results}B, table~S3).
+    This result further indicated that using $\dnds$ as a proxy for the efficiency of purifying selection is biased due to the presence of beneficial back-mutations.
+    By discarding beneficial back-mutations from the estimation of $\dnds$, this corrected estimation represents the true efficiency of purifying selection.
+    By comparing these two ways of calculating $\dnds$ (see Materials \& Methods), we estimated that $\dnds$ values are inflated by between 22\% and 27\% across genera because of beneficial back-mutations while the latter only represent between 1\% and 2\% of mutational opportunities (table~S2).
 
-    Within populations, the frequencies at which SNPs are segregating is also providing information on their selective effect.
-    For instance, deleterious SNPs are segregating at lower frequencies because of the effect of purifying selection, which removes them from the population.
-    It is possible to estimate the DFE at the population scale by gathering information across many SNPs~\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009, galtier_adaptive_2016, tataru_inference_2017} and these approaches offer a unique opportunity to compare selection coefficients estimated at the population scale ($\Spop$) and at the phylogenetic scale ($\Sphy$).
-    We estimated the DFE at the population level and gathered robust statistical estimates by grouping SNPs observed in 5 classes of predicted selection coefficient (e.g.~in humans of African descent in fig.~\ref{fig:homo-afr-results}): severely deleterious with $\divStrongDel$, deleterious with $\divDel$, weakly deleterious with $\divWeakDel$, weakly beneficial with $\divWeakAdv$ and beneficial with $\divAdv$ (fig.~\ref{fig:homo-afr-results}B).
-	%in mat/met
-	%To obtain a quantitative estimate of the distribution of selection coefficient for each category of SNPs, we used the model polyDFE~\cite{tataru_inference_2017, tataru_polydfe_2020}.
-    %This model uses the count of derived alleles for each frequency class (fig.~\ref{fig:homo-afr-results}C) to infer the distribution of fitness effects (DFE).
-    %Moreover, the model relies on the mutational opportunities ($L$) for each category of $\Sphy$ (fig.~\ref{fig:homo-afr-results}A, see Material \& Methods) as well as the count of synonymous derived alleles used as a neutral model, which allow to control for demographic effects, and polarization errors when inferring the ancestral states.
-    From the DFE, we further estimated the proportion of beneficial mutations ($\PpolyAdv$), nearly-neutral mutations ($\PpolyNeutral$) and deleterious mutations ($\PpolyDel$) for each class of selection previously defined (fig.~\ref{fig:homo-afr-results}D).
-    We found that SNPs predicted to be deleterious based on the selection coefficient $\Sphy$ estimated across the phylogenetic tree of mammals were effectively purged at the population scale (red and yellow columns in fig.~\ref{fig:homo-afr-results}D)
-    Purifying selection was therefore largely predictable and amino acids with low fitness across mammals were effectively purged away in each population.
-    Then, SNPs predicted to be beneficial based on the selection coefficient $\Sphy$ estimated at the phylogenetic scale were indeed beneficial for individuals currently bearing them (blue column in fig.~\ref{fig:homo-afr-results}D).
-    These results confirmed that selection towards amino acids that are restoring existing function is ongoing in these populations.
-    Between these two extreme cases, SNPs predicted to be weakly selected (cyan and orange columns in fig.~\ref{fig:homo-afr-results}D) were effectively composed of neutral, beneficial and deleterious mutations.
+    \subsection*{Selection in populations}
+    Second, we assessed whether our scaled selection coefficients ($\Sphy$) were predictive of selective forces exerted at the population level.
+    To achieve this, we reconstructed the ancestral genome of each population to polarize single nucleotide polymorphism (SNPS) segregating in the population.
+    The scaled selection coefficient ($\Sphy$) predicted for every non-synonymous SNPs allow us to classify them as either $\Sphy^{\text{d}}$, $\Sphy^{\text{n}}$ or $\Sphy^{\text{b}}$ (fig.~\ref{fig:method}B-C).
 
-    We replicated our experiment across 28 populations of different mammal species (fig.~\ref{fig:heatmap}) and found that SNPs predicted to be deleterious were indeed purged at the population scale (red and yellow rows in fig.~\ref{fig:heatmap}A).
-    However, SNPs predicted to be weakly beneficial ($\divWeakAdv$) were composed of a mix of neutral and selected mutations with varying proportions across the different populations (cyan and orange row in fig.~\ref{fig:heatmap}B).
-    Finally, SNPs predicted to be beneficial back-mutations ($\divAdv$) were found to be beneficial with varying proportions across populations (blue row in fig.~\ref{fig:heatmap}C).
+    In humans, some SNPs have been associated to specific clinical prognosis terms\cite{landrum_clinvar_2018}.
+Those clinical terms have been obtained by clinical evaluation of the impact of variants on human Mendelian disorders\cite{landrum_clinvar_2018}.
+Thus they provide an orthogonal estimate of the effect of a mutation on human health, giving us an opportunity to evaluate whether this effect is in accordance with its predicted fitness effect.
+    To do so, we investigated whether the non-synonymous SNPs classified as $\Sphy^{\text{d}}$ or as $\Sphy^{\text{b}}$ showed an enrichment in specific clinical terms in comparison to SNPs classified as $\Sphy^{\text{n}}$.
+    Our results show that SNPs predicted as deleterious are associated to clinical terms such as \textit{Likely Pathogenic} and \textit{Pathogenic}, implying that, in general, the selective pressure of a mutation exerted across mammals is also predictive of its clinical effect in humans (table~S6).
+    Conversely, back-mutations are associated with clinical terms such as \textit{Benign} and \textit{Likely Benign}, which shows that back-mutations are less likely to be functionally damaging.
+
+    In addition to clinical prognosis, frequencies at which SNPs are segregating within populations also provide information on their selective effects.
+    For instance, deleterious SNPs are usually segregating at lower frequencies because of the effect of purifying selection, which tends to remove them from the population.
+    By gathering information across many SNPs, it is possible to estimate the distribution of fitness effects (DFE) at the population scale, taking synonymous SNPs as a neutral expectation\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009, galtier_adaptive_2016, tataru_inference_2017}.
+    From the estimated DFE, we can derive the proportion of beneficial mutations ($\PpolyAdv$), nearly-neutral mutations ($\PpolyNeutral$) and deleterious mutations ($\PpolyDel$) at the population scale.
+    These approaches offer a unique opportunity to contrast selection coefficients estimated at the population scale ($\Spop$) and at the phylogenetic scale ($\Sphy$).
+
+    Across our classes of selection ($\Sphy^{\text{d}}$, $\Sphy^{\text{n}}$ and $\Sphy^{\text{b}}$), one can ultimately estimate the proportion of false positives and false negatives, leading to an estimation of \textit{precision} and \textit{recall} (see Materials \& Methods).
+    Across 28 populations of different mammal species, mutations predicted to be deleterious at the phylogenetic scale were indeed purged at the population scale, with a \textit{precision} in the range of 89--97\% (table.~\ref{table:proba}).
+    Conversely, a \textit{recall} in the range of 95--98\% implies that mutations found to be deleterious at the population scale were most likely predicted to be so at the phylogenetic scale (table.~\ref{table:proba}).
+    Altogether, purifying selection is largely predictable and amino acids with negative fitness effects across mammals were effectively purged away in each population.
+
+    Mutations predicted as $\Sphy^{\text{n}}$ were effectively composed of a mix of neutral and selected mutations with varying \textit{precision} (18--74\%) and \textit{recall} (21--52\%) across the different populations (table.~\ref{table:proba}).
     The variable proportions found between populations can be explained by the effective number of individuals in the population ($\Ne$), which is known to be a major driver of selection efficacy.
-    Since $\Ne$ is not directly measurable, we used the Watterson $\theta_w$ as a proxy to order populations by their levels of synonymous diversity.
-    Higher synonymous diversity was associated with a smaller proportion of nearly-neutral mutations (fig.~\ref{fig:diversity}A\&B).
-    This result confirmed the nearly-neutral theory and suggested that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) were more likely to discriminate between beneficial and deleterious mutations (fig~S1-S9), while mutations in populations with low diversity (e.g.~\textit{Homo}) were effectively nearly-neutral.
+    Since $\Ne$ is not directly measurable, we used Watterson's $\theta_w$ as a proxy to order populations by their levels of synonymous diversity.
+    Higher synonymous diversity was associated with a smaller proportion of nearly-neutral mutations (fig.~\ref{fig:diversity}A).
+    This result follows the prediction of the nearly-neutral theory and suggests that in populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}), discrimination between beneficial and deleterious mutations is more likely to occur (fig~S1-S9).
+    Conversely, in populations with lower diversity (e.g.~\textit{Homo}) many more mutations are effectively neutral.
 
-    \subsection*{Proportion of back-mutations among all beneficial mutations}
-
-    Finally, we proposed an estimator for the probability of a beneficial mutation to be a beneficial back-mutation, computed as $\mathbb{P} [ \Sphy > 1  \given  \Spop > 1]$ (fig.~\ref{fig:method}C-F).
-    We obtained from the analyses above the probabilities $\mathbb{P} [ \Sphy > 1 ]$, $\mathbb{P} [ \Spop > 1 ]$, $\mathbb{P} [ \Spop > 1  \given  \Sphy > 1]$.
-    First, $\mathbb{P} [ \Sphy > 1 ]$ is the probability for a beneficial back-mutation ($\Sphy > 1$) from the ancestral sequence (blue fill of histogram in fig~\ref{fig:homo-afr-results}A and table~S3).
-    Second, $\mathbb{P} [ \Spop > 1 ]$ is the probability of mutation to be beneficial at the level of the population ($\Spop > 1$), estimated from all available SNPs (black fill in fig~\ref{fig:diversity}A and table~S3).
-    Finally, $\mathbb{P} [ \Spop > 1  \given  \Sphy > 1]$ is the probability for a back-mutation ($\Sphy > 1$) to be effectively beneficial at the level of the population ($\Spop > 1$), when we restricted our analysis on SNPs that were already predicted to be beneficial back-mutations (black fill for the category $\Sphy > 1$ in fig~\ref{fig:homo-afr-results}D and table~S3).
-    Combining these probabilities using Bayes theorem allowed us to obtain the probability for a beneficial mutation to be a back-mutation $\mathbb{P} [ \Sphy > 1  \given  \Spop > 1]$ (see Material \& Methods).
-    We estimated $\mathbb{P} [ \Sphy > 1  \given  \Spop > 1]$ across all populations sampled and obtained a proportion that varied between 10 and 26\% (table~S3).
-
-    The proportion of back-mutations among all beneficial ones did not show a clear relationship with the synonymous diversity within a population (Watterson $\theta_w$) (fig.~\ref{fig:diversity}C).
-    Indeed, the relationship between $\Ne$ and the proportion of beneficial back-mutations is not trivial and should highly depend on time scales~\cite{charlesworth_other_2007}.
-    A population that experienced a high $\Ne$ along its evolutionary time should be closer to the optimal state under a stable fitness landscape because of the higher efficacy of selection.
-    This should decrease the probability of beneficial back-mutations~\cite{huber_determining_2017}.
-    On the other hand, a high $\Ne$ over a short evolutionary time will induce more extreme fitness effects and a larger proportion of mutations will be beneficial (otherwise effectively neutral), thus increasing the proportion of beneficial back-mutations.
-    Overall, the proportion of beneficial back-mutations is expected to be more dependent on long-term effective population size as well as contraction or expansion rather than on the short term effective population size captured by the synonymous diversity~\cite{charlesworth_other_2007,huber_determining_2017}.
+    %Of note, mutations with $\Sphy>1$ only represented ca.~1.5\% of all possible new mutations, but ca.~8.5\% of all observed mutations in the population (blue in fig.~\ref{fig:homo-afr-results}A-B, table~S3).
+    Finally, mutations predicted to be beneficial back-mutations based on the selection coefficients at the phylogenetic scale ($\Sphy^{\text{b}}$) were indeed beneficial for individuals currently bearing them, with a precision in the range of 15--52\% (table.~\ref{table:proba}).
+    This result confirms that selection towards amino acids that are restoring existing functions is ongoing in these populations.
+    Importantly, the \textit{recall} value in this case, computed as $\proba [ \Sphy^{\text{b}}  \given  \Spop^{\text{b}}]$, is the probability for a beneficial mutation at the population scale to be a beneficial back-mutation, that is, going toward a fitter amino-acid (fig.~\ref{fig:method}F).
+    In other words, the \textit{recall} value quantifies the amount of beneficial mutations that are restoring damaged genomes instead of creating adaptive innovations.
+    Across the 28 populations, this proportion is in the range of 11--70\% (table.~\ref{table:proba}).
 
@@
         \caption{
-            Panel A: Distribution of fitness effects ($\Sphy$), predicted for all possible mutations away from the ancestral human genome.
-            Mutations are divided into 5 classes of selection: severely deleterious (red), deleterious (yellow), weakly deleterious (light green), weakly beneficial (green) and beneficial (blue, supposedly beneficial back-mutations).
-            Panel B. Distribution of fitness effects ($\Sphy$) for all observed SNPs in a sample of 8 individuals (out of 512 in the original dataset) of African descent.
-            If they are less mutations observed than expected, this class is thus undergoing purifying selection.
-            Panel B: The site-frequency spectrum (SFS) represents the proportion of mutations (y-axis) with a given number of derived alleles in the population (x-axis).
-            SFS are drawn for a random sample of 16 alleles (mean in solid line and standard deviation in filled color) for each class of selection and for synonymous mutations which are supposedly neutral (black).
-            At high frequencies, supposedly severally deleterious mutations are underrepresented.
-            Panel D.
-For each class of selection (and for the set of all non-synonymous mutations), information from the SFS and the distribution of fitness effects are combined at the population scale to estimate the proportion of beneficial mutations $\PpolyAdv$, of nearly-neutral mutations $\PpolyNeutral$ and of deleterious mutations $\PpolyDel$.
+            (A) Distribution of fitness effects ($\Sphy$), predicted for all possible mutations away from the ancestral human genome.
+            Mutations are divided into three classes of selection: deleterious ($\Sphy^{\text{d}}$ in red), nearly-neutral ($\Sphy^{\text{n}}$ in green) and beneficial ($\Sphy^{\text{b}}$ blue, supposedly beneficial back-mutations).
+            (B) Distribution of fitness effects ($\Sphy$) for all observed substitutions along the \textit{Homo} branch after the \textit{Homo}-\textit{Pan} splits.
+            If there are less substitutions observed than expected, this class is thus undergoing purifying selection, as is the case of for $\Sphy^{\text{d}}$.
+            (C) The site-frequency spectrum (SFS) in humans of African descent for a random sample of 16 alleles (mean in solid line and standard deviation in color shade) for each class of selection and for synonymous mutations, which are supposedly neutral (black).
+The SFS represents the proportion of mutations (y-axis) with a given number of derived alleles in the population (x-axis).
+            At high frequencies, deleterious mutations are underrepresented.
+            (D) Proportion of beneficial $\PpolyAdv$, nearly-neutral $\PpolyNeutral$ and deleterious mutations $\PpolyDel$ estimated at the population scale for each class of selection at the phylogenetic scale.
+Proportions depicted here are not weighted by mutational opportunities.
         }
@@
 
-    \begin{figure*}[!ht]
+    \begin{table*}[tb]
         \centering
-        \includegraphics[width=\textwidth, page=1] {artworks/figure.heatmap}
+        \begin{adjustbox}{width=\textwidth}
+            \begin{tabular}{||l|l|r||r|r||r|r||r|r||}
+                \toprule
+                \multicolumn{3}{||c||}{} &
+                \multicolumn{2}{c||}{\shortstack{\textbf{Deleterious mutations} \\ $\bm{\Spop^{\text{d}} \coloneqq \Spop<-1}$ \\ $\bm{\Sphy^{\text{d}} \coloneqq \Sphy<-1}$}} &
+                \multicolumn{2}{c||}{\shortstack{\textbf{Nearly-neutral mutations} \\ $\bm{\Spop^{\text{n}} \coloneqq -1<\Spop<1}$ \\ $\bm{\Sphy^{\text{n}} \coloneqq -1<\Sphy<1}$}} &
+                \multicolumn{2}{c||}{\shortstack{\textbf{Beneficial mutations} \\ $\bm{\Spop^{\text{b}} \coloneqq \Spop>1}$ \\ $\bm{\Sphy^{\text{b}} \coloneqq \Sphy>1}$}}
+                \\ \hline
+                \textbf{Population} &
+                \textbf{Species} &
+                $\bm{\pi_{\text{S}}}$ &
+                \makecell{\textbf{Precision} \\ $\bm{\proba [\Spop^{\text{d}} \given \Sphy^{\text{d}}]}$} &
+                \makecell{\textbf{Recall} \\ $\bm{\proba [\Sphy^{\text{d}} \given \Spop^{\text{d}}]}$}             &
+                \makecell{\textbf{Precision}      \\ $\bm{\proba [\Spop^{\text{n}} \given \Sphy^{\text{n}}]}$}                 &
+                \makecell{\textbf{Recall}          \\ $\bm{\proba [\Sphy^{\text{n}} \given \Spop^{\text{n}}]}$}               &
+                \makecell{\textbf{Precision}          \\ $\bm{\proba [\Spop^{\text{b}} \given \Sphy^{\text{b}}]}$}            &
+                \makecell{\textbf{Recall}        \\ $\bm{\proba [\Sphy^{\text{b}} \given \Spop^{\text{b}}]}$}
+                \\   \midrule
+                \rowcolor{LIGHTGREY} Equus c.   & Equus caballus        & $ 0.002$ & $ 0.918$ & $ 0.957$ & $ 0.186$ & $ 0.213$ & $ 0.519$ & $ 0.122$ \\
+                Iran                 & Bos taurus        & $ 0.002$ & $ 0.924$ & $ 0.965$ & $ 0.565$ & $ 0.356$ & $ 0.368$ & $ 0.702$ \\
+                Uganda                & Bos taurus        & $ 0.005$ & $ 0.943$ & $ 0.961$ & $ 0.516$ & $ 0.396$ & $ 0.255$ & $ 0.425$ \\
+                \rowcolor{LIGHTGREY} Australia              & Capra hircus        & $ 0.003$ & $ 0.941$ & $ 0.964$ & $ 0.592$ & $ 0.434$ & $ 0.147$ & $ 0.308$ \\
+                \rowcolor{LIGHTGREY} France                 & Capra hircus          & $ 0.004$ & $ 0.940$ & $ 0.963$ & $ 0.571$ & $ 0.418$ & $ 0.149$ & $ 0.304$ \\
+                \rowcolor{LIGHTGREY} Iran (C. aegagrus) & Capra hircus          & $ 0.004$ & $ 0.948$ & $ 0.960$ & $ 0.515$ & $ 0.446$ & $ 0.147$ & $ 0.157$ \\
+                \rowcolor{LIGHTGREY} Iran     & Capra hircus          & $ 0.004$ & $ 0.942$ & $ 0.961$ & $ 0.534$ & $ 0.410$ & $ 0.152$ & $ 0.258$ \\
+                \rowcolor{LIGHTGREY} Italy              & Capra hircus          & $ 0.004$ & $ 0.940$ & $ 0.963$ & $ 0.579$ & $ 0.421$ & $ 0.147$ & $ 0.316$ \\
+                Morocco              & Capra hircus          & $ 0.004$ & $ 0.939$ & $ 0.960$ & $ 0.549$ & $ 0.404$ & $ 0.186$ & $ 0.398$ \\
+                Iran             & Ovis aries & $ 0.007$ & $ 0.957$ & $ 0.954$ & $ 0.412$ & $ 0.416$ & $ 0.158$ & $ 0.191$ \\
+                Iran (O. orientalis)    & Ovis aries & $ 0.009$ & $ 0.961$ & $ 0.955$ & $ 0.413$ & $ 0.437$ & $ 0.157$ & $ 0.180$ \\
+                Iran (O. vignei)             & Ovis aries & $ 0.007$ & $ 0.968$ & $ 0.951$ & $ 0.356$ & $ 0.516$ & $ 0.186$ & $ 0.118$ \\
+                Various               & Ovis aries & $ 0.008$ & $ 0.958$ & $ 0.955$ & $ 0.428$ & $ 0.431$ & $ 0.156$ & $ 0.188$ \\
+                Morocco                & Ovis aries & $ 0.008$ & $ 0.960$ & $ 0.953$ & $ 0.447$ & $ 0.460$ & $ 0.190$ & $ 0.292$ \\
+                \rowcolor{LIGHTGREY} Barbados                & Chlorocebus sabaeus & $ 0.004$ & $ 0.931$ & $ 0.969$ & $ 0.628$ & $ 0.402$ & $ 0.282$ & $ 0.630$ \\
+                \rowcolor{LIGHTGREY} Central Afr. Rep.         & Chlorocebus sabaeus & $ 0.006$ & $ 0.941$ & $ 0.964$ & $ 0.514$ & $ 0.408$ & $ 0.310$ & $ 0.263$ \\
+                \rowcolor{LIGHTGREY} Ethiopia          & Chlorocebus sabaeus & $ 0.005$ & $ 0.933$ & $ 0.967$ & $ 0.586$ & $ 0.393$ & $ 0.298$ & $ 0.456$ \\
+                \rowcolor{LIGHTGREY} Gambia               & Chlorocebus sabaeus & $ 0.005$ & $ 0.937$ & $ 0.967$ & $ 0.590$ & $ 0.414$ & $ 0.305$ & $ 0.422$ \\
+                \rowcolor{LIGHTGREY} Kenya              & Chlorocebus sabaeus        & $ 0.005$ & $ 0.942$ & $ 0.965$ & $ 0.526$ & $ 0.418$ & $ 0.296$ & $ 0.253$ \\
+                \rowcolor{LIGHTGREY} Nevis     & Chlorocebus sabaeus        & $ 0.003$ & $ 0.930$ & $ 0.970$ & $ 0.637$ & $ 0.401$ & $ 0.285$ & $ 0.696$ \\
+                \rowcolor{LIGHTGREY} South Africa           & Chlorocebus sabaeus        & $ 0.006$ & $ 0.937$ & $ 0.964$ & $ 0.530$ & $ 0.393$ & $ 0.323$ & $ 0.338$ \\
+                \rowcolor{LIGHTGREY} Saint Kitts             & Chlorocebus sabaeus        & $ 0.004$ & $ 0.931$ & $ 0.969$ & $ 0.611$ & $ 0.393$ & $ 0.292$ & $ 0.604$ \\
+                \rowcolor{LIGHTGREY} Zambia          & Chlorocebus sabaeus        & $ 0.006$ & $ 0.941$ & $ 0.963$ & $ 0.506$ & $ 0.408$ & $ 0.309$ & $ 0.252$ \\
+                African          & Homo sapiens        & $ 0.002$ & $ 0.896$ & $ 0.968$ & $ 0.550$ & $ 0.297$ & $ 0.371$ & $ 0.284$ \\
+                Admixed American          & Homo sapiens        & $ 0.002$ & $ 0.890$ & $ 0.979$ & $ 0.710$ & $ 0.333$ & $ 0.368$ & $ 0.464$ \\
+                East Asian          & Homo sapiens        & $ 0.002$ & $ 0.890$ & $ 0.971$ & $ 0.578$ & $ 0.289$ & $ 0.369$ & $ 0.358$ \\
+                European          & Homo sapiens        & $ 0.002$ & $ 0.891$ & $ 0.980$ & $ 0.739$ & $ 0.345$ & $ 0.368$ & $ 0.499$ \\
+                South Asian          & Homo sapiens        & $ 0.002$ & $ 0.895$ & $ 0.981$ & $ 0.740$ & $ 0.356$ & $ 0.369$ & $ 0.423$ \\
+                \bottomrule
+            \end{tabular}
+        \end{adjustbox}
         \caption{
-            Reproducibility of results shown in figure~\ref{fig:homo-afr-results} in 28 populations across 6 genera.
-            For each class of selection at the phylogenetic scale ($\Sphyclass \in \{ \divStrongDel, \divDel,  \divWeakDel,  \divWeakAdv, \divAdv \}$, in rows), site-frequency spectra and total number of sites are combined at the population scale to estimate the proportion of beneficial mutations ($\PpolyAdv$) in the top panel, of nearly-neutral mutations ($\PpolyNeutral$) in the middle panel and of deleterious mutations ($\PpolyDel$) in the bottom panel.
-        }.
-        \label{fig:heatmap}
-    \end{figure*}
+            Precision and \textit{recall} for estimated selection coefficient of mutations given by mutation-selection models ($\Sphy$), in 28 populations across 6 genera.
+            Precision and \textit{recall} are computed for three classes of mutations: deleterious, nearly-neutral and beneficial.
+            Precision is the recovered estimation of selection coefficient at population scale ($\Spop$) given that $\Sphy$ is known.
+            Conversely, \textit{recall} is the recovered estimation of $\Sphy$ given selection coefficient at the population scale ($\Spop$) is known.
+            Recall for beneficial mutations ($\proba [\Sphy^{\text{b}} \given \Spop^{\text{b}}]$) is thus the proportion of beneficial back-mutations among all beneficial mutations.
+            $\bm{\pi_{\text{S}}}$ is the observed genetic diversity (number of SNPs per site) counted over synonymous sites.
+        }
+        \label{table:proba}
+    \end{table*}
+
+    \subsection*{Beneficial mutations are not necessarily adaptive}
+
+    This study represents an important step towards an integration of different evolutionary scales necessary to decipher the combined effects of mutation, selection and drift on genome evolution.
+    In particular, quantifying the proportion of beneficial back-mutations among all beneficial mutations has only been achievable by combining genome-wide data from both phylogenetic and population scales.
+    At the phylogenetic scale, for each site of a protein-coding DNA alignment, codon diversity can allow for the reconstruction of an amino-acid fitness landscape, assuming that this landscape is stable along the phylogeny.
+    Across all sites, these amino-acid fitness landscapes allow us to predict the selection coefficient ($\Sphy$) of any mutation along a protein coding sequence.
+    These selective effects can be compared to observations at the population level.
+    By doing so, we have been able to confirm that mutations predicted to be deleterious ($\Sphy^{\text{d}} \coloneqq \Sphy < -1$) are purified away in extant populations.
+    Our results reflect on previous studies showing that SIFT scores\cite{ng_sift_2003, vaser_sift_2016}, which are based on amino-acid alignments across species, have also been found to be informative of the deleterious fitness effects exerted at the population scale\cite{chen_hunting_2021}.
+    However, and contrary to SIFT scores, our mutation-selection model is parameterized by a fitness function such that changes are directly interpretable as fitness effects.
+    In this regard, an interesting prediction of our model is that back-mutations are beneficial because they are reverting previous deleterious changes.
+    We have tested this hypothesis and have found that these back-mutations ($\Sphy^{\text{b}} \coloneqq \Sphy > 1 $) are indeed beneficial in extant populations.
+    We estimated that between 18 and 78\% of all beneficial mutations in mammalian populations have not been driven by adaptation, but instead have reversed deleterious substitutions which have accumulated along the phylogeny.
+    These results suggest that many beneficial mutations are non-adaptive, but are rather restoring ancestral states of higher fitness.
+    Hence, the extent of adaptive evolution can only be correctly estimated if we can account for the number of beneficial back-mutations\cite{keightley_what_2010, rice_evolutionarily_2015}.
+    Altogether, we argue that we should dissociate positive selection from adaptive evolution and limit the use of adaptive mutations to those that are associated with adaptation to environmental change as such\cite{charlesworth_other_2007, mustonen_fitness_2009}.
+
+    \subsection*{Interpreting the proportion of beneficial back-mutations}
+
+    Across the genome, both beneficial-back mutations and deleterious mutations reaching fixation generate a balance in which genomes are constantly damaged and restored simultaneously at different loci.
+    Essentially, since the probability of fixation of mutations depends on the effective population size ($\Ne$), the history of $\Ne$ plays a crucial role in the amount of beneficial back-mutations compensating deleterious mutations\cite{latrille_inferring_2021}.
+    For example, a population size expansion will increase the efficacy of selection and a larger proportion of mutations will be beneficial (otherwise effectively neutral), thus increasing the number of beneficial back-mutations.
+    On the other hand, a population that has experienced a high $\Ne$ throughout its history should be closer to an optimal state under a stable fitness landscape having suffered fewer fixations of deleterious mutations and therefore decreasing the probability of beneficial back-mutations\cite{huber_determining_2017}.
+    Overall, the proportion of beneficial back-mutations is expected to be more dependent on the long-term $\Ne$, as well as its expansions and contractions, rather than on the short-term $\Ne$\cite{charlesworth_other_2007,huber_determining_2017}.
+    In this regard, the proportion of back-mutations among all beneficial ones did not show a clear relationship with the synonymous diversity within a population (Watterson's $\theta_w$) (fig.~\ref{fig:diversity}B), which should, in theory, reflect the short-term $\Ne$.
+
+    %We have to acknowledge that the mammalian case study might also not be representative of other clades.
+    %Indeed, long-term population sizes are relatively small in mammals, which allow large amounts of deleterious mutations to be fixed, and thus, a lot of opportunities for beneficial back-mutations to arise.
+    %It would thus be of great interest to reproduce our analysis with other clades, such as \textit{Drosophila} or \textit{Saccharomyces} which have higher effective population sizes.
+    %Indeed when the effective population size is higher, the number of effectively neutral mutational opportunities should be reduced.
+    %Allowing for changes in effective population sizes along the phylogeny have been developed\cite{latrille_inferring_2021}, but are, for the moment, too computationally intensive to be performed genome-wide.
+    %This reduction should mechanistically increase the proportion of adaptive substitutions.
+    %However, this does not imply that the rate of adaptation (i.e the number of changes in the fitness landscape per site per generation) is higher \cite{galtier_adaptive_2016}.
+
+    The exact estimation of the contribution of beneficial back-mutations to positive selection relies on some hypotheses at both the phylogenetic and population scales and is sensitive to methodological limitations.
+    Indeed, in order to be conservative, we considered that any mutation under positive selection at the scale of populations, but not predicted as such at the phylogenetic scale (false negatives) is potentially an adaptation.
+    However, adaptive mutations are not the only contributors to these false negatives since limited data quality and potentially inadequate modelling choices of both the fitness landscape and the DFE might also lead to false negatives.
+    Moreover, a mutation which is inferred to be nearly-neutral at the phylogenetic scale, but found to be positively selected at the population scale will also be considered as a false negative (and thus an adaptation), even if this discrepancy could just be due to a population size expansion \cite{lanfear_population_2014, jones_shifting_2017, platt_protein_2018}.
+    Given this inflation of false negatives, we consider our estimated proportion of adaptive mutations among beneficial ones to be an overestimation and, hence, our estimation of beneficial back-mutations among advantageous ones should be taken as a lower bound.
+
+    %Regarding the distribution of fitness effects (DFE) estimated at the population scale, there is no consensus on its expected shape\cite{welch_divergence_2008, bataillon_effects_2014}, although it has been found to be reliably constant between closely related species\cite{castellano_comparison_2019}.
+    %We modelled the DFE as a continuous distribution, with the negative side of the DFE as a gamma distribution, and the positive side as an exponential distribution with a mean greater than one.
+    %To check for robustness in our results despite the uncertainty of the underlying DFE, we also performed our analysis assuming a discretized DFE with five categories of selection coefficients, instead of three.
+    %Our results are consistent, with the proportion of back-mutations among all beneficial mutations ranging from 3 to 20\% across populations when modelling a DFE with five categories (table~S5).
+    %Consequently, even though our general framework contrasting the phylogenetic and population scales is theoretically consistent, we acknowledge that estimating the proportion of back-mutations among all beneficial ones is dependent on the the underlying DFE at the population scale and the threshold used to define a beneficial mutation.
+    %As a result, further work is required to investigate the shape of the DFE at the population scale.
+    %Notably, the reconstructed distribution of $\Sphy$ values obtained in our study has a negative mode (around $\Sphy=-5$), consistent with experimental DFEs obtained by mutation accumulation (fig.~S10).
+    %Contrarily, continuous DFEs estimated at the population scale have by definition a mode at 0.
+    %We argue that methods estimating DFE at the population scale should assume a mode shifted toward negative values of $\Spop$.
+    % Second, at the population scale, the threshold to consider a mutation beneficial ($\Spop >1 $ or $\Sphy > 1$) discards slightly beneficial mutations.
+    % To also consider slightly-beneficial mutations, we performed the same analysis with a threshold of zero.
+    %With this methodology, the proportion of back-mutations among all beneficial mutations increases and ranges from 12 to 45\% across populations(table~S4).
 
@@
         \caption{
-            Panel A.
-For each population, the proportion of beneficial ($\PpolyAdv$), nearly-neutral ($\PpolyNeutral$) and of deleterious ($\PpolyDel$) mutations estimated at the population scale using all SNPs available.
-            Population are sorted for increased synonymous diversity.
-            Panel B. Proportion of nearly-neutral mutations ($\mathbb{P} [ -1 < \Spop < 1]$ in y-axis), shown as a function of the synonymous diversity (Watterson $\theta_w$ in x-axis).
-            Panel C.
-Proportion of beneficial back-mutations among all beneficial mutations ($\mathbb{P} [ \Sphy > 1  \given  \Spop > 1]$ in y-axis), shown as a function of the synonymous diversity (Watterson $\theta_w$ in x-axis).
+            (A) Proportion of nearly-neutral mutations at the population scale ($\proba [ \Spop^{\text{n}}]$ in the y-axis), shown as a function of the synonymous diversity (Watterson's $\theta_w$ in the x-axis).
+            (B) Proportion of beneficial back-mutations among all beneficial mutations ($\proba [ \Sphy^{\text{b}}  \given  \Spop^{\text{b}}]$ in the y-axis), shown as a function of the synonymous diversity (Watterson's $\theta_w$ in the x-axis).
         }
@@
 
-    \subsection*{A bridge between phylogenetic and population-genetics}
-    In this study, we first estimated selective effects of mutations inside protein coding sequence, under a model assuming no adaptation at the phylogenetic scale.
-    We then estimated the proportion of beneficial back-mutations, that are not adaptive innovations, and subsequently estimated their proportion among all beneficial mutations at the population scale.
-    Our work confirms that deleterious substitutions have accumulated in mammals and are currently being eliminated, resulting in up to 25\% of beneficial mutations that are not adaptive innovations, but instead are repairing previous deleterious changes.
+    \subsection*{The role of epistasis in mammalian protein-coding genes}
 
-    At the phylogenetic scale, we have found that we can use mutation-selection codon models to predict the selection coefficient of a mutation ($\Sphy$).
-    However, we so far assumed no changes in effective population size along the phylogeny while it has been established that population size changes have a major effect on selection dynamics~\cite{lanfear_population_2014, jones_shifting_2017, platt_protein_2018}.
-    Mutation-selection models with changes in effective population sizes along the phylogeny have been developed~\cite{latrille_inferring_2021}, but are, for the moment, too computational intensive to be performed genome-wide.
-    Hybrid mutation-selection and phenomenological codon models could provide a way forward to integrate site-specific selection and branch-specific drift~\cite{brevet_reconstructing_2021a}.
-    As for the estimate of selection, SIFT scores based on amino acid alignments across species have also been found to be informative of the selection pressure exerted at the population scale~\cite{chen_hunting_2021}.
-    We also concur that mutations with a low SIFT score are more deleterious in the different populations, and conversely mutations with a high SIFT scores are more beneficial (supp.\ mat.\  section SIFT scores).
-    In practice, SIFT scores are more coarse grained, with for example a bulk of mutations with a score of 1.0 (the highest), and it does not provide a boundary between beneficial and deleterious mutations.
-    On the contrary, mutation-selection codon models are genuinely taking into account the tug-of-war between scarce beneficial mutations likely to reach fixation and a bulk of deleterious mutations eventually reaching fixation due to their sheer mass.
-    As such, these models can be used as a null model to predict the expected rate of evolution of proteins~\cite{spielman_relationship_2015, dosreis_how_2015} under a stable fitness landscape.
-    A departure from this null model of evolution would indicate that proteins are evolving under a changing fitness landscape~\cite{cvijovic_fate_2015, rodrigue_detecting_2017, tamuri_mutationselection_2021} and is a signal of pervasive adaptive evolution~\cite{rodrigue_bayesian_2021} or of pervasive epistasis~\cite{rodrigue_detecting_2017}.
-    As such, a stable fitness landscape as a null model is thus statistically more powerful to detect adaptation than assuming that the null model is neutral evolution.
-    Taken together, mutation-selection models are a mandatory tool in evolutionary biology to detect and quantify adaptation at the phylogenetic scale, while acknowledging the contribution of beneficial back-mutations.
+    In our study, we focused on mutations toward a more optimal amino-acid at a given site, assuming that amino-acid fitness landscapes are site-specific and also independent of one another.
+    Contrarily, under epistasis, the fitness effect of a mutation at a particular site depends on the amino-acids present at other sites.
+    Epistasis therefore allows for compensatory mutations, which restore fitness through mutations at loci different from where deleterious mutations take place, and this process also leaves signals interpretable as non-adaptive beneficial mutations\cite{hartl_compensatory_1996, pollock_strong_2014, starr_epistasis_2016}.
+    Also, epistasis has been shown to play a role in the evolution of protein-coding genes, with amino-acid residues in contact within a protein or between proteins tending to co-evolve\cite{breen_epistasis_2012, starr_epistasis_2016}.
+    Particularly, the residues in contact co-evolve to become more compatible with each other generating an entrenchment, making empirical evidence for beneficial back-mutations harder to find since restoring mutations becomes less and less likely to occur over time\cite{goldstein_nonadaptive_2015, goldstein_sequence_2017, park_epistatic_2022}.
+    Nevertheless, the fact that we observe such a high proportion of beneficial back-mutations suggests that the underlying assumptions of our model, namely site-independence, implying no epistasis, and a static fitness landscape, are a reasonable approximation for the underlying fitness landscape of proteins.
+    Our results imply that the fitness effects of new mutations are mostly conserved across mammalian orthologs, in agreement with other studies showing that for conserved orthologs with similar structures and functions, models without epistasis provide a reasonable estimate of fitness effects in protein coding genes\cite{ashenberg_mutational_2013, youssef_consequences_2020}.
 
-    At the population scale ($\Spop$), our results also rely on some hypothesis and thresholds.
-    We first defined the threshold to consider a mutation beneficial ($\Spop$ or $\Sphy$ greater than one), such that nearly-neutral mutations that are only slightly-beneficial are discarded.
-    To also consider slightly-beneficial mutations, we performed the same analysis with a threshold of zero.
-    With this methodology, the proportion of back-mutations among all beneficial mutations increases and ranges from 12 to 45\% across populations(table~S4).
-    Second, there is no consensus on the expected shape of the distribution of fitness effects (DFE)~\cite{welch_divergence_2008, bataillon_effects_2014}, although it has been found to be reliably constant between closely related species~\cite{castellano_comparison_2019}.
-    We used a model that allowed the inference of a continuous DFE by modelling the negative side of the DFE as a gamma distribution, and the positive side as an exponential distribution with a mean greater than one.
-    To control for the uncertainty of the underlying DFE, we also performed our analysis assuming a discretized DFE with 5 categories of selection coefficients, and the proportion of back-mutations among all beneficial mutations with this DFE ranges from 3 to 20\% across populations (table~S5).
-    Consequently, even though our general framework contrasting the phylogenetic and population scale is theoretically consistent, we acknowledge that estimating the proportion of back-mutations among all beneficial ones is dependent on the assumption for the underlying DFE at the population scale and the threshold used to define a beneficial mutation.
-    As a result, further work are required to investigate the shape of the DFE at the population scale.
-    Notably, DFE estimated at the mammalian scale (fig.~\ref{fig:homo-afr-results}A) have a negative mode (around $\Sphy=-5$), consistent with experimental DFEs obtained by mutation accumulation (fig.~S10).
-    Contrarily, continuous DFEs estimated at the population scale have by definition a mode at 0.
-    We argue that methods estimating DFE at the population scale should as a result assume a mode shifted toward negative values of $\Spop$.
+    \subsection*{Detecting adaptation above the nearly-neutral background}
 
-    Aside from methodological limitations, the mammalian case study might also not be representative of other clades.
-    Indeed, mammals have relatively small long term population sizes, which allow large amounts of deleterious mutations to be fixed, and thus, there are a lot of opportunities for beneficial back-mutations to arise.
-    It would thus be of great interest to reproduce our experiment with other clades, such as \textit{Drosophila} or birds which tend to have higher effective population size.
-    It would also be interesting to have access to more shallow but wider phylogenies to estimate fitness landscapes at short time-scales.
+    A long-standing debate in molecular evolution is whether the variations we observe between species in protein-coding genes are mostly due to nearly-neutral mutations reaching fixation by drift, or if they are mostly due to adaptation \cite{kimura_evolutionary_1968,kern_neutral_2018,jensen_importance_2019,gillespie_substitution_1994,Ohta1992}.
+    Here we provide evidence that in mammalian conserved orthologs, a large proportion of substitutions are due to the fixation of both deleterious mutations and beneficial back-mutations.
+    However, a central question regarding how to detect adaptation above this background of nearly-neutral substitutions remains\cite{kimura_evolutionary_1968,ohta_development_1996}.
 
-    From a structural biology perspective, we have found that proteins are not optimal for their fitness, which has been proved for their kinetics and thermodynamics~\cite{hartl_compensatory_1996, taverna_why_2002, goldstein_evolution_2011}.
-    In this context of suboptimal fitness, compensatory mutations can repair damage caused by deleterious mutations at another loci and generate a widespread signal of positive selection~\cite{hartl_compensatory_1996, pollock_strong_2014, starr_epistasis_2016}.
-    In our study we focused on mutations toward a more optimal amino-acid at a given site, not accounting for compensatory mutations since we assumed a model of fitness landscape without epistasis, where site-specific amino-acid profiles are independent of one another.
-    As shown in other studies, these models without epistasis provide a reasonable estimate of average fitness profiles~\cite{youssef_consequences_2020}.
-    But most importantly, we argue that our estimation of the amount of beneficial back-mutations is an underestimation, and that accounting for compensatory mutations by means of epistasis would mechanically increase our estimate.
-    Indeed, a fluctuating fitness landscape due to an external forces (i.e.~changes in environment) results in an acceleration of the rate of evolution~\cite{rodrigue_detecting_2017, rodrigue_bayesian_2021}, which generates epistatic mutations that are immediately beneficial~\cite{gong_epistatically_2014}.
-    In contrast, pervasive epistasis generates the opposite pattern, an entrenchment~\cite{goldstein_evolutionary_2004, goldstein_nonadaptive_2015} resulting in a slowing down of the rate evolution~\cite{rodrigue_detecting_2017, patel_epistasis_2022} or a standstill~\cite{youssef_evolution_2022}.
-    In other words, under pervasive epistasis, finding empirical evidence for beneficial back-mutations is harder since restoring mutations become less and less likely to occur over time~\cite{goldstein_nonadaptive_2015, goldstein_sequence_2017, park_epistatic_2022}.
-    As our study shows that beneficial back-mutations should not be overlooked, we argue that both beneficial back-mutations and compensatory mutations play an important role in preventing our genome from collapsing under a mutation load.
+    One first strategy is precisely to use a nearly-neutral substitution model as a null model of evolution.
+    Under a strictly neutral evolution of protein-coding sequence, the ratio of non-synonymous over synonymous substitutions ($\dnds$) is expected to be equal to one.
+    Deviations from this neutral expectation, such as $\dnds > 1$, which can be generated by an excess of non-synonymous substitutions, is generally interpreted as a sign of adaptation.
+    However, as we have shown in this study, a $\dnds > 1$ is not necessarily a signature of adaption, but can be due to beneficial back-mutations.
+    So, by relaxing the strict neutrality and assuming a stable fitness landscape instead, one can predict the expected rate of evolution, called $\omega_0$\cite{spielman_relationship_2015, dosreis_how_2015}.
+    In this manner, adaptation can be alternatively considered as evolution under a changing fitness landscape and tested as such by searching for the signature of $\dnds > \omega_0$\cite{cvijovic_fate_2015, rodrigue_detecting_2017, rodrigue_bayesian_2021}.
+    By using a stable fitness landscape as a null model of evolution, thus accounting for selective constraints exerted on the different amino-acids, the statistical power in testing for adaptation is increased\cite{latrille_genes_2023}.
+    Another strategy to detect adaptation, instead of relying solely on summary statistics (such as $\dnds$ or $\omega_0$), is to include changes in the fitness landscapes inherently within the mutation-selection framework\cite{tamuri_mutationselection_2021}.
+    Such mechanistic models could be more general than site-specific fitness landscapes, including both epistasis and changing fitness landscapes\cite{goldstein_sequence_2017, stolyarova_senescence_2020}.
 
-    In conclusion, we showed that by integrating genome-wide datasets at the phylogeny and the population scale, it is possible to estimate the proportion of beneficial mutations repairing existing functions instead of generating adaptive innovations.
-    This study at the interface between phylogenetic and population-genetics thus provide a step toward an integration of different scales necessary to decipher the combined effects of mutation, selection and drift on genome evolution.
-    We argue that our approach is general and our methodology can be readily applied to different estimations of fitness landscape at the phylogenetic scale, and different models and methods estimating distribution of fitness effects at the population scale.
+    Here, we have provided empirical evidence that an evolutionary model assuming a stable fitness landscape at the mammalian scale allows us to predict the fitness effects of mutations in extant populations and individuals, acknowledging the balance between deleterious and beneficial back-mutations.
+    We argue that such a model represents a null expectation for the evolution of protein-coding genes in the absence of adaptation.
+    In that sense, adaptation should retain its original meaning associated with a change in the underlying fitness landscape and be modelled as such.
 
@@
     \label{sec:acknowledgment}
-    We gratefully acknowledge the help of Mélodie Bastian, Nicolas Lartillot and Laurent Duret for their advice and reviews concerning this manuscript.
+    We gratefully acknowledge the help of Mélodie Bastian, Nicolas Lartillot, Carina Farah Mugal and Laurent Duret for their advice and reviews concerning this manuscript.
     This work was performed using the computing facilities of the CC LBBE/PRABI\@.
@@
 
-    Protein-coding DNA sequences alignments in placental mammals and their corresponding gene trees are from the \href{https://www.orthomam.univ-montp2.fr}{OrthoMaM} database, and processed as in \textcite{latrille_genes_2022}.
-    OrthoMaM contains a total of $116$ mammalian reference sequences in v10c~\cite{ranwez_orthomam_2007, douzery_orthomam_2014, scornavacca_orthomam_2019}.
-    Genes located on the X, Y chromosomes and the mitochondrial genome were discarded from the analysis, because the level of polymorphism, which is necessary in the population-based analyses, is expected to be different in these three genomic regions.
+    Protein-coding DNA sequence alignments in placental mammals and their corresponding gene trees are from the \href{https://www.orthomam.univ-montp2.fr}{OrthoMaM} database, and were processed as in \textcite{latrille_genes_2023}.
+    OrthoMaM contains a total of $116$ mammalian reference sequences in v10c\cite{ranwez_orthomam_2007, douzery_orthomam_2014, scornavacca_orthomam_2019}.
+    Genes located on the X and Y chromosomes, and on the mitochondrial genome were discarded from the analysis because the level of polymorphism, which is necessary for population-based analyses, is expected to be different in these three regions compared to the autosomal genome.
     Sequences of species for which we used population-level polymorphism (see below), as well as their sister species, were removed from the analysis to ensure independence between the data used in the phylogenetic and population scales.
-    Altogether, our genome-wide dataset contains $14,509$ protein-coding DNA sequences for at most $87$ sequences of placental mammals.
+    Altogether, our genome-wide dataset contains $14,509$ protein-coding DNA sequences in $87$ placental mammals.
 
-    \subsection{Selection coefficient ($\Sphy$) in phylogeny-based method}
+    \subsection{Selection coefficient ($\Sphy$) in a phylogeny-based method}
     \label{subsec:s-phylogeny-method}
-    One of the most used methods to predict selective effects is SIFT (Sort Intolerant From Tolerant), which reliably detects deleterious mutations in many taxa~\cite{ng_sift_2003, vaser_sift_2016}.
-    However, SIFT scores are not interpretable as a selection coefficient.
-    Moreover, SIFT scores do not account for some key processes that can influence the abundance of an amino-acid in an alignment.
-    For instance, it does not take into account phylogenetic inertia, mutation biases, GC-biased gene conversion, or mutational paths.
-    Here, we analyzed the phylogenetic level data using mutation-selection models.
-    These models assume that the protein-coding sequence are at mutation-selection balance under a fixed fitness landscape characterized by a fitness vector over the $20$ amino acid at each site~\cite{yang_mutationselection_2008, halpern_evolutionary_1998, rodrigue_mechanistic_2010}.
+    We analyzed the phylogenetic level data using mutation-selection models.
+    These models assume that the protein-coding sequences are at mutation-selection balance under a fixed fitness landscape characterized by a fitness vector over the $20$ amino-acids at each site\cite{yang_mutationselection_2008, halpern_evolutionary_1998, rodrigue_mechanistic_2010}.
     Mathematically, the rate of non-synonymous substitution from codon $a$ to codon $b$ ($q_{a \mapsto b}^{(i)}$) at site $i$ of the sequence is equal to the rate of mutation of the underlying nucleotide change ($\mu_{a \mapsto b}$) multiplied by the scaled probability of fixation of the mutation ($\proba_{a \mapsto b}^{(i)}$).
-    The probability of fixation depends on the difference of scaled fitness of the amino acid encoded by the mutated codon ($F_b^{(i)}$) and the amino acid encoded by the original codon ($F_a^{(i)}$) at site $i$~\cite{wright_evolution_1931, fisher_genetical_1930}.
+    The probability of fixation depends on the difference between the scaled fitness of the amino-acid encoded by the mutated codon ($F_b^{(i)}$) and the amino acid encoded by the original codon ($F_a^{(i)}$) at site $i$\cite{wright_evolution_1931, fisher_genetical_1930}.
     The rate of substitution from codon $a$ to $b$ at a site $i$ is thus:
@@
     \end{equation}
-    Fitting the mutation-selection model on a multi-species sequence alignment leads to an estimation of the mutation rate matrix ($\UniDimArray{\mu}$) as well as the 20 amino acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$.
-    The selection coefficient for a mutation from codon $a$ to codon $b$ at site $i$ is defined :
+    Fitting the mutation-selection model on a multi-species sequence alignment leads to an estimation of the $4 \times 4$ nucleotide mutation rate matrix ($\UniDimArray{\mu}$) as well as the $20$ amino-acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$.
+    The selection coefficient for a mutation from codon $a$ to codon $b$ at site $i$ is defined as:
     \begin{equation}
@@
     %In the manuscript and the following material, the source ($a$) and target ($b$) codons as well as the site ($i$) are implicit and thus never explicitly written.
-    We used the Bayesian software \textit{BayesCode} (\url{https://github.com/ThibaultLatrille/bayescode}) to estimate the selection coefficients for each protein-coding genes in the mammal dataset.
-    We ran the Markov chain Monte-Carlo (MCMC) algorithm implemented in BayesCode for $2,000$ generations as described in \textcite{latrille_genes_2022}.
-    For each gene, after discarding a burn-in period of $1,000$ generations of MCMC, we obtained posterior mean estimates (over the $1,000$ generations left of MCMC) of the mutation rate matrix ($\UniDimArray{\mu}$) as well as the 20 amino acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$.
+    We used the Bayesian software \textit{BayesCode} (\url{https://github.com/ThibaultLatrille/bayescode}) to estimate the selection coefficients for each protein-coding gene in the mammalian dataset.
+    We ran the Markov chain Monte-Carlo (MCMC) algorithm implemented in BayesCode for $2,000$ generations as described in \textcite{latrille_genes_2023}.
+    For each gene, after discarding a burn-in period of $1,000$ generations of MCMC, we obtained posterior mean estimates (over the $1,000$ generations left of MCMC) of the mutation rate matrix ($\UniDimArray{\mu}$) as well as the $20$ amino-acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$.
 
@@
 
-    The genetic variants representing the population level polymorphism were obtained from the following species and respective available datasets: \textit{Equus caballus} (EquCab2 assembly in the EVA study PRJEB9799~\cite{alabri_whole_2020}), \textit{Bos taurus} (UMD3.1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}), \textit{Ovis aries} (Oar\_v3.1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}), \textit{Capra Hircus} (CHIR1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}, converted to ARS1 assembly with dbSNP identifiers\cite{sherry_dbsnp_2001}), \textit{Chlorocebus sabaeus} (ChlSab1.1 assembly in the EVA project PRJEB22989~\cite{svardal_ancient_2017}), \textit{Homo sapiens} (GRCh38 assembly from the 1000-genome project~\cite{consortium_integrated_2012, the1000genomesprojectconsortium_global_2015}).
+    The genetic variants representing the population level polymorphisms were obtained from the following species and respective available datasets: \textit{Equus caballus} (EquCab2 assembly in the EVA study PRJEB9799\cite{alabri_whole_2020}), \textit{Bos taurus} (UMD3.1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}), \textit{Ovis aries} (Oar\_v3.1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}), \textit{Capra hircus} (CHIR1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}, converted to ARS1 assembly with dbSNP identifiers\cite{sherry_dbsnp_2001}), \textit{Chlorocebus sabaeus} (ChlSab1.1 assembly in the EVA project PRJEB22989\cite{svardal_ancient_2017}), \textit{Homo sapiens} (GRCh38 assembly in the 1000-genome project\cite{zheng-bradley_alignment_2017}).
     In total, we analyzed 28 populations across the 6 different species with polymorphism data.
-    The data was processed as described in \textcite{latrille_genes_2022}.
+    The data was processed as described in \textcite{latrille_genes_2023}.
 
-    Genetic variants that were not found within a gene were not used in further analyses.
-    We also did not analyzed insertions and deletions and focused only on Single Nucleotide Polymorphisms (SNPs) with a single mutant allele, while stop codon variants were also discarded.
-    First, each SNP (chromosome, position, strand) in the focal species was matched to its relative position (chromosome, position, strand) in the protein-coding DNA alignment by first converting the genomic positions to relative position in the coding sequence (CDS) using gene annotation files (GTF format) downloaded from Ensembl (\url{ensembl.org}).
-    We then verified that the SNP downloaded from Ensembl were matching the reference in the CDS in FASTA format.
-    Second, the relative position in the CDS was converted to position in the multi-species sequence alignment (containing gaps) from OrthoMaM database (see section \ref{subsec:s-phylogeny-method}) by doing a global pairwise alignment, using the Biopython function pairwise2, between the CDS fasta and the sequence found in the alignment.
-    This conversion from genomic position to alignment position was only possible when the assembly used for SNP calling was the same as the one used in the alignment, the GTF annotations and the FASTA sequences.
-    SNPs were polarized using the $3$ closest outgroups found in the OrthoMam alignment with est-usfs v2.04~\cite{keightley_inferring_2018}.
+    Regarding our polymorphism dataset, only bi-allelic single nucleotide polymorphisms (SNPs) found within a gene were considered, while nonsense variants and indels were discarded.
+    To construct the dataset, we first recovered the location of each SNP (represented by its chromosome, position, and strand) in the focal species and matched it to its corresponding position in the coding sequence (CDS) using gene annotation files (GTF format) downloaded from Ensembl (\url{ensembl.org}).
+    We then verified that the SNP downloaded from Ensembl matched the reference in the CDS in FASTA format.
+    Next, the position in the CDS was converted to the corresponding position in the multi-species sequence alignment (containing gaps) from the OrthoMaM database (see section \ref{subsec:s-phylogeny-method}) for the corresponging gene, by doing a global pairwise alignment (Biopython function pairwise2).
+    This conversion from genomic position to alignment position was only possible when the assembly used for SNP-calling was the same as the one used in the OrthoMaM alignment, the GTF annotations and the FASTA sequences.
+    SNPs were polarized using the three closest outgroups found in the OrthoMaM alignment with est-usfs v2.04\cite{keightley_inferring_2018}.
 
     \subsection{Mutational opportunities}
-    \label{subsec:nunber-of-sites}.
-    For each population with polymorphism data available, the polarized SNPs (ancestral and derived alleles) were used to reconstruct the ancestral DNA sequence, containing only substitutions and no segregating polymorphisms.
+    \label{subsec:nunber-of-sites}
+    For any new mutation, its mutational opportunities refer to its likelihood of falling into a certain category (synonymous, deleterious, nearly-neutral, or beneficial).
+    Deriving such opportunities is necessary to estimate the strength of selection exerted at the population scale since different categories might have different mutational opportunities and hence polymorphism and divergence need to be corrected accordingly (see section \ref{subsec:substitution-mapping-in-the-terminal-branch}, \ref{subsec:s-polymorphism-method} and \ref{subsec:precisison_recall}).
+    To calculate mutational opportunities we reconstructed the ancestral genome of each of the 28 populations, which differs from the corresponding species' reference genome since it accounts for the variability present in the specific population.
+    So, for each population we used the polarized SNPs to reconstruct the ancestral DNA sequence, containing only substitutions and no segregating polymorphisms.
     If a SNP was still segregating in the population, the ancestral version of the SNP was used.
-    However, if the derived allele was shared by all individuals in the population, the allele was considered fixed and the derived allele of the SNP was used as the ancestral.
-    This ancestral genome is different from the reference genome as it accounts for the variability present in the population analysed.
-    From this reconstructed ancestral genome at the base of the population genealogy, all possible mutations were computed, weighted by the mutation rate between nucleotide ($\mu$), which was estimated at the phylogenetic scale.
-    The total mutation rate for synonymous mutations, called $\mu_{\textrm{syn}}$, was estimated as the sum across the whole genome.
-    Similarly, the total mutation rate for each class of selection $\Sphyclass$, called $\mu\left( \Sphyclass \right)$, was estimated as the sum across all non-synonymous mutations if their selection coefficient at the phylogenetic scale ($\Sphy$) was in the class $\Sphy \in \Sphyclass$ (e.g.
-$\Sphyclass = \divAdv$).
-    Finally, the mutational opportunities ($L \left( \Sphyclass \right)$) for each class of selection coefficient ($\Sphyclass$) was finally computed as the total number of sites across the genome ($L_{tot}$) weighted by the ratio of the aggregated mutations rates falling in the class ($\mu\left( \Sphyclass \right)$) over the total mutation rate for all possible mutations ($\mu_{tot}$) as:
-    \begin{align}
-        L \left( \Sphyclass \right) &= L_{tot} \frac{\mu\left( \Sphyclass \right)}{\mu_{tot}}, \\
-        L_{\textrm{syn}} &= L_{tot} \frac{\mu_{\textrm{syn}}}{\mu_{tot}}.
-    \end{align}
+
+    From the reconstructed ancestral genome at the base of the population genealogy, all possible mutations were computed, weighted by the instantaneous rate of change between nucleotides obtained from the mutation rate matrix ($\UniDimArray{\mu}$, see \ref{subsec:s-phylogeny-method}), summing to $\mu_{\text{tot}}$ across the whole genome, and to $\mu_{\text{syn}}$ when restricted to synonymous mutations.
+    Finally, the mutational opportunities for synonymous mutations was computed as the total number of sites across the genome ($L_{\text{tot}}$) weighted by the proportion of synonymous mutations among all possible mutations as:
+    \begin{equation}
+        L_{\text{syn}} = L_{\text{tot}} \frac{\mu_{\text{syn}}}{\mu_{\text{tot}}}.
+    \end{equation}
+
+    Similarly, for non-synonymous mutations, the total mutation rate for each class of selection $\Sphyclass \in \{\Sphy^{\text{d}}, \Sphy^{\text{n}}, \Sphy^{\text{b}} \}$, called $\mu\left( \Sphyclass \right)$, was estimated as the sum across all non-synonymous mutations if their selection coefficient at the phylogenetic scale is in the class ($\Sphy \in \Sphyclass$).
+    Accordingly, the mutational opportunities ($L \left( \Sphyclass \right)$) for each class of selection coefficient ($\Sphyclass$) was finally computed as the total number of sites across the genome ($L_{\text{tot}}$) weighted by the ratio of the aggregated mutations rates falling in the class ($\mu\left( \Sphyclass \right)$)
+    \begin{equation}
+        L \left( \Sphyclass \right) = L_{\text{tot}} \frac{\mu\left( \Sphyclass \right)}{\mu_{\text{tot}}},
+    \end{equation}
+
+    Finally, $\proba [ \Sphyclass ]$ is the probability for a non-synonymous mutation to be in the class $\Sphyclass$, thus computed as:
+    \begin{equation}
+        \proba[\Sphyclass] = \frac{L\left( \Sphyclass \right)}{\sum_{\mathcal{D}\in \{\Sphy^{\text{d}}, \Sphy^{\text{n}}, \Sphy^{\text{b}} \} } L\left(\mathcal{D} \right)},
+        \label{eq:proba-dfe-mutsel}
+    \end{equation}
 
@@
     For each gene and for each population with polymorphism data available, the genome at the base of the population genealogy was reconstructed (see section \ref{subsec:nunber-of-sites}).
-    We used the ancestral genome reconstructed at the base of the population genealogy and the $3$ closest outgroups found in the OrthoMam alignment to infer the ancestral protein-coding DNA sequences for each node of the 4-taxa tree by applying the M5 codon model (gamma site rate variation) as implemented in FastML.v3.11~\cite{ashkenazy_fastml_2012}.
+    We used the ancestral genome reconstructed at the base of the population genealogy and the three closest outgroups found in the OrthoMaM alignment to infer the ancestral protein-coding DNA sequences for each node of the 4-taxa tree by applying the M5 codon model (gamma site rate variation) as implemented in FastML.v3.11\cite{ashkenazy_fastml_2012}.
     All polarized codon substitutions were then obtained by comparing the ancestral protein-coding DNA sequences before the split to the sister species (closest outgroup) to the genome at the base of the population genealogy.
-    We considered \textit{Ceratotherium simum simum} as \textit{Equus caballus} sister species; \textit{Bison bison bison} as \textit{Bos taurus} sister species; \textit{Pantholops hodgsonii} as \textit{Ovis aries} sister species; \textit{Pantholops hodgsonii} as \textit{Capra Hircus} sister species; \textit{Macaca mulatta} as \textit{Chlorocebus sabaeus} sister species and finally we considered \textit{Pan troglodytes} as \textit{Homo sapiens} sister species.
+    We considered \textit{Ceratotherium simum simum} as \textit{Equus caballus} sister species; \textit{Bison bison bison} as \textit{Bos taurus} sister species; \textit{Pantholops hodgsonii} as \textit{Ovis aries} sister species; \textit{Pantholops hodgsonii} as \textit{Capra hircus} sister species; \textit{Macaca mulatta} as \textit{Chlorocebus sabaeus} sister species and finally we considered \textit{Pan troglodytes} as \textit{Homo sapiens} sister species.
     The selection coefficient ($\Sphy$) of each substitution was then obtained by comparing the difference in amino acid fitnesses for each polarized non-synonymous codon substitution, by referring to the site-specific fitness profile obtained in the phylogeny-based method (see~\ref{subsec:s-phylogeny-method}).
@@
     \begin{align}
+        \begin{dcases}
             \dn \left( \Sphyclass \right) &= \dfrac{D\left( \Sphyclass \right)}{L \left( \Sphyclass \right)}, \\
-        \ds &= \dfrac{D_{\textrm{syn}}}{L_{\textrm{syn}}},
+            \ds &= \dfrac{D_{\text{syn}}}{L_{\text{syn}}},
+        \end{dcases}
     \end{align}
-    where $D \left( \Sphyclass \right) $ was the number of non-synonymous substitutions in the class $\Sphyclass$, $D_{\textrm{syn}}$ was the number of synonymous substitutions across the genome, while $L \left( \Sphyclass \right)$ and $L_{\textrm{syn}}$ were the number of non-synonymous and synonymous mutational opportunities as defined in section \ref{subsec:nunber-of-sites}.
-    The fraction of non-adaptive beneficial substitutions $R(\dnds)$ was computed as the ratio between the difference in the numbers of beneficial substitutions ($\dnds$), which were due to beneficial back-mutations, and the estimated divergence when we removed beneficial back-mutations $\dn (\Sphy < 0) / \ds$, over $\dnds$.
+    where $D \left( \Sphyclass \right) $ was the number of non-synonymous substitutions in the class $\Sphyclass$, $D_{\text{syn}}$ was the number of synonymous substitutions across the genome, while $L \left( \Sphyclass \right)$ and $L_{\text{syn}}$ were the number of non-synonymous and synonymous mutational opportunities as defined in section \ref{subsec:nunber-of-sites}.
+    $R(\dnds)$ was computed as the ratio between the difference in the numbers of beneficial substitutions ($\dnds$), which were due to beneficial back-mutations, and the estimated divergence when we removed beneficial back-mutations $\dn (\Sphy < 0) / \ds$, over $\dnds$.
     Of note, the quantities $R(\dn)$ and $R(\dnds)$ are equivalent due to simplification of the factor $\ds$:
     \begin{equation}
-        R(\dnds) = \dfrac{\dnds - \dn(\Sphy < 0) / \ds}{\dnds} = \dfrac{\dn - \dn(\Sphy < 0)}{\dn} = R(\dn)
+        R(\dnds) = \dfrac{\dnds - \dn(\Sphy < 0) / \ds}{\dnds} = \dfrac{\dn - \dn(\Sphy < 0)}{\dn} = R(\dn).
     \end{equation}
@@
     \label{subsec:s-polymorphism-method}
+    To obtain a quantitative estimate of the distribution of selection coefficients for each category of SNPs, we used the model polyDFE\cite{tataru_inference_2017, tataru_polydfe_2020}.
+    This model uses the count of derived alleles to infer the distribution of fitness effects (DFE).
     The probability to sample an allele at a given frequency (before fixation or extinction) is informative of its scaled selection coefficient at the population scale ($\Spop$).
     Pooled across many sites, the site-frequency spectrum (SFS) provides therefore information on the underlying $\Spop$ of mutations.
-    However, estimating a single $\Spop$ for all sampled mutations is biologically unrealistic and a distribution of fitness effects (DFE) of mutations is usually assumed~\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009}.
-    We used the software polyDFE~\cite{tataru_inference_2017, tataru_polydfe_2020} that implemented a mixture of a $\Gamma$ and Exponential distributions to model the DFE of non-synonymous mutations, while synonymous mutations are considered neutral.
+    However, estimating a single $\Spop$ for all sampled mutations is biologically unrealistic and a DFE of mutations is usually assumed\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009}.
+    The polyDFE\cite{tataru_inference_2017, tataru_polydfe_2020} software implements a mixture of a $\Gamma$ and exponential distributions to model the DFE of non-synonymous mutations, while synonymous mutations are considered neutral.
     The model estimates the parameters $\DelMean$ , $b$, $p_b$ and $\AdvMean$ for non-synonymous mutations as:
@@
     \end{equation}
-    where $\DelMean \leq -1 $ was the estimated mean of the DFE for $\Spop \leq 0$,
-    $b \geq 0.4$ was the estimated shape of the $\Gamma$ distribution,
-    $0 \leq p_b \leq 1$ was the estimated probability that $\Spop > 0$,
-    $\AdvMean \geq 1$ wass the estimated mean of the DFE for $\Spop > 0$,
-    and $f_{\Gamma}(x; m, b)$ was the density of the $\Gamma$ distribution with mean m and shape b, while $f_{e}(x; m)$ is the density of the Exponential distribution with mean $m$.
-    Once the DFE was fitted to the data, the proportion of beneficial ($\PpolyAdv$), nearly-neutral ($\PpolyNeutral$) and deleterious mutations ($\PpolyDel$) were given as:
+    where $\DelMean \leq -1 $ is the estimated mean of the DFE for $\Spop \leq 0$;
+    $b \geq 0.4$ is the estimated shape of the $\Gamma$ distribution;
+    $0 \leq p_b \leq 1$ is the estimated probability that $\Spop > 0$;
+    $\AdvMean \geq 1$ is the estimated mean of the DFE for $\Spop > 0$;
+    and $f_{\Gamma}(x; m, b)$ is the density of the $\Gamma$ distribution with mean $m$ and shape $b$, while $f_{e}(x; m)$ is the density of the exponential distribution with mean $m$.
+    Once the DFE is fitted to the data, the proportion of beneficial ($\PpolyAdv$), nearly-neutral ($\PpolyNeutral$) and deleterious mutations ($\PpolyDel$) are given as:
     \begin{align}
-        \PpolyAdv &= p_b \int_{1}^{+\infty} f_{e}(\Spop; \AdvMean) \der \Spop,  \label{eq:polyProbaAdv} \\
-        \PpolyNeutral &= p_b \int_{0}^{1} f_{e}(\Spop; \AdvMean) \der \Spop + \left( 1 - p_b \right) \int_{0}^{1} f_{\Gamma}(\Spop; -\DelMean, b) \der \Spop, \\
-        \PpolyDel &= \left( 1 - p_b \right) \int_{1}^{+\infty} f_{\Gamma}(\Spop; -\DelMean, b) \der \Spop. \label{eq:polyProbaDel}
+        \PpolyDel &= \proba [ \Spop < -1] = \left( 1 - p_b \right) \int_{1}^{+\infty} f_{\Gamma}(\Spop; -\DelMean, b) \der \Spop, \label{eq:polyProbaDel} \\
+        \PpolyNeutral &= \proba [ -1 < \Spop < 1] = p_b \int_{0}^{1} f_{e}(\Spop; \AdvMean) \der \Spop + \left( 1 - p_b \right) \int_{0}^{1} f_{\Gamma}(\Spop; -\DelMean, b) \der \Spop, \\
+        \PpolyAdv &= \proba [ \Spop > 1] = p_b \int_{1}^{+\infty} f_{e}(\Spop; \AdvMean) \der \Spop. \label{eq:polyProbaAdv}
     \end{align}
 
-    PolyDFE required one SFS for non-synonymous mutations and one for synonymous mutations (neutral expectation), as well as the number of sites on which each SFS was sampled.
+    PolyDFE requires one SFS for non-synonymous mutations and one for synonymous mutations (neutral expectation), as well as the number of sites on which each SFS was sampled namely the mutational opportunities ($L(\Sphyclass)$ and $L_{\text{syn}}$.
     For populations containing more than $8$ individuals, the site-frequency spectrum (SFS) was subsampled down to $16$ chromosomes ($8$ diploid individuals) without replacement (hyper-geometric distribution) to alleviate the effect of different sampling depth in the 28 populations.
@@
 
-    Using Bayes theorem, we obtained the probability for a beneficial mutation to be a back-mutation by estimating the probability that a mutation was a back-mutation ($\divAdv$) given that it was beneficial ($\polyAdv$), as:
+    \subsection{\textit{Precision} and \textit{recall}}
+    \label{subsec:precisison_recall}
+    For readability, we hereby give \textit{precision} and \textit{recall} for beneficial mutations ($\Sphy^{\text{b}} \coloneqq \Sphy > 1$ and $\Spop^{\text{b}} \coloneqq \Spop > 1$), but it can be obtained using the same derivation for the deleterious mutations ($\Sphy \text{ or } \Spop < -1$) and nearly-neutral mutations ($-1 < \Sphy \text{ or } \Spop < 1$).
+
+    \textit{Precision} is the ratio $TP / (TP + FP)$, where TP are \textit{true positives} ($\proba [ \Spop^{\text{b}} \cap  \Sphy^{\text{b}}]$) and FP are \textit{false positives} ($\proba [ \text{not } \Spop^{\text{b}} \cap \Sphy^{\text{b}}]$).
+    The denominator $(TP + FP)$ can be simplified using the law of total probability as:
     \begin{equation}
-        \proba \left[\divAdv \given \polyAdv\right] = \frac{\proba \left[\polyAdv \given \divAdv\right] \times \proba\left[\divAdv\right]}{\PpolyAdv},
+        \proba [ \Spop^{\text{b}} \cap \Sphy^{\text{b}}] + \proba [\text{not } \Spop^{\text{b}} \cap \Sphy^{\text{b}}] = \proba [ \Sphy^{\text{b}}],
+    \end{equation}
+    which corresponds to the total probability of a mutation to be a predicted positive ($\proba [ \Sphy^{\text{b}}]$).
+    Altogether, \textit{precision} for beneficial mutations can be written as conditional probability:
+    \begin{equation}
+        \frac{\proba [ \Spop^{\text{b}}  \cap  \Sphy^{\text{b}}]}{\proba [ \Sphy^{\text{b}}]} = \proba [ \Spop^{\text{b}}  \given  \Sphy^{\text{b}}].
+    \end{equation}
+    Namely, \textit{precision} corresponds to the probability for a back-mutation ($\Sphy^{\text{b}}$) to be effectively beneficial at the level of the population ($\Spop^{\text{b}}$).
+    This probability is obtained by restricting our analysis on SNPs that are predicted to be beneficial back-mutations (black fill for the category $\Sphy^{\text{b}}$ in fig~\ref{fig:homo-afr-results}D).
+
+    \textit{Recall} is the ratio $TP / (TP + FN)$, where TP are \textit{true positives} ($\proba [ \Spop^{\text{b}}  \cap  \Sphy^{\text{b}}]$) and FN are \textit{false negatives} ($\proba [ \Spop^{\text{b}}  \cap \text{not } \Sphy^{\text{b}}]$).
+    The denominator $(TP + FN)$ can be simplified using the law of total probability as:
+    \begin{equation}
+        \proba [ \Spop^{\text{b}}  \cap  \Sphy^{\text{b}}] + \proba [ \Spop^{\text{b}} \cap \text{not } \Sphy^{\text{b}}] = \proba [ \Spop^{\text{b}}],
+    \end{equation}
+    which corresponds to the total probability of a mutation to be a positive ($\proba [ \Spop^{\text{b}}]$).
+    Altogether, \textit{recall} for beneficial mutations can be written as conditional probability:
+    \begin{equation}
+        \frac{\proba [ \Spop^{\text{b}} \cap  \Sphy^{\text{b}}]}{\proba [ \Spop^{\text{b}}]} = \proba [ \Sphy^{\text{b}}  \given \Spop^{\text{b}} ].
+    \end{equation}
+    Namely, \textit{recall} corresponds to the probability for a beneficial mutation at the level of population ($\Spop^{\text{b}}$) to be a beneficial back-mutation ($\Sphy^{\text{b}}$).
+    Using Bayes theorem, \textit{recall} can be re-written as:
+    \begin{equation}
+        \proba [\Sphy^{\text{b}} \given \Spop^{\text{b}}] = \frac{\proba [\Spop^{\text{b}} \given \Sphy^{\text{b}}] \times \proba[\Sphy^{\text{b}}]}{\PpolyAdv},
         \label{eq:bayes}
     \end{equation}
-    where $\PpolyAdv$ was computed from all SNPS, $\proba \left[\polyAdv \given \divAdv\right]$ was obtained from the set of SNPs in the class $\Sphyclass = \divAdv$, and $\proba\left[\divAdv\right]$ was the probability for a new mutation to be inside the class $\divAdv$, thus computed as:
+    First, $\proba [\Spop^{\text{b}} \given \Sphy^{\text{b}}]$ is computed as above (\textit{precision}).
+    Second, $\proba [ \Sphy^{\text{b}} ]$ is obtained from equation \ref{eq:proba-dfe-mutsel}.
+    Finally, $\proba [ \Spop^{\text{b}} ]$ is the probability of mutation to be beneficial at the level of the population, which can be computed from the law of total probabilities as:
     \begin{equation}
-        \proba\left[\divAdv\right] = \frac{L\left( \Sphyclass = \divAdv \right)}{L_{tot}},
-        \label{eq:proba-dfe-mutsel}
+        \proba [ \Spop^{\text{b}} ] = \sum_{\Sphyclass \in \{\Sphy^{\text{d}}, \Sphy^{\text{n}}, \Sphy^{\text{b}} \} }\proba [\Spop^{\text{b}} \given \Sphyclass ] \times \proba [\Sphyclass ].
+        \label{eq:total_proba}
     \end{equation}
-
     \printbibliography

### 2023-04-03 manuscript/include-MutSel-non-adaptive.tex
Updated manuscript before NG corrections

@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Bos_taurus.IRBT.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins3Mask0.9/DFE.Bos_taurus.IRBT.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Bos_taurus.IRBT.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/ancestral_bins3Mask0.9/Bos_taurus.IRBT.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Bos_taurus.IRBT.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Bos_taurus.IRBT.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Bos_taurus.IRBT.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Bos_taurus.IRBT.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Bos_taurus.UGBT.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins3Mask0.9/DFE.Bos_taurus.UGBT.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Bos_taurus.UGBT.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/ancestral_bins3Mask0.9/Bos_taurus.UGBT.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Bos_taurus.UGBT.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Bos_taurus.UGBT.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Bos_taurus.UGBT.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Bos_taurus.UGBT.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.AUCH.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.AUCH.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.AUCH.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/ancestral_bins3Mask0.9/Capra_hircus.AUCH.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Capra_hircus.AUCH.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Capra_hircus.AUCH.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Capra_hircus.AUCH.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Capra_hircus.AUCH.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.FRCH.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.FRCH.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.FRCH.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/ancestral_bins3Mask0.9/Capra_hircus.FRCH.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Capra_hircus.FRCH.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Capra_hircus.FRCH.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Capra_hircus.FRCH.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Capra_hircus.FRCH.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.IRCA.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.IRCA.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.IRCA.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/ancestral_bins3Mask0.9/Capra_hircus.IRCA.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Capra_hircus.IRCA.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Capra_hircus.IRCA.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Capra_hircus.IRCA.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Capra_hircus.IRCA.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.IRCH.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.IRCH.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.IRCH.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/ancestral_bins3Mask0.9/Capra_hircus.IRCH.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Capra_hircus.IRCH.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Capra_hircus.IRCH.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Capra_hircus.IRCH.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Capra_hircus.IRCH.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.ITCH.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.ITCH.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.ITCH.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/ancestral_bins3Mask0.9/Capra_hircus.ITCH.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Capra_hircus.ITCH.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Capra_hircus.ITCH.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Capra_hircus.ITCH.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Capra_hircus.ITCH.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Capra_hircus.MOCH.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.MOCH.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Capra_hircus.MOCH.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/ancestral_bins3Mask0.9/Capra_hircus.MOCH.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Capra_hircus.MOCH.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Capra_hircus.MOCH.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Capra_hircus.MOCH.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Capra_hircus.MOCH.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Barbados.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.Barbados.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Barbados.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/ancestral_bins3Mask0.9/Chlorocebus_sabaeus.Barbados.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Barbados.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Chlorocebus_sabaeus.Barbados.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Barbados.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Chlorocebus_sabaeus.Barbados.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Central_African_Republic.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.Central_African_Republic.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Central_African_Republic.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/ancestral_bins3Mask0.9/Chlorocebus_sabaeus.Central_African_Republic.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Ethiopia.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.Ethiopia.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Ethiopia.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/ancestral_bins3Mask0.9/Chlorocebus_sabaeus.Ethiopia.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Gambia.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.Gambia.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Gambia.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/ancestral_bins3Mask0.9/Chlorocebus_sabaeus.Gambia.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Gambia.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Chlorocebus_sabaeus.Gambia.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Gambia.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Chlorocebus_sabaeus.Gambia.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Kenya.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.Kenya.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Kenya.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/ancestral_bins3Mask0.9/Chlorocebus_sabaeus.Kenya.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Kenya.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Chlorocebus_sabaeus.Kenya.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Kenya.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Chlorocebus_sabaeus.Kenya.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Nevis.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.Nevis.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Nevis.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/ancestral_bins3Mask0.9/Chlorocebus_sabaeus.Nevis.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Nevis.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Chlorocebus_sabaeus.Nevis.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Nevis.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Chlorocebus_sabaeus.Nevis.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Saint_Kitts.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.Saint_Kitts.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Saint_Kitts.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/ancestral_bins3Mask0.9/Chlorocebus_sabaeus.Saint_Kitts.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Saint_Kitts.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Chlorocebus_sabaeus.Saint_Kitts.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Saint_Kitts.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Chlorocebus_sabaeus.Saint_Kitts.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.South_Africa.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.South_Africa.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.South_Africa.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/ancestral_bins3Mask0.9/Chlorocebus_sabaeus.South_Africa.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.South_Africa.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Chlorocebus_sabaeus.South_Africa.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.South_Africa.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Chlorocebus_sabaeus.South_Africa.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Chlorocebus_sabaeus.Zambia.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.Zambia.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Chlorocebus_sabaeus.Zambia.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/ancestral_bins3Mask0.9/Chlorocebus_sabaeus.Zambia.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Zambia.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Chlorocebus_sabaeus.Zambia.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Chlorocebus_sabaeus.Zambia.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Chlorocebus_sabaeus.Zambia.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Equus_caballus.up.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins3Mask0.9/DFE.Equus_caballus.up.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Equus_caballus.up.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/ancestral_bins3Mask0.9/Equus_caballus.up.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Equus_caballus.up.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Equus_caballus.up.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Equus_caballus.up.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Equus_caballus.up.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.AFR.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins3Mask0.9/DFE.Homo_sapiens.AFR.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Homo_sapiens.AFR.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/ancestral_bins3Mask0.9/Homo_sapiens.AFR.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Homo_sapiens.AFR.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Homo_sapiens.AFR.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Homo_sapiens.AFR.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Homo_sapiens.AFR.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.AMR.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins3Mask0.9/DFE.Homo_sapiens.AMR.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Homo_sapiens.AMR.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/ancestral_bins3Mask0.9/Homo_sapiens.AMR.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Homo_sapiens.AMR.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Homo_sapiens.AMR.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Homo_sapiens.AMR.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Homo_sapiens.AMR.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.EAS.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins3Mask0.9/DFE.Homo_sapiens.EAS.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Homo_sapiens.EAS.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/ancestral_bins3Mask0.9/Homo_sapiens.EAS.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Homo_sapiens.EAS.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Homo_sapiens.EAS.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Homo_sapiens.EAS.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Homo_sapiens.EAS.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.EUR.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins3Mask0.9/DFE.Homo_sapiens.EUR.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Homo_sapiens.EUR.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/ancestral_bins3Mask0.9/Homo_sapiens.EUR.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Homo_sapiens.EUR.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Homo_sapiens.EUR.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Homo_sapiens.EUR.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Homo_sapiens.EUR.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Homo_sapiens.SAS.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins3Mask0.9/DFE.Homo_sapiens.SAS.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Homo_sapiens.SAS.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/ancestral_bins3Mask0.9/Homo_sapiens.SAS.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Homo_sapiens.SAS.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Homo_sapiens.SAS.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Homo_sapiens.SAS.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Homo_sapiens.SAS.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.IROA.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins3Mask0.9/DFE.Ovis_aries.IROA.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Ovis_aries.IROA.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/ancestral_bins3Mask0.9/Ovis_aries.IROA.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Ovis_aries.IROA.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Ovis_aries.IROA.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Ovis_aries.IROA.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Ovis_aries.IROA.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.IROO.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins3Mask0.9/DFE.Ovis_aries.IROO.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Ovis_aries.IROO.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/ancestral_bins3Mask0.9/Ovis_aries.IROO.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Ovis_aries.IROO.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Ovis_aries.IROO.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Ovis_aries.IROO.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Ovis_aries.IROO.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.IROV.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins3Mask0.9/DFE.Ovis_aries.IROV.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Ovis_aries.IROV.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/ancestral_bins3Mask0.9/Ovis_aries.IROV.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Ovis_aries.IROV.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Ovis_aries.IROV.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Ovis_aries.IROV.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Ovis_aries.IROV.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.ISGC.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins3Mask0.9/DFE.Ovis_aries.ISGC.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Ovis_aries.ISGC.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/ancestral_bins3Mask0.9/Ovis_aries.ISGC.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Ovis_aries.ISGC.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Ovis_aries.ISGC.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.4\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Ovis_aries.ISGC.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Ovis_aries.ISGC.MutSel.polyDFE_C.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins5/DFE.Ovis_aries.MOOA.MutSel.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/opportunities_bins3Mask0.9/DFE.Ovis_aries.MOOA.MutSel.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../data_processed/vcf_annotate_bins5/snps.Ovis_aries.MOOA.MutSel.histogram.pdf}
+    \includegraphics[width=\linewidth, page=1]{../data_processed/ancestral_bins3Mask0.9/Ovis_aries.MOOA.pdf}
 \end{minipage}
@@
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Ovis_aries.MOOA.MutSel-sfs.normalize.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Ovis_aries.MOOA.MutSel-sfs.normalize.pdf}
 \end{minipage}
 \begin{minipage}{0.49\linewidth}
-    \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/analysis/Ovis_aries.MOOA.MutSel.polyDFE_C.pdf}
+    \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC/analysis/Ovis_aries.MOOA.MutSel.polyDFE_C.pdf}
 \end{minipage}

### 2023-04-03 manuscript/main.tex
Updated manuscript before NG corrections

@@
 \newcommand{\Sphy}{S_{0}}
-\newcommand{\Sphyclass}{\mathcal{C}}
+\newcommand{\SphyDel}{\Sphy^{d}}
+\newcommand{\SphyNeu}{\Sphy^{n}}
+\newcommand{\SphyBen}{\Sphy^{b}}
+\newcommand{\Sphyclass}{x}
+\newcommand{\SphyclassAlt}{y}
 \newcommand{\given}{\mid}
 \newcommand{\Spop}{S}
-\newcommand{\PpolyDel}{\proba [ \Spop^{\text{d}}]}
-\newcommand{\PpolyNeutral}{\proba [ \Spop^{\text{n}} ]}
-\newcommand{\PpolyAdv}{\proba [ \Spop^{\text{b}} ]}
+\newcommand{\SpopDel}{\Spop^{d}}
+\newcommand{\SpopNeu}{\Spop^{n}}
+\newcommand{\SpopBen}{\Spop^{b}}
+\newcommand{\ProbaPopDel}{\proba [ \SpopDel]}
+\newcommand{\ProbaPopNeu}{\proba [ \SpopNeu ]}
+\newcommand{\ProbaPopBen}{\proba [ \SpopBen ]}
 \newcommand{\AdvMean}{\beta_b}
@@
 
-    Adaptation is considered one of the main processes shaping the diversity of forms and functions across the tree of life\cite{darwin_origin_1859}.
-    In evolution, adaptation is tightly linked to the notion of environmental change and to species responding to this change\cite{merrell_adaptive_1994, gavrilets_adaptive_2009}.
-    For adaptation to take place, there needs to be variation within populations, which at the molecular level mostly appears via mutations in the DNA sequence.
-    While neutral mutations will have no impact on the fitness of an individual, deleterious mutations have a negative effect and beneficial mutations lead their bearer toward a higher fitness.
-    Compared to a neutral mutation, a beneficial mutation is thus more likely to reach fixation in the population, resulting in a substitution at the species level.
-    Upon environmental change, adaptive beneficial mutations toward new fitness optima are more likely to rise in frequency, resulting in an increased substitution rate (fig.~\ref{fig:fitness-landscape}A).
-    Altogether, an accelerated substitution rate is thus commonly interpreted as a sign of adaptation\cite{mcdonald_adaptative_1991, smith_adaptive_2002, welch_estimating_2006}.
-    The current availability of large-scale genomic data and the development of theoretical models have enabled us to detect and quantify acceleration of substitution rates across genes and lineages, and these analyses have become common practice in evolutionary biology\cite{yang_statistical_2000, eyre-walker_genomic_2006, moutinho_variation_2019}.
-    These approaches have led to a better understanding of the processes determining the rates of molecular evolution.
-    However, they have had the collateral effect of associating beneficial mutations with adaptive evolution when, in fact, adaptive evolution is not the only process that can lead to beneficial mutations\cite{charlesworth_other_2007, mustonen_fitness_2009}.
+    Adaptation is one of the main processes shaping the diversity of forms and functions across the tree of life~\cite{darwin_origin_1859}.
+    Evolutionary adaptation is tightly linked to environmental change and species responding to this change~\cite{merrell_adaptive_1994, gavrilets_adaptive_2009}.
+    For adaptation to occur, there must be variation within populations, which mostly appears via mutations in the DNA sequence.
+    While neutral mutations will not impact an individual's fitness, deleterious mutations have a negative effect, and beneficial mutations improve their bearer's fitness.
+    A beneficial mutation is thus more likely than a neutral mutation to invade the population (fixation), resulting in a substitution at the species level.
+    Upon environmental change, because adaptive beneficial mutations toward new fitness optima are more likely, the number of substitutions also increases (fig.~\ref{fig:fitness-landscape}A).
+    An increased substitution rate is thus commonly interpreted as a sign of adaptation~\cite{mcdonald_adaptative_1991, smith_adaptive_2002, welch_estimating_2006}.
+    The availability of large-scale genomic data and the development of theoretical models have enabled the detection and quantification of substitution rate increases across genes and lineages~\cite{yang_statistical_2000, eyre-walker_genomic_2006, moutinho_variation_2019}.
+    These approaches, now common  practice in evolutionary biology, helped better understand the processes underpinning the rates of molecular evolution.
+    However, a collateral effect has been conflating beneficial mutations with adaptive evolution when adaptive evolution is not the only process that can lead to beneficial mutations~\cite{charlesworth_other_2007, mustonen_fitness_2009}.
 
-    In a constant environment, a deleterious mutation can reach fixation in the population by genetic drift\cite{Ohta1992}.
-    Subsequently, a new mutation restoring the ancestral fitness will thus be beneficial (fig.~\ref{fig:fitness-landscape}B), even though no change in the environment has occurred\cite{hartl_compensatory_1996, sella_application_2005, mustonen_fitness_2009, cvijovic_fate_2015}.
-    The restoration of the ancestral fitness can happen with a mutation occurring either at a different locus from that of the initial mutation, in which case it is referred to as a compensatory mutation\cite{hartl_compensatory_1996, mustonen_fitness_2009}, or at the same locus of the initial mutation, referred to as a beneficial back-mutation\cite{piganeau_estimating_2003, charlesworth_other_2007}.
-    Now, while compensatory mutations induce genetic changes at the sequence level, and thus genetic diversification, beneficial back-mutations reduce the inter-specific genetic diversity and do not contribute to genetic innovation.
-    Although beneficial back-mutations were considered negligible in the enunciation of the nearly-neutral theory by Tomoko Ohta\cite{Ohta1992}, their importance during a population size expansion has been acknowledged more recently\cite{charlesworth_other_2007}.
-    However, differentiating between an adaptive mutation and a beneficial back-mutation has remained challenging\cite{chi_detecting_2020}.
-    In this study, we seek to find empirical evidence for beneficial back-mutations and to test long-standing questions in molecular evolution such as how common are beneficial back-mutations, and
-    what is the probability for any beneficial mutation observed in current populations to be a back-mutation.
-    By addressing these questions we provide novel insight on the process of adaptation and, more broadly, on how natural selection has affected protein-coding DNA sequences throughout evolution.
+    In a constant environment, a deleterious mutation can reach fixation by genetic drift~\cite{Ohta1992}.
+    A new mutation restoring the ancestral fitness will thus be beneficial (fig.~\ref{fig:fitness-landscape}B), even though the environment has not changed~\cite{hartl_compensatory_1996, sella_application_2005, mustonen_fitness_2009, cvijovic_fate_2015}.
+    The restoration of the ancestral fitness can either happen through a mutation at a different locus – called a compensatory mutation~\cite{hartl_compensatory_1996, mustonen_fitness_2009}, or at the locus of the initial mutation – called a beneficial back-mutation~\cite{piganeau_estimating_2003, charlesworth_other_2007}.
+    While compensatory mutations change the sequence and thus induce genetic diversification, beneficial back-mutations reduce the genetic diversity and do not contribute to genetic innovation.
+    Although Tomoko Ohta considered beneficial back-mutations negligible in her nearly-neutral theory~\cite{Ohta1992}, their importance has now been acknowledged for expanding populations~\cite{charlesworth_other_2007}.
+    However, differentiating between an adaptive mutation and a beneficial back-mutation remains challenging\cite{chi_detecting_2020}.
+    In this study, we seek empirical evidence for beneficial back-mutations and test long-standing related questions, such as how common they are, and what the probability is for any beneficial mutation observed in current populations to be a back-mutation.
+    By addressing these questions, we provide novel insight into the process of adaptation and, more broadly, into how natural selection has affected protein-coding DNA sequences throughout evolution.
 
+\section*{Results}
     \subsection*{Fitness landscape reconstruction}
 
-    An adaptive mutation responding to a change in the environment or a beneficial back-mutation have equivalent consequences for their bearer\cite{charlesworth_other_2007}.
+    An adaptive mutation responding to a change in the environment or a beneficial back-mutation have equivalent consequences for their bearer~\cite{charlesworth_other_2007}.
     Similarly, at the level of the population, both types of mutations will result in a positive transmission bias of the beneficial allele.
@@
     While adaptive mutations promote phenotype diversification (fig.~\ref{fig:fitness-landscape}C), beneficial back-mutations promote phenotype stability and may help preserve well established biological systems (fig.~\ref{fig:fitness-landscape}D).
-    Additionally, the direction of adaptive evolution is unpredictable because it is caused by an unpredictable change in the environment and, hence, in the underlying fitness landscape\cite{bazykin_changing_2015}.
+    Additionally, the direction of adaptive evolution is unpredictable because it is caused by an unpredictable change in the environment and, hence, in the underlying fitness landscape~\cite{bazykin_changing_2015}.
     On the other hand, beneficial back-mutations are predictable if the underlying stable fitness landscape is known because changes from non-optimal amino acids to optimal ones will be expected.
-    In this context, the mutation-selection framework permits to relate the patterns of substitution along a phylogeny to the underlying fitness landscape\cite{halpern_evolutionary_1998, mccandlish_modeling_2014}.
-    Such mutation-selection models applied to protein coding DNA sequences allow us to estimate relative fitnesses for all amino-acids for each site of the sequence, explicitly assuming that the underlying fitness landscape is stable along the phylogenetic tree\cite{rodrigue_mechanistic_2010, tamuri_estimating_2012, rodrigue_detecting_2017}.
+    In this context, the mutation-selection framework permits to relate the patterns of substitution along a phylogeny to the underlying fitness landscape~\cite{halpern_evolutionary_1998, mccandlish_modeling_2014}.
+    Such mutation-selection models applied to protein coding DNA sequences allow us to estimate relative fitnesses for all amino-acids for each site of the sequence, explicitly assuming that the underlying fitness landscape is stable along the phylogenetic tree~\cite{rodrigue_mechanistic_2010, tamuri_estimating_2012, rodrigue_detecting_2017}.
     Importantly, because mutation-selection models at the phylogenetic scale are based on population-genetics equations, their estimates of fitness effects are directly interpretable as fitness effects for an individual within a population.
-    %These methods account for phylogenetic relationships, the structure of the genetic code and accommodate for underlying mutational biases\cite{rodrigue_mechanistic_2010, tamuri_estimating_2012, latrille_improved_2022}.
+    %These methods account for phylogenetic relationships, the structure of the genetic code and accommodate for underlying mutational biases~\cite{rodrigue_mechanistic_2010, tamuri_estimating_2012, latrille_improved_2022}.
 
@@
     The placental mammals represent an excellent study system to perform such analysis.
-    Having originated $\sim$100 Mya\cite{kumar_timetree_2017}, they diversified quickly.
-    Additionally, polymorphism data are available for many species\cite{howe_ensembl_2021} as high quality protein-coding DNA alignments across the genome\cite{ranwez_orthomam_2007, scornavacca_orthomam_2019}.
+    Having originated $\sim$100 Mya~\cite{kumar_timetree_2017}, they diversified quickly.
+    Additionally, polymorphism data are available for many species~\cite{howe_ensembl_2021} as high quality protein-coding DNA alignments across the genome~\cite{ranwez_orthomam_2007, scornavacca_orthomam_2019}.
     By restricting our analysis to protein-coding orthologous genes across all the phylogeny, we restrict our analysis to genes mostly under functional constrains across mammals.
@@
     From the fitness landscape, we can calculate the scaled selection coefficient $\Sphy$ for any possible amino-acid change at each position.
-    From the selection coefficient, we can classify any mutation as either a deleterious mutation toward a less fit amino-acid ($\Sphy^{\text{d}}$), a nearly-neutral mutation ($\Sphy^{\text{n}}$) or a beneficial back-mutation toward a known fitter amino-acid ($\Sphy^{\text{b}}$).
+    From the selection coefficient, we can classify any mutation as either a deleterious mutation toward a less fit amino-acid ($\SphyDel$), a nearly-neutral mutation ($\SphyNeu$) or a beneficial back-mutation toward a known fitter amino-acid ($\SphyBen$).
     Having identified which potential DNA changes represent beneficial back-mutations (fig~\ref{fig:method}B), we retrieved polymorphism data from 28 populations belonging to 6 genera (\textit{Equus}, \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus} and \textit{Homo}) to assess the presence of beneficial back-mutations at the population scale.
@@
             For every possible mutation, the difference in amino-acid fitness before and after the mutation allows us to compute the selection coefficient at the phylogenetic scale ($\Sphy$).
-            Mutations with $\Sphy < -1$ are considered deleterious ($\Sphy^{\text{d}}$ in red), and mutations with $-1 < \Sphy < 1$ are considered nearly-neutral ($\Sphy^{\text{n}}$ in green).
-            Mutations with $\Sphy > 1$ are toward a fitter amino-acids, and thus are considered beneficial back-mutations ($\Sphy^{\text{b}}$ in green blue), repairing existing functions (B).
+            Mutations with $\Sphy < -1$ are considered deleterious ($\SphyDel$ in red), and mutations with $-1 < \Sphy < 1$ are considered nearly-neutral ($\SphyNeu$ in green).
+            Mutations with $\Sphy > 1$ are toward a fitter amino-acids, and thus are considered beneficial back-mutations ($\SphyBen$ in blue), repairing existing functions (B).
             At the population scale (C), each observed single nucleotide polymorphism (SNP) segregating in the population is classified according to its $\Sphy$ value.
@@
             Together, substitutions and polymorphisms are contrasted to synonymous changes used as a neutral expectation such as estimate selection coefficients at the population scale ($\Spop$).
-            For each class of selection ($\Sphy^{\text{b}}$, $\Sphy^{\text{n}}$, $\Sphy^{\text{d}}$), we can thus assess whether $\Sphy$ predicts $\Spop$ (E), and compute \textit{precision} (F-G) and \textit{recall} (F-H) for each class.
-            The \textit{recall} value for the class $\Sphy^{\text{b}}$ is the probability of back-mutations among all beneficial ones (H).
+            For each class of selection ($\SphyBen$, $\SphyNeu$, $\SphyDel$), we can thus assess whether $\Sphy$ predicts $\Spop$ (E), and compute \textit{precision} (F-G) and \textit{recall} (F-H) for each class.
+            The \textit{recall} value for the class $\SphyBen$ is the probability of back-mutations among all beneficial ones (H).
         }
@@
     Importantly, the mammalian alignment used to estimate amino-acid fitness landscape does not include the genera for which we reconstructed the substitutions, to avoid fallacy and circularity in the reasoning.
-    Because $\Sphy$ was based on estimation of fitness effects at the mammalian scale, mutations with $\Sphy>1$ were considered beneficial back-mutations ($\Sphy^{\text{b}}$), toward a fitter amino acid.
-    Among all the substitutions that were found in each terminal branch, between 10 and 13\% were $\Sphy^{\text{b}}$ (table~S1).
+    Because $\Sphy$ was based on estimation of fitness effects at the mammalian scale, mutations with $\Sphy>1$ were considered beneficial back-mutations ($\SphyBen$), toward a fitter amino acid.
+    Among all the substitutions that were found in each terminal branch, between 10 and 13\% were $\SphyBen$ (table~S1).
     In principle, beneficial back-mutations are bound to reach fixation more often than neutral substitutions.
-    Hence, we calculated the $\dnds$ ratio of non-synonymous over synonymous divergence for all terminal lineages, restricting the non-synonymous changes to our set of $\Sphy^{\text{b}}$.
-    We obtained values between 1.15 and 1.68 in the different lineages (table~S1), implying that $\Sphy^{\text{b}}$ reached fixation more frequently than synonymous mutations that are supposed to be neutral, which means that these back-mutations are effectively beneficial.
+    Hence, we calculated the $\dnds$ ratio of non-synonymous over synonymous divergence for all terminal lineages, restricting the non-synonymous changes to our set of $\SphyBen$.
+    We obtained values between 1.15 and 1.68 in the different lineages (table~S1), implying that $\SphyBen$ reached fixation more frequently than synonymous mutations that are supposed to be neutral, which means that these back-mutations are effectively beneficial.
 
@@
     To achieve this, we reconstructed the ancestral genome of each population to polarize single nucleotide polymorphism (SNPS) segregating in the population.
-    The scaled selection coefficient ($\Sphy$) predicted for every non-synonymous SNPs allow us to classify them as either $\Sphy^{\text{d}}$, $\Sphy^{\text{n}}$ or $\Sphy^{\text{b}}$ (fig.~\ref{fig:method}B-C).
+    The scaled selection coefficient ($\Sphy$) predicted for every non-synonymous SNPs allow us to classify them as either $\SphyDel$, $\SphyNeu$ or $\SphyBen$ (fig.~\ref{fig:method}B-C).
 
-    In humans, some SNPs have been associated to specific clinical prognosis terms\cite{landrum_clinvar_2018}.
-Those clinical terms have been obtained by clinical evaluation of the impact of variants on human Mendelian disorders\cite{landrum_clinvar_2018}.
+    In humans, some SNPs have been associated to specific clinical prognosis terms~\cite{landrum_clinvar_2018}.
+Those clinical terms have been obtained by clinical evaluation of the impact of variants on human Mendelian disorders~\cite{landrum_clinvar_2018}.
 Thus they provide an orthogonal estimate of the effect of a mutation on human health, giving us an opportunity to evaluate whether this effect is in accordance with its predicted fitness effect.
-    To do so, we investigated whether the non-synonymous SNPs classified as $\Sphy^{\text{d}}$ or as $\Sphy^{\text{b}}$ showed an enrichment in specific clinical terms in comparison to SNPs classified as $\Sphy^{\text{n}}$.
+    To do so, we investigated whether the non-synonymous SNPs classified as $\SphyDel$ or as $\SphyBen$ showed an enrichment in specific clinical terms in comparison to SNPs classified as $\SphyNeu$.
     Our results show that SNPs predicted as deleterious are associated to clinical terms such as \textit{Likely Pathogenic} and \textit{Pathogenic}, implying that, in general, the selective pressure of a mutation exerted across mammals is also predictive of its clinical effect in humans (table~S6).
@@
     For instance, deleterious SNPs are usually segregating at lower frequencies because of the effect of purifying selection, which tends to remove them from the population.
-    By gathering information across many SNPs, it is possible to estimate the distribution of fitness effects (DFE) at the population scale, taking synonymous SNPs as a neutral expectation\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009, galtier_adaptive_2016, tataru_inference_2017}.
-    From the estimated DFE, we can derive the proportion of beneficial mutations ($\PpolyAdv$), nearly-neutral mutations ($\PpolyNeutral$) and deleterious mutations ($\PpolyDel$) at the population scale.
+    By gathering information across many SNPs, it is possible to estimate the distribution of fitness effects (DFE) at the population scale, taking synonymous SNPs as a neutral expectation~\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009, galtier_adaptive_2016, tataru_inference_2017}.
+    From the estimated DFE, we can derive the proportion of beneficial mutations ($\ProbaPopBen$), nearly-neutral mutations ($\ProbaPopNeu$) and deleterious mutations ($\ProbaPopDel$) at the population scale.
     These approaches offer a unique opportunity to contrast selection coefficients estimated at the population scale ($\Spop$) and at the phylogenetic scale ($\Sphy$).
 
-    Across our classes of selection ($\Sphy^{\text{d}}$, $\Sphy^{\text{n}}$ and $\Sphy^{\text{b}}$), one can ultimately estimate the proportion of false positives and false negatives, leading to an estimation of \textit{precision} and \textit{recall} (see Materials \& Methods).
+    Across our classes of selection ($\SphyDel$, $\SphyNeu$ and $\SphyBen$), one can ultimately estimate the proportion of false positives and false negatives, leading to an estimation of \textit{precision} and \textit{recall} (see Materials \& Methods).
     Across 28 populations of different mammal species, mutations predicted to be deleterious at the phylogenetic scale were indeed purged at the population scale, with a \textit{precision} in the range of 89--97\% (table.~\ref{table:proba}).
@@
 
-    Mutations predicted as $\Sphy^{\text{n}}$ were effectively composed of a mix of neutral and selected mutations with varying \textit{precision} (18--74\%) and \textit{recall} (21--52\%) across the different populations (table.~\ref{table:proba}).
+    Mutations predicted as $\SphyNeu$ were effectively composed of a mix of neutral and selected mutations with varying \textit{precision} (18--74\%) and \textit{recall} (21--52\%) across the different populations (table.~\ref{table:proba}).
     The variable proportions found between populations can be explained by the effective number of individuals in the population ($\Ne$), which is known to be a major driver of selection efficacy.
@@
     %Of note, mutations with $\Sphy>1$ only represented ca.~1.5\% of all possible new mutations, but ca.~8.5\% of all observed mutations in the population (blue in fig.~\ref{fig:homo-afr-results}A-B, table~S3).
-    Finally, mutations predicted to be beneficial back-mutations based on the selection coefficients at the phylogenetic scale ($\Sphy^{\text{b}}$) were indeed beneficial for individuals currently bearing them, with a precision in the range of 15--52\% (table.~\ref{table:proba}).
+    Finally, mutations predicted to be beneficial back-mutations based on the selection coefficients at the phylogenetic scale ($\SphyBen$) were indeed beneficial for individuals currently bearing them, with a precision in the range of 15--52\% (table.~\ref{table:proba}).
     This result confirms that selection towards amino acids that are restoring existing functions is ongoing in these populations.
-    Importantly, the \textit{recall} value in this case, computed as $\proba [ \Sphy^{\text{b}}  \given  \Spop^{\text{b}}]$, is the probability for a beneficial mutation at the population scale to be a beneficial back-mutation, that is, going toward a fitter amino-acid (fig.~\ref{fig:method}F).
+    Importantly, the \textit{recall} value in this case, computed as $\proba [ \SphyBen  \given  \SpopBen]$, is the probability for a beneficial mutation at the population scale to be a beneficial back-mutation, that is, going toward a fitter amino-acid (fig.~\ref{fig:method}F).
     In other words, the \textit{recall} value quantifies the amount of beneficial mutations that are restoring damaged genomes instead of creating adaptive innovations.
@@
             (A) Distribution of fitness effects ($\Sphy$), predicted for all possible mutations away from the ancestral human genome.
-            Mutations are divided into three classes of selection: deleterious ($\Sphy^{\text{d}}$ in red), nearly-neutral ($\Sphy^{\text{n}}$ in green) and beneficial ($\Sphy^{\text{b}}$ blue, supposedly beneficial back-mutations).
+            Mutations are divided into three classes of selection: deleterious ($\SphyDel$ in red), nearly-neutral ($\SphyNeu$ in green) and beneficial ($\SphyBen$ blue, supposedly beneficial back-mutations).
             (B) Distribution of fitness effects ($\Sphy$) for all observed substitutions along the \textit{Homo} branch after the \textit{Homo}-\textit{Pan} splits.
-            If there are less substitutions observed than expected, this class is thus undergoing purifying selection, as is the case of for $\Sphy^{\text{d}}$.
+            If there are less substitutions observed than expected, this class is thus undergoing purifying selection, as is the case of for $\SphyDel$.
             (C) The site-frequency spectrum (SFS) in humans of African descent for a random sample of 16 alleles (mean in solid line and standard deviation in color shade) for each class of selection and for synonymous mutations, which are supposedly neutral (black).
@@
             At high frequencies, deleterious mutations are underrepresented.
-            (D) Proportion of beneficial $\PpolyAdv$, nearly-neutral $\PpolyNeutral$ and deleterious mutations $\PpolyDel$ estimated at the population scale for each class of selection at the phylogenetic scale.
+            (D) Proportion of beneficial $\ProbaPopBen$, nearly-neutral $\ProbaPopNeu$ and deleterious mutations $\ProbaPopDel$ estimated at the population scale for each class of selection at the phylogenetic scale.
 Proportions depicted here are not weighted by mutational opportunities.
@@
                 \multicolumn{3}{||c||}{} &
-                \multicolumn{2}{c||}{\shortstack{\textbf{Deleterious mutations} \\ $\bm{\Spop^{\text{d}} \coloneqq \Spop<-1}$ \\ $\bm{\Sphy^{\text{d}} \coloneqq \Sphy<-1}$}} &
-                \multicolumn{2}{c||}{\shortstack{\textbf{Nearly-neutral mutations} \\ $\bm{\Spop^{\text{n}} \coloneqq -1<\Spop<1}$ \\ $\bm{\Sphy^{\text{n}} \coloneqq -1<\Sphy<1}$}} &
-                \multicolumn{2}{c||}{\shortstack{\textbf{Beneficial mutations} \\ $\bm{\Spop^{\text{b}} \coloneqq \Spop>1}$ \\ $\bm{\Sphy^{\text{b}} \coloneqq \Sphy>1}$}}
+                \multicolumn{2}{c||}{\shortstack{\textbf{Deleterious mutations} \\ $\bm{\SpopDel \coloneqq \Spop<-1}$ \\ $\bm{\SphyDel \coloneqq \Sphy<-1}$}} &
+                \multicolumn{2}{c||}{\shortstack{\textbf{Nearly-neutral mutations} \\ $\bm{\SpopNeu \coloneqq -1<\Spop<1}$ \\ $\bm{\SphyNeu \coloneqq -1<\Sphy<1}$}} &
+                \multicolumn{2}{c||}{\shortstack{\textbf{Beneficial mutations} \\ $\bm{\SpopBen \coloneqq \Spop>1}$ \\ $\bm{\SphyBen \coloneqq \Sphy>1}$}}
                 \\ \hline
@@
                 $\bm{\pi_{\text{S}}}$ &
-                \makecell{\textbf{Precision} \\ $\bm{\proba [\Spop^{\text{d}} \given \Sphy^{\text{d}}]}$} &
-                \makecell{\textbf{Recall} \\ $\bm{\proba [\Sphy^{\text{d}} \given \Spop^{\text{d}}]}$}             &
-                \makecell{\textbf{Precision}      \\ $\bm{\proba [\Spop^{\text{n}} \given \Sphy^{\text{n}}]}$}                 &
-                \makecell{\textbf{Recall}          \\ $\bm{\proba [\Sphy^{\text{n}} \given \Spop^{\text{n}}]}$}               &
-                \makecell{\textbf{Precision}          \\ $\bm{\proba [\Spop^{\text{b}} \given \Sphy^{\text{b}}]}$}            &
-                \makecell{\textbf{Recall}        \\ $\bm{\proba [\Sphy^{\text{b}} \given \Spop^{\text{b}}]}$}
+                \makecell{\textbf{Precision} \\ $\bm{\proba [\SpopDel \given \SphyDel]}$} &
+                \makecell{\textbf{Recall} \\ $\bm{\proba [\SphyDel \given \SpopDel]}$}             &
+                \makecell{\textbf{Precision}      \\ $\bm{\proba [\SpopNeu \given \SphyNeu]}$}                 &
+                \makecell{\textbf{Recall}          \\ $\bm{\proba [\SphyNeu \given \SpopNeu]}$}               &
+                \makecell{\textbf{Precision}          \\ $\bm{\proba [\SpopBen \given \SphyBen]}$}            &
+                \makecell{\textbf{Recall}        \\ $\bm{\proba [\SphyBen \given \SpopBen]}$}
                 \\   \midrule
@@
             Conversely, \textit{recall} is the recovered estimation of $\Sphy$ given selection coefficient at the population scale ($\Spop$) is known.
-            Recall for beneficial mutations ($\proba [\Sphy^{\text{b}} \given \Spop^{\text{b}}]$) is thus the proportion of beneficial back-mutations among all beneficial mutations.
+            Recall for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is thus the proportion of beneficial back-mutations among all beneficial mutations.
             $\bm{\pi_{\text{S}}}$ is the observed genetic diversity (number of SNPs per site) counted over synonymous sites.
@@
 
+\section*{Discussion}
     \subsection*{Beneficial mutations are not necessarily adaptive}
@@
     These selective effects can be compared to observations at the population level.
-    By doing so, we have been able to confirm that mutations predicted to be deleterious ($\Sphy^{\text{d}} \coloneqq \Sphy < -1$) are purified away in extant populations.
-    Our results reflect on previous studies showing that SIFT scores\cite{ng_sift_2003, vaser_sift_2016}, which are based on amino-acid alignments across species, have also been found to be informative of the deleterious fitness effects exerted at the population scale\cite{chen_hunting_2021}.
+    By doing so, we have been able to confirm that mutations predicted to be deleterious ($\SphyDel \coloneqq \Sphy < -1$) are purified away in extant populations.
+    Our results reflect on previous studies showing that SIFT scores~\cite{ng_sift_2003, vaser_sift_2016}, which are based on amino-acid alignments across species, have also been found to be informative of the deleterious fitness effects exerted at the population scale~\cite{chen_hunting_2021}.
     However, and contrary to SIFT scores, our mutation-selection model is parameterized by a fitness function such that changes are directly interpretable as fitness effects.
     In this regard, an interesting prediction of our model is that back-mutations are beneficial because they are reverting previous deleterious changes.
-    We have tested this hypothesis and have found that these back-mutations ($\Sphy^{\text{b}} \coloneqq \Sphy > 1 $) are indeed beneficial in extant populations.
+    We have tested this hypothesis and have found that these back-mutations ($\SphyBen \coloneqq \Sphy > 1 $) are indeed beneficial in extant populations.
     We estimated that between 18 and 78\% of all beneficial mutations in mammalian populations have not been driven by adaptation, but instead have reversed deleterious substitutions which have accumulated along the phylogeny.
     These results suggest that many beneficial mutations are non-adaptive, but are rather restoring ancestral states of higher fitness.
-    Hence, the extent of adaptive evolution can only be correctly estimated if we can account for the number of beneficial back-mutations\cite{keightley_what_2010, rice_evolutionarily_2015}.
-    Altogether, we argue that we should dissociate positive selection from adaptive evolution and limit the use of adaptive mutations to those that are associated with adaptation to environmental change as such\cite{charlesworth_other_2007, mustonen_fitness_2009}.
+    Hence, the extent of adaptive evolution can only be correctly estimated if we can account for the number of beneficial back-mutations~\cite{keightley_what_2010, rice_evolutionarily_2015}.
+    Altogether, we argue that we should dissociate positive selection from adaptive evolution and limit the use of adaptive mutations to those that are associated with adaptation to environmental change as such~\cite{charlesworth_other_2007, mustonen_fitness_2009}.
 
@@
     Across the genome, both beneficial-back mutations and deleterious mutations reaching fixation generate a balance in which genomes are constantly damaged and restored simultaneously at different loci.
-    Essentially, since the probability of fixation of mutations depends on the effective population size ($\Ne$), the history of $\Ne$ plays a crucial role in the amount of beneficial back-mutations compensating deleterious mutations\cite{latrille_inferring_2021}.
+    Essentially, since the probability of fixation of mutations depends on the effective population size ($\Ne$), the history of $\Ne$ plays a crucial role in the amount of beneficial back-mutations compensating deleterious mutations~\cite{latrille_inferring_2021}.
     For example, a population size expansion will increase the efficacy of selection and a larger proportion of mutations will be beneficial (otherwise effectively neutral), thus increasing the number of beneficial back-mutations.
-    On the other hand, a population that has experienced a high $\Ne$ throughout its history should be closer to an optimal state under a stable fitness landscape having suffered fewer fixations of deleterious mutations and therefore decreasing the probability of beneficial back-mutations\cite{huber_determining_2017}.
-    Overall, the proportion of beneficial back-mutations is expected to be more dependent on the long-term $\Ne$, as well as its expansions and contractions, rather than on the short-term $\Ne$\cite{charlesworth_other_2007,huber_determining_2017}.
+    On the other hand, a population that has experienced a high $\Ne$ throughout its history should be closer to an optimal state under a stable fitness landscape having suffered fewer fixations of deleterious mutations and therefore decreasing the probability of beneficial back-mutations~\cite{huber_determining_2017}.
+    Overall, the proportion of beneficial back-mutations is expected to be more dependent on the long-term $\Ne$, as well as its expansions and contractions, rather than on the short-term $\Ne$~\cite{charlesworth_other_2007,huber_determining_2017}.
     In this regard, the proportion of back-mutations among all beneficial ones did not show a clear relationship with the synonymous diversity within a population (Watterson's $\theta_w$) (fig.~\ref{fig:diversity}B), which should, in theory, reflect the short-term $\Ne$.
@@
     %Indeed when the effective population size is higher, the number of effectively neutral mutational opportunities should be reduced.
-    %Allowing for changes in effective population sizes along the phylogeny have been developed\cite{latrille_inferring_2021}, but are, for the moment, too computationally intensive to be performed genome-wide.
+    %Allowing for changes in effective population sizes along the phylogeny have been developed~\cite{latrille_inferring_2021}, but are, for the moment, too computationally intensive to be performed genome-wide.
     %This reduction should mechanistically increase the proportion of adaptive substitutions.
-    %However, this does not imply that the rate of adaptation (i.e the number of changes in the fitness landscape per site per generation) is higher \cite{galtier_adaptive_2016}.
+    %However, this does not imply that the rate of adaptation (i.e the number of changes in the fitness landscape per site per generation) is higher ~\cite{galtier_adaptive_2016}.
 
@@
     However, adaptive mutations are not the only contributors to these false negatives since limited data quality and potentially inadequate modelling choices of both the fitness landscape and the DFE might also lead to false negatives.
-    Moreover, a mutation which is inferred to be nearly-neutral at the phylogenetic scale, but found to be positively selected at the population scale will also be considered as a false negative (and thus an adaptation), even if this discrepancy could just be due to a population size expansion \cite{lanfear_population_2014, jones_shifting_2017, platt_protein_2018}.
+    Moreover, a mutation which is inferred to be nearly-neutral at the phylogenetic scale, but found to be positively selected at the population scale will also be considered as a false negative (and thus an adaptation), even if this discrepancy could just be due to a population size expansion ~\cite{lanfear_population_2014, jones_shifting_2017, platt_protein_2018}.
     Given this inflation of false negatives, we consider our estimated proportion of adaptive mutations among beneficial ones to be an overestimation and, hence, our estimation of beneficial back-mutations among advantageous ones should be taken as a lower bound.
 
-    %Regarding the distribution of fitness effects (DFE) estimated at the population scale, there is no consensus on its expected shape\cite{welch_divergence_2008, bataillon_effects_2014}, although it has been found to be reliably constant between closely related species\cite{castellano_comparison_2019}.
+    %Regarding the distribution of fitness effects (DFE) estimated at the population scale, there is no consensus on its expected shape~\cite{welch_divergence_2008, bataillon_effects_2014}, although it has been found to be reliably constant between closely related species~\cite{castellano_comparison_2019}.
     %We modelled the DFE as a continuous distribution, with the negative side of the DFE as a gamma distribution, and the positive side as an exponential distribution with a mean greater than one.
@@
         \caption{
-            (A) Proportion of nearly-neutral mutations at the population scale ($\proba [ \Spop^{\text{n}}]$ in the y-axis), shown as a function of the synonymous diversity (Watterson's $\theta_w$ in the x-axis).
-            (B) Proportion of beneficial back-mutations among all beneficial mutations ($\proba [ \Sphy^{\text{b}}  \given  \Spop^{\text{b}}]$ in the y-axis), shown as a function of the synonymous diversity (Watterson's $\theta_w$ in the x-axis).
+            (A) Proportion of nearly-neutral mutations at the population scale ($\proba [ \SpopNeu]$ in the y-axis), shown as a function of the synonymous diversity (Watterson's $\theta_w$ in the x-axis).
+            (B) Proportion of beneficial back-mutations among all beneficial mutations ($\proba [ \SphyBen  \given  \SpopBen]$ in the y-axis), shown as a function of the synonymous diversity (Watterson's $\theta_w$ in the x-axis).
         }
@@
     Contrarily, under epistasis, the fitness effect of a mutation at a particular site depends on the amino-acids present at other sites.
-    Epistasis therefore allows for compensatory mutations, which restore fitness through mutations at loci different from where deleterious mutations take place, and this process also leaves signals interpretable as non-adaptive beneficial mutations\cite{hartl_compensatory_1996, pollock_strong_2014, starr_epistasis_2016}.
-    Also, epistasis has been shown to play a role in the evolution of protein-coding genes, with amino-acid residues in contact within a protein or between proteins tending to co-evolve\cite{breen_epistasis_2012, starr_epistasis_2016}.
-    Particularly, the residues in contact co-evolve to become more compatible with each other generating an entrenchment, making empirical evidence for beneficial back-mutations harder to find since restoring mutations becomes less and less likely to occur over time\cite{goldstein_nonadaptive_2015, goldstein_sequence_2017, park_epistatic_2022}.
+    Epistasis therefore allows for compensatory mutations, which restore fitness through mutations at loci different from where deleterious mutations take place, and this process also leaves signals interpretable as non-adaptive beneficial mutations~\cite{hartl_compensatory_1996, pollock_strong_2014, starr_epistasis_2016}.
+    Also, epistasis has been shown to play a role in the evolution of protein-coding genes, with amino-acid residues in contact within a protein or between proteins tending to co-evolve~\cite{breen_epistasis_2012, starr_epistasis_2016}.
+    Particularly, the residues in contact co-evolve to become more compatible with each other generating an entrenchment, making empirical evidence for beneficial back-mutations harder to find since restoring mutations becomes less and less likely to occur over time~\cite{goldstein_nonadaptive_2015, goldstein_sequence_2017, park_epistatic_2022}.
     Nevertheless, the fact that we observe such a high proportion of beneficial back-mutations suggests that the underlying assumptions of our model, namely site-independence, implying no epistasis, and a static fitness landscape, are a reasonable approximation for the underlying fitness landscape of proteins.
-    Our results imply that the fitness effects of new mutations are mostly conserved across mammalian orthologs, in agreement with other studies showing that for conserved orthologs with similar structures and functions, models without epistasis provide a reasonable estimate of fitness effects in protein coding genes\cite{ashenberg_mutational_2013, youssef_consequences_2020}.
+    Our results imply that the fitness effects of new mutations are mostly conserved across mammalian orthologs, in agreement with other studies showing that for conserved orthologs with similar structures and functions, models without epistasis provide a reasonable estimate of fitness effects in protein coding genes~\cite{ashenberg_mutational_2013, youssef_consequences_2020}.
 
@@
 
-    A long-standing debate in molecular evolution is whether the variations we observe between species in protein-coding genes are mostly due to nearly-neutral mutations reaching fixation by drift, or if they are mostly due to adaptation \cite{kimura_evolutionary_1968,kern_neutral_2018,jensen_importance_2019,gillespie_substitution_1994,Ohta1992}.
+    A long-standing debate in molecular evolution is whether the variations we observe between species in protein-coding genes are mostly due to nearly-neutral mutations reaching fixation by drift, or if they are mostly due to adaptation ~\cite{kimura_evolutionary_1968,kern_neutral_2018,jensen_importance_2019,gillespie_substitution_1994,Ohta1992}.
     Here we provide evidence that in mammalian conserved orthologs, a large proportion of substitutions are due to the fixation of both deleterious mutations and beneficial back-mutations.
-    However, a central question regarding how to detect adaptation above this background of nearly-neutral substitutions remains\cite{kimura_evolutionary_1968,ohta_development_1996}.
+    However, a central question regarding how to detect adaptation above this background of nearly-neutral substitutions remains~\cite{kimura_evolutionary_1968,ohta_development_1996}.
 
@@
     However, as we have shown in this study, a $\dnds > 1$ is not necessarily a signature of adaption, but can be due to beneficial back-mutations.
-    So, by relaxing the strict neutrality and assuming a stable fitness landscape instead, one can predict the expected rate of evolution, called $\omega_0$\cite{spielman_relationship_2015, dosreis_how_2015}.
-    In this manner, adaptation can be alternatively considered as evolution under a changing fitness landscape and tested as such by searching for the signature of $\dnds > \omega_0$\cite{cvijovic_fate_2015, rodrigue_detecting_2017, rodrigue_bayesian_2021}.
-    By using a stable fitness landscape as a null model of evolution, thus accounting for selective constraints exerted on the different amino-acids, the statistical power in testing for adaptation is increased\cite{latrille_genes_2023}.
-    Another strategy to detect adaptation, instead of relying solely on summary statistics (such as $\dnds$ or $\omega_0$), is to include changes in the fitness landscapes inherently within the mutation-selection framework\cite{tamuri_mutationselection_2021}.
-    Such mechanistic models could be more general than site-specific fitness landscapes, including both epistasis and changing fitness landscapes\cite{goldstein_sequence_2017, stolyarova_senescence_2020}.
+    So, by relaxing the strict neutrality and assuming a stable fitness landscape instead, one can predict the expected rate of evolution, called $\omega_0$~\cite{spielman_relationship_2015, dosreis_how_2015}.
+    In this manner, adaptation can be alternatively considered as evolution under a changing fitness landscape and tested as such by searching for the signature of $\dnds > \omega_0$~\cite{cvijovic_fate_2015, rodrigue_detecting_2017, rodrigue_bayesian_2021}.
+    By using a stable fitness landscape as a null model of evolution, thus accounting for selective constraints exerted on the different amino-acids, the statistical power in testing for adaptation is increased~\cite{latrille_genes_2023}.
+    Another strategy to detect adaptation, instead of relying solely on summary statistics (such as $\dnds$ or $\omega_0$), is to include changes in the fitness landscapes inherently within the mutation-selection framework~\cite{tamuri_mutationselection_2021}.
+    Such mechanistic models could be more general than site-specific fitness landscapes, including both epistasis and changing fitness landscapes~\cite{goldstein_sequence_2017, stolyarova_senescence_2020}.
 
@@
 
-    Protein-coding DNA sequence alignments in placental mammals and their corresponding gene trees are from the \href{https://www.orthomam.univ-montp2.fr}{OrthoMaM} database, and were processed as in \textcite{latrille_genes_2023}.
-    OrthoMaM contains a total of $116$ mammalian reference sequences in v10c\cite{ranwez_orthomam_2007, douzery_orthomam_2014, scornavacca_orthomam_2019}.
-    Genes located on the X and Y chromosomes, and on the mitochondrial genome were discarded from the analysis because the level of polymorphism, which is necessary for population-based analyses, is expected to be different in these three regions compared to the autosomal genome.
-    Sequences of species for which we used population-level polymorphism (see below), as well as their sister species, were removed from the analysis to ensure independence between the data used in the phylogenetic and population scales.
+    Protein-coding DNA sequence alignments in placental mammals and their corresponding gene trees come from the \href{https://www.orthomam.univ-montp2.fr}{OrthoMaM} database and were processed as in \textcite{latrille_genes_2023}.
+    OrthoMaM contains a total of $116$ mammalian reference sequences in v10c~\cite{ranwez_orthomam_2007, douzery_orthomam_2014, scornavacca_orthomam_2019}.
+    Genes located on the X and Y chromosomes and the mitochondrial genome were discarded from the analysis because the level of polymorphism – which is necessary for population-based analyses – is expected to be different in these three regions compared to the autosomal genome.
+    Sequences of species for which we used population-level polymorphism (see below) and their sister species, were removed from the analysis to ensure independence between the data used in the phylogenetic and population scales.
     Altogether, our genome-wide dataset contains $14,509$ protein-coding DNA sequences in $87$ placental mammals.
@@
     \label{subsec:s-phylogeny-method}
-    We analyzed the phylogenetic level data using mutation-selection models.
-    These models assume that the protein-coding sequences are at mutation-selection balance under a fixed fitness landscape characterized by a fitness vector over the $20$ amino-acids at each site\cite{yang_mutationselection_2008, halpern_evolutionary_1998, rodrigue_mechanistic_2010}.
-    Mathematically, the rate of non-synonymous substitution from codon $a$ to codon $b$ ($q_{a \mapsto b}^{(i)}$) at site $i$ of the sequence is equal to the rate of mutation of the underlying nucleotide change ($\mu_{a \mapsto b}$) multiplied by the scaled probability of fixation of the mutation ($\proba_{a \mapsto b}^{(i)}$).
-    The probability of fixation depends on the difference between the scaled fitness of the amino-acid encoded by the mutated codon ($F_b^{(i)}$) and the amino acid encoded by the original codon ($F_a^{(i)}$) at site $i$\cite{wright_evolution_1931, fisher_genetical_1930}.
+    We analyzed the phylogenetic-level data using mutation-selection models.
+    These models assume the protein-coding sequences are at mutation-selection balance under a fixed fitness landscape characterized by a fitness vector over the $20$ amino acids at each site~\cite{yang_mutationselection_2008, halpern_evolutionary_1998, rodrigue_mechanistic_2010}.
+    Mathematically, the rate of non-synonymous substitution from codon $a$ to codon $b$ ($q_{a \mapsto b}^{(i)}$) at site $i$ of the sequence is equal to the rate of mutation of the underlying nucleotide change ($\mu_{a \mapsto b}$) multiplied by the scaled probability of mutation fixation ($\proba_{a \mapsto b}^{(i)}$).
+    The probability of fixation depends on the difference between the scaled fitness of the amino acid encoded by the mutated codon ($F_b^{(i)}$) and the amino acid encoded by the original codon ($F_a^{(i)}$) at site $i$~\cite{wright_evolution_1931, fisher_genetical_1930}.
     The rate of substitution from codon $a$ to $b$ at a site $i$ is thus:
@@
     We ran the Markov chain Monte-Carlo (MCMC) algorithm implemented in BayesCode for $2,000$ generations as described in \textcite{latrille_genes_2023}.
-    For each gene, after discarding a burn-in period of $1,000$ generations of MCMC, we obtained posterior mean estimates (over the $1,000$ generations left of MCMC) of the mutation rate matrix ($\UniDimArray{\mu}$) as well as the $20$ amino-acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$.
+    For each gene, after discarding a burn-in period of $1,000$ generations of MCMC, we obtained posterior mean estimates (over the $1,000$ generations left of MCMC) of the mutation rate matrix ($\UniDimArray{\mu}$) as well as the $20$ amino acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$.
 
@@
 
-    The genetic variants representing the population level polymorphisms were obtained from the following species and respective available datasets: \textit{Equus caballus} (EquCab2 assembly in the EVA study PRJEB9799\cite{alabri_whole_2020}), \textit{Bos taurus} (UMD3.1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}), \textit{Ovis aries} (Oar\_v3.1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}), \textit{Capra hircus} (CHIR1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}, converted to ARS1 assembly with dbSNP identifiers\cite{sherry_dbsnp_2001}), \textit{Chlorocebus sabaeus} (ChlSab1.1 assembly in the EVA project PRJEB22989\cite{svardal_ancient_2017}), \textit{Homo sapiens} (GRCh38 assembly in the 1000-genome project\cite{zheng-bradley_alignment_2017}).
+    The genetic variants representing the population level polymorphisms were obtained from the following species and their available datasets: \textit{Equus caballus} (EquCab2 assembly in the EVA study PRJEB9799~\cite{alabri_whole_2020}), \textit{Bos taurus} (UMD3.1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}), \textit{Ovis aries} (Oar\_v3.1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}), \textit{Capra hircus} (CHIR1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}, converted to ARS1 assembly with dbSNP identifiers~\cite{sherry_dbsnp_2001}), \textit{Chlorocebus sabaeus} (ChlSab1.1 assembly in the EVA project PRJEB22989~\cite{svardal_ancient_2017}), \textit{Homo sapiens} (GRCh38 assembly in the 1000-genome project~\cite{zheng-bradley_alignment_2017}).
     In total, we analyzed 28 populations across the 6 different species with polymorphism data.
@@
 
-    Regarding our polymorphism dataset, only bi-allelic single nucleotide polymorphisms (SNPs) found within a gene were considered, while nonsense variants and indels were discarded.
+    Only bi-allelic single nucleotide polymorphisms (SNPs) found within a gene were in our polymorphism dataset, while nonsense variants and indels were discarded.
     To construct the dataset, we first recovered the location of each SNP (represented by its chromosome, position, and strand) in the focal species and matched it to its corresponding position in the coding sequence (CDS) using gene annotation files (GTF format) downloaded from Ensembl (\url{ensembl.org}).
     We then verified that the SNP downloaded from Ensembl matched the reference in the CDS in FASTA format.
-    Next, the position in the CDS was converted to the corresponding position in the multi-species sequence alignment (containing gaps) from the OrthoMaM database (see section \ref{subsec:s-phylogeny-method}) for the corresponging gene, by doing a global pairwise alignment (Biopython function pairwise2).
-    This conversion from genomic position to alignment position was only possible when the assembly used for SNP-calling was the same as the one used in the OrthoMaM alignment, the GTF annotations and the FASTA sequences.
-    SNPs were polarized using the three closest outgroups found in the OrthoMaM alignment with est-usfs v2.04\cite{keightley_inferring_2018}.
+    Next, the position in the CDS was converted to the corresponding position in the multi-species sequence alignment (containing gaps) from the OrthoMaM database (see section \ref{subsec:s-phylogeny-method}) for the corresponding gene by doing a global pairwise alignment (Biopython function pairwise2).
+    This conversion from genomic position to alignment position was only possible when the assembly used for SNP-calling was the same as the one used in the OrthoMaM alignment, the GTF annotations, and the FASTA sequences.
+    SNPs were polarized using the three closest outgroups found in the OrthoMaM alignment with est-usfs v2.04~\cite{keightley_inferring_2018}.
 
@@
     \label{subsec:nunber-of-sites}
-    For any new mutation, its mutational opportunities refer to its likelihood of falling into a certain category (synonymous, deleterious, nearly-neutral, or beneficial).
-    Deriving such opportunities is necessary to estimate the strength of selection exerted at the population scale since different categories might have different mutational opportunities and hence polymorphism and divergence need to be corrected accordingly (see section \ref{subsec:substitution-mapping-in-the-terminal-branch}, \ref{subsec:s-polymorphism-method} and \ref{subsec:precisison_recall}).
-    To calculate mutational opportunities we reconstructed the ancestral genome of each of the 28 populations, which differs from the corresponding species' reference genome since it accounts for the variability present in the specific population.
-    So, for each population we used the polarized SNPs to reconstruct the ancestral DNA sequence, containing only substitutions and no segregating polymorphisms.
-    If a SNP was still segregating in the population, the ancestral version of the SNP was used.
+    The mutational opportunities of any new mutation refer to its likelihood of falling into a specific category (synonymous, deleterious, nearly-neutral, or beneficial).
+    Deriving such opportunities is necessary to estimate the strength of selection exerted at the population scale since different categories might have different mutational opportunities, and thus polymorphism and divergence need to be corrected accordingly (see sections \ref{subsec:substitution-mapping-in-the-terminal-branch}, \ref{subsec:s-polymorphism-method}, and \ref{subsec:precisison_recall}).
+    To calculate mutational opportunities, we reconstructed the ancestral genome of each of the 28 populations, which differs from the corresponding species' reference genome since it accounts for the variability present in the specific population.
+    So, for each population, we used the polarized SNPs to reconstruct the ancestral DNA sequence, containing only substitutions and no segregating polymorphisms.
+    If an SNP was still segregating in the population, we used its ancestral version.
 
     From the reconstructed ancestral genome at the base of the population genealogy, all possible mutations were computed, weighted by the instantaneous rate of change between nucleotides obtained from the mutation rate matrix ($\UniDimArray{\mu}$, see \ref{subsec:s-phylogeny-method}), summing to $\mu_{\text{tot}}$ across the whole genome, and to $\mu_{\text{syn}}$ when restricted to synonymous mutations.
-    Finally, the mutational opportunities for synonymous mutations was computed as the total number of sites across the genome ($L_{\text{tot}}$) weighted by the proportion of synonymous mutations among all possible mutations as:
+    Finally, the mutational opportunities for synonymous mutations were computed as the total number of sites across the genome ($L_{\text{tot}}$) weighted by the proportion of synonymous mutations among all possible mutations as:
     \begin{equation}
@@
 
-    Similarly, for non-synonymous mutations, the total mutation rate for each class of selection $\Sphyclass \in \{\Sphy^{\text{d}}, \Sphy^{\text{n}}, \Sphy^{\text{b}} \}$, called $\mu\left( \Sphyclass \right)$, was estimated as the sum across all non-synonymous mutations if their selection coefficient at the phylogenetic scale is in the class ($\Sphy \in \Sphyclass$).
+    Similarly, for non-synonymous mutations, the total mutation rate for each class of selection $\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$, called $\mu\left( \Sphyclass \right)$, was estimated as the sum across all non-synonymous mutations if their selection coefficient at the phylogenetic scale is in the class ($\Sphy \in \Sphyclass$).
     Accordingly, the mutational opportunities ($L \left( \Sphyclass \right)$) for each class of selection coefficient ($\Sphyclass$) was finally computed as the total number of sites across the genome ($L_{\text{tot}}$) weighted by the ratio of the aggregated mutations rates falling in the class ($\mu\left( \Sphyclass \right)$)
@@
     \begin{equation}
-        \proba[\Sphyclass] = \frac{L\left( \Sphyclass \right)}{\sum_{\mathcal{D}\in \{\Sphy^{\text{d}}, \Sphy^{\text{n}}, \Sphy^{\text{b}} \} } L\left(\mathcal{D} \right)},
+        \proba[\Sphyclass] = \frac{L\left( \Sphyclass \right)}{\sum_{\SphyclassAlt\in \{\SphyDel, \SphyNeu, \SphyBen \} } L\left(\SphyclassAlt \right)},
         \label{eq:proba-dfe-mutsel}
@@
     \label{subsec:substitution-mapping-in-the-terminal-branch}
-    For each gene and for each population with polymorphism data available, the genome at the base of the population genealogy was reconstructed (see section \ref{subsec:nunber-of-sites}).
-    We used the ancestral genome reconstructed at the base of the population genealogy and the three closest outgroups found in the OrthoMaM alignment to infer the ancestral protein-coding DNA sequences for each node of the 4-taxa tree by applying the M5 codon model (gamma site rate variation) as implemented in FastML.v3.11\cite{ashkenazy_fastml_2012}.
+    For each gene and each population with polymorphism data available, the genome at the base of the population genealogy was reconstructed (see section \ref{subsec:nunber-of-sites}).
+    We used the ancestral genome reconstructed at the base of the population genealogy and the three closest outgroups found in the OrthoMaM alignment to infer the ancestral protein-coding DNA sequences for each node of the 4-taxa tree by applying the M5 codon model (gamma site rate variation) as implemented in FastML.v3.11~\cite{ashkenazy_fastml_2012}.
     All polarized codon substitutions were then obtained by comparing the ancestral protein-coding DNA sequences before the split to the sister species (closest outgroup) to the genome at the base of the population genealogy.
-    We considered \textit{Ceratotherium simum simum} as \textit{Equus caballus} sister species; \textit{Bison bison bison} as \textit{Bos taurus} sister species; \textit{Pantholops hodgsonii} as \textit{Ovis aries} sister species; \textit{Pantholops hodgsonii} as \textit{Capra hircus} sister species; \textit{Macaca mulatta} as \textit{Chlorocebus sabaeus} sister species and finally we considered \textit{Pan troglodytes} as \textit{Homo sapiens} sister species.
+    We considered \textit{Ceratotherium simum simum} as \textit{Equus caballus} sister species; \textit{Bison bison bison} as \textit{Bos taurus} sister species; \textit{Pantholops hodgsonii} as \textit{Ovis aries} sister species; \textit{Pantholops hodgsonii} as \textit{Capra hircus} sister species; \textit{Macaca mulatta} as \textit{Chlorocebus sabaeus} sister species and finally, we considered \textit{Pan troglodytes} as \textit{Homo sapiens} sister species.
     The selection coefficient ($\Sphy$) of each substitution was then obtained by comparing the difference in amino acid fitnesses for each polarized non-synonymous codon substitution, by referring to the site-specific fitness profile obtained in the phylogeny-based method (see~\ref{subsec:s-phylogeny-method}).
@@
     \end{align}
-    where $D \left( \Sphyclass \right) $ was the number of non-synonymous substitutions in the class $\Sphyclass$, $D_{\text{syn}}$ was the number of synonymous substitutions across the genome, while $L \left( \Sphyclass \right)$ and $L_{\text{syn}}$ were the number of non-synonymous and synonymous mutational opportunities as defined in section \ref{subsec:nunber-of-sites}.
+    where $D \left( \Sphyclass \right) $ was the number of non-synonymous substitutions in class $\Sphyclass$, $D_{\text{syn}}$ was the number of synonymous substitutions across the genome, while $L \left( \Sphyclass \right)$ and $L_{\text{syn}}$ were the numbers of non-synonymous and synonymous mutational opportunities as defined in section \ref{subsec:nunber-of-sites}.
     $R(\dnds)$ was computed as the ratio between the difference in the numbers of beneficial substitutions ($\dnds$), which were due to beneficial back-mutations, and the estimated divergence when we removed beneficial back-mutations $\dn (\Sphy < 0) / \ds$, over $\dnds$.
-    Of note, the quantities $R(\dn)$ and $R(\dnds)$ are equivalent due to simplification of the factor $\ds$:
+    Note that the quantities $R(\dn)$ and $R(\dnds)$ are equivalent due to the simplification of the factor $\ds$:
     \begin{equation}
@@
     \label{subsec:s-polymorphism-method}
-    To obtain a quantitative estimate of the distribution of selection coefficients for each category of SNPs, we used the model polyDFE\cite{tataru_inference_2017, tataru_polydfe_2020}.
+    To obtain a quantitative estimate of the distribution of selection coefficients for each category of SNPs, we used the model polyDFE~\cite{tataru_inference_2017, tataru_polydfe_2020}.
     This model uses the count of derived alleles to infer the distribution of fitness effects (DFE).
-    The probability to sample an allele at a given frequency (before fixation or extinction) is informative of its scaled selection coefficient at the population scale ($\Spop$).
-    Pooled across many sites, the site-frequency spectrum (SFS) provides therefore information on the underlying $\Spop$ of mutations.
-    However, estimating a single $\Spop$ for all sampled mutations is biologically unrealistic and a DFE of mutations is usually assumed\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009}.
+    The probability of sampling an allele at a given frequency (before fixation or extinction) is informative of its scaled selection coefficient at the population scale ($\Spop$).
+    Therefore, pooled across many sites, the site-frequency spectrum (SFS) provides information on the underlying $\Spop$ of mutations.
+    However, estimating a single $\Spop$ for all sampled mutations is biologically unrealistic, and a DFE of mutations is usually assumed~\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009}.
     The polyDFE\cite{tataru_inference_2017, tataru_polydfe_2020} software implements a mixture of a $\Gamma$ and exponential distributions to model the DFE of non-synonymous mutations, while synonymous mutations are considered neutral.
@@
     and $f_{\Gamma}(x; m, b)$ is the density of the $\Gamma$ distribution with mean $m$ and shape $b$, while $f_{e}(x; m)$ is the density of the exponential distribution with mean $m$.
-    Once the DFE is fitted to the data, the proportion of beneficial ($\PpolyAdv$), nearly-neutral ($\PpolyNeutral$) and deleterious mutations ($\PpolyDel$) are given as:
+    Once the DFE is fitted to the data, the proportion of beneficial ($\ProbaPopBen$), nearly-neutral ($\ProbaPopNeu$) and deleterious mutations ($\ProbaPopDel$) are given as:
     \begin{align}
-        \PpolyDel &= \proba [ \Spop < -1] = \left( 1 - p_b \right) \int_{1}^{+\infty} f_{\Gamma}(\Spop; -\DelMean, b) \der \Spop, \label{eq:polyProbaDel} \\
-        \PpolyNeutral &= \proba [ -1 < \Spop < 1] = p_b \int_{0}^{1} f_{e}(\Spop; \AdvMean) \der \Spop + \left( 1 - p_b \right) \int_{0}^{1} f_{\Gamma}(\Spop; -\DelMean, b) \der \Spop, \\
-        \PpolyAdv &= \proba [ \Spop > 1] = p_b \int_{1}^{+\infty} f_{e}(\Spop; \AdvMean) \der \Spop. \label{eq:polyProbaAdv}
+        \ProbaPopDel &= \proba [ \Spop < -1] = \left( 1 - p_b \right) \int_{1}^{+\infty} f_{\Gamma}(\Spop; -\DelMean, b) \der \Spop, \label{eq:polyProbaDel} \\
+        \ProbaPopNeu &= \proba [ -1 < \Spop < 1] = p_b \int_{0}^{1} f_{e}(\Spop; \AdvMean) \der \Spop + \left( 1 - p_b \right) \int_{0}^{1} f_{\Gamma}(\Spop; -\DelMean, b) \der \Spop, \\
+        \ProbaPopBen &= \proba [ \Spop > 1] = p_b \int_{1}^{+\infty} f_{e}(\Spop; \AdvMean) \der \Spop. \label{eq:polyProbaAdv}
     \end{align}
 
-    PolyDFE requires one SFS for non-synonymous mutations and one for synonymous mutations (neutral expectation), as well as the number of sites on which each SFS was sampled namely the mutational opportunities ($L(\Sphyclass)$ and $L_{\text{syn}}$.
-    For populations containing more than $8$ individuals, the site-frequency spectrum (SFS) was subsampled down to $16$ chromosomes ($8$ diploid individuals) without replacement (hyper-geometric distribution) to alleviate the effect of different sampling depth in the 28 populations.
+    PolyDFE requires one SFS for non-synonymous mutations and one for synonymous mutations (neutral expectation), as well as the number of sites on which each SFS was sampled, namely the mutational opportunities ($L(\Sphyclass)$ and $L_{\text{syn}}$.
+    For populations containing more than $8$ individuals, the site-frequency spectrum (SFS) was subsampled down to $16$ chromosomes ($8$ diploid individuals) without replacement (hyper-geometric distribution) to alleviate the effect of different sampling depths in the 28 populations.
     Altogether, for each class of selection ($\Sphyclass$) of non-synonymous SNPs (or for all SNPs), we thus estimated the parameters of the DFE $\left( \Spop; \DelMean , b, p_b, \AdvMean \right)$ using maximum likelihood with polyDFE from the number of sites and the SFS obtained by aggregating all the SNPs in the selection class.
-    Once fitted to the data, the parameters of the DFE $\left( \Spop; \DelMean , b, p_b, \AdvMean \right)$ were used to compute $\PpolyAdv$, $\PpolyNeutral$, $\PpolyDel$ using eq.~\ref{eq:polyProbaAdv}-\ref{eq:polyProbaDel}.
+    Once fitted to the data, the parameters of the DFE $\left( \Spop; \DelMean , b, p_b, \AdvMean \right)$ were used to compute $\ProbaPopBen$, $\ProbaPopNeu$, $\ProbaPopDel$ using eq.~\ref{eq:polyProbaAdv}-\ref{eq:polyProbaDel}.
 
@@
     \label{subsec:precisison_recall}
-    For readability, we hereby give \textit{precision} and \textit{recall} for beneficial mutations ($\Sphy^{\text{b}} \coloneqq \Sphy > 1$ and $\Spop^{\text{b}} \coloneqq \Spop > 1$), but it can be obtained using the same derivation for the deleterious mutations ($\Sphy \text{ or } \Spop < -1$) and nearly-neutral mutations ($-1 < \Sphy \text{ or } \Spop < 1$).
+    For readability, we give here \textit{precision} and \textit{recall} for beneficial mutations ($\SphyBen \coloneqq \Sphy > 1$ and $\SpopBen \coloneqq \Spop > 1$), but it can be obtained using the same derivation for the deleterious mutations ($\Sphy \text{ or } \Spop < -1$) and nearly-neutral mutations ($-1 < \Sphy \text{ or } \Spop < 1$).
 
-    \textit{Precision} is the ratio $TP / (TP + FP)$, where TP are \textit{true positives} ($\proba [ \Spop^{\text{b}} \cap  \Sphy^{\text{b}}]$) and FP are \textit{false positives} ($\proba [ \text{not } \Spop^{\text{b}} \cap \Sphy^{\text{b}}]$).
+    \textit{Precision} is the ratio $TP / (TP + FP)$, where TP are \textit{true positives} ($\proba [ \SpopBen \cap  \SphyBen]$) and FP are \textit{false positives} ($\proba [ \text{not } \SpopBen \cap \SphyBen]$).
     The denominator $(TP + FP)$ can be simplified using the law of total probability as:
     \begin{equation}
-        \proba [ \Spop^{\text{b}} \cap \Sphy^{\text{b}}] + \proba [\text{not } \Spop^{\text{b}} \cap \Sphy^{\text{b}}] = \proba [ \Sphy^{\text{b}}],
+        \proba [ \SpopBen \cap \SphyBen] + \proba [\text{not } \SpopBen \cap \SphyBen] = \proba [ \SphyBen],
     \end{equation}
-    which corresponds to the total probability of a mutation to be a predicted positive ($\proba [ \Sphy^{\text{b}}]$).
+    which corresponds to the total probability of a mutation to be a predicted positive ($\proba [ \SphyBen]$).
     Altogether, \textit{precision} for beneficial mutations can be written as conditional probability:
     \begin{equation}
-        \frac{\proba [ \Spop^{\text{b}}  \cap  \Sphy^{\text{b}}]}{\proba [ \Sphy^{\text{b}}]} = \proba [ \Spop^{\text{b}}  \given  \Sphy^{\text{b}}].
+        \frac{\proba [ \SpopBen  \cap  \SphyBen]}{\proba [ \SphyBen]} = \proba [ \SpopBen  \given  \SphyBen].
     \end{equation}
-    Namely, \textit{precision} corresponds to the probability for a back-mutation ($\Sphy^{\text{b}}$) to be effectively beneficial at the level of the population ($\Spop^{\text{b}}$).
-    This probability is obtained by restricting our analysis on SNPs that are predicted to be beneficial back-mutations (black fill for the category $\Sphy^{\text{b}}$ in fig~\ref{fig:homo-afr-results}D).
+    Namely, \textit{precision} corresponds to the probability for a back-mutation ($\SphyBen$) to be effectively beneficial at the population level ($\SpopBen$).
+    This probability is obtained by restricting our analysis to SNPs that are predicted to be beneficial back-mutations (black fill for the category $\SphyBen$ in fig~\ref{fig:homo-afr-results}D).
 
-    \textit{Recall} is the ratio $TP / (TP + FN)$, where TP are \textit{true positives} ($\proba [ \Spop^{\text{b}}  \cap  \Sphy^{\text{b}}]$) and FN are \textit{false negatives} ($\proba [ \Spop^{\text{b}}  \cap \text{not } \Sphy^{\text{b}}]$).
+    The \textit{Recall} is the ratio $TP / (TP + FN)$, where TP are \textit{true positives} ($\proba [ \SpopBen  \cap  \SphyBen]$) and FN are \textit{false negatives} ($\proba [ \SpopBen  \cap \text{not } \SphyBen]$).
     The denominator $(TP + FN)$ can be simplified using the law of total probability as:
     \begin{equation}
-        \proba [ \Spop^{\text{b}}  \cap  \Sphy^{\text{b}}] + \proba [ \Spop^{\text{b}} \cap \text{not } \Sphy^{\text{b}}] = \proba [ \Spop^{\text{b}}],
+        \proba [ \SpopBen  \cap  \SphyBen] + \proba [ \SpopBen \cap \text{not } \SphyBen] = \proba [ \SpopBen],
     \end{equation}
-    which corresponds to the total probability of a mutation to be a positive ($\proba [ \Spop^{\text{b}}]$).
+    which corresponds to the total probability of a mutation being positive ($\proba [ \SpopBen]$).
     Altogether, \textit{recall} for beneficial mutations can be written as conditional probability:
     \begin{equation}
-        \frac{\proba [ \Spop^{\text{b}} \cap  \Sphy^{\text{b}}]}{\proba [ \Spop^{\text{b}}]} = \proba [ \Sphy^{\text{b}}  \given \Spop^{\text{b}} ].
+        \frac{\proba [ \SpopBen \cap  \SphyBen]}{\proba [ \SpopBen]} = \proba [ \SphyBen  \given \SpopBen ].
     \end{equation}
-    Namely, \textit{recall} corresponds to the probability for a beneficial mutation at the level of population ($\Spop^{\text{b}}$) to be a beneficial back-mutation ($\Sphy^{\text{b}}$).
+    Namely, \textit{recall} corresponds to the probability for a beneficial mutation at the population level ($\SpopBen$) to be a beneficial back-mutation ($\SphyBen$).
     Using Bayes theorem, \textit{recall} can be re-written as:
     \begin{equation}
-        \proba [\Sphy^{\text{b}} \given \Spop^{\text{b}}] = \frac{\proba [\Spop^{\text{b}} \given \Sphy^{\text{b}}] \times \proba[\Sphy^{\text{b}}]}{\PpolyAdv},
+        \proba [\SphyBen \given \SpopBen] = \frac{\proba [\SpopBen \given \SphyBen] \times \proba[\SphyBen]}{\ProbaPopBen},
         \label{eq:bayes}
     \end{equation}
-    First, $\proba [\Spop^{\text{b}} \given \Sphy^{\text{b}}]$ is computed as above (\textit{precision}).
-    Second, $\proba [ \Sphy^{\text{b}} ]$ is obtained from equation \ref{eq:proba-dfe-mutsel}.
-    Finally, $\proba [ \Spop^{\text{b}} ]$ is the probability of mutation to be beneficial at the level of the population, which can be computed from the law of total probabilities as:
+    First, $\proba [\SpopBen \given \SphyBen]$ is computed as above (\textit{precision}).
+    Second, $\proba [ \SphyBen ]$ is obtained from equation \ref{eq:proba-dfe-mutsel}.
+    Finally, $\proba [ \SpopBen ]$ is the probability of mutation to be beneficial at the level of the population, which can be computed from the law of total probabilities as:
     \begin{equation}
-        \proba [ \Spop^{\text{b}} ] = \sum_{\Sphyclass \in \{\Sphy^{\text{d}}, \Sphy^{\text{n}}, \Sphy^{\text{b}} \} }\proba [\Spop^{\text{b}} \given \Sphyclass ] \times \proba [\Sphyclass ].
+        \proba [ \SpopBen ] = \sum_{\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \} }\proba [\SpopBen \given \Sphyclass ] \times \proba [\Sphyclass ].
         \label{eq:total_proba}

### 2023-04-03 manuscript/supp-mat.tex
Updated manuscript, changed colors.
Updated manuscript before NG corrections

@@
 \newcommand{\SphyMean}{\overline{\Sphy}}
-\newcommand{\divStrongDel}{\Sphy < -3}
-\newcommand{\divDel}{-3 < \Sphy < -1}
-\newcommand{\divWeakDel}{-1 < \Sphy < 0}
-\newcommand{\divWeakAdv}{0 < \Sphy < 1}
-\newcommand{\divAdv}{ \Sphy > 1}
-\newcommand{\PdivStrongDel}{\proba \left[ \divStrongDel \right]}
+\newcommand{\divDel}{\Sphy^{\text{d}}}
+\newcommand{\divWeak}{\Sphy^{\text{n}}}
+\newcommand{\divAdv}{\Sphy^{\text{b}}}
 \newcommand{\PdivDel}{\proba \left[ \divDel \right]}
-\newcommand{\PdivWeakDel}{\proba \left[ \divWeakDel \right]}
-\newcommand{\PdivWeakAdv}{\proba \left[ \divWeakAdv \right]}
+\newcommand{\PdivWeak}{\proba \left[ \divWeak \right]}
 \newcommand{\PdivAdv}{\proba \left[ \divAdv \right]}
@@
 \newcommand{\SpopMean}{\overline{\Spop}}
-\newcommand{\polyDel}{\Spop < -1}
-\newcommand{\polyNeutral}{-1 < \Spop < 1}
-\newcommand{\polyAdv}{ \Spop > 1}
+\newcommand{\polyDel}{\Spop^{\text{d}}}
+\newcommand{\polyNeutral}{\Spop^{\text{n}}}
+\newcommand{\polyAdv}{\Spop^{\text{b}}}
 \newcommand{\PpolyDel}{\proba \left[ \polyDel \right]}
@@
 
-\title{Up to 25\% of beneficial mutations in protein sequences are not adaptive innovations in mammals}
+\title{\textbf{Empirical evidence for beneficial mutations that are not adaptive innovations in mammals}}
 
@@
     \large
-    \textbf{T. {Latrille}$^{1}$, J. {Joseph}$^{2}$, N. {Salamin}$^{1}$}\\
-    \normalsize
-    $^{1}$Université de Lausanne, Lausanne, Switzerland\\
-    $^{2}$Université de Lyon, CNRS, LBBE UMR 5558, Villeurbanne, France \\
+    \textbf{T. {Latrille}$^{1}$, J. {Joseph}$^{2}$, D.~A. {Hartasánchez}$^{1}$, N. {Salamin}$^{1}$}\\
+    \scriptsize $^{1}$Department of Computational Biology, Université de Lausanne, Lausanne, Switzerland\\
+    \scriptsize $^{2}$Université de Lyon, Université Lyon 1, CNRS, VetAgro Sup, Laboratoire de Biométrie et Biologie Evolutive, UMR5558, Villeurbanne, France \\
     \texttt{\href{mailto:thibault.latrille@ens-lyon.org}{thibault.latrille@ens-lyon.org}} \\
@@
     \end{scriptsize}
-    The gene-specific mutation matrix ($\UniDimArray{\mu}$) is also obtained by running \textit{readmutselomega}, reading 1000 points of MCMC (first 1000 are considered as burn-in) with the options:
+    The gene-specific $4 \times 4$ nucleotide mutation rate matrix ($\UniDimArray{\mu}$) is also obtained by running \textit{readmutselomega}, reading 1000 points of MCMC (first 1000 are considered as burn-in) with the options:
     \begin{scriptsize}
@@
         \scriptsize
-        \begin{longtable*}{|l|l|r|r|r|}
+        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
             \toprule
-            Population & Species & Tajima $\theta_{\pi}$ & $\mathbb{P}_{div}[\Sphy > 1]$ & $\dn(\Sphy > 1) / \ds$ \\
+            Population &             Species & Tajima $\theta_{\pi}$  & $\mathbb{P}_{div}[ S_0^{b} ]$ & $\omega $ & $\omega ( S_0^{d} )$ & $\omega ( S_0^{n} )$ & $\omega ( S_0^{b} )$ \\
+            \midrule
+            \endfirsthead
+
+            \toprule
+            Population &             Species & Tajima $\theta_{\pi}$  & $\mathbb{P}_{div}[ S_0^{b} ]$ & $\omega $ & $\omega ( S_0^{d} )$ & $\omega ( S_0^{n} )$ & $\omega ( S_0^{b} )$ \\
             \midrule
@@
             \midrule
-            \multicolumn{5}{r}{{Continued on next page}} \\
+            \multicolumn{8}{r}{{Continued on next page}} \\
             \midrule
@@
             \endlastfoot
-            Equus c. &      Equus caballus &               $ 0.002$ &                $ 0.116$ &              $ 1.214$ \\
-            Iran &          Bos taurus &               $ 0.005$ &                $ 0.128$ &              $ 1.309$ \\
-            Uganda &          Bos taurus &               $ 0.005$ &                $ 0.130$ &              $ 1.352$ \\
-            Australia &        Capra hircus &               $ 0.003$ &                $ 0.121$ &              $ 1.147$ \\
-            France &        Capra hircus &               $ 0.003$ &                $ 0.121$ &              $ 1.154$ \\
-            Iran (C. aegagrus) &        Capra hircus &               $ 0.003$ &                $ 0.121$ &              $ 1.154$ \\
-            Iran &        Capra hircus &               $ 0.004$ &                $ 0.122$ &              $ 1.164$ \\
-            Italy &        Capra hircus &               $ 0.003$ &                $ 0.120$ &              $ 1.148$ \\
-            Morocco &        Capra hircus &               $ 0.004$ &                $ 0.123$ &              $ 1.170$ \\
-            Iran &          Ovis aries &               $ 0.007$ &                $ 0.113$ &              $ 1.210$ \\
-            Iran (O. orientalis) &          Ovis aries &               $ 0.009$ &                $ 0.112$ &              $ 1.214$ \\
-            Iran (O. vignei) &          Ovis aries &               $ 0.007$ &                $ 0.113$ &              $ 1.200$ \\
-            Various &          Ovis aries &               $ 0.009$ &                $ 0.112$ &              $ 1.207$ \\
-            Morocco &          Ovis aries &               $ 0.007$ &                $ 0.113$ &              $ 1.215$ \\
-            Barbados & Chlorocebus sabaeus &               $ 0.004$ &                $ 0.122$ &              $ 1.477$ \\
-            Central Afr. Rep. & Chlorocebus sabaeus &               $ 0.006$ &                $ 0.123$ &              $ 1.501$ \\
-            Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &                $ 0.123$ &              $ 1.494$ \\
-            Gambia & Chlorocebus sabaeus &               $ 0.005$ &                $ 0.123$ &              $ 1.491$ \\
-            Kenya & Chlorocebus sabaeus &               $ 0.005$ &                $ 0.123$ &              $ 1.503$ \\
-            Nevis & Chlorocebus sabaeus &               $ 0.003$ &                $ 0.123$ &              $ 1.484$ \\
-            South Africa & Chlorocebus sabaeus &               $ 0.006$ &                $ 0.125$ &              $ 1.528$ \\
-            Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &                $ 0.123$ &              $ 1.495$ \\
-            Zambia & Chlorocebus sabaeus &               $ 0.006$ &                $ 0.123$ &              $ 1.493$ \\
-            African &        Homo sapiens &               $ 0.003$ &                $ 0.102$ &              $ 1.676$ \\
-            Admixed American &        Homo sapiens &               $ 0.002$ &                $ 0.102$ &              $ 1.669$ \\
-            East Asian &        Homo sapiens &               $ 0.002$ &                $ 0.102$ &              $ 1.682$ \\
-            European &        Homo sapiens &               $ 0.002$ &                $ 0.101$ &              $ 1.659$ \\
-            South Asian &        Homo sapiens &               $ 0.002$ &                $ 0.102$ &              $ 1.676$ \\
+            Equus c. &      Equus caballus &               $ 0.002$ &                      $ 0.118$ &  $ 0.147$ &             $ 0.075$ &             $ 0.823$ &             $ 1.203$ \\
+            Iran &          Bos taurus &               $ 0.002$ &                      $ 0.123$ &  $ 0.131$ &             $ 0.074$ &             $ 0.627$ &             $ 1.206$ \\
+            Uganda &          Bos taurus &               $ 0.005$ &                      $ 0.125$ &  $ 0.134$ &             $ 0.075$ &             $ 0.637$ &             $ 1.252$ \\
+            Australia &        Capra hircus &               $ 0.003$ &                      $ 0.121$ &  $ 0.125$ &             $ 0.068$ &             $ 0.629$ &             $ 1.099$ \\
+            France &        Capra hircus &               $ 0.004$ &                      $ 0.120$ &  $ 0.126$ &             $ 0.068$ &             $ 0.633$ &             $ 1.102$ \\
+            Iran (C. aegagrus) &        Capra hircus &               $ 0.004$ &                      $ 0.120$ &  $ 0.125$ &             $ 0.068$ &             $ 0.630$ &             $ 1.100$ \\
+            Iran &        Capra hircus &               $ 0.004$ &                      $ 0.121$ &  $ 0.125$ &             $ 0.067$ &             $ 0.630$ &             $ 1.108$ \\
+            Italy &        Capra hircus &               $ 0.004$ &                      $ 0.120$ &  $ 0.126$ &             $ 0.068$ &             $ 0.634$ &             $ 1.102$ \\
+            Morocco &        Capra hircus &               $ 0.004$ &                      $ 0.122$ &  $ 0.125$ &             $ 0.067$ &             $ 0.631$ &             $ 1.112$ \\
+            Iran &          Ovis aries &               $ 0.007$ &                      $ 0.109$ &  $ 0.146$ &             $ 0.091$ &             $ 0.616$ &             $ 1.148$ \\
+            Iran (O. orientalis) &          Ovis aries &               $ 0.009$ &                      $ 0.108$ &  $ 0.148$ &             $ 0.093$ &             $ 0.617$ &             $ 1.145$ \\
+            Iran (O. vignei) &          Ovis aries &               $ 0.007$ &                      $ 0.109$ &  $ 0.146$ &             $ 0.091$ &             $ 0.617$ &             $ 1.134$ \\
+            Various &          Ovis aries &               $ 0.008$ &                      $ 0.107$ &  $ 0.148$ &             $ 0.093$ &             $ 0.617$ &             $ 1.134$ \\
+            Morocco &          Ovis aries &               $ 0.008$ &                      $ 0.108$ &  $ 0.148$ &             $ 0.093$ &             $ 0.619$ &             $ 1.149$ \\
+            Barbados & Chlorocebus sabaeus &               $ 0.004$ &                      $ 0.122$ &  $ 0.133$ &             $ 0.071$ &             $ 0.696$ &             $ 1.397$ \\
+            Central Afr. Rep. & Chlorocebus sabaeus &               $ 0.006$ &                      $ 0.124$ &  $ 0.134$ &             $ 0.071$ &             $ 0.701$ &             $ 1.431$ \\
+            Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &                      $ 0.124$ &  $ 0.134$ &             $ 0.071$ &             $ 0.699$ &             $ 1.422$ \\
+            Gambia & Chlorocebus sabaeus &               $ 0.005$ &                      $ 0.123$ &  $ 0.134$ &             $ 0.071$ &             $ 0.703$ &             $ 1.411$ \\
+            Kenya & Chlorocebus sabaeus &               $ 0.005$ &                      $ 0.123$ &  $ 0.134$ &             $ 0.071$ &             $ 0.699$ &             $ 1.419$ \\
+            Nevis & Chlorocebus sabaeus &               $ 0.003$ &                      $ 0.123$ &  $ 0.133$ &             $ 0.071$ &             $ 0.699$ &             $ 1.407$ \\
+            South Africa & Chlorocebus sabaeus &               $ 0.006$ &                      $ 0.125$ &  $ 0.134$ &             $ 0.070$ &             $ 0.704$ &             $ 1.447$ \\
+            Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &                      $ 0.123$ &  $ 0.133$ &             $ 0.070$ &             $ 0.699$ &             $ 1.413$ \\
+            Zambia & Chlorocebus sabaeus &               $ 0.006$ &                      $ 0.123$ &  $ 0.134$ &             $ 0.071$ &             $ 0.699$ &             $ 1.410$ \\
+            African &        Homo sapiens &               $ 0.002$ &                      $ 0.099$ &  $ 0.192$ &             $ 0.118$ &             $ 0.865$ &             $ 1.609$ \\
+            Admixed American &        Homo sapiens &               $ 0.002$ &                      $ 0.099$ &  $ 0.192$ &             $ 0.118$ &             $ 0.865$ &             $ 1.607$ \\
+            East Asian &        Homo sapiens &               $ 0.002$ &                      $ 0.098$ &  $ 0.192$ &             $ 0.118$ &             $ 0.869$ &             $ 1.607$ \\
+            European &        Homo sapiens &               $ 0.002$ &                      $ 0.098$ &  $ 0.192$ &             $ 0.118$ &             $ 0.865$ &             $ 1.598$ \\
+            South Asian &        Homo sapiens &               $ 0.002$ &                      $ 0.099$ &  $ 0.192$ &             $ 0.118$ &             $ 0.867$ &             $ 1.610$ \\
         \end{longtable*}
@@
         \item $\mathbb{P}_{div}[\Sphy > 1]$ is the proportion of substitutions in the terminal branch observed with a selection coefficient at the phylogenetic scale larger than 1 ($\Sphy > 1$).
+        \item $\dn(\Sphy > 1) / \ds$ is the ratio of non-synonymous over synonymous divergence (also called $\dnds$) estimated for the non-synonymous substitutions in the terminal branch with a selection coefficient larger than 1 ($\Sphy > 1$).
+        \item $\dn(\Sphy > 1) / \ds$ is the ratio of non-synonymous over synonymous divergence (also called $\dnds$) estimated for the non-synonymous substitutions in the terminal branch with a selection coefficient larger than 1 ($\Sphy > 1$).
         \item $\dn(\Sphy > 1) / \ds$ is the ratio of non-synonymous over synonymous divergence (also called $\dnds$) estimated for the non-synonymous substitutions in the terminal branch with a selection coefficient larger than 1 ($\Sphy > 1$).
@@
     \subsection{Correlation with diversity}
+    For each population, the proportion of beneficial ($\PpolyAdv$), nearly-neutral ($\PpolyNeutral$) and of deleterious ($\PpolyDel$) mutations estimated at the population-genetic scale is shown as function of Watterson's diversity ($\Theta_w$).
 
@@
     \captionof{figure}{~}
-    \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/regression-MutSel/results.watterson.all_P-Seq0.scatter.pdf}
+    \begin{minipage}{0.49\linewidth}
+        \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC-masked/regression-MutSel/results.watterson.all_P-Sweak.scatter.pdf}
     \end{minipage}
-    \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/regression-MutSel/results.watterson.neg-weak_P-Seq0.scatter.pdf}
-    \end{minipage}
-    \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/regression-MutSel/results.watterson.pos-weak_P-Seq0.scatter.pdf}
+    \begin{minipage}{0.49\linewidth}
+        \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC-masked/regression-MutSel/results.watterson.weak_P-Sweak.scatter.pdf}
     \end{minipage}
@@
         \item $\ \proba [ \polyNeutral ]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) between -1 and 1, estimated for the whole genome.
-        \item $\ \proba [ \polyNeutral \given \divWeakDel]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) between -1 and 1, estimated of SNPs observed with a selection coefficient at the phylogenetic scale ($\Sphy$) between -1 and 0.
-        \item $\ \proba [ \polyNeutral \given \divWeakAdv ]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) between -1 and 1, estimated of SNPs observed with a selection coefficient at the phylogenetic scale ($\Sphy$) between 0 and 1.
+        \item $\ \proba [ \polyNeutral \given \divWeak ]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) between -1 and 1, estimated of SNPs observed with a selection coefficient at the phylogenetic scale ($\Sphy$) between -1 and 1.
     \end{itemize}
+
+    We confirmed that higher synonymous diversity is typically accompanied by a smaller proportion of neutral mutations.
+    This result is specially visible when we restricted the analysis to class of mutations that are supposedly nearly-neutral at the phylogenetic scale ($\divWeak$).
+    This result suggests that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) are more likely to discriminate whether mutations are beneficial or deleterious.
+    Alternatively stated, mutations in populations with low diversity (e.g.~\textit{Homo}) are effectively nearly-neutral and behave as would a neutral mutation.
+    This result is qualitatively in accordance with the nearly-neutral theory of evolution which argues that mutations are less efficiently selected for in small populations.
 
@@
     \captionof{figure}{~}
-    \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/regression-MutSel/results.watterson.all_P-Sinf0.scatter.pdf}
+    \begin{minipage}{0.49\linewidth}
+        \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC-masked/regression-MutSel/results.watterson.all_P-Sneg.scatter.pdf}
     \end{minipage}
-    \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/regression-MutSel/results.watterson.neg_P-Sinf0.scatter.pdf}
-    \end{minipage}
-    \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/regression-MutSel/results.watterson.neg-strong_P-Sinf0.scatter.pdf}
+    \begin{minipage}{0.49\linewidth}
+        \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC-masked/regression-MutSel/results.watterson.neg_P-Sneg.scatter.pdf}
     \end{minipage}
@@
         \item $\ \proba [ \polyDel ]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) lower than -1, estimated for the whole genome.
-        \item $\ \proba [ \polyDel \given \divDel]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) lower than -1, estimated of SNPs observed with a selection coefficient at the phylogenetic scale ($\Sphy$) between -3 and -3.
-        \item $\ \proba [ \polyDel \given \divStrongDel ]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) lower than -1, estimated of SNPs observed with a selection coefficient at the phylogenetic scale ($\Sphy$) lower than -3.
+        \item $\ \proba [ \polyDel \given \divDel]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) lower than -1, estimated of SNPs observed with a selection coefficient at the phylogenetic scale ($\Sphy$) lower than -1.
     \end{itemize}
@@
     \captionof{figure}{~}
-    \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/regression-MutSel/results.watterson.all_P-Ssup0.scatter.pdf}
+    \begin{minipage}{0.49\linewidth}
+        \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC-masked/regression-MutSel/results.watterson.all_P-Spos.scatter.pdf}
     \end{minipage}
-    \begin{minipage}{0.32\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/5bins-all/regression-MutSel/results.watterson.pos_P-Ssup0.scatter.pdf}
+    \begin{minipage}{0.49\linewidth}
+        \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC-masked/regression-MutSel/results.watterson.pos_P-Spos.scatter.pdf}
     \end{minipage}
@@
 
-%    \subsection{Selection efficacy correlation with diversity}\label{subsec:selection-efficacy-correlation-with-diversity}
-%    The mean of the DFE $\SpopMean$ estimated by polyDFE is given by:
-%    \begin{align*}
-%        \SpopMean & = \int_{-\infty}^{+\infty} \Spop \phi \left( \Spop; \Spop_d , b, p_b, \Spop_b \right) \der \Spop \\
-%        & = p_b \Spop_b + \left( 1 - p_b \right) \Spop_d
-%    \end{align*}
-%
-%    To look further into the relation between diversity and selection efficacy, we studied the estimation of the mean $\SpopMean$ as a function of the mean $\SphyMean$ for a subset of SNPs, for which $\SphyMean$ is close to $0$.
-%    Indeed, polyDFE is a nearly-neutral model and is not able to reliably compute selection coefficients for only strongly deleterious or only strongly beneficial SNPs.
-%    Sliding windows of $5,000$ SNPs are taken with a mean $\SphyMean$ between $-0.5$ and $0.5$.
-%    $\SpopMean$ is estimated for each group, with some groups that might have part of same SNPs that overlap.
-%    The relationship between $\SpopMean$ and $\SphyMean$ can be described by a second-order polynomial, and the slope of this polynomial at $\SphyMean=0$ gives the ratio $\SpopMean/\SphyMean$ for each population.
-%    \captionof{figure}{~}
-%    \begin{center}
-%        \includegraphics[width=\linewidth, page=1]{artworks/figure.slope-beta-S}
-%    \end{center}
-%
-%    We observe that $\SpopMean/\SphyMean$, representing the efficacy of selection at the short versus long-term is positively correlated with synonymous diversity, a proxy of effective population size.
-%    Altogether, populations with a large effective population size are under more efficient selection, confirming the prediction of the nearly-neutral theory of evolution that mutations are less likely to be considered neutral in populations with high diversity (see~\ref{subsec:proportion-nearly-neutral-mutations}, left scatter-plot), especially for mutations predicted already to be nearly-neutral at the phylogenetic scale (see~\ref{subsec:proportion-nearly-neutral-mutations}, middle and right scatter-plot).
-%    As a consequence of an increased selection efficiency, mutations in populations with high diversity are mechanistically more likely to be deleterious (see~\ref{subsec:proportion-deleterious-mutations}, left scatter-plot), especially for mutations predicted already to be deleterious at the phylogenetic scale (see~\ref{subsec:proportion-deleterious-mutations}, middle and right scatter-plot).
-%    A decrease in the proportion of neutral mutation did not translate into a mechanical increase in the proportion of beneficial mutations.
-%    Instead, populations with higher diversity have a lower proportion of beneficial mutations, this effect is also more pronounced for mutations predicted to be beneficial at the phylogenetic scale.
-%    This discrepancy can be explained by the fact that populations with larger diversity have already depleted the putatively beneficial mutations, and that only deleterious are remaining possible.
-%    In other words, being on the top of a fixed fitness landscape leaves you with only paths going downhill.
-%    Altogether, populations with increased diversity are showing signature of increased selection efficiency and are also less likely to generate positively selected mutations.
-%   \newpage
-
-    \subsection{Proportion of selected mutations}
-
-    For each population, the proportion of beneficial ($p_+=\PpolyAdv$), nearly-neutral ($\PpolyNeutral$) and of deleterious ($\PpolyDel$) mutations estimated at the population-genetic scale is shown.
-    Estimation is performed with SNPs with different class of selection at the phylogenetic scale: $\Sphyclass \in \{ \divStrongDel, \divDel, \divWeakDel, \divWeakAdv, \divAdv \}$
-    Population are sorted for increased synonymous diversity.
+    \section{Clinically related terms for non-synonymous mutations}
 
     \begin{center}
-        \captionof{figure}{~}
-        \begin{minipage}{0.9\linewidth}
-            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-all/results/Theta.MutSel.all.stacked.pdf}
-        \end{minipage}
-        \begin{minipage}{0.09\linewidth}
-            \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
-        \end{minipage}
-        \captionof{figure}{~}
-        \begin{minipage}{0.9\linewidth}
-            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-all/results/Theta.MutSel.neg-strong.stacked.pdf} \\
-        \end{minipage}
-        \begin{minipage}{0.09\linewidth}
-            \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
-        \end{minipage}\captionof{figure}{~}
-        \begin{minipage}{0.9\linewidth}
-            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-all/results/Theta.MutSel.neg.stacked.pdf} \\
-        \end{minipage}
-        \begin{minipage}{0.09\linewidth}
-            \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
-        \end{minipage}\captionof{figure}{~}
-        \begin{minipage}{0.9\linewidth}
-            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-all/results/Theta.MutSel.neg-weak.stacked.pdf} \\
-        \end{minipage}
-        \begin{minipage}{0.09\linewidth}
-            \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
-        \end{minipage}\captionof{figure}{~}
-        \begin{minipage}{0.9\linewidth}
-            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-all/results/Theta.MutSel.pos-weak.stacked.pdf} \\
-        \end{minipage}
-        \begin{minipage}{0.09\linewidth}
-            \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
-        \end{minipage}\captionof{figure}{~}
-        \begin{minipage}{0.9\linewidth}
-            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-all/results/Theta.MutSel.pos.stacked.pdf}
-        \end{minipage}
-        \begin{minipage}{0.09\linewidth}
-            \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
-        \end{minipage}
+        \captionof{table}{Clinically related terms for $\Sphy < -1$}
+        \begin{tabular}{|l|r|r|r|r|r|}
+            \toprule
+            SNP clinical ontology & $n_{\mathrm{Observed}}$ & $n_{\mathrm{Expected}}$ & Odds ratio & $p_{\mathrm{v}}$ & $p_{\mathrm{v-adjusted}}$ \\
+            \midrule
+            Benign                & 2969                    & $4043.0$                & $ 0.734$   & $ 1.000$             & $ 1.000~~$                    \\
+            Likely benign         & 2994                    & $3399.8$                & $ 0.881$   & $ 0.999$             & $ 1.000~~$                    \\
+            Risk factor           & 102                     & $ 118.2$                & $ 0.863$   & $ 0.798$             & $ 1.000~~$                    \\
+            Likely pathogenic     & 221                     & $  68.5$                  & $ 3.226$   & $1.7\times 10^{-8}$  & $\bm{6.7\times 10^{-8}{^*}}$  \\
+            Pathogenic            & 560                     & $ 193.6$                & $ 2.893$   & $4.2\times 10^{-17}$ & $\bm{2.1\times 10^{-16}{^*}}$ \\
+            \bottomrule
+        \end{tabular}
     \end{center}
-    We confirmed that higher synonymous diversity is typically accompanied by a smaller proportion of neutral mutations.
-    This result is specially visible when we restricted the analysis to class of mutations that are supposedly nearly-neutral at the phylogenetic scale ($\divWeakDel$ and $\divWeakAdv$).
-    This result suggests that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) are more likely to discriminate whether mutations are beneficial or deleterious.
-    Alternatively stated, mutations in populations with low diversity (e.g.~\textit{Homo}) are effectively nearly-neutral and behave as would a neutral mutation.
-    This result is qualitatively in accordance with the nearly-neutral theory of evolution which argues that mutations are less efficiently selected for in small populations.
+    In humans, non-synonymous SNPs in the test group (deleterious mutations with $\Sphy < -1$) are contrasted to SNPs in the control group (nearly-neutral mutations with $-1 < \Sphy < 1$).
+    For each clinical term, a 2x2 contingency tables is built by counting the number of SNPs based on their selection coefficient and their clinical terms (whether they have this specific term or not).
+    Fisher's exact tests are then performed for these 2x2 contingency tables.
+    $^*$ signify that the$p_{\mathrm{v}}^{\mathrm{adj}}$ corrected for multiple comparison (Holm–Bonferroni correction) is lower than the risk $\alpha=0.05$.
+    SNPs predicted with $\Sphy < -1$ are statistically associated to clinical terms such as \textit{Likely Pathogenic} and \textit{Pathogenic}.
+
+    \begin{center}
+        \captionof{table}{Clinically related terms for $\Sphy > 1$}
+        \begin{tabular}{|l|r|r|r|r|r|}
+            \toprule
+            SNP clinical ontology & $n_{\mathrm{Observed}}$ & $n_{\mathrm{Expected}}$ & Odds ratio & $p_{\mathrm{v}}$ & $p_{\mathrm{v-adjusted}}$ \\
+            \midrule
+            Benign                & 319                     & $ 261.7$                & $ 1.219$   & $ 0.002$         & $\bm{ 0.009{^*}}$         \\
+            Likely benign         & 263                     & $ 222.7$                & $ 1.181$   & $ 0.012$         & $\bm{ 0.049{^*}}$         \\
+            Risk factor           & 5                       & $ 7.847$                & $ 0.637$   & $ 0.879$         & $ 0.879~~$                \\
+            Likely pathogenic     & 7                       & $ 4.552$                & $ 1.538$   & $ 0.227$         & $ 0.682~~$                \\
+            Pathogenic            & 16                      & $  12.9$                  & $ 1.241$   & $ 0.268$         & $ 0.682~~$                \\
+            \bottomrule
+        \end{tabular}
+    \end{center}
+    In humans, non-synonymous SNPs in the test group (beneficial back-mutations with $\Sphy > 1$) are contrasted to SNPs in the control group (nearly-neutral mutations with $-1 < \Sphy < 1$).
+    For each clinical term, a 2x2 contingency tables is built by counting the number of SNPs based on their selection coefficient and their clinical terms (whether they have this specific term or not).
+    Fisher's exact tests are then performed for these 2x2 contingency tables.
+    $^*$ signify that the$p_{\mathrm{v}}^{\mathrm{adj}}$ corrected for multiple comparison (Holm–Bonferroni correction) is lower than the risk $\alpha=0.05$.
+    Beneficial back-mutations $\Sphy > 1$ are associated with clinical terms such as \textit{Benign} and \textit{Likely Benign}.
+
+    \newpage
 
     \section{Distribution of fitness effects}
-
     \captionof{figure}{~}
@@
     \end{minipage}
-    \begin{itemize}
-        \item Left panel: Distribution of fitness effects experimentally determined in Yeast, data obtained in \textcite{shen_synonymous_2022}.
-        \item Middle panel: Distribution of fitness effects ($\Sphy$) as predicted with mutation-selection codon models, from reconstructed ancestral genome in \textit{Homo sapiens}).
-    \end{itemize}
+    Left panel: distribution of fitness effects experimentally determined in Yeast, data obtained in \textcite{shen_synonymous_2022}.
+    Right panel:  distribution of fitness effects ($\Sphy$) as predicted with mutation-selection codon models, from reconstructed ancestral genome in \textit{Homo sapiens}.
     The DFE predicted with mutation-selection codon models has a negative mode, consistently with experimental DFEs, meaning that most mutations are effectively deleterious.
@@
     \newpage
-
-    \section{SIFT scores}\label{sec:sift-scores}
-
-    \subsection{Proportion of selected mutations}\label{subsec:proportion-of-selected-mutations}
-    For each population, the proportion of beneficial ($\PpolyAdv$), nearly-neutral ($\PpolyNeutral$) and of deleterious ($\PpolyDel$) mutations estimated at the population-genetic scale is shown.
-    Estimation is performed with SNPs with different class of SIFT scores at the phylogenetic scale.
-    Population are sorted for increased synonymous diversity.
-
-    \begin{center}
-        \captionof{figure}{~}
-        \begin{minipage}{0.9\linewidth}
-            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-all/results/Theta.SIFT.all.stacked.pdf}
-        \end{minipage}
-        \begin{minipage}{0.09\linewidth}
-            \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
-        \end{minipage}
-        \captionof{figure}{~}
-        \begin{minipage}{0.9\linewidth}
-            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-all/results/Theta.SIFT.neg-strong.stacked.pdf} \\
-        \end{minipage}
-        \begin{minipage}{0.09\linewidth}
-            \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
-        \end{minipage}\captionof{figure}{~}
-        \begin{minipage}{0.9\linewidth}
-            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-all/results/Theta.SIFT.neg.stacked.pdf} \\
-        \end{minipage}
-        \begin{minipage}{0.09\linewidth}
-            \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
-        \end{minipage}\captionof{figure}{~}
-        \begin{minipage}{0.9\linewidth}
-            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-all/results/Theta.SIFT.neg-weak.stacked.pdf} \\
-        \end{minipage}
-        \begin{minipage}{0.09\linewidth}
-            \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
-        \end{minipage}\captionof{figure}{~}
-        \begin{minipage}{0.9\linewidth}
-            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-all/results/Theta.SIFT.pos-weak.stacked.pdf} \\
-        \end{minipage}
-        \begin{minipage}{0.09\linewidth}
-            \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
-        \end{minipage}\captionof{figure}{~}
-        \begin{minipage}{0.9\linewidth}
-            \includegraphics[width=0.95\linewidth, page=1]{../experiments/5bins-all/results/Theta.SIFT.pos.stacked.pdf}
-        \end{minipage}
-        \begin{minipage}{0.09\linewidth}
-            \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
-        \end{minipage}
-    \end{center}
-    Sites with a higher SIFT score at the phylogenetic scale are more positively selected in the different populations.
-
-    % The previous section showed that mutations with a higher SIFT score at the phylogenetic scale are more positively selected in the different populations.
-    % However, whenever we removed the category of SNPs with the highest SIFT score ($\textrm{SIFT} \geq 0.8$), we expected the estimation of $p_+ (\textrm{SIFT} < 0.8)$ to be lower than $p_+$ (estimated on the all dataset), as we have shown that $p_+ (\Sphy < 0) < p_+$ with mutation-selection codon models.
-    % Thus SIFT scores are not providing reliable information on the current selective strength exerted on mutations, at least for high SIFT scores.
-    % Moreover, there is no defined threshold (here we arbitrarily used 0.8) to cut-off between beneficial and deleterious changes.
-
-%    \section{SIFT scores: histograms and SFS for each population}\label{sec:sift-scores:-histograms-and-sfs-for-each-population}
-%    For each population, the same figure is shown.
-%    \begin{itemize}
-%        \item Top-left panel: Histogram of SIFT score for all possible mutations away from the ancestral genome, giving the number of sites ($L$, in y-axis) across the genome with a given SIFT score.
-%        Mutations are divided into 5 classes: severely deleterious (blue), deleterious (green), weakly deleterious (light green), weakly beneficial (yellow) and beneficial (red).
-%        \item Top-right panel: Histogram of SIFT score for all observed mutations in a sample of 8 individuals (out of 512 in the original dataset) of African descent.
-%        If they are less mutations observed than expected, this class is thus undergoing purifying selection.
-%        \item Bottom-left panel: The site-frequency spectrum (SFS) represents the proportion of mutations (y-axis) with a given number of derived alleles in the population (x-axis).
-%        SFS are drawn for a random sample of 16 alleles (mean in solid line and standard deviation in filled color) for each class of selection coefficient and for synonymous mutations which are supposedly neutral (black).
-%        At high frequencies, supposedly severally deleterious mutations are underrepresented.
-%        \item Bottom-right panel:For each class of selection (and for the set of all non-synonymous mutations), information from the SFS and the expected total mutation rate are combined at the population-genetic scale to estimate the proportion of beneficial mutations $\PpolyAdv$, of nearly-neutral mutations $\PpolyNeutral$ and of deleterious mutations $\PpolyDel$.
-%    \end{itemize}
-%    \input{include-SIFT-non-adaptive}
-
-    \section*{References}
-    \printbibliography
+    \section{References}
+    \printbibliography[heading=none]
 

### 2023-04-26 manuscript/main.tex
Nicolas G. corrections

@@
 \newcommand{\Sphy}{S_{0}}
-\newcommand{\SphyDel}{\Sphy^{d}}
-\newcommand{\SphyNeu}{\Sphy^{n}}
-\newcommand{\SphyBen}{\Sphy^{b}}
+\newcommand{\SphyDel}{\mathcal{D}_0}
+\newcommand{\SphyNeu}{\mathcal{N}_0}
+\newcommand{\SphyBen}{\mathcal{B}_0}
 \newcommand{\Sphyclass}{x}
@@
 \newcommand{\Spop}{S}
-\newcommand{\SpopDel}{\Spop^{d}}
-\newcommand{\SpopNeu}{\Spop^{n}}
-\newcommand{\SpopBen}{\Spop^{b}}
+\newcommand{\SpopDel}{\mathcal{D}}
+\newcommand{\SpopNeu}{\mathcal{N}}
+\newcommand{\SpopBen}{\mathcal{B}}
 \newcommand{\ProbaPopDel}{\proba [ \SpopDel]}
@@
 \title{Mammalian protein-coding genes exhibit widespread beneficial mutations that are not adaptive}
-% Empirical evidence for widespread beneficial mutations that are not adaptive in mammalian genes
 
@@
     \begin{abstract}
-        Mutations can be beneficial by bringing an innovation to their bearer, allowing them to adapt to changes in their environments.
+        Mutations can be beneficial by bringing innovation to their bearer, allowing them to adapt to environmental change.
         However, mutations can also be beneficial because they are reverting previous deleterious changes, simply restoring pre-existing functions.
-By integrating phylogenomic and population data in mammals we estimated the contribution of beneficial back-mutations to molecular evolution, which has remained widely overlooked to this day.
-Applying a mutation-selection model to mammalian conserved protein-coding genes, we estimated amino-acid fitness landscapes.
-Assuming no changes in these fitness landscapes, any beneficial mutation is necessarily a back-mutation.
-We confirm that these beneficial back-mutations are positively selected in extant populations and demonstrate that a substantial part of ongoing positive selection is not driven by adaptation to environmental change in mammals.
+        By integrating phylogenomic and population data in mammals, we estimated the contribution of beneficial back-mutations to molecular evolution, which had remained widely overlooked so far.
+        Applying a mutation-selection model, we estimated amino acid fitness landscapes for mammalian protein-coding genes.
+        Assuming these fitness landscapes do not change, any beneficial mutation is necessarily a back-mutation.
+        We confirmed that these beneficial back-mutations are positively selected in extant populations and demonstrated that a substantial part of ongoing positive selection is not driven by adaptation to environmental change.
     \end{abstract}
@@
     While neutral mutations will not impact an individual's fitness, deleterious mutations have a negative effect, and beneficial mutations improve their bearer's fitness.
-    A beneficial mutation is thus more likely than a neutral mutation to invade the population (fixation), resulting in a substitution at the species level.
+    A beneficial mutation is thus more likely than a neutral mutation to invade the population and reach fixation, resulting in a substitution at the species level.
     Upon environmental change, because adaptive beneficial mutations toward new fitness optima are more likely, the number of substitutions also increases (fig.~\ref{fig:fitness-landscape}A).
     An increased substitution rate is thus commonly interpreted as a sign of adaptation~\cite{mcdonald_adaptative_1991, smith_adaptive_2002, welch_estimating_2006}.
-    The availability of large-scale genomic data and the development of theoretical models have enabled the detection and quantification of substitution rate increases across genes and lineages~\cite{yang_statistical_2000, eyre-walker_genomic_2006, moutinho_variation_2019}.
+    The availability of large-scale genomic data and the development of theoretical models have enabled the detection and quantification of substitution rate changes across genes and lineages~\cite{yang_statistical_2000, eyre-walker_genomic_2006, moutinho_variation_2019}.
     These approaches, now common practice in evolutionary biology, helped better understand the processes underpinning the rates of molecular evolution.
@@
     A new mutation restoring the ancestral fitness will thus be beneficial (fig.~\ref{fig:fitness-landscape}B), even though the environment has not changed~\cite{hartl_compensatory_1996, sella_application_2005, mustonen_fitness_2009, cvijovic_fate_2015}.
-    The restoration of the ancestral fitness can either happen through a mutation at a different locus – called a compensatory mutation~\cite{hartl_compensatory_1996, mustonen_fitness_2009}, or at the locus of the initial mutation – called a beneficial back-mutation~\cite{piganeau_estimating_2003, charlesworth_other_2007}.
-    While compensatory mutations change the sequence and thus induce genetic diversification, beneficial back-mutations reduce the genetic diversity and do not contribute to genetic innovation.
+    The restoration of the ancestral fitness can either happen through a mutation at a different locus –~called a compensatory mutation~\cite{hartl_compensatory_1996, mustonen_fitness_2009}, or at the locus of the initial mutation –~called a beneficial back-mutation~\cite{piganeau_estimating_2003, charlesworth_other_2007}.
+    While compensatory mutations change the sequence and thus induce genetic diversification, beneficial back-mutations reduce genetic diversity and do not contribute to genetic innovation.
     Although Tomoko Ohta considered beneficial back-mutations negligible in her nearly-neutral theory~\cite{Ohta1992}, their importance has now been acknowledged for expanding populations~\cite{charlesworth_other_2007}.
-    However, differentiating between an adaptive mutation and a beneficial back-mutation remains challenging\cite{chi_detecting_2020}.
-    In this study, we seek empirical evidence for beneficial back-mutations and test long-standing related questions, such as how common they are, and what the probability is for any beneficial mutation observed in current populations to be a back-mutation.
-    By addressing these questions, we provide novel insight into the process of adaptation and, more broadly, into how natural selection has affected protein-coding DNA sequences throughout evolution.
+    However, differentiating between an adaptive mutation and a beneficial back-mutation remains challenging~\cite{chi_detecting_2020}.
+    Indeed, an adaptive mutation responding to a change in the environment and a beneficial back-mutation have equivalent consequences for their bearer~\cite{charlesworth_other_2007}.
+    Similarly, at the population level, both types of mutations will result in a positive transmission bias of the beneficial allele.
+    However, at the macro-evolutionary scale, the consequences of these two types of mutations are fundamentally different.
+    While adaptive mutations promote phenotype diversification (fig.~\ref{fig:fitness-landscape}C), beneficial back-mutations promote phenotype stability and may help preserve well-established biological systems (fig.~\ref{fig:fitness-landscape}D).
+    Additionally, the direction of adaptive evolution is unpredictable because it is caused by an unforeseen change in the environment and, hence, in the underlying fitness landscape~\cite{bazykin_changing_2015}.
+    On the other hand, beneficial back-mutations are predictable if the underlying stable fitness landscape is known because changes from non-optimal amino acids to optimal ones will be expected.
 
-\section*{Results}
+    %In this study, we seek empirical evidence for beneficial back-mutations and test long-standing related questions, such as how common they are and what the probability is for any beneficial mutation observed in current populations to be a back-mutation.
+    %By addressing these questions, we provide novel insight into the process of adaptation and, more broadly, into how natural selection has affected protein-coding DNA sequences throughout evolution.
     \subsection*{Fitness landscape reconstruction}
-
-    An adaptive mutation responding to a change in the environment or a beneficial back-mutation have equivalent consequences for their bearer~\cite{charlesworth_other_2007}.
-    Similarly, at the level of the population, both types of mutations will result in a positive transmission bias of the beneficial allele.
-    However, at the macro-evolutionary scale the consequences of these two types of mutations are fundamentally different.
-    While adaptive mutations promote phenotype diversification (fig.~\ref{fig:fitness-landscape}C), beneficial back-mutations promote phenotype stability and may help preserve well established biological systems (fig.~\ref{fig:fitness-landscape}D).
-    Additionally, the direction of adaptive evolution is unpredictable because it is caused by an unpredictable change in the environment and, hence, in the underlying fitness landscape~\cite{bazykin_changing_2015}.
-    On the other hand, beneficial back-mutations are predictable if the underlying stable fitness landscape is known because changes from non-optimal amino acids to optimal ones will be expected.
-    In this context, the mutation-selection framework permits to relate the patterns of substitution along a phylogeny to the underlying fitness landscape~\cite{halpern_evolutionary_1998, mccandlish_modeling_2014}.
-    Such mutation-selection models applied to protein coding DNA sequences allow us to estimate relative fitnesses for all amino-acids for each site of the sequence, explicitly assuming that the underlying fitness landscape is stable along the phylogenetic tree~\cite{rodrigue_mechanistic_2010, tamuri_estimating_2012, rodrigue_detecting_2017}.
-    Importantly, because mutation-selection models at the phylogenetic scale are based on population-genetics equations, their estimates of fitness effects are directly interpretable as fitness effects for an individual within a population.
+    The mutation-selection framework permits to link the patterns of substitution along a phylogeny with the underlying fitness landscape~\cite{halpern_evolutionary_1998, mccandlish_modeling_2014}.
+    Such mutation-selection models applied to protein-coding DNA sequences allow us to estimate relative fitnesses for all amino acids for each site of the sequence, explicitly assuming that the underlying fitness landscape is stable along the phylogenetic tree~\cite{rodrigue_mechanistic_2010, tamuri_estimating_2012, rodrigue_detecting_2017}.
+    Importantly, because mutation-selection models at the phylogenetic scale are based on population-genetics equations, their estimates of selection coefficients are directly interpretable as fitness effects for an individual within a population.
     %These methods account for phylogenetic relationships, the structure of the genetic code and accommodate for underlying mutational biases~\cite{rodrigue_mechanistic_2010, tamuri_estimating_2012, latrille_improved_2022}.
 
-    Theoretically, we can thus use large-scale genomic data to assess whether the fitnesses estimated at the phylogenetic scale are predictive of the fitness effect at the population scale, for both deleterious and beneficial back-mutations.
+    Theoretically, we can thus use large-scale genomic data to assess whether the fitnesses estimated at the phylogenetic scale predict the fitness effect at the population scale for both deleterious and beneficial back-mutations.
     The placental mammals represent an excellent study system to perform such analysis.
-    Having originated $\sim$100 Mya~\cite{kumar_timetree_2017}, they diversified quickly.
-    Additionally, polymorphism data are available for many species~\cite{howe_ensembl_2021} as high quality protein-coding DNA alignments across the genome~\cite{ranwez_orthomam_2007, scornavacca_orthomam_2019}.
-    By restricting our analysis to protein-coding orthologous genes across all the phylogeny, we restrict our analysis to genes mostly under functional constrains across mammals.
-    For each gene, fitting the mutation-selection model to the multi-species sequence alignment assuming that the underlying fitness landscape is stable along the phylogenetic tree allows obtain relative fitnesses for all amino-acids for each site of the alignment (fig~\ref{fig:method}A).
-    From the fitness landscape, we can calculate the scaled selection coefficient $\Sphy$ for any possible amino-acid change at each position.
-    From the selection coefficient, we can classify any mutation as either a deleterious mutation toward a less fit amino-acid ($\SphyDel$), a nearly-neutral mutation ($\SphyNeu$) or a beneficial back-mutation toward a known fitter amino-acid ($\SphyBen$).
-    Having identified which potential DNA changes represent beneficial back-mutations (fig~\ref{fig:method}B), we retrieved polymorphism data from 28 populations belonging to 6 genera (\textit{Equus}, \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus} and \textit{Homo}) to assess the presence of beneficial back-mutations at the population scale.
-    We focused on currently segregating mutations within populations and also on substitutions in the terminal branches, and checked if any of these observed changes where beneficial back-mutations (fig~\ref{fig:method}C-E).
-    Essentially, by integrating large scale genomic datasets at both phylogenetic and population scales we have been able to estimate the amount of beneficial back-mutations across the entire exome for 6 different mammalian genera (fig~\ref{fig:method}F-H).
+    Having originated $\sim$100 million years ago~\cite{kumar_timetree_2017}, they diversified quickly.
+    Additionally, polymorphism data are available for many species~\cite{howe_ensembl_2021}, as are high quality protein-coding DNA alignments across the genome~\cite{ranwez_orthomam_2007, scornavacca_orthomam_2019}.
+    By restricting our analysis to protein-coding orthologous genes, we focus on genes under functional constrains across mammals.
+    For each gene, fitting the mutation-selection model to the multi-species sequence alignment, assuming that the underlying fitness landscape is stable along the phylogenetic tree, allows us to obtain relative fitnesses for all amino acids for each site of the alignment (fig.~\ref{fig:method}A).
+    From the fitness landscape, we can calculate the scaled selection coefficient ($\Sphy$) for any possible amino acid change at each position.
+    According to its $\Sphy$ value, we can classify any mutation as either a deleterious mutation toward a less fit amino acid ($\SphyDel \coloneqq \Sphy < -1$), a nearly-neutral mutation ($\SphyNeu \coloneqq -1 < \Sphy <1$) or a beneficial back-mutation toward a known fitter amino acid ($\SphyBen \coloneqq \Sphy > 1$).
+    Having identified which potential DNA changes represent beneficial back-mutations (fig.~\ref{fig:method}B), we retrieved polymorphism data from 28 populations belonging to 6 genera (\textit{Equus}, \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus}, and \textit{Homo}) to assess the presence of beneficial back-mutations at the population scale.
+    We focused on mutations currently segregating within populations and substitutions in the terminal branches, and checked if any of these observed changes were beneficial back-mutations (fig.~\ref{fig:method}C-E).
+    In this study, by integrating large-scale genomic datasets at both phylogenetic and population scales, we have been able to estimate the number of beneficial back-mutations across the entire exome of the six genera (figs.~\ref{fig:method}F-G).
 
@@
         \caption{
-            (A \& B) At a given site of a protein-coding DNA sequence, the different amino-acids (x-axis) have different fitness values (y-axis).
+            (A \& B) For a given codon position of a protein-coding DNA sequence, amino acids (x-axis) have different fitness values (y-axis).
             Under a fluctuating fitness landscape (A), these fitnesses change with time.
-            The protein sequence follows the moving target defined by the amino-acid fitnesses, and since substitutions are accepted preferentially if they are in the direction of this target, substitutions are on average adaptive.
-            At the phylogenetic scale (C) beneficial substitutions are common (positive signs), promoting phenotype diversification across species.
-            Under a stable fitness landscape (B), most mutations reaching fixation are either slightly deleterious reaching fixation due to drift, or are beneficial back-mutations restoring a more optimal amino-acid.
-            At the phylogenetic scale (D) deleterious substitutions (negative signs) are often reverted via beneficial back-mutations (positive signs), promoting phenotype stability and preserving well established biological systems.
-            Even though individually any back-mutation might have a small beneficial effect on its bearer, we expect beneficial back-mutations to be scattered across the genome and the genome-wide signature of beneficial back-mutations to be detectable and quantifiable.}
+            The protein sequence follows the moving target defined by the amino-acid fitnesses.
+Since substitutions are preferentially accepted if they are in the direction of this target, substitutions are, on average, adaptive.
+            At the phylogenetic scale (C), beneficial substitutions are common (positive signs), promoting phenotype diversification across species.
+            Under a stable fitness landscape (B), most mutations reaching fixation are either slightly deleterious reaching fixation due to drift or are beneficial back-mutations restoring a more optimal amino acid.
+            At the phylogenetic scale (D), deleterious substitutions (negative signs) are often reverted via beneficial back-mutations (positive signs), promoting phenotype stability and preserving well-established biological systems.
+            Even though, individually, any back-mutation might have a small beneficial effect on its bearer, we expect beneficial back-mutations to be scattered across the genome and the genome-wide signature of beneficial back-mutations to be detectable and quantifiable.}
         \label{fig:fitness-landscape}
@@
             Selection coefficients at the phylogenetic and population scales.
-            At the phylogenetic scale (A), the amino-acid Wrightian fitness for each site is estimated from protein-coding DNA alignments using mutation-selection codon models.
-            For every possible mutation, the difference in amino-acid fitness before and after the mutation allows us to compute the selection coefficient at the phylogenetic scale ($\Sphy$).
-            Mutations with $\Sphy < -1$ are considered deleterious ($\SphyDel$ in red), and mutations with $-1 < \Sphy < 1$ are considered nearly-neutral ($\SphyNeu$ in green).
-            Mutations with $\Sphy > 1$ are toward a fitter amino-acids, and thus are considered beneficial back-mutations ($\SphyBen$ in blue), repairing existing functions (B).
-            At the population scale (C), each observed single nucleotide polymorphism (SNP) segregating in the population is classified according to its $\Sphy$ value.
+            At the phylogenetic scale (A), we estimated the amino-acid Wrightian fitness for each site from protein-coding DNA alignments using mutation-selection codon models.
+            For every possible mutation, the difference in amino acid fitness before and after the mutation allows us to compute the selection coefficient at the phylogenetic scale ($\Sphy$).
+            Depending on $\Sphy$ (B) mutations can be predicted as deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) or beneficial back-mutations ($\SphyBen$) toward a fitter amino acid and repairing existing functions.
+            At the population scale (C), each observed single nucleotide polymorphism (SNP) segregating in the population can also be classified according to its $\Sphy$ value.
             Similarly, substitutions along the terminal branch are classified depending on their $\Sphy$ value.
             Together, substitutions and polymorphisms are contrasted to synonymous changes used as a neutral expectation such as estimate selection coefficients at the population scale ($\Spop$).
-            For each class of selection ($\SphyBen$, $\SphyNeu$, $\SphyDel$), we can thus assess whether $\Sphy$ predicts $\Spop$ (E), and compute \textit{precision} (F-G) and \textit{recall} (F-H) for each class.
-            The \textit{recall} value for the class $\SphyBen$ is the probability of back-mutations among all beneficial ones (H).
+            For each class of selection ($\SphyDel$, $\SphyNeu$, $\SphyBen$), we can thus assess whether $\Sphy$ predicts $\Spop$ and compute \textit{precision} (F) and \textit{recall} (G) for each class.
+            The \textit{recall} value for class $\SphyBen$ is the probability of back-mutations among all beneficial ones (G).
         }
@@
     \subsection*{Selection along the terminal branches}
-    First, we assessed whether fitness effects derived from the mutation-selection model at the phylogenetic scale are predictive of selection occurring in terminal branches.
-    To achieve this, we recovered the mutations that reached fixation in the terminal branches of 6 different mammalian genera.
-    Only mutations fixed in a population were considered as substitutions in the corresponding branch, while segregating mutations were discarded from this analysis.
-    For each substitution identified in the terminal branches, we obtained its scaled selection coefficient ($\Sphy$) as the change in amino-acid fitness at the corresponding codon site in the mammalian alignment (fig.~\ref{fig:method}A-C).
-    Importantly, the mammalian alignment used to estimate amino-acid fitness landscape does not include the genera for which we reconstructed the substitutions, to avoid fallacy and circularity in the reasoning.
-    Because $\Sphy$ was based on estimation of fitness effects at the mammalian scale, mutations with $\Sphy>1$ were considered beneficial back-mutations ($\SphyBen$), toward a fitter amino acid.
-    Among all the substitutions that were found in each terminal branch, between 10 and 13\% were $\SphyBen$ (table~S1).
+    First, we assessed whether fitness effects derived from the mutation-selection model at the phylogenetic scale predict selection occurring in terminal branches.
+    We recovered the mutations that reached fixation in the terminal branches of the six genera.
+    We only considered mutations fixed in a population as substitutions in the corresponding branch and discarded segregating mutations.
+    We classified each substitution identified in the terminal branches as either $\SphyDel$, $\SphyNeu$, or $\SphyBen$ depending on its $\Sphy$ value obtained at the phylogenetic scale (fig.~\ref{fig:method}A-C).
+    Importantly, the mammalian alignment used to estimate the amino acid fitness landscape did not include the genera for which we reconstructed the substitutions to avoid fallacy and circular reasoning.
+    Because $\Sphy$ was based on estimating fitness effects at the mammalian scale, mutations with $\Sphy>1$ were considered beneficial back-mutations ($\SphyBen$) toward a fitter amino acid.
+    Among all the substitutions found in each terminal branch, between 10 and 13\% were $\SphyBen$ (table~S1 and fig.~\ref{fig:homo-afr-results}B for humans).
     In principle, beneficial back-mutations are bound to reach fixation more often than neutral substitutions.
-    Hence, we calculated the $\dnds$ ratio of non-synonymous over synonymous divergence for all terminal lineages, restricting the non-synonymous changes to our set of $\SphyBen$.
-    We obtained values between 1.15 and 1.68 in the different lineages (table~S1), implying that $\SphyBen$ reached fixation more frequently than synonymous mutations that are supposed to be neutral, which means that these back-mutations are effectively beneficial.
+    Hence, we calculated the $\dnds$ ratio of non-synonymous over synonymous divergence for all terminal lineages, focusing on the non-synonymous changes predicted as beneficial back-mutations ($\dn(\SphyBen) / \ds$).
+    We obtained values between 1.15 and 1.68 in the different lineages (table~S1), implying that $\SphyBen$ mutations reached fixation more frequently than synonymous mutations that are supposed to be neutral, implying that these back-mutations are effectively beneficial.
 
-    This result further indicated that using $\dnds$ as a proxy for the efficiency of purifying selection is biased due to the presence of beneficial back-mutations.
-    By discarding beneficial back-mutations from the estimation of $\dnds$, this corrected estimation represents the true efficiency of purifying selection.
-    By comparing these two ways of calculating $\dnds$ (see Materials \& Methods), we estimated that $\dnds$ values are inflated by between 22\% and 27\% across genera because of beneficial back-mutations while the latter only represent between 1\% and 2\% of mutational opportunities (table~S2).
+    This result further indicated that using $\dnds$ as an estimate of adaptation is biased due to the presence of beneficial back-mutations among the non-synonymous substitutions.
+    By discarding all beneficial back-mutations we can obtain an estimate of $\dnds$ which is not inflated.
+    By comparing these two ways of calculating $\dnds$ (see section~S\ref{subsec:substitution-mapping-in-the-terminal-branch} in Materials \& Methods), we calculated that beneficial back-mutations inflate $\dnds$ values by between 22\% and 27\% across genera while only representing between 1\% and 2\% of mutational opportunities (table~S2 andfig.~\ref{fig:homo-afr-results}A for humans).
 
     \subsection*{Selection in populations}
-    Second, we assessed whether our scaled selection coefficients ($\Sphy$) were predictive of selective forces exerted at the population level.
-    To achieve this, we reconstructed the ancestral genome of each population to polarize single nucleotide polymorphism (SNPS) segregating in the population.
-    The scaled selection coefficient ($\Sphy$) predicted for every non-synonymous SNPs allow us to classify them as either $\SphyDel$, $\SphyNeu$ or $\SphyBen$ (fig.~\ref{fig:method}B-C).
+    Second, we assessed whether our calculated $\Sphy$ values are also indicative of the selective forces exerted at the population level.
+    So, we retrieved single nucleotide polymorphisms (SNPs) segregating in 28 mammalian populations.
+    To determine if SNPs were ancestral of derived, we reconstructed the ancestral genome of each population.
+    We then classified every non-synonymous SNP as either $\SphyDel$, $\SphyNeu$, or $\SphyBen$ according its $\Sphy$ value (fig.~\ref{fig:method}B-C).
 
-    In humans, some SNPs have been associated to specific clinical prognosis terms~\cite{landrum_clinvar_2018}.
-Those clinical terms have been obtained by clinical evaluation of the impact of variants on human Mendelian disorders~\cite{landrum_clinvar_2018}.
-Thus they provide an orthogonal estimate of the effect of a mutation on human health, giving us an opportunity to evaluate whether this effect is in accordance with its predicted fitness effect.
-    To do so, we investigated whether the non-synonymous SNPs classified as $\SphyDel$ or as $\SphyBen$ showed an enrichment in specific clinical terms in comparison to SNPs classified as $\SphyNeu$.
-    Our results show that SNPs predicted as deleterious are associated to clinical terms such as \textit{Likely Pathogenic} and \textit{Pathogenic}, implying that, in general, the selective pressure of a mutation exerted across mammals is also predictive of its clinical effect in humans (table~S6).
+    In humans, some SNPs have been associated with specific clinical prognosis terms~\cite{landrum_clinvar_2018} obtained by clinical evaluation of the impact of variants on human Mendelian disorders~\cite{landrum_clinvar_2018}.
+    Thus, they provide an orthogonal estimate of the effect of a mutation on human health, allowing us to evaluate whether this effect follows its predicted fitness effect.
+    Therefore, we investigated whether the non-synonymous SNPs classified as $\SphyDel$ or $\SphyBen$ showed enrichment in specific clinical terms compared to SNPs classified as $\SphyNeu$.
+    Our results show that SNPs predicted as deleterious are associated with clinical terms such as \textit{Likely Pathogenic} and \textit{Pathogenic}, implying that, in general, the selective pressure of a mutation exerted across mammals is also predictive of its clinical effect in humans (table~S6).
     Conversely, back-mutations are associated with clinical terms such as \textit{Benign} and \textit{Likely Benign}, which shows that back-mutations are less likely to be functionally damaging.
 
-    In addition to clinical prognosis, frequencies at which SNPs are segregating within populations also provide information on their selective effects.
-    For instance, deleterious SNPs are usually segregating at lower frequencies because of the effect of purifying selection, which tends to remove them from the population.
+    In addition to clinical prognosis, frequencies at which SNPs are segregating within populations provide information on their selective effects.
+    For instance, deleterious SNPs usually segregate at lower frequencies because of purifying selection, which tends to remove them from the population (fig.~\ref{fig:homo-afr-results}C for humans).
     By gathering information across many SNPs, it is possible to estimate the distribution of fitness effects (DFE) at the population scale, taking synonymous SNPs as a neutral expectation~\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009, galtier_adaptive_2016, tataru_inference_2017}.
-    From the estimated DFE, we can derive the proportion of beneficial mutations ($\ProbaPopBen$), nearly-neutral mutations ($\ProbaPopNeu$) and deleterious mutations ($\ProbaPopDel$) at the population scale.
+    From the estimated DFE, we can derive the proportion of beneficial mutations ($\ProbaPopBen$), nearly-neutral mutations ($\ProbaPopNeu$) and deleterious mutations ($\ProbaPopDel$) at the population scale (see section~\ref{subsec:s-polymorphism-method} in Materials \& Methods).
     These approaches offer a unique opportunity to contrast selection coefficients estimated at the population scale ($\Spop$) and at the phylogenetic scale ($\Sphy$).
 
-    Across our classes of selection ($\SphyDel$, $\SphyNeu$ and $\SphyBen$), one can ultimately estimate the proportion of false positives and false negatives, leading to an estimation of \textit{precision} and \textit{recall} (see Materials \& Methods).
-    Across 28 populations of different mammal species, mutations predicted to be deleterious at the phylogenetic scale were indeed purged at the population scale, with a \textit{precision} in the range of 89--97\% (table.~\ref{table:proba}).
-    Conversely, a \textit{recall} in the range of 95--98\% implies that mutations found to be deleterious at the population scale were most likely predicted to be so at the phylogenetic scale (table.~\ref{table:proba}).
-    Altogether, purifying selection is largely predictable and amino acids with negative fitness effects across mammals were effectively purged away in each population.
+    Across our selection classes ($\SphyDel$, $\SphyNeu$ and $\SphyBen$), one can ultimately estimate the proportion of correct and incorrect predictions, leading to an estimation of \textit{precision} and \textit{recall} (fig.~\ref{fig:method}F-G and section~\ref{subsec:precisison_recall} in Materials \& Methods).
+    Across 28 populations of different mammal species, mutations predicted to be deleterious at the phylogenetic scale ($\ProbaPopDel$) were indeed purged at the population scale, with a \textit{precision} in the range of 89--97\% (table~\ref{table:proba} and fig.~\ref{fig:homo-afr-results}D for humans).
+    Conversely, a \textit{recall} in the range of 95--98\% implies that mutations found to be deleterious at the population scale were most likely also predicted to be deleterious at the phylogenetic scale (table~\ref{table:proba}).
+    Altogether, purifying selection is largely predictable and amino acids with negative fitness across mammals have been effectively purged away in each population.
 
-    Mutations predicted as $\SphyNeu$ were effectively composed of a mix of neutral and selected mutations with varying \textit{precision} (18--74\%) and \textit{recall} (21--52\%) across the different populations (table.~\ref{table:proba}).
-    The variable proportions found between populations can be explained by the effective number of individuals in the population ($\Ne$), which is known to be a major driver of selection efficacy.
-    Since $\Ne$ is not directly measurable, we used Watterson's $\theta_w$ as a proxy to order populations by their levels of synonymous diversity.
+    Mutations predicted as $\SphyNeu$ were effectively composed of a mix of neutral and selected mutations with varying \textit{precision} (18--74\%) and \textit{recall} (21--52\%) across the different populations (table~\ref{table:proba}, fig.~\ref{fig:homo-afr-results}D for Humans).
+    The variable proportions between populations can be explained by the effective number of individuals in the population ($\Ne$), a major driver of selection efficacy.
+    Since $\Ne$ is not directly measurable, we used Watterson's $\theta_S$ as a proxy to order populations by their levels of synonymous diversity.
     Higher synonymous diversity was associated with a smaller proportion of nearly-neutral mutations (fig.~\ref{fig:diversity}A).
-    This result follows the prediction of the nearly-neutral theory and suggests that in populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}), discrimination between beneficial and deleterious mutations is more likely to occur (fig~S1-S9).
-    Conversely, in populations with lower diversity (e.g.~\textit{Homo}) many more mutations are effectively neutral.
+    This result follows the prediction of the nearly-neutral theory and suggests that in populations with higher diversity (e.g.,~\textit{Bos} or \textit{Ovis}), discrimination between beneficial and deleterious mutations is more likely to occur (figs.~S1-S9).
+    Conversely, many more mutations are effectively neutral in populations with lower diversity (e.g.,~\textit{Homo}).
 
     %Of note, mutations with $\Sphy>1$ only represented ca.~1.5\% of all possible new mutations, but ca.~8.5\% of all observed mutations in the population (blue in fig.~\ref{fig:homo-afr-results}A-B, table~S3).
-    Finally, mutations predicted to be beneficial back-mutations based on the selection coefficients at the phylogenetic scale ($\SphyBen$) were indeed beneficial for individuals currently bearing them, with a precision in the range of 15--52\% (table.~\ref{table:proba}).
-    This result confirms that selection towards amino acids that are restoring existing functions is ongoing in these populations.
-    Importantly, the \textit{recall} value in this case, computed as $\proba [ \SphyBen  \given  \SpopBen]$, is the probability for a beneficial mutation at the population scale to be a beneficial back-mutation, that is, going toward a fitter amino-acid (fig.~\ref{fig:method}F).
-    In other words, the \textit{recall} value quantifies the amount of beneficial mutations that are restoring damaged genomes instead of creating adaptive innovations.
-    Across the 28 populations, this proportion is in the range of 11--70\% (table.~\ref{table:proba}).
+    Finally, mutations predicted to be beneficial back-mutations based on the selection coefficients at the phylogenetic scale ($\SphyBen$) were indeed beneficial for individuals bearing them, with a \textit{precision} (fig.~\ref{fig:method}F) in the range of 15--52\% (table~\ref{table:proba} and fig.~\ref{fig:homo-afr-results}D for humans).
+    This result confirms that selection towards amino acids restoring existing functions is ongoing in these populations.
+    Importantly, the \textit{recall} value in this case, computed as $\proba [ \SphyBen  \given  \SpopBen]$, is the probability for a beneficial mutation at the population scale to be a beneficial back-mutation, i.e., going toward a fitter amino acid (fig.~\ref{fig:method}G).
+    In other words, the \textit{recall} value quantifies the number of beneficial mutations restoring damaged genomes instead of creating adaptive innovations.
+    Across the 28 populations, this proportion is in the range of 11--70\% (table~\ref{table:proba}).
 
@@
         \caption{
-            (A) Distribution of fitness effects ($\Sphy$), predicted for all possible mutations away from the ancestral human genome.
-            Mutations are divided into three classes of selection: deleterious ($\SphyDel$ in red), nearly-neutral ($\SphyNeu$ in green) and beneficial ($\SphyBen$ blue, supposedly beneficial back-mutations).
-            (B) Distribution of fitness effects ($\Sphy$) for all observed substitutions along the \textit{Homo} branch after the \textit{Homo}-\textit{Pan} splits.
-            If there are less substitutions observed than expected, this class is thus undergoing purifying selection, as is the case of for $\SphyDel$.
-            (C) The site-frequency spectrum (SFS) in humans of African descent for a random sample of 16 alleles (mean in solid line and standard deviation in color shade) for each class of selection and for synonymous mutations, which are supposedly neutral (black).
+            (A) Distribution of scaled selection coefficients ($\Sphy$), predicted for all possible mutations away from the ancestral human genome.
+            Mutations are divided into three classes of selection: deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial ($\SphyBen$, supposedly beneficial back-mutations).
+            (B) Distribution of scaled selection coefficients ($\Sphy$) for all observed substitutions along the \textit{Homo} branch after the \textit{Homo}-\textit{Pan} split.
+            If there are fewer substitutions than expected, this class is thus undergoing purifying selection, as is the case for $\SphyDel$.
+            (C) The site-frequency spectrum (SFS) in humans of African descent for a random sample of 16 alleles (means in solid lines and standard deviations in color shades) for each class of selection and for synonymous mutations, supposedly neutral (black).
 The SFS represents the proportion of mutations (y-axis) with a given number of derived alleles in the population (x-axis).
             At high frequencies, deleterious mutations are underrepresented.
-            (D) Proportion of beneficial $\ProbaPopBen$, nearly-neutral $\ProbaPopNeu$ and deleterious mutations $\ProbaPopDel$ estimated at the population scale for each class of selection at the phylogenetic scale.
-Proportions depicted here are not weighted by mutational opportunities.
+            (D) Proportion of beneficial $\ProbaPopDel$, nearly-neutral $\ProbaPopNeu$, and deleterious mutations $\ProbaPopBen$ estimated at the population scale for each class of selection at the phylogenetic scale.
+Proportions depicted here are not weighted by their mutational opportunities.
         }
@@
                 \textbf{Species} &
-                $\bm{\pi_{\text{S}}}$ &
+                $\bm{\theta_{\text{S}}}$ &
                 \makecell{\textbf{Precision} \\ $\bm{\proba [\SpopDel \given \SphyDel]}$} &
@@
         \caption{
-            Precision and \textit{recall} for estimated selection coefficient of mutations given by mutation-selection models ($\Sphy$), in 28 populations across 6 genera.
-            Precision and \textit{recall} are computed for three classes of mutations: deleterious, nearly-neutral and beneficial.
-            Precision is the recovered estimation of selection coefficient at population scale ($\Spop$) given that $\Sphy$ is known.
-            Conversely, \textit{recall} is the recovered estimation of $\Sphy$ given selection coefficient at the population scale ($\Spop$) is known.
-            Recall for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is thus the proportion of beneficial back-mutations among all beneficial mutations.
-            $\bm{\pi_{\text{S}}}$ is the observed genetic diversity (number of SNPs per site) counted over synonymous sites.
+            \textit{Precision} and \textit{recall} for estimated selection coefficient of mutations given by mutation-selection models ($\Sphy$).
+            \textit{Precision} is the estimation of the selection coefficient at population scale ($\Spop$) given that $\Sphy$ is known.
+            Conversely, \textit{recall} is the estimation of $\Sphy$ given selection coefficient at the population scale ($\Spop$) is known.
+            \textit{Recall} for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is thus the proportion of beneficial back-mutations among all beneficial mutations.
+            Watterson's $\theta_{\text{S}}$ is the observed genetic diversity calculated for synonymous changes.
         }
@@
 
-    This study represents an important step towards an integration of different evolutionary scales necessary to decipher the combined effects of mutation, selection and drift on genome evolution.
-    In particular, quantifying the proportion of beneficial back-mutations among all beneficial mutations has only been achievable by combining genome-wide data from both phylogenetic and population scales.
-    At the phylogenetic scale, for each site of a protein-coding DNA alignment, codon diversity can allow for the reconstruction of an amino-acid fitness landscape, assuming that this landscape is stable along the phylogeny.
-    Across all sites, these amino-acid fitness landscapes allow us to predict the selection coefficient ($\Sphy$) of any mutation along a protein coding sequence.
-    These selective effects can be compared to observations at the population level.
-    By doing so, we have been able to confirm that mutations predicted to be deleterious ($\SphyDel \coloneqq \Sphy < -1$) are purified away in extant populations.
-    Our results reflect on previous studies showing that SIFT scores~\cite{ng_sift_2003, vaser_sift_2016}, which are based on amino-acid alignments across species, have also been found to be informative of the deleterious fitness effects exerted at the population scale~\cite{chen_hunting_2021}.
-    However, and contrary to SIFT scores, our mutation-selection model is parameterized by a fitness function such that changes are directly interpretable as fitness effects.
-    In this regard, an interesting prediction of our model is that back-mutations are beneficial because they are reverting previous deleterious changes.
-    We have tested this hypothesis and have found that these back-mutations ($\SphyBen \coloneqq \Sphy > 1 $) are indeed beneficial in extant populations.
-    We estimated that between 18 and 78\% of all beneficial mutations in mammalian populations have not been driven by adaptation, but instead have reversed deleterious substitutions which have accumulated along the phylogeny.
-    These results suggest that many beneficial mutations are non-adaptive, but are rather restoring ancestral states of higher fitness.
-    Hence, the extent of adaptive evolution can only be correctly estimated if we can account for the number of beneficial back-mutations~\cite{keightley_what_2010, rice_evolutionarily_2015}.
+    This study represents an essential step toward integrating the different evolutionary scales necessary to understand the combined effects of mutation, selection, and drift on genome evolution.
+    In particular, we have been able to quantify the proportion of beneficial back-mutations among all beneficial mutations, which has only been achievable by combining genome-wide data from both phylogenetic and population scales.
+    At the phylogenetic scale, codon diversity at each site of a protein-coding DNA alignment allows for reconstructing an amino acid fitness landscape, assuming that this landscape is stable along the phylogeny.
+    These amino-acid fitness landscapes allow us to predict any mutation’s selection coefficient ($\Sphy$) along a protein-coding sequence.
+    We can compare these selective effects to observations at the population level.
+    By doing so, we confirmed that mutations predicted to be deleterious ($\SphyDel \coloneqq \Sphy < -1$) are purified away in extant populations.
+    Our results concur with previous studies showing that SIFT scores~\cite{ng_sift_2003, vaser_sift_2016}, based on amino acid alignments across species, also inform on the deleterious fitness effects exerted at the population scale~\cite{chen_hunting_2021}.
+    However – contrary to SIFT scores – our mutation-selection model is parameterized by a fitness function such that changes are directly interpretable as fitness effects.
+    In this regard, an interesting prediction of our model is that back-mutations are beneficial because they revert previous deleterious changes.
+    We have tested this hypothesis and found that these back-mutations ($\SphyBen \coloneqq \Sphy > 1 $) are indeed beneficial in extant populations.
+    We estimated that between 18 and 78\% of all beneficial mutations in mammalian populations have not been driven by adaptation but instead have reversed deleterious substitutions which have accumulated along the phylogeny.
+    These results suggest that many beneficial mutations are non-adaptive but rather restore ancestral states of higher fitness.
+    Hence, we can correctly estimate the extent of adaptive evolution only if we account for the number of beneficial back-mutations~\cite{keightley_what_2010, rice_evolutionarily_2015}.
     Altogether, we argue that we should dissociate positive selection from adaptive evolution and limit the use of adaptive mutations to those that are associated with adaptation to environmental change as such~\cite{charlesworth_other_2007, mustonen_fitness_2009}.
@@
 
-    Across the genome, both beneficial-back mutations and deleterious mutations reaching fixation generate a balance in which genomes are constantly damaged and restored simultaneously at different loci.
-    Essentially, since the probability of fixation of mutations depends on the effective population size ($\Ne$), the history of $\Ne$ plays a crucial role in the amount of beneficial back-mutations compensating deleterious mutations~\cite{latrille_inferring_2021}.
-    For example, a population size expansion will increase the efficacy of selection and a larger proportion of mutations will be beneficial (otherwise effectively neutral), thus increasing the number of beneficial back-mutations.
-    On the other hand, a population that has experienced a high $\Ne$ throughout its history should be closer to an optimal state under a stable fitness landscape having suffered fewer fixations of deleterious mutations and therefore decreasing the probability of beneficial back-mutations~\cite{huber_determining_2017}.
-    Overall, the proportion of beneficial back-mutations is expected to be more dependent on the long-term $\Ne$, as well as its expansions and contractions, rather than on the short-term $\Ne$~\cite{charlesworth_other_2007,huber_determining_2017}.
-    In this regard, the proportion of back-mutations among all beneficial ones did not show a clear relationship with the synonymous diversity within a population (Watterson's $\theta_w$) (fig.~\ref{fig:diversity}B), which should, in theory, reflect the short-term $\Ne$.
+    Across the genome, beneficial-back mutations and deleterious mutations reaching fixation create a balance in which genomes are constantly damaged and restored simultaneously at different loci.
+    Since the probability of fixation of mutations depends on the effective population size ($\Ne$), the history of $\Ne$ plays a crucial role in setting the number of beneficial back-mutations compensating for deleterious mutations~\cite{latrille_inferring_2021}.
+    For example, a population size expansion will increase the efficacy of selection, and a larger proportion of mutations will be beneficial (otherwise effectively neutral), thus increasing the number of beneficial back-mutations.
+    On the other hand, a population that has experienced a high $\Ne$ throughout its history should be closer to an optimal state under a stable fitness landscape, having suffered fewer fixations of deleterious mutations and therefore decreasing the probability of beneficial back-mutations~\cite{huber_determining_2017}.
+    Overall, we expect the proportion of beneficial back-mutations to be more dependent on $\Ne$’s long-term expansions and contractions than on the short-term ones~\cite{charlesworth_other_2007,huber_determining_2017}.
+    Indeed the proportion of back-mutations among all beneficial mutations did not show a clear relationship with the synonymous diversity within a population (Watterson's $\theta_S$) (fig.~\ref{fig:diversity}B), which should, in theory, reflect the population's short-term $\Ne$.
 
@@
     %This reduction should mechanistically increase the proportion of adaptive substitutions.
-    %However, this does not imply that the rate of adaptation (i.e the number of changes in the fitness landscape per site per generation) is higher ~\cite{galtier_adaptive_2016}.
+    %However, this does not imply that the rate of adaptation (i.e the number of changes in the fitness landscape per site per generation) is higher~\cite{galtier_adaptive_2016}.
 
     The exact estimation of the contribution of beneficial back-mutations to positive selection relies on some hypotheses at both the phylogenetic and population scales and is sensitive to methodological limitations.
-    Indeed, in order to be conservative, we considered that any mutation under positive selection at the scale of populations, but not predicted as such at the phylogenetic scale (false negatives) is potentially an adaptation.
-    However, adaptive mutations are not the only contributors to these false negatives since limited data quality and potentially inadequate modelling choices of both the fitness landscape and the DFE might also lead to false negatives.
-    Moreover, a mutation which is inferred to be nearly-neutral at the phylogenetic scale, but found to be positively selected at the population scale will also be considered as a false negative (and thus an adaptation), even if this discrepancy could just be due to a population size expansion ~\cite{lanfear_population_2014, jones_shifting_2017, platt_protein_2018}.
-    Given this inflation of false negatives, we consider our estimated proportion of adaptive mutations among beneficial ones to be an overestimation and, hence, our estimation of beneficial back-mutations among advantageous ones should be taken as a lower bound.
+    Indeed, to be conservative, we considered that any mutation under positive selection at the population scale ($\SpopBen$) but not predicted as such at the phylogenetic scale (not $\SphyBen$) is potentially an adaptation.
+    However, adaptation is not the only factor hindering the detection of beneficial back-mutations; data quality and potentially inadequate modeling choices of both the fitness landscape and the DFE might also lead to missed predictions.
+    Moreover, a mutation inferred as nearly-neutral at the phylogenetic scale ($\SphyNeu$) but positively selected at the population scale ($\SpopBen$) will also be considered a missed prediction, even if this discrepancy could just be due to a population size expansion~\cite{lanfear_population_2014, jones_shifting_2017, platt_protein_2018}.
+    Given this inflation of missed predictions, we consider our estimated proportion of adaptive mutations among beneficial ones to be an overestimation.
+Therefore, our estimation of beneficial back-mutations among advantageous ones should be taken as a lower bound.
 
@@
         \caption{
-            (A) Proportion of nearly-neutral mutations at the population scale ($\proba [ \SpopNeu]$ in the y-axis), shown as a function of the synonymous diversity (Watterson's $\theta_w$ in the x-axis).
-            (B) Proportion of beneficial back-mutations among all beneficial mutations ($\proba [ \SphyBen  \given  \SpopBen]$ in the y-axis), shown as a function of the synonymous diversity (Watterson's $\theta_w$ in the x-axis).
+            (A) Proportion of nearly-neutral mutations at the population scale ($\proba [ \SpopNeu]$ in the y-axis), shown as a function of the synonymous diversity (Watterson's $\theta_{\text{S}}$ in the x-axis).
+            (B) Proportion of beneficial back-mutations among all beneficial mutations ($\proba [ \SphyBen  \given  \SpopBen]$ in the y-axis), shown as a function of the synonymous diversity (Watterson's $\theta_{\text{S}}$ in the x-axis).
         }
@@
 
-    \subsection*{The role of epistasis in mammalian protein-coding genes}
-
-    In our study, we focused on mutations toward a more optimal amino-acid at a given site, assuming that amino-acid fitness landscapes are site-specific and also independent of one another.
-    Contrarily, under epistasis, the fitness effect of a mutation at a particular site depends on the amino-acids present at other sites.
-    Epistasis therefore allows for compensatory mutations, which restore fitness through mutations at loci different from where deleterious mutations take place, and this process also leaves signals interpretable as non-adaptive beneficial mutations~\cite{hartl_compensatory_1996, pollock_strong_2014, starr_epistasis_2016}.
-    Also, epistasis has been shown to play a role in the evolution of protein-coding genes, with amino-acid residues in contact within a protein or between proteins tending to co-evolve~\cite{breen_epistasis_2012, starr_epistasis_2016}.
-    Particularly, the residues in contact co-evolve to become more compatible with each other generating an entrenchment, making empirical evidence for beneficial back-mutations harder to find since restoring mutations becomes less and less likely to occur over time~\cite{goldstein_nonadaptive_2015, goldstein_sequence_2017, park_epistatic_2022}.
-    Nevertheless, the fact that we observe such a high proportion of beneficial back-mutations suggests that the underlying assumptions of our model, namely site-independence, implying no epistasis, and a static fitness landscape, are a reasonable approximation for the underlying fitness landscape of proteins.
-    Our results imply that the fitness effects of new mutations are mostly conserved across mammalian orthologs, in agreement with other studies showing that for conserved orthologs with similar structures and functions, models without epistasis provide a reasonable estimate of fitness effects in protein coding genes~\cite{ashenberg_mutational_2013, youssef_consequences_2020}.
+    %\subsection*{The role of epistasis in mammalian protein-coding genes}
+    %
+    %In our study, we focused on mutations toward a more optimal amino-acid at a given site, assuming that amino-acid fitness landscapes are site-specific and also independent of one another.
+    %Contrarily, under epistasis, the fitness effect of a mutation at a particular site depends on the amino-acids present at other sites.
+    %Epistasis therefore allows for compensatory mutations, which restore fitness through mutations at loci different from where deleterious mutations take place, and this process also leaves signals interpretable as non-adaptive beneficial mutations~\cite{hartl_compensatory_1996, pollock_strong_2014, starr_epistasis_2016}.
+    %Also, epistasis has been shown to play a role in the evolution of protein-coding genes, with amino-acid residues in contact within a protein or between proteins tending to co-evolve~\cite{breen_epistasis_2012, starr_epistasis_2016}.
+    %Particularly, the residues in contact co-evolve to become more compatible with each other generating an entrenchment, making empirical evidence for beneficial back-mutations harder to find since restoring mutations becomes less and less likely to occur over time~\cite{goldstein_nonadaptive_2015, goldstein_sequence_2017, park_epistatic_2022}.
+    %Nevertheless, the fact that we observe such a high proportion of beneficial back-mutations suggests that the underlying assumptions of our model, namely site-independence, implying no epistasis, and a static fitness landscape, are a reasonable approximation for the underlying fitness landscape of proteins.
+    %Our results imply that the fitness effects of new mutations are mostly conserved across mammalian orthologs, in agreement with other studies showing that for conserved orthologs with similar structures and functions, models without epistasis provide a reasonable estimate of fitness effects in protein coding genes~\cite{ashenberg_mutational_2013, youssef_consequences_2020}.
 
@@
 
-    A long-standing debate in molecular evolution is whether the variations we observe between species in protein-coding genes are mostly due to nearly-neutral mutations reaching fixation by drift, or if they are mostly due to adaptation ~\cite{kimura_evolutionary_1968,kern_neutral_2018,jensen_importance_2019,gillespie_substitution_1994,Ohta1992}.
-    Here we provide evidence that in mammalian conserved orthologs, a large proportion of substitutions are due to the fixation of both deleterious mutations and beneficial back-mutations.
-    However, a central question regarding how to detect adaptation above this background of nearly-neutral substitutions remains~\cite{kimura_evolutionary_1968,ohta_development_1996}.
+    A long-standing debate in molecular evolution is whether the variations we observe between species in protein-coding genes are primarily due to nearly-neutral mutations reaching fixation by drift or primarily due to adaptation~\cite{kimura_evolutionary_1968,kern_neutral_2018,jensen_importance_2019,gillespie_substitution_1994,Ohta1992}.
+    Here we provide evidence that in mammalian orthologs, many substitutions occur through fixation of both deleterious mutations and beneficial back-mutations.
+    However, detecting adaptation above this background of nearly-neutral substitutions remains a central question~\cite{kimura_evolutionary_1968,ohta_development_1996}.
 
     One first strategy is precisely to use a nearly-neutral substitution model as a null model of evolution.
-    Under a strictly neutral evolution of protein-coding sequence, the ratio of non-synonymous over synonymous substitutions ($\dnds$) is expected to be equal to one.
+    Under a strictly neutral evolution of protein-coding sequence, we expect the ratio of non-synonymous over synonymous substitutions ($\dnds$) to be equal to one.
     Deviations from this neutral expectation, such as $\dnds > 1$, which can be generated by an excess of non-synonymous substitutions, is generally interpreted as a sign of adaptation.
-    However, as we have shown in this study, a $\dnds > 1$ is not necessarily a signature of adaption, but can be due to beneficial back-mutations.
+    However, as shown in this study, a $\dnds > 1$ is not necessarily a signature of adaptation but can be due to beneficial back-mutations.
     So, by relaxing the strict neutrality and assuming a stable fitness landscape instead, one can predict the expected rate of evolution, called $\omega_0$~\cite{spielman_relationship_2015, dosreis_how_2015}.
-    In this manner, adaptation can be alternatively considered as evolution under a changing fitness landscape and tested as such by searching for the signature of $\dnds > \omega_0$~\cite{cvijovic_fate_2015, rodrigue_detecting_2017, rodrigue_bayesian_2021}.
-    By using a stable fitness landscape as a null model of evolution, thus accounting for selective constraints exerted on the different amino-acids, the statistical power in testing for adaptation is increased~\cite{latrille_genes_2023}.
-    Another strategy to detect adaptation, instead of relying solely on summary statistics (such as $\dnds$ or $\omega_0$), is to include changes in the fitness landscapes inherently within the mutation-selection framework~\cite{tamuri_mutationselection_2021}.
-    Such mechanistic models could be more general than site-specific fitness landscapes, including both epistasis and changing fitness landscapes~\cite{goldstein_sequence_2017, stolyarova_senescence_2020}.
+    Adaptation can thus be considered as evolution under a changing fitness landscape and tested as such by searching for the signature of $\dnds > \omega_0$~\cite{cvijovic_fate_2015, rodrigue_detecting_2017, rodrigue_bayesian_2021}.
+    Using a stable fitness landscape as a null model of evolution, thus accounting for selective constraints exerted on the different amino acids, increased the statistical power in testing for adaptation~\cite{latrille_genes_2023}.
+    Instead of relying solely on summary statistics (such as $\dnds$ or $\omega_0$), another strategy to detect adaptation is to include changes in the fitness landscapes inherently within the mutation-selection framework~\cite{tamuri_mutationselection_2021}.
+    Such mechanistic models could be more general than site-specific fitness landscapes, including epistasis and changing fitness landscapes~\cite{goldstein_sequence_2017, stolyarova_senescence_2020}.
 
@@
     We argue that such a model represents a null expectation for the evolution of protein-coding genes in the absence of adaptation.
-    In that sense, adaptation should retain its original meaning associated with a change in the underlying fitness landscape and be modelled as such.
+    In that sense, to avoid conflating beneficial mutations with adaptive evolution, the term ``adaptation`` should retain its original meaning associated with a change in the underlying fitness landscape and be modelled as such.
 
@@
     This study makes use of data generated by the NextGen Consortium.
-    The European Union’s Seventh Framework Programme (FP7/2010-2014) provided funding for the project under grant agreement no 244356 - “NextGen”.
     \textbf{Funding:}
     Université de Lausanne; Agence Nationale de la Recherche, Grant ANR-19-CE12-0019 / HotRec.
+    The European Union’s Seventh Framework Programme (FP7/2010-2014) provided funding for the project under grant agreement no 244356 - “NextGen”.
     \textbf{Author contributions:}
@@
 
-    \subsection{Phylogenetic dataset}
+    \subsection{Phylogenetic dataset}\label{subsec:phylo-dataset}
 
@@
     OrthoMaM contains a total of $116$ mammalian reference sequences in v10c~\cite{ranwez_orthomam_2007, douzery_orthomam_2014, scornavacca_orthomam_2019}.
-    Genes located on the X and Y chromosomes and the mitochondrial genome were discarded from the analysis because the level of polymorphism – which is necessary for population-based analyses – is expected to be different in these three regions compared to the autosomal genome.
-    Sequences of species for which we used population-level polymorphism (see below) and their sister species, were removed from the analysis to ensure independence between the data used in the phylogenetic and population scales.
+    Genes located on the X and Y chromosomes and on the mitochondrial genome were discarded from the analysis because the level of polymorphism –~which is necessary for population-based analyses~– is expected to be different in these three regions compared to the autosomal genome.
+    Sequences of species for which we used population-level polymorphism (see section \ref{subsec:polymorphism-dataset}) and their sister species, were removed from the analysis to ensure independence between the data used in the phylogenetic and population scales.
     Altogether, our genome-wide dataset contains $14,509$ protein-coding DNA sequences in $87$ placental mammals.
@@
             q_{a \mapsto b}^{(i)} & = 0 \text{ if codons $a$ and $b$ are more than one mutation away,} \\
-            q_{a \mapsto b}^{(i)} & = \mu_{a \mapsto b} \text{ if codons $a$ and $b$ are synonymous,} \\
+            q_{a \mapsto b}^{(i)} & = \mu_{a \mapsto b} \text{ if codons $a$ and $b$ are synonymous, and}\\
             q_{a \mapsto b}^{(i)} & = \mu_{a \mapsto b} \dfrac{F_b^{(i)} - F_a^{(i)}}{1 - \e^{F_a^{(i)} - F_b^{(i)}}} \text{ if codons $a$ and $b$ are non-synonymous}.
@@
     \end{equation}
-    %In the manuscript and the following material, the source ($a$) and target ($b$) codons as well as the site ($i$) are implicit and thus never explicitly written.
+    In our subsequent derivation the source ($a$) and target ($b$) codons as well as the site ($i$) are implicit and thus never explicitly written.
     We used the Bayesian software \textit{BayesCode} (\url{https://github.com/ThibaultLatrille/bayescode}) to estimate the selection coefficients for each protein-coding gene in the mammalian dataset.
@@
 
-    The genetic variants representing the population level polymorphisms were obtained from the following species and their available datasets: \textit{Equus caballus} (EquCab2 assembly in the EVA study PRJEB9799~\cite{alabri_whole_2020}), \textit{Bos taurus} (UMD3.1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}), \textit{Ovis aries} (Oar\_v3.1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}), \textit{Capra hircus} (CHIR1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}, converted to ARS1 assembly with dbSNP identifiers~\cite{sherry_dbsnp_2001}), \textit{Chlorocebus sabaeus} (ChlSab1.1 assembly in the EVA project PRJEB22989~\cite{svardal_ancient_2017}), \textit{Homo sapiens} (GRCh38 assembly in the 1000-genome project~\cite{zheng-bradley_alignment_2017}).
+    The genetic variants representing the population level polymorphisms were obtained from the following species and their available datasets: \textit{Equus caballus} (EquCab2 assembly in the EVA study PRJEB9799~\cite{alabri_whole_2020}), \textit{Bos taurus} (UMD3.1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}), \textit{Ovis aries} (Oar\_v3.1 assembly in the NextGen project), \textit{Capra hircus} (CHIR1 assembly in the NextGen project), converted to ARS1 assembly with dbSNP identifiers~\cite{sherry_dbsnp_2001}), \textit{Chlorocebus sabaeus} (ChlSab1.1 assembly in the EVA project PRJEB22989~\cite{svardal_ancient_2017}), \textit{Homo sapiens} (GRCh38 assembly in the 1000 Genomes Project~\cite{zheng-bradley_alignment_2017}).
     In total, we analyzed 28 populations across the 6 different species with polymorphism data.
@@
     We then verified that the SNP downloaded from Ensembl matched the reference in the CDS in FASTA format.
-    Next, the position in the CDS was converted to the corresponding position in the multi-species sequence alignment (containing gaps) from the OrthoMaM database (see section \ref{subsec:s-phylogeny-method}) for the corresponding gene by doing a global pairwise alignment (Biopython function pairwise2).
+    Next, the position in the CDS was converted to the corresponding position in the multi-species sequence alignment (containing gaps) from the OrthoMaM database (see section~\ref{subsec:s-phylogeny-method}) for the corresponding gene by doing a global pairwise alignment (Biopython function pairwise2).
     This conversion from genomic position to alignment position was only possible when the assembly used for SNP-calling was the same as the one used in the OrthoMaM alignment, the GTF annotations, and the FASTA sequences.
@@
     The mutational opportunities of any new mutation refer to its likelihood of falling into a specific category (synonymous, deleterious, nearly-neutral, or beneficial).
-    Deriving such opportunities is necessary to estimate the strength of selection exerted at the population scale since different categories might have different mutational opportunities, and thus polymorphism and divergence need to be corrected accordingly (see sections \ref{subsec:substitution-mapping-in-the-terminal-branch}, \ref{subsec:s-polymorphism-method}, and \ref{subsec:precisison_recall}).
+    Deriving such opportunities is necessary to estimate the strength of selection exerted at the population scale since different categories might have different mutational opportunities, and thus polymorphism and divergence need to be corrected accordingly (see sections~\ref{subsec:substitution-mapping-in-the-terminal-branch},~\ref{subsec:s-polymorphism-method}, and~\ref{subsec:precisison_recall}).
     To calculate mutational opportunities, we reconstructed the ancestral genome of each of the 28 populations, which differs from the corresponding species' reference genome since it accounts for the variability present in the specific population.
@@
 
-    From the reconstructed ancestral genome at the base of the population genealogy, all possible mutations were computed, weighted by the instantaneous rate of change between nucleotides obtained from the mutation rate matrix ($\UniDimArray{\mu}$, see \ref{subsec:s-phylogeny-method}), summing to $\mu_{\text{tot}}$ across the whole genome, and to $\mu_{\text{syn}}$ when restricted to synonymous mutations.
+    From the reconstructed ancestral genome at the base of the population genealogy, all possible mutations were computed, weighted by the instantaneous rate of change between nucleotides obtained from the mutation rate matrix ($\UniDimArray{\mu}$, see section~\ref{subsec:s-phylogeny-method}), summing to $\mu_{\text{tot}}$ across the whole genome, and to $\mu_{\text{syn}}$ when restricted to synonymous mutations.
     Finally, the mutational opportunities for synonymous mutations were computed as the total number of sites across the genome ($L_{\text{tot}}$) weighted by the proportion of synonymous mutations among all possible mutations as:
@@
 
-    Similarly, for non-synonymous mutations, the total mutation rate for each class of selection $\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$, called $\mu\left( \Sphyclass \right)$, was estimated as the sum across all non-synonymous mutations if their selection coefficient at the phylogenetic scale is in the class ($\Sphy \in \Sphyclass$).
-    Accordingly, the mutational opportunities ($L \left( \Sphyclass \right)$) for each class of selection coefficient ($\Sphyclass$) was finally computed as the total number of sites across the genome ($L_{\text{tot}}$) weighted by the ratio of the aggregated mutations rates falling in the class ($\mu\left( \Sphyclass \right)$)
+    Similarly, for non-synonymous mutations, the total mutation rate for each class of selection $\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$, called $\mu\left( \Sphyclass \right)$, was estimated as the sum across all non-synonymous mutations if their selection coefficient at the phylogenetic scale is in the class $\Sphy \in \Sphyclass$.
+    Accordingly, the mutational opportunities ($L \left( \Sphyclass \right)$) for each class of selection coefficient ($\Sphyclass$) was finally computed as the total number of sites across the genome ($L_{\text{tot}}$) weighted by the ratio of the aggregated mutations rates falling in the class $\mu\left( \Sphyclass \right)$:
     \begin{equation}
-        L \left( \Sphyclass \right) = L_{\text{tot}} \frac{\mu\left( \Sphyclass \right)}{\mu_{\text{tot}}},
+        L \left( \Sphyclass \right) = L_{\text{tot}} \frac{\mu\left( \Sphyclass \right)}{\mu_{\text{tot}}}.
     \end{equation}
@@
     \begin{equation}
-        \proba[\Sphyclass] = \frac{L\left( \Sphyclass \right)}{\sum_{\SphyclassAlt\in \{\SphyDel, \SphyNeu, \SphyBen \} } L\left(\SphyclassAlt \right)},
+        \proba[\Sphyclass] = \frac{L\left( \Sphyclass \right)}{\sum_{\SphyclassAlt\in \{\SphyDel, \SphyNeu, \SphyBen \} } L\left(\SphyclassAlt \right)}.
         \label{eq:proba-dfe-mutsel}
@@
     \label{subsec:substitution-mapping-in-the-terminal-branch}
-    For each gene and each population with polymorphism data available, the genome at the base of the population genealogy was reconstructed (see section \ref{subsec:nunber-of-sites}).
+    For each gene and each population with polymorphism data available, the genome at the base of the population genealogy was reconstructed (see section~\ref{subsec:nunber-of-sites}).
     We used the ancestral genome reconstructed at the base of the population genealogy and the three closest outgroups found in the OrthoMaM alignment to infer the ancestral protein-coding DNA sequences for each node of the 4-taxa tree by applying the M5 codon model (gamma site rate variation) as implemented in FastML.v3.11~\cite{ashkenazy_fastml_2012}.
-    All polarized codon substitutions were then obtained by comparing the ancestral protein-coding DNA sequences before the split to the sister species (closest outgroup) to the genome at the base of the population genealogy.
-    We considered \textit{Ceratotherium simum simum} as \textit{Equus caballus} sister species; \textit{Bison bison bison} as \textit{Bos taurus} sister species; \textit{Pantholops hodgsonii} as \textit{Ovis aries} sister species; \textit{Pantholops hodgsonii} as \textit{Capra hircus} sister species; \textit{Macaca mulatta} as \textit{Chlorocebus sabaeus} sister species and finally, we considered \textit{Pan troglodytes} as \textit{Homo sapiens} sister species.
-    The selection coefficient ($\Sphy$) of each substitution was then obtained by comparing the difference in amino acid fitnesses for each polarized non-synonymous codon substitution, by referring to the site-specific fitness profile obtained in the phylogeny-based method (see~\ref{subsec:s-phylogeny-method}).
-    Finally, the rate of non-synonymous over synonymous substitution for a given class of selection coefficient ($\Sphyclass$) was computed as:
+    All polarized codon substitutions were then obtained by comparing the ancestral protein-coding DNA sequences before the split from the sister species (closest outgroup) to the genome at the base of the population genealogy.
+    We considered \textit{Ceratotherium simum simum} as \textit{Equus caballus'} sister species; \textit{Bison bison bison} as \textit{Bos taurus'} sister species; \textit{Pantholops hodgsonii} as \textit{Ovis aries'} sister species; \textit{Pantholops hodgsonii} as \textit{Capra hircus'} sister species; \textit{Macaca mulatta} as \textit{Chlorocebus sabaeus'} sister species and finally, we considered \textit{Pan troglodytes} as \textit{Homo sapiens'} sister species.
+    The selection coefficient ($\Sphy$) of each substitution was then obtained by comparing the difference in amino acid fitnesses for each polarized non-synonymous codon substitution, by referring to the site-specific fitness profile obtained in the phylogeny-based method (see section~\ref{subsec:s-phylogeny-method}).
+    Finally, the rate of non-synonymous over synonymous substitutions for a given class of selection coefficient ($\Sphyclass$) was computed as:
     \begin{align}
@@
     \end{align}
-    where $D \left( \Sphyclass \right) $ was the number of non-synonymous substitutions in class $\Sphyclass$, $D_{\text{syn}}$ was the number of synonymous substitutions across the genome, while $L \left( \Sphyclass \right)$ and $L_{\text{syn}}$ were the numbers of non-synonymous and synonymous mutational opportunities as defined in section \ref{subsec:nunber-of-sites}.
-    $R(\dnds)$ was computed as the ratio between the difference in the numbers of beneficial substitutions ($\dnds$), which were due to beneficial back-mutations, and the estimated divergence when we removed beneficial back-mutations $\dn (\Sphy < 0) / \ds$, over $\dnds$.
-    Note that the quantities $R(\dn)$ and $R(\dnds)$ are equivalent due to the simplification of the factor $\ds$:
+    where $D \left( \Sphyclass \right) $ was the number of non-synonymous substitutions in class $\Sphyclass$, $D_{\text{syn}}$ was the number of synonymous substitutions across the genome, while $L \left( \Sphyclass \right)$ and $L_{\text{syn}}$ were the numbers of non-synonymous and synonymous mutational opportunities, respectively, as defined in section~\ref{subsec:nunber-of-sites}.
+    $\delta(\dnds)$ was computed as the difference between $\dnds$ computed over all substitutions and $\dnds$ when we removed beneficial back-mutations $\dn (\Sphy < 1) / \ds$, normalized by $\dnds$.
+    Note that the quantities $\delta(\dnds)$ and $\delta(\dn)$ are equivalent due to the simplification of the factor $\ds$:
     \begin{equation}
-        R(\dnds) = \dfrac{\dnds - \dn(\Sphy < 0) / \ds}{\dnds} = \dfrac{\dn - \dn(\Sphy < 0)}{\dn} = R(\dn).
+        \delta(\dnds) = \dfrac{\dnds - \dn(\Sphy < 1) / \ds}{\dnds} = \dfrac{\dn - \dn(\Sphy < 1)}{\dn} = \delta(\dn).
     \end{equation}
 
-    \subsection{Selection coefficient ($\Spop$) in population-based method}
+    \subsection{Scaled selection coefficients ($\Spop$) in a population-based method}
     \label{subsec:s-polymorphism-method}
-    To obtain a quantitative estimate of the distribution of selection coefficients for each category of SNPs, we used the model polyDFE~\cite{tataru_inference_2017, tataru_polydfe_2020}.
+    To obtain a quantitative estimate of the distribution of selection coefficients for each category of SNPs, we used the polyDFE model~\cite{tataru_inference_2017, tataru_polydfe_2020}.
     This model uses the count of derived alleles to infer the distribution of fitness effects (DFE).
@@
     and $f_{\Gamma}(x; m, b)$ is the density of the $\Gamma$ distribution with mean $m$ and shape $b$, while $f_{e}(x; m)$ is the density of the exponential distribution with mean $m$.
-    Once the DFE is fitted to the data, the proportion of beneficial ($\ProbaPopBen$), nearly-neutral ($\ProbaPopNeu$) and deleterious mutations ($\ProbaPopDel$) are given as:
+    Once the DFE is fitted to the data, the proportion of deleterious ($\ProbaPopDel$), nearly-neutral ($\ProbaPopNeu$) and beneficial mutations ($\ProbaPopBen$) are given as:
     \begin{align}
@@
 
-    PolyDFE requires one SFS for non-synonymous mutations and one for synonymous mutations (neutral expectation), as well as the number of sites on which each SFS was sampled, namely the mutational opportunities ($L(\Sphyclass)$ and $L_{\text{syn}}$.
-    For populations containing more than $8$ individuals, the site-frequency spectrum (SFS) was subsampled down to $16$ chromosomes ($8$ diploid individuals) without replacement (hyper-geometric distribution) to alleviate the effect of different sampling depths in the 28 populations.
-    Altogether, for each class of selection ($\Sphyclass$) of non-synonymous SNPs (or for all SNPs), we thus estimated the parameters of the DFE $\left( \Spop; \DelMean , b, p_b, \AdvMean \right)$ using maximum likelihood with polyDFE from the number of sites and the SFS obtained by aggregating all the SNPs in the selection class.
-    Once fitted to the data, the parameters of the DFE $\left( \Spop; \DelMean , b, p_b, \AdvMean \right)$ were used to compute $\ProbaPopBen$, $\ProbaPopNeu$, $\ProbaPopDel$ using eq.~\ref{eq:polyProbaAdv}-\ref{eq:polyProbaDel}.
+    PolyDFE requires one SFS for non-synonymous mutations and one for synonymous mutations (neutral expectation), as well as the number of sites on which each SFS was sampled, namely the mutational opportunities $L(\Sphyclass)$ and $L_{\text{syn}}$.
+    For populations containing more than $8$ individuals, the SFS was subsampled down to $16$ chromosomes ($8$ diploid individuals) without replacement (hyper-geometric distribution) to alleviate the effect of different sampling depths in the 28 populations.
+    Altogether, for each class of selection ($\Sphyclass$) of non-synonymous SNPs (or for all SNPs), we estimated the parameters of the DFE $\left( \Spop; \DelMean , b, p_b, \AdvMean \right)$ using maximum likelihood with polyDFE from the number of sites and the SFS obtained by aggregating all the SNPs in the selection class.
+    Once fitted to the data, the parameters of the DFE $\left( \Spop; \DelMean , b, p_b, \AdvMean \right)$ were used to compute $\ProbaPopDel$, $\ProbaPopNeu$, and $\ProbaPopBen$, using eqs.~\ref{eq:polyProbaDel}-\ref{eq:polyProbaAdv}.
 
@@
     \label{subsec:precisison_recall}
-    For readability, we give here \textit{precision} and \textit{recall} for beneficial mutations ($\SphyBen \coloneqq \Sphy > 1$ and $\SpopBen \coloneqq \Spop > 1$), but it can be obtained using the same derivation for the deleterious mutations ($\Sphy \text{ or } \Spop < -1$) and nearly-neutral mutations ($-1 < \Sphy \text{ or } \Spop < 1$).
+    For readability, we give here \textit{precision} and \textit{recall} for beneficial mutations ($\SphyBen$ and $\SpopBen$), but it can be obtained using the same derivation for the deleterious mutations ($\SphyDel$ and $\SpopDel$) and nearly-neutral mutations ($\SphyNeu$ and $\SpopNeu$).
 
-    \textit{Precision} is the ratio $TP / (TP + FP)$, where TP are \textit{true positives} ($\proba [ \SpopBen \cap  \SphyBen]$) and FP are \textit{false positives} ($\proba [ \text{not } \SpopBen \cap \SphyBen]$).
-    The denominator $(TP + FP)$ can be simplified using the law of total probability as:
-    \begin{equation}
-        \proba [ \SpopBen \cap \SphyBen] + \proba [\text{not } \SpopBen \cap \SphyBen] = \proba [ \SphyBen],
-    \end{equation}
-    which corresponds to the total probability of a mutation to be a predicted positive ($\proba [ \SphyBen]$).
-    Altogether, \textit{precision} for beneficial mutations can be written as conditional probability:
+    \textit{Precision} is the proportion of mutations correctly predicted as beneficial ($\proba [ \SpopBen \cap  \SphyBen]$) out of all predicted as beneficial back-mutations ($\proba [ \SphyBen]$), which can be written as a conditional probability:
     \begin{equation}
         \frac{\proba [ \SpopBen  \cap  \SphyBen]}{\proba [ \SphyBen]} = \proba [ \SpopBen  \given  \SphyBen].
+        \label{eq:precision}
     \end{equation}
     Namely, \textit{precision} corresponds to the probability for a back-mutation ($\SphyBen$) to be effectively beneficial at the population level ($\SpopBen$).
-    This probability is obtained by restricting our analysis to SNPs that are predicted to be beneficial back-mutations (black fill for the category $\SphyBen$ in fig~\ref{fig:homo-afr-results}D).
+    This probability is obtained by restricting our analysis to SNPs that are predicted to be beneficial back-mutations (black fill for the category $\SphyBen$ in fig.~\ref{fig:homo-afr-results}D).
 
-    The \textit{Recall} is the ratio $TP / (TP + FN)$, where TP are \textit{true positives} ($\proba [ \SpopBen  \cap  \SphyBen]$) and FN are \textit{false negatives} ($\proba [ \SpopBen  \cap \text{not } \SphyBen]$).
-    The denominator $(TP + FN)$ can be simplified using the law of total probability as:
-    \begin{equation}
-        \proba [ \SpopBen  \cap  \SphyBen] + \proba [ \SpopBen \cap \text{not } \SphyBen] = \proba [ \SpopBen],
-    \end{equation}
-    which corresponds to the total probability of a mutation being positive ($\proba [ \SpopBen]$).
-    Altogether, \textit{recall} for beneficial mutations can be written as conditional probability:
+    \textit{Recall} is the proportion of mutations correctly predicted as beneficial ($\proba [ \SpopBen \cap  \SphyBen]$) out of all beneficial mutations ($\proba [ \SpopBen]$), which can be written as a conditional probability:
     \begin{equation}
@@
     \end{equation}
-    First, $\proba [\SpopBen \given \SphyBen]$ is computed as above (\textit{precision}).
-    Second, $\proba [ \SphyBen ]$ is obtained from equation \ref{eq:proba-dfe-mutsel}.
-    Finally, $\proba [ \SpopBen ]$ is the probability of mutation to be beneficial at the level of the population, which can be computed from the law of total probabilities as:
+    where $\proba [\SpopBen \given \SphyBen]$ and $\proba [ \SphyBen ]$ can be calculated using equations~\ref{eq:precision} and \ref{eq:proba-dfe-mutsel}, respectively, and $\proba [ \SpopBen ]$ is the probability of a mutation to be beneficial at the level of the population, which can be computed from the law of total probabilities as:
     \begin{equation}

### 2023-05-02 manuscript/main.tex
Prepare submission tex files. Updated figures.

@@
 \usepackage{makecell}
+\usepackage{orcidlink}
 
@@
 \newcommand{\DelMean}{\beta_d}
+\newcommand{\thetaSyn}{\theta_{\text{S}}}
 \renewcommand{\baselinestretch}{1.5}
@@
 \title{Mammalian protein-coding genes exhibit widespread beneficial mutations that are not adaptive}
+\rhead{\scshape Beneficial yet non-adaptive mutations}
 
@@
     \large
-    \textbf{T. {Latrille}$^{1}$, J. {Joseph}$^{2}$, D.~A. {Hartasánchez}$^{1}$, N. {Salamin}$^{1}$}\\
+    \textbf{T.
+{Latrille}$^{1\dag}$\orcidlink{0000-0002-9643-4668}, J.
+{Joseph}$^{2\dag}$, D.~A.
+{Hartasánchez}$^{1}$\orcidlink{0000-0003-2596-6883}, N.
+{Salamin}$^{1}$\orcidlink{0000-0002-3963-4954}}\\
     \normalsize
     $^{1}$Department of Computational Biology, Université de Lausanne, Lausanne, Switzerland\\
-    $^{2}$Université de Lyon, Université Lyon 1, CNRS, VetAgro Sup, Laboratoire de Biométrie et Biologie Evolutive, UMR5558, Villeurbanne, France \\
+    $^{2}$Laboratoire de Biométrie et Biologie Evolutive, UMR5558, Université Lyon 1, Villeurbanne, France \\
+    $^{\dag}$These authors contributed equally to this work\\
     \texttt{\href{mailto:thibault.latrille@ens-lyon.org}{thibault.latrille@ens-lyon.org}} \\
@@
             Depending on $\Sphy$ (B) mutations can be predicted as deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) or beneficial back-mutations ($\SphyBen$) toward a fitter amino acid and repairing existing functions.
-            At the population scale (C), each observed single nucleotide polymorphism (SNP) segregating in the population can also be classified according to its $\Sphy$ value.
-            Similarly, substitutions along the terminal branch are classified depending on their $\Sphy$ value.
-            Together, substitutions and polymorphisms are contrasted to synonymous changes used as a neutral expectation such as estimate selection coefficients at the population scale ($\Spop$).
-            For each class of selection ($\SphyDel$, $\SphyNeu$, $\SphyBen$), we can thus assess whether $\Sphy$ predicts $\Spop$ and compute \textit{precision} (F) and \textit{recall} (G) for each class.
+            Substitutions along the terminal branch are classified depending on their $\Sphy$ value (C).
+            At the population scale, each observed single nucleotide polymorphism (SNP) segregating in the population can also be classified according to its $\Sphy$ value.
+            Occurence and frequency in the population of non-synonymous and synonymous (deemed neutral) polymorphisms (D-E) is used to estimate selection coefficients at the population scale ($\Spop$), for each class of selection ($\SphyDel$, $\SphyNeu$, $\SphyBen$).
+            We can thus assess whether $\Sphy$ predicts $\Spop$ and compute \textit{precision} (F) and \textit{recall} (G) for each class.
             The \textit{recall} value for class $\SphyBen$ is the probability of back-mutations among all beneficial ones (G).
@@
     Among all the substitutions found in each terminal branch, between 10 and 13\% were $\SphyBen$ (table~S1 and fig.~\ref{fig:homo-afr-results}B for humans).
-    In principle, beneficial back-mutations are bound to reach fixation more often than neutral substitutions.
+    In principle, beneficial back-mutations are bound to reach fixation more often than neutral mutations.
     Hence, we calculated the $\dnds$ ratio of non-synonymous over synonymous divergence for all terminal lineages, focusing on the non-synonymous changes predicted as beneficial back-mutations ($\dn(\SphyBen) / \ds$).
-    We obtained values between 1.15 and 1.68 in the different lineages (table~S1), implying that $\SphyBen$ mutations reached fixation more frequently than synonymous mutations that are supposed to be neutral, implying that these back-mutations are effectively beneficial.
+    We obtained values between 1.10 and 1.61 in the different lineages (table~S1), implying that $\SphyBen$ mutations reached fixation more frequently than synonymous mutations that are supposed to be neutral, implying that these back-mutations are effectively beneficial.
 
@@
     By discarding all beneficial back-mutations we can obtain an estimate of $\dnds$ which is not inflated.
-    By comparing these two ways of calculating $\dnds$ (see section~S\ref{subsec:substitution-mapping-in-the-terminal-branch} in Materials \& Methods), we calculated that beneficial back-mutations inflate $\dnds$ values by between 22\% and 27\% across genera while only representing between 1\% and 2\% of mutational opportunities (table~S2 andfig.~\ref{fig:homo-afr-results}A for humans).
+    By comparing these two ways of calculating $\dnds$ (see section~\ref{subsec:substitution-mapping-in-the-terminal-branch} in Materials \& Methods), we calculated that beneficial back-mutations inflate $\dnds$ values by between 9 and 11\% across genera while only representing between 1.2 and 1.4\% of non-synonymous mutations (table~S2-3 and fig.~\ref{fig:homo-afr-results}A for humans).
 
@@
     Therefore, we investigated whether the non-synonymous SNPs classified as $\SphyDel$ or $\SphyBen$ showed enrichment in specific clinical terms compared to SNPs classified as $\SphyNeu$.
-    Our results show that SNPs predicted as deleterious are associated with clinical terms such as \textit{Likely Pathogenic} and \textit{Pathogenic}, implying that, in general, the selective pressure of a mutation exerted across mammals is also predictive of its clinical effect in humans (table~S6).
-    Conversely, back-mutations are associated with clinical terms such as \textit{Benign} and \textit{Likely Benign}, which shows that back-mutations are less likely to be functionally damaging.
+    Our results show that SNPs predicted as deleterious are associated with clinical terms such as \textit{Likely Pathogenic} and \textit{Pathogenic}, implying that, in general, the selective pressure of a mutation exerted across mammals is also predictive of its clinical effect in humans (table~S4).
+    Conversely, back-mutations are associated with clinical terms such as \textit{Benign} and \textit{Likely Benign}, which shows that back-mutations are less likely to be functionally damaging (table~S5).
 
@@
     Across our selection classes ($\SphyDel$, $\SphyNeu$ and $\SphyBen$), one can ultimately estimate the proportion of correct and incorrect predictions, leading to an estimation of \textit{precision} and \textit{recall} (fig.~\ref{fig:method}F-G and section~\ref{subsec:precisison_recall} in Materials \& Methods).
-    Across 28 populations of different mammal species, mutations predicted to be deleterious at the phylogenetic scale ($\ProbaPopDel$) were indeed purged at the population scale, with a \textit{precision} in the range of 89--97\% (table~\ref{table:proba} and fig.~\ref{fig:homo-afr-results}D for humans).
-    Conversely, a \textit{recall} in the range of 95--98\% implies that mutations found to be deleterious at the population scale were most likely also predicted to be deleterious at the phylogenetic scale (table~\ref{table:proba}).
+    Across 28 populations of different mammal species, mutations predicted to be deleterious at the phylogenetic scale ($\ProbaPopDel$) were indeed purged at the population scale, with a \textit{precision} in the range of 89--96\% (table~\ref{table:proba} and fig.~\ref{fig:homo-afr-results}D for humans).
+    Conversely, a \textit{recall} in the range of 95--100\% implies that mutations found to be deleterious at the population scale were most likely also predicted to be deleterious at the phylogenetic scale (table~\ref{table:proba}).
     Altogether, purifying selection is largely predictable and amino acids with negative fitness across mammals have been effectively purged away in each population.
 
-    Mutations predicted as $\SphyNeu$ were effectively composed of a mix of neutral and selected mutations with varying \textit{precision} (18--74\%) and \textit{recall} (21--52\%) across the different populations (table~\ref{table:proba}, fig.~\ref{fig:homo-afr-results}D for Humans).
+    Mutations predicted as $\SphyNeu$ were effectively composed of a mix of neutral and selected mutations with varying \textit{precision} (36--73\%) and \textit{recall} (30--45\%) across the different populations (table~\ref{table:proba}, fig.~\ref{fig:homo-afr-results}D for Humans).
     The variable proportions between populations can be explained by the effective number of individuals in the population ($\Ne$), a major driver of selection efficacy.
-    Since $\Ne$ is not directly measurable, we used Watterson's $\theta_S$ as a proxy to order populations by their levels of synonymous diversity.
+    Since $\Ne$ is not directly measurable, we used Watterson's $\thetaSyn$ as a proxy to order populations by their levels of synonymous diversity.
     Higher synonymous diversity was associated with a smaller proportion of nearly-neutral mutations (fig.~\ref{fig:diversity}A).
@@
 
-    %Of note, mutations with $\Sphy>1$ only represented ca.~1.5\% of all possible new mutations, but ca.~8.5\% of all observed mutations in the population (blue in fig.~\ref{fig:homo-afr-results}A-B, table~S3).
-    Finally, mutations predicted to be beneficial back-mutations based on the selection coefficients at the phylogenetic scale ($\SphyBen$) were indeed beneficial for individuals bearing them, with a \textit{precision} (fig.~\ref{fig:method}F) in the range of 15--52\% (table~\ref{table:proba} and fig.~\ref{fig:homo-afr-results}D for humans).
+    Finally, mutations predicted to be beneficial back-mutations based on the selection coefficients at the phylogenetic scale ($\SphyBen$) were indeed beneficial for individuals bearing them, with a \textit{precision} (fig.~\ref{fig:method}F) in the range of 15--86\% (table~\ref{table:proba} and fig.~\ref{fig:homo-afr-results}D for humans).
     This result confirms that selection towards amino acids restoring existing functions is ongoing in these populations.
@@
     In other words, the \textit{recall} value quantifies the number of beneficial mutations restoring damaged genomes instead of creating adaptive innovations.
-    Across the 28 populations, this proportion is in the range of 11--70\% (table~\ref{table:proba}).
+    Across the 28 populations, this proportion is in the range of 13--80\% (table~\ref{table:proba}).
 
@@
                 \textbf{Species} &
-                $\bm{\theta_{\text{S}}}$ &
+                $\bm{\thetaSyn}$ &
                 \makecell{\textbf{Precision} \\ $\bm{\proba [\SpopDel \given \SphyDel]}$} &
@@
                 \\   \midrule
-                \rowcolor{LIGHTGREY} Equus c.   & Equus caballus        & $ 0.002$ & $ 0.918$ & $ 0.957$ & $ 0.186$ & $ 0.213$ & $ 0.519$ & $ 0.122$ \\
-                Iran                 & Bos taurus        & $ 0.002$ & $ 0.924$ & $ 0.965$ & $ 0.565$ & $ 0.356$ & $ 0.368$ & $ 0.702$ \\
-                Uganda                & Bos taurus        & $ 0.005$ & $ 0.943$ & $ 0.961$ & $ 0.516$ & $ 0.396$ & $ 0.255$ & $ 0.425$ \\
-                \rowcolor{LIGHTGREY} Australia              & Capra hircus        & $ 0.003$ & $ 0.941$ & $ 0.964$ & $ 0.592$ & $ 0.434$ & $ 0.147$ & $ 0.308$ \\
-                \rowcolor{LIGHTGREY} France                 & Capra hircus          & $ 0.004$ & $ 0.940$ & $ 0.963$ & $ 0.571$ & $ 0.418$ & $ 0.149$ & $ 0.304$ \\
-                \rowcolor{LIGHTGREY} Iran (C. aegagrus) & Capra hircus          & $ 0.004$ & $ 0.948$ & $ 0.960$ & $ 0.515$ & $ 0.446$ & $ 0.147$ & $ 0.157$ \\
-                \rowcolor{LIGHTGREY} Iran     & Capra hircus          & $ 0.004$ & $ 0.942$ & $ 0.961$ & $ 0.534$ & $ 0.410$ & $ 0.152$ & $ 0.258$ \\
-                \rowcolor{LIGHTGREY} Italy              & Capra hircus          & $ 0.004$ & $ 0.940$ & $ 0.963$ & $ 0.579$ & $ 0.421$ & $ 0.147$ & $ 0.316$ \\
-                Morocco              & Capra hircus          & $ 0.004$ & $ 0.939$ & $ 0.960$ & $ 0.549$ & $ 0.404$ & $ 0.186$ & $ 0.398$ \\
-                Iran             & Ovis aries & $ 0.007$ & $ 0.957$ & $ 0.954$ & $ 0.412$ & $ 0.416$ & $ 0.158$ & $ 0.191$ \\
-                Iran (O. orientalis)    & Ovis aries & $ 0.009$ & $ 0.961$ & $ 0.955$ & $ 0.413$ & $ 0.437$ & $ 0.157$ & $ 0.180$ \\
-                Iran (O. vignei)             & Ovis aries & $ 0.007$ & $ 0.968$ & $ 0.951$ & $ 0.356$ & $ 0.516$ & $ 0.186$ & $ 0.118$ \\
-                Various               & Ovis aries & $ 0.008$ & $ 0.958$ & $ 0.955$ & $ 0.428$ & $ 0.431$ & $ 0.156$ & $ 0.188$ \\
-                Morocco                & Ovis aries & $ 0.008$ & $ 0.960$ & $ 0.953$ & $ 0.447$ & $ 0.460$ & $ 0.190$ & $ 0.292$ \\
-                \rowcolor{LIGHTGREY} Barbados                & Chlorocebus sabaeus & $ 0.004$ & $ 0.931$ & $ 0.969$ & $ 0.628$ & $ 0.402$ & $ 0.282$ & $ 0.630$ \\
-                \rowcolor{LIGHTGREY} Central Afr. Rep.         & Chlorocebus sabaeus & $ 0.006$ & $ 0.941$ & $ 0.964$ & $ 0.514$ & $ 0.408$ & $ 0.310$ & $ 0.263$ \\
-                \rowcolor{LIGHTGREY} Ethiopia          & Chlorocebus sabaeus & $ 0.005$ & $ 0.933$ & $ 0.967$ & $ 0.586$ & $ 0.393$ & $ 0.298$ & $ 0.456$ \\
-                \rowcolor{LIGHTGREY} Gambia               & Chlorocebus sabaeus & $ 0.005$ & $ 0.937$ & $ 0.967$ & $ 0.590$ & $ 0.414$ & $ 0.305$ & $ 0.422$ \\
-                \rowcolor{LIGHTGREY} Kenya              & Chlorocebus sabaeus        & $ 0.005$ & $ 0.942$ & $ 0.965$ & $ 0.526$ & $ 0.418$ & $ 0.296$ & $ 0.253$ \\
-                \rowcolor{LIGHTGREY} Nevis     & Chlorocebus sabaeus        & $ 0.003$ & $ 0.930$ & $ 0.970$ & $ 0.637$ & $ 0.401$ & $ 0.285$ & $ 0.696$ \\
-                \rowcolor{LIGHTGREY} South Africa           & Chlorocebus sabaeus        & $ 0.006$ & $ 0.937$ & $ 0.964$ & $ 0.530$ & $ 0.393$ & $ 0.323$ & $ 0.338$ \\
-                \rowcolor{LIGHTGREY} Saint Kitts             & Chlorocebus sabaeus        & $ 0.004$ & $ 0.931$ & $ 0.969$ & $ 0.611$ & $ 0.393$ & $ 0.292$ & $ 0.604$ \\
-                \rowcolor{LIGHTGREY} Zambia          & Chlorocebus sabaeus        & $ 0.006$ & $ 0.941$ & $ 0.963$ & $ 0.506$ & $ 0.408$ & $ 0.309$ & $ 0.252$ \\
-                African          & Homo sapiens        & $ 0.002$ & $ 0.896$ & $ 0.968$ & $ 0.550$ & $ 0.297$ & $ 0.371$ & $ 0.284$ \\
-                Admixed American          & Homo sapiens        & $ 0.002$ & $ 0.890$ & $ 0.979$ & $ 0.710$ & $ 0.333$ & $ 0.368$ & $ 0.464$ \\
-                East Asian          & Homo sapiens        & $ 0.002$ & $ 0.890$ & $ 0.971$ & $ 0.578$ & $ 0.289$ & $ 0.369$ & $ 0.358$ \\
-                European          & Homo sapiens        & $ 0.002$ & $ 0.891$ & $ 0.980$ & $ 0.739$ & $ 0.345$ & $ 0.368$ & $ 0.499$ \\
-                South Asian          & Homo sapiens        & $ 0.002$ & $ 0.895$ & $ 0.981$ & $ 0.740$ & $ 0.356$ & $ 0.369$ & $ 0.423$ \\
+                \rowcolor{LIGHTGREY}              Equus c. & Equus caballus        & $ 0.002$ & $ 0.908$ & $ 0.976$ & $ 0.730$ & $ 0.383$ & $ 0.580$ & $ 0.809$ \\
+                Iran               & Bos taurus        & $ 0.002$ & $ 0.898$ & $ 1.000$ & $ 0.632$ & $ 0.340$ & $ 0.857$ & $ 0.277$ \\
+                Uganda              & Bos taurus        & $ 0.005$ & $ 0.942$ & $ 0.963$ & $ 0.497$ & $ 0.393$ & $ 0.488$ & $ 0.483$ \\
+                \rowcolor{LIGHTGREY} Australia            & Capra hircus        & $ 0.003$ & $ 0.934$ & $ 0.966$ & $ 0.524$ & $ 0.425$ & $ 0.368$ & $ 0.196$ \\
+                \rowcolor{LIGHTGREY} France                                    & Capra hircus          & $ 0.004$ & $ 0.936$ & $ 0.965$ & $ 0.506$ & $ 0.412$ & $ 0.368$ & $ 0.211$ \\
+                \rowcolor{LIGHTGREY} Iran (C. aegagrus)                    & Capra hircus          & $ 0.004$ & $ 0.940$ & $ 0.961$ & $ 0.478$ & $ 0.438$ & $ 0.221$ & $ 0.114$ \\
+                \rowcolor{LIGHTGREY} Iran                        & Capra hircus          & $ 0.004$ & $ 0.945$ & $ 0.960$ & $ 0.419$ & $ 0.400$ & $ 0.368$ & $ 0.211$ \\
+                \rowcolor{LIGHTGREY} Italy                                 & Capra hircus          & $ 0.004$ & $ 0.937$ & $ 0.963$ & $ 0.548$ & $ 0.426$ & $ 0.270$ & $ 0.220$ \\
+                \rowcolor{LIGHTGREY} Morocco                                 & Capra hircus          & $ 0.004$ & $ 0.942$ & $ 0.964$ & $ 0.522$ & $ 0.428$ & $ 0.368$ & $ 0.276$ \\
+                Iran           & Ovis aries & $ 0.007$ & $ 0.953$ & $ 0.954$ & $ 0.450$ & $ 0.406$ & $ 0.169$ & $ 0.392$ \\
+                Iran (O. orientalis)  & Ovis aries & $ 0.009$ & $ 0.958$ & $ 0.953$ & $ 0.417$ & $ 0.431$ & $ 0.153$ & $ 0.180$ \\
+                Iran (O. vignei)           & Ovis aries & $ 0.007$ & $ 0.960$ & $ 0.951$ & $ 0.360$ & $ 0.449$ & $ 0.195$ & $ 0.133$ \\
+                Various             & Ovis aries & $ 0.008$ & $ 0.955$ & $ 0.954$ & $ 0.435$ & $ 0.426$ & $ 0.190$ & $ 0.228$ \\
+                Morocco              & Ovis aries & $ 0.008$ & $ 0.956$ & $ 0.955$ & $ 0.449$ & $ 0.410$ & $ 0.136$ & $ 0.353$ \\
+                \rowcolor{LIGHTGREY} Barbados              & Chlorocebus sabaeus & $ 0.004$ & $ 0.925$ & $ 0.969$ & $ 0.536$ & $ 0.377$ & $ 0.565$ & $ 0.306$ \\
+                \rowcolor{LIGHTGREY} Central Afr. Rep.       & Chlorocebus sabaeus & $ 0.006$ & $ 0.940$ & $ 0.964$ & $ 0.495$ & $ 0.404$ & $ 0.429$ & $ 0.274$ \\
+                \rowcolor{LIGHTGREY} Ethiopia        & Chlorocebus sabaeus & $ 0.005$ & $ 0.925$ & $ 0.969$ & $ 0.560$ & $ 0.400$ & $ 0.462$ & $ 0.239$ \\
+                \rowcolor{LIGHTGREY} Gambia             & Chlorocebus sabaeus & $ 0.005$ & $ 0.934$ & $ 0.969$ & $ 0.610$ & $ 0.409$ & $ 0.486$ & $ 0.774$ \\
+                \rowcolor{LIGHTGREY} Kenya                                 & Chlorocebus sabaeus        & $ 0.005$ & $ 0.938$ & $ 0.965$ & $ 0.519$ & $ 0.434$ & $ 0.478$ & $ 0.243$ \\
+                \rowcolor{LIGHTGREY} Nevis                        & Chlorocebus sabaeus        & $ 0.003$ & $ 0.923$ & $ 0.970$ & $ 0.609$ & $ 0.393$ & $ 0.516$ & $ 0.393$ \\
+                \rowcolor{LIGHTGREY} South Africa                              & Chlorocebus sabaeus        & $ 0.006$ & $ 0.935$ & $ 0.965$ & $ 0.542$ & $ 0.409$ & $ 0.490$ & $ 0.360$ \\
+                \rowcolor{LIGHTGREY} Saint Kitts                                & Chlorocebus sabaeus        & $ 0.004$ & $ 0.926$ & $ 0.969$ & $ 0.562$ & $ 0.377$ & $ 0.515$ & $ 0.367$ \\
+                \rowcolor{LIGHTGREY} Zambia                             & Chlorocebus sabaeus        & $ 0.006$ & $ 0.937$ & $ 0.965$ & $ 0.494$ & $ 0.413$ & $ 0.499$ & $ 0.249$ \\
+                African                             & Homo sapiens        & $ 0.002$ & $ 0.899$ & $ 0.970$ & $ 0.571$ & $ 0.334$ & $ 0.678$ & $ 0.319$ \\
+                Admixed American                             & Homo sapiens        & $ 0.002$ & $ 0.888$ & $ 0.972$ & $ 0.581$ & $ 0.301$ & $ 0.635$ & $ 0.361$ \\
+                East Asian                             & Homo sapiens        & $ 0.002$ & $ 0.894$ & $ 0.973$ & $ 0.583$ & $ 0.335$ & $ 0.611$ & $ 0.233$ \\
+                European                             & Homo sapiens        & $ 0.002$ & $ 0.896$ & $ 0.972$ & $ 0.581$ & $ 0.350$ & $ 0.619$ & $ 0.217$ \\
+                South Asian                             & Homo sapiens        & $ 0.002$ & $ 0.898$ & $ 0.972$ & $ 0.580$ & $ 0.354$ & $ 0.628$ & $ 0.222$ \\
                 \bottomrule
@@
             \textit{Recall} for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is thus the proportion of beneficial back-mutations among all beneficial mutations.
-            Watterson's $\theta_{\text{S}}$ is the observed genetic diversity calculated for synonymous changes.
+            Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
         }
@@
     We have tested this hypothesis and found that these back-mutations ($\SphyBen \coloneqq \Sphy > 1 $) are indeed beneficial in extant populations.
-    We estimated that between 18 and 78\% of all beneficial mutations in mammalian populations have not been driven by adaptation but instead have reversed deleterious substitutions which have accumulated along the phylogeny.
+    We estimated that between 13 and 80\% of all beneficial mutations in mammalian populations have not been driven by adaptation but instead have reversed deleterious substitutions which have accumulated along the phylogeny.
     These results suggest that many beneficial mutations are non-adaptive but rather restore ancestral states of higher fitness.
@@
     Overall, we expect the proportion of beneficial back-mutations to be more dependent on $\Ne$’s long-term expansions and contractions than on the short-term ones~\cite{charlesworth_other_2007,huber_determining_2017}.
-    Indeed the proportion of back-mutations among all beneficial mutations did not show a clear relationship with the synonymous diversity within a population (Watterson's $\theta_S$) (fig.~\ref{fig:diversity}B), which should, in theory, reflect the population's short-term $\Ne$.
+    Indeed the proportion of back-mutations among all beneficial mutations did not show a clear relationship with the synonymous diversity within a population (Watterson's $\thetaSyn$) (fig.~\ref{fig:diversity}B), which should, in theory, reflect the population's short-term $\Ne$.
 
@@
     %Regarding the distribution of fitness effects (DFE) estimated at the population scale, there is no consensus on its expected shape~\cite{welch_divergence_2008, bataillon_effects_2014}, although it has been found to be reliably constant between closely related species~\cite{castellano_comparison_2019}.
-    %We modelled the DFE as a continuous distribution, with the negative side of the DFE as a gamma distribution, and the positive side as an exponential distribution with a mean greater than one.
-    %To check for robustness in our results despite the uncertainty of the underlying DFE, we also performed our analysis assuming a discretized DFE with five categories of selection coefficients, instead of three.
-    %Our results are consistent, with the proportion of back-mutations among all beneficial mutations ranging from 3 to 20\% across populations when modelling a DFE with five categories (table~S5).
+    %We modelled the DFE as a continuous distribution, but to check for robustness in our results despite the uncertainty of the underlying DFE, we also performed our analysis assuming a discretized DFE.
+    %Our results are consistent, with the proportion of back-mutations among all beneficial mutations ranging from XX to XX\% across populations when modelling a DFE as a discrete distributio.
     %Consequently, even though our general framework contrasting the phylogenetic and population scales is theoretically consistent, we acknowledge that estimating the proportion of back-mutations among all beneficial ones is dependent on the the underlying DFE at the population scale and the threshold used to define a beneficial mutation.
     %As a result, further work is required to investigate the shape of the DFE at the population scale.
-    %Notably, the reconstructed distribution of $\Sphy$ values obtained in our study has a negative mode (around $\Sphy=-5$), consistent with experimental DFEs obtained by mutation accumulation (fig.~S10).
+    %Notably, the reconstructed distribution of $\Sphy$ values obtained in our study has a negative mode (around $\Sphy=-5$), consistent with experimental DFEs obtained by mutation accumulation.
     %Contrarily, continuous DFEs estimated at the population scale have by definition a mode at 0.
     %We argue that methods estimating DFE at the population scale should assume a mode shifted toward negative values of $\Spop$.
-    % Second, at the population scale, the threshold to consider a mutation beneficial ($\Spop >1 $ or $\Sphy > 1$) discards slightly beneficial mutations.
-    % To also consider slightly-beneficial mutations, we performed the same analysis with a threshold of zero.
-    %With this methodology, the proportion of back-mutations among all beneficial mutations increases and ranges from 12 to 45\% across populations(table~S4).
 
@@
         \caption{
-            (A) Proportion of nearly-neutral mutations at the population scale ($\proba [ \SpopNeu]$ in the y-axis), shown as a function of the synonymous diversity (Watterson's $\theta_{\text{S}}$ in the x-axis).
-            (B) Proportion of beneficial back-mutations among all beneficial mutations ($\proba [ \SphyBen  \given  \SpopBen]$ in the y-axis), shown as a function of the synonymous diversity (Watterson's $\theta_{\text{S}}$ in the x-axis).
+            (A) Proportion of nearly-neutral mutations at the population scale ($\proba [ \SpopNeu]$ in the y-axis), shown as a function of the synonymous diversity (Watterson's $\thetaSyn$ in the x-axis).
+            (B) Proportion of beneficial back-mutations among all beneficial mutations ($\proba [ \SphyBen  \given  \SpopBen]$ in the y-axis), shown as a function of the synonymous diversity (Watterson's $\thetaSyn$ in the x-axis).
         }
@@
     \label{sec:acknowledgment}
-    We gratefully acknowledge the help of Mélodie Bastian, Nicolas Lartillot, Carina Farah Mugal and Laurent Duret for their advice and reviews concerning this manuscript.
+    We gratefully acknowledge the help of Mélodie Bastian, Nicolas Lartillot, Carina Farah Mugal, Laurent Duret and Nicolas Gambardella for their advice and reviews concerning this manuscript.
     This work was performed using the computing facilities of the CC LBBE/PRABI\@.
@@
     \textbf{Data and materials availability:}
+    The data underlying this article are available at \url{https://doi.org/10.5281/zenodo.7878954}.
     Snakemake pipeline, analysis scripts and documentation are available at \href{https://github.com/ThibaultLatrille/SelCoeff}{github.com/ThibaultLatrille/SelCoeff}.
@@
     Sequences of species for which we used population-level polymorphism (see section \ref{subsec:polymorphism-dataset}) and their sister species, were removed from the analysis to ensure independence between the data used in the phylogenetic and population scales.
+    Sites in the alignment containing more than 10\% of gaps across the species were discarded.
     Altogether, our genome-wide dataset contains $14,509$ protein-coding DNA sequences in $87$ placental mammals.
@@
     This conversion from genomic position to alignment position was only possible when the assembly used for SNP-calling was the same as the one used in the OrthoMaM alignment, the GTF annotations, and the FASTA sequences.
-    SNPs were polarized using the three closest outgroups found in the OrthoMaM alignment with est-usfs v2.04~\cite{keightley_inferring_2018}.
+    SNPs were polarized using the three closest outgroups found in the OrthoMaM alignment with est-usfs v2.04~\cite{keightley_inferring_2018}, and SNPs with a derived probability lower than 0.99 were discarded (1\% of false positive).
 
@@
     The selection coefficient ($\Sphy$) of each substitution was then obtained by comparing the difference in amino acid fitnesses for each polarized non-synonymous codon substitution, by referring to the site-specific fitness profile obtained in the phylogeny-based method (see section~\ref{subsec:s-phylogeny-method}).
-    Finally, the rate of non-synonymous over synonymous substitutions for a given class of selection coefficient ($\Sphyclass$) was computed as:
+    Finally, the rate of non-synonymous over synonymous substitutions for a given class of selection coefficient ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$) was computed as:
     \begin{align}
@@
             \ds &= \dfrac{D_{\text{syn}}}{L_{\text{syn}}},
-        \end{dcases}
+        \end{dcases}\label{eq:dnds}
     \end{align}
@@
     \begin{equation}
-        \delta(\dnds) = \dfrac{\dnds - \dn(\Sphy < 1) / \ds}{\dnds} = \dfrac{\dn - \dn(\Sphy < 1)}{\dn} = \delta(\dn).
+        \delta(\dnds) = \dfrac{\dnds - \dn(\Sphy < 1) / \ds}{\dnds} = \dfrac{\dn - \dn(\Sphy < 1)}{\dn} = \delta(\dn).\label{eq:delta-dnds}
     \end{equation}
@@
     The polyDFE\cite{tataru_inference_2017, tataru_polydfe_2020} software implements a mixture of a $\Gamma$ and exponential distributions to model the DFE of non-synonymous mutations, while synonymous mutations are considered neutral.
-    The model estimates the parameters $\DelMean$ , $b$, $p_b$ and $\AdvMean$ for non-synonymous mutations as:
+    The model estimates the parameters $\DelMean$, $b$, $p_b$ and $\AdvMean$ for non-synonymous mutations as:
     \begin{equation}
@@
     where $\DelMean \leq -1 $ is the estimated mean of the DFE for $\Spop \leq 0$;
-    $b \geq 0.4$ is the estimated shape of the $\Gamma$ distribution;
+    $b \geq 0.2$ is the estimated shape of the $\Gamma$ distribution;
     $0 \leq p_b \leq 1$ is the estimated probability that $\Spop > 0$;
     $\AdvMean \geq 1$ is the estimated mean of the DFE for $\Spop > 0$;
-    and $f_{\Gamma}(x; m, b)$ is the density of the $\Gamma$ distribution with mean $m$ and shape $b$, while $f_{e}(x; m)$ is the density of the exponential distribution with mean $m$.
-    Once the DFE is fitted to the data, the proportion of deleterious ($\ProbaPopDel$), nearly-neutral ($\ProbaPopNeu$) and beneficial mutations ($\ProbaPopBen$) are given as:
+    and $f_{\Gamma}(\Spop; m, b)$ is the density of the $\Gamma$ distribution with mean $m$ and shape $b$, while $f_{e}(\Spop; m)$ is the density of the exponential distribution with mean $m$.
+
+    PolyDFE requires one SFS for non-synonymous mutations and one for synonymous mutations (neutral expectation), as well as the number of sites on which each SFS was sampled.
+    For populations containing more than $8$ individuals, the SFS was subsampled down to $16$ chromosomes ($8$ diploid individuals) without replacement (hyper-geometric distribution) to alleviate the effect of different sampling depths in the 28 populations.
+    Altogether, for each class of selection ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$) of non-synonymous SNPs, we aggregated all the SNPs in the selection class $\Sphyclass$ as an SFS.
+    The number of sites on which each SFS was sampled is given by $L(\Sphyclass)$ for the non-synonymous SFS and $L_{\text{syn}}$ for the synonymous SFS respectively.
+    For each class of selection $\Sphyclass$, once fitted to the data using maximum likelihood with polyDFE, the parameters of the DFE $\left( \DelMean , b, p_b, \AdvMean \right)$ were used to compute $\proba [ \SpopDel \given  \Sphyclass] $, $\proba [ \SpopNeu \given \Sphyclass]$, and $\proba [ \SpopBen \given \Sphyclass]$ as:
     \begin{align}
-        \ProbaPopDel &= \proba [ \Spop < -1] = \left( 1 - p_b \right) \int_{1}^{+\infty} f_{\Gamma}(\Spop; -\DelMean, b) \der \Spop, \label{eq:polyProbaDel} \\
-        \ProbaPopNeu &= \proba [ -1 < \Spop < 1] = p_b \int_{0}^{1} f_{e}(\Spop; \AdvMean) \der \Spop + \left( 1 - p_b \right) \int_{0}^{1} f_{\Gamma}(\Spop; -\DelMean, b) \der \Spop, \\
-        \ProbaPopBen &= \proba [ \Spop > 1] = p_b \int_{1}^{+\infty} f_{e}(\Spop; \AdvMean) \der \Spop. \label{eq:polyProbaAdv}
+        \proba [ \SpopDel \given  \Sphyclass] &= \proba [ \Spop < -1 \given \Sphyclass ] = \left( 1 - p_b \right) \int_{1}^{+\infty} f_{\Gamma}(\Spop; -\DelMean, b) \der \Spop, \label{eq:polyProbaDel} \\
+        \proba [ \SpopNeu \given \Sphyclass] &= \proba [ -1 < \Spop < 1 \given \Sphyclass ] = p_b \int_{0}^{1} f_{e}(\Spop; \AdvMean) \der \Spop + \left( 1 - p_b \right) \int_{0}^{1} f_{\Gamma}(\Spop; -\DelMean, b) \der \Spop, \\
+        \proba [ \SpopBen \given \Sphyclass] &= \proba [ \Spop > 1 \given \Sphyclass] = p_b \int_{1}^{+\infty} f_{e}(\Spop; \AdvMean) \der \Spop. \label{eq:polyProbaAdv}
     \end{align}
-
-    PolyDFE requires one SFS for non-synonymous mutations and one for synonymous mutations (neutral expectation), as well as the number of sites on which each SFS was sampled, namely the mutational opportunities $L(\Sphyclass)$ and $L_{\text{syn}}$.
-    For populations containing more than $8$ individuals, the SFS was subsampled down to $16$ chromosomes ($8$ diploid individuals) without replacement (hyper-geometric distribution) to alleviate the effect of different sampling depths in the 28 populations.
-    Altogether, for each class of selection ($\Sphyclass$) of non-synonymous SNPs (or for all SNPs), we estimated the parameters of the DFE $\left( \Spop; \DelMean , b, p_b, \AdvMean \right)$ using maximum likelihood with polyDFE from the number of sites and the SFS obtained by aggregating all the SNPs in the selection class.
-    Once fitted to the data, the parameters of the DFE $\left( \Spop; \DelMean , b, p_b, \AdvMean \right)$ were used to compute $\ProbaPopDel$, $\ProbaPopNeu$, and $\ProbaPopBen$, using eqs.~\ref{eq:polyProbaDel}-\ref{eq:polyProbaAdv}.
 
@@
     Namely, \textit{precision} corresponds to the probability for a back-mutation ($\SphyBen$) to be effectively beneficial at the population level ($\SpopBen$).
-    This probability is obtained by restricting our analysis to SNPs that are predicted to be beneficial back-mutations (black fill for the category $\SphyBen$ in fig.~\ref{fig:homo-afr-results}D).
+    This probability, computed from eq.~\ref{eq:polyProbaAdv}, is obtained by restricting our analysis to SNPs that are predicted to be beneficial back-mutations (yellow fill for the category $\SphyBen$ in fig.~\ref{fig:homo-afr-results}D).
 
@@
     \end{equation}
-    where $\proba [\SpopBen \given \SphyBen]$ and $\proba [ \SphyBen ]$ can be calculated using equations~\ref{eq:precision} and \ref{eq:proba-dfe-mutsel}, respectively, and $\proba [ \SpopBen ]$ is the probability of a mutation to be beneficial at the level of the population, which can be computed from the law of total probabilities as:
+    where $\proba [\SpopBen \given \SphyBen]$ and $\proba [ \SphyBen ]$ can be calculated using equations~\ref{eq:precision} and~\ref{eq:proba-dfe-mutsel}, respectively, and $\proba [ \SpopBen ]$ is the probability of a mutation to be beneficial at the level of the population, which can be computed from the law of total probabilities as:
     \begin{equation}

### 2023-05-02 manuscript/scifile.tex
Prepare submission tex files. Updated figures.

--- 2023-05-02 manuscript/main.tex
@@
-%! BibTeX Compiler = biber
-%TC:ignore
-\documentclass{article}
+% Use only LaTeX2e, calling the article.cls class and 12-point type.
+
+\documentclass[12pt]{article}
+
+% Users of the {thebibliography} environment or BibTeX should use the
+% scicite.sty package, downloadable from *Science* at
+% http://www.sciencemag.org/authors/preparing-manuscripts-using-latex 
+% This package should properly format in-text
+% reference calls and reference-list numbers.
+
+\usepackage{scicite}
+
+\usepackage{times}
+
+% The preamble here sets up a lot of new/revised commands and
+% environments.  It's annoying, but please do *not* try to strip these
+% out into a separate .sty file (which could lead to the loss of some
+% information when we convert the file to other formats).  Instead, keep
+% them in the preamble of your main LaTeX source file.
+
+% The following parameters seem to provide a reasonable page setup.
+
+\topmargin 0.0cm
+\oddsidemargin 0.2cm
+\textwidth 16cm 
+\textheight 21cm
+\footskip 1.0cm
 
 \usepackage{xcolor, colortbl}
-\definecolor{BLUELINK}{HTML}{0645AD}
-\definecolor{DARKBLUELINK}{HTML}{0B0080}
 \definecolor{LIGHTGREY}{gray}{0.9}
-\PassOptionsToPackage{hyphens}{url}
 \usepackage[colorlinks=false]{hyperref}
-% for linking between references, figures, TOC, etc in the pdf document
-\hypersetup{colorlinks,
-    linkcolor=DARKBLUELINK,
-    anchorcolor=DARKBLUELINK,
-    citecolor=DARKBLUELINK,
-    filecolor=DARKBLUELINK,
-    menucolor=DARKBLUELINK,
-    urlcolor=BLUELINK
-} % Color citation links in purple
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{naturalnames}{hyperref}
-
-\usepackage{biorxiv}
-\usepackage[backend=biber,eprint=false,isbn=false,url=false,intitle=true,style=nature,date=year]{biblatex}
-\addbibresource{codon_models.bib}
-
-\usepackage{url}
 \usepackage{amssymb,amsfonts,amsmath,amsthm,mathtools}
-\usepackage{lmodern}
-\usepackage{xfrac, nicefrac}
 \usepackage{bm}
-\usepackage{listings, enumerate, enumitem}
 \usepackage[export]{adjustbox}
-\usepackage{graphicx}
 \usepackage{bbold}
-\usepackage{pdfpages}
-\pdfinclusioncopyfonts=1
-\usepackage{lineno}
 \usepackage{tabu}
@@
 \usepackage{makecell}
-\usepackage{orcidlink}
+\usepackage{graphicx}
+\usepackage{pdfpages}
+\pdfinclusioncopyfonts=1
 
-\newcommand{\NS}[1]{\textcolor{red}{\textbf{\emph{[NS: #1]}}}}
-
+%The next command sets up an environment for the abstract to your paper.
 \newcommand{\UniDimArray}[1]{\bm{#1}}
@@
 \newcommand{\thetaSyn}{\theta_{\text{S}}}
-\renewcommand{\baselinestretch}{1.5}
-\renewcommand{\arraystretch}{0.6}
-\linenumbers
-\frenchspacing
+
+\newenvironment{sciabstract}{%
+\begin{quote} \bf}
+{\end{quote}}
+
+% Include your paper's title here
 
 \title{Mammalian protein-coding genes exhibit widespread beneficial mutations that are not adaptive}
-\rhead{\scshape Beneficial yet non-adaptive mutations}
 
-\author{
-    \large
-    \textbf{T.
-{Latrille}$^{1\dag}$\orcidlink{0000-0002-9643-4668}, J.
-{Joseph}$^{2\dag}$, D.~A.
-{Hartasánchez}$^{1}$\orcidlink{0000-0003-2596-6883}, N.
-{Salamin}$^{1}$\orcidlink{0000-0002-3963-4954}}\\
-    \normalsize
-    $^{1}$Department of Computational Biology, Université de Lausanne, Lausanne, Switzerland\\
-    $^{2}$Laboratoire de Biométrie et Biologie Evolutive, UMR5558, Université Lyon 1, Villeurbanne, France \\
-    $^{\dag}$These authors contributed equally to this work\\
-    \texttt{\href{mailto:thibault.latrille@ens-lyon.org}{thibault.latrille@ens-lyon.org}} \\
+% Place the author information here.  Please hand-code the contact
+% information and notecalls; do *not* use \footnote commands.  Let the
+% author contact information appear immediately below the author names
+% as shown.  We would also prefer that you don't change the type-size
+% settings shown here.
+
+\author
+{T. {Latrille}$^{1\dag\ast}$, J. {Joseph}$^{2\dag}$, D.~A. {Hartasánchez}$^{1}$, N. {Salamin}$^{1}$\\
+\\
+\normalsize{$^{1}$Department of Computational Biology, Université de Lausanne, Lausanne, Switzerland}\\
+\normalsize{$^{2}$Laboratoire de Biométrie et Biologie Evolutive, UMR5558, Université Lyon 1, Villeurbanne, France}\\
+\normalsize{$^{\dag}$These authors contributed equally to this work}\\
+\normalsize{$^\ast$To whom correspondence should be addressed; E-mail:  \href{mailto:thibault.latrille@ens-lyon.org}{thibault.latrille@ens-lyon.org}.}
 }
 
-% The submission checklist is available at:
-% https://docs.google.com/document/d/1aHCF1on0mHTK2DoroPCLP_xto4xwHnGJCGwaL1Vm2UE/edit?usp=sharing
+% Include the date command, but leave its argument blank.
+
+\date{}
+
+%%%%%%%%%%%%%%%%% END OF PREAMBLE %%%%%%%%%%%%%%%%
 
 \begin{document}
+
+% Double-space the manuscript.
+
+\baselineskip24pt
+
+% Make the title.
+
 \maketitle
 
-%TC:endignore
-    \begin{abstract}
+% Place your abstract within the special {sciabstract} environment.
+
+\begin{sciabstract}
     Mutations can be beneficial by bringing innovation to their bearer, allowing them to adapt to environmental change.
@@
     We confirmed that these beneficial back-mutations are positively selected in extant populations and demonstrated that a substantial part of ongoing positive selection is not driven by adaptation to environmental change.
-    \end{abstract}
+\end{sciabstract}
 
-    \keywords{Adaptation \and Back-mutations \and Phylogenetics \and Population-genetics \and Codon models }
-
+\section*{Introduction}
 Adaptation is one of the main processes shaping the diversity of forms and functions across the tree of life~\cite{darwin_origin_1859}.
@@
 
-    %In this study, we seek empirical evidence for beneficial back-mutations and test long-standing related questions, such as how common they are and what the probability is for any beneficial mutation observed in current populations to be a back-mutation.
-    %By addressing these questions, we provide novel insight into the process of adaptation and, more broadly, into how natural selection has affected protein-coding DNA sequences throughout evolution.
 \subsection*{Fitness landscape reconstruction}
@@
 Importantly, because mutation-selection models at the phylogenetic scale are based on population-genetics equations, their estimates of selection coefficients are directly interpretable as fitness effects for an individual within a population.
-    %These methods account for phylogenetic relationships, the structure of the genetic code and accommodate for underlying mutational biases~\cite{rodrigue_mechanistic_2010, tamuri_estimating_2012, latrille_improved_2022}.
 
@@
 By discarding all beneficial back-mutations we can obtain an estimate of $\dnds$ which is not inflated.
-    By comparing these two ways of calculating $\dnds$ (see section~\ref{subsec:substitution-mapping-in-the-terminal-branch} in Materials \& Methods), we calculated that beneficial back-mutations inflate $\dnds$ values by between 9 and 11\% across genera while only representing between 1.2 and 1.4\% of non-synonymous mutations (table~S2-3 and fig.~\ref{fig:homo-afr-results}A for humans).
+By comparing these two ways of calculating $\dnds$ (see section~1.5 in Materials \& Methods), we calculated that beneficial back-mutations inflate $\dnds$ values by between 9 and 11\% across genera while only representing between 1.2 and 1.4\% of non-synonymous mutations (table~S2-3 and fig.~\ref{fig:homo-afr-results}A for humans).
 
@@
 By gathering information across many SNPs, it is possible to estimate the distribution of fitness effects (DFE) at the population scale, taking synonymous SNPs as a neutral expectation~\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009, galtier_adaptive_2016, tataru_inference_2017}.
-    From the estimated DFE, we can derive the proportion of beneficial mutations ($\ProbaPopBen$), nearly-neutral mutations ($\ProbaPopNeu$) and deleterious mutations ($\ProbaPopDel$) at the population scale (see section~\ref{subsec:s-polymorphism-method} in Materials \& Methods).
+From the estimated DFE, we can derive the proportion of beneficial mutations ($\ProbaPopBen$), nearly-neutral mutations ($\ProbaPopNeu$) and deleterious mutations ($\ProbaPopDel$) at the population scale (see section~1.6 in Materials \& Methods).
 These approaches offer a unique opportunity to contrast selection coefficients estimated at the population scale ($\Spop$) and at the phylogenetic scale ($\Sphy$).
 
-    Across our selection classes ($\SphyDel$, $\SphyNeu$ and $\SphyBen$), one can ultimately estimate the proportion of correct and incorrect predictions, leading to an estimation of \textit{precision} and \textit{recall} (fig.~\ref{fig:method}F-G and section~\ref{subsec:precisison_recall} in Materials \& Methods).
+Across our selection classes ($\SphyDel$, $\SphyNeu$ and $\SphyBen$), one can ultimately estimate the proportion of correct and incorrect predictions, leading to an estimation of \textit{precision} and \textit{recall} (fig.~\ref{fig:method}F-G and section~1.7 in Materials \& Methods).
 Across 28 populations of different mammal species, mutations predicted to be deleterious at the phylogenetic scale ($\ProbaPopDel$) were indeed purged at the population scale, with a \textit{precision} in the range of 89--96\% (table~\ref{table:proba} and fig.~\ref{fig:homo-afr-results}D for humans).
@@
 
-    %We have to acknowledge that the mammalian case study might also not be representative of other clades.
-    %Indeed, long-term population sizes are relatively small in mammals, which allow large amounts of deleterious mutations to be fixed, and thus, a lot of opportunities for beneficial back-mutations to arise.
-    %It would thus be of great interest to reproduce our analysis with other clades, such as \textit{Drosophila} or \textit{Saccharomyces} which have higher effective population sizes.
-    %Indeed when the effective population size is higher, the number of effectively neutral mutational opportunities should be reduced.
-    %Allowing for changes in effective population sizes along the phylogeny have been developed~\cite{latrille_inferring_2021}, but are, for the moment, too computationally intensive to be performed genome-wide.
-    %This reduction should mechanistically increase the proportion of adaptive substitutions.
-    %However, this does not imply that the rate of adaptation (i.e the number of changes in the fitness landscape per site per generation) is higher~\cite{galtier_adaptive_2016}.
-
 The exact estimation of the contribution of beneficial back-mutations to positive selection relies on some hypotheses at both the phylogenetic and population scales and is sensitive to methodological limitations.
@@
 Therefore, our estimation of beneficial back-mutations among advantageous ones should be taken as a lower bound.
-
-    %Regarding the distribution of fitness effects (DFE) estimated at the population scale, there is no consensus on its expected shape~\cite{welch_divergence_2008, bataillon_effects_2014}, although it has been found to be reliably constant between closely related species~\cite{castellano_comparison_2019}.
-    %We modelled the DFE as a continuous distribution, but to check for robustness in our results despite the uncertainty of the underlying DFE, we also performed our analysis assuming a discretized DFE.
-    %Our results are consistent, with the proportion of back-mutations among all beneficial mutations ranging from XX to XX\% across populations when modelling a DFE as a discrete distributio.
-    %Consequently, even though our general framework contrasting the phylogenetic and population scales is theoretically consistent, we acknowledge that estimating the proportion of back-mutations among all beneficial ones is dependent on the the underlying DFE at the population scale and the threshold used to define a beneficial mutation.
-    %As a result, further work is required to investigate the shape of the DFE at the population scale.
-    %Notably, the reconstructed distribution of $\Sphy$ values obtained in our study has a negative mode (around $\Sphy=-5$), consistent with experimental DFEs obtained by mutation accumulation.
-    %Contrarily, continuous DFEs estimated at the population scale have by definition a mode at 0.
-    %We argue that methods estimating DFE at the population scale should assume a mode shifted toward negative values of $\Spop$.
 
@@
 \end{figure*}
-
-    %\subsection*{The role of epistasis in mammalian protein-coding genes}
-    %
-    %In our study, we focused on mutations toward a more optimal amino-acid at a given site, assuming that amino-acid fitness landscapes are site-specific and also independent of one another.
-    %Contrarily, under epistasis, the fitness effect of a mutation at a particular site depends on the amino-acids present at other sites.
-    %Epistasis therefore allows for compensatory mutations, which restore fitness through mutations at loci different from where deleterious mutations take place, and this process also leaves signals interpretable as non-adaptive beneficial mutations~\cite{hartl_compensatory_1996, pollock_strong_2014, starr_epistasis_2016}.
-    %Also, epistasis has been shown to play a role in the evolution of protein-coding genes, with amino-acid residues in contact within a protein or between proteins tending to co-evolve~\cite{breen_epistasis_2012, starr_epistasis_2016}.
-    %Particularly, the residues in contact co-evolve to become more compatible with each other generating an entrenchment, making empirical evidence for beneficial back-mutations harder to find since restoring mutations becomes less and less likely to occur over time~\cite{goldstein_nonadaptive_2015, goldstein_sequence_2017, park_epistatic_2022}.
-    %Nevertheless, the fact that we observe such a high proportion of beneficial back-mutations suggests that the underlying assumptions of our model, namely site-independence, implying no epistasis, and a static fitness landscape, are a reasonable approximation for the underlying fitness landscape of proteins.
-    %Our results imply that the fitness effects of new mutations are mostly conserved across mammalian orthologs, in agreement with other studies showing that for conserved orthologs with similar structures and functions, models without epistasis provide a reasonable estimate of fitness effects in protein coding genes~\cite{ashenberg_mutational_2013, youssef_consequences_2020}.
 
@@
 
-%TC:ignore
+\bibliography{codon_models_bibtex}
+\bibliographystyle{Science}
+
 \section*{Acknowledgements}
@@
 
-    \section{Materials \& Methods}
-    \label{sec:methods}
+%Here you should list the contents of your Supplementary Materials -- below is an example. 
+%You should include a list of Supplementary figures, Tables, and any references that appear only in the SM. 
+%Note that the reference numbering continues from the main text to the SM.
+% In the example below, Refs. 4-10 were cited only in the SM.     
+\section*{Supplementary materials}
+Materials and Methods\\
+Supplementary Text\\
+Figs. S1 to S16\\
+Tables S1 to S3\\
+References \textit{(S1-S19)}
 
-    \subsection{Phylogenetic dataset}\label{subsec:phylo-dataset}
-
-    Protein-coding DNA sequence alignments in placental mammals and their corresponding gene trees come from the \href{https://www.orthomam.univ-montp2.fr}{OrthoMaM} database and were processed as in \textcite{latrille_genes_2023}.
-    OrthoMaM contains a total of $116$ mammalian reference sequences in v10c~\cite{ranwez_orthomam_2007, douzery_orthomam_2014, scornavacca_orthomam_2019}.
-    Genes located on the X and Y chromosomes and on the mitochondrial genome were discarded from the analysis because the level of polymorphism –~which is necessary for population-based analyses~– is expected to be different in these three regions compared to the autosomal genome.
-    Sequences of species for which we used population-level polymorphism (see section \ref{subsec:polymorphism-dataset}) and their sister species, were removed from the analysis to ensure independence between the data used in the phylogenetic and population scales.
-    Sites in the alignment containing more than 10\% of gaps across the species were discarded.
-    Altogether, our genome-wide dataset contains $14,509$ protein-coding DNA sequences in $87$ placental mammals.
-
-    \subsection{Selection coefficient ($\Sphy$) in a phylogeny-based method}
-    \label{subsec:s-phylogeny-method}
-    We analyzed the phylogenetic-level data using mutation-selection models.
-    These models assume the protein-coding sequences are at mutation-selection balance under a fixed fitness landscape characterized by a fitness vector over the $20$ amino acids at each site~\cite{yang_mutationselection_2008, halpern_evolutionary_1998, rodrigue_mechanistic_2010}.
-    Mathematically, the rate of non-synonymous substitution from codon $a$ to codon $b$ ($q_{a \mapsto b}^{(i)}$) at site $i$ of the sequence is equal to the rate of mutation of the underlying nucleotide change ($\mu_{a \mapsto b}$) multiplied by the scaled probability of mutation fixation ($\proba_{a \mapsto b}^{(i)}$).
-    The probability of fixation depends on the difference between the scaled fitness of the amino acid encoded by the mutated codon ($F_b^{(i)}$) and the amino acid encoded by the original codon ($F_a^{(i)}$) at site $i$~\cite{wright_evolution_1931, fisher_genetical_1930}.
-    The rate of substitution from codon $a$ to $b$ at a site $i$ is thus:
-    \begin{equation}
-        \begin{dcases}
-            q_{a \mapsto b}^{(i)} & = 0 \text{ if codons $a$ and $b$ are more than one mutation away,} \\
-            q_{a \mapsto b}^{(i)} & = \mu_{a \mapsto b} \text{ if codons $a$ and $b$ are synonymous, and}\\
-            q_{a \mapsto b}^{(i)} & = \mu_{a \mapsto b} \dfrac{F_b^{(i)} - F_a^{(i)}}{1 - \e^{F_a^{(i)} - F_b^{(i)}}} \text{ if codons $a$ and $b$ are non-synonymous}.
-        \end{dcases}
-    \end{equation}
-    Fitting the mutation-selection model on a multi-species sequence alignment leads to an estimation of the $4 \times 4$ nucleotide mutation rate matrix ($\UniDimArray{\mu}$) as well as the $20$ amino-acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$.
-    The selection coefficient for a mutation from codon $a$ to codon $b$ at site $i$ is defined as:
-    \begin{equation}
-        \Sphy^{(i)} (a \mapsto b) = \Delta F^{(i)} = F^{(i)}_{b} - F^{(i)}_{a}.
-    \end{equation}
-    In our subsequent derivation the source ($a$) and target ($b$) codons as well as the site ($i$) are implicit and thus never explicitly written.
-    We used the Bayesian software \textit{BayesCode} (\url{https://github.com/ThibaultLatrille/bayescode}) to estimate the selection coefficients for each protein-coding gene in the mammalian dataset.
-    We ran the Markov chain Monte-Carlo (MCMC) algorithm implemented in BayesCode for $2,000$ generations as described in \textcite{latrille_genes_2023}.
-    For each gene, after discarding a burn-in period of $1,000$ generations of MCMC, we obtained posterior mean estimates (over the $1,000$ generations left of MCMC) of the mutation rate matrix ($\UniDimArray{\mu}$) as well as the $20$ amino acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$.
-
-    \subsection{Polymorphism dataset}
-    \label{subsec:polymorphism-dataset}
-
-    The genetic variants representing the population level polymorphisms were obtained from the following species and their available datasets: \textit{Equus caballus} (EquCab2 assembly in the EVA study PRJEB9799~\cite{alabri_whole_2020}), \textit{Bos taurus} (UMD3.1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}), \textit{Ovis aries} (Oar\_v3.1 assembly in the NextGen project), \textit{Capra hircus} (CHIR1 assembly in the NextGen project), converted to ARS1 assembly with dbSNP identifiers~\cite{sherry_dbsnp_2001}), \textit{Chlorocebus sabaeus} (ChlSab1.1 assembly in the EVA project PRJEB22989~\cite{svardal_ancient_2017}), \textit{Homo sapiens} (GRCh38 assembly in the 1000 Genomes Project~\cite{zheng-bradley_alignment_2017}).
-    In total, we analyzed 28 populations across the 6 different species with polymorphism data.
-    The data was processed as described in \textcite{latrille_genes_2023}.
-
-    Only bi-allelic single nucleotide polymorphisms (SNPs) found within a gene were in our polymorphism dataset, while nonsense variants and indels were discarded.
-    To construct the dataset, we first recovered the location of each SNP (represented by its chromosome, position, and strand) in the focal species and matched it to its corresponding position in the coding sequence (CDS) using gene annotation files (GTF format) downloaded from Ensembl (\url{ensembl.org}).
-    We then verified that the SNP downloaded from Ensembl matched the reference in the CDS in FASTA format.
-    Next, the position in the CDS was converted to the corresponding position in the multi-species sequence alignment (containing gaps) from the OrthoMaM database (see section~\ref{subsec:s-phylogeny-method}) for the corresponding gene by doing a global pairwise alignment (Biopython function pairwise2).
-    This conversion from genomic position to alignment position was only possible when the assembly used for SNP-calling was the same as the one used in the OrthoMaM alignment, the GTF annotations, and the FASTA sequences.
-    SNPs were polarized using the three closest outgroups found in the OrthoMaM alignment with est-usfs v2.04~\cite{keightley_inferring_2018}, and SNPs with a derived probability lower than 0.99 were discarded (1\% of false positive).
-
-    \subsection{Mutational opportunities}
-    \label{subsec:nunber-of-sites}
-    The mutational opportunities of any new mutation refer to its likelihood of falling into a specific category (synonymous, deleterious, nearly-neutral, or beneficial).
-    Deriving such opportunities is necessary to estimate the strength of selection exerted at the population scale since different categories might have different mutational opportunities, and thus polymorphism and divergence need to be corrected accordingly (see sections~\ref{subsec:substitution-mapping-in-the-terminal-branch},~\ref{subsec:s-polymorphism-method}, and~\ref{subsec:precisison_recall}).
-    To calculate mutational opportunities, we reconstructed the ancestral genome of each of the 28 populations, which differs from the corresponding species' reference genome since it accounts for the variability present in the specific population.
-    So, for each population, we used the polarized SNPs to reconstruct the ancestral DNA sequence, containing only substitutions and no segregating polymorphisms.
-    If an SNP was still segregating in the population, we used its ancestral version.
-
-    From the reconstructed ancestral genome at the base of the population genealogy, all possible mutations were computed, weighted by the instantaneous rate of change between nucleotides obtained from the mutation rate matrix ($\UniDimArray{\mu}$, see section~\ref{subsec:s-phylogeny-method}), summing to $\mu_{\text{tot}}$ across the whole genome, and to $\mu_{\text{syn}}$ when restricted to synonymous mutations.
-    Finally, the mutational opportunities for synonymous mutations were computed as the total number of sites across the genome ($L_{\text{tot}}$) weighted by the proportion of synonymous mutations among all possible mutations as:
-    \begin{equation}
-        L_{\text{syn}} = L_{\text{tot}} \frac{\mu_{\text{syn}}}{\mu_{\text{tot}}}.
-    \end{equation}
-
-    Similarly, for non-synonymous mutations, the total mutation rate for each class of selection $\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$, called $\mu\left( \Sphyclass \right)$, was estimated as the sum across all non-synonymous mutations if their selection coefficient at the phylogenetic scale is in the class $\Sphy \in \Sphyclass$.
-    Accordingly, the mutational opportunities ($L \left( \Sphyclass \right)$) for each class of selection coefficient ($\Sphyclass$) was finally computed as the total number of sites across the genome ($L_{\text{tot}}$) weighted by the ratio of the aggregated mutations rates falling in the class $\mu\left( \Sphyclass \right)$:
-    \begin{equation}
-        L \left( \Sphyclass \right) = L_{\text{tot}} \frac{\mu\left( \Sphyclass \right)}{\mu_{\text{tot}}}.
-    \end{equation}
-
-    Finally, $\proba [ \Sphyclass ]$ is the probability for a non-synonymous mutation to be in the class $\Sphyclass$, thus computed as:
-    \begin{equation}
-        \proba[\Sphyclass] = \frac{L\left( \Sphyclass \right)}{\sum_{\SphyclassAlt\in \{\SphyDel, \SphyNeu, \SphyBen \} } L\left(\SphyclassAlt \right)}.
-        \label{eq:proba-dfe-mutsel}
-    \end{equation}
-
-    \subsection{Substitution mapping in the terminal branch}
-    \label{subsec:substitution-mapping-in-the-terminal-branch}
-    For each gene and each population with polymorphism data available, the genome at the base of the population genealogy was reconstructed (see section~\ref{subsec:nunber-of-sites}).
-    We used the ancestral genome reconstructed at the base of the population genealogy and the three closest outgroups found in the OrthoMaM alignment to infer the ancestral protein-coding DNA sequences for each node of the 4-taxa tree by applying the M5 codon model (gamma site rate variation) as implemented in FastML.v3.11~\cite{ashkenazy_fastml_2012}.
-    All polarized codon substitutions were then obtained by comparing the ancestral protein-coding DNA sequences before the split from the sister species (closest outgroup) to the genome at the base of the population genealogy.
-    We considered \textit{Ceratotherium simum simum} as \textit{Equus caballus'} sister species; \textit{Bison bison bison} as \textit{Bos taurus'} sister species; \textit{Pantholops hodgsonii} as \textit{Ovis aries'} sister species; \textit{Pantholops hodgsonii} as \textit{Capra hircus'} sister species; \textit{Macaca mulatta} as \textit{Chlorocebus sabaeus'} sister species and finally, we considered \textit{Pan troglodytes} as \textit{Homo sapiens'} sister species.
-    The selection coefficient ($\Sphy$) of each substitution was then obtained by comparing the difference in amino acid fitnesses for each polarized non-synonymous codon substitution, by referring to the site-specific fitness profile obtained in the phylogeny-based method (see section~\ref{subsec:s-phylogeny-method}).
-    Finally, the rate of non-synonymous over synonymous substitutions for a given class of selection coefficient ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$) was computed as:
-    \begin{align}
-        \begin{dcases}
-            \dn \left( \Sphyclass \right) &= \dfrac{D\left( \Sphyclass \right)}{L \left( \Sphyclass \right)}, \\
-            \ds &= \dfrac{D_{\text{syn}}}{L_{\text{syn}}},
-        \end{dcases}\label{eq:dnds}
-    \end{align}
-    where $D \left( \Sphyclass \right) $ was the number of non-synonymous substitutions in class $\Sphyclass$, $D_{\text{syn}}$ was the number of synonymous substitutions across the genome, while $L \left( \Sphyclass \right)$ and $L_{\text{syn}}$ were the numbers of non-synonymous and synonymous mutational opportunities, respectively, as defined in section~\ref{subsec:nunber-of-sites}.
-    $\delta(\dnds)$ was computed as the difference between $\dnds$ computed over all substitutions and $\dnds$ when we removed beneficial back-mutations $\dn (\Sphy < 1) / \ds$, normalized by $\dnds$.
-    Note that the quantities $\delta(\dnds)$ and $\delta(\dn)$ are equivalent due to the simplification of the factor $\ds$:
-    \begin{equation}
-        \delta(\dnds) = \dfrac{\dnds - \dn(\Sphy < 1) / \ds}{\dnds} = \dfrac{\dn - \dn(\Sphy < 1)}{\dn} = \delta(\dn).\label{eq:delta-dnds}
-    \end{equation}
-
-    \subsection{Scaled selection coefficients ($\Spop$) in a population-based method}
-    \label{subsec:s-polymorphism-method}
-    To obtain a quantitative estimate of the distribution of selection coefficients for each category of SNPs, we used the polyDFE model~\cite{tataru_inference_2017, tataru_polydfe_2020}.
-    This model uses the count of derived alleles to infer the distribution of fitness effects (DFE).
-    The probability of sampling an allele at a given frequency (before fixation or extinction) is informative of its scaled selection coefficient at the population scale ($\Spop$).
-    Therefore, pooled across many sites, the site-frequency spectrum (SFS) provides information on the underlying $\Spop$ of mutations.
-    However, estimating a single $\Spop$ for all sampled mutations is biologically unrealistic, and a DFE of mutations is usually assumed~\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009}.
-    The polyDFE\cite{tataru_inference_2017, tataru_polydfe_2020} software implements a mixture of a $\Gamma$ and exponential distributions to model the DFE of non-synonymous mutations, while synonymous mutations are considered neutral.
-    The model estimates the parameters $\DelMean$, $b$, $p_b$ and $\AdvMean$ for non-synonymous mutations as:
-    \begin{equation}
-        \phi \left( \Spop; \DelMean , b, p_b, \AdvMean \right) =
-        \begin{dcases}
-            \left( 1 - p_b \right) f_{\Gamma}(-\Spop; -\DelMean, b) & \text{ if $\Spop \leq 0$,} \\
-            p_b f_{e}(\Spop; \AdvMean) & \text{ if $\Spop > 0$,} \\
-        \end{dcases}
-    \end{equation}
-    where $\DelMean \leq -1 $ is the estimated mean of the DFE for $\Spop \leq 0$;
-    $b \geq 0.2$ is the estimated shape of the $\Gamma$ distribution;
-    $0 \leq p_b \leq 1$ is the estimated probability that $\Spop > 0$;
-    $\AdvMean \geq 1$ is the estimated mean of the DFE for $\Spop > 0$;
-    and $f_{\Gamma}(\Spop; m, b)$ is the density of the $\Gamma$ distribution with mean $m$ and shape $b$, while $f_{e}(\Spop; m)$ is the density of the exponential distribution with mean $m$.
-
-    PolyDFE requires one SFS for non-synonymous mutations and one for synonymous mutations (neutral expectation), as well as the number of sites on which each SFS was sampled.
-    For populations containing more than $8$ individuals, the SFS was subsampled down to $16$ chromosomes ($8$ diploid individuals) without replacement (hyper-geometric distribution) to alleviate the effect of different sampling depths in the 28 populations.
-    Altogether, for each class of selection ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$) of non-synonymous SNPs, we aggregated all the SNPs in the selection class $\Sphyclass$ as an SFS.
-    The number of sites on which each SFS was sampled is given by $L(\Sphyclass)$ for the non-synonymous SFS and $L_{\text{syn}}$ for the synonymous SFS respectively.
-    For each class of selection $\Sphyclass$, once fitted to the data using maximum likelihood with polyDFE, the parameters of the DFE $\left( \DelMean , b, p_b, \AdvMean \right)$ were used to compute $\proba [ \SpopDel \given  \Sphyclass] $, $\proba [ \SpopNeu \given \Sphyclass]$, and $\proba [ \SpopBen \given \Sphyclass]$ as:
-    \begin{align}
-        \proba [ \SpopDel \given  \Sphyclass] &= \proba [ \Spop < -1 \given \Sphyclass ] = \left( 1 - p_b \right) \int_{1}^{+\infty} f_{\Gamma}(\Spop; -\DelMean, b) \der \Spop, \label{eq:polyProbaDel} \\
-        \proba [ \SpopNeu \given \Sphyclass] &= \proba [ -1 < \Spop < 1 \given \Sphyclass ] = p_b \int_{0}^{1} f_{e}(\Spop; \AdvMean) \der \Spop + \left( 1 - p_b \right) \int_{0}^{1} f_{\Gamma}(\Spop; -\DelMean, b) \der \Spop, \\
-        \proba [ \SpopBen \given \Sphyclass] &= \proba [ \Spop > 1 \given \Sphyclass] = p_b \int_{1}^{+\infty} f_{e}(\Spop; \AdvMean) \der \Spop. \label{eq:polyProbaAdv}
-    \end{align}
-
-    \subsection{\textit{Precision} and \textit{recall}}
-    \label{subsec:precisison_recall}
-    For readability, we give here \textit{precision} and \textit{recall} for beneficial mutations ($\SphyBen$ and $\SpopBen$), but it can be obtained using the same derivation for the deleterious mutations ($\SphyDel$ and $\SpopDel$) and nearly-neutral mutations ($\SphyNeu$ and $\SpopNeu$).
-
-    \textit{Precision} is the proportion of mutations correctly predicted as beneficial ($\proba [ \SpopBen \cap  \SphyBen]$) out of all predicted as beneficial back-mutations ($\proba [ \SphyBen]$), which can be written as a conditional probability:
-    \begin{equation}
-        \frac{\proba [ \SpopBen  \cap  \SphyBen]}{\proba [ \SphyBen]} = \proba [ \SpopBen  \given  \SphyBen].
-        \label{eq:precision}
-    \end{equation}
-    Namely, \textit{precision} corresponds to the probability for a back-mutation ($\SphyBen$) to be effectively beneficial at the population level ($\SpopBen$).
-    This probability, computed from eq.~\ref{eq:polyProbaAdv}, is obtained by restricting our analysis to SNPs that are predicted to be beneficial back-mutations (yellow fill for the category $\SphyBen$ in fig.~\ref{fig:homo-afr-results}D).
-
-    \textit{Recall} is the proportion of mutations correctly predicted as beneficial ($\proba [ \SpopBen \cap  \SphyBen]$) out of all beneficial mutations ($\proba [ \SpopBen]$), which can be written as a conditional probability:
-    \begin{equation}
-        \frac{\proba [ \SpopBen \cap  \SphyBen]}{\proba [ \SpopBen]} = \proba [ \SphyBen  \given \SpopBen ].
-    \end{equation}
-    Namely, \textit{recall} corresponds to the probability for a beneficial mutation at the population level ($\SpopBen$) to be a beneficial back-mutation ($\SphyBen$).
-    Using Bayes theorem, \textit{recall} can be re-written as:
-    \begin{equation}
-        \proba [\SphyBen \given \SpopBen] = \frac{\proba [\SpopBen \given \SphyBen] \times \proba[\SphyBen]}{\ProbaPopBen},
-        \label{eq:bayes}
-    \end{equation}
-    where $\proba [\SpopBen \given \SphyBen]$ and $\proba [ \SphyBen ]$ can be calculated using equations~\ref{eq:precision} and~\ref{eq:proba-dfe-mutsel}, respectively, and $\proba [ \SpopBen ]$ is the probability of a mutation to be beneficial at the level of the population, which can be computed from the law of total probabilities as:
-    \begin{equation}
-        \proba [ \SpopBen ] = \sum_{\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \} }\proba [\SpopBen \given \Sphyclass ] \times \proba [\Sphyclass ].
-        \label{eq:total_proba}
-    \end{equation}
-    \printbibliography
 \end{document}
-%TC:endignore

### 2023-05-02 manuscript/scifile_SI.tex
Prepare submission tex files. Updated figures.

% Use only LaTeX2e, calling the article.cls class and 12-point type.

\documentclass[12pt]{article}

% Users of the {thebibliography} environment or BibTeX should use the
% scicite.sty package, downloadable from *Science* at
% http://www.sciencemag.org/authors/preparing-manuscripts-using-latex 
% This package should properly format in-text
% reference calls and reference-list numbers.

\usepackage{scicite}

\usepackage{times}

% The preamble here sets up a lot of new/revised commands and
% environments.  It's annoying, but please do *not* try to strip these
% out into a separate .sty file (which could lead to the loss of some
% information when we convert the file to other formats).  Instead, keep
% them in the preamble of your main LaTeX source file.

% The following parameters seem to provide a reasonable page setup.

\topmargin 0.0cm
\oddsidemargin 0.2cm
\textwidth 16cm
\textheight 21cm
\footskip 1.0cm

\usepackage{caption}
\usepackage{xcolor, colortbl}
\definecolor{LIGHTGREY}{gray}{0.9}
\usepackage[colorlinks=false]{hyperref}
\usepackage{amssymb,amsfonts,amsmath,amsthm,mathtools}
\usepackage{bm,bbold}
\usepackage{verbatim}
\usepackage{float}
\usepackage{listings, enumerate, enumitem}
\usepackage[export]{adjustbox}
\usepackage{tabu}
\usepackage{longtable}
\tabulinesep=0.6mm
\newcommand\cellwidth{\TX@col@width}
\usepackage{hhline}
\setlength{\arrayrulewidth}{1.2pt}
\usepackage{multicol,multirow,array}
\usepackage{etoolbox}
\AtBeginEnvironment{tabu}{\footnotesize}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{graphicx}
\pdfinclusioncopyfonts=1

\renewcommand{\thetable}{S\arabic{table}}
\renewcommand{\thefigure}{S\arabic{figure}}

%The next command sets up an environment for the abstract to your paper.
\newcommand{\UniDimArray}[1]{\bm{#1}}
\newcommand{\der}{\text{d}}
\newcommand{\e}{\text{e}}
\newcommand{\Ne}{N_{\text{e}}}
\newcommand{\proba}{\mathbb{P}}
\newcommand{\pfix}{\proba_{\text{fix}}}
\newcommand{\dn}{d_N}
\newcommand{\ds}{d_S}
\newcommand{\dnds}{\dn / \ds}
\newcommand{\Sphy}{S_{0}}
\newcommand{\SphyDel}{\mathcal{D}_0}
\newcommand{\SphyNeu}{\mathcal{N}_0}
\newcommand{\SphyBen}{\mathcal{B}_0}
\newcommand{\Sphyclass}{x}
\newcommand{\SphyclassAlt}{y}
\newcommand{\given}{\mid}
\newcommand{\Spop}{S}
\newcommand{\SpopDel}{\mathcal{D}}
\newcommand{\SpopNeu}{\mathcal{N}}
\newcommand{\SpopBen}{\mathcal{B}}
\newcommand{\ProbaPopDel}{\proba [ \SpopDel]}
\newcommand{\ProbaPopNeu}{\proba [ \SpopNeu ]}
\newcommand{\ProbaPopBen}{\proba [ \SpopBen ]}
\newcommand{\AdvMean}{\beta_b}
\newcommand{\DelMean}{\beta_d}
\newcommand{\thetaSyn}{\theta_{\text{S}}}

\newenvironment{sciabstract}{%
    \begin{quote} \bf}
    {\end{quote}}

% Include your paper's title here

\title{\textbf{Supplementary materials}\\\vspace*{1cm}Mammalian protein-coding genes exhibit widespread beneficial mutations that are not adaptive}

% Place the author information here.  Please hand-code the contact
% information and notecalls; do *not* use \footnote commands.  Let the
% author contact information appear immediately below the author names
% as shown.  We would also prefer that you don't change the type-size
% settings shown here.

\author
{T. {Latrille}$^{1\dag\ast}$, J. {Joseph}$^{2\dag}$, D.~A. {Hartasánchez}$^{1}$, N. {Salamin}$^{1}$\\
\\
\normalsize{$^{1}$Department of Computational Biology, Université de Lausanne, Lausanne, Switzerland}\\
\normalsize{$^{2}$Laboratoire de Biométrie et Biologie Evolutive, UMR5558, Université Lyon 1, Villeurbanne, France}\\
\normalsize{$^{\dag}$These authors contributed equally to this work}\\
\normalsize{$^\ast$To whom correspondence should be addressed; E-mail:  \href{mailto:thibault.latrille@ens-lyon.org}{thibault.latrille@ens-lyon.org}.}
}

% Include the date command, but leave its argument blank.

\date{}

%%%%%%%%%%%%%%%%% END OF PREAMBLE %%%%%%%%%%%%%%%%

\begin{document}

% Double-space the manuscript.

    \baselineskip24pt

% Make the title.

    \maketitle

% Place your abstract within the special {sciabstract} environment.

    \begin{sciabstract}
        Mutations can be beneficial by bringing innovation to their bearer, allowing them to adapt to environmental change.
        However, mutations can also be beneficial because they are reverting previous deleterious changes, simply restoring pre-existing functions.
        By integrating phylogenomic and population data in mammals, we estimated the contribution of beneficial back-mutations to molecular evolution, which had remained widely overlooked so far.
        Applying a mutation-selection model, we estimated amino acid fitness landscapes for mammalian protein-coding genes.
        Assuming these fitness landscapes do not change, any beneficial mutation is necessarily a back-mutation.
        We confirmed that these beneficial back-mutations are positively selected in extant populations and demonstrated that a substantial part of ongoing positive selection is not driven by adaptation to environmental change.
    \end{sciabstract}

    \part*{Supplementary materials}
    \tableofcontents
    \clearpage

    \section{Materials \& Methods}
    \label{sec:methods}

    \subsection{Phylogenetic dataset}\label{subsec:phylo-dataset}

    Protein-coding DNA sequence alignments in placental mammals and their corresponding gene trees come from the \href{https://www.orthomam.univ-montp2.fr}{OrthoMaM} database and were processed as in Latrille \textit{et al} (2023)\cite{latrille_genes_2023}.
    OrthoMaM contains a total of $116$ mammalian reference sequences in v10c~\cite{ranwez_orthomam_2007, douzery_orthomam_2014, scornavacca_orthomam_2019}.
    Genes located on the X and Y chromosomes and on the mitochondrial genome were discarded from the analysis because the level of polymorphism –~which is necessary for population-based analyses~– is expected to be different in these three regions compared to the autosomal genome.
    Sequences of species for which we used population-level polymorphism (see section \ref{subsec:polymorphism-dataset}) and their sister species, were removed from the analysis to ensure independence between the data used in the phylogenetic and population scales.
    Sites in the alignment containing more than 10\% of gaps across the species were discarded.
    Altogether, our genome-wide dataset contains $14,509$ protein-coding DNA sequences in $87$ placental mammals.

    \subsection{Selection coefficient ($\Sphy$) in a phylogeny-based method}
    \label{subsec:s-phylogeny-method}
    We analyzed the phylogenetic-level data using mutation-selection models.
    These models assume the protein-coding sequences are at mutation-selection balance under a fixed fitness landscape characterized by a fitness vector over the $20$ amino acids at each site~\cite{yang_mutationselection_2008, halpern_evolutionary_1998, rodrigue_mechanistic_2010}.
    Mathematically, the rate of non-synonymous substitution from codon $a$ to codon $b$ ($q_{a \mapsto b}^{(i)}$) at site $i$ of the sequence is equal to the rate of mutation of the underlying nucleotide change ($\mu_{a \mapsto b}$) multiplied by the scaled probability of mutation fixation ($\proba_{a \mapsto b}^{(i)}$).
    The probability of fixation depends on the difference between the scaled fitness of the amino acid encoded by the mutated codon ($F_b^{(i)}$) and the amino acid encoded by the original codon ($F_a^{(i)}$) at site $i$~\cite{wright_evolution_1931, fisher_genetical_1930}.
    The rate of substitution from codon $a$ to $b$ at a site $i$ is thus:
    \begin{equation}
        \begin{dcases}
            q_{a \mapsto b}^{(i)} & = 0 \text{ if codons $a$ and $b$ are more than one mutation away,} \\
            q_{a \mapsto b}^{(i)} & = \mu_{a \mapsto b} \text{ if codons $a$ and $b$ are synonymous, and}\\
            q_{a \mapsto b}^{(i)} & = \mu_{a \mapsto b} \dfrac{F_b^{(i)} - F_a^{(i)}}{1 - \e^{F_a^{(i)} - F_b^{(i)}}} \text{ if codons $a$ and $b$ are non-synonymous}.
        \end{dcases}
    \end{equation}
    Fitting the mutation-selection model on a multi-species sequence alignment leads to an estimation of the $4 \times 4$ nucleotide mutation rate matrix ($\UniDimArray{\mu}$) as well as the $20$ amino-acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$.
    The selection coefficient for a mutation from codon $a$ to codon $b$ at site $i$ is defined as:
    \begin{equation}
        \Sphy^{(i)} (a \mapsto b) = \Delta F^{(i)} = F^{(i)}_{b} - F^{(i)}_{a}.
    \end{equation}
    In our subsequent derivation the source ($a$) and target ($b$) codons as well as the site ($i$) are implicit and thus never explicitly written.
    We used the Bayesian software \textit{BayesCode} (\url{https://github.com/ThibaultLatrille/bayescode}) to estimate the selection coefficients for each protein-coding gene in the mammalian dataset.
    We ran the Markov chain Monte-Carlo (MCMC) algorithm implemented in BayesCode for $2,000$ generations as described in Latrille \textit{et al} (2023)\cite{latrille_genes_2023}.
    For each gene, after discarding a burn-in period of $1,000$ generations of MCMC, we obtained posterior mean estimates (over the $1,000$ generations left of MCMC) of the mutation rate matrix ($\UniDimArray{\mu}$) as well as the $20$ amino acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$.

    \subsection{Polymorphism dataset}
    \label{subsec:polymorphism-dataset}

    The genetic variants representing the population level polymorphisms were obtained from the following species and their available datasets: \textit{Equus caballus} (EquCab2 assembly in the EVA study PRJEB9799~\cite{alabri_whole_2020}), \textit{Bos taurus} (UMD3.1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}), \textit{Ovis aries} (Oar\_v3.1 assembly in the NextGen project), \textit{Capra hircus} (CHIR1 assembly in the NextGen project), converted to ARS1 assembly with dbSNP identifiers~\cite{sherry_dbsnp_2001}), \textit{Chlorocebus sabaeus} (ChlSab1.1 assembly in the EVA project PRJEB22989~\cite{svardal_ancient_2017}), \textit{Homo sapiens} (GRCh38 assembly in the 1000 Genomes Project~\cite{zheng-bradley_alignment_2017}).
    In total, we analyzed 28 populations across the 6 different species with polymorphism data.
    The data was processed as described in Latrille \textit{et al} (2023)\cite{latrille_genes_2023}.

    Only bi-allelic single nucleotide polymorphisms (SNPs) found within a gene were in our polymorphism dataset, while nonsense variants and indels were discarded.
    To construct the dataset, we first recovered the location of each SNP (represented by its chromosome, position, and strand) in the focal species and matched it to its corresponding position in the coding sequence (CDS) using gene annotation files (GTF format) downloaded from Ensembl (\url{ensembl.org}).
    We then verified that the SNP downloaded from Ensembl matched the reference in the CDS in FASTA format.
    Next, the position in the CDS was converted to the corresponding position in the multi-species sequence alignment (containing gaps) from the OrthoMaM database (see section~\ref{subsec:s-phylogeny-method}) for the corresponding gene by doing a global pairwise alignment (Biopython function pairwise2).
    This conversion from genomic position to alignment position was only possible when the assembly used for SNP-calling was the same as the one used in the OrthoMaM alignment, the GTF annotations, and the FASTA sequences.
    SNPs were polarized using the three closest outgroups found in the OrthoMaM alignment with est-usfs v2.04~\cite{keightley_inferring_2018}, and SNPs with a derived probability lower than 0.99 were discarded (1\% of false positive).

    \subsection{Mutational opportunities}
    \label{subsec:nunber-of-sites}
    The mutational opportunities of any new mutation refer to its likelihood of falling into a specific category (synonymous, deleterious, nearly-neutral, or beneficial).
    Deriving such opportunities is necessary to estimate the strength of selection exerted at the population scale since different categories might have different mutational opportunities, and thus polymorphism and divergence need to be corrected accordingly (see sections~\ref{subsec:substitution-mapping-in-the-terminal-branch},~\ref{subsec:s-polymorphism-method}, and~\ref{subsec:precisison_recall}).
    To calculate mutational opportunities, we reconstructed the ancestral genome of each of the 28 populations, which differs from the corresponding species' reference genome since it accounts for the variability present in the specific population.
    So, for each population, we used the polarized SNPs to reconstruct the ancestral DNA sequence, containing only substitutions and no segregating polymorphisms.
    If an SNP was still segregating in the population, we used its ancestral version.

    From the reconstructed ancestral genome at the base of the population genealogy, all possible mutations were computed, weighted by the instantaneous rate of change between nucleotides obtained from the mutation rate matrix ($\UniDimArray{\mu}$, see section~\ref{subsec:s-phylogeny-method}), summing to $\mu_{\text{tot}}$ across the whole genome, and to $\mu_{\text{syn}}$ when restricted to synonymous mutations.
    Finally, the mutational opportunities for synonymous mutations were computed as the total number of sites across the genome ($L_{\text{tot}}$) weighted by the proportion of synonymous mutations among all possible mutations as:
    \begin{equation}
        L_{\text{syn}} = L_{\text{tot}} \frac{\mu_{\text{syn}}}{\mu_{\text{tot}}}.
    \end{equation}

    Similarly, for non-synonymous mutations, the total mutation rate for each class of selection $\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$, called $\mu\left( \Sphyclass \right)$, was estimated as the sum across all non-synonymous mutations if their selection coefficient at the phylogenetic scale is in the class $\Sphy \in \Sphyclass$.
    Accordingly, the mutational opportunities ($L \left( \Sphyclass \right)$) for each class of selection coefficient ($\Sphyclass$) was finally computed as the total number of sites across the genome ($L_{\text{tot}}$) weighted by the ratio of the aggregated mutations rates falling in the class $\mu\left( \Sphyclass \right)$:
    \begin{equation}
        L \left( \Sphyclass \right) = L_{\text{tot}} \frac{\mu\left( \Sphyclass \right)}{\mu_{\text{tot}}}.
    \end{equation}

    Finally, $\proba [ \Sphyclass ]$ is the probability for a non-synonymous mutation to be in the class $\Sphyclass$, thus computed as:
    \begin{equation}
        \proba[\Sphyclass] = \frac{L\left( \Sphyclass \right)}{\sum_{\SphyclassAlt\in \{\SphyDel, \SphyNeu, \SphyBen \} } L\left(\SphyclassAlt \right)}.
        \label{eq:proba-dfe-mutsel}
    \end{equation}

    \subsection{Substitution mapping in the terminal branch}
    \label{subsec:substitution-mapping-in-the-terminal-branch}
    For each gene and each population with polymorphism data available, the genome at the base of the population genealogy was reconstructed (see section~\ref{subsec:nunber-of-sites}).
    We used the ancestral genome reconstructed at the base of the population genealogy and the three closest outgroups found in the OrthoMaM alignment to infer the ancestral protein-coding DNA sequences for each node of the 4-taxa tree by applying the M5 codon model (gamma site rate variation) as implemented in FastML.v3.11~\cite{ashkenazy_fastml_2012}.
    All polarized codon substitutions were then obtained by comparing the ancestral protein-coding DNA sequences before the split from the sister species (closest outgroup) to the genome at the base of the population genealogy.
    We considered \textit{Ceratotherium simum simum} as \textit{Equus caballus'} sister species; \textit{Bison bison bison} as \textit{Bos taurus'} sister species; \textit{Pantholops hodgsonii} as \textit{Ovis aries'} sister species; \textit{Pantholops hodgsonii} as \textit{Capra hircus'} sister species; \textit{Macaca mulatta} as \textit{Chlorocebus sabaeus'} sister species and finally, we considered \textit{Pan troglodytes} as \textit{Homo sapiens'} sister species.
    The selection coefficient ($\Sphy$) of each substitution was then obtained by comparing the difference in amino acid fitnesses for each polarized non-synonymous codon substitution, by referring to the site-specific fitness profile obtained in the phylogeny-based method (see section~\ref{subsec:s-phylogeny-method}).
    Finally, the rate of non-synonymous over synonymous substitutions for a given class of selection coefficient ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$) was computed as:
    \begin{align}
        \begin{dcases}
            \dn \left( \Sphyclass \right) &= \dfrac{D\left( \Sphyclass \right)}{L \left( \Sphyclass \right)}, \\
            \ds &= \dfrac{D_{\text{syn}}}{L_{\text{syn}}},
        \end{dcases}\label{eq:dnds}
    \end{align}
    where $D \left( \Sphyclass \right) $ was the number of non-synonymous substitutions in class $\Sphyclass$, $D_{\text{syn}}$ was the number of synonymous substitutions across the genome, while $L \left( \Sphyclass \right)$ and $L_{\text{syn}}$ were the numbers of non-synonymous and synonymous mutational opportunities, respectively, as defined in section~\ref{subsec:nunber-of-sites}.
    $\delta(\dnds)$ was computed as the difference between $\dnds$ computed over all substitutions and $\dnds$ when we removed beneficial back-mutations $\dn (\Sphy < 1) / \ds$, normalized by $\dnds$.
    Note that the quantities $\delta(\dnds)$ and $\delta(\dn)$ are equivalent due to the simplification of the factor $\ds$:
    \begin{equation}
        \delta(\dnds) = \dfrac{\dnds - \dn(\Sphy < 1) / \ds}{\dnds} = \dfrac{\dn - \dn(\Sphy < 1)}{\dn} = \delta(\dn).\label{eq:delta-dnds}
    \end{equation}

    \subsection{Scaled selection coefficients ($\Spop$) in a population-based method}
    \label{subsec:s-polymorphism-method}
    To obtain a quantitative estimate of the distribution of selection coefficients for each category of SNPs, we used the polyDFE model~\cite{tataru_inference_2017, tataru_polydfe_2020}.
    This model uses the count of derived alleles to infer the distribution of fitness effects (DFE).
    The probability of sampling an allele at a given frequency (before fixation or extinction) is informative of its scaled selection coefficient at the population scale ($\Spop$).
    Therefore, pooled across many sites, the site-frequency spectrum (SFS) provides information on the underlying $\Spop$ of mutations.
    However, estimating a single $\Spop$ for all sampled mutations is biologically unrealistic, and a DFE of mutations is usually assumed~\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009}.
    The polyDFE\cite{tataru_inference_2017, tataru_polydfe_2020} software implements a mixture of a $\Gamma$ and exponential distributions to model the DFE of non-synonymous mutations, while synonymous mutations are considered neutral.
    The model estimates the parameters $\DelMean$, $b$, $p_b$ and $\AdvMean$ for non-synonymous mutations as:
    \begin{equation}
        \phi \left( \Spop; \DelMean , b, p_b, \AdvMean \right) =
        \begin{dcases}
            \left( 1 - p_b \right) f_{\Gamma}(-\Spop; -\DelMean, b) & \text{ if $\Spop \leq 0$,} \\
            p_b f_{e}(\Spop; \AdvMean) & \text{ if $\Spop > 0$,} \\
        \end{dcases}
    \end{equation}
    where $\DelMean \leq -1 $ is the estimated mean of the DFE for $\Spop \leq 0$;
    $b \geq 0.2$ is the estimated shape of the $\Gamma$ distribution;
    $0 \leq p_b \leq 1$ is the estimated probability that $\Spop > 0$;
    $\AdvMean \geq 1$ is the estimated mean of the DFE for $\Spop > 0$;
    and $f_{\Gamma}(\Spop; m, b)$ is the density of the $\Gamma$ distribution with mean $m$ and shape $b$, while $f_{e}(\Spop; m)$ is the density of the exponential distribution with mean $m$.

    PolyDFE requires one SFS for non-synonymous mutations and one for synonymous mutations (neutral expectation), as well as the number of sites on which each SFS was sampled.
    For populations containing more than $8$ individuals, the SFS was subsampled down to $16$ chromosomes ($8$ diploid individuals) without replacement (hyper-geometric distribution) to alleviate the effect of different sampling depths in the 28 populations.
    Altogether, for each class of selection ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$) of non-synonymous SNPs, we aggregated all the SNPs in the selection class $\Sphyclass$ as an SFS.
    The number of sites on which each SFS was sampled is given by $L(\Sphyclass)$ for the non-synonymous SFS and $L_{\text{syn}}$ for the synonymous SFS respectively.
    For each class of selection $\Sphyclass$, once fitted to the data using maximum likelihood with polyDFE, the parameters of the DFE $\left( \DelMean , b, p_b, \AdvMean \right)$ were used to compute $\proba [ \SpopDel \given  \Sphyclass] $, $\proba [ \SpopNeu \given \Sphyclass]$, and $\proba [ \SpopBen \given \Sphyclass]$ as:
    \begin{align}
        \proba [ \SpopDel \given  \Sphyclass] &= \proba [ \Spop < -1 \given \Sphyclass ] = \left( 1 - p_b \right) \int_{1}^{+\infty} f_{\Gamma}(\Spop; -\DelMean, b) \der \Spop, \label{eq:polyProbaDel} \\
        \proba [ \SpopNeu \given \Sphyclass] &= \proba [ -1 < \Spop < 1 \given \Sphyclass ] = p_b \int_{0}^{1} f_{e}(\Spop; \AdvMean) \der \Spop + \left( 1 - p_b \right) \int_{0}^{1} f_{\Gamma}(\Spop; -\DelMean, b) \der \Spop, \\
        \proba [ \SpopBen \given \Sphyclass] &= \proba [ \Spop > 1 \given \Sphyclass] = p_b \int_{1}^{+\infty} f_{e}(\Spop; \AdvMean) \der \Spop. \label{eq:polyProbaAdv}
    \end{align}

    \subsection{\textit{Precision} and \textit{recall}}
    \label{subsec:precisison_recall}
    For readability, we give here \textit{precision} and \textit{recall} for beneficial mutations ($\SphyBen$ and $\SpopBen$), but it can be obtained using the same derivation for the deleterious mutations ($\SphyDel$ and $\SpopDel$) and nearly-neutral mutations ($\SphyNeu$ and $\SpopNeu$).

    \textit{Precision} is the proportion of mutations correctly predicted as beneficial ($\proba [ \SpopBen \cap  \SphyBen]$) out of all predicted as beneficial back-mutations ($\proba [ \SphyBen]$), which can be written as a conditional probability:
    \begin{equation}
        \frac{\proba [ \SpopBen  \cap  \SphyBen]}{\proba [ \SphyBen]} = \proba [ \SpopBen  \given  \SphyBen].
        \label{eq:precision}
    \end{equation}
    Namely, \textit{precision} corresponds to the probability for a back-mutation ($\SphyBen$) to be effectively beneficial at the population level ($\SpopBen$).
    This probability, computed from eq.~\ref{eq:polyProbaAdv}, is obtained by restricting our analysis to SNPs that are predicted to be beneficial back-mutations (yellow fill for the category $\SphyBen$ in fig.~3D).

    \textit{Recall} is the proportion of mutations correctly predicted as beneficial ($\proba [ \SpopBen \cap  \SphyBen]$) out of all beneficial mutations ($\proba [ \SpopBen]$), which can be written as a conditional probability:
    \begin{equation}
        \frac{\proba [ \SpopBen \cap  \SphyBen]}{\proba [ \SpopBen]} = \proba [ \SphyBen  \given \SpopBen ].
    \end{equation}
    Namely, \textit{recall} corresponds to the probability for a beneficial mutation at the population level ($\SpopBen$) to be a beneficial back-mutation ($\SphyBen$).
    Using Bayes theorem, \textit{recall} can be re-written as:
    \begin{equation}
        \proba [\SphyBen \given \SpopBen] = \frac{\proba [\SpopBen \given \SphyBen] \times \proba[\SphyBen]}{\ProbaPopBen},
        \label{eq:bayes}
    \end{equation}
    where $\proba [\SpopBen \given \SphyBen]$ and $\proba [ \SphyBen ]$ can be calculated using equations~\ref{eq:precision} and~\ref{eq:proba-dfe-mutsel}, respectively, and $\proba [ \SpopBen ]$ is the probability of a mutation to be beneficial at the level of the population, which can be computed from the law of total probabilities as:
    \begin{equation}
        \proba [ \SpopBen ] = \sum_{\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \} }\proba [\SpopBen \given \Sphyclass ] \times \proba [\Sphyclass ].
        \label{eq:total_proba}
    \end{equation}

    \section{Beneficial mutations in the terminal lineages and populations}\label{sec:beneficial-mutations}

    \subsection{Mutation-selection codon models}
    \label{sec:site-specific-mutation-selection-codon-models}
    In BayesCode (\url{https://github.com/ThibaultLatrille/bayescode}), mutation-selection codon models are obtained by running \textit{mutselomega} for 2000 points of MCMC with the options:
    \begin{scriptsize}
        \begin{verbatim}
 mutselomega ---omegashift 0.0 --ncat 30 -a my_alignment.phy -t my_tree.newick -u 2000 my_genename
        \end{verbatim}
    \end{scriptsize}
    The collection of site-specific fitness profiles ($\UniDimArray{F^{(i)}}, \forall i$) are then obtained by running \textit{readmutselomega}, reading 1000 points of MCMC (first 1000 are considered as burn-in) with the options:
    \begin{scriptsize}
        \begin{verbatim}
 readmutselomega --every 1 --until 2000 --burnin 1000 --ss my_genename
        \end{verbatim}
    \end{scriptsize}
    The gene-specific $4 \times 4$ nucleotide mutation rate matrix ($\UniDimArray{\mu}$) is also obtained by running \textit{readmutselomega}, reading 1000 points of MCMC (first 1000 are considered as burn-in) with the options:
    \begin{scriptsize}
        \begin{verbatim}
 readmutselomega --every 1 --until 2000 --burnin 1000 --nuc my_genename
        \end{verbatim}
    \end{scriptsize}

    \subsection{Summary tables}\label{subsec:summary-table-mutsel}

    \subsubsection{$\dnds$ for deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial back-mutations ($\SphyBen$)}
    \begin{center}
        \captionof{table}{$\dnds$ for deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial back-mutations ($\SphyBen$).}
        \scriptsize
        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
            \toprule
            Population &             Species & Watterson's $\thetaSyn$  & $\proba_{div}[ \SphyBen ]$ & $\dnds $ & $\dn ( \SphyDel ) / \ds$ & $\dn ( \SphyNeu ) / \ds$ & $\dn ( \SphyBen ) / \ds$ \\
            \midrule
            \endhead
            \midrule
            \multicolumn{8}{r}{{Continued on next page}} \\
            \midrule
            \endfoot

            \bottomrule
            \endlastfoot
            \rowcolor{LIGHTGREY} Equus c. &      Equus caballus &               $ 0.002$ &                    $ 0.118$ &  $ 0.147$ &            $ 0.075$ &                $ 0.823$ &           $ 1.203$ \\
            Iran &          Bos taurus &               $ 0.002$ &                    $ 0.123$ &  $ 0.131$ &            $ 0.074$ &                $ 0.627$ &           $ 1.206$ \\
            Uganda &          Bos taurus &               $ 0.005$ &                    $ 0.125$ &  $ 0.134$ &            $ 0.075$ &                $ 0.637$ &           $ 1.252$ \\
            \rowcolor{LIGHTGREY} Australia &        Capra hircus &               $ 0.003$ &                    $ 0.121$ &  $ 0.125$ &            $ 0.068$ &                $ 0.629$ &           $ 1.099$ \\
            \rowcolor{LIGHTGREY} France &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.126$ &            $ 0.068$ &                $ 0.633$ &           $ 1.102$ \\
            \rowcolor{LIGHTGREY} Iran (C. aegagrus) &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.125$ &            $ 0.068$ &                $ 0.630$ &           $ 1.100$ \\
            \rowcolor{LIGHTGREY} Iran &        Capra hircus &               $ 0.004$ &                    $ 0.121$ &  $ 0.125$ &            $ 0.067$ &                $ 0.630$ &           $ 1.108$ \\
            \rowcolor{LIGHTGREY} Italy &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.126$ &            $ 0.068$ &                $ 0.634$ &           $ 1.102$ \\
            \rowcolor{LIGHTGREY} Morocco &        Capra hircus &               $ 0.004$ &                    $ 0.122$ &  $ 0.125$ &            $ 0.067$ &                $ 0.631$ &           $ 1.112$ \\
            Iran &          Ovis aries &               $ 0.007$ &                    $ 0.109$ &  $ 0.146$ &            $ 0.091$ &                $ 0.616$ &           $ 1.148$ \\
            Iran (O. orientalis) &          Ovis aries &               $ 0.009$ &                    $ 0.108$ &  $ 0.148$ &            $ 0.093$ &                $ 0.617$ &           $ 1.145$ \\
            Iran (O. vignei) &          Ovis aries &               $ 0.007$ &                    $ 0.109$ &  $ 0.146$ &            $ 0.091$ &                $ 0.617$ &           $ 1.134$ \\
            Various &          Ovis aries &               $ 0.008$ &                    $ 0.107$ &  $ 0.148$ &            $ 0.093$ &                $ 0.617$ &           $ 1.134$ \\
            Morocco &          Ovis aries &               $ 0.008$ &                    $ 0.108$ &  $ 0.148$ &            $ 0.093$ &                $ 0.619$ &           $ 1.149$ \\
            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus &               $ 0.004$ &                    $ 0.122$ &  $ 0.133$ &            $ 0.071$ &                $ 0.696$ &           $ 1.397$ \\
            \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.124$ &  $ 0.134$ &            $ 0.071$ &                $ 0.701$ &           $ 1.431$ \\
            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.124$ &  $ 0.134$ &            $ 0.071$ &                $ 0.699$ &           $ 1.422$ \\
            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.123$ &  $ 0.134$ &            $ 0.071$ &                $ 0.703$ &           $ 1.411$ \\
            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.123$ &  $ 0.134$ &            $ 0.071$ &                $ 0.699$ &           $ 1.419$ \\
            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus &               $ 0.003$ &                    $ 0.123$ &  $ 0.133$ &            $ 0.071$ &                $ 0.699$ &           $ 1.407$ \\
            \rowcolor{LIGHTGREY} South Africa  & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.125$ &  $ 0.134$ &            $ 0.070$ &                $ 0.704$ &           $ 1.447$ \\
            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &                    $ 0.123$ &  $ 0.133$ &            $ 0.070$ &                $ 0.699$ &           $ 1.413$ \\
            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.123$ &  $ 0.134$ &            $ 0.071$ &                $ 0.699$ &           $ 1.410$ \\
            African &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &            $ 0.118$ &                $ 0.865$ &           $ 1.609$ \\
            Admixed American &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &            $ 0.118$ &                $ 0.865$ &           $ 1.607$ \\
            East Asian &        Homo sapiens &               $ 0.002$ &                    $ 0.098$ &  $ 0.192$ &            $ 0.118$ &                $ 0.869$ &           $ 1.607$ \\
            European &        Homo sapiens &               $ 0.002$ &                    $ 0.098$ &  $ 0.192$ &            $ 0.118$ &                $ 0.865$ &           $ 1.598$ \\
            South Asian &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &            $ 0.118$ &                $ 0.867$ &           $ 1.610$ \\
        \end{longtable*}
    \end{center}
    \begin{itemize}
        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
        \item $\proba_{div}[\SphyBen]$ is the proportion of substitutions in the terminal branch that are $\SphyBen$.
        \item $\dn(\SphyDel) / \ds$ (eq.~\ref{eq:dnds}) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are $\SphyDel$.
        \item $\dn(\SphyNeu) / \ds$ (eq.~\ref{eq:dnds}) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are $\SphyNeu$.
        \item $\dn(\SphyBen) / \ds$ (eq.~\ref{eq:dnds}) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are $\SphyBen$.
    \end{itemize}

    \newpage

    \subsubsection{$\dnds$ over-estimation due to beneficial back-mutations}
    \begin{center}
        \captionof{table}{$\dnds$ over-estimation due to beneficial back-mutations.}
        \scriptsize
        \begin{longtable*}{|l|l|r|r|r|r|r|}
            \toprule
            Population & Species & Watterson's $\thetaSyn$ & $\proba_{div}[\Sphy > 1]$ & $\dnds $ & $\dn(\Sphy < 1) / \ds$ & $\delta(\dnds )$ \\
            \midrule
            \endhead
            \midrule
            \multicolumn{7}{r}{{Continued on next page}} \\
            \midrule
            \endfoot

            \bottomrule
            \endlastfoot
            \rowcolor{LIGHTGREY} Equus c. &      Equus caballus &               $ 0.002$ &                    $ 0.118$ &  $ 0.147$ &           $ 0.131$ &     $  10.5$ \\
            Iran &          Bos taurus &               $ 0.002$ &                    $ 0.123$ &  $ 0.131$ &           $ 0.117$ &     $  11.1$ \\
            Uganda &          Bos taurus &               $ 0.005$ &                    $ 0.125$ &  $ 0.134$ &           $ 0.118$ &     $  11.3$ \\
            \rowcolor{LIGHTGREY} Australia &        Capra hircus &               $ 0.003$ &                    $ 0.121$ &  $ 0.125$ &           $ 0.111$ &     $  10.8$ \\
            \rowcolor{LIGHTGREY} France &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.126$ &           $ 0.112$ &     $  10.8$ \\
            \rowcolor{LIGHTGREY} Iran (C. aegagrus) &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.125$ &           $ 0.111$ &     $  10.8$ \\
            \rowcolor{LIGHTGREY} Iran &        Capra hircus &               $ 0.004$ &                    $ 0.121$ &  $ 0.125$ &           $ 0.111$ &     $  10.9$ \\
            \rowcolor{LIGHTGREY} Italy &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.126$ &           $ 0.112$ &     $  10.8$ \\
            \rowcolor{LIGHTGREY} Morocco &        Capra hircus &               $ 0.004$ &                    $ 0.122$ &  $ 0.125$ &           $ 0.111$ &     $  11.0$ \\
            Iran &          Ovis aries &               $ 0.007$ &                    $ 0.109$ &  $ 0.146$ &           $ 0.132$ &     $ 9.671$ \\
            Iran (O. orientalis) &          Ovis aries &               $ 0.009$ &                    $ 0.108$ &  $ 0.148$ &           $ 0.134$ &     $ 9.516$ \\
            Iran (O. vignei) &          Ovis aries &               $ 0.007$ &                    $ 0.109$ &  $ 0.146$ &           $ 0.132$ &     $ 9.598$ \\
            Various &          Ovis aries &               $ 0.008$ &                    $ 0.107$ &  $ 0.148$ &           $ 0.134$ &     $ 9.439$ \\
            Morocco &          Ovis aries &               $ 0.008$ &                    $ 0.108$ &  $ 0.148$ &           $ 0.134$ &     $ 9.582$ \\
            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus &               $ 0.004$ &                    $ 0.122$ &  $ 0.133$ &           $ 0.118$ &     $  11.2$ \\
            \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.124$ &  $ 0.134$ &           $ 0.119$ &     $  11.3$ \\
            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.124$ &  $ 0.134$ &           $ 0.118$ &     $  11.3$ \\
            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.123$ &  $ 0.134$ &           $ 0.119$ &     $  11.2$ \\
            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.123$ &  $ 0.134$ &           $ 0.119$ &     $  11.3$ \\
            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus &               $ 0.003$ &                    $ 0.123$ &  $ 0.133$ &           $ 0.118$ &     $  11.3$ \\
            \rowcolor{LIGHTGREY} South Africa  & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.125$ &  $ 0.134$ &           $ 0.118$ &     $  11.5$ \\
            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &                    $ 0.123$ &  $ 0.133$ &           $ 0.118$ &     $  11.3$ \\
            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.123$ &  $ 0.134$ &           $ 0.119$ &     $  11.2$ \\
            African &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &           $ 0.175$ &     $ 8.799$ \\
            Admixed American &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &           $ 0.175$ &     $ 8.780$ \\
            East Asian &        Homo sapiens &               $ 0.002$ &                    $ 0.098$ &  $ 0.192$ &           $ 0.175$ &     $ 8.768$ \\
            European &        Homo sapiens &               $ 0.002$ &                    $ 0.098$ &  $ 0.192$ &           $ 0.175$ &     $ 8.728$ \\
            South Asian &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &           $ 0.175$ &     $ 8.788$ \\
        \end{longtable*}
    \end{center}
    \begin{itemize}
        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
        \item $\proba_{div}[\SphyBen]$ is the proportion of substitutions in the terminal branch that are $\SphyBen$.
        \item $\dnds$ (eq.~\ref{eq:dnds}) is the ratio of non-synonymous over synonymous substitutions estimated for all the non-synonymous substitutions in the terminal branch.
        \item $\dn(\Sphy < 1) / \ds$ (eq.~\ref{eq:dnds}) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are not $\SphyBen$.
        This is the estimated divergence when we removed beneficial back-mutations.
        \item $\delta(\dnds)$ (eq.~\ref{eq:delta-dnds}) is the fraction of the divergence ($\dnds$) that is over-estimated, $\dnds$ is compared to the estimated divergence when we removed beneficial back-mutations $\dn(\Sphy < 1) / \ds$.
    \end{itemize}
    We estimated that between 9 and 11\% of $\dnds$ is over-estimated, corresponding to beneficial back-mutation inflating the $\dnds$ statistic.

    \newpage

    \subsubsection{Probabilities of beneficial back-mutations}
    \begin{center}
        \captionof{table}{Probability of beneficial back-mutations among all beneficial ones.}
        \scriptsize
        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
            \toprule
            Population & Species & Watterson's $\thetaSyn$ & $\proba[\SphyBen]$ & $\proba [ \SpopBen ]$ & $\frac{\proba[\SphyBen]}{\proba[ \SpopBen ]}$ & $\proba [ \SpopBen \given \SphyBen]$ & $\proba[\SphyBen\given \SpopBen ]$ \\
            \midrule
            \endhead
            \midrule
            \multicolumn{8}{r}{{Continued on next page}} \\
            \midrule
            \endfoot

            \bottomrule
            \endlastfoot
            \rowcolor{LIGHTGREY} Equus c. &      Equus caballus &               $ 0.002$ &              $ 0.014$ &              $ 0.010$ &                                          $ 1.395$ &                         $ 0.580$ &                      $ 0.809$ \\
            Iran &          Bos taurus &               $ 0.002$ &              $ 0.013$ &              $ 0.041$ &                                          $ 0.323$ &                         $ 0.857$ &                      $ 0.277$ \\
            Uganda &          Bos taurus &               $ 0.005$ &              $ 0.013$ &              $ 0.013$ &                                          $ 0.991$ &                         $ 0.488$ &                      $ 0.483$ \\
            \rowcolor{LIGHTGREY} Australia &        Capra hircus &               $ 0.003$ &              $ 0.014$ &              $ 0.026$ &                                          $ 0.532$ &                         $ 0.368$ &                      $ 0.196$ \\
            \rowcolor{LIGHTGREY} France &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.572$ &                         $ 0.368$ &                      $ 0.211$ \\
            \rowcolor{LIGHTGREY} Iran (C. aegagrus) &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.026$ &                                          $ 0.516$ &                         $ 0.221$ &                      $ 0.114$ \\
            \rowcolor{LIGHTGREY} Iran &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.573$ &                         $ 0.368$ &                      $ 0.211$ \\
            \rowcolor{LIGHTGREY} Italy &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.017$ &                                          $ 0.814$ &                         $ 0.270$ &                      $ 0.220$ \\
            \rowcolor{LIGHTGREY} Morocco &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.018$ &                                          $ 0.751$ &                         $ 0.368$ &                      $ 0.276$ \\
            Iran &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.006$ &                                          $ 2.321$ &                         $ 0.169$ &                      $ 0.392$ \\
            Iran (O. orientalis) &          Ovis aries &               $ 0.009$ &              $ 0.014$ &              $ 0.012$ &                                          $ 1.178$ &                         $ 0.153$ &                      $ 0.180$ \\
            Iran (O. vignei) &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.020$ &                                          $ 0.683$ &                         $ 0.195$ &                      $ 0.133$ \\
            Various &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.012$ &                                          $ 1.201$ &                         $ 0.190$ &                      $ 0.228$ \\
            Morocco &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.005$ &                                          $ 2.589$ &                         $ 0.136$ &                      $ 0.353$ \\
            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.022$ &                                          $ 0.541$ &                         $ 0.565$ &                      $ 0.306$ \\
            \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.018$ &                                          $ 0.639$ &                         $ 0.429$ &                      $ 0.274$ \\
            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.022$ &                                          $ 0.516$ &                         $ 0.462$ &                      $ 0.239$ \\
            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.007$ &                                          $ 1.592$ &                         $ 0.486$ &                      $ 0.774$ \\
            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.023$ &                                          $ 0.508$ &                         $ 0.478$ &                      $ 0.243$ \\
            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus &               $ 0.003$ &              $ 0.012$ &              $ 0.015$ &                                          $ 0.762$ &                         $ 0.516$ &                      $ 0.393$ \\
            \rowcolor{LIGHTGREY} South Africa  & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.016$ &                                          $ 0.734$ &                         $ 0.490$ &                      $ 0.360$ \\
            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.016$ &                                          $ 0.713$ &                         $ 0.515$ &                      $ 0.367$ \\
            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.023$ &                                          $ 0.500$ &                         $ 0.499$ &                      $ 0.249$ \\
            African &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.025$ &                                          $ 0.470$ &                         $ 0.678$ &                      $ 0.319$ \\
            Admixed American &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.021$ &                                          $ 0.569$ &                         $ 0.635$ &                      $ 0.361$ \\
            East Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.031$ &                                          $ 0.381$ &                         $ 0.611$ &                      $ 0.233$ \\
            European &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.034$ &                                          $ 0.350$ &                         $ 0.619$ &                      $ 0.217$ \\
            South Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.033$ &                                          $ 0.354$ &                         $ 0.628$ &                      $ 0.222$ \\
        \end{longtable*}
    \end{center}
    \begin{itemize}
        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
        \item $\proba [ \SphyBen ]$ (eq.~\ref{eq:proba-dfe-mutsel}) is the probability for a new mutation a beneficial back-mutation.
        These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1, thus toward a more fit amino-acid.
        \item $\proba [ \SpopBen ]$ (eq.~\ref{eq:total_proba}) is the probability for a mutation to be beneficial.
        These mutations have a selection coefficient at the population-scale larger than 1.
        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~\ref{eq:polyProbaAdv}) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale (the \textit{precision}).
        \item $\proba [ \SphyBen \given \SpopBen]$ (eq.~\ref{eq:bayes}) is the probability for a mutation to a beneficial back-mutations, given it is beneficial (the \textit{recall}).
        This probability is obtained using Bayes' formula.
    \end{itemize}
    \newpage

    \subsection{Correlation with diversity}
    For each population, the proportion of beneficial ($\ProbaPopBen$), nearly-neutral ($\ProbaPopNeu$) and of deleterious ($\ProbaPopDel$) mutations estimated at the population-genetic scale is shown as function of Watterson's's diversity ($\thetaSyn$).

    \subsubsection{Proportion of nearly-neutral mutations ($\SpopNeu$)}\label{subsec:proportion-nearly-neutral-mutations}
    \captionof{figure}{~}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC-nodiv/regression-MutSel/results.watterson.all_P-Sweak.scatter.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC-nodiv/regression-MutSel/results.watterson.weak_P-Sweak.scatter.pdf}
    \end{minipage}
    \begin{itemize}
        \item $\ \proba [ \SpopNeu ]$ (eq.~\ref{eq:total_proba}) is the probability for a mutation to be nearly-neutral.
        These mutations have a selection coefficient at the population-scale between -1 and 1.
        \item $\ \proba [ \SpopNeu \given \SphyNeu ]$ (eq.~\ref{eq:polyProbaAdv}) is the probability for a mutation to be nearly-neutral at the population scale, given it is predicted to be a nearly-neutral at the phylogenetic scale.
    \end{itemize}

    We confirmed that higher synonymous diversity is typically accompanied by a smaller proportion of neutral mutations.
    This result is specially visible when we restricted the analysis to class of mutations that are supposedly nearly-neutral at the phylogenetic scale ($\SphyNeu$).
    This result suggests that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) are more likely to discriminate whether mutations are beneficial or deleterious.
    Alternatively stated, mutations in populations with low diversity (e.g.~\textit{Homo}) are effectively nearly-neutral and behave as would a neutral mutation.
    This result is qualitatively in accordance with the nearly-neutral theory of evolution which argues that mutations are less efficiently selected for in small populations.

    \subsubsection{Proportion of deleterious mutations ($\SpopDel$)}\label{subsec:proportion-deleterious-mutations}
    \captionof{figure}{~}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC-nodiv/regression-MutSel/results.watterson.all_P-Sneg.scatter.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC-nodiv/regression-MutSel/results.watterson.neg_P-Sneg.scatter.pdf}
    \end{minipage}
    \begin{itemize}
        \item $\ \proba [ \SpopDel ]$ (eq.~\ref{eq:total_proba}) is the probability for a mutation to be deleterious.
        These mutations have a selection coefficient at the population-scale lower than -1.
        \item $\ \proba [ \SpopDel \given \SphyDel ]$ (eq.~\ref{eq:polyProbaAdv}) is the probability for a mutation to be deleterious at the population scale, given it is predicted to be a deleterious at the phylogenetic scale.
    \end{itemize}

    \subsubsection{Proportion of beneficial mutations ($\SpopBen$)}\label{subsec:proportion-beneficial-mutations}
    \captionof{figure}{~}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC-nodiv/regression-MutSel/results.watterson.all_P-Spos.scatter.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC-nodiv/regression-MutSel/results.watterson.pos_P-Spos.scatter.pdf}
    \end{minipage}
    \begin{itemize}
        \item $\proba [ \SpopBen ]$ (eq.~\ref{eq:total_proba}) is the probability for a mutation to be beneficial.
        These mutations have a selection coefficient at the population-scale larger than 1.
        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~\ref{eq:polyProbaAdv}) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale (the \textit{precision}).
    \end{itemize}

    \newpage

    \section{Clinically related terms for mutations}

    \subsection{Terms associated with deleterious mutations $\SphyDel$}
    \begin{center}
        \captionof{table}{Terms associated with deleterious mutations $\SphyDel$}
        \begin{tabular}{|l|r|r|r|r|r|}
            \toprule
            SNP clinical ontology & $n_{\mathrm{Observed}}$ & $n_{\mathrm{Expected}}$ & Odds ratio & $p_{\mathrm{v}}$ & $p_{\mathrm{v-adjusted}}$ \\
            \midrule
            Benign                & 2969                    & $4043.0$                & $ 0.734$   & $ 1.000$             & $ 1.000~~$                    \\
            Likely benign         & 2994                    & $3399.8$                & $ 0.881$   & $ 0.999$             & $ 1.000~~$                    \\
            Risk factor           & 102                     & $ 118.2$                & $ 0.863$   & $ 0.798$             & $ 1.000~~$                    \\
            Likely pathogenic     & 221                     & $  68.5$                  & $ 3.226$   & $1.7\times 10^{-8}$  & $\bm{6.7\times 10^{-8}{^*}}$  \\
            Pathogenic            & 560                     & $ 193.6$                & $ 2.893$   & $4.2\times 10^{-17}$ & $\bm{2.1\times 10^{-16}{^*}}$ \\
            \bottomrule
        \end{tabular}
    \end{center}
    In humans, non-synonymous SNPs in the test group ($\SphyDel$) are contrasted to SNPs in the control group ($\SphyNeu$).
    For each clinical term, a 2x2 contingency tables is built by counting the number of SNPs based on their selection coefficient and their clinical terms (whether they have this specific term or not).
    Fisher's exact tests are then performed for these 2x2 contingency tables.
    $^*$ signify that the$p_{\mathrm{v}}^{\mathrm{adj}}$ corrected for multiple comparison (Holm–Bonferroni correction) is lower than the risk $\alpha=0.05$.
    SNPs predicted with $\SphyDel$ are statistically associated to clinical terms such as \textit{Likely Pathogenic} and \textit{Pathogenic}.

    \subsection{Terms associated with beneficial back-mutations $\SphyBen$}
    \begin{center}
        \captionof{table}{Terms associated with beneficial back-mutations $\SphyBen$}
        \begin{tabular}{|l|r|r|r|r|r|}
            \toprule
            SNP clinical ontology & $n_{\mathrm{Observed}}$ & $n_{\mathrm{Expected}}$ & Odds ratio & $p_{\mathrm{v}}$ & $p_{\mathrm{v-adjusted}}$ \\
            \midrule
            Benign                & 319                     & $ 261.7$                & $ 1.219$   & $ 0.002$         & $\bm{ 0.009{^*}}$         \\
            Likely benign         & 263                     & $ 222.7$                & $ 1.181$   & $ 0.012$         & $\bm{ 0.049{^*}}$         \\
            Risk factor           & 5                       & $ 7.847$                & $ 0.637$   & $ 0.879$         & $ 0.879~~$                \\
            Likely pathogenic     & 7                       & $ 4.552$                & $ 1.538$   & $ 0.227$         & $ 0.682~~$                \\
            Pathogenic            & 16                      & $  12.9$                  & $ 1.241$   & $ 0.268$         & $ 0.682~~$                \\
            \bottomrule
        \end{tabular}
    \end{center}
    In humans, non-synonymous SNPs in the test group ($\SphyBen$) are contrasted to SNPs in the control group ($\SphyNeu$).
    For each clinical term, a 2x2 contingency tables is built by counting the number of SNPs based on their selection coefficient and their clinical terms (whether they have this specific term or not).
    Fisher's exact tests are then performed for these 2x2 contingency tables.
    $^*$ signify that the$p_{\mathrm{v}}^{\mathrm{adj}}$ corrected for multiple comparison (Holm–Bonferroni correction) is lower than the risk $\alpha=0.05$.
    Beneficial back-mutations are associated with clinical terms such as \textit{Benign} and \textit{Likely Benign}.
    \newpage

    \section{Mutation-selection models: DFE and SFS for each population}\label{sec:mutation-selection-models:-histograms-and-sfs-for-each-population}
    For each population, the same figure is shown.
    \begin{itemize}
        \item Top-left panel: Distribution of fitness effects ($\Sphy$), predicted for all possible mutations away from the ancestral human genome.
        Mutations are divided into 5 classes of selection: severely deleterious (blue), deleterious (green), weakly deleterious (light green), weakly beneficial (yellow) and beneficial (red, supposedly beneficial back-mutations).
        \item Top-right panel: Distribution of scaled selection coefficients ($\Sphy$) for all observed substitutions along the terminal branch (after the split to the sister species).
        If there are fewer substitutions than expected, this class is thus undergoing purifying selection.
        \item Bottom-left panel: The site-frequency spectrum (SFS) represents the proportion of mutations (y-axis) with a given number of derived alleles in the population (x-axis).
        SFS are drawn for a random sample of 16 alleles (mean in solid line and standard deviation in filled color) for each class of selection coefficient and for synonymous mutations which are supposedly neutral (black).
        At high frequencies, supposedly severally deleterious mutations are underrepresented.
        \item Bottom-right panel:For each class of selection (and for the set of all non-synonymous mutations), information from the SFS and the expected total mutation rate are combined at the population-genetic scale to estimate the proportion of beneficial mutations $\ProbaPopBen$, of nearly-neutral mutations $\ProbaPopNeu$ and of deleterious mutations $\ProbaPopDel$.
    \end{itemize}

    \input{include-MutSel-non-adaptive}
    \newpage

    \section{Including divergence data for the estimation of $\Spop$}

    \subsection{Including divergence in polyDFE}
    Divergence data (number of substitutions per site) can also be included into polyDFE to estimate the DFE.
    For the class of a given class of selection coefficient ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$), the number of substitutions has already been computed and is given by $D\left( \Sphyclass \right)$ (see eq.~\ref{eq:dnds}), and the number of sites is given by $L \left( \Sphyclass \right)$ (see eq.~4).
    Otherwise, the procedure is the same as described section \textit{Scaled selection coefficients ($\Spop$) in a population-based method}.

    \subsection{Probabilities of beneficial back-mutations}
    \begin{center}
        \captionof{table}{Probability of beneficial back-mutations among all beneficial ones.}
        \scriptsize
        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
            \toprule
            Population & Species & Watterson's $\thetaSyn$ & $\proba[\SphyBen]$ & $\proba [ \SpopBen ]$ & $\frac{\proba[\SphyBen]}{\proba[ \SpopBen ]}$ & $\proba [ \SpopBen \given \SphyBen]$ & $\proba[\SphyBen\given \SpopBen ]$ \\
            \midrule
            \endhead
            \midrule
            \multicolumn{8}{r}{{Continued on next page}} \\
            \midrule
            \endfoot

            \bottomrule
            \endlastfoot
            \rowcolor{LIGHTGREY} Equus c. &      Equus caballus &               $ 0.002$ &              $ 0.014$ &              $ 0.061$ &                                          $ 0.235$ &                         $ 0.519$ &                      $ 0.122$ \\
            Iran &          Bos taurus &               $ 0.002$ &              $ 0.013$ &              $ 0.007$ &                                          $ 1.908$ &                         $ 0.368$ &                      $ 0.702$ \\
            Uganda &          Bos taurus &               $ 0.005$ &              $ 0.013$ &              $ 0.008$ &                                          $ 1.667$ &                         $ 0.255$ &                      $ 0.425$ \\
            \rowcolor{LIGHTGREY} Australia &        Capra hircus &               $ 0.003$ &              $ 0.014$ &              $ 0.007$ &                                          $ 2.099$ &                         $ 0.147$ &                      $ 0.308$ \\
            \rowcolor{LIGHTGREY} France &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.007$ &                                          $ 2.043$ &                         $ 0.149$ &                      $ 0.304$ \\
            \rowcolor{LIGHTGREY} Iran (C. aegagrus) &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.013$ &                                          $ 1.069$ &                         $ 0.147$ &                      $ 0.157$ \\
            \rowcolor{LIGHTGREY} Iran &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.008$ &                                          $ 1.699$ &                         $ 0.152$ &                      $ 0.258$ \\
            \rowcolor{LIGHTGREY} Italy &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.006$ &                                          $ 2.160$ &                         $ 0.147$ &                      $ 0.316$ \\
            \rowcolor{LIGHTGREY} Morocco &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.006$ &                                          $ 2.141$ &                         $ 0.186$ &                      $ 0.398$ \\
            Iran &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.012$ &                                          $ 1.210$ &                         $ 0.158$ &                      $ 0.191$ \\
            Iran (O. orientalis) &          Ovis aries &               $ 0.009$ &              $ 0.014$ &              $ 0.012$ &                                          $ 1.144$ &                         $ 0.157$ &                      $ 0.180$ \\
            Iran (O. vignei) &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.022$ &                                          $ 0.631$ &                         $ 0.186$ &                      $ 0.118$ \\
            Various &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.012$ &                                          $ 1.211$ &                         $ 0.156$ &                      $ 0.188$ \\
            Morocco &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.009$ &                                          $ 1.536$ &                         $ 0.190$ &                      $ 0.292$ \\
            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.005$ &                                          $ 2.230$ &                         $ 0.282$ &                      $ 0.630$ \\
            \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.014$ &                                          $ 0.849$ &                         $ 0.310$ &                      $ 0.263$ \\
            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.008$ &                                          $ 1.530$ &                         $ 0.298$ &                      $ 0.456$ \\
            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.008$ &                                          $ 1.384$ &                         $ 0.305$ &                      $ 0.422$ \\
            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.014$ &                                          $ 0.854$ &                         $ 0.296$ &                      $ 0.253$ \\
            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus &               $ 0.003$ &              $ 0.012$ &              $ 0.005$ &                                          $ 2.438$ &                         $ 0.285$ &                      $ 0.696$ \\
            \rowcolor{LIGHTGREY} South Africa  & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.011$ &                                          $ 1.047$ &                         $ 0.323$ &                      $ 0.338$ \\
            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.006$ &                                          $ 2.070$ &                         $ 0.292$ &                      $ 0.604$ \\
            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.014$ &                                          $ 0.816$ &                         $ 0.309$ &                      $ 0.252$ \\
            African &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.015$ &                                          $ 0.765$ &                         $ 0.371$ &                      $ 0.284$ \\
            Admixed American &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.009$ &                                          $ 1.259$ &                         $ 0.368$ &                      $ 0.464$ \\
            East Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.012$ &                                          $ 0.973$ &                         $ 0.369$ &                      $ 0.358$ \\
            European &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.009$ &                                          $ 1.356$ &                         $ 0.368$ &                      $ 0.499$ \\
            South Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.010$ &                                          $ 1.147$ &                         $ 0.369$ &                      $ 0.423$ \\
        \end{longtable*}
    \end{center}
    \begin{itemize}
        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
        \item $\proba [ \SphyBen ]$ (eq.~\ref{eq:proba-dfe-mutsel}) is the probability for a new mutation a beneficial back-mutation.
        These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1, thus toward a more fit amino-acid.
        \item $\proba [ \SpopBen ]$ (eq.~\ref{eq:total_proba}) is the probability for a mutation to be beneficial.
        These mutations have a selection coefficient at the population-scale larger than 1.
        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~\ref{eq:polyProbaAdv}) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale (the \textit{precision}).
        \item $\proba [ \SphyBen \given \SpopBen]$ (eq.~\ref{eq:bayes}) is the probability for a mutation to a beneficial back-mutations, given it is beneficial (the \textit{recall}).
        This probability is obtained using Bayes' formula.
    \end{itemize}
    \newpage

    \subsection{Precision and recall}
    \captionof{table}{Precision and recall}
    \begin{center}
        \begin{adjustbox}{width=\textwidth}
            \begin{tabular}{||l|l|r||r|r||r|r||r|r||}
                \toprule
                \multicolumn{3}{||c||}{} &
                \multicolumn{2}{c||}{\shortstack{\textbf{Deleterious mutations} \\ $\bm{\SpopDel \coloneqq \Spop<-1}$ \\ $\bm{\SphyDel \coloneqq \Sphy<-1}$}} &
                \multicolumn{2}{c||}{\shortstack{\textbf{Nearly-neutral mutations} \\ $\bm{\SpopNeu \coloneqq -1<\Spop<1}$ \\ $\bm{\SphyNeu \coloneqq -1<\Sphy<1}$}} &
                \multicolumn{2}{c||}{\shortstack{\textbf{Beneficial mutations} \\ $\bm{\SpopBen \coloneqq \Spop>1}$ \\ $\bm{\SphyBen \coloneqq \Sphy>1}$}}
                \\ \hline
                \textbf{Population} &
                \textbf{Species} &
                $\bm{\thetaSyn}$ &
                \makecell{\textbf{Precision} \\ $\bm{\proba [\SpopDel \given \SphyDel]}$} &
                \makecell{\textbf{Recall} \\ $\bm{\proba [\SphyDel \given \SpopDel]}$}           &
                \makecell{\textbf{Precision}      \\ $\bm{\proba [\SpopNeu \given \SphyNeu]}$}                                    &
                \makecell{\textbf{Recall}          \\ $\bm{\proba [\SphyNeu \given \SpopNeu]}$}                                  &
                \makecell{\textbf{Precision}          \\ $\bm{\proba [\SpopBen \given \SphyBen]}$}          &
                \makecell{\textbf{Recall}        \\ $\bm{\proba [\SphyBen \given \SpopBen]}$}
                \\   \midrule
                \rowcolor{LIGHTGREY} Equus c. & Equus caballus        & $ 0.002$ & $ 0.918$ & $ 0.957$ & $ 0.186$ & $ 0.213$ & $ 0.519$ & $ 0.122$ \\
                Iran               & Bos taurus        & $ 0.002$ & $ 0.924$ & $ 0.965$ & $ 0.565$ & $ 0.356$ & $ 0.368$ & $ 0.702$ \\
                Uganda              & Bos taurus        & $ 0.005$ & $ 0.943$ & $ 0.961$ & $ 0.516$ & $ 0.396$ & $ 0.255$ & $ 0.425$ \\
                \rowcolor{LIGHTGREY} Australia            & Capra hircus        & $ 0.003$ & $ 0.941$ & $ 0.964$ & $ 0.592$ & $ 0.434$ & $ 0.147$ & $ 0.308$ \\
                \rowcolor{LIGHTGREY} France                                    & Capra hircus          & $ 0.004$ & $ 0.940$ & $ 0.963$ & $ 0.571$ & $ 0.418$ & $ 0.149$ & $ 0.304$ \\
                \rowcolor{LIGHTGREY} Iran (C. aegagrus)                    & Capra hircus          & $ 0.004$ & $ 0.948$ & $ 0.960$ & $ 0.515$ & $ 0.446$ & $ 0.147$ & $ 0.157$ \\
                \rowcolor{LIGHTGREY} Iran                        & Capra hircus          & $ 0.004$ & $ 0.942$ & $ 0.961$ & $ 0.534$ & $ 0.410$ & $ 0.152$ & $ 0.258$ \\
                \rowcolor{LIGHTGREY} Italy                                 & Capra hircus          & $ 0.004$ & $ 0.940$ & $ 0.963$ & $ 0.579$ & $ 0.421$ & $ 0.147$ & $ 0.316$ \\
                \rowcolor{LIGHTGREY} Morocco                                 & Capra hircus          & $ 0.004$ & $ 0.939$ & $ 0.960$ & $ 0.549$ & $ 0.404$ & $ 0.186$ & $ 0.398$ \\
                Iran           & Ovis aries & $ 0.007$ & $ 0.957$ & $ 0.954$ & $ 0.412$ & $ 0.416$ & $ 0.158$ & $ 0.191$ \\
                Iran (O. orientalis)  & Ovis aries & $ 0.009$ & $ 0.961$ & $ 0.955$ & $ 0.413$ & $ 0.437$ & $ 0.157$ & $ 0.180$ \\
                Iran (O. vignei)           & Ovis aries & $ 0.007$ & $ 0.968$ & $ 0.951$ & $ 0.356$ & $ 0.516$ & $ 0.186$ & $ 0.118$ \\
                Various             & Ovis aries & $ 0.008$ & $ 0.958$ & $ 0.955$ & $ 0.428$ & $ 0.431$ & $ 0.156$ & $ 0.188$ \\
                Morocco              & Ovis aries & $ 0.008$ & $ 0.960$ & $ 0.953$ & $ 0.447$ & $ 0.460$ & $ 0.190$ & $ 0.292$ \\
                \rowcolor{LIGHTGREY} Barbados              & Chlorocebus sabaeus & $ 0.004$ & $ 0.931$ & $ 0.969$ & $ 0.628$ & $ 0.402$ & $ 0.282$ & $ 0.630$ \\
                \rowcolor{LIGHTGREY} Central Afr. Rep.       & Chlorocebus sabaeus & $ 0.006$ & $ 0.941$ & $ 0.964$ & $ 0.514$ & $ 0.408$ & $ 0.310$ & $ 0.263$ \\
                \rowcolor{LIGHTGREY} Ethiopia        & Chlorocebus sabaeus & $ 0.005$ & $ 0.933$ & $ 0.967$ & $ 0.586$ & $ 0.393$ & $ 0.298$ & $ 0.456$ \\
                \rowcolor{LIGHTGREY} Gambia             & Chlorocebus sabaeus & $ 0.005$ & $ 0.937$ & $ 0.967$ & $ 0.590$ & $ 0.414$ & $ 0.305$ & $ 0.422$ \\
                \rowcolor{LIGHTGREY} Kenya                                 & Chlorocebus sabaeus        & $ 0.005$ & $ 0.942$ & $ 0.965$ & $ 0.526$ & $ 0.418$ & $ 0.296$ & $ 0.253$ \\
                \rowcolor{LIGHTGREY} Nevis                        & Chlorocebus sabaeus        & $ 0.003$ & $ 0.930$ & $ 0.970$ & $ 0.637$ & $ 0.401$ & $ 0.285$ & $ 0.696$ \\
                \rowcolor{LIGHTGREY} South Africa                              & Chlorocebus sabaeus        & $ 0.006$ & $ 0.937$ & $ 0.964$ & $ 0.530$ & $ 0.393$ & $ 0.323$ & $ 0.338$ \\
                \rowcolor{LIGHTGREY} Saint Kitts                                & Chlorocebus sabaeus        & $ 0.004$ & $ 0.931$ & $ 0.969$ & $ 0.611$ & $ 0.393$ & $ 0.292$ & $ 0.604$ \\
                \rowcolor{LIGHTGREY} Zambia                             & Chlorocebus sabaeus        & $ 0.006$ & $ 0.941$ & $ 0.963$ & $ 0.506$ & $ 0.408$ & $ 0.309$ & $ 0.252$ \\
                African                             & Homo sapiens        & $ 0.002$ & $ 0.896$ & $ 0.968$ & $ 0.550$ & $ 0.297$ & $ 0.371$ & $ 0.284$ \\
                Admixed American                             & Homo sapiens        & $ 0.002$ & $ 0.890$ & $ 0.979$ & $ 0.710$ & $ 0.333$ & $ 0.368$ & $ 0.464$ \\
                East Asian                             & Homo sapiens        & $ 0.002$ & $ 0.890$ & $ 0.971$ & $ 0.578$ & $ 0.289$ & $ 0.369$ & $ 0.358$ \\
                European                             & Homo sapiens        & $ 0.002$ & $ 0.891$ & $ 0.980$ & $ 0.739$ & $ 0.345$ & $ 0.368$ & $ 0.499$ \\
                South Asian                             & Homo sapiens        & $ 0.002$ & $ 0.895$ & $ 0.981$ & $ 0.740$ & $ 0.356$ & $ 0.369$ & $ 0.423$ \\
                \bottomrule
            \end{tabular}
        \end{adjustbox}
    \end{center}
    \begin{itemize}
        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
        \item \textit{Precision} is the estimation of the selection coefficient at population scale ($\Spop$) given that $\Sphy$ is known.
        \item  \textit{recall} is the estimation of $\Sphy$ given selection coefficient at the population scale ($\Spop$) is known.
        \item \textit{Recall} for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is thus the proportion of beneficial back-mutations among all beneficial mutations.
    \end{itemize}

    \bibliography{codon_models_bibtex}
    \bibliographystyle{Science}

\end{document}

### 2023-05-02 copy_artworks.sh

@@ -1,26 +1,16 @@
 #!/usr/bin/env bash
-\cp -rf ./experiments/5bins-mC/results/Theta.MutSel.all.stacked.pdf ./manuscript/artworks/stacked.allSNPs.pdf
-\cp -rf ./experiments/5bins-mC/results/Theta.MutSel.pos-weak.stacked.pdf ./manuscript/artworks/stacked.weak-pos-SNPs.pdf
-\cp -rf ./experiments/5bins-mC/results/Theta.MutSel.neg-weak.stacked.pdf ./manuscript/artworks/stacked.weak-neg-SNPs.pdf
-\cp -rf ./experiments/5bins-mC/results/Theta.MutSel.P-Seq0.heatmap.pdf ./manuscript/artworks/heatmap.neutral.pdf
-\cp -rf ./experiments/5bins-mC/results/Theta.MutSel.P-Sinf0.heatmap.pdf ./manuscript/artworks/heatmap.neg.pdf
-\cp -rf ./experiments/5bins-mC/results/Theta.MutSel.P-Ssup0.heatmap.pdf ./manuscript/artworks/heatmap.pos.pdf
-\cp -rf ./experiments/5bins-mC/analysis/Homo_sapiens.AFR.MutSel-sfs.normalize.pdf ./manuscript/artworks/AFR.SFS.pdf
-\cp -rf ./experiments/5bins-mC/analysis/Homo_sapiens.AFR.MutSel.polyDFE_C.pdf ./manuscript/artworks/AFR.polyDFE.pdf
-\cp -rf ./data_processed/opportunities_bins5Mask0.9/DFE.Homo_sapiens.AFR.MutSel.pdf ./manuscript/artworks/AFR.histogramDFE.pdf
-\cp -rf ./data_processed/vcf_annotate_bins5Mask0.9/snps.Homo_sapiens.AFR.MutSel.histogram.pdf ./manuscript/artworks/AFR.histogramSNP.pdf
-\cp -rf ./data_processed/vcf_annotate_bins5Mask0.9/snps.Homo_sapiens.AFR.MutSel.histogram.full.pdf ./manuscript/artworks/AFR.histogramSNP.full.pdf
-\cp -rf ./data_processed/ancestral_bins5Mask0.9/Homo_sapiens.AFR.pdf ./manuscript/artworks/AFR.histogramDiv.pdf
[…]

### 2023-05-02 scripts/annotate_vcf.py

@@ -77,7 +77,7 @@ def read_vcf(vcf, sift_file, mask_grouped, subsample, anc_proba):
 def classify_snps(dico_snp, method, cat_snps):
     s_list = dico_snp[method]
     type_list = dico_snp["snp_type"]
-    sampled = dico_snp["snp_type"]
+    sampled = dico_snp["sampled"]
     cat_list, intervals, dico_cat = list(), list(), defaultdict(list)
 
     if cat_snps.bins > 10:

### 2023-05-02 scripts/libraries.py

@@ -487,11 +487,11 @@ class CategorySNP(list):
         else:
             assert method == "MutSel"
             if self.bins == 2:
-                self.inner_bound = [0]
+                self.inner_bound = [1]
                 self.dico = {
-                    "neg": P("$S_0 < 0$", RED, -np.float("infinity"), 0),
+                    "neg": P("$S_0 < 1$", RED, -np.float("infinity"), 1),
                     "syn": P("$Synonymous$", 'black', None, None),
-                    "pos": P("$S_0 >0$", BLUE, 0, np.float("infinity"))
+                    "pos": P("$S_0 > 1$", BLUE, 1, np.float("infinity"))
                 }
             elif self.bins == 3:
                 self.inner_bound = [-1, 1]

### 2023-05-02 scripts/parse_results_DFE.py

@@ -137,7 +137,6 @@ def alpha_model_D(p_list, s_list, lim_left=0.0):
     return sum([q for s, q in zip(s_list, q_linspace) if lim_left < s]) / sum(q_linspace)
 
 
-
 def main(args):
     os.makedirs(os.path.dirname(args.output), exist_ok=True)
     string = ''.join(open(args.postprocessing, "r").readlines())
@@ -155,14 +154,13 @@ def main(args):
             p_list = np.array([v for k, v in out.items() if "p(s=" in k])
             s_list = np.array([v for k, v in out.items() if "S_" in k])
             out_list = [f"p(s={s})={p}" for s, p in zip(s_list, p_list)]
-            if cat == "all":
-                print(f"{file} - {cat}:\n{out_list}")
+            print(f"{file} - {cat}:\n{out_list}")
             assert abs(sum(p_list) - 1.0) < 1e-4
             out["S+"] = sum([p * s for p, s in zip(p_list, s_list) if s > 0])
             out["S-"] = sum([p * s for p, s in zip(p_list, s_list) if s < 0])
             out["S"] = sum([p * s for p, s in zip(p_list, s_list)])
-            out[polydfe_cat_list[0]] = sum([p for p, s in zip(p_list, s_list) if s >= 1])
-            out[polydfe_cat_list[1]] = sum([p for p, s in zip(p_list, s_list) if -1 <= s < 1])
+            out[polydfe_cat_list[0]] = sum([p for p, s in zip(p_list, s_list) if s > 1])
+            out[polydfe_cat_list[1]] = sum([p for p, s in zip(p_list, s_list) if -1 <= s <= 1])
             out[polydfe_cat_list[2]] = sum([p for p, s in zip(p_list, s_list) if s < -1])
             out["p_b"] = sum([p for p, s in zip(p_list, s_list) if s >= 0])
             for lim_left in alpha_sup_limits:

### 2023-05-02 scripts/plot_heatmap.py

@@ -15,7 +15,7 @@ def plot_stack_param(list_pops, df_all, pop_colors, title, output):
     fig, ax = plt.subplots(figsize=(1920 / my_dpi, 780 / my_dpi), dpi=my_dpi)
     x_pos = range(len(list_pops))
     hatches_list = ['', '', '//']
-    colors_list = ["black", "silver", "white"]
+    colors_list = [LIGHTYELLOW_RGB, "silver", "white"]
     edgecolors_list = ["black", "black", "black"]
     bottom = np.array([0.0] * len(list_pops))
     for p_i, param in enumerate(polydfe_cat_dico):

### 2023-05-02 scripts/plot_regression.py

@@ -43,7 +43,7 @@ def discard_col(col, df):
 def generate_xy_plot(cat_snps):
     pr = "\\mathbb{P}"
     xy_dico = defaultdict(list)
-    dico_label = {'pop': "Population", "species": "Species", "watterson": "Watterson $\\theta_W$",
+    dico_label = {'pop': "Population", "species": "Species", "watterson": "Watterson $\\theta_S$",
                   "proba": "$\\mathbb{P}$", "logL": "logL"}
 
     y_dico = {"tajima": "Tajima $\\theta_{\\pi}$ ",
@@ -52,6 +52,7 @@ def generate_xy_plot(cat_snps):
               "betaS_ratio": "Slope of $\\overline{S}(\\overline{S_0})$ at $\\overline{S_0}=0$",
               "fay_wu": "Fay and Wu $\\theta_{H}$", "D_tajima": "Tajima's $D$", "H_fay_wu": "Fay and Wu's $H$"}
     y_dico.update({f'all_{cat_poly}': v for cat_poly, v in polydfe_cat_dico.items()})
+    y_dico.update({f'mut_sum_{cat_poly}': v for cat_poly, v in polydfe_cat_dico.items()})
 
     for cat_S0 in cat_snps.non_syn_list + ['all']:
         s0 = ""
@@ -86,7 +87,6 @@ def generate_xy_plot(cat_snps):
         for cat_beta in cat_snps.non_syn_list + ['all']:
             s = cat_snps.label(cat_beta).replace('S_0', 'S').replace("$", "")
             y_dico[f'bayes_{cat_S0}_P-{cat_beta}'] = f"{pr}[{s} {given_s0}]$"
-
     for y, y_label in y_dico.items():
         xy_dico["x"].append("watterson")
         xy_dico["y"].append(y)
@@ -112,10 +112,6 @@ def generate_xy_plot(cat_snps):
 
 def column_format(size):
     return "|" + "|".join(["l"] * 2 + ["r"] * (size - 2)) + "|"
-
-
-def logit(x):
-    return np.log(x / (1 - x))
 
 
 def main(args):
@@ -187,10 +183,6 @@ def main(args):
             if discard_col(col_y, df):
                 continue
             x, y = df[col_x], df[col_y]
-            if 'P-' in col_y and ("ratio" not in col_y) and ("bayes" not in col_y):
-                y = logit(y)
[…]

### 2023-05-02 scripts/plot_sfs.py

@@ -35,9 +35,12 @@ def plot_sfs(cat_snps, snp_sfs, normed_sfs_syn_mean, max_daf, daf_axis, output, 
 
         mean_sfs = np.mean(sfs, axis=0)
         std_sfs = np.std(sfs, axis=0)
-        plt.scatter(daf_axis, mean_sfs, color=cat_snps.color(cat))
-        plt.plot(daf_axis, mean_sfs, label=cat_snps.label(cat), color=cat_snps.color(cat), linewidth=1.0)
-        plt.fill_between(daf_axis, mean_sfs - std_sfs, mean_sfs + std_sfs, linewidth=1.0,
+        # Filter out daf=0 and non-finite values
+        f_sfs = ((mean_sfs > 0) & np.isfinite(mean_sfs))
+        plt.scatter(daf_axis[f_sfs], mean_sfs[f_sfs], color=cat_snps.color(cat), s=1.0)
+        plt.plot(daf_axis[f_sfs], mean_sfs[f_sfs], label=cat_snps.label(cat), color=cat_snps.color(cat), linewidth=1.0)
+        if len(sfs) > 1:
+            plt.fill_between(daf_axis, mean_sfs - std_sfs, mean_sfs + std_sfs, linewidth=1.0,
                          color=cat_snps.color(cat), alpha=0.2)
     if max_daf < 32:
         ax.xaxis.set_major_locator(plt.MultipleLocator(1))
@@ -116,7 +119,7 @@ def main(args):
     for theta_method in sfs_weight:
         theta_dict[theta_method].append(theta(sfs_nonsyn_mean[1:] / ldn, max_daf, theta_method))
 
-    daf_axis = range(1, max_daf)
+    daf_axis = np.array(range(1, max_daf))
     for cat, mean_sfs in snp_sfs_mean.items():
         if cat == "syn":
             ld_cat = lds

### 2023-05-02 scripts/tex_sfs.py

@@ -47,15 +47,16 @@ def main(args):
             for pop, sfs in nested_dict_2.items():
                 if len(nested_dict_2) > 1:
                     o.write("\\subsubsection{" + sample_dico[format_pop(pop)] + "} \n \n")
-                hist_suffix = f"{sp}.{pop}.{method}.histogram.pdf".replace(' ', '_')
-                hist_path = f"{args.hist_prefix}{hist_suffix}"
+
                 dfe_suffix = f"{sp}.{pop}.{method}.pdf".replace(' ', '_')
                 dfe_path = f"{args.dfe_prefix}{dfe_suffix}"
-
                 o.write(minipage(0.49, dfe_path))
+
+                hist_suffix = f"{sp}.{pop}.pdf".replace(' ', '_')
+                hist_path = f"{args.hist_prefix}{hist_suffix}"
                 o.write(minipage(0.49, hist_path))
                 o.write("\\\\ \n")
-                o.write(minipage(0.49, sfs.replace(".pdf", ".pdf")))
+                o.write(minipage(0.49, sfs.replace(".pdf", ".normalize.pdf")))
                 for model in ["C", "D"]:
                     polyDFE = sfs.replace("-sfs.pdf", f".polyDFE_{model}.pdf")
                     if os.path.exists(polyDFE):

### 2023-05-03 manuscript/main.tex
Added artworks. Updated manuscript.

@@
 {Latrille}$^{1\dag}$\orcidlink{0000-0002-9643-4668}, J.
-{Joseph}$^{2\dag}$, D.~A.
+{Joseph}$^{2\dag}$\orcidlink{0009-0002-1312-9930}, D.~A.
 {Hartasánchez}$^{1}$\orcidlink{0000-0003-2596-6883}, N.
@@
 
-    Theoretically, we can thus use large-scale genomic data to assess whether the fitnesses estimated at the phylogenetic scale predict the fitness effect at the population scale for both deleterious and beneficial back-mutations.
+    Theoretically, we can thus use large-scale genomic data to assess whether the fitness estimated at the phylogenetic scale predict the fitness effect at the population scale for both deleterious and beneficial back-mutations.
     The placental mammals represent an excellent study system to perform such analysis.
-    Having originated $\sim$100 million years ago~\cite{kumar_timetree_2017}, they diversified quickly.
+    Having originated $\sim$102 million years ago, they diversified quickly~\cite{foley_genomic_2023}.
     Additionally, polymorphism data are available for many species~\cite{howe_ensembl_2021}, as are high quality protein-coding DNA alignments across the genome~\cite{ranwez_orthomam_2007, scornavacca_orthomam_2019}.
-    By restricting our analysis to protein-coding orthologous genes, we focus on genes under functional constrains across mammals.
+    By performing our analysis on 14,509 protein-coding orthologous genes across 87 species, we focus on sequences under functional constraints across mammals.
     For each gene, fitting the mutation-selection model to the multi-species sequence alignment, assuming that the underlying fitness landscape is stable along the phylogenetic tree, allows us to obtain relative fitnesses for all amino acids for each site of the alignment (fig.~\ref{fig:method}A).
@@
             Selection coefficients at the phylogenetic and population scales.
-            At the phylogenetic scale (A), we estimated the amino-acid Wrightian fitness for each site from protein-coding DNA alignments using mutation-selection codon models.
+            At the phylogenetic scale (A), we estimated the amino-acid fitness for each site from protein-coding DNA alignments using mutation-selection codon models.
             For every possible mutation, the difference in amino acid fitness before and after the mutation allows us to compute the selection coefficient at the phylogenetic scale ($\Sphy$).
             Depending on $\Sphy$ (B) mutations can be predicted as deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) or beneficial back-mutations ($\SphyBen$) toward a fitter amino acid and repairing existing functions.
-            Substitutions along the terminal branch are classified depending on their $\Sphy$ value (C).
-            At the population scale, each observed single nucleotide polymorphism (SNP) segregating in the population can also be classified according to its $\Sphy$ value.
-            Occurence and frequency in the population of non-synonymous and synonymous (deemed neutral) polymorphisms (D-E) is used to estimate selection coefficients at the population scale ($\Spop$), for each class of selection ($\SphyDel$, $\SphyNeu$, $\SphyBen$).
+            At the population scale, each observed single nucleotide polymorphism (SNP) segregating in the population can also be classified according to its $\Sphy$ value (C).
+            Occurrence and frequency in the population of non-synonymous polymorphisms, contrasted to synonymous polymorphisms (deemed neutral) is used to estimate selection coefficients (D-E) at the population scale ($\Spop$), for each class of selection ($\SphyDel$, $\SphyNeu$, $\SphyBen$).
             We can thus assess whether $\Sphy$ predicts $\Spop$ and compute \textit{precision} (F) and \textit{recall} (G) for each class.
@@
     Hence, we calculated the $\dnds$ ratio of non-synonymous over synonymous divergence for all terminal lineages, focusing on the non-synonymous changes predicted as beneficial back-mutations ($\dn(\SphyBen) / \ds$).
-    We obtained values between 1.10 and 1.61 in the different lineages (table~S1), implying that $\SphyBen$ mutations reached fixation more frequently than synonymous mutations that are supposed to be neutral, implying that these back-mutations are effectively beneficial.
+    We obtained values between 1.10 and 1.61 in the different lineages (table~S1), implying i) that $\SphyBen$ mutations reached fixation more frequently than synonymous mutations that are supposed to be neutral, and ii) that these back-mutations are effectively beneficial.
 
@@
     By discarding all beneficial back-mutations we can obtain an estimate of $\dnds$ which is not inflated.
-    By comparing these two ways of calculating $\dnds$ (see section~\ref{subsec:substitution-mapping-in-the-terminal-branch} in Materials \& Methods), we calculated that beneficial back-mutations inflate $\dnds$ values by between 9 and 11\% across genera while only representing between 1.2 and 1.4\% of non-synonymous mutations (table~S2-3 and fig.~\ref{fig:homo-afr-results}A for humans).
+    By comparing these two ways of calculating $\dnds$ (see section~\ref{subsec:substitution-mapping-in-the-terminal-branch} in Materials \& Methods), we calculated that beneficial back-mutations inflate $\dnds$ values by between 9 and 11\% across genera while only representing between 1.2 and 1.4\% of non-synonymous mutations (tables~S2-3 and fig.~\ref{fig:homo-afr-results}A for humans).
 
@@
     Second, we assessed whether our calculated $\Sphy$ values are also indicative of the selective forces exerted at the population level.
-    So, we retrieved single nucleotide polymorphisms (SNPs) segregating in 28 mammalian populations.
+    We retrieved single nucleotide polymorphisms (SNPs) segregating in 28 mammalian populations.
     To determine if SNPs were ancestral of derived, we reconstructed the ancestral genome of each population.
@@
 
-    In humans, some SNPs have been associated with specific clinical prognosis terms~\cite{landrum_clinvar_2018} obtained by clinical evaluation of the impact of variants on human Mendelian disorders~\cite{landrum_clinvar_2018}.
+    In humans, some SNPs have been associated with specific clinical prognosis terms obtained by clinical evaluation of the impact of variants on human Mendelian disorders~\cite{landrum_clinvar_2018}.
     Thus, they provide an orthogonal estimate of the effect of a mutation on human health, allowing us to evaluate whether this effect follows its predicted fitness effect.
     Therefore, we investigated whether the non-synonymous SNPs classified as $\SphyDel$ or $\SphyBen$ showed enrichment in specific clinical terms compared to SNPs classified as $\SphyNeu$.
-    Our results show that SNPs predicted as deleterious are associated with clinical terms such as \textit{Likely Pathogenic} and \textit{Pathogenic}, implying that, in general, the selective pressure of a mutation exerted across mammals is also predictive of its clinical effect in humans (table~S4).
+    Our results show that SNPs predicted as deleterious are associated with clinical terms such as \textit{Likely Pathogenic} and \textit{Pathogenic}, implying that, in general, the selective pressure of a mutation exerted across mammals is also predictive of its clinical effect in humans (table~S4)~\cite{sullivan_leveraging_2023}.
     Conversely, back-mutations are associated with clinical terms such as \textit{Benign} and \textit{Likely Benign}, which shows that back-mutations are less likely to be functionally damaging (table~S5).
@@
     Higher synonymous diversity was associated with a smaller proportion of nearly-neutral mutations (fig.~\ref{fig:diversity}A).
-    This result follows the prediction of the nearly-neutral theory and suggests that in populations with higher diversity (e.g.,~\textit{Bos} or \textit{Ovis}), discrimination between beneficial and deleterious mutations is more likely to occur (figs.~S1-S9).
+    This result follows the prediction of the nearly-neutral theory and suggests that in populations with higher diversity (e.g.,~\textit{Bos} or \textit{Ovis}), discrimination between beneficial and deleterious mutations is more likely to occur (figs.~S1-S6).
     Conversely, many more mutations are effectively neutral in populations with lower diversity (e.g.,~\textit{Homo}).
@@
     These amino-acid fitness landscapes allow us to predict any mutation’s selection coefficient ($\Sphy$) along a protein-coding sequence.
-    We can compare these selective effects to observations at the population level.
+    We can compare these selective effects to observations at the population level (figs.~S1-3).
     By doing so, we confirmed that mutations predicted to be deleterious ($\SphyDel \coloneqq \Sphy < -1$) are purified away in extant populations.
@@
     Moreover, a mutation inferred as nearly-neutral at the phylogenetic scale ($\SphyNeu$) but positively selected at the population scale ($\SpopBen$) will also be considered a missed prediction, even if this discrepancy could just be due to a population size expansion~\cite{lanfear_population_2014, jones_shifting_2017, platt_protein_2018}.
-    Given this inflation of missed predictions, we consider our estimated proportion of adaptive mutations among beneficial ones to be an overestimation.
-    Therefore, our estimation of beneficial back-mutations among advantageous ones should be taken as a lower bound.
+    Given this inflation of missed predictions, our estimated proportion of adaptive mutations among beneficial ones is likely to be an overestimation.
+    In practice, advantageous mutations can be depleted in the $\SphyNeu$ and $\SphyDel$ class in some species but pervasive in others, depending on the model used to infer the DFE at the population scale (tables~S6-9).
+    It appears that our estimation can be quite sensitive to model misspecification and overall, while we provide an order of magnitude for the contribution of beneficial back-mutations to positive selection, further methodological development on the estimation of the distribution of fitness effects is needed to increase the confidence on this value.
 
@@
     \label{sec:acknowledgment}
-    We gratefully acknowledge the help of Mélodie Bastian, Nicolas Lartillot, Carina Farah Mugal, Laurent Duret and Nicolas Gambardella for their advice and reviews concerning this manuscript.
+    We gratefully acknowledge the help of Mélodie Bastian, Nicolas Lartillot, Carina Farah Mugal, Laurent Duret, Alexandre Reymond, Daniele Silvestro and Nicolas Gambardella for their advice and reviews concerning this manuscript.
     This work was performed using the computing facilities of the CC LBBE/PRABI\@.
@@
     OrthoMaM contains a total of $116$ mammalian reference sequences in v10c~\cite{ranwez_orthomam_2007, douzery_orthomam_2014, scornavacca_orthomam_2019}.
+
     Genes located on the X and Y chromosomes and on the mitochondrial genome were discarded from the analysis because the level of polymorphism –~which is necessary for population-based analyses~– is expected to be different in these three regions compared to the autosomal genome.
@@
     \label{subsec:s-phylogeny-method}
+
     We analyzed the phylogenetic-level data using mutation-selection models.
@@
     The probability of fixation depends on the difference between the scaled fitness of the amino acid encoded by the mutated codon ($F_b^{(i)}$) and the amino acid encoded by the original codon ($F_a^{(i)}$) at site $i$~\cite{wright_evolution_1931, fisher_genetical_1930}.
+
     The rate of substitution from codon $a$ to $b$ at a site $i$ is thus:
@@
     \end{equation}
-    Fitting the mutation-selection model on a multi-species sequence alignment leads to an estimation of the $4 \times 4$ nucleotide mutation rate matrix ($\UniDimArray{\mu}$) as well as the $20$ amino-acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$.
+
+    Fitting the mutation-selection model on a multi-species sequence alignment leads to an estimation of the gene-wide $4 \times 4$ nucleotide mutation rate matrix ($\UniDimArray{\mu}$) as well as the $20$ amino-acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$.
     The selection coefficient for a mutation from codon $a$ to codon $b$ at site $i$ is defined as:
@@
     This conversion from genomic position to alignment position was only possible when the assembly used for SNP-calling was the same as the one used in the OrthoMaM alignment, the GTF annotations, and the FASTA sequences.
-    SNPs were polarized using the three closest outgroups found in the OrthoMaM alignment with est-usfs v2.04~\cite{keightley_inferring_2018}, and SNPs with a derived probability lower than 0.99 were discarded (1\% of false positive).
+    SNPs were polarized using the three closest outgroups found in the OrthoMaM alignment with est-usfs v2.04~\cite{keightley_inferring_2018}, and alleles with a probability of being derived lower than 0.99 were discarded.
 
@@
     So, for each population, we used the polarized SNPs to reconstruct the ancestral DNA sequence, containing only substitutions and no segregating polymorphisms.
-    If an SNP was still segregating in the population, we used its ancestral version.
+    If a SNP was still segregating in the population, we used its ancestral version.
 
-    From the reconstructed ancestral genome at the base of the population genealogy, all possible mutations were computed, weighted by the instantaneous rate of change between nucleotides obtained from the mutation rate matrix ($\UniDimArray{\mu}$, see section~\ref{subsec:s-phylogeny-method}), summing to $\mu_{\text{tot}}$ across the whole genome, and to $\mu_{\text{syn}}$ when restricted to synonymous mutations.
+    From the reconstructed ancestral genome, all possible mutations were computed, weighted by the instantaneous rate of change between nucleotides obtained from the mutation rate matrix ($\UniDimArray{\mu}$, see section~\ref{subsec:s-phylogeny-method}), summing to $\mu_{\text{tot}}$ across the whole genome, and to $\mu_{\text{syn}}$ when restricted to synonymous mutations.
     Finally, the mutational opportunities for synonymous mutations were computed as the total number of sites across the genome ($L_{\text{tot}}$) weighted by the proportion of synonymous mutations among all possible mutations as:
+
     \begin{equation}
-        L_{\text{syn}} = L_{\text{tot}} \frac{\mu_{\text{syn}}}{\mu_{\text{tot}}}.
+        L_{\text{syn}} = L_{\text{tot}} \frac{\mu_{\text{syn}}}{\mu_{\text{tot}}}.\label{eq:mutation-opp}
     \end{equation}
@@
 
-    \subsection{Substitution mapping in the terminal branch}
+    \subsection{Substitution mapping and $\dnds$ in the terminal branch}
     \label{subsec:substitution-mapping-in-the-terminal-branch}
@@
     \label{subsec:s-polymorphism-method}
+
     To obtain a quantitative estimate of the distribution of selection coefficients for each category of SNPs, we used the polyDFE model~\cite{tataru_inference_2017, tataru_polydfe_2020}.
@@
     The model estimates the parameters $\DelMean$, $b$, $p_b$ and $\AdvMean$ for non-synonymous mutations as:
+
     \begin{equation}
@@
     \end{equation}
+
     where $\DelMean \leq -1 $ is the estimated mean of the DFE for $\Spop \leq 0$;
@@
     For each class of selection $\Sphyclass$, once fitted to the data using maximum likelihood with polyDFE, the parameters of the DFE $\left( \DelMean , b, p_b, \AdvMean \right)$ were used to compute $\proba [ \SpopDel \given  \Sphyclass] $, $\proba [ \SpopNeu \given \Sphyclass]$, and $\proba [ \SpopBen \given \Sphyclass]$ as:
+
     \begin{align}
@@
     \textit{Precision} is the proportion of mutations correctly predicted as beneficial ($\proba [ \SpopBen \cap  \SphyBen]$) out of all predicted as beneficial back-mutations ($\proba [ \SphyBen]$), which can be written as a conditional probability:
+
     \begin{equation}
@@
     \end{equation}
+
     where $\proba [\SpopBen \given \SphyBen]$ and $\proba [ \SphyBen ]$ can be calculated using equations~\ref{eq:precision} and~\ref{eq:proba-dfe-mutsel}, respectively, and $\proba [ \SpopBen ]$ is the probability of a mutation to be beneficial at the level of the population, which can be computed from the law of total probabilities as:
+
     \begin{equation}

### 2023-05-03 manuscript/scifile.tex
Added artworks. Updated manuscript.

@@
 \section*{Introduction}
-Adaptation is one of the main processes shaping the diversity of forms and functions across the tree of life~\cite{darwin_origin_1859}.
+Adaptation is one of the main processes shaping the diversity of forms and functions across the tree of life.
 Evolutionary adaptation is tightly linked to environmental change and species responding to this change~\cite{merrell_adaptive_1994, gavrilets_adaptive_2009}.
@@
 
-Theoretically, we can thus use large-scale genomic data to assess whether the fitnesses estimated at the phylogenetic scale predict the fitness effect at the population scale for both deleterious and beneficial back-mutations.
+Theoretically, we can thus use large-scale genomic data to assess whether the fitness estimated at the phylogenetic scale predict the fitness effect at the population scale for both deleterious and beneficial back-mutations.
 The placental mammals represent an excellent study system to perform such analysis.
-Having originated $\sim$100 million years ago~\cite{kumar_timetree_2017}, they diversified quickly.
-Additionally, polymorphism data are available for many species~\cite{howe_ensembl_2021}, as are high quality protein-coding DNA alignments across the genome~\cite{ranwez_orthomam_2007, scornavacca_orthomam_2019}.
-By restricting our analysis to protein-coding orthologous genes, we focus on genes under functional constrains across mammals.
+Having originated $\sim$102 million years ago, they diversified quickly~\cite{foley_genomic_2023}.
+Additionally, polymorphism data are available for many species~\cite{howe_ensembl_2021}, as are high quality protein-coding DNA alignments across the genome~\cite{scornavacca_orthomam_2019}.
+By performing our analysis on 14,509 protein-coding orthologous genes across 87 species, we focus on sequences under functional constraints across mammals.
 For each gene, fitting the mutation-selection model to the multi-species sequence alignment, assuming that the underlying fitness landscape is stable along the phylogenetic tree, allows us to obtain relative fitnesses for all amino acids for each site of the alignment (fig.~\ref{fig:method}A).
@@
         Selection coefficients at the phylogenetic and population scales.
-        At the phylogenetic scale (A), we estimated the amino-acid Wrightian fitness for each site from protein-coding DNA alignments using mutation-selection codon models.
+        At the phylogenetic scale (A), we estimated the amino-acid fitness for each site from protein-coding DNA alignments using mutation-selection codon models.
         For every possible mutation, the difference in amino acid fitness before and after the mutation allows us to compute the selection coefficient at the phylogenetic scale ($\Sphy$).
         Depending on $\Sphy$ (B) mutations can be predicted as deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) or beneficial back-mutations ($\SphyBen$) toward a fitter amino acid and repairing existing functions.
-        Substitutions along the terminal branch are classified depending on their $\Sphy$ value (C).
-        At the population scale, each observed single nucleotide polymorphism (SNP) segregating in the population can also be classified according to its $\Sphy$ value.
-        Occurence and frequency in the population of non-synonymous and synonymous (deemed neutral) polymorphisms (D-E) is used to estimate selection coefficients at the population scale ($\Spop$), for each class of selection ($\SphyDel$, $\SphyNeu$, $\SphyBen$).
+        At the population scale, each observed single nucleotide polymorphism (SNP) segregating in the population can also be classified according to its $\Sphy$ value (C).
+        Occurrence and frequency in the population of non-synonymous polymorphisms, contrasted to synonymous polymorphisms (deemed neutral) is used to estimate selection coefficients (D-E) at the population scale ($\Spop$), for each class of selection ($\SphyDel$, $\SphyNeu$, $\SphyBen$).
         We can thus assess whether $\Sphy$ predicts $\Spop$ and compute \textit{precision} (F) and \textit{recall} (G) for each class.
@@
 Hence, we calculated the $\dnds$ ratio of non-synonymous over synonymous divergence for all terminal lineages, focusing on the non-synonymous changes predicted as beneficial back-mutations ($\dn(\SphyBen) / \ds$).
-We obtained values between 1.10 and 1.61 in the different lineages (table~S1), implying that $\SphyBen$ mutations reached fixation more frequently than synonymous mutations that are supposed to be neutral, implying that these back-mutations are effectively beneficial.
+We obtained values between 1.10 and 1.61 in the different lineages (table~S1), implying i) that $\SphyBen$ mutations reached fixation more frequently than synonymous mutations that are supposed to be neutral, and ii) that these back-mutations are effectively beneficial.
 
@@
 By discarding all beneficial back-mutations we can obtain an estimate of $\dnds$ which is not inflated.
-By comparing these two ways of calculating $\dnds$ (see section~1.5 in Materials \& Methods), we calculated that beneficial back-mutations inflate $\dnds$ values by between 9 and 11\% across genera while only representing between 1.2 and 1.4\% of non-synonymous mutations (table~S2-3 and fig.~\ref{fig:homo-afr-results}A for humans).
+By comparing these two ways of calculating $\dnds$ (see section~1.5 in Materials \& Methods), we calculated that beneficial back-mutations inflate $\dnds$ values by between 9 and 11\% across genera while only representing between 1.2 and 1.4\% of non-synonymous mutations (tables~S2-3 and fig.~\ref{fig:homo-afr-results}A for humans).
 
@@
 Second, we assessed whether our calculated $\Sphy$ values are also indicative of the selective forces exerted at the population level.
-So, we retrieved single nucleotide polymorphisms (SNPs) segregating in 28 mammalian populations.
+We retrieved single nucleotide polymorphisms (SNPs) segregating in 28 mammalian populations.
 To determine if SNPs were ancestral of derived, we reconstructed the ancestral genome of each population.
@@
 
-In humans, some SNPs have been associated with specific clinical prognosis terms~\cite{landrum_clinvar_2018} obtained by clinical evaluation of the impact of variants on human Mendelian disorders~\cite{landrum_clinvar_2018}.
+In humans, some SNPs have been associated with specific clinical prognosis terms obtained by clinical evaluation of the impact of variants on human Mendelian disorders~\cite{landrum_clinvar_2018}.
 Thus, they provide an orthogonal estimate of the effect of a mutation on human health, allowing us to evaluate whether this effect follows its predicted fitness effect.
 Therefore, we investigated whether the non-synonymous SNPs classified as $\SphyDel$ or $\SphyBen$ showed enrichment in specific clinical terms compared to SNPs classified as $\SphyNeu$.
-Our results show that SNPs predicted as deleterious are associated with clinical terms such as \textit{Likely Pathogenic} and \textit{Pathogenic}, implying that, in general, the selective pressure of a mutation exerted across mammals is also predictive of its clinical effect in humans (table~S4).
+Our results show that SNPs predicted as deleterious are associated with clinical terms such as \textit{Likely Pathogenic} and \textit{Pathogenic}, implying that, in general, the selective pressure of a mutation exerted across mammals is also predictive of its clinical effect in humans (table~S4)~\cite{sullivan_leveraging_2023}.
 Conversely, back-mutations are associated with clinical terms such as \textit{Benign} and \textit{Likely Benign}, which shows that back-mutations are less likely to be functionally damaging (table~S5).
@@
 Higher synonymous diversity was associated with a smaller proportion of nearly-neutral mutations (fig.~\ref{fig:diversity}A).
-This result follows the prediction of the nearly-neutral theory and suggests that in populations with higher diversity (e.g.,~\textit{Bos} or \textit{Ovis}), discrimination between beneficial and deleterious mutations is more likely to occur (figs.~S1-S9).
+This result follows the prediction of the nearly-neutral theory and suggests that in populations with higher diversity (e.g.,~\textit{Bos} or \textit{Ovis}), discrimination between beneficial and deleterious mutations is more likely to occur (figs.~S1-S6).
 Conversely, many more mutations are effectively neutral in populations with lower diversity (e.g.,~\textit{Homo}).
@@
 These amino-acid fitness landscapes allow us to predict any mutation’s selection coefficient ($\Sphy$) along a protein-coding sequence.
-We can compare these selective effects to observations at the population level.
+We can compare these selective effects to observations at the population level (figs.~S1-3).
 By doing so, we confirmed that mutations predicted to be deleterious ($\SphyDel \coloneqq \Sphy < -1$) are purified away in extant populations.
@@
 Moreover, a mutation inferred as nearly-neutral at the phylogenetic scale ($\SphyNeu$) but positively selected at the population scale ($\SpopBen$) will also be considered a missed prediction, even if this discrepancy could just be due to a population size expansion~\cite{lanfear_population_2014, jones_shifting_2017, platt_protein_2018}.
-Given this inflation of missed predictions, we consider our estimated proportion of adaptive mutations among beneficial ones to be an overestimation.
-Therefore, our estimation of beneficial back-mutations among advantageous ones should be taken as a lower bound.
+Given this inflation of missed predictions, our estimated proportion of adaptive mutations among beneficial ones is likely to be an overestimation.
+In practice, advantageous mutations can be depleted in the $\SphyNeu$ and $\SphyDel$ class in some species but pervasive in others, depending on the model used to infer the DFE at the population scale (tables~S6-9).
+It appears that our estimation can be quite sensitive to model misspecification and overall, while we provide an order of magnitude for the contribution of beneficial back-mutations to positive selection, further methodological development on the estimation of the distribution of fitness effects is needed to increase the confidence on this value.
 
@@
 \label{sec:acknowledgment}
-We gratefully acknowledge the help of Mélodie Bastian, Nicolas Lartillot, Carina Farah Mugal, Laurent Duret and Nicolas Gambardella for their advice and reviews concerning this manuscript.
+We gratefully acknowledge the help of Mélodie Bastian, Nicolas Lartillot, Carina Farah Mugal, Laurent Duret, Alexandre Reymond, Daniele Silvestro and Nicolas Gambardella for their advice and reviews concerning this manuscript.
 This work was performed using the computing facilities of the CC LBBE/PRABI\@.
@@
 The data underlying this article are available at \url{https://doi.org/10.5281/zenodo.7878954}.
-Snakemake pipeline, analysis scripts and documentation are available at \href{https://github.com/ThibaultLatrille/SelCoeff}{github.com/ThibaultLatrille/SelCoeff}.
+Snakemake pipeline, analysis scripts and documentation are available at \url{https://github.com/ThibaultLatrille/SelCoeff}.
 
@@
 Materials and Methods\\
+Eqs. S1 to S15\\
 Supplementary Text\\
-Figs. S1 to S16\\
-Tables S1 to S3\\
+Figs. S1 to S6\\
+Tables S1 to S9\\
 References \textit{(S1-S19)}

### 2023-05-03 manuscript/scifile_SI.tex
Added artworks. Updated manuscript.

@@
 \usepackage{graphicx}
+\usepackage{orcidlink}
 \pdfinclusioncopyfonts=1
@@
 \author
-{T. {Latrille}$^{1\dag\ast}$, J. {Joseph}$^{2\dag}$, D.~A. {Hartasánchez}$^{1}$, N. {Salamin}$^{1}$\\
+{T.
+{Latrille}$^{1\dag}$\orcidlink{0000-0002-9643-4668}, J.
+{Joseph}$^{2\dag}$\orcidlink{0009-0002-1312-9930}, D.~A.
+{Hartasánchez}$^{1}$\orcidlink{0000-0003-2596-6883}, N.
+{Salamin}$^{1}$\orcidlink{0000-0002-3963-4954}\\
 \\
@@
     \label{sec:site-specific-mutation-selection-codon-models}
-    In BayesCode (\url{https://github.com/ThibaultLatrille/bayescode}), mutation-selection codon models are obtained by running \textit{mutselomega} for 2000 points of MCMC with the options:
+    In \textit{BayesCode} (\url{https://github.com/ThibaultLatrille/bayescode}), we ran the mutation-selection codon models \textit{mutselomega} for 2000 points of MCMC with the options:
     \begin{scriptsize}
@@
         This is the estimated divergence when we removed beneficial back-mutations.
-        \item $\delta(\dnds)$ (eq.~\ref{eq:delta-dnds}) is the fraction of the divergence ($\dnds$) that is over-estimated, $\dnds$ is compared to the estimated divergence when we removed beneficial back-mutations $\dn(\Sphy < 1) / \ds$.
+        \item $\delta(\dnds)$ (eq.~7) is the fraction of the divergence ($\dnds$) that is over-estimated, $\dnds$ is compared to the estimated divergence when we removed beneficial back-mutations $\dn(\Sphy < 1) / \ds$.
     \end{itemize}
@@
         \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item $\proba [ \SphyBen ]$ (eq.~\ref{eq:proba-dfe-mutsel}) is the probability for a new mutation a beneficial back-mutation.
+        \item $\proba [ \SphyBen ]$ (eq.~\ref{eq:proba-dfe-mutsel}) is the probability for a new mutation to be a beneficial back-mutation.
         These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1, thus toward a more fit amino-acid.
@@
         \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~\ref{eq:polyProbaAdv}) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale (the \textit{precision}).
-        \item $\proba [ \SphyBen \given \SpopBen]$ (eq.~\ref{eq:bayes}) is the probability for a mutation to a beneficial back-mutations, given it is beneficial (the \textit{recall}).
+        \item $\proba [ \SphyBen \given \SpopBen]$ (eq.~\ref{eq:bayes}) is the probability for a mutation to a beneficial back-mutations, given it is beneficial at the population scale (the \textit{recall}).
         This probability is obtained using Bayes' formula.
@@
 
+    \subsection{Replicability across mammals}
+    The proportion of deleterious ($\ProbaPopDel$), nearly-neutral ($\ProbaPopNeu$) and of beneficial ($\ProbaPopBen$) mutations estimated at the population-genetic scale across the different populations is shown for each class of selection ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$).
+
+    \captionof{figure}{Estimation of selection at the population scale for $\SphyDel$ mutations}
+    \begin{minipage}{0.9\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/Theta.neg.stacked.pdf}
+    \end{minipage}
+    \begin{minipage}{0.09\linewidth}
+        \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
+    \end{minipage}
+
+    \captionof{figure}{Estimation of selection at the population scale for $\SphyNeu$ mutations}
+    \begin{minipage}{0.9\linewidth}
+        \includegraphics[width=\linewidth, page=1]{artworks/Theta.weak.stacked.pdf}
+    \end{minipage}
+    \begin{minipage}{0.09\linewidth}
+        \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
+    \end{minipage}
+
+    \newpage
+    \captionof{figure}{Estimation of selection at the population scale for $\SphyBen$ mutations}
+    \begin{minipage}{0.9\linewidth}
+        \includegraphics[width=\linewidth, page=1]{artworks/Theta.pos.stacked.pdf}
+    \end{minipage}
+    \begin{minipage}{0.09\linewidth}
+        \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
+    \end{minipage}
+
     \subsection{Correlation with diversity}
-    For each population, the proportion of beneficial ($\ProbaPopBen$), nearly-neutral ($\ProbaPopNeu$) and of deleterious ($\ProbaPopDel$) mutations estimated at the population-genetic scale is shown as function of Watterson's's diversity ($\thetaSyn$).
+    For each population, the proportion of deleterious ($\ProbaPopDel$), nearly-neutral ($\ProbaPopNeu$) and of beneficial ($\ProbaPopBen$) mutations estimated at the population-genetic scale is shown as function of Watterson's's diversity ($\thetaSyn$).
+
+    \subsubsection{Proportion of deleterious mutations ($\SpopDel$)}\label{subsec:proportion-deleterious-mutations}
+    \captionof{figure}{Proportion of deleterious mutations ($\SpopDel$)}
+    \begin{minipage}{0.49\linewidth}
+        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.all_P-Sneg.scatter.pdf}
+    \end{minipage}
+    \begin{minipage}{0.49\linewidth}
+        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.neg_P-Sneg.scatter.pdf}
+    \end{minipage}
+    \begin{itemize}
+        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
+        \item $\proba [ \SpopDel ]$ (computed as eq.~\ref{eq:total_proba} but for $\SpopDel$)  is the probability for a mutation to be deleterious.
+        These mutations have a selection coefficient at the population-scale lower than -1.
+        \item $\proba [ \SpopDel \given \SphyDel ]$ computed as eq.~\ref{eq:polyProbaAdv} but for $\SpopDel$ and $\SphyDel$) is the probability for a mutation to be deleterious at the population scale, given it is predicted to be a deleterious at the phylogenetic scale.
+    \end{itemize}
+
+    We can see that higher synonymous diversity ($\thetaSyn$) is typically accompanied by a higher proportion of effectively deleterious mutations at the population scale ($\proba [ \SpopDel ]$).
+    This trend is also confirmed when we restricted the analysis to class of mutations that are supposedly deleterious at the phylogenetic scale ($\SphyDel$).
+    This result is qualitatively in accordance with the nearly-neutral theory of evolution which argues that very slightly deleterious mutations are more efficiently purified in large populations.
 
     \subsubsection{Proportion of nearly-neutral mutations ($\SpopNeu$)}\label{subsec:proportion-nearly-neutral-mutations}
-    \captionof{figure}{~}
+    \captionof{figure}{Proportion of nearly-neutral mutations ($\SpopNeu$)}
     \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC-nodiv/regression-MutSel/results.watterson.all_P-Sweak.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.all_P-Sweak.scatter.pdf}
     \end{minipage}
     \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC-nodiv/regression-MutSel/results.watterson.weak_P-Sweak.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.weak_P-Sweak.scatter.pdf}
     \end{minipage}
     \begin{itemize}
-        \item $\ \proba [ \SpopNeu ]$ (eq.~\ref{eq:total_proba}) is the probability for a mutation to be nearly-neutral.
+        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
+        \item $\proba [ \SpopNeu ]$ (computed as eq.~\ref{eq:total_proba} but for $\SpopNeu$) is the probability for a mutation to be nearly-neutral.
         These mutations have a selection coefficient at the population-scale between -1 and 1.
-        \item $\ \proba [ \SpopNeu \given \SphyNeu ]$ (eq.~\ref{eq:polyProbaAdv}) is the probability for a mutation to be nearly-neutral at the population scale, given it is predicted to be a nearly-neutral at the phylogenetic scale.
+        \item $\proba [ \SpopNeu \given \SphyNeu ]$ (computed as eq.~\ref{eq:polyProbaAdv} but for $\SpopNeu$ and $\SphyNeu$) is the probability for a mutation to be nearly-neutral at the population scale, given it is predicted to be a nearly-neutral at the phylogenetic scale.
     \end{itemize}
 
-    We confirmed that higher synonymous diversity is typically accompanied by a smaller proportion of neutral mutations.
-    This result is specially visible when we restricted the analysis to class of mutations that are supposedly nearly-neutral at the phylogenetic scale ($\SphyNeu$).
+    We confirmed that higher synonymous diversity ($\thetaSyn$) is typically accompanied by a smaller proportion of neutral mutations at the population scale ($\proba [ \SpopNeu ]$ in the range 0.06-0.18).
+    This result is more pronounced ($\proba [ \SpopNeu \given \SphyNeu ]$ in the range 0.36-0.73) when we restricted the analysis to class of mutations that are supposedly nearly-neutral at the phylogenetic scale ($\SphyNeu$).
     This result suggests that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) are more likely to discriminate whether mutations are beneficial or deleterious.
@@
 
-    \subsubsection{Proportion of deleterious mutations ($\SpopDel$)}\label{subsec:proportion-deleterious-mutations}
-    \captionof{figure}{~}
+    \subsubsection{Proportion of beneficial mutations ($\SpopBen$)}\label{subsec:proportion-beneficial-mutations}
+    \captionof{figure}{Proportion of beneficial mutations ($\SpopBen$)}
     \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC-nodiv/regression-MutSel/results.watterson.all_P-Sneg.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.all_P-Spos.scatter.pdf}
     \end{minipage}
     \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC-nodiv/regression-MutSel/results.watterson.neg_P-Sneg.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.pos_P-Spos.scatter.pdf}
     \end{minipage}
     \begin{itemize}
-        \item $\ \proba [ \SpopDel ]$ (eq.~\ref{eq:total_proba}) is the probability for a mutation to be deleterious.
-        These mutations have a selection coefficient at the population-scale lower than -1.
-        \item $\ \proba [ \SpopDel \given \SphyDel ]$ (eq.~\ref{eq:polyProbaAdv}) is the probability for a mutation to be deleterious at the population scale, given it is predicted to be a deleterious at the phylogenetic scale.
-    \end{itemize}
-
-    \subsubsection{Proportion of beneficial mutations ($\SpopBen$)}\label{subsec:proportion-beneficial-mutations}
-    \captionof{figure}{~}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC-nodiv/regression-MutSel/results.watterson.all_P-Spos.scatter.pdf}
-    \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC-nodiv/regression-MutSel/results.watterson.pos_P-Spos.scatter.pdf}
-    \end{minipage}
-    \begin{itemize}
+        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
         \item $\proba [ \SpopBen ]$ (eq.~\ref{eq:total_proba}) is the probability for a mutation to be beneficial.
@@
     \end{itemize}
+    Higher synonymous diversity ($\thetaSyn$) is accompanied by a smaller proportion of beneficial mutations at the population scale ($\proba [ \SpopBen ]$).
+    This trend is also confirmed when we restricted the analysis to class of mutations that are supposedly beneficial back-mutations at the phylogenetic scale ($\SphyBen$).
+    This result is much more difficult to interpret.
+    The fraction of beneficial back mutations is supposed to depend on long term demographic history, which is not directly accessible.
+    If the long term effective population size is relatively similar to the short term one, we expect little opportunity for beneficial back-mutations.
+    And thus, counter-intuitively we expect a diminution of positively selected mutations.
+    However, we can see that the proportion of beneficial back-mutations among advantageous one does not decrease with synonymous diversity.
+    This means that somehow adaptive mutations also decrease with synonymous diversity for a reason we fail to explain.
 
@@
     \section{Clinically related terms for mutations}
-
     \subsection{Terms associated with deleterious mutations $\SphyDel$}
@@
     Fisher's exact tests are then performed for these 2x2 contingency tables.
-    $^*$ signify that the$p_{\mathrm{v}}^{\mathrm{adj}}$ corrected for multiple comparison (Holm–Bonferroni correction) is lower than the risk $\alpha=0.05$.
+    $^*$ for $p_{\mathrm{v}}^{\mathrm{adj}}$ corrected for multiple comparison (Holm–Bonferroni correction) lower than the risk $\alpha=0.05$.
     SNPs predicted with $\SphyDel$ are statistically associated to clinical terms such as \textit{Likely Pathogenic} and \textit{Pathogenic}.
@@
     Fisher's exact tests are then performed for these 2x2 contingency tables.
-    $^*$ signify that the$p_{\mathrm{v}}^{\mathrm{adj}}$ corrected for multiple comparison (Holm–Bonferroni correction) is lower than the risk $\alpha=0.05$.
+    $^*$ for $p_{\mathrm{v}}^{\mathrm{adj}}$ corrected for multiple comparison (Holm–Bonferroni correction) lower than the risk $\alpha=0.05$.
     Beneficial back-mutations are associated with clinical terms such as \textit{Benign} and \textit{Likely Benign}.
-    \newpage
-
-    \section{Mutation-selection models: DFE and SFS for each population}\label{sec:mutation-selection-models:-histograms-and-sfs-for-each-population}
-    For each population, the same figure is shown.
-    \begin{itemize}
-        \item Top-left panel: Distribution of fitness effects ($\Sphy$), predicted for all possible mutations away from the ancestral human genome.
-        Mutations are divided into 5 classes of selection: severely deleterious (blue), deleterious (green), weakly deleterious (light green), weakly beneficial (yellow) and beneficial (red, supposedly beneficial back-mutations).
-        \item Top-right panel: Distribution of scaled selection coefficients ($\Sphy$) for all observed substitutions along the terminal branch (after the split to the sister species).
-        If there are fewer substitutions than expected, this class is thus undergoing purifying selection.
-        \item Bottom-left panel: The site-frequency spectrum (SFS) represents the proportion of mutations (y-axis) with a given number of derived alleles in the population (x-axis).
-        SFS are drawn for a random sample of 16 alleles (mean in solid line and standard deviation in filled color) for each class of selection coefficient and for synonymous mutations which are supposedly neutral (black).
-        At high frequencies, supposedly severally deleterious mutations are underrepresented.
-        \item Bottom-right panel:For each class of selection (and for the set of all non-synonymous mutations), information from the SFS and the expected total mutation rate are combined at the population-genetic scale to estimate the proportion of beneficial mutations $\ProbaPopBen$, of nearly-neutral mutations $\ProbaPopNeu$ and of deleterious mutations $\ProbaPopDel$.
-    \end{itemize}
-
-    \input{include-MutSel-non-adaptive}
     \newpage
@@
     Divergence data (number of substitutions per site) can also be included into polyDFE to estimate the DFE.
-    For the class of a given class of selection coefficient ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$), the number of substitutions has already been computed and is given by $D\left( \Sphyclass \right)$ (see eq.~\ref{eq:dnds}), and the number of sites is given by $L \left( \Sphyclass \right)$ (see eq.~4).
+    For the class of a given class of selection coefficient ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$), the number of substitutions has already been computed and is given by $D\left( \Sphyclass \right)$ (see eq.~\ref{eq:dnds}), and the number of sites is given by $L \left( \Sphyclass \right)$ (see eq.~\ref{eq:mutation-opp}).
     Otherwise, the procedure is the same as described section \textit{Scaled selection coefficients ($\Spop$) in a population-based method}.
@@
         \item \textit{Precision} is the estimation of the selection coefficient at population scale ($\Spop$) given that $\Sphy$ is known.
-        \item  \textit{recall} is the estimation of $\Sphy$ given selection coefficient at the population scale ($\Spop$) is known.
+        \item  \textit{Recall} is the estimation of $\Sphy$ given selection coefficient at the population scale ($\Spop$) is known.
         \item \textit{Recall} for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is thus the proportion of beneficial back-mutations among all beneficial mutations.
     \end{itemize}
+
+    Altogether, comparing this table to tables 1 and S3, we acknowledge that the exact proportion of beneficial back-mutations among all beneficial ones is different whether we included or not substitutions in the terminal lineage for the estimation of $\Spop$.
+    However, we can still see that beneficial back-mutations are positively selected compared to neutral and deleterious ones, and this result is not sensitive to inclusion of substitutions in the terminal lineage.
+
+    \newpage
+    \section{Discrete distribution of $\Spop$ at the population scale}
+
+    \subsection{polyDFE model D (discrete distribution)}
+    With polyDFE model D, the DFE of non-synonymous mutations is given as a discrete DFE of $K$ categories (instead of a continuous distribution in model C), where the selection coefficients of each category $i$ ($1 \leq i \leq K$) are fixed parameters $\Spop_i$, and each value $\Spop_i$ has a probability $p_i$ (estimated), with $\sum_{i=1}^{K} p_i =1$.
+    We used $K=6$ with $\Spop_1 = -500$, $\Spop_2 = -4$, $\Spop_3 =-1$, $\Spop_4 = 0$, $\Spop_5 = 1$, $\Spop_6 = 4$.\\
+    For each class of selection $\Sphyclass$, the parameters $p_i$ ($i \in \{ 1 \leq i \leq 6 \}$) were used to compute $\proba [ \SpopDel \given  \Sphyclass] $, $\proba [ \SpopNeu \given \Sphyclass]$, and $\proba [ \SpopBen \given \Sphyclass]$ as:
+    \begin{align}
+        \proba [ \SpopDel \given  \Sphyclass] &= \proba [ \Spop < -1 \given \Sphyclass ] = p_1 + p_2 \label{eq:polyProbaDel-mD} \\
+        \proba [ \SpopNeu \given \Sphyclass] &= \proba [ -1 < \Spop < 1 \given \Sphyclass ] = p_3 + p_4 + p_5,  \\
+        \proba [ \SpopBen \given \Sphyclass] &= p_6. \label{eq:polyProbaAdv-mD}
+    \end{align}
+
+    \subsection{Probabilities of beneficial back-mutations}
+    \begin{center}
+        \captionof{table}{Probability of beneficial back-mutations among all beneficial ones.}
+        \scriptsize
+        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
+            \toprule
+            Population & Species & Watterson's $\thetaSyn$ & $\proba[\SphyBen]$ & $\proba [ \SpopBen ]$ & $\frac{\proba[\SphyBen]}{\proba[ \SpopBen ]}$ & $\proba [ \SpopBen \given \SphyBen]$ & $\proba[\SphyBen\given \SpopBen ]$ \\
+            \midrule
+            \endhead
+            \midrule
+            \multicolumn{8}{r}{{Continued on next page}} \\
+            \midrule
+            \endfoot
+
+            \bottomrule
+            \endlastfoot
+            \rowcolor{LIGHTGREY} Equus c.
+&      Equus caballus &               $ 0.002$ &              $ 0.014$ &              $ 0.006$ &                                          $ 2.230$ &                         $ 0.141$ &                      $ 0.316$ \\
+            Iran &          Bos taurus &               $ 0.002$ &              $ 0.013$ &              $ 0.006$ &                                          $ 2.200$ &                         $ 0.136$ &                      $ 0.298$ \\
+            Uganda &          Bos taurus &               $ 0.005$ &              $ 0.013$ &              $ 0.011$ &                                          $ 1.177$ &                         $ 0.138$ &                      $ 0.162$ \\
+            \rowcolor{LIGHTGREY} Australia &        Capra hircus &               $ 0.003$ &              $ 0.014$ &              $ 0.002$ &                                          $ 6.467$ &                         $ 0.135$ &                      $ 0.871$ \\
+            \rowcolor{LIGHTGREY} France &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.002$ &                                          $ 6.407$ &                         $ 0.132$ &                      $ 0.845$ \\
+            \rowcolor{LIGHTGREY} Iran (C.
+aegagrus) &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.002$ &                                          $ 5.993$ &                         $ 0.129$ &                      $ 0.772$ \\
+            \rowcolor{LIGHTGREY} Iran &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.004$ &                                          $ 3.656$ &                         $ 0.138$ &                      $ 0.506$ \\
+            \rowcolor{LIGHTGREY} Italy &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.002$ &                                          $ 6.216$ &                         $ 0.127$ &                      $ 0.787$ \\
+            \rowcolor{LIGHTGREY} Morocco &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.002$ &                                          $ 6.019$ &                         $ 0.141$ &                      $ 0.848$ \\
+            Iran &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.588$ &                         $ 0.148$ &                      $ 0.087$ \\
+            Iran (O.
+orientalis) &          Ovis aries &               $ 0.009$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.569$ &                         $ 0.143$ &                      $ 0.081$ \\
+            Iran (O.
+vignei) &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.587$ &                         $ 0.127$ &                      $ 0.075$ \\
+            Various &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.588$ &                         $ 0.146$ &                      $ 0.086$ \\
+            Morocco &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.025$ &                                          $ 0.564$ &                         $ 0.145$ &                      $ 0.082$ \\
+            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.002$ &                                          $ 5.689$ &                         $ 0.170$ &                      $ 0.968$ \\
+            \rowcolor{LIGHTGREY} Central Afr.
+Rep.
+& Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.005$ &                                          $ 2.142$ &                         $ 0.156$ &                      $ 0.334$ \\
+            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.002$ &                                          $ 5.910$ &                         $ 0.160$ &                      $ 0.945$ \\
+            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.006$ &                                          $ 1.850$ &                         $ 0.157$ &                      $ 0.290$ \\
+            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.004$ &                                          $ 2.802$ &                         $ 0.163$ &                      $ 0.456$ \\
+            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus &               $ 0.003$ &              $ 0.012$ &              $ 0.002$ &                                          $ 5.396$ &                         $ 0.169$ &                      $ 0.910$ \\
+            \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.005$ &                                          $ 2.154$ &                         $ 0.153$ &                      $ 0.329$ \\
+            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.002$ &                                          $ 5.094$ &                         $ 0.164$ &                      $ 0.834$ \\
+            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.006$ &                                          $ 1.952$ &                         $ 0.153$ &                      $ 0.298$ \\
+            African &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.014$ &                                          $ 0.869$ &                         $ 0.141$ &                      $ 0.123$ \\
+            Admixed American &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.010$ &                                          $ 1.130$ &                         $ 0.161$ &                      $ 0.182$ \\
+            East Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.007$ &                                          $ 1.602$ &                         $ 0.162$ &                      $ 0.259$ \\
+            European &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.009$ &                                          $ 1.336$ &                         $ 0.163$ &                      $ 0.217$ \\
+            South Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.009$ &                                          $ 1.342$ &                         $ 0.163$ &                      $ 0.219$ \\
+        \end{longtable*}
+    \end{center}
+    \begin{itemize}
+        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
+        \item $\proba [ \SphyBen ]$ (eq.~\ref{eq:proba-dfe-mutsel}) is the probability for a new mutation a beneficial back-mutation.
+        These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1, thus toward a more fit amino-acid.
+        \item $\proba [ \SpopBen ]$ (eq.~\ref{eq:total_proba}) is the probability for a mutation to be beneficial.
+        These mutations have a selection coefficient at the population-scale larger than 1.
+        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~\ref{eq:polyProbaAdv}) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale (the \textit{precision}).
+        \item $\proba [ \SphyBen \given \SpopBen]$ (eq.~\ref{eq:bayes}) is the probability for a mutation to a beneficial back-mutations, given it is beneficial (the \textit{recall}).
+        This probability is obtained using Bayes' formula.
+    \end{itemize}
+    \newpage
+
+    \subsection{Precision and recall}
+    \captionof{table}{Precision and recall}
+    \begin{center}
+        \begin{adjustbox}{width=\textwidth}
+            \begin{tabular}{||l|l|r||r|r||r|r||r|r||}
+                \toprule
+                \multicolumn{3}{||c||}{} &
+                \multicolumn{2}{c||}{\shortstack{\textbf{Deleterious mutations} \\ $\bm{\SpopDel \coloneqq \Spop<-1}$ \\ $\bm{\SphyDel \coloneqq \Sphy<-1}$}} &
+                \multicolumn{2}{c||}{\shortstack{\textbf{Nearly-neutral mutations} \\ $\bm{\SpopNeu \coloneqq -1<\Spop<1}$ \\ $\bm{\SphyNeu \coloneqq -1<\Sphy<1}$}} &
+                \multicolumn{2}{c||}{\shortstack{\textbf{Beneficial mutations} \\ $\bm{\SpopBen \coloneqq \Spop>1}$ \\ $\bm{\SphyBen \coloneqq \Sphy>1}$}}
+                \\ \hline
+                \textbf{Population} &
+                \textbf{Species} &
+                $\bm{\thetaSyn}$ &
+                \makecell{\textbf{Precision} \\ $\bm{\proba [\SpopDel \given \SphyDel]}$} &
+                \makecell{\textbf{Recall} \\ $\bm{\proba [\SphyDel \given \SpopDel]}$}           &
+                \makecell{\textbf{Precision}      \\ $\bm{\proba [\SpopNeu \given \SphyNeu]}$}                                    &
+                \makecell{\textbf{Recall}          \\ $\bm{\proba [\SphyNeu \given \SpopNeu]}$}                                  &
+                \makecell{\textbf{Precision}          \\ $\bm{\proba [\SpopBen \given \SphyBen]}$}          &
+                \makecell{\textbf{Recall}        \\ $\bm{\proba [\SphyBen \given \SpopBen]}$}
+                \\   \midrule
+                \rowcolor{LIGHTGREY} Equus c. & Equus caballus        & $ 0.002$ & $ 0.895$ & $ 0.969$ & $ 0.645$ & $ 0.315$ & $ 0.141$ & $ 0.316$ \\
+                Iran               & Bos taurus        & $ 0.002$ & $ 0.878$ & $ 0.968$ & $ 0.632$ & $ 0.286$ & $ 0.136$ & $ 0.298$ \\
+                Uganda              & Bos taurus        & $ 0.005$ & $ 0.951$ & $ 0.963$ & $ 0.597$ & $ 0.508$ & $ 0.138$ & $ 0.162$ \\
+                \rowcolor{LIGHTGREY} Australia            & Capra hircus        & $ 0.003$ & $ 0.895$ & $ 0.981$ & $ 0.830$ & $ 0.379$ & $ 0.135$ & $ 0.871$ \\
+                \rowcolor{LIGHTGREY} France                                    & Capra hircus          & $ 0.004$ & $ 0.896$ & $ 0.978$ & $ 0.801$ & $ 0.373$ & $ 0.132$ & $ 0.845$ \\
+                \rowcolor{LIGHTGREY} Iran (C. aegagrus)                    & Capra hircus          & $ 0.004$ & $ 0.913$ & $ 0.971$ & $ 0.711$ & $ 0.383$ & $ 0.129$ & $ 0.772$ \\
+                \rowcolor{LIGHTGREY} Iran                        & Capra hircus          & $ 0.004$ & $ 0.949$ & $ 0.968$ & $ 0.655$ & $ 0.481$ & $ 0.138$ & $ 0.506$ \\
+                \rowcolor{LIGHTGREY} Italy                                 & Capra hircus          & $ 0.004$ & $ 0.894$ & $ 0.979$ & $ 0.814$ & $ 0.373$ & $ 0.127$ & $ 0.787$ \\
+                \rowcolor{LIGHTGREY} Morocco                                 & Capra hircus          & $ 0.004$ & $ 0.951$ & $ 0.972$ & $ 0.709$ & $ 0.504$ & $ 0.141$ & $ 0.848$ \\
+                Iran           & Ovis aries & $ 0.007$ & $ 0.980$ & $ 0.956$ & $ 0.456$ & $ 0.799$ & $ 0.148$ & $ 0.087$ \\
+                Iran (O. orientalis)  & Ovis aries & $ 0.009$ & $ 0.979$ & $ 0.955$ & $ 0.454$ & $ 0.798$ & $ 0.143$ & $ 0.081$ \\
+                Iran (O. vignei)           & Ovis aries & $ 0.007$ & $ 0.974$ & $ 0.957$ & $ 0.483$ & $ 0.729$ & $ 0.127$ & $ 0.075$ \\
+                Various             & Ovis aries & $ 0.008$ & $ 0.979$ & $ 0.958$ & $ 0.500$ & $ 0.813$ & $ 0.146$ & $ 0.086$ \\
+                Morocco              & Ovis aries & $ 0.008$ & $ 0.980$ & $ 0.952$ & $ 0.392$ & $ 0.774$ & $ 0.145$ & $ 0.082$ \\
+                \rowcolor{LIGHTGREY} Barbados              & Chlorocebus sabaeus & $ 0.004$ & $ 0.880$ & $ 0.984$ & $ 0.854$ & $ 0.354$ & $ 0.170$ & $ 0.968$ \\
+                \rowcolor{LIGHTGREY} Central Afr. Rep.       & Chlorocebus sabaeus & $ 0.006$ & $ 0.932$ & $ 0.968$ & $ 0.634$ & $ 0.413$ & $ 0.156$ & $ 0.334$ \\
+                \rowcolor{LIGHTGREY} Ethiopia        & Chlorocebus sabaeus & $ 0.005$ & $ 0.877$ & $ 0.980$ & $ 0.810$ & $ 0.337$ & $ 0.160$ & $ 0.945$ \\
+                \rowcolor{LIGHTGREY} Gambia             & Chlorocebus sabaeus & $ 0.005$ & $ 0.947$ & $ 0.977$ & $ 0.745$ & $ 0.518$ & $ 0.157$ & $ 0.290$ \\
+                \rowcolor{LIGHTGREY} Kenya                                 & Chlorocebus sabaeus        & $ 0.005$ & $ 0.903$ & $ 0.969$ & $ 0.664$ & $ 0.343$ & $ 0.163$ & $ 0.456$ \\
+                \rowcolor{LIGHTGREY} Nevis                        & Chlorocebus sabaeus        & $ 0.003$ & $ 0.880$ & $ 0.984$ & $ 0.861$ & $ 0.357$ & $ 0.169$ & $ 0.910$ \\
+                \rowcolor{LIGHTGREY} South Africa                              & Chlorocebus sabaeus        & $ 0.006$ & $ 0.931$ & $ 0.967$ & $ 0.615$ & $ 0.401$ & $ 0.153$ & $ 0.329$ \\
+                \rowcolor{LIGHTGREY} Saint Kitts                                & Chlorocebus sabaeus        & $ 0.004$ & $ 0.883$ & $ 0.982$ & $ 0.834$ & $ 0.355$ & $ 0.164$ & $ 0.834$ \\
+                \rowcolor{LIGHTGREY} Zambia                             & Chlorocebus sabaeus        & $ 0.006$ & $ 0.896$ & $ 0.969$ & $ 0.659$ & $ 0.332$ & $ 0.153$ & $ 0.298$ \\
+                African                             & Homo sapiens        & $ 0.002$ & $ 0.946$ & $ 0.971$ & $ 0.630$ & $ 0.486$ & $ 0.141$ & $ 0.123$ \\
+                Admixed American                             & Homo sapiens        & $ 0.002$ & $ 0.929$ & $ 0.972$ & $ 0.636$ & $ 0.410$ & $ 0.161$ & $ 0.182$ \\
+                East Asian                             & Homo sapiens        & $ 0.002$ & $ 0.937$ & $ 0.973$ & $ 0.647$ & $ 0.429$ & $ 0.162$ & $ 0.259$ \\
+                European                             & Homo sapiens        & $ 0.002$ & $ 0.937$ & $ 0.973$ & $ 0.643$ & $ 0.433$ & $ 0.163$ & $ 0.217$ \\
+                South Asian                             & Homo sapiens        & $ 0.002$ & $ 0.939$ & $ 0.972$ & $ 0.639$ & $ 0.439$ & $ 0.163$ & $ 0.219$ \\
+                \bottomrule
+            \end{tabular}
+        \end{adjustbox}
+    \end{center}
+    \begin{itemize}
+        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
+        \item \textit{Precision} is the estimation of the selection coefficient at population scale ($\Spop$) given that $\Sphy$ is known.
+        \item \textit{Recall} is the estimation of $\Sphy$ given selection coefficient at the population scale ($\Spop$) is known.
+        \item \textit{Recall} for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is thus the proportion of beneficial back-mutations among all beneficial mutations.
+    \end{itemize}
+
+    Altogether, comparing this table to tables 1 and S3, we acknowledge that the exact proportion of beneficial back-mutations among all beneficial ones is dependent on the model used to estimate the DFE.
+    However, we can still see that beneficial back-mutations are positively selected compared to neutral and deleterious ones, and this result is not sensitive to the underlying DFE at the population scale.
 

### 2023-05-03 manuscript/supp-mat.tex
Added artworks. Updated manuscript.

@@
 \usepackage{xcolor, colortbl}
+\definecolor{LIGHTGREY}{gray}{0.9}
 \definecolor{BLUELINK}{HTML}{0645AD}
@@
 \usepackage{booktabs}
+\usepackage{makecell}
+\usepackage{orcidlink}
 \usepackage{graphicx}
@@
 \newcommand{\Sphy}{S_{0}}
-\newcommand{\Sphyclass}{\mathcal{C}}
 \newcommand{\SphyMean}{\overline{\Sphy}}
-\newcommand{\divDel}{\Sphy^{\text{d}}}
-\newcommand{\divWeak}{\Sphy^{\text{n}}}
-\newcommand{\divAdv}{\Sphy^{\text{b}}}
-\newcommand{\PdivDel}{\proba \left[ \divDel \right]}
-\newcommand{\PdivWeak}{\proba \left[ \divWeak \right]}
-\newcommand{\PdivAdv}{\proba \left[ \divAdv \right]}
+\newcommand{\SphyDel}{\mathcal{D}_0}
+\newcommand{\SphyNeu}{\mathcal{N}_0}
+\newcommand{\SphyBen}{\mathcal{B}_0}
+\newcommand{\Sphyclass}{x}
+\newcommand{\SphyclassAlt}{y}
 \newcommand{\given}{\mid}
 \newcommand{\Spop}{S}
-\newcommand{\SpopMean}{\overline{\Spop}}
-\newcommand{\polyDel}{\Spop^{\text{d}}}
-\newcommand{\polyNeutral}{\Spop^{\text{n}}}
-\newcommand{\polyAdv}{\Spop^{\text{b}}}
-\newcommand{\PpolyDel}{\proba \left[ \polyDel \right]}
-\newcommand{\PpolyNeutral}{\proba \left[ \polyNeutral \right]}
-\newcommand{\PpolyAdv}{\proba \left[ \polyAdv \right]}
+\newcommand{\SpopDel}{\mathcal{D}}
+\newcommand{\SpopNeu}{\mathcal{N}}
+\newcommand{\SpopBen}{\mathcal{B}}
+\newcommand{\ProbaPopDel}{\proba [ \SpopDel]}
+\newcommand{\ProbaPopNeu}{\proba [ \SpopNeu ]}
+\newcommand{\ProbaPopBen}{\proba [ \SpopBen ]}
+\newcommand{\AdvMean}{\beta_b}
+\newcommand{\DelMean}{\beta_d}
+\newcommand{\thetaSyn}{\theta_{\text{S}}}
 
-\title{\textbf{Empirical evidence for beneficial mutations that are not adaptive innovations in mammals}}
+\title{\textbf{Mammalian protein-coding genes exhibit widespread beneficial mutations that are not adaptive}}
 
@@
     \large
-    \textbf{T. {Latrille}$^{1}$, J. {Joseph}$^{2}$, D.~A. {Hartasánchez}$^{1}$, N. {Salamin}$^{1}$}\\
+    \textbf{T.
+{Latrille}$^{1\dag}$\orcidlink{0000-0002-9643-4668}, J.
+{Joseph}$^{2\dag}$\orcidlink{0009-0002-1312-9930}, D.~A.
+{Hartasánchez}$^{1}$\orcidlink{0000-0003-2596-6883}, N.
+{Salamin}$^{1}$\orcidlink{0000-0002-3963-4954}}\\
     \scriptsize $^{1}$Department of Computational Biology, Université de Lausanne, Lausanne, Switzerland\\
-    \scriptsize $^{2}$Université de Lyon, Université Lyon 1, CNRS, VetAgro Sup, Laboratoire de Biométrie et Biologie Evolutive, UMR5558, Villeurbanne, France \\
-    \texttt{\href{mailto:thibault.latrille@ens-lyon.org}{thibault.latrille@ens-lyon.org}} \\
+    \scriptsize $^{2}$Laboratoire de Biométrie et Biologie Evolutive, UMR5558, Université Lyon 1, Villeurbanne, France \\
+    \scriptsize $^{\dag}$These authors contributed equally to this work\\
+    \normalsize \texttt{\href{mailto:thibault.latrille@ens-lyon.org}{thibault.latrille@ens-lyon.org}} \\
 }
@@
 
-    \section{Mutation-selection codon models}\label{sec:site-specific-mutation-selection-codon-models}
-    In BayesCode (\url{https://github.com/ThibaultLatrille/bayescode}), mutation-selection codon models are obtained by running \textit{mutselomega} for 2000 points of MCMC with the options:
+    \section{Beneficial mutations in the terminal lineages and populations}\label{sec:beneficial-mutations}
+
+    \subsection{Mutation-selection codon models}
+    \label{sec:site-specific-mutation-selection-codon-models}
+    In \textit{BayesCode} (\url{https://github.com/ThibaultLatrille/bayescode}), we ran the mutation-selection codon models \textit{mutselomega} for 2000 points of MCMC with the options:
     \begin{scriptsize}
@@
 
-    \subsubsection{$\dnds$ and beneficial back-mutations}
+    \subsubsection{$\dnds$ for deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial back-mutations ($\SphyBen$)}
     \begin{center}
-        \captionof{table}{$\dnds$ of beneficial back-mutations.}
+        \captionof{table}{$\dnds$ for deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial back-mutations ($\SphyBen$).}
         \scriptsize
@@
             \toprule
-            Population &             Species & Tajima $\theta_{\pi}$  & $\mathbb{P}_{div}[ S_0^{b} ]$ & $\omega $ & $\omega ( S_0^{d} )$ & $\omega ( S_0^{n} )$ & $\omega ( S_0^{b} )$ \\
-            \midrule
-            \endfirsthead
-
-            \toprule
-            Population &             Species & Tajima $\theta_{\pi}$  & $\mathbb{P}_{div}[ S_0^{b} ]$ & $\omega $ & $\omega ( S_0^{d} )$ & $\omega ( S_0^{n} )$ & $\omega ( S_0^{b} )$ \\
+            Population &             Species & Watterson's $\thetaSyn$  & $\proba_{div}[ \SphyBen ]$ & $\dnds $ & $\dn ( \SphyDel ) / \ds$ & $\dn ( \SphyNeu ) / \ds$ & $\dn ( \SphyBen ) / \ds$ \\
             \midrule
@@
             \endlastfoot
-            Equus c. &      Equus caballus &               $ 0.002$ &                      $ 0.118$ &  $ 0.147$ &             $ 0.075$ &             $ 0.823$ &             $ 1.203$ \\
+            \rowcolor{LIGHTGREY} Equus c.
+&      Equus caballus &               $ 0.002$ &                    $ 0.118$ &  $ 0.147$ &            $ 0.075$ &                $ 0.823$ &           $ 1.203$ \\
             Iran &          Bos taurus &               $ 0.002$ &                    $ 0.123$ &  $ 0.131$ &            $ 0.074$ &                $ 0.627$ &           $ 1.206$ \\
             Uganda &          Bos taurus &               $ 0.005$ &                    $ 0.125$ &  $ 0.134$ &            $ 0.075$ &                $ 0.637$ &           $ 1.252$ \\
-            Australia &        Capra hircus &               $ 0.003$ &                      $ 0.121$ &  $ 0.125$ &             $ 0.068$ &             $ 0.629$ &             $ 1.099$ \\
-            France &        Capra hircus &               $ 0.004$ &                      $ 0.120$ &  $ 0.126$ &             $ 0.068$ &             $ 0.633$ &             $ 1.102$ \\
-            Iran (C. aegagrus) &        Capra hircus &               $ 0.004$ &                      $ 0.120$ &  $ 0.125$ &             $ 0.068$ &             $ 0.630$ &             $ 1.100$ \\
-            Iran &        Capra hircus &               $ 0.004$ &                      $ 0.121$ &  $ 0.125$ &             $ 0.067$ &             $ 0.630$ &             $ 1.108$ \\
-            Italy &        Capra hircus &               $ 0.004$ &                      $ 0.120$ &  $ 0.126$ &             $ 0.068$ &             $ 0.634$ &             $ 1.102$ \\
-            Morocco &        Capra hircus &               $ 0.004$ &                      $ 0.122$ &  $ 0.125$ &             $ 0.067$ &             $ 0.631$ &             $ 1.112$ \\
+            \rowcolor{LIGHTGREY} Australia &        Capra hircus &               $ 0.003$ &                    $ 0.121$ &  $ 0.125$ &            $ 0.068$ &                $ 0.629$ &           $ 1.099$ \\
+            \rowcolor{LIGHTGREY} France &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.126$ &            $ 0.068$ &                $ 0.633$ &           $ 1.102$ \\
+            \rowcolor{LIGHTGREY} Iran (C.
+aegagrus) &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.125$ &            $ 0.068$ &                $ 0.630$ &           $ 1.100$ \\
+            \rowcolor{LIGHTGREY} Iran &        Capra hircus &               $ 0.004$ &                    $ 0.121$ &  $ 0.125$ &            $ 0.067$ &                $ 0.630$ &           $ 1.108$ \\
+            \rowcolor{LIGHTGREY} Italy &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.126$ &            $ 0.068$ &                $ 0.634$ &           $ 1.102$ \\
+            \rowcolor{LIGHTGREY} Morocco &        Capra hircus &               $ 0.004$ &                    $ 0.122$ &  $ 0.125$ &            $ 0.067$ &                $ 0.631$ &           $ 1.112$ \\
             Iran &          Ovis aries &               $ 0.007$ &                    $ 0.109$ &  $ 0.146$ &            $ 0.091$ &                $ 0.616$ &           $ 1.148$ \\
@@
             Morocco &          Ovis aries &               $ 0.008$ &                    $ 0.108$ &  $ 0.148$ &            $ 0.093$ &                $ 0.619$ &           $ 1.149$ \\
-            Barbados & Chlorocebus sabaeus &               $ 0.004$ &                      $ 0.122$ &  $ 0.133$ &             $ 0.071$ &             $ 0.696$ &             $ 1.397$ \\
-            Central Afr. Rep. & Chlorocebus sabaeus &               $ 0.006$ &                      $ 0.124$ &  $ 0.134$ &             $ 0.071$ &             $ 0.701$ &             $ 1.431$ \\
-            Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &                      $ 0.124$ &  $ 0.134$ &             $ 0.071$ &             $ 0.699$ &             $ 1.422$ \\
-            Gambia & Chlorocebus sabaeus &               $ 0.005$ &                      $ 0.123$ &  $ 0.134$ &             $ 0.071$ &             $ 0.703$ &             $ 1.411$ \\
-            Kenya & Chlorocebus sabaeus &               $ 0.005$ &                      $ 0.123$ &  $ 0.134$ &             $ 0.071$ &             $ 0.699$ &             $ 1.419$ \\
-            Nevis & Chlorocebus sabaeus &               $ 0.003$ &                      $ 0.123$ &  $ 0.133$ &             $ 0.071$ &             $ 0.699$ &             $ 1.407$ \\
-            South Africa & Chlorocebus sabaeus &               $ 0.006$ &                      $ 0.125$ &  $ 0.134$ &             $ 0.070$ &             $ 0.704$ &             $ 1.447$ \\
-            Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &                      $ 0.123$ &  $ 0.133$ &             $ 0.070$ &             $ 0.699$ &             $ 1.413$ \\
-            Zambia & Chlorocebus sabaeus &               $ 0.006$ &                      $ 0.123$ &  $ 0.134$ &             $ 0.071$ &             $ 0.699$ &             $ 1.410$ \\
+            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus &               $ 0.004$ &                    $ 0.122$ &  $ 0.133$ &            $ 0.071$ &                $ 0.696$ &           $ 1.397$ \\
+            \rowcolor{LIGHTGREY} Central Afr.
+Rep.
+& Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.124$ &  $ 0.134$ &            $ 0.071$ &                $ 0.701$ &           $ 1.431$ \\
+            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.124$ &  $ 0.134$ &            $ 0.071$ &                $ 0.699$ &           $ 1.422$ \\
+            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.123$ &  $ 0.134$ &            $ 0.071$ &                $ 0.703$ &           $ 1.411$ \\
+            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.123$ &  $ 0.134$ &            $ 0.071$ &                $ 0.699$ &           $ 1.419$ \\
+            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus &               $ 0.003$ &                    $ 0.123$ &  $ 0.133$ &            $ 0.071$ &                $ 0.699$ &           $ 1.407$ \\
+            \rowcolor{LIGHTGREY} South Africa  & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.125$ &  $ 0.134$ &            $ 0.070$ &                $ 0.704$ &           $ 1.447$ \\
+            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &                    $ 0.123$ &  $ 0.133$ &            $ 0.070$ &                $ 0.699$ &           $ 1.413$ \\
+            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.123$ &  $ 0.134$ &            $ 0.071$ &                $ 0.699$ &           $ 1.410$ \\
             African &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &            $ 0.118$ &                $ 0.865$ &           $ 1.609$ \\
@@
     \begin{itemize}
-        \item Tajima $\theta$ is the synonymous diversity.
-        \item $\mathbb{P}_{div}[\Sphy > 1]$ is the proportion of substitutions in the terminal branch observed with a selection coefficient at the phylogenetic scale larger than 1 ($\Sphy > 1$).
-        \item $\dn(\Sphy > 1) / \ds$ is the ratio of non-synonymous over synonymous divergence (also called $\dnds$) estimated for the non-synonymous substitutions in the terminal branch with a selection coefficient larger than 1 ($\Sphy > 1$).
-        \item $\dn(\Sphy > 1) / \ds$ is the ratio of non-synonymous over synonymous divergence (also called $\dnds$) estimated for the non-synonymous substitutions in the terminal branch with a selection coefficient larger than 1 ($\Sphy > 1$).
-        \item $\dn(\Sphy > 1) / \ds$ is the ratio of non-synonymous over synonymous divergence (also called $\dnds$) estimated for the non-synonymous substitutions in the terminal branch with a selection coefficient larger than 1 ($\Sphy > 1$).
+        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
+        \item $\proba_{div}[\SphyBen]$ is the proportion of substitutions in the terminal branch that are $\SphyBen$.
+        \item $\dn(\SphyDel) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are $\SphyDel$.
+        \item $\dn(\SphyNeu) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are $\SphyNeu$.
+        \item $\dn(\SphyBen) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are $\SphyBen$.
     \end{itemize}
@@
     \newpage
+
+    \subsubsection{$\dnds$ over-estimation due to beneficial back-mutations}
     \begin{center}
@@
             \toprule
-            Population & Species & Tajima $\theta_{\pi}$ & $\mathbb{P}_{div}[\Sphy > 0]$ & $\dnds $ & $\dn(\Sphy < 0) / \ds$ & R($\dnds $) \\
+            Population & Species & Watterson's $\thetaSyn$ & $\proba_{div}[\Sphy > 1]$ & $\dnds $ & $\dn(\Sphy < 1) / \ds$ & $\delta(\dnds )$ \\
             \midrule
@@
             \endlastfoot
-            Equus c. &      Equus caballus &               $ 0.002$ &                $ 0.307$ &        $ 0.182$ &              $ 0.133$ &           $  27.0$ \\
-            Iran &          Bos taurus &               $ 0.005$ &                $ 0.298$ &        $ 0.164$ &              $ 0.122$ &           $  26.1$ \\
-            Uganda &          Bos taurus &               $ 0.005$ &                $ 0.303$ &        $ 0.167$ &              $ 0.123$ &           $  26.6$ \\
-            Australia &        Capra hircus &               $ 0.003$ &                $ 0.301$ &        $ 0.157$ &              $ 0.116$ &           $  26.4$ \\
-            France &        Capra hircus &               $ 0.003$ &                $ 0.300$ &        $ 0.158$ &              $ 0.116$ &           $  26.3$ \\
-            Iran (C. aegagrus) &        Capra hircus &               $ 0.003$ &                $ 0.300$ &        $ 0.158$ &              $ 0.116$ &           $  26.3$ \\
-            Iran &        Capra hircus &               $ 0.004$ &                $ 0.303$ &        $ 0.157$ &              $ 0.115$ &           $  26.6$ \\
-            Italy &        Capra hircus &               $ 0.003$ &                $ 0.300$ &        $ 0.158$ &              $ 0.116$ &           $  26.3$ \\
-            Morocco &        Capra hircus &               $ 0.004$ &                $ 0.303$ &        $ 0.157$ &              $ 0.115$ &           $  26.6$ \\
-            Iran &          Ovis aries &               $ 0.007$ &                $ 0.266$ &        $ 0.179$ &              $ 0.138$ &           $  22.7$ \\
-            Iran (O. orientalis) &          Ovis aries &               $ 0.009$ &                $ 0.265$ &        $ 0.180$ &              $ 0.140$ &           $  22.6$ \\
-            Iran (O. vignei) &          Ovis aries &               $ 0.007$ &                $ 0.268$ &        $ 0.178$ &              $ 0.137$ &           $  22.8$ \\
-            Various &          Ovis aries &               $ 0.009$ &                $ 0.264$ &        $ 0.180$ &              $ 0.140$ &           $  22.5$ \\
-            Morocco &          Ovis aries &               $ 0.007$ &                $ 0.265$ &        $ 0.180$ &              $ 0.140$ &           $  22.6$ \\
-            Barbados & Chlorocebus sabaeus &               $ 0.004$ &                $ 0.303$ &        $ 0.172$ &              $ 0.126$ &           $  26.8$ \\
-            Central Afr. Rep. & Chlorocebus sabaeus &               $ 0.006$ &                $ 0.304$ &        $ 0.173$ &              $ 0.126$ &           $  27.0$ \\
-            Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &                $ 0.305$ &        $ 0.172$ &              $ 0.126$ &           $  27.1$ \\
-            Gambia & Chlorocebus sabaeus &               $ 0.005$ &                $ 0.304$ &        $ 0.172$ &              $ 0.126$ &           $  26.9$ \\
-            Kenya & Chlorocebus sabaeus &               $ 0.005$ &                $ 0.304$ &        $ 0.173$ &              $ 0.126$ &           $  27.0$ \\
-            Nevis & Chlorocebus sabaeus &               $ 0.003$ &                $ 0.304$ &        $ 0.172$ &              $ 0.126$ &           $  26.9$ \\
-            South Africa & Chlorocebus sabaeus &               $ 0.006$ &                $ 0.307$ &        $ 0.172$ &              $ 0.125$ &           $  27.3$ \\
-            Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &                $ 0.306$ &        $ 0.172$ &              $ 0.125$ &           $  27.1$ \\
-            Zambia & Chlorocebus sabaeus &               $ 0.006$ &                $ 0.304$ &        $ 0.172$ &              $ 0.126$ &           $  27.0$ \\
-            African &        Homo sapiens &               $ 0.003$ &                $ 0.257$ &        $ 0.237$ &              $ 0.185$ &           $  22.0$ \\
-            Admixed American &        Homo sapiens &               $ 0.002$ &                $ 0.256$ &        $ 0.237$ &              $ 0.185$ &           $  21.9$ \\
-            East Asian &        Homo sapiens &               $ 0.002$ &                $ 0.258$ &        $ 0.238$ &              $ 0.185$ &           $  22.0$ \\
-            European &        Homo sapiens &               $ 0.002$ &                $ 0.256$ &        $ 0.237$ &              $ 0.185$ &           $  21.8$ \\
-            South Asian &        Homo sapiens &               $ 0.002$ &                $ 0.257$ &        $ 0.237$ &              $ 0.185$ &           $  22.0$ \\
+            \rowcolor{LIGHTGREY} Equus c. &      Equus caballus &               $ 0.002$ &                    $ 0.118$ &  $ 0.147$ &           $ 0.131$ &     $  10.5$ \\
+            Iran &          Bos taurus &               $ 0.002$ &                    $ 0.123$ &  $ 0.131$ &           $ 0.117$ &     $  11.1$ \\
+            Uganda &          Bos taurus &               $ 0.005$ &                    $ 0.125$ &  $ 0.134$ &           $ 0.118$ &     $  11.3$ \\
+            \rowcolor{LIGHTGREY} Australia &        Capra hircus &               $ 0.003$ &                    $ 0.121$ &  $ 0.125$ &           $ 0.111$ &     $  10.8$ \\
+            \rowcolor{LIGHTGREY} France &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.126$ &           $ 0.112$ &     $  10.8$ \\
+            \rowcolor{LIGHTGREY} Iran (C. aegagrus) &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.125$ &           $ 0.111$ &     $  10.8$ \\
+            \rowcolor{LIGHTGREY} Iran &        Capra hircus &               $ 0.004$ &                    $ 0.121$ &  $ 0.125$ &           $ 0.111$ &     $  10.9$ \\
+            \rowcolor{LIGHTGREY} Italy &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.126$ &           $ 0.112$ &     $  10.8$ \\
+            \rowcolor{LIGHTGREY} Morocco &        Capra hircus &               $ 0.004$ &                    $ 0.122$ &  $ 0.125$ &           $ 0.111$ &     $  11.0$ \\
+            Iran &          Ovis aries &               $ 0.007$ &                    $ 0.109$ &  $ 0.146$ &           $ 0.132$ &     $ 9.671$ \\
+            Iran (O. orientalis) &          Ovis aries &               $ 0.009$ &                    $ 0.108$ &  $ 0.148$ &           $ 0.134$ &     $ 9.516$ \\
+            Iran (O. vignei) &          Ovis aries &               $ 0.007$ &                    $ 0.109$ &  $ 0.146$ &           $ 0.132$ &     $ 9.598$ \\
+            Various &          Ovis aries &               $ 0.008$ &                    $ 0.107$ &  $ 0.148$ &           $ 0.134$ &     $ 9.439$ \\
+            Morocco &          Ovis aries &               $ 0.008$ &                    $ 0.108$ &  $ 0.148$ &           $ 0.134$ &     $ 9.582$ \\
+            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus &               $ 0.004$ &                    $ 0.122$ &  $ 0.133$ &           $ 0.118$ &     $  11.2$ \\
+            \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.124$ &  $ 0.134$ &           $ 0.119$ &     $  11.3$ \\
+            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.124$ &  $ 0.134$ &           $ 0.118$ &     $  11.3$ \\
+            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.123$ &  $ 0.134$ &           $ 0.119$ &     $  11.2$ \\
+            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.123$ &  $ 0.134$ &           $ 0.119$ &     $  11.3$ \\
+            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus &               $ 0.003$ &                    $ 0.123$ &  $ 0.133$ &           $ 0.118$ &     $  11.3$ \\
+            \rowcolor{LIGHTGREY} South Africa  & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.125$ &  $ 0.134$ &           $ 0.118$ &     $  11.5$ \\
+            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &                    $ 0.123$ &  $ 0.133$ &           $ 0.118$ &     $  11.3$ \\
+            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.123$ &  $ 0.134$ &           $ 0.119$ &     $  11.2$ \\
+            African &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &           $ 0.175$ &     $ 8.799$ \\
+            Admixed American &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &           $ 0.175$ &     $ 8.780$ \\
+            East Asian &        Homo sapiens &               $ 0.002$ &                    $ 0.098$ &  $ 0.192$ &           $ 0.175$ &     $ 8.768$ \\
+            European &        Homo sapiens &               $ 0.002$ &                    $ 0.098$ &  $ 0.192$ &           $ 0.175$ &     $ 8.728$ \\
+            South Asian &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &           $ 0.175$ &     $ 8.788$ \\
         \end{longtable*}
@@
     \begin{itemize}
-        \item Tajima $\theta$ is the synonymous diversity.
-        \item $\mathbb{P}_{div}[\Sphy > 0]$ is the proportion of substitutions in the terminal branch observed with a selection coefficient at the phylogenetic scale larger than 0 ($\Sphy > 0$).
-        \item $\dnds$ is the ratio of non-synonymous over synonymous divergence estimated for all the non-synonymous substitutions in the terminal branch.
-        \item $\dn(\Sphy < 0) / \ds$ is the ratio of non-synonymous over synonymous divergence estimated for the non-synonymous substitutions in the terminal branch with a selection coefficient lower than 0 ($\Sphy < 0$).
+        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
+        \item $\proba_{div}[\SphyBen]$ is the proportion of substitutions in the terminal branch that are $\SphyBen$.
+        \item $\dnds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions estimated for all the non-synonymous substitutions in the terminal branch.
+        \item $\dn(\Sphy < 1) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are not $\SphyBen$.
         This is the estimated divergence when we removed beneficial back-mutations.
-        \item $R(\dnds)=\dfrac{\dnds - \dn(\Sphy < 0) / \ds}{\dnds}$ is the fraction of the divergence ($\dnds$) that is over-estimated, $\dnds$ is compared to the estimated divergence when we removed beneficial back-mutations $\dn(\Sphy < 0) / \ds$.
+        \item $\delta(\dnds)$ (eq.~7) is the fraction of the divergence ($\dnds$) that is over-estimated, $\dnds$ is compared to the estimated divergence when we removed beneficial back-mutations $\dn(\Sphy < 1) / \ds$.
     \end{itemize}
-    We estimated that between 20 and 25\% of $\dnds$ is over-estimated ($R(\dnds)$), corresponding to beneficial back-mutation inflating the $\dnds$ statistic.
+    We estimated that between 9 and 11\% of $\dnds$ is over-estimated, corresponding to beneficial back-mutation inflating the $\dnds$ statistic.
 
@@
     \begin{center}
-        \captionof{table}{Probability of beneficial back-mutations among all beneficial ones with PolyDFE model C.}
+        \captionof{table}{Probability of beneficial back-mutations among all beneficial ones.}
         \scriptsize
@@
             \toprule
-            Population & Species & Tajima $\theta_{\pi}$ & $\mathbb{P}[\Sphy > 1]$ & $\mathbb{P} [ \Spop > 1 ]$ & $\frac{\mathbb{P}[\Sphy > 1]}{\mathbb{P}[ \Spop > 1 ]}$ & $\mathbb{P} [ \Spop > 1 \given \Sphy > 1]$ & $\mathbb{P}[\Sphy > 1\given \Spop > 1 ]$ \\
+            Population & Species & Watterson's $\thetaSyn$ & $\proba[\SphyBen]$ & $\proba [ \SpopBen ]$ & $\frac{\proba[\SphyBen]}{\proba[ \SpopBen ]}$ & $\proba [ \SpopBen \given \SphyBen]$ & $\proba[\SphyBen\given \SpopBen ]$ \\
             \midrule
@@
             \endlastfoot
-            Equus c.
-&      Equus caballus &               $ 0.002$ &          $ 0.017$ &                   $ 0.046$ &                                          $ 0.378$ &                         $ 0.678$ &                      $ 0.256$ \\
-            Iran &          Bos taurus &               $ 0.005$ &          $ 0.016$ &                   $ 0.040$ &                                          $ 0.402$ &                         $ 0.525$ &                      $ 0.211$ \\
-            Uganda &          Bos taurus &               $ 0.005$ &          $ 0.016$ &                   $ 0.038$ &                                          $ 0.420$ &                         $ 0.610$ &                      $ 0.256$ \\
-            Australia &        Capra hircus &               $ 0.003$ &          $ 0.017$ &                   $ 0.039$ &                                          $ 0.419$ &                         $ 0.368$ &                      $ 0.154$ \\
-            France &        Capra hircus &               $ 0.003$ &          $ 0.017$ &                   $ 0.038$ &                                          $ 0.440$ &                         $ 0.368$ &                      $ 0.162$ \\
-            Iran (C.
-aegagrus) &        Capra hircus &               $ 0.003$ &          $ 0.017$ &                   $ 0.040$ &                                          $ 0.418$ &                         $ 0.235$ &                      $ 0.098$ \\
-            Iran &        Capra hircus &               $ 0.004$ &          $ 0.017$ &                   $ 0.033$ &                                          $ 0.500$ &                         $ 0.368$ &                      $ 0.184$ \\
-            Italy &        Capra hircus &               $ 0.003$ &          $ 0.017$ &                   $ 0.035$ &                                          $ 0.466$ &                         $ 0.309$ &                      $ 0.144$ \\
-            Morocco &        Capra hircus &               $ 0.004$ &          $ 0.017$ &                   $ 0.032$ &                                          $ 0.514$ &                         $ 0.368$ &                      $ 0.189$ \\
-            Iran &          Ovis aries &               $ 0.007$ &          $ 0.017$ &                   $ 0.024$ &                                          $ 0.686$ &                         $ 0.174$ &                      $ 0.119$ \\
+            \rowcolor{LIGHTGREY} Equus c.
+&      Equus caballus &               $ 0.002$ &              $ 0.014$ &              $ 0.010$ &                                          $ 1.395$ &                         $ 0.580$ &                      $ 0.809$ \\
+            Iran &          Bos taurus &               $ 0.002$ &              $ 0.013$ &              $ 0.041$ &                                          $ 0.323$ &                         $ 0.857$ &                      $ 0.277$ \\
+            Uganda &          Bos taurus &               $ 0.005$ &              $ 0.013$ &              $ 0.013$ &                                          $ 0.991$ &                         $ 0.488$ &                      $ 0.483$ \\
+            \rowcolor{LIGHTGREY} Australia &        Capra hircus &               $ 0.003$ &              $ 0.014$ &              $ 0.026$ &                                          $ 0.532$ &                         $ 0.368$ &                      $ 0.196$ \\
+            \rowcolor{LIGHTGREY} France &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.572$ &                         $ 0.368$ &                      $ 0.211$ \\
+            \rowcolor{LIGHTGREY} Iran (C.
+aegagrus) &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.026$ &                                          $ 0.516$ &                         $ 0.221$ &                      $ 0.114$ \\
+            \rowcolor{LIGHTGREY} Iran &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.573$ &                         $ 0.368$ &                      $ 0.211$ \\
+            \rowcolor{LIGHTGREY} Italy &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.017$ &                                          $ 0.814$ &                         $ 0.270$ &                      $ 0.220$ \\
+            \rowcolor{LIGHTGREY} Morocco &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.018$ &                                          $ 0.751$ &                         $ 0.368$ &                      $ 0.276$ \\
+            Iran &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.006$ &                                          $ 2.321$ &                         $ 0.169$ &                      $ 0.392$ \\
             Iran (O.
-orientalis) &          Ovis aries &               $ 0.009$ &          $ 0.017$ &                   $ 0.027$ &                                          $ 0.612$ &                         $ 0.165$ &                      $ 0.101$ \\
+orientalis) &          Ovis aries &               $ 0.009$ &              $ 0.014$ &              $ 0.012$ &                                          $ 1.178$ &                         $ 0.153$ &                      $ 0.180$ \\
             Iran (O.
-vignei) &          Ovis aries &               $ 0.007$ &          $ 0.017$ &                   $ 0.031$ &                                          $ 0.542$ &                         $ 0.228$ &                      $ 0.124$ \\
-            Various &          Ovis aries &               $ 0.009$ &          $ 0.017$ &                   $ 0.026$ &                                          $ 0.641$ &                         $ 0.238$ &                      $ 0.153$ \\
-            Morocco &          Ovis aries &               $ 0.007$ &          $ 0.017$ &                   $ 0.023$ &                                          $ 0.742$ &                         $ 0.192$ &                      $ 0.142$ \\
-            Barbados & Chlorocebus sabaeus &               $ 0.004$ &          $ 0.014$ &                   $ 0.045$ &                                          $ 0.319$ &                         $ 0.595$ &                      $ 0.190$ \\
-            Central Afr.
+vignei) &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.020$ &                                          $ 0.683$ &                         $ 0.195$ &                      $ 0.133$ \\
+            Various &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.012$ &                                          $ 1.201$ &                         $ 0.190$ &                      $ 0.228$ \\
+            Morocco &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.005$ &                                          $ 2.589$ &                         $ 0.136$ &                      $ 0.353$ \\
+            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.022$ &                                          $ 0.541$ &                         $ 0.565$ &                      $ 0.306$ \\
+            \rowcolor{LIGHTGREY} Central Afr.
 Rep.
-& Chlorocebus sabaeus &               $ 0.006$ &          $ 0.014$ &                   $ 0.039$ &                                          $ 0.368$ &                         $ 0.497$ &                      $ 0.183$ \\
-            Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &          $ 0.014$ &                   $ 0.044$ &                                          $ 0.322$ &                         $ 0.502$ &                      $ 0.162$ \\
-            Gambia & Chlorocebus sabaeus &               $ 0.005$ &          $ 0.014$ &                   $ 0.034$ &                                          $ 0.415$ &                         $ 0.541$ &                      $ 0.224$ \\
-            Kenya & Chlorocebus sabaeus &               $ 0.005$ &          $ 0.014$ &                   $ 0.039$ &                                          $ 0.363$ &                         $ 0.492$ &                      $ 0.179$ \\
-            Nevis & Chlorocebus sabaeus &               $ 0.003$ &          $ 0.014$ &                   $ 0.041$ &                                          $ 0.345$ &                         $ 0.549$ &                      $ 0.190$ \\
-            South Africa & Chlorocebus sabaeus &               $ 0.006$ &          $ 0.014$ &                   $ 0.039$ &                                          $ 0.367$ &                         $ 0.504$ &                      $ 0.185$ \\
-            Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &          $ 0.014$ &                   $ 0.043$ &                                          $ 0.326$ &                         $ 0.538$ &                      $ 0.175$ \\
-            Zambia & Chlorocebus sabaeus &               $ 0.006$ &          $ 0.014$ &                   $ 0.043$ &                                          $ 0.332$ &                         $ 0.529$ &                      $ 0.175$ \\
-            African &        Homo sapiens &               $ 0.003$ &          $ 0.014$ &                   $ 0.042$ &                                          $ 0.343$ &                         $ 0.724$ &                      $ 0.249$ \\
-            Admixed American &        Homo sapiens &               $ 0.002$ &          $ 0.014$ &                   $ 0.040$ &                                          $ 0.358$ &                         $ 0.695$ &                      $ 0.249$ \\
-            East Asian &        Homo sapiens &               $ 0.002$ &          $ 0.014$ &                   $ 0.039$ &                                          $ 0.366$ &                         $ 0.652$ &                      $ 0.239$ \\
-            European &        Homo sapiens &               $ 0.002$ &          $ 0.014$ &                   $ 0.039$ &                                          $ 0.373$ &                         $ 0.666$ &                      $ 0.249$ \\
-            South Asian &        Homo sapiens &               $ 0.002$ &          $ 0.014$ &                   $ 0.038$ &                                          $ 0.378$ &                         $ 0.677$ &                      $ 0.256$ \\
+& Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.018$ &                                          $ 0.639$ &                         $ 0.429$ &                      $ 0.274$ \\
+            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.022$ &                                          $ 0.516$ &                         $ 0.462$ &                      $ 0.239$ \\
+            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.007$ &                                          $ 1.592$ &                         $ 0.486$ &                      $ 0.774$ \\
+            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.023$ &                                          $ 0.508$ &                         $ 0.478$ &                      $ 0.243$ \\
+            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus &               $ 0.003$ &              $ 0.012$ &              $ 0.015$ &                                          $ 0.762$ &                         $ 0.516$ &                      $ 0.393$ \\
+            \rowcolor{LIGHTGREY} South Africa  & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.016$ &                                          $ 0.734$ &                         $ 0.490$ &                      $ 0.360$ \\
+            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.016$ &                                          $ 0.713$ &                         $ 0.515$ &                      $ 0.367$ \\
+            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.023$ &                                          $ 0.500$ &                         $ 0.499$ &                      $ 0.249$ \\
+            African &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.025$ &                                          $ 0.470$ &                         $ 0.678$ &                      $ 0.319$ \\
+            Admixed American &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.021$ &                                          $ 0.569$ &                         $ 0.635$ &                      $ 0.361$ \\
+            East Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.031$ &                                          $ 0.381$ &                         $ 0.611$ &                      $ 0.233$ \\
+            European &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.034$ &                                          $ 0.350$ &                         $ 0.619$ &                      $ 0.217$ \\
+            South Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.033$ &                                          $ 0.354$ &                         $ 0.628$ &                      $ 0.222$ \\
         \end{longtable*}
@@
     \begin{itemize}
-        \item Tajima $\theta$ is the synonymous diversity.
-        \item $\mathbb{P} [ \Sphy > 1 ]$ is the probability for a new mutation a beneficial back-mutation.
-        These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1 ($\Sphy > 1$), thus toward a more fit amino-acid.
-        In other words, this probability is the part of the DFE estimated by mutation-selection models greater than 1.
-        \item $\mathbb{P} [ \Spop > 1 ]$ is the probability for a mutation to be beneficial.
-        These mutations have a selection coefficient at the population-scale larger than 1 ($\Spop > 1$), estimated from all SNPs in the population.
-        In other words, this probability is the part of the DFE estimated by polyDFE greater than 1.
-        \item $\mathbb{P} [ \Spop > 1 \given \Sphy > 1]$ is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale.
-        These mutations have a selection coefficient at the population scale larger than 1 ($\Spop > 1$), estimated by polyDFE on the SNPs with a predicted selection coefficient at the phylogenetic scale larger than 1 ($\Sphy > 1$).
-        In other words, this probability is the part of the DFE estimated by polyDFE greater than 1, when we restricted our analysis on SNPs that are already predicted by mutation-selection models to have a selection coefficient ($\Sphy$) greater than 1.
-        \item $\mathbb{P} [ \Sphy > 1 \given \Spop > 1]$ is the probability for a mutation to a beneficial back-mutations, given it is beneficial.
+        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
+        \item $\proba [ \SphyBen ]$ (eq.~5) is the probability for a new mutation to be a beneficial back-mutation.
+        These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1, thus toward a more fit amino-acid.
+        \item $\proba [ \SpopBen ]$ (eq.~15) is the probability for a mutation to be beneficial.
+        These mutations have a selection coefficient at the population-scale larger than 1.
+        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale (the \textit{precision}).
+        \item $\proba [ \SphyBen \given \SpopBen]$ (eq.~14) is the probability for a mutation to a beneficial back-mutations, given it is beneficial at the population scale (the \textit{recall}).
         This probability is obtained using Bayes' formula.
     \end{itemize}
-    With polyDFE model C, the DFE of non-synonymous mutations is given as a mixture of a $\Gamma$ (negative side) and Exponential (positive side) distributions, see Materials and Methods.
+    \newpage
+
+    \subsection{Replicability across mammals}
+    The proportion of deleterious ($\ProbaPopDel$), nearly-neutral ($\ProbaPopNeu$) and of beneficial ($\ProbaPopBen$) mutations estimated at the population-genetic scale across the different populations is shown for each class of selection ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$).
+
+    \captionof{figure}{Estimation of selection at the population scale for $\SphyDel$ mutations}
+    \begin{minipage}{0.9\linewidth}
+    \includegraphics[width=\linewidth, page=1]{artworks/Theta.neg.stacked.pdf}
+    \end{minipage}
+    \begin{minipage}{0.09\linewidth}
+        \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
+    \end{minipage}
+
+    \captionof{figure}{Estimation of selection at the population scale for $\SphyNeu$ mutations}
+    \begin{minipage}{0.9\linewidth}
+        \includegraphics[width=\linewidth, page=1]{artworks/Theta.weak.stacked.pdf}
+    \end{minipage}
+    \begin{minipage}{0.09\linewidth}
+        \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
+    \end{minipage}
 
     \newpage
-    \begin{center}
-        \captionof{table}{Probability of beneficial back-mutations among all beneficial ones (including slightly-beneficial mutations) with PolyDFE model C.}
-        \scriptsize
-        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
-            \toprule
-            Population & Species & Tajima $\theta_{\pi}$ & $\mathbb{P}[\Sphy > 0]$ & $\mathbb{P} [ \Spop > 0 ]$ & $\frac{\mathbb{P}[\Sphy > 0]}{\mathbb{P}[ \Spop > 0 ]}$ & $\mathbb{P} [ \Spop > 0 \given \Sphy > 0]$ & $\mathbb{P}[\Sphy > 0\given \Spop > 0 ]$ \\
-            \midrule
-            \endhead
-            \midrule
-            \multicolumn{8}{r}{{Continued on next page}} \\
-            \midrule
-            \endfoot
-
-            \bottomrule
-            \endlastfoot
-            Equus c.
-&      Equus caballus &               $ 0.002$ &             $ 0.050$ &              $ 0.125$ &                                     $ 0.403$ &                       $ 1.000$ &                 $ 0.403$ \\
-            Iran &          Bos taurus &               $ 0.005$ &             $ 0.050$ &              $ 0.108$ &                                     $ 0.457$ &                       $ 0.640$ &                 $ 0.293$ \\
-            Uganda &          Bos taurus &               $ 0.005$ &             $ 0.050$ &              $ 0.104$ &                                     $ 0.477$ &                       $ 0.708$ &                 $ 0.338$ \\
-            Australia &        Capra hircus &               $ 0.003$ &             $ 0.051$ &              $ 0.107$ &                                     $ 0.471$ &                       $ 0.416$ &                 $ 0.196$ \\
-            France &        Capra hircus &               $ 0.003$ &             $ 0.051$ &              $ 0.102$ &                                     $ 0.495$ &                       $ 0.464$ &                 $ 0.230$ \\
-            Iran (C.
-aegagrus) &        Capra hircus &               $ 0.003$ &             $ 0.051$ &              $ 0.107$ &                                     $ 0.473$ &                       $ 0.327$ &                 $ 0.155$ \\
-            Iran &        Capra hircus &               $ 0.004$ &             $ 0.051$ &              $ 0.089$ &                                     $ 0.569$ &                       $ 0.384$ &                 $ 0.219$ \\
-            Italy &        Capra hircus &               $ 0.003$ &             $ 0.051$ &              $ 0.096$ &                                     $ 0.525$ &                       $ 0.402$ &                 $ 0.211$ \\
-            Morocco &        Capra hircus &               $ 0.004$ &             $ 0.051$ &              $ 0.088$ &                                     $ 0.571$ &                       $ 0.408$ &                 $ 0.233$ \\
-            Iran &          Ovis aries &               $ 0.007$ &             $ 0.051$ &              $ 0.066$ &                                     $ 0.769$ &                       $ 0.159$ &                 $ 0.122$ \\
-            Iran (O.
-orientalis) &          Ovis aries &               $ 0.009$ &             $ 0.051$ &              $ 0.074$ &                                     $ 0.686$ &                       $ 0.259$ &                 $ 0.177$ \\
-            Iran (O.
-vignei) &          Ovis aries &               $ 0.007$ &             $ 0.051$ &              $ 0.084$ &                                     $ 0.605$ &                       $ 0.499$ &                 $ 0.302$ \\
-            Various &          Ovis aries &               $ 0.009$ &             $ 0.051$ &              $ 0.071$ &                                     $ 0.712$ &                       $ 0.253$ &                 $ 0.180$ \\
-            Morocco &          Ovis aries &               $ 0.007$ &             $ 0.051$ &              $ 0.060$ &                                     $ 0.839$ &                       $ 0.155$ &                 $ 0.130$ \\
-            Barbados & Chlorocebus sabaeus &               $ 0.004$ &             $ 0.048$ &              $ 0.121$ &                                     $ 0.392$ &                       $ 0.771$ &                 $ 0.303$ \\
-            Central Afr.
-Rep.
-& Chlorocebus sabaeus &               $ 0.006$ &             $ 0.047$ &              $ 0.105$ &                                     $ 0.454$ &                       $ 0.637$ &                 $ 0.289$ \\
-            Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &             $ 0.047$ &              $ 0.120$ &                                     $ 0.395$ &                       $ 0.708$ &                 $ 0.280$ \\
-            Gambia & Chlorocebus sabaeus &               $ 0.005$ &             $ 0.047$ &              $ 0.090$ &                                     $ 0.528$ &                       $ 0.725$ &                 $ 0.383$ \\
-            Kenya & Chlorocebus sabaeus &               $ 0.005$ &             $ 0.047$ &              $ 0.106$ &                                     $ 0.447$ &                       $ 0.627$ &                 $ 0.280$ \\
-            Nevis & Chlorocebus sabaeus &               $ 0.003$ &             $ 0.048$ &              $ 0.111$ &                                     $ 0.429$ &                       $ 0.676$ &                 $ 0.290$ \\
-            South Africa & Chlorocebus sabaeus &               $ 0.006$ &             $ 0.047$ &              $ 0.104$ &                                     $ 0.456$ &                       $ 0.659$ &                 $ 0.301$ \\
-            Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &             $ 0.047$ &              $ 0.117$ &                                     $ 0.405$ &                       $ 0.723$ &                 $ 0.293$ \\
-            Zambia & Chlorocebus sabaeus &               $ 0.006$ &             $ 0.047$ &              $ 0.116$ &                                     $ 0.409$ &                       $ 0.671$ &                 $ 0.275$ \\
-            African &        Homo sapiens &               $ 0.003$ &             $ 0.048$ &              $ 0.114$ &                                     $ 0.424$ &                       $ 1.000$ &                 $ 0.424$ \\
-            Admixed American &        Homo sapiens &               $ 0.002$ &             $ 0.048$ &              $ 0.110$ &                                     $ 0.437$ &                       $ 1.000$ &                 $ 0.437$ \\
-            East Asian &        Homo sapiens &               $ 0.002$ &             $ 0.048$ &              $ 0.106$ &                                     $ 0.453$ &                       $ 1.000$ &                 $ 0.453$ \\
-            European &        Homo sapiens &               $ 0.002$ &             $ 0.048$ &              $ 0.107$ &                                     $ 0.452$ &                       $ 1.000$ &                 $ 0.452$ \\
-            South Asian &        Homo sapiens &               $ 0.002$ &             $ 0.048$ &              $ 0.106$ &                                     $ 0.454$ &                       $ 1.000$ &                 $ 0.454$ \\
-        \end{longtable*}
-    \end{center}
-    \begin{itemize}
-        \item Tajima $\theta$ is the synonymous diversity.
-        \item $\mathbb{P} [ \Sphy > 0 ]$ is the probability for a new mutation a beneficial back-mutation.
-        These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 0 ($\Sphy > 0$), thus toward a more fit amino-acid.
-        In other words, this probability is the part of the DFE estimated by mutation-selection models greater than 0.
-        \item $\mathbb{P} [ \Spop > 0 ]$ is the probability for a mutation to be beneficial.
-        These mutations have a selection coefficient at the population-scale larger than 0 ($\Spop > 0$), estimated from all SNPs in the population.
-        In other words, this probability is the part of the DFE estimated by polyDFE greater than 0.
-        \item $\mathbb{P} [ \Spop > 0 \given \Sphy > 0]$ is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale.
-        These mutations have a selection coefficient at the population scale larger than 0 ($\Spop > 0$), estimated by polyDFE on the SNPs with a predicted selection coefficient at the phylogenetic scale larger than 0 ($\Sphy > 0$).
-        In other words, this probability is the part of the DFE estimated by polyDFE greater than 0, when we restricted our analysis on SNPs that are already predicted by mutation-selection models to have a selection coefficient ($\Sphy$) greater than 0.
-        \item $\mathbb{P} [ \Sphy > 0 \given \Spop > 0]$ is the probability for a mutation to a beneficial back-mutations, given it is beneficial.
-        This probability is obtained using Bayes' formula.
-    \end{itemize}
-    With polyDFE model C, the DFE of non-synonymous mutations is given as a mixture of a $\Gamma$ (negative side) and Exponential (positive side) distributions, see Materials and Methods.
-
-    \newpage
-    \begin{center}
-        \captionof{table}{Probability of beneficial back-mutations among all beneficial ones (including slightly-beneficial mutations) with PolyDFE model D.}
-        \scriptsize
-        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
-            \toprule
-            Population & Species & Tajima $\theta_{\pi}$ & $\mathbb{P}[\Sphy \geq 0]$ & $\mathbb{P} [ \Spop \geq 0 ]$ & $\frac{\mathbb{P}[\Sphy \geq 0]}{\mathbb{P}[ \Spop \geq 0 ]}$ & $\mathbb{P} [ \Spop \geq 0 \given \Sphy \geq 0]$ & $\mathbb{P}[\Sphy \geq 0\given \Spop \geq 0 ]$ \\
-            \midrule
-            \endhead
-            \midrule
-            \multicolumn{8}{r}{{Continued on next page}} \\
-            \midrule
-            \endfoot
-
-            \bottomrule
-            \endlastfoot
-            Equus c.
-&      Equus caballus &               $ 0.002$ &             $ 0.050$ &              $ 0.219$ &                                     $ 0.230$ &                       $ 0.461$ &                 $ 0.106$ \\
-            Iran &          Bos taurus &               $ 0.005$ &             $ 0.050$ &              $ 0.181$ &                                     $ 0.274$ &                       $ 0.407$ &                 $ 0.112$ \\
-            Uganda &          Bos taurus &               $ 0.005$ &             $ 0.050$ &              $ 0.175$ &                                     $ 0.283$ &                       $ 0.470$ &                 $ 0.133$ \\
-            Australia &        Capra hircus &               $ 0.003$ &             $ 0.051$ &              $ 0.182$ &                                     $ 0.277$ &                       $ 0.472$ &                 $ 0.131$ \\
-            France &        Capra hircus &               $ 0.003$ &             $ 0.051$ &              $ 0.177$ &                                     $ 0.286$ &                       $ 0.492$ &                 $ 0.141$ \\
-            Iran (C.
-aegagrus) &        Capra hircus &               $ 0.003$ &             $ 0.051$ &              $ 0.171$ &                                     $ 0.295$ &                       $ 0.463$ &                 $ 0.137$ \\
-            Iran &        Capra hircus &               $ 0.004$ &             $ 0.051$ &              $ 0.161$ &                                     $ 0.313$ &                       $ 0.450$ &                 $ 0.141$ \\
-            Italy &        Capra hircus &               $ 0.003$ &             $ 0.051$ &              $ 0.174$ &                                     $ 0.291$ &                       $ 0.509$ &                 $ 0.148$ \\
-            Morocco &        Capra hircus &               $ 0.004$ &             $ 0.051$ &              $ 0.170$ &                                     $ 0.298$ &                       $ 0.442$ &                 $ 0.132$ \\
-            Iran &          Ovis aries &               $ 0.007$ &             $ 0.051$ &              $ 0.141$ &                                     $ 0.359$ &                       $ 0.506$ &                 $ 0.182$ \\
-            Iran (O.
-orientalis) &          Ovis aries &               $ 0.009$ &             $ 0.051$ &              $ 0.139$ &                                     $ 0.365$ &                       $ 0.484$ &                 $ 0.177$ \\
-            Iran (O.
-vignei) &          Ovis aries &               $ 0.007$ &             $ 0.051$ &              $ 0.134$ &                                     $ 0.379$ &                       $ 0.517$ &                 $ 0.196$ \\
-            Various &          Ovis aries &               $ 0.009$ &             $ 0.051$ &              $ 0.136$ &                                     $ 0.372$ &                       $ 0.513$ &                 $ 0.191$ \\
-            Morocco &          Ovis aries &               $ 0.007$ &             $ 0.051$ &              $ 0.139$ &                                     $ 0.364$ &                       $ 0.477$ &                 $ 0.174$ \\
-            Barbados & Chlorocebus sabaeus &               $ 0.004$ &             $ 0.048$ &              $ 0.205$ &                                     $ 0.232$ &                       $ 0.543$ &                 $ 0.126$ \\
-            Central Afr.
-Rep.
-& Chlorocebus sabaeus &               $ 0.006$ &             $ 0.047$ &              $ 0.179$ &                                     $ 0.265$ &                       $ 0.345$ &                 $ 0.091$ \\
-            Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &             $ 0.047$ &              $ 0.203$ &                                     $ 0.234$ &                       $ 0.464$ &                 $ 0.108$ \\
-            Gambia & Chlorocebus sabaeus &               $ 0.005$ &             $ 0.047$ &              $ 0.183$ &                                     $ 0.260$ &                       $ 0.442$ &                 $ 0.115$ \\
-            Kenya & Chlorocebus sabaeus &               $ 0.005$ &             $ 0.047$ &              $ 0.179$ &                                     $ 0.265$ &                       $ 0.478$ &                 $ 0.127$ \\
-            Nevis & Chlorocebus sabaeus &               $ 0.003$ &             $ 0.048$ &              $ 0.203$ &                                     $ 0.234$ &                       $ 0.552$ &                 $ 0.129$ \\
-            South Africa & Chlorocebus sabaeus &               $ 0.006$ &             $ 0.047$ &              $ 0.184$ &                                     $ 0.258$ &                       $ 0.477$ &                 $ 0.123$ \\
-            Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &             $ 0.047$ &              $ 0.204$ &                                     $ 0.233$ &                       $ 0.527$ &                 $ 0.123$ \\
-            Zambia & Chlorocebus sabaeus &               $ 0.006$ &             $ 0.047$ &              $ 0.187$ &                                     $ 0.253$ &                       $ 0.477$ &                 $ 0.121$ \\
-            African &        Homo sapiens &               $ 0.003$ &             $ 0.048$ &              $ 0.239$ &                                     $ 0.202$ &                       $ 0.158$ &                 $ 0.032$ \\
-            Admixed American &        Homo sapiens &               $ 0.002$ &             $ 0.048$ &              $ 0.252$ &                                     $ 0.192$ &                       $ 0.452$ &                 $ 0.087$ \\
-            East Asian &        Homo sapiens &               $ 0.002$ &             $ 0.048$ &              $ 0.260$ &                                     $ 0.185$ &                       $ 0.440$ &                 $ 0.082$ \\
-            European &        Homo sapiens &               $ 0.002$ &             $ 0.048$ &              $ 0.255$ &                                     $ 0.189$ &                       $ 0.453$ &                 $ 0.086$ \\
-            South Asian &        Homo sapiens &               $ 0.002$ &             $ 0.048$ &              $ 0.248$ &                                     $ 0.194$ &                       $ 0.439$ &                 $ 0.085$ \\
-        \end{longtable*}
-    \end{center}
-    \begin{itemize}
-        \item Tajima $\theta$ is the synonymous diversity.
-        \item $\mathbb{P} [ \Sphy \geq 0 ]$ is the probability for a new mutation a beneficial back-mutation.
-        These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 0 ($\Sphy \geq 0$), thus toward a more fit amino-acid.
-        In other words, this probability is the part of the DFE estimated by mutation-selection models greater than 0.
-        \item $\mathbb{P} [ \Spop \geq 0 ]$ is the probability for a mutation to be beneficial.
-        These mutations have a selection coefficient at the population-scale larger than 0 ($\Spop \geq 0$), estimated from all SNPs in the population.
-        In other words, this probability is the part of the DFE estimated by polyDFE greater than 0.
-        \item $\mathbb{P} [ \Spop \geq 0 \given \Sphy \geq 0]$ is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale.
-        These mutations have a selection coefficient at the population scale larger than 0 ($\Spop \geq 0$), estimated by polyDFE on the SNPs with a predicted selection coefficient at the phylogenetic scale larger than 0 ($\Sphy \geq 0$).
-        In other words, this probability is the part of the DFE estimated by polyDFE greater than 0, when we restricted our analysis on SNPs that are already predicted by mutation-selection models to have a selection coefficient ($\Sphy$) greater than 0.
-        \item $\mathbb{P} [ \Sphy \geq 0 \given \Spop \geq 0]$ is the probability for a mutation to a beneficial back-mutations, given it is beneficial.
-        This probability is obtained using Bayes' formula.
-    \end{itemize}
-    With polyDFE model D, the DFE of non-synonymous mutations is given as a discrete DFE of $K$ categories, where the selection coefficients of each category $i$ ($1 \leq i \leq K$) are fixed parameters $\Spop_i$, and each value $\Spop_i$ has a probability $p_i$ (estimated), with $\sum_{i=1}^{K} p_i =1$.
-    We used $K=5$ with $\Spop_1 = -400$, $\Spop_2 = -10$, $\Spop_3 = 0$, $\Spop_4 = 1$, $\Spop_5 = 4$.\\
-
-    Altogether, comparing tables S3-S5, we acknowledge that estimating the proportion of beneficial back-mutations among all beneficial ones is dependent on the assumption for the underlying distribution of fitness effects at the population scale and the threshold used to define a beneficial mutation.
-    \newpage
+    \captionof{figure}{Estimation of selection at the population scale for $\SphyBen$ mutations}
+    \begin{minipage}{0.9\linewidth}
+        \includegraphics[width=\linewidth, page=1]{artworks/Theta.pos.stacked.pdf}
+    \end{minipage}
+    \begin{minipage}{0.09\linewidth}
+        \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
+    \end{minipage}
 
     \subsection{Correlation with diversity}
-    For each population, the proportion of beneficial ($\PpolyAdv$), nearly-neutral ($\PpolyNeutral$) and of deleterious ($\PpolyDel$) mutations estimated at the population-genetic scale is shown as function of Watterson's diversity ($\Theta_w$).
+    For each population, the proportion of deleterious ($\ProbaPopDel$), nearly-neutral ($\ProbaPopNeu$) and of beneficial ($\ProbaPopBen$) mutations estimated at the population-genetic scale is shown as function of Watterson's's diversity ($\thetaSyn$).
 
-    \subsubsection{Proportion of nearly-neutral mutations ($\polyNeutral$)}\label{subsec:proportion-nearly-neutral-mutations}
-    \captionof{figure}{~}
+    \subsubsection{Proportion of deleterious mutations ($\SpopDel$)}\label{subsec:proportion-deleterious-mutations}
+    \captionof{figure}{Proportion of deleterious mutations ($\SpopDel$)}
     \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC-masked/regression-MutSel/results.watterson.all_P-Sweak.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.all_P-Sneg.scatter.pdf}
     \end{minipage}
     \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC-masked/regression-MutSel/results.watterson.weak_P-Sweak.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.neg_P-Sneg.scatter.pdf}
     \end{minipage}
     \begin{itemize}
-        \item $\ \proba [ \polyNeutral ]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) between -1 and 1, estimated for the whole genome.
-        \item $\ \proba [ \polyNeutral \given \divWeak ]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) between -1 and 1, estimated of SNPs observed with a selection coefficient at the phylogenetic scale ($\Sphy$) between -1 and 1.
+        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
+        \item $\proba [ \SpopDel ]$ (eq.~15) is the probability for a mutation to be deleterious.
+        These mutations have a selection coefficient at the population-scale lower than -1.
+        \item $\proba [ \SpopDel \given \SphyDel ]$ (eq.~12) is the probability for a mutation to be deleterious at the population scale, given it is predicted to be a deleterious at the phylogenetic scale.
     \end{itemize}
 
-    We confirmed that higher synonymous diversity is typically accompanied by a smaller proportion of neutral mutations.
-    This result is specially visible when we restricted the analysis to class of mutations that are supposedly nearly-neutral at the phylogenetic scale ($\divWeak$).
+    We can see that higher synonymous diversity ($\thetaSyn$) is typically accompanied by a higher proportion of effectively deleterious mutations at the population scale ($\proba [ \SpopDel ]$).
+    This trend is also confirmed when we restricted the analysis to class of mutations that are supposedly deleterious at the phylogenetic scale ($\SphyDel$).
+    This result is qualitatively in accordance with the nearly-neutral theory of evolution which argues that very slightly deleterious mutations are more efficiently purified in large populations.
+
+    \subsubsection{Proportion of nearly-neutral mutations ($\SpopNeu$)}\label{subsec:proportion-nearly-neutral-mutations}
+    \captionof{figure}{Proportion of nearly-neutral mutations ($\SpopNeu$)}
+    \begin{minipage}{0.49\linewidth}
+        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.all_P-Sweak.scatter.pdf}
+    \end{minipage}
+    \begin{minipage}{0.49\linewidth}
+        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.weak_P-Sweak.scatter.pdf}
+    \end{minipage}
+    \begin{itemize}
+        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
+        \item $\proba [ \SpopNeu ]$ (eq.~15) is the probability for a mutation to be nearly-neutral.
+        These mutations have a selection coefficient at the population-scale between -1 and 1.
+        \item $\proba [ \SpopNeu \given \SphyNeu ]$ (eq.~12) is the probability for a mutation to be nearly-neutral at the population scale, given it is predicted to be a nearly-neutral at the phylogenetic scale.
+    \end{itemize}
+
+    We confirmed that higher synonymous diversity ($\thetaSyn$) is typically accompanied by a smaller proportion of neutral mutations at the population scale ($\proba [ \SpopNeu ]$ in the range 0.06-0.18).
+    This result is more pronounced ($\proba [ \SpopNeu \given \SphyNeu ]$ in the range 0.36-0.73) when we restricted the analysis to class of mutations that are supposedly nearly-neutral at the phylogenetic scale ($\SphyNeu$).
     This result suggests that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) are more likely to discriminate whether mutations are beneficial or deleterious.
@@
 
-    \subsubsection{Proportion of deleterious mutations ($\polyDel$)}\label{subsec:proportion-deleterious-mutations}
-    \captionof{figure}{~}
+    \subsubsection{Proportion of beneficial mutations ($\SpopBen$)}\label{subsec:proportion-beneficial-mutations}
+    \captionof{figure}{Proportion of beneficial mutations ($\SpopBen$)}
     \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC-masked/regression-MutSel/results.watterson.all_P-Sneg.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.all_P-Spos.scatter.pdf}
     \end{minipage}
     \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC-masked/regression-MutSel/results.watterson.neg_P-Sneg.scatter.pdf}
+        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.pos_P-Spos.scatter.pdf}
     \end{minipage}
     \begin{itemize}
-        \item $\ \proba [ \polyDel ]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) lower than -1, estimated for the whole genome.
-        \item $\ \proba [ \polyDel \given \divDel]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) lower than -1, estimated of SNPs observed with a selection coefficient at the phylogenetic scale ($\Sphy$) lower than -1.
+        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
+        \item $\proba [ \SpopBen ]$ (eq.~15) is the probability for a mutation to be beneficial.
+        These mutations have a selection coefficient at the population-scale larger than 1.
+        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale (the \textit{precision}).
     \end{itemize}
-
-    \subsubsection{Proportion of beneficial mutations ($\polyAdv$)}\label{subsec:proportion-beneficial-mutations}
-    \captionof{figure}{~}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC-masked/regression-MutSel/results.watterson.all_P-Spos.scatter.pdf}
-    \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{../experiments/3bins-mC-masked/regression-MutSel/results.watterson.pos_P-Spos.scatter.pdf}
-    \end{minipage}
-    \begin{itemize}
-        \item $ \proba [ \polyAdv ]$ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) greater than 1, estimated for the whole genome.
-        \item $\proba [ \polyAdv \given \divAdv] $ is the proportion of DFE with a selection coefficient at the population-genetic scale ($\Spop$) greater than 1, estimated of SNPs observed with a selection coefficient at the phylogenetic scale ($\Sphy$) greater than 1.
-    \end{itemize}
+    Higher synonymous diversity ($\thetaSyn$) is accompanied by a smaller proportion of beneficial mutations at the population scale ($\proba [ \SpopBen ]$).
+    This trend is also confirmed when we restricted the analysis to class of mutations that are supposedly beneficial back-mutations at the phylogenetic scale ($\SphyBen$).
+    This result is much more difficult to interpret.
+    The fraction of beneficial back mutations is supposed to depend on long term demographic history, which is not directly accessible.
+    If the long term effective population size is relatively similar to the short term one, we expect little opportunity for beneficial back-mutations.
+    And thus, counter-intuitively we expect a diminution of positively selected mutations.
+    However, we can see that the proportion of beneficial back-mutations among advantageous one does not decrease with synonymous diversity.
+    This means that somehow adaptive mutations also decrease with synonymous diversity for a reason we fail to explain.
 
@@
 
-    \section{Clinically related terms for non-synonymous mutations}
-
+    \section{Clinically related terms for mutations}
+    \subsection{Terms associated with deleterious mutations $\SphyDel$}
     \begin{center}
-        \captionof{table}{Clinically related terms for $\Sphy < -1$}
+        \captionof{table}{Terms associated with deleterious mutations $\SphyDel$}
         \begin{tabular}{|l|r|r|r|r|r|}
@@
     \end{center}
-    In humans, non-synonymous SNPs in the test group (deleterious mutations with $\Sphy < -1$) are contrasted to SNPs in the control group (nearly-neutral mutations with $-1 < \Sphy < 1$).
+    In humans, non-synonymous SNPs in the test group ($\SphyDel$) are contrasted to SNPs in the control group ($\SphyNeu$).
     For each clinical term, a 2x2 contingency tables is built by counting the number of SNPs based on their selection coefficient and their clinical terms (whether they have this specific term or not).
     Fisher's exact tests are then performed for these 2x2 contingency tables.
-    $^*$ signify that the$p_{\mathrm{v}}^{\mathrm{adj}}$ corrected for multiple comparison (Holm–Bonferroni correction) is lower than the risk $\alpha=0.05$.
-    SNPs predicted with $\Sphy < -1$ are statistically associated to clinical terms such as \textit{Likely Pathogenic} and \textit{Pathogenic}.
+    $^*$ for $p_{\mathrm{v}}^{\mathrm{adj}}$ corrected for multiple comparison (Holm–Bonferroni correction) lower than the risk $\alpha=0.05$.
+    SNPs predicted with $\SphyDel$ are statistically associated to clinical terms such as \textit{Likely Pathogenic} and \textit{Pathogenic}.
 
+    \subsection{Terms associated with beneficial back-mutations $\SphyBen$}
     \begin{center}
-        \captionof{table}{Clinically related terms for $\Sphy > 1$}
+        \captionof{table}{Terms associated with beneficial back-mutations $\SphyBen$}
         \begin{tabular}{|l|r|r|r|r|r|}
@@
     \end{center}
-    In humans, non-synonymous SNPs in the test group (beneficial back-mutations with $\Sphy > 1$) are contrasted to SNPs in the control group (nearly-neutral mutations with $-1 < \Sphy < 1$).
+    In humans, non-synonymous SNPs in the test group ($\SphyBen$) are contrasted to SNPs in the control group ($\SphyNeu$).
     For each clinical term, a 2x2 contingency tables is built by counting the number of SNPs based on their selection coefficient and their clinical terms (whether they have this specific term or not).
     Fisher's exact tests are then performed for these 2x2 contingency tables.
-    $^*$ signify that the$p_{\mathrm{v}}^{\mathrm{adj}}$ corrected for multiple comparison (Holm–Bonferroni correction) is lower than the risk $\alpha=0.05$.
-    Beneficial back-mutations $\Sphy > 1$ are associated with clinical terms such as \textit{Benign} and \textit{Likely Benign}.
+    $^*$ for $p_{\mathrm{v}}^{\mathrm{adj}}$ corrected for multiple comparison (Holm–Bonferroni correction) lower than the risk $\alpha=0.05$.
+    Beneficial back-mutations are associated with clinical terms such as \textit{Benign} and \textit{Likely Benign}.
+    \newpage
+
+    \section{Including divergence data for the estimation of $\Spop$}
+
+    \subsection{Including divergence in polyDFE}
+    Divergence data (number of substitutions per site) can also be included into polyDFE to estimate the DFE.
+    For the class of a given class of selection coefficient ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$), the number of substitutions has already been computed and is given by $D\left( \Sphyclass \right)$ (see eq.~6), and the number of sites is given by $L \left( \Sphyclass \right)$ (see eq.~4).
+    Otherwise, the procedure is the same as described section \textit{Scaled selection coefficients ($\Spop$) in a population-based method}.
+
+    \subsection{Probabilities of beneficial back-mutations}
+    \begin{center}
+        \captionof{table}{Probability of beneficial back-mutations among all beneficial ones.}
+        \scriptsize
+        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
+            \toprule
+            Population & Species & Watterson's $\thetaSyn$ & $\proba[\SphyBen]$ & $\proba [ \SpopBen ]$ & $\frac{\proba[\SphyBen]}{\proba[ \SpopBen ]}$ & $\proba [ \SpopBen \given \SphyBen]$ & $\proba[\SphyBen\given \SpopBen ]$ \\
+            \midrule
+            \endhead
+            \midrule
+            \multicolumn{8}{r}{{Continued on next page}} \\
+            \midrule
+            \endfoot
+
+            \bottomrule
+            \endlastfoot
+            \rowcolor{LIGHTGREY} Equus c.
+&      Equus caballus &               $ 0.002$ &              $ 0.014$ &              $ 0.061$ &                                          $ 0.235$ &                         $ 0.519$ &                      $ 0.122$ \\
+            Iran &          Bos taurus &               $ 0.002$ &              $ 0.013$ &              $ 0.007$ &                                          $ 1.908$ &                         $ 0.368$ &                      $ 0.702$ \\
+            Uganda &          Bos taurus &               $ 0.005$ &              $ 0.013$ &              $ 0.008$ &                                          $ 1.667$ &                         $ 0.255$ &                      $ 0.425$ \\
+            \rowcolor{LIGHTGREY} Australia &        Capra hircus &               $ 0.003$ &              $ 0.014$ &              $ 0.007$ &                                          $ 2.099$ &                         $ 0.147$ &                      $ 0.308$ \\
+            \rowcolor{LIGHTGREY} France &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.007$ &                                          $ 2.043$ &                         $ 0.149$ &                      $ 0.304$ \\
+            \rowcolor{LIGHTGREY} Iran (C.
+aegagrus) &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.013$ &                                          $ 1.069$ &                         $ 0.147$ &                      $ 0.157$ \\
+            \rowcolor{LIGHTGREY} Iran &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.008$ &                                          $ 1.699$ &                         $ 0.152$ &                      $ 0.258$ \\
+            \rowcolor{LIGHTGREY} Italy &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.006$ &                                          $ 2.160$ &                         $ 0.147$ &                      $ 0.316$ \\
+            \rowcolor{LIGHTGREY} Morocco &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.006$ &                                          $ 2.141$ &                         $ 0.186$ &                      $ 0.398$ \\
+            Iran &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.012$ &                                          $ 1.210$ &                         $ 0.158$ &                      $ 0.191$ \\
+            Iran (O.
+orientalis) &          Ovis aries &               $ 0.009$ &              $ 0.014$ &              $ 0.012$ &                                          $ 1.144$ &                         $ 0.157$ &                      $ 0.180$ \\
+            Iran (O.
+vignei) &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.022$ &                                          $ 0.631$ &                         $ 0.186$ &                      $ 0.118$ \\
+            Various &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.012$ &                                          $ 1.211$ &                         $ 0.156$ &                      $ 0.188$ \\
+            Morocco &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.009$ &                                          $ 1.536$ &                         $ 0.190$ &                      $ 0.292$ \\
+            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.005$ &                                          $ 2.230$ &                         $ 0.282$ &                      $ 0.630$ \\
+            \rowcolor{LIGHTGREY} Central Afr.
+Rep.
+& Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.014$ &                                          $ 0.849$ &                         $ 0.310$ &                      $ 0.263$ \\
+            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.008$ &                                          $ 1.530$ &                         $ 0.298$ &                      $ 0.456$ \\
+            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.008$ &                                          $ 1.384$ &                         $ 0.305$ &                      $ 0.422$ \\
+            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.014$ &                                          $ 0.854$ &                         $ 0.296$ &                      $ 0.253$ \\
+            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus &               $ 0.003$ &              $ 0.012$ &              $ 0.005$ &                                          $ 2.438$ &                         $ 0.285$ &                      $ 0.696$ \\
+            \rowcolor{LIGHTGREY} South Africa  & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.011$ &                                          $ 1.047$ &                         $ 0.323$ &                      $ 0.338$ \\
+            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.006$ &                                          $ 2.070$ &                         $ 0.292$ &                      $ 0.604$ \\
+            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.014$ &                                          $ 0.816$ &                         $ 0.309$ &                      $ 0.252$ \\
+            African &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.015$ &                                          $ 0.765$ &                         $ 0.371$ &                      $ 0.284$ \\
+            Admixed American &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.009$ &                                          $ 1.259$ &                         $ 0.368$ &                      $ 0.464$ \\
+            East Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.012$ &                                          $ 0.973$ &                         $ 0.369$ &                      $ 0.358$ \\
+            European &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.009$ &                                          $ 1.356$ &                         $ 0.368$ &                      $ 0.499$ \\
+            South Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.010$ &                                          $ 1.147$ &                         $ 0.369$ &                      $ 0.423$ \\
+        \end{longtable*}
+    \end{center}
+    \begin{itemize}
+        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
+        \item $\proba [ \SphyBen ]$ (eq.~5) is the probability for a new mutation a beneficial back-mutation.
+        These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1, thus toward a more fit amino-acid.
+        \item $\proba [ \SpopBen ]$ (eq.~15) is the probability for a mutation to be beneficial.
+        These mutations have a selection coefficient at the population-scale larger than 1.
+        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale (the \textit{precision}).
+        \item $\proba [ \SphyBen \given \SpopBen]$ (eq.~14) is the probability for a mutation to a beneficial back-mutations, given it is beneficial (the \textit{recall}).
+        This probability is obtained using Bayes' formula.
+    \end{itemize}
+    \newpage
+
+    \subsection{Precision and recall}
+    \captionof{table}{Precision and recall}
+    \begin{center}
+        \begin{adjustbox}{width=\textwidth}
+            \begin{tabular}{||l|l|r||r|r||r|r||r|r||}
+                \toprule
+                \multicolumn{3}{||c||}{} &
+                \multicolumn{2}{c||}{\shortstack{\textbf{Deleterious mutations} \\ $\bm{\SpopDel \coloneqq \Spop<-1}$ \\ $\bm{\SphyDel \coloneqq \Sphy<-1}$}} &
+                \multicolumn{2}{c||}{\shortstack{\textbf{Nearly-neutral mutations} \\ $\bm{\SpopNeu \coloneqq -1<\Spop<1}$ \\ $\bm{\SphyNeu \coloneqq -1<\Sphy<1}$}} &
+                \multicolumn{2}{c||}{\shortstack{\textbf{Beneficial mutations} \\ $\bm{\SpopBen \coloneqq \Spop>1}$ \\ $\bm{\SphyBen \coloneqq \Sphy>1}$}}
+                \\ \hline
+                \textbf{Population} &
+                \textbf{Species} &
+                $\bm{\thetaSyn}$ &
+                \makecell{\textbf{Precision} \\ $\bm{\proba [\SpopDel \given \SphyDel]}$} &
+                \makecell{\textbf{Recall} \\ $\bm{\proba [\SphyDel \given \SpopDel]}$}           &
+                \makecell{\textbf{Precision}      \\ $\bm{\proba [\SpopNeu \given \SphyNeu]}$}                                    &
+                \makecell{\textbf{Recall}          \\ $\bm{\proba [\SphyNeu \given \SpopNeu]}$}                                  &
+                \makecell{\textbf{Precision}          \\ $\bm{\proba [\SpopBen \given \SphyBen]}$}          &
+                \makecell{\textbf{Recall}        \\ $\bm{\proba [\SphyBen \given \SpopBen]}$}
+                \\   \midrule
+                \rowcolor{LIGHTGREY} Equus c. & Equus caballus        & $ 0.002$ & $ 0.918$ & $ 0.957$ & $ 0.186$ & $ 0.213$ & $ 0.519$ & $ 0.122$ \\
+                Iran               & Bos taurus        & $ 0.002$ & $ 0.924$ & $ 0.965$ & $ 0.565$ & $ 0.356$ & $ 0.368$ & $ 0.702$ \\
+                Uganda              & Bos taurus        & $ 0.005$ & $ 0.943$ & $ 0.961$ & $ 0.516$ & $ 0.396$ & $ 0.255$ & $ 0.425$ \\
+                \rowcolor{LIGHTGREY} Australia            & Capra hircus        & $ 0.003$ & $ 0.941$ & $ 0.964$ & $ 0.592$ & $ 0.434$ & $ 0.147$ & $ 0.308$ \\
+                \rowcolor{LIGHTGREY} France                                    & Capra hircus          & $ 0.004$ & $ 0.940$ & $ 0.963$ & $ 0.571$ & $ 0.418$ & $ 0.149$ & $ 0.304$ \\
+                \rowcolor{LIGHTGREY} Iran (C. aegagrus)                    & Capra hircus          & $ 0.004$ & $ 0.948$ & $ 0.960$ & $ 0.515$ & $ 0.446$ & $ 0.147$ & $ 0.157$ \\
+                \rowcolor{LIGHTGREY} Iran                        & Capra hircus          & $ 0.004$ & $ 0.942$ & $ 0.961$ & $ 0.534$ & $ 0.410$ & $ 0.152$ & $ 0.258$ \\
+                \rowcolor{LIGHTGREY} Italy                                 & Capra hircus          & $ 0.004$ & $ 0.940$ & $ 0.963$ & $ 0.579$ & $ 0.421$ & $ 0.147$ & $ 0.316$ \\
+                \rowcolor{LIGHTGREY} Morocco                                 & Capra hircus          & $ 0.004$ & $ 0.939$ & $ 0.960$ & $ 0.549$ & $ 0.404$ & $ 0.186$ & $ 0.398$ \\
+                Iran           & Ovis aries & $ 0.007$ & $ 0.957$ & $ 0.954$ & $ 0.412$ & $ 0.416$ & $ 0.158$ & $ 0.191$ \\
+                Iran (O. orientalis)  & Ovis aries & $ 0.009$ & $ 0.961$ & $ 0.955$ & $ 0.413$ & $ 0.437$ & $ 0.157$ & $ 0.180$ \\
+                Iran (O. vignei)           & Ovis aries & $ 0.007$ & $ 0.968$ & $ 0.951$ & $ 0.356$ & $ 0.516$ & $ 0.186$ & $ 0.118$ \\
+                Various             & Ovis aries & $ 0.008$ & $ 0.958$ & $ 0.955$ & $ 0.428$ & $ 0.431$ & $ 0.156$ & $ 0.188$ \\
+                Morocco              & Ovis aries & $ 0.008$ & $ 0.960$ & $ 0.953$ & $ 0.447$ & $ 0.460$ & $ 0.190$ & $ 0.292$ \\
+                \rowcolor{LIGHTGREY} Barbados              & Chlorocebus sabaeus & $ 0.004$ & $ 0.931$ & $ 0.969$ & $ 0.628$ & $ 0.402$ & $ 0.282$ & $ 0.630$ \\
+                \rowcolor{LIGHTGREY} Central Afr. Rep.       & Chlorocebus sabaeus & $ 0.006$ & $ 0.941$ & $ 0.964$ & $ 0.514$ & $ 0.408$ & $ 0.310$ & $ 0.263$ \\
+                \rowcolor{LIGHTGREY} Ethiopia        & Chlorocebus sabaeus & $ 0.005$ & $ 0.933$ & $ 0.967$ & $ 0.586$ & $ 0.393$ & $ 0.298$ & $ 0.456$ \\
+                \rowcolor{LIGHTGREY} Gambia             & Chlorocebus sabaeus & $ 0.005$ & $ 0.937$ & $ 0.967$ & $ 0.590$ & $ 0.414$ & $ 0.305$ & $ 0.422$ \\
+                \rowcolor{LIGHTGREY} Kenya                                 & Chlorocebus sabaeus        & $ 0.005$ & $ 0.942$ & $ 0.965$ & $ 0.526$ & $ 0.418$ & $ 0.296$ & $ 0.253$ \\
+                \rowcolor{LIGHTGREY} Nevis                        & Chlorocebus sabaeus        & $ 0.003$ & $ 0.930$ & $ 0.970$ & $ 0.637$ & $ 0.401$ & $ 0.285$ & $ 0.696$ \\
+                \rowcolor{LIGHTGREY} South Africa                              & Chlorocebus sabaeus        & $ 0.006$ & $ 0.937$ & $ 0.964$ & $ 0.530$ & $ 0.393$ & $ 0.323$ & $ 0.338$ \\
+                \rowcolor{LIGHTGREY} Saint Kitts                                & Chlorocebus sabaeus        & $ 0.004$ & $ 0.931$ & $ 0.969$ & $ 0.611$ & $ 0.393$ & $ 0.292$ & $ 0.604$ \\
+                \rowcolor{LIGHTGREY} Zambia                             & Chlorocebus sabaeus        & $ 0.006$ & $ 0.941$ & $ 0.963$ & $ 0.506$ & $ 0.408$ & $ 0.309$ & $ 0.252$ \\
+                African                             & Homo sapiens        & $ 0.002$ & $ 0.896$ & $ 0.968$ & $ 0.550$ & $ 0.297$ & $ 0.371$ & $ 0.284$ \\
+                Admixed American                             & Homo sapiens        & $ 0.002$ & $ 0.890$ & $ 0.979$ & $ 0.710$ & $ 0.333$ & $ 0.368$ & $ 0.464$ \\
+                East Asian                             & Homo sapiens        & $ 0.002$ & $ 0.890$ & $ 0.971$ & $ 0.578$ & $ 0.289$ & $ 0.369$ & $ 0.358$ \\
+                European                             & Homo sapiens        & $ 0.002$ & $ 0.891$ & $ 0.980$ & $ 0.739$ & $ 0.345$ & $ 0.368$ & $ 0.499$ \\
+                South Asian                             & Homo sapiens        & $ 0.002$ & $ 0.895$ & $ 0.981$ & $ 0.740$ & $ 0.356$ & $ 0.369$ & $ 0.423$ \\
+                \bottomrule
+            \end{tabular}
+        \end{adjustbox}
+    \end{center}
+    \begin{itemize}
+        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
+        \item \textit{Precision} is the estimation of the selection coefficient at population scale ($\Spop$) given that $\Sphy$ is known.
+        \item  \textit{Recall} is the estimation of $\Sphy$ given selection coefficient at the population scale ($\Spop$) is known.
+        \item \textit{Recall} for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is thus the proportion of beneficial back-mutations among all beneficial mutations.
+    \end{itemize}
+
+    Altogether, comparing this table to tables 1 and S3, we acknowledge that the exact proportion of beneficial back-mutations among all beneficial ones is different whether we included or not substitutions in the terminal lineage for the estimation of $\Spop$.
+    However, we can still see that beneficial back-mutations are positively selected compared to neutral and deleterious ones, and this result is not sensitive to inclusion of substitutions in the terminal lineage.
 
     \newpage
+    \section{Discrete distribution of $\Spop$ at the population scale}
 
-    \section{Distribution of fitness effects}
-    \captionof{figure}{~}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/2bins.Yeast.experimentalDFE.pdf}
-    \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/2bins.AFR.histogramDFE.pdf}
-    \end{minipage}
-    Left panel: distribution of fitness effects experimentally determined in Yeast, data obtained in \textcite{shen_synonymous_2022}.
-    Right panel:  distribution of fitness effects ($\Sphy$) as predicted with mutation-selection codon models, from reconstructed ancestral genome in \textit{Homo sapiens}.
-    The DFE predicted with mutation-selection codon models has a negative mode, consistently with experimental DFEs, meaning that most mutations are effectively deleterious.
+    \subsection{polyDFE model D (discrete distribution)}
+    With polyDFE model D, the DFE of non-synonymous mutations is given as a discrete DFE of $K$ categories (instead of a continuous distribution in model C), where the selection coefficients of each category $i$ ($1 \leq i \leq K$) are fixed parameters $\Spop_i$, and each value $\Spop_i$ has a probability $p_i$ (estimated), with $\sum_{i=1}^{K} p_i =1$.
+    We used $K=6$ with $\Spop_1 = -500$, $\Spop_2 = -4$, $\Spop_3 =-1$, $\Spop_4 = 0$, $\Spop_5 = 1$, $\Spop_6 = 4$.\\
+    For each class of selection $\Sphyclass$, the parameters $p_i$ ($i \in \{ 1 \leq i \leq 6 \}$) were used to compute $\proba [ \SpopDel \given  \Sphyclass] $, $\proba [ \SpopNeu \given \Sphyclass]$, and $\proba [ \SpopBen \given \Sphyclass]$ as:
+    \begin{align}
+        \proba [ \SpopDel \given  \Sphyclass] &= \proba [ \Spop < -1 \given \Sphyclass ] = p_1 + p_2 \label{eq:polyProbaDel} \\
+        \proba [ \SpopNeu \given \Sphyclass] &= \proba [ -1 < \Spop < 1 \given \Sphyclass ] = p_3 + p_4 + p_5,  \\
+        \proba [ \SpopBen \given \Sphyclass] &= p_6. \label{eq:polyProbaAdv}
+    \end{align}
 
+    \subsection{Probabilities of beneficial back-mutations}
+    \begin{center}
+        \captionof{table}{Probability of beneficial back-mutations among all beneficial ones.}
+        \scriptsize
+        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
+            \toprule
+            Population & Species & Watterson's $\thetaSyn$ & $\proba[\SphyBen]$ & $\proba [ \SpopBen ]$ & $\frac{\proba[\SphyBen]}{\proba[ \SpopBen ]}$ & $\proba [ \SpopBen \given \SphyBen]$ & $\proba[\SphyBen\given \SpopBen ]$ \\
+            \midrule
+            \endhead
+            \midrule
+            \multicolumn{8}{r}{{Continued on next page}} \\
+            \midrule
+            \endfoot
+
+            \bottomrule
+            \endlastfoot
+            \rowcolor{LIGHTGREY} Equus c.
+&      Equus caballus &               $ 0.002$ &              $ 0.014$ &              $ 0.006$ &                                          $ 2.230$ &                         $ 0.141$ &                      $ 0.316$ \\
+            Iran &          Bos taurus &               $ 0.002$ &              $ 0.013$ &              $ 0.006$ &                                          $ 2.200$ &                         $ 0.136$ &                      $ 0.298$ \\
+            Uganda &          Bos taurus &               $ 0.005$ &              $ 0.013$ &              $ 0.011$ &                                          $ 1.177$ &                         $ 0.138$ &                      $ 0.162$ \\
+            \rowcolor{LIGHTGREY} Australia &        Capra hircus &               $ 0.003$ &              $ 0.014$ &              $ 0.002$ &                                          $ 6.467$ &                         $ 0.135$ &                      $ 0.871$ \\
+            \rowcolor{LIGHTGREY} France &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.002$ &                                          $ 6.407$ &                         $ 0.132$ &                      $ 0.845$ \\
+            \rowcolor{LIGHTGREY} Iran (C.
+aegagrus) &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.002$ &                                          $ 5.993$ &                         $ 0.129$ &                      $ 0.772$ \\
+            \rowcolor{LIGHTGREY} Iran &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.004$ &                                          $ 3.656$ &                         $ 0.138$ &                      $ 0.506$ \\
+            \rowcolor{LIGHTGREY} Italy &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.002$ &                                          $ 6.216$ &                         $ 0.127$ &                      $ 0.787$ \\
+            \rowcolor{LIGHTGREY} Morocco &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.002$ &                                          $ 6.019$ &                         $ 0.141$ &                      $ 0.848$ \\
+            Iran &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.588$ &                         $ 0.148$ &                      $ 0.087$ \\
+            Iran (O.
+orientalis) &          Ovis aries &               $ 0.009$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.569$ &                         $ 0.143$ &                      $ 0.081$ \\
+            Iran (O.
+vignei) &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.587$ &                         $ 0.127$ &                      $ 0.075$ \\
+            Various &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.588$ &                         $ 0.146$ &                      $ 0.086$ \\
+            Morocco &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.025$ &                                          $ 0.564$ &                         $ 0.145$ &                      $ 0.082$ \\
+            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.002$ &                                          $ 5.689$ &                         $ 0.170$ &                      $ 0.968$ \\
+            \rowcolor{LIGHTGREY} Central Afr.
+Rep.
+& Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.005$ &                                          $ 2.142$ &                         $ 0.156$ &                      $ 0.334$ \\
+            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.002$ &                                          $ 5.910$ &                         $ 0.160$ &                      $ 0.945$ \\
+            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.006$ &                                          $ 1.850$ &                         $ 0.157$ &                      $ 0.290$ \\
+            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.004$ &                                          $ 2.802$ &                         $ 0.163$ &                      $ 0.456$ \\
+            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus &               $ 0.003$ &              $ 0.012$ &              $ 0.002$ &                                          $ 5.396$ &                         $ 0.169$ &                      $ 0.910$ \\
+            \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.005$ &                                          $ 2.154$ &                         $ 0.153$ &                      $ 0.329$ \\
+            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.002$ &                                          $ 5.094$ &                         $ 0.164$ &                      $ 0.834$ \\
+            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.006$ &                                          $ 1.952$ &                         $ 0.153$ &                      $ 0.298$ \\
+            African &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.014$ &                                          $ 0.869$ &                         $ 0.141$ &                      $ 0.123$ \\
+            Admixed American &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.010$ &                                          $ 1.130$ &                         $ 0.161$ &                      $ 0.182$ \\
+            East Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.007$ &                                          $ 1.602$ &                         $ 0.162$ &                      $ 0.259$ \\
+            European &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.009$ &                                          $ 1.336$ &                         $ 0.163$ &                      $ 0.217$ \\
+            South Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.009$ &                                          $ 1.342$ &                         $ 0.163$ &                      $ 0.219$ \\
+        \end{longtable*}
+    \end{center}
+    \begin{itemize}
+        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
+        \item $\proba [ \SphyBen ]$ (eq.~5) is the probability for a new mutation a beneficial back-mutation.
+        These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1, thus toward a more fit amino-acid.
+        \item $\proba [ \SpopBen ]$ (eq.~15) is the probability for a mutation to be beneficial.
+        These mutations have a selection coefficient at the population-scale larger than 1.
+        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale (the \textit{precision}).
+        \item $\proba [ \SphyBen \given \SpopBen]$ (eq.~14) is the probability for a mutation to a beneficial back-mutations, given it is beneficial (the \textit{recall}).
+        This probability is obtained using Bayes' formula.
+    \end{itemize}
     \newpage
 
-    \section{Mutation-selection models: DFE and SFS for each population}\label{sec:mutation-selection-models:-histograms-and-sfs-for-each-population}
-    For each population, the same figure is shown.
+    \subsection{Precision and recall}
+    \captionof{table}{Precision and recall}
+    \begin{center}
+        \begin{adjustbox}{width=\textwidth}
+            \begin{tabular}{||l|l|r||r|r||r|r||r|r||}
+                \toprule
+                \multicolumn{3}{||c||}{} &
+                \multicolumn{2}{c||}{\shortstack{\textbf{Deleterious mutations} \\ $\bm{\SpopDel \coloneqq \Spop<-1}$ \\ $\bm{\SphyDel \coloneqq \Sphy<-1}$}} &
+                \multicolumn{2}{c||}{\shortstack{\textbf{Nearly-neutral mutations} \\ $\bm{\SpopNeu \coloneqq -1<\Spop<1}$ \\ $\bm{\SphyNeu \coloneqq -1<\Sphy<1}$}} &
+                \multicolumn{2}{c||}{\shortstack{\textbf{Beneficial mutations} \\ $\bm{\SpopBen \coloneqq \Spop>1}$ \\ $\bm{\SphyBen \coloneqq \Sphy>1}$}}
+                \\ \hline
+                \textbf{Population} &
+                \textbf{Species} &
+                $\bm{\thetaSyn}$ &
+                \makecell{\textbf{Precision} \\ $\bm{\proba [\SpopDel \given \SphyDel]}$} &
+                \makecell{\textbf{Recall} \\ $\bm{\proba [\SphyDel \given \SpopDel]}$}           &
+                \makecell{\textbf{Precision}      \\ $\bm{\proba [\SpopNeu \given \SphyNeu]}$}                                    &
+                \makecell{\textbf{Recall}          \\ $\bm{\proba [\SphyNeu \given \SpopNeu]}$}                                  &
+                \makecell{\textbf{Precision}          \\ $\bm{\proba [\SpopBen \given \SphyBen]}$}          &
+                \makecell{\textbf{Recall}        \\ $\bm{\proba [\SphyBen \given \SpopBen]}$}
+                \\   \midrule
+                \rowcolor{LIGHTGREY} Equus c. & Equus caballus        & $ 0.002$ & $ 0.895$ & $ 0.969$ & $ 0.645$ & $ 0.315$ & $ 0.141$ & $ 0.316$ \\
+                Iran               & Bos taurus        & $ 0.002$ & $ 0.878$ & $ 0.968$ & $ 0.632$ & $ 0.286$ & $ 0.136$ & $ 0.298$ \\
+                Uganda              & Bos taurus        & $ 0.005$ & $ 0.951$ & $ 0.963$ & $ 0.597$ & $ 0.508$ & $ 0.138$ & $ 0.162$ \\
+                \rowcolor{LIGHTGREY} Australia            & Capra hircus        & $ 0.003$ & $ 0.895$ & $ 0.981$ & $ 0.830$ & $ 0.379$ & $ 0.135$ & $ 0.871$ \\
+                \rowcolor{LIGHTGREY} France                                    & Capra hircus          & $ 0.004$ & $ 0.896$ & $ 0.978$ & $ 0.801$ & $ 0.373$ & $ 0.132$ & $ 0.845$ \\
+                \rowcolor{LIGHTGREY} Iran (C. aegagrus)                    & Capra hircus          & $ 0.004$ & $ 0.913$ & $ 0.971$ & $ 0.711$ & $ 0.383$ & $ 0.129$ & $ 0.772$ \\
+                \rowcolor{LIGHTGREY} Iran                        & Capra hircus          & $ 0.004$ & $ 0.949$ & $ 0.968$ & $ 0.655$ & $ 0.481$ & $ 0.138$ & $ 0.506$ \\
+                \rowcolor{LIGHTGREY} Italy                                 & Capra hircus          & $ 0.004$ & $ 0.894$ & $ 0.979$ & $ 0.814$ & $ 0.373$ & $ 0.127$ & $ 0.787$ \\
+                \rowcolor{LIGHTGREY} Morocco                                 & Capra hircus          & $ 0.004$ & $ 0.951$ & $ 0.972$ & $ 0.709$ & $ 0.504$ & $ 0.141$ & $ 0.848$ \\
+                Iran           & Ovis aries & $ 0.007$ & $ 0.980$ & $ 0.956$ & $ 0.456$ & $ 0.799$ & $ 0.148$ & $ 0.087$ \\
+                Iran (O. orientalis)  & Ovis aries & $ 0.009$ & $ 0.979$ & $ 0.955$ & $ 0.454$ & $ 0.798$ & $ 0.143$ & $ 0.081$ \\
+                Iran (O. vignei)           & Ovis aries & $ 0.007$ & $ 0.974$ & $ 0.957$ & $ 0.483$ & $ 0.729$ & $ 0.127$ & $ 0.075$ \\
+                Various             & Ovis aries & $ 0.008$ & $ 0.979$ & $ 0.958$ & $ 0.500$ & $ 0.813$ & $ 0.146$ & $ 0.086$ \\
+                Morocco              & Ovis aries & $ 0.008$ & $ 0.980$ & $ 0.952$ & $ 0.392$ & $ 0.774$ & $ 0.145$ & $ 0.082$ \\
+                \rowcolor{LIGHTGREY} Barbados              & Chlorocebus sabaeus & $ 0.004$ & $ 0.880$ & $ 0.984$ & $ 0.854$ & $ 0.354$ & $ 0.170$ & $ 0.968$ \\
+                \rowcolor{LIGHTGREY} Central Afr. Rep.       & Chlorocebus sabaeus & $ 0.006$ & $ 0.932$ & $ 0.968$ & $ 0.634$ & $ 0.413$ & $ 0.156$ & $ 0.334$ \\
+                \rowcolor{LIGHTGREY} Ethiopia        & Chlorocebus sabaeus & $ 0.005$ & $ 0.877$ & $ 0.980$ & $ 0.810$ & $ 0.337$ & $ 0.160$ & $ 0.945$ \\
+                \rowcolor{LIGHTGREY} Gambia             & Chlorocebus sabaeus & $ 0.005$ & $ 0.947$ & $ 0.977$ & $ 0.745$ & $ 0.518$ & $ 0.157$ & $ 0.290$ \\
+                \rowcolor{LIGHTGREY} Kenya                                 & Chlorocebus sabaeus        & $ 0.005$ & $ 0.903$ & $ 0.969$ & $ 0.664$ & $ 0.343$ & $ 0.163$ & $ 0.456$ \\
+                \rowcolor{LIGHTGREY} Nevis                        & Chlorocebus sabaeus        & $ 0.003$ & $ 0.880$ & $ 0.984$ & $ 0.861$ & $ 0.357$ & $ 0.169$ & $ 0.910$ \\
+                \rowcolor{LIGHTGREY} South Africa                              & Chlorocebus sabaeus        & $ 0.006$ & $ 0.931$ & $ 0.967$ & $ 0.615$ & $ 0.401$ & $ 0.153$ & $ 0.329$ \\
+                \rowcolor{LIGHTGREY} Saint Kitts                                & Chlorocebus sabaeus        & $ 0.004$ & $ 0.883$ & $ 0.982$ & $ 0.834$ & $ 0.355$ & $ 0.164$ & $ 0.834$ \\
+                \rowcolor{LIGHTGREY} Zambia                             & Chlorocebus sabaeus        & $ 0.006$ & $ 0.896$ & $ 0.969$ & $ 0.659$ & $ 0.332$ & $ 0.153$ & $ 0.298$ \\
+                African                             & Homo sapiens        & $ 0.002$ & $ 0.946$ & $ 0.971$ & $ 0.630$ & $ 0.486$ & $ 0.141$ & $ 0.123$ \\
+                Admixed American                             & Homo sapiens        & $ 0.002$ & $ 0.929$ & $ 0.972$ & $ 0.636$ & $ 0.410$ & $ 0.161$ & $ 0.182$ \\
+                East Asian                             & Homo sapiens        & $ 0.002$ & $ 0.937$ & $ 0.973$ & $ 0.647$ & $ 0.429$ & $ 0.162$ & $ 0.259$ \\
+                European                             & Homo sapiens        & $ 0.002$ & $ 0.937$ & $ 0.973$ & $ 0.643$ & $ 0.433$ & $ 0.163$ & $ 0.217$ \\
+                South Asian                             & Homo sapiens        & $ 0.002$ & $ 0.939$ & $ 0.972$ & $ 0.639$ & $ 0.439$ & $ 0.163$ & $ 0.219$ \\
+                \bottomrule
+            \end{tabular}
+        \end{adjustbox}
+    \end{center}
     \begin{itemize}
-        \item Top-left panel: Distribution of fitness effects ($\Sphy$), predicted for all possible mutations away from the ancestral human genome.
-        Mutations are divided into 5 classes of selection: severely deleterious (blue), deleterious (green), weakly deleterious (light green), weakly beneficial (yellow) and beneficial (red, supposedly beneficial back-mutations).
-        \item Top-right panel: Histogram of predicted selection coefficients ($\Sphy$) for all observed mutations in a sample of 8 individuals (out of 512 in the original dataset) of African descent.
-        If they are less mutations observed than expected, this class is thus undergoing purifying selection.
-        \item Bottom-left panel: The site-frequency spectrum (SFS) represents the proportion of mutations (y-axis) with a given number of derived alleles in the population (x-axis).
-        SFS are drawn for a random sample of 16 alleles (mean in solid line and standard deviation in filled color) for each class of selection coefficient and for synonymous mutations which are supposedly neutral (black).
-        At high frequencies, supposedly severally deleterious mutations are underrepresented.
-        \item Bottom-right panel:For each class of selection (and for the set of all non-synonymous mutations), information from the SFS and the expected total mutation rate are combined at the population-genetic scale to estimate the proportion of beneficial mutations $\PpolyAdv$, of nearly-neutral mutations $\PpolyNeutral$ and of deleterious mutations $\PpolyDel$.
+        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
+        \item \textit{Precision} is the estimation of the selection coefficient at population scale ($\Spop$) given that $\Sphy$ is known.
+        \item \textit{Recall} is the estimation of $\Sphy$ given selection coefficient at the population scale ($\Spop$) is known.
+        \item \textit{Recall} for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is thus the proportion of beneficial back-mutations among all beneficial mutations.
     \end{itemize}
 
-    \input{include-MutSel-non-adaptive}
+    Altogether, comparing this table to tables 1 and S3, we acknowledge that the exact proportion of beneficial back-mutations among all beneficial ones is dependent on the model used to estimate the DFE.
+    However, we can still see that beneficial back-mutations are positively selected compared to neutral and deleterious ones, and this result is not sensitive to the underlying DFE at the population scale.
 
-    \newpage
-    \section{References}
-    \printbibliography[heading=none]
+    %\section{References}
+    %\printbibliography[heading=none]
 
+    %    \section{Distribution of fitness effects}
+    %    \captionof{figure}{~}
+    %    \begin{minipage}{0.49\linewidth}
+    %        \includegraphics[width=\linewidth, page=1]{artworks/2bins.Yeast.experimentalDFE.pdf}
+    %    \end{minipage}
+    %    \begin{minipage}{0.49\linewidth}
+    %        \includegraphics[width=\linewidth, page=1]{artworks/2bins.AFR.histogramDFE.pdf}
+    %    \end{minipage}
+    %    Left panel: distribution of fitness effects experimentally determined in Yeast, data obtained in \textcite{shen_synonymous_2022}.
+    %    Right panel:  distribution of fitness effects ($\Sphy$) as predicted with mutation-selection codon models, from reconstructed ancestral genome in \textit{Homo sapiens}.
+    %    The DFE predicted with mutation-selection codon models has a negative mode, consistently with experimental DFEs, meaning that most mutations are effectively deleterious.
 \end{document}

### 2023-05-03 manuscript/main.tex
Manuscript ready to submit.

@@
     Additionally, polymorphism data are available for many species~\cite{howe_ensembl_2021}, as are high quality protein-coding DNA alignments across the genome~\cite{ranwez_orthomam_2007, scornavacca_orthomam_2019}.
-    By performing our analysis on 14,509 protein-coding orthologous genes across 87 species, we focus on sequences under functional constraints across mammals.
+    By performing our analysis on 14,509 orthologous protein-coding genes across 87 species, we focus on sequences under functional constraints across mammals.
     For each gene, fitting the mutation-selection model to the multi-species sequence alignment, assuming that the underlying fitness landscape is stable along the phylogenetic tree, allows us to obtain relative fitnesses for all amino acids for each site of the alignment (fig.~\ref{fig:method}A).
@@
 
-    Mutations predicted as $\SphyNeu$ were effectively composed of a mix of neutral and selected mutations with varying \textit{precision} (36--73\%) and \textit{recall} (30--45\%) across the different populations (table~\ref{table:proba}, fig.~\ref{fig:homo-afr-results}D for Humans).
+    Mutations predicted as $\SphyNeu$ were effectively composed of a mix of neutral and selected mutations with varying \textit{precision} (36--73\%) and \textit{recall} (30--45\%) across the different populations (table~\ref{table:proba}, fig.~\ref{fig:homo-afr-results}D for humans).
     The variable proportions between populations can be explained by the effective number of individuals in the population ($\Ne$), a major driver of selection efficacy.
@@
 
-    Finally, mutations predicted to be beneficial back-mutations based on the selection coefficients at the phylogenetic scale ($\SphyBen$) were indeed beneficial for individuals bearing them, with a \textit{precision} (fig.~\ref{fig:method}F) in the range of 15--86\% (table~\ref{table:proba} and fig.~\ref{fig:homo-afr-results}D for humans).
+    Finally, mutations predicted to be beneficial back-mutations based on the selection coefficients at the phylogenetic scale ($\SphyBen$) were indeed beneficial for individuals bearing them, with a \textit{precision} (fig.~\ref{fig:method}F) in the range of 13--86\% (table~\ref{table:proba} and fig.~\ref{fig:homo-afr-results}D for humans).
     This result confirms that selection towards amino acids restoring existing functions is ongoing in these populations.
@@
     In other words, the \textit{recall} value quantifies the number of beneficial mutations restoring damaged genomes instead of creating adaptive innovations.
-    Across the 28 populations, this proportion is in the range of 13--80\% (table~\ref{table:proba}).
+    Across the 28 populations, this proportion is in the range of 11--81\% (table~\ref{table:proba}).
 
@@
     We have tested this hypothesis and found that these back-mutations ($\SphyBen \coloneqq \Sphy > 1 $) are indeed beneficial in extant populations.
-    We estimated that between 13 and 80\% of all beneficial mutations in mammalian populations have not been driven by adaptation but instead have reversed deleterious substitutions which have accumulated along the phylogeny.
+    We estimated that between 11 and 81\% of all beneficial mutations in mammalian populations have not been driven by adaptation but instead have reversed deleterious substitutions which have accumulated along the phylogeny.
+    More specifically, in three out of four populations analyzed, the percentage of beneficial mutations estimated to be back-mutations falls between 20 and 40\%.
     These results suggest that many beneficial mutations are non-adaptive but rather restore ancestral states of higher fitness.
@@
     However, adaptation is not the only factor hindering the detection of beneficial back-mutations; data quality and potentially inadequate modeling choices of both the fitness landscape and the DFE might also lead to missed predictions.
+    Given that our amino-acid fitness landscapes are site-specific and also independent of one another, missed prediction can be also due to epistasis where the fitness landscape at a given site depends on the residue present at other sites~\cite{starr_epistasis_2016, park_epistatic_2022}.
     Moreover, a mutation inferred as nearly-neutral at the phylogenetic scale ($\SphyNeu$) but positively selected at the population scale ($\SpopBen$) will also be considered a missed prediction, even if this discrepancy could just be due to a population size expansion~\cite{lanfear_population_2014, jones_shifting_2017, platt_protein_2018}.
@@
 
-    A long-standing debate in molecular evolution is whether the variations we observe between species in protein-coding genes are primarily due to nearly-neutral mutations reaching fixation by drift or primarily due to adaptation~\cite{kimura_evolutionary_1968,kern_neutral_2018,jensen_importance_2019,gillespie_substitution_1994,Ohta1992}.
+    A long-standing debate in molecular evolution is whether the variations we observe between species in protein-coding genes are primarily due to nearly-neutral mutations reaching fixation by drift or primarily due to adaptation~\cite{kimura_evolutionary_1968,jensen_importance_2019,gillespie_substitution_1994,Ohta1992}.
     Here we provide evidence that in mammalian orthologs, many substitutions occur through fixation of both deleterious mutations and beneficial back-mutations.
@@
     \begin{equation}
-        L_{\text{syn}} = L_{\text{tot}} \frac{\mu_{\text{syn}}}{\mu_{\text{tot}}}.\label{eq:mutation-opp}
+        L_{\text{syn}} = L_{\text{tot}} \frac{\mu_{\text{syn}}}{\mu_{\text{tot}}}.
     \end{equation}
@@
     \begin{equation}
-        L \left( \Sphyclass \right) = L_{\text{tot}} \frac{\mu\left( \Sphyclass \right)}{\mu_{\text{tot}}}.
+        L \left( \Sphyclass \right) = L_{\text{tot}} \frac{\mu\left( \Sphyclass \right)}{\mu_{\text{tot}}}.\label{eq:mutation-opp}
     \end{equation}
@@
     \begin{equation}
-        \proba[\Sphyclass] = \frac{L\left( \Sphyclass \right)}{\sum_{\SphyclassAlt\in \{\SphyDel, \SphyNeu, \SphyBen \} } L\left(\SphyclassAlt \right)}.
-        \label{eq:proba-dfe-mutsel}
+        \proba[\Sphyclass] = \frac{L\left( \Sphyclass \right)}{\sum_{\SphyclassAlt\in \{\SphyDel, \SphyNeu, \SphyBen \} } L\left(\SphyclassAlt \right)}.\label{eq:proba-dfe-mutsel}
     \end{equation}

### 2023-05-03 manuscript/scifile.tex
Manuscript ready to submit.

@@
 Additionally, polymorphism data are available for many species~\cite{howe_ensembl_2021}, as are high quality protein-coding DNA alignments across the genome~\cite{scornavacca_orthomam_2019}.
-By performing our analysis on 14,509 protein-coding orthologous genes across 87 species, we focus on sequences under functional constraints across mammals.
+By performing our analysis on 14,509 orthologous protein-coding genes across 87 species, we focus on sequences under functional constraints across mammals.
 For each gene, fitting the mutation-selection model to the multi-species sequence alignment, assuming that the underlying fitness landscape is stable along the phylogenetic tree, allows us to obtain relative fitnesses for all amino acids for each site of the alignment (fig.~\ref{fig:method}A).
@@
 
-Mutations predicted as $\SphyNeu$ were effectively composed of a mix of neutral and selected mutations with varying \textit{precision} (36--73\%) and \textit{recall} (30--45\%) across the different populations (table~\ref{table:proba}, fig.~\ref{fig:homo-afr-results}D for Humans).
+Mutations predicted as $\SphyNeu$ were effectively composed of a mix of neutral and selected mutations with varying \textit{precision} (36--73\%) and \textit{recall} (30--45\%) across the different populations (table~\ref{table:proba}, fig.~\ref{fig:homo-afr-results}D for humans).
 The variable proportions between populations can be explained by the effective number of individuals in the population ($\Ne$), a major driver of selection efficacy.
@@
 
-Finally, mutations predicted to be beneficial back-mutations based on the selection coefficients at the phylogenetic scale ($\SphyBen$) were indeed beneficial for individuals bearing them, with a \textit{precision} (fig.~\ref{fig:method}F) in the range of 15--86\% (table~\ref{table:proba} and fig.~\ref{fig:homo-afr-results}D for humans).
+Finally, mutations predicted to be beneficial back-mutations based on the selection coefficients at the phylogenetic scale ($\SphyBen$) were indeed beneficial for individuals bearing them, with a \textit{precision} (fig.~\ref{fig:method}F) in the range of 13--86\% (table~\ref{table:proba} and fig.~\ref{fig:homo-afr-results}D for humans).
 This result confirms that selection towards amino acids restoring existing functions is ongoing in these populations.
@@
 In other words, the \textit{recall} value quantifies the number of beneficial mutations restoring damaged genomes instead of creating adaptive innovations.
-Across the 28 populations, this proportion is in the range of 13--80\% (table~\ref{table:proba}).
+Across the 28 populations, this proportion is in the range of 11--81\% (table~\ref{table:proba}).
 
@@
 We have tested this hypothesis and found that these back-mutations ($\SphyBen \coloneqq \Sphy > 1 $) are indeed beneficial in extant populations.
-We estimated that between 13 and 80\% of all beneficial mutations in mammalian populations have not been driven by adaptation but instead have reversed deleterious substitutions which have accumulated along the phylogeny.
+We estimated that between 11 and 81\% of all beneficial mutations in mammalian populations have not been driven by adaptation but instead have reversed deleterious substitutions which have accumulated along the phylogeny.
+More specifically, in three out of four populations analyzed, the percentage of beneficial mutations estimated to be back-mutations falls between 20 and 40\%.
 These results suggest that many beneficial mutations are non-adaptive but rather restore ancestral states of higher fitness.
@@
 However, adaptation is not the only factor hindering the detection of beneficial back-mutations; data quality and potentially inadequate modeling choices of both the fitness landscape and the DFE might also lead to missed predictions.
+Given that our amino-acid fitness landscapes are site-specific and also independent of one another, missed prediction can be also due to epistasis where the fitness landscape at a given site depends on the residue present at other sites~\cite{starr_epistasis_2016, park_epistatic_2022}.
 Moreover, a mutation inferred as nearly-neutral at the phylogenetic scale ($\SphyNeu$) but positively selected at the population scale ($\SpopBen$) will also be considered a missed prediction, even if this discrepancy could just be due to a population size expansion~\cite{lanfear_population_2014, jones_shifting_2017, platt_protein_2018}.
@@
 
-A long-standing debate in molecular evolution is whether the variations we observe between species in protein-coding genes are primarily due to nearly-neutral mutations reaching fixation by drift or primarily due to adaptation~\cite{kimura_evolutionary_1968,kern_neutral_2018,jensen_importance_2019,gillespie_substitution_1994,Ohta1992}.
+A long-standing debate in molecular evolution is whether the variations we observe between species in protein-coding genes are primarily due to nearly-neutral mutations reaching fixation by drift or primarily due to adaptation~\cite{kimura_evolutionary_1968,jensen_importance_2019,gillespie_substitution_1994,Ohta1992}.
 Here we provide evidence that in mammalian orthologs, many substitutions occur through fixation of both deleterious mutations and beneficial back-mutations.

### 2023-08-21 manuscript/main-revision.tex
Run the experiment while filtering for ontologies. Prepare for PGLS.

--- 2023-05-03 manuscript/main.tex
@@
 % The submission checklist is available at:
-% https://docs.google.com/document/d/1aHCF1on0mHTK2DoroPCLP_xto4xwHnGJCGwaL1Vm2UE/edit?usp=sharing
+% https://docs.google.com/document/d/1SScaqEAgZGpeaXxpWPDh1NOLaDDLLmkGOYgaGvbY-4o/edit#
+% Response to reviewers at:
+% https://docs.google.com/document/d/1kzt4uf6GgmuAVHx6-LQyzFuee9biyaWoMV6RNO6lSzI/edit?usp=sharing
 
@@
         Mutations can be beneficial by bringing innovation to their bearer, allowing them to adapt to environmental change.
-        However, mutations can also be beneficial because they are reverting previous deleterious changes, simply restoring pre-existing functions.
-        By integrating phylogenomic and population data in mammals, we estimated the contribution of beneficial back-mutations to molecular evolution, which had remained widely overlooked so far.
-        Applying a mutation-selection model, we estimated amino acid fitness landscapes for mammalian protein-coding genes.
-        Assuming these fitness landscapes do not change, any beneficial mutation is necessarily a back-mutation.
-        We confirmed that these beneficial back-mutations are positively selected in extant populations and demonstrated that a substantial part of ongoing positive selection is not driven by adaptation to environmental change.
+These mutations are typically unpredictable since they respond to an unforeseen change in the environment.
+However, mutations can also be beneficial because they are simply restoring an ancestral sequence of higher fitness that was lost due to genetic drift.
+In contrast to adaptive mutations, these beneficial back-mutations can be predicted if the underlying fitness landscape is stable and known.
+The contribution of such beneficial back-mutations to molecular evolution has been widely neglected mainly because their detection is very challenging.
+We have here reconstructed protein-coding-gene fitness landscapes shared between mammals, using mutation-selection models and a multi-species alignments across 87 mammals.
+These fitness landscapes have allowed us to predict the fitness effect of polymorphisms found in 28 mammalian populations.
+Using methods that quantify selection at the population level, we have confirmed that beneficial back-mutations are indeed positively selected in extant populations.
+We observe that beneficial back-mutations represent between 20\% and 40\% of all beneficial mutations in 21 of 28 populations analyzed, showing that a substantial part of ongoing positive selection is not driven by adaptation to environmental change in mammals.
+Our work shows that deleterious substitutions are accumulating in mammals and are being reverted, generating a balance in which genomes are damaged and restored simultaneously at different loci, ultimately resulting in a widespread signal of non-adaptive positive selection.
     \end{abstract}
@@
 
+    \section*{Significance statement}
+    The extent to which adaptation to changing environments is shaping genomes is a central question in molecular evolution.
+To quantify the rate of adaptation, population geneticists have typically used signatures of positive selection.
+However, mutations restoring an ancestral sequence of higher fitness lost by genetic drift are also positively selected, but they do not respond to a change in the environment.
+In this study, we have managed to distinguish beneficial mutations that are due to changing environments and those that are restoring pre-existing functions in mammals.
+We show that a substantial proportion of beneficial mutations cannot be interpreted as adaptive.
+
+    \section*{Introduction}
     Adaptation is one of the main processes shaping the diversity of forms and functions across the tree of life~\cite{darwin_origin_1859}.
@@
 
-    %In this study, we seek empirical evidence for beneficial back-mutations and test long-standing related questions, such as how common they are and what the probability is for any beneficial mutation observed in current populations to be a back-mutation.
-    %By addressing these questions, we provide novel insight into the process of adaptation and, more broadly, into how natural selection has affected protein-coding DNA sequences throughout evolution.
     \subsection*{Fitness landscape reconstruction}
@@
     Importantly, because mutation-selection models at the phylogenetic scale are based on population-genetics equations, their estimates of selection coefficients are directly interpretable as fitness effects for an individual within a population.
-    %These methods account for phylogenetic relationships, the structure of the genetic code and accommodate for underlying mutational biases~\cite{rodrigue_mechanistic_2010, tamuri_estimating_2012, latrille_improved_2022}.
 
@@
 
-    \begin{figure*}[!ht]
-        \centering
-        \includegraphics[width=\textwidth, page=1] {artworks/figure.fitness-landscape}
-        \caption{
-            (A \& B) For a given codon position of a protein-coding DNA sequence, amino acids (x-axis) have different fitness values (y-axis).
-            Under a fluctuating fitness landscape (A), these fitnesses change with time.
-            The protein sequence follows the moving target defined by the amino-acid fitnesses.
-Since substitutions are preferentially accepted if they are in the direction of this target, substitutions are, on average, adaptive.
-            At the phylogenetic scale (C), beneficial substitutions are common (positive signs), promoting phenotype diversification across species.
-            Under a stable fitness landscape (B), most mutations reaching fixation are either slightly deleterious reaching fixation due to drift or are beneficial back-mutations restoring a more optimal amino acid.
-            At the phylogenetic scale (D), deleterious substitutions (negative signs) are often reverted via beneficial back-mutations (positive signs), promoting phenotype stability and preserving well-established biological systems.
-            Even though, individually, any back-mutation might have a small beneficial effect on its bearer, we expect beneficial back-mutations to be scattered across the genome and the genome-wide signature of beneficial back-mutations to be detectable and quantifiable.}
-        \label{fig:fitness-landscape}
-    \end{figure*}
-
-    \begin{figure*}[!ht]
-        \centering
-        \includegraphics[width=\textwidth, page=1] {artworks/figure.method.proba}
-        \caption{
-            Selection coefficients at the phylogenetic and population scales.
-            At the phylogenetic scale (A), we estimated the amino-acid fitness for each site from protein-coding DNA alignments using mutation-selection codon models.
-            For every possible mutation, the difference in amino acid fitness before and after the mutation allows us to compute the selection coefficient at the phylogenetic scale ($\Sphy$).
-            Depending on $\Sphy$ (B) mutations can be predicted as deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) or beneficial back-mutations ($\SphyBen$) toward a fitter amino acid and repairing existing functions.
-            At the population scale, each observed single nucleotide polymorphism (SNP) segregating in the population can also be classified according to its $\Sphy$ value (C).
-            Occurrence and frequency in the population of non-synonymous polymorphisms, contrasted to synonymous polymorphisms (deemed neutral) is used to estimate selection coefficients (D-E) at the population scale ($\Spop$), for each class of selection ($\SphyDel$, $\SphyNeu$, $\SphyBen$).
-            We can thus assess whether $\Sphy$ predicts $\Spop$ and compute \textit{precision} (F) and \textit{recall} (G) for each class.
-            The \textit{recall} value for class $\SphyBen$ is the probability of back-mutations among all beneficial ones (G).
-        }
-        \label{fig:method}
-    \end{figure*}
+    \section*{Results}
 
@@
 
-    \begin{figure*}[!ht]
-        \centering
-        \includegraphics[width=\textwidth, page=1] {artworks/figure.homo-afr-results}
-        \caption{
-            (A) Distribution of scaled selection coefficients ($\Sphy$), predicted for all possible mutations away from the ancestral human genome.
-            Mutations are divided into three classes of selection: deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial ($\SphyBen$, supposedly beneficial back-mutations).
-            (B) Distribution of scaled selection coefficients ($\Sphy$) for all observed substitutions along the \textit{Homo} branch after the \textit{Homo}-\textit{Pan} split.
-            If there are fewer substitutions than expected, this class is thus undergoing purifying selection, as is the case for $\SphyDel$.
-            (C) The site-frequency spectrum (SFS) in humans of African descent for a random sample of 16 alleles (means in solid lines and standard deviations in color shades) for each class of selection and for synonymous mutations, supposedly neutral (black).
-The SFS represents the proportion of mutations (y-axis) with a given number of derived alleles in the population (x-axis).
-            At high frequencies, deleterious mutations are underrepresented.
-            (D) Proportion of beneficial $\ProbaPopDel$, nearly-neutral $\ProbaPopNeu$, and deleterious mutations $\ProbaPopBen$ estimated at the population scale for each class of selection at the phylogenetic scale.
-Proportions depicted here are not weighted by their mutational opportunities.
-        }
-        \label{fig:homo-afr-results}
-    \end{figure*}
-
-    \begin{table*}[tb]
-        \centering
-        \begin{adjustbox}{width=\textwidth}
-            \begin{tabular}{||l|l|r||r|r||r|r||r|r||}
-                \toprule
-                \multicolumn{3}{||c||}{} &
-                \multicolumn{2}{c||}{\shortstack{\textbf{Deleterious mutations} \\ $\bm{\SpopDel \coloneqq \Spop<-1}$ \\ $\bm{\SphyDel \coloneqq \Sphy<-1}$}} &
-                \multicolumn{2}{c||}{\shortstack{\textbf{Nearly-neutral mutations} \\ $\bm{\SpopNeu \coloneqq -1<\Spop<1}$ \\ $\bm{\SphyNeu \coloneqq -1<\Sphy<1}$}} &
-                \multicolumn{2}{c||}{\shortstack{\textbf{Beneficial mutations} \\ $\bm{\SpopBen \coloneqq \Spop>1}$ \\ $\bm{\SphyBen \coloneqq \Sphy>1}$}}
-                \\ \hline
-                \textbf{Population} &
-                \textbf{Species} &
-                $\bm{\thetaSyn}$ &
-                \makecell{\textbf{Precision} \\ $\bm{\proba [\SpopDel \given \SphyDel]}$} &
-                \makecell{\textbf{Recall} \\ $\bm{\proba [\SphyDel \given \SpopDel]}$}            &
-                \makecell{\textbf{Precision}      \\ $\bm{\proba [\SpopNeu \given \SphyNeu]}$}                                    &
-                \makecell{\textbf{Recall}          \\ $\bm{\proba [\SphyNeu \given \SpopNeu]}$}                                  &
-                \makecell{\textbf{Precision}          \\ $\bm{\proba [\SpopBen \given \SphyBen]}$}          &
-                \makecell{\textbf{Recall}        \\ $\bm{\proba [\SphyBen \given \SpopBen]}$}
-                \\   \midrule
-                \rowcolor{LIGHTGREY}              Equus c. & Equus caballus        & $ 0.002$ & $ 0.908$ & $ 0.976$ & $ 0.730$ & $ 0.383$ & $ 0.580$ & $ 0.809$ \\
-                Iran               & Bos taurus        & $ 0.002$ & $ 0.898$ & $ 1.000$ & $ 0.632$ & $ 0.340$ & $ 0.857$ & $ 0.277$ \\
-                Uganda              & Bos taurus        & $ 0.005$ & $ 0.942$ & $ 0.963$ & $ 0.497$ & $ 0.393$ & $ 0.488$ & $ 0.483$ \\
-                \rowcolor{LIGHTGREY} Australia            & Capra hircus        & $ 0.003$ & $ 0.934$ & $ 0.966$ & $ 0.524$ & $ 0.425$ & $ 0.368$ & $ 0.196$ \\
-                \rowcolor{LIGHTGREY} France                                    & Capra hircus          & $ 0.004$ & $ 0.936$ & $ 0.965$ & $ 0.506$ & $ 0.412$ & $ 0.368$ & $ 0.211$ \\
-                \rowcolor{LIGHTGREY} Iran (C. aegagrus)                    & Capra hircus          & $ 0.004$ & $ 0.940$ & $ 0.961$ & $ 0.478$ & $ 0.438$ & $ 0.221$ & $ 0.114$ \\
-                \rowcolor{LIGHTGREY} Iran                        & Capra hircus          & $ 0.004$ & $ 0.945$ & $ 0.960$ & $ 0.419$ & $ 0.400$ & $ 0.368$ & $ 0.211$ \\
-                \rowcolor{LIGHTGREY} Italy                                 & Capra hircus          & $ 0.004$ & $ 0.937$ & $ 0.963$ & $ 0.548$ & $ 0.426$ & $ 0.270$ & $ 0.220$ \\
-                \rowcolor{LIGHTGREY} Morocco                                 & Capra hircus          & $ 0.004$ & $ 0.942$ & $ 0.964$ & $ 0.522$ & $ 0.428$ & $ 0.368$ & $ 0.276$ \\
-                Iran           & Ovis aries & $ 0.007$ & $ 0.953$ & $ 0.954$ & $ 0.450$ & $ 0.406$ & $ 0.169$ & $ 0.392$ \\
-                Iran (O. orientalis)  & Ovis aries & $ 0.009$ & $ 0.958$ & $ 0.953$ & $ 0.417$ & $ 0.431$ & $ 0.153$ & $ 0.180$ \\
-                Iran (O. vignei)           & Ovis aries & $ 0.007$ & $ 0.960$ & $ 0.951$ & $ 0.360$ & $ 0.449$ & $ 0.195$ & $ 0.133$ \\
-                Various             & Ovis aries & $ 0.008$ & $ 0.955$ & $ 0.954$ & $ 0.435$ & $ 0.426$ & $ 0.190$ & $ 0.228$ \\
-                Morocco              & Ovis aries & $ 0.008$ & $ 0.956$ & $ 0.955$ & $ 0.449$ & $ 0.410$ & $ 0.136$ & $ 0.353$ \\
-                \rowcolor{LIGHTGREY} Barbados              & Chlorocebus sabaeus & $ 0.004$ & $ 0.925$ & $ 0.969$ & $ 0.536$ & $ 0.377$ & $ 0.565$ & $ 0.306$ \\
-                \rowcolor{LIGHTGREY} Central Afr. Rep.       & Chlorocebus sabaeus & $ 0.006$ & $ 0.940$ & $ 0.964$ & $ 0.495$ & $ 0.404$ & $ 0.429$ & $ 0.274$ \\
-                \rowcolor{LIGHTGREY} Ethiopia        & Chlorocebus sabaeus & $ 0.005$ & $ 0.925$ & $ 0.969$ & $ 0.560$ & $ 0.400$ & $ 0.462$ & $ 0.239$ \\
-                \rowcolor{LIGHTGREY} Gambia             & Chlorocebus sabaeus & $ 0.005$ & $ 0.934$ & $ 0.969$ & $ 0.610$ & $ 0.409$ & $ 0.486$ & $ 0.774$ \\
-                \rowcolor{LIGHTGREY} Kenya                                 & Chlorocebus sabaeus        & $ 0.005$ & $ 0.938$ & $ 0.965$ & $ 0.519$ & $ 0.434$ & $ 0.478$ & $ 0.243$ \\
-                \rowcolor{LIGHTGREY} Nevis                        & Chlorocebus sabaeus        & $ 0.003$ & $ 0.923$ & $ 0.970$ & $ 0.609$ & $ 0.393$ & $ 0.516$ & $ 0.393$ \\
-                \rowcolor{LIGHTGREY} South Africa                              & Chlorocebus sabaeus        & $ 0.006$ & $ 0.935$ & $ 0.965$ & $ 0.542$ & $ 0.409$ & $ 0.490$ & $ 0.360$ \\
-                \rowcolor{LIGHTGREY} Saint Kitts                                & Chlorocebus sabaeus        & $ 0.004$ & $ 0.926$ & $ 0.969$ & $ 0.562$ & $ 0.377$ & $ 0.515$ & $ 0.367$ \\
-                \rowcolor{LIGHTGREY} Zambia                             & Chlorocebus sabaeus        & $ 0.006$ & $ 0.937$ & $ 0.965$ & $ 0.494$ & $ 0.413$ & $ 0.499$ & $ 0.249$ \\
-                African                             & Homo sapiens        & $ 0.002$ & $ 0.899$ & $ 0.970$ & $ 0.571$ & $ 0.334$ & $ 0.678$ & $ 0.319$ \\
-                Admixed American                             & Homo sapiens        & $ 0.002$ & $ 0.888$ & $ 0.972$ & $ 0.581$ & $ 0.301$ & $ 0.635$ & $ 0.361$ \\
-                East Asian                             & Homo sapiens        & $ 0.002$ & $ 0.894$ & $ 0.973$ & $ 0.583$ & $ 0.335$ & $ 0.611$ & $ 0.233$ \\
-                European                             & Homo sapiens        & $ 0.002$ & $ 0.896$ & $ 0.972$ & $ 0.581$ & $ 0.350$ & $ 0.619$ & $ 0.217$ \\
-                South Asian                             & Homo sapiens        & $ 0.002$ & $ 0.898$ & $ 0.972$ & $ 0.580$ & $ 0.354$ & $ 0.628$ & $ 0.222$ \\
-                \bottomrule
-            \end{tabular}
-        \end{adjustbox}
-        \caption{
-            \textit{Precision} and \textit{recall} for estimated selection coefficient of mutations given by mutation-selection models ($\Sphy$).
-            \textit{Precision} is the estimation of the selection coefficient at population scale ($\Spop$) given that $\Sphy$ is known.
-            Conversely, \textit{recall} is the estimation of $\Sphy$ given selection coefficient at the population scale ($\Spop$) is known.
-            \textit{Recall} for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is thus the proportion of beneficial back-mutations among all beneficial mutations.
-            Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        }
-        \label{table:proba}
-    \end{table*}
-
     \section*{Discussion}
@@
     We estimated that between 11 and 81\% of all beneficial mutations in mammalian populations have not been driven by adaptation but instead have reversed deleterious substitutions which have accumulated along the phylogeny.
-    More specifically, in three out of four populations analyzed, the percentage of beneficial mutations estimated to be back-mutations falls between 20 and 40\%.
+    More specifically, in 21 out of 28 populations analyzed, the percentage of beneficial mutations estimated to be back-mutations falls between 20 and 40\%.
     These results suggest that many beneficial mutations are non-adaptive but rather restore ancestral states of higher fitness.
@@
 
-    %We have to acknowledge that the mammalian case study might also not be representative of other clades.
-    %Indeed, long-term population sizes are relatively small in mammals, which allow large amounts of deleterious mutations to be fixed, and thus, a lot of opportunities for beneficial back-mutations to arise.
-    %It would thus be of great interest to reproduce our analysis with other clades, such as \textit{Drosophila} or \textit{Saccharomyces} which have higher effective population sizes.
-    %Indeed when the effective population size is higher, the number of effectively neutral mutational opportunities should be reduced.
-    %Allowing for changes in effective population sizes along the phylogeny have been developed~\cite{latrille_inferring_2021}, but are, for the moment, too computationally intensive to be performed genome-wide.
-    %This reduction should mechanistically increase the proportion of adaptive substitutions.
-    %However, this does not imply that the rate of adaptation (i.e the number of changes in the fitness landscape per site per generation) is higher~\cite{galtier_adaptive_2016}.
-
     The exact estimation of the contribution of beneficial back-mutations to positive selection relies on some hypotheses at both the phylogenetic and population scales and is sensitive to methodological limitations.
@@
     However, adaptation is not the only factor hindering the detection of beneficial back-mutations; data quality and potentially inadequate modeling choices of both the fitness landscape and the DFE might also lead to missed predictions.
-    Given that our amino-acid fitness landscapes are site-specific and also independent of one another, missed prediction can be also due to epistasis where the fitness landscape at a given site depends on the residue present at other sites~\cite{starr_epistasis_2016, park_epistatic_2022}.
+    Our model assumes that amino-acid fitness landscapes are site-specific and also independent of one another, whereas under epistasis, the fitness effect of a mutation at a particular site depends on the amino-acids present at other sites~\cite{starr_epistasis_2016, park_epistatic_2022}.
+    Epistasis therefore allows for compensatory mutations, which restore fitness through mutations at loci different from where deleterious mutations take place, and this process also leaves signals interpretable as non-adaptive beneficial mutations~\cite{hartl_compensatory_1996, pollock_strong_2014, starr_epistasis_2016}.
+    Also, epistasis has been shown to play a role in the evolution of protein-coding genes, with amino-acid residues in contact within a protein or between proteins tending to co-evolve~\cite{breen_epistasis_2012, starr_epistasis_2016}.
+    Particularly, the residues in contact co-evolve to become more compatible with each other generating an entrenchment, making empirical evidence for beneficial back-mutations harder to find since restoring mutations becomes less and less likely to occur over time~\cite{goldstein_nonadaptive_2015, goldstein_sequence_2017, park_epistatic_2022}.
+    Nevertheless, the fact that we observe such a high proportion of beneficial back-mutations suggests that the underlying assumptions of our model, namely site-independence, implying no epistasis, and a static fitness landscape, are a reasonable approximation for the underlying fitness landscape of proteins.
+    Our results imply that the fitness effects of new mutations are mostly conserved across mammalian orthologs, in agreement with other studies showing that for conserved orthologs with similar structures and functions, models without epistasis provide a reasonable estimate of fitness effects in protein coding genes~\cite{ashenberg_mutational_2013, youssef_consequences_2020}.
     Moreover, a mutation inferred as nearly-neutral at the phylogenetic scale ($\SphyNeu$) but positively selected at the population scale ($\SpopBen$) will also be considered a missed prediction, even if this discrepancy could just be due to a population size expansion~\cite{lanfear_population_2014, jones_shifting_2017, platt_protein_2018}.
@@
     It appears that our estimation can be quite sensitive to model misspecification and overall, while we provide an order of magnitude for the contribution of beneficial back-mutations to positive selection, further methodological development on the estimation of the distribution of fitness effects is needed to increase the confidence on this value.
-
-    %Regarding the distribution of fitness effects (DFE) estimated at the population scale, there is no consensus on its expected shape~\cite{welch_divergence_2008, bataillon_effects_2014}, although it has been found to be reliably constant between closely related species~\cite{castellano_comparison_2019}.
-    %We modelled the DFE as a continuous distribution, but to check for robustness in our results despite the uncertainty of the underlying DFE, we also performed our analysis assuming a discretized DFE.
-    %Our results are consistent, with the proportion of back-mutations among all beneficial mutations ranging from XX to XX\% across populations when modelling a DFE as a discrete distributio.
-    %Consequently, even though our general framework contrasting the phylogenetic and population scales is theoretically consistent, we acknowledge that estimating the proportion of back-mutations among all beneficial ones is dependent on the the underlying DFE at the population scale and the threshold used to define a beneficial mutation.
-    %As a result, further work is required to investigate the shape of the DFE at the population scale.
-    %Notably, the reconstructed distribution of $\Sphy$ values obtained in our study has a negative mode (around $\Sphy=-5$), consistent with experimental DFEs obtained by mutation accumulation.
-    %Contrarily, continuous DFEs estimated at the population scale have by definition a mode at 0.
-    %We argue that methods estimating DFE at the population scale should assume a mode shifted toward negative values of $\Spop$.
-
-    \begin{figure*}[!ht]
-        \centering
-        \includegraphics[width=\textwidth, page=1] {artworks/figure.diversity}
-        \caption{
-            (A) Proportion of nearly-neutral mutations at the population scale ($\proba [ \SpopNeu]$ in the y-axis), shown as a function of the synonymous diversity (Watterson's $\thetaSyn$ in the x-axis).
-            (B) Proportion of beneficial back-mutations among all beneficial mutations ($\proba [ \SphyBen  \given  \SpopBen]$ in the y-axis), shown as a function of the synonymous diversity (Watterson's $\thetaSyn$ in the x-axis).
-        }
-        \label{fig:diversity}
-    \end{figure*}
-
-    %\subsection*{The role of epistasis in mammalian protein-coding genes}
-    %
-    %In our study, we focused on mutations toward a more optimal amino-acid at a given site, assuming that amino-acid fitness landscapes are site-specific and also independent of one another.
-    %Contrarily, under epistasis, the fitness effect of a mutation at a particular site depends on the amino-acids present at other sites.
-    %Epistasis therefore allows for compensatory mutations, which restore fitness through mutations at loci different from where deleterious mutations take place, and this process also leaves signals interpretable as non-adaptive beneficial mutations~\cite{hartl_compensatory_1996, pollock_strong_2014, starr_epistasis_2016}.
-    %Also, epistasis has been shown to play a role in the evolution of protein-coding genes, with amino-acid residues in contact within a protein or between proteins tending to co-evolve~\cite{breen_epistasis_2012, starr_epistasis_2016}.
-    %Particularly, the residues in contact co-evolve to become more compatible with each other generating an entrenchment, making empirical evidence for beneficial back-mutations harder to find since restoring mutations becomes less and less likely to occur over time~\cite{goldstein_nonadaptive_2015, goldstein_sequence_2017, park_epistatic_2022}.
-    %Nevertheless, the fact that we observe such a high proportion of beneficial back-mutations suggests that the underlying assumptions of our model, namely site-independence, implying no epistasis, and a static fitness landscape, are a reasonable approximation for the underlying fitness landscape of proteins.
-    %Our results imply that the fitness effects of new mutations are mostly conserved across mammalian orthologs, in agreement with other studies showing that for conserved orthologs with similar structures and functions, models without epistasis provide a reasonable estimate of fitness effects in protein coding genes~\cite{ashenberg_mutational_2013, youssef_consequences_2020}.
 
@@
     In that sense, to avoid conflating beneficial mutations with adaptive evolution, the term ``adaptation`` should retain its original meaning associated with a change in the underlying fitness landscape and be modelled as such.
-
-%TC:ignore
-    \section*{Acknowledgements}
-    \label{sec:acknowledgment}
-    We gratefully acknowledge the help of Mélodie Bastian, Nicolas Lartillot, Carina Farah Mugal, Laurent Duret, Alexandre Reymond, Daniele Silvestro and Nicolas Gambardella for their advice and reviews concerning this manuscript.
-    This work was performed using the computing facilities of the CC LBBE/PRABI\@.
-    This study makes use of data generated by the NextGen Consortium.
-    \textbf{Funding:}
-    Université de Lausanne; Agence Nationale de la Recherche, Grant ANR-19-CE12-0019 / HotRec.
-    The European Union’s Seventh Framework Programme (FP7/2010-2014) provided funding for the project under grant agreement no 244356 - “NextGen”.
-    \textbf{Author contributions:}
-    Original idea: T.L.\ and J.J.;
-    Model conception: T.L., J.J.\ and N.S.;
-    Code: T.L.;
-    Data analyses: T.L.\ and J.J.;
-    Interpretation: T.L., J.J., D.A.H.\ and N.S.;
-    First draft: T.L.\ and J.J.;
-    Editing and revisions: T.L., J.J., D.A.H.\ and N.S.
-    Project management and funding: N.S\@.
-    \textbf{Competing interests:}
-    The authors declare no conflicts of interest.
-    \textbf{Data and materials availability:}
-    The data underlying this article are available at \url{https://doi.org/10.5281/zenodo.7878954}.
-    Snakemake pipeline, analysis scripts and documentation are available at \href{https://github.com/ThibaultLatrille/SelCoeff}{github.com/ThibaultLatrille/SelCoeff}.
 
@@
     \end{equation}
+
+    \section*{Data availability}
+    The data underlying this article are available at \url{https://doi.org/10.5281/zenodo.7878954}.
+    Snakemake pipeline, analysis scripts and documentation are available at \href{https://github.com/ThibaultLatrille/SelCoeff}{github.com/ThibaultLatrille/SelCoeff}.
+
+    \section*{Acknowledgements}
+    \label{sec:acknowledgment}
+    We gratefully acknowledge the help of Mélodie Bastian, Nicolas Lartillot, Carina Farah Mugal, Laurent Duret, Alexandre Reymond, Daniele Silvestro and Nicolas Gambardella for their advice and reviews concerning this manuscript.
+    This work was performed using the computing facilities of the CC LBBE/PRABI\@.
+    This study makes use of data generated by the NextGen Consortium.
+    Funding:
+    Université de Lausanne; Agence Nationale de la Recherche, Grant ANR-19-CE12-0019 / HotRec.
+    The European Union’s Seventh Framework Programme (FP7/2010-2014) provided funding for the project under grant agreement no 244356 - “NextGen”.
+
+    \section*{Competing interests}
+    The authors declare no conflicts of interest.
+
+    \section*{Author information}
+    Original idea: T.L.\ and J.J.;
+    Model conception: T.L., J.J.\ and N.S.;
+    Code: T.L.;
+    Data analyses: T.L.\ and J.J.;
+    Interpretation: T.L., J.J., D.A.H.\ and N.S.;
+    First draft: T.L.\ and J.J.;
+    Editing and revisions: T.L., J.J., D.A.H.\ and N.S.
+    Project management and funding: N.S\@.
+
+%TC:ignore
     \printbibliography
+%TC:endignore
+\newpage
+    \begin{figure*}[!htb]
+        \centering
+        \includegraphics[width=\textwidth, page=1] {artworks/figure.fitness-landscape}
+        \caption{
+            (A \& B) For a given codon position of a protein-coding DNA sequence, amino acids (x-axis) have different fitness values (y-axis).
+            Under a fluctuating fitness landscape (A), these fitnesses change with time.
+            The protein sequence follows the moving target defined by the amino-acid fitnesses.
+Since substitutions are preferentially accepted if they are in the direction of this target, substitutions are, on average, adaptive.
+            At the phylogenetic scale (C), beneficial substitutions are common (positive signs), promoting phenotype diversification across species.
+            Under a stable fitness landscape (B), most mutations reaching fixation are either slightly deleterious reaching fixation due to drift or are beneficial back-mutations restoring a more optimal amino acid.
+            At the phylogenetic scale (D), deleterious substitutions (negative signs) are often reverted via beneficial back-mutations (positive signs), promoting phenotype stability and preserving well-established biological systems.
+            Even though, individually, any back-mutation might have a small beneficial effect on its bearer, we expect beneficial back-mutations to be scattered across the genome and the genome-wide signature of beneficial back-mutations to be detectable and quantifiable.}
+        \label{fig:fitness-landscape}
+    \end{figure*}
+
+    \begin{figure*}[!h]
+        \centering
+        \includegraphics[width=\textwidth, page=1] {artworks/figure.method.proba}
+        \caption{
+            Selection coefficients at the phylogenetic and population scales.
+            At the phylogenetic scale (A), we estimated the amino-acid fitness for each site from protein-coding DNA alignments using mutation-selection codon models.
+            For every possible mutation, the difference in amino acid fitness before and after the mutation allows us to compute the selection coefficient at the phylogenetic scale ($\Sphy$).
+            Depending on $\Sphy$ (B) mutations can be predicted as deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) or beneficial back-mutations ($\SphyBen$) toward a fitter amino acid and repairing existing functions.
+            At the population scale, each observed single nucleotide polymorphism (SNP) segregating in the population can also be classified according to its $\Sphy$ value (C).
+            Occurrence and frequency in the population of non-synonymous polymorphisms, contrasted to synonymous polymorphisms (deemed neutral) is used to estimate selection coefficients (D-E) at the population scale ($\Spop$), for each class of selection ($\SphyDel$, $\SphyNeu$, $\SphyBen$).
+            We can thus assess whether $\Sphy$ predicts $\Spop$ and compute \textit{precision} (F) and \textit{recall} (G) for each class.
+            The \textit{recall} value for class $\SphyBen$ is the probability of back-mutations among all beneficial ones (G).
+        }
+        \label{fig:method}
+    \end{figure*}
+
+    \begin{figure*}[!h]
+        \centering
+        \includegraphics[width=\textwidth, page=1] {artworks/figure.homo-afr-results}
+        \caption{
+            (A) Distribution of scaled selection coefficients ($\Sphy$), predicted for all possible mutations away from the ancestral human genome.
+            Mutations are divided into three classes of selection: deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial ($\SphyBen$, supposedly beneficial back-mutations).
+            (B) Distribution of scaled selection coefficients ($\Sphy$) for all observed substitutions along the \textit{Homo} branch after the \textit{Homo}-\textit{Pan} split.
+            If there are fewer substitutions than expected, this class is thus undergoing purifying selection, as is the case for $\SphyDel$.
+            (C) The site-frequency spectrum (SFS) in humans of African descent for a random sample of 16 alleles (means in solid lines and standard deviations in color shades) for each class of selection and for synonymous mutations, supposedly neutral (black).
+The SFS represents the proportion of mutations (y-axis) with a given number of derived alleles in the population (x-axis).
+            At high frequencies, deleterious mutations are underrepresented.
+            (D) Proportion of beneficial $\ProbaPopDel$, nearly-neutral $\ProbaPopNeu$, and deleterious mutations $\ProbaPopBen$ estimated at the population scale for each class of selection at the phylogenetic scale.
+Proportions depicted here are not weighted by their mutational opportunities.
+        }
+        \label{fig:homo-afr-results}
+    \end{figure*}
+
+    \begin{figure*}[!ht]
+        \centering
+        \includegraphics[width=\textwidth, page=1] {artworks/figure.diversity}
+        \caption{
+            (A) Proportion of nearly-neutral mutations at the population scale ($\proba [ \SpopNeu]$ in the y-axis), shown as a function of the synonymous diversity (Watterson's $\thetaSyn$ in the x-axis).
+            (B) Proportion of beneficial back-mutations among all beneficial mutations ($\proba [ \SphyBen  \given  \SpopBen]$ in the y-axis), shown as a function of the synonymous diversity (Watterson's $\thetaSyn$ in the x-axis).
+        }
+        \label{fig:diversity}
+    \end{figure*}
+
+    \begin{table*}[tb]
+%TC:ignore
+        \centering
+        \begin{adjustbox}{width=\textwidth}
+            \begin{tabular}{||l|l|r||r|r||r|r||r|r||}
+                \toprule
+                \multicolumn{3}{||c||}{} &
+                \multicolumn{2}{c||}{\shortstack{\textbf{Deleterious mutations} \\ $\bm{\SpopDel \coloneqq \Spop<-1}$ \\ $\bm{\SphyDel \coloneqq \Sphy<-1}$}} &
+                \multicolumn{2}{c||}{\shortstack{\textbf{Nearly-neutral mutations} \\ $\bm{\SpopNeu \coloneqq -1<\Spop<1}$ \\ $\bm{\SphyNeu \coloneqq -1<\Sphy<1}$}} &
+                \multicolumn{2}{c||}{\shortstack{\textbf{Beneficial mutations} \\ $\bm{\SpopBen \coloneqq \Spop>1}$ \\ $\bm{\SphyBen \coloneqq \Sphy>1}$}}
+                \\ \hline
+                \textbf{Population} &
+                \textbf{Species} &
+                $\bm{\thetaSyn}$ &
+                \makecell{\textbf{Precision} \\ $\bm{\proba [\SpopDel \given \SphyDel]}$} &
+                \makecell{\textbf{Recall} \\ $\bm{\proba [\SphyDel \given \SpopDel]}$}            &
+                \makecell{\textbf{Precision}      \\ $\bm{\proba [\SpopNeu \given \SphyNeu]}$}                                    &
+                \makecell{\textbf{Recall}          \\ $\bm{\proba [\SphyNeu \given \SpopNeu]}$}                                  &
+                \makecell{\textbf{Precision}          \\ $\bm{\proba [\SpopBen \given \SphyBen]}$}          &
+                \makecell{\textbf{Recall}        \\ $\bm{\proba [\SphyBen \given \SpopBen]}$}
+                \\   \midrule
+                \rowcolor{LIGHTGREY}              Equus c. & Equus caballus        & $ 0.002$ & $ 0.908$ & $ 0.976$ & $ 0.730$ & $ 0.383$ & $ 0.580$ & $ 0.809$ \\
+                Iran               & Bos taurus        & $ 0.002$ & $ 0.898$ & $ 1.000$ & $ 0.632$ & $ 0.340$ & $ 0.857$ & $ 0.277$ \\
+                Uganda              & Bos taurus        & $ 0.005$ & $ 0.942$ & $ 0.963$ & $ 0.497$ & $ 0.393$ & $ 0.488$ & $ 0.483$ \\
+                \rowcolor{LIGHTGREY} Australia            & Capra hircus        & $ 0.003$ & $ 0.934$ & $ 0.966$ & $ 0.524$ & $ 0.425$ & $ 0.368$ & $ 0.196$ \\
+                \rowcolor{LIGHTGREY} France                                    & Capra hircus          & $ 0.004$ & $ 0.936$ & $ 0.965$ & $ 0.506$ & $ 0.412$ & $ 0.368$ & $ 0.211$ \\
+                \rowcolor{LIGHTGREY} Iran (C. aegagrus)                    & Capra hircus          & $ 0.004$ & $ 0.940$ & $ 0.961$ & $ 0.478$ & $ 0.438$ & $ 0.221$ & $ 0.114$ \\
+                \rowcolor{LIGHTGREY} Iran                        & Capra hircus          & $ 0.004$ & $ 0.945$ & $ 0.960$ & $ 0.419$ & $ 0.400$ & $ 0.368$ & $ 0.211$ \\
+                \rowcolor{LIGHTGREY} Italy                                 & Capra hircus          & $ 0.004$ & $ 0.937$ & $ 0.963$ & $ 0.548$ & $ 0.426$ & $ 0.270$ & $ 0.220$ \\
+                \rowcolor{LIGHTGREY} Morocco                                 & Capra hircus          & $ 0.004$ & $ 0.942$ & $ 0.964$ & $ 0.522$ & $ 0.428$ & $ 0.368$ & $ 0.276$ \\
+                Iran           & Ovis aries & $ 0.007$ & $ 0.953$ & $ 0.954$ & $ 0.450$ & $ 0.406$ & $ 0.169$ & $ 0.392$ \\
+                Iran (O. orientalis)  & Ovis aries & $ 0.009$ & $ 0.958$ & $ 0.953$ & $ 0.417$ & $ 0.431$ & $ 0.153$ & $ 0.180$ \\
+                Iran (O. vignei)           & Ovis aries & $ 0.007$ & $ 0.960$ & $ 0.951$ & $ 0.360$ & $ 0.449$ & $ 0.195$ & $ 0.133$ \\
+                Various             & Ovis aries & $ 0.008$ & $ 0.955$ & $ 0.954$ & $ 0.435$ & $ 0.426$ & $ 0.190$ & $ 0.228$ \\
+                Morocco              & Ovis aries & $ 0.008$ & $ 0.956$ & $ 0.955$ & $ 0.449$ & $ 0.410$ & $ 0.136$ & $ 0.353$ \\
+                \rowcolor{LIGHTGREY} Barbados              & Chlorocebus sabaeus & $ 0.004$ & $ 0.925$ & $ 0.969$ & $ 0.536$ & $ 0.377$ & $ 0.565$ & $ 0.306$ \\
+                \rowcolor{LIGHTGREY} Central Afr. Rep.       & Chlorocebus sabaeus & $ 0.006$ & $ 0.940$ & $ 0.964$ & $ 0.495$ & $ 0.404$ & $ 0.429$ & $ 0.274$ \\
+                \rowcolor{LIGHTGREY} Ethiopia        & Chlorocebus sabaeus & $ 0.005$ & $ 0.925$ & $ 0.969$ & $ 0.560$ & $ 0.400$ & $ 0.462$ & $ 0.239$ \\
+                \rowcolor{LIGHTGREY} Gambia             & Chlorocebus sabaeus & $ 0.005$ & $ 0.934$ & $ 0.969$ & $ 0.610$ & $ 0.409$ & $ 0.486$ & $ 0.774$ \\
+                \rowcolor{LIGHTGREY} Kenya                                 & Chlorocebus sabaeus        & $ 0.005$ & $ 0.938$ & $ 0.965$ & $ 0.519$ & $ 0.434$ & $ 0.478$ & $ 0.243$ \\
+                \rowcolor{LIGHTGREY} Nevis                        & Chlorocebus sabaeus        & $ 0.003$ & $ 0.923$ & $ 0.970$ & $ 0.609$ & $ 0.393$ & $ 0.516$ & $ 0.393$ \\
+                \rowcolor{LIGHTGREY} South Africa                              & Chlorocebus sabaeus        & $ 0.006$ & $ 0.935$ & $ 0.965$ & $ 0.542$ & $ 0.409$ & $ 0.490$ & $ 0.360$ \\
+                \rowcolor{LIGHTGREY} Saint Kitts                                & Chlorocebus sabaeus        & $ 0.004$ & $ 0.926$ & $ 0.969$ & $ 0.562$ & $ 0.377$ & $ 0.515$ & $ 0.367$ \\
+                \rowcolor{LIGHTGREY} Zambia                             & Chlorocebus sabaeus        & $ 0.006$ & $ 0.937$ & $ 0.965$ & $ 0.494$ & $ 0.413$ & $ 0.499$ & $ 0.249$ \\
+                African                             & Homo sapiens        & $ 0.002$ & $ 0.899$ & $ 0.970$ & $ 0.571$ & $ 0.334$ & $ 0.678$ & $ 0.319$ \\
+                Admixed American                             & Homo sapiens        & $ 0.002$ & $ 0.888$ & $ 0.972$ & $ 0.581$ & $ 0.301$ & $ 0.635$ & $ 0.361$ \\
+                East Asian                             & Homo sapiens        & $ 0.002$ & $ 0.894$ & $ 0.973$ & $ 0.583$ & $ 0.335$ & $ 0.611$ & $ 0.233$ \\
+                European                             & Homo sapiens        & $ 0.002$ & $ 0.896$ & $ 0.972$ & $ 0.581$ & $ 0.350$ & $ 0.619$ & $ 0.217$ \\
+                South Asian                             & Homo sapiens        & $ 0.002$ & $ 0.898$ & $ 0.972$ & $ 0.580$ & $ 0.354$ & $ 0.628$ & $ 0.222$ \\
+                \bottomrule
+            \end{tabular}
+        \end{adjustbox}
+%TC:endignore
+        \caption{
+            \textit{Precision} and \textit{recall} for estimated selection coefficient of mutations given by mutation-selection models ($\Sphy$).
+            \textit{Precision} is the estimation of the selection coefficient at population scale ($\Spop$) given that $\Sphy$ is known.
+            Conversely, \textit{recall} is the estimation of $\Sphy$ given selection coefficient at the population scale ($\Spop$) is known.
+            \textit{Recall} for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is thus the proportion of beneficial back-mutations among all beneficial mutations.
+            Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
+        }
+        \label{table:proba}
+    \end{table*}
 \end{document}
-%TC:endignore

### 2023-08-21 run_all.sh

@@ -1,6 +1,7 @@
 #!/usr/bin/env bash
-for FILE in config/config_*.yaml;
+for FILE in config/config_3cat_Onto*.yaml;
 do
   cp -f "${FILE}" config/config.yaml
+  snakemake --unlock
   snakemake -j 8 -k --rerun-incomplete
 done

### 2023-08-21 scripts/PGLS.R

@@ -1,0 +1,41 @@
+library(ape)
+library(geiger)
+library(nlme)
+library(phytools)
+
+setwd("~/Documents/SelCoeff")
+
+mamData <- read.csv("experiments/3bins-mC-OntoRegTrans/regression-MutSel/results.tsv", row.names = 1)
+mamTree <- read.tree("data_processed/trimmed_tree_sample_all.tsv.tree")
+plot(mamTree)
+
+name.check(mamTree, mamData)
+
+y_label <- "mut_sum_P.Sweak"
+y_label <- "bayes_P.Spos_P.pos"
+plot(mamData[, c("pop_size", y_label)])
+
+# Extract columns
+x <- mamData[, "pop_size"]
+y <- mamData[, y_label]
+# Give them names
+names(y) <- names(x) <- rownames(mamData)
+
+# pgls model
+pglsModel <- gls(y ~ x, correlation = corBrownian(phy = mamTree),
+                 data = mamData, method = "ML")
+summary(pglsModel)
+t <- summary(pglsModel)$tTable
+
+# Calculate PICs
+yPic <- pic(y, mamTree)
+xPic <- pic(x, mamTree)
+# Make a model
+picModel <- lm(yPic ~ xPic - 1)
+# Yes, significant
+summary(picModel)
+
+# plot yPic
+plot(yPic ~ xPic)
+abline(a = 0, b = coef(picModel))
+

### 2023-08-21 scripts/libraries.py

@@ -54,9 +54,9 @@ codontable.update({
 confidence_interval = namedtuple('confidence_interval', ['low', 'mean', 'up'])
 sfs_weight = {"watterson": lambda i, n: 1.0 / i, "tajima": lambda i, n: n - i, "fay_wu": lambda i, n: i}
 polydfe_cat_dico = {
-    "P-Spos": "$\\mathbb{P} [ S > 1 ]$",
-    "P-Sweak": "$\\mathbb{P} [ -1 < S < 1 ]$",
-    "P-Sneg": "$\\mathbb{P} [ S < -1 ]$",
+    "P-Spos": "$\\mathbb{P} [ \\mathcal{B} ]$",
+    "P-Sweak": "$\\mathbb{P} [ \\mathcal{N} ]$",
+    "P-Sneg": "$\\mathbb{P} [ \\mathcal{D} ]$",
 }
 alpha_sup_limits = [0, 1, 3, 5]
 polydfe_cat_list = list(polydfe_cat_dico.keys())
@@ -218,7 +218,7 @@ class CdsRates(dict):
                 self.add_ensg(ensg)
             return np.log(self[ensg][ref_aa][c_site])
         else:
-            return np.float("infinity")
+            return float("infinity")
 
     def rate(self, ensg, ref_aa, alt_aa, c_site):
         if ensg not in self:
@@ -462,7 +462,7 @@ class CategorySNP(list):
                 self.inner_bound = [1.0]
                 self.dico = {
                     "neg": P("$\\omega < 1$", RED, 0, 1.0),
-                    "pos": P("$\\omega > 1$", BLUE, 1.0, np.float("infinity")),
+                    "pos": P("$\\omega > 1$", BLUE, 1.0, float("infinity")),
                     "syn": P("$Synonymous$", 'black', None, None)
                 }
             elif self.bins == 3:
@@ -470,7 +470,7 @@ class CategorySNP(list):
                 self.dico = {
                     "neg": P("$\\omega<0.05$", RED, 0, 0.05),
                     "weak": P("$0.05<\\omega<1.0$", GREEN, 0.05, 1.0),
-                    "pos": P("$\\omega > 1$", BLUE, 1.0, np.float("infinity")),
+                    "pos": P("$\\omega > 1$", BLUE, 1.0, float("infinity")),
                     "syn": P("$Synonymous$", 'black', None, None)
                 }
             else:
[…]

### 2023-08-21 scripts/mask_adaptation.py

@@ -17,7 +17,7 @@ def main(args):
         path_omega = f"{f_path}/siteomega_1.run.ci0.025.tsv"
         omega_lower = pd.read_csv(path_omega, sep="\t")["omega_lower"].values[1:]
 
-        adaptation = np.argwhere(omega_lower > mutsel_upper)
+        adaptation = np.argwhere(omega_lower < mutsel_upper)
         output_dict["ensg"].extend([ensg.replace('__', '_null_').replace('_NT', '')] * len(adaptation))
         output_dict["pos"].extend([i[0] for i in adaptation])
 

### 2023-08-21 scripts/mask_ontology.py

@@ -1,0 +1,44 @@
+import os
+import argparse
+import pandas as pd
+from collections import defaultdict
+from libraries import open_fasta, translate_cds
+
+
+def main(args):
+    os.makedirs(os.path.dirname(args.output), exist_ok=True)
+    output_dict = defaultdict(list)
+
+    df = pd.read_csv(args.ontology_tsv, sep="\t",
+                     dtype={"go_id": str, "go_name": str, "go_cds_count": int, "go_cds": str})
+    df = df[df["go_name"] == args.ontology_key]
+    if len(df) > 1:
+        print(f"Multiple rows found for {args.ontology_key}, taking the first one")
+    ensg_list = set(df["go_cds"].values[0].split("; "))
+    assert len(ensg_list) == df["go_cds_count"].values[0]
+
+    files = sorted(os.listdir(args.fasta_folder))
+    for fasta_file in files:
+        ensg = fasta_file.replace("__", "_null_").replace("_NT.fasta", "")
+        if ensg in ensg_list:
+            print(f"Not masking {ensg}")
+            continue
+        else:
+            print(f"Masking {ensg}")
+        fasta_dict = open_fasta(f"{args.fasta_folder}/{fasta_file}")
+        first_key = next(iter(fasta_dict))
+        nbr_sites = len(fasta_dict[first_key])
+        output_dict["ensg"].extend([ensg] * nbr_sites)
+        output_dict["pos"].extend(range(nbr_sites))
+
+    df = pd.DataFrame(output_dict)
+    df.to_csv(args.output, index=False, sep="\t")
+
+
+if __name__ == '__main__':
+    parser = argparse.ArgumentParser(formatter_class=argparse.ArgumentDefaultsHelpFormatter)
+    parser.add_argument('--fasta_folder', required=True, type=str, dest="fasta_folder", help="The fasta folder path")
+    parser.add_argument('--ontology_tsv', required=True, type=str, dest="ontology_tsv", help="The ontology tsv path")
+    parser.add_argument('--ontology_key', required=True, type=str, dest="ontology_key", help="The ontology key")
+    parser.add_argument('--output', required=True, type=str, dest="output", help="Output tsv path")
+    main(parser.parse_args())

### 2023-08-21 scripts/onto_compare.py

@@ -1,0 +1,20 @@
+import pandas as pd
+from scipy.stats import wilcoxon
+
+
+def open_results(exp):
+    tmp_df = pd.read_csv(f"experiments/{exp}/regression-MutSel/results.tsv", sep="\t", index_col=0)
+    return tmp_df["bayes_P-Spos_P-pos"]
+
+
+control = "3bins-mC"
+dico_df = {control: open_results(control)}
+cases = ["3bins-mC-OntoCytoplasme", "3bins-mC-OntoNucleus", "3bins-mC-OntoMembrane", "3bins-mC-OntoProtBind",
+         "3bins-mC-OntoRegTrans"]
+
+for case in cases:
+    dico_df[case] = open_results(case)
+    res = wilcoxon(dico_df[control], dico_df[case], alternative="two-sided")
+    print(case, res, (dico_df[case] / dico_df[control]).mean())
+
+df = pd.DataFrame(dico_df)

### 2023-08-21 scripts/plot_heatmap.py

@@ -46,16 +46,24 @@ def main(args):
     os.makedirs(os.path.dirname(args.output), exist_ok=True)
     df_theta = pd.concat([open_tsv(filepath) for filepath in sorted(args.tsv_theta)])
     df_dfe = pd.concat([open_tsv(filepath) for filepath in sorted(args.tsv_dfe)])
+
+    df_mut_rates = pd.read_csv(args.tsv_mut_rate, sep="\t")
+    # group mutationr rates per species and compute mean
+    df_mut_rates = df_mut_rates.groupby("Species").mean().reset_index()
+    dico_mut_rates = {row["Species"]: row["MutationRatePerGeneration"] for _, row in df_mut_rates.iterrows()}
+
     df_merge = pd.merge(df_theta, df_dfe, how="outer", on=["pop", "species", "method", "category"])
     df_merge["D_tajima"] = df_merge["tajima"] - df_merge["watterson"]
     df_merge["H_fay_wu"] = df_merge["tajima"] - df_merge["fay_wu"]
-    d_dict = {"watterson": "Watterson $\\theta_W$"}
+    # Apply the mutation rate to the Watterson estimator
+    df_merge["pop_size"] = df_merge.apply(lambda r: r["tajima"] / (4 * dico_mut_rates[r["species"]]), axis=1)
+    d_dict = {"watterson": "Watterson $\\theta_W$", "pop_size": "Effective population size $N_e$"}
     d_dict.update(polydfe_cat_dico)
 
     df_merge = df_merge.iloc[df_merge.apply(lambda r: sp_sorted(format_pop(r["pop"]), r["species"]), axis=1).argsort()]
     df_merge.to_csv(args.output, sep="\t", index=False)
     pop2sp = {pop: sp for (pop, sp), d in df_merge.groupby(["pop", "species"])}
-    pop2theta = {pop: d["tajima"].values[0] for pop, d in df_merge[df_merge["category"] == "syn"].groupby(["pop"])}
+    pop2theta = {pop: d["pop_size"].values[0] for pop, d in df_merge[df_merge["category"] == "syn"].groupby("pop")}
 
     species = {k: None for k in df_merge["species"]}
     cmtab10 = get_cmap('tab10')
@@ -63,10 +71,10 @@ def main(args):
 
     sample_dico = sample_list_dico(args.sample_list)
     df_merge = df_merge[df_merge["category"] != "syn"]
-    for method, df in df_merge.groupby(["method"]):
+    for method, df in df_merge.groupby("method"):
[…]

### 2023-08-21 scripts/plot_regression.py

@@ -4,13 +4,8 @@ import numpy as np
 import pandas as pd
 from functools import reduce
 from itertools import product
-from collections import defaultdict
-import statsmodels.api as sm
 from matplotlib.cm import get_cmap
-from matplotlib.lines import Line2D
 from libraries import my_dpi, plt, polydfe_cat_dico, tex_f, sort_df, sp_sorted, format_pop, CategorySNP
-
-markers = ["o", "d", "s", '.']
 
 
 def open_tsv(filepath, cat_snps, method):
@@ -21,8 +16,7 @@ def open_tsv(filepath, cat_snps, method):
         df_theta = df_theta.drop(["method", "species", "category"], axis=1)
         df_dfe = ddf[(ddf["method"] == method) & (ddf["category"] != "syn")]
         cols = list(polydfe_cat_dico) + [f"P-{cat}" for cat in cat_snps.non_syn_list]
-        cols += ['p_b', 'S_b', 'S_d', 'b', 'logL', 'S', 'S+', 'S-', 'fay_wu', 'tajima', 'watterson', 'div']
-        cols += ["omega_Adiv", "omega_div"]
+        cols += ['pop_size', 'div', "omega_div"]
         m_list = []
         for col in cols:
             if col in df_dfe:
@@ -30,7 +24,7 @@ def open_tsv(filepath, cat_snps, method):
                 m_list.append(matrix)
         df_pivot = pd.concat(m_list, axis=1)
         ddf = pd.merge(df_pivot, df_theta, on=["pop"])
-    elif "bounds" in os.path.basename(filepath):
+    elif "bounds" in os.path.dirname(filepath).split("/")[-1]:
         ddf = ddf[ddf["method"] == method]
         ddf = ddf.pivot(index="pop", columns="cat", values="sampled_fraction").add_suffix('_snps')
     return ddf
@@ -40,74 +34,34 @@ def discard_col(col, df):
     return (col not in df) or (df.dtypes[col] == object) or (not np.all(np.isfinite(df[col])))
 
 
-def generate_xy_plot(cat_snps):
-    pr = "\\mathbb{P}"
-    xy_dico = defaultdict(list)
-    dico_label = {'pop': "Population", "species": "Species", "watterson": "Watterson $\\theta_S$",
[…]

### 2023-08-21 scripts/table_ontology.py

@@ -1,0 +1,54 @@
+import os
+import argparse
+import pandas as pd
+from lxml import etree
+from collections import defaultdict
+
+
+def ontology_table(xml_folder: str, set_ensg: set) -> (dict, dict, set):
+    print('Finding CDS ontologies.')
+    go_id2name, go_id2cds_list = {}, {}
+    all_go_set = set()
+    for file in os.listdir(xml_folder):
+        root = etree.parse(xml_folder + "/" + file).getroot()
+        for annot in root.find('goAnnot').findall("annot"):
+            go_id = annot.find('goId').text
+            go_name = annot.find('goName').text
+            if go_id not in go_id2name:
+                go_id2name[go_id] = go_name.replace('"', '')
+            if go_id not in go_id2cds_list:
+                go_id2cds_list[go_id] = set()
+            ensg = file.replace(".xml", "")
+            assert ensg in set_ensg
+            go_id2cds_list[go_id].add(ensg)
+            all_go_set.add(ensg)
+    print('CDS ontologies found.')
+    return go_id2cds_list, go_id2name, all_go_set
+
+
+def main(folder: str, xml_folder: str, output: str):
+    list_ensg = set([i[:-3] for i in os.listdir(folder)])
+    go_id2cds_list, go_id2name, set_all_go_cds = ontology_table(xml_folder, list_ensg)
+
+    # Create a dataframe with 4 columns: go_id, go_name, go_cds_count, go_cds
+    output_dict = defaultdict(list)
+    for go_id in go_id2cds_list:
+        output_dict["go_id"].append(go_id)
+        go_name = go_id2name[go_id].replace(' ', '-').replace("_", "-").replace("/", "-")
+        output_dict["go_name"].append(go_name)
+        output_dict["go_cds_count"].append(len(go_id2cds_list[go_id]))
+        output_dict["go_cds"].append("; ".join(list(go_id2cds_list[go_id])))
+
+    df = pd.DataFrame(output_dict)
+    df = df.sort_values(by=['go_cds_count'], ascending=False)
+    df.to_csv(output, sep="\t", index=False)
+
+
+if __name__ == '__main__':
+    parser = argparse.ArgumentParser(formatter_class=argparse.ArgumentDefaultsHelpFormatter)
+    parser.add_argument('-f', '--folder', required=True, type=str, dest="folder",
+                        help="folder containing OrthoMam results")
[…]

### 2023-08-21 scripts/tex_sfs.py

@@ -56,7 +56,7 @@ def main(args):
                 hist_path = f"{args.hist_prefix}{hist_suffix}"
                 o.write(minipage(0.49, hist_path))
                 o.write("\\\\ \n")
-                o.write(minipage(0.49, sfs.replace(".pdf", ".normalize.pdf")))
+                o.write(minipage(0.49, sfs))
                 for model in ["C", "D"]:
                     polyDFE = sfs.replace("-sfs.pdf", f".polyDFE_{model}.pdf")
                     if os.path.exists(polyDFE):

### 2023-08-21 scripts/trim_tree.py

@@ -1,0 +1,78 @@
+import os
+import argparse
+from ete3 import Tree
+import pandas as pd
+import numpy as np
+from libraries import format_pop
+
+
+def prune_tree(input_tree: Tree, list_taxa: list) -> Tree:
+    tree = input_tree.copy()
+
+    # Prune tree
+    tree.prune(list_taxa, preserve_branch_length=True)
+    assert len(tree.get_leaves()) == len(list_taxa), f"Pruning failed: {len(tree.get_leaves())} != {len(list_taxa)}"
+
+    # Add polytomies if branch length are 0
+    remove_nodes = set([n for n in tree.traverse() if (n.dist == 0.0 and not n.is_root())])
+    for n in remove_nodes:
+        n.delete()
+    assert len(set([n for n in tree.traverse()]).intersection(remove_nodes)) == 0
+    for n in tree.traverse():
+        if not n.is_root():
+            assert n.dist > 0.0, f"Branch length is 0.0 for node {n.name}"
+    return tree
+
+
+def sister_species(tree: Tree, specie: str, populations: list) -> Tree:
+    leaves = tree.get_leaves_by_name(specie)
+    assert len(leaves) == 1
+    node = leaves[0]
+
+    while True:
+        node = node.up
+        leaves = node.get_leaf_names()
+        diff_genus_names = [k for k in leaves if k.split("_")[0] != specie.split("_")[0]]
+        if len(diff_genus_names) > 0:
+            break
+
+    # Compute the distance between the node and the leaves
+    distances = []
+    for c in node.get_leaves():
+        d = node.get_distance(c)
+        distances.append(d)
+    assert len(distances) == len(node.get_leaves())
+    # Assert that the distance are similar
+    d = np.mean(distances)
+    if not np.allclose(distances, np.mean(distances), atol=1e-5):
+        print("Warning: distances are not similar")
+        print(distances)
+        print(node)
+
+    set_leaves = set(tree.get_leaf_names())
+    for pop in populations:
+        assert pop not in set_leaves
+        node.add_child(name=pop, dist=d)
+    return tree
+
+
+def main(args):
+    os.makedirs(os.path.dirname(args.output), exist_ok=True)
+
+    df_sample = pd.read_csv(args.sample, sep="\t")
+    tree = Tree(args.tree, quoted_node_names=True, format=1)
+
+    for species, df_sub in df_sample.groupby("Species"):
+        print(species)
[…]

### 2023-10-11 copy_artworks.sh
Estimate Ne, perform PGLM and mask ontology/adaptive genes

@@ -4,13 +4,14 @@
 \cp -rf ./experiments/3bins-mC-nodiv/analysis/Homo_sapiens.AFR.MutSel.polyDFE_C.pdf ./manuscript/artworks/AFR.polyDFE.pdf
 \cp -rf ./data_processed/opportunities_bins3Mask0.9/DFE.Homo_sapiens.AFR.MutSel.pdf ./manuscript/artworks/AFR.histogramDFE.pdf
 \cp -rf ./data_processed/ancestral_bins3Mask0.9/Homo_sapiens.AFR.pdf ./manuscript/artworks/AFR.histogramDiv.pdf
-\cp -rf ./experiments/3bins-mC-nodiv/regression-MutSel/results.watterson.bayes_P-Spos_P-pos.scatter.pdf ./manuscript/artworks/results.watterson.Bayes.pdf
-\cp -rf ./experiments/3bins-mC-nodiv/regression-MutSel/results.watterson.mut_sum_P-Sweak.scatter.pdf ./manuscript/artworks/results.watterson.all_P-Sweak.scatter.pdf
-\cp -rf ./experiments/3bins-mC-nodiv/regression-MutSel/results.watterson.weak_P-Sweak.scatter.pdf ./manuscript/artworks/results.watterson.weak_P-Sweak.scatter.pdf
-\cp -rf ./experiments/3bins-mC-nodiv/regression-MutSel/results.watterson.mut_sum_P-Sneg.scatter.pdf ./manuscript/artworks/results.watterson.all_P-Sneg.scatter.pdf
-\cp -rf ./experiments/3bins-mC-nodiv/regression-MutSel/results.watterson.neg_P-Sneg.scatter.pdf ./manuscript/artworks/results.watterson.neg_P-Sneg.scatter.pdf
-\cp -rf ./experiments/3bins-mC-nodiv/regression-MutSel/results.watterson.mut_sum_P-Spos.scatter.pdf ./manuscript/artworks/results.watterson.all_P-Spos.scatter.pdf
-\cp -rf ./experiments/3bins-mC-nodiv/regression-MutSel/results.watterson.pos_P-Spos.scatter.pdf ./manuscript/artworks/results.watterson.pos_P-Spos.scatter.pdf
[…]

### 2023-10-11 scripts/PGLS.R

@@ -1,41 +1,53 @@
-library(ape)
-library(geiger)
-library(nlme)
-library(phytools)
+library("argparse")
+library("geiger")
+library("caper")
 
-setwd("~/Documents/SelCoeff")
+# create parser object
+parser <- ArgumentParser()
+parser$add_argument("--input_tsv", help = "Input tsv file")
+parser$add_argument("--input_tree", help = "Input tree file")
+parser$add_argument("--output_tsv", help = "Output tsv file")
 
-mamData <- read.csv("experiments/3bins-mC-OntoRegTrans/regression-MutSel/results.tsv", row.names = 1)
-mamTree <- read.tree("data_processed/trimmed_tree_sample_all.tsv.tree")
-plot(mamTree)
+args <- parser$parse_args()
+mamData <- read.csv(args$input_tsv, row.names = 1, sep = "\t", check.names = FALSE)
+mamData$Names <- rownames(mamData)
 
+mamTree <- read.tree(args$input_tree)
 name.check(mamTree, mamData)
 
-y_label <- "mut_sum_P.Sweak"
-y_label <- "bayes_P.Spos_P.pos"
-plot(mamData[, c("pop_size", y_label)])
+x_label <- "pop_size"
+table_output <- data.frame()
+for (y_label in colnames(mamData)) {
+    if ((y_label == "pop_size") || (y_label == "Names") || (y_label == "species")) {
+        next
+    }
+    # Extract columns
+    print(y_label)
+    mamData$y <- mamData[, y_label]
 
-# Extract columns
-x <- mamData[, "pop_size"]
-y <- mamData[, y_label]
-# Give them names
-names(y) <- names(x) <- rownames(mamData)
+    # test if y contains only floats otherwise skip
+    if (any(is.na(as.numeric(mamData$y)))) {
+        next
+    }
+    # test if y contains only the same value otherwise skip
+    if (length(unique(as.numeric(mamData$y))) == 1) {
+        next
+    }
+    cdat <- comparative.data(data = mamData, phy = mamTree, names.col = "Names")
+    m <- pgls(y ~ pop_size, data = cdat, lambda = 1.0)
+    s <- summary(m)
+    
+    t <- s$coefficients
+    # Add column with y_label and x_label
+    t <- cbind(t, y_label)
+    t <- cbind(t, x_label)
+    r2 <- c(s$adj.r.squared, s$r.squared)
+    t <- cbind(t, r2)
[…]

### 2023-10-11 scripts/SNP_effect.py

@@ -110,6 +110,7 @@ def adjusted_holm_pval(d, prefix="", alpha=0.05, format_p=True):
 
 
 def main(input_vcf, input_effect, tex_source, output, mask_list):
+    os.makedirs(os.path.dirname(output), exist_ok=True)
     mask_grouped = merge_mask_list(mask_list)
 
     cat_snps = CategorySNP("MutSel", bins=3)
@@ -158,8 +159,10 @@ def main(input_vcf, input_effect, tex_source, output, mask_list):
             o.write(f"{cat_snps.dico[cat].label}\\\\\n")
             df_sub = adjusted_holm_pval(df_sub, alpha=0.05, format_p=False)
             df_sub = format_pval_df(df_sub, alpha=0.05)
-            tex = df_sub.to_latex(index=False, escape=False, float_format=tex_f, header=header,
-                                  columns=[c for c in df_sub if c != "cat"], column_format="|l|r|r|r|r|r|")
+            columns = [c for c in df_sub if c != "cat"]
+            df_out = df_sub[columns]
+            df_out = df_out.rename(columns={k: v for k, v in zip(columns, header)})
+            tex = df_out.to_latex(index=False, escape=False, float_format=tex_f, column_format="|l|r|r|r|r|r|")
             o.write(tex)
             o.write("\\end{center}\n")
 

### 2023-10-11 scripts/compare_ontology_ratio.py

@@ -1,0 +1,68 @@
+import os
+import argparse
+import pandas as pd
+from collections import defaultdict
+from scipy.stats import wilcoxon
+from libraries import sort_df, tex_f, row_color
+
+
+def open_results(path: str, sample_list: str) -> dict:
+    df = pd.read_csv(os.path.join(path, "regression-MutSel", "results.tsv"), sep="\t")
+    df = sort_df(df, args.sample_list)  # assign the pop name to the index
+    df = row_color(df)  # assign the pop name to the index
+    df_out = df[["pop", "species", "recall_pos"]]
+    return df_out
+
+
+def main(experiments: str, sample_list: str, output: str):
+    # Iter over folders with "Onto" in the name
+    control_name = "3bins-mC"
+    control_path = os.path.join(experiments, control_name)
+    control_df = open_results(control_path, sample_list)
+    control = control_df["recall_pos"].values
+
+    case_path_list = [os.path.join(experiments, f) for f in os.listdir(experiments)]
+    case_path_list = [f for f in case_path_list if os.path.isdir(f)]
+    case_path_list = [f for f in case_path_list if (("Adaptation" in f))]
+
+    print(control)
+    out_dict = defaultdict(list)
+    tex_file = open(output.replace(".tsv", f".{control_name}.tex"), "w")
+    for case_path in case_path_list:
+        case_name = os.path.basename(case_path)
+        print(f"Comparing {case_name} to control")
+
+        tex_file.write(f"\\section{{{case_name.replace('-', ' ')}}}\n")
+        case_df = open_results(case_path, sample_list)
+
+        assert case_df["species"].equals(
+            control_df["species"]), f"Species differ between {case_name} and {control_name}"
+        assert case_df["pop"].equals(control_df["pop"]), f"Populations differ between {case_name} and {control_name}"
+
+        # T-test paired between case and control
+        case = case_df["recall_pos"].values
+        res = wilcoxon(control, case, alternative="less")
+
+        out_df = pd.DataFrame({"pop": case_df["pop"], "species": case_df["species"], "control": control, "case": case})
+        tex_file.write(out_df.to_latex(index=False, escape=False, float_format=tex_f))
+        r = (case / control).mean()
+        s, p = res[0], res[1]
+        print(f"{case}\n\ts={s:.2g}, p={p:.2g}, r={r:.2g}")
+        tex_file.write(f"\\textbf{{s={s:.2g}, p={p:.2g}, r={r:.2g}}}\n")
[…]

### 2023-10-11 scripts/libraries.py

@@ -8,12 +8,11 @@ import pandas as pd
 from collections import namedtuple, defaultdict
 import matplotlib
 
-matplotlib.rcParams["font.family"] = ["Latin Modern Sans"]
 matplotlib.use('Agg')
 import matplotlib.pyplot as plt
 from matplotlib.collections import LineCollection
 from matplotlib.colors import to_rgb
-from matplotlib.cm import get_cmap
+from matplotlib import colormaps
 
 fontsize = 16
 fontsize_legend = 14
@@ -321,14 +320,6 @@ def sp_sorted(pop, sp):
         return out
 
 
-def extend_pop(p, sample):
-    fp = format_pop(p)
-    if sample[p] == fp:
-        return p
-    else:
-        return f"{sample[p]} ({fp})"
-
-
 def sample_list_dico(sample_list_path):
     df = pd.read_csv(sample_list_path, sep='\t')
     df["pop"] = df.apply(lambda r: format_pop(r["SampleName"].replace("_", " ")), axis=1)
@@ -341,6 +332,15 @@ def sort_df(df, sample_list_path):
     df["species"] = df.apply(lambda r: r["species"].replace("_", " "), axis=1)
     dico_sample = sample_list_dico(sample_list_path)
     df["pop"] = df.apply(lambda r: dico_sample[r["pop"]], axis=1)
+    return df
+
+
+def row_color(df):
+    species_list = df["species"].unique()
+    # Add "\rowcolor{LIGHTGREY}" for populations, skip 1 species out of 2
+    species_grey = {s for i, s in enumerate(species_list) if i % 2 == 0}
+    color_tag = "\\rowcolor{LIGHTGREY} "
+    df["pop"] = df.apply(lambda r: color_tag + r["pop"] if (r["species"] in species_grey) else r["pop"], axis=1)
     return df
 
 
@@ -518,7 +518,7 @@ class CategorySNP(list):
         self.non_syn_list = [i for i in self if i != "syn"]
 
     def add_intervals(self, intervals):
-        cmap = get_cmap('viridis_r')
+        cmap = colormaps['viridis_r']
         self.dico = {"syn": P("Synonymous", 'black', None, None)}
         for bound in intervals:
             b = int(bound.cat.split("_")[-1])

### 2023-10-11 scripts/mask_ontology.py

@@ -21,10 +21,10 @@ def main(args):
     for fasta_file in files:
         ensg = fasta_file.replace("__", "_null_").replace("_NT.fasta", "")
         if ensg in ensg_list:
+            print(f"Masking {ensg}")
+        else:
             print(f"Not masking {ensg}")
             continue
-        else:
-            print(f"Masking {ensg}")
         fasta_dict = open_fasta(f"{args.fasta_folder}/{fasta_file}")
         first_key = next(iter(fasta_dict))
         nbr_sites = len(fasta_dict[first_key])

### 2023-10-11 scripts/parse_results_DFE.py

@@ -5,6 +5,7 @@ from libraries import *
 from rpy2.robjects.packages import SignatureTranslatedAnonymousPackage
 
 
+
 def read_poly_dfe(path, proc_R):
     out_poly_dfe = {}
     with open(path, 'r') as f:

### 2023-10-11 scripts/plot_heatmap.py

@@ -1,5 +1,4 @@
 import argparse
-from matplotlib import cm
 import seaborn as sns
 from libraries import *
 
@@ -66,7 +65,7 @@ def main(args):
     pop2theta = {pop: d["pop_size"].values[0] for pop, d in df_merge[df_merge["category"] == "syn"].groupby("pop")}
 
     species = {k: None for k in df_merge["species"]}
-    cmtab10 = get_cmap('tab10')
+    cmtab10 = colormaps['tab10']
     colors = {sp: cmtab10((t_i + 1) / len(species)) for t_i, sp in enumerate(species)}
 
     sample_dico = sample_list_dico(args.sample_list)
@@ -99,7 +98,7 @@ def main(args):
             start, end = np.nanmin(matrix), np.nanmax(matrix)
             if d.startswith("P-"):
                 start, end = 0.0, 1.0
-            rd_bu = cm.get_cmap('viridis_r')
+            rd_bu = colormaps['viridis_r']
             if start != 0.0 and np.sign(start) != np.sign(end):
                 midpoint = - start / (np.nanmax(matrix) - start)
                 rd_bu = shiftedColorMap(rd_bu, midpoint=midpoint, name='shifted')

### 2023-10-11 scripts/plot_multiple_regression.py

@@ -3,7 +3,7 @@ import argparse
 import numpy as np
 import pandas as pd
 from collections import defaultdict
-from matplotlib.cm import get_cmap
+from matplotlib import colormaps
 from matplotlib.lines import Line2D
 from libraries import my_dpi, format_pop, plt, sp_sorted
 
@@ -22,7 +22,7 @@ def main(args):
     sp2pop = {sp: list(set(df["pop"])) for sp, df in df_merge.groupby("species", sort=False)}
     df_merge = df_merge.iloc[::-1]
     merge_out = []
-    cm = get_cmap('tab10')
+    cm = colormaps['tab10']
     colors = {sp: cm((i + 1) / len(sp2pop)) for i, sp in enumerate(sp2pop)}
     for method, df_filter in df_merge.groupby("method"):
         plt.figure(figsize=(1920 / my_dpi, 960 / my_dpi), dpi=my_dpi)

### 2023-10-11 scripts/plot_regression.py

@@ -3,9 +3,10 @@ import argparse
 import numpy as np
 import pandas as pd
 from functools import reduce
+from collections import defaultdict
 from itertools import product
-from matplotlib.cm import get_cmap
-from libraries import my_dpi, plt, polydfe_cat_dico, tex_f, sort_df, sp_sorted, format_pop, CategorySNP
+from matplotlib import colormaps
+from libraries import my_dpi, plt, polydfe_cat_dico, tex_f, sort_df, sp_sorted, format_pop, CategorySNP, row_color
 
 
 def open_tsv(filepath, cat_snps, method):
@@ -35,7 +36,7 @@ def discard_col(col, df):
 
 
 def generate_dico_labels(cat_snps: CategorySNP):
-    dico_label = {'pop': "Population", "species": "Species", "pop_size": "Effective population size $N_e$"}
+    dico_label = {'pop': "Population", "species": "Species", "pop_size": "Effective population size $N_e$ (x1000)"}
 
     pr = "\\mathbb{P}"
     y_dico = {f'all_{cat_S}': v for cat_S, v in polydfe_cat_dico.items()}
@@ -51,13 +52,13 @@ def generate_dico_labels(cat_snps: CategorySNP):
         dico_label[cat_S0] = f"${pr}[{s0}]$"
         dico_label[f'{cat_S0}_omega_div'] = f"$\\omega {bracket_s0}$"
         dico_label[f"proba_{cat_S0}_div"] = f"${pr}_{{div}}[{s0}]$"
-        dico_label[f'sensitivity_{cat_S0}'] = f"TPR ${bracket_s0}$"
+        dico_label[f'recall_{cat_S0}'] = f"TPR ${bracket_s0}$"
         dico_label[f'precision_{cat_S0}'] = f"PPV ${bracket_s0}$"
 
         for cat_S, s_tex in polydfe_cat_dico.items():
             s = s_tex[s_tex.find("[") + 1:s_tex.rfind("]")]
-            dico_label[f'{cat_S0}_{cat_S}'] = f"${pr}[{s} {given_s0}]$"
-            dico_label[f'frac_{cat_S0}_{cat_S}'] = f"$\\frac{{{pr}[{s0}]}}{{{pr}[{s}]}}$"
+            y_dico[f'{cat_S0}_{cat_S}'] = f"${pr}[{s} {given_s0}]$"
[…]

### 2023-10-11 scripts/plot_sfs.py

@@ -95,7 +95,8 @@ def main(args):
     snps_daf = defaultdict(list)
 
     for cat in cat_snps:
-        df = df_snps[df_snps[f"cat_{args.method}"].str.contains(f"|{cat}|", regex=False)]
+        # mask of finite values
+        df = df_snps[df_snps[f"cat_{args.method}"].str.contains(f"|{cat}|", regex=False, na=False)]
         for k in df["count"]:
             if max_daf < sample_size:
                 count = [np.random.hypergeometric(k, sample_size - k, max_daf) for _ in range(args.nbr_replicates)]

### 2023-10-11 scripts/tex_sfs.py

@@ -43,20 +43,19 @@ def main(args):
         o.write("\\end{center}\n")
 
         for sp, nested_dict_2 in nested_dict_1.items():
-            o.write("\\subsection{" + (sp.split(" ")[0] if sp in ["Capra hircus", "Ovis aries"] else sp) + "} \n \n")
+            o.write("\\section{" + (sp.split(" ")[0] if sp in ["Capra hircus", "Ovis aries"] else sp) + "} \n \n")
             for pop, sfs in nested_dict_2.items():
                 if len(nested_dict_2) > 1:
-                    o.write("\\subsubsection{" + sample_dico[format_pop(pop)] + "} \n \n")
+                    o.write("\\subsection{" + sample_dico[format_pop(pop)] + "} \n \n")
 
                 dfe_suffix = f"{sp}.{pop}.{method}.pdf".replace(' ', '_')
                 dfe_path = f"{args.dfe_prefix}{dfe_suffix}"
-                o.write(minipage(0.49, dfe_path))
-
                 hist_suffix = f"{sp}.{pop}.pdf".replace(' ', '_')
                 hist_path = f"{args.hist_prefix}{hist_suffix}"
+                o.write(minipage(0.49, dfe_path))
                 o.write(minipage(0.49, hist_path))
                 o.write("\\\\ \n")
-                o.write(minipage(0.49, sfs))
+                o.write(minipage(0.49, sfs.replace("-sfs.pdf", "-sfs.normalize.pdf")))
                 for model in ["C", "D"]:
                     polyDFE = sfs.replace("-sfs.pdf", f".polyDFE_{model}.pdf")
                     if os.path.exists(polyDFE):

### 2023-10-11 manuscript/main-revision.tex
Manuscript revision, updated figures.

@@
 Using methods that quantify selection at the population level, we have confirmed that beneficial back-mutations are indeed positively selected in extant populations.
-We observe that beneficial back-mutations represent between 20\% and 40\% of all beneficial mutations in 21 of 28 populations analyzed, showing that a substantial part of ongoing positive selection is not driven by adaptation to environmental change in mammals.
+We observe that beneficial back-mutations represent between 15\% and 45\% of all beneficial mutations in 24 of 28 populations analyzed, showing that a substantial part of ongoing positive selection is not driven by adaptation to environmental change in mammals.
 Our work shows that deleterious substitutions are accumulating in mammals and are being reverted, generating a balance in which genomes are damaged and restored simultaneously at different loci, ultimately resulting in a widespread signal of non-adaptive positive selection.
@@
     The availability of large-scale genomic data and the development of theoretical models have enabled the detection and quantification of substitution rate changes across genes and lineages~\cite{yang_statistical_2000, eyre-walker_genomic_2006, moutinho_variation_2019}.
-    These approaches, now common practice in evolutionary biology, helped better understand the processes underpinning the rates of molecular evolution.
+    These approaches, now common practice in evolutionary biology, have helped better understand the processes underpinning the rates of molecular evolution, contributing to disentangling the effects of mutation, selection and drift in evolution~\cite{lynch_mutation_2023}.
     However, a collateral effect has been conflating beneficial mutations with adaptive evolution when adaptive evolution is not the only process that can lead to beneficial mutations~\cite{charlesworth_other_2007, mustonen_fitness_2009}.
@@
     In a constant environment, a deleterious mutation can reach fixation by genetic drift~\cite{Ohta1992}.
-    A new mutation restoring the ancestral fitness will thus be beneficial (fig.~\ref{fig:fitness-landscape}B), even though the environment has not changed~\cite{hartl_compensatory_1996, sella_application_2005, mustonen_fitness_2009, cvijovic_fate_2015}.
+    A new mutation restoring the ancestral fitness will thus be beneficial (fig.~\ref{fig:fitness-landscape}B), even though the environment has not changed~\cite{gillespie_ohta_1995, hartl_compensatory_1996, sella_application_2005, mustonen_fitness_2009, cvijovic_fate_2015}.
     The restoration of the ancestral fitness can either happen through a mutation at a different locus –~called a compensatory mutation~\cite{hartl_compensatory_1996, mustonen_fitness_2009}, or at the locus of the initial mutation –~called a beneficial back-mutation~\cite{piganeau_estimating_2003, charlesworth_other_2007}.
@@
     However, differentiating between an adaptive mutation and a beneficial back-mutation remains challenging~\cite{chi_detecting_2020}.
-    Indeed, an adaptive mutation responding to a change in the environment and a beneficial back-mutation have equivalent consequences for their bearer~\cite{charlesworth_other_2007}.
+    Indeed, an adaptive mutation responding to a change in the environment and a beneficial back-mutation have equivalent fitness consequences for their bearer~\cite{charlesworth_other_2007}.
     Similarly, at the population level, both types of mutations will result in a positive transmission bias of the beneficial allele.
@@
     Additionally, the direction of adaptive evolution is unpredictable because it is caused by an unforeseen change in the environment and, hence, in the underlying fitness landscape~\cite{bazykin_changing_2015}.
-    On the other hand, beneficial back-mutations are predictable if the underlying stable fitness landscape is known because changes from non-optimal amino acids to optimal ones will be expected.
+    On the other hand, beneficial back-mutations are predictable because, under a stable fitness landscape, any change from non-optimal to optimal amino acids will move back the site towards the equilibrium expected under the fitness landscape~\cite{moses_inferring_2009, fischer_germline_2011, chen_hunting_2021}.
+    It can then be distinguished from truly novel beneficial mutations because the latter are not expected to mutate towards amino-acids of higher fitnesses defined by the stable fitness landscape.
 
     \subsection*{Fitness landscape reconstruction}
+
     The mutation-selection framework permits to link the patterns of substitution along a phylogeny with the underlying fitness landscape~\cite{halpern_evolutionary_1998, mccandlish_modeling_2014}.
     Such mutation-selection models applied to protein-coding DNA sequences allow us to estimate relative fitnesses for all amino acids for each site of the sequence, explicitly assuming that the underlying fitness landscape is stable along the phylogenetic tree~\cite{rodrigue_mechanistic_2010, tamuri_estimating_2012, rodrigue_detecting_2017}.
-    Importantly, because mutation-selection models at the phylogenetic scale are based on population-genetics equations, their estimates of selection coefficients are directly interpretable as fitness effects for an individual within a population.
+    Moreover, because our model assumes a fixed landscape, it implicitly assumes that $\Ne$ is constant along the phylogeny.
+    The consequences of this assumption are discussed below.
+    Importantly, because mutation-selection models at the phylogenetic scale are based on population-genetics equations, their estimates of selection coefficients are directly interpretable as fitness effects at the population scale.
+    Moreover, because mutation-selection models work at the DNA level, we are able to account for mutational bias in DNA and structure of the genetic code.
+    The model further integrates the shared evolutionary history between samples and their divergence, which, together, allow us to estimate fitness effect in mammalian phylogenies even though sequences are not independent samples and might not represent the equilibrium distribution of amino acids (see section \ref{subsec:s-phylogeny-method} in Materials \& Methods, model parameters in section S1).
 
@@
     Additionally, polymorphism data are available for many species~\cite{howe_ensembl_2021}, as are high quality protein-coding DNA alignments across the genome~\cite{ranwez_orthomam_2007, scornavacca_orthomam_2019}.
-    By performing our analysis on 14,509 orthologous protein-coding genes across 87 species, we focus on sequences under functional constraints across mammals.
+    By performing our analysis on 14,509 orthologous protein-coding genes across 87 species, , we focus on genes shared across all mammals in our dataset and not newly functionalized genes in a lineage.
+    This filtering does in fact bias the selection of genes towards genes which can better fit the stable fitness landscape assumption.
     For each gene, fitting the mutation-selection model to the multi-species sequence alignment, assuming that the underlying fitness landscape is stable along the phylogenetic tree, allows us to obtain relative fitnesses for all amino acids for each site of the alignment (fig.~\ref{fig:method}A).
-    From the fitness landscape, we can calculate the scaled selection coefficient ($\Sphy$) for any possible amino acid change at each position.
-    According to its $\Sphy$ value, we can classify any mutation as either a deleterious mutation toward a less fit amino acid ($\SphyDel \coloneqq \Sphy < -1$), a nearly-neutral mutation ($\SphyNeu \coloneqq -1 < \Sphy <1$) or a beneficial back-mutation toward a known fitter amino acid ($\SphyBen \coloneqq \Sphy > 1$).
-    Having identified which potential DNA changes represent beneficial back-mutations (fig.~\ref{fig:method}B), we retrieved polymorphism data from 28 populations belonging to 6 genera (\textit{Equus}, \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus}, and \textit{Homo}) to assess the presence of beneficial back-mutations at the population scale.
+    Given these relative fitnesses ($F$) for each amino acid, the difference in fitness between a pair of amino acids is the scaled selection coefficient ($\Sphy = \Delta F$).
+    Such scaled selection coefficients ($\Sphy$) are formally the product of the selection coefficient at the individual level ($s$) and the effective population size ($\Ne$), as $\Sphy = 4 \Ne \times s$, and inform us on the strength of selection exerted on amino acids changes.
+    Thus, according to its $\Sphy$ value, we can classify any mutation as either a deleterious mutation toward a less fit amino acid ($\SphyDel \coloneqq \Sphy < -1$), a nearly-neutral mutation ($\SphyNeu \coloneqq -1 < \Sphy <1$) or a beneficial back-mutation toward a known fitter amino acid ($\SphyBen \coloneqq \Sphy > 1$).
+
+    Having identified which potential DNA changes represent beneficial back-mutations (fig.~\ref{fig:method}B), we retrieved polymorphism data from 28 wild and domesticated populations belonging to 6 genera (\textit{Equus}, \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus}, and \textit{Homo}) to assess the presence of beneficial back-mutations at the population scale.
     We focused on mutations currently segregating within populations and substitutions in the terminal branches, and checked if any of these observed changes were beneficial back-mutations (fig.~\ref{fig:method}C-E).
-    In this study, by integrating large-scale genomic datasets at both phylogenetic and population scales, we have been able to estimate the number of beneficial back-mutations across the entire exome of the six genera (figs.~\ref{fig:method}F-G).
+    A similar approach demonstrated the presence of beneficial back-mutations in humans~\cite{moses_inferring_2009, fischer_germline_2011} and in plants~\cite{chen_hunting_2021}.
+    However, the model used to reconstruct the static fitness landscape in these studies can only be applied to deeply conserved protein domains in the tree of life, which corresponds to the subpart of the proteome that evolves slowly.
+    The mutation-selection model used in the present work integrates phylogenetic relationships, and thus allows us to estimate the fitness landscape in shallower phylogenies, and therefore can be applied almost genome-wide~\cite{rodrigue_mutationselection_2010}.
+    Moreover, because our model works at the DNA and codon level instead of the amino acid level, an estimation of genome-wide contribution of beneficial-back mutations to positive selection across populations is accessible.
+    More precisely, we first quantified the likelihood of any DNA mutation to be a beneficial back-mutation, meaning whenever a DNA mutation increases fitness under a stable fitness landscape ($\SphyBen$).
+    Subsequently, by quantifying the total amount of beneficial mutations in the current population across all types of DNA mutations ($\SphyDel$, $\SphyDel$ and $\SphyBen$), we could tease apart beneficial back-mutations from beneficial adaptive mutations resulting from a change in the fitness landscape.
+    Altogether, in this study, by integrating large-scale genomic datasets at both phylogenetic and population scales, we propose a way to explicitly quantify the contribution of beneficial back-mutations to positive selection across the entire exome of the six genera (figs.~\ref{fig:method}F-G).
 
@@
     We recovered the mutations that reached fixation in the terminal branches of the six genera.
-    We only considered mutations fixed in a population as substitutions in the corresponding branch and discarded segregating mutations.
+    We only considered mutations fixed in a population as substitutions in the corresponding branch by discarding mutations segregating in our population samples.
     We classified each substitution identified in the terminal branches as either $\SphyDel$, $\SphyNeu$, or $\SphyBen$ depending on its $\Sphy$ value obtained at the phylogenetic scale (fig.~\ref{fig:method}A-C).
-    Importantly, the mammalian alignment used to estimate the amino acid fitness landscape did not include the genera for which we reconstructed the substitutions to avoid fallacy and circular reasoning.
-    Because $\Sphy$ was based on estimating fitness effects at the mammalian scale, mutations with $\Sphy>1$ were considered beneficial back-mutations ($\SphyBen$) toward a fitter amino acid.
-    Among all the substitutions found in each terminal branch, between 10 and 13\% were $\SphyBen$ (table~S1 and fig.~\ref{fig:homo-afr-results}B for humans).
+    Importantly, the mammalian alignment used to estimate the amino acid fitness landscape did not include the genera for which we estimated selection at the population scale as this would bias the estimate of the fitness landscape and generate circular reasoning.
+    Because $\Sphy$ was based on estimating fitness effects at the phylogenetic scale for all mammals, substitutions with $\Sphy>1$ ($\SphyBen$) bring the population toward an amino acid which is predicted to be fitter in mammals and are thus considered as beneficial back-substitutions rather than a species-specific adaptive change.
+    Among all the substitutions found in each terminal branch, between 10 and 13\% were $\SphyBen$, while instead beneficial back-mutations represent between 0.9 and 1.2\% of all non-synonymous mutations (table~S1 and fig.~\ref{fig:homo-afr-results}A-B for humans).
     In principle, beneficial back-mutations are bound to reach fixation more often than neutral mutations.
     Hence, we calculated the $\dnds$ ratio of non-synonymous over synonymous divergence for all terminal lineages, focusing on the non-synonymous changes predicted as beneficial back-mutations ($\dn(\SphyBen) / \ds$).
-    We obtained values between 1.10 and 1.61 in the different lineages (table~S1), implying i) that $\SphyBen$ mutations reached fixation more frequently than synonymous mutations that are supposed to be neutral, and ii) that these back-mutations are effectively beneficial.
+    We obtained values between 1.17 and 1.75 in the different lineages (table~S2), implying i) that $\SphyBen$ mutations reached fixation more frequently than synonymous mutations that are supposed to be neutral, and ii) that these back-mutations are effectively beneficial.
 
@@
     By discarding all beneficial back-mutations we can obtain an estimate of $\dnds$ which is not inflated.
-    By comparing these two ways of calculating $\dnds$ (see section~\ref{subsec:substitution-mapping-in-the-terminal-branch} in Materials \& Methods), we calculated that beneficial back-mutations inflate $\dnds$ values by between 9 and 11\% across genera while only representing between 1.2 and 1.4\% of non-synonymous mutations (tables~S2-3 and fig.~\ref{fig:homo-afr-results}A for humans).
+    By comparing these two ways of calculating $\dnds$ (see section~\ref{subsec:substitution-mapping-in-the-terminal-branch} in Materials \& Methods), we calculated that beneficial back-mutations inflate $\dnds$ values by between 9 and 12\% across genera while only representing between 0.9 and 1.2\% of non-synonymous mutations (table~S3).
 
     \subsection*{Selection in populations}
-    Second, we assessed whether our calculated $\Sphy$ values are also indicative of the selective forces exerted at the population level.
+    Second, we assessed whether our calculated $\Sphy$ values predicted at the phylogenetic scale were also indicative of the selective forces exerted at the population level.
     We retrieved single nucleotide polymorphisms (SNPs) segregating in 28 mammalian populations.
-    To determine if SNPs were ancestral of derived, we reconstructed the ancestral genome of each population.
+    To determine if SNPs were ancestral of derived, we reconstructed the ancestral exome of each population.
     We then classified every non-synonymous SNP as either $\SphyDel$, $\SphyNeu$, or $\SphyBen$ according its $\Sphy$ value (fig.~\ref{fig:method}B-C).
 
-    In humans, some SNPs have been associated with specific clinical prognosis terms obtained by clinical evaluation of the impact of variants on human Mendelian disorders~\cite{landrum_clinvar_2018}.
-    Thus, they provide an orthogonal estimate of the effect of a mutation on human health, allowing us to evaluate whether this effect follows its predicted fitness effect.
+    In humans, some SNPs have been associated with specific clinical prognosis terms obtained by clinical evaluation of the impact of variants on human Mendelian disorders ~\cite{landrum_clinvar_2018}.
+    Although this classification also relies on deep protein alignments and therefore cannot be considered an independent result from our own, it does provide a consistency check if the effect of a mutation on human health is in line with its fitness effect predicted by our method.
     Therefore, we investigated whether the non-synonymous SNPs classified as $\SphyDel$ or $\SphyBen$ showed enrichment in specific clinical terms compared to SNPs classified as $\SphyNeu$.
@@
     Across our selection classes ($\SphyDel$, $\SphyNeu$ and $\SphyBen$), one can ultimately estimate the proportion of correct and incorrect predictions, leading to an estimation of \textit{precision} and \textit{recall} (fig.~\ref{fig:method}F-G and section~\ref{subsec:precisison_recall} in Materials \& Methods).
-    Across 28 populations of different mammal species, mutations predicted to be deleterious at the phylogenetic scale ($\ProbaPopDel$) were indeed purged at the population scale, with a \textit{precision} in the range of 89--96\% (table~\ref{table:proba} and fig.~\ref{fig:homo-afr-results}D for humans).
-    Conversely, a \textit{recall} in the range of 95--100\% implies that mutations found to be deleterious at the population scale were most likely also predicted to be deleterious at the phylogenetic scale (table~\ref{table:proba}).
+    Across 28 populations of different mammal species, mutations predicted to be deleterious at the phylogenetic scale ($\ProbaPopDel$) were indeed purged at the population scale, with a \textit{precision} in the range of 90--97\% (table~\ref{table:proba} and fig.~\ref{fig:homo-afr-results}D for humans).
+    Conversely, a \textit{recall} in the range of 96--100\% implies that mutations found to be deleterious at the population scale were most likely also predicted to be deleterious at the phylogenetic scale (table~\ref{table:proba}).
     Altogether, purifying selection is largely predictable and amino acids with negative fitness across mammals have been effectively purged away in each population.
 
-    Mutations predicted as $\SphyNeu$ were effectively composed of a mix of neutral and selected mutations with varying \textit{precision} (36--73\%) and \textit{recall} (30--45\%) across the different populations (table~\ref{table:proba}, fig.~\ref{fig:homo-afr-results}D for humans).
+    Mutations predicted as $\SphyNeu$ were effectively composed of a mix of neutral and selected mutations with varying \textit{precision} (36--63\%) and \textit{recall} (32--45\%) across the different populations (table~\ref{table:proba}, fig.~\ref{fig:homo-afr-results}D for humans).
     The variable proportions between populations can be explained by the effective number of individuals in the population ($\Ne$), a major driver of selection efficacy.
-    Since $\Ne$ is not directly measurable, we used Watterson's $\thetaSyn$ as a proxy to order populations by their levels of synonymous diversity.
-    Higher synonymous diversity was associated with a smaller proportion of nearly-neutral mutations (fig.~\ref{fig:diversity}A).
-    This result follows the prediction of the nearly-neutral theory and suggests that in populations with higher diversity (e.g.,~\textit{Bos} or \textit{Ovis}), discrimination between beneficial and deleterious mutations is more likely to occur (figs.~S1-S6).
+    Moreover, estimates of mutation rate per generation ($u$), from \textcite{bergeron_evolution_2023} and \textcite{orlando_recalibrating_2013}, and Watterson’s $\theta$ obtained from the synonymous SFS as in \textcite{achaz_frequency_2009} allow us to obtain $\Ne$ through $\Ne=\theta/(4 \times u)$.
+    Using correlation analyses that accounted for phylogenetic relationship (see section \ref{subsec:correlation-diversity} in Materials \& Methods), we found that higher $\Ne$ was associated with a smaller proportion of nearly-neutral mutations ($r^2=0.31$, $p=0.001$, fig.~\ref{fig:diversity}A).
+    This result follows the prediction of the nearly-neutral theory and suggests that in populations with higher diversity (e.g.,~\textit{Bos} or \textit{Ovis}), discrimination between beneficial and deleterious mutations is more likely to occur (figs.~S1-S3).
     Conversely, many more mutations are effectively neutral in populations with lower diversity (e.g.,~\textit{Homo}).
 
-    Finally, mutations predicted to be beneficial back-mutations based on the selection coefficients at the phylogenetic scale ($\SphyBen$) were indeed beneficial for individuals bearing them, with a \textit{precision} (fig.~\ref{fig:method}F) in the range of 13--86\% (table~\ref{table:proba} and fig.~\ref{fig:homo-afr-results}D for humans).
+    Finally, mutations predicted to be beneficial back-mutations based on the selection coefficients at the phylogenetic scale ($\SphyBen$) were indeed beneficial for individuals bearing them, with a \textit{precision} (fig.~\ref{fig:method}F) in the range of 19--87\% (table~\ref{table:proba} and fig.~\ref{fig:homo-afr-results}D for humans).
     This result confirms that selection towards amino acids restoring existing functions is ongoing in these populations.
-    Importantly, the \textit{recall} value in this case, computed as $\proba [ \SphyBen  \given  \SpopBen]$, is the probability for a beneficial mutation at the population scale to be a beneficial back-mutation, i.e., going toward a fitter amino acid (fig.~\ref{fig:method}G).
+    Importantly, the \textit{recall} value in this case, computed as $\proba [ \SphyBen  \given  \SpopBen]$, is the probability for a beneficial mutation at the population scale to be a beneficial back-mutation, i.e., going toward a fitter amino acid (fig.~\ref{fig:method}G, table~S6).
     In other words, the \textit{recall} value quantifies the number of beneficial mutations restoring damaged genomes instead of creating adaptive innovations.
-    Across the 28 populations, this proportion is in the range of 11--81\% (table~\ref{table:proba}).
+    Across the 28 populations, this proportion is in the range of 11--82\% (table~\ref{table:proba}).
+
+    Because the back-mutation equilibrium model should fit better for genes with uniformly conserved functions, as a control, we filtered out genes under adaptation \cite{latrille_genes_2023}, and indeed we found an increase in the proportion of beneficial back-mutations ($\proba [ \SphyBen  \given  \SpopBen]$), consistent with our expectation (Wilcoxon signed-rank, $s=80$, $p=0.002$, table~S7).
 
@@
     These amino-acid fitness landscapes allow us to predict any mutation’s selection coefficient ($\Sphy$) along a protein-coding sequence.
-    We can compare these selective effects to observations at the population level (figs.~S1-3).
+    We can compare these selective effects to observations at the population level (figs.~S4-6).
     By doing so, we confirmed that mutations predicted to be deleterious ($\SphyDel \coloneqq \Sphy < -1$) are purified away in extant populations.
@@
     We have tested this hypothesis and found that these back-mutations ($\SphyBen \coloneqq \Sphy > 1 $) are indeed beneficial in extant populations.
-    We estimated that between 11 and 81\% of all beneficial mutations in mammalian populations have not been driven by adaptation but instead have reversed deleterious substitutions which have accumulated along the phylogeny.
-    More specifically, in 21 out of 28 populations analyzed, the percentage of beneficial mutations estimated to be back-mutations falls between 20 and 40\%.
+    We estimated that between 11 and 82\% of all beneficial mutations in mammalian populations have not been driven by adaptation but instead have reversed deleterious substitutions which have accumulated along the phylogeny.
+    More specifically, in 24 out of 28 populations analyzed, the percentage of beneficial mutations estimated to be back-mutations falls between 15 and 45\%.
     These results suggest that many beneficial mutations are non-adaptive but rather restore ancestral states of higher fitness.
@@
     Overall, we expect the proportion of beneficial back-mutations to be more dependent on $\Ne$’s long-term expansions and contractions than on the short-term ones~\cite{charlesworth_other_2007,huber_determining_2017}.
-    Indeed the proportion of back-mutations among all beneficial mutations did not show a clear relationship with the synonymous diversity within a population (Watterson's $\thetaSyn$) (fig.~\ref{fig:diversity}B), which should, in theory, reflect the population's short-term $\Ne$.
+    Accounting for phylogenetic relationships, we found no correlation between the proportion of back-mutations and $\Ne$ ($r^2=0.00$, $p=0.772$, fig.~\ref{fig:diversity}B)
 
@@
     However, adaptation is not the only factor hindering the detection of beneficial back-mutations; data quality and potentially inadequate modeling choices of both the fitness landscape and the DFE might also lead to missed predictions.
-    Our model assumes that amino-acid fitness landscapes are site-specific and also independent of one another, whereas under epistasis, the fitness effect of a mutation at a particular site depends on the amino-acids present at other sites~\cite{starr_epistasis_2016, park_epistatic_2022}.
-    Epistasis therefore allows for compensatory mutations, which restore fitness through mutations at loci different from where deleterious mutations take place, and this process also leaves signals interpretable as non-adaptive beneficial mutations~\cite{hartl_compensatory_1996, pollock_strong_2014, starr_epistasis_2016}.
-    Also, epistasis has been shown to play a role in the evolution of protein-coding genes, with amino-acid residues in contact within a protein or between proteins tending to co-evolve~\cite{breen_epistasis_2012, starr_epistasis_2016}.
-    Particularly, the residues in contact co-evolve to become more compatible with each other generating an entrenchment, making empirical evidence for beneficial back-mutations harder to find since restoring mutations becomes less and less likely to occur over time~\cite{goldstein_nonadaptive_2015, goldstein_sequence_2017, park_epistatic_2022}.
-    Nevertheless, the fact that we observe such a high proportion of beneficial back-mutations suggests that the underlying assumptions of our model, namely site-independence, implying no epistasis, and a static fitness landscape, are a reasonable approximation for the underlying fitness landscape of proteins.
-    Our results imply that the fitness effects of new mutations are mostly conserved across mammalian orthologs, in agreement with other studies showing that for conserved orthologs with similar structures and functions, models without epistasis provide a reasonable estimate of fitness effects in protein coding genes~\cite{ashenberg_mutational_2013, youssef_consequences_2020}.
-    Moreover, a mutation inferred as nearly-neutral at the phylogenetic scale ($\SphyNeu$) but positively selected at the population scale ($\SpopBen$) will also be considered a missed prediction, even if this discrepancy could just be due to a population size expansion~\cite{lanfear_population_2014, jones_shifting_2017, platt_protein_2018}.
-    Given this inflation of missed predictions, our estimated proportion of adaptive mutations among beneficial ones is likely to be an overestimation.
-    In practice, advantageous mutations can be depleted in the $\SphyNeu$ and $\SphyDel$ class in some species but pervasive in others, depending on the model used to infer the DFE at the population scale (tables~S6-9).
+
+    Our model assumes that amino-acid fitness landscapes are site-specific and also independent of one another, whereas under pervasive epistasis, the fitness effect of any mutation at a particular site would depend on the amino-acids present at other sites.
+    Epistasis has been shown to play a role in the evolution of protein-coding genes, with amino-acid residues in contact within a protein or between proteins tending to co-evolve~\cite{morcos_directcoupling_2011, marks_protein_2012, starr_epistasis_2016}.
+    Particularly, the residues in contact co-evolve to become more compatible with each other generating an entrenchment~\cite{goldstein_nonadaptive_2015, goldstein_sequence_2017, park_epistatic_2022}.
+    Epistasis therefore allows for compensatory mutations, which restore fitness through mutations at loci different from where deleterious mutations take place, representing, hence, another case of non-adaptive beneficial mutations, but one which is not accounted for by our method.
+    Therefore, many of the beneficial mutations that we classify as putatively adaptive might in fact be compensatory mutations, making our estimation of the rate of non-adaptive beneficial mutations conservative.
+
+    Despite epistasis being an important factor in protein evolution, several deep mutational scanning laboratory experiments have revealed that a site-specific fitness landscape is a reasonable approximation of the fitness landscape of proteins, and even predicts the evolution of sequences in nature~\cite{ashenberg_mutational_2013, doud_sitespecific_2015, bloom_identification_2017}.
+    Additionally, the fact that we observe such a high proportion of beneficial back-mutations suggests that the underlying assumptions of our model, namely site-independence, implying no epistasis, and a static fitness landscape, are a reasonable approximation for the underlying fitness landscape of proteins~\cite{youssef_consequences_2020}.
+    Our results imply that the fitness effects of new mutations are mostly conserved across mammalian orthologs, in agreement with other studies showing that for conserved orthologs with similar structures and functions, models without epistasis provide a reasonable estimate of fitness effects in protein coding genes~\cite{ashenberg_mutational_2013, doud_sitespecific_2015, bloom_identification_2017, youssef_consequences_2020}.
+
+    Moreover, because our model assumes a fixed landscape, it implicitly assumes that $\Ne$ is constant along the phylogeny.
+    Fluctuations due to changes in the fitness landscape or in $\Ne$ will be averaged out by the assumption of the current model that $\Ne$ is constant across lineages.
+    It was recently shown~\cite{latrille_inferring_2021}, using highly computer intensive mutation-selection models with fluctuating $\Ne$, that relaxing the assumption of a constant $\Ne$ results in more extreme estimates of amino-acid fitnesses than with the standard model used in the present study.
+    In other words, by assuming a constant $\Ne$, we are underpowered to detect beneficial back-mutations since amino-acids will have more similar fitnesses and mutations that would otherwise fall into $\SpopBen$ or $\SpopDel$ will be classified as $\SpopNeu$, resulting ultimately in lower estimates of the proportion of beneficial back-mutations ($\proba [ \SphyBen  \given  \SpopBen]$).
+    Given this inflation of missed predictions due to change in population sizes~\cite{lanfear_population_2014, jones_shifting_2017, platt_protein_2018}, our estimated proportion of beneficial back-mutations among adaptive ones is likely to be an underestimation.
+    In practice, advantageous mutations can be depleted in the $\SphyNeu$ and $\SphyDel$ class in some species but pervasive in others, depending on the model used to infer the DFE at the population scale (tables~S8-12).
     It appears that our estimation can be quite sensitive to model misspecification and overall, while we provide an order of magnitude for the contribution of beneficial back-mutations to positive selection, further methodological development on the estimation of the distribution of fitness effects is needed to increase the confidence on this value.
@@
     Fitting the mutation-selection model on a multi-species sequence alignment leads to an estimation of the gene-wide $4 \times 4$ nucleotide mutation rate matrix ($\UniDimArray{\mu}$) as well as the $20$ amino-acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$.
+    The priors and full configuration of the model are given in section S1.
+    From a technical perspective, the Bayesian estimation is a two-step procedure.
+    The first step is a data augmentation of the alignment, consisting in sampling a detailed substitution history along the phylogenetic tree for each site, given the current value of the model parameters.
+    In the second step, the parameters of the model can then be directly updated by a Gibbs sampling procedure, conditional on the current substitution history.
+    Alternating between these two sampling steps yields a Markov chain Monte-Carlo (MCMC) procedure whose equilibrium distribution is the posterior probability density of interest~\cite{lartillot_bayesian_2004, rodrigue_bayesian_2008}.
+    Additionally, across-site heterogeneities in amino acid fitness profiles are captured by a Dirichlet process.
+    More precisely, the number of amino-acid fitness profiles estimated is lower than the number of sites in the alignment.
+    Consequently each profile has several sites assigned to it, resulting in a particular configuration of the Dirichlet process.
+    Conversely, sites with similar signatures are assigned to the same fitness profile.
+    This configuration of the Dirichlet process is resampled through the MCMC, so that each site has its own posterior distribution of amino acid fitness profile~\cite{rodrigue_mutationselection_2010, lartillot_inference_2013}.
+    From a more mechanistic perspective, even though not all amino-acids occur at every single codon site of the DNA alignment, we can nevertheless estimate the distribution of amino-acid fitnesses by generalizing the information recovered across sites and across amino-acids based on the phylogenetic relationship among samples.
+    In particular, synonymous substitutions along the tree contain the signal to estimate branch lengths and the nucleotide transition matrix, while non-synonymous substitutions contain information on fitness difference between codons connected by single nucleotide changes~\cite{rodrigue_mutationselection_2010}.
+
     The selection coefficient for a mutation from codon $a$ to codon $b$ at site $i$ is defined as:
@@
     In our subsequent derivation the source ($a$) and target ($b$) codons as well as the site ($i$) are implicit and thus never explicitly written.
-    We used the Bayesian software \textit{BayesCode} (\url{https://github.com/ThibaultLatrille/bayescode}) to estimate the selection coefficients for each protein-coding gene in the mammalian dataset.
-    We ran the Markov chain Monte-Carlo (MCMC) algorithm implemented in BayesCode for $2,000$ generations as described in \textcite{latrille_genes_2023}.
+
+    We used the Bayesian software \textit{BayesCode} (\url{https://github.com/ThibaultLatrille/bayescode}, v1.3.1) to estimate the selection coefficients for each protein-coding gene in the mammalian dataset.
+    We ran the MCMC algorithm implemented in BayesCode for $2,000$ generations as described in \textcite{latrille_genes_2023}.
     For each gene, after discarding a burn-in period of $1,000$ generations of MCMC, we obtained posterior mean estimates (over the $1,000$ generations left of MCMC) of the mutation rate matrix ($\UniDimArray{\mu}$) as well as the $20$ amino acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$.
@@
     Deriving such opportunities is necessary to estimate the strength of selection exerted at the population scale since different categories might have different mutational opportunities, and thus polymorphism and divergence need to be corrected accordingly (see sections~\ref{subsec:substitution-mapping-in-the-terminal-branch},~\ref{subsec:s-polymorphism-method}, and~\ref{subsec:precisison_recall}).
-    To calculate mutational opportunities, we reconstructed the ancestral genome of each of the 28 populations, which differs from the corresponding species' reference genome since it accounts for the variability present in the specific population.
-    So, for each population, we used the polarized SNPs to reconstruct the ancestral DNA sequence, containing only substitutions and no segregating polymorphisms.
-    If a SNP was still segregating in the population, we used its ancestral version.
+    To calculate mutational opportunities, we reconstructed the ancestral exome of each of the 28 populations by using the most likely ancestral state from est-usfs (see section \ref{subsec:polymorphism-dataset}), which differs from the corresponding species reference exome since it accounts for the variability present in the specific population.
 
-    From the reconstructed ancestral genome, all possible mutations were computed, weighted by the instantaneous rate of change between nucleotides obtained from the mutation rate matrix ($\UniDimArray{\mu}$, see section~\ref{subsec:s-phylogeny-method}), summing to $\mu_{\text{tot}}$ across the whole genome, and to $\mu_{\text{syn}}$ when restricted to synonymous mutations.
-    Finally, the mutational opportunities for synonymous mutations were computed as the total number of sites across the genome ($L_{\text{tot}}$) weighted by the proportion of synonymous mutations among all possible mutations as:
+    From the reconstructed ancestral exome, all possible mutations were computed, weighted by the instantaneous rate of change between nucleotides obtained from the mutation rate matrix ($\UniDimArray{\mu}$, see section~\ref{subsec:s-phylogeny-method}), summing to $\mu_{\text{tot}}$ across the whole exome, and to $\mu_{\text{syn}}$ when restricted to synonymous mutations.
+    Finally, the mutational opportunities for synonymous mutations were computed as the total number of sites across the exome ($L_{\text{tot}}$) weighted by the proportion of synonymous mutations among all possible mutations as:
 
@@
     Similarly, for non-synonymous mutations, the total mutation rate for each class of selection $\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$, called $\mu\left( \Sphyclass \right)$, was estimated as the sum across all non-synonymous mutations if their selection coefficient at the phylogenetic scale is in the class $\Sphy \in \Sphyclass$.
-    Accordingly, the mutational opportunities ($L \left( \Sphyclass \right)$) for each class of selection coefficient ($\Sphyclass$) was finally computed as the total number of sites across the genome ($L_{\text{tot}}$) weighted by the ratio of the aggregated mutations rates falling in the class $\mu\left( \Sphyclass \right)$:
+    Accordingly, the mutational opportunities ($L \left( \Sphyclass \right)$) for each class of selection coefficient ($\Sphyclass$) was finally computed as the total number of sites across the exome ($L_{\text{tot}}$) weighted by the ratio of the aggregated mutations rates falling in the class $\mu\left( \Sphyclass \right)$:
     \begin{equation}
@@
     \label{subsec:substitution-mapping-in-the-terminal-branch}
-    For each gene and each population with polymorphism data available, the genome at the base of the population genealogy was reconstructed (see section~\ref{subsec:nunber-of-sites}).
-    We used the ancestral genome reconstructed at the base of the population genealogy and the three closest outgroups found in the OrthoMaM alignment to infer the ancestral protein-coding DNA sequences for each node of the 4-taxa tree by applying the M5 codon model (gamma site rate variation) as implemented in FastML.v3.11~\cite{ashkenazy_fastml_2012}.
-    All polarized codon substitutions were then obtained by comparing the ancestral protein-coding DNA sequences before the split from the sister species (closest outgroup) to the genome at the base of the population genealogy.
+    We inferred the protein-coding DNA sequences for each node of the 4-taxa tree containing the focal species and the three closest outgroups species found in the OrthoMaM alignment by applying the M5 codon model (gamma site rate variation) as implemented in FastML.v3.11~\cite{ashkenazy_fastml_2012}.
+    Consequently, for each focal species we reconstructed the protein coding DNA sequence of the whole exome at the base of the terminal branch before the split from the sister species.
     We considered \textit{Ceratotherium simum simum} as \textit{Equus caballus'} sister species; \textit{Bison bison bison} as \textit{Bos taurus'} sister species; \textit{Pantholops hodgsonii} as \textit{Ovis aries'} sister species; \textit{Pantholops hodgsonii} as \textit{Capra hircus'} sister species; \textit{Macaca mulatta} as \textit{Chlorocebus sabaeus'} sister species and finally, we considered \textit{Pan troglodytes} as \textit{Homo sapiens'} sister species.
-    The selection coefficient ($\Sphy$) of each substitution was then obtained by comparing the difference in amino acid fitnesses for each polarized non-synonymous codon substitution, by referring to the site-specific fitness profile obtained in the phylogeny-based method (see section~\ref{subsec:s-phylogeny-method}).
+    From this reconstructed exome, we determined the direction of the substitution occurring along the terminal branch of the phylogenetic tree toward each extant population.
+    SNPs segregating in the population were discarded, and the most likely ancestral state from est-usfs (see section \ref{subsec:polymorphism-dataset}) was used as the reference for each extant population.
+    For each substitution, we recovered its $\Sphy$ value as calculated through the phylogeny-based method (see section~\ref{subsec:s-phylogeny-method}).
     Finally, the rate of non-synonymous over synonymous substitutions for a given class of selection coefficient ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$) was computed as:
@@
     \end{align}
-    where $D \left( \Sphyclass \right) $ was the number of non-synonymous substitutions in class $\Sphyclass$, $D_{\text{syn}}$ was the number of synonymous substitutions across the genome, while $L \left( \Sphyclass \right)$ and $L_{\text{syn}}$ were the numbers of non-synonymous and synonymous mutational opportunities, respectively, as defined in section~\ref{subsec:nunber-of-sites}.
+    where $D \left( \Sphyclass \right) $ was the number of non-synonymous substitutions in class $\Sphyclass$, $D_{\text{syn}}$ was the number of synonymous substitutions across the exome, while $L \left( \Sphyclass \right)$ and $L_{\text{syn}}$ were the numbers of non-synonymous and synonymous mutational opportunities, respectively, as defined in section~\ref{subsec:nunber-of-sites}.
     $\delta(\dnds)$ was computed as the difference between $\dnds$ computed over all substitutions and $\dnds$ when we removed beneficial back-mutations $\dn (\Sphy < 1) / \ds$, normalized by $\dnds$.
@@
 
+    \subsection{Correlation with effective population size ($\Ne$)}
+    \label{subsec:correlation-diversity}
+    Genetic diversity estimator Watterson's $\thetaSyn$ was obtained for each population from the synonymous SFS as in \textcite{achaz_frequency_2009}.
+    For each popuation, $\Ne$ was estimated from the equation $\Ne=\thetaSyn / (4 \times u)$, where $u$ is the mutation rate per generation.
+    Estimates for $u$ were averaged per species across the pedigree-based estimation in \textcite{bergeron_evolution_2023} for \textit{Homo}, \textit{Bos}, \textit{Capra} and \textit{Chlorocebus}.
+    For \textit{Ovis} we used the estimated $u$ of \textit{Capra}.
+    For \textit{Equus}, we used $u$ as estimated in \textcite{orlando_recalibrating_2013} ($u=7.24\times10^{-9}$).
+    Because a correlation must account for phylogenetic relationship and non-independence of samples, we fitted a Phylogenetic Generalized Linear Model in \textit{R} with the package \texttt{caper}~\cite{orme_caper_2013}.
+    The mammalian dated tree is obtained from TimeTree~\cite{kumar_timetree_2017} and pruned to the species under study, with multi-furcation of the different populations from each species placed at the same divergence time as the species (section S4.1).
+
     \section*{Data availability}
@@
         \caption{
-            (A) Distribution of scaled selection coefficients ($\Sphy$), predicted for all possible mutations away from the ancestral human genome.
-            Mutations are divided into three classes of selection: deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial ($\SphyBen$, supposedly beneficial back-mutations).
-            (B) Distribution of scaled selection coefficients ($\Sphy$) for all observed substitutions along the \textit{Homo} branch after the \textit{Homo}-\textit{Pan} split.
+            (A) Distribution of scaled selection coefficients ($\Sphy$), predicted for all possible non-synonymous DNA mutations away from the ancestral human exome (section \ref{subsec:nunber-of-sites}).
+            Mutations are divided into three classes of selection: deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial ($\SphyBen$, supposedly beneficial back-mutations)
+            (B) Distribution of scaled selection coefficients ($\Sphy$) for all observed substitutions along the \textit{Homo} branch after the \textit{Homo}-\textit{Pan} split (section \ref{subsec:substitution-mapping-in-the-terminal-branch}).
             If there are fewer substitutions than expected, this class is thus undergoing purifying selection, as is the case for $\SphyDel$.
@@
             At high frequencies, deleterious mutations are underrepresented.
-            (D) Proportion of beneficial $\ProbaPopDel$, nearly-neutral $\ProbaPopNeu$, and deleterious mutations $\ProbaPopBen$ estimated at the population scale for each class of selection at the phylogenetic scale.
+            (D) Proportion of beneficial $\ProbaPopDel$, nearly-neutral $\ProbaPopNeu$, and deleterious mutations $\ProbaPopBen$ estimated at the population scale for each class of selection at the phylogenetic scale (section \ref{subsec:s-polymorphism-method}).
 Proportions depicted here are not weighted by their mutational opportunities.
@@
         \caption{
-            (A) Proportion of nearly-neutral mutations at the population scale ($\proba [ \SpopNeu]$ in the y-axis), shown as a function of the synonymous diversity (Watterson's $\thetaSyn$ in the x-axis).
-            (B) Proportion of beneficial back-mutations among all beneficial mutations ($\proba [ \SphyBen  \given  \SpopBen]$ in the y-axis), shown as a function of the synonymous diversity (Watterson's $\thetaSyn$ in the x-axis).
+            Populations in circles, mean of the species across the populations as squares.
+            (A) Proportion of nearly-neutral mutations at the population scale ($\proba [ \SpopNeu]$ in the y-axis), shown as a function of estimated effective population size ($\Ne$ in the x-axis).
+            (B) Proportion of beneficial back-mutations among all beneficial mutations ($\proba [ \SphyBen  \given  \SpopBen]$ in the y-axis), shown as a function of $\Ne$ in x-axis.
+            Correlations account for phylogenetic relationship and non-independence of samples, through the fit of a Phylogenetic Generalized Linear Model (see section~\ref{subsec:s-polymorphism-method} in Materials \& Methods).
         }
@@
                 \textbf{Species} &
-                $\bm{\thetaSyn}$ &
+                $\bm{\Ne}$ &
                 \makecell{\textbf{Precision} \\ $\bm{\proba [\SpopDel \given \SphyDel]}$} &
@@
                 \\   \midrule
-                \rowcolor{LIGHTGREY}              Equus c. & Equus caballus        & $ 0.002$ & $ 0.908$ & $ 0.976$ & $ 0.730$ & $ 0.383$ & $ 0.580$ & $ 0.809$ \\
-                Iran               & Bos taurus        & $ 0.002$ & $ 0.898$ & $ 1.000$ & $ 0.632$ & $ 0.340$ & $ 0.857$ & $ 0.277$ \\
-                Uganda              & Bos taurus        & $ 0.005$ & $ 0.942$ & $ 0.963$ & $ 0.497$ & $ 0.393$ & $ 0.488$ & $ 0.483$ \\
-                \rowcolor{LIGHTGREY} Australia            & Capra hircus        & $ 0.003$ & $ 0.934$ & $ 0.966$ & $ 0.524$ & $ 0.425$ & $ 0.368$ & $ 0.196$ \\
-                \rowcolor{LIGHTGREY} France                                    & Capra hircus          & $ 0.004$ & $ 0.936$ & $ 0.965$ & $ 0.506$ & $ 0.412$ & $ 0.368$ & $ 0.211$ \\
-                \rowcolor{LIGHTGREY} Iran (C. aegagrus)                    & Capra hircus          & $ 0.004$ & $ 0.940$ & $ 0.961$ & $ 0.478$ & $ 0.438$ & $ 0.221$ & $ 0.114$ \\
-                \rowcolor{LIGHTGREY} Iran                        & Capra hircus          & $ 0.004$ & $ 0.945$ & $ 0.960$ & $ 0.419$ & $ 0.400$ & $ 0.368$ & $ 0.211$ \\
-                \rowcolor{LIGHTGREY} Italy                                 & Capra hircus          & $ 0.004$ & $ 0.937$ & $ 0.963$ & $ 0.548$ & $ 0.426$ & $ 0.270$ & $ 0.220$ \\
-                \rowcolor{LIGHTGREY} Morocco                                 & Capra hircus          & $ 0.004$ & $ 0.942$ & $ 0.964$ & $ 0.522$ & $ 0.428$ & $ 0.368$ & $ 0.276$ \\
-                Iran           & Ovis aries & $ 0.007$ & $ 0.953$ & $ 0.954$ & $ 0.450$ & $ 0.406$ & $ 0.169$ & $ 0.392$ \\
-                Iran (O. orientalis)  & Ovis aries & $ 0.009$ & $ 0.958$ & $ 0.953$ & $ 0.417$ & $ 0.431$ & $ 0.153$ & $ 0.180$ \\
-                Iran (O. vignei)           & Ovis aries & $ 0.007$ & $ 0.960$ & $ 0.951$ & $ 0.360$ & $ 0.449$ & $ 0.195$ & $ 0.133$ \\
-                Various             & Ovis aries & $ 0.008$ & $ 0.955$ & $ 0.954$ & $ 0.435$ & $ 0.426$ & $ 0.190$ & $ 0.228$ \\
-                Morocco              & Ovis aries & $ 0.008$ & $ 0.956$ & $ 0.955$ & $ 0.449$ & $ 0.410$ & $ 0.136$ & $ 0.353$ \\
-                \rowcolor{LIGHTGREY} Barbados              & Chlorocebus sabaeus & $ 0.004$ & $ 0.925$ & $ 0.969$ & $ 0.536$ & $ 0.377$ & $ 0.565$ & $ 0.306$ \\
-                \rowcolor{LIGHTGREY} Central Afr. Rep.       & Chlorocebus sabaeus & $ 0.006$ & $ 0.940$ & $ 0.964$ & $ 0.495$ & $ 0.404$ & $ 0.429$ & $ 0.274$ \\
-                \rowcolor{LIGHTGREY} Ethiopia        & Chlorocebus sabaeus & $ 0.005$ & $ 0.925$ & $ 0.969$ & $ 0.560$ & $ 0.400$ & $ 0.462$ & $ 0.239$ \\
-                \rowcolor{LIGHTGREY} Gambia             & Chlorocebus sabaeus & $ 0.005$ & $ 0.934$ & $ 0.969$ & $ 0.610$ & $ 0.409$ & $ 0.486$ & $ 0.774$ \\
-                \rowcolor{LIGHTGREY} Kenya                                 & Chlorocebus sabaeus        & $ 0.005$ & $ 0.938$ & $ 0.965$ & $ 0.519$ & $ 0.434$ & $ 0.478$ & $ 0.243$ \\
-                \rowcolor{LIGHTGREY} Nevis                        & Chlorocebus sabaeus        & $ 0.003$ & $ 0.923$ & $ 0.970$ & $ 0.609$ & $ 0.393$ & $ 0.516$ & $ 0.393$ \\
-                \rowcolor{LIGHTGREY} South Africa                              & Chlorocebus sabaeus        & $ 0.006$ & $ 0.935$ & $ 0.965$ & $ 0.542$ & $ 0.409$ & $ 0.490$ & $ 0.360$ \\
-                \rowcolor{LIGHTGREY} Saint Kitts                                & Chlorocebus sabaeus        & $ 0.004$ & $ 0.926$ & $ 0.969$ & $ 0.562$ & $ 0.377$ & $ 0.515$ & $ 0.367$ \\
-                \rowcolor{LIGHTGREY} Zambia                             & Chlorocebus sabaeus        & $ 0.006$ & $ 0.937$ & $ 0.965$ & $ 0.494$ & $ 0.413$ & $ 0.499$ & $ 0.249$ \\
-                African                             & Homo sapiens        & $ 0.002$ & $ 0.899$ & $ 0.970$ & $ 0.571$ & $ 0.334$ & $ 0.678$ & $ 0.319$ \\
-                Admixed American                             & Homo sapiens        & $ 0.002$ & $ 0.888$ & $ 0.972$ & $ 0.581$ & $ 0.301$ & $ 0.635$ & $ 0.361$ \\
-                East Asian                             & Homo sapiens        & $ 0.002$ & $ 0.894$ & $ 0.973$ & $ 0.583$ & $ 0.335$ & $ 0.611$ & $ 0.233$ \\
-                European                             & Homo sapiens        & $ 0.002$ & $ 0.896$ & $ 0.972$ & $ 0.581$ & $ 0.350$ & $ 0.619$ & $ 0.217$ \\
-                South Asian                             & Homo sapiens        & $ 0.002$ & $ 0.898$ & $ 0.972$ & $ 0.580$ & $ 0.354$ & $ 0.628$ & $ 0.222$ \\
+                \rowcolor{LIGHTGREY} Equus c. & Equus caballus & $7.5\times 10^{4}$ & $ 0.923$ & $ 0.972$ & $ 0.570$ & $ 0.341$ & $ 0.648$ & $ 0.536$ \\
+                Iran & Bos taurus & $5.6\times 10^{4}$ & $ 0.915$ & $ 1.000$ & $ 0.632$ & $ 0.358$ & $ 0.873$ & $ 0.243$ \\
+                Uganda & Bos taurus & $1.3\times 10^{5}$ & $ 0.951$ & $ 0.969$ & $ 0.495$ & $ 0.414$ & $ 0.576$ & $ 0.415$ \\
+                \rowcolor{LIGHTGREY} Australia & Capra hircus & $1.7\times 10^{5}$ & $ 0.944$ & $ 0.971$ & $ 0.527$ & $ 0.437$ & $ 0.368$ & $ 0.177$ \\
+                \rowcolor{LIGHTGREY} France & Capra hircus & $1.9\times 10^{5}$ & $ 0.946$ & $ 0.971$ & $ 0.508$ & $ 0.423$ & $ 0.368$ & $ 0.190$ \\
+                \rowcolor{LIGHTGREY} Iran (C. aegagrus) & Capra hircus & $1.9\times 10^{5}$ & $ 0.948$ & $ 0.969$ & $ 0.486$ & $ 0.444$ & $ 0.368$ & $ 0.165$ \\
+                \rowcolor{LIGHTGREY} Iran & Capra hircus & $2.3\times 10^{5}$ & $ 0.953$ & $ 0.966$ & $ 0.425$ & $ 0.407$ & $ 0.368$ & $ 0.193$ \\
+                \rowcolor{LIGHTGREY} Italy & Capra hircus & $1.9\times 10^{5}$ & $ 0.947$ & $ 0.971$ & $ 0.551$ & $ 0.439$ & $ 0.368$ & $ 0.243$ \\
+                \rowcolor{LIGHTGREY} Morocco & Capra hircus & $2.2\times 10^{5}$ & $ 0.950$ & $ 0.970$ & $ 0.527$ & $ 0.440$ & $ 0.368$ & $ 0.245$ \\
+                Iran & Ovis aries & $3.8\times 10^{5}$ & $ 0.961$ & $ 0.961$ & $ 0.452$ & $ 0.415$ & $ 0.205$ & $ 0.407$ \\
+                Iran (O. orientalis) & Ovis aries & $4.5\times 10^{5}$ & $ 0.964$ & $ 0.960$ & $ 0.420$ & $ 0.445$ & $ 0.193$ & $ 0.190$ \\
+                Iran (O. vignei) & Ovis aries & $3.7\times 10^{5}$ & $ 0.967$ & $ 0.959$ & $ 0.361$ & $ 0.470$ & $ 0.190$ & $ 0.110$ \\
+                Various & Ovis aries & $4.1\times 10^{5}$ & $ 0.962$ & $ 0.962$ & $ 0.433$ & $ 0.440$ & $ 0.229$ & $ 0.222$ \\
+                Morocco & Ovis aries & $ 4\times 10^{5}$ & $ 0.962$ & $ 0.961$ & $ 0.462$ & $ 0.424$ & $ 0.211$ & $ 0.514$ \\
+                \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus & $1.1\times 10^{5}$ & $ 0.935$ & $ 0.975$ & $ 0.565$ & $ 0.402$ & $ 0.648$ & $ 0.293$ \\
+                \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus & $1.7\times 10^{5}$ & $ 0.948$ & $ 0.971$ & $ 0.508$ & $ 0.423$ & $ 0.535$ & $ 0.275$ \\
+                \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus & $1.4\times 10^{5}$ & $ 0.935$ & $ 0.975$ & $ 0.580$ & $ 0.416$ & $ 0.552$ & $ 0.245$ \\
+                \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus & $1.4\times 10^{5}$ & $ 0.944$ & $ 0.975$ & $ 0.654$ & $ 0.437$ & $ 0.577$ & $ 0.821$ \\
+                \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus & $1.5\times 10^{5}$ & $ 0.946$ & $ 0.972$ & $ 0.538$ & $ 0.453$ & $ 0.588$ & $ 0.257$ \\
+                \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus & $ 1\times 10^{5}$ & $ 0.933$ & $ 0.976$ & $ 0.629$ & $ 0.412$ & $ 0.599$ & $ 0.358$ \\
+                \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus & $1.8\times 10^{5}$ & $ 0.944$ & $ 0.971$ & $ 0.548$ & $ 0.423$ & $ 0.574$ & $ 0.341$ \\
+                \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus & $1.2\times 10^{5}$ & $ 0.936$ & $ 0.975$ & $ 0.586$ & $ 0.402$ & $ 0.598$ & $ 0.336$ \\
+                \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus & $1.7\times 10^{5}$ & $ 0.945$ & $ 0.971$ & $ 0.512$ & $ 0.432$ & $ 0.585$ & $ 0.250$ \\
+                African & Homo sapiens & $5.6\times 10^{4}$ & $ 0.911$ & $ 0.976$ & $ 0.579$ & $ 0.325$ & $ 0.721$ & $ 0.349$ \\
+                Admixed American & Homo sapiens & $4.5\times 10^{4}$ & $ 0.902$ & $ 0.978$ & $ 0.584$ & $ 0.299$ & $ 0.690$ & $ 0.345$ \\
+                East Asian & Homo sapiens & $ 4\times 10^{4}$ & $ 0.905$ & $ 0.978$ & $ 0.585$ & $ 0.325$ & $ 0.688$ & $ 0.249$ \\
+                European & Homo sapiens & $4.2\times 10^{4}$ & $ 0.906$ & $ 0.978$ & $ 0.584$ & $ 0.329$ & $ 0.688$ & $ 0.248$ \\
+                South Asian & Homo sapiens & $4.4\times 10^{4}$ & $ 0.908$ & $ 0.978$ & $ 0.584$ & $ 0.342$ & $ 0.691$ & $ 0.224$ \\
                 \bottomrule
@@
             \textit{Recall} for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is thus the proportion of beneficial back-mutations among all beneficial mutations.
-            Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
+            $\Ne$ is the estimated effective population size for each population.
         }

### 2023-10-11 manuscript/supp-mat-revision.tex
Supp. mat. revisions for diff
Manuscript revision, updated figures.

--- 2023-05-03 manuscript/supp-mat.tex
@@
 \usepackage{xcolor, colortbl}
+\definecolor{RED}{HTML}{EB6231}
+\definecolor{BLUE}{HTML}{5D80B4}
 \definecolor{LIGHTGREY}{gray}{0.9}
@@
 
+\usepackage{bbm}
 \usepackage[margin=50pt]{geometry}
@@
 \usepackage{graphicx}
+\usepackage{blkarray}
+\usepackage{pgf,tikz}
+\usetikzlibrary{shapes,arrows,backgrounds,fit,positioning,arrows,automata,calc}
+\tikzset{res/.style={ellipse,draw,minimum height=1.0cm,minimum width=0.8cm}}
+\tikzset{literal/.style={rectangle,draw,minimum height=0.5cm,minimum width=0.8cm,text width = 1.2 cm, align = center}}
+
 \pdfinclusioncopyfonts=1
+
+\renewcommand{\baselinestretch}{1.5}
+\renewcommand{\arraystretch}{0.6}
+\frenchspacing
 
@@
 \renewcommand{\thefigure}{S\arabic{figure}}
+\renewcommand{\theequation}{S.\arabic{equation}}
 
 \newcommand{\UniDimArray}[1]{\bm{#1}}
+\newcommand{\BiDimArray}[1]{\bm{#1}}
+
 \newcommand{\der}{\text{d}}
@@
 \newcommand{\thetaSyn}{\theta_{\text{S}}}
+\newcommand{\pvalue}{p\text{-value}}
+
+% Model
+\newcommand{\submatrix}{q}
+\newcommand{\Submatrix}{\BiDimArray{\submatrix}}
+\newcommand{\probmatrix}{P}
+\newcommand{\Probmatrix}{\BiDimArray{\probmatrix}}
+\newcommand{\fit}{F}
+\newcommand{\Fit}{\UniDimArray{\fit}}
+\newcommand{\indice}{l}
+\newcommand{\indiceexp}{^{(\indice)}}
+\newcommand{\ci}{{a}}
+\newcommand{\cj}{{b}}
+\newcommand{\itoj}{\ci \mapsto \cj}
+\newcommand{\nuc}{\mathcal{M}}
+\newcommand{\fiti}{\fit_{\ci}}
+\newcommand{\fitj}{\fit_{\cj}}
+\newcommand{\mutmatrix}{R}
+\newcommand{\Mutmatrix}{\BiDimArray{\mutmatrix}}
+\newcommand{\exchan}{\rho}
+\newcommand{\Exchan}{\UniDimArray{\exchan}}
+\newcommand{\mutequi}{\sigma}
+\newcommand{\Mutequi}{\UniDimArray{\mutequi}}
+\newcommand{\Tree}{\mathcal{T}}
+\newcommand{\branch}{\text{j}}
+\newcommand{\branchexp}{^{(\branch)}}
+\newcommand{\branchlength}{l}
+% Alignment
+\newcommand{\data}{D}
+\newcommand{\Data}{\BiDimArray{\data}}
+\newcommand{\site}{\text{i}}
+\newcommand{\Nsite}{\text{N}}
+\newcommand{\siteexp}{^{(\site)}}
+\newcommand{\Setsite}{\site \in \{1, \hdots, \Nsite\} }
+\newcommand{\branchsiteexp}{^{(\branch, \site)}}
+% Categories
+\newcommand{\cat}{\text{k}}
+\newcommand{\Ncat}{\text{K}}
+\newcommand{\catexp}{^{(\cat)}}
+\newcommand{\catInterval}{\{1, \hdots, \Ncat\}}
+\newcommand{\Setcat}{\cat \in \catInterval }
+\newcommand{\branchcatexp}{^{(\branch, \cat)}}
+\newcommand{\profile}{\phi}
+\newcommand{\Profile}{\UniDimArray{\profile}}
+\newcommand{\concentrationProfile}{\alpha}
+\newcommand{\centerProfile}{\UniDimArray{\gamma}}
+\newcommand{\catVar}{\kappa}
+\newcommand{\catsite}{\catVar\left(\site\right)}
+\newcommand{\catmultivar}{m}
+\newcommand{\catMultiVar}{\UniDimArray{\catmultivar}}
+\newcommand{\stickbreaking}{\theta}
+\newcommand{\StickBreaking}{\UniDimArray{\stickbreaking}}
+\newcommand{\stick}{\psi}
+\newcommand{\stickbreakinghyper}{\beta}
+\newcommand{\Multivariate}{\UniDimArray{Z}}
+\newcommand{\subhistory}{\mathcal{H}}
 
@@
 
-    \section{Beneficial mutations in the terminal lineages and populations}\label{sec:beneficial-mutations}
+    \section{Mutation-selection codon models}\label{sec:mutsel}
 
-    \subsection{Mutation-selection codon models}
-    \label{sec:site-specific-mutation-selection-codon-models}
-    In \textit{BayesCode} (\url{https://github.com/ThibaultLatrille/bayescode}), we ran the mutation-selection codon models \textit{mutselomega} for 2000 points of MCMC with the options:
+    \subsection{Prior distributions and parameters of the model}\label{subsec:priors}
+
+    The parameterization of the models is described as a Bayesian hierarchical model, including the prior distributions and the parameters of the model.
+    This hierarchical model is formally represented as directed acyclic graph of dependencies between variables, depicted below.
+    Nodes of the directed acyclic graph are the variables, and edges are the functions.
+    Hyper-parameters are depicted in {\color{RED}{red}} circles, random variables in {\color{BLUE}{blue}} circles, and transformed variables in black.
+            {\color{BLUE}{Blue}} dashed line denotes a drawing from a random distribution, and black solid lines denote a function.
+    All the nodes pointing toward a given node (upstream) are its dependencies which determines its distribution.
+    The other way around, following the arrows in the DAG (downstream), simple {prior} distributions are combined together to form more complex joint {prior} distribution which ultimately defines the {prior} distribution of the model.
+
+    \begin{center}
+        \begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=0.6cm and 1.2cm,semithick]
+            \tikzstyle{every state}=[]
+
+            \node[state] (P) {$\Probmatrix\branchsiteexp$};
+            \node[state] (Q) [below right=of P] {$\Submatrix\branchsiteexp$};
+            \node[state] (R) [below right=of Q] {$\Mutmatrix$};
+            \node[state] (BL) [right=of P] {$\branchlength\branchexp$};
+            \node[res] (BLH) [RED, right=of BL] {$ \lambda, \tau $};
+            \node[state] (f) [right=of Q] {$\Fit\siteexp $};
+            \node[state] (Ex) [BLUE, below right=of R] {$\Exchan$};
+            \node[state] (Equi) [BLUE, right=of R] {$\Mutequi$};
+            \node[state] (Base) [BLUE, above right=of f] {$\Profile\catexp$};
+            \node[state] (cat) [BLUE, right=of f] {$\catsite$};
+            \node[res] (ExH) [RED, right=of Ex] {$1,1,1,1,1,1$};
+            \node[res] (EquiH) [RED, right=of Equi] {$1,1,1,1$};
+            \node[state] (baseH) [RED, right=of Base] {$\concentrationProfile, \centerProfile $};
+            \node[state] (sb) [BLUE, right=of cat] {$\StickBreaking$};
+            \node[state] (sbH) [RED, right=of sb] {$\stickbreakinghyper$};
+
+            \path
+            (Q) edge [black] node [above right] {\ref{eq:Probmatrix}} (P)
+            (BL) edge [black] node [] {} (P)
+            (R) edge [black] node {} (Q)
+            (f) edge [black] node [above] {\ref{eq:subrates}} (Q)
+            (Ex) edge [black] node [] {} (R)
+            (Equi) edge [black] node [below] {\ref{eq:gtr-mutrates}} (R)
+            (Base) edge [black] node {} (f)
+            (cat) edge [black] node [above] {\ref{eq:sitefitness}} (f)
+            (BLH) edge [dashed, BLUE] node [above] {\ref{eq:branchlength}} (BL)
+            (ExH) edge [dashed, BLUE] node [above] {\ref{eq:DistribExchan}} (Ex)
+            (EquiH) edge [dashed, BLUE] node [above] {\ref{eq:DistribMutequi}} (Equi)
+            (baseH) edge [dashed, BLUE] node [above] {\ref{eq:DistribBase}} (Base)
+            (sb) edge [dashed, BLUE] node [above] {\ref{eq:DistribMultinomial}} (cat)
+            (sbH) edge [dashed, BLUE] node [above] {\ref{eq:DistribStickBreaking},\ref{eq:Beta}} (sb);
+        \end{tikzpicture}
+    \end{center}
+
+    \subsection{Nucleotide mutation rates}
+    The generalized time-reversible (GTR) nucleotide mutation rate matrix $\Mutmatrix$ is a function of the nucleotide frequencies $\Mutequi$ and the symmetric exchangeability rates $\Exchan$~\cite{tavare_probabilistic_1986}.
+    $\Mutequi = (\mutequi_A , \mutequi_C , \mutequi_G , \mutequi_T)$ is the equilibrium base frequency vector, giving the frequency at which each base occurs at each site.
+    $\Exchan = \left( \exchan_{AC}, \exchan_{AG}, \exchan_{AT}, \exchan_{CG}, \exchan_{CT}, \exchan_{GT}\right)$ is the vector of exchangeabilities between nucleotides.
+    Altogether, the rate matrix is:
+    \begin{equation}
+        \label{eq:gtr-mutrates}
+        \Mutmatrix =
+        \begin{blockarray}{ccccc}
+            & A & C & G & T \\
+            \begin{block}{c(cccc)}
+                A & - & {\exchan_{AC}\mutequi_C} & {\exchan_{AG}\mutequi_G} & {\exchan_{AT}\mutequi_T} \\
+                C & {\exchan_{AC}\mutequi_A} &                        - & {\exchan_{CG}\mutequi_G} & {\exchan_{CT}\mutequi_T} \\
+                G & {\exchan_{AG}\mutequi_A} & {\exchan_{CG}\mutequi_C} &                        - & {\exchan_{GT}\mutequi_T} \\
+                T & {\exchan_{AT}\mutequi_A} & {\exchan_{CT}\mutequi_C} & {\exchan_{GT}\mutequi_G} & - \\
+            \end{block}
+        \end{blockarray}
+    \end{equation}
+    By definition, the sum of the entries in each row of the nucleotide rate matrix $\Mutmatrix$ is equal to $0$, giving the diagonal entries:
+    \begin{equation}
+        \mutmatrix_{a,a} = - \sum\limits_{ b \neq a, b \in \{A, C, G, T\} } \mutmatrix_{a,b}
+    \end{equation}
+    The {prior} on the exchangeabilities $\Exchan$ is a uniform Dirichlet distribution of dimension $6$:
+    \begin{equation}
+        \label{eq:DistribExchan}
+        \Exchan \sim \text{Dir}\left( 1,1,1,1,1,1 \right).
+    \end{equation}
+    The {prior} on the equilibrium base frequencies $\Mutequi$ is a uniform Dirichlet distribution of dimension $4$:
+    \begin{equation}
+        \label{eq:DistribMutequi}
+        \Mutequi \sim \text{Dir}\left( 1,1,1,1 \right)
+    \end{equation}
+    The general time-reversible nucleotide matrix is normalized with a total flow of $1$:
+    \begin{equation}
+        \sum\limits_{a \in \{A, C, G, T\}} - \mutequi_a \mutmatrix_{a,a} = 1,
+    \end{equation}
+    such that we expect $1$ {substitution} per unit of branch length.
+
+    \subsection{Site-specific amino-acid fitness profiles}
+    \label{sec:profiles}
+    Site-specific amino-acid fitness profiles are assumed i.i.d. from a mixture model, itself endowed with a truncated Dirichlet process prior.
+    Specifically, the mixture has $\Ncat$ components ($\Ncat = 30$ by default).
+    The prior on component weights~($\StickBreaking$) is modeled using a stick-breaking process, truncated at $\Ncat$ and of parameter $\stickbreakinghyper=1$:
+    \begin{align}
+        \label{eq:DistribStickBreaking}
+        \begin{split}
+            & \StickBreaking \sim \text{StickBreaking}\left( \Ncat, \stickbreakinghyper \right)\\
+            \iff & \stickbreaking_{\cat} = \stick_{\cat}\cdot \prod _{{\indice=1}}^{{\cat-1}}\left(1-\stick_{\indice}\right),\ \Setcat,
+        \end{split}
+    \end{align}
+    where $\stick_{\cat}$ are i.i.d. from a beta distribution
+    \begin{equation}
+        \label{eq:Beta}
+        \stick_{\cat} \sim \text{Beta}\left( 1, \stickbreakinghyper \right),\ \Setcat.
+    \end{equation}
+    Of note, the weights decrease geometrically in expectation, at rate $\stickbreakinghyper$, such that lower values of $\stickbreakinghyper$ induce more heterogeneous distributions of weights.
+
+    Each component of the mixture defines a 20-dimensional fitness profile $\Profile\catexp$ (summing to $1$), for $ \Setcat$.
+    These fitness profiles are i.i.d. from a Dirichlet of center $\centerProfile=1$ and concentration $\concentrationProfile=1$:
+    \begin{equation}
+        \label{eq:DistribBase}
+        \Profile\catexp \sim \text{Dir}\left( \centerProfile,\ \concentrationProfile \right),\ \Setcat.
+    \end{equation}
+
+    Site allocations to the mixture components $\catsite \in \catInterval $, for $\Setsite$ running over the $\Nsite$ sites of the alignment, are i.i.d. multinomial of parameter $\StickBreaking$:
+    \begin{align}
+        \label{eq:DistribMultinomial}
+        \catMultiVar \sim \text{Multinomial}\left( \StickBreaking \right), \\
+        \text{ where } \catmultivar_{\cat} = \sum_{\Setsite} \mathbbm{1}_{\catsite = \cat}
+    \end{align}
+
+    For a given parameter configuration for the mixture, the scaled fitness $\Fit\siteexp$ at site $\site$, are obtained by taking the logarithm of fitness assigned to this site:
+    \begin{equation}
+        \label{eq:sitefitness}
+        \Fit\siteexp = \ln \left( \Profile^{\left( \catsite \right)} \right),\ \Setsite.
+    \end{equation}
+
+    \subsection{Branch length}
+    The topology of the rooted phylogenetic tree is supposed to be known and is not estimated by the model.
+    The branch lengths $\branchlength\branchexp$ are defined as the expected number of {neutral} substitutions per {DNA} site along a branch, each from a Gamma distribution of mean $\lambda=0.1$ and scale $\tau=1$:
+    \begin{equation}
+        \label{eq:branchlength}
+        \branchlength\branchexp \sim \text{Gamma}\left( \lambda, \tau \right).
+    \end{equation}
+
+    \subsection{Codon substitution rates}
+
+    The mutation rate between codons $\ci$ and $\cj$, denoted $\mu_{\itoj}$ depends on the underlying nucleotide change between the codons.
+    First, if codons $\ci$ and $\cj$ are not nearest-neighbours, $\mu_{\itoj}$ is equal to $0$.
+    Second, if codons $\ci$ and $\cj$ are only one mutation away, $\mu_{\itoj}$ is given by the underlying nucleotide relative rate~(${\mutmatrix_{\itoj}}$).
+
+    For a given site $\site$, the {codon} {substitution} rate matrix $\Submatrix\siteexp$ is given by:
+    \begin{equation}
+        \label{eq:subrates}
+        \begin{dcases}
+            \submatrix\siteexp_{\itoj} = 0\text{ if codons $\ci$ and $\cj$ are not nearest-neighbors,} \\
+            \submatrix\siteexp_{\itoj} = \mu_{\itoj}\text{ if codons $\ci$ and $\cj$ are {synonymous},} \\
+            \submatrix\siteexp_{\itoj} = \mu_{\itoj} \dfrac{ \fitj\siteexp - \fiti\siteexp}{{1 - \e^{\fiti\siteexp - \fitj\siteexp} }} \text{ if $\ci$ and $\cj$ are non-synonymous,}\\
+            \submatrix\siteexp_{\ci, \ci} = - \sum\limits_{ \cj \neq \ci, \cj=1}^{61} \submatrix\siteexp_{\itoj}.
+        \end{dcases}
+    \end{equation}
+    Together, the probability of transition between codons for a given branch $\branch$ and site $\site$ is:
+    \begin{equation}
+        \label{eq:Probmatrix}
+        \Probmatrix\branchsiteexp = \e^{\branchlength\branchexp \Submatrix\siteexp},
+    \end{equation}
+    which are the matrices necessary to compute the {likelihood} of the data ($\data$) given the parameters of the model using the pruning algorithm.
+
+    \subsection{Bayesian implementation}
+    \label{sec:Bayesian}
+    Bayesian inference was conducted using Markov Chain Monte Carlo (MCMC).
+    Most phylogenetic {MCMC} samplers target the distribution over the model parameters given the sequence alignment, which means that they have to repeatedly invoke the pruning algorithm to recalculate the {likelihood} which is most often the limiting step of the {MCMC}.
+    An alternative, which is used here, is to do the {MCMC} conditionally on the detailed {substitution} history $\subhistory$, thus doing the {MCMC} over the augmented configuration~($\subhistory$, $\data$), under the target distribution obtained by combining the mapping-based {likelihood} with the {prior} over model parameters.
+    The key idea that makes this strategy efficient is that the mapping-based {likelihood} depends on compact summary statistics of $\subhistory$, leading to very fast evaluation of the {likelihood}.
+    On the other hand, this requires to implement more complex {MCMC} procedures that have to alternate between:
+    \begin{enumerate}
+        \item sampling $\subhistory$ conditionally on the data and the current parameter configuration.
+        \item re-sampling the parameters conditionally on $\subhistory$.
+    \end{enumerate}
+
+    To implement the mapping-based {MCMC} sampling strategy, we first sample the detailed {substitution} history $\subhistory$ for all sites along the tree.
+    Several methods exist for doing this~\cite{nielsen_mapping_2002,rodrigue_uniformization_2008}, which are used here in combination (first trying the accept-reject method of Nielsen, then switching to the uniformization approach of Rodrigue \textit{et al} if the first round has failed).
+
+    Then, we write down the probability of $\subhistory$ given the parameters, and finally, we collect all factors that depend on some parameter of interest and make some simplifications.
+    This ultimately leads to relatively compact sufficient statistics allowing for fast numerical evaluation of the likelihood~\cite{irvahn_phylogenetic_2014,davydov_state_2017}.
+
+    \subsection{BayesCode software}\label{subsec:bayescode}
+    In \textit{BayesCode} (\href{https://github.com/ThibaultLatrille/BayesCode}{github.com/ThibaultLatrille/BayesCode}, v1.3.1), we ran the mutation-selection codon models \textit{mutselomega} for 2000 points of MCMC with the options:
     \begin{scriptsize}
@@
 
+    \newpage
+
+    \section{Beneficial mutations in the terminal lineages and populations}\label{sec:beneficial-mutations}
+
     \subsection{Summary tables}\label{subsec:summary-table-mutsel}
 
-    \subsubsection{$\dnds$ for deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial back-mutations ($\SphyBen$)}
+    \subsubsection{Probability of mutations and substitutions to be $\SphyDel$, $\SphyNeu$ or $\SphyBen$}
     \begin{center}
-        \captionof{table}{$\dnds$ for deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial back-mutations ($\SphyBen$).}
+        \captionof{table}{Probability of mutations and substitutions to be $\SphyDel$, $\SphyNeu$ or $\SphyBen$.}
         \scriptsize
@@
             \toprule
-            Population &             Species & Watterson's $\thetaSyn$  & $\proba_{div}[ \SphyBen ]$ & $\dnds $ & $\dn ( \SphyDel ) / \ds$ & $\dn ( \SphyNeu ) / \ds$ & $\dn ( \SphyBen ) / \ds$ \\
+            Population &             Species & $\proba[ \SphyDel ]$ & $\proba[ \SphyNeu ]$ & $\proba[ \SphyBen ]$ & $\proba_{div}[ \SphyDel ]$ & $\proba_{div}[ \SphyNeu ]$ & $\proba_{div}[ \SphyBen ]$ \\
             \midrule
@@
             \endlastfoot
-            \rowcolor{LIGHTGREY} Equus c.
-&      Equus caballus &               $ 0.002$ &                    $ 0.118$ &  $ 0.147$ &            $ 0.075$ &                $ 0.823$ &           $ 1.203$ \\
-            Iran &          Bos taurus &               $ 0.002$ &                    $ 0.123$ &  $ 0.131$ &            $ 0.074$ &                $ 0.627$ &           $ 1.206$ \\
-            Uganda &          Bos taurus &               $ 0.005$ &                    $ 0.125$ &  $ 0.134$ &            $ 0.075$ &                $ 0.637$ &           $ 1.252$ \\
-            \rowcolor{LIGHTGREY} Australia &        Capra hircus &               $ 0.003$ &                    $ 0.121$ &  $ 0.125$ &            $ 0.068$ &                $ 0.629$ &           $ 1.099$ \\
-            \rowcolor{LIGHTGREY} France &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.126$ &            $ 0.068$ &                $ 0.633$ &           $ 1.102$ \\
-            \rowcolor{LIGHTGREY} Iran (C.
-aegagrus) &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.125$ &            $ 0.068$ &                $ 0.630$ &           $ 1.100$ \\
-            \rowcolor{LIGHTGREY} Iran &        Capra hircus &               $ 0.004$ &                    $ 0.121$ &  $ 0.125$ &            $ 0.067$ &                $ 0.630$ &           $ 1.108$ \\
-            \rowcolor{LIGHTGREY} Italy &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.126$ &            $ 0.068$ &                $ 0.634$ &           $ 1.102$ \\
-            \rowcolor{LIGHTGREY} Morocco &        Capra hircus &               $ 0.004$ &                    $ 0.122$ &  $ 0.125$ &            $ 0.067$ &                $ 0.631$ &           $ 1.112$ \\
-            Iran &          Ovis aries &               $ 0.007$ &                    $ 0.109$ &  $ 0.146$ &            $ 0.091$ &                $ 0.616$ &           $ 1.148$ \\
-            Iran (O. orientalis) &          Ovis aries &               $ 0.009$ &                    $ 0.108$ &  $ 0.148$ &            $ 0.093$ &                $ 0.617$ &           $ 1.145$ \\
-            Iran (O. vignei) &          Ovis aries &               $ 0.007$ &                    $ 0.109$ &  $ 0.146$ &            $ 0.091$ &                $ 0.617$ &           $ 1.134$ \\
-            Various &          Ovis aries &               $ 0.008$ &                    $ 0.107$ &  $ 0.148$ &            $ 0.093$ &                $ 0.617$ &           $ 1.134$ \\
-            Morocco &          Ovis aries &               $ 0.008$ &                    $ 0.108$ &  $ 0.148$ &            $ 0.093$ &                $ 0.619$ &           $ 1.149$ \\
-            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus &               $ 0.004$ &                    $ 0.122$ &  $ 0.133$ &            $ 0.071$ &                $ 0.696$ &           $ 1.397$ \\
-            \rowcolor{LIGHTGREY} Central Afr.
-Rep.
-& Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.124$ &  $ 0.134$ &            $ 0.071$ &                $ 0.701$ &           $ 1.431$ \\
-            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.124$ &  $ 0.134$ &            $ 0.071$ &                $ 0.699$ &           $ 1.422$ \\
-            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.123$ &  $ 0.134$ &            $ 0.071$ &                $ 0.703$ &           $ 1.411$ \\
-            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.123$ &  $ 0.134$ &            $ 0.071$ &                $ 0.699$ &           $ 1.419$ \\
-            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus &               $ 0.003$ &                    $ 0.123$ &  $ 0.133$ &            $ 0.071$ &                $ 0.699$ &           $ 1.407$ \\
-            \rowcolor{LIGHTGREY} South Africa  & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.125$ &  $ 0.134$ &            $ 0.070$ &                $ 0.704$ &           $ 1.447$ \\
-            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &                    $ 0.123$ &  $ 0.133$ &            $ 0.070$ &                $ 0.699$ &           $ 1.413$ \\
-            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.123$ &  $ 0.134$ &            $ 0.071$ &                $ 0.699$ &           $ 1.410$ \\
-            African &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &            $ 0.118$ &                $ 0.865$ &           $ 1.609$ \\
-            Admixed American &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &            $ 0.118$ &                $ 0.865$ &           $ 1.607$ \\
-            East Asian &        Homo sapiens &               $ 0.002$ &                    $ 0.098$ &  $ 0.192$ &            $ 0.118$ &                $ 0.869$ &           $ 1.607$ \\
-            European &        Homo sapiens &               $ 0.002$ &                    $ 0.098$ &  $ 0.192$ &            $ 0.118$ &                $ 0.865$ &           $ 1.598$ \\
-            South Asian &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &            $ 0.118$ &                $ 0.867$ &           $ 1.610$ \\
+            \rowcolor{LIGHTGREY} Equus c. & Equus caballus & $ 0.923$ & $ 0.065$ & $ 0.012$ & $ 0.462$ & $ 0.419$ & $ 0.118$ \\
+            Iran & Bos taurus & $ 0.924$ & $ 0.065$ & $ 0.011$ & $ 0.515$ & $ 0.362$ & $ 0.123$ \\
+            Uganda & Bos taurus & $ 0.924$ & $ 0.065$ & $ 0.011$ & $ 0.514$ & $ 0.361$ & $ 0.125$ \\
+            \rowcolor{LIGHTGREY} Australia & Capra hircus & $ 0.923$ & $ 0.066$ & $ 0.011$ & $ 0.494$ & $ 0.386$ & $ 0.121$ \\
+            \rowcolor{LIGHTGREY} France & Capra hircus & $ 0.923$ & $ 0.066$ & $ 0.011$ & $ 0.494$ & $ 0.386$ & $ 0.120$ \\
+            \rowcolor{LIGHTGREY} Iran (C. aegagrus) & Capra hircus & $ 0.923$ & $ 0.066$ & $ 0.011$ & $ 0.493$ & $ 0.386$ & $ 0.120$ \\
+            \rowcolor{LIGHTGREY} Iran & Capra hircus & $ 0.923$ & $ 0.066$ & $ 0.011$ & $ 0.492$ & $ 0.387$ & $ 0.121$ \\
+            \rowcolor{LIGHTGREY} Italy & Capra hircus & $ 0.923$ & $ 0.066$ & $ 0.011$ & $ 0.494$ & $ 0.386$ & $ 0.120$ \\
+            \rowcolor{LIGHTGREY} Morocco & Capra hircus & $ 0.923$ & $ 0.066$ & $ 0.011$ & $ 0.491$ & $ 0.387$ & $ 0.122$ \\
+            Iran & Ovis aries & $ 0.922$ & $ 0.067$ & $ 0.012$ & $ 0.568$ & $ 0.323$ & $ 0.109$ \\
+            Iran (O. orientalis) & Ovis aries & $ 0.922$ & $ 0.067$ & $ 0.011$ & $ 0.573$ & $ 0.320$ & $ 0.108$ \\
+            Iran (O. vignei) & Ovis aries & $ 0.922$ & $ 0.067$ & $ 0.012$ & $ 0.567$ & $ 0.325$ & $ 0.109$ \\
+            Various & Ovis aries & $ 0.922$ & $ 0.067$ & $ 0.011$ & $ 0.572$ & $ 0.321$ & $ 0.107$ \\
+            Morocco & Ovis aries & $ 0.922$ & $ 0.067$ & $ 0.012$ & $ 0.570$ & $ 0.321$ & $ 0.108$ \\
+            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus & $ 0.926$ & $ 0.065$ & $ 0.009$ & $ 0.485$ & $ 0.393$ & $ 0.122$ \\
+            \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus & $ 0.926$ & $ 0.065$ & $ 0.009$ & $ 0.485$ & $ 0.391$ & $ 0.124$ \\
+            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus & $ 0.926$ & $ 0.065$ & $ 0.009$ & $ 0.484$ & $ 0.393$ & $ 0.124$ \\
+            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus & $ 0.926$ & $ 0.065$ & $ 0.009$ & $ 0.483$ & $ 0.394$ & $ 0.123$ \\
+            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus & $ 0.926$ & $ 0.065$ & $ 0.009$ & $ 0.485$ & $ 0.392$ & $ 0.123$ \\
+            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus & $ 0.926$ & $ 0.065$ & $ 0.009$ & $ 0.484$ & $ 0.393$ & $ 0.123$ \\
+            \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus & $ 0.926$ & $ 0.065$ & $ 0.009$ & $ 0.480$ & $ 0.394$ & $ 0.125$ \\
+            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus & $ 0.926$ & $ 0.065$ & $ 0.009$ & $ 0.483$ & $ 0.394$ & $ 0.123$ \\
+            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus & $ 0.926$ & $ 0.065$ & $ 0.009$ & $ 0.485$ & $ 0.393$ & $ 0.123$ \\
+            African & Homo sapiens & $ 0.925$ & $ 0.065$ & $ 0.010$ & $ 0.561$ & $ 0.341$ & $ 0.099$ \\
+            Admixed American & Homo sapiens & $ 0.925$ & $ 0.065$ & $ 0.010$ & $ 0.561$ & $ 0.340$ & $ 0.099$ \\
+            East Asian & Homo sapiens & $ 0.925$ & $ 0.065$ & $ 0.010$ & $ 0.560$ & $ 0.341$ & $ 0.098$ \\
+            European & Homo sapiens & $ 0.925$ & $ 0.065$ & $ 0.010$ & $ 0.562$ & $ 0.340$ & $ 0.098$ \\
+            South Asian & Homo sapiens & $ 0.925$ & $ 0.065$ & $ 0.010$ & $ 0.561$ & $ 0.341$ & $ 0.099$ \\
         \end{longtable*}
@@
     \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
+        \item $\proba [ \SphyDel ]$ (eq.~5) is the probability for a new mutation to be a deleterious.
+        These mutations have a selection coefficient predicted at the phylogenetic-scale lower than -1, thus toward a less fit amino-acid.
+        \item $\proba [ \SphyNeu ]$ (eq.~5) is the probability for a new mutation to be a nearly-neutral.
+        These mutations have a selection coefficient predicted at the phylogenetic-scale between -1 and 1.
+        \item $\proba [ \SphyBen ]$ (eq.~5) is the probability for a new mutation to be a beneficial back-mutation.
+        These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1, thus toward a more fit amino-acid.
+        \item $\proba_{div}[\SphyDel]$ is the proportion of substitutions in the terminal branch that are $\SphyDel$.
+        \item $\proba_{div}[\SphyNeu]$ is the proportion of substitutions in the terminal branch that are $\SphyNeu$.
         \item $\proba_{div}[\SphyBen]$ is the proportion of substitutions in the terminal branch that are $\SphyBen$.
+    \end{itemize}
+    \newpage
+
+    \subsubsection{$\dnds$ for $\SphyDel$, $\SphyNeu$ or $\SphyBen$}
+    \begin{center}
+        \captionof{table}{$\dnds$ for $\SphyDel$, $\SphyNeu$ or $\SphyBen$.}
+        \scriptsize
+        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
+            \toprule
+            Population &             Species & $\dnds $ & $\dn ( \SphyDel ) / \ds$ & $\dn ( \SphyNeu ) / \ds$ & $\dn ( \SphyBen ) / \ds$ \\
+            \midrule
+            \endhead
+            \midrule
+            \multicolumn{8}{r}{{Continued on next page}} \\
+            \midrule
+            \endfoot
+
+            \bottomrule
+            \endlastfoot
+            \rowcolor{LIGHTGREY} Equus c. & Equus caballus & $ 0.129$ & $ 0.065$ & $ 0.832$ & $ 1.267$ \\
+            Iran & Bos taurus & $ 0.114$ & $ 0.063$ & $ 0.629$ & $ 1.280$ \\
+            Uganda & Bos taurus & $ 0.116$ & $ 0.064$ & $ 0.638$ & $ 1.328$ \\
+            \rowcolor{LIGHTGREY} Australia & Capra hircus & $ 0.108$ & $ 0.058$ & $ 0.631$ & $ 1.169$ \\
+            \rowcolor{LIGHTGREY} France & Capra hircus & $ 0.109$ & $ 0.058$ & $ 0.635$ & $ 1.172$ \\
+            \rowcolor{LIGHTGREY} Iran (C. aegagrus) & Capra hircus & $ 0.108$ & $ 0.058$ & $ 0.632$ & $ 1.170$ \\
+            \rowcolor{LIGHTGREY} Iran & Capra hircus & $ 0.108$ & $ 0.058$ & $ 0.632$ & $ 1.178$ \\
+            \rowcolor{LIGHTGREY} Italy & Capra hircus & $ 0.109$ & $ 0.058$ & $ 0.636$ & $ 1.171$ \\
+            \rowcolor{LIGHTGREY} Morocco & Capra hircus & $ 0.108$ & $ 0.058$ & $ 0.633$ & $ 1.183$ \\
+            Iran & Ovis aries & $ 0.128$ & $ 0.079$ & $ 0.619$ & $ 1.215$ \\
+            Iran (O. orientalis) & Ovis aries & $ 0.129$ & $ 0.080$ & $ 0.619$ & $ 1.212$ \\
+            Iran (O. vignei) & Ovis aries & $ 0.127$ & $ 0.078$ & $ 0.619$ & $ 1.201$ \\
+            Various & Ovis aries & $ 0.129$ & $ 0.080$ & $ 0.620$ & $ 1.201$ \\
+            Morocco & Ovis aries & $ 0.129$ & $ 0.080$ & $ 0.621$ & $ 1.217$ \\
+            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus & $ 0.118$ & $ 0.062$ & $ 0.713$ & $ 1.521$ \\
+            \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus & $ 0.119$ & $ 0.062$ & $ 0.717$ & $ 1.559$ \\
+            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus & $ 0.118$ & $ 0.062$ & $ 0.716$ & $ 1.549$ \\
+            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus & $ 0.119$ & $ 0.062$ & $ 0.719$ & $ 1.537$ \\
+            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus & $ 0.119$ & $ 0.062$ & $ 0.716$ & $ 1.546$ \\
+            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus & $ 0.118$ & $ 0.062$ & $ 0.715$ & $ 1.532$ \\
+            \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus & $ 0.119$ & $ 0.062$ & $ 0.720$ & $ 1.577$ \\
+            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus & $ 0.118$ & $ 0.062$ & $ 0.715$ & $ 1.539$ \\
+            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus & $ 0.118$ & $ 0.062$ & $ 0.716$ & $ 1.537$ \\
+            African & Homo sapiens & $ 0.170$ & $ 0.103$ & $ 0.885$ & $ 1.744$ \\
+            Admixed American & Homo sapiens & $ 0.170$ & $ 0.103$ & $ 0.884$ & $ 1.742$ \\
+            East Asian & Homo sapiens & $ 0.170$ & $ 0.103$ & $ 0.888$ & $ 1.742$ \\
+            European & Homo sapiens & $ 0.170$ & $ 0.103$ & $ 0.884$ & $ 1.733$ \\
+            South Asian & Homo sapiens & $ 0.170$ & $ 0.103$ & $ 0.886$ & $ 1.745$ \\
+        \end{longtable*}
+    \end{center}
+    \begin{itemize}
+        \item $\dnds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions estimated for all the non-synonymous substitutions in the terminal branch.
         \item $\dn(\SphyDel) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are $\SphyDel$.
@@
             \toprule
-            Population & Species & Watterson's $\thetaSyn$ & $\proba_{div}[\Sphy > 1]$ & $\dnds $ & $\dn(\Sphy < 1) / \ds$ & $\delta(\dnds )$ \\
+            Population & Species & $\dnds $ & $\dn(\Sphy < 1) / \ds$ & $\delta(\dnds )$ \\
             \midrule
@@
             \endlastfoot
-            \rowcolor{LIGHTGREY} Equus c. &      Equus caballus &               $ 0.002$ &                    $ 0.118$ &  $ 0.147$ &           $ 0.131$ &     $  10.5$ \\
-            Iran &          Bos taurus &               $ 0.002$ &                    $ 0.123$ &  $ 0.131$ &           $ 0.117$ &     $  11.1$ \\
-            Uganda &          Bos taurus &               $ 0.005$ &                    $ 0.125$ &  $ 0.134$ &           $ 0.118$ &     $  11.3$ \\
-            \rowcolor{LIGHTGREY} Australia &        Capra hircus &               $ 0.003$ &                    $ 0.121$ &  $ 0.125$ &           $ 0.111$ &     $  10.8$ \\
-            \rowcolor{LIGHTGREY} France &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.126$ &           $ 0.112$ &     $  10.8$ \\
-            \rowcolor{LIGHTGREY} Iran (C. aegagrus) &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.125$ &           $ 0.111$ &     $  10.8$ \\
-            \rowcolor{LIGHTGREY} Iran &        Capra hircus &               $ 0.004$ &                    $ 0.121$ &  $ 0.125$ &           $ 0.111$ &     $  10.9$ \\
-            \rowcolor{LIGHTGREY} Italy &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.126$ &           $ 0.112$ &     $  10.8$ \\
-            \rowcolor{LIGHTGREY} Morocco &        Capra hircus &               $ 0.004$ &                    $ 0.122$ &  $ 0.125$ &           $ 0.111$ &     $  11.0$ \\
-            Iran &          Ovis aries &               $ 0.007$ &                    $ 0.109$ &  $ 0.146$ &           $ 0.132$ &     $ 9.671$ \\
-            Iran (O. orientalis) &          Ovis aries &               $ 0.009$ &                    $ 0.108$ &  $ 0.148$ &           $ 0.134$ &     $ 9.516$ \\
-            Iran (O. vignei) &          Ovis aries &               $ 0.007$ &                    $ 0.109$ &  $ 0.146$ &           $ 0.132$ &     $ 9.598$ \\
-            Various &          Ovis aries &               $ 0.008$ &                    $ 0.107$ &  $ 0.148$ &           $ 0.134$ &     $ 9.439$ \\
-            Morocco &          Ovis aries &               $ 0.008$ &                    $ 0.108$ &  $ 0.148$ &           $ 0.134$ &     $ 9.582$ \\
-            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus &               $ 0.004$ &                    $ 0.122$ &  $ 0.133$ &           $ 0.118$ &     $  11.2$ \\
-            \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.124$ &  $ 0.134$ &           $ 0.119$ &     $  11.3$ \\
-            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.124$ &  $ 0.134$ &           $ 0.118$ &     $  11.3$ \\
-            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.123$ &  $ 0.134$ &           $ 0.119$ &     $  11.2$ \\
-            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.123$ &  $ 0.134$ &           $ 0.119$ &     $  11.3$ \\
-            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus &               $ 0.003$ &                    $ 0.123$ &  $ 0.133$ &           $ 0.118$ &     $  11.3$ \\
-            \rowcolor{LIGHTGREY} South Africa  & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.125$ &  $ 0.134$ &           $ 0.118$ &     $  11.5$ \\
-            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &                    $ 0.123$ &  $ 0.133$ &           $ 0.118$ &     $  11.3$ \\
-            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.123$ &  $ 0.134$ &           $ 0.119$ &     $  11.2$ \\
-            African &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &           $ 0.175$ &     $ 8.799$ \\
-            Admixed American &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &           $ 0.175$ &     $ 8.780$ \\
-            East Asian &        Homo sapiens &               $ 0.002$ &                    $ 0.098$ &  $ 0.192$ &           $ 0.175$ &     $ 8.768$ \\
-            European &        Homo sapiens &               $ 0.002$ &                    $ 0.098$ &  $ 0.192$ &           $ 0.175$ &     $ 8.728$ \\
-            South Asian &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &           $ 0.175$ &     $ 8.788$ \\
+            \rowcolor{LIGHTGREY} Equus c. & Equus caballus & $ 0.129$ & $ 0.115$ & $  10.7$ \\
+            Iran & Bos taurus & $ 0.114$ & $ 0.101$ & $  11.3$ \\
+            Uganda & Bos taurus & $ 0.116$ & $ 0.102$ & $  11.5$ \\
+            \rowcolor{LIGHTGREY} Australia & Capra hircus & $ 0.108$ & $ 0.096$ & $  11.1$ \\
+            \rowcolor{LIGHTGREY} France & Capra hircus & $ 0.109$ & $ 0.097$ & $  11.0$ \\
+            \rowcolor{LIGHTGREY} Iran (C. aegagrus) & Capra hircus & $ 0.108$ & $ 0.096$ & $  11.1$ \\
+            \rowcolor{LIGHTGREY} Iran & Capra hircus & $ 0.108$ & $ 0.096$ & $  11.2$ \\
+            \rowcolor{LIGHTGREY} Italy & Capra hircus & $ 0.109$ & $ 0.097$ & $  11.0$ \\
+            \rowcolor{LIGHTGREY} Morocco & Capra hircus & $ 0.108$ & $ 0.096$ & $  11.2$ \\
+            Iran & Ovis aries & $ 0.128$ & $ 0.115$ & $ 9.894$ \\
+            Iran (O. orientalis) & Ovis aries & $ 0.129$ & $ 0.117$ & $ 9.740$ \\
+            Iran (O. vignei) & Ovis aries & $ 0.127$ & $ 0.115$ & $ 9.822$ \\
+            Various & Ovis aries & $ 0.129$ & $ 0.116$ & $ 9.663$ \\
+            Morocco & Ovis aries & $ 0.129$ & $ 0.116$ & $ 9.805$ \\
+            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus & $ 0.118$ & $ 0.104$ & $  11.4$ \\
+            \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus & $ 0.119$ & $ 0.105$ & $  11.5$ \\
+            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus & $ 0.118$ & $ 0.105$ & $  11.5$ \\
+            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus & $ 0.119$ & $ 0.105$ & $  11.4$ \\
+            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus & $ 0.119$ & $ 0.105$ & $  11.5$ \\
+            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus & $ 0.118$ & $ 0.105$ & $  11.4$ \\
+            \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus & $ 0.119$ & $ 0.105$ & $  11.7$ \\
+            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus & $ 0.118$ & $ 0.104$ & $  11.5$ \\
+            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus & $ 0.118$ & $ 0.105$ & $  11.4$ \\
+            African & Homo sapiens & $ 0.170$ & $ 0.154$ & $ 8.996$ \\
+            Admixed American & Homo sapiens & $ 0.170$ & $ 0.155$ & $ 8.978$ \\
+            East Asian & Homo sapiens & $ 0.170$ & $ 0.155$ & $ 8.966$ \\
+            European & Homo sapiens & $ 0.170$ & $ 0.155$ & $ 8.926$ \\
+            South Asian & Homo sapiens & $ 0.170$ & $ 0.155$ & $ 8.986$ \\
         \end{longtable*}
@@
     \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item $\proba_{div}[\SphyBen]$ is the proportion of substitutions in the terminal branch that are $\SphyBen$.
         \item $\dnds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions estimated for all the non-synonymous substitutions in the terminal branch.
@@
     We estimated that between 9 and 11\% of $\dnds$ is over-estimated, corresponding to beneficial back-mutation inflating the $\dnds$ statistic.
-
-    \newpage
-
-    \subsubsection{Probabilities of beneficial back-mutations}
-    \begin{center}
-        \captionof{table}{Probability of beneficial back-mutations among all beneficial ones.}
-        \scriptsize
-        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
-            \toprule
-            Population & Species & Watterson's $\thetaSyn$ & $\proba[\SphyBen]$ & $\proba [ \SpopBen ]$ & $\frac{\proba[\SphyBen]}{\proba[ \SpopBen ]}$ & $\proba [ \SpopBen \given \SphyBen]$ & $\proba[\SphyBen\given \SpopBen ]$ \\
-            \midrule
-            \endhead
-            \midrule
-            \multicolumn{8}{r}{{Continued on next page}} \\
-            \midrule
-            \endfoot
-
-            \bottomrule
-            \endlastfoot
-            \rowcolor{LIGHTGREY} Equus c.
-&      Equus caballus &               $ 0.002$ &              $ 0.014$ &              $ 0.010$ &                                          $ 1.395$ &                         $ 0.580$ &                      $ 0.809$ \\
-            Iran &          Bos taurus &               $ 0.002$ &              $ 0.013$ &              $ 0.041$ &                                          $ 0.323$ &                         $ 0.857$ &                      $ 0.277$ \\
-            Uganda &          Bos taurus &               $ 0.005$ &              $ 0.013$ &              $ 0.013$ &                                          $ 0.991$ &                         $ 0.488$ &                      $ 0.483$ \\
-            \rowcolor{LIGHTGREY} Australia &        Capra hircus &               $ 0.003$ &              $ 0.014$ &              $ 0.026$ &                                          $ 0.532$ &                         $ 0.368$ &                      $ 0.196$ \\
-            \rowcolor{LIGHTGREY} France &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.572$ &                         $ 0.368$ &                      $ 0.211$ \\
-            \rowcolor{LIGHTGREY} Iran (C.
-aegagrus) &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.026$ &                                          $ 0.516$ &                         $ 0.221$ &                      $ 0.114$ \\
-            \rowcolor{LIGHTGREY} Iran &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.573$ &                         $ 0.368$ &                      $ 0.211$ \\
-            \rowcolor{LIGHTGREY} Italy &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.017$ &                                          $ 0.814$ &                         $ 0.270$ &                      $ 0.220$ \\
-            \rowcolor{LIGHTGREY} Morocco &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.018$ &                                          $ 0.751$ &                         $ 0.368$ &                      $ 0.276$ \\
-            Iran &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.006$ &                                          $ 2.321$ &                         $ 0.169$ &                      $ 0.392$ \\
-            Iran (O.
-orientalis) &          Ovis aries &               $ 0.009$ &              $ 0.014$ &              $ 0.012$ &                                          $ 1.178$ &                         $ 0.153$ &                      $ 0.180$ \\
-            Iran (O.
-vignei) &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.020$ &                                          $ 0.683$ &                         $ 0.195$ &                      $ 0.133$ \\
-            Various &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.012$ &                                          $ 1.201$ &                         $ 0.190$ &                      $ 0.228$ \\
-            Morocco &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.005$ &                                          $ 2.589$ &                         $ 0.136$ &                      $ 0.353$ \\
-            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.022$ &                                          $ 0.541$ &                         $ 0.565$ &                      $ 0.306$ \\
-            \rowcolor{LIGHTGREY} Central Afr.
-Rep.
-& Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.018$ &                                          $ 0.639$ &                         $ 0.429$ &                      $ 0.274$ \\
-            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.022$ &                                          $ 0.516$ &                         $ 0.462$ &                      $ 0.239$ \\
-            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.007$ &                                          $ 1.592$ &                         $ 0.486$ &                      $ 0.774$ \\
-            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.023$ &                                          $ 0.508$ &                         $ 0.478$ &                      $ 0.243$ \\
-            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus &               $ 0.003$ &              $ 0.012$ &              $ 0.015$ &                                          $ 0.762$ &                         $ 0.516$ &                      $ 0.393$ \\
-            \rowcolor{LIGHTGREY} South Africa  & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.016$ &                                          $ 0.734$ &                         $ 0.490$ &                      $ 0.360$ \\
-            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.016$ &                                          $ 0.713$ &                         $ 0.515$ &                      $ 0.367$ \\
-            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.023$ &                                          $ 0.500$ &                         $ 0.499$ &                      $ 0.249$ \\
-            African &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.025$ &                                          $ 0.470$ &                         $ 0.678$ &                      $ 0.319$ \\
-            Admixed American &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.021$ &                                          $ 0.569$ &                         $ 0.635$ &                      $ 0.361$ \\
-            East Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.031$ &                                          $ 0.381$ &                         $ 0.611$ &                      $ 0.233$ \\
-            European &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.034$ &                                          $ 0.350$ &                         $ 0.619$ &                      $ 0.217$ \\
-            South Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.033$ &                                          $ 0.354$ &                         $ 0.628$ &                      $ 0.222$ \\
-        \end{longtable*}
-    \end{center}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item $\proba [ \SphyBen ]$ (eq.~5) is the probability for a new mutation to be a beneficial back-mutation.
-        These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1, thus toward a more fit amino-acid.
-        \item $\proba [ \SpopBen ]$ (eq.~15) is the probability for a mutation to be beneficial.
-        These mutations have a selection coefficient at the population-scale larger than 1.
-        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale (the \textit{precision}).
-        \item $\proba [ \SphyBen \given \SpopBen]$ (eq.~14) is the probability for a mutation to a beneficial back-mutations, given it is beneficial at the population scale (the \textit{recall}).
-        This probability is obtained using Bayes' formula.
-    \end{itemize}
-    \newpage
-
-    \subsection{Replicability across mammals}
-    The proportion of deleterious ($\ProbaPopDel$), nearly-neutral ($\ProbaPopNeu$) and of beneficial ($\ProbaPopBen$) mutations estimated at the population-genetic scale across the different populations is shown for each class of selection ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$).
-
-    \captionof{figure}{Estimation of selection at the population scale for $\SphyDel$ mutations}
-    \begin{minipage}{0.9\linewidth}
-    \includegraphics[width=\linewidth, page=1]{artworks/Theta.neg.stacked.pdf}
-    \end{minipage}
-    \begin{minipage}{0.09\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
-    \end{minipage}
-
-    \captionof{figure}{Estimation of selection at the population scale for $\SphyNeu$ mutations}
-    \begin{minipage}{0.9\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/Theta.weak.stacked.pdf}
-    \end{minipage}
-    \begin{minipage}{0.09\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
-    \end{minipage}
-
-    \newpage
-    \captionof{figure}{Estimation of selection at the population scale for $\SphyBen$ mutations}
-    \begin{minipage}{0.9\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/Theta.pos.stacked.pdf}
-    \end{minipage}
-    \begin{minipage}{0.09\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
-    \end{minipage}
-
-    \subsection{Correlation with diversity}
-    For each population, the proportion of deleterious ($\ProbaPopDel$), nearly-neutral ($\ProbaPopNeu$) and of beneficial ($\ProbaPopBen$) mutations estimated at the population-genetic scale is shown as function of Watterson's's diversity ($\thetaSyn$).
-
-    \subsubsection{Proportion of deleterious mutations ($\SpopDel$)}\label{subsec:proportion-deleterious-mutations}
-    \captionof{figure}{Proportion of deleterious mutations ($\SpopDel$)}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.all_P-Sneg.scatter.pdf}
-    \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.neg_P-Sneg.scatter.pdf}
-    \end{minipage}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item $\proba [ \SpopDel ]$ (eq.~15) is the probability for a mutation to be deleterious.
-        These mutations have a selection coefficient at the population-scale lower than -1.
-        \item $\proba [ \SpopDel \given \SphyDel ]$ (eq.~12) is the probability for a mutation to be deleterious at the population scale, given it is predicted to be a deleterious at the phylogenetic scale.
-    \end{itemize}
-
-    We can see that higher synonymous diversity ($\thetaSyn$) is typically accompanied by a higher proportion of effectively deleterious mutations at the population scale ($\proba [ \SpopDel ]$).
-    This trend is also confirmed when we restricted the analysis to class of mutations that are supposedly deleterious at the phylogenetic scale ($\SphyDel$).
-    This result is qualitatively in accordance with the nearly-neutral theory of evolution which argues that very slightly deleterious mutations are more efficiently purified in large populations.
-
-    \subsubsection{Proportion of nearly-neutral mutations ($\SpopNeu$)}\label{subsec:proportion-nearly-neutral-mutations}
-    \captionof{figure}{Proportion of nearly-neutral mutations ($\SpopNeu$)}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.all_P-Sweak.scatter.pdf}
-    \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.weak_P-Sweak.scatter.pdf}
-    \end{minipage}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item $\proba [ \SpopNeu ]$ (eq.~15) is the probability for a mutation to be nearly-neutral.
-        These mutations have a selection coefficient at the population-scale between -1 and 1.
-        \item $\proba [ \SpopNeu \given \SphyNeu ]$ (eq.~12) is the probability for a mutation to be nearly-neutral at the population scale, given it is predicted to be a nearly-neutral at the phylogenetic scale.
-    \end{itemize}
-
-    We confirmed that higher synonymous diversity ($\thetaSyn$) is typically accompanied by a smaller proportion of neutral mutations at the population scale ($\proba [ \SpopNeu ]$ in the range 0.06-0.18).
-    This result is more pronounced ($\proba [ \SpopNeu \given \SphyNeu ]$ in the range 0.36-0.73) when we restricted the analysis to class of mutations that are supposedly nearly-neutral at the phylogenetic scale ($\SphyNeu$).
-    This result suggests that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) are more likely to discriminate whether mutations are beneficial or deleterious.
-    Alternatively stated, mutations in populations with low diversity (e.g.~\textit{Homo}) are effectively nearly-neutral and behave as would a neutral mutation.
-    This result is qualitatively in accordance with the nearly-neutral theory of evolution which argues that mutations are less efficiently selected for in small populations.
-
-    \subsubsection{Proportion of beneficial mutations ($\SpopBen$)}\label{subsec:proportion-beneficial-mutations}
-    \captionof{figure}{Proportion of beneficial mutations ($\SpopBen$)}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.all_P-Spos.scatter.pdf}
-    \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.pos_P-Spos.scatter.pdf}
-    \end{minipage}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item $\proba [ \SpopBen ]$ (eq.~15) is the probability for a mutation to be beneficial.
-        These mutations have a selection coefficient at the population-scale larger than 1.
-        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale (the \textit{precision}).
-    \end{itemize}
-    Higher synonymous diversity ($\thetaSyn$) is accompanied by a smaller proportion of beneficial mutations at the population scale ($\proba [ \SpopBen ]$).
-    This trend is also confirmed when we restricted the analysis to class of mutations that are supposedly beneficial back-mutations at the phylogenetic scale ($\SphyBen$).
-    This result is much more difficult to interpret.
-    The fraction of beneficial back mutations is supposed to depend on long term demographic history, which is not directly accessible.
-    If the long term effective population size is relatively similar to the short term one, we expect little opportunity for beneficial back-mutations.
-    And thus, counter-intuitively we expect a diminution of positively selected mutations.
-    However, we can see that the proportion of beneficial back-mutations among advantageous one does not decrease with synonymous diversity.
-    This means that somehow adaptive mutations also decrease with synonymous diversity for a reason we fail to explain.
 
@@
 
+    \section{Correlation with diversity}
+
+    \subsection{Phylogenetic Generalized Linear Model}
+
+    Because a correlation must account for phylogenetic relationship and non-independence of samples, we fitted a Phylogenetic Generalized Linear Model (PGLM) in R with the package caper\cite{orme_caper_2013}, with multi-furcation of the different populations inside each species.
+    The mammalian tree imported from TimeTree\cite{kumar_timetree_2017} and pruned to the species used in this study.
+    Multifurcations of the different populations are placed at the same divergence time as the species.
+
+    \lstinputlisting[breaklines]{artworks/PGLM.tree}
+
+    \begin{center}
+        \includegraphics[width=0.65\linewidth, page=1]{artworks/PGLM.pdf}
+    \end{center}
+
+    Then, for each population, the proportion of deleterious ($\ProbaPopDel$), nearly-neutral ($\ProbaPopNeu$) and of beneficial ($\ProbaPopBen$) mutations estimated at the population-genetic scale is shown as function of $\Ne$.
+    $r^2$ and p-value are obtained from the PGLM model.
+
+    \newpage
+    \subsubsection{Proportion of deleterious mutations ($\SpopDel$)}\label{subsec:proportion-deleterious-mutations}
+    \captionof{figure}{Proportion of deleterious mutations ($\SpopDel$)}
+    \begin{minipage}{0.49\linewidth}
+        \includegraphics[width=\linewidth, page=1]{artworks/results.pop_size.all_P-Sneg.scatter.pdf}
+    \end{minipage}
+    \begin{minipage}{0.49\linewidth}
+        \includegraphics[width=\linewidth, page=1]{artworks/results.pop_size.neg_P-Sneg.scatter.pdf}
+    \end{minipage}
+    \begin{itemize}
+        \item $\Ne$ is the estimated effective population size.
+        \item $\proba [ \SpopDel ]$ (eq.~15) is the probability for a mutation to be deleterious.
+        These mutations have a selection coefficient at the population-scale lower than -1.
+        \item $\proba [ \SpopDel \given \SphyDel ]$ (eq.~12) is the probability for a mutation to be deleterious at the population scale, given it is predicted to be a deleterious at the phylogenetic scale.
+    \end{itemize}
+
+    We can see that higher effective population size ($\Ne$) is typically accompanied by a higher proportion of effectively deleterious mutations at the population scale ($\proba [ \SpopDel ]$).
+    This trend is also confirmed when we restricted the analysis to class of mutations that are supposedly deleterious at the phylogenetic scale ($\SphyDel$).
+    This result is qualitatively in accordance with the nearly-neutral theory of evolution which argues that very slightly deleterious mutations are more efficiently purified in large populations.
+
+    \newpage
+    \subsubsection{Proportion of nearly-neutral mutations ($\SpopNeu$)}\label{subsec:proportion-nearly-neutral-mutations}
+    \captionof{figure}{Proportion of nearly-neutral mutations ($\SpopNeu$)}
+    \begin{minipage}{0.49\linewidth}
+        \includegraphics[width=\linewidth, page=1]{artworks/results.pop_size.all_P-Sweak.scatter.pdf}
+    \end{minipage}
+    \begin{minipage}{0.49\linewidth}
+        \includegraphics[width=\linewidth, page=1]{artworks/results.pop_size.weak_P-Sweak.scatter.pdf}
+    \end{minipage}
+    \begin{itemize}
+        \item $\Ne$ is the estimated effective population size.
+        \item $\proba [ \SpopNeu ]$ (eq.~15) is the probability for a mutation to be nearly-neutral.
+        These mutations have a selection coefficient at the population-scale between -1 and 1.
+        \item $\proba [ \SpopNeu \given \SphyNeu ]$ (eq.~12) is the probability for a mutation to be nearly-neutral at the population scale, given it is predicted to be a nearly-neutral at the phylogenetic scale.
+    \end{itemize}
+
+    We confirmed that higher effective population size ($\Ne$) is typically accompanied by a smaller proportion of neutral mutations at the population scale ($\proba [ \SpopNeu ]$ in the range 0.06-0.18).
+    This result is more pronounced ($\proba [ \SpopNeu \given \SphyNeu ]$ in the range 0.36-0.73) when we restricted the analysis to class of mutations that are supposedly nearly-neutral at the phylogenetic scale ($\SphyNeu$).
+    This result suggests that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) are more likely to discriminate whether mutations are beneficial or deleterious.
+    Alternatively stated, mutations in populations with low diversity (e.g.~\textit{Homo}) are effectively nearly-neutral and behave as would a neutral mutation.
+    This result is qualitatively in accordance with the nearly-neutral theory of evolution which argues that mutations are less efficiently selected for in small populations.
+
+    \newpage
+    \subsubsection{Proportion of beneficial mutations ($\SpopBen$)}\label{subsec:proportion-beneficial-mutations}
+    \captionof{figure}{Proportion of beneficial mutations ($\SpopBen$)}
+    \begin{minipage}{0.49\linewidth}
+        \includegraphics[width=\linewidth, page=1]{artworks/results.pop_size.all_P-Spos.scatter.pdf}
+    \end{minipage}
+    \begin{minipage}{0.49\linewidth}
+        \includegraphics[width=\linewidth, page=1]{artworks/results.pop_size.pos_P-Spos.scatter.pdf}
+    \end{minipage}
+    \begin{itemize}
+        \item $\Ne$ is the estimated effective population size.
+        \item $\proba [ \SpopBen ]$ (eq.~15) is the probability for a mutation to be beneficial.
+        These mutations have a selection coefficient at the population-scale larger than 1.
+        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale (the \textit{precision}).
+    \end{itemize}
+    Higher effective population size ($\Ne$) is accompanied by a smaller proportion of beneficial mutations at the population scale ($\proba [ \SpopBen ]$).
+    This trend is also confirmed when we restricted the analysis to class of mutations that are supposedly beneficial back-mutations at the phylogenetic scale ($\SphyBen$).
+    This result is much more difficult to interpret.
+    The fraction of beneficial back mutations is supposed to depend on long term demographic history, which is not directly accessible.
+    If the long term effective population size is relatively similar to the short term one, we expect little opportunity for beneficial back-mutations.
+    And thus, counter-intuitively we expect a diminution of positively selected mutations.
+    However, we can see that the proportion of beneficial back-mutations among advantageous one does not decrease with $\Ne$.
+    This means that somehow adaptive mutations also decrease with $\Ne$ for a reason we fail to explain.
+
+    \newpage
+
+    \section{Probabilities of beneficial back-mutations among all beneficial ones ($\proba[\SphyBen\given \SpopBen ]$)}
+    \begin{center}
+        \captionof{table}{Probability of beneficial back-mutations among all beneficial ones ($\proba[\SphyBen\given \SpopBen ]$).}
+        \scriptsize
+        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
+            \toprule
+            Population & Species & $N_e$ & $\proba[\SphyBen]$ & $\proba [ \SpopBen ]$ & $\frac{\proba[\SphyBen]}{\proba[ \SpopBen ]}$ & $\proba [ \SpopBen \given \SphyBen]$ & $\proba[\SphyBen\given \SpopBen ]$ \\
+            \midrule
+            \endhead
+            \midrule
+            \multicolumn{8}{r}{{Continued on next page}} \\
+            \midrule
+            \endfoot
+            \bottomrule
+            \endlastfoot
+            \rowcolor{LIGHTGREY} Equus c. & Equus caballus & $7.5\times 10^{4}$ & $ 0.012$ & $ 0.015$ & $ 0.827$ & $ 0.648$ & $ 0.536$ \\
+            Iran & Bos taurus & $5.6\times 10^{4}$ & $ 0.011$ & $ 0.039$ & $ 0.279$ & $ 0.873$ & $ 0.243$ \\
+            Uganda & Bos taurus & $1.3\times 10^{5}$ & $ 0.011$ & $ 0.015$ & $ 0.720$ & $ 0.576$ & $ 0.415$ \\
+            \rowcolor{LIGHTGREY} Australia & Capra hircus & $1.7\times 10^{5}$ & $ 0.011$ & $ 0.023$ & $ 0.480$ & $ 0.368$ & $ 0.177$ \\
+            \rowcolor{LIGHTGREY} France & Capra hircus & $1.9\times 10^{5}$ & $ 0.011$ & $ 0.022$ & $ 0.515$ & $ 0.368$ & $ 0.190$ \\
+            \rowcolor{LIGHTGREY} Iran (C. aegagrus) & Capra hircus & $1.9\times 10^{5}$ & $ 0.011$ & $ 0.025$ & $ 0.448$ & $ 0.368$ & $ 0.165$ \\
+            \rowcolor{LIGHTGREY} Iran & Capra hircus & $2.3\times 10^{5}$ & $ 0.011$ & $ 0.021$ & $ 0.525$ & $ 0.368$ & $ 0.193$ \\
+            \rowcolor{LIGHTGREY} Italy & Capra hircus & $1.9\times 10^{5}$ & $ 0.011$ & $ 0.017$ & $ 0.660$ & $ 0.368$ & $ 0.243$ \\
+            \rowcolor{LIGHTGREY} Morocco & Capra hircus & $2.2\times 10^{5}$ & $ 0.011$ & $ 0.017$ & $ 0.667$ & $ 0.368$ & $ 0.245$ \\
+            Iran & Ovis aries & $3.8\times 10^{5}$ & $ 0.012$ & $ 0.006$ & $ 1.984$ & $ 0.205$ & $ 0.407$ \\
+            Iran (O. orientalis) & Ovis aries & $4.5\times 10^{5}$ & $ 0.011$ & $ 0.012$ & $ 0.983$ & $ 0.193$ & $ 0.190$ \\
+            Iran (O. vignei) & Ovis aries & $3.7\times 10^{5}$ & $ 0.012$ & $ 0.020$ & $ 0.579$ & $ 0.190$ & $ 0.110$ \\
+            Various & Ovis aries & $4.1\times 10^{5}$ & $ 0.011$ & $ 0.012$ & $ 0.967$ & $ 0.229$ & $ 0.222$ \\
+            Morocco & Ovis aries & $ 4\times 10^{5}$ & $ 0.012$ & $ 0.005$ & $ 2.435$ & $ 0.211$ & $ 0.514$ \\
+            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus & $1.1\times 10^{5}$ & $ 0.009$ & $ 0.021$ & $ 0.452$ & $ 0.648$ & $ 0.293$ \\
+            \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus & $1.7\times 10^{5}$ & $ 0.009$ & $ 0.018$ & $ 0.515$ & $ 0.535$ & $ 0.275$ \\
+            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus & $1.4\times 10^{5}$ & $ 0.009$ & $ 0.021$ & $ 0.444$ & $ 0.552$ & $ 0.245$ \\
+            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus & $1.4\times 10^{5}$ & $ 0.009$ & $ 0.007$ & $ 1.423$ & $ 0.577$ & $ 0.821$ \\
+            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus & $1.5\times 10^{5}$ & $ 0.009$ & $ 0.022$ & $ 0.437$ & $ 0.588$ & $ 0.257$ \\
+            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus & $ 1\times 10^{5}$ & $ 0.009$ & $ 0.016$ & $ 0.597$ & $ 0.599$ & $ 0.358$ \\
+            \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus & $1.8\times 10^{5}$ & $ 0.009$ & $ 0.016$ & $ 0.594$ & $ 0.574$ & $ 0.341$ \\
+            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus & $1.2\times 10^{5}$ & $ 0.009$ & $ 0.017$ & $ 0.563$ & $ 0.598$ & $ 0.336$ \\
+            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus & $1.7\times 10^{5}$ & $ 0.009$ & $ 0.022$ & $ 0.427$ & $ 0.585$ & $ 0.250$ \\
+            African & Homo sapiens & $5.6\times 10^{4}$ & $ 0.010$ & $ 0.020$ & $ 0.484$ & $ 0.721$ & $ 0.349$ \\
+            Admixed American & Homo sapiens & $4.5\times 10^{4}$ & $ 0.010$ & $ 0.019$ & $ 0.500$ & $ 0.690$ & $ 0.345$ \\
+            East Asian & Homo sapiens & $ 4\times 10^{4}$ & $ 0.010$ & $ 0.027$ & $ 0.362$ & $ 0.688$ & $ 0.249$ \\
+            European & Homo sapiens & $4.2\times 10^{4}$ & $ 0.010$ & $ 0.027$ & $ 0.361$ & $ 0.688$ & $ 0.248$ \\
+            South Asian & Homo sapiens & $4.4\times 10^{4}$ & $ 0.010$ & $ 0.030$ & $ 0.324$ & $ 0.691$ & $ 0.224$ \\
+        \end{longtable*}
+    \end{center}
+    \begin{itemize}
+        \item $\Ne$ is the estimated effective population size.
+        \item $\proba [ \SphyBen ]$ (eq.~5) is the probability for a new mutation to be a beneficial back-mutation.
+        These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1, thus toward a more fit amino-acid.
+        \item $\proba [ \SpopBen ]$ (eq.~15) is the probability for a mutation to be beneficial.
+        These mutations have a selection coefficient at the population-scale larger than 1.
+        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale (the \textit{precision}).
+        \item $\proba [ \SphyBen \given \SpopBen]$ (eq.~14) is the probability for a mutation to a beneficial back-mutations, given it is beneficial at the population scale (the \textit{recall}).
+        This probability is obtained using Bayes' formula.
+    \end{itemize}
+
+    \newpage
+
+    \section{Excluding genes under adaptation}
+
+    \begin{center}
+        \captionof{table}{$\proba[\SphyBen\given \SpopBen ]$ for each population when excluding or not genes under adaptation.}
+        \begin{tabular}{|l|l|r|r|}
+            \toprule
+            Population & Species & Control & Case \\
+            \midrule
+            \rowcolor{LIGHTGREY} Equus c. & Equus caballus & $ 0.536$ & $ 0.880$ \\
+            Iran & Bos taurus & $ 0.243$ & $ 0.249$ \\
+            Uganda & Bos taurus & $ 0.415$ & $ 0.429$ \\
+            \rowcolor{LIGHTGREY} Australia & Capra hircus & $ 0.177$ & $ 0.190$ \\
+            \rowcolor{LIGHTGREY} France & Capra hircus & $ 0.190$ & $ 0.201$ \\
+            \rowcolor{LIGHTGREY} Iran (C. aegagrus) & Capra hircus & $ 0.165$ & $ 0.169$ \\
+            \rowcolor{LIGHTGREY} Iran & Capra hircus & $ 0.193$ & $ 0.176$ \\
+            \rowcolor{LIGHTGREY} Italy & Capra hircus & $ 0.243$ & $ 0.261$ \\
+            \rowcolor{LIGHTGREY} Morocco & Capra hircus & $ 0.245$ & $ 0.283$ \\
+            \rowcolor{LIGHTGREY} Iran & Ovis aries & $ 0.407$ & $ 0.454$ \\
+            Iran (O. orientalis) & Ovis aries & $ 0.190$ & $ 0.207$ \\
+            Iran (O. vignei) & Ovis aries & $ 0.110$ & $ 0.135$ \\
+            Various & Ovis aries & $ 0.222$ & $ 0.246$ \\
+            Morocco & Ovis aries & $ 0.514$ & $ 0.627$ \\
+            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus & $ 0.293$ & $ 0.325$ \\
+            \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus & $ 0.275$ & $ 0.273$ \\
+            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus & $ 0.245$ & $ 0.242$ \\
+            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus & $ 0.821$ & $ 0.873$ \\
+            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus & $ 0.257$ & $ 0.254$ \\
+            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus & $ 0.358$ & $ 0.395$ \\
+            \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus & $ 0.341$ & $ 0.375$ \\
+            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus & $ 0.336$ & $ 0.355$ \\
+            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus & $ 0.250$ & $ 0.263$ \\
+            African & Homo sapiens & $ 0.349$ & $ 0.363$ \\
+            Admixed American & Homo sapiens & $ 0.345$ & $ 0.312$ \\
+            East Asian & Homo sapiens & $ 0.249$ & $ 0.233$ \\
+            European & Homo sapiens & $ 0.248$ & $ 0.211$ \\
+            South Asian & Homo sapiens & $ 0.224$ & $ 0.218$ \\
+            \bottomrule
+        \end{tabular}
+    \end{center}
+    Genes under adaptation retrieved from~\cite{latrille_genes_2023}.
+    Comparison of $\proba[\SphyBen\given \SpopBen ]$ for the whole genome (control) and when excluding genes under adaptation (case).
+    The non-parametric Wilcoxon signed-rank test tests the null hypothesis that the distribution of the differences (case versus control) is symmetric about zero.
+    Applied to the paired samples (case and control), Wilcoxon signed-rank test results in $s=80$ with $\pvalue=0.002$. for one-sided test (case higher than control).
+    The proportion of beneficial back-mutations ($\proba[\SphyBen\given \SpopBen ]$) is higher when excluding genes under adaptation, consistent with our expectation that genes with uniformly conserved functions should fit better the back-mutation equilibrium model.
+
+    \newpage
+
+    \section{Replicability across populations}
+    The proportion of deleterious ($\ProbaPopDel$), nearly-neutral ($\ProbaPopNeu$) and of beneficial ($\ProbaPopBen$) mutations estimated at the population-genetic scale across the different populations is shown for each class of selection ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$).
+
+    \captionof{figure}{Estimation of selection at the population scale for $\SphyDel$ mutations}
+    \begin{minipage}{0.9\linewidth}
+        \includegraphics[width=\linewidth, page=1]{artworks/Theta.neg.stacked.pdf}
+    \end{minipage}
+    \begin{minipage}{0.09\linewidth}
+        \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
+    \end{minipage}
+
+    \newpage
+
+    \captionof{figure}{Estimation of selection at the population scale for $\SphyNeu$ mutations}
+    \begin{minipage}{0.9\linewidth}
+        \includegraphics[width=\linewidth, page=1]{artworks/Theta.weak.stacked.pdf}
+    \end{minipage}
+    \begin{minipage}{0.09\linewidth}
+        \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
+    \end{minipage}
+
+    \captionof{figure}{Estimation of selection at the population scale for $\SphyBen$ mutations}
+    \begin{minipage}{0.9\linewidth}
+        \includegraphics[width=\linewidth, page=1]{artworks/Theta.pos.stacked.pdf}
+    \end{minipage}
+    \begin{minipage}{0.09\linewidth}
+        \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
+    \end{minipage}
+
+    \newpage
+
     \section{Including divergence data for the estimation of $\Spop$}
@@
     \begin{center}
-        \captionof{table}{Probability of beneficial back-mutations among all beneficial ones.}
+        \captionof{table}{Probability of beneficial back-mutations among all beneficial ones - including divergence.}
         \scriptsize
@@
             \toprule
-            Population & Species & Watterson's $\thetaSyn$ & $\proba[\SphyBen]$ & $\proba [ \SpopBen ]$ & $\frac{\proba[\SphyBen]}{\proba[ \SpopBen ]}$ & $\proba [ \SpopBen \given \SphyBen]$ & $\proba[\SphyBen\given \SpopBen ]$ \\
+            Population & Species & $\Ne$ & $\proba[\SphyBen]$ & $\proba [ \SpopBen ]$ & $\frac{\proba[\SphyBen]}{\proba[ \SpopBen ]}$ & $\proba [ \SpopBen \given \SphyBen]$ & $\proba[\SphyBen\given \SpopBen ]$ \\
             \midrule
@@
             \endlastfoot
-            \rowcolor{LIGHTGREY} Equus c.
-&      Equus caballus &               $ 0.002$ &              $ 0.014$ &              $ 0.061$ &                                          $ 0.235$ &                         $ 0.519$ &                      $ 0.122$ \\
-            Iran &          Bos taurus &               $ 0.002$ &              $ 0.013$ &              $ 0.007$ &                                          $ 1.908$ &                         $ 0.368$ &                      $ 0.702$ \\
-            Uganda &          Bos taurus &               $ 0.005$ &              $ 0.013$ &              $ 0.008$ &                                          $ 1.667$ &                         $ 0.255$ &                      $ 0.425$ \\
-            \rowcolor{LIGHTGREY} Australia &        Capra hircus &               $ 0.003$ &              $ 0.014$ &              $ 0.007$ &                                          $ 2.099$ &                         $ 0.147$ &                      $ 0.308$ \\
-            \rowcolor{LIGHTGREY} France &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.007$ &                                          $ 2.043$ &                         $ 0.149$ &                      $ 0.304$ \\
-            \rowcolor{LIGHTGREY} Iran (C.
-aegagrus) &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.013$ &                                          $ 1.069$ &                         $ 0.147$ &                      $ 0.157$ \\
-            \rowcolor{LIGHTGREY} Iran &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.008$ &                                          $ 1.699$ &                         $ 0.152$ &                      $ 0.258$ \\
-            \rowcolor{LIGHTGREY} Italy &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.006$ &                                          $ 2.160$ &                         $ 0.147$ &                      $ 0.316$ \\
-            \rowcolor{LIGHTGREY} Morocco &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.006$ &                                          $ 2.141$ &                         $ 0.186$ &                      $ 0.398$ \\
-            Iran &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.012$ &                                          $ 1.210$ &                         $ 0.158$ &                      $ 0.191$ \\
-            Iran (O.
-orientalis) &          Ovis aries &               $ 0.009$ &              $ 0.014$ &              $ 0.012$ &                                          $ 1.144$ &                         $ 0.157$ &                      $ 0.180$ \\
-            Iran (O.
-vignei) &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.022$ &                                          $ 0.631$ &                         $ 0.186$ &                      $ 0.118$ \\
-            Various &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.012$ &                                          $ 1.211$ &                         $ 0.156$ &                      $ 0.188$ \\
-            Morocco &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.009$ &                                          $ 1.536$ &                         $ 0.190$ &                      $ 0.292$ \\
-            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.005$ &                                          $ 2.230$ &                         $ 0.282$ &                      $ 0.630$ \\
-            \rowcolor{LIGHTGREY} Central Afr.
-Rep.
-& Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.014$ &                                          $ 0.849$ &                         $ 0.310$ &                      $ 0.263$ \\
-            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.008$ &                                          $ 1.530$ &                         $ 0.298$ &                      $ 0.456$ \\
-            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.008$ &                                          $ 1.384$ &                         $ 0.305$ &                      $ 0.422$ \\
-            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.014$ &                                          $ 0.854$ &                         $ 0.296$ &                      $ 0.253$ \\
-            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus &               $ 0.003$ &              $ 0.012$ &              $ 0.005$ &                                          $ 2.438$ &                         $ 0.285$ &                      $ 0.696$ \\
-            \rowcolor{LIGHTGREY} South Africa  & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.011$ &                                          $ 1.047$ &                         $ 0.323$ &                      $ 0.338$ \\
-            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.006$ &                                          $ 2.070$ &                         $ 0.292$ &                      $ 0.604$ \\
-            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.014$ &                                          $ 0.816$ &                         $ 0.309$ &                      $ 0.252$ \\
-            African &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.015$ &                                          $ 0.765$ &                         $ 0.371$ &                      $ 0.284$ \\
-            Admixed American &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.009$ &                                          $ 1.259$ &                         $ 0.368$ &                      $ 0.464$ \\
-            East Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.012$ &                                          $ 0.973$ &                         $ 0.369$ &                      $ 0.358$ \\
-            European &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.009$ &                                          $ 1.356$ &                         $ 0.368$ &                      $ 0.499$ \\
-            South Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.010$ &                                          $ 1.147$ &                         $ 0.369$ &                      $ 0.423$ \\
+            \rowcolor{LIGHTGREY} Equus c. & Equus caballus & $7.5\times 10^{4}$ & $ 0.012$ & $ 0.057$ & $ 0.213$ & $ 0.498$ & $ 0.106$ \\
+            Iran & Bos taurus & $5.6\times 10^{4}$ & $ 0.011$ & $ 0.006$ & $ 1.860$ & $ 0.368$ & $ 0.684$ \\
+            Uganda & Bos taurus & $1.3\times 10^{5}$ & $ 0.011$ & $ 0.012$ & $ 0.900$ & $ 0.307$ & $ 0.276$ \\
+            \rowcolor{LIGHTGREY} Australia & Capra hircus & $1.7\times 10^{5}$ & $ 0.011$ & $ 0.007$ & $ 1.651$ & $ 0.178$ & $ 0.294$ \\
+            \rowcolor{LIGHTGREY} France & Capra hircus & $1.9\times 10^{5}$ & $ 0.011$ & $ 0.007$ & $ 1.614$ & $ 0.183$ & $ 0.295$ \\
+            \rowcolor{LIGHTGREY} Iran (C. aegagrus) & Capra hircus & $1.9\times 10^{5}$ & $ 0.011$ & $ 0.012$ & $ 0.923$ & $ 0.177$ & $ 0.163$ \\
+            \rowcolor{LIGHTGREY} Iran & Capra hircus & $2.3\times 10^{5}$ & $ 0.011$ & $ 0.008$ & $ 1.483$ & $ 0.184$ & $ 0.273$ \\
+            \rowcolor{LIGHTGREY} Italy & Capra hircus & $1.9\times 10^{5}$ & $ 0.011$ & $ 0.007$ & $ 1.686$ & $ 0.178$ & $ 0.299$ \\
+            \rowcolor{LIGHTGREY} Morocco & Capra hircus & $2.2\times 10^{5}$ & $ 0.011$ & $ 0.006$ & $ 1.892$ & $ 0.184$ & $ 0.349$ \\
+            Iran & Ovis aries & $3.8\times 10^{5}$ & $ 0.012$ & $ 0.010$ & $ 1.132$ & $ 0.189$ & $ 0.214$ \\
+            Iran (O. orientalis) & Ovis aries & $4.5\times 10^{5}$ & $ 0.011$ & $ 0.011$ & $ 1.012$ & $ 0.213$ & $ 0.216$ \\
+            Iran (O. vignei) & Ovis aries & $3.7\times 10^{5}$ & $ 0.012$ & $ 0.021$ & $ 0.561$ & $ 0.186$ & $ 0.105$ \\
+            Various & Ovis aries & $4.1\times 10^{5}$ & $ 0.011$ & $ 0.011$ & $ 1.069$ & $ 0.215$ & $ 0.229$ \\
+            Morocco & Ovis aries & $ 4\times 10^{5}$ & $ 0.012$ & $ 0.012$ & $ 0.973$ & $ 0.217$ & $ 0.211$ \\
+            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus & $1.1\times 10^{5}$ & $ 0.009$ & $ 0.004$ & $ 2.120$ & $ 0.341$ & $ 0.723$ \\
+            \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus & $1.7\times 10^{5}$ & $ 0.009$ & $ 0.013$ & $ 0.720$ & $ 0.368$ & $ 0.265$ \\
+            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus & $1.4\times 10^{5}$ & $ 0.009$ & $ 0.007$ & $ 1.352$ & $ 0.368$ & $ 0.498$ \\
+            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus & $1.4\times 10^{5}$ & $ 0.009$ & $ 0.010$ & $ 0.956$ & $ 0.368$ & $ 0.352$ \\
+            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus & $1.5\times 10^{5}$ & $ 0.009$ & $ 0.013$ & $ 0.727$ & $ 0.368$ & $ 0.268$ \\
+            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus & $ 1\times 10^{5}$ & $ 0.009$ & $ 0.004$ & $ 2.133$ & $ 0.368$ & $ 0.784$ \\
+            \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus & $1.8\times 10^{5}$ & $ 0.009$ & $ 0.011$ & $ 0.874$ & $ 0.368$ & $ 0.322$ \\
+            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus & $1.2\times 10^{5}$ & $ 0.009$ & $ 0.005$ & $ 1.905$ & $ 0.368$ & $ 0.701$ \\
+            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus & $1.7\times 10^{5}$ & $ 0.009$ & $ 0.014$ & $ 0.698$ & $ 0.368$ & $ 0.257$ \\
+            African & Homo sapiens & $5.6\times 10^{4}$ & $ 0.010$ & $ 0.013$ & $ 0.726$ & $ 0.437$ & $ 0.317$ \\
+            Admixed American & Homo sapiens & $4.5\times 10^{4}$ & $ 0.010$ & $ 0.011$ & $ 0.886$ & $ 0.429$ & $ 0.380$ \\
+            East Asian & Homo sapiens & $ 4\times 10^{4}$ & $ 0.010$ & $ 0.008$ & $ 1.213$ & $ 0.426$ & $ 0.517$ \\
+            European & Homo sapiens & $4.1\times 10^{4}$ & $ 0.010$ & $ 0.009$ & $ 1.104$ & $ 0.422$ & $ 0.466$ \\
+            South Asian & Homo sapiens & $4.4\times 10^{4}$ & $ 0.010$ & $ 0.009$ & $ 1.016$ & $ 0.426$ & $ 0.433$ \\
         \end{longtable*}
@@
     \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
+        \item $\Ne$ is the estimated effective population size.
         \item $\proba [ \SphyBen ]$ (eq.~5) is the probability for a new mutation a beneficial back-mutation.
@@
     \subsection{Precision and recall}
-    \captionof{table}{Precision and recall}
+    \captionof{table}{Precision and recall - including divergence}
     \begin{center}
@@
                 \\   \midrule
-                \rowcolor{LIGHTGREY} Equus c. & Equus caballus        & $ 0.002$ & $ 0.918$ & $ 0.957$ & $ 0.186$ & $ 0.213$ & $ 0.519$ & $ 0.122$ \\
-                Iran               & Bos taurus        & $ 0.002$ & $ 0.924$ & $ 0.965$ & $ 0.565$ & $ 0.356$ & $ 0.368$ & $ 0.702$ \\
-                Uganda              & Bos taurus        & $ 0.005$ & $ 0.943$ & $ 0.961$ & $ 0.516$ & $ 0.396$ & $ 0.255$ & $ 0.425$ \\
-                \rowcolor{LIGHTGREY} Australia            & Capra hircus        & $ 0.003$ & $ 0.941$ & $ 0.964$ & $ 0.592$ & $ 0.434$ & $ 0.147$ & $ 0.308$ \\
-                \rowcolor{LIGHTGREY} France                                    & Capra hircus          & $ 0.004$ & $ 0.940$ & $ 0.963$ & $ 0.571$ & $ 0.418$ & $ 0.149$ & $ 0.304$ \\
-                \rowcolor{LIGHTGREY} Iran (C. aegagrus)                    & Capra hircus          & $ 0.004$ & $ 0.948$ & $ 0.960$ & $ 0.515$ & $ 0.446$ & $ 0.147$ & $ 0.157$ \\
-                \rowcolor{LIGHTGREY} Iran                        & Capra hircus          & $ 0.004$ & $ 0.942$ & $ 0.961$ & $ 0.534$ & $ 0.410$ & $ 0.152$ & $ 0.258$ \\
-                \rowcolor{LIGHTGREY} Italy                                 & Capra hircus          & $ 0.004$ & $ 0.940$ & $ 0.963$ & $ 0.579$ & $ 0.421$ & $ 0.147$ & $ 0.316$ \\
-                \rowcolor{LIGHTGREY} Morocco                                 & Capra hircus          & $ 0.004$ & $ 0.939$ & $ 0.960$ & $ 0.549$ & $ 0.404$ & $ 0.186$ & $ 0.398$ \\
-                Iran           & Ovis aries & $ 0.007$ & $ 0.957$ & $ 0.954$ & $ 0.412$ & $ 0.416$ & $ 0.158$ & $ 0.191$ \\
-                Iran (O. orientalis)  & Ovis aries & $ 0.009$ & $ 0.961$ & $ 0.955$ & $ 0.413$ & $ 0.437$ & $ 0.157$ & $ 0.180$ \\
-                Iran (O. vignei)           & Ovis aries & $ 0.007$ & $ 0.968$ & $ 0.951$ & $ 0.356$ & $ 0.516$ & $ 0.186$ & $ 0.118$ \\
-                Various             & Ovis aries & $ 0.008$ & $ 0.958$ & $ 0.955$ & $ 0.428$ & $ 0.431$ & $ 0.156$ & $ 0.188$ \\
-                Morocco              & Ovis aries & $ 0.008$ & $ 0.960$ & $ 0.953$ & $ 0.447$ & $ 0.460$ & $ 0.190$ & $ 0.292$ \\
-                \rowcolor{LIGHTGREY} Barbados              & Chlorocebus sabaeus & $ 0.004$ & $ 0.931$ & $ 0.969$ & $ 0.628$ & $ 0.402$ & $ 0.282$ & $ 0.630$ \\
-                \rowcolor{LIGHTGREY} Central Afr. Rep.       & Chlorocebus sabaeus & $ 0.006$ & $ 0.941$ & $ 0.964$ & $ 0.514$ & $ 0.408$ & $ 0.310$ & $ 0.263$ \\
-                \rowcolor{LIGHTGREY} Ethiopia        & Chlorocebus sabaeus & $ 0.005$ & $ 0.933$ & $ 0.967$ & $ 0.586$ & $ 0.393$ & $ 0.298$ & $ 0.456$ \\
-                \rowcolor{LIGHTGREY} Gambia             & Chlorocebus sabaeus & $ 0.005$ & $ 0.937$ & $ 0.967$ & $ 0.590$ & $ 0.414$ & $ 0.305$ & $ 0.422$ \\
-                \rowcolor{LIGHTGREY} Kenya                                 & Chlorocebus sabaeus        & $ 0.005$ & $ 0.942$ & $ 0.965$ & $ 0.526$ & $ 0.418$ & $ 0.296$ & $ 0.253$ \\
-                \rowcolor{LIGHTGREY} Nevis                        & Chlorocebus sabaeus        & $ 0.003$ & $ 0.930$ & $ 0.970$ & $ 0.637$ & $ 0.401$ & $ 0.285$ & $ 0.696$ \\
-                \rowcolor{LIGHTGREY} South Africa                              & Chlorocebus sabaeus        & $ 0.006$ & $ 0.937$ & $ 0.964$ & $ 0.530$ & $ 0.393$ & $ 0.323$ & $ 0.338$ \\
-                \rowcolor{LIGHTGREY} Saint Kitts                                & Chlorocebus sabaeus        & $ 0.004$ & $ 0.931$ & $ 0.969$ & $ 0.611$ & $ 0.393$ & $ 0.292$ & $ 0.604$ \\
-                \rowcolor{LIGHTGREY} Zambia                             & Chlorocebus sabaeus        & $ 0.006$ & $ 0.941$ & $ 0.963$ & $ 0.506$ & $ 0.408$ & $ 0.309$ & $ 0.252$ \\
-                African                             & Homo sapiens        & $ 0.002$ & $ 0.896$ & $ 0.968$ & $ 0.550$ & $ 0.297$ & $ 0.371$ & $ 0.284$ \\
-                Admixed American                             & Homo sapiens        & $ 0.002$ & $ 0.890$ & $ 0.979$ & $ 0.710$ & $ 0.333$ & $ 0.368$ & $ 0.464$ \\
-                East Asian                             & Homo sapiens        & $ 0.002$ & $ 0.890$ & $ 0.971$ & $ 0.578$ & $ 0.289$ & $ 0.369$ & $ 0.358$ \\
-                European                             & Homo sapiens        & $ 0.002$ & $ 0.891$ & $ 0.980$ & $ 0.739$ & $ 0.345$ & $ 0.368$ & $ 0.499$ \\
-                South Asian                             & Homo sapiens        & $ 0.002$ & $ 0.895$ & $ 0.981$ & $ 0.740$ & $ 0.356$ & $ 0.369$ & $ 0.423$ \\
+                \rowcolor{LIGHTGREY} Equus c. & Equus caballus & $7.5\times 10^{4}$ & $ 0.937$ & $ 0.955$ & $ 0.111$ & $ 0.192$ & $ 0.498$ & $ 0.106$ \\
+                Iran & Bos taurus & $5.6\times 10^{4}$ & $ 0.935$ & $ 0.970$ & $ 0.565$ & $ 0.356$ & $ 0.368$ & $ 0.684$ \\
+                Uganda & Bos taurus & $1.3\times 10^{5}$ & $ 0.951$ & $ 0.967$ & $ 0.516$ & $ 0.422$ & $ 0.307$ & $ 0.276$ \\
+                \rowcolor{LIGHTGREY} Australia & Capra hircus & $1.7\times 10^{5}$ & $ 0.952$ & $ 0.970$ & $ 0.598$ & $ 0.452$ & $ 0.178$ & $ 0.294$ \\
+                \rowcolor{LIGHTGREY} France & Capra hircus & $1.9\times 10^{5}$ & $ 0.951$ & $ 0.969$ & $ 0.574$ & $ 0.433$ & $ 0.183$ & $ 0.295$ \\
+                \rowcolor{LIGHTGREY} Iran (C. aegagrus) & Capra hircus & $1.9\times 10^{5}$ & $ 0.957$ & $ 0.966$ & $ 0.515$ & $ 0.460$ & $ 0.177$ & $ 0.163$ \\
+                \rowcolor{LIGHTGREY} Iran & Capra hircus & $2.3\times 10^{5}$ & $ 0.951$ & $ 0.967$ & $ 0.542$ & $ 0.422$ & $ 0.184$ & $ 0.273$ \\
+                \rowcolor{LIGHTGREY} Italy & Capra hircus & $1.9\times 10^{5}$ & $ 0.951$ & $ 0.969$ & $ 0.582$ & $ 0.436$ & $ 0.178$ & $ 0.299$ \\
+                \rowcolor{LIGHTGREY} Morocco & Capra hircus & $2.2\times 10^{5}$ & $ 0.949$ & $ 0.968$ & $ 0.556$ & $ 0.412$ & $ 0.184$ & $ 0.349$ \\
+                Iran & Ovis aries & $3.8\times 10^{5}$ & $ 0.963$ & $ 0.962$ & $ 0.421$ & $ 0.424$ & $ 0.189$ & $ 0.214$ \\
+                Iran (O. orientalis) & Ovis aries & $4.5\times 10^{5}$ & $ 0.968$ & $ 0.961$ & $ 0.413$ & $ 0.460$ & $ 0.213$ & $ 0.216$ \\
+                Iran (O. vignei) & Ovis aries & $3.7\times 10^{5}$ & $ 0.972$ & $ 0.959$ & $ 0.360$ & $ 0.528$ & $ 0.186$ & $ 0.105$ \\
+                Various & Ovis aries & $4.1\times 10^{5}$ & $ 0.966$ & $ 0.961$ & $ 0.430$ & $ 0.454$ & $ 0.215$ & $ 0.229$ \\
+                Morocco & Ovis aries & $ 4\times 10^{5}$ & $ 0.966$ & $ 0.958$ & $ 0.372$ & $ 0.416$ & $ 0.217$ & $ 0.211$ \\
+                \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus & $1.1\times 10^{5}$ & $ 0.940$ & $ 0.976$ & $ 0.654$ & $ 0.409$ & $ 0.341$ & $ 0.723$ \\
+                \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus & $1.7\times 10^{5}$ & $ 0.950$ & $ 0.971$ & $ 0.526$ & $ 0.421$ & $ 0.368$ & $ 0.265$ \\
+                \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus & $1.4\times 10^{5}$ & $ 0.942$ & $ 0.974$ & $ 0.609$ & $ 0.402$ & $ 0.368$ & $ 0.498$ \\
+                \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus & $1.4\times 10^{5}$ & $ 0.950$ & $ 0.974$ & $ 0.611$ & $ 0.452$ & $ 0.368$ & $ 0.352$ \\
+                \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus & $1.5\times 10^{5}$ & $ 0.950$ & $ 0.972$ & $ 0.545$ & $ 0.434$ & $ 0.368$ & $ 0.268$ \\
+                \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus & $ 1\times 10^{5}$ & $ 0.940$ & $ 0.977$ & $ 0.668$ & $ 0.412$ & $ 0.368$ & $ 0.784$ \\
+                \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus & $1.8\times 10^{5}$ & $ 0.947$ & $ 0.972$ & $ 0.550$ & $ 0.411$ & $ 0.368$ & $ 0.322$ \\
+                \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus & $1.2\times 10^{5}$ & $ 0.940$ & $ 0.976$ & $ 0.646$ & $ 0.407$ & $ 0.368$ & $ 0.701$ \\
+                \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus & $1.7\times 10^{5}$ & $ 0.950$ & $ 0.971$ & $ 0.527$ & $ 0.426$ & $ 0.368$ & $ 0.257$ \\
+                African & Homo sapiens & $5.6\times 10^{4}$ & $ 0.911$ & $ 0.980$ & $ 0.666$ & $ 0.341$ & $ 0.437$ & $ 0.317$ \\
+                Admixed American & Homo sapiens & $4.5\times 10^{4}$ & $ 0.902$ & $ 0.976$ & $ 0.580$ & $ 0.284$ & $ 0.429$ & $ 0.380$ \\
+                East Asian & Homo sapiens & $ 4\times 10^{4}$ & $ 0.904$ & $ 0.984$ & $ 0.744$ & $ 0.341$ & $ 0.426$ & $ 0.517$ \\
+                European & Homo sapiens & $4.1\times 10^{4}$ & $ 0.906$ & $ 0.984$ & $ 0.737$ & $ 0.344$ & $ 0.422$ & $ 0.466$ \\
+                South Asian & Homo sapiens & $4.4\times 10^{4}$ & $ 0.907$ & $ 0.984$ & $ 0.737$ & $ 0.349$ & $ 0.426$ & $ 0.433$ \\
                 \bottomrule
@@
     \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
+        \item $\Ne$ is the estimated effective population size.
         \item \textit{Precision} is the estimation of the selection coefficient at population scale ($\Spop$) given that $\Sphy$ is known.
@@
     However, we can still see that beneficial back-mutations are positively selected compared to neutral and deleterious ones, and this result is not sensitive to inclusion of substitutions in the terminal lineage.
+    \newpage
+
+    \subsection{Excluding genes under adaptation}
+
+    \begin{center}
+        \captionof{table}{$\proba[\SphyBen\given \SpopBen ]$ for each population when excluding or not genes under adaptation - including divergence.}
+        \begin{tabular}{|l|l|r|r|}
+            \toprule
+            Population & Species & Control & Case \\
+            \midrule
+            \rowcolor{LIGHTGREY} Equus c. & Equus caballus & $ 0.106$ & $ 0.106$ \\
+            Iran & Bos taurus & $ 0.684$ & $ 0.755$ \\
+            Uganda & Bos taurus & $ 0.276$ & $ 0.310$ \\
+            \rowcolor{LIGHTGREY} Australia & Capra hircus & $ 0.294$ & $ 0.319$ \\
+            \rowcolor{LIGHTGREY} France & Capra hircus & $ 0.295$ & $ 0.325$ \\
+            \rowcolor{LIGHTGREY} Iran (C. aegagrus) & Capra hircus & $ 0.163$ & $ 0.174$ \\
+            \rowcolor{LIGHTGREY} Iran & Capra hircus & $ 0.273$ & $ 0.299$ \\
+            \rowcolor{LIGHTGREY} Italy & Capra hircus & $ 0.299$ & $ 0.321$ \\
+            \rowcolor{LIGHTGREY} Morocco & Capra hircus & $ 0.349$ & $ 0.419$ \\
+            Iran & Ovis aries & $ 0.214$ & $ 0.241$ \\
+            Iran (O. orientalis) & Ovis aries & $ 0.216$ & $ 0.213$ \\
+            Iran (O. vignei) & Ovis aries & $ 0.105$ & $ 0.089$ \\
+            Various & Ovis aries & $ 0.229$ & $ 0.196$ \\
+            Morocco & Ovis aries & $ 0.211$ & $ 0.206$ \\
+            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus & $ 0.723$ & $ 0.833$ \\
+            \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus & $ 0.265$ & $ 0.285$ \\
+            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus & $ 0.498$ & $ 0.547$ \\
+            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus & $ 0.352$ & $ 0.571$ \\
+            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus & $ 0.268$ & $ 0.265$ \\
+            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus & $ 0.784$ & $ 0.892$ \\
+            \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus & $ 0.322$ & $ 0.307$ \\
+            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus & $ 0.701$ & $ 0.825$ \\
+            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus & $ 0.257$ & $ 0.271$ \\
+            African & Homo sapiens & $ 0.317$ & $ 0.278$ \\
+            Admixed American & Homo sapiens & $ 0.380$ & $ 0.363$ \\
+            East Asian & Homo sapiens & $ 0.517$ & $ 0.499$ \\
+            European & Homo sapiens & $ 0.466$ & $ 0.456$ \\
+            South Asian & Homo sapiens & $ 0.433$ & $ 0.304$ \\
+            \bottomrule
+        \end{tabular}
+    \end{center}
+    Genes under adaptation retrieved from~\cite{latrille_genes_2023}.
+    Comparison of $\proba[\SphyBen\given \SpopBen ]$ while including divergence for the whole genome (control) and when excluding genes under adaptation (case).
+    The non-parametric Wilcoxon signed-rank test tests the null hypothesis that the distribution of the differences (case versus control) is symmetric about zero.
+    Applied to the paired samples (case and control), Wilcoxon signed-rank test results in $s=120$ with $\pvalue=0.027$ for one-sided test (case higher than control).
+    The proportion of beneficial back-mutations ($\proba[\SphyBen\given \SpopBen ]$) is higher when excluding genes under adaptation, consistent with our expectation that genes with uniformly conserved functions should fit better the back-mutation equilibrium model.
 
     \newpage
+
     \section{Discrete distribution of $\Spop$ at the population scale}
@@
     \subsection{polyDFE model D (discrete distribution)}
-    With polyDFE model D, the DFE of non-synonymous mutations is given as a discrete DFE of $K$ categories (instead of a continuous distribution in model C), where the selection coefficients of each category $i$ ($1 \leq i \leq K$) are fixed parameters $\Spop_i$, and each value $\Spop_i$ has a probability $p_i$ (estimated), with $\sum_{i=1}^{K} p_i =1$.
+    Additionally to including divergence, with also tested our prediction with polyDFE model D instead of model C.
+    In polyDFE model D, the DFE of non-synonymous mutations is given as a discrete DFE of $K$ categories (instead of a continuous distribution in model C), where the selection coefficients of each category $i$ ($1 \leq i \leq K$) are fixed parameters $\Spop_i$, and each value $\Spop_i$ has a probability $p_i$ (estimated), with $\sum_{i=1}^{K} p_i =1$.
     We used $K=6$ with $\Spop_1 = -500$, $\Spop_2 = -4$, $\Spop_3 =-1$, $\Spop_4 = 0$, $\Spop_5 = 1$, $\Spop_6 = 4$.\\
@@
     \begin{align}
-        \proba [ \SpopDel \given  \Sphyclass] &= \proba [ \Spop < -1 \given \Sphyclass ] = p_1 + p_2 \label{eq:polyProbaDel} \\
+        \proba [ \SpopDel \given  \Sphyclass] &= \proba [ \Spop < -1 \given \Sphyclass ] = p_1 + p_2 \label{eq:polyProbaDel-mD} \\
         \proba [ \SpopNeu \given \Sphyclass] &= \proba [ -1 < \Spop < 1 \given \Sphyclass ] = p_3 + p_4 + p_5,  \\
-        \proba [ \SpopBen \given \Sphyclass] &= p_6. \label{eq:polyProbaAdv}
+        \proba [ \SpopBen \given \Sphyclass] &= \proba [  \Spop > 1 \given \Sphyclass ] = p_6.  \label{eq:polyProbaAdv-mD}
     \end{align}
@@
     \begin{center}
-        \captionof{table}{Probability of beneficial back-mutations among all beneficial ones.}
+        \captionof{table}{Probability of beneficial back-mutations among all beneficial ones - model D.}
         \scriptsize
@@
             \endlastfoot
-            \rowcolor{LIGHTGREY} Equus c.
-&      Equus caballus &               $ 0.002$ &              $ 0.014$ &              $ 0.006$ &                                          $ 2.230$ &                         $ 0.141$ &                      $ 0.316$ \\
-            Iran &          Bos taurus &               $ 0.002$ &              $ 0.013$ &              $ 0.006$ &                                          $ 2.200$ &                         $ 0.136$ &                      $ 0.298$ \\
-            Uganda &          Bos taurus &               $ 0.005$ &              $ 0.013$ &              $ 0.011$ &                                          $ 1.177$ &                         $ 0.138$ &                      $ 0.162$ \\
-            \rowcolor{LIGHTGREY} Australia &        Capra hircus &               $ 0.003$ &              $ 0.014$ &              $ 0.002$ &                                          $ 6.467$ &                         $ 0.135$ &                      $ 0.871$ \\
-            \rowcolor{LIGHTGREY} France &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.002$ &                                          $ 6.407$ &                         $ 0.132$ &                      $ 0.845$ \\
-            \rowcolor{LIGHTGREY} Iran (C.
-aegagrus) &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.002$ &                                          $ 5.993$ &                         $ 0.129$ &                      $ 0.772$ \\
-            \rowcolor{LIGHTGREY} Iran &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.004$ &                                          $ 3.656$ &                         $ 0.138$ &                      $ 0.506$ \\
-            \rowcolor{LIGHTGREY} Italy &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.002$ &                                          $ 6.216$ &                         $ 0.127$ &                      $ 0.787$ \\
-            \rowcolor{LIGHTGREY} Morocco &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.002$ &                                          $ 6.019$ &                         $ 0.141$ &                      $ 0.848$ \\
-            Iran &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.588$ &                         $ 0.148$ &                      $ 0.087$ \\
-            Iran (O.
-orientalis) &          Ovis aries &               $ 0.009$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.569$ &                         $ 0.143$ &                      $ 0.081$ \\
-            Iran (O.
-vignei) &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.587$ &                         $ 0.127$ &                      $ 0.075$ \\
-            Various &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.588$ &                         $ 0.146$ &                      $ 0.086$ \\
-            Morocco &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.025$ &                                          $ 0.564$ &                         $ 0.145$ &                      $ 0.082$ \\
-            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.002$ &                                          $ 5.689$ &                         $ 0.170$ &                      $ 0.968$ \\
-            \rowcolor{LIGHTGREY} Central Afr.
-Rep.
-& Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.005$ &                                          $ 2.142$ &                         $ 0.156$ &                      $ 0.334$ \\
-            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.002$ &                                          $ 5.910$ &                         $ 0.160$ &                      $ 0.945$ \\
-            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.006$ &                                          $ 1.850$ &                         $ 0.157$ &                      $ 0.290$ \\
-            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.004$ &                                          $ 2.802$ &                         $ 0.163$ &                      $ 0.456$ \\
-            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus &               $ 0.003$ &              $ 0.012$ &              $ 0.002$ &                                          $ 5.396$ &                         $ 0.169$ &                      $ 0.910$ \\
-            \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.005$ &                                          $ 2.154$ &                         $ 0.153$ &                      $ 0.329$ \\
-            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.002$ &                                          $ 5.094$ &                         $ 0.164$ &                      $ 0.834$ \\
-            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.006$ &                                          $ 1.952$ &                         $ 0.153$ &                      $ 0.298$ \\
-            African &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.014$ &                                          $ 0.869$ &                         $ 0.141$ &                      $ 0.123$ \\
-            Admixed American &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.010$ &                                          $ 1.130$ &                         $ 0.161$ &                      $ 0.182$ \\
-            East Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.007$ &                                          $ 1.602$ &                         $ 0.162$ &                      $ 0.259$ \\
-            European &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.009$ &                                          $ 1.336$ &                         $ 0.163$ &                      $ 0.217$ \\
-            South Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.009$ &                                          $ 1.342$ &                         $ 0.163$ &                      $ 0.219$ \\
+            \rowcolor{LIGHTGREY} Equus c. & Equus caballus & $7.5\times 10^{4}$ & $ 0.012$ & $ 0.006$ & $ 2.050$ & $ 0.163$ & $ 0.334$ \\
+            Iran & Bos taurus & $5.6\times 10^{4}$ & $ 0.011$ & $ 0.005$ & $ 2.125$ & $ 0.133$ & $ 0.283$ \\
+            Uganda & Bos taurus & $1.3\times 10^{5}$ & $ 0.011$ & $ 0.010$ & $ 1.139$ & $ 0.140$ & $ 0.159$ \\
+            \rowcolor{LIGHTGREY} Australia & Capra hircus & $1.7\times 10^{5}$ & $ 0.011$ & $ 0.002$ & $ 5.637$ & $ 0.151$ & $ 0.850$ \\
+            \rowcolor{LIGHTGREY} France & Capra hircus & $1.9\times 10^{5}$ & $ 0.011$ & $ 0.002$ & $ 6.117$ & $ 0.154$ & $ 0.940$ \\
+            \rowcolor{LIGHTGREY} Iran (C. aegagrus) & Capra hircus & $1.9\times 10^{5}$ & $ 0.011$ & $ 0.002$ & $ 5.842$ & $ 0.156$ & $ 0.911$ \\
+            \rowcolor{LIGHTGREY} Iran & Capra hircus & $2.3\times 10^{5}$ & $ 0.011$ & $ 0.002$ & $ 6.400$ & $ 0.147$ & $ 0.943$ \\
+            \rowcolor{LIGHTGREY} Italy & Capra hircus & $1.9\times 10^{5}$ & $ 0.011$ & $ 0.002$ & $ 5.793$ & $ 0.155$ & $ 0.895$ \\
+            \rowcolor{LIGHTGREY} Morocco & Capra hircus & $2.2\times 10^{5}$ & $ 0.011$ & $ 0.003$ & $ 4.192$ & $ 0.150$ & $ 0.627$ \\
+            Iran & Ovis aries & $3.8\times 10^{5}$ & $ 0.012$ & $ 0.020$ & $ 0.584$ & $ 0.154$ & $ 0.090$ \\
+            Iran (O. orientalis) & Ovis aries & $4.5\times 10^{5}$ & $ 0.011$ & $ 0.021$ & $ 0.535$ & $ 0.148$ & $ 0.079$ \\
+            Iran (O. vignei) & Ovis aries & $3.7\times 10^{5}$ & $ 0.012$ & $ 0.020$ & $ 0.568$ & $ 0.151$ & $ 0.086$ \\
+            Various & Ovis aries & $4.1\times 10^{5}$ & $ 0.011$ & $ 0.021$ & $ 0.553$ & $ 0.152$ & $ 0.084$ \\
+            Morocco & Ovis aries & $ 4\times 10^{5}$ & $ 0.012$ & $ 0.022$ & $ 0.529$ & $ 0.153$ & $ 0.081$ \\
+            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus & $1.1\times 10^{5}$ & $ 0.009$ & $ 0.002$ & $ 5.152$ & $ 0.170$ & $ 0.877$ \\
+            \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus & $1.7\times 10^{5}$ & $ 0.009$ & $ 0.007$ & $ 1.266$ & $ 0.157$ & $ 0.199$ \\
+            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus & $1.4\times 10^{5}$ & $ 0.009$ & $ 0.002$ & $ 3.979$ & $ 0.161$ & $ 0.640$ \\
+            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus & $1.4\times 10^{5}$ & $ 0.009$ & $ 0.008$ & $ 1.201$ & $ 0.159$ & $ 0.191$ \\
+            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus & $1.5\times 10^{5}$ & $ 0.009$ & $ 0.003$ & $ 2.801$ & $ 0.165$ & $ 0.461$ \\
+            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus & $ 1\times 10^{5}$ & $ 0.009$ & $ 0.002$ & $ 5.361$ & $ 0.169$ & $ 0.908$ \\
+            \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus & $1.8\times 10^{5}$ & $ 0.009$ & $ 0.005$ & $ 1.912$ & $ 0.154$ & $ 0.294$ \\
+            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus & $1.2\times 10^{5}$ & $ 0.009$ & $ 0.002$ & $ 4.561$ & $ 0.165$ & $ 0.753$ \\
+            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus & $1.7\times 10^{5}$ & $ 0.009$ & $ 0.004$ & $ 2.661$ & $ 0.153$ & $ 0.406$ \\
+            African & Homo sapiens & $5.6\times 10^{4}$ & $ 0.010$ & $ 0.010$ & $ 0.997$ & $ 0.154$ & $ 0.154$ \\
+            Admixed American & Homo sapiens & $4.5\times 10^{4}$ & $ 0.010$ & $ 0.008$ & $ 1.206$ & $ 0.158$ & $ 0.190$ \\
+            East Asian & Homo sapiens & $ 4\times 10^{4}$ & $ 0.010$ & $ 0.007$ & $ 1.455$ & $ 0.163$ & $ 0.237$ \\
+            European & Homo sapiens & $4.2\times 10^{4}$ & $ 0.010$ & $ 0.007$ & $ 1.316$ & $ 0.167$ & $ 0.219$ \\
+            South Asian & Homo sapiens & $4.4\times 10^{4}$ & $ 0.010$ & $ 0.007$ & $ 1.340$ & $ 0.164$ & $ 0.219$ \\
         \end{longtable*}
@@
     \subsection{Precision and recall}
-    \captionof{table}{Precision and recall}
+    \captionof{table}{Precision and recall - model D}
     \begin{center}
@@
                 \\   \midrule
-                \rowcolor{LIGHTGREY} Equus c. & Equus caballus        & $ 0.002$ & $ 0.895$ & $ 0.969$ & $ 0.645$ & $ 0.315$ & $ 0.141$ & $ 0.316$ \\
-                Iran               & Bos taurus        & $ 0.002$ & $ 0.878$ & $ 0.968$ & $ 0.632$ & $ 0.286$ & $ 0.136$ & $ 0.298$ \\
-                Uganda              & Bos taurus        & $ 0.005$ & $ 0.951$ & $ 0.963$ & $ 0.597$ & $ 0.508$ & $ 0.138$ & $ 0.162$ \\
-                \rowcolor{LIGHTGREY} Australia            & Capra hircus        & $ 0.003$ & $ 0.895$ & $ 0.981$ & $ 0.830$ & $ 0.379$ & $ 0.135$ & $ 0.871$ \\
-                \rowcolor{LIGHTGREY} France                                    & Capra hircus          & $ 0.004$ & $ 0.896$ & $ 0.978$ & $ 0.801$ & $ 0.373$ & $ 0.132$ & $ 0.845$ \\
-                \rowcolor{LIGHTGREY} Iran (C. aegagrus)                    & Capra hircus          & $ 0.004$ & $ 0.913$ & $ 0.971$ & $ 0.711$ & $ 0.383$ & $ 0.129$ & $ 0.772$ \\
-                \rowcolor{LIGHTGREY} Iran                        & Capra hircus          & $ 0.004$ & $ 0.949$ & $ 0.968$ & $ 0.655$ & $ 0.481$ & $ 0.138$ & $ 0.506$ \\
-                \rowcolor{LIGHTGREY} Italy                                 & Capra hircus          & $ 0.004$ & $ 0.894$ & $ 0.979$ & $ 0.814$ & $ 0.373$ & $ 0.127$ & $ 0.787$ \\
-                \rowcolor{LIGHTGREY} Morocco                                 & Capra hircus          & $ 0.004$ & $ 0.951$ & $ 0.972$ & $ 0.709$ & $ 0.504$ & $ 0.141$ & $ 0.848$ \\
-                Iran           & Ovis aries & $ 0.007$ & $ 0.980$ & $ 0.956$ & $ 0.456$ & $ 0.799$ & $ 0.148$ & $ 0.087$ \\
-                Iran (O. orientalis)  & Ovis aries & $ 0.009$ & $ 0.979$ & $ 0.955$ & $ 0.454$ & $ 0.798$ & $ 0.143$ & $ 0.081$ \\
-                Iran (O. vignei)           & Ovis aries & $ 0.007$ & $ 0.974$ & $ 0.957$ & $ 0.483$ & $ 0.729$ & $ 0.127$ & $ 0.075$ \\
-                Various             & Ovis aries & $ 0.008$ & $ 0.979$ & $ 0.958$ & $ 0.500$ & $ 0.813$ & $ 0.146$ & $ 0.086$ \\
-                Morocco              & Ovis aries & $ 0.008$ & $ 0.980$ & $ 0.952$ & $ 0.392$ & $ 0.774$ & $ 0.145$ & $ 0.082$ \\
-                \rowcolor{LIGHTGREY} Barbados              & Chlorocebus sabaeus & $ 0.004$ & $ 0.880$ & $ 0.984$ & $ 0.854$ & $ 0.354$ & $ 0.170$ & $ 0.968$ \\
-                \rowcolor{LIGHTGREY} Central Afr. Rep.       & Chlorocebus sabaeus & $ 0.006$ & $ 0.932$ & $ 0.968$ & $ 0.634$ & $ 0.413$ & $ 0.156$ & $ 0.334$ \\
-                \rowcolor{LIGHTGREY} Ethiopia        & Chlorocebus sabaeus & $ 0.005$ & $ 0.877$ & $ 0.980$ & $ 0.810$ & $ 0.337$ & $ 0.160$ & $ 0.945$ \\
-                \rowcolor{LIGHTGREY} Gambia             & Chlorocebus sabaeus & $ 0.005$ & $ 0.947$ & $ 0.977$ & $ 0.745$ & $ 0.518$ & $ 0.157$ & $ 0.290$ \\
-                \rowcolor{LIGHTGREY} Kenya                                 & Chlorocebus sabaeus        & $ 0.005$ & $ 0.903$ & $ 0.969$ & $ 0.664$ & $ 0.343$ & $ 0.163$ & $ 0.456$ \\
-                \rowcolor{LIGHTGREY} Nevis                        & Chlorocebus sabaeus        & $ 0.003$ & $ 0.880$ & $ 0.984$ & $ 0.861$ & $ 0.357$ & $ 0.169$ & $ 0.910$ \\
-                \rowcolor{LIGHTGREY} South Africa                              & Chlorocebus sabaeus        & $ 0.006$ & $ 0.931$ & $ 0.967$ & $ 0.615$ & $ 0.401$ & $ 0.153$ & $ 0.329$ \\
-                \rowcolor{LIGHTGREY} Saint Kitts                                & Chlorocebus sabaeus        & $ 0.004$ & $ 0.883$ & $ 0.982$ & $ 0.834$ & $ 0.355$ & $ 0.164$ & $ 0.834$ \\
-                \rowcolor{LIGHTGREY} Zambia                             & Chlorocebus sabaeus        & $ 0.006$ & $ 0.896$ & $ 0.969$ & $ 0.659$ & $ 0.332$ & $ 0.153$ & $ 0.298$ \\
-                African                             & Homo sapiens        & $ 0.002$ & $ 0.946$ & $ 0.971$ & $ 0.630$ & $ 0.486$ & $ 0.141$ & $ 0.123$ \\
-                Admixed American                             & Homo sapiens        & $ 0.002$ & $ 0.929$ & $ 0.972$ & $ 0.636$ & $ 0.410$ & $ 0.161$ & $ 0.182$ \\
-                East Asian                             & Homo sapiens        & $ 0.002$ & $ 0.937$ & $ 0.973$ & $ 0.647$ & $ 0.429$ & $ 0.162$ & $ 0.259$ \\
-                European                             & Homo sapiens        & $ 0.002$ & $ 0.937$ & $ 0.973$ & $ 0.643$ & $ 0.433$ & $ 0.163$ & $ 0.217$ \\
-                South Asian                             & Homo sapiens        & $ 0.002$ & $ 0.939$ & $ 0.972$ & $ 0.639$ & $ 0.439$ & $ 0.163$ & $ 0.219$ \\
+                \rowcolor{LIGHTGREY} Equus c. & Equus caballus & $7.5\times 10^{4}$ & $ 0.911$ & $ 0.974$ & $ 0.645$ & $ 0.319$ & $ 0.163$ & $ 0.334$ \\
+                Iran & Bos taurus & $5.6\times 10^{4}$ & $ 0.895$ & $ 0.973$ & $ 0.639$ & $ 0.288$ & $ 0.133$ & $ 0.283$ \\
+                Uganda & Bos taurus & $1.3\times 10^{5}$ & $ 0.951$ & $ 0.974$ & $ 0.664$ & $ 0.492$ & $ 0.140$ & $ 0.159$ \\
+                \rowcolor{LIGHTGREY} Australia & Capra hircus & $1.7\times 10^{5}$ & $ 0.912$ & $ 0.984$ & $ 0.834$ & $ 0.386$ & $ 0.151$ & $ 0.850$ \\
+                \rowcolor{LIGHTGREY} France & Capra hircus & $1.9\times 10^{5}$ & $ 0.912$ & $ 0.983$ & $ 0.819$ & $ 0.381$ & $ 0.154$ & $ 0.940$ \\
+                \rowcolor{LIGHTGREY} Iran (C. aegagrus) & Capra hircus & $1.9\times 10^{5}$ & $ 0.928$ & $ 0.980$ & $ 0.767$ & $ 0.408$ & $ 0.156$ & $ 0.911$ \\
+                \rowcolor{LIGHTGREY} Iran & Capra hircus & $2.3\times 10^{5}$ & $ 0.955$ & $ 0.969$ & $ 0.616$ & $ 0.459$ & $ 0.147$ & $ 0.943$ \\
+                \rowcolor{LIGHTGREY} Italy & Capra hircus & $1.9\times 10^{5}$ & $ 0.911$ & $ 0.983$ & $ 0.822$ & $ 0.379$ & $ 0.155$ & $ 0.895$ \\
+                \rowcolor{LIGHTGREY} Morocco & Capra hircus & $2.2\times 10^{5}$ & $ 0.950$ & $ 0.976$ & $ 0.706$ & $ 0.468$ & $ 0.150$ & $ 0.627$ \\
+                Iran & Ovis aries & $3.8\times 10^{5}$ & $ 0.983$ & $ 0.958$ & $ 0.421$ & $ 0.796$ & $ 0.154$ & $ 0.090$ \\
+                Iran (O. orientalis) & Ovis aries & $4.5\times 10^{5}$ & $ 0.982$ & $ 0.961$ & $ 0.448$ & $ 0.806$ & $ 0.148$ & $ 0.079$ \\
+                Iran (O. vignei) & Ovis aries & $3.7\times 10^{5}$ & $ 0.974$ & $ 0.963$ & $ 0.480$ & $ 0.685$ & $ 0.151$ & $ 0.086$ \\
+                Various & Ovis aries & $4.1\times 10^{5}$ & $ 0.982$ & $ 0.964$ & $ 0.500$ & $ 0.822$ & $ 0.152$ & $ 0.084$ \\
+                Morocco & Ovis aries & $ 4\times 10^{5}$ & $ 0.983$ & $ 0.958$ & $ 0.387$ & $ 0.782$ & $ 0.153$ & $ 0.081$ \\
+                \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus & $1.1\times 10^{5}$ & $ 0.895$ & $ 0.987$ & $ 0.860$ & $ 0.351$ & $ 0.170$ & $ 0.877$ \\
+                \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus & $1.7\times 10^{5}$ & $ 0.925$ & $ 0.974$ & $ 0.653$ & $ 0.373$ & $ 0.157$ & $ 0.199$ \\
+                \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus & $1.4\times 10^{5}$ & $ 0.892$ & $ 0.980$ & $ 0.763$ & $ 0.320$ & $ 0.161$ & $ 0.640$ \\
+                \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus & $1.4\times 10^{5}$ & $ 0.939$ & $ 0.982$ & $ 0.770$ & $ 0.469$ & $ 0.159$ & $ 0.191$ \\
+                \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus & $1.5\times 10^{5}$ & $ 0.916$ & $ 0.976$ & $ 0.680$ & $ 0.345$ & $ 0.165$ & $ 0.461$ \\
+                \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus & $ 1\times 10^{5}$ & $ 0.895$ & $ 0.989$ & $ 0.884$ & $ 0.358$ & $ 0.169$ & $ 0.908$ \\
+                \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus & $1.8\times 10^{5}$ & $ 0.930$ & $ 0.971$ & $ 0.604$ & $ 0.361$ & $ 0.154$ & $ 0.294$ \\
+                \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus & $1.2\times 10^{5}$ & $ 0.898$ & $ 0.986$ & $ 0.839$ & $ 0.353$ & $ 0.165$ & $ 0.753$ \\
+                \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus & $1.7\times 10^{5}$ & $ 0.912$ & $ 0.975$ & $ 0.676$ & $ 0.335$ & $ 0.153$ & $ 0.406$ \\
+                African & Homo sapiens & $5.6\times 10^{4}$ & $ 0.945$ & $ 0.976$ & $ 0.627$ & $ 0.431$ & $ 0.154$ & $ 0.154$ \\
+                Admixed American & Homo sapiens & $4.5\times 10^{4}$ & $ 0.936$ & $ 0.977$ & $ 0.641$ & $ 0.397$ & $ 0.158$ & $ 0.190$ \\
+                East Asian & Homo sapiens & $ 4\times 10^{4}$ & $ 0.943$ & $ 0.977$ & $ 0.648$ & $ 0.422$ & $ 0.163$ & $ 0.237$ \\
+                European & Homo sapiens & $4.2\times 10^{4}$ & $ 0.945$ & $ 0.977$ & $ 0.644$ & $ 0.429$ & $ 0.167$ & $ 0.219$ \\
+                South Asian & Homo sapiens & $4.4\times 10^{4}$ & $ 0.945$ & $ 0.977$ & $ 0.644$ & $ 0.430$ & $ 0.164$ & $ 0.219$ \\
                 \bottomrule
@@
 
-    Altogether, comparing this table to tables 1 and S3, we acknowledge that the exact proportion of beneficial back-mutations among all beneficial ones is dependent on the model used to estimate the DFE.
+    Altogether, comparing this table other estimations, we acknowledge that the exact proportion of beneficial back-mutations among all beneficial ones is dependent on the model used to estimate the DFE.
     However, we can still see that beneficial back-mutations are positively selected compared to neutral and deleterious ones, and this result is not sensitive to the underlying DFE at the population scale.
 
-    %\section{References}
-    %\printbibliography[heading=none]
+    \newpage
 
-    %    \section{Distribution of fitness effects}
-    %    \captionof{figure}{~}
-    %    \begin{minipage}{0.49\linewidth}
-    %        \includegraphics[width=\linewidth, page=1]{artworks/2bins.Yeast.experimentalDFE.pdf}
-    %    \end{minipage}
-    %    \begin{minipage}{0.49\linewidth}
-    %        \includegraphics[width=\linewidth, page=1]{artworks/2bins.AFR.histogramDFE.pdf}
-    %    \end{minipage}
-    %    Left panel: distribution of fitness effects experimentally determined in Yeast, data obtained in \textcite{shen_synonymous_2022}.
-    %    Right panel:  distribution of fitness effects ($\Sphy$) as predicted with mutation-selection codon models, from reconstructed ancestral genome in \textit{Homo sapiens}.
-    %    The DFE predicted with mutation-selection codon models has a negative mode, consistently with experimental DFEs, meaning that most mutations are effectively deleterious.
+    \newpage
+    \printbibliography
 \end{document}

### 2023-10-11 run_all.sh

@@ -1,7 +1,7 @@
-#!/usr/bin/env bash
-for FILE in config/config_3cat_Onto*.yaml;
+for FILE in config/config_*.yaml;
 do
+  echo "Running ${FILE}"
   cp -f "${FILE}" config/config.yaml
   snakemake --unlock
-  snakemake -j 8 -k --rerun-incomplete
+  snakemake -j 10 -k --rerun-incomplete
 done

### 2023-10-14 manuscript/main-PNAS.tex
Revision manuscript: 2023-08692R

--- 2023-10-11 manuscript/main-revision.tex
@@
-%! BibTeX Compiler = biber
-%TC:ignore
-\documentclass{article}
+\documentclass[9pt,twocolumn,twoside,lineno]{pnas-new}
+% Use the lineno option to display guide line numbers if required.
 
-\usepackage{xcolor, colortbl}
-\definecolor{BLUELINK}{HTML}{0645AD}
-\definecolor{DARKBLUELINK}{HTML}{0B0080}
-\definecolor{LIGHTGREY}{gray}{0.9}
-\PassOptionsToPackage{hyphens}{url}
-\usepackage[colorlinks=false]{hyperref}
-% for linking between references, figures, TOC, etc in the pdf document
-\hypersetup{colorlinks,
-    linkcolor=DARKBLUELINK,
-    anchorcolor=DARKBLUELINK,
-    citecolor=DARKBLUELINK,
-    filecolor=DARKBLUELINK,
-    menucolor=DARKBLUELINK,
-    urlcolor=BLUELINK
-} % Color citation links in purple
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{naturalnames}{hyperref}
-
-\usepackage{biorxiv}
-\usepackage[backend=biber,eprint=false,isbn=false,url=false,intitle=true,style=nature,date=year]{biblatex}
-\addbibresource{codon_models.bib}
-
-\usepackage{url}
 \usepackage{amssymb,amsfonts,amsmath,amsthm,mathtools}
-\usepackage{lmodern}
-\usepackage{xfrac, nicefrac}
 \usepackage{bm}
-\usepackage{listings, enumerate, enumitem}
+\usepackage{makecell}
 \usepackage[export]{adjustbox}
-\usepackage{graphicx}
-\usepackage{bbold}
-\usepackage{pdfpages}
-\pdfinclusioncopyfonts=1
-\usepackage{lineno}
-\usepackage{tabu}
-\usepackage{hhline}
-\usepackage{multicol,multirow,array}
-\usepackage{etoolbox}
-\usepackage{booktabs}
-\usepackage{makecell}
-\usepackage{orcidlink}
-
-\newcommand{\NS}[1]{\textcolor{red}{\textbf{\emph{[NS: #1]}}}}
-
 \newcommand{\UniDimArray}[1]{\bm{#1}}
@@
 \newcommand{\thetaSyn}{\theta_{\text{S}}}
-\renewcommand{\baselinestretch}{1.5}
-\renewcommand{\arraystretch}{0.6}
-\linenumbers
-\frenchspacing
+\definecolor{LIGHTGREY}{gray}{0.9}
+
+\templatetype{pnasresearcharticle} % Choose template 
+% {pnasresearcharticle} = Template for a two-column research article
+% {pnasmathematics} %= Template for a one-column mathematics article
+% {pnasinvited} %= Template for a PNAS invited submission
 
 \title{Mammalian protein-coding genes exhibit widespread beneficial mutations that are not adaptive}
-\rhead{\scshape Beneficial yet non-adaptive mutations}
 
-\author{
-    \large
-    \textbf{T.
-{Latrille}$^{1\dag}$\orcidlink{0000-0002-9643-4668}, J.
-{Joseph}$^{2\dag}$\orcidlink{0009-0002-1312-9930}, D.~A.
-{Hartasánchez}$^{1}$\orcidlink{0000-0003-2596-6883}, N.
-{Salamin}$^{1}$\orcidlink{0000-0002-3963-4954}}\\
-    \normalsize
-    $^{1}$Department of Computational Biology, Université de Lausanne, Lausanne, Switzerland\\
-    $^{2}$Laboratoire de Biométrie et Biologie Evolutive, UMR5558, Université Lyon 1, Villeurbanne, France \\
-    $^{\dag}$These authors contributed equally to this work\\
-    \texttt{\href{mailto:thibault.latrille@ens-lyon.org}{thibault.latrille@ens-lyon.org}} \\
+% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
+\author[1]{T. {Latrille}}
+\author[2]{J. {Joseph}}
+\author[1]{D.~A. {Hartasánchez}}
+\author[1]{N. {Salamin}}
+
+\affil[1]{Department of Computational Biology, Université de Lausanne, Lausanne, Switzerland}
+\affil[2]{Laboratoire de Biométrie et Biologie Evolutive, UMR5558, Université Lyon 1, Villeurbanne, France}
+
+% Please give the surname of the lead author for the running footer
+\leadauthor{Latrille}
+
+% Please add here a significance statement to explain the relevance of your work
+\significancestatement{
+       The extent to which adaptation to changing environments is shaping genomes is a central question in molecular evolution.
+       To quantify the rate of adaptation, population geneticists have typically used signatures of positive selection.
+       However, mutations restoring an ancestral sequence of higher fitness lost by genetic drift are also positively selected, but they do not respond to a change in the environment.
+       In this study, we have managed to distinguish beneficial mutations that are due to changing environments and those that are restoring pre-existing functions in mammals.
+       We show that a substantial proportion of beneficial mutations cannot be interpreted as adaptive.
 }
 
-% The submission checklist is available at:
-% https://docs.google.com/document/d/1SScaqEAgZGpeaXxpWPDh1NOLaDDLLmkGOYgaGvbY-4o/edit#
-% Response to reviewers at:
-% https://docs.google.com/document/d/1kzt4uf6GgmuAVHx6-LQyzFuee9biyaWoMV6RNO6lSzI/edit?usp=sharing
+% Please include corresponding author, author contribution and author declaration information
+\authorcontributions{Original idea: T.L.\ and J.J.;
+Model conception: T.L., J.J.\ and N.S.;
+Code: T.L.;
+Data analyses: T.L.\ and J.J.;
+Interpretation: T.L., J.J., D.A.H.\ and N.S.;
+First draft: T.L.\ and J.J.;
+Editing and revisions: T.L., J.J., D.A.H.\ and N.S.
+Project management and funding: N.S\@.}
+\authordeclaration{The author declares no competing interest.}
+\equalauthors{\textsuperscript{1}T.L. contributed equally to this work with J.J.}
+\correspondingauthor{E-mail: \href{mailto:thibault.latrille@ens-lyon.org}{thibault.latrille@ens-lyon.org}}
 
-\begin{document}
-    \maketitle
+% Keywords are not mandatory, but authors are strongly encouraged to provide them. If provided, please include two to five keywords, separated by the pipe symbol, e.g:
+\keywords{Adaptation $|$ Back-mutations $|$ Phylogenetics $|$ Population-genetics $|$ Codon models }
 
-%TC:endignore
 \begin{abstract}
@@
 Using methods that quantify selection at the population level, we have confirmed that beneficial back-mutations are indeed positively selected in extant populations.
+Our work confirms that deleterious substitutions are accumulating in mammals and are being reverted, generating a balance in which genomes are damaged and restored simultaneously at different loci.
 We observe that beneficial back-mutations represent between 15\% and 45\% of all beneficial mutations in 24 of 28 populations analyzed, showing that a substantial part of ongoing positive selection is not driven by adaptation to environmental change in mammals.
-Our work shows that deleterious substitutions are accumulating in mammals and are being reverted, generating a balance in which genomes are damaged and restored simultaneously at different loci, ultimately resulting in a widespread signal of non-adaptive positive selection.
 \end{abstract}
 
-    \keywords{Adaptation \and Back-mutations \and Phylogenetics \and Population-genetics \and Codon models }
+\dates{This manuscript was compiled on \today}
+\doi{\url{www.pnas.org/cgi/doi/10.1073/pnas.XXXXXXXXXX}}
 
-    \section*{Significance statement}
-    The extent to which adaptation to changing environments is shaping genomes is a central question in molecular evolution.
-To quantify the rate of adaptation, population geneticists have typically used signatures of positive selection.
-However, mutations restoring an ancestral sequence of higher fitness lost by genetic drift are also positively selected, but they do not respond to a change in the environment.
-In this study, we have managed to distinguish beneficial mutations that are due to changing environments and those that are restoring pre-existing functions in mammals.
-We show that a substantial proportion of beneficial mutations cannot be interpreted as adaptive.
+\begin{document}
 
-    \section*{Introduction}
-    Adaptation is one of the main processes shaping the diversity of forms and functions across the tree of life~\cite{darwin_origin_1859}.
+\maketitle
+\thispagestyle{firststyle}
+\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}
+
+\firstpage[3]{3}
+\dropcap{A}daptation is one of the main processes shaping the diversity of forms and functions across the tree of life~\cite{darwin_origin_1859}.
 Evolutionary adaptation is tightly linked to environmental change and species responding to this change~\cite{merrell_adaptive_1994, gavrilets_adaptive_2009}.
@@
 These approaches, now common practice in evolutionary biology, have helped better understand the processes underpinning the rates of molecular evolution, contributing to disentangling the effects of mutation, selection and drift in evolution~\cite{lynch_mutation_2023}.
-    However, a collateral effect has been conflating beneficial mutations with adaptive evolution when adaptive evolution is not the only process that can lead to beneficial mutations~\cite{charlesworth_other_2007, mustonen_fitness_2009}.
+However, a collateral effect has been conflating beneficial mutations with adaptive evolution when adaptive evolution is not the only process that can lead to beneficial mutations~\cite{charlesworth_other_2007, mustonen_fitness_2009, jones_shifting_2017}.
 
@@
 While compensatory mutations change the sequence and thus induce genetic diversification, beneficial back-mutations reduce genetic diversity and do not contribute to genetic innovation.
-    Although Tomoko Ohta considered beneficial back-mutations negligible in her nearly-neutral theory~\cite{Ohta1992}, their importance has now been acknowledged for expanding populations~\cite{charlesworth_other_2007}.
+
+Although Tomoko Ohta considered beneficial back-mutations negligible in her nearly-neutral theory~\cite{Ohta1992}, their importance has now been acknowledged for
+expanding populations~\cite{charlesworth_other_2007}.
 However, differentiating between an adaptive mutation and a beneficial back-mutation remains challenging~\cite{chi_detecting_2020}.
@@
 On the other hand, beneficial back-mutations are predictable because, under a stable fitness landscape, any change from non-optimal to optimal amino acids will move back the site towards the equilibrium expected under the fitness landscape~\cite{moses_inferring_2009, fischer_germline_2011, chen_hunting_2021}.
-    It can then be distinguished from truly novel beneficial mutations because the latter are not expected to mutate towards amino-acids of higher fitnesses defined by the stable fitness landscape.
+It can then be distinguished from truly novel beneficial mutations because the latter are not expected to mutate mutate towards the amino acids of higher fitnesses defined by the stable fitness landscape but rather mutate to amino acids showing a diversified pattern (fig.~\ref{fig:fitness-landscape}).
+
+\begin{figure*}[htb]
+       \centering
+       \includegraphics[width=17.8cm, page=1]{figure1}
+       \caption{
+              (A \& B) For a given codon position of a protein-coding DNA sequence, amino acids (x-axis) have different fitness values (y-axis).
+              Under a fluctuating fitness landscape (A), these fitnesses change with time.
+              The protein sequence follows the moving target defined by the amino-acid fitnesses.
+Since substitutions are preferentially accepted if they are in the direction of this target, substitutions are, on average, adaptive.
+              At the phylogenetic scale (C), beneficial substitutions are common (positive signs), promoting phenotype diversification across species.
+              Under a stable fitness landscape (B), most mutations reaching fixation are either slightly deleterious reaching fixation due to drift or are beneficial back-mutations restoring a more optimal amino acid.
+              At the phylogenetic scale (D), deleterious substitutions (negative signs) are often reverted via beneficial back-mutations (positive signs), promoting phenotype stability and preserving well-established biological systems.
+              Even though, individually, any back-mutation might have a small beneficial effect on its bearer, we expect beneficial back-mutations to be scattered across the genome and the genome-wide signature of beneficial back-mutations to be detectable and quantifiable.}
+       \label{fig:fitness-landscape}
+\end{figure*}
+
+\begin{figure*}[htb]
+       \centering
+       \includegraphics[width=17.8cm, page=1]{figure2}
+       \caption{
+              Selection coefficients at the phylogenetic and population scales.
+              At the phylogenetic scale (A), we estimated the amino-acid fitness for each site from protein-coding DNA alignments using mutation-selection codon models.
+              For every possible mutation, the difference in amino-acid fitness before and after the mutation allows us to compute the selection coefficient at the phylogenetic scale ($\Sphy$).
+              Depending on $\Sphy$ (B) mutations can be predicted as deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) or beneficial back-mutations ($\SphyBen$) toward a fitter amino acid and repairing existing functions.
+              At the population scale, each observed single nucleotide polymorphism (SNP) segregating in the population can also be classified according to its $\Sphy$ value (C).
+              Occurrence and frequency in the population of non-synonymous polymorphisms, contrasted to synonymous polymorphisms (deemed neutral) is used to estimate selection coefficients (D-E) at the population scale ($\Spop$), for each class of selection ($\SphyDel$, $\SphyNeu$, $\SphyBen$).
+              We can thus assess whether $\Sphy$ predicts $\Spop$ and compute \textit{precision} (F) and \textit{recall} (G) for each class.
+              The \textit{recall} value for class $\SphyBen$ is the probability of back-mutations among all beneficial ones (G).
+       }
+       \label{fig:method}
+\end{figure*}
 
@@
 
-    The mutation-selection framework permits to link the patterns of substitution along a phylogeny with the underlying fitness landscape~\cite{halpern_evolutionary_1998, mccandlish_modeling_2014}.
-    Such mutation-selection models applied to protein-coding DNA sequences allow us to estimate relative fitnesses for all amino acids for each site of the sequence, explicitly assuming that the underlying fitness landscape is stable along the phylogenetic tree~\cite{rodrigue_mechanistic_2010, tamuri_estimating_2012, rodrigue_detecting_2017}.
-    Moreover, because our model assumes a fixed landscape, it implicitly assumes that $\Ne$ is constant along the phylogeny.
-    The consequences of this assumption are discussed below.
-    Importantly, because mutation-selection models at the phylogenetic scale are based on population-genetics equations, their estimates of selection coefficients are directly interpretable as fitness effects at the population scale.
-    Moreover, because mutation-selection models work at the DNA level, we are able to account for mutational bias in DNA and structure of the genetic code.
-    The model further integrates the shared evolutionary history between samples and their divergence, which, together, allow us to estimate fitness effect in mammalian phylogenies even though sequences are not independent samples and might not represent the equilibrium distribution of amino acids (see section \ref{subsec:s-phylogeny-method} in Materials \& Methods, model parameters in section S1).
+The mutation-selection framework permits to link the patterns of substitution along a phylogenetic tree with the underlying fitness landscape~\cite{halpern_evolutionary_1998, mccandlish_modeling_2014}.
+Such mutation-selection models applied to protein-coding DNA sequences at the codon level allow us to estimate relative fitnesses for all amino acids for each site of the sequence, explicitly assuming that the underlying fitness landscape is stable along the phylogenetic tree~\cite{rodrigue_mechanistic_2010, tamuri_estimating_2012, rodrigue_detecting_2017}.
+Moreover, effective population size ($\Ne$) is considered constant along the phylogenetic tree precisely because of the fixed fitness landscape assumption, the consequences of which are detailed in the Discussion.
+Importantly, because mutation-selection codon models at the phylogenetic scale are based on population-genetics equations, their estimates of selection coefficients are directly interpretable as fitness effects at the population scale; and because they work at the DNA level, we are able to account for mutational bias in DNA and structure of the genetic code.
+The model further integrates the shared evolutionary history between samples and their divergence, which, together, allow us to estimate fitness effects in mammalian phylogenetic trees even though sequences are not independent samples and might not represent the equilibrium distribution of amino acids (see section \ref{subsec:s-phylogeny-method} in Materials \& Methods, model parameters in section S1).
 
@@
 Additionally, polymorphism data are available for many species~\cite{howe_ensembl_2021}, as are high quality protein-coding DNA alignments across the genome~\cite{ranwez_orthomam_2007, scornavacca_orthomam_2019}.
-    By performing our analysis on 14,509 orthologous protein-coding genes across 87 species, , we focus on genes shared across all mammals in our dataset and not newly functionalized genes in a lineage.
-    This filtering does in fact bias the selection of genes towards genes which can better fit the stable fitness landscape assumption.
+By performing our analysis on 14,509 orthologous protein-coding genes across 87 species, we focus on genes shared across all mammals in our dataset and not newly functionalized genes in a lineage.
+
 For each gene, fitting the mutation-selection model to the multi-species sequence alignment, assuming that the underlying fitness landscape is stable along the phylogenetic tree, allows us to obtain relative fitnesses for all amino acids for each site of the alignment (fig.~\ref{fig:method}A).
-    Given these relative fitnesses ($F$) for each amino acid, the difference in fitness between a pair of amino acids is the scaled selection coefficient ($\Sphy = \Delta F$).
-    Such scaled selection coefficients ($\Sphy$) are formally the product of the selection coefficient at the individual level ($s$) and the effective population size ($\Ne$), as $\Sphy = 4 \Ne \times s$, and inform us on the strength of selection exerted on amino acids changes.
+Given these relative fitnesses ($F$) for each amino acid, the difference in fitness between a pair of amino acids is the scaled selection coefficient ($\Sphy = \Delta F$), which is formally the product of the selection coefficient at the individual level ($s$) and the effective population size ($\Ne$), as $\Sphy = 4 \Ne \times s$.
+The value of $\Sphy$ informs us on the strength of selection exerted on amino acids changes.
 Thus, according to its $\Sphy$ value, we can classify any mutation as either a deleterious mutation toward a less fit amino acid ($\SphyDel \coloneqq \Sphy < -1$), a nearly-neutral mutation ($\SphyNeu \coloneqq -1 < \Sphy <1$) or a beneficial back-mutation toward a known fitter amino acid ($\SphyBen \coloneqq \Sphy > 1$).
@@
 A similar approach demonstrated the presence of beneficial back-mutations in humans~\cite{moses_inferring_2009, fischer_germline_2011} and in plants~\cite{chen_hunting_2021}.
-    However, the model used to reconstruct the static fitness landscape in these studies can only be applied to deeply conserved protein domains in the tree of life, which corresponds to the subpart of the proteome that evolves slowly.
-    The mutation-selection model used in the present work integrates phylogenetic relationships, and thus allows us to estimate the fitness landscape in shallower phylogenies, and therefore can be applied almost genome-wide~\cite{rodrigue_mutationselection_2010}.
-    Moreover, because our model works at the DNA and codon level instead of the amino acid level, an estimation of genome-wide contribution of beneficial-back mutations to positive selection across populations is accessible.
-    More precisely, we first quantified the likelihood of any DNA mutation to be a beneficial back-mutation, meaning whenever a DNA mutation increases fitness under a stable fitness landscape ($\SphyBen$).
+However, the model used to reconstruct the static fitness landscape in these studies can only be applied to deeply conserved protein domains in the tree of life, which corresponds to a subpart of the proteome that evolves slowly.
+The mutation-selection model used in the present work integrates phylogenetic relationships, and thus allows us to estimate the fitness landscape in shallower phylogenetic trees, and therefore can be applied almost genome-wide~\cite{rodrigue_mutationselection_2010}.
+
+We first quantified the likelihood of any DNA mutation to be a beneficial back-mutation, that is, whenever a DNA mutation increases fitness under a stable fitness landscape ($\SphyBen$).
 Subsequently, by quantifying the total amount of beneficial mutations in the current population across all types of DNA mutations ($\SphyDel$, $\SphyDel$ and $\SphyBen$), we could tease apart beneficial back-mutations from beneficial adaptive mutations resulting from a change in the fitness landscape.
@@
 
-    \section*{Results}
+\section*{Results}\label{sec:results}
 
@@
 We classified each substitution identified in the terminal branches as either $\SphyDel$, $\SphyNeu$, or $\SphyBen$ depending on its $\Sphy$ value obtained at the phylogenetic scale (fig.~\ref{fig:method}A-C).
-    Importantly, the mammalian alignment used to estimate the amino acid fitness landscape did not include the genera for which we estimated selection at the population scale as this would bias the estimate of the fitness landscape and generate circular reasoning.
-    Because $\Sphy$ was based on estimating fitness effects at the phylogenetic scale for all mammals, substitutions with $\Sphy>1$ ($\SphyBen$) bring the population toward an amino acid which is predicted to be fitter in mammals and are thus considered as beneficial back-substitutions rather than a species-specific adaptive change.
+Importantly, the mammalian alignment used to estimate the amino-acid fitness landscape did not include the genera for which we estimated selection at the population scale as this would bias the estimate of the fitness landscape and generate circular reasoning.
+Because $\Sphy$ was based on estimating fitness effects at the phylogenetic scale for all mammals, substitutions with $\Sphy>1$ ($\SphyBen$) bring the population toward an amino acid predicted to be fitter in mammals.
+These changes are thus considered as beneficial back-substitutions rather than a species-specific adaptive change.
 Among all the substitutions found in each terminal branch, between 10 and 13\% were $\SphyBen$, while instead beneficial back-mutations represent between 0.9 and 1.2\% of all non-synonymous mutations (table~S1 and fig.~\ref{fig:homo-afr-results}A-B for humans).
@@
 Across 28 populations of different mammal species, mutations predicted to be deleterious at the phylogenetic scale ($\ProbaPopDel$) were indeed purged at the population scale, with a \textit{precision} in the range of 90--97\% (table~\ref{table:proba} and fig.~\ref{fig:homo-afr-results}D for humans).
-    Conversely, a \textit{recall} in the range of 96--100\% implies that mutations found to be deleterious at the population scale were most likely also predicted to be deleterious at the phylogenetic scale (table~\ref{table:proba}).
+Conversely, a \textit{recall} in the range of 96--100\% implied that mutations found to be deleterious at the population scale were most likely also predicted to be deleterious at the phylogenetic scale (table~\ref{table:proba}).
 Altogether, purifying selection is largely predictable and amino acids with negative fitness across mammals have been effectively purged away in each population.
@@
 The variable proportions between populations can be explained by the effective number of individuals in the population ($\Ne$), a major driver of selection efficacy.
-    Moreover, estimates of mutation rate per generation ($u$), from \textcite{bergeron_evolution_2023} and \textcite{orlando_recalibrating_2013}, and Watterson’s $\theta$ obtained from the synonymous SFS as in \textcite{achaz_frequency_2009} allow us to obtain $\Ne$ through $\Ne=\theta/(4 \times u)$.
+Moreover, estimates of mutation rate per generation ($u$), from \cite[Bergeron et al]{bergeron_evolution_2023} and \cite[Orlando et al]{orlando_recalibrating_2013}, and Watterson’s $\theta$ obtained from the synonymous SFS as in \cite[Achaz]{achaz_frequency_2009} allow us to obtain $\Ne$ through $\Ne=\theta/(4 \times u)$.
 Using correlation analyses that accounted for phylogenetic relationship (see section \ref{subsec:correlation-diversity} in Materials \& Methods), we found that higher $\Ne$ was associated with a smaller proportion of nearly-neutral mutations ($r^2=0.31$, $p=0.001$, fig.~\ref{fig:diversity}A).
@@
 
-    Because the back-mutation equilibrium model should fit better for genes with uniformly conserved functions, as a control, we filtered out genes under adaptation \cite{latrille_genes_2023}, and indeed we found an increase in the proportion of beneficial back-mutations ($\proba [ \SphyBen  \given  \SpopBen]$), consistent with our expectation (Wilcoxon signed-rank, $s=80$, $p=0.002$, table~S7).
+Because the phylogenetic mutation-selection codon model should fit better for genes with uniformly conserved functions, as a control, we filtered out genes under pervasive adaptation~\cite{latrille_genes_2023}, and indeed we found an increase in the proportion of beneficial back-mutations ($\proba [ \SphyBen  \given  \SpopBen]$), consistent with our expectation (Wilcoxon signed-rank, $s=80$, $p=0.002$, table~S7).
 
-    \section*{Discussion}
+\begin{figure*}[htb]
+       \centering
+       \includegraphics[width=17.8cm, page=1]{figure3}
+       \caption{
+              (A) Distribution of scaled selection coefficients ($\Sphy$), predicted for all possible non-synonymous DNA mutations away from the ancestral human exome (section \ref{subsec:nunber-of-sites}).
+              Mutations are divided into three classes of selection: deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial ($\SphyBen$, supposedly beneficial back-mutations)
+              (B) Distribution of scaled selection coefficients ($\Sphy$) for all observed substitutions along the \textit{Homo} branch after the \textit{Homo}-\textit{Pan} split (section \ref{subsec:substitution-mapping-in-the-terminal-branch}).
+              If there are fewer substitutions than expected, this class is thus undergoing purifying selection, as is the case for $\SphyDel$.
+              (C) The site-frequency spectrum (SFS) in humans of African descent for a random sample of 16 alleles (means in solid lines and standard deviations in color shades) for each class of selection and for synonymous mutations, supposedly neutral (black).
+The SFS represents the proportion of mutations (y-axis) with a given number of derived alleles in the population (x-axis).
+              At high frequencies, deleterious mutations are underrepresented.
+              (D) Proportion of beneficial $\ProbaPopDel$, nearly-neutral $\ProbaPopNeu$, and deleterious mutations $\ProbaPopBen$ estimated at the population scale for each class of selection at the phylogenetic scale (section \ref{subsec:s-polymorphism-method}).
+Proportions depicted here are not weighted by their mutational opportunities.
+       }
+       \label{fig:homo-afr-results}
+\end{figure*}
+
+\begin{table*}[tb]
+       \centering
+       \begin{adjustbox}{width=17.8cm}
+              \begin{tabular}{||l|l|r||r|r||r|r||r|r||}
+                     \toprule
+                     \multicolumn{3}{||c||}{} &
+                     \multicolumn{2}{c||}{\shortstack{\textbf{Deleterious mutations} \\ $\bm{\SpopDel \coloneqq \Spop<-1}$ \\ $\bm{\SphyDel \coloneqq \Sphy<-1}$}} &
+                     \multicolumn{2}{c||}{\shortstack{\textbf{Nearly-neutral mutations} \\ $\bm{\SpopNeu \coloneqq -1<\Spop<1}$ \\ $\bm{\SphyNeu \coloneqq -1<\Sphy<1}$}} &
+                     \multicolumn{2}{c||}{\shortstack{\textbf{Beneficial mutations} \\ $\bm{\SpopBen \coloneqq \Spop>1}$ \\ $\bm{\SphyBen \coloneqq \Sphy>1}$}}
+                     \\ \hline
+                     \textbf{Population} &
+                     \textbf{Species} &
+                     $\bm{\Ne}$ &
+                     \makecell{\textbf{Precision} \\ $\bm{\proba [\SpopDel \given \SphyDel]}$} &
+                     \makecell{\textbf{Recall} \\ $\bm{\proba [\SphyDel \given \SpopDel]}$}            &
+                     \makecell{\textbf{Precision}      \\ $\bm{\proba [\SpopNeu \given \SphyNeu]}$}                                    &
+                     \makecell{\textbf{Recall}          \\ $\bm{\proba [\SphyNeu \given \SpopNeu]}$}                                  &
+                     \makecell{\textbf{Precision}          \\ $\bm{\proba [\SpopBen \given \SphyBen]}$}          &
+                     \makecell{\textbf{Recall}        \\ $\bm{\proba [\SphyBen \given \SpopBen]}$}
+                     \\   \midrule
+                     \rowcolor{LIGHTGREY} Equus c. & Equus caballus & $7.5\times 10^{4}$ & $ 0.923$ & $ 0.972$ & $ 0.570$ & $ 0.341$ & $ 0.648$ & $ 0.536$ \\
+                     Iran & Bos taurus & $5.6\times 10^{4}$ & $ 0.915$ & $ 1.000$ & $ 0.632$ & $ 0.358$ & $ 0.873$ & $ 0.243$ \\
+                     Uganda & Bos taurus & $1.3\times 10^{5}$ & $ 0.951$ & $ 0.969$ & $ 0.495$ & $ 0.414$ & $ 0.576$ & $ 0.415$ \\
+                     \rowcolor{LIGHTGREY} Australia & Capra hircus & $1.7\times 10^{5}$ & $ 0.944$ & $ 0.971$ & $ 0.527$ & $ 0.437$ & $ 0.368$ & $ 0.177$ \\
+                     \rowcolor{LIGHTGREY} France & Capra hircus & $1.9\times 10^{5}$ & $ 0.946$ & $ 0.971$ & $ 0.508$ & $ 0.423$ & $ 0.368$ & $ 0.190$ \\
+                     \rowcolor{LIGHTGREY} Iran (C. aegagrus) & Capra hircus & $1.9\times 10^{5}$ & $ 0.948$ & $ 0.969$ & $ 0.486$ & $ 0.444$ & $ 0.368$ & $ 0.165$ \\
+                     \rowcolor{LIGHTGREY} Iran & Capra hircus & $2.3\times 10^{5}$ & $ 0.953$ & $ 0.966$ & $ 0.425$ & $ 0.407$ & $ 0.368$ & $ 0.193$ \\
+                     \rowcolor{LIGHTGREY} Italy & Capra hircus & $1.9\times 10^{5}$ & $ 0.947$ & $ 0.971$ & $ 0.551$ & $ 0.439$ & $ 0.368$ & $ 0.243$ \\
+                     \rowcolor{LIGHTGREY} Morocco & Capra hircus & $2.2\times 10^{5}$ & $ 0.950$ & $ 0.970$ & $ 0.527$ & $ 0.440$ & $ 0.368$ & $ 0.245$ \\
+                     Iran & Ovis aries & $3.8\times 10^{5}$ & $ 0.961$ & $ 0.961$ & $ 0.452$ & $ 0.415$ & $ 0.205$ & $ 0.407$ \\
+                     Iran (O. orientalis) & Ovis aries & $4.5\times 10^{5}$ & $ 0.964$ & $ 0.960$ & $ 0.420$ & $ 0.445$ & $ 0.193$ & $ 0.190$ \\
+                     Iran (O. vignei) & Ovis aries & $3.7\times 10^{5}$ & $ 0.967$ & $ 0.959$ & $ 0.361$ & $ 0.470$ & $ 0.190$ & $ 0.110$ \\
+                     Various & Ovis aries & $4.1\times 10^{5}$ & $ 0.962$ & $ 0.962$ & $ 0.433$ & $ 0.440$ & $ 0.229$ & $ 0.222$ \\
+                     Morocco & Ovis aries & $ 4\times 10^{5}$ & $ 0.962$ & $ 0.961$ & $ 0.462$ & $ 0.424$ & $ 0.211$ & $ 0.514$ \\
+                     \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus & $1.1\times 10^{5}$ & $ 0.935$ & $ 0.975$ & $ 0.565$ & $ 0.402$ & $ 0.648$ & $ 0.293$ \\
+                     \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus & $1.7\times 10^{5}$ & $ 0.948$ & $ 0.971$ & $ 0.508$ & $ 0.423$ & $ 0.535$ & $ 0.275$ \\
+                     \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus & $1.4\times 10^{5}$ & $ 0.935$ & $ 0.975$ & $ 0.580$ & $ 0.416$ & $ 0.552$ & $ 0.245$ \\
+                     \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus & $1.4\times 10^{5}$ & $ 0.944$ & $ 0.975$ & $ 0.654$ & $ 0.437$ & $ 0.577$ & $ 0.821$ \\
+                     \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus & $1.5\times 10^{5}$ & $ 0.946$ & $ 0.972$ & $ 0.538$ & $ 0.453$ & $ 0.588$ & $ 0.257$ \\
+                     \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus & $ 1\times 10^{5}$ & $ 0.933$ & $ 0.976$ & $ 0.629$ & $ 0.412$ & $ 0.599$ & $ 0.358$ \\
+                     \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus & $1.8\times 10^{5}$ & $ 0.944$ & $ 0.971$ & $ 0.548$ & $ 0.423$ & $ 0.574$ & $ 0.341$ \\
+                     \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus & $1.2\times 10^{5}$ & $ 0.936$ & $ 0.975$ & $ 0.586$ & $ 0.402$ & $ 0.598$ & $ 0.336$ \\
+                     \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus & $1.7\times 10^{5}$ & $ 0.945$ & $ 0.971$ & $ 0.512$ & $ 0.432$ & $ 0.585$ & $ 0.250$ \\
+                     African & Homo sapiens & $5.6\times 10^{4}$ & $ 0.911$ & $ 0.976$ & $ 0.579$ & $ 0.325$ & $ 0.721$ & $ 0.349$ \\
+                     Admixed American & Homo sapiens & $4.5\times 10^{4}$ & $ 0.902$ & $ 0.978$ & $ 0.584$ & $ 0.299$ & $ 0.690$ & $ 0.345$ \\
+                     East Asian & Homo sapiens & $ 4\times 10^{4}$ & $ 0.905$ & $ 0.978$ & $ 0.585$ & $ 0.325$ & $ 0.688$ & $ 0.249$ \\
+                     European & Homo sapiens & $4.2\times 10^{4}$ & $ 0.906$ & $ 0.978$ & $ 0.584$ & $ 0.329$ & $ 0.688$ & $ 0.248$ \\
+                     South Asian & Homo sapiens & $4.4\times 10^{4}$ & $ 0.908$ & $ 0.978$ & $ 0.584$ & $ 0.342$ & $ 0.691$ & $ 0.224$ \\
+                     \bottomrule
+              \end{tabular}
+       \end{adjustbox}
+       \caption{
+              \textit{Precision} and \textit{recall} for estimated selection coefficient of mutations given by mutation-selection models ($\Sphy$).
+              \textit{Precision} is the estimation of the selection coefficient at population scale ($\Spop$) given that $\Sphy$ is known.
+              Conversely, \textit{recall} is the estimation of $\Sphy$ given selection coefficient at the population scale ($\Spop$) is known.
+              \textit{Recall} for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is thus the proportion of beneficial back-mutations among all beneficial mutations.
+              $\Ne$ is the estimated effective population size for each population.
+       }
+       \label{table:proba}
+\end{table*}
+
+\begin{figure*}[htb]
+       \centering
+       \includegraphics[width=17.8cm, page=1]{figure4}
+       \caption{
+              Populations in circles, mean of the species across the populations as squares.
+              (A) Proportion of nearly-neutral mutations at the population scale ($\proba [ \SpopNeu]$ in the y-axis), shown as a function of estimated effective population size ($\Ne$ in the x-axis).
+              (B) Proportion of beneficial back-mutations among all beneficial mutations ($\proba [ \SphyBen  \given  \SpopBen]$ in the y-axis), shown as a function of $\Ne$ in x-axis.
+              Correlations account for phylogenetic relationship and non-independence of samples, through the fit of a Phylogenetic Generalized Linear Model (see section~\ref{subsec:s-polymorphism-method} in Materials \& Methods).
+       }
+       \label{fig:diversity}
+\end{figure*}
+
+\section*{Discussion}\label{sec:discussion}
+
 \subsection*{Beneficial mutations are not necessarily adaptive}
@@
 In particular, we have been able to quantify the proportion of beneficial back-mutations among all beneficial mutations, which has only been achievable by combining genome-wide data from both phylogenetic and population scales.
-    At the phylogenetic scale, codon diversity at each site of a protein-coding DNA alignment allows for reconstructing an amino acid fitness landscape, assuming that this landscape is stable along the phylogeny.
+At the phylogenetic scale, codon diversity at each site of a protein-coding DNA alignment allows for reconstructing an amino-acid fitness landscape, assuming that this landscape is stable along the phylogenetic tree.
 These amino-acid fitness landscapes allow us to predict any mutation’s selection coefficient ($\Sphy$) along a protein-coding sequence.
@@
 We have tested this hypothesis and found that these back-mutations ($\SphyBen \coloneqq \Sphy > 1 $) are indeed beneficial in extant populations.
-    We estimated that between 11 and 82\% of all beneficial mutations in mammalian populations have not been driven by adaptation but instead have reversed deleterious substitutions which have accumulated along the phylogeny.
+We estimated that between 11 and 82\% of all beneficial mutations in mammalian populations have not been driven by adaptation but instead have reversed deleterious substitutions which have accumulated along the phylogenetic tree.
 More specifically, in 24 out of 28 populations analyzed, the percentage of beneficial mutations estimated to be back-mutations falls between 15 and 45\%.
@@
 
-    Our model assumes that amino-acid fitness landscapes are site-specific and also independent of one another, whereas under pervasive epistasis, the fitness effect of any mutation at a particular site would depend on the amino-acids present at other sites.
+Our model assumes that amino-acid fitness landscapes are site-specific and also independent of one another, whereas under pervasive epistasis, the fitness effect of any mutation at a particular site would depend on the amino acids present at other sites.
 Epistasis has been shown to play a role in the evolution of protein-coding genes, with amino-acid residues in contact within a protein or between proteins tending to co-evolve~\cite{morcos_directcoupling_2011, marks_protein_2012, starr_epistasis_2016}.
 Particularly, the residues in contact co-evolve to become more compatible with each other generating an entrenchment~\cite{goldstein_nonadaptive_2015, goldstein_sequence_2017, park_epistatic_2022}.
-    Epistasis therefore allows for compensatory mutations, which restore fitness through mutations at loci different from where deleterious mutations take place, representing, hence, another case of non-adaptive beneficial mutations, but one which is not accounted for by our method.
-    Therefore, many of the beneficial mutations that we classify as putatively adaptive might in fact be compensatory mutations, making our estimation of the rate of non-adaptive beneficial mutations conservative.
+Epistasis therefore allows for compensatory mutations, which restore fitness through mutations at loci different from where deleterious mutations took place.
+It therefore, represents another case case of non-adaptive beneficial mutations, but one which is not accounted for by our method.
+Therefore, the beneficial mutations that we classify as putatively adaptive might in fact be compensatory mutations, making our estimation of the rate of non-adaptive beneficial mutations conservative.
 
 Despite epistasis being an important factor in protein evolution, several deep mutational scanning laboratory experiments have revealed that a site-specific fitness landscape is a reasonable approximation of the fitness landscape of proteins, and even predicts the evolution of sequences in nature~\cite{ashenberg_mutational_2013, doud_sitespecific_2015, bloom_identification_2017}.
-    Additionally, the fact that we observe such a high proportion of beneficial back-mutations suggests that the underlying assumptions of our model, namely site-independence, implying no epistasis, and a static fitness landscape, are a reasonable approximation for the underlying fitness landscape of proteins~\cite{youssef_consequences_2020}.
-    Our results imply that the fitness effects of new mutations are mostly conserved across mammalian orthologs, in agreement with other studies showing that for conserved orthologs with similar structures and functions, models without epistasis provide a reasonable estimate of fitness effects in protein coding genes~\cite{ashenberg_mutational_2013, doud_sitespecific_2015, bloom_identification_2017, youssef_consequences_2020}.
+Additionally, the fact that we observe such a high proportion of beneficial back-mutations suggests that the underlying assumptions of our model, namely site-independence, implying no epistasis, and a static fitness landscape, are a reasonable approximation for the underlying fitness landscape of proteins.
+Our results imply that the fitness effects of new mutations are mostly conserved across mammalian orthologs, in agreement with other studies showing that for conserved orthologs with similar structures and functions, models without epistasis provide a reasonable estimate of fitness effects in protein coding genes~\cite{youssef_consequences_2020, vigue_deciphering_2022}.
 
-    Moreover, because our model assumes a fixed landscape, it implicitly assumes that $\Ne$ is constant along the phylogeny.
+Moreover, because our model assumes a fixed landscape, it implicitly assumes that $\Ne$ is constant along the phylogenetic tree.
 Fluctuations due to changes in the fitness landscape or in $\Ne$ will be averaged out by the assumption of the current model that $\Ne$ is constant across lineages.
-    It was recently shown~\cite{latrille_inferring_2021}, using highly computer intensive mutation-selection models with fluctuating $\Ne$, that relaxing the assumption of a constant $\Ne$ results in more extreme estimates of amino-acid fitnesses than with the standard model used in the present study.
-    In other words, by assuming a constant $\Ne$, we are underpowered to detect beneficial back-mutations since amino-acids will have more similar fitnesses and mutations that would otherwise fall into $\SpopBen$ or $\SpopDel$ will be classified as $\SpopNeu$, resulting ultimately in lower estimates of the proportion of beneficial back-mutations ($\proba [ \SphyBen  \given  \SpopBen]$).
-    Given this inflation of missed predictions due to change in population sizes~\cite{lanfear_population_2014, jones_shifting_2017, platt_protein_2018}, our estimated proportion of beneficial back-mutations among adaptive ones is likely to be an underestimation.
+It was recently shown~\cite{latrille_inferring_2021}, using highly computer intensive mutation-selection models with fluctuating $\Ne$, that relaxing the assumption of a constant $\Ne$ results in more extreme estimates of amino-acid fitnesses than with the standard model used in this study.
+In other words, by assuming a constant $\Ne$, we are underpowered to detect beneficial back-mutations since amino acids will have more similar fitnesses.
+As a consequence, mutations that would otherwise fall into $\SpopBen$ or $\SpopDel$ will be classified as $\SpopNeu$, resulting ultimately in lower estimates of the proportion of beneficial back-mutations ($\proba [ \SphyBen  \given  \SpopBen]$).
+Given this inflation of missed predictions due to change in population sizes~\cite{lanfear_population_2014, jones_shifting_2017, platt_protein_2018}, our estimated proportion of beneficial back-mutations among adaptive ones is likely to therefore be an underestimation.
 In practice, advantageous mutations can be depleted in the $\SphyNeu$ and $\SphyDel$ class in some species but pervasive in others, depending on the model used to infer the DFE at the population scale (tables~S8-12).
@@
 
-    \section{Materials \& Methods}
-    \label{sec:methods}
+%TC:ignore
+\section{Author information}\label{sec:author-information}
+TL, NR and NL designed the study.
+TL gathered and formatted the data and conducted the analyses with \texttt{BayesCode} using scripts in \texttt{Python} and pipeline in \texttt{Snakemake}.
+TL, NR and NL contributed to the writing of the manuscript.
 
+\matmethods{
        \subsection{Phylogenetic dataset}\label{subsec:phylo-dataset}
 
-    Protein-coding DNA sequence alignments in placental mammals and their corresponding gene trees come from the \href{https://www.orthomam.univ-montp2.fr}{OrthoMaM} database and were processed as in \textcite{latrille_genes_2023}.
+       Protein-coding DNA sequence alignments in placental mammals and their corresponding gene trees come from the \href{https://www.orthomam.univ-montp2.fr}{OrthoMaM} database and were processed as in \cite[Latrille et al]{latrille_genes_2023}.
        OrthoMaM contains a total of $116$ mammalian reference sequences in v10c~\cite{ranwez_orthomam_2007, douzery_orthomam_2014, scornavacca_orthomam_2019}.
@@
        The priors and full configuration of the model are given in section S1.
-    From a technical perspective, the Bayesian estimation is a two-step procedure.
+       From a technical perspective, the Bayesian estimation is a two-step procedure~\cite{rodrigue_bayesian_2008}.
        The first step is a data augmentation of the alignment, consisting in sampling a detailed substitution history along the phylogenetic tree for each site, given the current value of the model parameters.
@@
        Alternating between these two sampling steps yields a Markov chain Monte-Carlo (MCMC) procedure whose equilibrium distribution is the posterior probability density of interest~\cite{lartillot_bayesian_2004, rodrigue_bayesian_2008}.
-    Additionally, across-site heterogeneities in amino acid fitness profiles are captured by a Dirichlet process.
+       Additionally, across-site heterogeneities in amino-acid fitness profiles are captured by a Dirichlet process.
        More precisely, the number of amino-acid fitness profiles estimated is lower than the number of sites in the alignment.
@@
        Conversely, sites with similar signatures are assigned to the same fitness profile.
-    This configuration of the Dirichlet process is resampled through the MCMC, so that each site has its own posterior distribution of amino acid fitness profile~\cite{rodrigue_mutationselection_2010, lartillot_inference_2013}.
-    From a more mechanistic perspective, even though not all amino-acids occur at every single codon site of the DNA alignment, we can nevertheless estimate the distribution of amino-acid fitnesses by generalizing the information recovered across sites and across amino-acids based on the phylogenetic relationship among samples.
+       This configuration of the Dirichlet process is resampled through the MCMC to estimate a posterior distribution of amino acid profiles for each site specifically~\cite{rodrigue_mutationselection_2010, lartillot_inference_2013}.
+       From a more mechanistic perspective, even though not all amino acids occur at every single codon site of the DNA alignment, we can nevertheless estimate the distribution of amino-acid fitnesses by generalizing the information recovered across sites and across amino acids based on the phylogenetic relationship among samples.
        In particular, synonymous substitutions along the tree contain the signal to estimate branch lengths and the nucleotide transition matrix, while non-synonymous substitutions contain information on fitness difference between codons connected by single nucleotide changes~\cite{rodrigue_mutationselection_2010}.
@@
        We used the Bayesian software \textit{BayesCode} (\url{https://github.com/ThibaultLatrille/bayescode}, v1.3.1) to estimate the selection coefficients for each protein-coding gene in the mammalian dataset.
-    We ran the MCMC algorithm implemented in BayesCode for $2,000$ generations as described in \textcite{latrille_genes_2023}.
-    For each gene, after discarding a burn-in period of $1,000$ generations of MCMC, we obtained posterior mean estimates (over the $1,000$ generations left of MCMC) of the mutation rate matrix ($\UniDimArray{\mu}$) as well as the $20$ amino acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$.
+       We ran the MCMC algorithm implemented in BayesCode for $2,000$ generations as described in \cite[Latrille et al]{latrille_genes_2023}.
+       For each gene, after discarding a burn-in period of $1,000$ generations of MCMC, we obtained posterior mean estimates (over the $1,000$ generations left of MCMC) of the mutation rate matrix ($\UniDimArray{\mu}$) as well as the $20$ amino-acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$.
 
@@
        In total, we analyzed 28 populations across the 6 different species with polymorphism data.
-    The data was processed as described in \textcite{latrille_genes_2023}.
+       The data was processed as described in \cite[Latrille et al]{latrille_genes_2023}.
 
@@
               \proba [ \SpopDel \given  \Sphyclass] &= \proba [ \Spop < -1 \given \Sphyclass ] = \left( 1 - p_b \right) \int_{1}^{+\infty} f_{\Gamma}(\Spop; -\DelMean, b) \der \Spop, \label{eq:polyProbaDel} \\
-        \proba [ \SpopNeu \given \Sphyclass] &= \proba [ -1 < \Spop < 1 \given \Sphyclass ] = p_b \int_{0}^{1} f_{e}(\Spop; \AdvMean) \der \Spop + \left( 1 - p_b \right) \int_{0}^{1} f_{\Gamma}(\Spop; -\DelMean, b) \der \Spop, \\
+              \proba [ \SpopNeu \given \Sphyclass] &= \proba [ -1 < \Spop < 1 \given \Sphyclass ] = p_b \int_{0}^{1} f_{e}(\Spop; \AdvMean) \der \Spop + \\ \nonumber &\left( 1 - p_b \right) \int_{0}^{1} f_{\Gamma}(\Spop; -\DelMean, b) \der \Spop, \\
               \proba [ \SpopBen \given \Sphyclass] &= \proba [ \Spop > 1 \given \Sphyclass] = p_b \int_{1}^{+\infty} f_{e}(\Spop; \AdvMean) \der \Spop. \label{eq:polyProbaAdv}
@@
        \label{subsec:correlation-diversity}
-    Genetic diversity estimator Watterson's $\thetaSyn$ was obtained for each population from the synonymous SFS as in \textcite{achaz_frequency_2009}.
+       Genetic diversity estimator Watterson's $\thetaSyn$ was obtained for each population from the synonymous SFS as in \cite[Achaz]{achaz_frequency_2009}.
        For each popuation, $\Ne$ was estimated from the equation $\Ne=\thetaSyn / (4 \times u)$, where $u$ is the mutation rate per generation.
-    Estimates for $u$ were averaged per species across the pedigree-based estimation in \textcite{bergeron_evolution_2023} for \textit{Homo}, \textit{Bos}, \textit{Capra} and \textit{Chlorocebus}.
+       Estimates for $u$ were averaged per species across the pedigree-based estimation in \cite[Bergeron et al]{bergeron_evolution_2023} for \textit{Homo}, \textit{Bos}, \textit{Capra} and \textit{Chlorocebus}.
        For \textit{Ovis} we used the estimated $u$ of \textit{Capra}.
-    For \textit{Equus}, we used $u$ as estimated in \textcite{orlando_recalibrating_2013} ($u=7.24\times10^{-9}$).
+       For \textit{Equus}, we used $u$ as estimated in \cite[Orlando et al]{orlando_recalibrating_2013} ($u=7.24\times10^{-9}$).
        Because a correlation must account for phylogenetic relationship and non-independence of samples, we fitted a Phylogenetic Generalized Linear Model in \textit{R} with the package \texttt{caper}~\cite{orme_caper_2013}.
-    The mammalian dated tree is obtained from TimeTree~\cite{kumar_timetree_2017} and pruned to the species under study, with multi-furcation of the different populations from each species placed at the same divergence time as the species (section S4.1).
+       The mammalian dated tree was obtained from TimeTree~\cite{kumar_timetree_2017} and pruned to include only the species analysed in this study, with multi-furcation of the different populations from each species placed at the same divergence time as the species (section S4.1).
 
-    \section*{Data availability}
+       \section{Data availability}\label{sec:data-availability}
        The data underlying this article are available at \url{https://doi.org/10.5281/zenodo.7878954}.
        Snakemake pipeline, analysis scripts and documentation are available at \href{https://github.com/ThibaultLatrille/SelCoeff}{github.com/ThibaultLatrille/SelCoeff}.
+}
 
-    \section*{Acknowledgements}
-    \label{sec:acknowledgment}
+\showmatmethods{} % Display the Materials and Methods section
+
+\acknow{
        We gratefully acknowledge the help of Mélodie Bastian, Nicolas Lartillot, Carina Farah Mugal, Laurent Duret, Alexandre Reymond, Daniele Silvestro and Nicolas Gambardella for their advice and reviews concerning this manuscript.
@@
        The European Union’s Seventh Framework Programme (FP7/2010-2014) provided funding for the project under grant agreement no 244356 - “NextGen”.
+}
 
-    \section*{Competing interests}
-    The authors declare no conflicts of interest.
+\showacknow{} % Display the acknowledgments section
 
-    \section*{Author information}
-    Original idea: T.L.\ and J.J.;
-    Model conception: T.L., J.J.\ and N.S.;
-    Code: T.L.;
-    Data analyses: T.L.\ and J.J.;
-    Interpretation: T.L., J.J., D.A.H.\ and N.S.;
-    First draft: T.L.\ and J.J.;
-    Editing and revisions: T.L., J.J., D.A.H.\ and N.S.
-    Project management and funding: N.S\@.
+% Bibliography
+\bibliography{references_bibtex}
 
-%TC:ignore
-    \printbibliography
-%TC:endignore
-\newpage
-    \begin{figure*}[!htb]
-        \centering
-        \includegraphics[width=\textwidth, page=1] {artworks/figure.fitness-landscape}
-        \caption{
-            (A \& B) For a given codon position of a protein-coding DNA sequence, amino acids (x-axis) have different fitness values (y-axis).
-            Under a fluctuating fitness landscape (A), these fitnesses change with time.
-            The protein sequence follows the moving target defined by the amino-acid fitnesses.
-Since substitutions are preferentially accepted if they are in the direction of this target, substitutions are, on average, adaptive.
-            At the phylogenetic scale (C), beneficial substitutions are common (positive signs), promoting phenotype diversification across species.
-            Under a stable fitness landscape (B), most mutations reaching fixation are either slightly deleterious reaching fixation due to drift or are beneficial back-mutations restoring a more optimal amino acid.
-            At the phylogenetic scale (D), deleterious substitutions (negative signs) are often reverted via beneficial back-mutations (positive signs), promoting phenotype stability and preserving well-established biological systems.
-            Even though, individually, any back-mutation might have a small beneficial effect on its bearer, we expect beneficial back-mutations to be scattered across the genome and the genome-wide signature of beneficial back-mutations to be detectable and quantifiable.}
-        \label{fig:fitness-landscape}
-    \end{figure*}
-
-    \begin{figure*}[!h]
-        \centering
-        \includegraphics[width=\textwidth, page=1] {artworks/figure.method.proba}
-        \caption{
-            Selection coefficients at the phylogenetic and population scales.
-            At the phylogenetic scale (A), we estimated the amino-acid fitness for each site from protein-coding DNA alignments using mutation-selection codon models.
-            For every possible mutation, the difference in amino acid fitness before and after the mutation allows us to compute the selection coefficient at the phylogenetic scale ($\Sphy$).
-            Depending on $\Sphy$ (B) mutations can be predicted as deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) or beneficial back-mutations ($\SphyBen$) toward a fitter amino acid and repairing existing functions.
-            At the population scale, each observed single nucleotide polymorphism (SNP) segregating in the population can also be classified according to its $\Sphy$ value (C).
-            Occurrence and frequency in the population of non-synonymous polymorphisms, contrasted to synonymous polymorphisms (deemed neutral) is used to estimate selection coefficients (D-E) at the population scale ($\Spop$), for each class of selection ($\SphyDel$, $\SphyNeu$, $\SphyBen$).
-            We can thus assess whether $\Sphy$ predicts $\Spop$ and compute \textit{precision} (F) and \textit{recall} (G) for each class.
-            The \textit{recall} value for class $\SphyBen$ is the probability of back-mutations among all beneficial ones (G).
-        }
-        \label{fig:method}
-    \end{figure*}
-
-    \begin{figure*}[!h]
-        \centering
-        \includegraphics[width=\textwidth, page=1] {artworks/figure.homo-afr-results}
-        \caption{
-            (A) Distribution of scaled selection coefficients ($\Sphy$), predicted for all possible non-synonymous DNA mutations away from the ancestral human exome (section \ref{subsec:nunber-of-sites}).
-            Mutations are divided into three classes of selection: deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial ($\SphyBen$, supposedly beneficial back-mutations)
-            (B) Distribution of scaled selection coefficients ($\Sphy$) for all observed substitutions along the \textit{Homo} branch after the \textit{Homo}-\textit{Pan} split (section \ref{subsec:substitution-mapping-in-the-terminal-branch}).
-            If there are fewer substitutions than expected, this class is thus undergoing purifying selection, as is the case for $\SphyDel$.
-            (C) The site-frequency spectrum (SFS) in humans of African descent for a random sample of 16 alleles (means in solid lines and standard deviations in color shades) for each class of selection and for synonymous mutations, supposedly neutral (black).
-The SFS represents the proportion of mutations (y-axis) with a given number of derived alleles in the population (x-axis).
-            At high frequencies, deleterious mutations are underrepresented.
-            (D) Proportion of beneficial $\ProbaPopDel$, nearly-neutral $\ProbaPopNeu$, and deleterious mutations $\ProbaPopBen$ estimated at the population scale for each class of selection at the phylogenetic scale (section \ref{subsec:s-polymorphism-method}).
-Proportions depicted here are not weighted by their mutational opportunities.
-        }
-        \label{fig:homo-afr-results}
-    \end{figure*}
-
-    \begin{figure*}[!ht]
-        \centering
-        \includegraphics[width=\textwidth, page=1] {artworks/figure.diversity}
-        \caption{
-            Populations in circles, mean of the species across the populations as squares.
-            (A) Proportion of nearly-neutral mutations at the population scale ($\proba [ \SpopNeu]$ in the y-axis), shown as a function of estimated effective population size ($\Ne$ in the x-axis).
-            (B) Proportion of beneficial back-mutations among all beneficial mutations ($\proba [ \SphyBen  \given  \SpopBen]$ in the y-axis), shown as a function of $\Ne$ in x-axis.
-            Correlations account for phylogenetic relationship and non-independence of samples, through the fit of a Phylogenetic Generalized Linear Model (see section~\ref{subsec:s-polymorphism-method} in Materials \& Methods).
-        }
-        \label{fig:diversity}
-    \end{figure*}
-
-    \begin{table*}[tb]
-%TC:ignore
-        \centering
-        \begin{adjustbox}{width=\textwidth}
-            \begin{tabular}{||l|l|r||r|r||r|r||r|r||}
-                \toprule
-                \multicolumn{3}{||c||}{} &
-                \multicolumn{2}{c||}{\shortstack{\textbf{Deleterious mutations} \\ $\bm{\SpopDel \coloneqq \Spop<-1}$ \\ $\bm{\SphyDel \coloneqq \Sphy<-1}$}} &
-                \multicolumn{2}{c||}{\shortstack{\textbf{Nearly-neutral mutations} \\ $\bm{\SpopNeu \coloneqq -1<\Spop<1}$ \\ $\bm{\SphyNeu \coloneqq -1<\Sphy<1}$}} &
-                \multicolumn{2}{c||}{\shortstack{\textbf{Beneficial mutations} \\ $\bm{\SpopBen \coloneqq \Spop>1}$ \\ $\bm{\SphyBen \coloneqq \Sphy>1}$}}
-                \\ \hline
-                \textbf{Population} &
-                \textbf{Species} &
-                $\bm{\Ne}$ &
-                \makecell{\textbf{Precision} \\ $\bm{\proba [\SpopDel \given \SphyDel]}$} &
-                \makecell{\textbf{Recall} \\ $\bm{\proba [\SphyDel \given \SpopDel]}$}            &
-                \makecell{\textbf{Precision}      \\ $\bm{\proba [\SpopNeu \given \SphyNeu]}$}                                    &
-                \makecell{\textbf{Recall}          \\ $\bm{\proba [\SphyNeu \given \SpopNeu]}$}                                  &
-                \makecell{\textbf{Precision}          \\ $\bm{\proba [\SpopBen \given \SphyBen]}$}          &
-                \makecell{\textbf{Recall}        \\ $\bm{\proba [\SphyBen \given \SpopBen]}$}
-                \\   \midrule
-                \rowcolor{LIGHTGREY} Equus c. & Equus caballus & $7.5\times 10^{4}$ & $ 0.923$ & $ 0.972$ & $ 0.570$ & $ 0.341$ & $ 0.648$ & $ 0.536$ \\
-                Iran & Bos taurus & $5.6\times 10^{4}$ & $ 0.915$ & $ 1.000$ & $ 0.632$ & $ 0.358$ & $ 0.873$ & $ 0.243$ \\
-                Uganda & Bos taurus & $1.3\times 10^{5}$ & $ 0.951$ & $ 0.969$ & $ 0.495$ & $ 0.414$ & $ 0.576$ & $ 0.415$ \\
-                \rowcolor{LIGHTGREY} Australia & Capra hircus & $1.7\times 10^{5}$ & $ 0.944$ & $ 0.971$ & $ 0.527$ & $ 0.437$ & $ 0.368$ & $ 0.177$ \\
-                \rowcolor{LIGHTGREY} France & Capra hircus & $1.9\times 10^{5}$ & $ 0.946$ & $ 0.971$ & $ 0.508$ & $ 0.423$ & $ 0.368$ & $ 0.190$ \\
-                \rowcolor{LIGHTGREY} Iran (C. aegagrus) & Capra hircus & $1.9\times 10^{5}$ & $ 0.948$ & $ 0.969$ & $ 0.486$ & $ 0.444$ & $ 0.368$ & $ 0.165$ \\
-                \rowcolor{LIGHTGREY} Iran & Capra hircus & $2.3\times 10^{5}$ & $ 0.953$ & $ 0.966$ & $ 0.425$ & $ 0.407$ & $ 0.368$ & $ 0.193$ \\
-                \rowcolor{LIGHTGREY} Italy & Capra hircus & $1.9\times 10^{5}$ & $ 0.947$ & $ 0.971$ & $ 0.551$ & $ 0.439$ & $ 0.368$ & $ 0.243$ \\
-                \rowcolor{LIGHTGREY} Morocco & Capra hircus & $2.2\times 10^{5}$ & $ 0.950$ & $ 0.970$ & $ 0.527$ & $ 0.440$ & $ 0.368$ & $ 0.245$ \\
-                Iran & Ovis aries & $3.8\times 10^{5}$ & $ 0.961$ & $ 0.961$ & $ 0.452$ & $ 0.415$ & $ 0.205$ & $ 0.407$ \\
-                Iran (O. orientalis) & Ovis aries & $4.5\times 10^{5}$ & $ 0.964$ & $ 0.960$ & $ 0.420$ & $ 0.445$ & $ 0.193$ & $ 0.190$ \\
-                Iran (O. vignei) & Ovis aries & $3.7\times 10^{5}$ & $ 0.967$ & $ 0.959$ & $ 0.361$ & $ 0.470$ & $ 0.190$ & $ 0.110$ \\
-                Various & Ovis aries & $4.1\times 10^{5}$ & $ 0.962$ & $ 0.962$ & $ 0.433$ & $ 0.440$ & $ 0.229$ & $ 0.222$ \\
-                Morocco & Ovis aries & $ 4\times 10^{5}$ & $ 0.962$ & $ 0.961$ & $ 0.462$ & $ 0.424$ & $ 0.211$ & $ 0.514$ \\
-                \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus & $1.1\times 10^{5}$ & $ 0.935$ & $ 0.975$ & $ 0.565$ & $ 0.402$ & $ 0.648$ & $ 0.293$ \\
-                \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus & $1.7\times 10^{5}$ & $ 0.948$ & $ 0.971$ & $ 0.508$ & $ 0.423$ & $ 0.535$ & $ 0.275$ \\
-                \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus & $1.4\times 10^{5}$ & $ 0.935$ & $ 0.975$ & $ 0.580$ & $ 0.416$ & $ 0.552$ & $ 0.245$ \\
-                \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus & $1.4\times 10^{5}$ & $ 0.944$ & $ 0.975$ & $ 0.654$ & $ 0.437$ & $ 0.577$ & $ 0.821$ \\
-                \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus & $1.5\times 10^{5}$ & $ 0.946$ & $ 0.972$ & $ 0.538$ & $ 0.453$ & $ 0.588$ & $ 0.257$ \\
-                \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus & $ 1\times 10^{5}$ & $ 0.933$ & $ 0.976$ & $ 0.629$ & $ 0.412$ & $ 0.599$ & $ 0.358$ \\
-                \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus & $1.8\times 10^{5}$ & $ 0.944$ & $ 0.971$ & $ 0.548$ & $ 0.423$ & $ 0.574$ & $ 0.341$ \\
-                \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus & $1.2\times 10^{5}$ & $ 0.936$ & $ 0.975$ & $ 0.586$ & $ 0.402$ & $ 0.598$ & $ 0.336$ \\
-                \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus & $1.7\times 10^{5}$ & $ 0.945$ & $ 0.971$ & $ 0.512$ & $ 0.432$ & $ 0.585$ & $ 0.250$ \\
-                African & Homo sapiens & $5.6\times 10^{4}$ & $ 0.911$ & $ 0.976$ & $ 0.579$ & $ 0.325$ & $ 0.721$ & $ 0.349$ \\
-                Admixed American & Homo sapiens & $4.5\times 10^{4}$ & $ 0.902$ & $ 0.978$ & $ 0.584$ & $ 0.299$ & $ 0.690$ & $ 0.345$ \\
-                East Asian & Homo sapiens & $ 4\times 10^{4}$ & $ 0.905$ & $ 0.978$ & $ 0.585$ & $ 0.325$ & $ 0.688$ & $ 0.249$ \\
-                European & Homo sapiens & $4.2\times 10^{4}$ & $ 0.906$ & $ 0.978$ & $ 0.584$ & $ 0.329$ & $ 0.688$ & $ 0.248$ \\
-                South Asian & Homo sapiens & $4.4\times 10^{4}$ & $ 0.908$ & $ 0.978$ & $ 0.584$ & $ 0.342$ & $ 0.691$ & $ 0.224$ \\
-                \bottomrule
-            \end{tabular}
-        \end{adjustbox}
-%TC:endignore
-        \caption{
-            \textit{Precision} and \textit{recall} for estimated selection coefficient of mutations given by mutation-selection models ($\Sphy$).
-            \textit{Precision} is the estimation of the selection coefficient at population scale ($\Spop$) given that $\Sphy$ is known.
-            Conversely, \textit{recall} is the estimation of $\Sphy$ given selection coefficient at the population scale ($\Spop$) is known.
-            \textit{Recall} for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is thus the proportion of beneficial back-mutations among all beneficial mutations.
-            $\Ne$ is the estimated effective population size for each population.
-        }
-        \label{table:proba}
-    \end{table*}
 \end{document}

### 2023-10-14 manuscript/supp-figure3.tex
Revision manuscript: 2023-08692R

%TC:ignore
\documentclass{article}

\usepackage{xcolor, colortbl}
\definecolor{BLUELINK}{HTML}{0645AD}
\definecolor{DARKBLUELINK}{HTML}{0B0080}
\PassOptionsToPackage{hyphens}{url}
\usepackage[colorlinks=false]{hyperref}
% for linking between references, figures, TOC, etc in the pdf document
\hypersetup{colorlinks,
    linkcolor=DARKBLUELINK,
    anchorcolor=DARKBLUELINK,
    citecolor=DARKBLUELINK,
    filecolor=DARKBLUELINK,
    menucolor=DARKBLUELINK,
    urlcolor=BLUELINK
} % Color citation links in purple
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{naturalnames}{hyperref}

\usepackage[margin=60pt]{geometry}
\usepackage{amssymb,amsfonts,amsmath,amsthm,mathtools}
\usepackage{lmodern}
\usepackage{bm,bbold}
\usepackage{verbatim}
\usepackage{float}
\usepackage{listings, enumerate, enumitem}
\usepackage[export]{adjustbox}
\usepackage{tabu}
\usepackage{longtable}
\tabulinesep=0.6mm
\newcommand\cellwidth{\TX@col@width}
\usepackage{hhline}
\setlength{\arrayrulewidth}{1.2pt}
\usepackage{multicol,multirow,array}
\usepackage{etoolbox}
\AtBeginEnvironment{tabu}{\footnotesize}
\usepackage{booktabs}
\usepackage{graphicx}
\pdfinclusioncopyfonts=1

\newcommand{\UniDimArray}[1]{\bm{#1}}
\newcommand{\der}{\text{d}}
\newcommand{\e}{\text{e}}
\newcommand{\Ne}{N_{\text{e}}}
\newcommand{\proba}{\mathbb{P}}
\newcommand{\pfix}{\proba_{\text{fix}}}
\newcommand{\dn}{d_N}
\newcommand{\ds}{d_S}
\newcommand{\dnds}{\dn / \ds}
\newcommand{\Sphy}{S_{0}}
\newcommand{\SphyDel}{\mathcal{D}_0}
\newcommand{\SphyNeu}{\mathcal{N}_0}
\newcommand{\SphyBen}{\mathcal{B}_0}
\newcommand{\Sphyclass}{x}
\newcommand{\SphyclassAlt}{y}
\newcommand{\given}{\mid}
\newcommand{\Spop}{S}
\newcommand{\SpopDel}{\mathcal{D}}
\newcommand{\SpopNeu}{\mathcal{N}}
\newcommand{\SpopBen}{\mathcal{B}}
\newcommand{\ProbaPopDel}{\proba [ \SpopDel]}
\newcommand{\ProbaPopNeu}{\proba [ \SpopNeu ]}
\newcommand{\ProbaPopBen}{\proba [ \SpopBen ]}
\newcommand{\AdvMean}{\beta_b}
\newcommand{\DelMean}{\beta_d}
\newcommand{\thetaSyn}{\theta_{\text{S}}}

\title{Replicability of figure 3 across populations}
\date{~}
\author{~}

\begin{document}
    \maketitle
    \tableofcontents

    \newpage

    (Top-left) Distribution of scaled selection coefficients ($\Sphy$), predicted for all possible non-synonymous DNA mutations away from the ancestral exome.
    Mutations are divided into three classes of selection: deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial ($\SphyBen$, supposedly beneficial back-mutations)

    (Top-right) Distribution of scaled selection coefficients ($\Sphy$) for all observed substitutions along the terminal branch of the tree.
    If there are fewer substitutions than expected, this class is thus undergoing purifying selection, as is the case for $\SphyDel$.

    (Bottom-left) The site-frequency spectrum (SFS) for a random sample of 16 alleles (means in solid lines and standard deviations in color shades) for each class of selection and for synonymous mutations, supposedly neutral (black).
    The SFS represents the proportion of mutations (y-axis) with a given number of derived alleles in the population (x-axis).
    At high frequencies, deleterious mutations are underrepresented.

    (Bottom-right) Proportion of beneficial $\ProbaPopDel$, nearly-neutral $\ProbaPopNeu$, and deleterious mutations $\ProbaPopBen$ estimated at the population scale for each class of selection at the phylogenetic scale.
    Proportions depicted here are not weighted by their mutational opportunities.
    \section{Bos taurus}

    \subsection{Iran}

    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Bos_taurus.IRBT.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Bos_taurus.IRBT.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Bos_taurus.IRBT.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Bos_taurus.IRBT.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \\
    \subsection{Uganda}

    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Bos_taurus.UGBT.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Bos_taurus.UGBT.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Bos_taurus.UGBT.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Bos_taurus.UGBT.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \\
    \section{Capra}

    \subsection{Australia}

    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.AUCH.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Capra_hircus.AUCH.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.AUCH.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.AUCH.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \\
    \subsection{France}

    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.FRCH.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Capra_hircus.FRCH.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.FRCH.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.FRCH.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \\
    \subsection{Iran (C. aegagrus)}

    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.IRCA.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Capra_hircus.IRCA.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.IRCA.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.IRCA.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \\
    \subsection{Iran}

    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.IRCH.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Capra_hircus.IRCH.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.IRCH.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.IRCH.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \\
    \subsection{Italy}

    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.ITCH.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Capra_hircus.ITCH.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.ITCH.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.ITCH.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \\
    \subsection{Morocco}

    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.MOCH.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Capra_hircus.MOCH.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.MOCH.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.MOCH.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \\
    \section{Chlorocebus sabaeus}

    \subsection{Barbados}

    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.Barbados.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Chlorocebus_sabaeus.Barbados.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.Barbados.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.Barbados.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \\
    \subsection{Central Afr. Rep.}

    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.Central_African_Republic.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Chlorocebus_sabaeus.Central_African_Republic.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \\
    \subsection{Ethiopia}

    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.Ethiopia.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Chlorocebus_sabaeus.Ethiopia.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \\
    \subsection{Gambia}

    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.Gambia.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Chlorocebus_sabaeus.Gambia.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.Gambia.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.Gambia.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \\
    \subsection{Kenya}

    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.Kenya.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Chlorocebus_sabaeus.Kenya.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.Kenya.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.Kenya.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \\
    \subsection{Nevis}

    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.Nevis.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Chlorocebus_sabaeus.Nevis.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.Nevis.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.Nevis.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \\
    \subsection{Saint Kitts}

    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.Saint_Kitts.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Chlorocebus_sabaeus.Saint_Kitts.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.Saint_Kitts.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.Saint_Kitts.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \\
    \subsection{South Africa}

    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.South_Africa.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Chlorocebus_sabaeus.South_Africa.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.South_Africa.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.South_Africa.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \\
    \subsection{Zambia}

    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.Zambia.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Chlorocebus_sabaeus.Zambia.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.Zambia.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.Zambia.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \\
    \section{Equus caballus}

    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Equus_caballus.up.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Equus_caballus.up.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Equus_caballus.up.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Equus_caballus.up.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \\
    \section{Homo sapiens}

    \subsection{African}

    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Homo_sapiens.AFR.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Homo_sapiens.AFR.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Homo_sapiens.AFR.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Homo_sapiens.AFR.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \\
    \subsection{Admixed American}

    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Homo_sapiens.AMR.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Homo_sapiens.AMR.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Homo_sapiens.AMR.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Homo_sapiens.AMR.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \\
    \subsection{East Asian}

    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Homo_sapiens.EAS.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Homo_sapiens.EAS.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Homo_sapiens.EAS.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Homo_sapiens.EAS.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \\
    \subsection{European}

    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Homo_sapiens.EUR.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Homo_sapiens.EUR.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Homo_sapiens.EUR.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Homo_sapiens.EUR.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \\
    \subsection{South Asian}

    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Homo_sapiens.SAS.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Homo_sapiens.SAS.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Homo_sapiens.SAS.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Homo_sapiens.SAS.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \\
    \section{Ovis}

    \subsection{Iran}

    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Ovis_aries.IROA.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Ovis_aries.IROA.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Ovis_aries.IROA.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Ovis_aries.IROA.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \\
    \subsection{Iran (O. orientalis)}

    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Ovis_aries.IROO.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Ovis_aries.IROO.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Ovis_aries.IROO.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Ovis_aries.IROO.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \\
    \subsection{Iran (O. vignei)}

    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Ovis_aries.IROV.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Ovis_aries.IROV.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Ovis_aries.IROV.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Ovis_aries.IROV.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \\
    \subsection{Various}

    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Ovis_aries.ISGC.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Ovis_aries.ISGC.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Ovis_aries.ISGC.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Ovis_aries.ISGC.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \\
    \subsection{Morocco}

    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Ovis_aries.MOOA.MutSel.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Ovis_aries.MOOA.pdf}
    \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Ovis_aries.MOOA.MutSel-sfs.normalize.pdf}
    \end{minipage}
    \begin{minipage}{0.49\linewidth}
        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Ovis_aries.MOOA.MutSel.polyDFE_C.pdf}
    \end{minipage}
    \\

\end{document}

### 2024-01-22 manuscript/main-PNAS.tex
Prepating files for revision round 2

@@
 
-%TC:ignore
-\section{Author information}\label{sec:author-information}
-TL, NR and NL designed the study.
-TL gathered and formatted the data and conducted the analyses with \texttt{BayesCode} using scripts in \texttt{Python} and pipeline in \texttt{Snakemake}.
-TL, NR and NL contributed to the writing of the manuscript.
-
 \matmethods{

### 2024-01-22 manuscript/main-revision-2.tex
Prepating files for revision round 2

--- 2024-01-22 manuscript/main-PNAS.tex
@@
-\documentclass[9pt,twocolumn,twoside,lineno]{pnas-new}
-% Use the lineno option to display guide line numbers if required.
+%! BibTeX Compiler = biber
+%TC:ignore
+\documentclass{article}
 
+\usepackage{xcolor, colortbl}
+\definecolor{BLUELINK}{HTML}{0645AD}
+\definecolor{DARKBLUELINK}{HTML}{0B0080}
+\definecolor{LIGHTGREY}{gray}{0.9}
+\PassOptionsToPackage{hyphens}{url}
+\usepackage[colorlinks=false]{hyperref}
+% for linking between references, figures, TOC, etc in the pdf document
+\hypersetup{colorlinks,
+    linkcolor=DARKBLUELINK,
+    anchorcolor=DARKBLUELINK,
+    citecolor=DARKBLUELINK,
+    filecolor=DARKBLUELINK,
+    menucolor=DARKBLUELINK,
+    urlcolor=BLUELINK
+} % Color citation links in purple
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{naturalnames}{hyperref}
+
+\usepackage{biorxiv}
+\usepackage[backend=biber,eprint=false,isbn=false,url=false,intitle=true,style=nature,date=year]{biblatex}
+\addbibresource{codon_models.bib}
+
+\usepackage{url}
 \usepackage{amssymb,amsfonts,amsmath,amsthm,mathtools}
+\usepackage{lmodern}
+\usepackage{xfrac, nicefrac}
 \usepackage{bm}
+\usepackage{listings, enumerate, enumitem}
+\usepackage[export]{adjustbox}
+\usepackage{graphicx}
+\usepackage{bbold}
+\usepackage{pdfpages}
+\pdfinclusioncopyfonts=1
+\usepackage{lineno}
+\usepackage{tabu}
+\usepackage{hhline}
+\usepackage{multicol,multirow,array}
+\usepackage{etoolbox}
+\usepackage{booktabs}
 \usepackage{makecell}
-\usepackage[export]{adjustbox}
+\usepackage{orcidlink}
+
+\newcommand{\NS}[1]{\textcolor{red}{\textbf{\emph{[NS: #1]}}}}
+
 \newcommand{\UniDimArray}[1]{\bm{#1}}
@@
 \newcommand{\thetaSyn}{\theta_{\text{S}}}
-\definecolor{LIGHTGREY}{gray}{0.9}
-
-\templatetype{pnasresearcharticle} % Choose template 
-% {pnasresearcharticle} = Template for a two-column research article
-% {pnasmathematics} %= Template for a one-column mathematics article
-% {pnasinvited} %= Template for a PNAS invited submission
+\renewcommand{\baselinestretch}{1.5}
+\renewcommand{\arraystretch}{0.6}
+\linenumbers
+\frenchspacing
 
 \title{Mammalian protein-coding genes exhibit widespread beneficial mutations that are not adaptive}
+\rhead{\scshape Beneficial yet non-adaptive mutations}
 
-% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
-\author[1]{T. {Latrille}}
-\author[2]{J. {Joseph}}
-\author[1]{D.~A. {Hartasánchez}}
-\author[1]{N. {Salamin}}
-
-\affil[1]{Department of Computational Biology, Université de Lausanne, Lausanne, Switzerland}
-\affil[2]{Laboratoire de Biométrie et Biologie Evolutive, UMR5558, Université Lyon 1, Villeurbanne, France}
-
-% Please give the surname of the lead author for the running footer
-\leadauthor{Latrille}
-
-% Please add here a significance statement to explain the relevance of your work
-\significancestatement{
-       The extent to which adaptation to changing environments is shaping genomes is a central question in molecular evolution.
-       To quantify the rate of adaptation, population geneticists have typically used signatures of positive selection.
-       However, mutations restoring an ancestral sequence of higher fitness lost by genetic drift are also positively selected, but they do not respond to a change in the environment.
-       In this study, we have managed to distinguish beneficial mutations that are due to changing environments and those that are restoring pre-existing functions in mammals.
-       We show that a substantial proportion of beneficial mutations cannot be interpreted as adaptive.
+\author{
+    \large
+    \textbf{T.
+{Latrille}$^{1\dag}$\orcidlink{0000-0002-9643-4668}, J.
+{Joseph}$^{2\dag}$\orcidlink{0009-0002-1312-9930}, D.~A.
+{Hartasánchez}$^{1}$\orcidlink{0000-0003-2596-6883}, N.
+{Salamin}$^{1}$\orcidlink{0000-0002-3963-4954}}\\
+    \normalsize
+    $^{1}$Department of Computational Biology, Université de Lausanne, Lausanne, Switzerland\\
+    $^{2}$Laboratoire de Biométrie et Biologie Evolutive, UMR5558, Université Lyon 1, Villeurbanne, France \\
+    $^{\dag}$These authors contributed equally to this work\\
+    \texttt{\href{mailto:thibault.latrille@ens-lyon.org}{thibault.latrille@ens-lyon.org}} \\
 }
 
-% Please include corresponding author, author contribution and author declaration information
-\authorcontributions{Original idea: T.L.\ and J.J.;
-Model conception: T.L., J.J.\ and N.S.;
-Code: T.L.;
-Data analyses: T.L.\ and J.J.;
-Interpretation: T.L., J.J., D.A.H.\ and N.S.;
-First draft: T.L.\ and J.J.;
-Editing and revisions: T.L., J.J., D.A.H.\ and N.S.
-Project management and funding: N.S\@.}
-\authordeclaration{The author declares no competing interest.}
-\equalauthors{\textsuperscript{1}T.L. contributed equally to this work with J.J.}
-\correspondingauthor{E-mail: \href{mailto:thibault.latrille@ens-lyon.org}{thibault.latrille@ens-lyon.org}}
+% The submission checklist is available at:
+% https://docs.google.com/document/d/1SScaqEAgZGpeaXxpWPDh1NOLaDDLLmkGOYgaGvbY-4o/edit#
+% Response to reviewers at:
+% https://docs.google.com/document/d/1kzt4uf6GgmuAVHx6-LQyzFuee9biyaWoMV6RNO6lSzI/edit?usp=sharing
 
-% Keywords are not mandatory, but authors are strongly encouraged to provide them. If provided, please include two to five keywords, separated by the pipe symbol, e.g:
-\keywords{Adaptation $|$ Back-mutations $|$ Phylogenetics $|$ Population-genetics $|$ Codon models }
+\begin{document}
+    \maketitle
 
+%TC:endignore
     \begin{abstract}
@@
 
-\dates{This manuscript was compiled on \today}
-\doi{\url{www.pnas.org/cgi/doi/10.1073/pnas.XXXXXXXXXX}}
+    \keywords{Adaptation \and Back-mutations \and Phylogenetics \and Population-genetics \and Codon models }
 
-\begin{document}
+    \section*{Significance statement}
+    The extent to which adaptation to changing environments is shaping genomes is a central question in molecular evolution.
+To quantify the rate of adaptation, population geneticists have typically used signatures of positive selection.
+However, mutations restoring an ancestral sequence of higher fitness lost by genetic drift are also positively selected, but they do not respond to a change in the environment.
+In this study, we have managed to distinguish beneficial mutations that are due to changing environments and those that are restoring pre-existing functions in mammals.
+We show that a substantial proportion of beneficial mutations cannot be interpreted as adaptive.
 
-\maketitle
-\thispagestyle{firststyle}
-\ifthenelse{\boolean{shortarticle}}{\ifthenelse{\boolean{singlecolumn}}{\abscontentformatted}{\abscontent}}{}
-
-\firstpage[3]{3}
-\dropcap{A}daptation is one of the main processes shaping the diversity of forms and functions across the tree of life~\cite{darwin_origin_1859}.
+    \section*{Introduction}
+    Adaptation is one of the main processes shaping the diversity of forms and functions across the tree of life~\cite{darwin_origin_1859}.
     Evolutionary adaptation is tightly linked to environmental change and species responding to this change~\cite{merrell_adaptive_1994, gavrilets_adaptive_2009}.
@@
     While compensatory mutations change the sequence and thus induce genetic diversification, beneficial back-mutations reduce genetic diversity and do not contribute to genetic innovation.
-
-Although Tomoko Ohta considered beneficial back-mutations negligible in her nearly-neutral theory~\cite{Ohta1992}, their importance has now been acknowledged for
-expanding populations~\cite{charlesworth_other_2007}.
+    Although Tomoko Ohta considered beneficial back-mutations negligible in her nearly-neutral theory~\cite{Ohta1992}, their importance has now been acknowledged for expanding populations~\cite{charlesworth_other_2007}.
     However, differentiating between an adaptive mutation and a beneficial back-mutation remains challenging~\cite{chi_detecting_2020}.
@@
     It can then be distinguished from truly novel beneficial mutations because the latter are not expected to mutate mutate towards the amino acids of higher fitnesses defined by the stable fitness landscape but rather mutate to amino acids showing a diversified pattern (fig.~\ref{fig:fitness-landscape}).
-
-\begin{figure*}[htb]
-       \centering
-       \includegraphics[width=17.8cm, page=1]{figure1}
-       \caption{
-              (A \& B) For a given codon position of a protein-coding DNA sequence, amino acids (x-axis) have different fitness values (y-axis).
-              Under a fluctuating fitness landscape (A), these fitnesses change with time.
-              The protein sequence follows the moving target defined by the amino-acid fitnesses.
-Since substitutions are preferentially accepted if they are in the direction of this target, substitutions are, on average, adaptive.
-              At the phylogenetic scale (C), beneficial substitutions are common (positive signs), promoting phenotype diversification across species.
-              Under a stable fitness landscape (B), most mutations reaching fixation are either slightly deleterious reaching fixation due to drift or are beneficial back-mutations restoring a more optimal amino acid.
-              At the phylogenetic scale (D), deleterious substitutions (negative signs) are often reverted via beneficial back-mutations (positive signs), promoting phenotype stability and preserving well-established biological systems.
-              Even though, individually, any back-mutation might have a small beneficial effect on its bearer, we expect beneficial back-mutations to be scattered across the genome and the genome-wide signature of beneficial back-mutations to be detectable and quantifiable.}
-       \label{fig:fitness-landscape}
-\end{figure*}
-
-\begin{figure*}[htb]
-       \centering
-       \includegraphics[width=17.8cm, page=1]{figure2}
-       \caption{
-              Selection coefficients at the phylogenetic and population scales.
-              At the phylogenetic scale (A), we estimated the amino-acid fitness for each site from protein-coding DNA alignments using mutation-selection codon models.
-              For every possible mutation, the difference in amino-acid fitness before and after the mutation allows us to compute the selection coefficient at the phylogenetic scale ($\Sphy$).
-              Depending on $\Sphy$ (B) mutations can be predicted as deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) or beneficial back-mutations ($\SphyBen$) toward a fitter amino acid and repairing existing functions.
-              At the population scale, each observed single nucleotide polymorphism (SNP) segregating in the population can also be classified according to its $\Sphy$ value (C).
-              Occurrence and frequency in the population of non-synonymous polymorphisms, contrasted to synonymous polymorphisms (deemed neutral) is used to estimate selection coefficients (D-E) at the population scale ($\Spop$), for each class of selection ($\SphyDel$, $\SphyNeu$, $\SphyBen$).
-              We can thus assess whether $\Sphy$ predicts $\Spop$ and compute \textit{precision} (F) and \textit{recall} (G) for each class.
-              The \textit{recall} value for class $\SphyBen$ is the probability of back-mutations among all beneficial ones (G).
-       }
-       \label{fig:method}
-\end{figure*}
 
@@
 
-\section*{Results}\label{sec:results}
+    \section*{Results}
 
@@
     The variable proportions between populations can be explained by the effective number of individuals in the population ($\Ne$), a major driver of selection efficacy.
-Moreover, estimates of mutation rate per generation ($u$), from \cite[Bergeron et al]{bergeron_evolution_2023} and \cite[Orlando et al]{orlando_recalibrating_2013}, and Watterson’s $\theta$ obtained from the synonymous SFS as in \cite[Achaz]{achaz_frequency_2009} allow us to obtain $\Ne$ through $\Ne=\theta/(4 \times u)$.
+    Moreover, estimates of mutation rate per generation ($u$), from \textcite{bergeron_evolution_2023} and \textcite{orlando_recalibrating_2013}, and Watterson’s $\theta$ obtained from the synonymous SFS as in \textcite{achaz_frequency_2009} allow us to obtain $\Ne$ through $\Ne=\theta/(4 \times u)$.
     Using correlation analyses that accounted for phylogenetic relationship (see section \ref{subsec:correlation-diversity} in Materials \& Methods), we found that higher $\Ne$ was associated with a smaller proportion of nearly-neutral mutations ($r^2=0.31$, $p=0.001$, fig.~\ref{fig:diversity}A).
@@
 
-\begin{figure*}[htb]
-       \centering
-       \includegraphics[width=17.8cm, page=1]{figure3}
-       \caption{
-              (A) Distribution of scaled selection coefficients ($\Sphy$), predicted for all possible non-synonymous DNA mutations away from the ancestral human exome (section \ref{subsec:nunber-of-sites}).
-              Mutations are divided into three classes of selection: deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial ($\SphyBen$, supposedly beneficial back-mutations)
-              (B) Distribution of scaled selection coefficients ($\Sphy$) for all observed substitutions along the \textit{Homo} branch after the \textit{Homo}-\textit{Pan} split (section \ref{subsec:substitution-mapping-in-the-terminal-branch}).
-              If there are fewer substitutions than expected, this class is thus undergoing purifying selection, as is the case for $\SphyDel$.
-              (C) The site-frequency spectrum (SFS) in humans of African descent for a random sample of 16 alleles (means in solid lines and standard deviations in color shades) for each class of selection and for synonymous mutations, supposedly neutral (black).
-The SFS represents the proportion of mutations (y-axis) with a given number of derived alleles in the population (x-axis).
-              At high frequencies, deleterious mutations are underrepresented.
-              (D) Proportion of beneficial $\ProbaPopDel$, nearly-neutral $\ProbaPopNeu$, and deleterious mutations $\ProbaPopBen$ estimated at the population scale for each class of selection at the phylogenetic scale (section \ref{subsec:s-polymorphism-method}).
-Proportions depicted here are not weighted by their mutational opportunities.
-       }
-       \label{fig:homo-afr-results}
-\end{figure*}
-
-\begin{table*}[tb]
-       \centering
-       \begin{adjustbox}{width=17.8cm}
-              \begin{tabular}{||l|l|r||r|r||r|r||r|r||}
-                     \toprule
-                     \multicolumn{3}{||c||}{} &
-                     \multicolumn{2}{c||}{\shortstack{\textbf{Deleterious mutations} \\ $\bm{\SpopDel \coloneqq \Spop<-1}$ \\ $\bm{\SphyDel \coloneqq \Sphy<-1}$}} &
-                     \multicolumn{2}{c||}{\shortstack{\textbf{Nearly-neutral mutations} \\ $\bm{\SpopNeu \coloneqq -1<\Spop<1}$ \\ $\bm{\SphyNeu \coloneqq -1<\Sphy<1}$}} &
-                     \multicolumn{2}{c||}{\shortstack{\textbf{Beneficial mutations} \\ $\bm{\SpopBen \coloneqq \Spop>1}$ \\ $\bm{\SphyBen \coloneqq \Sphy>1}$}}
-                     \\ \hline
-                     \textbf{Population} &
-                     \textbf{Species} &
-                     $\bm{\Ne}$ &
-                     \makecell{\textbf{Precision} \\ $\bm{\proba [\SpopDel \given \SphyDel]}$} &
-                     \makecell{\textbf{Recall} \\ $\bm{\proba [\SphyDel \given \SpopDel]}$}            &
-                     \makecell{\textbf{Precision}      \\ $\bm{\proba [\SpopNeu \given \SphyNeu]}$}                                    &
-                     \makecell{\textbf{Recall}          \\ $\bm{\proba [\SphyNeu \given \SpopNeu]}$}                                  &
-                     \makecell{\textbf{Precision}          \\ $\bm{\proba [\SpopBen \given \SphyBen]}$}          &
-                     \makecell{\textbf{Recall}        \\ $\bm{\proba [\SphyBen \given \SpopBen]}$}
-                     \\   \midrule
-                     \rowcolor{LIGHTGREY} Equus c. & Equus caballus & $7.5\times 10^{4}$ & $ 0.923$ & $ 0.972$ & $ 0.570$ & $ 0.341$ & $ 0.648$ & $ 0.536$ \\
-                     Iran & Bos taurus & $5.6\times 10^{4}$ & $ 0.915$ & $ 1.000$ & $ 0.632$ & $ 0.358$ & $ 0.873$ & $ 0.243$ \\
-                     Uganda & Bos taurus & $1.3\times 10^{5}$ & $ 0.951$ & $ 0.969$ & $ 0.495$ & $ 0.414$ & $ 0.576$ & $ 0.415$ \\
-                     \rowcolor{LIGHTGREY} Australia & Capra hircus & $1.7\times 10^{5}$ & $ 0.944$ & $ 0.971$ & $ 0.527$ & $ 0.437$ & $ 0.368$ & $ 0.177$ \\
-                     \rowcolor{LIGHTGREY} France & Capra hircus & $1.9\times 10^{5}$ & $ 0.946$ & $ 0.971$ & $ 0.508$ & $ 0.423$ & $ 0.368$ & $ 0.190$ \\
-                     \rowcolor{LIGHTGREY} Iran (C. aegagrus) & Capra hircus & $1.9\times 10^{5}$ & $ 0.948$ & $ 0.969$ & $ 0.486$ & $ 0.444$ & $ 0.368$ & $ 0.165$ \\
-                     \rowcolor{LIGHTGREY} Iran & Capra hircus & $2.3\times 10^{5}$ & $ 0.953$ & $ 0.966$ & $ 0.425$ & $ 0.407$ & $ 0.368$ & $ 0.193$ \\
-                     \rowcolor{LIGHTGREY} Italy & Capra hircus & $1.9\times 10^{5}$ & $ 0.947$ & $ 0.971$ & $ 0.551$ & $ 0.439$ & $ 0.368$ & $ 0.243$ \\
-                     \rowcolor{LIGHTGREY} Morocco & Capra hircus & $2.2\times 10^{5}$ & $ 0.950$ & $ 0.970$ & $ 0.527$ & $ 0.440$ & $ 0.368$ & $ 0.245$ \\
-                     Iran & Ovis aries & $3.8\times 10^{5}$ & $ 0.961$ & $ 0.961$ & $ 0.452$ & $ 0.415$ & $ 0.205$ & $ 0.407$ \\
-                     Iran (O. orientalis) & Ovis aries & $4.5\times 10^{5}$ & $ 0.964$ & $ 0.960$ & $ 0.420$ & $ 0.445$ & $ 0.193$ & $ 0.190$ \\
-                     Iran (O. vignei) & Ovis aries & $3.7\times 10^{5}$ & $ 0.967$ & $ 0.959$ & $ 0.361$ & $ 0.470$ & $ 0.190$ & $ 0.110$ \\
-                     Various & Ovis aries & $4.1\times 10^{5}$ & $ 0.962$ & $ 0.962$ & $ 0.433$ & $ 0.440$ & $ 0.229$ & $ 0.222$ \\
-                     Morocco & Ovis aries & $ 4\times 10^{5}$ & $ 0.962$ & $ 0.961$ & $ 0.462$ & $ 0.424$ & $ 0.211$ & $ 0.514$ \\
-                     \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus & $1.1\times 10^{5}$ & $ 0.935$ & $ 0.975$ & $ 0.565$ & $ 0.402$ & $ 0.648$ & $ 0.293$ \\
-                     \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus & $1.7\times 10^{5}$ & $ 0.948$ & $ 0.971$ & $ 0.508$ & $ 0.423$ & $ 0.535$ & $ 0.275$ \\
-                     \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus & $1.4\times 10^{5}$ & $ 0.935$ & $ 0.975$ & $ 0.580$ & $ 0.416$ & $ 0.552$ & $ 0.245$ \\
-                     \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus & $1.4\times 10^{5}$ & $ 0.944$ & $ 0.975$ & $ 0.654$ & $ 0.437$ & $ 0.577$ & $ 0.821$ \\
-                     \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus & $1.5\times 10^{5}$ & $ 0.946$ & $ 0.972$ & $ 0.538$ & $ 0.453$ & $ 0.588$ & $ 0.257$ \\
-                     \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus & $ 1\times 10^{5}$ & $ 0.933$ & $ 0.976$ & $ 0.629$ & $ 0.412$ & $ 0.599$ & $ 0.358$ \\
-                     \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus & $1.8\times 10^{5}$ & $ 0.944$ & $ 0.971$ & $ 0.548$ & $ 0.423$ & $ 0.574$ & $ 0.341$ \\
-                     \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus & $1.2\times 10^{5}$ & $ 0.936$ & $ 0.975$ & $ 0.586$ & $ 0.402$ & $ 0.598$ & $ 0.336$ \\
-                     \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus & $1.7\times 10^{5}$ & $ 0.945$ & $ 0.971$ & $ 0.512$ & $ 0.432$ & $ 0.585$ & $ 0.250$ \\
-                     African & Homo sapiens & $5.6\times 10^{4}$ & $ 0.911$ & $ 0.976$ & $ 0.579$ & $ 0.325$ & $ 0.721$ & $ 0.349$ \\
-                     Admixed American & Homo sapiens & $4.5\times 10^{4}$ & $ 0.902$ & $ 0.978$ & $ 0.584$ & $ 0.299$ & $ 0.690$ & $ 0.345$ \\
-                     East Asian & Homo sapiens & $ 4\times 10^{4}$ & $ 0.905$ & $ 0.978$ & $ 0.585$ & $ 0.325$ & $ 0.688$ & $ 0.249$ \\
-                     European & Homo sapiens & $4.2\times 10^{4}$ & $ 0.906$ & $ 0.978$ & $ 0.584$ & $ 0.329$ & $ 0.688$ & $ 0.248$ \\
-                     South Asian & Homo sapiens & $4.4\times 10^{4}$ & $ 0.908$ & $ 0.978$ & $ 0.584$ & $ 0.342$ & $ 0.691$ & $ 0.224$ \\
-                     \bottomrule
-              \end{tabular}
-       \end{adjustbox}
-       \caption{
-              \textit{Precision} and \textit{recall} for estimated selection coefficient of mutations given by mutation-selection models ($\Sphy$).
-              \textit{Precision} is the estimation of the selection coefficient at population scale ($\Spop$) given that $\Sphy$ is known.
-              Conversely, \textit{recall} is the estimation of $\Sphy$ given selection coefficient at the population scale ($\Spop$) is known.
-              \textit{Recall} for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is thus the proportion of beneficial back-mutations among all beneficial mutations.
-              $\Ne$ is the estimated effective population size for each population.
-       }
-       \label{table:proba}
-\end{table*}
-
-\begin{figure*}[htb]
-       \centering
-       \includegraphics[width=17.8cm, page=1]{figure4}
-       \caption{
-              Populations in circles, mean of the species across the populations as squares.
-              (A) Proportion of nearly-neutral mutations at the population scale ($\proba [ \SpopNeu]$ in the y-axis), shown as a function of estimated effective population size ($\Ne$ in the x-axis).
-              (B) Proportion of beneficial back-mutations among all beneficial mutations ($\proba [ \SphyBen  \given  \SpopBen]$ in the y-axis), shown as a function of $\Ne$ in x-axis.
-              Correlations account for phylogenetic relationship and non-independence of samples, through the fit of a Phylogenetic Generalized Linear Model (see section~\ref{subsec:s-polymorphism-method} in Materials \& Methods).
-       }
-       \label{fig:diversity}
-\end{figure*}
-
-\section*{Discussion}\label{sec:discussion}
-
+    \section*{Discussion}
     \subsection*{Beneficial mutations are not necessarily adaptive}
@@
 
-\matmethods{
+    \section{Materials \& Methods}
+    \label{sec:methods}
+
     \subsection{Phylogenetic dataset}\label{subsec:phylo-dataset}
 
-       Protein-coding DNA sequence alignments in placental mammals and their corresponding gene trees come from the \href{https://www.orthomam.univ-montp2.fr}{OrthoMaM} database and were processed as in \cite[Latrille et al]{latrille_genes_2023}.
+    Protein-coding DNA sequence alignments in placental mammals and their corresponding gene trees come from the \href{https://www.orthomam.univ-montp2.fr}{OrthoMaM} database and were processed as in \textcite{latrille_genes_2023}.
     OrthoMaM contains a total of $116$ mammalian reference sequences in v10c~\cite{ranwez_orthomam_2007, douzery_orthomam_2014, scornavacca_orthomam_2019}.
@@
     We used the Bayesian software \textit{BayesCode} (\url{https://github.com/ThibaultLatrille/bayescode}, v1.3.1) to estimate the selection coefficients for each protein-coding gene in the mammalian dataset.
-       We ran the MCMC algorithm implemented in BayesCode for $2,000$ generations as described in \cite[Latrille et al]{latrille_genes_2023}.
+    We ran the MCMC algorithm implemented in BayesCode for $2,000$ generations as described in \textcite{latrille_genes_2023}.
     For each gene, after discarding a burn-in period of $1,000$ generations of MCMC, we obtained posterior mean estimates (over the $1,000$ generations left of MCMC) of the mutation rate matrix ($\UniDimArray{\mu}$) as well as the $20$ amino-acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$.
@@
     In total, we analyzed 28 populations across the 6 different species with polymorphism data.
-       The data was processed as described in \cite[Latrille et al]{latrille_genes_2023}.
+    The data was processed as described in \textcite{latrille_genes_2023}.
 
@@
         \proba [ \SpopDel \given  \Sphyclass] &= \proba [ \Spop < -1 \given \Sphyclass ] = \left( 1 - p_b \right) \int_{1}^{+\infty} f_{\Gamma}(\Spop; -\DelMean, b) \der \Spop, \label{eq:polyProbaDel} \\
-              \proba [ \SpopNeu \given \Sphyclass] &= \proba [ -1 < \Spop < 1 \given \Sphyclass ] = p_b \int_{0}^{1} f_{e}(\Spop; \AdvMean) \der \Spop + \\ \nonumber &\left( 1 - p_b \right) \int_{0}^{1} f_{\Gamma}(\Spop; -\DelMean, b) \der \Spop, \\
+        \proba [ \SpopNeu \given \Sphyclass] &= \proba [ -1 < \Spop < 1 \given \Sphyclass ] = p_b \int_{0}^{1} f_{e}(\Spop; \AdvMean) \der \Spop + \left( 1 - p_b \right) \int_{0}^{1} f_{\Gamma}(\Spop; -\DelMean, b) \der \Spop, \\
         \proba [ \SpopBen \given \Sphyclass] &= \proba [ \Spop > 1 \given \Sphyclass] = p_b \int_{1}^{+\infty} f_{e}(\Spop; \AdvMean) \der \Spop. \label{eq:polyProbaAdv}
@@
     \label{subsec:correlation-diversity}
-       Genetic diversity estimator Watterson's $\thetaSyn$ was obtained for each population from the synonymous SFS as in \cite[Achaz]{achaz_frequency_2009}.
+    Genetic diversity estimator Watterson's $\thetaSyn$ was obtained for each population from the synonymous SFS as in \textcite{achaz_frequency_2009}.
     For each popuation, $\Ne$ was estimated from the equation $\Ne=\thetaSyn / (4 \times u)$, where $u$ is the mutation rate per generation.
-       Estimates for $u$ were averaged per species across the pedigree-based estimation in \cite[Bergeron et al]{bergeron_evolution_2023} for \textit{Homo}, \textit{Bos}, \textit{Capra} and \textit{Chlorocebus}.
+    Estimates for $u$ were averaged per species across the pedigree-based estimation in \textcite{bergeron_evolution_2023} for \textit{Homo}, \textit{Bos}, \textit{Capra} and \textit{Chlorocebus}.
     For \textit{Ovis} we used the estimated $u$ of \textit{Capra}.
-       For \textit{Equus}, we used $u$ as estimated in \cite[Orlando et al]{orlando_recalibrating_2013} ($u=7.24\times10^{-9}$).
+    For \textit{Equus}, we used $u$ as estimated in \textcite{orlando_recalibrating_2013} ($u=7.24\times10^{-9}$).
     Because a correlation must account for phylogenetic relationship and non-independence of samples, we fitted a Phylogenetic Generalized Linear Model in \textit{R} with the package \texttt{caper}~\cite{orme_caper_2013}.
@@
 
-       \section{Data availability}\label{sec:data-availability}
+    \section*{Data availability}
     The data underlying this article are available at \url{https://doi.org/10.5281/zenodo.7878954}.
     Snakemake pipeline, analysis scripts and documentation are available at \href{https://github.com/ThibaultLatrille/SelCoeff}{github.com/ThibaultLatrille/SelCoeff}.
-}
 
-\showmatmethods{} % Display the Materials and Methods section
-
-\acknow{
+    \section*{Acknowledgements}
+    \label{sec:acknowledgment}
     We gratefully acknowledge the help of Mélodie Bastian, Nicolas Lartillot, Carina Farah Mugal, Laurent Duret, Alexandre Reymond, Daniele Silvestro and Nicolas Gambardella for their advice and reviews concerning this manuscript.
@@
     The European Union’s Seventh Framework Programme (FP7/2010-2014) provided funding for the project under grant agreement no 244356 - “NextGen”.
+
+    \section*{Competing interests}
+    The authors declare no conflicts of interest.
+
+    \section*{Author information}
+    Original idea: T.L.\ and J.J.;
+    Model conception: T.L., J.J.\ and N.S.;
+    Code: T.L.;
+    Data analyses: T.L.\ and J.J.;
+    Interpretation: T.L., J.J., D.A.H.\ and N.S.;
+    First draft: T.L.\ and J.J.;
+    Editing and revisions: T.L., J.J., D.A.H.\ and N.S.
+    Project management and funding: N.S\@.
+
+%TC:ignore
+    \printbibliography
+%TC:endignore
+\newpage
+    \begin{figure*}[!htb]
+        \centering
+        \includegraphics[width=\textwidth, page=1] {artworks/figure.fitness-landscape}
+        \caption{
+            (A \& B) For a given codon position of a protein-coding DNA sequence, amino acids (x-axis) have different fitness values (y-axis).
+            Under a fluctuating fitness landscape (A), these fitnesses change with time.
+            The protein sequence follows the moving target defined by the amino-acid fitnesses.
+Since substitutions are preferentially accepted if they are in the direction of this target, substitutions are, on average, adaptive.
+            At the phylogenetic scale (C), beneficial substitutions are common (positive signs), promoting phenotype diversification across species.
+            Under a stable fitness landscape (B), most mutations reaching fixation are either slightly deleterious reaching fixation due to drift or are beneficial back-mutations restoring a more optimal amino acid.
+            At the phylogenetic scale (D), deleterious substitutions (negative signs) are often reverted via beneficial back-mutations (positive signs), promoting phenotype stability and preserving well-established biological systems.
+            Even though, individually, any back-mutation might have a small beneficial effect on its bearer, we expect beneficial back-mutations to be scattered across the genome and the genome-wide signature of beneficial back-mutations to be detectable and quantifiable.}
+        \label{fig:fitness-landscape}
+    \end{figure*}
+
+    \begin{figure*}[!h]
+        \centering
+        \includegraphics[width=\textwidth, page=1] {artworks/figure.method.proba}
+        \caption{
+            Selection coefficients at the phylogenetic and population scales.
+            At the phylogenetic scale (A), we estimated the amino-acid fitness for each site from protein-coding DNA alignments using mutation-selection codon models.
+            For every possible mutation, the difference in amino-acid fitness before and after the mutation allows us to compute the selection coefficient at the phylogenetic scale ($\Sphy$).
+            Depending on $\Sphy$ (B) mutations can be predicted as deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) or beneficial back-mutations ($\SphyBen$) toward a fitter amino acid and repairing existing functions.
+            At the population scale, each observed single nucleotide polymorphism (SNP) segregating in the population can also be classified according to its $\Sphy$ value (C).
+            Occurrence and frequency in the population of non-synonymous polymorphisms, contrasted to synonymous polymorphisms (deemed neutral) is used to estimate selection coefficients (D-E) at the population scale ($\Spop$), for each class of selection ($\SphyDel$, $\SphyNeu$, $\SphyBen$).
+            We can thus assess whether $\Sphy$ predicts $\Spop$ and compute \textit{precision} (F) and \textit{recall} (G) for each class.
+            The \textit{recall} value for class $\SphyBen$ is the probability of back-mutations among all beneficial ones (G).
         }
+        \label{fig:method}
+    \end{figure*}
 
-\showacknow{} % Display the acknowledgments section
+    \begin{figure*}[!h]
+        \centering
+        \includegraphics[width=\textwidth, page=1] {artworks/figure.homo-afr-results}
+        \caption{
+            (A) Distribution of scaled selection coefficients ($\Sphy$), predicted for all possible non-synonymous DNA mutations away from the ancestral human exome (section \ref{subsec:nunber-of-sites}).
+            Mutations are divided into three classes of selection: deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial ($\SphyBen$, supposedly beneficial back-mutations)
+            (B) Distribution of scaled selection coefficients ($\Sphy$) for all observed substitutions along the \textit{Homo} branch after the \textit{Homo}-\textit{Pan} split (section \ref{subsec:substitution-mapping-in-the-terminal-branch}).
+            If there are fewer substitutions than expected, this class is thus undergoing purifying selection, as is the case for $\SphyDel$.
+            (C) The site-frequency spectrum (SFS) in humans of African descent for a random sample of 16 alleles (means in solid lines and standard deviations in color shades) for each class of selection and for synonymous mutations, supposedly neutral (black).
+The SFS represents the proportion of mutations (y-axis) with a given number of derived alleles in the population (x-axis).
+            At high frequencies, deleterious mutations are underrepresented.
+            (D) Proportion of beneficial $\ProbaPopDel$, nearly-neutral $\ProbaPopNeu$, and deleterious mutations $\ProbaPopBen$ estimated at the population scale for each class of selection at the phylogenetic scale (section \ref{subsec:s-polymorphism-method}).
+Proportions depicted here are not weighted by their mutational opportunities.
+        }
+        \label{fig:homo-afr-results}
+    \end{figure*}
 
-% Bibliography
-\bibliography{references_bibtex}
+    \begin{figure*}[!ht]
+        \centering
+        \includegraphics[width=\textwidth, page=1] {artworks/figure.diversity}
+        \caption{
+            Populations in circles, mean of the species across the populations as squares.
+            (A) Proportion of nearly-neutral mutations at the population scale ($\proba [ \SpopNeu]$ in the y-axis), shown as a function of estimated effective population size ($\Ne$ in the x-axis).
+            (B) Proportion of beneficial back-mutations among all beneficial mutations ($\proba [ \SphyBen  \given  \SpopBen]$ in the y-axis), shown as a function of $\Ne$ in x-axis.
+            Correlations account for phylogenetic relationship and non-independence of samples, through the fit of a Phylogenetic Generalized Linear Model (see section~\ref{subsec:s-polymorphism-method} in Materials \& Methods).
+        }
+        \label{fig:diversity}
+    \end{figure*}
 
+    \begin{table*}[tb]
+%TC:ignore
+        \centering
+        \begin{adjustbox}{width=\textwidth}
+            \begin{tabular}{||l|l|r||r|r||r|r||r|r||}
+                \toprule
+                \multicolumn{3}{||c||}{} &
+                \multicolumn{2}{c||}{\shortstack{\textbf{Deleterious mutations} \\ $\bm{\SpopDel \coloneqq \Spop<-1}$ \\ $\bm{\SphyDel \coloneqq \Sphy<-1}$}} &
+                \multicolumn{2}{c||}{\shortstack{\textbf{Nearly-neutral mutations} \\ $\bm{\SpopNeu \coloneqq -1<\Spop<1}$ \\ $\bm{\SphyNeu \coloneqq -1<\Sphy<1}$}} &
+                \multicolumn{2}{c||}{\shortstack{\textbf{Beneficial mutations} \\ $\bm{\SpopBen \coloneqq \Spop>1}$ \\ $\bm{\SphyBen \coloneqq \Sphy>1}$}}
+                \\ \hline
+                \textbf{Population} &
+                \textbf{Species} &
+                $\bm{\Ne}$ &
+                \makecell{\textbf{Precision} \\ $\bm{\proba [\SpopDel \given \SphyDel]}$} &
+                \makecell{\textbf{Recall} \\ $\bm{\proba [\SphyDel \given \SpopDel]}$}            &
+                \makecell{\textbf{Precision}      \\ $\bm{\proba [\SpopNeu \given \SphyNeu]}$}                                    &
+                \makecell{\textbf{Recall}          \\ $\bm{\proba [\SphyNeu \given \SpopNeu]}$}                                  &
+                \makecell{\textbf{Precision}          \\ $\bm{\proba [\SpopBen \given \SphyBen]}$}          &
+                \makecell{\textbf{Recall}        \\ $\bm{\proba [\SphyBen \given \SpopBen]}$}
+                \\   \midrule
+                \rowcolor{LIGHTGREY} Equus c. & Equus caballus & $7.5\times 10^{4}$ & $ 0.923$ & $ 0.972$ & $ 0.570$ & $ 0.341$ & $ 0.648$ & $ 0.536$ \\
+                Iran & Bos taurus & $5.6\times 10^{4}$ & $ 0.915$ & $ 1.000$ & $ 0.632$ & $ 0.358$ & $ 0.873$ & $ 0.243$ \\
+                Uganda & Bos taurus & $1.3\times 10^{5}$ & $ 0.951$ & $ 0.969$ & $ 0.495$ & $ 0.414$ & $ 0.576$ & $ 0.415$ \\
+                \rowcolor{LIGHTGREY} Australia & Capra hircus & $1.7\times 10^{5}$ & $ 0.944$ & $ 0.971$ & $ 0.527$ & $ 0.437$ & $ 0.368$ & $ 0.177$ \\
+                \rowcolor{LIGHTGREY} France & Capra hircus & $1.9\times 10^{5}$ & $ 0.946$ & $ 0.971$ & $ 0.508$ & $ 0.423$ & $ 0.368$ & $ 0.190$ \\
+                \rowcolor{LIGHTGREY} Iran (C. aegagrus) & Capra hircus & $1.9\times 10^{5}$ & $ 0.948$ & $ 0.969$ & $ 0.486$ & $ 0.444$ & $ 0.368$ & $ 0.165$ \\
+                \rowcolor{LIGHTGREY} Iran & Capra hircus & $2.3\times 10^{5}$ & $ 0.953$ & $ 0.966$ & $ 0.425$ & $ 0.407$ & $ 0.368$ & $ 0.193$ \\
+                \rowcolor{LIGHTGREY} Italy & Capra hircus & $1.9\times 10^{5}$ & $ 0.947$ & $ 0.971$ & $ 0.551$ & $ 0.439$ & $ 0.368$ & $ 0.243$ \\
+                \rowcolor{LIGHTGREY} Morocco & Capra hircus & $2.2\times 10^{5}$ & $ 0.950$ & $ 0.970$ & $ 0.527$ & $ 0.440$ & $ 0.368$ & $ 0.245$ \\
+                Iran & Ovis aries & $3.8\times 10^{5}$ & $ 0.961$ & $ 0.961$ & $ 0.452$ & $ 0.415$ & $ 0.205$ & $ 0.407$ \\
+                Iran (O. orientalis) & Ovis aries & $4.5\times 10^{5}$ & $ 0.964$ & $ 0.960$ & $ 0.420$ & $ 0.445$ & $ 0.193$ & $ 0.190$ \\
+                Iran (O. vignei) & Ovis aries & $3.7\times 10^{5}$ & $ 0.967$ & $ 0.959$ & $ 0.361$ & $ 0.470$ & $ 0.190$ & $ 0.110$ \\
+                Various & Ovis aries & $4.1\times 10^{5}$ & $ 0.962$ & $ 0.962$ & $ 0.433$ & $ 0.440$ & $ 0.229$ & $ 0.222$ \\
+                Morocco & Ovis aries & $ 4\times 10^{5}$ & $ 0.962$ & $ 0.961$ & $ 0.462$ & $ 0.424$ & $ 0.211$ & $ 0.514$ \\
+                \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus & $1.1\times 10^{5}$ & $ 0.935$ & $ 0.975$ & $ 0.565$ & $ 0.402$ & $ 0.648$ & $ 0.293$ \\
+                \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus & $1.7\times 10^{5}$ & $ 0.948$ & $ 0.971$ & $ 0.508$ & $ 0.423$ & $ 0.535$ & $ 0.275$ \\
+                \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus & $1.4\times 10^{5}$ & $ 0.935$ & $ 0.975$ & $ 0.580$ & $ 0.416$ & $ 0.552$ & $ 0.245$ \\
+                \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus & $1.4\times 10^{5}$ & $ 0.944$ & $ 0.975$ & $ 0.654$ & $ 0.437$ & $ 0.577$ & $ 0.821$ \\
+                \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus & $1.5\times 10^{5}$ & $ 0.946$ & $ 0.972$ & $ 0.538$ & $ 0.453$ & $ 0.588$ & $ 0.257$ \\
+                \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus & $ 1\times 10^{5}$ & $ 0.933$ & $ 0.976$ & $ 0.629$ & $ 0.412$ & $ 0.599$ & $ 0.358$ \\
+                \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus & $1.8\times 10^{5}$ & $ 0.944$ & $ 0.971$ & $ 0.548$ & $ 0.423$ & $ 0.574$ & $ 0.341$ \\
+                \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus & $1.2\times 10^{5}$ & $ 0.936$ & $ 0.975$ & $ 0.586$ & $ 0.402$ & $ 0.598$ & $ 0.336$ \\
+                \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus & $1.7\times 10^{5}$ & $ 0.945$ & $ 0.971$ & $ 0.512$ & $ 0.432$ & $ 0.585$ & $ 0.250$ \\
+                African & Homo sapiens & $5.6\times 10^{4}$ & $ 0.911$ & $ 0.976$ & $ 0.579$ & $ 0.325$ & $ 0.721$ & $ 0.349$ \\
+                Admixed American & Homo sapiens & $4.5\times 10^{4}$ & $ 0.902$ & $ 0.978$ & $ 0.584$ & $ 0.299$ & $ 0.690$ & $ 0.345$ \\
+                East Asian & Homo sapiens & $ 4\times 10^{4}$ & $ 0.905$ & $ 0.978$ & $ 0.585$ & $ 0.325$ & $ 0.688$ & $ 0.249$ \\
+                European & Homo sapiens & $4.2\times 10^{4}$ & $ 0.906$ & $ 0.978$ & $ 0.584$ & $ 0.329$ & $ 0.688$ & $ 0.248$ \\
+                South Asian & Homo sapiens & $4.4\times 10^{4}$ & $ 0.908$ & $ 0.978$ & $ 0.584$ & $ 0.342$ & $ 0.691$ & $ 0.224$ \\
+                \bottomrule
+            \end{tabular}
+        \end{adjustbox}
+%TC:endignore
+        \caption{
+            \textit{Precision} and \textit{recall} for estimated selection coefficient of mutations given by mutation-selection models ($\Sphy$).
+            \textit{Precision} is the estimation of the selection coefficient at population scale ($\Spop$) given that $\Sphy$ is known.
+            Conversely, \textit{recall} is the estimation of $\Sphy$ given selection coefficient at the population scale ($\Spop$) is known.
+            \textit{Recall} for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is thus the proportion of beneficial back-mutations among all beneficial mutations.
+            $\Ne$ is the estimated effective population size for each population.
+        }
+        \label{table:proba}
+    \end{table*}
 \end{document}

### 2024-03-04 manuscript/main-PNAS.tex
Manuscript revision 2

@@
 To quantify the rate of adaptation, population geneticists have typically used signatures of positive selection.
-       However, mutations restoring an ancestral sequence of higher fitness lost by genetic drift are also positively selected, but they do not respond to a change in the environment.
+However, mutations restoring an ancestral state of higher fitness lost by genetic drift are also positively selected, but they do not respond to a change in the environment.
 In this study, we have managed to distinguish beneficial mutations that are due to changing environments and those that are restoring pre-existing functions in mammals.
@@
 % Keywords are not mandatory, but authors are strongly encouraged to provide them. If provided, please include two to five keywords, separated by the pipe symbol, e.g:
-\keywords{Adaptation $|$ Back-mutations $|$ Phylogenetics $|$ Population-genetics $|$ Codon models }
+\keywords{Adaptation $|$ Nearly-neutral $|$ Phylogenetics $|$ Population-genetics $|$ Codon models }
 
@@
 These mutations are typically unpredictable since they respond to an unforeseen change in the environment.
-However, mutations can also be beneficial because they are simply restoring an ancestral sequence of higher fitness that was lost due to genetic drift.
-In contrast to adaptive mutations, these beneficial back-mutations can be predicted if the underlying fitness landscape is stable and known.
-The contribution of such beneficial back-mutations to molecular evolution has been widely neglected mainly because their detection is very challenging.
+However, mutations can also be beneficial because they are simply restoring a state of higher fitness that was lost due to genetic drift in a stable environment.
+In contrast to adaptive mutations, these beneficial non-adaptive mutations can be predicted if the underlying fitness landscape is stable and known.
+The contribution of such non-adaptive mutations to molecular evolution has been widely neglected mainly because their detection is very challenging.
 We have here reconstructed protein-coding-gene fitness landscapes shared between mammals, using mutation-selection models and a multi-species alignments across 87 mammals.
 These fitness landscapes have allowed us to predict the fitness effect of polymorphisms found in 28 mammalian populations.
-Using methods that quantify selection at the population level, we have confirmed that beneficial back-mutations are indeed positively selected in extant populations.
+Using methods that quantify selection at the population level, we have confirmed that beneficial non-adaptive mutations are indeed positively selected in extant populations.
 Our work confirms that deleterious substitutions are accumulating in mammals and are being reverted, generating a balance in which genomes are damaged and restored simultaneously at different loci.
-We observe that beneficial back-mutations represent between 15\% and 45\% of all beneficial mutations in 24 of 28 populations analyzed, showing that a substantial part of ongoing positive selection is not driven by adaptation to environmental change in mammals.
+We observe that beneficial non-adaptive mutations represent between 15\% and 45\% of all beneficial mutations in 24 of 28 populations analyzed, showing that a substantial part of ongoing positive selection is not driven solely by adaptation to environmental change in mammals.
 \end{abstract}
@@
 
-\firstpage[3]{3}
+\firstpage[1]{2}
 \dropcap{A}daptation is one of the main processes shaping the diversity of forms and functions across the tree of life~\cite{darwin_origin_1859}.
@@
 
-In a constant environment, a deleterious mutation can reach fixation by genetic drift~\cite{Ohta1992}.
+\subsection*{Beneficial yet non-adaptive mutations}
+
+In a constant environment, a deleterious mutation can reach fixation by genetic drift~\cite{ohta_nearly_1992}.
 A new mutation restoring the ancestral fitness will thus be beneficial (fig.~\ref{fig:fitness-landscape}B), even though the environment has not changed~\cite{gillespie_ohta_1995, hartl_compensatory_1996, sella_application_2005, mustonen_fitness_2009, cvijovic_fate_2015}.
-The restoration of the ancestral fitness can either happen through a mutation at a different locus –~called a compensatory mutation~\cite{hartl_compensatory_1996, mustonen_fitness_2009}, or at the locus of the initial mutation –~called a beneficial back-mutation~\cite{piganeau_estimating_2003, charlesworth_other_2007}.
-While compensatory mutations change the sequence and thus induce genetic diversification, beneficial back-mutations reduce genetic diversity and do not contribute to genetic innovation.
-
-Although Tomoko Ohta considered beneficial back-mutations negligible in her nearly-neutral theory~\cite{Ohta1992}, their importance has now been acknowledged for
-expanding populations~\cite{charlesworth_other_2007}.
-However, differentiating between an adaptive mutation and a beneficial back-mutation remains challenging~\cite{chi_detecting_2020}.
-Indeed, an adaptive mutation responding to a change in the environment and a beneficial back-mutation have equivalent fitness consequences for their bearer~\cite{charlesworth_other_2007}.
+We will refer to as beneficial non-adaptive mutations to those mutations that restore the ancestral fitness under the assumption that the fitness landscape has not changed~\cite{piganeau_estimating_2003, charlesworth_other_2007}.
+Such mutations can happen through a mutation at a different locus, in which case it is called a compensatory mutation~\cite{hartl_compensatory_1996, mustonen_fitness_2009}.
+While compensatory mutations change the sequence and thus induce genetic diversification, beneficial non-adaptive mutations at the locus of the initial mutation reduce genetic diversity and do not contribute to genetic innovation, which are the focus of this manuscript.
+Although Tomoko Ohta considered beneficial non-adaptive mutations negligible in her nearly-neutral theory~\cite{ohta_nearly_1992}, their importance has now been acknowledged for expanding populations~\cite{charlesworth_other_2007}.
+However, differentiating between an adaptive mutation and a beneficial non-adaptive mutation remains challenging~\cite{chi_detecting_2020}.
+Indeed, an adaptive mutation responding to a change in the environment and a beneficial non-adaptive mutation have equivalent fitness consequences for their bearer~\cite{charlesworth_other_2007}.
 Similarly, at the population level, both types of mutations will result in a positive transmission bias of the beneficial allele.
 However, at the macro-evolutionary scale, the consequences of these two types of mutations are fundamentally different.
-While adaptive mutations promote phenotype diversification (fig.~\ref{fig:fitness-landscape}C), beneficial back-mutations promote phenotype stability and may help preserve well-established biological systems (fig.~\ref{fig:fitness-landscape}D).
+While adaptive mutations promote phenotype diversification (fig.~\ref{fig:fitness-landscape}C), beneficial non-adaptive mutations promote phenotype stability and may help preserve well-established biological systems (fig.~\ref{fig:fitness-landscape}D).
 Additionally, the direction of adaptive evolution is unpredictable because it is caused by an unforeseen change in the environment and, hence, in the underlying fitness landscape~\cite{bazykin_changing_2015}.
-On the other hand, beneficial back-mutations are predictable because, under a stable fitness landscape, any change from non-optimal to optimal amino acids will move back the site towards the equilibrium expected under the fitness landscape~\cite{moses_inferring_2009, fischer_germline_2011, chen_hunting_2021}.
-It can then be distinguished from truly novel beneficial mutations because the latter are not expected to mutate mutate towards the amino acids of higher fitnesses defined by the stable fitness landscape but rather mutate to amino acids showing a diversified pattern (fig.~\ref{fig:fitness-landscape}).
+On the other hand, beneficial non-adaptive mutations are predictable because, under a stable fitness landscape, any change from non-optimal to optimal amino acids will move back the site toward the equilibrium expected under the fitness landscape~\cite{moses_inferring_2009, fischer_germline_2011, chen_hunting_2021}.
+They can then be distinguished from truly novel beneficial mutations because the latter are not expected to mutate toward the amino acids of higher fitnesses defined by the stable fitness landscape but rather mutate to amino acids showing a diversified pattern (fig.~\ref{fig:fitness-landscape}).
 
@@
               At the phylogenetic scale (C), beneficial substitutions are common (positive signs), promoting phenotype diversification across species.
-              Under a stable fitness landscape (B), most mutations reaching fixation are either slightly deleterious reaching fixation due to drift or are beneficial back-mutations restoring a more optimal amino acid.
-              At the phylogenetic scale (D), deleterious substitutions (negative signs) are often reverted via beneficial back-mutations (positive signs), promoting phenotype stability and preserving well-established biological systems.
-              Even though, individually, any back-mutation might have a small beneficial effect on its bearer, we expect beneficial back-mutations to be scattered across the genome and the genome-wide signature of beneficial back-mutations to be detectable and quantifiable.}
+              Under a stable fitness landscape (B), most mutations reaching fixation are either slightly deleterious reaching fixation due to drift or are beneficial non-adaptive mutations restoring a more optimal amino acid.
+              At the phylogenetic scale (D), deleterious substitutions (negative signs) are often reverted via beneficial non-adaptive mutations (positive signs), promoting phenotype stability and preserving well-established biological systems.
+              Even though, individually, any beneficial non-adaptive mutation might have a weak effect on its bearer, we expect them to be scattered across the genome and the genome-wide signature of beneficial non-adaptive mutations to be detectable and quantifiable.}
        \label{fig:fitness-landscape}
@@
               For every possible mutation, the difference in amino-acid fitness before and after the mutation allows us to compute the selection coefficient at the phylogenetic scale ($\Sphy$).
-              Depending on $\Sphy$ (B) mutations can be predicted as deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) or beneficial back-mutations ($\SphyBen$) toward a fitter amino acid and repairing existing functions.
+              Depending on $\Sphy$ (B) mutations can be predicted as deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) or beneficial non-adaptive mutations ($\SphyBen$) toward a fitter amino acid and repairing existing functions.
               At the population scale, each observed single nucleotide polymorphism (SNP) segregating in the population can also be classified according to its $\Sphy$ value (C).
@@
               We can thus assess whether $\Sphy$ predicts $\Spop$ and compute \textit{precision} (F) and \textit{recall} (G) for each class.
-              The \textit{recall} value for class $\SphyBen$ is the probability of back-mutations among all beneficial ones (G).
+              The \textit{recall} value for class $\SphyBen$ is the probability for beneficial mutations to be non-adaptive (G).
        }
@@
 
-Theoretically, we can thus use large-scale genomic data to assess whether the fitness estimated at the phylogenetic scale predict the fitness effect at the population scale for both deleterious and beneficial back-mutations.
+Theoretically, we can thus use large-scale genomic data to assess whether the fitness estimated at the phylogenetic scale predicts the fitness effect at the population scale for both deleterious and beneficial non-adaptive mutations.
 The placental mammals represent an excellent study system to perform such analysis.
@@
 The value of $\Sphy$ informs us on the strength of selection exerted on amino acids changes.
-Thus, according to its $\Sphy$ value, we can classify any mutation as either a deleterious mutation toward a less fit amino acid ($\SphyDel \coloneqq \Sphy < -1$), a nearly-neutral mutation ($\SphyNeu \coloneqq -1 < \Sphy <1$) or a beneficial back-mutation toward a known fitter amino acid ($\SphyBen \coloneqq \Sphy > 1$).
+Thus, according to its $\Sphy$ value, we can classify any mutation as either a deleterious mutation toward a less fit amino acid ($\SphyDel \coloneqq \Sphy < -1$), a nearly-neutral mutation ($\SphyNeu \coloneqq -1 < \Sphy <1$), or a mutation toward a known fitter amino acid constituting thus a beneficial non-adaptive mutation ($\SphyBen \coloneqq \Sphy > 1$).
 
-Having identified which potential DNA changes represent beneficial back-mutations (fig.~\ref{fig:method}B), we retrieved polymorphism data from 28 wild and domesticated populations belonging to 6 genera (\textit{Equus}, \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus}, and \textit{Homo}) to assess the presence of beneficial back-mutations at the population scale.
-We focused on mutations currently segregating within populations and substitutions in the terminal branches, and checked if any of these observed changes were beneficial back-mutations (fig.~\ref{fig:method}C-E).
-A similar approach demonstrated the presence of beneficial back-mutations in humans~\cite{moses_inferring_2009, fischer_germline_2011} and in plants~\cite{chen_hunting_2021}.
+Having identified which potential DNA changes represent beneficial non-adaptive mutations (fig.~\ref{fig:method}B), we retrieved polymorphism data from 28 wild and domesticated populations belonging to six genera (\textit{Equus}, \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus}, and \textit{Homo}) to assess the presence of beneficial non-adaptive mutations at the population scale.
+We focused on mutations currently segregating within populations and substitutions in the terminal branches, and checked if any of these observed changes were indeed beneficial (fig.~\ref{fig:method}C-E).
+A similar approach demonstrated the presence of beneficial non-adaptive mutations in humans~\cite{moses_inferring_2009, fischer_germline_2011} and in plants~\cite{chen_hunting_2021}.
 However, the model used to reconstruct the static fitness landscape in these studies can only be applied to deeply conserved protein domains in the tree of life, which corresponds to a subpart of the proteome that evolves slowly.
-The mutation-selection model used in the present work integrates phylogenetic relationships, and thus allows us to estimate the fitness landscape in shallower phylogenetic trees, and therefore can be applied almost genome-wide~\cite{rodrigue_mutationselection_2010}.
+The mutation-selection model used in the present work integrates phylogenetic relationships, and thus allows us to estimate the fitness landscape in shallower phylogenetic trees, and therefore can be applied almost exome-wide~\cite{rodrigue_mutationselection_2010}.
 
-We first quantified the likelihood of any DNA mutation to be a beneficial back-mutation, that is, whenever a DNA mutation increases fitness under a stable fitness landscape ($\SphyBen$).
-Subsequently, by quantifying the total amount of beneficial mutations in the current population across all types of DNA mutations ($\SphyDel$, $\SphyDel$ and $\SphyBen$), we could tease apart beneficial back-mutations from beneficial adaptive mutations resulting from a change in the fitness landscape.
-Altogether, in this study, by integrating large-scale genomic datasets at both phylogenetic and population scales, we propose a way to explicitly quantify the contribution of beneficial back-mutations to positive selection across the entire exome of the six genera (figs.~\ref{fig:method}F-G).
+We first quantified the likelihood of any DNA mutation to be a beneficial non-adaptive mutation, that is, whenever a DNA mutation increases fitness under a stable fitness landscape ($\SphyBen$).
+Subsequently, by quantifying the total amount of beneficial mutations in the current population across all types of DNA mutations ($\SphyDel$, $\SphyNeu$ and $\SphyBen$), we could tease apart beneficial non-adaptive from adaptive mutations resulting from a change in the fitness landscape.
+Altogether, in this study, by integrating large-scale genomic datasets at both phylogenetic and population scales, we propose a way to explicitly quantify the contribution of beneficial non-adaptive mutations to positive selection across the entire exome of the six genera (figs.~\ref{fig:method}F-G).
 
-\section*{Results}\label{sec:results}
+\section*{Results}
 
@@
 We classified each substitution identified in the terminal branches as either $\SphyDel$, $\SphyNeu$, or $\SphyBen$ depending on its $\Sphy$ value obtained at the phylogenetic scale (fig.~\ref{fig:method}A-C).
-Importantly, the mammalian alignment used to estimate the amino-acid fitness landscape did not include the genera for which we estimated selection at the population scale as this would bias the estimate of the fitness landscape and generate circular reasoning.
-Because $\Sphy$ was based on estimating fitness effects at the phylogenetic scale for all mammals, substitutions with $\Sphy>1$ ($\SphyBen$) bring the population toward an amino acid predicted to be fitter in mammals.
-These changes are thus considered as beneficial back-substitutions rather than a species-specific adaptive change.
-Among all the substitutions found in each terminal branch, between 10 and 13\% were $\SphyBen$, while instead beneficial back-mutations represent between 0.9 and 1.2\% of all non-synonymous mutations (table~S1 and fig.~\ref{fig:homo-afr-results}A-B for humans).
-In principle, beneficial back-mutations are bound to reach fixation more often than neutral mutations.
-Hence, we calculated the $\dnds$ ratio of non-synonymous over synonymous divergence for all terminal lineages, focusing on the non-synonymous changes predicted as beneficial back-mutations ($\dn(\SphyBen) / \ds$).
-We obtained values between 1.17 and 1.75 in the different lineages (table~S2), implying i) that $\SphyBen$ mutations reached fixation more frequently than synonymous mutations that are supposed to be neutral, and ii) that these back-mutations are effectively beneficial.
+Because estimation $\Sphy$ was based on the assumption that the fitness landscape is stable across mammals, $\SphyBen$ mutations (i.e., with $\Sphy>1$) bring the bearer of this mutation toward an amino acid predicted to be fitter across mammals.
+Importantly, the mammalian alignment used to estimate the amino acid fitness landscape did not include the six focal genera and their sister species.
+This ensures independence between, on the one hand, the fitness landscape estimated, and on the other hand, both substitutions that occurred in the terminal branches, and segregating polymorphisms of the focal populations.
+Example substitutions in the terminal lineage of \textit{Chlorocebus sabaeus} which are classified as $\SphyBen$ are shown in supplementary materials (section S2).
+For instance, in the mammalian protein-coding DNA alignment of gene \textit{SELE}, the nucleotide at site 1722 has mutated (from T to C) at the base of Simiiformes (monkeys and apes), modifying the corresponding amino acid from Serine to Proline, but has been subsequently reverted in the branch of \textit{Chlorocebus sabaeus} (fig.~S1).
+However, other substitutions classified as $\SphyBen$ in the terminal branch of \textit{Chlorocebus sabaeus} cannot be clearly interpreted as reversions along the terminal branch, and show several transitions to this amino acid across the mammalian phylogeny, as for instance site 3145 of gene \textit{THSD7A} (fig.~S2).
 
-This result further indicated that using $\dnds$ as an estimate of adaptation is biased due to the presence of beneficial back-mutations among the non-synonymous substitutions.
-By discarding all beneficial back-mutations we can obtain an estimate of $\dnds$ which is not inflated.
-By comparing these two ways of calculating $\dnds$ (see section~\ref{subsec:substitution-mapping-in-the-terminal-branch} in Materials \& Methods), we calculated that beneficial back-mutations inflate $\dnds$ values by between 9 and 12\% across genera while only representing between 0.9 and 1.2\% of non-synonymous mutations (table~S3).
+Among all the substitutions found in each terminal branch, between 10 and 13\% were $\SphyBen$, while $\SphyBen$ mutations only represent between 0.9 and 1.2\% of all non-synonymous mutations (table~S1 and fig.~\ref{fig:homo-afr-results}A-B for humans).
+Furthermore, since in principle, $\SphyBen$ mutations are bound to reach fixation more often than neutral mutations, we calculated the $\dnds$ ratio of non-synonymous over synonymous divergence for all terminal lineages, focusing on the non-synonymous changes predicted as $\SphyBen$ mutations ($\dn(\SphyBen) / \ds$).
+We obtained values between 1.17 and 1.75 in the different lineages (table~S2), meaning that $\SphyBen$ mutations reach fixation slightly more frequently than synonymous mutations that are supposed to be neutral, consistent with these $\SphyBen$ mutations being weakly beneficial.
+
+This result further indicates that using $\dnds$ as an estimate of adaptation is biased due to the presence of beneficial non-adaptive mutations among the non-synonymous substitutions.
+By discarding all beneficial non-adaptive mutations we can obtain an estimate of $\dnds$ which is not inflated.
+By comparing these two ways of calculating $\dnds$ (see section~\ref{subsec:substitution-mapping-in-the-terminal-branch} in Materials \& Methods), we calculated that beneficial non-adaptive mutations inflate $\dnds$ values by between 9 and 12\% across genera.
+This represents a substantial increase when considering that beneficial non-adaptive mutations only represent between 0.9 and 1.2\% of non-synonymous mutational opportunities (table~S3).
 
@@
 
-In humans, some SNPs have been associated with specific clinical prognosis terms obtained by clinical evaluation of the impact of variants on human Mendelian disorders ~\cite{landrum_clinvar_2018}.
+In humans, some SNPs have been associated with specific clinical prognosis terms obtained by clinical evaluation of the impact of variants on human Mendelian disorders~\cite{landrum_clinvar_2018}.
 Although this classification also relies on deep protein alignments and therefore cannot be considered an independent result from our own, it does provide a consistency check if the effect of a mutation on human health is in line with its fitness effect predicted by our method.
@@
 Our results show that SNPs predicted as deleterious are associated with clinical terms such as \textit{Likely Pathogenic} and \textit{Pathogenic}, implying that, in general, the selective pressure of a mutation exerted across mammals is also predictive of its clinical effect in humans (table~S4)~\cite{sullivan_leveraging_2023}.
-Conversely, back-mutations are associated with clinical terms such as \textit{Benign} and \textit{Likely Benign}, which shows that back-mutations are less likely to be functionally damaging (table~S5).
+Conversely, $\SphyBen$ mutations are associated with clinical terms such as \textit{Benign} and \textit{Likely Benign}, which shows that $\SphyBen$ mutations are less likely to be functionally damaging (table~S5).
 
@@
 The variable proportions between populations can be explained by the effective number of individuals in the population ($\Ne$), a major driver of selection efficacy.
-Moreover, estimates of mutation rate per generation ($u$), from \cite[Bergeron et al]{bergeron_evolution_2023} and \cite[Orlando et al]{orlando_recalibrating_2013}, and Watterson’s $\theta$ obtained from the synonymous SFS as in \cite[Achaz]{achaz_frequency_2009} allow us to obtain $\Ne$ through $\Ne=\theta/(4 \times u)$.
+Moreover, estimates of mutation rate per generation ($u$), from~\cite[Bergeron et al]{bergeron_evolution_2023} and~\cite[Orlando et al]{orlando_recalibrating_2013}, and Watterson’s $\theta$ obtained from the synonymous SFS as in~\cite[Achaz]{achaz_frequency_2009} allow us to obtain $\Ne$ through $\Ne=\theta/4 u)$.
 Using correlation analyses that accounted for phylogenetic relationship (see section \ref{subsec:correlation-diversity} in Materials \& Methods), we found that higher $\Ne$ was associated with a smaller proportion of nearly-neutral mutations ($r^2=0.31$, $p=0.001$, fig.~\ref{fig:diversity}A).
-This result follows the prediction of the nearly-neutral theory and suggests that in populations with higher diversity (e.g.,~\textit{Bos} or \textit{Ovis}), discrimination between beneficial and deleterious mutations is more likely to occur (figs.~S1-S3).
+This result follows the prediction of the nearly-neutral theory and suggests that in populations with higher diversity (e.g.,~\textit{Bos} or \textit{Ovis}), discrimination between beneficial and deleterious mutations is more likely to occur (figs.~S3-S5).
 Conversely, many more mutations are effectively neutral in populations with lower diversity (e.g.,~\textit{Homo}).
 
-Finally, mutations predicted to be beneficial back-mutations based on the selection coefficients at the phylogenetic scale ($\SphyBen$) were indeed beneficial for individuals bearing them, with a \textit{precision} (fig.~\ref{fig:method}F) in the range of 19--87\% (table~\ref{table:proba} and fig.~\ref{fig:homo-afr-results}D for humans).
-This result confirms that selection towards amino acids restoring existing functions is ongoing in these populations.
-Importantly, the \textit{recall} value in this case, computed as $\proba [ \SphyBen  \given  \SpopBen]$, is the probability for a beneficial mutation at the population scale to be a beneficial back-mutation, i.e., going toward a fitter amino acid (fig.~\ref{fig:method}G, table~S6).
+Finally, mutations predicted to be $\SphyBen$ were indeed beneficial for individuals bearing them, with a \textit{precision} (fig.~\ref{fig:method}F) in the range of 19--87\% (table~\ref{table:proba} and fig.~\ref{fig:homo-afr-results}D for humans).
+This result confirms that selection toward amino acids restoring existing functions is ongoing in these populations.
+Importantly, the \textit{recall} value in this case, computed as $\proba [ \SphyBen  \given  \SpopBen]$, is the probability for a beneficial mutation at the population scale to be a non-adaptive, i.e., going toward a  fitter amino acid given a stable fitness landscape (fig.~\ref{fig:method}G, table~S6).
 In other words, the \textit{recall} value quantifies the number of beneficial mutations restoring damaged genomes instead of creating adaptive innovations.
@@
 
-Because the phylogenetic mutation-selection codon model should fit better for genes with uniformly conserved functions, as a control, we filtered out genes under pervasive adaptation~\cite{latrille_genes_2023}, and indeed we found an increase in the proportion of beneficial back-mutations ($\proba [ \SphyBen  \given  \SpopBen]$), consistent with our expectation (Wilcoxon signed-rank, $s=80$, $p=0.002$, table~S7).
+Additionally, we controlled that these estimations are not affected by SNP mispolarization (figs.~S6-S7).
+Moreover, because the phylogenetic mutation-selection codon model should fit better for genes with uniformly conserved functions, as a control, we filtered out genes under pervasive adaptation~\cite{latrille_genes_2023}, and indeed we found an increase in the proportion of beneficial mutations that are non-adaptive ($\proba [ \SphyBen  \given  \SpopBen]$), consistent with our expectation (Wilcoxon signed-rank, $s=80$, $p=0.002$, table~S7).
 
@@
               (A) Distribution of scaled selection coefficients ($\Sphy$), predicted for all possible non-synonymous DNA mutations away from the ancestral human exome (section \ref{subsec:nunber-of-sites}).
-              Mutations are divided into three classes of selection: deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial ($\SphyBen$, supposedly beneficial back-mutations)
+              Mutations are divided into three classes of selection: deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial ($\SphyBen$, supposedly beneficial non-adaptive mutations)
               (B) Distribution of scaled selection coefficients ($\Sphy$) for all observed substitutions along the \textit{Homo} branch after the \textit{Homo}-\textit{Pan} split (section \ref{subsec:substitution-mapping-in-the-terminal-branch}).
@@
               Conversely, \textit{recall} is the estimation of $\Sphy$ given selection coefficient at the population scale ($\Spop$) is known.
-              \textit{Recall} for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is thus the proportion of beneficial back-mutations among all beneficial mutations.
+              \textit{Recall} for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is thus the proportion of beneficial non-adaptive mutations among all beneficial mutations.
               $\Ne$ is the estimated effective population size for each population.
@@
               (A) Proportion of nearly-neutral mutations at the population scale ($\proba [ \SpopNeu]$ in the y-axis), shown as a function of estimated effective population size ($\Ne$ in the x-axis).
-              (B) Proportion of beneficial back-mutations among all beneficial mutations ($\proba [ \SphyBen  \given  \SpopBen]$ in the y-axis), shown as a function of $\Ne$ in x-axis.
+              (B) Proportion of beneficial non-adaptive mutations among all beneficial mutations ($\proba [ \SphyBen  \given  \SpopBen]$ in the y-axis), shown as a function of $\Ne$ in x-axis.
               Correlations account for phylogenetic relationship and non-independence of samples, through the fit of a Phylogenetic Generalized Linear Model (see section~\ref{subsec:s-polymorphism-method} in Materials \& Methods).
@@
 
-\section*{Discussion}\label{sec:discussion}
-
+\section*{Discussion}
 \subsection*{Beneficial mutations are not necessarily adaptive}
@@
 This study represents an essential step toward integrating the different evolutionary scales necessary to understand the combined effects of mutation, selection, and drift on genome evolution.
-In particular, we have been able to quantify the proportion of beneficial back-mutations among all beneficial mutations, which has only been achievable by combining genome-wide data from both phylogenetic and population scales.
+In particular, we have been able to quantify the proportion of beneficial mutations that are non-adapative (i.e., not a response to a change in fitness landscape), which has only been achievable by combining exome-wide data from both phylogenetic and population scales.
 At the phylogenetic scale, codon diversity at each site of a protein-coding DNA alignment allows for reconstructing an amino-acid fitness landscape, assuming that this landscape is stable along the phylogenetic tree.
 These amino-acid fitness landscapes allow us to predict any mutation’s selection coefficient ($\Sphy$) along a protein-coding sequence.
-We can compare these selective effects to observations at the population level (figs.~S4-6).
-By doing so, we confirmed that mutations predicted to be deleterious ($\SphyDel \coloneqq \Sphy < -1$) are purified away in extant populations.
+We have compared these selective effects to observations at the population level (figs.~S8-10), and by doing so, we have confirmed that mutations predicted to be deleterious ($\SphyDel \coloneqq \Sphy < -1$) are generally purified away in extant populations.
 Our results concur with previous studies showing that SIFT scores~\cite{ng_sift_2003, vaser_sift_2016}, based on amino acid alignments across species, also inform on the deleterious fitness effects exerted at the population scale~\cite{chen_hunting_2021}.
-However – contrary to SIFT scores – our mutation-selection model is parameterized by a fitness function such that changes are directly interpretable as fitness effects.
-In this regard, an interesting prediction of our model is that back-mutations are beneficial because they revert previous deleterious changes.
-We have tested this hypothesis and found that these back-mutations ($\SphyBen \coloneqq \Sphy > 1 $) are indeed beneficial in extant populations.
-We estimated that between 11 and 82\% of all beneficial mutations in mammalian populations have not been driven by adaptation but instead have reversed deleterious substitutions which have accumulated along the phylogenetic tree.
-More specifically, in 24 out of 28 populations analyzed, the percentage of beneficial mutations estimated to be back-mutations falls between 15 and 45\%.
-These results suggest that many beneficial mutations are non-adaptive but rather restore ancestral states of higher fitness.
-Hence, we can correctly estimate the extent of adaptive evolution only if we account for the number of beneficial back-mutations~\cite{keightley_what_2010, rice_evolutionarily_2015}.
+However, contrary to SIFT scores, our mutation-selection model is parameterized by a fitness function such that changes are directly interpretable as fitness effects (see also section S7).
+In this regard, an interesting prediction of our model is that some deleterious mutations reach fixation due to genetic drift, while beneficial non-adaptive mutations are restoring states of higher fitness.
+We have tested this hypothesis and have found that a substantial part of these predicted non-adaptive mutations ($\SphyBen \coloneqq \Sphy > 1 $) are indeed beneficial in extant populations.
+We estimate that between 11 and 82\% of all beneficial mutations in mammalian populations are not adaptive.
+More specifically, in 24 out of 28 populations analyzed, the percentage of beneficial mutations estimated to be non-adaptive falls between 15 and 45\%.
+These results suggest that many beneficial mutations are not adaptive, but rather restore states of higher fitness.
+Hence, we can correctly estimate the extent of adaptive evolution only if we account for the number of beneficial non-adaptive mutations~\cite{keightley_what_2010, rice_evolutionarily_2015}.
 Altogether, we argue that we should dissociate positive selection from adaptive evolution and limit the use of adaptive mutations to those that are associated with adaptation to environmental change as such~\cite{charlesworth_other_2007, mustonen_fitness_2009}.
 
-\subsection*{Interpreting the proportion of beneficial back-mutations}
+\subsection*{The influence of effective population size}
 
-Across the genome, beneficial-back mutations and deleterious mutations reaching fixation create a balance in which genomes are constantly damaged and restored simultaneously at different loci.
-Since the probability of fixation of mutations depends on the effective population size ($\Ne$), the history of $\Ne$ plays a crucial role in setting the number of beneficial back-mutations compensating for deleterious mutations~\cite{latrille_inferring_2021}.
-For example, a population size expansion will increase the efficacy of selection, and a larger proportion of mutations will be beneficial (otherwise effectively neutral), thus increasing the number of beneficial back-mutations.
-On the other hand, a population that has experienced a high $\Ne$ throughout its history should be closer to an optimal state under a stable fitness landscape, having suffered fewer fixations of deleterious mutations and therefore decreasing the probability of beneficial back-mutations~\cite{huber_determining_2017}.
-Overall, we expect the proportion of beneficial back-mutations to be more dependent on $\Ne$’s long-term expansions and contractions than on the short-term ones~\cite{charlesworth_other_2007,huber_determining_2017}.
-Accounting for phylogenetic relationships, we found no correlation between the proportion of back-mutations and $\Ne$ ($r^2=0.00$, $p=0.772$, fig.~\ref{fig:diversity}B)
+Across the genome, beneficial non-adaptive mutations and deleterious mutations reaching fixation create a balance in which genomes are constantly damaged and restored simultaneously at different loci due to drift.
+Since the probability of fixation of mutations depends on the effective population size ($\Ne$), the history of $\Ne$ plays a crucial role in determining the number of beneficial non-adaptive mutations compensating for deleterious mutations~\cite{latrille_inferring_2021}.
+For example, a population size expansion will increase the efficacy of selection, and a larger proportion of mutations will be beneficial (otherwise effectively neutral), thus increasing the number of beneficial non-adaptive mutations.
+On the other hand, a population that has experienced a high $\Ne$ throughout its history should be closer to an optimal state under a stable fitness landscape, having suffered fewer fixations of deleterious mutations and therefore decreasing the probability of beneficial non-adaptive mutations~\cite{huber_determining_2017}.
+Overall, we expect the proportion of beneficial non-adaptive mutations to be more dependent on $\Ne$’s long-term expansions and contractions than on the short-term ones~\cite{charlesworth_other_2007,huber_determining_2017}.
+Accounting for phylogenetic relationships, we found no correlation between the proportion of beneficial non-adaptive mutations and estimates of $\Ne$ based on genetic diversity ($r^2=0.00$, $p=0.772$, fig.~\ref{fig:diversity}B).
 
-The exact estimation of the contribution of beneficial back-mutations to positive selection relies on some hypotheses at both the phylogenetic and population scales and is sensitive to methodological limitations.
-Indeed, to be conservative, we considered that any mutation under positive selection at the population scale ($\SpopBen$) but not predicted as such at the phylogenetic scale (not $\SphyBen$) is potentially an adaptation.
-However, adaptation is not the only factor hindering the detection of beneficial back-mutations; data quality and potentially inadequate modeling choices of both the fitness landscape and the DFE might also lead to missed predictions.
+Moreover, because our model assumes a fixed fitness landscape, it implicitly assumes that $\Ne$ is constant along the phylogenetic tree.
+Fluctuations due to changes in the fitness landscape or in $\Ne$ will be averaged out by the assumption of the current model that $\Ne$ is constant across lineages.
+It was recently shown~\cite{latrille_inferring_2021}, using computer intensive mutation-selection models with fluctuating $\Ne$, that relaxing the assumption of a constant $\Ne$ results in more extreme estimates of amino-acid fitnesses than with the standard model used in this study.
+In other words, by assuming a constant $\Ne$, we are underpowered to detect beneficial non-adaptive mutations since amino acids will have more similar fitnesses.
+As a consequence, some of the beneficial non-adaptive mutations currently segregating in population will be incorrectly classified as nearly-neutral by the mutation-selection model, and thus be wrongly interpreted as adaptive.
+This ultimately results in lower estimates of the proportion of beneficial non-adaptive mutations.
+Given this inflation of missed predictions due to change in population sizes~\cite{lanfear_population_2014, jones_shifting_2017, platt_protein_2018}, our estimated proportion of beneficial non-adaptive mutations among adaptive ones is likely to be an underestimation.
+
+\subsection*{The role of epistasis and compensatory mutations}
 
@@
 Particularly, the residues in contact co-evolve to become more compatible with each other generating an entrenchment~\cite{goldstein_nonadaptive_2015, goldstein_sequence_2017, park_epistatic_2022}.
-Epistasis therefore allows for compensatory mutations, which restore fitness through mutations at loci different from where deleterious mutations took place.
-It therefore, represents another case case of non-adaptive beneficial mutations, but one which is not accounted for by our method.
-Therefore, the beneficial mutations that we classify as putatively adaptive might in fact be compensatory mutations, making our estimation of the rate of non-adaptive beneficial mutations conservative.
+Epistasis therefore allows for compensatory mutations, which restore fitness through mutations at loci different from where deleterious mutations took place, representing another case of non-adaptive beneficial mutations, but one which is not accounted for by our method.
+Hence, the beneficial mutations that we classify as putatively adaptive might in fact be compensatory mutations, making our estimation of the rate of non-adaptive beneficial mutations conservative.
 
-Despite epistasis being an important factor in protein evolution, several deep mutational scanning laboratory experiments have revealed that a site-specific fitness landscape is a reasonable approximation of the fitness landscape of proteins, and even predicts the evolution of sequences in nature~\cite{ashenberg_mutational_2013, doud_sitespecific_2015, bloom_identification_2017}.
-Additionally, the fact that we observe such a high proportion of beneficial back-mutations suggests that the underlying assumptions of our model, namely site-independence, implying no epistasis, and a static fitness landscape, are a reasonable approximation for the underlying fitness landscape of proteins.
+Despite epistasis being an important factor in protein evolution, several deep-mutational scanning experiments have revealed that a site-specific fitness landscape predicts the evolution of sequences in nature with considerable accuracy~\cite{ashenberg_mutational_2013, doud_sitespecific_2015, bloom_identification_2017}.
+Additionally, the fact that we observe such a high proportion of beneficial non-adaptive mutations suggests that the underlying assumptions of our model, namely site-independence, implying no epistasis, and a static fitness landscape, are a reasonable approximation for the underlying fitness landscape of proteins.
 Our results imply that the fitness effects of new mutations are mostly conserved across mammalian orthologs, in agreement with other studies showing that for conserved orthologs with similar structures and functions, models without epistasis provide a reasonable estimate of fitness effects in protein coding genes~\cite{youssef_consequences_2020, vigue_deciphering_2022}.
 
-Moreover, because our model assumes a fixed landscape, it implicitly assumes that $\Ne$ is constant along the phylogenetic tree.
-Fluctuations due to changes in the fitness landscape or in $\Ne$ will be averaged out by the assumption of the current model that $\Ne$ is constant across lineages.
-It was recently shown~\cite{latrille_inferring_2021}, using highly computer intensive mutation-selection models with fluctuating $\Ne$, that relaxing the assumption of a constant $\Ne$ results in more extreme estimates of amino-acid fitnesses than with the standard model used in this study.
-In other words, by assuming a constant $\Ne$, we are underpowered to detect beneficial back-mutations since amino acids will have more similar fitnesses.
-As a consequence, mutations that would otherwise fall into $\SpopBen$ or $\SpopDel$ will be classified as $\SpopNeu$, resulting ultimately in lower estimates of the proportion of beneficial back-mutations ($\proba [ \SphyBen  \given  \SpopBen]$).
-Given this inflation of missed predictions due to change in population sizes~\cite{lanfear_population_2014, jones_shifting_2017, platt_protein_2018}, our estimated proportion of beneficial back-mutations among adaptive ones is likely to therefore be an underestimation.
-In practice, advantageous mutations can be depleted in the $\SphyNeu$ and $\SphyDel$ class in some species but pervasive in others, depending on the model used to infer the DFE at the population scale (tables~S8-12).
-It appears that our estimation can be quite sensitive to model misspecification and overall, while we provide an order of magnitude for the contribution of beneficial back-mutations to positive selection, further methodological development on the estimation of the distribution of fitness effects is needed to increase the confidence on this value.
+\subsection*{Other assumptions and methodological limitations}
+
+The exact estimation of the contribution of beneficial non-adaptive mutations to positive selection relies on some hypotheses at both the phylogenetic and population scales and is sensitive to methodological limitations.
+Indeed, data quality and potentially inadequate modeling choices of both the fitness landscape (at the phylogenetic scale) and fitness effects (at the population scale) might also lead to missed prediction~\cite{moutinho_variation_2019}.
+To be conservative, we considered that any mutation under positive selection at the population scale ($\SpopBen$) but not predicted as such at the phylogenetic scale (not $\SphyBen$) is potentially an adaptation.
+In practice, we obtained different values of the proportion of non-adaptive beneficial mutations depending on the model used to infer the fitness effects at the population scale, and the filtering or not of CpG mutations~\cite{eyre-walker_how_2014} (tables~S8-14).
+It appears that our estimation can be sensitive to model misspecification and overall, while we provide an order of magnitude for the contribution of beneficial non-adaptive mutations to positive selection, methodological improvement on the estimation of the distribution of fitness effects is needed to increase the precision of this value.
+
+Importantly, if there are several substitutions toward the same amino acid along the mammalian tree, (see fig.~S2) our mutation-selection model cannot distinguish between a scenario where mammals have fixed deleterious mutations that are reverted in several lineages, from more complex scenarios involving adaptation.
+In a first scenario, repeated changes of fitness landscapes in the same direction could occur along several lineages, leading to repeated substitutions in multiple lineages (parallel or convergent adaptation).
+Of note, repeated substitutions that we observe (section~S2) are spread across the phylogeny and are usually shared by distant species/clades with very different lifestyles and environments.
+It is therefore unlikely that all the beneficial mutations that we classified as non-adaptive (between 15 and 45\%) would result from parallel adaptation.
+In a second scenario, an environmental change that occurred near the root of placental mammals ($\sim$100 Mys ago), to which extant populations are currently responding through weakly adaptive mutations could also lead to repeated substitutions toward the same amino acids.
+However, for this latter hypothesis to totally explain our results, it would imply that a large proportion of weakly adaptive mutations arising in present day populations of mammals are the late consequence of $\sim$100 Mys-old environmental changes.
+While we cannot rule out that some cases of the latter scenarios are included in our results, we argue that the hypothesis of non-adaptive evolution on a fixed fitness landscape of functionally constrained proteins remains more parsimonious for most cases.
 
@@
 
-A long-standing debate in molecular evolution is whether the variations we observe between species in protein-coding genes are primarily due to nearly-neutral mutations reaching fixation by drift or primarily due to adaptation~\cite{kimura_evolutionary_1968,jensen_importance_2019,gillespie_substitution_1994,Ohta1992}.
-Here we provide evidence that in mammalian orthologs, many substitutions occur through fixation of both deleterious mutations and beneficial back-mutations.
-However, detecting adaptation above this background of nearly-neutral substitutions remains a central question~\cite{kimura_evolutionary_1968,ohta_development_1996}.
+A long-standing debate in molecular evolution is whether the variations we observe between species in protein-coding genes are primarily due to nearly-neutral mutations reaching fixation by drift or primarily due to adaptation~\cite{kimura_evolutionary_1968,jensen_importance_2019,gillespie_substitution_1994,ohta_nearly_1992}.
+Here we provide evidence that in mammalian orthologs, many substitutions occur through fixation of both deleterious mutations and beneficial non-adaptive mutations.
+However, detecting adaptation above this background of nearly-neutral substitutions remains a challenge~\cite{kimura_evolutionary_1968,ohta_development_1996}.
 
@@
 Deviations from this neutral expectation, such as $\dnds > 1$, which can be generated by an excess of non-synonymous substitutions, is generally interpreted as a sign of adaptation.
-However, as shown in this study, a $\dnds > 1$ is not necessarily a signature of adaptation but can be due to beneficial back-mutations.
+However, as shown in this study, a $\dnds > 1$ is not necessarily a signature of adaptation but can be due to beneficial non-adaptive mutations.
 So, by relaxing the strict neutrality and assuming a stable fitness landscape instead, one can predict the expected rate of evolution, called $\omega_0$~\cite{spielman_relationship_2015, dosreis_how_2015}.
@@
 
-Here, we have provided empirical evidence that an evolutionary model assuming a stable fitness landscape at the mammalian scale allows us to predict the fitness effects of mutations in extant populations and individuals, acknowledging the balance between deleterious and beneficial back-mutations.
-We argue that such a model represents a null expectation for the evolution of protein-coding genes in the absence of adaptation.
+\subsection*{Conclusions}
+
+Here, we have provided empirical evidence that an evolutionary model assuming a stable fitness landscape at the mammalian scale allows us to predict the fitness effects of mutations in extant populations and individuals, acknowledging the balance between deleterious and beneficial non-adaptive mutations.
+We argue that such a model would represent a null expectation for the evolution of protein-coding genes in the absence of adaptation.
+Altogether, because a substantial part of positive selection can be explained by beneficial non-adaptive mutations, but not its entirety, we argue that the mammalian exome is shaped by both adaptive and non-adaptive processes, and that none of them alone is sufficient to explain the observed patterns of changes.
 In that sense, to avoid conflating beneficial mutations with adaptive evolution, the term ``adaptation`` should retain its original meaning associated with a change in the underlying fitness landscape and be modelled as such.
@@
 \matmethods{
-       \subsection{Phylogenetic dataset}\label{subsec:phylo-dataset}
+       \subsection{Phylogenetic dataset}
 
@@
        where $D \left( \Sphyclass \right) $ was the number of non-synonymous substitutions in class $\Sphyclass$, $D_{\text{syn}}$ was the number of synonymous substitutions across the exome, while $L \left( \Sphyclass \right)$ and $L_{\text{syn}}$ were the numbers of non-synonymous and synonymous mutational opportunities, respectively, as defined in section~\ref{subsec:nunber-of-sites}.
-       $\delta(\dnds)$ was computed as the difference between $\dnds$ computed over all substitutions and $\dnds$ when we removed beneficial back-mutations $\dn (\Sphy < 1) / \ds$, normalized by $\dnds$.
+       $\delta(\dnds)$ was computed as the difference between $\dnds$ computed over all substitutions and $\dnds$ when we removed beneficial non-adaptive mutations $\dn (\Sphy < 1) / \ds$, normalized by $\dnds$.
        Note that the quantities $\delta(\dnds)$ and $\delta(\dn)$ are equivalent due to the simplification of the factor $\ds$:
@@
 
-       \textit{Precision} is the proportion of mutations correctly predicted as beneficial ($\proba [ \SpopBen \cap  \SphyBen]$) out of all predicted as beneficial back-mutations ($\proba [ \SphyBen]$), which can be written as a conditional probability:
+       \textit{Precision} is the proportion of mutations correctly predicted as beneficial ($\proba [ \SpopBen \cap  \SphyBen]$) out of all predicted as beneficial non-adaptive mutations ($\proba [ \SphyBen]$), which can be written as a conditional probability:
 
@@
        \end{equation}
-       Namely, \textit{precision} corresponds to the probability for a back-mutation ($\SphyBen$) to be effectively beneficial at the population level ($\SpopBen$).
-       This probability, computed from eq.~\ref{eq:polyProbaAdv}, is obtained by restricting our analysis to SNPs that are predicted to be beneficial back-mutations (yellow fill for the category $\SphyBen$ in fig.~\ref{fig:homo-afr-results}D).
+       Namely, \textit{precision} corresponds to the probability for a $\SphyBen$ mutation to be effectively beneficial at the population level ($\SpopBen$).
+       This probability, computed from eq.~\ref{eq:polyProbaAdv}, is obtained by restricting our analysis to SNPs that are predicted to be beneficial non-adaptive mutations (yellow fill for the category $\SphyBen$ in fig.~\ref{fig:homo-afr-results}D).
 
@@
        \end{equation}
-       Namely, \textit{recall} corresponds to the probability for a beneficial mutation at the population level ($\SpopBen$) to be a beneficial back-mutation ($\SphyBen$).
+       Namely, \textit{recall} corresponds to the probability for a beneficial mutation at the population level ($\SpopBen$) to be a beneficial non-adaptive mutation ($\SphyBen$).
        Using Bayes theorem, \textit{recall} can be re-written as:
@@
 
-       \section{Data availability}\label{sec:data-availability}
-       The data underlying this article are available at \url{https://doi.org/10.5281/zenodo.7878954}.
+       \section*{Data availability}
+       The data underlying this article are available at \url{https://doi.org/10.5281/zenodo.7878953}.
        Snakemake pipeline, analysis scripts and documentation are available at \href{https://github.com/ThibaultLatrille/SelCoeff}{github.com/ThibaultLatrille/SelCoeff}.

### 2024-03-04 manuscript/supp-figure3.tex
Manuscript revision 2

@@
 
-\newcommand{\UniDimArray}[1]{\bm{#1}}
-\newcommand{\der}{\text{d}}
-\newcommand{\e}{\text{e}}
-\newcommand{\Ne}{N_{\text{e}}}
-\newcommand{\proba}{\mathbb{P}}
-\newcommand{\pfix}{\proba_{\text{fix}}}
-\newcommand{\dn}{d_N}
-\newcommand{\ds}{d_S}
-\newcommand{\dnds}{\dn / \ds}
-\newcommand{\Sphy}{S_{0}}
-\newcommand{\SphyDel}{\mathcal{D}_0}
-\newcommand{\SphyNeu}{\mathcal{N}_0}
-\newcommand{\SphyBen}{\mathcal{B}_0}
-\newcommand{\Sphyclass}{x}
-\newcommand{\SphyclassAlt}{y}
-\newcommand{\given}{\mid}
-\newcommand{\Spop}{S}
-\newcommand{\SpopDel}{\mathcal{D}}
-\newcommand{\SpopNeu}{\mathcal{N}}
-\newcommand{\SpopBen}{\mathcal{B}}
-\newcommand{\ProbaPopDel}{\proba [ \SpopDel]}
-\newcommand{\ProbaPopNeu}{\proba [ \SpopNeu ]}
-\newcommand{\ProbaPopBen}{\proba [ \SpopBen ]}
-\newcommand{\AdvMean}{\beta_b}
-\newcommand{\DelMean}{\beta_d}
-\newcommand{\thetaSyn}{\theta_{\text{S}}}
-
-\title{Replicability of figure 3 across populations}
+\title{Replicability across populations (S7.2)}
 \date{~}
@@
     \tableofcontents
-
     \newpage
 
-    (Top-left) Distribution of scaled selection coefficients ($\Sphy$), predicted for all possible non-synonymous DNA mutations away from the ancestral exome.
-    Mutations are divided into three classes of selection: deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial ($\SphyBen$, supposedly beneficial back-mutations)
-
-    (Top-right) Distribution of scaled selection coefficients ($\Sphy$) for all observed substitutions along the terminal branch of the tree.
-    If there are fewer substitutions than expected, this class is thus undergoing purifying selection, as is the case for $\SphyDel$.
-
-    (Bottom-left) The site-frequency spectrum (SFS) for a random sample of 16 alleles (means in solid lines and standard deviations in color shades) for each class of selection and for synonymous mutations, supposedly neutral (black).
-    The SFS represents the proportion of mutations (y-axis) with a given number of derived alleles in the population (x-axis).
-    At high frequencies, deleterious mutations are underrepresented.
-
-    (Bottom-right) Proportion of beneficial $\ProbaPopDel$, nearly-neutral $\ProbaPopNeu$, and deleterious mutations $\ProbaPopBen$ estimated at the population scale for each class of selection at the phylogenetic scale.
-    Proportions depicted here are not weighted by their mutational opportunities.
     \section{Bos taurus}
@@
 
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny A: Expected DFE for mutations}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Bos_taurus.IRBT.MutSel.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Bos_taurus.IRBT.pdf}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny B: Expected DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Bos_taurus.IRBT.MutSel.Flow.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny C: Observed DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/subs.Bos_taurus.IRBT.bins3Mask0.9.pdf}
     \end{minipage}
     \\
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny D: Observed DFE for polymorphisms}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/poly.Bos_taurus.IRBT.bins3Mask0.9.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny E: Site frequency spectrum}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Bos_taurus.IRBT.MutSel-sfs.normalize.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Bos_taurus.IRBT.MutSel.polyDFE_C.pdf}
     \end{minipage}
-    \\
     \subsection{Uganda}
 
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny A: Expected DFE for mutations}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Bos_taurus.UGBT.MutSel.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Bos_taurus.UGBT.pdf}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny B: Expected DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Bos_taurus.UGBT.MutSel.Flow.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny C: Observed DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/subs.Bos_taurus.UGBT.bins3Mask0.9.pdf}
     \end{minipage}
     \\
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny D: Observed DFE for polymorphisms}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/poly.Bos_taurus.UGBT.bins3Mask0.9.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny E: Site frequency spectrum}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Bos_taurus.UGBT.MutSel-sfs.normalize.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Bos_taurus.UGBT.MutSel.polyDFE_C.pdf}
     \end{minipage}
-    \\
     \section{Capra}
@@
 
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny A: Expected DFE for mutations}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.AUCH.MutSel.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Capra_hircus.AUCH.pdf}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny B: Expected DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.AUCH.MutSel.Flow.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny C: Observed DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/subs.Capra_hircus.AUCH.bins3Mask0.9.pdf}
     \end{minipage}
     \\
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny D: Observed DFE for polymorphisms}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/poly.Capra_hircus.AUCH.bins3Mask0.9.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny E: Site frequency spectrum}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.AUCH.MutSel-sfs.normalize.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.AUCH.MutSel.polyDFE_C.pdf}
     \end{minipage}
-    \\
     \subsection{France}
 
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny A: Expected DFE for mutations}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.FRCH.MutSel.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Capra_hircus.FRCH.pdf}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny B: Expected DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.FRCH.MutSel.Flow.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny C: Observed DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/subs.Capra_hircus.FRCH.bins3Mask0.9.pdf}
     \end{minipage}
     \\
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny D: Observed DFE for polymorphisms}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/poly.Capra_hircus.FRCH.bins3Mask0.9.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny E: Site frequency spectrum}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.FRCH.MutSel-sfs.normalize.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.FRCH.MutSel.polyDFE_C.pdf}
     \end{minipage}
-    \\
     \subsection{Iran (C. aegagrus)}
 
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny A: Expected DFE for mutations}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.IRCA.MutSel.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Capra_hircus.IRCA.pdf}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny B: Expected DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.IRCA.MutSel.Flow.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny C: Observed DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/subs.Capra_hircus.IRCA.bins3Mask0.9.pdf}
     \end{minipage}
     \\
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny D: Observed DFE for polymorphisms}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/poly.Capra_hircus.IRCA.bins3Mask0.9.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny E: Site frequency spectrum}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.IRCA.MutSel-sfs.normalize.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.IRCA.MutSel.polyDFE_C.pdf}
     \end{minipage}
-    \\
     \subsection{Iran}
 
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny A: Expected DFE for mutations}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.IRCH.MutSel.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Capra_hircus.IRCH.pdf}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny B: Expected DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.IRCH.MutSel.Flow.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny C: Observed DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/subs.Capra_hircus.IRCH.bins3Mask0.9.pdf}
     \end{minipage}
     \\
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny D: Observed DFE for polymorphisms}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/poly.Capra_hircus.IRCH.bins3Mask0.9.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny E: Site frequency spectrum}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.IRCH.MutSel-sfs.normalize.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.IRCH.MutSel.polyDFE_C.pdf}
     \end{minipage}
-    \\
     \subsection{Italy}
 
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny A: Expected DFE for mutations}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.ITCH.MutSel.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Capra_hircus.ITCH.pdf}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny B: Expected DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.ITCH.MutSel.Flow.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny C: Observed DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/subs.Capra_hircus.ITCH.bins3Mask0.9.pdf}
     \end{minipage}
     \\
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny D: Observed DFE for polymorphisms}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/poly.Capra_hircus.ITCH.bins3Mask0.9.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny E: Site frequency spectrum}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.ITCH.MutSel-sfs.normalize.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.ITCH.MutSel.polyDFE_C.pdf}
     \end{minipage}
-    \\
     \subsection{Morocco}
 
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny A: Expected DFE for mutations}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.MOCH.MutSel.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Capra_hircus.MOCH.pdf}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny B: Expected DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Capra_hircus.MOCH.MutSel.Flow.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny C: Observed DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/subs.Capra_hircus.MOCH.bins3Mask0.9.pdf}
     \end{minipage}
     \\
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny D: Observed DFE for polymorphisms}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/poly.Capra_hircus.MOCH.bins3Mask0.9.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny E: Site frequency spectrum}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.MOCH.MutSel-sfs.normalize.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Capra_hircus.MOCH.MutSel.polyDFE_C.pdf}
     \end{minipage}
-    \\
     \section{Chlorocebus sabaeus}
@@
 
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny A: Expected DFE for mutations}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.Barbados.MutSel.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Chlorocebus_sabaeus.Barbados.pdf}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny B: Expected DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.Barbados.MutSel.Flow.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny C: Observed DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/subs.Chlorocebus_sabaeus.Barbados.bins3Mask0.9.pdf}
     \end{minipage}
     \\
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny D: Observed DFE for polymorphisms}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/poly.Chlorocebus_sabaeus.Barbados.bins3Mask0.9.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny E: Site frequency spectrum}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.Barbados.MutSel-sfs.normalize.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.Barbados.MutSel.polyDFE_C.pdf}
     \end{minipage}
-    \\
     \subsection{Central Afr. Rep.}
 
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny A: Expected DFE for mutations}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.Central_African_Republic.MutSel.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Chlorocebus_sabaeus.Central_African_Republic.pdf}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny B: Expected DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.Central_African_Republic.MutSel.Flow.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny C: Observed DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/subs.Chlorocebus_sabaeus.Central_African_Republic.bins3Mask0.9.pdf}
     \end{minipage}
     \\
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny D: Observed DFE for polymorphisms}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/poly.Chlorocebus_sabaeus.Central_African_Republic.bins3Mask0.9.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny E: Site frequency spectrum}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel-sfs.normalize.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.Central_African_Republic.MutSel.polyDFE_C.pdf}
     \end{minipage}
-    \\
     \subsection{Ethiopia}
 
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny A: Expected DFE for mutations}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.Ethiopia.MutSel.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Chlorocebus_sabaeus.Ethiopia.pdf}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny B: Expected DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.Ethiopia.MutSel.Flow.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny C: Observed DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/subs.Chlorocebus_sabaeus.Ethiopia.bins3Mask0.9.pdf}
     \end{minipage}
     \\
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny D: Observed DFE for polymorphisms}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/poly.Chlorocebus_sabaeus.Ethiopia.bins3Mask0.9.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny E: Site frequency spectrum}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel-sfs.normalize.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.Ethiopia.MutSel.polyDFE_C.pdf}
     \end{minipage}
-    \\
     \subsection{Gambia}
 
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny A: Expected DFE for mutations}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.Gambia.MutSel.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Chlorocebus_sabaeus.Gambia.pdf}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny B: Expected DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.Gambia.MutSel.Flow.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny C: Observed DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/subs.Chlorocebus_sabaeus.Gambia.bins3Mask0.9.pdf}
     \end{minipage}
     \\
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny D: Observed DFE for polymorphisms}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/poly.Chlorocebus_sabaeus.Gambia.bins3Mask0.9.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny E: Site frequency spectrum}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.Gambia.MutSel-sfs.normalize.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.Gambia.MutSel.polyDFE_C.pdf}
     \end{minipage}
-    \\
     \subsection{Kenya}
 
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny A: Expected DFE for mutations}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.Kenya.MutSel.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Chlorocebus_sabaeus.Kenya.pdf}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny B: Expected DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.Kenya.MutSel.Flow.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny C: Observed DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/subs.Chlorocebus_sabaeus.Kenya.bins3Mask0.9.pdf}
     \end{minipage}
     \\
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny D: Observed DFE for polymorphisms}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/poly.Chlorocebus_sabaeus.Kenya.bins3Mask0.9.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny E: Site frequency spectrum}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.Kenya.MutSel-sfs.normalize.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.Kenya.MutSel.polyDFE_C.pdf}
     \end{minipage}
-    \\
     \subsection{Nevis}
 
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny A: Expected DFE for mutations}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.Nevis.MutSel.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Chlorocebus_sabaeus.Nevis.pdf}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny B: Expected DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.Nevis.MutSel.Flow.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny C: Observed DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/subs.Chlorocebus_sabaeus.Nevis.bins3Mask0.9.pdf}
     \end{minipage}
     \\
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny D: Observed DFE for polymorphisms}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/poly.Chlorocebus_sabaeus.Nevis.bins3Mask0.9.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny E: Site frequency spectrum}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.Nevis.MutSel-sfs.normalize.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.Nevis.MutSel.polyDFE_C.pdf}
     \end{minipage}
-    \\
     \subsection{Saint Kitts}
 
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny A: Expected DFE for mutations}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.Saint_Kitts.MutSel.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Chlorocebus_sabaeus.Saint_Kitts.pdf}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny B: Expected DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.Saint_Kitts.MutSel.Flow.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny C: Observed DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/subs.Chlorocebus_sabaeus.Saint_Kitts.bins3Mask0.9.pdf}
     \end{minipage}
     \\
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny D: Observed DFE for polymorphisms}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/poly.Chlorocebus_sabaeus.Saint_Kitts.bins3Mask0.9.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny E: Site frequency spectrum}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.Saint_Kitts.MutSel-sfs.normalize.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.Saint_Kitts.MutSel.polyDFE_C.pdf}
     \end{minipage}
-    \\
     \subsection{South Africa}
 
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny A: Expected DFE for mutations}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.South_Africa.MutSel.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Chlorocebus_sabaeus.South_Africa.pdf}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny B: Expected DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.South_Africa.MutSel.Flow.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny C: Observed DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/subs.Chlorocebus_sabaeus.South_Africa.bins3Mask0.9.pdf}
     \end{minipage}
     \\
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny D: Observed DFE for polymorphisms}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/poly.Chlorocebus_sabaeus.South_Africa.bins3Mask0.9.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny E: Site frequency spectrum}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.South_Africa.MutSel-sfs.normalize.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.South_Africa.MutSel.polyDFE_C.pdf}
     \end{minipage}
-    \\
     \subsection{Zambia}
 
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny A: Expected DFE for mutations}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.Zambia.MutSel.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Chlorocebus_sabaeus.Zambia.pdf}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny B: Expected DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Chlorocebus_sabaeus.Zambia.MutSel.Flow.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny C: Observed DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/subs.Chlorocebus_sabaeus.Zambia.bins3Mask0.9.pdf}
     \end{minipage}
     \\
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny D: Observed DFE for polymorphisms}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/poly.Chlorocebus_sabaeus.Zambia.bins3Mask0.9.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny E: Site frequency spectrum}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.Zambia.MutSel-sfs.normalize.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Chlorocebus_sabaeus.Zambia.MutSel.polyDFE_C.pdf}
     \end{minipage}
-    \\
     \section{Equus caballus}
 
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny A: Expected DFE for mutations}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Equus_caballus.up.MutSel.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Equus_caballus.up.pdf}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny B: Expected DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Equus_caballus.up.MutSel.Flow.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny C: Observed DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/subs.Equus_caballus.up.bins3Mask0.9.pdf}
     \end{minipage}
     \\
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny D: Observed DFE for polymorphisms}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/poly.Equus_caballus.up.bins3Mask0.9.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny E: Site frequency spectrum}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Equus_caballus.up.MutSel-sfs.normalize.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Equus_caballus.up.MutSel.polyDFE_C.pdf}
     \end{minipage}
-    \\
     \section{Homo sapiens}
@@
 
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny A: Expected DFE for mutations}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Homo_sapiens.AFR.MutSel.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Homo_sapiens.AFR.pdf}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny B: Expected DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Homo_sapiens.AFR.MutSel.Flow.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny C: Observed DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/subs.Homo_sapiens.AFR.bins3Mask0.9.pdf}
     \end{minipage}
     \\
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny D: Observed DFE for polymorphisms}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/poly.Homo_sapiens.AFR.bins3Mask0.9.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny E: Site frequency spectrum}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Homo_sapiens.AFR.MutSel-sfs.normalize.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Homo_sapiens.AFR.MutSel.polyDFE_C.pdf}
     \end{minipage}
-    \\
     \subsection{Admixed American}
 
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny A: Expected DFE for mutations}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Homo_sapiens.AMR.MutSel.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Homo_sapiens.AMR.pdf}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny B: Expected DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Homo_sapiens.AMR.MutSel.Flow.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny C: Observed DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/subs.Homo_sapiens.AMR.bins3Mask0.9.pdf}
     \end{minipage}
     \\
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny D: Observed DFE for polymorphisms}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/poly.Homo_sapiens.AMR.bins3Mask0.9.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny E: Site frequency spectrum}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Homo_sapiens.AMR.MutSel-sfs.normalize.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Homo_sapiens.AMR.MutSel.polyDFE_C.pdf}
     \end{minipage}
-    \\
     \subsection{East Asian}
 
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny A: Expected DFE for mutations}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Homo_sapiens.EAS.MutSel.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Homo_sapiens.EAS.pdf}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny B: Expected DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Homo_sapiens.EAS.MutSel.Flow.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny C: Observed DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/subs.Homo_sapiens.EAS.bins3Mask0.9.pdf}
     \end{minipage}
     \\
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny D: Observed DFE for polymorphisms}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/poly.Homo_sapiens.EAS.bins3Mask0.9.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny E: Site frequency spectrum}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Homo_sapiens.EAS.MutSel-sfs.normalize.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Homo_sapiens.EAS.MutSel.polyDFE_C.pdf}
     \end{minipage}
-    \\
     \subsection{European}
 
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny A: Expected DFE for mutations}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Homo_sapiens.EUR.MutSel.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Homo_sapiens.EUR.pdf}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny B: Expected DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Homo_sapiens.EUR.MutSel.Flow.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny C: Observed DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/subs.Homo_sapiens.EUR.bins3Mask0.9.pdf}
     \end{minipage}
     \\
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny D: Observed DFE for polymorphisms}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/poly.Homo_sapiens.EUR.bins3Mask0.9.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny E: Site frequency spectrum}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Homo_sapiens.EUR.MutSel-sfs.normalize.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Homo_sapiens.EUR.MutSel.polyDFE_C.pdf}
     \end{minipage}
-    \\
     \subsection{South Asian}
 
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny A: Expected DFE for mutations}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Homo_sapiens.SAS.MutSel.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Homo_sapiens.SAS.pdf}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny B: Expected DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Homo_sapiens.SAS.MutSel.Flow.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny C: Observed DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/subs.Homo_sapiens.SAS.bins3Mask0.9.pdf}
     \end{minipage}
     \\
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny D: Observed DFE for polymorphisms}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/poly.Homo_sapiens.SAS.bins3Mask0.9.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny E: Site frequency spectrum}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Homo_sapiens.SAS.MutSel-sfs.normalize.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Homo_sapiens.SAS.MutSel.polyDFE_C.pdf}
     \end{minipage}
-    \\
     \section{Ovis}
@@
 
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny A: Expected DFE for mutations}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Ovis_aries.IROA.MutSel.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Ovis_aries.IROA.pdf}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny B: Expected DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Ovis_aries.IROA.MutSel.Flow.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny C: Observed DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/subs.Ovis_aries.IROA.bins3Mask0.9.pdf}
     \end{minipage}
     \\
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny D: Observed DFE for polymorphisms}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/poly.Ovis_aries.IROA.bins3Mask0.9.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny E: Site frequency spectrum}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Ovis_aries.IROA.MutSel-sfs.normalize.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Ovis_aries.IROA.MutSel.polyDFE_C.pdf}
     \end{minipage}
-    \\
     \subsection{Iran (O. orientalis)}
 
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny A: Expected DFE for mutations}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Ovis_aries.IROO.MutSel.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Ovis_aries.IROO.pdf}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny B: Expected DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Ovis_aries.IROO.MutSel.Flow.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny C: Observed DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/subs.Ovis_aries.IROO.bins3Mask0.9.pdf}
     \end{minipage}
     \\
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny D: Observed DFE for polymorphisms}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/poly.Ovis_aries.IROO.bins3Mask0.9.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny E: Site frequency spectrum}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Ovis_aries.IROO.MutSel-sfs.normalize.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Ovis_aries.IROO.MutSel.polyDFE_C.pdf}
     \end{minipage}
-    \\
     \subsection{Iran (O. vignei)}
 
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny A: Expected DFE for mutations}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Ovis_aries.IROV.MutSel.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Ovis_aries.IROV.pdf}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny B: Expected DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Ovis_aries.IROV.MutSel.Flow.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny C: Observed DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/subs.Ovis_aries.IROV.bins3Mask0.9.pdf}
     \end{minipage}
     \\
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny D: Observed DFE for polymorphisms}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/poly.Ovis_aries.IROV.bins3Mask0.9.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny E: Site frequency spectrum}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Ovis_aries.IROV.MutSel-sfs.normalize.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Ovis_aries.IROV.MutSel.polyDFE_C.pdf}
     \end{minipage}
-    \\
     \subsection{Various}
 
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny A: Expected DFE for mutations}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Ovis_aries.ISGC.MutSel.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Ovis_aries.ISGC.pdf}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny B: Expected DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Ovis_aries.ISGC.MutSel.Flow.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny C: Observed DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/subs.Ovis_aries.ISGC.bins3Mask0.9.pdf}
     \end{minipage}
     \\
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny D: Observed DFE for polymorphisms}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/poly.Ovis_aries.ISGC.bins3Mask0.9.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny E: Site frequency spectrum}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Ovis_aries.ISGC.MutSel-sfs.normalize.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Ovis_aries.ISGC.MutSel.polyDFE_C.pdf}
     \end{minipage}
-    \\
     \subsection{Morocco}
 
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny A: Expected DFE for mutations}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Ovis_aries.MOOA.MutSel.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/ancestral_bins3Mask0.9/Ovis_aries.MOOA.pdf}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny B: Expected DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/data_processed/opportunities_bins3Mask0.9/DFE.Ovis_aries.MOOA.MutSel.Flow.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny C: Observed DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/subs.Ovis_aries.MOOA.bins3Mask0.9.pdf}
     \end{minipage}
     \\
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny D: Observed DFE for polymorphisms}
+        \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/supp/hist/poly.Ovis_aries.MOOA.bins3Mask0.9.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny E: Site frequency spectrum}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Ovis_aries.MOOA.MutSel-sfs.normalize.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
         \includegraphics[width=\linewidth, page=1]{/Users/tlatrille/Documents/SelCoeff/experiments/3bins-mC-nodiv/analysis/Ovis_aries.MOOA.MutSel.polyDFE_C.pdf}
     \end{minipage}
-    \\
 

### 2024-03-04 manuscript/supp-mat-revision-2.tex
Manuscript revision 2

--- 2023-10-11 manuscript/supp-mat-revision.tex
@@
     \tableofcontents
+
+    \newpage
+    \listoffigures
+
+    \newpage
+    \listoftables
+
     \clearpage
-
     \section{Mutation-selection codon models}\label{sec:mutsel}
@@
             {\color{BLUE}{Blue}} dashed line denotes a drawing from a random distribution, and black solid lines denote a function.
-    All the nodes pointing toward a given node (upstream) are its dependencies which determines its distribution.
-    The other way around, following the arrows in the DAG (downstream), simple {prior} distributions are combined together to form more complex joint {prior} distribution which ultimately defines the {prior} distribution of the model.
+    All the nodes pointing toward a given node (upstream) are its dependencies which determine its distribution.
+    The other way around, following the arrows in the DAG (downstream), simple {prior} distributions are combined together to form more complex joint {prior} distributions which ultimately define the {prior} distribution of the model.
 
@@
             \node[state] (R) [below right=of Q] {$\Mutmatrix$};
-            \node[state] (BL) [right=of P] {$\branchlength\branchexp$};
+            \node[state] (BL) [BLUE, right=of P] {$\branchlength\branchexp$};
             \node[res] (BLH) [RED, right=of BL] {$ \lambda, \tau $};
@@
             \begin{block}{c(cccc)}
-                A & - & {\exchan_{AC}\mutequi_C} & {\exchan_{AG}\mutequi_G} & {\exchan_{AT}\mutequi_T} \\
-                C & {\exchan_{AC}\mutequi_A} &                        - & {\exchan_{CG}\mutequi_G} & {\exchan_{CT}\mutequi_T} \\
-                G & {\exchan_{AG}\mutequi_A} & {\exchan_{CG}\mutequi_C} &                        - & {\exchan_{GT}\mutequi_T} \\
-                T & {\exchan_{AT}\mutequi_A} & {\exchan_{CT}\mutequi_C} & {\exchan_{GT}\mutequi_G} & - \\
+                A & -\mu_A & {\exchan_{AC}\mutequi_C} & {\exchan_{AG}\mutequi_G} & {\exchan_{AT}\mutequi_T} \\
+                C & {\exchan_{AC}\mutequi_A} &                        -\mu_C & {\exchan_{CG}\mutequi_G} & {\exchan_{CT}\mutequi_T} \\
+                G & {\exchan_{AG}\mutequi_A} & {\exchan_{CG}\mutequi_C} &                        -\mu_G & {\exchan_{GT}\mutequi_T} \\
+                T & {\exchan_{AT}\mutequi_A} & {\exchan_{CT}\mutequi_C} & {\exchan_{GT}\mutequi_G} & -\mu_T\\
             \end{block}
@@
     \begin{equation}
-        \mutmatrix_{a,a} = - \sum\limits_{ b \neq a, b \in \{A, C, G, T\} } \mutmatrix_{a,b}
+        \mu_a = \sum\limits_{ b \neq a, b \in \{A, C, G, T\} } \mutmatrix_{a,b}
     \end{equation}
@@
     To implement the mapping-based {MCMC} sampling strategy, we first sample the detailed {substitution} history $\subhistory$ for all sites along the tree.
-    Several methods exist for doing this~\cite{nielsen_mapping_2002,rodrigue_uniformization_2008}, which are used here in combination (first trying the accept-reject method of Nielsen, then switching to the uniformization approach of Rodrigue \textit{et al} if the first round has failed).
+    Several methods exist for doing this~\cite{nielsen_mapping_2002,rodrigue_uniformization_2008}, which are used here in combination (first trying the accept-reject method of \textcite{nielsen_mapping_2002}, then switching to the uniformization approach of \textcite{rodrigue_uniformization_2008} if the first round has failed).
 
@@
 
-    \subsection{Summary tables}\label{subsec:summary-table-mutsel}
+    \subsection{Example sites}\label{subsec:example-sites}
+
+    We extracted protein-coding DNA alignments across mammals centered around the codon site (two flanking codons in white background) for which the beneficial non-adaptive mutations ($\SphyBen$) have been detected in \textit{Chlorocebus sabaeus}.
+    We also show the translated amino acids of this region.
+    For instance, in DNA alignment of gene SELE shown below, the nucleotide at site 1722 has mutated (from T to C) at the basis of Simiiformes (monkeys and apes), modifying the corresponding amino acid from Serine to Proline, but has been subsequently reverted in the branch of \textit{Chlorocebus sabaeus}.
+    However, other substitutions classified as $\SphyBen$ cannot be clearly interpreted as reversions \textit{sensu stricto} along the terminal branch of \textit{Chlorocebus sabaeus}.
+    Indeed, we acknowledge that on a fixed fitness landscape, a deleterious mutation can be compensated by transitions to other fitter amino-acids, and not necessarily the ancestral one.
+
+    In the figures below, the first line is the name of the gene, the second line the position of the mutation in the OrthoMam protein-coding DNA alignment, and the arrow in the third line corresponds to the nucleotide position of the mutation.
+    Finally, for reproducibility, we generated the fasta alignment for all $\SphyBen$ mutations that we detected, either in the terminal lineage or in segregating polymorphism.
+    These fasta files are available at Zenodo (\url{https://doi.org/10.5281/zenodo.7878953}), across all populations, under the compressed archive \textit{alignment\_focused\_around\_non\_adaptive\_mutations.zip} and we provide a python script to obtain the figures shown below given these alignments.
+
+    \newpage
+    \begin{center}
+        \captionof{figure}{Examples sites of $\SphyBen$ mutations in \textit{Chlorocebus sabaeus} (reversions).}.
+        \includegraphics[width=0.95\linewidth, page=1]{artworks/Alignment.Chlorocebus_sabaeus.Saint_Kitts-0.pdf}
+    \end{center}
+
+    \newpage
+    \begin{center}
+        \captionof{figure}{Examples sites of $\SphyBen$ mutations in \textit{Chlorocebus sabaeus}.}.
+        \includegraphics[width=0.95\linewidth, page=1]{artworks/Alignment.Chlorocebus_sabaeus.Saint_Kitts-1.pdf}
+    \end{center}
+
+    \newpage
+    \subsection{Selection along the terminal branches}\label{subsec:summary-table-mutsel}
 
@@
         These mutations have a selection coefficient predicted at the phylogenetic-scale between -1 and 1.
-        \item $\proba [ \SphyBen ]$ (eq.~5) is the probability for a new mutation to be a beneficial back-mutation.
+        \item $\proba [ \SphyBen ]$ (eq.~5) is the probability for a new mutation to be a  non-adaptive beneficial mutation.
         These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1, thus toward a more fit amino-acid.
@@
         \scriptsize
-        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
+        \begin{longtable*}{|l|r|r|r|r|}
             \toprule
-            Population &             Species & $\dnds $ & $\dn ( \SphyDel ) / \ds$ & $\dn ( \SphyNeu ) / \ds$ & $\dn ( \SphyBen ) / \ds$ \\
+            Species & $\dnds $ & $\dn ( \SphyDel ) / \ds$ & $\dn ( \SphyNeu ) / \ds$ & $\dn ( \SphyBen ) / \ds$ \\
             \midrule
@@
             \midrule
-            \multicolumn{8}{r}{{Continued on next page}} \\
+            \multicolumn{5}{r}{{Continued on next page}} \\
             \midrule
@@
             \endlastfoot
-            \rowcolor{LIGHTGREY} Equus c. & Equus caballus & $ 0.129$ & $ 0.065$ & $ 0.832$ & $ 1.267$ \\
-            Iran & Bos taurus & $ 0.114$ & $ 0.063$ & $ 0.629$ & $ 1.280$ \\
-            Uganda & Bos taurus & $ 0.116$ & $ 0.064$ & $ 0.638$ & $ 1.328$ \\
-            \rowcolor{LIGHTGREY} Australia & Capra hircus & $ 0.108$ & $ 0.058$ & $ 0.631$ & $ 1.169$ \\
-            \rowcolor{LIGHTGREY} France & Capra hircus & $ 0.109$ & $ 0.058$ & $ 0.635$ & $ 1.172$ \\
-            \rowcolor{LIGHTGREY} Iran (C. aegagrus) & Capra hircus & $ 0.108$ & $ 0.058$ & $ 0.632$ & $ 1.170$ \\
-            \rowcolor{LIGHTGREY} Iran & Capra hircus & $ 0.108$ & $ 0.058$ & $ 0.632$ & $ 1.178$ \\
-            \rowcolor{LIGHTGREY} Italy & Capra hircus & $ 0.109$ & $ 0.058$ & $ 0.636$ & $ 1.171$ \\
-            \rowcolor{LIGHTGREY} Morocco & Capra hircus & $ 0.108$ & $ 0.058$ & $ 0.633$ & $ 1.183$ \\
-            Iran & Ovis aries & $ 0.128$ & $ 0.079$ & $ 0.619$ & $ 1.215$ \\
-            Iran (O. orientalis) & Ovis aries & $ 0.129$ & $ 0.080$ & $ 0.619$ & $ 1.212$ \\
-            Iran (O. vignei) & Ovis aries & $ 0.127$ & $ 0.078$ & $ 0.619$ & $ 1.201$ \\
-            Various & Ovis aries & $ 0.129$ & $ 0.080$ & $ 0.620$ & $ 1.201$ \\
-            Morocco & Ovis aries & $ 0.129$ & $ 0.080$ & $ 0.621$ & $ 1.217$ \\
-            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus & $ 0.118$ & $ 0.062$ & $ 0.713$ & $ 1.521$ \\
-            \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus & $ 0.119$ & $ 0.062$ & $ 0.717$ & $ 1.559$ \\
-            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus & $ 0.118$ & $ 0.062$ & $ 0.716$ & $ 1.549$ \\
-            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus & $ 0.119$ & $ 0.062$ & $ 0.719$ & $ 1.537$ \\
-            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus & $ 0.119$ & $ 0.062$ & $ 0.716$ & $ 1.546$ \\
-            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus & $ 0.118$ & $ 0.062$ & $ 0.715$ & $ 1.532$ \\
-            \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus & $ 0.119$ & $ 0.062$ & $ 0.720$ & $ 1.577$ \\
-            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus & $ 0.118$ & $ 0.062$ & $ 0.715$ & $ 1.539$ \\
-            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus & $ 0.118$ & $ 0.062$ & $ 0.716$ & $ 1.537$ \\
-            African & Homo sapiens & $ 0.170$ & $ 0.103$ & $ 0.885$ & $ 1.744$ \\
-            Admixed American & Homo sapiens & $ 0.170$ & $ 0.103$ & $ 0.884$ & $ 1.742$ \\
-            East Asian & Homo sapiens & $ 0.170$ & $ 0.103$ & $ 0.888$ & $ 1.742$ \\
-            European & Homo sapiens & $ 0.170$ & $ 0.103$ & $ 0.884$ & $ 1.733$ \\
-            South Asian & Homo sapiens & $ 0.170$ & $ 0.103$ & $ 0.886$ & $ 1.745$ \\
+            \rowcolor{LIGHTGREY} Equus caballus & $ 0.129$ & $ 0.065$ & $ 0.832$ & $ 1.267$ \\
+            Bos taurus & [$ 0.114$, $ 0.116$] & [$ 0.063$, $ 0.064$] & [$ 0.629$, $ 0.638$] & [$ 1.280$, $ 1.328$] \\
+            \rowcolor{LIGHTGREY} Capra hircus & [$ 0.108$, $ 0.109$] & [$ 0.058$, $ 0.058$] & [$ 0.631$, $ 0.636$] & [$ 1.169$, $ 1.183$] \\
+            Ovis aries & [$ 0.127$, $ 0.129$] & [$ 0.078$, $ 0.080$] & [$ 0.619$, $ 0.621$] & [$ 1.201$, $ 1.217$] \\
+            \rowcolor{LIGHTGREY} Chlorocebus sabaeus & [$ 0.118$, $ 0.119$] & [$ 0.062$, $ 0.062$] & [$ 0.713$, $ 0.720$] & [$ 1.521$, $ 1.577$] \\
+            Homo sapiens & [$ 0.170$, $ 0.170$] & [$ 0.103$, $ 0.103$] & [$ 0.884$, $ 0.888$] & [$ 1.733$, $ 1.745$] \\
         \end{longtable*}
@@
     \end{itemize}
-
-    \newpage
-
-    \subsubsection{$\dnds$ over-estimation due to beneficial back-mutations}
-    \begin{center}
-        \captionof{table}{$\dnds$ over-estimation due to beneficial back-mutations.}
+    SNP are considered fixed in the populations if all sampled individuals are homozygous for the derived allele, in which case we consider this SNP not to be segregating but as fixed as a substitution.
+    This effect results in $\dn / \ds$ that can change across populations, denoted as a range per species.
+    $\dn(\SphyBen) / \ds$ values observed are above 1 and are consistent with slightly advantageous mutations.\\
+
+    Theoretically, $\omega = \dn / \ds$ can be related to the underlying scaled selection coefficient ($S$) with the relation $\omega = S /(1-\exp(-S))$ as in \cite[eq. 3]{nielsen_estimating_2003}.
+    In our experiments our observed $\dn(\SphyBen) / \ds$ is on the range $1.169$ (\textit{C.
+hircus}) to 1.745 (\textit{H.
+sapiens}), translating into average $S$ of $\approx0.32$ to $\approx1.24$, so indeed only slightly advantageous.\\
+
+    Of note, observing $\dn(\SphyBen) / \ds >1$ is an important check that $\SphyBen$ mutations are indeed positively selected with an increased substitution rate.
+    Since $\dn(\SphyNeu) / \ds$ is close to 1 for the predicted nearly-neutral mutations, this means that the selection coefficients predicted at the mutation-selection balance are good proxies of selection, then observing $\dn(\SphyBen) / \ds > 1$ is evidence of positive selection of predicted non-adaptive beneficial mutations.
+
+    \newpage
+    \subsubsection{$\dnds$ over-estimation due to non-adaptive beneficial mutations}
+    \begin{center}
+        \captionof{table}{$\dnds$ over-estimation due to non-adaptive beneficial mutations.}
         \scriptsize
-        \begin{longtable*}{|l|l|r|r|r|r|r|}
+        \begin{longtable*}{|l|r|r|r|}
             \toprule
-            Population & Species & $\dnds $ & $\dn(\Sphy < 1) / \ds$ & $\delta(\dnds )$ \\
+            Species & $\dnds $ & $\dn(\Sphy < 1) / \ds$ & $\delta(\dnds )$ \\
             \midrule
@@
             \midrule
-            \multicolumn{7}{r}{{Continued on next page}} \\
+            \multicolumn{4}{r}{{Continued on next page}} \\
             \midrule
@@
             \endlastfoot
-            \rowcolor{LIGHTGREY} Equus c. & Equus caballus & $ 0.129$ & $ 0.115$ & $  10.7$ \\
-            Iran & Bos taurus & $ 0.114$ & $ 0.101$ & $  11.3$ \\
-            Uganda & Bos taurus & $ 0.116$ & $ 0.102$ & $  11.5$ \\
-            \rowcolor{LIGHTGREY} Australia & Capra hircus & $ 0.108$ & $ 0.096$ & $  11.1$ \\
-            \rowcolor{LIGHTGREY} France & Capra hircus & $ 0.109$ & $ 0.097$ & $  11.0$ \\
-            \rowcolor{LIGHTGREY} Iran (C. aegagrus) & Capra hircus & $ 0.108$ & $ 0.096$ & $  11.1$ \\
-            \rowcolor{LIGHTGREY} Iran & Capra hircus & $ 0.108$ & $ 0.096$ & $  11.2$ \\
-            \rowcolor{LIGHTGREY} Italy & Capra hircus & $ 0.109$ & $ 0.097$ & $  11.0$ \\
-            \rowcolor{LIGHTGREY} Morocco & Capra hircus & $ 0.108$ & $ 0.096$ & $  11.2$ \\
-            Iran & Ovis aries & $ 0.128$ & $ 0.115$ & $ 9.894$ \\
-            Iran (O. orientalis) & Ovis aries & $ 0.129$ & $ 0.117$ & $ 9.740$ \\
-            Iran (O. vignei) & Ovis aries & $ 0.127$ & $ 0.115$ & $ 9.822$ \\
-            Various & Ovis aries & $ 0.129$ & $ 0.116$ & $ 9.663$ \\
-            Morocco & Ovis aries & $ 0.129$ & $ 0.116$ & $ 9.805$ \\
-            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus & $ 0.118$ & $ 0.104$ & $  11.4$ \\
-            \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus & $ 0.119$ & $ 0.105$ & $  11.5$ \\
-            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus & $ 0.118$ & $ 0.105$ & $  11.5$ \\
-            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus & $ 0.119$ & $ 0.105$ & $  11.4$ \\
-            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus & $ 0.119$ & $ 0.105$ & $  11.5$ \\
-            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus & $ 0.118$ & $ 0.105$ & $  11.4$ \\
-            \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus & $ 0.119$ & $ 0.105$ & $  11.7$ \\
-            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus & $ 0.118$ & $ 0.104$ & $  11.5$ \\
-            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus & $ 0.118$ & $ 0.105$ & $  11.4$ \\
-            African & Homo sapiens & $ 0.170$ & $ 0.154$ & $ 8.996$ \\
-            Admixed American & Homo sapiens & $ 0.170$ & $ 0.155$ & $ 8.978$ \\
-            East Asian & Homo sapiens & $ 0.170$ & $ 0.155$ & $ 8.966$ \\
-            European & Homo sapiens & $ 0.170$ & $ 0.155$ & $ 8.926$ \\
-            South Asian & Homo sapiens & $ 0.170$ & $ 0.155$ & $ 8.986$ \\
+            \rowcolor{LIGHTGREY} Equus caballus & $ 0.129$ & $ 0.115$ & $  10.7$ \\
+            Bos taurus & [$ 0.114$, $ 0.116$] & [$ 0.101$, $ 0.102$] & [$  11.3$, $  11.5$] \\
+            \rowcolor{LIGHTGREY} Capra hircus & [$ 0.108$, $ 0.109$] & [$ 0.096$, $ 0.097$] & [$  11.0$, $  11.2$] \\
+            Chlorocebus sabaeus & [$ 0.118$, $ 0.119$] & [$ 0.104$, $ 0.105$] & [$  11.4$, $  11.7$] \\
+            \rowcolor{LIGHTGREY} Homo sapiens & [$ 0.170$, $ 0.170$] & [$ 0.154$, $ 0.155$] & [$ 8.926$, $ 8.996$] \\
+            Ovis aries & [$ 0.127$, $ 0.129$] & [$ 0.115$, $ 0.117$] & [$ 9.663$, $ 9.894$] \\
         \end{longtable*}
@@
         \item $\dn(\Sphy < 1) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are not $\SphyBen$.
-        This is the estimated divergence when we removed beneficial back-mutations.
-        \item $\delta(\dnds)$ (eq.~7) is the fraction of the divergence ($\dnds$) that is over-estimated, $\dnds$ is compared to the estimated divergence when we removed beneficial back-mutations $\dn(\Sphy < 1) / \ds$.
-    \end{itemize}
-    We estimated that between 9 and 11\% of $\dnds$ is over-estimated, corresponding to beneficial back-mutation inflating the $\dnds$ statistic.
+        This is the estimated divergence when we removed non-adaptive beneficial mutations.
+        \item $\delta(\dnds)$ (eq.~7) is the fraction of the divergence ($\dnds$) that is over-estimated, $\dnds$ is compared to the estimated divergence when we removed non-adaptive beneficial mutations $\dn(\Sphy < 1) / \ds$.
+    \end{itemize}
+    We estimated that between 9 and 11\% of $\dnds$ is over-estimated, corresponding to non-adaptive beneficial mutations inflating the $\dnds$ statistic.
 
@@
     \begin{center}
-        \captionof{table}{Terms associated with deleterious mutations $\SphyDel$}
+        \captionof{table}{Terms associated with deleterious mutations $\SphyDel$.}
         \begin{tabular}{|l|r|r|r|r|r|}
@@
 
-    \subsection{Terms associated with beneficial back-mutations $\SphyBen$}
-    \begin{center}
-        \captionof{table}{Terms associated with beneficial back-mutations $\SphyBen$}
+    \subsection{Terms associated with non-adaptive beneficial mutations $\SphyBen$}
+    \begin{center}
+        \captionof{table}{Terms associated with non-adaptive beneficial mutations $\SphyBen$.}
         \begin{tabular}{|l|r|r|r|r|r|}
@@
     $^*$ for $p_{\mathrm{v}}^{\mathrm{adj}}$ corrected for multiple comparison (Holm–Bonferroni correction) lower than the risk $\alpha=0.05$.
-    Beneficial back-mutations are associated with clinical terms such as \textit{Benign} and \textit{Likely Benign}.
+    Beneficial non-adaptive mutations are associated with clinical terms such as \textit{Benign} and \textit{Likely Benign}.
     \newpage
@@
     \subsubsection{Proportion of deleterious mutations ($\SpopDel$)}\label{subsec:proportion-deleterious-mutations}
-    \captionof{figure}{Proportion of deleterious mutations ($\SpopDel$)}
+    \captionof{figure}{Proportion of deleterious mutations ($\SpopDel$).}
     \begin{minipage}{0.49\linewidth}
@@
     \subsubsection{Proportion of nearly-neutral mutations ($\SpopNeu$)}\label{subsec:proportion-nearly-neutral-mutations}
-    \captionof{figure}{Proportion of nearly-neutral mutations ($\SpopNeu$)}
+    \captionof{figure}{Proportion of nearly-neutral mutations ($\SpopNeu$).}
     \begin{minipage}{0.49\linewidth}
@@
     This result suggests that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) are more likely to discriminate whether mutations are beneficial or deleterious.
-    Alternatively stated, mutations in populations with low diversity (e.g.~\textit{Homo}) are effectively nearly-neutral and behave as would a neutral mutation.
+    Alternatively stated, mutations in populations with low diversity (e.g.~\textit{Homo}) are effectively nearly-neutral and behave as a neutral mutation would.
     This result is qualitatively in accordance with the nearly-neutral theory of evolution which argues that mutations are less efficiently selected for in small populations.
@@
     \subsubsection{Proportion of beneficial mutations ($\SpopBen$)}\label{subsec:proportion-beneficial-mutations}
-    \captionof{figure}{Proportion of beneficial mutations ($\SpopBen$)}
+    \captionof{figure}{Proportion of beneficial mutations ($\SpopBen$).}
     \begin{minipage}{0.49\linewidth}
@@
         These mutations have a selection coefficient at the population-scale larger than 1.
-        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale (the \textit{precision}).
+        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a non-adaptive beneficial mutation at the phylogenetic scale (the \textit{precision}).
     \end{itemize}
     Higher effective population size ($\Ne$) is accompanied by a smaller proportion of beneficial mutations at the population scale ($\proba [ \SpopBen ]$).
-    This trend is also confirmed when we restricted the analysis to class of mutations that are supposedly beneficial back-mutations at the phylogenetic scale ($\SphyBen$).
-    This result is much more difficult to interpret.
-    The fraction of beneficial back mutations is supposed to depend on long term demographic history, which is not directly accessible.
-    If the long term effective population size is relatively similar to the short term one, we expect little opportunity for beneficial back-mutations.
-    And thus, counter-intuitively we expect a diminution of positively selected mutations.
-    However, we can see that the proportion of beneficial back-mutations among advantageous one does not decrease with $\Ne$.
-    This means that somehow adaptive mutations also decrease with $\Ne$ for a reason we fail to explain.
-
-    \newpage
-
-    \section{Probabilities of beneficial back-mutations among all beneficial ones ($\proba[\SphyBen\given \SpopBen ]$)}
-    \begin{center}
-        \captionof{table}{Probability of beneficial back-mutations among all beneficial ones ($\proba[\SphyBen\given \SpopBen ]$).}
+    This trend is also confirmed when we restricted the analysis to class of mutations that are supposedly non-adaptive beneficial mutations at the phylogenetic scale ($\SphyBen$).
+
+    \newpage
+
+    \section{Probability for beneficial mutations to be non-adaptive ($\proba[\SphyBen\given \SpopBen ]$)}
+
+    \subsection{Across the different populations}
+    \begin{center}
+        \captionof{table}{Probability for beneficial mutations to be non-adaptive ($\proba[\SphyBen\given \SpopBen ]$).}
         \scriptsize
@@
         \item $\Ne$ is the estimated effective population size.
-        \item $\proba [ \SphyBen ]$ (eq.~5) is the probability for a new mutation to be a beneficial back-mutation.
+        \item $\proba [ \SphyBen ]$ (eq.~5) is the probability for a new mutation to be a non-adaptive beneficial mutation.
         These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1, thus toward a more fit amino-acid.
@@
         These mutations have a selection coefficient at the population-scale larger than 1.
-        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale (the \textit{precision}).
-        \item $\proba [ \SphyBen \given \SpopBen]$ (eq.~14) is the probability for a mutation to a beneficial back-mutations, given it is beneficial at the population scale (the \textit{recall}).
+        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given that it is predicted to be a non-adaptive beneficial mutation at the phylogenetic scale (the \textit{precision}).
+        \item $\proba [ \SphyBen \given \SpopBen]$ (eq.~14) is the probability for a mutation to be non-adaptive given that it is beneficial at the population scale (the \textit{recall}).
         This probability is obtained using Bayes' formula.
@@
     \newpage
-
+    \subsection{Misannotations of ancestral alleles}
+
+    A potential caveat of our method to is that if a deleterious derived allele segregates at low frequency but is wrongly annotated as ancestral, it will result in a SNP that will be both predicted as advantageous and segregating at high frequency, wrongly suggesting that this variant is correctly inferred as beneficial.
+    In this context misannotations of ancestral alleles could inflate our estimation of the proportion of beneficial non-adaptive mutations.
+    However, we show that this problem impacts our estimation in two ways, albeit, only slightly. \\
+
+    First, if misannotation is influencing the recall for $\SphyBen$ ($\proba[\SphyBen\given \SpopBen ]$), then the recall should increase as a function of  divergence to the sister species ($\ds$: number of synonymous substitutions per sites) since divergence would increase the rate of misannotations.
+    Shown below is recall $\proba[\SphyBen\given \SpopBen ]$ as a function of divergence ($\ds$) in which the latter is not an explanatory variable.
+
+    \begin{center}
+        \captionof{figure}{$\proba[\SphyBen\given \SpopBen ]$ as a function of distance to the sister species.}
+        \includegraphics[width=0.75\linewidth, page=1]{artworks/results.distance.recall_pos.scatter.pdf}
+    \end{center}
+
+    \newpage
+
+    Second, the distribution of selection coefficients ($\Sphy$) that we observed for segregating mutations and for divergence also suggests that we effectively controlled for misannotations.
+    Under a scenario where beneficial non-adaptive mutations would only be the result of misannotations, one would expect that the positive part of the fitness effects (i.e.
+$\proba[\Sphy]$) of observed polymorphism currently segregating in the population should reflect the negative one (i.e.
+$\proba[-\Sphy]$).
+    Indeed, the number of misannotated beneficial mutations should be proportional to the number of deleterious mutations with the same selection coefficient.
+    The ratio between advantageous and deleterious polymorphisms of the same selection coefficient should therefore be a constant that represents the rate of misannotation (typically influenced by the distance to the sister species).
+    However, this is not what we observe in the DFE of polymorphisms (shown below in the African population of \textit{Homo sapiens}) thus giving us the confidence that misannotations are not common.
+
+    \begin{center}
+        \captionof{figure}{Ratio of $\proba[\Sphy]$ over $\proba[-\Sphy]$ for polymorphisms of the African population of \textit{Homo sapiens}.}
+        \includegraphics[width=0.75\linewidth, page=1]{artworks/poly.Homo_sapiens.AFR.folded_ratio.pdf}
+    \end{center}
+
+    Overall, the observed DFE of substitution is much better explained by the expected DFE of new mutations (section S\ref{subsec:expectedDFE} than by mispolarizations).
+
+    \newpage
     \section{Excluding genes under adaptation}
 
-    \begin{center}
-        \captionof{table}{$\proba[\SphyBen\given \SpopBen ]$ for each population when excluding or not genes under adaptation.}
+    \subsection{Probability for beneficial mutations to be non-adaptive}
+    \begin{center}
+        \captionof{table}{$\proba[\SphyBen\given \SpopBen ]$ excluding or not genes under adaptation.}
         \begin{tabular}{|l|l|r|r|}
@@
     \end{center}
-    Genes under adaptation retrieved from~\cite{latrille_genes_2023}.
+    Genes under adaptation retrieved from \textcite{latrille_genes_2023}.
     Comparison of $\proba[\SphyBen\given \SpopBen ]$ for the whole genome (control) and when excluding genes under adaptation (case).
-    The non-parametric Wilcoxon signed-rank test tests the null hypothesis that the distribution of the differences (case versus control) is symmetric about zero.
-    Applied to the paired samples (case and control), Wilcoxon signed-rank test results in $s=80$ with $\pvalue=0.002$. for one-sided test (case higher than control).
-    The proportion of beneficial back-mutations ($\proba[\SphyBen\given \SpopBen ]$) is higher when excluding genes under adaptation, consistent with our expectation that genes with uniformly conserved functions should fit better the back-mutation equilibrium model.
-
-    \newpage
-
-    \section{Replicability across populations}
+    The non-parametric Wilcoxon signed-rank test evaluates the null hypothesis that the distribution of the differences (case versus control) is symmetric about zero.
+    Applied to the paired samples (case and control), Wilcoxon signed-rank test results in $s=80$ with $\pvalue=0.002$, for the one-sided test (case higher than control).
+    The proportion of non-adaptive beneficial mutations ($\proba[\SphyBen\given \SpopBen ]$) is higher when excluding genes under adaptation, consistent with our expectation that genes with uniformly conserved functions should fit better the nearly-neutral equilibrium model.
+
+    \newpage
+
+    \section{Contrasting selection at the phylogenetic and population-genetic scale}
+
+    \subsection{Selection at the population-genetic scale}
     The proportion of deleterious ($\ProbaPopDel$), nearly-neutral ($\ProbaPopNeu$) and of beneficial ($\ProbaPopBen$) mutations estimated at the population-genetic scale across the different populations is shown for each class of selection ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$).
 
-    \captionof{figure}{Estimation of selection at the population scale for $\SphyDel$ mutations}
+    \captionof{figure}{Estimation of selection at the population scale for $\SphyDel$ mutations.}
+    \begin{center}
+        \begin{minipage}{0.75\linewidth}
             \begin{minipage}{0.9\linewidth}
@@
             \end{minipage}
-
-    \newpage
-
-    \captionof{figure}{Estimation of selection at the population scale for $\SphyNeu$ mutations}
+        \end{minipage}
+    \end{center}
+
+    \captionof{figure}{Estimation of selection at the population scale for $\SphyNeu$ mutations.}
+    \begin{center}
+        \begin{minipage}{0.75\linewidth}
             \begin{minipage}{0.9\linewidth}
@@
             \end{minipage}
-
-    \captionof{figure}{Estimation of selection at the population scale for $\SphyBen$ mutations}
+        \end{minipage}
+    \end{center}
+
+    \captionof{figure}{Estimation of selection at the population scale for $\SphyBen$ mutations.}
+    \begin{center}
+        \begin{minipage}{0.75\linewidth}
             \begin{minipage}{0.9\linewidth}
@@
             \end{minipage}
-
-    \newpage
-
+        \end{minipage}
+    \end{center}
+
+    \newpage
+    \subsection{Distribution of scaled selection coefficients ($\Sphy$)}\label{subsec:expectedDFE}
+
+    Theoretically, the selection coefficient ($\Sphy$) for any mutation is related to its probability of fixation by the equation $\proba_{\text{fix}} (\Sphy) = \Sphy/(1-\exp(-\Sphy)) $.
+    It is thus possible to predict the distribution of $\Sphy$ of substitutions given the distribution of $\Sphy$ for mutations (e.g.
+panel A below) by weighting the different mutations by their $\proba_{\text{fix}} (\Sphy)$.
+    The predicted DFE of substitutions (panel B below) matches the observed DFE of substitutions (panel C below) in the terminal lineage, meaning that the $\Sphy$ obtained by phylogenetic mutation-selection codon models is a strong predictor of selection effectively exerted on mutations in terminal lineages.
+
+    The figures shown below are obtained in the Saint Kitts population of \textit{Chlorocebus sabaeus}.
+    These figures across the 28 populations are available at Zenodo (\url{https://doi.org/10.5281/zenodo.7878953}) in file \textit{distribution\_S0\_28\_populations.pdf}.\\
+
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny A: Expected DFE for mutations}
+        \includegraphics[width=\linewidth, page=1]{artworks/DFE.Chlorocebus_sabaeus.Saint_Kitts.MutSel.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny B: Expected DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{artworks/DFE.Chlorocebus_sabaeus.Saint_Kitts.MutSel.Flow.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny C: Observed DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{artworks/subs.Chlorocebus_sabaeus.Saint_Kitts.bins3Mask0.9.pdf}
+    \end{minipage}
+    \\
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny D: Observed DFE for polymorphisms}
+        \includegraphics[width=\linewidth, page=1]{artworks/poly.Chlorocebus_sabaeus.Saint_Kitts.bins3Mask0.9.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny E: Site frequency spectrum}
+        \includegraphics[width=\linewidth, page=1]{artworks/Chlorocebus_sabaeus.Saint_Kitts.MutSel-sfs.normalize.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
+        \includegraphics[width=\linewidth, page=1]{artworks/Chlorocebus_sabaeus.Saint_Kitts.MutSel.polyDFE_C.pdf}
+    \end{minipage}
+
+    \begin{itemize}[itemsep=0pt]
+        \item A: Distribution of scaled selection coefficients ($\Sphy$), predicted for all possible non-synonymous DNA mutations away from the ancestral exome.
+        Mutations are divided into three classes of selection: deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial non-adaptive ($\SphyBen$).
+        \item B: Expected distribution of $\Sphy$ for substitutions obtained by transforming the distribution of $\Sphy$ for mutations (panel A) by weighting each mutation by its scaled probability of fixation given by $\proba_{\text{fix}} (\Sphy) = \Sphy/(1-\exp(-\Sphy))$.
+        \item C: Distribution of scaled selection coefficients ($\Sphy$) for all observed substitutions along the terminal branch of the phylogenetic tree.
+        \item D: Distribution of scaled selection coefficients ($\Sphy$) for all observed polymorphisms currently segregating in the population.
+        \item E: The site-frequency spectrum (SFS) in the population for a random sample of 16 alleles (means in solid lines and standard deviations in color shades) for each class of selection and for synonymous mutations, supposedly neutral (black).
+The SFS represents the proportion of mutations (y-axis) with a given number of derived alleles in the population (x-axis).
+At high frequencies, deleterious mutations are underrepresented.
+        \item F: Proportion of beneficial $\ProbaPopDel$, nearly-neutral $\ProbaPopNeu$, and deleterious mutations $\ProbaPopBen$  estimated at the population scale for each class of selection at the phylogenetic scale.
+Proportions depicted here are not weighted by their mutational opportunities.
+    \end{itemize}
+
+    \section{Filtering of variable sites}
+
+    \subsection{Masking CpG transitions}
+    We also tested our prediction while masking CpG transitions since the mutation rate of CpG dinucleotides is higher than the mutation rate of other dinucleotides, which can affect the estimation of the DFE.
+    Any nucleotide transition including a CpG dinucleotide either in the ancestral or derived state is considered as a CpG transition.
+    We masked all CpG transitions in the mutational opportunities, the substitutions in the terminal branches, and the polymorphisms segregating in the population.
+We then re-estimated the DFE and the proportion of non-adaptive beneficial mutations.
+
+    \subsection{Probability for beneficial mutations to be non-adaptive}
+    \begin{center}
+        \captionof{table}{$\proba[\SphyBen\given \SpopBen ]$ while masking CpG transitions.}
+        \scriptsize
+        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
+            \toprule
+            Population & Species & $\Ne$ & $\proba[\SphyBen]$ & $\proba [ \SpopBen ]$ & $\frac{\proba[\SphyBen]}{\proba[ \SpopBen ]}$ & $\proba [ \SpopBen \given \SphyBen]$ & $\proba[\SphyBen\given \SpopBen ]$ \\
+            \midrule
+            \endhead
+            \midrule
+            \multicolumn{8}{r}{{Continued on next page}} \\
+            \midrule
+            \endfoot
+
+            \bottomrule
+            \endlastfoot
+            \rowcolor{LIGHTGREY} Equus c. & Equus caballus & $7.5\times 10^{4}$ & $ 0.012$ & $ 0.028$ & $ 0.421$ & $ 0.543$ & $ 0.229$ \\
+            Iran & Bos taurus & $5.6\times 10^{4}$ & $ 0.011$ & $ 0.038$ & $ 0.283$ & $ 0.797$ & $ 0.226$ \\
+            Uganda & Bos taurus & $1.3\times 10^{5}$ & $ 0.011$ & $ 0.022$ & $ 0.479$ & $ 0.406$ & $ 0.195$ \\
+            \rowcolor{LIGHTGREY} Australia & Capra hircus & $1.7\times 10^{5}$ & $ 0.011$ & $ 0.024$ & $ 0.454$ & $ 0.158$ & $ 0.072$ \\
+            \rowcolor{LIGHTGREY} France & Capra hircus & $1.9\times 10^{5}$ & $ 0.011$ & $ 0.034$ & $ 0.320$ & $ 0.258$ & $ 0.082$ \\
+            \rowcolor{LIGHTGREY} Iran (C. aegagrus) & Capra hircus & $1.9\times 10^{5}$ & $ 0.011$ & $ 0.032$ & $ 0.341$ & $ 0.268$ & $ 0.091$ \\
+            \rowcolor{LIGHTGREY} Iran & Capra hircus & $2.3\times 10^{5}$ & $ 0.011$ & $ 0.026$ & $ 0.417$ & $ 0.294$ & $ 0.123$ \\
+            \rowcolor{LIGHTGREY} Italy & Capra hircus & $1.9\times 10^{5}$ & $ 0.011$ & $ 0.023$ & $ 0.472$ & $ 0.100$ & $ 0.047$ \\
+            \rowcolor{LIGHTGREY} Morocco & Capra hircus & $2.2\times 10^{5}$ & $ 0.011$ & $ 0.018$ & $ 0.593$ & $ 0.141$ & $ 0.083$ \\
+            Iran & Ovis aries & $3.8\times 10^{5}$ & $ 0.011$ & $ 0.012$ & $ 0.981$ & $ 0.243$ & $ 0.239$ \\
+            Iran (O. orientalis) & Ovis aries & $4.5\times 10^{5}$ & $ 0.011$ & $ 0.019$ & $ 0.603$ & $ 0.155$ & $ 0.093$ \\
+            Iran (O. vignei) & Ovis aries & $3.7\times 10^{5}$ & $ 0.011$ & $ 0.025$ & $ 0.445$ & $ 0.252$ & $ 0.112$ \\
+            Various & Ovis aries & $4.1\times 10^{5}$ & $ 0.011$ & $ 0.016$ & $ 0.704$ & $ 0.198$ & $ 0.139$ \\
+            Morocco & Ovis aries & $ 4\times 10^{5}$ & $ 0.011$ & $ 0.008$ & $ 1.389$ & $ 0.165$ & $ 0.229$ \\
+            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus & $1.1\times 10^{5}$ & $ 0.009$ & $ 0.013$ & $ 0.752$ & $ 0.231$ & $ 0.174$ \\
+            \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus & $1.7\times 10^{5}$ & $ 0.009$ & $ 0.018$ & $ 0.519$ & $ 0.209$ & $ 0.108$ \\
+            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus & $1.4\times 10^{5}$ & $ 0.009$ & $ 0.025$ & $ 0.385$ & $ 0.241$ & $ 0.093$ \\
+            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus & $1.4\times 10^{5}$ & $ 0.009$ & $ 0.007$ & $ 1.346$ & $ 0.204$ & $ 0.275$ \\
+            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus & $1.5\times 10^{5}$ & $ 0.009$ & $ 0.021$ & $ 0.443$ & $ 0.239$ & $ 0.106$ \\
+            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus & $ 1\times 10^{5}$ & $ 0.009$ & $ 0.014$ & $ 0.690$ & $ 0.146$ & $ 0.101$ \\
+            \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus & $1.8\times 10^{5}$ & $ 0.009$ & $ 0.019$ & $ 0.498$ & $ 0.272$ & $ 0.135$ \\
+            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus & $1.2\times 10^{5}$ & $ 0.009$ & $ 0.017$ & $ 0.567$ & $ 0.217$ & $ 0.123$ \\
+            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus & $1.7\times 10^{5}$ & $ 0.009$ & $ 0.024$ & $ 0.388$ & $ 0.308$ & $ 0.119$ \\
+            African & Homo sapiens & $5.6\times 10^{4}$ & $ 0.010$ & $ 0.026$ & $ 0.367$ & $ 0.411$ & $ 0.151$ \\
+            Admixed American & Homo sapiens & $4.5\times 10^{4}$ & $ 0.010$ & $ 0.017$ & $ 0.551$ & $ 0.374$ & $ 0.206$ \\
+            East Asian & Homo sapiens & $ 4\times 10^{4}$ & $ 0.010$ & $ 0.029$ & $ 0.332$ & $ 0.370$ & $ 0.123$ \\
+            European & Homo sapiens & $4.2\times 10^{4}$ & $ 0.010$ & $ 0.031$ & $ 0.304$ & $ 0.371$ & $ 0.113$ \\
+            South Asian & Homo sapiens & $4.4\times 10^{4}$ & $ 0.010$ & $ 0.032$ & $ 0.302$ & $ 0.369$ & $ 0.111$ \\
+        \end{longtable*}
+    \end{center}
+    \begin{itemize}
+        \item $\Ne$ is the estimated effective population size.
+        \item $\proba [ \SphyBen ]$ (eq.~5) is the probability for a new mutation a non-adaptive beneficial mutation.
+        These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1, thus toward a more fit amino-acid.
+        \item $\proba [ \SpopBen ]$ (eq.~15) is the probability for a mutation to be beneficial.
+        These mutations have a selection coefficient at the population-scale larger than 1.
+        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a non-adaptive beneficial mutation at the phylogenetic scale (the \textit{precision}).
+        \item $\proba [ \SphyBen \given \SpopBen]$ (eq.~14) is the probability for a mutation to be non-adaptive given it is beneficial at the population scale (the \textit{recall}).
+        This probability is obtained using Bayes' formula.
+    \end{itemize}
+    \newpage
+
+    \subsection{Precision and recall}
+    \captionof{table}{Precision and recall while masking CpG transitions.}
+    \begin{center}
+        \begin{adjustbox}{width=\textwidth}
+            \begin{tabular}{||l|l|r||r|r||r|r||r|r||}
+                \toprule
+                \multicolumn{3}{||c||}{} &
+                \multicolumn{2}{c||}{\shortstack{\textbf{Deleterious mutations} \\ $\bm{\SpopDel \coloneqq \Spop<-1}$ \\ $\bm{\SphyDel \coloneqq \Sphy<-1}$}} &
+                \multicolumn{2}{c||}{\shortstack{\textbf{Nearly-neutral mutations} \\ $\bm{\SpopNeu \coloneqq -1<\Spop<1}$ \\ $\bm{\SphyNeu \coloneqq -1<\Sphy<1}$}} &
+                \multicolumn{2}{c||}{\shortstack{\textbf{Beneficial mutations} \\ $\bm{\SpopBen \coloneqq \Spop>1}$ \\ $\bm{\SphyBen \coloneqq \Sphy>1}$}}
+                \\ \hline
+                \textbf{Population} &
+                \textbf{Species} &
+                $\bm{\Ne}$ &
+                \makecell{\textbf{Precision} \\ $\bm{\proba [\SpopDel \given \SphyDel]}$} &
+                \makecell{\textbf{Recall} \\ $\bm{\proba [\SphyDel \given \SpopDel]}$}           &
+                \makecell{\textbf{Precision}      \\ $\bm{\proba [\SpopNeu \given \SphyNeu]}$}                                    &
+                \makecell{\textbf{Recall}          \\ $\bm{\proba [\SphyNeu \given \SpopNeu]}$}                                  &
+                \makecell{\textbf{Precision}          \\ $\bm{\proba [\SpopBen \given \SphyBen]}$}          &
+                \makecell{\textbf{Recall}        \\ $\bm{\proba [\SphyBen \given \SpopBen]}$}
+                \\   \midrule
+                \rowcolor{LIGHTGREY} Equus c. & Equus caballus & $7.5\times 10^{4}$ & $ 0.887$ & $ 0.984$ & $ 0.740$ & $ 0.356$ & $ 0.543$ & $ 0.229$ \\
+                Iran & Bos taurus & $5.6\times 10^{4}$ & $ 0.888$ & $ 1.000$ & $ 0.632$ & $ 0.302$ & $ 0.797$ & $ 0.226$ \\
+                Uganda & Bos taurus & $1.3\times 10^{5}$ & $ 0.929$ & $ 0.973$ & $ 0.501$ & $ 0.349$ & $ 0.406$ & $ 0.195$ \\
+                \rowcolor{LIGHTGREY} Australia & Capra hircus & $1.7\times 10^{5}$ & $ 0.926$ & $ 0.972$ & $ 0.609$ & $ 0.421$ & $ 0.158$ & $ 0.072$ \\
+                \rowcolor{LIGHTGREY} France & Capra hircus & $1.9\times 10^{5}$ & $ 0.927$ & $ 0.959$ & $ 0.354$ & $ 0.321$ & $ 0.258$ & $ 0.082$ \\
+                \rowcolor{LIGHTGREY} Iran (C. aegagrus) & Capra hircus & $1.9\times 10^{5}$ & $ 0.931$ & $ 0.967$ & $ 0.502$ & $ 0.423$ & $ 0.268$ & $ 0.091$ \\
+                \rowcolor{LIGHTGREY} Iran & Capra hircus & $2.3\times 10^{5}$ & $ 0.937$ & $ 0.966$ & $ 0.529$ & $ 0.451$ & $ 0.294$ & $ 0.123$ \\
+                \rowcolor{LIGHTGREY} Italy & Capra hircus & $1.9\times 10^{5}$ & $ 0.927$ & $ 0.970$ & $ 0.550$ & $ 0.390$ & $ 0.100$ & $ 0.047$ \\
+                \rowcolor{LIGHTGREY} Morocco & Capra hircus & $2.2\times 10^{5}$ & $ 0.933$ & $ 0.965$ & $ 0.534$ & $ 0.401$ & $ 0.141$ & $ 0.083$ \\
+                Iran & Ovis aries & $3.8\times 10^{5}$ & $ 0.947$ & $ 0.957$ & $ 0.446$ & $ 0.393$ & $ 0.243$ & $ 0.239$ \\
+                Iran (O. orientalis) & Ovis aries & $4.5\times 10^{5}$ & $ 0.951$ & $ 0.961$ & $ 0.396$ & $ 0.386$ & $ 0.155$ & $ 0.093$ \\
+                Iran (O. vignei) & Ovis aries & $3.7\times 10^{5}$ & $ 0.954$ & $ 0.960$ & $ 0.379$ & $ 0.432$ & $ 0.252$ & $ 0.112$ \\
+                Various & Ovis aries & $4.1\times 10^{5}$ & $ 0.949$ & $ 0.956$ & $ 0.434$ & $ 0.418$ & $ 0.198$ & $ 0.139$ \\
+                Morocco & Ovis aries & $ 4\times 10^{5}$ & $ 0.946$ & $ 0.959$ & $ 0.453$ & $ 0.374$ & $ 0.165$ & $ 0.229$ \\
+                \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus & $1.1\times 10^{5}$ & $ 0.916$ & $ 0.971$ & $ 0.523$ & $ 0.306$ & $ 0.231$ & $ 0.174$ \\
+                \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus & $1.7\times 10^{5}$ & $ 0.933$ & $ 0.969$ & $ 0.486$ & $ 0.353$ & $ 0.209$ & $ 0.108$ \\
+                \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus & $1.4\times 10^{5}$ & $ 0.918$ & $ 0.973$ & $ 0.533$ & $ 0.348$ & $ 0.241$ & $ 0.093$ \\
+                \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus & $1.4\times 10^{5}$ & $ 0.925$ & $ 0.971$ & $ 0.572$ & $ 0.343$ & $ 0.204$ & $ 0.275$ \\
+                \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus & $1.5\times 10^{5}$ & $ 0.931$ & $ 0.971$ & $ 0.521$ & $ 0.378$ & $ 0.239$ & $ 0.106$ \\
+                \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus & $ 1\times 10^{5}$ & $ 0.916$ & $ 0.972$ & $ 0.535$ & $ 0.313$ & $ 0.146$ & $ 0.101$ \\
+                \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus & $1.8\times 10^{5}$ & $ 0.928$ & $ 0.970$ & $ 0.546$ & $ 0.378$ & $ 0.272$ & $ 0.135$ \\
+                \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus & $1.2\times 10^{5}$ & $ 0.917$ & $ 0.971$ & $ 0.507$ & $ 0.309$ & $ 0.217$ & $ 0.123$ \\
+                \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus & $1.7\times 10^{5}$ & $ 0.930$ & $ 0.969$ & $ 0.495$ & $ 0.372$ & $ 0.308$ & $ 0.119$ \\
+                African & Homo sapiens & $5.6\times 10^{4}$ & $ 0.888$ & $ 0.978$ & $ 0.587$ & $ 0.296$ & $ 0.411$ & $ 0.151$ \\
+                Admixed American & Homo sapiens & $4.5\times 10^{4}$ & $ 0.874$ & $ 0.979$ & $ 0.591$ & $ 0.256$ & $ 0.374$ & $ 0.206$ \\
+                East Asian & Homo sapiens & $ 4\times 10^{4}$ & $ 0.877$ & $ 0.980$ & $ 0.593$ & $ 0.280$ & $ 0.370$ & $ 0.123$ \\
+                European & Homo sapiens & $4.2\times 10^{4}$ & $ 0.885$ & $ 0.980$ & $ 0.591$ & $ 0.301$ & $ 0.371$ & $ 0.113$ \\
+                South Asian & Homo sapiens & $4.4\times 10^{4}$ & $ 0.886$ & $ 0.979$ & $ 0.591$ & $ 0.303$ & $ 0.369$ & $ 0.111$ \\
+                \bottomrule
+            \end{tabular}
+        \end{adjustbox}
+    \end{center}
+    \begin{itemize}
+        \item $\Ne$ is the estimated effective population size.
+        \item \textit{Precision} is the estimation of the selection coefficient at population scale ($\Spop$) given that $\Sphy$ is known.
+        \item \textit{Recall} is the estimation of $\Sphy$ given selection coefficient at the population scale ($\Spop$) is known.
+        \item \textit{Recall} for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is the probability for a mutation to be non-adaptive given it is beneficial at the population scale.
+    \end{itemize}
+
+    Altogether, comparing this table other estimations, we acknowledge that the exact proportion of non-adaptive among beneficial mutations is dependent on the whether we masked CpG sites.
+    However, we can still see that non-adaptive beneficial mutations are positively selected compared to neutral and deleterious ones, and this result is not dependent on whether we masked CpG sites or not.
+
+    \newpage
+
+    \subsection{Example site-frequency spectrum}\label{subsec:CpG-expectedDFE}
+
+    The site-frequency spectrum (SFS, panel A) and the congruency between fitness effects estimates ($\Sphy$ versus $\Sphy$, panel B) shown below are obtained in the African population of \textit{Homo sapiens} and the South African population of \textit{Chlorocebus sabaeus}.
+
+    \begin{center}
+        \captionof{figure}{Site-frequency spectrum in African population of \textit{Homo sapiens}, masking CpG transitions.}
+        \begin{minipage}{0.49\linewidth}
+            \flushleft {\tiny A: Site frequency spectrum}
+            \includegraphics[width=\linewidth, page=1]{artworks/CpG.Homo_sapiens.AFR.MutSel-sfs.pdf}
+        \end{minipage}
+        \begin{minipage}{0.49\linewidth}
+            \flushleft {\tiny B: $S$ as function of $S_0$ for each class}
+            \includegraphics[width=\linewidth, page=1]{artworks/CpG.Homo_sapiens.AFR.MutSel.polyDFE_C.pdf}
+        \end{minipage}
+    \end{center}
+
+    \begin{center}
+        \captionof{figure}{Site-frequency spectrum in South African population of \textit{Chlorocebus sabaeus}, masking CpG transitions.}
+        \begin{minipage}{0.49\linewidth}
+            \flushleft {\tiny A: Site frequency spectrum}
+            \includegraphics[width=\linewidth, page=1]{artworks/CpG.Chlorocebus_sabaeus.South_Africa.MutSel-sfs.pdf}
+        \end{minipage}
+        \begin{minipage}{0.49\linewidth}
+            \flushleft {\tiny B: $S$ as function of $S_0$ for each class}
+            \includegraphics[width=\linewidth, page=1]{artworks/CpG.Chlorocebus_sabaeus.South_Africa.MutSel.polyDFE_C.pdf}
+        \end{minipage}
+    \end{center}
+
+    \begin{itemize}[itemsep=0pt]
+        \item A: The site-frequency spectrum (SFS) in the population for a random sample of 16 alleles (means in solid lines and standard deviations in color shades) for each class of selection and for synonymous mutations, supposedly neutral (black).
+The SFS represents the proportion of mutations (y-axis) with a given number of derived alleles in the population (x-axis).
+Here SFS are weighted by the mutational opportunities in each class of selection (synonymous, $\SphyDel$, $\SphyNeu$ and $\SphyBen$).
+        \item B: Proportion of beneficial $\ProbaPopDel$, nearly-neutral $\ProbaPopNeu$, and deleterious mutations $\ProbaPopBen$  estimated at the population scale for each class of selection at the phylogenetic scale.
+Proportions depicted here are not weighted by their mutational opportunities.
+    \end{itemize}
+
+    \newpage
     \section{Including divergence data for the estimation of $\Spop$}
@@
 
-    \subsection{Probabilities of beneficial back-mutations}
-    \begin{center}
-        \captionof{table}{Probability of beneficial back-mutations among all beneficial ones - including divergence.}
+    \subsection{Probability for beneficial mutations to be non-adaptive}
+    \begin{center}
+        \captionof{table}{$\proba[\SphyBen\given \SpopBen ]$ when including divergence to estimate $\Spop$.}
         \scriptsize
@@
         \item $\Ne$ is the estimated effective population size.
-        \item $\proba [ \SphyBen ]$ (eq.~5) is the probability for a new mutation a beneficial back-mutation.
+        \item $\proba [ \SphyBen ]$ (eq.~5) is the probability for a new mutation a non-adaptive mutation.
         These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1, thus toward a more fit amino-acid.
@@
         These mutations have a selection coefficient at the population-scale larger than 1.
-        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale (the \textit{precision}).
-        \item $\proba [ \SphyBen \given \SpopBen]$ (eq.~14) is the probability for a mutation to a beneficial back-mutations, given it is beneficial (the \textit{recall}).
+        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a non-adaptive mutation at the phylogenetic scale (the \textit{precision}).
+        \item $\proba [ \SphyBen \given \SpopBen]$ (eq.~14) is the probability for a mutation to be non-adaptive given it is beneficial at the population scale (the \textit{recall}).
         This probability is obtained using Bayes' formula.
@@
     \subsection{Precision and recall}
-    \captionof{table}{Precision and recall - including divergence}
+    \captionof{table}{Precision and recall while including divergence to estimate $\Spop$.}
     \begin{center}
@@
         \item  \textit{Recall} is the estimation of $\Sphy$ given selection coefficient at the population scale ($\Spop$) is known.
-        \item \textit{Recall} for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is thus the proportion of beneficial back-mutations among all beneficial mutations.
-    \end{itemize}
-
-    Altogether, comparing this table to tables 1 and S3, we acknowledge that the exact proportion of beneficial back-mutations among all beneficial ones is different whether we included or not substitutions in the terminal lineage for the estimation of $\Spop$.
-    However, we can still see that beneficial back-mutations are positively selected compared to neutral and deleterious ones, and this result is not sensitive to inclusion of substitutions in the terminal lineage.
+        \item \textit{Recall} for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is the probability for a mutation to be non-adaptive given it is beneficial at the population scale.
+    \end{itemize}
+
+    Altogether, comparing this table to tables 1 and S3, we acknowledge that the exact proportion of non-adaptive beneficial mutations among all beneficial ones is different whether we included or not substitutions in the terminal lineage for the estimation of $\Spop$.
+    However, we can still see that non-adaptive beneficial mutations are positively selected compared to neutral and deleterious ones, and this result is not sensitive to inclusion of substitutions in the terminal lineage.
+    \newpage
+
+    \subsection{Misannotations of ancestral alleles}
+
+    If misannotation is influencing the recall for $\SphyBen$ ($\proba[\SphyBen\given \SpopBen ]$), then the recall should increase as a function of  divergence to the sister species ($\ds$: number of synonymous substitutions per sites) since divergence would increase the rate of misannotations.
+    Shown below is recall $\proba[\SphyBen\given \SpopBen ]$ as a function of divergence ($\ds$) in which the latter is not an explanatory variable.
+
+    \begin{center}
+        \captionof{figure}{$\proba[\SphyBen\given \SpopBen ]$ while including divergence to estimate $\Spop$, as a function of distance to the sister species.}
+        \includegraphics[width=0.75\linewidth, page=1]{artworks/results.distance.recall_pos.div.scatter.pdf}
+    \end{center}
+
     \newpage
@@
     \begin{center}
-        \captionof{table}{$\proba[\SphyBen\given \SpopBen ]$ for each population when excluding or not genes under adaptation - including divergence.}
+        \captionof{table}{$\proba[\SphyBen\given \SpopBen ]$ excluding or not genes under adaptation, when including divergence to estimate $\Spop$.}
         \begin{tabular}{|l|l|r|r|}
@@
     Applied to the paired samples (case and control), Wilcoxon signed-rank test results in $s=120$ with $\pvalue=0.027$ for one-sided test (case higher than control).
-    The proportion of beneficial back-mutations ($\proba[\SphyBen\given \SpopBen ]$) is higher when excluding genes under adaptation, consistent with our expectation that genes with uniformly conserved functions should fit better the back-mutation equilibrium model.
+    The proportion of beneficial non-adaptive mutations ($\proba[\SphyBen\given \SpopBen ]$) is higher when excluding genes under adaptation, consistent with our expectation that genes with uniformly conserved functions should fit better the nearly-neutral equilibrium model.
 
@@
 
-    \subsection{Probabilities of beneficial back-mutations}
-    \begin{center}
-        \captionof{table}{Probability of beneficial back-mutations among all beneficial ones - model D.}
+    \subsection{Probability for beneficial mutations to be non-adaptive}
+    \begin{center}
+        \captionof{table}{$\proba[\SphyBen\given \SpopBen ]$ when using a discrete DFE to estimate $\Spop$.}
         \scriptsize
@@
         \item $\Ne$ is the estimated effective population size.
-        \item $\proba [ \SphyBen ]$ (eq.~5) is the probability for a new mutation a beneficial back-mutation.
+        \item $\proba [ \SphyBen ]$ (eq.~5) is the probability for a new mutation a non-adaptive beneficial mutation.
         These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1, thus toward a more fit amino-acid.
@@
         These mutations have a selection coefficient at the population-scale larger than 1.
-        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale (the \textit{precision}).
-        \item $\proba [ \SphyBen \given \SpopBen]$ (eq.~14) is the probability for a mutation to a beneficial back-mutations, given it is beneficial (the \textit{recall}).
+        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial non-adaptive mutation at the phylogenetic scale (the \textit{precision}).
+        \item $\proba [ \SphyBen \given \SpopBen]$ (eq.~14) is the probability for a mutation to be non-adaptive given it is beneficial at the population scale (the \textit{recall}).
         This probability is obtained using Bayes' formula.
     \end{itemize}
-    \newpage
 
     \subsection{Precision and recall}
-    \captionof{table}{Precision and recall - model D}
+    \captionof{table}{Precision and recall when using a discrete DFE to estimate $\Spop$.}
     \begin{center}
@@
         \item \textit{Recall} is the estimation of $\Sphy$ given selection coefficient at the population scale ($\Spop$) is known.
-        \item \textit{Recall} for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is thus the proportion of beneficial back-mutations among all beneficial mutations.
-    \end{itemize}
-
-    Altogether, comparing this table other estimations, we acknowledge that the exact proportion of beneficial back-mutations among all beneficial ones is dependent on the model used to estimate the DFE.
-    However, we can still see that beneficial back-mutations are positively selected compared to neutral and deleterious ones, and this result is not sensitive to the underlying DFE at the population scale.
-
-    \newpage
-
-    \newpage
+        \item \textit{Recall} for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is the probability for a mutation to be non-adaptive given it is beneficial at the population scale.
+    \end{itemize}
+
+    Altogether, comparing this table other estimations, we acknowledge that the exact proportion of non-adaptive among all beneficial ones is dependent on the model used to estimate the DFE.
+    However, we can still see that non-adaptive beneficial mutations are positively selected compared to neutral and deleterious ones, and this result is not sensitive to the underlying DFE at the population scale.
+
+    \newpage
+
+    \newpage
+
     \printbibliography

### 2024-03-04 copy_artworks.sh

@@ -4,6 +4,8 @@
 \cp -rf ./experiments/3bins-mC-nodiv/analysis/Homo_sapiens.AFR.MutSel.polyDFE_C.pdf ./manuscript/artworks/AFR.polyDFE.pdf
 \cp -rf ./data_processed/opportunities_bins3Mask0.9/DFE.Homo_sapiens.AFR.MutSel.pdf ./manuscript/artworks/AFR.histogramDFE.pdf
 \cp -rf ./data_processed/ancestral_bins3Mask0.9/Homo_sapiens.AFR.pdf ./manuscript/artworks/AFR.histogramDiv.pdf
+\cp -rf ./supp/hist/subs.Homo_sapiens.AFR.bins3Mask0.9.folded_ratio.pdf ./manuscript/artworks/subs.Homo_sapiens.AFR.folded_ratio.pdf
+\cp -rf ./supp/hist/poly.Homo_sapiens.AFR.bins3Mask0.9.folded_ratio.pdf ./manuscript/artworks/poly.Homo_sapiens.AFR.folded_ratio.pdf
 \cp -rf ./experiments/3bins-mC-nodiv/regression-MutSel/results.pop_size.bayes_P-Spos_P-pos.scatter.pdf ./manuscript/artworks/results.pop_size.Bayes.pdf
 \cp -rf ./experiments/3bins-mC-nodiv/regression-MutSel/results.pop_size.mut_sum_P-Sweak.scatter.pdf ./manuscript/artworks/results.pop_size.all_P-Sweak.scatter.pdf
 \cp -rf ./experiments/3bins-mC-nodiv/regression-MutSel/results.pop_size.weak_P-Sweak.scatter.pdf ./manuscript/artworks/results.pop_size.weak_P-Sweak.scatter.pdf
@@ -14,4 +16,17 @@
 \cp -rf ./experiments/3bins-mC-nodiv/results/Theta.MutSel.weak.stacked.pdf ./manuscript/artworks/Theta.weak.stacked.pdf
 \cp -rf ./experiments/3bins-mC-nodiv/results/Theta.MutSel.neg.stacked.pdf ./manuscript/artworks/Theta.neg.stacked.pdf
 \cp -rf ./experiments/3bins-mC-nodiv/results/Theta.MutSel.pos.stacked.pdf ./manuscript/artworks/Theta.pos.stacked.pdf
[…]

### 2024-03-04 scripts/compare_ontology_ratio.py

@@ -1,14 +1,19 @@
 import os
 import argparse
 import pandas as pd
+from itertools import product
 from collections import defaultdict
 from scipy.stats import wilcoxon
 from libraries import sort_df, tex_f, row_color
 
 
-def open_results(path: str, sample_list: str) -> dict:
-    df = pd.read_csv(os.path.join(path, "regression-MutSel", "results.tsv"), sep="\t")
-    df = sort_df(df, args.sample_list)  # assign the pop name to the index
+def open_results(path: str, sample_list: str) -> pd.DataFrame:
+    path_tsv = os.path.join(path, "regression-MutSel", "results.tsv")
+    if not os.path.exists(path_tsv):
+        print(f"\nSkipping {path} as it does not contain a results.tsv")
+        return pd.DataFrame()
+    df = pd.read_csv(path_tsv, sep="\t")
+    df = sort_df(df, sample_list)  # assign the pop name to the index
     df = row_color(df)  # assign the pop name to the index
     df_out = df[["pop", "species", "recall_pos"]]
     return df_out
@@ -16,28 +21,33 @@ def open_results(path: str, sample_list: str) -> dict:
 
 def main(experiments: str, sample_list: str, output: str):
     # Iter over folders with "Onto" in the name
-    control_name = "3bins-mC"
-    control_path = os.path.join(experiments, control_name)
-    control_df = open_results(control_path, sample_list)
-    control = control_df["recall_pos"].values
-
-    case_path_list = [os.path.join(experiments, f) for f in os.listdir(experiments)]
+    case_path_list = sorted([os.path.join(experiments, f) for f in os.listdir(experiments)])
     case_path_list = [f for f in case_path_list if os.path.isdir(f)]
-    case_path_list = [f for f in case_path_list if (("Adaptation" in f))]
+    case_path_list = [f for f in case_path_list if ("NonAdaptive" in f)]
+    control_list = ["3bins-mC-nodiv", "3bins-mD"]
 
-    print(control)
     out_dict = defaultdict(list)
-    tex_file = open(output.replace(".tsv", f".{control_name}.tex"), "w")
-    for case_path in case_path_list:
+    tex_file = open(output.replace(".tsv", f".tex"), "w")
+    for case_path, control_name in product(case_path_list, control_list):
         case_name = os.path.basename(case_path)
-        print(f"Comparing {case_name} to control")
+        if case_name == control_name:
+            continue
[…]

### 2024-03-04 scripts/ete3_custom_faces.py

@@ -2,6 +2,7 @@ from __future__ import absolute_import
 from __future__ import print_function
 import re
 import math
+from itertools import product
 from collections import defaultdict
 
 try:
@@ -27,72 +28,40 @@ from ete3.treeview.qt import (QGraphicsRectItem, QGraphicsLineItem,
 
 from ete3.treeview.main import add_face_to_node, _Background, _Border, COLOR_SCHEMES
 
-_aafgcolors = {
-    'A': "#000000",
-    'R': "#000000",
-    'N': "#000000",
-    'D': "#000000",
-    'C': "#000000",
-    'Q': "#000000",
-    'E': "#000000",
-    'G': "#000000",
-    'H': "#000000",
-    'I': "#000000",
-    'L': "#000000",
-    'K': "#000000",
-    'M': "#000000",
-    'F': "#000000",
-    'P': "#000000",
-    'S': "#000000",
-    'T': "#000000",
-    'W': "#000000",
-    'Y': "#000000",
-    'V': "#000000",
-    'B': "#000000",
-    'Z': "#000000",
-    'X': "#000000",
-    '.': "#000000",
-    '-': "#000000",
-}
+_aafgcolors = defaultdict(lambda: "#000000")
+_aafgcolors.update({
+    '_': "#FFFFFF"
+})
 
-_aabgcolors = {
-    'A': "#C8C8C8",
-    'R': "#145AFF",
-    'N': "#00DCDC",
-    'D': "#E60A0A",
-    'C': "#E6E600",
-    'Q': "#00DCDC",
-    'E': "#E60A0A",
-    'G': "#EBEBEB",
-    'H': "#8282D2",
-    'I': "#0F820F",
-    'L': "#0F820F",
-    'K': "#145AFF",
-    'M': "#E6E600",
-    'F': "#3232AA",
-    'P': "#DC9682",
-    'S': "#FA9600",
-    'T': "#FA9600",
-    'W': "#B45AB4",
-    'Y': "#3232AA",
-    'V': "#0F820F",
-    'B': "#FF69B4",
-    'Z': "#FF69B4",
-    'X': "#BEA06E",
-    '.': "#FFFFFF",
-    '-': "#FFFFFF",
-}
+_aabgcolors = defaultdict(lambda: "#FFFFFF")
+_aabgcolors.update(
+    {
+        "A": "#fea0fd",
+        "C": "#fc0cfe",
+        "D": "#2e7bbe",
+        "E": "#677892",
[…]

### 2024-03-04 scripts/libraries.py

@@ -102,10 +102,14 @@ def clean_ensg_path(path):
     return path
 
 
+def open_file(path):
+    path = clean_ensg_path(path)
+    return gzip.open(path, 'rt') if path.endswith(".gz") else open(path, 'r')
+
+
 def open_fasta(path):
     outfile = {}
-    path = clean_ensg_path(path)
-    ali_file = gzip.open(path, 'rt') if path.endswith(".gz") else open(path, 'r')
+    ali_file = open_file(path)
     for seq_id in ali_file:
         outfile[seq_id.replace('>', '').strip()] = ali_file.readline().strip()
     return outfile
@@ -115,7 +119,7 @@ def fasta_txt(dico_fasta):
     return "\n".join([f">{seq_id}\n{seq}" for seq_id, seq in dico_fasta.items()])
 
 
-def write_fasta(dico_fasta, output):
+def write_fasta(dico_fasta: dict[str: str], output: str):
     outfile = gzip.open(output, 'wt') if output.endswith(".gz") else open(output, 'w')
     outfile.write(fasta_txt(dico_fasta))
     outfile.close()

### 2024-03-04 scripts/mask_adaptation.py

@@ -1,39 +1,45 @@
 import os
 import argparse
-import numpy as np
 import pandas as pd
 from collections import defaultdict
-gene_level = True
 
 
 def main(args):
     os.makedirs(os.path.dirname(args.output), exist_ok=True)
     output_dict = defaultdict(list)
-
+    print("Site level:", args.site_level, "Output:", args.output, "ωᴬ:", args.omega_A)
     for ensg in os.listdir(args.exp_folder):
         if "ENSG" not in ensg:
             continue
         f_path = f"{args.exp_folder}/{ensg}"
-        path_mutsel = f"{f_path}/sitemutsel_1.run.ci0.025.tsv"
-        path_omega = f"{f_path}/siteomega_1.run.ci0.025.tsv"
+        ensg_name = ensg.replace('__', '_null_').replace('_NT', '')
+        ci = "0.025"
+        path_mutsel = f"{f_path}/sitemutsel_1.run.ci{ci}.tsv"
+        path_omega = f"{f_path}/siteomega_1.run.ci{ci}.tsv"
         array_mutsel = pd.read_csv(path_mutsel, sep="\t")["omega_upper"].values
         array_omega = pd.read_csv(path_omega, sep="\t")["omega_lower"].values
         assert len(array_mutsel) == len(array_omega)
-        nbr_sites = len(array_mutsel) - 1
-        ensg_name = ensg.replace('__', '_null_').replace('_NT', '')
-        if gene_level:
-            mutsel_upper = array_mutsel[0]
-            omega_lower = array_omega[0]
-            if omega_lower > mutsel_upper:
-                output_dict["ensg"].extend([ensg_name] * nbr_sites)
-                output_dict["pos"].extend(range(nbr_sites))
-        else:
-            mutsel_upper = pd.read_csv(path_mutsel, sep="\t")["omega_upper"].values[1:]
-            omega_lower = pd.read_csv(path_omega, sep="\t")["omega_lower"].values[1:]
-            adaptation = np.argwhere(omega_lower > mutsel_upper)
+        mutsel_upper = array_mutsel[0]
+        omega_lower = array_omega[0]
+        if omega_lower > mutsel_upper:
+            nbr_sites = len(array_mutsel) - 1
+            output_dict["ensg"].extend([ensg_name] * nbr_sites)
+            output_dict["pos"].extend(range(nbr_sites))
+        elif args.site_level:
+            if args.omega_A:
+                path_mutsel = f"{f_path}/sitemutsel_1.run.omegaA.tsv"
[…]

### 2024-03-04 scripts/onto_compare.py

@@ -1,20 +1,0 @@
-import pandas as pd
-from scipy.stats import wilcoxon
-
-
-def open_results(exp):
-    tmp_df = pd.read_csv(f"experiments/{exp}/regression-MutSel/results.tsv", sep="\t", index_col=0)
-    return tmp_df["bayes_P-Spos_P-pos"]
-
-
-control = "3bins-mC"
-dico_df = {control: open_results(control)}
-cases = ["3bins-mC-OntoCytoplasme", "3bins-mC-OntoNucleus", "3bins-mC-OntoMembrane", "3bins-mC-OntoProtBind",
-         "3bins-mC-OntoRegTrans"]
-
-for case in cases:
-    dico_df[case] = open_results(case)
-    res = wilcoxon(dico_df[control], dico_df[case], alternative="two-sided")
-    print(case, res, (dico_df[case] / dico_df[control]).mean())
-
-df = pd.DataFrame(dico_df)

### 2024-03-04 scripts/tex_sfs.py

@@ -9,9 +9,10 @@ dict_method = {"MutSel": "Site-specific Mutation-Selection codon models.",
                "SIFT": "SIFT score", }
 
 
-def minipage(size, file):
-    assert os.path.exists(file), f"{file} does not exist."
+def minipage(size, file, name=""):
+    assert os.path.exists(file), f"File {file} does not exist"
     out = "\\begin{minipage}{" + str(size) + "\\linewidth} \n"
+    out += "\\flushleft {\\tiny " + name + "}\n"
     out += "\\includegraphics[width=\\linewidth, page=1]{" + file + "} \n"
     out += "\\end{minipage}\n"
     return out
@@ -52,30 +53,33 @@ def main(args):
                 dfe_suffix = f"{sp}.{pop}.{method}.pdf".replace(' ', '_')
                 dfe_path = f"{args.dfe_prefix}{dfe_suffix}"
 
-                six_panels = "/TSV/" in args.hist_prefix
+                six_panels = "/HOLD_" in args.hist_prefix
                 if six_panels:
                     hist_holder = f"{sp}.{pop}.".replace(' ', '_')
                     hist_subs_path = args.hist_prefix.replace("/HOLD_", "/subs." + hist_holder) + ".pdf"
                     hist_poly_path = args.hist_prefix.replace("/HOLD_", "/poly." + hist_holder) + ".pdf"
 
-                    o.write(minipage(0.32, dfe_path))
-                    o.write(minipage(0.32, dfe_path.replace(".pdf", ".Flow.pdf")))
-                    o.write(minipage(0.32, hist_subs_path))
+                    o.write(minipage(0.32, dfe_path, "A: Expected DFE for mutations"))
+                    o.write(minipage(0.32, dfe_path.replace(".pdf", ".Flow.pdf"),
+                                     "B: Expected DFE for substitutions"))
+                    o.write(minipage(0.32, hist_subs_path, "C: Observed DFE for substitutions"))
 
                     o.write("\\\\ \n")
-                    o.write(minipage(0.32, hist_poly_path))
-                    o.write(minipage(0.32, sfs.replace("-sfs.pdf", "-sfs.normalize.pdf")))
+                    o.write(minipage(0.32, hist_poly_path, "D: Observed DFE for polymorphisms"))
+                    o.write(minipage(0.32, sfs.replace("-sfs.pdf", "-sfs.normalize.pdf"),
+                                     "E: Site frequency spectrum"))
                     for model in ["C", "D"]:
[…]

### 2024-03-06 manuscript/main-PNAS.tex
Added figure titles in supp. mat.

@@
 Importantly, because mutation-selection codon models at the phylogenetic scale are based on population-genetics equations, their estimates of selection coefficients are directly interpretable as fitness effects at the population scale; and because they work at the DNA level, we are able to account for mutational bias in DNA and structure of the genetic code.
-The model further integrates the shared evolutionary history between samples and their divergence, which, together, allow us to estimate fitness effects in mammalian phylogenetic trees even though sequences are not independent samples and might not represent the equilibrium distribution of amino acids (see section \ref{subsec:s-phylogeny-method} in Materials \& Methods, model parameters in section S1).
+The model further integrates the shared evolutionary history between samples and their divergence, which, together, allow us to estimate fitness effects in mammalian phylogenetic trees even though sequences are not independent samples and might not represent the equilibrium distribution of amino acids (see section \ref{subsec:s-phylogeny-method} in Materials \& Methods, model parameters in section S1 and fig.~S1).
 
@@
 Example substitutions in the terminal lineage of \textit{Chlorocebus sabaeus} which are classified as $\SphyBen$ are shown in supplementary materials (section S2).
-For instance, in the mammalian protein-coding DNA alignment of gene \textit{SELE}, the nucleotide at site 1722 has mutated (from T to C) at the base of Simiiformes (monkeys and apes), modifying the corresponding amino acid from Serine to Proline, but has been subsequently reverted in the branch of \textit{Chlorocebus sabaeus} (fig.~S1).
-However, other substitutions classified as $\SphyBen$ in the terminal branch of \textit{Chlorocebus sabaeus} cannot be clearly interpreted as reversions along the terminal branch, and show several transitions to this amino acid across the mammalian phylogeny, as for instance site 3145 of gene \textit{THSD7A} (fig.~S2).
+For instance, in the mammalian protein-coding DNA alignment of gene \textit{SELE}, the nucleotide at site 1722 has mutated (from T to C) at the base of Simiiformes (monkeys and apes), modifying the corresponding amino acid from Serine to Proline, but has been subsequently reverted in the branch of \textit{Chlorocebus sabaeus} (fig.~S2).
+However, other substitutions classified as $\SphyBen$ in the terminal branch of \textit{Chlorocebus sabaeus} cannot be clearly interpreted as reversions along the terminal branch, and show several transitions to this amino acid across the mammalian phylogeny, as for instance site 3145 of gene \textit{THSD7A} (fig.~S3).
 
@@
 
-Importantly, if there are several substitutions toward the same amino acid along the mammalian tree, (see fig.~S2) our mutation-selection model cannot distinguish between a scenario where mammals have fixed deleterious mutations that are reverted in several lineages, from more complex scenarios involving adaptation.
+Importantly, if there are several substitutions toward the same amino acid along the mammalian tree, (see fig.~S3) our mutation-selection model cannot distinguish between a scenario where mammals have fixed deleterious mutations that are reverted in several lineages, from more complex scenarios involving adaptation.
 In a first scenario, repeated changes of fitness landscapes in the same direction could occur along several lineages, leading to repeated substitutions in multiple lineages (parallel or convergent adaptation).

### 2024-03-06 manuscript/main-revision-2.tex
Added figure titles in supp. mat.

@@
 These mutations are typically unpredictable since they respond to an unforeseen change in the environment.
-However, mutations can also be beneficial because they are simply restoring an ancestral sequence of higher fitness that was lost due to genetic drift.
-In contrast to adaptive mutations, these beneficial back-mutations can be predicted if the underlying fitness landscape is stable and known.
-The contribution of such beneficial back-mutations to molecular evolution has been widely neglected mainly because their detection is very challenging.
+However, mutations can also be beneficial because they are simply restoring a state of higher fitness that was lost due to genetic drift in a stable environment.
+In contrast to adaptive mutations, these beneficial non-adaptive mutations can be predicted if the underlying fitness landscape is stable and known.
+The contribution of such non-adaptive mutations to molecular evolution has been widely neglected mainly because their detection is very challenging.
 We have here reconstructed protein-coding-gene fitness landscapes shared between mammals, using mutation-selection models and a multi-species alignments across 87 mammals.
 These fitness landscapes have allowed us to predict the fitness effect of polymorphisms found in 28 mammalian populations.
-Using methods that quantify selection at the population level, we have confirmed that beneficial back-mutations are indeed positively selected in extant populations.
+Using methods that quantify selection at the population level, we have confirmed that beneficial non-adaptive mutations are indeed positively selected in extant populations.
 Our work confirms that deleterious substitutions are accumulating in mammals and are being reverted, generating a balance in which genomes are damaged and restored simultaneously at different loci.
-We observe that beneficial back-mutations represent between 15\% and 45\% of all beneficial mutations in 24 of 28 populations analyzed, showing that a substantial part of ongoing positive selection is not driven by adaptation to environmental change in mammals.
+We observe that beneficial non-adaptive mutations represent between 15\% and 45\% of all beneficial mutations in 24 of 28 populations analyzed, showing that a substantial part of ongoing positive selection is not driven solely by adaptation to environmental change in mammals.
     \end{abstract}
 
-    \keywords{Adaptation \and Back-mutations \and Phylogenetics \and Population-genetics \and Codon models }
+    \keywords{Adaptation \and Nearly-neutral \and Phylogenetics \and Population-genetics \and Codon models }
 
@@
 To quantify the rate of adaptation, population geneticists have typically used signatures of positive selection.
-However, mutations restoring an ancestral sequence of higher fitness lost by genetic drift are also positively selected, but they do not respond to a change in the environment.
+However, mutations restoring an ancestral state of higher fitness lost by genetic drift are also positively selected, but they do not respond to a change in the environment.
 In this study, we have managed to distinguish beneficial mutations that are due to changing environments and those that are restoring pre-existing functions in mammals.
@@
 
-    In a constant environment, a deleterious mutation can reach fixation by genetic drift~\cite{Ohta1992}.
+    \subsection*{Beneficial yet non-adaptive mutations}
+
+    In a constant environment, a deleterious mutation can reach fixation by genetic drift~\cite{ohta_nearly_1992}.
     A new mutation restoring the ancestral fitness will thus be beneficial (fig.~\ref{fig:fitness-landscape}B), even though the environment has not changed~\cite{gillespie_ohta_1995, hartl_compensatory_1996, sella_application_2005, mustonen_fitness_2009, cvijovic_fate_2015}.
-    The restoration of the ancestral fitness can either happen through a mutation at a different locus –~called a compensatory mutation~\cite{hartl_compensatory_1996, mustonen_fitness_2009}, or at the locus of the initial mutation –~called a beneficial back-mutation~\cite{piganeau_estimating_2003, charlesworth_other_2007}.
-    While compensatory mutations change the sequence and thus induce genetic diversification, beneficial back-mutations reduce genetic diversity and do not contribute to genetic innovation.
-    Although Tomoko Ohta considered beneficial back-mutations negligible in her nearly-neutral theory~\cite{Ohta1992}, their importance has now been acknowledged for expanding populations~\cite{charlesworth_other_2007}.
-    However, differentiating between an adaptive mutation and a beneficial back-mutation remains challenging~\cite{chi_detecting_2020}.
-    Indeed, an adaptive mutation responding to a change in the environment and a beneficial back-mutation have equivalent fitness consequences for their bearer~\cite{charlesworth_other_2007}.
+    We will refer to as beneficial non-adaptive mutations to those mutations that restore the ancestral fitness under the assumption that the fitness landscape has not changed~\cite{piganeau_estimating_2003, charlesworth_other_2007}.
+    Such mutations can happen through a mutation at a different locus, in which case it is called a compensatory mutation~\cite{hartl_compensatory_1996, mustonen_fitness_2009}.
+    While compensatory mutations change the sequence and thus induce genetic diversification, beneficial non-adaptive mutations at the locus of the initial mutation reduce genetic diversity and do not contribute to genetic innovation, which are the focus of this manuscript.
+    Although Tomoko Ohta considered beneficial non-adaptive mutations negligible in her nearly-neutral theory~\cite{ohta_nearly_1992}, their importance has now been acknowledged for expanding populations~\cite{charlesworth_other_2007}.
+    However, differentiating between an adaptive mutation and a beneficial non-adaptive mutation remains challenging~\cite{chi_detecting_2020}.
+    Indeed, an adaptive mutation responding to a change in the environment and a beneficial non-adaptive mutation have equivalent fitness consequences for their bearer~\cite{charlesworth_other_2007}.
     Similarly, at the population level, both types of mutations will result in a positive transmission bias of the beneficial allele.
     However, at the macro-evolutionary scale, the consequences of these two types of mutations are fundamentally different.
-    While adaptive mutations promote phenotype diversification (fig.~\ref{fig:fitness-landscape}C), beneficial back-mutations promote phenotype stability and may help preserve well-established biological systems (fig.~\ref{fig:fitness-landscape}D).
+    While adaptive mutations promote phenotype diversification (fig.~\ref{fig:fitness-landscape}C), beneficial non-adaptive mutations promote phenotype stability and may help preserve well-established biological systems (fig.~\ref{fig:fitness-landscape}D).
     Additionally, the direction of adaptive evolution is unpredictable because it is caused by an unforeseen change in the environment and, hence, in the underlying fitness landscape~\cite{bazykin_changing_2015}.
-    On the other hand, beneficial back-mutations are predictable because, under a stable fitness landscape, any change from non-optimal to optimal amino acids will move back the site towards the equilibrium expected under the fitness landscape~\cite{moses_inferring_2009, fischer_germline_2011, chen_hunting_2021}.
-    It can then be distinguished from truly novel beneficial mutations because the latter are not expected to mutate mutate towards the amino acids of higher fitnesses defined by the stable fitness landscape but rather mutate to amino acids showing a diversified pattern (fig.~\ref{fig:fitness-landscape}).
+    On the other hand, beneficial non-adaptive mutations are predictable because, under a stable fitness landscape, any change from non-optimal to optimal amino acids will move back the site toward the equilibrium expected under the fitness landscape~\cite{moses_inferring_2009, fischer_germline_2011, chen_hunting_2021}.
+    They can then be distinguished from truly novel beneficial mutations because the latter are not expected to mutate toward the amino acids of higher fitnesses defined by the stable fitness landscape but rather mutate to amino acids showing a diversified pattern (fig.~\ref{fig:fitness-landscape}).
 
@@
     Importantly, because mutation-selection codon models at the phylogenetic scale are based on population-genetics equations, their estimates of selection coefficients are directly interpretable as fitness effects at the population scale; and because they work at the DNA level, we are able to account for mutational bias in DNA and structure of the genetic code.
-    The model further integrates the shared evolutionary history between samples and their divergence, which, together, allow us to estimate fitness effects in mammalian phylogenetic trees even though sequences are not independent samples and might not represent the equilibrium distribution of amino acids (see section \ref{subsec:s-phylogeny-method} in Materials \& Methods, model parameters in section S1).
+    The model further integrates the shared evolutionary history between samples and their divergence, which, together, allow us to estimate fitness effects in mammalian phylogenetic trees even though sequences are not independent samples and might not represent the equilibrium distribution of amino acids (see section \ref{subsec:s-phylogeny-method} in Materials \& Methods, model parameters in section S1 and fig.~S1).
 
-    Theoretically, we can thus use large-scale genomic data to assess whether the fitness estimated at the phylogenetic scale predict the fitness effect at the population scale for both deleterious and beneficial back-mutations.
+    Theoretically, we can thus use large-scale genomic data to assess whether the fitness estimated at the phylogenetic scale predicts the fitness effect at the population scale for both deleterious and beneficial non-adaptive mutations.
     The placental mammals represent an excellent study system to perform such analysis.
@@
 The value of $\Sphy$ informs us on the strength of selection exerted on amino acids changes.
-    Thus, according to its $\Sphy$ value, we can classify any mutation as either a deleterious mutation toward a less fit amino acid ($\SphyDel \coloneqq \Sphy < -1$), a nearly-neutral mutation ($\SphyNeu \coloneqq -1 < \Sphy <1$) or a beneficial back-mutation toward a known fitter amino acid ($\SphyBen \coloneqq \Sphy > 1$).
+    Thus, according to its $\Sphy$ value, we can classify any mutation as either a deleterious mutation toward a less fit amino acid ($\SphyDel \coloneqq \Sphy < -1$), a nearly-neutral mutation ($\SphyNeu \coloneqq -1 < \Sphy <1$), or a mutation toward a known fitter amino acid constituting thus a beneficial non-adaptive mutation ($\SphyBen \coloneqq \Sphy > 1$).
 
-    Having identified which potential DNA changes represent beneficial back-mutations (fig.~\ref{fig:method}B), we retrieved polymorphism data from 28 wild and domesticated populations belonging to 6 genera (\textit{Equus}, \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus}, and \textit{Homo}) to assess the presence of beneficial back-mutations at the population scale.
-    We focused on mutations currently segregating within populations and substitutions in the terminal branches, and checked if any of these observed changes were beneficial back-mutations (fig.~\ref{fig:method}C-E).
-    A similar approach demonstrated the presence of beneficial back-mutations in humans~\cite{moses_inferring_2009, fischer_germline_2011} and in plants~\cite{chen_hunting_2021}.
+    Having identified which potential DNA changes represent beneficial non-adaptive mutations (fig.~\ref{fig:method}B), we retrieved polymorphism data from 28 wild and domesticated populations belonging to six genera (\textit{Equus}, \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus}, and \textit{Homo}) to assess the presence of beneficial non-adaptive mutations at the population scale.
+    We focused on mutations currently segregating within populations and substitutions in the terminal branches, and checked if any of these observed changes were indeed beneficial (fig.~\ref{fig:method}C-E).
+    A similar approach demonstrated the presence of beneficial non-adaptive mutations in humans~\cite{moses_inferring_2009, fischer_germline_2011} and in plants~\cite{chen_hunting_2021}.
     However, the model used to reconstruct the static fitness landscape in these studies can only be applied to deeply conserved protein domains in the tree of life, which corresponds to a subpart of the proteome that evolves slowly.
-    The mutation-selection model used in the present work integrates phylogenetic relationships, and thus allows us to estimate the fitness landscape in shallower phylogenetic trees, and therefore can be applied almost genome-wide~\cite{rodrigue_mutationselection_2010}.
+    The mutation-selection model used in the present work integrates phylogenetic relationships, and thus allows us to estimate the fitness landscape in shallower phylogenetic trees, and therefore can be applied almost exome-wide~\cite{rodrigue_mutationselection_2010}.
 
-    We first quantified the likelihood of any DNA mutation to be a beneficial back-mutation, that is, whenever a DNA mutation increases fitness under a stable fitness landscape ($\SphyBen$).
-    Subsequently, by quantifying the total amount of beneficial mutations in the current population across all types of DNA mutations ($\SphyDel$, $\SphyDel$ and $\SphyBen$), we could tease apart beneficial back-mutations from beneficial adaptive mutations resulting from a change in the fitness landscape.
-    Altogether, in this study, by integrating large-scale genomic datasets at both phylogenetic and population scales, we propose a way to explicitly quantify the contribution of beneficial back-mutations to positive selection across the entire exome of the six genera (figs.~\ref{fig:method}F-G).
+    We first quantified the likelihood of any DNA mutation to be a beneficial non-adaptive mutation, that is, whenever a DNA mutation increases fitness under a stable fitness landscape ($\SphyBen$).
+    Subsequently, by quantifying the total amount of beneficial mutations in the current population across all types of DNA mutations ($\SphyDel$, $\SphyNeu$ and $\SphyBen$), we could tease apart beneficial non-adaptive from adaptive mutations resulting from a change in the fitness landscape.
+    Altogether, in this study, by integrating large-scale genomic datasets at both phylogenetic and population scales, we propose a way to explicitly quantify the contribution of beneficial non-adaptive mutations to positive selection across the entire exome of the six genera (figs.~\ref{fig:method}F-G).
 
@@
     We classified each substitution identified in the terminal branches as either $\SphyDel$, $\SphyNeu$, or $\SphyBen$ depending on its $\Sphy$ value obtained at the phylogenetic scale (fig.~\ref{fig:method}A-C).
-    Importantly, the mammalian alignment used to estimate the amino-acid fitness landscape did not include the genera for which we estimated selection at the population scale as this would bias the estimate of the fitness landscape and generate circular reasoning.
-    Because $\Sphy$ was based on estimating fitness effects at the phylogenetic scale for all mammals, substitutions with $\Sphy>1$ ($\SphyBen$) bring the population toward an amino acid predicted to be fitter in mammals.
-    These changes are thus considered as beneficial back-substitutions rather than a species-specific adaptive change.
-    Among all the substitutions found in each terminal branch, between 10 and 13\% were $\SphyBen$, while instead beneficial back-mutations represent between 0.9 and 1.2\% of all non-synonymous mutations (table~S1 and fig.~\ref{fig:homo-afr-results}A-B for humans).
-    In principle, beneficial back-mutations are bound to reach fixation more often than neutral mutations.
-    Hence, we calculated the $\dnds$ ratio of non-synonymous over synonymous divergence for all terminal lineages, focusing on the non-synonymous changes predicted as beneficial back-mutations ($\dn(\SphyBen) / \ds$).
-    We obtained values between 1.17 and 1.75 in the different lineages (table~S2), implying i) that $\SphyBen$ mutations reached fixation more frequently than synonymous mutations that are supposed to be neutral, and ii) that these back-mutations are effectively beneficial.
+    Because estimation $\Sphy$ was based on the assumption that the fitness landscape is stable across mammals, $\SphyBen$ mutations (i.e., with $\Sphy>1$) bring the bearer of this mutation toward an amino acid predicted to be fitter across mammals.
+    Importantly, the mammalian alignment used to estimate the amino acid fitness landscape did not include the six focal genera and their sister species.
+    This ensures independence between, on the one hand, the fitness landscape estimated, and on the other hand, both substitutions that occurred in the terminal branches, and segregating polymorphisms of the focal populations.
+    Example substitutions in the terminal lineage of \textit{Chlorocebus sabaeus} which are classified as $\SphyBen$ are shown in supplementary materials (section S2).
+    For instance, in the mammalian protein-coding DNA alignment of gene \textit{SELE}, the nucleotide at site 1722 has mutated (from T to C) at the base of Simiiformes (monkeys and apes), modifying the corresponding amino acid from Serine to Proline, but has been subsequently reverted in the branch of \textit{Chlorocebus sabaeus} (fig.~S2).
+    However, other substitutions classified as $\SphyBen$ in the terminal branch of \textit{Chlorocebus sabaeus} cannot be clearly interpreted as reversions along the terminal branch, and show several transitions to this amino acid across the mammalian phylogeny, as for instance site 3145 of gene \textit{THSD7A} (fig.~S3).
 
-    This result further indicated that using $\dnds$ as an estimate of adaptation is biased due to the presence of beneficial back-mutations among the non-synonymous substitutions.
-    By discarding all beneficial back-mutations we can obtain an estimate of $\dnds$ which is not inflated.
-    By comparing these two ways of calculating $\dnds$ (see section~\ref{subsec:substitution-mapping-in-the-terminal-branch} in Materials \& Methods), we calculated that beneficial back-mutations inflate $\dnds$ values by between 9 and 12\% across genera while only representing between 0.9 and 1.2\% of non-synonymous mutations (table~S3).
+    Among all the substitutions found in each terminal branch, between 10 and 13\% were $\SphyBen$, while $\SphyBen$ mutations only represent between 0.9 and 1.2\% of all non-synonymous mutations (table~S1 and fig.~\ref{fig:homo-afr-results}A-B for humans).
+    Furthermore, since in principle, $\SphyBen$ mutations are bound to reach fixation more often than neutral mutations, we calculated the $\dnds$ ratio of non-synonymous over synonymous divergence for all terminal lineages, focusing on the non-synonymous changes predicted as $\SphyBen$ mutations ($\dn(\SphyBen) / \ds$).
+    We obtained values between 1.17 and 1.75 in the different lineages (table~S2), meaning that $\SphyBen$ mutations reach fixation slightly more frequently than synonymous mutations that are supposed to be neutral, consistent with these $\SphyBen$ mutations being weakly beneficial.
+
+    This result further indicates that using $\dnds$ as an estimate of adaptation is biased due to the presence of beneficial non-adaptive mutations among the non-synonymous substitutions.
+    By discarding all beneficial non-adaptive mutations we can obtain an estimate of $\dnds$ which is not inflated.
+    By comparing these two ways of calculating $\dnds$ (see section~\ref{subsec:substitution-mapping-in-the-terminal-branch} in Materials \& Methods), we calculated that beneficial non-adaptive mutations inflate $\dnds$ values by between 9 and 12\% across genera.
+This represents a substantial increase when considering that beneficial non-adaptive mutations only represent between 0.9 and 1.2\% of non-synonymous mutational opportunities (table~S3).
 
@@
 
-    In humans, some SNPs have been associated with specific clinical prognosis terms obtained by clinical evaluation of the impact of variants on human Mendelian disorders ~\cite{landrum_clinvar_2018}.
+    In humans, some SNPs have been associated with specific clinical prognosis terms obtained by clinical evaluation of the impact of variants on human Mendelian disorders~\cite{landrum_clinvar_2018}.
     Although this classification also relies on deep protein alignments and therefore cannot be considered an independent result from our own, it does provide a consistency check if the effect of a mutation on human health is in line with its fitness effect predicted by our method.
@@
     Our results show that SNPs predicted as deleterious are associated with clinical terms such as \textit{Likely Pathogenic} and \textit{Pathogenic}, implying that, in general, the selective pressure of a mutation exerted across mammals is also predictive of its clinical effect in humans (table~S4)~\cite{sullivan_leveraging_2023}.
-    Conversely, back-mutations are associated with clinical terms such as \textit{Benign} and \textit{Likely Benign}, which shows that back-mutations are less likely to be functionally damaging (table~S5).
+    Conversely, $\SphyBen$ mutations are associated with clinical terms such as \textit{Benign} and \textit{Likely Benign}, which shows that $\SphyBen$ mutations are less likely to be functionally damaging (table~S5).
 
@@
     The variable proportions between populations can be explained by the effective number of individuals in the population ($\Ne$), a major driver of selection efficacy.
-    Moreover, estimates of mutation rate per generation ($u$), from \textcite{bergeron_evolution_2023} and \textcite{orlando_recalibrating_2013}, and Watterson’s $\theta$ obtained from the synonymous SFS as in \textcite{achaz_frequency_2009} allow us to obtain $\Ne$ through $\Ne=\theta/(4 \times u)$.
+    Moreover, estimates of mutation rate per generation ($u$), from \textcite{bergeron_evolution_2023} and \textcite{orlando_recalibrating_2013}, and Watterson’s $\theta$ obtained from the synonymous SFS as in \textcite{achaz_frequency_2009}, allow us to obtain $\Ne$ through $\Ne=\theta/4 u)$.
     Using correlation analyses that accounted for phylogenetic relationship (see section \ref{subsec:correlation-diversity} in Materials \& Methods), we found that higher $\Ne$ was associated with a smaller proportion of nearly-neutral mutations ($r^2=0.31$, $p=0.001$, fig.~\ref{fig:diversity}A).
-    This result follows the prediction of the nearly-neutral theory and suggests that in populations with higher diversity (e.g.,~\textit{Bos} or \textit{Ovis}), discrimination between beneficial and deleterious mutations is more likely to occur (figs.~S1-S3).
+    This result follows the prediction of the nearly-neutral theory and suggests that in populations with higher diversity (e.g.,~\textit{Bos} or \textit{Ovis}), discrimination between beneficial and deleterious mutations is more likely to occur (figs.~S3-S5).
     Conversely, many more mutations are effectively neutral in populations with lower diversity (e.g.,~\textit{Homo}).
 
-    Finally, mutations predicted to be beneficial back-mutations based on the selection coefficients at the phylogenetic scale ($\SphyBen$) were indeed beneficial for individuals bearing them, with a \textit{precision} (fig.~\ref{fig:method}F) in the range of 19--87\% (table~\ref{table:proba} and fig.~\ref{fig:homo-afr-results}D for humans).
-    This result confirms that selection towards amino acids restoring existing functions is ongoing in these populations.
-    Importantly, the \textit{recall} value in this case, computed as $\proba [ \SphyBen  \given  \SpopBen]$, is the probability for a beneficial mutation at the population scale to be a beneficial back-mutation, i.e., going toward a fitter amino acid (fig.~\ref{fig:method}G, table~S6).
+    Finally, mutations predicted to be $\SphyBen$ were indeed beneficial for individuals bearing them, with a \textit{precision} (fig.~\ref{fig:method}F) in the range of 19--87\% (table~\ref{table:proba} and fig.~\ref{fig:homo-afr-results}D for humans).
+    This result confirms that selection toward amino acids restoring existing functions is ongoing in these populations.
+    Importantly, the \textit{recall} value in this case, computed as $\proba [ \SphyBen  \given  \SpopBen]$, is the probability for a beneficial mutation at the population scale to be a non-adaptive, i.e., going toward a  fitter amino acid given a stable fitness landscape (fig.~\ref{fig:method}G, table~S6).
     In other words, the \textit{recall} value quantifies the number of beneficial mutations restoring damaged genomes instead of creating adaptive innovations.
@@
 
-    Because the phylogenetic mutation-selection codon model should fit better for genes with uniformly conserved functions, as a control, we filtered out genes under pervasive adaptation~\cite{latrille_genes_2023}, and indeed we found an increase in the proportion of beneficial back-mutations ($\proba [ \SphyBen  \given  \SpopBen]$), consistent with our expectation (Wilcoxon signed-rank, $s=80$, $p=0.002$, table~S7).
+    Additionally, we controlled that these estimations are not affected by SNP mispolarization (figs.~S6-S7).
+    Moreover, because the phylogenetic mutation-selection codon model should fit better for genes with uniformly conserved functions, as a control, we filtered out genes under pervasive adaptation~\cite{latrille_genes_2023}, and indeed we found an increase in the proportion of beneficial mutations that are non-adaptive ($\proba [ \SphyBen  \given  \SpopBen]$), consistent with our expectation (Wilcoxon signed-rank, $s=80$, $p=0.002$, table~S7).
 
@@
     This study represents an essential step toward integrating the different evolutionary scales necessary to understand the combined effects of mutation, selection, and drift on genome evolution.
-    In particular, we have been able to quantify the proportion of beneficial back-mutations among all beneficial mutations, which has only been achievable by combining genome-wide data from both phylogenetic and population scales.
+    In particular, we have been able to quantify the proportion of beneficial mutations that are non-adapative (i.e., not a response to a change in fitness landscape), which has only been achievable by combining exome-wide data from both phylogenetic and population scales.
     At the phylogenetic scale, codon diversity at each site of a protein-coding DNA alignment allows for reconstructing an amino-acid fitness landscape, assuming that this landscape is stable along the phylogenetic tree.
     These amino-acid fitness landscapes allow us to predict any mutation’s selection coefficient ($\Sphy$) along a protein-coding sequence.
-    We can compare these selective effects to observations at the population level (figs.~S4-6).
-    By doing so, we confirmed that mutations predicted to be deleterious ($\SphyDel \coloneqq \Sphy < -1$) are purified away in extant populations.
+    We have compared these selective effects to observations at the population level (figs.~S8-10), and by doing so, we have confirmed that mutations predicted to be deleterious ($\SphyDel \coloneqq \Sphy < -1$) are generally purified away in extant populations.
     Our results concur with previous studies showing that SIFT scores~\cite{ng_sift_2003, vaser_sift_2016}, based on amino acid alignments across species, also inform on the deleterious fitness effects exerted at the population scale~\cite{chen_hunting_2021}.
-    However – contrary to SIFT scores – our mutation-selection model is parameterized by a fitness function such that changes are directly interpretable as fitness effects.
-    In this regard, an interesting prediction of our model is that back-mutations are beneficial because they revert previous deleterious changes.
-    We have tested this hypothesis and found that these back-mutations ($\SphyBen \coloneqq \Sphy > 1 $) are indeed beneficial in extant populations.
-    We estimated that between 11 and 82\% of all beneficial mutations in mammalian populations have not been driven by adaptation but instead have reversed deleterious substitutions which have accumulated along the phylogenetic tree.
-    More specifically, in 24 out of 28 populations analyzed, the percentage of beneficial mutations estimated to be back-mutations falls between 15 and 45\%.
-    These results suggest that many beneficial mutations are non-adaptive but rather restore ancestral states of higher fitness.
-    Hence, we can correctly estimate the extent of adaptive evolution only if we account for the number of beneficial back-mutations~\cite{keightley_what_2010, rice_evolutionarily_2015}.
+    However, contrary to SIFT scores, our mutation-selection model is parameterized by a fitness function such that changes are directly interpretable as fitness effects (see also section S7).
+    In this regard, an interesting prediction of our model is that some deleterious mutations reach fixation due to genetic drift, while beneficial non-adaptive mutations are restoring states of higher fitness.
+    We have tested this hypothesis and have found that a substantial part of these predicted non-adaptive mutations ($\SphyBen \coloneqq \Sphy > 1 $) are indeed beneficial in extant populations.
+    We estimate that between 11 and 82\% of all beneficial mutations in mammalian populations are not adaptive.
+    More specifically, in 24 out of 28 populations analyzed, the percentage of beneficial mutations estimated to be non-adaptive falls between 15 and 45\%.
+    These results suggest that many beneficial mutations are not adaptive, but rather restore states of higher fitness.
+    Hence, we can correctly estimate the extent of adaptive evolution only if we account for the number of beneficial non-adaptive mutations~\cite{keightley_what_2010, rice_evolutionarily_2015}.
     Altogether, we argue that we should dissociate positive selection from adaptive evolution and limit the use of adaptive mutations to those that are associated with adaptation to environmental change as such~\cite{charlesworth_other_2007, mustonen_fitness_2009}.
 
-    \subsection*{Interpreting the proportion of beneficial back-mutations}
+    \subsection*{The influence of effective population size}
 
-    Across the genome, beneficial-back mutations and deleterious mutations reaching fixation create a balance in which genomes are constantly damaged and restored simultaneously at different loci.
-    Since the probability of fixation of mutations depends on the effective population size ($\Ne$), the history of $\Ne$ plays a crucial role in setting the number of beneficial back-mutations compensating for deleterious mutations~\cite{latrille_inferring_2021}.
-    For example, a population size expansion will increase the efficacy of selection, and a larger proportion of mutations will be beneficial (otherwise effectively neutral), thus increasing the number of beneficial back-mutations.
-    On the other hand, a population that has experienced a high $\Ne$ throughout its history should be closer to an optimal state under a stable fitness landscape, having suffered fewer fixations of deleterious mutations and therefore decreasing the probability of beneficial back-mutations~\cite{huber_determining_2017}.
-    Overall, we expect the proportion of beneficial back-mutations to be more dependent on $\Ne$’s long-term expansions and contractions than on the short-term ones~\cite{charlesworth_other_2007,huber_determining_2017}.
-    Accounting for phylogenetic relationships, we found no correlation between the proportion of back-mutations and $\Ne$ ($r^2=0.00$, $p=0.772$, fig.~\ref{fig:diversity}B)
+    Across the genome, beneficial non-adaptive mutations and deleterious mutations reaching fixation create a balance in which genomes are constantly damaged and restored simultaneously at different loci due to drift.
+    Since the probability of fixation of mutations depends on the effective population size ($\Ne$), the history of $\Ne$ plays a crucial role in determining the number of beneficial non-adaptive mutations compensating for deleterious mutations~\cite{latrille_inferring_2021}.
+    For example, a population size expansion will increase the efficacy of selection, and a larger proportion of mutations will be beneficial (otherwise effectively neutral), thus increasing the number of beneficial non-adaptive mutations.
+    On the other hand, a population that has experienced a high $\Ne$ throughout its history should be closer to an optimal state under a stable fitness landscape, having suffered fewer fixations of deleterious mutations and therefore decreasing the probability of beneficial non-adaptive mutations~\cite{huber_determining_2017}.
+    Overall, we expect the proportion of beneficial non-adaptive mutations to be more dependent on $\Ne$’s long-term expansions and contractions than on the short-term ones~\cite{charlesworth_other_2007,huber_determining_2017}.
+    Accounting for phylogenetic relationships, we found no correlation between the proportion of beneficial non-adaptive mutations and estimates of $\Ne$ based on genetic diversity ($r^2=0.00$, $p=0.772$, fig.~\ref{fig:diversity}B).
 
-    The exact estimation of the contribution of beneficial back-mutations to positive selection relies on some hypotheses at both the phylogenetic and population scales and is sensitive to methodological limitations.
-    Indeed, to be conservative, we considered that any mutation under positive selection at the population scale ($\SpopBen$) but not predicted as such at the phylogenetic scale (not $\SphyBen$) is potentially an adaptation.
-    However, adaptation is not the only factor hindering the detection of beneficial back-mutations; data quality and potentially inadequate modeling choices of both the fitness landscape and the DFE might also lead to missed predictions.
+    Moreover, because our model assumes a fixed fitness landscape, it implicitly assumes that $\Ne$ is constant along the phylogenetic tree.
+    Fluctuations due to changes in the fitness landscape or in $\Ne$ will be averaged out by the assumption of the current model that $\Ne$ is constant across lineages.
+    It was recently shown~\cite{latrille_inferring_2021}, using computer intensive mutation-selection models with fluctuating $\Ne$, that relaxing the assumption of a constant $\Ne$ results in more extreme estimates of amino-acid fitnesses than with the standard model used in this study.
+    In other words, by assuming a constant $\Ne$, we are underpowered to detect beneficial non-adaptive mutations since amino acids will have more similar fitnesses.
+    As a consequence, some of the beneficial non-adaptive mutations currently segregating in population will be incorrectly classified as nearly-neutral by the mutation-selection model, and thus be wrongly interpreted as adaptive.
+    This ultimately results in lower estimates of the proportion of beneficial non-adaptive mutations.
+    Given this inflation of missed predictions due to change in population sizes~\cite{lanfear_population_2014, jones_shifting_2017, platt_protein_2018}, our estimated proportion of beneficial non-adaptive mutations among adaptive ones is likely to be an underestimation.
+
+    \subsection*{The role of epistasis and compensatory mutations}
 
@@
     Particularly, the residues in contact co-evolve to become more compatible with each other generating an entrenchment~\cite{goldstein_nonadaptive_2015, goldstein_sequence_2017, park_epistatic_2022}.
-    Epistasis therefore allows for compensatory mutations, which restore fitness through mutations at loci different from where deleterious mutations took place.
-    It therefore, represents another case case of non-adaptive beneficial mutations, but one which is not accounted for by our method.
-    Therefore, the beneficial mutations that we classify as putatively adaptive might in fact be compensatory mutations, making our estimation of the rate of non-adaptive beneficial mutations conservative.
+    Epistasis therefore allows for compensatory mutations, which restore fitness through mutations at loci different from where deleterious mutations took place, representing another case of non-adaptive beneficial mutations, but one which is not accounted for by our method.
+    Hence, the beneficial mutations that we classify as putatively adaptive might in fact be compensatory mutations, making our estimation of the rate of non-adaptive beneficial mutations conservative.
 
-    Despite epistasis being an important factor in protein evolution, several deep mutational scanning laboratory experiments have revealed that a site-specific fitness landscape is a reasonable approximation of the fitness landscape of proteins, and even predicts the evolution of sequences in nature~\cite{ashenberg_mutational_2013, doud_sitespecific_2015, bloom_identification_2017}.
-    Additionally, the fact that we observe such a high proportion of beneficial back-mutations suggests that the underlying assumptions of our model, namely site-independence, implying no epistasis, and a static fitness landscape, are a reasonable approximation for the underlying fitness landscape of proteins.
+    Despite epistasis being an important factor in protein evolution, several deep-mutational scanning experiments have revealed that a site-specific fitness landscape predicts the evolution of sequences in nature with considerable accuracy~\cite{ashenberg_mutational_2013, doud_sitespecific_2015, bloom_identification_2017}.
+    Additionally, the fact that we observe such a high proportion of beneficial non-adaptive mutations suggests that the underlying assumptions of our model, namely site-independence, implying no epistasis, and a static fitness landscape, are a reasonable approximation for the underlying fitness landscape of proteins.
     Our results imply that the fitness effects of new mutations are mostly conserved across mammalian orthologs, in agreement with other studies showing that for conserved orthologs with similar structures and functions, models without epistasis provide a reasonable estimate of fitness effects in protein coding genes~\cite{youssef_consequences_2020, vigue_deciphering_2022}.
 
-    Moreover, because our model assumes a fixed landscape, it implicitly assumes that $\Ne$ is constant along the phylogenetic tree.
-    Fluctuations due to changes in the fitness landscape or in $\Ne$ will be averaged out by the assumption of the current model that $\Ne$ is constant across lineages.
-    It was recently shown~\cite{latrille_inferring_2021}, using highly computer intensive mutation-selection models with fluctuating $\Ne$, that relaxing the assumption of a constant $\Ne$ results in more extreme estimates of amino-acid fitnesses than with the standard model used in this study.
-    In other words, by assuming a constant $\Ne$, we are underpowered to detect beneficial back-mutations since amino acids will have more similar fitnesses.
-    As a consequence, mutations that would otherwise fall into $\SpopBen$ or $\SpopDel$ will be classified as $\SpopNeu$, resulting ultimately in lower estimates of the proportion of beneficial back-mutations ($\proba [ \SphyBen  \given  \SpopBen]$).
-    Given this inflation of missed predictions due to change in population sizes~\cite{lanfear_population_2014, jones_shifting_2017, platt_protein_2018}, our estimated proportion of beneficial back-mutations among adaptive ones is likely to therefore be an underestimation.
-    In practice, advantageous mutations can be depleted in the $\SphyNeu$ and $\SphyDel$ class in some species but pervasive in others, depending on the model used to infer the DFE at the population scale (tables~S8-12).
-    It appears that our estimation can be quite sensitive to model misspecification and overall, while we provide an order of magnitude for the contribution of beneficial back-mutations to positive selection, further methodological development on the estimation of the distribution of fitness effects is needed to increase the confidence on this value.
+    \subsection*{Other assumptions and methodological limitations}
+
+    The exact estimation of the contribution of beneficial non-adaptive mutations to positive selection relies on some hypotheses at both the phylogenetic and population scales and is sensitive to methodological limitations.
+    Indeed, data quality and potentially inadequate modeling choices of both the fitness landscape (at the phylogenetic scale) and fitness effects (at the population scale) might also lead to missed prediction~\cite{moutinho_variation_2019}.
+    To be conservative, we considered that any mutation under positive selection at the population scale ($\SpopBen$) but not predicted as such at the phylogenetic scale (not $\SphyBen$) is potentially an adaptation.
+    In practice, we obtained different values of the proportion of non-adaptive beneficial mutations depending on the model used to infer the fitness effects at the population scale, and the filtering or not of CpG mutations~\cite{eyre-walker_how_2014} (tables~S8-14).
+    It appears that our estimation can be sensitive to model misspecification and overall, while we provide an order of magnitude for the contribution of beneficial non-adaptive mutations to positive selection, methodological improvement on the estimation of the distribution of fitness effects is needed to increase the precision of this value.
+
+    Importantly, if there are several substitutions toward the same amino acid along the mammalian tree, (see fig.~S3) our mutation-selection model cannot distinguish between a scenario where mammals have fixed deleterious mutations that are reverted in several lineages, from more complex scenarios involving adaptation.
+    In a first scenario, repeated changes of fitness landscapes in the same direction could occur along several lineages, leading to repeated substitutions in multiple lineages (parallel or convergent adaptation).
+    Of note, repeated substitutions that we observe (section~S2) are spread across the phylogeny and are usually shared by distant species/clades with very different lifestyles and environments.
+    It is therefore unlikely that all the beneficial mutations that we classified as non-adaptive (between 15 and 45\%) would result from parallel adaptation.
+    In a second scenario, an environmental change that occurred near the root of placental mammals ($\sim$100 Mys ago), to which extant populations are currently responding through weakly adaptive mutations could also lead to repeated substitutions toward the same amino acids.
+    However, for this latter hypothesis to totally explain our results, it would imply that a large proportion of weakly adaptive mutations arising in present day populations of mammals are the late consequence of $\sim$100 Mys-old environmental changes.
+    While we cannot rule out that some cases of the latter scenarios are included in our results, we argue that the hypothesis of non-adaptive evolution on a fixed fitness landscape of functionally constrained proteins remains more parsimonious for most cases.
 
@@
 
-    A long-standing debate in molecular evolution is whether the variations we observe between species in protein-coding genes are primarily due to nearly-neutral mutations reaching fixation by drift or primarily due to adaptation~\cite{kimura_evolutionary_1968,jensen_importance_2019,gillespie_substitution_1994,Ohta1992}.
-    Here we provide evidence that in mammalian orthologs, many substitutions occur through fixation of both deleterious mutations and beneficial back-mutations.
-    However, detecting adaptation above this background of nearly-neutral substitutions remains a central question~\cite{kimura_evolutionary_1968,ohta_development_1996}.
+    A long-standing debate in molecular evolution is whether the variations we observe between species in protein-coding genes are primarily due to nearly-neutral mutations reaching fixation by drift or primarily due to adaptation~\cite{kimura_evolutionary_1968,jensen_importance_2019,gillespie_substitution_1994,ohta_nearly_1992}.
+    Here we provide evidence that in mammalian orthologs, many substitutions occur through fixation of both deleterious mutations and beneficial non-adaptive mutations.
+    However, detecting adaptation above this background of nearly-neutral substitutions remains a challenge~\cite{kimura_evolutionary_1968,ohta_development_1996}.
 
@@
     Deviations from this neutral expectation, such as $\dnds > 1$, which can be generated by an excess of non-synonymous substitutions, is generally interpreted as a sign of adaptation.
-    However, as shown in this study, a $\dnds > 1$ is not necessarily a signature of adaptation but can be due to beneficial back-mutations.
+    However, as shown in this study, a $\dnds > 1$ is not necessarily a signature of adaptation but can be due to beneficial non-adaptive mutations.
     So, by relaxing the strict neutrality and assuming a stable fitness landscape instead, one can predict the expected rate of evolution, called $\omega_0$~\cite{spielman_relationship_2015, dosreis_how_2015}.
@@
 
-    Here, we have provided empirical evidence that an evolutionary model assuming a stable fitness landscape at the mammalian scale allows us to predict the fitness effects of mutations in extant populations and individuals, acknowledging the balance between deleterious and beneficial back-mutations.
-    We argue that such a model represents a null expectation for the evolution of protein-coding genes in the absence of adaptation.
+    \subsection*{Conclusions}
+
+    Here, we have provided empirical evidence that an evolutionary model assuming a stable fitness landscape at the mammalian scale allows us to predict the fitness effects of mutations in extant populations and individuals, acknowledging the balance between deleterious and beneficial non-adaptive mutations.
+    We argue that such a model would represent a null expectation for the evolution of protein-coding genes in the absence of adaptation.
+    Altogether, because a substantial part of positive selection can be explained by beneficial non-adaptive mutations, but not its entirety, we argue that the mammalian exome is shaped by both adaptive and non-adaptive processes, and that none of them alone is sufficient to explain the observed patterns of changes.
     In that sense, to avoid conflating beneficial mutations with adaptive evolution, the term ``adaptation`` should retain its original meaning associated with a change in the underlying fitness landscape and be modelled as such.
@@
     where $D \left( \Sphyclass \right) $ was the number of non-synonymous substitutions in class $\Sphyclass$, $D_{\text{syn}}$ was the number of synonymous substitutions across the exome, while $L \left( \Sphyclass \right)$ and $L_{\text{syn}}$ were the numbers of non-synonymous and synonymous mutational opportunities, respectively, as defined in section~\ref{subsec:nunber-of-sites}.
-    $\delta(\dnds)$ was computed as the difference between $\dnds$ computed over all substitutions and $\dnds$ when we removed beneficial back-mutations $\dn (\Sphy < 1) / \ds$, normalized by $\dnds$.
+    $\delta(\dnds)$ was computed as the difference between $\dnds$ computed over all substitutions and $\dnds$ when we removed beneficial non-adaptive mutations $\dn (\Sphy < 1) / \ds$, normalized by $\dnds$.
     Note that the quantities $\delta(\dnds)$ and $\delta(\dn)$ are equivalent due to the simplification of the factor $\ds$:
@@
 
-    \textit{Precision} is the proportion of mutations correctly predicted as beneficial ($\proba [ \SpopBen \cap  \SphyBen]$) out of all predicted as beneficial back-mutations ($\proba [ \SphyBen]$), which can be written as a conditional probability:
+    \textit{Precision} is the proportion of mutations correctly predicted as beneficial ($\proba [ \SpopBen \cap  \SphyBen]$) out of all predicted as beneficial non-adaptive mutations ($\proba [ \SphyBen]$), which can be written as a conditional probability:
 
@@
     \end{equation}
-    Namely, \textit{precision} corresponds to the probability for a back-mutation ($\SphyBen$) to be effectively beneficial at the population level ($\SpopBen$).
-    This probability, computed from eq.~\ref{eq:polyProbaAdv}, is obtained by restricting our analysis to SNPs that are predicted to be beneficial back-mutations (yellow fill for the category $\SphyBen$ in fig.~\ref{fig:homo-afr-results}D).
+    Namely, \textit{precision} corresponds to the probability for a $\SphyBen$ mutation to be effectively beneficial at the population level ($\SpopBen$).
+    This probability, computed from eq.~\ref{eq:polyProbaAdv}, is obtained by restricting our analysis to SNPs that are predicted to be beneficial non-adaptive mutations (yellow fill for the category $\SphyBen$ in fig.~\ref{fig:homo-afr-results}D).
 
@@
     \end{equation}
-    Namely, \textit{recall} corresponds to the probability for a beneficial mutation at the population level ($\SpopBen$) to be a beneficial back-mutation ($\SphyBen$).
+    Namely, \textit{recall} corresponds to the probability for a beneficial mutation at the population level ($\SpopBen$) to be a beneficial non-adaptive mutation ($\SphyBen$).
     Using Bayes theorem, \textit{recall} can be re-written as:
@@
     \section*{Data availability}
-    The data underlying this article are available at \url{https://doi.org/10.5281/zenodo.7878954}.
+    The data underlying this article are available at \url{https://doi.org/10.5281/zenodo.7878953}.
     Snakemake pipeline, analysis scripts and documentation are available at \href{https://github.com/ThibaultLatrille/SelCoeff}{github.com/ThibaultLatrille/SelCoeff}.
@@
             At the phylogenetic scale (C), beneficial substitutions are common (positive signs), promoting phenotype diversification across species.
-            Under a stable fitness landscape (B), most mutations reaching fixation are either slightly deleterious reaching fixation due to drift or are beneficial back-mutations restoring a more optimal amino acid.
-            At the phylogenetic scale (D), deleterious substitutions (negative signs) are often reverted via beneficial back-mutations (positive signs), promoting phenotype stability and preserving well-established biological systems.
-            Even though, individually, any back-mutation might have a small beneficial effect on its bearer, we expect beneficial back-mutations to be scattered across the genome and the genome-wide signature of beneficial back-mutations to be detectable and quantifiable.}
+            Under a stable fitness landscape (B), most mutations reaching fixation are either slightly deleterious reaching fixation due to drift or are beneficial non-adaptive mutations restoring a more optimal amino acid.
+            At the phylogenetic scale (D), deleterious substitutions (negative signs) are often reverted via beneficial non-adaptive mutations (positive signs), promoting phenotype stability and preserving well-established biological systems.
+            Even though, individually, any beneficial non-adaptive mutation might have a weak effect on its bearer, we expect them to be scattered across the genome and the genome-wide signature of beneficial non-adaptive mutations to be detectable and quantifiable.}
         \label{fig:fitness-landscape}
@@
             For every possible mutation, the difference in amino-acid fitness before and after the mutation allows us to compute the selection coefficient at the phylogenetic scale ($\Sphy$).
-            Depending on $\Sphy$ (B) mutations can be predicted as deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) or beneficial back-mutations ($\SphyBen$) toward a fitter amino acid and repairing existing functions.
+            Depending on $\Sphy$ (B) mutations can be predicted as deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) or beneficial non-adaptive mutations ($\SphyBen$) toward a fitter amino acid and repairing existing functions.
             At the population scale, each observed single nucleotide polymorphism (SNP) segregating in the population can also be classified according to its $\Sphy$ value (C).
@@
             We can thus assess whether $\Sphy$ predicts $\Spop$ and compute \textit{precision} (F) and \textit{recall} (G) for each class.
-            The \textit{recall} value for class $\SphyBen$ is the probability of back-mutations among all beneficial ones (G).
+            The \textit{recall} value for class $\SphyBen$ is the probability for beneficial mutations to be non-adaptive (G).
         }
@@
             (A) Distribution of scaled selection coefficients ($\Sphy$), predicted for all possible non-synonymous DNA mutations away from the ancestral human exome (section \ref{subsec:nunber-of-sites}).
-            Mutations are divided into three classes of selection: deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial ($\SphyBen$, supposedly beneficial back-mutations)
+            Mutations are divided into three classes of selection: deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial ($\SphyBen$, supposedly beneficial non-adaptive mutations)
             (B) Distribution of scaled selection coefficients ($\Sphy$) for all observed substitutions along the \textit{Homo} branch after the \textit{Homo}-\textit{Pan} split (section \ref{subsec:substitution-mapping-in-the-terminal-branch}).
@@
             (A) Proportion of nearly-neutral mutations at the population scale ($\proba [ \SpopNeu]$ in the y-axis), shown as a function of estimated effective population size ($\Ne$ in the x-axis).
-            (B) Proportion of beneficial back-mutations among all beneficial mutations ($\proba [ \SphyBen  \given  \SpopBen]$ in the y-axis), shown as a function of $\Ne$ in x-axis.
+            (B) Proportion of beneficial non-adaptive mutations among all beneficial mutations ($\proba [ \SphyBen  \given  \SpopBen]$ in the y-axis), shown as a function of $\Ne$ in x-axis.
             Correlations account for phylogenetic relationship and non-independence of samples, through the fit of a Phylogenetic Generalized Linear Model (see section~\ref{subsec:s-polymorphism-method} in Materials \& Methods).
@@
             Conversely, \textit{recall} is the estimation of $\Sphy$ given selection coefficient at the population scale ($\Spop$) is known.
-            \textit{Recall} for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is thus the proportion of beneficial back-mutations among all beneficial mutations.
+            \textit{Recall} for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is thus the proportion of beneficial non-adaptive mutations among all beneficial mutations.
             $\Ne$ is the estimated effective population size for each population.

### 2024-03-06 manuscript/supp-mat-revision-2.tex
Added figure titles in supp. mat.

@@
     This hierarchical model is formally represented as directed acyclic graph of dependencies between variables, depicted below.
-    Nodes of the directed acyclic graph are the variables, and edges are the functions.
-    Hyper-parameters are depicted in {\color{RED}{red}} circles, random variables in {\color{BLUE}{blue}} circles, and transformed variables in black.
-            {\color{BLUE}{Blue}} dashed line denotes a drawing from a random distribution, and black solid lines denote a function.
-    All the nodes pointing toward a given node (upstream) are its dependencies which determine its distribution.
-    The other way around, following the arrows in the DAG (downstream), simple {prior} distributions are combined together to form more complex joint {prior} distributions which ultimately define the {prior} distribution of the model.
-
-    \begin{center}
+
+    \begin{center}
+        \captionof{figure}{Bayesian hierarchical model.}
         \begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=0.6cm and 1.2cm,semithick]
@@
     \end{center}
+
+    Nodes of the directed acyclic graph are the variables, and edges are the functions.
+    Hyper-parameters are depicted in {\color{RED}{red}} circles, random variables in {\color{BLUE}{blue}} circles, and transformed variables in black.
+            {\color{BLUE}{Blue}} dashed line denotes a drawing from a random distribution, and black solid lines denote a function.
+    All the nodes pointing toward a given node (upstream) are its dependencies which determine its distribution.
+    The other way around, following the arrows in the DAG (downstream), simple {prior} distributions are combined together to form more complex joint {prior} distributions which ultimately define the {prior} distribution of the model.
 
@@
     Because a correlation must account for phylogenetic relationship and non-independence of samples, we fitted a Phylogenetic Generalized Linear Model (PGLM) in R with the package caper\cite{orme_caper_2013}, with multi-furcation of the different populations inside each species.
-    The mammalian tree imported from TimeTree\cite{kumar_timetree_2017} and pruned to the species used in this study.
+    The mammalian tree imported from TimeTree\cite{kumar_timetree_2017} and pruned to the species used in this study is, in newick format:
+
+    \lstinputlisting[breaklines]{artworks/PGLM.tree}
+
+    And shown in the figure below:
+    \begin{center}
+        \captionof{figure}{Tree used for PGLM (Phylogenetic Generalized Linear Model).}
+        \includegraphics[width=0.65\linewidth, page=1]{artworks/PGLM.pdf}
+    \end{center}
+
     Multifurcations of the different populations are placed at the same divergence time as the species.
-
-    \lstinputlisting[breaklines]{artworks/PGLM.tree}
-
-    \begin{center}
-        \includegraphics[width=0.65\linewidth, page=1]{artworks/PGLM.pdf}
-    \end{center}
-
     Then, for each population, the proportion of deleterious ($\ProbaPopDel$), nearly-neutral ($\ProbaPopNeu$) and of beneficial ($\ProbaPopBen$) mutations estimated at the population-genetic scale is shown as function of $\Ne$.
@@
 
+    \captionof{figure}{Distribution of scaled selection coefficients ($\Sphy$).}
     \begin{minipage}{0.32\linewidth}
@@
 
+    \small
     \begin{itemize}[itemsep=0pt]
@@
     \end{itemize}
+    \normalsize
 

### 2024-04-22 manuscript/main-biorxiv-2.tex
SNP ontology enrichment

--- 2024-03-06 manuscript/main-revision-2.tex
@@
 
-\title{Mammalian protein-coding genes exhibit widespread beneficial mutations that are not adaptive}
+\title{Estimating the proportion of beneficial mutations that are not adaptive in mammals}
 \rhead{\scshape Beneficial yet non-adaptive mutations}
@@
     Across our selection classes ($\SphyDel$, $\SphyNeu$ and $\SphyBen$), one can ultimately estimate the proportion of correct and incorrect predictions, leading to an estimation of \textit{precision} and \textit{recall} (fig.~\ref{fig:method}F-G and section~\ref{subsec:precisison_recall} in Materials \& Methods).
-    Across 28 populations of different mammal species, mutations predicted to be deleterious at the phylogenetic scale ($\ProbaPopDel$) were indeed purged at the population scale, with a \textit{precision} in the range of 90--97\% (table~\ref{table:proba} and fig.~\ref{fig:homo-afr-results}D for humans).
+    Across 28 populations of different mammal species, mutations predicted to be deleterious at the phylogenetic scale ($\SphyDel$) were indeed purged at the population scale, with a \textit{precision} in the range of 90--97\% (table~\ref{table:proba} and fig.~\ref{fig:homo-afr-results}D for humans).
     Conversely, a \textit{recall} in the range of 96--100\% implied that mutations found to be deleterious at the population scale were most likely also predicted to be deleterious at the phylogenetic scale (table~\ref{table:proba}).

### 2024-04-22 manuscript/main-biorxiv.tex
SNP ontology enrichment

--- 2023-05-03 manuscript/main.tex
@@
 % The submission checklist is available at:
-% https://docs.google.com/document/d/1aHCF1on0mHTK2DoroPCLP_xto4xwHnGJCGwaL1Vm2UE/edit?usp=sharing
+% https://docs.google.com/document/d/1SScaqEAgZGpeaXxpWPDh1NOLaDDLLmkGOYgaGvbY-4o/edit#
 
@@
     Having originated $\sim$102 million years ago, they diversified quickly~\cite{foley_genomic_2023}.
-    Additionally, polymorphism data are available for many species~\cite{howe_ensembl_2021}, as are high quality protein-coding DNA alignments across the genome~\cite{ranwez_orthomam_2007, scornavacca_orthomam_2019}.
+    Additionally, polymorphism data are available for many species~\cite{howe_ensembl_2021}, as are high quality protein-coding DNA alignments across the genome~\cite{ranwez_orthomam_2007, scornavacca_orthomam_2019}.Mutations can be beneficial by bringing innovation to their bearer, allowing them to adapt to environmental change.
+        However, mutations can also be beneficial because they are reverting previous deleterious changes, simply restoring pre-existing functions.
+        By integrating phylogenomic and population data in mammals, we estimated the contribution of beneficial back-mutations to molecular evolution, which had remained widely overlooked so far.
+        Applying a mutation-selection model, we estimated amino acid fitness landscapes for mammalian protein-coding genes.
+        Assuming these fitness landscapes do not change, any beneficial mutation is necessarily a back-mutation.
+        We confirmed that these beneficial back-mutations are positively selected in extant populations and demonstrated that a substantial part of ongoing positive selection is not driven by adaptation to environmental change.
     By performing our analysis on 14,509 orthologous protein-coding genes across 87 species, we focus on sequences under functional constraints across mammals.

### 2024-04-22 manuscript/supp-mat-biorxiv-2.tex
SNP ontology enrichment

--- 2024-03-06 manuscript/supp-mat-revision-2.tex
@@
         \catMultiVar \sim \text{Multinomial}\left( \StickBreaking \right), \\
-        \text{ where } \catmultivar_{\cat} = \sum_{\Setsite} \mathbbm{1}_{\catsite = \cat}
+        \text{ where } \catmultivar_{\cat} = \sum_{\Setsite} \mathbb{1}_{\catsite = \cat}
     \end{align}
@@
     \newpage
-
+    \section{Gene ontology enrichment}
+
+    For each gene, we computed the proportion of $\SphyBen$ sites.
+    For each ontology, the proportion of sites under adaptation is compared between the set of genes sharing this given ontology and the rest of the genes with Mann-Whitney U test.
+    $p_{\mathrm{v}}^{\mathrm{adj}}$ are corrected for multiple comparison (Holm–Bonferroni correction).
+    $^*$ for $p_{\mathrm{v}}^{\mathrm{adj}}$ corrected for multiple comparison (Holm–Bonferroni correction) lower than the risk $\alpha=0.05$.
+
+    \begin{center}
+        \captionof{table}{Ontology enrichment}
+        \scriptsize
+        \begin{longtable*}{|l|r|r|r|r|r|r|}
+            \toprule
+            Gene ontology & p(go) & r(go/no go) & Mann-Whitney U & $p_{\mathrm{v}}$ & $p_{\mathrm{v}}^{\mathrm{adj}}$ \\
+            \midrule
+            \endhead
+            \midrule
+            \multicolumn{6}{r}{Continued on next page} \\
+            \midrule
+            \endfoot
+            \bottomrule
+            \endlastfoot
+            proteinaceous extracellul... & $ 0.069$ & $ 1.679$ & $2.4\times 10^{5}$ & $0.00042$ & $ 0.118~~$ \\
+            extracellular region & $ 0.178$ & $ 1.518$ & $ 8\times 10^{5}$ & $ 0.002$ & $ 0.599~~$ \\
+            extracellular matrix orga... & $ 0.039$ & $ 2.102$ & $1.3\times 10^{5}$ & $ 0.003$ & $ 0.746~~$ \\
+            receptor-mediated endocyt... & $ 0.027$ & $ 1.253$ & $8.1\times 10^{4}$ & $ 0.006$ & $ 1.000~~$ \\
+            regulation of transcripti... & $ 0.069$ & $ 0.482$ & $7.1\times 10^{5}$ & $ 0.008$ & $ 1.000~~$ \\
+            cytosol & $ 0.212$ & $ 0.714$ & $1.4\times 10^{6}$ & $ 0.013$ & $ 1.000~~$ \\
+            nucleoplasm & $ 0.124$ & $ 0.505$ & $ 1\times 10^{6}$ & $ 0.014$ & $ 1.000~~$ \\
+            transcription from RNA po... & $ 0.008$ & $ 0.106$ & $2.3\times 10^{5}$ & $ 0.015$ & $ 1.000~~$ \\
+            microtubule-based movemen... & $ 0.023$ & $ 1.054$ & $7.2\times 10^{4}$ & $ 0.016$ & $ 1.000~~$ \\
+            nucleus & $ 0.266$ & $ 0.713$ & $1.5\times 10^{6}$ & $ 0.020$ & $ 1.000~~$ \\
+            ATPase activity & $ 0.031$ & $ 0.924$ & $9.3\times 10^{4}$ & $ 0.025$ & $ 1.000~~$ \\
+            mitochondrion & $ 0.058$ & $ 0.517$ & $5.5\times 10^{5}$ & $ 0.029$ & $ 1.000~~$ \\
+            transcription & $ 0.073$ & $ 0.544$ & $6.8\times 10^{5}$ & $ 0.030$ & $ 1.000~~$ \\
+            cytoplasm & $ 0.317$ & $ 0.708$ & $1.6\times 10^{6}$ & $ 0.032$ & $ 1.000~~$ \\
+            Golgi membrane & $ 0.012$ & $ 0.102$ & $2.4\times 10^{5}$ & $ 0.033$ & $ 1.000~~$ \\
+            RNA polymerase II transcr... & $ 0.027$ & $ 0.460$ & $3.4\times 10^{5}$ & $ 0.046$ & $ 1.000~~$ \\
+            cell adhesion & $ 0.062$ & $ 1.220$ & $2.9\times 10^{5}$ & $ 0.054$ & $ 1.000~~$ \\
+            actin filament binding & $ 0.019$ & $ 0.897$ & $6.7\times 10^{4}$ & $ 0.060$ & $ 1.000~~$ \\
+            dendrite & $ 0.008$ & $ 0.112$ & $1.7\times 10^{5}$ & $ 0.067$ & $ 1.000~~$ \\
+            regulation of signal tran... & $ 0.019$ & $ 1.402$ & $ 7\times 10^{4}$ & $ 0.069$ & $ 1.000~~$ \\
+            sequence-specific DNA bin... & $ 0.015$ & $ 0.286$ & $2.1\times 10^{5}$ & $ 0.072$ & $ 1.000~~$ \\
+            spermatogenesis & $ 0.039$ & $ 1.633$ & $1.6\times 10^{5}$ & $ 0.081$ & $ 1.000~~$ \\
+            cell surface receptor sig... & $ 0.031$ & $ 2.126$ & $1.3\times 10^{5}$ & $ 0.086$ & $ 1.000~~$ \\
+            regulation of receptor ac... & $ 0.027$ & $ 3.275$ & $1.2\times 10^{5}$ & $ 0.088$ & $ 1.000~~$ \\
+            Golgi apparatus & $ 0.046$ & $ 0.477$ & $4.8\times 10^{5}$ & $ 0.094$ & $ 1.000~~$ \\
+            receptor complex & $ 0.023$ & $ 1.407$ & $9.4\times 10^{4}$ & $ 0.108$ & $ 1.000~~$ \\
+            positive regulation of tr... & $ 0.039$ & $ 0.435$ & $4.1\times 10^{5}$ & $ 0.111$ & $ 1.000~~$ \\
+            viral process & $ 0.008$ & $ 0.844$ & $1.5\times 10^{5}$ & $ 0.114$ & $ 1.000~~$ \\
+            mRNA processing & $ 0.004$ & $ 0.061$ & $1.1\times 10^{5}$ & $ 0.118$ & $ 1.000~~$ \\
+            endocytosis & $ 0.023$ & $ 1.602$ & $9.8\times 10^{4}$ & $ 0.123$ & $ 1.000~~$ \\
+            transferase activity & $ 0.004$ & $ 0.089$ & $ 1\times 10^{5}$ & $ 0.125$ & $ 1.000~~$ \\
+            negative regulation of ce... & $ 0.015$ & $ 3.268$ & $6.2\times 10^{4}$ & $ 0.125$ & $ 1.000~~$ \\
+            positive regulation of GT... & $ 0.035$ & $ 2.351$ & $1.7\times 10^{5}$ & $ 0.127$ & $ 1.000~~$ \\
+            oxidation-reduction proce... & $ 0.019$ & $ 0.754$ & $2.6\times 10^{5}$ & $ 0.128$ & $ 1.000~~$ \\
+            post-translational protei... & $ 0.008$ & $ 0.299$ & $1.4\times 10^{5}$ & $ 0.130$ & $ 1.000~~$ \\
+            mitochondrial inner membr... & $ 0.008$ & $ 0.661$ & $1.5\times 10^{5}$ & $ 0.130$ & $ 1.000~~$ \\
+            protein C-terminus bindin... & $ 0.004$ & $ 0.021$ & $ 1\times 10^{5}$ & $ 0.134$ & $ 1.000~~$ \\
+            transcription factor bind... & $ 0.004$ & $ 0.159$ & $ 1\times 10^{5}$ & $ 0.135$ & $ 1.000~~$ \\
+            cytoskeleton organization & $ 0.019$ & $ 1.607$ & $7.9\times 10^{4}$ & $ 0.137$ & $ 1.000~~$ \\
+            cell migration & $ 0.004$ & $ 0.110$ & $9.9\times 10^{4}$ & $ 0.143$ & $ 1.000~~$ \\
+            extracellular space & $ 0.100$ & $ 1.295$ & $5.4\times 10^{5}$ & $ 0.144$ & $ 1.000~~$ \\
+            extracellular exosome & $ 0.104$ & $ 0.694$ & $8.4\times 10^{5}$ & $ 0.145$ & $ 1.000~~$ \\
+            apoptotic process & $ 0.015$ & $ 0.660$ & $2.2\times 10^{5}$ & $ 0.145$ & $ 1.000~~$ \\
+            cell junction & $ 0.031$ & $ 0.314$ & $3.4\times 10^{5}$ & $ 0.152$ & $ 1.000~~$ \\
+            DNA binding & $ 0.077$ & $ 0.705$ & $6.5\times 10^{5}$ & $ 0.155$ & $ 1.000~~$ \\
+            postsynaptic density & $ 0.004$ & $ 0.223$ & $9.7\times 10^{4}$ & $ 0.157$ & $ 1.000~~$ \\
+            hydrolase activity & $ 0.081$ & $ 0.526$ & $6.7\times 10^{5}$ & $ 0.157$ & $ 1.000~~$ \\
+            transcription regulatory ... & $ 0.004$ & $ 0.228$ & $9.5\times 10^{4}$ & $ 0.163$ & $ 1.000~~$ \\
+            DNA binding transcription... & $ 0.027$ & $ 0.436$ & $3.1\times 10^{5}$ & $ 0.164$ & $ 1.000~~$ \\
+            signal transducer activit... & $ 0.027$ & $ 0.371$ & $ 3\times 10^{5}$ & $ 0.167$ & $ 1.000~~$ \\
+            aging & $ 0.015$ & $ 2.107$ & $6.3\times 10^{4}$ & $ 0.169$ & $ 1.000~~$ \\
+            transcription coactivator... & $ 0.004$ & $ 0.687$ & $9.6\times 10^{4}$ & $ 0.172$ & $ 1.000~~$ \\
+            synapse & $ 0.019$ & $ 0.255$ & $2.3\times 10^{5}$ & $ 0.172$ & $ 1.000~~$ \\
+            positive regulation of ER... & $ 0.019$ & $ 2.201$ & $8.4\times 10^{4}$ & $ 0.172$ & $ 1.000~~$ \\
+            sensory perception of sou... & $ 0.015$ & $ 1.737$ & $6.3\times 10^{4}$ & $ 0.182$ & $ 1.000~~$ \\
+            metalloendopeptidase acti... & $ 0.019$ & $ 0.600$ & $ 8\times 10^{4}$ & $ 0.183$ & $ 1.000~~$ \\
+            response to drug & $ 0.004$ & $ 0.082$ & $8.8\times 10^{4}$ & $ 0.183$ & $ 1.000~~$ \\
+            skeletal system developme... & $ 0.015$ & $ 1.590$ & $6.5\times 10^{4}$ & $ 0.189$ & $ 1.000~~$ \\
+            mitochondrial matrix & $ 0.008$ & $ 0.421$ & $1.3\times 10^{5}$ & $ 0.193$ & $ 1.000~~$ \\
+            immune system process & $ 0.012$ & $ 0.299$ & $1.6\times 10^{5}$ & $ 0.194$ & $ 1.000~~$ \\
+            cell-matrix adhesion & $ 0.015$ & $ 0.999$ & $6.3\times 10^{4}$ & $ 0.198$ & $ 1.000~~$ \\
+            receptor binding & $ 0.031$ & $ 2.044$ & $1.5\times 10^{5}$ & $ 0.201$ & $ 1.000~~$ \\
+            ion transmembrane transpo... & $ 0.008$ & $ 0.363$ & $1.3\times 10^{5}$ & $ 0.204$ & $ 1.000~~$ \\
+            nervous system developmen... & $ 0.015$ & $ 0.401$ & $ 2\times 10^{5}$ & $ 0.205$ & $ 1.000~~$ \\
+            oxidoreductase activity & $ 0.019$ & $ 0.843$ & $2.3\times 10^{5}$ & $ 0.210$ & $ 1.000~~$ \\
+            innate immune response & $ 0.012$ & $ 0.243$ & $1.6\times 10^{5}$ & $ 0.218$ & $ 1.000~~$ \\
+            RNA polymerase II proxima... & $ 0.012$ & $ 0.595$ & $1.6\times 10^{5}$ & $ 0.219$ & $ 1.000~~$ \\
+            positive regulation of ce... & $ 0.004$ & $ 0.117$ & $ 8\times 10^{4}$ & $ 0.230$ & $ 1.000~~$ \\
+            protein binding & $ 0.587$ & $ 0.735$ & $1.7\times 10^{6}$ & $ 0.244$ & $ 1.000~~$ \\
+            binding & $ 0.046$ & $ 0.648$ & $ 2\times 10^{5}$ & $ 0.248$ & $ 1.000~~$ \\
+            DNA replication & $ 0.019$ & $ 1.388$ & $8.9\times 10^{4}$ & $ 0.248$ & $ 1.000~~$ \\
+            RNA splicing & $ 0.008$ & $ 0.095$ & $7.6\times 10^{4}$ & $ 0.250$ & $ 1.000~~$ \\
+            transcription factor comp... & $ 0.004$ & $ 0.280$ & $7.8\times 10^{4}$ & $ 0.253$ & $ 1.000~~$ \\
+            transmembrane transport & $ 0.054$ & $ 1.414$ & $2.8\times 10^{5}$ & $ 0.255$ & $ 1.000~~$ \\
+            neuronal cell body & $ 0.012$ & $ 0.386$ & $1.5\times 10^{5}$ & $ 0.255$ & $ 1.000~~$ \\
+            regulation of cell shape & $ 0.015$ & $ 1.945$ & $ 7\times 10^{4}$ & $ 0.256$ & $ 1.000~~$ \\
+            external side of plasma m... & $ 0.004$ & $ 0.042$ & $7.5\times 10^{4}$ & $ 0.259$ & $ 1.000~~$ \\
+            endomembrane system & $ 0.015$ & $ 3.003$ & $7.4\times 10^{4}$ & $ 0.264$ & $ 1.000~~$ \\
+            protein folding & $ 0.015$ & $ 1.691$ & $7.2\times 10^{4}$ & $ 0.267$ & $ 1.000~~$ \\
+            protein polyubiquitinatio... & $ 0.004$ & $ 0.431$ & $7.7\times 10^{4}$ & $ 0.271$ & $ 1.000~~$ \\
+            inflammatory response & $ 0.027$ & $ 1.745$ & $1.4\times 10^{5}$ & $ 0.273$ & $ 1.000~~$ \\
+            protein heterodimerizatio... & $ 0.035$ & $ 1.731$ & $1.9\times 10^{5}$ & $ 0.283$ & $ 1.000~~$ \\
+            membrane raft & $ 0.008$ & $ 0.207$ & $1.1\times 10^{5}$ & $ 0.285$ & $ 1.000~~$ \\
+            transcriptional activator... & $ 0.008$ & $ 0.242$ & $1.1\times 10^{5}$ & $ 0.290$ & $ 1.000~~$ \\
+            perinuclear region of cyt... & $ 0.027$ & $ 0.611$ & $2.5\times 10^{5}$ & $ 0.291$ & $ 1.000~~$ \\
+            regulation of cell prolif... & $ 0.019$ & $ 1.644$ & $9.4\times 10^{4}$ & $ 0.291$ & $ 1.000~~$ \\
+            sodium ion transport & $ 0.004$ & $ 0.185$ & $7.1\times 10^{4}$ & $ 0.294$ & $ 1.000~~$ \\
+            negative regulation of ce... & $ 0.015$ & $ 0.395$ & $1.8\times 10^{5}$ & $ 0.304$ & $ 1.000~~$ \\
+            macromolecular complex bi... & $ 0.004$ & $ 0.190$ & $ 7\times 10^{4}$ & $ 0.307$ & $ 1.000~~$ \\
+            positive regulation of tr... & $ 0.023$ & $ 0.782$ & $2.4\times 10^{5}$ & $ 0.315$ & $ 1.000~~$ \\
+            cilium & $ 0.023$ & $ 0.956$ & $1.2\times 10^{5}$ & $ 0.315$ & $ 1.000~~$ \\
+            signal transduction & $ 0.089$ & $ 0.724$ & $ 7\times 10^{5}$ & $ 0.317$ & $ 1.000~~$ \\
+            lipid metabolic process & $ 0.046$ & $ 1.542$ & $2.4\times 10^{5}$ & $ 0.321$ & $ 1.000~~$ \\
+            cell-cell signaling & $ 0.004$ & $ 0.475$ & $ 7\times 10^{4}$ & $ 0.325$ & $ 1.000~~$ \\
+            protein homooligomerizati... & $ 0.004$ & $ 0.475$ & $ 7\times 10^{4}$ & $ 0.325$ & $ 1.000~~$ \\
+            integrin binding & $ 0.004$ & $ 0.143$ & $6.6\times 10^{4}$ & $ 0.331$ & $ 1.000~~$ \\
+            actin binding & $ 0.027$ & $ 0.693$ & $1.4\times 10^{5}$ & $ 0.344$ & $ 1.000~~$ \\
+            symporter activity & $ 0.004$ & $ 0.334$ & $6.6\times 10^{4}$ & $ 0.348$ & $ 1.000~~$ \\
+            DNA repair & $ 0.015$ & $ 0.277$ & $1.7\times 10^{5}$ & $ 0.351$ & $ 1.000~~$ \\
+            cell differentiation & $ 0.066$ & $ 0.834$ & $3.5\times 10^{5}$ & $ 0.358$ & $ 1.000~~$ \\
+        \end{longtable*}
+    \end{center}
+
+    \newpage
     \section{Clinically related terms for mutations}
+
     \subsection{Terms associated with deleterious mutations $\SphyDel$}

### 2024-04-22 scripts/SNP_ontology.py

@@ -1,0 +1,178 @@
+import os
+import argparse
+from collections import defaultdict
+import numpy as np
+import pandas as pd
+import scipy.stats as st
+from libraries import CategorySNP, merge_mask_list, open_fasta, clean_ensg_path
+from table_ontology import ontology_table
+from SNP_effect import adjusted_holm_pval, format_pval_df, tex_f
+from write_variations import masked_sub, cat_sub
+import matplotlib.pyplot as plt
+
+# LaTeX preamble
+
+
+preamble_list = [r'\documentclass{article}', r'\usepackage{lmodern}', r'\usepackage[export]{adjustbox}',
+                 r'\usepackage{tabu}', r'\tabulinesep=0.6mm', r'\newcommand\cellwidth{\TX@col@width}',
+                 r'\usepackage{hhline}', r'\setlength{\arrayrulewidth}{1.2pt}', r'\usepackage{multicol,multirow,array}',
+                 r'\usepackage{etoolbox}', r'\usepackage{bm}', r'\AtBeginEnvironment{tabu}{\footnotesize}',
+                 r'\usepackage{booktabs}', r'\usepackage[margin=40pt]{geometry}', r'\usepackage{longtable}']
+
+
+def n_sites_ensg(fasta_folder, mask_grouped):
+    dico_n_sites = {}
+    for file in os.listdir(fasta_folder):
+        if file.endswith(".fasta") and file.startswith("ENSG"):
+            fasta = open_fasta(clean_ensg_path(os.path.join(fasta_folder, file)))
+            ensg = file[:-9]
+            if ensg.endswith("_"):
+                ensg = ensg + "null"
+            n_sites = len(fasta[list(fasta.keys())[0]]) // 3
+            if ensg in mask_grouped:
+                n_sites -= len(mask_grouped[ensg])
+            dico_n_sites[ensg] = n_sites
+    return dico_n_sites
+
+
+def open_df(input_path, mask_list, bins, windows, bounds):
+    cat_snps = CategorySNP("MutSel", bounds, bins=bins, windows=windows)
+    mask_grouped = merge_mask_list(mask_list)
+    df = pd.read_csv(input_path, sep='\t')
+    df["MASKED"] = df.apply(lambda row: masked_sub(row, mask_grouped), axis=1)
+    n_masked = len(df[df.MASKED])
+    print(f"Number of masked sites: {n_masked} out of {len(df)} ({n_masked / len(df) * 100:.2f}%)")
[…]

### 2024-06-19 manuscript/main-biorxiv-2.tex
Prepare for PLOS G. revisions

@@
 
+    First, $\SphyBen$ SNPs are spread across the genomes and not strongly associated to the ontology terms of their respective genes (table~S4, fig.~S4).
     In humans, some SNPs have been associated with specific clinical prognosis terms obtained by clinical evaluation of the impact of variants on human Mendelian disorders~\cite{landrum_clinvar_2018}.
@@
     Therefore, we investigated whether the non-synonymous SNPs classified as $\SphyDel$ or $\SphyBen$ showed enrichment in specific clinical terms compared to SNPs classified as $\SphyNeu$.
-    Our results show that SNPs predicted as deleterious are associated with clinical terms such as \textit{Likely Pathogenic} and \textit{Pathogenic}, implying that, in general, the selective pressure of a mutation exerted across mammals is also predictive of its clinical effect in humans (table~S4)~\cite{sullivan_leveraging_2023}.
-    Conversely, $\SphyBen$ mutations are associated with clinical terms such as \textit{Benign} and \textit{Likely Benign}, which shows that $\SphyBen$ mutations are less likely to be functionally damaging (table~S5).
+    Our results show that SNPs predicted as deleterious are associated with clinical terms such as \textit{Likely Pathogenic} and \textit{Pathogenic}, implying that, in general, the selective pressure of a mutation exerted across mammals is also predictive of its clinical effect in humans (table~S5)~\cite{sullivan_leveraging_2023}.
+    Conversely, $\SphyBen$ mutations are associated with clinical terms such as \textit{Benign} and \textit{Likely Benign}, which shows that $\SphyBen$ mutations are less likely to be functionally damaging (table~S6).
 
@@
     This result confirms that selection toward amino acids restoring existing functions is ongoing in these populations.
-    Importantly, the \textit{recall} value in this case, computed as $\proba [ \SphyBen  \given  \SpopBen]$, is the probability for a beneficial mutation at the population scale to be a non-adaptive, i.e., going toward a  fitter amino acid given a stable fitness landscape (fig.~\ref{fig:method}G, table~S6).
+    Importantly, the \textit{recall} value in this case, computed as $\proba [ \SphyBen  \given  \SpopBen]$, is the probability for a beneficial mutation at the population scale to be a non-adaptive, i.e., going toward a  fitter amino acid given a stable fitness landscape (fig.~\ref{fig:method}G, table~S7).
     In other words, the \textit{recall} value quantifies the number of beneficial mutations restoring damaged genomes instead of creating adaptive innovations.
@@
     Additionally, we controlled that these estimations are not affected by SNP mispolarization (figs.~S6-S7).
-    Moreover, because the phylogenetic mutation-selection codon model should fit better for genes with uniformly conserved functions, as a control, we filtered out genes under pervasive adaptation~\cite{latrille_genes_2023}, and indeed we found an increase in the proportion of beneficial mutations that are non-adaptive ($\proba [ \SphyBen  \given  \SpopBen]$), consistent with our expectation (Wilcoxon signed-rank, $s=80$, $p=0.002$, table~S7).
+    Moreover, because the phylogenetic mutation-selection codon model should fit better for genes with uniformly conserved functions, as a control, we filtered out genes under pervasive adaptation~\cite{latrille_genes_2023}, and indeed we found an increase in the proportion of beneficial mutations that are non-adaptive ($\proba [ \SphyBen  \given  \SpopBen]$), consistent with our expectation (Wilcoxon signed-rank, $s=80$, $p=0.002$, table~S8).
 

### 2024-06-19 manuscript/supp-mat.tex
Prepare for PLOS G. revisions

@@
 \newcommand{\thetaSyn}{\theta_{\text{S}}}
-
-\title{\textbf{Mammalian protein-coding genes exhibit widespread beneficial mutations that are not adaptive}}
+\newcommand{\pvalue}{p\text{-value}}
+
+% Model
+\newcommand{\submatrix}{q}
+\newcommand{\Submatrix}{\BiDimArray{\submatrix}}
+\newcommand{\probmatrix}{P}
+\newcommand{\Probmatrix}{\BiDimArray{\probmatrix}}
+\newcommand{\fit}{F}
+\newcommand{\Fit}{\UniDimArray{\fit}}
+\newcommand{\indice}{l}
+\newcommand{\indiceexp}{^{(\indice)}}
+\newcommand{\ci}{{a}}
+\newcommand{\cj}{{b}}
+\newcommand{\itoj}{\ci \mapsto \cj}
+\newcommand{\nuc}{\mathcal{M}}
+\newcommand{\fiti}{\fit_{\ci}}
+\newcommand{\fitj}{\fit_{\cj}}
+\newcommand{\mutmatrix}{R}
+\newcommand{\Mutmatrix}{\BiDimArray{\mutmatrix}}
+\newcommand{\exchan}{\rho}
+\newcommand{\Exchan}{\UniDimArray{\exchan}}
+\newcommand{\mutequi}{\sigma}
+\newcommand{\Mutequi}{\UniDimArray{\mutequi}}
+\newcommand{\Tree}{\mathcal{T}}
+\newcommand{\branch}{\text{j}}
+\newcommand{\branchexp}{^{(\branch)}}
+\newcommand{\branchlength}{l}
+% Alignment
+\newcommand{\data}{D}
+\newcommand{\Data}{\BiDimArray{\data}}
+\newcommand{\site}{\text{i}}
+\newcommand{\Nsite}{\text{N}}
+\newcommand{\siteexp}{^{(\site)}}
+\newcommand{\Setsite}{\site \in \{1, \hdots, \Nsite\} }
+\newcommand{\branchsiteexp}{^{(\branch, \site)}}
+% Categories
+\newcommand{\cat}{\text{k}}
+\newcommand{\Ncat}{\text{K}}
+\newcommand{\catexp}{^{(\cat)}}
+\newcommand{\catInterval}{\{1, \hdots, \Ncat\}}
+\newcommand{\Setcat}{\cat \in \catInterval }
+\newcommand{\branchcatexp}{^{(\branch, \cat)}}
+\newcommand{\profile}{\phi}
+\newcommand{\Profile}{\UniDimArray{\profile}}
+\newcommand{\concentrationProfile}{\alpha}
+\newcommand{\centerProfile}{\UniDimArray{\gamma}}
+\newcommand{\catVar}{\kappa}
+\newcommand{\catsite}{\catVar\left(\site\right)}
+\newcommand{\catmultivar}{m}
+\newcommand{\catMultiVar}{\UniDimArray{\catmultivar}}
+\newcommand{\stickbreaking}{\theta}
+\newcommand{\StickBreaking}{\UniDimArray{\stickbreaking}}
+\newcommand{\stick}{\psi}
+\newcommand{\stickbreakinghyper}{\beta}
+\newcommand{\Multivariate}{\UniDimArray{Z}}
+\newcommand{\subhistory}{\mathcal{H}}
+
+\title{\textbf{Estimating the proportion of beneficial mutations that are not adaptive in mammals}}
 
@@
     \tableofcontents
+
+    \newpage
+    \listoffigures
+
+    \newpage
+    \listoftables
+
     \clearpage
-
-    \section{Beneficial mutations in the terminal lineages and populations}\label{sec:beneficial-mutations}
-
-    \subsection{Mutation-selection codon models}
-    \label{sec:site-specific-mutation-selection-codon-models}
-    In \textit{BayesCode} (\url{https://github.com/ThibaultLatrille/bayescode}), we ran the mutation-selection codon models \textit{mutselomega} for 2000 points of MCMC with the options:
+    \section{Mutation-selection codon models}\label{sec:mutsel}
+
+    \subsection{Prior distributions and parameters of the model}\label{subsec:priors}
+
+    The parameterization of the models is described as a Bayesian hierarchical model, including the prior distributions and the parameters of the model.
+    This hierarchical model is formally represented as directed acyclic graph of dependencies between variables, depicted below.
+
+    \begin{center}
+        \captionof{figure}{Bayesian hierarchical model.}
+        \begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=0.6cm and 1.2cm,semithick]
+            \tikzstyle{every state}=[]
+
+            \node[state] (P) {$\Probmatrix\branchsiteexp$};
+            \node[state] (Q) [below right=of P] {$\Submatrix\branchsiteexp$};
+            \node[state] (R) [below right=of Q] {$\Mutmatrix$};
+            \node[state] (BL) [BLUE, right=of P] {$\branchlength\branchexp$};
+            \node[res] (BLH) [RED, right=of BL] {$ \lambda, \tau $};
+            \node[state] (f) [right=of Q] {$\Fit\siteexp $};
+            \node[state] (Ex) [BLUE, below right=of R] {$\Exchan$};
+            \node[state] (Equi) [BLUE, right=of R] {$\Mutequi$};
+            \node[state] (Base) [BLUE, above right=of f] {$\Profile\catexp$};
+            \node[state] (cat) [BLUE, right=of f] {$\catsite$};
+            \node[res] (ExH) [RED, right=of Ex] {$1,1,1,1,1,1$};
+            \node[res] (EquiH) [RED, right=of Equi] {$1,1,1,1$};
+            \node[state] (baseH) [RED, right=of Base] {$\concentrationProfile, \centerProfile $};
+            \node[state] (sb) [BLUE, right=of cat] {$\StickBreaking$};
+            \node[state] (sbH) [RED, right=of sb] {$\stickbreakinghyper$};
+
+            \path
+            (Q) edge [black] node [above right] {\ref{eq:Probmatrix}} (P)
+            (BL) edge [black] node [] {} (P)
+            (R) edge [black] node {} (Q)
+            (f) edge [black] node [above] {\ref{eq:subrates}} (Q)
+            (Ex) edge [black] node [] {} (R)
+            (Equi) edge [black] node [below] {\ref{eq:gtr-mutrates}} (R)
+            (Base) edge [black] node {} (f)
+            (cat) edge [black] node [above] {\ref{eq:sitefitness}} (f)
+            (BLH) edge [dashed, BLUE] node [above] {\ref{eq:branchlength}} (BL)
+            (ExH) edge [dashed, BLUE] node [above] {\ref{eq:DistribExchan}} (Ex)
+            (EquiH) edge [dashed, BLUE] node [above] {\ref{eq:DistribMutequi}} (Equi)
+            (baseH) edge [dashed, BLUE] node [above] {\ref{eq:DistribBase}} (Base)
+            (sb) edge [dashed, BLUE] node [above] {\ref{eq:DistribMultinomial}} (cat)
+            (sbH) edge [dashed, BLUE] node [above] {\ref{eq:DistribStickBreaking},\ref{eq:Beta}} (sb);
+        \end{tikzpicture}
+    \end{center}
+
+    Nodes of the directed acyclic graph are the variables, and edges are the functions.
+    Hyper-parameters are depicted in {\color{RED}{red}} circles, random variables in {\color{BLUE}{blue}} circles, and transformed variables in black.
+            {\color{BLUE}{Blue}} dashed line denotes a drawing from a random distribution, and black solid lines denote a function.
+    All the nodes pointing toward a given node (upstream) are its dependencies which determine its distribution.
+    The other way around, following the arrows in the DAG (downstream), simple {prior} distributions are combined together to form more complex joint {prior} distributions which ultimately define the {prior} distribution of the model.
+
+    \subsection{Nucleotide mutation rates}
+    The generalized time-reversible (GTR) nucleotide mutation rate matrix $\Mutmatrix$ is a function of the nucleotide frequencies $\Mutequi$ and the symmetric exchangeability rates $\Exchan$~\cite{tavare_probabilistic_1986}.
+    $\Mutequi = (\mutequi_A , \mutequi_C , \mutequi_G , \mutequi_T)$ is the equilibrium base frequency vector, giving the frequency at which each base occurs at each site.
+    $\Exchan = \left( \exchan_{AC}, \exchan_{AG}, \exchan_{AT}, \exchan_{CG}, \exchan_{CT}, \exchan_{GT}\right)$ is the vector of exchangeabilities between nucleotides.
+    Altogether, the rate matrix is:
+    \begin{equation}
+        \label{eq:gtr-mutrates}
+        \Mutmatrix =
+        \begin{blockarray}{ccccc}
+            & A & C & G & T \\
+            \begin{block}{c(cccc)}
+                A & -\mu_A & {\exchan_{AC}\mutequi_C} & {\exchan_{AG}\mutequi_G} & {\exchan_{AT}\mutequi_T} \\
+                C & {\exchan_{AC}\mutequi_A} &                        -\mu_C & {\exchan_{CG}\mutequi_G} & {\exchan_{CT}\mutequi_T} \\
+                G & {\exchan_{AG}\mutequi_A} & {\exchan_{CG}\mutequi_C} &                        -\mu_G & {\exchan_{GT}\mutequi_T} \\
+                T & {\exchan_{AT}\mutequi_A} & {\exchan_{CT}\mutequi_C} & {\exchan_{GT}\mutequi_G} & -\mu_T\\
+            \end{block}
+        \end{blockarray}
+    \end{equation}
+    By definition, the sum of the entries in each row of the nucleotide rate matrix $\Mutmatrix$ is equal to $0$, giving the diagonal entries:
+    \begin{equation}
+        \mu_a = \sum\limits_{ b \neq a, b \in \{A, C, G, T\} } \mutmatrix_{a,b}
+    \end{equation}
+    The {prior} on the exchangeabilities $\Exchan$ is a uniform Dirichlet distribution of dimension $6$:
+    \begin{equation}
+        \label{eq:DistribExchan}
+        \Exchan \sim \text{Dir}\left( 1,1,1,1,1,1 \right).
+    \end{equation}
+    The {prior} on the equilibrium base frequencies $\Mutequi$ is a uniform Dirichlet distribution of dimension $4$:
+    \begin{equation}
+        \label{eq:DistribMutequi}
+        \Mutequi \sim \text{Dir}\left( 1,1,1,1 \right)
+    \end{equation}
+    The general time-reversible nucleotide matrix is normalized with a total flow of $1$:
+    \begin{equation}
+        \sum\limits_{a \in \{A, C, G, T\}} - \mutequi_a \mutmatrix_{a,a} = 1,
+    \end{equation}
+    such that we expect $1$ {substitution} per unit of branch length.
+
+    \subsection{Site-specific amino-acid fitness profiles}
+    \label{sec:profiles}
+    Site-specific amino-acid fitness profiles are assumed i.i.d. from a mixture model, itself endowed with a truncated Dirichlet process prior.
+    Specifically, the mixture has $\Ncat$ components ($\Ncat = 30$ by default).
+    The prior on component weights~($\StickBreaking$) is modeled using a stick-breaking process, truncated at $\Ncat$ and of parameter $\stickbreakinghyper=1$:
+    \begin{align}
+        \label{eq:DistribStickBreaking}
+        \begin{split}
+            & \StickBreaking \sim \text{StickBreaking}\left( \Ncat, \stickbreakinghyper \right)\\
+            \iff & \stickbreaking_{\cat} = \stick_{\cat}\cdot \prod _{{\indice=1}}^{{\cat-1}}\left(1-\stick_{\indice}\right),\ \Setcat,
+        \end{split}
+    \end{align}
+    where $\stick_{\cat}$ are i.i.d. from a beta distribution
+    \begin{equation}
+        \label{eq:Beta}
+        \stick_{\cat} \sim \text{Beta}\left( 1, \stickbreakinghyper \right),\ \Setcat.
+    \end{equation}
+    Of note, the weights decrease geometrically in expectation, at rate $\stickbreakinghyper$, such that lower values of $\stickbreakinghyper$ induce more heterogeneous distributions of weights.
+
+    Each component of the mixture defines a 20-dimensional fitness profile $\Profile\catexp$ (summing to $1$), for $ \Setcat$.
+    These fitness profiles are i.i.d. from a Dirichlet of center $\centerProfile=1$ and concentration $\concentrationProfile=1$:
+    \begin{equation}
+        \label{eq:DistribBase}
+        \Profile\catexp \sim \text{Dir}\left( \centerProfile,\ \concentrationProfile \right),\ \Setcat.
+    \end{equation}
+
+    Site allocations to the mixture components $\catsite \in \catInterval $, for $\Setsite$ running over the $\Nsite$ sites of the alignment, are i.i.d. multinomial of parameter $\StickBreaking$:
+    \begin{align}
+        \label{eq:DistribMultinomial}
+        \catMultiVar \sim \text{Multinomial}\left( \StickBreaking \right), \\
+        \text{ where } \catmultivar_{\cat} = \sum_{\Setsite} \mathbb{1}_{\catsite = \cat}
+    \end{align}
+
+    For a given parameter configuration for the mixture, the scaled fitness $\Fit\siteexp$ at site $\site$, are obtained by taking the logarithm of fitness assigned to this site:
+    \begin{equation}
+        \label{eq:sitefitness}
+        \Fit\siteexp = \ln \left( \Profile^{\left( \catsite \right)} \right),\ \Setsite.
+    \end{equation}
+
+    \subsection{Branch length}
+    The topology of the rooted phylogenetic tree is supposed to be known and is not estimated by the model.
+    The branch lengths $\branchlength\branchexp$ are defined as the expected number of {neutral} substitutions per {DNA} site along a branch, each from a Gamma distribution of mean $\lambda=0.1$ and scale $\tau=1$:
+    \begin{equation}
+        \label{eq:branchlength}
+        \branchlength\branchexp \sim \text{Gamma}\left( \lambda, \tau \right).
+    \end{equation}
+
+    \subsection{Codon substitution rates}
+
+    The mutation rate between codons $\ci$ and $\cj$, denoted $\mu_{\itoj}$ depends on the underlying nucleotide change between the codons.
+    First, if codons $\ci$ and $\cj$ are not nearest-neighbours, $\mu_{\itoj}$ is equal to $0$.
+    Second, if codons $\ci$ and $\cj$ are only one mutation away, $\mu_{\itoj}$ is given by the underlying nucleotide relative rate~(${\mutmatrix_{\itoj}}$).
+
+    For a given site $\site$, the {codon} {substitution} rate matrix $\Submatrix\siteexp$ is given by:
+    \begin{equation}
+        \label{eq:subrates}
+        \begin{dcases}
+            \submatrix\siteexp_{\itoj} = 0\text{ if codons $\ci$ and $\cj$ are not nearest-neighbors,} \\
+            \submatrix\siteexp_{\itoj} = \mu_{\itoj}\text{ if codons $\ci$ and $\cj$ are {synonymous},} \\
+            \submatrix\siteexp_{\itoj} = \mu_{\itoj} \dfrac{ \fitj\siteexp - \fiti\siteexp}{{1 - \e^{\fiti\siteexp - \fitj\siteexp} }} \text{ if $\ci$ and $\cj$ are non-synonymous,}\\
+            \submatrix\siteexp_{\ci, \ci} = - \sum\limits_{ \cj \neq \ci, \cj=1}^{61} \submatrix\siteexp_{\itoj}.
+        \end{dcases}
+    \end{equation}
+    Together, the probability of transition between codons for a given branch $\branch$ and site $\site$ is:
+    \begin{equation}
+        \label{eq:Probmatrix}
+        \Probmatrix\branchsiteexp = \e^{\branchlength\branchexp \Submatrix\siteexp},
+    \end{equation}
+    which are the matrices necessary to compute the {likelihood} of the data ($\data$) given the parameters of the model using the pruning algorithm.
+
+    \subsection{Bayesian implementation}
+    \label{sec:Bayesian}
+    Bayesian inference was conducted using Markov Chain Monte Carlo (MCMC).
+    Most phylogenetic {MCMC} samplers target the distribution over the model parameters given the sequence alignment, which means that they have to repeatedly invoke the pruning algorithm to recalculate the {likelihood} which is most often the limiting step of the {MCMC}.
+    An alternative, which is used here, is to do the {MCMC} conditionally on the detailed {substitution} history $\subhistory$, thus doing the {MCMC} over the augmented configuration~($\subhistory$, $\data$), under the target distribution obtained by combining the mapping-based {likelihood} with the {prior} over model parameters.
+    The key idea that makes this strategy efficient is that the mapping-based {likelihood} depends on compact summary statistics of $\subhistory$, leading to very fast evaluation of the {likelihood}.
+    On the other hand, this requires to implement more complex {MCMC} procedures that have to alternate between:
+    \begin{enumerate}
+        \item sampling $\subhistory$ conditionally on the data and the current parameter configuration.
+        \item re-sampling the parameters conditionally on $\subhistory$.
+    \end{enumerate}
+
+    To implement the mapping-based {MCMC} sampling strategy, we first sample the detailed {substitution} history $\subhistory$ for all sites along the tree.
+    Several methods exist for doing this~\cite{nielsen_mapping_2002,rodrigue_uniformization_2008}, which are used here in combination (first trying the accept-reject method of \textcite{nielsen_mapping_2002}, then switching to the uniformization approach of \textcite{rodrigue_uniformization_2008} if the first round has failed).
+
+    Then, we write down the probability of $\subhistory$ given the parameters, and finally, we collect all factors that depend on some parameter of interest and make some simplifications.
+    This ultimately leads to relatively compact sufficient statistics allowing for fast numerical evaluation of the likelihood~\cite{irvahn_phylogenetic_2014,davydov_state_2017}.
+
+    \subsection{BayesCode software}\label{subsec:bayescode}
+    In \textit{BayesCode} (\href{https://github.com/ThibaultLatrille/BayesCode}{github.com/ThibaultLatrille/BayesCode}, v1.3.1), we ran the mutation-selection codon models \textit{mutselomega} for 2000 points of MCMC with the options:
     \begin{scriptsize}
@@
 
-    \subsection{Summary tables}\label{subsec:summary-table-mutsel}
-
-    \subsubsection{$\dnds$ for deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial back-mutations ($\SphyBen$)}
-    \begin{center}
-        \captionof{table}{$\dnds$ for deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial back-mutations ($\SphyBen$).}
+    \newpage
+
+    \section{Beneficial mutations in the terminal lineages and populations}\label{sec:beneficial-mutations}
+
+    \subsection{Example sites}\label{subsec:example-sites}
+
+    We extracted protein-coding DNA alignments across mammals centered around the codon site (two flanking codons in white background) for which the beneficial non-adaptive mutations ($\SphyBen$) have been detected in \textit{Chlorocebus sabaeus}.
+    We also show the translated amino acids of this region.
+    For instance, in DNA alignment of gene SELE shown below, the nucleotide at site 1722 has mutated (from T to C) at the basis of Simiiformes (monkeys and apes), modifying the corresponding amino acid from Serine to Proline, but has been subsequently reverted in the branch of \textit{Chlorocebus sabaeus}.
+    However, other substitutions classified as $\SphyBen$ cannot be clearly interpreted as reversions \textit{sensu stricto} along the terminal branch of \textit{Chlorocebus sabaeus}.
+    Indeed, we acknowledge that on a fixed fitness landscape, a deleterious mutation can be compensated by transitions to other fitter amino-acids, and not necessarily the ancestral one.
+
+    In the figures below, the first line is the name of the gene, the second line the position of the mutation in the OrthoMam protein-coding DNA alignment, and the arrow in the third line corresponds to the nucleotide position of the mutation.
+    Finally, for reproducibility, we generated the fasta alignment for all $\SphyBen$ mutations that we detected, either in the terminal lineage or in segregating polymorphism.
+    These fasta files are available at Zenodo (\url{https://doi.org/10.5281/zenodo.7878953}), across all populations, under the compressed archive \textit{alignment\_focused\_around\_non\_adaptive\_mutations.zip} and we provide a python script to obtain the figures shown below given these alignments.
+
+    \newpage
+    \begin{center}
+        \captionof{figure}{Examples sites of $\SphyBen$ mutations in \textit{Chlorocebus sabaeus} (reversions).}.
+        \includegraphics[width=0.95\linewidth, page=1]{artworks/Alignment.Chlorocebus_sabaeus.Saint_Kitts-0.pdf}
+    \end{center}
+
+    \newpage
+    \begin{center}
+        \captionof{figure}{Examples sites of $\SphyBen$ mutations in \textit{Chlorocebus sabaeus}.}.
+        \includegraphics[width=0.95\linewidth, page=1]{artworks/Alignment.Chlorocebus_sabaeus.Saint_Kitts-1.pdf}
+    \end{center}
+
+    \newpage
+    \subsection{Selection along the terminal branches}\label{subsec:summary-table-mutsel}
+
+    \subsubsection{Probability of mutations and substitutions to be $\SphyDel$, $\SphyNeu$ or $\SphyBen$}
+    \begin{center}
+        \captionof{table}{Probability of mutations and substitutions to be $\SphyDel$, $\SphyNeu$ or $\SphyBen$.}
         \scriptsize
@@
     \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
+        \item $\proba [ \SphyDel ]$ (eq.~5) is the probability for a new mutation to be a deleterious.
+        These mutations have a selection coefficient predicted at the phylogenetic-scale lower than -1, thus toward a less fit amino-acid.
+        \item $\proba [ \SphyNeu ]$ (eq.~5) is the probability for a new mutation to be a nearly-neutral.
+        These mutations have a selection coefficient predicted at the phylogenetic-scale between -1 and 1.
+        \item $\proba [ \SphyBen ]$ (eq.~5) is the probability for a new mutation to be a  non-adaptive beneficial mutation.
+        These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1, thus toward a more fit amino-acid.
+        \item $\proba_{div}[\SphyDel]$ is the proportion of substitutions in the terminal branch that are $\SphyDel$.
+        \item $\proba_{div}[\SphyNeu]$ is the proportion of substitutions in the terminal branch that are $\SphyNeu$.
         \item $\proba_{div}[\SphyBen]$ is the proportion of substitutions in the terminal branch that are $\SphyBen$.
+    \end{itemize}
+    \newpage
+
+    \subsubsection{$\dnds$ for $\SphyDel$, $\SphyNeu$ or $\SphyBen$}
+    \begin{center}
+        \captionof{table}{$\dnds$ for $\SphyDel$, $\SphyNeu$ or $\SphyBen$.}
+        \scriptsize
+        \begin{longtable*}{|l|r|r|r|r|}
+            \toprule
+            Species & $\dnds $ & $\dn ( \SphyDel ) / \ds$ & $\dn ( \SphyNeu ) / \ds$ & $\dn ( \SphyBen ) / \ds$ \\
+            \midrule
+            \endhead
+            \midrule
+            \multicolumn{5}{r}{{Continued on next page}} \\
+            \midrule
+            \endfoot
+
+            \bottomrule
+            \endlastfoot
+            \rowcolor{LIGHTGREY} Equus caballus & $ 0.129$ & $ 0.065$ & $ 0.832$ & $ 1.267$ \\
+            Bos taurus & [$ 0.114$, $ 0.116$] & [$ 0.063$, $ 0.064$] & [$ 0.629$, $ 0.638$] & [$ 1.280$, $ 1.328$] \\
+            \rowcolor{LIGHTGREY} Capra hircus & [$ 0.108$, $ 0.109$] & [$ 0.058$, $ 0.058$] & [$ 0.631$, $ 0.636$] & [$ 1.169$, $ 1.183$] \\
+            Ovis aries & [$ 0.127$, $ 0.129$] & [$ 0.078$, $ 0.080$] & [$ 0.619$, $ 0.621$] & [$ 1.201$, $ 1.217$] \\
+            \rowcolor{LIGHTGREY} Chlorocebus sabaeus & [$ 0.118$, $ 0.119$] & [$ 0.062$, $ 0.062$] & [$ 0.713$, $ 0.720$] & [$ 1.521$, $ 1.577$] \\
+            Homo sapiens & [$ 0.170$, $ 0.170$] & [$ 0.103$, $ 0.103$] & [$ 0.884$, $ 0.888$] & [$ 1.733$, $ 1.745$] \\
+        \end{longtable*}
+    \end{center}
+    \begin{itemize}
+        \item $\dnds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions estimated for all the non-synonymous substitutions in the terminal branch.
         \item $\dn(\SphyDel) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are $\SphyDel$.
@@
     \end{itemize}
-
-    \newpage
-
-    \subsubsection{$\dnds$ over-estimation due to beneficial back-mutations}
-    \begin{center}
-        \captionof{table}{$\dnds$ over-estimation due to beneficial back-mutations.}
+    SNP are considered fixed in the populations if all sampled individuals are homozygous for the derived allele, in which case we consider this SNP not to be segregating but as fixed as a substitution.
+    This effect results in $\dn / \ds$ that can change across populations, denoted as a range per species.
+    $\dn(\SphyBen) / \ds$ values observed are above 1 and are consistent with slightly advantageous mutations.\\
+
+    Theoretically, $\omega = \dn / \ds$ can be related to the underlying scaled selection coefficient ($S$) with the relation $\omega = S /(1-\exp(-S))$ as in \cite[eq. 3]{nielsen_estimating_2003}.
+    In our experiments our observed $\dn(\SphyBen) / \ds$ is on the range $1.169$ (\textit{C.
+hircus}) to 1.745 (\textit{H.
+sapiens}), translating into average $S$ of $\approx0.32$ to $\approx1.24$, so indeed only slightly advantageous.\\
+
+    Of note, observing $\dn(\SphyBen) / \ds >1$ is an important check that $\SphyBen$ mutations are indeed positively selected with an increased substitution rate.
+    Since $\dn(\SphyNeu) / \ds$ is close to 1 for the predicted nearly-neutral mutations, this means that the selection coefficients predicted at the mutation-selection balance are good proxies of selection, then observing $\dn(\SphyBen) / \ds > 1$ is evidence of positive selection of predicted non-adaptive beneficial mutations.
+
+    \newpage
+    \subsubsection{$\dnds$ over-estimation due to non-adaptive beneficial mutations}
+    \begin{center}
+        \captionof{table}{$\dnds$ over-estimation due to non-adaptive beneficial mutations.}
+        \scriptsize
+        \begin{longtable*}{|l|r|r|r|}
+            \toprule
+            Species & $\dnds $ & $\dn(\Sphy < 1) / \ds$ & $\delta(\dnds )$ \\
+            \midrule
+            \endhead
+            \midrule
+            \multicolumn{4}{r}{{Continued on next page}} \\
+            \midrule
+            \endfoot
+
+            \bottomrule
+            \endlastfoot
+            \rowcolor{LIGHTGREY} Equus caballus & $ 0.129$ & $ 0.115$ & $  10.7$ \\
+            Bos taurus & [$ 0.114$, $ 0.116$] & [$ 0.101$, $ 0.102$] & [$  11.3$, $  11.5$] \\
+            \rowcolor{LIGHTGREY} Capra hircus & [$ 0.108$, $ 0.109$] & [$ 0.096$, $ 0.097$] & [$  11.0$, $  11.2$] \\
+            Chlorocebus sabaeus & [$ 0.118$, $ 0.119$] & [$ 0.104$, $ 0.105$] & [$  11.4$, $  11.7$] \\
+            \rowcolor{LIGHTGREY} Homo sapiens & [$ 0.170$, $ 0.170$] & [$ 0.154$, $ 0.155$] & [$ 8.926$, $ 8.996$] \\
+            Ovis aries & [$ 0.127$, $ 0.129$] & [$ 0.115$, $ 0.117$] & [$ 9.663$, $ 9.894$] \\
+        \end{longtable*}
+    \end{center}
+    \begin{itemize}
+        \item $\dnds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions estimated for all the non-synonymous substitutions in the terminal branch.
+        \item $\dn(\Sphy < 1) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are not $\SphyBen$.
+        This is the estimated divergence when we removed non-adaptive beneficial mutations.
+        \item $\delta(\dnds)$ (eq.~7) is the fraction of the divergence ($\dnds$) that is over-estimated, $\dnds$ is compared to the estimated divergence when we removed non-adaptive beneficial mutations $\dn(\Sphy < 1) / \ds$.
+    \end{itemize}
+    We estimated that between 9 and 11\% of $\dnds$ is over-estimated, corresponding to non-adaptive beneficial mutations inflating the $\dnds$ statistic.
+
+    \newpage
+    \section{Gene ontology enrichment}
+
+    \subsection{Gene ontology enrichment in $\SphyBen$ SNPs}
+
+    To assess whether $\SphyBen$ SNPs are enriched in specific gene functions, we used gene ontology (GO) terms at the gene level.
+    Thus, for each $\SphyBen$ SNP detected in a focal population, we annotated this SNP with GO terms inherited from the gene in which the SNP is located.
+    We restricted this analysis solely on genes annotated with at least one GO term. \\
+
+    In order to assess the weight of each GO term in the set of $\SphyBen$ SNPs, we computed the proportion of $\SphyBen$ SNPs annotated with a given GO term.
+    Thus, for each GO term, $p$ is the proportion of $\SphyBen$ SNPs that are annotated with this focal GO term among all annotated $\SphyBen$ SNPs.\\
+
+    In order to test if the distribution of $\SphyBen$ SNPs is different between genes sharing a common GO term and the rest of the genes, we used a Mann-Whitney U test.
+    To do so, first, for each gene, we computed the proportion of sites that have a $\SphyBen$ SNP, called $p[ \SphyBen ]$ (can be 0 if no $\SphyBen$ SNP is detected for this gene).
+    Second, for each GO term, $r$ is the ratio of the mean of $p[ \SphyBen ]$ in the set of genes sharing the focal ontology over the mean of $p[ \SphyBen ]$ in the rest of the genes.
+    Third, Mann-Whitney U test (two-sided) is used to test if the distribution of $p[ \SphyBen ]$ is different between the two sets of genes (U statistic and p-value $p_{\mathrm{v}}$).
+    Finally, $p_{\mathrm{v}}^{\mathrm{adj}}$ are corrected for multiple comparison (Holm–Bonferroni correction across the ontology terms).
+    $^*$ for $p_{\mathrm{v}}^{\mathrm{adj}}$ corrected for multiple comparison (Holm–Bonferroni correction) lower than the risk $\alpha=0.05$. \\
+
+    The table below shows the GO terms (first 100 rows with the lowest $p_{\mathrm{v}}$) that are enriched in genes with $\SphyBen$ SNP in human (european population).
+
+    \begin{center}
+        \captionof{table}{Gene ontology enrichment in $\SphyBen$ SNPs}
         \scriptsize
@@
             \toprule
-            Population & Species & Watterson's $\thetaSyn$ & $\proba_{div}[\Sphy > 1]$ & $\dnds $ & $\dn(\Sphy < 1) / \ds$ & $\delta(\dnds )$ \\
+            GO id & GO name & $p$ & $r$ & Mann-Whitney U & $p_{\mathrm{v}}$ & $p_{\mathrm{v}}^{\mathrm{adj}}$ \\
             \midrule
@@
             \midrule
-            \multicolumn{7}{r}{{Continued on next page}} \\
+            \multicolumn{7}{r}{Continued on next page} \\
             \midrule
             \endfoot
-
             \bottomrule
             \endlastfoot
-            \rowcolor{LIGHTGREY} Equus c. &      Equus caballus &               $ 0.002$ &                    $ 0.118$ &  $ 0.147$ &           $ 0.131$ &     $  10.5$ \\
-            Iran &          Bos taurus &               $ 0.002$ &                    $ 0.123$ &  $ 0.131$ &           $ 0.117$ &     $  11.1$ \\
-            Uganda &          Bos taurus &               $ 0.005$ &                    $ 0.125$ &  $ 0.134$ &           $ 0.118$ &     $  11.3$ \\
-            \rowcolor{LIGHTGREY} Australia &        Capra hircus &               $ 0.003$ &                    $ 0.121$ &  $ 0.125$ &           $ 0.111$ &     $  10.8$ \\
-            \rowcolor{LIGHTGREY} France &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.126$ &           $ 0.112$ &     $  10.8$ \\
-            \rowcolor{LIGHTGREY} Iran (C. aegagrus) &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.125$ &           $ 0.111$ &     $  10.8$ \\
-            \rowcolor{LIGHTGREY} Iran &        Capra hircus &               $ 0.004$ &                    $ 0.121$ &  $ 0.125$ &           $ 0.111$ &     $  10.9$ \\
-            \rowcolor{LIGHTGREY} Italy &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.126$ &           $ 0.112$ &     $  10.8$ \\
-            \rowcolor{LIGHTGREY} Morocco &        Capra hircus &               $ 0.004$ &                    $ 0.122$ &  $ 0.125$ &           $ 0.111$ &     $  11.0$ \\
-            Iran &          Ovis aries &               $ 0.007$ &                    $ 0.109$ &  $ 0.146$ &           $ 0.132$ &     $ 9.671$ \\
-            Iran (O. orientalis) &          Ovis aries &               $ 0.009$ &                    $ 0.108$ &  $ 0.148$ &           $ 0.134$ &     $ 9.516$ \\
-            Iran (O. vignei) &          Ovis aries &               $ 0.007$ &                    $ 0.109$ &  $ 0.146$ &           $ 0.132$ &     $ 9.598$ \\
-            Various &          Ovis aries &               $ 0.008$ &                    $ 0.107$ &  $ 0.148$ &           $ 0.134$ &     $ 9.439$ \\
-            Morocco &          Ovis aries &               $ 0.008$ &                    $ 0.108$ &  $ 0.148$ &           $ 0.134$ &     $ 9.582$ \\
-            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus &               $ 0.004$ &                    $ 0.122$ &  $ 0.133$ &           $ 0.118$ &     $  11.2$ \\
-            \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.124$ &  $ 0.134$ &           $ 0.119$ &     $  11.3$ \\
-            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.124$ &  $ 0.134$ &           $ 0.118$ &     $  11.3$ \\
-            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.123$ &  $ 0.134$ &           $ 0.119$ &     $  11.2$ \\
-            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.123$ &  $ 0.134$ &           $ 0.119$ &     $  11.3$ \\
-            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus &               $ 0.003$ &                    $ 0.123$ &  $ 0.133$ &           $ 0.118$ &     $  11.3$ \\
-            \rowcolor{LIGHTGREY} South Africa  & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.125$ &  $ 0.134$ &           $ 0.118$ &     $  11.5$ \\
-            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &                    $ 0.123$ &  $ 0.133$ &           $ 0.118$ &     $  11.3$ \\
-            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.123$ &  $ 0.134$ &           $ 0.119$ &     $  11.2$ \\
-            African &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &           $ 0.175$ &     $ 8.799$ \\
-            Admixed American &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &           $ 0.175$ &     $ 8.780$ \\
-            East Asian &        Homo sapiens &               $ 0.002$ &                    $ 0.098$ &  $ 0.192$ &           $ 0.175$ &     $ 8.768$ \\
-            European &        Homo sapiens &               $ 0.002$ &                    $ 0.098$ &  $ 0.192$ &           $ 0.175$ &     $ 8.728$ \\
-            South Asian &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &           $ 0.175$ &     $ 8.788$ \\
+            GO:0003777 & microtubule motor activity & $ 0.027$ & $ 1.802$ & $1.1\times 10^{5}$ & $1.8\times 10^{-6}$ & $\bm{0.0008{^*}}$ \\
+            GO:0005578 & proteinaceous extracellular matrix & $ 0.069$ & $ 2.071$ & $4.7\times 10^{5}$ & $1.9\times 10^{-6}$ & $\bm{0.00084{^*}}$ \\
+            GO:0003774 & motor activity & $ 0.023$ & $ 1.127$ & $1.1\times 10^{5}$ & $6.7\times 10^{-5}$ & $\bm{ 0.029{^*}}$ \\
+            GO:0030198 & extracellular matrix organization & $ 0.039$ & $ 1.956$ & $2.7\times 10^{5}$ & $0.00055$ & $ 0.239~~$ \\
+            GO:0007018 & microtubule-based movement & $ 0.023$ & $ 0.924$ & $1.3\times 10^{5}$ & $0.00073$ & $ 0.315~~$ \\
+            GO:0005576 & extracellular region & $ 0.178$ & $ 2.195$ & $1.9\times 10^{6}$ & $0.00083$ & $ 0.359~~$ \\
+            GO:0006898 & receptor-mediated endocytosis & $ 0.027$ & $ 1.803$ & $1.7\times 10^{5}$ & $ 0.001$ & $ 0.512~~$ \\
+            GO:0006355 & regulation of transcription & $ 0.069$ & $ 0.275$ & $1.9\times 10^{6}$ & $ 0.002$ & $ 0.815~~$ \\
+            GO:0005604 & basement membrane & $ 0.019$ & $ 1.638$ & $1.1\times 10^{5}$ & $ 0.002$ & $ 0.852~~$ \\
+            GO:0007229 & integrin-mediated signaling pathway & $ 0.019$ & $ 1.930$ & $1.1\times 10^{5}$ & $ 0.003$ & $ 1.000~~$ \\
+            GO:0016887 & ATPase activity & $ 0.031$ & $ 1.149$ & $1.8\times 10^{5}$ & $ 0.003$ & $ 1.000~~$ \\
+            GO:0007155 & cell adhesion & $ 0.062$ & $ 1.438$ & $5.8\times 10^{5}$ & $ 0.005$ & $ 1.000~~$ \\
+            GO:0005634 & nucleus & $ 0.266$ & $ 0.557$ & $3.9\times 10^{6}$ & $ 0.005$ & $ 1.000~~$ \\
+            GO:0006351 & transcription & $ 0.073$ & $ 0.339$ & $1.9\times 10^{6}$ & $ 0.008$ & $ 1.000~~$ \\
+            GO:0005654 & nucleoplasm & $ 0.124$ & $ 0.443$ & $2.6\times 10^{6}$ & $ 0.009$ & $ 1.000~~$ \\
+            GO:0006366 & transcription from RNA polymerase II promoter & $ 0.008$ & $ 0.063$ & $6.2\times 10^{5}$ & $ 0.011$ & $ 1.000~~$ \\
+            GO:0005829 & cytosol & $ 0.212$ & $ 0.541$ & $3.5\times 10^{6}$ & $ 0.012$ & $ 1.000~~$ \\
+            GO:0016853 & isomerase activity & $ 0.015$ & $ 4.066$ & $ 1\times 10^{5}$ & $ 0.015$ & $ 1.000~~$ \\
+            GO:0071356 & cellular response to tumor necrosis factor & $ 0.015$ & $ 7.069$ & $ 1\times 10^{5}$ & $ 0.016$ & $ 1.000~~$ \\
+            GO:0005518 & collagen binding & $ 0.015$ & $ 2.900$ & $ 1\times 10^{5}$ & $ 0.017$ & $ 1.000~~$ \\
+            GO:0043087 & regulation of GTPase activity & $ 0.015$ & $ 2.025$ & $1.1\times 10^{5}$ & $ 0.027$ & $ 1.000~~$ \\
+            GO:0000139 & Golgi membrane & $ 0.012$ & $ 0.214$ & $6.3\times 10^{5}$ & $ 0.028$ & $ 1.000~~$ \\
+            GO:0043235 & receptor complex & $ 0.023$ & $ 0.935$ & $1.9\times 10^{5}$ & $ 0.028$ & $ 1.000~~$ \\
+            GO:0000981 & RNA polymerase II transcription factor activity & $ 0.027$ & $ 0.452$ & $9.1\times 10^{5}$ & $ 0.029$ & $ 1.000~~$ \\
+            GO:0005739 & mitochondrion & $ 0.058$ & $ 0.471$ & $1.4\times 10^{6}$ & $ 0.029$ & $ 1.000~~$ \\
+            GO:0005581 & collagen trimer & $ 0.015$ & $ 2.124$ & $1.1\times 10^{5}$ & $ 0.036$ & $ 1.000~~$ \\
+            GO:0051015 & actin filament binding & $ 0.019$ & $ 0.912$ & $1.5\times 10^{5}$ & $ 0.036$ & $ 1.000~~$ \\
+            GO:0001843 & neural tube closure & $ 0.015$ & $ 1.164$ & $1.1\times 10^{5}$ & $ 0.036$ & $ 1.000~~$ \\
+            GO:0005737 & cytoplasm & $ 0.317$ & $ 0.692$ & $4.1\times 10^{6}$ & $ 0.037$ & $ 1.000~~$ \\
+            GO:0043565 & sequence-specific DNA binding & $ 0.015$ & $ 0.308$ & $ 6\times 10^{5}$ & $ 0.039$ & $ 1.000~~$ \\
+            GO:0004222 & metalloendopeptidase activity & $ 0.019$ & $ 1.188$ & $1.6\times 10^{5}$ & $ 0.043$ & $ 1.000~~$ \\
+            GO:0007166 & cell surface receptor signaling pathway & $ 0.031$ & $ 2.871$ & $ 3\times 10^{5}$ & $ 0.046$ & $ 1.000~~$ \\
+            GO:0007156 & homophilic cell adhesion via plasma membrane... & $ 0.015$ & $ 1.013$ & $1.2\times 10^{5}$ & $ 0.050$ & $ 1.000~~$ \\
+            GO:0007286 & spermatid development & $ 0.015$ & $ 2.497$ & $1.2\times 10^{5}$ & $ 0.051$ & $ 1.000~~$ \\
+            GO:0008202 & steroid metabolic process & $ 0.015$ & $ 2.755$ & $1.2\times 10^{5}$ & $ 0.051$ & $ 1.000~~$ \\
+            GO:0061024 & membrane organization & $ 0.019$ & $ 1.516$ & $1.6\times 10^{5}$ & $ 0.052$ & $ 1.000~~$ \\
+            GO:1901796 & regulation of signal transduction by p53 class... & $ 0.019$ & $ 1.333$ & $1.6\times 10^{5}$ & $ 0.058$ & $ 1.000~~$ \\
+            GO:0006397 & mRNA processing & $ 0.004$ & $ 0.210$ & $3.5\times 10^{5}$ & $ 0.061$ & $ 1.000~~$ \\
+            GO:0006915 & apoptotic process & $ 0.015$ & $ 0.463$ & $6.4\times 10^{5}$ & $ 0.065$ & $ 1.000~~$ \\
+            GO:0043547 & positive regulation of GTPase activity & $ 0.035$ & $ 2.651$ & $3.7\times 10^{5}$ & $ 0.068$ & $ 1.000~~$ \\
+            GO:0007010 & cytoskeleton organization & $ 0.019$ & $ 1.771$ & $1.7\times 10^{5}$ & $ 0.068$ & $ 1.000~~$ \\
+            GO:0030308 & negative regulation of cell growth & $ 0.015$ & $ 3.055$ & $1.3\times 10^{5}$ & $ 0.070$ & $ 1.000~~$ \\
+            GO:0007160 & cell-matrix adhesion & $ 0.015$ & $ 1.046$ & $1.2\times 10^{5}$ & $ 0.073$ & $ 1.000~~$ \\
+            GO:0006897 & endocytosis & $ 0.023$ & $ 1.408$ & $2.2\times 10^{5}$ & $ 0.073$ & $ 1.000~~$ \\
+            GO:0003677 & DNA binding & $ 0.077$ & $ 0.448$ & $1.7\times 10^{6}$ & $ 0.075$ & $ 1.000~~$ \\
+            GO:0043202 & lysosomal lumen & $ 0.015$ & $ 1.522$ & $1.3\times 10^{5}$ & $ 0.075$ & $ 1.000~~$ \\
+            GO:0003700 & DNA binding transcription factor activity & $ 0.027$ & $ 0.343$ & $8.7\times 10^{5}$ & $ 0.076$ & $ 1.000~~$ \\
+            GO:0008134 & transcription factor binding & $ 0.004$ & $ 0.048$ & $3.2\times 10^{5}$ & $ 0.077$ & $ 1.000~~$ \\
+            GO:0005488 & binding & $ 0.046$ & $ 0.641$ & $4.1\times 10^{5}$ & $ 0.078$ & $ 1.000~~$ \\
+            GO:0045944 & positive regulation of transcription from RNA... & $ 0.039$ & $ 0.324$ & $1.1\times 10^{6}$ & $ 0.085$ & $ 1.000~~$ \\
+            GO:0005794 & Golgi apparatus & $ 0.046$ & $ 0.430$ & $1.2\times 10^{6}$ & $ 0.087$ & $ 1.000~~$ \\
+            GO:0016032 & viral process & $ 0.008$ & $ 0.321$ & $4.1\times 10^{5}$ & $ 0.089$ & $ 1.000~~$ \\
+            GO:0055085 & transmembrane transport & $ 0.054$ & $ 1.533$ & $5.9\times 10^{5}$ & $ 0.092$ & $ 1.000~~$ \\
+            GO:0006260 & DNA replication & $ 0.019$ & $ 1.051$ & $1.8\times 10^{5}$ & $ 0.096$ & $ 1.000~~$ \\
+            GO:0030425 & dendrite & $ 0.008$ & $ 0.121$ & $3.9\times 10^{5}$ & $ 0.099$ & $ 1.000~~$ \\
+            GO:0005524 & ATP binding & $ 0.127$ & $ 0.666$ & $1.5\times 10^{6}$ & $ 0.103$ & $ 1.000~~$ \\
+            GO:0005615 & extracellular space & $ 0.100$ & $ 1.699$ & $1.3\times 10^{6}$ & $ 0.107$ & $ 1.000~~$ \\
+            GO:0007283 & spermatogenesis & $ 0.039$ & $ 1.824$ & $3.9\times 10^{5}$ & $ 0.108$ & $ 1.000~~$ \\
+            GO:0005179 & hormone activity & $ 0.012$ & $ 7.683$ & $9.9\times 10^{4}$ & $ 0.118$ & $ 1.000~~$ \\
+            GO:0098793 & presynapse & $ 0.012$ & $ 2.065$ & $9.6\times 10^{4}$ & $ 0.119$ & $ 1.000~~$ \\
+            GO:0005254 & chloride channel activity & $ 0.012$ & $ 1.694$ & $9.6\times 10^{4}$ & $ 0.124$ & $ 1.000~~$ \\
+            GO:0036064 & ciliary basal body & $ 0.015$ & $ 1.378$ & $1.4\times 10^{5}$ & $ 0.125$ & $ 1.000~~$ \\
+            GO:0070062 & extracellular exosome & $ 0.104$ & $ 0.570$ & $2.1\times 10^{6}$ & $ 0.125$ & $ 1.000~~$ \\
+            GO:0090630 & activation of GTPase activity & $ 0.012$ & $ 2.519$ & $9.9\times 10^{4}$ & $ 0.127$ & $ 1.000~~$ \\
+            GO:0044212 & transcription regulatory region DNA binding & $ 0.004$ & $ 0.322$ & $2.7\times 10^{5}$ & $ 0.128$ & $ 1.000~~$ \\
+            GO:0055114 & oxidation-reduction process & $ 0.019$ & $ 0.482$ & $6.4\times 10^{5}$ & $ 0.129$ & $ 1.000~~$ \\
+            GO:0019886 & antigen processing and presentation of exogenous... & $ 0.012$ & $ 1.393$ & $9.6\times 10^{4}$ & $ 0.129$ & $ 1.000~~$ \\
+            GO:0005743 & mitochondrial inner membrane & $ 0.008$ & $ 0.463$ & $3.7\times 10^{5}$ & $ 0.133$ & $ 1.000~~$ \\
+            GO:0022617 & extracellular matrix disassembly & $ 0.012$ & $ 1.009$ & $9.6\times 10^{4}$ & $ 0.135$ & $ 1.000~~$ \\
+            GO:0042493 & response to drug & $ 0.004$ & $ 0.043$ & $2.6\times 10^{5}$ & $ 0.137$ & $ 1.000~~$ \\
+            GO:0008380 & RNA splicing & $ 0.008$ & $ 0.098$ & $2.6\times 10^{5}$ & $ 0.139$ & $ 1.000~~$ \\
+            GO:0043687 & post-translational protein modification & $ 0.008$ & $ 0.319$ & $3.6\times 10^{5}$ & $ 0.140$ & $ 1.000~~$ \\
+            GO:0010951 & negative regulation of endopeptidase activity & $ 0.012$ & $ 2.037$ & $9.9\times 10^{4}$ & $ 0.140$ & $ 1.000~~$ \\
+            GO:0000978 & RNA polymerase II proximal promoter... & $ 0.012$ & $ 0.250$ & $4.5\times 10^{5}$ & $ 0.140$ & $ 1.000~~$ \\
+            GO:0003713 & transcription coactivator activity & $ 0.004$ & $ 0.339$ & $2.6\times 10^{5}$ & $ 0.142$ & $ 1.000~~$ \\
+            GO:0001227 & transcriptional repressor activity & $ 0.012$ & $ 1.384$ & $9.9\times 10^{4}$ & $ 0.144$ & $ 1.000~~$ \\
+            GO:0005623 & cell & $ 0.012$ & $ 1.927$ & $ 1\times 10^{5}$ & $ 0.150$ & $ 1.000~~$ \\
+            GO:0030574 & collagen catabolic process & $ 0.012$ & $ 1.036$ & $9.9\times 10^{4}$ & $ 0.151$ & $ 1.000~~$ \\
+            GO:0006457 & protein folding & $ 0.015$ & $ 2.465$ & $1.5\times 10^{5}$ & $ 0.158$ & $ 1.000~~$ \\
+            GO:0016477 & cell migration & $ 0.004$ & $ 0.121$ & $2.4\times 10^{5}$ & $ 0.159$ & $ 1.000~~$ \\
+            GO:0070374 & positive regulation of ERK1 and ERK2 cascade & $ 0.019$ & $ 4.238$ & $ 2\times 10^{5}$ & $ 0.160$ & $ 1.000~~$ \\
+            GO:0007605 & sensory perception of sound & $ 0.015$ & $ 0.824$ & $1.5\times 10^{5}$ & $ 0.162$ & $ 1.000~~$ \\
+            GO:0031225 & anchored component of membrane & $ 0.012$ & $ 0.892$ & $ 1\times 10^{5}$ & $ 0.171$ & $ 1.000~~$ \\
+            GO:0016757 & transferase activity & $ 0.004$ & $ 0.435$ & $2.4\times 10^{5}$ & $ 0.177$ & $ 1.000~~$ \\
+            GO:0002376 & immune system process & $ 0.012$ & $ 0.411$ & $4.3\times 10^{5}$ & $ 0.177$ & $ 1.000~~$ \\
+            GO:0005759 & mitochondrial matrix & $ 0.008$ & $ 0.361$ & $3.3\times 10^{5}$ & $ 0.185$ & $ 1.000~~$ \\
+            GO:0010389 & regulation of G2/M transition of mitotic cell... & $ 0.012$ & $ 0.924$ & $ 1\times 10^{5}$ & $ 0.188$ & $ 1.000~~$ \\
+            GO:0005667 & transcription factor complex & $ 0.004$ & $ 0.177$ & $2.3\times 10^{5}$ & $ 0.189$ & $ 1.000~~$ \\
+            GO:0030054 & cell junction & $ 0.031$ & $ 0.251$ & $8.1\times 10^{5}$ & $ 0.190$ & $ 1.000~~$ \\
+            GO:0001650 & fibrillar center & $ 0.019$ & $ 1.540$ & $1.1\times 10^{5}$ & $ 0.191$ & $ 1.000~~$ \\
+            GO:0014069 & postsynaptic density & $ 0.004$ & $ 0.172$ & $2.2\times 10^{5}$ & $ 0.200$ & $ 1.000~~$ \\
+            GO:0046934 & phosphatidylinositol-4 & $ 0.012$ & $ 1.135$ & $1.1\times 10^{5}$ & $ 0.201$ & $ 1.000~~$ \\
+            GO:0007267 & cell-cell signaling & $ 0.004$ & $ 0.354$ & $2.2\times 10^{5}$ & $ 0.201$ & $ 1.000~~$ \\
+            GO:0001649 & osteoblast differentiation & $ 0.012$ & $ 1.917$ & $1.1\times 10^{5}$ & $ 0.201$ & $ 1.000~~$ \\
+            GO:0045893 & positive regulation of transcription & $ 0.023$ & $ 0.596$ & $6.6\times 10^{5}$ & $ 0.205$ & $ 1.000~~$ \\
+            GO:0007399 & nervous system development & $ 0.015$ & $ 0.450$ & $ 5\times 10^{5}$ & $ 0.205$ & $ 1.000~~$ \\
+            GO:0001501 & skeletal system development & $ 0.015$ & $ 1.212$ & $1.6\times 10^{5}$ & $ 0.207$ & $ 1.000~~$ \\
+            GO:0019903 & protein phosphatase binding & $ 0.012$ & $ 0.875$ & $1.1\times 10^{5}$ & $ 0.208$ & $ 1.000~~$ \\
+            GO:1902476 & chloride transmembrane transport & $ 0.012$ & $ 1.458$ & $1.1\times 10^{5}$ & $ 0.210$ & $ 1.000~~$ \\
+            GO:0007568 & aging & $ 0.015$ & $ 2.053$ & $1.6\times 10^{5}$ & $ 0.210$ & $ 1.000~~$ \\
         \end{longtable*}
     \end{center}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item $\proba_{div}[\SphyBen]$ is the proportion of substitutions in the terminal branch that are $\SphyBen$.
-        \item $\dnds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions estimated for all the non-synonymous substitutions in the terminal branch.
-        \item $\dn(\Sphy < 1) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are not $\SphyBen$.
-        This is the estimated divergence when we removed beneficial back-mutations.
-        \item $\delta(\dnds)$ (eq.~7) is the fraction of the divergence ($\dnds$) that is over-estimated, $\dnds$ is compared to the estimated divergence when we removed beneficial back-mutations $\dn(\Sphy < 1) / \ds$.
-    \end{itemize}
-    We estimated that between 9 and 11\% of $\dnds$ is over-estimated, corresponding to beneficial back-mutation inflating the $\dnds$ statistic.
-
-    \newpage
-
-    \subsubsection{Probabilities of beneficial back-mutations}
-    \begin{center}
-        \captionof{table}{Probability of beneficial back-mutations among all beneficial ones.}
-        \scriptsize
-        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
-            \toprule
-            Population & Species & Watterson's $\thetaSyn$ & $\proba[\SphyBen]$ & $\proba [ \SpopBen ]$ & $\frac{\proba[\SphyBen]}{\proba[ \SpopBen ]}$ & $\proba [ \SpopBen \given \SphyBen]$ & $\proba[\SphyBen\given \SpopBen ]$ \\
-            \midrule
-            \endhead
-            \midrule
-            \multicolumn{8}{r}{{Continued on next page}} \\
-            \midrule
-            \endfoot
-
-            \bottomrule
-            \endlastfoot
-            \rowcolor{LIGHTGREY} Equus c.
-&      Equus caballus &               $ 0.002$ &              $ 0.014$ &              $ 0.010$ &                                          $ 1.395$ &                         $ 0.580$ &                      $ 0.809$ \\
-            Iran &          Bos taurus &               $ 0.002$ &              $ 0.013$ &              $ 0.041$ &                                          $ 0.323$ &                         $ 0.857$ &                      $ 0.277$ \\
-            Uganda &          Bos taurus &               $ 0.005$ &              $ 0.013$ &              $ 0.013$ &                                          $ 0.991$ &                         $ 0.488$ &                      $ 0.483$ \\
-            \rowcolor{LIGHTGREY} Australia &        Capra hircus &               $ 0.003$ &              $ 0.014$ &              $ 0.026$ &                                          $ 0.532$ &                         $ 0.368$ &                      $ 0.196$ \\
-            \rowcolor{LIGHTGREY} France &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.572$ &                         $ 0.368$ &                      $ 0.211$ \\
-            \rowcolor{LIGHTGREY} Iran (C.
-aegagrus) &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.026$ &                                          $ 0.516$ &                         $ 0.221$ &                      $ 0.114$ \\
-            \rowcolor{LIGHTGREY} Iran &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.573$ &                         $ 0.368$ &                      $ 0.211$ \\
-            \rowcolor{LIGHTGREY} Italy &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.017$ &                                          $ 0.814$ &                         $ 0.270$ &                      $ 0.220$ \\
-            \rowcolor{LIGHTGREY} Morocco &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.018$ &                                          $ 0.751$ &                         $ 0.368$ &                      $ 0.276$ \\
-            Iran &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.006$ &                                          $ 2.321$ &                         $ 0.169$ &                      $ 0.392$ \\
-            Iran (O.
-orientalis) &          Ovis aries &               $ 0.009$ &              $ 0.014$ &              $ 0.012$ &                                          $ 1.178$ &                         $ 0.153$ &                      $ 0.180$ \\
-            Iran (O.
-vignei) &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.020$ &                                          $ 0.683$ &                         $ 0.195$ &                      $ 0.133$ \\
-            Various &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.012$ &                                          $ 1.201$ &                         $ 0.190$ &                      $ 0.228$ \\
-            Morocco &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.005$ &                                          $ 2.589$ &                         $ 0.136$ &                      $ 0.353$ \\
-            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.022$ &                                          $ 0.541$ &                         $ 0.565$ &                      $ 0.306$ \\
-            \rowcolor{LIGHTGREY} Central Afr.
-Rep.
-& Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.018$ &                                          $ 0.639$ &                         $ 0.429$ &                      $ 0.274$ \\
-            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.022$ &                                          $ 0.516$ &                         $ 0.462$ &                      $ 0.239$ \\
-            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.007$ &                                          $ 1.592$ &                         $ 0.486$ &                      $ 0.774$ \\
-            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.023$ &                                          $ 0.508$ &                         $ 0.478$ &                      $ 0.243$ \\
-            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus &               $ 0.003$ &              $ 0.012$ &              $ 0.015$ &                                          $ 0.762$ &                         $ 0.516$ &                      $ 0.393$ \\
-            \rowcolor{LIGHTGREY} South Africa  & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.016$ &                                          $ 0.734$ &                         $ 0.490$ &                      $ 0.360$ \\
-            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.016$ &                                          $ 0.713$ &                         $ 0.515$ &                      $ 0.367$ \\
-            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.023$ &                                          $ 0.500$ &                         $ 0.499$ &                      $ 0.249$ \\
-            African &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.025$ &                                          $ 0.470$ &                         $ 0.678$ &                      $ 0.319$ \\
-            Admixed American &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.021$ &                                          $ 0.569$ &                         $ 0.635$ &                      $ 0.361$ \\
-            East Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.031$ &                                          $ 0.381$ &                         $ 0.611$ &                      $ 0.233$ \\
-            European &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.034$ &                                          $ 0.350$ &                         $ 0.619$ &                      $ 0.217$ \\
-            South Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.033$ &                                          $ 0.354$ &                         $ 0.628$ &                      $ 0.222$ \\
-        \end{longtable*}
-    \end{center}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item $\proba [ \SphyBen ]$ (eq.~5) is the probability for a new mutation to be a beneficial back-mutation.
-        These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1, thus toward a more fit amino-acid.
-        \item $\proba [ \SpopBen ]$ (eq.~15) is the probability for a mutation to be beneficial.
-        These mutations have a selection coefficient at the population-scale larger than 1.
-        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale (the \textit{precision}).
-        \item $\proba [ \SphyBen \given \SpopBen]$ (eq.~14) is the probability for a mutation to a beneficial back-mutations, given it is beneficial at the population scale (the \textit{recall}).
-        This probability is obtained using Bayes' formula.
-    \end{itemize}
-    \newpage
-
-    \subsection{Replicability across mammals}
-    The proportion of deleterious ($\ProbaPopDel$), nearly-neutral ($\ProbaPopNeu$) and of beneficial ($\ProbaPopBen$) mutations estimated at the population-genetic scale across the different populations is shown for each class of selection ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$).
-
-    \captionof{figure}{Estimation of selection at the population scale for $\SphyDel$ mutations}
-    \begin{minipage}{0.9\linewidth}
-    \includegraphics[width=\linewidth, page=1]{artworks/Theta.neg.stacked.pdf}
-    \end{minipage}
-    \begin{minipage}{0.09\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
-    \end{minipage}
-
-    \captionof{figure}{Estimation of selection at the population scale for $\SphyNeu$ mutations}
-    \begin{minipage}{0.9\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/Theta.weak.stacked.pdf}
-    \end{minipage}
-    \begin{minipage}{0.09\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
-    \end{minipage}
-
-    \newpage
-    \captionof{figure}{Estimation of selection at the population scale for $\SphyBen$ mutations}
-    \begin{minipage}{0.9\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/Theta.pos.stacked.pdf}
-    \end{minipage}
-    \begin{minipage}{0.09\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
-    \end{minipage}
-
-    \subsection{Correlation with diversity}
-    For each population, the proportion of deleterious ($\ProbaPopDel$), nearly-neutral ($\ProbaPopNeu$) and of beneficial ($\ProbaPopBen$) mutations estimated at the population-genetic scale is shown as function of Watterson's's diversity ($\thetaSyn$).
-
-    \subsubsection{Proportion of deleterious mutations ($\SpopDel$)}\label{subsec:proportion-deleterious-mutations}
-    \captionof{figure}{Proportion of deleterious mutations ($\SpopDel$)}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.all_P-Sneg.scatter.pdf}
-    \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.neg_P-Sneg.scatter.pdf}
-    \end{minipage}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item $\proba [ \SpopDel ]$ (eq.~15) is the probability for a mutation to be deleterious.
-        These mutations have a selection coefficient at the population-scale lower than -1.
-        \item $\proba [ \SpopDel \given \SphyDel ]$ (eq.~12) is the probability for a mutation to be deleterious at the population scale, given it is predicted to be a deleterious at the phylogenetic scale.
-    \end{itemize}
-
-    We can see that higher synonymous diversity ($\thetaSyn$) is typically accompanied by a higher proportion of effectively deleterious mutations at the population scale ($\proba [ \SpopDel ]$).
-    This trend is also confirmed when we restricted the analysis to class of mutations that are supposedly deleterious at the phylogenetic scale ($\SphyDel$).
-    This result is qualitatively in accordance with the nearly-neutral theory of evolution which argues that very slightly deleterious mutations are more efficiently purified in large populations.
-
-    \subsubsection{Proportion of nearly-neutral mutations ($\SpopNeu$)}\label{subsec:proportion-nearly-neutral-mutations}
-    \captionof{figure}{Proportion of nearly-neutral mutations ($\SpopNeu$)}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.all_P-Sweak.scatter.pdf}
-    \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.weak_P-Sweak.scatter.pdf}
-    \end{minipage}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item $\proba [ \SpopNeu ]$ (eq.~15) is the probability for a mutation to be nearly-neutral.
-        These mutations have a selection coefficient at the population-scale between -1 and 1.
-        \item $\proba [ \SpopNeu \given \SphyNeu ]$ (eq.~12) is the probability for a mutation to be nearly-neutral at the population scale, given it is predicted to be a nearly-neutral at the phylogenetic scale.
-    \end{itemize}
-
-    We confirmed that higher synonymous diversity ($\thetaSyn$) is typically accompanied by a smaller proportion of neutral mutations at the population scale ($\proba [ \SpopNeu ]$ in the range 0.06-0.18).
-    This result is more pronounced ($\proba [ \SpopNeu \given \SphyNeu ]$ in the range 0.36-0.73) when we restricted the analysis to class of mutations that are supposedly nearly-neutral at the phylogenetic scale ($\SphyNeu$).
-    This result suggests that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) are more likely to discriminate whether mutations are beneficial or deleterious.
-    Alternatively stated, mutations in populations with low diversity (e.g.~\textit{Homo}) are effectively nearly-neutral and behave as would a neutral mutation.
-    This result is qualitatively in accordance with the nearly-neutral theory of evolution which argues that mutations are less efficiently selected for in small populations.
-
-    \subsubsection{Proportion of beneficial mutations ($\SpopBen$)}\label{subsec:proportion-beneficial-mutations}
-    \captionof{figure}{Proportion of beneficial mutations ($\SpopBen$)}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.all_P-Spos.scatter.pdf}
-    \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.pos_P-Spos.scatter.pdf}
-    \end{minipage}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item $\proba [ \SpopBen ]$ (eq.~15) is the probability for a mutation to be beneficial.
-        These mutations have a selection coefficient at the population-scale larger than 1.
-        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale (the \textit{precision}).
-    \end{itemize}
-    Higher synonymous diversity ($\thetaSyn$) is accompanied by a smaller proportion of beneficial mutations at the population scale ($\proba [ \SpopBen ]$).
-    This trend is also confirmed when we restricted the analysis to class of mutations that are supposedly beneficial back-mutations at the phylogenetic scale ($\SphyBen$).
-    This result is much more difficult to interpret.
-    The fraction of beneficial back mutations is supposed to depend on long term demographic history, which is not directly accessible.
-    If the long term effective population size is relatively similar to the short term one, we expect little opportunity for beneficial back-mutations.
-    And thus, counter-intuitively we expect a diminution of positively selected mutations.
-    However, we can see that the proportion of beneficial back-mutations among advantageous one does not decrease with synonymous diversity.
-    This means that somehow adaptive mutations also decrease with synonymous diversity for a reason we fail to explain.
+
+    \newpage
+    \subsection{Enrichment in $\SphyBen$ SNPs across all gene ontology terms}
+    Across all 347 gene ontology terms, the distribution of $p_{\mathrm{v}}$ is shown in the histogram below.
+    \begin{center}
+        \captionof{figure}{Enrichment in $\SphyBen$ SNPs across all gene ontology terms.}
+        \includegraphics[width=0.65\linewidth]{artworks/ontology_poly.Homo_sapiens.EUR.hist.pdf}
+    \end{center}
 
@@
     \section{Clinically related terms for mutations}
+
     \subsection{Terms associated with deleterious mutations $\SphyDel$}
     \begin{center}
-        \captionof{table}{Terms associated with deleterious mutations $\SphyDel$}
+        \captionof{table}{Terms associated with deleterious mutations $\SphyDel$.}
         \begin{tabular}{|l|r|r|r|r|r|}
@@
     \end{center}
-    In humans, non-synonymous SNPs in the test group ($\SphyDel$) are contrasted to SNPs in the control group ($\SphyNeu$).
+    In humans (european population), non-synonymous SNPs in the test group ($\SphyDel$) are contrasted to SNPs in the control group ($\SphyNeu$).
     For each clinical term, a 2x2 contingency tables is built by counting the number of SNPs based on their selection coefficient and their clinical terms (whether they have this specific term or not).
@@
     $^*$ for $p_{\mathrm{v}}^{\mathrm{adj}}$ corrected for multiple comparison (Holm–Bonferroni correction) lower than the risk $\alpha=0.05$.
-    Beneficial back-mutations are associated with clinical terms such as \textit{Benign} and \textit{Likely Benign}.
-    \newpage
-
-    \section{Including divergence data for the estimation of $\Spop$}
-
-    \subsection{Including divergence in polyDFE}
-    Divergence data (number of substitutions per site) can also be included into polyDFE to estimate the DFE.
-    For the class of a given class of selection coefficient ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$), the number of substitutions has already been computed and is given by $D\left( \Sphyclass \right)$ (see eq.~6), and the number of sites is given by $L \left( \Sphyclass \right)$ (see eq.~4).
-    Otherwise, the procedure is the same as described section \textit{Scaled selection coefficients ($\Spop$) in a population-based method}.
-
-    \subsection{Probabilities of beneficial back-mutations}
-    \begin{center}
-        \captionof{table}{Probability of beneficial back-mutations among all beneficial ones.}
+    Beneficial non-adaptive mutations are associated with clinical terms such as \textit{Benign} and \textit{Likely Benign}.
+    \newpage
+
+    \section{Correlation with diversity}
+
+    \subsection{Phylogenetic Generalized Linear Model}
+
+    Because a correlation must account for phylogenetic relationship and non-independence of samples, we fitted a Phylogenetic Generalized Linear Model (PGLM) in R with the package caper\cite{orme_caper_2013}, with multi-furcation of the different populations inside each species.
+    The mammalian tree imported from TimeTree\cite{kumar_timetree_2017} and pruned to the species used in this study is, in newick format:
+
+    \lstinputlisting[breaklines]{artworks/PGLM.tree}
+
+    And shown in the figure below:
+    \begin{center}
+        \captionof{figure}{Tree used for PGLM (Phylogenetic Generalized Linear Model).}
+        \includegraphics[width=0.65\linewidth, page=1]{artworks/PGLM.pdf}
+    \end{center}
+
+    Multifurcations of the different populations are placed at the same divergence time as the species.
+    Then, for each population, the proportion of deleterious ($\ProbaPopDel$), nearly-neutral ($\ProbaPopNeu$) and of beneficial ($\ProbaPopBen$) mutations estimated at the population-genetic scale is shown as function of $\Ne$.
+    $r^2$ and p-value are obtained from the PGLM model.
+
+    \newpage
+    \subsubsection{Proportion of deleterious mutations ($\SpopDel$)}\label{subsec:proportion-deleterious-mutations}
+    \captionof{figure}{Proportion of deleterious mutations ($\SpopDel$).}
+    \begin{minipage}{0.49\linewidth}
+        \includegraphics[width=\linewidth, page=1]{artworks/results.pop_size.all_P-Sneg.scatter.pdf}
+    \end{minipage}
+    \begin{minipage}{0.49\linewidth}
+        \includegraphics[width=\linewidth, page=1]{artworks/results.pop_size.neg_P-Sneg.scatter.pdf}
+    \end{minipage}
+    \begin{itemize}
+        \item $\Ne$ is the estimated effective population size.
+        \item $\proba [ \SpopDel ]$ (eq.~15) is the probability for a mutation to be deleterious.
+        These mutations have a selection coefficient at the population-scale lower than -1.
+        \item $\proba [ \SpopDel \given \SphyDel ]$ (eq.~12) is the probability for a mutation to be deleterious at the population scale, given it is predicted to be a deleterious at the phylogenetic scale.
+    \end{itemize}
+
+    We can see that higher effective population size ($\Ne$) is typically accompanied by a higher proportion of effectively deleterious mutations at the population scale ($\proba [ \SpopDel ]$).
+    This trend is also confirmed when we restricted the analysis to class of mutations that are supposedly deleterious at the phylogenetic scale ($\SphyDel$).
+    This result is qualitatively in accordance with the nearly-neutral theory of evolution which argues that very slightly deleterious mutations are more efficiently purified in large populations.
+
+    \newpage
+    \subsubsection{Proportion of nearly-neutral mutations ($\SpopNeu$)}\label{subsec:proportion-nearly-neutral-mutations}
+    \captionof{figure}{Proportion of nearly-neutral mutations ($\SpopNeu$).}
+    \begin{minipage}{0.49\linewidth}
+        \includegraphics[width=\linewidth, page=1]{artworks/results.pop_size.all_P-Sweak.scatter.pdf}
+    \end{minipage}
+    \begin{minipage}{0.49\linewidth}
+        \includegraphics[width=\linewidth, page=1]{artworks/results.pop_size.weak_P-Sweak.scatter.pdf}
+    \end{minipage}
+    \begin{itemize}
+        \item $\Ne$ is the estimated effective population size.
+        \item $\proba [ \SpopNeu ]$ (eq.~15) is the probability for a mutation to be nearly-neutral.
+        These mutations have a selection coefficient at the population-scale between -1 and 1.
+        \item $\proba [ \SpopNeu \given \SphyNeu ]$ (eq.~12) is the probability for a mutation to be nearly-neutral at the population scale, given it is predicted to be a nearly-neutral at the phylogenetic scale.
+    \end{itemize}
+
+    We confirmed that higher effective population size ($\Ne$) is typically accompanied by a smaller proportion of neutral mutations at the population scale ($\proba [ \SpopNeu ]$ in the range 0.06-0.18).
+    This result is more pronounced ($\proba [ \SpopNeu \given \SphyNeu ]$ in the range 0.36-0.73) when we restricted the analysis to class of mutations that are supposedly nearly-neutral at the phylogenetic scale ($\SphyNeu$).
+    This result suggests that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) are more likely to discriminate whether mutations are beneficial or deleterious.
+    Alternatively stated, mutations in populations with low diversity (e.g.~\textit{Homo}) are effectively nearly-neutral and behave as a neutral mutation would.
+    This result is qualitatively in accordance with the nearly-neutral theory of evolution which argues that mutations are less efficiently selected for in small populations.
+
+    \newpage
+    \subsubsection{Proportion of beneficial mutations ($\SpopBen$)}\label{subsec:proportion-beneficial-mutations}
+    \captionof{figure}{Proportion of beneficial mutations ($\SpopBen$).}
+    \begin{minipage}{0.49\linewidth}
+        \includegraphics[width=\linewidth, page=1]{artworks/results.pop_size.all_P-Spos.scatter.pdf}
+    \end{minipage}
+    \begin{minipage}{0.49\linewidth}
+        \includegraphics[width=\linewidth, page=1]{artworks/results.pop_size.pos_P-Spos.scatter.pdf}
+    \end{minipage}
+    \begin{itemize}
+        \item $\Ne$ is the estimated effective population size.
+        \item $\proba [ \SpopBen ]$ (eq.~15) is the probability for a mutation to be beneficial.
+        These mutations have a selection coefficient at the population-scale larger than 1.
+        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a non-adaptive beneficial mutation at the phylogenetic scale (the \textit{precision}).
+    \end{itemize}
+    Higher effective population size ($\Ne$) is accompanied by a smaller proportion of beneficial mutations at the population scale ($\proba [ \SpopBen ]$).
+    This trend is also confirmed when we restricted the analysis to class of mutations that are supposedly non-adaptive beneficial mutations at the phylogenetic scale ($\SphyBen$).
+
+    \newpage
+
+    \section{Probability for beneficial mutations to be non-adaptive ($\proba[\SphyBen\given \SpopBen ]$)}
+
+    \subsection{Across the different populations}
+    \begin{center}
+        \captionof{table}{Probability for beneficial mutations to be non-adaptive ($\proba[\SphyBen\given \SpopBen ]$).}
         \scriptsize
@@
             \toprule
-            Population & Species & Watterson's $\thetaSyn$ & $\proba[\SphyBen]$ & $\proba [ \SpopBen ]$ & $\frac{\proba[\SphyBen]}{\proba[ \SpopBen ]}$ & $\proba [ \SpopBen \given \SphyBen]$ & $\proba[\SphyBen\given \SpopBen ]$ \\
+            Population & Species & $N_e$ & $\proba[\SphyBen]$ & $\proba [ \SpopBen ]$ & $\frac{\proba[\SphyBen]}{\proba[ \SpopBen ]}$ & $\proba [ \SpopBen \given \SphyBen]$ & $\proba[\SphyBen\given \SpopBen ]$ \\
             \midrule
@@
             \endfoot
-
             \bottomrule
             \endlastfoot
-            \rowcolor{LIGHTGREY} Equus c.
-&      Equus caballus &               $ 0.002$ &              $ 0.014$ &              $ 0.061$ &                                          $ 0.235$ &                         $ 0.519$ &                      $ 0.122$ \\
-            Iran &          Bos taurus &               $ 0.002$ &              $ 0.013$ &              $ 0.007$ &                                          $ 1.908$ &                         $ 0.368$ &                      $ 0.702$ \\
-            Uganda &          Bos taurus &               $ 0.005$ &              $ 0.013$ &              $ 0.008$ &                                          $ 1.667$ &                         $ 0.255$ &                      $ 0.425$ \\
-            \rowcolor{LIGHTGREY} Australia &        Capra hircus &               $ 0.003$ &              $ 0.014$ &              $ 0.007$ &                                          $ 2.099$ &                         $ 0.147$ &                      $ 0.308$ \\
-            \rowcolor{LIGHTGREY} France &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.007$ &                                          $ 2.043$ &                         $ 0.149$ &                      $ 0.304$ \\
-            \rowcolor{LIGHTGREY} Iran (C.
-aegagrus) &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.013$ &                                          $ 1.069$ &                         $ 0.147$ &                      $ 0.157$ \\
-            \rowcolor{LIGHTGREY} Iran &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.008$ &                                          $ 1.699$ &                         $ 0.152$ &                      $ 0.258$ \\
-            \rowcolor{LIGHTGREY} Italy &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.006$ &                                          $ 2.160$ &                         $ 0.147$ &                      $ 0.316$ \\
-            \rowcolor{LIGHTGREY} Morocco &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.006$ &                                          $ 2.141$ &                         $ 0.186$ &                      $ 0.398$ \\
-            Iran &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.012$ &                                          $ 1.210$ &                         $ 0.158$ &                      $ 0.191$ \\
-            Iran (O.
-orientalis) &          Ovis aries &               $ 0.009$ &              $ 0.014$ &              $ 0.012$ &                                          $ 1.144$ &                         $ 0.157$ &                      $ 0.180$ \\
-            Iran (O.
-vignei) &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.022$ &                                          $ 0.631$ &                         $ 0.186$ &                      $ 0.118$ \\
-            Various &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.012$ &                                          $ 1.211$ &                         $ 0.156$ &                      $ 0.188$ \\
-            Morocco &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.009$ &                                          $ 1.536$ &                         $ 0.190$ &                      $ 0.292$ \\
-            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.005$ &                                          $ 2.230$ &                         $ 0.282$ &                      $ 0.630$ \\
-            \rowcolor{LIGHTGREY} Central Afr.
-Rep.
-& Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.014$ &                                          $ 0.849$ &                         $ 0.310$ &                      $ 0.263$ \\
-            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.008$ &                                          $ 1.530$ &                         $ 0.298$ &                      $ 0.456$ \\
-            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.008$ &                                          $ 1.384$ &                         $ 0.305$ &                      $ 0.422$ \\
-            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.014$ &                                          $ 0.854$ &                         $ 0.296$ &                      $ 0.253$ \\
-            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus &               $ 0.003$ &              $ 0.012$ &              $ 0.005$ &                                          $ 2.438$ &                         $ 0.285$ &                      $ 0.696$ \\
-            \rowcolor{LIGHTGREY} South Africa  & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.011$ &                                          $ 1.047$ &                         $ 0.323$ &                      $ 0.338$ \\
-            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.006$ &                                          $ 2.070$ &                         $ 0.292$ &                      $ 0.604$ \\
-            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.014$ &                                          $ 0.816$ &                         $ 0.309$ &                      $ 0.252$ \\
-            African &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.015$ &                                          $ 0.765$ &                         $ 0.371$ &                      $ 0.284$ \\
-            Admixed American &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.009$ &                                          $ 1.259$ &                         $ 0.368$ &                      $ 0.464$ \\
-            East Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.012$ &                                          $ 0.973$ &                         $ 0.369$ &                      $ 0.358$ \\
-            European &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.009$ &                                          $ 1.356$ &                         $ 0.368$ &                      $ 0.499$ \\
-            South Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.010$ &                                          $ 1.147$ &                         $ 0.369$ &                      $ 0.423$ \\
+            \rowcolor{LIGHTGREY} Equus c. & Equus caballus & $7.5\times 10^{4}$ & $ 0.012$ & $ 0.015$ & $ 0.827$ & $ 0.648$ & $ 0.536$ \\
+            Iran & Bos taurus & $5.6\times 10^{4}$ & $ 0.011$ & $ 0.039$ & $ 0.279$ & $ 0.873$ & $ 0.243$ \\
+            Uganda & Bos taurus & $1.3\times 10^{5}$ & $ 0.011$ & $ 0.015$ & $ 0.720$ & $ 0.576$ & $ 0.415$ \\
+            \rowcolor{LIGHTGREY} Australia & Capra hircus & $1.7\times 10^{5}$ & $ 0.011$ & $ 0.023$ & $ 0.480$ & $ 0.368$ & $ 0.177$ \\
+            \rowcolor{LIGHTGREY} France & Capra hircus & $1.9\times 10^{5}$ & $ 0.011$ & $ 0.022$ & $ 0.515$ & $ 0.368$ & $ 0.190$ \\
+            \rowcolor{LIGHTGREY} Iran (C. aegagrus) & Capra hircus & $1.9\times 10^{5}$ & $ 0.011$ & $ 0.025$ & $ 0.448$ & $ 0.368$ & $ 0.165$ \\
+            \rowcolor{LIGHTGREY} Iran & Capra hircus & $2.3\times 10^{5}$ & $ 0.011$ & $ 0.021$ & $ 0.525$ & $ 0.368$ & $ 0.193$ \\
+            \rowcolor{LIGHTGREY} Italy & Capra hircus & $1.9\times 10^{5}$ & $ 0.011$ & $ 0.017$ & $ 0.660$ & $ 0.368$ & $ 0.243$ \\
+            \rowcolor{LIGHTGREY} Morocco & Capra hircus & $2.2\times 10^{5}$ & $ 0.011$ & $ 0.017$ & $ 0.667$ & $ 0.368$ & $ 0.245$ \\
+            Iran & Ovis aries & $3.8\times 10^{5}$ & $ 0.012$ & $ 0.006$ & $ 1.984$ & $ 0.205$ & $ 0.407$ \\
+            Iran (O. orientalis) & Ovis aries & $4.5\times 10^{5}$ & $ 0.011$ & $ 0.012$ & $ 0.983$ & $ 0.193$ & $ 0.190$ \\
+            Iran (O. vignei) & Ovis aries & $3.7\times 10^{5}$ & $ 0.012$ & $ 0.020$ & $ 0.579$ & $ 0.190$ & $ 0.110$ \\
+            Various & Ovis aries & $4.1\times 10^{5}$ & $ 0.011$ & $ 0.012$ & $ 0.967$ & $ 0.229$ & $ 0.222$ \\
+            Morocco & Ovis aries & $ 4\times 10^{5}$ & $ 0.012$ & $ 0.005$ & $ 2.435$ & $ 0.211$ & $ 0.514$ \\
+            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus & $1.1\times 10^{5}$ & $ 0.009$ & $ 0.021$ & $ 0.452$ & $ 0.648$ & $ 0.293$ \\
+            \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus & $1.7\times 10^{5}$ & $ 0.009$ & $ 0.018$ & $ 0.515$ & $ 0.535$ & $ 0.275$ \\
+            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus & $1.4\times 10^{5}$ & $ 0.009$ & $ 0.021$ & $ 0.444$ & $ 0.552$ & $ 0.245$ \\
+            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus & $1.4\times 10^{5}$ & $ 0.009$ & $ 0.007$ & $ 1.423$ & $ 0.577$ & $ 0.821$ \\
+            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus & $1.5\times 10^{5}$ & $ 0.009$ & $ 0.022$ & $ 0.437$ & $ 0.588$ & $ 0.257$ \\
+            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus & $ 1\times 10^{5}$ & $ 0.009$ & $ 0.016$ & $ 0.597$ & $ 0.599$ & $ 0.358$ \\
+            \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus & $1.8\times 10^{5}$ & $ 0.009$ & $ 0.016$ & $ 0.594$ & $ 0.574$ & $ 0.341$ \\
+            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus & $1.2\times 10^{5}$ & $ 0.009$ & $ 0.017$ & $ 0.563$ & $ 0.598$ & $ 0.336$ \\
+            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus & $1.7\times 10^{5}$ & $ 0.009$ & $ 0.022$ & $ 0.427$ & $ 0.585$ & $ 0.250$ \\
+            African & Homo sapiens & $5.6\times 10^{4}$ & $ 0.010$ & $ 0.020$ & $ 0.484$ & $ 0.721$ & $ 0.349$ \\
+            Admixed American & Homo sapiens & $4.5\times 10^{4}$ & $ 0.010$ & $ 0.019$ & $ 0.500$ & $ 0.690$ & $ 0.345$ \\
+            East Asian & Homo sapiens & $ 4\times 10^{4}$ & $ 0.010$ & $ 0.027$ & $ 0.362$ & $ 0.688$ & $ 0.249$ \\
+            European & Homo sapiens & $4.2\times 10^{4}$ & $ 0.010$ & $ 0.027$ & $ 0.361$ & $ 0.688$ & $ 0.248$ \\
+            South Asian & Homo sapiens & $4.4\times 10^{4}$ & $ 0.010$ & $ 0.030$ & $ 0.324$ & $ 0.691$ & $ 0.224$ \\
         \end{longtable*}
@@
     \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item $\proba [ \SphyBen ]$ (eq.~5) is the probability for a new mutation a beneficial back-mutation.
+        \item $\Ne$ is the estimated effective population size.
+        \item $\proba [ \SphyBen ]$ (eq.~5) is the probability for a new mutation to be a non-adaptive beneficial mutation.
         These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1, thus toward a more fit amino-acid.
@@
         These mutations have a selection coefficient at the population-scale larger than 1.
-        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale (the \textit{precision}).
-        \item $\proba [ \SphyBen \given \SpopBen]$ (eq.~14) is the probability for a mutation to a beneficial back-mutations, given it is beneficial (the \textit{recall}).
+        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given that it is predicted to be a non-adaptive beneficial mutation at the phylogenetic scale (the \textit{precision}).
+        \item $\proba [ \SphyBen \given \SpopBen]$ (eq.~14) is the probability for a mutation to be non-adaptive given that it is beneficial at the population scale (the \textit{recall}).
         This probability is obtained using Bayes' formula.
     \end{itemize}
+
+    \newpage
+    \subsection{Misannotations of ancestral alleles}
+
+    A potential caveat of our method to is that if a deleterious derived allele segregates at low frequency but is wrongly annotated as ancestral, it will result in a SNP that will be both predicted as advantageous and segregating at high frequency, wrongly suggesting that this variant is correctly inferred as beneficial.
+    In this context misannotations of ancestral alleles could inflate our estimation of the proportion of beneficial non-adaptive mutations.
+    However, we show that this problem impacts our estimation in two ways, albeit, only slightly. \\
+
+    First, if misannotation is influencing the recall for $\SphyBen$ ($\proba[\SphyBen\given \SpopBen ]$), then the recall should increase as a function of  divergence to the sister species ($\ds$: number of synonymous substitutions per sites) since divergence would increase the rate of misannotations.
+    Shown below is recall $\proba[\SphyBen\given \SpopBen ]$ as a function of divergence ($\ds$) in which the latter is not an explanatory variable.
+
+    \begin{center}
+        \captionof{figure}{$\proba[\SphyBen\given \SpopBen ]$ as a function of distance to the sister species.}
+        \includegraphics[width=0.75\linewidth, page=1]{artworks/results.distance.recall_pos.scatter.pdf}
+    \end{center}
+
+    \newpage
+
+    Second, the distribution of selection coefficients ($\Sphy$) that we observed for segregating mutations and for divergence also suggests that we effectively controlled for misannotations.
+    Under a scenario where beneficial non-adaptive mutations would only be the result of misannotations, one would expect that the positive part of the fitness effects (i.e.
+$\proba[\Sphy]$) of observed polymorphism currently segregating in the population should reflect the negative one (i.e.
+$\proba[-\Sphy]$).
+    Indeed, the number of misannotated beneficial mutations should be proportional to the number of deleterious mutations with the same selection coefficient.
+    The ratio between advantageous and deleterious polymorphisms of the same selection coefficient should therefore be a constant that represents the rate of misannotation (typically influenced by the distance to the sister species).
+    However, this is not what we observe in the DFE of polymorphisms (shown below in the African population of \textit{Homo sapiens}) thus giving us the confidence that misannotations are not common.
+
+    \begin{center}
+        \captionof{figure}{Ratio of $\proba[\Sphy]$ over $\proba[-\Sphy]$ for polymorphisms of the African population of \textit{Homo sapiens}.}
+        \includegraphics[width=0.75\linewidth, page=1]{artworks/poly.Homo_sapiens.AFR.folded_ratio.pdf}
+    \end{center}
+
+    Overall, the observed DFE of substitution is much better explained by the expected DFE of new mutations (section S\ref{subsec:expectedDFE} than by mispolarizations).
+
+    \newpage
+    \section{Excluding genes under adaptation}
+
+    \subsection{Probability for beneficial mutations to be non-adaptive}
+    \begin{center}
+        \captionof{table}{$\proba[\SphyBen\given \SpopBen ]$ excluding or not genes under adaptation.}
+        \begin{tabular}{|l|l|r|r|}
+            \toprule
+            Population & Species & Control & Case \\
+            \midrule
+            \rowcolor{LIGHTGREY} Equus c. & Equus caballus & $ 0.536$ & $ 0.880$ \\
+            Iran & Bos taurus & $ 0.243$ & $ 0.249$ \\
+            Uganda & Bos taurus & $ 0.415$ & $ 0.429$ \\
+            \rowcolor{LIGHTGREY} Australia & Capra hircus & $ 0.177$ & $ 0.190$ \\
+            \rowcolor{LIGHTGREY} France & Capra hircus & $ 0.190$ & $ 0.201$ \\
+            \rowcolor{LIGHTGREY} Iran (C. aegagrus) & Capra hircus & $ 0.165$ & $ 0.169$ \\
+            \rowcolor{LIGHTGREY} Iran & Capra hircus & $ 0.193$ & $ 0.176$ \\
+            \rowcolor{LIGHTGREY} Italy & Capra hircus & $ 0.243$ & $ 0.261$ \\
+            \rowcolor{LIGHTGREY} Morocco & Capra hircus & $ 0.245$ & $ 0.283$ \\
+            \rowcolor{LIGHTGREY} Iran & Ovis aries & $ 0.407$ & $ 0.454$ \\
+            Iran (O. orientalis) & Ovis aries & $ 0.190$ & $ 0.207$ \\
+            Iran (O. vignei) & Ovis aries & $ 0.110$ & $ 0.135$ \\
+            Various & Ovis aries & $ 0.222$ & $ 0.246$ \\
+            Morocco & Ovis aries & $ 0.514$ & $ 0.627$ \\
+            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus & $ 0.293$ & $ 0.325$ \\
+            \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus & $ 0.275$ & $ 0.273$ \\
+            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus & $ 0.245$ & $ 0.242$ \\
+            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus & $ 0.821$ & $ 0.873$ \\
+            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus & $ 0.257$ & $ 0.254$ \\
+            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus & $ 0.358$ & $ 0.395$ \\
+            \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus & $ 0.341$ & $ 0.375$ \\
+            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus & $ 0.336$ & $ 0.355$ \\
+            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus & $ 0.250$ & $ 0.263$ \\
+            African & Homo sapiens & $ 0.349$ & $ 0.363$ \\
+            Admixed American & Homo sapiens & $ 0.345$ & $ 0.312$ \\
+            East Asian & Homo sapiens & $ 0.249$ & $ 0.233$ \\
+            European & Homo sapiens & $ 0.248$ & $ 0.211$ \\
+            South Asian & Homo sapiens & $ 0.224$ & $ 0.218$ \\
+            \bottomrule
+        \end{tabular}
+    \end{center}
+    Genes under adaptation retrieved from \textcite{latrille_genes_2023}.
+    Comparison of $\proba[\SphyBen\given \SpopBen ]$ for the whole genome (control) and when excluding genes under adaptation (case).
+    The non-parametric Wilcoxon signed-rank test evaluates the null hypothesis that the distribution of the differences (case versus control) is symmetric about zero.
+    Applied to the paired samples (case and control), Wilcoxon signed-rank test results in $s=80$ with $\pvalue=0.002$, for the one-sided test (case higher than control).
+    The proportion of non-adaptive beneficial mutations ($\proba[\SphyBen\given \SpopBen ]$) is higher when excluding genes under adaptation, consistent with our expectation that genes with uniformly conserved functions should fit better the nearly-neutral equilibrium model.
+
+    \newpage
+
+    \section{Contrasting selection at the phylogenetic and population-genetic scale}
+
+    \subsection{Selection at the population-genetic scale}
+    The proportion of deleterious ($\ProbaPopDel$), nearly-neutral ($\ProbaPopNeu$) and of beneficial ($\ProbaPopBen$) mutations estimated at the population-genetic scale across the different populations is shown for each class of selection ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$).
+
+    \captionof{figure}{Estimation of selection at the population scale for $\SphyDel$ mutations.}
+    \begin{center}
+        \begin{minipage}{0.75\linewidth}
+            \begin{minipage}{0.9\linewidth}
+                \includegraphics[width=\linewidth, page=1]{artworks/Theta.neg.stacked.pdf}
+            \end{minipage}
+            \begin{minipage}{0.09\linewidth}
+                \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
+            \end{minipage}
+        \end{minipage}
+    \end{center}
+
+    \captionof{figure}{Estimation of selection at the population scale for $\SphyNeu$ mutations.}
+    \begin{center}
+        \begin{minipage}{0.75\linewidth}
+            \begin{minipage}{0.9\linewidth}
+                \includegraphics[width=\linewidth, page=1]{artworks/Theta.weak.stacked.pdf}
+            \end{minipage}
+            \begin{minipage}{0.09\linewidth}
+                \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
+            \end{minipage}
+        \end{minipage}
+    \end{center}
+
+    \captionof{figure}{Estimation of selection at the population scale for $\SphyBen$ mutations.}
+    \begin{center}
+        \begin{minipage}{0.75\linewidth}
+            \begin{minipage}{0.9\linewidth}
+                \includegraphics[width=\linewidth, page=1]{artworks/Theta.pos.stacked.pdf}
+            \end{minipage}
+            \begin{minipage}{0.09\linewidth}
+                \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
+            \end{minipage}
+        \end{minipage}
+    \end{center}
+
+    \newpage
+    \subsection{Distribution of scaled selection coefficients ($\Sphy$)}\label{subsec:expectedDFE}
+
+    Theoretically, the selection coefficient ($\Sphy$) for any mutation is related to its probability of fixation by the equation $\proba_{\text{fix}} (\Sphy) = \Sphy/(1-\exp(-\Sphy)) $.
+    It is thus possible to predict the distribution of $\Sphy$ of substitutions given the distribution of $\Sphy$ for mutations (e.g.
+panel A below) by weighting the different mutations by their $\proba_{\text{fix}} (\Sphy)$.
+    The predicted DFE of substitutions (panel B below) matches the observed DFE of substitutions (panel C below) in the terminal lineage, meaning that the $\Sphy$ obtained by phylogenetic mutation-selection codon models is a strong predictor of selection effectively exerted on mutations in terminal lineages.
+
+    The figures shown below are obtained in the Saint Kitts population of \textit{Chlorocebus sabaeus}.
+    These figures across the 28 populations are available at Zenodo (\url{https://doi.org/10.5281/zenodo.7878953}) in file \textit{distribution\_S0\_28\_populations.pdf}.\\
+
+    \captionof{figure}{Distribution of scaled selection coefficients ($\Sphy$).}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny A: Expected DFE for mutations}
+        \includegraphics[width=\linewidth, page=1]{artworks/DFE.Chlorocebus_sabaeus.Saint_Kitts.MutSel.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny B: Expected DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{artworks/DFE.Chlorocebus_sabaeus.Saint_Kitts.MutSel.Flow.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny C: Observed DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{artworks/subs.Chlorocebus_sabaeus.Saint_Kitts.bins3Mask0.9.pdf}
+    \end{minipage}
+    \\
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny D: Observed DFE for polymorphisms}
+        \includegraphics[width=\linewidth, page=1]{artworks/poly.Chlorocebus_sabaeus.Saint_Kitts.bins3Mask0.9.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny E: Site frequency spectrum}
+        \includegraphics[width=\linewidth, page=1]{artworks/Chlorocebus_sabaeus.Saint_Kitts.MutSel-sfs.normalize.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
+        \includegraphics[width=\linewidth, page=1]{artworks/Chlorocebus_sabaeus.Saint_Kitts.MutSel.polyDFE_C.pdf}
+    \end{minipage}
+
+    \small
+    \begin{itemize}[itemsep=0pt]
+        \item A: Distribution of scaled selection coefficients ($\Sphy$), predicted for all possible non-synonymous DNA mutations away from the ancestral exome.
+        Mutations are divided into three classes of selection: deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial non-adaptive ($\SphyBen$).
+        \item B: Expected distribution of $\Sphy$ for substitutions obtained by transforming the distribution of $\Sphy$ for mutations (panel A) by weighting each mutation by its scaled probability of fixation given by $\proba_{\text{fix}} (\Sphy) = \Sphy/(1-\exp(-\Sphy))$.
+        \item C: Distribution of scaled selection coefficients ($\Sphy$) for all observed substitutions along the terminal branch of the phylogenetic tree.
+        \item D: Distribution of scaled selection coefficients ($\Sphy$) for all observed polymorphisms currently segregating in the population.
+        \item E: The site-frequency spectrum (SFS) in the population for a random sample of 16 alleles (means in solid lines and standard deviations in color shades) for each class of selection and for synonymous mutations, supposedly neutral (black).
+The SFS represents the proportion of mutations (y-axis) with a given number of derived alleles in the population (x-axis).
+At high frequencies, deleterious mutations are underrepresented.
+        \item F: Proportion of beneficial $\ProbaPopDel$, nearly-neutral $\ProbaPopNeu$, and deleterious mutations $\ProbaPopBen$  estimated at the population scale for each class of selection at the phylogenetic scale.
+Proportions depicted here are not weighted by their mutational opportunities.
+    \end{itemize}
+    \normalsize
+
+    \section{Filtering of variable sites}
+
+    \subsection{Masking CpG transitions}
+    We also tested our prediction while masking CpG transitions since the mutation rate of CpG dinucleotides is higher than the mutation rate of other dinucleotides, which can affect the estimation of the DFE.
+    Any nucleotide transition including a CpG dinucleotide either in the ancestral or derived state is considered as a CpG transition.
+    We masked all CpG transitions in the mutational opportunities, the substitutions in the terminal branches, and the polymorphisms segregating in the population.
+We then re-estimated the DFE and the proportion of non-adaptive beneficial mutations.
+
+    \subsection{Probability for beneficial mutations to be non-adaptive}
+    \begin{center}
+        \captionof{table}{$\proba[\SphyBen\given \SpopBen ]$ while masking CpG transitions.}
+        \scriptsize
+        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
+            \toprule
+            Population & Species & $\Ne$ & $\proba[\SphyBen]$ & $\proba [ \SpopBen ]$ & $\frac{\proba[\SphyBen]}{\proba[ \SpopBen ]}$ & $\proba [ \SpopBen \given \SphyBen]$ & $\proba[\SphyBen\given \SpopBen ]$ \\
+            \midrule
+            \endhead
+            \midrule
+            \multicolumn{8}{r}{{Continued on next page}} \\
+            \midrule
+            \endfoot
+
+            \bottomrule
+            \endlastfoot
+            \rowcolor{LIGHTGREY} Equus c. & Equus caballus & $7.5\times 10^{4}$ & $ 0.012$ & $ 0.028$ & $ 0.421$ & $ 0.543$ & $ 0.229$ \\
+            Iran & Bos taurus & $5.6\times 10^{4}$ & $ 0.011$ & $ 0.038$ & $ 0.283$ & $ 0.797$ & $ 0.226$ \\
+            Uganda & Bos taurus & $1.3\times 10^{5}$ & $ 0.011$ & $ 0.022$ & $ 0.479$ & $ 0.406$ & $ 0.195$ \\
+            \rowcolor{LIGHTGREY} Australia & Capra hircus & $1.7\times 10^{5}$ & $ 0.011$ & $ 0.024$ & $ 0.454$ & $ 0.158$ & $ 0.072$ \\
+            \rowcolor{LIGHTGREY} France & Capra hircus & $1.9\times 10^{5}$ & $ 0.011$ & $ 0.034$ & $ 0.320$ & $ 0.258$ & $ 0.082$ \\
+            \rowcolor{LIGHTGREY} Iran (C. aegagrus) & Capra hircus & $1.9\times 10^{5}$ & $ 0.011$ & $ 0.032$ & $ 0.341$ & $ 0.268$ & $ 0.091$ \\
+            \rowcolor{LIGHTGREY} Iran & Capra hircus & $2.3\times 10^{5}$ & $ 0.011$ & $ 0.026$ & $ 0.417$ & $ 0.294$ & $ 0.123$ \\
+            \rowcolor{LIGHTGREY} Italy & Capra hircus & $1.9\times 10^{5}$ & $ 0.011$ & $ 0.023$ & $ 0.472$ & $ 0.100$ & $ 0.047$ \\
+            \rowcolor{LIGHTGREY} Morocco & Capra hircus & $2.2\times 10^{5}$ & $ 0.011$ & $ 0.018$ & $ 0.593$ & $ 0.141$ & $ 0.083$ \\
+            Iran & Ovis aries & $3.8\times 10^{5}$ & $ 0.011$ & $ 0.012$ & $ 0.981$ & $ 0.243$ & $ 0.239$ \\
+            Iran (O. orientalis) & Ovis aries & $4.5\times 10^{5}$ & $ 0.011$ & $ 0.019$ & $ 0.603$ & $ 0.155$ & $ 0.093$ \\
+            Iran (O. vignei) & Ovis aries & $3.7\times 10^{5}$ & $ 0.011$ & $ 0.025$ & $ 0.445$ & $ 0.252$ & $ 0.112$ \\
+            Various & Ovis aries & $4.1\times 10^{5}$ & $ 0.011$ & $ 0.016$ & $ 0.704$ & $ 0.198$ & $ 0.139$ \\
+            Morocco & Ovis aries & $ 4\times 10^{5}$ & $ 0.011$ & $ 0.008$ & $ 1.389$ & $ 0.165$ & $ 0.229$ \\
+            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus & $1.1\times 10^{5}$ & $ 0.009$ & $ 0.013$ & $ 0.752$ & $ 0.231$ & $ 0.174$ \\
+            \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus & $1.7\times 10^{5}$ & $ 0.009$ & $ 0.018$ & $ 0.519$ & $ 0.209$ & $ 0.108$ \\
+            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus & $1.4\times 10^{5}$ & $ 0.009$ & $ 0.025$ & $ 0.385$ & $ 0.241$ & $ 0.093$ \\
+            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus & $1.4\times 10^{5}$ & $ 0.009$ & $ 0.007$ & $ 1.346$ & $ 0.204$ & $ 0.275$ \\
+            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus & $1.5\times 10^{5}$ & $ 0.009$ & $ 0.021$ & $ 0.443$ & $ 0.239$ & $ 0.106$ \\
+            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus & $ 1\times 10^{5}$ & $ 0.009$ & $ 0.014$ & $ 0.690$ & $ 0.146$ & $ 0.101$ \\
+            \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus & $1.8\times 10^{5}$ & $ 0.009$ & $ 0.019$ & $ 0.498$ & $ 0.272$ & $ 0.135$ \\
+            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus & $1.2\times 10^{5}$ & $ 0.009$ & $ 0.017$ & $ 0.567$ & $ 0.217$ & $ 0.123$ \\
+            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus & $1.7\times 10^{5}$ & $ 0.009$ & $ 0.024$ & $ 0.388$ & $ 0.308$ & $ 0.119$ \\
+            African & Homo sapiens & $5.6\times 10^{4}$ & $ 0.010$ & $ 0.026$ & $ 0.367$ & $ 0.411$ & $ 0.151$ \\
+            Admixed American & Homo sapiens & $4.5\times 10^{4}$ & $ 0.010$ & $ 0.017$ & $ 0.551$ & $ 0.374$ & $ 0.206$ \\
+            East Asian & Homo sapiens & $ 4\times 10^{4}$ & $ 0.010$ & $ 0.029$ & $ 0.332$ & $ 0.370$ & $ 0.123$ \\
+            European & Homo sapiens & $4.2\times 10^{4}$ & $ 0.010$ & $ 0.031$ & $ 0.304$ & $ 0.371$ & $ 0.113$ \\
+            South Asian & Homo sapiens & $4.4\times 10^{4}$ & $ 0.010$ & $ 0.032$ & $ 0.302$ & $ 0.369$ & $ 0.111$ \\
+        \end{longtable*}
+    \end{center}
+    \begin{itemize}
+        \item $\Ne$ is the estimated effective population size.
+        \item $\proba [ \SphyBen ]$ (eq.~5) is the probability for a new mutation a non-adaptive beneficial mutation.
+        These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1, thus toward a more fit amino-acid.
+        \item $\proba [ \SpopBen ]$ (eq.~15) is the probability for a mutation to be beneficial.
+        These mutations have a selection coefficient at the population-scale larger than 1.
+        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a non-adaptive beneficial mutation at the phylogenetic scale (the \textit{precision}).
+        \item $\proba [ \SphyBen \given \SpopBen]$ (eq.~14) is the probability for a mutation to be non-adaptive given it is beneficial at the population scale (the \textit{recall}).
+        This probability is obtained using Bayes' formula.
+    \end{itemize}
     \newpage
@@
     \subsection{Precision and recall}
-    \captionof{table}{Precision and recall}
+    \captionof{table}{Precision and recall while masking CpG transitions.}
     \begin{center}
@@
                 \\   \midrule
-                \rowcolor{LIGHTGREY} Equus c. & Equus caballus        & $ 0.002$ & $ 0.918$ & $ 0.957$ & $ 0.186$ & $ 0.213$ & $ 0.519$ & $ 0.122$ \\
-                Iran               & Bos taurus        & $ 0.002$ & $ 0.924$ & $ 0.965$ & $ 0.565$ & $ 0.356$ & $ 0.368$ & $ 0.702$ \\
-                Uganda              & Bos taurus        & $ 0.005$ & $ 0.943$ & $ 0.961$ & $ 0.516$ & $ 0.396$ & $ 0.255$ & $ 0.425$ \\
-                \rowcolor{LIGHTGREY} Australia            & Capra hircus        & $ 0.003$ & $ 0.941$ & $ 0.964$ & $ 0.592$ & $ 0.434$ & $ 0.147$ & $ 0.308$ \\
-                \rowcolor{LIGHTGREY} France                                    & Capra hircus          & $ 0.004$ & $ 0.940$ & $ 0.963$ & $ 0.571$ & $ 0.418$ & $ 0.149$ & $ 0.304$ \\
-                \rowcolor{LIGHTGREY} Iran (C. aegagrus)                    & Capra hircus          & $ 0.004$ & $ 0.948$ & $ 0.960$ & $ 0.515$ & $ 0.446$ & $ 0.147$ & $ 0.157$ \\
-                \rowcolor{LIGHTGREY} Iran                        & Capra hircus          & $ 0.004$ & $ 0.942$ & $ 0.961$ & $ 0.534$ & $ 0.410$ & $ 0.152$ & $ 0.258$ \\
-                \rowcolor{LIGHTGREY} Italy                                 & Capra hircus          & $ 0.004$ & $ 0.940$ & $ 0.963$ & $ 0.579$ & $ 0.421$ & $ 0.147$ & $ 0.316$ \\
-                \rowcolor{LIGHTGREY} Morocco                                 & Capra hircus          & $ 0.004$ & $ 0.939$ & $ 0.960$ & $ 0.549$ & $ 0.404$ & $ 0.186$ & $ 0.398$ \\
-                Iran           & Ovis aries & $ 0.007$ & $ 0.957$ & $ 0.954$ & $ 0.412$ & $ 0.416$ & $ 0.158$ & $ 0.191$ \\
-                Iran (O. orientalis)  & Ovis aries & $ 0.009$ & $ 0.961$ & $ 0.955$ & $ 0.413$ & $ 0.437$ & $ 0.157$ & $ 0.180$ \\
-                Iran (O. vignei)           & Ovis aries & $ 0.007$ & $ 0.968$ & $ 0.951$ & $ 0.356$ & $ 0.516$ & $ 0.186$ & $ 0.118$ \\
-                Various             & Ovis aries & $ 0.008$ & $ 0.958$ & $ 0.955$ & $ 0.428$ & $ 0.431$ & $ 0.156$ & $ 0.188$ \\
-                Morocco              & Ovis aries & $ 0.008$ & $ 0.960$ & $ 0.953$ & $ 0.447$ & $ 0.460$ & $ 0.190$ & $ 0.292$ \\
-                \rowcolor{LIGHTGREY} Barbados              & Chlorocebus sabaeus & $ 0.004$ & $ 0.931$ & $ 0.969$ & $ 0.628$ & $ 0.402$ & $ 0.282$ & $ 0.630$ \\
-                \rowcolor{LIGHTGREY} Central Afr. Rep.       & Chlorocebus sabaeus & $ 0.006$ & $ 0.941$ & $ 0.964$ & $ 0.514$ & $ 0.408$ & $ 0.310$ & $ 0.263$ \\
-                \rowcolor{LIGHTGREY} Ethiopia        & Chlorocebus sabaeus & $ 0.005$ & $ 0.933$ & $ 0.967$ & $ 0.586$ & $ 0.393$ & $ 0.298$ & $ 0.456$ \\
-                \rowcolor{LIGHTGREY} Gambia             & Chlorocebus sabaeus & $ 0.005$ & $ 0.937$ & $ 0.967$ & $ 0.590$ & $ 0.414$ & $ 0.305$ & $ 0.422$ \\
-                \rowcolor{LIGHTGREY} Kenya                                 & Chlorocebus sabaeus        & $ 0.005$ & $ 0.942$ & $ 0.965$ & $ 0.526$ & $ 0.418$ & $ 0.296$ & $ 0.253$ \\
-                \rowcolor{LIGHTGREY} Nevis                        & Chlorocebus sabaeus        & $ 0.003$ & $ 0.930$ & $ 0.970$ & $ 0.637$ & $ 0.401$ & $ 0.285$ & $ 0.696$ \\
-                \rowcolor{LIGHTGREY} South Africa                              & Chlorocebus sabaeus        & $ 0.006$ & $ 0.937$ & $ 0.964$ & $ 0.530$ & $ 0.393$ & $ 0.323$ & $ 0.338$ \\
-                \rowcolor{LIGHTGREY} Saint Kitts                                & Chlorocebus sabaeus        & $ 0.004$ & $ 0.931$ & $ 0.969$ & $ 0.611$ & $ 0.393$ & $ 0.292$ & $ 0.604$ \\
-                \rowcolor{LIGHTGREY} Zambia                             & Chlorocebus sabaeus        & $ 0.006$ & $ 0.941$ & $ 0.963$ & $ 0.506$ & $ 0.408$ & $ 0.309$ & $ 0.252$ \\
-                African                             & Homo sapiens        & $ 0.002$ & $ 0.896$ & $ 0.968$ & $ 0.550$ & $ 0.297$ & $ 0.371$ & $ 0.284$ \\
-                Admixed American                             & Homo sapiens        & $ 0.002$ & $ 0.890$ & $ 0.979$ & $ 0.710$ & $ 0.333$ & $ 0.368$ & $ 0.464$ \\
-                East Asian                             & Homo sapiens        & $ 0.002$ & $ 0.890$ & $ 0.971$ & $ 0.578$ & $ 0.289$ & $ 0.369$ & $ 0.358$ \\
-                European                             & Homo sapiens        & $ 0.002$ & $ 0.891$ & $ 0.980$ & $ 0.739$ & $ 0.345$ & $ 0.368$ & $ 0.499$ \\
-                South Asian                             & Homo sapiens        & $ 0.002$ & $ 0.895$ & $ 0.981$ & $ 0.740$ & $ 0.356$ & $ 0.369$ & $ 0.423$ \\
+                \rowcolor{LIGHTGREY} Equus c. & Equus caballus & $7.5\times 10^{4}$ & $ 0.887$ & $ 0.984$ & $ 0.740$ & $ 0.356$ & $ 0.543$ & $ 0.229$ \\
+                Iran & Bos taurus & $5.6\times 10^{4}$ & $ 0.888$ & $ 1.000$ & $ 0.632$ & $ 0.302$ & $ 0.797$ & $ 0.226$ \\
+                Uganda & Bos taurus & $1.3\times 10^{5}$ & $ 0.929$ & $ 0.973$ & $ 0.501$ & $ 0.349$ & $ 0.406$ & $ 0.195$ \\
+                \rowcolor{LIGHTGREY} Australia & Capra hircus & $1.7\times 10^{5}$ & $ 0.926$ & $ 0.972$ & $ 0.609$ & $ 0.421$ & $ 0.158$ & $ 0.072$ \\
+                \rowcolor{LIGHTGREY} France & Capra hircus & $1.9\times 10^{5}$ & $ 0.927$ & $ 0.959$ & $ 0.354$ & $ 0.321$ & $ 0.258$ & $ 0.082$ \\
+                \rowcolor{LIGHTGREY} Iran (C. aegagrus) & Capra hircus & $1.9\times 10^{5}$ & $ 0.931$ & $ 0.967$ & $ 0.502$ & $ 0.423$ & $ 0.268$ & $ 0.091$ \\
+                \rowcolor{LIGHTGREY} Iran & Capra hircus & $2.3\times 10^{5}$ & $ 0.937$ & $ 0.966$ & $ 0.529$ & $ 0.451$ & $ 0.294$ & $ 0.123$ \\
+                \rowcolor{LIGHTGREY} Italy & Capra hircus & $1.9\times 10^{5}$ & $ 0.927$ & $ 0.970$ & $ 0.550$ & $ 0.390$ & $ 0.100$ & $ 0.047$ \\
+                \rowcolor{LIGHTGREY} Morocco & Capra hircus & $2.2\times 10^{5}$ & $ 0.933$ & $ 0.965$ & $ 0.534$ & $ 0.401$ & $ 0.141$ & $ 0.083$ \\
+                Iran & Ovis aries & $3.8\times 10^{5}$ & $ 0.947$ & $ 0.957$ & $ 0.446$ & $ 0.393$ & $ 0.243$ & $ 0.239$ \\
+                Iran (O. orientalis) & Ovis aries & $4.5\times 10^{5}$ & $ 0.951$ & $ 0.961$ & $ 0.396$ & $ 0.386$ & $ 0.155$ & $ 0.093$ \\
+                Iran (O. vignei) & Ovis aries & $3.7\times 10^{5}$ & $ 0.954$ & $ 0.960$ & $ 0.379$ & $ 0.432$ & $ 0.252$ & $ 0.112$ \\
+                Various & Ovis aries & $4.1\times 10^{5}$ & $ 0.949$ & $ 0.956$ & $ 0.434$ & $ 0.418$ & $ 0.198$ & $ 0.139$ \\
+                Morocco & Ovis aries & $ 4\times 10^{5}$ & $ 0.946$ & $ 0.959$ & $ 0.453$ & $ 0.374$ & $ 0.165$ & $ 0.229$ \\
+                \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus & $1.1\times 10^{5}$ & $ 0.916$ & $ 0.971$ & $ 0.523$ & $ 0.306$ & $ 0.231$ & $ 0.174$ \\
+                \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus & $1.7\times 10^{5}$ & $ 0.933$ & $ 0.969$ & $ 0.486$ & $ 0.353$ & $ 0.209$ & $ 0.108$ \\
+                \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus & $1.4\times 10^{5}$ & $ 0.918$ & $ 0.973$ & $ 0.533$ & $ 0.348$ & $ 0.241$ & $ 0.093$ \\
+                \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus & $1.4\times 10^{5}$ & $ 0.925$ & $ 0.971$ & $ 0.572$ & $ 0.343$ & $ 0.204$ & $ 0.275$ \\
+                \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus & $1.5\times 10^{5}$ & $ 0.931$ & $ 0.971$ & $ 0.521$ & $ 0.378$ & $ 0.239$ & $ 0.106$ \\
+                \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus & $ 1\times 10^{5}$ & $ 0.916$ & $ 0.972$ & $ 0.535$ & $ 0.313$ & $ 0.146$ & $ 0.101$ \\
+                \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus & $1.8\times 10^{5}$ & $ 0.928$ & $ 0.970$ & $ 0.546$ & $ 0.378$ & $ 0.272$ & $ 0.135$ \\
+                \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus & $1.2\times 10^{5}$ & $ 0.917$ & $ 0.971$ & $ 0.507$ & $ 0.309$ & $ 0.217$ & $ 0.123$ \\
+                \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus & $1.7\times 10^{5}$ & $ 0.930$ & $ 0.969$ & $ 0.495$ & $ 0.372$ & $ 0.308$ & $ 0.119$ \\
+                African & Homo sapiens & $5.6\times 10^{4}$ & $ 0.888$ & $ 0.978$ & $ 0.587$ & $ 0.296$ & $ 0.411$ & $ 0.151$ \\
+                Admixed American & Homo sapiens & $4.5\times 10^{4}$ & $ 0.874$ & $ 0.979$ & $ 0.591$ & $ 0.256$ & $ 0.374$ & $ 0.206$ \\
+                East Asian & Homo sapiens & $ 4\times 10^{4}$ & $ 0.877$ & $ 0.980$ & $ 0.593$ & $ 0.280$ & $ 0.370$ & $ 0.123$ \\
+                European & Homo sapiens & $4.2\times 10^{4}$ & $ 0.885$ & $ 0.980$ & $ 0.591$ & $ 0.301$ & $ 0.371$ & $ 0.113$ \\
+                South Asian & Homo sapiens & $4.4\times 10^{4}$ & $ 0.886$ & $ 0.979$ & $ 0.591$ & $ 0.303$ & $ 0.369$ & $ 0.111$ \\
                 \bottomrule
@@
     \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
+        \item $\Ne$ is the estimated effective population size.
         \item \textit{Precision} is the estimation of the selection coefficient at population scale ($\Spop$) given that $\Sphy$ is known.
         \item \textit{Recall} is the estimation of $\Sphy$ given selection coefficient at the population scale ($\Spop$) is known.
-        \item \textit{Recall} for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is thus the proportion of beneficial back-mutations among all beneficial mutations.
+        \item \textit{Recall} for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is the probability for a mutation to be non-adaptive given it is beneficial at the population scale.
     \end{itemize}
 
-    Altogether, comparing this table to tables 1 and S3, we acknowledge that the exact proportion of beneficial back-mutations among all beneficial ones is different whether we included or not substitutions in the terminal lineage for the estimation of $\Spop$.
-    However, we can still see that beneficial back-mutations are positively selected compared to neutral and deleterious ones, and this result is not sensitive to inclusion of substitutions in the terminal lineage.
-
-    \newpage
-    \section{Discrete distribution of $\Spop$ at the population scale}
-
-    \subsection{polyDFE model D (discrete distribution)}
-    With polyDFE model D, the DFE of non-synonymous mutations is given as a discrete DFE of $K$ categories (instead of a continuous distribution in model C), where the selection coefficients of each category $i$ ($1 \leq i \leq K$) are fixed parameters $\Spop_i$, and each value $\Spop_i$ has a probability $p_i$ (estimated), with $\sum_{i=1}^{K} p_i =1$.
-    We used $K=6$ with $\Spop_1 = -500$, $\Spop_2 = -4$, $\Spop_3 =-1$, $\Spop_4 = 0$, $\Spop_5 = 1$, $\Spop_6 = 4$.\\
-    For each class of selection $\Sphyclass$, the parameters $p_i$ ($i \in \{ 1 \leq i \leq 6 \}$) were used to compute $\proba [ \SpopDel \given  \Sphyclass] $, $\proba [ \SpopNeu \given \Sphyclass]$, and $\proba [ \SpopBen \given \Sphyclass]$ as:
-    \begin{align}
-        \proba [ \SpopDel \given  \Sphyclass] &= \proba [ \Spop < -1 \given \Sphyclass ] = p_1 + p_2 \label{eq:polyProbaDel} \\
-        \proba [ \SpopNeu \given \Sphyclass] &= \proba [ -1 < \Spop < 1 \given \Sphyclass ] = p_3 + p_4 + p_5,  \\
-        \proba [ \SpopBen \given \Sphyclass] &= p_6. \label{eq:polyProbaAdv}
-    \end{align}
-
-    \subsection{Probabilities of beneficial back-mutations}
-    \begin{center}
-        \captionof{table}{Probability of beneficial back-mutations among all beneficial ones.}
+    Altogether, comparing this table other estimations, we acknowledge that the exact proportion of non-adaptive among beneficial mutations is dependent on the whether we masked CpG sites.
+    However, we can still see that non-adaptive beneficial mutations are positively selected compared to neutral and deleterious ones, and this result is not dependent on whether we masked CpG sites or not.
+
+    \newpage
+
+    \subsection{Example site-frequency spectrum}\label{subsec:CpG-expectedDFE}
+
+    The site-frequency spectrum (SFS, panel A) and the congruency between fitness effects estimates ($\Sphy$ versus $\Sphy$, panel B) shown below are obtained in the African population of \textit{Homo sapiens} and the South African population of \textit{Chlorocebus sabaeus}.
+
+    \begin{center}
+        \captionof{figure}{Site-frequency spectrum in African population of \textit{Homo sapiens}, masking CpG transitions.}
+        \begin{minipage}{0.49\linewidth}
+            \flushleft {\tiny A: Site frequency spectrum}
+            \includegraphics[width=\linewidth, page=1]{artworks/CpG.Homo_sapiens.AFR.MutSel-sfs.pdf}
+        \end{minipage}
+        \begin{minipage}{0.49\linewidth}
+            \flushleft {\tiny B: $S$ as function of $S_0$ for each class}
+            \includegraphics[width=\linewidth, page=1]{artworks/CpG.Homo_sapiens.AFR.MutSel.polyDFE_C.pdf}
+        \end{minipage}
+    \end{center}
+
+    \begin{center}
+        \captionof{figure}{Site-frequency spectrum in South African population of \textit{Chlorocebus sabaeus}, masking CpG transitions.}
+        \begin{minipage}{0.49\linewidth}
+            \flushleft {\tiny A: Site frequency spectrum}
+            \includegraphics[width=\linewidth, page=1]{artworks/CpG.Chlorocebus_sabaeus.South_Africa.MutSel-sfs.pdf}
+        \end{minipage}
+        \begin{minipage}{0.49\linewidth}
+            \flushleft {\tiny B: $S$ as function of $S_0$ for each class}
+            \includegraphics[width=\linewidth, page=1]{artworks/CpG.Chlorocebus_sabaeus.South_Africa.MutSel.polyDFE_C.pdf}
+        \end{minipage}
+    \end{center}
+
+    \begin{itemize}[itemsep=0pt]
+        \item A: The site-frequency spectrum (SFS) in the population for a random sample of 16 alleles (means in solid lines and standard deviations in color shades) for each class of selection and for synonymous mutations, supposedly neutral (black).
+The SFS represents the proportion of mutations (y-axis) with a given number of derived alleles in the population (x-axis).
+Here SFS are weighted by the mutational opportunities in each class of selection (synonymous, $\SphyDel$, $\SphyNeu$ and $\SphyBen$).
+        \item B: Proportion of beneficial $\ProbaPopDel$, nearly-neutral $\ProbaPopNeu$, and deleterious mutations $\ProbaPopBen$  estimated at the population scale for each class of selection at the phylogenetic scale.
+Proportions depicted here are not weighted by their mutational opportunities.
+    \end{itemize}
+
+    \newpage
+    \section{Including divergence data for the estimation of $\Spop$}
+
+    \subsection{Including divergence in polyDFE}
+    Divergence data (number of substitutions per site) can also be included into polyDFE to estimate the DFE.
+    For the class of a given class of selection coefficient ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$), the number of substitutions has already been computed and is given by $D\left( \Sphyclass \right)$ (see eq.~6), and the number of sites is given by $L \left( \Sphyclass \right)$ (see eq.~4).
+    Otherwise, the procedure is the same as described section \textit{Scaled selection coefficients ($\Spop$) in a population-based method}.
+
+    \subsection{Probability for beneficial mutations to be non-adaptive}
+    \begin{center}
+        \captionof{table}{$\proba[\SphyBen\given \SpopBen ]$ when including divergence to estimate $\Spop$.}
         \scriptsize
@@
             \endlastfoot
-            \rowcolor{LIGHTGREY} Equus c.
-&      Equus caballus &               $ 0.002$ &              $ 0.014$ &              $ 0.006$ &                                          $ 2.230$ &                         $ 0.141$ &                      $ 0.316$ \\
-            Iran &          Bos taurus &               $ 0.002$ &              $ 0.013$ &              $ 0.006$ &                                          $ 2.200$ &                         $ 0.136$ &                      $ 0.298$ \\
-            Uganda &          Bos taurus &               $ 0.005$ &              $ 0.013$ &              $ 0.011$ &                                          $ 1.177$ &                         $ 0.138$ &                      $ 0.162$ \\
-            \rowcolor{LIGHTGREY} Australia &        Capra hircus &               $ 0.003$ &              $ 0.014$ &              $ 0.002$ &                                          $ 6.467$ &                         $ 0.135$ &                      $ 0.871$ \\
-            \rowcolor{LIGHTGREY} France &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.002$ &                                          $ 6.407$ &                         $ 0.132$ &                      $ 0.845$ \\
-            \rowcolor{LIGHTGREY} Iran (C.
-aegagrus) &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.002$ &                                          $ 5.993$ &                         $ 0.129$ &                      $ 0.772$ \\
-            \rowcolor{LIGHTGREY} Iran &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.004$ &                                          $ 3.656$ &                         $ 0.138$ &                      $ 0.506$ \\
-            \rowcolor{LIGHTGREY} Italy &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.002$ &                                          $ 6.216$ &                         $ 0.127$ &                      $ 0.787$ \\
-            \rowcolor{LIGHTGREY} Morocco &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.002$ &                                          $ 6.019$ &                         $ 0.141$ &                      $ 0.848$ \\
-            Iran &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.588$ &                         $ 0.148$ &                      $ 0.087$ \\
-            Iran (O.
-orientalis) &          Ovis aries &               $ 0.009$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.569$ &                         $ 0.143$ &                      $ 0.081$ \\
-            Iran (O.
-vignei) &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.587$ &                         $ 0.127$ &                      $ 0.075$ \\
-            Various &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.588$ &                         $ 0.146$ &                      $ 0.086$ \\
-            Morocco &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.025$ &                                          $ 0.564$ &                         $ 0.145$ &                      $ 0.082$ \\
-            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.002$ &                                          $ 5.689$ &                         $ 0.170$ &                      $ 0.968$ \\
-            \rowcolor{LIGHTGREY} Central Afr.
-Rep.
-& Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.005$ &                                          $ 2.142$ &                         $ 0.156$ &                      $ 0.334$ \\
-            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.002$ &                                          $ 5.910$ &                         $ 0.160$ &                      $ 0.945$ \\
-            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.006$ &                                          $ 1.850$ &                         $ 0.157$ &                      $ 0.290$ \\
-            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.004$ &                                          $ 2.802$ &                         $ 0.163$ &                      $ 0.456$ \\
-            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus &               $ 0.003$ &              $ 0.012$ &              $ 0.002$ &                                          $ 5.396$ &                         $ 0.169$ &                      $ 0.910$ \\
-            \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.005$ &                                          $ 2.154$ &                         $ 0.153$ &                      $ 0.329$ \\
-            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.002$ &                                          $ 5.094$ &                         $ 0.164$ &                      $ 0.834$ \\
-            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.006$ &                                          $ 1.952$ &                         $ 0.153$ &                      $ 0.298$ \\
-            African &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.014$ &                                          $ 0.869$ &                         $ 0.141$ &                      $ 0.123$ \\
-            Admixed American &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.010$ &                                          $ 1.130$ &                         $ 0.161$ &                      $ 0.182$ \\
-            East Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.007$ &                                          $ 1.602$ &                         $ 0.162$ &                      $ 0.259$ \\
-            European &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.009$ &                                          $ 1.336$ &                         $ 0.163$ &                      $ 0.217$ \\
-            South Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.009$ &                                          $ 1.342$ &                         $ 0.163$ &                      $ 0.219$ \\
+            \rowcolor{LIGHTGREY} Equus c. & Equus caballus & $7.5\times 10^{4}$ & $ 0.012$ & $ 0.057$ & $ 0.213$ & $ 0.498$ & $ 0.106$ \\
+            Iran & Bos taurus & $5.6\times 10^{4}$ & $ 0.011$ & $ 0.006$ & $ 1.860$ & $ 0.368$ & $ 0.684$ \\
+            Uganda & Bos taurus & $1.3\times 10^{5}$ & $ 0.011$ & $ 0.012$ & $ 0.900$ & $ 0.307$ & $ 0.276$ \\
+            \rowcolor{LIGHTGREY} Australia & Capra hircus & $1.7\times 10^{5}$ & $ 0.011$ & $ 0.007$ & $ 1.651$ & $ 0.178$ & $ 0.294$ \\
+            \rowcolor{LIGHTGREY} France & Capra hircus & $1.9\times 10^{5}$ & $ 0.011$ & $ 0.007$ & $ 1.614$ & $ 0.183$ & $ 0.295$ \\
+            \rowcolor{LIGHTGREY} Iran (C. aegagrus) & Capra hircus & $1.9\times 10^{5}$ & $ 0.011$ & $ 0.012$ & $ 0.923$ & $ 0.177$ & $ 0.163$ \\
+            \rowcolor{LIGHTGREY} Iran & Capra hircus & $2.3\times 10^{5}$ & $ 0.011$ & $ 0.008$ & $ 1.483$ & $ 0.184$ & $ 0.273$ \\
+            \rowcolor{LIGHTGREY} Italy & Capra hircus & $1.9\times 10^{5}$ & $ 0.011$ & $ 0.007$ & $ 1.686$ & $ 0.178$ & $ 0.299$ \\
+            \rowcolor{LIGHTGREY} Morocco & Capra hircus & $2.2\times 10^{5}$ & $ 0.011$ & $ 0.006$ & $ 1.892$ & $ 0.184$ & $ 0.349$ \\
+            Iran & Ovis aries & $3.8\times 10^{5}$ & $ 0.012$ & $ 0.010$ & $ 1.132$ & $ 0.189$ & $ 0.214$ \\
+            Iran (O. orientalis) & Ovis aries & $4.5\times 10^{5}$ & $ 0.011$ & $ 0.011$ & $ 1.012$ & $ 0.213$ & $ 0.216$ \\
+            Iran (O. vignei) & Ovis aries & $3.7\times 10^{5}$ & $ 0.012$ & $ 0.021$ & $ 0.561$ & $ 0.186$ & $ 0.105$ \\
+            Various & Ovis aries & $4.1\times 10^{5}$ & $ 0.011$ & $ 0.011$ & $ 1.069$ & $ 0.215$ & $ 0.229$ \\
+            Morocco & Ovis aries & $ 4\times 10^{5}$ & $ 0.012$ & $ 0.012$ & $ 0.973$ & $ 0.217$ & $ 0.211$ \\
+            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus & $1.1\times 10^{5}$ & $ 0.009$ & $ 0.004$ & $ 2.120$ & $ 0.341$ & $ 0.723$ \\
+            \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus & $1.7\times 10^{5}$ & $ 0.009$ & $ 0.013$ & $ 0.720$ & $ 0.368$ & $ 0.265$ \\
+            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus & $1.4\times 10^{5}$ & $ 0.009$ & $ 0.007$ & $ 1.352$ & $ 0.368$ & $ 0.498$ \\
+            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus & $1.4\times 10^{5}$ & $ 0.009$ & $ 0.010$ & $ 0.956$ & $ 0.368$ & $ 0.352$ \\
+            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus & $1.5\times 10^{5}$ & $ 0.009$ & $ 0.013$ & $ 0.727$ & $ 0.368$ & $ 0.268$ \\
+            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus & $ 1\times 10^{5}$ & $ 0.009$ & $ 0.004$ & $ 2.133$ & $ 0.368$ & $ 0.784$ \\
+            \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus & $1.8\times 10^{5}$ & $ 0.009$ & $ 0.011$ & $ 0.874$ & $ 0.368$ & $ 0.322$ \\
+            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus & $1.2\times 10^{5}$ & $ 0.009$ & $ 0.005$ & $ 1.905$ & $ 0.368$ & $ 0.701$ \\
+            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus & $1.7\times 10^{5}$ & $ 0.009$ & $ 0.014$ & $ 0.698$ & $ 0.368$ & $ 0.257$ \\
+            African & Homo sapiens & $5.6\times 10^{4}$ & $ 0.010$ & $ 0.013$ & $ 0.726$ & $ 0.437$ & $ 0.317$ \\
+            Admixed American & Homo sapiens & $4.5\times 10^{4}$ & $ 0.010$ & $ 0.011$ & $ 0.886$ & $ 0.429$ & $ 0.380$ \\
+            East Asian & Homo sapiens & $ 4\times 10^{4}$ & $ 0.010$ & $ 0.008$ & $ 1.213$ & $ 0.426$ & $ 0.517$ \\
+            European & Homo sapiens & $4.1\times 10^{4}$ & $ 0.010$ & $ 0.009$ & $ 1.104$ & $ 0.422$ & $ 0.466$ \\
+            South Asian & Homo sapiens & $4.4\times 10^{4}$ & $ 0.010$ & $ 0.009$ & $ 1.016$ & $ 0.426$ & $ 0.433$ \\
         \end{longtable*}
@@
     \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item $\proba [ \SphyBen ]$ (eq.~5) is the probability for a new mutation a beneficial back-mutation.
+        \item $\Ne$ is the estimated effective population size.
+        \item $\proba [ \SphyBen ]$ (eq.~5) is the probability for a new mutation a non-adaptive mutation.
         These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1, thus toward a more fit amino-acid.
@@
     \subsection{Precision and recall}
-    \captionof{table}{Precision and recall}
+    \captionof{table}{Precision and recall while including divergence to estimate $\Spop$.}
     \begin{center}
@@
                 \\   \midrule
-                \rowcolor{LIGHTGREY} Equus c. & Equus caballus        & $ 0.002$ & $ 0.895$ & $ 0.969$ & $ 0.645$ & $ 0.315$ & $ 0.141$ & $ 0.316$ \\
-                Iran               & Bos taurus        & $ 0.002$ & $ 0.878$ & $ 0.968$ & $ 0.632$ & $ 0.286$ & $ 0.136$ & $ 0.298$ \\
-                Uganda              & Bos taurus        & $ 0.005$ & $ 0.951$ & $ 0.963$ & $ 0.597$ & $ 0.508$ & $ 0.138$ & $ 0.162$ \\
-                \rowcolor{LIGHTGREY} Australia            & Capra hircus        & $ 0.003$ & $ 0.895$ & $ 0.981$ & $ 0.830$ & $ 0.379$ & $ 0.135$ & $ 0.871$ \\
-                \rowcolor{LIGHTGREY} France                                    & Capra hircus          & $ 0.004$ & $ 0.896$ & $ 0.978$ & $ 0.801$ & $ 0.373$ & $ 0.132$ & $ 0.845$ \\
-                \rowcolor{LIGHTGREY} Iran (C. aegagrus)                    & Capra hircus          & $ 0.004$ & $ 0.913$ & $ 0.971$ & $ 0.711$ & $ 0.383$ & $ 0.129$ & $ 0.772$ \\
-                \rowcolor{LIGHTGREY} Iran                        & Capra hircus          & $ 0.004$ & $ 0.949$ & $ 0.968$ & $ 0.655$ & $ 0.481$ & $ 0.138$ & $ 0.506$ \\
-                \rowcolor{LIGHTGREY} Italy                                 & Capra hircus          & $ 0.004$ & $ 0.894$ & $ 0.979$ & $ 0.814$ & $ 0.373$ & $ 0.127$ & $ 0.787$ \\
-                \rowcolor{LIGHTGREY} Morocco                                 & Capra hircus          & $ 0.004$ & $ 0.951$ & $ 0.972$ & $ 0.709$ & $ 0.504$ & $ 0.141$ & $ 0.848$ \\
-                Iran           & Ovis aries & $ 0.007$ & $ 0.980$ & $ 0.956$ & $ 0.456$ & $ 0.799$ & $ 0.148$ & $ 0.087$ \\
-                Iran (O. orientalis)  & Ovis aries & $ 0.009$ & $ 0.979$ & $ 0.955$ & $ 0.454$ & $ 0.798$ & $ 0.143$ & $ 0.081$ \\
-                Iran (O. vignei)           & Ovis aries & $ 0.007$ & $ 0.974$ & $ 0.957$ & $ 0.483$ & $ 0.729$ & $ 0.127$ & $ 0.075$ \\
-                Various             & Ovis aries & $ 0.008$ & $ 0.979$ & $ 0.958$ & $ 0.500$ & $ 0.813$ & $ 0.146$ & $ 0.086$ \\
-                Morocco              & Ovis aries & $ 0.008$ & $ 0.980$ & $ 0.952$ & $ 0.392$ & $ 0.774$ & $ 0.145$ & $ 0.082$ \\
-                \rowcolor{LIGHTGREY} Barbados              & Chlorocebus sabaeus & $ 0.004$ & $ 0.880$ & $ 0.984$ & $ 0.854$ & $ 0.354$ & $ 0.170$ & $ 0.968$ \\
-                \rowcolor{LIGHTGREY} Central Afr. Rep.       & Chlorocebus sabaeus & $ 0.006$ & $ 0.932$ & $ 0.968$ & $ 0.634$ & $ 0.413$ & $ 0.156$ & $ 0.334$ \\
-                \rowcolor{LIGHTGREY} Ethiopia        & Chlorocebus sabaeus & $ 0.005$ & $ 0.877$ & $ 0.980$ & $ 0.810$ & $ 0.337$ & $ 0.160$ & $ 0.945$ \\
-                \rowcolor{LIGHTGREY} Gambia             & Chlorocebus sabaeus & $ 0.005$ & $ 0.947$ & $ 0.977$ & $ 0.745$ & $ 0.518$ & $ 0.157$ & $ 0.290$ \\
-                \rowcolor{LIGHTGREY} Kenya                                 & Chlorocebus sabaeus        & $ 0.005$ & $ 0.903$ & $ 0.969$ & $ 0.664$ & $ 0.343$ & $ 0.163$ & $ 0.456$ \\
-                \rowcolor{LIGHTGREY} Nevis                        & Chlorocebus sabaeus        & $ 0.003$ & $ 0.880$ & $ 0.984$ & $ 0.861$ & $ 0.357$ & $ 0.169$ & $ 0.910$ \\
-                \rowcolor{LIGHTGREY} South Africa                              & Chlorocebus sabaeus        & $ 0.006$ & $ 0.931$ & $ 0.967$ & $ 0.615$ & $ 0.401$ & $ 0.153$ & $ 0.329$ \\
-                \rowcolor{LIGHTGREY} Saint Kitts                                & Chlorocebus sabaeus        & $ 0.004$ & $ 0.883$ & $ 0.982$ & $ 0.834$ & $ 0.355$ & $ 0.164$ & $ 0.834$ \\
-                \rowcolor{LIGHTGREY} Zambia                             & Chlorocebus sabaeus        & $ 0.006$ & $ 0.896$ & $ 0.969$ & $ 0.659$ & $ 0.332$ & $ 0.153$ & $ 0.298$ \\
-                African                             & Homo sapiens        & $ 0.002$ & $ 0.946$ & $ 0.971$ & $ 0.630$ & $ 0.486$ & $ 0.141$ & $ 0.123$ \\
-                Admixed American                             & Homo sapiens        & $ 0.002$ & $ 0.929$ & $ 0.972$ & $ 0.636$ & $ 0.410$ & $ 0.161$ & $ 0.182$ \\
-                East Asian                             & Homo sapiens        & $ 0.002$ & $ 0.937$ & $ 0.973$ & $ 0.647$ & $ 0.429$ & $ 0.162$ & $ 0.259$ \\
-                European                             & Homo sapiens        & $ 0.002$ & $ 0.937$ & $ 0.973$ & $ 0.643$ & $ 0.433$ & $ 0.163$ & $ 0.217$ \\
-                South Asian                             & Homo sapiens        & $ 0.002$ & $ 0.939$ & $ 0.972$ & $ 0.639$ & $ 0.439$ & $ 0.163$ & $ 0.219$ \\
+                \rowcolor{LIGHTGREY} Equus c. & Equus caballus & $7.5\times 10^{4}$ & $ 0.937$ & $ 0.955$ & $ 0.111$ & $ 0.192$ & $ 0.498$ & $ 0.106$ \\
+                Iran & Bos taurus & $5.6\times 10^{4}$ & $ 0.935$ & $ 0.970$ & $ 0.565$ & $ 0.356$ & $ 0.368$ & $ 0.684$ \\
+                Uganda & Bos taurus & $1.3\times 10^{5}$ & $ 0.951$ & $ 0.967$ & $ 0.516$ & $ 0.422$ & $ 0.307$ & $ 0.276$ \\
+                \rowcolor{LIGHTGREY} Australia & Capra hircus & $1.7\times 10^{5}$ & $ 0.952$ & $ 0.970$ & $ 0.598$ & $ 0.452$ & $ 0.178$ & $ 0.294$ \\
+                \rowcolor{LIGHTGREY} France & Capra hircus & $1.9\times 10^{5}$ & $ 0.951$ & $ 0.969$ & $ 0.574$ & $ 0.433$ & $ 0.183$ & $ 0.295$ \\
+                \rowcolor{LIGHTGREY} Iran (C. aegagrus) & Capra hircus & $1.9\times 10^{5}$ & $ 0.957$ & $ 0.966$ & $ 0.515$ & $ 0.460$ & $ 0.177$ & $ 0.163$ \\
+                \rowcolor{LIGHTGREY} Iran & Capra hircus & $2.3\times 10^{5}$ & $ 0.951$ & $ 0.967$ & $ 0.542$ & $ 0.422$ & $ 0.184$ & $ 0.273$ \\
+                \rowcolor{LIGHTGREY} Italy & Capra hircus & $1.9\times 10^{5}$ & $ 0.951$ & $ 0.969$ & $ 0.582$ & $ 0.436$ & $ 0.178$ & $ 0.299$ \\
+                \rowcolor{LIGHTGREY} Morocco & Capra hircus & $2.2\times 10^{5}$ & $ 0.949$ & $ 0.968$ & $ 0.556$ & $ 0.412$ & $ 0.184$ & $ 0.349$ \\
+                Iran & Ovis aries & $3.8\times 10^{5}$ & $ 0.963$ & $ 0.962$ & $ 0.421$ & $ 0.424$ & $ 0.189$ & $ 0.214$ \\
+                Iran (O. orientalis) & Ovis aries & $4.5\times 10^{5}$ & $ 0.968$ & $ 0.961$ & $ 0.413$ & $ 0.460$ & $ 0.213$ & $ 0.216$ \\
+                Iran (O. vignei) & Ovis aries & $3.7\times 10^{5}$ & $ 0.972$ & $ 0.959$ & $ 0.360$ & $ 0.528$ & $ 0.186$ & $ 0.105$ \\
+                Various & Ovis aries & $4.1\times 10^{5}$ & $ 0.966$ & $ 0.961$ & $ 0.430$ & $ 0.454$ & $ 0.215$ & $ 0.229$ \\
+                Morocco & Ovis aries & $ 4\times 10^{5}$ & $ 0.966$ & $ 0.958$ & $ 0.372$ & $ 0.416$ & $ 0.217$ & $ 0.211$ \\
+                \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus & $1.1\times 10^{5}$ & $ 0.940$ & $ 0.976$ & $ 0.654$ & $ 0.409$ & $ 0.341$ & $ 0.723$ \\
+                \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus & $1.7\times 10^{5}$ & $ 0.950$ & $ 0.971$ & $ 0.526$ & $ 0.421$ & $ 0.368$ & $ 0.265$ \\
+                \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus & $1.4\times 10^{5}$ & $ 0.942$ & $ 0.974$ & $ 0.609$ & $ 0.402$ & $ 0.368$ & $ 0.498$ \\
+                \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus & $1.4\times 10^{5}$ & $ 0.950$ & $ 0.974$ & $ 0.611$ & $ 0.452$ & $ 0.368$ & $ 0.352$ \\
+                \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus & $1.5\times 10^{5}$ & $ 0.950$ & $ 0.972$ & $ 0.545$ & $ 0.434$ & $ 0.368$ & $ 0.268$ \\
+                \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus & $ 1\times 10^{5}$ & $ 0.940$ & $ 0.977$ & $ 0.668$ & $ 0.412$ & $ 0.368$ & $ 0.784$ \\
+                \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus & $1.8\times 10^{5}$ & $ 0.947$ & $ 0.972$ & $ 0.550$ & $ 0.411$ & $ 0.368$ & $ 0.322$ \\
+                \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus & $1.2\times 10^{5}$ & $ 0.940$ & $ 0.976$ & $ 0.646$ & $ 0.407$ & $ 0.368$ & $ 0.701$ \\
+                \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus & $1.7\times 10^{5}$ & $ 0.950$ & $ 0.971$ & $ 0.527$ & $ 0.426$ & $ 0.368$ & $ 0.257$ \\
+                African & Homo sapiens & $5.6\times 10^{4}$ & $ 0.911$ & $ 0.980$ & $ 0.666$ & $ 0.341$ & $ 0.437$ & $ 0.317$ \\
+                Admixed American & Homo sapiens & $4.5\times 10^{4}$ & $ 0.902$ & $ 0.976$ & $ 0.580$ & $ 0.284$ & $ 0.429$ & $ 0.380$ \\
+                East Asian & Homo sapiens & $ 4\times 10^{4}$ & $ 0.904$ & $ 0.984$ & $ 0.744$ & $ 0.341$ & $ 0.426$ & $ 0.517$ \\
+                European & Homo sapiens & $4.1\times 10^{4}$ & $ 0.906$ & $ 0.984$ & $ 0.737$ & $ 0.344$ & $ 0.422$ & $ 0.466$ \\
+                South Asian & Homo sapiens & $4.4\times 10^{4}$ & $ 0.907$ & $ 0.984$ & $ 0.737$ & $ 0.349$ & $ 0.426$ & $ 0.433$ \\
                 \bottomrule
@@
     \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
+        \item $\Ne$ is the estimated effective population size.
         \item \textit{Precision} is the estimation of the selection coefficient at population scale ($\Spop$) given that $\Sphy$ is known.
         \item  \textit{Recall} is the estimation of $\Sphy$ given selection coefficient at the population scale ($\Spop$) is known.
-        \item \textit{Recall} for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is thus the proportion of beneficial back-mutations among all beneficial mutations.
+        \item \textit{Recall} for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is the probability for a mutation to be non-adaptive given it is beneficial at the population scale.
     \end{itemize}
 
-    Altogether, comparing this table to tables 1 and S3, we acknowledge that the exact proportion of beneficial back-mutations among all beneficial ones is dependent on the model used to estimate the DFE.
-    However, we can still see that beneficial back-mutations are positively selected compared to neutral and deleterious ones, and this result is not sensitive to the underlying DFE at the population scale.
-
-    %\section{References}
-    %\printbibliography[heading=none]
-
-    %    \section{Distribution of fitness effects}
-    %    \captionof{figure}{~}
-    %    \begin{minipage}{0.49\linewidth}
-    %        \includegraphics[width=\linewidth, page=1]{artworks/2bins.Yeast.experimentalDFE.pdf}
-    %    \end{minipage}
-    %    \begin{minipage}{0.49\linewidth}
-    %        \includegraphics[width=\linewidth, page=1]{artworks/2bins.AFR.histogramDFE.pdf}
-    %    \end{minipage}
-    %    Left panel: distribution of fitness effects experimentally determined in Yeast, data obtained in \textcite{shen_synonymous_2022}.
-    %    Right panel:  distribution of fitness effects ($\Sphy$) as predicted with mutation-selection codon models, from reconstructed ancestral genome in \textit{Homo sapiens}.
-    %    The DFE predicted with mutation-selection codon models has a negative mode, consistently with experimental DFEs, meaning that most mutations are effectively deleterious.
+    Altogether, comparing this table to tables 1 and S3, we acknowledge that the exact proportion of non-adaptive beneficial mutations among all beneficial ones is different whether we included or not substitutions in the terminal lineage for the estimation of $\Spop$.
+    However, we can still see that non-adaptive beneficial mutations are positively selected compared to neutral and deleterious ones, and this result is not sensitive to inclusion of substitutions in the terminal lineage.
+    \newpage
+
+    \subsection{Misannotations of ancestral alleles}
+
+    If misannotation is influencing the recall for $\SphyBen$ ($\proba[\SphyBen\given \SpopBen ]$), then the recall should increase as a function of  divergence to the sister species ($\ds$: number of synonymous substitutions per sites) since divergence would increase the rate of misannotations.
+    Shown below is recall $\proba[\SphyBen\given \SpopBen ]$ as a function of divergence ($\ds$) in which the latter is not an explanatory variable.
+
+    \begin{center}
+        \captionof{figure}{$\proba[\SphyBen\given \SpopBen ]$ while including divergence to estimate $\Spop$, as a function of distance to the sister species.}
+        \includegraphics[width=0.75\linewidth, page=1]{artworks/results.distance.recall_pos.div.scatter.pdf}
+    \end{center}
+
+    \newpage
+
+    \subsection{Excluding genes under adaptation}
+
+    \begin{center}
+        \captionof{table}{$\proba[\SphyBen\given \SpopBen ]$ excluding or not genes under adaptation, when including divergence to estimate $\Spop$.}
+        \begin{tabular}{|l|l|r|r|}
+            \toprule
+            Population & Species & Control & Case \\
+            \midrule
+            \rowcolor{LIGHTGREY} Equus c. & Equus caballus & $ 0.106$ & $ 0.106$ \\
+            Iran & Bos taurus & $ 0.684$ & $ 0.755$ \\
+            Uganda & Bos taurus & $ 0.276$ & $ 0.310$ \\
+            \rowcolor{LIGHTGREY} Australia & Capra hircus & $ 0.294$ & $ 0.319$ \\
+            \rowcolor{LIGHTGREY} France & Capra hircus & $ 0.295$ & $ 0.325$ \\
+            \rowcolor{LIGHTGREY} Iran (C. aegagrus) & Capra hircus & $ 0.163$ & $ 0.174$ \\
+            \rowcolor{LIGHTGREY} Iran & Capra hircus & $ 0.273$ & $ 0.299$ \\
+            \rowcolor{LIGHTGREY} Italy & Capra hircus & $ 0.299$ & $ 0.321$ \\
+            \rowcolor{LIGHTGREY} Morocco & Capra hircus & $ 0.349$ & $ 0.419$ \\
+            Iran & Ovis aries & $ 0.214$ & $ 0.241$ \\
+            Iran (O. orientalis) & Ovis aries & $ 0.216$ & $ 0.213$ \\
+            Iran (O. vignei) & Ovis aries & $ 0.105$ & $ 0.089$ \\
+            Various & Ovis aries & $ 0.229$ & $ 0.196$ \\
+            Morocco & Ovis aries & $ 0.211$ & $ 0.206$ \\
+            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus & $ 0.723$ & $ 0.833$ \\
+            \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus & $ 0.265$ & $ 0.285$ \\
+            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus & $ 0.498$ & $ 0.547$ \\
+            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus & $ 0.352$ & $ 0.571$ \\
+            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus & $ 0.268$ & $ 0.265$ \\
+            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus & $ 0.784$ & $ 0.892$ \\
+            \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus & $ 0.322$ & $ 0.307$ \\
+            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus & $ 0.701$ & $ 0.825$ \\
+            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus & $ 0.257$ & $ 0.271$ \\
+            African & Homo sapiens & $ 0.317$ & $ 0.278$ \\
+            Admixed American & Homo sapiens & $ 0.380$ & $ 0.363$ \\
+            East Asian & Homo sapiens & $ 0.517$ & $ 0.499$ \\
+            European & Homo sapiens & $ 0.466$ & $ 0.456$ \\
+            South Asian & Homo sapiens & $ 0.433$ & $ 0.304$ \\
+            \bottomrule
+        \end{tabular}
+    \end{center}
+    Genes under adaptation retrieved from~\cite{latrille_genes_2023}.
+    Comparison of $\proba[\SphyBen\given \SpopBen ]$ while including divergence for the whole genome (control) and when excluding genes under adaptation (case).
+    The non-parametric Wilcoxon signed-rank test tests the null hypothesis that the distribution of the differences (case versus control) is symmetric about zero.
+    Applied to the paired samples (case and control), Wilcoxon signed-rank test results in $s=120$ with $\pvalue=0.027$ for one-sided test (case higher than control).
+    The proportion of beneficial non-adaptive mutations ($\proba[\SphyBen\given \SpopBen ]$) is higher when excluding genes under adaptation, consistent with our expectation that genes with uniformly conserved functions should fit better the nearly-neutral equilibrium model.
+
+    \newpage
+
+    \section{Discrete distribution of $\Spop$ at the population scale}
+
+    \subsection{polyDFE model D (discrete distribution)}
+    Additionally to including divergence, with also tested our prediction with polyDFE model D instead of model C.
+    In polyDFE model D, the DFE of non-synonymous mutations is given as a discrete DFE of $K$ categories (instead of a continuous distribution in model C), where the selection coefficients of each category $i$ ($1 \leq i \leq K$) are fixed parameters $\Spop_i$, and each value $\Spop_i$ has a probability $p_i$ (estimated), with $\sum_{i=1}^{K} p_i =1$.
+    We used $K=6$ with $\Spop_1 = -500$, $\Spop_2 = -4$, $\Spop_3 =-1$, $\Spop_4 = 0$, $\Spop_5 = 1$, $\Spop_6 = 4$.\\
+    For each class of selection $\Sphyclass$, the parameters $p_i$ ($i \in \{ 1 \leq i \leq 6 \}$) were used to compute $\proba [ \SpopDel \given  \Sphyclass] $, $\proba [ \SpopNeu \given \Sphyclass]$, and $\proba [ \SpopBen \given \Sphyclass]$ as:
+    \begin{align}
+        \proba [ \SpopDel \given  \Sphyclass] &= \proba [ \Spop < -1 \given \Sphyclass ] = p_1 + p_2 \label{eq:polyProbaDel-mD} \\
+        \proba [ \SpopNeu \given \Sphyclass] &= \proba [ -1 < \Spop < 1 \given \Sphyclass ] = p_3 + p_4 + p_5,  \\
+        \proba [ \SpopBen \given \Sphyclass] &= \proba [  \Spop > 1 \given \Sphyclass ] = p_6.  \label{eq:polyProbaAdv-mD}
+    \end{align}
+
+    \subsection{Probability for beneficial mutations to be non-adaptive}
+    \begin{center}
+        \captionof{table}{$\proba[\SphyBen\given \SpopBen ]$ when using a discrete DFE to estimate $\Spop$.}
+        \scriptsize
+        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
+            \toprule
+            Population & Species & $\Ne$ & $\proba[\SphyBen]$ & $\proba [ \SpopBen ]$ & $\frac{\proba[\SphyBen]}{\proba[ \SpopBen ]}$ & $\proba [ \SpopBen \given \SphyBen]$ & $\proba[\SphyBen\given \SpopBen ]$ \\
+            \midrule
+            \endhead
+            \midrule
+            \multicolumn{8}{r}{{Continued on next page}} \\
+            \midrule
+            \endfoot
+
+            \bottomrule
+            \endlastfoot
+            \rowcolor{LIGHTGREY} Equus c. & Equus caballus & $7.5\times 10^{4}$ & $ 0.012$ & $ 0.006$ & $ 2.050$ & $ 0.163$ & $ 0.334$ \\
+            Iran & Bos taurus & $5.6\times 10^{4}$ & $ 0.011$ & $ 0.005$ & $ 2.125$ & $ 0.133$ & $ 0.283$ \\
+            Uganda & Bos taurus & $1.3\times 10^{5}$ & $ 0.011$ & $ 0.010$ & $ 1.139$ & $ 0.140$ & $ 0.159$ \\
+            \rowcolor{LIGHTGREY} Australia & Capra hircus & $1.7\times 10^{5}$ & $ 0.011$ & $ 0.002$ & $ 5.637$ & $ 0.151$ & $ 0.850$ \\
+            \rowcolor{LIGHTGREY} France & Capra hircus & $1.9\times 10^{5}$ & $ 0.011$ & $ 0.002$ & $ 6.117$ & $ 0.154$ & $ 0.940$ \\
+            \rowcolor{LIGHTGREY} Iran (C. aegagrus) & Capra hircus & $1.9\times 10^{5}$ & $ 0.011$ & $ 0.002$ & $ 5.842$ & $ 0.156$ & $ 0.911$ \\
+            \rowcolor{LIGHTGREY} Iran & Capra hircus & $2.3\times 10^{5}$ & $ 0.011$ & $ 0.002$ & $ 6.400$ & $ 0.147$ & $ 0.943$ \\
+            \rowcolor{LIGHTGREY} Italy & Capra hircus & $1.9\times 10^{5}$ & $ 0.011$ & $ 0.002$ & $ 5.793$ & $ 0.155$ & $ 0.895$ \\
+            \rowcolor{LIGHTGREY} Morocco & Capra hircus & $2.2\times 10^{5}$ & $ 0.011$ & $ 0.003$ & $ 4.192$ & $ 0.150$ & $ 0.627$ \\
+            Iran & Ovis aries & $3.8\times 10^{5}$ & $ 0.012$ & $ 0.020$ & $ 0.584$ & $ 0.154$ & $ 0.090$ \\
+            Iran (O. orientalis) & Ovis aries & $4.5\times 10^{5}$ & $ 0.011$ & $ 0.021$ & $ 0.535$ & $ 0.148$ & $ 0.079$ \\
+            Iran (O. vignei) & Ovis aries & $3.7\times 10^{5}$ & $ 0.012$ & $ 0.020$ & $ 0.568$ & $ 0.151$ & $ 0.086$ \\
+            Various & Ovis aries & $4.1\times 10^{5}$ & $ 0.011$ & $ 0.021$ & $ 0.553$ & $ 0.152$ & $ 0.084$ \\
+            Morocco & Ovis aries & $ 4\times 10^{5}$ & $ 0.012$ & $ 0.022$ & $ 0.529$ & $ 0.153$ & $ 0.081$ \\
+            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus & $1.1\times 10^{5}$ & $ 0.009$ & $ 0.002$ & $ 5.152$ & $ 0.170$ & $ 0.877$ \\
+            \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus & $1.7\times 10^{5}$ & $ 0.009$ & $ 0.007$ & $ 1.266$ & $ 0.157$ & $ 0.199$ \\
+            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus & $1.4\times 10^{5}$ & $ 0.009$ & $ 0.002$ & $ 3.979$ & $ 0.161$ & $ 0.640$ \\
+            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus & $1.4\times 10^{5}$ & $ 0.009$ & $ 0.008$ & $ 1.201$ & $ 0.159$ & $ 0.191$ \\
+            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus & $1.5\times 10^{5}$ & $ 0.009$ & $ 0.003$ & $ 2.801$ & $ 0.165$ & $ 0.461$ \\
+            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus & $ 1\times 10^{5}$ & $ 0.009$ & $ 0.002$ & $ 5.361$ & $ 0.169$ & $ 0.908$ \\
+            \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus & $1.8\times 10^{5}$ & $ 0.009$ & $ 0.005$ & $ 1.912$ & $ 0.154$ & $ 0.294$ \\
+            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus & $1.2\times 10^{5}$ & $ 0.009$ & $ 0.002$ & $ 4.561$ & $ 0.165$ & $ 0.753$ \\
+            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus & $1.7\times 10^{5}$ & $ 0.009$ & $ 0.004$ & $ 2.661$ & $ 0.153$ & $ 0.406$ \\
+            African & Homo sapiens & $5.6\times 10^{4}$ & $ 0.010$ & $ 0.010$ & $ 0.997$ & $ 0.154$ & $ 0.154$ \\
+            Admixed American & Homo sapiens & $4.5\times 10^{4}$ & $ 0.010$ & $ 0.008$ & $ 1.206$ & $ 0.158$ & $ 0.190$ \\
+            East Asian & Homo sapiens & $ 4\times 10^{4}$ & $ 0.010$ & $ 0.007$ & $ 1.455$ & $ 0.163$ & $ 0.237$ \\
+            European & Homo sapiens & $4.2\times 10^{4}$ & $ 0.010$ & $ 0.007$ & $ 1.316$ & $ 0.167$ & $ 0.219$ \\
+            South Asian & Homo sapiens & $4.4\times 10^{4}$ & $ 0.010$ & $ 0.007$ & $ 1.340$ & $ 0.164$ & $ 0.219$ \\
+        \end{longtable*}
+    \end{center}
+    \begin{itemize}
+        \item $\Ne$ is the estimated effective population size.
+        \item $\proba [ \SphyBen ]$ (eq.~5) is the probability for a new mutation a non-adaptive beneficial mutation.
+        These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1, thus toward a more fit amino-acid.
+        \item $\proba [ \SpopBen ]$ (eq.~15) is the probability for a mutation to be beneficial.
+        These mutations have a selection coefficient at the population-scale larger than 1.
+        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial non-adaptive mutation at the phylogenetic scale (the \textit{precision}).
+        \item $\proba [ \SphyBen \given \SpopBen]$ (eq.~14) is the probability for a mutation to be non-adaptive given it is beneficial at the population scale (the \textit{recall}).
+        This probability is obtained using Bayes' formula.
+    \end{itemize}
+
+    \subsection{Precision and recall}
+    \captionof{table}{Precision and recall when using a discrete DFE to estimate $\Spop$.}
+    \begin{center}
+        \begin{adjustbox}{width=\textwidth}
+            \begin{tabular}{||l|l|r||r|r||r|r||r|r||}
+                \toprule
+                \multicolumn{3}{||c||}{} &
+                \multicolumn{2}{c||}{\shortstack{\textbf{Deleterious mutations} \\ $\bm{\SpopDel \coloneqq \Spop<-1}$ \\ $\bm{\SphyDel \coloneqq \Sphy<-1}$}} &
+                \multicolumn{2}{c||}{\shortstack{\textbf{Nearly-neutral mutations} \\ $\bm{\SpopNeu \coloneqq -1<\Spop<1}$ \\ $\bm{\SphyNeu \coloneqq -1<\Sphy<1}$}} &
+                \multicolumn{2}{c||}{\shortstack{\textbf{Beneficial mutations} \\ $\bm{\SpopBen \coloneqq \Spop>1}$ \\ $\bm{\SphyBen \coloneqq \Sphy>1}$}}
+                \\ \hline
+                \textbf{Population} &
+                \textbf{Species} &
+                $\bm{\Ne}$ &
+                \makecell{\textbf{Precision} \\ $\bm{\proba [\SpopDel \given \SphyDel]}$} &
+                \makecell{\textbf{Recall} \\ $\bm{\proba [\SphyDel \given \SpopDel]}$}           &
+                \makecell{\textbf{Precision}      \\ $\bm{\proba [\SpopNeu \given \SphyNeu]}$}                                    &
+                \makecell{\textbf{Recall}          \\ $\bm{\proba [\SphyNeu \given \SpopNeu]}$}                                  &
+                \makecell{\textbf{Precision}          \\ $\bm{\proba [\SpopBen \given \SphyBen]}$}          &
+                \makecell{\textbf{Recall}        \\ $\bm{\proba [\SphyBen \given \SpopBen]}$}
+                \\   \midrule
+                \rowcolor{LIGHTGREY} Equus c. & Equus caballus & $7.5\times 10^{4}$ & $ 0.911$ & $ 0.974$ & $ 0.645$ & $ 0.319$ & $ 0.163$ & $ 0.334$ \\
+                Iran & Bos taurus & $5.6\times 10^{4}$ & $ 0.895$ & $ 0.973$ & $ 0.639$ & $ 0.288$ & $ 0.133$ & $ 0.283$ \\
+                Uganda & Bos taurus & $1.3\times 10^{5}$ & $ 0.951$ & $ 0.974$ & $ 0.664$ & $ 0.492$ & $ 0.140$ & $ 0.159$ \\
+                \rowcolor{LIGHTGREY} Australia & Capra hircus & $1.7\times 10^{5}$ & $ 0.912$ & $ 0.984$ & $ 0.834$ & $ 0.386$ & $ 0.151$ & $ 0.850$ \\
+                \rowcolor{LIGHTGREY} France & Capra hircus & $1.9\times 10^{5}$ & $ 0.912$ & $ 0.983$ & $ 0.819$ & $ 0.381$ & $ 0.154$ & $ 0.940$ \\
+                \rowcolor{LIGHTGREY} Iran (C. aegagrus) & Capra hircus & $1.9\times 10^{5}$ & $ 0.928$ & $ 0.980$ & $ 0.767$ & $ 0.408$ & $ 0.156$ & $ 0.911$ \\
+                \rowcolor{LIGHTGREY} Iran & Capra hircus & $2.3\times 10^{5}$ & $ 0.955$ & $ 0.969$ & $ 0.616$ & $ 0.459$ & $ 0.147$ & $ 0.943$ \\
+                \rowcolor{LIGHTGREY} Italy & Capra hircus & $1.9\times 10^{5}$ & $ 0.911$ & $ 0.983$ & $ 0.822$ & $ 0.379$ & $ 0.155$ & $ 0.895$ \\
+                \rowcolor{LIGHTGREY} Morocco & Capra hircus & $2.2\times 10^{5}$ & $ 0.950$ & $ 0.976$ & $ 0.706$ & $ 0.468$ & $ 0.150$ & $ 0.627$ \\
+                Iran & Ovis aries & $3.8\times 10^{5}$ & $ 0.983$ & $ 0.958$ & $ 0.421$ & $ 0.796$ & $ 0.154$ & $ 0.090$ \\
+                Iran (O. orientalis) & Ovis aries & $4.5\times 10^{5}$ & $ 0.982$ & $ 0.961$ & $ 0.448$ & $ 0.806$ & $ 0.148$ & $ 0.079$ \\
+                Iran (O. vignei) & Ovis aries & $3.7\times 10^{5}$ & $ 0.974$ & $ 0.963$ & $ 0.480$ & $ 0.685$ & $ 0.151$ & $ 0.086$ \\
+                Various & Ovis aries & $4.1\times 10^{5}$ & $ 0.982$ & $ 0.964$ & $ 0.500$ & $ 0.822$ & $ 0.152$ & $ 0.084$ \\
+                Morocco & Ovis aries & $ 4\times 10^{5}$ & $ 0.983$ & $ 0.958$ & $ 0.387$ & $ 0.782$ & $ 0.153$ & $ 0.081$ \\
+                \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus & $1.1\times 10^{5}$ & $ 0.895$ & $ 0.987$ & $ 0.860$ & $ 0.351$ & $ 0.170$ & $ 0.877$ \\
+                \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus & $1.7\times 10^{5}$ & $ 0.925$ & $ 0.974$ & $ 0.653$ & $ 0.373$ & $ 0.157$ & $ 0.199$ \\
+                \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus & $1.4\times 10^{5}$ & $ 0.892$ & $ 0.980$ & $ 0.763$ & $ 0.320$ & $ 0.161$ & $ 0.640$ \\
+                \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus & $1.4\times 10^{5}$ & $ 0.939$ & $ 0.982$ & $ 0.770$ & $ 0.469$ & $ 0.159$ & $ 0.191$ \\
+                \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus & $1.5\times 10^{5}$ & $ 0.916$ & $ 0.976$ & $ 0.680$ & $ 0.345$ & $ 0.165$ & $ 0.461$ \\
+                \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus & $ 1\times 10^{5}$ & $ 0.895$ & $ 0.989$ & $ 0.884$ & $ 0.358$ & $ 0.169$ & $ 0.908$ \\
+                \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus & $1.8\times 10^{5}$ & $ 0.930$ & $ 0.971$ & $ 0.604$ & $ 0.361$ & $ 0.154$ & $ 0.294$ \\
+                \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus & $1.2\times 10^{5}$ & $ 0.898$ & $ 0.986$ & $ 0.839$ & $ 0.353$ & $ 0.165$ & $ 0.753$ \\
+                \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus & $1.7\times 10^{5}$ & $ 0.912$ & $ 0.975$ & $ 0.676$ & $ 0.335$ & $ 0.153$ & $ 0.406$ \\
+                African & Homo sapiens & $5.6\times 10^{4}$ & $ 0.945$ & $ 0.976$ & $ 0.627$ & $ 0.431$ & $ 0.154$ & $ 0.154$ \\
+                Admixed American & Homo sapiens & $4.5\times 10^{4}$ & $ 0.936$ & $ 0.977$ & $ 0.641$ & $ 0.397$ & $ 0.158$ & $ 0.190$ \\
+                East Asian & Homo sapiens & $ 4\times 10^{4}$ & $ 0.943$ & $ 0.977$ & $ 0.648$ & $ 0.422$ & $ 0.163$ & $ 0.237$ \\
+                European & Homo sapiens & $4.2\times 10^{4}$ & $ 0.945$ & $ 0.977$ & $ 0.644$ & $ 0.429$ & $ 0.167$ & $ 0.219$ \\
+                South Asian & Homo sapiens & $4.4\times 10^{4}$ & $ 0.945$ & $ 0.977$ & $ 0.644$ & $ 0.430$ & $ 0.164$ & $ 0.219$ \\
+                \bottomrule
+            \end{tabular}
+        \end{adjustbox}
+    \end{center}
+    \begin{itemize}
+        \item $\Ne$ is the estimated effective population size.
+        \item \textit{Precision} is the estimation of the selection coefficient at population scale ($\Spop$) given that $\Sphy$ is known.
+        \item \textit{Recall} is the estimation of $\Sphy$ given selection coefficient at the population scale ($\Spop$) is known.
+        \item \textit{Recall} for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is the probability for a mutation to be non-adaptive given it is beneficial at the population scale.
+    \end{itemize}
+
+    Altogether, comparing this table other estimations, we acknowledge that the exact proportion of non-adaptive among all beneficial ones is dependent on the model used to estimate the DFE.
+    However, we can still see that non-adaptive beneficial mutations are positively selected compared to neutral and deleterious ones, and this result is not sensitive to the underlying DFE at the population scale.
+
+    \newpage
+
+    \newpage
+
+    \printbibliography
 \end{document}

### 2024-06-19 manuscript/compile.sh
Renamed diff files

@@ -1,1 +1,3 @@
-latexdiff main.tex main-revision.tex > diff.tex
+latexdiff main-PNAS.tex main-PNAS-revision.tex > diff-PNAS-revision.tex
+latexdiff main-PNAS-revision.tex main-PNAS-revision-2.tex > diff-PNAS-revision-2.tex
+latexdiff main-PLOS.tex main.tex > diff-PLOS-revision.tex

### 2024-09-26 manuscript/main-PLOS-revision.tex
Updated manuscipt for PLOSG revision

--- 2024-06-19 manuscript/main-biorxiv-2.tex
@@
 \usepackage[backend=biber,eprint=false,isbn=false,url=false,intitle=true,style=nature,date=year]{biblatex}
-\addbibresource{codon_models.bib}
+\addbibresource{references.bib}
 
@@
 Our work confirms that deleterious substitutions are accumulating in mammals and are being reverted, generating a balance in which genomes are damaged and restored simultaneously at different loci.
-We observe that beneficial non-adaptive mutations represent between 15\% and 45\% of all beneficial mutations in 24 of 28 populations analyzed, showing that a substantial part of ongoing positive selection is not driven solely by adaptation to environmental change in mammals.
+We observe that beneficial non-adaptive mutations represent between 15\% and 45\% of all beneficial mutations in 24 of 28 populations analyzed, suggesting that a substantial part of ongoing positive selection is not driven solely by adaptation to environmental change in mammals.
     \end{abstract}
@@
     Evolutionary adaptation is tightly linked to environmental change and species responding to this change~\cite{merrell_adaptive_1994, gavrilets_adaptive_2009}.
+    Such environmental changes are either abiotic (e.g. temperature, humidity) or biotic (e.g. pressure from predators or viruses~\cite{enard_viruses_2016}).
     For adaptation to occur, there must be variation within populations, which mostly appears via mutations in the DNA sequence.
@@
     A beneficial mutation is thus more likely than a neutral mutation to invade the population and reach fixation, resulting in a substitution at the species level.
+
     Upon environmental change, because adaptive beneficial mutations toward new fitness optima are more likely, the number of substitutions also increases (fig.~\ref{fig:fitness-landscape}A).
@@
     The mutation-selection framework permits to link the patterns of substitution along a phylogenetic tree with the underlying fitness landscape~\cite{halpern_evolutionary_1998, mccandlish_modeling_2014}.
-    Such mutation-selection models applied to protein-coding DNA sequences at the codon level allow us to estimate relative fitnesses for all amino acids for each site of the sequence, explicitly assuming that the underlying fitness landscape is stable along the phylogenetic tree~\cite{rodrigue_mechanistic_2010, tamuri_estimating_2012, rodrigue_detecting_2017}.
+    Such mutation-selection models applied to protein-coding DNA sequence alignments at the codon level allow us to estimate relative fitnesses for all amino acids for each site of the sequence, explicitly assuming that the underlying fitness landscape is stable along the phylogenetic tree~\cite{rodrigue_mechanistic_2010, tamuri_estimating_2012, rodrigue_detecting_2017}.
     Moreover, effective population size ($\Ne$) is considered constant along the phylogenetic tree precisely because of the fixed fitness landscape assumption, the consequences of which are detailed in the Discussion.
     Importantly, because mutation-selection codon models at the phylogenetic scale are based on population-genetics equations, their estimates of selection coefficients are directly interpretable as fitness effects at the population scale; and because they work at the DNA level, we are able to account for mutational bias in DNA and structure of the genetic code.
-    The model further integrates the shared evolutionary history between samples and their divergence, which, together, allow us to estimate fitness effects in mammalian phylogenetic trees even though sequences are not independent samples and might not represent the equilibrium distribution of amino acids (see section \ref{subsec:s-phylogeny-method} in Materials \& Methods, model parameters in section S1 and fig.~S1).
+    The model further integrates the shared evolutionary history between samples and their divergence, which, together, allow us to estimate fitness effects in sequence alignments even though sequences are not independent samples and might not represent the equilibrium distribution of amino acids (see section \ref{subsec:s-phylogeny-method} in Materials \& Methods, model parameters in section S1 and fig.~S1).
 
-    Theoretically, we can thus use large-scale genomic data to assess whether the fitness estimated at the phylogenetic scale predicts the fitness effect at the population scale for both deleterious and beneficial non-adaptive mutations.
-    The placental mammals represent an excellent study system to perform such analysis.
+    Accordingly, fitting the mutation-selection model to a multi-species sequence alignment allows us to obtain relative fitnesses for all amino acids (fig.~\ref{fig:method}A).
+    The difference in fitness between a pair of amino acids allows us to predict whether any mutation would be a deleterious mutation toward a less fit amino acid, a nearly-neutral mutation, or a mutation toward a known fitter amino acid constituting thus a beneficial non-adaptive mutation (fig.~\ref{fig:method}B).
+    We can hence use large-scale genomic data to test whether such fitnesses estimated at the phylogenetic scale predict the fitness effects at the population scale.
+    The placental mammals represent an excellent study system to perform such an analysis.
     Having originated $\sim$102 million years ago, they diversified quickly~\cite{foley_genomic_2023}.
@@
 
-    For each gene, fitting the mutation-selection model to the multi-species sequence alignment, assuming that the underlying fitness landscape is stable along the phylogenetic tree, allows us to obtain relative fitnesses for all amino acids for each site of the alignment (fig.~\ref{fig:method}A).
-    Given these relative fitnesses ($F$) for each amino acid, the difference in fitness between a pair of amino acids is the scaled selection coefficient ($\Sphy = \Delta F$), which is formally the product of the selection coefficient at the individual level ($s$) and the effective population size ($\Ne$), as $\Sphy = 4 \Ne \times s$.
-The value of $\Sphy$ informs us on the strength of selection exerted on amino acids changes.
-    Thus, according to its $\Sphy$ value, we can classify any mutation as either a deleterious mutation toward a less fit amino acid ($\SphyDel \coloneqq \Sphy < -1$), a nearly-neutral mutation ($\SphyNeu \coloneqq -1 < \Sphy <1$), or a mutation toward a known fitter amino acid constituting thus a beneficial non-adaptive mutation ($\SphyBen \coloneqq \Sphy > 1$).
-
-    Having identified which potential DNA changes represent beneficial non-adaptive mutations (fig.~\ref{fig:method}B), we retrieved polymorphism data from 28 wild and domesticated populations belonging to six genera (\textit{Equus}, \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus}, and \textit{Homo}) to assess the presence of beneficial non-adaptive mutations at the population scale.
-    We focused on mutations currently segregating within populations and substitutions in the terminal branches, and checked if any of these observed changes were indeed beneficial (fig.~\ref{fig:method}C-E).
+    Having identified which potential DNA changes represent beneficial non-adaptive mutations (fig.~\ref{fig:method}A-B), we retrieved polymorphism data from 28 wild and domesticated populations belonging to six genera (\textit{Equus}, \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus}, and \textit{Homo}) to assess the presence of beneficial non-adaptive mutations at the population scale.
+    We focused on both mutations currently segregating within populations and on substitutions in the terminal branches, and checked if any of these observed changes were indeed beneficial (fig.~\ref{fig:method}C-E).
     A similar approach demonstrated the presence of beneficial non-adaptive mutations in humans~\cite{moses_inferring_2009, fischer_germline_2011} and in plants~\cite{chen_hunting_2021}.
@@
 
-    We first quantified the likelihood of any DNA mutation to be a beneficial non-adaptive mutation, that is, whenever a DNA mutation increases fitness under a stable fitness landscape ($\SphyBen$).
-    Subsequently, by quantifying the total amount of beneficial mutations in the current population across all types of DNA mutations ($\SphyDel$, $\SphyNeu$ and $\SphyBen$), we could tease apart beneficial non-adaptive from adaptive mutations resulting from a change in the fitness landscape.
+    We first quantified the likelihood of any DNA mutation to be a beneficial non-adaptive mutation, that is, whenever a DNA mutation increases fitness under a stable fitness landscape.
+    Subsequently, by quantifying the total amount of beneficial mutations in the current population across all types of DNA mutations, we could tease apart beneficial non-adaptive from adaptive mutations resulting from a change in the fitness landscape.
     Altogether, in this study, by integrating large-scale genomic datasets at both phylogenetic and population scales, we propose a way to explicitly quantify the contribution of beneficial non-adaptive mutations to positive selection across the entire exome of the six genera (figs.~\ref{fig:method}F-G).
@@
     We only considered mutations fixed in a population as substitutions in the corresponding branch by discarding mutations segregating in our population samples.
-    We classified each substitution identified in the terminal branches as either $\SphyDel$, $\SphyNeu$, or $\SphyBen$ depending on its $\Sphy$ value obtained at the phylogenetic scale (fig.~\ref{fig:method}A-C).
-    Because estimation $\Sphy$ was based on the assumption that the fitness landscape is stable across mammals, $\SphyBen$ mutations (i.e., with $\Sphy>1$) bring the bearer of this mutation toward an amino acid predicted to be fitter across mammals.
+    For each substitution identified in the terminal branches we obtained its $\Sphy$ value such as predicted at the mammalian scale (fig.~\ref{fig:method}A-B).
+    We could classify each substitution as either deleterious $\SphyDel \coloneqq \Sphy < -1$), nearly-neutral ($\SphyNeu \coloneqq -1 < \Sphy <1$), or beneficial ($\SphyBen \coloneqq \Sphy > 1$)
+    Because $\Sphy$ values were based on the assumption that the fitness landscape is stable across mammals, $\SphyBen$ mutations (i.e., with $\Sphy>1$) bring the bearer of this mutation toward an amino acid predicted to be fitter across mammals.
     Importantly, the mammalian alignment used to estimate the amino acid fitness landscape did not include the six focal genera and their sister species.
@@
     Among all the substitutions found in each terminal branch, between 10 and 13\% were $\SphyBen$, while $\SphyBen$ mutations only represent between 0.9 and 1.2\% of all non-synonymous mutations (table~S1 and fig.~\ref{fig:homo-afr-results}A-B for humans).
+    Of note, if we were to assume a stationary mutation-selection-drift equilibrium in the terminal lineage, we would expect a symmetric proportion of positively ($\SphyBen$) and negatively ($\SphyDel$) selected substitutions if there were no adaptation.
+    The lack of symmetry along the terminal branches then provides a means to estimate the frequency of non-adaptive beneficial substitutions.
+    Mathematically, twice the fraction of $\SphyBen$ substitutions is an estimate of this rate.
+    This rate is highly consistent across lineages (table~S1) and suggests an overall frequency of nearly neutral substitutions due to consistent long-term selection pressures, mutation and drift of approximately 20\% of all substitutions (20\%-26\% across species).
+
     Furthermore, since in principle, $\SphyBen$ mutations are bound to reach fixation more often than neutral mutations, we calculated the $\dnds$ ratio of non-synonymous over synonymous divergence for all terminal lineages, focusing on the non-synonymous changes predicted as $\SphyBen$ mutations ($\dn(\SphyBen) / \ds$).
     We obtained values between 1.17 and 1.75 in the different lineages (table~S2), meaning that $\SphyBen$ mutations reach fixation slightly more frequently than synonymous mutations that are supposed to be neutral, consistent with these $\SphyBen$ mutations being weakly beneficial.
+    Such an observation is consistent with the premise that $\SphyBen$ mutations are weakly beneficial, translating to a scaled selection coefficient between 0.32 and 1.24 (table~S2).
+    Finding $\dn(\SphyBen) / \ds > 1$ for these sites confirms that these sites are closer to optimality at the end of the branch than at the beginning.
+    Even though the beneficial effect of these mutations does not come from an environmental change, it does not change the fact that they have contributed positively to the population’s fitness.
+    It is just that at mutation-selection-drift equilibrium, the increase in fitness at these sites is offset by deleterious substitutions elsewhere in the genome so that there is no net adaptation.
 
-    This result further indicates that using $\dnds$ as an estimate of adaptation is biased due to the presence of beneficial non-adaptive mutations among the non-synonymous substitutions.
+    This result further indicates that using $\dnds$ as an estimate of purifying selection is biased (overestimated) due to the presence of beneficial non-adaptive mutations among the non-synonymous substitutions.
     By discarding all beneficial non-adaptive mutations we can obtain an estimate of $\dnds$ which is not inflated.
@@
 
-    First, $\SphyBen$ SNPs are spread across the genomes and not strongly associated to the ontology terms of their respective genes (table~S4, fig.~S4).
+    First, SNPs classified as $\SphyBen$ are spread across the genomes and not strongly associated to the ontology terms of their respective genes (table~S4, fig.~S4).
     In humans, some SNPs have been associated with specific clinical prognosis terms obtained by clinical evaluation of the impact of variants on human Mendelian disorders~\cite{landrum_clinvar_2018}.
-    Although this classification also relies on deep protein alignments and therefore cannot be considered an independent result from our own, it does provide a consistency check if the effect of a mutation on human health is in line with its fitness effect predicted by our method.
+    Although this classification also relies on deep protein alignments and therefore cannot be considered an independent result from our own, it does provide a consistency check if the effect of a mutation on human health is in line with its fitness effect predicted by our method~\cite{grimm_evaluation_2015}.
     Therefore, we investigated whether the non-synonymous SNPs classified as $\SphyDel$ or $\SphyBen$ showed enrichment in specific clinical terms compared to SNPs classified as $\SphyNeu$.
@@
     For instance, deleterious SNPs usually segregate at lower frequencies because of purifying selection, which tends to remove them from the population (fig.~\ref{fig:homo-afr-results}C for humans).
-    By gathering information across many SNPs, it is possible to estimate the distribution of fitness effects (DFE) at the population scale, taking synonymous SNPs as a neutral expectation~\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009, galtier_adaptive_2016, tataru_inference_2017}.
-    From the estimated DFE, we can derive the proportion of beneficial mutations ($\ProbaPopBen$), nearly-neutral mutations ($\ProbaPopNeu$) and deleterious mutations ($\ProbaPopDel$) at the population scale (see section~\ref{subsec:s-polymorphism-method} in Materials \& Methods).
+    By gathering information across many SNPs, it is possible to estimate the distribution of fitness effects at the population scale, taking synonymous SNPs as a neutral expectation~\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009, galtier_adaptive_2016, tataru_inference_2017}.
+    From these estimated fitness effects, we can derive the proportion of beneficial mutations ($\ProbaPopBen$), nearly-neutral mutations ($\ProbaPopNeu$) and deleterious mutations ($\ProbaPopDel$) at the population scale (see section~\ref{subsec:s-polymorphism-method} in Materials \& Methods, figs.~S5-S8).
     These approaches offer a unique opportunity to contrast selection coefficients estimated at the population scale ($\Spop$) and at the phylogenetic scale ($\Sphy$).
@@
     Using correlation analyses that accounted for phylogenetic relationship (see section \ref{subsec:correlation-diversity} in Materials \& Methods), we found that higher $\Ne$ was associated with a smaller proportion of nearly-neutral mutations ($r^2=0.31$, $p=0.001$, fig.~\ref{fig:diversity}A).
-    This result follows the prediction of the nearly-neutral theory and suggests that in populations with higher diversity (e.g.,~\textit{Bos} or \textit{Ovis}), discrimination between beneficial and deleterious mutations is more likely to occur (figs.~S3-S5).
+    This result follows the prediction of the nearly-neutral theory and suggests that in populations with higher diversity (e.g.,~\textit{Bos} or \textit{Ovis}), discrimination between beneficial and deleterious mutations is more likely to occur (figs.~S9-S12).
     Conversely, many more mutations are effectively neutral in populations with lower diversity (e.g.,~\textit{Homo}).
@@
     In other words, the \textit{recall} value quantifies the number of beneficial mutations restoring damaged genomes instead of creating adaptive innovations.
-    Across the 28 populations, this proportion is in the range of 11--82\% (table~\ref{table:proba}).
+    Across the 28 populations, this proportion is in the range of 11--82\% (table~\ref{table:proba}), with a mean of 30\%.
+    Accounting for phylogenetic relationships, we found no correlation between the proportion of beneficial non-adaptive mutations and estimates of $\Ne$ based on genetic diversity ($r^2=0.00$, $p=0.772$, fig.~\ref{fig:diversity}B).
 
-    Additionally, we controlled that these estimations are not affected by SNP mispolarization (figs.~S6-S7).
-    Moreover, because the phylogenetic mutation-selection codon model should fit better for genes with uniformly conserved functions, as a control, we filtered out genes under pervasive adaptation~\cite{latrille_genes_2023}, and indeed we found an increase in the proportion of beneficial mutations that are non-adaptive ($\proba [ \SphyBen  \given  \SpopBen]$), consistent with our expectation (Wilcoxon signed-rank, $s=80$, $p=0.002$, table~S8).
+    We additionally performed controls and simulations to ensure our results were robust.
+    First, we controlled that these estimations were not affected by SNP mispolarization (figs.~S13-S14).
+    Second, we performed simulations at the population-genetic level and confirmed that our method was able to recover the proportion of beneficial mutations that are non-adaptive in synthetic polymorphism datasets (fig.~S15).
+    Third, we ran our analysis filtering out CpG mutations and obtained values of $\proba [ \SphyBen \given \SpopBen]$ in the range of 5--27\%, with a mean of 14\% (tables~S8-9 and fig.~S16-17), providing more conservative estimates.
+    Finally, because the phylogenetic mutation-selection codon model should fit better for genes with uniformly conserved functions, we filtered out genes under pervasive adaptation~\cite{latrille_genes_2023} as a control.
+    In this subset of the exome, containing genes with a more stable fitness landscape, we found an increase in the proportion of beneficial mutations that are non-adaptive (Wilcoxon signed-rank, $s=80$, $p=0.002$, table~S10), consistent with our expectation that beneficial mutations occur more frequently in genes under changing fitness landscapes.
+
+    \subsection*{Selection in the terminal lineage and in populations}
+
+    As an alternative to relying solely on currently segregating mutations to quantify selection, one can leverage both polymorphism within a population and substitutions in the terminal lineage to estimate the distribution of fitness effects (DFE).
+    Hence, we estimated \textit{precision} and \textit{recall} as done previously, but now including the number of substitutions per site as input for the DFE estimators (see \ref{subsec:s-polymorphism-method} in Materials \& Methods and fig.~S18).
+    When including substitutions in the terminal lineage, estimates of $\proba [ \SphyBen \given \SpopBen]$ are in the 10--78\% range with a mean of 36\% (table~S11-12), and 19 out of 28 estimates fall between 15\% and 45\%.
+
+    Additionally, we controlled that these estimations were not affected by SNP mispolarization (fig.~S19).
+    We also filtered out genes under pervasive adaptation, and again found an increase in $\proba [ \SphyBen \given \SpopBen]$, consistent with our expectation (Wilcoxon signed-rank, $s=120$, $p=0.027$, table~S13).
+    We assessed the impact of fitting the same functional form of DFE to the three different categories of changes $\SphyDel$, $\SphyNeu$ and $\SphyBen$.
+    To this aim we computed the total amount of current selection by fitting either a single DFE on the whole dataset or by summing the other three independent DFEs.
+    These disjoint estimates are well correlated, with a goodness of fit $r^2={0.95, 0.89, 0.82}$ for $\proba [\SpopDel]$, $\proba [\SpopNeu]$ and $\proba [\SpopBen]$, respectively (figs.~S20-22).
+    Finally, we evaluated the effect of fitting a parametric functional form for the DFE.
+    As implemented in \textcite{tataru_inference_2017}, the DFE is a mixture between a reflected gamma distribution and an exponential distribution (eq.~\ref{eq:parametric-dfe}, section~\ref{subsec:precisison_recall} in Materials \& Methods).
+    Instead of using such a continuous DFE, we also tested our prediction with a non-parametric functional form for the DFE, obtaining estimates of $\proba [ \SphyBen \given \SpopBen]$ in the 8--94\% range, with a mean of 43\% (tables~S14-15).
 
@@
     These amino-acid fitness landscapes allow us to predict any mutation’s selection coefficient ($\Sphy$) along a protein-coding sequence.
-    We have compared these selective effects to observations at the population level (figs.~S8-10), and by doing so, we have confirmed that mutations predicted to be deleterious ($\SphyDel \coloneqq \Sphy < -1$) are generally purified away in extant populations.
+    We have compared these selective effects to observations at the population level, and by doing so, we have confirmed that mutations predicted to be deleterious ($\SphyDel \coloneqq \Sphy < -1$) are generally purified away in extant populations.
     Our results concur with previous studies showing that SIFT scores~\cite{ng_sift_2003, vaser_sift_2016}, based on amino acid alignments across species, also inform on the deleterious fitness effects exerted at the population scale~\cite{chen_hunting_2021}.
-    However, contrary to SIFT scores, our mutation-selection model is parameterized by a fitness function such that changes are directly interpretable as fitness effects (see also section S7).
-    In this regard, an interesting prediction of our model is that some deleterious mutations reach fixation due to genetic drift, while beneficial non-adaptive mutations are restoring states of higher fitness.
+    However, contrary to SIFT scores, our mutation-selection model is parameterized by a fitness function such that changes are directly interpretable as fitness effects (see also section S5).
+    In this regard, an interesting prediction of our model is that some deleterious mutations reach fixation due to genetic drift, while beneficial non-adaptive mutations restore states of higher fitness.
     We have tested this hypothesis and have found that a substantial part of these predicted non-adaptive mutations ($\SphyBen \coloneqq \Sphy > 1 $) are indeed beneficial in extant populations.
@@
     Hence, we can correctly estimate the extent of adaptive evolution only if we account for the number of beneficial non-adaptive mutations~\cite{keightley_what_2010, rice_evolutionarily_2015}.
-    Altogether, we argue that we should dissociate positive selection from adaptive evolution and limit the use of adaptive mutations to those that are associated with adaptation to environmental change as such~\cite{charlesworth_other_2007, mustonen_fitness_2009}.
+    Here instead, we argue that we should dissociate positive selection from adaptive evolution and limit the use of adaptive mutations to those that are associated with adaptation to environmental change as such~\cite{charlesworth_other_2007, mustonen_fitness_2009, mustonen_fitness_2010}.
+
+    \subsection*{Assumptions and methodological limitations}
+
+    The exact estimation of the contribution of beneficial non-adaptive mutations to positive selection relies on some hypotheses at both the phylogenetic and population scales and is sensitive to methodological limitations.
+    Indeed, data quality and potentially inadequate modeling choices of both the fitness landscape (at the phylogenetic scale) and fitness effects (at the population scale) might also lead to missed predictions~\cite{moutinho_variation_2019}.
+    In practice, we obtained different values of the proportion of non-adaptive beneficial mutations depending on i) the filtering or not of CpG mutations~\cite{eyre-walker_how_2014}, ii) whether we included substitutions in the terminal lineage along with within-population polymorphisms to estimate fitness effects~\cite{tataru_inference_2017}, and iii) the model used to infer the fitness effects.
+    It appears that our estimation can be sensitive to model misspecification and overall, while we provide an order of magnitude for the contribution of beneficial non-adaptive mutations to positive selection, methodological improvement on the estimation of the DFE is needed to increase the precision of this value.
+
+    To be conservative, we considered mutations as adaptive if they were detected as being under positive selection at the population scale despite them being either incorrectly predicted as deleterious ($\SphyDel$) or nearly-neutral ($\SphyNeu \coloneqq -1 < \Sphy <1$) from the amino-acid mammalian fitnesses.
+    An example of an incorrectly predicted deleterious mutation ($\SphyDel$) from its fitness landscape could be an amino acid having always been deleterious across mammals, but being advantageous ($\SpopBen$) in the current species due to environmental changes or a major shift in their fitness landscape (e.g.
+domestication)
+    To visualize an example of a wrongly predicted nearly-neutral mutation, we can first imagine a site where only hydrophilic amino acids are accepted because of the protein properties (e.g.
+a surface site of a globular protein).
+    Let us then assume that such a site is also a target for viruses, hence promoting amino-acid changes which modify the site's viral affinity~\cite{enard_viruses_2016}.
+    Given the selective pressure favoring amino-acid change, but restricting the possibilities to hydrophilic amino acids, most hydrophilic amino acids will likely be visited along the phylogenetic tree and the mutation-selection model will give high and similar fitnesses to all of them.
+    In such a case, any mutation between hydrophilic amino acids will be wrongly predicted as nearly-neutral ($\SphyNeu$), while it is in fact adaptive.
+    In summary, under a changing fitness landscapes~\cite{mustonen_molecular_2008}, our phylogenetic mutation-selection model takes an average over fitness changes observed along the phylogeny, causing beneficial mutations ($\SpopBen$) to be predicted as either deleterious ($\SphyDel$) or nearly-neutral ($\SphyNeu$), therefore mechanically reducing $\proba [ \SphyBen \given \SpopBen]$, and making our estimate conservative.
+
+    \subsection*{Convergent adaptation}
+
+    If there are several substitutions toward the same amino acid along the mammalian tree (see fig.~S3), our mutation-selection model cannot formally distinguish between a scenario where mammals have fixed deleterious mutations that are reverted in several lineages, from more complex scenarios involving convergent adaptation across mammals.
+    In a first scenario, repeated changes of fitness landscapes in the same direction could occur along several lineages, leading to repeated substitutions in multiple lineages (parallel or convergent adaptation).
+    In a second scenario, an environmental change that occurred near the root of placental mammals ($\sim$100 Mys ago), to which extant populations are currently responding independently through weakly adaptive mutations, could also lead to repeated substitutions toward the same amino acids.
+    Importantly, we would usually expect adaptive convergent mutations to be linked to particular converging phenotypes across mammals, and hence, they should not massively affect the whole genome as we find (table~S4, fig.
+S4).
+    Moreover, after filtering out genes usually associated to recurrent adaptation (e.g. immune genes), we recover an even higher proportion of beneficial non-adaptive mutations (table~S8).
+    For these reasons, we argue that the signal of predictable positive selection we recover in extant population is indeed mainly driven by non-adaptive evolution.
 
@@
     Overall, we expect the proportion of beneficial non-adaptive mutations to be more dependent on $\Ne$’s long-term expansions and contractions than on the short-term ones~\cite{charlesworth_other_2007,huber_determining_2017}.
-    Accounting for phylogenetic relationships, we found no correlation between the proportion of beneficial non-adaptive mutations and estimates of $\Ne$ based on genetic diversity ($r^2=0.00$, $p=0.772$, fig.~\ref{fig:diversity}B).
 
@@
     In other words, by assuming a constant $\Ne$, we are underpowered to detect beneficial non-adaptive mutations since amino acids will have more similar fitnesses.
-    As a consequence, some of the beneficial non-adaptive mutations currently segregating in population will be incorrectly classified as nearly-neutral by the mutation-selection model, and thus be wrongly interpreted as adaptive.
+    As a consequence, some of the beneficial non-adaptive mutations currently segregating in population will be incorrectly classified as nearly-neutral by the mutation-selection model, and thus be wrongly interpreted as adaptive (see previous section).
     This ultimately results in lower estimates of the proportion of beneficial non-adaptive mutations.
@@
     Our model assumes that amino-acid fitness landscapes are site-specific and also independent of one another, whereas under pervasive epistasis, the fitness effect of any mutation at a particular site would depend on the amino acids present at other sites.
-    Epistasis has been shown to play a role in the evolution of protein-coding genes, with amino-acid residues in contact within a protein or between proteins tending to co-evolve~\cite{morcos_directcoupling_2011, marks_protein_2012, starr_epistasis_2016}.
+    Epistasis is common for mutations that influence the protein’s physical properties (e.g.
+conformation, stability, or affinity for ligands) or might arise due to nonlinear relationship between the protein’s physical properties and fitness~\cite{starr_epistasis_2016}.
+    Regardless of its origin, epistasis has been shown to play a role in the evolution of protein-coding genes, with amino-acid residues in contact within a protein or between proteins tending to co-evolve~\cite{morcos_directcoupling_2011, marks_protein_2012, starr_epistasis_2016}.
     Particularly, the residues in contact co-evolve to become more compatible with each other generating an entrenchment~\cite{goldstein_nonadaptive_2015, goldstein_sequence_2017, park_epistatic_2022}.
@@
     Our results imply that the fitness effects of new mutations are mostly conserved across mammalian orthologs, in agreement with other studies showing that for conserved orthologs with similar structures and functions, models without epistasis provide a reasonable estimate of fitness effects in protein coding genes~\cite{youssef_consequences_2020, vigue_deciphering_2022}.
-
-    \subsection*{Other assumptions and methodological limitations}
-
-    The exact estimation of the contribution of beneficial non-adaptive mutations to positive selection relies on some hypotheses at both the phylogenetic and population scales and is sensitive to methodological limitations.
-    Indeed, data quality and potentially inadequate modeling choices of both the fitness landscape (at the phylogenetic scale) and fitness effects (at the population scale) might also lead to missed prediction~\cite{moutinho_variation_2019}.
-    To be conservative, we considered that any mutation under positive selection at the population scale ($\SpopBen$) but not predicted as such at the phylogenetic scale (not $\SphyBen$) is potentially an adaptation.
-    In practice, we obtained different values of the proportion of non-adaptive beneficial mutations depending on the model used to infer the fitness effects at the population scale, and the filtering or not of CpG mutations~\cite{eyre-walker_how_2014} (tables~S8-14).
-    It appears that our estimation can be sensitive to model misspecification and overall, while we provide an order of magnitude for the contribution of beneficial non-adaptive mutations to positive selection, methodological improvement on the estimation of the distribution of fitness effects is needed to increase the precision of this value.
-
-    Importantly, if there are several substitutions toward the same amino acid along the mammalian tree, (see fig.~S3) our mutation-selection model cannot distinguish between a scenario where mammals have fixed deleterious mutations that are reverted in several lineages, from more complex scenarios involving adaptation.
-    In a first scenario, repeated changes of fitness landscapes in the same direction could occur along several lineages, leading to repeated substitutions in multiple lineages (parallel or convergent adaptation).
-    Of note, repeated substitutions that we observe (section~S2) are spread across the phylogeny and are usually shared by distant species/clades with very different lifestyles and environments.
-    It is therefore unlikely that all the beneficial mutations that we classified as non-adaptive (between 15 and 45\%) would result from parallel adaptation.
-    In a second scenario, an environmental change that occurred near the root of placental mammals ($\sim$100 Mys ago), to which extant populations are currently responding through weakly adaptive mutations could also lead to repeated substitutions toward the same amino acids.
-    However, for this latter hypothesis to totally explain our results, it would imply that a large proportion of weakly adaptive mutations arising in present day populations of mammals are the late consequence of $\sim$100 Mys-old environmental changes.
-    While we cannot rule out that some cases of the latter scenarios are included in our results, we argue that the hypothesis of non-adaptive evolution on a fixed fitness landscape of functionally constrained proteins remains more parsimonious for most cases.
+    Conceptually, the framework presented here, with the addition of a more complex protein fitness landscape at the phylogenetic scale, could be used to infer the relative contribution of compensatory mutations to non-adaptive and adaptive evolution.
 
@@
 
-    A long-standing debate in molecular evolution is whether the variations we observe between species in protein-coding genes are primarily due to nearly-neutral mutations reaching fixation by drift or primarily due to adaptation~\cite{kimura_evolutionary_1968,jensen_importance_2019,gillespie_substitution_1994,ohta_nearly_1992}.
-    Here we provide evidence that in mammalian orthologs, many substitutions occur through fixation of both deleterious mutations and beneficial non-adaptive mutations.
-    However, detecting adaptation above this background of nearly-neutral substitutions remains a challenge~\cite{kimura_evolutionary_1968,ohta_development_1996}.
+    A long-standing debate in molecular evolution is whether the variation we observe between species in protein-coding genes is primarily due to nearly-neutral mutations reaching fixation by drift or primarily due to adaptation~\cite{kimura_evolutionary_1968,ohta_nearly_1992,gillespie_substitution_1994,jensen_importance_2019}.
+    Measuring the ``rate of adaptation'' in proteins, as pioneered by \textcite{mcdonald_adaptative_1991}, has been central to inform this debate~\cite{galtier_half_2024}.
+    However, the McDonald \& Kreitman test detects signatures of accelerated evolution in a given terminal branch compared to an expectation based on polymorphism present in the population.
+It considers the fraction of substitutions that fix too quickly as ``adaptive''~\cite{mcdonald_adaptative_1991, smith_adaptive_2002, welch_estimating_2006} despite there being other processes that can lead to their fixation~\cite{galtier_adaptation_2007,rousselle_influence_2019,joseph_increased_2024a} and some of these substitutions being beneficial but non-adaptive~\cite{hartl_compensatory_1996, charlesworth_other_2007, mustonen_fitness_2009, jones_shifting_2017}.
+    Here, the expectation is built on the pattern of substitutions across a phylogeny compared to the fitness effects that can be estimated from both substitutions in a terminal lineage and polymorphism in populations.
+    Moreover, the goal is not to detect a fraction of beneficial substitution (i.e.
+``adaptive'' substitutions for \textcite{mcdonald_adaptative_1991}), but to estimate the proportion of non-adaptive mutations among beneficial ones.
 
-    One first strategy is precisely to use a nearly-neutral substitution model as a null model of evolution.
+    We provide evidence that in mammalian orthologs, many substitutions occur through fixation of both deleterious mutations and beneficial non-adaptive mutations.
+    Detecting adaptation above this background of substitutions remains a challenge~\cite{kimura_evolutionary_1968, ohta_development_1996}.
+    Mathematically, the surplus of positive selection due to an externally-driven changing fitness landscape is called \textit{fitness flux}, and requires experimentally measuring the selection coefficient of each mutation in each genetic background.
+    The \textit{fitness flux} can be estimated if either the substitutions history is known~\cite{mustonen_fitness_2009} or changes of frequency in currently segregating variants~\cite{mustonen_fitness_2010}.
+    Without experimentally measured selection coefficients, another strategy is precisely to use a nearly-neutral substitution model as a null model of evolution.
     Under a strictly neutral evolution of protein-coding sequence, we expect the ratio of non-synonymous over synonymous substitutions ($\dnds$) to be equal to one.
@@
     Using a stable fitness landscape as a null model of evolution, thus accounting for selective constraints exerted on the different amino acids, increased the statistical power in testing for adaptation~\cite{latrille_genes_2023}.
-    Instead of relying solely on summary statistics (such as $\dnds$ or $\omega_0$), another strategy to detect adaptation is to include changes in the fitness landscapes inherently within the mutation-selection framework~\cite{tamuri_mutationselection_2021}.
+    Instead of relying solely on summary statistics (such as $\dnds$ or $\omega_0$), another strategy to detect adaptation is to include changes in the fitness landscapes inherently within the mutation selection framework, either with small changes along the phylogeny ~\cite{tamuri_mutationselection_2021} or either by allowing fitness to change on subsets of branches ~\cite{kazmi_detecting_2019, stolyarova_senescence_2020}.
     Such mechanistic models could be more general than site-specific fitness landscapes, including epistasis and changing fitness landscapes~\cite{goldstein_sequence_2017, stolyarova_senescence_2020}.
@@
 
-    Here, we have provided empirical evidence that an evolutionary model assuming a stable fitness landscape at the mammalian scale allows us to predict the fitness effects of mutations in extant populations and individuals, acknowledging the balance between deleterious and beneficial non-adaptive mutations.
+    We have provided empirical evidence that an evolutionary model assuming a stable fitness landscape at the mammalian scale allows us to predict the fitness effects of mutations in extant populations and individuals, acknowledging the balance between deleterious and beneficial non-adaptive mutations.
     We argue that such a model would represent a null expectation for the evolution of protein-coding genes in the absence of adaptation.
     Altogether, because a substantial part of positive selection can be explained by beneficial non-adaptive mutations, but not its entirety, we argue that the mammalian exome is shaped by both adaptive and non-adaptive processes, and that none of them alone is sufficient to explain the observed patterns of changes.
-    In that sense, to avoid conflating beneficial mutations with adaptive evolution, the term ``adaptation`` should retain its original meaning associated with a change in the underlying fitness landscape and be modelled as such.
+    In that sense, to avoid conflating beneficial mutations with adaptive evolution, the term ``adaptation`` should retain its original meaning associated with a change in the underlying fitness landscape and be modelled as such~\cite{mustonen_fitness_2009, mustonen_fitness_2010}.
 
+    \newpage
     \section{Materials \& Methods}
@@
     In our subsequent derivation the source ($a$) and target ($b$) codons as well as the site ($i$) are implicit and thus never explicitly written.
+
+    The scaled selection coefficient ($\Sphy = \Delta F$) is formally the product of the selection coefficient at the individual level ($s$) and the effective population size ($\Ne$), as $\Sphy = 4 \Ne \times s$.
+The value of $\Sphy$ informs us on the strength of selection exerted on amino acids changes.
+    Thus, according to its $\Sphy$ value, we can classify any mutation as either a deleterious mutation toward a less fit amino acid ($\SphyDel \coloneqq \Sphy < -1$), a nearly-neutral mutation ($\SphyNeu \coloneqq -1 < \Sphy <1$), or a mutation toward a known fitter amino acid, constituting thus a beneficial non-adaptive mutation ($\SphyBen \coloneqq \Sphy > 1$).
 
@@
 
-    To obtain a quantitative estimate of the distribution of selection coefficients for each category of SNPs, we used the polyDFE model~\cite{tataru_inference_2017, tataru_polydfe_2020}.
+    To obtain a quantitative estimate of the distribution of selection coefficients for each category of SNPs, we used the \textit{polyDFE} model~\cite{tataru_inference_2017, tataru_polydfe_2020}.
     This model uses the count of derived alleles to infer the distribution of fitness effects (DFE).
@@
     However, estimating a single $\Spop$ for all sampled mutations is biologically unrealistic, and a DFE of mutations is usually assumed~\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009}.
-    The polyDFE\cite{tataru_inference_2017, tataru_polydfe_2020} software implements a mixture of a $\Gamma$ and exponential distributions to model the DFE of non-synonymous mutations, while synonymous mutations are considered neutral.
+    The \textit{polyDFE}\cite{tataru_inference_2017, tataru_polydfe_2020} software implements a mixture of a $\Gamma$ and exponential distributions to model the DFE of non-synonymous mutations, while synonymous mutations are considered neutral.
     The model estimates the parameters $\DelMean$, $b$, $p_b$ and $\AdvMean$ for non-synonymous mutations as:
@@
     \begin{equation}
+        \label{eq:parametric-dfe}
         \phi \left( \Spop; \DelMean , b, p_b, \AdvMean \right) =
@@
 
-    PolyDFE requires one SFS for non-synonymous mutations and one for synonymous mutations (neutral expectation), as well as the number of sites on which each SFS was sampled.
+    \textit{PolyDFE} requires one SFS for non-synonymous mutations and one for synonymous mutations (neutral expectation), as well as the number of sites on which each SFS was sampled.
     For populations containing more than $8$ individuals, the SFS was subsampled down to $16$ chromosomes ($8$ diploid individuals) without replacement (hyper-geometric distribution) to alleviate the effect of different sampling depths in the 28 populations.
@@
     The number of sites on which each SFS was sampled is given by $L(\Sphyclass)$ for the non-synonymous SFS and $L_{\text{syn}}$ for the synonymous SFS respectively.
-    For each class of selection $\Sphyclass$, once fitted to the data using maximum likelihood with polyDFE, the parameters of the DFE $\left( \DelMean , b, p_b, \AdvMean \right)$ were used to compute $\proba [ \SpopDel \given  \Sphyclass] $, $\proba [ \SpopNeu \given \Sphyclass]$, and $\proba [ \SpopBen \given \Sphyclass]$ as:
+    For each class of selection $\Sphyclass$, once fitted to the data using maximum likelihood with \textit{polyDFE}, the parameters of the DFE $\left( \DelMean , b, p_b, \AdvMean \right)$ were used to compute $\proba [ \SpopDel \given  \Sphyclass] $, $\proba [ \SpopNeu \given \Sphyclass]$, and $\proba [ \SpopBen \given \Sphyclass]$ as:
 
     \begin{align}
-        \proba [ \SpopDel \given  \Sphyclass] &= \proba [ \Spop < -1 \given \Sphyclass ] = \left( 1 - p_b \right) \int_{1}^{+\infty} f_{\Gamma}(\Spop; -\DelMean, b) \der \Spop, \label{eq:polyProbaDel} \\
-        \proba [ \SpopNeu \given \Sphyclass] &= \proba [ -1 < \Spop < 1 \given \Sphyclass ] = p_b \int_{0}^{1} f_{e}(\Spop; \AdvMean) \der \Spop + \left( 1 - p_b \right) \int_{0}^{1} f_{\Gamma}(\Spop; -\DelMean, b) \der \Spop, \\
+        \proba [ \SpopDel \given  \Sphyclass] &= \proba [ \Spop < -1 \given \Sphyclass ] = \left( 1 - p_b \right) \int_{-\infty}^{-1} f_{\Gamma}(-\Spop; -\DelMean, b) \der \Spop, \label{eq:polyProbaDel} \\
+        \proba [ \SpopNeu \given \Sphyclass] &= \proba [ -1 < \Spop < 1 \given \Sphyclass ] = \left( 1 - p_b \right) \int_{-1}^{0} f_{\Gamma}(-\Spop; -\DelMean, b) \der \Spop + p_b \int_{0}^{1} f_{e}(\Spop; \AdvMean) \der \Spop, \\
         \proba [ \SpopBen \given \Sphyclass] &= \proba [ \Spop > 1 \given \Sphyclass] = p_b \int_{1}^{+\infty} f_{e}(\Spop; \AdvMean) \der \Spop. \label{eq:polyProbaAdv}
     \end{align}
+
+    Rather than relying solely on currently segregating mutations to quantify selection, \textit{polyDFE} can leverage both divergence and polymorphism to estimate the parameters of the DFE.
+    We can thus add four more inputs to \textit{polyDFE}: $D \left( \Sphyclass \right) $, $L \left( \Sphyclass \right)$, $D_{\text{syn}}$ and $L_{\text{syn}}$ such as defined in the previous section.
+    Because the estimates of DFE are different with this method, we naturally obtained different values of $\proba [ \SpopDel \given  \Sphyclass] $, $\proba [ \SpopNeu \given \Sphyclass]$, and $\proba [ \SpopBen \given \Sphyclass]$.
 
@@
     For \textit{Equus}, we used $u$ as estimated in \textcite{orlando_recalibrating_2013} ($u=7.24\times10^{-9}$).
-    Because a correlation must account for phylogenetic relationship and non-independence of samples, we fitted a Phylogenetic Generalized Linear Model in \textit{R} with the package \texttt{caper}~\cite{orme_caper_2013}.
+    Because a correlation must account for phylogenetic relationship and non-independence of samples, we fitted a Phylogenetic Generalized Linear Model in \textit{R} with the method \texttt{pgls} with default settings from the package \texttt{caper}~\cite{orme_caper_2013}.
     The mammalian dated tree was obtained from TimeTree~\cite{kumar_timetree_2017} and pruned to include only the species analysed in this study, with multi-furcation of the different populations from each species placed at the same divergence time as the species (section S4.1).
@@
             (A \& B) For a given codon position of a protein-coding DNA sequence, amino acids (x-axis) have different fitness values (y-axis).
-            Under a fluctuating fitness landscape (A), these fitnesses change with time.
+            Under a changing fitness landscape (A), these fitnesses fluctuate with time.
             The protein sequence follows the moving target defined by the amino-acid fitnesses.

### 2024-09-26 copy_artworks.sh

@@ -17,7 +17,13 @@
 \cp -rf ./experiments/3bins-mC-nodiv/results/Theta.MutSel.neg.stacked.pdf ./manuscript/artworks/Theta.neg.stacked.pdf
 \cp -rf ./experiments/3bins-mC-nodiv/results/Theta.MutSel.pos.stacked.pdf ./manuscript/artworks/Theta.pos.stacked.pdf
 \cp -rf ./experiments/3bins-mC-nodiv/regression-MutSel/results.distance.recall_pos.scatter.pdf ./manuscript/artworks/results.distance.recall_pos.scatter.pdf
+\cp -rf ./experiments/3bins-mC-nodiv/regression-MutSel/results.reg.P-Sneg.scatter.pdf ./manuscript/artworks/results.reg.neg.scatter.pdf
+\cp -rf ./experiments/3bins-mC-nodiv/regression-MutSel/results.reg.P-Sweak.scatter.pdf ./manuscript/artworks/results.reg.weak.scatter.pdf
+\cp -rf ./experiments/3bins-mC-nodiv/regression-MutSel/results.reg.P-Spos.scatter.pdf ./manuscript/artworks/results.reg.pos.scatter.pdf
 \cp -rf ./experiments/3bins-mC/regression-MutSel/results.distance.recall_pos.scatter.pdf ./manuscript/artworks/results.distance.recall_pos.div.scatter.pdf
+\cp -rf ./experiments/3bins-mC/regression-MutSel/results.reg.P-Sneg.scatter.pdf ./manuscript/artworks/results.reg.neg.div.scatter.pdf
+\cp -rf ./experiments/3bins-mC/regression-MutSel/results.reg.P-Sweak.scatter.pdf ./manuscript/artworks/results.reg.weak.div.scatter.pdf
+\cp -rf ./experiments/3bins-mC/regression-MutSel/results.reg.P-Spos.scatter.pdf ./manuscript/artworks/results.reg.pos.div.scatter.pdf
 \cp -rf ./data_processed/upset_plot/bins3Mask0.9.pdf ./manuscript/artworks/UpSet_plot.pdf
 \cp -rf ./data_processed/trimmed_tree_sample_all.tsv.tree ./manuscript/artworks/PGLM.tree
[…]

### 2024-12-05 manuscript/main-PLOS-revision-bbl.tex
Prepare files for revision

--- 2024-09-26 manuscript/main-PLOS-revision.tex
@@
-%! BibTeX Compiler = biber
-%TC:ignore
 \documentclass{article}
@@
 
-\usepackage{biorxiv}
-\usepackage[backend=biber,eprint=false,isbn=false,url=false,intitle=true,style=nature,date=year]{biblatex}
-\addbibresource{references.bib}
+\renewenvironment{abstract}
+{
+    \centerline
+    {\large \bfseries \scshape Abstract}
+    \begin{quote}
+    }
+    {
+    \end{quote}
+}
+
+\def\keywordname{{\bfseries \emph Keywords}}%
+\def\keywords#1{\par\addvspace\medskipamount{\rightskip=0pt plus1cm
+\def\and{\ifhmode\unskip\nobreak\fi\ $\cdot$
+}\noindent\keywordname\enspace\ignorespaces#1\par}}
+
+%\usepackage{biorxiv}
 
@@
 \usepackage{orcidlink}
-
-\newcommand{\NS}[1]{\textcolor{red}{\textbf{\emph{[NS: #1]}}}}
+\usepackage[verbose=true,letterpaper]{geometry}
+\AtBeginDocument{
+    \newgeometry{
+        textheight=9in,
+        textwidth=6.5in,
+        top=1in,
+        headheight=14pt,
+        headsep=25pt,
+        footskip=30pt
+    }
+}
+
+\bibliographystyle{plos2015}
 
@@
 \title{Estimating the proportion of beneficial mutations that are not adaptive in mammals}
-\rhead{\scshape Beneficial yet non-adaptive mutations}
 
 \author{
-    \large
-    \textbf{T.
+    \small \textbf{T.
 {Latrille}$^{1\dag}$\orcidlink{0000-0002-9643-4668}, J.
@@
 {Salamin}$^{1}$\orcidlink{0000-0002-3963-4954}}\\
-    \normalsize
-    $^{1}$Department of Computational Biology, Université de Lausanne, Lausanne, Switzerland\\
-    $^{2}$Laboratoire de Biométrie et Biologie Evolutive, UMR5558, Université Lyon 1, Villeurbanne, France \\
-    $^{\dag}$These authors contributed equally to this work\\
-    \texttt{\href{mailto:thibault.latrille@ens-lyon.org}{thibault.latrille@ens-lyon.org}} \\
+    \small $^{1}$Department of Computational Biology, Université de Lausanne, Lausanne, Switzerland\\
+    \small $^{2}$Laboratoire de Biométrie et Biologie Evolutive, UMR5558, Université Lyon 1, Villeurbanne, France \\
+    \small $^{\dag}$These authors contributed equally to this work\\
+    \small  \texttt{\href{mailto:thibault.latrille@ens-lyon.org}{thibault.latrille@ens-lyon.org}} \\
 }
-
-% The submission checklist is available at:
-% https://docs.google.com/document/d/1SScaqEAgZGpeaXxpWPDh1NOLaDDLLmkGOYgaGvbY-4o/edit#
-% Response to reviewers at:
-% https://docs.google.com/document/d/1kzt4uf6GgmuAVHx6-LQyzFuee9biyaWoMV6RNO6lSzI/edit?usp=sharing
 
@@
 
-%TC:endignore
     \begin{abstract}
@@
 
-    \section*{Significance statement}
+    \section*{Author summary}
     The extent to which adaptation to changing environments is shaping genomes is a central question in molecular evolution.
@@
     The variable proportions between populations can be explained by the effective number of individuals in the population ($\Ne$), a major driver of selection efficacy.
-    Moreover, estimates of mutation rate per generation ($u$), from \textcite{bergeron_evolution_2023} and \textcite{orlando_recalibrating_2013}, and Watterson’s $\theta$ obtained from the synonymous SFS as in \textcite{achaz_frequency_2009}, allow us to obtain $\Ne$ through $\Ne=\theta/4 u)$.
+    Moreover, estimates of mutation rate per generation ($u$), from Bergeron \textit{et al.}~\cite{bergeron_evolution_2023} and Orlando \textit{et al.}~\cite{orlando_recalibrating_2013}, and Watterson’s $\theta$ obtained from the synonymous SFS as in Achaz~\cite{achaz_frequency_2009}, allow us to obtain $\Ne$ through $\Ne=\theta/4 u)$.
     Using correlation analyses that accounted for phylogenetic relationship (see section \ref{subsec:correlation-diversity} in Materials \& Methods), we found that higher $\Ne$ was associated with a smaller proportion of nearly-neutral mutations ($r^2=0.31$, $p=0.001$, fig.~\ref{fig:diversity}A).
@@
     Finally, we evaluated the effect of fitting a parametric functional form for the DFE.
-    As implemented in \textcite{tataru_inference_2017}, the DFE is a mixture between a reflected gamma distribution and an exponential distribution (eq.~\ref{eq:parametric-dfe}, section~\ref{subsec:precisison_recall} in Materials \& Methods).
+    As implemented in Tataru \textit{et al.}~\cite{tataru_inference_2017}, the DFE is a mixture between a reflected gamma distribution and an exponential distribution (eq.~\ref{eq:parametric-dfe}, section~\ref{subsec:precisison_recall} in Materials \& Methods).
     Instead of using such a continuous DFE, we also tested our prediction with a non-parametric functional form for the DFE, obtaining estimates of $\proba [ \SphyBen \given \SpopBen]$ in the 8--94\% range, with a mean of 43\% (tables~S14-15).
@@
     A long-standing debate in molecular evolution is whether the variation we observe between species in protein-coding genes is primarily due to nearly-neutral mutations reaching fixation by drift or primarily due to adaptation~\cite{kimura_evolutionary_1968,ohta_nearly_1992,gillespie_substitution_1994,jensen_importance_2019}.
-    Measuring the ``rate of adaptation'' in proteins, as pioneered by \textcite{mcdonald_adaptative_1991}, has been central to inform this debate~\cite{galtier_half_2024}.
+    Measuring the ``rate of adaptation'' in proteins, as pioneered by McDonald \& Kreitman~\cite{mcdonald_adaptative_1991}, has been central to inform this debate~\cite{galtier_half_2024}.
     However, the McDonald \& Kreitman test detects signatures of accelerated evolution in a given terminal branch compared to an expectation based on polymorphism present in the population.
@@
     Moreover, the goal is not to detect a fraction of beneficial substitution (i.e.
-``adaptive'' substitutions for \textcite{mcdonald_adaptative_1991}), but to estimate the proportion of non-adaptive mutations among beneficial ones.
+``adaptive'' substitutions for McDonald \& Kreitman~\cite{mcdonald_adaptative_1991}), but to estimate the proportion of non-adaptive mutations among beneficial ones.
 
@@
 
-    Protein-coding DNA sequence alignments in placental mammals and their corresponding gene trees come from the \href{https://www.orthomam.univ-montp2.fr}{OrthoMaM} database and were processed as in \textcite{latrille_genes_2023}.
+    Protein-coding DNA sequence alignments in placental mammals and their corresponding gene trees come from the \href{https://www.orthomam.univ-montp2.fr}{OrthoMaM} database and were processed as in Latrille \textit{et al.}~\cite{latrille_genes_2023}.
     OrthoMaM contains a total of $116$ mammalian reference sequences in v10c~\cite{ranwez_orthomam_2007, douzery_orthomam_2014, scornavacca_orthomam_2019}.
@@
     We used the Bayesian software \textit{BayesCode} (\url{https://github.com/ThibaultLatrille/bayescode}, v1.3.1) to estimate the selection coefficients for each protein-coding gene in the mammalian dataset.
-    We ran the MCMC algorithm implemented in BayesCode for $2,000$ generations as described in \textcite{latrille_genes_2023}.
+    We ran the MCMC algorithm implemented in BayesCode for $2,000$ generations as described in Latrille \textit{et al.}~\cite{latrille_genes_2023}.
     For each gene, after discarding a burn-in period of $1,000$ generations of MCMC, we obtained posterior mean estimates (over the $1,000$ generations left of MCMC) of the mutation rate matrix ($\UniDimArray{\mu}$) as well as the $20$ amino-acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$.
@@
     In total, we analyzed 28 populations across the 6 different species with polymorphism data.
-    The data was processed as described in \textcite{latrille_genes_2023}.
+    The data was processed as described in Latrille \textit{et al.}~\cite{latrille_genes_2023}.
 
@@
     \label{subsec:correlation-diversity}
-    Genetic diversity estimator Watterson's $\thetaSyn$ was obtained for each population from the synonymous SFS as in \textcite{achaz_frequency_2009}.
+    Genetic diversity estimator Watterson's $\thetaSyn$ was obtained for each population from the synonymous SFS as in Achaz~\cite{achaz_frequency_2009}.
     For each popuation, $\Ne$ was estimated from the equation $\Ne=\thetaSyn / (4 \times u)$, where $u$ is the mutation rate per generation.
-    Estimates for $u$ were averaged per species across the pedigree-based estimation in \textcite{bergeron_evolution_2023} for \textit{Homo}, \textit{Bos}, \textit{Capra} and \textit{Chlorocebus}.
+    Estimates for $u$ were averaged per species across the pedigree-based estimation in~\cite{bergeron_evolution_2023} for \textit{Homo}, \textit{Bos}, \textit{Capra} and \textit{Chlorocebus}.
     For \textit{Ovis} we used the estimated $u$ of \textit{Capra}.
-    For \textit{Equus}, we used $u$ as estimated in \textcite{orlando_recalibrating_2013} ($u=7.24\times10^{-9}$).
+    For \textit{Equus}, we used $u$ as estimated in Orlando \textit{et al.}~\cite{orlando_recalibrating_2013} ($u=7.24\times10^{-9}$).
     Because a correlation must account for phylogenetic relationship and non-independence of samples, we fitted a Phylogenetic Generalized Linear Model in \textit{R} with the method \texttt{pgls} with default settings from the package \texttt{caper}~\cite{orme_caper_2013}.
@@
 
-%TC:ignore
-    \printbibliography
-%TC:endignore
+    \begin{thebibliography}{10}
+
+        \bibitem{darwin_origin_1859}
+        Darwin C.
+        \newblock On the {{Origin}} of {{Species}} by {{Means}} of {{Natural
+        Selection}}, or the {{Preservation}} of {{Favoured Races}} in the
+            {{Struggle}} for {{Life}}. vol. 220.
+        \newblock John Murray; 1859.
+
+        \bibitem{merrell_adaptive_1994}
+        Merrell DJ.
+        \newblock The {{Adaptive Seascape}}: {{The Mechanism}} of {{Evolution}}.
+        \newblock U of Minnesota Press; 1994.
+
+        \bibitem{gavrilets_adaptive_2009}
+        Gavrilets S, Losos JB.
+        \newblock Adaptive {{Radiation}}: {{Contrasting Theory}} with {{Data}}.
+        \newblock Science. 2009;323(5915):732--737.
+        \newblock doi:{10.1126/science.1157966}.
+
+        \bibitem{enard_viruses_2016}
+        Enard D, Cai L, Gwennap C, Petrov DA.
+        \newblock Viruses Are a Dominant Driver of Protein Adaptation in Mammals.
+        \newblock eLife. 2016;5:e12469.
+        \newblock doi:{10.7554/eLife.12469}.
+
+        \bibitem{mcdonald_adaptative_1991}
+        McDonald JH, Kreitman M.
+        \newblock Adaptative Protein Evolution at {{Adh}} Locus in {{Drosophila}}.
+        \newblock Nature. 1991;351(6328):652--654.
+        \newblock doi:{10.1038/351652a0}.
+
+        \bibitem{smith_adaptive_2002}
+        Smith NGC, {Eyre-Walker} A.
+        \newblock Adaptive Protein Evolution in {{Drosophila}}.
+        \newblock Nature. 2002;415(6875):1022--1024.
+        \newblock doi:{10.1038/4151022a}.
+
+        \bibitem{welch_estimating_2006}
+        Welch JJ.
+        \newblock Estimating the {{Genomewide Rate}} of {{Adaptive Protein Evolution}}
+        in {{Drosophila}}.
+        \newblock Genetics. 2006;173(2):821--837.
+        \newblock doi:{10.1534/genetics.106.056911}.
+
+        \bibitem{yang_statistical_2000}
+        Yang Z, Bielawski JR.
+        \newblock Statistical Methods for Detecting Molecular Adaptation.
+        \newblock Trends in Ecology and Evolution. 2000;15(12):496--503.
+        \newblock doi:{10.1016/S0169-5347(00)01994-7}.
+
+        \bibitem{eyre-walker_genomic_2006}
+        {Eyre-Walker} A.
+        \newblock The Genomic Rate of Adaptive Evolution.
+        \newblock Trends in Ecology \& Evolution. 2006;21(10):569--575.
+        \newblock doi:{10.1016/j.tree.2006.06.015}.
+
+        \bibitem{moutinho_variation_2019}
+        Moutinho AF, Bataillon T, Dutheil JY.
+        \newblock Variation of the Adaptive Substitution Rate between Species and
+        within Genomes.
+        \newblock Evolutionary Ecology. 2019;34(3):315--338.
+        \newblock doi:{10.1007/s10682-019-10026-z}.
+
+        \bibitem{lynch_mutation_2023}
+        Lynch M.
+        \newblock Mutation Pressure, Drift, and the Pace of Molecular Coevolution.
+        \newblock Proceedings of the National Academy of Sciences.
+        2023;120(27):e2306741120.
+        \newblock doi:{10.1073/pnas.2306741120}.
+
+        \bibitem{charlesworth_other_2007}
+        Charlesworth J, {Eyre-Walker} A.
+        \newblock The Other Side of the Nearly Neutral Theory, Evidence of Slightly
+        Advantageous Back-Mutations.
+        \newblock Proceedings of the National Academy of Sciences.
+        2007;104(43):16992--16997.
+        \newblock doi:{10.1073/pnas.0705456104}.
+
+        \bibitem{mustonen_fitness_2009}
+        Mustonen V, L{\"a}ssig M.
+        \newblock From Fitness Landscapes to Seascapes: Non-Equilibrium Dynamics of
+        Selection and Adaptation.
+        \newblock Trends in genetics. 2009;25(3):111--119.
+        \newblock doi:{10.1016/j.tig.2009.01.002}.
+
+        \bibitem{jones_shifting_2017}
+        Jones CT, Youssef N, Susko E, Bielawski JP.
+        \newblock Shifting Balance on a Static Mutation--Selection Landscape: A Novel
+        Scenario of Positive Selection.
+        \newblock Molecular Biology and Evolution. 2017;34(2):391--407.
+        \newblock doi:{10.1093/molbev/msw237}.
+
+        \bibitem{ohta_nearly_1992}
+        Ohta T.
+        \newblock The Nearly Neutral Theory of Molecular Evolution.
+        \newblock Annual Review of Ecology and Systematics. 1992;23(1992):263--286.
+
+        \bibitem{gillespie_ohta_1995}
+        Gillespie JH.
+        \newblock On {{Ohta}}'s Hypothesis: {{Most}} Amino Acid Substitutions Are
+        Deleterious.
+        \newblock Journal of Molecular Evolution. 1995;40(1):64--69.
+        \newblock doi:{10.1007/BF00166596}.
+
+        \bibitem{hartl_compensatory_1996}
+        Hartl DL, Taubes CH.
+        \newblock Compensatory Nearly Neutral Mutations: {{Selection}} without
+        Adaptation.
+        \newblock Journal of Theoretical Biology. 1996;182(3):303--309.
+        \newblock doi:{10.1006/jtbi.1996.0168}.
+
+        \bibitem{sella_application_2005}
+        Sella G, Hirsh AE.
+        \newblock The Application of Statistical Physics to Evolutionary Biology.
+        \newblock Proceedings of the National Academy of Sciences of the United States
+        of America. 2005;102(27):9541--9546.
+        \newblock doi:{10.1073/pnas.0501865102}.
+
+        \bibitem{cvijovic_fate_2015}
+        Cvijovi{\'c} I, Good BH, Jerison ER, Desai MM.
+        \newblock Fate of a Mutation in a Fluctuating Environment.
+        \newblock Proceedings of the National Academy of Sciences.
+        2015;112(36):E5021--E5028.
+        \newblock doi:{10.1073/pnas.1505406112}.
+
+        \bibitem{piganeau_estimating_2003}
+        Piganeau G, {Eyre-Walker} A.
+        \newblock Estimating the Distribution of Fitness Effects from {{DNA}} Sequence
+        Data: {{Implications}} for the Molecular Clock.
+        \newblock Proceedings of the National Academy of Sciences of the United States
+        of America. 2003;100(18):10335--10340.
+        \newblock doi:{10.1073/pnas.1833064100}.
+
+        \bibitem{chi_detecting_2020}
+        Chi PB, Kosater WM, Liberles DA.
+        \newblock Detecting {{Signatures}} of {{Positive Selection}} against a
+            {{Backdrop}} of {{Compensatory Processes}}.
+        \newblock Molecular Biology and Evolution. 2020;37(11):3353--3362.
+        \newblock doi:{10.1093/molbev/msaa161}.
+
+        \bibitem{bazykin_changing_2015}
+        Bazykin GA.
+        \newblock Changing Preferences: Deformation of Single Position Amino Acid
+        Fitness Landscapes and Evolution of Proteins.
+        \newblock Biology letters. 2015;11(10):20150315.
+        \newblock doi:{10.1098/rsbl.2015.0315}.
+
+        \bibitem{moses_inferring_2009}
+        Moses AM, Durbin R.
+        \newblock Inferring {{Selection}} on {{Amino Acid Preference}} in {{Protein
+        Domains}}.
+        \newblock Molecular Biology and Evolution. 2009;26(3):527--536.
+        \newblock doi:{10.1093/molbev/msn286}.
+
+        \bibitem{fischer_germline_2011}
+        Fischer A, Greenman C, Mustonen V.
+        \newblock Germline {{Fitness-Based Scoring}} of {{Cancer Mutations}}.
+        \newblock Genetics. 2011;188(2):383--393.
+        \newblock doi:{10.1534/genetics.111.127480}.
+
+        \bibitem{chen_hunting_2021}
+        Chen J, Bataillon T, Gl{\'e}min S, Lascoux M.
+        \newblock Hunting for Beneficial Mutations: Conditioning on {{SIFT}} Scores
+        When Estimating the Distribution of Fitness Effect of New Mutations.
+        \newblock Genome Biology and Evolution. 2021;doi:{10.1093/gbe/evab151}.
+
+        \bibitem{halpern_evolutionary_1998}
+        Halpern AL, Bruno WJ.
+        \newblock Evolutionary Distances for Protein-Coding Sequences: Modeling
+        Site-Specific Residue Frequencies.
+        \newblock Molecular Biology and Evolution. 1998;15(7):910--917.
+        \newblock doi:{10.1093/oxfordjournals.molbev.a025995}.
+
+        \bibitem{mccandlish_modeling_2014}
+        McCandlish DM, Stoltzfus A.
+        \newblock Modeling Evolution Using the Probability of Fixation: {{History}} and
+        Implications.
+        \newblock Quarterly Review of Biology. 2014;89(3):225--252.
+        \newblock doi:{10.1086/677571}.
+
+        \bibitem{rodrigue_mechanistic_2010}
+        Rodrigue N, Philippe H.
+        \newblock Mechanistic Revisions of Phenomenological Modeling Strategies in
+        Molecular Evolution.
+        \newblock Trends in Genetics. 2010;26(6):248--252.
+        \newblock doi:{10.1016/j.tig.2010.04.001}.
+
+        \bibitem{tamuri_estimating_2012}
+        Tamuri AU, Goldstein RA.
+        \newblock Estimating the Distribution of Selection Coefficients from
+        Phylogenetic Data Using Sitewise Mutation-Selection Models.
+        \newblock Genetics. 2012;190(3):1101--1115.
+        \newblock doi:{10.1534/genetics.111.136432}.
+
+        \bibitem{rodrigue_detecting_2017}
+        Rodrigue N, Lartillot N.
+        \newblock Detecting Adaptation in Protein-Coding Genes Using a {{Bayesian}}
+        Site- Heterogeneous Mutation-Selection Codon Substitution Model.
+        \newblock Molecular Biology and Evolution. 2017;34(1):204--214.
+        \newblock doi:{10.1093/molbev/msw220}.
+
+        \bibitem{foley_genomic_2023}
+        Foley NM, Mason VC, Harris AJ, Bredemeyer KR, Damas J, Lewin HA, et~al.
+        \newblock A Genomic Timescale for Placental Mammal Evolution.
+        \newblock Science. 2023;380(6643):eabl8189.
+        \newblock doi:{10.1126/science.abl8189}.
+
+        \bibitem{howe_ensembl_2021}
+        Howe KL, Achuthan P, Allen J, Allen J, {Alvarez-Jarreta} J, Amode MR, et~al.
+        \newblock Ensembl 2021.
+        \newblock Nucleic Acids Research. 2021;49(D1):D884--D891.
+        \newblock doi:{10.1093/nar/gkaa942}.
+
+        \bibitem{ranwez_orthomam_2007}
+        Ranwez V, Delsuc F, Ranwez S, Belkhir K, Tilak MK, Douzery EJ.
+        \newblock {{OrthoMaM}}: {{A}} Database of Orthologous Genomic Markers for
+        Placental Mammal Phylogenetics.
+        \newblock BMC Evolutionary Biology. 2007;7(1):1--12.
+        \newblock doi:{10.1186/1471-2148-7-241}.
+
+        \bibitem{scornavacca_orthomam_2019}
+        Scornavacca C, Belkhir K, Lopez J, Dernat R, Delsuc F, Douzery EJP, et~al.
+        \newblock {{OrthoMaM}} V10: {{Scaling-up}} Orthologous Coding Sequence and Exon
+        Alignments with More than One Hundred Mammalian Genomes.
+        \newblock Molecular Biology and Evolution. 2019;36(4):861--862.
+        \newblock doi:{10.1093/molbev/msz015}.
+
+        \bibitem{rodrigue_mutationselection_2010}
+        Rodrigue N, Philippe H, Lartillot N.
+        \newblock Mutation-Selection Models of Coding Sequence Evolution with
+        Site-Heterogeneous Amino Acid Fitness Profiles.
+        \newblock Proceedings of the National Academy of Sciences of the United States
+        of America. 2010;107(10):4629--34.
+        \newblock doi:{10.1073/pnas.0910915107}.
+
+        \bibitem{landrum_clinvar_2018}
+        Landrum MJ, Lee JM, Benson M, Brown GR, Chao C, Chitipiralla S, et~al.
+        \newblock {{ClinVar}}: Improving Access to Variant Interpretations and
+        Supporting Evidence.
+        \newblock Nucleic Acids Research. 2018;46(D1):D1062--D1067.
+        \newblock doi:{10.1093/nar/gkx1153}.
+
+        \bibitem{grimm_evaluation_2015}
+        Grimm DG, Azencott CA, Aicheler F, Gieraths U, MacArthur DG, Samocha KE, et~al.
+        \newblock The {{Evaluation}} of {{Tools Used}} to {{Predict}} the {{Impact}} of
+            {{Missense Variants Is Hindered}} by {{Two Types}} of {{Circularity}}.
+        \newblock Human Mutation. 2015;36(5):513--523.
+        \newblock doi:{10.1002/humu.22768}.
+
+        \bibitem{sullivan_leveraging_2023}
+        Sullivan PF, Meadows JRS, Gazal S, Phan BN, Li X, Genereux DP, et~al.
+        \newblock Leveraging Base-Pair Mammalian Constraint to Understand Genetic
+        Variation and Human Disease.
+        \newblock Science. 2023;380(6643):eabn2937.
+        \newblock doi:{10.1126/science.abn2937}.
+
+        \bibitem{eyre-walker_distribution_2006}
+        {Eyre-Walker} A, Woolfit M, Phelps T.
+        \newblock The Distribution of Fitness Effects of New Deleterious Amino Acid
+        Mutations in Humans.
+        \newblock Genetics. 2006;173(2):891--900.
+        \newblock doi:{10.1534/genetics.106.057570}.
+
+        \bibitem{eyre-walker_estimating_2009}
+        {Eyre-Walker} A, Keightley PD.
+        \newblock Estimating the {{Rate}} of {{Adaptive Molecular Evolution}} in the
+            {{Presence}} of {{Slightly Deleterious Mutations}} and {{Population Size
+        Change}}.
+        \newblock Molecular Biology and Evolution. 2009;26(9):2097--2108.
+        \newblock doi:{10.1093/molbev/msp119}.
+
+        \bibitem{galtier_adaptive_2016}
+        Galtier N.
+        \newblock Adaptive Protein Evolution in Animals and the Effective Population
+        Size Hypothesis.
+        \newblock PLoS Genetics. 2016;12(1):e1005774.
+        \newblock doi:{10.1371/journal.pgen.1005774}.
+
+        \bibitem{tataru_inference_2017}
+        Tataru P, Mollion M, Gl{\'e}min S, Bataillon T.
+        \newblock Inference of Distribution of Fitness Effects and Proportion of
+        Adaptive Substitutions from Polymorphism Data.
+        \newblock Genetics. 2017;207(3):1103--1119.
+        \newblock doi:{10.1534/genetics.117.300323}.
+
+        \bibitem{bergeron_evolution_2023}
+        Bergeron LA, Besenbacher S, Zheng J, Li P, Bertelsen MF, Quintard B, et~al.
+        \newblock Evolution of the Germline Mutation Rate across Vertebrates.
+        \newblock Nature. 2023; p. 1--7.
+        \newblock doi:{10.1038/s41586-023-05752-y}.
+
+        \bibitem{orlando_recalibrating_2013}
+        Orlando L, Ginolhac A, Zhang G, Froese D, Albrechtsen A, Stiller M, et~al.
+        \newblock Recalibrating {{Equus}} Evolution Using the Genome Sequence of an
+        Early {{Middle Pleistocene}} Horse.
+        \newblock Nature. 2013;499(7456):74--78.
+        \newblock doi:{10.1038/nature12323}.
+
+        \bibitem{achaz_frequency_2009}
+        Achaz G.
+        \newblock Frequency {{Spectrum Neutrality Tests}}: {{One}} for {{All}} and
+            {{All}} for {{One}}.
+        \newblock Genetics. 2009;183(1):249--258.
+        \newblock doi:{10.1534/genetics.109.104042}.
+
+        \bibitem{latrille_genes_2023}
+        Latrille T, Rodrigue N, Lartillot N.
+        \newblock Genes and Sites under Adaptation at the Phylogenetic Scale Also
+        Exhibit Adaptation at the Population-Genetic Scale.
+        \newblock Proceedings of the National Academy of Sciences of the United States
+        of America. 2023;120(11):e2214977120.
+        \newblock doi:{10.1073/pnas.2214977120}.
+
+        \bibitem{ng_sift_2003}
+        Ng PC, Henikoff S.
+        \newblock {{SIFT}}: Predicting Amino Acid Changes That Affect Protein Function.
+        \newblock Nucleic Acids Research. 2003;31(13):3812--3814.
+        \newblock doi:{10.1093/nar/gkg509}.
+
+        \bibitem{vaser_sift_2016}
+        Vaser R, Adusumalli S, Leng SN, Sikic M, Ng PC.
+        \newblock {{SIFT}} Missense Predictions for Genomes.
+        \newblock Nature Protocols. 2016;11(1):1--9.
+        \newblock doi:{10.1038/nprot.2015.123}.
+
+        \bibitem{keightley_what_2010}
+        Keightley PD, {Eyre-Walker} A.
+        \newblock What Can We Learn about the Distribution of Fitness Effects of New
+        Mutations from {{DNA}} Sequence Data?
+        \newblock Philosophical Transactions of the Royal Society B: Biological
+        Sciences. 2010;365(1544):1187--1193.
+        \newblock doi:{10.1098/rstb.2009.0266}.
+
+        \bibitem{rice_evolutionarily_2015}
+        Rice DP, Good BH, Desai MM.
+        \newblock The {{Evolutionarily Stable Distribution}} of {{Fitness Effects}}.
+        \newblock Genetics. 2015;200(1):321--329.
+        \newblock doi:{10.1534/genetics.114.173815}.
+
+        \bibitem{mustonen_fitness_2010}
+        Mustonen V, L{\"a}ssig M.
+        \newblock Fitness Flux and Ubiquity of Adaptive Evolution.
+        \newblock Proceedings of the National Academy of Sciences.
+        2010;107(9):4248--4253.
+        \newblock doi:{10.1073/pnas.0907953107}.
+
+        \bibitem{eyre-walker_how_2014}
+        {Eyre-Walker} A, {Eyre-Walker} YC.
+        \newblock How Much of the Variation in the Mutation Rate along the Human Genome
+        Can Be Explained?
+        \newblock G3: Genes, Genomes, Genetics. 2014;4(9):1667--1670.
+        \newblock doi:{10.1534/g3.114.012849}.
+
+        \bibitem{mustonen_molecular_2008}
+        Mustonen V, L{\"a}ssig M.
+        \newblock Molecular {{Evolution}} under {{Fitness Fluctuations}}.
+        \newblock Physical Review Letters. 2008;100(10):108101.
+        \newblock doi:{10.1103/PhysRevLett.100.108101}.
+
+        \bibitem{latrille_inferring_2021}
+        Latrille T, Lanore V, Lartillot N.
+        \newblock Inferring Long-Term Effective Population Size with
+        Mutation--Selection Models.
+        \newblock Molecular Biology and Evolution. 2021;38(10):4573--4587.
+        \newblock doi:{10.1093/molbev/msab160}.
+
+        \bibitem{huber_determining_2017}
+        Huber CD, Kim BY, Marsden CD, Lohmueller KE.
+        \newblock Determining the Factors Driving Selective Effects of New
+        Nonsynonymous Mutations.
+        \newblock Proceedings of the National Academy of Sciences.
+        2017;114(17):4465--4470.
+        \newblock doi:{10.1073/pnas.1619508114}.
+
+        \bibitem{lanfear_population_2014}
+        Lanfear R, Kokko H, {Eyre-Walker} A.
+        \newblock Population Size and the Rate of Evolution.
+        \newblock Trends in Ecology and Evolution. 2014;29(1):33--41.
+        \newblock doi:{10.1016/j.tree.2013.09.009}.
+
+        \bibitem{platt_protein_2018}
+        Platt A, Weber CC, Liberles DA.
+        \newblock Protein Evolution Depends on Multiple Distinct Population Size
+        Parameters.
+        \newblock BMC Evolutionary Biology. 2018;18(1):1--9.
+        \newblock doi:{10.1186/s12862-017-1085-x}.
+
+        \bibitem{starr_epistasis_2016}
+        Starr TN, Thornton JW.
+        \newblock Epistasis in Protein Evolution.
+        \newblock Protein Science. 2016;25(7):1204--1218.
+        \newblock doi:{10.1002/pro.2897}.
+
+        \bibitem{morcos_directcoupling_2011}
+        Morcos F, Pagnani A, Lunt B, Bertolino A, Marks DS, Sander C, et~al.
+        \newblock Direct-Coupling Analysis of Residue Coevolution Captures Native
+        Contacts across Many Protein Families.
+        \newblock Proceedings of the National Academy of Sciences.
+        2011;108(49):E1293--E1301.
+        \newblock doi:{10.1073/pnas.1111471108}.
+
+        \bibitem{marks_protein_2012}
+        Marks DS, Hopf TA, Sander C.
+        \newblock Protein Structure Prediction from Sequence Variation.
+        \newblock Nature Biotechnology. 2012;30(11):1072--1080.
+        \newblock doi:{10.1038/nbt.2419}.
+
+        \bibitem{goldstein_nonadaptive_2015}
+        Goldstein RA, Pollard ST, Shah SD, Pollock DD.
+        \newblock Nonadaptive {{Amino Acid Convergence Rates Decrease}} over {{Time}}.
+        \newblock Molecular Biology and Evolution. 2015;32(6):1373--1381.
+        \newblock doi:{10.1093/molbev/msv041}.
+
+        \bibitem{goldstein_sequence_2017}
+        Goldstein RA, Pollock DD.
+        \newblock Sequence Entropy of Folding and the Absolute Rate of Amino Acid
+        Substitutions.
+        \newblock Nature Ecology \& Evolution. 2017;1(12):1923--1930.
+        \newblock doi:{10.1038/s41559-017-0338-9}.
+
+        \bibitem{park_epistatic_2022}
+        Park Y, Metzger BPH, Thornton JW.
+        \newblock Epistatic Drift Causes Gradual Decay of Predictability in Protein
+        Evolution.
+        \newblock Science. 2022;376(6595):823--830.
+        \newblock doi:{10.1126/science.abn6895}.
+
+        \bibitem{ashenberg_mutational_2013}
+        Ashenberg O, Gong LI, Bloom JD.
+        \newblock Mutational Effects on Stability Are Largely Conserved during Protein
+        Evolution.
+        \newblock Proceedings of the National Academy of Sciences of the United States
+        of America. 2013;110(52):21071--21076.
+        \newblock doi:{10.1073/pnas.1314781111}.
+
+        \bibitem{doud_sitespecific_2015}
+        Doud MB, Ashenberg O, Bloom JD.
+        \newblock Site-{{Specific Amino Acid Preferences Are Mostly Conserved}} in
+            {{Two Closely Related Protein Homologs}}.
+        \newblock Molecular Biology and Evolution. 2015;32(11):2944--2960.
+        \newblock doi:{10.1093/molbev/msv167}.
+
+        \bibitem{bloom_identification_2017}
+        Bloom JD.
+        \newblock Identification of Positive Selection in Genes Is Greatly Improved by
+        Using Experimentally Informed Site-Specific Models.
+        \newblock Biology Direct. 2017;12(1):1--24.
+        \newblock doi:{10.1186/s13062-016-0172-z}.
+
+        \bibitem{youssef_consequences_2020}
+        Youssef N, Susko E, Bielawski JP.
+        \newblock Consequences of Stability-Induced Epistasis for Substitution Rates.
+        \newblock Molecular Biology and Evolution. 2020;doi:{10.1093/molbev/msaa151}.
+
+        \bibitem{vigue_deciphering_2022}
+        Vigu{\'e} L, Croce G, Petitjean M, Rupp{\'e} E, Tenaillon O, Weigt M.
+        \newblock Deciphering Polymorphism in 61,157 {{Escherichia}} Coli Genomes via
+        Epistatic Sequence Landscapes.
+        \newblock Nature Communications. 2022;13(1):4030.
+        \newblock doi:{10.1038/s41467-022-31643-3}.
+
+        \bibitem{kimura_evolutionary_1968}
+        Kimura M.
+        \newblock Evolutionary Rate at the Molecular Level.
+        \newblock Nature. 1968;217(5129):624--626.
+
+        \bibitem{gillespie_substitution_1994}
+        Gillespie JH.
+        \newblock Substitution Processes in Molecular Evolution. {{III}}.
+            {{Deleterious}} Alleles.
+        \newblock Genetics. 1994;138(3):943--952.
+        \newblock doi:{10.1093/genetics/138.3.943}.
+
+        \bibitem{jensen_importance_2019}
+        Jensen JD, Payseur BA, Stephan W, Aquadro CF, Lynch M, Charlesworth D, et~al.
+        \newblock The Importance of the {{Neutral Theory}} in 1968 and 50 Years on:
+            {{A}} Response to {{Kern}} and {{Hahn}} 2018.
+        \newblock Evolution. 2019;73(1):111--114.
+        \newblock doi:{10.1111/evo.13650}.
+
+        \bibitem{galtier_half_2024}
+        Galtier N.
+        \newblock Half a {{Century}} of {{Controversy}}: {{The
+        Neutralist}}/{{Selectionist Debate}} in {{Molecular Evolution}}.
+        \newblock Genome Biology and Evolution. 2024;16(2):evae003.
+        \newblock doi:{10.1093/gbe/evae003}.
+
+        \bibitem{galtier_adaptation_2007}
+        Galtier N, Duret L.
+        \newblock Adaptation or Biased Gene Conversion? {{Extending}} the Null
+        Hypothesis of Molecular Evolution.
+        \newblock Trends in Genetics. 2007;23(6):273--277.
+        \newblock doi:{10.1016/j.tig.2007.03.011}.
+
+        \bibitem{rousselle_influence_2019}
+        Rousselle M, Laverr{\'e} A, Figuet E, Nabholz B, Galtier N.
+        \newblock Influence of {{Recombination}} and {{GC-biased Gene Conversion}} on
+        the {{Adaptive}} and {{Nonadaptive Substitution Rate}} in {{Mammals}} versus
+            {{Birds}}.
+        \newblock Molecular Biology and Evolution. 2019;36(3):458--471.
+        \newblock doi:{10.1093/molbev/msy243}.
+
+        \bibitem{joseph_increased_2024a}
+        Joseph J.
+        \newblock Increased {{Positive Selection}} in {{Highly Recombining Genes Does}}
+        Not {{Necessarily Reflect}} an {{Evolutionary Advantage}} of
+            {{Recombination}}.
+        \newblock Molecular Biology and Evolution. 2024; p. msae107.
+        \newblock doi:{10.1093/molbev/msae107}.
+
+        \bibitem{ohta_development_1996}
+        Ohta T, Gillespie JH.
+        \newblock Development of {{Neutral}} and {{Nearly Neutral Theories}}.
+        \newblock Theoretical Population Biology. 1996;49(2):128--142.
+        \newblock doi:{10.1006/tpbi.1996.0007}.
+
+        \bibitem{spielman_relationship_2015}
+        Spielman SJ, Wilke CO.
+        \newblock The Relationship between {{dN}}/{{dS}} and Scaled Selection
+        Coefficients.
+        \newblock Molecular biology and evolution. 2015;32(4):1097--1108.
+        \newblock doi:{10.1093/molbev/msv003}.
+
+        \bibitem{dosreis_how_2015}
+        Dos~Reis M.
+        \newblock How to Calculate the Non-Synonymous to Synonymous Rate Ratio of
+        Protein-Coding Genes under the Fisher-Wright Mutation-Selection Framework.
+        \newblock Biology Letters. 2015;11(4):20141031.
+        \newblock doi:{10.1098/rsbl.2014.1031}.
+
+        \bibitem{rodrigue_bayesian_2021}
+        Rodrigue N, Latrille T, Lartillot N.
+        \newblock A {{Bayesian}} Mutation-Selection Framework for Detecting
+        Site-Specific Adaptive Evolution in Protein-Coding Genes.
+        \newblock Molecular Biology and Evolution. 2021;38(3):1199--1208.
+        \newblock doi:{10.1093/molbev/msaa265}.
+
+        \bibitem{tamuri_mutationselection_2021}
+        Tamuri AU, {dos Reis} M.
+        \newblock A Mutation-Selection Model of Protein Evolution under Persistent
+        Positive Selection.
+        \newblock Molecular Biology and Evolution. 2021;doi:{10.1093/molbev/msab309}.
+
+        \bibitem{kazmi_detecting_2019}
+        Kazmi SO, Rodrigue N.
+        \newblock Detecting Amino Acid Preference Shifts with Codon-Level
+        Mutation-Selection Mixture Models.
+        \newblock BMC Evolutionary Biology. 2019;19(1):62.
+        \newblock doi:{10.1186/s12862-019-1358-7}.
+
+        \bibitem{stolyarova_senescence_2020}
+        Stolyarova AV, Nabieva E, Ptushenko VV, Favorov AV, Popova AV, Neverov AD,
+        et~al.
+        \newblock Senescence and Entrenchment in Evolution of Amino Acid Sites.
+        \newblock Nature Communications. 2020;11(1):4603.
+        \newblock doi:{10.1038/s41467-020-18366-z}.
+
+        \bibitem{douzery_orthomam_2014}
+        Douzery EJP, Scornavacca C, Romiguier J, Belkhir K, Galtier N, Delsuc F, et~al.
+        \newblock {{OrthoMaM}} v8: {{A}} Database of Orthologous Exons and Coding
+        Sequences for Comparative Genomics in Mammals.
+        \newblock Molecular Biology and Evolution. 2014;31(7):1923--1928.
+        \newblock doi:{10.1093/molbev/msu132}.
+
+        \bibitem{yang_mutationselection_2008}
+        Yang Z, Nielsen R.
+        \newblock Mutation-Selection Models of Codon Substitution and Their Use to
+        Estimate Selective Strengths on Codon Usage.
+        \newblock Molecular Biology and Evolution. 2008;25(3):568--579.
+        \newblock doi:{10.1093/molbev/msm284}.
+
+        \bibitem{wright_evolution_1931}
+        Wright S.
+        \newblock Evolution in {{Mendelian}} Populations.
+        \newblock Genetics. 1931;16(2):97--159.
+        \newblock doi:{10.1093/genetics/16.2.97}.
+
+        \bibitem{fisher_genetical_1930}
+        Fisher RA.
+        \newblock The {{Genetical Theory}} of {{Natural Selection}}.
+        \newblock The Clarendon Press; 1930.
+
+        \bibitem{rodrigue_bayesian_2008}
+        Rodrigue N, Lartillot N, Philippe H.
+        \newblock Bayesian Comparisons of Codon Substitution Models.
+        \newblock Genetics. 2008;180(3):1579--1591.
+        \newblock doi:{10.1534/genetics.108.092254}.
+
+        \bibitem{lartillot_bayesian_2004}
+        Lartillot N.
+        \newblock A Bayesian Mixture Model for Across-Site Heterogeneities in the
+        Amino-Acid Replacement Process.
+        \newblock Molecular biology and evolution. 2004;21(6):1095--1109.
+        \newblock doi:{10.1093/molbev/msh112}.
+
+        \bibitem{lartillot_inference_2013}
+        Lartillot N.
+        \newblock Inf{\'e}rence Probabiliste Pour La Phylog{\'e}nie, La G{\'e}nomique
+        Comparative et Les Sciences de La Macro-{\'E}volution; 2013.
+
+        \bibitem{alabri_whole_2020}
+        Al~Abri MA, Holl HM, Kalla SE, Sutter NB, Brooks SA.
+        \newblock Whole Genome Detection of Sequence and Structural Polymorphism in Six
+        Diverse Horses.
+        \newblock PLoS ONE. 2020;15(4):e0230899.
+        \newblock doi:{10.1371/journal.pone.0230899}.
+
+        \bibitem{sherry_dbsnp_2001}
+        Sherry ST, Ward MH, Kholodov M, Baker J, Phan L, Smigielski EM, et~al.
+        \newblock {{dbSNP}}: The {{NCBI}} Database of Genetic Variation.
+        \newblock Nucleic Acids Research. 2001;29(1):308--311.
+        \newblock doi:{10.1093/nar/29.1.308}.
+
+        \bibitem{svardal_ancient_2017}
+        Svardal H, Jasinska AJ, Apetrei C, Coppola G, Huang Y, Schmitt CA, et~al.
+        \newblock Ancient Hybridization and Strong Adaptation to Viruses across
+            {{African}} Vervet Monkey Populations.
+        \newblock Nature Genetics. 2017;49(12):1705--1713.
+        \newblock doi:{10.1038/ng.3980}.
+
+        \bibitem{zheng-bradley_alignment_2017}
+        {Zheng-Bradley} X, Streeter I, Fairley S, Richardson D, Clarke L, Flicek P,
+        et~al.
+        \newblock Alignment of 1000 {{Genomes Project}} Reads to Reference Assembly
+            {{GRCh38}}.
+        \newblock GigaScience. 2017;6(7):gix038.
+        \newblock doi:{10.1093/gigascience/gix038}.
+
+        \bibitem{keightley_inferring_2018}
+        Keightley PD, Jackson BC.
+        \newblock Inferring the Probability of the Derived vs the Ancestral Allelic
+        State at a Polymorphic Site.
+        \newblock Genetics. 2018;209(3):897--906.
+        \newblock doi:{10.1534/genetics.118.301120}.
+
+        \bibitem{ashkenazy_fastml_2012}
+        Ashkenazy H, Penn O, {Doron-Faigenboim} A, Cohen O, Cannarozzi G, Zomer O,
+        et~al.
+        \newblock {{FastML}}: A Web Server for Probabilistic Reconstruction of
+        Ancestral Sequences.
+        \newblock Nucleic Acids Research. 2012;40(W1):W580--W584.
+        \newblock doi:{10.1093/nar/gks498}.
+
+        \bibitem{tataru_polydfe_2020}
+        Tataru P, Bataillon T.
+        \newblock {{polyDFE}}: {{Inferring}} the Distribution of Fitness Effects and
+        Properties of Beneficial Mutations from Polymorphism Data.
+        \newblock In: Methods in {{Molecular Biology}}. vol. 2090. Humana Press Inc.;
+        2020. p. 125--146.
+
+        \bibitem{orme_caper_2013}
+        Orme D, Freckleton R, Thomas G, Petzoldt T, Fritz S, Isaac N, et~al.
+        \newblock The Caper Package: Comparative Analysis of Phylogenetics and
+        Evolution in {{R}}.
+        \newblock R package version. 2013;5(2):1--36.
+
+        \bibitem{kumar_timetree_2017}
+        Kumar S, Stecher G, Suleski M, Hedges SB.
+        \newblock {{TimeTree}}: A Resource for Timelines, Timetrees, and Divergence
+        Times.
+        \newblock Molecular Biology and Evolution. 2017;34(7):1812--1819.
+        \newblock doi:{10.1093/molbev/msx116}.
+
+    \end{thebibliography}
+
+    \newpage
+    \section*{Supplementary figures and tables}
+    \subsection*{List of Figures}
+    \begin{itemize}
+        \item S1: Bayesian hierarchical model (p.5).
+        \item S2: Examples sites of $\SphyBen$ mutations in \textit{Chlorocebus sabaeus} (reversions) (p.10).
+        \item S3: Examples sites of $\SphyBen$ mutations in \textit{Chlorocebus sabaeus} (p.11).
+        \item S4: Enrichment in $\SphyBen$ SNPs across all gene ontology terms (p.17).
+        \item S5: Estimation of selection at the population scale for $\SphyDel$ mutations (p.19).
+        \item S6: Estimation of selection at the population scale for $\SphyNeu$ mutations (p.19).
+        \item S7: Estimation of selection at the population scale for $\SphyBen$ mutations (p.19).
+        \item S8: Distribution of scaled selection coefficients ($\Sphy$) (p.20).
+        \item S9: Tree used for PGLM (Phylogenetic Generalized Linear Model) (p.21).
+        \item S10: Proportion of deleterious mutations ($\SpopDel$) (p.22).
+        \item S11: Proportion of nearly-neutral mutations ($\SpopNeu$) (p.23).
+        \item S12: Proportion of beneficial mutations ($\SpopBen$) (p.24).
+        \item S13: $\proba[\SphyBen\given \SpopBen ]$ as a function of distance to the sister species (p.26).
+        \item S14: Ratio of $\proba[\Sphy]$ over $\proba[-\Sphy]$ for polymorphisms of the African population of \textit{Homo sapiens} (p.27).
+        \item S15: Simulations of site-frequency spectra (p.29).
+        \item S16: Site-frequency spectrum in African population of \textit{Homo sapiens}, masking CpG transitions  (p.32).
+        \item S17: Site-frequency spectrum in South African population of \textit{Chlorocebus sabaeus}, masking CpG transitions (p.32).
+        \item S18: Including substitutions in the terminal lineage to estimate $\Spop$ (p.34).
+        \item S19: $\proba[\SphyBen\given \SpopBen ]$ while including divergence to estimate $\Spop$, as a function of distance to the sister species (p.37).
+        \item S20: $\proba [ \SpopDel ]$ when fitting a single or three DFEs (p.40).
+        \item S21: $\proba [ \SpopNeu ]$ when fitting a single or three DFEs (p.40).
+        \item S22: $\proba [ \SpopBen ]$ when fitting a single or three DFEs (p.40).
+    \end{itemize}
+
+    \newpage
+    \subsection*{List of Tables}
+    \begin{itemize}
+    \item S1: Probability of mutations and substitutions to be $\SphyDel$, $\SphyNeu$ or $\SphyBen$ (p.12).
+    \item S2: $\dnds$ for $\SphyDel$, $\SphyNeu$ or $\SphyBen$ (p.13).
+    \item S3: $\dnds$ over-estimation due to non-adaptive beneficial mutations (p.14).
+    \item S4: Gene ontology enrichment in $\SphyBen$ SNPs (p.15).
+    \item S5: Terms associated with deleterious mutations $\SphyDel$ (p.18).
+    \item S6: Terms associated with non-adaptive beneficial mutations $\SphyBen$ (p.18).
+    \item S7: Probability for beneficial mutations to be non-adaptive ($\proba[\SphyBen\given \SpopBen ]$) (p.25).
+    \item S8: $\proba[\SphyBen\given \SpopBen ]$ while masking CpG transitions (p.30).
+    \item S9: Precision and recall while masking CpG transitions (p.31).
+    \item S10: $\proba[\SphyBen\given \SpopBen ]$ excluding or not genes under adaptation (p.33).
+    \item S11: $\proba[\SphyBen\given \SpopBen ]$ when including divergence to estimate $\Spop$ (p.35).
+    \item S12: Precision and recall while including divergence to estimate $\Spop$ (p.36).
+    \item S13: $\proba[\SphyBen\given \SpopBen ]$ excluding or not genes under adaptation, when including divergence to estimate $\Spop$ (p.38).
+    \item S14: $\proba[\SphyBen\given \SpopBen ]$ when using a discrete DFE to estimate $\Spop$ (p.41).
+    \item S15: Precision and recall when using a discrete DFE to estimate $\Spop$ (p.42).
+    \end{itemize}
+
     \newpage
@@
         \centering
-        \includegraphics[width=\textwidth, page=1] {artworks/figure.fitness-landscape}
+        \includegraphics[width=\textwidth, page=1] {figure1.eps}
         \caption{
@@
         \centering
-        \includegraphics[width=\textwidth, page=1] {artworks/figure.method.proba}
+        \includegraphics[width=\textwidth, page=1] {figure2.eps}
         \caption{
@@
             The \textit{recall} value for class $\SphyBen$ is the probability for beneficial mutations to be non-adaptive (G).
+            Icons are adapted from \href{https://phylopic.org}{https://phylopic.org} under a Creative Commons license.
         }
@@
         \centering
-        \includegraphics[width=\textwidth, page=1] {artworks/figure.homo-afr-results}
+        \includegraphics[width=\textwidth, page=1] {figure3.eps}
         \caption{
@@
         \centering
-        \includegraphics[width=\textwidth, page=1] {artworks/figure.diversity}
+        \includegraphics[width=\textwidth, page=1] {figure4.eps}
         \caption{
@@
     \begin{table*}[tb]
-%TC:ignore
         \centering
@@
         \end{adjustbox}
-%TC:endignore
         \caption{

### 2024-12-05 manuscript/main-PLOS-revision-2-plos2015.tex
Revision PLOS Genetics round 2

--- 2024-12-05 manuscript/main-PLOS-revision-bbl.tex
@@
-\documentclass{article}
-
-\usepackage{xcolor, colortbl}
-\definecolor{BLUELINK}{HTML}{0645AD}
-\definecolor{DARKBLUELINK}{HTML}{0B0080}
+% Template for PLoS
+% Version 3.6 Aug 2022
+%
+% % % % % % % % % % % % % % % % % % % % % %
+%
+% -- IMPORTANT NOTE
+%
+% This template contains comments intended
+% to minimize problems and delays during our production
+% process. Please follow the template instructions
+% whenever possible.
+%
+% % % % % % % % % % % % % % % % % % % % % % %
+%
+% Once your paper is accepted for publication,
+% PLEASE REMOVE ALL TRACKED CHANGES in this file
+% and leave only the final text of your manuscript.
+% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
+% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
+%
+%
+% There are no restrictions on package use within the LaTeX files except that no packages listed in the template may be deleted.
+%
+% Please do not include colors or graphics in the text.
+%
+% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
+%
+% % % % % % % % % % % % % % % % % % % % % % %
+%
+% -- FIGURES AND TABLES
+%
+% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
+%
+% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
+% - Figures should be uploaded separately from your manuscript file.
+% - Figures generated using LaTeX should be extracted and removed from the PDF before submission.
+% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
+% For figure citations, please use "Fig" instead of "Figure".
+% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
+%
+% Tables should be cell-based and may not contain:
+% - spacing/line breaks within cells to alter layout or alignment
+% - do not nest tabular environments (no tabular environments within tabular environments)
+% - no graphics or colored text (cell background color/shading OK)
+% See http://journals.plos.org/plosone/s/tables for table guidelines.
+%
+% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
+%
+% % % % % % % % % % % % % % % % % % % % % % % %
+%
+% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
+%
+% IMPORTANT
+% Below are a few tips to help format your equations and other special characters according to our specifications.
+For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
+%
+% For inline equations, please be sure to include all portions of an equation in the math environment.
+For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
+%
+% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
+%
+% Please add line breaks to long display equations when possible in order to fit size of the column.
+%
+% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
+%
+% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2".
+%
+% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
+%
+% % % % % % % % % % % % % % % % % % % % % % % %
+%
+% Please contact latex@plos.org with any questions.
+%
+% % % % % % % % % % % % % % % % % % % % % % % %
+
+\documentclass[10pt,letterpaper]{article}
+\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
+
+% amsmath and amssymb packages, useful for mathematical formulas and symbols
+\usepackage{amsmath,amssymb}
+
+% Use adjustwidth environment to exceed column width (see example table in text)
+\usepackage{changepage}
+
+% textcomp package and marvosym package for additional characters
+\usepackage{textcomp,marvosym}
+
+% cite package, to clean up citations in the main text. Do not remove.
+\usepackage{cite}
+
+% Use nameref to cite supporting information files (see Supporting Information section for more info)
+\usepackage{nameref,hyperref}
+
+% line numbers
+\usepackage[right]{lineno}
+
+% ligatures disabled
+\usepackage{microtype}
+\DisableLigatures[f]{encoding = *, family = * }
+
+% color can be used to apply background shading to table cells only
+\usepackage[table]{xcolor}
+
+% array package and thick rules for tables
+\usepackage{array}
+
+% create "+" rule type for thick vertical lines
+\newcolumntype{+}{!{\vrule width 2pt}}
+
+% create \thickcline for thick horizontal lines of variable length
+\newlength\savedwidth
+\newcommand\thickcline[1]{%
+\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
+\cline{#1}%
+\noalign{\vskip\arrayrulewidth}%
+\noalign{\global\arrayrulewidth\savedwidth}%
+}
+
+% \thickhline command for thick horizontal lines that span the table
+\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
+\hline
+\noalign{\global\arrayrulewidth\savedwidth}}
+
+% Remove comment for double spacing
+%\usepackage{setspace}
+%\doublespacing
+
+% Text layout
+\raggedright
+\setlength{\parindent}{0.5cm}
+\textwidth 5.25in
+\textheight 8.75in
+
+% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
+% Captions will be left justified
+\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
+\renewcommand{\figurename}{Fig}
+
+% Use the PLoS provided BiBTeX style
+\bibliographystyle{plos2015}
+
+% Remove brackets from numbering in List of References
+\makeatletter
+\renewcommand{\@biblabel}[1]{\quad#1.}
+\makeatother
+
+% Header and Footer with logo
+\usepackage{lastpage,fancyhdr,graphicx}
+\usepackage{epstopdf}
+%\pagestyle{myheadings}
+\pagestyle{fancy}
+\fancyhf{}
+%\setlength{\headheight}{27.023pt}
+%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
+\rfoot{\thepage/\pageref{LastPage}}
+\renewcommand{\headrulewidth}{0pt}
+\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
+\fancyheadoffset[L]{2.25in}
+\fancyfootoffset[L]{2.25in}
+\lfoot{\today}
+
+%% Include all macros below
+\usepackage{mathtools}
 \definecolor{LIGHTGREY}{gray}{0.9}
-\PassOptionsToPackage{hyphens}{url}
-\usepackage[colorlinks=false]{hyperref}
-% for linking between references, figures, TOC, etc in the pdf document
-\hypersetup{colorlinks,
-    linkcolor=DARKBLUELINK,
-    anchorcolor=DARKBLUELINK,
-    citecolor=DARKBLUELINK,
-    filecolor=DARKBLUELINK,
-    menucolor=DARKBLUELINK,
-    urlcolor=BLUELINK
-} % Color citation links in purple
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{naturalnames}{hyperref}
-
-\renewenvironment{abstract}
-{
-    \centerline
-    {\large \bfseries \scshape Abstract}
-    \begin{quote}
-    }
-    {
-    \end{quote}
-}
-
-\def\keywordname{{\bfseries \emph Keywords}}%
-\def\keywords#1{\par\addvspace\medskipamount{\rightskip=0pt plus1cm
-\def\and{\ifhmode\unskip\nobreak\fi\ $\cdot$
-}\noindent\keywordname\enspace\ignorespaces#1\par}}
-
-%\usepackage{biorxiv}
-
-\usepackage{url}
-\usepackage{amssymb,amsfonts,amsmath,amsthm,mathtools}
-\usepackage{lmodern}
-\usepackage{xfrac, nicefrac}
 \usepackage{bm}
-\usepackage{listings, enumerate, enumitem}
-\usepackage[export]{adjustbox}
-\usepackage{graphicx}
-\usepackage{bbold}
-\usepackage{pdfpages}
-\pdfinclusioncopyfonts=1
-\usepackage{lineno}
-\usepackage{tabu}
-\usepackage{hhline}
-\usepackage{multicol,multirow,array}
-\usepackage{etoolbox}
 \usepackage{booktabs}
 \usepackage{makecell}
-\usepackage{orcidlink}
-\usepackage[verbose=true,letterpaper]{geometry}
-\AtBeginDocument{
-    \newgeometry{
-        textheight=9in,
-        textwidth=6.5in,
-        top=1in,
-        headheight=14pt,
-        headsep=25pt,
-        footskip=30pt
-    }
-}
-
-\bibliographystyle{plos2015}
-
-\newcommand{\UniDimArray}[1]{\bm{#1}}
+
 \newcommand{\der}{\text{d}}
@@
 \newcommand{\thetaSyn}{\theta_{\text{S}}}
-\renewcommand{\baselinestretch}{1.5}
-\renewcommand{\arraystretch}{0.6}
-\linenumbers
-\frenchspacing
-
-\title{Estimating the proportion of beneficial mutations that are not adaptive in mammals}
-
-\author{
-    \small \textbf{T.
-{Latrille}$^{1\dag}$\orcidlink{0000-0002-9643-4668}, J.
-{Joseph}$^{2\dag}$\orcidlink{0009-0002-1312-9930}, D.~A.
-{Hartasánchez}$^{1}$\orcidlink{0000-0003-2596-6883}, N.
-{Salamin}$^{1}$\orcidlink{0000-0002-3963-4954}}\\
-    \small $^{1}$Department of Computational Biology, Université de Lausanne, Lausanne, Switzerland\\
-    \small $^{2}$Laboratoire de Biométrie et Biologie Evolutive, UMR5558, Université Lyon 1, Villeurbanne, France \\
-    \small $^{\dag}$These authors contributed equally to this work\\
-    \small  \texttt{\href{mailto:thibault.latrille@ens-lyon.org}{thibault.latrille@ens-lyon.org}} \\
+%\renewcommand{\baselinestretch}{1.5}
+%\renewcommand{\arraystretch}{0.6}
+
+%% END MACROS SECTION
+
+\begin{document}
+\vspace*{0.2in}
+
+% Title must be 250 characters or less.
+\begin{flushleft}
+{\Large
+\textbf\newline{Estimating the proportion of beneficial mutations that are not adaptive in mammals} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
 }
-
-\begin{document}
-    \maketitle
-
-    \begin{abstract}
+\newline
+% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
+\\
+T. {Latrille}\textsuperscript{1\ddag*},
+J. {Joseph}\textsuperscript{2\ddag},
+D.~A. {Hartasánchez}\textsuperscript{1},
+N. {Salamin}\textsuperscript{1}
+\\
+\bigskip
+\textbf{1} Department of Computational Biology, Université de Lausanne, Lausanne, Switzerland
+\\
+\textbf{2} Laboratoire de Biométrie et Biologie Evolutive, UMR5558, Université Lyon 1, Villeurbanne, France
+\\
+
+\bigskip
+
+% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
+%
+% Remove or comment out the author notes below if they aren't used.
+%
+% Primary Equal Contribution Note
+% \Yinyang These authors contributed equally to this work.
+
+% Additional Equal Contribution Note
+% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
+\ddag These authors also contributed equally to this work.
+
+% Current address notes
+% \textcurrency Current Address: Department of Computational Biology, Université de Lausanne, Lausanne, Switzerland % change symbol to "\textcurrency a" if more than one current address note
+
+% Group/Consortium Author Note
+
+% Use the asterisk to denote corresponding authorship and provide email address in note below.
+* \href{mailto:thibault.latrille@ens-lyon.org}{thibault.latrille@ens-lyon.org}
+
+\end{flushleft}
+
+\section*{Abstract}
 Mutations can be beneficial by bringing innovation to their bearer, allowing them to adapt to environmental change.
@@
 We observe that beneficial non-adaptive mutations represent between 15\% and 45\% of all beneficial mutations in 24 of 28 populations analyzed, suggesting that a substantial part of ongoing positive selection is not driven solely by adaptation to environmental change in mammals.
-    \end{abstract}
-
-    \keywords{Adaptation \and Nearly-neutral \and Phylogenetics \and Population-genetics \and Codon models }
 
@@
 We show that a substantial proportion of beneficial mutations cannot be interpreted as adaptive.
+
+\linenumbers
 
@@
 
-    Upon environmental change, because adaptive beneficial mutations toward new fitness optima are more likely, the number of substitutions also increases (fig.~\ref{fig:fitness-landscape}A).
+Upon environmental change, because adaptive beneficial mutations toward new fitness optima are more likely, the number of substitutions also increases (Fig~\ref{fig:fitness-landscape}A).
 An increased substitution rate is thus commonly interpreted as a sign of adaptation~\cite{mcdonald_adaptative_1991, smith_adaptive_2002, welch_estimating_2006}.
@@
 
-    \subsection*{Beneficial yet non-adaptive mutations}
-
-    In a constant environment, a deleterious mutation can reach fixation by genetic drift~\cite{ohta_nearly_1992}.
-    A new mutation restoring the ancestral fitness will thus be beneficial (fig.~\ref{fig:fitness-landscape}B), even though the environment has not changed~\cite{gillespie_ohta_1995, hartl_compensatory_1996, sella_application_2005, mustonen_fitness_2009, cvijovic_fate_2015}.
-    We will refer to as beneficial non-adaptive mutations to those mutations that restore the ancestral fitness under the assumption that the fitness landscape has not changed~\cite{piganeau_estimating_2003, charlesworth_other_2007}.
-    Such mutations can happen through a mutation at a different locus, in which case it is called a compensatory mutation~\cite{hartl_compensatory_1996, mustonen_fitness_2009}.
-    While compensatory mutations change the sequence and thus induce genetic diversification, beneficial non-adaptive mutations at the locus of the initial mutation reduce genetic diversity and do not contribute to genetic innovation, which are the focus of this manuscript.
-    Although Tomoko Ohta considered beneficial non-adaptive mutations negligible in her nearly-neutral theory~\cite{ohta_nearly_1992}, their importance has now been acknowledged for expanding populations~\cite{charlesworth_other_2007}.
-    However, differentiating between an adaptive mutation and a beneficial non-adaptive mutation remains challenging~\cite{chi_detecting_2020}.
-    Indeed, an adaptive mutation responding to a change in the environment and a beneficial non-adaptive mutation have equivalent fitness consequences for their bearer~\cite{charlesworth_other_2007}.
-    Similarly, at the population level, both types of mutations will result in a positive transmission bias of the beneficial allele.
-    However, at the macro-evolutionary scale, the consequences of these two types of mutations are fundamentally different.
-    While adaptive mutations promote phenotype diversification (fig.~\ref{fig:fitness-landscape}C), beneficial non-adaptive mutations promote phenotype stability and may help preserve well-established biological systems (fig.~\ref{fig:fitness-landscape}D).
-    Additionally, the direction of adaptive evolution is unpredictable because it is caused by an unforeseen change in the environment and, hence, in the underlying fitness landscape~\cite{bazykin_changing_2015}.
-    On the other hand, beneficial non-adaptive mutations are predictable because, under a stable fitness landscape, any change from non-optimal to optimal amino acids will move back the site toward the equilibrium expected under the fitness landscape~\cite{moses_inferring_2009, fischer_germline_2011, chen_hunting_2021}.
-    They can then be distinguished from truly novel beneficial mutations because the latter are not expected to mutate toward the amino acids of higher fitnesses defined by the stable fitness landscape but rather mutate to amino acids showing a diversified pattern (fig.~\ref{fig:fitness-landscape}).
-
-    \subsection*{Fitness landscape reconstruction}
-
-    The mutation-selection framework permits to link the patterns of substitution along a phylogenetic tree with the underlying fitness landscape~\cite{halpern_evolutionary_1998, mccandlish_modeling_2014}.
-    Such mutation-selection models applied to protein-coding DNA sequence alignments at the codon level allow us to estimate relative fitnesses for all amino acids for each site of the sequence, explicitly assuming that the underlying fitness landscape is stable along the phylogenetic tree~\cite{rodrigue_mechanistic_2010, tamuri_estimating_2012, rodrigue_detecting_2017}.
-    Moreover, effective population size ($\Ne$) is considered constant along the phylogenetic tree precisely because of the fixed fitness landscape assumption, the consequences of which are detailed in the Discussion.
-    Importantly, because mutation-selection codon models at the phylogenetic scale are based on population-genetics equations, their estimates of selection coefficients are directly interpretable as fitness effects at the population scale; and because they work at the DNA level, we are able to account for mutational bias in DNA and structure of the genetic code.
-    The model further integrates the shared evolutionary history between samples and their divergence, which, together, allow us to estimate fitness effects in sequence alignments even though sequences are not independent samples and might not represent the equilibrium distribution of amino acids (see section \ref{subsec:s-phylogeny-method} in Materials \& Methods, model parameters in section S1 and fig.~S1).
-
-    Accordingly, fitting the mutation-selection model to a multi-species sequence alignment allows us to obtain relative fitnesses for all amino acids (fig.~\ref{fig:method}A).
-    The difference in fitness between a pair of amino acids allows us to predict whether any mutation would be a deleterious mutation toward a less fit amino acid, a nearly-neutral mutation, or a mutation toward a known fitter amino acid constituting thus a beneficial non-adaptive mutation (fig.~\ref{fig:method}B).
-    We can hence use large-scale genomic data to test whether such fitnesses estimated at the phylogenetic scale predict the fitness effects at the population scale.
-    The placental mammals represent an excellent study system to perform such an analysis.
-    Having originated $\sim$102 million years ago, they diversified quickly~\cite{foley_genomic_2023}.
-    Additionally, polymorphism data are available for many species~\cite{howe_ensembl_2021}, as are high quality protein-coding DNA alignments across the genome~\cite{ranwez_orthomam_2007, scornavacca_orthomam_2019}.
-    By performing our analysis on 14,509 orthologous protein-coding genes across 87 species, we focus on genes shared across all mammals in our dataset and not newly functionalized genes in a lineage.
-
-    Having identified which potential DNA changes represent beneficial non-adaptive mutations (fig.~\ref{fig:method}A-B), we retrieved polymorphism data from 28 wild and domesticated populations belonging to six genera (\textit{Equus}, \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus}, and \textit{Homo}) to assess the presence of beneficial non-adaptive mutations at the population scale.
-    We focused on both mutations currently segregating within populations and on substitutions in the terminal branches, and checked if any of these observed changes were indeed beneficial (fig.~\ref{fig:method}C-E).
-    A similar approach demonstrated the presence of beneficial non-adaptive mutations in humans~\cite{moses_inferring_2009, fischer_germline_2011} and in plants~\cite{chen_hunting_2021}.
-    However, the model used to reconstruct the static fitness landscape in these studies can only be applied to deeply conserved protein domains in the tree of life, which corresponds to a subpart of the proteome that evolves slowly.
-    The mutation-selection model used in the present work integrates phylogenetic relationships, and thus allows us to estimate the fitness landscape in shallower phylogenetic trees, and therefore can be applied almost exome-wide~\cite{rodrigue_mutationselection_2010}.
-
-    We first quantified the likelihood of any DNA mutation to be a beneficial non-adaptive mutation, that is, whenever a DNA mutation increases fitness under a stable fitness landscape.
-    Subsequently, by quantifying the total amount of beneficial mutations in the current population across all types of DNA mutations, we could tease apart beneficial non-adaptive from adaptive mutations resulting from a change in the fitness landscape.
-    Altogether, in this study, by integrating large-scale genomic datasets at both phylogenetic and population scales, we propose a way to explicitly quantify the contribution of beneficial non-adaptive mutations to positive selection across the entire exome of the six genera (figs.~\ref{fig:method}F-G).
-
-    \section*{Results}
-
-    \subsection*{Selection along the terminal branches}
-    First, we assessed whether fitness effects derived from the mutation-selection model at the phylogenetic scale predict selection occurring in terminal branches.
-    We recovered the mutations that reached fixation in the terminal branches of the six genera.
-    We only considered mutations fixed in a population as substitutions in the corresponding branch by discarding mutations segregating in our population samples.
-    For each substitution identified in the terminal branches we obtained its $\Sphy$ value such as predicted at the mammalian scale (fig.~\ref{fig:method}A-B).
-    We could classify each substitution as either deleterious $\SphyDel \coloneqq \Sphy < -1$), nearly-neutral ($\SphyNeu \coloneqq -1 < \Sphy <1$), or beneficial ($\SphyBen \coloneqq \Sphy > 1$)
-    Because $\Sphy$ values were based on the assumption that the fitness landscape is stable across mammals, $\SphyBen$ mutations (i.e., with $\Sphy>1$) bring the bearer of this mutation toward an amino acid predicted to be fitter across mammals.
-    Importantly, the mammalian alignment used to estimate the amino acid fitness landscape did not include the six focal genera and their sister species.
-    This ensures independence between, on the one hand, the fitness landscape estimated, and on the other hand, both substitutions that occurred in the terminal branches, and segregating polymorphisms of the focal populations.
-    Example substitutions in the terminal lineage of \textit{Chlorocebus sabaeus} which are classified as $\SphyBen$ are shown in supplementary materials (section S2).
-    For instance, in the mammalian protein-coding DNA alignment of gene \textit{SELE}, the nucleotide at site 1722 has mutated (from T to C) at the base of Simiiformes (monkeys and apes), modifying the corresponding amino acid from Serine to Proline, but has been subsequently reverted in the branch of \textit{Chlorocebus sabaeus} (fig.~S2).
-    However, other substitutions classified as $\SphyBen$ in the terminal branch of \textit{Chlorocebus sabaeus} cannot be clearly interpreted as reversions along the terminal branch, and show several transitions to this amino acid across the mammalian phylogeny, as for instance site 3145 of gene \textit{THSD7A} (fig.~S3).
-
-    Among all the substitutions found in each terminal branch, between 10 and 13\% were $\SphyBen$, while $\SphyBen$ mutations only represent between 0.9 and 1.2\% of all non-synonymous mutations (table~S1 and fig.~\ref{fig:homo-afr-results}A-B for humans).
-    Of note, if we were to assume a stationary mutation-selection-drift equilibrium in the terminal lineage, we would expect a symmetric proportion of positively ($\SphyBen$) and negatively ($\SphyDel$) selected substitutions if there were no adaptation.
-    The lack of symmetry along the terminal branches then provides a means to estimate the frequency of non-adaptive beneficial substitutions.
-    Mathematically, twice the fraction of $\SphyBen$ substitutions is an estimate of this rate.
-    This rate is highly consistent across lineages (table~S1) and suggests an overall frequency of nearly neutral substitutions due to consistent long-term selection pressures, mutation and drift of approximately 20\% of all substitutions (20\%-26\% across species).
-
-    Furthermore, since in principle, $\SphyBen$ mutations are bound to reach fixation more often than neutral mutations, we calculated the $\dnds$ ratio of non-synonymous over synonymous divergence for all terminal lineages, focusing on the non-synonymous changes predicted as $\SphyBen$ mutations ($\dn(\SphyBen) / \ds$).
-    We obtained values between 1.17 and 1.75 in the different lineages (table~S2), meaning that $\SphyBen$ mutations reach fixation slightly more frequently than synonymous mutations that are supposed to be neutral, consistent with these $\SphyBen$ mutations being weakly beneficial.
-    Such an observation is consistent with the premise that $\SphyBen$ mutations are weakly beneficial, translating to a scaled selection coefficient between 0.32 and 1.24 (table~S2).
-    Finding $\dn(\SphyBen) / \ds > 1$ for these sites confirms that these sites are closer to optimality at the end of the branch than at the beginning.
-    Even though the beneficial effect of these mutations does not come from an environmental change, it does not change the fact that they have contributed positively to the population’s fitness.
-    It is just that at mutation-selection-drift equilibrium, the increase in fitness at these sites is offset by deleterious substitutions elsewhere in the genome so that there is no net adaptation.
-
-    This result further indicates that using $\dnds$ as an estimate of purifying selection is biased (overestimated) due to the presence of beneficial non-adaptive mutations among the non-synonymous substitutions.
-    By discarding all beneficial non-adaptive mutations we can obtain an estimate of $\dnds$ which is not inflated.
-    By comparing these two ways of calculating $\dnds$ (see section~\ref{subsec:substitution-mapping-in-the-terminal-branch} in Materials \& Methods), we calculated that beneficial non-adaptive mutations inflate $\dnds$ values by between 9 and 12\% across genera.
-This represents a substantial increase when considering that beneficial non-adaptive mutations only represent between 0.9 and 1.2\% of non-synonymous mutational opportunities (table~S3).
-
-    \subsection*{Selection in populations}
-    Second, we assessed whether our calculated $\Sphy$ values predicted at the phylogenetic scale were also indicative of the selective forces exerted at the population level.
-    We retrieved single nucleotide polymorphisms (SNPs) segregating in 28 mammalian populations.
-    To determine if SNPs were ancestral of derived, we reconstructed the ancestral exome of each population.
-    We then classified every non-synonymous SNP as either $\SphyDel$, $\SphyNeu$, or $\SphyBen$ according its $\Sphy$ value (fig.~\ref{fig:method}B-C).
-
-    First, SNPs classified as $\SphyBen$ are spread across the genomes and not strongly associated to the ontology terms of their respective genes (table~S4, fig.~S4).
-    In humans, some SNPs have been associated with specific clinical prognosis terms obtained by clinical evaluation of the impact of variants on human Mendelian disorders~\cite{landrum_clinvar_2018}.
-    Although this classification also relies on deep protein alignments and therefore cannot be considered an independent result from our own, it does provide a consistency check if the effect of a mutation on human health is in line with its fitness effect predicted by our method~\cite{grimm_evaluation_2015}.
-    Therefore, we investigated whether the non-synonymous SNPs classified as $\SphyDel$ or $\SphyBen$ showed enrichment in specific clinical terms compared to SNPs classified as $\SphyNeu$.
-    Our results show that SNPs predicted as deleterious are associated with clinical terms such as \textit{Likely Pathogenic} and \textit{Pathogenic}, implying that, in general, the selective pressure of a mutation exerted across mammals is also predictive of its clinical effect in humans (table~S5)~\cite{sullivan_leveraging_2023}.
-    Conversely, $\SphyBen$ mutations are associated with clinical terms such as \textit{Benign} and \textit{Likely Benign}, which shows that $\SphyBen$ mutations are less likely to be functionally damaging (table~S6).
-
-    In addition to clinical prognosis, frequencies at which SNPs are segregating within populations provide information on their selective effects.
-    For instance, deleterious SNPs usually segregate at lower frequencies because of purifying selection, which tends to remove them from the population (fig.~\ref{fig:homo-afr-results}C for humans).
-    By gathering information across many SNPs, it is possible to estimate the distribution of fitness effects at the population scale, taking synonymous SNPs as a neutral expectation~\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009, galtier_adaptive_2016, tataru_inference_2017}.
-    From these estimated fitness effects, we can derive the proportion of beneficial mutations ($\ProbaPopBen$), nearly-neutral mutations ($\ProbaPopNeu$) and deleterious mutations ($\ProbaPopDel$) at the population scale (see section~\ref{subsec:s-polymorphism-method} in Materials \& Methods, figs.~S5-S8).
-    These approaches offer a unique opportunity to contrast selection coefficients estimated at the population scale ($\Spop$) and at the phylogenetic scale ($\Sphy$).
-
-    Across our selection classes ($\SphyDel$, $\SphyNeu$ and $\SphyBen$), one can ultimately estimate the proportion of correct and incorrect predictions, leading to an estimation of \textit{precision} and \textit{recall} (fig.~\ref{fig:method}F-G and section~\ref{subsec:precisison_recall} in Materials \& Methods).
-    Across 28 populations of different mammal species, mutations predicted to be deleterious at the phylogenetic scale ($\SphyDel$) were indeed purged at the population scale, with a \textit{precision} in the range of 90--97\% (table~\ref{table:proba} and fig.~\ref{fig:homo-afr-results}D for humans).
-    Conversely, a \textit{recall} in the range of 96--100\% implied that mutations found to be deleterious at the population scale were most likely also predicted to be deleterious at the phylogenetic scale (table~\ref{table:proba}).
-    Altogether, purifying selection is largely predictable and amino acids with negative fitness across mammals have been effectively purged away in each population.
-
-    Mutations predicted as $\SphyNeu$ were effectively composed of a mix of neutral and selected mutations with varying \textit{precision} (36--63\%) and \textit{recall} (32--45\%) across the different populations (table~\ref{table:proba}, fig.~\ref{fig:homo-afr-results}D for humans).
-    The variable proportions between populations can be explained by the effective number of individuals in the population ($\Ne$), a major driver of selection efficacy.
-    Moreover, estimates of mutation rate per generation ($u$), from Bergeron \textit{et al.}~\cite{bergeron_evolution_2023} and Orlando \textit{et al.}~\cite{orlando_recalibrating_2013}, and Watterson’s $\theta$ obtained from the synonymous SFS as in Achaz~\cite{achaz_frequency_2009}, allow us to obtain $\Ne$ through $\Ne=\theta/4 u)$.
-    Using correlation analyses that accounted for phylogenetic relationship (see section \ref{subsec:correlation-diversity} in Materials \& Methods), we found that higher $\Ne$ was associated with a smaller proportion of nearly-neutral mutations ($r^2=0.31$, $p=0.001$, fig.~\ref{fig:diversity}A).
-    This result follows the prediction of the nearly-neutral theory and suggests that in populations with higher diversity (e.g.,~\textit{Bos} or \textit{Ovis}), discrimination between beneficial and deleterious mutations is more likely to occur (figs.~S9-S12).
-    Conversely, many more mutations are effectively neutral in populations with lower diversity (e.g.,~\textit{Homo}).
-
-    Finally, mutations predicted to be $\SphyBen$ were indeed beneficial for individuals bearing them, with a \textit{precision} (fig.~\ref{fig:method}F) in the range of 19--87\% (table~\ref{table:proba} and fig.~\ref{fig:homo-afr-results}D for humans).
-    This result confirms that selection toward amino acids restoring existing functions is ongoing in these populations.
-    Importantly, the \textit{recall} value in this case, computed as $\proba [ \SphyBen \given \SpopBen]$, is the probability for a beneficial mutation at the population scale to be a non-adaptive, i.e., going toward a fitter amino acid given a stable fitness landscape (fig.~\ref{fig:method}G, table~S7).
-    In other words, the \textit{recall} value quantifies the number of beneficial mutations restoring damaged genomes instead of creating adaptive innovations.
-    Across the 28 populations, this proportion is in the range of 11--82\% (table~\ref{table:proba}), with a mean of 30\%.
-    Accounting for phylogenetic relationships, we found no correlation between the proportion of beneficial non-adaptive mutations and estimates of $\Ne$ based on genetic diversity ($r^2=0.00$, $p=0.772$, fig.~\ref{fig:diversity}B).
-
-    We additionally performed controls and simulations to ensure our results were robust.
-    First, we controlled that these estimations were not affected by SNP mispolarization (figs.~S13-S14).
-    Second, we performed simulations at the population-genetic level and confirmed that our method was able to recover the proportion of beneficial mutations that are non-adaptive in synthetic polymorphism datasets (fig.~S15).
-    Third, we ran our analysis filtering out CpG mutations and obtained values of $\proba [ \SphyBen \given \SpopBen]$ in the range of 5--27\%, with a mean of 14\% (tables~S8-9 and fig.~S16-17), providing more conservative estimates.
-    Finally, because the phylogenetic mutation-selection codon model should fit better for genes with uniformly conserved functions, we filtered out genes under pervasive adaptation~\cite{latrille_genes_2023} as a control.
-    In this subset of the exome, containing genes with a more stable fitness landscape, we found an increase in the proportion of beneficial mutations that are non-adaptive (Wilcoxon signed-rank, $s=80$, $p=0.002$, table~S10), consistent with our expectation that beneficial mutations occur more frequently in genes under changing fitness landscapes.
-
-    \subsection*{Selection in the terminal lineage and in populations}
-
-    As an alternative to relying solely on currently segregating mutations to quantify selection, one can leverage both polymorphism within a population and substitutions in the terminal lineage to estimate the distribution of fitness effects (DFE).
-    Hence, we estimated \textit{precision} and \textit{recall} as done previously, but now including the number of substitutions per site as input for the DFE estimators (see \ref{subsec:s-polymorphism-method} in Materials \& Methods and fig.~S18).
-    When including substitutions in the terminal lineage, estimates of $\proba [ \SphyBen \given \SpopBen]$ are in the 10--78\% range with a mean of 36\% (table~S11-12), and 19 out of 28 estimates fall between 15\% and 45\%.
-
-    Additionally, we controlled that these estimations were not affected by SNP mispolarization (fig.~S19).
-    We also filtered out genes under pervasive adaptation, and again found an increase in $\proba [ \SphyBen \given \SpopBen]$, consistent with our expectation (Wilcoxon signed-rank, $s=120$, $p=0.027$, table~S13).
-    We assessed the impact of fitting the same functional form of DFE to the three different categories of changes $\SphyDel$, $\SphyNeu$ and $\SphyBen$.
-    To this aim we computed the total amount of current selection by fitting either a single DFE on the whole dataset or by summing the other three independent DFEs.
-    These disjoint estimates are well correlated, with a goodness of fit $r^2={0.95, 0.89, 0.82}$ for $\proba [\SpopDel]$, $\proba [\SpopNeu]$ and $\proba [\SpopBen]$, respectively (figs.~S20-22).
-    Finally, we evaluated the effect of fitting a parametric functional form for the DFE.
-    As implemented in Tataru \textit{et al.}~\cite{tataru_inference_2017}, the DFE is a mixture between a reflected gamma distribution and an exponential distribution (eq.~\ref{eq:parametric-dfe}, section~\ref{subsec:precisison_recall} in Materials \& Methods).
-    Instead of using such a continuous DFE, we also tested our prediction with a non-parametric functional form for the DFE, obtaining estimates of $\proba [ \SphyBen \given \SpopBen]$ in the 8--94\% range, with a mean of 43\% (tables~S14-15).
-
-    \section*{Discussion}
-    \subsection*{Beneficial mutations are not necessarily adaptive}
-
-    This study represents an essential step toward integrating the different evolutionary scales necessary to understand the combined effects of mutation, selection, and drift on genome evolution.
-    In particular, we have been able to quantify the proportion of beneficial mutations that are non-adapative (i.e., not a response to a change in fitness landscape), which has only been achievable by combining exome-wide data from both phylogenetic and population scales.
-    At the phylogenetic scale, codon diversity at each site of a protein-coding DNA alignment allows for reconstructing an amino-acid fitness landscape, assuming that this landscape is stable along the phylogenetic tree.
-    These amino-acid fitness landscapes allow us to predict any mutation’s selection coefficient ($\Sphy$) along a protein-coding sequence.
-    We have compared these selective effects to observations at the population level, and by doing so, we have confirmed that mutations predicted to be deleterious ($\SphyDel \coloneqq \Sphy < -1$) are generally purified away in extant populations.
-    Our results concur with previous studies showing that SIFT scores~\cite{ng_sift_2003, vaser_sift_2016}, based on amino acid alignments across species, also inform on the deleterious fitness effects exerted at the population scale~\cite{chen_hunting_2021}.
-    However, contrary to SIFT scores, our mutation-selection model is parameterized by a fitness function such that changes are directly interpretable as fitness effects (see also section S5).
-    In this regard, an interesting prediction of our model is that some deleterious mutations reach fixation due to genetic drift, while beneficial non-adaptive mutations restore states of higher fitness.
-    We have tested this hypothesis and have found that a substantial part of these predicted non-adaptive mutations ($\SphyBen \coloneqq \Sphy > 1 $) are indeed beneficial in extant populations.
-    We estimate that between 11 and 82\% of all beneficial mutations in mammalian populations are not adaptive.
-    More specifically, in 24 out of 28 populations analyzed, the percentage of beneficial mutations estimated to be non-adaptive falls between 15 and 45\%.
-    These results suggest that many beneficial mutations are not adaptive, but rather restore states of higher fitness.
-    Hence, we can correctly estimate the extent of adaptive evolution only if we account for the number of beneficial non-adaptive mutations~\cite{keightley_what_2010, rice_evolutionarily_2015}.
-    Here instead, we argue that we should dissociate positive selection from adaptive evolution and limit the use of adaptive mutations to those that are associated with adaptation to environmental change as such~\cite{charlesworth_other_2007, mustonen_fitness_2009, mustonen_fitness_2010}.
-
-    \subsection*{Assumptions and methodological limitations}
-
-    The exact estimation of the contribution of beneficial non-adaptive mutations to positive selection relies on some hypotheses at both the phylogenetic and population scales and is sensitive to methodological limitations.
-    Indeed, data quality and potentially inadequate modeling choices of both the fitness landscape (at the phylogenetic scale) and fitness effects (at the population scale) might also lead to missed predictions~\cite{moutinho_variation_2019}.
-    In practice, we obtained different values of the proportion of non-adaptive beneficial mutations depending on i) the filtering or not of CpG mutations~\cite{eyre-walker_how_2014}, ii) whether we included substitutions in the terminal lineage along with within-population polymorphisms to estimate fitness effects~\cite{tataru_inference_2017}, and iii) the model used to infer the fitness effects.
-    It appears that our estimation can be sensitive to model misspecification and overall, while we provide an order of magnitude for the contribution of beneficial non-adaptive mutations to positive selection, methodological improvement on the estimation of the DFE is needed to increase the precision of this value.
-
-    To be conservative, we considered mutations as adaptive if they were detected as being under positive selection at the population scale despite them being either incorrectly predicted as deleterious ($\SphyDel$) or nearly-neutral ($\SphyNeu \coloneqq -1 < \Sphy <1$) from the amino-acid mammalian fitnesses.
-    An example of an incorrectly predicted deleterious mutation ($\SphyDel$) from its fitness landscape could be an amino acid having always been deleterious across mammals, but being advantageous ($\SpopBen$) in the current species due to environmental changes or a major shift in their fitness landscape (e.g.
-domestication)
-    To visualize an example of a wrongly predicted nearly-neutral mutation, we can first imagine a site where only hydrophilic amino acids are accepted because of the protein properties (e.g.
-a surface site of a globular protein).
-    Let us then assume that such a site is also a target for viruses, hence promoting amino-acid changes which modify the site's viral affinity~\cite{enard_viruses_2016}.
-    Given the selective pressure favoring amino-acid change, but restricting the possibilities to hydrophilic amino acids, most hydrophilic amino acids will likely be visited along the phylogenetic tree and the mutation-selection model will give high and similar fitnesses to all of them.
-    In such a case, any mutation between hydrophilic amino acids will be wrongly predicted as nearly-neutral ($\SphyNeu$), while it is in fact adaptive.
-    In summary, under a changing fitness landscapes~\cite{mustonen_molecular_2008}, our phylogenetic mutation-selection model takes an average over fitness changes observed along the phylogeny, causing beneficial mutations ($\SpopBen$) to be predicted as either deleterious ($\SphyDel$) or nearly-neutral ($\SphyNeu$), therefore mechanically reducing $\proba [ \SphyBen \given \SpopBen]$, and making our estimate conservative.
-
-    \subsection*{Convergent adaptation}
-
-    If there are several substitutions toward the same amino acid along the mammalian tree (see fig.~S3), our mutation-selection model cannot formally distinguish between a scenario where mammals have fixed deleterious mutations that are reverted in several lineages, from more complex scenarios involving convergent adaptation across mammals.
-    In a first scenario, repeated changes of fitness landscapes in the same direction could occur along several lineages, leading to repeated substitutions in multiple lineages (parallel or convergent adaptation).
-    In a second scenario, an environmental change that occurred near the root of placental mammals ($\sim$100 Mys ago), to which extant populations are currently responding independently through weakly adaptive mutations, could also lead to repeated substitutions toward the same amino acids.
-    Importantly, we would usually expect adaptive convergent mutations to be linked to particular converging phenotypes across mammals, and hence, they should not massively affect the whole genome as we find (table~S4, fig.
-S4).
-    Moreover, after filtering out genes usually associated to recurrent adaptation (e.g. immune genes), we recover an even higher proportion of beneficial non-adaptive mutations (table~S8).
-    For these reasons, we argue that the signal of predictable positive selection we recover in extant population is indeed mainly driven by non-adaptive evolution.
-
-    \subsection*{The influence of effective population size}
-
-    Across the genome, beneficial non-adaptive mutations and deleterious mutations reaching fixation create a balance in which genomes are constantly damaged and restored simultaneously at different loci due to drift.
-    Since the probability of fixation of mutations depends on the effective population size ($\Ne$), the history of $\Ne$ plays a crucial role in determining the number of beneficial non-adaptive mutations compensating for deleterious mutations~\cite{latrille_inferring_2021}.
-    For example, a population size expansion will increase the efficacy of selection, and a larger proportion of mutations will be beneficial (otherwise effectively neutral), thus increasing the number of beneficial non-adaptive mutations.
-    On the other hand, a population that has experienced a high $\Ne$ throughout its history should be closer to an optimal state under a stable fitness landscape, having suffered fewer fixations of deleterious mutations and therefore decreasing the probability of beneficial non-adaptive mutations~\cite{huber_determining_2017}.
-    Overall, we expect the proportion of beneficial non-adaptive mutations to be more dependent on $\Ne$’s long-term expansions and contractions than on the short-term ones~\cite{charlesworth_other_2007,huber_determining_2017}.
-
-    Moreover, because our model assumes a fixed fitness landscape, it implicitly assumes that $\Ne$ is constant along the phylogenetic tree.
-    Fluctuations due to changes in the fitness landscape or in $\Ne$ will be averaged out by the assumption of the current model that $\Ne$ is constant across lineages.
-    It was recently shown~\cite{latrille_inferring_2021}, using computer intensive mutation-selection models with fluctuating $\Ne$, that relaxing the assumption of a constant $\Ne$ results in more extreme estimates of amino-acid fitnesses than with the standard model used in this study.
-    In other words, by assuming a constant $\Ne$, we are underpowered to detect beneficial non-adaptive mutations since amino acids will have more similar fitnesses.
-    As a consequence, some of the beneficial non-adaptive mutations currently segregating in population will be incorrectly classified as nearly-neutral by the mutation-selection model, and thus be wrongly interpreted as adaptive (see previous section).
-    This ultimately results in lower estimates of the proportion of beneficial non-adaptive mutations.
-    Given this inflation of missed predictions due to change in population sizes~\cite{lanfear_population_2014, jones_shifting_2017, platt_protein_2018}, our estimated proportion of beneficial non-adaptive mutations among adaptive ones is likely to be an underestimation.
-
-    \subsection*{The role of epistasis and compensatory mutations}
-
-    Our model assumes that amino-acid fitness landscapes are site-specific and also independent of one another, whereas under pervasive epistasis, the fitness effect of any mutation at a particular site would depend on the amino acids present at other sites.
-    Epistasis is common for mutations that influence the protein’s physical properties (e.g.
-conformation, stability, or affinity for ligands) or might arise due to nonlinear relationship between the protein’s physical properties and fitness~\cite{starr_epistasis_2016}.
-    Regardless of its origin, epistasis has been shown to play a role in the evolution of protein-coding genes, with amino-acid residues in contact within a protein or between proteins tending to co-evolve~\cite{morcos_directcoupling_2011, marks_protein_2012, starr_epistasis_2016}.
-    Particularly, the residues in contact co-evolve to become more compatible with each other generating an entrenchment~\cite{goldstein_nonadaptive_2015, goldstein_sequence_2017, park_epistatic_2022}.
-    Epistasis therefore allows for compensatory mutations, which restore fitness through mutations at loci different from where deleterious mutations took place, representing another case of non-adaptive beneficial mutations, but one which is not accounted for by our method.
-    Hence, the beneficial mutations that we classify as putatively adaptive might in fact be compensatory mutations, making our estimation of the rate of non-adaptive beneficial mutations conservative.
-
-    Despite epistasis being an important factor in protein evolution, several deep-mutational scanning experiments have revealed that a site-specific fitness landscape predicts the evolution of sequences in nature with considerable accuracy~\cite{ashenberg_mutational_2013, doud_sitespecific_2015, bloom_identification_2017}.
-    Additionally, the fact that we observe such a high proportion of beneficial non-adaptive mutations suggests that the underlying assumptions of our model, namely site-independence, implying no epistasis, and a static fitness landscape, are a reasonable approximation for the underlying fitness landscape of proteins.
-    Our results imply that the fitness effects of new mutations are mostly conserved across mammalian orthologs, in agreement with other studies showing that for conserved orthologs with similar structures and functions, models without epistasis provide a reasonable estimate of fitness effects in protein coding genes~\cite{youssef_consequences_2020, vigue_deciphering_2022}.
-    Conceptually, the framework presented here, with the addition of a more complex protein fitness landscape at the phylogenetic scale, could be used to infer the relative contribution of compensatory mutations to non-adaptive and adaptive evolution.
-
-    \subsection*{Detecting adaptation above the nearly-neutral background}
-
-    A long-standing debate in molecular evolution is whether the variation we observe between species in protein-coding genes is primarily due to nearly-neutral mutations reaching fixation by drift or primarily due to adaptation~\cite{kimura_evolutionary_1968,ohta_nearly_1992,gillespie_substitution_1994,jensen_importance_2019}.
-    Measuring the ``rate of adaptation'' in proteins, as pioneered by McDonald \& Kreitman~\cite{mcdonald_adaptative_1991}, has been central to inform this debate~\cite{galtier_half_2024}.
-    However, the McDonald \& Kreitman test detects signatures of accelerated evolution in a given terminal branch compared to an expectation based on polymorphism present in the population.
-It considers the fraction of substitutions that fix too quickly as ``adaptive''~\cite{mcdonald_adaptative_1991, smith_adaptive_2002, welch_estimating_2006} despite there being other processes that can lead to their fixation~\cite{galtier_adaptation_2007,rousselle_influence_2019,joseph_increased_2024a} and some of these substitutions being beneficial but non-adaptive~\cite{hartl_compensatory_1996, charlesworth_other_2007, mustonen_fitness_2009, jones_shifting_2017}.
-    Here, the expectation is built on the pattern of substitutions across a phylogeny compared to the fitness effects that can be estimated from both substitutions in a terminal lineage and polymorphism in populations.
-    Moreover, the goal is not to detect a fraction of beneficial substitution (i.e.
-``adaptive'' substitutions for McDonald \& Kreitman~\cite{mcdonald_adaptative_1991}), but to estimate the proportion of non-adaptive mutations among beneficial ones.
-
-    We provide evidence that in mammalian orthologs, many substitutions occur through fixation of both deleterious mutations and beneficial non-adaptive mutations.
-    Detecting adaptation above this background of substitutions remains a challenge~\cite{kimura_evolutionary_1968, ohta_development_1996}.
-    Mathematically, the surplus of positive selection due to an externally-driven changing fitness landscape is called \textit{fitness flux}, and requires experimentally measuring the selection coefficient of each mutation in each genetic background.
-    The \textit{fitness flux} can be estimated if either the substitutions history is known~\cite{mustonen_fitness_2009} or changes of frequency in currently segregating variants~\cite{mustonen_fitness_2010}.
-    Without experimentally measured selection coefficients, another strategy is precisely to use a nearly-neutral substitution model as a null model of evolution.
-    Under a strictly neutral evolution of protein-coding sequence, we expect the ratio of non-synonymous over synonymous substitutions ($\dnds$) to be equal to one.
-    Deviations from this neutral expectation, such as $\dnds > 1$, which can be generated by an excess of non-synonymous substitutions, is generally interpreted as a sign of adaptation.
-    However, as shown in this study, a $\dnds > 1$ is not necessarily a signature of adaptation but can be due to beneficial non-adaptive mutations.
-    So, by relaxing the strict neutrality and assuming a stable fitness landscape instead, one can predict the expected rate of evolution, called $\omega_0$~\cite{spielman_relationship_2015, dosreis_how_2015}.
-    Adaptation can thus be considered as evolution under a changing fitness landscape and tested as such by searching for the signature of $\dnds > \omega_0$~\cite{cvijovic_fate_2015, rodrigue_detecting_2017, rodrigue_bayesian_2021}.
-    Using a stable fitness landscape as a null model of evolution, thus accounting for selective constraints exerted on the different amino acids, increased the statistical power in testing for adaptation~\cite{latrille_genes_2023}.
-    Instead of relying solely on summary statistics (such as $\dnds$ or $\omega_0$), another strategy to detect adaptation is to include changes in the fitness landscapes inherently within the mutation selection framework, either with small changes along the phylogeny ~\cite{tamuri_mutationselection_2021} or either by allowing fitness to change on subsets of branches ~\cite{kazmi_detecting_2019, stolyarova_senescence_2020}.
-    Such mechanistic models could be more general than site-specific fitness landscapes, including epistasis and changing fitness landscapes~\cite{goldstein_sequence_2017, stolyarova_senescence_2020}.
-
-    \subsection*{Conclusions}
-
-    We have provided empirical evidence that an evolutionary model assuming a stable fitness landscape at the mammalian scale allows us to predict the fitness effects of mutations in extant populations and individuals, acknowledging the balance between deleterious and beneficial non-adaptive mutations.
-    We argue that such a model would represent a null expectation for the evolution of protein-coding genes in the absence of adaptation.
-    Altogether, because a substantial part of positive selection can be explained by beneficial non-adaptive mutations, but not its entirety, we argue that the mammalian exome is shaped by both adaptive and non-adaptive processes, and that none of them alone is sufficient to explain the observed patterns of changes.
-    In that sense, to avoid conflating beneficial mutations with adaptive evolution, the term ``adaptation`` should retain its original meaning associated with a change in the underlying fitness landscape and be modelled as such~\cite{mustonen_fitness_2009, mustonen_fitness_2010}.
-
-    \newpage
-    \section{Materials \& Methods}
-    \label{sec:methods}
-
-    \subsection{Phylogenetic dataset}\label{subsec:phylo-dataset}
-
-    Protein-coding DNA sequence alignments in placental mammals and their corresponding gene trees come from the \href{https://www.orthomam.univ-montp2.fr}{OrthoMaM} database and were processed as in Latrille \textit{et al.}~\cite{latrille_genes_2023}.
-    OrthoMaM contains a total of $116$ mammalian reference sequences in v10c~\cite{ranwez_orthomam_2007, douzery_orthomam_2014, scornavacca_orthomam_2019}.
-
-    Genes located on the X and Y chromosomes and on the mitochondrial genome were discarded from the analysis because the level of polymorphism –~which is necessary for population-based analyses~– is expected to be different in these three regions compared to the autosomal genome.
-    Sequences of species for which we used population-level polymorphism (see section \ref{subsec:polymorphism-dataset}) and their sister species, were removed from the analysis to ensure independence between the data used in the phylogenetic and population scales.
-    Sites in the alignment containing more than 10\% of gaps across the species were discarded.
-    Altogether, our genome-wide dataset contains $14,509$ protein-coding DNA sequences in $87$ placental mammals.
-
-    \subsection{Selection coefficient ($\Sphy$) in a phylogeny-based method}
-    \label{subsec:s-phylogeny-method}
-
-    We analyzed the phylogenetic-level data using mutation-selection models.
-    These models assume the protein-coding sequences are at mutation-selection balance under a fixed fitness landscape characterized by a fitness vector over the $20$ amino acids at each site~\cite{yang_mutationselection_2008, halpern_evolutionary_1998, rodrigue_mechanistic_2010}.
-    Mathematically, the rate of non-synonymous substitution from codon $a$ to codon $b$ ($q_{a \mapsto b}^{(i)}$) at site $i$ of the sequence is equal to the rate of mutation of the underlying nucleotide change ($\mu_{a \mapsto b}$) multiplied by the scaled probability of mutation fixation ($\proba_{a \mapsto b}^{(i)}$).
-    The probability of fixation depends on the difference between the scaled fitness of the amino acid encoded by the mutated codon ($F_b^{(i)}$) and the amino acid encoded by the original codon ($F_a^{(i)}$) at site $i$~\cite{wright_evolution_1931, fisher_genetical_1930}.
-
-    The rate of substitution from codon $a$ to $b$ at a site $i$ is thus:
-    \begin{equation}
-        \begin{dcases}
-            q_{a \mapsto b}^{(i)} & = 0 \text{ if codons $a$ and $b$ are more than one mutation away,} \\
-            q_{a \mapsto b}^{(i)} & = \mu_{a \mapsto b} \text{ if codons $a$ and $b$ are synonymous, and}\\
-            q_{a \mapsto b}^{(i)} & = \mu_{a \mapsto b} \dfrac{F_b^{(i)} - F_a^{(i)}}{1 - \e^{F_a^{(i)} - F_b^{(i)}}} \text{ if codons $a$ and $b$ are non-synonymous}.
-        \end{dcases}
-    \end{equation}
-
-    Fitting the mutation-selection model on a multi-species sequence alignment leads to an estimation of the gene-wide $4 \times 4$ nucleotide mutation rate matrix ($\UniDimArray{\mu}$) as well as the $20$ amino-acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$.
-    The priors and full configuration of the model are given in section S1.
-    From a technical perspective, the Bayesian estimation is a two-step procedure~\cite{rodrigue_bayesian_2008}.
-    The first step is a data augmentation of the alignment, consisting in sampling a detailed substitution history along the phylogenetic tree for each site, given the current value of the model parameters.
-    In the second step, the parameters of the model can then be directly updated by a Gibbs sampling procedure, conditional on the current substitution history.
-    Alternating between these two sampling steps yields a Markov chain Monte-Carlo (MCMC) procedure whose equilibrium distribution is the posterior probability density of interest~\cite{lartillot_bayesian_2004, rodrigue_bayesian_2008}.
-    Additionally, across-site heterogeneities in amino-acid fitness profiles are captured by a Dirichlet process.
-    More precisely, the number of amino-acid fitness profiles estimated is lower than the number of sites in the alignment.
-    Consequently each profile has several sites assigned to it, resulting in a particular configuration of the Dirichlet process.
-    Conversely, sites with similar signatures are assigned to the same fitness profile.
-    This configuration of the Dirichlet process is resampled through the MCMC to estimate a posterior distribution of amino acid profiles for each site specifically~\cite{rodrigue_mutationselection_2010, lartillot_inference_2013}.
-    From a more mechanistic perspective, even though not all amino acids occur at every single codon site of the DNA alignment, we can nevertheless estimate the distribution of amino-acid fitnesses by generalizing the information recovered across sites and across amino acids based on the phylogenetic relationship among samples.
-    In particular, synonymous substitutions along the tree contain the signal to estimate branch lengths and the nucleotide transition matrix, while non-synonymous substitutions contain information on fitness difference between codons connected by single nucleotide changes~\cite{rodrigue_mutationselection_2010}.
-
-    The selection coefficient for a mutation from codon $a$ to codon $b$ at site $i$ is defined as:
-    \begin{equation}
-        \Sphy^{(i)} (a \mapsto b) = \Delta F^{(i)} = F^{(i)}_{b} - F^{(i)}_{a}.
-    \end{equation}
-    In our subsequent derivation the source ($a$) and target ($b$) codons as well as the site ($i$) are implicit and thus never explicitly written.
-
-    The scaled selection coefficient ($\Sphy = \Delta F$) is formally the product of the selection coefficient at the individual level ($s$) and the effective population size ($\Ne$), as $\Sphy = 4 \Ne \times s$.
-The value of $\Sphy$ informs us on the strength of selection exerted on amino acids changes.
-    Thus, according to its $\Sphy$ value, we can classify any mutation as either a deleterious mutation toward a less fit amino acid ($\SphyDel \coloneqq \Sphy < -1$), a nearly-neutral mutation ($\SphyNeu \coloneqq -1 < \Sphy <1$), or a mutation toward a known fitter amino acid, constituting thus a beneficial non-adaptive mutation ($\SphyBen \coloneqq \Sphy > 1$).
-
-    We used the Bayesian software \textit{BayesCode} (\url{https://github.com/ThibaultLatrille/bayescode}, v1.3.1) to estimate the selection coefficients for each protein-coding gene in the mammalian dataset.
-    We ran the MCMC algorithm implemented in BayesCode for $2,000$ generations as described in Latrille \textit{et al.}~\cite{latrille_genes_2023}.
-    For each gene, after discarding a burn-in period of $1,000$ generations of MCMC, we obtained posterior mean estimates (over the $1,000$ generations left of MCMC) of the mutation rate matrix ($\UniDimArray{\mu}$) as well as the $20$ amino-acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$.
-
-    \subsection{Polymorphism dataset}
-    \label{subsec:polymorphism-dataset}
-
-    The genetic variants representing the population level polymorphisms were obtained from the following species and their available datasets: \textit{Equus caballus} (EquCab2 assembly in the EVA study PRJEB9799~\cite{alabri_whole_2020}), \textit{Bos taurus} (UMD3.1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}), \textit{Ovis aries} (Oar\_v3.1 assembly in the NextGen project), \textit{Capra hircus} (CHIR1 assembly in the NextGen project), converted to ARS1 assembly with dbSNP identifiers~\cite{sherry_dbsnp_2001}), \textit{Chlorocebus sabaeus} (ChlSab1.1 assembly in the EVA project PRJEB22989~\cite{svardal_ancient_2017}), \textit{Homo sapiens} (GRCh38 assembly in the 1000 Genomes Project~\cite{zheng-bradley_alignment_2017}).
-    In total, we analyzed 28 populations across the 6 different species with polymorphism data.
-    The data was processed as described in Latrille \textit{et al.}~\cite{latrille_genes_2023}.
-
-    Only bi-allelic single nucleotide polymorphisms (SNPs) found within a gene were in our polymorphism dataset, while nonsense variants and indels were discarded.
-    To construct the dataset, we first recovered the location of each SNP (represented by its chromosome, position, and strand) in the focal species and matched it to its corresponding position in the coding sequence (CDS) using gene annotation files (GTF format) downloaded from Ensembl (\url{ensembl.org}).
-    We then verified that the SNP downloaded from Ensembl matched the reference in the CDS in FASTA format.
-    Next, the position in the CDS was converted to the corresponding position in the multi-species sequence alignment (containing gaps) from the OrthoMaM database (see section~\ref{subsec:s-phylogeny-method}) for the corresponding gene by doing a global pairwise alignment (Biopython function pairwise2).
-    This conversion from genomic position to alignment position was only possible when the assembly used for SNP-calling was the same as the one used in the OrthoMaM alignment, the GTF annotations, and the FASTA sequences.
-    SNPs were polarized using the three closest outgroups found in the OrthoMaM alignment with est-usfs v2.04~\cite{keightley_inferring_2018}, and alleles with a probability of being derived lower than 0.99 were discarded.
-
-    \subsection{Mutational opportunities}
-    \label{subsec:nunber-of-sites}
-    The mutational opportunities of any new mutation refer to its likelihood of falling into a specific category (synonymous, deleterious, nearly-neutral, or beneficial).
-    Deriving such opportunities is necessary to estimate the strength of selection exerted at the population scale since different categories might have different mutational opportunities, and thus polymorphism and divergence need to be corrected accordingly (see sections~\ref{subsec:substitution-mapping-in-the-terminal-branch},~\ref{subsec:s-polymorphism-method}, and~\ref{subsec:precisison_recall}).
-    To calculate mutational opportunities, we reconstructed the ancestral exome of each of the 28 populations by using the most likely ancestral state from est-usfs (see section \ref{subsec:polymorphism-dataset}), which differs from the corresponding species reference exome since it accounts for the variability present in the specific population.
-
-    From the reconstructed ancestral exome, all possible mutations were computed, weighted by the instantaneous rate of change between nucleotides obtained from the mutation rate matrix ($\UniDimArray{\mu}$, see section~\ref{subsec:s-phylogeny-method}), summing to $\mu_{\text{tot}}$ across the whole exome, and to $\mu_{\text{syn}}$ when restricted to synonymous mutations.
-    Finally, the mutational opportunities for synonymous mutations were computed as the total number of sites across the exome ($L_{\text{tot}}$) weighted by the proportion of synonymous mutations among all possible mutations as:
-
-    \begin{equation}
-        L_{\text{syn}} = L_{\text{tot}} \frac{\mu_{\text{syn}}}{\mu_{\text{tot}}}.
-    \end{equation}
-
-    Similarly, for non-synonymous mutations, the total mutation rate for each class of selection $\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$, called $\mu\left( \Sphyclass \right)$, was estimated as the sum across all non-synonymous mutations if their selection coefficient at the phylogenetic scale is in the class $\Sphy \in \Sphyclass$.
-    Accordingly, the mutational opportunities ($L \left( \Sphyclass \right)$) for each class of selection coefficient ($\Sphyclass$) was finally computed as the total number of sites across the exome ($L_{\text{tot}}$) weighted by the ratio of the aggregated mutations rates falling in the class $\mu\left( \Sphyclass \right)$:
-    \begin{equation}
-        L \left( \Sphyclass \right) = L_{\text{tot}} \frac{\mu\left( \Sphyclass \right)}{\mu_{\text{tot}}}.\label{eq:mutation-opp}
-    \end{equation}
-
-    Finally, $\proba [ \Sphyclass ]$ is the probability for a non-synonymous mutation to be in the class $\Sphyclass$, thus computed as:
-    \begin{equation}
-        \proba[\Sphyclass] = \frac{L\left( \Sphyclass \right)}{\sum_{\SphyclassAlt\in \{\SphyDel, \SphyNeu, \SphyBen \} } L\left(\SphyclassAlt \right)}.\label{eq:proba-dfe-mutsel}
-    \end{equation}
-
-    \subsection{Substitution mapping and $\dnds$ in the terminal branch}
-    \label{subsec:substitution-mapping-in-the-terminal-branch}
-    We inferred the protein-coding DNA sequences for each node of the 4-taxa tree containing the focal species and the three closest outgroups species found in the OrthoMaM alignment by applying the M5 codon model (gamma site rate variation) as implemented in FastML.v3.11~\cite{ashkenazy_fastml_2012}.
-    Consequently, for each focal species we reconstructed the protein coding DNA sequence of the whole exome at the base of the terminal branch before the split from the sister species.
-    We considered \textit{Ceratotherium simum simum} as \textit{Equus caballus'} sister species; \textit{Bison bison bison} as \textit{Bos taurus'} sister species; \textit{Pantholops hodgsonii} as \textit{Ovis aries'} sister species; \textit{Pantholops hodgsonii} as \textit{Capra hircus'} sister species; \textit{Macaca mulatta} as \textit{Chlorocebus sabaeus'} sister species and finally, we considered \textit{Pan troglodytes} as \textit{Homo sapiens'} sister species.
-    From this reconstructed exome, we determined the direction of the substitution occurring along the terminal branch of the phylogenetic tree toward each extant population.
-    SNPs segregating in the population were discarded, and the most likely ancestral state from est-usfs (see section \ref{subsec:polymorphism-dataset}) was used as the reference for each extant population.
-    For each substitution, we recovered its $\Sphy$ value as calculated through the phylogeny-based method (see section~\ref{subsec:s-phylogeny-method}).
-    Finally, the rate of non-synonymous over synonymous substitutions for a given class of selection coefficient ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$) was computed as:
-    \begin{align}
-        \begin{dcases}
-            \dn \left( \Sphyclass \right) &= \dfrac{D\left( \Sphyclass \right)}{L \left( \Sphyclass \right)}, \\
-            \ds &= \dfrac{D_{\text{syn}}}{L_{\text{syn}}},
-        \end{dcases}\label{eq:dnds}
-    \end{align}
-    where $D \left( \Sphyclass \right) $ was the number of non-synonymous substitutions in class $\Sphyclass$, $D_{\text{syn}}$ was the number of synonymous substitutions across the exome, while $L \left( \Sphyclass \right)$ and $L_{\text{syn}}$ were the numbers of non-synonymous and synonymous mutational opportunities, respectively, as defined in section~\ref{subsec:nunber-of-sites}.
-    $\delta(\dnds)$ was computed as the difference between $\dnds$ computed over all substitutions and $\dnds$ when we removed beneficial non-adaptive mutations $\dn (\Sphy < 1) / \ds$, normalized by $\dnds$.
-    Note that the quantities $\delta(\dnds)$ and $\delta(\dn)$ are equivalent due to the simplification of the factor $\ds$:
-    \begin{equation}
-        \delta(\dnds) = \dfrac{\dnds - \dn(\Sphy < 1) / \ds}{\dnds} = \dfrac{\dn - \dn(\Sphy < 1)}{\dn} = \delta(\dn).\label{eq:delta-dnds}
-    \end{equation}
-
-    \subsection{Scaled selection coefficients ($\Spop$) in a population-based method}
-    \label{subsec:s-polymorphism-method}
-
-    To obtain a quantitative estimate of the distribution of selection coefficients for each category of SNPs, we used the \textit{polyDFE} model~\cite{tataru_inference_2017, tataru_polydfe_2020}.
-    This model uses the count of derived alleles to infer the distribution of fitness effects (DFE).
-    The probability of sampling an allele at a given frequency (before fixation or extinction) is informative of its scaled selection coefficient at the population scale ($\Spop$).
-    Therefore, pooled across many sites, the site-frequency spectrum (SFS) provides information on the underlying $\Spop$ of mutations.
-    However, estimating a single $\Spop$ for all sampled mutations is biologically unrealistic, and a DFE of mutations is usually assumed~\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009}.
-    The \textit{polyDFE}\cite{tataru_inference_2017, tataru_polydfe_2020} software implements a mixture of a $\Gamma$ and exponential distributions to model the DFE of non-synonymous mutations, while synonymous mutations are considered neutral.
-    The model estimates the parameters $\DelMean$, $b$, $p_b$ and $\AdvMean$ for non-synonymous mutations as:
-
-    \begin{equation}
-        \label{eq:parametric-dfe}
-        \phi \left( \Spop; \DelMean , b, p_b, \AdvMean \right) =
-        \begin{dcases}
-            \left( 1 - p_b \right) f_{\Gamma}(-\Spop; -\DelMean, b) & \text{ if $\Spop \leq 0$,} \\
-            p_b f_{e}(\Spop; \AdvMean) & \text{ if $\Spop > 0$,} \\
-        \end{dcases}
-    \end{equation}
-
-    where $\DelMean \leq -1 $ is the estimated mean of the DFE for $\Spop \leq 0$;
-    $b \geq 0.2$ is the estimated shape of the $\Gamma$ distribution;
-    $0 \leq p_b \leq 1$ is the estimated probability that $\Spop > 0$;
-    $\AdvMean \geq 1$ is the estimated mean of the DFE for $\Spop > 0$;
-    and $f_{\Gamma}(\Spop; m, b)$ is the density of the $\Gamma$ distribution with mean $m$ and shape $b$, while $f_{e}(\Spop; m)$ is the density of the exponential distribution with mean $m$.
-
-    \textit{PolyDFE} requires one SFS for non-synonymous mutations and one for synonymous mutations (neutral expectation), as well as the number of sites on which each SFS was sampled.
-    For populations containing more than $8$ individuals, the SFS was subsampled down to $16$ chromosomes ($8$ diploid individuals) without replacement (hyper-geometric distribution) to alleviate the effect of different sampling depths in the 28 populations.
-    Altogether, for each class of selection ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$) of non-synonymous SNPs, we aggregated all the SNPs in the selection class $\Sphyclass$ as an SFS.
-    The number of sites on which each SFS was sampled is given by $L(\Sphyclass)$ for the non-synonymous SFS and $L_{\text{syn}}$ for the synonymous SFS respectively.
-    For each class of selection $\Sphyclass$, once fitted to the data using maximum likelihood with \textit{polyDFE}, the parameters of the DFE $\left( \DelMean , b, p_b, \AdvMean \right)$ were used to compute $\proba [ \SpopDel \given  \Sphyclass] $, $\proba [ \SpopNeu \given \Sphyclass]$, and $\proba [ \SpopBen \given \Sphyclass]$ as:
-
-    \begin{align}
-        \proba [ \SpopDel \given  \Sphyclass] &= \proba [ \Spop < -1 \given \Sphyclass ] = \left( 1 - p_b \right) \int_{-\infty}^{-1} f_{\Gamma}(-\Spop; -\DelMean, b) \der \Spop, \label{eq:polyProbaDel} \\
-        \proba [ \SpopNeu \given \Sphyclass] &= \proba [ -1 < \Spop < 1 \given \Sphyclass ] = \left( 1 - p_b \right) \int_{-1}^{0} f_{\Gamma}(-\Spop; -\DelMean, b) \der \Spop + p_b \int_{0}^{1} f_{e}(\Spop; \AdvMean) \der \Spop, \\
-        \proba [ \SpopBen \given \Sphyclass] &= \proba [ \Spop > 1 \given \Sphyclass] = p_b \int_{1}^{+\infty} f_{e}(\Spop; \AdvMean) \der \Spop. \label{eq:polyProbaAdv}
-    \end{align}
-
-    Rather than relying solely on currently segregating mutations to quantify selection, \textit{polyDFE} can leverage both divergence and polymorphism to estimate the parameters of the DFE.
-    We can thus add four more inputs to \textit{polyDFE}: $D \left( \Sphyclass \right) $, $L \left( \Sphyclass \right)$, $D_{\text{syn}}$ and $L_{\text{syn}}$ such as defined in the previous section.
-    Because the estimates of DFE are different with this method, we naturally obtained different values of $\proba [ \SpopDel \given  \Sphyclass] $, $\proba [ \SpopNeu \given \Sphyclass]$, and $\proba [ \SpopBen \given \Sphyclass]$.
-
-    \subsection{\textit{Precision} and \textit{recall}}
-    \label{subsec:precisison_recall}
-    For readability, we give here \textit{precision} and \textit{recall} for beneficial mutations ($\SphyBen$ and $\SpopBen$), but it can be obtained using the same derivation for the deleterious mutations ($\SphyDel$ and $\SpopDel$) and nearly-neutral mutations ($\SphyNeu$ and $\SpopNeu$).
-
-    \textit{Precision} is the proportion of mutations correctly predicted as beneficial ($\proba [ \SpopBen \cap  \SphyBen]$) out of all predicted as beneficial non-adaptive mutations ($\proba [ \SphyBen]$), which can be written as a conditional probability:
-
-    \begin{equation}
-        \frac{\proba [ \SpopBen  \cap  \SphyBen]}{\proba [ \SphyBen]} = \proba [ \SpopBen \given \SphyBen].
-        \label{eq:precision}
-    \end{equation}
-    Namely, \textit{precision} corresponds to the probability for a $\SphyBen$ mutation to be effectively beneficial at the population level ($\SpopBen$).
-    This probability, computed from eq.~\ref{eq:polyProbaAdv}, is obtained by restricting our analysis to SNPs that are predicted to be beneficial non-adaptive mutations (yellow fill for the category $\SphyBen$ in fig.~\ref{fig:homo-afr-results}D).
-
-    \textit{Recall} is the proportion of mutations correctly predicted as beneficial ($\proba [ \SpopBen \cap  \SphyBen]$) out of all beneficial mutations ($\proba [ \SpopBen]$), which can be written as a conditional probability:
-    \begin{equation}
-        \frac{\proba [ \SpopBen \cap  \SphyBen]}{\proba [ \SpopBen]} = \proba [ \SphyBen  \given \SpopBen ].
-    \end{equation}
-    Namely, \textit{recall} corresponds to the probability for a beneficial mutation at the population level ($\SpopBen$) to be a beneficial non-adaptive mutation ($\SphyBen$).
-    Using Bayes theorem, \textit{recall} can be re-written as:
-    \begin{equation}
-        \proba [\SphyBen \given \SpopBen] = \frac{\proba [\SpopBen \given \SphyBen] \times \proba[\SphyBen]}{\ProbaPopBen},
-        \label{eq:bayes}
-    \end{equation}
-
-    where $\proba [\SpopBen \given \SphyBen]$ and $\proba [ \SphyBen ]$ can be calculated using equations~\ref{eq:precision} and~\ref{eq:proba-dfe-mutsel}, respectively, and $\proba [ \SpopBen ]$ is the probability of a mutation to be beneficial at the level of the population, which can be computed from the law of total probabilities as:
-
-    \begin{equation}
-        \proba [ \SpopBen ] = \sum_{\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \} }\proba [\SpopBen \given \Sphyclass ] \times \proba [\Sphyclass ].
-        \label{eq:total_proba}
-    \end{equation}
-
-    \subsection{Correlation with effective population size ($\Ne$)}
-    \label{subsec:correlation-diversity}
-    Genetic diversity estimator Watterson's $\thetaSyn$ was obtained for each population from the synonymous SFS as in Achaz~\cite{achaz_frequency_2009}.
-    For each popuation, $\Ne$ was estimated from the equation $\Ne=\thetaSyn / (4 \times u)$, where $u$ is the mutation rate per generation.
-    Estimates for $u$ were averaged per species across the pedigree-based estimation in~\cite{bergeron_evolution_2023} for \textit{Homo}, \textit{Bos}, \textit{Capra} and \textit{Chlorocebus}.
-    For \textit{Ovis} we used the estimated $u$ of \textit{Capra}.
-    For \textit{Equus}, we used $u$ as estimated in Orlando \textit{et al.}~\cite{orlando_recalibrating_2013} ($u=7.24\times10^{-9}$).
-    Because a correlation must account for phylogenetic relationship and non-independence of samples, we fitted a Phylogenetic Generalized Linear Model in \textit{R} with the method \texttt{pgls} with default settings from the package \texttt{caper}~\cite{orme_caper_2013}.
-    The mammalian dated tree was obtained from TimeTree~\cite{kumar_timetree_2017} and pruned to include only the species analysed in this study, with multi-furcation of the different populations from each species placed at the same divergence time as the species (section S4.1).
-
-    \section*{Data availability}
-    The data underlying this article are available at \url{https://doi.org/10.5281/zenodo.7878953}.
-    Snakemake pipeline, analysis scripts and documentation are available at \href{https://github.com/ThibaultLatrille/SelCoeff}{github.com/ThibaultLatrille/SelCoeff}.
-
-    \section*{Acknowledgements}
-    \label{sec:acknowledgment}
-    We gratefully acknowledge the help of Mélodie Bastian, Nicolas Lartillot, Carina Farah Mugal, Laurent Duret, Alexandre Reymond, Daniele Silvestro and Nicolas Gambardella for their advice and reviews concerning this manuscript.
-    This work was performed using the computing facilities of the CC LBBE/PRABI\@.
-    This study makes use of data generated by the NextGen Consortium.
-    Funding:
-    Université de Lausanne; Agence Nationale de la Recherche, Grant ANR-19-CE12-0019 / HotRec.
-    The European Union’s Seventh Framework Programme (FP7/2010-2014) provided funding for the project under grant agreement no 244356 - “NextGen”.
-
-    \section*{Competing interests}
-    The authors declare no conflicts of interest.
-
-    \section*{Author information}
-    Original idea: T.L.\ and J.J.;
-    Model conception: T.L., J.J.\ and N.S.;
-    Code: T.L.;
-    Data analyses: T.L.\ and J.J.;
-    Interpretation: T.L., J.J., D.A.H.\ and N.S.;
-    First draft: T.L.\ and J.J.;
-    Editing and revisions: T.L., J.J., D.A.H.\ and N.S.
-    Project management and funding: N.S\@.
-
-    \begin{thebibliography}{10}
-
-        \bibitem{darwin_origin_1859}
-        Darwin C.
-        \newblock On the {{Origin}} of {{Species}} by {{Means}} of {{Natural
-        Selection}}, or the {{Preservation}} of {{Favoured Races}} in the
-            {{Struggle}} for {{Life}}. vol. 220.
-        \newblock John Murray; 1859.
-
-        \bibitem{merrell_adaptive_1994}
-        Merrell DJ.
-        \newblock The {{Adaptive Seascape}}: {{The Mechanism}} of {{Evolution}}.
-        \newblock U of Minnesota Press; 1994.
-
-        \bibitem{gavrilets_adaptive_2009}
-        Gavrilets S, Losos JB.
-        \newblock Adaptive {{Radiation}}: {{Contrasting Theory}} with {{Data}}.
-        \newblock Science. 2009;323(5915):732--737.
-        \newblock doi:{10.1126/science.1157966}.
-
-        \bibitem{enard_viruses_2016}
-        Enard D, Cai L, Gwennap C, Petrov DA.
-        \newblock Viruses Are a Dominant Driver of Protein Adaptation in Mammals.
-        \newblock eLife. 2016;5:e12469.
-        \newblock doi:{10.7554/eLife.12469}.
-
-        \bibitem{mcdonald_adaptative_1991}
-        McDonald JH, Kreitman M.
-        \newblock Adaptative Protein Evolution at {{Adh}} Locus in {{Drosophila}}.
-        \newblock Nature. 1991;351(6328):652--654.
-        \newblock doi:{10.1038/351652a0}.
-
-        \bibitem{smith_adaptive_2002}
-        Smith NGC, {Eyre-Walker} A.
-        \newblock Adaptive Protein Evolution in {{Drosophila}}.
-        \newblock Nature. 2002;415(6875):1022--1024.
-        \newblock doi:{10.1038/4151022a}.
-
-        \bibitem{welch_estimating_2006}
-        Welch JJ.
-        \newblock Estimating the {{Genomewide Rate}} of {{Adaptive Protein Evolution}}
-        in {{Drosophila}}.
-        \newblock Genetics. 2006;173(2):821--837.
-        \newblock doi:{10.1534/genetics.106.056911}.
-
-        \bibitem{yang_statistical_2000}
-        Yang Z, Bielawski JR.
-        \newblock Statistical Methods for Detecting Molecular Adaptation.
-        \newblock Trends in Ecology and Evolution. 2000;15(12):496--503.
-        \newblock doi:{10.1016/S0169-5347(00)01994-7}.
-
-        \bibitem{eyre-walker_genomic_2006}
-        {Eyre-Walker} A.
-        \newblock The Genomic Rate of Adaptive Evolution.
-        \newblock Trends in Ecology \& Evolution. 2006;21(10):569--575.
-        \newblock doi:{10.1016/j.tree.2006.06.015}.
-
-        \bibitem{moutinho_variation_2019}
-        Moutinho AF, Bataillon T, Dutheil JY.
-        \newblock Variation of the Adaptive Substitution Rate between Species and
-        within Genomes.
-        \newblock Evolutionary Ecology. 2019;34(3):315--338.
-        \newblock doi:{10.1007/s10682-019-10026-z}.
-
-        \bibitem{lynch_mutation_2023}
-        Lynch M.
-        \newblock Mutation Pressure, Drift, and the Pace of Molecular Coevolution.
-        \newblock Proceedings of the National Academy of Sciences.
-        2023;120(27):e2306741120.
-        \newblock doi:{10.1073/pnas.2306741120}.
-
-        \bibitem{charlesworth_other_2007}
-        Charlesworth J, {Eyre-Walker} A.
-        \newblock The Other Side of the Nearly Neutral Theory, Evidence of Slightly
-        Advantageous Back-Mutations.
-        \newblock Proceedings of the National Academy of Sciences.
-        2007;104(43):16992--16997.
-        \newblock doi:{10.1073/pnas.0705456104}.
-
-        \bibitem{mustonen_fitness_2009}
-        Mustonen V, L{\"a}ssig M.
-        \newblock From Fitness Landscapes to Seascapes: Non-Equilibrium Dynamics of
-        Selection and Adaptation.
-        \newblock Trends in genetics. 2009;25(3):111--119.
-        \newblock doi:{10.1016/j.tig.2009.01.002}.
-
-        \bibitem{jones_shifting_2017}
-        Jones CT, Youssef N, Susko E, Bielawski JP.
-        \newblock Shifting Balance on a Static Mutation--Selection Landscape: A Novel
-        Scenario of Positive Selection.
-        \newblock Molecular Biology and Evolution. 2017;34(2):391--407.
-        \newblock doi:{10.1093/molbev/msw237}.
-
-        \bibitem{ohta_nearly_1992}
-        Ohta T.
-        \newblock The Nearly Neutral Theory of Molecular Evolution.
-        \newblock Annual Review of Ecology and Systematics. 1992;23(1992):263--286.
-
-        \bibitem{gillespie_ohta_1995}
-        Gillespie JH.
-        \newblock On {{Ohta}}'s Hypothesis: {{Most}} Amino Acid Substitutions Are
-        Deleterious.
-        \newblock Journal of Molecular Evolution. 1995;40(1):64--69.
-        \newblock doi:{10.1007/BF00166596}.
-
-        \bibitem{hartl_compensatory_1996}
-        Hartl DL, Taubes CH.
-        \newblock Compensatory Nearly Neutral Mutations: {{Selection}} without
-        Adaptation.
-        \newblock Journal of Theoretical Biology. 1996;182(3):303--309.
-        \newblock doi:{10.1006/jtbi.1996.0168}.
-
-        \bibitem{sella_application_2005}
-        Sella G, Hirsh AE.
-        \newblock The Application of Statistical Physics to Evolutionary Biology.
-        \newblock Proceedings of the National Academy of Sciences of the United States
-        of America. 2005;102(27):9541--9546.
-        \newblock doi:{10.1073/pnas.0501865102}.
-
-        \bibitem{cvijovic_fate_2015}
-        Cvijovi{\'c} I, Good BH, Jerison ER, Desai MM.
-        \newblock Fate of a Mutation in a Fluctuating Environment.
-        \newblock Proceedings of the National Academy of Sciences.
-        2015;112(36):E5021--E5028.
-        \newblock doi:{10.1073/pnas.1505406112}.
-
-        \bibitem{piganeau_estimating_2003}
-        Piganeau G, {Eyre-Walker} A.
-        \newblock Estimating the Distribution of Fitness Effects from {{DNA}} Sequence
-        Data: {{Implications}} for the Molecular Clock.
-        \newblock Proceedings of the National Academy of Sciences of the United States
-        of America. 2003;100(18):10335--10340.
-        \newblock doi:{10.1073/pnas.1833064100}.
-
-        \bibitem{chi_detecting_2020}
-        Chi PB, Kosater WM, Liberles DA.
-        \newblock Detecting {{Signatures}} of {{Positive Selection}} against a
-            {{Backdrop}} of {{Compensatory Processes}}.
-        \newblock Molecular Biology and Evolution. 2020;37(11):3353--3362.
-        \newblock doi:{10.1093/molbev/msaa161}.
-
-        \bibitem{bazykin_changing_2015}
-        Bazykin GA.
-        \newblock Changing Preferences: Deformation of Single Position Amino Acid
-        Fitness Landscapes and Evolution of Proteins.
-        \newblock Biology letters. 2015;11(10):20150315.
-        \newblock doi:{10.1098/rsbl.2015.0315}.
-
-        \bibitem{moses_inferring_2009}
-        Moses AM, Durbin R.
-        \newblock Inferring {{Selection}} on {{Amino Acid Preference}} in {{Protein
-        Domains}}.
-        \newblock Molecular Biology and Evolution. 2009;26(3):527--536.
-        \newblock doi:{10.1093/molbev/msn286}.
-
-        \bibitem{fischer_germline_2011}
-        Fischer A, Greenman C, Mustonen V.
-        \newblock Germline {{Fitness-Based Scoring}} of {{Cancer Mutations}}.
-        \newblock Genetics. 2011;188(2):383--393.
-        \newblock doi:{10.1534/genetics.111.127480}.
-
-        \bibitem{chen_hunting_2021}
-        Chen J, Bataillon T, Gl{\'e}min S, Lascoux M.
-        \newblock Hunting for Beneficial Mutations: Conditioning on {{SIFT}} Scores
-        When Estimating the Distribution of Fitness Effect of New Mutations.
-        \newblock Genome Biology and Evolution. 2021;doi:{10.1093/gbe/evab151}.
-
-        \bibitem{halpern_evolutionary_1998}
-        Halpern AL, Bruno WJ.
-        \newblock Evolutionary Distances for Protein-Coding Sequences: Modeling
-        Site-Specific Residue Frequencies.
-        \newblock Molecular Biology and Evolution. 1998;15(7):910--917.
-        \newblock doi:{10.1093/oxfordjournals.molbev.a025995}.
-
-        \bibitem{mccandlish_modeling_2014}
-        McCandlish DM, Stoltzfus A.
-        \newblock Modeling Evolution Using the Probability of Fixation: {{History}} and
-        Implications.
-        \newblock Quarterly Review of Biology. 2014;89(3):225--252.
-        \newblock doi:{10.1086/677571}.
-
-        \bibitem{rodrigue_mechanistic_2010}
-        Rodrigue N, Philippe H.
-        \newblock Mechanistic Revisions of Phenomenological Modeling Strategies in
-        Molecular Evolution.
-        \newblock Trends in Genetics. 2010;26(6):248--252.
-        \newblock doi:{10.1016/j.tig.2010.04.001}.
-
-        \bibitem{tamuri_estimating_2012}
-        Tamuri AU, Goldstein RA.
-        \newblock Estimating the Distribution of Selection Coefficients from
-        Phylogenetic Data Using Sitewise Mutation-Selection Models.
-        \newblock Genetics. 2012;190(3):1101--1115.
-        \newblock doi:{10.1534/genetics.111.136432}.
-
-        \bibitem{rodrigue_detecting_2017}
-        Rodrigue N, Lartillot N.
-        \newblock Detecting Adaptation in Protein-Coding Genes Using a {{Bayesian}}
-        Site- Heterogeneous Mutation-Selection Codon Substitution Model.
-        \newblock Molecular Biology and Evolution. 2017;34(1):204--214.
-        \newblock doi:{10.1093/molbev/msw220}.
-
-        \bibitem{foley_genomic_2023}
-        Foley NM, Mason VC, Harris AJ, Bredemeyer KR, Damas J, Lewin HA, et~al.
-        \newblock A Genomic Timescale for Placental Mammal Evolution.
-        \newblock Science. 2023;380(6643):eabl8189.
-        \newblock doi:{10.1126/science.abl8189}.
-
-        \bibitem{howe_ensembl_2021}
-        Howe KL, Achuthan P, Allen J, Allen J, {Alvarez-Jarreta} J, Amode MR, et~al.
-        \newblock Ensembl 2021.
-        \newblock Nucleic Acids Research. 2021;49(D1):D884--D891.
-        \newblock doi:{10.1093/nar/gkaa942}.
-
-        \bibitem{ranwez_orthomam_2007}
-        Ranwez V, Delsuc F, Ranwez S, Belkhir K, Tilak MK, Douzery EJ.
-        \newblock {{OrthoMaM}}: {{A}} Database of Orthologous Genomic Markers for
-        Placental Mammal Phylogenetics.
-        \newblock BMC Evolutionary Biology. 2007;7(1):1--12.
-        \newblock doi:{10.1186/1471-2148-7-241}.
-
-        \bibitem{scornavacca_orthomam_2019}
-        Scornavacca C, Belkhir K, Lopez J, Dernat R, Delsuc F, Douzery EJP, et~al.
-        \newblock {{OrthoMaM}} V10: {{Scaling-up}} Orthologous Coding Sequence and Exon
-        Alignments with More than One Hundred Mammalian Genomes.
-        \newblock Molecular Biology and Evolution. 2019;36(4):861--862.
-        \newblock doi:{10.1093/molbev/msz015}.
-
-        \bibitem{rodrigue_mutationselection_2010}
-        Rodrigue N, Philippe H, Lartillot N.
-        \newblock Mutation-Selection Models of Coding Sequence Evolution with
-        Site-Heterogeneous Amino Acid Fitness Profiles.
-        \newblock Proceedings of the National Academy of Sciences of the United States
-        of America. 2010;107(10):4629--34.
-        \newblock doi:{10.1073/pnas.0910915107}.
-
-        \bibitem{landrum_clinvar_2018}
-        Landrum MJ, Lee JM, Benson M, Brown GR, Chao C, Chitipiralla S, et~al.
-        \newblock {{ClinVar}}: Improving Access to Variant Interpretations and
-        Supporting Evidence.
-        \newblock Nucleic Acids Research. 2018;46(D1):D1062--D1067.
-        \newblock doi:{10.1093/nar/gkx1153}.
-
-        \bibitem{grimm_evaluation_2015}
-        Grimm DG, Azencott CA, Aicheler F, Gieraths U, MacArthur DG, Samocha KE, et~al.
-        \newblock The {{Evaluation}} of {{Tools Used}} to {{Predict}} the {{Impact}} of
-            {{Missense Variants Is Hindered}} by {{Two Types}} of {{Circularity}}.
-        \newblock Human Mutation. 2015;36(5):513--523.
-        \newblock doi:{10.1002/humu.22768}.
-
-        \bibitem{sullivan_leveraging_2023}
-        Sullivan PF, Meadows JRS, Gazal S, Phan BN, Li X, Genereux DP, et~al.
-        \newblock Leveraging Base-Pair Mammalian Constraint to Understand Genetic
-        Variation and Human Disease.
-        \newblock Science. 2023;380(6643):eabn2937.
-        \newblock doi:{10.1126/science.abn2937}.
-
-        \bibitem{eyre-walker_distribution_2006}
-        {Eyre-Walker} A, Woolfit M, Phelps T.
-        \newblock The Distribution of Fitness Effects of New Deleterious Amino Acid
-        Mutations in Humans.
-        \newblock Genetics. 2006;173(2):891--900.
-        \newblock doi:{10.1534/genetics.106.057570}.
-
-        \bibitem{eyre-walker_estimating_2009}
-        {Eyre-Walker} A, Keightley PD.
-        \newblock Estimating the {{Rate}} of {{Adaptive Molecular Evolution}} in the
-            {{Presence}} of {{Slightly Deleterious Mutations}} and {{Population Size
-        Change}}.
-        \newblock Molecular Biology and Evolution. 2009;26(9):2097--2108.
-        \newblock doi:{10.1093/molbev/msp119}.
-
-        \bibitem{galtier_adaptive_2016}
-        Galtier N.
-        \newblock Adaptive Protein Evolution in Animals and the Effective Population
-        Size Hypothesis.
-        \newblock PLoS Genetics. 2016;12(1):e1005774.
-        \newblock doi:{10.1371/journal.pgen.1005774}.
-
-        \bibitem{tataru_inference_2017}
-        Tataru P, Mollion M, Gl{\'e}min S, Bataillon T.
-        \newblock Inference of Distribution of Fitness Effects and Proportion of
-        Adaptive Substitutions from Polymorphism Data.
-        \newblock Genetics. 2017;207(3):1103--1119.
-        \newblock doi:{10.1534/genetics.117.300323}.
-
-        \bibitem{bergeron_evolution_2023}
-        Bergeron LA, Besenbacher S, Zheng J, Li P, Bertelsen MF, Quintard B, et~al.
-        \newblock Evolution of the Germline Mutation Rate across Vertebrates.
-        \newblock Nature. 2023; p. 1--7.
-        \newblock doi:{10.1038/s41586-023-05752-y}.
-
-        \bibitem{orlando_recalibrating_2013}
-        Orlando L, Ginolhac A, Zhang G, Froese D, Albrechtsen A, Stiller M, et~al.
-        \newblock Recalibrating {{Equus}} Evolution Using the Genome Sequence of an
-        Early {{Middle Pleistocene}} Horse.
-        \newblock Nature. 2013;499(7456):74--78.
-        \newblock doi:{10.1038/nature12323}.
-
-        \bibitem{achaz_frequency_2009}
-        Achaz G.
-        \newblock Frequency {{Spectrum Neutrality Tests}}: {{One}} for {{All}} and
-            {{All}} for {{One}}.
-        \newblock Genetics. 2009;183(1):249--258.
-        \newblock doi:{10.1534/genetics.109.104042}.
-
-        \bibitem{latrille_genes_2023}
-        Latrille T, Rodrigue N, Lartillot N.
-        \newblock Genes and Sites under Adaptation at the Phylogenetic Scale Also
-        Exhibit Adaptation at the Population-Genetic Scale.
-        \newblock Proceedings of the National Academy of Sciences of the United States
-        of America. 2023;120(11):e2214977120.
-        \newblock doi:{10.1073/pnas.2214977120}.
-
-        \bibitem{ng_sift_2003}
-        Ng PC, Henikoff S.
-        \newblock {{SIFT}}: Predicting Amino Acid Changes That Affect Protein Function.
-        \newblock Nucleic Acids Research. 2003;31(13):3812--3814.
-        \newblock doi:{10.1093/nar/gkg509}.
-
-        \bibitem{vaser_sift_2016}
-        Vaser R, Adusumalli S, Leng SN, Sikic M, Ng PC.
-        \newblock {{SIFT}} Missense Predictions for Genomes.
-        \newblock Nature Protocols. 2016;11(1):1--9.
-        \newblock doi:{10.1038/nprot.2015.123}.
-
-        \bibitem{keightley_what_2010}
-        Keightley PD, {Eyre-Walker} A.
-        \newblock What Can We Learn about the Distribution of Fitness Effects of New
-        Mutations from {{DNA}} Sequence Data?
-        \newblock Philosophical Transactions of the Royal Society B: Biological
-        Sciences. 2010;365(1544):1187--1193.
-        \newblock doi:{10.1098/rstb.2009.0266}.
-
-        \bibitem{rice_evolutionarily_2015}
-        Rice DP, Good BH, Desai MM.
-        \newblock The {{Evolutionarily Stable Distribution}} of {{Fitness Effects}}.
-        \newblock Genetics. 2015;200(1):321--329.
-        \newblock doi:{10.1534/genetics.114.173815}.
-
-        \bibitem{mustonen_fitness_2010}
-        Mustonen V, L{\"a}ssig M.
-        \newblock Fitness Flux and Ubiquity of Adaptive Evolution.
-        \newblock Proceedings of the National Academy of Sciences.
-        2010;107(9):4248--4253.
-        \newblock doi:{10.1073/pnas.0907953107}.
-
-        \bibitem{eyre-walker_how_2014}
-        {Eyre-Walker} A, {Eyre-Walker} YC.
-        \newblock How Much of the Variation in the Mutation Rate along the Human Genome
-        Can Be Explained?
-        \newblock G3: Genes, Genomes, Genetics. 2014;4(9):1667--1670.
-        \newblock doi:{10.1534/g3.114.012849}.
-
-        \bibitem{mustonen_molecular_2008}
-        Mustonen V, L{\"a}ssig M.
-        \newblock Molecular {{Evolution}} under {{Fitness Fluctuations}}.
-        \newblock Physical Review Letters. 2008;100(10):108101.
-        \newblock doi:{10.1103/PhysRevLett.100.108101}.
-
-        \bibitem{latrille_inferring_2021}
-        Latrille T, Lanore V, Lartillot N.
-        \newblock Inferring Long-Term Effective Population Size with
-        Mutation--Selection Models.
-        \newblock Molecular Biology and Evolution. 2021;38(10):4573--4587.
-        \newblock doi:{10.1093/molbev/msab160}.
-
-        \bibitem{huber_determining_2017}
-        Huber CD, Kim BY, Marsden CD, Lohmueller KE.
-        \newblock Determining the Factors Driving Selective Effects of New
-        Nonsynonymous Mutations.
-        \newblock Proceedings of the National Academy of Sciences.
-        2017;114(17):4465--4470.
-        \newblock doi:{10.1073/pnas.1619508114}.
-
-        \bibitem{lanfear_population_2014}
-        Lanfear R, Kokko H, {Eyre-Walker} A.
-        \newblock Population Size and the Rate of Evolution.
-        \newblock Trends in Ecology and Evolution. 2014;29(1):33--41.
-        \newblock doi:{10.1016/j.tree.2013.09.009}.
-
-        \bibitem{platt_protein_2018}
-        Platt A, Weber CC, Liberles DA.
-        \newblock Protein Evolution Depends on Multiple Distinct Population Size
-        Parameters.
-        \newblock BMC Evolutionary Biology. 2018;18(1):1--9.
-        \newblock doi:{10.1186/s12862-017-1085-x}.
-
-        \bibitem{starr_epistasis_2016}
-        Starr TN, Thornton JW.
-        \newblock Epistasis in Protein Evolution.
-        \newblock Protein Science. 2016;25(7):1204--1218.
-        \newblock doi:{10.1002/pro.2897}.
-
-        \bibitem{morcos_directcoupling_2011}
-        Morcos F, Pagnani A, Lunt B, Bertolino A, Marks DS, Sander C, et~al.
-        \newblock Direct-Coupling Analysis of Residue Coevolution Captures Native
-        Contacts across Many Protein Families.
-        \newblock Proceedings of the National Academy of Sciences.
-        2011;108(49):E1293--E1301.
-        \newblock doi:{10.1073/pnas.1111471108}.
-
-        \bibitem{marks_protein_2012}
-        Marks DS, Hopf TA, Sander C.
-        \newblock Protein Structure Prediction from Sequence Variation.
-        \newblock Nature Biotechnology. 2012;30(11):1072--1080.
-        \newblock doi:{10.1038/nbt.2419}.
-
-        \bibitem{goldstein_nonadaptive_2015}
-        Goldstein RA, Pollard ST, Shah SD, Pollock DD.
-        \newblock Nonadaptive {{Amino Acid Convergence Rates Decrease}} over {{Time}}.
-        \newblock Molecular Biology and Evolution. 2015;32(6):1373--1381.
-        \newblock doi:{10.1093/molbev/msv041}.
-
-        \bibitem{goldstein_sequence_2017}
-        Goldstein RA, Pollock DD.
-        \newblock Sequence Entropy of Folding and the Absolute Rate of Amino Acid
-        Substitutions.
-        \newblock Nature Ecology \& Evolution. 2017;1(12):1923--1930.
-        \newblock doi:{10.1038/s41559-017-0338-9}.
-
-        \bibitem{park_epistatic_2022}
-        Park Y, Metzger BPH, Thornton JW.
-        \newblock Epistatic Drift Causes Gradual Decay of Predictability in Protein
-        Evolution.
-        \newblock Science. 2022;376(6595):823--830.
-        \newblock doi:{10.1126/science.abn6895}.
-
-        \bibitem{ashenberg_mutational_2013}
-        Ashenberg O, Gong LI, Bloom JD.
-        \newblock Mutational Effects on Stability Are Largely Conserved during Protein
-        Evolution.
-        \newblock Proceedings of the National Academy of Sciences of the United States
-        of America. 2013;110(52):21071--21076.
-        \newblock doi:{10.1073/pnas.1314781111}.
-
-        \bibitem{doud_sitespecific_2015}
-        Doud MB, Ashenberg O, Bloom JD.
-        \newblock Site-{{Specific Amino Acid Preferences Are Mostly Conserved}} in
-            {{Two Closely Related Protein Homologs}}.
-        \newblock Molecular Biology and Evolution. 2015;32(11):2944--2960.
-        \newblock doi:{10.1093/molbev/msv167}.
-
-        \bibitem{bloom_identification_2017}
-        Bloom JD.
-        \newblock Identification of Positive Selection in Genes Is Greatly Improved by
-        Using Experimentally Informed Site-Specific Models.
-        \newblock Biology Direct. 2017;12(1):1--24.
-        \newblock doi:{10.1186/s13062-016-0172-z}.
-
-        \bibitem{youssef_consequences_2020}
-        Youssef N, Susko E, Bielawski JP.
-        \newblock Consequences of Stability-Induced Epistasis for Substitution Rates.
-        \newblock Molecular Biology and Evolution. 2020;doi:{10.1093/molbev/msaa151}.
-
-        \bibitem{vigue_deciphering_2022}
-        Vigu{\'e} L, Croce G, Petitjean M, Rupp{\'e} E, Tenaillon O, Weigt M.
-        \newblock Deciphering Polymorphism in 61,157 {{Escherichia}} Coli Genomes via
-        Epistatic Sequence Landscapes.
-        \newblock Nature Communications. 2022;13(1):4030.
-        \newblock doi:{10.1038/s41467-022-31643-3}.
-
-        \bibitem{kimura_evolutionary_1968}
-        Kimura M.
-        \newblock Evolutionary Rate at the Molecular Level.
-        \newblock Nature. 1968;217(5129):624--626.
-
-        \bibitem{gillespie_substitution_1994}
-        Gillespie JH.
-        \newblock Substitution Processes in Molecular Evolution. {{III}}.
-            {{Deleterious}} Alleles.
-        \newblock Genetics. 1994;138(3):943--952.
-        \newblock doi:{10.1093/genetics/138.3.943}.
-
-        \bibitem{jensen_importance_2019}
-        Jensen JD, Payseur BA, Stephan W, Aquadro CF, Lynch M, Charlesworth D, et~al.
-        \newblock The Importance of the {{Neutral Theory}} in 1968 and 50 Years on:
-            {{A}} Response to {{Kern}} and {{Hahn}} 2018.
-        \newblock Evolution. 2019;73(1):111--114.
-        \newblock doi:{10.1111/evo.13650}.
-
-        \bibitem{galtier_half_2024}
-        Galtier N.
-        \newblock Half a {{Century}} of {{Controversy}}: {{The
-        Neutralist}}/{{Selectionist Debate}} in {{Molecular Evolution}}.
-        \newblock Genome Biology and Evolution. 2024;16(2):evae003.
-        \newblock doi:{10.1093/gbe/evae003}.
-
-        \bibitem{galtier_adaptation_2007}
-        Galtier N, Duret L.
-        \newblock Adaptation or Biased Gene Conversion? {{Extending}} the Null
-        Hypothesis of Molecular Evolution.
-        \newblock Trends in Genetics. 2007;23(6):273--277.
-        \newblock doi:{10.1016/j.tig.2007.03.011}.
-
-        \bibitem{rousselle_influence_2019}
-        Rousselle M, Laverr{\'e} A, Figuet E, Nabholz B, Galtier N.
-        \newblock Influence of {{Recombination}} and {{GC-biased Gene Conversion}} on
-        the {{Adaptive}} and {{Nonadaptive Substitution Rate}} in {{Mammals}} versus
-            {{Birds}}.
-        \newblock Molecular Biology and Evolution. 2019;36(3):458--471.
-        \newblock doi:{10.1093/molbev/msy243}.
-
-        \bibitem{joseph_increased_2024a}
-        Joseph J.
-        \newblock Increased {{Positive Selection}} in {{Highly Recombining Genes Does}}
-        Not {{Necessarily Reflect}} an {{Evolutionary Advantage}} of
-            {{Recombination}}.
-        \newblock Molecular Biology and Evolution. 2024; p. msae107.
-        \newblock doi:{10.1093/molbev/msae107}.
-
-        \bibitem{ohta_development_1996}
-        Ohta T, Gillespie JH.
-        \newblock Development of {{Neutral}} and {{Nearly Neutral Theories}}.
-        \newblock Theoretical Population Biology. 1996;49(2):128--142.
-        \newblock doi:{10.1006/tpbi.1996.0007}.
-
-        \bibitem{spielman_relationship_2015}
-        Spielman SJ, Wilke CO.
-        \newblock The Relationship between {{dN}}/{{dS}} and Scaled Selection
-        Coefficients.
-        \newblock Molecular biology and evolution. 2015;32(4):1097--1108.
-        \newblock doi:{10.1093/molbev/msv003}.
-
-        \bibitem{dosreis_how_2015}
-        Dos~Reis M.
-        \newblock How to Calculate the Non-Synonymous to Synonymous Rate Ratio of
-        Protein-Coding Genes under the Fisher-Wright Mutation-Selection Framework.
-        \newblock Biology Letters. 2015;11(4):20141031.
-        \newblock doi:{10.1098/rsbl.2014.1031}.
-
-        \bibitem{rodrigue_bayesian_2021}
-        Rodrigue N, Latrille T, Lartillot N.
-        \newblock A {{Bayesian}} Mutation-Selection Framework for Detecting
-        Site-Specific Adaptive Evolution in Protein-Coding Genes.
-        \newblock Molecular Biology and Evolution. 2021;38(3):1199--1208.
-        \newblock doi:{10.1093/molbev/msaa265}.
-
-        \bibitem{tamuri_mutationselection_2021}
-        Tamuri AU, {dos Reis} M.
-        \newblock A Mutation-Selection Model of Protein Evolution under Persistent
-        Positive Selection.
-        \newblock Molecular Biology and Evolution. 2021;doi:{10.1093/molbev/msab309}.
-
-        \bibitem{kazmi_detecting_2019}
-        Kazmi SO, Rodrigue N.
-        \newblock Detecting Amino Acid Preference Shifts with Codon-Level
-        Mutation-Selection Mixture Models.
-        \newblock BMC Evolutionary Biology. 2019;19(1):62.
-        \newblock doi:{10.1186/s12862-019-1358-7}.
-
-        \bibitem{stolyarova_senescence_2020}
-        Stolyarova AV, Nabieva E, Ptushenko VV, Favorov AV, Popova AV, Neverov AD,
-        et~al.
-        \newblock Senescence and Entrenchment in Evolution of Amino Acid Sites.
-        \newblock Nature Communications. 2020;11(1):4603.
-        \newblock doi:{10.1038/s41467-020-18366-z}.
-
-        \bibitem{douzery_orthomam_2014}
-        Douzery EJP, Scornavacca C, Romiguier J, Belkhir K, Galtier N, Delsuc F, et~al.
-        \newblock {{OrthoMaM}} v8: {{A}} Database of Orthologous Exons and Coding
-        Sequences for Comparative Genomics in Mammals.
-        \newblock Molecular Biology and Evolution. 2014;31(7):1923--1928.
-        \newblock doi:{10.1093/molbev/msu132}.
-
-        \bibitem{yang_mutationselection_2008}
-        Yang Z, Nielsen R.
-        \newblock Mutation-Selection Models of Codon Substitution and Their Use to
-        Estimate Selective Strengths on Codon Usage.
-        \newblock Molecular Biology and Evolution. 2008;25(3):568--579.
-        \newblock doi:{10.1093/molbev/msm284}.
-
-        \bibitem{wright_evolution_1931}
-        Wright S.
-        \newblock Evolution in {{Mendelian}} Populations.
-        \newblock Genetics. 1931;16(2):97--159.
-        \newblock doi:{10.1093/genetics/16.2.97}.
-
-        \bibitem{fisher_genetical_1930}
-        Fisher RA.
-        \newblock The {{Genetical Theory}} of {{Natural Selection}}.
-        \newblock The Clarendon Press; 1930.
-
-        \bibitem{rodrigue_bayesian_2008}
-        Rodrigue N, Lartillot N, Philippe H.
-        \newblock Bayesian Comparisons of Codon Substitution Models.
-        \newblock Genetics. 2008;180(3):1579--1591.
-        \newblock doi:{10.1534/genetics.108.092254}.
-
-        \bibitem{lartillot_bayesian_2004}
-        Lartillot N.
-        \newblock A Bayesian Mixture Model for Across-Site Heterogeneities in the
-        Amino-Acid Replacement Process.
-        \newblock Molecular biology and evolution. 2004;21(6):1095--1109.
-        \newblock doi:{10.1093/molbev/msh112}.
-
-        \bibitem{lartillot_inference_2013}
-        Lartillot N.
-        \newblock Inf{\'e}rence Probabiliste Pour La Phylog{\'e}nie, La G{\'e}nomique
-        Comparative et Les Sciences de La Macro-{\'E}volution; 2013.
-
-        \bibitem{alabri_whole_2020}
-        Al~Abri MA, Holl HM, Kalla SE, Sutter NB, Brooks SA.
-        \newblock Whole Genome Detection of Sequence and Structural Polymorphism in Six
-        Diverse Horses.
-        \newblock PLoS ONE. 2020;15(4):e0230899.
-        \newblock doi:{10.1371/journal.pone.0230899}.
-
-        \bibitem{sherry_dbsnp_2001}
-        Sherry ST, Ward MH, Kholodov M, Baker J, Phan L, Smigielski EM, et~al.
-        \newblock {{dbSNP}}: The {{NCBI}} Database of Genetic Variation.
-        \newblock Nucleic Acids Research. 2001;29(1):308--311.
-        \newblock doi:{10.1093/nar/29.1.308}.
-
-        \bibitem{svardal_ancient_2017}
-        Svardal H, Jasinska AJ, Apetrei C, Coppola G, Huang Y, Schmitt CA, et~al.
-        \newblock Ancient Hybridization and Strong Adaptation to Viruses across
-            {{African}} Vervet Monkey Populations.
-        \newblock Nature Genetics. 2017;49(12):1705--1713.
-        \newblock doi:{10.1038/ng.3980}.
-
-        \bibitem{zheng-bradley_alignment_2017}
-        {Zheng-Bradley} X, Streeter I, Fairley S, Richardson D, Clarke L, Flicek P,
-        et~al.
-        \newblock Alignment of 1000 {{Genomes Project}} Reads to Reference Assembly
-            {{GRCh38}}.
-        \newblock GigaScience. 2017;6(7):gix038.
-        \newblock doi:{10.1093/gigascience/gix038}.
-
-        \bibitem{keightley_inferring_2018}
-        Keightley PD, Jackson BC.
-        \newblock Inferring the Probability of the Derived vs the Ancestral Allelic
-        State at a Polymorphic Site.
-        \newblock Genetics. 2018;209(3):897--906.
-        \newblock doi:{10.1534/genetics.118.301120}.
-
-        \bibitem{ashkenazy_fastml_2012}
-        Ashkenazy H, Penn O, {Doron-Faigenboim} A, Cohen O, Cannarozzi G, Zomer O,
-        et~al.
-        \newblock {{FastML}}: A Web Server for Probabilistic Reconstruction of
-        Ancestral Sequences.
-        \newblock Nucleic Acids Research. 2012;40(W1):W580--W584.
-        \newblock doi:{10.1093/nar/gks498}.
-
-        \bibitem{tataru_polydfe_2020}
-        Tataru P, Bataillon T.
-        \newblock {{polyDFE}}: {{Inferring}} the Distribution of Fitness Effects and
-        Properties of Beneficial Mutations from Polymorphism Data.
-        \newblock In: Methods in {{Molecular Biology}}. vol. 2090. Humana Press Inc.;
-        2020. p. 125--146.
-
-        \bibitem{orme_caper_2013}
-        Orme D, Freckleton R, Thomas G, Petzoldt T, Fritz S, Isaac N, et~al.
-        \newblock The Caper Package: Comparative Analysis of Phylogenetics and
-        Evolution in {{R}}.
-        \newblock R package version. 2013;5(2):1--36.
-
-        \bibitem{kumar_timetree_2017}
-        Kumar S, Stecher G, Suleski M, Hedges SB.
-        \newblock {{TimeTree}}: A Resource for Timelines, Timetrees, and Divergence
-        Times.
-        \newblock Molecular Biology and Evolution. 2017;34(7):1812--1819.
-        \newblock doi:{10.1093/molbev/msx116}.
-
-    \end{thebibliography}
-
-    \newpage
-    \section*{Supplementary figures and tables}
-    \subsection*{List of Figures}
-    \begin{itemize}
-        \item S1: Bayesian hierarchical model (p.5).
-        \item S2: Examples sites of $\SphyBen$ mutations in \textit{Chlorocebus sabaeus} (reversions) (p.10).
-        \item S3: Examples sites of $\SphyBen$ mutations in \textit{Chlorocebus sabaeus} (p.11).
-        \item S4: Enrichment in $\SphyBen$ SNPs across all gene ontology terms (p.17).
-        \item S5: Estimation of selection at the population scale for $\SphyDel$ mutations (p.19).
-        \item S6: Estimation of selection at the population scale for $\SphyNeu$ mutations (p.19).
-        \item S7: Estimation of selection at the population scale for $\SphyBen$ mutations (p.19).
-        \item S8: Distribution of scaled selection coefficients ($\Sphy$) (p.20).
-        \item S9: Tree used for PGLM (Phylogenetic Generalized Linear Model) (p.21).
-        \item S10: Proportion of deleterious mutations ($\SpopDel$) (p.22).
-        \item S11: Proportion of nearly-neutral mutations ($\SpopNeu$) (p.23).
-        \item S12: Proportion of beneficial mutations ($\SpopBen$) (p.24).
-        \item S13: $\proba[\SphyBen\given \SpopBen ]$ as a function of distance to the sister species (p.26).
-        \item S14: Ratio of $\proba[\Sphy]$ over $\proba[-\Sphy]$ for polymorphisms of the African population of \textit{Homo sapiens} (p.27).
-        \item S15: Simulations of site-frequency spectra (p.29).
-        \item S16: Site-frequency spectrum in African population of \textit{Homo sapiens}, masking CpG transitions  (p.32).
-        \item S17: Site-frequency spectrum in South African population of \textit{Chlorocebus sabaeus}, masking CpG transitions (p.32).
-        \item S18: Including substitutions in the terminal lineage to estimate $\Spop$ (p.34).
-        \item S19: $\proba[\SphyBen\given \SpopBen ]$ while including divergence to estimate $\Spop$, as a function of distance to the sister species (p.37).
-        \item S20: $\proba [ \SpopDel ]$ when fitting a single or three DFEs (p.40).
-        \item S21: $\proba [ \SpopNeu ]$ when fitting a single or three DFEs (p.40).
-        \item S22: $\proba [ \SpopBen ]$ when fitting a single or three DFEs (p.40).
-    \end{itemize}
-
-    \newpage
-    \subsection*{List of Tables}
-    \begin{itemize}
-    \item S1: Probability of mutations and substitutions to be $\SphyDel$, $\SphyNeu$ or $\SphyBen$ (p.12).
-    \item S2: $\dnds$ for $\SphyDel$, $\SphyNeu$ or $\SphyBen$ (p.13).
-    \item S3: $\dnds$ over-estimation due to non-adaptive beneficial mutations (p.14).
-    \item S4: Gene ontology enrichment in $\SphyBen$ SNPs (p.15).
-    \item S5: Terms associated with deleterious mutations $\SphyDel$ (p.18).
-    \item S6: Terms associated with non-adaptive beneficial mutations $\SphyBen$ (p.18).
-    \item S7: Probability for beneficial mutations to be non-adaptive ($\proba[\SphyBen\given \SpopBen ]$) (p.25).
-    \item S8: $\proba[\SphyBen\given \SpopBen ]$ while masking CpG transitions (p.30).
-    \item S9: Precision and recall while masking CpG transitions (p.31).
-    \item S10: $\proba[\SphyBen\given \SpopBen ]$ excluding or not genes under adaptation (p.33).
-    \item S11: $\proba[\SphyBen\given \SpopBen ]$ when including divergence to estimate $\Spop$ (p.35).
-    \item S12: Precision and recall while including divergence to estimate $\Spop$ (p.36).
-    \item S13: $\proba[\SphyBen\given \SpopBen ]$ excluding or not genes under adaptation, when including divergence to estimate $\Spop$ (p.38).
-    \item S14: $\proba[\SphyBen\given \SpopBen ]$ when using a discrete DFE to estimate $\Spop$ (p.41).
-    \item S15: Precision and recall when using a discrete DFE to estimate $\Spop$ (p.42).
-    \end{itemize}
-
-    \newpage
-    \begin{figure*}[!htb]
+\begin{figure}[!htb]
 \centering
@@
 \caption{
+{\bf Changing and stable fitness landscapes.}
 (A \& B) For a given codon position of a protein-coding DNA sequence, amino acids (x-axis) have different fitness values (y-axis).
@@
 \label{fig:fitness-landscape}
-    \end{figure*}
-
-    \begin{figure*}[!h]
+\end{figure}
+
+\subsection*{Beneficial yet non-adaptive mutations}
+
+In a constant environment, a deleterious mutation can reach fixation by genetic drift~\cite{ohta_nearly_1992}.
+A new mutation restoring the ancestral fitness will thus be beneficial (Fig~\ref{fig:fitness-landscape}B), even though the environment has not changed~\cite{gillespie_ohta_1995, hartl_compensatory_1996, sella_application_2005, mustonen_fitness_2009, cvijovic_fate_2015}.
+We will refer to as beneficial non-adaptive mutations to those mutations that restore the ancestral fitness under the assumption that the fitness landscape has not changed~\cite{piganeau_estimating_2003, charlesworth_other_2007}.
+Such mutations can happen through a mutation at a different locus, in which case it is called a compensatory mutation~\cite{hartl_compensatory_1996, mustonen_fitness_2009}.
+While compensatory mutations change the sequence and thus induce genetic diversification, beneficial non-adaptive mutations at the locus of the initial mutation reduce genetic diversity and do not contribute to genetic innovation, which are the focus of this manuscript.
+Although Tomoko Ohta considered beneficial non-adaptive mutations negligible in her nearly-neutral theory~\cite{ohta_nearly_1992}, their importance has now been acknowledged for expanding populations~\cite{charlesworth_other_2007}.
+However, differentiating between an adaptive mutation and a beneficial non-adaptive mutation remains challenging~\cite{chi_detecting_2020}.
+Indeed, an adaptive mutation responding to a change in the environment and a beneficial non-adaptive mutation have equivalent fitness consequences for their bearer~\cite{charlesworth_other_2007}.
+Similarly, at the population level, both types of mutations will result in a positive transmission bias of the beneficial allele.
+However, at the macro-evolutionary scale, the consequences of these two types of mutations are fundamentally different.
+While adaptive mutations promote phenotype diversification (Fig~\ref{fig:fitness-landscape}C), beneficial non-adaptive mutations promote phenotype stability and may help preserve well-established biological systems (Fig~\ref{fig:fitness-landscape}D).
+Additionally, the direction of adaptive evolution is unpredictable because it is caused by an unforeseen change in the environment and, hence, in the underlying fitness landscape~\cite{bazykin_changing_2015}.
+On the other hand, beneficial non-adaptive mutations are predictable because, under a stable fitness landscape, any change from non-optimal to optimal amino acids will move back the site toward the equilibrium expected under the fitness landscape~\cite{moses_inferring_2009, fischer_germline_2011, chen_hunting_2021}.
+They can then be distinguished from truly novel beneficial mutations because the latter are not expected to mutate toward the amino acids of higher fitnesses defined by the stable fitness landscape but rather mutate to amino acids showing a diversified pattern (Fig~\ref{fig:fitness-landscape}).
+
+\subsection*{Fitness landscape reconstruction}
+
+The mutation-selection framework permits to link the patterns of substitution along a phylogenetic tree with the underlying fitness landscape~\cite{halpern_evolutionary_1998, mccandlish_modeling_2014}.
+Such mutation-selection models applied to protein-coding DNA sequence alignments at the codon level allow us to estimate relative fitnesses for all amino acids for each site of the sequence, explicitly assuming that the underlying fitness landscape is stable along the phylogenetic tree~\cite{rodrigue_mechanistic_2010, tamuri_estimating_2012, rodrigue_detecting_2017}.
+Moreover, effective population size ($\Ne$) is considered constant along the phylogenetic tree precisely because of the fixed fitness landscape assumption, the consequences of which are detailed in the Discussion.
+Importantly, because mutation-selection codon models at the phylogenetic scale are based on population-genetics equations, their estimates of selection coefficients are directly interpretable as fitness effects at the population scale; and because they work at the DNA level, we are able to account for mutational bias in DNA and structure of the genetic code.
+The model further integrates the shared evolutionary history between samples and their divergence, which, together, allow us to estimate fitness effects in sequence alignments even though sequences are not independent samples and might not represent the equilibrium distribution of amino acids (see section~\ref{subsec:s-phylogeny-method} in Materials \& Methods).
+Detailed model description is available in~\nameref{S1_File} (\nameref{S1_Fig}).
+
+Accordingly, fitting the mutation-selection model to a multi-species sequence alignment allows us to obtain relative fitnesses for all amino acids (Fig~\ref{fig:method}A).
+The difference in fitness between a pair of amino acids allows us to predict whether any mutation would be a deleterious mutation toward a less fit amino acid, a nearly-neutral mutation, or a mutation toward a known fitter amino acid constituting thus a beneficial non-adaptive mutation (Fig~\ref{fig:method}B).
+We can hence use large-scale genomic data to test whether such fitnesses estimated at the phylogenetic scale predict the fitness effects at the population scale.
+The placental mammals represent an excellent study system to perform such an analysis.
+Having originated $\sim$102 million years ago, they diversified quickly~\cite{foley_genomic_2023}.
+Additionally, polymorphism data are available for many species~\cite{howe_ensembl_2021}, as are high quality protein-coding DNA alignments across the genome~\cite{ranwez_orthomam_2007, scornavacca_orthomam_2019}.
+By performing our analysis on 14,509 orthologous protein-coding genes across 87 species, we focus on genes shared across all mammals in our dataset and not newly functionalized genes in a lineage.
+
+\begin{figure}[!ht]
+\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
 \centering
-        \includegraphics[width=\textwidth, page=1] {figure2.eps}
+\includegraphics[width=1.4\textwidth, page=1] {figure2.eps}
 \caption{
-            Selection coefficients at the phylogenetic and population scales.
+{\bf Selection coefficients at the phylogenetic and population scales.}
 At the phylogenetic scale (A), we estimated the amino-acid fitness for each site from protein-coding DNA alignments using mutation-selection codon models.
@@
 \label{fig:method}
-    \end{figure*}
-
-    \begin{figure*}[!h]
+\end{adjustwidth}
+\end{figure}
+
+Having identified which potential DNA changes represent beneficial non-adaptive mutations (Fig~\ref{fig:method}A-B), we retrieved polymorphism data from 28 wild and domesticated populations belonging to six genera (\textit{Equus}, \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus}, and \textit{Homo}) to assess the presence of beneficial non-adaptive mutations at the population scale.
+We focused on both mutations currently segregating within populations and on substitutions in the terminal branches, and checked if any of these observed changes were indeed beneficial (Fig~\ref{fig:method}C-E).
+A similar approach demonstrated the presence of beneficial non-adaptive mutations in humans~\cite{moses_inferring_2009, fischer_germline_2011} and in plants~\cite{chen_hunting_2021}.
+However, the model used to reconstruct the static fitness landscape in these studies can only be applied to deeply conserved protein domains in the tree of life, which corresponds to a subpart of the proteome that evolves slowly.
+The mutation-selection model used in the present work integrates phylogenetic relationships, and thus allows us to estimate the fitness landscape in shallower phylogenetic trees, and therefore can be applied almost exome-wide~\cite{rodrigue_mutationselection_2010}.
+
+We first quantified the likelihood of any DNA mutation to be a beneficial non-adaptive mutation, that is, whenever a DNA mutation increases fitness under a stable fitness landscape.
+Subsequently, by quantifying the total amount of beneficial mutations in the current population across all types of DNA mutations, we could tease apart beneficial non-adaptive from adaptive mutations resulting from a change in the fitness landscape.
+Altogether, in this study, by integrating large-scale genomic datasets at both phylogenetic and population scales, we propose a way to explicitly quantify the contribution of beneficial non-adaptive mutations to positive selection across the entire exome of the six genera (figs.~\ref{fig:method}F-G).
+
+\section*{Results}
+
+\subsection*{Selection along the terminal branches}
+First, we assessed whether fitness effects derived from the mutation-selection model at the phylogenetic scale predict selection occurring in terminal branches.
+We recovered the mutations that reached fixation in the terminal branches of the six genera.
+We only considered mutations fixed in a population as substitutions in the corresponding branch by discarding mutations segregating in our population samples.
+For each substitution identified in the terminal branches we obtained its $\Sphy$ value such as predicted at the mammalian scale (Fig~\ref{fig:method}A-B).
+We could classify each substitution as either deleterious $\SphyDel \coloneqq \Sphy < -1$), nearly-neutral ($\SphyNeu \coloneqq -1 < \Sphy <1$), or beneficial ($\SphyBen \coloneqq \Sphy > 1$)
+Because $\Sphy$ values were based on the assumption that the fitness landscape is stable across mammals, $\SphyBen$ mutations (i.e., with $\Sphy>1$) bring the bearer of this mutation toward an amino acid predicted to be fitter across mammals.
+Importantly, the mammalian alignment used to estimate the amino acid fitness landscape did not include the six focal genera and their sister species.
+This ensures independence between, on the one hand, the fitness landscape estimated, and on the other hand, both substitutions that occurred in the terminal branches, and segregating polymorphisms of the focal populations.
+Example substitutions in the terminal lineage of \textit{Chlorocebus sabaeus} which are classified as $\SphyBen$ are shown in supplementary materials (section S2).
+For instance, in the mammalian protein-coding DNA alignment of gene \textit{SELE}, the nucleotide at site 1722 has mutated (from T to C) at the base of Simiiformes (monkeys and apes), modifying the corresponding amino acid from Serine to Proline, but has been subsequently reverted in the branch of \textit{Chlorocebus sabaeus} (\nameref{S2_Fig}).
+However, other substitutions classified as $\SphyBen$ in the terminal branch of \textit{Chlorocebus sabaeus} cannot be clearly interpreted as reversions along the terminal branch, and show several transitions to this amino acid across the mammalian phylogeny, as for instance site 3145 of gene \textit{THSD7A} (\nameref{S3_Fig}).
+
+Among all the substitutions found in each terminal branch, between 10 and 13\% were $\SphyBen$, while $\SphyBen$ mutations only represent between 0.9 and 1.2\% of all non-synonymous mutations (Fig~\ref{fig:homo-afr-results}A-B for humans and ~\nameref{S1_Table} for all dataset).
+Of note, if we were to assume a stationary mutation-selection-drift equilibrium in the terminal lineage, we would expect a symmetric proportion of positively ($\SphyBen$) and negatively ($\SphyDel$) selected substitutions if there were no adaptation.
+The lack of symmetry along the terminal branches then provides a means to estimate the frequency of non-adaptive beneficial substitutions.
+Mathematically, twice the fraction of $\SphyBen$ substitutions is an estimate of this rate.
+This rate is highly consistent across lineages (\nameref{S1_Table}) and suggests an overall frequency of nearly neutral substitutions due to consistent long-term selection pressures, mutation and drift of approximately 20\% of all substitutions (20\%-26\% across species).
+
+\begin{figure}[!ht]
+\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
 \centering
-        \includegraphics[width=\textwidth, page=1] {figure3.eps}
+\includegraphics[width=1.4\textwidth, page=1] {figure3.eps}
 \caption{
+{\bf Selection coefficients of mutations in humans of African descent.}
 (A) Distribution of scaled selection coefficients ($\Sphy$), predicted for all possible non-synonymous DNA mutations away from the ancestral human exome (section \ref{subsec:nunber-of-sites}).
@@
 \label{fig:homo-afr-results}
-    \end{figure*}
-
-    \begin{figure*}[!ht]
+\end{adjustwidth}
+\end{figure}
+
+Furthermore, since in principle, $\SphyBen$ mutations are bound to reach fixation more often than neutral mutations, we calculated the $\dnds$ ratio of non-synonymous over synonymous divergence for all terminal lineages, focusing on the non-synonymous changes predicted as $\SphyBen$ mutations ($\dn(\SphyBen) / \ds$).
+We obtained values between 1.17 and 1.75 in the different lineages (\nameref{S2_Table}), meaning that $\SphyBen$ mutations reach fixation slightly more frequently than synonymous mutations that are supposed to be neutral, consistent with these $\SphyBen$ mutations being weakly beneficial.
+Such an observation is consistent with the premise that $\SphyBen$ mutations are weakly beneficial, translating to a scaled selection coefficient between 0.32 and 1.24 (\nameref{S2_Table}).
+Finding $\dn(\SphyBen) / \ds > 1$ for these sites confirms that these sites are closer to optimality at the end of the branch than at the beginning.
+Even though the beneficial effect of these mutations does not come from an environmental change, it does not change the fact that they have contributed positively to the population’s fitness.
+It is just that at mutation-selection-drift equilibrium, the increase in fitness at these sites is offset by deleterious substitutions elsewhere in the genome so that there is no net adaptation.
+
+This result further indicates that using $\dnds$ as an estimate of purifying selection is biased (overestimated) due to the presence of beneficial non-adaptive mutations among the non-synonymous substitutions.
+By discarding all beneficial non-adaptive mutations we can obtain an estimate of $\dnds$ which is not inflated.
+By comparing these two ways of calculating $\dnds$ (see section~\ref{subsec:substitution-mapping-in-the-terminal-branch} in Materials \& Methods), we calculated that beneficial non-adaptive mutations inflate $\dnds$ values by between 9 and 12\% across genera.
+This represents a substantial increase when considering that beneficial non-adaptive mutations only represent between 0.9 and 1.2\% of non-synonymous mutational opportunities (\nameref{S3_Table}).
+
+\subsection*{Selection in populations}
+Second, we assessed whether our calculated $\Sphy$ values predicted at the phylogenetic scale were also indicative of the selective forces exerted at the population level.
+We retrieved single nucleotide polymorphisms (SNPs) segregating in 28 mammalian populations.
+To determine if SNPs were ancestral of derived, we reconstructed the ancestral exome of each population.
+We then classified every non-synonymous SNP as either $\SphyDel$, $\SphyNeu$, or $\SphyBen$ according its $\Sphy$ value (Fig~\ref{fig:method}B-C).
+
+First, SNPs classified as $\SphyBen$ are spread across the genomes and not strongly associated to the ontology terms of their respective genes (\nameref{S4_Table},~\nameref{S4_Fig}).
+In humans, some SNPs have been associated with specific clinical prognosis terms obtained by clinical evaluation of the impact of variants on human Mendelian disorders~\cite{landrum_clinvar_2018}.
+Although this classification also relies on deep protein alignments and therefore cannot be considered an independent result from our own, it does provide a consistency check if the effect of a mutation on human health is in line with its fitness effect predicted by our method~\cite{grimm_evaluation_2015}.
+Therefore, we investigated whether the non-synonymous SNPs classified as $\SphyDel$ or $\SphyBen$ showed enrichment in specific clinical terms compared to SNPs classified as $\SphyNeu$.
+Our results show that SNPs predicted as deleterious are associated with clinical terms such as \textit{Likely Pathogenic} and \textit{Pathogenic}, implying that, in general, the selective pressure of a mutation exerted across mammals is also predictive of its clinical effect in humans (\nameref{S5_Table})~\cite{sullivan_leveraging_2023}.
+Conversely, $\SphyBen$ mutations are associated with clinical terms such as \textit{Benign} and \textit{Likely Benign}, which shows that $\SphyBen$ mutations are less likely to be functionally damaging (\nameref{S6_Table}).
+
+In addition to clinical prognosis, frequencies at which SNPs are segregating within populations provide information on their selective effects.
+For instance, deleterious SNPs usually segregate at lower frequencies because of purifying selection, which tends to remove them from the population (Fig~\ref{fig:homo-afr-results}C for humans).
+By gathering information across many SNPs, it is possible to estimate the distribution of fitness effects at the population scale, taking synonymous SNPs as a neutral expectation~\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009, galtier_adaptive_2016, tataru_inference_2017}.
+From these estimated fitness effects, we can derive the proportion of deleterious mutations ($\ProbaPopDel$,~\nameref{S5_Fig}), nearly-neutral mutations ($\ProbaPopNeu$,~\nameref{S6_Fig}) and beneficial mutations ($\ProbaPopBen$,~\nameref{S7_Fig}) at the population scale (see section~\ref{subsec:s-polymorphism-method} in Materials \& Methods).
+These approaches offer a unique opportunity to contrast selection coefficients estimated at the phylogenetic scale ($\Sphy$) and at the population scale ($\Spop$) in different dataset (\nameref{S8_Fig}).
+
+Across our selection classes ($\SphyDel$, $\SphyNeu$ and $\SphyBen$), one can ultimately estimate the proportion of correct and incorrect predictions, leading to an estimation of \textit{precision} and \textit{recall} (Fig~\ref{fig:method}F-G and section~\ref{subsec:precisison_recall} in Materials \& Methods).
+Across 28 populations of different mammal species, mutations predicted to be deleterious at the phylogenetic scale ($\SphyDel$) were indeed purged at the population scale, with a \textit{precision} in the range of 90--97\% (Table~\ref{table:proba} and Fig~\ref{fig:homo-afr-results}D for humans).
+Conversely, a \textit{recall} in the range of 96--100\% implied that mutations found to be deleterious at the population scale were most likely also predicted to be deleterious at the phylogenetic scale (Table~\ref{table:proba}).
+Altogether, purifying selection is largely predictable and amino acids with negative fitness across mammals have been effectively purged away in each population.
+
+\begin{table}[!ht]
+\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
 \centering
-        \includegraphics[width=\textwidth, page=1] {figure4.eps}
 \caption{
-            Populations in circles, mean of the species across the populations as squares.
-            (A) Proportion of nearly-neutral mutations at the population scale ($\proba [ \SpopNeu]$ in the y-axis), shown as a function of estimated effective population size ($\Ne$ in the x-axis).
-            (B) Proportion of beneficial non-adaptive mutations among all beneficial mutations ($\proba [ \SphyBen \given \SpopBen]$ in the y-axis), shown as a function of $\Ne$ in x-axis.
-            Correlations account for phylogenetic relationship and non-independence of samples, through the fit of a Phylogenetic Generalized Linear Model (see section~\ref{subsec:s-polymorphism-method} in Materials \& Methods).
-        }
-        \label{fig:diversity}
-    \end{figure*}
-
-    \begin{table*}[tb]
-        \centering
-        \begin{adjustbox}{width=\textwidth}
+{\bf \textit{Precision} and \textit{recall} for estimated selection coefficient of mutations given by mutation-selection models ($\bm{\Sphy}$).}}
+\scriptsize
 \begin{tabular}{||l|l|r||r|r||r|r||r|r||}
@@
 \end{tabular}
-        \end{adjustbox}
-        \caption{
-            \textit{Precision} and \textit{recall} for estimated selection coefficient of mutations given by mutation-selection models ($\Sphy$).
-            \textit{Precision} is the estimation of the selection coefficient at population scale ($\Spop$) given that $\Sphy$ is known.
+\normalsize
+\begin{flushleft} \textit{Precision} is the estimation of the selection coefficient at population scale ($\Spop$) given that $\Sphy$ is known.
 Conversely, \textit{recall} is the estimation of $\Sphy$ given selection coefficient at the population scale ($\Spop$) is known.
@@
 $\Ne$ is the estimated effective population size for each population.
+\end{flushleft}
+\label{table:proba}
+\end{adjustwidth}
+\end{table}
+
+Mutations predicted as $\SphyNeu$ were effectively composed of a mix of neutral and selected mutations with varying \textit{precision} (36--63\%) and \textit{recall} (32--45\%) across the different populations (Table~\ref{table:proba}, Fig~\ref{fig:homo-afr-results}D for humans).
+The variable proportions between populations can be explained by the effective number of individuals in the population ($\Ne$), a major driver of selection efficacy.
+Moreover, estimates of mutation rate per generation ($u$), from Bergeron \textit{et al.}~\cite{bergeron_evolution_2023} and Orlando \textit{et al.}~\cite{orlando_recalibrating_2013}, and Watterson’s $\theta$ obtained from the synonymous SFS as in Achaz~\cite{achaz_frequency_2009}, allow us to obtain $\Ne$ through $\Ne=\theta/4 u)$.
+Using correlation analyses that accounted for phylogenetic relationship (see section~\ref{subsec:correlation-diversity} in Materials \& Methods,~\nameref{S9_Fig}), we found that higher $\Ne$ was associated with a smaller proportion of nearly-neutral mutations ($r^2=0.31$, $p=0.001$, Fig~\ref{fig:diversity}A).
+This result follows the prediction of the nearly-neutral theory and suggests that in populations with higher diversity (e.g.,~\textit{Bos} or \textit{Ovis}), discrimination between beneficial and deleterious mutations is more likely to occur (\nameref{S10_Fig},~\nameref{S11_Fig},~\nameref{S12_Fig}).
+Conversely, many more mutations are effectively neutral in populations with lower diversity (e.g.,~\textit{Homo}).
+
+\begin{figure}[!ht]
+\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\centering
+\includegraphics[width=1.4\textwidth, page=1] {figure4.eps}
+\caption{
+{\bf Proportion of nearly-neutral mutations and beneficial non-adaptive mutations as a function of effective population size ($\Ne$).}
+Populations in circles, mean of the species across the populations as squares.
+(A) Proportion of nearly-neutral mutations at the population scale ($\proba [ \SpopNeu]$ in the y-axis), shown as a function of estimated effective population size ($\Ne$ in the x-axis).
+(B) Proportion of beneficial non-adaptive mutations among all beneficial mutations ($\proba [ \SphyBen \given \SpopBen]$ in the y-axis), shown as a function of $\Ne$ in x-axis.
+Correlations account for phylogenetic relationship and non-independence of samples, through the fit of a Phylogenetic Generalized Linear Model (see section~\ref{subsec:s-polymorphism-method} in Materials \& Methods).
 }
-        \label{table:proba}
-    \end{table*}
+\label{fig:diversity}
+\end{adjustwidth}
+\end{figure}
+
+Finally, mutations predicted to be $\SphyBen$ were indeed beneficial for individuals bearing them, with a \textit{precision} (Fig~\ref{fig:method}F) in the range of 19--87\% (Table~\ref{table:proba} and Fig~\ref{fig:homo-afr-results}D for humans).
+This result confirms that selection toward amino acids restoring existing functions is ongoing in these populations.
+Importantly, the \textit{recall} value in this case, computed as $\proba [ \SphyBen \given \SpopBen]$, is the probability for a beneficial mutation at the population scale to be a non-adaptive, i.e., going toward a fitter amino acid given a stable fitness landscape (Fig~\ref{fig:method}G,~\nameref{S7_Table}).
+In other words, the \textit{recall} value quantifies the number of beneficial mutations restoring damaged genomes instead of creating adaptive innovations.
+Across the 28 populations, this proportion is in the range of 11--82\% (Table~\ref{table:proba}), with a mean of 30\%.
+Accounting for phylogenetic relationships, we found no correlation between the proportion of beneficial non-adaptive mutations and estimates of $\Ne$ based on genetic diversity ($r^2=0.00$, $p=0.772$, Fig~\ref{fig:diversity}B).
+
+We additionally performed controls and simulations to ensure our results were robust.
+First, we controlled that these estimations were not affected by SNP mispolarization (\nameref{S13_Fig},~\nameref{S14_Fig}).
+Second, we performed simulations at the population-genetic level and confirmed that our method was able to recover the proportion of beneficial mutations that are non-adaptive in synthetic polymorphism datasets (\nameref{S15_Fig}).
+Third, we ran our analysis filtering out CpG mutations and obtained values of $\proba [ \SphyBen \given \SpopBen]$ in the range of 5--27\%, with a mean of 14\% (\nameref{S8_Table}, \nameref{S9_Table}, \nameref{S16_Fig}), providing more conservative estimates.
+Finally, because the phylogenetic mutation-selection codon model should fit better for genes with uniformly conserved functions, we filtered out genes under pervasive adaptation~\cite{latrille_genes_2023} as a control.
+In this subset of the exome, containing genes with a more stable fitness landscape, we found an increase in the proportion of beneficial mutations that are non-adaptive (Wilcoxon signed-rank, $s=80$, $p=0.002$,~\nameref{S10_Table}), consistent with our expectation that beneficial mutations occur more frequently in genes under changing fitness landscapes.
+
+\subsection*{Selection in the terminal lineage and in populations}
+
+As an alternative to relying solely on currently segregating mutations to quantify selection, one can leverage both polymorphism within a population and substitutions in the terminal lineage to estimate the distribution of fitness effects (DFE).
+Hence, we estimated \textit{precision} and \textit{recall} as done previously, but now including the number of substitutions per site as input for the DFE estimators (see~\ref{subsec:s-polymorphism-method} in Materials \& Methods and~\nameref{S17_Fig}).
+When including substitutions in the terminal lineage, estimates of $\proba [ \SphyBen \given \SpopBen]$ are in the 10--78\% range with a mean of 36\%, and 19 out of 28 estimates fall between 15\% and 45\% (\nameref{S11_Table}, \nameref{S12_Table}).
+
+Additionally, we controlled that these estimations were not affected by SNP mispolarization (\nameref{S18_Fig}).
+We also filtered out genes under pervasive adaptation, and again found an increase in $\proba [ \SphyBen \given \SpopBen]$, consistent with our expectation (Wilcoxon signed-rank, $s=120$, $p=0.027$,~\nameref{S13_Table}).
+We assessed the impact of fitting the same functional form of DFE to the three different categories of changes $\SphyDel$, $\SphyNeu$ and $\SphyBen$.
+To this aim we computed the total amount of current selection by fitting either a single DFE on the whole dataset or by summing the other three independent DFEs.
+These disjoint estimates are well correlated, with a goodness of fit $r^2={0.95, 0.89, 0.82}$ for respectively $\proba [\SpopDel]$ (\nameref{S19_Fig}), $\proba [\SpopNeu]$(\nameref{S20_Fig}) and $\proba [\SpopBen]$ (\nameref{S21_Fig}).
+Finally, we evaluated the effect of fitting a parametric functional form for the DFE.
+As implemented in Tataru \textit{et al.}~\cite{tataru_inference_2017}, the DFE is a mixture between a reflected gamma distribution and an exponential distribution (eq.~\ref{eq:parametric-dfe}, section~\ref{subsec:precisison_recall} in Materials \& Methods).
+Instead of using such a continuous DFE, we also tested our prediction with a non-parametric functional form for the DFE, obtaining estimates of $\proba [ \SphyBen \given \SpopBen]$ in the 8--94\% range, with a mean of 43\% (\nameref{S14_Table}, \nameref{S15_Table}).
+
+\section*{Discussion}
+\subsection*{Beneficial mutations are not necessarily adaptive}
+
+This study represents an essential step toward integrating the different evolutionary scales necessary to understand the combined effects of mutation, selection, and drift on genome evolution.
+In particular, we have been able to quantify the proportion of beneficial mutations that are non-adapative (i.e., not a response to a change in fitness landscape), which has only been achievable by combining exome-wide data from both phylogenetic and population scales.
+At the phylogenetic scale, codon diversity at each site of a protein-coding DNA alignment allows for reconstructing an amino-acid fitness landscape, assuming that this landscape is stable along the phylogenetic tree.
+These amino-acid fitness landscapes allow us to predict any mutation’s selection coefficient ($\Sphy$) along a protein-coding sequence.
+We have compared these selective effects to observations at the population level, and by doing so, we have confirmed that mutations predicted to be deleterious ($\SphyDel \coloneqq \Sphy < -1$) are generally purified away in extant populations.
+Our results concur with previous studies showing that SIFT scores~\cite{ng_sift_2003, vaser_sift_2016}, based on amino acid alignments across species, also inform on the deleterious fitness effects exerted at the population scale~\cite{chen_hunting_2021}.
+However, contrary to SIFT scores, our mutation-selection model is parameterized by a fitness function such that changes are directly interpretable as fitness effects (see also section S5).
+In this regard, an interesting prediction of our model is that some deleterious mutations reach fixation due to genetic drift, while beneficial non-adaptive mutations restore states of higher fitness.
+We have tested this hypothesis and have found that a substantial part of these predicted non-adaptive mutations ($\SphyBen \coloneqq \Sphy > 1 $) are indeed beneficial in extant populations.
+We estimate that between 11 and 82\% of all beneficial mutations in mammalian populations are not adaptive.
+More specifically, in 24 out of 28 populations analyzed, the percentage of beneficial mutations estimated to be non-adaptive falls between 15 and 45\%.
+These results suggest that many beneficial mutations are not adaptive, but rather restore states of higher fitness.
+Hence, we can correctly estimate the extent of adaptive evolution only if we account for the number of beneficial non-adaptive mutations~\cite{keightley_what_2010, rice_evolutionarily_2015}.
+Here instead, we argue that we should dissociate positive selection from adaptive evolution and limit the use of adaptive mutations to those that are associated with adaptation to environmental change as such~\cite{charlesworth_other_2007, mustonen_fitness_2009, mustonen_fitness_2010}.
+
+\subsection*{Assumptions and methodological limitations}
+
+The exact estimation of the contribution of beneficial non-adaptive mutations to positive selection relies on some hypotheses at both the phylogenetic and population scales and is sensitive to methodological limitations.
+Indeed, data quality and potentially inadequate modeling choices of both the fitness landscape (at the phylogenetic scale) and fitness effects (at the population scale) might also lead to missed predictions~\cite{moutinho_variation_2019}.
+In practice, we obtained different values of the proportion of non-adaptive beneficial mutations depending on i) the filtering or not of CpG mutations~\cite{eyre-walker_how_2014}, ii) whether we included substitutions in the terminal lineage along with within-population polymorphisms to estimate fitness effects~\cite{tataru_inference_2017}, and iii) the model used to infer the fitness effects.
+It appears that our estimation can be sensitive to model misspecification and overall, while we provide an order of magnitude for the contribution of beneficial non-adaptive mutations to positive selection, methodological improvement on the estimation of the DFE is needed to increase the precision of this value.
+
+To be conservative, we considered mutations as adaptive if they were detected as being under positive selection at the population scale despite them being either incorrectly predicted as deleterious ($\SphyDel$) or nearly-neutral ($\SphyNeu \coloneqq -1 < \Sphy <1$) from the amino-acid mammalian fitnesses.
+An example of an incorrectly predicted deleterious mutation ($\SphyDel$) from its fitness landscape could be an amino acid having always been deleterious across mammals, but being advantageous ($\SpopBen$) in the current species due to environmental changes or a major shift in their fitness landscape (e.g.
+domestication)
+To visualize an example of a wrongly predicted nearly-neutral mutation, we can first imagine a site where only hydrophilic amino acids are accepted because of the protein properties (e.g.
+a surface site of a globular protein).
+Let us then assume that such a site is also a target for viruses, hence promoting amino-acid changes which modify the site's viral affinity~\cite{enard_viruses_2016}.
+Given the selective pressure favoring amino-acid change, but restricting the possibilities to hydrophilic amino acids, most hydrophilic amino acids will likely be visited along the phylogenetic tree and the mutation-selection model will give high and similar fitnesses to all of them.
+In such a case, any mutation between hydrophilic amino acids will be wrongly predicted as nearly-neutral ($\SphyNeu$), while it is in fact adaptive.
+In summary, under a changing fitness landscapes~\cite{mustonen_molecular_2008}, our phylogenetic mutation-selection model takes an average over fitness changes observed along the phylogeny, causing beneficial mutations ($\SpopBen$) to be predicted as either deleterious ($\SphyDel$) or nearly-neutral ($\SphyNeu$), therefore mechanically reducing $\proba [ \SphyBen \given \SpopBen]$, and making our estimate conservative.
+
+\subsection*{Convergent adaptation}
+
+If there are several substitutions toward the same amino acid along the mammalian tree (\nameref{S3_Fig}), our mutation-selection model cannot formally distinguish between a scenario where mammals have fixed deleterious mutations that are reverted in several lineages, from more complex scenarios involving convergent adaptation across mammals.
+In a first scenario, repeated changes of fitness landscapes in the same direction could occur along several lineages, leading to repeated substitutions in multiple lineages (parallel or convergent adaptation).
+In a second scenario, an environmental change that occurred near the root of placental mammals ($\sim$100 Mys ago), to which extant populations are currently responding independently through weakly adaptive mutations, could also lead to repeated substitutions toward the same amino acids.
+Importantly, we would usually expect adaptive convergent mutations to be linked to particular converging phenotypes across mammals, and hence, they should not massively affect the whole genome as we find (\nameref{S4_Table},~\nameref{S4_Fig}).
+Moreover, after filtering out genes usually associated to recurrent adaptation (e.g. immune genes), we recover an even higher proportion of beneficial non-adaptive mutations (\nameref{S8_Table}).
+For these reasons, we argue that the signal of predictable positive selection we recover in extant population is indeed mainly driven by non-adaptive evolution.
+
+\subsection*{The influence of effective population size}
+
+Across the genome, beneficial non-adaptive mutations and deleterious mutations reaching fixation create a balance in which genomes are constantly damaged and restored simultaneously at different loci due to drift.
+Since the probability of fixation of mutations depends on the effective population size ($\Ne$), the history of $\Ne$ plays a crucial role in determining the number of beneficial non-adaptive mutations compensating for deleterious mutations~\cite{latrille_inferring_2021}.
+For example, a population size expansion will increase the efficacy of selection, and a larger proportion of mutations will be beneficial (otherwise effectively neutral), thus increasing the number of beneficial non-adaptive mutations.
+On the other hand, a population that has experienced a high $\Ne$ throughout its history should be closer to an optimal state under a stable fitness landscape, having suffered fewer fixations of deleterious mutations and therefore decreasing the probability of beneficial non-adaptive mutations~\cite{huber_determining_2017}.
+Overall, we expect the proportion of beneficial non-adaptive mutations to be more dependent on $\Ne$’s long-term expansions and contractions than on the short-term ones~\cite{charlesworth_other_2007,huber_determining_2017}.
+
+Moreover, because our model assumes a fixed fitness landscape, it implicitly assumes that $\Ne$ is constant along the phylogenetic tree.
+Fluctuations due to changes in the fitness landscape or in $\Ne$ will be averaged out by the assumption of the current model that $\Ne$ is constant across lineages.
+It was recently shown~\cite{latrille_inferring_2021}, using computer intensive mutation-selection models with fluctuating $\Ne$, that relaxing the assumption of a constant $\Ne$ results in more extreme estimates of amino-acid fitnesses than with the standard model used in this study.
+In other words, by assuming a constant $\Ne$, we are underpowered to detect beneficial non-adaptive mutations since amino acids will have more similar fitnesses.
+As a consequence, some of the beneficial non-adaptive mutations currently segregating in population will be incorrectly classified as nearly-neutral by the mutation-selection model, and thus be wrongly interpreted as adaptive (see previous section).
+This ultimately results in lower estimates of the proportion of beneficial non-adaptive mutations.
+Given this inflation of missed predictions due to change in population sizes~\cite{lanfear_population_2014, jones_shifting_2017, platt_protein_2018}, our estimated proportion of beneficial non-adaptive mutations among adaptive ones is likely to be an underestimation.
+
+\subsection*{The role of epistasis and compensatory mutations}
+
+Our model assumes that amino-acid fitness landscapes are site-specific and also independent of one another, whereas under pervasive epistasis, the fitness effect of any mutation at a particular site would depend on the amino acids present at other sites.
+Epistasis is common for mutations that influence the protein’s physical properties (e.g.
+conformation, stability, or affinity for ligands) or might arise due to nonlinear relationship between the protein’s physical properties and fitness~\cite{starr_epistasis_2016}.
+Regardless of its origin, epistasis has been shown to play a role in the evolution of protein-coding genes, with amino-acid residues in contact within a protein or between proteins tending to co-evolve~\cite{morcos_directcoupling_2011, marks_protein_2012, starr_epistasis_2016}.
+Particularly, the residues in contact co-evolve to become more compatible with each other generating an entrenchment~\cite{goldstein_nonadaptive_2015, goldstein_sequence_2017, park_epistatic_2022}.
+Epistasis therefore allows for compensatory mutations, which restore fitness through mutations at loci different from where deleterious mutations took place, representing another case of non-adaptive beneficial mutations, but one which is not accounted for by our method.
+Hence, the beneficial mutations that we classify as putatively adaptive might in fact be compensatory mutations, making our estimation of the rate of non-adaptive beneficial mutations conservative.
+
+Despite epistasis being an important factor in protein evolution, several deep-mutational scanning experiments have revealed that a site-specific fitness landscape predicts the evolution of sequences in nature with considerable accuracy~\cite{ashenberg_mutational_2013, doud_sitespecific_2015, bloom_identification_2017}.
+Additionally, the fact that we observe such a high proportion of beneficial non-adaptive mutations suggests that the underlying assumptions of our model, namely site-independence, implying no epistasis, and a static fitness landscape, are a reasonable approximation for the underlying fitness landscape of proteins.
+Our results imply that the fitness effects of new mutations are mostly conserved across mammalian orthologs, in agreement with other studies showing that for conserved orthologs with similar structures and functions, models without epistasis provide a reasonable estimate of fitness effects in protein coding genes~\cite{youssef_consequences_2020, vigue_deciphering_2022}.
+Conceptually, the framework presented here, with the addition of a more complex protein fitness landscape at the phylogenetic scale, could be used to infer the relative contribution of compensatory mutations to non-adaptive and adaptive evolution.
+
+\subsection*{Detecting adaptation above the nearly-neutral background}
+
+A long-standing debate in molecular evolution is whether the variation we observe between species in protein-coding genes is primarily due to nearly-neutral mutations reaching fixation by drift or primarily due to adaptation~\cite{kimura_evolutionary_1968,ohta_nearly_1992,gillespie_substitution_1994,jensen_importance_2019}.
+Measuring the ``rate of adaptation'' in proteins, as pioneered by McDonald \& Kreitman~\cite{mcdonald_adaptative_1991}, has been central to inform this debate~\cite{galtier_half_2024}.
+However, the McDonald \& Kreitman test detects signatures of accelerated evolution in a given terminal branch compared to an expectation based on polymorphism present in the population.
+It considers the fraction of substitutions that fix too quickly as ``adaptive''~\cite{mcdonald_adaptative_1991, smith_adaptive_2002, welch_estimating_2006} despite there being other processes that can lead to their fixation~\cite{galtier_adaptation_2007,rousselle_influence_2019,joseph_increased_2024a} and some of these substitutions being beneficial but non-adaptive~\cite{hartl_compensatory_1996, charlesworth_other_2007, mustonen_fitness_2009, jones_shifting_2017}.
+Here, the expectation is built on the pattern of substitutions across a phylogeny compared to the fitness effects that can be estimated from both substitutions in a terminal lineage and polymorphism in populations.
+Moreover, the goal is not to detect a fraction of beneficial substitution (i.e.
+``adaptive'' substitutions for McDonald \& Kreitman~\cite{mcdonald_adaptative_1991}), but to estimate the proportion of non-adaptive mutations among beneficial ones.
+
+We provide evidence that in mammalian orthologs, many substitutions occur through fixation of both deleterious mutations and beneficial non-adaptive mutations.
+Detecting adaptation above this background of substitutions remains a challenge~\cite{kimura_evolutionary_1968, ohta_development_1996}.
+Mathematically, the surplus of positive selection due to an externally-driven changing fitness landscape is called \textit{fitness flux}, and requires experimentally measuring the selection coefficient of each mutation in each genetic background.
+The \textit{fitness flux} can be estimated if either the substitutions history is known~\cite{mustonen_fitness_2009} or changes of frequency in currently segregating variants~\cite{mustonen_fitness_2010}.
+Without experimentally measured selection coefficients, another strategy is precisely to use a nearly-neutral substitution model as a null model of evolution.
+Under a strictly neutral evolution of protein-coding sequence, we expect the ratio of non-synonymous over synonymous substitutions ($\dnds$) to be equal to one.
+Deviations from this neutral expectation, such as $\dnds > 1$, which can be generated by an excess of non-synonymous substitutions, is generally interpreted as a sign of adaptation.
+However, as shown in this study, a $\dnds > 1$ is not necessarily a signature of adaptation but can be due to beneficial non-adaptive mutations.
+So, by relaxing the strict neutrality and assuming a stable fitness landscape instead, one can predict the expected rate of evolution, called $\omega_0$~\cite{spielman_relationship_2015, dosreis_how_2015}.
+Adaptation can thus be considered as evolution under a changing fitness landscape and tested as such by searching for the signature of $\dnds > \omega_0$~\cite{cvijovic_fate_2015, rodrigue_detecting_2017, rodrigue_bayesian_2021}.
+Using a stable fitness landscape as a null model of evolution, thus accounting for selective constraints exerted on the different amino acids, increased the statistical power in testing for adaptation~\cite{latrille_genes_2023}.
+Instead of relying solely on summary statistics (such as $\dnds$ or $\omega_0$), another strategy to detect adaptation is to include changes in the fitness landscapes inherently within the mutation selection framework, either with small changes along the phylogeny ~\cite{tamuri_mutationselection_2021} or either by allowing fitness to change on subsets of branches ~\cite{kazmi_detecting_2019, stolyarova_senescence_2020}.
+Such mechanistic models could be more general than site-specific fitness landscapes, including epistasis and changing fitness landscapes~\cite{goldstein_sequence_2017, stolyarova_senescence_2020}.
+
+\subsection*{Conclusions}
+
+We have provided empirical evidence that an evolutionary model assuming a stable fitness landscape at the mammalian scale allows us to predict the fitness effects of mutations in extant populations and individuals, acknowledging the balance between deleterious and beneficial non-adaptive mutations.
+We argue that such a model would represent a null expectation for the evolution of protein-coding genes in the absence of adaptation.
+Altogether, because a substantial part of positive selection can be explained by beneficial non-adaptive mutations, but not its entirety, we argue that the mammalian exome is shaped by both adaptive and non-adaptive processes, and that none of them alone is sufficient to explain the observed patterns of changes.
+In that sense, to avoid conflating beneficial mutations with adaptive evolution, the term ``adaptation`` should retain its original meaning associated with a change in the underlying fitness landscape and be modelled as such~\cite{mustonen_fitness_2009, mustonen_fitness_2010}.
+
+\newpage
+\section{Materials \& Methods}
+\label{sec:methods}
+
+\subsection{Phylogenetic dataset}\label{subsec:phylo-dataset}
+
+Protein-coding DNA sequence alignments in placental mammals and their corresponding gene trees come from the \href{https://www.orthomam.univ-montp2.fr}{OrthoMaM} database and were processed as in Latrille \textit{et al.}~\cite{latrille_genes_2023}.
+OrthoMaM contains a total of $116$ mammalian reference sequences in v10c~\cite{ranwez_orthomam_2007, douzery_orthomam_2014, scornavacca_orthomam_2019}.
+
+Genes located on the X and Y chromosomes and on the mitochondrial genome were discarded from the analysis because the level of polymorphism –~which is necessary for population-based analyses~– is expected to be different in these three regions compared to the autosomal genome.
+Sequences of species for which we used population-level polymorphism (see section~\ref{subsec:polymorphism-dataset}) and their sister species, were removed from the analysis to ensure independence between the data used in the phylogenetic and population scales.
+Sites in the alignment containing more than 10\% of gaps across the species were discarded.
+Altogether, our genome-wide dataset contains $14,509$ protein-coding DNA sequences in $87$ placental mammals.
+
+\subsection{Selection coefficient (\texorpdfstring{$\bm{\Sphy}$}{S₀}) in a phylogeny-based method}
+\label{subsec:s-phylogeny-method}
+
+We analyzed the phylogenetic-level data using mutation-selection models.
+These models assume the protein-coding sequences are at mutation-selection balance under a fixed fitness landscape characterized by a fitness vector over the $20$ amino acids at each site~\cite{yang_mutationselection_2008, halpern_evolutionary_1998, rodrigue_mechanistic_2010}.
+Mathematically, the rate of non-synonymous substitution from codon $a$ to codon $b$ ($q_{a \mapsto b}^{(i)}$) at site $i$ of the sequence is equal to the rate of mutation of the underlying nucleotide change ($\mu_{a \mapsto b}$) multiplied by the scaled probability of mutation fixation ($\proba_{a \mapsto b}^{(i)}$).
+The probability of fixation depends on the difference between the scaled fitness of the amino acid encoded by the mutated codon ($F_b^{(i)}$) and the amino acid encoded by the original codon ($F_a^{(i)}$) at site $i$~\cite{wright_evolution_1931, fisher_genetical_1930}.
+
+The rate of substitution from codon $a$ to $b$ at a site $i$ is thus:
+\begin{equation}
+\begin{dcases}
+q_{a \mapsto b}^{(i)} & = 0 \text{ if codons $a$ and $b$ are more than one mutation away,} \\
+q_{a \mapsto b}^{(i)} & = \mu_{a \mapsto b} \text{ if codons $a$ and $b$ are synonymous, and}\\
+q_{a \mapsto b}^{(i)} & = \mu_{a \mapsto b} \dfrac{F_b^{(i)} - F_a^{(i)}}{1 - \e^{F_a^{(i)} - F_b^{(i)}}} \text{ if codons $a$ and $b$ are non-synonymous}.
+\end{dcases}
+\end{equation}
+
+Fitting the mutation-selection model on a multi-species sequence alignment leads to an estimation of the gene-wide $4 \times 4$ nucleotide mutation rate matrix ($\bm{\mu}$) as well as the $20$ amino-acid fitness landscape ($\bm{F^{(i)}}$) at each site $i$.
+The priors and full configuration of the model are given in section S1.
+From a technical perspective, the Bayesian estimation is a two-step procedure~\cite{rodrigue_bayesian_2008}.
+The first step is a data augmentation of the alignment, consisting in sampling a detailed substitution history along the phylogenetic tree for each site, given the current value of the model parameters.
+In the second step, the parameters of the model can then be directly updated by a Gibbs sampling procedure, conditional on the current substitution history.
+Alternating between these two sampling steps yields a Markov chain Monte-Carlo (MCMC) procedure whose equilibrium distribution is the posterior probability density of interest~\cite{lartillot_bayesian_2004, rodrigue_bayesian_2008}.
+Additionally, across-site heterogeneities in amino-acid fitness profiles are captured by a Dirichlet process.
+More precisely, the number of amino-acid fitness profiles estimated is lower than the number of sites in the alignment.
+Consequently each profile has several sites assigned to it, resulting in a particular configuration of the Dirichlet process.
+Conversely, sites with similar signatures are assigned to the same fitness profile.
+This configuration of the Dirichlet process is resampled through the MCMC to estimate a posterior distribution of amino acid profiles for each site specifically~\cite{rodrigue_mutationselection_2010, lartillot_inference_2013}.
+From a more mechanistic perspective, even though not all amino acids occur at every single codon site of the DNA alignment, we can nevertheless estimate the distribution of amino-acid fitnesses by generalizing the information recovered across sites and across amino acids based on the phylogenetic relationship among samples.
+In particular, synonymous substitutions along the tree contain the signal to estimate branch lengths and the nucleotide transition matrix, while non-synonymous substitutions contain information on fitness difference between codons connected by single nucleotide changes~\cite{rodrigue_mutationselection_2010}.
+
+The selection coefficient for a mutation from codon $a$ to codon $b$ at site $i$ is defined as:
+\begin{equation}
+\Sphy^{(i)} (a \mapsto b) = \Delta F^{(i)} = F^{(i)}_{b} - F^{(i)}_{a}.
+\end{equation}
+In our subsequent derivation the source ($a$) and target ($b$) codons as well as the site ($i$) are implicit and thus never explicitly written.
+
+The scaled selection coefficient ($\Sphy = \Delta F$) is formally the product of the selection coefficient at the individual level ($s$) and the effective population size ($\Ne$), as $\Sphy = 4 \Ne \times s$.
+The value of $\Sphy$ informs us on the strength of selection exerted on amino acids changes.
+Thus, according to its $\Sphy$ value, we can classify any mutation as either a deleterious mutation toward a less fit amino acid ($\SphyDel \coloneqq \Sphy < -1$), a nearly-neutral mutation ($\SphyNeu \coloneqq -1 < \Sphy <1$), or a mutation toward a known fitter amino acid, constituting thus a beneficial non-adaptive mutation ($\SphyBen \coloneqq \Sphy > 1$).
+
+We used the Bayesian software \textit{BayesCode} (\url{https://github.com/ThibaultLatrille/bayescode}, v1.3.1) to estimate the selection coefficients for each protein-coding gene in the mammalian dataset.
+We ran the MCMC algorithm implemented in BayesCode for $2,000$ generations as described in Latrille \textit{et al.}~\cite{latrille_genes_2023}.
+For each gene, after discarding a burn-in period of $1,000$ generations of MCMC, we obtained posterior mean estimates (over the $1,000$ generations left of MCMC) of the mutation rate matrix ($\bm{\mu}$) as well as the $20$ amino-acid fitness landscape ($\bm{F^{(i)}}$) at each site $i$.
+
+\subsection{Polymorphism dataset}
+\label{subsec:polymorphism-dataset}
+
+The genetic variants representing the population level polymorphisms were obtained from the following species and their available datasets: \textit{Equus caballus} (EquCab2 assembly in the EVA study PRJEB9799~\cite{alabri_whole_2020}), \textit{Bos taurus} (UMD3.1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}), \textit{Ovis aries} (Oar\_v3.1 assembly in the NextGen project), \textit{Capra hircus} (CHIR1 assembly in the NextGen project), converted to ARS1 assembly with dbSNP identifiers~\cite{sherry_dbsnp_2001}), \textit{Chlorocebus sabaeus} (ChlSab1.1 assembly in the EVA project PRJEB22989~\cite{svardal_ancient_2017}), \textit{Homo sapiens} (GRCh38 assembly in the 1000 Genomes Project~\cite{zheng-bradley_alignment_2017}).
+In total, we analyzed 28 populations across the 6 different species with polymorphism data.
+The data was processed as described in Latrille \textit{et al.}~\cite{latrille_genes_2023}.
+
+Only bi-allelic single nucleotide polymorphisms (SNPs) found within a gene were in our polymorphism dataset, while nonsense variants and indels were discarded.
+To construct the dataset, we first recovered the location of each SNP (represented by its chromosome, position, and strand) in the focal species and matched it to its corresponding position in the coding sequence (CDS) using gene annotation files (GTF format) downloaded from Ensembl (\url{ensembl.org}).
+We then verified that the SNP downloaded from Ensembl matched the reference in the CDS in FASTA format.
+Next, the position in the CDS was converted to the corresponding position in the multi-species sequence alignment (containing gaps) from the OrthoMaM database (see section~\ref{subsec:s-phylogeny-method}) for the corresponding gene by doing a global pairwise alignment (Biopython function pairwise2).
+This conversion from genomic position to alignment position was only possible when the assembly used for SNP-calling was the same as the one used in the OrthoMaM alignment, the GTF annotations, and the FASTA sequences.
+SNPs were polarized using the three closest outgroups found in the OrthoMaM alignment with est-usfs v2.04~\cite{keightley_inferring_2018}, and alleles with a probability of being derived lower than 0.99 were discarded.
+
+\subsection{Mutational opportunities}
+\label{subsec:nunber-of-sites}
+The mutational opportunities of any new mutation refer to its likelihood of falling into a specific category (synonymous, deleterious, nearly-neutral, or beneficial).
+Deriving such opportunities is necessary to estimate the strength of selection exerted at the population scale since different categories might have different mutational opportunities, and thus polymorphism and divergence need to be corrected accordingly (see sections~\ref{subsec:substitution-mapping-in-the-terminal-branch},~\ref{subsec:s-polymorphism-method}, and~\ref{subsec:precisison_recall}).
+To calculate mutational opportunities, we reconstructed the ancestral exome of each of the 28 populations by using the most likely ancestral state from est-usfs (see section~\ref{subsec:polymorphism-dataset}), which differs from the corresponding species reference exome since it accounts for the variability present in the specific population.
+
+From the reconstructed ancestral exome, all possible mutations were computed, weighted by the instantaneous rate of change between nucleotides obtained from the mutation rate matrix ($\bm{\mu}$, see section~\ref{subsec:s-phylogeny-method}), summing to $\mu_{\text{tot}}$ across the whole exome, and to $\mu_{\text{syn}}$ when restricted to synonymous mutations.
+Finally, the mutational opportunities for synonymous mutations were computed as the total number of sites across the exome ($L_{\text{tot}}$) weighted by the proportion of synonymous mutations among all possible mutations as:
+
+\begin{equation}
+L_{\text{syn}} = L_{\text{tot}} \frac{\mu_{\text{syn}}}{\mu_{\text{tot}}}.
+\end{equation}
+
+Similarly, for non-synonymous mutations, the total mutation rate for each class of selection $\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$, called $\mu\left( \Sphyclass \right)$, was estimated as the sum across all non-synonymous mutations if their selection coefficient at the phylogenetic scale is in the class $\Sphy \in \Sphyclass$.
+Accordingly, the mutational opportunities ($L \left( \Sphyclass \right)$) for each class of selection coefficient ($\Sphyclass$) was finally computed as the total number of sites across the exome ($L_{\text{tot}}$) weighted by the ratio of the aggregated mutations rates falling in the class $\mu\left( \Sphyclass \right)$:
+\begin{equation}
+L \left( \Sphyclass \right) = L_{\text{tot}} \frac{\mu\left( \Sphyclass \right)}{\mu_{\text{tot}}}.\label{eq:mutation-opp}
+\end{equation}
+
+Finally, $\proba [ \Sphyclass ]$ is the probability for a non-synonymous mutation to be in the class $\Sphyclass$, thus computed as:
+\begin{equation}
+\proba[\Sphyclass] = \frac{L\left( \Sphyclass \right)}{\sum_{\SphyclassAlt\in \{\SphyDel, \SphyNeu, \SphyBen \} } L\left(\SphyclassAlt \right)}.\label{eq:proba-dfe-mutsel}
+\end{equation}
+
+\subsection{Substitution mapping and \texorpdfstring{$\bm{\dnds}$}{dₙ/dₛ} in the terminal branch}
+\label{subsec:substitution-mapping-in-the-terminal-branch}
+We inferred the protein-coding DNA sequences for each node of the 4-taxa tree containing the focal species and the three closest outgroups species found in the OrthoMaM alignment by applying the M5 codon model (gamma site rate variation) as implemented in FastML.v3.11~\cite{ashkenazy_fastml_2012}.
+Consequently, for each focal species we reconstructed the protein coding DNA sequence of the whole exome at the base of the terminal branch before the split from the sister species.
+We considered \textit{Ceratotherium simum simum} as \textit{Equus caballus'} sister species; \textit{Bison bison bison} as \textit{Bos taurus'} sister species; \textit{Pantholops hodgsonii} as \textit{Ovis aries'} sister species; \textit{Pantholops hodgsonii} as \textit{Capra hircus'} sister species; \textit{Macaca mulatta} as \textit{Chlorocebus sabaeus'} sister species and finally, we considered \textit{Pan troglodytes} as \textit{Homo sapiens'} sister species.
+From this reconstructed exome, we determined the direction of the substitution occurring along the terminal branch of the phylogenetic tree toward each extant population.
+SNPs segregating in the population were discarded, and the most likely ancestral state from est-usfs (see section~\ref{subsec:polymorphism-dataset}) was used as the reference for each extant population.
+For each substitution, we recovered its $\Sphy$ value as calculated through the phylogeny-based method (see section~\ref{subsec:s-phylogeny-method}).
+Finally, the rate of non-synonymous over synonymous substitutions for a given class of selection coefficient ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$) was computed as:
+\begin{align}
+\begin{dcases}
+\dn \left( \Sphyclass \right) &= \dfrac{D\left( \Sphyclass \right)}{L \left( \Sphyclass \right)}, \\
+\ds &= \dfrac{D_{\text{syn}}}{L_{\text{syn}}},
+\end{dcases}\label{eq:dnds}
+\end{align}
+where $D \left( \Sphyclass \right) $ was the number of non-synonymous substitutions in class $\Sphyclass$, $D_{\text{syn}}$ was the number of synonymous substitutions across the exome, while $L \left( \Sphyclass \right)$ and $L_{\text{syn}}$ were the numbers of non-synonymous and synonymous mutational opportunities, respectively, as defined in section~\ref{subsec:nunber-of-sites}.
+$\delta(\dnds)$ was computed as the difference between $\dnds$ computed over all substitutions and $\dnds$ when we removed beneficial non-adaptive mutations $\dn (\Sphy < 1) / \ds$, normalized by $\dnds$.
+Note that the quantities $\delta(\dnds)$ and $\delta(\dn)$ are equivalent due to the simplification of the factor $\ds$:
+\begin{equation}
+\delta(\dnds) = \dfrac{\dnds - \dn(\Sphy < 1) / \ds}{\dnds} = \dfrac{\dn - \dn(\Sphy < 1)}{\dn} = \delta(\dn).\label{eq:delta-dnds}
+\end{equation}
+
+\subsection{Scaled selection coefficients (\texorpdfstring{$\bm{\Spop}$}{S}) in a population-based method}
+\label{subsec:s-polymorphism-method}
+
+To obtain a quantitative estimate of the distribution of selection coefficients for each category of SNPs, we used the \textit{polyDFE} model~\cite{tataru_inference_2017, tataru_polydfe_2020}.
+This model uses the count of derived alleles to infer the distribution of fitness effects (DFE).
+The probability of sampling an allele at a given frequency (before fixation or extinction) is informative of its scaled selection coefficient at the population scale ($\Spop$).
+Therefore, pooled across many sites, the site-frequency spectrum (SFS) provides information on the underlying $\Spop$ of mutations.
+However, estimating a single $\Spop$ for all sampled mutations is biologically unrealistic, and a DFE of mutations is usually assumed~\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009}.
+The \textit{polyDFE}\cite{tataru_inference_2017, tataru_polydfe_2020} software implements a mixture of a $\Gamma$ and exponential distributions to model the DFE of non-synonymous mutations, while synonymous mutations are considered neutral.
+The model estimates the parameters $\DelMean$, $b$, $p_b$ and $\AdvMean$ for non-synonymous mutations as:
+
+\begin{equation}
+\label{eq:parametric-dfe}
+\phi \left( \Spop; \DelMean , b, p_b, \AdvMean \right) =
+\begin{dcases}
+\left( 1 - p_b \right) f_{\Gamma}(-\Spop; -\DelMean, b) & \text{ if $\Spop \leq 0$,} \\
+p_b f_{e}(\Spop; \AdvMean) & \text{ if $\Spop > 0$,} \\
+\end{dcases}
+\end{equation}
+
+where $\DelMean \leq -1 $ is the estimated mean of the DFE for $\Spop \leq 0$;
+$b \geq 0.2$ is the estimated shape of the $\Gamma$ distribution;
+$0 \leq p_b \leq 1$ is the estimated probability that $\Spop > 0$;
+$\AdvMean \geq 1$ is the estimated mean of the DFE for $\Spop > 0$;
+and $f_{\Gamma}(\Spop; m, b)$ is the density of the $\Gamma$ distribution with mean $m$ and shape $b$, while $f_{e}(\Spop; m)$ is the density of the exponential distribution with mean $m$.
+
+\textit{PolyDFE} requires one SFS for non-synonymous mutations and one for synonymous mutations (neutral expectation), as well as the number of sites on which each SFS was sampled.
+For populations containing more than $8$ individuals, the SFS was subsampled down to $16$ chromosomes ($8$ diploid individuals) without replacement (hyper-geometric distribution) to alleviate the effect of different sampling depths in the 28 populations.
+Altogether, for each class of selection ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$) of non-synonymous SNPs, we aggregated all the SNPs in the selection class $\Sphyclass$ as an SFS.
+The number of sites on which each SFS was sampled is given by $L(\Sphyclass)$ for the non-synonymous SFS and $L_{\text{syn}}$ for the synonymous SFS respectively.
+For each class of selection $\Sphyclass$, once fitted to the data using maximum likelihood with \textit{polyDFE}, the parameters of the DFE $\left( \DelMean , b, p_b, \AdvMean \right)$ were used to compute $\proba [ \SpopDel \given  \Sphyclass] $, $\proba [ \SpopNeu \given \Sphyclass]$, and $\proba [ \SpopBen \given \Sphyclass]$ as:
+
+\begin{align}
+\proba [ \SpopDel \given  \Sphyclass] &= \proba [ \Spop < -1 \given \Sphyclass ] = \left( 1 - p_b \right) \int_{-\infty}^{-1} f_{\Gamma}(-\Spop; -\DelMean, b) \der \Spop, \label{eq:polyProbaDel} \\
+\proba [ \SpopNeu \given \Sphyclass] &= \proba [ -1 < \Spop < 1 \given \Sphyclass ] = \left( 1 - p_b \right) \int_{-1}^{0} f_{\Gamma}(-\Spop; -\DelMean, b) \der \Spop + p_b \int_{0}^{1} f_{e}(\Spop; \AdvMean) \der \Spop, \\
+\proba [ \SpopBen \given \Sphyclass] &= \proba [ \Spop > 1 \given \Sphyclass] = p_b \int_{1}^{+\infty} f_{e}(\Spop; \AdvMean) \der \Spop. \label{eq:polyProbaAdv}
+\end{align}
+
+Rather than relying solely on currently segregating mutations to quantify selection, \textit{polyDFE} can leverage both divergence and polymorphism to estimate the parameters of the DFE.
+We can thus add four more inputs to \textit{polyDFE}: $D \left( \Sphyclass \right) $, $L \left( \Sphyclass \right)$, $D_{\text{syn}}$ and $L_{\text{syn}}$ such as defined in the previous section.
+Because the estimates of DFE are different with this method, we naturally obtained different values of $\proba [ \SpopDel \given  \Sphyclass] $, $\proba [ \SpopNeu \given \Sphyclass]$, and $\proba [ \SpopBen \given \Sphyclass]$.
+
+\subsection{\textit{Precision} and \textit{recall}}
+\label{subsec:precisison_recall}
+For readability, we give here \textit{precision} and \textit{recall} for beneficial mutations ($\SphyBen$ and $\SpopBen$), but it can be obtained using the same derivation for the deleterious mutations ($\SphyDel$ and $\SpopDel$) and nearly-neutral mutations ($\SphyNeu$ and $\SpopNeu$).
+
+\textit{Precision} is the proportion of mutations correctly predicted as beneficial ($\proba [ \SpopBen \cap  \SphyBen]$) out of all predicted as beneficial non-adaptive mutations ($\proba [ \SphyBen]$), which can be written as a conditional probability:
+
+\begin{equation}
+\frac{\proba [ \SpopBen  \cap  \SphyBen]}{\proba [ \SphyBen]} = \proba [ \SpopBen \given \SphyBen].
+\label{eq:precision}
+\end{equation}
+Namely, \textit{precision} corresponds to the probability for a $\SphyBen$ mutation to be effectively beneficial at the population level ($\SpopBen$).
+This probability, computed from eq.~\ref{eq:polyProbaAdv}, is obtained by restricting our analysis to SNPs that are predicted to be beneficial non-adaptive mutations (yellow fill for the category $\SphyBen$ in Fig~\ref{fig:homo-afr-results}D).
+
+\textit{Recall} is the proportion of mutations correctly predicted as beneficial ($\proba [ \SpopBen \cap  \SphyBen]$) out of all beneficial mutations ($\proba [ \SpopBen]$), which can be written as a conditional probability:
+\begin{equation}
+\frac{\proba [ \SpopBen \cap  \SphyBen]}{\proba [ \SpopBen]} = \proba [ \SphyBen  \given \SpopBen ].
+\end{equation}
+Namely, \textit{recall} corresponds to the probability for a beneficial mutation at the population level ($\SpopBen$) to be a beneficial non-adaptive mutation ($\SphyBen$).
+Using Bayes theorem, \textit{recall} can be re-written as:
+\begin{equation}
+\proba [\SphyBen \given \SpopBen] = \frac{\proba [\SpopBen \given \SphyBen] \times \proba[\SphyBen]}{\ProbaPopBen},
+\label{eq:bayes}
+\end{equation}
+
+where $\proba [\SpopBen \given \SphyBen]$ and $\proba [ \SphyBen ]$ can be calculated using equations~\ref{eq:precision} and~\ref{eq:proba-dfe-mutsel}, respectively, and $\proba [ \SpopBen ]$ is the probability of a mutation to be beneficial at the level of the population, which can be computed from the law of total probabilities as:
+
+\begin{equation}
+\proba [ \SpopBen ] = \sum_{\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \} }\proba [\SpopBen \given \Sphyclass ] \times \proba [\Sphyclass ].
+\label{eq:total_proba}
+\end{equation}
+
+\subsection{Correlation with effective population size (\texorpdfstring{$\bm{\Ne}$}{Nₑ})}
+\label{subsec:correlation-diversity}
+Genetic diversity estimator Watterson's $\thetaSyn$ was obtained for each population from the synonymous SFS as in Achaz~\cite{achaz_frequency_2009}.
+For each popuation, $\Ne$ was estimated from the equation $\Ne=\thetaSyn / (4 \times u)$, where $u$ is the mutation rate per generation.
+Estimates for $u$ were averaged per species across the pedigree-based estimation in~\cite{bergeron_evolution_2023} for \textit{Homo}, \textit{Bos}, \textit{Capra} and \textit{Chlorocebus}.
+For \textit{Ovis} we used the estimated $u$ of \textit{Capra}.
+For \textit{Equus}, we used $u$ as estimated in Orlando \textit{et al.}~\cite{orlando_recalibrating_2013} ($u=7.24\times10^{-9}$).
+Because a correlation must account for phylogenetic relationship and non-independence of samples, we fitted a Phylogenetic Generalized Linear Model in \textit{R} with the method \texttt{pgls} with default settings from the package \texttt{caper}~\cite{orme_caper_2013}.
+The mammalian dated tree was obtained from TimeTree~\cite{kumar_timetree_2017} and pruned to include only the species analysed in this study, with multi-furcation of the different populations from each species placed at the same divergence time as the species (section S4.1).
+
+\section*{Data availability}
+The data underlying this article are available at \url{https://doi.org/10.5281/zenodo.7878953}.
+Snakemake pipeline, analysis scripts and documentation are available at \href{https://github.com/ThibaultLatrille/SelCoeff}{github.com/ThibaultLatrille/SelCoeff}.
+
+\section*{Acknowledgements}
+\label{sec:acknowledgment}
+We gratefully acknowledge the help of Mélodie Bastian, Nicolas Lartillot, Carina Farah Mugal, Laurent Duret, Alexandre Reymond, Daniele Silvestro and Nicolas Gambardella for their advice and reviews concerning this manuscript.
+This work was performed using the computing facilities of the CC LBBE/PRABI\@.
+This study makes use of data generated by the NextGen Consortium.
+Funding:
+Université de Lausanne; Agence Nationale de la Recherche, Grant ANR-19-CE12-0019 / HotRec.
+
+\section*{Competing interests}
+The authors declare no conflicts of interest.
+
+\section*{Author information}
+Original idea: T.L.\ and J.J.;
+Model conception: T.L., J.J.\ and N.S.;
+Code: T.L.;
+Data analyses: T.L.\ and J.J.;
+Interpretation: T.L., J.J., D.A.H.\ and N.S.;
+First draft: T.L.\ and J.J.;
+Editing and revisions: T.L., J.J., D.A.H.\ and N.S.
+Project management and funding: N.S\@.
+
+\newpage
+\section*{Supporting information}
+
+\paragraph*{S1 File.}
+\label{S1_File}
+{\bf Supplementary appendix.} Contains 43 pages of supplementary information: model parameterization, supplementary figures (S1 Fig to S21 Fig) and supplementary tables (S1 Table to S15 Table).
+
+\subsection*{List of Figures}
+\paragraph*{S1 Fig.}
+\label{S1_Fig}
+{\bf Bayesian hierarchical model.}
+
+\paragraph*{S2 Fig.}
+\label{S2_Fig}
+{\bf Examples of $\bm{\SphyBen}$ mutation sites in \textit{Chlorocebus sabaeus} (reversions).}
+
+\paragraph*{S3 Fig.}
+\label{S3_Fig}
+{\bf Examples of $\bm{\SphyBen}$ mutation sites in \textit{Chlorocebus sabaeus}.}
+
+\paragraph*{S4 Fig.}
+\label{S4_Fig}
+{\bf Enrichment in $\bm{\SphyBen}$ SNPs across all gene ontology terms.}
+
+\paragraph*{S5 Fig.}
+\label{S5_Fig}
+{\bf Estimation of selection at the population scale for $\bm{\SphyDel}$ mutations.}
+
+\paragraph*{S6 Fig.}
+\label{S6_Fig}
+{\bf Estimation of selection at the population scale for $\bm{\SphyNeu}$ mutations.}
+
+\paragraph*{S7 Fig.}
+\label{S7_Fig}
+{\bf Estimation of selection at the population scale for $\bm{\SphyBen}$ mutations.}
+
+\paragraph*{S8 Fig.}
+\label{S8_Fig}
+{\bf Distribution of scaled selection coefficients ($\bm{\Sphy}$).}
+
+\paragraph*{S9 Fig.}
+\label{S9_Fig}
+{\bf Tree used for PGLM (Phylogenetic Generalized Linear Model).}
+
+\paragraph*{S10 Fig.}
+\label{S10_Fig}
+{\bf Relationship between the proportion of deleterious mutations ($\bm{\SpopDel}$) and effective population size.}
+
+\paragraph*{S11 Fig.}
+\label{S11_Fig}
+{\bf Relationship between the proportion of deleterious mutations ($\bm{\SpopNeu}$) and effective population size.}
+
+\paragraph*{S12 Fig.}
+\label{S12_Fig}
+{\bf Relationship between the proportion of deleterious mutations ($\bm{\SpopBen}$) and effective population size.}
+
+\paragraph*{S13 Fig.}
+\label{S13_Fig}
+{\bf $\bm{\proba[\SphyBen\given \SpopBen ]}$ as a function of distance to the sister species.}
+
+\paragraph*{S14 Fig.}
+\label{S14_Fig}
+{\bf Ratio of $\bm{\proba[\Sphy]}$ over $\bm{\proba[-\Sphy]}$ for polymorphisms of the African population of \textit{Homo sapiens}.}
+
+\paragraph*{S15 Fig.}
+\label{S15_Fig}
+{\bf Proportion of non-adaptive mutations among beneficial ones ($\bm{\proba{[}\SphyBen\given \SpopBen {]}}$) estimated on synthetic site-frequency spectra.}
+
+\paragraph*{S16 Fig.}
+\label{S16_Fig}
+{\bf Site-frequency spectrum when masking CpG transitions.}
+
+\paragraph*{S17 Fig.}
+\label{S17_Fig}
+{\bf Including substitutions in the terminal lineage to estimate $\bm{\Spop}$.}
+
+\paragraph*{S18 Fig.}
+\label{S18_Fig}
+{\bf $\bm{\proba[\SphyBen\given \SpopBen ]}$ when including divergence to estimate $\bm{\Spop}$, as a function of distance to the sister species.}
+
+\paragraph*{S19 Fig.}
+\label{S19_Fig}
+{\bf $\bm{\proba [ \SpopDel ]}$ when fitting a single or three DFEs.}
+
+\paragraph*{S20 Fig.}
+\label{S20_Fig}
+{\bf $\bm{\proba [ \SpopNeu ]}$ when fitting a single or three DFEs.}
+
+\paragraph*{S21 Fig.}
+\label{S21_Fig}
+{\bf $\bm{\proba [ \SpopBen ]}$ when fitting a single or three DFEs.}
+
+\newpage
+\subsection*{List of Tables}
+\paragraph*{S1 Table.}
+\label{S1_Table}
+{\bf Probability of mutations and substitutions to be $\bm{\SphyDel}$, $\bm{\SphyNeu}$ or $\bm{\SphyBen}$.}
+
+\paragraph*{S2 Table.}
+\label{S2_Table}
+{\bf $\bm{\dnds}$ for $\bm{\SphyDel}$, $\bm{\SphyNeu}$ or $\bm{\SphyBen}$.}
+
+\paragraph*{S3 Table.}
+\label{S3_Table}
+{\bf $\bm{\dnds}$ over-estimation due to non-adaptive beneficial mutations.}
+
+\paragraph*{S4 Table.}
+\label{S4_Table}
+{\bf Gene ontology enrichment in $\bm{\SphyBen}$ SNPs.}
+
+\paragraph*{S5 Table.}
+\label{S5_Table}
+{\bf Terms associated with deleterious mutations $\bm{\SphyDel}$.}
+
+\paragraph*{S6 Table.}
+\label{S6_Table}
+{\bf Terms associated with non-adaptive beneficial mutations $\bm{\SphyBen}$.}
+
+\paragraph*{S7 Table.}
+\label{S7_Table}
+{\bf Probability for beneficial mutations to be non-adaptive ($\bm{\proba[\SphyBen\given \SpopBen ]}$).}
+
+\paragraph*{S8 Table.}
+\label{S8_Table}
+{\bf $\bm{\proba[\SphyBen\given \SpopBen ]}$ when masking CpG transitions.}
+
+\paragraph*{S9 Table.}
+\label{S9_Table}
+{\bf Precision and recall when masking CpG transitions.}
+
+\paragraph*{S10 Table.}
+\label{S10_Table}
+{\bf $\bm{\proba[\SphyBen\given \SpopBen ]}$ excluding or not genes under adaptation.}
+
+\paragraph*{S11 Table.}
+\label{S11_Table}
+{\bf $\bm{\proba[\SphyBen\given \SpopBen ]}$ when including divergence to estimate $\bm{\Spop}$.}
+
+\paragraph*{S12 Table.}
+\label{S12_Table}
+{\bf Precision and recall when including divergence to estimate $\bm{\Spop}$.}
+
+\paragraph*{S13 Table.}
+\label{S13_Table}
+{\bf $\bm{\proba[\SphyBen\given \SpopBen ]}$ excluding or not genes under adaptation, when including divergence to estimate $\bm{\Spop}$.}
+
+\paragraph*{S14 Table.}
+\label{S14_Table}
+{\bf $\bm{\proba[\SphyBen\given \SpopBen ]}$ when using a discrete DFE to estimate $\bm{\Spop}$.}
+
+\paragraph*{S15 Table.}
+\label{S15_Table}
+{\bf Precision and recall when using a discrete DFE to estimate $\bm{\Spop}$.}
+
+% Either type in your references using
+% \begin{thebibliography}{}
+% \bibitem{}
+% Text
+% \end{thebibliography}
+%
+% or
+%
+% Compile your BiBTeX database using our plos2015.bst
+% style file and paste the contents of your .bbl file
+% here. See http://journals.plos.org/plosone/s/latex for
+% step-by-step instructions.
+%
+\begin{thebibliography}{10}
+
+\bibitem{darwin_origin_1859}
+Darwin C.
+\newblock On the {{Origin}} of {{Species}} by {{Means}} of {{Natural
+Selection}}, or the {{Preservation}} of {{Favoured Races}} in the
+{{Struggle}} for {{Life}}. vol. 220.
+\newblock John Murray; 1859.
+
+\bibitem{merrell_adaptive_1994}
+Merrell DJ.
+\newblock The {{Adaptive Seascape}}: {{The Mechanism}} of {{Evolution}}.
+\newblock U of Minnesota Press; 1994.
+
+\bibitem{gavrilets_adaptive_2009}
+Gavrilets S, Losos JB.
+\newblock Adaptive {{Radiation}}: {{Contrasting Theory}} with {{Data}}.
+\newblock Science. 2009;323(5915):732--737.
+\newblock doi:{10.1126/science.1157966}.
+
+\bibitem{enard_viruses_2016}
+Enard D, Cai L, Gwennap C, Petrov DA.
+\newblock Viruses Are a Dominant Driver of Protein Adaptation in Mammals.
+\newblock eLife. 2016;5:e12469.
+\newblock doi:{10.7554/eLife.12469}.
+
+\bibitem{mcdonald_adaptative_1991}
+McDonald JH, Kreitman M.
+\newblock Adaptative Protein Evolution at {{Adh}} Locus in {{Drosophila}}.
+\newblock Nature. 1991;351(6328):652--654.
+\newblock doi:{10.1038/351652a0}.
+
+\bibitem{smith_adaptive_2002}
+Smith NGC, {Eyre-Walker} A.
+\newblock Adaptive Protein Evolution in {{Drosophila}}.
+\newblock Nature. 2002;415(6875):1022--1024.
+\newblock doi:{10.1038/4151022a}.
+
+\bibitem{welch_estimating_2006}
+Welch JJ.
+\newblock Estimating the {{Genomewide Rate}} of {{Adaptive Protein Evolution}}
+in {{Drosophila}}.
+\newblock Genetics. 2006;173(2):821--837.
+\newblock doi:{10.1534/genetics.106.056911}.
+
+\bibitem{yang_statistical_2000}
+Yang Z, Bielawski JR.
+\newblock Statistical Methods for Detecting Molecular Adaptation.
+\newblock Trends in Ecology and Evolution. 2000;15(12):496--503.
+\newblock doi:{10.1016/S0169-5347(00)01994-7}.
+
+\bibitem{eyre-walker_genomic_2006}
+{Eyre-Walker} A.
+\newblock The Genomic Rate of Adaptive Evolution.
+\newblock Trends in Ecology \& Evolution. 2006;21(10):569--575.
+\newblock doi:{10.1016/j.tree.2006.06.015}.
+
+\bibitem{moutinho_variation_2019}
+Moutinho AF, Bataillon T, Dutheil JY.
+\newblock Variation of the Adaptive Substitution Rate between Species and
+within Genomes.
+\newblock Evolutionary Ecology. 2019;34(3):315--338.
+\newblock doi:{10.1007/s10682-019-10026-z}.
+
+\bibitem{lynch_mutation_2023}
+Lynch M.
+\newblock Mutation Pressure, Drift, and the Pace of Molecular Coevolution.
+\newblock Proceedings of the National Academy of Sciences.
+2023;120(27):e2306741120.
+\newblock doi:{10.1073/pnas.2306741120}.
+
+\bibitem{charlesworth_other_2007}
+Charlesworth J, {Eyre-Walker} A.
+\newblock The Other Side of the Nearly Neutral Theory, Evidence of Slightly
+Advantageous Back-Mutations.
+\newblock Proceedings of the National Academy of Sciences.
+2007;104(43):16992--16997.
+\newblock doi:{10.1073/pnas.0705456104}.
+
+\bibitem{mustonen_fitness_2009}
+Mustonen V, L{\"a}ssig M.
+\newblock From Fitness Landscapes to Seascapes: Non-Equilibrium Dynamics of
+Selection and Adaptation.
+\newblock Trends in genetics. 2009;25(3):111--119.
+\newblock doi:{10.1016/j.tig.2009.01.002}.
+
+\bibitem{jones_shifting_2017}
+Jones CT, Youssef N, Susko E, Bielawski JP.
+\newblock Shifting Balance on a Static Mutation--Selection Landscape: A Novel
+Scenario of Positive Selection.
+\newblock Molecular Biology and Evolution. 2017;34(2):391--407.
+\newblock doi:{10.1093/molbev/msw237}.
+
+\bibitem{ohta_nearly_1992}
+Ohta T.
+\newblock The Nearly Neutral Theory of Molecular Evolution.
+\newblock Annual Review of Ecology and Systematics. 1992;23(1992):263--286.
+
+\bibitem{gillespie_ohta_1995}
+Gillespie JH.
+\newblock On {{Ohta}}'s Hypothesis: {{Most}} Amino Acid Substitutions Are
+Deleterious.
+\newblock Journal of Molecular Evolution. 1995;40(1):64--69.
+\newblock doi:{10.1007/BF00166596}.
+
+\bibitem{hartl_compensatory_1996}
+Hartl DL, Taubes CH.
+\newblock Compensatory Nearly Neutral Mutations: {{Selection}} without
+Adaptation.
+\newblock Journal of Theoretical Biology. 1996;182(3):303--309.
+\newblock doi:{10.1006/jtbi.1996.0168}.
+
+\bibitem{sella_application_2005}
+Sella G, Hirsh AE.
+\newblock The Application of Statistical Physics to Evolutionary Biology.
+\newblock Proceedings of the National Academy of Sciences of the United States
+of America. 2005;102(27):9541--9546.
+\newblock doi:{10.1073/pnas.0501865102}.
+
+\bibitem{cvijovic_fate_2015}
+Cvijovi{\'c} I, Good BH, Jerison ER, Desai MM.
+\newblock Fate of a Mutation in a Fluctuating Environment.
+\newblock Proceedings of the National Academy of Sciences.
+2015;112(36):E5021--E5028.
+\newblock doi:{10.1073/pnas.1505406112}.
+
+\bibitem{piganeau_estimating_2003}
+Piganeau G, {Eyre-Walker} A.
+\newblock Estimating the Distribution of Fitness Effects from {{DNA}} Sequence
+Data: {{Implications}} for the Molecular Clock.
+\newblock Proceedings of the National Academy of Sciences of the United States
+of America. 2003;100(18):10335--10340.
+\newblock doi:{10.1073/pnas.1833064100}.
+
+\bibitem{chi_detecting_2020}
+Chi PB, Kosater WM, Liberles DA.
+\newblock Detecting {{Signatures}} of {{Positive Selection}} against a
+{{Backdrop}} of {{Compensatory Processes}}.
+\newblock Molecular Biology and Evolution. 2020;37(11):3353--3362.
+\newblock doi:{10.1093/molbev/msaa161}.
+
+\bibitem{bazykin_changing_2015}
+Bazykin GA.
+\newblock Changing Preferences: Deformation of Single Position Amino Acid
+Fitness Landscapes and Evolution of Proteins.
+\newblock Biology letters. 2015;11(10):20150315.
+\newblock doi:{10.1098/rsbl.2015.0315}.
+
+\bibitem{moses_inferring_2009}
+Moses AM, Durbin R.
+\newblock Inferring {{Selection}} on {{Amino Acid Preference}} in {{Protein
+Domains}}.
+\newblock Molecular Biology and Evolution. 2009;26(3):527--536.
+\newblock doi:{10.1093/molbev/msn286}.
+
+\bibitem{fischer_germline_2011}
+Fischer A, Greenman C, Mustonen V.
+\newblock Germline {{Fitness-Based Scoring}} of {{Cancer Mutations}}.
+\newblock Genetics. 2011;188(2):383--393.
+\newblock doi:{10.1534/genetics.111.127480}.
+
+\bibitem{chen_hunting_2021}
+Chen J, Bataillon T, Gl{\'e}min S, Lascoux M.
+\newblock Hunting for Beneficial Mutations: Conditioning on {{SIFT}} Scores
+When Estimating the Distribution of Fitness Effect of New Mutations.
+\newblock Genome Biology and Evolution. 2021;doi:{10.1093/gbe/evab151}.
+
+\bibitem{halpern_evolutionary_1998}
+Halpern AL, Bruno WJ.
+\newblock Evolutionary Distances for Protein-Coding Sequences: Modeling
+Site-Specific Residue Frequencies.
+\newblock Molecular Biology and Evolution. 1998;15(7):910--917.
+\newblock doi:{10.1093/oxfordjournals.molbev.a025995}.
+
+\bibitem{mccandlish_modeling_2014}
+McCandlish DM, Stoltzfus A.
+\newblock Modeling Evolution Using the Probability of Fixation: {{History}} and
+Implications.
+\newblock Quarterly Review of Biology. 2014;89(3):225--252.
+\newblock doi:{10.1086/677571}.
+
+\bibitem{rodrigue_mechanistic_2010}
+Rodrigue N, Philippe H.
+\newblock Mechanistic Revisions of Phenomenological Modeling Strategies in
+Molecular Evolution.
+\newblock Trends in Genetics. 2010;26(6):248--252.
+\newblock doi:{10.1016/j.tig.2010.04.001}.
+
+\bibitem{tamuri_estimating_2012}
+Tamuri AU, Goldstein RA.
+\newblock Estimating the Distribution of Selection Coefficients from
+Phylogenetic Data Using Sitewise Mutation-Selection Models.
+\newblock Genetics. 2012;190(3):1101--1115.
+\newblock doi:{10.1534/genetics.111.136432}.
+
+\bibitem{rodrigue_detecting_2017}
+Rodrigue N, Lartillot N.
+\newblock Detecting Adaptation in Protein-Coding Genes Using a {{Bayesian}}
+Site- Heterogeneous Mutation-Selection Codon Substitution Model.
+\newblock Molecular Biology and Evolution. 2017;34(1):204--214.
+\newblock doi:{10.1093/molbev/msw220}.
+
+\bibitem{foley_genomic_2023}
+Foley NM, Mason VC, Harris AJ, Bredemeyer KR, Damas J, Lewin HA, et~al.
+\newblock A Genomic Timescale for Placental Mammal Evolution.
+\newblock Science. 2023;380(6643):eabl8189.
+\newblock doi:{10.1126/science.abl8189}.
+
+\bibitem{howe_ensembl_2021}
+Howe KL, Achuthan P, Allen J, Allen J, {Alvarez-Jarreta} J, Amode MR, et~al.
+\newblock Ensembl 2021.
+\newblock Nucleic Acids Research. 2021;49(D1):D884--D891.
+\newblock doi:{10.1093/nar/gkaa942}.
+
+\bibitem{ranwez_orthomam_2007}
+Ranwez V, Delsuc F, Ranwez S, Belkhir K, Tilak MK, Douzery EJ.
+\newblock {{OrthoMaM}}: {{A}} Database of Orthologous Genomic Markers for
+Placental Mammal Phylogenetics.
+\newblock BMC Evolutionary Biology. 2007;7(1):1--12.
+\newblock doi:{10.1186/1471-2148-7-241}.
+
+\bibitem{scornavacca_orthomam_2019}
+Scornavacca C, Belkhir K, Lopez J, Dernat R, Delsuc F, Douzery EJP, et~al.
+\newblock {{OrthoMaM}} V10: {{Scaling-up}} Orthologous Coding Sequence and Exon
+Alignments with More than One Hundred Mammalian Genomes.
+\newblock Molecular Biology and Evolution. 2019;36(4):861--862.
+\newblock doi:{10.1093/molbev/msz015}.
+
+\bibitem{rodrigue_mutationselection_2010}
+Rodrigue N, Philippe H, Lartillot N.
+\newblock Mutation-Selection Models of Coding Sequence Evolution with
+Site-Heterogeneous Amino Acid Fitness Profiles.
+\newblock Proceedings of the National Academy of Sciences of the United States
+of America. 2010;107(10):4629--34.
+\newblock doi:{10.1073/pnas.0910915107}.
+
+\bibitem{landrum_clinvar_2018}
+Landrum MJ, Lee JM, Benson M, Brown GR, Chao C, Chitipiralla S, et~al.
+\newblock {{ClinVar}}: Improving Access to Variant Interpretations and
+Supporting Evidence.
+\newblock Nucleic Acids Research. 2018;46(D1):D1062--D1067.
+\newblock doi:{10.1093/nar/gkx1153}.
+
+\bibitem{grimm_evaluation_2015}
+Grimm DG, Azencott CA, Aicheler F, Gieraths U, MacArthur DG, Samocha KE, et~al.
+\newblock The {{Evaluation}} of {{Tools Used}} to {{Predict}} the {{Impact}} of
+{{Missense Variants Is Hindered}} by {{Two Types}} of {{Circularity}}.
+\newblock Human Mutation. 2015;36(5):513--523.
+\newblock doi:{10.1002/humu.22768}.
+
+\bibitem{sullivan_leveraging_2023}
+Sullivan PF, Meadows JRS, Gazal S, Phan BN, Li X, Genereux DP, et~al.
+\newblock Leveraging Base-Pair Mammalian Constraint to Understand Genetic
+Variation and Human Disease.
+\newblock Science. 2023;380(6643):eabn2937.
+\newblock doi:{10.1126/science.abn2937}.
+
+\bibitem{eyre-walker_distribution_2006}
+{Eyre-Walker} A, Woolfit M, Phelps T.
+\newblock The Distribution of Fitness Effects of New Deleterious Amino Acid
+Mutations in Humans.
+\newblock Genetics. 2006;173(2):891--900.
+\newblock doi:{10.1534/genetics.106.057570}.
+
+\bibitem{eyre-walker_estimating_2009}
+{Eyre-Walker} A, Keightley PD.
+\newblock Estimating the {{Rate}} of {{Adaptive Molecular Evolution}} in the
+{{Presence}} of {{Slightly Deleterious Mutations}} and {{Population Size
+Change}}.
+\newblock Molecular Biology and Evolution. 2009;26(9):2097--2108.
+\newblock doi:{10.1093/molbev/msp119}.
+
+\bibitem{galtier_adaptive_2016}
+Galtier N.
+\newblock Adaptive Protein Evolution in Animals and the Effective Population
+Size Hypothesis.
+\newblock PLoS Genetics. 2016;12(1):e1005774.
+\newblock doi:{10.1371/journal.pgen.1005774}.
+
+\bibitem{tataru_inference_2017}
+Tataru P, Mollion M, Gl{\'e}min S, Bataillon T.
+\newblock Inference of Distribution of Fitness Effects and Proportion of
+Adaptive Substitutions from Polymorphism Data.
+\newblock Genetics. 2017;207(3):1103--1119.
+\newblock doi:{10.1534/genetics.117.300323}.
+
+\bibitem{bergeron_evolution_2023}
+Bergeron LA, Besenbacher S, Zheng J, Li P, Bertelsen MF, Quintard B, et~al.
+\newblock Evolution of the Germline Mutation Rate across Vertebrates.
+\newblock Nature. 2023; p. 1--7.
+\newblock doi:{10.1038/s41586-023-05752-y}.
+
+\bibitem{orlando_recalibrating_2013}
+Orlando L, Ginolhac A, Zhang G, Froese D, Albrechtsen A, Stiller M, et~al.
+\newblock Recalibrating {{Equus}} Evolution Using the Genome Sequence of an
+Early {{Middle Pleistocene}} Horse.
+\newblock Nature. 2013;499(7456):74--78.
+\newblock doi:{10.1038/nature12323}.
+
+\bibitem{achaz_frequency_2009}
+Achaz G.
+\newblock Frequency {{Spectrum Neutrality Tests}}: {{One}} for {{All}} and
+{{All}} for {{One}}.
+\newblock Genetics. 2009;183(1):249--258.
+\newblock doi:{10.1534/genetics.109.104042}.
+
+\bibitem{latrille_genes_2023}
+Latrille T, Rodrigue N, Lartillot N.
+\newblock Genes and Sites under Adaptation at the Phylogenetic Scale Also
+Exhibit Adaptation at the Population-Genetic Scale.
+\newblock Proceedings of the National Academy of Sciences of the United States
+of America. 2023;120(11):e2214977120.
+\newblock doi:{10.1073/pnas.2214977120}.
+
+\bibitem{ng_sift_2003}
+Ng PC, Henikoff S.
+\newblock {{SIFT}}: Predicting Amino Acid Changes That Affect Protein Function.
+\newblock Nucleic Acids Research. 2003;31(13):3812--3814.
+\newblock doi:{10.1093/nar/gkg509}.
+
+\bibitem{vaser_sift_2016}
+Vaser R, Adusumalli S, Leng SN, Sikic M, Ng PC.
+\newblock {{SIFT}} Missense Predictions for Genomes.
+\newblock Nature Protocols. 2016;11(1):1--9.
+\newblock doi:{10.1038/nprot.2015.123}.
+
+\bibitem{keightley_what_2010}
+Keightley PD, {Eyre-Walker} A.
+\newblock What Can We Learn about the Distribution of Fitness Effects of New
+Mutations from {{DNA}} Sequence Data?
+\newblock Philosophical Transactions of the Royal Society B: Biological
+Sciences. 2010;365(1544):1187--1193.
+\newblock doi:{10.1098/rstb.2009.0266}.
+
+\bibitem{rice_evolutionarily_2015}
+Rice DP, Good BH, Desai MM.
+\newblock The {{Evolutionarily Stable Distribution}} of {{Fitness Effects}}.
+\newblock Genetics. 2015;200(1):321--329.
+\newblock doi:{10.1534/genetics.114.173815}.
+
+\bibitem{mustonen_fitness_2010}
+Mustonen V, L{\"a}ssig M.
+\newblock Fitness Flux and Ubiquity of Adaptive Evolution.
+\newblock Proceedings of the National Academy of Sciences.
+2010;107(9):4248--4253.
+\newblock doi:{10.1073/pnas.0907953107}.
+
+\bibitem{eyre-walker_how_2014}
+{Eyre-Walker} A, {Eyre-Walker} YC.
+\newblock How Much of the Variation in the Mutation Rate along the Human Genome
+Can Be Explained?
+\newblock G3: Genes, Genomes, Genetics. 2014;4(9):1667--1670.
+\newblock doi:{10.1534/g3.114.012849}.
+
+\bibitem{mustonen_molecular_2008}
+Mustonen V, L{\"a}ssig M.
+\newblock Molecular {{Evolution}} under {{Fitness Fluctuations}}.
+\newblock Physical Review Letters. 2008;100(10):108101.
+\newblock doi:{10.1103/PhysRevLett.100.108101}.
+
+\bibitem{latrille_inferring_2021}
+Latrille T, Lanore V, Lartillot N.
+\newblock Inferring Long-Term Effective Population Size with
+Mutation--Selection Models.
+\newblock Molecular Biology and Evolution. 2021;38(10):4573--4587.
+\newblock doi:{10.1093/molbev/msab160}.
+
+\bibitem{huber_determining_2017}
+Huber CD, Kim BY, Marsden CD, Lohmueller KE.
+\newblock Determining the Factors Driving Selective Effects of New
+Nonsynonymous Mutations.
+\newblock Proceedings of the National Academy of Sciences.
+2017;114(17):4465--4470.
+\newblock doi:{10.1073/pnas.1619508114}.
+
+\bibitem{lanfear_population_2014}
+Lanfear R, Kokko H, {Eyre-Walker} A.
+\newblock Population Size and the Rate of Evolution.
+\newblock Trends in Ecology and Evolution. 2014;29(1):33--41.
+\newblock doi:{10.1016/j.tree.2013.09.009}.
+
+\bibitem{platt_protein_2018}
+Platt A, Weber CC, Liberles DA.
+\newblock Protein Evolution Depends on Multiple Distinct Population Size
+Parameters.
+\newblock BMC Evolutionary Biology. 2018;18(1):1--9.
+\newblock doi:{10.1186/s12862-017-1085-x}.
+
+\bibitem{starr_epistasis_2016}
+Starr TN, Thornton JW.
+\newblock Epistasis in Protein Evolution.
+\newblock Protein Science. 2016;25(7):1204--1218.
+\newblock doi:{10.1002/pro.2897}.
+
+\bibitem{morcos_directcoupling_2011}
+Morcos F, Pagnani A, Lunt B, Bertolino A, Marks DS, Sander C, et~al.
+\newblock Direct-Coupling Analysis of Residue Coevolution Captures Native
+Contacts across Many Protein Families.
+\newblock Proceedings of the National Academy of Sciences.
+2011;108(49):E1293--E1301.
+\newblock doi:{10.1073/pnas.1111471108}.
+
+\bibitem{marks_protein_2012}
+Marks DS, Hopf TA, Sander C.
+\newblock Protein Structure Prediction from Sequence Variation.
+\newblock Nature Biotechnology. 2012;30(11):1072--1080.
+\newblock doi:{10.1038/nbt.2419}.
+
+\bibitem{goldstein_nonadaptive_2015}
+Goldstein RA, Pollard ST, Shah SD, Pollock DD.
+\newblock Nonadaptive {{Amino Acid Convergence Rates Decrease}} over {{Time}}.
+\newblock Molecular Biology and Evolution. 2015;32(6):1373--1381.
+\newblock doi:{10.1093/molbev/msv041}.
+
+\bibitem{goldstein_sequence_2017}
+Goldstein RA, Pollock DD.
+\newblock Sequence Entropy of Folding and the Absolute Rate of Amino Acid
+Substitutions.
+\newblock Nature Ecology \& Evolution. 2017;1(12):1923--1930.
+\newblock doi:{10.1038/s41559-017-0338-9}.
+
+\bibitem{park_epistatic_2022}
+Park Y, Metzger BPH, Thornton JW.
+\newblock Epistatic Drift Causes Gradual Decay of Predictability in Protein
+Evolution.
+\newblock Science. 2022;376(6595):823--830.
+\newblock doi:{10.1126/science.abn6895}.
+
+\bibitem{ashenberg_mutational_2013}
+Ashenberg O, Gong LI, Bloom JD.
+\newblock Mutational Effects on Stability Are Largely Conserved during Protein
+Evolution.
+\newblock Proceedings of the National Academy of Sciences of the United States
+of America. 2013;110(52):21071--21076.
+\newblock doi:{10.1073/pnas.1314781111}.
+
+\bibitem{doud_sitespecific_2015}
+Doud MB, Ashenberg O, Bloom JD.
+\newblock Site-{{Specific Amino Acid Preferences Are Mostly Conserved}} in
+{{Two Closely Related Protein Homologs}}.
+\newblock Molecular Biology and Evolution. 2015;32(11):2944--2960.
+\newblock doi:{10.1093/molbev/msv167}.
+
+\bibitem{bloom_identification_2017}
+Bloom JD.
+\newblock Identification of Positive Selection in Genes Is Greatly Improved by
+Using Experimentally Informed Site-Specific Models.
+\newblock Biology Direct. 2017;12(1):1--24.
+\newblock doi:{10.1186/s13062-016-0172-z}.
+
+\bibitem{youssef_consequences_2020}
+Youssef N, Susko E, Bielawski JP.
+\newblock Consequences of Stability-Induced Epistasis for Substitution Rates.
+\newblock Molecular Biology and Evolution. 2020;doi:{10.1093/molbev/msaa151}.
+
+\bibitem{vigue_deciphering_2022}
+Vigu{\'e} L, Croce G, Petitjean M, Rupp{\'e} E, Tenaillon O, Weigt M.
+\newblock Deciphering Polymorphism in 61,157 {{Escherichia}} Coli Genomes via
+Epistatic Sequence Landscapes.
+\newblock Nature Communications. 2022;13(1):4030.
+\newblock doi:{10.1038/s41467-022-31643-3}.
+
+\bibitem{kimura_evolutionary_1968}
+Kimura M.
+\newblock Evolutionary Rate at the Molecular Level.
+\newblock Nature. 1968;217(5129):624--626.
+
+\bibitem{gillespie_substitution_1994}
+Gillespie JH.
+\newblock Substitution Processes in Molecular Evolution. {{III}}.
+{{Deleterious}} Alleles.
+\newblock Genetics. 1994;138(3):943--952.
+\newblock doi:{10.1093/genetics/138.3.943}.
+
+\bibitem{jensen_importance_2019}
+Jensen JD, Payseur BA, Stephan W, Aquadro CF, Lynch M, Charlesworth D, et~al.
+\newblock The Importance of the {{Neutral Theory}} in 1968 and 50 Years on:
+{{A}} Response to {{Kern}} and {{Hahn}} 2018.
+\newblock Evolution. 2019;73(1):111--114.
+\newblock doi:{10.1111/evo.13650}.
+
+\bibitem{galtier_half_2024}
+Galtier N.
+\newblock Half a {{Century}} of {{Controversy}}: {{The
+Neutralist}}/{{Selectionist Debate}} in {{Molecular Evolution}}.
+\newblock Genome Biology and Evolution. 2024;16(2):evae003.
+\newblock doi:{10.1093/gbe/evae003}.
+
+\bibitem{galtier_adaptation_2007}
+Galtier N, Duret L.
+\newblock Adaptation or Biased Gene Conversion? {{Extending}} the Null
+Hypothesis of Molecular Evolution.
+\newblock Trends in Genetics. 2007;23(6):273--277.
+\newblock doi:{10.1016/j.tig.2007.03.011}.
+
+\bibitem{rousselle_influence_2019}
+Rousselle M, Laverr{\'e} A, Figuet E, Nabholz B, Galtier N.
+\newblock Influence of {{Recombination}} and {{GC-biased Gene Conversion}} on
+the {{Adaptive}} and {{Nonadaptive Substitution Rate}} in {{Mammals}} versus
+{{Birds}}.
+\newblock Molecular Biology and Evolution. 2019;36(3):458--471.
+\newblock doi:{10.1093/molbev/msy243}.
+
+\bibitem{joseph_increased_2024a}
+Joseph J.
+\newblock Increased {{Positive Selection}} in {{Highly Recombining Genes Does}}
+Not {{Necessarily Reflect}} an {{Evolutionary Advantage}} of
+{{Recombination}}.
+\newblock Molecular Biology and Evolution. 2024; p. msae107.
+\newblock doi:{10.1093/molbev/msae107}.
+
+\bibitem{ohta_development_1996}
+Ohta T, Gillespie JH.
+\newblock Development of {{Neutral}} and {{Nearly Neutral Theories}}.
+\newblock Theoretical Population Biology. 1996;49(2):128--142.
+\newblock doi:{10.1006/tpbi.1996.0007}.
+
+\bibitem{spielman_relationship_2015}
+Spielman SJ, Wilke CO.
+\newblock The Relationship between {{dN}}/{{dS}} and Scaled Selection
+Coefficients.
+\newblock Molecular biology and evolution. 2015;32(4):1097--1108.
+\newblock doi:{10.1093/molbev/msv003}.
+
+\bibitem{dosreis_how_2015}
+Dos~Reis M.
+\newblock How to Calculate the Non-Synonymous to Synonymous Rate Ratio of
+Protein-Coding Genes under the Fisher-Wright Mutation-Selection Framework.
+\newblock Biology Letters. 2015;11(4):20141031.
+\newblock doi:{10.1098/rsbl.2014.1031}.
+
+\bibitem{rodrigue_bayesian_2021}
+Rodrigue N, Latrille T, Lartillot N.
+\newblock A {{Bayesian}} Mutation-Selection Framework for Detecting
+Site-Specific Adaptive Evolution in Protein-Coding Genes.
+\newblock Molecular Biology and Evolution. 2021;38(3):1199--1208.
+\newblock doi:{10.1093/molbev/msaa265}.
+
+\bibitem{tamuri_mutationselection_2021}
+Tamuri AU, {dos Reis} M.
+\newblock A Mutation-Selection Model of Protein Evolution under Persistent
+Positive Selection.
+\newblock Molecular Biology and Evolution. 2021;doi:{10.1093/molbev/msab309}.
+
+\bibitem{kazmi_detecting_2019}
+Kazmi SO, Rodrigue N.
+\newblock Detecting Amino Acid Preference Shifts with Codon-Level
+Mutation-Selection Mixture Models.
+\newblock BMC Evolutionary Biology. 2019;19(1):62.
+\newblock doi:{10.1186/s12862-019-1358-7}.
+
+\bibitem{stolyarova_senescence_2020}
+Stolyarova AV, Nabieva E, Ptushenko VV, Favorov AV, Popova AV, Neverov AD,
+et~al.
+\newblock Senescence and Entrenchment in Evolution of Amino Acid Sites.
+\newblock Nature Communications. 2020;11(1):4603.
+\newblock doi:{10.1038/s41467-020-18366-z}.
+
+\bibitem{douzery_orthomam_2014}
+Douzery EJP, Scornavacca C, Romiguier J, Belkhir K, Galtier N, Delsuc F, et~al.
+\newblock {{OrthoMaM}} v8: {{A}} Database of Orthologous Exons and Coding
+Sequences for Comparative Genomics in Mammals.
+\newblock Molecular Biology and Evolution. 2014;31(7):1923--1928.
+\newblock doi:{10.1093/molbev/msu132}.
+
+\bibitem{yang_mutationselection_2008}
+Yang Z, Nielsen R.
+\newblock Mutation-Selection Models of Codon Substitution and Their Use to
+Estimate Selective Strengths on Codon Usage.
+\newblock Molecular Biology and Evolution. 2008;25(3):568--579.
+\newblock doi:{10.1093/molbev/msm284}.
+
+\bibitem{wright_evolution_1931}
+Wright S.
+\newblock Evolution in {{Mendelian}} Populations.
+\newblock Genetics. 1931;16(2):97--159.
+\newblock doi:{10.1093/genetics/16.2.97}.
+
+\bibitem{fisher_genetical_1930}
+Fisher RA.
+\newblock The {{Genetical Theory}} of {{Natural Selection}}.
+\newblock The Clarendon Press; 1930.
+
+\bibitem{rodrigue_bayesian_2008}
+Rodrigue N, Lartillot N, Philippe H.
+\newblock Bayesian Comparisons of Codon Substitution Models.
+\newblock Genetics. 2008;180(3):1579--1591.
+\newblock doi:{10.1534/genetics.108.092254}.
+
+\bibitem{lartillot_bayesian_2004}
+Lartillot N.
+\newblock A Bayesian Mixture Model for Across-Site Heterogeneities in the
+Amino-Acid Replacement Process.
+\newblock Molecular biology and evolution. 2004;21(6):1095--1109.
+\newblock doi:{10.1093/molbev/msh112}.
+
+\bibitem{lartillot_inference_2013}
+Lartillot N.
+\newblock Inf{\'e}rence Probabiliste Pour La Phylog{\'e}nie, La G{\'e}nomique
+Comparative et Les Sciences de La Macro-{\'E}volution; 2013.
+
+\bibitem{alabri_whole_2020}
+Al~Abri MA, Holl HM, Kalla SE, Sutter NB, Brooks SA.
+\newblock Whole Genome Detection of Sequence and Structural Polymorphism in Six
+Diverse Horses.
+\newblock PLoS ONE. 2020;15(4):e0230899.
+\newblock doi:{10.1371/journal.pone.0230899}.
+
+\bibitem{sherry_dbsnp_2001}
+Sherry ST, Ward MH, Kholodov M, Baker J, Phan L, Smigielski EM, et~al.
+\newblock {{dbSNP}}: The {{NCBI}} Database of Genetic Variation.
+\newblock Nucleic Acids Research. 2001;29(1):308--311.
+\newblock doi:{10.1093/nar/29.1.308}.
+
+\bibitem{svardal_ancient_2017}
+Svardal H, Jasinska AJ, Apetrei C, Coppola G, Huang Y, Schmitt CA, et~al.
+\newblock Ancient Hybridization and Strong Adaptation to Viruses across
+{{African}} Vervet Monkey Populations.
+\newblock Nature Genetics. 2017;49(12):1705--1713.
+\newblock doi:{10.1038/ng.3980}.
+
+\bibitem{zheng-bradley_alignment_2017}
+{Zheng-Bradley} X, Streeter I, Fairley S, Richardson D, Clarke L, Flicek P,
+et~al.
+\newblock Alignment of 1000 {{Genomes Project}} Reads to Reference Assembly
+{{GRCh38}}.
+\newblock GigaScience. 2017;6(7):gix038.
+\newblock doi:{10.1093/gigascience/gix038}.
+
+\bibitem{keightley_inferring_2018}
+Keightley PD, Jackson BC.
+\newblock Inferring the Probability of the Derived vs the Ancestral Allelic
+State at a Polymorphic Site.
+\newblock Genetics. 2018;209(3):897--906.
+\newblock doi:{10.1534/genetics.118.301120}.
+
+\bibitem{ashkenazy_fastml_2012}
+Ashkenazy H, Penn O, {Doron-Faigenboim} A, Cohen O, Cannarozzi G, Zomer O,
+et~al.
+\newblock {{FastML}}: A Web Server for Probabilistic Reconstruction of
+Ancestral Sequences.
+\newblock Nucleic Acids Research. 2012;40(W1):W580--W584.
+\newblock doi:{10.1093/nar/gks498}.
+
+\bibitem{tataru_polydfe_2020}
+Tataru P, Bataillon T.
+\newblock {{polyDFE}}: {{Inferring}} the Distribution of Fitness Effects and
+Properties of Beneficial Mutations from Polymorphism Data.
+\newblock In: Methods in {{Molecular Biology}}. vol. 2090. Humana Press Inc.;
+2020. p. 125--146.
+
+\bibitem{orme_caper_2013}
+Orme D, Freckleton R, Thomas G, Petzoldt T, Fritz S, Isaac N, et~al.
+\newblock The Caper Package: Comparative Analysis of Phylogenetics and
+Evolution in {{R}}.
+\newblock R package version. 2013;5(2):1--36.
+
+\bibitem{kumar_timetree_2017}
+Kumar S, Stecher G, Suleski M, Hedges SB.
+\newblock {{TimeTree}}: A Resource for Timelines, Timetrees, and Divergence
+Times.
+\newblock Molecular Biology and Evolution. 2017;34(7):1812--1819.
+\newblock doi:{10.1093/molbev/msx116}.
+
+\end{thebibliography}
+
 \end{document}

### 2024-12-05 manuscript/main-PLOS-revision-plos2015.tex
Revision PLOS Genetics round 2

--- 2024-12-05 manuscript/main-PLOS-revision-bbl.tex
@@
 However, a collateral effect has been conflating beneficial mutations with adaptive evolution when adaptive evolution is not the only process that can lead to beneficial mutations~\cite{charlesworth_other_2007, mustonen_fitness_2009, jones_shifting_2017}.
+
+\begin{figure}[!htb]
+\centering
+\includegraphics[width=\textwidth, page=1] {figure1.eps}
+\caption{
+(A \& B) For a given codon position of a protein-coding DNA sequence, amino acids (x-axis) have different fitness values (y-axis).
+Under a changing fitness landscape (A), these fitnesses fluctuate with time.
+The protein sequence follows the moving target defined by the amino-acid fitnesses.
+Since substitutions are preferentially accepted if they are in the direction of this target, substitutions are, on average, adaptive.
+At the phylogenetic scale (C), beneficial substitutions are common (positive signs), promoting phenotype diversification across species.
+Under a stable fitness landscape (B), most mutations reaching fixation are either slightly deleterious reaching fixation due to drift or are beneficial non-adaptive mutations restoring a more optimal amino acid.
+At the phylogenetic scale (D), deleterious substitutions (negative signs) are often reverted via beneficial non-adaptive mutations (positive signs), promoting phenotype stability and preserving well-established biological systems.
+Even though, individually, any beneficial non-adaptive mutation might have a weak effect on its bearer, we expect them to be scattered across the genome and the genome-wide signature of beneficial non-adaptive mutations to be detectable and quantifiable.}
+\label{fig:fitness-landscape}
+\end{figure}
 
@@
 
+\begin{figure}[!ht]
+\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\centering
+\includegraphics[width=1.4\textwidth, page=1] {figure2.eps}
+\caption{
+Selection coefficients at the phylogenetic and population scales.
+At the phylogenetic scale (A), we estimated the amino-acid fitness for each site from protein-coding DNA alignments using mutation-selection codon models.
+For every possible mutation, the difference in amino-acid fitness before and after the mutation allows us to compute the selection coefficient at the phylogenetic scale ($\Sphy$).
+Depending on $\Sphy$ (B) mutations can be predicted as deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) or beneficial non-adaptive mutations ($\SphyBen$) toward a fitter amino acid and repairing existing functions.
+At the population scale, each observed single nucleotide polymorphism (SNP) segregating in the population can also be classified according to its $\Sphy$ value (C).
+Occurrence and frequency in the population of non-synonymous polymorphisms, contrasted to synonymous polymorphisms (deemed neutral) is used to estimate selection coefficients (D-E) at the population scale ($\Spop$), for each class of selection ($\SphyDel$, $\SphyNeu$, $\SphyBen$).
+We can thus assess whether $\Sphy$ predicts $\Spop$ and compute \textit{precision} (F) and \textit{recall} (G) for each class.
+The \textit{recall} value for class $\SphyBen$ is the probability for beneficial mutations to be non-adaptive (G).
+Icons are adapted from \href{https://phylopic.org}{https://phylopic.org} under a Creative Commons license.
+}
+\label{fig:method}
+\end{adjustwidth}
+\end{figure}
+
 Having identified which potential DNA changes represent beneficial non-adaptive mutations (fig.~\ref{fig:method}A-B), we retrieved polymorphism data from 28 wild and domesticated populations belonging to six genera (\textit{Equus}, \textit{Bos}, \textit{Capra}, \textit{Ovis}, \textit{Chlorocebus}, and \textit{Homo}) to assess the presence of beneficial non-adaptive mutations at the population scale.
@@
 
-    Furthermore, since in principle, $\SphyBen$ mutations are bound to reach fixation more often than neutral mutations, we calculated the $\dnds$ ratio of non-synonymous over synonymous divergence for all terminal lineages, focusing on the non-synonymous changes predicted as $\SphyBen$ mutations ($\dn(\SphyBen) / \ds$).
-    We obtained values between 1.17 and 1.75 in the different lineages (table~S2), meaning that $\SphyBen$ mutations reach fixation slightly more frequently than synonymous mutations that are supposed to be neutral, consistent with these $\SphyBen$ mutations being weakly beneficial.
-    Such an observation is consistent with the premise that $\SphyBen$ mutations are weakly beneficial, translating to a scaled selection coefficient between 0.32 and 1.24 (table~S2).
-    Finding $\dn(\SphyBen) / \ds > 1$ for these sites confirms that these sites are closer to optimality at the end of the branch than at the beginning.
-    Even though the beneficial effect of these mutations does not come from an environmental change, it does not change the fact that they have contributed positively to the population’s fitness.
-    It is just that at mutation-selection-drift equilibrium, the increase in fitness at these sites is offset by deleterious substitutions elsewhere in the genome so that there is no net adaptation.
-
-    This result further indicates that using $\dnds$ as an estimate of purifying selection is biased (overestimated) due to the presence of beneficial non-adaptive mutations among the non-synonymous substitutions.
-    By discarding all beneficial non-adaptive mutations we can obtain an estimate of $\dnds$ which is not inflated.
-    By comparing these two ways of calculating $\dnds$ (see section~\ref{subsec:substitution-mapping-in-the-terminal-branch} in Materials \& Methods), we calculated that beneficial non-adaptive mutations inflate $\dnds$ values by between 9 and 12\% across genera.
-This represents a substantial increase when considering that beneficial non-adaptive mutations only represent between 0.9 and 1.2\% of non-synonymous mutational opportunities (table~S3).
-
-    \subsection*{Selection in populations}
-    Second, we assessed whether our calculated $\Sphy$ values predicted at the phylogenetic scale were also indicative of the selective forces exerted at the population level.
-    We retrieved single nucleotide polymorphisms (SNPs) segregating in 28 mammalian populations.
-    To determine if SNPs were ancestral of derived, we reconstructed the ancestral exome of each population.
-    We then classified every non-synonymous SNP as either $\SphyDel$, $\SphyNeu$, or $\SphyBen$ according its $\Sphy$ value (fig.~\ref{fig:method}B-C).
-
-    First, SNPs classified as $\SphyBen$ are spread across the genomes and not strongly associated to the ontology terms of their respective genes (table~S4, fig.~S4).
-    In humans, some SNPs have been associated with specific clinical prognosis terms obtained by clinical evaluation of the impact of variants on human Mendelian disorders~\cite{landrum_clinvar_2018}.
-    Although this classification also relies on deep protein alignments and therefore cannot be considered an independent result from our own, it does provide a consistency check if the effect of a mutation on human health is in line with its fitness effect predicted by our method~\cite{grimm_evaluation_2015}.
-    Therefore, we investigated whether the non-synonymous SNPs classified as $\SphyDel$ or $\SphyBen$ showed enrichment in specific clinical terms compared to SNPs classified as $\SphyNeu$.
-    Our results show that SNPs predicted as deleterious are associated with clinical terms such as \textit{Likely Pathogenic} and \textit{Pathogenic}, implying that, in general, the selective pressure of a mutation exerted across mammals is also predictive of its clinical effect in humans (table~S5)~\cite{sullivan_leveraging_2023}.
-    Conversely, $\SphyBen$ mutations are associated with clinical terms such as \textit{Benign} and \textit{Likely Benign}, which shows that $\SphyBen$ mutations are less likely to be functionally damaging (table~S6).
-
-    In addition to clinical prognosis, frequencies at which SNPs are segregating within populations provide information on their selective effects.
-    For instance, deleterious SNPs usually segregate at lower frequencies because of purifying selection, which tends to remove them from the population (fig.~\ref{fig:homo-afr-results}C for humans).
-    By gathering information across many SNPs, it is possible to estimate the distribution of fitness effects at the population scale, taking synonymous SNPs as a neutral expectation~\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009, galtier_adaptive_2016, tataru_inference_2017}.
-    From these estimated fitness effects, we can derive the proportion of beneficial mutations ($\ProbaPopBen$), nearly-neutral mutations ($\ProbaPopNeu$) and deleterious mutations ($\ProbaPopDel$) at the population scale (see section~\ref{subsec:s-polymorphism-method} in Materials \& Methods, figs.~S5-S8).
-    These approaches offer a unique opportunity to contrast selection coefficients estimated at the population scale ($\Spop$) and at the phylogenetic scale ($\Sphy$).
-
-    Across our selection classes ($\SphyDel$, $\SphyNeu$ and $\SphyBen$), one can ultimately estimate the proportion of correct and incorrect predictions, leading to an estimation of \textit{precision} and \textit{recall} (fig.~\ref{fig:method}F-G and section~\ref{subsec:precisison_recall} in Materials \& Methods).
-    Across 28 populations of different mammal species, mutations predicted to be deleterious at the phylogenetic scale ($\SphyDel$) were indeed purged at the population scale, with a \textit{precision} in the range of 90--97\% (table~\ref{table:proba} and fig.~\ref{fig:homo-afr-results}D for humans).
-    Conversely, a \textit{recall} in the range of 96--100\% implied that mutations found to be deleterious at the population scale were most likely also predicted to be deleterious at the phylogenetic scale (table~\ref{table:proba}).
-    Altogether, purifying selection is largely predictable and amino acids with negative fitness across mammals have been effectively purged away in each population.
-
-    Mutations predicted as $\SphyNeu$ were effectively composed of a mix of neutral and selected mutations with varying \textit{precision} (36--63\%) and \textit{recall} (32--45\%) across the different populations (table~\ref{table:proba}, fig.~\ref{fig:homo-afr-results}D for humans).
-    The variable proportions between populations can be explained by the effective number of individuals in the population ($\Ne$), a major driver of selection efficacy.
-    Moreover, estimates of mutation rate per generation ($u$), from Bergeron \textit{et al.}~\cite{bergeron_evolution_2023} and Orlando \textit{et al.}~\cite{orlando_recalibrating_2013}, and Watterson’s $\theta$ obtained from the synonymous SFS as in Achaz~\cite{achaz_frequency_2009}, allow us to obtain $\Ne$ through $\Ne=\theta/4 u)$.
-    Using correlation analyses that accounted for phylogenetic relationship (see section \ref{subsec:correlation-diversity} in Materials \& Methods), we found that higher $\Ne$ was associated with a smaller proportion of nearly-neutral mutations ($r^2=0.31$, $p=0.001$, fig.~\ref{fig:diversity}A).
-    This result follows the prediction of the nearly-neutral theory and suggests that in populations with higher diversity (e.g.,~\textit{Bos} or \textit{Ovis}), discrimination between beneficial and deleterious mutations is more likely to occur (figs.~S9-S12).
-    Conversely, many more mutations are effectively neutral in populations with lower diversity (e.g.,~\textit{Homo}).
-
-    Finally, mutations predicted to be $\SphyBen$ were indeed beneficial for individuals bearing them, with a \textit{precision} (fig.~\ref{fig:method}F) in the range of 19--87\% (table~\ref{table:proba} and fig.~\ref{fig:homo-afr-results}D for humans).
-    This result confirms that selection toward amino acids restoring existing functions is ongoing in these populations.
-    Importantly, the \textit{recall} value in this case, computed as $\proba [ \SphyBen \given \SpopBen]$, is the probability for a beneficial mutation at the population scale to be a non-adaptive, i.e., going toward a fitter amino acid given a stable fitness landscape (fig.~\ref{fig:method}G, table~S7).
-    In other words, the \textit{recall} value quantifies the number of beneficial mutations restoring damaged genomes instead of creating adaptive innovations.
-    Across the 28 populations, this proportion is in the range of 11--82\% (table~\ref{table:proba}), with a mean of 30\%.
-    Accounting for phylogenetic relationships, we found no correlation between the proportion of beneficial non-adaptive mutations and estimates of $\Ne$ based on genetic diversity ($r^2=0.00$, $p=0.772$, fig.~\ref{fig:diversity}B).
-
-    We additionally performed controls and simulations to ensure our results were robust.
-    First, we controlled that these estimations were not affected by SNP mispolarization (figs.~S13-S14).
-    Second, we performed simulations at the population-genetic level and confirmed that our method was able to recover the proportion of beneficial mutations that are non-adaptive in synthetic polymorphism datasets (fig.~S15).
-    Third, we ran our analysis filtering out CpG mutations and obtained values of $\proba [ \SphyBen \given \SpopBen]$ in the range of 5--27\%, with a mean of 14\% (tables~S8-9 and fig.~S16-17), providing more conservative estimates.
-    Finally, because the phylogenetic mutation-selection codon model should fit better for genes with uniformly conserved functions, we filtered out genes under pervasive adaptation~\cite{latrille_genes_2023} as a control.
-    In this subset of the exome, containing genes with a more stable fitness landscape, we found an increase in the proportion of beneficial mutations that are non-adaptive (Wilcoxon signed-rank, $s=80$, $p=0.002$, table~S10), consistent with our expectation that beneficial mutations occur more frequently in genes under changing fitness landscapes.
-
-    \subsection*{Selection in the terminal lineage and in populations}
-
-    As an alternative to relying solely on currently segregating mutations to quantify selection, one can leverage both polymorphism within a population and substitutions in the terminal lineage to estimate the distribution of fitness effects (DFE).
-    Hence, we estimated \textit{precision} and \textit{recall} as done previously, but now including the number of substitutions per site as input for the DFE estimators (see \ref{subsec:s-polymorphism-method} in Materials \& Methods and fig.~S18).
-    When including substitutions in the terminal lineage, estimates of $\proba [ \SphyBen \given \SpopBen]$ are in the 10--78\% range with a mean of 36\% (table~S11-12), and 19 out of 28 estimates fall between 15\% and 45\%.
-
-    Additionally, we controlled that these estimations were not affected by SNP mispolarization (fig.~S19).
-    We also filtered out genes under pervasive adaptation, and again found an increase in $\proba [ \SphyBen \given \SpopBen]$, consistent with our expectation (Wilcoxon signed-rank, $s=120$, $p=0.027$, table~S13).
-    We assessed the impact of fitting the same functional form of DFE to the three different categories of changes $\SphyDel$, $\SphyNeu$ and $\SphyBen$.
-    To this aim we computed the total amount of current selection by fitting either a single DFE on the whole dataset or by summing the other three independent DFEs.
-    These disjoint estimates are well correlated, with a goodness of fit $r^2={0.95, 0.89, 0.82}$ for $\proba [\SpopDel]$, $\proba [\SpopNeu]$ and $\proba [\SpopBen]$, respectively (figs.~S20-22).
-    Finally, we evaluated the effect of fitting a parametric functional form for the DFE.
-    As implemented in Tataru \textit{et al.}~\cite{tataru_inference_2017}, the DFE is a mixture between a reflected gamma distribution and an exponential distribution (eq.~\ref{eq:parametric-dfe}, section~\ref{subsec:precisison_recall} in Materials \& Methods).
-    Instead of using such a continuous DFE, we also tested our prediction with a non-parametric functional form for the DFE, obtaining estimates of $\proba [ \SphyBen \given \SpopBen]$ in the 8--94\% range, with a mean of 43\% (tables~S14-15).
-
-    \section*{Discussion}
-    \subsection*{Beneficial mutations are not necessarily adaptive}
-
-    This study represents an essential step toward integrating the different evolutionary scales necessary to understand the combined effects of mutation, selection, and drift on genome evolution.
-    In particular, we have been able to quantify the proportion of beneficial mutations that are non-adapative (i.e., not a response to a change in fitness landscape), which has only been achievable by combining exome-wide data from both phylogenetic and population scales.
-    At the phylogenetic scale, codon diversity at each site of a protein-coding DNA alignment allows for reconstructing an amino-acid fitness landscape, assuming that this landscape is stable along the phylogenetic tree.
-    These amino-acid fitness landscapes allow us to predict any mutation’s selection coefficient ($\Sphy$) along a protein-coding sequence.
-    We have compared these selective effects to observations at the population level, and by doing so, we have confirmed that mutations predicted to be deleterious ($\SphyDel \coloneqq \Sphy < -1$) are generally purified away in extant populations.
-    Our results concur with previous studies showing that SIFT scores~\cite{ng_sift_2003, vaser_sift_2016}, based on amino acid alignments across species, also inform on the deleterious fitness effects exerted at the population scale~\cite{chen_hunting_2021}.
-    However, contrary to SIFT scores, our mutation-selection model is parameterized by a fitness function such that changes are directly interpretable as fitness effects (see also section S5).
-    In this regard, an interesting prediction of our model is that some deleterious mutations reach fixation due to genetic drift, while beneficial non-adaptive mutations restore states of higher fitness.
-    We have tested this hypothesis and have found that a substantial part of these predicted non-adaptive mutations ($\SphyBen \coloneqq \Sphy > 1 $) are indeed beneficial in extant populations.
-    We estimate that between 11 and 82\% of all beneficial mutations in mammalian populations are not adaptive.
-    More specifically, in 24 out of 28 populations analyzed, the percentage of beneficial mutations estimated to be non-adaptive falls between 15 and 45\%.
-    These results suggest that many beneficial mutations are not adaptive, but rather restore states of higher fitness.
-    Hence, we can correctly estimate the extent of adaptive evolution only if we account for the number of beneficial non-adaptive mutations~\cite{keightley_what_2010, rice_evolutionarily_2015}.
-    Here instead, we argue that we should dissociate positive selection from adaptive evolution and limit the use of adaptive mutations to those that are associated with adaptation to environmental change as such~\cite{charlesworth_other_2007, mustonen_fitness_2009, mustonen_fitness_2010}.
-
-    \subsection*{Assumptions and methodological limitations}
-
-    The exact estimation of the contribution of beneficial non-adaptive mutations to positive selection relies on some hypotheses at both the phylogenetic and population scales and is sensitive to methodological limitations.
-    Indeed, data quality and potentially inadequate modeling choices of both the fitness landscape (at the phylogenetic scale) and fitness effects (at the population scale) might also lead to missed predictions~\cite{moutinho_variation_2019}.
-    In practice, we obtained different values of the proportion of non-adaptive beneficial mutations depending on i) the filtering or not of CpG mutations~\cite{eyre-walker_how_2014}, ii) whether we included substitutions in the terminal lineage along with within-population polymorphisms to estimate fitness effects~\cite{tataru_inference_2017}, and iii) the model used to infer the fitness effects.
-    It appears that our estimation can be sensitive to model misspecification and overall, while we provide an order of magnitude for the contribution of beneficial non-adaptive mutations to positive selection, methodological improvement on the estimation of the DFE is needed to increase the precision of this value.
-
-    To be conservative, we considered mutations as adaptive if they were detected as being under positive selection at the population scale despite them being either incorrectly predicted as deleterious ($\SphyDel$) or nearly-neutral ($\SphyNeu \coloneqq -1 < \Sphy <1$) from the amino-acid mammalian fitnesses.
-    An example of an incorrectly predicted deleterious mutation ($\SphyDel$) from its fitness landscape could be an amino acid having always been deleterious across mammals, but being advantageous ($\SpopBen$) in the current species due to environmental changes or a major shift in their fitness landscape (e.g.
-domestication)
-    To visualize an example of a wrongly predicted nearly-neutral mutation, we can first imagine a site where only hydrophilic amino acids are accepted because of the protein properties (e.g.
-a surface site of a globular protein).
-    Let us then assume that such a site is also a target for viruses, hence promoting amino-acid changes which modify the site's viral affinity~\cite{enard_viruses_2016}.
-    Given the selective pressure favoring amino-acid change, but restricting the possibilities to hydrophilic amino acids, most hydrophilic amino acids will likely be visited along the phylogenetic tree and the mutation-selection model will give high and similar fitnesses to all of them.
-    In such a case, any mutation between hydrophilic amino acids will be wrongly predicted as nearly-neutral ($\SphyNeu$), while it is in fact adaptive.
-    In summary, under a changing fitness landscapes~\cite{mustonen_molecular_2008}, our phylogenetic mutation-selection model takes an average over fitness changes observed along the phylogeny, causing beneficial mutations ($\SpopBen$) to be predicted as either deleterious ($\SphyDel$) or nearly-neutral ($\SphyNeu$), therefore mechanically reducing $\proba [ \SphyBen \given \SpopBen]$, and making our estimate conservative.
-
-    \subsection*{Convergent adaptation}
-
-    If there are several substitutions toward the same amino acid along the mammalian tree (see fig.~S3), our mutation-selection model cannot formally distinguish between a scenario where mammals have fixed deleterious mutations that are reverted in several lineages, from more complex scenarios involving convergent adaptation across mammals.
-    In a first scenario, repeated changes of fitness landscapes in the same direction could occur along several lineages, leading to repeated substitutions in multiple lineages (parallel or convergent adaptation).
-    In a second scenario, an environmental change that occurred near the root of placental mammals ($\sim$100 Mys ago), to which extant populations are currently responding independently through weakly adaptive mutations, could also lead to repeated substitutions toward the same amino acids.
-    Importantly, we would usually expect adaptive convergent mutations to be linked to particular converging phenotypes across mammals, and hence, they should not massively affect the whole genome as we find (table~S4, fig.
-S4).
-    Moreover, after filtering out genes usually associated to recurrent adaptation (e.g. immune genes), we recover an even higher proportion of beneficial non-adaptive mutations (table~S8).
-    For these reasons, we argue that the signal of predictable positive selection we recover in extant population is indeed mainly driven by non-adaptive evolution.
-
-    \subsection*{The influence of effective population size}
-
-    Across the genome, beneficial non-adaptive mutations and deleterious mutations reaching fixation create a balance in which genomes are constantly damaged and restored simultaneously at different loci due to drift.
-    Since the probability of fixation of mutations depends on the effective population size ($\Ne$), the history of $\Ne$ plays a crucial role in determining the number of beneficial non-adaptive mutations compensating for deleterious mutations~\cite{latrille_inferring_2021}.
-    For example, a population size expansion will increase the efficacy of selection, and a larger proportion of mutations will be beneficial (otherwise effectively neutral), thus increasing the number of beneficial non-adaptive mutations.
-    On the other hand, a population that has experienced a high $\Ne$ throughout its history should be closer to an optimal state under a stable fitness landscape, having suffered fewer fixations of deleterious mutations and therefore decreasing the probability of beneficial non-adaptive mutations~\cite{huber_determining_2017}.
-    Overall, we expect the proportion of beneficial non-adaptive mutations to be more dependent on $\Ne$’s long-term expansions and contractions than on the short-term ones~\cite{charlesworth_other_2007,huber_determining_2017}.
-
-    Moreover, because our model assumes a fixed fitness landscape, it implicitly assumes that $\Ne$ is constant along the phylogenetic tree.
-    Fluctuations due to changes in the fitness landscape or in $\Ne$ will be averaged out by the assumption of the current model that $\Ne$ is constant across lineages.
-    It was recently shown~\cite{latrille_inferring_2021}, using computer intensive mutation-selection models with fluctuating $\Ne$, that relaxing the assumption of a constant $\Ne$ results in more extreme estimates of amino-acid fitnesses than with the standard model used in this study.
-    In other words, by assuming a constant $\Ne$, we are underpowered to detect beneficial non-adaptive mutations since amino acids will have more similar fitnesses.
-    As a consequence, some of the beneficial non-adaptive mutations currently segregating in population will be incorrectly classified as nearly-neutral by the mutation-selection model, and thus be wrongly interpreted as adaptive (see previous section).
-    This ultimately results in lower estimates of the proportion of beneficial non-adaptive mutations.
-    Given this inflation of missed predictions due to change in population sizes~\cite{lanfear_population_2014, jones_shifting_2017, platt_protein_2018}, our estimated proportion of beneficial non-adaptive mutations among adaptive ones is likely to be an underestimation.
-
-    \subsection*{The role of epistasis and compensatory mutations}
-
-    Our model assumes that amino-acid fitness landscapes are site-specific and also independent of one another, whereas under pervasive epistasis, the fitness effect of any mutation at a particular site would depend on the amino acids present at other sites.
-    Epistasis is common for mutations that influence the protein’s physical properties (e.g.
-conformation, stability, or affinity for ligands) or might arise due to nonlinear relationship between the protein’s physical properties and fitness~\cite{starr_epistasis_2016}.
-    Regardless of its origin, epistasis has been shown to play a role in the evolution of protein-coding genes, with amino-acid residues in contact within a protein or between proteins tending to co-evolve~\cite{morcos_directcoupling_2011, marks_protein_2012, starr_epistasis_2016}.
-    Particularly, the residues in contact co-evolve to become more compatible with each other generating an entrenchment~\cite{goldstein_nonadaptive_2015, goldstein_sequence_2017, park_epistatic_2022}.
-    Epistasis therefore allows for compensatory mutations, which restore fitness through mutations at loci different from where deleterious mutations took place, representing another case of non-adaptive beneficial mutations, but one which is not accounted for by our method.
-    Hence, the beneficial mutations that we classify as putatively adaptive might in fact be compensatory mutations, making our estimation of the rate of non-adaptive beneficial mutations conservative.
-
-    Despite epistasis being an important factor in protein evolution, several deep-mutational scanning experiments have revealed that a site-specific fitness landscape predicts the evolution of sequences in nature with considerable accuracy~\cite{ashenberg_mutational_2013, doud_sitespecific_2015, bloom_identification_2017}.
-    Additionally, the fact that we observe such a high proportion of beneficial non-adaptive mutations suggests that the underlying assumptions of our model, namely site-independence, implying no epistasis, and a static fitness landscape, are a reasonable approximation for the underlying fitness landscape of proteins.
-    Our results imply that the fitness effects of new mutations are mostly conserved across mammalian orthologs, in agreement with other studies showing that for conserved orthologs with similar structures and functions, models without epistasis provide a reasonable estimate of fitness effects in protein coding genes~\cite{youssef_consequences_2020, vigue_deciphering_2022}.
-    Conceptually, the framework presented here, with the addition of a more complex protein fitness landscape at the phylogenetic scale, could be used to infer the relative contribution of compensatory mutations to non-adaptive and adaptive evolution.
-
-    \subsection*{Detecting adaptation above the nearly-neutral background}
-
-    A long-standing debate in molecular evolution is whether the variation we observe between species in protein-coding genes is primarily due to nearly-neutral mutations reaching fixation by drift or primarily due to adaptation~\cite{kimura_evolutionary_1968,ohta_nearly_1992,gillespie_substitution_1994,jensen_importance_2019}.
-    Measuring the ``rate of adaptation'' in proteins, as pioneered by McDonald \& Kreitman~\cite{mcdonald_adaptative_1991}, has been central to inform this debate~\cite{galtier_half_2024}.
-    However, the McDonald \& Kreitman test detects signatures of accelerated evolution in a given terminal branch compared to an expectation based on polymorphism present in the population.
-It considers the fraction of substitutions that fix too quickly as ``adaptive''~\cite{mcdonald_adaptative_1991, smith_adaptive_2002, welch_estimating_2006} despite there being other processes that can lead to their fixation~\cite{galtier_adaptation_2007,rousselle_influence_2019,joseph_increased_2024a} and some of these substitutions being beneficial but non-adaptive~\cite{hartl_compensatory_1996, charlesworth_other_2007, mustonen_fitness_2009, jones_shifting_2017}.
-    Here, the expectation is built on the pattern of substitutions across a phylogeny compared to the fitness effects that can be estimated from both substitutions in a terminal lineage and polymorphism in populations.
-    Moreover, the goal is not to detect a fraction of beneficial substitution (i.e.
-``adaptive'' substitutions for McDonald \& Kreitman~\cite{mcdonald_adaptative_1991}), but to estimate the proportion of non-adaptive mutations among beneficial ones.
-
-    We provide evidence that in mammalian orthologs, many substitutions occur through fixation of both deleterious mutations and beneficial non-adaptive mutations.
-    Detecting adaptation above this background of substitutions remains a challenge~\cite{kimura_evolutionary_1968, ohta_development_1996}.
-    Mathematically, the surplus of positive selection due to an externally-driven changing fitness landscape is called \textit{fitness flux}, and requires experimentally measuring the selection coefficient of each mutation in each genetic background.
-    The \textit{fitness flux} can be estimated if either the substitutions history is known~\cite{mustonen_fitness_2009} or changes of frequency in currently segregating variants~\cite{mustonen_fitness_2010}.
-    Without experimentally measured selection coefficients, another strategy is precisely to use a nearly-neutral substitution model as a null model of evolution.
-    Under a strictly neutral evolution of protein-coding sequence, we expect the ratio of non-synonymous over synonymous substitutions ($\dnds$) to be equal to one.
-    Deviations from this neutral expectation, such as $\dnds > 1$, which can be generated by an excess of non-synonymous substitutions, is generally interpreted as a sign of adaptation.
-    However, as shown in this study, a $\dnds > 1$ is not necessarily a signature of adaptation but can be due to beneficial non-adaptive mutations.
-    So, by relaxing the strict neutrality and assuming a stable fitness landscape instead, one can predict the expected rate of evolution, called $\omega_0$~\cite{spielman_relationship_2015, dosreis_how_2015}.
-    Adaptation can thus be considered as evolution under a changing fitness landscape and tested as such by searching for the signature of $\dnds > \omega_0$~\cite{cvijovic_fate_2015, rodrigue_detecting_2017, rodrigue_bayesian_2021}.
-    Using a stable fitness landscape as a null model of evolution, thus accounting for selective constraints exerted on the different amino acids, increased the statistical power in testing for adaptation~\cite{latrille_genes_2023}.
-    Instead of relying solely on summary statistics (such as $\dnds$ or $\omega_0$), another strategy to detect adaptation is to include changes in the fitness landscapes inherently within the mutation selection framework, either with small changes along the phylogeny ~\cite{tamuri_mutationselection_2021} or either by allowing fitness to change on subsets of branches ~\cite{kazmi_detecting_2019, stolyarova_senescence_2020}.
-    Such mechanistic models could be more general than site-specific fitness landscapes, including epistasis and changing fitness landscapes~\cite{goldstein_sequence_2017, stolyarova_senescence_2020}.
-
-    \subsection*{Conclusions}
-
-    We have provided empirical evidence that an evolutionary model assuming a stable fitness landscape at the mammalian scale allows us to predict the fitness effects of mutations in extant populations and individuals, acknowledging the balance between deleterious and beneficial non-adaptive mutations.
-    We argue that such a model would represent a null expectation for the evolution of protein-coding genes in the absence of adaptation.
-    Altogether, because a substantial part of positive selection can be explained by beneficial non-adaptive mutations, but not its entirety, we argue that the mammalian exome is shaped by both adaptive and non-adaptive processes, and that none of them alone is sufficient to explain the observed patterns of changes.
-    In that sense, to avoid conflating beneficial mutations with adaptive evolution, the term ``adaptation`` should retain its original meaning associated with a change in the underlying fitness landscape and be modelled as such~\cite{mustonen_fitness_2009, mustonen_fitness_2010}.
-
-    \newpage
-    \section{Materials \& Methods}
-    \label{sec:methods}
-
-    \subsection{Phylogenetic dataset}\label{subsec:phylo-dataset}
-
-    Protein-coding DNA sequence alignments in placental mammals and their corresponding gene trees come from the \href{https://www.orthomam.univ-montp2.fr}{OrthoMaM} database and were processed as in Latrille \textit{et al.}~\cite{latrille_genes_2023}.
-    OrthoMaM contains a total of $116$ mammalian reference sequences in v10c~\cite{ranwez_orthomam_2007, douzery_orthomam_2014, scornavacca_orthomam_2019}.
-
-    Genes located on the X and Y chromosomes and on the mitochondrial genome were discarded from the analysis because the level of polymorphism –~which is necessary for population-based analyses~– is expected to be different in these three regions compared to the autosomal genome.
-    Sequences of species for which we used population-level polymorphism (see section \ref{subsec:polymorphism-dataset}) and their sister species, were removed from the analysis to ensure independence between the data used in the phylogenetic and population scales.
-    Sites in the alignment containing more than 10\% of gaps across the species were discarded.
-    Altogether, our genome-wide dataset contains $14,509$ protein-coding DNA sequences in $87$ placental mammals.
-
-    \subsection{Selection coefficient ($\Sphy$) in a phylogeny-based method}
-    \label{subsec:s-phylogeny-method}
-
-    We analyzed the phylogenetic-level data using mutation-selection models.
-    These models assume the protein-coding sequences are at mutation-selection balance under a fixed fitness landscape characterized by a fitness vector over the $20$ amino acids at each site~\cite{yang_mutationselection_2008, halpern_evolutionary_1998, rodrigue_mechanistic_2010}.
-    Mathematically, the rate of non-synonymous substitution from codon $a$ to codon $b$ ($q_{a \mapsto b}^{(i)}$) at site $i$ of the sequence is equal to the rate of mutation of the underlying nucleotide change ($\mu_{a \mapsto b}$) multiplied by the scaled probability of mutation fixation ($\proba_{a \mapsto b}^{(i)}$).
-    The probability of fixation depends on the difference between the scaled fitness of the amino acid encoded by the mutated codon ($F_b^{(i)}$) and the amino acid encoded by the original codon ($F_a^{(i)}$) at site $i$~\cite{wright_evolution_1931, fisher_genetical_1930}.
-
-    The rate of substitution from codon $a$ to $b$ at a site $i$ is thus:
-    \begin{equation}
-        \begin{dcases}
-            q_{a \mapsto b}^{(i)} & = 0 \text{ if codons $a$ and $b$ are more than one mutation away,} \\
-            q_{a \mapsto b}^{(i)} & = \mu_{a \mapsto b} \text{ if codons $a$ and $b$ are synonymous, and}\\
-            q_{a \mapsto b}^{(i)} & = \mu_{a \mapsto b} \dfrac{F_b^{(i)} - F_a^{(i)}}{1 - \e^{F_a^{(i)} - F_b^{(i)}}} \text{ if codons $a$ and $b$ are non-synonymous}.
-        \end{dcases}
-    \end{equation}
-
-    Fitting the mutation-selection model on a multi-species sequence alignment leads to an estimation of the gene-wide $4 \times 4$ nucleotide mutation rate matrix ($\UniDimArray{\mu}$) as well as the $20$ amino-acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$.
-    The priors and full configuration of the model are given in section S1.
-    From a technical perspective, the Bayesian estimation is a two-step procedure~\cite{rodrigue_bayesian_2008}.
-    The first step is a data augmentation of the alignment, consisting in sampling a detailed substitution history along the phylogenetic tree for each site, given the current value of the model parameters.
-    In the second step, the parameters of the model can then be directly updated by a Gibbs sampling procedure, conditional on the current substitution history.
-    Alternating between these two sampling steps yields a Markov chain Monte-Carlo (MCMC) procedure whose equilibrium distribution is the posterior probability density of interest~\cite{lartillot_bayesian_2004, rodrigue_bayesian_2008}.
-    Additionally, across-site heterogeneities in amino-acid fitness profiles are captured by a Dirichlet process.
-    More precisely, the number of amino-acid fitness profiles estimated is lower than the number of sites in the alignment.
-    Consequently each profile has several sites assigned to it, resulting in a particular configuration of the Dirichlet process.
-    Conversely, sites with similar signatures are assigned to the same fitness profile.
-    This configuration of the Dirichlet process is resampled through the MCMC to estimate a posterior distribution of amino acid profiles for each site specifically~\cite{rodrigue_mutationselection_2010, lartillot_inference_2013}.
-    From a more mechanistic perspective, even though not all amino acids occur at every single codon site of the DNA alignment, we can nevertheless estimate the distribution of amino-acid fitnesses by generalizing the information recovered across sites and across amino acids based on the phylogenetic relationship among samples.
-    In particular, synonymous substitutions along the tree contain the signal to estimate branch lengths and the nucleotide transition matrix, while non-synonymous substitutions contain information on fitness difference between codons connected by single nucleotide changes~\cite{rodrigue_mutationselection_2010}.
-
-    The selection coefficient for a mutation from codon $a$ to codon $b$ at site $i$ is defined as:
-    \begin{equation}
-        \Sphy^{(i)} (a \mapsto b) = \Delta F^{(i)} = F^{(i)}_{b} - F^{(i)}_{a}.
-    \end{equation}
-    In our subsequent derivation the source ($a$) and target ($b$) codons as well as the site ($i$) are implicit and thus never explicitly written.
-
-    The scaled selection coefficient ($\Sphy = \Delta F$) is formally the product of the selection coefficient at the individual level ($s$) and the effective population size ($\Ne$), as $\Sphy = 4 \Ne \times s$.
-The value of $\Sphy$ informs us on the strength of selection exerted on amino acids changes.
-    Thus, according to its $\Sphy$ value, we can classify any mutation as either a deleterious mutation toward a less fit amino acid ($\SphyDel \coloneqq \Sphy < -1$), a nearly-neutral mutation ($\SphyNeu \coloneqq -1 < \Sphy <1$), or a mutation toward a known fitter amino acid, constituting thus a beneficial non-adaptive mutation ($\SphyBen \coloneqq \Sphy > 1$).
-
-    We used the Bayesian software \textit{BayesCode} (\url{https://github.com/ThibaultLatrille/bayescode}, v1.3.1) to estimate the selection coefficients for each protein-coding gene in the mammalian dataset.
-    We ran the MCMC algorithm implemented in BayesCode for $2,000$ generations as described in Latrille \textit{et al.}~\cite{latrille_genes_2023}.
-    For each gene, after discarding a burn-in period of $1,000$ generations of MCMC, we obtained posterior mean estimates (over the $1,000$ generations left of MCMC) of the mutation rate matrix ($\UniDimArray{\mu}$) as well as the $20$ amino-acid fitness landscape ($\UniDimArray{F^{(i)}}$) at each site $i$.
-
-    \subsection{Polymorphism dataset}
-    \label{subsec:polymorphism-dataset}
-
-    The genetic variants representing the population level polymorphisms were obtained from the following species and their available datasets: \textit{Equus caballus} (EquCab2 assembly in the EVA study PRJEB9799~\cite{alabri_whole_2020}), \textit{Bos taurus} (UMD3.1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}), \textit{Ovis aries} (Oar\_v3.1 assembly in the NextGen project), \textit{Capra hircus} (CHIR1 assembly in the NextGen project), converted to ARS1 assembly with dbSNP identifiers~\cite{sherry_dbsnp_2001}), \textit{Chlorocebus sabaeus} (ChlSab1.1 assembly in the EVA project PRJEB22989~\cite{svardal_ancient_2017}), \textit{Homo sapiens} (GRCh38 assembly in the 1000 Genomes Project~\cite{zheng-bradley_alignment_2017}).
-    In total, we analyzed 28 populations across the 6 different species with polymorphism data.
-    The data was processed as described in Latrille \textit{et al.}~\cite{latrille_genes_2023}.
-
-    Only bi-allelic single nucleotide polymorphisms (SNPs) found within a gene were in our polymorphism dataset, while nonsense variants and indels were discarded.
-    To construct the dataset, we first recovered the location of each SNP (represented by its chromosome, position, and strand) in the focal species and matched it to its corresponding position in the coding sequence (CDS) using gene annotation files (GTF format) downloaded from Ensembl (\url{ensembl.org}).
-    We then verified that the SNP downloaded from Ensembl matched the reference in the CDS in FASTA format.
-    Next, the position in the CDS was converted to the corresponding position in the multi-species sequence alignment (containing gaps) from the OrthoMaM database (see section~\ref{subsec:s-phylogeny-method}) for the corresponding gene by doing a global pairwise alignment (Biopython function pairwise2).
-    This conversion from genomic position to alignment position was only possible when the assembly used for SNP-calling was the same as the one used in the OrthoMaM alignment, the GTF annotations, and the FASTA sequences.
-    SNPs were polarized using the three closest outgroups found in the OrthoMaM alignment with est-usfs v2.04~\cite{keightley_inferring_2018}, and alleles with a probability of being derived lower than 0.99 were discarded.
-
-    \subsection{Mutational opportunities}
-    \label{subsec:nunber-of-sites}
-    The mutational opportunities of any new mutation refer to its likelihood of falling into a specific category (synonymous, deleterious, nearly-neutral, or beneficial).
-    Deriving such opportunities is necessary to estimate the strength of selection exerted at the population scale since different categories might have different mutational opportunities, and thus polymorphism and divergence need to be corrected accordingly (see sections~\ref{subsec:substitution-mapping-in-the-terminal-branch},~\ref{subsec:s-polymorphism-method}, and~\ref{subsec:precisison_recall}).
-    To calculate mutational opportunities, we reconstructed the ancestral exome of each of the 28 populations by using the most likely ancestral state from est-usfs (see section \ref{subsec:polymorphism-dataset}), which differs from the corresponding species reference exome since it accounts for the variability present in the specific population.
-
-    From the reconstructed ancestral exome, all possible mutations were computed, weighted by the instantaneous rate of change between nucleotides obtained from the mutation rate matrix ($\UniDimArray{\mu}$, see section~\ref{subsec:s-phylogeny-method}), summing to $\mu_{\text{tot}}$ across the whole exome, and to $\mu_{\text{syn}}$ when restricted to synonymous mutations.
-    Finally, the mutational opportunities for synonymous mutations were computed as the total number of sites across the exome ($L_{\text{tot}}$) weighted by the proportion of synonymous mutations among all possible mutations as:
-
-    \begin{equation}
-        L_{\text{syn}} = L_{\text{tot}} \frac{\mu_{\text{syn}}}{\mu_{\text{tot}}}.
-    \end{equation}
-
-    Similarly, for non-synonymous mutations, the total mutation rate for each class of selection $\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$, called $\mu\left( \Sphyclass \right)$, was estimated as the sum across all non-synonymous mutations if their selection coefficient at the phylogenetic scale is in the class $\Sphy \in \Sphyclass$.
-    Accordingly, the mutational opportunities ($L \left( \Sphyclass \right)$) for each class of selection coefficient ($\Sphyclass$) was finally computed as the total number of sites across the exome ($L_{\text{tot}}$) weighted by the ratio of the aggregated mutations rates falling in the class $\mu\left( \Sphyclass \right)$:
-    \begin{equation}
-        L \left( \Sphyclass \right) = L_{\text{tot}} \frac{\mu\left( \Sphyclass \right)}{\mu_{\text{tot}}}.\label{eq:mutation-opp}
-    \end{equation}
-
-    Finally, $\proba [ \Sphyclass ]$ is the probability for a non-synonymous mutation to be in the class $\Sphyclass$, thus computed as:
-    \begin{equation}
-        \proba[\Sphyclass] = \frac{L\left( \Sphyclass \right)}{\sum_{\SphyclassAlt\in \{\SphyDel, \SphyNeu, \SphyBen \} } L\left(\SphyclassAlt \right)}.\label{eq:proba-dfe-mutsel}
-    \end{equation}
-
-    \subsection{Substitution mapping and $\dnds$ in the terminal branch}
-    \label{subsec:substitution-mapping-in-the-terminal-branch}
-    We inferred the protein-coding DNA sequences for each node of the 4-taxa tree containing the focal species and the three closest outgroups species found in the OrthoMaM alignment by applying the M5 codon model (gamma site rate variation) as implemented in FastML.v3.11~\cite{ashkenazy_fastml_2012}.
-    Consequently, for each focal species we reconstructed the protein coding DNA sequence of the whole exome at the base of the terminal branch before the split from the sister species.
-    We considered \textit{Ceratotherium simum simum} as \textit{Equus caballus'} sister species; \textit{Bison bison bison} as \textit{Bos taurus'} sister species; \textit{Pantholops hodgsonii} as \textit{Ovis aries'} sister species; \textit{Pantholops hodgsonii} as \textit{Capra hircus'} sister species; \textit{Macaca mulatta} as \textit{Chlorocebus sabaeus'} sister species and finally, we considered \textit{Pan troglodytes} as \textit{Homo sapiens'} sister species.
-    From this reconstructed exome, we determined the direction of the substitution occurring along the terminal branch of the phylogenetic tree toward each extant population.
-    SNPs segregating in the population were discarded, and the most likely ancestral state from est-usfs (see section \ref{subsec:polymorphism-dataset}) was used as the reference for each extant population.
-    For each substitution, we recovered its $\Sphy$ value as calculated through the phylogeny-based method (see section~\ref{subsec:s-phylogeny-method}).
-    Finally, the rate of non-synonymous over synonymous substitutions for a given class of selection coefficient ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$) was computed as:
-    \begin{align}
-        \begin{dcases}
-            \dn \left( \Sphyclass \right) &= \dfrac{D\left( \Sphyclass \right)}{L \left( \Sphyclass \right)}, \\
-            \ds &= \dfrac{D_{\text{syn}}}{L_{\text{syn}}},
-        \end{dcases}\label{eq:dnds}
-    \end{align}
-    where $D \left( \Sphyclass \right) $ was the number of non-synonymous substitutions in class $\Sphyclass$, $D_{\text{syn}}$ was the number of synonymous substitutions across the exome, while $L \left( \Sphyclass \right)$ and $L_{\text{syn}}$ were the numbers of non-synonymous and synonymous mutational opportunities, respectively, as defined in section~\ref{subsec:nunber-of-sites}.
-    $\delta(\dnds)$ was computed as the difference between $\dnds$ computed over all substitutions and $\dnds$ when we removed beneficial non-adaptive mutations $\dn (\Sphy < 1) / \ds$, normalized by $\dnds$.
-    Note that the quantities $\delta(\dnds)$ and $\delta(\dn)$ are equivalent due to the simplification of the factor $\ds$:
-    \begin{equation}
-        \delta(\dnds) = \dfrac{\dnds - \dn(\Sphy < 1) / \ds}{\dnds} = \dfrac{\dn - \dn(\Sphy < 1)}{\dn} = \delta(\dn).\label{eq:delta-dnds}
-    \end{equation}
-
-    \subsection{Scaled selection coefficients ($\Spop$) in a population-based method}
-    \label{subsec:s-polymorphism-method}
-
-    To obtain a quantitative estimate of the distribution of selection coefficients for each category of SNPs, we used the \textit{polyDFE} model~\cite{tataru_inference_2017, tataru_polydfe_2020}.
-    This model uses the count of derived alleles to infer the distribution of fitness effects (DFE).
-    The probability of sampling an allele at a given frequency (before fixation or extinction) is informative of its scaled selection coefficient at the population scale ($\Spop$).
-    Therefore, pooled across many sites, the site-frequency spectrum (SFS) provides information on the underlying $\Spop$ of mutations.
-    However, estimating a single $\Spop$ for all sampled mutations is biologically unrealistic, and a DFE of mutations is usually assumed~\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009}.
-    The \textit{polyDFE}\cite{tataru_inference_2017, tataru_polydfe_2020} software implements a mixture of a $\Gamma$ and exponential distributions to model the DFE of non-synonymous mutations, while synonymous mutations are considered neutral.
-    The model estimates the parameters $\DelMean$, $b$, $p_b$ and $\AdvMean$ for non-synonymous mutations as:
-
-    \begin{equation}
-        \label{eq:parametric-dfe}
-        \phi \left( \Spop; \DelMean , b, p_b, \AdvMean \right) =
-        \begin{dcases}
-            \left( 1 - p_b \right) f_{\Gamma}(-\Spop; -\DelMean, b) & \text{ if $\Spop \leq 0$,} \\
-            p_b f_{e}(\Spop; \AdvMean) & \text{ if $\Spop > 0$,} \\
-        \end{dcases}
-    \end{equation}
-
-    where $\DelMean \leq -1 $ is the estimated mean of the DFE for $\Spop \leq 0$;
-    $b \geq 0.2$ is the estimated shape of the $\Gamma$ distribution;
-    $0 \leq p_b \leq 1$ is the estimated probability that $\Spop > 0$;
-    $\AdvMean \geq 1$ is the estimated mean of the DFE for $\Spop > 0$;
-    and $f_{\Gamma}(\Spop; m, b)$ is the density of the $\Gamma$ distribution with mean $m$ and shape $b$, while $f_{e}(\Spop; m)$ is the density of the exponential distribution with mean $m$.
-
-    \textit{PolyDFE} requires one SFS for non-synonymous mutations and one for synonymous mutations (neutral expectation), as well as the number of sites on which each SFS was sampled.
-    For populations containing more than $8$ individuals, the SFS was subsampled down to $16$ chromosomes ($8$ diploid individuals) without replacement (hyper-geometric distribution) to alleviate the effect of different sampling depths in the 28 populations.
-    Altogether, for each class of selection ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$) of non-synonymous SNPs, we aggregated all the SNPs in the selection class $\Sphyclass$ as an SFS.
-    The number of sites on which each SFS was sampled is given by $L(\Sphyclass)$ for the non-synonymous SFS and $L_{\text{syn}}$ for the synonymous SFS respectively.
-    For each class of selection $\Sphyclass$, once fitted to the data using maximum likelihood with \textit{polyDFE}, the parameters of the DFE $\left( \DelMean , b, p_b, \AdvMean \right)$ were used to compute $\proba [ \SpopDel \given  \Sphyclass] $, $\proba [ \SpopNeu \given \Sphyclass]$, and $\proba [ \SpopBen \given \Sphyclass]$ as:
-
-    \begin{align}
-        \proba [ \SpopDel \given  \Sphyclass] &= \proba [ \Spop < -1 \given \Sphyclass ] = \left( 1 - p_b \right) \int_{-\infty}^{-1} f_{\Gamma}(-\Spop; -\DelMean, b) \der \Spop, \label{eq:polyProbaDel} \\
-        \proba [ \SpopNeu \given \Sphyclass] &= \proba [ -1 < \Spop < 1 \given \Sphyclass ] = \left( 1 - p_b \right) \int_{-1}^{0} f_{\Gamma}(-\Spop; -\DelMean, b) \der \Spop + p_b \int_{0}^{1} f_{e}(\Spop; \AdvMean) \der \Spop, \\
-        \proba [ \SpopBen \given \Sphyclass] &= \proba [ \Spop > 1 \given \Sphyclass] = p_b \int_{1}^{+\infty} f_{e}(\Spop; \AdvMean) \der \Spop. \label{eq:polyProbaAdv}
-    \end{align}
-
-    Rather than relying solely on currently segregating mutations to quantify selection, \textit{polyDFE} can leverage both divergence and polymorphism to estimate the parameters of the DFE.
-    We can thus add four more inputs to \textit{polyDFE}: $D \left( \Sphyclass \right) $, $L \left( \Sphyclass \right)$, $D_{\text{syn}}$ and $L_{\text{syn}}$ such as defined in the previous section.
-    Because the estimates of DFE are different with this method, we naturally obtained different values of $\proba [ \SpopDel \given  \Sphyclass] $, $\proba [ \SpopNeu \given \Sphyclass]$, and $\proba [ \SpopBen \given \Sphyclass]$.
-
-    \subsection{\textit{Precision} and \textit{recall}}
-    \label{subsec:precisison_recall}
-    For readability, we give here \textit{precision} and \textit{recall} for beneficial mutations ($\SphyBen$ and $\SpopBen$), but it can be obtained using the same derivation for the deleterious mutations ($\SphyDel$ and $\SpopDel$) and nearly-neutral mutations ($\SphyNeu$ and $\SpopNeu$).
-
-    \textit{Precision} is the proportion of mutations correctly predicted as beneficial ($\proba [ \SpopBen \cap  \SphyBen]$) out of all predicted as beneficial non-adaptive mutations ($\proba [ \SphyBen]$), which can be written as a conditional probability:
-
-    \begin{equation}
-        \frac{\proba [ \SpopBen  \cap  \SphyBen]}{\proba [ \SphyBen]} = \proba [ \SpopBen \given \SphyBen].
-        \label{eq:precision}
-    \end{equation}
-    Namely, \textit{precision} corresponds to the probability for a $\SphyBen$ mutation to be effectively beneficial at the population level ($\SpopBen$).
-    This probability, computed from eq.~\ref{eq:polyProbaAdv}, is obtained by restricting our analysis to SNPs that are predicted to be beneficial non-adaptive mutations (yellow fill for the category $\SphyBen$ in fig.~\ref{fig:homo-afr-results}D).
-
-    \textit{Recall} is the proportion of mutations correctly predicted as beneficial ($\proba [ \SpopBen \cap  \SphyBen]$) out of all beneficial mutations ($\proba [ \SpopBen]$), which can be written as a conditional probability:
-    \begin{equation}
-        \frac{\proba [ \SpopBen \cap  \SphyBen]}{\proba [ \SpopBen]} = \proba [ \SphyBen  \given \SpopBen ].
-    \end{equation}
-    Namely, \textit{recall} corresponds to the probability for a beneficial mutation at the population level ($\SpopBen$) to be a beneficial non-adaptive mutation ($\SphyBen$).
-    Using Bayes theorem, \textit{recall} can be re-written as:
-    \begin{equation}
-        \proba [\SphyBen \given \SpopBen] = \frac{\proba [\SpopBen \given \SphyBen] \times \proba[\SphyBen]}{\ProbaPopBen},
-        \label{eq:bayes}
-    \end{equation}
-
-    where $\proba [\SpopBen \given \SphyBen]$ and $\proba [ \SphyBen ]$ can be calculated using equations~\ref{eq:precision} and~\ref{eq:proba-dfe-mutsel}, respectively, and $\proba [ \SpopBen ]$ is the probability of a mutation to be beneficial at the level of the population, which can be computed from the law of total probabilities as:
-
-    \begin{equation}
-        \proba [ \SpopBen ] = \sum_{\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \} }\proba [\SpopBen \given \Sphyclass ] \times \proba [\Sphyclass ].
-        \label{eq:total_proba}
-    \end{equation}
-
-    \subsection{Correlation with effective population size ($\Ne$)}
-    \label{subsec:correlation-diversity}
-    Genetic diversity estimator Watterson's $\thetaSyn$ was obtained for each population from the synonymous SFS as in Achaz~\cite{achaz_frequency_2009}.
-    For each popuation, $\Ne$ was estimated from the equation $\Ne=\thetaSyn / (4 \times u)$, where $u$ is the mutation rate per generation.
-    Estimates for $u$ were averaged per species across the pedigree-based estimation in~\cite{bergeron_evolution_2023} for \textit{Homo}, \textit{Bos}, \textit{Capra} and \textit{Chlorocebus}.
-    For \textit{Ovis} we used the estimated $u$ of \textit{Capra}.
-    For \textit{Equus}, we used $u$ as estimated in Orlando \textit{et al.}~\cite{orlando_recalibrating_2013} ($u=7.24\times10^{-9}$).
-    Because a correlation must account for phylogenetic relationship and non-independence of samples, we fitted a Phylogenetic Generalized Linear Model in \textit{R} with the method \texttt{pgls} with default settings from the package \texttt{caper}~\cite{orme_caper_2013}.
-    The mammalian dated tree was obtained from TimeTree~\cite{kumar_timetree_2017} and pruned to include only the species analysed in this study, with multi-furcation of the different populations from each species placed at the same divergence time as the species (section S4.1).
-
-    \section*{Data availability}
-    The data underlying this article are available at \url{https://doi.org/10.5281/zenodo.7878953}.
-    Snakemake pipeline, analysis scripts and documentation are available at \href{https://github.com/ThibaultLatrille/SelCoeff}{github.com/ThibaultLatrille/SelCoeff}.
-
-    \section*{Acknowledgements}
-    \label{sec:acknowledgment}
-    We gratefully acknowledge the help of Mélodie Bastian, Nicolas Lartillot, Carina Farah Mugal, Laurent Duret, Alexandre Reymond, Daniele Silvestro and Nicolas Gambardella for their advice and reviews concerning this manuscript.
-    This work was performed using the computing facilities of the CC LBBE/PRABI\@.
-    This study makes use of data generated by the NextGen Consortium.
-    Funding:
-    Université de Lausanne; Agence Nationale de la Recherche, Grant ANR-19-CE12-0019 / HotRec.
-    The European Union’s Seventh Framework Programme (FP7/2010-2014) provided funding for the project under grant agreement no 244356 - “NextGen”.
-
-    \section*{Competing interests}
-    The authors declare no conflicts of interest.
-
-    \section*{Author information}
-    Original idea: T.L.\ and J.J.;
-    Model conception: T.L., J.J.\ and N.S.;
-    Code: T.L.;
-    Data analyses: T.L.\ and J.J.;
-    Interpretation: T.L., J.J., D.A.H.\ and N.S.;
-    First draft: T.L.\ and J.J.;
-    Editing and revisions: T.L., J.J., D.A.H.\ and N.S.
-    Project management and funding: N.S\@.
-
-    \begin{thebibliography}{10}
-
-        \bibitem{darwin_origin_1859}
-        Darwin C.
-        \newblock On the {{Origin}} of {{Species}} by {{Means}} of {{Natural
-        Selection}}, or the {{Preservation}} of {{Favoured Races}} in the
-            {{Struggle}} for {{Life}}. vol. 220.
-        \newblock John Murray; 1859.
-
-        \bibitem{merrell_adaptive_1994}
-        Merrell DJ.
-        \newblock The {{Adaptive Seascape}}: {{The Mechanism}} of {{Evolution}}.
-        \newblock U of Minnesota Press; 1994.
-
-        \bibitem{gavrilets_adaptive_2009}
-        Gavrilets S, Losos JB.
-        \newblock Adaptive {{Radiation}}: {{Contrasting Theory}} with {{Data}}.
-        \newblock Science. 2009;323(5915):732--737.
-        \newblock doi:{10.1126/science.1157966}.
-
-        \bibitem{enard_viruses_2016}
-        Enard D, Cai L, Gwennap C, Petrov DA.
-        \newblock Viruses Are a Dominant Driver of Protein Adaptation in Mammals.
-        \newblock eLife. 2016;5:e12469.
-        \newblock doi:{10.7554/eLife.12469}.
-
-        \bibitem{mcdonald_adaptative_1991}
-        McDonald JH, Kreitman M.
-        \newblock Adaptative Protein Evolution at {{Adh}} Locus in {{Drosophila}}.
-        \newblock Nature. 1991;351(6328):652--654.
-        \newblock doi:{10.1038/351652a0}.
-
-        \bibitem{smith_adaptive_2002}
-        Smith NGC, {Eyre-Walker} A.
-        \newblock Adaptive Protein Evolution in {{Drosophila}}.
-        \newblock Nature. 2002;415(6875):1022--1024.
-        \newblock doi:{10.1038/4151022a}.
-
-        \bibitem{welch_estimating_2006}
-        Welch JJ.
-        \newblock Estimating the {{Genomewide Rate}} of {{Adaptive Protein Evolution}}
-        in {{Drosophila}}.
-        \newblock Genetics. 2006;173(2):821--837.
-        \newblock doi:{10.1534/genetics.106.056911}.
-
-        \bibitem{yang_statistical_2000}
-        Yang Z, Bielawski JR.
-        \newblock Statistical Methods for Detecting Molecular Adaptation.
-        \newblock Trends in Ecology and Evolution. 2000;15(12):496--503.
-        \newblock doi:{10.1016/S0169-5347(00)01994-7}.
-
-        \bibitem{eyre-walker_genomic_2006}
-        {Eyre-Walker} A.
-        \newblock The Genomic Rate of Adaptive Evolution.
-        \newblock Trends in Ecology \& Evolution. 2006;21(10):569--575.
-        \newblock doi:{10.1016/j.tree.2006.06.015}.
-
-        \bibitem{moutinho_variation_2019}
-        Moutinho AF, Bataillon T, Dutheil JY.
-        \newblock Variation of the Adaptive Substitution Rate between Species and
-        within Genomes.
-        \newblock Evolutionary Ecology. 2019;34(3):315--338.
-        \newblock doi:{10.1007/s10682-019-10026-z}.
-
-        \bibitem{lynch_mutation_2023}
-        Lynch M.
-        \newblock Mutation Pressure, Drift, and the Pace of Molecular Coevolution.
-        \newblock Proceedings of the National Academy of Sciences.
-        2023;120(27):e2306741120.
-        \newblock doi:{10.1073/pnas.2306741120}.
-
-        \bibitem{charlesworth_other_2007}
-        Charlesworth J, {Eyre-Walker} A.
-        \newblock The Other Side of the Nearly Neutral Theory, Evidence of Slightly
-        Advantageous Back-Mutations.
-        \newblock Proceedings of the National Academy of Sciences.
-        2007;104(43):16992--16997.
-        \newblock doi:{10.1073/pnas.0705456104}.
-
-        \bibitem{mustonen_fitness_2009}
-        Mustonen V, L{\"a}ssig M.
-        \newblock From Fitness Landscapes to Seascapes: Non-Equilibrium Dynamics of
-        Selection and Adaptation.
-        \newblock Trends in genetics. 2009;25(3):111--119.
-        \newblock doi:{10.1016/j.tig.2009.01.002}.
-
-        \bibitem{jones_shifting_2017}
-        Jones CT, Youssef N, Susko E, Bielawski JP.
-        \newblock Shifting Balance on a Static Mutation--Selection Landscape: A Novel
-        Scenario of Positive Selection.
-        \newblock Molecular Biology and Evolution. 2017;34(2):391--407.
-        \newblock doi:{10.1093/molbev/msw237}.
-
-        \bibitem{ohta_nearly_1992}
-        Ohta T.
-        \newblock The Nearly Neutral Theory of Molecular Evolution.
-        \newblock Annual Review of Ecology and Systematics. 1992;23(1992):263--286.
-
-        \bibitem{gillespie_ohta_1995}
-        Gillespie JH.
-        \newblock On {{Ohta}}'s Hypothesis: {{Most}} Amino Acid Substitutions Are
-        Deleterious.
-        \newblock Journal of Molecular Evolution. 1995;40(1):64--69.
-        \newblock doi:{10.1007/BF00166596}.
-
-        \bibitem{hartl_compensatory_1996}
-        Hartl DL, Taubes CH.
-        \newblock Compensatory Nearly Neutral Mutations: {{Selection}} without
-        Adaptation.
-        \newblock Journal of Theoretical Biology. 1996;182(3):303--309.
-        \newblock doi:{10.1006/jtbi.1996.0168}.
-
-        \bibitem{sella_application_2005}
-        Sella G, Hirsh AE.
-        \newblock The Application of Statistical Physics to Evolutionary Biology.
-        \newblock Proceedings of the National Academy of Sciences of the United States
-        of America. 2005;102(27):9541--9546.
-        \newblock doi:{10.1073/pnas.0501865102}.
-
-        \bibitem{cvijovic_fate_2015}
-        Cvijovi{\'c} I, Good BH, Jerison ER, Desai MM.
-        \newblock Fate of a Mutation in a Fluctuating Environment.
-        \newblock Proceedings of the National Academy of Sciences.
-        2015;112(36):E5021--E5028.
-        \newblock doi:{10.1073/pnas.1505406112}.
-
-        \bibitem{piganeau_estimating_2003}
-        Piganeau G, {Eyre-Walker} A.
-        \newblock Estimating the Distribution of Fitness Effects from {{DNA}} Sequence
-        Data: {{Implications}} for the Molecular Clock.
-        \newblock Proceedings of the National Academy of Sciences of the United States
-        of America. 2003;100(18):10335--10340.
-        \newblock doi:{10.1073/pnas.1833064100}.
-
-        \bibitem{chi_detecting_2020}
-        Chi PB, Kosater WM, Liberles DA.
-        \newblock Detecting {{Signatures}} of {{Positive Selection}} against a
-            {{Backdrop}} of {{Compensatory Processes}}.
-        \newblock Molecular Biology and Evolution. 2020;37(11):3353--3362.
-        \newblock doi:{10.1093/molbev/msaa161}.
-
-        \bibitem{bazykin_changing_2015}
-        Bazykin GA.
-        \newblock Changing Preferences: Deformation of Single Position Amino Acid
-        Fitness Landscapes and Evolution of Proteins.
-        \newblock Biology letters. 2015;11(10):20150315.
-        \newblock doi:{10.1098/rsbl.2015.0315}.
-
-        \bibitem{moses_inferring_2009}
-        Moses AM, Durbin R.
-        \newblock Inferring {{Selection}} on {{Amino Acid Preference}} in {{Protein
-        Domains}}.
-        \newblock Molecular Biology and Evolution. 2009;26(3):527--536.
-        \newblock doi:{10.1093/molbev/msn286}.
-
-        \bibitem{fischer_germline_2011}
-        Fischer A, Greenman C, Mustonen V.
-        \newblock Germline {{Fitness-Based Scoring}} of {{Cancer Mutations}}.
-        \newblock Genetics. 2011;188(2):383--393.
-        \newblock doi:{10.1534/genetics.111.127480}.
-
-        \bibitem{chen_hunting_2021}
-        Chen J, Bataillon T, Gl{\'e}min S, Lascoux M.
-        \newblock Hunting for Beneficial Mutations: Conditioning on {{SIFT}} Scores
-        When Estimating the Distribution of Fitness Effect of New Mutations.
-        \newblock Genome Biology and Evolution. 2021;doi:{10.1093/gbe/evab151}.
-
-        \bibitem{halpern_evolutionary_1998}
-        Halpern AL, Bruno WJ.
-        \newblock Evolutionary Distances for Protein-Coding Sequences: Modeling
-        Site-Specific Residue Frequencies.
-        \newblock Molecular Biology and Evolution. 1998;15(7):910--917.
-        \newblock doi:{10.1093/oxfordjournals.molbev.a025995}.
-
-        \bibitem{mccandlish_modeling_2014}
-        McCandlish DM, Stoltzfus A.
-        \newblock Modeling Evolution Using the Probability of Fixation: {{History}} and
-        Implications.
-        \newblock Quarterly Review of Biology. 2014;89(3):225--252.
-        \newblock doi:{10.1086/677571}.
-
-        \bibitem{rodrigue_mechanistic_2010}
-        Rodrigue N, Philippe H.
-        \newblock Mechanistic Revisions of Phenomenological Modeling Strategies in
-        Molecular Evolution.
-        \newblock Trends in Genetics. 2010;26(6):248--252.
-        \newblock doi:{10.1016/j.tig.2010.04.001}.
-
-        \bibitem{tamuri_estimating_2012}
-        Tamuri AU, Goldstein RA.
-        \newblock Estimating the Distribution of Selection Coefficients from
-        Phylogenetic Data Using Sitewise Mutation-Selection Models.
-        \newblock Genetics. 2012;190(3):1101--1115.
-        \newblock doi:{10.1534/genetics.111.136432}.
-
-        \bibitem{rodrigue_detecting_2017}
-        Rodrigue N, Lartillot N.
-        \newblock Detecting Adaptation in Protein-Coding Genes Using a {{Bayesian}}
-        Site- Heterogeneous Mutation-Selection Codon Substitution Model.
-        \newblock Molecular Biology and Evolution. 2017;34(1):204--214.
-        \newblock doi:{10.1093/molbev/msw220}.
-
-        \bibitem{foley_genomic_2023}
-        Foley NM, Mason VC, Harris AJ, Bredemeyer KR, Damas J, Lewin HA, et~al.
-        \newblock A Genomic Timescale for Placental Mammal Evolution.
-        \newblock Science. 2023;380(6643):eabl8189.
-        \newblock doi:{10.1126/science.abl8189}.
-
-        \bibitem{howe_ensembl_2021}
-        Howe KL, Achuthan P, Allen J, Allen J, {Alvarez-Jarreta} J, Amode MR, et~al.
-        \newblock Ensembl 2021.
-        \newblock Nucleic Acids Research. 2021;49(D1):D884--D891.
-        \newblock doi:{10.1093/nar/gkaa942}.
-
-        \bibitem{ranwez_orthomam_2007}
-        Ranwez V, Delsuc F, Ranwez S, Belkhir K, Tilak MK, Douzery EJ.
-        \newblock {{OrthoMaM}}: {{A}} Database of Orthologous Genomic Markers for
-        Placental Mammal Phylogenetics.
-        \newblock BMC Evolutionary Biology. 2007;7(1):1--12.
-        \newblock doi:{10.1186/1471-2148-7-241}.
-
-        \bibitem{scornavacca_orthomam_2019}
-        Scornavacca C, Belkhir K, Lopez J, Dernat R, Delsuc F, Douzery EJP, et~al.
-        \newblock {{OrthoMaM}} V10: {{Scaling-up}} Orthologous Coding Sequence and Exon
-        Alignments with More than One Hundred Mammalian Genomes.
-        \newblock Molecular Biology and Evolution. 2019;36(4):861--862.
-        \newblock doi:{10.1093/molbev/msz015}.
-
-        \bibitem{rodrigue_mutationselection_2010}
-        Rodrigue N, Philippe H, Lartillot N.
-        \newblock Mutation-Selection Models of Coding Sequence Evolution with
-        Site-Heterogeneous Amino Acid Fitness Profiles.
-        \newblock Proceedings of the National Academy of Sciences of the United States
-        of America. 2010;107(10):4629--34.
-        \newblock doi:{10.1073/pnas.0910915107}.
-
-        \bibitem{landrum_clinvar_2018}
-        Landrum MJ, Lee JM, Benson M, Brown GR, Chao C, Chitipiralla S, et~al.
-        \newblock {{ClinVar}}: Improving Access to Variant Interpretations and
-        Supporting Evidence.
-        \newblock Nucleic Acids Research. 2018;46(D1):D1062--D1067.
-        \newblock doi:{10.1093/nar/gkx1153}.
-
-        \bibitem{grimm_evaluation_2015}
-        Grimm DG, Azencott CA, Aicheler F, Gieraths U, MacArthur DG, Samocha KE, et~al.
-        \newblock The {{Evaluation}} of {{Tools Used}} to {{Predict}} the {{Impact}} of
-            {{Missense Variants Is Hindered}} by {{Two Types}} of {{Circularity}}.
-        \newblock Human Mutation. 2015;36(5):513--523.
-        \newblock doi:{10.1002/humu.22768}.
-
-        \bibitem{sullivan_leveraging_2023}
-        Sullivan PF, Meadows JRS, Gazal S, Phan BN, Li X, Genereux DP, et~al.
-        \newblock Leveraging Base-Pair Mammalian Constraint to Understand Genetic
-        Variation and Human Disease.
-        \newblock Science. 2023;380(6643):eabn2937.
-        \newblock doi:{10.1126/science.abn2937}.
-
-        \bibitem{eyre-walker_distribution_2006}
-        {Eyre-Walker} A, Woolfit M, Phelps T.
-        \newblock The Distribution of Fitness Effects of New Deleterious Amino Acid
-        Mutations in Humans.
-        \newblock Genetics. 2006;173(2):891--900.
-        \newblock doi:{10.1534/genetics.106.057570}.
-
-        \bibitem{eyre-walker_estimating_2009}
-        {Eyre-Walker} A, Keightley PD.
-        \newblock Estimating the {{Rate}} of {{Adaptive Molecular Evolution}} in the
-            {{Presence}} of {{Slightly Deleterious Mutations}} and {{Population Size
-        Change}}.
-        \newblock Molecular Biology and Evolution. 2009;26(9):2097--2108.
-        \newblock doi:{10.1093/molbev/msp119}.
-
-        \bibitem{galtier_adaptive_2016}
-        Galtier N.
-        \newblock Adaptive Protein Evolution in Animals and the Effective Population
-        Size Hypothesis.
-        \newblock PLoS Genetics. 2016;12(1):e1005774.
-        \newblock doi:{10.1371/journal.pgen.1005774}.
-
-        \bibitem{tataru_inference_2017}
-        Tataru P, Mollion M, Gl{\'e}min S, Bataillon T.
-        \newblock Inference of Distribution of Fitness Effects and Proportion of
-        Adaptive Substitutions from Polymorphism Data.
-        \newblock Genetics. 2017;207(3):1103--1119.
-        \newblock doi:{10.1534/genetics.117.300323}.
-
-        \bibitem{bergeron_evolution_2023}
-        Bergeron LA, Besenbacher S, Zheng J, Li P, Bertelsen MF, Quintard B, et~al.
-        \newblock Evolution of the Germline Mutation Rate across Vertebrates.
-        \newblock Nature. 2023; p. 1--7.
-        \newblock doi:{10.1038/s41586-023-05752-y}.
-
-        \bibitem{orlando_recalibrating_2013}
-        Orlando L, Ginolhac A, Zhang G, Froese D, Albrechtsen A, Stiller M, et~al.
-        \newblock Recalibrating {{Equus}} Evolution Using the Genome Sequence of an
-        Early {{Middle Pleistocene}} Horse.
-        \newblock Nature. 2013;499(7456):74--78.
-        \newblock doi:{10.1038/nature12323}.
-
-        \bibitem{achaz_frequency_2009}
-        Achaz G.
-        \newblock Frequency {{Spectrum Neutrality Tests}}: {{One}} for {{All}} and
-            {{All}} for {{One}}.
-        \newblock Genetics. 2009;183(1):249--258.
-        \newblock doi:{10.1534/genetics.109.104042}.
-
-        \bibitem{latrille_genes_2023}
-        Latrille T, Rodrigue N, Lartillot N.
-        \newblock Genes and Sites under Adaptation at the Phylogenetic Scale Also
-        Exhibit Adaptation at the Population-Genetic Scale.
-        \newblock Proceedings of the National Academy of Sciences of the United States
-        of America. 2023;120(11):e2214977120.
-        \newblock doi:{10.1073/pnas.2214977120}.
-
-        \bibitem{ng_sift_2003}
-        Ng PC, Henikoff S.
-        \newblock {{SIFT}}: Predicting Amino Acid Changes That Affect Protein Function.
-        \newblock Nucleic Acids Research. 2003;31(13):3812--3814.
-        \newblock doi:{10.1093/nar/gkg509}.
-
-        \bibitem{vaser_sift_2016}
-        Vaser R, Adusumalli S, Leng SN, Sikic M, Ng PC.
-        \newblock {{SIFT}} Missense Predictions for Genomes.
-        \newblock Nature Protocols. 2016;11(1):1--9.
-        \newblock doi:{10.1038/nprot.2015.123}.
-
-        \bibitem{keightley_what_2010}
-        Keightley PD, {Eyre-Walker} A.
-        \newblock What Can We Learn about the Distribution of Fitness Effects of New
-        Mutations from {{DNA}} Sequence Data?
-        \newblock Philosophical Transactions of the Royal Society B: Biological
-        Sciences. 2010;365(1544):1187--1193.
-        \newblock doi:{10.1098/rstb.2009.0266}.
-
-        \bibitem{rice_evolutionarily_2015}
-        Rice DP, Good BH, Desai MM.
-        \newblock The {{Evolutionarily Stable Distribution}} of {{Fitness Effects}}.
-        \newblock Genetics. 2015;200(1):321--329.
-        \newblock doi:{10.1534/genetics.114.173815}.
-
-        \bibitem{mustonen_fitness_2010}
-        Mustonen V, L{\"a}ssig M.
-        \newblock Fitness Flux and Ubiquity of Adaptive Evolution.
-        \newblock Proceedings of the National Academy of Sciences.
-        2010;107(9):4248--4253.
-        \newblock doi:{10.1073/pnas.0907953107}.
-
-        \bibitem{eyre-walker_how_2014}
-        {Eyre-Walker} A, {Eyre-Walker} YC.
-        \newblock How Much of the Variation in the Mutation Rate along the Human Genome
-        Can Be Explained?
-        \newblock G3: Genes, Genomes, Genetics. 2014;4(9):1667--1670.
-        \newblock doi:{10.1534/g3.114.012849}.
-
-        \bibitem{mustonen_molecular_2008}
-        Mustonen V, L{\"a}ssig M.
-        \newblock Molecular {{Evolution}} under {{Fitness Fluctuations}}.
-        \newblock Physical Review Letters. 2008;100(10):108101.
-        \newblock doi:{10.1103/PhysRevLett.100.108101}.
-
-        \bibitem{latrille_inferring_2021}
-        Latrille T, Lanore V, Lartillot N.
-        \newblock Inferring Long-Term Effective Population Size with
-        Mutation--Selection Models.
-        \newblock Molecular Biology and Evolution. 2021;38(10):4573--4587.
-        \newblock doi:{10.1093/molbev/msab160}.
-
-        \bibitem{huber_determining_2017}
-        Huber CD, Kim BY, Marsden CD, Lohmueller KE.
-        \newblock Determining the Factors Driving Selective Effects of New
-        Nonsynonymous Mutations.
-        \newblock Proceedings of the National Academy of Sciences.
-        2017;114(17):4465--4470.
-        \newblock doi:{10.1073/pnas.1619508114}.
-
-        \bibitem{lanfear_population_2014}
-        Lanfear R, Kokko H, {Eyre-Walker} A.
-        \newblock Population Size and the Rate of Evolution.
-        \newblock Trends in Ecology and Evolution. 2014;29(1):33--41.
-        \newblock doi:{10.1016/j.tree.2013.09.009}.
-
-        \bibitem{platt_protein_2018}
-        Platt A, Weber CC, Liberles DA.
-        \newblock Protein Evolution Depends on Multiple Distinct Population Size
-        Parameters.
-        \newblock BMC Evolutionary Biology. 2018;18(1):1--9.
-        \newblock doi:{10.1186/s12862-017-1085-x}.
-
-        \bibitem{starr_epistasis_2016}
-        Starr TN, Thornton JW.
-        \newblock Epistasis in Protein Evolution.
-        \newblock Protein Science. 2016;25(7):1204--1218.
-        \newblock doi:{10.1002/pro.2897}.
-
-        \bibitem{morcos_directcoupling_2011}
-        Morcos F, Pagnani A, Lunt B, Bertolino A, Marks DS, Sander C, et~al.
-        \newblock Direct-Coupling Analysis of Residue Coevolution Captures Native
-        Contacts across Many Protein Families.
-        \newblock Proceedings of the National Academy of Sciences.
-        2011;108(49):E1293--E1301.
-        \newblock doi:{10.1073/pnas.1111471108}.
-
-        \bibitem{marks_protein_2012}
-        Marks DS, Hopf TA, Sander C.
-        \newblock Protein Structure Prediction from Sequence Variation.
-        \newblock Nature Biotechnology. 2012;30(11):1072--1080.
-        \newblock doi:{10.1038/nbt.2419}.
-
-        \bibitem{goldstein_nonadaptive_2015}
-        Goldstein RA, Pollard ST, Shah SD, Pollock DD.
-        \newblock Nonadaptive {{Amino Acid Convergence Rates Decrease}} over {{Time}}.
-        \newblock Molecular Biology and Evolution. 2015;32(6):1373--1381.
-        \newblock doi:{10.1093/molbev/msv041}.
-
-        \bibitem{goldstein_sequence_2017}
-        Goldstein RA, Pollock DD.
-        \newblock Sequence Entropy of Folding and the Absolute Rate of Amino Acid
-        Substitutions.
-        \newblock Nature Ecology \& Evolution. 2017;1(12):1923--1930.
-        \newblock doi:{10.1038/s41559-017-0338-9}.
-
-        \bibitem{park_epistatic_2022}
-        Park Y, Metzger BPH, Thornton JW.
-        \newblock Epistatic Drift Causes Gradual Decay of Predictability in Protein
-        Evolution.
-        \newblock Science. 2022;376(6595):823--830.
-        \newblock doi:{10.1126/science.abn6895}.
-
-        \bibitem{ashenberg_mutational_2013}
-        Ashenberg O, Gong LI, Bloom JD.
-        \newblock Mutational Effects on Stability Are Largely Conserved during Protein
-        Evolution.
-        \newblock Proceedings of the National Academy of Sciences of the United States
-        of America. 2013;110(52):21071--21076.
-        \newblock doi:{10.1073/pnas.1314781111}.
-
-        \bibitem{doud_sitespecific_2015}
-        Doud MB, Ashenberg O, Bloom JD.
-        \newblock Site-{{Specific Amino Acid Preferences Are Mostly Conserved}} in
-            {{Two Closely Related Protein Homologs}}.
-        \newblock Molecular Biology and Evolution. 2015;32(11):2944--2960.
-        \newblock doi:{10.1093/molbev/msv167}.
-
-        \bibitem{bloom_identification_2017}
-        Bloom JD.
-        \newblock Identification of Positive Selection in Genes Is Greatly Improved by
-        Using Experimentally Informed Site-Specific Models.
-        \newblock Biology Direct. 2017;12(1):1--24.
-        \newblock doi:{10.1186/s13062-016-0172-z}.
-
-        \bibitem{youssef_consequences_2020}
-        Youssef N, Susko E, Bielawski JP.
-        \newblock Consequences of Stability-Induced Epistasis for Substitution Rates.
-        \newblock Molecular Biology and Evolution. 2020;doi:{10.1093/molbev/msaa151}.
-
-        \bibitem{vigue_deciphering_2022}
-        Vigu{\'e} L, Croce G, Petitjean M, Rupp{\'e} E, Tenaillon O, Weigt M.
-        \newblock Deciphering Polymorphism in 61,157 {{Escherichia}} Coli Genomes via
-        Epistatic Sequence Landscapes.
-        \newblock Nature Communications. 2022;13(1):4030.
-        \newblock doi:{10.1038/s41467-022-31643-3}.
-
-        \bibitem{kimura_evolutionary_1968}
-        Kimura M.
-        \newblock Evolutionary Rate at the Molecular Level.
-        \newblock Nature. 1968;217(5129):624--626.
-
-        \bibitem{gillespie_substitution_1994}
-        Gillespie JH.
-        \newblock Substitution Processes in Molecular Evolution. {{III}}.
-            {{Deleterious}} Alleles.
-        \newblock Genetics. 1994;138(3):943--952.
-        \newblock doi:{10.1093/genetics/138.3.943}.
-
-        \bibitem{jensen_importance_2019}
-        Jensen JD, Payseur BA, Stephan W, Aquadro CF, Lynch M, Charlesworth D, et~al.
-        \newblock The Importance of the {{Neutral Theory}} in 1968 and 50 Years on:
-            {{A}} Response to {{Kern}} and {{Hahn}} 2018.
-        \newblock Evolution. 2019;73(1):111--114.
-        \newblock doi:{10.1111/evo.13650}.
-
-        \bibitem{galtier_half_2024}
-        Galtier N.
-        \newblock Half a {{Century}} of {{Controversy}}: {{The
-        Neutralist}}/{{Selectionist Debate}} in {{Molecular Evolution}}.
-        \newblock Genome Biology and Evolution. 2024;16(2):evae003.
-        \newblock doi:{10.1093/gbe/evae003}.
-
-        \bibitem{galtier_adaptation_2007}
-        Galtier N, Duret L.
-        \newblock Adaptation or Biased Gene Conversion? {{Extending}} the Null
-        Hypothesis of Molecular Evolution.
-        \newblock Trends in Genetics. 2007;23(6):273--277.
-        \newblock doi:{10.1016/j.tig.2007.03.011}.
-
-        \bibitem{rousselle_influence_2019}
-        Rousselle M, Laverr{\'e} A, Figuet E, Nabholz B, Galtier N.
-        \newblock Influence of {{Recombination}} and {{GC-biased Gene Conversion}} on
-        the {{Adaptive}} and {{Nonadaptive Substitution Rate}} in {{Mammals}} versus
-            {{Birds}}.
-        \newblock Molecular Biology and Evolution. 2019;36(3):458--471.
-        \newblock doi:{10.1093/molbev/msy243}.
-
-        \bibitem{joseph_increased_2024a}
-        Joseph J.
-        \newblock Increased {{Positive Selection}} in {{Highly Recombining Genes Does}}
-        Not {{Necessarily Reflect}} an {{Evolutionary Advantage}} of
-            {{Recombination}}.
-        \newblock Molecular Biology and Evolution. 2024; p. msae107.
-        \newblock doi:{10.1093/molbev/msae107}.
-
-        \bibitem{ohta_development_1996}
-        Ohta T, Gillespie JH.
-        \newblock Development of {{Neutral}} and {{Nearly Neutral Theories}}.
-        \newblock Theoretical Population Biology. 1996;49(2):128--142.
-        \newblock doi:{10.1006/tpbi.1996.0007}.
-
-        \bibitem{spielman_relationship_2015}
-        Spielman SJ, Wilke CO.
-        \newblock The Relationship between {{dN}}/{{dS}} and Scaled Selection
-        Coefficients.
-        \newblock Molecular biology and evolution. 2015;32(4):1097--1108.
-        \newblock doi:{10.1093/molbev/msv003}.
-
-        \bibitem{dosreis_how_2015}
-        Dos~Reis M.
-        \newblock How to Calculate the Non-Synonymous to Synonymous Rate Ratio of
-        Protein-Coding Genes under the Fisher-Wright Mutation-Selection Framework.
-        \newblock Biology Letters. 2015;11(4):20141031.
-        \newblock doi:{10.1098/rsbl.2014.1031}.
-
-        \bibitem{rodrigue_bayesian_2021}
-        Rodrigue N, Latrille T, Lartillot N.
-        \newblock A {{Bayesian}} Mutation-Selection Framework for Detecting
-        Site-Specific Adaptive Evolution in Protein-Coding Genes.
-        \newblock Molecular Biology and Evolution. 2021;38(3):1199--1208.
-        \newblock doi:{10.1093/molbev/msaa265}.
-
-        \bibitem{tamuri_mutationselection_2021}
-        Tamuri AU, {dos Reis} M.
-        \newblock A Mutation-Selection Model of Protein Evolution under Persistent
-        Positive Selection.
-        \newblock Molecular Biology and Evolution. 2021;doi:{10.1093/molbev/msab309}.
-
-        \bibitem{kazmi_detecting_2019}
-        Kazmi SO, Rodrigue N.
-        \newblock Detecting Amino Acid Preference Shifts with Codon-Level
-        Mutation-Selection Mixture Models.
-        \newblock BMC Evolutionary Biology. 2019;19(1):62.
-        \newblock doi:{10.1186/s12862-019-1358-7}.
-
-        \bibitem{stolyarova_senescence_2020}
-        Stolyarova AV, Nabieva E, Ptushenko VV, Favorov AV, Popova AV, Neverov AD,
-        et~al.
-        \newblock Senescence and Entrenchment in Evolution of Amino Acid Sites.
-        \newblock Nature Communications. 2020;11(1):4603.
-        \newblock doi:{10.1038/s41467-020-18366-z}.
-
-        \bibitem{douzery_orthomam_2014}
-        Douzery EJP, Scornavacca C, Romiguier J, Belkhir K, Galtier N, Delsuc F, et~al.
-        \newblock {{OrthoMaM}} v8: {{A}} Database of Orthologous Exons and Coding
-        Sequences for Comparative Genomics in Mammals.
-        \newblock Molecular Biology and Evolution. 2014;31(7):1923--1928.
-        \newblock doi:{10.1093/molbev/msu132}.
-
-        \bibitem{yang_mutationselection_2008}
-        Yang Z, Nielsen R.
-        \newblock Mutation-Selection Models of Codon Substitution and Their Use to
-        Estimate Selective Strengths on Codon Usage.
-        \newblock Molecular Biology and Evolution. 2008;25(3):568--579.
-        \newblock doi:{10.1093/molbev/msm284}.
-
-        \bibitem{wright_evolution_1931}
-        Wright S.
-        \newblock Evolution in {{Mendelian}} Populations.
-        \newblock Genetics. 1931;16(2):97--159.
-        \newblock doi:{10.1093/genetics/16.2.97}.
-
-        \bibitem{fisher_genetical_1930}
-        Fisher RA.
-        \newblock The {{Genetical Theory}} of {{Natural Selection}}.
-        \newblock The Clarendon Press; 1930.
-
-        \bibitem{rodrigue_bayesian_2008}
-        Rodrigue N, Lartillot N, Philippe H.
-        \newblock Bayesian Comparisons of Codon Substitution Models.
-        \newblock Genetics. 2008;180(3):1579--1591.
-        \newblock doi:{10.1534/genetics.108.092254}.
-
-        \bibitem{lartillot_bayesian_2004}
-        Lartillot N.
-        \newblock A Bayesian Mixture Model for Across-Site Heterogeneities in the
-        Amino-Acid Replacement Process.
-        \newblock Molecular biology and evolution. 2004;21(6):1095--1109.
-        \newblock doi:{10.1093/molbev/msh112}.
-
-        \bibitem{lartillot_inference_2013}
-        Lartillot N.
-        \newblock Inf{\'e}rence Probabiliste Pour La Phylog{\'e}nie, La G{\'e}nomique
-        Comparative et Les Sciences de La Macro-{\'E}volution; 2013.
-
-        \bibitem{alabri_whole_2020}
-        Al~Abri MA, Holl HM, Kalla SE, Sutter NB, Brooks SA.
-        \newblock Whole Genome Detection of Sequence and Structural Polymorphism in Six
-        Diverse Horses.
-        \newblock PLoS ONE. 2020;15(4):e0230899.
-        \newblock doi:{10.1371/journal.pone.0230899}.
-
-        \bibitem{sherry_dbsnp_2001}
-        Sherry ST, Ward MH, Kholodov M, Baker J, Phan L, Smigielski EM, et~al.
-        \newblock {{dbSNP}}: The {{NCBI}} Database of Genetic Variation.
-        \newblock Nucleic Acids Research. 2001;29(1):308--311.
-        \newblock doi:{10.1093/nar/29.1.308}.
-
-        \bibitem{svardal_ancient_2017}
-        Svardal H, Jasinska AJ, Apetrei C, Coppola G, Huang Y, Schmitt CA, et~al.
-        \newblock Ancient Hybridization and Strong Adaptation to Viruses across
-            {{African}} Vervet Monkey Populations.
-        \newblock Nature Genetics. 2017;49(12):1705--1713.
-        \newblock doi:{10.1038/ng.3980}.
-
-        \bibitem{zheng-bradley_alignment_2017}
-        {Zheng-Bradley} X, Streeter I, Fairley S, Richardson D, Clarke L, Flicek P,
-        et~al.
-        \newblock Alignment of 1000 {{Genomes Project}} Reads to Reference Assembly
-            {{GRCh38}}.
-        \newblock GigaScience. 2017;6(7):gix038.
-        \newblock doi:{10.1093/gigascience/gix038}.
-
-        \bibitem{keightley_inferring_2018}
-        Keightley PD, Jackson BC.
-        \newblock Inferring the Probability of the Derived vs the Ancestral Allelic
-        State at a Polymorphic Site.
-        \newblock Genetics. 2018;209(3):897--906.
-        \newblock doi:{10.1534/genetics.118.301120}.
-
-        \bibitem{ashkenazy_fastml_2012}
-        Ashkenazy H, Penn O, {Doron-Faigenboim} A, Cohen O, Cannarozzi G, Zomer O,
-        et~al.
-        \newblock {{FastML}}: A Web Server for Probabilistic Reconstruction of
-        Ancestral Sequences.
-        \newblock Nucleic Acids Research. 2012;40(W1):W580--W584.
-        \newblock doi:{10.1093/nar/gks498}.
-
-        \bibitem{tataru_polydfe_2020}
-        Tataru P, Bataillon T.
-        \newblock {{polyDFE}}: {{Inferring}} the Distribution of Fitness Effects and
-        Properties of Beneficial Mutations from Polymorphism Data.
-        \newblock In: Methods in {{Molecular Biology}}. vol. 2090. Humana Press Inc.;
-        2020. p. 125--146.
-
-        \bibitem{orme_caper_2013}
-        Orme D, Freckleton R, Thomas G, Petzoldt T, Fritz S, Isaac N, et~al.
-        \newblock The Caper Package: Comparative Analysis of Phylogenetics and
-        Evolution in {{R}}.
-        \newblock R package version. 2013;5(2):1--36.
-
-        \bibitem{kumar_timetree_2017}
-        Kumar S, Stecher G, Suleski M, Hedges SB.
-        \newblock {{TimeTree}}: A Resource for Timelines, Timetrees, and Divergence
-        Times.
-        \newblock Molecular Biology and Evolution. 2017;34(7):1812--1819.
-        \newblock doi:{10.1093/molbev/msx116}.
-
-    \end{thebibliography}
-
-    \newpage
-    \section*{Supplementary figures and tables}
-    \subsection*{List of Figures}
-    \begin{itemize}
-        \item S1: Bayesian hierarchical model (p.5).
-        \item S2: Examples sites of $\SphyBen$ mutations in \textit{Chlorocebus sabaeus} (reversions) (p.10).
-        \item S3: Examples sites of $\SphyBen$ mutations in \textit{Chlorocebus sabaeus} (p.11).
-        \item S4: Enrichment in $\SphyBen$ SNPs across all gene ontology terms (p.17).
-        \item S5: Estimation of selection at the population scale for $\SphyDel$ mutations (p.19).
-        \item S6: Estimation of selection at the population scale for $\SphyNeu$ mutations (p.19).
-        \item S7: Estimation of selection at the population scale for $\SphyBen$ mutations (p.19).
-        \item S8: Distribution of scaled selection coefficients ($\Sphy$) (p.20).
-        \item S9: Tree used for PGLM (Phylogenetic Generalized Linear Model) (p.21).
-        \item S10: Proportion of deleterious mutations ($\SpopDel$) (p.22).
-        \item S11: Proportion of nearly-neutral mutations ($\SpopNeu$) (p.23).
-        \item S12: Proportion of beneficial mutations ($\SpopBen$) (p.24).
-        \item S13: $\proba[\SphyBen\given \SpopBen ]$ as a function of distance to the sister species (p.26).
-        \item S14: Ratio of $\proba[\Sphy]$ over $\proba[-\Sphy]$ for polymorphisms of the African population of \textit{Homo sapiens} (p.27).
-        \item S15: Simulations of site-frequency spectra (p.29).
-        \item S16: Site-frequency spectrum in African population of \textit{Homo sapiens}, masking CpG transitions  (p.32).
-        \item S17: Site-frequency spectrum in South African population of \textit{Chlorocebus sabaeus}, masking CpG transitions (p.32).
-        \item S18: Including substitutions in the terminal lineage to estimate $\Spop$ (p.34).
-        \item S19: $\proba[\SphyBen\given \SpopBen ]$ while including divergence to estimate $\Spop$, as a function of distance to the sister species (p.37).
-        \item S20: $\proba [ \SpopDel ]$ when fitting a single or three DFEs (p.40).
-        \item S21: $\proba [ \SpopNeu ]$ when fitting a single or three DFEs (p.40).
-        \item S22: $\proba [ \SpopBen ]$ when fitting a single or three DFEs (p.40).
-    \end{itemize}
-
-    \newpage
-    \subsection*{List of Tables}
-    \begin{itemize}
-    \item S1: Probability of mutations and substitutions to be $\SphyDel$, $\SphyNeu$ or $\SphyBen$ (p.12).
-    \item S2: $\dnds$ for $\SphyDel$, $\SphyNeu$ or $\SphyBen$ (p.13).
-    \item S3: $\dnds$ over-estimation due to non-adaptive beneficial mutations (p.14).
-    \item S4: Gene ontology enrichment in $\SphyBen$ SNPs (p.15).
-    \item S5: Terms associated with deleterious mutations $\SphyDel$ (p.18).
-    \item S6: Terms associated with non-adaptive beneficial mutations $\SphyBen$ (p.18).
-    \item S7: Probability for beneficial mutations to be non-adaptive ($\proba[\SphyBen\given \SpopBen ]$) (p.25).
-    \item S8: $\proba[\SphyBen\given \SpopBen ]$ while masking CpG transitions (p.30).
-    \item S9: Precision and recall while masking CpG transitions (p.31).
-    \item S10: $\proba[\SphyBen\given \SpopBen ]$ excluding or not genes under adaptation (p.33).
-    \item S11: $\proba[\SphyBen\given \SpopBen ]$ when including divergence to estimate $\Spop$ (p.35).
-    \item S12: Precision and recall while including divergence to estimate $\Spop$ (p.36).
-    \item S13: $\proba[\SphyBen\given \SpopBen ]$ excluding or not genes under adaptation, when including divergence to estimate $\Spop$ (p.38).
-    \item S14: $\proba[\SphyBen\given \SpopBen ]$ when using a discrete DFE to estimate $\Spop$ (p.41).
-    \item S15: Precision and recall when using a discrete DFE to estimate $\Spop$ (p.42).
-    \end{itemize}
-
-    \newpage
-    \begin{figure*}[!htb]
+\begin{figure}[!ht]
+\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
 \centering
-        \includegraphics[width=\textwidth, page=1] {figure1.eps}
-        \caption{
-            (A \& B) For a given codon position of a protein-coding DNA sequence, amino acids (x-axis) have different fitness values (y-axis).
-            Under a changing fitness landscape (A), these fitnesses fluctuate with time.
-            The protein sequence follows the moving target defined by the amino-acid fitnesses.
-Since substitutions are preferentially accepted if they are in the direction of this target, substitutions are, on average, adaptive.
-            At the phylogenetic scale (C), beneficial substitutions are common (positive signs), promoting phenotype diversification across species.
-            Under a stable fitness landscape (B), most mutations reaching fixation are either slightly deleterious reaching fixation due to drift or are beneficial non-adaptive mutations restoring a more optimal amino acid.
-            At the phylogenetic scale (D), deleterious substitutions (negative signs) are often reverted via beneficial non-adaptive mutations (positive signs), promoting phenotype stability and preserving well-established biological systems.
-            Even though, individually, any beneficial non-adaptive mutation might have a weak effect on its bearer, we expect them to be scattered across the genome and the genome-wide signature of beneficial non-adaptive mutations to be detectable and quantifiable.}
-        \label{fig:fitness-landscape}
-    \end{figure*}
-
-    \begin{figure*}[!h]
-        \centering
-        \includegraphics[width=\textwidth, page=1] {figure2.eps}
-        \caption{
-            Selection coefficients at the phylogenetic and population scales.
-            At the phylogenetic scale (A), we estimated the amino-acid fitness for each site from protein-coding DNA alignments using mutation-selection codon models.
-            For every possible mutation, the difference in amino-acid fitness before and after the mutation allows us to compute the selection coefficient at the phylogenetic scale ($\Sphy$).
-            Depending on $\Sphy$ (B) mutations can be predicted as deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) or beneficial non-adaptive mutations ($\SphyBen$) toward a fitter amino acid and repairing existing functions.
-            At the population scale, each observed single nucleotide polymorphism (SNP) segregating in the population can also be classified according to its $\Sphy$ value (C).
-            Occurrence and frequency in the population of non-synonymous polymorphisms, contrasted to synonymous polymorphisms (deemed neutral) is used to estimate selection coefficients (D-E) at the population scale ($\Spop$), for each class of selection ($\SphyDel$, $\SphyNeu$, $\SphyBen$).
-            We can thus assess whether $\Sphy$ predicts $\Spop$ and compute \textit{precision} (F) and \textit{recall} (G) for each class.
-            The \textit{recall} value for class $\SphyBen$ is the probability for beneficial mutations to be non-adaptive (G).
-            Icons are adapted from \href{https://phylopic.org}{https://phylopic.org} under a Creative Commons license.
-        }
-        \label{fig:method}
-    \end{figure*}
-
-    \begin{figure*}[!h]
-        \centering
-        \includegraphics[width=\textwidth, page=1] {figure3.eps}
+\includegraphics[width=1.4\textwidth, page=1] {figure3.eps}
 \caption{
@@
 \label{fig:homo-afr-results}
-    \end{figure*}
-
-    \begin{figure*}[!ht]
+\end{adjustwidth}
+\end{figure}
+
+Furthermore, since in principle, $\SphyBen$ mutations are bound to reach fixation more often than neutral mutations, we calculated the $\dnds$ ratio of non-synonymous over synonymous divergence for all terminal lineages, focusing on the non-synonymous changes predicted as $\SphyBen$ mutations ($\dn(\SphyBen) / \ds$).
+We obtained values between 1.17 and 1.75 in the different lineages (table~S2), meaning that $\SphyBen$ mutations reach fixation slightly more frequently than synonymous mutations that are supposed to be neutral, consistent with these $\SphyBen$ mutations being weakly beneficial.
+Such an observation is consistent with the premise that $\SphyBen$ mutations are weakly beneficial, translating to a scaled selection coefficient between 0.32 and 1.24 (table~S2).
+Finding $\dn(\SphyBen) / \ds > 1$ for these sites confirms that these sites are closer to optimality at the end of the branch than at the beginning.
+Even though the beneficial effect of these mutations does not come from an environmental change, it does not change the fact that they have contributed positively to the population’s fitness.
+It is just that at mutation-selection-drift equilibrium, the increase in fitness at these sites is offset by deleterious substitutions elsewhere in the genome so that there is no net adaptation.
+
+This result further indicates that using $\dnds$ as an estimate of purifying selection is biased (overestimated) due to the presence of beneficial non-adaptive mutations among the non-synonymous substitutions.
+By discarding all beneficial non-adaptive mutations we can obtain an estimate of $\dnds$ which is not inflated.
+By comparing these two ways of calculating $\dnds$ (see section~\ref{subsec:substitution-mapping-in-the-terminal-branch} in Materials \& Methods), we calculated that beneficial non-adaptive mutations inflate $\dnds$ values by between 9 and 12\% across genera.
+This represents a substantial increase when considering that beneficial non-adaptive mutations only represent between 0.9 and 1.2\% of non-synonymous mutational opportunities (table~S3).
+
+\subsection*{Selection in populations}
+Second, we assessed whether our calculated $\Sphy$ values predicted at the phylogenetic scale were also indicative of the selective forces exerted at the population level.
+We retrieved single nucleotide polymorphisms (SNPs) segregating in 28 mammalian populations.
+To determine if SNPs were ancestral of derived, we reconstructed the ancestral exome of each population.
+We then classified every non-synonymous SNP as either $\SphyDel$, $\SphyNeu$, or $\SphyBen$ according its $\Sphy$ value (fig.~\ref{fig:method}B-C).
+
+First, SNPs classified as $\SphyBen$ are spread across the genomes and not strongly associated to the ontology terms of their respective genes (table~S4, fig.~S4).
+In humans, some SNPs have been associated with specific clinical prognosis terms obtained by clinical evaluation of the impact of variants on human Mendelian disorders~\cite{landrum_clinvar_2018}.
+Although this classification also relies on deep protein alignments and therefore cannot be considered an independent result from our own, it does provide a consistency check if the effect of a mutation on human health is in line with its fitness effect predicted by our method~\cite{grimm_evaluation_2015}.
+Therefore, we investigated whether the non-synonymous SNPs classified as $\SphyDel$ or $\SphyBen$ showed enrichment in specific clinical terms compared to SNPs classified as $\SphyNeu$.
+Our results show that SNPs predicted as deleterious are associated with clinical terms such as \textit{Likely Pathogenic} and \textit{Pathogenic}, implying that, in general, the selective pressure of a mutation exerted across mammals is also predictive of its clinical effect in humans (table~S5)~\cite{sullivan_leveraging_2023}.
+Conversely, $\SphyBen$ mutations are associated with clinical terms such as \textit{Benign} and \textit{Likely Benign}, which shows that $\SphyBen$ mutations are less likely to be functionally damaging (table~S6).
+
+In addition to clinical prognosis, frequencies at which SNPs are segregating within populations provide information on their selective effects.
+For instance, deleterious SNPs usually segregate at lower frequencies because of purifying selection, which tends to remove them from the population (fig.~\ref{fig:homo-afr-results}C for humans).
+By gathering information across many SNPs, it is possible to estimate the distribution of fitness effects at the population scale, taking synonymous SNPs as a neutral expectation~\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009, galtier_adaptive_2016, tataru_inference_2017}.
+From these estimated fitness effects, we can derive the proportion of beneficial mutations ($\ProbaPopBen$), nearly-neutral mutations ($\ProbaPopNeu$) and deleterious mutations ($\ProbaPopDel$) at the population scale (see section~\ref{subsec:s-polymorphism-method} in Materials \& Methods, figs.~S5-S8).
+These approaches offer a unique opportunity to contrast selection coefficients estimated at the population scale ($\Spop$) and at the phylogenetic scale ($\Sphy$).
+
+Across our selection classes ($\SphyDel$, $\SphyNeu$ and $\SphyBen$), one can ultimately estimate the proportion of correct and incorrect predictions, leading to an estimation of \textit{precision} and \textit{recall} (fig.~\ref{fig:method}F-G and section~\ref{subsec:precisison_recall} in Materials \& Methods).
+Across 28 populations of different mammal species, mutations predicted to be deleterious at the phylogenetic scale ($\SphyDel$) were indeed purged at the population scale, with a \textit{precision} in the range of 90--97\% (table~\ref{table:proba} and fig.~\ref{fig:homo-afr-results}D for humans).
+Conversely, a \textit{recall} in the range of 96--100\% implied that mutations found to be deleterious at the population scale were most likely also predicted to be deleterious at the phylogenetic scale (table~\ref{table:proba}).
+Altogether, purifying selection is largely predictable and amino acids with negative fitness across mammals have been effectively purged away in each population.
+
+\begin{table}[!ht]
+\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
 \centering
-        \includegraphics[width=\textwidth, page=1] {figure4.eps}
-        \caption{
-            Populations in circles, mean of the species across the populations as squares.
-            (A) Proportion of nearly-neutral mutations at the population scale ($\proba [ \SpopNeu]$ in the y-axis), shown as a function of estimated effective population size ($\Ne$ in the x-axis).
-            (B) Proportion of beneficial non-adaptive mutations among all beneficial mutations ($\proba [ \SphyBen \given \SpopBen]$ in the y-axis), shown as a function of $\Ne$ in x-axis.
-            Correlations account for phylogenetic relationship and non-independence of samples, through the fit of a Phylogenetic Generalized Linear Model (see section~\ref{subsec:s-polymorphism-method} in Materials \& Methods).
-        }
-        \label{fig:diversity}
-    \end{figure*}
-
-    \begin{table*}[tb]
-        \centering
-        \begin{adjustbox}{width=\textwidth}
+\caption{}
+\scriptsize
 \begin{tabular}{||l|l|r||r|r||r|r||r|r||}
@@
 \end{tabular}
-        \end{adjustbox}
-        \caption{
+\normalsize
+\begin{flushleft}
 \textit{Precision} and \textit{recall} for estimated selection coefficient of mutations given by mutation-selection models ($\Sphy$).
@@
 $\Ne$ is the estimated effective population size for each population.
+\end{flushleft}
+\label{table:proba}
+\end{adjustwidth}
+\end{table}
+
+Mutations predicted as $\SphyNeu$ were effectively composed of a mix of neutral and selected mutations with varying \textit{precision} (36--63\%) and \textit{recall} (32--45\%) across the different populations (table~\ref{table:proba}, fig.~\ref{fig:homo-afr-results}D for humans).
+The variable proportions between populations can be explained by the effective number of individuals in the population ($\Ne$), a major driver of selection efficacy.
+Moreover, estimates of mutation rate per generation ($u$), from Bergeron \textit{et al.}~\cite{bergeron_evolution_2023} and Orlando \textit{et al.}~\cite{orlando_recalibrating_2013}, and Watterson’s $\theta$ obtained from the synonymous SFS as in Achaz~\cite{achaz_frequency_2009}, allow us to obtain $\Ne$ through $\Ne=\theta/4 u)$.
+Using correlation analyses that accounted for phylogenetic relationship (see section \ref{subsec:correlation-diversity} in Materials \& Methods), we found that higher $\Ne$ was associated with a smaller proportion of nearly-neutral mutations ($r^2=0.31$, $p=0.001$, fig.~\ref{fig:diversity}A).
+This result follows the prediction of the nearly-neutral theory and suggests that in populations with higher diversity (e.g.,~\textit{Bos} or \textit{Ovis}), discrimination between beneficial and deleterious mutations is more likely to occur (figs.~S9-S12).
+Conversely, many more mutations are effectively neutral in populations with lower diversity (e.g.,~\textit{Homo}).
+
+\begin{figure}[!ht]
+\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\centering
+\includegraphics[width=1.4\textwidth, page=1] {figure4.eps}
+\caption{
+Populations in circles, mean of the species across the populations as squares.
+(A) Proportion of nearly-neutral mutations at the population scale ($\proba [ \SpopNeu]$ in the y-axis), shown as a function of estimated effective population size ($\Ne$ in the x-axis).
+(B) Proportion of beneficial non-adaptive mutations among all beneficial mutations ($\proba [ \SphyBen \given \SpopBen]$ in the y-axis), shown as a function of $\Ne$ in x-axis.
+Correlations account for phylogenetic relationship and non-independence of samples, through the fit of a Phylogenetic Generalized Linear Model (see section~\ref{subsec:s-polymorphism-method} in Materials \& Methods).
 }
-        \label{table:proba}
-    \end{table*}
+\label{fig:diversity}
+\end{adjustwidth}
+\end{figure}
+
+Finally, mutations predicted to be $\SphyBen$ were indeed beneficial for individuals bearing them, with a \textit{precision} (fig.~\ref{fig:method}F) in the range of 19--87\% (table~\ref{table:proba} and fig.~\ref{fig:homo-afr-results}D for humans).
+This result confirms that selection toward amino acids restoring existing functions is ongoing in these populations.
+Importantly, the \textit{recall} value in this case, computed as $\proba [ \SphyBen \given \SpopBen]$, is the probability for a beneficial mutation at the population scale to be a non-adaptive, i.e., going toward a fitter amino acid given a stable fitness landscape (fig.~\ref{fig:method}G, table~S7).
+In other words, the \textit{recall} value quantifies the number of beneficial mutations restoring damaged genomes instead of creating adaptive innovations.
+Across the 28 populations, this proportion is in the range of 11--82\% (table~\ref{table:proba}), with a mean of 30\%.
+Accounting for phylogenetic relationships, we found no correlation between the proportion of beneficial non-adaptive mutations and estimates of $\Ne$ based on genetic diversity ($r^2=0.00$, $p=0.772$, fig.~\ref{fig:diversity}B).
+
+We additionally performed controls and simulations to ensure our results were robust.
+First, we controlled that these estimations were not affected by SNP mispolarization (figs.~S13-S14).
+Second, we performed simulations at the population-genetic level and confirmed that our method was able to recover the proportion of beneficial mutations that are non-adaptive in synthetic polymorphism datasets (fig.~S15).
+Third, we ran our analysis filtering out CpG mutations and obtained values of $\proba [ \SphyBen \given \SpopBen]$ in the range of 5--27\%, with a mean of 14\% (tables~S8-9 and fig.~S16-17), providing more conservative estimates.
+Finally, because the phylogenetic mutation-selection codon model should fit better for genes with uniformly conserved functions, we filtered out genes under pervasive adaptation~\cite{latrille_genes_2023} as a control.
+In this subset of the exome, containing genes with a more stable fitness landscape, we found an increase in the proportion of beneficial mutations that are non-adaptive (Wilcoxon signed-rank, $s=80$, $p=0.002$, table~S10), consistent with our expectation that beneficial mutations occur more frequently in genes under changing fitness landscapes.
+
+\subsection*{Selection in the terminal lineage and in populations}
+
+As an alternative to relying solely on currently segregating mutations to quantify selection, one can leverage both polymorphism within a population and substitutions in the terminal lineage to estimate the distribution of fitness effects (DFE).
+Hence, we estimated \textit{precision} and \textit{recall} as done previously, but now including the number of substitutions per site as input for the DFE estimators (see \ref{subsec:s-polymorphism-method} in Materials \& Methods and fig.~S18).
+When including substitutions in the terminal lineage, estimates of $\proba [ \SphyBen \given \SpopBen]$ are in the 10--78\% range with a mean of 36\% (table~S11-12), and 19 out of 28 estimates fall between 15\% and 45\%.
+
+Additionally, we controlled that these estimations were not affected by SNP mispolarization (fig.~S19).
+We also filtered out genes under pervasive adaptation, and again found an increase in $\proba [ \SphyBen \given \SpopBen]$, consistent with our expectation (Wilcoxon signed-rank, $s=120$, $p=0.027$, table~S13).
+We assessed the impact of fitting the same functional form of DFE to the three different categories of changes $\SphyDel$, $\SphyNeu$ and $\SphyBen$.
+To this aim we computed the total amount of current selection by fitting either a single DFE on the whole dataset or by summing the other three independent DFEs.
+These disjoint estimates are well correlated, with a goodness of fit $r^2={0.95, 0.89, 0.82}$ for $\proba [\SpopDel]$, $\proba [\SpopNeu]$ and $\proba [\SpopBen]$, respectively (figs.~S20-22).
+Finally, we evaluated the effect of fitting a parametric functional form for the DFE.
+As implemented in Tataru \textit{et al.}~\cite{tataru_inference_2017}, the DFE is a mixture between a reflected gamma distribution and an exponential distribution (eq.~\ref{eq:parametric-dfe}, section~\ref{subsec:precisison_recall} in Materials \& Methods).
+Instead of using such a continuous DFE, we also tested our prediction with a non-parametric functional form for the DFE, obtaining estimates of $\proba [ \SphyBen \given \SpopBen]$ in the 8--94\% range, with a mean of 43\% (tables~S14-15).
+
+\section*{Discussion}
+\subsection*{Beneficial mutations are not necessarily adaptive}
+
+This study represents an essential step toward integrating the different evolutionary scales necessary to understand the combined effects of mutation, selection, and drift on genome evolution.
+In particular, we have been able to quantify the proportion of beneficial mutations that are non-adapative (i.e., not a response to a change in fitness landscape), which has only been achievable by combining exome-wide data from both phylogenetic and population scales.
+At the phylogenetic scale, codon diversity at each site of a protein-coding DNA alignment allows for reconstructing an amino-acid fitness landscape, assuming that this landscape is stable along the phylogenetic tree.
+These amino-acid fitness landscapes allow us to predict any mutation’s selection coefficient ($\Sphy$) along a protein-coding sequence.
+We have compared these selective effects to observations at the population level, and by doing so, we have confirmed that mutations predicted to be deleterious ($\SphyDel \coloneqq \Sphy < -1$) are generally purified away in extant populations.
+Our results concur with previous studies showing that SIFT scores~\cite{ng_sift_2003, vaser_sift_2016}, based on amino acid alignments across species, also inform on the deleterious fitness effects exerted at the population scale~\cite{chen_hunting_2021}.
+However, contrary to SIFT scores, our mutation-selection model is parameterized by a fitness function such that changes are directly interpretable as fitness effects (see also section S5).
+In this regard, an interesting prediction of our model is that some deleterious mutations reach fixation due to genetic drift, while beneficial non-adaptive mutations restore states of higher fitness.
+We have tested this hypothesis and have found that a substantial part of these predicted non-adaptive mutations ($\SphyBen \coloneqq \Sphy > 1 $) are indeed beneficial in extant populations.
+We estimate that between 11 and 82\% of all beneficial mutations in mammalian populations are not adaptive.
+More specifically, in 24 out of 28 populations analyzed, the percentage of beneficial mutations estimated to be non-adaptive falls between 15 and 45\%.
+These results suggest that many beneficial mutations are not adaptive, but rather restore states of higher fitness.
+Hence, we can correctly estimate the extent of adaptive evolution only if we account for the number of beneficial non-adaptive mutations~\cite{keightley_what_2010, rice_evolutionarily_2015}.
+Here instead, we argue that we should dissociate positive selection from adaptive evolution and limit the use of adaptive mutations to those that are associated with adaptation to environmental change as such~\cite{charlesworth_other_2007, mustonen_fitness_2009, mustonen_fitness_2010}.
+
+\subsection*{Assumptions and methodological limitations}
+
+The exact estimation of the contribution of beneficial non-adaptive mutations to positive selection relies on some hypotheses at both the phylogenetic and population scales and is sensitive to methodological limitations.
+Indeed, data quality and potentially inadequate modeling choices of both the fitness landscape (at the phylogenetic scale) and fitness effects (at the population scale) might also lead to missed predictions~\cite{moutinho_variation_2019}.
+In practice, we obtained different values of the proportion of non-adaptive beneficial mutations depending on i) the filtering or not of CpG mutations~\cite{eyre-walker_how_2014}, ii) whether we included substitutions in the terminal lineage along with within-population polymorphisms to estimate fitness effects~\cite{tataru_inference_2017}, and iii) the model used to infer the fitness effects.
+It appears that our estimation can be sensitive to model misspecification and overall, while we provide an order of magnitude for the contribution of beneficial non-adaptive mutations to positive selection, methodological improvement on the estimation of the DFE is needed to increase the precision of this value.
+
+To be conservative, we considered mutations as adaptive if they were detected as being under positive selection at the population scale despite them being either incorrectly predicted as deleterious ($\SphyDel$) or nearly-neutral ($\SphyNeu \coloneqq -1 < \Sphy <1$) from the amino-acid mammalian fitnesses.
+An example of an incorrectly predicted deleterious mutation ($\SphyDel$) from its fitness landscape could be an amino acid having always been deleterious across mammals, but being advantageous ($\SpopBen$) in the current species due to environmental changes or a major shift in their fitness landscape (e.g.
+domestication)
+To visualize an example of a wrongly predicted nearly-neutral mutation, we can first imagine a site where only hydrophilic amino acids are accepted because of the protein properties (e.g.
+a surface site of a globular protein).
+Let us then assume that such a site is also a target for viruses, hence promoting amino-acid changes which modify the site's viral affinity~\cite{enard_viruses_2016}.
+Given the selective pressure favoring amino-acid change, but restricting the possibilities to hydrophilic amino acids, most hydrophilic amino acids will likely be visited along the phylogenetic tree and the mutation-selection model will give high and similar fitnesses to all of them.
+In such a case, any mutation between hydrophilic amino acids will be wrongly predicted as nearly-neutral ($\SphyNeu$), while it is in fact adaptive.
+In summary, under a changing fitness landscapes~\cite{mustonen_molecular_2008}, our phylogenetic mutation-selection model takes an average over fitness changes observed along the phylogeny, causing beneficial mutations ($\SpopBen$) to be predicted as either deleterious ($\SphyDel$) or nearly-neutral ($\SphyNeu$), therefore mechanically reducing $\proba [ \SphyBen \given \SpopBen]$, and making our estimate conservative.
+
+\subsection*{Convergent adaptation}
+
+If there are several substitutions toward the same amino acid along the mammalian tree (see fig.~S3), our mutation-selection model cannot formally distinguish between a scenario where mammals have fixed deleterious mutations that are reverted in several lineages, from more complex scenarios involving convergent adaptation across mammals.
+In a first scenario, repeated changes of fitness landscapes in the same direction could occur along several lineages, leading to repeated substitutions in multiple lineages (parallel or convergent adaptation).
+In a second scenario, an environmental change that occurred near the root of placental mammals ($\sim$100 Mys ago), to which extant populations are currently responding independently through weakly adaptive mutations, could also lead to repeated substitutions toward the same amino acids.
+Importantly, we would usually expect adaptive convergent mutations to be linked to particular converging phenotypes across mammals, and hence, they should not massively affect the whole genome as we find (table~S4, fig.
+S4).
+Moreover, after filtering out genes usually associated to recurrent adaptation (e.g. immune genes), we recover an even higher proportion of beneficial non-adaptive mutations (table~S8).
+For these reasons, we argue that the signal of predictable positive selection we recover in extant population is indeed mainly driven by non-adaptive evolution.
+
+\subsection*{The influence of effective population size}
+
+Across the genome, beneficial non-adaptive mutations and deleterious mutations reaching fixation create a balance in which genomes are constantly damaged and restored simultaneously at different loci due to drift.
+Since the probability of fixation of mutations depends on the effective population size ($\Ne$), the history of $\Ne$ plays a crucial role in determining the number of beneficial non-adaptive mutations compensating for deleterious mutations~\cite{latrille_inferring_2021}.
+For example, a population size expansion will increase the efficacy of selection, and a larger proportion of mutations will be beneficial (otherwise effectively neutral), thus increasing the number of beneficial non-adaptive mutations.
+On the other hand, a population that has experienced a high $\Ne$ throughout its history should be closer to an optimal state under a stable fitness landscape, having suffered fewer fixations of deleterious mutations and therefore decreasing the probability of beneficial non-adaptive mutations~\cite{huber_determining_2017}.
+Overall, we expect the proportion of beneficial non-adaptive mutations to be more dependent on $\Ne$’s long-term expansions and contractions than on the short-term ones~\cite{charlesworth_other_2007,huber_determining_2017}.
+
+Moreover, because our model assumes a fixed fitness landscape, it implicitly assumes that $\Ne$ is constant along the phylogenetic tree.
+Fluctuations due to changes in the fitness landscape or in $\Ne$ will be averaged out by the assumption of the current model that $\Ne$ is constant across lineages.
+It was recently shown~\cite{latrille_inferring_2021}, using computer intensive mutation-selection models with fluctuating $\Ne$, that relaxing the assumption of a constant $\Ne$ results in more extreme estimates of amino-acid fitnesses than with the standard model used in this study.
+In other words, by assuming a constant $\Ne$, we are underpowered to detect beneficial non-adaptive mutations since amino acids will have more similar fitnesses.
+As a consequence, some of the beneficial non-adaptive mutations currently segregating in population will be incorrectly classified as nearly-neutral by the mutation-selection model, and thus be wrongly interpreted as adaptive (see previous section).
+This ultimately results in lower estimates of the proportion of beneficial non-adaptive mutations.
+Given this inflation of missed predictions due to change in population sizes~\cite{lanfear_population_2014, jones_shifting_2017, platt_protein_2018}, our estimated proportion of beneficial non-adaptive mutations among adaptive ones is likely to be an underestimation.
+
+\subsection*{The role of epistasis and compensatory mutations}
+
+Our model assumes that amino-acid fitness landscapes are site-specific and also independent of one another, whereas under pervasive epistasis, the fitness effect of any mutation at a particular site would depend on the amino acids present at other sites.
+Epistasis is common for mutations that influence the protein’s physical properties (e.g.
+conformation, stability, or affinity for ligands) or might arise due to nonlinear relationship between the protein’s physical properties and fitness~\cite{starr_epistasis_2016}.
+Regardless of its origin, epistasis has been shown to play a role in the evolution of protein-coding genes, with amino-acid residues in contact within a protein or between proteins tending to co-evolve~\cite{morcos_directcoupling_2011, marks_protein_2012, starr_epistasis_2016}.
+Particularly, the residues in contact co-evolve to become more compatible with each other generating an entrenchment~\cite{goldstein_nonadaptive_2015, goldstein_sequence_2017, park_epistatic_2022}.
+Epistasis therefore allows for compensatory mutations, which restore fitness through mutations at loci different from where deleterious mutations took place, representing another case of non-adaptive beneficial mutations, but one which is not accounted for by our method.
+Hence, the beneficial mutations that we classify as putatively adaptive might in fact be compensatory mutations, making our estimation of the rate of non-adaptive beneficial mutations conservative.
+
+Despite epistasis being an important factor in protein evolution, several deep-mutational scanning experiments have revealed that a site-specific fitness landscape predicts the evolution of sequences in nature with considerable accuracy~\cite{ashenberg_mutational_2013, doud_sitespecific_2015, bloom_identification_2017}.
+Additionally, the fact that we observe such a high proportion of beneficial non-adaptive mutations suggests that the underlying assumptions of our model, namely site-independence, implying no epistasis, and a static fitness landscape, are a reasonable approximation for the underlying fitness landscape of proteins.
+Our results imply that the fitness effects of new mutations are mostly conserved across mammalian orthologs, in agreement with other studies showing that for conserved orthologs with similar structures and functions, models without epistasis provide a reasonable estimate of fitness effects in protein coding genes~\cite{youssef_consequences_2020, vigue_deciphering_2022}.
+Conceptually, the framework presented here, with the addition of a more complex protein fitness landscape at the phylogenetic scale, could be used to infer the relative contribution of compensatory mutations to non-adaptive and adaptive evolution.
+
+\subsection*{Detecting adaptation above the nearly-neutral background}
+
+A long-standing debate in molecular evolution is whether the variation we observe between species in protein-coding genes is primarily due to nearly-neutral mutations reaching fixation by drift or primarily due to adaptation~\cite{kimura_evolutionary_1968,ohta_nearly_1992,gillespie_substitution_1994,jensen_importance_2019}.
+Measuring the ``rate of adaptation'' in proteins, as pioneered by McDonald \& Kreitman~\cite{mcdonald_adaptative_1991}, has been central to inform this debate~\cite{galtier_half_2024}.
+However, the McDonald \& Kreitman test detects signatures of accelerated evolution in a given terminal branch compared to an expectation based on polymorphism present in the population.
+It considers the fraction of substitutions that fix too quickly as ``adaptive''~\cite{mcdonald_adaptative_1991, smith_adaptive_2002, welch_estimating_2006} despite there being other processes that can lead to their fixation~\cite{galtier_adaptation_2007,rousselle_influence_2019,joseph_increased_2024a} and some of these substitutions being beneficial but non-adaptive~\cite{hartl_compensatory_1996, charlesworth_other_2007, mustonen_fitness_2009, jones_shifting_2017}.
+Here, the expectation is built on the pattern of substitutions across a phylogeny compared to the fitness effects that can be estimated from both substitutions in a terminal lineage and polymorphism in populations.
+Moreover, the goal is not to detect a fraction of beneficial substitution (i.e.
+``adaptive'' substitutions for McDonald \& Kreitman~\cite{mcdonald_adaptative_1991}), but to estimate the proportion of non-adaptive mutations among beneficial ones.
+
+We provide evidence that in mammalian orthologs, many substitutions occur through fixation of both deleterious mutations and beneficial non-adaptive mutations.
+Detecting adaptation above this background of substitutions remains a challenge~\cite{kimura_evolutionary_1968, ohta_development_1996}.
+Mathematically, the surplus of positive selection due to an externally-driven changing fitness landscape is called \textit{fitness flux}, and requires experimentally measuring the selection coefficient of each mutation in each genetic background.
+The \textit{fitness flux} can be estimated if either the substitutions history is known~\cite{mustonen_fitness_2009} or changes of frequency in currently segregating variants~\cite{mustonen_fitness_2010}.
+Without experimentally measured selection coefficients, another strategy is precisely to use a nearly-neutral substitution model as a null model of evolution.
+Under a strictly neutral evolution of protein-coding sequence, we expect the ratio of non-synonymous over synonymous substitutions ($\dnds$) to be equal to one.
+Deviations from this neutral expectation, such as $\dnds > 1$, which can be generated by an excess of non-synonymous substitutions, is generally interpreted as a sign of adaptation.
+However, as shown in this study, a $\dnds > 1$ is not necessarily a signature of adaptation but can be due to beneficial non-adaptive mutations.
+So, by relaxing the strict neutrality and assuming a stable fitness landscape instead, one can predict the expected rate of evolution, called $\omega_0$~\cite{spielman_relationship_2015, dosreis_how_2015}.
+Adaptation can thus be considered as evolution under a changing fitness landscape and tested as such by searching for the signature of $\dnds > \omega_0$~\cite{cvijovic_fate_2015, rodrigue_detecting_2017, rodrigue_bayesian_2021}.
+Using a stable fitness landscape as a null model of evolution, thus accounting for selective constraints exerted on the different amino acids, increased the statistical power in testing for adaptation~\cite{latrille_genes_2023}.
+Instead of relying solely on summary statistics (such as $\dnds$ or $\omega_0$), another strategy to detect adaptation is to include changes in the fitness landscapes inherently within the mutation selection framework, either with small changes along the phylogeny ~\cite{tamuri_mutationselection_2021} or either by allowing fitness to change on subsets of branches ~\cite{kazmi_detecting_2019, stolyarova_senescence_2020}.
+Such mechanistic models could be more general than site-specific fitness landscapes, including epistasis and changing fitness landscapes~\cite{goldstein_sequence_2017, stolyarova_senescence_2020}.
+
+\subsection*{Conclusions}
+
+We have provided empirical evidence that an evolutionary model assuming a stable fitness landscape at the mammalian scale allows us to predict the fitness effects of mutations in extant populations and individuals, acknowledging the balance between deleterious and beneficial non-adaptive mutations.
+We argue that such a model would represent a null expectation for the evolution of protein-coding genes in the absence of adaptation.
+Altogether, because a substantial part of positive selection can be explained by beneficial non-adaptive mutations, but not its entirety, we argue that the mammalian exome is shaped by both adaptive and non-adaptive processes, and that none of them alone is sufficient to explain the observed patterns of changes.
+In that sense, to avoid conflating beneficial mutations with adaptive evolution, the term ``adaptation`` should retain its original meaning associated with a change in the underlying fitness landscape and be modelled as such~\cite{mustonen_fitness_2009, mustonen_fitness_2010}.
+
+\newpage
+\section{Materials \& Methods}
+\label{sec:methods}
+
+\subsection{Phylogenetic dataset}\label{subsec:phylo-dataset}
+
+Protein-coding DNA sequence alignments in placental mammals and their corresponding gene trees come from the \href{https://www.orthomam.univ-montp2.fr}{OrthoMaM} database and were processed as in Latrille \textit{et al.}~\cite{latrille_genes_2023}.
+OrthoMaM contains a total of $116$ mammalian reference sequences in v10c~\cite{ranwez_orthomam_2007, douzery_orthomam_2014, scornavacca_orthomam_2019}.
+
+Genes located on the X and Y chromosomes and on the mitochondrial genome were discarded from the analysis because the level of polymorphism –~which is necessary for population-based analyses~– is expected to be different in these three regions compared to the autosomal genome.
+Sequences of species for which we used population-level polymorphism (see section \ref{subsec:polymorphism-dataset}) and their sister species, were removed from the analysis to ensure independence between the data used in the phylogenetic and population scales.
+Sites in the alignment containing more than 10\% of gaps across the species were discarded.
+Altogether, our genome-wide dataset contains $14,509$ protein-coding DNA sequences in $87$ placental mammals.
+
+\subsection{Selection coefficient ($\Sphy$) in a phylogeny-based method}
+\label{subsec:s-phylogeny-method}
+
+We analyzed the phylogenetic-level data using mutation-selection models.
+These models assume the protein-coding sequences are at mutation-selection balance under a fixed fitness landscape characterized by a fitness vector over the $20$ amino acids at each site~\cite{yang_mutationselection_2008, halpern_evolutionary_1998, rodrigue_mechanistic_2010}.
+Mathematically, the rate of non-synonymous substitution from codon $a$ to codon $b$ ($q_{a \mapsto b}^{(i)}$) at site $i$ of the sequence is equal to the rate of mutation of the underlying nucleotide change ($\mu_{a \mapsto b}$) multiplied by the scaled probability of mutation fixation ($\proba_{a \mapsto b}^{(i)}$).
+The probability of fixation depends on the difference between the scaled fitness of the amino acid encoded by the mutated codon ($F_b^{(i)}$) and the amino acid encoded by the original codon ($F_a^{(i)}$) at site $i$~\cite{wright_evolution_1931, fisher_genetical_1930}.
+
+The rate of substitution from codon $a$ to $b$ at a site $i$ is thus:
+\begin{equation}
+\begin{dcases}
+q_{a \mapsto b}^{(i)} & = 0 \text{ if codons $a$ and $b$ are more than one mutation away,} \\
+q_{a \mapsto b}^{(i)} & = \mu_{a \mapsto b} \text{ if codons $a$ and $b$ are synonymous, and}\\
+q_{a \mapsto b}^{(i)} & = \mu_{a \mapsto b} \dfrac{F_b^{(i)} - F_a^{(i)}}{1 - \e^{F_a^{(i)} - F_b^{(i)}}} \text{ if codons $a$ and $b$ are non-synonymous}.
+\end{dcases}
+\end{equation}
+
+Fitting the mutation-selection model on a multi-species sequence alignment leads to an estimation of the gene-wide $4 \times 4$ nucleotide mutation rate matrix ($\bm{\mu}$) as well as the $20$ amino-acid fitness landscape ($\bm{F^{(i)}}$) at each site $i$.
+The priors and full configuration of the model are given in section S1.
+From a technical perspective, the Bayesian estimation is a two-step procedure~\cite{rodrigue_bayesian_2008}.
+The first step is a data augmentation of the alignment, consisting in sampling a detailed substitution history along the phylogenetic tree for each site, given the current value of the model parameters.
+In the second step, the parameters of the model can then be directly updated by a Gibbs sampling procedure, conditional on the current substitution history.
+Alternating between these two sampling steps yields a Markov chain Monte-Carlo (MCMC) procedure whose equilibrium distribution is the posterior probability density of interest~\cite{lartillot_bayesian_2004, rodrigue_bayesian_2008}.
+Additionally, across-site heterogeneities in amino-acid fitness profiles are captured by a Dirichlet process.
+More precisely, the number of amino-acid fitness profiles estimated is lower than the number of sites in the alignment.
+Consequently each profile has several sites assigned to it, resulting in a particular configuration of the Dirichlet process.
+Conversely, sites with similar signatures are assigned to the same fitness profile.
+This configuration of the Dirichlet process is resampled through the MCMC to estimate a posterior distribution of amino acid profiles for each site specifically~\cite{rodrigue_mutationselection_2010, lartillot_inference_2013}.
+From a more mechanistic perspective, even though not all amino acids occur at every single codon site of the DNA alignment, we can nevertheless estimate the distribution of amino-acid fitnesses by generalizing the information recovered across sites and across amino acids based on the phylogenetic relationship among samples.
+In particular, synonymous substitutions along the tree contain the signal to estimate branch lengths and the nucleotide transition matrix, while non-synonymous substitutions contain information on fitness difference between codons connected by single nucleotide changes~\cite{rodrigue_mutationselection_2010}.
+
+The selection coefficient for a mutation from codon $a$ to codon $b$ at site $i$ is defined as:
+\begin{equation}
+\Sphy^{(i)} (a \mapsto b) = \Delta F^{(i)} = F^{(i)}_{b} - F^{(i)}_{a}.
+\end{equation}
+In our subsequent derivation the source ($a$) and target ($b$) codons as well as the site ($i$) are implicit and thus never explicitly written.
+
+The scaled selection coefficient ($\Sphy = \Delta F$) is formally the product of the selection coefficient at the individual level ($s$) and the effective population size ($\Ne$), as $\Sphy = 4 \Ne \times s$.
+The value of $\Sphy$ informs us on the strength of selection exerted on amino acids changes.
+Thus, according to its $\Sphy$ value, we can classify any mutation as either a deleterious mutation toward a less fit amino acid ($\SphyDel \coloneqq \Sphy < -1$), a nearly-neutral mutation ($\SphyNeu \coloneqq -1 < \Sphy <1$), or a mutation toward a known fitter amino acid, constituting thus a beneficial non-adaptive mutation ($\SphyBen \coloneqq \Sphy > 1$).
+
+We used the Bayesian software \textit{BayesCode} (\url{https://github.com/ThibaultLatrille/bayescode}, v1.3.1) to estimate the selection coefficients for each protein-coding gene in the mammalian dataset.
+We ran the MCMC algorithm implemented in BayesCode for $2,000$ generations as described in Latrille \textit{et al.}~\cite{latrille_genes_2023}.
+For each gene, after discarding a burn-in period of $1,000$ generations of MCMC, we obtained posterior mean estimates (over the $1,000$ generations left of MCMC) of the mutation rate matrix ($\bm{\mu}$) as well as the $20$ amino-acid fitness landscape ($\bm{F^{(i)}}$) at each site $i$.
+
+\subsection{Polymorphism dataset}
+\label{subsec:polymorphism-dataset}
+
+The genetic variants representing the population level polymorphisms were obtained from the following species and their available datasets: \textit{Equus caballus} (EquCab2 assembly in the EVA study PRJEB9799~\cite{alabri_whole_2020}), \textit{Bos taurus} (UMD3.1 assembly in the NextGen project: \url{https://projects.ensembl.org/nextgen/}), \textit{Ovis aries} (Oar\_v3.1 assembly in the NextGen project), \textit{Capra hircus} (CHIR1 assembly in the NextGen project), converted to ARS1 assembly with dbSNP identifiers~\cite{sherry_dbsnp_2001}), \textit{Chlorocebus sabaeus} (ChlSab1.1 assembly in the EVA project PRJEB22989~\cite{svardal_ancient_2017}), \textit{Homo sapiens} (GRCh38 assembly in the 1000 Genomes Project~\cite{zheng-bradley_alignment_2017}).
+In total, we analyzed 28 populations across the 6 different species with polymorphism data.
+The data was processed as described in Latrille \textit{et al.}~\cite{latrille_genes_2023}.
+
+Only bi-allelic single nucleotide polymorphisms (SNPs) found within a gene were in our polymorphism dataset, while nonsense variants and indels were discarded.
+To construct the dataset, we first recovered the location of each SNP (represented by its chromosome, position, and strand) in the focal species and matched it to its corresponding position in the coding sequence (CDS) using gene annotation files (GTF format) downloaded from Ensembl (\url{ensembl.org}).
+We then verified that the SNP downloaded from Ensembl matched the reference in the CDS in FASTA format.
+Next, the position in the CDS was converted to the corresponding position in the multi-species sequence alignment (containing gaps) from the OrthoMaM database (see section~\ref{subsec:s-phylogeny-method}) for the corresponding gene by doing a global pairwise alignment (Biopython function pairwise2).
+This conversion from genomic position to alignment position was only possible when the assembly used for SNP-calling was the same as the one used in the OrthoMaM alignment, the GTF annotations, and the FASTA sequences.
+SNPs were polarized using the three closest outgroups found in the OrthoMaM alignment with est-usfs v2.04~\cite{keightley_inferring_2018}, and alleles with a probability of being derived lower than 0.99 were discarded.
+
+\subsection{Mutational opportunities}
+\label{subsec:nunber-of-sites}
+The mutational opportunities of any new mutation refer to its likelihood of falling into a specific category (synonymous, deleterious, nearly-neutral, or beneficial).
+Deriving such opportunities is necessary to estimate the strength of selection exerted at the population scale since different categories might have different mutational opportunities, and thus polymorphism and divergence need to be corrected accordingly (see sections~\ref{subsec:substitution-mapping-in-the-terminal-branch},~\ref{subsec:s-polymorphism-method}, and~\ref{subsec:precisison_recall}).
+To calculate mutational opportunities, we reconstructed the ancestral exome of each of the 28 populations by using the most likely ancestral state from est-usfs (see section \ref{subsec:polymorphism-dataset}), which differs from the corresponding species reference exome since it accounts for the variability present in the specific population.
+
+From the reconstructed ancestral exome, all possible mutations were computed, weighted by the instantaneous rate of change between nucleotides obtained from the mutation rate matrix ($\bm{\mu}$, see section~\ref{subsec:s-phylogeny-method}), summing to $\mu_{\text{tot}}$ across the whole exome, and to $\mu_{\text{syn}}$ when restricted to synonymous mutations.
+Finally, the mutational opportunities for synonymous mutations were computed as the total number of sites across the exome ($L_{\text{tot}}$) weighted by the proportion of synonymous mutations among all possible mutations as:
+
+\begin{equation}
+L_{\text{syn}} = L_{\text{tot}} \frac{\mu_{\text{syn}}}{\mu_{\text{tot}}}.
+\end{equation}
+
+Similarly, for non-synonymous mutations, the total mutation rate for each class of selection $\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$, called $\mu\left( \Sphyclass \right)$, was estimated as the sum across all non-synonymous mutations if their selection coefficient at the phylogenetic scale is in the class $\Sphy \in \Sphyclass$.
+Accordingly, the mutational opportunities ($L \left( \Sphyclass \right)$) for each class of selection coefficient ($\Sphyclass$) was finally computed as the total number of sites across the exome ($L_{\text{tot}}$) weighted by the ratio of the aggregated mutations rates falling in the class $\mu\left( \Sphyclass \right)$:
+\begin{equation}
+L \left( \Sphyclass \right) = L_{\text{tot}} \frac{\mu\left( \Sphyclass \right)}{\mu_{\text{tot}}}.\label{eq:mutation-opp}
+\end{equation}
+
+Finally, $\proba [ \Sphyclass ]$ is the probability for a non-synonymous mutation to be in the class $\Sphyclass$, thus computed as:
+\begin{equation}
+\proba[\Sphyclass] = \frac{L\left( \Sphyclass \right)}{\sum_{\SphyclassAlt\in \{\SphyDel, \SphyNeu, \SphyBen \} } L\left(\SphyclassAlt \right)}.\label{eq:proba-dfe-mutsel}
+\end{equation}
+
+\subsection{Substitution mapping and $\dnds$ in the terminal branch}
+\label{subsec:substitution-mapping-in-the-terminal-branch}
+We inferred the protein-coding DNA sequences for each node of the 4-taxa tree containing the focal species and the three closest outgroups species found in the OrthoMaM alignment by applying the M5 codon model (gamma site rate variation) as implemented in FastML.v3.11~\cite{ashkenazy_fastml_2012}.
+Consequently, for each focal species we reconstructed the protein coding DNA sequence of the whole exome at the base of the terminal branch before the split from the sister species.
+We considered \textit{Ceratotherium simum simum} as \textit{Equus caballus'} sister species; \textit{Bison bison bison} as \textit{Bos taurus'} sister species; \textit{Pantholops hodgsonii} as \textit{Ovis aries'} sister species; \textit{Pantholops hodgsonii} as \textit{Capra hircus'} sister species; \textit{Macaca mulatta} as \textit{Chlorocebus sabaeus'} sister species and finally, we considered \textit{Pan troglodytes} as \textit{Homo sapiens'} sister species.
+From this reconstructed exome, we determined the direction of the substitution occurring along the terminal branch of the phylogenetic tree toward each extant population.
+SNPs segregating in the population were discarded, and the most likely ancestral state from est-usfs (see section \ref{subsec:polymorphism-dataset}) was used as the reference for each extant population.
+For each substitution, we recovered its $\Sphy$ value as calculated through the phylogeny-based method (see section~\ref{subsec:s-phylogeny-method}).
+Finally, the rate of non-synonymous over synonymous substitutions for a given class of selection coefficient ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$) was computed as:
+\begin{align}
+\begin{dcases}
+\dn \left( \Sphyclass \right) &= \dfrac{D\left( \Sphyclass \right)}{L \left( \Sphyclass \right)}, \\
+\ds &= \dfrac{D_{\text{syn}}}{L_{\text{syn}}},
+\end{dcases}\label{eq:dnds}
+\end{align}
+where $D \left( \Sphyclass \right) $ was the number of non-synonymous substitutions in class $\Sphyclass$, $D_{\text{syn}}$ was the number of synonymous substitutions across the exome, while $L \left( \Sphyclass \right)$ and $L_{\text{syn}}$ were the numbers of non-synonymous and synonymous mutational opportunities, respectively, as defined in section~\ref{subsec:nunber-of-sites}.
+$\delta(\dnds)$ was computed as the difference between $\dnds$ computed over all substitutions and $\dnds$ when we removed beneficial non-adaptive mutations $\dn (\Sphy < 1) / \ds$, normalized by $\dnds$.
+Note that the quantities $\delta(\dnds)$ and $\delta(\dn)$ are equivalent due to the simplification of the factor $\ds$:
+\begin{equation}
+\delta(\dnds) = \dfrac{\dnds - \dn(\Sphy < 1) / \ds}{\dnds} = \dfrac{\dn - \dn(\Sphy < 1)}{\dn} = \delta(\dn).\label{eq:delta-dnds}
+\end{equation}
+
+\subsection{Scaled selection coefficients ($\Spop$) in a population-based method}
+\label{subsec:s-polymorphism-method}
+
+To obtain a quantitative estimate of the distribution of selection coefficients for each category of SNPs, we used the \textit{polyDFE} model~\cite{tataru_inference_2017, tataru_polydfe_2020}.
+This model uses the count of derived alleles to infer the distribution of fitness effects (DFE).
+The probability of sampling an allele at a given frequency (before fixation or extinction) is informative of its scaled selection coefficient at the population scale ($\Spop$).
+Therefore, pooled across many sites, the site-frequency spectrum (SFS) provides information on the underlying $\Spop$ of mutations.
+However, estimating a single $\Spop$ for all sampled mutations is biologically unrealistic, and a DFE of mutations is usually assumed~\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009}.
+The \textit{polyDFE}\cite{tataru_inference_2017, tataru_polydfe_2020} software implements a mixture of a $\Gamma$ and exponential distributions to model the DFE of non-synonymous mutations, while synonymous mutations are considered neutral.
+The model estimates the parameters $\DelMean$, $b$, $p_b$ and $\AdvMean$ for non-synonymous mutations as:
+
+\begin{equation}
+\label{eq:parametric-dfe}
+\phi \left( \Spop; \DelMean , b, p_b, \AdvMean \right) =
+\begin{dcases}
+\left( 1 - p_b \right) f_{\Gamma}(-\Spop; -\DelMean, b) & \text{ if $\Spop \leq 0$,} \\
+p_b f_{e}(\Spop; \AdvMean) & \text{ if $\Spop > 0$,} \\
+\end{dcases}
+\end{equation}
+
+where $\DelMean \leq -1 $ is the estimated mean of the DFE for $\Spop \leq 0$;
+$b \geq 0.2$ is the estimated shape of the $\Gamma$ distribution;
+$0 \leq p_b \leq 1$ is the estimated probability that $\Spop > 0$;
+$\AdvMean \geq 1$ is the estimated mean of the DFE for $\Spop > 0$;
+and $f_{\Gamma}(\Spop; m, b)$ is the density of the $\Gamma$ distribution with mean $m$ and shape $b$, while $f_{e}(\Spop; m)$ is the density of the exponential distribution with mean $m$.
+
+\textit{PolyDFE} requires one SFS for non-synonymous mutations and one for synonymous mutations (neutral expectation), as well as the number of sites on which each SFS was sampled.
+For populations containing more than $8$ individuals, the SFS was subsampled down to $16$ chromosomes ($8$ diploid individuals) without replacement (hyper-geometric distribution) to alleviate the effect of different sampling depths in the 28 populations.
+Altogether, for each class of selection ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$) of non-synonymous SNPs, we aggregated all the SNPs in the selection class $\Sphyclass$ as an SFS.
+The number of sites on which each SFS was sampled is given by $L(\Sphyclass)$ for the non-synonymous SFS and $L_{\text{syn}}$ for the synonymous SFS respectively.
+For each class of selection $\Sphyclass$, once fitted to the data using maximum likelihood with \textit{polyDFE}, the parameters of the DFE $\left( \DelMean , b, p_b, \AdvMean \right)$ were used to compute $\proba [ \SpopDel \given  \Sphyclass] $, $\proba [ \SpopNeu \given \Sphyclass]$, and $\proba [ \SpopBen \given \Sphyclass]$ as:
+
+\begin{align}
+\proba [ \SpopDel \given  \Sphyclass] &= \proba [ \Spop < -1 \given \Sphyclass ] = \left( 1 - p_b \right) \int_{-\infty}^{-1} f_{\Gamma}(-\Spop; -\DelMean, b) \der \Spop, \label{eq:polyProbaDel} \\
+\proba [ \SpopNeu \given \Sphyclass] &= \proba [ -1 < \Spop < 1 \given \Sphyclass ] = \left( 1 - p_b \right) \int_{-1}^{0} f_{\Gamma}(-\Spop; -\DelMean, b) \der \Spop + p_b \int_{0}^{1} f_{e}(\Spop; \AdvMean) \der \Spop, \\
+\proba [ \SpopBen \given \Sphyclass] &= \proba [ \Spop > 1 \given \Sphyclass] = p_b \int_{1}^{+\infty} f_{e}(\Spop; \AdvMean) \der \Spop. \label{eq:polyProbaAdv}
+\end{align}
+
+Rather than relying solely on currently segregating mutations to quantify selection, \textit{polyDFE} can leverage both divergence and polymorphism to estimate the parameters of the DFE.
+We can thus add four more inputs to \textit{polyDFE}: $D \left( \Sphyclass \right) $, $L \left( \Sphyclass \right)$, $D_{\text{syn}}$ and $L_{\text{syn}}$ such as defined in the previous section.
+Because the estimates of DFE are different with this method, we naturally obtained different values of $\proba [ \SpopDel \given  \Sphyclass] $, $\proba [ \SpopNeu \given \Sphyclass]$, and $\proba [ \SpopBen \given \Sphyclass]$.
+
+\subsection{\textit{Precision} and \textit{recall}}
+\label{subsec:precisison_recall}
+For readability, we give here \textit{precision} and \textit{recall} for beneficial mutations ($\SphyBen$ and $\SpopBen$), but it can be obtained using the same derivation for the deleterious mutations ($\SphyDel$ and $\SpopDel$) and nearly-neutral mutations ($\SphyNeu$ and $\SpopNeu$).
+
+\textit{Precision} is the proportion of mutations correctly predicted as beneficial ($\proba [ \SpopBen \cap  \SphyBen]$) out of all predicted as beneficial non-adaptive mutations ($\proba [ \SphyBen]$), which can be written as a conditional probability:
+
+\begin{equation}
+\frac{\proba [ \SpopBen  \cap  \SphyBen]}{\proba [ \SphyBen]} = \proba [ \SpopBen \given \SphyBen].
+\label{eq:precision}
+\end{equation}
+Namely, \textit{precision} corresponds to the probability for a $\SphyBen$ mutation to be effectively beneficial at the population level ($\SpopBen$).
+This probability, computed from eq.~\ref{eq:polyProbaAdv}, is obtained by restricting our analysis to SNPs that are predicted to be beneficial non-adaptive mutations (yellow fill for the category $\SphyBen$ in fig.~\ref{fig:homo-afr-results}D).
+
+\textit{Recall} is the proportion of mutations correctly predicted as beneficial ($\proba [ \SpopBen \cap  \SphyBen]$) out of all beneficial mutations ($\proba [ \SpopBen]$), which can be written as a conditional probability:
+\begin{equation}
+\frac{\proba [ \SpopBen \cap  \SphyBen]}{\proba [ \SpopBen]} = \proba [ \SphyBen  \given \SpopBen ].
+\end{equation}
+Namely, \textit{recall} corresponds to the probability for a beneficial mutation at the population level ($\SpopBen$) to be a beneficial non-adaptive mutation ($\SphyBen$).
+Using Bayes theorem, \textit{recall} can be re-written as:
+\begin{equation}
+\proba [\SphyBen \given \SpopBen] = \frac{\proba [\SpopBen \given \SphyBen] \times \proba[\SphyBen]}{\ProbaPopBen},
+\label{eq:bayes}
+\end{equation}
+
+where $\proba [\SpopBen \given \SphyBen]$ and $\proba [ \SphyBen ]$ can be calculated using equations~\ref{eq:precision} and~\ref{eq:proba-dfe-mutsel}, respectively, and $\proba [ \SpopBen ]$ is the probability of a mutation to be beneficial at the level of the population, which can be computed from the law of total probabilities as:
+
+\begin{equation}
+\proba [ \SpopBen ] = \sum_{\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \} }\proba [\SpopBen \given \Sphyclass ] \times \proba [\Sphyclass ].
+\label{eq:total_proba}
+\end{equation}
+
+\subsection{Correlation with effective population size ($\Ne$)}
+\label{subsec:correlation-diversity}
+Genetic diversity estimator Watterson's $\thetaSyn$ was obtained for each population from the synonymous SFS as in Achaz~\cite{achaz_frequency_2009}.
+For each popuation, $\Ne$ was estimated from the equation $\Ne=\thetaSyn / (4 \times u)$, where $u$ is the mutation rate per generation.
+Estimates for $u$ were averaged per species across the pedigree-based estimation in~\cite{bergeron_evolution_2023} for \textit{Homo}, \textit{Bos}, \textit{Capra} and \textit{Chlorocebus}.
+For \textit{Ovis} we used the estimated $u$ of \textit{Capra}.
+For \textit{Equus}, we used $u$ as estimated in Orlando \textit{et al.}~\cite{orlando_recalibrating_2013} ($u=7.24\times10^{-9}$).
+Because a correlation must account for phylogenetic relationship and non-independence of samples, we fitted a Phylogenetic Generalized Linear Model in \textit{R} with the method \texttt{pgls} with default settings from the package \texttt{caper}~\cite{orme_caper_2013}.
+The mammalian dated tree was obtained from TimeTree~\cite{kumar_timetree_2017} and pruned to include only the species analysed in this study, with multi-furcation of the different populations from each species placed at the same divergence time as the species (section S4.1).
+
+\section*{Data availability}
+The data underlying this article are available at \url{https://doi.org/10.5281/zenodo.7878953}.
+Snakemake pipeline, analysis scripts and documentation are available at \href{https://github.com/ThibaultLatrille/SelCoeff}{github.com/ThibaultLatrille/SelCoeff}.
+
+\section*{Acknowledgements}
+\label{sec:acknowledgment}
+We gratefully acknowledge the help of Mélodie Bastian, Nicolas Lartillot, Carina Farah Mugal, Laurent Duret, Alexandre Reymond, Daniele Silvestro and Nicolas Gambardella for their advice and reviews concerning this manuscript.
+This work was performed using the computing facilities of the CC LBBE/PRABI\@.
+This study makes use of data generated by the NextGen Consortium.
+Funding:
+Université de Lausanne; Agence Nationale de la Recherche, Grant ANR-19-CE12-0019 / HotRec.
+The European Union’s Seventh Framework Programme (FP7/2010-2014) provided funding for the project under grant agreement no 244356 - “NextGen”.
+
+\section*{Competing interests}
+The authors declare no conflicts of interest.
+
+\section*{Author information}
+Original idea: T.L.\ and J.J.;
+Model conception: T.L., J.J.\ and N.S.;
+Code: T.L.;
+Data analyses: T.L.\ and J.J.;
+Interpretation: T.L., J.J., D.A.H.\ and N.S.;
+First draft: T.L.\ and J.J.;
+Editing and revisions: T.L., J.J., D.A.H.\ and N.S.
+Project management and funding: N.S\@.
+
+% Either type in your references using
+% \begin{thebibliography}{}
+% \bibitem{}
+% Text
+% \end{thebibliography}
+%
+% or
+%
+% Compile your BiBTeX database using our plos2015.bst
+% style file and paste the contents of your .bbl file
+% here. See http://journals.plos.org/plosone/s/latex for
+% step-by-step instructions.
+%
+\begin{thebibliography}{10}
+
+\bibitem{darwin_origin_1859}
+Darwin C.
+\newblock On the {{Origin}} of {{Species}} by {{Means}} of {{Natural
+Selection}}, or the {{Preservation}} of {{Favoured Races}} in the
+{{Struggle}} for {{Life}}. vol. 220.
+\newblock John Murray; 1859.
+
+\bibitem{merrell_adaptive_1994}
+Merrell DJ.
+\newblock The {{Adaptive Seascape}}: {{The Mechanism}} of {{Evolution}}.
+\newblock U of Minnesota Press; 1994.
+
+\bibitem{gavrilets_adaptive_2009}
+Gavrilets S, Losos JB.
+\newblock Adaptive {{Radiation}}: {{Contrasting Theory}} with {{Data}}.
+\newblock Science. 2009;323(5915):732--737.
+\newblock doi:{10.1126/science.1157966}.
+
+\bibitem{enard_viruses_2016}
+Enard D, Cai L, Gwennap C, Petrov DA.
+\newblock Viruses Are a Dominant Driver of Protein Adaptation in Mammals.
+\newblock eLife. 2016;5:e12469.
+\newblock doi:{10.7554/eLife.12469}.
+
+\bibitem{mcdonald_adaptative_1991}
+McDonald JH, Kreitman M.
+\newblock Adaptative Protein Evolution at {{Adh}} Locus in {{Drosophila}}.
+\newblock Nature. 1991;351(6328):652--654.
+\newblock doi:{10.1038/351652a0}.
+
+\bibitem{smith_adaptive_2002}
+Smith NGC, {Eyre-Walker} A.
+\newblock Adaptive Protein Evolution in {{Drosophila}}.
+\newblock Nature. 2002;415(6875):1022--1024.
+\newblock doi:{10.1038/4151022a}.
+
+\bibitem{welch_estimating_2006}
+Welch JJ.
+\newblock Estimating the {{Genomewide Rate}} of {{Adaptive Protein Evolution}}
+in {{Drosophila}}.
+\newblock Genetics. 2006;173(2):821--837.
+\newblock doi:{10.1534/genetics.106.056911}.
+
+\bibitem{yang_statistical_2000}
+Yang Z, Bielawski JR.
+\newblock Statistical Methods for Detecting Molecular Adaptation.
+\newblock Trends in Ecology and Evolution. 2000;15(12):496--503.
+\newblock doi:{10.1016/S0169-5347(00)01994-7}.
+
+\bibitem{eyre-walker_genomic_2006}
+{Eyre-Walker} A.
+\newblock The Genomic Rate of Adaptive Evolution.
+\newblock Trends in Ecology \& Evolution. 2006;21(10):569--575.
+\newblock doi:{10.1016/j.tree.2006.06.015}.
+
+\bibitem{moutinho_variation_2019}
+Moutinho AF, Bataillon T, Dutheil JY.
+\newblock Variation of the Adaptive Substitution Rate between Species and
+within Genomes.
+\newblock Evolutionary Ecology. 2019;34(3):315--338.
+\newblock doi:{10.1007/s10682-019-10026-z}.
+
+\bibitem{lynch_mutation_2023}
+Lynch M.
+\newblock Mutation Pressure, Drift, and the Pace of Molecular Coevolution.
+\newblock Proceedings of the National Academy of Sciences.
+2023;120(27):e2306741120.
+\newblock doi:{10.1073/pnas.2306741120}.
+
+\bibitem{charlesworth_other_2007}
+Charlesworth J, {Eyre-Walker} A.
+\newblock The Other Side of the Nearly Neutral Theory, Evidence of Slightly
+Advantageous Back-Mutations.
+\newblock Proceedings of the National Academy of Sciences.
+2007;104(43):16992--16997.
+\newblock doi:{10.1073/pnas.0705456104}.
+
+\bibitem{mustonen_fitness_2009}
+Mustonen V, L{\"a}ssig M.
+\newblock From Fitness Landscapes to Seascapes: Non-Equilibrium Dynamics of
+Selection and Adaptation.
+\newblock Trends in genetics. 2009;25(3):111--119.
+\newblock doi:{10.1016/j.tig.2009.01.002}.
+
+\bibitem{jones_shifting_2017}
+Jones CT, Youssef N, Susko E, Bielawski JP.
+\newblock Shifting Balance on a Static Mutation--Selection Landscape: A Novel
+Scenario of Positive Selection.
+\newblock Molecular Biology and Evolution. 2017;34(2):391--407.
+\newblock doi:{10.1093/molbev/msw237}.
+
+\bibitem{ohta_nearly_1992}
+Ohta T.
+\newblock The Nearly Neutral Theory of Molecular Evolution.
+\newblock Annual Review of Ecology and Systematics. 1992;23(1992):263--286.
+
+\bibitem{gillespie_ohta_1995}
+Gillespie JH.
+\newblock On {{Ohta}}'s Hypothesis: {{Most}} Amino Acid Substitutions Are
+Deleterious.
+\newblock Journal of Molecular Evolution. 1995;40(1):64--69.
+\newblock doi:{10.1007/BF00166596}.
+
+\bibitem{hartl_compensatory_1996}
+Hartl DL, Taubes CH.
+\newblock Compensatory Nearly Neutral Mutations: {{Selection}} without
+Adaptation.
+\newblock Journal of Theoretical Biology. 1996;182(3):303--309.
+\newblock doi:{10.1006/jtbi.1996.0168}.
+
+\bibitem{sella_application_2005}
+Sella G, Hirsh AE.
+\newblock The Application of Statistical Physics to Evolutionary Biology.
+\newblock Proceedings of the National Academy of Sciences of the United States
+of America. 2005;102(27):9541--9546.
+\newblock doi:{10.1073/pnas.0501865102}.
+
+\bibitem{cvijovic_fate_2015}
+Cvijovi{\'c} I, Good BH, Jerison ER, Desai MM.
+\newblock Fate of a Mutation in a Fluctuating Environment.
+\newblock Proceedings of the National Academy of Sciences.
+2015;112(36):E5021--E5028.
+\newblock doi:{10.1073/pnas.1505406112}.
+
+\bibitem{piganeau_estimating_2003}
+Piganeau G, {Eyre-Walker} A.
+\newblock Estimating the Distribution of Fitness Effects from {{DNA}} Sequence
+Data: {{Implications}} for the Molecular Clock.
+\newblock Proceedings of the National Academy of Sciences of the United States
+of America. 2003;100(18):10335--10340.
+\newblock doi:{10.1073/pnas.1833064100}.
+
+\bibitem{chi_detecting_2020}
+Chi PB, Kosater WM, Liberles DA.
+\newblock Detecting {{Signatures}} of {{Positive Selection}} against a
+{{Backdrop}} of {{Compensatory Processes}}.
+\newblock Molecular Biology and Evolution. 2020;37(11):3353--3362.
+\newblock doi:{10.1093/molbev/msaa161}.
+
+\bibitem{bazykin_changing_2015}
+Bazykin GA.
+\newblock Changing Preferences: Deformation of Single Position Amino Acid
+Fitness Landscapes and Evolution of Proteins.
+\newblock Biology letters. 2015;11(10):20150315.
+\newblock doi:{10.1098/rsbl.2015.0315}.
+
+\bibitem{moses_inferring_2009}
+Moses AM, Durbin R.
+\newblock Inferring {{Selection}} on {{Amino Acid Preference}} in {{Protein
+Domains}}.
+\newblock Molecular Biology and Evolution. 2009;26(3):527--536.
+\newblock doi:{10.1093/molbev/msn286}.
+
+\bibitem{fischer_germline_2011}
+Fischer A, Greenman C, Mustonen V.
+\newblock Germline {{Fitness-Based Scoring}} of {{Cancer Mutations}}.
+\newblock Genetics. 2011;188(2):383--393.
+\newblock doi:{10.1534/genetics.111.127480}.
+
+\bibitem{chen_hunting_2021}
+Chen J, Bataillon T, Gl{\'e}min S, Lascoux M.
+\newblock Hunting for Beneficial Mutations: Conditioning on {{SIFT}} Scores
+When Estimating the Distribution of Fitness Effect of New Mutations.
+\newblock Genome Biology and Evolution. 2021;doi:{10.1093/gbe/evab151}.
+
+\bibitem{halpern_evolutionary_1998}
+Halpern AL, Bruno WJ.
+\newblock Evolutionary Distances for Protein-Coding Sequences: Modeling
+Site-Specific Residue Frequencies.
+\newblock Molecular Biology and Evolution. 1998;15(7):910--917.
+\newblock doi:{10.1093/oxfordjournals.molbev.a025995}.
+
+\bibitem{mccandlish_modeling_2014}
+McCandlish DM, Stoltzfus A.
+\newblock Modeling Evolution Using the Probability of Fixation: {{History}} and
+Implications.
+\newblock Quarterly Review of Biology. 2014;89(3):225--252.
+\newblock doi:{10.1086/677571}.
+
+\bibitem{rodrigue_mechanistic_2010}
+Rodrigue N, Philippe H.
+\newblock Mechanistic Revisions of Phenomenological Modeling Strategies in
+Molecular Evolution.
+\newblock Trends in Genetics. 2010;26(6):248--252.
+\newblock doi:{10.1016/j.tig.2010.04.001}.
+
+\bibitem{tamuri_estimating_2012}
+Tamuri AU, Goldstein RA.
+\newblock Estimating the Distribution of Selection Coefficients from
+Phylogenetic Data Using Sitewise Mutation-Selection Models.
+\newblock Genetics. 2012;190(3):1101--1115.
+\newblock doi:{10.1534/genetics.111.136432}.
+
+\bibitem{rodrigue_detecting_2017}
+Rodrigue N, Lartillot N.
+\newblock Detecting Adaptation in Protein-Coding Genes Using a {{Bayesian}}
+Site- Heterogeneous Mutation-Selection Codon Substitution Model.
+\newblock Molecular Biology and Evolution. 2017;34(1):204--214.
+\newblock doi:{10.1093/molbev/msw220}.
+
+\bibitem{foley_genomic_2023}
+Foley NM, Mason VC, Harris AJ, Bredemeyer KR, Damas J, Lewin HA, et~al.
+\newblock A Genomic Timescale for Placental Mammal Evolution.
+\newblock Science. 2023;380(6643):eabl8189.
+\newblock doi:{10.1126/science.abl8189}.
+
+\bibitem{howe_ensembl_2021}
+Howe KL, Achuthan P, Allen J, Allen J, {Alvarez-Jarreta} J, Amode MR, et~al.
+\newblock Ensembl 2021.
+\newblock Nucleic Acids Research. 2021;49(D1):D884--D891.
+\newblock doi:{10.1093/nar/gkaa942}.
+
+\bibitem{ranwez_orthomam_2007}
+Ranwez V, Delsuc F, Ranwez S, Belkhir K, Tilak MK, Douzery EJ.
+\newblock {{OrthoMaM}}: {{A}} Database of Orthologous Genomic Markers for
+Placental Mammal Phylogenetics.
+\newblock BMC Evolutionary Biology. 2007;7(1):1--12.
+\newblock doi:{10.1186/1471-2148-7-241}.
+
+\bibitem{scornavacca_orthomam_2019}
+Scornavacca C, Belkhir K, Lopez J, Dernat R, Delsuc F, Douzery EJP, et~al.
+\newblock {{OrthoMaM}} V10: {{Scaling-up}} Orthologous Coding Sequence and Exon
+Alignments with More than One Hundred Mammalian Genomes.
+\newblock Molecular Biology and Evolution. 2019;36(4):861--862.
+\newblock doi:{10.1093/molbev/msz015}.
+
+\bibitem{rodrigue_mutationselection_2010}
+Rodrigue N, Philippe H, Lartillot N.
+\newblock Mutation-Selection Models of Coding Sequence Evolution with
+Site-Heterogeneous Amino Acid Fitness Profiles.
+\newblock Proceedings of the National Academy of Sciences of the United States
+of America. 2010;107(10):4629--34.
+\newblock doi:{10.1073/pnas.0910915107}.
+
+\bibitem{landrum_clinvar_2018}
+Landrum MJ, Lee JM, Benson M, Brown GR, Chao C, Chitipiralla S, et~al.
+\newblock {{ClinVar}}: Improving Access to Variant Interpretations and
+Supporting Evidence.
+\newblock Nucleic Acids Research. 2018;46(D1):D1062--D1067.
+\newblock doi:{10.1093/nar/gkx1153}.
+
+\bibitem{grimm_evaluation_2015}
+Grimm DG, Azencott CA, Aicheler F, Gieraths U, MacArthur DG, Samocha KE, et~al.
+\newblock The {{Evaluation}} of {{Tools Used}} to {{Predict}} the {{Impact}} of
+{{Missense Variants Is Hindered}} by {{Two Types}} of {{Circularity}}.
+\newblock Human Mutation. 2015;36(5):513--523.
+\newblock doi:{10.1002/humu.22768}.
+
+\bibitem{sullivan_leveraging_2023}
+Sullivan PF, Meadows JRS, Gazal S, Phan BN, Li X, Genereux DP, et~al.
+\newblock Leveraging Base-Pair Mammalian Constraint to Understand Genetic
+Variation and Human Disease.
+\newblock Science. 2023;380(6643):eabn2937.
+\newblock doi:{10.1126/science.abn2937}.
+
+\bibitem{eyre-walker_distribution_2006}
+{Eyre-Walker} A, Woolfit M, Phelps T.
+\newblock The Distribution of Fitness Effects of New Deleterious Amino Acid
+Mutations in Humans.
+\newblock Genetics. 2006;173(2):891--900.
+\newblock doi:{10.1534/genetics.106.057570}.
+
+\bibitem{eyre-walker_estimating_2009}
+{Eyre-Walker} A, Keightley PD.
+\newblock Estimating the {{Rate}} of {{Adaptive Molecular Evolution}} in the
+{{Presence}} of {{Slightly Deleterious Mutations}} and {{Population Size
+Change}}.
+\newblock Molecular Biology and Evolution. 2009;26(9):2097--2108.
+\newblock doi:{10.1093/molbev/msp119}.
+
+\bibitem{galtier_adaptive_2016}
+Galtier N.
+\newblock Adaptive Protein Evolution in Animals and the Effective Population
+Size Hypothesis.
+\newblock PLoS Genetics. 2016;12(1):e1005774.
+\newblock doi:{10.1371/journal.pgen.1005774}.
+
+\bibitem{tataru_inference_2017}
+Tataru P, Mollion M, Gl{\'e}min S, Bataillon T.
+\newblock Inference of Distribution of Fitness Effects and Proportion of
+Adaptive Substitutions from Polymorphism Data.
+\newblock Genetics. 2017;207(3):1103--1119.
+\newblock doi:{10.1534/genetics.117.300323}.
+
+\bibitem{bergeron_evolution_2023}
+Bergeron LA, Besenbacher S, Zheng J, Li P, Bertelsen MF, Quintard B, et~al.
+\newblock Evolution of the Germline Mutation Rate across Vertebrates.
+\newblock Nature. 2023; p. 1--7.
+\newblock doi:{10.1038/s41586-023-05752-y}.
+
+\bibitem{orlando_recalibrating_2013}
+Orlando L, Ginolhac A, Zhang G, Froese D, Albrechtsen A, Stiller M, et~al.
+\newblock Recalibrating {{Equus}} Evolution Using the Genome Sequence of an
+Early {{Middle Pleistocene}} Horse.
+\newblock Nature. 2013;499(7456):74--78.
+\newblock doi:{10.1038/nature12323}.
+
+\bibitem{achaz_frequency_2009}
+Achaz G.
+\newblock Frequency {{Spectrum Neutrality Tests}}: {{One}} for {{All}} and
+{{All}} for {{One}}.
+\newblock Genetics. 2009;183(1):249--258.
+\newblock doi:{10.1534/genetics.109.104042}.
+
+\bibitem{latrille_genes_2023}
+Latrille T, Rodrigue N, Lartillot N.
+\newblock Genes and Sites under Adaptation at the Phylogenetic Scale Also
+Exhibit Adaptation at the Population-Genetic Scale.
+\newblock Proceedings of the National Academy of Sciences of the United States
+of America. 2023;120(11):e2214977120.
+\newblock doi:{10.1073/pnas.2214977120}.
+
+\bibitem{ng_sift_2003}
+Ng PC, Henikoff S.
+\newblock {{SIFT}}: Predicting Amino Acid Changes That Affect Protein Function.
+\newblock Nucleic Acids Research. 2003;31(13):3812--3814.
+\newblock doi:{10.1093/nar/gkg509}.
+
+\bibitem{vaser_sift_2016}
+Vaser R, Adusumalli S, Leng SN, Sikic M, Ng PC.
+\newblock {{SIFT}} Missense Predictions for Genomes.
+\newblock Nature Protocols. 2016;11(1):1--9.
+\newblock doi:{10.1038/nprot.2015.123}.
+
+\bibitem{keightley_what_2010}
+Keightley PD, {Eyre-Walker} A.
+\newblock What Can We Learn about the Distribution of Fitness Effects of New
+Mutations from {{DNA}} Sequence Data?
+\newblock Philosophical Transactions of the Royal Society B: Biological
+Sciences. 2010;365(1544):1187--1193.
+\newblock doi:{10.1098/rstb.2009.0266}.
+
+\bibitem{rice_evolutionarily_2015}
+Rice DP, Good BH, Desai MM.
+\newblock The {{Evolutionarily Stable Distribution}} of {{Fitness Effects}}.
+\newblock Genetics. 2015;200(1):321--329.
+\newblock doi:{10.1534/genetics.114.173815}.
+
+\bibitem{mustonen_fitness_2010}
+Mustonen V, L{\"a}ssig M.
+\newblock Fitness Flux and Ubiquity of Adaptive Evolution.
+\newblock Proceedings of the National Academy of Sciences.
+2010;107(9):4248--4253.
+\newblock doi:{10.1073/pnas.0907953107}.
+
+\bibitem{eyre-walker_how_2014}
+{Eyre-Walker} A, {Eyre-Walker} YC.
+\newblock How Much of the Variation in the Mutation Rate along the Human Genome
+Can Be Explained?
+\newblock G3: Genes, Genomes, Genetics. 2014;4(9):1667--1670.
+\newblock doi:{10.1534/g3.114.012849}.
+
+\bibitem{mustonen_molecular_2008}
+Mustonen V, L{\"a}ssig M.
+\newblock Molecular {{Evolution}} under {{Fitness Fluctuations}}.
+\newblock Physical Review Letters. 2008;100(10):108101.
+\newblock doi:{10.1103/PhysRevLett.100.108101}.
+
+\bibitem{latrille_inferring_2021}
+Latrille T, Lanore V, Lartillot N.
+\newblock Inferring Long-Term Effective Population Size with
+Mutation--Selection Models.
+\newblock Molecular Biology and Evolution. 2021;38(10):4573--4587.
+\newblock doi:{10.1093/molbev/msab160}.
+
+\bibitem{huber_determining_2017}
+Huber CD, Kim BY, Marsden CD, Lohmueller KE.
+\newblock Determining the Factors Driving Selective Effects of New
+Nonsynonymous Mutations.
+\newblock Proceedings of the National Academy of Sciences.
+2017;114(17):4465--4470.
+\newblock doi:{10.1073/pnas.1619508114}.
+
+\bibitem{lanfear_population_2014}
+Lanfear R, Kokko H, {Eyre-Walker} A.
+\newblock Population Size and the Rate of Evolution.
+\newblock Trends in Ecology and Evolution. 2014;29(1):33--41.
+\newblock doi:{10.1016/j.tree.2013.09.009}.
+
+\bibitem{platt_protein_2018}
+Platt A, Weber CC, Liberles DA.
+\newblock Protein Evolution Depends on Multiple Distinct Population Size
+Parameters.
+\newblock BMC Evolutionary Biology. 2018;18(1):1--9.
+\newblock doi:{10.1186/s12862-017-1085-x}.
+
+\bibitem{starr_epistasis_2016}
+Starr TN, Thornton JW.
+\newblock Epistasis in Protein Evolution.
+\newblock Protein Science. 2016;25(7):1204--1218.
+\newblock doi:{10.1002/pro.2897}.
+
+\bibitem{morcos_directcoupling_2011}
+Morcos F, Pagnani A, Lunt B, Bertolino A, Marks DS, Sander C, et~al.
+\newblock Direct-Coupling Analysis of Residue Coevolution Captures Native
+Contacts across Many Protein Families.
+\newblock Proceedings of the National Academy of Sciences.
+2011;108(49):E1293--E1301.
+\newblock doi:{10.1073/pnas.1111471108}.
+
+\bibitem{marks_protein_2012}
+Marks DS, Hopf TA, Sander C.
+\newblock Protein Structure Prediction from Sequence Variation.
+\newblock Nature Biotechnology. 2012;30(11):1072--1080.
+\newblock doi:{10.1038/nbt.2419}.
+
+\bibitem{goldstein_nonadaptive_2015}
+Goldstein RA, Pollard ST, Shah SD, Pollock DD.
+\newblock Nonadaptive {{Amino Acid Convergence Rates Decrease}} over {{Time}}.
+\newblock Molecular Biology and Evolution. 2015;32(6):1373--1381.
+\newblock doi:{10.1093/molbev/msv041}.
+
+\bibitem{goldstein_sequence_2017}
+Goldstein RA, Pollock DD.
+\newblock Sequence Entropy of Folding and the Absolute Rate of Amino Acid
+Substitutions.
+\newblock Nature Ecology \& Evolution. 2017;1(12):1923--1930.
+\newblock doi:{10.1038/s41559-017-0338-9}.
+
+\bibitem{park_epistatic_2022}
+Park Y, Metzger BPH, Thornton JW.
+\newblock Epistatic Drift Causes Gradual Decay of Predictability in Protein
+Evolution.
+\newblock Science. 2022;376(6595):823--830.
+\newblock doi:{10.1126/science.abn6895}.
+
+\bibitem{ashenberg_mutational_2013}
+Ashenberg O, Gong LI, Bloom JD.
+\newblock Mutational Effects on Stability Are Largely Conserved during Protein
+Evolution.
+\newblock Proceedings of the National Academy of Sciences of the United States
+of America. 2013;110(52):21071--21076.
+\newblock doi:{10.1073/pnas.1314781111}.
+
+\bibitem{doud_sitespecific_2015}
+Doud MB, Ashenberg O, Bloom JD.
+\newblock Site-{{Specific Amino Acid Preferences Are Mostly Conserved}} in
+{{Two Closely Related Protein Homologs}}.
+\newblock Molecular Biology and Evolution. 2015;32(11):2944--2960.
+\newblock doi:{10.1093/molbev/msv167}.
+
+\bibitem{bloom_identification_2017}
+Bloom JD.
+\newblock Identification of Positive Selection in Genes Is Greatly Improved by
+Using Experimentally Informed Site-Specific Models.
+\newblock Biology Direct. 2017;12(1):1--24.
+\newblock doi:{10.1186/s13062-016-0172-z}.
+
+\bibitem{youssef_consequences_2020}
+Youssef N, Susko E, Bielawski JP.
+\newblock Consequences of Stability-Induced Epistasis for Substitution Rates.
+\newblock Molecular Biology and Evolution. 2020;doi:{10.1093/molbev/msaa151}.
+
+\bibitem{vigue_deciphering_2022}
+Vigu{\'e} L, Croce G, Petitjean M, Rupp{\'e} E, Tenaillon O, Weigt M.
+\newblock Deciphering Polymorphism in 61,157 {{Escherichia}} Coli Genomes via
+Epistatic Sequence Landscapes.
+\newblock Nature Communications. 2022;13(1):4030.
+\newblock doi:{10.1038/s41467-022-31643-3}.
+
+\bibitem{kimura_evolutionary_1968}
+Kimura M.
+\newblock Evolutionary Rate at the Molecular Level.
+\newblock Nature. 1968;217(5129):624--626.
+
+\bibitem{gillespie_substitution_1994}
+Gillespie JH.
+\newblock Substitution Processes in Molecular Evolution. {{III}}.
+{{Deleterious}} Alleles.
+\newblock Genetics. 1994;138(3):943--952.
+\newblock doi:{10.1093/genetics/138.3.943}.
+
+\bibitem{jensen_importance_2019}
+Jensen JD, Payseur BA, Stephan W, Aquadro CF, Lynch M, Charlesworth D, et~al.
+\newblock The Importance of the {{Neutral Theory}} in 1968 and 50 Years on:
+{{A}} Response to {{Kern}} and {{Hahn}} 2018.
+\newblock Evolution. 2019;73(1):111--114.
+\newblock doi:{10.1111/evo.13650}.
+
+\bibitem{galtier_half_2024}
+Galtier N.
+\newblock Half a {{Century}} of {{Controversy}}: {{The
+Neutralist}}/{{Selectionist Debate}} in {{Molecular Evolution}}.
+\newblock Genome Biology and Evolution. 2024;16(2):evae003.
+\newblock doi:{10.1093/gbe/evae003}.
+
+\bibitem{galtier_adaptation_2007}
+Galtier N, Duret L.
+\newblock Adaptation or Biased Gene Conversion? {{Extending}} the Null
+Hypothesis of Molecular Evolution.
+\newblock Trends in Genetics. 2007;23(6):273--277.
+\newblock doi:{10.1016/j.tig.2007.03.011}.
+
+\bibitem{rousselle_influence_2019}
+Rousselle M, Laverr{\'e} A, Figuet E, Nabholz B, Galtier N.
+\newblock Influence of {{Recombination}} and {{GC-biased Gene Conversion}} on
+the {{Adaptive}} and {{Nonadaptive Substitution Rate}} in {{Mammals}} versus
+{{Birds}}.
+\newblock Molecular Biology and Evolution. 2019;36(3):458--471.
+\newblock doi:{10.1093/molbev/msy243}.
+
+\bibitem{joseph_increased_2024a}
+Joseph J.
+\newblock Increased {{Positive Selection}} in {{Highly Recombining Genes Does}}
+Not {{Necessarily Reflect}} an {{Evolutionary Advantage}} of
+{{Recombination}}.
+\newblock Molecular Biology and Evolution. 2024; p. msae107.
+\newblock doi:{10.1093/molbev/msae107}.
+
+\bibitem{ohta_development_1996}
+Ohta T, Gillespie JH.
+\newblock Development of {{Neutral}} and {{Nearly Neutral Theories}}.
+\newblock Theoretical Population Biology. 1996;49(2):128--142.
+\newblock doi:{10.1006/tpbi.1996.0007}.
+
+\bibitem{spielman_relationship_2015}
+Spielman SJ, Wilke CO.
+\newblock The Relationship between {{dN}}/{{dS}} and Scaled Selection
+Coefficients.
+\newblock Molecular biology and evolution. 2015;32(4):1097--1108.
+\newblock doi:{10.1093/molbev/msv003}.
+
+\bibitem{dosreis_how_2015}
+Dos~Reis M.
+\newblock How to Calculate the Non-Synonymous to Synonymous Rate Ratio of
+Protein-Coding Genes under the Fisher-Wright Mutation-Selection Framework.
+\newblock Biology Letters. 2015;11(4):20141031.
+\newblock doi:{10.1098/rsbl.2014.1031}.
+
+\bibitem{rodrigue_bayesian_2021}
+Rodrigue N, Latrille T, Lartillot N.
+\newblock A {{Bayesian}} Mutation-Selection Framework for Detecting
+Site-Specific Adaptive Evolution in Protein-Coding Genes.
+\newblock Molecular Biology and Evolution. 2021;38(3):1199--1208.
+\newblock doi:{10.1093/molbev/msaa265}.
+
+\bibitem{tamuri_mutationselection_2021}
+Tamuri AU, {dos Reis} M.
+\newblock A Mutation-Selection Model of Protein Evolution under Persistent
+Positive Selection.
+\newblock Molecular Biology and Evolution. 2021;doi:{10.1093/molbev/msab309}.
+
+\bibitem{kazmi_detecting_2019}
+Kazmi SO, Rodrigue N.
+\newblock Detecting Amino Acid Preference Shifts with Codon-Level
+Mutation-Selection Mixture Models.
+\newblock BMC Evolutionary Biology. 2019;19(1):62.
+\newblock doi:{10.1186/s12862-019-1358-7}.
+
+\bibitem{stolyarova_senescence_2020}
+Stolyarova AV, Nabieva E, Ptushenko VV, Favorov AV, Popova AV, Neverov AD,
+et~al.
+\newblock Senescence and Entrenchment in Evolution of Amino Acid Sites.
+\newblock Nature Communications. 2020;11(1):4603.
+\newblock doi:{10.1038/s41467-020-18366-z}.
+
+\bibitem{douzery_orthomam_2014}
+Douzery EJP, Scornavacca C, Romiguier J, Belkhir K, Galtier N, Delsuc F, et~al.
+\newblock {{OrthoMaM}} v8: {{A}} Database of Orthologous Exons and Coding
+Sequences for Comparative Genomics in Mammals.
+\newblock Molecular Biology and Evolution. 2014;31(7):1923--1928.
+\newblock doi:{10.1093/molbev/msu132}.
+
+\bibitem{yang_mutationselection_2008}
+Yang Z, Nielsen R.
+\newblock Mutation-Selection Models of Codon Substitution and Their Use to
+Estimate Selective Strengths on Codon Usage.
+\newblock Molecular Biology and Evolution. 2008;25(3):568--579.
+\newblock doi:{10.1093/molbev/msm284}.
+
+\bibitem{wright_evolution_1931}
+Wright S.
+\newblock Evolution in {{Mendelian}} Populations.
+\newblock Genetics. 1931;16(2):97--159.
+\newblock doi:{10.1093/genetics/16.2.97}.
+
+\bibitem{fisher_genetical_1930}
+Fisher RA.
+\newblock The {{Genetical Theory}} of {{Natural Selection}}.
+\newblock The Clarendon Press; 1930.
+
+\bibitem{rodrigue_bayesian_2008}
+Rodrigue N, Lartillot N, Philippe H.
+\newblock Bayesian Comparisons of Codon Substitution Models.
+\newblock Genetics. 2008;180(3):1579--1591.
+\newblock doi:{10.1534/genetics.108.092254}.
+
+\bibitem{lartillot_bayesian_2004}
+Lartillot N.
+\newblock A Bayesian Mixture Model for Across-Site Heterogeneities in the
+Amino-Acid Replacement Process.
+\newblock Molecular biology and evolution. 2004;21(6):1095--1109.
+\newblock doi:{10.1093/molbev/msh112}.
+
+\bibitem{lartillot_inference_2013}
+Lartillot N.
+\newblock Inf{\'e}rence Probabiliste Pour La Phylog{\'e}nie, La G{\'e}nomique
+Comparative et Les Sciences de La Macro-{\'E}volution; 2013.
+
+\bibitem{alabri_whole_2020}
+Al~Abri MA, Holl HM, Kalla SE, Sutter NB, Brooks SA.
+\newblock Whole Genome Detection of Sequence and Structural Polymorphism in Six
+Diverse Horses.
+\newblock PLoS ONE. 2020;15(4):e0230899.
+\newblock doi:{10.1371/journal.pone.0230899}.
+
+\bibitem{sherry_dbsnp_2001}
+Sherry ST, Ward MH, Kholodov M, Baker J, Phan L, Smigielski EM, et~al.
+\newblock {{dbSNP}}: The {{NCBI}} Database of Genetic Variation.
+\newblock Nucleic Acids Research. 2001;29(1):308--311.
+\newblock doi:{10.1093/nar/29.1.308}.
+
+\bibitem{svardal_ancient_2017}
+Svardal H, Jasinska AJ, Apetrei C, Coppola G, Huang Y, Schmitt CA, et~al.
+\newblock Ancient Hybridization and Strong Adaptation to Viruses across
+{{African}} Vervet Monkey Populations.
+\newblock Nature Genetics. 2017;49(12):1705--1713.
+\newblock doi:{10.1038/ng.3980}.
+
+\bibitem{zheng-bradley_alignment_2017}
+{Zheng-Bradley} X, Streeter I, Fairley S, Richardson D, Clarke L, Flicek P,
+et~al.
+\newblock Alignment of 1000 {{Genomes Project}} Reads to Reference Assembly
+{{GRCh38}}.
+\newblock GigaScience. 2017;6(7):gix038.
+\newblock doi:{10.1093/gigascience/gix038}.
+
+\bibitem{keightley_inferring_2018}
+Keightley PD, Jackson BC.
+\newblock Inferring the Probability of the Derived vs the Ancestral Allelic
+State at a Polymorphic Site.
+\newblock Genetics. 2018;209(3):897--906.
+\newblock doi:{10.1534/genetics.118.301120}.
+
+\bibitem{ashkenazy_fastml_2012}
+Ashkenazy H, Penn O, {Doron-Faigenboim} A, Cohen O, Cannarozzi G, Zomer O,
+et~al.
+\newblock {{FastML}}: A Web Server for Probabilistic Reconstruction of
+Ancestral Sequences.
+\newblock Nucleic Acids Research. 2012;40(W1):W580--W584.
+\newblock doi:{10.1093/nar/gks498}.
+
+\bibitem{tataru_polydfe_2020}
+Tataru P, Bataillon T.
+\newblock {{polyDFE}}: {{Inferring}} the Distribution of Fitness Effects and
+Properties of Beneficial Mutations from Polymorphism Data.
+\newblock In: Methods in {{Molecular Biology}}. vol. 2090. Humana Press Inc.;
+2020. p. 125--146.
+
+\bibitem{orme_caper_2013}
+Orme D, Freckleton R, Thomas G, Petzoldt T, Fritz S, Isaac N, et~al.
+\newblock The Caper Package: Comparative Analysis of Phylogenetics and
+Evolution in {{R}}.
+\newblock R package version. 2013;5(2):1--36.
+
+\bibitem{kumar_timetree_2017}
+Kumar S, Stecher G, Suleski M, Hedges SB.
+\newblock {{TimeTree}}: A Resource for Timelines, Timetrees, and Divergence
+Times.
+\newblock Molecular Biology and Evolution. 2017;34(7):1812--1819.
+\newblock doi:{10.1093/molbev/msx116}.
+
+\end{thebibliography}
+
+\newpage
+\section*{Supplementary figures and tables}
+\subsection*{List of Figures}
+\begin{itemize}
+\item S1: Bayesian hierarchical model (p.5).
+\item S2: Examples sites of $\SphyBen$ mutations in \textit{Chlorocebus sabaeus} (reversions) (p.10).
+\item S3: Examples sites of $\SphyBen$ mutations in \textit{Chlorocebus sabaeus} (p.11).
+\item S4: Enrichment in $\SphyBen$ SNPs across all gene ontology terms (p.17).
+\item S5: Estimation of selection at the population scale for $\SphyDel$ mutations (p.19).
+\item S6: Estimation of selection at the population scale for $\SphyNeu$ mutations (p.19).
+\item S7: Estimation of selection at the population scale for $\SphyBen$ mutations (p.19).
+\item S8: Distribution of scaled selection coefficients ($\Sphy$) (p.20).
+\item S9: Tree used for PGLM (Phylogenetic Generalized Linear Model) (p.21).
+\item S10: Proportion of deleterious mutations ($\SpopDel$) (p.22).
+\item S11: Proportion of nearly-neutral mutations ($\SpopNeu$) (p.23).
+\item S12: Proportion of beneficial mutations ($\SpopBen$) (p.24).
+\item S13: $\proba[\SphyBen\given \SpopBen ]$ as a function of distance to the sister species (p.26).
+\item S14: Ratio of $\proba[\Sphy]$ over $\proba[-\Sphy]$ for polymorphisms of the African population of \textit{Homo sapiens} (p.27).
+\item S15: Simulations of site-frequency spectra (p.29).
+\item S16: Site-frequency spectrum in African population of \textit{Homo sapiens}, masking CpG transitions  (p.32).
+\item S17: Site-frequency spectrum in South African population of \textit{Chlorocebus sabaeus}, masking CpG transitions (p.32).
+\item S18: Including substitutions in the terminal lineage to estimate $\Spop$ (p.34).
+\item S19: $\proba[\SphyBen\given \SpopBen ]$ while including divergence to estimate $\Spop$, as a function of distance to the sister species (p.37).
+\item S20: $\proba [ \SpopDel ]$ when fitting a single or three DFEs (p.40).
+\item S21: $\proba [ \SpopNeu ]$ when fitting a single or three DFEs (p.40).
+\item S22: $\proba [ \SpopBen ]$ when fitting a single or three DFEs (p.40).
+\end{itemize}
+
+\newpage
+\subsection*{List of Tables}
+\begin{itemize}
+\item S1: Probability of mutations and substitutions to be $\SphyDel$, $\SphyNeu$ or $\SphyBen$ (p.12).
+\item S2: $\dnds$ for $\SphyDel$, $\SphyNeu$ or $\SphyBen$ (p.13).
+\item S3: $\dnds$ over-estimation due to non-adaptive beneficial mutations (p.14).
+\item S4: Gene ontology enrichment in $\SphyBen$ SNPs (p.15).
+\item S5: Terms associated with deleterious mutations $\SphyDel$ (p.18).
+\item S6: Terms associated with non-adaptive beneficial mutations $\SphyBen$ (p.18).
+\item S7: Probability for beneficial mutations to be non-adaptive ($\proba[\SphyBen\given \SpopBen ]$) (p.25).
+\item S8: $\proba[\SphyBen\given \SpopBen ]$ while masking CpG transitions (p.30).
+\item S9: Precision and recall while masking CpG transitions (p.31).
+\item S10: $\proba[\SphyBen\given \SpopBen ]$ excluding or not genes under adaptation (p.33).
+\item S11: $\proba[\SphyBen\given \SpopBen ]$ when including divergence to estimate $\Spop$ (p.35).
+\item S12: Precision and recall while including divergence to estimate $\Spop$ (p.36).
+\item S13: $\proba[\SphyBen\given \SpopBen ]$ excluding or not genes under adaptation, when including divergence to estimate $\Spop$ (p.38).
+\item S14: $\proba[\SphyBen\given \SpopBen ]$ when using a discrete DFE to estimate $\Spop$ (p.41).
+\item S15: Precision and recall when using a discrete DFE to estimate $\Spop$ (p.42).
+\end{itemize}
+
 \end{document}

### 2024-12-05 manuscript/supp-mat-PLOS-revision-2.tex
Revision PLOS Genetics round 2

--- 2024-06-19 manuscript/supp-mat.tex
@@
 \documentclass{article}
-\usepackage{caption}
+\usepackage[hypcap=false]{caption}
 \usepackage{xcolor, colortbl}
@@
 \definecolor{DARKBLUELINK}{HTML}{0B0080}
+\usepackage[colorlinks=false]{hyperref}
 \PassOptionsToPackage{hyphens}{url}
-\usepackage[colorlinks=false]{hyperref}
 % for linking between references, figures, TOC, etc in the pdf document
@@
 \newcommand{\SpopBen}{\mathcal{B}}
-\newcommand{\ProbaPopDel}{\proba [ \SpopDel]}
-\newcommand{\ProbaPopNeu}{\proba [ \SpopNeu ]}
-\newcommand{\ProbaPopBen}{\proba [ \SpopBen ]}
+\newcommand{\ProbaPopDel}{\proba{[} \SpopDel]}
+\newcommand{\ProbaPopNeu}{\proba{[} \SpopNeu ]}
+\newcommand{\ProbaPopBen}{\proba{[} \SpopBen ]}
 \newcommand{\AdvMean}{\beta_b}
@@
 
-    The parameterization of the models is described as a Bayesian hierarchical model, including the prior distributions and the parameters of the model.
-    This hierarchical model is formally represented as directed acyclic graph of dependencies between variables, depicted below.
-
-    \begin{center}
-        \captionof{figure}{Bayesian hierarchical model.}
+    We here present the Mutation-selection codon model as a Bayesian hierarchical model, including the prior distributions and the parameters of the model.
+    This hierarchical model is formally represented as directed acyclic graph of dependencies between variables, depicted in Figure~\ref{mutsel-illustration}:
+
+    \begin{center}
+
         \begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=0.6cm and 1.2cm,semithick]
@@
         \end{tikzpicture}
-    \end{center}
-
-    Nodes of the directed acyclic graph are the variables, and edges are the functions.
+        \captionof{figure}[Bayesian hierarchical model.]{
+    \textbf{Bayesian hierarchical model.} Nodes of the directed acyclic graph are the variables, and edges are the functions.
     Hyper-parameters are depicted in {\color{RED}{red}} circles, random variables in {\color{BLUE}{blue}} circles, and transformed variables in black.
@@
     The other way around, following the arrows in the DAG (downstream), simple {prior} distributions are combined together to form more complex joint {prior} distributions which ultimately define the {prior} distribution of the model.
+    Equations~\ref{eq:gtr-mutrates} to~\ref{eq:Probmatrix} describe the relationship between variables (sections~\ref{sec:nuc} to~\ref{sec:codon}).
+    \label{mutsel-illustration}}
+    \end{center}
 
     \subsection{Nucleotide mutation rates}
+    \label{sec:nuc}
     The generalized time-reversible (GTR) nucleotide mutation rate matrix $\Mutmatrix$ is a function of the nucleotide frequencies $\Mutequi$ and the symmetric exchangeability rates $\Exchan$~\cite{tavare_probabilistic_1986}.
@@
     \subsection{Codon substitution rates}
-
+    \label{sec:codon}
     The mutation rate between codons $\ci$ and $\cj$, denoted $\mu_{\itoj}$ depends on the underlying nucleotide change between the codons.
@@
             \submatrix\siteexp_{\itoj} = \mu_{\itoj}\text{ if codons $\ci$ and $\cj$ are {synonymous},} \\
-            \submatrix\siteexp_{\itoj} = \mu_{\itoj} \dfrac{ \fitj\siteexp - \fiti\siteexp}{{1 - \e^{\fiti\siteexp - \fitj\siteexp} }} \text{ if $\ci$ and $\cj$ are non-synonymous,}\\
+            \submatrix\siteexp_{\itoj} = \mu_{\itoj} \dfrac{ \fitj\siteexp - \fiti\siteexp}{{1 - \e^{\fiti\siteexp - \fitj\siteexp} }} \text{ if codons $\ci$ and $\cj$ are non-synonymous,}\\
             \submatrix\siteexp_{\ci, \ci} = - \sum\limits_{ \cj \neq \ci, \cj=1}^{61} \submatrix\siteexp_{\itoj}.
@@
     An alternative, which is used here, is to do the {MCMC} conditionally on the detailed {substitution} history $\subhistory$, thus doing the {MCMC} over the augmented configuration~($\subhistory$, $\data$), under the target distribution obtained by combining the mapping-based {likelihood} with the {prior} over model parameters.
-    The key idea that makes this strategy efficient is that the mapping-based {likelihood} depends on compact summary statistics of $\subhistory$, leading to very fast evaluation of the {likelihood}.
+    The key idea that makes this strategy efficient is that the mapping-based {likelihood} depends on compact summary statistics of $\subhistory$, leading to a very fast evaluation of the {likelihood}.
     On the other hand, this requires to implement more complex {MCMC} procedures that have to alternate between:
@@
     To implement the mapping-based {MCMC} sampling strategy, we first sample the detailed {substitution} history $\subhistory$ for all sites along the tree.
-    Several methods exist for doing this~\cite{nielsen_mapping_2002,rodrigue_uniformization_2008}, which are used here in combination (first trying the accept-reject method of \textcite{nielsen_mapping_2002}, then switching to the uniformization approach of \textcite{rodrigue_uniformization_2008} if the first round has failed).
+    Several methods exist for doing this~\cite{nielsen_mapping_2002,rodrigue_uniformization_2008}, which are used here in combination: first trying the accept-reject method of \textcite{nielsen_mapping_2002}, then switching to the uniformization approach of \textcite{rodrigue_uniformization_2008} if the first round has failed.
 
@@
 
-    \newpage
-
     \section{Beneficial mutations in the terminal lineages and populations}\label{sec:beneficial-mutations}
@@
     We also show the translated amino acids of this region.
-    For instance, in DNA alignment of gene SELE shown below, the nucleotide at site 1722 has mutated (from T to C) at the basis of Simiiformes (monkeys and apes), modifying the corresponding amino acid from Serine to Proline, but has been subsequently reverted in the branch of \textit{Chlorocebus sabaeus}.
+    For instance, in DNA alignment of gene SELE (\ref{fig:example-1}), the nucleotide at site 1722 has mutated (from T to C) at the basis of Simiiformes (monkeys and apes), modifying the corresponding amino acid from Serine to Proline, but has been subsequently reverted in the branch of \textit{Chlorocebus sabaeus}.
     However, other substitutions classified as $\SphyBen$ cannot be clearly interpreted as reversions \textit{sensu stricto} along the terminal branch of \textit{Chlorocebus sabaeus}.
@@
 
-    In the figures below, the first line is the name of the gene, the second line the position of the mutation in the OrthoMam protein-coding DNA alignment, and the arrow in the third line corresponds to the nucleotide position of the mutation.
-    Finally, for reproducibility, we generated the fasta alignment for all $\SphyBen$ mutations that we detected, either in the terminal lineage or in segregating polymorphism.
-    These fasta files are available at Zenodo (\url{https://doi.org/10.5281/zenodo.7878953}), across all populations, under the compressed archive \textit{alignment\_focused\_around\_non\_adaptive\_mutations.zip} and we provide a python script to obtain the figures shown below given these alignments.
-
-    \newpage
-    \begin{center}
-        \captionof{figure}{Examples sites of $\SphyBen$ mutations in \textit{Chlorocebus sabaeus} (reversions).}.
-        \includegraphics[width=0.95\linewidth, page=1]{artworks/Alignment.Chlorocebus_sabaeus.Saint_Kitts-0.pdf}
-    \end{center}
-
-    \newpage
-    \begin{center}
-        \captionof{figure}{Examples sites of $\SphyBen$ mutations in \textit{Chlorocebus sabaeus}.}.
-        \includegraphics[width=0.95\linewidth, page=1]{artworks/Alignment.Chlorocebus_sabaeus.Saint_Kitts-1.pdf}
+    Finally, we generated the fasta alignment for all $\SphyBen$ mutations that we detected, either in the terminal lineage or in segregating polymorphisms.
+    These fasta files are available at Zenodo (\url{https://doi.org/10.5281/zenodo.7878953}), across all populations, under a zip file (\textit{alignment\_around\_non\_adaptive\_mutations.zip}) alongside a python script to obtain the figures (as in Figures~\ref{fig:example-1} and~\ref{fig:example-2}) given these alignments (\textit{plot\_variations.py}).
+
+    \newpage
+    \begin{center}
+        \includegraphics[width=0.9\linewidth, page=1]{artworks/Alignment.Chlorocebus_sabaeus.Saint_Kitts-0.pdf}
+        \captionof{figure}[Examples sites of $\SphyBen$ mutations in \textit{Chlorocebus sabaeus} (reversions).]{\textbf{Examples sites of $\bm{\SphyBen}$ mutations in \textit{Chlorocebus sabaeus}  (reversions).} The first line is the name of the gene, the second line the position of the mutation in the OrthoMam protein-coding DNA alignment, and the arrows in the third line correspond to the position of the mutation in the nucleotide sequence (left) and in the corresponding amino acid sequence (right)\label{fig:example-1}}
+    \end{center}
+
+    \newpage
+    \begin{center}
+        \includegraphics[width=0.9\linewidth, page=1]{artworks/Alignment.Chlorocebus_sabaeus.Saint_Kitts-1.pdf}
+        \captionof{figure}[Examples sites of $\SphyBen$ mutations in \textit{Chlorocebus sabaeus}.]{\textbf{Examples sites of $\bm{\SphyBen}$ mutations in \textit{Chlorocebus sabaeus}.} The first line is the name of the gene, the second line the position of the mutation in the OrthoMam protein-coding DNA alignment, and the arrows in the third line correspond to the position of the mutation in the nucleotide sequence (left) and in the corresponding amino acid sequence (right).\label{fig:example-2}}
     \end{center}
@@
 
-    \subsubsection{Probability of mutations and substitutions to be $\SphyDel$, $\SphyNeu$ or $\SphyBen$}
-    \begin{center}
-        \captionof{table}{Probability of mutations and substitutions to be $\SphyDel$, $\SphyNeu$ or $\SphyBen$.}
+    \subsubsection{Probability of mutations and substitutions to be \texorpdfstring{$\SphyDel$}{D₀}, \texorpdfstring{$\SphyNeu$}{N₀} or \texorpdfstring{$\SphyBen$}{B₀}}
+    Among all the substitutions found in each terminal branch, between 10 and 13\% were $\SphyBen$ ($\proba_{div}[ \SphyBen {]}$), while $\SphyBen$ mutations only represent between 0.9 and 1.2\% of all non-synonymous mutations ($\proba[ \SphyBen {]}$), as shown in Table~\ref{table:pdiv}.
+
+    \begin{center}
         \scriptsize
@@
             \toprule
-            Population &             Species & $\proba[ \SphyDel ]$ & $\proba[ \SphyNeu ]$ & $\proba[ \SphyBen ]$ & $\proba_{div}[ \SphyDel ]$ & $\proba_{div}[ \SphyNeu ]$ & $\proba_{div}[ \SphyBen ]$ \\
+            Population &             Species & $\proba{[} \SphyDel {]}$ & $\proba{[} \SphyNeu {]}$ & $\proba{[} \SphyBen {]}$ & $\proba_{div}[ \SphyDel {]}$ & $\proba_{div}[ \SphyNeu {]}$ & $\proba_{div}[ \SphyBen {]}$ \\
             \midrule
@@
         \end{longtable*}
-    \end{center}
-    \begin{itemize}
-        \item $\proba [ \SphyDel ]$ (eq.~5) is the probability for a new mutation to be a deleterious.
+    \captionof{table}[Probability of mutations and substitutions to be $\SphyDel$, $\SphyNeu$ or $\SphyBen$.]{\textbf{Probability of mutations and substitutions to be $\bm{\SphyDel}$, $\bm{\SphyNeu}$ or $\bm{\SphyBen}$.}
+    $\proba{[} \SphyDel {]}$ (eq.~5) is the probability for a new mutation to be deleterious.
      These mutations have a selection coefficient predicted at the phylogenetic-scale lower than -1, thus toward a less fit amino-acid.
-        \item $\proba [ \SphyNeu ]$ (eq.~5) is the probability for a new mutation to be a nearly-neutral.
+    $\proba{[} \SphyNeu {]}$ (eq.~5) is the probability for a new mutation to be nearly-neutral.
     These mutations have a selection coefficient predicted at the phylogenetic-scale between -1 and 1.
-        \item $\proba [ \SphyBen ]$ (eq.~5) is the probability for a new mutation to be a  non-adaptive beneficial mutation.
+    $\proba{[} \SphyBen {]}$ (eq.~5) is the probability for a new mutation to be non-adaptive beneficial.
     These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1, thus toward a more fit amino-acid.
-        \item $\proba_{div}[\SphyDel]$ is the proportion of substitutions in the terminal branch that are $\SphyDel$.
-        \item $\proba_{div}[\SphyNeu]$ is the proportion of substitutions in the terminal branch that are $\SphyNeu$.
-        \item $\proba_{div}[\SphyBen]$ is the proportion of substitutions in the terminal branch that are $\SphyBen$.
-    \end{itemize}
-    \newpage
-
-    \subsubsection{$\dnds$ for $\SphyDel$, $\SphyNeu$ or $\SphyBen$}
-    \begin{center}
-        \captionof{table}{$\dnds$ for $\SphyDel$, $\SphyNeu$ or $\SphyBen$.}
+    $\proba_{div}[\SphyDel{]}$ is the proportion of substitutions in the terminal branch that are $\SphyDel$.
+    $\proba_{div}[\SphyNeu{]}$ is the proportion of substitutions in the terminal branch that are $\SphyNeu$.
+    $\proba_{div}[\SphyBen{]}$ is the proportion of substitutions in the terminal branch that are $\SphyBen$.\label{table:pdiv}}
+    \end{center}
+    \newpage
+
+    \subsubsection{\texorpdfstring{$\dnds$}{dₙ/dₛ} for \texorpdfstring{$\SphyDel$}{D₀}, \texorpdfstring{$\SphyNeu$}{N₀} or \texorpdfstring{$\SphyBen$}{B₀}}
+    Theoretically, $\omega = \dn / \ds$ can be related to the underlying scaled selection coefficient ($S$) with the relation $\omega = S /(1-\exp(-S))$ as in \cite[eq. 3]{nielsen_estimating_2003}.
+    In our experiments, our observed $\dn(\SphyBen) / \ds$ is within the range of $1.169$ (\textit{C.
+hircus}) to 1.745 (\textit{H.
+sapiens}), as shown in Table~\ref{table:dnds}, translating into an average $S$ of $\approx0.32$ to $\approx1.24$, so indeed only slightly advantageous.\\
+
+    Of note, observing $\dn(\SphyBen) / \ds >1$ is an important check that $\SphyBen$ mutations are indeed positively selected with an increased substitution rate.
+    Since $\dn(\SphyNeu) / \ds$ is close to 1 for the predicted nearly-neutral mutations, this means that the selection coefficients predicted at the mutation-selection balance are good proxies of selection, then observing $\dn(\SphyBen) / \ds > 1$ is evidence of positive selection of predicted non-adaptive beneficial mutations.
+    \begin{center}
         \scriptsize
@@
         \end{longtable*}
-    \end{center}
-    \begin{itemize}
-        \item $\dnds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions estimated for all the non-synonymous substitutions in the terminal branch.
-        \item $\dn(\SphyDel) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are $\SphyDel$.
-        \item $\dn(\SphyNeu) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are $\SphyNeu$.
-        \item $\dn(\SphyBen) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are $\SphyBen$.
-    \end{itemize}
-    SNP are considered fixed in the populations if all sampled individuals are homozygous for the derived allele, in which case we consider this SNP not to be segregating but as fixed as a substitution.
-    This effect results in $\dn / \ds$ that can change across populations, denoted as a range per species.
-    $\dn(\SphyBen) / \ds$ values observed are above 1 and are consistent with slightly advantageous mutations.\\
-
-    Theoretically, $\omega = \dn / \ds$ can be related to the underlying scaled selection coefficient ($S$) with the relation $\omega = S /(1-\exp(-S))$ as in \cite[eq. 3]{nielsen_estimating_2003}.
-    In our experiments our observed $\dn(\SphyBen) / \ds$ is on the range $1.169$ (\textit{C.
-hircus}) to 1.745 (\textit{H.
-sapiens}), translating into average $S$ of $\approx0.32$ to $\approx1.24$, so indeed only slightly advantageous.\\
-
-    Of note, observing $\dn(\SphyBen) / \ds >1$ is an important check that $\SphyBen$ mutations are indeed positively selected with an increased substitution rate.
-    Since $\dn(\SphyNeu) / \ds$ is close to 1 for the predicted nearly-neutral mutations, this means that the selection coefficients predicted at the mutation-selection balance are good proxies of selection, then observing $\dn(\SphyBen) / \ds > 1$ is evidence of positive selection of predicted non-adaptive beneficial mutations.
-
-    \newpage
-    \subsubsection{$\dnds$ over-estimation due to non-adaptive beneficial mutations}
-    \begin{center}
-        \captionof{table}{$\dnds$ over-estimation due to non-adaptive beneficial mutations.}
+    \captionof{table}[$\dnds$ for $\SphyDel$, $\SphyNeu$ or $\SphyBen$.]{\textbf{$\bm{\dnds}$ for $\bm{\SphyDel}$, $\bm{\SphyNeu}$ or $\bm{\SphyBen}$.}
+    $\dnds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions estimated for all the non-synonymous substitutions in the terminal branch.
+    $\dn(\SphyDel) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are $\SphyDel$.
+    $\dn(\SphyNeu) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are $\SphyNeu$.
+    $\dn(\SphyBen) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are $\SphyBen$.
+    SNPs are considered fixed (as a substitution) in the populations if all sampled individuals are homozygous for the derived allele.
+    This effect results in $\dn / \ds$ varying across populations, denoted as a range per species.
+    $\dn(\SphyBen) / \ds$ values observed are above 1 and are consistent with slightly advantageous mutations.\label{table:dnds}}
+    \end{center}
+
+    \newpage
+    \subsubsection{\texorpdfstring{$\dnds$}{dₙ/dₛ} over-estimation due to non-adaptive beneficial mutations}
+    We estimated that between $\approx9$ and $\approx12\%$ of $\dnds$ is over-estimated, corresponding to non-adaptive beneficial mutations inflating the $\dnds$ statistic, as shown in Table~\ref{table:dnds-delta}.
+    \begin{center}
         \scriptsize
@@
         \end{longtable*}
-    \end{center}
-    \begin{itemize}
-        \item $\dnds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions estimated for all the non-synonymous substitutions in the terminal branch.
-        \item $\dn(\Sphy < 1) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are not $\SphyBen$.
-        This is the estimated divergence when we removed non-adaptive beneficial mutations.
-        \item $\delta(\dnds)$ (eq.~7) is the fraction of the divergence ($\dnds$) that is over-estimated, $\dnds$ is compared to the estimated divergence when we removed non-adaptive beneficial mutations $\dn(\Sphy < 1) / \ds$.
-    \end{itemize}
-    We estimated that between 9 and 11\% of $\dnds$ is over-estimated, corresponding to non-adaptive beneficial mutations inflating the $\dnds$ statistic.
-
+        \captionof{table}[$\dnds$ over-estimation due to non-adaptive beneficial mutations.]{\textbf{$\bm{\dnds}$ over-estimation due to non-adaptive beneficial mutations.}
+        $\dnds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions estimated for all the non-synonymous substitutions in the terminal branch.
+        $\dn(\Sphy < 1) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are not $\SphyBen$.
+        This is the estimated divergence when we remove non-adaptive beneficial mutations.
+        $\delta(\dnds)$ (eq.~7) is the fraction of the divergence ($\dnds$) that is over-estimated: the difference between $\dnds$ and $\dn(\Sphy < 1) / \ds$.\label{table:dnds-delta}}
+    \end{center}
     \newpage
@@
 
-    \subsection{Gene ontology enrichment in $\SphyBen$ SNPs}
+    \subsection{Gene ontology enrichment in \texorpdfstring{$\SphyBen$}{B₀} SNPs}
 
@@
     Thus, for each $\SphyBen$ SNP detected in a focal population, we annotated this SNP with GO terms inherited from the gene in which the SNP is located.
-    We restricted this analysis solely on genes annotated with at least one GO term. \\
-
-    In order to assess the weight of each GO term in the set of $\SphyBen$ SNPs, we computed the proportion of $\SphyBen$ SNPs annotated with a given GO term.
-    Thus, for each GO term, $p$ is the proportion of $\SphyBen$ SNPs that are annotated with this focal GO term among all annotated $\SphyBen$ SNPs.\\
-
-    In order to test if the distribution of $\SphyBen$ SNPs is different between genes sharing a common GO term and the rest of the genes, we used a Mann-Whitney U test.
-    To do so, first, for each gene, we computed the proportion of sites that have a $\SphyBen$ SNP, called $p[ \SphyBen ]$ (can be 0 if no $\SphyBen$ SNP is detected for this gene).
-    Second, for each GO term, $r$ is the ratio of the mean of $p[ \SphyBen ]$ in the set of genes sharing the focal ontology over the mean of $p[ \SphyBen ]$ in the rest of the genes.
-    Third, Mann-Whitney U test (two-sided) is used to test if the distribution of $p[ \SphyBen ]$ is different between the two sets of genes (U statistic and p-value $p_{\mathrm{v}}$).
-    Finally, $p_{\mathrm{v}}^{\mathrm{adj}}$ are corrected for multiple comparison (Holm–Bonferroni correction across the ontology terms).
-    $^*$ for $p_{\mathrm{v}}^{\mathrm{adj}}$ corrected for multiple comparison (Holm–Bonferroni correction) lower than the risk $\alpha=0.05$. \\
-
-    The table below shows the GO terms (first 100 rows with the lowest $p_{\mathrm{v}}$) that are enriched in genes with $\SphyBen$ SNP in human (european population).
-
-    \begin{center}
-        \captionof{table}{Gene ontology enrichment in $\SphyBen$ SNPs}
+    We restricted this analysis solely on genes annotated with at least one GO term.
+    To assess the weight of each GO term in the set of $\SphyBen$ SNPs, we computed the proportion of $\SphyBen$ SNPs annotated with a given GO term.
+    We then tested if the distribution of $\SphyBen$ SNPs is different between genes sharing a common GO term and the rest of the genes, as shown in Table~\ref{table:ontology}.
+
+    \begin{center}
         \scriptsize
@@
         \end{longtable*}
-    \end{center}
-
-    \newpage
-    \subsection{Enrichment in $\SphyBen$ SNPs across all gene ontology terms}
-    Across all 347 gene ontology terms, the distribution of $p_{\mathrm{v}}$ is shown in the histogram below.
-    \begin{center}
-        \captionof{figure}{Enrichment in $\SphyBen$ SNPs across all gene ontology terms.}
+        \captionof{table}[Gene ontology enrichment in $\SphyBen$ SNPs.]{\textbf{Gene ontology enrichment in $\bm{\SphyBen}$ SNPs.} GO terms that are enriched in genes with $\SphyBen$ SNPs in European humans (shown here are the first 100 rows with the lowest $p_{\mathrm{v}}$).
+        For each GO term, $p$ is the proportion of $\SphyBen$ SNPs that are annotated with this focal GO term among all annotated $\SphyBen$ SNPs.
+        For each gene, $p[ \SphyBen {]}$ is the proportion of sites that have a $\SphyBen$ SNP (can be 0 if no $\SphyBen$ SNP is detected for this gene).
+        For each GO term, $r$ is the ratio of the mean of $p[ \SphyBen {]}$ in the set of genes sharing the focal ontology over the mean of $p[ \SphyBen {]}$ in the rest of the genes.
+        Mann-Whitney U is the statistic testing if the distribution of $p[ \SphyBen {]}$ is different between the two sets of genes (p-value $p_{\mathrm{v}}$ for the two-sided test).
+        $p_{\mathrm{v}}^{\mathrm{adj}}$ are corrected for multiple comparison (Holm–Bonferroni correction across the ontology terms).
+        $^*$ for $p_{\mathrm{v}}^{\mathrm{adj}}$ lower than the risk $\alpha=0.05$.\label{table:ontology}
+        }
+    \end{center}
+
+    \newpage
+    \subsection{Enrichment in \texorpdfstring{$\SphyBen$}{B₀} SNPs across all gene ontology terms}
+    Whether SNPs classified as $\SphyBen$ are associated to a particular ontology is tested with a Mann-Whitney U statistic as described in Table~\ref{table:ontology}.
+    This test is performed across across all 347 gene ontology terms, giving one $p_{\mathrm{v}}$ per ontology (Table~\ref{table:ontology} for the 100 lowest $p_{\mathrm{v}}$).
+    The distribution of $p_{\mathrm{v}}$ are not strongly associated to the ontology terms of their respective genes, as shown in the histogram of Figure~\ref{fig:ontology-p}.
+
+    \begin{center}
         \includegraphics[width=0.65\linewidth]{artworks/ontology_poly.Homo_sapiens.EUR.hist.pdf}
+        \captionof{figure}[Enrichment in $\SphyBen$ SNPs across all gene ontology terms.]{\textbf{Enrichment in $\bm{\SphyBen}$ SNPs across all gene ontology terms}.
+In order to test if the distribution of $\SphyBen$ SNPs is different between genes sharing a common GO term and the rest of the genes, we used a Mann-Whitney U test.
+The distribution of $p_{\mathrm{v}}$ obtained across all 347 gene ontology terms is shown as a histogram.\label{fig:ontology-p}}
     \end{center}
@@
 
-    \subsection{Terms associated with deleterious mutations $\SphyDel$}
-    \begin{center}
-        \captionof{table}{Terms associated with deleterious mutations $\SphyDel$.}
+    \subsection{Terms associated with deleterious mutations \texorpdfstring{$\SphyDel$}{D₀}}
+    SNPs predicted with $\SphyDel$ are statistically associated to clinical terms such as \textit{Likely Pathogenic} and \textit{Pathogenic}, as shown in Table~\ref{table:ontology-neg}.
+
+    \begin{center}
         \begin{tabular}{|l|r|r|r|r|r|}
@@
         \end{tabular}
-    \end{center}
-    In humans (european population), non-synonymous SNPs in the test group ($\SphyDel$) are contrasted to SNPs in the control group ($\SphyNeu$).
-    For each clinical term, a 2x2 contingency tables is built by counting the number of SNPs based on their selection coefficient and their clinical terms (whether they have this specific term or not).
+        \captionof{table}[Terms associated with deleterious mutations $\SphyDel$.]{\textbf{Terms associated with deleterious mutations $\bm{\SphyDel}$.}
+        In humans (European population), non-synonymous SNPs in the test group ($\SphyDel$) are contrasted to SNPs in the control group ($\SphyNeu$).
+        For each clinical term, a 2x2 contingency table is built by counting the number of SNPs based on their selection coefficient and their clinical terms (whether they have this specific term or not).
         Fisher's exact tests are then performed for these 2x2 contingency tables.
-    $^*$ for $p_{\mathrm{v}}^{\mathrm{adj}}$ corrected for multiple comparison (Holm–Bonferroni correction) lower than the risk $\alpha=0.05$.
-    SNPs predicted with $\SphyDel$ are statistically associated to clinical terms such as \textit{Likely Pathogenic} and \textit{Pathogenic}.
-
-    \subsection{Terms associated with non-adaptive beneficial mutations $\SphyBen$}
-    \begin{center}
-        \captionof{table}{Terms associated with non-adaptive beneficial mutations $\SphyBen$.}
+        $^*$ for $p_{\mathrm{v}}^{\mathrm{adj}}$ corrected for multiple comparison (Holm–Bonferroni correction) lower than the risk $\alpha=0.05$.\label{table:ontology-neg}}
+    \end{center}
+
+    \subsection{Terms associated with non-adaptive beneficial mutations \texorpdfstring{$\SphyBen$}{B₀}}
+    Beneficial non-adaptive mutations are associated with clinical terms such as \textit{Benign} and \textit{Likely Benign}, as shown in Table~\ref{table:ontology-pos}.
+    \begin{center}
         \begin{tabular}{|l|r|r|r|r|r|}
@@
         \end{tabular}
-    \end{center}
-    In humans, non-synonymous SNPs in the test group ($\SphyBen$) are contrasted to SNPs in the control group ($\SphyNeu$).
-    For each clinical term, a 2x2 contingency tables is built by counting the number of SNPs based on their selection coefficient and their clinical terms (whether they have this specific term or not).
+        \captionof{table}[Terms associated with non-adaptive beneficial mutations $\SphyBen$.]{\textbf{Terms associated with non-adaptive beneficial mutations $\bm{\SphyBen}$.}
+        In humans (European population), non-synonymous SNPs in the test group ($\SphyBen$) are contrasted to SNPs in the control group ($\SphyNeu$).
+        For each clinical term, a 2x2 contingency table is built by counting the number of SNPs based on their selection coefficient and their clinical terms (whether they have this specific term or not).
         Fisher's exact tests are then performed for these 2x2 contingency tables.
-    $^*$ for $p_{\mathrm{v}}^{\mathrm{adj}}$ corrected for multiple comparison (Holm–Bonferroni correction) lower than the risk $\alpha=0.05$.
-    Beneficial non-adaptive mutations are associated with clinical terms such as \textit{Benign} and \textit{Likely Benign}.
-    \newpage
-
+        $^*$ for $p_{\mathrm{v}}^{\mathrm{adj}}$ corrected for multiple comparison (Holm–Bonferroni correction) lower than the risk $\alpha=0.05$.\label{table:ontology-pos}}
+    \end{center}
+
+    \newpage
+
+    \section{Contrasting selection at the phylogenetic and population-genetic scales}
+
+    \subsection{Selection at the population-genetic scale}
+    The proportion of deleterious ($\ProbaPopDel$), nearly-neutral ($\ProbaPopNeu$) and of beneficial ($\ProbaPopBen$) mutations estimated at the population-genetic scale across the different populations is shown for each class of selection:
+    $\SphyDel$ (Figure~\ref{fig:pop-neg}), $\SphyNeu$ (Figure~\ref{fig:pop-weak}) and $\SphyBen$ (Figure~\ref{fig:pop-pos}).
+
+    \begin{center}
+        \begin{minipage}{0.75\linewidth}
+            \begin{minipage}{0.9\linewidth}
+                \includegraphics[width=\linewidth, page=1]{artworks/Theta.neg.stacked.pdf}
+            \end{minipage}
+            \begin{minipage}{0.09\linewidth}
+                \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
+            \end{minipage}
+        \end{minipage}
+    \captionof{figure}[Estimation of selection at the population scale for $\SphyDel$ mutations.]{\textbf{Estimation of selection at the population scale for $\bm{\SphyDel}$ mutations.} Each stack bar corresponds to the DFE of new mutations predicted to be $\SphyDel$  by the mutation selection model, in a given population.
+The dashed area represents the proportion of deleterious mutations ($\SpopDel$), the gray area that of neutral mutations ($\SpopNeu$), and the yellow area that of beneficial mutations ($\SpopBen$).\label{fig:pop-neg}}
+    \end{center}
+
+    \begin{center}
+        \begin{minipage}{0.75\linewidth}
+            \begin{minipage}{0.9\linewidth}
+                \includegraphics[width=\linewidth, page=1]{artworks/Theta.weak.stacked.pdf}
+            \end{minipage}
+            \begin{minipage}{0.09\linewidth}
+                \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
+            \end{minipage}
+        \end{minipage}
+    \captionof{figure}[Estimation of selection at the population scale for $\SphyNeu$ mutations.]{\textbf{Estimation of selection at the population scale for $\bm{\SphyNeu}$ mutations.} Each stack bar corresponds to the DFE of new mutations predicted to be $\SphyNeu$ by the mutation selection model, in a given population.
+The dashed area represents the proportion of deleterious mutations ($\SpopDel$), the gray area that of neutral mutations ($\SpopNeu$), and the yellow area that of beneficial mutations ($\SpopBen$).\label{fig:pop-weak}}
+    \end{center}
+
+    \begin{center}
+        \begin{minipage}{0.75\linewidth}
+            \begin{minipage}{0.9\linewidth}
+                \includegraphics[width=\linewidth, page=1]{artworks/Theta.pos.stacked.pdf}
+            \end{minipage}
+            \begin{minipage}{0.09\linewidth}
+                \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
+            \end{minipage}
+        \end{minipage}
+    \captionof{figure}[Estimation of selection at the population scale for $\SphyBen$ mutations.]{\textbf{Estimation of selection at the population scale for $\bm{\SphyBen}$ mutations.} Each stack bar corresponds to the DFE of new mutations predicted to be $\SphyBen$ by the mutation selection model, in a given population.
+The dashed area represents the proportion of deleterious mutations ($\SpopDel$), the gray area that of neutral mutations ($\SpopNeu$), and the yellow area that of beneficial mutations ($\SpopBen$).\label{fig:pop-pos}}
+    \end{center}
+
+    \newpage
+    \subsection{Distribution of scaled selection coefficients (\texorpdfstring{$\Sphy$}{S₀})}\label{subsec:expectedDFE}
+
+    Theoretically, the selection coefficient ($\Sphy$) for any mutation is related to its probability of fixation by the equation $\proba_{\text{fix}} (\Sphy) = \Sphy/(1-\exp(-\Sphy)) $.
+    It is thus possible to predict the distribution of $\Sphy$ of substitutions given the distribution of $\Sphy$ for mutations (Figure~\ref{dfe-sfs}A for one population of \textit{Chlorocebus sabaeus}) by weighting the different mutations by their $\proba_{\text{fix}} (\Sphy)$.
+    The predicted DFE (distribution of fitness effects) of substitutions (Figure~\ref{dfe-sfs}B) matches the observed DFE of substitutions (Figure~\ref{dfe-sfs}C) in the terminal lineage, meaning that the $\Sphy$ obtained by phylogenetic mutation-selection codon models is a strong predictor of selection effectively exerted on mutations in terminal lineages.
+    Equivalent figures to Figure~\ref{dfe-sfs} for each one of the 28 populations are available at Zenodo (\url{https://doi.org/10.5281/zenodo.7878953}) in file \textit{distribution\_S0\_28\_populations.pdf}.\\
+
+    \begin{center}
+        \begin{minipage}{0.32\linewidth}
+            \flushleft {\tiny A: Expected DFE for mutations}
+            \includegraphics[width=\linewidth, page=1]{artworks/DFE.Chlorocebus_sabaeus.Saint_Kitts.MutSel.pdf}
+        \end{minipage}
+        \begin{minipage}{0.32\linewidth}
+            \flushleft {\tiny B: Expected DFE for substitutions}
+            \includegraphics[width=\linewidth, page=1]{artworks/DFE.Chlorocebus_sabaeus.Saint_Kitts.MutSel.Flow.pdf}
+        \end{minipage}
+        \begin{minipage}{0.32\linewidth}
+            \flushleft {\tiny C: Observed DFE for substitutions}
+            \includegraphics[width=\linewidth, page=1]{artworks/subs.Chlorocebus_sabaeus.Saint_Kitts.bins3Mask0.9.pdf}
+        \end{minipage}
+        \\
+        \begin{minipage}{0.32\linewidth}
+            \flushleft {\tiny D: Observed DFE for polymorphisms}
+            \includegraphics[width=\linewidth, page=1]{artworks/poly.Chlorocebus_sabaeus.Saint_Kitts.bins3Mask0.9.pdf}
+        \end{minipage}
+        \begin{minipage}{0.32\linewidth}
+            \flushleft {\tiny E: Site frequency spectrum}
+            \includegraphics[width=\linewidth, page=1]{artworks/Chlorocebus_sabaeus.Saint_Kitts.MutSel-sfs.normalize.pdf}
+        \end{minipage}
+        \begin{minipage}{0.32\linewidth}
+            \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
+            \includegraphics[width=\linewidth, page=1]{artworks/Chlorocebus_sabaeus.Saint_Kitts.MutSel.polyDFE_C.pdf}
+        \end{minipage}
+        \captionof{figure}[Distribution of scaled selection coefficients ($\Sphy$).]{\textbf{Distribution of scaled selection coefficients ($\bm{\Sphy}$) in the Saint Kitts population of \textit{Chlorocebus sabaeus}.}
+        A) Distribution of scaled selection coefficients ($\Sphy$), predicted for all possible non-synonymous DNA mutations away from the ancestral exome.
+        Mutations are divided into three classes of selection: deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial non-adaptive ($\SphyBen$).
+        B) Expected distribution of $\Sphy$ for substitutions obtained by transforming the distribution of $\Sphy$ for mutations (panel A) by weighting each mutation by its scaled probability of fixation given by $\proba_{\text{fix}} (\Sphy) = \Sphy/(1-\exp(-\Sphy))$.
+        C) Distribution of scaled selection coefficients ($\Sphy$) for all observed substitutions along the terminal branch of the phylogenetic tree.
+        D) Distribution of scaled selection coefficients ($\Sphy$) for all observed polymorphisms currently segregating in the population.
+        E) The site-frequency spectrum (SFS) in the population for a random sample of 16 alleles (means in solid lines and standard deviations in color shades) for each class of selection and for synonymous mutations, supposedly neutral (black).
+The SFS represents the proportion of mutations (y-axis) with a given number of derived alleles in the population (x-axis).
+At high frequencies, deleterious mutations are underrepresented.
+        F) Proportion of beneficial $\ProbaPopDel$, nearly-neutral $\ProbaPopNeu$, and deleterious mutations $\ProbaPopBen$  estimated at the population scale for each class of selection at the phylogenetic scale.
+Proportions depicted here are not weighted by their mutational opportunities.}
+        \label{dfe-sfs}
+    \end{center}
+
+    \newpage
     \section{Correlation with diversity}
@@
 
-    Because a correlation must account for phylogenetic relationship and non-independence of samples, we fitted a Phylogenetic Generalized Linear Model (PGLM) in R with the package caper\cite{orme_caper_2013}, with multi-furcation of the different populations inside each species.
-    The mammalian tree imported from TimeTree\cite{kumar_timetree_2017} and pruned to the species used in this study is, in newick format:
+    Because a correlation must account for phylogenetic relationship and non-independence of samples, we fitted a Phylogenetic Generalized Linear Model (PGLM) in R with the package caper~\cite{orme_caper_2013}, with multi-furcation of the different populations inside each species.
+    The mammalian tree imported from TimeTree~\cite{kumar_timetree_2017} and pruned to the species used in this study (Figure~\ref{tree}) is shown in newick format:
 
@@
 
-    And shown in the figure below:
-    \begin{center}
-        \captionof{figure}{Tree used for PGLM (Phylogenetic Generalized Linear Model).}
+    \begin{center}
         \includegraphics[width=0.65\linewidth, page=1]{artworks/PGLM.pdf}
-    \end{center}
-
-    Multifurcations of the different populations are placed at the same divergence time as the species.
-    Then, for each population, the proportion of deleterious ($\ProbaPopDel$), nearly-neutral ($\ProbaPopNeu$) and of beneficial ($\ProbaPopBen$) mutations estimated at the population-genetic scale is shown as function of $\Ne$.
-    $r^2$ and p-value are obtained from the PGLM model.
-
-    \newpage
-    \subsubsection{Proportion of deleterious mutations ($\SpopDel$)}\label{subsec:proportion-deleterious-mutations}
-    \captionof{figure}{Proportion of deleterious mutations ($\SpopDel$).}
+        \captionof{figure}[Tree used for PGLM (Phylogenetic Generalized Linear Model).]{\textbf{Tree used for PGLM (Phylogenetic Generalized Linear Model).} The mammalian dated tree was obtained from TimeTree~\cite{kumar_timetree_2017} and pruned to include only the species analysed in this study, with multi-furcation of the different populations from each species placed at the same divergence time as the divergence to the sister species.}
+        \label{tree}
+    \end{center}
+
+    \newpage
+    Accounting for phylogenetic relationship and non-independence of samples, through the fit of a Phylogenetic Generalized Linear Model, we can estimate regression coefficient between two variables.
+    Thus, for each population, the proportion of deleterious ($\ProbaPopDel$,~\ref{fig:pop-neg-prop}), nearly-neutral ($\ProbaPopNeu$,~\ref{fig:pop-weak-prop}) and beneficial ($\ProbaPopBen$,~\ref{fig:pop-pos-prop}) mutations estimated at the population-genetic scale is shown as function of $\Ne$, and we estimated regression coefficients.
+
+    \subsubsection{Proportion of deleterious mutations (\texorpdfstring{$\SpopDel$}{D})}\label{subsec:proportion-deleterious-mutations}
+
+    Higher effective population size ($\Ne$) is typically accompanied by a higher proportion of effectively deleterious mutations at the population scale ($\proba{[} \SpopDel {]}$), as shown in~\ref{fig:pop-neg-prop} (left panel).
+    This trend is also confirmed when we restricted the analysis to class of mutations that are supposedly deleterious at the phylogenetic scale ($\SphyDel$), as shown in~\ref{fig:pop-neg-prop} (right panel).
+    This result is qualitatively in accordance with the nearly-neutral theory of evolution which argues that very slightly deleterious mutations are more efficiently purified in large populations.
+
+    \begin{center}
     \begin{minipage}{0.49\linewidth}
@@
     \end{minipage}
-    \begin{itemize}
-        \item $\Ne$ is the estimated effective population size.
-        \item $\proba [ \SpopDel ]$ (eq.~15) is the probability for a mutation to be deleterious.
-        These mutations have a selection coefficient at the population-scale lower than -1.
-        \item $\proba [ \SpopDel \given \SphyDel ]$ (eq.~12) is the probability for a mutation to be deleterious at the population scale, given it is predicted to be a deleterious at the phylogenetic scale.
-    \end{itemize}
-
-    We can see that higher effective population size ($\Ne$) is typically accompanied by a higher proportion of effectively deleterious mutations at the population scale ($\proba [ \SpopDel ]$).
-    This trend is also confirmed when we restricted the analysis to class of mutations that are supposedly deleterious at the phylogenetic scale ($\SphyDel$).
-    This result is qualitatively in accordance with the nearly-neutral theory of evolution which argues that very slightly deleterious mutations are more efficiently purified in large populations.
-
-    \newpage
-    \subsubsection{Proportion of nearly-neutral mutations ($\SpopNeu$)}\label{subsec:proportion-nearly-neutral-mutations}
-    \captionof{figure}{Proportion of nearly-neutral mutations ($\SpopNeu$).}
+    \captionof{figure}[Relationship between the proportion of deleterious mutations ($\SpopDel$) and effective population size.]{\textbf{Relationship between the proportion of deleterious mutations ($\bm{\SpopDel}$) and effective population size.}
+    Left) Proportion of deleterious mutations at the population scale ($\proba{[} \SpopNeu{]}$), shown as a function of estimated effective population size ($\Ne$).
+Right) Probability for a mutation to be deleterious at the population scale, given it is predicted to be deleterious at the phylogenetic scale, as a function of estimated effective population size ($\Ne$).
+Populations are represented by circles, and squares are the mean for the species.
+Correlations account for phylogenetic relationship and non-independence of samples, through the fit of a Phylogenetic Generalized Linear Model (see Materials \& Methods).\label{fig:pop-neg-prop}}
+    \end{center}
+
+    \subsubsection{Proportion of nearly-neutral mutations (\texorpdfstring{$\SpopNeu$}{N})}\label{subsec:proportion-nearly-neutral-mutations}
+    Higher effective population size ($\Ne$) is typically accompanied by a smaller proportion of neutral mutations at the population scale ($\proba{[} \SpopNeu {]}$ in the range 0.06-0.18), as shown in~\ref{fig:pop-weak-prop} (left panel).
+    This result is more pronounced ($\proba{[} \SpopNeu \given \SphyNeu {]}$ in the range 0.36-0.73) when we restricted the analysis to the class of mutations that are supposedly nearly-neutral at the phylogenetic scale ($\SphyNeu$), as shown in~\ref{fig:pop-pos-prop} (right panel).
+    This result suggests that in populations with higher diversity (e.g.,~\textit{Bos} or \textit{Ovis}), mutations are more likely to be detected as under selection (positive or negative).
+    Alternatively stated, mutations in populations with low diversity (e.g.,~\textit{Homo}) are effectively nearly-neutral and behave as neutral mutations would.
+    This result is qualitatively in accordance with the nearly-neutral theory of evolution which argues that mutations are less efficiently selected for in small populations.
+
+    \newpage
+    \begin{center}
         \begin{minipage}{0.49\linewidth}
@@
         \end{minipage}
-    \begin{itemize}
-        \item $\Ne$ is the estimated effective population size.
-        \item $\proba [ \SpopNeu ]$ (eq.~15) is the probability for a mutation to be nearly-neutral.
-        These mutations have a selection coefficient at the population-scale between -1 and 1.
-        \item $\proba [ \SpopNeu \given \SphyNeu ]$ (eq.~12) is the probability for a mutation to be nearly-neutral at the population scale, given it is predicted to be a nearly-neutral at the phylogenetic scale.
-    \end{itemize}
-
-    We confirmed that higher effective population size ($\Ne$) is typically accompanied by a smaller proportion of neutral mutations at the population scale ($\proba [ \SpopNeu ]$ in the range 0.06-0.18).
-    This result is more pronounced ($\proba [ \SpopNeu \given \SphyNeu ]$ in the range 0.36-0.73) when we restricted the analysis to class of mutations that are supposedly nearly-neutral at the phylogenetic scale ($\SphyNeu$).
-    This result suggests that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) are more likely to discriminate whether mutations are beneficial or deleterious.
-    Alternatively stated, mutations in populations with low diversity (e.g.~\textit{Homo}) are effectively nearly-neutral and behave as a neutral mutation would.
-    This result is qualitatively in accordance with the nearly-neutral theory of evolution which argues that mutations are less efficiently selected for in small populations.
-
-    \newpage
-    \subsubsection{Proportion of beneficial mutations ($\SpopBen$)}\label{subsec:proportion-beneficial-mutations}
-    \captionof{figure}{Proportion of beneficial mutations ($\SpopBen$).}
+        \captionof{figure}[Relationship between the proportion of nearly-neutral mutations ($\SpopNeu$) and effective population size.]{\textbf{Relationship between the proportion of nearly-neutral mutations ($\bm{\SpopNeu}$) and effective population size..}
+        Left) Proportion of deleterious mutations at the population scale ($\proba{[} \SpopNeu{]}$), shown as a function of estimated effective population size ($\Ne$).
+Right) Probability for a mutation to be nearly-neutral at the population scale, given it is predicted to be nearly-neutral at the phylogenetic scale, as a function of estimated effective population size ($\Ne$).
+Populations are represented by circles, and squares are the mean for the species.
+Correlations account for phylogenetic relationship and non-independence of samples, through the fit of a Phylogenetic Generalized Linear Model (see Materials \& Methods).\label{fig:pop-weak-prop}}
+    \end{center}
+
+    \subsubsection{Proportion of beneficial mutations (\texorpdfstring{$\SpopBen$}{B})}\label{subsec:proportion-beneficial-mutations}
+    A higher effective population size ($\Ne$) is accompanied by a smaller proportion of beneficial mutations at the population scale ($\proba{[} \SpopBen {]}$), as shown in~\ref{fig:pop-pos-prop} (left panel).
+    This trend is also confirmed when we restricted the analysis to the class of mutations that are supposedly non-adaptive beneficial at the phylogenetic scale ($\SphyBen$), as shown in~\ref{fig:pop-pos-prop} (right panel).
+
+    \begin{center}
         \begin{minipage}{0.49\linewidth}
@@
         \end{minipage}
-    \begin{itemize}
-        \item $\Ne$ is the estimated effective population size.
-        \item $\proba [ \SpopBen ]$ (eq.~15) is the probability for a mutation to be beneficial.
-        These mutations have a selection coefficient at the population-scale larger than 1.
-        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a non-adaptive beneficial mutation at the phylogenetic scale (the \textit{precision}).
-    \end{itemize}
-    Higher effective population size ($\Ne$) is accompanied by a smaller proportion of beneficial mutations at the population scale ($\proba [ \SpopBen ]$).
-    This trend is also confirmed when we restricted the analysis to class of mutations that are supposedly non-adaptive beneficial mutations at the phylogenetic scale ($\SphyBen$).
-
-    \newpage
-
-    \section{Probability for beneficial mutations to be non-adaptive ($\proba[\SphyBen\given \SpopBen ]$)}
-
-    \subsection{Across the different populations}
-    \begin{center}
-        \captionof{table}{Probability for beneficial mutations to be non-adaptive ($\proba[\SphyBen\given \SpopBen ]$).}
+        \captionof{figure}[Relationship between the proportion of beneficial mutations ($\SpopBen$) and effective population size.]{\textbf{Relationship between the proportion of beneficial mutations ($\bm{\SpopBen}$) and effective population size.}
+        Left) Proportion of beneficial mutations at the population scale ($\proba{[} \SpopNeu{]}$), shown as a function of estimated effective population size ($\Ne$).
+Right) Probability for a mutation to be beneficial at the population scale, given it is predicted to be beneficial at the phylogenetic scale, as a function of estimated effective population size ($\Ne$).
+Populations are represented by circles, and squares are the mean for the species.
+Correlations account for phylogenetic relationship and non-independence of samples, through the fit of a Phylogenetic Generalized Linear Model (see Materials \& Methods).\label{fig:pop-pos-prop}}
+    \end{center}
+
+    \newpage
+
+    \section{Probability for beneficial mutations to be non-adaptive (\texorpdfstring{$\proba{[}\SphyBen\given \SpopBen {]}$}{P[B₀|B]})}
+
+    \subsection{Across different populations}
+    Probability for beneficial mutations to be non-adaptive, namely $\proba{[}\SphyBen\given \SpopBen {]}$, is obtained from Bayes' formula (eq.~14) merging three terms: the probability for a new mutation to be a non-adaptive beneficial mutation ($\proba{[} \SphyBen {]}$, eq.~5), the probability for a mutation to be beneficial ($\proba{[} \SpopBen {]}$, eq.~15) and the probability for a mutation to be beneficial at the population scale given that it is predicted to be a non-adaptive beneficial mutation at the phylogenetic scale ($\proba{[} \SpopBen \given \SphyBen{]}$, eq.~12).
+    These four estimates across populations are shown in Table~\ref{table:proba}.
+
+    \begin{center}
         \scriptsize
@@
             \toprule
-            Population & Species & $N_e$ & $\proba[\SphyBen]$ & $\proba [ \SpopBen ]$ & $\frac{\proba[\SphyBen]}{\proba[ \SpopBen ]}$ & $\proba [ \SpopBen \given \SphyBen]$ & $\proba[\SphyBen\given \SpopBen ]$ \\
+            Population & Species & $N_e$ & $\proba{[}\SphyBen{]}$ & $\proba{[} \SpopBen {]}$ & $\frac{\proba{[}\SphyBen]}{\proba{[} \SpopBen ]}$ & $\proba{[} \SpopBen \given \SphyBen{]}$ & $\proba{[}\SphyBen\given \SpopBen {]}$ \\
             \midrule
@@
         \end{longtable*}
-    \end{center}
-    \begin{itemize}
-        \item $\Ne$ is the estimated effective population size.
-        \item $\proba [ \SphyBen ]$ (eq.~5) is the probability for a new mutation to be a non-adaptive beneficial mutation.
+        \captionof{table}[Probability for beneficial mutations to be non-adaptive ($\proba{[}\SphyBen\given \SpopBen {]}$)]{
+        \textbf{Probability for beneficial mutations to be non-adaptive ($\bm{\proba{[}\SphyBen\given \SpopBen {]}}$).}
+        $\Ne$ is the estimated effective population size.
+        $\proba{[} \SphyBen {]}$ (eq.~5) is the probability for a new mutation to be a non-adaptive beneficial mutation.
         These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1, thus toward a more fit amino-acid.
-        \item $\proba [ \SpopBen ]$ (eq.~15) is the probability for a mutation to be beneficial.
+        $\proba{[} \SpopBen {]}$ (eq.~15) is the probability for a mutation to be beneficial.
         These mutations have a selection coefficient at the population-scale larger than 1.
-        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given that it is predicted to be a non-adaptive beneficial mutation at the phylogenetic scale (the \textit{precision}).
-        \item $\proba [ \SphyBen \given \SpopBen]$ (eq.~14) is the probability for a mutation to be non-adaptive given that it is beneficial at the population scale (the \textit{recall}).
+        $\proba{[} \SpopBen \given \SphyBen{]}$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given that it is predicted to be a non-adaptive beneficial mutation at the phylogenetic scale (the \textit{precision}).
+        $\proba{[} \SphyBen \given \SpopBen{]}$ (eq.~14) is the probability for a mutation to be non-adaptive given that it is beneficial at the population scale (the \textit{recall}).
         This probability is obtained using Bayes' formula.
-    \end{itemize}
+        \label{table:proba}
+        }
+    \end{center}
 
@@
 
-    A potential caveat of our method to is that if a deleterious derived allele segregates at low frequency but is wrongly annotated as ancestral, it will result in a SNP that will be both predicted as advantageous and segregating at high frequency, wrongly suggesting that this variant is correctly inferred as beneficial.
-    In this context misannotations of ancestral alleles could inflate our estimation of the proportion of beneficial non-adaptive mutations.
+    A potential caveat of our method is that if a deleterious derived allele segregates at low frequency but is wrongly annotated as ancestral, it will result in a SNP that will be both predicted as advantageous and segregating at high frequency, wrongly suggesting that this variant is correctly inferred as beneficial.
+    In this context, misannotations of ancestral alleles could inflate our estimation of the proportion of beneficial non-adaptive mutations.
     However, we show that this problem impacts our estimation in two ways, albeit, only slightly. \\
 
-    First, if misannotation is influencing the recall for $\SphyBen$ ($\proba[\SphyBen\given \SpopBen ]$), then the recall should increase as a function of  divergence to the sister species ($\ds$: number of synonymous substitutions per sites) since divergence would increase the rate of misannotations.
-    Shown below is recall $\proba[\SphyBen\given \SpopBen ]$ as a function of divergence ($\ds$) in which the latter is not an explanatory variable.
-
-    \begin{center}
-        \captionof{figure}{$\proba[\SphyBen\given \SpopBen ]$ as a function of distance to the sister species.}
+    First, if misannotation is influencing the recall for $\SphyBen$ ($\proba{[}\SphyBen\given \SpopBen {]}$), then the recall should increase as a function of  divergence to the sister species ($\ds$: number of synonymous substitutions per site) since divergence would increase the rate of misannotations.
+    Shown in Figure~\ref{fig:distance-sister} is recall $\proba{[}\SphyBen\given \SpopBen {]}$ as a function of divergence ($\ds$) in which the latter is not an explanatory variable.
+
+    \begin{center}
         \includegraphics[width=0.75\linewidth, page=1]{artworks/results.distance.recall_pos.scatter.pdf}
+        \captionof{figure}[$\proba{[}\SphyBen\given \SpopBen {]}$ as a function of distance to the sister species.]{\textbf{Proportion of non-adaptive mutations among beneficial ones ($\bm{\proba{[}\SphyBen\given \SpopBen {]}}$) as a function of distance to the sister species.}
+        $\proba{[} \SphyBen \given \SpopBen{]}$ (eq.~14) is the probability for a beneficial mutation to be non-adaptive.
+        $\ds$ is number of synonymous substitutions per site that occurred since divergence with the sister species (closest species in the mammalian tree).
+        Populations are represented by circles, and squares are the mean for the species.
+        Correlations account for phylogenetic relationship and non-independence of samples, through the fit of a Phylogenetic Generalized Linear Model (see Materials \& Methods).\label{fig:distance-sister}}
     \end{center}
@@
     Second, the distribution of selection coefficients ($\Sphy$) that we observed for segregating mutations and for divergence also suggests that we effectively controlled for misannotations.
-    Under a scenario where beneficial non-adaptive mutations would only be the result of misannotations, one would expect that the positive part of the fitness effects (i.e.
-$\proba[\Sphy]$) of observed polymorphism currently segregating in the population should reflect the negative one (i.e.
-$\proba[-\Sphy]$).
+    Under a scenario where beneficial non-adaptive mutations would only be the result of misannotations, one would expect that the positive part of the fitness effects ($\proba{[}\Sphy{]}$) of observed polymorphisms currently segregating in the population should reflect the negative one ($\proba{[}-\Sphy{]}$).
     Indeed, the number of misannotated beneficial mutations should be proportional to the number of deleterious mutations with the same selection coefficient.
     The ratio between advantageous and deleterious polymorphisms of the same selection coefficient should therefore be a constant that represents the rate of misannotation (typically influenced by the distance to the sister species).
-    However, this is not what we observe in the DFE of polymorphisms (shown below in the African population of \textit{Homo sapiens}) thus giving us the confidence that misannotations are not common.
-
-    \begin{center}
-        \captionof{figure}{Ratio of $\proba[\Sphy]$ over $\proba[-\Sphy]$ for polymorphisms of the African population of \textit{Homo sapiens}.}
+    However, this is not what we observe in the DFE of polymorphisms (shown in Figure~\ref{mispol-expectation} for the African population of \textit{Homo sapiens}) thus giving us the confidence that misannotations are not common.
+    Overall, the observed DFE of substitutions is much better explained by the expected DFE of new mutations (section S\ref{subsec:expectedDFE} than by misannotations).
+
+    \begin{center}
         \includegraphics[width=0.75\linewidth, page=1]{artworks/poly.Homo_sapiens.AFR.folded_ratio.pdf}
-    \end{center}
-
-    Overall, the observed DFE of substitution is much better explained by the expected DFE of new mutations (section S\ref{subsec:expectedDFE} than by mispolarizations).
-
-    \newpage
-    \section{Excluding genes under adaptation}
-
-    \subsection{Probability for beneficial mutations to be non-adaptive}
-    \begin{center}
-        \captionof{table}{$\proba[\SphyBen\given \SpopBen ]$ excluding or not genes under adaptation.}
-        \begin{tabular}{|l|l|r|r|}
-            \toprule
-            Population & Species & Control & Case \\
-            \midrule
-            \rowcolor{LIGHTGREY} Equus c. & Equus caballus & $ 0.536$ & $ 0.880$ \\
-            Iran & Bos taurus & $ 0.243$ & $ 0.249$ \\
-            Uganda & Bos taurus & $ 0.415$ & $ 0.429$ \\
-            \rowcolor{LIGHTGREY} Australia & Capra hircus & $ 0.177$ & $ 0.190$ \\
-            \rowcolor{LIGHTGREY} France & Capra hircus & $ 0.190$ & $ 0.201$ \\
-            \rowcolor{LIGHTGREY} Iran (C. aegagrus) & Capra hircus & $ 0.165$ & $ 0.169$ \\
-            \rowcolor{LIGHTGREY} Iran & Capra hircus & $ 0.193$ & $ 0.176$ \\
-            \rowcolor{LIGHTGREY} Italy & Capra hircus & $ 0.243$ & $ 0.261$ \\
-            \rowcolor{LIGHTGREY} Morocco & Capra hircus & $ 0.245$ & $ 0.283$ \\
-            \rowcolor{LIGHTGREY} Iran & Ovis aries & $ 0.407$ & $ 0.454$ \\
-            Iran (O. orientalis) & Ovis aries & $ 0.190$ & $ 0.207$ \\
-            Iran (O. vignei) & Ovis aries & $ 0.110$ & $ 0.135$ \\
-            Various & Ovis aries & $ 0.222$ & $ 0.246$ \\
-            Morocco & Ovis aries & $ 0.514$ & $ 0.627$ \\
-            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus & $ 0.293$ & $ 0.325$ \\
-            \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus & $ 0.275$ & $ 0.273$ \\
-            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus & $ 0.245$ & $ 0.242$ \\
-            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus & $ 0.821$ & $ 0.873$ \\
-            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus & $ 0.257$ & $ 0.254$ \\
-            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus & $ 0.358$ & $ 0.395$ \\
-            \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus & $ 0.341$ & $ 0.375$ \\
-            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus & $ 0.336$ & $ 0.355$ \\
-            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus & $ 0.250$ & $ 0.263$ \\
-            African & Homo sapiens & $ 0.349$ & $ 0.363$ \\
-            Admixed American & Homo sapiens & $ 0.345$ & $ 0.312$ \\
-            East Asian & Homo sapiens & $ 0.249$ & $ 0.233$ \\
-            European & Homo sapiens & $ 0.248$ & $ 0.211$ \\
-            South Asian & Homo sapiens & $ 0.224$ & $ 0.218$ \\
-            \bottomrule
-        \end{tabular}
-    \end{center}
-    Genes under adaptation retrieved from \textcite{latrille_genes_2023}.
-    Comparison of $\proba[\SphyBen\given \SpopBen ]$ for the whole genome (control) and when excluding genes under adaptation (case).
-    The non-parametric Wilcoxon signed-rank test evaluates the null hypothesis that the distribution of the differences (case versus control) is symmetric about zero.
-    Applied to the paired samples (case and control), Wilcoxon signed-rank test results in $s=80$ with $\pvalue=0.002$, for the one-sided test (case higher than control).
-    The proportion of non-adaptive beneficial mutations ($\proba[\SphyBen\given \SpopBen ]$) is higher when excluding genes under adaptation, consistent with our expectation that genes with uniformly conserved functions should fit better the nearly-neutral equilibrium model.
-
-    \newpage
-
-    \section{Contrasting selection at the phylogenetic and population-genetic scale}
-
-    \subsection{Selection at the population-genetic scale}
-    The proportion of deleterious ($\ProbaPopDel$), nearly-neutral ($\ProbaPopNeu$) and of beneficial ($\ProbaPopBen$) mutations estimated at the population-genetic scale across the different populations is shown for each class of selection ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$).
-
-    \captionof{figure}{Estimation of selection at the population scale for $\SphyDel$ mutations.}
-    \begin{center}
-        \begin{minipage}{0.75\linewidth}
-            \begin{minipage}{0.9\linewidth}
-                \includegraphics[width=\linewidth, page=1]{artworks/Theta.neg.stacked.pdf}
-            \end{minipage}
-            \begin{minipage}{0.09\linewidth}
-                \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
-            \end{minipage}
-        \end{minipage}
-    \end{center}
-
-    \captionof{figure}{Estimation of selection at the population scale for $\SphyNeu$ mutations.}
-    \begin{center}
-        \begin{minipage}{0.75\linewidth}
-            \begin{minipage}{0.9\linewidth}
-                \includegraphics[width=\linewidth, page=1]{artworks/Theta.weak.stacked.pdf}
-            \end{minipage}
-            \begin{minipage}{0.09\linewidth}
-                \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
-            \end{minipage}
-        \end{minipage}
-    \end{center}
-
-    \captionof{figure}{Estimation of selection at the population scale for $\SphyBen$ mutations.}
-    \begin{center}
-        \begin{minipage}{0.75\linewidth}
-            \begin{minipage}{0.9\linewidth}
-                \includegraphics[width=\linewidth, page=1]{artworks/Theta.pos.stacked.pdf}
-            \end{minipage}
-            \begin{minipage}{0.09\linewidth}
-                \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
-            \end{minipage}
-        \end{minipage}
-    \end{center}
-
-    \newpage
-    \subsection{Distribution of scaled selection coefficients ($\Sphy$)}\label{subsec:expectedDFE}
-
-    Theoretically, the selection coefficient ($\Sphy$) for any mutation is related to its probability of fixation by the equation $\proba_{\text{fix}} (\Sphy) = \Sphy/(1-\exp(-\Sphy)) $.
-    It is thus possible to predict the distribution of $\Sphy$ of substitutions given the distribution of $\Sphy$ for mutations (e.g.
-panel A below) by weighting the different mutations by their $\proba_{\text{fix}} (\Sphy)$.
-    The predicted DFE of substitutions (panel B below) matches the observed DFE of substitutions (panel C below) in the terminal lineage, meaning that the $\Sphy$ obtained by phylogenetic mutation-selection codon models is a strong predictor of selection effectively exerted on mutations in terminal lineages.
-
-    The figures shown below are obtained in the Saint Kitts population of \textit{Chlorocebus sabaeus}.
-    These figures across the 28 populations are available at Zenodo (\url{https://doi.org/10.5281/zenodo.7878953}) in file \textit{distribution\_S0\_28\_populations.pdf}.\\
-
-    \captionof{figure}{Distribution of scaled selection coefficients ($\Sphy$).}
-    \begin{minipage}{0.32\linewidth}
-        \flushleft {\tiny A: Expected DFE for mutations}
-        \includegraphics[width=\linewidth, page=1]{artworks/DFE.Chlorocebus_sabaeus.Saint_Kitts.MutSel.pdf}
-    \end{minipage}
-    \begin{minipage}{0.32\linewidth}
-        \flushleft {\tiny B: Expected DFE for substitutions}
-        \includegraphics[width=\linewidth, page=1]{artworks/DFE.Chlorocebus_sabaeus.Saint_Kitts.MutSel.Flow.pdf}
-    \end{minipage}
-    \begin{minipage}{0.32\linewidth}
-        \flushleft {\tiny C: Observed DFE for substitutions}
-        \includegraphics[width=\linewidth, page=1]{artworks/subs.Chlorocebus_sabaeus.Saint_Kitts.bins3Mask0.9.pdf}
-    \end{minipage}
-    \\
-    \begin{minipage}{0.32\linewidth}
-        \flushleft {\tiny D: Observed DFE for polymorphisms}
-        \includegraphics[width=\linewidth, page=1]{artworks/poly.Chlorocebus_sabaeus.Saint_Kitts.bins3Mask0.9.pdf}
-    \end{minipage}
-    \begin{minipage}{0.32\linewidth}
-        \flushleft {\tiny E: Site frequency spectrum}
-        \includegraphics[width=\linewidth, page=1]{artworks/Chlorocebus_sabaeus.Saint_Kitts.MutSel-sfs.normalize.pdf}
-    \end{minipage}
-    \begin{minipage}{0.32\linewidth}
-        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
-        \includegraphics[width=\linewidth, page=1]{artworks/Chlorocebus_sabaeus.Saint_Kitts.MutSel.polyDFE_C.pdf}
-    \end{minipage}
-
-    \small
-    \begin{itemize}[itemsep=0pt]
-        \item A: Distribution of scaled selection coefficients ($\Sphy$), predicted for all possible non-synonymous DNA mutations away from the ancestral exome.
-        Mutations are divided into three classes of selection: deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial non-adaptive ($\SphyBen$).
-        \item B: Expected distribution of $\Sphy$ for substitutions obtained by transforming the distribution of $\Sphy$ for mutations (panel A) by weighting each mutation by its scaled probability of fixation given by $\proba_{\text{fix}} (\Sphy) = \Sphy/(1-\exp(-\Sphy))$.
-        \item C: Distribution of scaled selection coefficients ($\Sphy$) for all observed substitutions along the terminal branch of the phylogenetic tree.
-        \item D: Distribution of scaled selection coefficients ($\Sphy$) for all observed polymorphisms currently segregating in the population.
-        \item E: The site-frequency spectrum (SFS) in the population for a random sample of 16 alleles (means in solid lines and standard deviations in color shades) for each class of selection and for synonymous mutations, supposedly neutral (black).
-The SFS represents the proportion of mutations (y-axis) with a given number of derived alleles in the population (x-axis).
-At high frequencies, deleterious mutations are underrepresented.
-        \item F: Proportion of beneficial $\ProbaPopDel$, nearly-neutral $\ProbaPopNeu$, and deleterious mutations $\ProbaPopBen$  estimated at the population scale for each class of selection at the phylogenetic scale.
-Proportions depicted here are not weighted by their mutational opportunities.
+        \captionof{figure}[Ratio of $\proba{[}\Sphy{]}$ over $\proba{[}-\Sphy{]}$ for polymorphisms of the African population of \textit{Homo sapiens}.]{\textbf{Ratio of $\bm{\proba{[}\Sphy{]}}$ over $\bm{\proba{[}-\Sphy{]}}$ for polymorphisms of the African population of \textit{Homo sapiens}.}
+        From the histogram of distribution of scaled selection coefficients ($\Sphy$) for all observed polymorphism, we obtain 30 bins for positive selection coefficient ($\Sphy$) and 30 bins for negative selection coefficient ($\Sphy$).
+For a given bin of $\Sphy$, $\proba{[}\Sphy{]}$ the number of observed polymorphisms in the positive part, while $\proba{[}-\Sphy{]}$ the number of observed polymorphisms in the negative part.
+$\bm{\proba{[}\Sphy{]} / \proba{[}-\Sphy{]}}$ is the ratio of the positive part over the negative part.
+Alternatively stated, it is folding Figure~\ref{dfe-sfs}D around 0, by taking the right part (positive $\Sphy$) of the histogram over the left part (negative $\Sphy$).
+        }
+        \label{mispol-expectation}
+    \end{center}
+
+    \newpage
+    \subsection{Simulations of site-frequency spectra}
+
+    We performed population-genetic simulations to test whether our approach is able to recover the proportion of beneficial mutations that are non-adaptive in synthetic polymorphism datasets.
+    More specifically, we performed simulations of site-frequency spectra, thus at the population-genetic scale, by using a mixture of the DFEs that is predicted from the phylogenetic mutation-selection model, and adding adaptive mutations to this DFE.
+    In practice, simulations are performed under the Poisson Random Field (PRF) framework of population genetics\cite{sawyer_population_1992}.
+    Each simulation generates a synthetic synonymous SFS, and a synthetic non-synonymous SFS for the mutations in the category $x \in \{ \SphyDel, \SphyNeu, \SphyBen \}$.
+
+    Technically, for non-synonymous mutations, we first draw a random sample of the selection coefficients from the mixture of DFEs using $\proba{[}y \given x{]}$ for $y \in \{ \SpopDel, \SpopNeu, \SpopBen \}$ as parameters.
+    Importantly, $\proba{[}\SpopBen \given \SphyDel{]}$ and $\proba{[}\SpopBen \given \SphyNeu{]}$ are considered adaptive mutations, and thus their selection coefficients have a selection coefficient of $S_{\text{adaptive}}=10$.
+    All the others are drawn for the DFEs that are predicted from the phylogenetic mutation-selection model.
+    Synonymous mutations are considered neutral and have $S=0$.
+
+    Given these selection coefficients, to obtain the expected SFS we integrate over the limiting density of frequency that mutations are segregating in the population, as described from eqs.
+1--2 in \textcite{tataru_inference_2017}.
+    And finally, given this expected SFS, we perform a Poisson random sampling to obtain a sampled SFS of size n matching the total number of polymorphism to simulate.
+
+    In summary, the simulations generates a synonymous SFS, and a non-synonymous SFS for the mutations in the category $x \in \{ \SphyDel, \SphyNeu, \SphyBen \}$, and require as input the following:
+    \begin{itemize}
+        \item Total number of polymorphisms to simulate (synonymous and non-synonymous).
+        \item The DFE of $\Sphy$ predicted from the phylogenetic mutation-selection.
+        \item Estimates of $\proba{[}y \given x{]}$ for $y \in \{ \SpopDel, \SpopNeu, \SpopBen \}$.
+        \item Selection coefficient for adaptive mutations, here $S_{\text{adaptive}}=20$.
+        \item The sampled SFS size $n$, here $n=16$ (i.e.\ twice the number of sampled individuals).
     \end{itemize}
-    \normalsize
+
+    From these two SFS (synonymous and non-synonymous), we run polyDFE to obtain $\proba{[}\SpopDel \given x{]}$, $\proba{[}\SpopNeu \given x{]}$ and $\proba{[}\SpopBen \given x{]}$ (eqs.\ 9--11).
+    By doing so for the 3 categories $x \in \{ \SphyDel, \SphyNeu, \SphyBen \}$, we can ultimately compute $\proba{[}\SphyBen \given \SpopBen{]}$ (eqs.\ 14--15), which can be then be compared to the ground truth.
+
+    We used 8 different sets of parameters ($\proba{[}y \given x{]}$ and number of polymorphisms) and simulated 10 replicates for each set of parameters, shown in Figure~\ref{fig:simulations}.
+    These set of input parameters are provided to match $\proba{[}\SphyBen \given \SpopBen{]}$ of the following populations: Set 1 for Admixed American (\textit{Homo sapiens}), Set 2 for African (\textit{Homo sapiens}), Set 3 for Nevis (\textit{Chlorocebus sabaeus}), Set 4 for Iran (\textit{Ovis orientalis}), Set 5 for Uganda (\textit{Bos taurus}), Set 6 for Morocco (\textit{Ovis aries}), Set 7 for \textit{Equus caballus}, Set 8 for Gambia (\textit{Chlorocebus sabaeus}).
+    For each synthetic data we ran polyDFE and derived $\proba{[}\SphyBen \given \SpopBen{]}$ which was then compared to the ground truth (calculated analytically from the set parameters $\proba{[}y \given x], x \in \{ \SphyDel, \SphyNeu, \SphyBen \}, y \in \{ \SpopDel, \SpopNeu, \SpopBen \}$).
+    These simulations show that we are able to accurately retrieve the proportion of non-adaptive mutations in those synthetic datasets.
+
+    \begin{center}
+        \includegraphics[width=\linewidth, page=1]{artworks/simulations.pos.pdf}
+        \captionof{figure}[Proportion of non-adaptive mutations among beneficial ones ($\proba{[}\SphyBen\given \SpopBen {]}$) estimated on synthetic site-frequency spectra.]{\textbf{Proportion of non-adaptive mutations among beneficial ones ($\bm{\proba{[}\SphyBen\given \SpopBen {]}}$) estimated on synthetic site-frequency spectra.} Each set has ben simulated using a different value for $\proba{[}\SphyBen\given \SpopBen {]}$.
+Bars correspond to the $\proba{[}\SphyBen\given \SpopBen {]}$ used to simulate the site-frequency spectra, each blue circle corresponds to $\proba{[}\SphyBen\given \SpopBen {]}$ estimated by one polyDFE simulation, and red crosses correspond to the mean of estimations across 10 replicates.\label{fig:simulations}}
+    \end{center}
 
@@
     \subsection{Masking CpG transitions}
-    We also tested our prediction while masking CpG transitions since the mutation rate of CpG dinucleotides is higher than the mutation rate of other dinucleotides, which can affect the estimation of the DFE.
+    We also tested our prediction when masking CpG transitions since the mutation rate of CpG dinucleotides is higher than the mutation rate of other dinucleotides, which can affect the estimation of the DFE.
     Any nucleotide transition including a CpG dinucleotide either in the ancestral or derived state is considered as a CpG transition.
@@
 
+    \newpage
     \subsection{Probability for beneficial mutations to be non-adaptive}
-    \begin{center}
-        \captionof{table}{$\proba[\SphyBen\given \SpopBen ]$ while masking CpG transitions.}
+    When filtering out CpG sites, the estimation of $\proba{[} \SpopBen {]}$ and $\proba{[}\SphyBen\given \SpopBen {]}$ across populations is shown in Table~\ref{table:no-CpG-bayes}.
+    Comparing these results with Table~\ref{table:proba}, we acknowledge that the exact proportion of non-adaptive among beneficial mutations is dependent on the whether we masked CpG sites.
+    However, we can still see that non-adaptive beneficial mutations are positively selected compared to neutral and deleterious ones, and this result is not dependent on whether we masked CpG sites or not.
+
+    \begin{center}
         \scriptsize
@@
             \toprule
-            Population & Species & $\Ne$ & $\proba[\SphyBen]$ & $\proba [ \SpopBen ]$ & $\frac{\proba[\SphyBen]}{\proba[ \SpopBen ]}$ & $\proba [ \SpopBen \given \SphyBen]$ & $\proba[\SphyBen\given \SpopBen ]$ \\
+            Population & Species & $\Ne$ & $\proba{[}\SphyBen{]}$ & $\proba{[} \SpopBen {]}$ & $\frac{\proba{[}\SphyBen]}{\proba{[} \SpopBen ]}$ & $\proba{[} \SpopBen \given \SphyBen{]}$ & $\proba{[}\SphyBen\given \SpopBen {]}$ \\
             \midrule
@@
         \end{longtable*}
-    \end{center}
-    \begin{itemize}
-        \item $\Ne$ is the estimated effective population size.
-        \item $\proba [ \SphyBen ]$ (eq.~5) is the probability for a new mutation a non-adaptive beneficial mutation.
+        \captionof{table}[$\proba{[}\SphyBen\given \SpopBen {]}$ when masking CpG transitions.]{\textbf{$\bm{\proba{[}\SphyBen\given \SpopBen {]}}$ when masking CpG transitions.}
+        $\Ne$ is the estimated effective population size.
+        $\proba{[} \SphyBen {]}$ (eq.~5) is the probability for a new mutation to be a non-adaptive beneficial mutation.
         These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1, thus toward a more fit amino-acid.
-        \item $\proba [ \SpopBen ]$ (eq.~15) is the probability for a mutation to be beneficial.
+        $\proba{[} \SpopBen {]}$ (eq.~15) is the probability for a mutation to be beneficial.
         These mutations have a selection coefficient at the population-scale larger than 1.
-        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a non-adaptive beneficial mutation at the phylogenetic scale (the \textit{precision}).
-        \item $\proba [ \SphyBen \given \SpopBen]$ (eq.~14) is the probability for a mutation to be non-adaptive given it is beneficial at the population scale (the \textit{recall}).
-        This probability is obtained using Bayes' formula.
-    \end{itemize}
+        $\proba{[} \SpopBen \given \SphyBen{]}$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a non-adaptive beneficial mutation at the phylogenetic scale (the \textit{precision}).
+        $\proba{[} \SphyBen \given \SpopBen{]}$ (eq.~14) is the probability for a mutation to be non-adaptive given it is beneficial at the population scale (the \textit{recall}).
+        This probability is obtained using Bayes' formula.\label{table:no-CpG-bayes}}
+    \end{center}
+
     \newpage
@@
     \subsection{Precision and recall}
-    \captionof{table}{Precision and recall while masking CpG transitions.}
+    The estimation of precision and recall across populations while filtering out CpG sites for the estimation of $\Spop$ is shown in Table~\ref{table:no-CpG}.
+    Comparing these results with tables 1, we acknowledge that the exact quantification of \textit{precision} and \textit{recall} is dependent on the whether we masked CpG sites.
+    However, we can still see that non-adaptive beneficial mutations are positively selected compared to neutral and deleterious ones, and this result is not dependent on whether we masked CpG sites or not.
     \begin{center}
@@
                 $\bm{\Ne}$ &
-                \makecell{\textbf{Precision} \\ $\bm{\proba [\SpopDel \given \SphyDel]}$} &
-                \makecell{\textbf{Recall} \\ $\bm{\proba [\SphyDel \given \SpopDel]}$}           &
-                \makecell{\textbf{Precision}      \\ $\bm{\proba [\SpopNeu \given \SphyNeu]}$}                                    &
-                \makecell{\textbf{Recall}          \\ $\bm{\proba [\SphyNeu \given \SpopNeu]}$}                                  &
-                \makecell{\textbf{Precision}          \\ $\bm{\proba [\SpopBen \given \SphyBen]}$}          &
-                \makecell{\textbf{Recall}        \\ $\bm{\proba [\SphyBen \given \SpopBen]}$}
+                \makecell{\textbf{Precision} \\ $\bm{\proba{[}\SpopDel \given \SphyDel]}$} &
+                \makecell{\textbf{Recall} \\ $\bm{\proba{[}\SphyDel \given \SpopDel]}$}           &
+                \makecell{\textbf{Precision}      \\ $\bm{\proba{[}\SpopNeu \given \SphyNeu]}$}                                    &
+                \makecell{\textbf{Recall}          \\ $\bm{\proba{[}\SphyNeu \given \SpopNeu]}$}                                  &
+                \makecell{\textbf{Precision}          \\ $\bm{\proba{[}\SpopBen \given \SphyBen]}$}          &
+                \makecell{\textbf{Recall}        \\ $\bm{\proba{[}\SphyBen \given \SpopBen]}$}
                 \\   \midrule
@@
         \end{adjustbox}
-    \end{center}
-    \begin{itemize}
-        \item $\Ne$ is the estimated effective population size.
-        \item \textit{Precision} is the estimation of the selection coefficient at population scale ($\Spop$) given that $\Sphy$ is known.
-        \item \textit{Recall} is the estimation of $\Sphy$ given selection coefficient at the population scale ($\Spop$) is known.
-        \item \textit{Recall} for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is the probability for a mutation to be non-adaptive given it is beneficial at the population scale.
-    \end{itemize}
-
-    Altogether, comparing this table other estimations, we acknowledge that the exact proportion of non-adaptive among beneficial mutations is dependent on the whether we masked CpG sites.
-    However, we can still see that non-adaptive beneficial mutations are positively selected compared to neutral and deleterious ones, and this result is not dependent on whether we masked CpG sites or not.
+        \captionof{table}[Precision and recall when masking CpG transitions.]{
+        \textbf{Precision and recall when masking CpG transitions.}
+        $\Ne$ is the estimated effective population size.
+        \textit{Precision} is the estimation of the selection coefficient at population scale ($\Spop$) given that $\Sphy$ is known.
+        \textit{Recall} is the estimation of $\Sphy$ given selection coefficient at the population scale ($\Spop$) is known.
+        \textit{Recall} for beneficial mutations ($\proba{[}\SphyBen \given \SpopBen{]}$) is the probability for a mutation to be non-adaptive given it is beneficial at the population scale.\label{table:no-CpG}}
+    \end{center}
 
@@
 
-    The site-frequency spectrum (SFS, panel A) and the congruency between fitness effects estimates ($\Sphy$ versus $\Sphy$, panel B) shown below are obtained in the African population of \textit{Homo sapiens} and the South African population of \textit{Chlorocebus sabaeus}.
-
-    \begin{center}
-        \captionof{figure}{Site-frequency spectrum in African population of \textit{Homo sapiens}, masking CpG transitions.}
+    The site-frequency spectrum (SFS, panel A) and the congruency between fitness effects estimates ($\Spop$ versus $\Sphy$, panel B) are shown in Figure~\ref{mutsel-dfe-sfs} for the African population of \textit{Homo sapiens} and the South African population of \textit{Chlorocebus sabaeus}.
+
+    \begin{center}
         \begin{minipage}{0.49\linewidth}
@@
         \begin{minipage}{0.49\linewidth}
-            \flushleft {\tiny B: $S$ as function of $S_0$ for each class}
+            \flushleft {\tiny B: $\Spop$ as function of $\Sphy$ for each class}
             \includegraphics[width=\linewidth, page=1]{artworks/CpG.Homo_sapiens.AFR.MutSel.polyDFE_C.pdf}
@@
     \begin{center}
-        \captionof{figure}{Site-frequency spectrum in South African population of \textit{Chlorocebus sabaeus}, masking CpG transitions.}
         \begin{minipage}{0.49\linewidth}
-            \flushleft {\tiny A: Site frequency spectrum}
+            \flushleft {\tiny C: Site frequency spectrum}
             \includegraphics[width=\linewidth, page=1]{artworks/CpG.Chlorocebus_sabaeus.South_Africa.MutSel-sfs.pdf}
@@
         \begin{minipage}{0.49\linewidth}
-            \flushleft {\tiny B: $S$ as function of $S_0$ for each class}
+            \flushleft* {\tiny D: $\Spop$ as function of $\Sphy$ for each class}
             \includegraphics[width=\linewidth, page=1]{artworks/CpG.Chlorocebus_sabaeus.South_Africa.MutSel.polyDFE_C.pdf}
         \end{minipage}
-    \end{center}
-
-    \begin{itemize}[itemsep=0pt]
-        \item A: The site-frequency spectrum (SFS) in the population for a random sample of 16 alleles (means in solid lines and standard deviations in color shades) for each class of selection and for synonymous mutations, supposedly neutral (black).
+    \captionof{figure}[Site-frequency spectrum when masking CpG transitions.]{\textbf{Site-frequency spectrum when masking CpG transitions.} Left (A\&C): the site-frequency spectrum (SFS) in the population for a random sample of 16 alleles (means in solid lines and standard deviations in color shades) for each class of selection ($\SphyDel$, $\SphyNeu$ and $\SphyBen$) and for synonymous mutations, supposedly neutral (black).
 The SFS represents the proportion of mutations (y-axis) with a given number of derived alleles in the population (x-axis).
 Here SFS are weighted by the mutational opportunities in each class of selection (synonymous, $\SphyDel$, $\SphyNeu$ and $\SphyBen$).
-        \item B: Proportion of beneficial $\ProbaPopDel$, nearly-neutral $\ProbaPopNeu$, and deleterious mutations $\ProbaPopBen$  estimated at the population scale for each class of selection at the phylogenetic scale.
+Right (B\&D): proportion of beneficial $\ProbaPopDel$, nearly-neutral $\ProbaPopNeu$, and deleterious mutations $\ProbaPopBen$  estimated at the population scale for each class of selection at the phylogenetic scale.
 Proportions depicted here are not weighted by their mutational opportunities.
-    \end{itemize}
-
-    \newpage
-    \section{Including divergence data for the estimation of $\Spop$}
-
-    \subsection{Including divergence in polyDFE}
-    Divergence data (number of substitutions per site) can also be included into polyDFE to estimate the DFE.
-    For the class of a given class of selection coefficient ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$), the number of substitutions has already been computed and is given by $D\left( \Sphyclass \right)$ (see eq.~6), and the number of sites is given by $L \left( \Sphyclass \right)$ (see eq.~4).
+Top (A\&C): \textit{Homo sapiens}, African population.
+Bottom (C\&D): \textit{Chlorocebus sabaeus}, South Africa population.}
+    \label{mutsel-dfe-sfs}
+    \end{center}
+
+    \newpage
+
+    \section{Excluding genes under adaptation}
+    The proportion of beneficial non-adaptive mutations ($\proba{[}\SphyBen\given \SpopBen {]}$) is higher when excluding genes under adaptation, as shown in Table~\ref{table:no-adaptation-div}, consistent with our expectation that genes with uniformly conserved functions should fit better the nearly-neutral equilibrium model.
+
+    \begin{center}
+        \begin{tabular}{|l|l|r|r|}
+            \toprule
+            Population & Species & Control & Case \\
+            \midrule
+            \rowcolor{LIGHTGREY} Equus c. & Equus caballus & $ 0.536$ & $ 0.880$ \\
+            Iran & Bos taurus & $ 0.243$ & $ 0.249$ \\
+            Uganda & Bos taurus & $ 0.415$ & $ 0.429$ \\
+            \rowcolor{LIGHTGREY} Australia & Capra hircus & $ 0.177$ & $ 0.190$ \\
+            \rowcolor{LIGHTGREY} France & Capra hircus & $ 0.190$ & $ 0.201$ \\
+            \rowcolor{LIGHTGREY} Iran (C. aegagrus) & Capra hircus & $ 0.165$ & $ 0.169$ \\
+            \rowcolor{LIGHTGREY} Iran & Capra hircus & $ 0.193$ & $ 0.176$ \\
+            \rowcolor{LIGHTGREY} Italy & Capra hircus & $ 0.243$ & $ 0.261$ \\
+            \rowcolor{LIGHTGREY} Morocco & Capra hircus & $ 0.245$ & $ 0.283$ \\
+            \rowcolor{LIGHTGREY} Iran & Ovis aries & $ 0.407$ & $ 0.454$ \\
+            Iran (O. orientalis) & Ovis aries & $ 0.190$ & $ 0.207$ \\
+            Iran (O. vignei) & Ovis aries & $ 0.110$ & $ 0.135$ \\
+            Various & Ovis aries & $ 0.222$ & $ 0.246$ \\
+            Morocco & Ovis aries & $ 0.514$ & $ 0.627$ \\
+            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus & $ 0.293$ & $ 0.325$ \\
+            \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus & $ 0.275$ & $ 0.273$ \\
+            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus & $ 0.245$ & $ 0.242$ \\
+            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus & $ 0.821$ & $ 0.873$ \\
+            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus & $ 0.257$ & $ 0.254$ \\
+            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus & $ 0.358$ & $ 0.395$ \\
+            \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus & $ 0.341$ & $ 0.375$ \\
+            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus & $ 0.336$ & $ 0.355$ \\
+            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus & $ 0.250$ & $ 0.263$ \\
+            African & Homo sapiens & $ 0.349$ & $ 0.363$ \\
+            Admixed American & Homo sapiens & $ 0.345$ & $ 0.312$ \\
+            East Asian & Homo sapiens & $ 0.249$ & $ 0.233$ \\
+            European & Homo sapiens & $ 0.248$ & $ 0.211$ \\
+            South Asian & Homo sapiens & $ 0.224$ & $ 0.218$ \\
+            \bottomrule
+        \end{tabular}
+        \captionof{table}[$\proba{[}\SphyBen\given \SpopBen {]}$ excluding or not genes under adaptation.]{\textbf{$\bm{\proba{[}\SphyBen\given \SpopBen {]}}$ excluding or not genes under adaptation.}
+        Genes under adaptation retrieved from \textcite{latrille_genes_2023}.
+        Comparison of $\proba{[}\SphyBen\given \SpopBen {]}$ for the whole genome (control) and when excluding genes under adaptation (case).
+        The non-parametric Wilcoxon signed-rank test evaluates the null hypothesis that the distribution of the differences (case versus control) is symmetric around zero.
+        Applied to the paired samples (case and control), Wilcoxon signed-rank test results in $s=80$ with $\pvalue=0.002$, for the one-sided test (case higher than control).\label{table:no-adaptation}}
+    \end{center}
+
+    \newpage
+
+    \section{Including substitutions in the terminal lineage to estimate \texorpdfstring{$\Spop$}{S}}
+
+    \subsection{Including substitutions in polyDFE}
+
+    Divergence data (number of substitutions per site) can also be included into polyDFE to estimate the DFE, as shown in figure~\ref{fig-incdiv}.
+    For the class of a given class of selection coefficient ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$), the number of substitutions has already been computed and is given by $D\left( \Sphyclass \right)$ (eq.~6), and the number of sites is given by $L \left( \Sphyclass \right)$ (eq.~4).
     Otherwise, the procedure is the same as described section \textit{Scaled selection coefficients ($\Spop$) in a population-based method}.
 
+    \begin{center}
+            \includegraphics[width=\textwidth, page=1] {artworks/figure.method.proba.div.pdf}
+            \captionof{figure}[Including substitutions in the terminal lineage to estimate $\Spop$]{\textbf{Including substitutions in the terminal lineage to estimate $\bm{\Spop}$.} Same as Figure 2 in the main text, but including substitutions in the terminal lineage to estimate $\Spop$.
+            At the phylogenetic scale (A), we estimated the amino-acid fitness for each site from protein-coding DNA alignments using mutation-selection codon models.
+            For every possible mutation, the difference in amino-acid fitness before and after the mutation allows us to compute the selection coefficient at the phylogenetic scale ($\Sphy$).
+            Depending on $\Sphy$ (B) mutations can be predicted as deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) or beneficial non-adaptive mutations ($\SphyBen$) toward a fitter amino acid and repairing existing functions.
+            For each population, each observed single nucleotide polymorphism (SNP) segregating can also be classified according to its $\Sphy$ value (C).
+            Within the terminal lineage leading to this population, each substitution can be classified according to its $\Spop$ value (C).
+            Non-synonymous polymorphisms and divergence, contrasted to synonymous polymorphisms and divergence (deemed neutral) is used to estimate selection coefficients (D-E) at the population scale ($\Spop$), for each class of selection ($\SphyDel$, $\SphyNeu$, $\SphyBen$).
+            We can thus assess whether $\Sphy$ predicts $\Spop$ and compute \textit{precision} (F) and \textit{recall} (G) for each class.
+            The \textit{recall} value for class $\SphyBen$ is the probability for beneficial mutations to be non-adaptive (G).
+            \label{fig-incdiv}
+            }
+    \end{center}
+
+    \newpage
+
     \subsection{Probability for beneficial mutations to be non-adaptive}
-    \begin{center}
-        \captionof{table}{$\proba[\SphyBen\given \SpopBen ]$ when including divergence to estimate $\Spop$.}
+    The estimation of $\proba{[} \SpopBen {]}$ and $\proba{[}\SphyBen\given \SpopBen {]}$ across populations when including substitutions in the terminal lineage and fitting a discrete DFE to $\Spop$ is shown in Table~\ref{table:inc-div-bayes}.
+    Altogether, comparing these results with table~\ref{table:proba}, we acknowledge that the exact proportion of non-adaptive among all beneficial mutations is dependent whether we included or not substitutions in the terminal lineage for the estimation of $\Spop$.
+    However, we can still see that non-adaptive beneficial mutations are positively selected compared to neutral and deleterious ones, and this result is valid whether we included or not substitutions in the terminal lineage for the estimation of $\Spop$.
+
+    \begin{center}
         \scriptsize
@@
         \end{longtable*}
-    \end{center}
-    \begin{itemize}
-        \item $\Ne$ is the estimated effective population size.
-        \item $\proba [ \SphyBen ]$ (eq.~5) is the probability for a new mutation a non-adaptive mutation.
+        \captionof{table}[$\proba{[}\SphyBen\given \SpopBen {]}$ when including divergence to estimate $\Spop$.]{\textbf{$\bm{\proba{[}\SphyBen\given \SpopBen {]}}$ when including divergence to estimate $\bm{\Spop}$.}
+        $\Ne$ is the estimated effective population size.
+        $\proba{[} \SphyBen {]}$ (eq.~5) is the probability for a new mutation to be a non-adaptive mutation.
         These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1, thus toward a more fit amino-acid.
-        \item $\proba [ \SpopBen ]$ (eq.~15) is the probability for a mutation to be beneficial.
+        $\proba{[} \SpopBen {]}$ (eq.~15) is the probability for a mutation to be beneficial.
         These mutations have a selection coefficient at the population-scale larger than 1.
-        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a non-adaptive mutation at the phylogenetic scale (the \textit{precision}).
-        \item $\proba [ \SphyBen \given \SpopBen]$ (eq.~14) is the probability for a mutation to be non-adaptive given it is beneficial at the population scale (the \textit{recall}).
-        This probability is obtained using Bayes' formula.
-    \end{itemize}
+        $\proba{[} \SpopBen \given \SphyBen{]}$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a non-adaptive mutation at the phylogenetic scale (the \textit{precision}).
+        $\proba{[} \SphyBen \given \SpopBen{]}$ (eq.~14) is the probability for a mutation to be non-adaptive given it is beneficial at the population scale (the \textit{recall}).
+        This probability is obtained using Bayes' formula.\label{table:inc-div-bayes}}
+    \end{center}
+
     \newpage
@@
     \subsection{Precision and recall}
-    \captionof{table}{Precision and recall while including divergence to estimate $\Spop$.}
+    The estimation of \textit{precision} and \textit{recall} across populations when including substitutions in the terminal lineage for the estimation of $\Spop$ is shown in Table~\ref{table:inc-div}.
+    Comparing these results with tables 1, we acknowledge that the exact quantification of \textit{precision} and \textit{recall} is dependent on whether we included or not substitutions in the terminal lineage for the estimation of $\Spop$.
+    However, we can still see that non-adaptive beneficial mutations are positively selected compared to neutral and deleterious ones, and this result is valid whether we included or not substitutions in the terminal lineage for the estimation of $\Spop$.
+
     \begin{center}
@@
         \end{adjustbox}
-    \end{center}
-    \begin{itemize}
-        \item $\Ne$ is the estimated effective population size.
-        \item \textit{Precision} is the estimation of the selection coefficient at population scale ($\Spop$) given that $\Sphy$ is known.
-        \item  \textit{Recall} is the estimation of $\Sphy$ given selection coefficient at the population scale ($\Spop$) is known.
-        \item \textit{Recall} for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is the probability for a mutation to be non-adaptive given it is beneficial at the population scale.
-    \end{itemize}
-
-    Altogether, comparing this table to tables 1 and S3, we acknowledge that the exact proportion of non-adaptive beneficial mutations among all beneficial ones is different whether we included or not substitutions in the terminal lineage for the estimation of $\Spop$.
-    However, we can still see that non-adaptive beneficial mutations are positively selected compared to neutral and deleterious ones, and this result is not sensitive to inclusion of substitutions in the terminal lineage.
+        \captionof{table}[Precision and recall when including divergence to estimate $\Spop$.]{\textbf{Precision and recall when including divergence to estimate $\bm{\Spop}$.}
+        $\Ne$ is the estimated effective population size.
+        \textit{Precision} is the estimation of the selection coefficient at population scale ($\Spop$) given that $\Sphy$ is known.
+        \textit{Recall} is the estimation of $\Sphy$ given selection coefficient at the population scale ($\Spop$) is known.
+        \textit{Recall} for beneficial mutations ($\proba{[}\SphyBen \given \SpopBen{]}$) is the probability for a mutation to be non-adaptive given it is beneficial at the population scale.
+        \label{table:inc-div}}
+    \end{center}
+
     \newpage
@@
 
-    If misannotation is influencing the recall for $\SphyBen$ ($\proba[\SphyBen\given \SpopBen ]$), then the recall should increase as a function of  divergence to the sister species ($\ds$: number of synonymous substitutions per sites) since divergence would increase the rate of misannotations.
-    Shown below is recall $\proba[\SphyBen\given \SpopBen ]$ as a function of divergence ($\ds$) in which the latter is not an explanatory variable.
-
-    \begin{center}
-        \captionof{figure}{$\proba[\SphyBen\given \SpopBen ]$ while including divergence to estimate $\Spop$, as a function of distance to the sister species.}
+    If misannotation is influencing the recall for $\SphyBen$ ($\proba{[}\SphyBen\given \SpopBen {]}$), then the recall should increase as a function of  divergence to the sister species ($\ds$: number of synonymous substitutions per sites) since divergence would increase the rate of misannotations.
+    Shown in Figure~\ref{fig:distance-incdiv} is recall $\proba{[}\SphyBen\given \SpopBen {]}$ as a function of divergence ($\ds$) in which the latter is not an explanatory variable.
+
+    \begin{center}
         \includegraphics[width=0.75\linewidth, page=1]{artworks/results.distance.recall_pos.div.scatter.pdf}
+        \captionof{figure}[$\proba{[}\SphyBen\given \SpopBen {]}$ when including divergence to estimate $\Spop$, as a function of distance to the sister species.]{\textbf{$\bm{\proba{[}\SphyBen\given \SpopBen {]}}$ when including divergence to estimate $\bm{\Spop}$, as a function of distance to the sister species}.
+$\proba{[} \SphyBen \given \SpopBen{]}$ (eq.~14) is the probability for a beneficial mutation to be non-adaptive.
+$\ds$ is number of synonymous substitutions per site that occurred since divergence with the sister species (closest species in the mammalian tree).
+Same as Figure~\ref{fig:distance-sister} but including divergence to estimate $\Spop$.
+Populations are represented by circles, and squares are the mean for the species.
+Correlations account for phylogenetic relationship and non-independence of samples, through the fit of a Phylogenetic Generalized Linear Model (see Materials \& Methods).\label{fig:distance-incdiv}}
     \end{center}
@@
     \subsection{Excluding genes under adaptation}
-
-    \begin{center}
-        \captionof{table}{$\proba[\SphyBen\given \SpopBen ]$ excluding or not genes under adaptation, when including divergence to estimate $\Spop$.}
+    The proportion of beneficial non-adaptive mutations ($\proba{[}\SphyBen\given \SpopBen {]}$) is higher when excluding genes under adaptation, as shown in Table~\ref{table:no-adaptation-div}, consistent with our expectation that genes with uniformly conserved functions should fit better the nearly-neutral equilibrium model.
+
+    \begin{center}
         \begin{tabular}{|l|l|r|r|}
@@
         \end{tabular}
-    \end{center}
+        \captionof{table}[$\proba{[}\SphyBen\given \SpopBen {]}$ excluding or not genes under adaptation, when including divergence to estimate $\Spop$.]{\textbf{$\bm{\proba{[}\SphyBen\given \SpopBen {]}}$ excluding or not genes under adaptation, when including divergence to estimate $\bm{\Spop}$.}
         Genes under adaptation retrieved from~\cite{latrille_genes_2023}.
-    Comparison of $\proba[\SphyBen\given \SpopBen ]$ while including divergence for the whole genome (control) and when excluding genes under adaptation (case).
+        Comparison of $\proba{[}\SphyBen\given \SpopBen {]}$ when including divergence for the whole genome (control) and when excluding genes under adaptation (case).
         The non-parametric Wilcoxon signed-rank test tests the null hypothesis that the distribution of the differences (case versus control) is symmetric about zero.
-    Applied to the paired samples (case and control), Wilcoxon signed-rank test results in $s=120$ with $\pvalue=0.027$ for one-sided test (case higher than control).
-    The proportion of beneficial non-adaptive mutations ($\proba[\SphyBen\given \SpopBen ]$) is higher when excluding genes under adaptation, consistent with our expectation that genes with uniformly conserved functions should fit better the nearly-neutral equilibrium model.
-
-    \newpage
-
-    \section{Discrete distribution of $\Spop$ at the population scale}
-
-    \subsection{polyDFE model D (discrete distribution)}
-    Additionally to including divergence, with also tested our prediction with polyDFE model D instead of model C.
+        Applied to the paired samples (case and control), Wilcoxon signed-rank test results in $s=120$ with $\pvalue=0.027$ for one-sided test (case higher than control).\label{table:no-adaptation-div}
+        }
+    \end{center}
+
+    \newpage
+    \subsection{Fitting one or three distributions of fitness effects}
+
+    We also performed another test to assess that fitting the same functional form of DFE to three categories of selection (i.e., $\SphyDel, \SphyNeu, \SphyBen$) is a sound methodology.
+    Typically, $\proba{[} \SpopBen {]}$ can be computed from two different estimates, by either splitting data (polymorphism within populations and substitutions in the terminal lineages) in three category (i.e., $\SphyDel, \SphyNeu, \SphyBen$) or not at all.
+    In the case of splitting data in three categories and fitting three DFEs, $\proba{[} \SpopBen {]}$ is obtained by summing over the three categories using the law of total probability (eq.\ 15):
+
+    \begin{equation}
+        \proba{[} \SpopBen ] \text{ (three DFEs) } = \proba{[}\SpopBen \given \SphyDel ] \times \proba{[}\SphyDel ] + \proba{[}\SpopBen \given \SphyNeu ] \times \proba{[}\SphyNeu ] + \proba{[}\SpopBen \given \SphyBen ] \times \proba{[}\SphyBen ].
+        \label{eq:total_proba}
+    \end{equation}
+
+    But it is also possible to compute $\proba{[} \SpopBen {]}$ directly from fitting one DFE to the full data (polymorphism within populations and substitutions in the terminal lineages), not splitting at all, and then $\proba{[} \SpopBen {]}$ is obtained from the parameters of the DFE (eq.\ 11):
+    \begin{align}
+        \proba{[} \SpopBen ] \text{ (one DFE) } &= \proba{[} \Spop > 1 ] = p_b \int_{1}^{+\infty} f_{e}(\Spop; \AdvMean) \der \Spop. \label{eq:polyProbaAdv}
+    \end{align}
+
+    We reproduced this experiment for $\proba{[} \SpopDel {]}$ (Figure~\ref{fig:one-three-neg}), $\proba{[} \SpopNeu {]}$ (Figure~\ref{fig:one-three-weak}) and $\proba{[} \SpopBen {]}$ (Figure~\ref{fig:one-three-pos}).
+
+    \begin{center}
+        \includegraphics[width=0.75\linewidth, page=1]{artworks/results.reg.neg.div.scatter.pdf}
+        \captionof{figure}[$\proba{[} \SpopDel {]}$ when fitting a single or three DFEs.]{\textbf{$\bm{\proba{[} \SpopDel {]}}$ when fitting a single or three DFEs.} Populations are represented by circles, and squares are the mean for the species.
+Goodness of fit is calculated as the coefficient of determination ($R^2$) for the prediction $\proba{[} \SpopDel ] \text{ (three DFEs) } = \proba{[} \SpopDel ] \text{ (one DFE) }$, meaning calculating the residuals of the fit to the 1:1 line.\label{fig:one-three-neg}}
+    \end{center}
+
+    \newpage
+    \begin{center}
+        \includegraphics[width=0.75\linewidth, page=1]{artworks/results.reg.weak.div.scatter.pdf}
+        \captionof{figure}[$\proba{[} \SpopNeu {]}$ when fitting a single or three DFEs.]{\textbf{$\bm{\proba{[} \SpopNeu {]}}$ when fitting a single or three DFEs.} Populations are represented by circles, and squares are the mean for the species.
+Goodness of fit is calculated as the coefficient of determination ($R^2$) for the prediction $\proba{[} \SpopNeu ] \text{ (three DFEs) } = \proba{[} \SpopNeu ] \text{ (one DFE) }$, meaning calculating the residuals of the fit to the 1:1 line.\label{fig:one-three-weak}}
+    \end{center}
+
+    \begin{center}
+        \includegraphics[width=0.75\linewidth, page=1]{artworks/results.reg.pos.div.scatter.pdf}
+        \captionof{figure}[$\proba{[} \SpopBen {]}$ when fitting a single or three DFEs.]{\textbf{$\bm{\proba{[} \SpopBen {]}}$ when fitting a single or three DFEs.} Populations are represented by circles, and squares are the mean for the species.
+Goodness of fit is calculated as the coefficient of determination ($R^2$) for the prediction $\proba{[} \SpopBen ] \text{ (three DFEs) } = \proba{[} \SpopBen ] \text{ (one DFE) }$, meaning calculating the residuals of the fit to the 1:1 line.\label{fig:one-three-pos}}
+    \end{center}
+
+    \newpage
+
+    \section{Non-parametric distribution of fitness effects}
+
+    \subsection{polyDFE model D (non-parametric)}
+    Additionally to including divergence, we also tested our prediction with polyDFE model D instead of model C.
     In polyDFE model D, the DFE of non-synonymous mutations is given as a discrete DFE of $K$ categories (instead of a continuous distribution in model C), where the selection coefficients of each category $i$ ($1 \leq i \leq K$) are fixed parameters $\Spop_i$, and each value $\Spop_i$ has a probability $p_i$ (estimated), with $\sum_{i=1}^{K} p_i =1$.
     We used $K=6$ with $\Spop_1 = -500$, $\Spop_2 = -4$, $\Spop_3 =-1$, $\Spop_4 = 0$, $\Spop_5 = 1$, $\Spop_6 = 4$.\\
-    For each class of selection $\Sphyclass$, the parameters $p_i$ ($i \in \{ 1 \leq i \leq 6 \}$) were used to compute $\proba [ \SpopDel \given  \Sphyclass] $, $\proba [ \SpopNeu \given \Sphyclass]$, and $\proba [ \SpopBen \given \Sphyclass]$ as:
+
+    For each class of selection $\Sphyclass$, the parameters $p_i$ ($i \in \{ 1 \leq i \leq 6 \}$) were used to compute $\proba{[} \SpopDel \given  \Sphyclass{]}$, $\proba{[} \SpopNeu \given \Sphyclass{]}$, and $\proba{[} \SpopBen \given \Sphyclass{]}$ as:
     \begin{align}
-        \proba [ \SpopDel \given  \Sphyclass] &= \proba [ \Spop < -1 \given \Sphyclass ] = p_1 + p_2 \label{eq:polyProbaDel-mD} \\
-        \proba [ \SpopNeu \given \Sphyclass] &= \proba [ -1 < \Spop < 1 \given \Sphyclass ] = p_3 + p_4 + p_5,  \\
-        \proba [ \SpopBen \given \Sphyclass] &= \proba [  \Spop > 1 \given \Sphyclass ] = p_6.  \label{eq:polyProbaAdv-mD}
+        \proba{[} \SpopDel \given  \Sphyclass] &= \proba{[} \Spop < -1 \given \Sphyclass ] = p_1 + p_2 \label{eq:polyProbaDel-mD} \\
+        \proba{[} \SpopNeu \given \Sphyclass] &= \proba{[} -1 < \Spop < 1 \given \Sphyclass ] = p_3 + p_4 + p_5,  \\
+        \proba{[} \SpopBen \given \Sphyclass] &= \proba{[}  \Spop > 1 \given \Sphyclass ] = p_6.  \label{eq:polyProbaAdv-mD}
     \end{align}
 
+    \newpage
     \subsection{Probability for beneficial mutations to be non-adaptive}
-    \begin{center}
-        \captionof{table}{$\proba[\SphyBen\given \SpopBen ]$ when using a discrete DFE to estimate $\Spop$.}
+    The estimation of $\proba{[} \SpopBen {]}$ and $\proba{[}\SphyBen\given \SpopBen {]}$ across populations when including substitutions in the terminal lineage and fitting a discrete DFE to $\Spop$ is shown in Table~\ref{table:discrete-dfe-bayes}.
+    Altogether, comparing these results with table~\ref{table:inc-div-bayes}, we acknowledge that the exact proportion of non-adaptive among all beneficial mutations is dependent on the model used to estimate the DFE.
+    However, we can still see that non-adaptive beneficial mutations are positively selected compared to neutral and deleterious ones, and this result is valid for different underlying DFE.
+
+    \begin{center}
         \scriptsize
@@
         \end{longtable*}
-    \end{center}
-    \begin{itemize}
-        \item $\Ne$ is the estimated effective population size.
-        \item $\proba [ \SphyBen ]$ (eq.~5) is the probability for a new mutation a non-adaptive beneficial mutation.
+        \captionof{table}[$\proba{[}\SphyBen\given \SpopBen {]}$ when using a discrete DFE to estimate $\Spop$.]{\textbf{$\bm{\proba{[}\SphyBen\given \SpopBen {]}}$ when using a discrete DFE to estimate $\bm{\Spop}$.}
+        $\Ne$ is the estimated effective population size.
+        $\proba{[} \SphyBen {]}$ (eq.~5) is the probability for a new mutation to be a non-adaptive beneficial mutation.
         These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1, thus toward a more fit amino-acid.
-        \item $\proba [ \SpopBen ]$ (eq.~15) is the probability for a mutation to be beneficial.
+        $\proba{[} \SpopBen {]}$ (eq.~15) is the probability for a mutation to be beneficial.
         These mutations have a selection coefficient at the population-scale larger than 1.
-        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial non-adaptive mutation at the phylogenetic scale (the \textit{precision}).
-        \item $\proba [ \SphyBen \given \SpopBen]$ (eq.~14) is the probability for a mutation to be non-adaptive given it is beneficial at the population scale (the \textit{recall}).
-        This probability is obtained using Bayes' formula.
-    \end{itemize}
-
+        $\proba{[} \SpopBen \given \SphyBen{]}$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial non-adaptive mutation at the phylogenetic scale (the \textit{precision}).
+        $\proba{[} \SphyBen \given \SpopBen{]}$ (eq.~14) is the probability for a mutation to be non-adaptive given it is beneficial at the population scale (the \textit{recall}).
+        This probability is obtained using Bayes' formula.\label{table:discrete-dfe-bayes}}
+    \end{center}
+
+    \newpage
     \subsection{Precision and recall}
-    \captionof{table}{Precision and recall when using a discrete DFE to estimate $\Spop$.}
+    The estimation of \textit{precision} and \textit{recall} across populations when including substitutions in the terminal lineage and fitting a discrete DFE to $\Spop$ is shown in Table~\ref{table:discrete-dfe}.
+    Altogether, comparing these results with table~\ref{table:inc-div}, we acknowledge that the exact quantification of \textit{precision} and \textit{recall} is dependent on the model used to estimate the DFE.
+    However, we can still see that non-adaptive beneficial mutations are positively selected compared to neutral and deleterious ones, and this result is valid for different underlying DFE.
+
     \begin{center}
@@
         \end{adjustbox}
-    \end{center}
-    \begin{itemize}
-        \item $\Ne$ is the estimated effective population size.
-        \item \textit{Precision} is the estimation of the selection coefficient at population scale ($\Spop$) given that $\Sphy$ is known.
-        \item \textit{Recall} is the estimation of $\Sphy$ given selection coefficient at the population scale ($\Spop$) is known.
-        \item \textit{Recall} for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is the probability for a mutation to be non-adaptive given it is beneficial at the population scale.
-    \end{itemize}
-
-    Altogether, comparing this table other estimations, we acknowledge that the exact proportion of non-adaptive among all beneficial ones is dependent on the model used to estimate the DFE.
-    However, we can still see that non-adaptive beneficial mutations are positively selected compared to neutral and deleterious ones, and this result is not sensitive to the underlying DFE at the population scale.
-
-    \newpage
+        \captionof{table}[Precision and recall when using a discrete DFE to estimate $\Spop$.]{\textbf{Precision and recall when using a discrete DFE to estimate $\bm{\Spop}$.}
+        $\Ne$ is the estimated effective population size.
+        \textit{Precision} is the estimation of the selection coefficient at population scale ($\Spop$) given that $\Sphy$ is known.
+        \textit{Recall} is the estimation of $\Sphy$ given selection coefficient at the population scale ($\Spop$) is known.
+        \textit{Recall} for beneficial mutations ($\proba{[}\SphyBen \given \SpopBen{]}$) is the probability for a mutation to be non-adaptive given it is beneficial at the population scale.\label{table:discrete-dfe}}
+    \end{center}
 

### 2024-12-06 manuscript/main-PLOS-revision-2-plos2015.tex
Technical check requests

@@
 This study makes use of data generated by the NextGen Consortium.
-Funding:
-Université de Lausanne; Agence Nationale de la Recherche, Grant ANR-19-CE12-0019 / HotRec.
+
+\section*{Funding}
+This work was funded by Faculté de Biologie et de Médecine, Université de Lausanne (https://www.unil.ch; to TL, DAH and NS) and Agence Nationale de la Recherche (https://anr.fr/; grant ANR-19-CE12-0019 / HotRec to JJ).
+The funders did not play any role in the study design, data collection and analysis, decision to publish, or preparation of the manuscript.
 
 \section*{Competing interests}
-The authors declare no conflicts of interest.
+The authors have declared that no competing interests exist.
 

### 2024-12-16 manuscript/S1 File.tex
Split Supplementary materials into 4 files.

--- 2023-05-03 manuscript/supp-mat.tex
@@
 \documentclass{article}
-\usepackage{caption}
+\usepackage[hypcap=false]{caption}
 \usepackage{xcolor, colortbl}
+\definecolor{RED}{HTML}{EB6231}
+\definecolor{BLUE}{HTML}{5D80B4}
 \definecolor{LIGHTGREY}{gray}{0.9}
@@
 \usepackage{graphicx}
+\usepackage{blkarray}
+\usepackage{pgf,tikz}
+\usetikzlibrary{shapes,arrows,backgrounds,fit,positioning,arrows,automata,calc}
+\tikzset{res/.style={ellipse,draw,minimum height=1.0cm,minimum width=0.8cm}}
+\tikzset{literal/.style={rectangle,draw,minimum height=0.5cm,minimum width=0.8cm,text width = 1.2 cm, align = center}}
+
 \pdfinclusioncopyfonts=1
 
-\renewcommand{\thetable}{S\arabic{table}}
-\renewcommand{\thefigure}{S\arabic{figure}}
+\renewcommand{\baselinestretch}{1.5}
+\renewcommand{\arraystretch}{0.6}
+\frenchspacing
+
+\renewcommand{\thetable}{\Alph{table}}
+\renewcommand{\thefigure}{\Alph{figure}}
+\renewcommand{\theequation}{S.\arabic{equation}}
 
 \newcommand{\UniDimArray}[1]{\bm{#1}}
+\newcommand{\BiDimArray}[1]{\bm{#1}}
+
 \newcommand{\der}{\text{d}}
@@
 \newcommand{\thetaSyn}{\theta_{\text{S}}}
+\newcommand{\pvalue}{p\text{-value}}
 
-\title{\textbf{Mammalian protein-coding genes exhibit widespread beneficial mutations that are not adaptive}}
+% Model
+\newcommand{\submatrix}{q}
+\newcommand{\Submatrix}{\BiDimArray{\submatrix}}
+\newcommand{\probmatrix}{P}
+\newcommand{\Probmatrix}{\BiDimArray{\probmatrix}}
+\newcommand{\fit}{F}
+\newcommand{\Fit}{\UniDimArray{\fit}}
+\newcommand{\indice}{l}
+\newcommand{\indiceexp}{^{(\indice)}}
+\newcommand{\ci}{{a}}
+\newcommand{\cj}{{b}}
+\newcommand{\itoj}{\ci \mapsto \cj}
+\newcommand{\nuc}{\mathcal{M}}
+\newcommand{\fiti}{\fit_{\ci}}
+\newcommand{\fitj}{\fit_{\cj}}
+\newcommand{\mutmatrix}{R}
+\newcommand{\Mutmatrix}{\BiDimArray{\mutmatrix}}
+\newcommand{\exchan}{\rho}
+\newcommand{\Exchan}{\UniDimArray{\exchan}}
+\newcommand{\mutequi}{\sigma}
+\newcommand{\Mutequi}{\UniDimArray{\mutequi}}
+\newcommand{\Tree}{\mathcal{T}}
+\newcommand{\branch}{\text{j}}
+\newcommand{\branchexp}{^{(\branch)}}
+\newcommand{\branchlength}{l}
+% Alignment
+\newcommand{\data}{D}
+\newcommand{\Data}{\BiDimArray{\data}}
+\newcommand{\site}{\text{i}}
+\newcommand{\Nsite}{\text{N}}
+\newcommand{\siteexp}{^{(\site)}}
+\newcommand{\Setsite}{\site \in \{1, \hdots, \Nsite\} }
+\newcommand{\branchsiteexp}{^{(\branch, \site)}}
+% Categories
+\newcommand{\cat}{\text{k}}
+\newcommand{\Ncat}{\text{K}}
+\newcommand{\catexp}{^{(\cat)}}
+\newcommand{\catInterval}{\{1, \hdots, \Ncat\}}
+\newcommand{\Setcat}{\cat \in \catInterval }
+\newcommand{\branchcatexp}{^{(\branch, \cat)}}
+\newcommand{\profile}{\phi}
+\newcommand{\Profile}{\UniDimArray{\profile}}
+\newcommand{\concentrationProfile}{\alpha}
+\newcommand{\centerProfile}{\UniDimArray{\gamma}}
+\newcommand{\catVar}{\kappa}
+\newcommand{\catsite}{\catVar\left(\site\right)}
+\newcommand{\catmultivar}{m}
+\newcommand{\catMultiVar}{\UniDimArray{\catmultivar}}
+\newcommand{\stickbreaking}{\theta}
+\newcommand{\StickBreaking}{\UniDimArray{\stickbreaking}}
+\newcommand{\stick}{\psi}
+\newcommand{\stickbreakinghyper}{\beta}
+\newcommand{\Multivariate}{\UniDimArray{Z}}
+\newcommand{\subhistory}{\mathcal{H}}
+
+\title{\textbf{Estimating the proportion of beneficial mutations that are not adaptive in mammals}}
 
@@
     \maketitle
-    \part*{Supplementary materials}
+    \part*{S1 File}
+    \vspace{-1em}
     \tableofcontents
+    \listoffigures
+
     \clearpage
+    \section{Mutation-selection codon models}\label{sec:mutsel}
 
-    \section{Beneficial mutations in the terminal lineages and populations}\label{sec:beneficial-mutations}
+    \subsection{Prior distributions and parameters of the model}\label{subsec:priors}
 
-    \subsection{Mutation-selection codon models}
-    \label{sec:site-specific-mutation-selection-codon-models}
-    In \textit{BayesCode} (\url{https://github.com/ThibaultLatrille/bayescode}), we ran the mutation-selection codon models \textit{mutselomega} for 2000 points of MCMC with the options:
+    We here present the Mutation-selection codon model as a Bayesian hierarchical model, including the prior distributions and the parameters of the model.
+    This hierarchical model is formally represented as directed acyclic graph of dependencies between variables, depicted in Figure~\ref{mutsel-illustration}:
+
+    \begin{center}
+
+        \begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=0.6cm and 1.2cm,semithick]
+            \tikzstyle{every state}=[]
+
+            \node[state] (P) {$\Probmatrix\branchsiteexp$};
+            \node[state] (Q) [below right=of P] {$\Submatrix\branchsiteexp$};
+            \node[state] (R) [below right=of Q] {$\Mutmatrix$};
+            \node[state] (BL) [BLUE, right=of P] {$\branchlength\branchexp$};
+            \node[res] (BLH) [RED, right=of BL] {$ \lambda, \tau $};
+            \node[state] (f) [right=of Q] {$\Fit\siteexp $};
+            \node[state] (Ex) [BLUE, below right=of R] {$\Exchan$};
+            \node[state] (Equi) [BLUE, right=of R] {$\Mutequi$};
+            \node[state] (Base) [BLUE, above right=of f] {$\Profile\catexp$};
+            \node[state] (cat) [BLUE, right=of f] {$\catsite$};
+            \node[res] (ExH) [RED, right=of Ex] {$1,1,1,1,1,1$};
+            \node[res] (EquiH) [RED, right=of Equi] {$1,1,1,1$};
+            \node[state] (baseH) [RED, right=of Base] {$\concentrationProfile, \centerProfile $};
+            \node[state] (sb) [BLUE, right=of cat] {$\StickBreaking$};
+            \node[state] (sbH) [RED, right=of sb] {$\stickbreakinghyper$};
+
+            \path
+            (Q) edge [black] node [above right] {\ref{eq:Probmatrix}} (P)
+            (BL) edge [black] node [] {} (P)
+            (R) edge [black] node {} (Q)
+            (f) edge [black] node [above] {\ref{eq:subrates}} (Q)
+            (Ex) edge [black] node [] {} (R)
+            (Equi) edge [black] node [below] {\ref{eq:gtr-mutrates}} (R)
+            (Base) edge [black] node {} (f)
+            (cat) edge [black] node [above] {\ref{eq:sitefitness}} (f)
+            (BLH) edge [dashed, BLUE] node [above] {\ref{eq:branchlength}} (BL)
+            (ExH) edge [dashed, BLUE] node [above] {\ref{eq:DistribExchan}} (Ex)
+            (EquiH) edge [dashed, BLUE] node [above] {\ref{eq:DistribMutequi}} (Equi)
+            (baseH) edge [dashed, BLUE] node [above] {\ref{eq:DistribBase}} (Base)
+            (sb) edge [dashed, BLUE] node [above] {\ref{eq:DistribMultinomial}} (cat)
+            (sbH) edge [dashed, BLUE] node [above] {\ref{eq:DistribStickBreaking},\ref{eq:Beta}} (sb);
+        \end{tikzpicture}
+        \captionof{figure}[Bayesian hierarchical model.]{
+    \textbf{Bayesian hierarchical model.} Nodes of the directed acyclic graph are the variables, and edges are the functions.
+    Hyper-parameters are depicted in {\color{RED}{red}} circles, random variables in {\color{BLUE}{blue}} circles, and transformed variables in black.
+    {\color{BLUE}{Blue}} dashed line denotes a drawing from a random distribution, and black solid lines denote a function.
+    All the nodes pointing toward a given node (upstream) are its dependencies which determine its distribution.
+    The other way around, following the arrows in the DAG (downstream), simple {prior} distributions are combined together to form more complex joint {prior} distributions which ultimately define the {prior} distribution of the model.
+    Equations~\ref{eq:gtr-mutrates} to~\ref{eq:Probmatrix} describe the relationship between variables (sections~\ref{sec:nuc} to~\ref{sec:codon}).
+    \label{mutsel-illustration}}
+    \end{center}
+
+    \subsection{Nucleotide mutation rates}
+    \label{sec:nuc}
+    The generalized time-reversible (GTR) nucleotide mutation rate matrix $\Mutmatrix$ is a function of the nucleotide frequencies $\Mutequi$ and the symmetric exchangeability rates $\Exchan$~\cite{tavare_probabilistic_1986}.
+    $\Mutequi = (\mutequi_A , \mutequi_C , \mutequi_G , \mutequi_T)$ is the equilibrium base frequency vector, giving the frequency at which each base occurs at each site.
+    $\Exchan = \left( \exchan_{AC}, \exchan_{AG}, \exchan_{AT}, \exchan_{CG}, \exchan_{CT}, \exchan_{GT}\right)$ is the vector of exchangeabilities between nucleotides.
+    Altogether, the rate matrix is:
+    \begin{equation}
+        \label{eq:gtr-mutrates}
+        \Mutmatrix =
+        \begin{blockarray}{ccccc}
+            & A & C & G & T \\
+            \begin{block}{c(cccc)}
+                A & -\mu_A & {\exchan_{AC}\mutequi_C} & {\exchan_{AG}\mutequi_G} & {\exchan_{AT}\mutequi_T} \\
+                C & {\exchan_{AC}\mutequi_A} &                        -\mu_C & {\exchan_{CG}\mutequi_G} & {\exchan_{CT}\mutequi_T} \\
+                G & {\exchan_{AG}\mutequi_A} & {\exchan_{CG}\mutequi_C} &                        -\mu_G & {\exchan_{GT}\mutequi_T} \\
+                T & {\exchan_{AT}\mutequi_A} & {\exchan_{CT}\mutequi_C} & {\exchan_{GT}\mutequi_G} & -\mu_T\\
+            \end{block}
+        \end{blockarray}
+    \end{equation}
+    By definition, the sum of the entries in each row of the nucleotide rate matrix $\Mutmatrix$ is equal to $0$, giving the diagonal entries:
+    \begin{equation}
+        \mu_a = \sum\limits_{ b \neq a, b \in \{A, C, G, T\} } \mutmatrix_{a,b}
+    \end{equation}
+    The {prior} on the exchangeabilities $\Exchan$ is a uniform Dirichlet distribution of dimension $6$:
+    \begin{equation}
+        \label{eq:DistribExchan}
+        \Exchan \sim \text{Dir}\left( 1,1,1,1,1,1 \right).
+    \end{equation}
+    The {prior} on the equilibrium base frequencies $\Mutequi$ is a uniform Dirichlet distribution of dimension $4$:
+    \begin{equation}
+        \label{eq:DistribMutequi}
+        \Mutequi \sim \text{Dir}\left( 1,1,1,1 \right)
+    \end{equation}
+    The general time-reversible nucleotide matrix is normalized with a total flow of $1$:
+    \begin{equation}
+        \sum\limits_{a \in \{A, C, G, T\}} - \mutequi_a \mutmatrix_{a,a} = 1,
+    \end{equation}
+    such that we expect $1$ {substitution} per unit of branch length.
+
+    \subsection{Site-specific amino-acid fitness profiles}
+    \label{sec:profiles}
+    Site-specific amino-acid fitness profiles are assumed i.i.d. from a mixture model, itself endowed with a truncated Dirichlet process prior.
+    Specifically, the mixture has $\Ncat$ components ($\Ncat = 30$ by default).
+    The prior on component weights~($\StickBreaking$) is modeled using a stick-breaking process, truncated at $\Ncat$ and of parameter $\stickbreakinghyper=1$:
+    \begin{align}
+        \label{eq:DistribStickBreaking}
+        \begin{split}
+            & \StickBreaking \sim \text{StickBreaking}\left( \Ncat, \stickbreakinghyper \right)\\
+            \iff & \stickbreaking_{\cat} = \stick_{\cat}\cdot \prod _{{\indice=1}}^{{\cat-1}}\left(1-\stick_{\indice}\right),\ \Setcat,
+        \end{split}
+    \end{align}
+    where $\stick_{\cat}$ are i.i.d. from a beta distribution
+    \begin{equation}
+        \label{eq:Beta}
+        \stick_{\cat} \sim \text{Beta}\left( 1, \stickbreakinghyper \right),\ \Setcat.
+    \end{equation}
+    Of note, the weights decrease geometrically in expectation, at rate $\stickbreakinghyper$, such that lower values of $\stickbreakinghyper$ induce more heterogeneous distributions of weights.
+
+    Each component of the mixture defines a 20-dimensional fitness profile $\Profile\catexp$ (summing to $1$), for $ \Setcat$.
+    These fitness profiles are i.i.d. from a Dirichlet of center $\centerProfile=1$ and concentration $\concentrationProfile=1$:
+    \begin{equation}
+        \label{eq:DistribBase}
+        \Profile\catexp \sim \text{Dir}\left( \centerProfile,\ \concentrationProfile \right),\ \Setcat.
+    \end{equation}
+
+    Site allocations to the mixture components $\catsite \in \catInterval $, for $\Setsite$ running over the $\Nsite$ sites of the alignment, are i.i.d. multinomial of parameter $\StickBreaking$:
+    \begin{align}
+        \label{eq:DistribMultinomial}
+        \catMultiVar \sim \text{Multinomial}\left( \StickBreaking \right), \\
+        \text{ where } \catmultivar_{\cat} = \sum_{\Setsite} \mathbb{1}_{\catsite = \cat}
+    \end{align}
+
+    For a given parameter configuration for the mixture, the scaled fitness $\Fit\siteexp$ at site $\site$, are obtained by taking the logarithm of fitness assigned to this site:
+    \begin{equation}
+        \label{eq:sitefitness}
+        \Fit\siteexp = \ln \left( \Profile^{\left( \catsite \right)} \right),\ \Setsite.
+    \end{equation}
+
+    \subsection{Branch length}
+    The topology of the rooted phylogenetic tree is supposed to be known and is not estimated by the model.
+    The branch lengths $\branchlength\branchexp$ are defined as the expected number of {neutral} substitutions per {DNA} site along a branch, each from a Gamma distribution of mean $\lambda=0.1$ and scale $\tau=1$:
+    \begin{equation}
+        \label{eq:branchlength}
+        \branchlength\branchexp \sim \text{Gamma}\left( \lambda, \tau \right).
+    \end{equation}
+
+    \subsection{Codon substitution rates}
+    \label{sec:codon}
+    The mutation rate between codons $\ci$ and $\cj$, denoted $\mu_{\itoj}$ depends on the underlying nucleotide change between the codons.
+    First, if codons $\ci$ and $\cj$ are not nearest-neighbours, $\mu_{\itoj}$ is equal to $0$.
+    Second, if codons $\ci$ and $\cj$ are only one mutation away, $\mu_{\itoj}$ is given by the underlying nucleotide relative rate~(${\mutmatrix_{\itoj}}$).
+
+    For a given site $\site$, the {codon} {substitution} rate matrix $\Submatrix\siteexp$ is given by:
+    \begin{equation}
+        \label{eq:subrates}
+        \begin{dcases}
+            \submatrix\siteexp_{\itoj} = 0\text{ if codons $\ci$ and $\cj$ are not nearest-neighbors,} \\
+            \submatrix\siteexp_{\itoj} = \mu_{\itoj}\text{ if codons $\ci$ and $\cj$ are {synonymous},} \\
+            \submatrix\siteexp_{\itoj} = \mu_{\itoj} \dfrac{ \fitj\siteexp - \fiti\siteexp}{{1 - \e^{\fiti\siteexp - \fitj\siteexp} }} \text{ if codons $\ci$ and $\cj$ are non-synonymous,}\\
+            \submatrix\siteexp_{\ci, \ci} = - \sum\limits_{ \cj \neq \ci, \cj=1}^{61} \submatrix\siteexp_{\itoj}.
+        \end{dcases}
+    \end{equation}
+    Together, the probability of transition between codons for a given branch $\branch$ and site $\site$ is:
+    \begin{equation}
+        \label{eq:Probmatrix}
+        \Probmatrix\branchsiteexp = \e^{\branchlength\branchexp \Submatrix\siteexp},
+    \end{equation}
+    which are the matrices necessary to compute the {likelihood} of the data ($\data$) given the parameters of the model using the pruning algorithm.
+
+    \subsection{Bayesian implementation}
+    \label{sec:Bayesian}
+    Bayesian inference was conducted using Markov Chain Monte Carlo (MCMC).
+    Most phylogenetic {MCMC} samplers target the distribution over the model parameters given the sequence alignment, which means that they have to repeatedly invoke the pruning algorithm to recalculate the {likelihood} which is most often the limiting step of the {MCMC}.
+    An alternative, which is used here, is to do the {MCMC} conditionally on the detailed {substitution} history $\subhistory$, thus doing the {MCMC} over the augmented configuration~($\subhistory$, $\data$), under the target distribution obtained by combining the mapping-based {likelihood} with the {prior} over model parameters.
+    The key idea that makes this strategy efficient is that the mapping-based {likelihood} depends on compact summary statistics of $\subhistory$, leading to a very fast evaluation of the {likelihood}.
+    On the other hand, this requires to implement more complex {MCMC} procedures that have to alternate between:
+    \begin{enumerate}
+        \item sampling $\subhistory$ conditionally on the data and the current parameter configuration.
+        \item re-sampling the parameters conditionally on $\subhistory$.
+    \end{enumerate}
+
+    To implement the mapping-based {MCMC} sampling strategy, we first sample the detailed {substitution} history $\subhistory$ for all sites along the tree.
+    Several methods exist for doing this~\cite{nielsen_mapping_2002,rodrigue_uniformization_2008}, which are used here in combination: first trying the accept-reject method of \textcite{nielsen_mapping_2002}, then switching to the uniformization approach of \textcite{rodrigue_uniformization_2008} if the first round has failed.
+
+    Then, we write down the probability of $\subhistory$ given the parameters, and finally, we collect all factors that depend on some parameter of interest and make some simplifications.
+    This ultimately leads to relatively compact sufficient statistics allowing for fast numerical evaluation of the likelihood~\cite{irvahn_phylogenetic_2014,davydov_state_2017}.
+
+    \subsection{BayesCode software}\label{subsec:bayescode}
+    In \textit{BayesCode} (\href{https://github.com/ThibaultLatrille/BayesCode}{github.com/ThibaultLatrille/BayesCode}, v1.3.1), we ran the mutation-selection codon models \textit{mutselomega} for 2000 points of MCMC with the options:
     \begin{scriptsize}
@@
 
-    \subsection{Summary tables}\label{subsec:summary-table-mutsel}
-
-    \subsubsection{$\dnds$ for deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial back-mutations ($\SphyBen$)}
-    \begin{center}
-        \captionof{table}{$\dnds$ for deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial back-mutations ($\SphyBen$).}
-        \scriptsize
-        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
-            \toprule
-            Population &             Species & Watterson's $\thetaSyn$  & $\proba_{div}[ \SphyBen ]$ & $\dnds $ & $\dn ( \SphyDel ) / \ds$ & $\dn ( \SphyNeu ) / \ds$ & $\dn ( \SphyBen ) / \ds$ \\
-            \midrule
-            \endhead
-            \midrule
-            \multicolumn{8}{r}{{Continued on next page}} \\
-            \midrule
-            \endfoot
-
-            \bottomrule
-            \endlastfoot
-            \rowcolor{LIGHTGREY} Equus c.
-&      Equus caballus &               $ 0.002$ &                    $ 0.118$ &  $ 0.147$ &            $ 0.075$ &                $ 0.823$ &           $ 1.203$ \\
-            Iran &          Bos taurus &               $ 0.002$ &                    $ 0.123$ &  $ 0.131$ &            $ 0.074$ &                $ 0.627$ &           $ 1.206$ \\
-            Uganda &          Bos taurus &               $ 0.005$ &                    $ 0.125$ &  $ 0.134$ &            $ 0.075$ &                $ 0.637$ &           $ 1.252$ \\
-            \rowcolor{LIGHTGREY} Australia &        Capra hircus &               $ 0.003$ &                    $ 0.121$ &  $ 0.125$ &            $ 0.068$ &                $ 0.629$ &           $ 1.099$ \\
-            \rowcolor{LIGHTGREY} France &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.126$ &            $ 0.068$ &                $ 0.633$ &           $ 1.102$ \\
-            \rowcolor{LIGHTGREY} Iran (C.
-aegagrus) &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.125$ &            $ 0.068$ &                $ 0.630$ &           $ 1.100$ \\
-            \rowcolor{LIGHTGREY} Iran &        Capra hircus &               $ 0.004$ &                    $ 0.121$ &  $ 0.125$ &            $ 0.067$ &                $ 0.630$ &           $ 1.108$ \\
-            \rowcolor{LIGHTGREY} Italy &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.126$ &            $ 0.068$ &                $ 0.634$ &           $ 1.102$ \\
-            \rowcolor{LIGHTGREY} Morocco &        Capra hircus &               $ 0.004$ &                    $ 0.122$ &  $ 0.125$ &            $ 0.067$ &                $ 0.631$ &           $ 1.112$ \\
-            Iran &          Ovis aries &               $ 0.007$ &                    $ 0.109$ &  $ 0.146$ &            $ 0.091$ &                $ 0.616$ &           $ 1.148$ \\
-            Iran (O. orientalis) &          Ovis aries &               $ 0.009$ &                    $ 0.108$ &  $ 0.148$ &            $ 0.093$ &                $ 0.617$ &           $ 1.145$ \\
-            Iran (O. vignei) &          Ovis aries &               $ 0.007$ &                    $ 0.109$ &  $ 0.146$ &            $ 0.091$ &                $ 0.617$ &           $ 1.134$ \\
-            Various &          Ovis aries &               $ 0.008$ &                    $ 0.107$ &  $ 0.148$ &            $ 0.093$ &                $ 0.617$ &           $ 1.134$ \\
-            Morocco &          Ovis aries &               $ 0.008$ &                    $ 0.108$ &  $ 0.148$ &            $ 0.093$ &                $ 0.619$ &           $ 1.149$ \\
-            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus &               $ 0.004$ &                    $ 0.122$ &  $ 0.133$ &            $ 0.071$ &                $ 0.696$ &           $ 1.397$ \\
-            \rowcolor{LIGHTGREY} Central Afr.
-Rep.
-& Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.124$ &  $ 0.134$ &            $ 0.071$ &                $ 0.701$ &           $ 1.431$ \\
-            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.124$ &  $ 0.134$ &            $ 0.071$ &                $ 0.699$ &           $ 1.422$ \\
-            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.123$ &  $ 0.134$ &            $ 0.071$ &                $ 0.703$ &           $ 1.411$ \\
-            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.123$ &  $ 0.134$ &            $ 0.071$ &                $ 0.699$ &           $ 1.419$ \\
-            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus &               $ 0.003$ &                    $ 0.123$ &  $ 0.133$ &            $ 0.071$ &                $ 0.699$ &           $ 1.407$ \\
-            \rowcolor{LIGHTGREY} South Africa  & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.125$ &  $ 0.134$ &            $ 0.070$ &                $ 0.704$ &           $ 1.447$ \\
-            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &                    $ 0.123$ &  $ 0.133$ &            $ 0.070$ &                $ 0.699$ &           $ 1.413$ \\
-            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.123$ &  $ 0.134$ &            $ 0.071$ &                $ 0.699$ &           $ 1.410$ \\
-            African &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &            $ 0.118$ &                $ 0.865$ &           $ 1.609$ \\
-            Admixed American &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &            $ 0.118$ &                $ 0.865$ &           $ 1.607$ \\
-            East Asian &        Homo sapiens &               $ 0.002$ &                    $ 0.098$ &  $ 0.192$ &            $ 0.118$ &                $ 0.869$ &           $ 1.607$ \\
-            European &        Homo sapiens &               $ 0.002$ &                    $ 0.098$ &  $ 0.192$ &            $ 0.118$ &                $ 0.865$ &           $ 1.598$ \\
-            South Asian &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &            $ 0.118$ &                $ 0.867$ &           $ 1.610$ \\
-        \end{longtable*}
-    \end{center}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item $\proba_{div}[\SphyBen]$ is the proportion of substitutions in the terminal branch that are $\SphyBen$.
-        \item $\dn(\SphyDel) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are $\SphyDel$.
-        \item $\dn(\SphyNeu) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are $\SphyNeu$.
-        \item $\dn(\SphyBen) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are $\SphyBen$.
-    \end{itemize}
-
-    \newpage
-
-    \subsubsection{$\dnds$ over-estimation due to beneficial back-mutations}
-    \begin{center}
-        \captionof{table}{$\dnds$ over-estimation due to beneficial back-mutations.}
-        \scriptsize
-        \begin{longtable*}{|l|l|r|r|r|r|r|}
-            \toprule
-            Population & Species & Watterson's $\thetaSyn$ & $\proba_{div}[\Sphy > 1]$ & $\dnds $ & $\dn(\Sphy < 1) / \ds$ & $\delta(\dnds )$ \\
-            \midrule
-            \endhead
-            \midrule
-            \multicolumn{7}{r}{{Continued on next page}} \\
-            \midrule
-            \endfoot
-
-            \bottomrule
-            \endlastfoot
-            \rowcolor{LIGHTGREY} Equus c. &      Equus caballus &               $ 0.002$ &                    $ 0.118$ &  $ 0.147$ &           $ 0.131$ &     $  10.5$ \\
-            Iran &          Bos taurus &               $ 0.002$ &                    $ 0.123$ &  $ 0.131$ &           $ 0.117$ &     $  11.1$ \\
-            Uganda &          Bos taurus &               $ 0.005$ &                    $ 0.125$ &  $ 0.134$ &           $ 0.118$ &     $  11.3$ \\
-            \rowcolor{LIGHTGREY} Australia &        Capra hircus &               $ 0.003$ &                    $ 0.121$ &  $ 0.125$ &           $ 0.111$ &     $  10.8$ \\
-            \rowcolor{LIGHTGREY} France &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.126$ &           $ 0.112$ &     $  10.8$ \\
-            \rowcolor{LIGHTGREY} Iran (C. aegagrus) &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.125$ &           $ 0.111$ &     $  10.8$ \\
-            \rowcolor{LIGHTGREY} Iran &        Capra hircus &               $ 0.004$ &                    $ 0.121$ &  $ 0.125$ &           $ 0.111$ &     $  10.9$ \\
-            \rowcolor{LIGHTGREY} Italy &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.126$ &           $ 0.112$ &     $  10.8$ \\
-            \rowcolor{LIGHTGREY} Morocco &        Capra hircus &               $ 0.004$ &                    $ 0.122$ &  $ 0.125$ &           $ 0.111$ &     $  11.0$ \\
-            Iran &          Ovis aries &               $ 0.007$ &                    $ 0.109$ &  $ 0.146$ &           $ 0.132$ &     $ 9.671$ \\
-            Iran (O. orientalis) &          Ovis aries &               $ 0.009$ &                    $ 0.108$ &  $ 0.148$ &           $ 0.134$ &     $ 9.516$ \\
-            Iran (O. vignei) &          Ovis aries &               $ 0.007$ &                    $ 0.109$ &  $ 0.146$ &           $ 0.132$ &     $ 9.598$ \\
-            Various &          Ovis aries &               $ 0.008$ &                    $ 0.107$ &  $ 0.148$ &           $ 0.134$ &     $ 9.439$ \\
-            Morocco &          Ovis aries &               $ 0.008$ &                    $ 0.108$ &  $ 0.148$ &           $ 0.134$ &     $ 9.582$ \\
-            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus &               $ 0.004$ &                    $ 0.122$ &  $ 0.133$ &           $ 0.118$ &     $  11.2$ \\
-            \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.124$ &  $ 0.134$ &           $ 0.119$ &     $  11.3$ \\
-            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.124$ &  $ 0.134$ &           $ 0.118$ &     $  11.3$ \\
-            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.123$ &  $ 0.134$ &           $ 0.119$ &     $  11.2$ \\
-            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.123$ &  $ 0.134$ &           $ 0.119$ &     $  11.3$ \\
-            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus &               $ 0.003$ &                    $ 0.123$ &  $ 0.133$ &           $ 0.118$ &     $  11.3$ \\
-            \rowcolor{LIGHTGREY} South Africa  & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.125$ &  $ 0.134$ &           $ 0.118$ &     $  11.5$ \\
-            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &                    $ 0.123$ &  $ 0.133$ &           $ 0.118$ &     $  11.3$ \\
-            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.123$ &  $ 0.134$ &           $ 0.119$ &     $  11.2$ \\
-            African &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &           $ 0.175$ &     $ 8.799$ \\
-            Admixed American &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &           $ 0.175$ &     $ 8.780$ \\
-            East Asian &        Homo sapiens &               $ 0.002$ &                    $ 0.098$ &  $ 0.192$ &           $ 0.175$ &     $ 8.768$ \\
-            European &        Homo sapiens &               $ 0.002$ &                    $ 0.098$ &  $ 0.192$ &           $ 0.175$ &     $ 8.728$ \\
-            South Asian &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &           $ 0.175$ &     $ 8.788$ \\
-        \end{longtable*}
-    \end{center}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item $\proba_{div}[\SphyBen]$ is the proportion of substitutions in the terminal branch that are $\SphyBen$.
-        \item $\dnds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions estimated for all the non-synonymous substitutions in the terminal branch.
-        \item $\dn(\Sphy < 1) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are not $\SphyBen$.
-        This is the estimated divergence when we removed beneficial back-mutations.
-        \item $\delta(\dnds)$ (eq.~7) is the fraction of the divergence ($\dnds$) that is over-estimated, $\dnds$ is compared to the estimated divergence when we removed beneficial back-mutations $\dn(\Sphy < 1) / \ds$.
-    \end{itemize}
-    We estimated that between 9 and 11\% of $\dnds$ is over-estimated, corresponding to beneficial back-mutation inflating the $\dnds$ statistic.
-
-    \newpage
-
-    \subsubsection{Probabilities of beneficial back-mutations}
-    \begin{center}
-        \captionof{table}{Probability of beneficial back-mutations among all beneficial ones.}
-        \scriptsize
-        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
-            \toprule
-            Population & Species & Watterson's $\thetaSyn$ & $\proba[\SphyBen]$ & $\proba [ \SpopBen ]$ & $\frac{\proba[\SphyBen]}{\proba[ \SpopBen ]}$ & $\proba [ \SpopBen \given \SphyBen]$ & $\proba[\SphyBen\given \SpopBen ]$ \\
-            \midrule
-            \endhead
-            \midrule
-            \multicolumn{8}{r}{{Continued on next page}} \\
-            \midrule
-            \endfoot
-
-            \bottomrule
-            \endlastfoot
-            \rowcolor{LIGHTGREY} Equus c.
-&      Equus caballus &               $ 0.002$ &              $ 0.014$ &              $ 0.010$ &                                          $ 1.395$ &                         $ 0.580$ &                      $ 0.809$ \\
-            Iran &          Bos taurus &               $ 0.002$ &              $ 0.013$ &              $ 0.041$ &                                          $ 0.323$ &                         $ 0.857$ &                      $ 0.277$ \\
-            Uganda &          Bos taurus &               $ 0.005$ &              $ 0.013$ &              $ 0.013$ &                                          $ 0.991$ &                         $ 0.488$ &                      $ 0.483$ \\
-            \rowcolor{LIGHTGREY} Australia &        Capra hircus &               $ 0.003$ &              $ 0.014$ &              $ 0.026$ &                                          $ 0.532$ &                         $ 0.368$ &                      $ 0.196$ \\
-            \rowcolor{LIGHTGREY} France &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.572$ &                         $ 0.368$ &                      $ 0.211$ \\
-            \rowcolor{LIGHTGREY} Iran (C.
-aegagrus) &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.026$ &                                          $ 0.516$ &                         $ 0.221$ &                      $ 0.114$ \\
-            \rowcolor{LIGHTGREY} Iran &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.573$ &                         $ 0.368$ &                      $ 0.211$ \\
-            \rowcolor{LIGHTGREY} Italy &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.017$ &                                          $ 0.814$ &                         $ 0.270$ &                      $ 0.220$ \\
-            \rowcolor{LIGHTGREY} Morocco &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.018$ &                                          $ 0.751$ &                         $ 0.368$ &                      $ 0.276$ \\
-            Iran &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.006$ &                                          $ 2.321$ &                         $ 0.169$ &                      $ 0.392$ \\
-            Iran (O.
-orientalis) &          Ovis aries &               $ 0.009$ &              $ 0.014$ &              $ 0.012$ &                                          $ 1.178$ &                         $ 0.153$ &                      $ 0.180$ \\
-            Iran (O.
-vignei) &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.020$ &                                          $ 0.683$ &                         $ 0.195$ &                      $ 0.133$ \\
-            Various &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.012$ &                                          $ 1.201$ &                         $ 0.190$ &                      $ 0.228$ \\
-            Morocco &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.005$ &                                          $ 2.589$ &                         $ 0.136$ &                      $ 0.353$ \\
-            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.022$ &                                          $ 0.541$ &                         $ 0.565$ &                      $ 0.306$ \\
-            \rowcolor{LIGHTGREY} Central Afr.
-Rep.
-& Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.018$ &                                          $ 0.639$ &                         $ 0.429$ &                      $ 0.274$ \\
-            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.022$ &                                          $ 0.516$ &                         $ 0.462$ &                      $ 0.239$ \\
-            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.007$ &                                          $ 1.592$ &                         $ 0.486$ &                      $ 0.774$ \\
-            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.023$ &                                          $ 0.508$ &                         $ 0.478$ &                      $ 0.243$ \\
-            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus &               $ 0.003$ &              $ 0.012$ &              $ 0.015$ &                                          $ 0.762$ &                         $ 0.516$ &                      $ 0.393$ \\
-            \rowcolor{LIGHTGREY} South Africa  & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.016$ &                                          $ 0.734$ &                         $ 0.490$ &                      $ 0.360$ \\
-            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.016$ &                                          $ 0.713$ &                         $ 0.515$ &                      $ 0.367$ \\
-            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.023$ &                                          $ 0.500$ &                         $ 0.499$ &                      $ 0.249$ \\
-            African &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.025$ &                                          $ 0.470$ &                         $ 0.678$ &                      $ 0.319$ \\
-            Admixed American &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.021$ &                                          $ 0.569$ &                         $ 0.635$ &                      $ 0.361$ \\
-            East Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.031$ &                                          $ 0.381$ &                         $ 0.611$ &                      $ 0.233$ \\
-            European &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.034$ &                                          $ 0.350$ &                         $ 0.619$ &                      $ 0.217$ \\
-            South Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.033$ &                                          $ 0.354$ &                         $ 0.628$ &                      $ 0.222$ \\
-        \end{longtable*}
-    \end{center}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item $\proba [ \SphyBen ]$ (eq.~5) is the probability for a new mutation to be a beneficial back-mutation.
-        These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1, thus toward a more fit amino-acid.
-        \item $\proba [ \SpopBen ]$ (eq.~15) is the probability for a mutation to be beneficial.
-        These mutations have a selection coefficient at the population-scale larger than 1.
-        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale (the \textit{precision}).
-        \item $\proba [ \SphyBen \given \SpopBen]$ (eq.~14) is the probability for a mutation to a beneficial back-mutations, given it is beneficial at the population scale (the \textit{recall}).
-        This probability is obtained using Bayes' formula.
-    \end{itemize}
-    \newpage
-
-    \subsection{Replicability across mammals}
-    The proportion of deleterious ($\ProbaPopDel$), nearly-neutral ($\ProbaPopNeu$) and of beneficial ($\ProbaPopBen$) mutations estimated at the population-genetic scale across the different populations is shown for each class of selection ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$).
-
-    \captionof{figure}{Estimation of selection at the population scale for $\SphyDel$ mutations}
-    \begin{minipage}{0.9\linewidth}
-    \includegraphics[width=\linewidth, page=1]{artworks/Theta.neg.stacked.pdf}
-    \end{minipage}
-    \begin{minipage}{0.09\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
-    \end{minipage}
-
-    \captionof{figure}{Estimation of selection at the population scale for $\SphyNeu$ mutations}
-    \begin{minipage}{0.9\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/Theta.weak.stacked.pdf}
-    \end{minipage}
-    \begin{minipage}{0.09\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
-    \end{minipage}
-
-    \newpage
-    \captionof{figure}{Estimation of selection at the population scale for $\SphyBen$ mutations}
-    \begin{minipage}{0.9\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/Theta.pos.stacked.pdf}
-    \end{minipage}
-    \begin{minipage}{0.09\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
-    \end{minipage}
-
-    \subsection{Correlation with diversity}
-    For each population, the proportion of deleterious ($\ProbaPopDel$), nearly-neutral ($\ProbaPopNeu$) and of beneficial ($\ProbaPopBen$) mutations estimated at the population-genetic scale is shown as function of Watterson's's diversity ($\thetaSyn$).
-
-    \subsubsection{Proportion of deleterious mutations ($\SpopDel$)}\label{subsec:proportion-deleterious-mutations}
-    \captionof{figure}{Proportion of deleterious mutations ($\SpopDel$)}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.all_P-Sneg.scatter.pdf}
-    \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.neg_P-Sneg.scatter.pdf}
-    \end{minipage}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item $\proba [ \SpopDel ]$ (eq.~15) is the probability for a mutation to be deleterious.
-        These mutations have a selection coefficient at the population-scale lower than -1.
-        \item $\proba [ \SpopDel \given \SphyDel ]$ (eq.~12) is the probability for a mutation to be deleterious at the population scale, given it is predicted to be a deleterious at the phylogenetic scale.
-    \end{itemize}
-
-    We can see that higher synonymous diversity ($\thetaSyn$) is typically accompanied by a higher proportion of effectively deleterious mutations at the population scale ($\proba [ \SpopDel ]$).
-    This trend is also confirmed when we restricted the analysis to class of mutations that are supposedly deleterious at the phylogenetic scale ($\SphyDel$).
-    This result is qualitatively in accordance with the nearly-neutral theory of evolution which argues that very slightly deleterious mutations are more efficiently purified in large populations.
-
-    \subsubsection{Proportion of nearly-neutral mutations ($\SpopNeu$)}\label{subsec:proportion-nearly-neutral-mutations}
-    \captionof{figure}{Proportion of nearly-neutral mutations ($\SpopNeu$)}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.all_P-Sweak.scatter.pdf}
-    \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.weak_P-Sweak.scatter.pdf}
-    \end{minipage}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item $\proba [ \SpopNeu ]$ (eq.~15) is the probability for a mutation to be nearly-neutral.
-        These mutations have a selection coefficient at the population-scale between -1 and 1.
-        \item $\proba [ \SpopNeu \given \SphyNeu ]$ (eq.~12) is the probability for a mutation to be nearly-neutral at the population scale, given it is predicted to be a nearly-neutral at the phylogenetic scale.
-    \end{itemize}
-
-    We confirmed that higher synonymous diversity ($\thetaSyn$) is typically accompanied by a smaller proportion of neutral mutations at the population scale ($\proba [ \SpopNeu ]$ in the range 0.06-0.18).
-    This result is more pronounced ($\proba [ \SpopNeu \given \SphyNeu ]$ in the range 0.36-0.73) when we restricted the analysis to class of mutations that are supposedly nearly-neutral at the phylogenetic scale ($\SphyNeu$).
-    This result suggests that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) are more likely to discriminate whether mutations are beneficial or deleterious.
-    Alternatively stated, mutations in populations with low diversity (e.g.~\textit{Homo}) are effectively nearly-neutral and behave as would a neutral mutation.
-    This result is qualitatively in accordance with the nearly-neutral theory of evolution which argues that mutations are less efficiently selected for in small populations.
-
-    \subsubsection{Proportion of beneficial mutations ($\SpopBen$)}\label{subsec:proportion-beneficial-mutations}
-    \captionof{figure}{Proportion of beneficial mutations ($\SpopBen$)}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.all_P-Spos.scatter.pdf}
-    \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.pos_P-Spos.scatter.pdf}
-    \end{minipage}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item $\proba [ \SpopBen ]$ (eq.~15) is the probability for a mutation to be beneficial.
-        These mutations have a selection coefficient at the population-scale larger than 1.
-        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale (the \textit{precision}).
-    \end{itemize}
-    Higher synonymous diversity ($\thetaSyn$) is accompanied by a smaller proportion of beneficial mutations at the population scale ($\proba [ \SpopBen ]$).
-    This trend is also confirmed when we restricted the analysis to class of mutations that are supposedly beneficial back-mutations at the phylogenetic scale ($\SphyBen$).
-    This result is much more difficult to interpret.
-    The fraction of beneficial back mutations is supposed to depend on long term demographic history, which is not directly accessible.
-    If the long term effective population size is relatively similar to the short term one, we expect little opportunity for beneficial back-mutations.
-    And thus, counter-intuitively we expect a diminution of positively selected mutations.
-    However, we can see that the proportion of beneficial back-mutations among advantageous one does not decrease with synonymous diversity.
-    This means that somehow adaptive mutations also decrease with synonymous diversity for a reason we fail to explain.
-
-    \newpage
-
-    \section{Clinically related terms for mutations}
-    \subsection{Terms associated with deleterious mutations $\SphyDel$}
-    \begin{center}
-        \captionof{table}{Terms associated with deleterious mutations $\SphyDel$}
-        \begin{tabular}{|l|r|r|r|r|r|}
-            \toprule
-            SNP clinical ontology & $n_{\mathrm{Observed}}$ & $n_{\mathrm{Expected}}$ & Odds ratio & $p_{\mathrm{v}}$ & $p_{\mathrm{v-adjusted}}$ \\
-            \midrule
-            Benign                & 2969                    & $4043.0$                & $ 0.734$   & $ 1.000$             & $ 1.000~~$                    \\
-            Likely benign         & 2994                    & $3399.8$                & $ 0.881$   & $ 0.999$             & $ 1.000~~$                    \\
-            Risk factor           & 102                     & $ 118.2$                & $ 0.863$   & $ 0.798$             & $ 1.000~~$                    \\
-            Likely pathogenic     & 221                     & $  68.5$                  & $ 3.226$   & $1.7\times 10^{-8}$  & $\bm{6.7\times 10^{-8}{^*}}$  \\
-            Pathogenic            & 560                     & $ 193.6$                & $ 2.893$   & $4.2\times 10^{-17}$ & $\bm{2.1\times 10^{-16}{^*}}$ \\
-            \bottomrule
-        \end{tabular}
-    \end{center}
-    In humans, non-synonymous SNPs in the test group ($\SphyDel$) are contrasted to SNPs in the control group ($\SphyNeu$).
-    For each clinical term, a 2x2 contingency tables is built by counting the number of SNPs based on their selection coefficient and their clinical terms (whether they have this specific term or not).
-    Fisher's exact tests are then performed for these 2x2 contingency tables.
-    $^*$ for $p_{\mathrm{v}}^{\mathrm{adj}}$ corrected for multiple comparison (Holm–Bonferroni correction) lower than the risk $\alpha=0.05$.
-    SNPs predicted with $\SphyDel$ are statistically associated to clinical terms such as \textit{Likely Pathogenic} and \textit{Pathogenic}.
-
-    \subsection{Terms associated with beneficial back-mutations $\SphyBen$}
-    \begin{center}
-        \captionof{table}{Terms associated with beneficial back-mutations $\SphyBen$}
-        \begin{tabular}{|l|r|r|r|r|r|}
-            \toprule
-            SNP clinical ontology & $n_{\mathrm{Observed}}$ & $n_{\mathrm{Expected}}$ & Odds ratio & $p_{\mathrm{v}}$ & $p_{\mathrm{v-adjusted}}$ \\
-            \midrule
-            Benign                & 319                     & $ 261.7$                & $ 1.219$   & $ 0.002$         & $\bm{ 0.009{^*}}$         \\
-            Likely benign         & 263                     & $ 222.7$                & $ 1.181$   & $ 0.012$         & $\bm{ 0.049{^*}}$         \\
-            Risk factor           & 5                       & $ 7.847$                & $ 0.637$   & $ 0.879$         & $ 0.879~~$                \\
-            Likely pathogenic     & 7                       & $ 4.552$                & $ 1.538$   & $ 0.227$         & $ 0.682~~$                \\
-            Pathogenic            & 16                      & $  12.9$                  & $ 1.241$   & $ 0.268$         & $ 0.682~~$                \\
-            \bottomrule
-        \end{tabular}
-    \end{center}
-    In humans, non-synonymous SNPs in the test group ($\SphyBen$) are contrasted to SNPs in the control group ($\SphyNeu$).
-    For each clinical term, a 2x2 contingency tables is built by counting the number of SNPs based on their selection coefficient and their clinical terms (whether they have this specific term or not).
-    Fisher's exact tests are then performed for these 2x2 contingency tables.
-    $^*$ for $p_{\mathrm{v}}^{\mathrm{adj}}$ corrected for multiple comparison (Holm–Bonferroni correction) lower than the risk $\alpha=0.05$.
-    Beneficial back-mutations are associated with clinical terms such as \textit{Benign} and \textit{Likely Benign}.
-    \newpage
-
-    \section{Including divergence data for the estimation of $\Spop$}
-
-    \subsection{Including divergence in polyDFE}
-    Divergence data (number of substitutions per site) can also be included into polyDFE to estimate the DFE.
-    For the class of a given class of selection coefficient ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$), the number of substitutions has already been computed and is given by $D\left( \Sphyclass \right)$ (see eq.~6), and the number of sites is given by $L \left( \Sphyclass \right)$ (see eq.~4).
-    Otherwise, the procedure is the same as described section \textit{Scaled selection coefficients ($\Spop$) in a population-based method}.
-
-    \subsection{Probabilities of beneficial back-mutations}
-    \begin{center}
-        \captionof{table}{Probability of beneficial back-mutations among all beneficial ones.}
-        \scriptsize
-        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
-            \toprule
-            Population & Species & Watterson's $\thetaSyn$ & $\proba[\SphyBen]$ & $\proba [ \SpopBen ]$ & $\frac{\proba[\SphyBen]}{\proba[ \SpopBen ]}$ & $\proba [ \SpopBen \given \SphyBen]$ & $\proba[\SphyBen\given \SpopBen ]$ \\
-            \midrule
-            \endhead
-            \midrule
-            \multicolumn{8}{r}{{Continued on next page}} \\
-            \midrule
-            \endfoot
-
-            \bottomrule
-            \endlastfoot
-            \rowcolor{LIGHTGREY} Equus c.
-&      Equus caballus &               $ 0.002$ &              $ 0.014$ &              $ 0.061$ &                                          $ 0.235$ &                         $ 0.519$ &                      $ 0.122$ \\
-            Iran &          Bos taurus &               $ 0.002$ &              $ 0.013$ &              $ 0.007$ &                                          $ 1.908$ &                         $ 0.368$ &                      $ 0.702$ \\
-            Uganda &          Bos taurus &               $ 0.005$ &              $ 0.013$ &              $ 0.008$ &                                          $ 1.667$ &                         $ 0.255$ &                      $ 0.425$ \\
-            \rowcolor{LIGHTGREY} Australia &        Capra hircus &               $ 0.003$ &              $ 0.014$ &              $ 0.007$ &                                          $ 2.099$ &                         $ 0.147$ &                      $ 0.308$ \\
-            \rowcolor{LIGHTGREY} France &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.007$ &                                          $ 2.043$ &                         $ 0.149$ &                      $ 0.304$ \\
-            \rowcolor{LIGHTGREY} Iran (C.
-aegagrus) &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.013$ &                                          $ 1.069$ &                         $ 0.147$ &                      $ 0.157$ \\
-            \rowcolor{LIGHTGREY} Iran &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.008$ &                                          $ 1.699$ &                         $ 0.152$ &                      $ 0.258$ \\
-            \rowcolor{LIGHTGREY} Italy &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.006$ &                                          $ 2.160$ &                         $ 0.147$ &                      $ 0.316$ \\
-            \rowcolor{LIGHTGREY} Morocco &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.006$ &                                          $ 2.141$ &                         $ 0.186$ &                      $ 0.398$ \\
-            Iran &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.012$ &                                          $ 1.210$ &                         $ 0.158$ &                      $ 0.191$ \\
-            Iran (O.
-orientalis) &          Ovis aries &               $ 0.009$ &              $ 0.014$ &              $ 0.012$ &                                          $ 1.144$ &                         $ 0.157$ &                      $ 0.180$ \\
-            Iran (O.
-vignei) &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.022$ &                                          $ 0.631$ &                         $ 0.186$ &                      $ 0.118$ \\
-            Various &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.012$ &                                          $ 1.211$ &                         $ 0.156$ &                      $ 0.188$ \\
-            Morocco &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.009$ &                                          $ 1.536$ &                         $ 0.190$ &                      $ 0.292$ \\
-            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.005$ &                                          $ 2.230$ &                         $ 0.282$ &                      $ 0.630$ \\
-            \rowcolor{LIGHTGREY} Central Afr.
-Rep.
-& Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.014$ &                                          $ 0.849$ &                         $ 0.310$ &                      $ 0.263$ \\
-            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.008$ &                                          $ 1.530$ &                         $ 0.298$ &                      $ 0.456$ \\
-            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.008$ &                                          $ 1.384$ &                         $ 0.305$ &                      $ 0.422$ \\
-            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.014$ &                                          $ 0.854$ &                         $ 0.296$ &                      $ 0.253$ \\
-            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus &               $ 0.003$ &              $ 0.012$ &              $ 0.005$ &                                          $ 2.438$ &                         $ 0.285$ &                      $ 0.696$ \\
-            \rowcolor{LIGHTGREY} South Africa  & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.011$ &                                          $ 1.047$ &                         $ 0.323$ &                      $ 0.338$ \\
-            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.006$ &                                          $ 2.070$ &                         $ 0.292$ &                      $ 0.604$ \\
-            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.014$ &                                          $ 0.816$ &                         $ 0.309$ &                      $ 0.252$ \\
-            African &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.015$ &                                          $ 0.765$ &                         $ 0.371$ &                      $ 0.284$ \\
-            Admixed American &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.009$ &                                          $ 1.259$ &                         $ 0.368$ &                      $ 0.464$ \\
-            East Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.012$ &                                          $ 0.973$ &                         $ 0.369$ &                      $ 0.358$ \\
-            European &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.009$ &                                          $ 1.356$ &                         $ 0.368$ &                      $ 0.499$ \\
-            South Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.010$ &                                          $ 1.147$ &                         $ 0.369$ &                      $ 0.423$ \\
-        \end{longtable*}
-    \end{center}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item $\proba [ \SphyBen ]$ (eq.~5) is the probability for a new mutation a beneficial back-mutation.
-        These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1, thus toward a more fit amino-acid.
-        \item $\proba [ \SpopBen ]$ (eq.~15) is the probability for a mutation to be beneficial.
-        These mutations have a selection coefficient at the population-scale larger than 1.
-        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale (the \textit{precision}).
-        \item $\proba [ \SphyBen \given \SpopBen]$ (eq.~14) is the probability for a mutation to a beneficial back-mutations, given it is beneficial (the \textit{recall}).
-        This probability is obtained using Bayes' formula.
-    \end{itemize}
-    \newpage
-
-    \subsection{Precision and recall}
-    \captionof{table}{Precision and recall}
-    \begin{center}
-        \begin{adjustbox}{width=\textwidth}
-            \begin{tabular}{||l|l|r||r|r||r|r||r|r||}
-                \toprule
-                \multicolumn{3}{||c||}{} &
-                \multicolumn{2}{c||}{\shortstack{\textbf{Deleterious mutations} \\ $\bm{\SpopDel \coloneqq \Spop<-1}$ \\ $\bm{\SphyDel \coloneqq \Sphy<-1}$}} &
-                \multicolumn{2}{c||}{\shortstack{\textbf{Nearly-neutral mutations} \\ $\bm{\SpopNeu \coloneqq -1<\Spop<1}$ \\ $\bm{\SphyNeu \coloneqq -1<\Sphy<1}$}} &
-                \multicolumn{2}{c||}{\shortstack{\textbf{Beneficial mutations} \\ $\bm{\SpopBen \coloneqq \Spop>1}$ \\ $\bm{\SphyBen \coloneqq \Sphy>1}$}}
-                \\ \hline
-                \textbf{Population} &
-                \textbf{Species} &
-                $\bm{\thetaSyn}$ &
-                \makecell{\textbf{Precision} \\ $\bm{\proba [\SpopDel \given \SphyDel]}$} &
-                \makecell{\textbf{Recall} \\ $\bm{\proba [\SphyDel \given \SpopDel]}$}           &
-                \makecell{\textbf{Precision}      \\ $\bm{\proba [\SpopNeu \given \SphyNeu]}$}                                    &
-                \makecell{\textbf{Recall}          \\ $\bm{\proba [\SphyNeu \given \SpopNeu]}$}                                  &
-                \makecell{\textbf{Precision}          \\ $\bm{\proba [\SpopBen \given \SphyBen]}$}          &
-                \makecell{\textbf{Recall}        \\ $\bm{\proba [\SphyBen \given \SpopBen]}$}
-                \\   \midrule
-                \rowcolor{LIGHTGREY} Equus c. & Equus caballus        & $ 0.002$ & $ 0.918$ & $ 0.957$ & $ 0.186$ & $ 0.213$ & $ 0.519$ & $ 0.122$ \\
-                Iran               & Bos taurus        & $ 0.002$ & $ 0.924$ & $ 0.965$ & $ 0.565$ & $ 0.356$ & $ 0.368$ & $ 0.702$ \\
-                Uganda              & Bos taurus        & $ 0.005$ & $ 0.943$ & $ 0.961$ & $ 0.516$ & $ 0.396$ & $ 0.255$ & $ 0.425$ \\
-                \rowcolor{LIGHTGREY} Australia            & Capra hircus        & $ 0.003$ & $ 0.941$ & $ 0.964$ & $ 0.592$ & $ 0.434$ & $ 0.147$ & $ 0.308$ \\
-                \rowcolor{LIGHTGREY} France                                    & Capra hircus          & $ 0.004$ & $ 0.940$ & $ 0.963$ & $ 0.571$ & $ 0.418$ & $ 0.149$ & $ 0.304$ \\
-                \rowcolor{LIGHTGREY} Iran (C. aegagrus)                    & Capra hircus          & $ 0.004$ & $ 0.948$ & $ 0.960$ & $ 0.515$ & $ 0.446$ & $ 0.147$ & $ 0.157$ \\
-                \rowcolor{LIGHTGREY} Iran                        & Capra hircus          & $ 0.004$ & $ 0.942$ & $ 0.961$ & $ 0.534$ & $ 0.410$ & $ 0.152$ & $ 0.258$ \\
-                \rowcolor{LIGHTGREY} Italy                                 & Capra hircus          & $ 0.004$ & $ 0.940$ & $ 0.963$ & $ 0.579$ & $ 0.421$ & $ 0.147$ & $ 0.316$ \\
-                \rowcolor{LIGHTGREY} Morocco                                 & Capra hircus          & $ 0.004$ & $ 0.939$ & $ 0.960$ & $ 0.549$ & $ 0.404$ & $ 0.186$ & $ 0.398$ \\
-                Iran           & Ovis aries & $ 0.007$ & $ 0.957$ & $ 0.954$ & $ 0.412$ & $ 0.416$ & $ 0.158$ & $ 0.191$ \\
-                Iran (O. orientalis)  & Ovis aries & $ 0.009$ & $ 0.961$ & $ 0.955$ & $ 0.413$ & $ 0.437$ & $ 0.157$ & $ 0.180$ \\
-                Iran (O. vignei)           & Ovis aries & $ 0.007$ & $ 0.968$ & $ 0.951$ & $ 0.356$ & $ 0.516$ & $ 0.186$ & $ 0.118$ \\
-                Various             & Ovis aries & $ 0.008$ & $ 0.958$ & $ 0.955$ & $ 0.428$ & $ 0.431$ & $ 0.156$ & $ 0.188$ \\
-                Morocco              & Ovis aries & $ 0.008$ & $ 0.960$ & $ 0.953$ & $ 0.447$ & $ 0.460$ & $ 0.190$ & $ 0.292$ \\
-                \rowcolor{LIGHTGREY} Barbados              & Chlorocebus sabaeus & $ 0.004$ & $ 0.931$ & $ 0.969$ & $ 0.628$ & $ 0.402$ & $ 0.282$ & $ 0.630$ \\
-                \rowcolor{LIGHTGREY} Central Afr. Rep.       & Chlorocebus sabaeus & $ 0.006$ & $ 0.941$ & $ 0.964$ & $ 0.514$ & $ 0.408$ & $ 0.310$ & $ 0.263$ \\
-                \rowcolor{LIGHTGREY} Ethiopia        & Chlorocebus sabaeus & $ 0.005$ & $ 0.933$ & $ 0.967$ & $ 0.586$ & $ 0.393$ & $ 0.298$ & $ 0.456$ \\
-                \rowcolor{LIGHTGREY} Gambia             & Chlorocebus sabaeus & $ 0.005$ & $ 0.937$ & $ 0.967$ & $ 0.590$ & $ 0.414$ & $ 0.305$ & $ 0.422$ \\
-                \rowcolor{LIGHTGREY} Kenya                                 & Chlorocebus sabaeus        & $ 0.005$ & $ 0.942$ & $ 0.965$ & $ 0.526$ & $ 0.418$ & $ 0.296$ & $ 0.253$ \\
-                \rowcolor{LIGHTGREY} Nevis                        & Chlorocebus sabaeus        & $ 0.003$ & $ 0.930$ & $ 0.970$ & $ 0.637$ & $ 0.401$ & $ 0.285$ & $ 0.696$ \\
-                \rowcolor{LIGHTGREY} South Africa                              & Chlorocebus sabaeus        & $ 0.006$ & $ 0.937$ & $ 0.964$ & $ 0.530$ & $ 0.393$ & $ 0.323$ & $ 0.338$ \\
-                \rowcolor{LIGHTGREY} Saint Kitts                                & Chlorocebus sabaeus        & $ 0.004$ & $ 0.931$ & $ 0.969$ & $ 0.611$ & $ 0.393$ & $ 0.292$ & $ 0.604$ \\
-                \rowcolor{LIGHTGREY} Zambia                             & Chlorocebus sabaeus        & $ 0.006$ & $ 0.941$ & $ 0.963$ & $ 0.506$ & $ 0.408$ & $ 0.309$ & $ 0.252$ \\
-                African                             & Homo sapiens        & $ 0.002$ & $ 0.896$ & $ 0.968$ & $ 0.550$ & $ 0.297$ & $ 0.371$ & $ 0.284$ \\
-                Admixed American                             & Homo sapiens        & $ 0.002$ & $ 0.890$ & $ 0.979$ & $ 0.710$ & $ 0.333$ & $ 0.368$ & $ 0.464$ \\
-                East Asian                             & Homo sapiens        & $ 0.002$ & $ 0.890$ & $ 0.971$ & $ 0.578$ & $ 0.289$ & $ 0.369$ & $ 0.358$ \\
-                European                             & Homo sapiens        & $ 0.002$ & $ 0.891$ & $ 0.980$ & $ 0.739$ & $ 0.345$ & $ 0.368$ & $ 0.499$ \\
-                South Asian                             & Homo sapiens        & $ 0.002$ & $ 0.895$ & $ 0.981$ & $ 0.740$ & $ 0.356$ & $ 0.369$ & $ 0.423$ \\
-                \bottomrule
-            \end{tabular}
-        \end{adjustbox}
-    \end{center}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item \textit{Precision} is the estimation of the selection coefficient at population scale ($\Spop$) given that $\Sphy$ is known.
-        \item  \textit{Recall} is the estimation of $\Sphy$ given selection coefficient at the population scale ($\Spop$) is known.
-        \item \textit{Recall} for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is thus the proportion of beneficial back-mutations among all beneficial mutations.
-    \end{itemize}
-
-    Altogether, comparing this table to tables 1 and S3, we acknowledge that the exact proportion of beneficial back-mutations among all beneficial ones is different whether we included or not substitutions in the terminal lineage for the estimation of $\Spop$.
-    However, we can still see that beneficial back-mutations are positively selected compared to neutral and deleterious ones, and this result is not sensitive to inclusion of substitutions in the terminal lineage.
-
-    \newpage
-    \section{Discrete distribution of $\Spop$ at the population scale}
-
-    \subsection{polyDFE model D (discrete distribution)}
-    With polyDFE model D, the DFE of non-synonymous mutations is given as a discrete DFE of $K$ categories (instead of a continuous distribution in model C), where the selection coefficients of each category $i$ ($1 \leq i \leq K$) are fixed parameters $\Spop_i$, and each value $\Spop_i$ has a probability $p_i$ (estimated), with $\sum_{i=1}^{K} p_i =1$.
-    We used $K=6$ with $\Spop_1 = -500$, $\Spop_2 = -4$, $\Spop_3 =-1$, $\Spop_4 = 0$, $\Spop_5 = 1$, $\Spop_6 = 4$.\\
-    For each class of selection $\Sphyclass$, the parameters $p_i$ ($i \in \{ 1 \leq i \leq 6 \}$) were used to compute $\proba [ \SpopDel \given  \Sphyclass] $, $\proba [ \SpopNeu \given \Sphyclass]$, and $\proba [ \SpopBen \given \Sphyclass]$ as:
-    \begin{align}
-        \proba [ \SpopDel \given  \Sphyclass] &= \proba [ \Spop < -1 \given \Sphyclass ] = p_1 + p_2 \label{eq:polyProbaDel} \\
-        \proba [ \SpopNeu \given \Sphyclass] &= \proba [ -1 < \Spop < 1 \given \Sphyclass ] = p_3 + p_4 + p_5,  \\
-        \proba [ \SpopBen \given \Sphyclass] &= p_6. \label{eq:polyProbaAdv}
-    \end{align}
-
-    \subsection{Probabilities of beneficial back-mutations}
-    \begin{center}
-        \captionof{table}{Probability of beneficial back-mutations among all beneficial ones.}
-        \scriptsize
-        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
-            \toprule
-            Population & Species & Watterson's $\thetaSyn$ & $\proba[\SphyBen]$ & $\proba [ \SpopBen ]$ & $\frac{\proba[\SphyBen]}{\proba[ \SpopBen ]}$ & $\proba [ \SpopBen \given \SphyBen]$ & $\proba[\SphyBen\given \SpopBen ]$ \\
-            \midrule
-            \endhead
-            \midrule
-            \multicolumn{8}{r}{{Continued on next page}} \\
-            \midrule
-            \endfoot
-
-            \bottomrule
-            \endlastfoot
-            \rowcolor{LIGHTGREY} Equus c.
-&      Equus caballus &               $ 0.002$ &              $ 0.014$ &              $ 0.006$ &                                          $ 2.230$ &                         $ 0.141$ &                      $ 0.316$ \\
-            Iran &          Bos taurus &               $ 0.002$ &              $ 0.013$ &              $ 0.006$ &                                          $ 2.200$ &                         $ 0.136$ &                      $ 0.298$ \\
-            Uganda &          Bos taurus &               $ 0.005$ &              $ 0.013$ &              $ 0.011$ &                                          $ 1.177$ &                         $ 0.138$ &                      $ 0.162$ \\
-            \rowcolor{LIGHTGREY} Australia &        Capra hircus &               $ 0.003$ &              $ 0.014$ &              $ 0.002$ &                                          $ 6.467$ &                         $ 0.135$ &                      $ 0.871$ \\
-            \rowcolor{LIGHTGREY} France &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.002$ &                                          $ 6.407$ &                         $ 0.132$ &                      $ 0.845$ \\
-            \rowcolor{LIGHTGREY} Iran (C.
-aegagrus) &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.002$ &                                          $ 5.993$ &                         $ 0.129$ &                      $ 0.772$ \\
-            \rowcolor{LIGHTGREY} Iran &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.004$ &                                          $ 3.656$ &                         $ 0.138$ &                      $ 0.506$ \\
-            \rowcolor{LIGHTGREY} Italy &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.002$ &                                          $ 6.216$ &                         $ 0.127$ &                      $ 0.787$ \\
-            \rowcolor{LIGHTGREY} Morocco &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.002$ &                                          $ 6.019$ &                         $ 0.141$ &                      $ 0.848$ \\
-            Iran &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.588$ &                         $ 0.148$ &                      $ 0.087$ \\
-            Iran (O.
-orientalis) &          Ovis aries &               $ 0.009$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.569$ &                         $ 0.143$ &                      $ 0.081$ \\
-            Iran (O.
-vignei) &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.587$ &                         $ 0.127$ &                      $ 0.075$ \\
-            Various &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.588$ &                         $ 0.146$ &                      $ 0.086$ \\
-            Morocco &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.025$ &                                          $ 0.564$ &                         $ 0.145$ &                      $ 0.082$ \\
-            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.002$ &                                          $ 5.689$ &                         $ 0.170$ &                      $ 0.968$ \\
-            \rowcolor{LIGHTGREY} Central Afr.
-Rep.
-& Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.005$ &                                          $ 2.142$ &                         $ 0.156$ &                      $ 0.334$ \\
-            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.002$ &                                          $ 5.910$ &                         $ 0.160$ &                      $ 0.945$ \\
-            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.006$ &                                          $ 1.850$ &                         $ 0.157$ &                      $ 0.290$ \\
-            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.004$ &                                          $ 2.802$ &                         $ 0.163$ &                      $ 0.456$ \\
-            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus &               $ 0.003$ &              $ 0.012$ &              $ 0.002$ &                                          $ 5.396$ &                         $ 0.169$ &                      $ 0.910$ \\
-            \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.005$ &                                          $ 2.154$ &                         $ 0.153$ &                      $ 0.329$ \\
-            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.002$ &                                          $ 5.094$ &                         $ 0.164$ &                      $ 0.834$ \\
-            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.006$ &                                          $ 1.952$ &                         $ 0.153$ &                      $ 0.298$ \\
-            African &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.014$ &                                          $ 0.869$ &                         $ 0.141$ &                      $ 0.123$ \\
-            Admixed American &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.010$ &                                          $ 1.130$ &                         $ 0.161$ &                      $ 0.182$ \\
-            East Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.007$ &                                          $ 1.602$ &                         $ 0.162$ &                      $ 0.259$ \\
-            European &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.009$ &                                          $ 1.336$ &                         $ 0.163$ &                      $ 0.217$ \\
-            South Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.009$ &                                          $ 1.342$ &                         $ 0.163$ &                      $ 0.219$ \\
-        \end{longtable*}
-    \end{center}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item $\proba [ \SphyBen ]$ (eq.~5) is the probability for a new mutation a beneficial back-mutation.
-        These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1, thus toward a more fit amino-acid.
-        \item $\proba [ \SpopBen ]$ (eq.~15) is the probability for a mutation to be beneficial.
-        These mutations have a selection coefficient at the population-scale larger than 1.
-        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale (the \textit{precision}).
-        \item $\proba [ \SphyBen \given \SpopBen]$ (eq.~14) is the probability for a mutation to a beneficial back-mutations, given it is beneficial (the \textit{recall}).
-        This probability is obtained using Bayes' formula.
-    \end{itemize}
-    \newpage
-
-    \subsection{Precision and recall}
-    \captionof{table}{Precision and recall}
-    \begin{center}
-        \begin{adjustbox}{width=\textwidth}
-            \begin{tabular}{||l|l|r||r|r||r|r||r|r||}
-                \toprule
-                \multicolumn{3}{||c||}{} &
-                \multicolumn{2}{c||}{\shortstack{\textbf{Deleterious mutations} \\ $\bm{\SpopDel \coloneqq \Spop<-1}$ \\ $\bm{\SphyDel \coloneqq \Sphy<-1}$}} &
-                \multicolumn{2}{c||}{\shortstack{\textbf{Nearly-neutral mutations} \\ $\bm{\SpopNeu \coloneqq -1<\Spop<1}$ \\ $\bm{\SphyNeu \coloneqq -1<\Sphy<1}$}} &
-                \multicolumn{2}{c||}{\shortstack{\textbf{Beneficial mutations} \\ $\bm{\SpopBen \coloneqq \Spop>1}$ \\ $\bm{\SphyBen \coloneqq \Sphy>1}$}}
-                \\ \hline
-                \textbf{Population} &
-                \textbf{Species} &
-                $\bm{\thetaSyn}$ &
-                \makecell{\textbf{Precision} \\ $\bm{\proba [\SpopDel \given \SphyDel]}$} &
-                \makecell{\textbf{Recall} \\ $\bm{\proba [\SphyDel \given \SpopDel]}$}           &
-                \makecell{\textbf{Precision}      \\ $\bm{\proba [\SpopNeu \given \SphyNeu]}$}                                    &
-                \makecell{\textbf{Recall}          \\ $\bm{\proba [\SphyNeu \given \SpopNeu]}$}                                  &
-                \makecell{\textbf{Precision}          \\ $\bm{\proba [\SpopBen \given \SphyBen]}$}          &
-                \makecell{\textbf{Recall}        \\ $\bm{\proba [\SphyBen \given \SpopBen]}$}
-                \\   \midrule
-                \rowcolor{LIGHTGREY} Equus c. & Equus caballus        & $ 0.002$ & $ 0.895$ & $ 0.969$ & $ 0.645$ & $ 0.315$ & $ 0.141$ & $ 0.316$ \\
-                Iran               & Bos taurus        & $ 0.002$ & $ 0.878$ & $ 0.968$ & $ 0.632$ & $ 0.286$ & $ 0.136$ & $ 0.298$ \\
-                Uganda              & Bos taurus        & $ 0.005$ & $ 0.951$ & $ 0.963$ & $ 0.597$ & $ 0.508$ & $ 0.138$ & $ 0.162$ \\
-                \rowcolor{LIGHTGREY} Australia            & Capra hircus        & $ 0.003$ & $ 0.895$ & $ 0.981$ & $ 0.830$ & $ 0.379$ & $ 0.135$ & $ 0.871$ \\
-                \rowcolor{LIGHTGREY} France                                    & Capra hircus          & $ 0.004$ & $ 0.896$ & $ 0.978$ & $ 0.801$ & $ 0.373$ & $ 0.132$ & $ 0.845$ \\
-                \rowcolor{LIGHTGREY} Iran (C. aegagrus)                    & Capra hircus          & $ 0.004$ & $ 0.913$ & $ 0.971$ & $ 0.711$ & $ 0.383$ & $ 0.129$ & $ 0.772$ \\
-                \rowcolor{LIGHTGREY} Iran                        & Capra hircus          & $ 0.004$ & $ 0.949$ & $ 0.968$ & $ 0.655$ & $ 0.481$ & $ 0.138$ & $ 0.506$ \\
-                \rowcolor{LIGHTGREY} Italy                                 & Capra hircus          & $ 0.004$ & $ 0.894$ & $ 0.979$ & $ 0.814$ & $ 0.373$ & $ 0.127$ & $ 0.787$ \\
-                \rowcolor{LIGHTGREY} Morocco                                 & Capra hircus          & $ 0.004$ & $ 0.951$ & $ 0.972$ & $ 0.709$ & $ 0.504$ & $ 0.141$ & $ 0.848$ \\
-                Iran           & Ovis aries & $ 0.007$ & $ 0.980$ & $ 0.956$ & $ 0.456$ & $ 0.799$ & $ 0.148$ & $ 0.087$ \\
-                Iran (O. orientalis)  & Ovis aries & $ 0.009$ & $ 0.979$ & $ 0.955$ & $ 0.454$ & $ 0.798$ & $ 0.143$ & $ 0.081$ \\
-                Iran (O. vignei)           & Ovis aries & $ 0.007$ & $ 0.974$ & $ 0.957$ & $ 0.483$ & $ 0.729$ & $ 0.127$ & $ 0.075$ \\
-                Various             & Ovis aries & $ 0.008$ & $ 0.979$ & $ 0.958$ & $ 0.500$ & $ 0.813$ & $ 0.146$ & $ 0.086$ \\
-                Morocco              & Ovis aries & $ 0.008$ & $ 0.980$ & $ 0.952$ & $ 0.392$ & $ 0.774$ & $ 0.145$ & $ 0.082$ \\
-                \rowcolor{LIGHTGREY} Barbados              & Chlorocebus sabaeus & $ 0.004$ & $ 0.880$ & $ 0.984$ & $ 0.854$ & $ 0.354$ & $ 0.170$ & $ 0.968$ \\
-                \rowcolor{LIGHTGREY} Central Afr. Rep.       & Chlorocebus sabaeus & $ 0.006$ & $ 0.932$ & $ 0.968$ & $ 0.634$ & $ 0.413$ & $ 0.156$ & $ 0.334$ \\
-                \rowcolor{LIGHTGREY} Ethiopia        & Chlorocebus sabaeus & $ 0.005$ & $ 0.877$ & $ 0.980$ & $ 0.810$ & $ 0.337$ & $ 0.160$ & $ 0.945$ \\
-                \rowcolor{LIGHTGREY} Gambia             & Chlorocebus sabaeus & $ 0.005$ & $ 0.947$ & $ 0.977$ & $ 0.745$ & $ 0.518$ & $ 0.157$ & $ 0.290$ \\
-                \rowcolor{LIGHTGREY} Kenya                                 & Chlorocebus sabaeus        & $ 0.005$ & $ 0.903$ & $ 0.969$ & $ 0.664$ & $ 0.343$ & $ 0.163$ & $ 0.456$ \\
-                \rowcolor{LIGHTGREY} Nevis                        & Chlorocebus sabaeus        & $ 0.003$ & $ 0.880$ & $ 0.984$ & $ 0.861$ & $ 0.357$ & $ 0.169$ & $ 0.910$ \\
-                \rowcolor{LIGHTGREY} South Africa                              & Chlorocebus sabaeus        & $ 0.006$ & $ 0.931$ & $ 0.967$ & $ 0.615$ & $ 0.401$ & $ 0.153$ & $ 0.329$ \\
-                \rowcolor{LIGHTGREY} Saint Kitts                                & Chlorocebus sabaeus        & $ 0.004$ & $ 0.883$ & $ 0.982$ & $ 0.834$ & $ 0.355$ & $ 0.164$ & $ 0.834$ \\
-                \rowcolor{LIGHTGREY} Zambia                             & Chlorocebus sabaeus        & $ 0.006$ & $ 0.896$ & $ 0.969$ & $ 0.659$ & $ 0.332$ & $ 0.153$ & $ 0.298$ \\
-                African                             & Homo sapiens        & $ 0.002$ & $ 0.946$ & $ 0.971$ & $ 0.630$ & $ 0.486$ & $ 0.141$ & $ 0.123$ \\
-                Admixed American                             & Homo sapiens        & $ 0.002$ & $ 0.929$ & $ 0.972$ & $ 0.636$ & $ 0.410$ & $ 0.161$ & $ 0.182$ \\
-                East Asian                             & Homo sapiens        & $ 0.002$ & $ 0.937$ & $ 0.973$ & $ 0.647$ & $ 0.429$ & $ 0.162$ & $ 0.259$ \\
-                European                             & Homo sapiens        & $ 0.002$ & $ 0.937$ & $ 0.973$ & $ 0.643$ & $ 0.433$ & $ 0.163$ & $ 0.217$ \\
-                South Asian                             & Homo sapiens        & $ 0.002$ & $ 0.939$ & $ 0.972$ & $ 0.639$ & $ 0.439$ & $ 0.163$ & $ 0.219$ \\
-                \bottomrule
-            \end{tabular}
-        \end{adjustbox}
-    \end{center}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item \textit{Precision} is the estimation of the selection coefficient at population scale ($\Spop$) given that $\Sphy$ is known.
-        \item \textit{Recall} is the estimation of $\Sphy$ given selection coefficient at the population scale ($\Spop$) is known.
-        \item \textit{Recall} for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is thus the proportion of beneficial back-mutations among all beneficial mutations.
-    \end{itemize}
-
-    Altogether, comparing this table to tables 1 and S3, we acknowledge that the exact proportion of beneficial back-mutations among all beneficial ones is dependent on the model used to estimate the DFE.
-    However, we can still see that beneficial back-mutations are positively selected compared to neutral and deleterious ones, and this result is not sensitive to the underlying DFE at the population scale.
-
-    %\section{References}
-    %\printbibliography[heading=none]
-
-    %    \section{Distribution of fitness effects}
-    %    \captionof{figure}{~}
-    %    \begin{minipage}{0.49\linewidth}
-    %        \includegraphics[width=\linewidth, page=1]{artworks/2bins.Yeast.experimentalDFE.pdf}
-    %    \end{minipage}
-    %    \begin{minipage}{0.49\linewidth}
-    %        \includegraphics[width=\linewidth, page=1]{artworks/2bins.AFR.histogramDFE.pdf}
-    %    \end{minipage}
-    %    Left panel: distribution of fitness effects experimentally determined in Yeast, data obtained in \textcite{shen_synonymous_2022}.
-    %    Right panel:  distribution of fitness effects ($\Sphy$) as predicted with mutation-selection codon models, from reconstructed ancestral genome in \textit{Homo sapiens}.
-    %    The DFE predicted with mutation-selection codon models has a negative mode, consistently with experimental DFEs, meaning that most mutations are effectively deleterious.
+    \printbibliography
 \end{document}

### 2024-12-16 manuscript/S2 File.tex
Split Supplementary materials into 4 files.

--- 2023-05-03 manuscript/supp-mat.tex
@@
     \maketitle
-    \part*{Supplementary materials}
+    \part*{S2 File}
+    \vspace{-1em}
     \tableofcontents
-    \clearpage
-
+    \newpage
+    \listoffigures
+    \listoftables
+    \newpage
     \section{Beneficial mutations in the terminal lineages and populations}\label{sec:beneficial-mutations}
 
-    \subsection{Mutation-selection codon models}
-    \label{sec:site-specific-mutation-selection-codon-models}
-    In \textit{BayesCode} (\url{https://github.com/ThibaultLatrille/bayescode}), we ran the mutation-selection codon models \textit{mutselomega} for 2000 points of MCMC with the options:
-    \begin{scriptsize}
-        \begin{verbatim}
- mutselomega ---omegashift 0.0 --ncat 30 -a my_alignment.phy -t my_tree.newick -u 2000 my_genename
-        \end{verbatim}
-    \end{scriptsize}
-    The collection of site-specific fitness profiles ($\UniDimArray{F^{(i)}}, \forall i$) are then obtained by running \textit{readmutselomega}, reading 1000 points of MCMC (first 1000 are considered as burn-in) with the options:
-    \begin{scriptsize}
-        \begin{verbatim}
- readmutselomega --every 1 --until 2000 --burnin 1000 --ss my_genename
-        \end{verbatim}
-    \end{scriptsize}
-    The gene-specific $4 \times 4$ nucleotide mutation rate matrix ($\UniDimArray{\mu}$) is also obtained by running \textit{readmutselomega}, reading 1000 points of MCMC (first 1000 are considered as burn-in) with the options:
-    \begin{scriptsize}
-        \begin{verbatim}
- readmutselomega --every 1 --until 2000 --burnin 1000 --nuc my_genename
-        \end{verbatim}
-    \end{scriptsize}
+    \subsection{Example sites}\label{subsec:example-sites}
 
-    \subsection{Summary tables}\label{subsec:summary-table-mutsel}
+    We extracted protein-coding DNA alignments across mammals centered around the codon site (two flanking codons in white background) for which the beneficial non-adaptive mutations ($\SphyBen$) have been detected in \textit{Chlorocebus sabaeus}.
+    We also show the translated amino acids of this region.
+    For instance, in DNA alignment of gene SELE (\ref{fig:example-1}), the nucleotide at site 1722 has mutated (from T to C) at the basis of Simiiformes (monkeys and apes), modifying the corresponding amino acid from Serine to Proline, but has been subsequently reverted in the branch of \textit{Chlorocebus sabaeus}.
+    However, other substitutions classified as $\SphyBen$ cannot be clearly interpreted as reversions \textit{sensu stricto} along the terminal branch of \textit{Chlorocebus sabaeus}.
+    Indeed, we acknowledge that on a fixed fitness landscape, a deleterious mutation can be compensated by transitions to other fitter amino-acids, and not necessarily the ancestral one.
 
-    \subsubsection{$\dnds$ for deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial back-mutations ($\SphyBen$)}
+    Finally, we generated the fasta alignment for all $\SphyBen$ mutations that we detected, either in the terminal lineage or in segregating polymorphisms.
+    These fasta files are available at Zenodo (\url{https://doi.org/10.5281/zenodo.7878953}), across all populations, under a zip file (\textit{alignment\_around\_non\_adaptive\_mutations.zip}) alongside a python script to obtain the figures (as in Figures~\ref{fig:example-1} and~\ref{fig:example-2}) given these alignments (\textit{plot\_variations.py}).
+
+    \newpage
     \begin{center}
-        \captionof{table}{$\dnds$ for deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial back-mutations ($\SphyBen$).}
+        \includegraphics[width=0.9\linewidth, page=1]{artworks/Alignment.Chlorocebus_sabaeus.Saint_Kitts-0.pdf}
+        \captionof{figure}[Examples sites of $\SphyBen$ mutations in \textit{Chlorocebus sabaeus} (reversions).]{\textbf{Examples sites of $\bm{\SphyBen}$ mutations in \textit{Chlorocebus sabaeus}  (reversions).} The first line is the name of the gene, the second line the position of the mutation in the OrthoMam protein-coding DNA alignment, and the arrows in the third line correspond to the position of the mutation in the nucleotide sequence (left) and in the corresponding amino acid sequence (right)\label{fig:example-1}}
+    \end{center}
+
+    \newpage
+    \begin{center}
+        \includegraphics[width=0.9\linewidth, page=1]{artworks/Alignment.Chlorocebus_sabaeus.Saint_Kitts-1.pdf}
+        \captionof{figure}[Examples sites of $\SphyBen$ mutations in \textit{Chlorocebus sabaeus}.]{\textbf{Examples sites of $\bm{\SphyBen}$ mutations in \textit{Chlorocebus sabaeus}.} The first line is the name of the gene, the second line the position of the mutation in the OrthoMam protein-coding DNA alignment, and the arrows in the third line correspond to the position of the mutation in the nucleotide sequence (left) and in the corresponding amino acid sequence (right).\label{fig:example-2}}
+    \end{center}
+
+    \newpage
+    \subsection{Selection along the terminal branches}\label{subsec:summary-table-mutsel}
+
+    \subsubsection{Probability of mutations and substitutions to be \texorpdfstring{$\SphyDel$}{D₀}, \texorpdfstring{$\SphyNeu$}{N₀} or \texorpdfstring{$\SphyBen$}{B₀}}
+    Among all the substitutions found in each terminal branch, between 10 and 13\% were $\SphyBen$ ($\proba_{div}[ \SphyBen {]}$), while $\SphyBen$ mutations only represent between 0.9 and 1.2\% of all non-synonymous mutations ($\proba[ \SphyBen {]}$), as shown in Table~\ref{table:pdiv}.
+
+    \begin{center}
         \scriptsize
@@
             \toprule
-            Population &             Species & Watterson's $\thetaSyn$  & $\proba_{div}[ \SphyBen ]$ & $\dnds $ & $\dn ( \SphyDel ) / \ds$ & $\dn ( \SphyNeu ) / \ds$ & $\dn ( \SphyBen ) / \ds$ \\
+            Population &             Species & $\proba{[} \SphyDel {]}$ & $\proba{[} \SphyNeu {]}$ & $\proba{[} \SphyBen {]}$ & $\proba_{div}[ \SphyDel {]}$ & $\proba_{div}[ \SphyNeu {]}$ & $\proba_{div}[ \SphyBen {]}$ \\
             \midrule
@@
             \endlastfoot
-            \rowcolor{LIGHTGREY} Equus c.
-&      Equus caballus &               $ 0.002$ &                    $ 0.118$ &  $ 0.147$ &            $ 0.075$ &                $ 0.823$ &           $ 1.203$ \\
-            Iran &          Bos taurus &               $ 0.002$ &                    $ 0.123$ &  $ 0.131$ &            $ 0.074$ &                $ 0.627$ &           $ 1.206$ \\
-            Uganda &          Bos taurus &               $ 0.005$ &                    $ 0.125$ &  $ 0.134$ &            $ 0.075$ &                $ 0.637$ &           $ 1.252$ \\
-            \rowcolor{LIGHTGREY} Australia &        Capra hircus &               $ 0.003$ &                    $ 0.121$ &  $ 0.125$ &            $ 0.068$ &                $ 0.629$ &           $ 1.099$ \\
-            \rowcolor{LIGHTGREY} France &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.126$ &            $ 0.068$ &                $ 0.633$ &           $ 1.102$ \\
-            \rowcolor{LIGHTGREY} Iran (C.
-aegagrus) &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.125$ &            $ 0.068$ &                $ 0.630$ &           $ 1.100$ \\
-            \rowcolor{LIGHTGREY} Iran &        Capra hircus &               $ 0.004$ &                    $ 0.121$ &  $ 0.125$ &            $ 0.067$ &                $ 0.630$ &           $ 1.108$ \\
-            \rowcolor{LIGHTGREY} Italy &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.126$ &            $ 0.068$ &                $ 0.634$ &           $ 1.102$ \\
-            \rowcolor{LIGHTGREY} Morocco &        Capra hircus &               $ 0.004$ &                    $ 0.122$ &  $ 0.125$ &            $ 0.067$ &                $ 0.631$ &           $ 1.112$ \\
-            Iran &          Ovis aries &               $ 0.007$ &                    $ 0.109$ &  $ 0.146$ &            $ 0.091$ &                $ 0.616$ &           $ 1.148$ \\
-            Iran (O. orientalis) &          Ovis aries &               $ 0.009$ &                    $ 0.108$ &  $ 0.148$ &            $ 0.093$ &                $ 0.617$ &           $ 1.145$ \\
-            Iran (O. vignei) &          Ovis aries &               $ 0.007$ &                    $ 0.109$ &  $ 0.146$ &            $ 0.091$ &                $ 0.617$ &           $ 1.134$ \\
-            Various &          Ovis aries &               $ 0.008$ &                    $ 0.107$ &  $ 0.148$ &            $ 0.093$ &                $ 0.617$ &           $ 1.134$ \\
-            Morocco &          Ovis aries &               $ 0.008$ &                    $ 0.108$ &  $ 0.148$ &            $ 0.093$ &                $ 0.619$ &           $ 1.149$ \\
-            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus &               $ 0.004$ &                    $ 0.122$ &  $ 0.133$ &            $ 0.071$ &                $ 0.696$ &           $ 1.397$ \\
-            \rowcolor{LIGHTGREY} Central Afr.
-Rep.
-& Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.124$ &  $ 0.134$ &            $ 0.071$ &                $ 0.701$ &           $ 1.431$ \\
-            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.124$ &  $ 0.134$ &            $ 0.071$ &                $ 0.699$ &           $ 1.422$ \\
-            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.123$ &  $ 0.134$ &            $ 0.071$ &                $ 0.703$ &           $ 1.411$ \\
-            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.123$ &  $ 0.134$ &            $ 0.071$ &                $ 0.699$ &           $ 1.419$ \\
-            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus &               $ 0.003$ &                    $ 0.123$ &  $ 0.133$ &            $ 0.071$ &                $ 0.699$ &           $ 1.407$ \\
-            \rowcolor{LIGHTGREY} South Africa  & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.125$ &  $ 0.134$ &            $ 0.070$ &                $ 0.704$ &           $ 1.447$ \\
-            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &                    $ 0.123$ &  $ 0.133$ &            $ 0.070$ &                $ 0.699$ &           $ 1.413$ \\
-            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.123$ &  $ 0.134$ &            $ 0.071$ &                $ 0.699$ &           $ 1.410$ \\
-            African &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &            $ 0.118$ &                $ 0.865$ &           $ 1.609$ \\
-            Admixed American &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &            $ 0.118$ &                $ 0.865$ &           $ 1.607$ \\
-            East Asian &        Homo sapiens &               $ 0.002$ &                    $ 0.098$ &  $ 0.192$ &            $ 0.118$ &                $ 0.869$ &           $ 1.607$ \\
-            European &        Homo sapiens &               $ 0.002$ &                    $ 0.098$ &  $ 0.192$ &            $ 0.118$ &                $ 0.865$ &           $ 1.598$ \\
-            South Asian &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &            $ 0.118$ &                $ 0.867$ &           $ 1.610$ \\
+            \rowcolor{LIGHTGREY} Equus c. & Equus caballus & $ 0.923$ & $ 0.065$ & $ 0.012$ & $ 0.462$ & $ 0.419$ & $ 0.118$ \\
+            Iran & Bos taurus & $ 0.924$ & $ 0.065$ & $ 0.011$ & $ 0.515$ & $ 0.362$ & $ 0.123$ \\
+            Uganda & Bos taurus & $ 0.924$ & $ 0.065$ & $ 0.011$ & $ 0.514$ & $ 0.361$ & $ 0.125$ \\
+            \rowcolor{LIGHTGREY} Australia & Capra hircus & $ 0.923$ & $ 0.066$ & $ 0.011$ & $ 0.494$ & $ 0.386$ & $ 0.121$ \\
+            \rowcolor{LIGHTGREY} France & Capra hircus & $ 0.923$ & $ 0.066$ & $ 0.011$ & $ 0.494$ & $ 0.386$ & $ 0.120$ \\
+            \rowcolor{LIGHTGREY} Iran (C. aegagrus) & Capra hircus & $ 0.923$ & $ 0.066$ & $ 0.011$ & $ 0.493$ & $ 0.386$ & $ 0.120$ \\
+            \rowcolor{LIGHTGREY} Iran & Capra hircus & $ 0.923$ & $ 0.066$ & $ 0.011$ & $ 0.492$ & $ 0.387$ & $ 0.121$ \\
+            \rowcolor{LIGHTGREY} Italy & Capra hircus & $ 0.923$ & $ 0.066$ & $ 0.011$ & $ 0.494$ & $ 0.386$ & $ 0.120$ \\
+            \rowcolor{LIGHTGREY} Morocco & Capra hircus & $ 0.923$ & $ 0.066$ & $ 0.011$ & $ 0.491$ & $ 0.387$ & $ 0.122$ \\
+            Iran & Ovis aries & $ 0.922$ & $ 0.067$ & $ 0.012$ & $ 0.568$ & $ 0.323$ & $ 0.109$ \\
+            Iran (O. orientalis) & Ovis aries & $ 0.922$ & $ 0.067$ & $ 0.011$ & $ 0.573$ & $ 0.320$ & $ 0.108$ \\
+            Iran (O. vignei) & Ovis aries & $ 0.922$ & $ 0.067$ & $ 0.012$ & $ 0.567$ & $ 0.325$ & $ 0.109$ \\
+            Various & Ovis aries & $ 0.922$ & $ 0.067$ & $ 0.011$ & $ 0.572$ & $ 0.321$ & $ 0.107$ \\
+            Morocco & Ovis aries & $ 0.922$ & $ 0.067$ & $ 0.012$ & $ 0.570$ & $ 0.321$ & $ 0.108$ \\
+            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus & $ 0.926$ & $ 0.065$ & $ 0.009$ & $ 0.485$ & $ 0.393$ & $ 0.122$ \\
+            \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus & $ 0.926$ & $ 0.065$ & $ 0.009$ & $ 0.485$ & $ 0.391$ & $ 0.124$ \\
+            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus & $ 0.926$ & $ 0.065$ & $ 0.009$ & $ 0.484$ & $ 0.393$ & $ 0.124$ \\
+            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus & $ 0.926$ & $ 0.065$ & $ 0.009$ & $ 0.483$ & $ 0.394$ & $ 0.123$ \\
+            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus & $ 0.926$ & $ 0.065$ & $ 0.009$ & $ 0.485$ & $ 0.392$ & $ 0.123$ \\
+            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus & $ 0.926$ & $ 0.065$ & $ 0.009$ & $ 0.484$ & $ 0.393$ & $ 0.123$ \\
+            \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus & $ 0.926$ & $ 0.065$ & $ 0.009$ & $ 0.480$ & $ 0.394$ & $ 0.125$ \\
+            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus & $ 0.926$ & $ 0.065$ & $ 0.009$ & $ 0.483$ & $ 0.394$ & $ 0.123$ \\
+            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus & $ 0.926$ & $ 0.065$ & $ 0.009$ & $ 0.485$ & $ 0.393$ & $ 0.123$ \\
+            African & Homo sapiens & $ 0.925$ & $ 0.065$ & $ 0.010$ & $ 0.561$ & $ 0.341$ & $ 0.099$ \\
+            Admixed American & Homo sapiens & $ 0.925$ & $ 0.065$ & $ 0.010$ & $ 0.561$ & $ 0.340$ & $ 0.099$ \\
+            East Asian & Homo sapiens & $ 0.925$ & $ 0.065$ & $ 0.010$ & $ 0.560$ & $ 0.341$ & $ 0.098$ \\
+            European & Homo sapiens & $ 0.925$ & $ 0.065$ & $ 0.010$ & $ 0.562$ & $ 0.340$ & $ 0.098$ \\
+            South Asian & Homo sapiens & $ 0.925$ & $ 0.065$ & $ 0.010$ & $ 0.561$ & $ 0.341$ & $ 0.099$ \\
         \end{longtable*}
+    \captionof{table}[Probability of mutations and substitutions to be $\SphyDel$, $\SphyNeu$ or $\SphyBen$.]{\textbf{Probability of mutations and substitutions to be $\bm{\SphyDel}$, $\bm{\SphyNeu}$ or $\bm{\SphyBen}$.}
+    $\proba{[} \SphyDel {]}$ (eq.~5) is the probability for a new mutation to be deleterious.
+     These mutations have a selection coefficient predicted at the phylogenetic-scale lower than -1, thus toward a less fit amino-acid.
+    $\proba{[} \SphyNeu {]}$ (eq.~5) is the probability for a new mutation to be nearly-neutral.
+    These mutations have a selection coefficient predicted at the phylogenetic-scale between -1 and 1.
+    $\proba{[} \SphyBen {]}$ (eq.~5) is the probability for a new mutation to be non-adaptive beneficial.
+    These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1, thus toward a more fit amino-acid.
+    $\proba_{div}[\SphyDel{]}$ is the proportion of substitutions in the terminal branch that are $\SphyDel$.
+    $\proba_{div}[\SphyNeu{]}$ is the proportion of substitutions in the terminal branch that are $\SphyNeu$.
+    $\proba_{div}[\SphyBen{]}$ is the proportion of substitutions in the terminal branch that are $\SphyBen$.\label{table:pdiv}}
     \end{center}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item $\proba_{div}[\SphyBen]$ is the proportion of substitutions in the terminal branch that are $\SphyBen$.
-        \item $\dn(\SphyDel) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are $\SphyDel$.
-        \item $\dn(\SphyNeu) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are $\SphyNeu$.
-        \item $\dn(\SphyBen) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are $\SphyBen$.
-    \end{itemize}
-
     \newpage
 
-    \subsubsection{$\dnds$ over-estimation due to beneficial back-mutations}
+    \subsubsection{\texorpdfstring{$\dnds$}{dₙ/dₛ} for \texorpdfstring{$\SphyDel$}{D₀}, \texorpdfstring{$\SphyNeu$}{N₀} or \texorpdfstring{$\SphyBen$}{B₀}}
+    Theoretically, $\omega = \dn / \ds$ can be related to the underlying scaled selection coefficient ($S$) with the relation $\omega = S /(1-\exp(-S))$ as in \cite[eq. 3]{nielsen_estimating_2003}.
+    In our experiments, our observed $\dn(\SphyBen) / \ds$ is within the range of $1.169$ (\textit{C.
+hircus}) to 1.745 (\textit{H.
+sapiens}), as shown in Table~\ref{table:dnds}, translating into an average $S$ of $\approx0.32$ to $\approx1.24$, so indeed only slightly advantageous.\\
+
+    Of note, observing $\dn(\SphyBen) / \ds >1$ is an important check that $\SphyBen$ mutations are indeed positively selected with an increased substitution rate.
+    Since $\dn(\SphyNeu) / \ds$ is close to 1 for the predicted nearly-neutral mutations, this means that the selection coefficients predicted at the mutation-selection balance are good proxies of selection, then observing $\dn(\SphyBen) / \ds > 1$ is evidence of positive selection of predicted non-adaptive beneficial mutations.
     \begin{center}
-        \captionof{table}{$\dnds$ over-estimation due to beneficial back-mutations.}
         \scriptsize
-        \begin{longtable*}{|l|l|r|r|r|r|r|}
+        \begin{longtable*}{|l|r|r|r|r|}
             \toprule
-            Population & Species & Watterson's $\thetaSyn$ & $\proba_{div}[\Sphy > 1]$ & $\dnds $ & $\dn(\Sphy < 1) / \ds$ & $\delta(\dnds )$ \\
+            Species & $\dnds $ & $\dn ( \SphyDel ) / \ds$ & $\dn ( \SphyNeu ) / \ds$ & $\dn ( \SphyBen ) / \ds$ \\
             \midrule
@@
             \midrule
-            \multicolumn{7}{r}{{Continued on next page}} \\
+            \multicolumn{5}{r}{{Continued on next page}} \\
             \midrule
@@
             \endlastfoot
-            \rowcolor{LIGHTGREY} Equus c. &      Equus caballus &               $ 0.002$ &                    $ 0.118$ &  $ 0.147$ &           $ 0.131$ &     $  10.5$ \\
-            Iran &          Bos taurus &               $ 0.002$ &                    $ 0.123$ &  $ 0.131$ &           $ 0.117$ &     $  11.1$ \\
-            Uganda &          Bos taurus &               $ 0.005$ &                    $ 0.125$ &  $ 0.134$ &           $ 0.118$ &     $  11.3$ \\
-            \rowcolor{LIGHTGREY} Australia &        Capra hircus &               $ 0.003$ &                    $ 0.121$ &  $ 0.125$ &           $ 0.111$ &     $  10.8$ \\
-            \rowcolor{LIGHTGREY} France &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.126$ &           $ 0.112$ &     $  10.8$ \\
-            \rowcolor{LIGHTGREY} Iran (C. aegagrus) &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.125$ &           $ 0.111$ &     $  10.8$ \\
-            \rowcolor{LIGHTGREY} Iran &        Capra hircus &               $ 0.004$ &                    $ 0.121$ &  $ 0.125$ &           $ 0.111$ &     $  10.9$ \\
-            \rowcolor{LIGHTGREY} Italy &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.126$ &           $ 0.112$ &     $  10.8$ \\
-            \rowcolor{LIGHTGREY} Morocco &        Capra hircus &               $ 0.004$ &                    $ 0.122$ &  $ 0.125$ &           $ 0.111$ &     $  11.0$ \\
-            Iran &          Ovis aries &               $ 0.007$ &                    $ 0.109$ &  $ 0.146$ &           $ 0.132$ &     $ 9.671$ \\
-            Iran (O. orientalis) &          Ovis aries &               $ 0.009$ &                    $ 0.108$ &  $ 0.148$ &           $ 0.134$ &     $ 9.516$ \\
-            Iran (O. vignei) &          Ovis aries &               $ 0.007$ &                    $ 0.109$ &  $ 0.146$ &           $ 0.132$ &     $ 9.598$ \\
-            Various &          Ovis aries &               $ 0.008$ &                    $ 0.107$ &  $ 0.148$ &           $ 0.134$ &     $ 9.439$ \\
-            Morocco &          Ovis aries &               $ 0.008$ &                    $ 0.108$ &  $ 0.148$ &           $ 0.134$ &     $ 9.582$ \\
-            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus &               $ 0.004$ &                    $ 0.122$ &  $ 0.133$ &           $ 0.118$ &     $  11.2$ \\
-            \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.124$ &  $ 0.134$ &           $ 0.119$ &     $  11.3$ \\
-            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.124$ &  $ 0.134$ &           $ 0.118$ &     $  11.3$ \\
-            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.123$ &  $ 0.134$ &           $ 0.119$ &     $  11.2$ \\
-            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.123$ &  $ 0.134$ &           $ 0.119$ &     $  11.3$ \\
-            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus &               $ 0.003$ &                    $ 0.123$ &  $ 0.133$ &           $ 0.118$ &     $  11.3$ \\
-            \rowcolor{LIGHTGREY} South Africa  & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.125$ &  $ 0.134$ &           $ 0.118$ &     $  11.5$ \\
-            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &                    $ 0.123$ &  $ 0.133$ &           $ 0.118$ &     $  11.3$ \\
-            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.123$ &  $ 0.134$ &           $ 0.119$ &     $  11.2$ \\
-            African &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &           $ 0.175$ &     $ 8.799$ \\
-            Admixed American &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &           $ 0.175$ &     $ 8.780$ \\
-            East Asian &        Homo sapiens &               $ 0.002$ &                    $ 0.098$ &  $ 0.192$ &           $ 0.175$ &     $ 8.768$ \\
-            European &        Homo sapiens &               $ 0.002$ &                    $ 0.098$ &  $ 0.192$ &           $ 0.175$ &     $ 8.728$ \\
-            South Asian &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &           $ 0.175$ &     $ 8.788$ \\
+            \rowcolor{LIGHTGREY} Equus caballus & $ 0.129$ & $ 0.065$ & $ 0.832$ & $ 1.267$ \\
+            Bos taurus & [$ 0.114$, $ 0.116$] & [$ 0.063$, $ 0.064$] & [$ 0.629$, $ 0.638$] & [$ 1.280$, $ 1.328$] \\
+            \rowcolor{LIGHTGREY} Capra hircus & [$ 0.108$, $ 0.109$] & [$ 0.058$, $ 0.058$] & [$ 0.631$, $ 0.636$] & [$ 1.169$, $ 1.183$] \\
+            Ovis aries & [$ 0.127$, $ 0.129$] & [$ 0.078$, $ 0.080$] & [$ 0.619$, $ 0.621$] & [$ 1.201$, $ 1.217$] \\
+            \rowcolor{LIGHTGREY} Chlorocebus sabaeus & [$ 0.118$, $ 0.119$] & [$ 0.062$, $ 0.062$] & [$ 0.713$, $ 0.720$] & [$ 1.521$, $ 1.577$] \\
+            Homo sapiens & [$ 0.170$, $ 0.170$] & [$ 0.103$, $ 0.103$] & [$ 0.884$, $ 0.888$] & [$ 1.733$, $ 1.745$] \\
         \end{longtable*}
+    \captionof{table}[$\dnds$ for $\SphyDel$, $\SphyNeu$ or $\SphyBen$.]{\textbf{$\bm{\dnds}$ for $\bm{\SphyDel}$, $\bm{\SphyNeu}$ or $\bm{\SphyBen}$.}
+    $\dnds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions estimated for all the non-synonymous substitutions in the terminal branch.
+    $\dn(\SphyDel) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are $\SphyDel$.
+    $\dn(\SphyNeu) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are $\SphyNeu$.
+    $\dn(\SphyBen) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are $\SphyBen$.
+    SNPs are considered fixed (as a substitution) in the populations if all sampled individuals are homozygous for the derived allele.
+    This effect results in $\dn / \ds$ varying across populations, denoted as a range per species.
+    $\dn(\SphyBen) / \ds$ values observed are above 1 and are consistent with slightly advantageous mutations.\label{table:dnds}}
     \end{center}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item $\proba_{div}[\SphyBen]$ is the proportion of substitutions in the terminal branch that are $\SphyBen$.
-        \item $\dnds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions estimated for all the non-synonymous substitutions in the terminal branch.
-        \item $\dn(\Sphy < 1) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are not $\SphyBen$.
-        This is the estimated divergence when we removed beneficial back-mutations.
-        \item $\delta(\dnds)$ (eq.~7) is the fraction of the divergence ($\dnds$) that is over-estimated, $\dnds$ is compared to the estimated divergence when we removed beneficial back-mutations $\dn(\Sphy < 1) / \ds$.
-    \end{itemize}
-    We estimated that between 9 and 11\% of $\dnds$ is over-estimated, corresponding to beneficial back-mutation inflating the $\dnds$ statistic.
 
     \newpage
-
-    \subsubsection{Probabilities of beneficial back-mutations}
+    \subsubsection{\texorpdfstring{$\dnds$}{dₙ/dₛ} over-estimation due to non-adaptive beneficial mutations}
+    We estimated that between $\approx9$ and $\approx12\%$ of $\dnds$ is over-estimated, corresponding to non-adaptive beneficial mutations inflating the $\dnds$ statistic, as shown in Table~\ref{table:dnds-delta}.
     \begin{center}
-        \captionof{table}{Probability of beneficial back-mutations among all beneficial ones.}
         \scriptsize
-        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
+        \begin{longtable*}{|l|r|r|r|}
             \toprule
-            Population & Species & Watterson's $\thetaSyn$ & $\proba[\SphyBen]$ & $\proba [ \SpopBen ]$ & $\frac{\proba[\SphyBen]}{\proba[ \SpopBen ]}$ & $\proba [ \SpopBen \given \SphyBen]$ & $\proba[\SphyBen\given \SpopBen ]$ \\
+            Species & $\dnds $ & $\dn(\Sphy < 1) / \ds$ & $\delta(\dnds )$ \\
             \midrule
@@
             \midrule
-            \multicolumn{8}{r}{{Continued on next page}} \\
+            \multicolumn{4}{r}{{Continued on next page}} \\
             \midrule
@@
             \endlastfoot
-            \rowcolor{LIGHTGREY} Equus c.
-&      Equus caballus &               $ 0.002$ &              $ 0.014$ &              $ 0.010$ &                                          $ 1.395$ &                         $ 0.580$ &                      $ 0.809$ \\
-            Iran &          Bos taurus &               $ 0.002$ &              $ 0.013$ &              $ 0.041$ &                                          $ 0.323$ &                         $ 0.857$ &                      $ 0.277$ \\
-            Uganda &          Bos taurus &               $ 0.005$ &              $ 0.013$ &              $ 0.013$ &                                          $ 0.991$ &                         $ 0.488$ &                      $ 0.483$ \\
-            \rowcolor{LIGHTGREY} Australia &        Capra hircus &               $ 0.003$ &              $ 0.014$ &              $ 0.026$ &                                          $ 0.532$ &                         $ 0.368$ &                      $ 0.196$ \\
-            \rowcolor{LIGHTGREY} France &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.572$ &                         $ 0.368$ &                      $ 0.211$ \\
-            \rowcolor{LIGHTGREY} Iran (C.
-aegagrus) &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.026$ &                                          $ 0.516$ &                         $ 0.221$ &                      $ 0.114$ \\
-            \rowcolor{LIGHTGREY} Iran &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.573$ &                         $ 0.368$ &                      $ 0.211$ \\
-            \rowcolor{LIGHTGREY} Italy &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.017$ &                                          $ 0.814$ &                         $ 0.270$ &                      $ 0.220$ \\
-            \rowcolor{LIGHTGREY} Morocco &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.018$ &                                          $ 0.751$ &                         $ 0.368$ &                      $ 0.276$ \\
-            Iran &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.006$ &                                          $ 2.321$ &                         $ 0.169$ &                      $ 0.392$ \\
-            Iran (O.
-orientalis) &          Ovis aries &               $ 0.009$ &              $ 0.014$ &              $ 0.012$ &                                          $ 1.178$ &                         $ 0.153$ &                      $ 0.180$ \\
-            Iran (O.
-vignei) &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.020$ &                                          $ 0.683$ &                         $ 0.195$ &                      $ 0.133$ \\
-            Various &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.012$ &                                          $ 1.201$ &                         $ 0.190$ &                      $ 0.228$ \\
-            Morocco &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.005$ &                                          $ 2.589$ &                         $ 0.136$ &                      $ 0.353$ \\
-            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.022$ &                                          $ 0.541$ &                         $ 0.565$ &                      $ 0.306$ \\
-            \rowcolor{LIGHTGREY} Central Afr.
-Rep.
-& Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.018$ &                                          $ 0.639$ &                         $ 0.429$ &                      $ 0.274$ \\
-            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.022$ &                                          $ 0.516$ &                         $ 0.462$ &                      $ 0.239$ \\
-            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.007$ &                                          $ 1.592$ &                         $ 0.486$ &                      $ 0.774$ \\
-            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.023$ &                                          $ 0.508$ &                         $ 0.478$ &                      $ 0.243$ \\
-            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus &               $ 0.003$ &              $ 0.012$ &              $ 0.015$ &                                          $ 0.762$ &                         $ 0.516$ &                      $ 0.393$ \\
-            \rowcolor{LIGHTGREY} South Africa  & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.016$ &                                          $ 0.734$ &                         $ 0.490$ &                      $ 0.360$ \\
-            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.016$ &                                          $ 0.713$ &                         $ 0.515$ &                      $ 0.367$ \\
-            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.023$ &                                          $ 0.500$ &                         $ 0.499$ &                      $ 0.249$ \\
-            African &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.025$ &                                          $ 0.470$ &                         $ 0.678$ &                      $ 0.319$ \\
-            Admixed American &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.021$ &                                          $ 0.569$ &                         $ 0.635$ &                      $ 0.361$ \\
-            East Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.031$ &                                          $ 0.381$ &                         $ 0.611$ &                      $ 0.233$ \\
-            European &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.034$ &                                          $ 0.350$ &                         $ 0.619$ &                      $ 0.217$ \\
-            South Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.033$ &                                          $ 0.354$ &                         $ 0.628$ &                      $ 0.222$ \\
+            \rowcolor{LIGHTGREY} Equus caballus & $ 0.129$ & $ 0.115$ & $  10.7$ \\
+            Bos taurus & [$ 0.114$, $ 0.116$] & [$ 0.101$, $ 0.102$] & [$  11.3$, $  11.5$] \\
+            \rowcolor{LIGHTGREY} Capra hircus & [$ 0.108$, $ 0.109$] & [$ 0.096$, $ 0.097$] & [$  11.0$, $  11.2$] \\
+            Chlorocebus sabaeus & [$ 0.118$, $ 0.119$] & [$ 0.104$, $ 0.105$] & [$  11.4$, $  11.7$] \\
+            \rowcolor{LIGHTGREY} Homo sapiens & [$ 0.170$, $ 0.170$] & [$ 0.154$, $ 0.155$] & [$ 8.926$, $ 8.996$] \\
+            Ovis aries & [$ 0.127$, $ 0.129$] & [$ 0.115$, $ 0.117$] & [$ 9.663$, $ 9.894$] \\
         \end{longtable*}
+        \captionof{table}[$\dnds$ over-estimation due to non-adaptive beneficial mutations.]{\textbf{$\bm{\dnds}$ over-estimation due to non-adaptive beneficial mutations.}
+        $\dnds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions estimated for all the non-synonymous substitutions in the terminal branch.
+        $\dn(\Sphy < 1) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are not $\SphyBen$.
+        This is the estimated divergence when we remove non-adaptive beneficial mutations.
+        $\delta(\dnds)$ (eq.~7) is the fraction of the divergence ($\dnds$) that is over-estimated: the difference between $\dnds$ and $\dn(\Sphy < 1) / \ds$.\label{table:dnds-delta}}
     \end{center}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item $\proba [ \SphyBen ]$ (eq.~5) is the probability for a new mutation to be a beneficial back-mutation.
-        These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1, thus toward a more fit amino-acid.
-        \item $\proba [ \SpopBen ]$ (eq.~15) is the probability for a mutation to be beneficial.
-        These mutations have a selection coefficient at the population-scale larger than 1.
-        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale (the \textit{precision}).
-        \item $\proba [ \SphyBen \given \SpopBen]$ (eq.~14) is the probability for a mutation to a beneficial back-mutations, given it is beneficial at the population scale (the \textit{recall}).
-        This probability is obtained using Bayes' formula.
-    \end{itemize}
     \newpage
+    \section{Gene ontology enrichment}
 
-    \subsection{Replicability across mammals}
-    The proportion of deleterious ($\ProbaPopDel$), nearly-neutral ($\ProbaPopNeu$) and of beneficial ($\ProbaPopBen$) mutations estimated at the population-genetic scale across the different populations is shown for each class of selection ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$).
+    \subsection{Gene ontology enrichment in \texorpdfstring{$\SphyBen$}{B₀} SNPs}
 
-    \captionof{figure}{Estimation of selection at the population scale for $\SphyDel$ mutations}
-    \begin{minipage}{0.9\linewidth}
-    \includegraphics[width=\linewidth, page=1]{artworks/Theta.neg.stacked.pdf}
-    \end{minipage}
-    \begin{minipage}{0.09\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
-    \end{minipage}
+    To assess whether $\SphyBen$ SNPs are enriched in specific gene functions, we used gene ontology (GO) terms at the gene level.
+    Thus, for each $\SphyBen$ SNP detected in a focal population, we annotated this SNP with GO terms inherited from the gene in which the SNP is located.
+    We restricted this analysis solely on genes annotated with at least one GO term.
+    To assess the weight of each GO term in the set of $\SphyBen$ SNPs, we computed the proportion of $\SphyBen$ SNPs annotated with a given GO term.
+    We then tested if the distribution of $\SphyBen$ SNPs is different between genes sharing a common GO term and the rest of the genes, as shown in Table~\ref{table:ontology}.
 
-    \captionof{figure}{Estimation of selection at the population scale for $\SphyNeu$ mutations}
-    \begin{minipage}{0.9\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/Theta.weak.stacked.pdf}
-    \end{minipage}
-    \begin{minipage}{0.09\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
-    \end{minipage}
+    \begin{center}
+        \scriptsize
+        \begin{longtable*}{|l|l|r|r|r|r|r|}
+            \toprule
+            GO id & GO name & $p$ & $r$ & Mann-Whitney U & $p_{\mathrm{v}}$ & $p_{\mathrm{v}}^{\mathrm{adj}}$ \\
+            \midrule
+            \endhead
+            \midrule
+            \multicolumn{7}{r}{Continued on next page} \\
+            \midrule
+            \endfoot
+            \bottomrule
+            \endlastfoot
+            GO:0003777 & microtubule motor activity & $ 0.027$ & $ 1.802$ & $1.1\times 10^{5}$ & $1.8\times 10^{-6}$ & $\bm{0.0008{^*}}$ \\
+            GO:0005578 & proteinaceous extracellular matrix & $ 0.069$ & $ 2.071$ & $4.7\times 10^{5}$ & $1.9\times 10^{-6}$ & $\bm{0.00084{^*}}$ \\
+            GO:0003774 & motor activity & $ 0.023$ & $ 1.127$ & $1.1\times 10^{5}$ & $6.7\times 10^{-5}$ & $\bm{ 0.029{^*}}$ \\
+            GO:0030198 & extracellular matrix organization & $ 0.039$ & $ 1.956$ & $2.7\times 10^{5}$ & $0.00055$ & $ 0.239~~$ \\
+            GO:0007018 & microtubule-based movement & $ 0.023$ & $ 0.924$ & $1.3\times 10^{5}$ & $0.00073$ & $ 0.315~~$ \\
+            GO:0005576 & extracellular region & $ 0.178$ & $ 2.195$ & $1.9\times 10^{6}$ & $0.00083$ & $ 0.359~~$ \\
+            GO:0006898 & receptor-mediated endocytosis & $ 0.027$ & $ 1.803$ & $1.7\times 10^{5}$ & $ 0.001$ & $ 0.512~~$ \\
+            GO:0006355 & regulation of transcription & $ 0.069$ & $ 0.275$ & $1.9\times 10^{6}$ & $ 0.002$ & $ 0.815~~$ \\
+            GO:0005604 & basement membrane & $ 0.019$ & $ 1.638$ & $1.1\times 10^{5}$ & $ 0.002$ & $ 0.852~~$ \\
+            GO:0007229 & integrin-mediated signaling pathway & $ 0.019$ & $ 1.930$ & $1.1\times 10^{5}$ & $ 0.003$ & $ 1.000~~$ \\
+            GO:0016887 & ATPase activity & $ 0.031$ & $ 1.149$ & $1.8\times 10^{5}$ & $ 0.003$ & $ 1.000~~$ \\
+            GO:0007155 & cell adhesion & $ 0.062$ & $ 1.438$ & $5.8\times 10^{5}$ & $ 0.005$ & $ 1.000~~$ \\
+            GO:0005634 & nucleus & $ 0.266$ & $ 0.557$ & $3.9\times 10^{6}$ & $ 0.005$ & $ 1.000~~$ \\
+            GO:0006351 & transcription & $ 0.073$ & $ 0.339$ & $1.9\times 10^{6}$ & $ 0.008$ & $ 1.000~~$ \\
+            GO:0005654 & nucleoplasm & $ 0.124$ & $ 0.443$ & $2.6\times 10^{6}$ & $ 0.009$ & $ 1.000~~$ \\
+            GO:0006366 & transcription from RNA polymerase II promoter & $ 0.008$ & $ 0.063$ & $6.2\times 10^{5}$ & $ 0.011$ & $ 1.000~~$ \\
+            GO:0005829 & cytosol & $ 0.212$ & $ 0.541$ & $3.5\times 10^{6}$ & $ 0.012$ & $ 1.000~~$ \\
+            GO:0016853 & isomerase activity & $ 0.015$ & $ 4.066$ & $ 1\times 10^{5}$ & $ 0.015$ & $ 1.000~~$ \\
+            GO:0071356 & cellular response to tumor necrosis factor & $ 0.015$ & $ 7.069$ & $ 1\times 10^{5}$ & $ 0.016$ & $ 1.000~~$ \\
+            GO:0005518 & collagen binding & $ 0.015$ & $ 2.900$ & $ 1\times 10^{5}$ & $ 0.017$ & $ 1.000~~$ \\
+            GO:0043087 & regulation of GTPase activity & $ 0.015$ & $ 2.025$ & $1.1\times 10^{5}$ & $ 0.027$ & $ 1.000~~$ \\
+            GO:0000139 & Golgi membrane & $ 0.012$ & $ 0.214$ & $6.3\times 10^{5}$ & $ 0.028$ & $ 1.000~~$ \\
+            GO:0043235 & receptor complex & $ 0.023$ & $ 0.935$ & $1.9\times 10^{5}$ & $ 0.028$ & $ 1.000~~$ \\
+            GO:0000981 & RNA polymerase II transcription factor activity & $ 0.027$ & $ 0.452$ & $9.1\times 10^{5}$ & $ 0.029$ & $ 1.000~~$ \\
+            GO:0005739 & mitochondrion & $ 0.058$ & $ 0.471$ & $1.4\times 10^{6}$ & $ 0.029$ & $ 1.000~~$ \\
+            GO:0005581 & collagen trimer & $ 0.015$ & $ 2.124$ & $1.1\times 10^{5}$ & $ 0.036$ & $ 1.000~~$ \\
+            GO:0051015 & actin filament binding & $ 0.019$ & $ 0.912$ & $1.5\times 10^{5}$ & $ 0.036$ & $ 1.000~~$ \\
+            GO:0001843 & neural tube closure & $ 0.015$ & $ 1.164$ & $1.1\times 10^{5}$ & $ 0.036$ & $ 1.000~~$ \\
+            GO:0005737 & cytoplasm & $ 0.317$ & $ 0.692$ & $4.1\times 10^{6}$ & $ 0.037$ & $ 1.000~~$ \\
+            GO:0043565 & sequence-specific DNA binding & $ 0.015$ & $ 0.308$ & $ 6\times 10^{5}$ & $ 0.039$ & $ 1.000~~$ \\
+            GO:0004222 & metalloendopeptidase activity & $ 0.019$ & $ 1.188$ & $1.6\times 10^{5}$ & $ 0.043$ & $ 1.000~~$ \\
+            GO:0007166 & cell surface receptor signaling pathway & $ 0.031$ & $ 2.871$ & $ 3\times 10^{5}$ & $ 0.046$ & $ 1.000~~$ \\
+            GO:0007156 & homophilic cell adhesion via plasma membrane... & $ 0.015$ & $ 1.013$ & $1.2\times 10^{5}$ & $ 0.050$ & $ 1.000~~$ \\
+            GO:0007286 & spermatid development & $ 0.015$ & $ 2.497$ & $1.2\times 10^{5}$ & $ 0.051$ & $ 1.000~~$ \\
+            GO:0008202 & steroid metabolic process & $ 0.015$ & $ 2.755$ & $1.2\times 10^{5}$ & $ 0.051$ & $ 1.000~~$ \\
+            GO:0061024 & membrane organization & $ 0.019$ & $ 1.516$ & $1.6\times 10^{5}$ & $ 0.052$ & $ 1.000~~$ \\
+            GO:1901796 & regulation of signal transduction by p53 class... & $ 0.019$ & $ 1.333$ & $1.6\times 10^{5}$ & $ 0.058$ & $ 1.000~~$ \\
+            GO:0006397 & mRNA processing & $ 0.004$ & $ 0.210$ & $3.5\times 10^{5}$ & $ 0.061$ & $ 1.000~~$ \\
+            GO:0006915 & apoptotic process & $ 0.015$ & $ 0.463$ & $6.4\times 10^{5}$ & $ 0.065$ & $ 1.000~~$ \\
+            GO:0043547 & positive regulation of GTPase activity & $ 0.035$ & $ 2.651$ & $3.7\times 10^{5}$ & $ 0.068$ & $ 1.000~~$ \\
+            GO:0007010 & cytoskeleton organization & $ 0.019$ & $ 1.771$ & $1.7\times 10^{5}$ & $ 0.068$ & $ 1.000~~$ \\
+            GO:0030308 & negative regulation of cell growth & $ 0.015$ & $ 3.055$ & $1.3\times 10^{5}$ & $ 0.070$ & $ 1.000~~$ \\
+            GO:0007160 & cell-matrix adhesion & $ 0.015$ & $ 1.046$ & $1.2\times 10^{5}$ & $ 0.073$ & $ 1.000~~$ \\
+            GO:0006897 & endocytosis & $ 0.023$ & $ 1.408$ & $2.2\times 10^{5}$ & $ 0.073$ & $ 1.000~~$ \\
+            GO:0003677 & DNA binding & $ 0.077$ & $ 0.448$ & $1.7\times 10^{6}$ & $ 0.075$ & $ 1.000~~$ \\
+            GO:0043202 & lysosomal lumen & $ 0.015$ & $ 1.522$ & $1.3\times 10^{5}$ & $ 0.075$ & $ 1.000~~$ \\
+            GO:0003700 & DNA binding transcription factor activity & $ 0.027$ & $ 0.343$ & $8.7\times 10^{5}$ & $ 0.076$ & $ 1.000~~$ \\
+            GO:0008134 & transcription factor binding & $ 0.004$ & $ 0.048$ & $3.2\times 10^{5}$ & $ 0.077$ & $ 1.000~~$ \\
+            GO:0005488 & binding & $ 0.046$ & $ 0.641$ & $4.1\times 10^{5}$ & $ 0.078$ & $ 1.000~~$ \\
+            GO:0045944 & positive regulation of transcription from RNA... & $ 0.039$ & $ 0.324$ & $1.1\times 10^{6}$ & $ 0.085$ & $ 1.000~~$ \\
+            GO:0005794 & Golgi apparatus & $ 0.046$ & $ 0.430$ & $1.2\times 10^{6}$ & $ 0.087$ & $ 1.000~~$ \\
+            GO:0016032 & viral process & $ 0.008$ & $ 0.321$ & $4.1\times 10^{5}$ & $ 0.089$ & $ 1.000~~$ \\
+            GO:0055085 & transmembrane transport & $ 0.054$ & $ 1.533$ & $5.9\times 10^{5}$ & $ 0.092$ & $ 1.000~~$ \\
+            GO:0006260 & DNA replication & $ 0.019$ & $ 1.051$ & $1.8\times 10^{5}$ & $ 0.096$ & $ 1.000~~$ \\
+            GO:0030425 & dendrite & $ 0.008$ & $ 0.121$ & $3.9\times 10^{5}$ & $ 0.099$ & $ 1.000~~$ \\
+            GO:0005524 & ATP binding & $ 0.127$ & $ 0.666$ & $1.5\times 10^{6}$ & $ 0.103$ & $ 1.000~~$ \\
+            GO:0005615 & extracellular space & $ 0.100$ & $ 1.699$ & $1.3\times 10^{6}$ & $ 0.107$ & $ 1.000~~$ \\
+            GO:0007283 & spermatogenesis & $ 0.039$ & $ 1.824$ & $3.9\times 10^{5}$ & $ 0.108$ & $ 1.000~~$ \\
+            GO:0005179 & hormone activity & $ 0.012$ & $ 7.683$ & $9.9\times 10^{4}$ & $ 0.118$ & $ 1.000~~$ \\
+            GO:0098793 & presynapse & $ 0.012$ & $ 2.065$ & $9.6\times 10^{4}$ & $ 0.119$ & $ 1.000~~$ \\
+            GO:0005254 & chloride channel activity & $ 0.012$ & $ 1.694$ & $9.6\times 10^{4}$ & $ 0.124$ & $ 1.000~~$ \\
+            GO:0036064 & ciliary basal body & $ 0.015$ & $ 1.378$ & $1.4\times 10^{5}$ & $ 0.125$ & $ 1.000~~$ \\
+            GO:0070062 & extracellular exosome & $ 0.104$ & $ 0.570$ & $2.1\times 10^{6}$ & $ 0.125$ & $ 1.000~~$ \\
+            GO:0090630 & activation of GTPase activity & $ 0.012$ & $ 2.519$ & $9.9\times 10^{4}$ & $ 0.127$ & $ 1.000~~$ \\
+            GO:0044212 & transcription regulatory region DNA binding & $ 0.004$ & $ 0.322$ & $2.7\times 10^{5}$ & $ 0.128$ & $ 1.000~~$ \\
+            GO:0055114 & oxidation-reduction process & $ 0.019$ & $ 0.482$ & $6.4\times 10^{5}$ & $ 0.129$ & $ 1.000~~$ \\
+            GO:0019886 & antigen processing and presentation of exogenous... & $ 0.012$ & $ 1.393$ & $9.6\times 10^{4}$ & $ 0.129$ & $ 1.000~~$ \\
+            GO:0005743 & mitochondrial inner membrane & $ 0.008$ & $ 0.463$ & $3.7\times 10^{5}$ & $ 0.133$ & $ 1.000~~$ \\
+            GO:0022617 & extracellular matrix disassembly & $ 0.012$ & $ 1.009$ & $9.6\times 10^{4}$ & $ 0.135$ & $ 1.000~~$ \\
+            GO:0042493 & response to drug & $ 0.004$ & $ 0.043$ & $2.6\times 10^{5}$ & $ 0.137$ & $ 1.000~~$ \\
+            GO:0008380 & RNA splicing & $ 0.008$ & $ 0.098$ & $2.6\times 10^{5}$ & $ 0.139$ & $ 1.000~~$ \\
+            GO:0043687 & post-translational protein modification & $ 0.008$ & $ 0.319$ & $3.6\times 10^{5}$ & $ 0.140$ & $ 1.000~~$ \\
+            GO:0010951 & negative regulation of endopeptidase activity & $ 0.012$ & $ 2.037$ & $9.9\times 10^{4}$ & $ 0.140$ & $ 1.000~~$ \\
+            GO:0000978 & RNA polymerase II proximal promoter... & $ 0.012$ & $ 0.250$ & $4.5\times 10^{5}$ & $ 0.140$ & $ 1.000~~$ \\
+            GO:0003713 & transcription coactivator activity & $ 0.004$ & $ 0.339$ & $2.6\times 10^{5}$ & $ 0.142$ & $ 1.000~~$ \\
+            GO:0001227 & transcriptional repressor activity & $ 0.012$ & $ 1.384$ & $9.9\times 10^{4}$ & $ 0.144$ & $ 1.000~~$ \\
+            GO:0005623 & cell & $ 0.012$ & $ 1.927$ & $ 1\times 10^{5}$ & $ 0.150$ & $ 1.000~~$ \\
+            GO:0030574 & collagen catabolic process & $ 0.012$ & $ 1.036$ & $9.9\times 10^{4}$ & $ 0.151$ & $ 1.000~~$ \\
+            GO:0006457 & protein folding & $ 0.015$ & $ 2.465$ & $1.5\times 10^{5}$ & $ 0.158$ & $ 1.000~~$ \\
+            GO:0016477 & cell migration & $ 0.004$ & $ 0.121$ & $2.4\times 10^{5}$ & $ 0.159$ & $ 1.000~~$ \\
+            GO:0070374 & positive regulation of ERK1 and ERK2 cascade & $ 0.019$ & $ 4.238$ & $ 2\times 10^{5}$ & $ 0.160$ & $ 1.000~~$ \\
+            GO:0007605 & sensory perception of sound & $ 0.015$ & $ 0.824$ & $1.5\times 10^{5}$ & $ 0.162$ & $ 1.000~~$ \\
+            GO:0031225 & anchored component of membrane & $ 0.012$ & $ 0.892$ & $ 1\times 10^{5}$ & $ 0.171$ & $ 1.000~~$ \\
+            GO:0016757 & transferase activity & $ 0.004$ & $ 0.435$ & $2.4\times 10^{5}$ & $ 0.177$ & $ 1.000~~$ \\
+            GO:0002376 & immune system process & $ 0.012$ & $ 0.411$ & $4.3\times 10^{5}$ & $ 0.177$ & $ 1.000~~$ \\
+            GO:0005759 & mitochondrial matrix & $ 0.008$ & $ 0.361$ & $3.3\times 10^{5}$ & $ 0.185$ & $ 1.000~~$ \\
+            GO:0010389 & regulation of G2/M transition of mitotic cell... & $ 0.012$ & $ 0.924$ & $ 1\times 10^{5}$ & $ 0.188$ & $ 1.000~~$ \\
+            GO:0005667 & transcription factor complex & $ 0.004$ & $ 0.177$ & $2.3\times 10^{5}$ & $ 0.189$ & $ 1.000~~$ \\
+            GO:0030054 & cell junction & $ 0.031$ & $ 0.251$ & $8.1\times 10^{5}$ & $ 0.190$ & $ 1.000~~$ \\
+            GO:0001650 & fibrillar center & $ 0.019$ & $ 1.540$ & $1.1\times 10^{5}$ & $ 0.191$ & $ 1.000~~$ \\
+            GO:0014069 & postsynaptic density & $ 0.004$ & $ 0.172$ & $2.2\times 10^{5}$ & $ 0.200$ & $ 1.000~~$ \\
+            GO:0046934 & phosphatidylinositol-4 & $ 0.012$ & $ 1.135$ & $1.1\times 10^{5}$ & $ 0.201$ & $ 1.000~~$ \\
+            GO:0007267 & cell-cell signaling & $ 0.004$ & $ 0.354$ & $2.2\times 10^{5}$ & $ 0.201$ & $ 1.000~~$ \\
+            GO:0001649 & osteoblast differentiation & $ 0.012$ & $ 1.917$ & $1.1\times 10^{5}$ & $ 0.201$ & $ 1.000~~$ \\
+            GO:0045893 & positive regulation of transcription & $ 0.023$ & $ 0.596$ & $6.6\times 10^{5}$ & $ 0.205$ & $ 1.000~~$ \\
+            GO:0007399 & nervous system development & $ 0.015$ & $ 0.450$ & $ 5\times 10^{5}$ & $ 0.205$ & $ 1.000~~$ \\
+            GO:0001501 & skeletal system development & $ 0.015$ & $ 1.212$ & $1.6\times 10^{5}$ & $ 0.207$ & $ 1.000~~$ \\
+            GO:0019903 & protein phosphatase binding & $ 0.012$ & $ 0.875$ & $1.1\times 10^{5}$ & $ 0.208$ & $ 1.000~~$ \\
+            GO:1902476 & chloride transmembrane transport & $ 0.012$ & $ 1.458$ & $1.1\times 10^{5}$ & $ 0.210$ & $ 1.000~~$ \\
+            GO:0007568 & aging & $ 0.015$ & $ 2.053$ & $1.6\times 10^{5}$ & $ 0.210$ & $ 1.000~~$ \\
+        \end{longtable*}
+        \captionof{table}[Gene ontology enrichment in $\SphyBen$ SNPs.]{\textbf{Gene ontology enrichment in $\bm{\SphyBen}$ SNPs.} GO terms that are enriched in genes with $\SphyBen$ SNPs in European humans (shown here are the first 100 rows with the lowest $p_{\mathrm{v}}$).
+        For each GO term, $p$ is the proportion of $\SphyBen$ SNPs that are annotated with this focal GO term among all annotated $\SphyBen$ SNPs.
+        For each gene, $p[ \SphyBen {]}$ is the proportion of sites that have a $\SphyBen$ SNP (can be 0 if no $\SphyBen$ SNP is detected for this gene).
+        For each GO term, $r$ is the ratio of the mean of $p[ \SphyBen {]}$ in the set of genes sharing the focal ontology over the mean of $p[ \SphyBen {]}$ in the rest of the genes.
+        Mann-Whitney U is the statistic testing if the distribution of $p[ \SphyBen {]}$ is different between the two sets of genes (p-value $p_{\mathrm{v}}$ for the two-sided test).
+        $p_{\mathrm{v}}^{\mathrm{adj}}$ are corrected for multiple comparison (Holm–Bonferroni correction across the ontology terms).
+        $^*$ for $p_{\mathrm{v}}^{\mathrm{adj}}$ lower than the risk $\alpha=0.05$.\label{table:ontology}
+        }
+    \end{center}
 
     \newpage
-    \captionof{figure}{Estimation of selection at the population scale for $\SphyBen$ mutations}
-    \begin{minipage}{0.9\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/Theta.pos.stacked.pdf}
-    \end{minipage}
-    \begin{minipage}{0.09\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
-    \end{minipage}
+    \subsection{Enrichment in \texorpdfstring{$\SphyBen$}{B₀} SNPs across all gene ontology terms}
+    Whether SNPs classified as $\SphyBen$ are associated to a particular ontology is tested with a Mann-Whitney U statistic as described in Table~\ref{table:ontology}.
+    This test is performed across across all 347 gene ontology terms, giving one $p_{\mathrm{v}}$ per ontology (Table~\ref{table:ontology} for the 100 lowest $p_{\mathrm{v}}$).
+    The distribution of $p_{\mathrm{v}}$ are not strongly associated to the ontology terms of their respective genes, as shown in the histogram of Figure~\ref{fig:ontology-p}.
 
-    \subsection{Correlation with diversity}
-    For each population, the proportion of deleterious ($\ProbaPopDel$), nearly-neutral ($\ProbaPopNeu$) and of beneficial ($\ProbaPopBen$) mutations estimated at the population-genetic scale is shown as function of Watterson's's diversity ($\thetaSyn$).
-
-    \subsubsection{Proportion of deleterious mutations ($\SpopDel$)}\label{subsec:proportion-deleterious-mutations}
-    \captionof{figure}{Proportion of deleterious mutations ($\SpopDel$)}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.all_P-Sneg.scatter.pdf}
-    \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.neg_P-Sneg.scatter.pdf}
-    \end{minipage}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item $\proba [ \SpopDel ]$ (eq.~15) is the probability for a mutation to be deleterious.
-        These mutations have a selection coefficient at the population-scale lower than -1.
-        \item $\proba [ \SpopDel \given \SphyDel ]$ (eq.~12) is the probability for a mutation to be deleterious at the population scale, given it is predicted to be a deleterious at the phylogenetic scale.
-    \end{itemize}
-
-    We can see that higher synonymous diversity ($\thetaSyn$) is typically accompanied by a higher proportion of effectively deleterious mutations at the population scale ($\proba [ \SpopDel ]$).
-    This trend is also confirmed when we restricted the analysis to class of mutations that are supposedly deleterious at the phylogenetic scale ($\SphyDel$).
-    This result is qualitatively in accordance with the nearly-neutral theory of evolution which argues that very slightly deleterious mutations are more efficiently purified in large populations.
-
-    \subsubsection{Proportion of nearly-neutral mutations ($\SpopNeu$)}\label{subsec:proportion-nearly-neutral-mutations}
-    \captionof{figure}{Proportion of nearly-neutral mutations ($\SpopNeu$)}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.all_P-Sweak.scatter.pdf}
-    \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.weak_P-Sweak.scatter.pdf}
-    \end{minipage}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item $\proba [ \SpopNeu ]$ (eq.~15) is the probability for a mutation to be nearly-neutral.
-        These mutations have a selection coefficient at the population-scale between -1 and 1.
-        \item $\proba [ \SpopNeu \given \SphyNeu ]$ (eq.~12) is the probability for a mutation to be nearly-neutral at the population scale, given it is predicted to be a nearly-neutral at the phylogenetic scale.
-    \end{itemize}
-
-    We confirmed that higher synonymous diversity ($\thetaSyn$) is typically accompanied by a smaller proportion of neutral mutations at the population scale ($\proba [ \SpopNeu ]$ in the range 0.06-0.18).
-    This result is more pronounced ($\proba [ \SpopNeu \given \SphyNeu ]$ in the range 0.36-0.73) when we restricted the analysis to class of mutations that are supposedly nearly-neutral at the phylogenetic scale ($\SphyNeu$).
-    This result suggests that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) are more likely to discriminate whether mutations are beneficial or deleterious.
-    Alternatively stated, mutations in populations with low diversity (e.g.~\textit{Homo}) are effectively nearly-neutral and behave as would a neutral mutation.
-    This result is qualitatively in accordance with the nearly-neutral theory of evolution which argues that mutations are less efficiently selected for in small populations.
-
-    \subsubsection{Proportion of beneficial mutations ($\SpopBen$)}\label{subsec:proportion-beneficial-mutations}
-    \captionof{figure}{Proportion of beneficial mutations ($\SpopBen$)}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.all_P-Spos.scatter.pdf}
-    \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.pos_P-Spos.scatter.pdf}
-    \end{minipage}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item $\proba [ \SpopBen ]$ (eq.~15) is the probability for a mutation to be beneficial.
-        These mutations have a selection coefficient at the population-scale larger than 1.
-        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale (the \textit{precision}).
-    \end{itemize}
-    Higher synonymous diversity ($\thetaSyn$) is accompanied by a smaller proportion of beneficial mutations at the population scale ($\proba [ \SpopBen ]$).
-    This trend is also confirmed when we restricted the analysis to class of mutations that are supposedly beneficial back-mutations at the phylogenetic scale ($\SphyBen$).
-    This result is much more difficult to interpret.
-    The fraction of beneficial back mutations is supposed to depend on long term demographic history, which is not directly accessible.
-    If the long term effective population size is relatively similar to the short term one, we expect little opportunity for beneficial back-mutations.
-    And thus, counter-intuitively we expect a diminution of positively selected mutations.
-    However, we can see that the proportion of beneficial back-mutations among advantageous one does not decrease with synonymous diversity.
-    This means that somehow adaptive mutations also decrease with synonymous diversity for a reason we fail to explain.
+    \begin{center}
+        \includegraphics[width=0.65\linewidth]{artworks/ontology_poly.Homo_sapiens.EUR.hist.pdf}
+        \captionof{figure}[Enrichment in $\SphyBen$ SNPs across all gene ontology terms.]{\textbf{Enrichment in $\bm{\SphyBen}$ SNPs across all gene ontology terms}.
+In order to test if the distribution of $\SphyBen$ SNPs is different between genes sharing a common GO term and the rest of the genes, we used a Mann-Whitney U test.
+The distribution of $p_{\mathrm{v}}$ obtained across all 347 gene ontology terms is shown as a histogram.\label{fig:ontology-p}}
+    \end{center}
 
@@
     \section{Clinically related terms for mutations}
-    \subsection{Terms associated with deleterious mutations $\SphyDel$}
+
+    \subsection{Terms associated with deleterious mutations \texorpdfstring{$\SphyDel$}{D₀}}
+    SNPs predicted with $\SphyDel$ are statistically associated to clinical terms such as \textit{Likely Pathogenic} and \textit{Pathogenic}, as shown in Table~\ref{table:ontology-neg}.
+
     \begin{center}
-        \captionof{table}{Terms associated with deleterious mutations $\SphyDel$}
         \begin{tabular}{|l|r|r|r|r|r|}
@@
         \end{tabular}
+        \captionof{table}[Terms associated with deleterious mutations $\SphyDel$.]{\textbf{Terms associated with deleterious mutations $\bm{\SphyDel}$.}
+        In humans (European population), non-synonymous SNPs in the test group ($\SphyDel$) are contrasted to SNPs in the control group ($\SphyNeu$).
+        For each clinical term, a 2x2 contingency table is built by counting the number of SNPs based on their selection coefficient and their clinical terms (whether they have this specific term or not).
+        Fisher's exact tests are then performed for these 2x2 contingency tables.
+        $^*$ for $p_{\mathrm{v}}^{\mathrm{adj}}$ corrected for multiple comparison (Holm–Bonferroni correction) lower than the risk $\alpha=0.05$.\label{table:ontology-neg}}
     \end{center}
-    In humans, non-synonymous SNPs in the test group ($\SphyDel$) are contrasted to SNPs in the control group ($\SphyNeu$).
-    For each clinical term, a 2x2 contingency tables is built by counting the number of SNPs based on their selection coefficient and their clinical terms (whether they have this specific term or not).
-    Fisher's exact tests are then performed for these 2x2 contingency tables.
-    $^*$ for $p_{\mathrm{v}}^{\mathrm{adj}}$ corrected for multiple comparison (Holm–Bonferroni correction) lower than the risk $\alpha=0.05$.
-    SNPs predicted with $\SphyDel$ are statistically associated to clinical terms such as \textit{Likely Pathogenic} and \textit{Pathogenic}.
 
-    \subsection{Terms associated with beneficial back-mutations $\SphyBen$}
+    \subsection{Terms associated with non-adaptive beneficial mutations \texorpdfstring{$\SphyBen$}{B₀}}
+    Beneficial non-adaptive mutations are associated with clinical terms such as \textit{Benign} and \textit{Likely Benign}, as shown in Table~\ref{table:ontology-pos}.
     \begin{center}
-        \captionof{table}{Terms associated with beneficial back-mutations $\SphyBen$}
         \begin{tabular}{|l|r|r|r|r|r|}
@@
         \end{tabular}
+        \captionof{table}[Terms associated with non-adaptive beneficial mutations $\SphyBen$.]{\textbf{Terms associated with non-adaptive beneficial mutations $\bm{\SphyBen}$.}
+        In humans (European population), non-synonymous SNPs in the test group ($\SphyBen$) are contrasted to SNPs in the control group ($\SphyNeu$).
+        For each clinical term, a 2x2 contingency table is built by counting the number of SNPs based on their selection coefficient and their clinical terms (whether they have this specific term or not).
+        Fisher's exact tests are then performed for these 2x2 contingency tables.
+        $^*$ for $p_{\mathrm{v}}^{\mathrm{adj}}$ corrected for multiple comparison (Holm–Bonferroni correction) lower than the risk $\alpha=0.05$.\label{table:ontology-pos}}
     \end{center}
-    In humans, non-synonymous SNPs in the test group ($\SphyBen$) are contrasted to SNPs in the control group ($\SphyNeu$).
-    For each clinical term, a 2x2 contingency tables is built by counting the number of SNPs based on their selection coefficient and their clinical terms (whether they have this specific term or not).
-    Fisher's exact tests are then performed for these 2x2 contingency tables.
-    $^*$ for $p_{\mathrm{v}}^{\mathrm{adj}}$ corrected for multiple comparison (Holm–Bonferroni correction) lower than the risk $\alpha=0.05$.
-    Beneficial back-mutations are associated with clinical terms such as \textit{Benign} and \textit{Likely Benign}.
-    \newpage
 
-    \section{Including divergence data for the estimation of $\Spop$}
-
-    \subsection{Including divergence in polyDFE}
-    Divergence data (number of substitutions per site) can also be included into polyDFE to estimate the DFE.
-    For the class of a given class of selection coefficient ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$), the number of substitutions has already been computed and is given by $D\left( \Sphyclass \right)$ (see eq.~6), and the number of sites is given by $L \left( \Sphyclass \right)$ (see eq.~4).
-    Otherwise, the procedure is the same as described section \textit{Scaled selection coefficients ($\Spop$) in a population-based method}.
-
-    \subsection{Probabilities of beneficial back-mutations}
-    \begin{center}
-        \captionof{table}{Probability of beneficial back-mutations among all beneficial ones.}
-        \scriptsize
-        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
-            \toprule
-            Population & Species & Watterson's $\thetaSyn$ & $\proba[\SphyBen]$ & $\proba [ \SpopBen ]$ & $\frac{\proba[\SphyBen]}{\proba[ \SpopBen ]}$ & $\proba [ \SpopBen \given \SphyBen]$ & $\proba[\SphyBen\given \SpopBen ]$ \\
-            \midrule
-            \endhead
-            \midrule
-            \multicolumn{8}{r}{{Continued on next page}} \\
-            \midrule
-            \endfoot
-
-            \bottomrule
-            \endlastfoot
-            \rowcolor{LIGHTGREY} Equus c.
-&      Equus caballus &               $ 0.002$ &              $ 0.014$ &              $ 0.061$ &                                          $ 0.235$ &                         $ 0.519$ &                      $ 0.122$ \\
-            Iran &          Bos taurus &               $ 0.002$ &              $ 0.013$ &              $ 0.007$ &                                          $ 1.908$ &                         $ 0.368$ &                      $ 0.702$ \\
-            Uganda &          Bos taurus &               $ 0.005$ &              $ 0.013$ &              $ 0.008$ &                                          $ 1.667$ &                         $ 0.255$ &                      $ 0.425$ \\
-            \rowcolor{LIGHTGREY} Australia &        Capra hircus &               $ 0.003$ &              $ 0.014$ &              $ 0.007$ &                                          $ 2.099$ &                         $ 0.147$ &                      $ 0.308$ \\
-            \rowcolor{LIGHTGREY} France &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.007$ &                                          $ 2.043$ &                         $ 0.149$ &                      $ 0.304$ \\
-            \rowcolor{LIGHTGREY} Iran (C.
-aegagrus) &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.013$ &                                          $ 1.069$ &                         $ 0.147$ &                      $ 0.157$ \\
-            \rowcolor{LIGHTGREY} Iran &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.008$ &                                          $ 1.699$ &                         $ 0.152$ &                      $ 0.258$ \\
-            \rowcolor{LIGHTGREY} Italy &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.006$ &                                          $ 2.160$ &                         $ 0.147$ &                      $ 0.316$ \\
-            \rowcolor{LIGHTGREY} Morocco &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.006$ &                                          $ 2.141$ &                         $ 0.186$ &                      $ 0.398$ \\
-            Iran &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.012$ &                                          $ 1.210$ &                         $ 0.158$ &                      $ 0.191$ \\
-            Iran (O.
-orientalis) &          Ovis aries &               $ 0.009$ &              $ 0.014$ &              $ 0.012$ &                                          $ 1.144$ &                         $ 0.157$ &                      $ 0.180$ \\
-            Iran (O.
-vignei) &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.022$ &                                          $ 0.631$ &                         $ 0.186$ &                      $ 0.118$ \\
-            Various &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.012$ &                                          $ 1.211$ &                         $ 0.156$ &                      $ 0.188$ \\
-            Morocco &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.009$ &                                          $ 1.536$ &                         $ 0.190$ &                      $ 0.292$ \\
-            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.005$ &                                          $ 2.230$ &                         $ 0.282$ &                      $ 0.630$ \\
-            \rowcolor{LIGHTGREY} Central Afr.
-Rep.
-& Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.014$ &                                          $ 0.849$ &                         $ 0.310$ &                      $ 0.263$ \\
-            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.008$ &                                          $ 1.530$ &                         $ 0.298$ &                      $ 0.456$ \\
-            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.008$ &                                          $ 1.384$ &                         $ 0.305$ &                      $ 0.422$ \\
-            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.014$ &                                          $ 0.854$ &                         $ 0.296$ &                      $ 0.253$ \\
-            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus &               $ 0.003$ &              $ 0.012$ &              $ 0.005$ &                                          $ 2.438$ &                         $ 0.285$ &                      $ 0.696$ \\
-            \rowcolor{LIGHTGREY} South Africa  & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.011$ &                                          $ 1.047$ &                         $ 0.323$ &                      $ 0.338$ \\
-            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.006$ &                                          $ 2.070$ &                         $ 0.292$ &                      $ 0.604$ \\
-            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.014$ &                                          $ 0.816$ &                         $ 0.309$ &                      $ 0.252$ \\
-            African &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.015$ &                                          $ 0.765$ &                         $ 0.371$ &                      $ 0.284$ \\
-            Admixed American &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.009$ &                                          $ 1.259$ &                         $ 0.368$ &                      $ 0.464$ \\
-            East Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.012$ &                                          $ 0.973$ &                         $ 0.369$ &                      $ 0.358$ \\
-            European &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.009$ &                                          $ 1.356$ &                         $ 0.368$ &                      $ 0.499$ \\
-            South Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.010$ &                                          $ 1.147$ &                         $ 0.369$ &                      $ 0.423$ \\
-        \end{longtable*}
-    \end{center}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item $\proba [ \SphyBen ]$ (eq.~5) is the probability for a new mutation a beneficial back-mutation.
-        These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1, thus toward a more fit amino-acid.
-        \item $\proba [ \SpopBen ]$ (eq.~15) is the probability for a mutation to be beneficial.
-        These mutations have a selection coefficient at the population-scale larger than 1.
-        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale (the \textit{precision}).
-        \item $\proba [ \SphyBen \given \SpopBen]$ (eq.~14) is the probability for a mutation to a beneficial back-mutations, given it is beneficial (the \textit{recall}).
-        This probability is obtained using Bayes' formula.
-    \end{itemize}
-    \newpage
-
-    \subsection{Precision and recall}
-    \captionof{table}{Precision and recall}
-    \begin{center}
-        \begin{adjustbox}{width=\textwidth}
-            \begin{tabular}{||l|l|r||r|r||r|r||r|r||}
-                \toprule
-                \multicolumn{3}{||c||}{} &
-                \multicolumn{2}{c||}{\shortstack{\textbf{Deleterious mutations} \\ $\bm{\SpopDel \coloneqq \Spop<-1}$ \\ $\bm{\SphyDel \coloneqq \Sphy<-1}$}} &
-                \multicolumn{2}{c||}{\shortstack{\textbf{Nearly-neutral mutations} \\ $\bm{\SpopNeu \coloneqq -1<\Spop<1}$ \\ $\bm{\SphyNeu \coloneqq -1<\Sphy<1}$}} &
-                \multicolumn{2}{c||}{\shortstack{\textbf{Beneficial mutations} \\ $\bm{\SpopBen \coloneqq \Spop>1}$ \\ $\bm{\SphyBen \coloneqq \Sphy>1}$}}
-                \\ \hline
-                \textbf{Population} &
-                \textbf{Species} &
-                $\bm{\thetaSyn}$ &
-                \makecell{\textbf{Precision} \\ $\bm{\proba [\SpopDel \given \SphyDel]}$} &
-                \makecell{\textbf{Recall} \\ $\bm{\proba [\SphyDel \given \SpopDel]}$}           &
-                \makecell{\textbf{Precision}      \\ $\bm{\proba [\SpopNeu \given \SphyNeu]}$}                                    &
-                \makecell{\textbf{Recall}          \\ $\bm{\proba [\SphyNeu \given \SpopNeu]}$}                                  &
-                \makecell{\textbf{Precision}          \\ $\bm{\proba [\SpopBen \given \SphyBen]}$}          &
-                \makecell{\textbf{Recall}        \\ $\bm{\proba [\SphyBen \given \SpopBen]}$}
-                \\   \midrule
-                \rowcolor{LIGHTGREY} Equus c. & Equus caballus        & $ 0.002$ & $ 0.918$ & $ 0.957$ & $ 0.186$ & $ 0.213$ & $ 0.519$ & $ 0.122$ \\
-                Iran               & Bos taurus        & $ 0.002$ & $ 0.924$ & $ 0.965$ & $ 0.565$ & $ 0.356$ & $ 0.368$ & $ 0.702$ \\
-                Uganda              & Bos taurus        & $ 0.005$ & $ 0.943$ & $ 0.961$ & $ 0.516$ & $ 0.396$ & $ 0.255$ & $ 0.425$ \\
-                \rowcolor{LIGHTGREY} Australia            & Capra hircus        & $ 0.003$ & $ 0.941$ & $ 0.964$ & $ 0.592$ & $ 0.434$ & $ 0.147$ & $ 0.308$ \\
-                \rowcolor{LIGHTGREY} France                                    & Capra hircus          & $ 0.004$ & $ 0.940$ & $ 0.963$ & $ 0.571$ & $ 0.418$ & $ 0.149$ & $ 0.304$ \\
-                \rowcolor{LIGHTGREY} Iran (C. aegagrus)                    & Capra hircus          & $ 0.004$ & $ 0.948$ & $ 0.960$ & $ 0.515$ & $ 0.446$ & $ 0.147$ & $ 0.157$ \\
-                \rowcolor{LIGHTGREY} Iran                        & Capra hircus          & $ 0.004$ & $ 0.942$ & $ 0.961$ & $ 0.534$ & $ 0.410$ & $ 0.152$ & $ 0.258$ \\
-                \rowcolor{LIGHTGREY} Italy                                 & Capra hircus          & $ 0.004$ & $ 0.940$ & $ 0.963$ & $ 0.579$ & $ 0.421$ & $ 0.147$ & $ 0.316$ \\
-                \rowcolor{LIGHTGREY} Morocco                                 & Capra hircus          & $ 0.004$ & $ 0.939$ & $ 0.960$ & $ 0.549$ & $ 0.404$ & $ 0.186$ & $ 0.398$ \\
-                Iran           & Ovis aries & $ 0.007$ & $ 0.957$ & $ 0.954$ & $ 0.412$ & $ 0.416$ & $ 0.158$ & $ 0.191$ \\
-                Iran (O. orientalis)  & Ovis aries & $ 0.009$ & $ 0.961$ & $ 0.955$ & $ 0.413$ & $ 0.437$ & $ 0.157$ & $ 0.180$ \\
-                Iran (O. vignei)           & Ovis aries & $ 0.007$ & $ 0.968$ & $ 0.951$ & $ 0.356$ & $ 0.516$ & $ 0.186$ & $ 0.118$ \\
-                Various             & Ovis aries & $ 0.008$ & $ 0.958$ & $ 0.955$ & $ 0.428$ & $ 0.431$ & $ 0.156$ & $ 0.188$ \\
-                Morocco              & Ovis aries & $ 0.008$ & $ 0.960$ & $ 0.953$ & $ 0.447$ & $ 0.460$ & $ 0.190$ & $ 0.292$ \\
-                \rowcolor{LIGHTGREY} Barbados              & Chlorocebus sabaeus & $ 0.004$ & $ 0.931$ & $ 0.969$ & $ 0.628$ & $ 0.402$ & $ 0.282$ & $ 0.630$ \\
-                \rowcolor{LIGHTGREY} Central Afr. Rep.       & Chlorocebus sabaeus & $ 0.006$ & $ 0.941$ & $ 0.964$ & $ 0.514$ & $ 0.408$ & $ 0.310$ & $ 0.263$ \\
-                \rowcolor{LIGHTGREY} Ethiopia        & Chlorocebus sabaeus & $ 0.005$ & $ 0.933$ & $ 0.967$ & $ 0.586$ & $ 0.393$ & $ 0.298$ & $ 0.456$ \\
-                \rowcolor{LIGHTGREY} Gambia             & Chlorocebus sabaeus & $ 0.005$ & $ 0.937$ & $ 0.967$ & $ 0.590$ & $ 0.414$ & $ 0.305$ & $ 0.422$ \\
-                \rowcolor{LIGHTGREY} Kenya                                 & Chlorocebus sabaeus        & $ 0.005$ & $ 0.942$ & $ 0.965$ & $ 0.526$ & $ 0.418$ & $ 0.296$ & $ 0.253$ \\
-                \rowcolor{LIGHTGREY} Nevis                        & Chlorocebus sabaeus        & $ 0.003$ & $ 0.930$ & $ 0.970$ & $ 0.637$ & $ 0.401$ & $ 0.285$ & $ 0.696$ \\
-                \rowcolor{LIGHTGREY} South Africa                              & Chlorocebus sabaeus        & $ 0.006$ & $ 0.937$ & $ 0.964$ & $ 0.530$ & $ 0.393$ & $ 0.323$ & $ 0.338$ \\
-                \rowcolor{LIGHTGREY} Saint Kitts                                & Chlorocebus sabaeus        & $ 0.004$ & $ 0.931$ & $ 0.969$ & $ 0.611$ & $ 0.393$ & $ 0.292$ & $ 0.604$ \\
-                \rowcolor{LIGHTGREY} Zambia                             & Chlorocebus sabaeus        & $ 0.006$ & $ 0.941$ & $ 0.963$ & $ 0.506$ & $ 0.408$ & $ 0.309$ & $ 0.252$ \\
-                African                             & Homo sapiens        & $ 0.002$ & $ 0.896$ & $ 0.968$ & $ 0.550$ & $ 0.297$ & $ 0.371$ & $ 0.284$ \\
-                Admixed American                             & Homo sapiens        & $ 0.002$ & $ 0.890$ & $ 0.979$ & $ 0.710$ & $ 0.333$ & $ 0.368$ & $ 0.464$ \\
-                East Asian                             & Homo sapiens        & $ 0.002$ & $ 0.890$ & $ 0.971$ & $ 0.578$ & $ 0.289$ & $ 0.369$ & $ 0.358$ \\
-                European                             & Homo sapiens        & $ 0.002$ & $ 0.891$ & $ 0.980$ & $ 0.739$ & $ 0.345$ & $ 0.368$ & $ 0.499$ \\
-                South Asian                             & Homo sapiens        & $ 0.002$ & $ 0.895$ & $ 0.981$ & $ 0.740$ & $ 0.356$ & $ 0.369$ & $ 0.423$ \\
-                \bottomrule
-            \end{tabular}
-        \end{adjustbox}
-    \end{center}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item \textit{Precision} is the estimation of the selection coefficient at population scale ($\Spop$) given that $\Sphy$ is known.
-        \item  \textit{Recall} is the estimation of $\Sphy$ given selection coefficient at the population scale ($\Spop$) is known.
-        \item \textit{Recall} for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is thus the proportion of beneficial back-mutations among all beneficial mutations.
-    \end{itemize}
-
-    Altogether, comparing this table to tables 1 and S3, we acknowledge that the exact proportion of beneficial back-mutations among all beneficial ones is different whether we included or not substitutions in the terminal lineage for the estimation of $\Spop$.
-    However, we can still see that beneficial back-mutations are positively selected compared to neutral and deleterious ones, and this result is not sensitive to inclusion of substitutions in the terminal lineage.
-
-    \newpage
-    \section{Discrete distribution of $\Spop$ at the population scale}
-
-    \subsection{polyDFE model D (discrete distribution)}
-    With polyDFE model D, the DFE of non-synonymous mutations is given as a discrete DFE of $K$ categories (instead of a continuous distribution in model C), where the selection coefficients of each category $i$ ($1 \leq i \leq K$) are fixed parameters $\Spop_i$, and each value $\Spop_i$ has a probability $p_i$ (estimated), with $\sum_{i=1}^{K} p_i =1$.
-    We used $K=6$ with $\Spop_1 = -500$, $\Spop_2 = -4$, $\Spop_3 =-1$, $\Spop_4 = 0$, $\Spop_5 = 1$, $\Spop_6 = 4$.\\
-    For each class of selection $\Sphyclass$, the parameters $p_i$ ($i \in \{ 1 \leq i \leq 6 \}$) were used to compute $\proba [ \SpopDel \given  \Sphyclass] $, $\proba [ \SpopNeu \given \Sphyclass]$, and $\proba [ \SpopBen \given \Sphyclass]$ as:
-    \begin{align}
-        \proba [ \SpopDel \given  \Sphyclass] &= \proba [ \Spop < -1 \given \Sphyclass ] = p_1 + p_2 \label{eq:polyProbaDel} \\
-        \proba [ \SpopNeu \given \Sphyclass] &= \proba [ -1 < \Spop < 1 \given \Sphyclass ] = p_3 + p_4 + p_5,  \\
-        \proba [ \SpopBen \given \Sphyclass] &= p_6. \label{eq:polyProbaAdv}
-    \end{align}
-
-    \subsection{Probabilities of beneficial back-mutations}
-    \begin{center}
-        \captionof{table}{Probability of beneficial back-mutations among all beneficial ones.}
-        \scriptsize
-        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
-            \toprule
-            Population & Species & Watterson's $\thetaSyn$ & $\proba[\SphyBen]$ & $\proba [ \SpopBen ]$ & $\frac{\proba[\SphyBen]}{\proba[ \SpopBen ]}$ & $\proba [ \SpopBen \given \SphyBen]$ & $\proba[\SphyBen\given \SpopBen ]$ \\
-            \midrule
-            \endhead
-            \midrule
-            \multicolumn{8}{r}{{Continued on next page}} \\
-            \midrule
-            \endfoot
-
-            \bottomrule
-            \endlastfoot
-            \rowcolor{LIGHTGREY} Equus c.
-&      Equus caballus &               $ 0.002$ &              $ 0.014$ &              $ 0.006$ &                                          $ 2.230$ &                         $ 0.141$ &                      $ 0.316$ \\
-            Iran &          Bos taurus &               $ 0.002$ &              $ 0.013$ &              $ 0.006$ &                                          $ 2.200$ &                         $ 0.136$ &                      $ 0.298$ \\
-            Uganda &          Bos taurus &               $ 0.005$ &              $ 0.013$ &              $ 0.011$ &                                          $ 1.177$ &                         $ 0.138$ &                      $ 0.162$ \\
-            \rowcolor{LIGHTGREY} Australia &        Capra hircus &               $ 0.003$ &              $ 0.014$ &              $ 0.002$ &                                          $ 6.467$ &                         $ 0.135$ &                      $ 0.871$ \\
-            \rowcolor{LIGHTGREY} France &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.002$ &                                          $ 6.407$ &                         $ 0.132$ &                      $ 0.845$ \\
-            \rowcolor{LIGHTGREY} Iran (C.
-aegagrus) &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.002$ &                                          $ 5.993$ &                         $ 0.129$ &                      $ 0.772$ \\
-            \rowcolor{LIGHTGREY} Iran &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.004$ &                                          $ 3.656$ &                         $ 0.138$ &                      $ 0.506$ \\
-            \rowcolor{LIGHTGREY} Italy &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.002$ &                                          $ 6.216$ &                         $ 0.127$ &                      $ 0.787$ \\
-            \rowcolor{LIGHTGREY} Morocco &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.002$ &                                          $ 6.019$ &                         $ 0.141$ &                      $ 0.848$ \\
-            Iran &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.588$ &                         $ 0.148$ &                      $ 0.087$ \\
-            Iran (O.
-orientalis) &          Ovis aries &               $ 0.009$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.569$ &                         $ 0.143$ &                      $ 0.081$ \\
-            Iran (O.
-vignei) &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.587$ &                         $ 0.127$ &                      $ 0.075$ \\
-            Various &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.588$ &                         $ 0.146$ &                      $ 0.086$ \\
-            Morocco &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.025$ &                                          $ 0.564$ &                         $ 0.145$ &                      $ 0.082$ \\
-            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.002$ &                                          $ 5.689$ &                         $ 0.170$ &                      $ 0.968$ \\
-            \rowcolor{LIGHTGREY} Central Afr.
-Rep.
-& Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.005$ &                                          $ 2.142$ &                         $ 0.156$ &                      $ 0.334$ \\
-            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.002$ &                                          $ 5.910$ &                         $ 0.160$ &                      $ 0.945$ \\
-            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.006$ &                                          $ 1.850$ &                         $ 0.157$ &                      $ 0.290$ \\
-            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.004$ &                                          $ 2.802$ &                         $ 0.163$ &                      $ 0.456$ \\
-            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus &               $ 0.003$ &              $ 0.012$ &              $ 0.002$ &                                          $ 5.396$ &                         $ 0.169$ &                      $ 0.910$ \\
-            \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.005$ &                                          $ 2.154$ &                         $ 0.153$ &                      $ 0.329$ \\
-            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.002$ &                                          $ 5.094$ &                         $ 0.164$ &                      $ 0.834$ \\
-            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.006$ &                                          $ 1.952$ &                         $ 0.153$ &                      $ 0.298$ \\
-            African &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.014$ &                                          $ 0.869$ &                         $ 0.141$ &                      $ 0.123$ \\
-            Admixed American &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.010$ &                                          $ 1.130$ &                         $ 0.161$ &                      $ 0.182$ \\
-            East Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.007$ &                                          $ 1.602$ &                         $ 0.162$ &                      $ 0.259$ \\
-            European &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.009$ &                                          $ 1.336$ &                         $ 0.163$ &                      $ 0.217$ \\
-            South Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.009$ &                                          $ 1.342$ &                         $ 0.163$ &                      $ 0.219$ \\
-        \end{longtable*}
-    \end{center}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item $\proba [ \SphyBen ]$ (eq.~5) is the probability for a new mutation a beneficial back-mutation.
-        These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1, thus toward a more fit amino-acid.
-        \item $\proba [ \SpopBen ]$ (eq.~15) is the probability for a mutation to be beneficial.
-        These mutations have a selection coefficient at the population-scale larger than 1.
-        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale (the \textit{precision}).
-        \item $\proba [ \SphyBen \given \SpopBen]$ (eq.~14) is the probability for a mutation to a beneficial back-mutations, given it is beneficial (the \textit{recall}).
-        This probability is obtained using Bayes' formula.
-    \end{itemize}
-    \newpage
-
-    \subsection{Precision and recall}
-    \captionof{table}{Precision and recall}
-    \begin{center}
-        \begin{adjustbox}{width=\textwidth}
-            \begin{tabular}{||l|l|r||r|r||r|r||r|r||}
-                \toprule
-                \multicolumn{3}{||c||}{} &
-                \multicolumn{2}{c||}{\shortstack{\textbf{Deleterious mutations} \\ $\bm{\SpopDel \coloneqq \Spop<-1}$ \\ $\bm{\SphyDel \coloneqq \Sphy<-1}$}} &
-                \multicolumn{2}{c||}{\shortstack{\textbf{Nearly-neutral mutations} \\ $\bm{\SpopNeu \coloneqq -1<\Spop<1}$ \\ $\bm{\SphyNeu \coloneqq -1<\Sphy<1}$}} &
-                \multicolumn{2}{c||}{\shortstack{\textbf{Beneficial mutations} \\ $\bm{\SpopBen \coloneqq \Spop>1}$ \\ $\bm{\SphyBen \coloneqq \Sphy>1}$}}
-                \\ \hline
-                \textbf{Population} &
-                \textbf{Species} &
-                $\bm{\thetaSyn}$ &
-                \makecell{\textbf{Precision} \\ $\bm{\proba [\SpopDel \given \SphyDel]}$} &
-                \makecell{\textbf{Recall} \\ $\bm{\proba [\SphyDel \given \SpopDel]}$}           &
-                \makecell{\textbf{Precision}      \\ $\bm{\proba [\SpopNeu \given \SphyNeu]}$}                                    &
-                \makecell{\textbf{Recall}          \\ $\bm{\proba [\SphyNeu \given \SpopNeu]}$}                                  &
-                \makecell{\textbf{Precision}          \\ $\bm{\proba [\SpopBen \given \SphyBen]}$}          &
-                \makecell{\textbf{Recall}        \\ $\bm{\proba [\SphyBen \given \SpopBen]}$}
-                \\   \midrule
-                \rowcolor{LIGHTGREY} Equus c. & Equus caballus        & $ 0.002$ & $ 0.895$ & $ 0.969$ & $ 0.645$ & $ 0.315$ & $ 0.141$ & $ 0.316$ \\
-                Iran               & Bos taurus        & $ 0.002$ & $ 0.878$ & $ 0.968$ & $ 0.632$ & $ 0.286$ & $ 0.136$ & $ 0.298$ \\
-                Uganda              & Bos taurus        & $ 0.005$ & $ 0.951$ & $ 0.963$ & $ 0.597$ & $ 0.508$ & $ 0.138$ & $ 0.162$ \\
-                \rowcolor{LIGHTGREY} Australia            & Capra hircus        & $ 0.003$ & $ 0.895$ & $ 0.981$ & $ 0.830$ & $ 0.379$ & $ 0.135$ & $ 0.871$ \\
-                \rowcolor{LIGHTGREY} France                                    & Capra hircus          & $ 0.004$ & $ 0.896$ & $ 0.978$ & $ 0.801$ & $ 0.373$ & $ 0.132$ & $ 0.845$ \\
-                \rowcolor{LIGHTGREY} Iran (C. aegagrus)                    & Capra hircus          & $ 0.004$ & $ 0.913$ & $ 0.971$ & $ 0.711$ & $ 0.383$ & $ 0.129$ & $ 0.772$ \\
-                \rowcolor{LIGHTGREY} Iran                        & Capra hircus          & $ 0.004$ & $ 0.949$ & $ 0.968$ & $ 0.655$ & $ 0.481$ & $ 0.138$ & $ 0.506$ \\
-                \rowcolor{LIGHTGREY} Italy                                 & Capra hircus          & $ 0.004$ & $ 0.894$ & $ 0.979$ & $ 0.814$ & $ 0.373$ & $ 0.127$ & $ 0.787$ \\
-                \rowcolor{LIGHTGREY} Morocco                                 & Capra hircus          & $ 0.004$ & $ 0.951$ & $ 0.972$ & $ 0.709$ & $ 0.504$ & $ 0.141$ & $ 0.848$ \\
-                Iran           & Ovis aries & $ 0.007$ & $ 0.980$ & $ 0.956$ & $ 0.456$ & $ 0.799$ & $ 0.148$ & $ 0.087$ \\
-                Iran (O. orientalis)  & Ovis aries & $ 0.009$ & $ 0.979$ & $ 0.955$ & $ 0.454$ & $ 0.798$ & $ 0.143$ & $ 0.081$ \\
-                Iran (O. vignei)           & Ovis aries & $ 0.007$ & $ 0.974$ & $ 0.957$ & $ 0.483$ & $ 0.729$ & $ 0.127$ & $ 0.075$ \\
-                Various             & Ovis aries & $ 0.008$ & $ 0.979$ & $ 0.958$ & $ 0.500$ & $ 0.813$ & $ 0.146$ & $ 0.086$ \\
-                Morocco              & Ovis aries & $ 0.008$ & $ 0.980$ & $ 0.952$ & $ 0.392$ & $ 0.774$ & $ 0.145$ & $ 0.082$ \\
-                \rowcolor{LIGHTGREY} Barbados              & Chlorocebus sabaeus & $ 0.004$ & $ 0.880$ & $ 0.984$ & $ 0.854$ & $ 0.354$ & $ 0.170$ & $ 0.968$ \\
-                \rowcolor{LIGHTGREY} Central Afr. Rep.       & Chlorocebus sabaeus & $ 0.006$ & $ 0.932$ & $ 0.968$ & $ 0.634$ & $ 0.413$ & $ 0.156$ & $ 0.334$ \\
-                \rowcolor{LIGHTGREY} Ethiopia        & Chlorocebus sabaeus & $ 0.005$ & $ 0.877$ & $ 0.980$ & $ 0.810$ & $ 0.337$ & $ 0.160$ & $ 0.945$ \\
-                \rowcolor{LIGHTGREY} Gambia             & Chlorocebus sabaeus & $ 0.005$ & $ 0.947$ & $ 0.977$ & $ 0.745$ & $ 0.518$ & $ 0.157$ & $ 0.290$ \\
-                \rowcolor{LIGHTGREY} Kenya                                 & Chlorocebus sabaeus        & $ 0.005$ & $ 0.903$ & $ 0.969$ & $ 0.664$ & $ 0.343$ & $ 0.163$ & $ 0.456$ \\
-                \rowcolor{LIGHTGREY} Nevis                        & Chlorocebus sabaeus        & $ 0.003$ & $ 0.880$ & $ 0.984$ & $ 0.861$ & $ 0.357$ & $ 0.169$ & $ 0.910$ \\
-                \rowcolor{LIGHTGREY} South Africa                              & Chlorocebus sabaeus        & $ 0.006$ & $ 0.931$ & $ 0.967$ & $ 0.615$ & $ 0.401$ & $ 0.153$ & $ 0.329$ \\
-                \rowcolor{LIGHTGREY} Saint Kitts                                & Chlorocebus sabaeus        & $ 0.004$ & $ 0.883$ & $ 0.982$ & $ 0.834$ & $ 0.355$ & $ 0.164$ & $ 0.834$ \\
-                \rowcolor{LIGHTGREY} Zambia                             & Chlorocebus sabaeus        & $ 0.006$ & $ 0.896$ & $ 0.969$ & $ 0.659$ & $ 0.332$ & $ 0.153$ & $ 0.298$ \\
-                African                             & Homo sapiens        & $ 0.002$ & $ 0.946$ & $ 0.971$ & $ 0.630$ & $ 0.486$ & $ 0.141$ & $ 0.123$ \\
-                Admixed American                             & Homo sapiens        & $ 0.002$ & $ 0.929$ & $ 0.972$ & $ 0.636$ & $ 0.410$ & $ 0.161$ & $ 0.182$ \\
-                East Asian                             & Homo sapiens        & $ 0.002$ & $ 0.937$ & $ 0.973$ & $ 0.647$ & $ 0.429$ & $ 0.162$ & $ 0.259$ \\
-                European                             & Homo sapiens        & $ 0.002$ & $ 0.937$ & $ 0.973$ & $ 0.643$ & $ 0.433$ & $ 0.163$ & $ 0.217$ \\
-                South Asian                             & Homo sapiens        & $ 0.002$ & $ 0.939$ & $ 0.972$ & $ 0.639$ & $ 0.439$ & $ 0.163$ & $ 0.219$ \\
-                \bottomrule
-            \end{tabular}
-        \end{adjustbox}
-    \end{center}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item \textit{Precision} is the estimation of the selection coefficient at population scale ($\Spop$) given that $\Sphy$ is known.
-        \item \textit{Recall} is the estimation of $\Sphy$ given selection coefficient at the population scale ($\Spop$) is known.
-        \item \textit{Recall} for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is thus the proportion of beneficial back-mutations among all beneficial mutations.
-    \end{itemize}
-
-    Altogether, comparing this table to tables 1 and S3, we acknowledge that the exact proportion of beneficial back-mutations among all beneficial ones is dependent on the model used to estimate the DFE.
-    However, we can still see that beneficial back-mutations are positively selected compared to neutral and deleterious ones, and this result is not sensitive to the underlying DFE at the population scale.
-
-    %\section{References}
-    %\printbibliography[heading=none]
-
-    %    \section{Distribution of fitness effects}
-    %    \captionof{figure}{~}
-    %    \begin{minipage}{0.49\linewidth}
-    %        \includegraphics[width=\linewidth, page=1]{artworks/2bins.Yeast.experimentalDFE.pdf}
-    %    \end{minipage}
-    %    \begin{minipage}{0.49\linewidth}
-    %        \includegraphics[width=\linewidth, page=1]{artworks/2bins.AFR.histogramDFE.pdf}
-    %    \end{minipage}
-    %    Left panel: distribution of fitness effects experimentally determined in Yeast, data obtained in \textcite{shen_synonymous_2022}.
-    %    Right panel:  distribution of fitness effects ($\Sphy$) as predicted with mutation-selection codon models, from reconstructed ancestral genome in \textit{Homo sapiens}.
-    %    The DFE predicted with mutation-selection codon models has a negative mode, consistently with experimental DFEs, meaning that most mutations are effectively deleterious.
+    \printbibliography
 \end{document}

### 2024-12-16 manuscript/S3 File.tex
Split Supplementary materials into 4 files.

--- 2023-05-03 manuscript/supp-mat.tex
@@
     \maketitle
-    \part*{Supplementary materials}
+    \part*{S3 File}
+    \vspace{-1em}
     \tableofcontents
+    \listoffigures
     \clearpage
 
-    \section{Beneficial mutations in the terminal lineages and populations}\label{sec:beneficial-mutations}
+    \section{Contrasting selection at the phylogenetic and population-genetic scales}
 
-    \subsection{Mutation-selection codon models}
-    \label{sec:site-specific-mutation-selection-codon-models}
-    In \textit{BayesCode} (\url{https://github.com/ThibaultLatrille/bayescode}), we ran the mutation-selection codon models \textit{mutselomega} for 2000 points of MCMC with the options:
-    \begin{scriptsize}
-        \begin{verbatim}
- mutselomega ---omegashift 0.0 --ncat 30 -a my_alignment.phy -t my_tree.newick -u 2000 my_genename
-        \end{verbatim}
-    \end{scriptsize}
-    The collection of site-specific fitness profiles ($\UniDimArray{F^{(i)}}, \forall i$) are then obtained by running \textit{readmutselomega}, reading 1000 points of MCMC (first 1000 are considered as burn-in) with the options:
-    \begin{scriptsize}
-        \begin{verbatim}
- readmutselomega --every 1 --until 2000 --burnin 1000 --ss my_genename
-        \end{verbatim}
-    \end{scriptsize}
-    The gene-specific $4 \times 4$ nucleotide mutation rate matrix ($\UniDimArray{\mu}$) is also obtained by running \textit{readmutselomega}, reading 1000 points of MCMC (first 1000 are considered as burn-in) with the options:
-    \begin{scriptsize}
-        \begin{verbatim}
- readmutselomega --every 1 --until 2000 --burnin 1000 --nuc my_genename
-        \end{verbatim}
-    \end{scriptsize}
+    \subsection{Selection at the population-genetic scale}
+    The proportion of deleterious ($\ProbaPopDel$), nearly-neutral ($\ProbaPopNeu$) and of beneficial ($\ProbaPopBen$) mutations estimated at the population-genetic scale across the different populations is shown for each class of selection:
+    $\SphyDel$ (Figure~\ref{fig:pop-neg}), $\SphyNeu$ (Figure~\ref{fig:pop-weak}) and $\SphyBen$ (Figure~\ref{fig:pop-pos}).
 
-    \subsection{Summary tables}\label{subsec:summary-table-mutsel}
-
-    \subsubsection{$\dnds$ for deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial back-mutations ($\SphyBen$)}
     \begin{center}
-        \captionof{table}{$\dnds$ for deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial back-mutations ($\SphyBen$).}
-        \scriptsize
-        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
-            \toprule
-            Population &             Species & Watterson's $\thetaSyn$  & $\proba_{div}[ \SphyBen ]$ & $\dnds $ & $\dn ( \SphyDel ) / \ds$ & $\dn ( \SphyNeu ) / \ds$ & $\dn ( \SphyBen ) / \ds$ \\
-            \midrule
-            \endhead
-            \midrule
-            \multicolumn{8}{r}{{Continued on next page}} \\
-            \midrule
-            \endfoot
-
-            \bottomrule
-            \endlastfoot
-            \rowcolor{LIGHTGREY} Equus c.
-&      Equus caballus &               $ 0.002$ &                    $ 0.118$ &  $ 0.147$ &            $ 0.075$ &                $ 0.823$ &           $ 1.203$ \\
-            Iran &          Bos taurus &               $ 0.002$ &                    $ 0.123$ &  $ 0.131$ &            $ 0.074$ &                $ 0.627$ &           $ 1.206$ \\
-            Uganda &          Bos taurus &               $ 0.005$ &                    $ 0.125$ &  $ 0.134$ &            $ 0.075$ &                $ 0.637$ &           $ 1.252$ \\
-            \rowcolor{LIGHTGREY} Australia &        Capra hircus &               $ 0.003$ &                    $ 0.121$ &  $ 0.125$ &            $ 0.068$ &                $ 0.629$ &           $ 1.099$ \\
-            \rowcolor{LIGHTGREY} France &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.126$ &            $ 0.068$ &                $ 0.633$ &           $ 1.102$ \\
-            \rowcolor{LIGHTGREY} Iran (C.
-aegagrus) &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.125$ &            $ 0.068$ &                $ 0.630$ &           $ 1.100$ \\
-            \rowcolor{LIGHTGREY} Iran &        Capra hircus &               $ 0.004$ &                    $ 0.121$ &  $ 0.125$ &            $ 0.067$ &                $ 0.630$ &           $ 1.108$ \\
-            \rowcolor{LIGHTGREY} Italy &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.126$ &            $ 0.068$ &                $ 0.634$ &           $ 1.102$ \\
-            \rowcolor{LIGHTGREY} Morocco &        Capra hircus &               $ 0.004$ &                    $ 0.122$ &  $ 0.125$ &            $ 0.067$ &                $ 0.631$ &           $ 1.112$ \\
-            Iran &          Ovis aries &               $ 0.007$ &                    $ 0.109$ &  $ 0.146$ &            $ 0.091$ &                $ 0.616$ &           $ 1.148$ \\
-            Iran (O. orientalis) &          Ovis aries &               $ 0.009$ &                    $ 0.108$ &  $ 0.148$ &            $ 0.093$ &                $ 0.617$ &           $ 1.145$ \\
-            Iran (O. vignei) &          Ovis aries &               $ 0.007$ &                    $ 0.109$ &  $ 0.146$ &            $ 0.091$ &                $ 0.617$ &           $ 1.134$ \\
-            Various &          Ovis aries &               $ 0.008$ &                    $ 0.107$ &  $ 0.148$ &            $ 0.093$ &                $ 0.617$ &           $ 1.134$ \\
-            Morocco &          Ovis aries &               $ 0.008$ &                    $ 0.108$ &  $ 0.148$ &            $ 0.093$ &                $ 0.619$ &           $ 1.149$ \\
-            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus &               $ 0.004$ &                    $ 0.122$ &  $ 0.133$ &            $ 0.071$ &                $ 0.696$ &           $ 1.397$ \\
-            \rowcolor{LIGHTGREY} Central Afr.
-Rep.
-& Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.124$ &  $ 0.134$ &            $ 0.071$ &                $ 0.701$ &           $ 1.431$ \\
-            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.124$ &  $ 0.134$ &            $ 0.071$ &                $ 0.699$ &           $ 1.422$ \\
-            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.123$ &  $ 0.134$ &            $ 0.071$ &                $ 0.703$ &           $ 1.411$ \\
-            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.123$ &  $ 0.134$ &            $ 0.071$ &                $ 0.699$ &           $ 1.419$ \\
-            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus &               $ 0.003$ &                    $ 0.123$ &  $ 0.133$ &            $ 0.071$ &                $ 0.699$ &           $ 1.407$ \\
-            \rowcolor{LIGHTGREY} South Africa  & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.125$ &  $ 0.134$ &            $ 0.070$ &                $ 0.704$ &           $ 1.447$ \\
-            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &                    $ 0.123$ &  $ 0.133$ &            $ 0.070$ &                $ 0.699$ &           $ 1.413$ \\
-            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.123$ &  $ 0.134$ &            $ 0.071$ &                $ 0.699$ &           $ 1.410$ \\
-            African &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &            $ 0.118$ &                $ 0.865$ &           $ 1.609$ \\
-            Admixed American &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &            $ 0.118$ &                $ 0.865$ &           $ 1.607$ \\
-            East Asian &        Homo sapiens &               $ 0.002$ &                    $ 0.098$ &  $ 0.192$ &            $ 0.118$ &                $ 0.869$ &           $ 1.607$ \\
-            European &        Homo sapiens &               $ 0.002$ &                    $ 0.098$ &  $ 0.192$ &            $ 0.118$ &                $ 0.865$ &           $ 1.598$ \\
-            South Asian &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &            $ 0.118$ &                $ 0.867$ &           $ 1.610$ \\
-        \end{longtable*}
-    \end{center}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item $\proba_{div}[\SphyBen]$ is the proportion of substitutions in the terminal branch that are $\SphyBen$.
-        \item $\dn(\SphyDel) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are $\SphyDel$.
-        \item $\dn(\SphyNeu) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are $\SphyNeu$.
-        \item $\dn(\SphyBen) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are $\SphyBen$.
-    \end{itemize}
-
-    \newpage
-
-    \subsubsection{$\dnds$ over-estimation due to beneficial back-mutations}
-    \begin{center}
-        \captionof{table}{$\dnds$ over-estimation due to beneficial back-mutations.}
-        \scriptsize
-        \begin{longtable*}{|l|l|r|r|r|r|r|}
-            \toprule
-            Population & Species & Watterson's $\thetaSyn$ & $\proba_{div}[\Sphy > 1]$ & $\dnds $ & $\dn(\Sphy < 1) / \ds$ & $\delta(\dnds )$ \\
-            \midrule
-            \endhead
-            \midrule
-            \multicolumn{7}{r}{{Continued on next page}} \\
-            \midrule
-            \endfoot
-
-            \bottomrule
-            \endlastfoot
-            \rowcolor{LIGHTGREY} Equus c. &      Equus caballus &               $ 0.002$ &                    $ 0.118$ &  $ 0.147$ &           $ 0.131$ &     $  10.5$ \\
-            Iran &          Bos taurus &               $ 0.002$ &                    $ 0.123$ &  $ 0.131$ &           $ 0.117$ &     $  11.1$ \\
-            Uganda &          Bos taurus &               $ 0.005$ &                    $ 0.125$ &  $ 0.134$ &           $ 0.118$ &     $  11.3$ \\
-            \rowcolor{LIGHTGREY} Australia &        Capra hircus &               $ 0.003$ &                    $ 0.121$ &  $ 0.125$ &           $ 0.111$ &     $  10.8$ \\
-            \rowcolor{LIGHTGREY} France &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.126$ &           $ 0.112$ &     $  10.8$ \\
-            \rowcolor{LIGHTGREY} Iran (C. aegagrus) &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.125$ &           $ 0.111$ &     $  10.8$ \\
-            \rowcolor{LIGHTGREY} Iran &        Capra hircus &               $ 0.004$ &                    $ 0.121$ &  $ 0.125$ &           $ 0.111$ &     $  10.9$ \\
-            \rowcolor{LIGHTGREY} Italy &        Capra hircus &               $ 0.004$ &                    $ 0.120$ &  $ 0.126$ &           $ 0.112$ &     $  10.8$ \\
-            \rowcolor{LIGHTGREY} Morocco &        Capra hircus &               $ 0.004$ &                    $ 0.122$ &  $ 0.125$ &           $ 0.111$ &     $  11.0$ \\
-            Iran &          Ovis aries &               $ 0.007$ &                    $ 0.109$ &  $ 0.146$ &           $ 0.132$ &     $ 9.671$ \\
-            Iran (O. orientalis) &          Ovis aries &               $ 0.009$ &                    $ 0.108$ &  $ 0.148$ &           $ 0.134$ &     $ 9.516$ \\
-            Iran (O. vignei) &          Ovis aries &               $ 0.007$ &                    $ 0.109$ &  $ 0.146$ &           $ 0.132$ &     $ 9.598$ \\
-            Various &          Ovis aries &               $ 0.008$ &                    $ 0.107$ &  $ 0.148$ &           $ 0.134$ &     $ 9.439$ \\
-            Morocco &          Ovis aries &               $ 0.008$ &                    $ 0.108$ &  $ 0.148$ &           $ 0.134$ &     $ 9.582$ \\
-            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus &               $ 0.004$ &                    $ 0.122$ &  $ 0.133$ &           $ 0.118$ &     $  11.2$ \\
-            \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.124$ &  $ 0.134$ &           $ 0.119$ &     $  11.3$ \\
-            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.124$ &  $ 0.134$ &           $ 0.118$ &     $  11.3$ \\
-            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.123$ &  $ 0.134$ &           $ 0.119$ &     $  11.2$ \\
-            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus &               $ 0.005$ &                    $ 0.123$ &  $ 0.134$ &           $ 0.119$ &     $  11.3$ \\
-            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus &               $ 0.003$ &                    $ 0.123$ &  $ 0.133$ &           $ 0.118$ &     $  11.3$ \\
-            \rowcolor{LIGHTGREY} South Africa  & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.125$ &  $ 0.134$ &           $ 0.118$ &     $  11.5$ \\
-            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &                    $ 0.123$ &  $ 0.133$ &           $ 0.118$ &     $  11.3$ \\
-            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus &               $ 0.006$ &                    $ 0.123$ &  $ 0.134$ &           $ 0.119$ &     $  11.2$ \\
-            African &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &           $ 0.175$ &     $ 8.799$ \\
-            Admixed American &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &           $ 0.175$ &     $ 8.780$ \\
-            East Asian &        Homo sapiens &               $ 0.002$ &                    $ 0.098$ &  $ 0.192$ &           $ 0.175$ &     $ 8.768$ \\
-            European &        Homo sapiens &               $ 0.002$ &                    $ 0.098$ &  $ 0.192$ &           $ 0.175$ &     $ 8.728$ \\
-            South Asian &        Homo sapiens &               $ 0.002$ &                    $ 0.099$ &  $ 0.192$ &           $ 0.175$ &     $ 8.788$ \\
-        \end{longtable*}
-    \end{center}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item $\proba_{div}[\SphyBen]$ is the proportion of substitutions in the terminal branch that are $\SphyBen$.
-        \item $\dnds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions estimated for all the non-synonymous substitutions in the terminal branch.
-        \item $\dn(\Sphy < 1) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are not $\SphyBen$.
-        This is the estimated divergence when we removed beneficial back-mutations.
-        \item $\delta(\dnds)$ (eq.~7) is the fraction of the divergence ($\dnds$) that is over-estimated, $\dnds$ is compared to the estimated divergence when we removed beneficial back-mutations $\dn(\Sphy < 1) / \ds$.
-    \end{itemize}
-    We estimated that between 9 and 11\% of $\dnds$ is over-estimated, corresponding to beneficial back-mutation inflating the $\dnds$ statistic.
-
-    \newpage
-
-    \subsubsection{Probabilities of beneficial back-mutations}
-    \begin{center}
-        \captionof{table}{Probability of beneficial back-mutations among all beneficial ones.}
-        \scriptsize
-        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
-            \toprule
-            Population & Species & Watterson's $\thetaSyn$ & $\proba[\SphyBen]$ & $\proba [ \SpopBen ]$ & $\frac{\proba[\SphyBen]}{\proba[ \SpopBen ]}$ & $\proba [ \SpopBen \given \SphyBen]$ & $\proba[\SphyBen\given \SpopBen ]$ \\
-            \midrule
-            \endhead
-            \midrule
-            \multicolumn{8}{r}{{Continued on next page}} \\
-            \midrule
-            \endfoot
-
-            \bottomrule
-            \endlastfoot
-            \rowcolor{LIGHTGREY} Equus c.
-&      Equus caballus &               $ 0.002$ &              $ 0.014$ &              $ 0.010$ &                                          $ 1.395$ &                         $ 0.580$ &                      $ 0.809$ \\
-            Iran &          Bos taurus &               $ 0.002$ &              $ 0.013$ &              $ 0.041$ &                                          $ 0.323$ &                         $ 0.857$ &                      $ 0.277$ \\
-            Uganda &          Bos taurus &               $ 0.005$ &              $ 0.013$ &              $ 0.013$ &                                          $ 0.991$ &                         $ 0.488$ &                      $ 0.483$ \\
-            \rowcolor{LIGHTGREY} Australia &        Capra hircus &               $ 0.003$ &              $ 0.014$ &              $ 0.026$ &                                          $ 0.532$ &                         $ 0.368$ &                      $ 0.196$ \\
-            \rowcolor{LIGHTGREY} France &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.572$ &                         $ 0.368$ &                      $ 0.211$ \\
-            \rowcolor{LIGHTGREY} Iran (C.
-aegagrus) &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.026$ &                                          $ 0.516$ &                         $ 0.221$ &                      $ 0.114$ \\
-            \rowcolor{LIGHTGREY} Iran &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.573$ &                         $ 0.368$ &                      $ 0.211$ \\
-            \rowcolor{LIGHTGREY} Italy &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.017$ &                                          $ 0.814$ &                         $ 0.270$ &                      $ 0.220$ \\
-            \rowcolor{LIGHTGREY} Morocco &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.018$ &                                          $ 0.751$ &                         $ 0.368$ &                      $ 0.276$ \\
-            Iran &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.006$ &                                          $ 2.321$ &                         $ 0.169$ &                      $ 0.392$ \\
-            Iran (O.
-orientalis) &          Ovis aries &               $ 0.009$ &              $ 0.014$ &              $ 0.012$ &                                          $ 1.178$ &                         $ 0.153$ &                      $ 0.180$ \\
-            Iran (O.
-vignei) &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.020$ &                                          $ 0.683$ &                         $ 0.195$ &                      $ 0.133$ \\
-            Various &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.012$ &                                          $ 1.201$ &                         $ 0.190$ &                      $ 0.228$ \\
-            Morocco &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.005$ &                                          $ 2.589$ &                         $ 0.136$ &                      $ 0.353$ \\
-            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.022$ &                                          $ 0.541$ &                         $ 0.565$ &                      $ 0.306$ \\
-            \rowcolor{LIGHTGREY} Central Afr.
-Rep.
-& Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.018$ &                                          $ 0.639$ &                         $ 0.429$ &                      $ 0.274$ \\
-            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.022$ &                                          $ 0.516$ &                         $ 0.462$ &                      $ 0.239$ \\
-            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.007$ &                                          $ 1.592$ &                         $ 0.486$ &                      $ 0.774$ \\
-            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.023$ &                                          $ 0.508$ &                         $ 0.478$ &                      $ 0.243$ \\
-            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus &               $ 0.003$ &              $ 0.012$ &              $ 0.015$ &                                          $ 0.762$ &                         $ 0.516$ &                      $ 0.393$ \\
-            \rowcolor{LIGHTGREY} South Africa  & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.016$ &                                          $ 0.734$ &                         $ 0.490$ &                      $ 0.360$ \\
-            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.016$ &                                          $ 0.713$ &                         $ 0.515$ &                      $ 0.367$ \\
-            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.023$ &                                          $ 0.500$ &                         $ 0.499$ &                      $ 0.249$ \\
-            African &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.025$ &                                          $ 0.470$ &                         $ 0.678$ &                      $ 0.319$ \\
-            Admixed American &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.021$ &                                          $ 0.569$ &                         $ 0.635$ &                      $ 0.361$ \\
-            East Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.031$ &                                          $ 0.381$ &                         $ 0.611$ &                      $ 0.233$ \\
-            European &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.034$ &                                          $ 0.350$ &                         $ 0.619$ &                      $ 0.217$ \\
-            South Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.033$ &                                          $ 0.354$ &                         $ 0.628$ &                      $ 0.222$ \\
-        \end{longtable*}
-    \end{center}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item $\proba [ \SphyBen ]$ (eq.~5) is the probability for a new mutation to be a beneficial back-mutation.
-        These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1, thus toward a more fit amino-acid.
-        \item $\proba [ \SpopBen ]$ (eq.~15) is the probability for a mutation to be beneficial.
-        These mutations have a selection coefficient at the population-scale larger than 1.
-        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale (the \textit{precision}).
-        \item $\proba [ \SphyBen \given \SpopBen]$ (eq.~14) is the probability for a mutation to a beneficial back-mutations, given it is beneficial at the population scale (the \textit{recall}).
-        This probability is obtained using Bayes' formula.
-    \end{itemize}
-    \newpage
-
-    \subsection{Replicability across mammals}
-    The proportion of deleterious ($\ProbaPopDel$), nearly-neutral ($\ProbaPopNeu$) and of beneficial ($\ProbaPopBen$) mutations estimated at the population-genetic scale across the different populations is shown for each class of selection ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$).
-
-    \captionof{figure}{Estimation of selection at the population scale for $\SphyDel$ mutations}
+        \begin{minipage}{0.75\linewidth}
             \begin{minipage}{0.9\linewidth}
@@
             \end{minipage}
+        \end{minipage}
+    \captionof{figure}[Estimation of selection at the population scale for $\SphyDel$ mutations.]{\textbf{Estimation of selection at the population scale for $\bm{\SphyDel}$ mutations.} Each stack bar corresponds to the DFE of new mutations predicted to be $\SphyDel$  by the mutation selection model, in a given population.
+The dashed area represents the proportion of deleterious mutations ($\SpopDel$), the gray area that of neutral mutations ($\SpopNeu$), and the yellow area that of beneficial mutations ($\SpopBen$).\label{fig:pop-neg}}
+    \end{center}
 
-    \captionof{figure}{Estimation of selection at the population scale for $\SphyNeu$ mutations}
+    \begin{center}
+        \begin{minipage}{0.75\linewidth}
             \begin{minipage}{0.9\linewidth}
@@
             \end{minipage}
+        \end{minipage}
+    \captionof{figure}[Estimation of selection at the population scale for $\SphyNeu$ mutations.]{\textbf{Estimation of selection at the population scale for $\bm{\SphyNeu}$ mutations.} Each stack bar corresponds to the DFE of new mutations predicted to be $\SphyNeu$ by the mutation selection model, in a given population.
+The dashed area represents the proportion of deleterious mutations ($\SpopDel$), the gray area that of neutral mutations ($\SpopNeu$), and the yellow area that of beneficial mutations ($\SpopBen$).\label{fig:pop-weak}}
+    \end{center}
 
-    \newpage
-    \captionof{figure}{Estimation of selection at the population scale for $\SphyBen$ mutations}
+    \begin{center}
+        \begin{minipage}{0.75\linewidth}
             \begin{minipage}{0.9\linewidth}
@@
             \end{minipage}
+        \end{minipage}
+    \captionof{figure}[Estimation of selection at the population scale for $\SphyBen$ mutations.]{\textbf{Estimation of selection at the population scale for $\bm{\SphyBen}$ mutations.} Each stack bar corresponds to the DFE of new mutations predicted to be $\SphyBen$ by the mutation selection model, in a given population.
+The dashed area represents the proportion of deleterious mutations ($\SpopDel$), the gray area that of neutral mutations ($\SpopNeu$), and the yellow area that of beneficial mutations ($\SpopBen$).\label{fig:pop-pos}}
+    \end{center}
 
-    \subsection{Correlation with diversity}
-    For each population, the proportion of deleterious ($\ProbaPopDel$), nearly-neutral ($\ProbaPopNeu$) and of beneficial ($\ProbaPopBen$) mutations estimated at the population-genetic scale is shown as function of Watterson's's diversity ($\thetaSyn$).
+    \subsection{Distribution of scaled selection coefficients (\texorpdfstring{$\Sphy$}{S₀})}\label{subsec:expectedDFE}
 
-    \subsubsection{Proportion of deleterious mutations ($\SpopDel$)}\label{subsec:proportion-deleterious-mutations}
-    \captionof{figure}{Proportion of deleterious mutations ($\SpopDel$)}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.all_P-Sneg.scatter.pdf}
+    Theoretically, the selection coefficient ($\Sphy$) for any mutation is related to its probability of fixation by the equation $\proba_{\text{fix}} (\Sphy) = \Sphy/(1-\exp(-\Sphy)) $.
+    It is thus possible to predict the distribution of $\Sphy$ of substitutions given the distribution of $\Sphy$ for mutations (Figure~\ref{dfe-sfs}A for one population of \textit{Chlorocebus sabaeus}) by weighting the different mutations by their $\proba_{\text{fix}} (\Sphy)$.
+    The predicted DFE (distribution of fitness effects) of substitutions (Figure~\ref{dfe-sfs}B) matches the observed DFE of substitutions (Figure~\ref{dfe-sfs}C) in the terminal lineage, meaning that the $\Sphy$ obtained by phylogenetic mutation-selection codon models is a strong predictor of selection effectively exerted on mutations in terminal lineages.
+    Equivalent figures to Figure~\ref{dfe-sfs} for each one of the 28 populations are available at Zenodo (\url{https://doi.org/10.5281/zenodo.7878953}) in file \textit{distribution\_S0\_28\_populations.pdf}.\\
+
+    \newpage
+    \begin{center}
+        \begin{minipage}{0.32\linewidth}
+            \flushleft {\tiny A: Expected DFE for mutations}
+            \includegraphics[width=\linewidth, page=1]{artworks/DFE.Chlorocebus_sabaeus.Saint_Kitts.MutSel.pdf}
         \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.neg_P-Sneg.scatter.pdf}
+        \begin{minipage}{0.32\linewidth}
+            \flushleft {\tiny B: Expected DFE for substitutions}
+            \includegraphics[width=\linewidth, page=1]{artworks/DFE.Chlorocebus_sabaeus.Saint_Kitts.MutSel.Flow.pdf}
         \end{minipage}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item $\proba [ \SpopDel ]$ (eq.~15) is the probability for a mutation to be deleterious.
-        These mutations have a selection coefficient at the population-scale lower than -1.
-        \item $\proba [ \SpopDel \given \SphyDel ]$ (eq.~12) is the probability for a mutation to be deleterious at the population scale, given it is predicted to be a deleterious at the phylogenetic scale.
-    \end{itemize}
+        \begin{minipage}{0.32\linewidth}
+            \flushleft {\tiny C: Observed DFE for substitutions}
+            \includegraphics[width=\linewidth, page=1]{artworks/subs.Chlorocebus_sabaeus.Saint_Kitts.bins3Mask0.9.pdf}
+        \end{minipage}
+        \\
+        \begin{minipage}{0.32\linewidth}
+            \flushleft {\tiny D: Observed DFE for polymorphisms}
+            \includegraphics[width=\linewidth, page=1]{artworks/poly.Chlorocebus_sabaeus.Saint_Kitts.bins3Mask0.9.pdf}
+        \end{minipage}
+        \begin{minipage}{0.32\linewidth}
+            \flushleft {\tiny E: Site frequency spectrum}
+            \includegraphics[width=\linewidth, page=1]{artworks/Chlorocebus_sabaeus.Saint_Kitts.MutSel-sfs.normalize.pdf}
+        \end{minipage}
+        \begin{minipage}{0.32\linewidth}
+            \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
+            \includegraphics[width=\linewidth, page=1]{artworks/Chlorocebus_sabaeus.Saint_Kitts.MutSel.polyDFE_C.pdf}
+        \end{minipage}
+        \captionof{figure}[Distribution of scaled selection coefficients ($\Sphy$).]{\textbf{Distribution of scaled selection coefficients ($\bm{\Sphy}$) in the Saint Kitts population of \textit{Chlorocebus sabaeus}.}
+        A) Distribution of scaled selection coefficients ($\Sphy$), predicted for all possible non-synonymous DNA mutations away from the ancestral exome.
+        Mutations are divided into three classes of selection: deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial non-adaptive ($\SphyBen$).
+        B) Expected distribution of $\Sphy$ for substitutions obtained by transforming the distribution of $\Sphy$ for mutations (panel A) by weighting each mutation by its scaled probability of fixation given by $\proba_{\text{fix}} (\Sphy) = \Sphy/(1-\exp(-\Sphy))$.
+        C) Distribution of scaled selection coefficients ($\Sphy$) for all observed substitutions along the terminal branch of the phylogenetic tree.
+        D) Distribution of scaled selection coefficients ($\Sphy$) for all observed polymorphisms currently segregating in the population.
+        E) The site-frequency spectrum (SFS) in the population for a random sample of 16 alleles (means in solid lines and standard deviations in color shades) for each class of selection and for synonymous mutations, supposedly neutral (black).
+The SFS represents the proportion of mutations (y-axis) with a given number of derived alleles in the population (x-axis).
+At high frequencies, deleterious mutations are underrepresented.
+        F) Proportion of beneficial $\ProbaPopDel$, nearly-neutral $\ProbaPopNeu$, and deleterious mutations $\ProbaPopBen$  estimated at the population scale for each class of selection at the phylogenetic scale.
+Proportions depicted here are not weighted by their mutational opportunities.}
+        \label{dfe-sfs}
+    \end{center}
 
-    We can see that higher synonymous diversity ($\thetaSyn$) is typically accompanied by a higher proportion of effectively deleterious mutations at the population scale ($\proba [ \SpopDel ]$).
-    This trend is also confirmed when we restricted the analysis to class of mutations that are supposedly deleterious at the phylogenetic scale ($\SphyDel$).
+    \newpage
+    \section{Correlation with diversity}
+
+    \subsection{Phylogenetic Generalized Linear Model}
+
+    Because a correlation must account for phylogenetic relationship and non-independence of samples, we fitted a Phylogenetic Generalized Linear Model (PGLM) in R with the package caper~\cite{orme_caper_2013}, with multi-furcation of the different populations inside each species.
+    The mammalian tree imported from TimeTree~\cite{kumar_timetree_2017} and pruned to the species used in this study (Figure~\ref{tree}) is shown in newick format:
+
+    \lstinputlisting[breaklines]{artworks/PGLM.tree}
+
+    \begin{center}
+        \includegraphics[width=0.65\linewidth, page=1]{artworks/PGLM.pdf}
+        \captionof{figure}[Tree used for PGLM (Phylogenetic Generalized Linear Model).]{\textbf{Tree used for PGLM (Phylogenetic Generalized Linear Model).} The mammalian dated tree was obtained from TimeTree~\cite{kumar_timetree_2017} and pruned to include only the species analysed in this study, with multi-furcation of the different populations from each species placed at the same divergence time as the divergence to the sister species.}
+        \label{tree}
+    \end{center}
+
+    \newpage
+    Accounting for phylogenetic relationship and non-independence of samples, through the fit of a Phylogenetic Generalized Linear Model, we can estimate regression coefficient between two variables.
+    Thus, for each population, the proportion of deleterious ($\ProbaPopDel$,~\ref{fig:pop-neg-prop}), nearly-neutral ($\ProbaPopNeu$,~\ref{fig:pop-weak-prop}) and beneficial ($\ProbaPopBen$,~\ref{fig:pop-pos-prop}) mutations estimated at the population-genetic scale is shown as function of $\Ne$, and we estimated regression coefficients.
+
+    \subsubsection{Proportion of deleterious mutations (\texorpdfstring{$\SpopDel$}{D})}\label{subsec:proportion-deleterious-mutations}
+
+    Higher effective population size ($\Ne$) is typically accompanied by a higher proportion of effectively deleterious mutations at the population scale ($\proba{[} \SpopDel {]}$), as shown in~\ref{fig:pop-neg-prop} (left panel).
+    This trend is also confirmed when we restricted the analysis to class of mutations that are supposedly deleterious at the phylogenetic scale ($\SphyDel$), as shown in~\ref{fig:pop-neg-prop} (right panel).
     This result is qualitatively in accordance with the nearly-neutral theory of evolution which argues that very slightly deleterious mutations are more efficiently purified in large populations.
 
-    \subsubsection{Proportion of nearly-neutral mutations ($\SpopNeu$)}\label{subsec:proportion-nearly-neutral-mutations}
-    \captionof{figure}{Proportion of nearly-neutral mutations ($\SpopNeu$)}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.all_P-Sweak.scatter.pdf}
+    \begin{center}
+    \begin{minipage}{0.45\linewidth}
+        \includegraphics[width=\linewidth, page=1]{artworks/results.pop_size.all_P-Sneg.scatter.pdf}
     \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.weak_P-Sweak.scatter.pdf}
+    \begin{minipage}{0.45\linewidth}
+        \includegraphics[width=\linewidth, page=1]{artworks/results.pop_size.neg_P-Sneg.scatter.pdf}
     \end{minipage}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item $\proba [ \SpopNeu ]$ (eq.~15) is the probability for a mutation to be nearly-neutral.
-        These mutations have a selection coefficient at the population-scale between -1 and 1.
-        \item $\proba [ \SpopNeu \given \SphyNeu ]$ (eq.~12) is the probability for a mutation to be nearly-neutral at the population scale, given it is predicted to be a nearly-neutral at the phylogenetic scale.
-    \end{itemize}
+    \captionof{figure}[Relationship between the proportion of deleterious mutations ($\SpopDel$) and effective population size.]{\textbf{Relationship between the proportion of deleterious mutations ($\bm{\SpopDel}$) and effective population size.}
+    Left) Proportion of deleterious mutations at the population scale ($\proba{[} \SpopNeu{]}$), shown as a function of estimated effective population size ($\Ne$).
+Right) Probability for a mutation to be deleterious at the population scale, given it is predicted to be deleterious at the phylogenetic scale, as a function of estimated effective population size ($\Ne$).
+Populations are represented by circles, and squares are the mean for the species.
+Correlations account for phylogenetic relationship and non-independence of samples, through the fit of a Phylogenetic Generalized Linear Model (see Materials \& Methods).\label{fig:pop-neg-prop}}
+    \end{center}
 
-    We confirmed that higher synonymous diversity ($\thetaSyn$) is typically accompanied by a smaller proportion of neutral mutations at the population scale ($\proba [ \SpopNeu ]$ in the range 0.06-0.18).
-    This result is more pronounced ($\proba [ \SpopNeu \given \SphyNeu ]$ in the range 0.36-0.73) when we restricted the analysis to class of mutations that are supposedly nearly-neutral at the phylogenetic scale ($\SphyNeu$).
-    This result suggests that populations with higher diversity (e.g.~\textit{Bos} or \textit{Ovis}) are more likely to discriminate whether mutations are beneficial or deleterious.
-    Alternatively stated, mutations in populations with low diversity (e.g.~\textit{Homo}) are effectively nearly-neutral and behave as would a neutral mutation.
+    \subsubsection{Proportion of nearly-neutral mutations (\texorpdfstring{$\SpopNeu$}{N})}\label{subsec:proportion-nearly-neutral-mutations}
+    Higher effective population size ($\Ne$) is typically accompanied by a smaller proportion of neutral mutations at the population scale ($\proba{[} \SpopNeu {]}$ in the range 0.06-0.18), as shown in~\ref{fig:pop-weak-prop} (left panel).
+    This result is more pronounced ($\proba{[} \SpopNeu \given \SphyNeu {]}$ in the range 0.36-0.73) when we restricted the analysis to the class of mutations that are supposedly nearly-neutral at the phylogenetic scale ($\SphyNeu$), as shown in~\ref{fig:pop-pos-prop} (right panel).
+    This result suggests that in populations with higher diversity (e.g.,~\textit{Bos} or \textit{Ovis}), mutations are more likely to be detected as under selection (positive or negative).
+    Alternatively stated, mutations in populations with low diversity (e.g.,~\textit{Homo}) are effectively nearly-neutral and behave as neutral mutations would.
     This result is qualitatively in accordance with the nearly-neutral theory of evolution which argues that mutations are less efficiently selected for in small populations.
 
-    \subsubsection{Proportion of beneficial mutations ($\SpopBen$)}\label{subsec:proportion-beneficial-mutations}
-    \captionof{figure}{Proportion of beneficial mutations ($\SpopBen$)}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.all_P-Spos.scatter.pdf}
+    \begin{center}
+        \begin{minipage}{0.45\linewidth}
+            \includegraphics[width=\linewidth, page=1]{artworks/results.pop_size.all_P-Sweak.scatter.pdf}
         \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/results.watterson.pos_P-Spos.scatter.pdf}
+        \begin{minipage}{0.45\linewidth}
+            \includegraphics[width=\linewidth, page=1]{artworks/results.pop_size.weak_P-Sweak.scatter.pdf}
         \end{minipage}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item $\proba [ \SpopBen ]$ (eq.~15) is the probability for a mutation to be beneficial.
-        These mutations have a selection coefficient at the population-scale larger than 1.
-        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale (the \textit{precision}).
-    \end{itemize}
-    Higher synonymous diversity ($\thetaSyn$) is accompanied by a smaller proportion of beneficial mutations at the population scale ($\proba [ \SpopBen ]$).
-    This trend is also confirmed when we restricted the analysis to class of mutations that are supposedly beneficial back-mutations at the phylogenetic scale ($\SphyBen$).
-    This result is much more difficult to interpret.
-    The fraction of beneficial back mutations is supposed to depend on long term demographic history, which is not directly accessible.
-    If the long term effective population size is relatively similar to the short term one, we expect little opportunity for beneficial back-mutations.
-    And thus, counter-intuitively we expect a diminution of positively selected mutations.
-    However, we can see that the proportion of beneficial back-mutations among advantageous one does not decrease with synonymous diversity.
-    This means that somehow adaptive mutations also decrease with synonymous diversity for a reason we fail to explain.
+        \captionof{figure}[Relationship between the proportion of nearly-neutral mutations ($\SpopNeu$) and effective population size.]{\textbf{Relationship between the proportion of nearly-neutral mutations ($\bm{\SpopNeu}$) and effective population size.}
+        Left) Proportion of deleterious mutations at the population scale ($\proba{[} \SpopNeu{]}$), shown as a function of estimated effective population size ($\Ne$).
+Right) Probability for a mutation to be nearly-neutral at the population scale, given it is predicted to be nearly-neutral at the phylogenetic scale, as a function of estimated effective population size ($\Ne$).
+Populations are represented by circles, and squares are the mean for the species.
+Correlations account for phylogenetic relationship and non-independence of samples, through the fit of a Phylogenetic Generalized Linear Model (see Materials \& Methods).\label{fig:pop-weak-prop}}
+    \end{center}
 
-    \newpage
+    \subsubsection{Proportion of beneficial mutations (\texorpdfstring{$\SpopBen$}{B})}\label{subsec:proportion-beneficial-mutations}
+    A higher effective population size ($\Ne$) is accompanied by a smaller proportion of beneficial mutations at the population scale ($\proba{[} \SpopBen {]}$), as shown in~\ref{fig:pop-pos-prop} (left panel).
+    This trend is also confirmed when we restricted the analysis to the class of mutations that are supposedly non-adaptive beneficial at the phylogenetic scale ($\SphyBen$), as shown in~\ref{fig:pop-pos-prop} (right panel).
 
-    \section{Clinically related terms for mutations}
-    \subsection{Terms associated with deleterious mutations $\SphyDel$}
     \begin{center}
-        \captionof{table}{Terms associated with deleterious mutations $\SphyDel$}
-        \begin{tabular}{|l|r|r|r|r|r|}
-            \toprule
-            SNP clinical ontology & $n_{\mathrm{Observed}}$ & $n_{\mathrm{Expected}}$ & Odds ratio & $p_{\mathrm{v}}$ & $p_{\mathrm{v-adjusted}}$ \\
-            \midrule
-            Benign                & 2969                    & $4043.0$                & $ 0.734$   & $ 1.000$             & $ 1.000~~$                    \\
-            Likely benign         & 2994                    & $3399.8$                & $ 0.881$   & $ 0.999$             & $ 1.000~~$                    \\
-            Risk factor           & 102                     & $ 118.2$                & $ 0.863$   & $ 0.798$             & $ 1.000~~$                    \\
-            Likely pathogenic     & 221                     & $  68.5$                  & $ 3.226$   & $1.7\times 10^{-8}$  & $\bm{6.7\times 10^{-8}{^*}}$  \\
-            Pathogenic            & 560                     & $ 193.6$                & $ 2.893$   & $4.2\times 10^{-17}$ & $\bm{2.1\times 10^{-16}{^*}}$ \\
-            \bottomrule
-        \end{tabular}
+        \begin{minipage}{0.45\linewidth}
+            \includegraphics[width=\linewidth, page=1]{artworks/results.pop_size.all_P-Spos.scatter.pdf}
+        \end{minipage}
+        \begin{minipage}{0.45\linewidth}
+            \includegraphics[width=\linewidth, page=1]{artworks/results.pop_size.pos_P-Spos.scatter.pdf}
+        \end{minipage}
+        \captionof{figure}[Relationship between the proportion of beneficial mutations ($\SpopBen$) and effective population size.]{\textbf{Relationship between the proportion of beneficial mutations ($\bm{\SpopBen}$) and effective population size.}
+        Left) Proportion of beneficial mutations at the population scale ($\proba{[} \SpopNeu{]}$), shown as a function of estimated effective population size ($\Ne$).
+Right) Probability for a mutation to be beneficial at the population scale, given it is predicted to be beneficial at the phylogenetic scale, as a function of estimated effective population size ($\Ne$).
+Populations are represented by circles, and squares are the mean for the species.
+Correlations account for phylogenetic relationship and non-independence of samples, through the fit of a Phylogenetic Generalized Linear Model (see Materials \& Methods).\label{fig:pop-pos-prop}}
     \end{center}
-    In humans, non-synonymous SNPs in the test group ($\SphyDel$) are contrasted to SNPs in the control group ($\SphyNeu$).
-    For each clinical term, a 2x2 contingency tables is built by counting the number of SNPs based on their selection coefficient and their clinical terms (whether they have this specific term or not).
-    Fisher's exact tests are then performed for these 2x2 contingency tables.
-    $^*$ for $p_{\mathrm{v}}^{\mathrm{adj}}$ corrected for multiple comparison (Holm–Bonferroni correction) lower than the risk $\alpha=0.05$.
-    SNPs predicted with $\SphyDel$ are statistically associated to clinical terms such as \textit{Likely Pathogenic} and \textit{Pathogenic}.
 
-    \subsection{Terms associated with beneficial back-mutations $\SphyBen$}
-    \begin{center}
-        \captionof{table}{Terms associated with beneficial back-mutations $\SphyBen$}
-        \begin{tabular}{|l|r|r|r|r|r|}
-            \toprule
-            SNP clinical ontology & $n_{\mathrm{Observed}}$ & $n_{\mathrm{Expected}}$ & Odds ratio & $p_{\mathrm{v}}$ & $p_{\mathrm{v-adjusted}}$ \\
-            \midrule
-            Benign                & 319                     & $ 261.7$                & $ 1.219$   & $ 0.002$         & $\bm{ 0.009{^*}}$         \\
-            Likely benign         & 263                     & $ 222.7$                & $ 1.181$   & $ 0.012$         & $\bm{ 0.049{^*}}$         \\
-            Risk factor           & 5                       & $ 7.847$                & $ 0.637$   & $ 0.879$         & $ 0.879~~$                \\
-            Likely pathogenic     & 7                       & $ 4.552$                & $ 1.538$   & $ 0.227$         & $ 0.682~~$                \\
-            Pathogenic            & 16                      & $  12.9$                  & $ 1.241$   & $ 0.268$         & $ 0.682~~$                \\
-            \bottomrule
-        \end{tabular}
-    \end{center}
-    In humans, non-synonymous SNPs in the test group ($\SphyBen$) are contrasted to SNPs in the control group ($\SphyNeu$).
-    For each clinical term, a 2x2 contingency tables is built by counting the number of SNPs based on their selection coefficient and their clinical terms (whether they have this specific term or not).
-    Fisher's exact tests are then performed for these 2x2 contingency tables.
-    $^*$ for $p_{\mathrm{v}}^{\mathrm{adj}}$ corrected for multiple comparison (Holm–Bonferroni correction) lower than the risk $\alpha=0.05$.
-    Beneficial back-mutations are associated with clinical terms such as \textit{Benign} and \textit{Likely Benign}.
-    \newpage
-
-    \section{Including divergence data for the estimation of $\Spop$}
-
-    \subsection{Including divergence in polyDFE}
-    Divergence data (number of substitutions per site) can also be included into polyDFE to estimate the DFE.
-    For the class of a given class of selection coefficient ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$), the number of substitutions has already been computed and is given by $D\left( \Sphyclass \right)$ (see eq.~6), and the number of sites is given by $L \left( \Sphyclass \right)$ (see eq.~4).
-    Otherwise, the procedure is the same as described section \textit{Scaled selection coefficients ($\Spop$) in a population-based method}.
-
-    \subsection{Probabilities of beneficial back-mutations}
-    \begin{center}
-        \captionof{table}{Probability of beneficial back-mutations among all beneficial ones.}
-        \scriptsize
-        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
-            \toprule
-            Population & Species & Watterson's $\thetaSyn$ & $\proba[\SphyBen]$ & $\proba [ \SpopBen ]$ & $\frac{\proba[\SphyBen]}{\proba[ \SpopBen ]}$ & $\proba [ \SpopBen \given \SphyBen]$ & $\proba[\SphyBen\given \SpopBen ]$ \\
-            \midrule
-            \endhead
-            \midrule
-            \multicolumn{8}{r}{{Continued on next page}} \\
-            \midrule
-            \endfoot
-
-            \bottomrule
-            \endlastfoot
-            \rowcolor{LIGHTGREY} Equus c.
-&      Equus caballus &               $ 0.002$ &              $ 0.014$ &              $ 0.061$ &                                          $ 0.235$ &                         $ 0.519$ &                      $ 0.122$ \\
-            Iran &          Bos taurus &               $ 0.002$ &              $ 0.013$ &              $ 0.007$ &                                          $ 1.908$ &                         $ 0.368$ &                      $ 0.702$ \\
-            Uganda &          Bos taurus &               $ 0.005$ &              $ 0.013$ &              $ 0.008$ &                                          $ 1.667$ &                         $ 0.255$ &                      $ 0.425$ \\
-            \rowcolor{LIGHTGREY} Australia &        Capra hircus &               $ 0.003$ &              $ 0.014$ &              $ 0.007$ &                                          $ 2.099$ &                         $ 0.147$ &                      $ 0.308$ \\
-            \rowcolor{LIGHTGREY} France &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.007$ &                                          $ 2.043$ &                         $ 0.149$ &                      $ 0.304$ \\
-            \rowcolor{LIGHTGREY} Iran (C.
-aegagrus) &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.013$ &                                          $ 1.069$ &                         $ 0.147$ &                      $ 0.157$ \\
-            \rowcolor{LIGHTGREY} Iran &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.008$ &                                          $ 1.699$ &                         $ 0.152$ &                      $ 0.258$ \\
-            \rowcolor{LIGHTGREY} Italy &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.006$ &                                          $ 2.160$ &                         $ 0.147$ &                      $ 0.316$ \\
-            \rowcolor{LIGHTGREY} Morocco &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.006$ &                                          $ 2.141$ &                         $ 0.186$ &                      $ 0.398$ \\
-            Iran &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.012$ &                                          $ 1.210$ &                         $ 0.158$ &                      $ 0.191$ \\
-            Iran (O.
-orientalis) &          Ovis aries &               $ 0.009$ &              $ 0.014$ &              $ 0.012$ &                                          $ 1.144$ &                         $ 0.157$ &                      $ 0.180$ \\
-            Iran (O.
-vignei) &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.022$ &                                          $ 0.631$ &                         $ 0.186$ &                      $ 0.118$ \\
-            Various &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.012$ &                                          $ 1.211$ &                         $ 0.156$ &                      $ 0.188$ \\
-            Morocco &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.009$ &                                          $ 1.536$ &                         $ 0.190$ &                      $ 0.292$ \\
-            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.005$ &                                          $ 2.230$ &                         $ 0.282$ &                      $ 0.630$ \\
-            \rowcolor{LIGHTGREY} Central Afr.
-Rep.
-& Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.014$ &                                          $ 0.849$ &                         $ 0.310$ &                      $ 0.263$ \\
-            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.008$ &                                          $ 1.530$ &                         $ 0.298$ &                      $ 0.456$ \\
-            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.008$ &                                          $ 1.384$ &                         $ 0.305$ &                      $ 0.422$ \\
-            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.014$ &                                          $ 0.854$ &                         $ 0.296$ &                      $ 0.253$ \\
-            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus &               $ 0.003$ &              $ 0.012$ &              $ 0.005$ &                                          $ 2.438$ &                         $ 0.285$ &                      $ 0.696$ \\
-            \rowcolor{LIGHTGREY} South Africa  & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.011$ &                                          $ 1.047$ &                         $ 0.323$ &                      $ 0.338$ \\
-            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.006$ &                                          $ 2.070$ &                         $ 0.292$ &                      $ 0.604$ \\
-            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.014$ &                                          $ 0.816$ &                         $ 0.309$ &                      $ 0.252$ \\
-            African &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.015$ &                                          $ 0.765$ &                         $ 0.371$ &                      $ 0.284$ \\
-            Admixed American &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.009$ &                                          $ 1.259$ &                         $ 0.368$ &                      $ 0.464$ \\
-            East Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.012$ &                                          $ 0.973$ &                         $ 0.369$ &                      $ 0.358$ \\
-            European &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.009$ &                                          $ 1.356$ &                         $ 0.368$ &                      $ 0.499$ \\
-            South Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.010$ &                                          $ 1.147$ &                         $ 0.369$ &                      $ 0.423$ \\
-        \end{longtable*}
-    \end{center}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item $\proba [ \SphyBen ]$ (eq.~5) is the probability for a new mutation a beneficial back-mutation.
-        These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1, thus toward a more fit amino-acid.
-        \item $\proba [ \SpopBen ]$ (eq.~15) is the probability for a mutation to be beneficial.
-        These mutations have a selection coefficient at the population-scale larger than 1.
-        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale (the \textit{precision}).
-        \item $\proba [ \SphyBen \given \SpopBen]$ (eq.~14) is the probability for a mutation to a beneficial back-mutations, given it is beneficial (the \textit{recall}).
-        This probability is obtained using Bayes' formula.
-    \end{itemize}
-    \newpage
-
-    \subsection{Precision and recall}
-    \captionof{table}{Precision and recall}
-    \begin{center}
-        \begin{adjustbox}{width=\textwidth}
-            \begin{tabular}{||l|l|r||r|r||r|r||r|r||}
-                \toprule
-                \multicolumn{3}{||c||}{} &
-                \multicolumn{2}{c||}{\shortstack{\textbf{Deleterious mutations} \\ $\bm{\SpopDel \coloneqq \Spop<-1}$ \\ $\bm{\SphyDel \coloneqq \Sphy<-1}$}} &
-                \multicolumn{2}{c||}{\shortstack{\textbf{Nearly-neutral mutations} \\ $\bm{\SpopNeu \coloneqq -1<\Spop<1}$ \\ $\bm{\SphyNeu \coloneqq -1<\Sphy<1}$}} &
-                \multicolumn{2}{c||}{\shortstack{\textbf{Beneficial mutations} \\ $\bm{\SpopBen \coloneqq \Spop>1}$ \\ $\bm{\SphyBen \coloneqq \Sphy>1}$}}
-                \\ \hline
-                \textbf{Population} &
-                \textbf{Species} &
-                $\bm{\thetaSyn}$ &
-                \makecell{\textbf{Precision} \\ $\bm{\proba [\SpopDel \given \SphyDel]}$} &
-                \makecell{\textbf{Recall} \\ $\bm{\proba [\SphyDel \given \SpopDel]}$}           &
-                \makecell{\textbf{Precision}      \\ $\bm{\proba [\SpopNeu \given \SphyNeu]}$}                                    &
-                \makecell{\textbf{Recall}          \\ $\bm{\proba [\SphyNeu \given \SpopNeu]}$}                                  &
-                \makecell{\textbf{Precision}          \\ $\bm{\proba [\SpopBen \given \SphyBen]}$}          &
-                \makecell{\textbf{Recall}        \\ $\bm{\proba [\SphyBen \given \SpopBen]}$}
-                \\   \midrule
-                \rowcolor{LIGHTGREY} Equus c. & Equus caballus        & $ 0.002$ & $ 0.918$ & $ 0.957$ & $ 0.186$ & $ 0.213$ & $ 0.519$ & $ 0.122$ \\
-                Iran               & Bos taurus        & $ 0.002$ & $ 0.924$ & $ 0.965$ & $ 0.565$ & $ 0.356$ & $ 0.368$ & $ 0.702$ \\
-                Uganda              & Bos taurus        & $ 0.005$ & $ 0.943$ & $ 0.961$ & $ 0.516$ & $ 0.396$ & $ 0.255$ & $ 0.425$ \\
-                \rowcolor{LIGHTGREY} Australia            & Capra hircus        & $ 0.003$ & $ 0.941$ & $ 0.964$ & $ 0.592$ & $ 0.434$ & $ 0.147$ & $ 0.308$ \\
-                \rowcolor{LIGHTGREY} France                                    & Capra hircus          & $ 0.004$ & $ 0.940$ & $ 0.963$ & $ 0.571$ & $ 0.418$ & $ 0.149$ & $ 0.304$ \\
-                \rowcolor{LIGHTGREY} Iran (C. aegagrus)                    & Capra hircus          & $ 0.004$ & $ 0.948$ & $ 0.960$ & $ 0.515$ & $ 0.446$ & $ 0.147$ & $ 0.157$ \\
-                \rowcolor{LIGHTGREY} Iran                        & Capra hircus          & $ 0.004$ & $ 0.942$ & $ 0.961$ & $ 0.534$ & $ 0.410$ & $ 0.152$ & $ 0.258$ \\
-                \rowcolor{LIGHTGREY} Italy                                 & Capra hircus          & $ 0.004$ & $ 0.940$ & $ 0.963$ & $ 0.579$ & $ 0.421$ & $ 0.147$ & $ 0.316$ \\
-                \rowcolor{LIGHTGREY} Morocco                                 & Capra hircus          & $ 0.004$ & $ 0.939$ & $ 0.960$ & $ 0.549$ & $ 0.404$ & $ 0.186$ & $ 0.398$ \\
-                Iran           & Ovis aries & $ 0.007$ & $ 0.957$ & $ 0.954$ & $ 0.412$ & $ 0.416$ & $ 0.158$ & $ 0.191$ \\
-                Iran (O. orientalis)  & Ovis aries & $ 0.009$ & $ 0.961$ & $ 0.955$ & $ 0.413$ & $ 0.437$ & $ 0.157$ & $ 0.180$ \\
-                Iran (O. vignei)           & Ovis aries & $ 0.007$ & $ 0.968$ & $ 0.951$ & $ 0.356$ & $ 0.516$ & $ 0.186$ & $ 0.118$ \\
-                Various             & Ovis aries & $ 0.008$ & $ 0.958$ & $ 0.955$ & $ 0.428$ & $ 0.431$ & $ 0.156$ & $ 0.188$ \\
-                Morocco              & Ovis aries & $ 0.008$ & $ 0.960$ & $ 0.953$ & $ 0.447$ & $ 0.460$ & $ 0.190$ & $ 0.292$ \\
-                \rowcolor{LIGHTGREY} Barbados              & Chlorocebus sabaeus & $ 0.004$ & $ 0.931$ & $ 0.969$ & $ 0.628$ & $ 0.402$ & $ 0.282$ & $ 0.630$ \\
-                \rowcolor{LIGHTGREY} Central Afr. Rep.       & Chlorocebus sabaeus & $ 0.006$ & $ 0.941$ & $ 0.964$ & $ 0.514$ & $ 0.408$ & $ 0.310$ & $ 0.263$ \\
-                \rowcolor{LIGHTGREY} Ethiopia        & Chlorocebus sabaeus & $ 0.005$ & $ 0.933$ & $ 0.967$ & $ 0.586$ & $ 0.393$ & $ 0.298$ & $ 0.456$ \\
-                \rowcolor{LIGHTGREY} Gambia             & Chlorocebus sabaeus & $ 0.005$ & $ 0.937$ & $ 0.967$ & $ 0.590$ & $ 0.414$ & $ 0.305$ & $ 0.422$ \\
-                \rowcolor{LIGHTGREY} Kenya                                 & Chlorocebus sabaeus        & $ 0.005$ & $ 0.942$ & $ 0.965$ & $ 0.526$ & $ 0.418$ & $ 0.296$ & $ 0.253$ \\
-                \rowcolor{LIGHTGREY} Nevis                        & Chlorocebus sabaeus        & $ 0.003$ & $ 0.930$ & $ 0.970$ & $ 0.637$ & $ 0.401$ & $ 0.285$ & $ 0.696$ \\
-                \rowcolor{LIGHTGREY} South Africa                              & Chlorocebus sabaeus        & $ 0.006$ & $ 0.937$ & $ 0.964$ & $ 0.530$ & $ 0.393$ & $ 0.323$ & $ 0.338$ \\
-                \rowcolor{LIGHTGREY} Saint Kitts                                & Chlorocebus sabaeus        & $ 0.004$ & $ 0.931$ & $ 0.969$ & $ 0.611$ & $ 0.393$ & $ 0.292$ & $ 0.604$ \\
-                \rowcolor{LIGHTGREY} Zambia                             & Chlorocebus sabaeus        & $ 0.006$ & $ 0.941$ & $ 0.963$ & $ 0.506$ & $ 0.408$ & $ 0.309$ & $ 0.252$ \\
-                African                             & Homo sapiens        & $ 0.002$ & $ 0.896$ & $ 0.968$ & $ 0.550$ & $ 0.297$ & $ 0.371$ & $ 0.284$ \\
-                Admixed American                             & Homo sapiens        & $ 0.002$ & $ 0.890$ & $ 0.979$ & $ 0.710$ & $ 0.333$ & $ 0.368$ & $ 0.464$ \\
-                East Asian                             & Homo sapiens        & $ 0.002$ & $ 0.890$ & $ 0.971$ & $ 0.578$ & $ 0.289$ & $ 0.369$ & $ 0.358$ \\
-                European                             & Homo sapiens        & $ 0.002$ & $ 0.891$ & $ 0.980$ & $ 0.739$ & $ 0.345$ & $ 0.368$ & $ 0.499$ \\
-                South Asian                             & Homo sapiens        & $ 0.002$ & $ 0.895$ & $ 0.981$ & $ 0.740$ & $ 0.356$ & $ 0.369$ & $ 0.423$ \\
-                \bottomrule
-            \end{tabular}
-        \end{adjustbox}
-    \end{center}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item \textit{Precision} is the estimation of the selection coefficient at population scale ($\Spop$) given that $\Sphy$ is known.
-        \item  \textit{Recall} is the estimation of $\Sphy$ given selection coefficient at the population scale ($\Spop$) is known.
-        \item \textit{Recall} for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is thus the proportion of beneficial back-mutations among all beneficial mutations.
-    \end{itemize}
-
-    Altogether, comparing this table to tables 1 and S3, we acknowledge that the exact proportion of beneficial back-mutations among all beneficial ones is different whether we included or not substitutions in the terminal lineage for the estimation of $\Spop$.
-    However, we can still see that beneficial back-mutations are positively selected compared to neutral and deleterious ones, and this result is not sensitive to inclusion of substitutions in the terminal lineage.
-
-    \newpage
-    \section{Discrete distribution of $\Spop$ at the population scale}
-
-    \subsection{polyDFE model D (discrete distribution)}
-    With polyDFE model D, the DFE of non-synonymous mutations is given as a discrete DFE of $K$ categories (instead of a continuous distribution in model C), where the selection coefficients of each category $i$ ($1 \leq i \leq K$) are fixed parameters $\Spop_i$, and each value $\Spop_i$ has a probability $p_i$ (estimated), with $\sum_{i=1}^{K} p_i =1$.
-    We used $K=6$ with $\Spop_1 = -500$, $\Spop_2 = -4$, $\Spop_3 =-1$, $\Spop_4 = 0$, $\Spop_5 = 1$, $\Spop_6 = 4$.\\
-    For each class of selection $\Sphyclass$, the parameters $p_i$ ($i \in \{ 1 \leq i \leq 6 \}$) were used to compute $\proba [ \SpopDel \given  \Sphyclass] $, $\proba [ \SpopNeu \given \Sphyclass]$, and $\proba [ \SpopBen \given \Sphyclass]$ as:
-    \begin{align}
-        \proba [ \SpopDel \given  \Sphyclass] &= \proba [ \Spop < -1 \given \Sphyclass ] = p_1 + p_2 \label{eq:polyProbaDel} \\
-        \proba [ \SpopNeu \given \Sphyclass] &= \proba [ -1 < \Spop < 1 \given \Sphyclass ] = p_3 + p_4 + p_5,  \\
-        \proba [ \SpopBen \given \Sphyclass] &= p_6. \label{eq:polyProbaAdv}
-    \end{align}
-
-    \subsection{Probabilities of beneficial back-mutations}
-    \begin{center}
-        \captionof{table}{Probability of beneficial back-mutations among all beneficial ones.}
-        \scriptsize
-        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
-            \toprule
-            Population & Species & Watterson's $\thetaSyn$ & $\proba[\SphyBen]$ & $\proba [ \SpopBen ]$ & $\frac{\proba[\SphyBen]}{\proba[ \SpopBen ]}$ & $\proba [ \SpopBen \given \SphyBen]$ & $\proba[\SphyBen\given \SpopBen ]$ \\
-            \midrule
-            \endhead
-            \midrule
-            \multicolumn{8}{r}{{Continued on next page}} \\
-            \midrule
-            \endfoot
-
-            \bottomrule
-            \endlastfoot
-            \rowcolor{LIGHTGREY} Equus c.
-&      Equus caballus &               $ 0.002$ &              $ 0.014$ &              $ 0.006$ &                                          $ 2.230$ &                         $ 0.141$ &                      $ 0.316$ \\
-            Iran &          Bos taurus &               $ 0.002$ &              $ 0.013$ &              $ 0.006$ &                                          $ 2.200$ &                         $ 0.136$ &                      $ 0.298$ \\
-            Uganda &          Bos taurus &               $ 0.005$ &              $ 0.013$ &              $ 0.011$ &                                          $ 1.177$ &                         $ 0.138$ &                      $ 0.162$ \\
-            \rowcolor{LIGHTGREY} Australia &        Capra hircus &               $ 0.003$ &              $ 0.014$ &              $ 0.002$ &                                          $ 6.467$ &                         $ 0.135$ &                      $ 0.871$ \\
-            \rowcolor{LIGHTGREY} France &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.002$ &                                          $ 6.407$ &                         $ 0.132$ &                      $ 0.845$ \\
-            \rowcolor{LIGHTGREY} Iran (C.
-aegagrus) &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.002$ &                                          $ 5.993$ &                         $ 0.129$ &                      $ 0.772$ \\
-            \rowcolor{LIGHTGREY} Iran &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.004$ &                                          $ 3.656$ &                         $ 0.138$ &                      $ 0.506$ \\
-            \rowcolor{LIGHTGREY} Italy &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.002$ &                                          $ 6.216$ &                         $ 0.127$ &                      $ 0.787$ \\
-            \rowcolor{LIGHTGREY} Morocco &        Capra hircus &               $ 0.004$ &              $ 0.014$ &              $ 0.002$ &                                          $ 6.019$ &                         $ 0.141$ &                      $ 0.848$ \\
-            Iran &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.588$ &                         $ 0.148$ &                      $ 0.087$ \\
-            Iran (O.
-orientalis) &          Ovis aries &               $ 0.009$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.569$ &                         $ 0.143$ &                      $ 0.081$ \\
-            Iran (O.
-vignei) &          Ovis aries &               $ 0.007$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.587$ &                         $ 0.127$ &                      $ 0.075$ \\
-            Various &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.024$ &                                          $ 0.588$ &                         $ 0.146$ &                      $ 0.086$ \\
-            Morocco &          Ovis aries &               $ 0.008$ &              $ 0.014$ &              $ 0.025$ &                                          $ 0.564$ &                         $ 0.145$ &                      $ 0.082$ \\
-            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.002$ &                                          $ 5.689$ &                         $ 0.170$ &                      $ 0.968$ \\
-            \rowcolor{LIGHTGREY} Central Afr.
-Rep.
-& Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.005$ &                                          $ 2.142$ &                         $ 0.156$ &                      $ 0.334$ \\
-            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.002$ &                                          $ 5.910$ &                         $ 0.160$ &                      $ 0.945$ \\
-            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.006$ &                                          $ 1.850$ &                         $ 0.157$ &                      $ 0.290$ \\
-            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus &               $ 0.005$ &              $ 0.012$ &              $ 0.004$ &                                          $ 2.802$ &                         $ 0.163$ &                      $ 0.456$ \\
-            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus &               $ 0.003$ &              $ 0.012$ &              $ 0.002$ &                                          $ 5.396$ &                         $ 0.169$ &                      $ 0.910$ \\
-            \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.005$ &                                          $ 2.154$ &                         $ 0.153$ &                      $ 0.329$ \\
-            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus &               $ 0.004$ &              $ 0.012$ &              $ 0.002$ &                                          $ 5.094$ &                         $ 0.164$ &                      $ 0.834$ \\
-            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus &               $ 0.006$ &              $ 0.012$ &              $ 0.006$ &                                          $ 1.952$ &                         $ 0.153$ &                      $ 0.298$ \\
-            African &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.014$ &                                          $ 0.869$ &                         $ 0.141$ &                      $ 0.123$ \\
-            Admixed American &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.010$ &                                          $ 1.130$ &                         $ 0.161$ &                      $ 0.182$ \\
-            East Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.007$ &                                          $ 1.602$ &                         $ 0.162$ &                      $ 0.259$ \\
-            European &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.009$ &                                          $ 1.336$ &                         $ 0.163$ &                      $ 0.217$ \\
-            South Asian &        Homo sapiens &               $ 0.002$ &              $ 0.012$ &              $ 0.009$ &                                          $ 1.342$ &                         $ 0.163$ &                      $ 0.219$ \\
-        \end{longtable*}
-    \end{center}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item $\proba [ \SphyBen ]$ (eq.~5) is the probability for a new mutation a beneficial back-mutation.
-        These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1, thus toward a more fit amino-acid.
-        \item $\proba [ \SpopBen ]$ (eq.~15) is the probability for a mutation to be beneficial.
-        These mutations have a selection coefficient at the population-scale larger than 1.
-        \item $\proba [ \SpopBen \given \SphyBen]$ (eq.~12) is the probability for a mutation to be beneficial at the population scale, given it is predicted to be a beneficial back-mutation at the phylogenetic scale (the \textit{precision}).
-        \item $\proba [ \SphyBen \given \SpopBen]$ (eq.~14) is the probability for a mutation to a beneficial back-mutations, given it is beneficial (the \textit{recall}).
-        This probability is obtained using Bayes' formula.
-    \end{itemize}
-    \newpage
-
-    \subsection{Precision and recall}
-    \captionof{table}{Precision and recall}
-    \begin{center}
-        \begin{adjustbox}{width=\textwidth}
-            \begin{tabular}{||l|l|r||r|r||r|r||r|r||}
-                \toprule
-                \multicolumn{3}{||c||}{} &
-                \multicolumn{2}{c||}{\shortstack{\textbf{Deleterious mutations} \\ $\bm{\SpopDel \coloneqq \Spop<-1}$ \\ $\bm{\SphyDel \coloneqq \Sphy<-1}$}} &
-                \multicolumn{2}{c||}{\shortstack{\textbf{Nearly-neutral mutations} \\ $\bm{\SpopNeu \coloneqq -1<\Spop<1}$ \\ $\bm{\SphyNeu \coloneqq -1<\Sphy<1}$}} &
-                \multicolumn{2}{c||}{\shortstack{\textbf{Beneficial mutations} \\ $\bm{\SpopBen \coloneqq \Spop>1}$ \\ $\bm{\SphyBen \coloneqq \Sphy>1}$}}
-                \\ \hline
-                \textbf{Population} &
-                \textbf{Species} &
-                $\bm{\thetaSyn}$ &
-                \makecell{\textbf{Precision} \\ $\bm{\proba [\SpopDel \given \SphyDel]}$} &
-                \makecell{\textbf{Recall} \\ $\bm{\proba [\SphyDel \given \SpopDel]}$}           &
-                \makecell{\textbf{Precision}      \\ $\bm{\proba [\SpopNeu \given \SphyNeu]}$}                                    &
-                \makecell{\textbf{Recall}          \\ $\bm{\proba [\SphyNeu \given \SpopNeu]}$}                                  &
-                \makecell{\textbf{Precision}          \\ $\bm{\proba [\SpopBen \given \SphyBen]}$}          &
-                \makecell{\textbf{Recall}        \\ $\bm{\proba [\SphyBen \given \SpopBen]}$}
-                \\   \midrule
-                \rowcolor{LIGHTGREY} Equus c. & Equus caballus        & $ 0.002$ & $ 0.895$ & $ 0.969$ & $ 0.645$ & $ 0.315$ & $ 0.141$ & $ 0.316$ \\
-                Iran               & Bos taurus        & $ 0.002$ & $ 0.878$ & $ 0.968$ & $ 0.632$ & $ 0.286$ & $ 0.136$ & $ 0.298$ \\
-                Uganda              & Bos taurus        & $ 0.005$ & $ 0.951$ & $ 0.963$ & $ 0.597$ & $ 0.508$ & $ 0.138$ & $ 0.162$ \\
-                \rowcolor{LIGHTGREY} Australia            & Capra hircus        & $ 0.003$ & $ 0.895$ & $ 0.981$ & $ 0.830$ & $ 0.379$ & $ 0.135$ & $ 0.871$ \\
-                \rowcolor{LIGHTGREY} France                                    & Capra hircus          & $ 0.004$ & $ 0.896$ & $ 0.978$ & $ 0.801$ & $ 0.373$ & $ 0.132$ & $ 0.845$ \\
-                \rowcolor{LIGHTGREY} Iran (C. aegagrus)                    & Capra hircus          & $ 0.004$ & $ 0.913$ & $ 0.971$ & $ 0.711$ & $ 0.383$ & $ 0.129$ & $ 0.772$ \\
-                \rowcolor{LIGHTGREY} Iran                        & Capra hircus          & $ 0.004$ & $ 0.949$ & $ 0.968$ & $ 0.655$ & $ 0.481$ & $ 0.138$ & $ 0.506$ \\
-                \rowcolor{LIGHTGREY} Italy                                 & Capra hircus          & $ 0.004$ & $ 0.894$ & $ 0.979$ & $ 0.814$ & $ 0.373$ & $ 0.127$ & $ 0.787$ \\
-                \rowcolor{LIGHTGREY} Morocco                                 & Capra hircus          & $ 0.004$ & $ 0.951$ & $ 0.972$ & $ 0.709$ & $ 0.504$ & $ 0.141$ & $ 0.848$ \\
-                Iran           & Ovis aries & $ 0.007$ & $ 0.980$ & $ 0.956$ & $ 0.456$ & $ 0.799$ & $ 0.148$ & $ 0.087$ \\
-                Iran (O. orientalis)  & Ovis aries & $ 0.009$ & $ 0.979$ & $ 0.955$ & $ 0.454$ & $ 0.798$ & $ 0.143$ & $ 0.081$ \\
-                Iran (O. vignei)           & Ovis aries & $ 0.007$ & $ 0.974$ & $ 0.957$ & $ 0.483$ & $ 0.729$ & $ 0.127$ & $ 0.075$ \\
-                Various             & Ovis aries & $ 0.008$ & $ 0.979$ & $ 0.958$ & $ 0.500$ & $ 0.813$ & $ 0.146$ & $ 0.086$ \\
-                Morocco              & Ovis aries & $ 0.008$ & $ 0.980$ & $ 0.952$ & $ 0.392$ & $ 0.774$ & $ 0.145$ & $ 0.082$ \\
-                \rowcolor{LIGHTGREY} Barbados              & Chlorocebus sabaeus & $ 0.004$ & $ 0.880$ & $ 0.984$ & $ 0.854$ & $ 0.354$ & $ 0.170$ & $ 0.968$ \\
-                \rowcolor{LIGHTGREY} Central Afr. Rep.       & Chlorocebus sabaeus & $ 0.006$ & $ 0.932$ & $ 0.968$ & $ 0.634$ & $ 0.413$ & $ 0.156$ & $ 0.334$ \\
-                \rowcolor{LIGHTGREY} Ethiopia        & Chlorocebus sabaeus & $ 0.005$ & $ 0.877$ & $ 0.980$ & $ 0.810$ & $ 0.337$ & $ 0.160$ & $ 0.945$ \\
-                \rowcolor{LIGHTGREY} Gambia             & Chlorocebus sabaeus & $ 0.005$ & $ 0.947$ & $ 0.977$ & $ 0.745$ & $ 0.518$ & $ 0.157$ & $ 0.290$ \\
-                \rowcolor{LIGHTGREY} Kenya                                 & Chlorocebus sabaeus        & $ 0.005$ & $ 0.903$ & $ 0.969$ & $ 0.664$ & $ 0.343$ & $ 0.163$ & $ 0.456$ \\
-                \rowcolor{LIGHTGREY} Nevis                        & Chlorocebus sabaeus        & $ 0.003$ & $ 0.880$ & $ 0.984$ & $ 0.861$ & $ 0.357$ & $ 0.169$ & $ 0.910$ \\
-                \rowcolor{LIGHTGREY} South Africa                              & Chlorocebus sabaeus        & $ 0.006$ & $ 0.931$ & $ 0.967$ & $ 0.615$ & $ 0.401$ & $ 0.153$ & $ 0.329$ \\
-                \rowcolor{LIGHTGREY} Saint Kitts                                & Chlorocebus sabaeus        & $ 0.004$ & $ 0.883$ & $ 0.982$ & $ 0.834$ & $ 0.355$ & $ 0.164$ & $ 0.834$ \\
-                \rowcolor{LIGHTGREY} Zambia                             & Chlorocebus sabaeus        & $ 0.006$ & $ 0.896$ & $ 0.969$ & $ 0.659$ & $ 0.332$ & $ 0.153$ & $ 0.298$ \\
-                African                             & Homo sapiens        & $ 0.002$ & $ 0.946$ & $ 0.971$ & $ 0.630$ & $ 0.486$ & $ 0.141$ & $ 0.123$ \\
-                Admixed American                             & Homo sapiens        & $ 0.002$ & $ 0.929$ & $ 0.972$ & $ 0.636$ & $ 0.410$ & $ 0.161$ & $ 0.182$ \\
-                East Asian                             & Homo sapiens        & $ 0.002$ & $ 0.937$ & $ 0.973$ & $ 0.647$ & $ 0.429$ & $ 0.162$ & $ 0.259$ \\
-                European                             & Homo sapiens        & $ 0.002$ & $ 0.937$ & $ 0.973$ & $ 0.643$ & $ 0.433$ & $ 0.163$ & $ 0.217$ \\
-                South Asian                             & Homo sapiens        & $ 0.002$ & $ 0.939$ & $ 0.972$ & $ 0.639$ & $ 0.439$ & $ 0.163$ & $ 0.219$ \\
-                \bottomrule
-            \end{tabular}
-        \end{adjustbox}
-    \end{center}
-    \begin{itemize}
-        \item Watterson's $\thetaSyn$ is the observed genetic diversity calculated for synonymous changes.
-        \item \textit{Precision} is the estimation of the selection coefficient at population scale ($\Spop$) given that $\Sphy$ is known.
-        \item \textit{Recall} is the estimation of $\Sphy$ given selection coefficient at the population scale ($\Spop$) is known.
-        \item \textit{Recall} for beneficial mutations ($\proba [\SphyBen \given \SpopBen]$) is thus the proportion of beneficial back-mutations among all beneficial mutations.
-    \end{itemize}
-
-    Altogether, comparing this table to tables 1 and S3, we acknowledge that the exact proportion of beneficial back-mutations among all beneficial ones is dependent on the model used to estimate the DFE.
-    However, we can still see that beneficial back-mutations are positively selected compared to neutral and deleterious ones, and this result is not sensitive to the underlying DFE at the population scale.
-
-    %\section{References}
-    %\printbibliography[heading=none]
-
-    %    \section{Distribution of fitness effects}
-    %    \captionof{figure}{~}
-    %    \begin{minipage}{0.49\linewidth}
-    %        \includegraphics[width=\linewidth, page=1]{artworks/2bins.Yeast.experimentalDFE.pdf}
-    %    \end{minipage}
-    %    \begin{minipage}{0.49\linewidth}
-    %        \includegraphics[width=\linewidth, page=1]{artworks/2bins.AFR.histogramDFE.pdf}
-    %    \end{minipage}
-    %    Left panel: distribution of fitness effects experimentally determined in Yeast, data obtained in \textcite{shen_synonymous_2022}.
-    %    Right panel:  distribution of fitness effects ($\Sphy$) as predicted with mutation-selection codon models, from reconstructed ancestral genome in \textit{Homo sapiens}.
-    %    The DFE predicted with mutation-selection codon models has a negative mode, consistently with experimental DFEs, meaning that most mutations are effectively deleterious.
+    \printbibliography
 \end{document}

### 2024-12-16 manuscript/S4 File.tex
Split Supplementary materials into 4 files.

--- 2024-12-05 manuscript/supp-mat-PLOS-revision-2.tex
@@
 
-\renewcommand{\thetable}{S\arabic{table}}
-\renewcommand{\thefigure}{S\arabic{figure}}
+\renewcommand{\thetable}{\Alph{table}}
+\renewcommand{\thefigure}{\Alph{figure}}
 \renewcommand{\theequation}{S.\arabic{equation}}
@@
     \maketitle
-    \part*{Supplementary materials}
+    \part*{S4 File}
+    \vspace{-1em}
     \tableofcontents
-
-    \newpage
     \listoffigures
-
-    \newpage
     \listoftables
-
     \clearpage
-    \section{Mutation-selection codon models}\label{sec:mutsel}
-
-    \subsection{Prior distributions and parameters of the model}\label{subsec:priors}
-
-    We here present the Mutation-selection codon model as a Bayesian hierarchical model, including the prior distributions and the parameters of the model.
-    This hierarchical model is formally represented as directed acyclic graph of dependencies between variables, depicted in Figure~\ref{mutsel-illustration}:
-
-    \begin{center}
-
-        \begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=0.6cm and 1.2cm,semithick]
-            \tikzstyle{every state}=[]
-
-            \node[state] (P) {$\Probmatrix\branchsiteexp$};
-            \node[state] (Q) [below right=of P] {$\Submatrix\branchsiteexp$};
-            \node[state] (R) [below right=of Q] {$\Mutmatrix$};
-            \node[state] (BL) [BLUE, right=of P] {$\branchlength\branchexp$};
-            \node[res] (BLH) [RED, right=of BL] {$ \lambda, \tau $};
-            \node[state] (f) [right=of Q] {$\Fit\siteexp $};
-            \node[state] (Ex) [BLUE, below right=of R] {$\Exchan$};
-            \node[state] (Equi) [BLUE, right=of R] {$\Mutequi$};
-            \node[state] (Base) [BLUE, above right=of f] {$\Profile\catexp$};
-            \node[state] (cat) [BLUE, right=of f] {$\catsite$};
-            \node[res] (ExH) [RED, right=of Ex] {$1,1,1,1,1,1$};
-            \node[res] (EquiH) [RED, right=of Equi] {$1,1,1,1$};
-            \node[state] (baseH) [RED, right=of Base] {$\concentrationProfile, \centerProfile $};
-            \node[state] (sb) [BLUE, right=of cat] {$\StickBreaking$};
-            \node[state] (sbH) [RED, right=of sb] {$\stickbreakinghyper$};
-
-            \path
-            (Q) edge [black] node [above right] {\ref{eq:Probmatrix}} (P)
-            (BL) edge [black] node [] {} (P)
-            (R) edge [black] node {} (Q)
-            (f) edge [black] node [above] {\ref{eq:subrates}} (Q)
-            (Ex) edge [black] node [] {} (R)
-            (Equi) edge [black] node [below] {\ref{eq:gtr-mutrates}} (R)
-            (Base) edge [black] node {} (f)
-            (cat) edge [black] node [above] {\ref{eq:sitefitness}} (f)
-            (BLH) edge [dashed, BLUE] node [above] {\ref{eq:branchlength}} (BL)
-            (ExH) edge [dashed, BLUE] node [above] {\ref{eq:DistribExchan}} (Ex)
-            (EquiH) edge [dashed, BLUE] node [above] {\ref{eq:DistribMutequi}} (Equi)
-            (baseH) edge [dashed, BLUE] node [above] {\ref{eq:DistribBase}} (Base)
-            (sb) edge [dashed, BLUE] node [above] {\ref{eq:DistribMultinomial}} (cat)
-            (sbH) edge [dashed, BLUE] node [above] {\ref{eq:DistribStickBreaking},\ref{eq:Beta}} (sb);
-        \end{tikzpicture}
-        \captionof{figure}[Bayesian hierarchical model.]{
-    \textbf{Bayesian hierarchical model.} Nodes of the directed acyclic graph are the variables, and edges are the functions.
-    Hyper-parameters are depicted in {\color{RED}{red}} circles, random variables in {\color{BLUE}{blue}} circles, and transformed variables in black.
-    {\color{BLUE}{Blue}} dashed line denotes a drawing from a random distribution, and black solid lines denote a function.
-    All the nodes pointing toward a given node (upstream) are its dependencies which determine its distribution.
-    The other way around, following the arrows in the DAG (downstream), simple {prior} distributions are combined together to form more complex joint {prior} distributions which ultimately define the {prior} distribution of the model.
-    Equations~\ref{eq:gtr-mutrates} to~\ref{eq:Probmatrix} describe the relationship between variables (sections~\ref{sec:nuc} to~\ref{sec:codon}).
-    \label{mutsel-illustration}}
-    \end{center}
-
-    \subsection{Nucleotide mutation rates}
-    \label{sec:nuc}
-    The generalized time-reversible (GTR) nucleotide mutation rate matrix $\Mutmatrix$ is a function of the nucleotide frequencies $\Mutequi$ and the symmetric exchangeability rates $\Exchan$~\cite{tavare_probabilistic_1986}.
-    $\Mutequi = (\mutequi_A , \mutequi_C , \mutequi_G , \mutequi_T)$ is the equilibrium base frequency vector, giving the frequency at which each base occurs at each site.
-    $\Exchan = \left( \exchan_{AC}, \exchan_{AG}, \exchan_{AT}, \exchan_{CG}, \exchan_{CT}, \exchan_{GT}\right)$ is the vector of exchangeabilities between nucleotides.
-    Altogether, the rate matrix is:
-    \begin{equation}
-        \label{eq:gtr-mutrates}
-        \Mutmatrix =
-        \begin{blockarray}{ccccc}
-            & A & C & G & T \\
-            \begin{block}{c(cccc)}
-                A & -\mu_A & {\exchan_{AC}\mutequi_C} & {\exchan_{AG}\mutequi_G} & {\exchan_{AT}\mutequi_T} \\
-                C & {\exchan_{AC}\mutequi_A} &                        -\mu_C & {\exchan_{CG}\mutequi_G} & {\exchan_{CT}\mutequi_T} \\
-                G & {\exchan_{AG}\mutequi_A} & {\exchan_{CG}\mutequi_C} &                        -\mu_G & {\exchan_{GT}\mutequi_T} \\
-                T & {\exchan_{AT}\mutequi_A} & {\exchan_{CT}\mutequi_C} & {\exchan_{GT}\mutequi_G} & -\mu_T\\
-            \end{block}
-        \end{blockarray}
-    \end{equation}
-    By definition, the sum of the entries in each row of the nucleotide rate matrix $\Mutmatrix$ is equal to $0$, giving the diagonal entries:
-    \begin{equation}
-        \mu_a = \sum\limits_{ b \neq a, b \in \{A, C, G, T\} } \mutmatrix_{a,b}
-    \end{equation}
-    The {prior} on the exchangeabilities $\Exchan$ is a uniform Dirichlet distribution of dimension $6$:
-    \begin{equation}
-        \label{eq:DistribExchan}
-        \Exchan \sim \text{Dir}\left( 1,1,1,1,1,1 \right).
-    \end{equation}
-    The {prior} on the equilibrium base frequencies $\Mutequi$ is a uniform Dirichlet distribution of dimension $4$:
-    \begin{equation}
-        \label{eq:DistribMutequi}
-        \Mutequi \sim \text{Dir}\left( 1,1,1,1 \right)
-    \end{equation}
-    The general time-reversible nucleotide matrix is normalized with a total flow of $1$:
-    \begin{equation}
-        \sum\limits_{a \in \{A, C, G, T\}} - \mutequi_a \mutmatrix_{a,a} = 1,
-    \end{equation}
-    such that we expect $1$ {substitution} per unit of branch length.
-
-    \subsection{Site-specific amino-acid fitness profiles}
-    \label{sec:profiles}
-    Site-specific amino-acid fitness profiles are assumed i.i.d. from a mixture model, itself endowed with a truncated Dirichlet process prior.
-    Specifically, the mixture has $\Ncat$ components ($\Ncat = 30$ by default).
-    The prior on component weights~($\StickBreaking$) is modeled using a stick-breaking process, truncated at $\Ncat$ and of parameter $\stickbreakinghyper=1$:
-    \begin{align}
-        \label{eq:DistribStickBreaking}
-        \begin{split}
-            & \StickBreaking \sim \text{StickBreaking}\left( \Ncat, \stickbreakinghyper \right)\\
-            \iff & \stickbreaking_{\cat} = \stick_{\cat}\cdot \prod _{{\indice=1}}^{{\cat-1}}\left(1-\stick_{\indice}\right),\ \Setcat,
-        \end{split}
-    \end{align}
-    where $\stick_{\cat}$ are i.i.d. from a beta distribution
-    \begin{equation}
-        \label{eq:Beta}
-        \stick_{\cat} \sim \text{Beta}\left( 1, \stickbreakinghyper \right),\ \Setcat.
-    \end{equation}
-    Of note, the weights decrease geometrically in expectation, at rate $\stickbreakinghyper$, such that lower values of $\stickbreakinghyper$ induce more heterogeneous distributions of weights.
-
-    Each component of the mixture defines a 20-dimensional fitness profile $\Profile\catexp$ (summing to $1$), for $ \Setcat$.
-    These fitness profiles are i.i.d. from a Dirichlet of center $\centerProfile=1$ and concentration $\concentrationProfile=1$:
-    \begin{equation}
-        \label{eq:DistribBase}
-        \Profile\catexp \sim \text{Dir}\left( \centerProfile,\ \concentrationProfile \right),\ \Setcat.
-    \end{equation}
-
-    Site allocations to the mixture components $\catsite \in \catInterval $, for $\Setsite$ running over the $\Nsite$ sites of the alignment, are i.i.d. multinomial of parameter $\StickBreaking$:
-    \begin{align}
-        \label{eq:DistribMultinomial}
-        \catMultiVar \sim \text{Multinomial}\left( \StickBreaking \right), \\
-        \text{ where } \catmultivar_{\cat} = \sum_{\Setsite} \mathbb{1}_{\catsite = \cat}
-    \end{align}
-
-    For a given parameter configuration for the mixture, the scaled fitness $\Fit\siteexp$ at site $\site$, are obtained by taking the logarithm of fitness assigned to this site:
-    \begin{equation}
-        \label{eq:sitefitness}
-        \Fit\siteexp = \ln \left( \Profile^{\left( \catsite \right)} \right),\ \Setsite.
-    \end{equation}
-
-    \subsection{Branch length}
-    The topology of the rooted phylogenetic tree is supposed to be known and is not estimated by the model.
-    The branch lengths $\branchlength\branchexp$ are defined as the expected number of {neutral} substitutions per {DNA} site along a branch, each from a Gamma distribution of mean $\lambda=0.1$ and scale $\tau=1$:
-    \begin{equation}
-        \label{eq:branchlength}
-        \branchlength\branchexp \sim \text{Gamma}\left( \lambda, \tau \right).
-    \end{equation}
-
-    \subsection{Codon substitution rates}
-    \label{sec:codon}
-    The mutation rate between codons $\ci$ and $\cj$, denoted $\mu_{\itoj}$ depends on the underlying nucleotide change between the codons.
-    First, if codons $\ci$ and $\cj$ are not nearest-neighbours, $\mu_{\itoj}$ is equal to $0$.
-    Second, if codons $\ci$ and $\cj$ are only one mutation away, $\mu_{\itoj}$ is given by the underlying nucleotide relative rate~(${\mutmatrix_{\itoj}}$).
-
-    For a given site $\site$, the {codon} {substitution} rate matrix $\Submatrix\siteexp$ is given by:
-    \begin{equation}
-        \label{eq:subrates}
-        \begin{dcases}
-            \submatrix\siteexp_{\itoj} = 0\text{ if codons $\ci$ and $\cj$ are not nearest-neighbors,} \\
-            \submatrix\siteexp_{\itoj} = \mu_{\itoj}\text{ if codons $\ci$ and $\cj$ are {synonymous},} \\
-            \submatrix\siteexp_{\itoj} = \mu_{\itoj} \dfrac{ \fitj\siteexp - \fiti\siteexp}{{1 - \e^{\fiti\siteexp - \fitj\siteexp} }} \text{ if codons $\ci$ and $\cj$ are non-synonymous,}\\
-            \submatrix\siteexp_{\ci, \ci} = - \sum\limits_{ \cj \neq \ci, \cj=1}^{61} \submatrix\siteexp_{\itoj}.
-        \end{dcases}
-    \end{equation}
-    Together, the probability of transition between codons for a given branch $\branch$ and site $\site$ is:
-    \begin{equation}
-        \label{eq:Probmatrix}
-        \Probmatrix\branchsiteexp = \e^{\branchlength\branchexp \Submatrix\siteexp},
-    \end{equation}
-    which are the matrices necessary to compute the {likelihood} of the data ($\data$) given the parameters of the model using the pruning algorithm.
-
-    \subsection{Bayesian implementation}
-    \label{sec:Bayesian}
-    Bayesian inference was conducted using Markov Chain Monte Carlo (MCMC).
-    Most phylogenetic {MCMC} samplers target the distribution over the model parameters given the sequence alignment, which means that they have to repeatedly invoke the pruning algorithm to recalculate the {likelihood} which is most often the limiting step of the {MCMC}.
-    An alternative, which is used here, is to do the {MCMC} conditionally on the detailed {substitution} history $\subhistory$, thus doing the {MCMC} over the augmented configuration~($\subhistory$, $\data$), under the target distribution obtained by combining the mapping-based {likelihood} with the {prior} over model parameters.
-    The key idea that makes this strategy efficient is that the mapping-based {likelihood} depends on compact summary statistics of $\subhistory$, leading to a very fast evaluation of the {likelihood}.
-    On the other hand, this requires to implement more complex {MCMC} procedures that have to alternate between:
-    \begin{enumerate}
-        \item sampling $\subhistory$ conditionally on the data and the current parameter configuration.
-        \item re-sampling the parameters conditionally on $\subhistory$.
-    \end{enumerate}
-
-    To implement the mapping-based {MCMC} sampling strategy, we first sample the detailed {substitution} history $\subhistory$ for all sites along the tree.
-    Several methods exist for doing this~\cite{nielsen_mapping_2002,rodrigue_uniformization_2008}, which are used here in combination: first trying the accept-reject method of \textcite{nielsen_mapping_2002}, then switching to the uniformization approach of \textcite{rodrigue_uniformization_2008} if the first round has failed.
-
-    Then, we write down the probability of $\subhistory$ given the parameters, and finally, we collect all factors that depend on some parameter of interest and make some simplifications.
-    This ultimately leads to relatively compact sufficient statistics allowing for fast numerical evaluation of the likelihood~\cite{irvahn_phylogenetic_2014,davydov_state_2017}.
-
-    \subsection{BayesCode software}\label{subsec:bayescode}
-    In \textit{BayesCode} (\href{https://github.com/ThibaultLatrille/BayesCode}{github.com/ThibaultLatrille/BayesCode}, v1.3.1), we ran the mutation-selection codon models \textit{mutselomega} for 2000 points of MCMC with the options:
-    \begin{scriptsize}
-        \begin{verbatim}
- mutselomega ---omegashift 0.0 --ncat 30 -a my_alignment.phy -t my_tree.newick -u 2000 my_genename
-        \end{verbatim}
-    \end{scriptsize}
-    The collection of site-specific fitness profiles ($\UniDimArray{F^{(i)}}, \forall i$) are then obtained by running \textit{readmutselomega}, reading 1000 points of MCMC (first 1000 are considered as burn-in) with the options:
-    \begin{scriptsize}
-        \begin{verbatim}
- readmutselomega --every 1 --until 2000 --burnin 1000 --ss my_genename
-        \end{verbatim}
-    \end{scriptsize}
-    The gene-specific $4 \times 4$ nucleotide mutation rate matrix ($\UniDimArray{\mu}$) is also obtained by running \textit{readmutselomega}, reading 1000 points of MCMC (first 1000 are considered as burn-in) with the options:
-    \begin{scriptsize}
-        \begin{verbatim}
- readmutselomega --every 1 --until 2000 --burnin 1000 --nuc my_genename
-        \end{verbatim}
-    \end{scriptsize}
-
-    \section{Beneficial mutations in the terminal lineages and populations}\label{sec:beneficial-mutations}
-
-    \subsection{Example sites}\label{subsec:example-sites}
-
-    We extracted protein-coding DNA alignments across mammals centered around the codon site (two flanking codons in white background) for which the beneficial non-adaptive mutations ($\SphyBen$) have been detected in \textit{Chlorocebus sabaeus}.
-    We also show the translated amino acids of this region.
-    For instance, in DNA alignment of gene SELE (\ref{fig:example-1}), the nucleotide at site 1722 has mutated (from T to C) at the basis of Simiiformes (monkeys and apes), modifying the corresponding amino acid from Serine to Proline, but has been subsequently reverted in the branch of \textit{Chlorocebus sabaeus}.
-    However, other substitutions classified as $\SphyBen$ cannot be clearly interpreted as reversions \textit{sensu stricto} along the terminal branch of \textit{Chlorocebus sabaeus}.
-    Indeed, we acknowledge that on a fixed fitness landscape, a deleterious mutation can be compensated by transitions to other fitter amino-acids, and not necessarily the ancestral one.
-
-    Finally, we generated the fasta alignment for all $\SphyBen$ mutations that we detected, either in the terminal lineage or in segregating polymorphisms.
-    These fasta files are available at Zenodo (\url{https://doi.org/10.5281/zenodo.7878953}), across all populations, under a zip file (\textit{alignment\_around\_non\_adaptive\_mutations.zip}) alongside a python script to obtain the figures (as in Figures~\ref{fig:example-1} and~\ref{fig:example-2}) given these alignments (\textit{plot\_variations.py}).
-
-    \newpage
-    \begin{center}
-        \includegraphics[width=0.9\linewidth, page=1]{artworks/Alignment.Chlorocebus_sabaeus.Saint_Kitts-0.pdf}
-        \captionof{figure}[Examples sites of $\SphyBen$ mutations in \textit{Chlorocebus sabaeus} (reversions).]{\textbf{Examples sites of $\bm{\SphyBen}$ mutations in \textit{Chlorocebus sabaeus}  (reversions).} The first line is the name of the gene, the second line the position of the mutation in the OrthoMam protein-coding DNA alignment, and the arrows in the third line correspond to the position of the mutation in the nucleotide sequence (left) and in the corresponding amino acid sequence (right)\label{fig:example-1}}
-    \end{center}
-
-    \newpage
-    \begin{center}
-        \includegraphics[width=0.9\linewidth, page=1]{artworks/Alignment.Chlorocebus_sabaeus.Saint_Kitts-1.pdf}
-        \captionof{figure}[Examples sites of $\SphyBen$ mutations in \textit{Chlorocebus sabaeus}.]{\textbf{Examples sites of $\bm{\SphyBen}$ mutations in \textit{Chlorocebus sabaeus}.} The first line is the name of the gene, the second line the position of the mutation in the OrthoMam protein-coding DNA alignment, and the arrows in the third line correspond to the position of the mutation in the nucleotide sequence (left) and in the corresponding amino acid sequence (right).\label{fig:example-2}}
-    \end{center}
-
-    \newpage
-    \subsection{Selection along the terminal branches}\label{subsec:summary-table-mutsel}
-
-    \subsubsection{Probability of mutations and substitutions to be \texorpdfstring{$\SphyDel$}{D₀}, \texorpdfstring{$\SphyNeu$}{N₀} or \texorpdfstring{$\SphyBen$}{B₀}}
-    Among all the substitutions found in each terminal branch, between 10 and 13\% were $\SphyBen$ ($\proba_{div}[ \SphyBen {]}$), while $\SphyBen$ mutations only represent between 0.9 and 1.2\% of all non-synonymous mutations ($\proba[ \SphyBen {]}$), as shown in Table~\ref{table:pdiv}.
-
-    \begin{center}
-        \scriptsize
-        \begin{longtable*}{|l|l|r|r|r|r|r|r|}
-            \toprule
-            Population &             Species & $\proba{[} \SphyDel {]}$ & $\proba{[} \SphyNeu {]}$ & $\proba{[} \SphyBen {]}$ & $\proba_{div}[ \SphyDel {]}$ & $\proba_{div}[ \SphyNeu {]}$ & $\proba_{div}[ \SphyBen {]}$ \\
-            \midrule
-            \endhead
-            \midrule
-            \multicolumn{8}{r}{{Continued on next page}} \\
-            \midrule
-            \endfoot
-
-            \bottomrule
-            \endlastfoot
-            \rowcolor{LIGHTGREY} Equus c. & Equus caballus & $ 0.923$ & $ 0.065$ & $ 0.012$ & $ 0.462$ & $ 0.419$ & $ 0.118$ \\
-            Iran & Bos taurus & $ 0.924$ & $ 0.065$ & $ 0.011$ & $ 0.515$ & $ 0.362$ & $ 0.123$ \\
-            Uganda & Bos taurus & $ 0.924$ & $ 0.065$ & $ 0.011$ & $ 0.514$ & $ 0.361$ & $ 0.125$ \\
-            \rowcolor{LIGHTGREY} Australia & Capra hircus & $ 0.923$ & $ 0.066$ & $ 0.011$ & $ 0.494$ & $ 0.386$ & $ 0.121$ \\
-            \rowcolor{LIGHTGREY} France & Capra hircus & $ 0.923$ & $ 0.066$ & $ 0.011$ & $ 0.494$ & $ 0.386$ & $ 0.120$ \\
-            \rowcolor{LIGHTGREY} Iran (C. aegagrus) & Capra hircus & $ 0.923$ & $ 0.066$ & $ 0.011$ & $ 0.493$ & $ 0.386$ & $ 0.120$ \\
-            \rowcolor{LIGHTGREY} Iran & Capra hircus & $ 0.923$ & $ 0.066$ & $ 0.011$ & $ 0.492$ & $ 0.387$ & $ 0.121$ \\
-            \rowcolor{LIGHTGREY} Italy & Capra hircus & $ 0.923$ & $ 0.066$ & $ 0.011$ & $ 0.494$ & $ 0.386$ & $ 0.120$ \\
-            \rowcolor{LIGHTGREY} Morocco & Capra hircus & $ 0.923$ & $ 0.066$ & $ 0.011$ & $ 0.491$ & $ 0.387$ & $ 0.122$ \\
-            Iran & Ovis aries & $ 0.922$ & $ 0.067$ & $ 0.012$ & $ 0.568$ & $ 0.323$ & $ 0.109$ \\
-            Iran (O. orientalis) & Ovis aries & $ 0.922$ & $ 0.067$ & $ 0.011$ & $ 0.573$ & $ 0.320$ & $ 0.108$ \\
-            Iran (O. vignei) & Ovis aries & $ 0.922$ & $ 0.067$ & $ 0.012$ & $ 0.567$ & $ 0.325$ & $ 0.109$ \\
-            Various & Ovis aries & $ 0.922$ & $ 0.067$ & $ 0.011$ & $ 0.572$ & $ 0.321$ & $ 0.107$ \\
-            Morocco & Ovis aries & $ 0.922$ & $ 0.067$ & $ 0.012$ & $ 0.570$ & $ 0.321$ & $ 0.108$ \\
-            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus & $ 0.926$ & $ 0.065$ & $ 0.009$ & $ 0.485$ & $ 0.393$ & $ 0.122$ \\
-            \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus & $ 0.926$ & $ 0.065$ & $ 0.009$ & $ 0.485$ & $ 0.391$ & $ 0.124$ \\
-            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus & $ 0.926$ & $ 0.065$ & $ 0.009$ & $ 0.484$ & $ 0.393$ & $ 0.124$ \\
-            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus & $ 0.926$ & $ 0.065$ & $ 0.009$ & $ 0.483$ & $ 0.394$ & $ 0.123$ \\
-            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus & $ 0.926$ & $ 0.065$ & $ 0.009$ & $ 0.485$ & $ 0.392$ & $ 0.123$ \\
-            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus & $ 0.926$ & $ 0.065$ & $ 0.009$ & $ 0.484$ & $ 0.393$ & $ 0.123$ \\
-            \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus & $ 0.926$ & $ 0.065$ & $ 0.009$ & $ 0.480$ & $ 0.394$ & $ 0.125$ \\
-            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus & $ 0.926$ & $ 0.065$ & $ 0.009$ & $ 0.483$ & $ 0.394$ & $ 0.123$ \\
-            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus & $ 0.926$ & $ 0.065$ & $ 0.009$ & $ 0.485$ & $ 0.393$ & $ 0.123$ \\
-            African & Homo sapiens & $ 0.925$ & $ 0.065$ & $ 0.010$ & $ 0.561$ & $ 0.341$ & $ 0.099$ \\
-            Admixed American & Homo sapiens & $ 0.925$ & $ 0.065$ & $ 0.010$ & $ 0.561$ & $ 0.340$ & $ 0.099$ \\
-            East Asian & Homo sapiens & $ 0.925$ & $ 0.065$ & $ 0.010$ & $ 0.560$ & $ 0.341$ & $ 0.098$ \\
-            European & Homo sapiens & $ 0.925$ & $ 0.065$ & $ 0.010$ & $ 0.562$ & $ 0.340$ & $ 0.098$ \\
-            South Asian & Homo sapiens & $ 0.925$ & $ 0.065$ & $ 0.010$ & $ 0.561$ & $ 0.341$ & $ 0.099$ \\
-        \end{longtable*}
-    \captionof{table}[Probability of mutations and substitutions to be $\SphyDel$, $\SphyNeu$ or $\SphyBen$.]{\textbf{Probability of mutations and substitutions to be $\bm{\SphyDel}$, $\bm{\SphyNeu}$ or $\bm{\SphyBen}$.}
-    $\proba{[} \SphyDel {]}$ (eq.~5) is the probability for a new mutation to be deleterious.
-     These mutations have a selection coefficient predicted at the phylogenetic-scale lower than -1, thus toward a less fit amino-acid.
-    $\proba{[} \SphyNeu {]}$ (eq.~5) is the probability for a new mutation to be nearly-neutral.
-    These mutations have a selection coefficient predicted at the phylogenetic-scale between -1 and 1.
-    $\proba{[} \SphyBen {]}$ (eq.~5) is the probability for a new mutation to be non-adaptive beneficial.
-    These mutations have a selection coefficient predicted at the phylogenetic-scale larger than 1, thus toward a more fit amino-acid.
-    $\proba_{div}[\SphyDel{]}$ is the proportion of substitutions in the terminal branch that are $\SphyDel$.
-    $\proba_{div}[\SphyNeu{]}$ is the proportion of substitutions in the terminal branch that are $\SphyNeu$.
-    $\proba_{div}[\SphyBen{]}$ is the proportion of substitutions in the terminal branch that are $\SphyBen$.\label{table:pdiv}}
-    \end{center}
-    \newpage
-
-    \subsubsection{\texorpdfstring{$\dnds$}{dₙ/dₛ} for \texorpdfstring{$\SphyDel$}{D₀}, \texorpdfstring{$\SphyNeu$}{N₀} or \texorpdfstring{$\SphyBen$}{B₀}}
-    Theoretically, $\omega = \dn / \ds$ can be related to the underlying scaled selection coefficient ($S$) with the relation $\omega = S /(1-\exp(-S))$ as in \cite[eq. 3]{nielsen_estimating_2003}.
-    In our experiments, our observed $\dn(\SphyBen) / \ds$ is within the range of $1.169$ (\textit{C.
-hircus}) to 1.745 (\textit{H.
-sapiens}), as shown in Table~\ref{table:dnds}, translating into an average $S$ of $\approx0.32$ to $\approx1.24$, so indeed only slightly advantageous.\\
-
-    Of note, observing $\dn(\SphyBen) / \ds >1$ is an important check that $\SphyBen$ mutations are indeed positively selected with an increased substitution rate.
-    Since $\dn(\SphyNeu) / \ds$ is close to 1 for the predicted nearly-neutral mutations, this means that the selection coefficients predicted at the mutation-selection balance are good proxies of selection, then observing $\dn(\SphyBen) / \ds > 1$ is evidence of positive selection of predicted non-adaptive beneficial mutations.
-    \begin{center}
-        \scriptsize
-        \begin{longtable*}{|l|r|r|r|r|}
-            \toprule
-            Species & $\dnds $ & $\dn ( \SphyDel ) / \ds$ & $\dn ( \SphyNeu ) / \ds$ & $\dn ( \SphyBen ) / \ds$ \\
-            \midrule
-            \endhead
-            \midrule
-            \multicolumn{5}{r}{{Continued on next page}} \\
-            \midrule
-            \endfoot
-
-            \bottomrule
-            \endlastfoot
-            \rowcolor{LIGHTGREY} Equus caballus & $ 0.129$ & $ 0.065$ & $ 0.832$ & $ 1.267$ \\
-            Bos taurus & [$ 0.114$, $ 0.116$] & [$ 0.063$, $ 0.064$] & [$ 0.629$, $ 0.638$] & [$ 1.280$, $ 1.328$] \\
-            \rowcolor{LIGHTGREY} Capra hircus & [$ 0.108$, $ 0.109$] & [$ 0.058$, $ 0.058$] & [$ 0.631$, $ 0.636$] & [$ 1.169$, $ 1.183$] \\
-            Ovis aries & [$ 0.127$, $ 0.129$] & [$ 0.078$, $ 0.080$] & [$ 0.619$, $ 0.621$] & [$ 1.201$, $ 1.217$] \\
-            \rowcolor{LIGHTGREY} Chlorocebus sabaeus & [$ 0.118$, $ 0.119$] & [$ 0.062$, $ 0.062$] & [$ 0.713$, $ 0.720$] & [$ 1.521$, $ 1.577$] \\
-            Homo sapiens & [$ 0.170$, $ 0.170$] & [$ 0.103$, $ 0.103$] & [$ 0.884$, $ 0.888$] & [$ 1.733$, $ 1.745$] \\
-        \end{longtable*}
-    \captionof{table}[$\dnds$ for $\SphyDel$, $\SphyNeu$ or $\SphyBen$.]{\textbf{$\bm{\dnds}$ for $\bm{\SphyDel}$, $\bm{\SphyNeu}$ or $\bm{\SphyBen}$.}
-    $\dnds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions estimated for all the non-synonymous substitutions in the terminal branch.
-    $\dn(\SphyDel) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are $\SphyDel$.
-    $\dn(\SphyNeu) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are $\SphyNeu$.
-    $\dn(\SphyBen) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are $\SphyBen$.
-    SNPs are considered fixed (as a substitution) in the populations if all sampled individuals are homozygous for the derived allele.
-    This effect results in $\dn / \ds$ varying across populations, denoted as a range per species.
-    $\dn(\SphyBen) / \ds$ values observed are above 1 and are consistent with slightly advantageous mutations.\label{table:dnds}}
-    \end{center}
-
-    \newpage
-    \subsubsection{\texorpdfstring{$\dnds$}{dₙ/dₛ} over-estimation due to non-adaptive beneficial mutations}
-    We estimated that between $\approx9$ and $\approx12\%$ of $\dnds$ is over-estimated, corresponding to non-adaptive beneficial mutations inflating the $\dnds$ statistic, as shown in Table~\ref{table:dnds-delta}.
-    \begin{center}
-        \scriptsize
-        \begin{longtable*}{|l|r|r|r|}
-            \toprule
-            Species & $\dnds $ & $\dn(\Sphy < 1) / \ds$ & $\delta(\dnds )$ \\
-            \midrule
-            \endhead
-            \midrule
-            \multicolumn{4}{r}{{Continued on next page}} \\
-            \midrule
-            \endfoot
-
-            \bottomrule
-            \endlastfoot
-            \rowcolor{LIGHTGREY} Equus caballus & $ 0.129$ & $ 0.115$ & $  10.7$ \\
-            Bos taurus & [$ 0.114$, $ 0.116$] & [$ 0.101$, $ 0.102$] & [$  11.3$, $  11.5$] \\
-            \rowcolor{LIGHTGREY} Capra hircus & [$ 0.108$, $ 0.109$] & [$ 0.096$, $ 0.097$] & [$  11.0$, $  11.2$] \\
-            Chlorocebus sabaeus & [$ 0.118$, $ 0.119$] & [$ 0.104$, $ 0.105$] & [$  11.4$, $  11.7$] \\
-            \rowcolor{LIGHTGREY} Homo sapiens & [$ 0.170$, $ 0.170$] & [$ 0.154$, $ 0.155$] & [$ 8.926$, $ 8.996$] \\
-            Ovis aries & [$ 0.127$, $ 0.129$] & [$ 0.115$, $ 0.117$] & [$ 9.663$, $ 9.894$] \\
-        \end{longtable*}
-        \captionof{table}[$\dnds$ over-estimation due to non-adaptive beneficial mutations.]{\textbf{$\bm{\dnds}$ over-estimation due to non-adaptive beneficial mutations.}
-        $\dnds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions estimated for all the non-synonymous substitutions in the terminal branch.
-        $\dn(\Sphy < 1) / \ds$ (eq.~6) is the ratio of non-synonymous over synonymous substitutions, when restricted to non-synonymous substitutions in the terminal branch that are not $\SphyBen$.
-        This is the estimated divergence when we remove non-adaptive beneficial mutations.
-        $\delta(\dnds)$ (eq.~7) is the fraction of the divergence ($\dnds$) that is over-estimated: the difference between $\dnds$ and $\dn(\Sphy < 1) / \ds$.\label{table:dnds-delta}}
-    \end{center}
-    \newpage
-    \section{Gene ontology enrichment}
-
-    \subsection{Gene ontology enrichment in \texorpdfstring{$\SphyBen$}{B₀} SNPs}
-
-    To assess whether $\SphyBen$ SNPs are enriched in specific gene functions, we used gene ontology (GO) terms at the gene level.
-    Thus, for each $\SphyBen$ SNP detected in a focal population, we annotated this SNP with GO terms inherited from the gene in which the SNP is located.
-    We restricted this analysis solely on genes annotated with at least one GO term.
-    To assess the weight of each GO term in the set of $\SphyBen$ SNPs, we computed the proportion of $\SphyBen$ SNPs annotated with a given GO term.
-    We then tested if the distribution of $\SphyBen$ SNPs is different between genes sharing a common GO term and the rest of the genes, as shown in Table~\ref{table:ontology}.
-
-    \begin{center}
-        \scriptsize
-        \begin{longtable*}{|l|l|r|r|r|r|r|}
-            \toprule
-            GO id & GO name & $p$ & $r$ & Mann-Whitney U & $p_{\mathrm{v}}$ & $p_{\mathrm{v}}^{\mathrm{adj}}$ \\
-            \midrule
-            \endhead
-            \midrule
-            \multicolumn{7}{r}{Continued on next page} \\
-            \midrule
-            \endfoot
-            \bottomrule
-            \endlastfoot
-            GO:0003777 & microtubule motor activity & $ 0.027$ & $ 1.802$ & $1.1\times 10^{5}$ & $1.8\times 10^{-6}$ & $\bm{0.0008{^*}}$ \\
-            GO:0005578 & proteinaceous extracellular matrix & $ 0.069$ & $ 2.071$ & $4.7\times 10^{5}$ & $1.9\times 10^{-6}$ & $\bm{0.00084{^*}}$ \\
-            GO:0003774 & motor activity & $ 0.023$ & $ 1.127$ & $1.1\times 10^{5}$ & $6.7\times 10^{-5}$ & $\bm{ 0.029{^*}}$ \\
-            GO:0030198 & extracellular matrix organization & $ 0.039$ & $ 1.956$ & $2.7\times 10^{5}$ & $0.00055$ & $ 0.239~~$ \\
-            GO:0007018 & microtubule-based movement & $ 0.023$ & $ 0.924$ & $1.3\times 10^{5}$ & $0.00073$ & $ 0.315~~$ \\
-            GO:0005576 & extracellular region & $ 0.178$ & $ 2.195$ & $1.9\times 10^{6}$ & $0.00083$ & $ 0.359~~$ \\
-            GO:0006898 & receptor-mediated endocytosis & $ 0.027$ & $ 1.803$ & $1.7\times 10^{5}$ & $ 0.001$ & $ 0.512~~$ \\
-            GO:0006355 & regulation of transcription & $ 0.069$ & $ 0.275$ & $1.9\times 10^{6}$ & $ 0.002$ & $ 0.815~~$ \\
-            GO:0005604 & basement membrane & $ 0.019$ & $ 1.638$ & $1.1\times 10^{5}$ & $ 0.002$ & $ 0.852~~$ \\
-            GO:0007229 & integrin-mediated signaling pathway & $ 0.019$ & $ 1.930$ & $1.1\times 10^{5}$ & $ 0.003$ & $ 1.000~~$ \\
-            GO:0016887 & ATPase activity & $ 0.031$ & $ 1.149$ & $1.8\times 10^{5}$ & $ 0.003$ & $ 1.000~~$ \\
-            GO:0007155 & cell adhesion & $ 0.062$ & $ 1.438$ & $5.8\times 10^{5}$ & $ 0.005$ & $ 1.000~~$ \\
-            GO:0005634 & nucleus & $ 0.266$ & $ 0.557$ & $3.9\times 10^{6}$ & $ 0.005$ & $ 1.000~~$ \\
-            GO:0006351 & transcription & $ 0.073$ & $ 0.339$ & $1.9\times 10^{6}$ & $ 0.008$ & $ 1.000~~$ \\
-            GO:0005654 & nucleoplasm & $ 0.124$ & $ 0.443$ & $2.6\times 10^{6}$ & $ 0.009$ & $ 1.000~~$ \\
-            GO:0006366 & transcription from RNA polymerase II promoter & $ 0.008$ & $ 0.063$ & $6.2\times 10^{5}$ & $ 0.011$ & $ 1.000~~$ \\
-            GO:0005829 & cytosol & $ 0.212$ & $ 0.541$ & $3.5\times 10^{6}$ & $ 0.012$ & $ 1.000~~$ \\
-            GO:0016853 & isomerase activity & $ 0.015$ & $ 4.066$ & $ 1\times 10^{5}$ & $ 0.015$ & $ 1.000~~$ \\
-            GO:0071356 & cellular response to tumor necrosis factor & $ 0.015$ & $ 7.069$ & $ 1\times 10^{5}$ & $ 0.016$ & $ 1.000~~$ \\
-            GO:0005518 & collagen binding & $ 0.015$ & $ 2.900$ & $ 1\times 10^{5}$ & $ 0.017$ & $ 1.000~~$ \\
-            GO:0043087 & regulation of GTPase activity & $ 0.015$ & $ 2.025$ & $1.1\times 10^{5}$ & $ 0.027$ & $ 1.000~~$ \\
-            GO:0000139 & Golgi membrane & $ 0.012$ & $ 0.214$ & $6.3\times 10^{5}$ & $ 0.028$ & $ 1.000~~$ \\
-            GO:0043235 & receptor complex & $ 0.023$ & $ 0.935$ & $1.9\times 10^{5}$ & $ 0.028$ & $ 1.000~~$ \\
-            GO:0000981 & RNA polymerase II transcription factor activity & $ 0.027$ & $ 0.452$ & $9.1\times 10^{5}$ & $ 0.029$ & $ 1.000~~$ \\
-            GO:0005739 & mitochondrion & $ 0.058$ & $ 0.471$ & $1.4\times 10^{6}$ & $ 0.029$ & $ 1.000~~$ \\
-            GO:0005581 & collagen trimer & $ 0.015$ & $ 2.124$ & $1.1\times 10^{5}$ & $ 0.036$ & $ 1.000~~$ \\
-            GO:0051015 & actin filament binding & $ 0.019$ & $ 0.912$ & $1.5\times 10^{5}$ & $ 0.036$ & $ 1.000~~$ \\
-            GO:0001843 & neural tube closure & $ 0.015$ & $ 1.164$ & $1.1\times 10^{5}$ & $ 0.036$ & $ 1.000~~$ \\
-            GO:0005737 & cytoplasm & $ 0.317$ & $ 0.692$ & $4.1\times 10^{6}$ & $ 0.037$ & $ 1.000~~$ \\
-            GO:0043565 & sequence-specific DNA binding & $ 0.015$ & $ 0.308$ & $ 6\times 10^{5}$ & $ 0.039$ & $ 1.000~~$ \\
-            GO:0004222 & metalloendopeptidase activity & $ 0.019$ & $ 1.188$ & $1.6\times 10^{5}$ & $ 0.043$ & $ 1.000~~$ \\
-            GO:0007166 & cell surface receptor signaling pathway & $ 0.031$ & $ 2.871$ & $ 3\times 10^{5}$ & $ 0.046$ & $ 1.000~~$ \\
-            GO:0007156 & homophilic cell adhesion via plasma membrane... & $ 0.015$ & $ 1.013$ & $1.2\times 10^{5}$ & $ 0.050$ & $ 1.000~~$ \\
-            GO:0007286 & spermatid development & $ 0.015$ & $ 2.497$ & $1.2\times 10^{5}$ & $ 0.051$ & $ 1.000~~$ \\
-            GO:0008202 & steroid metabolic process & $ 0.015$ & $ 2.755$ & $1.2\times 10^{5}$ & $ 0.051$ & $ 1.000~~$ \\
-            GO:0061024 & membrane organization & $ 0.019$ & $ 1.516$ & $1.6\times 10^{5}$ & $ 0.052$ & $ 1.000~~$ \\
-            GO:1901796 & regulation of signal transduction by p53 class... & $ 0.019$ & $ 1.333$ & $1.6\times 10^{5}$ & $ 0.058$ & $ 1.000~~$ \\
-            GO:0006397 & mRNA processing & $ 0.004$ & $ 0.210$ & $3.5\times 10^{5}$ & $ 0.061$ & $ 1.000~~$ \\
-            GO:0006915 & apoptotic process & $ 0.015$ & $ 0.463$ & $6.4\times 10^{5}$ & $ 0.065$ & $ 1.000~~$ \\
-            GO:0043547 & positive regulation of GTPase activity & $ 0.035$ & $ 2.651$ & $3.7\times 10^{5}$ & $ 0.068$ & $ 1.000~~$ \\
-            GO:0007010 & cytoskeleton organization & $ 0.019$ & $ 1.771$ & $1.7\times 10^{5}$ & $ 0.068$ & $ 1.000~~$ \\
-            GO:0030308 & negative regulation of cell growth & $ 0.015$ & $ 3.055$ & $1.3\times 10^{5}$ & $ 0.070$ & $ 1.000~~$ \\
-            GO:0007160 & cell-matrix adhesion & $ 0.015$ & $ 1.046$ & $1.2\times 10^{5}$ & $ 0.073$ & $ 1.000~~$ \\
-            GO:0006897 & endocytosis & $ 0.023$ & $ 1.408$ & $2.2\times 10^{5}$ & $ 0.073$ & $ 1.000~~$ \\
-            GO:0003677 & DNA binding & $ 0.077$ & $ 0.448$ & $1.7\times 10^{6}$ & $ 0.075$ & $ 1.000~~$ \\
-            GO:0043202 & lysosomal lumen & $ 0.015$ & $ 1.522$ & $1.3\times 10^{5}$ & $ 0.075$ & $ 1.000~~$ \\
-            GO:0003700 & DNA binding transcription factor activity & $ 0.027$ & $ 0.343$ & $8.7\times 10^{5}$ & $ 0.076$ & $ 1.000~~$ \\
-            GO:0008134 & transcription factor binding & $ 0.004$ & $ 0.048$ & $3.2\times 10^{5}$ & $ 0.077$ & $ 1.000~~$ \\
-            GO:0005488 & binding & $ 0.046$ & $ 0.641$ & $4.1\times 10^{5}$ & $ 0.078$ & $ 1.000~~$ \\
-            GO:0045944 & positive regulation of transcription from RNA... & $ 0.039$ & $ 0.324$ & $1.1\times 10^{6}$ & $ 0.085$ & $ 1.000~~$ \\
-            GO:0005794 & Golgi apparatus & $ 0.046$ & $ 0.430$ & $1.2\times 10^{6}$ & $ 0.087$ & $ 1.000~~$ \\
-            GO:0016032 & viral process & $ 0.008$ & $ 0.321$ & $4.1\times 10^{5}$ & $ 0.089$ & $ 1.000~~$ \\
-            GO:0055085 & transmembrane transport & $ 0.054$ & $ 1.533$ & $5.9\times 10^{5}$ & $ 0.092$ & $ 1.000~~$ \\
-            GO:0006260 & DNA replication & $ 0.019$ & $ 1.051$ & $1.8\times 10^{5}$ & $ 0.096$ & $ 1.000~~$ \\
-            GO:0030425 & dendrite & $ 0.008$ & $ 0.121$ & $3.9\times 10^{5}$ & $ 0.099$ & $ 1.000~~$ \\
-            GO:0005524 & ATP binding & $ 0.127$ & $ 0.666$ & $1.5\times 10^{6}$ & $ 0.103$ & $ 1.000~~$ \\
-            GO:0005615 & extracellular space & $ 0.100$ & $ 1.699$ & $1.3\times 10^{6}$ & $ 0.107$ & $ 1.000~~$ \\
-            GO:0007283 & spermatogenesis & $ 0.039$ & $ 1.824$ & $3.9\times 10^{5}$ & $ 0.108$ & $ 1.000~~$ \\
-            GO:0005179 & hormone activity & $ 0.012$ & $ 7.683$ & $9.9\times 10^{4}$ & $ 0.118$ & $ 1.000~~$ \\
-            GO:0098793 & presynapse & $ 0.012$ & $ 2.065$ & $9.6\times 10^{4}$ & $ 0.119$ & $ 1.000~~$ \\
-            GO:0005254 & chloride channel activity & $ 0.012$ & $ 1.694$ & $9.6\times 10^{4}$ & $ 0.124$ & $ 1.000~~$ \\
-            GO:0036064 & ciliary basal body & $ 0.015$ & $ 1.378$ & $1.4\times 10^{5}$ & $ 0.125$ & $ 1.000~~$ \\
-            GO:0070062 & extracellular exosome & $ 0.104$ & $ 0.570$ & $2.1\times 10^{6}$ & $ 0.125$ & $ 1.000~~$ \\
-            GO:0090630 & activation of GTPase activity & $ 0.012$ & $ 2.519$ & $9.9\times 10^{4}$ & $ 0.127$ & $ 1.000~~$ \\
-            GO:0044212 & transcription regulatory region DNA binding & $ 0.004$ & $ 0.322$ & $2.7\times 10^{5}$ & $ 0.128$ & $ 1.000~~$ \\
-            GO:0055114 & oxidation-reduction process & $ 0.019$ & $ 0.482$ & $6.4\times 10^{5}$ & $ 0.129$ & $ 1.000~~$ \\
-            GO:0019886 & antigen processing and presentation of exogenous... & $ 0.012$ & $ 1.393$ & $9.6\times 10^{4}$ & $ 0.129$ & $ 1.000~~$ \\
-            GO:0005743 & mitochondrial inner membrane & $ 0.008$ & $ 0.463$ & $3.7\times 10^{5}$ & $ 0.133$ & $ 1.000~~$ \\
-            GO:0022617 & extracellular matrix disassembly & $ 0.012$ & $ 1.009$ & $9.6\times 10^{4}$ & $ 0.135$ & $ 1.000~~$ \\
-            GO:0042493 & response to drug & $ 0.004$ & $ 0.043$ & $2.6\times 10^{5}$ & $ 0.137$ & $ 1.000~~$ \\
-            GO:0008380 & RNA splicing & $ 0.008$ & $ 0.098$ & $2.6\times 10^{5}$ & $ 0.139$ & $ 1.000~~$ \\
-            GO:0043687 & post-translational protein modification & $ 0.008$ & $ 0.319$ & $3.6\times 10^{5}$ & $ 0.140$ & $ 1.000~~$ \\
-            GO:0010951 & negative regulation of endopeptidase activity & $ 0.012$ & $ 2.037$ & $9.9\times 10^{4}$ & $ 0.140$ & $ 1.000~~$ \\
-            GO:0000978 & RNA polymerase II proximal promoter... & $ 0.012$ & $ 0.250$ & $4.5\times 10^{5}$ & $ 0.140$ & $ 1.000~~$ \\
-            GO:0003713 & transcription coactivator activity & $ 0.004$ & $ 0.339$ & $2.6\times 10^{5}$ & $ 0.142$ & $ 1.000~~$ \\
-            GO:0001227 & transcriptional repressor activity & $ 0.012$ & $ 1.384$ & $9.9\times 10^{4}$ & $ 0.144$ & $ 1.000~~$ \\
-            GO:0005623 & cell & $ 0.012$ & $ 1.927$ & $ 1\times 10^{5}$ & $ 0.150$ & $ 1.000~~$ \\
-            GO:0030574 & collagen catabolic process & $ 0.012$ & $ 1.036$ & $9.9\times 10^{4}$ & $ 0.151$ & $ 1.000~~$ \\
-            GO:0006457 & protein folding & $ 0.015$ & $ 2.465$ & $1.5\times 10^{5}$ & $ 0.158$ & $ 1.000~~$ \\
-            GO:0016477 & cell migration & $ 0.004$ & $ 0.121$ & $2.4\times 10^{5}$ & $ 0.159$ & $ 1.000~~$ \\
-            GO:0070374 & positive regulation of ERK1 and ERK2 cascade & $ 0.019$ & $ 4.238$ & $ 2\times 10^{5}$ & $ 0.160$ & $ 1.000~~$ \\
-            GO:0007605 & sensory perception of sound & $ 0.015$ & $ 0.824$ & $1.5\times 10^{5}$ & $ 0.162$ & $ 1.000~~$ \\
-            GO:0031225 & anchored component of membrane & $ 0.012$ & $ 0.892$ & $ 1\times 10^{5}$ & $ 0.171$ & $ 1.000~~$ \\
-            GO:0016757 & transferase activity & $ 0.004$ & $ 0.435$ & $2.4\times 10^{5}$ & $ 0.177$ & $ 1.000~~$ \\
-            GO:0002376 & immune system process & $ 0.012$ & $ 0.411$ & $4.3\times 10^{5}$ & $ 0.177$ & $ 1.000~~$ \\
-            GO:0005759 & mitochondrial matrix & $ 0.008$ & $ 0.361$ & $3.3\times 10^{5}$ & $ 0.185$ & $ 1.000~~$ \\
-            GO:0010389 & regulation of G2/M transition of mitotic cell... & $ 0.012$ & $ 0.924$ & $ 1\times 10^{5}$ & $ 0.188$ & $ 1.000~~$ \\
-            GO:0005667 & transcription factor complex & $ 0.004$ & $ 0.177$ & $2.3\times 10^{5}$ & $ 0.189$ & $ 1.000~~$ \\
-            GO:0030054 & cell junction & $ 0.031$ & $ 0.251$ & $8.1\times 10^{5}$ & $ 0.190$ & $ 1.000~~$ \\
-            GO:0001650 & fibrillar center & $ 0.019$ & $ 1.540$ & $1.1\times 10^{5}$ & $ 0.191$ & $ 1.000~~$ \\
-            GO:0014069 & postsynaptic density & $ 0.004$ & $ 0.172$ & $2.2\times 10^{5}$ & $ 0.200$ & $ 1.000~~$ \\
-            GO:0046934 & phosphatidylinositol-4 & $ 0.012$ & $ 1.135$ & $1.1\times 10^{5}$ & $ 0.201$ & $ 1.000~~$ \\
-            GO:0007267 & cell-cell signaling & $ 0.004$ & $ 0.354$ & $2.2\times 10^{5}$ & $ 0.201$ & $ 1.000~~$ \\
-            GO:0001649 & osteoblast differentiation & $ 0.012$ & $ 1.917$ & $1.1\times 10^{5}$ & $ 0.201$ & $ 1.000~~$ \\
-            GO:0045893 & positive regulation of transcription & $ 0.023$ & $ 0.596$ & $6.6\times 10^{5}$ & $ 0.205$ & $ 1.000~~$ \\
-            GO:0007399 & nervous system development & $ 0.015$ & $ 0.450$ & $ 5\times 10^{5}$ & $ 0.205$ & $ 1.000~~$ \\
-            GO:0001501 & skeletal system development & $ 0.015$ & $ 1.212$ & $1.6\times 10^{5}$ & $ 0.207$ & $ 1.000~~$ \\
-            GO:0019903 & protein phosphatase binding & $ 0.012$ & $ 0.875$ & $1.1\times 10^{5}$ & $ 0.208$ & $ 1.000~~$ \\
-            GO:1902476 & chloride transmembrane transport & $ 0.012$ & $ 1.458$ & $1.1\times 10^{5}$ & $ 0.210$ & $ 1.000~~$ \\
-            GO:0007568 & aging & $ 0.015$ & $ 2.053$ & $1.6\times 10^{5}$ & $ 0.210$ & $ 1.000~~$ \\
-        \end{longtable*}
-        \captionof{table}[Gene ontology enrichment in $\SphyBen$ SNPs.]{\textbf{Gene ontology enrichment in $\bm{\SphyBen}$ SNPs.} GO terms that are enriched in genes with $\SphyBen$ SNPs in European humans (shown here are the first 100 rows with the lowest $p_{\mathrm{v}}$).
-        For each GO term, $p$ is the proportion of $\SphyBen$ SNPs that are annotated with this focal GO term among all annotated $\SphyBen$ SNPs.
-        For each gene, $p[ \SphyBen {]}$ is the proportion of sites that have a $\SphyBen$ SNP (can be 0 if no $\SphyBen$ SNP is detected for this gene).
-        For each GO term, $r$ is the ratio of the mean of $p[ \SphyBen {]}$ in the set of genes sharing the focal ontology over the mean of $p[ \SphyBen {]}$ in the rest of the genes.
-        Mann-Whitney U is the statistic testing if the distribution of $p[ \SphyBen {]}$ is different between the two sets of genes (p-value $p_{\mathrm{v}}$ for the two-sided test).
-        $p_{\mathrm{v}}^{\mathrm{adj}}$ are corrected for multiple comparison (Holm–Bonferroni correction across the ontology terms).
-        $^*$ for $p_{\mathrm{v}}^{\mathrm{adj}}$ lower than the risk $\alpha=0.05$.\label{table:ontology}
-        }
-    \end{center}
-
-    \newpage
-    \subsection{Enrichment in \texorpdfstring{$\SphyBen$}{B₀} SNPs across all gene ontology terms}
-    Whether SNPs classified as $\SphyBen$ are associated to a particular ontology is tested with a Mann-Whitney U statistic as described in Table~\ref{table:ontology}.
-    This test is performed across across all 347 gene ontology terms, giving one $p_{\mathrm{v}}$ per ontology (Table~\ref{table:ontology} for the 100 lowest $p_{\mathrm{v}}$).
-    The distribution of $p_{\mathrm{v}}$ are not strongly associated to the ontology terms of their respective genes, as shown in the histogram of Figure~\ref{fig:ontology-p}.
-
-    \begin{center}
-        \includegraphics[width=0.65\linewidth]{artworks/ontology_poly.Homo_sapiens.EUR.hist.pdf}
-        \captionof{figure}[Enrichment in $\SphyBen$ SNPs across all gene ontology terms.]{\textbf{Enrichment in $\bm{\SphyBen}$ SNPs across all gene ontology terms}.
-In order to test if the distribution of $\SphyBen$ SNPs is different between genes sharing a common GO term and the rest of the genes, we used a Mann-Whitney U test.
-The distribution of $p_{\mathrm{v}}$ obtained across all 347 gene ontology terms is shown as a histogram.\label{fig:ontology-p}}
-    \end{center}
-
-    \newpage
-
-    \section{Clinically related terms for mutations}
-
-    \subsection{Terms associated with deleterious mutations \texorpdfstring{$\SphyDel$}{D₀}}
-    SNPs predicted with $\SphyDel$ are statistically associated to clinical terms such as \textit{Likely Pathogenic} and \textit{Pathogenic}, as shown in Table~\ref{table:ontology-neg}.
-
-    \begin{center}
-        \begin{tabular}{|l|r|r|r|r|r|}
-            \toprule
-            SNP clinical ontology & $n_{\mathrm{Observed}}$ & $n_{\mathrm{Expected}}$ & Odds ratio & $p_{\mathrm{v}}$ & $p_{\mathrm{v-adjusted}}$ \\
-            \midrule
-            Benign                & 2969                    & $4043.0$                & $ 0.734$   & $ 1.000$             & $ 1.000~~$                    \\
-            Likely benign         & 2994                    & $3399.8$                & $ 0.881$   & $ 0.999$             & $ 1.000~~$                    \\
-            Risk factor           & 102                     & $ 118.2$                & $ 0.863$   & $ 0.798$             & $ 1.000~~$                    \\
-            Likely pathogenic     & 221                     & $  68.5$                  & $ 3.226$   & $1.7\times 10^{-8}$  & $\bm{6.7\times 10^{-8}{^*}}$  \\
-            Pathogenic            & 560                     & $ 193.6$                & $ 2.893$   & $4.2\times 10^{-17}$ & $\bm{2.1\times 10^{-16}{^*}}$ \\
-            \bottomrule
-        \end{tabular}
-        \captionof{table}[Terms associated with deleterious mutations $\SphyDel$.]{\textbf{Terms associated with deleterious mutations $\bm{\SphyDel}$.}
-        In humans (European population), non-synonymous SNPs in the test group ($\SphyDel$) are contrasted to SNPs in the control group ($\SphyNeu$).
-        For each clinical term, a 2x2 contingency table is built by counting the number of SNPs based on their selection coefficient and their clinical terms (whether they have this specific term or not).
-        Fisher's exact tests are then performed for these 2x2 contingency tables.
-        $^*$ for $p_{\mathrm{v}}^{\mathrm{adj}}$ corrected for multiple comparison (Holm–Bonferroni correction) lower than the risk $\alpha=0.05$.\label{table:ontology-neg}}
-    \end{center}
-
-    \subsection{Terms associated with non-adaptive beneficial mutations \texorpdfstring{$\SphyBen$}{B₀}}
-    Beneficial non-adaptive mutations are associated with clinical terms such as \textit{Benign} and \textit{Likely Benign}, as shown in Table~\ref{table:ontology-pos}.
-    \begin{center}
-        \begin{tabular}{|l|r|r|r|r|r|}
-            \toprule
-            SNP clinical ontology & $n_{\mathrm{Observed}}$ & $n_{\mathrm{Expected}}$ & Odds ratio & $p_{\mathrm{v}}$ & $p_{\mathrm{v-adjusted}}$ \\
-            \midrule
-            Benign                & 319                     & $ 261.7$                & $ 1.219$   & $ 0.002$         & $\bm{ 0.009{^*}}$         \\
-            Likely benign         & 263                     & $ 222.7$                & $ 1.181$   & $ 0.012$         & $\bm{ 0.049{^*}}$         \\
-            Risk factor           & 5                       & $ 7.847$                & $ 0.637$   & $ 0.879$         & $ 0.879~~$                \\
-            Likely pathogenic     & 7                       & $ 4.552$                & $ 1.538$   & $ 0.227$         & $ 0.682~~$                \\
-            Pathogenic            & 16                      & $  12.9$                  & $ 1.241$   & $ 0.268$         & $ 0.682~~$                \\
-            \bottomrule
-        \end{tabular}
-        \captionof{table}[Terms associated with non-adaptive beneficial mutations $\SphyBen$.]{\textbf{Terms associated with non-adaptive beneficial mutations $\bm{\SphyBen}$.}
-        In humans (European population), non-synonymous SNPs in the test group ($\SphyBen$) are contrasted to SNPs in the control group ($\SphyNeu$).
-        For each clinical term, a 2x2 contingency table is built by counting the number of SNPs based on their selection coefficient and their clinical terms (whether they have this specific term or not).
-        Fisher's exact tests are then performed for these 2x2 contingency tables.
-        $^*$ for $p_{\mathrm{v}}^{\mathrm{adj}}$ corrected for multiple comparison (Holm–Bonferroni correction) lower than the risk $\alpha=0.05$.\label{table:ontology-pos}}
-    \end{center}
-
-    \newpage
-
-    \section{Contrasting selection at the phylogenetic and population-genetic scales}
-
-    \subsection{Selection at the population-genetic scale}
-    The proportion of deleterious ($\ProbaPopDel$), nearly-neutral ($\ProbaPopNeu$) and of beneficial ($\ProbaPopBen$) mutations estimated at the population-genetic scale across the different populations is shown for each class of selection:
-    $\SphyDel$ (Figure~\ref{fig:pop-neg}), $\SphyNeu$ (Figure~\ref{fig:pop-weak}) and $\SphyBen$ (Figure~\ref{fig:pop-pos}).
-
-    \begin{center}
-        \begin{minipage}{0.75\linewidth}
-            \begin{minipage}{0.9\linewidth}
-                \includegraphics[width=\linewidth, page=1]{artworks/Theta.neg.stacked.pdf}
-            \end{minipage}
-            \begin{minipage}{0.09\linewidth}
-                \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
-            \end{minipage}
-        \end{minipage}
-    \captionof{figure}[Estimation of selection at the population scale for $\SphyDel$ mutations.]{\textbf{Estimation of selection at the population scale for $\bm{\SphyDel}$ mutations.} Each stack bar corresponds to the DFE of new mutations predicted to be $\SphyDel$  by the mutation selection model, in a given population.
-The dashed area represents the proportion of deleterious mutations ($\SpopDel$), the gray area that of neutral mutations ($\SpopNeu$), and the yellow area that of beneficial mutations ($\SpopBen$).\label{fig:pop-neg}}
-    \end{center}
-
-    \begin{center}
-        \begin{minipage}{0.75\linewidth}
-            \begin{minipage}{0.9\linewidth}
-                \includegraphics[width=\linewidth, page=1]{artworks/Theta.weak.stacked.pdf}
-            \end{minipage}
-            \begin{minipage}{0.09\linewidth}
-                \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
-            \end{minipage}
-        \end{minipage}
-    \captionof{figure}[Estimation of selection at the population scale for $\SphyNeu$ mutations.]{\textbf{Estimation of selection at the population scale for $\bm{\SphyNeu}$ mutations.} Each stack bar corresponds to the DFE of new mutations predicted to be $\SphyNeu$ by the mutation selection model, in a given population.
-The dashed area represents the proportion of deleterious mutations ($\SpopDel$), the gray area that of neutral mutations ($\SpopNeu$), and the yellow area that of beneficial mutations ($\SpopBen$).\label{fig:pop-weak}}
-    \end{center}
-
-    \begin{center}
-        \begin{minipage}{0.75\linewidth}
-            \begin{minipage}{0.9\linewidth}
-                \includegraphics[width=\linewidth, page=1]{artworks/Theta.pos.stacked.pdf}
-            \end{minipage}
-            \begin{minipage}{0.09\linewidth}
-                \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
-            \end{minipage}
-        \end{minipage}
-    \captionof{figure}[Estimation of selection at the population scale for $\SphyBen$ mutations.]{\textbf{Estimation of selection at the population scale for $\bm{\SphyBen}$ mutations.} Each stack bar corresponds to the DFE of new mutations predicted to be $\SphyBen$ by the mutation selection model, in a given population.
-The dashed area represents the proportion of deleterious mutations ($\SpopDel$), the gray area that of neutral mutations ($\SpopNeu$), and the yellow area that of beneficial mutations ($\SpopBen$).\label{fig:pop-pos}}
-    \end{center}
-
-    \newpage
-    \subsection{Distribution of scaled selection coefficients (\texorpdfstring{$\Sphy$}{S₀})}\label{subsec:expectedDFE}
-
-    Theoretically, the selection coefficient ($\Sphy$) for any mutation is related to its probability of fixation by the equation $\proba_{\text{fix}} (\Sphy) = \Sphy/(1-\exp(-\Sphy)) $.
-    It is thus possible to predict the distribution of $\Sphy$ of substitutions given the distribution of $\Sphy$ for mutations (Figure~\ref{dfe-sfs}A for one population of \textit{Chlorocebus sabaeus}) by weighting the different mutations by their $\proba_{\text{fix}} (\Sphy)$.
-    The predicted DFE (distribution of fitness effects) of substitutions (Figure~\ref{dfe-sfs}B) matches the observed DFE of substitutions (Figure~\ref{dfe-sfs}C) in the terminal lineage, meaning that the $\Sphy$ obtained by phylogenetic mutation-selection codon models is a strong predictor of selection effectively exerted on mutations in terminal lineages.
-    Equivalent figures to Figure~\ref{dfe-sfs} for each one of the 28 populations are available at Zenodo (\url{https://doi.org/10.5281/zenodo.7878953}) in file \textit{distribution\_S0\_28\_populations.pdf}.\\
-
-    \begin{center}
-        \begin{minipage}{0.32\linewidth}
-            \flushleft {\tiny A: Expected DFE for mutations}
-            \includegraphics[width=\linewidth, page=1]{artworks/DFE.Chlorocebus_sabaeus.Saint_Kitts.MutSel.pdf}
-        \end{minipage}
-        \begin{minipage}{0.32\linewidth}
-            \flushleft {\tiny B: Expected DFE for substitutions}
-            \includegraphics[width=\linewidth, page=1]{artworks/DFE.Chlorocebus_sabaeus.Saint_Kitts.MutSel.Flow.pdf}
-        \end{minipage}
-        \begin{minipage}{0.32\linewidth}
-            \flushleft {\tiny C: Observed DFE for substitutions}
-            \includegraphics[width=\linewidth, page=1]{artworks/subs.Chlorocebus_sabaeus.Saint_Kitts.bins3Mask0.9.pdf}
-        \end{minipage}
-        \\
-        \begin{minipage}{0.32\linewidth}
-            \flushleft {\tiny D: Observed DFE for polymorphisms}
-            \includegraphics[width=\linewidth, page=1]{artworks/poly.Chlorocebus_sabaeus.Saint_Kitts.bins3Mask0.9.pdf}
-        \end{minipage}
-        \begin{minipage}{0.32\linewidth}
-            \flushleft {\tiny E: Site frequency spectrum}
-            \includegraphics[width=\linewidth, page=1]{artworks/Chlorocebus_sabaeus.Saint_Kitts.MutSel-sfs.normalize.pdf}
-        \end{minipage}
-        \begin{minipage}{0.32\linewidth}
-            \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
-            \includegraphics[width=\linewidth, page=1]{artworks/Chlorocebus_sabaeus.Saint_Kitts.MutSel.polyDFE_C.pdf}
-        \end{minipage}
-        \captionof{figure}[Distribution of scaled selection coefficients ($\Sphy$).]{\textbf{Distribution of scaled selection coefficients ($\bm{\Sphy}$) in the Saint Kitts population of \textit{Chlorocebus sabaeus}.}
-        A) Distribution of scaled selection coefficients ($\Sphy$), predicted for all possible non-synonymous DNA mutations away from the ancestral exome.
-        Mutations are divided into three classes of selection: deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial non-adaptive ($\SphyBen$).
-        B) Expected distribution of $\Sphy$ for substitutions obtained by transforming the distribution of $\Sphy$ for mutations (panel A) by weighting each mutation by its scaled probability of fixation given by $\proba_{\text{fix}} (\Sphy) = \Sphy/(1-\exp(-\Sphy))$.
-        C) Distribution of scaled selection coefficients ($\Sphy$) for all observed substitutions along the terminal branch of the phylogenetic tree.
-        D) Distribution of scaled selection coefficients ($\Sphy$) for all observed polymorphisms currently segregating in the population.
-        E) The site-frequency spectrum (SFS) in the population for a random sample of 16 alleles (means in solid lines and standard deviations in color shades) for each class of selection and for synonymous mutations, supposedly neutral (black).
-The SFS represents the proportion of mutations (y-axis) with a given number of derived alleles in the population (x-axis).
-At high frequencies, deleterious mutations are underrepresented.
-        F) Proportion of beneficial $\ProbaPopDel$, nearly-neutral $\ProbaPopNeu$, and deleterious mutations $\ProbaPopBen$  estimated at the population scale for each class of selection at the phylogenetic scale.
-Proportions depicted here are not weighted by their mutational opportunities.}
-        \label{dfe-sfs}
-    \end{center}
-
-    \newpage
-    \section{Correlation with diversity}
-
-    \subsection{Phylogenetic Generalized Linear Model}
-
-    Because a correlation must account for phylogenetic relationship and non-independence of samples, we fitted a Phylogenetic Generalized Linear Model (PGLM) in R with the package caper~\cite{orme_caper_2013}, with multi-furcation of the different populations inside each species.
-    The mammalian tree imported from TimeTree~\cite{kumar_timetree_2017} and pruned to the species used in this study (Figure~\ref{tree}) is shown in newick format:
-
-    \lstinputlisting[breaklines]{artworks/PGLM.tree}
-
-    \begin{center}
-        \includegraphics[width=0.65\linewidth, page=1]{artworks/PGLM.pdf}
-        \captionof{figure}[Tree used for PGLM (Phylogenetic Generalized Linear Model).]{\textbf{Tree used for PGLM (Phylogenetic Generalized Linear Model).} The mammalian dated tree was obtained from TimeTree~\cite{kumar_timetree_2017} and pruned to include only the species analysed in this study, with multi-furcation of the different populations from each species placed at the same divergence time as the divergence to the sister species.}
-        \label{tree}
-    \end{center}
-
-    \newpage
-    Accounting for phylogenetic relationship and non-independence of samples, through the fit of a Phylogenetic Generalized Linear Model, we can estimate regression coefficient between two variables.
-    Thus, for each population, the proportion of deleterious ($\ProbaPopDel$,~\ref{fig:pop-neg-prop}), nearly-neutral ($\ProbaPopNeu$,~\ref{fig:pop-weak-prop}) and beneficial ($\ProbaPopBen$,~\ref{fig:pop-pos-prop}) mutations estimated at the population-genetic scale is shown as function of $\Ne$, and we estimated regression coefficients.
-
-    \subsubsection{Proportion of deleterious mutations (\texorpdfstring{$\SpopDel$}{D})}\label{subsec:proportion-deleterious-mutations}
-
-    Higher effective population size ($\Ne$) is typically accompanied by a higher proportion of effectively deleterious mutations at the population scale ($\proba{[} \SpopDel {]}$), as shown in~\ref{fig:pop-neg-prop} (left panel).
-    This trend is also confirmed when we restricted the analysis to class of mutations that are supposedly deleterious at the phylogenetic scale ($\SphyDel$), as shown in~\ref{fig:pop-neg-prop} (right panel).
-    This result is qualitatively in accordance with the nearly-neutral theory of evolution which argues that very slightly deleterious mutations are more efficiently purified in large populations.
-
-    \begin{center}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/results.pop_size.all_P-Sneg.scatter.pdf}
-    \end{minipage}
-    \begin{minipage}{0.49\linewidth}
-        \includegraphics[width=\linewidth, page=1]{artworks/results.pop_size.neg_P-Sneg.scatter.pdf}
-    \end{minipage}
-    \captionof{figure}[Relationship between the proportion of deleterious mutations ($\SpopDel$) and effective population size.]{\textbf{Relationship between the proportion of deleterious mutations ($\bm{\SpopDel}$) and effective population size.}
-    Left) Proportion of deleterious mutations at the population scale ($\proba{[} \SpopNeu{]}$), shown as a function of estimated effective population size ($\Ne$).
-Right) Probability for a mutation to be deleterious at the population scale, given it is predicted to be deleterious at the phylogenetic scale, as a function of estimated effective population size ($\Ne$).
-Populations are represented by circles, and squares are the mean for the species.
-Correlations account for phylogenetic relationship and non-independence of samples, through the fit of a Phylogenetic Generalized Linear Model (see Materials \& Methods).\label{fig:pop-neg-prop}}
-    \end{center}
-
-    \subsubsection{Proportion of nearly-neutral mutations (\texorpdfstring{$\SpopNeu$}{N})}\label{subsec:proportion-nearly-neutral-mutations}
-    Higher effective population size ($\Ne$) is typically accompanied by a smaller proportion of neutral mutations at the population scale ($\proba{[} \SpopNeu {]}$ in the range 0.06-0.18), as shown in~\ref{fig:pop-weak-prop} (left panel).
-    This result is more pronounced ($\proba{[} \SpopNeu \given \SphyNeu {]}$ in the range 0.36-0.73) when we restricted the analysis to the class of mutations that are supposedly nearly-neutral at the phylogenetic scale ($\SphyNeu$), as shown in~\ref{fig:pop-pos-prop} (right panel).
-    This result suggests that in populations with higher diversity (e.g.,~\textit{Bos} or \textit{Ovis}), mutations are more likely to be detected as under selection (positive or negative).
-    Alternatively stated, mutations in populations with low diversity (e.g.,~\textit{Homo}) are effectively nearly-neutral and behave as neutral mutations would.
-    This result is qualitatively in accordance with the nearly-neutral theory of evolution which argues that mutations are less efficiently selected for in small populations.
-
-    \newpage
-    \begin{center}
-        \begin{minipage}{0.49\linewidth}
-            \includegraphics[width=\linewidth, page=1]{artworks/results.pop_size.all_P-Sweak.scatter.pdf}
-        \end{minipage}
-        \begin{minipage}{0.49\linewidth}
-            \includegraphics[width=\linewidth, page=1]{artworks/results.pop_size.weak_P-Sweak.scatter.pdf}
-        \end{minipage}
-        \captionof{figure}[Relationship between the proportion of nearly-neutral mutations ($\SpopNeu$) and effective population size.]{\textbf{Relationship between the proportion of nearly-neutral mutations ($\bm{\SpopNeu}$) and effective population size..}
-        Left) Proportion of deleterious mutations at the population scale ($\proba{[} \SpopNeu{]}$), shown as a function of estimated effective population size ($\Ne$).
-Right) Probability for a mutation to be nearly-neutral at the population scale, given it is predicted to be nearly-neutral at the phylogenetic scale, as a function of estimated effective population size ($\Ne$).
-Populations are represented by circles, and squares are the mean for the species.
-Correlations account for phylogenetic relationship and non-independence of samples, through the fit of a Phylogenetic Generalized Linear Model (see Materials \& Methods).\label{fig:pop-weak-prop}}
-    \end{center}
-
-    \subsubsection{Proportion of beneficial mutations (\texorpdfstring{$\SpopBen$}{B})}\label{subsec:proportion-beneficial-mutations}
-    A higher effective population size ($\Ne$) is accompanied by a smaller proportion of beneficial mutations at the population scale ($\proba{[} \SpopBen {]}$), as shown in~\ref{fig:pop-pos-prop} (left panel).
-    This trend is also confirmed when we restricted the analysis to the class of mutations that are supposedly non-adaptive beneficial at the phylogenetic scale ($\SphyBen$), as shown in~\ref{fig:pop-pos-prop} (right panel).
-
-    \begin{center}
-        \begin{minipage}{0.49\linewidth}
-            \includegraphics[width=\linewidth, page=1]{artworks/results.pop_size.all_P-Spos.scatter.pdf}
-        \end{minipage}
-        \begin{minipage}{0.49\linewidth}
-            \includegraphics[width=\linewidth, page=1]{artworks/results.pop_size.pos_P-Spos.scatter.pdf}
-        \end{minipage}
-        \captionof{figure}[Relationship between the proportion of beneficial mutations ($\SpopBen$) and effective population size.]{\textbf{Relationship between the proportion of beneficial mutations ($\bm{\SpopBen}$) and effective population size.}
-        Left) Proportion of beneficial mutations at the population scale ($\proba{[} \SpopNeu{]}$), shown as a function of estimated effective population size ($\Ne$).
-Right) Probability for a mutation to be beneficial at the population scale, given it is predicted to be beneficial at the phylogenetic scale, as a function of estimated effective population size ($\Ne$).
-Populations are represented by circles, and squares are the mean for the species.
-Correlations account for phylogenetic relationship and non-independence of samples, through the fit of a Phylogenetic Generalized Linear Model (see Materials \& Methods).\label{fig:pop-pos-prop}}
-    \end{center}
-
-    \newpage
 
@@
 $\bm{\proba{[}\Sphy{]} / \proba{[}-\Sphy{]}}$ is the ratio of the positive part over the negative part.
-Alternatively stated, it is folding Figure~\ref{dfe-sfs}D around 0, by taking the right part (positive $\Sphy$) of the histogram over the left part (negative $\Sphy$).
+Alternatively stated, it is folding the DFE of observed polymorphism (Panel~D of Fig~D in S3~File) around 0, by taking the right part (positive $\Sphy$) of the histogram over the left part (negative $\Sphy$).
         }
@@
             The \textit{recall} value for class $\SphyBen$ is the probability for beneficial mutations to be non-adaptive (G).
+            Icons are adapted from \href{https://phylopic.org}{https://phylopic.org} under a Creative Commons license.
             \label{fig-incdiv}
@@
 
-    \newpage
     \subsection{Probability for beneficial mutations to be non-adaptive}
@@
     However, we can still see that non-adaptive beneficial mutations are positively selected compared to neutral and deleterious ones, and this result is valid for different underlying DFE.
+    \newpage
 
@@
 
-    \newpage
-
     \printbibliography

### 2024-12-16 manuscript/main-PLOS-revision-2-plos2015-formatting.tex
Split Supplementary materials into 4 files.

--- 2024-12-05 manuscript/main-PLOS-revision-2-plos2015.tex
@@
 
-% Use nameref to cite supporting information files (see Supporting Information section for more info)
+% Use nameref to cite supporting information files (see Supporting Information section~for more info)
 \usepackage{nameref,hyperref}
@@
 The model further integrates the shared evolutionary history between samples and their divergence, which, together, allow us to estimate fitness effects in sequence alignments even though sequences are not independent samples and might not represent the equilibrium distribution of amino acids (see section~\ref{subsec:s-phylogeny-method} in Materials \& Methods).
-Detailed model description is available in~\nameref{S1_File} (\nameref{S1_Fig}).
+The detailed model implementation is available in~\nameref{S1_File}, described as a Bayesian hierarchical model (Fig~A in~\nameref{S1_File}).
 
@@
 Subsequently, by quantifying the total amount of beneficial mutations in the current population across all types of DNA mutations, we could tease apart beneficial non-adaptive from adaptive mutations resulting from a change in the fitness landscape.
-Altogether, in this study, by integrating large-scale genomic datasets at both phylogenetic and population scales, we propose a way to explicitly quantify the contribution of beneficial non-adaptive mutations to positive selection across the entire exome of the six genera (figs.~\ref{fig:method}F-G).
+Altogether, in this study, by integrating large-scale genomic datasets at both phylogenetic and population scales, we propose a way to explicitly quantify the contribution of beneficial non-adaptive mutations to positive selection across the entire exome of the six genera (Fig~\ref{fig:method}F-G).
 
@@
 This ensures independence between, on the one hand, the fitness landscape estimated, and on the other hand, both substitutions that occurred in the terminal branches, and segregating polymorphisms of the focal populations.
-Example substitutions in the terminal lineage of \textit{Chlorocebus sabaeus} which are classified as $\SphyBen$ are shown in supplementary materials (section S2).
-For instance, in the mammalian protein-coding DNA alignment of gene \textit{SELE}, the nucleotide at site 1722 has mutated (from T to C) at the base of Simiiformes (monkeys and apes), modifying the corresponding amino acid from Serine to Proline, but has been subsequently reverted in the branch of \textit{Chlorocebus sabaeus} (\nameref{S2_Fig}).
-However, other substitutions classified as $\SphyBen$ in the terminal branch of \textit{Chlorocebus sabaeus} cannot be clearly interpreted as reversions along the terminal branch, and show several transitions to this amino acid across the mammalian phylogeny, as for instance site 3145 of gene \textit{THSD7A} (\nameref{S3_Fig}).
-
-Among all the substitutions found in each terminal branch, between 10 and 13\% were $\SphyBen$, while $\SphyBen$ mutations only represent between 0.9 and 1.2\% of all non-synonymous mutations (Fig~\ref{fig:homo-afr-results}A-B for humans and ~\nameref{S1_Table} for all dataset).
+Example substitutions in the terminal lineage of \textit{Chlorocebus sabaeus} which are classified as $\SphyBen$ are shown in~\nameref{S2_File} (section~1.1).
+For instance, in the mammalian protein-coding DNA alignment of gene \textit{SELE}, the nucleotide at site 1722 has mutated (from T to C) at the base of Simiiformes (monkeys and apes), modifying the corresponding amino acid from Serine to Proline, but has been subsequently reverted in the branch of \textit{Chlorocebus sabaeus} (Fig~A in~\nameref{S2_File}).
+However, other substitutions classified as $\SphyBen$ in the terminal branch of \textit{Chlorocebus sabaeus} cannot be clearly interpreted as reversions along the terminal branch, and show several transitions to this amino acid across the mammalian phylogeny, as for instance site 3145 of gene \textit{THSD7A} (Fig~B in~\nameref{S2_File}).
+
+Among all the substitutions found in each terminal branch, between 10 and 13\% were $\SphyBen$, while $\SphyBen$ mutations only represent between 0.9 and 1.2\% of all non-synonymous mutations (Fig~\ref{fig:homo-afr-results}A-B for humans, Table~A in~\nameref{S2_File} for all dataset).
 Of note, if we were to assume a stationary mutation-selection-drift equilibrium in the terminal lineage, we would expect a symmetric proportion of positively ($\SphyBen$) and negatively ($\SphyDel$) selected substitutions if there were no adaptation.
@@
 Mathematically, twice the fraction of $\SphyBen$ substitutions is an estimate of this rate.
-This rate is highly consistent across lineages (\nameref{S1_Table}) and suggests an overall frequency of nearly neutral substitutions due to consistent long-term selection pressures, mutation and drift of approximately 20\% of all substitutions (20\%-26\% across species).
+This rate is highly consistent across lineages (Table~A in~\nameref{S2_File}) and suggests an overall frequency of nearly neutral substitutions due to consistent long-term selection pressures, mutation and drift of approximately 20\% of all substitutions (20\%-26\% across species).
 
@@
 {\bf Selection coefficients of mutations in humans of African descent.}
-(A) Distribution of scaled selection coefficients ($\Sphy$), predicted for all possible non-synonymous DNA mutations away from the ancestral human exome (section \ref{subsec:nunber-of-sites}).
+(A) Distribution of scaled selection coefficients ($\Sphy$), predicted for all possible non-synonymous DNA mutations away from the ancestral human exome (section~\ref{subsec:nunber-of-sites}).
 Mutations are divided into three classes of selection: deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial ($\SphyBen$, supposedly beneficial non-adaptive mutations)
-(B) Distribution of scaled selection coefficients ($\Sphy$) for all observed substitutions along the \textit{Homo} branch after the \textit{Homo}-\textit{Pan} split (section \ref{subsec:substitution-mapping-in-the-terminal-branch}).
+(B) Distribution of scaled selection coefficients ($\Sphy$) for all observed substitutions along the \textit{Homo} branch after the \textit{Homo}-\textit{Pan} split (section~\ref{subsec:substitution-mapping-in-the-terminal-branch}).
 If there are fewer substitutions than expected, this class is thus undergoing purifying selection, as is the case for $\SphyDel$.
@@
 At high frequencies, deleterious mutations are underrepresented.
-(D) Proportion of beneficial $\ProbaPopDel$, nearly-neutral $\ProbaPopNeu$, and deleterious mutations $\ProbaPopBen$ estimated at the population scale for each class of selection at the phylogenetic scale (section \ref{subsec:s-polymorphism-method}).
+(D) Proportion of beneficial $\ProbaPopDel$, nearly-neutral $\ProbaPopNeu$, and deleterious mutations $\ProbaPopBen$ estimated at the population scale for each class of selection at the phylogenetic scale (section~\ref{subsec:s-polymorphism-method}).
 Proportions depicted here are not weighted by their mutational opportunities.
@@
 Furthermore, since in principle, $\SphyBen$ mutations are bound to reach fixation more often than neutral mutations, we calculated the $\dnds$ ratio of non-synonymous over synonymous divergence for all terminal lineages, focusing on the non-synonymous changes predicted as $\SphyBen$ mutations ($\dn(\SphyBen) / \ds$).
-We obtained values between 1.17 and 1.75 in the different lineages (\nameref{S2_Table}), meaning that $\SphyBen$ mutations reach fixation slightly more frequently than synonymous mutations that are supposed to be neutral, consistent with these $\SphyBen$ mutations being weakly beneficial.
-Such an observation is consistent with the premise that $\SphyBen$ mutations are weakly beneficial, translating to a scaled selection coefficient between 0.32 and 1.24 (\nameref{S2_Table}).
+We obtained values between 1.17 and 1.75 in the different lineages (Table~B in~\nameref{S2_File}), meaning that $\SphyBen$ mutations reach fixation slightly more frequently than synonymous mutations that are supposed to be neutral, consistent with these $\SphyBen$ mutations being weakly beneficial.
+Such an observation is consistent with the premise that $\SphyBen$ mutations are weakly beneficial, translating to a scaled selection coefficient between 0.32 and 1.24 (section~1.2 in~\nameref{S2_File}).
 Finding $\dn(\SphyBen) / \ds > 1$ for these sites confirms that these sites are closer to optimality at the end of the branch than at the beginning.
@@
 By discarding all beneficial non-adaptive mutations we can obtain an estimate of $\dnds$ which is not inflated.
-By comparing these two ways of calculating $\dnds$ (see section~\ref{subsec:substitution-mapping-in-the-terminal-branch} in Materials \& Methods), we calculated that beneficial non-adaptive mutations inflate $\dnds$ values by between 9 and 12\% across genera.
-This represents a substantial increase when considering that beneficial non-adaptive mutations only represent between 0.9 and 1.2\% of non-synonymous mutational opportunities (\nameref{S3_Table}).
+By comparing these two ways of calculating $\dnds$ (see section~\ref{subsec:substitution-mapping-in-the-terminal-branch} in Materials \& Methods), we calculated that beneficial non-adaptive mutations inflate $\dnds$ values by between 9 and 12\% across genera (Table~C in~\nameref{S2_File}).
+This represents a substantial increase when considering that beneficial non-adaptive mutations only represent between 0.9 and 1.2\% of non-synonymous mutational opportunities (Table~A in~\nameref{S2_File}).
 
@@
 
-First, SNPs classified as $\SphyBen$ are spread across the genomes and not strongly associated to the ontology terms of their respective genes (\nameref{S4_Table},~\nameref{S4_Fig}).
+First, SNPs classified as $\SphyBen$ are spread across the genomes and not strongly associated to the ontology terms of their respective genes (Table~D and Fig~C in~\nameref{S2_File}).
 In humans, some SNPs have been associated with specific clinical prognosis terms obtained by clinical evaluation of the impact of variants on human Mendelian disorders~\cite{landrum_clinvar_2018}.
@@
 Therefore, we investigated whether the non-synonymous SNPs classified as $\SphyDel$ or $\SphyBen$ showed enrichment in specific clinical terms compared to SNPs classified as $\SphyNeu$.
-Our results show that SNPs predicted as deleterious are associated with clinical terms such as \textit{Likely Pathogenic} and \textit{Pathogenic}, implying that, in general, the selective pressure of a mutation exerted across mammals is also predictive of its clinical effect in humans (\nameref{S5_Table})~\cite{sullivan_leveraging_2023}.
-Conversely, $\SphyBen$ mutations are associated with clinical terms such as \textit{Benign} and \textit{Likely Benign}, which shows that $\SphyBen$ mutations are less likely to be functionally damaging (\nameref{S6_Table}).
+Our results show that SNPs predicted as deleterious are associated with clinical terms such as \textit{Likely Pathogenic} and \textit{Pathogenic}, implying that, in general, the selective pressure of a mutation exerted across mammals is also predictive of its clinical effect in humans (Table~E in~\nameref{S2_File})~\cite{sullivan_leveraging_2023}.
+Conversely, $\SphyBen$ mutations are associated with clinical terms such as \textit{Benign} and \textit{Likely Benign}, which shows that $\SphyBen$ mutations are less likely to be functionally damaging (Table~F in~\nameref{S2_File}).
 
@@
 By gathering information across many SNPs, it is possible to estimate the distribution of fitness effects at the population scale, taking synonymous SNPs as a neutral expectation~\cite{eyre-walker_distribution_2006, eyre-walker_estimating_2009, galtier_adaptive_2016, tataru_inference_2017}.
-From these estimated fitness effects, we can derive the proportion of deleterious mutations ($\ProbaPopDel$,~\nameref{S5_Fig}), nearly-neutral mutations ($\ProbaPopNeu$,~\nameref{S6_Fig}) and beneficial mutations ($\ProbaPopBen$,~\nameref{S7_Fig}) at the population scale (see section~\ref{subsec:s-polymorphism-method} in Materials \& Methods).
-These approaches offer a unique opportunity to contrast selection coefficients estimated at the phylogenetic scale ($\Sphy$) and at the population scale ($\Spop$) in different dataset (\nameref{S8_Fig}).
+From these estimated fitness effects, we can derive the proportion of deleterious mutations ($\ProbaPopDel$), nearly-neutral mutations ($\ProbaPopNeu$) and beneficial mutations ($\ProbaPopBen$) at the population scale (see section~\ref{subsec:s-polymorphism-method} in Materials \& Methods, Fig~A-C in~\nameref{S3_File}).
+These approaches offer a unique opportunity to contrast selection coefficients estimated at the phylogenetic scale ($\Sphy$) and at the population scale ($\Spop$) in different dataset (Fig~D in~\nameref{S3_File}).
 
@@
 Moreover, estimates of mutation rate per generation ($u$), from Bergeron \textit{et al.}~\cite{bergeron_evolution_2023} and Orlando \textit{et al.}~\cite{orlando_recalibrating_2013}, and Watterson’s $\theta$ obtained from the synonymous SFS as in Achaz~\cite{achaz_frequency_2009}, allow us to obtain $\Ne$ through $\Ne=\theta/4 u)$.
-Using correlation analyses that accounted for phylogenetic relationship (see section~\ref{subsec:correlation-diversity} in Materials \& Methods,~\nameref{S9_Fig}), we found that higher $\Ne$ was associated with a smaller proportion of nearly-neutral mutations ($r^2=0.31$, $p=0.001$, Fig~\ref{fig:diversity}A).
-This result follows the prediction of the nearly-neutral theory and suggests that in populations with higher diversity (e.g.,~\textit{Bos} or \textit{Ovis}), discrimination between beneficial and deleterious mutations is more likely to occur (\nameref{S10_Fig},~\nameref{S11_Fig},~\nameref{S12_Fig}).
+Using correlation analyses that accounted for phylogenetic relationship (see section~\ref{subsec:correlation-diversity} in Materials \& Methods, Fig~E in~\nameref{S3_File}), we found that higher $\Ne$ was associated with a smaller proportion of nearly-neutral mutations ($r^2=0.31$, $p=0.001$, Fig~\ref{fig:diversity}A).
+This result follows the prediction of the nearly-neutral theory and suggests that in populations with higher diversity (e.g.,~\textit{Bos} or \textit{Ovis}), discrimination between beneficial and deleterious mutations is more likely to occur (Fig~F-H in~\nameref{S3_File}).
 Conversely, many more mutations are effectively neutral in populations with lower diversity (e.g.,~\textit{Homo}).
@@
 This result confirms that selection toward amino acids restoring existing functions is ongoing in these populations.
-Importantly, the \textit{recall} value in this case, computed as $\proba [ \SphyBen \given \SpopBen]$, is the probability for a beneficial mutation at the population scale to be a non-adaptive, i.e., going toward a fitter amino acid given a stable fitness landscape (Fig~\ref{fig:method}G,~\nameref{S7_Table}).
+Importantly, the \textit{recall} value in this case, computed as $\proba [ \SphyBen \given \SpopBen]$, is the probability for a beneficial mutation at the population scale to be a non-adaptive, i.e., going toward a fitter amino acid given a stable fitness landscape (Fig~\ref{fig:method}G, Table~A in~\nameref{S4_File}).
 In other words, the \textit{recall} value quantifies the number of beneficial mutations restoring damaged genomes instead of creating adaptive innovations.
@@
 We additionally performed controls and simulations to ensure our results were robust.
-First, we controlled that these estimations were not affected by SNP mispolarization (\nameref{S13_Fig},~\nameref{S14_Fig}).
-Second, we performed simulations at the population-genetic level and confirmed that our method was able to recover the proportion of beneficial mutations that are non-adaptive in synthetic polymorphism datasets (\nameref{S15_Fig}).
-Third, we ran our analysis filtering out CpG mutations and obtained values of $\proba [ \SphyBen \given \SpopBen]$ in the range of 5--27\%, with a mean of 14\% (\nameref{S8_Table}, \nameref{S9_Table}, \nameref{S16_Fig}), providing more conservative estimates.
+First, we controlled that these estimations were not affected by SNP mispolarization (Fig~A-B in~\nameref{S4_File}).
+Second, we performed simulations at the population-genetic level and confirmed that our method was able to recover the proportion of beneficial mutations that are non-adaptive in synthetic polymorphism datasets (Fig~C in~\nameref{S4_File}).
+Third, we ran our analysis filtering out CpG mutations and obtained values of $\proba [ \SphyBen \given \SpopBen]$ in the range of 5--27\%, with a mean of 14\% (Table~B-C in~\nameref{S4_File}, Fig~D in~\nameref{S4_File}), providing more conservative estimates.
 Finally, because the phylogenetic mutation-selection codon model should fit better for genes with uniformly conserved functions, we filtered out genes under pervasive adaptation~\cite{latrille_genes_2023} as a control.
-In this subset of the exome, containing genes with a more stable fitness landscape, we found an increase in the proportion of beneficial mutations that are non-adaptive (Wilcoxon signed-rank, $s=80$, $p=0.002$,~\nameref{S10_Table}), consistent with our expectation that beneficial mutations occur more frequently in genes under changing fitness landscapes.
+In this subset of the exome, containing genes with a more stable fitness landscape, we found an increase in the proportion of beneficial mutations that are non-adaptive (Wilcoxon signed-rank, $s=80$, $p=0.002$, Table~D in~\nameref{S4_File}), consistent with our expectation that beneficial mutations occur more frequently in genes under changing fitness landscapes.
 
@@
 As an alternative to relying solely on currently segregating mutations to quantify selection, one can leverage both polymorphism within a population and substitutions in the terminal lineage to estimate the distribution of fitness effects (DFE).
-Hence, we estimated \textit{precision} and \textit{recall} as done previously, but now including the number of substitutions per site as input for the DFE estimators (see~\ref{subsec:s-polymorphism-method} in Materials \& Methods and~\nameref{S17_Fig}).
-When including substitutions in the terminal lineage, estimates of $\proba [ \SphyBen \given \SpopBen]$ are in the 10--78\% range with a mean of 36\%, and 19 out of 28 estimates fall between 15\% and 45\% (\nameref{S11_Table}, \nameref{S12_Table}).
-
-Additionally, we controlled that these estimations were not affected by SNP mispolarization (\nameref{S18_Fig}).
-We also filtered out genes under pervasive adaptation, and again found an increase in $\proba [ \SphyBen \given \SpopBen]$, consistent with our expectation (Wilcoxon signed-rank, $s=120$, $p=0.027$,~\nameref{S13_Table}).
+Hence, we estimated \textit{precision} and \textit{recall} as done previously, but now including the number of substitutions per site as input for the DFE estimators (see~\ref{subsec:s-polymorphism-method} in Materials \& Methods and Fig~E in~\nameref{S4_File}).
+When including substitutions in the terminal lineage, estimates of $\proba [ \SphyBen \given \SpopBen]$ are in the 10--78\% range with a mean of 36\%, and 19 out of 28 estimates fall between 15\% and 45\% (Table~E-F in~\nameref{S4_File}).
+
+Additionally, we controlled that these estimations were not affected by SNP mispolarization (Fig~F in~\nameref{S4_File}).
+We also filtered out genes under pervasive adaptation, and again found an increase in $\proba [ \SphyBen \given \SpopBen]$, consistent with our expectation (Wilcoxon signed-rank, $s=120$, $p=0.027$, Table~G in~\nameref{S4_File}).
 We assessed the impact of fitting the same functional form of DFE to the three different categories of changes $\SphyDel$, $\SphyNeu$ and $\SphyBen$.
 To this aim we computed the total amount of current selection by fitting either a single DFE on the whole dataset or by summing the other three independent DFEs.
-These disjoint estimates are well correlated, with a goodness of fit $r^2={0.95, 0.89, 0.82}$ for respectively $\proba [\SpopDel]$ (\nameref{S19_Fig}), $\proba [\SpopNeu]$(\nameref{S20_Fig}) and $\proba [\SpopBen]$ (\nameref{S21_Fig}).
+These disjoint estimates are well correlated, with a goodness of fit $r^2={0.95, 0.89, 0.82}$ for respectively $\proba [\SpopDel]$ (Fig~G in~\nameref{S4_File}), $\proba [\SpopNeu]$(Fig~H in~\nameref{S4_File}) and $\proba [\SpopBen]$ (Fig~I in~\nameref{S4_File}).
 Finally, we evaluated the effect of fitting a parametric functional form for the DFE.
 As implemented in Tataru \textit{et al.}~\cite{tataru_inference_2017}, the DFE is a mixture between a reflected gamma distribution and an exponential distribution (eq.~\ref{eq:parametric-dfe}, section~\ref{subsec:precisison_recall} in Materials \& Methods).
-Instead of using such a continuous DFE, we also tested our prediction with a non-parametric functional form for the DFE, obtaining estimates of $\proba [ \SphyBen \given \SpopBen]$ in the 8--94\% range, with a mean of 43\% (\nameref{S14_Table}, \nameref{S15_Table}).
+Instead of using such a continuous DFE, we also tested our prediction with a non-parametric functional form for the DFE, obtaining estimates of $\proba [ \SphyBen \given \SpopBen]$ in the 8--94\% range, with a mean of 43\% (Table~H-I in~\nameref{S4_File}).
 
@@
 Our results concur with previous studies showing that SIFT scores~\cite{ng_sift_2003, vaser_sift_2016}, based on amino acid alignments across species, also inform on the deleterious fitness effects exerted at the population scale~\cite{chen_hunting_2021}.
-However, contrary to SIFT scores, our mutation-selection model is parameterized by a fitness function such that changes are directly interpretable as fitness effects (see also section S5).
+However, contrary to SIFT scores, our mutation-selection model is parameterized by a fitness function such that changes are directly interpretable as fitness effects (see also section~1 in~\nameref{S3_File}).
 In this regard, an interesting prediction of our model is that some deleterious mutations reach fixation due to genetic drift, while beneficial non-adaptive mutations restore states of higher fitness.
@@
 
-If there are several substitutions toward the same amino acid along the mammalian tree (\nameref{S3_Fig}), our mutation-selection model cannot formally distinguish between a scenario where mammals have fixed deleterious mutations that are reverted in several lineages, from more complex scenarios involving convergent adaptation across mammals.
+If there are several substitutions toward the same amino acid along the mammalian tree (section~1.1 in~\nameref{S2_File}), our mutation-selection model cannot formally distinguish between a scenario where mammals have fixed deleterious mutations that are reverted in several lineages, from more complex scenarios involving convergent adaptation across mammals.
 In a first scenario, repeated changes of fitness landscapes in the same direction could occur along several lineages, leading to repeated substitutions in multiple lineages (parallel or convergent adaptation).
 In a second scenario, an environmental change that occurred near the root of placental mammals ($\sim$100 Mys ago), to which extant populations are currently responding independently through weakly adaptive mutations, could also lead to repeated substitutions toward the same amino acids.
-Importantly, we would usually expect adaptive convergent mutations to be linked to particular converging phenotypes across mammals, and hence, they should not massively affect the whole genome as we find (\nameref{S4_Table},~\nameref{S4_Fig}).
-Moreover, after filtering out genes usually associated to recurrent adaptation (e.g. immune genes), we recover an even higher proportion of beneficial non-adaptive mutations (\nameref{S8_Table}).
+Importantly, we would usually expect adaptive convergent mutations to be linked to particular converging phenotypes across mammals, and hence, they should not massively affect the whole genome as we find (Fig~C and Table~D in~\nameref{S2_File}).
+Moreover, after filtering out genes usually associated to recurrent adaptation (e.g.
+immune genes), we recover an even higher proportion of beneficial non-adaptive mutations (Table~D in~\nameref{S4_File}).
 For these reasons, we argue that the signal of predictable positive selection we recover in extant population is indeed mainly driven by non-adaptive evolution.
@@
 q_{a \mapsto b}^{(i)} & = \mu_{a \mapsto b} \dfrac{F_b^{(i)} - F_a^{(i)}}{1 - \e^{F_a^{(i)} - F_b^{(i)}}} \text{ if codons $a$ and $b$ are non-synonymous}.
-\end{dcases}
+\end{dcases}\label{eq:subs}
 \end{equation}
@@
 Fitting the mutation-selection model on a multi-species sequence alignment leads to an estimation of the gene-wide $4 \times 4$ nucleotide mutation rate matrix ($\bm{\mu}$) as well as the $20$ amino-acid fitness landscape ($\bm{F^{(i)}}$) at each site $i$.
-The priors and full configuration of the model are given in section S1.
+The priors and full configuration of the model are given in~\nameref{S1_File} (section~1).
 From a technical perspective, the Bayesian estimation is a two-step procedure~\cite{rodrigue_bayesian_2008}.
@@
 \begin{equation}
-L_{\text{syn}} = L_{\text{tot}} \frac{\mu_{\text{syn}}}{\mu_{\text{tot}}}.
+L_{\text{syn}} = L_{\text{tot}} \frac{\mu_{\text{syn}}}{\mu_{\text{tot}}}.\label{eq:syn-opp}
 \end{equation}
@@
 Because a correlation must account for phylogenetic relationship and non-independence of samples, we fitted a Phylogenetic Generalized Linear Model in \textit{R} with the method \texttt{pgls} with default settings from the package \texttt{caper}~\cite{orme_caper_2013}.
-The mammalian dated tree was obtained from TimeTree~\cite{kumar_timetree_2017} and pruned to include only the species analysed in this study, with multi-furcation of the different populations from each species placed at the same divergence time as the species (section S4.1).
-
-\section*{Data availability}
-The data underlying this article are available at \url{https://doi.org/10.5281/zenodo.7878953}.
-Snakemake pipeline, analysis scripts and documentation are available at \href{https://github.com/ThibaultLatrille/SelCoeff}{github.com/ThibaultLatrille/SelCoeff}.
+The mammalian dated tree was obtained from TimeTree~\cite{kumar_timetree_2017} and pruned to include only the species analysed in this study, with multi-furcation of the different populations from each species placed at the same divergence time as the species (section~2.1 in~\nameref{S3_File}).
 
@@
 This study makes use of data generated by the NextGen Consortium.
-Funding:
-Université de Lausanne; Agence Nationale de la Recherche, Grant ANR-19-CE12-0019 / HotRec.
-
-\section*{Competing interests}
-The authors declare no conflicts of interest.
-
-\section*{Author information}
-Original idea: T.L.\ and J.J.;
-Model conception: T.L., J.J.\ and N.S.;
-Code: T.L.;
-Data analyses: T.L.\ and J.J.;
-Interpretation: T.L., J.J., D.A.H.\ and N.S.;
-First draft: T.L.\ and J.J.;
-Editing and revisions: T.L., J.J., D.A.H.\ and N.S.
-Project management and funding: N.S\@.
-
-\newpage
+
 \section*{Supporting information}
@@
 \label{S1_File}
-{\bf Supplementary appendix.} Contains 43 pages of supplementary information: model parameterization, supplementary figures (S1 Fig to S21 Fig) and supplementary tables (S1 Table to S15 Table).
-
-\subsection*{List of Figures}
-\paragraph*{S1 Fig.}
-\label{S1_Fig}
-{\bf Bayesian hierarchical model.}
-
-\paragraph*{S2 Fig.}
-\label{S2_Fig}
-{\bf Examples of $\bm{\SphyBen}$ mutation sites in \textit{Chlorocebus sabaeus} (reversions).}
-
-\paragraph*{S3 Fig.}
-\label{S3_Fig}
-{\bf Examples of $\bm{\SphyBen}$ mutation sites in \textit{Chlorocebus sabaeus}.}
-
-\paragraph*{S4 Fig.}
-\label{S4_Fig}
-{\bf Enrichment in $\bm{\SphyBen}$ SNPs across all gene ontology terms.}
-
-\paragraph*{S5 Fig.}
-\label{S5_Fig}
-{\bf Estimation of selection at the population scale for $\bm{\SphyDel}$ mutations.}
-
-\paragraph*{S6 Fig.}
-\label{S6_Fig}
-{\bf Estimation of selection at the population scale for $\bm{\SphyNeu}$ mutations.}
-
-\paragraph*{S7 Fig.}
-\label{S7_Fig}
-{\bf Estimation of selection at the population scale for $\bm{\SphyBen}$ mutations.}
-
-\paragraph*{S8 Fig.}
-\label{S8_Fig}
-{\bf Distribution of scaled selection coefficients ($\bm{\Sphy}$).}
-
-\paragraph*{S9 Fig.}
-\label{S9_Fig}
-{\bf Tree used for PGLM (Phylogenetic Generalized Linear Model).}
-
-\paragraph*{S10 Fig.}
-\label{S10_Fig}
-{\bf Relationship between the proportion of deleterious mutations ($\bm{\SpopDel}$) and effective population size.}
-
-\paragraph*{S11 Fig.}
-\label{S11_Fig}
-{\bf Relationship between the proportion of deleterious mutations ($\bm{\SpopNeu}$) and effective population size.}
-
-\paragraph*{S12 Fig.}
-\label{S12_Fig}
-{\bf Relationship between the proportion of deleterious mutations ($\bm{\SpopBen}$) and effective population size.}
-
-\paragraph*{S13 Fig.}
-\label{S13_Fig}
-{\bf $\bm{\proba[\SphyBen\given \SpopBen ]}$ as a function of distance to the sister species.}
-
-\paragraph*{S14 Fig.}
-\label{S14_Fig}
-{\bf Ratio of $\bm{\proba[\Sphy]}$ over $\bm{\proba[-\Sphy]}$ for polymorphisms of the African population of \textit{Homo sapiens}.}
-
-\paragraph*{S15 Fig.}
-\label{S15_Fig}
-{\bf Proportion of non-adaptive mutations among beneficial ones ($\bm{\proba{[}\SphyBen\given \SpopBen {]}}$) estimated on synthetic site-frequency spectra.}
-
-\paragraph*{S16 Fig.}
-\label{S16_Fig}
-{\bf Site-frequency spectrum when masking CpG transitions.}
-
-\paragraph*{S17 Fig.}
-\label{S17_Fig}
-{\bf Including substitutions in the terminal lineage to estimate $\bm{\Spop}$.}
-
-\paragraph*{S18 Fig.}
-\label{S18_Fig}
-{\bf $\bm{\proba[\SphyBen\given \SpopBen ]}$ when including divergence to estimate $\bm{\Spop}$, as a function of distance to the sister species.}
-
-\paragraph*{S19 Fig.}
-\label{S19_Fig}
-{\bf $\bm{\proba [ \SpopDel ]}$ when fitting a single or three DFEs.}
-
-\paragraph*{S20 Fig.}
-\label{S20_Fig}
-{\bf $\bm{\proba [ \SpopNeu ]}$ when fitting a single or three DFEs.}
-
-\paragraph*{S21 Fig.}
-\label{S21_Fig}
-{\bf $\bm{\proba [ \SpopBen ]}$ when fitting a single or three DFEs.}
-
-\newpage
-\subsection*{List of Tables}
-\paragraph*{S1 Table.}
-\label{S1_Table}
-{\bf Probability of mutations and substitutions to be $\bm{\SphyDel}$, $\bm{\SphyNeu}$ or $\bm{\SphyBen}$.}
-
-\paragraph*{S2 Table.}
-\label{S2_Table}
-{\bf $\bm{\dnds}$ for $\bm{\SphyDel}$, $\bm{\SphyNeu}$ or $\bm{\SphyBen}$.}
-
-\paragraph*{S3 Table.}
-\label{S3_Table}
-{\bf $\bm{\dnds}$ over-estimation due to non-adaptive beneficial mutations.}
-
-\paragraph*{S4 Table.}
-\label{S4_Table}
-{\bf Gene ontology enrichment in $\bm{\SphyBen}$ SNPs.}
-
-\paragraph*{S5 Table.}
-\label{S5_Table}
-{\bf Terms associated with deleterious mutations $\bm{\SphyDel}$.}
-
-\paragraph*{S6 Table.}
-\label{S6_Table}
-{\bf Terms associated with non-adaptive beneficial mutations $\bm{\SphyBen}$.}
-
-\paragraph*{S7 Table.}
-\label{S7_Table}
-{\bf Probability for beneficial mutations to be non-adaptive ($\bm{\proba[\SphyBen\given \SpopBen ]}$).}
-
-\paragraph*{S8 Table.}
-\label{S8_Table}
-{\bf $\bm{\proba[\SphyBen\given \SpopBen ]}$ when masking CpG transitions.}
-
-\paragraph*{S9 Table.}
-\label{S9_Table}
-{\bf Precision and recall when masking CpG transitions.}
-
-\paragraph*{S10 Table.}
-\label{S10_Table}
-{\bf $\bm{\proba[\SphyBen\given \SpopBen ]}$ excluding or not genes under adaptation.}
-
-\paragraph*{S11 Table.}
-\label{S11_Table}
-{\bf $\bm{\proba[\SphyBen\given \SpopBen ]}$ when including divergence to estimate $\bm{\Spop}$.}
-
-\paragraph*{S12 Table.}
-\label{S12_Table}
-{\bf Precision and recall when including divergence to estimate $\bm{\Spop}$.}
-
-\paragraph*{S13 Table.}
-\label{S13_Table}
-{\bf $\bm{\proba[\SphyBen\given \SpopBen ]}$ excluding or not genes under adaptation, when including divergence to estimate $\bm{\Spop}$.}
-
-\paragraph*{S14 Table.}
-\label{S14_Table}
-{\bf $\bm{\proba[\SphyBen\given \SpopBen ]}$ when using a discrete DFE to estimate $\bm{\Spop}$.}
-
-\paragraph*{S15 Table.}
-\label{S15_Table}
-{\bf Precision and recall when using a discrete DFE to estimate $\bm{\Spop}$.}
+{\bf Supplementary appendix on the parameterization of Mutation-selection codon models.} Contains 5 pages of supplementary information including 1 figure (Fig A).
+
+\paragraph*{S2 File.}
+\label{S2_File}
+{\bf Supplementary appendix on the caracterization of non-adaptive beneficial mutations.} Contains 12 pages of supplementary information including 3 figures (Fig A to C) and 6 tables (Table A to F).
+
+\paragraph*{S3 File.}
+\label{S3_File}
+{\bf Supplementary appendix on the contrast of selection at the phylogenetic and population-genetic scales.} Contains 7 pages of supplementary information including 8 figures (Fig A to H).
+
+\paragraph*{S4 File.}
+\label{S4_File}
+{\bf Supplementary appendix on controls for estimating the proportion of beneficial mutations that are not adaptive.} Contains 21 pages of supplementary information including 9 figures (Fig A to I) and 9 tables (Table A to I).
 

### 2024-12-16 manuscript/compile.sh

@@ -2,3 +2,4 @@ latexdiff main-PNAS.tex main-PNAS-revision.tex > diff-PNAS-revision.tex
 latexdiff main-PNAS-revision.tex main-PNAS-revision-2.tex > diff-PNAS-revision-2.tex
 latexdiff main-PLOS.tex main-PLOS-revision.tex > diff-PLOS-revision.tex
 latexdiff main-PLOS-revision-plos2015.tex main-PLOS-revision-2-plos2015.tex > diff-PLOS-revision-2.tex
+latexdiff main-PLOS-revision-2-plos2015.tex main-PLOS-revision-2-plos2015-formatting.tex > diff-PLOS-revision-2-formatting.tex

### 2024-12-27 manuscript/previous-versions/supp-mat-PLOS-revision.tex
Moved tex files into a single folder

--- 2024-06-19 manuscript/supp-mat.tex
@@
     Finally, for reproducibility, we generated the fasta alignment for all $\SphyBen$ mutations that we detected, either in the terminal lineage or in segregating polymorphism.
-    These fasta files are available at Zenodo (\url{https://doi.org/10.5281/zenodo.7878953}), across all populations, under the compressed archive \textit{alignment\_focused\_around\_non\_adaptive\_mutations.zip} and we provide a python script to obtain the figures shown below given these alignments.
+    These fasta files are available at Zenodo (\url{https://doi.org/10.5281/zenodo.7878953}), across all populations, under a zip file (\textit{alignment\_around\_non\_adaptive\_mutations.zip}) and we provide a python script to obtain the figures shown below given these alignments (\textit{plot\_variations.py}).
 
@@
 
+    \section{Contrasting selection at the phylogenetic and population-genetic scale}
+
+    \subsection{Selection at the population-genetic scale}
+    The proportion of deleterious ($\ProbaPopDel$), nearly-neutral ($\ProbaPopNeu$) and of beneficial ($\ProbaPopBen$) mutations estimated at the population-genetic scale across the different populations is shown for each class of selection ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$).
+
+    \captionof{figure}{Estimation of selection at the population scale for $\SphyDel$ mutations.}
+    \begin{center}
+        \begin{minipage}{0.75\linewidth}
+            \begin{minipage}{0.9\linewidth}
+                \includegraphics[width=\linewidth, page=1]{artworks/Theta.neg.stacked.pdf}
+            \end{minipage}
+            \begin{minipage}{0.09\linewidth}
+                \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
+            \end{minipage}
+        \end{minipage}
+    \end{center}
+
+    \captionof{figure}{Estimation of selection at the population scale for $\SphyNeu$ mutations.}
+    \begin{center}
+        \begin{minipage}{0.75\linewidth}
+            \begin{minipage}{0.9\linewidth}
+                \includegraphics[width=\linewidth, page=1]{artworks/Theta.weak.stacked.pdf}
+            \end{minipage}
+            \begin{minipage}{0.09\linewidth}
+                \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
+            \end{minipage}
+        \end{minipage}
+    \end{center}
+
+    \captionof{figure}{Estimation of selection at the population scale for $\SphyBen$ mutations.}
+    \begin{center}
+        \begin{minipage}{0.75\linewidth}
+            \begin{minipage}{0.9\linewidth}
+                \includegraphics[width=\linewidth, page=1]{artworks/Theta.pos.stacked.pdf}
+            \end{minipage}
+            \begin{minipage}{0.09\linewidth}
+                \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
+            \end{minipage}
+        \end{minipage}
+    \end{center}
+
+    \newpage
+    \subsection{Distribution of scaled selection coefficients ($\Sphy$)}\label{subsec:expectedDFE}
+
+    Theoretically, the selection coefficient ($\Sphy$) for any mutation is related to its probability of fixation by the equation $\proba_{\text{fix}} (\Sphy) = \Sphy/(1-\exp(-\Sphy)) $.
+    It is thus possible to predict the distribution of $\Sphy$ of substitutions given the distribution of $\Sphy$ for mutations (e.g.
+panel A below) by weighting the different mutations by their $\proba_{\text{fix}} (\Sphy)$.
+    The predicted DFE of substitutions (panel B below) matches the observed DFE of substitutions (panel C below) in the terminal lineage, meaning that the $\Sphy$ obtained by phylogenetic mutation-selection codon models is a strong predictor of selection effectively exerted on mutations in terminal lineages.
+
+    The figures shown below are obtained in the Saint Kitts population of \textit{Chlorocebus sabaeus}.
+    These figures across the 28 populations are available at Zenodo (\url{https://doi.org/10.5281/zenodo.7878953}) in file \textit{distribution\_S0\_28\_populations.pdf}.\\
+
+    \captionof{figure}{Distribution of scaled selection coefficients ($\Sphy$).}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny A: Expected DFE for mutations}
+        \includegraphics[width=\linewidth, page=1]{artworks/DFE.Chlorocebus_sabaeus.Saint_Kitts.MutSel.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny B: Expected DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{artworks/DFE.Chlorocebus_sabaeus.Saint_Kitts.MutSel.Flow.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny C: Observed DFE for substitutions}
+        \includegraphics[width=\linewidth, page=1]{artworks/subs.Chlorocebus_sabaeus.Saint_Kitts.bins3Mask0.9.pdf}
+    \end{minipage}
+    \\
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny D: Observed DFE for polymorphisms}
+        \includegraphics[width=\linewidth, page=1]{artworks/poly.Chlorocebus_sabaeus.Saint_Kitts.bins3Mask0.9.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny E: Site frequency spectrum}
+        \includegraphics[width=\linewidth, page=1]{artworks/Chlorocebus_sabaeus.Saint_Kitts.MutSel-sfs.normalize.pdf}
+    \end{minipage}
+    \begin{minipage}{0.32\linewidth}
+        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
+        \includegraphics[width=\linewidth, page=1]{artworks/Chlorocebus_sabaeus.Saint_Kitts.MutSel.polyDFE_C.pdf}
+    \end{minipage}
+
+    \small
+    \begin{itemize}[itemsep=0pt]
+        \item A: Distribution of scaled selection coefficients ($\Sphy$), predicted for all possible non-synonymous DNA mutations away from the ancestral exome.
+        Mutations are divided into three classes of selection: deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial non-adaptive ($\SphyBen$).
+        \item B: Expected distribution of $\Sphy$ for substitutions obtained by transforming the distribution of $\Sphy$ for mutations (panel A) by weighting each mutation by its scaled probability of fixation given by $\proba_{\text{fix}} (\Sphy) = \Sphy/(1-\exp(-\Sphy))$.
+        \item C: Distribution of scaled selection coefficients ($\Sphy$) for all observed substitutions along the terminal branch of the phylogenetic tree.
+        \item D: Distribution of scaled selection coefficients ($\Sphy$) for all observed polymorphisms currently segregating in the population.
+        \item E: The site-frequency spectrum (SFS) in the population for a random sample of 16 alleles (means in solid lines and standard deviations in color shades) for each class of selection and for synonymous mutations, supposedly neutral (black).
+The SFS represents the proportion of mutations (y-axis) with a given number of derived alleles in the population (x-axis).
+At high frequencies, deleterious mutations are underrepresented.
+        \item F: Proportion of beneficial $\ProbaPopDel$, nearly-neutral $\ProbaPopNeu$, and deleterious mutations $\ProbaPopBen$  estimated at the population scale for each class of selection at the phylogenetic scale.
+Proportions depicted here are not weighted by their mutational opportunities.
+    \end{itemize}
+    \normalsize
+
+    \newpage
     \section{Correlation with diversity}
@@
     \newpage
-    \section{Excluding genes under adaptation}
-
-    \subsection{Probability for beneficial mutations to be non-adaptive}
-    \begin{center}
-        \captionof{table}{$\proba[\SphyBen\given \SpopBen ]$ excluding or not genes under adaptation.}
-        \begin{tabular}{|l|l|r|r|}
-            \toprule
-            Population & Species & Control & Case \\
-            \midrule
-            \rowcolor{LIGHTGREY} Equus c. & Equus caballus & $ 0.536$ & $ 0.880$ \\
-            Iran & Bos taurus & $ 0.243$ & $ 0.249$ \\
-            Uganda & Bos taurus & $ 0.415$ & $ 0.429$ \\
-            \rowcolor{LIGHTGREY} Australia & Capra hircus & $ 0.177$ & $ 0.190$ \\
-            \rowcolor{LIGHTGREY} France & Capra hircus & $ 0.190$ & $ 0.201$ \\
-            \rowcolor{LIGHTGREY} Iran (C. aegagrus) & Capra hircus & $ 0.165$ & $ 0.169$ \\
-            \rowcolor{LIGHTGREY} Iran & Capra hircus & $ 0.193$ & $ 0.176$ \\
-            \rowcolor{LIGHTGREY} Italy & Capra hircus & $ 0.243$ & $ 0.261$ \\
-            \rowcolor{LIGHTGREY} Morocco & Capra hircus & $ 0.245$ & $ 0.283$ \\
-            \rowcolor{LIGHTGREY} Iran & Ovis aries & $ 0.407$ & $ 0.454$ \\
-            Iran (O. orientalis) & Ovis aries & $ 0.190$ & $ 0.207$ \\
-            Iran (O. vignei) & Ovis aries & $ 0.110$ & $ 0.135$ \\
-            Various & Ovis aries & $ 0.222$ & $ 0.246$ \\
-            Morocco & Ovis aries & $ 0.514$ & $ 0.627$ \\
-            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus & $ 0.293$ & $ 0.325$ \\
-            \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus & $ 0.275$ & $ 0.273$ \\
-            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus & $ 0.245$ & $ 0.242$ \\
-            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus & $ 0.821$ & $ 0.873$ \\
-            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus & $ 0.257$ & $ 0.254$ \\
-            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus & $ 0.358$ & $ 0.395$ \\
-            \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus & $ 0.341$ & $ 0.375$ \\
-            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus & $ 0.336$ & $ 0.355$ \\
-            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus & $ 0.250$ & $ 0.263$ \\
-            African & Homo sapiens & $ 0.349$ & $ 0.363$ \\
-            Admixed American & Homo sapiens & $ 0.345$ & $ 0.312$ \\
-            East Asian & Homo sapiens & $ 0.249$ & $ 0.233$ \\
-            European & Homo sapiens & $ 0.248$ & $ 0.211$ \\
-            South Asian & Homo sapiens & $ 0.224$ & $ 0.218$ \\
-            \bottomrule
-        \end{tabular}
-    \end{center}
-    Genes under adaptation retrieved from \textcite{latrille_genes_2023}.
-    Comparison of $\proba[\SphyBen\given \SpopBen ]$ for the whole genome (control) and when excluding genes under adaptation (case).
-    The non-parametric Wilcoxon signed-rank test evaluates the null hypothesis that the distribution of the differences (case versus control) is symmetric about zero.
-    Applied to the paired samples (case and control), Wilcoxon signed-rank test results in $s=80$ with $\pvalue=0.002$, for the one-sided test (case higher than control).
-    The proportion of non-adaptive beneficial mutations ($\proba[\SphyBen\given \SpopBen ]$) is higher when excluding genes under adaptation, consistent with our expectation that genes with uniformly conserved functions should fit better the nearly-neutral equilibrium model.
-
-    \newpage
-
-    \section{Contrasting selection at the phylogenetic and population-genetic scale}
-
-    \subsection{Selection at the population-genetic scale}
-    The proportion of deleterious ($\ProbaPopDel$), nearly-neutral ($\ProbaPopNeu$) and of beneficial ($\ProbaPopBen$) mutations estimated at the population-genetic scale across the different populations is shown for each class of selection ($\Sphyclass \in \{\SphyDel, \SphyNeu, \SphyBen \}$).
-
-    \captionof{figure}{Estimation of selection at the population scale for $\SphyDel$ mutations.}
-    \begin{center}
-        \begin{minipage}{0.75\linewidth}
-            \begin{minipage}{0.9\linewidth}
-                \includegraphics[width=\linewidth, page=1]{artworks/Theta.neg.stacked.pdf}
-            \end{minipage}
-            \begin{minipage}{0.09\linewidth}
-                \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
-            \end{minipage}
-        \end{minipage}
-    \end{center}
-
-    \captionof{figure}{Estimation of selection at the population scale for $\SphyNeu$ mutations.}
-    \begin{center}
-        \begin{minipage}{0.75\linewidth}
-            \begin{minipage}{0.9\linewidth}
-                \includegraphics[width=\linewidth, page=1]{artworks/Theta.weak.stacked.pdf}
-            \end{minipage}
-            \begin{minipage}{0.09\linewidth}
-                \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
-            \end{minipage}
-        \end{minipage}
-    \end{center}
-
-    \captionof{figure}{Estimation of selection at the population scale for $\SphyBen$ mutations.}
-    \begin{center}
-        \begin{minipage}{0.75\linewidth}
-            \begin{minipage}{0.9\linewidth}
-                \includegraphics[width=\linewidth, page=1]{artworks/Theta.pos.stacked.pdf}
-            \end{minipage}
-            \begin{minipage}{0.09\linewidth}
-                \includegraphics[width=\linewidth, page=1]{artworks/legend.polycat}
-            \end{minipage}
-        \end{minipage}
-    \end{center}
-
-    \newpage
-    \subsection{Distribution of scaled selection coefficients ($\Sphy$)}\label{subsec:expectedDFE}
-
-    Theoretically, the selection coefficient ($\Sphy$) for any mutation is related to its probability of fixation by the equation $\proba_{\text{fix}} (\Sphy) = \Sphy/(1-\exp(-\Sphy)) $.
-    It is thus possible to predict the distribution of $\Sphy$ of substitutions given the distribution of $\Sphy$ for mutations (e.g.
-panel A below) by weighting the different mutations by their $\proba_{\text{fix}} (\Sphy)$.
-    The predicted DFE of substitutions (panel B below) matches the observed DFE of substitutions (panel C below) in the terminal lineage, meaning that the $\Sphy$ obtained by phylogenetic mutation-selection codon models is a strong predictor of selection effectively exerted on mutations in terminal lineages.
-
-    The figures shown below are obtained in the Saint Kitts population of \textit{Chlorocebus sabaeus}.
-    These figures across the 28 populations are available at Zenodo (\url{https://doi.org/10.5281/zenodo.7878953}) in file \textit{distribution\_S0\_28\_populations.pdf}.\\
-
-    \captionof{figure}{Distribution of scaled selection coefficients ($\Sphy$).}
-    \begin{minipage}{0.32\linewidth}
-        \flushleft {\tiny A: Expected DFE for mutations}
-        \includegraphics[width=\linewidth, page=1]{artworks/DFE.Chlorocebus_sabaeus.Saint_Kitts.MutSel.pdf}
-    \end{minipage}
-    \begin{minipage}{0.32\linewidth}
-        \flushleft {\tiny B: Expected DFE for substitutions}
-        \includegraphics[width=\linewidth, page=1]{artworks/DFE.Chlorocebus_sabaeus.Saint_Kitts.MutSel.Flow.pdf}
-    \end{minipage}
-    \begin{minipage}{0.32\linewidth}
-        \flushleft {\tiny C: Observed DFE for substitutions}
-        \includegraphics[width=\linewidth, page=1]{artworks/subs.Chlorocebus_sabaeus.Saint_Kitts.bins3Mask0.9.pdf}
-    \end{minipage}
-    \\
-    \begin{minipage}{0.32\linewidth}
-        \flushleft {\tiny D: Observed DFE for polymorphisms}
-        \includegraphics[width=\linewidth, page=1]{artworks/poly.Chlorocebus_sabaeus.Saint_Kitts.bins3Mask0.9.pdf}
-    \end{minipage}
-    \begin{minipage}{0.32\linewidth}
-        \flushleft {\tiny E: Site frequency spectrum}
-        \includegraphics[width=\linewidth, page=1]{artworks/Chlorocebus_sabaeus.Saint_Kitts.MutSel-sfs.normalize.pdf}
-    \end{minipage}
-    \begin{minipage}{0.32\linewidth}
-        \flushleft {\tiny F: $S$ as function of $S_0$ for each class}
-        \includegraphics[width=\linewidth, page=1]{artworks/Chlorocebus_sabaeus.Saint_Kitts.MutSel.polyDFE_C.pdf}
-    \end{minipage}
-
-    \small
-    \begin{itemize}[itemsep=0pt]
-        \item A: Distribution of scaled selection coefficients ($\Sphy$), predicted for all possible non-synonymous DNA mutations away from the ancestral exome.
-        Mutations are divided into three classes of selection: deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) and beneficial non-adaptive ($\SphyBen$).
-        \item B: Expected distribution of $\Sphy$ for substitutions obtained by transforming the distribution of $\Sphy$ for mutations (panel A) by weighting each mutation by its scaled probability of fixation given by $\proba_{\text{fix}} (\Sphy) = \Sphy/(1-\exp(-\Sphy))$.
-        \item C: Distribution of scaled selection coefficients ($\Sphy$) for all observed substitutions along the terminal branch of the phylogenetic tree.
-        \item D: Distribution of scaled selection coefficients ($\Sphy$) for all observed polymorphisms currently segregating in the population.
-        \item E: The site-frequency spectrum (SFS) in the population for a random sample of 16 alleles (means in solid lines and standard deviations in color shades) for each class of selection and for synonymous mutations, supposedly neutral (black).
-The SFS represents the proportion of mutations (y-axis) with a given number of derived alleles in the population (x-axis).
-At high frequencies, deleterious mutations are underrepresented.
-        \item F: Proportion of beneficial $\ProbaPopDel$, nearly-neutral $\ProbaPopNeu$, and deleterious mutations $\ProbaPopBen$  estimated at the population scale for each class of selection at the phylogenetic scale.
-Proportions depicted here are not weighted by their mutational opportunities.
+    \subsection{Simulations of site-frequency spectra}
+
+    We performed simulations based on population-genetic formalism to test whether our approach is able to recover the proportion of beneficial mutations that are non-adaptive in synthetic polymorphism datasets.
+    More specifically, we performed simulations of site-frequency spectra, thus at the population-genetic scale, by using a mixture of the DFEs that is predicted from the phylogenetic mutation-selection model, and adding adaptive mutations to this DFE.
+    In practice, simulations are performed under the Poisson Random Field (PRF) framework of population genetics\cite{sawyer_population_1992}.
+    Each simulation generates a synthetic synonymous SFS, and a synthetic non-synonymous SFS for the mutations in the category $x \in \{ \SphyDel, \SphyNeu, \SphyBen \}$.
+
+    Technically, for non-synonymous mutations, we first draw a random sample of the selection coefficients from the mixture of DFE using as parameter $\proba [y \given x]$ for $y \in \{ \SpopDel, \SpopNeu, \SpopBen \}$.
+    Importantly, $\proba [\SpopBen | \SphyDel]$ and $\proba [\SpopBen | \SphyNeu]$ are considered adaptive mutations, and thus their selection coefficients have a selection coefficient of $S_{\text{adaptive}}=10$.
+    All the others are drawn for the DFEs that are predicted from the phylogenetic mutation-selection model.
+    Synonymous mutations are considered neutral and have $S=0$.
+
+    Given these selection coefficients, to obtain the expected SFS we integrate over the limiting density of frequency that mutations are segregating in the population, as described from eqs.
+1--2 in \textcite{tataru_inference_2017}.
+    And finally, given this expected SFS, we perform a Poisson random sampling to obtain a sampled SFS of size n matching the total number of polymorphism to simulate.
+
+    In summary, the simulations generates a synonymous SFS, and a non-synonymous SFS for the mutations in the category $x \in \{ \SphyDel, \SphyNeu, \SphyBen \}$, and require as input the following:
+    \begin{itemize}
+        \item Total number of polymorphisms to simulate (synonymous and non-synonymous).
+        \item The DFE of $\Sphy$ predicted from the phylogenetic mutation-selection.
+        \item Estimates of $\proba [y \given x]$ for $y \in \{ \SpopDel, \SpopNeu, \SpopBen \}$.
+        \item Selection coefficient for adaptive mutations, here $S_{\text{adaptive}}=20$.
+        \item The sampled SFS size $n$, here $n=16$ (i.e.\ twice the number of sampled individuals).
     \end{itemize}
-    \normalsize
+
+    From these two SFS (synonymous and non-synonymous), we run polyDFE to obtain $\proba [\SpopDel \given x]$, $\proba [\SpopNeu \given x]$ and $\proba [\SpopBen \given x]$ (eqs.\ 9--11 in the main manuscript).
+    By doing so for the 3 categories $x \in \{ \SphyDel, \SphyNeu, \SphyBen \}$, we can ultimately compute $\proba [\SphyBen \given \SpopBen]$ (eqs.\ 14--15 in the main manuscript), which can be then be compared to the ground truth.
+
+    \newpage
+    \begin{center}
+        \captionof{figure}{Simulations of site-frequency spectra.}
+        \includegraphics[width=\linewidth, page=1]{artworks/simulations.pos.pdf}
+    \end{center}
+
+    We used 8 different set of parameters ($\proba [y \given x]$ and numbers of polymorphism) and simulated 10 replicates for each set of parameters.
+    These set of input parameters are provided to match $\proba [\SphyBen \given \SpopBen]$ of the following populations: Set 1 for Admixed American (Homo sapiens), Set 2 for African (Homo sapiens), Set 3 for Nevis (Chlorocebus sabaeus), Set 4 for Iran (Ovis orientalis), Set 5 for Uganda (Bos taurus), Set 6 for Morocco (Ovis aries), Set 7 for Equus caballus, Set 8 for Gambia (Chlorocebus sabaeus).
+    For each synthetic data we run polyDFE and derived $\proba [\SphyBen \given \SpopBen]$ which is then compared to the ground truth (calculated analytically from the set parameters $\proba [y \given x], x \in \{ \SphyDel, \SphyNeu, \SphyBen \}, y \in \{ \SpopDel, \SpopNeu, \SpopBen \}$).
+    These simulations show that we are able to retrieve accurately the proportion of non-adaptive mutations in those synthetic datasets.
+
+    \newpage
 
@@
     \newpage
-    \section{Including divergence data for the estimation of $\Spop$}
-
-    \subsection{Including divergence in polyDFE}
+
+    \section{Excluding genes under adaptation}
+
+    \subsection{Probability for beneficial mutations to be non-adaptive}
+    \begin{center}
+        \captionof{table}{$\proba[\SphyBen\given \SpopBen ]$ excluding or not genes under adaptation.}
+        \begin{tabular}{|l|l|r|r|}
+            \toprule
+            Population & Species & Control & Case \\
+            \midrule
+            \rowcolor{LIGHTGREY} Equus c. & Equus caballus & $ 0.536$ & $ 0.880$ \\
+            Iran & Bos taurus & $ 0.243$ & $ 0.249$ \\
+            Uganda & Bos taurus & $ 0.415$ & $ 0.429$ \\
+            \rowcolor{LIGHTGREY} Australia & Capra hircus & $ 0.177$ & $ 0.190$ \\
+            \rowcolor{LIGHTGREY} France & Capra hircus & $ 0.190$ & $ 0.201$ \\
+            \rowcolor{LIGHTGREY} Iran (C. aegagrus) & Capra hircus & $ 0.165$ & $ 0.169$ \\
+            \rowcolor{LIGHTGREY} Iran & Capra hircus & $ 0.193$ & $ 0.176$ \\
+            \rowcolor{LIGHTGREY} Italy & Capra hircus & $ 0.243$ & $ 0.261$ \\
+            \rowcolor{LIGHTGREY} Morocco & Capra hircus & $ 0.245$ & $ 0.283$ \\
+            \rowcolor{LIGHTGREY} Iran & Ovis aries & $ 0.407$ & $ 0.454$ \\
+            Iran (O. orientalis) & Ovis aries & $ 0.190$ & $ 0.207$ \\
+            Iran (O. vignei) & Ovis aries & $ 0.110$ & $ 0.135$ \\
+            Various & Ovis aries & $ 0.222$ & $ 0.246$ \\
+            Morocco & Ovis aries & $ 0.514$ & $ 0.627$ \\
+            \rowcolor{LIGHTGREY} Barbados & Chlorocebus sabaeus & $ 0.293$ & $ 0.325$ \\
+            \rowcolor{LIGHTGREY} Central Afr. Rep. & Chlorocebus sabaeus & $ 0.275$ & $ 0.273$ \\
+            \rowcolor{LIGHTGREY} Ethiopia & Chlorocebus sabaeus & $ 0.245$ & $ 0.242$ \\
+            \rowcolor{LIGHTGREY} Gambia & Chlorocebus sabaeus & $ 0.821$ & $ 0.873$ \\
+            \rowcolor{LIGHTGREY} Kenya & Chlorocebus sabaeus & $ 0.257$ & $ 0.254$ \\
+            \rowcolor{LIGHTGREY} Nevis & Chlorocebus sabaeus & $ 0.358$ & $ 0.395$ \\
+            \rowcolor{LIGHTGREY} South Africa & Chlorocebus sabaeus & $ 0.341$ & $ 0.375$ \\
+            \rowcolor{LIGHTGREY} Saint Kitts & Chlorocebus sabaeus & $ 0.336$ & $ 0.355$ \\
+            \rowcolor{LIGHTGREY} Zambia & Chlorocebus sabaeus & $ 0.250$ & $ 0.263$ \\
+            African & Homo sapiens & $ 0.349$ & $ 0.363$ \\
+            Admixed American & Homo sapiens & $ 0.345$ & $ 0.312$ \\
+            East Asian & Homo sapiens & $ 0.249$ & $ 0.233$ \\
+            European & Homo sapiens & $ 0.248$ & $ 0.211$ \\
+            South Asian & Homo sapiens & $ 0.224$ & $ 0.218$ \\
+            \bottomrule
+        \end{tabular}
+    \end{center}
+    Genes under adaptation retrieved from \textcite{latrille_genes_2023}.
+    Comparison of $\proba[\SphyBen\given \SpopBen ]$ for the whole genome (control) and when excluding genes under adaptation (case).
+    The non-parametric Wilcoxon signed-rank test evaluates the null hypothesis that the distribution of the differences (case versus control) is symmetric about zero.
+    Applied to the paired samples (case and control), Wilcoxon signed-rank test results in $s=80$ with $\pvalue=0.002$, for the one-sided test (case higher than control).
+    The proportion of non-adaptive beneficial mutations ($\proba[\SphyBen\given \SpopBen ]$) is higher when excluding genes under adaptation, consistent with our expectation that genes with uniformly conserved functions should fit better the nearly-neutral equilibrium model.
+
+    \newpage
+
+    \section{Including substitutions in the terminal lineage to estimate $\Spop$}
+
+    \captionof{figure}{Including substitutions in the terminal lineage to estimate $\Spop$.}
+    \includegraphics[width=\textwidth, page=1] {artworks/figure.method.proba.div.pdf}
+    Same as figure 2 in the main text, but including substitutions in the terminal lineage to estimate $\Spop$.
+    At the phylogenetic scale (A), we estimated the amino-acid fitness for each site from protein-coding DNA alignments using mutation-selection codon models.
+    For every possible mutation, the difference in amino-acid fitness before and after the mutation allows us to compute the selection coefficient at the phylogenetic scale ($\Sphy$).
+    Depending on $\Sphy$ (B) mutations can be predicted as deleterious ($\SphyDel$), nearly-neutral ($\SphyNeu$) or beneficial non-adaptive mutations ($\SphyBen$) toward a fitter amino acid and repairing existing functions.
+    For each population, each observed single nucleotide polymorphism (SNP) segregating can also be classified according to its $\Sphy$ value (C).
+    Within the terminal lineage leading to this population, each substitution can be classified according to its $\Spop$ value (C).
+    Non-synonymous polymorphisms and divergence, contrasted to synonymous polymorphisms and divergence (deemed neutral) is used to estimate selection coefficients (D-E) at the population scale ($\Spop$), for each class of selection ($\SphyDel$, $\SphyNeu$, $\SphyBen$).
+    We can thus assess whether $\Sphy$ predicts $\Spop$ and compute \textit{precision} (F) and \textit{recall} (G) for each class.
+    The \textit{recall} value for class $\SphyBen$ is the probability for beneficial mutations to be non-adaptive (G).
+
+    \subsection{Including substitutions in polyDFE}
     Divergence data (number of substitutions per site) can also be included into polyDFE to estimate the DFE.
@@
 
+    \newpage
     \subsection{Probability for beneficial mutations to be non-adaptive}
@@
     \newpage
-
-    \section{Discrete distribution of $\Spop$ at the population scale}
-
-    \subsection{polyDFE model D (discrete distribution)}
+    \subsection{Fitting one or three distributions of fitness effects}
+
+    We also performed another test to assess that fitting the same functional form of DFE (distribution of fitness effects) to three categories of selection (i.e.
+$\SphyDel, \SphyNeu, \SphyBen$) is a sound methodology.
+    Typically, $\proba [ \SpopBen ]$ can be computed from two different estimates, by either splitting data (polymorphism within populations and substitutions in the terminal lineages) in three category (i.e.
+$\SphyDel, \SphyNeu, \SphyBen$) or not at all.
+    In the case of splitting data in three categories and fitting three DFE, $\proba [ \SpopBen ]$ is obtained by summing over the three category using the law of total probability (eq.\ 15 in the main manuscript):
+
+    \begin{equation}
+        \proba [ \SpopBen ] \text{ (three DFE) } = \proba [\SpopBen \given \SphyDel ] \times \proba [\SphyDel ] + \proba [\SpopBen \given \SphyNeu ] \times \proba [\SphyNeu ] + \proba [\SpopBen \given \SphyBen ] \times \proba [\SphyBen ].
+        \label{eq:total_proba}
+    \end{equation}
+
+    But it is also possible to compute $\proba [ \SpopBen ]$ directly from fitting one DFE to the full data (polymorphism within populations and substitutions in the terminal lineages), not splitting at all, and then $\proba [ \SpopBen ]$ is obtained from the parameters of the DFE (eq.\ 11 in the main manuscript):
+    \begin{align}
+        \proba [ \SpopBen ] \text{ (one DFE) } &= \proba [ \Spop > 1 ] = p_b \int_{1}^{+\infty} f_{e}(\Spop; \AdvMean) \der \Spop. \label{eq:polyProbaAdv}
+    \end{align}
+
+    We reproduced this experiment for $\proba [ \SpopDel ]$, $\proba [ \SpopNeu ]$ and $\proba [ \SpopBen ]$ as shown below.
+    The goodness of fit is calculated as the coefficient of determination ($R^2$) for the prediction $\proba [ \SpopBen ] \text{ (three DFE) } = \proba [ \SpopBen ] \text{ (one DFE) }$, meaning calculating the residuals of the fit to the 1:1 line.
+
+    \newpage
+    \begin{center}
+        \captionof{figure}{$\proba [ \SpopDel ]$ when fitting a single or three DFEs.}
+        \includegraphics[width=0.75\linewidth, page=1]{artworks/results.reg.neg.div.scatter.pdf}
+    \end{center}
+    \begin{center}
+        \captionof{figure}{$\proba [ \SpopNeu ]$ when fitting a single or three DFEs.}
+        \includegraphics[width=0.75\linewidth, page=1]{artworks/results.reg.weak.div.scatter.pdf}
+    \end{center}
+    \begin{center}
+        \captionof{figure}{$\proba [ \SpopBen ]$ when fitting a single or three DFEs.}
+        \includegraphics[width=0.75\linewidth, page=1]{artworks/results.reg.pos.div.scatter.pdf}
+    \end{center}
+
+    \newpage
+
+    \section{Non-parametric distribution of fitness effects}
+
+    \subsection{polyDFE model D (non-parametric)}
     Additionally to including divergence, with also tested our prediction with polyDFE model D instead of model C.
@@
     Altogether, comparing this table other estimations, we acknowledge that the exact proportion of non-adaptive among all beneficial ones is dependent on the model used to estimate the DFE.
-    However, we can still see that non-adaptive beneficial mutations are positively selected compared to neutral and deleterious ones, and this result is not sensitive to the underlying DFE at the population scale.
-
-    \newpage
+    However, we can still see that non-adaptive beneficial mutations are positively selected compared to neutral and deleterious ones, and this result is valid for different underlying DFE.
 
